### 2014-01-16 Studies/Chicago_2012/Report/Chicago_Fire.tex
Add case study on Chicago fire from 2012

\documentclass[11pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../../Bibliography/commoncommands}

% Rename chapter headings
\renewcommand{\chaptername}{Section}
\renewcommand{\bibname}{References}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

\begin{document}

\bibliographystyle{unsrt}
\pagestyle{empty}

\begin{minipage}[t][9in][s]{6.25in}

\headerB{
Simulation of the Dynamics of an \\
Attic Fire in a 2 1/2 Story Wood \\
Frame Residential Structure \\
Chicago, IL \\
}

\headerC{
\flushright{
Craig G. Weinschenk \\
Daniel Madrzykowski \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

\flushright{\today \\
}

\vfill

\flushright{
\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}

\titlesigs

\end{minipage}

\newpage

\frontmatter

\pagestyle{plain}
\pagenumbering{roman}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\chapter{List of Acronyms}

\begin{tabbing}
\hspace{1.5in} \= \\
BC \> Battalion Chief \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
NIST \> National Institute of Standards and Technology \\
SFPE \> Society of Fire Protection Engineers \\
\end{tabbing}

\mainmatter

\chapter{Introduction}

\chapter{Fire Incident Summary}
The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \cite{NIOSH:Bowyer}.

On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a death of a fire captain and injury to a fire fighter.  At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.   Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.  After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.  Engine 123 arrived on scene at approximately 5:19. The victims were part of the Engine 123 crew.  The BC met the Captain and the Fire Fighter (victims) at the front door to the structure.  Then the Captain and Fire Fighter took their hose line to the second floor of the structure.  At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.   Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL 39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.   The fire fighter from TL 39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.   Both doors remain open and the fire fighter from TL 39 exits the structure.  Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 5:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.  No response was made by the Engine 123 Captain.  It is believed that the door between the rear porch and the second floor hallway, where the Engine 123 Captain and Fire Fighter were located may have failed by this time.  Approximately a minute later Engine 49 applied water to the fire in the attic.

Squad 5 entered the front of the structure at approximately 5:25 and headed to the second floor.  They heard a commotion and found the Engine 123 Captain collapsed on the kitchen floor and entangled with the Engine 123 firefighter.  A Mayday was called on the radio by Squad 5 at approximately  5:27 and the Engine 123 Captain was removed from the front of the building at approximately 5:29 and succumbed to his injuries at the hospital at 5:38.

\begin{table}
\centering
\caption{Fire and Simulation Event Timeline}
\vskip.5\baselineskip
\begin{tabular}{|c|c|c|}
\hline
Fire Time & Simulation Time & Action  \\
\hline \hline
        &        & Reported working fire with heavy smoke\\
5:17    &        & coming from the front and rear of the \\
        &        & structure's attic. \\ \hline
        &  0:00  & Simulation begins. Attic fire ignites. Initial \\ 
        &        & self ventilation on charlie side. \\ \hline
        &  0:20  & Front door opens. \\ \hline
5:20    &  0:40  & Attic self ventilation - heavy smoke reported. Porch fire ignites. \\ \hline
        &  0:45  & Additional self ventilation on charlie side. \\ \hline
        &  0:55  & Self ventilation on beta side. \\ \hline        
5:21:00 &        & Engine 123 Capt. and FF on 2$^{nd}$ floor. \\ \hline
        &        & Rear Exterior $-$ 1$^{st}$ floor door to enclosed \\
5:21:30 &  2:10  & porch opened, fire in rear porch begins to \\
        &        & increase HRR. \\ \hline
        &  2:15  & Additional self ventilation on beta side. \\ \hline        
        &  2:40  & Top of interior door fails. \\ \hline
5:23    & $\approx$ 3:40       & No response from Engine 123: Capt. or FF. \\ \hline
5:24    &  N/A   & Water applied to attic from the rear exterior position. \\ \hline
        &  5:00  & Simulation ends. \\ \hline
\end{tabular}
\label{tab:fires}
\end{table}

\chapter{Fire Dynamics Simulator and Smokeview}
FDS is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.  Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.  The cells are contained together within one larger volume known as a computational domain.  The CFD model computes the density, velocity, temperature, pressure and species concentration of the gas in each cell.  Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.  FDS can utilize material properties of the furnishings, walls, floors, and ceilings to compute fire growth and spread.  One of the most important advantages of FDS is that it is verified and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Verification_Guide,FDS_Validation_Guide}.  A complete description of the FDS model is given in reference \cite{FDS_Tech_Guide}.

Smokeview is a software tool designed to visualize the results of the FDS \cite{Smokeview_Users_Guide}.  Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (92D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.  Smokeview allows the fire and fire movement to be visualized.  This is done by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.  Smokeview also visualizes static data at particular times using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.

\chapter{Model Input Parameters}
Input data from a number of sources must be collected and documented in order to simulate a fire with FDS or any other model. 
From the fire scene the following information must be gathered:
\begin{itemize}
\item The geometry of the building and the compartments being modeled.
\item The size and location of exterior and interior ventilation openings. 
\item Documentation and identification of the fuels used in the construction and finish of the building and their installed location
\item Documentation and identification of the fuels used as the contents of the building. 
\item Area of origin and approximate size of ignition source.
\item Documentation of fire damage to the building, fuel loads, victims or equipment.
\end{itemize}
From witnesses, first responders, reports, and recorded media such as fire ground radios or videos:
\begin{itemize}
\item Information on the timing of the fire development
\item Order and timing of ventilation opening to the outside
\item Weather conditions at the time of the fire
\end{itemize}
To develop the simulation, a timeline of events based on the collected information must be developed.   From this time line actions may be input into the model, such as venting a window at a given time.  Or the time line may be used in validating a model result.

The development of the model geometry and development of the input file is straight forward with guidance from the FDS users' manual \cite{FDS_Users_Guide} or third party software.  Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.  Examples of these requirements include:
\begin{itemize}
\item the computational cell size
\item model domain and boundaries conditions
\item the heat release rate (HRR) of the ignition source/initial fire
\item physical and thermal properties of fuels such as interior finish and furnishings
	\begin{itemize}
	\item density
	\item specific heat
	\item thermal conductivity
	\item ignition temperature
	\item heat of combustion
	\item heat release rate
	\item mass loss rate under various fire conditions
	\item pyrolyzate/combustion product emissions
	\item response to thermal exposures
	\item activation energy
	\end{itemize}
\end{itemize}
Since there is no all-inclusive, universal fire modeling input data base this type of information must be gathered from literature or generated for a given incident.  The sections below describe the input data and how it was modeled.

\section{Geometry}
\label{geom}
The structure is a 2 $\tfrac{1}{2}$ story residential structure with balloon frame construction and a wood gable roofing system. The structure has a 17.15 m (56 ft) by 6.15 m (20 ft) footprint. This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a total living area of approximately 110 m$^2$ (2200 ft$^2$). Additionally there is a half-story attic that was used to house the structure's hot water heater. Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top. There were two stairwells in the structure: the front stairwell connected the first and second levels and the rear stairwell (part of the enclosed porch) connected the first and second levels and provided access to the attic. Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}) show the interior dimensions of the first and second floor, respectively. The dimensions were found from on-scene measurements using a tape measure. Measurements were made to the nearest 1.27 cm (0.5 in). Based on difficulty of making some of the measurements due to the condition of the post-fire structure, the uncertainty in the measurements is estimated to be on the order of $\pm$ 1 \%. This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in). When considering the uncertainties in the fire ignition time, ventilation, and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.

The model geometry was constructed based on the measurements taken at the structure. The resolution of the model is to the nearest centimeter with that the recognition that the resolution is ultimately limited by the mesh resolution which will be discussed in Section \ref{mesh}. Fig.~(\ref{fig:smv_interior}) shows Smokeview renderings of cutaways of the beta and delta sides of the structure interior.

\begin{figure}[h!]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
\end{tabular*}
\caption{3D Smokeview rendering of structure interior looking from the charlie side: to the beta side (top) and to the delta side (bottom)}
\label{fig:smv_interior}
\end{figure}

\section{Fire}
\label{fire}

To estimate the dominant fuel(s), fire size, and structure ventilation, on-scene videos and post-incident reports are used. The fire was first noticed by a person on the street who informed the residents that smoke was pouring out of the attic. The residents, upon notification of the fire, observed that there was fire in their enclosed rear porch. Post-incident, the fire investigation concluded that the fire originated in the structure's attic.

Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing. The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic had oriented strand board (OSB) floors. If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide and soot yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:

\begin{multline}
\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.86(0.21\,\O_{2} + 0.79\,\N_{2}) \\ 
\rightarrow 5.69(0.0006\,\C\O + 0.17\,\C\O_{2} + 0.15\,\H_{2}\O + 0.674\,\N_{2} + 0.006\,\C)
\label{eq:wood_comb}
\end{multline}
The heat of combustion of wood for this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}. The heat of combustion quantifies the energy release per unit mass of the fuel.

From work by Babrauskas and Grayson \cite{babrauskas1990}, we can find an estimate for the energy release per unit time and unit area (kW/m$^2$). Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRR (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$). Taking a conservative approach, we assume the burning wood in the attic had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood. If we estimate that the average radiation feedback to the pyrolyzing fuel is 30 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release for wood is 65 kW/m$^2$.

Next, is determining the appropriate burnable area (exposed wood area) in the attic and in the second floor porch enclosure. Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1475 ft$^2$) plus there is 105 m$^2$ of floor area in the attic. Examination of post incident images showed the roof sustained more damage than the floor except for the floor area immediately over the back porch. That area will be considered as part of the porch fire. To estimate the attic fire size, we consider the area of the underside of the roof (134 m$^2$) and use an average heat release rate of wood of 65 kW/m$^2$. This results in a fire size of about 9 MW. To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the ceiling above the porch (13 m$^2$). The total area is 55 m$^2$ (592 ft$^2$). Using the same average heat release of 65 kW/m$^2$, the fire size on the porch is approximately 3.3 MW. The total fire size for this structure is estimated to be 12.3 MW.

Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in under 10 seconds. At the same time, part of the second floor window on the charlie side, 0.11 m$^2$ (1.2 ft$^2$) , fails providing initial ventilation.  The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in under 10 seconds. This corresponds to the report of heavy smoke from both the alpha, 0.08 m$^2$ (0.86 ft$^2$), and charlie, 0.1 m$^2$ (1 ft$^2$), sides of the attic. Additional ventilation occurs 45 and 55 seconds into the simulation as the fire burns through the exterior wall, 0.12 m$^2$ (1.3 ft$^2$), on both the beta and charlie side of the structure. At 130 seconds into the simulation, the back door is opened by a firefighter which results in a final fire induced ventilation. A hole, 0.2 m$^2$ (2.2 ft$^2$),  opens on the rear porch of the beta side at 135 seconds.

\section{Mesh}
\label{mesh}

For the simulation in this study, we can estimate a measure of how well the flow field is resolved by the non-dimensional expression $D^*/\dx$. Here $D^*$ is a characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
\begin{equation}
D^* = \left(
     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
     \right)^\frac{2}{5} 
\label{eq:mesh}
\end{equation}   
From the FDS User Guide \cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
relation $Q^* = (D^*/D)^{5/2}$.'' $D$ is the physical diameter of the fire. Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the characteristic fire diameter to cell size ratio based on the 3.3 MW porch fire is 15.5 and for the 9 MW fire is 23. Based on validation work performed for the U.S. Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16 \cite{NUREG_1824}. The grid resolution used in the model fall within typical, engineering $D^*/\dx$ values.

\chapter{Model Results}

\section{Heat Release Rate}
\label{HRR}
The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation. Examination of this information can indicate ignition time, if a fire is under ventilated (FDS HRR less than prescribed HRR), the impact of ventilation, or if complete extinction occurs among other characteristics of fire behavior. Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the defined input fires described in Section \ref{fire}. The two vertical lines represent when a firefighter opened the back door of the structure (dotted) and when the second floor interior door was estimated to fail (dash-dot).

\begin{figure}[h!]
\centering
\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
\caption{HRR versus time of FDS model of the West 50th St. fire. The first vertical line indicates when the back door failed, the second indicates when the interior hallway door failed.}
\label{fig:hrr}
\end{figure}

Just prior to the back door being opened, the HRR was 6.6 MW. This is below the specified HRR of 12.3 MW, indicated that the fire was under-ventilated. From the time the back doored was opened to estimated time the interior door failed (approximately 30 seconds), the HRR increased by approximately 35 \% to 8.9 MW.

\section{Temperature}

\section{Velocity}

\section{Pressure}

\section{Gas Concentrations}

\chapter{Discussion}

\section{Conditions in Hallway}

\section{Comparison of conditions with PPE and Victim Limitations}

\section{Tactical Considerations}

\chapter{Summary}

\chapter{Acknowledgements}

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,chicago}

\appendix

\chapter{Dimensioned Drawings}

\begin{figure}[h!]
\centering
\includegraphics[width=.80\textwidth]{../Figures/50th_Place_1st_Floor}
\caption {Dimensioned drawing of 1$^{st}$ floor}
\label{fig:first_floor}
\end{figure}

\begin{figure}[h!]
\centering
\includegraphics[width=.80\textwidth]{../Figures/50th_Place_2nd_Floor}
\caption {Dimensioned drawing of 2$^{nd}$ floor}
\label{fig:second_floor}
\end{figure}

\end{document}

### 2014-01-17 Studies/Chicago_2012/Report/Chicago_Fire.tex
Update to Chicago write-up

@@
 \hline
-Fire Time & Simulation Time & Action  \\
+Incident Time & Simulation Time & Fire Behavior / Fireground Operation  \\
 \hline \hline
@@
         &  2:40  & Top of interior door fails. \\ \hline
-5:23    & $\approx$ 3:40       & No response from Engine 123: Capt. or FF. \\ \hline
+5:23    &  3:40  & No response from Engine 123: Capt. or FF. \\ \hline
 5:24    &  N/A   & Water applied to attic from the rear exterior position. \\ \hline
@@
 Smokeview is a software tool designed to visualize the results of the FDS \cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (92D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
 Smokeview allows the fire and fire movement to be visualized.
@@
 The total fire size for this structure is estimated to be 12.3 MW.
+Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in under 10 seconds.
+The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in under 10 seconds.
 
-Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in under 10 seconds.
+\section{Vents}
+\label{Vents}
+This simulation includes vents that account for the approximate leakage of the building envelope and changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls,breaking windows,etc).
+The times of the ventilation changes are provided in Table \ref{tab:vents}.
+
 At the same time, part of the second floor window on the charlie side, 0.11 m$^2$ (1.2 ft$^2$) , fails providing initial ventilation.
@@
 A hole, 0.2 m$^2$ (2.2 ft$^2$), opens on the rear porch of the beta side at 135 seconds.
+
+\begin{table}
+\centering
+\caption{Ventilation Timeline}
+\vskip.5\baselineskip
+\begin{tabular}{|c|c|c|}
+\hline
+Incident Time & Simulation Time & Ventilation  \\
+\hline \hline
+        &        & Reported working fire with heavy smoke\\
+5:17    &        & coming from the front and rear of the \\
+        &        & structure's attic. \\ \hline
+        &  0:00  & Attic fire ignites. Initial \\ 
+        &        & self ventilation on charlie side. \\ \hline
+        &  0:20  & Front door opens. \\ \hline
+5:20    &  0:40  & Attic self ventilation - alpha and charlie sides. Porch fire ignites. \\ \hline
+        &  0:45  & Additional self ventilation on charlie side. \\ \hline
+        &  0:55  & Self ventilation on beta side. \\ \hline        
+5:21:30 &  2:10  & 1$^{st}$ floor door to enclosed porch opened \\ \hline
+        &  2:15  & Additional self ventilation on beta side. \\ \hline        
+        &  2:40  & Top of interior door fails. \\ \hline
+        &  5:00  & Simulation ends. \\ \hline
+\end{tabular}
+\label{tab:vents}
+\end{table}
 

### 2014-01-23 Studies/Chicago_2012/Report/Chicago_Fire.tex
Update to Chicago writeup

@@
 \chapter{Introduction}
+Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires \cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
+The overriding objective of all of these studies is to improve the safety of fire fighters.
+
+On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
+Changes in the ventilation flow path cause a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
+NIST assisted with examining the fire dynamics of this incident.
+NIST performed computer simulations of the fire using the FDS and Smokeview, a visualization tool, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
+The specific objectives of the simulations detailed in this report are:
+\begin{enumerate}
+\item To examine with physics-based calculations the effect of flow path on the thermal and fire conditions in this multi-story residential structure.
+\item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
+\end{enumerate}
+This document describes the input and the results of the FDS (version 6.0.0) simulations.
 
@@
 
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a death of a fire captain and injury to a fire fighter.
+On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.
 At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.

### 2014-02-01 Studies/Chicago_2012/Report/Chicago_Fire.tex
Update to Chicago writeup

@@
 On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-Changes in the ventilation flow path cause a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
+Changes in the ventilation flow path caused a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
 NIST assisted with examining the fire dynamics of this incident.
-NIST performed computer simulations of the fire using the FDS and Smokeview, a visualization tool, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
+NIST performed computer simulations of the fire using Fire Dynamics Simulator and Smokeview, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
@@
 Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
-FDS can utilize material properties of the furnishings, walls, floors, and ceilings to compute fire growth and spread.
-One of the most important advantages of FDS is that it is verified and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Verification_Guide,FDS_Validation_Guide}.
+One of the most important advantages of FDS is that it is  mathematically verified \cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Validation_Guide}.
 A complete description of the FDS model is given in reference \cite{FDS_Tech_Guide}.
@@
 From this time line actions may be input into the model, such as venting a window at a given time.
-Or the time line may be used in validating a model result.
 
@@
 This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in).
-When considering the uncertainties in the fire ignition time, ventilation, and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
+When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
 
-The model geometry was constructed based on the measurements taken at the structure.
-The resolution of the model is to the nearest centimeter with that the recognition that the resolution is ultimately limited by the mesh resolution which will be discussed in Section \ref{mesh}.
-Fig.~(\ref{fig:smv_interior}) shows Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
+The resolution of the model geometry input is to the nearest centimeter with that the recognition that the resolution is ultimately limited by the mesh resolution which will be discussed in Section \ref{mesh}.
+Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
 
@@
 \end{tabular*}
-\caption{3D Smokeview rendering of structure interior looking from the charlie side: to the beta side (top) and to the delta side (bottom)}
+\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
 \label{fig:smv_interior}
@@
 The total fire size for this structure is estimated to be 12.3 MW.
-Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in under 10 seconds.
-The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in under 10 seconds.
+Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 8 seconds.
+The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in 8 seconds.
 
@@
 \label{Vents}
-This simulation includes vents that account for the approximate leakage of the building envelope and changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls,breaking windows,etc).
+This simulation includes vents that account for the approximate leakage of the building envelope and changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
@@
 From the FDS User Guide \cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.'' $D$ is the physical diameter of the fire.
+relation $Q^* = (D^*/D)^{5/2}$.'' Here, $D$ is the physical diameter of the fire as input to the model.
 Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the characteristic fire diameter to cell size ratio based on the 3.3 MW porch fire is 15.5 and for the 9 MW fire is 23.
@@
 Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16 \cite{NUREG_1824}.
-The grid resolution used in the model fall within typical, engineering $D^*/\dx$ values.
+The grid resolution used in the model falls within typical, engineering $D^*/\dx$ values.
+As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
 

### 2014-02-18 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: update to Chicago writeup

@@
 \hline
-Incident Time & Simulation Time & Fire Behavior / Fireground Operation  \\
+Incident Time & Baseline Simulation Time & Fire Behavior / Fireground Operation  \\
 \hline \hline
@@
 This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a total living area of approximately 110 m$^2$ (2200 ft$^2$).
+Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
 Additionally there is a half-story attic that was used to house the structure's hot water heater.
-Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
+Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
+Note that the damage is to the structure's attic.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.65\textwidth]{../Figures/exterior_alpha}
+\caption{Photograph showing the post-incident front (side alpha) exterior of the structure.}
+\label{fig:alpha_ex}
+\end{figure}
+
 There were two stairwells in the structure: the front stairwell connected the first and second levels and the rear stairwell (part of the enclosed porch) connected the first and second levels and provided access to the attic.
@@
 The resolution of the model geometry input is to the nearest centimeter with that the recognition that the resolution is ultimately limited by the mesh resolution which will be discussed in Section \ref{mesh}.
-Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
 
-\begin{figure}[h!]
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-\end{tabular*}
-\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-\label{fig:smv_interior}
-\end{figure}
+%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
+%\begin{figure}[h!]
+%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
+%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
+%\end{tabular*}
+%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
+%\label{fig:smv_interior}
+%\end{figure}
 
@@
 The residents, upon notification of the fire, observed that there was fire in their enclosed rear porch.
-Post-incident, the fire investigation concluded that the fire originated in the structure's attic.
+Post-incident, the fire investigation concluded that the fire originated in the structure's attic \cite{NIOSH:Bowyer}.
 
@@
 The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic had oriented strand board (OSB) floors.
+Fig.~(\ref{fig:charlie_ex}) shows the post-incident exterior of the charlie side of the structure.
+The figure shows the composition of the second floor and attic of the structure.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.65\textwidth]{../Figures/exterior_charlie}
+\caption{Photograph showing the post-incident rear (side charlie) exterior of the structure.}
+\label{fig:charlie_ex}
+\end{figure}
+
 If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide and soot yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
@@
 \end{multline}
+
+\begin{lstlisting}
+&SPEC ID = 'WOOD', FORMULA = 'CH1.7O0.74N0.002' /
+
+&REAC ID = 'wood' 
+    FUEL = 'WOOD', 
+    HEAT_OF_COMBUSTION=16400,
+    SOOT_YIELD = 0.015,
+    CO_YIELD = 0.004/
+\end{lstlisting}
+
 The heat of combustion of wood for this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}.
@@
 Taking a conservative approach, we assume the burning wood in the attic had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 30 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release for wood is 65 kW/m$^2$.
+If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release for wood is 51 kW/m$^2$.
 
 Next, is determining the appropriate burnable area (exposed wood area) in the attic and in the second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1475 ft$^2$) plus there is 105 m$^2$ of floor area in the attic.
-Examination of post incident images showed the roof sustained more damage than the floor except for the floor area immediately over the back porch.
+Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ plus there is 105 m$^2$ of floor area in the attic.
+Examination of post incident images showed that the floor immediately over the back porch was completely burned away.
 That area will be considered as part of the porch fire.
-To estimate the attic fire size, we consider the area of the underside of the roof (134 m$^2$) and use an average heat release rate of wood of 65 kW/m$^2$.
-This results in a fire size of about 9 MW.
-To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the ceiling above the porch (13 m$^2$).
-The total area is 55 m$^2$ (592 ft$^2$).
-Using the same average heat release of 65 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
+Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
+To estimate the total attic fire size, we consider the area of the underside of the roof (134 m$^2$) plus the floor area (43 m$^2$) and use an average heat release rate of wood of 51 kW/m$^2$.
+This results in a fire size of 9 MW.
+To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$).
+The total area is 64 m$^2$.
+Using the same average heat release of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
 The total fire size for this structure is estimated to be 12.3 MW.
-Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 8 seconds.
-The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in 8 seconds.
+Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
+The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
+A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
 

### 2014-02-20 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: update report writeup

@@
 HRR \> Heat Release Rate \\
+HRRPUA \> Heat Release Rate per Unit Area \\
 NIST \> National Institute of Standards and Technology \\
@@
         &  0:00  & Simulation begins. Attic fire ignites. Initial \\ 
-        &        & self ventilation on charlie side. \\ \hline
-        &  0:20  & Front door opens. \\ \hline
+        &        & self ventilation on charlie side. Front door opens. \\ \hline
 5:20    &  0:40  & Attic self ventilation - heavy smoke reported. Porch fire ignites. \\ \hline
@@
 \label{geom}
-The structure is a 2 $\tfrac{1}{2}$ story residential structure with balloon frame construction and a wood gable roofing system.
-The structure has a 17.15 m (56 ft) by 6.15 m (20 ft) footprint.
-This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a total living area of approximately 110 m$^2$ (2200 ft$^2$).
+The structure was a 2 $\tfrac{1}{2}$ story residential structure with balloon frame construction and a wood gable roofing system.
+The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint.
+This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
 Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
-Additionally there is a half-story attic that was used to house the structure's hot water heater.
+Additionally there was a half-story attic that was used to house the structure's hot water heater.
+There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
 Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
-Note that the damage is to the structure's attic.
+Note that the majority of the damage is to the structure's attic.
 
@@
 
-There were two stairwells in the structure: the front stairwell connected the first and second levels and the rear stairwell (part of the enclosed porch) connected the first and second levels and provided access to the attic.
 Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}) show the interior dimensions of the first and second floor, respectively.
@@
 When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
-
-The resolution of the model geometry input is to the nearest centimeter with that the recognition that the resolution is ultimately limited by the mesh resolution which will be discussed in Section \ref{mesh}.
 
@@
 
-To estimate the dominant fuel(s), fire size, and structure ventilation, on-scene videos and post-incident reports are used.
-The fire was first noticed by a person on the street who informed the residents that smoke was pouring out of the attic.
-The residents, upon notification of the fire, observed that there was fire in their enclosed rear porch.
+To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
 Post-incident, the fire investigation concluded that the fire originated in the structure's attic \cite{NIOSH:Bowyer}.
-
+Post-fire pictures revealed extensive damage to the attic and second floor rear porch (cf.
+Fig.~(\ref{fig:charlie_ex})).
 Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic had oriented strand board (OSB) floors.
-Fig.~(\ref{fig:charlie_ex}) shows the post-incident exterior of the charlie side of the structure.
-The figure shows the composition of the second floor and attic of the structure.
+The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
 
@@
 
-If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide and soot yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
+If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
 
 \begin{multline}
-\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.86(0.21\,\O_{2} + 0.79\,\N_{2}) \\ 
-\rightarrow 5.69(0.0006\,\C\O + 0.17\,\C\O_{2} + 0.15\,\H_{2}\O + 0.674\,\N_{2} + 0.006\,\C)
+\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
+\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
 \label{eq:wood_comb}
 \end{multline}
+
+The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}.
+The heat of combustion quantifies the energy release per unit mass of the fuel.
+The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
 
@@
 
-The heat of combustion of wood for this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}.
-The heat of combustion quantifies the energy release per unit mass of the fuel.
-
 From work by Babrauskas and Grayson \cite{babrauskas1990}, we can find an estimate for the energy release per unit time and unit area (kW/m$^2$).
@@
 Taking a conservative approach, we assume the burning wood in the attic had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release for wood is 51 kW/m$^2$.
+If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
 
@@
 Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we consider the area of the underside of the roof (134 m$^2$) plus the floor area (43 m$^2$) and use an average heat release rate of wood of 51 kW/m$^2$.
+To estimate the total attic fire size, we consider the area of the underside of the roof (134 m$^2$) plus the floor area (43 m$^2$) and use an HRRPUA of wood of 51 kW/m$^2$.
 This results in a fire size of 9 MW.
@@
 The total area is 64 m$^2$.
-Using the same average heat release of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
+Using the same HRRPUA of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
 The total fire size for this structure is estimated to be 12.3 MW.
@@
 \label{Vents}
-This simulation includes vents that account for the approximate leakage of the building envelope and changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+This simulation includes vents that account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
@@
 \centering
-\caption{Ventilation Timeline}
+\caption{Simulation Ventilation Timelines}
 \vskip.5\baselineskip
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{|c|c|c|c|}
 \hline
-Incident Time & Simulation Time & Ventilation  \\
+Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Structure Side \\
 \hline \hline
-        &        & Reported working fire with heavy smoke\\
-5:17    &        & coming from the front and rear of the \\
-        &        & structure's attic. \\ \hline
-        &  0:00  & Attic fire ignites. Initial \\ 
-        &        & self ventilation on charlie side. \\ \hline
-        &  0:20  & Front door opens. \\ \hline
-5:20    &  0:40  & Attic self ventilation - alpha and charlie sides. Porch fire ignites. \\ \hline
-        &  0:45  & Additional self ventilation on charlie side. \\ \hline
-        &  0:55  & Self ventilation on beta side. \\ \hline        
-5:21:30 &  2:10  & 1$^{st}$ floor door to enclosed porch opened \\ \hline
-        &  2:15  & Additional self ventilation on beta side. \\ \hline        
-        &  2:40  & Top of interior door fails. \\ \hline
-        &  5:00  & Simulation ends. \\ \hline
+0:00    &  0:00  & 0.11 & Charlie \\ \hline
+0:40    &  0:40  & 0.08 & Alpha and Charlie \\ \hline
+0:45    &  0:45  & 0.12 & Beta \\ \hline
+0:55    &  0:55  & 0.12 & Charlie \\ \hline        
+2:10    &  N/A   & 1.41 & Charlie \\ \hline
+2:15    &  N/A   & 0.2  & Beta \\ \hline        
+2:40    &  2:40  & 0.80 & Interior \\ \hline
+5:00    &  5:00  & \multicolumn{2}{|c|}{Simulation Ends}  \\ \hline
 \end{tabular}

### 2014-02-20 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: fix reference in writeup
Chicago Fire: update to Chicago writeup and bib

@@
 One of the most important advantages of FDS is that it is  mathematically verified \cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Validation_Guide}.
-A complete description of the FDS model is given in reference \cite{FDS_Tech_Guide}.
+A complete description of the FDS model is given in reference \cite{FDS_Math_Guide}.
 
@@
 Since there is no all-inclusive, universal fire modeling input data base this type of information must be gathered from literature or generated for a given incident.
-The sections below describe the input data and how it was modeled.
+For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters.
+The sections below describe these inputs.
+
+\begin{table}
+\centering
+\caption{Relevant Modeling Input Parameters}
+\vskip.5\baselineskip
+\begin{tabular}{|c|c|c|}
+\hline
+Category & Details & Report Section  \\
+\hline \hline
+ Simulation Time           & 5 minutes                             & -- \\ \hline
+ Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ \hline
+ Ambient Temperature       & 20 $^{\circ}$C                        & -- \\ \hline
+\multirow{4}{*}{Reaction}  & Fuel: Wood ($\C\H_{1.7}\O_{0.74}\N_{0.002}$)                & \multirow{4}{*}{Section~\ref{fire}} \\
+                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
+                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
+                           & Heat of Combustion: 16400 kJ/kg                             & \\ \hline
+\multirow{2}{*}{Fire Size} & Attic Fire: 9 MW                      & \multirow{2}{*}{Section~\ref{fire}} \\
+                           & Porch Fire: 3.3 MW                    & \\ \hline                      
+\end{tabular}
+\label{tab:mod_param}
+\end{table}
 
@@
 
-From work by Babrauskas and Grayson \cite{babrauskas1990}, we can find an estimate for the energy release per unit time and unit area (kW/m$^2$).
-Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRR (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Taking a conservative approach, we assume the burning wood in the attic had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ (assuming under-ventilated conditions within the structure) then an average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
+Note that using the input lines above will invoke the simple chemistry reaction balance in FDS.
+This means that fuel and air react to form only CO$_2$, CO, H$_2$O, Soot, and N$_2$.
+If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them \cite{FDS_Users_Guide}.
+Based on above input lines FDS uses the default, mixing-controlled fast chemistry combustion model.
+This mechanism  states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach \cite{FDS_Math_Guide}.
+While FDS provides users to the option to use a more complex finite-rate combustion mechanism, we do not have sufficient evidence to justify deviating from the default specifications.
 
-Next, is determining the appropriate burnable area (exposed wood area) in the attic and in the second floor porch enclosure.
+To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson \cite{babrauskas1990}.
+Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRRPUA (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
+Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
+Based on the range of heat flux exposures, the data was fit to determine HRRPUA ($y$) as a function of exposure ($x$):
+
+\begin{equation}
+y = ax+b
+\label{eq:heat_flux}
+\end{equation}
+
+In Eq.~\ref{eq:heat_flux}, $a$ and $b$ are experimental constants.
+For Douglas Fir plywood these values were found to be 1.43 and 22 respectively.
+Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$ \cite{tsaidrysdale}.
+If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ because of under-ventilated conditions within the structure, then following Eq.~\ref{eq:heat_flux} the average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
+
+To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
 Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ plus there is 105 m$^2$ of floor area in the attic.
-Examination of post incident images showed that the floor immediately over the back porch was completely burned away.
+Examination of post incident images showed that the floor immediately over the back porch burned away.
 That area will be considered as part of the porch fire.
 Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we consider the area of the underside of the roof (134 m$^2$) plus the floor area (43 m$^2$) and use an HRRPUA of wood of 51 kW/m$^2$.
-This results in a fire size of 9 MW.
+To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$).
+Using an HRRPUA of wood of 51 kW/m$^2$, results in a fire size of 9 MW.
 To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$).
@@
 The total fire size for this structure is estimated to be 12.3 MW.
-Since it is unknown when the fire started relative to notification of a fire, the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
-The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
+Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
+First is that the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
+The porch fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
 A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
+The second is that the sources of the gas phase wood fuel are of fixed area and at fixed locations (2 sources for attic, 1 source for porch).
+The following lines define the source fires for an FDS input file:
+
+\begin{lstlisting}
+&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE',TAU_Q=10 /
+&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
+&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
+&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE',DEVC_ID='SECOND FIRE'/ 1.5 m^2
+&DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
+\end{lstlisting}
+Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes of a specific area.
 
@@
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
-
-At the same time, part of the second floor window on the charlie side, 0.11 m$^2$ (1.2 ft$^2$) , fails providing initial ventilation.
-The attic fire starts 40 seconds into the simulation and ramps to 3.3 MW in under 10 seconds.
-This corresponds to the report of heavy smoke from both the alpha, 0.08 m$^2$ (0.86 ft$^2$), and charlie, 0.1 m$^2$ (1 ft$^2$), sides of the attic.
-Additional ventilation occurs 45 and 55 seconds into the simulation as the fire burns through the exterior wall, 0.12 m$^2$ (1.3 ft$^2$), on both the beta and charlie side of the structure.
-At 130 seconds into the simulation, the back door is opened by a firefighter which results in a final fire induced ventilation.
-A hole, 0.2 m$^2$ (2.2 ft$^2$), opens on the rear porch of the beta side at 135 seconds.
+Structure leakage has been shown to be important when modeling enclosure fires \cite{beal2009}.
+The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of structure of this type.
+Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
 
@@
 \vskip.5\baselineskip
-\begin{tabular}{|c|c|c|c|}
+\begin{tabular}{|c|c|c|c|c|}
 \hline
-Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Structure Side \\
+Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Type & Structure Side \\
 \hline \hline
-0:00    &  0:00  & 0.11 & Charlie \\ \hline
-0:40    &  0:40  & 0.08 & Alpha and Charlie \\ \hline
-0:45    &  0:45  & 0.12 & Beta \\ \hline
-0:55    &  0:55  & 0.12 & Charlie \\ \hline        
-2:10    &  N/A   & 1.41 & Charlie \\ \hline
-2:15    &  N/A   & 0.2  & Beta \\ \hline        
-2:40    &  2:40  & 0.80 & Interior \\ \hline
-5:00    &  5:00  & \multicolumn{2}{|c|}{Simulation Ends}  \\ \hline
+0:00    &  0:00  & 0.11 & Window      & Charlie \\ \hline
+0:40    &  0:40  & 0.08 & Breach (x2) & Alpha and Charlie \\ \hline
+0:45    &  0:45  & 0.12 & Breach      & Beta \\ \hline
+0:55    &  0:55  & 0.12 & Breach      & Charlie \\ \hline        
+2:10    &  N/A   & 1.41 & Door        & Charlie \\ \hline
+2:15    &  N/A   & 0.2  & Breach      & Beta \\ \hline        
+2:40    &  2:40  & 0.80 & Door        & Interior \\ \hline
+5:00    &  5:00  & \multicolumn{3}{|c|}{Simulation Ends}  \\ \hline
 \end{tabular}

### 2014-02-21 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: update report, images

@@
 \vskip.5\baselineskip
-\begin{tabular}{|c|c|c|}
+\begin{tabular}{|l|l|l|}
 \hline
-Category & Details & Report Section  \\
+Parameter & Description & Reference  \\
 \hline \hline
@@
  Ambient Temperature       & 20 $^{\circ}$C                        & -- \\ \hline
-\multirow{4}{*}{Reaction}  & Fuel: Wood ($\C\H_{1.7}\O_{0.74}\N_{0.002}$)                & \multirow{4}{*}{Section~\ref{fire}} \\
+\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{6}{*}{Section~\ref{fire}} \\
                            & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
                            & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ \hline
-\multirow{2}{*}{Fire Size} & Attic Fire: 9 MW                      & \multirow{2}{*}{Section~\ref{fire}} \\
+                           & Heat of Combustion: 16400 kJ/kg                             & \\ \cline{1-2}
+\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \\ 
                            & Porch Fire: 3.3 MW                                          & \\ \hline                      
+\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{6}{*}{Section~\ref{matl}} \\
+                                   & $\rho$: 510 \; kg/m$^3$         & \\
+                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\ \cline{1-2}
+\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         & \\ 
+                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
+                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\ \hline  
 \end{tabular}
@@
 
+\section{Materials}
+\label{matl}
+While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
+In this study, we define gypsum \cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood \cite{Incropera:1} for the unfinished portions of the attic and rear porch.
+The text provided below are the lines necessary to define these materials in an FDS input file.
+
+\begin{lstlisting}
+&MATL ID        = 'GYPSUM'
+    FYI = 'Quintiere, Fire Behavior' 
+    CONDUCTIVITY    = 0.48
+    SPECIFIC_HEAT   = 0.84
+    DENSITY = 1440./
+
+&MATL ID        = 'WOOD_MAT'
+    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
+    CONDUCTIVITY    = 0.12
+    SPECIFIC_HEAT   = 1.38
+    DENSITY = 510./ 
+\end{lstlisting}
+
 \section{Vents}
@@
 This simulation includes vents that account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+There are two ventilation scenarios that are considered in this study.
+The first is the baseline case where the ventilation times and ventilation areas represent our best understanding of the incident.
+The second case does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
@@
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
+Fig.~(\ref{fig:geom_grid}) shows the
+alpha side (front) of the structure rendered in Smokeview with the 10 cm mesh.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
+\caption{Alpha side of the structure with 10 cm computation mesh.}
+\label{fig:geom_grid}
+\end{figure}
+
+As discussed Section~\ref{geom}, the structure has 17.15 m by 6.15 m footprint with a total height of 8.56 m.
+To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
+The total volume of the computational domain is 24 m by 10 m by 10 m.
+At 10 cm resolution this would result in 2.4 million computational cells.
+To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
+Fig.~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
+\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m by 10 m by 5 m.}
+\label{fig:mult_mesh}
+\end{figure}
 
@@
 The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation.
-Examination of this information can indicate ignition time, if a fire is under ventilated (FDS HRR less than prescribed HRR), the impact of ventilation, or if complete extinction occurs among other characteristics of fire behavior.
-Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the defined input fires described in Section \ref{fire}.
-The two vertical lines represent when a firefighter opened the back door of the structure (dotted) and when the second floor interior door was estimated to fail (dash-dot).
+Here, we examine the data to examine the impact of ventilation on fire size.
+Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
+The two vertical lines represent when a firefighter opened the back door of the structure (t = 130s) and when the second floor interior door was estimated to fail (t = 160s).
 
@@
 
-Just prior to the back door being opened, the HRR was 6.6 MW.
+%Just prior to the back door being opened, the HRR was 6.6 MW.
 This is below the specified HRR of 12.3 MW, indicated that the fire was under-ventilated.
@@
 
-\section{Velocity}
-
 \section{Pressure}
-
-\section{Gas Concentrations}
 
@@
 \section{Conditions in Hallway}
-
-\section{Comparison of conditions with PPE and Victim Limitations}
 

### 2014-03-04 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: add smv image, update results, input files, and processing script

@@
 
+In Fig.~(\ref{fig:hrr}), the solid line is the FDS HRR from the venting conditions that represent our attempt to model the on-scene conditions.
+The dashed line represents the case where the rear door opening and subsequent beta side breach do not occur.
+The dash-dotted line is the prescribed FDS input HRR.
+We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR.
+The HRR first peaks at just under 9 MW at approximately 20 seconds into the simulation.
+The HRR proceeds to drop to 5 MW as the available oxygen inside the structure gets consumed.
+There is insufficient available oxygen in the structure to combust all of the fuel.
+As a result there is excess fuel buildup within the attic and back porch and burning occurs exterior to the structure where fuel at oxygen can mix at the various vents.
+Fig.~(\ref{fig:smv_ext_fire}) illustrates flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
+The HRR spikes back up to 9 MW at 58 seconds (after additional wall breaches, see Table~\ref{tab:vents}) before again dropping to 5 MW.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.80\textwidth]{../Figures/smv_exterior_fire}
+\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
+\label{fig:smv_ext_fire}
+\end{figure}
+
 %Just prior to the back door being opened, the HRR was 6.6 MW.

### 2014-03-04 Studies/Chicago_2012/Scripts/chicago_hrr.py

@@ -12,11 +12,11 @@ def movingaverage(interval, window_size):
 
 C_FDS = np.genfromtxt('../FDS_Output_Files/west_50th_baseline_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
 HRR = C_FDS['HRR']/1000
-HRR_avg = movingaverage(HRR,10)
+HRR_avg = movingaverage(HRR,2)
 
 ND_FDS = np.genfromtxt('../FDS_Output_Files/west_50th_norear_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
 HRR_ND = ND_FDS['HRR']/1000
-HRR_ND_avg = movingaverage(HRR_ND,10)
+HRR_ND_avg = movingaverage(HRR_ND,2)
 
 HRR_theo = [None]*1000
 HRR_time = list(xrange(1000))
@@ -31,7 +31,7 @@ for i in range (0, 999):
 	else:
 		HRR_theo[i] = 12.3
 
-print HRR_avg[129],HRR_avg[160]
+print HRR_avg[129],HRR_avg[161],HRR_ND_avg[161]
 
 plt.figure
 plt.plot(HRR_time,HRR_theo,'b-.',mfc='none',label='Prescribed HRR',linewidth=2)

### 2014-03-07 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: update to report write up.

@@
 After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.
-Engine 123 arrived on scene at approximately 5:19.
+Engine 123 arrived on scene at approximately 17:19.
 The victims were part of the Engine 123 crew.
@@
 Both doors remain open and the fire fighter from TL 39 exits the structure.
-Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 5:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.
+Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 17:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.
 No response was made by the Engine 123 Captain.
@@
 
-Squad 5 entered the front of the structure at approximately 5:25 and headed to the second floor.
+Squad 5 entered the front of the structure at approximately 17:25 and headed to the second floor.
 They heard a commotion and found the Engine 123 Captain collapsed on the kitchen floor and entangled with the Engine 123 firefighter.
-A Mayday was called on the radio by Squad 5 at approximately  5:27 and the Engine 123 Captain was removed from the front of the building at approximately 5:29 and succumbed to his injuries at the hospital at 5:38.
+A Mayday was called on the radio by Squad 5 at approximately  17:27 and the Engine 123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
+Table~\ref{tab:fire_info} presents the timeline of the fire.
 
-\begin{table}
+\bigskip 
+\begin{minipage}{.8\linewidth}
 \centering
-\caption{Fire and Simulation Event Timeline}
-\vskip.5\baselineskip
-\begin{tabular}{|c|c|c|}
-\hline
-Incident Time & Baseline Simulation Time & Fire Behavior / Fireground Operation  \\
-\hline \hline
-        &        & Reported working fire with heavy smoke\\
-5:17    &        & coming from the front and rear of the \\
-        &        & structure's attic. \\ \hline
-        &  0:00  & Simulation begins. Attic fire ignites. Initial \\ 
-        &        & self ventilation on charlie side. Front door opens. \\ \hline
-5:20    &  0:40  & Attic self ventilation - heavy smoke reported. Porch fire ignites. \\ \hline
-        &  0:45  & Additional self ventilation on charlie side. \\ \hline
-        &  0:55  & Self ventilation on beta side. \\ \hline        
-5:21:00 &        & Engine 123 Capt. and FF on 2$^{nd}$ floor. \\ \hline
-        &        & Rear Exterior $-$ 1$^{st}$ floor door to enclosed \\
-5:21:30 &  2:10  & porch opened, fire in rear porch begins to \\
-        &        & increase HRR. \\ \hline
-        &  2:15  & Additional self ventilation on beta side. \\ \hline        
-        &  2:40  & Top of interior door fails. \\ \hline
-5:23    &  3:40  & No response from Engine 123: Capt. or FF. \\ \hline
-5:24    &  N/A   & Water applied to attic from the rear exterior position. \\ \hline
-        &  5:00  & Simulation ends. \\ \hline
-\end{tabular}
-\label{tab:fires}
-\end{table}
+\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
+\begin{tabular}{c m{0.25in}}
+\toprule[1.5pt]
+Incident Time & Fire Behavior / Fireground Operation  \\
+\midrule
+17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
+17:16    & Dispatch for a {\bf Still Alarm} \\
+17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
+17:21:00 & Engine 123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
+17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
+17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from Engine 123: Capt. or FF. \\
+17:24    & Water applied to attic from the rear exterior position. \\
+17:27    & IC calls a Mayday \\
+17:29    & Engine 123 Capt. carried out of structure. \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\big-skip
+\end{minipage}
 
@@
 
-\begin{table}
+\bigskip
+\begin{minipage}{.8\linewidth}
 \centering
-\caption{Relevant Modeling Input Parameters}
-\vskip.5\baselineskip
-\begin{tabular}{|l|l|l|}
-\hline
+\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
+\begin{tabular}{lll}
+\toprule[1.5pt]
 Parameter & Description & Reference  \\
-\hline \hline
- Simulation Time           & 5 minutes                             & -- \\ \hline
- Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ \hline
- Ambient Temperature       & 20 $^{\circ}$C                        & -- \\ \hline
-\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{6}{*}{Section~\ref{fire}} \\
+\midrule
+ Simulation Time           & 5 minutes                             & -- \\[.25cm]
+ Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
+ Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
+\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
                            & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
                            & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ \cline{1-2}
-\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \\ 
-                           & Porch Fire: 3.3 MW                                          & \\ \hline                      
-\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{6}{*}{Section~\ref{matl}} \\
+                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
+\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
+                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
+\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
                                    & $\rho$: 510 \; kg/m$^3$         & \\
-                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\ \cline{1-2}
-\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         & \\ 
+                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
+\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                    & $\rho$: 1440 \; kg/m$^3$        & \\ 
-                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\ \hline  
-\end{tabular}
-\label{tab:mod_param}
-\end{table}
+                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\bigskip
+\end{minipage}
 
@@
 
-\begin{table}
+\bigskip
+\begin{minipage}{.8\linewidth}
 \centering
-\caption{Simulation Ventilation Timelines}
-\vskip.5\baselineskip
-\begin{tabular}{|c|c|c|c|c|}
-\hline
+\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
+\begin{tabular}{ccccc}
+\toprule[1.5pt]
 Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Type & Structure Side \\
-\hline \hline
-0:00    &  0:00  & 0.11 & Window      & Charlie \\ \hline
-0:40    &  0:40  & 0.08 & Breach (x2) & Alpha and Charlie \\ \hline
-0:45    &  0:45  & 0.12 & Breach      & Beta \\ \hline
-0:55    &  0:55  & 0.12 & Breach      & Charlie \\ \hline        
-2:10    &  N/A   & 1.41 & Door        & Charlie \\ \hline
-2:15    &  N/A   & 0.2  & Breach      & Beta \\ \hline        
-2:40    &  2:40  & 0.80 & Door        & Interior \\ \hline
-5:00    &  5:00  & \multicolumn{3}{|c|}{Simulation Ends}  \\ \hline
-\end{tabular}
-\label{tab:vents}
-\end{table}
+\midrule
+0:00    &  0:00  & 0.11 & Window      & Charlie \\
+0:40    &  0:40  & 0.08 & Breach (x2) & Alpha and Charlie \\
+0:45    &  0:45  & 0.12 & Breach      & Beta \\
+0:55    &  0:55  & 0.12 & Breach      & Charlie \\     
+2:10    &  N/A   & 1.41 & Door        & Charlie \\
+2:15    &  N/A   & 0.2  & Breach      & Beta \\        
+2:40    &  2:40  & 0.80 & Door        & Interior \\
+5:00    &  5:00  & \multicolumn{3}{c}{Simulation Ends}  \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\bigskip
+\end{minipage}
 
@@
 Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
-The two vertical lines represent when a firefighter opened the back door of the structure (t = 130s) and when the second floor interior door was estimated to fail (t = 160s).
+The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).
 
@@
 The HRR proceeds to drop to 5 MW as the available oxygen inside the structure gets consumed.
-There is insufficient available oxygen in the structure to combust all of the fuel.
-As a result there is excess fuel buildup within the attic and back porch and burning occurs exterior to the structure where fuel at oxygen can mix at the various vents.
-Fig.~(\ref{fig:smv_ext_fire}) illustrates flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
-The HRR spikes back up to 9 MW at 58 seconds (after additional wall breaches, see Table~\ref{tab:vents}) before again dropping to 5 MW.
+There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs at then vents.
+Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
+Despite the fire becoming under-ventilated, the mass flow rate of fuel into the structure remains constant.
+As a result there is a buildup of pressure and excess fuel within the attic and back porch.
+After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the HRR spikes to 9 MW before again dropping to about 6 MW.
+This peak occurs because the additional vents provide pathways for pressure relief.
+Unburned fuel at above ambient pressure flow out of the structure, mix with oxygen, and react.
+As the pressure drops, the flow of fuel out of the structure slows and the HRR drops.
+
+From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW), when the rear door is opened in the the baseline (solid line) case.
+The opening of the rear door coincides with a breach on the beta side of the structure.
+The open door and breach act as additional pressure releases for the structure.
+The high pressure unburned fuel inside the structure flows toward ambient pressure of the external environment.
+The fuel mixes with oxygen, burns, and the HRR spikes from about 7 MW to 9.7 MW at 139 seconds.
+As the pressure differential drops, the HRR correspondingly drops toward 9 MW at 160 seconds.
+In the case where the rear door and beta wall penetration do not occur, the HRR steadily climbs from 7 MW at 130 seconds to 9 MW at 160 seconds.
+At the time of door failure, the HRR in both cases was approximately 9 MW. While there is more total energy released in the case where the back door was opened, at the
 
@@
 \end{figure}
-
-%Just prior to the back door being opened, the HRR was 6.6 MW.
-This is below the specified HRR of 12.3 MW, indicated that the fire was under-ventilated.
-From the time the back doored was opened to estimated time the interior door failed (approximately 30 seconds), the HRR increased by approximately 35 \% to 8.9 MW.
 

### 2014-03-10 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: minor update to report

@@
 Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires \cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
+NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
 The overriding objective of all of these studies is to improve the safety of fire fighters.
@@
 \chapter{Fire Incident Summary}
-The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \cite{NIOSH:Bowyer}.
+The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
 
@@
 \end{tabular}\par
-\big-skip
+\bigskip
 \end{minipage}
@@
 
-The development of the model geometry and development of the input file is straight forward with guidance from the FDS users' manual \cite{FDS_Users_Guide} or third party software.
+The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide  \cite{FDS_Users_Guide} or third party software.
 Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
@@
 \item physical and thermal properties of fuels such as interior finish and furnishings
-	\begin{itemize}
-	\item density
-	\item specific heat
-	\item thermal conductivity
-	\item ignition temperature
-	\item heat of combustion
-	\item heat release rate
-	\item mass loss rate under various fire conditions
-	\item pyrolyzate/combustion product emissions
-	\item response to thermal exposures
-	\item activation energy
-	\end{itemize}
 \end{itemize}
@@
 \begin{minipage}{.8\linewidth}
-\centering
 \captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
@@
 \label{geom}
-The structure was a 2 $\tfrac{1}{2}$ story residential structure with balloon frame construction and a wood gable roofing system.
+The structure was a 2 1/2 story residential structure with balloon frame construction and a wood gable roofing system.
 The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint.

### 2014-03-11 Studies/Chicago_2012/Report/Chicago_Fire.tex
Chicago Fire: working on tables

@@
 After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.
-Engine 123 arrived on scene at approximately 17:19.
-The victims were part of the Engine 123 crew.
-The BC met the Captain and the Fire Fighter (victims) at the front door to the structure.
-Then the Captain and Fire Fighter took their hose line to the second floor of the structure.
+Engine 123 (E123) arrived on scene at approximately 17:19.
+The victims were part of the E123 crew.
+The BC met the Captain and the Firefighter (victims) at the front door to the structure.
+Then the Captain and Firefighter took their hose line to the second floor of the structure.
 At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
-Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL 39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
-The fire fighter from TL 39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
-Both doors remain open and the fire fighter from TL 39 exits the structure.
-Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the Engine 123 Captain at 17:23, to alert him to the fire conditions and to advise him that Engine 49 would be applying water to the fire on the rear of the structure from the exterior.
-No response was made by the Engine 123 Captain.
-It is believed that the door between the rear porch and the second floor hallway, where the Engine 123 Captain and Fire Fighter were located may have failed by this time.
-Approximately a minute later Engine 49 applied water to the fire in the attic.
+Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
+The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
+Both doors remain open and the firefighter from TL39 exits the structure.
+Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior.
+No response was made by the E123 Captain.
+It is believed that the door between the rear porch and the second floor hallway, where the E123 Captain and firefighter were located may have failed by this time.
+Approximately a minute later E49 applied water to the fire in the attic.
 
-Squad 5 entered the front of the structure at approximately 17:25 and headed to the second floor.
-They heard a commotion and found the Engine 123 Captain collapsed on the kitchen floor and entangled with the Engine 123 firefighter.
-A Mayday was called on the radio by Squad 5 at approximately  17:27 and the Engine 123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
+Squad 5 (S5) entered the front of the structure at approximately 17:25 and headed to the second floor.
+They heard a commotion and found the E123 Captain collapsed on the kitchen floor and entangled with the E123 firefighter.
+A Mayday was called on the radio by S5 at approximately  17:27 and the E123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
 Table~\ref{tab:fire_info} presents the timeline of the fire.
 
-\bigskip 
-\begin{minipage}{.8\linewidth}
+\begin{table}[!h]
 \centering
 \captionof{table}{Fire Event Timeline}\label{tab:fire_info}
-\begin{tabular}{c m{0.25in}}
+\begin{tabularx}{0.8\textwidth}{c p{3cm}}
 \toprule[1.5pt]
@@
 17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
-17:21:00 & Engine 123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
+17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
 17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
-17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from Engine 123: Capt. or FF. \\
+17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
 17:24    & Water applied to attic from the rear exterior position. \\
 17:27    & IC calls a Mayday \\
-17:29    & Engine 123 Capt. carried out of structure. \\
+17:29    & E123 Capt. carried out of structure. \\
 \bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
+\end{tabularx}
+\end{table}
 

### 2014-03-14 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: rename directory, update report and python

--- 2014-03-11 Studies/Chicago_2012/Report/Chicago_Fire.tex
@@
 
-\begin{table}[!h]
+\bigskip 
+\begin{minipage}{.8\linewidth}
 \centering
 \captionof{table}{Fire Event Timeline}\label{tab:fire_info}
-\begin{tabularx}{0.8\textwidth}{c p{3cm}}
+\begin{tabular}{c m{0.25in}}
 \toprule[1.5pt]
@@
 17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
-17:16    & Dispatch for a {\bf Still Alarm} \\
+17:16    & Dispatch for a Still Alarm \\
 17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
@@
 \bottomrule[1.25pt]
-\end{tabularx}
-\end{table}
+\end{tabular}\par
+\bigskip
+\end{minipage}
 
@@
 Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
-One of the most important advantages of FDS is that it is  mathematically verified \cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Validation_Guide}.
-A complete description of the FDS model is given in reference \cite{FDS_Math_Guide}.
+One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
+A complete description of the FDS model is given in reference~\cite{FDS_Math_Guide}.
 
-Smokeview is a software tool designed to visualize the results of the FDS \cite{Smokeview_Users_Guide}.
+Smokeview is a software tool designed to visualize the results of the FDS~\cite{Smokeview_Users_Guide}.
 Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
@@
 
-The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide  \cite{FDS_Users_Guide} or third party software.
+The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide ~\cite{FDS_Users_Guide} or third party software.
 Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
@@
 The structure was a 2 1/2 story residential structure with balloon frame construction and a wood gable roofing system.
-The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint.
+The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
+Fig.~(\ref{fig:simp_geom})).
 This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
@@
 There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
+Entry to the structure can be made either in the front (Alpha side) or rear (Charlie side).
+The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch (cf.
+Fig.~(\ref{fig:simp_geom})).
+A second floor interior door, connecting the rear porch and the hallway, failed and rapidly changed the tenability conditions for firefighters present on the second floor.
+More discussion on interior conditions can be found in Chapter~\ref{results}.
 Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
 Note that the majority of the damage is to the structure's attic.
+
+\begin{figure}[h!]
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+\includegraphics[width=6in]{../Figures/Simple_1_metric} \\
+\includegraphics[width=6in]{../Figures/Simple_2_metric}
+\end{tabular*}
+\caption{Top view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified.}
+\label{fig:simp_geom}
+\end{figure}
 
@@
 To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
-Post-incident, the fire investigation concluded that the fire originated in the structure's attic \cite{NIOSH:Bowyer}.
+Post-incident, the fire investigation concluded that the fire originated in the structure's attic~\cite{NIOSH:Bowyer}.
 Post-fire pictures revealed extensive damage to the attic and second floor rear porch (cf.
@@
 
-If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
+If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook~\cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
 
@@
 
-The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}.
+The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the energy release per unit mass of the fuel.
@@
 This means that fuel and air react to form only CO$_2$, CO, H$_2$O, Soot, and N$_2$.
-If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them \cite{FDS_Users_Guide}.
+If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
 Based on above input lines FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism  states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach \cite{FDS_Math_Guide}.
+This mechanism  states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
 While FDS provides users to the option to use a more complex finite-rate combustion mechanism, we do not have sufficient evidence to justify deviating from the default specifications.
 
-To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson \cite{babrauskas1990}.
+To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
 Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRRPUA (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
+Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples~\cite{babrauskas1990}, similar to that of Douglas Fir plywood.
 Based on the range of heat flux exposures, the data was fit to determine HRRPUA ($y$) as a function of exposure ($x$):
@@
 For Douglas Fir plywood these values were found to be 1.43 and 22 respectively.
-Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$ \cite{tsaidrysdale}.
+Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$~\cite{tsaidrysdale}.
 If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ because of under-ventilated conditions within the structure, then following Eq.~\ref{eq:heat_flux} the average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
@@
 To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ plus there is 105 m$^2$ of floor area in the attic.
+Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1453 ft$^2$) plus there is 105 m$^2$ (1130 ft$^2$) of floor area in the attic.
 Examination of post incident images showed that the floor immediately over the back porch burned away.
@@
 Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$).
+To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$ (463 ft$^2$)).
 Using an HRRPUA of wood of 51 kW/m$^2$, results in a fire size of 9 MW.
-To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$).
-The total area is 64 m$^2$.
+To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$ (258 ft$^2$)).
+The total area is 64 m$^2$ (689 ft$^2$).
 Using the same HRRPUA of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
@@
 While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
-In this study, we define gypsum \cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood \cite{Incropera:1} for the unfinished portions of the attic and rear porch.
+In this study, we define gypsum~\cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
 The text provided below are the lines necessary to define these materials in an FDS input file.
@@
 There are two ventilation scenarios that are considered in this study.
-The first is the baseline case where the ventilation times and ventilation areas represent our best understanding of the incident.
-The second case does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
+The first is the baseline simulation where the ventilation times and ventilation areas represent our best understanding of the incident.
+The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
-Structure leakage has been shown to be important when modeling enclosure fires \cite{beal2009}.
+Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
 The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of structure of this type.
@@
 \toprule[1.5pt]
-Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Type & Structure Side \\
+Baseline Simulation & Alternative Simulation & Ventilation Area [m$^2$] & Type & Structure Side \\
 \midrule
-0:00    &  0:00  & 0.11 & Window      & Charlie \\
-0:40    &  0:40  & 0.08 & Breach (x2) & Alpha and Charlie \\
-0:45    &  0:45  & 0.12 & Breach      & Beta \\
-0:55    &  0:55  & 0.12 & Breach      & Charlie \\     
-2:10    &  N/A   & 1.41 & Door        & Charlie \\
-2:15    &  N/A   & 0.2  & Breach      & Beta \\        
-2:40    &  2:40  & 0.80 & Door        & Interior \\
-5:00    &  5:00  & \multicolumn{3}{c}{Simulation Ends}  \\
+00    &  00   & 0.11 & Window      & Charlie \\
+40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
+45    &  45   & 0.12 & Breach      & Beta \\
+55    &  55   & 0.12 & Breach      & Charlie \\     
+130   &  N/A  & 1.41 & Door        & Charlie \\
+135   &  N/A  & 0.2  & Breach      & Beta \\        
+160   &  160  & 0.80 & Door        & Interior \\
+300   &  300  & \multicolumn{3}{c}{Simulation Ends}  \\
 \bottomrule[1.25pt]
@@
 \end{equation}   
-From the FDS User Guide \cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
+From the FDS User Guide~\cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
 relation $Q^* = (D^*/D)^{5/2}$.'' Here, $D$ is the physical diameter of the fire as input to the model.
@@
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16 \cite{NUREG_1824}.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 1~\cite{NUREG_1824}.
 The grid resolution used in the model falls within typical, engineering $D^*/\dx$ values.
@@
 
-As discussed Section~\ref{geom}, the structure has 17.15 m by 6.15 m footprint with a total height of 8.56 m.
+As discussed Section~\ref{geom}, the structure has 17.15 m (56 ft) by 6.15 m (20ft) footprint with a total height of 8.56 m (28 ft).
 To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
-The total volume of the computational domain is 24 m by 10 m by 10 m.
-At 10 cm resolution this would result in 2.4 million computational cells.
+The total volume of the computational domain is 24 m (79 ft) by 10 m (33 ft) by 10 m (33 ft).
+At 10 cm (3.9 in) resolution this would result in 2.4 million computational cells.
 To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m by 10 m by 5 m.}
+\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m (9.8 ft) by 10 m (33 ft) by 5 m (16.4 ft).}
 \label{fig:mult_mesh}
@@
 \chapter{Model Results}
+\label{results}
 
@@
 
-In Fig.~(\ref{fig:hrr}), the solid line is the FDS HRR from the venting conditions that represent our attempt to model the on-scene conditions.
-The dashed line represents the case where the rear door opening and subsequent beta side breach do not occur.
+In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions).
+The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur.
 The dash-dotted line is the prescribed FDS input HRR.
 We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR.
-The HRR first peaks at just under 9 MW at approximately 20 seconds into the simulation.
-The HRR proceeds to drop to 5 MW as the available oxygen inside the structure gets consumed.
-There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs at then vents.
+The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited.
+The HRR drops to 5 MW as the available oxygen inside the structure gets consumed.
+There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents.
 Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
-Despite the fire becoming under-ventilated, the mass flow rate of fuel into the structure remains constant.
-As a result there is a buildup of pressure and excess fuel within the attic and back porch.
-After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the HRR spikes to 9 MW before again dropping to about 6 MW.
-This peak occurs because the additional vents provide pathways for pressure relief.
-Unburned fuel at above ambient pressure flow out of the structure, mix with oxygen, and react.
-As the pressure drops, the flow of fuel out of the structure slows and the HRR drops.
+After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW.
+The HRR then begins to increase towarda a sustainable steady state value.
 
-From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW), when the rear door is opened in the the baseline (solid line) case.
-The opening of the rear door coincides with a breach on the beta side of the structure.
+From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW).
+At 130 seconds the rear door is opened in the baseline simulation.
+At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}).
 The open door and breach act as additional pressure releases for the structure.
-The high pressure unburned fuel inside the structure flows toward ambient pressure of the external environment.
-The fuel mixes with oxygen, burns, and the HRR spikes from about 7 MW to 9.7 MW at 139 seconds.
-As the pressure differential drops, the HRR correspondingly drops toward 9 MW at 160 seconds.
-In the case where the rear door and beta wall penetration do not occur, the HRR steadily climbs from 7 MW at 130 seconds to 9 MW at 160 seconds.
-At the time of door failure, the HRR in both cases was approximately 9 MW. While there is more total energy released in the case where the back door was opened, at the
+Again, the abrupt change in ventilation causes the HRR to spike.
+Here we see a rise from 7 MW to 9.7 MW at 139 seconds.
+At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases.
+While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door.
 
@@
 \section{Temperature}
+
+\begin{figure}[h!]
+\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_129}
+\input{../Scripts/colorbar_metric} 
+\caption{Temperature 1 second prior to rear door opening.}
+\label{fig:temp_129s}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_159}
+\input{../Scripts/colorbar_metric} 
+\caption{Temperature 1 second prior to interior door failing.}
+\label{fig:temp_159s}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_161}
+\input{../Scripts/colorbar_metric} 
+\caption{Temperature 1 second after interior door fails.}
+\label{fig:temp_161s}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
+\input{../Scripts/colorbar_std} 
+\input{../Scripts/colorbar_metric}
+\caption{Temperature 15 seconds after interior door fails.}
+\label{fig:temp_175s}
+\end{figure}
 

### 2014-03-14 Studies/2012_Chicago/Scripts/chicago_hrr.py

@@ -1,0 +1,53 @@
+#Weinschenk
+#8-7-13
+
+import numpy as np
+import matplotlib.pyplot as plt
+from matplotlib import rc
+rc('font',**{'family':'serif','serif':['Times New Roman'],'size':16})
+
+def movingaverage(interval, window_size):
+    window= np.ones(int(window_size))/float(window_size)
+    return np.convolve(interval, window, 'same')
+
+C_FDS = np.genfromtxt('../FDS_Output_Files/west_50th_baseline_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR = C_FDS['HRR']/1000
+HRR_avg = movingaverage(HRR,2)
+
+ND_FDS = np.genfromtxt('../FDS_Output_Files/west_50th_norear_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR_ND = ND_FDS['HRR']/1000
+HRR_ND_avg = movingaverage(HRR_ND,2)
+
+HRR_theo = [None]*1000
+HRR_time = list(xrange(1000))
+
+for i in range (0, 999):
+	if i <= 10:
+		HRR_theo[i] = (9./10)*i
+	elif i > 10 and i <= 40:
+		HRR_theo[i] = 9
+	elif i > 40 and i <= 50:
+		HRR_theo[i] = 9 + (3.3/10)*(i-40)
+	else:
+		HRR_theo[i] = 12.3
+
+print HRR_avg[129],HRR_avg[161],HRR_ND_avg[161]
+
+plt.figure
+plt.plot(HRR_time,HRR_theo,'b-.',mfc='none',label='Prescribed HRR',linewidth=2)
+plt.plot(C_FDS['Time'],HRR_avg,'r-',mfc='none',label='FDS Model HRR (Baseline Simulation)',linewidth=2)
+plt.plot(ND_FDS['Time'],HRR_ND_avg,'g--',mfc='none',label='FDS Model HRR (Alternative Simulation)',linewidth=2)
+plt.text(98, 2, 'Rear Door Open', 
+	 horizontalalignment='center',
+     verticalalignment='center')
+plt.text(195, 2, 'Interior Door Fail', 
+	 horizontalalignment='center',
+     verticalalignment='center')
+plt.axvline(x=130, ymin=0, ymax=12.3/20,linestyle='-',linewidth=2,color = '#000000')
[…]

### 2014-03-14 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co Fire: update name

--- 2014-03-11 Studies/Chicago_2012/Report/Chicago_Fire.tex
@@
 
-\input{../../../Bibliography/commoncommands}
+\input{../Bibliography/commoncommands}
 
@@
 \renewcommand{\sb}[1]{_\mathrm{#1}}
-\renewcommand{\C}{\mbox{C}}
-\renewcommand{\H}{\mbox{H}}
-\renewcommand{\O}{\mbox{O}}
-\newcommand{\N}{\mbox{N}}
 
@@
 \headerB{
-Simulation of the Dynamics of an \\
-Attic Fire in a 2 1/2 Story Wood \\
-Frame Residential Structure \\
-Chicago, IL \\
+Fire Investigation\\
+Title\\
 }
@@
 \flushright{
-Craig G. Weinschenk \\
-Daniel Madrzykowski \\
-Kristopher J. Overholt \\
+Authors \\
 {\em Fire Research Division \\
@@
 \flushright{
-\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+\includegraphics[width=2.in]{../Bibliography/nistident_flright_vec} \\[.3in]
 }
@@
 
-\cleardoublepage
+\clearpage
 \phantomsection
@@
 \hspace{1.5in} \= \\
-BC \> Battalion Chief \\
 FDS \> Fire Dynamics Simulator \\
@@
 HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
 NIST \> National Institute of Standards and Technology \\
-SFPE \> Society of Fire Protection Engineers \\
 \end{tabbing}
@@
 \chapter{Introduction}
-Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
-The overriding objective of all of these studies is to improve the safety of fire fighters.
-
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-Changes in the ventilation flow path caused a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
-NIST assisted with examining the fire dynamics of this incident.
-NIST performed computer simulations of the fire using Fire Dynamics Simulator and Smokeview, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
-The specific objectives of the simulations detailed in this report are:
-\begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the thermal and fire conditions in this multi-story residential structure.
-\item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
-\end{enumerate}
-This document describes the input and the results of the FDS (version 6.0.0) simulations.
 
 \chapter{Fire Incident Summary}
-The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
-
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.
-At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.
-Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.
-After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.
-Engine 123 (E123) arrived on scene at approximately 17:19.
-The victims were part of the E123 crew.
-The BC met the Captain and the Firefighter (victims) at the front door to the structure.
-Then the Captain and Firefighter took their hose line to the second floor of the structure.
-At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
-Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
-The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
-Both doors remain open and the firefighter from TL39 exits the structure.
-Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior.
-No response was made by the E123 Captain.
-It is believed that the door between the rear porch and the second floor hallway, where the E123 Captain and firefighter were located may have failed by this time.
-Approximately a minute later E49 applied water to the fire in the attic.
-
-Squad 5 (S5) entered the front of the structure at approximately 17:25 and headed to the second floor.
-They heard a commotion and found the E123 Captain collapsed on the kitchen floor and entangled with the E123 firefighter.
-A Mayday was called on the radio by S5 at approximately  17:27 and the E123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
-Table~\ref{tab:fire_info} presents the timeline of the fire.
-
-\begin{table}[!h]
-\centering
-\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
-\begin{tabularx}{0.8\textwidth}{c p{3cm}}
-\toprule[1.5pt]
-Incident Time & Fire Behavior / Fireground Operation  \\
-\midrule
-17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
-17:16    & Dispatch for a {\bf Still Alarm} \\
-17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
-17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
-17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
-17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
-17:24    & Water applied to attic from the rear exterior position. \\
-17:27    & IC calls a Mayday \\
-17:29    & E123 Capt. carried out of structure. \\
-\bottomrule[1.25pt]
-\end{tabularx}
-\end{table}
 
 \chapter{Fire Dynamics Simulator and Smokeview}
-FDS is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
-Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
-The cells are contained together within one larger volume known as a computational domain.
-The CFD model computes the density, velocity, temperature, pressure and species concentration of the gas in each cell.
-Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
-One of the most important advantages of FDS is that it is  mathematically verified \cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data \cite{FDS_Validation_Guide}.
-A complete description of the FDS model is given in reference \cite{FDS_Math_Guide}.
-
-Smokeview is a software tool designed to visualize the results of the FDS \cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
-Smokeview allows the fire and fire movement to be visualized.
-This is done by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
-Smokeview also visualizes static data at particular times using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
 
 \chapter{Model Input Parameters}
-Input data from a number of sources must be collected and documented in order to simulate a fire with FDS or any other model. 
-From the fire scene the following information must be gathered:
-\begin{itemize}
-\item The geometry of the building and the compartments being modeled.
-\item The size and location of exterior and interior ventilation openings. 
-\item Documentation and identification of the fuels used in the construction and finish of the building and their installed location
-\item Documentation and identification of the fuels used as the contents of the building. 
-\item Area of origin and approximate size of ignition source.
-\item Documentation of fire damage to the building, fuel loads, victims or equipment.
-\end{itemize}
-From witnesses, first responders, reports, and recorded media such as fire ground radios or videos:
-\begin{itemize}
-\item Information on the timing of the fire development
-\item Order and timing of ventilation opening to the outside
-\item Weather conditions at the time of the fire
-\end{itemize}
-To develop the simulation, a timeline of events based on the collected information must be developed.
-From this time line actions may be input into the model, such as venting a window at a given time.
-
-The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide  \cite{FDS_Users_Guide} or third party software.
-Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
-Examples of these requirements include:
-\begin{itemize}
-\item the computational cell size
-\item model domain and boundaries conditions
-\item the heat release rate (HRR) of the ignition source/initial fire
-\item physical and thermal properties of fuels such as interior finish and furnishings
-\end{itemize}
-Since there is no all-inclusive, universal fire modeling input data base this type of information must be gathered from literature or generated for a given incident.
-For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters.
-The sections below describe these inputs.
-
-\bigskip
-\begin{minipage}{.8\linewidth}
-\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
-\begin{tabular}{lll}
-\toprule[1.5pt]
-Parameter & Description & Reference  \\
-\midrule
- Simulation Time           & 5 minutes                             & -- \\[.25cm]
- Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
-                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
-                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
-\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
-                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
-                                   & $\rho$: 510 \; kg/m$^3$         & \\
-                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
-                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-\section{Geometry}
-\label{geom}
-The structure was a 2 1/2 story residential structure with balloon frame construction and a wood gable roofing system.
-The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint.
-This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
-Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
-Additionally there was a half-story attic that was used to house the structure's hot water heater.
-There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
-Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
-Note that the majority of the damage is to the structure's attic.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_alpha}
-\caption{Photograph showing the post-incident front (side alpha) exterior of the structure.}
-\label{fig:alpha_ex}
-\end{figure}
-
-Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}) show the interior dimensions of the first and second floor, respectively.
-The dimensions were found from on-scene measurements using a tape measure.
-Measurements were made to the nearest 1.27 cm (0.5 in).
-Based on difficulty of making some of the measurements due to the condition of the post-fire structure, the uncertainty in the measurements is estimated to be on the order of $\pm$ 1 \%.
-This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in).
-When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
-
-%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%\begin{figure}[h!]
-%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-%\end{tabular*}
-%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-%\label{fig:smv_interior}
-%\end{figure}
-
-\section{Fire}
-\label{fire}
-
-To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
-Post-incident, the fire investigation concluded that the fire originated in the structure's attic \cite{NIOSH:Bowyer}.
-Post-fire pictures revealed extensive damage to the attic and second floor rear porch (cf.
-Fig.~(\ref{fig:charlie_ex})).
-Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_charlie}
-\caption{Photograph showing the post-incident rear (side charlie) exterior of the structure.}
-\label{fig:charlie_ex}
-\end{figure}
-
-If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook \cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
-
-\begin{multline}
-\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
-\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
-\label{eq:wood_comb}
-\end{multline}
-
-The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook \cite{SFPE:Tewarson}.
-The heat of combustion quantifies the energy release per unit mass of the fuel.
-The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
-
-\begin{lstlisting}
-&SPEC ID = 'WOOD', FORMULA = 'CH1.7O0.74N0.002' /
-
-&REAC ID = 'wood' 
-    FUEL = 'WOOD', 
-    HEAT_OF_COMBUSTION=16400,
-    SOOT_YIELD = 0.015,
-    CO_YIELD = 0.004/
-\end{lstlisting}
-
-Note that using the input lines above will invoke the simple chemistry reaction balance in FDS.
-This means that fuel and air react to form only CO$_2$, CO, H$_2$O, Soot, and N$_2$.
-If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them \cite{FDS_Users_Guide}.
-Based on above input lines FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism  states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach \cite{FDS_Math_Guide}.
-While FDS provides users to the option to use a more complex finite-rate combustion mechanism, we do not have sufficient evidence to justify deviating from the default specifications.
-
-To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson \cite{babrauskas1990}.
-Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRRPUA (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples \cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-Based on the range of heat flux exposures, the data was fit to determine HRRPUA ($y$) as a function of exposure ($x$):
-
-\begin{equation}
-y = ax+b
-\label{eq:heat_flux}
-\end{equation}
-
-In Eq.~\ref{eq:heat_flux}, $a$ and $b$ are experimental constants.
-For Douglas Fir plywood these values were found to be 1.43 and 22 respectively.
-Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$ \cite{tsaidrysdale}.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ because of under-ventilated conditions within the structure, then following Eq.~\ref{eq:heat_flux} the average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
-
-To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ plus there is 105 m$^2$ of floor area in the attic.
-Examination of post incident images showed that the floor immediately over the back porch burned away.
-That area will be considered as part of the porch fire.
-Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$).
-Using an HRRPUA of wood of 51 kW/m$^2$, results in a fire size of 9 MW.
-To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$).
-The total area is 64 m$^2$.
-Using the same HRRPUA of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
-The total fire size for this structure is estimated to be 12.3 MW.
-Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
-First is that the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
-The porch fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
-A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
-The second is that the sources of the gas phase wood fuel are of fixed area and at fixed locations (2 sources for attic, 1 source for porch).
-The following lines define the source fires for an FDS input file:
-
-\begin{lstlisting}
-&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE',TAU_Q=10 /
-&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE',DEVC_ID='SECOND FIRE'/ 1.5 m^2
-&DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
-\end{lstlisting}
-Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes of a specific area.
-
-\section{Materials}
-\label{matl}
-While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
-In this study, we define gypsum \cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood \cite{Incropera:1} for the unfinished portions of the attic and rear porch.
-The text provided below are the lines necessary to define these materials in an FDS input file.
-
-\begin{lstlisting}
-&MATL ID        = 'GYPSUM'
-    FYI = 'Quintiere, Fire Behavior' 
-    CONDUCTIVITY    = 0.48
-    SPECIFIC_HEAT   = 0.84
-    DENSITY = 1440./
-
-&MATL ID        = 'WOOD_MAT'
-    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
-    CONDUCTIVITY    = 0.12
-    SPECIFIC_HEAT   = 1.38
-    DENSITY = 510./ 
-\end{lstlisting}
-
-\section{Vents}
-\label{Vents}
-This simulation includes vents that account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
-There are two ventilation scenarios that are considered in this study.
-The first is the baseline case where the ventilation times and ventilation areas represent our best understanding of the incident.
-The second case does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
-The times of the ventilation changes are provided in Table \ref{tab:vents}.
-Structure leakage has been shown to be important when modeling enclosure fires \cite{beal2009}.
-The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of structure of this type.
-Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
-
-\bigskip
-\begin{minipage}{.8\linewidth}
-\centering
-\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
-\begin{tabular}{ccccc}
-\toprule[1.5pt]
-Baseline & No Rear Door Open & Ventilation Area [m$^2$] & Type & Structure Side \\
-\midrule
-0:00    &  0:00  & 0.11 & Window      & Charlie \\
-0:40    &  0:40  & 0.08 & Breach (x2) & Alpha and Charlie \\
-0:45    &  0:45  & 0.12 & Breach      & Beta \\
-0:55    &  0:55  & 0.12 & Breach      & Charlie \\     
-2:10    &  N/A   & 1.41 & Door        & Charlie \\
-2:15    &  N/A   & 0.2  & Breach      & Beta \\        
-2:40    &  2:40  & 0.80 & Door        & Interior \\
-5:00    &  5:00  & \multicolumn{3}{c}{Simulation Ends}  \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-\section{Mesh}
-\label{mesh}
-
-For the simulation in this study, we can estimate a measure of how well the flow field is resolved by the non-dimensional expression $D^*/\dx$.
-Here $D^*$ is a characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
-\begin{equation}
-D^* = \left(
-     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
-     \right)^\frac{2}{5} 
-\label{eq:mesh}
-\end{equation}   
-From the FDS User Guide \cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.'' Here, $D$ is the physical diameter of the fire as input to the model.
-Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the characteristic fire diameter to cell size ratio based on the 3.3 MW porch fire is 15.5 and for the 9 MW fire is 23.
-Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16 \cite{NUREG_1824}.
-The grid resolution used in the model falls within typical, engineering $D^*/\dx$ values.
-As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
-Fig.~(\ref{fig:geom_grid}) shows the
-alpha side (front) of the structure rendered in Smokeview with the 10 cm mesh.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
-\caption{Alpha side of the structure with 10 cm computation mesh.}
-\label{fig:geom_grid}
-\end{figure}
-
-As discussed Section~\ref{geom}, the structure has 17.15 m by 6.15 m footprint with a total height of 8.56 m.
-To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
-The total volume of the computational domain is 24 m by 10 m by 10 m.
-At 10 cm resolution this would result in 2.4 million computational cells.
-To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
-Fig.~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m by 10 m by 5 m.}
-\label{fig:mult_mesh}
-\end{figure}
 
@@
 
-\section{Heat Release Rate}
-\label{HRR}
-The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation.
-Here, we examine the data to examine the impact of ventilation on fire size.
-Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
-The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-\caption{HRR versus time of FDS model of the West 50th St. fire. The first vertical line indicates when the back door failed, the second indicates when the interior hallway door failed.}
-\label{fig:hrr}
-\end{figure}
-
-In Fig.~(\ref{fig:hrr}), the solid line is the FDS HRR from the venting conditions that represent our attempt to model the on-scene conditions.
-The dashed line represents the case where the rear door opening and subsequent beta side breach do not occur.
-The dash-dotted line is the prescribed FDS input HRR.
-We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR.
-The HRR first peaks at just under 9 MW at approximately 20 seconds into the simulation.
-The HRR proceeds to drop to 5 MW as the available oxygen inside the structure gets consumed.
-There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs at then vents.
-Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
-Despite the fire becoming under-ventilated, the mass flow rate of fuel into the structure remains constant.
-As a result there is a buildup of pressure and excess fuel within the attic and back porch.
-After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the HRR spikes to 9 MW before again dropping to about 6 MW.
-This peak occurs because the additional vents provide pathways for pressure relief.
-Unburned fuel at above ambient pressure flow out of the structure, mix with oxygen, and react.
-As the pressure drops, the flow of fuel out of the structure slows and the HRR drops.
-
-From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW), when the rear door is opened in the the baseline (solid line) case.
-The opening of the rear door coincides with a breach on the beta side of the structure.
-The open door and breach act as additional pressure releases for the structure.
-The high pressure unburned fuel inside the structure flows toward ambient pressure of the external environment.
-The fuel mixes with oxygen, burns, and the HRR spikes from about 7 MW to 9.7 MW at 139 seconds.
-As the pressure differential drops, the HRR correspondingly drops toward 9 MW at 160 seconds.
-In the case where the rear door and beta wall penetration do not occur, the HRR steadily climbs from 7 MW at 130 seconds to 9 MW at 160 seconds.
-At the time of door failure, the HRR in both cases was approximately 9 MW. While there is more total energy released in the case where the back door was opened, at the
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/smv_exterior_fire}
-\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
-\label{fig:smv_ext_fire}
-\end{figure}
-
-\section{Temperature}
-
-\section{Pressure}
-
 \chapter{Discussion}
-
-\section{Conditions in Hallway}
-
-\section{Tactical Considerations}
 
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,chicago}
+\bibliography{../Bibliography/FDS_refs,../Bibliography/FDS_general,../Bibliography/FDS_mathcomp}
 
@@
 
-\chapter{Dimensioned Drawings}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption {Dimensioned drawing of 1$^{st}$ floor}
-\label{fig:first_floor}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption {Dimensioned drawing of 2$^{nd}$ floor}
-\label{fig:second_floor}
-\end{figure}
-
 \end{document}

### 2014-03-17 Studies/2012_Chicago/Report/run_all.sh
Chicago Fire: update report and images, add run all script

@@ -1,0 +1,39 @@
+#!/bin/bash
+python ../Scripts/chicago_hrr.py
+
+clean_build=1
+
+# Build FDS Verification Guide
+pdflatex -interaction nonstopmode Chicago_Fire &> Chicago_Fire.err
+bibtex Chicago_Fire &> Chicago_Fire.err
+pdflatex -interaction nonstopmode Chicago_Fire &> Chicago_Fire.err
+pdflatex -interaction nonstopmode Chicago_Fire &> Chicago_Fire.err
+
+# Scan and report any errors in the LaTeX build process
+if [[ `grep -E "Error:|Fatal error|! LaTeX Error:|Paragraph ended before|Missing \\\$ inserted|Misplaced" -I Chicago_Fire.err | grep -v "xpdf supports version 1.5"` == "" ]]
+   then
+      # Continue along
+      :
+   else
+      echo "LaTeX errors detected:"
+      grep -E "Error:|Fatal error|! LaTeX Error:|Paragraph ended before|Missing \\\$ inserted|Misplaced" -I Chicago_Fire.err | grep -v "xpdf supports version 1.5"
+      clean_build=0
+fi
+
+# Check for LaTeX warnings (undefined references or duplicate labels)
+if [[ `grep -E "undefined|multiply defined|multiply-defined" -I Chicago_Fire.err` == "" ]]
+   then
+      # Continue along
+      :
+   else
+      echo "LaTeX warnings detected:"
+      grep -E "undefined|multiply defined|multiply-defined" -I Chicago_Fire.err
+      clean_build=0
+fi
+
+if [[ $clean_build == 0 ]]
+   then
+      :
+   else
+      echo "Chicago_Fire built successfully!"
+fi    

### 2014-03-17 Studies/2012_Chicago/Scripts/chicago_hrr.py

@@ -31,7 +31,7 @@ for i in range (0, 999):
 	else:
 		HRR_theo[i] = 12.3
 
-print HRR_avg[129],HRR_avg[161],HRR_ND_avg[161]
+#print HRR_avg[129],HRR_avg[161],HRR_ND_avg[161]
 
 plt.figure
 plt.plot(HRR_time,HRR_theo,'b-.',mfc='none',label='Prescribed HRR',linewidth=2)

### 2014-03-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update report and images, add run all script
Chicago Fire: add 2 figures, update report

@@
 After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW.
-The HRR then begins to increase towarda a sustainable steady state value.
+The HRR then begins to increase towards a sustainable steady state value.
 
@@
 While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door.
+Therefore, further more detailed analysis will focus on the results of the baseline simulation results.
 
@@
 \centering
-\includegraphics[width=.80\textwidth]{../Figures/smv_exterior_fire}
+\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
 \caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
@@
 \section{Temperature}
+The focus area for analysis of the temperature simulation results are the attic, the rear porch and connecting stairwell, and the interior hallways which connects the rear porch to the front stairwell.
 
-\begin{figure}[h!]
-\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_129}
+\begin{figure}[!ht]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
+\input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature 1 second prior to rear door opening.}
+\caption{Temperature from baseline simulation, 1 second prior to rear door opening.}
 \label{fig:temp_129s}
@@
 
-\begin{figure}[h!]
-\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_159}
+\begin{figure}[!ht]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
+\input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature 1 second prior to interior door failing.}
+\caption{Temperature from baseline simulation, 1 second prior to interior door failing.}
 \label{fig:temp_159s}
@@
 
-\begin{figure}[h!]
-\includegraphics[width=.8\textwidth]{../Figures/west_50th_baseline_161}
+\begin{figure}[!ht]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
+\input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature 1 second after interior door fails.}
+\caption{Temperature from baseline simulation, 1 second after interior door fails.}
 \label{fig:temp_161s}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature 15 seconds after interior door fails.}
+\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
 \label{fig:temp_175s}

### 2014-03-19 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: minor report update

@@
 While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door.
-Therefore, further more detailed analysis will focus on the results of the baseline simulation results.
+Therefore, the following analysis will focus on the results of the baseline simulation results.
 
@@
 \section{Temperature}
-The focus area for analysis of the temperature simulation results are the attic, the rear porch and connecting stairwell, and the interior hallways which connects the rear porch to the front stairwell.
+For analysis of the predicted simulation temperatures, the analysis will focus on the high hazard areas of the structure: the attic, the rear porch and connecting stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions.
+The first time to consider is just before a firefighter opened the rear porch door (cf.
+Fig.~(\ref{fig:temp_129s})).
 

### 2014-03-24 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update report

@@
 The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation.
-Here, we examine the data to examine the impact of ventilation on fire size.
+Here, we examine impact of ventilation on fire size.
 Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
@@
 The dash-dotted line is the prescribed FDS input HRR.
-We can see that within the first 10 seconds, there are under-ventilated conditions within the structure as the modeled HRR is below the prescribed HRR.
+We can see that within the first 10 seconds, the structure is under-ventilated as the modeled HRR is below the prescribed HRR.
 The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited.
@@
 At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases.
-While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters on the alpha side of the second floor porch door.
-Therefore, the following analysis will focus on the results of the baseline simulation results.
+While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters inside the structure.
+Therefore, the continued analysis will focus on the results of the baseline simulation results.
 
@@
 \section{Temperature}
-For analysis of the predicted simulation temperatures, the analysis will focus on the high hazard areas of the structure: the attic, the rear porch and connecting stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
 Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions.
-The first time to consider is just before a firefighter opened the rear porch door (cf.
-Fig.~(\ref{fig:temp_129s})).
+The first times are 129 seconds into the simulation, just before a firefighter opened the rear porch door (cf.
+Fig.~(\ref{fig:temp_129s})) and 159 seconds into the simulation, just before the interior door fails (cf.
+Fig.~(\ref{fig:temp_159s})).
 
@@
 \end{figure}
+
+The
 

### 2014-03-24 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update report, add pressure colorbar tex file, add images

@@
 There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents.
-Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
+Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40 seconds.
 After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW.
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second prior to rear door opening.}
+\caption{FDS predicted temperature contours, 1 second prior to rear door opening.}
 \label{fig:temp_129s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second prior to interior door failing.}
+\caption{FDS predicted temperature contours, 1 second prior to interior door failure.}
 \label{fig:temp_159s}
@@
 
-The
+Fig.~(\ref{fig:temp_129s}) shows temperatures of at least 260 $^{\circ}$C (500 $^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+High temperatures, between 80 $^{\circ}$C (185 $^{\circ}$F) and 200 $^{\circ}$C (390 $^{\circ}$F), also extend down to the 1$^{st}$ floor rear entrance.
+Before the interior door fails, Fig.~(\ref{fig:temp_159s}), the inflow ambient air from the open door lowers the temperature local to the doorway, but we know from Fig.~(\ref{fig:hrr}) that over this interval the HRR spikes because of the additional ventilation.
+After the second floor door fails, (cf.
+Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flows in the direction of lower pressure (the front door).
+Note that the conditions in the attic remain  We can focus on this area, (cf.
+Fig.~(\ref{fig:temp_161s})), to see the the flow of gases through the doorway.
 
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second after interior door fails.}
+\caption{FDS predicted temperature contours, 1 second after interior door fails.}
 \label{fig:temp_161s}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161v}
+\input{../Scripts/colorbar_std} 
+\input{../Scripts/colorbar_metric}
+\caption{FDS predicted temperature vectors, 1 second after interior door fails.}
+\label{fig:temp_161v}
 \end{figure}
@@
 \section{Pressure}
+
+\begin{figure}[!ht]
+\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
+\input{../Scripts/colorbar_metric_pres}
+\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
+\label{fig:pres_159s}
+\end{figure}
 

### 2014-03-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Fire: update table structure in writeup

@@
 
-\bigskip 
-\begin{minipage}{.8\linewidth}
+\begin{table}
 \centering
 \captionof{table}{Fire Event Timeline}\label{tab:fire_info}
-\begin{tabular}{c m{0.25in}}
+\begin{tabular}{l l}
 \toprule[1.5pt]
@@
 \midrule
-17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
-17:16    & Dispatch for a Still Alarm \\
-17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
-17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
-17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
-17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
-17:24    & Water applied to attic from the rear exterior position. \\
-17:27    & IC calls a Mayday \\
+\multirow{2}{*}{17:15} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+         & \\[.25cm]
+17:16    & Dispatch for a Still Alarm. \\ [.25cm]
+\multirow{2}{*}{17:20}    & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
+         & \\[.25cm] 
+17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
+17:21:30 & 1$^{st}$ floor exterior porch door opened. \\[.25cm]
+\multirow{2}{*}{17:23}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+         & \\[.25cm]
+17:24    & Water applied to attic from the rear exterior position. \\[.25cm]
+17:27    & IC calls a Mayday. \\[.25cm]
 17:29    & E123 Capt. carried out of structure. \\
@@
 \end{tabular}\par
-\bigskip
-\end{minipage}
+\end{table}
 
@@
 
-\bigskip
-\begin{minipage}{.8\linewidth}
+\begin{table}
+\centering
 \captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
@@
 
-\bigskip
-\begin{minipage}{.8\linewidth}
+\begin{table}
 \centering
@@
 160   &  160  & 0.80 & Door        & Interior \\
-300   &  300  & \multicolumn{3}{c}{Simulation Ends}  \\
 \bottomrule[1.25pt]
 \end{tabular}\par
-\bigskip
-\end{minipage}
+\end{table}
 

### 2014-04-16 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo_2014_04: Add report files

--- 2014-03-24 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 \headerB{
-Simulation of the Dynamics of an \\
-Attic Fire in a 2 1/2 Story Wood \\
-Frame Residential Structure \\
-Chicago, IL \\
+Delco 2014
 }
@@
 \flushright{
+Daniel Madrzykowski \\
 Craig G. Weinschenk \\
-Daniel Madrzykowski \\
 Kristopher J. Overholt \\
@@
 NIST \> National Institute of Standards and Technology \\
-SFPE \> Society of Fire Protection Engineers \\
 \end{tabbing}
@@
 \chapter{Introduction}
-Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
-The overriding objective of all of these studies is to improve the safety of fire fighters.
+\label{chap:Introduction}
 
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-Changes in the ventilation flow path caused a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
-NIST assisted with examining the fire dynamics of this incident.
-NIST performed computer simulations of the fire using Fire Dynamics Simulator and Smokeview, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
-The specific objectives of the simulations detailed in this report are:
-\begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the thermal and fire conditions in this multi-story residential structure.
-\item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
-\end{enumerate}
-This document describes the input and the results of the FDS (version 6.0.0) simulations.
-
-\chapter{Fire Incident Summary}
-The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
-
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.
-At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.
-Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.
-After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.
-Engine 123 (E123) arrived on scene at approximately 17:19.
-The victims were part of the E123 crew.
-The BC met the Captain and the Firefighter (victims) at the front door to the structure.
-Then the Captain and Firefighter took their hose line to the second floor of the structure.
-At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
-Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
-The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
-Both doors remain open and the firefighter from TL39 exits the structure.
-Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior.
-No response was made by the E123 Captain.
-It is believed that the door between the rear porch and the second floor hallway, where the E123 Captain and firefighter were located may have failed by this time.
-Approximately a minute later E49 applied water to the fire in the attic.
-
-Squad 5 (S5) entered the front of the structure at approximately 17:25 and headed to the second floor.
-They heard a commotion and found the E123 Captain collapsed on the kitchen floor and entangled with the E123 firefighter.
-A Mayday was called on the radio by S5 at approximately  17:27 and the E123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
-Table~\ref{tab:fire_info} presents the timeline of the fire.
-
-\bigskip 
-\begin{minipage}{.8\linewidth}
-\centering
-\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
-\begin{tabular}{c m{0.25in}}
-\toprule[1.5pt]
-Incident Time & Fire Behavior / Fireground Operation  \\
-\midrule
-17:15    & Reported working fire with heavy smoke coming from the front and rear of the structure's attic. \\
-17:16    & Dispatch for a Still Alarm \\
-17:20    & Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear. \\  
-17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\
-17:21:30 & 1$^{st}$ floor exterior porch door opened. \\
-17:23    & Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF. \\
-17:24    & Water applied to attic from the rear exterior position. \\
-17:27    & IC calls a Mayday \\
-17:29    & E123 Capt. carried out of structure. \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-\chapter{Fire Dynamics Simulator and Smokeview}
-FDS is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
-Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
-The cells are contained together within one larger volume known as a computational domain.
-The CFD model computes the density, velocity, temperature, pressure and species concentration of the gas in each cell.
-Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
-One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
-A complete description of the FDS model is given in reference~\cite{FDS_Math_Guide}.
-
-Smokeview is a software tool designed to visualize the results of the FDS~\cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
-Smokeview allows the fire and fire movement to be visualized.
-This is done by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
-Smokeview also visualizes static data at particular times using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
-
-\chapter{Model Input Parameters}
-Input data from a number of sources must be collected and documented in order to simulate a fire with FDS or any other model. 
-From the fire scene the following information must be gathered:
-\begin{itemize}
-\item The geometry of the building and the compartments being modeled.
-\item The size and location of exterior and interior ventilation openings. 
-\item Documentation and identification of the fuels used in the construction and finish of the building and their installed location
-\item Documentation and identification of the fuels used as the contents of the building. 
-\item Area of origin and approximate size of ignition source.
-\item Documentation of fire damage to the building, fuel loads, victims or equipment.
-\end{itemize}
-From witnesses, first responders, reports, and recorded media such as fire ground radios or videos:
-\begin{itemize}
-\item Information on the timing of the fire development
-\item Order and timing of ventilation opening to the outside
-\item Weather conditions at the time of the fire
-\end{itemize}
-To develop the simulation, a timeline of events based on the collected information must be developed.
-From this time line actions may be input into the model, such as venting a window at a given time.
-
-The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide ~\cite{FDS_Users_Guide} or third party software.
-Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
-Examples of these requirements include:
-\begin{itemize}
-\item the computational cell size
-\item model domain and boundaries conditions
-\item the heat release rate (HRR) of the ignition source/initial fire
-\item physical and thermal properties of fuels such as interior finish and furnishings
-\end{itemize}
-Since there is no all-inclusive, universal fire modeling input data base this type of information must be gathered from literature or generated for a given incident.
-For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters.
-The sections below describe these inputs.
-
-\bigskip
-\begin{minipage}{.8\linewidth}
-\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
-\begin{tabular}{lll}
-\toprule[1.5pt]
-Parameter & Description & Reference  \\
-\midrule
- Simulation Time           & 5 minutes                             & -- \\[.25cm]
- Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
-                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
-                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
-\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
-                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
-                                   & $\rho$: 510 \; kg/m$^3$         & \\
-                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
-                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-\section{Geometry}
-\label{geom}
-The structure was a 2 1/2 story residential structure with balloon frame construction and a wood gable roofing system.
-The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
-Fig.~(\ref{fig:simp_geom})).
-This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
-Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
-Additionally there was a half-story attic that was used to house the structure's hot water heater.
-There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
-Entry to the structure can be made either in the front (Alpha side) or rear (Charlie side).
-The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch (cf.
-Fig.~(\ref{fig:simp_geom})).
-A second floor interior door, connecting the rear porch and the hallway, failed and rapidly changed the tenability conditions for firefighters present on the second floor.
-More discussion on interior conditions can be found in Chapter~\ref{results}.
-Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
-Note that the majority of the damage is to the structure's attic.
-
-\begin{figure}[h!]
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-\includegraphics[width=6in]{../Figures/Simple_1_metric} \\
-\includegraphics[width=6in]{../Figures/Simple_2_metric}
-\end{tabular*}
-\caption{Top view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified.}
-\label{fig:simp_geom}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_alpha}
-\caption{Photograph showing the post-incident front (side alpha) exterior of the structure.}
-\label{fig:alpha_ex}
-\end{figure}
-
-Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}) show the interior dimensions of the first and second floor, respectively.
-The dimensions were found from on-scene measurements using a tape measure.
-Measurements were made to the nearest 1.27 cm (0.5 in).
-Based on difficulty of making some of the measurements due to the condition of the post-fire structure, the uncertainty in the measurements is estimated to be on the order of $\pm$ 1 \%.
-This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in).
-When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
-
-%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%\begin{figure}[h!]
-%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-%\end{tabular*}
-%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-%\label{fig:smv_interior}
-%\end{figure}
-
-\section{Fire}
-\label{fire}
-
-To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
-Post-incident, the fire investigation concluded that the fire originated in the structure's attic~\cite{NIOSH:Bowyer}.
-Post-fire pictures revealed extensive damage to the attic and second floor rear porch (cf.
-Fig.~(\ref{fig:charlie_ex})).
-Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_charlie}
-\caption{Photograph showing the post-incident rear (side charlie) exterior of the structure.}
-\label{fig:charlie_ex}
-\end{figure}
-
-If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook~\cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
-
-\begin{multline}
-\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
-\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
-\label{eq:wood_comb}
-\end{multline}
-
-The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
-The heat of combustion quantifies the energy release per unit mass of the fuel.
-The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
-
-\begin{lstlisting}
-&SPEC ID = 'WOOD', FORMULA = 'CH1.7O0.74N0.002' /
-
-&REAC ID = 'wood' 
-    FUEL = 'WOOD', 
-    HEAT_OF_COMBUSTION=16400,
-    SOOT_YIELD = 0.015,
-    CO_YIELD = 0.004/
-\end{lstlisting}
-
-Note that using the input lines above will invoke the simple chemistry reaction balance in FDS.
-This means that fuel and air react to form only CO$_2$, CO, H$_2$O, Soot, and N$_2$.
-If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
-Based on above input lines FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism  states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
-While FDS provides users to the option to use a more complex finite-rate combustion mechanism, we do not have sufficient evidence to justify deviating from the default specifications.
-
-To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
-Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRRPUA (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples~\cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-Based on the range of heat flux exposures, the data was fit to determine HRRPUA ($y$) as a function of exposure ($x$):
-
-\begin{equation}
-y = ax+b
-\label{eq:heat_flux}
-\end{equation}
-
-In Eq.~\ref{eq:heat_flux}, $a$ and $b$ are experimental constants.
-For Douglas Fir plywood these values were found to be 1.43 and 22 respectively.
-Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$~\cite{tsaidrysdale}.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ because of under-ventilated conditions within the structure, then following Eq.~\ref{eq:heat_flux} the average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
-
-To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1453 ft$^2$) plus there is 105 m$^2$ (1130 ft$^2$) of floor area in the attic.
-Examination of post incident images showed that the floor immediately over the back porch burned away.
-That area will be considered as part of the porch fire.
-Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$ (463 ft$^2$)).
-Using an HRRPUA of wood of 51 kW/m$^2$, results in a fire size of 9 MW.
-To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$ (258 ft$^2$)).
-The total area is 64 m$^2$ (689 ft$^2$).
-Using the same HRRPUA of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
-The total fire size for this structure is estimated to be 12.3 MW.
-Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
-First is that the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
-The porch fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
-A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
-The second is that the sources of the gas phase wood fuel are of fixed area and at fixed locations (2 sources for attic, 1 source for porch).
-The following lines define the source fires for an FDS input file:
-
-\begin{lstlisting}
-&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE',TAU_Q=10 /
-&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE',DEVC_ID='SECOND FIRE'/ 1.5 m^2
-&DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
-\end{lstlisting}
-Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes of a specific area.
-
-\section{Materials}
-\label{matl}
-While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
-In this study, we define gypsum~\cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
-The text provided below are the lines necessary to define these materials in an FDS input file.
-
-\begin{lstlisting}
-&MATL ID        = 'GYPSUM'
-    FYI = 'Quintiere, Fire Behavior' 
-    CONDUCTIVITY    = 0.48
-    SPECIFIC_HEAT   = 0.84
-    DENSITY = 1440./
-
-&MATL ID        = 'WOOD_MAT'
-    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
-    CONDUCTIVITY    = 0.12
-    SPECIFIC_HEAT   = 1.38
-    DENSITY = 510./ 
-\end{lstlisting}
-
-\section{Vents}
-\label{Vents}
-This simulation includes vents that account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
-There are two ventilation scenarios that are considered in this study.
-The first is the baseline simulation where the ventilation times and ventilation areas represent our best understanding of the incident.
-The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
-The times of the ventilation changes are provided in Table \ref{tab:vents}.
-Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of structure of this type.
-Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
-
-\bigskip
-\begin{minipage}{.8\linewidth}
-\centering
-\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
-\begin{tabular}{ccccc}
-\toprule[1.5pt]
-Baseline Simulation & Alternative Simulation & Ventilation Area [m$^2$] & Type & Structure Side \\
-\midrule
-00    &  00   & 0.11 & Window      & Charlie \\
-40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
-45    &  45   & 0.12 & Breach      & Beta \\
-55    &  55   & 0.12 & Breach      & Charlie \\     
-130   &  N/A  & 1.41 & Door        & Charlie \\
-135   &  N/A  & 0.2  & Breach      & Beta \\        
-160   &  160  & 0.80 & Door        & Interior \\
-300   &  300  & \multicolumn{3}{c}{Simulation Ends}  \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\bigskip
-\end{minipage}
-
-\section{Mesh}
-\label{mesh}
-
-For the simulation in this study, we can estimate a measure of how well the flow field is resolved by the non-dimensional expression $D^*/\dx$.
-Here $D^*$ is a characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
-\begin{equation}
-D^* = \left(
-     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
-     \right)^\frac{2}{5} 
-\label{eq:mesh}
-\end{equation}   
-From the FDS User Guide~\cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.'' Here, $D$ is the physical diameter of the fire as input to the model.
-Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the characteristic fire diameter to cell size ratio based on the 3.3 MW porch fire is 15.5 and for the 9 MW fire is 23.
-Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 1~\cite{NUREG_1824}.
-The grid resolution used in the model falls within typical, engineering $D^*/\dx$ values.
-As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
-Fig.~(\ref{fig:geom_grid}) shows the
-alpha side (front) of the structure rendered in Smokeview with the 10 cm mesh.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
-\caption{Alpha side of the structure with 10 cm computation mesh.}
-\label{fig:geom_grid}
-\end{figure}
-
-As discussed Section~\ref{geom}, the structure has 17.15 m (56 ft) by 6.15 m (20ft) footprint with a total height of 8.56 m (28 ft).
-To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
-The total volume of the computational domain is 24 m (79 ft) by 10 m (33 ft) by 10 m (33 ft).
-At 10 cm (3.9 in) resolution this would result in 2.4 million computational cells.
-To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
-Fig.~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m (9.8 ft) by 10 m (33 ft) by 5 m (16.4 ft).}
-\label{fig:mult_mesh}
-\end{figure}
+\chapter{Experimental Setup}
+\label{chap:Experimental_Setup}
 
 \chapter{Model Results}
-\label{results}
+\label{chap:Model_Results}
 
-\section{Heat Release Rate}
-\label{HRR}
-The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation.
-Here, we examine impact of ventilation on fire size.
-Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
-The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-\caption{HRR versus time of FDS model of the West 50th St. fire. The first vertical line indicates when the back door failed, the second indicates when the interior hallway door failed.}
-\label{fig:hrr}
-\end{figure}
-
-In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions).
-The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur.
-The dash-dotted line is the prescribed FDS input HRR.
-We can see that within the first 10 seconds, the structure is under-ventilated as the modeled HRR is below the prescribed HRR.
-The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited.
-The HRR drops to 5 MW as the available oxygen inside the structure gets consumed.
-There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents.
-Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40s.
-After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW.
-The HRR then begins to increase towards a sustainable steady state value.
-
-From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW).
-At 130 seconds the rear door is opened in the baseline simulation.
-At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}).
-The open door and breach act as additional pressure releases for the structure.
-Again, the abrupt change in ventilation causes the HRR to spike.
-Here we see a rise from 7 MW to 9.7 MW at 139 seconds.
-At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases.
-While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters inside the structure.
-Therefore, the continued analysis will focus on the results of the baseline simulation results.
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
-\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
-\label{fig:smv_ext_fire}
-\end{figure}
-
-\section{Temperature}
-Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions.
-The first times are 129 seconds into the simulation, just before a firefighter opened the rear porch door (cf.
-Fig.~(\ref{fig:temp_129s})) and 159 seconds into the simulation, just before the interior door fails (cf.
-Fig.~(\ref{fig:temp_159s})).
-
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second prior to rear door opening.}
-\label{fig:temp_129s}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second prior to interior door failing.}
-\label{fig:temp_159s}
-\end{figure}
-
-The
-
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 1 second after interior door fails.}
-\label{fig:temp_161s}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
-\label{fig:temp_175s}
-\end{figure}
-
-\section{Pressure}
-
-\chapter{Discussion}
-
-\section{Conditions in Hallway}
-
-\section{Tactical Considerations}
-
-\chapter{Summary}
+\chapter{Conclusions}
+\label{chap:Conclusions}
 
 \chapter{Acknowledgements}
+\label{chap:Acknowledgements}
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,chicago}
+\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}
 
@@
 
-\chapter{Dimensioned Drawings}
+\chapter{Appendix A}
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption {Dimensioned drawing of 1$^{st}$ floor}
-\label{fig:first_floor}
-\end{figure}
-
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption {Dimensioned drawing of 2$^{nd}$ floor}
-\label{fig:second_floor}
-\end{figure}
+Placeholder
 

### 2014-04-20 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo: Add HOSE plots to report

@@
 \newcommand{\N}{\mbox{N}}
+
+% Center all figures
+\makeatletter
+\g@addto@macro\@floatboxreset\centering
+\makeatother
 
@@
 
-\chapter{Model Results}
-\label{chap:Model_Results}
+\chapter{Results}
+\label{chap:Results}
+
+\section{Hose Flow Tests}
+
+\subsection{DNTADM}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A6}
+\caption{BDP at interior door CD, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A7}
+\caption{BDP at exterior door A, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTADM_HOSE}
+\caption{Hose pressure, Test DNTADM}
+\label{fig:HOSE_DNTADM_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DNTODF}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A6}
+\caption{BDP at interior door CD, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A7}
+\caption{BDP at exterior door A, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DNTODF_HOSE}
+\caption{Hose pressure, Test DNTODF}
+\label{fig:HOSE_DNTODF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DSTADF}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A6}
+\caption{BDP at interior door CD, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A7}
+\caption{BDP at exterior door A, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTADF_HOSE}
+\caption{Hose pressure, Test DSTADF}
+\label{fig:HOSE_DSTADF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DSTODF}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A6}
+\caption{BDP at interior door CD, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A7}
+\caption{BDP at exterior door A, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_DSTODF_HOSE}
+\caption{Hose pressure, Test DSTODF}
+\label{fig:HOSE_DSTODF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{IMAODM}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A6}
+\caption{BDP at interior door CD, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A7}
+\caption{BDP at exterior door A, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMAODM_HOSE}
+\caption{Hose pressure, Test IMAODM}
+\label{fig:HOSE_IMAODM_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{IMTADM}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A6}
+\caption{BDP at interior door CD, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A7}
+\caption{BDP at exterior door A, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_IMTADM_HOSE}
+\caption{Hose pressure, Test IMTADM}
+\label{fig:HOSE_IMTADM_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{STODF Demonstration}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A6}
+\caption{BDP at interior door CD, Test TODF\_Demo}
+\label{fig:HOSE_STODF_demo_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A7}
+\caption{BDP at exterior door A, Test TODF\_Demo}
+\label{fig:HOSE_STODF_demo_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A8}
+\caption{BDP at exterior door C\_West, Test TODF\_Demo}
+\label{fig:HOSE_STODF_demo_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_BDP_A9}
+\caption{BDP at exterior door C\_East, Test TODF\_Demo}
+\label{fig:HOSE_STODF_demo_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/HOSE/HOSE_STODF_demo_HOSE}
+\caption{Hose pressure, Test TODF\_Demo}
+\label{fig:HOSE_STODF_demo_HOSE}
+\end{figure}
 

### 2014-04-20 Projects/DelCo_2014_04/Scripts/plot.py

@@ -118,10 +118,10 @@ for f in os.listdir(data_dir):
                     plot(t, quantity, lw=2, label=channel)
 
             ax1 = gca()
-            legend(loc='lower right', fontsize=8)
             xlabel('Time', fontsize=20)
             xticks(fontsize=16)
             yticks(fontsize=16)
+            legend(loc='lower right', fontsize=8)
             grid(True)
 
             try:
@@ -145,5 +145,5 @@ for f in os.listdir(data_dir):
             elif 'HOSE_' in test_name:
                 folder_name = 'HOSE/'
 
-            savefig('../Figures/' + folder_name + test_name + '_' + group[0].rstrip('_') + '.pdf')
+            savefig('../Figures/' + folder_name + test_name + '_' + group[0].rstrip('_') + '.png')
             close('all')

### 2014-04-21 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo: Edits to report and timing labels

--- 2014-04-16 Projects/DelCo_2014_04/Report/DelCo_2014.tex
@@
 
-\chapter{Model Results}
-\label{chap:Model_Results}
+\chapter{Results}
+\label{chap:Results}
+
+\section{Hose Flow Tests}
+
+\subsection{DNTADM}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A6}
+\caption{BDP at interior door CD, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A7}
+\caption{BDP at exterior door A, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DNTADM}
+\label{fig:HOSE_DNTADM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_HOSE}
+\caption{Hose pressure, Test DNTADM}
+\label{fig:HOSE_DNTADM_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DNTODF}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A6}
+\caption{BDP at interior door CD, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A7}
+\caption{BDP at exterior door A, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DNTODF}
+\label{fig:HOSE_DNTODF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_HOSE}
+\caption{Hose pressure, Test DNTODF}
+\label{fig:HOSE_DNTODF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DSTADF}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A6}
+\caption{BDP at interior door CD, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A7}
+\caption{BDP at exterior door A, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DSTADF}
+\label{fig:HOSE_DSTADF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_HOSE}
+\caption{Hose pressure, Test DSTADF}
+\label{fig:HOSE_DSTADF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{DSTODF}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A6}
+\caption{BDP at interior door CD, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A7}
+\caption{BDP at exterior door A, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A8}
+\caption{BDP at exterior door C\_West, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A9}
+\caption{BDP at exterior door C\_East, Test DSTODF}
+\label{fig:HOSE_DSTODF_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_HOSE}
+\caption{Hose pressure, Test DSTODF}
+\label{fig:HOSE_DSTODF_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{IMAODM}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A6}
+\caption{BDP at interior door CD, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A7}
+\caption{BDP at exterior door A, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test IMAODM}
+\label{fig:HOSE_IMAODM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_HOSE}
+\caption{Hose pressure, Test IMAODM}
+\label{fig:HOSE_IMAODM_HOSE}
+\end{figure}
+
+\clearpage
+
+\subsection{IMTADM}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A6}
+\caption{BDP at interior door CD, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A7}
+\caption{BDP at exterior door A, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A8}
+\caption{BDP at exterior door C\_West, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A9}
+\caption{BDP at exterior door C\_East, Test IMTADM}
+\label{fig:HOSE_IMTADM_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_HOSE}
+\caption{Hose pressure, Test IMTADM}
+\label{fig:HOSE_IMTADM_HOSE}
+\end{figure}
 

### 2014-04-22 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo: Remove interior BDP plots for tests with a closed left hallway

@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A6}
-\caption{BDP at interior door CD, Test DNTADM}
-\label{fig:HOSE_DNTADM_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
 \includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A7}
@@
 \subsection{DNTODF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A6}
-\caption{BDP at interior door CD, Test DNTODF}
-\label{fig:HOSE_DNTODF_BDP_A6}
-\end{figure}
 
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A6}
-\caption{BDP at interior door CD, Test DSTADF}
-\label{fig:HOSE_DSTADF_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
 \includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A7}
@@
 \subsection{DSTODF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A6}
-\caption{BDP at interior door CD, Test DSTODF}
-\label{fig:HOSE_DSTODF_BDP_A6}
-\end{figure}
 

### 2014-04-29 Equipment/Equipment_Manual/Equipment_Manual.tex
Equipment: Create Equipment Manual

\documentclass[12pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../Bibliography/commoncommands}

\renewcommand{\bibname}{Equipment_Manual}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

\begin{document}

\bibliographystyle{unsrt}
\pagestyle{empty}

\begin{minipage}[t][9in][s]{6.25in}

\headerB{
Fire Fighting Technology \\
Equipment Manual
}

\headerC{
\flushright{
Kristopher J. Overholt \\
Craig G. Weinschenk \\
Roy A. McLane \\
Jay A. McElroy \\
Daniel Madrzykowski \\
\bigskip
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

\flushright{\today \\
}

\vfill

\flushright{
\includegraphics[width=2.in]{../../Bibliography/nistident_flright_vec} \\[.3in]
}

\titlesigs

\end{minipage}

\newpage

\frontmatter

\pagestyle{plain}
\pagenumbering{roman}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\chapter{List of Acronyms}

\begin{tabbing}
\hspace{1.5in} \= \\
DVR \> Digital Video Recorder \\
\end{tabbing}

\mainmatter

\chapter{Video}
\label{chap:Video}

\section{Digital Video Recorder Notes}

Model number: Samsung SRD-1680D

Samsung Customer Service: 877-213-1222

When running the ``Backup'' operation (to export the DVR movies to an external HDD), the DVR splits up files into 2.08 GB .avi movie files. See the video editing workflow section for information on joining multiple split videos into a single video file.

\subsection*{FAQ}

\begin{itemize}
\item Can I dump .avi files directly to an external drive? Quality?
    \begin{itemize}
    \item Can dump directly to AVI for a given date/time range, retains 1080 HD quality
    \end{itemize}
\item How are hard disks formatted in DVR (FAT32, exFAT, proprietary)?
    \begin{itemize}
    \item NTFS formatted
    \end{itemize}
\item How are files stored internally (.avi, proprietary)?
    \begin{itemize}
    \item Saved internally in DVR format, can export to AVI or to SCC (proprietary format)
    \end{itemize}
\item Can the internal drives be configured as RAID?
    \begin{itemize}
    \item Not internally
    \end{itemize}
\item What happens if one drive fails and other internal drives are available while recording?
    \begin{itemize}
    \item Seamless failover to other available drives
    \end{itemize}
\item How should an external drive be formatted?
    \begin{itemize}
    \item External USB drive should be formatted as FAT32. You can do this using the built in format function.
    \end{itemize}
\item Limit on number of connected smartphone viewers or remote viewers?
    \begin{itemize}
    \item Remote: Search 3, Live unicast 10, Live multicast 20
    \item Mobile: 1 Live, 1 CH playback
    \end{itemize}
\end{itemize}

\section{Video Editing Workflow}

\subsection{Digital Video Recorder}

The process for recording and extracting video from the DVR is as follows:
\begin{enumerate}
\item Record video.
\item Backup the video to an external drive to .avi format (H.264 codec and AVI container).
\item Convert the .avi videos to .mp4 format (H.264 codec and MPEG-4 container) for editing. A tool such as Handbrake is recommended.
\end{enumerate}
It is recommended that you maintain the original .avi files and subtitle files, which contain the date/timestamp information for future reference.

\subsection{Combining Videos}

The GoPro cameras and DVR split long videos into multiple files. If you need to combine multiple .mp4 videos into one file, you can use a tool such as MP4Box or Avidemux. Multiple video files can also result from the DVR if a video channel loses signal temporarily. If this is the case, be sure to add blank video to pad any time that passed while the video channel signal was lost.

\subsection{Creating Multi-Camera Videos}

You can combine multiple videos into a multi-camera video using software such as Adobe Premiere or any other non-linear video editing software.

\end{document}

### 2014-04-29 Equipment/Equipment_Manual/Equipment_Manual.tex
Equipment Manual: Update to video editing section

@@
-\documentclass[12pt,oneside]{book}
+\documentclass[11pt,oneside]{book}
 
@@
 
-The GoPro cameras and DVR split long videos into multiple files.
+The GoPro cameras and DVR split long videos into multiple files because of the format of the file systems that they write to.
 If you need to combine multiple .mp4 videos into one file, you can use a tool such as MP4Box or Avidemux.
-Multiple video files can also result from the DVR if a video channel loses signal temporarily.
+Multiple video files can also result from the DVR if a video channel temporarily loses signal.
 If this is the case, be sure to add blank video to pad any time that passed while the video channel signal was lost.
+
+For example, to seamlessly combine two video files (video\_1.mp4 and video\_2.mp4) into one video file (video\_output.mp4), the command line tool MP4Box can be used with the following command
+
+\begin{verbatim}
+MP4Box -cat video_1.mp4 -cat video_2.mp4 -new video_output.mp4
+\end{verbatim}
 

### 2014-04-30 Projects/DelCo_2014_04/Report/DelCo_2014.tex
DelCo: Update report with new plots

@@
 
-\subsection{DNTADM}
+\subsection{DNXAXX}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A7}
-\caption{BDP at exterior door A, Test DNTADM}
-\label{fig:HOSE_DNTADM_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
+\label{fig:HOSE_DNXAXX_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A8}
-\caption{BDP at exterior door C\_West, Test DNTADM}
-\label{fig:HOSE_DNTADM_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
+\label{fig:HOSE_DNXAXX_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_BDP_A9}
-\caption{BDP at exterior door C\_East, Test DNTADM}
-\label{fig:HOSE_DNTADM_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
+\label{fig:HOSE_DNXAXX_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTADM_HOSE}
-\caption{Hose pressure, Test DNTADM}
-\label{fig:HOSE_DNTADM_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_HOSE}
+\caption{Hose pressure, Test HOSE\_DNXAXX}
+\label{fig:HOSE_DNXAXX_HOSE}
 \end{figure}
@@
 
-\subsection{DNTODF}
+\subsection{DNXOXF}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A7}
-\caption{BDP at exterior door A, Test DNTODF}
-\label{fig:HOSE_DNTODF_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
+\label{fig:HOSE_DNXOXF_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A8}
-\caption{BDP at exterior door C\_West, Test DNTODF}
-\label{fig:HOSE_DNTODF_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
+\label{fig:HOSE_DNXOXF_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_BDP_A9}
-\caption{BDP at exterior door C\_East, Test DNTODF}
-\label{fig:HOSE_DNTODF_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
+\label{fig:HOSE_DNXOXF_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DNTODF_HOSE}
-\caption{Hose pressure, Test DNTODF}
-\label{fig:HOSE_DNTODF_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_HOSE}
+\caption{Hose pressure, Test HOSE\_DNXOXF}
+\label{fig:HOSE_DNXOXF_HOSE}
 \end{figure}
@@
 
-\subsection{DSTADF}
+\subsection{DSXAXF}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A7}
-\caption{BDP at exterior door A, Test DSTADF}
-\label{fig:HOSE_DSTADF_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
+\label{fig:HOSE_DSXAXF_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A8}
-\caption{BDP at exterior door C\_West, Test DSTADF}
-\label{fig:HOSE_DSTADF_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
+\label{fig:HOSE_DSXAXF_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_BDP_A9}
-\caption{BDP at exterior door C\_East, Test DSTADF}
-\label{fig:HOSE_DSTADF_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
+\label{fig:HOSE_DSXAXF_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTADF_HOSE}
-\caption{Hose pressure, Test DSTADF}
-\label{fig:HOSE_DSTADF_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_HOSE}
+\caption{Hose pressure, Test HOSE\_DSXAXF}
+\label{fig:HOSE_DSXAXF_HOSE}
 \end{figure}
@@
 
-\subsection{DSTODF}
+\subsection{DSXOXF}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A7}
-\caption{BDP at exterior door A, Test DSTODF}
-\label{fig:HOSE_DSTODF_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
+\label{fig:HOSE_DSXOXF_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A8}
-\caption{BDP at exterior door C\_West, Test DSTODF}
-\label{fig:HOSE_DSTODF_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
+\label{fig:HOSE_DSXOXF_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_BDP_A9}
-\caption{BDP at exterior door C\_East, Test DSTODF}
-\label{fig:HOSE_DSTODF_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
+\label{fig:HOSE_DSXOXF_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_DSTODF_HOSE}
-\caption{Hose pressure, Test DSTODF}
-\label{fig:HOSE_DSTODF_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_HOSE}
+\caption{Hose pressure, Test HOSE\_DSXOXF}
+\label{fig:HOSE_DSXOXF_HOSE}
 \end{figure}
@@
 
-\subsection{IMAODM}
+\subsection{IXAOXX}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A6}
-\caption{BDP at interior door CD, Test IMAODM}
-\label{fig:HOSE_IMAODM_BDP_A6}
+\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A6}
+\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
+\label{fig:HOSE_IXAOXX_BDP_A6}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A7}
-\caption{BDP at exterior door A, Test IMAODM}
-\label{fig:HOSE_IMAODM_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
+\label{fig:HOSE_IXAOXX_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A8}
-\caption{BDP at exterior door C\_West, Test IMAODM}
-\label{fig:HOSE_IMAODM_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
+\label{fig:HOSE_IXAOXX_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_BDP_A9}
-\caption{BDP at exterior door C\_East, Test IMAODM}
-\label{fig:HOSE_IMAODM_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
+\label{fig:HOSE_IXAOXX_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMAODM_HOSE}
-\caption{Hose pressure, Test IMAODM}
-\label{fig:HOSE_IMAODM_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_HOSE}
+\caption{Hose pressure, Test HOSE\_IXAOXX}
+\label{fig:HOSE_IXAOXX_HOSE}
 \end{figure}
@@
 
-\subsection{IMTADM}
+\subsection{IXXAXX}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A6}
-\caption{BDP at interior door CD, Test IMTADM}
-\label{fig:HOSE_IMTADM_BDP_A6}
+\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A6}
+\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
+\label{fig:HOSE_IXXAXX_BDP_A6}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A7}
-\caption{BDP at exterior door A, Test IMTADM}
-\label{fig:HOSE_IMTADM_BDP_A7}
+\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A7}
+\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
+\label{fig:HOSE_IXXAXX_BDP_A7}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A8}
-\caption{BDP at exterior door C\_West, Test IMTADM}
-\label{fig:HOSE_IMTADM_BDP_A8}
+\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
+\label{fig:HOSE_IXXAXX_BDP_A8}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_BDP_A9}
-\caption{BDP at exterior door C\_East, Test IMTADM}
-\label{fig:HOSE_IMTADM_BDP_A9}
+\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
+\label{fig:HOSE_IXXAXX_BDP_A9}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE/HOSE_IMTADM_HOSE}
-\caption{Hose pressure, Test IMTADM}
-\label{fig:HOSE_IMTADM_HOSE}
+\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_HOSE}
+\caption{Hose pressure, Test HOSE\_IXXAXX}
+\label{fig:HOSE_IXXAXX_HOSE}
 \end{figure}
+
+\clearpage
+
+\section{Fire Tests}
+
+\subsection{FIRE\_FA2S1C1NCX1\_1}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
+\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
+\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
+\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
+\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_GAS}
+\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_HF}
+\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
+\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
+\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
+\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
+\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
+\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
+\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
+\end{figure}
+
+\clearpage
+
+\subsection{FIRE\_FA2S1C1NCX1\_2}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
+\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
+\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
+\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
+\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_GAS}
+\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_HF}
+\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
+\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
+\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
+\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
+\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
+\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
+\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
+\end{figure}
+
+\clearpage
+
+\subsection{FIRE\_FA2S1C1NCX1\_3}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
+\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
+\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
+\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
+\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
+\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
+\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_GAS}
+\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_HF}
+\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
+\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
+\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
+\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
+\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
+\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
+\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
+\end{figure}
+
+\clearpage
 

### 2014-05-01 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Add notes about splitting video

--- 2014-04-29 Equipment/Equipment_Manual/Equipment_Manual.tex
@@
 
-\renewcommand{\bibname}{Equipment_Manual}
+\renewcommand{\bibname}{Equipment_Guide}
 
@@
 Fire Fighting Technology \\
-Equipment Manual
+Equipment Guide
 }
@@
 If you need to combine multiple .mp4 videos into one file, you can use a tool such as MP4Box or Avidemux.
+The benefit of these tools over a full video editor is that they can perform simple video operations without reencoding the video, so the processing is much faster.
+
 Multiple video files can also result from the DVR if a video channel temporarily loses signal.
@@
 
+\subsection{Splitting Videos}
+
+You can split an .mp4 video into multiple videos (without reencoding) with MP4Box.
+For example, if you have a 60~s video (video\_input.mp4), you can extract video from 30~s to 60~s and save the output to a new file (video\_output.mp4) with the following command
+
+\begin{verbatim}
+MP4Box -splitx 30:60 video_input.mp4 -out video_output.mp4
+\end{verbatim}
+
 \subsection{Creating Multi-Camera Videos}

### 2014-05-06 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Add gas analyzer diagnostic information

@@
 
+\chapter{Gas Analyzer}
+\label{chap:Gas_Analyzer}
+
+\section{Diagnostics}
+
+The following screens provide useful diagnostic information that can be sent to technical support:
+
+\begin{itemize}
+\item To display the version and serial number, press Main $\rightarrow$ F5 $\rightarrow$ F10.
+\item To display flow diagnostics, press Main $\rightarrow$ F3.
+\item To display raw voltage/channel values, press Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows.
+\end{itemize}
+
 \chapter{Video}

### 2014-05-07 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Add info on gas analyers; add placeholders for other equipment; add testing procedure

@@
 
+\chapter{Data Acquisition System}
+
+\chapter{Thermocouples}
+
+\section{Uncertainty}
+
+Uncertainty
+
+\chapter{Bi-Directional Probes}
+
+\section{Uncertainty}
+
+Uncertainty
+
+\chapter{Heat Flux Gauges}
+
+\section{Uncertainty}
+
+Uncertainty
+
 \chapter{Gas Analyzer}
@@
 
+The CAI 602P Gas Analyzer can detect gas concentrations for CO$_2$, CO, and O$_2$ and output a voltage from 0~V to 5~V, which corresponds to 0~\% gas concentration to full-scale concentration.
+
+\section{Internals}
+
+The internal pump is located in the center of the chassis.
+The O$_2$ sensor is located under the foam cover.
+The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.
+
+\section{Usage}
+
+Important Note: The optimal pressure from the upstream sample and calibration gas is 0~psi!
+The internal gas analyzer components should never have an upstream pressure in excess of 2~psi.
+Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragms.
+
+\begin{itemize}
+\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage
+\item Perform zero and span calibration on all analyzers.
+    \begin{itemize}
+    \item Flow N$_2$ and zero the CO$_2$, CO, and O$_2$ channels.
+    \item Flow CO$_2$/CO calibration gas and span the CO$_2$ and CO channels.
+    \item Use ambient air to span the O$_2$ channel.
+    \end{itemize}
+\item Set the upper ranges to the appropriate setting, which corresponds to 5~V on the output to the DAQ.
+\item Measure the delay time for the sample gas to travel in the plumbing to the analyzer.
+You can do this by holding a CO$_2$ source near the sample port and measuring the time from exposing the sample port until the gas analyzer reads an increased value.
+Record this time so that the gas concentration can be offset later.
+\item You are ready to record data to the DAQ.
+\end{itemize}
+
+\section{External Plumbing}
+
+Calibration (span) gas (CO$_2$ and CO) $\rightarrow$ Bypass tee $\rightarrow$ Span gas inlet.
+
+Sample tubes $\rightarrow$ Filter in dry ice (for scrubbing and cooling) $\rightarrow$ Sample pump (bypass value is on) $\rightarrow$ Sample inlet on gas analyzer $\rightarrow$ Outlet tube directed away from operator.
+
+\section{Uncertainty}
+
+Uncertainty
+
 \section{Diagnostics}
 
+\subsection{No Internal Flow}
+
+If the flow drops to zero, then display the flow diagnostics by pressing Main $\rightarrow$ F3.
+Check the internal flow value for the three gases.
+If it is zero, then there might be a issue with the internal plumbing if the upstream pressure (from sample or calibration gases) exceeded 2~psi.
+Check power to the internal pump and ensure that it is operating.
+
+\subsection{Bad Gas Concentration Readings}
+
+If the channel is reading gas concentration values out of range or sporadic values, you may need to clean the internal sensor cell windows.
+Check the raw voltages in the analyzer setup by pressing Main $\rightarrow$ F5 $\rightarrow$ F6 $\rightarrow$ F2, then cycle through each gas using the left/right arrows.
+The raw voltages should be around 1.0~V at 0~\% concentration, and 9~V at full-scale concentration.
+Refer to Section~10 of the CAI 600P User Manual for more information.
+
+\subsection{Diagnostic Information}
+
 The following screens provide useful diagnostic information that can be sent to technical support:
-
 \begin{itemize}
@@
 \end{itemize}
+
+Refer to Section~10 of the CAI 600P User Manual for more information on maintenance and troubleshooting.
 
@@
 
-You can combine multiple videos into a multi-camera video using software such as Adobe Premiere or any other non-linear video editing software.
+You can combine multiple videos into a multi-camera video using software such as Adobe Premiere Pro or any other non-linear video editing software.
+
+\appendix
+
+\chapter{Testing Procedure}
+
+\section{Initial Startup}
+
+\begin{itemize}
+\item Power on the following devices:
+    \begin{itemize}
+    \item Uninterruptible Power Supplies (UPSs)
+    \item WiFi routers
+    \item Hose flow / Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
+    \item DAQs and laptops
+    \item Gas analyzers (leave running as long as possible during testing)
+    \item Digital video recorder (DVR)
+    \item Bullet cameras
+    \item Thermal imaging cameras (TICs) (check battery level)
+    \item Digital video cassette recorders (DVCRs) (check battery level)
+    \item GoPros (check battery level)
+    \item Video cameras (check battery level)
+    \end{itemize}
+\end{itemize}
+
+\section{Calibration}
+
+\begin{itemize}
+\item Synchronize time on DAQ computers and digital video recorder
+
+\item Verify operation of all:
+    \begin{itemize}
+    \item Video channels
+    \item DAQ channels
+    \item Check toggle switches on TC-2095s for appropriate measurement device
+    \item Gas analyzers
+    \end{itemize}
+
+\item Calibrate gas analyzers with zero and span gases
+
+\item 1 minute calibration run to separate output file (cover BDPs, check TCs, etc.)
+
+\end{itemize}
+
+\section{Primary Testing Procedure}
+
+\begin{itemize}
+\item Verify testing procedure with all personnel
+\item Safety checks
+
+\item Power on gas analyzer pump
+
+\item Turn on water for heat flux gauges
+
+\item Check Arduino battery level
+\item Power on Arduino data loggers
+
+\item Start recording on:
+    \begin{itemize}
+    \item GoPros
+    \item Video cameras
+    \item DVCRs (Mobile TIC)
+    \end{itemize}
+
+\item Start synced recording on: [MARK DATE/TIME]
+    \begin{itemize}
+    \item DVR
+    \item DAQ data
+    \end{itemize}
+
+\item 1 minute pre-test run (with all doors closed)
+
+\item Begin test [MARK DATE/TIME]
+
+\item Follow testing procedure
+
+\item End test [MARK DATE/TIME]
+
+\item Stop synced recording on: [MARK DATE/TIME]
+    \begin{itemize}
+    \item DAQ
+    \item DVR
+    \end{itemize}
+
+\item Stop recording on:
+    \begin{itemize}
+    \item GoPros
+    \item Video cameras
+    \item DVCRs (Mobile TIC)
+    \end{itemize}
+
+\item Power off gas analyzer pump
+
+\item Power off Arduino data loggers
+
+\item Verify successful recording and operation of all DAQ channels in output file
+
+\item Prepare for next test
+\end{itemize}
+
+\section{Data Dump}
+
+\begin{itemize}
+\item Retrieve data from:
+    \begin{itemize}
+    \item DAQ
+    \item DVR
+    \item GoPros
+    \item Video cameras with digital media
+    \item Arduinos
+    \end{itemize}
+
+\item Swap and label tapes from video cameras and DVCRs as needed
+
+\item Make 3 copies of all data on external hard drives
+
+\item Verify integrity of data
+
+\item On return from trip, extract video from DVCRs
+\end{itemize}
+
+\section{Battery Charging}
+
+\begin{itemize}
+\item Charge all batteries on:
+    \begin{itemize}
+    \item Laptops
+    \item Arduinos
+    \item Bullet camera batteries
+    \item TICs
+    \item GoPros
+    \item Video cameras
+    \item DVCRs
+    \end{itemize}
+\end{itemize}
 

### 2014-05-29 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: minor update to report

@@
 \multirow{2}{*}{17:15} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
-         & \\[.25cm]
+         & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
 17:16    & Dispatch for a Still Alarm. \\ [.25cm]
@@
 \label{geom}
-The structure was a 2 1/2 story residential structure with balloon frame construction and a wood gable roofing system.
+The structure was a 2 1/2 story residential building with balloon frame construction and a wood gable roofing system.
 The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
@@
 Fig.~(\ref{fig:simp_geom})).
-A second floor interior door, connecting the rear porch and the hallway, failed and rapidly changed the tenability conditions for firefighters present on the second floor.
-More discussion on interior conditions can be found in Chapter~\ref{results}.
+Discussion of the fire's impact on interior conditions can be found in Section~\ref{results}.
 Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
@@
 This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in).
-When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not expected to be a major factor.
+When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not a major factor.
 
@@
 Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate how several key events correspond to changing interior conditions.
+Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate the changing interior conditions.
 The first times are 129 seconds into the simulation, just before a firefighter opened the rear porch door (cf.
@@
 After the second floor door fails, (cf.
-Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flows in the direction of lower pressure (the front door).
-Note that the conditions in the attic remain  We can focus on this area, (cf.
-Fig.~(\ref{fig:temp_161s})), to see the the flow of gases through the doorway.
-
+Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flows in the direction of lower pressure (towards the front door).
+Note that the conditions in the attic do not seem to be influenced.
 \begin{figure}[!ht]
@@
 \begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_165v}
 \input{../Scripts/colorbar_std} 
@@
 \chapter{Discussion}
-
+The discussion will be broken up into two parts.
+The first part will address the results of the computational modeling as they relate to the interior hallways conditions.
+The second part will examine the the model results and observed outcomes of fire as they relate to tactics discussed in recent experimental research.
 \section{Conditions in Hallway}

### 2014-06-03 Equipment/Equipment_Guide/Equipment_Guide.tex
Update equipment document

@@
 \hspace{1.5in} \= \\
+BDP \> Bi-Directional Probe \\
 DVR \> Digital Video Recorder \\
+NI \> National Instruments \\
+TC \> Thermocouple \\
 \end{tabbing}
@@
 
+Data acquisition systems are constructed using National Instruments (NI) hardware.
+The systems starts with the chassis - NI SCXI-1000/NI SCXI-1001.
+The 1000 is a 4-slot chassis while the 1001 is a 12-slot chassis.
+The max scan rate of the chassis is (5 $\mu$s $\times$ \# of channels used)$^{-1}$.
+Connecting the chassis to the computer (via USB) is the NI SCXI-1600 which is a 200 kS/s 16-bit digitizer.
+
 \chapter{Thermocouples}
+\label{chap:thermocouple}
+
+Two types of k-type thermocouples (TCs) are used: bare bead and metal sheathed.
+The bare bead TCs are made from 30 gauge glass braid insulated solid wire.
+The bare bead thermocouples are used in the TC trees and single point measurements.
+The metal sheathed TCs (\#125-KSL-600-U from Furnace Parts) feature a 1/8 in diameter Inconel 600 sheath and an ungrounded junction.
+These TCs are moisture proof and are used in conjunction with the bi-directional probes.
 
@@
 
-Uncertainty
+\begin{table}
+\centering
+\captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
+\begin{tabular}{l l l}
+\toprule[1.5pt]
+Thermocouple Type & Temperature Range & Error  \\
+\midrule
+Bare bead  &  & \\ 
+Inconel sheathed    & 0 - 1260 $^{\circ}$C &  MAX($\pm$ 1.11$^{\circ}$C; $\pm$ 0.4 $\%$)   \\ 
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
+\section{Thermocouple Welders}
+
+Two different welders are used to construct the bare bead TCs.
+
+\section{Thermocouple Extension Wire}
 

### 2014-06-04 Equipment/Equipment_Guide/Equipment_Guide.tex
Add DAQ schematic and update equipment guide

@@
 \chapter{Data Acquisition System}
+\label{chap:DAQ}
 
+\section{Hardware}
 Data acquisition systems are constructed using National Instruments (NI) hardware.
@@
 The max scan rate of the chassis is (5 $\mu$s $\times$ \# of channels used)$^{-1}$.
-Connecting the chassis to the computer (via USB) is the NI SCXI-1600 which is a 200 kS/s 16-bit digitizer.
+A 200 kS/s 16-bit digitizer, NI SCXI-1600, connects the chassis to the computer (via USB).
+The remaining chassis slots are filled with the NI SCXI-1102.
+The SCXI-1102 is a 32 channel thermocouple amplifier/voltage input module.
+Each SCXI-1102 is connected to a TC-2095; a shielded, 32 channel, rack-mountable terminal accessory.
+All of the measurement devices connect to the TC-2095 using either chromel-alomel connectors (temperature) or copper-copper connectors (voltage).
+A schematic of the hardware configuration is shown in Fig.~(\ref{fig:daq_schem}).
+
+\begin{figure}[h!]
+\includegraphics[width=5in]{Figures/DAQ_Schematic}
+\caption{Schematic of data acquisition hardware.}
+\label{fig:daq_schem}
+\end{figure}
+
+\section{Software}
+Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the laptop must also have a 32-bit operating system on it.
 
@@
 The metal sheathed TCs (\#125-KSL-600-U from Furnace Parts) feature a 1/8 in diameter Inconel 600 sheath and an ungrounded junction.
-These TCs are moisture proof and are used in conjunction with the bi-directional probes.
+These TCs are moisture proof and are typically used in conjunction with bi-directional probes.
 
@@
 
-\begin{table}
+\begin{table}[h!]
 \centering
@@
 \midrule
-Bare bead  &  & \\ 
-Inconel sheathed    & 0 - 1260 $^{\circ}$C &  MAX($\pm$ 1.11$^{\circ}$C; $\pm$ 0.4 $\%$)   \\ 
+Bare bead (SLE)     & 0 - 1250 $^{\circ}$C &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\ 
+Inconel sheathed    & 0 - 1260 $^{\circ}$C &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)   \\ 
 \bottomrule[1.25pt]
@@
 
+Two sets of type K extension wire are used: single pair (EXPP-K-24-S-1000) or 20 pair (20KX24SPP). Both wires are 24 gauge, 7-32 stranded, polyvinyl coated wire.
+
+\section{Thermocouple Connectors}
+
+Thermocouple miniature connectors are high temperature liquid crystal polymer (HMPW-K-M). Thermocouple miniature panel jacks are used with the BDP boxes (MPJ-K-F).
+
+\begin{table}[h!]
+\centering
+\captionof{table}{Thermocouple Connections}\label{tab:TC_connect}
+\begin{tabular}{l l l}
+\toprule[1.5pt]
+Use & Connection End 1 & Connection End 2  \\
+\midrule
+TC Tree/Single TC    & TC Bead                 & Male  \\ 
+Inconel sheathed      & TC Bead                 & Male  \\
+Single Extension       & Female                   & Male  \\
+BDP TC Extension    & Male                       & Male \\
+20 Pair Extension     & Female Panel Jack & Male \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
 \chapter{Bi-Directional Probes}
@@
 
+Medtherm Corporation Schmidt-Boelter total heat flux gages and radiometers are used with full scale outputs that range from 20 kW/m$^2$ to 100 kW/m$^2$.
+Each transducer outputs millivolts.
+Voltage is converted to heat flux using a conversion factor provided on each device's unique data sheet.
+
 \section{Uncertainty}
 
-Uncertainty
+Calibration is performed in compliance with ISO/IEC 17025, ANSI/NCSL Z540-1, and MIL-STD-45662A to Medtherm PI-20 with traceability to the National Institute of Standards and Technology.
+The total expanded uncertainty is $\pm 3\%$ with a coverage factor = 2 (95 $\%$ confidence level).
 

### 2014-06-04 Equipment/Equipment_Guide/Equipment_Guide.tex
Update equipment guide

@@
 \section{Software}
-Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the laptop must also have a 32-bit operating system on it.
+Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the computer must also have a 32-bit operating system on it.
 
@@
 Two different welders are used to construct the bare bead TCs.
+The Miyachi Unitek TC Welder (01-0196-02) is a manual feed thermocouple welder designed to weld thermocouple wires together without oxide layers by using argon cover gas.
+The welder can handle wires from 38 gauge to 20 gauge.
 

### 2014-06-06 Equipment/Equipment_Guide/Equipment_Guide.tex
Update equipment guide, add schematic of pressure boxes

@@
 NI \> National Instruments \\
+NIST \> National Institute of Standards and Technology \\
 TC \> Thermocouple \\
@@
 These TCs are moisture proof and are typically used in conjunction with bi-directional probes.
+The sheathed TCs are typically ordered with a 48 in TC and 120 in type K lead wire (NIST01A from Furnace Parts) or a 144 in TC and 120 in type K lead wire (NIST01B from Furnace Parts).
 
@@
 
-Thermocouple miniature connectors are high temperature liquid crystal polymer (HMPW-K-M). Thermocouple miniature panel jacks are used with the BDP boxes (MPJ-K-F).
+Thermocouple miniature connectors are high temperature liquid crystal polymer (HMPW-K-M/F). Thermocouple miniature panel jacks are used with the BDP boxes (MPJ-K-F).
 
@@
 BDP TC Extension    & Male                       & Male \\
+BDP Box                   & Female Panel Jack & Female Panel Jack \\
 20 Pair Extension     & Female Panel Jack & Male \\
@@
 \chapter{Bi-Directional Probes}
+\label{chap:bdp}
+
+Bi-directional probes are order from ... size specs. Pressure measurements are made using a XX Setra.
+
+\begin{figure}[h!]
+\includegraphics[width=5in]{Figures/BDP_Box}
+\caption{Schematic of pressure measurement setup for use with BDPs.}
+\label{fig:daq_schem}
+\end{figure}
 

### 2014-06-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update writeup

@@
 Here we see a rise from 7 MW to 9.7 MW at 139 seconds.
-At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation in both cases.
-While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the fire represented a significant hazard to firefighters inside the structure.
-Therefore, the continued analysis will focus on the results of the baseline simulation results.
+At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation.
+While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the interior conditions represented a significant hazard to firefighters inside the structure.
+Therefore, the analysis will focus on the results of the baseline simulation.
 
@@
 \label{fig:smv_ext_fire}
+\end{figure}
+
+\section{Pressure}
+As the fire grows in the attic and back porch, the pressure rises.
+Fig.~(\ref{fig:pres_159s}) shows the pressure rise in the structure just before the interior door failed in the simulation.
+On the rear porch, the pressure rise ranges from a 4 Pa over pressure 1 m off the floor to greater than 10 Pa at the ceiling.
+\begin{figure}[!ht]
+\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
+\input{../Scripts/colorbar_metric_pres}
+\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
+\label{fig:pres_159s}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161v}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{FDS predicted temperature vectors, 1 second after interior door fails.}
-\label{fig:temp_161v}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_165v}
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
 \input{../Scripts/colorbar_std} 
@@
 
-\section{Pressure}
-
-\begin{figure}[!ht]
-\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
-\input{../Scripts/colorbar_metric_pres}
-\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
-\label{fig:pres_159s}
-\end{figure}
+From Fig.~(\ref{fig:temp_175s}), 15 seconds after the door failed, high temperature gases have descended to approximately 1 m (3.28 ft) off the ground through the interior hallway and have spilled into the kitchen (recall layout from Fig.~(\ref{fig:simp_geom})).
 

### 2014-06-08 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: add two figures, update writeup

@@
 There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
-Entry to the structure can be made either in the front (Alpha side) or rear (Charlie side).
-The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch (cf.
-Fig.~(\ref{fig:simp_geom})).
+Entry to the structure can be made either in the front (Alpha side) or rear (Charlie side), see Fig.~(\ref{fig:simp_geom}).
+The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
 Discussion of the fire's impact on interior conditions can be found in Section~\ref{results}.
@@
 
+\section{Timeline}
+\label{timeline}
+From the NIOSH report~\cite{NIOSH:Bowyer}, a timeline of events was able to be created, see Table~\ref{tab:fire_info}.
+Due to a lack of information about when the fire ignited, an ignition time/start of the simulation needed to be estimated.
+We estimate that the simulation starts at 17:19:20.
+Since the actually time was unknown, the fire growth rate in the computational model is such that when firefighters enter the structure, the hazard level in the model is similar to the real situation.
+A second unknown that was estimated was the time when the second floor door fails (2:40 into the simulation).
+While this time is not exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
+Table~\ref{tab:firesim} shows the fireground timeline along with the corresponding simulation times.
+
+\begin{table}
+\centering
+\captionof{table}{Fire - Simulation Event Timeline}\label{tab:firesim}
+\begin{tabular}{l l l}
+\toprule[1.5pt]
+Incident Time & Simulation Time & Fire Behavior / Fireground Operation  \\
+\midrule
+\multirow{2}{*}{17:15} &    & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+         & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
+17:16 &      & Dispatch for a Still Alarm. \\ [0.25cm]
+         &  \multirow{2}{*} {0:00} &  \multirow{2}{*}{\parbox{10cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
+         & & \\[0.25cm]
+\multirow{2}{*}{17:20} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
+         & & \\[.25cm] 
+         & 0:45 & Model ventilation on charlie side. \\[.25cm] 
+         & 0:55 & Model ventilation on beta side. \\[.25cm] 
+17:21:00 &  & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
+17:21:30 & 2:10 & 1$^{st}$ floor exterior porch door opened. Attic fire ignites in model. \\[.25cm]
+        & 2:15 & Additional model ventilation on beta side. \\[.25cm] 
+        & 2:40 & Top of interior door fails in model. \\[.25cm] 
+\multirow{2}{*}{17:23}    & \multirow{2}{*}{3:40} & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+         & & \\[.25cm]
+17:24    &   & Water applied to attic from the rear exterior position. \\[.25cm]
+17:27    & 5:00  & IC calls a Mayday. Simulation ends. \\[.25cm]
+17:29    &   & E123 Capt. carried out of structure. \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
 \chapter{Model Results}
@@
 \begin{figure}[!ht]
-\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres}
+\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
 \input{../Scripts/colorbar_metric_pres}
@@
 \label{fig:pres_159s}
+\end{figure}
+Gases at elevated pressure will always travel toward an area of lower pressure.
+When the interior door fails, the lower pressure outlet is through the front door on the alpha side of the structure.
+As a result, the gases produced by the fire will flow through the interior hallway, through the kitchen, down the front stairs and out the front door.
+The velocity vectors in Fig.~(\ref{fig:velo_175s}), 15 seconds after the interior door fails, confirms this flow direction within the structure.
+\begin{figure}[!ht]
+\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_velo_175}
+\input{../Scripts/colorbar_std_velo}
+\input{../Scripts/colorbar_metric_velo}
+\caption{FDS predicted velocity vectors, 15 second after interior door failure.}
+\label{fig:velo_175s}
 \end{figure}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature from baseline simulation, 15 seconds after interior door fails.}
+\caption{FDS predicted temperature contours, 15 seconds after interior door fails.}
 \label{fig:temp_175s}

### 2014-06-09 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: add images, color bar scripts, and update report

@@
 \chapter{Fire Incident Summary}
+\label{fire_sum}
 The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
@@
          & & \\[0.25cm]
-\multirow{2}{*}{17:20} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
+\multirow{2}{*}{17:20} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
+Rear porch ignites in model.}} \\
          & & \\[.25cm] 
@@
          & 0:55 & Model ventilation on beta side. \\[.25cm] 
-17:21:00 &  & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
+17:21:00 & 1:40 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
 17:21:30 & 2:10 & 1$^{st}$ floor exterior porch door opened. Attic fire ignites in model. \\[.25cm]
@@
 \section{Temperature}
+\label{temp}
 Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
@@
 The second part will examine the the model results and observed outcomes of fire as they relate to tactics discussed in recent experimental research.
-\section{Conditions in Hallway}
+
+\section{Hallway Flow Path}
+From on-reports from the BC (Chapter~\ref{fire_sum}) and simulation results (Chapter~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
+The simulation, however, showed a high hazard environment developing on the second floor.
+By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was involved.
+Temperature and pressure, greater than 260 $^{\circ}$C (500 $^{\circ}$F) and 5 Pa respectively, were on the Charlie side of the steel door at the rear of the structure.
+Exposure to these conditions weakened the structural integrity of the door, eventually leading to a partial failure.
+Fig.~(\ref{fig:chicago_doorfold}) shows the state of the rear door post fire.
+Note the large crease in the door just above the knob.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
+\caption{Post fire image of interior door.}
+\label{fig:chicago_doorfold}
+\end{figure}
+Recent experiments conducting by the National Institute of Standards and Technology revealed similar post-fire states after doors were exposed to fires.
+Fig.~(\ref{fig:SC_doorfold}) shows doors from two different house fire experiments in which the door folded in the direction of the flow path.
+
+\begin{figure}[h!]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
+   \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
+\end{tabular*}
+\caption{Post experiment images of door failures.}
+\label{fig:SC_doorfold}
+\end{figure}
+
+While we have an estimated time of failure for the door, the key take away is that after the door failed an interior flow path from the Charlie side to the Alpha side of the structure was created.
+This resulted in a rapid change in the conditions within the flow path.
+The combustion gases at elevated temperature and pressure flowed toward ambient conditions; the flow path was through the interior hallway, kitchen, and down the Alpha-Delta stairwell and out of the structure through the front door.
+The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases  on the second flow following the door failure.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
+\caption{Flow path on second floor following interior door failure.}
+\label{fig:flowpath_1}
+\end{figure}
+
+\subsection{Assessing the Hazard}
+
+A firefighter inside is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
+While firefighters wear protective gear, the gear only offers finite levels of protection.
+The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140 $^{\circ}$C (284 $^{\circ}$F) \cite{mensch2011emergency}.
+Structural fire fighting coats and pants are tested to withstand temperatures of 260 $^{\circ}$C (500 $^{\circ}$F) \cite{nfpa2013standard}.
+Extended exposure to elevated temperatures can result in significant heat being transferred to the firefighter, putting him/her at risk.
+For the analysis of the model predicted exposure temperatures in the flow path, we have set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
+This means that temperatures visualized in the highest range in the model output are at a minimum of 260 $^{\circ}$C (500 $^{\circ}$F); the temperatures could be higher.
 
@@
 \chapter{Acknowledgements}
+The authors would like to thank the Chicago Fire Department, especially {\em names}.
+The authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
 

### 2014-06-10 Projects/DelCo_2014_04/Report/DelCo_2014.tex
Dan Test
Test Commit

@@
 
+\section{Experimental Structure}
+\label{sec:Experimental_Structure}
+
+\subsection{Construction}
+\label{sec:Construction}
+The building was composed of concrete walls, as shown in Fig.~\ref{fig:EL_Logo_Example}.
+
+\begin{figure}[!ht]
+\includegraphics[width=2in]{../Figures/el_logo_small}
+\caption{NIST Engineering Laboratory}
+\label{fig:EL_Logo_Example}
+\end{figure}
+
+\section{Fuel Load}
+
 \chapter{Results}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXAXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXAXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXAXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXAXX_HOSE}
 \caption{Hose pressure, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXOXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXOXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXOXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DNXOXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXAXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXAXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXAXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXAXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXOXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXOXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXOXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_DSXOXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A6}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXAOXX_BDP_A6}
 \caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXAOXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXAOXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXAOXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXAOXX_HOSE}
 \caption{Hose pressure, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A6}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXXAXX_BDP_A6}
 \caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXXAXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXXAXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXXAXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_HOSE}
+\includegraphics[width=6in]{../Figures_Plots/HOSE_IXXAXX_HOSE}
 \caption{Hose pressure, Test HOSE\_IXXAXX}
@@
 
-\section{Fire Tests}
+\section{Fire Tests ARE AWESOME!!}
 
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_GAS}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_HF}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_1_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_GAS}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_HF}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_2_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_GAS}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_HF}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
+\includegraphics[width=6in]{../Figures_Plots/FIRE_FA2S1C1NCX1_3_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}

### 2014-06-10 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update report and add figures

@@
 
-A firefighter inside is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
-While firefighters wear protective gear, the gear only offers finite levels of protection.
+A firefighter is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
+While firefighters wear protective gear, gear only offers finite levels of protection.
 The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140 $^{\circ}$C (284 $^{\circ}$F) \cite{mensch2011emergency}.
 Structural fire fighting coats and pants are tested to withstand temperatures of 260 $^{\circ}$C (500 $^{\circ}$F) \cite{nfpa2013standard}.
-Extended exposure to elevated temperatures can result in significant heat being transferred to the firefighter, putting him/her at risk.
-For the analysis of the model predicted exposure temperatures in the flow path, we have set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
-This means that temperatures visualized in the highest range in the model output are at a minimum of 260 $^{\circ}$C (500 $^{\circ}$F); the temperatures could be higher.
+Extended exposure to elevated temperatures can result in significant heat transferred to the firefighter, putting him/her at risk.
+Therefore, for analysis of the model predicted exposure temperatures, we set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
+This means that temperatures visualized in the highest range in the model output are at a minimum of 260 $^{\circ}$C (500 $^{\circ}$F); predicted temperatures could in fact be higher.
+
+Prior to door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
+Temperatures are highest at the Beta-Charlie corner where there is sufficient oxygen due to self-ventilation.
+Five seconds after the door fails, hot gases have traveled the length of the interior hallway and approached the doorway into the kitchen, approximately 4.5 m (14.8 ft) away from the source fire (cf Fig.~(\ref{fig:temp_top_165})).
+One minute after the door fails, the hallway temperatures are nominally at or above 260 $^{\circ}$C (500 $^{\circ}$F) through out the hallways corridor (cf Fig.~(\ref{fig:temp_top_220})).
+This illustrates the the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning on the rear porch.
+The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
+Fig.~(\ref{fig:temp_top_220}) also shows that that temperatures in the kitchen dropped below 100 $^{\circ}$C (212 $^{\circ}$F) as the large supply of air cooled/diluted the exhaust gases.
+Based on post-incident images of the kitchen and second floor stairwell, these predicted temperatures are realistic.
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_159}
+\caption{PLACEHOLDER: Temperature contours on the second floor, 1 second prior to door failure, 6ft above the floor.}
+\label{fig:temp_top_159}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_165}
+\caption{PLACEHOLDER: Temperature contour on the second floor, 5 seconds after door failure, 6ft above the floor.}
+\label{fig:temp_top_165}
+\end{figure}
+
+\begin{figure}[h!]
+\centering
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_200}
+\caption{PLACEHOLDER: Temperature contour on the second floor, 60 seconds after door failure, 6ft above the floor.}
+\label{fig:temp_top_220}
+\end{figure}
 
 \section{Tactical Considerations}
+In the last fifteen years, there have been fires throughout the country where the change in a flow path has had a significant impact on firefighter and occupant safety:
+
+{\bf UNDER DEVELOPMENT}
+
+\begin{itemize}
+\item NE Washington D.C., 1999
+\item Keokuk, IA, 1999
+\item Houston, TX, 2011
+\item Riverdale Heights, MD, 2012 
+\end{itemize}
 
 \chapter{Summary}
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 1/2 story single family structure in Chicago, Il that resulted in the death of a firefighter.
+The modeled fuel, fire size, and fire growth rate were estimated taking into account all available information: NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
+This resulted in a specified source fire of 12.3 MW, however based on ventilation the model predicted a peak HRR of $\approx$ 10 MW.
+The fire began in the attic and spread into the rear (Charlie side) porch.
+Spread of high temperature, toxic gases into the structure was limited by a closed steel door on the second floor.
+After prolonged exposure to elevated temperature and pressure, the door eventually failed.
+Prior to the door failure, a FF and Captain were on the second floor in the interior hallway.
+The door failure lead to the creation of flow path towards the front (Alpha side) door on the first floor of the structure.
+The flow path was comprised of toxic, high temperature combustion gases that rapidly changed the conditions where the FF and Captain were working.
+The rapid change in hazard level overcame the Captain before he could find egress to safety.
+After a MayDay, the Captain was rescued from the structure but later succumbed to his injuries.
 

### 2014-06-11 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update report and bib file

@@
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Fig.~(\ref{fig:temp_top_220}) also shows that that temperatures in the kitchen dropped below 100 $^{\circ}$C (212 $^{\circ}$F) as the large supply of air cooled/diluted the exhaust gases.
-Based on post-incident images of the kitchen and second floor stairwell, these predicted temperatures are realistic.
+Fig.~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90 $^{\circ}$C (194 $^{\circ}$F) and temperatures at the top of the stairs were at or below 70 $^{\circ}$C (158 $^{\circ}$F).
+At these points in the structure, the exhaust gases in the flow path are air cooled/diluted by the inflow ambient gas.
+Based on post-incident images of the kitchen and second floor stairwell, these predicted temperatures are on the appropriate order or magnitude.
 
@@
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_159}
-\caption{PLACEHOLDER: Temperature contours on the second floor, 1 second prior to door failure, 6ft above the floor.}
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
+\input{../Scripts/colorbar_std} 
+\input{../Scripts/colorbar_metric}
+\caption{Temperature contours on the second floor, 1 second prior to door failure, 1.83 m (6 ft) above the floor.}
 \label{fig:temp_top_159}
@@
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_165}
-\caption{PLACEHOLDER: Temperature contour on the second floor, 5 seconds after door failure, 6ft above the floor.}
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
+\input{../Scripts/colorbar_std} 
+\input{../Scripts/colorbar_metric}
+\caption{Temperature contours on the second floor, 5 seconds after door failure, 1.83 m (6 ft) above the floor.}
 \label{fig:temp_top_165}
@@
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_200}
-\caption{PLACEHOLDER: Temperature contour on the second floor, 60 seconds after door failure, 6ft above the floor.}
+\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
+\input{../Scripts/colorbar_std} 
+\input{../Scripts/colorbar_metric}
+\caption{Temperature contours on the second floor, 60 seconds after door failure, 1.83 m (6 ft) above the floor.}
 \label{fig:temp_top_220}
@@
 \section{Tactical Considerations}
-In the last fifteen years, there have been fires throughout the country where the change in a flow path has had a significant impact on firefighter and occupant safety:
+In the last fifteen years, there have been fires throughout the country where the change in a flow path has had a significant impact on firefighter and occupant safety.
+Table~\ref{tab:lodd} lists the NIOSH investigation report number, the outcome, and description of the flow path.
+It is clear that fires with rapid developing/changing flow paths, whether fire service induced, structure-failure induced, or nature induced are a significant hazard to the fire service.
+Prediction of the failure mode and failure time of the second floor door is not a reasonable expectation given the large set of unknowns the fire service faced on the fire ground.
+However, the timing of an interior attack on the structure given the state of fire growth in the rear of the structure identified by a size up, may not have been ideal.
+Research has shown that applying water from the exterior \cite{madrzykowski2009fire,kerber2009fire} into the structure can have a significant impact on controlling the fire prior to beginning interior operations.
 
-{\bf UNDER DEVELOPMENT}
-
-\begin{itemize}
-\item NE Washington D.C., 1999
-\item Keokuk, IA, 1999
-\item Houston, TX, 2011
-\item Riverdale Heights, MD, 2012 
-\end{itemize}
+\begin{table}
+\centering
+\captionof{table}{Flowpath LODD/LODI Incidents}\label{tab:lodd}
+\begin{tabular}{l l l}
+\toprule[1.5pt]
+NIOSH Report $\#$ & $\#$ LODD/LODI & Flow Path Details  \\
+\midrule
+\multirow{2}{*}{99-F01 \cite{NIOSH:Pettit} }    & \multirow{2}{*}{3 LODD}                                     & \multirow{2}{*}{\parbox{8cm} {From apartment into hallway on 10th floor of high-rise apartment building}} \\
+                 &                                                    & \\
+99-F21 \cite{NIOSH:Washenitz}         & 2 LODD/2 LODI                          & Basement to 1st floor \\
+F2000-04 \cite{NIOSH:Mezzanotte}   & 3 LODD/3 civilian deaths            & 1st floor to 2nd floor \\
+F2000-16 \cite{NIOSH:McFall} & 1 LODD/1 civilian death/1 LODI & 2nd floor hallway through 2nd floor apartment \\
+\multirow{2}{*}{F2000-23 \cite{NIOSH:McFall2}} & \multirow{2}{*}{1 LODD/2 LODI       }                   & \multirow{2}{*}{\parbox{8cm} {From ground level to 1st floor then to 2nd floor, flow exited through ceiling}} \\
+                 &                                                    & \\
+F2000-43 \cite{NIOSH:McFall3}         & 1 serious LODI/2 other LODI      & 1st floor to 2nd floor \\
+F2004-02  \cite{NIOSH:Berardinelli}  & 1 LODD                                       & 1st floor to basement \\
+F2005-02 \cite{NIOSH:Koedam}        & 1 LODD/4 LODI                           & C side to A side of the building \\
+F2005-04 \cite{NIOSH:McFall4}         & 1 LODD/9 LODI                           & Basement to 1st floor \\
+F2007-09 \cite{NIOSH:Tarley}           & 1 LODD/2 LODI                           & 3 story training burn $-$ flow through all levels \\
+F2007-35 \cite{NIOSH:Braddee}       & 4 LODI                                         & 1st floor to 2nd floor \\
+F2009-11 \cite{NIOSH:Merinar}         & 2 LODD                                        & C side to A side of the building \\
+F2011-13 \cite{NIOSH:Bowyer2}       & 2 LODD                                        & Lower level up stairs and through entry door and garage \\
+F2011-31 \cite{NIOSH:Loflin}            & 1 LODD                                        & Fire extended from lower level apartment \\
+F2012-28 \cite{NIOSH:Bowyer}        & 1 LODD/1LODI                            & Attic fire extended into closed porch and then into 2nd floor \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 
@@
 \includegraphics[width=.80\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption {Dimensioned drawing of 1$^{st}$ floor}
+\caption {Dimensioned drawing of 1$^{st}$ floor.}
 \label{fig:first_floor}
@@
 \includegraphics[width=.80\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption {Dimensioned drawing of 2$^{nd}$ floor}
+\caption {Dimensioned drawing of 2$^{nd}$ floor.}
 \label{fig:second_floor}

### 2014-06-16 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: add radios to charge list
Equipment Guide: Minor edits

@@
 The 1000 is a 4-slot chassis while the 1001 is a 12-slot chassis.
-The max scan rate of the chassis is (5 $\mu$s $\times$ \# of channels used)$^{-1}$.
-A 200 kS/s 16-bit digitizer, NI SCXI-1600, connects the chassis to the computer (via USB).
+The max scan rate of the chassis is (5~$\mu$s $\times$ \# of channels used)$^{-1}$.
+A 200~kS/s 16-bit digitizer, NI SCXI-1600, connects the chassis to the computer (via USB).
 The remaining chassis slots are filled with the NI SCXI-1102.
-The SCXI-1102 is a 32 channel thermocouple amplifier/voltage input module.
-Each SCXI-1102 is connected to a TC-2095; a shielded, 32 channel, rack-mountable terminal accessory.
-All of the measurement devices connect to the TC-2095 using either chromel-alomel connectors (temperature) or copper-copper connectors (voltage).
+The SCXI-1102 is a 32-channel thermocouple amplifier/voltage input module.
+Each SCXI-1102 is connected to a TC-2095; a shielded, 32-channel, rack-mountable terminal accessory.
+All of the measurement devices connect to the TC-2095 using either chromel-alumel connectors (temperature) or copper-copper connectors (voltage).
 A schematic of the hardware configuration is shown in Fig.~(\ref{fig:daq_schem}).
@@
 \section{Software}
-Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using DAQ-mX. Note that in the current configuration, the computer must also have a 32-bit operating system on it.
+Channel lists are built using NI-MAX and fed into 32-bit NI LabVIEW as a task using NI-DAQmx. Note that in the current configuration, the computer must also have a 32-bit operating system on it.
 
@@
 
-Two types of k-type thermocouples (TCs) are used: bare bead and metal sheathed.
-The bare bead TCs are made from 30 gauge glass braid insulated solid wire.
+Two types of type~K thermocouples (TCs) are used: bare bead and metal sheathed.
+The bare bead TCs are made from 30~gauge glass braid insulated solid wire.
 The bare bead thermocouples are used in the TC trees and single point measurements.
-The metal sheathed TCs (\#125-KSL-600-U from Furnace Parts) feature a 1/8 in diameter Inconel 600 sheath and an ungrounded junction.
+The metal sheathed TCs (\#125-KSL-600-U from Furnace Parts) have a 1/8~in diameter Inconel 600 sheath and an ungrounded junction.
 These TCs are moisture proof and are typically used in conjunction with bi-directional probes.
-The sheathed TCs are typically ordered with a 48 in TC and 120 in type K lead wire (NIST01A from Furnace Parts) or a 144 in TC and 120 in type K lead wire (NIST01B from Furnace Parts).
+The sheathed TCs are typically ordered with a 48~in TC and 120~in type~K lead wire (NIST01A from Furnace Parts) or a 144~in TC and 120~in type K lead wire (NIST01B from Furnace Parts).
 
@@
 \captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
-\begin{tabular}{l l l}
+\begin{tabular}{lll}
 \toprule[1.5pt]
@@
 The Miyachi Unitek TC Welder (01-0196-02) is a manual feed thermocouple welder designed to weld thermocouple wires together without oxide layers by using argon cover gas.
-The welder can handle wires from 38 gauge to 20 gauge.
+The welder can handle wires from 38~gauge to 20~gauge.
 
@@
 
-Two sets of type K extension wire are used: single pair (EXPP-K-24-S-1000) or 20 pair (20KX24SPP). Both wires are 24 gauge, 7-32 stranded, polyvinyl coated wire.
+Two sets of type~K extension wire are used: single pair (EXPP-K-24-S-1000) or 20 pair (20KX24SPP). Both wires are 24~gauge, 7-32 stranded, polyvinyl coated wire.
 
@@
 \captionof{table}{Thermocouple Connections}\label{tab:TC_connect}
-\begin{tabular}{l l l}
+\begin{tabular}{lll}
 \toprule[1.5pt]
@@
 \caption{Schematic of pressure measurement setup for use with BDPs.}
-\label{fig:daq_schem}
+\label{fig:bdp_schem}
 \end{figure}
@@
     \item DVCRs
+    \item Radios
     \end{itemize}

### 2014-06-16 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment: Delete and reorganize old water pressure sensor info

@@
 
+\chapter{Water Flow Sensor}
+\label{chap:Water_Flow_Sensor}
+
+Arduino Config, Setup, and Data Logging
+
+The Arduinos record voltage data locally, and they transmit voltage data to the host computer via the AMQP messaging protocol.
+The host computer uses RabbitMQ to act as a broker.
+Python scripts and the pika module send and receive AMQP messages.
+The following steps setup the host computer and Arduinos for this purpose.
+Server (Host Computer)
+
+Note: the following assumes that the server/host computer’s address is 192.168.1.100. It’s best to configure the host computer with a static IP address using static DHCP or manually.
+
+=== Host Computer (RabbitMQ) ===
+
+1) Install RabbitMQ for your platform and start the RabbitMQ server (./sbin/rabbitmq-server on Mac or Linux).
+
+https://www.rabbitmq.com/
+
+2) Copy the receive\_data.py script from the NIST-FIRE repository to the data logging computer.
+
+3) Install Python (The Anaconda Python distribution from Continuum Analytics is recommended)
+
+4) Install the pika module for Python using
+
+\begin{verbatim}
+pip install pika
+\end{verbatim}
+
+5) Run the receive\_data.py script as
+
+\begin{verbatim}
+python receive\_data.py 192.168.1.100 output.csv
+\end{verbatim}
+
+== Host Computer (NTP Time Server) ==
+
+On Windows, download and install the NTP server
+
+http://www.meinbergglobal.com/english/sw/ntp.htm
+
+Mac and Linux use NTP natively.
+
+=== Client (Arduino) ===
+
+== Install pressure\_sensor Sketch on the Arduino ==
+
+1) Install Arduino IDE
+
+http://arduino.cc/
+
+2) Plug the Arduino Yun into the USB port of the host computer.
+
+3) Set the Tools > Board to Arduino Yun and the Tools > Port to the /dev/ttyusbmodemXXXXXX setting that matches the plugged-in Arduino.
+
+4) A Sketch is a script that runs on the Arduino microcontroller.
+Using the Arduino IDE, install the pressure\_sensor Sketch on the Arduino from the NIST-FIRE repository.
+This enables the reading and writing of data from the analog-to-digital converter via the REST API on the Arduino.
+Note: this sketch requires the Adafruit ADS 1015 library from https://github.com/adafruit/Adafruit\_ADS1X15.
+
+== Configure the Arduino ==
+
+1) Unplug the Arduino from the computer, and power on the Arduino from the battery.
+
+2) Connect to the Arduino WiFi network.
+Access the Arduino web interface (http://arduino.local) with the default password of “arduino”.
+Set the Arduino name (referred to as <arduino\_name> in the following steps), time zone, and WiFi network information on the Arduino web config.
+Also, set the “REST API Access” to be “Open”.
+
+3) SSH to the Arduino at root@<arduino\_name>.local and install the SFTP server, ntpclient, pip, and pika (for AMQP) on the Arduino
+
+\begin{verbatim}
+opkg update
+opkg install openssh-sftp-server ntpclient distribute python-openssl
+easy\_install pip
+pip install pika
+\end{verbatim}
+
+4) By default, the microSD card on the Arduino is mounted at /mnt/sda1. Copy the send\_data.py script from the NIST-FIRE repository to /mnt/sda1 on the Arduino.
+
+5) Go to System > Startup > Local Startup in the Arduino web config and add a startup line to the Local Config section (/etc/rc.local)
+
+\begin{verbatim}
+python /mnt/sda1/send\_data.py 192.168.1.100 <arduino\_name> /mnt/sda1/output.csv
+\end{verbatim}
+
+6) The default NTP service is not very robust, so we will replace it with ntpclient and have it sync with the NTP server every 2 minutes. Disable the default NTP service using
+
+\begin{verbatim}
+/etc/init.d/sysntpd disable
+\end{verbatim}
+
+Configure the ntpclient service by editing /etc/config/ntpclient to be
+
+\begin{verbatim}
+config ntpserver
+        option hostname '192.168.1.100'
+        option port     '123'
+
+config ntpserver
+        option hostname '0.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '1.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '2.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '3.pool.ntp.org'
+        option port     '123'
+
+config ntpdrift                                 
+        option freq     '0'
+
+config ntpclient                                
+        option interval 120
+\end{verbatim}
+
+7) Reset power to the Arduino, and then it should start broadcasting data values within about 2 minutes of booting.
+
+\section{Parts}
+
+Mouser \#: 72-T93YB-1K 
+Mfr. \#: T93YB102KT20
+Desc.:  Trimmer Resistors - Through Hole 3/8" SQ V/ADJ 1K
+\$1.48
+
+Mouser \#:   595-TLV2772IP   
+Mfr. \#: TLV2772IP
+Desc.:  Operational Amplifiers - Op Amps Dual 2.7V R/R
+\$2.36
+
+Mouser \#:   517-929834-02-36-RK 
+Mfr. \#: 929834-02-36-RK
+Desc.: Headers \& Wire Housings FULL STICK HDR/36POS
+\$1.13
+
+Mouser \#:   932-MIKROE-513  
+Mfr. \#: MIKROE-513
+Desc.:  Jumper Wires WIRE JUMPER MALE TO MALE 15CM 10PK
+\$3.00
+
+Mouser \#:   932-MIKROE-197  
+Mfr. \#: MIKROE-197
+Desc.:  Daughter Cards \& OEM Boards SMARTPROTO PROTO ADAPTER BOARD
+\$4.90
+
+Mouser \#:   652-PDB12-H4251102BF    
+Mfr. \#: PDB12-H4251-102BF
+Desc.:  Potentiometers 1K LINEAR 12MM
+\$0.649
+
+\section{Flow Meters}
+
+Fire Research Corp.
+http://www.fireresearch.com/product.php?id=fta400
+
+Elkhart Brass Hose and Nozzle Accessories
+http://www.elkhartbrass.com/products/accessories/hose-nozzle/multimedia
+http://www.elkhartbrass.com/files/aa/downloads/catalog/catalog-f2-02-01.pdf
+
+Akron Brass Zero Torque Nozzle
+http://www.akronbrass.com/1-1-2-x-1-1-2-zero-torque-shutoff
+
+Omega Pressure Transducers
+http://www.omega.com/prodinfo/pressuretransducers.html
+
+Omega Flow Meters
+http://www.omega.com/pptst/FP7002.html
+http://www.omega.com/pptst/FPB100.html
+
+Task Force Tips Sho-Flow
+http://www.tft.com/productsearch/product\_details.cfm?product=SF-BF-BF-11L\&ProductGroup=Sho-Flow\%20Indicator
+
+Flow Equipment
+http://www.firehydrant.org/links/flowequip.html
+
+Hose Monster Equipment
+http://www.hosemonster.com/products-pages-30.php
+
+Pollard Water
+http://www.pollardwater.com/pages\_index/index\_flow\_testing.asp
+
 \appendix

### 2014-06-16 Equipment/Equipment_Guide/Equipment_Guide.tex
Equipment Guide: Edits to water flow sensor notes

--- 2014-06-16 Equipment/Equipment_Guide/Equipment_Guide.tex
@@
 
+\chapter{Water Flow Sensor}
+\label{chap:Water_Flow_Sensor}
+
+\section{Arduino Config, Setup, and Data Logging}
+
+The Arduinos record voltage data locally, and they transmit voltage data to the host computer via the AMQP messaging protocol.
+The host computer uses RabbitMQ to act as a broker.
+Python scripts and the pika module send and receive AMQP messages.
+The following steps setup the host computer and Arduinos for this purpose.
+
+\subsection{Host Computer (RabbitMQ)}
+
+Note: the following assumes that the server/host computer's address is 192.168.1.100. It's best to configure the host computer with a static IP address using static DHCP or manually.
+
+\begin{enumerate}
+\item Install RabbitMQ for your platform and start the RabbitMQ server (./sbin/rabbitmq-server on Mac or Linux).
+https://www.rabbitmq.com/
+\item Copy the receive\_data.py script from the NIST-FIRE repository to the data logging computer.
+\item Install Python (The Anaconda Python distribution from Continuum Analytics is recommended)
+\item Install the pika module for Python using
+\begin{verbatim}
+pip install pika
+\end{verbatim}
+\item Run the receive\_data.py script as
+\begin{verbatim}
+python receive_data.py 192.168.1.100 output.csv
+\end{verbatim}
+\end{enumerate}
+
+\subsection{Host Computer (NTP Time Server)}
+
+On Windows, download and install the NTP server
+
+http://www.meinbergglobal.com/english/sw/ntp.htm
+
+Note: you might need to disable the Windows Firewall service so that incoming connections will not be blocked.
+
+Mac and Linux use NTP natively.
+
+\subsection{Arduino Client (Sketch)}
+
+\begin{enumerate}
+\item Install Arduino IDE
+http://arduino.cc/
+\item Plug the Arduino Yun into the USB port of the host computer.
+\item Set the Tools > Board to Arduino Yun and the Tools > Port to the /dev/ttyusbmodemXXXXXX setting that matches the plugged-in Arduino.
+\item A Sketch is a script that runs on the Arduino microcontroller.
+Using the Arduino IDE, install the pressure\_sensor Sketch on the Arduino from the NIST-FIRE repository.
+This enables the reading and writing of data from the analog-to-digital converter via the REST API on the Arduino.
+Note: this sketch requires the Adafruit ADS 1015 library from https://github.com/adafruit/Adafruit\_ADS1X15.
+\end{enumerate}
+
+\subsection{Arduino Client (Linux)}
+
+\begin{enumerate}
+\item Unplug the Arduino from the computer, and power on the Arduino from the battery.
+\item Connect to the Arduino WiFi network.
+Access the Arduino web interface (http://arduino.local) with the default password of ``arduino''.
+Set the Arduino name (referred to as <arduino\_name> in the following steps), time zone, and WiFi network information on the Arduino web config.
+Also, set the ``REST API Access'' to be ``Open''.
+\item SSH to the Arduino at root@<arduino\_name>.local and install the SFTP server, ntpclient, pip, and pika (for AMQP) on the Arduino
+\begin{verbatim}
+opkg update
+opkg install openssh-sftp-server ntpclient distribute python-openssl
+easy_install pip
+pip install pika
+\end{verbatim}
+\item By default, the microSD card on the Arduino is mounted at /mnt/sda1. Copy the send\_data.py script from the NIST-FIRE repository to /mnt/sda1 on the Arduino.
+\item Go to System > Startup > Local Startup in the Arduino web config and add a startup line to the Local Config section (/etc/rc.local)
+\small
+\begin{verbatim}
+python /mnt/sda1/send_data.py 192.168.1.100 <arduino_name> /mnt/sda1/output.csv
+\end{verbatim}
+\normalsize
+\clearpage
+\item The default NTP service is not very robust, so we will replace it with ntpclient and have it sync with the NTP server every 2 minutes. Disable the default NTP service using
+\begin{verbatim}
+/etc/init.d/sysntpd disable
+\end{verbatim}
+Configure the ntpclient service by editing /etc/config/ntpclient to be
+\begin{verbatim}
+config ntpserver
+        option hostname '192.168.1.100'
+        option port     '123'
+
+config ntpserver
+        option hostname '0.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '1.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '2.pool.ntp.org'
+        option port     '123'
+
+config ntpserver
+        option hostname '3.pool.ntp.org'
+        option port     '123'
+
+config ntpdrift                                 
+        option freq     '0'
+
+config ntpclient                                
+        option interval 120
+\end{verbatim}
+\item Reset power to the Arduino, and then it should start broadcasting data values within about 2 minutes of booting.
+\end{enumerate}
+
+\section{Parts}
+
+\begin{itemize}
+\item Mouser \#:   517-929834-02-36-RK \\
+Mfr. \#: 929834-02-36-RK \\
+Desc.: Headers \& Wire Housings FULL STICK HDR/36POS \\
+\$1.13
+
+\item Mouser \#:   932-MIKROE-197 \\
+Mfr. \#: MIKROE-197 \\
+Desc.:  Daughter Cards \& OEM Boards SMARTPROTO PROTO ADAPTER BOARD \\
+\$4.90
+\end{itemize}
+
+%  ==============
+%  = Appendices =
+%  ==============
+
 \appendix

### 2014-06-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update report writeup

@@
 BC \> Battalion Chief \\
+E \> Engine \\
 FDS \> Fire Dynamics Simulator \\
@@
 HRRPUA \> Heat Release Rate per Unit Area \\
+LODD \> Line of Duty Death \\
+NIOSH \> National Institute for Occupational Safety and  Health \\
 NIST \> National Institute of Standards and Technology \\
 SFPE \> Society of Fire Protection Engineers \\
+SQ \> Squad \\
+TL \> Tower Ladder \\
 \end{tabbing}
@@
 Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other fatality fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
+NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other line of duty death (LODD) fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
 The overriding objective of all of these studies is to improve the safety of fire fighters.
@@
 On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-Changes in the ventilation flow path caused a rapid change in the fire dynamics resulting in fire and smoke penetration to an interior second floor hallway.
-NIST assisted with examining the fire dynamics of this incident.
-NIST performed computer simulations of the fire using Fire Dynamics Simulator and Smokeview, to provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
+Changes in the ventilation flow path resulted in fire and smoke penetration to an interior second floor hallway.
+NIST examined the fire dynamics of this incident at the request of NIOSH and Chicago Fire Department (CFD) .
+Computer simulations of the fire using Fire Dynamics Simulator and Smokeview, provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
 \begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the thermal and fire conditions in this multi-story residential structure.
+\item To examine with physics-based calculations the effect of flow path on the temperature, pressure and fire conditions in this multi-story residential structure.
 \item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
@@
 Then the Captain and Firefighter took their hose line to the second floor of the structure.
-At approximately 5:21, the Captain and Fire Fighter are on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
+At approximately 5:21, the Captain and Fire Fighter were on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
 Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
@@
 \toprule[1.5pt]
-Incident Time & Fire Behavior / Fireground Operation  \\
+Incident Time [hr:min:s] & Fire Behavior / Fireground Operation  \\
 \midrule
-\multirow{2}{*}{17:15} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+\multirow{2}{*}{17:15:00} & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
          & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-17:16    & Dispatch for a Still Alarm. \\ [.25cm]
-\multirow{2}{*}{17:20}    & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
+\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ is two engine companies, two truck companies, and a battalion chief.}} \\
+         & \\[.25cm]
+\multirow{2}{*}{17:20:00}    & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
          & \\[.25cm] 
@@
 17:21:30 & 1$^{st}$ floor exterior porch door opened. \\[.25cm]
-\multirow{2}{*}{17:23}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
          & \\[.25cm]
-17:24    & Water applied to attic from the rear exterior position. \\[.25cm]
-17:27    & IC calls a Mayday. \\[.25cm]
-17:29    & E123 Capt. carried out of structure. \\
+17:24:00    & Water applied to attic from the rear exterior position. \\[.25cm]
+17:25:00    & SQ5 makes entry through front of structure. \\[.25cm]
+17:27:00    & After hearing a Mayday call from SQ5, IC calls a Mayday. \\[.25cm]
+17:29:00    & E123 Capt. carried out of structure. \\
 \bottomrule[1.25pt]
@@
 \end{itemize}
-To develop the simulation, a timeline of events based on the collected information must be developed.
+To develop the simulation, a timeline of events based on the collected information is developed.
 From this time line actions may be input into the model, such as venting a window at a given time.
-
-The development of the model geometry and development of the input file is straight forward with guidance from the FDS User's Guide ~\cite{FDS_Users_Guide} or third party software.
+To develop the model geometry and remainder of the input file is straight forward with guidance from the FDS User's Guide ~\cite{FDS_Users_Guide} or third party software.
 Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
@@
 \label{geom}
-The structure was a 2 1/2 story residential building with balloon frame construction and a wood gable roofing system.
+The structure was a 2 1/2 story residential building with balloon frame construction and gable roof.
 The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
@@
 This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
-Interior walls were constructed from wood frame dimensioned lumber with 1.27 cm (0.5 in) gypsum board over top.
+Interior walls were constructed from wood frame dimensioned lumber with 12.7 mm (0.5 in) gypsum board over top.
 Additionally there was a half-story attic that was used to house the structure's hot water heater.
@@
 The dimensions were found from on-scene measurements using a tape measure.
-Measurements were made to the nearest 1.27 cm (0.5 in).
+Measurements were made to the nearest 12.7 mm (0.5 in).
 Based on difficulty of making some of the measurements due to the condition of the post-fire structure, the uncertainty in the measurements is estimated to be on the order of $\pm$ 1 \%.
@@
 \toprule[1.5pt]
-Baseline Simulation & Alternative Simulation & Ventilation Area [m$^2$] & Type & Structure Side \\
+Baseline Simulation [s] & Alternative Simulation [s] & Ventilation Area [m$^2$] & Type & Structure Side \\
 \midrule
-00    &  00   & 0.11 & Window      & Charlie \\
+0    &  0   & 0.11 & Window      & Charlie \\
 40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
@@
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 1~\cite{NUREG_1824}.
-The grid resolution used in the model falls within typical, engineering $D^*/\dx$ values.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824}.
+The grid resolution used in this model falls within typical, engineering $D^*/\dx$ values.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
@@
 \toprule[1.5pt]
-Incident Time & Simulation Time & Fire Behavior / Fireground Operation  \\
+Incident Time [hr:min:s] & Simulation Time [s] & Fire Behavior / Fireground Operation  \\
 \midrule
-\multirow{2}{*}{17:15} &    & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-17:16 &      & Dispatch for a Still Alarm. \\ [0.25cm]
-         &  \multirow{2}{*} {0:00} &  \multirow{2}{*}{\parbox{10cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
+\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ is two engine companies, two truck companies, and a battalion chief.}} \\
+         & \\[.25cm]
+         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{10cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
          & & \\[0.25cm]
-\multirow{2}{*}{17:20} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
+\multirow{2}{*}{17:20:00} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
 Rear porch ignites in model.}} \\
@@
          & 0:55 & Model ventilation on beta side. \\[.25cm] 
-17:21:00 & 1:40 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
-17:21:30 & 2:10 & 1$^{st}$ floor exterior porch door opened. Attic fire ignites in model. \\[.25cm]
-        & 2:15 & Additional model ventilation on beta side. \\[.25cm] 
-        & 2:40 & Top of interior door fails in model. \\[.25cm] 
-\multirow{2}{*}{17:23}    & \multirow{2}{*}{3:40} & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+17:21:00 & 100 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
+17:21:30 & 130 & 1$^{st}$ floor exterior porch door opened. Attic fire ignites in model. \\[.25cm]
+        & 135 & Additional model ventilation on beta side. \\[.25cm] 
+        & 160 & Top of interior door fails in model. \\[.25cm] 
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
          & & \\[.25cm]
-17:24    &   & Water applied to attic from the rear exterior position. \\[.25cm]
-17:27    & 5:00  & IC calls a Mayday. Simulation ends. \\[.25cm]
-17:29    &   & E123 Capt. carried out of structure. \\
+17:24:00    &   & Water applied to attic from the rear exterior position. \\[.25cm]
+17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
+\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{10cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
+         & &  \\[.25cm]
+17:29:00    &   & E123 Capt. carried out of structure. \\
 \bottomrule[1.25pt]

### 2014-06-19 Equipment/Equipment_Guide/Equipment_Guide.tex
Water Flow Sensor: Update Arduino sketch name

@@
 \item A Sketch is a script that runs on the Arduino microcontroller.
-Using the Arduino IDE, install the pressure\_sensor Sketch on the Arduino from the NIST-FIRE repository.
+Using the Arduino IDE, install the adc\_voltage Sketch on the Arduino from the NIST-FIRE repository.
 This enables the reading and writing of data from the analog-to-digital converter via the REST API on the Arduino.
-Note: this sketch requires the Adafruit ADS 1015 library from https://github.com/adafruit/Adafruit\_ADS1X15.
+Note: this sketch requires the Adafruit ADS 1X15 library from https://github.com/adafruit/Adafruit\_ADS1X15.
 \end{enumerate}

### 2014-06-20 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update report

@@
 \begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the temperature, pressure and fire conditions in this multi-story residential structure.
+\item To examine with physics-based calculations the effect of flow path on the temperature, pressure,Back and fire conditions in this multi-story residential structure.
 \item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
@@
          & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ is two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
          & \\[.25cm]
@@
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ is two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
          & \\[.25cm]

### 2014-06-20 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update to report addressing comments

@@
 Additionally there was a half-story attic that was used to house the structure's hot water heater.
-There were three sets of stairs in the structure: one front stairwell that connected the first and second levels, one rear stairwell that connected the first and second levels and a second rear set of stairs which provided access to the attic.
-Entry to the structure can be made either in the front (Alpha side) or rear (Charlie side), see Fig.~(\ref{fig:simp_geom}).
+There were three sets of stairs in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
+Entry to the first floor of thep structure can be made either in the front (Alpha side) or rear (Charlie side), see Fig.~(\ref{fig:simp_geom}).
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
@@
 \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-\includegraphics[width=6in]{../Figures/Simple_1_metric} \\
-\includegraphics[width=6in]{../Figures/Simple_2_metric}
+\includegraphics[width=6in]{../Figures/1st_Floor_Metric} \\
+\includegraphics[width=6in]{../Figures/2nd_Floor_Metric}
 \end{tabular*}
@@
          & & \\[0.25cm]
-\multirow{2}{*}{17:20:00} & \multirow{2}{*}{0:40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
+\multirow{2}{*}{17:20:00} & \multirow{2}{*}{40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
 Rear porch ignites in model.}} \\
          & & \\[.25cm] 
-         & 0:45 & Model ventilation on charlie side. \\[.25cm] 
-         & 0:55 & Model ventilation on beta side. \\[.25cm] 
+         & 45 & Model ventilation on charlie side. \\[.25cm] 
+         & 55 & Model ventilation on beta side. \\[.25cm] 
 17:21:00 & 100 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
@@
 \label{HRR}
-The heat release rate output data from FDS quantifies the model-predicted rate of energy release in the simulation.
+The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
 Here, we examine impact of ventilation on fire size.
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption{FDS predicted pressure contours, 1 second prior to interior door failure.}
+\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1 Pa is 1.4 $\times 10 ^{-4}$ psi.}
 \label{fig:pres_159s}
@@
 Gases at elevated pressure will always travel toward an area of lower pressure.
-When the interior door fails, the lower pressure outlet is through the front door on the alpha side of the structure.
-As a result, the gases produced by the fire will flow through the interior hallway, through the kitchen, down the front stairs and out the front door.
+The door acts as a boundary between the high and low pressure areas.
+Once the door fails open, the high pressure gases flow toward the low pressure areas in the house, hallway, kitchen, and front stairwell.
 The velocity vectors in Fig.~(\ref{fig:velo_175s}), 15 seconds after the interior door fails, confirms this flow direction within the structure.
@@
 \input{../Scripts/colorbar_metric_velo}
-\caption{FDS predicted velocity vectors, 15 second after interior door failure.}
+\caption{FDS simulated velocity vectors, 15 second after interior door failure.}
 \label{fig:velo_175s}
@@
 \label{temp}
-Analysis of the predicted simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+Analysis of the simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
 Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate the changing interior conditions.
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS predicted temperature contours, 1 second prior to rear door opening.}
+\caption{FDS simulated temperature contours, 1 second prior to rear door opening.}
 \label{fig:temp_129s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS predicted temperature contours, 1 second prior to interior door failure.}
+\caption{FDS simulated temperature contours, 1 second prior to interior door failure.}
 \label{fig:temp_159s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS predicted temperature contours, 1 second after interior door fails.}
+\caption{FDS simulated temperature contours, 1 second after interior door fails.}
 \label{fig:temp_161s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS predicted temperature contours, 15 seconds after interior door fails.}
+\caption{FDS simulated temperature contours, 15 seconds after interior door fails.}
 \label{fig:temp_175s}
@@
 \section{Hallway Flow Path}
-From on-reports from the BC (Chapter~\ref{fire_sum}) and simulation results (Chapter~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
-The simulation, however, showed a high hazard environment developing on the second floor.
-By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was involved.
+From on-scene reports from the BC (Chapter~\ref{fire_sum}) and simulation results (Chapter~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
+From the NIOSH report, while the BC was inside the structure on the second floor, the  BC observed only a light haze and a glow around the door between the hallway and enclosed porch.
+This indicated that some amount of the fire was burring in the area of the enclosed porch.
+The simulation shows a high hazard area in the attic and the enclosed porch at this time.
+By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
 Temperature and pressure, greater than 260 $^{\circ}$C (500 $^{\circ}$F) and 5 Pa respectively, were on the Charlie side of the steel door at the rear of the structure.
@@
 Recent experiments conducting by the National Institute of Standards and Technology revealed similar post-fire states after doors were exposed to fires.
-Fig.~(\ref{fig:SC_doorfold}) shows doors from two different house fire experiments in which the door folded in the direction of the flow path.
+Fig.~(\ref{fig:SC_doorfold}) shows doors from two different house fire experiments in different stages of degradation.
+In both cases note that the door knob assembly served as a pivot point for the upper portion of the steel from the door to collapse around.
+This is similar to the location of the folds in the remains of the steel door that was located between the hallway and the enclosed porch.
 
@@
 
-While we have an estimated time of failure for the door, the key take away is that after the door failed an interior flow path from the Charlie side to the Alpha side of the structure was created.
+While we have estimated the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch (Charlie side) to the kitchen (Alpha side) of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
-The combustion gases at elevated temperature and pressure flowed toward ambient conditions; the flow path was through the interior hallway, kitchen, and down the Alpha-Delta stairwell and out of the structure through the front door.
-The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases  on the second flow following the door failure.
+The combustion-gases at elevated temperature and pressure  in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seems to equalize.
+The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
 
@@
 
-A firefighter is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
+A person is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
 While firefighters wear protective gear, gear only offers finite levels of protection.
@@
 Extended exposure to elevated temperatures can result in significant heat transferred to the firefighter, putting him/her at risk.
-Therefore, for analysis of the model predicted exposure temperatures, we set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
+Therefore, for analysis of the modeled exposure temperatures, we set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
 This means that temperatures visualized in the highest range in the model output are at a minimum of 260 $^{\circ}$C (500 $^{\circ}$F); predicted temperatures could in fact be higher.
@@
 Prior to door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
-Temperatures are highest at the Beta-Charlie corner where there is sufficient oxygen due to self-ventilation.
+Temperatures are highest at the Beta-Charlie corner where there is sufficient oxygen due to the section of porch wall that had burned away allowing additional oxygen to mix with the fuel rich fire gases.
 Five seconds after the door fails, hot gases have traveled the length of the interior hallway and approached the doorway into the kitchen, approximately 4.5 m (14.8 ft) away from the source fire (cf Fig.~(\ref{fig:temp_top_165})).
-One minute after the door fails, the hallway temperatures are nominally at or above 260 $^{\circ}$C (500 $^{\circ}$F) through out the hallways corridor (cf Fig.~(\ref{fig:temp_top_220})).
-This illustrates the the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning on the rear porch.
+Within one minute after the door fails, the hallway temperatures are nominally at or above 260 $^{\circ}$C (500 $^{\circ}$F) through out the hallway (cf Fig.~(\ref{fig:temp_top_220})).
+This illustrates that the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
@@
 At these points in the structure, the exhaust gases in the flow path are air cooled/diluted by the inflow ambient gas.
-Based on post-incident images of the kitchen and second floor stairwell, these predicted temperatures are on the appropriate order or magnitude.
-
+These modeled temperatures are consistent with the post-incident conditions documented in the kitchen and second floor stairwell.
 \begin{figure}[h!]
@@
 \section{Tactical Considerations}
-In the last fifteen years, there have been fires throughout the country where the change in a flow path has had a significant impact on firefighter and occupant safety.
-Table~\ref{tab:lodd} lists the NIOSH investigation report number, the outcome, and description of the flow path.
-It is clear that fires with rapid developing/changing flow paths, whether fire service induced, structure-failure induced, or nature induced are a significant hazard to the fire service.
-Prediction of the failure mode and failure time of the second floor door is not a reasonable expectation given the large set of unknowns the fire service faced on the fire ground.
-However, the timing of an interior attack on the structure given the state of fire growth in the rear of the structure identified by a size up, may not have been ideal.
-Research has shown that applying water from the exterior \cite{madrzykowski2009fire,kerber2009fire} into the structure can have a significant impact on controlling the fire prior to beginning interior operations.
+There have been many fires where the change in a flow path has had an adverse impact on firefighter and occupant safety.
+Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years, where it could be determined that it was a flow path related incident.
+The table lists the NIOSH investigation number, the outcome, and a brief description of the flow path.
+
+Based on a review of these incidents, it is clear that fires with rapidly developing or changing flow paths are a significant hazard to the fire service.
+The development of, or changes in a flow path could be caused by the failure of a component of the structure, such as a door, window or portion of a ceiling, wall or floor.
+Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.
+Uncoordinated ventilation can also be the cause of increased thermal hazards within a flow path.
+
+In this case, the thermal degradation of the steel faced, wood framed, door led to a rapid change in thermal conditions in the hallway resulting in a lethal exposure to victim.
+Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns the fire fighters faced on the fire ground.
+In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
+Research has been conducted \cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, UL and others that demonstrates that applying water from the exterior into the fire area of a structure, prior to the start of interior operations, can significantly improve the safety of fire fighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
 
@@
 The modeled fuel, fire size, and fire growth rate were estimated taking into account all available information: NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3 MW, however based on ventilation the model predicted a peak HRR of $\approx$ 10 MW.
-The fire began in the attic and spread into the rear (Charlie side) porch.
-Spread of high temperature, toxic gases into the structure was limited by a closed steel door on the second floor.
-After prolonged exposure to elevated temperature and pressure, the door eventually failed.
-Prior to the door failure, a FF and Captain were on the second floor in the interior hallway.
-The door failure lead to the creation of flow path towards the front (Alpha side) door on the first floor of the structure.
-The flow path was comprised of toxic, high temperature combustion gases that rapidly changed the conditions where the FF and Captain were working.
-The rapid change in hazard level overcame the Captain before he could find egress to safety.
-After a MayDay, the Captain was rescued from the structure but later succumbed to his injuries.
+This resulted in a specified source fire of 12.3 MW, however based on the limited ventilation in the attic and enclosed porch the model generated a peak HRR of approximately 10 MW as a result of the limited supply of oxygen.
+The fire began in the attic and spread down into the enclosed porch on the rear (Charlie side) of the structure.
+The spread of heat and fire gases into the second floor of the structure was limited by a closed steel faced, wood framed door that was located between the enclosed porch and the hallway.
+After exposure to the elevated temperature and pressure from the fire in the porch area, the wood frame of the door decomposed and the steel faces of the door failed and collapsed inward.
+The door failure resulted in the creation of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
+The temperature of the gases that flowed into the hallway at face height exceeded 260 $^{\circ}$C (500 $^{\circ}$F).
+
+Unfortunately a FF and a Captain were advancing a hose line in the hallway at the time of the failure of the door.
+The Captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday, the Captain was rescued from the structure but later succumbed to his injuries.
 
 \chapter{Acknowledgements}
-The authors would like to thank the Chicago Fire Department, especially {\em names}.
-The authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
+The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck.
+The authors would also like to thank John Culbertson of Central Valley Fire District, MT for his assistance in compiling Table~\ref{tab:lodd}.
+Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
 

### 2014-06-20 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: update report

@@
 \begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the temperature, pressure,Back and fire conditions in this multi-story residential structure.
+\item To examine with physics-based calculations the effect of flow path on the temperature, pressure, and fire conditions in this multi-story residential structure.
 \item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
@@
 To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1453 ft$^2$) plus there is 105 m$^2$ (1130 ft$^2$) of floor area in the attic.
+Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1453 ft$^2$) with 7 m$^2$ (75 ft$^2$) walls on the Alpha and Charlie sides.
+Additionally there is 105 m$^2$ (1130 ft$^2$) of floor area in the attic.
 Examination of post incident images showed that the floor immediately over the back porch burned away.
 That area will be considered as part of the porch fire.
-Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire.
-To estimate the total attic fire size, we include the underside roof area (134 m$^2$) and the floor area (43 m$^2$ (463 ft$^2$)).
-Using an HRRPUA of wood of 51 kW/m$^2$, results in a fire size of 9 MW.
+Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire and 90 \% of the roof.
+To estimate the total attic fire size, we include the underside roof area (120 m$^2$), two end walls (14 m$^2$) and the floor area (43 m$^2$ (463 ft$^2$)).
+Using an HRRPUA of wood of 51 kW/m$^2$, results in a potential peak fire size of 9 MW.
 To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$ (258 ft$^2$)).
 The total area is 64 m$^2$ (689 ft$^2$).
-Using the same HRRPUA of 51 kW/m$^2$, the fire size on the porch is approximately 3.3 MW.
-The total fire size for this structure is estimated to be 12.3 MW.
+Using the same HRRPUA of 51 kW/m$^2$, the potential peak fire size on the porch is approximately 3.3 MW.
+The total fire size for this structure is estimated to be at peak,12.3 MW.
 Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
@@
 The second is that the sources of the gas phase wood fuel are of fixed area and at fixed locations (2 sources for attic, 1 source for porch).
-The following lines define the source fires for an FDS input file:
+The following lines define the source fires for this FDS input file:
 
@@
 In this study, we define gypsum~\cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
-The text provided below are the lines necessary to define these materials in an FDS input file.
+The text provided below are the lines necessary to define these materials in this FDS input file.
 
@@
 After the second floor door fails, (cf.
-Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flows in the direction of lower pressure (towards the front door).
-Note that the conditions in the attic do not seem to be influenced.
+Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flow in the direction of lower pressure (towards the front door).
+Note that the conditions in the attic do not appear to be influenced.
 \begin{figure}[!ht]

### 2014-06-21 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Rename files
Equipment Guide: Minor edit to path
Equipment: Add gas analyzer pictures

--- 2014-06-19 Equipment/Equipment_Guide/Equipment_Guide.tex
@@
 
-\input{../../Bibliography/commoncommands}
+\input{../Bibliography/commoncommands}
 
@@
 
+% Center all figures
+\makeatletter
+\g@addto@macro\@floatboxreset\centering
+\makeatother
+
 \begin{document}
@@
 Fire Fighting Technology \\
-Equipment Guide
+Equipment and Testing Guide
 }
@@
 \flushright{
-\includegraphics[width=2.in]{../../Bibliography/nistident_flright_vec} \\[.3in]
+\includegraphics[width=2.in]{../Bibliography/nistident_flright_vec} \\[.3in]
 }
@@
 
-The internal pump is located in the center of the chassis.
+An overview of the internal components of the gas analyzer is shown in Fig.~\ref{fig:gas_analyzer_5}.
+The internal pump is located in the center of the chassis, as shown in Fig.~\ref{fig:gas_analyzer_3}.
 The O$_2$ sensor is located under the foam cover.
 The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.
+
+\begin{figure}[h!]
+\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_5}
+\caption{Internal components of the gas analyzer.}
+\label{fig:gas_analyzer_5}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_3}
+\caption{Internal pump within the gas analyzer.}
+\label{fig:gas_analyzer_3}
+\end{figure}
 

### 2014-06-22 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Rename some Figures dirs

@@
 \begin{figure}[h!]
-\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_5}
+\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Figures/gas_analyzer_5}
 \caption{Internal components of the gas analyzer.}
@@
 \begin{figure}[h!]
-\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Pictures/gas_analyzer_3}
+\includegraphics[width=5in]{../Equipment/Gas_Analyzer/Figures/gas_analyzer_3}
 \caption{Internal pump within the gas analyzer.}

### 2014-06-22 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Edits to gas analyzer notes

@@
 
-The CAI 602P Gas Analyzer can detect gas concentrations for CO$_2$, CO, and O$_2$ and output a voltage from 0~V to 5~V, which corresponds to 0~\% gas concentration to full-scale concentration.
+The CAI 602P Gas Analyzer can detect gas concentrations for CO$_2$, CO, and O$_2$ and output a voltage from 0~V to 5~V, which corresponds to 0~\% gas concentration to a programmable full-scale concentration.
 
@@
 
-Important Note: The optimal pressure from the upstream sample and calibration gas is 0~psi!
+Important note: The optimal pressure from the upstream sample and calibration gas is 0~psi!
 The internal gas analyzer components should never have an upstream pressure in excess of 2~psi.
-Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragms.
+Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragm.
 
 \begin{itemize}
-\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage
-\item Perform zero and span calibration on all analyzers.
+\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage. Keep them powered on as long as possible during testing.
+\item Perform zero and span calibration on all analyzers. The F5 and F6 keys can be used as a shortcut to go from the home measurement screen to the zero and span screens.
     \begin{itemize}
@@
 \item Set the upper ranges to the appropriate setting, which corresponds to 5~V on the output to the DAQ.
-\item Measure the delay time for the sample gas to travel in the plumbing to the analyzer.
+\item Measure the delay time for the sample gas to travel through all of the plumbing (from the sample port to the analyzer).
 You can do this by holding a CO$_2$ source near the sample port and measuring the time from exposing the sample port until the gas analyzer reads an increased value.
-Record this time so that the gas concentration can be offset later.
+Record this time so that the gas concentration data can be offset at a later time.
 \item You are ready to record data to the DAQ.
@@
 If it is zero, then there might be a issue with the internal plumbing if the upstream pressure (from sample or calibration gases) exceeded 2~psi.
-Check power to the internal pump and ensure that it is operating.
+An internal gas line might have been disonnected or the pump might have been damaged.
+Check power to the internal pump and ensure that it is operating, and check the internal plumbing connections.
 

### 2014-06-26 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Add some notes to testing procedure
Equipment Guide: Edits to testing procedure

@@
     \begin{itemize}
+    \item Generators (check oil and gas levels)
     \item Uninterruptible Power Supplies (UPSs)
-    \item WiFi routers
-    \item Hose flow / Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
+    \item WiFi routers/repeaters
+    \item Arduino laptop with NTP, RabbitMQ, Python receive\_data.py script
     \item DAQs and laptops
+    \item Weather stations
     \item Gas analyzers (leave running as long as possible during testing)
     \item Digital video recorder (DVR)
-    \item Bullet cameras
-    \item Thermal imaging cameras (TICs) (check battery level)
-    \item Digital video cassette recorders (DVCRs) (check battery level)
-    \item GoPros (check battery level)
-    \item Video cameras (check battery level)
+    \item Bullet cameras and power supplies
+    \item Thermal imaging cameras (TICs)
+    \item Digital video cassette recorders (DVCRs)
+    \item GoPros
+    \item Video cameras
     \end{itemize}
@@
 
+\item Check and record lag time on gas analyzer probes
+
 \item 1 minute calibration run to separate output file (cover BDPs, check TCs, etc.)
@@
 \begin{itemize}
+\item Take GigaPan pictures as needed
+\item Distribute still cameras
+
 \item Verify testing procedure with all personnel
@@
 \item Power on gas analyzer pump
+\item Add dry ice to gas sample traps (or turn on gas dryer)
 
-\item Turn on water for heat flux gauges
+\item Turn on water for heat flux gauges, cool cans, etc.
 
-\item Check Arduino battery level
 \item Power on Arduino data loggers
@@
     \begin{itemize}
-    \item GoPros
+    \item GoPros (Sync GoPro time to DVR screen time)
     \item Video cameras
-    \item DVCRs (Mobile TIC)
-    \end{itemize}
-
-\item Start synced recording on: [MARK DATE/TIME]
-    \begin{itemize}
+    \item Mobile TIC
+    \item DAQ
     \item DVR
-    \item DAQ data
     \end{itemize}
@@
 
-\item Begin test [MARK DATE/TIME]
+\item Begin test
 
@@
 
-\item End test [MARK DATE/TIME]
+\item End test
 
-\item Stop synced recording on: [MARK DATE/TIME]
+\item Stop recording on:
     \begin{itemize}
@@
     \item DVR
-    \end{itemize}
-
-\item Stop recording on:
-    \begin{itemize}
     \item GoPros
     \item Video cameras
-    \item DVCRs (Mobile TIC)
+    \item Mobile TIC
     \end{itemize}
@@
 
+\item Take GigaPan pictures as needed
+
 \item Prepare for next test
@@
 \begin{itemize}
-\item Retrieve data from:
+\item Collect and organize data from:
     \begin{itemize}
@@
     \item GoPros
+    \item GigaPan
+    \item Weather station data logger
+    \item Mobile TIC
+    \item Arduinos
     \item Video cameras with digital media
-    \item Arduinos
+    \item Still cameras with digital media
     \end{itemize}
 
-\item Swap and label tapes from video cameras and DVCRs as needed
+\item Archive, swap and label tapes from video cameras and DVCRs if needed
 
-\item Make 3 copies of all data on external hard drives
+\item Make copies of all data on external hard drives
 
@@
 
-\item On return from trip, extract video from DVCRs
+\item Format GoPros, video and still camera media, mobile TIC, Arduinos, and GigaPan camera
+
+\item On return from trip, extract video from DVCR tapes
 \end{itemize}
@@
     \begin{itemize}
-    \item Laptops
-    \item Arduinos
-    \item Bullet camera batteries
+    \item Laptops and tablets
+    \item 12 V batteries
     \item TICs
@@
     \item Video cameras
+    \item Still cameras
+    \item GigaPan camera
     \item DVCRs
     \item Radios
+    \item Arduinos
     \end{itemize}

### 2014-07-01 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment Guide: Minor edit to testing procedure
Equipment Guide: Minor edit to test procedure

@@
     \item Bullet cameras and power supplies
-    \item Thermal imaging cameras (TICs)
-    \item Digital video cassette recorders (DVCRs)
-    \item GoPros
-    \item Video cameras
+    \item Thermal imaging cameras (TICs) (check battery levels)
+    \item Digital video cassette recorders (DVCRs) (check battery levels)
+    \item GoPros (check battery levels)
+    \item Video cameras (check battery levels)
     \end{itemize}
@@
 \begin{itemize}
-\item Synchronize time on DAQ computers and digital video recorder
+\item Synchronize clock time on DAQ computers, digital video recorder, etc.
 
@@
 
-\item Check and record lag time on gas analyzer probes
+\item Record serial number and probe location of gas analyzers; check and record lag time
 

### 2014-07-04 Projects/DelCo_2014_04/Report/DelCo_2014.tex
Undo test commit from r337
DelCo: Move plots dir

--- 2014-04-30 Projects/DelCo_2014_04/Report/DelCo_2014.tex
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
 \caption{Hose pressure, Test HOSE\_DNXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DNXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DSXAXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
 \caption{Hose pressure, Test HOSE\_DSXOXF}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A6}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
 \caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
 \caption{Hose pressure, Test HOSE\_IXAOXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A6}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
 \caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_HOSE}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
 \caption{Hose pressure, Test HOSE\_IXXAXX}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_GAS}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_HF}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_GAS}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_HF}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
 \caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
 \caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
 \caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
 \caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
 \caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
 \caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_GAS}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
 \caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_HF}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
 \caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
 \caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
 \caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
 \caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
 \caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
+\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
 \caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}

### 2014-07-04 Projects/DelCo_2014_04/Scripts/plot.py

@@ -228,7 +228,7 @@ for f in os.listdir(data_dir):
 
             # Save plot to file
             print 'Plotting ', group
-            savefig('../Figures_Plots/' + test_name + '_' + group[0].rstrip('_') + '.pdf')
+            savefig('../Figures/Script_Figures/' + test_name + '_' + group[0].rstrip('_') + '.pdf')
             close('all')
 
         close('all')

### 2014-07-04 Projects/DelCo_2014_04/Scripts/plot_streaming.py

@@ -1,47 +1,0 @@
-#!usr/bin/env python
-
-"""
-Reads a constantly updating .csv file and streams data to a plot
-in a bokeh server. You should start bokeh-server on the local machine.
-The plots can be accessed at http://localhost:5006/bokeh/
-"""
-
-import numpy as np
-import bokeh.plotting as bk
-from bokeh.objects import Glyph
-import time
-
-#  =================
-#  = User Settings =
-#  =================
-
-data_file = '../Experimental_Data/test_data.csv'
-
-#  ============
-#  = Plotting =
-#  ============
-
-data = np.genfromtxt(data_file, delimiter=',', names=True)
-x = data['Time']
-y = data['TC_A1_0p03_BC']
-
-bk.output_server('Plots')
-
-bk.line(x, y, color='#0000FF',
-        tools='pan,wheel_zoom,box_zoom,reset,resize,crosshair,select,previewsave,embed',
-        width=1200,height=300)
-bk.xaxis()[0].axis_label = 'Time'
-bk.yaxis()[0].axis_label = 'Temperature (C)'
-
-renderer = [r for r in bk.curplot().renderers if isinstance(r, Glyph)][0]
-ds = renderer.data_source
-
-while True:
-    data = np.genfromtxt(data_file, delimiter=',', names=True)
-    ds.data['x'] = data['Time']
-    ds.data['y'] = data['TC_A1_0p03_BC']
-
-    ds._dirty = True
-    bk.session().store_obj(ds)
-
-    time.sleep(1)

### 2014-07-17 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago_Fire: partial update of report based on review comments

@@
 \headerB{
-Simulation of the Dynamics of an \\
-Attic Fire in a 2 1/2 Story Wood \\
-Frame Residential Structure \\
+Simulation of an Attic Fire \\
+in a Wood Frame Residential Structure \\
 Chicago, IL \\
@@
 On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-Changes in the ventilation flow path resulted in fire and smoke penetration to an interior second floor hallway.
-NIST examined the fire dynamics of this incident at the request of NIOSH and Chicago Fire Department (CFD) .
+NIST examined the fire dynamics of this incident at the request of NIOSH and Chicago Fire Department (CFD).
 Computer simulations of the fire using Fire Dynamics Simulator and Smokeview, provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
@@
 
-\chapter{Fire Dynamics Simulator and Smokeview}
+\chapter{Model Description}
+\label{model}
 FDS is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
@@
 
-\chapter{Model Input Parameters}
 Input data from a number of sources must be collected and documented in order to simulate a fire with FDS or any other model.
-From the fire scene the following information must be gathered:
-\begin{itemize}
-\item The geometry of the building and the compartments being modeled.
-\item The size and location of exterior and interior ventilation openings. 
-\item Documentation and identification of the fuels used in the construction and finish of the building and their installed location
-\item Documentation and identification of the fuels used as the contents of the building. 
-\item Area of origin and approximate size of ignition source.
-\item Documentation of fire damage to the building, fuel loads, victims or equipment.
-\end{itemize}
-From witnesses, first responders, reports, and recorded media such as fire ground radios or videos:
-\begin{itemize}
-\item Information on the timing of the fire development
-\item Order and timing of ventilation opening to the outside
-\item Weather conditions at the time of the fire
-\end{itemize}
-To develop the simulation, a timeline of events based on the collected information is developed.
-From this time line actions may be input into the model, such as venting a window at a given time.
-To develop the model geometry and remainder of the input file is straight forward with guidance from the FDS User's Guide ~\cite{FDS_Users_Guide} or third party software.
-Engineering judgment, graduate level knowledge of fire dynamics, and modeling experience are required to  translate the information collected from the scene into appropriate and realistic computational information.
-Examples of these requirements include:
-\begin{itemize}
-\item the computational cell size
-\item model domain and boundaries conditions
-\item the heat release rate (HRR) of the ignition source/initial fire
-\item physical and thermal properties of fuels such as interior finish and furnishings
-\end{itemize}
-Since there is no all-inclusive, universal fire modeling input data base this type of information must be gathered from literature or generated for a given incident.
-For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters.
-The sections below describe these inputs.
-
-\begin{table}
-\centering
-\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
-\begin{tabular}{lll}
-\toprule[1.5pt]
-Parameter & Description & Reference  \\
-\midrule
- Simulation Time           & 5 minutes                             & -- \\[.25cm]
- Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
-                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
-                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
-\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
-                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
-                                   & $\rho$: 510 \; kg/m$^3$         & \\
-                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  & k: 0.48 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   & $\rho$: 1440 \; kg/m$^3$        & \\ 
-                                   & c$_{p}$: 0.84 \; \si{kJ/(kg.K)} & \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\end{table}
+For the model presented here, information was obtained from two main sources.
+From the fire scene the following information was gathered: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
+From witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, order and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
+The following subsections will describe the inputs used to construct the simulation, including any engineering approximations or assumptions that were made.
 
@@
 The structure was a 2 1/2 story residential building with balloon frame construction and gable roof.
+Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+Intermediate floors are built directly off of the studs.
+One potential issue with balloon frame construction, is that without fire stops, there is void space for fire to potentially travel between the floors.
 The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
@@
 This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
-Interior walls were constructed from wood frame dimensioned lumber with 12.7 mm (0.5 in) gypsum board over top.
+Interior walls were constructed from nominal lumber with 12.7 mm (0.5 in) gypsum board over top.
 Additionally there was a half-story attic that was used to house the structure's hot water heater.
 There were three sets of stairs in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
-Entry to the first floor of thep structure can be made either in the front (Alpha side) or rear (Charlie side), see Fig.~(\ref{fig:simp_geom}).
+Entry to the first floor of the structure can be made either in the front or rear, see Fig.~(\ref{fig:simp_geom}).
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
@@
 \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-\includegraphics[width=6in]{../Figures/1st_Floor_Metric} \\
-\includegraphics[width=6in]{../Figures/2nd_Floor_Metric}
+\includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
+\includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
 \end{tabular*}
-\caption{Top view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified.}
+\caption{Plan view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified.}
 \label{fig:simp_geom}
@@
 &MATL ID        = 'GYPSUM'
-    FYI = 'Quintiere, Fire Behavior' 
-    CONDUCTIVITY    = 0.48
-    SPECIFIC_HEAT   = 0.84
-    DENSITY = 1440./
+    FYI = 'Drysdale' 
+    CONDUCTIVITY    = 0.17
+    SPECIFIC_HEAT   = 1.09
+    DENSITY = 930./
 
@@
 
-\section{Vents}
+\section{Ventilation}
 \label{Vents}
@@
 \end{figure}
+
+For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters discussed in Section~\ref{model}.
+
+\begin{table}
+\centering
+\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
+\begin{tabular}{lll}
+\toprule[1.5pt]
+Parameter & Description & Reference  \\
+\midrule
+ Simulation Time           & 5 minutes                             & -- \\[.25cm]
+ Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
+ Ambient Temperature       & 25 $^{\circ}$C                        & -- \\ [.1cm]
+\multirow{4}{*}{Reaction: Wood}  & Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$              & \multirow{4}{*}{Section~\ref{fire}} \\
+                           & CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$  & \\
+                           & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
+                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
+\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
+                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
+\multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
+                                   & $\rho$: 510 \; kg/m$^3$         & \\
+                                   & c$_{p}$: 1.38 \; \si{kJ/(kg.K)} & \\[.25cm]
+\multirow{3}{*}{Material: Gypsum}  & k: 0.17 \; \si{W/(m.K)}         &  \multirow{3}{*}{Section~\ref{matl}}\\ 
+                                   & $\rho$: 930 \; kg/m$^3$        & \\ 
+                                   & c$_{p}$: 1.09 \; \si{kJ/(kg.K)} & \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 

### 2014-07-21 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: continued update to report write-up

@@
          & \\[.25cm] 
-17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
+17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4 in hose line. \\[.25cm]
 17:21:30 & 1$^{st}$ floor exterior porch door opened. \\[.25cm]
@@
 The structure was a 2 1/2 story residential building with balloon frame construction and gable roof.
-Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
 Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction, is that without fire stops, there is void space for fire to potentially travel between the floors.
-The structure had a 17.15 m (56 ft) by 6.15 m (20 ft) footprint (cf.
+One potential issue with balloon frame construction, is that without fire stops, there is void space for fire to potentially travel between the floors.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint (cf.
 Fig.~(\ref{fig:simp_geom})).
-This results in a floor area of approximately 105 m$^2$ (1100 ft$^2$) per floor and a main living area of approximately 110 m$^2$ (2200 ft$^2$).
-Interior walls were constructed from nominal lumber with 12.7 mm (0.5 in) gypsum board over top.
+This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
+Interior walls were constructed from nominal lumber with 12.7~mm (0.5~in) gypsum board over top~\cite{NIOSH:Bowyer}.
 Additionally there was a half-story attic that was used to house the structure's hot water heater.
@@
 Discussion of the fire's impact on interior conditions can be found in Section~\ref{results}.
-Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the alpha side of the structure.
-Note that the majority of the damage is to the structure's attic.
+Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the front and rear of the structure.
+Note that the majority of the damage is to the structure's attic and second floor rear porch.
+Fully dimensioned drawings of the first and second floor interiors can be found in Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}), respectively.
 
@@
 \centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_alpha}
-\caption{Photograph showing the post-incident front (side alpha) exterior of the structure.}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
+   \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
+\end{tabular*}
+\caption{Photograph showing the post-incident front (left) and rear (right) exterior of the structure.}
 \label{fig:alpha_ex}
 \end{figure}
-
-Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}) show the interior dimensions of the first and second floor, respectively.
-The dimensions were found from on-scene measurements using a tape measure.
-Measurements were made to the nearest 12.7 mm (0.5 in).
-Based on difficulty of making some of the measurements due to the condition of the post-fire structure, the uncertainty in the measurements is estimated to be on the order of $\pm$ 1 \%.
-This would result in measurements that could change by up $\pm$ 17 cm ($\approx$ 7 in).
-When considering the uncertainties in the initial fire development, ventilation (vent times and vent areas), and peak heat release rate among other factors, the uncertainty in the overall structure geometry is not a major factor.
-
 %Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
@@
 To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
-Post-incident, the fire investigation concluded that the fire originated in the structure's attic~\cite{NIOSH:Bowyer}.
-Post-fire pictures revealed extensive damage to the attic and second floor rear porch (cf.
-Fig.~(\ref{fig:charlie_ex})).
 Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch consist of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
+The attic and rear porch consisted of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
 
-\begin{figure}[h!]
-\centering
-\includegraphics[width=.65\textwidth]{../Figures/exterior_charlie}
-\caption{Photograph showing the post-incident rear (side charlie) exterior of the structure.}
-\label{fig:charlie_ex}
-\end{figure}
-
-If we represent wood with the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, and use carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) yields from the SFPE Handbook~\cite{SFPE:Tewarson}, we can write a balanced chemical reaction for wood oxidation:
+Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) found from the SFPE Handbook~\cite{SFPE:Tewarson}.
+A balanced chemical reaction for wood oxidation can written:
 
@@
 
-The heat of combustion of wood used in this simulation is 16400 kJ/kg (7050 BTU/lb), based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The heat of combustion of wood used in this simulation is 16400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the energy release per unit mass of the fuel.
@@
 To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
-Experiments were conducted in a cone calorimeter to determine the 5 minute average of HRRPUA (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Here, we take a conservative approach and assume the burning wood in the structure had the lowest energy density of the tested samples~\cite{babrauskas1990}, similar to that of Douglas Fir plywood.
-Based on the range of heat flux exposures, the data was fit to determine HRRPUA ($y$) as a function of exposure ($x$):
+Experiments were conducted in a cone calorimeter \footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials.} to determine the 5 minute average of HRRPUA  \footnote{HRRPUA is the heat release rate per unit area.} (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
+Babrauskas and Grayson~\cite{babrauskas1990} suggest that the heat release rate per unit area for a variety of woods is approximately 50~kW/m$^2$.
 
-\begin{equation}
-y = ax+b
-\label{eq:heat_flux}
-\end{equation}
-
-In Eq.~\ref{eq:heat_flux}, $a$ and $b$ are experimental constants.
-For Douglas Fir plywood these values were found to be 1.43 and 22 respectively.
-Typically radiative feedback from flaming combustion is between 20 kW/m$^2$ and 35 kW/m$^2$~\cite{tsaidrysdale}.
-If we estimate that the average radiation feedback to the pyrolyzing fuel is 20 kW/m$^2$ because of under-ventilated conditions within the structure, then following Eq.~\ref{eq:heat_flux} the average heat release per unit area (HRRPUA) for wood is 51 kW/m$^2$.
-
-To calculate the total fire size, we need to determine the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure.
-Based on the floor plan of the structure, the underside of the roof is approximately 134 m$^2$ (1453 ft$^2$) with 7 m$^2$ (75 ft$^2$) walls on the Alpha and Charlie sides.
-Additionally there is 105 m$^2$ (1130 ft$^2$) of floor area in the attic.
+To calculate the total fire size, the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
+Based on the floor plan of the structure, the underside of the roof is approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
+Additionally there is 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
 Examination of post incident images showed that the floor immediately over the back porch burned away.
 That area will be considered as part of the porch fire.
-Based on post-incident damage, we consider approximately 50 \% of the remaining floor area as fuel to the attic fire and 90 \% of the roof.
-To estimate the total attic fire size, we include the underside roof area (120 m$^2$), two end walls (14 m$^2$) and the floor area (43 m$^2$ (463 ft$^2$)).
-Using an HRRPUA of wood of 51 kW/m$^2$, results in a potential peak fire size of 9 MW.
-To estimate the porch fire size, we consider the the four walls of porch enclosure (42 m$^2$) and the floor and ceiling of the porch (24 m$^2$ (258 ft$^2$)).
-The total area is 64 m$^2$ (689 ft$^2$).
-Using the same HRRPUA of 51 kW/m$^2$, the potential peak fire size on the porch is approximately 3.3 MW.
-The total fire size for this structure is estimated to be at peak,12.3 MW.
+Based on post-incident damage, approximately 50 \% of the remaining floor area as fuel to the attic fire and 90 \% of the roof is con sidered.
+To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$) and the floor area (43~m$^2$ (463~ft$^2$)) are included.
+Using an HRRPUA of wood of 50~kW/m$^2$, results in a potential peak fire size of 9~MW.
+To estimate the porch fire size, the the four walls of porch enclosure (42~m$^2$) and the floor and ceiling of the porch (24~m$^2$ (258 ft$^2$)) are included.
+The total area is 64~m$^2$ (689~ft$^2$).
+Using the same HRRPUA of 50~kW/m$^2$, the potential peak fire size on the porch is approximately 3.3~MW.
+The total fire size for this structure is estimated to be at peak, 12.3~MW.
 Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
-First is that the attic fire starts at the beginning of the simulation and ramps up to 9 MW in 10 seconds.
-The porch fire starts 40 seconds into the simulation and ramps to 3.3 MW in 10 seconds.
+First is that the attic fire starts at the beginning of the simulation and ramps up to 9~MW in 10 seconds.
+The porch fire starts 40 seconds into the simulation and ramps to 3.3~MW in 10 seconds.
 A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
@@
 While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
-In this study, we define gypsum~\cite{Quintiere:2} for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
+In this study, gypsum~\cite{Drysdale:1} is used for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
 The text provided below are the lines necessary to define these materials in this FDS input file.
@@
 \label{Vents}
-This simulation includes vents that account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+The simulations in this study account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
 There are two ventilation scenarios that are considered in this study.
 The first is the baseline simulation where the ventilation times and ventilation areas represent our best understanding of the incident.
-The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent beta side wall breach.
+The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
 The times of the ventilation changes are provided in Table \ref{tab:vents}.
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of structure of this type.
+The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
 Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
@@
 \midrule
-0    &  0   & 0.11 & Window      & Charlie \\
-40    &  40   & 0.08 & Breach (x2) & Alpha and Charlie \\
-45    &  45   & 0.12 & Breach      & Beta \\
-55    &  55   & 0.12 & Breach      & Charlie \\     
-130   &  N/A  & 1.41 & Door        & Charlie \\
-135   &  N/A  & 0.2  & Breach      & Beta \\        
+0    &  0   & 0.11 & Window      & Rear \\
+40    &  40   & 0.08 & Breach (x2) & Front and Rear \\
+45    &  45   & 0.12 & Breach      & Left \\
+55    &  55   & 0.12 & Breach      & Rear \\     
+130   &  N/A  & 1.41 & Door        & Rear \\
+135   &  N/A  & 0.2  & Breach      & Left \\        
 160   &  160  & 0.80 & Door        & Interior \\
@@
 Fig.~(\ref{fig:geom_grid}) shows the
-alpha side (front) of the structure rendered in Smokeview with the 10 cm mesh.
+front of the structure rendered in Smokeview with the 10 cm mesh.
 
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
-\caption{Alpha side of the structure with 10 cm computation mesh.}
+\caption{Front side of the structure with 10 cm computation mesh.}
 \label{fig:geom_grid}
@@
 
-As discussed Section~\ref{geom}, the structure has 17.15 m (56 ft) by 6.15 m (20ft) footprint with a total height of 8.56 m (28 ft).
+As discussed Section~\ref{geom}, the structure has 17.15~m (56~ft) by 6.15~m (20~ft) footprint with a total height of 8.56~m (28~ft).
 To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
-The total volume of the computational domain is 24 m (79 ft) by 10 m (33 ft) by 10 m (33 ft).
-At 10 cm (3.9 in) resolution this would result in 2.4 million computational cells.
+The total volume of the computational domain is 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
+At 10~cm (3.9~in) resolution this would result in 2.4 million computational cells.
 To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption{Alpha-Delta side of the structure within computational domain. Each of the 16 meshes is 3 m (9.8 ft) by 10 m (33 ft) by 5 m (16.4 ft).}
+\caption{Front-right side of the structure within computational domain. Each of the 16 meshes is 3 m (9.8 ft) by 10 m (33 ft) by 5 m (16.4 ft).}
 \label{fig:mult_mesh}
@@
 
-For the simulations performed for this study, Table ~\ref{tab:mod_param} includes the relevant model input parameters discussed in Section~\ref{model}.
+For the simulations performed for this study, Table~\ref{tab:mod_param} includes the relevant model input parameters discussed in Section~\ref{model}.
 
@@
                            & Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$ & \\
-                           & Heat of Combustion: 16400 kJ/kg                             & \\ [.25cm]
-\multirow{2}{*}{Peak HRR}  & Attic Fire: 9 MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
-                           & Porch Fire: 3.3 MW                                          & \\ [.25cm]                     
+                           & Heat of Combustion: 16400~kJ/kg                             & \\ [.25cm]
+\multirow{2}{*}{Peak HRR}  & Attic Fire: 9~MW                                            & \multirow{2}{*}{Section~\ref{fire}}\\ 
+                           & Porch Fire: 3.3~MW                                          & \\ [.25cm]                     
 \multirow{3}{*}{Material: Wood}    & k: 0.12 \; \si{W/(m.K)})        & \multirow{3}{*}{Section~\ref{matl}} \\
@@
 The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Here, we examine impact of ventilation on fire size.
 Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
 The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).
+Due to a lack of information about when the fire ignited or how fast it grew, these parameters needed to be estimated.
+While the growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20 seconds) is atypically fast, analysis of the incipient stage of the fire growth was not considered in this study.
+The goal was to have a fire approach its estimated peak and become ventilation limited quickly to minimize computation time while aligning with the constraints of videos taken during the fire.
+Accuracy of heat transfer to the walls of the structure may be sacrificed by taking this approach, however all window, door, and wall failure were driven by the event timeline not modeling predicted failure temperatures.
 
@@
 We can see that within the first 10 seconds, the structure is under-ventilated as the modeled HRR is below the prescribed HRR.
-The HRR peaks at just under 9 MW (approximately 20 seconds into the simulation) before becoming oxygen limited.
-The HRR drops to 5 MW as the available oxygen inside the structure gets consumed.
+The HRR peaks at just under 9 MW before becoming oxygen limited.
+The HRR drops to 5~MW as the available oxygen inside the structure gets consumed.
 There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents.
 Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40 seconds.
-After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9 MW before again dropping to about 6 MW.
+After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9~MW before again dropping to about 6~MW.
 The HRR then begins to increase towards a sustainable steady state value.
 
-From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7 MW).
+From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7~MW).
 At 130 seconds the rear door is opened in the baseline simulation.
@@
 Again, the abrupt change in ventilation causes the HRR to spike.
-Here we see a rise from 7 MW to 9.7 MW at 139 seconds.
+Here we see a rise from 7~MW to 9.7~MW at 139 seconds.
 At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation.
@@
 Fig.~(\ref{fig:pres_159s}) shows the pressure rise in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4 Pa over pressure 1 m off the floor to greater than 10 Pa at the ceiling.
+On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa at the ceiling.
 \begin{figure}[!ht]
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1 Pa is 1.4 $\times 10 ^{-4}$ psi.}
+\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1~Pa is 1.4 $\times 10 ^{-4}$ psi.}
 \label{fig:pres_159s}
@@
 
-Fig.~(\ref{fig:temp_129s}) shows temperatures of at least 260 $^{\circ}$C (500 $^{\circ}$F) in the second floor rear porch and rear portion of the attic.
-High temperatures, between 80 $^{\circ}$C (185 $^{\circ}$F) and 200 $^{\circ}$C (390 $^{\circ}$F), also extend down to the 1$^{st}$ floor rear entrance.
+Fig.~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the 1$^{st}$ floor rear entrance.
 Before the interior door fails, Fig.~(\ref{fig:temp_159s}), the inflow ambient air from the open door lowers the temperature local to the doorway, but we know from Fig.~(\ref{fig:hrr}) that over this interval the HRR spikes because of the additional ventilation.
@@
 
-From Fig.~(\ref{fig:temp_175s}), 15 seconds after the door failed, high temperature gases have descended to approximately 1 m (3.28 ft) off the ground through the interior hallway and have spilled into the kitchen (recall layout from Fig.~(\ref{fig:simp_geom})).
+From Fig.~(\ref{fig:temp_175s}), 15 seconds after the door failed, high temperature gases have descended to approximately 1~m (3.28~ft) off the ground through the interior hallway and have spilled into the kitchen (recall layout from Fig.~(\ref{fig:simp_geom})).
 
@@
 \section{Hallway Flow Path}
-From on-scene reports from the BC (Chapter~\ref{fire_sum}) and simulation results (Chapter~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
+From on-scene reports from the BC (Section~\ref{fire_sum}) and simulation results (Section~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
 From the NIOSH report, while the BC was inside the structure on the second floor, the  BC observed only a light haze and a glow around the door between the hallway and enclosed porch.
@@
 By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature and pressure, greater than 260 $^{\circ}$C (500 $^{\circ}$F) and 5 Pa respectively, were on the Charlie side of the steel door at the rear of the structure.
+Temperature and pressure, greater than 260~$^{\circ}$C (500~$^{\circ}$F) and 5~Pa respectively, were on the rear side of the steel door at the rear of the structure.
 Exposure to these conditions weakened the structural integrity of the door, eventually leading to a partial failure.
@@
 
-While we have estimated the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch (Charlie side) to the kitchen (Alpha side) of the structure was created.
+While we have estimated the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
@@
 
-A person is susceptible to second degree burn injuries when exposed to temperatures 55 $^{\circ}$C (130 $^{\circ}$F) \cite{designation2003c}.
+A person is susceptible to second degree burn injuries when exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F) \cite{designation2003c}.
 While firefighters wear protective gear, gear only offers finite levels of protection.
-The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140 $^{\circ}$C (284 $^{\circ}$F) \cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures of 260 $^{\circ}$C (500 $^{\circ}$F) \cite{nfpa2013standard}.
+The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F) \cite{mensch2011emergency}.
+Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) \cite{nfpa2013standard}.
 Extended exposure to elevated temperatures can result in significant heat transferred to the firefighter, putting him/her at risk.
-Therefore, for analysis of the modeled exposure temperatures, we set the maximum visualized temperature to be all values that are 260 $^{\circ}$C (500 $^{\circ}$F) or above.
-This means that temperatures visualized in the highest range in the model output are at a minimum of 260 $^{\circ}$C (500 $^{\circ}$F); predicted temperatures could in fact be higher.
+Therefore, for analysis of the modeled exposure temperatures, we set the maximum visualized temperature to be all values that are 260~$^{\circ}$C (500~$^{\circ}$F) or above.
+This means that temperatures visualized in the highest range in the model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); predicted temperatures could in fact be higher.
 
 Prior to door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
-Temperatures are highest at the Beta-Charlie corner where there is sufficient oxygen due to the section of porch wall that had burned away allowing additional oxygen to mix with the fuel rich fire gases.
-Five seconds after the door fails, hot gases have traveled the length of the interior hallway and approached the doorway into the kitchen, approximately 4.5 m (14.8 ft) away from the source fire (cf Fig.~(\ref{fig:temp_top_165})).
-Within one minute after the door fails, the hallway temperatures are nominally at or above 260 $^{\circ}$C (500 $^{\circ}$F) through out the hallway (cf Fig.~(\ref{fig:temp_top_220})).
+Temperatures are highest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away allowing additional oxygen to mix with the fuel rich fire gases.
+Five seconds after the door fails, hot gases have traveled the length of the interior hallway and approached the doorway into the kitchen, approximately 4.5~m (14.8~ft) away from the source fire (cf.
+Fig.~(\ref{fig:temp_top_165})).
+Within one minute after the door fails, the hallway temperatures are nominally at or above 260~$^{\circ}$C (500~$^{\circ}$F) through out the hallway (cf Fig.~(\ref{fig:temp_top_220})).
 This illustrates that the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Fig.~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90 $^{\circ}$C (194 $^{\circ}$F) and temperatures at the top of the stairs were at or below 70 $^{\circ}$C (158 $^{\circ}$F).
+Fig.~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F) and temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
 At these points in the structure, the exhaust gases in the flow path are air cooled/diluted by the inflow ambient gas.
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 1 second prior to door failure, 1.83 m (6 ft) above the floor.}
+\caption{Temperature contours on the second floor, 1 second prior to door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_159}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 5 seconds after door failure, 1.83 m (6 ft) above the floor.}
+\caption{Temperature contours on the second floor, 5 seconds after door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_165}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 60 seconds after door failure, 1.83 m (6 ft) above the floor.}
+\caption{Temperature contours on the second floor, 60 seconds after door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_220}
@@
 F2004-02  \cite{NIOSH:Berardinelli}  & 1 LODD                                       & 1st floor to basement \\
-F2005-02 \cite{NIOSH:Koedam}        & 1 LODD/4 LODI                           & C side to A side of the building \\
+F2005-02 \cite{NIOSH:Koedam}        & 1 LODD/4 LODI                           & Rear to front of the building \\
 F2005-04 \cite{NIOSH:McFall4}         & 1 LODD/9 LODI                           & Basement to 1st floor \\
@@
 F2007-35 \cite{NIOSH:Braddee}       & 4 LODI                                         & 1st floor to 2nd floor \\
-F2009-11 \cite{NIOSH:Merinar}         & 2 LODD                                        & C side to A side of the building \\
+F2009-11 \cite{NIOSH:Merinar}         & 2 LODD                                        & Rear to front of the building \\
 F2011-13 \cite{NIOSH:Bowyer2}       & 2 LODD                                        & Lower level up stairs and through entry door and garage \\
@@
 The modeled fuel, fire size, and fire growth rate were estimated taking into account all available information: NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3 MW, however based on the limited ventilation in the attic and enclosed porch the model generated a peak HRR of approximately 10 MW as a result of the limited supply of oxygen.
+This resulted in a specified source fire of 12.3~MW, however based on the limited ventilation in the attic and enclosed porch the model generated a peak HRR of approximately 10 MW as a result of the limited supply of oxygen.
 The fire began in the attic and spread down into the enclosed porch on the rear (Charlie side) of the structure.
@@
 The door failure resulted in the creation of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway at face height exceeded 260 $^{\circ}$C (500 $^{\circ}$F).
+The temperature of the gases that flowed into the hallway at face height exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
 
@@
 \centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption {Dimensioned drawing of 1$^{st}$ floor.}
+\includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
+\caption {Dimensioned drawing of 1$^{st}$ floor. The measurements are accurate to within 15 cm (6 in).}
 \label{fig:first_floor}
@@
 \centering
-\includegraphics[width=.80\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption {Dimensioned drawing of 2$^{nd}$ floor.}
+\includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
+\caption {Dimensioned drawing of 2$^{nd}$ floor. The measurements are accurate to within 15 cm (6 in).}
 \label{fig:second_floor}

### 2014-07-23 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update report

@@
 HRRPUA \> Heat Release Rate per Unit Area \\
+IC \> Incident Command \\
 LODD \> Line of Duty Death \\
@@
 \label{fire_sum}
-The following account of events is based on information provided by NIST physical measurements on-scene, NIST photographs of the scene, time line information provided by the Chicago Fire Department and information provided from the NIOSH Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
+The following account of events is based on information provided from the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
+Details regarding times are taken from the report and should be considered approximate values.
 
 On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.
-At approximately 5:16 in the afternoon, a dispatch was made for ``smoke in the area''.
-Within a minute of dispatch, a Battalion Chief (BC) arrived and sized up the structure fire from the exterior and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.
-After speaking with the building occupants, the BC entered the structure and found light smoke on the second floor and a glow around the doorway that led from the second floor hallway to enclosed rear porch.
-Engine 123 (E123) arrived on scene at approximately 17:19.
-The victims were part of the E123 crew.
-The BC met the Captain and the Firefighter (victims) at the front door to the structure.
-Then the Captain and Firefighter took their hose line to the second floor of the structure.
-At approximately 5:21, the Captain and Fire Fighter were on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
+At approximately 17:16 hours, a dispatch was made for ``smoke in the area''.
+The dispatch was made because a person on the street saw smoke and notified the residents, who all promptly left the structure.
+A battalion chief (BC19) from the nearest station arrived on-scene about one minute after dispatch; the station was only several blocks away.
+BC19 performed an exterior size-up and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.
+BC19 assumed incident command (IC) of the fire scene.
+After speaking with the building occupants, the IC confirmed the structure was evacuated.
+The IC entered the structure to investigate the second floor.
+He found only light smoke on the second floor and a glow around the doorway that led to enclosed rear porch.
+
+Engine 123 (E123) arrived on scene at approximately 17:18.
+The IC met the E123 captain and firefighter at the front door to the structure.
+The captain and firefighter took their hose line to the second floor of the structure.
+At approximately 17:21, the captain and firefighter were on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
 Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
 The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
-Both doors remain open and the firefighter from TL39 exits the structure.
+The firefighter did not see any fire in the main part of the structure and proceeded to exit the structure.
 Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior.
@@
 \centering
-\captionof{table}{Fire Event Timeline}\label{tab:fire_info}
+\captionof{table}{Abridged NISOH approximate fire event timeline}\label{tab:fire_info}
 \begin{tabular}{l l}
@@
 \end{tabular*}
-\caption{Plan view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified.}
+\caption{Plan view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified Drawn using measurements collected by NIST staff.}
 \label{fig:simp_geom}
@@
 The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
-The times of the ventilation changes are provided in Table \ref{tab:vents}.
+The times of the ventilation changes are provided in Table~\ref{tab:vents}.
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
@@
 Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
+An unknown in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2:40 into the simulation).
+While this time may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
 
@@
 \label{timeline}
-From the NIOSH report~\cite{NIOSH:Bowyer}, a timeline of events was able to be created, see Table~\ref{tab:fire_info}.
-Due to a lack of information about when the fire ignited, an ignition time/start of the simulation needed to be estimated.
-We estimate that the simulation starts at 17:19:20.
-Since the actually time was unknown, the fire growth rate in the computational model is such that when firefighters enter the structure, the hazard level in the model is similar to the real situation.
-A second unknown that was estimated was the time when the second floor door fails (2:40 into the simulation).
-While this time is not exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
 Table~\ref{tab:firesim} shows the fireground timeline along with the corresponding simulation times.
@@
 \toprule[1.5pt]
-Incident Time [hr:min:s] & Simulation Time [s] & Fire Behavior / Fireground Operation  \\
+Incident Time [hr:min:s] & Model Time [s] & Fire Behavior / Fireground Operation  \\
 \midrule
-\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
          & \\[.25cm]
-         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{10cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
+         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{9cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
          & & \\[0.25cm]
-\multirow{2}{*}{17:20:00} & \multirow{2}{*}{40}  & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.
+\multirow{3}{*}{17:20:00} & \multirow{3}{*}{40}  & \multirow{3}{*}{\parbox{9cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.
 Rear porch ignites in model.}} \\
          & & \\[.25cm]
-         & 45 & Model ventilation on charlie side. \\[.25cm] 
-         & 55 & Model ventilation on beta side. \\[.25cm] 
+         & & \\[.25cm]  
+         & 45 & Ventilation through wall penetration on rear of structure. \\[.25cm] 
+         & 55 & Ventilation through wall penetration on left side of structure. \\[.25cm] 
 17:21:00 & 100 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
-17:21:30 & 130 & 1$^{st}$ floor exterior porch door opened. Attic fire ignites in model. \\[.25cm]
-        & 135 & Additional model ventilation on beta side. \\[.25cm] 
-        & 160 & Top of interior door fails in model. \\[.25cm] 
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{1$^{st}$ floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
+        &  & \\[.25cm]
+        & 135 & Additional ventilation through left side of structure. \\[.25cm] 
+        & 160 & Top of interior door fails in FDS model. \\[.25cm] 
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
          & & \\[.25cm]
@@
 17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
-\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{10cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
+\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{9cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
          & &  \\[.25cm]
@@
 While the growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20 seconds) is atypically fast, analysis of the incipient stage of the fire growth was not considered in this study.
-The goal was to have a fire approach its estimated peak and become ventilation limited quickly to minimize computation time while aligning with the constraints of videos taken during the fire.
+The goal was to have a fire approach its estimated peak and become ventilation limited quickly to minimize computation time while still aligning with the observations of video and picture evidence from the fire.
 Accuracy of heat transfer to the walls of the structure may be sacrificed by taking this approach, however all window, door, and wall failure were driven by the event timeline not modeling predicted failure temperatures.
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1~Pa is 1.4 $\times 10 ^{-4}$ psi.}
+\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1~Pa is 1.4 $\times 10 ^{-4}$~psi.}
 \label{fig:pres_159s}
@@
 By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature and pressure, greater than 260~$^{\circ}$C (500~$^{\circ}$F) and 5~Pa respectively, were on the rear side of the steel door at the rear of the structure.
+Temperature and pressure, greater than 260~$^{\circ}$C (500~$^{\circ}$F) and 5~Pa respectively, were on the porch side of the steel door at the rear of the structure.
 Exposure to these conditions weakened the structural integrity of the door, eventually leading to a partial failure.

### 2014-07-24 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg: Cleanup plot dirs and add report files

--- 2014-04-30 Projects/DelCo_2014_04/Report/DelCo_2014.tex
@@
 \headerB{
-Delco 2014
+Spartanburg 2014
 }
@@
 
+\section{Experimental Structure}
+\label{sec:Experimental_Structure}
+
+\subsection{Construction}
+\label{sec:Construction}
+
+\section{Fuel Load}
+
 \chapter{Results}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
 \label{fig:HOSE_DNXAXX_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_HOSE}
-\caption{Hose pressure, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_HOSE}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A7}
+\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
 \caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
 \label{fig:HOSE_DNXOXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{DSXAXF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{DSXOXF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{IXAOXX}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A6}
-\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_HOSE}
-\caption{Hose pressure, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{IXXAXX}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A6}
-\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_HOSE}
-\caption{Hose pressure, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_HOSE}
-\end{figure}
-
-\clearpage
-
-\section{Fire Tests}
-
-\subsection{FIRE\_FA2S1C1NCX1\_1}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
-\end{figure}
-
-\clearpage
-
-\subsection{FIRE\_FA2S1C1NCX1\_2}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
-\end{figure}
-
-\clearpage
-
-\subsection{FIRE\_FA2S1C1NCX1\_3}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
 \end{figure}

### 2014-07-24 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg: Initial commit of plots for various tests

@@
 
-\section{Hose Flow Tests}
+\section{286 College}
 
-\subsection{DNXAXX}
+\subsection{Test 1, Living room fire with sprinkler}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A7}
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
+\caption{286 College, Test 1, TC\_A3}
+\label{fig:286_College_Test_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
+\caption{286 College, Test 1, TC\_A4}
+\label{fig:286_College_Test_1_TC_A4}
 \end{figure}
@@
 
-\subsection{DNXOXF}
+\subsection{Test 2, Garage fire, exterior attack}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A7}
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
+\caption{286 College, Test 2, TC\_A1}
+\label{fig:286_College_Test_2_TC_A1}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 3, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
+\caption{286 College, Test 3, TC\_A1}
+\label{fig:286_College_Test_3_TC_A1}
+\end{figure}
+
+\clearpage
+
+\section{489 N. Forest}
+
+\subsection{Test 1, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
+\caption{489 N. Forest, Test 1, TC\_A1}
+\label{fig:489_N_Forest_Test_1_TC_A1}
+\end{figure}
+
+\subsection{Test 2, Second floor bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A1}
+\caption{489 N. Forest, Test 2, TC\_A1}
+\label{fig:489_N_Forest_Test_2_TC_A1}
+\end{figure}
+
+\clearpage
+
+\section{302 College}
+
+\subsection{Test 1, Bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
+\caption{302 College, Test 1, TC\_A1}
+\label{fig:302_College_Test_1_TC_A1}
+\end{figure}
+
+\subsection{Test 2, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
+\caption{302 College, Test 2, TC\_A1}
+\label{fig:302_College_Test_2_TC_A1}
+\end{figure}
+
+\subsection{Test 3, Bathroom and attic fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
+\caption{302 College, Test 3, TC\_A1}
+\label{fig:302_College_Test_3_TC_A1}
+\end{figure}
+
+\clearpage
+
+\section{305 Manning}
+
+\subsection{Test 1, Garage fire, interior attack}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
+\caption{305 Manning, Test 1, TC\_A1}
+\label{fig:305_Manning_Test_1_TC_A1}
+\end{figure}
+
+\subsection{Test 2, Bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
+\caption{305 Manning, Test 2, TC\_A1}
+\label{fig:305_Manning_Test_2_TC_A1}
+\end{figure}
+
+\subsection{Test 3, Complete burndown}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_TC_A1}
+\caption{305 Manning, Test 3, TC\_A1}
+\label{fig:305_Manning_Test_3_TC_A1}
+\end{figure}
+
+\clearpage
+
+\section{289 Manning}
+
+\subsection{Test 1, Basement fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
+\caption{286 College, Test 1, TC\_A1}
+\label{fig:289_Manning_Test_1_TC_A1}
+\end{figure}
+
+\subsection{Test 2, Deck and attic fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A1}
+\caption{286 College, Test 2, TC\_A1}
+\label{fig:289_Manning_Test_2_TC_A1}
 \end{figure}
@@
 
-\chapter{Appendix A}
+\chapter{Placeholder}
 

### 2014-07-24 Projects/Spartanburg_2014/Scripts/plot.py

@@ -230,7 +230,7 @@ for f in os.listdir(data_dir):
 
             # Save plot to file
             print 'Plotting ', group
-            savefig('../Figures_Plots/' + test_name + '_' + group[0].rstrip('_') + '.pdf')
+            savefig('../Figures/Script_Figures/' + test_name + '_' + group[0].rstrip('_') + '.pdf')
             close('all')
 
         close('all')

### 2014-07-24 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update report, input files, and figures

@@
 \label{fire_sum}
-The following account of events is based on information provided from the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report~\cite{NIOSH:Bowyer}.
-Details regarding times are taken from the report and should be considered approximate values.
+The account of events for this incident follows the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
+For analysis purposes, details regarding times are considered approximate values.
+The following incident narrative is taken from that NIOSH incident report~\cite{NIOSH:Bowyer}:
+\begin{quote}
+On November 2, 2012, a 54-year-old male career captain sustained injuries at a 2-1/2 story apartment building fire then died at the hospital.
+At 1716 hours, dispatch called a ``Still'' \footnote{The department defines a ``Still'' alarm to be two engine companies, two truck companies, and a battalion chief.} alarm for smoke in the area.
+Battalion Chief (BC) 19 was the first to leave the station that was just blocks away.
+He approached the fire structure by driving behind it then around to the front arriving on scene at 1717 hours.
+He reported a working fire with heavy smoke coming from the rear and front of the structure?s attic.
+Per fire department standard operating procedures, dispatch initiated a RIT \footnote{The department defines are ``RIT Response'' to be one truck company, one battalion chief, one ALS ambulance, and one EMS field officer.} response.
+At 1718 hours, E123 arrived on scene and BC19 was on scene and had assumed incident command (IC).
+The IC spoke with one of the occupants who stated everyone was out.
+The IC made entry through the front door to the stairwell to survey the interior of the 2nd floor.
+He noticed only a light haze throughout and glow around the Sector 3 door to the covered porch.
+The IC came back to the front door and met the E123 captain and a firefighter.
+They had stretched a horseshoe load which is 100 feet of 2-$\tfrac{1}{2}$ inch, a gated wye, and 150 feet of 1-$\tfrac{3}{4}$ inch hoseline to go to the 2nd floor, which is a standard department hose lay for this type occupancy.
+At 1720 hours, E49, T33, and TL39 arrived on scene.
 
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure resulted in the death of a fire captain and injury to a fire fighter.
-At approximately 17:16 hours, a dispatch was made for ``smoke in the area''.
-The dispatch was made because a person on the street saw smoke and notified the residents, who all promptly left the structure.
-A battalion chief (BC19) from the nearest station arrived on-scene about one minute after dispatch; the station was only several blocks away.
-BC19 performed an exterior size-up and reported a working fire with heavy smoke coming from the front and rear of the structure's attic.
-BC19 assumed incident command (IC) of the fire scene.
-After speaking with the building occupants, the IC confirmed the structure was evacuated.
-The IC entered the structure to investigate the second floor.
-He found only light smoke on the second floor and a glow around the doorway that led to enclosed rear porch.
+The IC made entry to the 1st floor apartment and worked his way to [the rear of the structure].
+He opened the back door to the covered porch and noticed heavy fire in the covered porch and rear stairwell area.
+At 1721 hours, the [E123 captain] and firefighter were on the 2nd floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
+The E49 crew had stretched a 2-$\tfrac{1}{2}$ inch hoseline [to the rear of the structure].
+The T33 crew set a ground ladder on [left side of the structure] and TL39 set the aerial to the roof about a third of the way back on [on the left side].
+A TL39 firefighter went to [rear of the structure] to check doors.
+He first went to the basement door which he was unable to force open.
+Then, he went to the first floor exterior enclosed porch door which was unlocked and he opened it up.
+He stated that he noticed fire light-up in the stairwell.
+He kicked in the locked door to the first floor apartment, preceded to walk in, saw no fire then backed out.
 
-Engine 123 (E123) arrived on scene at approximately 17:18.
-The IC met the E123 captain and firefighter at the front door to the structure.
-The captain and firefighter took their hose line to the second floor of the structure.
-At approximately 17:21, the captain and firefighter were on the second floor with their hoseline and had begun advancing the charged line toward the rear second floor door between the apartment and the enclosed porch.
-Approximately 30 seconds later, a fire fighter from Tower Ladder 39 (TL39) enters the enclosed porch on the rear of the structure by opening the rear exterior door to the first floor of the porch.
-The firefighter from TL39, notices ``the fire light up'' in the stairwell of the enclosed porch, and then kicks in the first level door between the rear porch and the main structure.
-The firefighter did not see any fire in the main part of the structure and proceeded to exit the structure.
-Given the amount of fire showing from the second floor of the rear porch and ``heavy fire'' in the stairwell of the rear porch, the BC radios the E123 Captain at 17:23, to alert him to the fire conditions and to advise him that E49 would be applying water to the fire on the rear of the structure from the exterior.
-No response was made by the E123 Captain.
-It is believed that the door between the rear porch and the second floor hallway, where the E123 Captain and firefighter were located may have failed by this time.
-Approximately a minute later E49 applied water to the fire in the attic.
+At 1723 hours, the IC radioed the [E123 captain] that there was heavy fire in the covered porch and attic area and that E49 was going to put water on the fire, around the [rear] attic window, but there was no acknowledgement from the [captain].
+E49 proceeded to put water on the [rear of the structure].
+The IC returned out front to the command post and donned his turnout gear.
+The lieutenant from TL39, the lieutenant and 2 firefighters from SQ5, and a E123 firefighter/paramedic (FF/PM) were near the kitchen area on the 2nd floor when they heard a loud commotion.
+The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the victim and other crew member untangled.
+The TL39 Lieutenant and SQ5 fire fighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
 
-Squad 5 (S5) entered the front of the structure at approximately 17:25 and headed to the second floor.
-They heard a commotion and found the E123 Captain collapsed on the kitchen floor and entangled with the E123 firefighter.
-A Mayday was called on the radio by S5 at approximately 17:27 and the E123 Captain was removed from the front of the building at approximately 17:29 and succumbed to his injuries at the hospital at 17:38.
-Table~\ref{tab:fire_info} presents the timeline of the fire.
+At 1727 hours, the TL39 crew had just completed the first hole in the roof about midway on [the right side] roof with minimal fire showing, when they heard the Mayday.
+The IC verified that a firefighter was down, called a Mayday, and requested a 2-11 Assignment \footnote{A 2-11 alarm is a 2nd alarm upgrade.
+The response is four engines, two trucks, one tower ladder, two battalion chiefs, one deputy district chief, one air mask service bottle truck, and a media affairs unit.}.
+Dispatch initiated a 2-11 alarm.
+SQ5 and other members on the 2nd floor grabbed the [E123 captain] and got him down the stairs.
+The TL39 crew, with assistance from a T33 and SQ5 firefighter, had just completed a second hole on [right side] of the roof about a third of the way back when conditions worsened.
+At 1729 hours, the roof ventilation crew was back in the aerial basket when they noticed the victim being brought out to the front yard.
+The victim was nonresponsive in the front yard and CPR was successfully performed.
+The IC met the A19 crew and escorted them to the [E123 captain].
+The revived [captain] was responsive and talking to the paramedics as he was loaded into the ambulance.
+At 1738 hours, the [captain] was transported to the local hospital where he had complications during airway management and died.
+\end{quote}
 
+\noindent For an overview of timeline of events, see Table~\ref{tab:fire_info}. A plan view of the structure and location where the captain collapsed can be found in Fig.~(\ref{fig:simp_geom}).
 \begin{table}
@@
          & \\[.25cm]
-\multirow{2}{*}{17:20:00}    & \multirow{2}{*}{\parbox{10cm} {Attic self ventilation - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
+\multirow{2}{*}{17:20:00}    & \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}} \\
          & \\[.25cm] 
-17:21:00 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4 in hose line. \\[.25cm]
-17:21:30 & 1$^{st}$ floor exterior porch door opened. \\[.25cm]
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+17:21:00 & E123 captain and firefighter on 2nd floor with 1-$\tfrac{3}{4}$ inch hoseline. \\[.25cm]
+17:21:30 & 1st floor exterior porch door opened. \\[.25cm]
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: captain or firefighter.}} \\
          & \\[.25cm]
@@
 17:27:00    & After hearing a Mayday call from SQ5, IC calls a Mayday. \\[.25cm]
-17:29:00    & E123 Capt. carried out of structure. \\
+17:29:00    & E123 captain carried out of structure. \\
 \bottomrule[1.25pt]
@@
 
-\section{Timeline}
-\label{timeline}
+\chapter{Model Results}
+\label{results}
+
+To examine results from the model, it is important to link the timelines from fire scene to the simulation.
 Table~\ref{tab:firesim} shows the fireground timeline along with the corresponding simulation times.
@@
          & \\[.25cm]
-         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{9cm} {Simulation starts. Attic fire ignites. Initial self ventilation on charlie side. Front door open.}} \\
+         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{9cm} {Simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
          & & \\[0.25cm]
@@
          & 55 & Ventilation through wall penetration on left side of structure. \\[.25cm] 
-17:21:00 & 100 & E123 Capt. and FF on 2$^{nd}$ floor with 1 3/4-in hose line. \\[.25cm]
-\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{1$^{st}$ floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
+17:21:00 & 100 & E123 captain and firefighter on 2nd floor with 1-$\tfrac{3}{4}$ inch hoseline. \\[.25cm]
+\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{1st floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
         &  & \\[.25cm]
@@
         & 160 & Top of interior door fails in FDS model. \\[.25cm] 
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: Capt. or FF.}} \\
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: captain or firefighter.}} \\
          & & \\[.25cm]
@@
          & &  \\[.25cm]
-17:29:00    &   & E123 Capt. carried out of structure. \\
+17:29:00    &   & E123 captain carried out of structure. \\
 \bottomrule[1.25pt]
@@
 \end{table}
-
-\chapter{Model Results}
-\label{results}
 
@@
 \section{Hallway Flow Path}
-From on-scene reports from the BC (Section~\ref{fire_sum}) and simulation results (Section~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report, while the BC was inside the structure on the second floor, the  BC observed only a light haze and a glow around the door between the hallway and enclosed porch.
-This indicated that some amount of the fire was burring in the area of the enclosed porch.
+From on-scene reports (Section~\ref{fire_sum}) and simulation results (Section~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
+From the NIOSH report, while the IC was inside the structure on the second floor, only a light haze and a glow around the door between the hallway and enclosed porch was observed.
+This indicated fthe presence of fire in the area of the enclosed porch.
 The simulation shows a high hazard area in the attic and the enclosed porch at this time.
-By the time the E123 Captain and FF arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
+By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
 Temperature and pressure, greater than 260~$^{\circ}$C (500~$^{\circ}$F) and 5~Pa respectively, were on the porch side of the steel door at the rear of the structure.
-Exposure to these conditions weakened the structural integrity of the door, eventually leading to a partial failure.
+Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
 Fig.~(\ref{fig:chicago_doorfold}) shows the state of the rear door post fire.
@@
 
-While we have estimated the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch to the kitchen of the structure was created.
+While we had to estimate the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
-The combustion-gases at elevated temperature and pressure  in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seems to equalize.
+The combustion-gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equalize.
 The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
@@
 Therefore, for analysis of the modeled exposure temperatures, we set the maximum visualized temperature to be all values that are 260~$^{\circ}$C (500~$^{\circ}$F) or above.
-This means that temperatures visualized in the highest range in the model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); predicted temperatures could in fact be higher.
+This means that temperatures visualized in the highest range in the model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); simulated temperatures could in fact be higher.
 
-Prior to door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
+Prior to the door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
 Temperatures are highest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away allowing additional oxygen to mix with the fuel rich fire gases.
@@
 Fig.~(\ref{fig:temp_top_165})).
-Within one minute after the door fails, the hallway temperatures are nominally at or above 260~$^{\circ}$C (500~$^{\circ}$F) through out the hallway (cf Fig.~(\ref{fig:temp_top_220})).
+Within one minute after the door fails, the hallway temperatures are nominally at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway (cf Fig.~(\ref{fig:temp_top_220})).
 This illustrates that the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
@@
 This resulted in a specified source fire of 12.3~MW, however based on the limited ventilation in the attic and enclosed porch the model generated a peak HRR of approximately 10 MW as a result of the limited supply of oxygen.
-The fire began in the attic and spread down into the enclosed porch on the rear (Charlie side) of the structure.
+The fire began in the attic and spread down into the enclosed porch on the rear of the structure.
 The spread of heat and fire gases into the second floor of the structure was limited by a closed steel faced, wood framed door that was located between the enclosed porch and the hallway.
@@
 
-Unfortunately a FF and a Captain were advancing a hose line in the hallway at the time of the failure of the door.
-The Captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday, the Captain was rescued from the structure but later succumbed to his injuries.
+Unfortunately a captain and firefighter were advancing a hose line in the hallway at the time of the failure of the door.
+The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday, the captain was rescued from the structure but later succumbed to his injuries.
 

### 2014-07-25 Studies/2012_Chicago/Report/Chicago_Fire.tex
Reports/Docs: Change font size to 12 pt
Chicago Report: Make edits throughout report

@@
-\documentclass[11pt,oneside]{book}
+\documentclass[12pt,oneside]{book}
 
@@
 \newcommand{\N}{\mbox{N}}
+
+% Extra packages
+\usepackage{xfrac}
 
@@
 \chapter{Introduction}
-Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements and standards, improve the understanding of the behavior, prevention and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) to provide insight on the fire development and thermal conditions of other line of duty death (LODD) fires~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
-The overriding objective of all of these studies is to improve the safety of fire fighters.
+Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
+The objective of all of these studies has been to improve the safety of fire fighters.
 
-On November 2, 2012, a fire in a 2 1/2 story wood frame residential structure claimed the life of a Chicago firefighter.
-NIST examined the fire dynamics of this incident at the request of NIOSH and Chicago Fire Department (CFD).
-Computer simulations of the fire using Fire Dynamics Simulator and Smokeview, provide insight on the fire development and thermal conditions that may have existed in the residence during the fire.
+On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago firefighter.
+NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
+Computer simulations of the fire incident were conducted using Fire Dynamics Simulator and Smokeview to provide insight into the fire development and thermal conditions that might have existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
 \begin{enumerate}
-\item To examine with physics-based calculations the effect of flow path on the temperature, pressure, and fire conditions in this multi-story residential structure.
-\item To provide visualization of fire behavior representative of what Chicago Fire Department members experienced during the course of their interior operations.
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
+\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department experienced during the course of their interior operations.
 \end{enumerate}
@@
 The account of events for this incident follows the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
-For analysis purposes, details regarding times are considered approximate values.
-The following incident narrative is taken from that NIOSH incident report~\cite{NIOSH:Bowyer}:
+For the purpose of this analysis, the details regarding times are considered to be approximate values.
+The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer}:
 \begin{quote}
 On November 2, 2012, a 54-year-old male career captain sustained injuries at a 2-1/2 story apartment building fire then died at the hospital.
-At 1716 hours, dispatch called a ``Still'' \footnote{The department defines a ``Still'' alarm to be two engine companies, two truck companies, and a battalion chief.} alarm for smoke in the area.
+At 1716 hours, dispatch called a ``Still'' alarm\footnote{The department defines a ``Still'' alarm to be two engine companies, two truck companies, and a battalion chief.} for smoke in the area.
 Battalion Chief (BC) 19 was the first to leave the station that was just blocks away.
 He approached the fire structure by driving behind it then around to the front arriving on scene at 1717 hours.
-He reported a working fire with heavy smoke coming from the rear and front of the structure?s attic.
-Per fire department standard operating procedures, dispatch initiated a RIT \footnote{The department defines are ``RIT Response'' to be one truck company, one battalion chief, one ALS ambulance, and one EMS field officer.} response.
+He reported a working fire with heavy smoke coming from the rear and front of the structure's attic.
+Per fire department standard operating procedures, dispatch initiated a RIT response\footnote{The department defines are ``RIT Response'' to be one truck company, one battalion chief, one ALS ambulance, and one EMS field officer.}.
 At 1718 hours, E123 arrived on scene and BC19 was on scene and had assumed incident command (IC).
 The IC spoke with one of the occupants who stated everyone was out.
-The IC made entry through the front door to the stairwell to survey the interior of the 2nd floor.
+The IC made entry through the front door to the stairwell to survey the interior of the 2\textsuperscript{nd} floor.
 He noticed only a light haze throughout and glow around the Sector 3 door to the covered porch.
 The IC came back to the front door and met the E123 captain and a firefighter.
-They had stretched a horseshoe load which is 100 feet of 2-$\tfrac{1}{2}$ inch, a gated wye, and 150 feet of 1-$\tfrac{3}{4}$ inch hoseline to go to the 2nd floor, which is a standard department hose lay for this type occupancy.
+They had stretched a horseshoe load which is 100 feet of 2\sfrac{1}{2}-inch, a gated wye, and 150 feet of 1\sfrac{3}{4}-inch hoseline to go to the 2\textsuperscript{nd} floor, which is a standard department hose lay for this type occupancy.
 At 1720 hours, E49, T33, and TL39 arrived on scene.
 
-The IC made entry to the 1st floor apartment and worked his way to [the rear of the structure].
+The IC made entry to the 1\textsuperscript{st} floor apartment and worked his way to [the rear of the structure].
 He opened the back door to the covered porch and noticed heavy fire in the covered porch and rear stairwell area.
-At 1721 hours, the [E123 captain] and firefighter were on the 2nd floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
-The E49 crew had stretched a 2-$\tfrac{1}{2}$ inch hoseline [to the rear of the structure].
-The T33 crew set a ground ladder on [left side of the structure] and TL39 set the aerial to the roof about a third of the way back on [on the left side].
-A TL39 firefighter went to [rear of the structure] to check doors.
+At 1721 hours, the [E123 captain] and firefighter were on the 2\textsuperscript{nd} floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
+The E49 crew had stretched a 2\sfrac{1}{2}-inch hoseline [to the rear of the structure].
+The T33 crew set a ground ladder on [the left side of the structure] and TL39 set the aerial to the roof about a third of the way back on [the left side].
+A TL39 firefighter went to [the rear of the structure] to check doors.
 He first went to the basement door which he was unable to force open.
@@
 
-At 1723 hours, the IC radioed the [E123 captain] that there was heavy fire in the covered porch and attic area and that E49 was going to put water on the fire, around the [rear] attic window, but there was no acknowledgement from the [captain].
+At 1723 hours, the IC radioed the [E123 captain] that there was heavy fire in the covered porch and attic area and that E49 was going to put water on the fire, around the [rear] attic window, but there was no acknowledgment from the [captain].
 E49 proceeded to put water on the [rear of the structure].
 The IC returned out front to the command post and donned his turnout gear.
-The lieutenant from TL39, the lieutenant and 2 firefighters from SQ5, and a E123 firefighter/paramedic (FF/PM) were near the kitchen area on the 2nd floor when they heard a loud commotion.
-The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the victim and other crew member untangled.
+The lieutenant from TL39, the lieutenant and 2 firefighters from SQ5, and a E123 firefighter/paramedic (FF/PM) were near the kitchen area on the 2\textsuperscript{nd} floor when they heard a loud commotion.
+The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the [captain] and other crew member untangled.
 The TL39 Lieutenant and SQ5 fire fighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
@@
 At 1727 hours, the TL39 crew had just completed the first hole in the roof about midway on [the right side] roof with minimal fire showing, when they heard the Mayday.
-The IC verified that a firefighter was down, called a Mayday, and requested a 2-11 Assignment \footnote{A 2-11 alarm is a 2nd alarm upgrade.
+The IC verified that a firefighter was down, called a Mayday, and requested a 2-11 Assignment\footnote{The department defines a 2-11 alarm as a second alarm upgrade.
 The response is four engines, two trucks, one tower ladder, two battalion chiefs, one deputy district chief, one air mask service bottle truck, and a media affairs unit.}.
 Dispatch initiated a 2-11 alarm.
-SQ5 and other members on the 2nd floor grabbed the [E123 captain] and got him down the stairs.
-The TL39 crew, with assistance from a T33 and SQ5 firefighter, had just completed a second hole on [right side] of the roof about a third of the way back when conditions worsened.
-At 1729 hours, the roof ventilation crew was back in the aerial basket when they noticed the victim being brought out to the front yard.
-The victim was nonresponsive in the front yard and CPR was successfully performed.
+SQ5 and other members on the 2\textsuperscript{nd} floor grabbed the [E123 captain] and got him down the stairs.
+The TL39 crew, with assistance from a T33 and SQ5 firefighter, had just completed a second hole on [the right side] of the roof about a third of the way back when conditions worsened.
+At 1729 hours, the roof ventilation crew was back in the aerial basket when they noticed the [captain] being brought out to the front yard.
+The [captain] was nonresponsive in the front yard and CPR was successfully performed.
 The IC met the A19 crew and escorted them to the [E123 captain].
@@
 
-\noindent For an overview of timeline of events, see Table~\ref{tab:fire_info}. A plan view of the structure and location where the captain collapsed can be found in Fig.~(\ref{fig:simp_geom}).
+\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~(\ref{fig:simp_geom}).
 \begin{table}
@@
 \captionof{table}{Abridged NISOH approximate fire event timeline}\label{tab:fire_info}
-\begin{tabular}{l l}
+\begin{tabular}{cl}
 \toprule[1.5pt]
-Incident Time [hr:min:s] & Fire Behavior / Fireground Operation  \\
+Incident Time  &  Fire Behavior / Fireground Operation  \\
+(hh:mm:ss)     &                                        \\
 \midrule
@@
          & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:16:00}    &  \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
          & \\[.25cm]
@@
          & \\[.25cm] 
-17:21:00 & E123 captain and firefighter on 2nd floor with 1-$\tfrac{3}{4}$ inch hoseline. \\[.25cm]
+17:21:00 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
 17:21:30 & 1st floor exterior porch door opened. \\[.25cm]
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: captain or firefighter.}} \\
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
          & \\[.25cm]
@@
 \label{model}
-FDS is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Fire Dynamics Simulator is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
 The cells are contained together within one larger volume known as a computational domain.
-The CFD model computes the density, velocity, temperature, pressure and species concentration of the gas in each cell.
+The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
 Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
 One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
-A complete description of the FDS model is given in reference~\cite{FDS_Math_Guide}.
+A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.
 
-Smokeview is a software tool designed to visualize the results of the FDS~\cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the modeled fire using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
+Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
 Smokeview allows the fire and fire movement to be visualized.
@@
 
-Input data from a number of sources must be collected and documented in order to simulate a fire with FDS or any other model.
-For the model presented here, information was obtained from two main sources.
-From the fire scene the following information was gathered: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
-From witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, order and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
-The following subsections will describe the inputs used to construct the simulation, including any engineering approximations or assumptions that were made.
+Input data from various sources must be collected and documented to simulate a fire using FDS or any other fire model.
+For the simulation results presented in this document, information was obtained from two primary sources.
+The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
+The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
+The following subsections will describe the inputs that were used to construct the simulation, including any engineering approximations or assumptions that were made.
 
@@
 \label{geom}
-The structure was a 2 1/2 story residential building with balloon frame construction and gable roof.
-\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+The structure involved in this fire incident was a 2~\sfrac{1}{2} story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
 Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction, is that without fire stops, there is void space for fire to potentially travel between the floors.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint (cf.
-Fig.~(\ref{fig:simp_geom})).
+One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~(\ref{fig:simp_geom}).
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
-Interior walls were constructed from nominal lumber with 12.7~mm (0.5~in) gypsum board over top~\cite{NIOSH:Bowyer}.
-Additionally there was a half-story attic that was used to house the structure's hot water heater.
-There were three sets of stairs in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
-Entry to the first floor of the structure can be made either in the front or rear, see Fig.~(\ref{fig:simp_geom}).
+The interior walls were constructed from nominal lumber with 12.7~mm (0.5~in) gypsum board over top~\cite{NIOSH:Bowyer}.
+Additionally, there was a half-story attic that contained the structure's hot water heater.
+Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
+Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~(\ref{fig:simp_geom}).
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
-Discussion of the fire's impact on interior conditions can be found in Section~\ref{results}.
-Fig.~(\ref{fig:alpha_ex}) shows the post-incident exterior of the front and rear of the structure.
-Note that the majority of the damage is to the structure's attic and second floor rear porch.
-Fully dimensioned drawings of the first and second floor interiors can be found in Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}), respectively.
+Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
+Figure~(\ref{fig:alpha_ex}) shows the exterior of the front and rear of the structure after the incident.
+Note that the majority of the damage occurred in the attic and rear porch on the second floor.
+Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}), respectively.
 
@@
 \end{tabular*}
-\caption{Plan view of 1st (top) and 2nd (bottom) floor of structure. Stairs and key rooms are identified Drawn using measurements collected by NIST staff.}
+\caption[Plan view of 1st (top) and 2nd (bottom) floor of structure.]{Plan view of 1st (top) and 2nd (bottom) floor of structure.
+Stairs and key rooms are identified using measurements collected by NIST.}
 \label{fig:simp_geom}
@@
 \end{tabular*}
-\caption{Photograph showing the post-incident front (left) and rear (right) exterior of the structure.}
+\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
 \label{fig:alpha_ex}
@@
 
-To estimate the fuel, fire size, and structure ventilation, on-scene videos and post-incident reports are used.
+To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
 Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch consisted of a fuel load that is mainly wood: the rear porch was enclosed with wood planks exteriorly covered by foam board and vinyl siding, the roof was asphalt shingles over wood planking, and the attic and porch had oriented strand board (OSB) floors.
+The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board (OSB).
 
 Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) found from the SFPE Handbook~\cite{SFPE:Tewarson}.
-A balanced chemical reaction for wood oxidation can written:
+A balanced chemical reaction for wood oxidation can written as:
 
@@
 
-The heat of combustion of wood used in this simulation is 16400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
-The heat of combustion quantifies the energy release per unit mass of the fuel.
+The value for the heat of combustion of wood used in this simulation was 16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The heat of combustion quantifies the amount of energy per unit mass of the fuel.
 The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
@@
     FUEL = 'WOOD', 
-    HEAT_OF_COMBUSTION=16400,
+    HEAT_OF_COMBUSTION = 16400,
     SOOT_YIELD = 0.015,
@@
 
-Note that using the input lines above will invoke the simple chemistry reaction balance in FDS.
-This means that fuel and air react to form only CO$_2$, CO, H$_2$O, Soot, and N$_2$.
-If there is a desire for any other combustion products then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
-Based on above input lines FDS uses the default, mixing-controlled fast chemistry combustion model.
+Note that using the input lines above will invoke the simple chemistry reaction mechanism in FDS in which fuel and air react to form only CO$_2$, CO, H$_2$O, soot, and N$_2$.
+If the inclusion for other combustion products is desired, then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
+Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
 This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
@@
 
-To estimate the energy release per unit time and unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
-Experiments were conducted in a cone calorimeter \footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials.} to determine the 5 minute average of HRRPUA  \footnote{HRRPUA is the heat release rate per unit area.} (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
+To estimate the energy release rate per unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
+Experiments were conducted in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials.} to determine the 5 minute average of HRRPUA\footnote{HRRPUA is the heat release rate per unit area.} (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
 Babrauskas and Grayson~\cite{babrauskas1990} suggest that the heat release rate per unit area for a variety of woods is approximately 50~kW/m$^2$.
 
-To calculate the total fire size, the appropriate burnable area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
+To calculate the total fire size, the appropriate burning area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
 Based on the floor plan of the structure, the underside of the roof is approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
-Additionally there is 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
-Examination of post incident images showed that the floor immediately over the back porch burned away.
-That area will be considered as part of the porch fire.
-Based on post-incident damage, approximately 50 \% of the remaining floor area as fuel to the attic fire and 90 \% of the roof is con sidered.
-To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$) and the floor area (43~m$^2$ (463~ft$^2$)) are included.
-Using an HRRPUA of wood of 50~kW/m$^2$, results in a potential peak fire size of 9~MW.
-To estimate the porch fire size, the the four walls of porch enclosure (42~m$^2$) and the floor and ceiling of the porch (24~m$^2$ (258 ft$^2$)) are included.
-The total area is 64~m$^2$ (689~ft$^2$).
-Using the same HRRPUA of 50~kW/m$^2$, the potential peak fire size on the porch is approximately 3.3~MW.
-The total fire size for this structure is estimated to be at peak, 12.3~MW.
-Since it is unknown when the fire started relative to notification of a fire or how fast the fire spread, several simplifications are made.
-First is that the attic fire starts at the beginning of the simulation and ramps up to 9~MW in 10 seconds.
-The porch fire starts 40 seconds into the simulation and ramps to 3.3~MW in 10 seconds.
-A ten second ramp to peak was used to prevent sharp velocity changes at the fire boundary condition in FDS.
-The second is that the sources of the gas phase wood fuel are of fixed area and at fixed locations (2 sources for attic, 1 source for porch).
-The following lines define the source fires for this FDS input file:
+Additionally, there is 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
+Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
+That area was considered to be part of the porch fire.
+Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
+To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
+Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
+To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
+Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch is approximately 3.3~MW.
+Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
+Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
+The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
+The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
+The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+The following lines define the source fires in the FDS input file:
 
 \begin{lstlisting}
-&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE',TAU_Q=10 /
+&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE', TAU_Q=10 /
 &VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
 &VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE',DEVC_ID='SECOND FIRE'/ 1.5 m^2
+&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 1.5 m^2
 &DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
 \end{lstlisting}
-Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes of a specific area.
+Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
 
@@
 \label{matl}
-While the fire was simplified to constant area fuel sources (Section~\ref{fire}), defining the material properties of the walls and ceiling are still important from a heat transfer perspective.
-In this study, gypsum~\cite{Drysdale:1} is used for the finished walls and ceilings on the main two floors of the structure and wood~\cite{Incropera:1} for the unfinished portions of the attic and rear porch.
-The text provided below are the lines necessary to define these materials in this FDS input file.
+While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+In this study, the material properties of gypsum~\cite{Drysdale:1} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+The following lines define these materials in the FDS input file:
 
@@
     SPECIFIC_HEAT = 1.09
-    DENSITY = 930./
+    DENSITY = 930. /
 
@@
     SPECIFIC_HEAT = 1.38
-    DENSITY = 510./ 
+    DENSITY = 510. / 
 \end{lstlisting}
@@
 \label{Vents}
-The simulations in this study account for the changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
-There are two ventilation scenarios that are considered in this study.
-The first is the baseline simulation where the ventilation times and ventilation areas represent our best understanding of the incident.
-The alternative simulation does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
+The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+Two different ventilation scenarios were considered in this study.
+The first scenario involves a baseline simulation in which the ventilation times and ventilation areas represent our best understanding of the incident.
+The second scenario, or alternative simulation, does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
 The times of the ventilation changes are provided in Table~\ref{tab:vents}.
@@
 The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
-Therefore, leakage would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
-An unknown in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2:40 into the simulation).
+Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
+An unknown in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
 While this time may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
@@
 \centering
-\captionof{table}{Simulation Ventilation Timelines}\label{tab:vents}
-\begin{tabular}{ccccc}
+\captionof{table}{Timeline of Ventilation Changes in the Simulation}\label{tab:vents}
+\begin{tabular}{cccll}
 \toprule[1.5pt]
-Baseline Simulation [s] & Alternative Simulation [s] & Ventilation Area [m$^2$] & Type & Structure Side \\
+Baseline    &  Alternative  &  Ventilation  &  Type         &  Side of         \\
+Simulation  &  Simulation   &  Area         &               &  Structure       \\
+{[s]}       &  {[s]}        &  [m$^2$]      &               &                  \\
 \midrule
@@
 
-For the simulation in this study, we can estimate a measure of how well the flow field is resolved by the non-dimensional expression $D^*/\dx$.
-Here $D^*$ is a characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
+For the simulation in this study, we can estimate a measure of how well the flow field is resolved by using the non-dimensional expression $D^*/\dx$.
+Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
 \begin{equation}
@@
 \end{equation}   
-From the FDS User Guide~\cite{FDS_Users_Guide}, ``the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.'' Here, $D$ is the physical diameter of the fire as input to the model.
-Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the characteristic fire diameter to cell size ratio based on the 3.3 MW porch fire is 15.5 and for the 9 MW fire is 23.
+From the FDS User Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
+relation $Q^* = (D^*/D)^{5/2}$.
+Here, $D$ is the physical diameter of the fire as it is specified in the simulation.
+Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the ratio of the characteristic fire diameter to the cell size ($D^*/\dx$) is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824}.
-The grid resolution used in this model falls within typical, engineering $D^*/\dx$ values.
-As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10 cm.
-Fig.~(\ref{fig:geom_grid}) shows the
-front of the structure rendered in Smokeview with the 10 cm mesh.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced reasonable results.
+The grid resolution used in this model is within typical engineering $D^*/\dx$ values.
+As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
+Figure~(\ref{fig:geom_grid}) shows the front of the structure rendered in Smokeview with the 10 cm mesh.
 
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
-\caption{Front side of the structure with 10 cm computation mesh.}
+\caption{Front side of the structure with 10 cm computational mesh.}
 \label{fig:geom_grid}
@@
 
-As discussed Section~\ref{geom}, the structure has 17.15~m (56~ft) by 6.15~m (20~ft) footprint with a total height of 8.56~m (28~ft).
-To ensure adequately resolved fluid flow into and out of the structure the computational domain is extended beyond the volume of the structure.
-The total volume of the computational domain is 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-At 10~cm (3.9~in) resolution this would result in 2.4 million computational cells.
-To make the simulation time more tractable, the domain was divided into 16 equal 150 thousand cell meshes to be processed in parallel.
-Fig.~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain.
+As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
+The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
+At a grid resolution of 10~cm (3.9~in), this would result in 2.4 million computational cells.
+To make the simulation time more reasonable, the domain was divided into 16 equal meshes (each containing 150 thousand grid cells) to be processed in parallel.
+Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes.
+For the simulations that were conducted as part of this study, Table~\ref{tab:mod_param} shows the relevant model input parameters that were discussed in Section~\ref{model}.
 
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption{Front-right side of the structure within computational domain. Each of the 16 meshes is 3 m (9.8 ft) by 10 m (33 ft) by 5 m (16.4 ft).}
+\caption[Front-right side of the structure within the computational domain (with multiple meshes).]{Front-right side of the structure within the computational domain (with multiple meshes).
+Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
 \label{fig:mult_mesh}
 \end{figure}
-
-For the simulations performed for this study, Table~\ref{tab:mod_param} includes the relevant model input parameters discussed in Section~\ref{model}.
 
@@
 \midrule
- Simulation Time           & 5 minutes                             & -- \\[.25cm]
- Grid Size                 & 10 cm                                 & Section~\ref{mesh} \\ [.25cm]
+ Simulation Time                   &  5 min                                                        & -- \\[.25cm]
+ Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
  Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
@@
                                    &  Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$  & \\
-                           & Heat of Combustion: 16400~kJ/kg                             & \\ [.25cm]
+                                   &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
 \multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
@@
 
-To examine results from the model, it is important to link the timelines from fire scene to the simulation.
+To examine the results of the simulations, it is important to link the timelines from fire scene to the simulation times.
 Table~\ref{tab:firesim} shows the fireground timeline along with the corresponding simulation times.
@@
 \centering
-\captionof{table}{Fire - Simulation Event Timeline}\label{tab:firesim}
-\begin{tabular}{l l l}
+\captionof{table}{Fire Incident and Simulation Event Timeline}\label{tab:firesim}
+\begin{tabular}{ccl}
 \toprule[1.5pt]
-Incident Time [hr:min:s] & Model Time [s] & Fire Behavior / Fireground Operation  \\
+Incident Time  &  Simulation Time  &  Fire Behavior / Fireground Operation  \\
+{[hh:mm:ss]}   &  {[s]}            &                                        \\
 \midrule
@@
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm $-$ two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
          & \\[.25cm]
@@
          & 55 & Ventilation through wall penetration on left side of structure. \\[.25cm] 
-17:21:00 & 100 & E123 captain and firefighter on 2nd floor with 1-$\tfrac{3}{4}$ inch hoseline. \\[.25cm]
+17:21:00 & 100 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
 \multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{1st floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
@@
         & 160 & Top of interior door fails in FDS model. \\[.25cm] 
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123: captain or firefighter.}} \\
+\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
          & & \\[.25cm]
@@
 The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Fig.~(\ref{fig:hrr}) shows the HRR versus time based on the prescribed fires described in Section \ref{fire} and the FDS results for two venting scenarios.
-The two vertical lines represent when a firefighter opened the back door of the structure (t = 130 s) and when the second floor interior door was estimated to fail (t = 160 s).
-Due to a lack of information about when the fire ignited or how fast it grew, these parameters needed to be estimated.
-While the growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20 seconds) is atypically fast, analysis of the incipient stage of the fire growth was not considered in this study.
-The goal was to have a fire approach its estimated peak and become ventilation limited quickly to minimize computation time while still aligning with the observations of video and picture evidence from the fire.
-Accuracy of heat transfer to the walls of the structure may be sacrificed by taking this approach, however all window, door, and wall failure were driven by the event timeline not modeling predicted failure temperatures.
+Figure~(\ref{fig:hrr}) shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
+The two vertical lines represent the time at which a firefighter opened the back door of the structure ($t$ = 130 s) and the time at which the second floor interior door was estimated to fail ($t$ = 160 s).
+Due to a lack of information about the time of fire ignition or how fast the fire grew, these parameters needed to be estimated.
+The growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
+The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while still aligning with the timeline observations of video and picture evidence from the fire.
+The accuracy of heat transfer to the walls of the structure may be sacrificed by using this approach; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
 
@@
 \includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-\caption{HRR versus time of FDS model of the West 50th St. fire. The first vertical line indicates when the back door failed, the second indicates when the interior hallway door failed.}
+\caption[HRR versus time from FDS simulations of the West 50th St.
+fire.]{HRR versus time from FDS simulations of the West 50th St.
+fire.
+The first vertical line indicates when the back door failed, and the second vertical line indicates when the interior hallway door failed.}
 \label{fig:hrr}
@@
 
-In Fig.~(\ref{fig:hrr}), the solid line is the baseline FDS simulation (this represents the on-scene conditions).
-The dashed line represents an alternative series events, specifically the rear door does not get opened and the subsequent beta side breach does not occur.
-The dash-dotted line is the prescribed FDS input HRR.
-We can see that within the first 10 seconds, the structure is under-ventilated as the modeled HRR is below the prescribed HRR.
-The HRR peaks at just under 9 MW before becoming oxygen limited.
-The HRR drops to 5~MW as the available oxygen inside the structure gets consumed.
-There is insufficient available oxygen in the structure to combust all of the fuel and combustion occurs locally at vents.
-Fig.~(\ref{fig:smv_ext_fire}) illustrates exterior flaming combustion through the failed Charlie side window and attic breach just after the second fire ignites at 40 seconds.
-After additional wall breaches at 45 and 55 seconds (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR spikes to 9~MW before again dropping to about 6~MW.
-The HRR then begins to increase towards a sustainable steady state value.
+In Fig.~(\ref{fig:hrr}), the solid line represents the baseline FDS simulation (this represents the on-scene conditions).
+The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach on the left-side of the structure does not occur.
+The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS.
+As shown in Fig.~(\ref{fig:hrr}), the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
+The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay.
+The HRR is reduced to 5~MW as the oxygen inside the structure is consumed.
+There is an insufficient amount of oxygen in the structure to combust all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
+Figure~(\ref{fig:smv_ext_fire}) shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
+After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
+The HRR then increases towards a sustainable steady-state value.
 
-From Fig.~(\ref{fig:hrr}), we see that the HRR for both FDS simulations are identical until 130 seconds (HRR $\approx$ 7~MW).
-At 130 seconds the rear door is opened in the baseline simulation.
-At 135 seconds there is an additional beta side breach (Table~\ref{tab:vents}).
+Figure~(\ref{fig:hrr}) indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
+At 130~s, the rear door is opened in the baseline simulation.
+At 135~s, there is an additional breach on the left side of the structure (Table~\ref{tab:vents}).
 The open door and breach act as additional pressure releases for the structure.
-Again, the abrupt change in ventilation causes the HRR to spike.
-Here we see a rise from 7~MW to 9.7~MW at 139 seconds.
-At the time of door failure (160 seconds), the HRR in both cases was approximately 9 MW as there was sufficient ventilation.
-While there might be some locally different burning characteristics between the baseline simulation and the alternate simulation, in both cases the interior conditions represented a significant hazard to firefighters inside the structure.
+Again, the abrupt change in ventilation causes the HRR to increase from 7~MW to 9.7~MW at 139~s.
+At the time of the door failure (160~s), the HRR in both cases was approximately 9~MW because of the increased amount of ventilation.
+While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, the interior conditions in both cases presented a significant hazard to firefighters inside of the structure.
 Therefore, the analysis will focus on the results of the baseline simulation.
@@
 \includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
-\caption{Smokeview rendering showing combustion occurring exterior to the structure on the Charlie side.}
+\caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
 \label{fig:smv_ext_fire}
@@
 \section{Pressure}
-As the fire grows in the attic and back porch, the pressure rises.
-Fig.~(\ref{fig:pres_159s}) shows the pressure rise in the structure just before the interior door failed in the simulation.
+
+As the fire grows in the attic and rear porch, the pressure rises.
+Figure~(\ref{fig:pres_159s}) shows the pressure conditions in the structure just before the interior door failed in the simulation.
 On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa at the ceiling.
+Gases at an elevated pressure will always move towards a region of lower pressure.
+The door serves as a boundary between the high and low pressure regions.
+Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
+The velocity vectors shown in Fig.~(\ref{fig:velo_175s}), 15~s after the interior door fails, confirm this flow direction within the structure.
+
 \begin{figure}[!ht]
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption{FDS simulated pressure contours, 1 second prior to interior door failure. Note 1~Pa is 1.4 $\times 10 ^{-4}$~psi.}
+\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.
+Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
 \label{fig:pres_159s}
 \end{figure}
-Gases at elevated pressure will always travel toward an area of lower pressure.
-The door acts as a boundary between the high and low pressure areas.
-Once the door fails open, the high pressure gases flow toward the low pressure areas in the house, hallway, kitchen, and front stairwell.
-The velocity vectors in Fig.~(\ref{fig:velo_175s}), 15 seconds after the interior door fails, confirms this flow direction within the structure.
+
 \begin{figure}[!ht]
@@
 \input{../Scripts/colorbar_metric_velo}
-\caption{FDS simulated velocity vectors, 15 second after interior door failure.}
+\caption{FDS simulated velocity vectors, 15~s after interior door failure.}
 \label{fig:velo_175s}
@@
 \label{temp}
-Analysis of the simulation temperatures will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-Here, we will examine the temperature profile through these high hazards area at several snapshots in time to illustrate the changing interior conditions.
-The first times are 129 seconds into the simulation, just before a firefighter opened the rear porch door (cf.
-Fig.~(\ref{fig:temp_129s})) and 159 seconds into the simulation, just before the interior door fails (cf.
-Fig.~(\ref{fig:temp_159s})).
+Analysis of the temperatures from the FDS simulation will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+The temperature profile at these high hazard areas will be shown via several snapshots in time to illustrate the change in the interior conditions.
+The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~(\ref{fig:temp_129s})), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~(\ref{fig:temp_159s})).
 
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1 second prior to rear door opening.}
+\caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
 \label{fig:temp_129s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1 second prior to interior door failure.}
+\caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
 \label{fig:temp_159s}
@@
 
-Fig.~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
-High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the 1$^{st}$ floor rear entrance.
-Before the interior door fails, Fig.~(\ref{fig:temp_159s}), the inflow ambient air from the open door lowers the temperature local to the doorway, but we know from Fig.~(\ref{fig:hrr}) that over this interval the HRR spikes because of the additional ventilation.
-After the second floor door fails, (cf.
-Fig.~(\ref{fig:temp_161s})), the high temperature gas that filled the back porch flow in the direction of lower pressure (towards the front door).
+Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the 1st floor.
+Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}).
+As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
 Note that the conditions in the attic do not appear to be influenced.
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1 second after interior door fails.}
+\caption{FDS simulated temperature contours, 1~s after interior door failure.}
 \label{fig:temp_161s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 15 seconds after interior door fails.}
+\caption{FDS simulated temperature contours, 15~s after the interior door failure.}
 \label{fig:temp_175s}
@@
 
-From Fig.~(\ref{fig:temp_175s}), 15 seconds after the door failed, high temperature gases have descended to approximately 1~m (3.28~ft) off the ground through the interior hallway and have spilled into the kitchen (recall layout from Fig.~(\ref{fig:simp_geom})).
+As shown in Fig.~(\ref{fig:temp_175s}), 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) from the floor through the interior hallway and are flowing into the kitchen (recall the layout from Fig.~(\ref{fig:simp_geom})).
 
 \chapter{Discussion}
-The discussion will be broken up into two parts.
-The first part will address the results of the computational modeling as they relate to the interior hallways conditions.
-The second part will examine the the model results and observed outcomes of fire as they relate to tactics discussed in recent experimental research.
+The results of the FDS simulations will be discussed in two sections.
+The first section will address the results of the computational modeling as they relate to the interior hallways conditions.
+The second section will examine the the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
 
 \section{Hallway Flow Path}
-From on-scene reports (Section~\ref{fire_sum}) and simulation results (Section~\ref{temp}), interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report, while the IC was inside the structure on the second floor, only a light haze and a glow around the door between the hallway and enclosed porch was observed.
-This indicated fthe presence of fire in the area of the enclosed porch.
-The simulation shows a high hazard area in the attic and the enclosed porch at this time.
+From on-scene reports (Section~\ref{fire_sum}) and the FDS simulation results (Section~\ref{temp}), the interior conditions on the second floor of the structure were initially tenable.
+From the NIOSH report, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
+This indicated the presence of fire in the area of the enclosed porch.
+The simulation results indicate a high hazard area in the attic and the enclosed porch at this time.
 By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature and pressure, greater than 260~$^{\circ}$C (500~$^{\circ}$F) and 5~Pa respectively, were on the porch side of the steel door at the rear of the structure.
+Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) and pressures greater than 5~Pa were present on the porch side of the steel door at the rear of the structure.
 Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
-Fig.~(\ref{fig:chicago_doorfold}) shows the state of the rear door post fire.
+Figure~(\ref{fig:chicago_doorfold}) shows the state of the rear door after the fire.
 Note the large crease in the door just above the knob.
@@
 \includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
-\caption{Post fire image of interior door.}
+\caption{Post-fire image of interior door.}
 \label{fig:chicago_doorfold}
 \end{figure}
-Recent experiments conducting by the National Institute of Standards and Technology revealed similar post-fire states after doors were exposed to fires.
-Fig.~(\ref{fig:SC_doorfold}) shows doors from two different house fire experiments in different stages of degradation.
-In both cases note that the door knob assembly served as a pivot point for the upper portion of the steel from the door to collapse around.
-This is similar to the location of the folds in the remains of the steel door that was located between the hallway and the enclosed porch.
+
+Recent experiments conducted by NIST revealed similar post-fire states after doors were exposed to fires.
+Figure~(\ref{fig:SC_doorfold}) shows doors from two different residential fire experiments in different stages of degradation.
+In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
+This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in the studied fire incident.
 
@@
 \end{tabular*}
-\caption{Post experiment images of door failures.}
+\caption{Post-experiment images of door failures.}
 \label{fig:SC_doorfold}
@@
 
-While we had to estimate the time of failure for the door, the key take away is that after the door failed an interior flow path from the enclosed porch to the kitchen of the structure was created.
+While we had to estimate the time at which the door failed, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
-The combustion-gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equalize.
+The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate.
 The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
@@
 \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-\caption{Flow path on second floor following interior door failure.}
+\caption{Flow path on the second floor after the interior door failure.}
 \label{fig:flowpath_1}
@@
 
-A person is susceptible to second degree burn injuries when exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F) \cite{designation2003c}.
-While firefighters wear protective gear, gear only offers finite levels of protection.
-The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F) \cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) \cite{nfpa2013standard}.
-Extended exposure to elevated temperatures can result in significant heat transferred to the firefighter, putting him/her at risk.
-Therefore, for analysis of the modeled exposure temperatures, we set the maximum visualized temperature to be all values that are 260~$^{\circ}$C (500~$^{\circ}$F) or above.
-This means that temperatures visualized in the highest range in the model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); simulated temperatures could in fact be higher.
+A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{designation2003c}.
+While firefighters wear protective gear, gear only offers a finite amount of protection.
+The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
+Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
+Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
+Therefore, for the analysis of the simulated exposure temperatures, we set the maximum visualized temperature to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
+This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.
 
-Prior to the door failure, the elevated temperatures on the second floor were limited to the rear porch, Fig.~(\ref{fig:temp_top_159}).
-Temperatures are highest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away allowing additional oxygen to mix with the fuel rich fire gases.
-Five seconds after the door fails, hot gases have traveled the length of the interior hallway and approached the doorway into the kitchen, approximately 4.5~m (14.8~ft) away from the source fire (cf.
-Fig.~(\ref{fig:temp_top_165})).
-Within one minute after the door fails, the hallway temperatures are nominally at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway (cf Fig.~(\ref{fig:temp_top_220})).
-This illustrates that the high temperature gases seen five seconds after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
+Prior to the door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}).
+The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
+Five seconds after the door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}).
+Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}).
+These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Fig.~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F) and temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
-At these points in the structure, the exhaust gases in the flow path are air cooled/diluted by the inflow ambient gas.
-These modeled temperatures are consistent with the post-incident conditions documented in the kitchen and second floor stairwell.
+Figure~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
+At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas.
+These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
 \begin{figure}[h!]
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
+\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
 \input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 1 second prior to door failure, 1.83~m (6~ft) above the floor.}
+\caption{Temperature contours on the second floor, 1~s prior to door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_159}
@@
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
+\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
 \input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 5 seconds after door failure, 1.83~m (6~ft) above the floor.}
+\caption{Temperature contours on the second floor, 5~s after door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_165}
@@
 \centering
-\includegraphics[width=.7\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
+\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
 \input{../Scripts/colorbar_std} 
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 60 seconds after door failure, 1.83~m (6~ft) above the floor.}
+\caption{Temperature contours on the second floor, 60~s after door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_220}
@@
 \section{Tactical Considerations}
-There have been many fires where the change in a flow path has had an adverse impact on firefighter and occupant safety.
-Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years, where it could be determined that it was a flow path related incident.
-The table lists the NIOSH investigation number, the outcome, and a brief description of the flow path.
+There have been many previous fire incidents in which changes in the flow paths have had an adverse impact on firefighter and occupant safety.
+Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years in which it could be determined that there was a flow path related incident.
+This table lists the NIOSH investigation number, the outcome, and a brief description of the flow path details.
 
 Based on a review of these incidents, it is clear that fires with rapidly developing or changing flow paths are a significant hazard to the fire service.
-The development of, or changes in a flow path could be caused by the failure of a component of the structure, such as a door, window or portion of a ceiling, wall or floor.
+The development of or changes in a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
 Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.
@@
 
-In this case, the thermal degradation of the steel faced, wood framed, door led to a rapid change in thermal conditions in the hallway resulting in a lethal exposure to victim.
-Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns the fire fighters faced on the fire ground.
+In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in a lethal exposure to fire fighters.
+Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the fire fighters faced on the fire ground.
 In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
-Research has been conducted \cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, UL and others that demonstrates that applying water from the exterior into the fire area of a structure, prior to the start of interior operations, can significantly improve the safety of fire fighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
+Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of fire fighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
 
@@
 \centering
-\captionof{table}{Flowpath LODD/LODI Incidents}\label{tab:lodd}
-\begin{tabular}{l l l}
+\captionof{table}{Flow path related LODD/LODI Incidents}\label{tab:lodd}
+\begin{tabular}{lll}
 \toprule[1.5pt]
-NIOSH Report $\#$ & $\#$ LODD/LODI & Flow Path Details  \\
+NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details  \\
 \midrule
-\multirow{2}{*}{99-F01 \cite{NIOSH:Pettit} }    & \multirow{2}{*}{3 LODD}                                     & \multirow{2}{*}{\parbox{8cm} {From apartment into hallway on 10th floor of high-rise apartment building}} \\
-                 &                                                    & \\
-99-F21 \cite{NIOSH:Washenitz}         & 2 LODD/2 LODI                          & Basement to 1st floor \\
-F2000-04 \cite{NIOSH:Mezzanotte}   & 3 LODD/3 civilian deaths            & 1st floor to 2nd floor \\
-F2000-16 \cite{NIOSH:McFall} & 1 LODD/1 civilian death/1 LODI & 2nd floor hallway through 2nd floor apartment \\
-\multirow{2}{*}{F2000-23 \cite{NIOSH:McFall2}} & \multirow{2}{*}{1 LODD/2 LODI       }                   & \multirow{2}{*}{\parbox{8cm} {From ground level to 1st floor then to 2nd floor, flow exited through ceiling}} \\
-                 &                                                    & \\
-F2000-43 \cite{NIOSH:McFall3}         & 1 serious LODI/2 other LODI      & 1st floor to 2nd floor \\
+99-F01   \cite{NIOSH:Pettit}        &  3 LODDs            &  From apartment into hallway on 10th                  \\
+                                    &                     &  floor of high-rise apartment building                \\
+99-F21   \cite{NIOSH:Washenitz}     &  2 LODDs            &  Basement to 1st floor                                \\
+                                    &  2 LODIs            &                                                       \\
+F2000-04 \cite{NIOSH:Mezzanotte}    &  3 LODDs            &  1st floor to 2nd floor                               \\
+                                    &  3 civilian deaths  &                                                       \\
+F2000-16 \cite{NIOSH:McFall}        &  1 LODD             &  2nd floor hallway through                            \\
+                                    &  1 LODI             &  2nd floor apartment                                  \\
+                                    &  1 civilian death   &                                                       \\
+F2000-23 \cite{NIOSH:McFall2}       &  1 LODD             &  From ground level to 1st floor then to               \\
+                                    &  2 LODIs            &  2nd floor, flow exited through ceiling               \\
+F2000-43 \cite{NIOSH:McFall3}       &  1 serious LODI     &  1st floor to 2nd floor                               \\
+                                    &  2 other LODIs      &                                                       \\
 F2004-02 \cite{NIOSH:Berardinelli}  &  1 LODD             &  1st floor to basement                                \\
-F2005-02 \cite{NIOSH:Koedam}        & 1 LODD/4 LODI                           & Rear to front of the building \\
-F2005-04 \cite{NIOSH:McFall4}         & 1 LODD/9 LODI                           & Basement to 1st floor \\
-F2007-09 \cite{NIOSH:Tarley}           & 1 LODD/2 LODI                           & 3 story training burn $-$ flow through all levels \\
-F2007-35 \cite{NIOSH:Braddee}       & 4 LODI                                         & 1st floor to 2nd floor \\
-F2009-11 \cite{NIOSH:Merinar}         & 2 LODD                                        & Rear to front of the building \\
-F2011-13 \cite{NIOSH:Bowyer2}       & 2 LODD                                        & Lower level up stairs and through entry door and garage \\
+F2005-02 \cite{NIOSH:Koedam}        &  1 LODD             &  Rear to front of the building                        \\
+                                    &  4 LODIs            &                                                       \\
+F2005-04 \cite{NIOSH:McFall4}       &  1 LODD             &  Basement to 1st floor                                \\
+                                    &  9 LODIs            &                                                       \\
+F2007-09 \cite{NIOSH:Tarley}        &  1 LODD             &  3 story training burn - flow through                 \\
+                                    &  2 LODIs            &  all levels                                           \\
+F2007-35 \cite{NIOSH:Braddee}       &  4 LODIs            &  1st floor to 2nd floor                               \\
+F2009-11 \cite{NIOSH:Merinar}       &  2 LODDs            &  Rear to front of the building                        \\
+F2011-13 \cite{NIOSH:Bowyer2}       &  2 LODDs            &  Lower level up stairs and through                    \\
+                                    &                     &  entry door and garage                                \\
 F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartment             \\
-F2012-28 \cite{NIOSH:Bowyer}        & 1 LODD/1LODI                            & Attic fire extended into closed porch and then into 2nd floor \\
+F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed                      \\
+                                    &  1 LODI             &  porch and then into 2nd floor                        \\
 \bottomrule[1.25pt]
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 1/2 story single family structure in Chicago, Il that resulted in the death of a firefighter.
-The modeled fuel, fire size, and fire growth rate were estimated taking into account all available information: NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3~MW, however based on the limited ventilation in the attic and enclosed porch the model generated a peak HRR of approximately 10 MW as a result of the limited supply of oxygen.
-The fire began in the attic and spread down into the enclosed porch on the rear of the structure.
-The spread of heat and fire gases into the second floor of the structure was limited by a closed steel faced, wood framed door that was located between the enclosed porch and the hallway.
-After exposure to the elevated temperature and pressure from the fire in the porch area, the wood frame of the door decomposed and the steel faces of the door failed and collapsed inward.
-The door failure resulted in the creation of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death of a firefighter.
+The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
+This resulted in a specified source fire of 12.3~MW.
+However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
+The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
+The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door that was located between the enclosed porch and the hallway.
+After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed and the steel faces of the door failed and collapsed inward.
+The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
 The temperature of the gases that flowed into the hallway at face height exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
 
-Unfortunately a captain and firefighter were advancing a hose line in the hallway at the time of the failure of the door.
+Unfortunately a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
 The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday, the captain was rescued from the structure but later succumbed to his injuries.
+After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.
 
-\chapter{Acknowledgements}
+\chapter{Acknowledgments}
 The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck.
-The authors would also like to thank John Culbertson of Central Valley Fire District, MT for his assistance in compiling Table~\ref{tab:lodd}.
+The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}.
 Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption {Dimensioned drawing of 1$^{st}$ floor. The measurements are accurate to within 15 cm (6 in).}
+\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15 cm (6 in).}
 \label{fig:first_floor}
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption {Dimensioned drawing of 2$^{nd}$ floor. The measurements are accurate to within 15 cm (6 in).}
+\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15 cm (6 in).}
 \label{fig:second_floor}

### 2014-07-27 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago Report: Minor edit
Chicago: minor edit to report

@@
 Incident Time  &  Fire Behavior / Fireground Operation  \\
-(hh:mm:ss)     &                                        \\
+{[hh:mm:ss]}   &                                        \\
 \midrule
@@
 
-While we had to estimate the time at which the door failed, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
+While the food failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15 cm (6 in).}
+\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:first_floor}
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15 cm (6 in).}
+\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:second_floor}

### 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago report: Fix typo

@@
 
-While the food failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
+While the door failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.

### 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Address some edits from reviewer

@@
 
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
 \headerB{
 Simulation of an Attic Fire \\
-in a Wood Frame Residential Structure \\
-Chicago, IL \\
+in a Wood Frame Residential \\
+Structure - Chicago, IL \\
+}
+
+\normalsize
+
+\headerC{
+{
+\flushright{
+Craig G. Weinschenk \\
+Daniel Madrzykowski \\
+Kristopher J. Overholt \\
+
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\endgroup
+}
+
+\vfill
+
+\flushright{
+
+\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+}
+}
+}
+
+\end{minipage}
+
+\newpage
+
+\frontmatter
+
+\pagenumbering{roman}
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
+\headerB{
+Simulation of an Attic Fire \\
+in a Wood Frame Residential \\
+Structure - Chicago, IL \\
 }
@@
 {\em Fire Research Division \\
-Engineering Laboratory \\
-Gaithersburg, Maryland, USA} \\ }
-}
+Engineering Laboratory} \\
 
-\flushright{\today \\
-}
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
+
+\vspace*{2\baselineskip}
+
+August 2014}}
 
@@
 
-\flushright{
-\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }
+
+\titlesigs
+
+\end{minipage}
+
+\newpage
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
+document in order to describe an experimental procedure or concept adequately. \\
+Such identification is not intended to imply recommendation or endorsement by the \\
+National Institute of Standards and Technology, nor is it intended to imply that the \\
+entities, materials, or equipment are necessarily the best available for the purpose. \\
 }
 
-\titlesigs
+\vspace{3in}
+
+\large
+\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
+% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+CODEN: NTNOEF }
+
+\vfill
+
+\hspace{1in}
 
@@
 
+\chapter*{\centering Abstract}
+\addcontentsline{toc}{chapter}{Abstract}
+The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain.
+The inputs for the FDS simulations are documented in this report.
+The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
+This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas.
+The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
+After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward.
+The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
+The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at face height.
+Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
+The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.
+
 \chapter{Introduction}
 Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Cook_County,Grosshandler:Station,Bryner:Charleston,barowy:texas}.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
 The objective of all of these studies has been to improve the safety of fire fighters.
 
-On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago firefighter.
+On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain.
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
@@
 The IC made entry through the front door to the stairwell to survey the interior of the 2\textsuperscript{nd} floor.
-He noticed only a light haze throughout and glow around the Sector 3 door to the covered porch.
+He noticed only a light haze throughout and glow around the [rear] door to the covered porch.
 The IC came back to the front door and met the E123 captain and a firefighter.
-They had stretched a horseshoe load which is 100 feet of 2\sfrac{1}{2}-inch, a gated wye, and 150 feet of 1\sfrac{3}{4}-inch hoseline to go to the 2\textsuperscript{nd} floor, which is a standard department hose lay for this type occupancy.
+They had stretched a [hose] load which is 100 feet of 2\sfrac{1}{2}-inch, a gated wye, and 150 feet of 1\sfrac{3}{4}-inch hoseline to go to the 2\textsuperscript{nd} floor, which is a standard department hose lay for this type occupancy.
 At 1720 hours, E49, T33, and TL39 arrived on scene.
@@
 The IC made entry to the 1\textsuperscript{st} floor apartment and worked his way to [the rear of the structure].
-He opened the back door to the covered porch and noticed heavy fire in the covered porch and rear stairwell area.
+He opened the [interior door opening into the covered porch on the rear of the house] and noticed heavy fire in the covered porch and rear stairwell area.
 At 1721 hours, the [E123 captain] and firefighter were on the 2\textsuperscript{nd} floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
@@
 \centering
-\captionof{table}{Abridged NISOH approximate fire event timeline}\label{tab:fire_info}
+\captionof{table}{Abridged NOISH approximate fire event timeline}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~(\ref{fig:simp_geom}).
+One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~(\ref{fig:simp_geom}).
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
@@
 %Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%\begin{figure}[h!]
+%\begin{figure}[!ht]
 %\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
@@
 \centering
-\captionof{table}{Timeline of Ventilation Changes in the Simulation}\label{tab:vents}
+\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
 \begin{tabular}{cccll}
@@
 \centering
-\captionof{table}{Relevant Modeling Input Parameters}\label{tab:mod_param}
+\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
 \begin{tabular}{lll}
@@
 \centering
-\captionof{table}{Fire Incident and Simulation Event Timeline}\label{tab:firesim}
+\captionof{table}{Fire incident and simulation event timeline}\label{tab:firesim}
 \begin{tabular}{ccl}
@@
 
-In Fig.~(\ref{fig:hrr}), the solid line represents the baseline FDS simulation (this represents the on-scene conditions).
-The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach on the left-side of the structure does not occur.
+In Fig.~(\ref{fig:hrr}), the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
+The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur.
 The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS.
@@
 Figure~(\ref{fig:pres_159s}) shows the pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa at the ceiling.
+On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa (0.00145~psi) at the ceiling.
 Gases at an elevated pressure will always move towards a region of lower pressure.
@@
 As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
-Note that the conditions in the attic do not appear to be influenced.
+Note that the conditions in the attic do not appear to change.
 \begin{figure}[!ht]
@@
 
-As shown in Fig.~(\ref{fig:temp_175s}), 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) from the floor through the interior hallway and are flowing into the kitchen (recall the layout from Fig.~(\ref{fig:simp_geom})).
+As shown in Fig.~(\ref{fig:temp_175s}), 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
 
@@
 By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) and pressures greater than 5~Pa were present on the porch side of the steel door at the rear of the structure.
+Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) and pressures greater than 5~Pa were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
 Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
 Figure~(\ref{fig:chicago_doorfold}) shows the state of the rear door after the fire.
-Note the large crease in the door just above the knob.
+Note the large crease in the steel face of the door just above the knob.
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
@@
 
-Recent experiments conducted by NIST revealed similar post-fire states after doors were exposed to fires.
+Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
 Figure~(\ref{fig:SC_doorfold}) shows doors from two different residential fire experiments in different stages of degradation.
@@
 
-While the door failure time needed to be estimated, the important detail is that after the door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
+After the interior door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
 This resulted in a rapid change in the conditions within the flow path.
@@
 
-Prior to the door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}).
+Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}).
 The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
-Five seconds after the door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}).
+Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}).
 Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}).
@@
 These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \centering
@@
 
-In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in a lethal exposure to fire fighters.
+In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in lethal conditions.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the fire fighters faced on the fire ground.
@@
 \centering
-\captionof{table}{Flow path related LODD/LODI Incidents}\label{tab:lodd}
+\captionof{table}{Flow path related LODD/LODI incidents}\label{tab:lodd}
 \begin{tabular}{lll}
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death of a firefighter.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death of a fire captain.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.

### 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits throughout

@@
          & \\[.25cm] 
-17:21:00 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
-17:21:30 & 1st floor exterior porch door opened. \\[.25cm]
+17:21:00 & E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
+17:21:30 & First floor exterior porch door opened. \\[.25cm]
 \multirow{2}{*}{17:23:00}    & \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
@@
 \end{tabular*}
-\caption[Plan view of 1st (top) and 2nd (bottom) floor of structure.]{Plan view of 1st (top) and 2nd (bottom) floor of structure.
+\caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
 Stairs and key rooms are identified using measurements collected by NIST.}
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption[Front-right side of the structure within the computational domain (with multiple meshes).]{Front-right side of the structure within the computational domain (with multiple meshes).
+\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
 Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
@@
          & 55 & Ventilation through wall penetration on left side of structure. \\[.25cm] 
-17:21:00 & 100 & E123 captain and firefighter on 2nd floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
-\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{1st floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
+17:21:00 & 100 & E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
+\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
         &  & \\[.25cm]
@@
 \includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-\caption[HRR versus time from FDS simulations of the West 50th St.
-fire.]{HRR versus time from FDS simulations of the West 50th St.
-fire.
-The first vertical line indicates when the back door failed, and the second vertical line indicates when the interior hallway door failed.}
+\caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
+The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
 \label{fig:hrr}
@@
 Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
-High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the 1st floor.
+High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
 Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}).
@@
 \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-\caption{Flow path on the second floor after the interior door failure.}
+\caption{Flow path on the second floor after interior door failure.}
 \label{fig:flowpath_1}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 1~s prior to door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
+{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_159}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 5~s after door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 5~s after interior door failure.]
+{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_165}
@@
 \input{../Scripts/colorbar_metric}
-\caption{Temperature contours on the second floor, 60~s after door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 60~s after interior door failure.]
+{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
 \label{fig:temp_top_220}
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption[Dimensioned drawing of 1st floor.]{Dimensioned drawing of 1st floor. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:first_floor}
@@
 \includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption[Dimensioned drawing of 2nd floor.]{Dimensioned drawing of 2nd floor. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:second_floor}

### 2014-07-28 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Reports/Docs: Change font size to 12 pt
Spartanburg 2014: Add appropriate plots to appendix per test; update test times

@@
 
-\section{286 College}
-
-\subsection{Test 1, Living room fire with sprinkler}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
-\caption{286 College, Test 1, TC\_A3}
-\label{fig:286_College_Test_1_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
-\caption{286 College, Test 1, TC\_A4}
-\label{fig:286_College_Test_1_TC_A4}
-\end{figure}
-
-\clearpage
-
-\subsection{Test 2, Garage fire, exterior attack}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
-\caption{286 College, Test 2, TC\_A1}
-\label{fig:286_College_Test_2_TC_A1}
-\end{figure}
-
-\clearpage
-
-\subsection{Test 3, Living room fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
-\caption{286 College, Test 3, TC\_A1}
-\label{fig:286_College_Test_3_TC_A1}
-\end{figure}
-
-\clearpage
-
-\section{489 N. Forest}
-
-\subsection{Test 1, Living room fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
-\caption{489 N. Forest, Test 1, TC\_A1}
-\label{fig:489_N_Forest_Test_1_TC_A1}
-\end{figure}
-
-\subsection{Test 2, Second floor bedroom fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A1}
-\caption{489 N. Forest, Test 2, TC\_A1}
-\label{fig:489_N_Forest_Test_2_TC_A1}
-\end{figure}
-
-\clearpage
-
-\section{302 College}
-
-\subsection{Test 1, Bedroom fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
-\caption{302 College, Test 1, TC\_A1}
-\label{fig:302_College_Test_1_TC_A1}
-\end{figure}
-
-\subsection{Test 2, Living room fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
-\caption{302 College, Test 2, TC\_A1}
-\label{fig:302_College_Test_2_TC_A1}
-\end{figure}
-
-\subsection{Test 3, Bathroom and attic fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
-\caption{302 College, Test 3, TC\_A1}
-\label{fig:302_College_Test_3_TC_A1}
-\end{figure}
-
-\clearpage
-
-\section{305 Manning}
-
-\subsection{Test 1, Garage fire, interior attack}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
-\caption{305 Manning, Test 1, TC\_A1}
-\label{fig:305_Manning_Test_1_TC_A1}
-\end{figure}
-
-\subsection{Test 2, Bedroom fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
-\caption{305 Manning, Test 2, TC\_A1}
-\label{fig:305_Manning_Test_2_TC_A1}
-\end{figure}
-
-\subsection{Test 3, Complete burndown}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_TC_A1}
-\caption{305 Manning, Test 3, TC\_A1}
-\label{fig:305_Manning_Test_3_TC_A1}
-\end{figure}
-
-\clearpage
-
-\section{289 Manning}
-
-\subsection{Test 1, Basement fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
-\caption{286 College, Test 1, TC\_A1}
-\label{fig:289_Manning_Test_1_TC_A1}
-\end{figure}
-
-\subsection{Test 2, Deck and attic fire}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A1}
-\caption{286 College, Test 2, TC\_A1}
-\label{fig:289_Manning_Test_2_TC_A1}
-\end{figure}
-
 \clearpage
@@
 
-\chapter{Placeholder}
+\chapter{All Tests}
 
-Placeholder
+\section{286 College}
+
+\subsection{Test 1, Living room fire with sprinkler}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
+\caption{286 College, Test 1, Temperature TC\_A3}
+\label{fig:286_College_Test_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
+\caption{286 College, Test 1, Temperature TC\_A4}
+\label{fig:286_College_Test_1_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_S_1}
+\caption{286 College, Test 1, Temperature TC\_S\_1}
+\label{fig:286_College_Test_1_TC_S_1}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 2, Garage fire, exterior attack}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
+\caption{286 College, Test 2, Temperature TC\_A1}
+\label{fig:286_College_Test_2_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A2}
+\caption{286 College, Test 2, Temperature TC\_A2}
+\label{fig:286_College_Test_2_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A6}
+\caption{286 College, Test 2, Temperature TC\_A6}
+\label{fig:286_College_Test_2_TC_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A7}
+\caption{286 College, Test 2, Temperature TC\_A7}
+\label{fig:286_College_Test_2_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A8}
+\caption{286 College, Test 2, Temperature TC\_A8}
+\label{fig:286_College_Test_2_TC_A8}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_HF}
+\caption{286 College, Test 2, Heat Flux}
+\label{fig:286_College_Test_2_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_P_S_1}
+\caption{286 College, Test 2, Pressure}
+\label{fig:286_College_Test_2_P_S_1}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 3, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
+\caption{286 College, Test 3, Temperature TC\_A1}
+\label{fig:286_College_Test_3_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A4}
+\caption{286 College, Test 3, Temperature TC\_A4}
+\label{fig:286_College_Test_3_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A5}
+\caption{286 College, Test 3, Temperature TC\_A5}
+\label{fig:286_College_Test_3_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_HF}
+\caption{286 College, Test 3, Heat Flux}
+\label{fig:286_College_Test_3_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_P_S_1}
+\caption{286 College, Test 3, Pressure}
+\label{fig:286_College_Test_3_P_S_1}
+\end{figure}
+
+\clearpage
+
+\section{489 N. Forest}
+
+\subsection{Test 1, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
+\caption{489 N. Forest, Test 1, Temperature TC\_A1}
+\label{fig:489_N_Forest_Test_1_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A2}
+\caption{489 N. Forest, Test 1, Temperature TC\_A2}
+\label{fig:489_N_Forest_Test_1_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A3}
+\caption{489 N. Forest, Test 1, Temperature TC\_A3}
+\label{fig:489_N_Forest_Test_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_S_1}
+\caption{489 N. Forest, Test 1, Temperature TC\_S\_1}
+\label{fig:489_N_Forest_Test_1_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_HF}
+\caption{489 N. Forest, Test 1, Heat Flux}
+\label{fig:489_N_Forest_Test_1_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_P_S_1}
+\caption{489 N. Forest, Test 1, Pressure}
+\label{fig:489_N_Forest_Test_1_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_GAS}
+\caption{489 N. Forest, Test 1, Gas Concentration}
+\label{fig:489_N_Forest_Test_1_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 2, Second floor bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A4}
+\caption{489 N. Forest, Test 2, Temperature TC\_A4}
+\label{fig:489_N_Forest_Test_2_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A5}
+\caption{489 N. Forest, Test 2, Temperature TC\_A5}
+\label{fig:489_N_Forest_Test_2_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A6}
+\caption{489 N. Forest, Test 2, Temperature TC\_A6}
+\label{fig:489_N_Forest_Test_2_TC_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A7}
+\caption{489 N. Forest, Test 2, Temperature TC\_A7}
+\label{fig:489_N_Forest_Test_2_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_S_1}
+\caption{489 N. Forest, Test 2, Temperature TC\_S\_1}
+\label{fig:489_N_Forest_Test_2_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_HF}
+\caption{489 N. Forest, Test 2, Heat Flux}
+\label{fig:489_N_Forest_Test_2_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_P_S_1}
+\caption{489 N. Forest, Test 2, Pressure}
+\label{fig:489_N_Forest_Test_2_P_S_1}
+\end{figure}
+
+\clearpage
+
+\section{302 College}
+
+\subsection{Test 1, Bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
+\caption{302 College, Test 1, Temperature TC\_A1}
+\label{fig:302_College_Test_1_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A3}
+\caption{302 College, Test 1, Temperature TC\_A3}
+\label{fig:302_College_Test_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A4}
+\caption{302 College, Test 1, Temperature TC\_A4}
+\label{fig:302_College_Test_1_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A5}
+\caption{302 College, Test 1, Temperature TC\_A5}
+\label{fig:302_College_Test_1_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_S_1}
+\caption{302 College, Test 1, Temperature TC\_S\_1}
+\label{fig:302_College_Test_1_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_HF}
+\caption{302 College, Test 1, Heat Flux}
+\label{fig:302_College_Test_1_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_P_S_1}
+\caption{302 College, Test 1, Pressure}
+\label{fig:302_College_Test_1_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_GAS}
+\caption{302 College, Test 1, Gas Concentration}
+\label{fig:302_College_Test_1_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 2, Living room fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
+\caption{302 College, Test 2, Temperature TC\_A1}
+\label{fig:302_College_Test_2_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A3}
+\caption{302 College, Test 2, Temperature TC\_A3}
+\label{fig:302_College_Test_2_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A4}
+\caption{302 College, Test 2, Temperature TC\_A4}
+\label{fig:302_College_Test_2_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A5}
+\caption{302 College, Test 2, Temperature TC\_A5}
+\label{fig:302_College_Test_2_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_S_1}
+\caption{302 College, Test 2, Temperature TC\_S\_1}
+\label{fig:302_College_Test_2_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_HF}
+\caption{302 College, Test 2, Heat Flux}
+\label{fig:302_College_Test_2_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_P_S_1}
+\caption{302 College, Test 2, Pressure}
+\label{fig:302_College_Test_2_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_GAS}
+\caption{302 College, Test 2, Gas Concentration}
+\label{fig:302_College_Test_2_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 3, Bathroom and attic fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
+\caption{302 College, Test 3, Temperature TC\_A1}
+\label{fig:302_College_Test_3_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A2}
+\caption{302 College, Test 3, Temperature TC\_A2}
+\label{fig:302_College_Test_3_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A3}
+\caption{302 College, Test 3, Temperature TC\_A3}
+\label{fig:302_College_Test_3_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A4}
+\caption{302 College, Test 3, Temperature TC\_A4}
+\label{fig:302_College_Test_3_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A5}
+\caption{302 College, Test 3, Temperature TC\_A5}
+\label{fig:302_College_Test_3_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_S_1}
+\caption{302 College, Test 3, Temperature TC\_S\_1}
+\label{fig:302_College_Test_3_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_HF}
+\caption{302 College, Test 3, Heat Flux}
+\label{fig:302_College_Test_3_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_P_S_1}
+\caption{302 College, Test 3, Pressure}
+\label{fig:302_College_Test_3_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_GAS}
+\caption{302 College, Test 3, Gas Concentration}
+\label{fig:302_College_Test_3_GAS}
+\end{figure}
+
+\clearpage
+
+\section{305 Manning}
+
+\subsection{Test 1, Garage fire, interior attack}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
+\caption{305 Manning, Test 1, Temperature TC\_A1}
+\label{fig:305_Manning_Test_1_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A2}
+\caption{305 Manning, Test 1, Temperature TC\_A2}
+\label{fig:305_Manning_Test_1_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A3}
+\caption{305 Manning, Test 1, Temperature TC\_A3}
+\label{fig:305_Manning_Test_1_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A4}
+\caption{305 Manning, Test 1, Temperature TC\_A4}
+\label{fig:305_Manning_Test_1_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A5}
+\caption{305 Manning, Test 1, Temperature TC\_A5}
+\label{fig:305_Manning_Test_1_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A6}
+\caption{305 Manning, Test 1, Temperature TC\_A6}
+\label{fig:305_Manning_Test_1_TC_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A7}
+\caption{305 Manning, Test 1, Temperature TC\_A7}
+\label{fig:305_Manning_Test_1_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_HF}
+\caption{305 Manning, Test 1, Heat Flux}
+\label{fig:305_Manning_Test_1_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_P_S_1}
+\caption{305 Manning, Test 1, Pressure}
+\label{fig:305_Manning_Test_1_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_GAS}
+\caption{305 Manning, Test 1, Gas Concentration}
+\label{fig:305_Manning_Test_1_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 2, Bedroom fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
+\caption{305 Manning, Test 2, Temperature TC\_A1}
+\label{fig:305_Manning_Test_2_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A2}
+\caption{305 Manning, Test 2, Temperature TC\_A2}
+\label{fig:305_Manning_Test_2_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A3}
+\caption{305 Manning, Test 2, Temperature TC\_A3}
+\label{fig:305_Manning_Test_2_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A4}
+\caption{305 Manning, Test 2, Temperature TC\_A4}
+\label{fig:305_Manning_Test_2_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A5}
+\caption{305 Manning, Test 2, Temperature TC\_A5}
+\label{fig:305_Manning_Test_2_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A6}
+\caption{305 Manning, Test 2, Temperature TC\_A6}
+\label{fig:305_Manning_Test_2_TC_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A7}
+\caption{305 Manning, Test 2, Temperature TC\_A7}
+\label{fig:305_Manning_Test_2_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_S_1}
+\caption{305 Manning, Test 2, Temperature TC\_S\_1}
+\label{fig:305_Manning_Test_2_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_HF}
+\caption{305 Manning, Test 2, Heat Flux}
+\label{fig:305_Manning_Test_2_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_P_S_1}
+\caption{305 Manning, Test 2, Pressure}
+\label{fig:305_Manning_Test_2_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_GAS}
+\caption{305 Manning, Test 2, Gas Concentration}
+\label{fig:305_Manning_Test_2_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 3, Complete burndown}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
+\caption{305 Manning, Test 3, Heat Flux}
+\label{fig:305_Manning_Test_3_HF}
+\end{figure}
+
+\clearpage
+
+\section{289 Manning}
+
+\subsection{Test 1, Basement fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
+\caption{286 College, Test 1, Temperature TC\_A1}
+\label{fig:289_Manning_Test_1_TC_A1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A4}
+\caption{286 College, Test 1, Temperature TC\_A4}
+\label{fig:289_Manning_Test_1_TC_A4}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A5}
+\caption{286 College, Test 1, Temperature TC\_A5}
+\label{fig:289_Manning_Test_1_TC_A5}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A6}
+\caption{286 College, Test 1, Temperature TC\_A6}
+\label{fig:289_Manning_Test_1_TC_A6}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A7}
+\caption{286 College, Test 1, Temperature TC\_A7}
+\label{fig:289_Manning_Test_1_TC_A7}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_S_1}
+\caption{286 College, Test 1, Temperature TC\_S\_1}
+\label{fig:289_Manning_Test_1_TC_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_HF}
+\caption{286 College, Test 1, Heat Flux}
+\label{fig:289_Manning_Test_1_HF}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_P_S_1}
+\caption{286 College, Test 1, Pressure}
+\label{fig:289_Manning_Test_1_P_S_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_GAS}
+\caption{286 College, Test 1, Gas Concentration}
+\label{fig:289_Manning_Test_1_GAS}
+\end{figure}
+
+\clearpage
+
+\subsection{Test 2, Deck and attic fire}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A2}
+\caption{286 College, Test 2, Temperature TC\_A2}
+\label{fig:289_Manning_Test_2_TC_A2}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A3}
+\caption{286 College, Test 2, Temperature TC\_A3}
+\label{fig:289_Manning_Test_2_TC_A3}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_HF}
+\caption{286 College, Test 2, Heat Flux}
+\label{fig:289_Manning_Test_2_HF}
+\end{figure}
 

### 2014-07-28 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Documentation/Reports: Minor style edit
Spartanburg 2014: Add fuel data

@@
 
-\subsection{Construction}
+\section{Construction}
 \label{sec:Construction}
@@
 \section{Fuel Load}
+\label{sec:Fuel_Load}
+
+\begin{sidewaystable}[!ht]
+\centering
+\caption{Fuel masses}
+\begin{tabular}{llcc}
+\hline\noalign{\smallskip}
+Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
+%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
+%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
+%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
+% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
+%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
+%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2 kg       \\
+3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
+2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
+3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
+Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
+2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
+2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
+3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
+3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
+3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
+Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
+3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
+Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
+\noalign{\smallskip}\hline
+\end{tabular}
+\label{tab:Fuel_Masses}
+\end{sidewaystable}
 
@@
 
-\chapter{Acknowledgements}
-\label{chap:Acknowledgements}
+\chapter{Acknowledgments}
+\label{chap:Acknowledgments}
 

### 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
Documents: Edit to frontmatter
Chicago: update report, images, and input files based on comments

@@
 
+\newpage
+\hspace{5in}
 \newpage
@@
 While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
-In this study, the material properties of gypsum~\cite{Drysdale:1} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+In this study, the material properties of gypsum~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
 The following lines define these materials in the FDS input file:
@@
 &MATL ID = 'GYPSUM'
-    FYI = 'Drysdale' 
-    CONDUCTIVITY = 0.17
-    SPECIFIC_HEAT = 1.09
-    DENSITY = 930. /
+    FYI = 'Wakili - Journal of Fire Sciences 2007' 
+    CONDUCTIVITY = 0.28
+    SPECIFIC_HEAT = 1.0
+    DENSITY = 810. /
 

### 2014-07-29 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg 2014: Minor edit
Spartanburg: Add plan drawings of instrumentation

@@
 
+% Extra packages
+\usepackage{xfrac}
+
 \begin{document}
@@
 
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
 \headerB{
-Spartanburg 2014
+Spartanburg Fire Tests \\
+2013--2014 \\
+}
+
+\normalsize
+
+\headerC{
+{
+\flushright{
+Daniel Madrzykowski \\
+Kristopher J. Overholt \\
+Craig G. Weinschenk \\
+
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\endgroup
+}
+
+\vfill
+
+\flushright{
+
+\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+}
+}
+}
+
+\end{minipage}
+
+\newpage
+\hspace{5in}
+\newpage
+
+\frontmatter
+
+\pagenumbering{roman}
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
+\headerB{
+Spartanburg Fire Tests \\
+2013--2014 \\
 }
@@
 Daniel Madrzykowski \\
+Kristopher J. Overholt \\
 Craig G. Weinschenk \\
-Kristopher J. Overholt \\
 {\em Fire Research Division \\
-Engineering Laboratory \\
-Gaithersburg, Maryland, USA} \\ }
-}
+Engineering Laboratory} \\
 
-\flushright{\today \\
-}
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
+
+\vspace*{2\baselineskip}
+
+August 2014}}
 
@@
 
+\section{Instrumentation}
+\label{sec:Instrumentation}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/286_College}
+\caption{Instrumentation, 286 College}
+\label{fig:Instrumentation_286_College}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_1st_Floor}
+\caption{Instrumentation, 489 N. Forest, first floor}
+\label{fig:Instrumentation_489_N_Forest_1st_Floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_2nd_Floor}
+\caption{Instrumentation, 489 N. Forest, second floor}
+\label{fig:Instrumentation_489_N_Forest_2nd_Floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/302_College}
+\caption{Instrumentation, 302 College}
+\label{fig:Instrumentation_302_College}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/305_Manning}
+\caption{Instrumentation, 305 Manning}
+\label{fig:Instrumentation_305_Manning}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
+\caption{Instrumentation, 305 Manning, first floor}
+\label{fig:Instrumentation_305_Manning_1st_Floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_2nd_Floor}
+\caption{Instrumentation, 305 Manning, second floor}
+\label{fig:Instrumentation_305_Manning_2nd_Floor}
+\end{figure}
+
+\clearpage
+
 \section{Fuel Load}
@@
 %   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
-%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2 kg       \\
+%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
 3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
@@
 
-\clearpage
+% \clearpage
 
-\subsection{Test 3, Complete burndown}
+% Heat flux measurements are large negative values
 
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
-\caption{305 Manning, Test 3, Heat Flux}
-\label{fig:305_Manning_Test_3_HF}
-\end{figure}
+% \subsection{Test 3, Complete burndown}
+
+% \begin{figure}[!ht]
+% \includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
+% \caption{305 Manning, Test 3, Heat Flux}
+% \label{fig:305_Manning_Test_3_HF}
+% \end{figure}
 

### 2014-07-29 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update report, images, and bib file

--- 2014-07-28 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1838}
 \end{flushright}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}
 \endgroup
@@
 \newpage
+\hspace{5in}
+\newpage
 
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1838 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 The IC made entry to the 1\textsuperscript{st} floor apartment and worked his way to [the rear of the structure].
-He opened the [interior door opening into the covered porch on the rear of the house] and noticed heavy fire in the covered porch and rear stairwell area.
+He opened the [interior door opening into the rear foyer on the backside of the house] and noticed heavy fire in the covered porch and rear stairwell area.
 At 1721 hours, the [E123 captain] and firefighter were on the 2\textsuperscript{nd} floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
@@
 He stated that he noticed fire light-up in the stairwell.
-He kicked in the locked door to the first floor apartment, preceded to walk in, saw no fire then backed out.
+He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], preceded to walk in, saw no fire then backed out.
 
@@
 While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
-In this study, the material properties of gypsum~\cite{Drysdale:1} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
 The following lines define these materials in the FDS input file:
@@
 \begin{lstlisting}
-&MATL ID = 'GYPSUM'
-    FYI = 'Drysdale' 
-    CONDUCTIVITY = 0.17
-    SPECIFIC_HEAT = 1.09
-    DENSITY = 930. /
+&MATL ID = 'GYPSUM BOARD'
+    FYI = 'Wakili - Journal of Fire Sciences 2007' 
+    CONDUCTIVITY = 0.28
+    SPECIFIC_HEAT = 1.0
+    DENSITY = 810. /
 
-&MATL ID = 'WOOD_MAT'
+&MATL ID = 'WOOD MAT'
     FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
@@
 An unknown in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
-While this time may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
+The second estimate was the area of failure.
+The bottom hinge from the door appeared to be closed throughout the fire due to lack of fire damage and soot on the interior faces the hinge and remaining wood (Fig.~(\ref{fig:door_frame})).
+It appears that the door collapsed and failed partially open.
+In the simulations only the upper portion of the door was assumed to fail.
+While this time and area may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
+\caption[Post incident image of rear porch doorframe.]{A post incident image of the second floor porch doorframe that failed taken from inside the structure looking toward the porch.
+Note that the hinge is still in take and there is under burned, ``clean'' wood at along the bottom portion of the frame.}
+\label{fig:door_frame}
+\end{figure}
 
@@
 \centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_grid}
-\caption{Front side of the structure with 10 cm computational mesh.}
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
+   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
+\end{tabular*}
+\caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
 \label{fig:geom_grid}
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,chicago}
+\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
 

### 2014-07-29 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits

@@
 Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+% http://dx.doi.org/10.6028/NIST.TN.1838 \\
 CODEN: NTNOEF }
@@
 The IC made entry to the 1\textsuperscript{st} floor apartment and worked his way to [the rear of the structure].
-He opened the [interior door opening into the rear foyer on the backside of the house] and noticed heavy fire in the covered porch and rear stairwell area.
+He opened the [interior door opening into the rear foyer on the back side of the house] and noticed heavy fire in the covered porch and rear stairwell area.
 At 1721 hours, the [E123 captain] and firefighter were on the 2\textsuperscript{nd} floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
@@
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
-An unknown in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
-The second estimate was the area of failure.
-The bottom hinge from the door appeared to be closed throughout the fire due to lack of fire damage and soot on the interior faces the hinge and remaining wood (Fig.~(\ref{fig:door_frame})).
+
+An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
+The area of failure was also estimated based on the following observations.
+The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~(\ref{fig:door_frame}).
 It appears that the door collapsed and failed partially open.
-In the simulations only the upper portion of the door was assumed to fail.
+In the simulations, only the upper portion of the door was assumed to fail.
 While this time and area may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
@@
 \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
-\caption[Post incident image of rear porch doorframe.]{A post incident image of the second floor porch doorframe that failed taken from inside the structure looking toward the porch.
-Note that the hinge is still in take and there is under burned, ``clean'' wood at along the bottom portion of the frame.}
+\caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
+Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
 \label{fig:door_frame}

### 2014-07-30 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update report based on comments

@@
 \centering
-\captionof{table}{Abridged NOISH approximate fire event timeline}\label{tab:fire_info}
+\captionof{table}{Abridged NIOSH approximate fire event timeline}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board (OSB).
+The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board.
 
 Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) found from the SFPE Handbook~\cite{SFPE:Tewarson}.
-A balanced chemical reaction for wood oxidation can written as:
+A balanced chemical reaction for wood combustion can written as:
 
@@
 This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
-While FDS provides users to the option to use a more complex finite-rate combustion mechanism, we do not have sufficient evidence to justify deviating from the default specifications.
+While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
 
@@
 &SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE', TAU_Q=10 /
-&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 2 m^2
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 1.5 m^2
+&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 
+&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 
+&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 
 &DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
@@
 
-\section{Mesh}
+\section{Numerical Mesh}
 \label{mesh}
@@
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced reasonable results.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were judged to be adequate for engineering calculations.
 The grid resolution used in this model is within typical engineering $D^*/\dx$ values.
@@
 At a grid resolution of 10~cm (3.9~in), this would result in 2.4 million computational cells.
-To make the simulation time more reasonable, the domain was divided into 16 equal meshes (each containing 150 thousand grid cells) to be processed in parallel.
+To make the simulation time more reasonable (a run time of approximately one and a half days), the domain was divided into 16 equal meshes (each containing 150 thousand grid cells) to be processed in parallel.
 Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 \multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
-         & \\[.25cm]
-         &  \multirow{2}{*} {0} &  \multirow{2}{*}{\parbox{9cm} {Simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
+         & & \\[.25cm]
+\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {Simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
+         & & \\[0.25cm]
          & & \\[0.25cm]
@@
          & & \\[.25cm]  
-         & 45 & Ventilation through wall penetration on rear of structure. \\[.25cm] 
-         & 55 & Ventilation through wall penetration on left side of structure. \\[.25cm] 
-17:21:00 & 100 & E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline. \\[.25cm]
-\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{9cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
+\multirow{2}{*}{}  & \multirow{2}{*}{45} & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on rear of structure.}} \\
+          & & \\[.25cm] 
+\multirow{2}{*}{}  & \multirow{2}{*}{55}  & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on left side of structure.}} \\ 
+          & & \\[.25cm] 
+\multirow{2}{*}{17:21:00} & \multirow{2}{*}{100} & \multirow{2}{*}{\parbox{8cm}{E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.}} \\
+         &  & \\[.25cm]
+\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{8cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
         &  & \\[.25cm]
@@
         & 160 & Top of interior door fails in FDS model. \\[.25cm] 
-\multirow{2}{*}{17:23:00}    & \multirow{2}{*}{220} & \multirow{2}{*}{\parbox{9cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
+\multirow{3}{*}{17:23:00}    & \multirow{3}{*}{220} & \multirow{3}{*}{\parbox{8cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
+         & & \\[.25cm]
          & & \\[.25cm]  
@@
 17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
-\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{9cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
+\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{8cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
          & &  \\[.25cm]

### 2014-07-30 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit

@@
 The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-At a grid resolution of 10~cm (3.9~in), this would result in 2.4 million computational cells.
-To make the simulation time more reasonable (a run time of approximately one and a half days), the domain was divided into 16 equal meshes (each containing 150 thousand grid cells) to be processed in parallel.
+At a grid resolution of 10~cm (3.9~in), this results in 2.4 million computational cells.
+The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
 Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes.

### 2014-07-31 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update from Werb comments

@@
 
-Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; {\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$) and soot ($y_{\mathrm{C}}=0.015 \; {\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$) found from the SFPE Handbook~\cite{SFPE:Tewarson}.
+Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) per kg of fuel consumed found from the SFPE Handbook~\cite{SFPE:Tewarson}.
 A balanced chemical reaction for wood combustion can written as:
@@
 
-To estimate the energy release rate per unit area (kW/m$^2$) of wood, we use work by Babrauskas and Grayson~\cite{babrauskas1990}.
+To estimate the energy release rate per unit area (kW/m$^2$) of wood, work by Babrauskas and Grayson~\cite{babrauskas1990} is used.
 Experiments were conducted in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials.} to determine the 5 minute average of HRRPUA\footnote{HRRPUA is the heat release rate per unit area.} (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
@@
 
-For the simulation in this study, we can estimate a measure of how well the flow field is resolved by using the non-dimensional expression $D^*/\dx$.
+For the simulation in this study, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$.
 Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
@@
 \multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
-                                   &  CO Yield: 0.004 \; ${\mathrm{kg_{CO}}/\mathrm{kg_{wood}}}$   & \\
-                                   &  Soot Yield: 0.015 \; ${\mathrm{kg_{C}}/\mathrm{kg_{wood}}}$  & \\
+                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
+                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
                                    &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
@@
                                    &  c$_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  &  k: 0.17 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   &  $\rho$: 930 \; kg/m$^3$                                      & \\ 
-                                   &  c$_{p}$: 1.09 \; \si{kJ/(kg.K)}                              & \\
+\multirow{3}{*}{Material: Gypsum}  &  k: 0.28 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
+                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
+                                   &  c$_{p}$: 1.0 \; \si{kJ/(kg.K)}                              & \\
 \bottomrule[1.25pt]
@@
 
+\newpage
+\begin{landscape}
+\centering
 \begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_velo_175}
+\includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
 \input{../Scripts/colorbar_std_velo}
@@
 \end{figure}
+\end{landscape}
+\newpage
 
@@
 By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) and pressures greater than 5~Pa were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
+Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
 Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
@@
 Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
-Therefore, for the analysis of the simulated exposure temperatures, we set the maximum visualized temperature to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
+Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
 This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.

### 2014-07-31 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits

@@
 
-Wood can be represented by the the following chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) per kg of fuel consumed found from the SFPE Handbook~\cite{SFPE:Tewarson}.
+Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$).
+The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the SFPE Handbook~\cite{SFPE:Tewarson}.
 A balanced chemical reaction for wood combustion can written as:
@@
 
-The value for the heat of combustion of wood used in this simulation was 16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the amount of energy per unit mass of the fuel.
@@
 The first section will address the results of the computational modeling as they relate to the interior hallways conditions.
-The second section will examine the the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
+The second section will examine the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
 

### 2014-08-04 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update
Chicago: Minor edit to units/symbols

@@
 TL \> Tower Ladder \\
+\end{tabbing}
+
+\chapter{List of Symbols}
+
+\begin{tabbing}
+\hspace{1.5in} \= \\
+ft \> foot \\
+m \> meter \\
+min \> minute \\
+Pa \> Pascal \\
+psi \> pound per square inch \\
+s \> second \\
+W \> Watt \\
+$k$ \> thermal conductivity \\
+$\rho$ \> density \\
+$c_{p}$ \> specific heat \\
 \end{tabbing}
@@
                                    &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    &  k: 0.12 \; \si{W/(m.K)})                                     & \multirow{3}{*}{Section~\ref{matl}} \\
+\multirow{3}{*}{Material: Wood}    &  $k$: 0.12 \; \si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
                                    &  $\rho$: 510 \; kg/m$^3$                                      & \\
-                                   &  c$_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  &  k: 0.28 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
+                                   &  $c_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
+\multirow{3}{*}{Material: Gypsum}  &  $k$: 0.28 \; \si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
                                    &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
-                                   &  c$_{p}$: 1.0 \; \si{kJ/(kg.K)}                              & \\
+                                   &  $c_{p}$: 1.0 \; \si{kJ/(kg.K)}                               & \\
 \bottomrule[1.25pt]

### 2014-08-04 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit to references
Chicago: Minor edit to acknowledgments

@@
 
-A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{designation2003c}.
+A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
 While firefighters wear protective gear, gear only offers a finite amount of protection.
@@
 The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}.
-Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
+Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.
 

### 2014-08-04 Studies/2011_San_Francisco/Report/SF_Fire.tex
San Francisco: Initial commit of report

--- 2014-07-31 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note 1838}
+\bf{NIST Technical Note XXXX}
 \end{flushright}
@@
 \headerB{
-Simulation of an Attic Fire \\
+Simulation of a Basement Fire \\
 in a Wood Frame Residential \\
-Structure - Chicago, IL \\
+Structure - San Francisco, CA \\
 }
@@
 \flushright{
+Kristopher J. Overholt \\
+Daniel Madrzykowski \\
 Craig G. Weinschenk \\
-Daniel Madrzykowski \\
-Kristopher J. Overholt \\
 
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
 \endgroup
@@
 \flushright{
+Kristopher J. Overholt \\
+Daniel Madrzykowski \\
 Craig G. Weinschenk \\
-Daniel Madrzykowski \\
-Kristopher J. Overholt \\
 {\em Fire Research Division \\
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note 1838 \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.1838 \\
+\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
+% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
 CODEN: NTNOEF }
@@
 
+\chapter{List of Symbols}
+
+\begin{tabbing}
+\hspace{1.5in} \= \\
+MW \> Megawatt \\
+s \> second \\
+min \> minute \\
+m \> meter \\
+ft \> foot \\
+Pa \> Pascal \\
+psi \> pound per square inch \\
+k \> thermal  conductivity \\
+$\rho$ \> density \\
+c$_{p}$ \> specific heat \\
+\end{tabbing}
+
 \mainmatter
@@
 \addcontentsline{toc}{chapter}{Abstract}
-The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain.
+% The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2 story, single family structure in XXXX, that resulted in the death of XXXX.
 The inputs for the FDS simulations are documented in this report.
@@
 
-On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain.
+% On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain.
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
@@
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.0.0) simulations.
+This document describes the input and the results of the FDS (version 6.1.1) simulations.
 
@@
 
-\begin{figure}[!ht]
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-\includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
-\includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
-\end{tabular*}
-\caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
+% \begin{figure}[!ht]
+% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+% \includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
+% \includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
+% \end{tabular*}
+% \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
 Stairs and key rooms are identified using measurements collected by NIST.}
-\label{fig:simp_geom}
-\end{figure}
+% \label{fig:simp_geom}
+% \end{figure}
 
-\begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
-   \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
-\end{tabular*}
-\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
-\label{fig:alpha_ex}
-\end{figure}
-%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%\begin{figure}[!ht]
-%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-%\end{tabular*}
-%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-%\label{fig:smv_interior}
-%\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
+%    \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
+% \end{tabular*}
+% \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
+% \label{fig:alpha_ex}
+% \end{figure}
+
+%%%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
+%%%\begin{figure}[!ht]
+%%%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+%%%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
+%%%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
+%%%\end{tabular*}
+%%%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
+%%%\label{fig:smv_interior}
+%%%\end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
-\caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
+% \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
 Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
-\label{fig:door_frame}
-\end{figure}
+% \label{fig:door_frame}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
-   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
-\end{tabular*}
-\caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
-\label{fig:geom_grid}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+%    \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
+%    \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
+% \end{tabular*}
+% \caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
+% \label{fig:geom_grid}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
+% \caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
 Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
-\label{fig:mult_mesh}
-\end{figure}
+% \label{fig:mult_mesh}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-\caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
+% \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
 The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
-\label{fig:hrr}
-\end{figure}
+% \label{fig:hrr}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
-\caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
-\label{fig:smv_ext_fire}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
+% \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
+% \label{fig:smv_ext_fire}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
-\input{../Scripts/colorbar_metric_pres}
-\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.
+% \begin{figure}[!ht]
+% \includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
+% \input{../Scripts/colorbar_metric_pres}
+% \caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.
 Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
-\label{fig:pres_159s}
-\end{figure}
+% \label{fig:pres_159s}
+% \end{figure}
 
-\newpage
-\begin{landscape}
-\centering
-\begin{figure}[!ht]
-\includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
-\input{../Scripts/colorbar_std_velo}
-\input{../Scripts/colorbar_metric_velo}
-\caption{FDS simulated velocity vectors, 15~s after interior door failure.}
-\label{fig:velo_175s}
-\end{figure}
-\end{landscape}
-\newpage
+% \newpage
+% \begin{landscape}
+% \centering
+% \begin{figure}[!ht]
+% \includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
+% \input{../Scripts/colorbar_std_velo}
+% \input{../Scripts/colorbar_metric_velo}
+% \caption{FDS simulated velocity vectors, 15~s after interior door failure.}
+% \label{fig:velo_175s}
+% \end{figure}
+% \end{landscape}
+% \newpage
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
-\label{fig:temp_129s}
-\end{figure}
+% \begin{figure}[!ht]
+% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
+% \label{fig:temp_129s}
+% \end{figure}
 
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
-\label{fig:temp_159s}
-\end{figure}
+% \begin{figure}[!ht]
+% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
+% \label{fig:temp_159s}
+% \end{figure}
 
@@
 Note that the conditions in the attic do not appear to change.
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s after interior door failure.}
-\label{fig:temp_161s}
-\end{figure}
 
-\begin{figure}[!ht]
-\includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 15~s after the interior door failure.}
-\label{fig:temp_175s}
-\end{figure}
+% \begin{figure}[!ht]
+% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption{FDS simulated temperature contours, 1~s after interior door failure.}
+% \label{fig:temp_161s}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption{FDS simulated temperature contours, 15~s after the interior door failure.}
+% \label{fig:temp_175s}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
-\caption{Post-fire image of interior door.}
-\label{fig:chicago_doorfold}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
+% \caption{Post-fire image of interior door.}
+% \label{fig:chicago_doorfold}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-   \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
-   \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
-\end{tabular*}
-\caption{Post-experiment images of door failures.}
-\label{fig:SC_doorfold}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
+%    \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
+% \end{tabular*}
+% \caption{Post-experiment images of door failures.}
+% \label{fig:SC_doorfold}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-\caption{Flow path on the second floor after interior door failure.}
-\label{fig:flowpath_1}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
+% \caption{Flow path on the second floor after interior door failure.}
+% \label{fig:flowpath_1}
+% \end{figure}
 
@@
 These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
-{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
-\label{fig:temp_top_159}
-\end{figure}
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 5~s after interior door failure.]
-{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
-\label{fig:temp_top_165}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
+% {Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
+% \label{fig:temp_top_159}
+% \end{figure}
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
-\input{../Scripts/colorbar_std} 
-\input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 60~s after interior door failure.]
-{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
-\label{fig:temp_top_220}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption[Temperature contours on the second floor, 5~s after interior door failure.]
+% {Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
+% \label{fig:temp_top_165}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
+% \input{../Scripts/colorbar_std} 
+% \input{../Scripts/colorbar_metric}
+% \caption[Temperature contours on the second floor, 60~s after interior door failure.]
+% {Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
+% \label{fig:temp_top_220}
+% \end{figure}
 
@@
 \chapter{Acknowledgments}
-The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck.
+The authors would like to thank XXXX.
 The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}.
-Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of University of Illinois Urbana-Champagne for their assistance in creating the drawings of the structure.
+Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
 
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:first_floor}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
+% \caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
+% \label{fig:first_floor}
+% \end{figure}
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:second_floor}
-\end{figure}
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
+% \caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}
+% \label{fig:second_floor}
+% \end{figure}
 

### 2014-08-04 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update input files, update report from comments

@@
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain.
-The inputs for the FDS simulations are documented in this report.
+The inputs for the FDS simulations are documented in this report and are based on the fee scenario including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
@@
 The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at face height.
+The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at 1.86~m (6~ft).
 Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
-The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.
+It appears that the captain was likely overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday call, the captain was rescued from the structure, but later succumbed to his injuries.
 
 \chapter{Introduction}
-Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
-The objective of all of these studies has been to improve the safety of fire fighters.
+The objective of these studies has been to improve the safety and effectiveness of firefighters.
 
@@
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
-Computer simulations of the fire incident were conducted using Fire Dynamics Simulator and Smokeview to provide insight into the fire development and thermal conditions that might have existed in the residence during the fire.
+Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  softwareto provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
@@
 \item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
-\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department experienced during the course of their interior operations.
+\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department likely experienced during the course of their interior operations.
 \end{enumerate}
 This document describes the input and the results of the FDS (version 6.0.0) simulations.
+The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
+Analysis of the simulation results focuses on the hazardous conditions that developed following the creation of a flow path inside the structure.
+The document is organized in the following fashion:  Section~\ref{fire_sum} describes the events of the fire incident, Section~\ref{model} describes the relevant input parameters and assumptions used to develop the simulations, Section~\ref{results} presents simulation results, and Section~\ref{discussion} discusses the model results as they relate to firefighter safety and effectiveness.
 
@@
 \label{fire_sum}
-The account of events for this incident follows the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
-For the purpose of this analysis, the details regarding times are considered to be approximate values.
+The account of events for this incident were documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
+For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
 The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer}:
@@
 He stated that he noticed fire light-up in the stairwell.
-He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], preceded to walk in, saw no fire then backed out.
+He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], proceeded to walk in, saw no fire then backed out.
 
@@
 The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the [captain] and other crew member untangled.
-The TL39 Lieutenant and SQ5 fire fighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
+The TL39 Lieutenant and SQ5 firefighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
 
@@
 
-\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~(\ref{fig:simp_geom}).
+\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}.
 \begin{table}
 \centering
-\captionof{table}{Abridged NIOSH approximate fire event timeline}\label{tab:fire_info}
+\captionof{table}{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 \label{model}
-Fire Dynamics Simulator is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+The Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
@@
 Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~(\ref{fig:simp_geom}).
+One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~\ref{fig:simp_geom}.
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
@@
 Additionally, there was a half-story attic that contained the structure's hot water heater.
-Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
-Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~(\ref{fig:simp_geom}).
+Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~\ref{fig:simp_geom}), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~\ref{fig:simp_geom}) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~\ref{fig:simp_geom}).
+Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
 Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
-Figure~(\ref{fig:alpha_ex}) shows the exterior of the front and rear of the structure after the incident.
+Figure~\ref{fig:alpha_ex} shows the exterior of the front and rear of the structure after the incident.
 Note that the majority of the damage occurred in the attic and rear porch on the second floor.
-Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}), respectively.
+Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
 
@@
 The area of failure was also estimated based on the following observations.
-The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~(\ref{fig:door_frame}).
+The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~\ref{fig:door_frame}.
 It appears that the door collapsed and failed partially open.
@@
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~(\ref{fig:geom_grid}) shows the front of the structure rendered in Smokeview with the 10 cm mesh.
+Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10 cm mesh.
 
@@
 The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Figure~(\ref{fig:hrr}) shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
+Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
 The two vertical lines represent the time at which a firefighter opened the back door of the structure ($t$ = 130 s) and the time at which the second floor interior door was estimated to fail ($t$ = 160 s).
 Due to a lack of information about the time of fire ignition or how fast the fire grew, these parameters needed to be estimated.
-The growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
+The growth rate shown in Fig.~\ref{fig:hrr} (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
 The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while still aligning with the timeline observations of video and picture evidence from the fire.
@@
 
-In Fig.~(\ref{fig:hrr}), the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
+In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
 The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur.
 The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS.
-As shown in Fig.~(\ref{fig:hrr}), the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
+As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
 The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay.
@@
 There is an insufficient amount of oxygen in the structure to combust all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
-Figure~(\ref{fig:smv_ext_fire}) shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
+Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
 After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
@@
 
-Figure~(\ref{fig:hrr}) indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
+Figure~\ref{fig:hrr} indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
 At 130~s, the rear door is opened in the baseline simulation.
@@
 As the fire grows in the attic and rear porch, the pressure rises.
-Figure~(\ref{fig:pres_159s}) shows the pressure conditions in the structure just before the interior door failed in the simulation.
+Figure~\ref{fig:pres_159s} shows the pressure conditions in the structure just before the interior door failed in the simulation.
 On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa (0.00145~psi) at the ceiling.
@@
 Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
-The velocity vectors shown in Fig.~(\ref{fig:velo_175s}), 15~s after the interior door fails, confirm this flow direction within the structure.
+The velocity vectors shown in Fig.~\ref{fig:velo_175s}, 15~s after the interior door fails, confirm this flow direction within the structure.
 
@@
 The temperature profile at these high hazard areas will be shown via several snapshots in time to illustrate the change in the interior conditions.
-The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~(\ref{fig:temp_129s})), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~(\ref{fig:temp_159s})).
+The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~\ref{fig:temp_129s}), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~\ref{fig:temp_159s}).
 
@@
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
-Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}).
-As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
+Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}.
+As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
 Note that the conditions in the attic do not appear to change.
@@
 
-As shown in Fig.~(\ref{fig:temp_175s}), 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
+As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
 
 \chapter{Discussion}
+\label{discussion}
 The results of the FDS simulations will be discussed in two sections.
@@
 Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
-Figure~(\ref{fig:chicago_doorfold}) shows the state of the rear door after the fire.
+Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
 Note the large crease in the steel face of the door just above the knob.
@@
 Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
-Figure~(\ref{fig:SC_doorfold}) shows doors from two different residential fire experiments in different stages of degradation.
+Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation.
 In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
@@
 The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate.
-The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
+The arrows in Fig.~\ref{fig:flowpath_1} show the flow direction of gases on the second floor following the door failure.
 
@@
 
-Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}).
+Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~\ref{fig:temp_top_159}.
 The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
-Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}).
-Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}).
+Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~\ref{fig:temp_top_165}.
+Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~\ref{fig:temp_top_220}.
 These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Figure~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
+Figure~\ref{fig:temp_top_220} also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
 At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas.
@@
 In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in lethal conditions.
-Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the fire fighters faced on the fire ground.
+Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.
 In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
-Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of fire fighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
+Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
 

### 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits

@@
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain.
-The inputs for the FDS simulations are documented in this report and are based on the fee scenario including the building geometry, interior furnishings, and ventilation conditions.
+The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
@@
 The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at 1.86~m (6~ft).
+The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at a height of 1.86~m (6~ft).
 Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
@@
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
-Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  softwareto provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
+Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
@@
 The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
-Analysis of the simulation results focuses on the hazardous conditions that developed following the creation of a flow path inside the structure.
-The document is organized in the following fashion:  Section~\ref{fire_sum} describes the events of the fire incident, Section~\ref{model} describes the relevant input parameters and assumptions used to develop the simulations, Section~\ref{results} presents simulation results, and Section~\ref{discussion} discusses the model results as they relate to firefighter safety and effectiveness.
+Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
+This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
 
@@
 \label{fire_sum}
-The account of events for this incident were documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
+The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
@@
 He stated that he noticed fire light-up in the stairwell.
-He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], proceeded to walk in, saw no fire then backed out.
+He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], [proceeded] to walk in, saw no fire then backed out.
 
@@
 The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the [captain] and other crew member untangled.
-The TL39 Lieutenant and SQ5 firefighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
+The TL39 Lieutenant and SQ5 fire fighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
 
@@
 \label{model}
-The Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
@@
 \end{figure}
+
 %Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
@@
 Based on a review of these incidents, it is clear that fires with rapidly developing or changing flow paths are a significant hazard to the fire service.
-The development of or changes in a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
+The development of (or changes to) a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
 Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.

### 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update table in report

@@
  Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
-                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
-                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
+ Ambient Temperature~\cite{NIOSH:Bowyer}              &  7~$^{\circ}$C (45~$^{\circ}$F)                                               & -- \\ [.1cm]
+\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
+                                   &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$   & \\
+                                   &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  & \\
                                    &  Heat of Combustion: 16,400~kJ/kg                             & \\ [.25cm]
@@
                                    &  Porch Fire: 3.3~MW                                           & \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    &  $k$: 0.12 \; \si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
-                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
-                                   &  $c_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  &  $k$: 0.28 \; \si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
-                                   &  $c_{p}$: 1.0 \; \si{kJ/(kg.K)}                               & \\
+\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }   &  $k$: 0.12~\si{W/(m.K)})                                   & \multirow{3}{*}{Section~\ref{matl}} \\
+                                   &  $\rho$: 510~kg/m$^3$                                      & \\
+                                   &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                              & \\[.25cm]
+\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
+                                   &  $\rho$: 810~kg/m$^3$                                      & \\ 
+                                   &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                               & \\
 \bottomrule[1.25pt]

### 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor cleanup to table

@@
 \toprule[1.5pt]
-Parameter & Description & Reference  \\
+Parameter & Description & Discussion  \\
 \midrule
@@
  Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature~\cite{NIOSH:Bowyer}              &  7~$^{\circ}$C (45~$^{\circ}$F)                                               & -- \\ [.1cm]
+ Ambient Temperature             &  25~$^{\circ}$C (77~$^{\circ}$F)$^{*}$                                               & -- \\ [.1cm]
 \multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
@@
 \end{tabular}\par
+$^{*}$ Initial interior temperatures were assumed to be 25~$^{\circ}$C, exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}
 \end{table}

### 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edits based on reviewer comments

--- 2014-08-05 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 \usepackage{xfrac}
+\usepackage{cite}
 
@@
 \chapter*{\centering Abstract}
-\addcontentsline{toc}{chapter}{Abstract}
-The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of a fire captain.
+The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
 The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
@@
 
-On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain.
+On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a captain of the Chicago Fire Department.
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
@@
 
-\chapter{Fire Incident Summary}
+\chapter{Summary of the Fire Incident}
 \label{fire_sum}
@@
 He reported a working fire with heavy smoke coming from the rear and front of the structure's attic.
-Per fire department standard operating procedures, dispatch initiated a RIT response\footnote{The department defines are ``RIT Response'' to be one truck company, one battalion chief, one ALS ambulance, and one EMS field officer.}.
+Per fire department standard operating procedures, dispatch initiated a RIT response\footnote{The department defines a rapid intervention team (RIT) response to be one truck company, one battalion chief, one advanced life support (ALS) ambulance, and one emergency medical services (EMS) field officer.}.
 At 1718 hours, E123 arrived on scene and BC19 was on scene and had assumed incident command (IC).
@@
 
-\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}.
+\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}, and more details of the fire development are provided in the following sections.
+
 \begin{table}
 \centering
-\captionof{table}{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
+\captionof{table}[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 \multirow{2}{*}{17:15:00}  &  \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
-         & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
+                           &                                                                                                                                          \\[.25cm] %blank rows exist for wrapping text.
+# of blanks is 1 less than number of rows
 \multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
@@
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
-The interior walls were constructed from nominal lumber with 12.7~mm (0.5~in) gypsum board over top~\cite{NIOSH:Bowyer}.
+The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer}.
 Additionally, there was a half-story attic that contained the structure's hot water heater.
@@
 Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
+
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
+Based on these sources of information, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
 The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board.
@@
 
-The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the amount of energy per unit mass of the fuel.
@@
 
-To estimate the energy release rate per unit area (kW/m$^2$) of wood, work by Babrauskas and Grayson~\cite{babrauskas1990} is used.
-Experiments were conducted in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials.} to determine the 5 minute average of HRRPUA\footnote{HRRPUA is the heat release rate per unit area.} (kW/m$^2$) for several different types of wood over a range of radiant heat fluxes (kW/m$^2$).
-Babrauskas and Grayson~\cite{babrauskas1990} suggest that the heat release rate per unit area for a variety of woods is approximately 50~kW/m$^2$.
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
 
 To calculate the total fire size, the appropriate burning area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
-Based on the floor plan of the structure, the underside of the roof is approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
-Additionally, there is 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
+Based on the floor plan of the structure, the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
+Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
 Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
@@
 To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
-Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch is approximately 3.3~MW.
+Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
 Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
@@
 
+\clearpage
+
 \section{Ventilation}
@@
 
-An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
+An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
 The area of failure was also estimated based on the following observations.
@@
 \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
-Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
+Note that the hinge is still intact and there is unburned, ``clean'' wood along the bottom portion of the frame.}
 \label{fig:door_frame}
@@
 55          &  55           &  0.12         &  Breach       &  Rear            \\
-130         &  N/A          &  1.41         &  Door         &  Rear            \\
-135         &  N/A          &  0.2          &  Breach       &  Left            \\
+130         &  N/A$^*$      &  1.41         &  Door         &  Rear            \\
+135         &  N/A$^*$      &  0.2          &  Breach       &  Left            \\
 160         &  160          &  0.80         &  Door         &  Interior        \\
@@
 \end{tabular}\par
+\footnotesize
+$^*$These ventilation events were not included in the alternative simulation.
+\normalsize
 \end{table}
@@
 
-For the simulation in this study, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$.
+For the simulation, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$.
 Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
@@
 D^* = \left(
-     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
+     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g}}
      \right)^\frac{2}{5} 
@@
 \end{equation}   
-From the FDS User Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
+From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
 relation $Q^* = (D^*/D)^{5/2}$.
-Here, $D$ is the physical diameter of the fire as it is specified in the simulation.
-Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the ratio of the characteristic fire diameter to the cell size ($D^*/\dx$) is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
+Following Eq.~(\ref{eq:mesh}) and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
 Based on validation work performed for the U.S.
@@
 The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-At a grid resolution of 10~cm (3.9~in), this results in 2.4 million computational cells.
+A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
 The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
@@
 \toprule[1.5pt]
-Parameter & Description & Reference  \\
+Parameter                                                  & Description                                   & Discussion                            \\
 \midrule
- Simulation Time                   &  5 min                                                        & -- \\[.25cm]
+Simulation Time                                            &  5 min                                        & --                                    \\ [.25cm]
 Grid Cell Size                                             &  10 cm                                        & Section~\ref{mesh}                    \\ [.25cm]
- Ambient Temperature~\cite{NIOSH:Bowyer}              &  7~$^{\circ}$C (45~$^{\circ}$F)                                               & -- \\ [.1cm]
+Ambient Temperature$^*$                                    &  25~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
 \multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
@@
                                                            &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
-\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
+\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{fire}}   \\ 
                                                            &  Porch Fire: 3.3~MW                           &                                       \\ [.25cm]                     
@@
                                                            &  $\rho$: 510~kg/m$^3$                         &                                       \\
-                                   &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                              & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                                    &  \multirow{3}{*}{Section~\ref{matl}}\\ 
+                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                       \\ [.25cm]
+\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
                                                            &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
@@
 \end{tabular}\par
+\footnotesize
+$^{*}$ Initial interior temperatures were assumed to be 25~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+\normalsize
 \end{table}
@@
 
-To examine the results of the simulations, it is important to link the timelines from fire scene to the simulation times.
-Table~\ref{tab:firesim} shows the fireground timeline along with the corresponding simulation times.
+To examine the results of the simulations, it is important to link the timelines from the fire scene to the simulation times.
+Table~\ref{tab:firesim} shows the fireground timeline~\cite{NIOSH:Bowyer} along with the corresponding simulation times.
 
@@
 \midrule
-\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Fire is reported with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
@@
          & & \\[.25cm]
-\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {Simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
+\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {FDS simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
          & & \\[0.25cm]
@@
 The growth rate shown in Fig.~\ref{fig:hrr} (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
-The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while still aligning with the timeline observations of video and picture evidence from the fire.
-The accuracy of heat transfer to the walls of the structure may be sacrificed by using this approach; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
+The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while aligning with the timeline observations of video and picture evidence from the fire.
+Using this approach, the accuracy of heat transfer to the walls of the structure may be sacrificed; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
 
@@
 \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
-The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
+The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
 \label{fig:hrr}
@@
 The open door and breach act as additional pressure releases for the structure.
-Again, the abrupt change in ventilation causes the HRR to increase from 7~MW to 9.7~MW at 139~s.
+Again, the abrupt change in ventilation causes the HRR to increase from approximately 7~MW to 9.7~MW at 139~s.
 At the time of the door failure (160~s), the HRR in both cases was approximately 9~MW because of the increased amount of ventilation.
@@
 
+\clearpage
+
 \section{Pressure}
 
-As the fire grows in the attic and rear porch, the pressure rises.
-Figure~\ref{fig:pres_159s} shows the pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa (0.00145~psi) at the ceiling.
+As the simulated fire grows in the attic and rear porch, the pressure rises.
+Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
+On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
 Gases at an elevated pressure will always move towards a region of lower pressure.
@@
 Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
-The velocity vectors shown in Fig.~\ref{fig:velo_175s}, 15~s after the interior door fails, confirm this flow direction within the structure.
+The velocity vectors shown in Fig.~\ref{fig:velo_175s} (15~s after the interior door fails) indicate the direction of flow within the structure.
 
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.
-Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
+\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.}
 \label{fig:pres_159s}
@@
 \label{temp}
-Analysis of the temperatures from the FDS simulation will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-The temperature profile at these high hazard areas will be shown via several snapshots in time to illustrate the change in the interior conditions.
+Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+The temperature profile at these high hazard areas is shown via several snapshots in time to illustrate the change in the interior conditions.
 The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~\ref{fig:temp_129s}), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~\ref{fig:temp_159s}).
@@
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
-Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}.
+Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}.
 As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
@@
 
-\chapter{Discussion}
+\chapter{Discussion of Simulation Results}
 \label{discussion}
-The results of the FDS simulations will be discussed in two sections.
-The first section will address the results of the computational modeling as they relate to the interior hallways conditions.
-The second section will examine the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
+The results of the FDS simulations are discussed in the following two sections.
+The first section addresses the results of the computational modeling as they relate to the interior hallways conditions.
+The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
 
-\section{Hallway Flow Path}
+\section{Simulated Hallway Flow Path}
 From on-scene reports (Section~\ref{fire_sum}) and the FDS simulation results (Section~\ref{temp}), the interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
+From the NIOSH report~\cite{NIOSH:Bowyer}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
 This indicated the presence of fire in the area of the enclosed porch.
-The simulation results indicate a high hazard area in the attic and the enclosed porch at this time.
+The simulation results indicate a high hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the attic and the enclosed porch at this time.
 By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
 Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
-Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
+Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure.
 Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
@@
 In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
-This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in the studied fire incident.
+This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in this fire incident.
 
@@
 
-After the interior door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
+After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.
 This resulted in a rapid change in the conditions within the flow path.
-The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate.
-The arrows in Fig.~\ref{fig:flowpath_1} show the flow direction of gases on the second floor following the door failure.
+The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door and flowed towards lower pressure areas in the hallways and kitchen.
+The arrows in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor following the door failure.
 
@@
 \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-\caption{Flow path on the second floor after interior door failure.}
+\caption{Summary of simulated flow path on the second floor after interior door failure.}
 \label{fig:flowpath_1}
@@
 
-\subsection{Assessing the Hazard}
+\clearpage
+
+\section{Assessing the Hazard}
 
 A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
-While firefighters wear protective gear, gear only offers a finite amount of protection.
+Although firefighters wear protective gear, gear only offers a finite amount of protection.
 The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
@@
 Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~\ref{fig:temp_top_165}.
-Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~\ref{fig:temp_top_220}.
+Within 60~s of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~\ref{fig:temp_top_220}.
 These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
@@
 These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
+
 \begin{figure}[!ht]
@@
 
+\clearpage
+
 \section{Tactical Considerations}
-There have been many previous fire incidents in which changes in the flow paths have had an adverse impact on firefighter and occupant safety.
-Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years in which it could be determined that there was a flow path related incident.
+There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
+Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
 This table lists the NIOSH investigation number, the outcome, and a brief description of the flow path details.
@@
 
-In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in lethal conditions.
+In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death of a fire captain.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
@@
 However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
+
 The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
@@
 The temperature of the gases that flowed into the hallway at face height exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
-
-Unfortunately a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
+Unfortunately, a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
 The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
@@
 
-\chapter{Acknowledgments}
+\chapter*{Acknowledgments}
 The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck.

### 2014-08-06 SURF Presentation/Willi_SURF_Presentation.tex
Uploaded SURF presentation and videos

\documentclass[t]{beamer}
\usepackage{beamerthemeSzeged}
\usecolortheme{beaver}
\usepackage{graphicx}
\usepackage{multimedia}
\usepackage{media9}

\title{Impact of Different Hose Stream Applications during Fire Suppression}
\author{Joseph Willi}
\institute [ ] % (optional, but mostly needed)
{\small University of Illinois at Urbana-Champaign\\
 %\includegraphics[scale=.1]{illini.jpg}\\
EL Fire Research Division - Fire Fighting Technology Group}
\date{\small August 6, 2014}

\begin{document}

\setbeamertemplate{itemize items}[circle]
\setbeamercolor{titlelike}{bg=gray!10!white}
\setbeamercolor{frametitle}{bg=gray!10!white}
\setbeamercolor{subsection in head/foot}{bg=black!15!white}
\setbeamercolor{background canvas}{bg=black!15!white}
\setbeamercolor{itemize item}{fg=darkred} % all frames will have red bullets
\beamertemplatenavigationsymbolsempty %removes navigation bar from all slides

\frame[plain]{\titlepage}%Oppurtunity to evaluate the effectiveness of different hose streams on fire suppression

\addtobeamertemplate{navigation symbols}{}{
    \usebeamerfont{footline}
    \usebeamercolor[gray]{footline}
    \hspace{1em}
    \insertframenumber/\inserttotalframenumber
} %adds frame number to slides

\section{Importance of Researching Fireground Tactics}
\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Importance of Researching Fireground Tactics\end{Large}}}
\end{frame}

\begin{frame}
\frametitle{How are Tactics Chosen on the Fireground?}
\begin{columns}
\column{.7\framewidth}
\begin{small}{Decisions based on habits learned from training 
\\~\\
Training based on a set of standard operating procedures (SOPs)
\\~\\
SOPs vary from entity to entity - different people have different opinions
\\~\\
More difficult to rely solely on experience today
\\~\\
Firefighters need to know the science behind tactics
\\~\\
Research bridges the gap between understanding how the fire behaves in its environment and how the fire environment will change when a specific tactic is implemented
}\end{small}
\column{.3\framewidth}
\\~\\
\centerline{\includegraphics[scale=.18]{FIRE.pdf}}
\end{columns}
\end{frame}

%\begin{frame}
%\frametitle{Fireground Tactics Research}
%Covers variety of topics
%\\~\\
%Investigations of close calls and line of duty deaths
%\\~\\
%Full-scale fire experiments to evaluate the effectiveness of certain tactics
%\\~\\
%Provides physical examples that can be related to fire behavior
%\end{frame}
%Forced convection means that the mass flow rate of the adjacent fluid (gas or liquid) is known and its temperature is the result of heat exchange between body and fluid

\begin{frame}
\frametitle{Changing the Flow Path}
Smoke and heat from a fire travel the path of least resistance 
\\~\\
Anyone in the flow path is exposed to hazardous conditions from the increased flow of heat and smoke
\\~\\
Paths can be altered through opening and closing windows and doors in the structure
\\~\\
\begin{columns}
\column{.5\framewidth}
\centerline{\includegraphics[scale=.46]{flow_path.png}}
\column{.5\framewidth}
\centerline{\includegraphics[scale=.46]{fds_flow_path.png}}
\end{columns}
\end{frame}

\section{Hose Streams}
\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Hose Streams\end{Large}}}
\end{frame}

\begin{frame}
\frametitle{What is a Hose Stream?}
\begin{columns}
	\column{.65\framewidth}
Stream of water or extinguishing agent discharged from a hose during fire suppression
\\~\\
Choice of stream dependent upon many factors
\\~\\
Streams vary in numerous ways
\\~\\
Many opinions throughout fire service about the ``best" stream
	\column{.3\framewidth}
	\\~\\
	\centerline{\includegraphics[scale=.17]{Combination_Nozzle.pdf}}
\end{columns}
\end{frame}

\begin{frame}
\frametitle{Different Hose Streams Considered}
\centerline{\movie[height=6.75cm, width=12.8cm, poster,loop,autostart]{}{Hose_Stream_Comparison_Full.avi}}
\end{frame}

\begin{frame}%talk about GPMs
\frametitle{Different Application Patterns Considered}
\centerline{\movie[height=6.75cm, width=12.8cm,poster,loop,autostart]{}{Application_Pattern_Comparison.avi}}
\end{frame}

\section{Experimental Setup and Results}
\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Experimental Setup and Results\end{Large}}}
\end{frame}

\begin{frame}
\frametitle{Overview of Experiments - Test Structures}
Conducted in two structures located at the Delaware County (DelCo) Emergency Training Services Training Center
%Structures surrounded by 2foot concrete blocks; were Y x Z, serving as a full scale representation of a typical residential structure
	\begin{columns}
    	\column{.5\framewidth}
    	\\~\\
		\centerline{\includegraphics[scale=.245]{east_structure.pdf}}
    	\column{.5\framewidth}
    	\\~\\
		\centerline{\includegraphics[scale=.245]{west_structure.pdf}}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Overview of Experiments - Types of Experiments}
\vspace{\baselineskip}	
\vspace{\baselineskip}
	\begin{columns}%discuss cold flow tests with PPV fan, work on explanation; cold flow tests -> hose tests -> full scale incremental fire tests
		\column{.33\framewidth}
		\centerline{Cold Flow Tests}
		\centerline{\includegraphics[scale=.165]{Cold_Flow_PPV.pdf}}	
		\\~\\ \pause
    	\column{.33\framewidth}
		\centerline{Hose Tests}
		\centerline{\includegraphics[scale=.165]{hose_test.pdf}}
		\\~\\ \pause
		\column{.33\framewidth}
		\centerline{Fire Tests}
		\centerline{\includegraphics[scale=.165]{fire_test.pdf}}
	\end{columns}
\end{frame}

\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Two Story Structure Hose Test\end{Large}}}
	\begin{columns}[T]
		\begin{column}{.5\framewidth}
		\centerline{\includegraphics[scale=.23]{West_Hose_SS.pdf}}
		\end{column}
		\begin{column}{.5\framewidth}
		\centerline{\includegraphics[scale=.23]{West_Hose_WF.pdf}}
		\end{column}
	\end{columns}
\end{frame}

\begin{frame}
\frametitle{Two Story - Hose Test Setup}
\centerline{\includegraphics[width=10cm, height=7cm]{West_Hose_Setup.pdf}}
\end{frame}

\begin{frame}%velocity in m/s vs time in seconds; consists of 8 BDPs evenly spaced in the doorway, starting with the black line at the top in the legend which was right below the door way, all the way to the gold line which is the air flow right above the floor; negative air flow indicates flow in the opposite direction(down the stairwell) and there is little of that from mixing of the air
\frametitle{Two Story - Hose Test Results - Straight Stream}
\centerline{\includegraphics[scale=.44]{West_Hose_SS_BDP10.pdf}}
\end{frame}

\begin{frame}%WF draws in significantly more air due to the larger area of the pattern, it's almost as if it's acting like a fan, drawing the air into the structure
\frametitle{Two Story - Hose Test Results - Wide Fog}
\centerline{\includegraphics[scale=.44]{West_Hose_WF_BDP10.pdf}}
\end{frame}

\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Two Story Structure Fire Test\end{Large}}}
\end{frame}

\begin{frame}
\frametitle{Two Story - Fire Test Setup}
\centerline{\includegraphics[width=10cm, height=7cm]{West_Fire_Setup.pdf}}
\end{frame}

\begin{frame}
\frametitle{Two Story - Fire Test Video}
\centerline{\movie[height=3.25cm, width=10cm,,poster]{}{Fire_Application_SS.avi}}
\centerline{\movie[height=3.25cm, width=10cm,,poster]{}{Fire_Application_WF.avi}}
\end{frame}

\begin{frame}%stress significance of velocity increase and impact they have on flow path
\frametitle{Two Story - Fire Test Results - Stairwell Door}
\centerline{\includegraphics[scale=.45]{West_Fire_SSWF_BDP10.pdf}}
\end{frame}

\begin{frame}%explain plot; mention steady temperatures near floor because that is where low pressure inlet is, describe 
\frametitle{Two Story - Fire Test Results - 2\textsuperscript{nd} Level Rear Door}
\centerline{\includegraphics[scale=.45]{Second_Story_WFSS_TC11.pdf}}
\end{frame}

\begin{frame}[c]
\centerline{\colorbox{gray!15!white}{\color{darkred}\begin{Large}Single Story Structure Fire Test\end{Large}}}
\end{frame}

\begin{frame}
\frametitle{Single Story - Fire Test Setup}
\centerline{\includegraphics[scale=.29]{East_Fire_Setup.jpg}}
\end{frame}

\begin{frame}
\frametitle{Single Story - Fire Test Results - Middle Room}
\centerline{\includegraphics[height=7.25cm,width=10.5cm]{East_Fire_SSNF_TC3.pdf}}
\end{frame}

\begin{frame}
\frametitle{Single Story - Fire Test Results - Front Room}
\centerline{\includegraphics[height=7.25cm, width=10.5cm]{East_Fire_SSNF_TC5.pdf}}
\end{frame}

\begin{frame}
\frametitle{Conclusions}
Application patterns have the potential to affect movement of gases
\\~\\
Straight stream does least amount of mixing of gases
\\~\\
Straight stream decreased hazard of flow path 
\\~\\
Wide fog increased hazardous conditions in stairwell by increasing the velocities by as much as 50\% in the flow path
\\~\\
%by presenting these results to the fire service, FFs can 
\end{frame}

\begin{frame}
\frametitle{Acknowledgments}
Gavin Horn
\\~\\
Dan Madrzykowski
\\~\\
Roy McLane
\\~\\
Craig Weinschenk
\\~\\
Kris Overholt
\\~\\
Keith Stakes
\\~\\
SURF Directors
\end{frame}

\begin{frame}[c]
\centerline{\color{darkred}\begin{Huge}Follow @NIST\textbf{\_}Fire\end{Huge}}
\end{frame}

\begin{frame}[c]
\centerline{\color{darkred}\begin{Huge}Questions?\end{Huge}}
\end{frame}

\end{document}

### 2014-08-06 Studies/2012_Chicago/Report/Chicago_Fire.tex
Bibliography: Graduate xfrac and cite packages to commoncommands
Chicago: update fds files, bibliography, and minor updates to report

@@
 \newcommand{\N}{\mbox{N}}
-
-% Extra packages
-\usepackage{xfrac}
-\usepackage{cite}
 
@@
 The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
-The following subsections will describe the inputs that were used to construct the simulation, including any engineering approximations or assumptions that were made.
+
+Based on the information collected, several engineering approximations were made. The actual ignition time is unknown.
+
+The following subsections will describe the inputs that were used to construct the simulation, including any approximations or assumptions that were made.
 
@@
 
-%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%\begin{figure}[!ht]
-%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-%\end{tabular*}
-%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-%\label{fig:smv_interior}
-%\end{figure}
-
 \section{Fire}
@@
 
-Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$).
-The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the SFPE Handbook~\cite{SFPE:Tewarson}.
+Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
 A balanced chemical reaction for wood combustion can written as:
@@
 
-The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
+The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the amount of energy per unit mass of the fuel.
@@
 Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were judged to be adequate for engineering calculations.
-The grid resolution used in this model is within typical engineering $D^*/\dx$ values.
+The grid resolution used in this model is within  or exceeds typical engineering $D^*/\dx$ values.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
@@
         &  & \\[.25cm]
-        & 135 & Additional ventilation through left side of structure. \\[.25cm] 
+        & 135 & Ventilation through left side of structure. \\[.25cm] 
         & 160 & Top of interior door fails in FDS model. \\[.25cm] 
@@
 \end{tabular}\par
+For specific information regarding ventilation areas used in FDS model, refer to Table~\ref{tab:vents}.
 \end{table}
@@
 Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
-Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure.
+Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:firesim}).
 Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
@@
 The arrows in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor following the door failure.
+Red colored arrows indicate that the gases were at an elevated temperature, while the blue arrows indicate that the gases were at temperatures close to ambient.
+The arrow that transitions from red to blue indicates that the gas began to cool as it approached the front of the structure.
+Note that at the second story doorway towards the front of the structure there are two arrows; this is an indication of bi-directional flow.
+The cool ambient air flowed in at the bottom while the gas at elevated temperature flowed out the top.
 
@@
 Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
+Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F), represents a Class III exposure~\cite{Donnelly2006}.
+Firefighters face increased risk when facing Class III exposures for greater than five minutes~\cite{Donnelly2006}.
 Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
+The these conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.

### 2014-08-06 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits to report

@@
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~(\ref{eq:mesh}) and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were judged to be adequate for engineering calculations.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
 The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
+
+As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
+The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
+A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10 cm mesh.
+Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
+Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
+Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 \end{tabular*}
-\caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
+\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
 \label{fig:geom_grid}
 \end{figure}
-
-As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
-To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
-The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
-Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes.
-For the simulations that were conducted as part of this study, Table~\ref{tab:mod_param} shows the relevant model input parameters that were discussed in Section~\ref{model}.
 
@@
 \midrule
-Simulation Time                                            &  5 min                                        & --                                    \\ [.25cm]
-Grid Cell Size                                             &  10 cm                                        & Section~\ref{mesh}                    \\ [.25cm]
+Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
+Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
 Ambient Temperature$^*$                                    &  25~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
@@
 \end{tabular}\par
-For specific information regarding ventilation areas used in FDS model, refer to Table~\ref{tab:vents}.
+\footnotesize
+For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
+\normalsize
 \end{table}
@@
 
-Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
@@
 The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door and flowed towards lower pressure areas in the hallways and kitchen.
-The arrows in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor following the door failure.
-Red colored arrows indicate that the gases were at an elevated temperature, while the blue arrows indicate that the gases were at temperatures close to ambient.
-The arrow that transitions from red to blue indicates that the gas began to cool as it approached the front of the structure.
-Note that at the second story doorway towards the front of the structure there are two arrows; this is an indication of bi-directional flow.
-The cool ambient air flowed in at the bottom while the gas at elevated temperature flowed out the top.
+The arrows shown in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor after the door failure.
+In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures.
+The arrow that transitions from red to blue indicates that the heated gases were cooling as they flowed away from the fire towards the front of the structure.
+The two arrows located at the door on the second floor (towards the front of the structure) indicate bi-directional flow.
+At that doorway, cool ambient air flowed towards the fire near the bottom of the door, and hot gases flowed away from the fire near the top of the door.
 
@@
 Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
-Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F), represents a Class III exposure~\cite{Donnelly2006}.
-Firefighters face increased risk when facing Class III exposures for greater than five minutes~\cite{Donnelly2006}.
+Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class III exposure~\cite{Donnelly2006}.
+Firefighters are at increased risk levels when encountering Class III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
 Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
-The these conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
+These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edit to default ambient temperature value in report

@@
 Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
-Ambient Temperature$^*$                                    &  25~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
+Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
 \multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
@@
 \footnotesize
-$^{*}$ Initial interior temperatures were assumed to be 25~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
 \normalsize

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update to report

@@
 
-Based on the information collected, several engineering approximations were made. The actual ignition time is unknown.
-
+The focus of the analysis of the model results is on the interior second floor conditions prior to and after the interior door failure.
+Based on the goals of the analysis and the information collected, several engineering approximations were made.
+For example, it is known that the fire showed signs of being under-ventilated when firefighters arrived~\cite{NIOSH:Bowyer}, however the exact ignition time, fire growth rate, and energy release of the fire were not known.
+The ignition time and growth rate were estimated to balance computational runtime while adhering to documented observations.
+The energy release of the fire was estimated using documentation of the potential fuel load within the structure.
+Though there may exist differences with respect to the actual values compared to though used in the model, the inputs were determined to best model this fire scenario.
 The following subsections will describe the inputs that were used to construct the simulation, including any approximations or assumptions that were made.
@@
 
+\clearpage
+
 \section{Materials}
@@
 \end{lstlisting}
-
-\clearpage
 

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edits throughout

--- 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 \chapter*{\centering Abstract}
-The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2 \sfrac{1}{2} story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
+The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2~\sfrac{1}{2}~story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
 The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
@@
 
-On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a captain of the Chicago Fire Department.
+On November 2, 2012, a fire in a 2~\sfrac{1}{2}~story wood frame residential structure claimed the life of a captain of the Chicago Fire Department.
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
@@
 
-Based on the information collected, several engineering approximations were made. The actual ignition time is unknown.
-
-The following subsections will describe the inputs that were used to construct the simulation, including any approximations or assumptions that were made.
+The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
+Based on the goals of the analysis and the information collected, several engineering approximations were made.
+For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
+The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+Although there might be differences between the actual values and those used in the simulation, the model input parameters represent our best estimate of the fire scenario based on the information that was available.
+The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
 
@@
 \label{geom}
-The structure involved in this fire incident was a 2~\sfrac{1}{2} story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
 Intermediate floors are built directly off of the studs.
@@
 
+\clearpage
+
 \section{Fire}
@@
 \begin{lstlisting}
-&SPEC ID = 'WOOD', FORMULA = 'CH1.7O0.74N0.002' /
+&SPEC ID='WOOD', FORMULA='CH1.7O0.74N0.002' /
 
@@
 &VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 
-&DEVC XYZ = -17.2,2,0 ID = 'SECOND FIRE', QUANTITY = 'TIME', SETPOINT = 40, INITIAL_STATE = .FALSE. /
+&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
 \end{lstlisting}
 Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
+
+\clearpage
 
@@
 
-\clearpage
-
 \section{Ventilation}
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
-\caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
-Note that the hinge is still intact and there is unburned, ``clean'' wood along the bottom portion of the frame.}
-\label{fig:door_frame}
-\end{figure}
+\clearpage
 
@@
 \end{table}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
+\caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
+Note that the hinge is still intact and there is unburned, ``clean'' wood along the bottom portion of the frame.}
+\label{fig:door_frame}
+\end{figure}
+
+\clearpage
 
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update to report

@@
 The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
-Although there might be differences between the actual values and those used in the simulation, the model input parameters represent our best estimate of the fire scenario based on the information that was available.
+According to the McCaffrey, Quintiere, and Harkleroad correlation for a typical compartment fire, a change in the hot gas layer temperature rise is proportional to a change in the HRR raised to the \sfrac{2}{3} power.
+Following this relationship, in a well ventilated compartment, a 7.5~\% increase in HRR would result in a 5~\% increase in temperature~\cite{NUREG_1824_Sup_1}.
+In reality, input variables more closely resemble distributions than fixed point values which are used as inputs into FDS.
+For a detailed discussion on propagation of parameter uncertainty, see NUREG-1824 Supplement 1~\cite{NUREG_1824_Sup_1}.
 The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edits to uncertainty discussion

--- 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
 The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
-Although there might be differences between the actual values and those used in the simulation, the model input parameters represent our best estimate of the fire scenario based on the information that was available.
+
+In reality, the quantities associated with these input parameters are not fixed values; rather, the model input parameters can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}.
 The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit to uncertainty discussion

@@
 
-In reality, the quantities associated with these input parameters are not fixed values; rather, the model input parameters can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
 Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).

### 2014-08-07 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update
Chicago: Edit author list

@@
 Craig G. Weinschenk \\
+Kristopher J. Overholt \\
 Daniel Madrzykowski \\
-Kristopher J. Overholt \\
 
@@
 Craig G. Weinschenk \\
+Kristopher J. Overholt \\
 Daniel Madrzykowski \\
-Kristopher J. Overholt \\
 {\em Fire Research Division \\
@@
 Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in NUREG-1824 Supplement~1~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
 The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
@@
 The HRR is reduced to 5~MW as the oxygen inside the structure is consumed.
-There is an insufficient amount of oxygen in the structure to combust all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
+There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
 Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.

### 2014-08-08 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update to report

@@
 This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
+Appendinx~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
 
@@
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3~MW.
+This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure.
 However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
@@
 The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway at face height exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
+The temperature of the gases that flowed into the hallway at face height was calculated to exceed 260~$^{\circ}$C (500~$^{\circ}$F).
 Unfortunately, a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
@@
 \chapter{Dimensioned Drawings}
-
+\label{app_draw}
 \begin{figure}[!ht]

### 2014-08-08 Studies/2013_PG_County/Report/PG_Co_Fire.tex
Documentation/Reports: Minor style edit
PG_County: add FDS files, plotting script, report formatting

@@
 
-\input{../Bibliography/commoncommands}
+\input{../../../Bibliography/commoncommands}
 
@@
 \renewcommand{\sb}[1]{_\mathrm{#1}}
+\renewcommand{\C}{\mbox{C}}
+\renewcommand{\H}{\mbox{H}}
+\renewcommand{\O}{\mbox{O}}
+\newcommand{\N}{\mbox{N}}
+
+% Extra packages
+\usepackage{xfrac}
 
@@
 
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
 \headerB{
-Fire Investigation\\
-Title\\
+Simulation of a Wind Driven \\
+Basement Fire - \\
+Riverdale Heights, MD \\
 }
 
+\normalsize
+
 \headerC{
+{
 \flushright{
-Authors \\
-{\em Fire Research Division \\
-Engineering Laboratory \\
-Gaithersburg, Maryland, USA} \\ }
-}
+Craig G. Weinschenk \\
+Kristopher J. Overholt \\
+Daniel Madrzykowski \\
 
-\flushright{\today \\
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\endgroup
 }
@@
 \flushright{
-\includegraphics[width=2.in]{../Bibliography/nistident_flright_vec} \\[.3in]
+
+\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+}
+}
 }
 
+\end{minipage}
+
+\newpage
+\hspace{5in}
+\newpage
+
+\frontmatter
+
+\pagenumbering{roman}
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
+\headerB{
+Simulation of a Wind Driven \\
+Basement Fire - \\
+Riverdale Heights, MD \\
+}
+
+\headerC{
+\flushright{
+Craig G. Weinschenk \\
+Kristopher J. Overholt \\
+Daniel Madrzykowski \\
+{\em Fire Research Division \\
+Engineering Laboratory} \\
+
+\vspace*{2\baselineskip}
+
+\begingroup
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
+
+\vspace*{2\baselineskip}
+
+August 2014}}
+
+\vfill
+
+\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }
+
 \titlesigs
+
+\end{minipage}
+
+\newpage
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
+document in order to describe an experimental procedure or concept adequately. \\
+Such identification is not intended to imply recommendation or endorsement by the \\
+National Institute of Standards and Technology, nor is it intended to imply that the \\
+entities, materials, or equipment are necessarily the best available for the purpose. \\
+}
+
+\vspace{3in}
+
+\large
+\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
+% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+CODEN: NTNOEF }
+
+\vfill
+
+\hspace{1in}
 
@@
 
-\clearpage
+\cleardoublepage
 \phantomsection
@@
 
+\chapter*{\centering Abstract}
+\addcontentsline{toc}{chapter}{Abstract}
+
 \chapter{Introduction}
@@
 \chapter{Fire Incident Summary}
+\label{fire_sum}
 
-\chapter{Fire Dynamics Simulator and Smokeview}
+\chapter{Model Description}
+\label{model}
+Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
+The cells are contained together within one larger volume known as a computational domain.
+The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
+Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
+One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
+A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.
 
-\chapter{Model Input Parameters}
+Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
+Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview allows the fire and fire movement to be visualized.
+This is done by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
+Smokeview also visualizes static data at particular times using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
+
+Input data from various sources must be collected and documented to simulate a fire using FDS or any other fire model.
+For the simulation results presented in this document, information was obtained from two primary sources.
+The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
+The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
+
+The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
+Based on the goals of the analysis and the information collected, several engineering approximations were made.
+For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
+The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+
+In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
+
+\section{Geometry}
+\label{geom}
+
+\section{Fire}
+\label{fire}
+
+\section{Materials}
+\label{matl}
+
+\section{Ventilation}
+\label{Vents}
+
+\section{Mesh}
+\label{mesh}
 
 \chapter{Model Results}
+\label{results}
+
+\section{Heat Release Rate}
+\label{HRR}
+
+\section{Pressure}
+
+\section{Temperature}
+\label{temp}
 
@@
 
-\chapter{Acknowledgements}
+\chapter{Acknowledgments}
 

### 2014-08-08 Studies/2013_PG_County/Scripts/pg_co_hrr.py

@@ -1,0 +1,132 @@
+#Weinschenk
+#7-14
+
+import os
+import numpy as np
+import pandas as pd
+from pylab import *
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+def movingaverage(interval, window_size):
+    window= np.ones(int(window_size))/float(window_size)
+    return np.convolve(interval, window, 'same')
+
+FDS_4MW_20 = np.genfromtxt('../FDS_Output_Files/pg_county_20mph_4MW_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR_4MW_20 = FDS_4MW_20['HRR']/1000
+HRR_4MW_20_avg = movingaverage(HRR_4MW_20,10)
+
+FDS_9MW_20 = np.genfromtxt('../FDS_Output_Files/pg_county_20mph_9MW_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR_9MW_20 = FDS_9MW_20['HRR']/1000
+HRR_9MW_20_avg = movingaverage(HRR_9MW_20,10)
+
+FDSdevc_9MW_20 = np.genfromtxt('../FDS_Output_Files/pg_county_20mph_9MW_devc.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR_B_9MW_20 = FDSdevc_9MW_20['Basement_HRR']/1000
+HRR_1_9MW_20 = FDSdevc_9MW_20['First_Floor_HRR']/1000
+HRR_B_9MW_20_avg = movingaverage(HRR_B_9MW_20,10)
+HRR_1_9MW_20_avg = movingaverage(HRR_1_9MW_20,10)
+HRR_T_9MW_20_avg = HRR_B_9MW_20_avg + HRR_1_9MW_20_avg
+
+FDS_9MW_10 = np.genfromtxt('../FDS_Output_Files/pg_county_10mph_9MW_hrr.csv', delimiter=',', skip_header=1, dtype=None, names=True)
+HRR_9MW_10 = FDS_9MW_10['HRR']/1000
+HRR_9MW_10_avg = movingaverage(HRR_9MW_10,10)
+
+FDSdevc_9MW_10 = np.genfromtxt('../FDS_Output_Files/pg_county_10mph_9MW_devc.csv', delimiter=',', skip_header=1, dtype=None, names=True)
[…]

### 2014-08-11 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Fix typo
Chicago: Minor edit

@@
 \chapter{Introduction}
-Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
@@
 This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
-Appendinx~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
+Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
 
@@
 \label{app_draw}
+
 \begin{figure}[!ht]

### 2014-08-11 Studies/2011_San_Francisco/Report/SF_Fire.tex
San Francisco: Updates from Chicago report

@@
 
-% Extra packages
-\usepackage{xfrac}
-
 \begin{document}
@@
 Kristopher J. Overholt \\
+Craig G. Weinschenk \\
 Daniel Madrzykowski \\
-Craig G. Weinschenk \\
 
@@
 Kristopher J. Overholt \\
+Craig G. Weinschenk \\
 Daniel Madrzykowski \\
-Craig G. Weinschenk \\
 {\em Fire Research Division \\
@@
 \hspace{1.5in} \= \\
-MW \> Megawatt \\
-s \> second \\
+ft \> foot \\
+m \> meter \\
 min \> minute \\
-m \> meter \\
-ft \> foot \\
 Pa \> Pascal \\
 psi \> pound per square inch \\
-k \> thermal  conductivity \\
+s \> second \\
+W \> Watt \\
+$k$ \> thermal conductivity \\
 $\rho$ \> density \\
-c$_{p}$ \> specific heat \\
+$c_{p}$ \> specific heat \\
 \end{tabbing}
@@
 \chapter*{\centering Abstract}
-\addcontentsline{toc}{chapter}{Abstract}
-% The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2 story, single family structure in XXXX, that resulted in the death of XXXX.
-The inputs for the FDS simulations are documented in this report.
+The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2~\sfrac{1}{2}~story, single family structure in San Francisco, CA, that resulted in the death of two firefighters.
+The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
@@
 The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at face height.
+The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at a height of 1.86~m (6~ft).
 Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
-The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.
+It appears that the captain was likely overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday call, the captain was rescued from the structure, but later succumbed to his injuries.
 
 \chapter{Introduction}
-Part of the mission of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
-The objective of all of these studies has been to improve the safety of fire fighters.
+The objective of these studies has been to improve the safety and effectiveness of firefighters.
 
-% On November 2, 2012, a fire in a 2~\sfrac{1}{2} story wood frame residential structure claimed the life of a Chicago fire captain.
+On November 2, 2012, a fire in a 2~\sfrac{1}{2}~story wood frame residential structure claimed the life of a captain of the Chicago Fire Department.
 NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
-Computer simulations of the fire incident were conducted using Fire Dynamics Simulator and Smokeview to provide insight into the fire development and thermal conditions that might have existed in the residence during the fire.
+Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
@@
 \item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
-\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department experienced during the course of their interior operations.
+\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department likely experienced during the course of their interior operations.
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.1.1) simulations.
+This document describes the input and the results of the FDS (version 6.0.0) simulations.
+The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
+Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
+This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
+Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
 
-\chapter{Fire Incident Summary}
+\chapter{Summary of the Fire Incident}
 \label{fire_sum}
-The account of events for this incident follows the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
-For the purpose of this analysis, the details regarding times are considered to be approximate values.
+The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
+For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
 The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer}:
@@
 He stated that he noticed fire light-up in the stairwell.
-He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], preceded to walk in, saw no fire then backed out.
+He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], [proceeded] to walk in, saw no fire then backed out.
 
@@
 
-\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events. A plan view of the structure and the location where the captain collapsed are shown in Fig.~(\ref{fig:simp_geom}).
+\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}, and more details of the fire development are provided in the following sections.
+
 \begin{table}
 \centering
-\captionof{table}{Abridged NIOSH approximate fire event timeline}\label{tab:fire_info}
+\captionof{table}[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 \label{model}
-Fire Dynamics Simulator is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
@@
 The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
-The following subsections will describe the inputs that were used to construct the simulation, including any engineering approximations or assumptions that were made.
+
+The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
+Based on the goals of the analysis and the information collected, several engineering approximations were made.
+For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
+The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+
+In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
 
@@
 \label{geom}
-The structure involved in this fire incident was a 2~\sfrac{1}{2} story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
 Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~(\ref{fig:simp_geom}).
+One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~\ref{fig:simp_geom}.
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
-The interior walls were constructed from nominal lumber with 12.7~mm (0.5~in) gypsum board over top~\cite{NIOSH:Bowyer}.
+The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer}.
 Additionally, there was a half-story attic that contained the structure's hot water heater.
-Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~(\ref{fig:simp_geom})), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~(\ref{fig:simp_geom})) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~(\ref{fig:simp_geom})).
-Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~(\ref{fig:simp_geom}).
+Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~\ref{fig:simp_geom}), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~\ref{fig:simp_geom}) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~\ref{fig:simp_geom}).
+Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
+
 The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
 Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
-Figure~(\ref{fig:alpha_ex}) shows the exterior of the front and rear of the structure after the incident.
+Figure~\ref{fig:alpha_ex} shows the exterior of the front and rear of the structure after the incident.
 Note that the majority of the damage occurred in the attic and rear porch on the second floor.
-Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~(\ref{fig:first_floor} and \ref{fig:second_floor}), respectively.
+Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
 
@@
 
-%%%Fig.~(\ref{fig:smv_interior}) shows 3D Smokeview renderings of cutaways of the beta and delta sides of the structure interior.
-%%%\begin{figure}[!ht]
-%%%\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%%%\includegraphics[width=.80\textwidth]{../Figures/interior_beta} \\
-%%%\includegraphics[width=.80\textwidth]{../Figures/interior_delta} \\
-%%%\end{tabular*}
-%%%\caption{3D Smokeview rendering of structure interior looking from the charlie side to both the beta side (top) and to the delta side (bottom)}
-%%%\label{fig:smv_interior}
-%%%\end{figure}
+\clearpage
 
@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these findings, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
+Based on these sources of information, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
 The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board.
 
-Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$).
-The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the SFPE Handbook~\cite{SFPE:Tewarson}.
+Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
 A balanced chemical reaction for wood combustion can written as:
@@
 
-An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (2~min and 40~s into the simulation).
+An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
 The area of failure was also estimated based on the following observations.
-The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~(\ref{fig:door_frame}).
+The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~\ref{fig:door_frame}.
 It appears that the door collapsed and failed partially open.
@@
 
-% \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
-% \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
-Note that the hinge is still intact and there is unburned, ``clean'' wood at along the bottom portion of the frame.}
-% \label{fig:door_frame}
-% \end{figure}
+\clearpage
 
@@
 \end{tabular}\par
+\footnotesize
+$^*$These ventilation events were not included in the alternative simulation.
+\normalsize
 \end{table}
+
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
+% \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
+Note that the hinge is still intact and there is unburned, ``clean'' wood along the bottom portion of the frame.}
+% \label{fig:door_frame}
+% \end{figure}
+
+\clearpage
 
@@
 \end{equation}
-From the FDS User Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
+From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
 relation $Q^* = (D^*/D)^{5/2}$.
-Here, $D$ is the physical diameter of the fire as it is specified in the simulation.
-Following Eq.~(\ref{eq:mesh}) and using 10 cm grid cells, the ratio of the characteristic fire diameter to the cell size ($D^*/\dx$) is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were judged to be adequate for engineering calculations.
-The grid resolution used in this model is within typical engineering $D^*/\dx$ values.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
+The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
+
+As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
+The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
+A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~(\ref{fig:geom_grid}) shows the front of the structure rendered in Smokeview with the 10 cm mesh.
+Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
+Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
+Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 % \end{tabular*}
-% \caption{Front (left) and rear (right) of the structure with 10 cm computational mesh.}
+% \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
 % \label{fig:geom_grid}
 % \end{figure}
-
-As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
-To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-At a grid resolution of 10~cm (3.9~in), this results in 2.4 million computational cells.
-The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
-Figure~(\ref{fig:mult_mesh}) shows the entire structure within the computational domain that has been divided into multiple meshes.
-For the simulations that were conducted as part of this study, Table~\ref{tab:mod_param} shows the relevant model input parameters that were discussed in Section~\ref{model}.
 
@@
 \toprule[1.5pt]
-Parameter & Description & Reference  \\
+Parameter                                                  & Description                                   & Discussion                            \\
 \midrule
- Simulation Time                   &  5 min                                                        & -- \\[.25cm]
- Grid Cell Size                    &  10 cm                                                        & Section~\ref{mesh} \\ [.25cm]
- Ambient Temperature               &  25 $^{\circ}$C                                               & -- \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood}    &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$                     & \multirow{4}{*}{Section~\ref{fire}} \\
-                                   &  CO Yield: 0.004 \; $\mathrm{kg}/\mathrm{kg}$   & \\
-                                   &  Soot Yield: 0.015 \; $\mathrm{kg}/\mathrm{kg}$  & \\
+Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
+Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
+Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
+\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
+                                                           &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                       \\
+                                                           &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                       \\
                                                            &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
-\multirow{2}{*}{Peak HRR}          &  Attic Fire: 9~MW                                             & \multirow{2}{*}{Section~\ref{fire}}\\ 
+\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{fire}}   \\ 
                                                            &  Porch Fire: 3.3~MW                           &                                       \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood}    &  k: 0.12 \; \si{W/(m.K)})                                     & \multirow{3}{*}{Section~\ref{matl}} \\
-                                   &  $\rho$: 510 \; kg/m$^3$                                      & \\
-                                   &  c$_{p}$: 1.38 \; \si{kJ/(kg.K)}                              & \\[.25cm]
-\multirow{3}{*}{Material: Gypsum}  &  k: 0.28 \; \si{W/(m.K)}                                      &  \multirow{3}{*}{Section~\ref{matl}}\\ 
-                                   &  $\rho$: 810 \; kg/m$^3$                                      & \\ 
-                                   &  c$_{p}$: 1.0 \; \si{kJ/(kg.K)}                              & \\
+\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\
+                                                           &  $\rho$: 510~kg/m$^3$                         &                                       \\
+                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                       \\ [.25cm]
+\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
+                                                           &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
+                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
 \bottomrule[1.25pt]
 \end{tabular}\par
+\footnotesize
+$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+\normalsize
 \end{table}
@@
 \end{tabular}\par
+\footnotesize
+For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
+\normalsize
 \end{table}
@@
 The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Figure~(\ref{fig:hrr}) shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
+Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
 The two vertical lines represent the time at which a firefighter opened the back door of the structure ($t$ = 130 s) and the time at which the second floor interior door was estimated to fail ($t$ = 160 s).
 Due to a lack of information about the time of fire ignition or how fast the fire grew, these parameters needed to be estimated.
-The growth rate shown in Fig.~(\ref{fig:hrr}) (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
-The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while still aligning with the timeline observations of video and picture evidence from the fire.
-The accuracy of heat transfer to the walls of the structure may be sacrificed by using this approach; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
+The growth rate shown in Fig.~\ref{fig:hrr} (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
+The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while aligning with the timeline observations of video and picture evidence from the fire.
+Using this approach, the accuracy of heat transfer to the walls of the structure may be sacrificed; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
 
@@
 % \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
-The first vertical line indicates the time at which the back door failed, and the second vertical line indicates the time at which the interior hallway door failed.}
+The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
 % \label{fig:hrr}
@@
 
-In Fig.~(\ref{fig:hrr}), the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
+In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
 The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur.
 The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS.
-As shown in Fig.~(\ref{fig:hrr}), the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
+As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
 The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay.
 The HRR is reduced to 5~MW as the oxygen inside the structure is consumed.
-There is an insufficient amount of oxygen in the structure to combust all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
-Figure~(\ref{fig:smv_ext_fire}) shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
+There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
+Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
 After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
@@
 
+\clearpage
+
 \section{Pressure}
 
-As the fire grows in the attic and rear porch, the pressure rises.
-Figure~(\ref{fig:pres_159s}) shows the pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa over pressure 1~m off the floor to greater than 10~Pa (0.00145~psi) at the ceiling.
+As the simulated fire grows in the attic and rear porch, the pressure rises.
+Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
+On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
 Gases at an elevated pressure will always move towards a region of lower pressure.
@@
 Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
-The velocity vectors shown in Fig.~(\ref{fig:velo_175s}), 15~s after the interior door fails, confirm this flow direction within the structure.
+The velocity vectors shown in Fig.~\ref{fig:velo_175s} (15~s after the interior door fails) indicate the direction of flow within the structure.
 
@@
 % \input{../Scripts/colorbar_metric_pres}
-% \caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.
-Note that 1~Pa is equal to $1.4 \times 10 ^{-4}$~psi.}
+% \caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.}
 % \label{fig:pres_159s}
@@
 
-% \newpage
+% \clearpage
+
 % \begin{landscape}
@@
 \label{temp}
-Analysis of the temperatures from the FDS simulation will focus on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-The temperature profile at these high hazard areas will be shown via several snapshots in time to illustrate the change in the interior conditions.
-The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~(\ref{fig:temp_129s})), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~(\ref{fig:temp_159s})).
+Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+The temperature profile at these high hazard areas is shown via several snapshots in time to illustrate the change in the interior conditions.
+The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~\ref{fig:temp_129s}), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~\ref{fig:temp_159s}).
 
@@
 
-Figure~(\ref{fig:temp_129s}) shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
-Before the interior door fails (Fig.~(\ref{fig:temp_159s})), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time the HRR increases because of the additional ventilation, as shown in Fig.~(\ref{fig:hrr}).
-As shown in Fig.~(\ref{fig:temp_161s}), after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
+Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}.
+As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
 Note that the conditions in the attic do not appear to change.
@@
 
-As shown in Fig.~(\ref{fig:temp_175s}), 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
+As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
 
-\chapter{Discussion}
-The results of the FDS simulations will be discussed in two sections.
-The first section will address the results of the computational modeling as they relate to the interior hallways conditions.
-The second section will examine the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
+\chapter{Discussion of Simulation Results}
+\label{discussion}
+The results of the FDS simulations are discussed in the following two sections.
+The first section addresses the results of the computational modeling as they relate to the interior hallways conditions.
+The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
 
-\section{Hallway Flow Path}
+\section{Simulated Hallway Flow Path}
 From on-scene reports (Section~\ref{fire_sum}) and the FDS simulation results (Section~\ref{temp}), the interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
+From the NIOSH report~\cite{NIOSH:Bowyer}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
 This indicated the presence of fire in the area of the enclosed porch.
-The simulation results indicate a high hazard area in the attic and the enclosed porch at this time.
+The simulation results indicate a high hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the attic and the enclosed porch at this time.
 By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
 Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
-Exposure to these conditions weakened the structural integrity of the door, which may have lead to a partial failure.
-Figure~(\ref{fig:chicago_doorfold}) shows the state of the rear door after the fire.
+Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:firesim}).
+Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
 Note the large crease in the steel face of the door just above the knob.
@@
 Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
-Figure~(\ref{fig:SC_doorfold}) shows doors from two different residential fire experiments in different stages of degradation.
+Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation.
 In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
-This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in the studied fire incident.
+This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in this fire incident.
 
@@
 
-After the interior door failed, an interior flow path from the enclosed porch to the kitchen of the structure was created.
+After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.
 This resulted in a rapid change in the conditions within the flow path.
-The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door to lower pressure areas in the hallways and kitchen, where the conditions seemed to equilibrate.
-The arrows in Fig.~(\ref{fig:flowpath_1}) show the flow direction of gases on the second floor following the door failure.
+The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door and flowed towards lower pressure areas in the hallways and kitchen.
+The arrows shown in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor after the door failure.
+In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures.
+The arrow that transitions from red to blue indicates that the heated gases were cooling as they flowed away from the fire towards the front of the structure.
+The two arrows located at the door on the second floor (towards the front of the structure) indicate bi-directional flow.
+At that doorway, cool ambient air flowed towards the fire near the bottom of the door, and hot gases flowed away from the fire near the top of the door.
 
@@
 % \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-% \caption{Flow path on the second floor after interior door failure.}
+% \caption{Summary of simulated flow path on the second floor after interior door failure.}
 % \label{fig:flowpath_1}
@@
 
-\subsection{Assessing the Hazard}
+\clearpage
 
-A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{designation2003c}.
-While firefighters wear protective gear, gear only offers a finite amount of protection.
+\section{Assessing the Hazard}
+
+A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
+Although firefighters wear protective gear, gear only offers a finite amount of protection.
 The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
@@
 Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
+Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class III exposure~\cite{Donnelly2006}.
+Firefighters are at increased risk levels when encountering Class III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
 Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 
-Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~(\ref{fig:temp_top_159}).
+Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~\ref{fig:temp_top_159}.
 The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
-Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~(\ref{fig:temp_top_165}).
-Within one minute of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~(\ref{fig:temp_top_220}).
+Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~\ref{fig:temp_top_165}.
+Within 60~s of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~\ref{fig:temp_top_220}.
 These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
 The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Figure~(\ref{fig:temp_top_220}) also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
+Figure~\ref{fig:temp_top_220} also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
 At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas.
@@
 
-In the present fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in lethal conditions.
-Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the fire fighters faced on the fire ground.
+In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
+These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
+Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.
 In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
-Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of fire fighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
+Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
 
@@
                                     &                     &  entry door and garage                   \\
-F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartment             \\
+F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartme  \\
 F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed         \\
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2 \sfrac{1}{2} story single family structure in Chicago, IL, that resulted in the death of a fire captain.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3~MW.
+This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure.
 However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
+
 The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
@@
 The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway at face height exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
-
-Unfortunately a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
+The temperature of the gases that flowed into the hallway at face height was calculated to exceed 260~$^{\circ}$C (500~$^{\circ}$F).
+Unfortunately, a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
 The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
@@
 
-\chapter{Acknowledgments}
+\chapter*{Acknowledgments}
 The authors would like to thank XXXX.
 The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}.
-Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
+Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.
 
@@
 \chapter{Dimensioned Drawings}
+\label{app_draw}
 

### 2014-08-11 Studies/2011_San_Francisco/Report/SF_Fire.tex
San Francisco: Edits to tables and styling throughout

@@
 \chapter*{\centering Abstract}
+
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2~\sfrac{1}{2}~story, single family structure in San Francisco, CA, that resulted in the death of two firefighters.
@@
 \chapter{Introduction}
+\label{sec:introduction}
+
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
@@
 Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
-This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
-Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
+This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{sec:model_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
+Appendix~\ref{sec:drawings} contains dimensioned drawings of the first and second floor of the structure.
 
 \chapter{Summary of the Fire Incident}
-\label{fire_sum}
+\label{sec:incident_summary}
+
 The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
@@
 
-\begin{table}
-\centering
-\captionof{table}[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}\label{tab:fire_info}
+\begin{table}[!ht]
+\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}
 \begin{tabular}{cl}
-\toprule[1.5pt]
+\toprule
 Incident Time  &  Fire Behavior / Fireground Operation                       \\
-{[hh:mm:ss]}               &                                                                                                                                          \\
+{(hh:mm:ss)}   &                                                             \\
 \midrule
-\multirow{2}{*}{17:15:00}  &  \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
-                           &                                                                                                                                          \\[.25cm] %blank rows exist for wrapping text.
-# of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
-                           &                                                                                                                                          \\[.25cm]
-\multirow{2}{*}{17:20:00}  &  \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}}      \\
-                           &                                                                                                                                          \\[.25cm] 
-17:21:00                   &  E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.                                                          \\[.25cm]
-17:21:30                   &  First floor exterior porch door opened.                                                                                                 \\[.25cm]
-\multirow{2}{*}{17:23:00}  &  \multirow{2}{*}{\parbox{10cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}}  \\
-                           &                                                                                                                                          \\[.25cm]
-17:24:00                   &   Water applied to attic from the rear exterior position.                                                                                \\[.25cm]
-17:25:00                   &   SQ5 makes entry through front of structure.                                                                                            \\[.25cm]
-17:27:00                   &   After hearing a Mayday call from SQ5, IC calls a Mayday.                                                                               \\[.25cm]
+17:15:00       &  Reported working fire with heavy smoke coming from the     \\ 
+               &  front and rear of the structure's attic.                   \\
+               &                                                             \\
+17:16:00       &  Dispatch for a ``Still'' alarm - two engine companies,     \\
+               &  two truck companies, and a battalion chief.                \\
+               &                                                             \\
+17:20:00       &  Attic windows break - heavy smoke out of front attic       \\
+               &  window and heavy smoke and fire out of rear.               \\
+               &                                                             \\
+17:21:00       &  E123 captain and firefighter on second floor               \\
+               &  with 1\sfrac{3}{4}-inch hoseline.                          \\
+               &                                                             \\
+17:21:30       &  First floor exterior porch door opened.                    \\
+               &                                                             \\
+17:23:00       &  Heavy fire report in rear stairwell and enclosed porch.    \\
+               &  No response from E123 captain or firefighter.              \\
+               &                                                             \\
+17:24:00       &  Water applied to attic from the rear exterior position.    \\
+               &                                                             \\
+17:25:00       &  SQ5 makes entry through front of structure.                \\
+               &                                                             \\
+17:27:00       &  After hearing a Mayday call from SQ5, IC calls a Mayday.   \\
+               &                                                             \\
 17:29:00       &  E123 captain carried out of structure.                     \\
-\bottomrule[1.25pt]
-\end{tabular}\par
+\bottomrule
+\end{tabular}
+\label{tab:fire_info}
 \end{table}
@@
 \chapter{Model Description}
-\label{model}
+\label{sec:model_description}
+
 Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
@@
 \section{Geometry}
-\label{geom}
+\label{sec:geometry}
+
 The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
@@
 
-The fire, which is described in Section~\ref{fire}, started in the attic and spread to the rear porch.
-Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
+The fire, which is described in Section~\ref{sec:fire}, started in the attic and spread to the rear porch.
+Discussion of the fire's impact on the interior conditions is provided in Section~\ref{sec:model_results}.
 Figure~\ref{fig:alpha_ex} shows the exterior of the front and rear of the structure after the incident.
@@
 % \begin{figure}[!ht]
-% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-% \includegraphics[width=\textwidth]{../Figures/1st_Floor_Metric} \\
-% \includegraphics[width=\textwidth]{../Figures/2nd_Floor_Metric}
-% \end{tabular*}
+% \includegraphics[width=in]{../Figures/1st_Floor_Metric} \\
+% \includegraphics[width=in]{../Figures/2nd_Floor_Metric}
 % \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
@@
 % \begin{figure}[!ht]
-% \centering
-% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/exterior_alpha} } &
-%    \scalebox{1.0}{ \includegraphics[width=2.67in]{../Figures/exterior_charlie} } \\
-% \end{tabular*}
+% \includegraphics[width=3in]{../Figures/exterior_alpha} \\
+% \includegraphics[width=2.67in]{../Figures/exterior_charlie}
 % \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
@@
 \section{Fire}
-\label{fire}
+\label{sec:fire}
 
@@
 \section{Materials}
-\label{matl}
-While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+\label{sec:materials}
+
+While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
@@
 \section{Ventilation}
-\label{Vents}
+\label{sec:ventilation}
+
 The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
@@
 
-\begin{table}
-\centering
-\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
+\begin{table}[!ht]
+\caption[Timeline of ventilation changes in the simulation]{Timeline of ventilation changes in the simulation}
 \begin{tabular}{cccll}
-\toprule[1.5pt]
+\toprule
 Baseline    &  Alternative  &  Ventilation  &  Type         &  Side of         \\
@@
 160         &  160          &  0.80         &  Door         &  Interior        \\
-\bottomrule[1.25pt]
-\end{tabular}\par
+\bottomrule
+\end{tabular}
 \footnotesize
-$^*$These ventilation events were not included in the alternative simulation.
+\\$^*$These ventilation events were not included in the alternative simulation.
 \normalsize
+\label{tab:vents}
 \end{table}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.80\textwidth]{../Figures/door_frame_burn}
+% \includegraphics[width=.80in]{../Figures/door_frame_burn}
 % \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
@@
 \section{Numerical Mesh}
-\label{mesh}
+\label{sec:numerical_mesh}
 
@@
 
-As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+As discussed in Section~\ref{sec:geometry}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
@@
 % \begin{figure}[!ht]
-% \centering
-% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%    \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
-%    \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
-% \end{tabular*}
+% \includegraphics[width=.49in]{../Figures/smv_exterior_grid} \\
+% \includegraphics[width=.488in]{../Figures/smv_exterior_grid_rear}
 % \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-% \caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
-Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
+% \includegraphics[width=.60in]{../Figures/smv_exterior_mesh}
+% \caption[Front-right side of the structure within the computational domain.]
+% {Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
 % \label{fig:mult_mesh}
@@
 
-\begin{table}
-\centering
-\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
+\begin{table}[!ht]
+\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
 \begin{tabular}{lll}
-\toprule[1.5pt]
+\toprule
 Parameter                                                  & Description                                   & Discussion                                     \\
@@
 Simulation Time                                            &  5~min                                        & --                                             \\ [.25cm]
-Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
+Grid Cell Size                                             &  10~cm                                        & Section~\ref{sec:numerical_mesh}               \\ [.25cm]
 Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                             \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
+\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{sec:fire}}        \\
                                                            &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                                \\
@@
                                                            &  Heat of Combustion: 16,400~kJ/kg             &                                                \\ [.25cm]
-\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{fire}}   \\ 
+\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{sec:fire}}        \\ 
                                                            &  Porch Fire: 3.3~MW                           &                                                \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\
+\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{sec:materials}}   \\
                                                            &  $\rho$: 510~kg/m$^3$                         &                                                \\
                                                            &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                                \\ [.25cm]
-\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
+\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{sec:materials}}  \\ 
                                                            &  $\rho$: 810~kg/m$^3$                         &                                                \\ 
                                                            &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                                \\
-\bottomrule[1.25pt]
-\end{tabular}\par
+\bottomrule
+\end{tabular}
 \footnotesize
-$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
 \normalsize
+\label{tab:mod_param}
 \end{table}
@@
 \chapter{Model Results}
-\label{results}
+\label{sec:model_results}
 
@@
 
-\begin{table}
-\centering
-\captionof{table}{Fire incident and simulation event timeline}\label{tab:firesim}
+\begin{table}[!ht]
+\caption[Fire incident and simulation event timeline]{Fire incident and simulation event timeline}
 \begin{tabular}{ccl}
-\toprule[1.5pt]
-Incident Time  &  Simulation Time  &  Fire Behavior / Fireground Operation  \\
-{[hh:mm:ss]}   &  {[s]}            &                                        \\
+\toprule
+Incident Time  &  Simulation  &  Fire Behavior / Fireground Operation                            \\
+               &  Time        &                                                                  \\
+{(hh:mm:ss)}   &  {(s)}       &                                                                  \\
 \midrule
-\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Fire is reported with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
-         & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
-         & & \\[.25cm]
-\multirow{3}{*} {} &  \multirow{3}{*} {0} &  \multirow{3}{*}{\parbox{8cm} {FDS simulation starts. Attic fire ignites. Initial ventilation through rear of structure. Front door open.}} \\
-         & & \\[0.25cm]
-         & & \\[0.25cm]
-\multirow{3}{*}{17:20:00} & \multirow{3}{*}{40}  & \multirow{3}{*}{\parbox{9cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.
-Rear porch ignites in model.}} \\
-         & & \\[.25cm]
-         & & \\[.25cm]  
-\multirow{2}{*}{}  & \multirow{2}{*}{45} & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on rear of structure.}} \\
-          & & \\[.25cm] 
-\multirow{2}{*}{}  & \multirow{2}{*}{55}  & \multirow{2}{*}{\parbox{8cm}{Ventilation through wall penetration on left side of structure.}} \\ 
-          & & \\[.25cm] 
-\multirow{2}{*}{17:21:00} & \multirow{2}{*}{100} & \multirow{2}{*}{\parbox{8cm}{E123 captain and firefighter on second floor with 1\sfrac{3}{4}-inch hoseline.}} \\
-         &  & \\[.25cm]
-\multirow{2}{*}{17:21:30} & \multirow{2}{*}{130} &  \multirow{2}{*}{\parbox{8cm}{First floor exterior porch door opened. Porch fire ignites in FDS model.}} \\
-        &  & \\[.25cm]
-        & 135 & Ventilation through left side of structure. \\[.25cm] 
-        & 160 & Top of interior door fails in FDS model. \\[.25cm] 
-\multirow{3}{*}{17:23:00}    & \multirow{3}{*}{220} & \multirow{3}{*}{\parbox{8cm} {Heavy fire report in rear stairwell and enclosed porch. No response from E123 captain or firefighter.}} \\
-         & & \\[.25cm]
-         & & \\[.25cm]  
-17:24:00    &   & Water applied to attic from the rear exterior position. \\[.25cm]
-17:25:00    &   & SQ5 makes entry through front of structure. \\[.25cm]
-\multirow{2}{*}{17:27:00}    & \multirow{2}{*}{300}  & \multirow{2}{*}{\parbox{8cm} {After hearing a Mayday call from SQ5, IC calls a Mayday. Simulation ends.}}\\
-         & &  \\[.25cm]
+17:15:00       &              &  Fire is reported with heavy smoke coming from the               \\ 
+               &              &  front and rear of the structure's attic.                        \\
+               &              &                                                                  \\
+17:16:00       &              &  Dispatch for a ``Still'' alarm - two engine companies,          \\
+               &              &  two truck companies, and a battalion chief.                     \\
+               &              &                                                                  \\
+               &  0           &  FDS simulation starts. Attic fire ignites. Initial              \\
+               &              &  ventilation through rear of structure. Front door open.         \\
+               &              &                                                                  \\
+17:20:00       &  40          &  Attic windows break - heavy smoke out of front attic            \\
+               &              &  window and heavy smoke and fire out of rear.                    \\
+               &              &  Rear porch ignites in model.                                    \\
+               &              &                                                                  \\
+               &  45          & Ventilation through wall penetration on rear of structure.       \\
+               &              &                                                                  \\
+               &  55          & Ventilation through wall penetration on left side of structure.  \\
+               &              &                                                                  \\
+17:21:00       &  100         & E123 captain and firefighter on second floor                     \\
+               &              & with 1\sfrac{3}{4}-inch hoseline.                                \\
+               &              &                                                                  \\
+17:21:30       &  130         & First floor exterior porch door opened.                          \\
+               &              & Porch fire ignites in FDS model.                                 \\
+               &              &                                                                  \\
+               &  135         & Ventilation through left side of structure.                      \\
+               &              &                                                                  \\
+               &  160         & Top of interior door fails in FDS model.                         \\
+               &              &                                                                  \\
+17:23:00       &  220         & Heavy fire report in rear stairwell and enclosed porch.          \\
+               &              & No response from E123 captain or firefighter.                    \\
+               &              &                                                                  \\
+17:24:00       &              & Water applied to attic from the rear exterior position.          \\
+               &              &                                                                  \\
+17:25:00       &              & SQ5 makes entry through front of structure.                      \\
+               &              &                                                                  \\
+17:27:00       &  300         & After hearing a Mayday call from SQ5, IC calls a Mayday.         \\
+               &              & Simulation ends.                                                 \\
+               &              &                                                                  \\
 17:29:00       &              & E123 captain carried out of structure.                           \\
-\bottomrule[1.25pt]
-\end{tabular}\par
+\bottomrule
+\end{tabular}
 \footnotesize
-For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
+\\ For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
 \normalsize
+\label{tab:firesim}
 \end{table}
@@
 \section{Heat Release Rate}
-\label{HRR}
+\label{sec:HRR}
+
 The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{Vents}.
+Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
 The two vertical lines represent the time at which a firefighter opened the back door of the structure ($t$ = 130 s) and the time at which the second floor interior door was estimated to fail ($t$ = 160 s).
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.80\textwidth]{../Figures/Chicago_Fire_HRR}
-% \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
+% \includegraphics[width=.80in]{../Figures/Chicago_Fire_HRR}
+% \caption[HRR versus time from the FDS simulations.]
+% {HRR versus time from the FDS simulations.
 The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
+% \includegraphics[width=.675in]{../Figures/smv_exterior_fire}
 % \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.75\textwidth]{../Figures/west_50th_baseline_pres2}
+% \includegraphics[width=.75in]{../Figures/west_50th_baseline_pres2}
 % \input{../Scripts/colorbar_metric_pres}
@@
 % \begin{landscape}
-% \centering
 % \begin{figure}[!ht]
-% \includegraphics[width=1.1\textwidth]{../Figures/west_50th_baseline_velo_175}
+% \includegraphics[width=1.1in]{../Figures/west_50th_baseline_velo_175}
 % \input{../Scripts/colorbar_std_velo}
@@
 \section{Temperature}
-\label{temp}
+\label{sec:temperature}
+
 Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_129}
+% \includegraphics[width=.675in]{../Figures/west_50th_baseline_129}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_159}
+% \includegraphics[width=.675in]{../Figures/west_50th_baseline_159}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_161}
+% \includegraphics[width=.675in]{../Figures/west_50th_baseline_161}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675\textwidth]{../Figures/west_50th_baseline_175}
+% \includegraphics[width=.675in]{../Figures/west_50th_baseline_175}
 % \input{../Scripts/colorbar_std} 
@@
 \chapter{Discussion of Simulation Results}
-\label{discussion}
+\label{sec:discussion}
+
 The results of the FDS simulations are discussed in the following two sections.
@@
 \section{Simulated Hallway Flow Path}
-From on-scene reports (Section~\ref{fire_sum}) and the FDS simulation results (Section~\ref{temp}), the interior conditions on the second floor of the structure were initially tenable.
+From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions on the second floor of the structure were initially tenable.
 From the NIOSH report~\cite{NIOSH:Bowyer}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
+% \includegraphics[width=.4in]{../Figures/Porch_Door_1}
 % \caption{Post-fire image of interior door.}
@@
 % \begin{figure}[!ht]
-% \centering
-% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-%    \scalebox{1.0}{ \includegraphics[width=3in]{../Figures/SC_Door_1} } &
-%    \scalebox{1.0}{ \includegraphics[width=2in]{../Figures/SC_Door_2} } \\
-% \end{tabular*}
+% \includegraphics[width=3in]{../Figures/SC_Door_1} \\
+% \includegraphics[width=2in]{../Figures/SC_Door_2}
 % \caption{Post-experiment images of door failures.}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
+% \includegraphics[width=.7in]{../Figures/ChicagoFlow}
 % \caption{Summary of simulated flow path on the second floor after interior door failure.}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_159_6ft}
+% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_159_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_165_6ft}
+% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_165_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=.68\textwidth]{../Figures/west_50th_baseline_top_220_6ft}
+% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_220_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 
-\begin{table}
-\centering
-\captionof{table}{Flow path related LODD/LODI incidents}\label{tab:lodd}
+\begin{table}[!ht]
+\caption[Flow path related LODD/LODI incidents]{Flow path related LODD/LODI incidents}
 \begin{tabular}{lll}
-\toprule[1.5pt]
+\toprule
 NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details  \\
@@
                                     &  1 LODI             &  porch and then into 2nd floor           \\
-\bottomrule[1.25pt]
-\end{tabular}\par
+\bottomrule
+\end{tabular}
+\label{tab:lodd}
 \end{table}
@@
 \chapter{Summary}
+\label{sec:summary}
+
 NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
@@
 \chapter{Dimensioned Drawings}
-\label{app_draw}
+\label{sec:drawings}
 
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
+% \includegraphics[width=1in]{../Figures/50th_Place_1st_Floor}
 % \caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
@@
 % \begin{figure}[!ht]
-% \centering
-% \includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
+% \includegraphics[width=1in]{../Figures/50th_Place_2nd_Floor}
 % \caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}

### 2014-08-11 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Rename tex file

--- 2014-08-11 Studies/2011_San_Francisco/Report/SF_Fire.tex
@@
 
-\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+\noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events.
 A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}, and more details of the fire development are provided in the following sections.
@@
 \end{tabular}
-\label{tab:fire_info}
+\label{tab:incident_timeline}
 \end{table}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=in]{../Figures/1st_Floor_Metric} \\
-% \includegraphics[width=in]{../Figures/2nd_Floor_Metric}
+% \includegraphics[width=5in]{../Figures/1st_Floor_Metric} \\
+% \includegraphics[width=5in]{../Figures/2nd_Floor_Metric}
 % \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=3in]{../Figures/exterior_alpha} \\
-% \includegraphics[width=2.67in]{../Figures/exterior_charlie}
+% \includegraphics[width=5in]{../Figures/exterior_alpha} \\
+% \includegraphics[width=5in]{../Figures/exterior_charlie}
 % \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
@@
 The second scenario, or alternative simulation, does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
-The times of the ventilation changes are provided in Table~\ref{tab:vents}.
+The times of the ventilation changes are provided in Table~\ref{tab:ventilation_timeline}.
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
@@
 
-An unknown parameter in Table~\ref{tab:vents} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
+An unknown parameter in Table~\ref{tab:ventilation_timeline} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
 The area of failure was also estimated based on the following observations.
@@
 \normalsize
-\label{tab:vents}
+\label{tab:ventilation_timeline}
 \end{table}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.80in]{../Figures/door_frame_burn}
+% \includegraphics[width=5in]{../Figures/door_frame_burn}
 % \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
@@
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=.49in]{../Figures/smv_exterior_grid} \\
-% \includegraphics[width=.488in]{../Figures/smv_exterior_grid_rear}
+Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
+
+% \begin{figure}[!ht]
+% \includegraphics[width=5in]{../Figures/smv_exterior_grid} \\
+% \includegraphics[width=5in]{../Figures/smv_exterior_grid_rear}
 % \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.60in]{../Figures/smv_exterior_mesh}
+% \includegraphics[width=5in]{../Figures/smv_exterior_mesh}
 % \caption[Front-right side of the structure within the computational domain.]
@@
 \midrule
-Simulation Time                                            &  5~min                                        & --                                             \\ [.25cm]
-Grid Cell Size                                             &  10~cm                                        & Section~\ref{sec:numerical_mesh}               \\ [.25cm]
-Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                             \\ [.1cm]
-\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{sec:fire}}        \\
+Simulation Time                           &  5~min                                        &  --                                \\
+Grid Cell Size                            &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
+Ambient Temperature$^*$                   &  20~$^{\circ}$C (77~$^{\circ}$F)              &  --                                \\
+Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fire}            \\
                                           &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
                                           &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
-                                                           &  Heat of Combustion: 16,400~kJ/kg             &                                                \\ [.25cm]
-\multirow{2}{*}{Peak HRR}                                  &  Attic Fire: 9~MW                             & \multirow{2}{*}{Section~\ref{sec:fire}}        \\ 
-                                                           &  Porch Fire: 3.3~MW                           &                                                \\ [.25cm]                     
-\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{sec:materials}}   \\
+                                          &  Heat of Combustion: 16,400~kJ/kg             &                                    \\
+Peak HRR                                  &  Attic Fire: 9~MW                             &  Section~\ref{sec:fire}            \\
+                                          &  Porch Fire: 3.3~MW                           &                                    \\
+Material: Wood~\cite{Incropera:1}         &  $k$: 0.12~\si{W/(m.K)})                      &  Section~\ref{sec:materials}       \\
                                           &  $\rho$: 510~kg/m$^3$                         &                                    \\
-                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                                \\ [.25cm]
-\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{sec:materials}}  \\ 
+                                          &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                    \\
+Material: Gypsum Board~\cite{WAKILI2007}  &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                           &  $\rho$: 810~kg/m$^3$                         &                                    \\
@@
 \normalsize
-\label{tab:mod_param}
+\label{tab:model_parameters}
 \end{table}
@@
 To examine the results of the simulations, it is important to link the timelines from the fire scene to the simulation times.
-Table~\ref{tab:firesim} shows the fireground timeline~\cite{NIOSH:Bowyer} along with the corresponding simulation times.
+Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{NIOSH:Bowyer} along with the corresponding simulation times.
 
@@
 \footnotesize
-\\ For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:vents}.
+\\ For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:ventilation_timeline}.
 \normalsize
-\label{tab:firesim}
+\label{tab:combined_timeline}
 \end{table}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.80in]{../Figures/Chicago_Fire_HRR}
+% \includegraphics[width=5in]{../Figures/Chicago_Fire_HRR}
 % \caption[HRR versus time from the FDS simulations.]
@@
 Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
-After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
+After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
 The HRR then increases towards a sustainable steady-state value.
@@
 At 130~s, the rear door is opened in the baseline simulation.
-At 135~s, there is an additional breach on the left side of the structure (Table~\ref{tab:vents}).
+At 135~s, there is an additional breach on the left side of the structure (Table~\ref{tab:ventilation_timeline}).
 The open door and breach act as additional pressure releases for the structure.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675in]{../Figures/smv_exterior_fire}
+% \includegraphics[width=5in]{../Figures/smv_exterior_fire}
 % \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.75in]{../Figures/west_50th_baseline_pres2}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_pres2}
 % \input{../Scripts/colorbar_metric_pres}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=1.1in]{../Figures/west_50th_baseline_velo_175}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_velo_175}
 % \input{../Scripts/colorbar_std_velo}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675in]{../Figures/west_50th_baseline_129}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_129}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675in]{../Figures/west_50th_baseline_159}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_159}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675in]{../Figures/west_50th_baseline_161}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_161}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.675in]{../Figures/west_50th_baseline_175}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_175}
 % \input{../Scripts/colorbar_std} 
@@
 The simulation results indicate a high hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the attic and the enclosed porch at this time.
-By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:firesim}) and approached the rear of the structure, the rear porch was fully involved.
+By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:combined_timeline}) and approached the rear of the structure, the rear porch was fully involved.
 Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
-Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:firesim}).
+Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:combined_timeline}).
 Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.4in]{../Figures/Porch_Door_1}
+% \includegraphics[width=5in]{../Figures/Porch_Door_1}
 % \caption{Post-fire image of interior door.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=3in]{../Figures/SC_Door_1} \\
-% \includegraphics[width=2in]{../Figures/SC_Door_2}
+% \includegraphics[width=5in]{../Figures/SC_Door_1} \\
+% \includegraphics[width=5in]{../Figures/SC_Door_2}
 % \caption{Post-experiment images of door failures.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.7in]{../Figures/ChicagoFlow}
+% \includegraphics[width=5in]{../Figures/ChicagoFlow}
 % \caption{Summary of simulated flow path on the second floor after interior door failure.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_159_6ft}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_159_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_165_6ft}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_165_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=.68in]{../Figures/west_50th_baseline_top_220_6ft}
+% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_220_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
-Table~\ref{tab:lodd} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
+Table~\ref{tab:LODD} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
 This table lists the NIOSH investigation number, the outcome, and a brief description of the flow path details.
@@
 \end{tabular}
-\label{tab:lodd}
+\label{tab:LODD}
 \end{table}
@@
 The authors would like to thank XXXX.
-The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:lodd}.
+The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}.
 Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=1in]{../Figures/50th_Place_1st_Floor}
+% \includegraphics[width=5in]{../Figures/50th_Place_1st_Floor}
 % \caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=1in]{../Figures/50th_Place_2nd_Floor}
+% \includegraphics[width=5in]{../Figures/50th_Place_2nd_Floor}
 % \caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}

### 2014-08-11 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: minor update timeline

@@
 \midrule
-\multirow{2}{*}{17:15:00}  &  \multirow{2}{*}{\parbox{10cm} {Reported working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
+\multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
+                           &                                                                                                                                          \\[.25cm]
+\multirow{2}{*}{17:17:00}  &  \multirow{2}{*}{\parbox{10cm} {On-scene report of a working fire with heavy smoke coming from the front and rear of the structure's attic.}}        \\ 
                            &                                                                                                                                          \\[.25cm] %blank rows exist for wrapping text.
 # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00}  &   \multirow{2}{*}{\parbox{10cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}}    \\
-                           &                                                                                                                                          \\[.25cm]
 \multirow{2}{*}{17:20:00}  &  \multirow{2}{*}{\parbox{10cm} {Attic windows break - heavy smoke out of front attic window and heavy smoke and fire out of rear.}}      \\

### 2014-08-11 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG County: update report, input files, and add department report

@@
 
-The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
-Based on the goals of the analysis and the information collected, several engineering approximations were made.
-For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
-The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+The analysis of the simulation results is focused on the impact of ventilation, specifically opening and closing the front door, on the conditions on the first floor of the structure.
 
@@
 
-\bibliography{../Bibliography/FDS_refs,../Bibliography/FDS_general,../Bibliography/FDS_mathcomp}
+\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
 

### 2014-08-11 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add NIOSH incident report

@@
 BC \> Battalion Chief \\
+DC \> Division Chief \\
 E \> Engine \\
@@
 LODD \> Line of Duty Death \\
+M \> Medic \\
 NIOSH \> National Institute for Occupational Safety and Health \\
 NIST \> National Institute of Standards and Technology \\
+RIC \> Rapid Intervention Crew \\
+RS \> Rescue Squad \\
 SFPE \> Society of Fire Protection Engineers \\
-SQ \> Squad \\
-TL \> Tower Ladder \\
+T \> Tower \\
 \end{tabbing}
@@
 
-The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on XXXX, within a 2~\sfrac{1}{2}~story, single family structure in San Francisco, CA, that resulted in the death of two firefighters.
+The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
 The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
-The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
-This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas.
-The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
+The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
+
+% The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
 After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward.
@@
 
-On November 2, 2012, a fire in a 2~\sfrac{1}{2}~story wood frame residential structure claimed the life of a captain of the Chicago Fire Department.
-NIST examined the fire dynamics of this incident at the request of NIOSH and the Chicago Fire Department.
+On June 2, 2011, a fire in a multi-level, wood-frame residential structure claimed the life of two firefighters of the San Francisco Fire Department.
+NIST examined the fire dynamics of this incident at the request of NIOSH and the San Francisco Fire Department.
 Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
@@
 \begin{enumerate}
-\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
-\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Chicago Fire Department likely experienced during the course of their interior operations.
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-level residential structure using physics-based calculations.
+\item To provide visualizations of the fire behavior that are representative of the conditions that members of the San Francisco Fire Department likely experienced during the course of their interior operations.
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.0.0) simulations.
+This document describes the input and the results of the FDS (version 6.1.1) simulations.
 The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
@@
 
-The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2012-28~\cite{NIOSH:Bowyer}.
+The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
-The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer}:
+The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer2}:
 \begin{quote}
-On November 2, 2012, a 54-year-old male career captain sustained injuries at a 2-1/2 story apartment building fire then died at the hospital.
-At 1716 hours, dispatch called a ``Still'' alarm\footnote{The department defines a ``Still'' alarm to be two engine companies, two truck companies, and a battalion chief.} for smoke in the area.
-Battalion Chief (BC) 19 was the first to leave the station that was just blocks away.
-He approached the fire structure by driving behind it then around to the front arriving on scene at 1717 hours.
-He reported a working fire with heavy smoke coming from the rear and front of the structure's attic.
-Per fire department standard operating procedures, dispatch initiated a RIT response\footnote{The department defines a rapid intervention team (RIT) response to be one truck company, one battalion chief, one advanced life support (ALS) ambulance, and one emergency medical services (EMS) field officer.}.
-At 1718 hours, E123 arrived on scene and BC19 was on scene and had assumed incident command (IC).
-The IC spoke with one of the occupants who stated everyone was out.
-The IC made entry through the front door to the stairwell to survey the interior of the 2\textsuperscript{nd} floor.
-He noticed only a light haze throughout and glow around the [rear] door to the covered porch.
-The IC came back to the front door and met the E123 captain and a firefighter.
-They had stretched a [hose] load which is 100 feet of 2\sfrac{1}{2}-inch, a gated wye, and 150 feet of 1\sfrac{3}{4}-inch hoseline to go to the 2\textsuperscript{nd} floor, which is a standard department hose lay for this type occupancy.
-At 1720 hours, E49, T33, and TL39 arrived on scene.
-
-The IC made entry to the 1\textsuperscript{st} floor apartment and worked his way to [the rear of the structure].
-He opened the [interior door opening into the rear foyer on the back side of the house] and noticed heavy fire in the covered porch and rear stairwell area.
-At 1721 hours, the [E123 captain] and firefighter were on the 2\textsuperscript{nd} floor where they flaked out, charged, and began advancing the hoseline to the rear door of the apartment.
-The E49 crew had stretched a 2\sfrac{1}{2}-inch hoseline [to the rear of the structure].
-The T33 crew set a ground ladder on [the left side of the structure] and TL39 set the aerial to the roof about a third of the way back on [the left side].
-A TL39 firefighter went to [the rear of the structure] to check doors.
-He first went to the basement door which he was unable to force open.
-Then, he went to the first floor exterior enclosed porch door which was unlocked and he opened it up.
-He stated that he noticed fire light-up in the stairwell.
-He kicked in the locked door [that connects the 1\textsuperscript{st} floor rear porch to the rear foyer], [proceeded] to walk in, saw no fire then backed out.
-
-At 1723 hours, the IC radioed the [E123 captain] that there was heavy fire in the covered porch and attic area and that E49 was going to put water on the fire, around the [rear] attic window, but there was no acknowledgment from the [captain].
-E49 proceeded to put water on the [rear of the structure].
-The IC returned out front to the command post and donned his turnout gear.
-The lieutenant from TL39, the lieutenant and 2 firefighters from SQ5, and a E123 firefighter/paramedic (FF/PM) were near the kitchen area on the 2\textsuperscript{nd} floor when they heard a loud commotion.
-The FF/PM heard the [E123 captain] yell ``get out of here.'' The FF/PM had no radio and he couldn't locate the [captain's] radio so he yelled Mayday as he tried to get the [captain] and other crew member untangled.
-The TL39 Lieutenant and SQ5 fire fighters heard the FF/PM's verbal Mayday and the SQ5 Lieutenant tried to transmit a Mayday over heavy radio traffic.
-
-At 1727 hours, the TL39 crew had just completed the first hole in the roof about midway on [the right side] roof with minimal fire showing, when they heard the Mayday.
-The IC verified that a firefighter was down, called a Mayday, and requested a 2-11 Assignment\footnote{The department defines a 2-11 alarm as a second alarm upgrade.
-The response is four engines, two trucks, one tower ladder, two battalion chiefs, one deputy district chief, one air mask service bottle truck, and a media affairs unit.}.
-Dispatch initiated a 2-11 alarm.
-SQ5 and other members on the 2\textsuperscript{nd} floor grabbed the [E123 captain] and got him down the stairs.
-The TL39 crew, with assistance from a T33 and SQ5 firefighter, had just completed a second hole on [the right side] of the roof about a third of the way back when conditions worsened.
-At 1729 hours, the roof ventilation crew was back in the aerial basket when they noticed the [captain] being brought out to the front yard.
-The [captain] was nonresponsive in the front yard and CPR was successfully performed.
-The IC met the A19 crew and escorted them to the [E123 captain].
-The revived [captain] was responsive and talking to the paramedics as he was loaded into the ambulance.
-At 1738 hours, the [captain] was transported to the local hospital where he had complications during airway management and died.
+At approximately 1045 hours, 3 engine companies, 2 truck companies, 1 heavy rescue squad, and 3 battalion chiefs were dispatched to a report of curtains on fire due to an electrical short at a single family residential structure.
+E26, with [the lieutenant] and [the fire fighter/paramedic], arrived at approximately 1048 hours, positioned just north of the front door on [the front side] of the fire structure on the narrow street.
+[The lieutenant] initially grabbed the CO$_2$ extinguisher because of a reported electrical fire.
+After consulting with the occupant, [the lieutenant] and [the fire fighter/paramedic] pulled a 1~3/4'' hoseline off the engine and made entry through the front door ([front side] street level), noticing light smoke.
+[The lieutenant] radioed on the fireground channel that ``smoke was showing and we have a working fire below grade.'' The transmission was acknowledged by both BC6 and DC 3.
+
+E24 arrived at approximately 1051 hours and positioned down the hill to allow T11, who was still en route, to get around them.
+At approximately 1052 hours, E11 and BC6 (shift relief BC with no assigned aide), traveling north with a view of [the rear side] of the structure, noticed no smoke or fire visible.
+E11 caught the hydrant just north of the structure and laid 3'' supply lines to both sides of E26.
+BC6 drove around E11 and parked in a neighboring driveway just north of the fire structure.
+BC6 (initial IC) radioed E26 for their location and they replied they were trying to locate the fire.
+The IC walked to the front of the fire structure and radioed E26 again about their status but got no response.
+The E11 crew was in the process of building a wye, when the IC instructed them to get a 1~3/4'' hoseline and some irons and go down the exterior wooden stairway of [the left side of the structure] and make entry at the door that was below grade.
+At approximately 1053 hours, BC9 arrived on scene and was assigned to supervise fire attack group responsibilities per protocol as second due BC.
+BC9 followed the E26's hoseline through the front door and encountered the E26 crew ([the lieutenant and the fire fighter/paramedic]) operating in the front hallway on the street level floor near the entrance to the garage and stairway to the basement.
+[The lieutenant] stated that the fire must be a floor below them.
+BC9 stated they would attack the fire from the [left side] of the structure and exited the front door, but the [lieutenant and the fire fighter/paramedic] did not follow.
+At approximately 1054 hours, the E24 crew made entry into the garage to check for access and attempt to intercept the E26 crew.
+They thought they heard what could have been SCBA cylinders clanging and hitting the floor just inside the doorway.
+
+At approximately 1056 hours, T15 and DC3 arrived on scene.
+DC3 took command as IC.
+The IC assigned T15 to the roof for ventilation.
+RS1 signaled to command they were going to split their crew per their normal protocol while operating with an engine company: 2 crew members going on first floor (RS1A) and 2 crew members going to the second floor (RS1B).
+The IC acknowledged.
+The RS1A entered the garage and headed for the door in the right corner of the garage to meet up with E24, but struggled since the door was blocked by vehicles and storage boxes inside the garage.
+The IC did a face-to-face with BC6 and instructed BC6 to get a layout of the fire structure from a resident.
+
+At approximately 1057 hours, BC9 went down a debris filled path along the outside of the [left side of the structure] to the wooden stairs connecting the basement door to the sub-basement door.
+He went to the sub-basement and forced the door open (see Photo 1).
+After seeing the room filled with light smoke, he looked around the B/C corner and saw smoke but no fire.
+BC6 located an older woman on the street, who resided at the fire structure and tried to get an understanding of the layout.
+At this point, dark smoke was observed about 2 feet off the ceiling in the garage.
+The smoke was not turbulent.
+At approximately 1058 hours, BC9 headed to the basement level man door.
+The fire self-vented out the glass door near the C/D corner (see Photo 2).
+BC9 forced the barred security door open with his halligan bar and then kicked the door open.
+The E11 crew advanced into the basement with the 1~3/4'' hoseline.
+At the door, they felt a blast of heat and observed heavy smoke in the fully involved room.
+The heat forced the E11 fire fighter operating the nozzle to back up.
+BC9 radioed, ``We have heavy fire and smoke and need a second line on [the left side of the structure].'' (see Photo 3).
+
+E32 had arrived on scene and reported to ``Command'' minutes earlier as RIC but the IC reassigned them to back up E11 on [the left side of the structure].
+The IC requested another RIC company from dispatch.
+At approximately 1100 hours, the E24 crew and RS1A were in the garage trying to make entry into the house but were unable to get past the doorway due to the extreme heat (see Photo 4).
+BC6 went to the IC to explain the layout and had noticed the dramatic change in the smoke (i.e., from gray to dark in color, lofting to pressurized speed, and medium to heavy volume) coming out of the garage covering the command post in the street.
+The IC tried again to radio E26 but received no response.
+The IC radioed E26 again and heard a garbled response.
+The IC thought the E26 crew was on the hoseline and near BC9.
+At approximately 1102 hours, the E32 crew had deployed a charged 1~3/4'' hoseline down to [the left side of the structure] and made entry behind E11's crew and began to fight the fire (see Photo 5).
+The IC assigned BC6 to Division 3 (the second floor) and the crew from T11 to make entry at the front door to search the upper floors.
+When the T11 crew approached the door, RS1B had just come out.
+The two crews regrouped to go back in with BC6.
+E24 and RS1A backed out of the garage.
+RS1A proceeded to [the left side of the structure], E24 proceeded to the front door and met up with BC6,~T11,~and~RS1B.
+
+At approximately 1105 hours, T15 radioed the IC that they were ready to vertically ventilate.
+The IC gave T15 the go ahead.
+At about that same time, RS1A made entry on [the left side of the structure] after the E11 crew knocked down the large room and contents fire.
+RSA1 radioed command that they were conducting a primary search.
+E24, T11 and RS1B regrouped at the front door, BC6 instructed T11 to stay at the front door and help feed the hoseline as BC6, E24 and RS1B made entry.
+After entering the front door, BC6, E24 and RS1B followed the E26 hoseline.
+BC6 had a thermal imaging camera, but the soot and smoke were so heavy he could not see the camera screen in the zero visibility.
+In zero visibility conditions, the E24 crew advanced to the bottom of the stairs of the first floor hallway.
+The E24 lieutenant followed E26's hoseline which led him to a metal door to the foyer which led to the garage and basement stairs.
+He pushed open the door and found [the lieutenant] in the first floor foyer at the top of the stairs to the basement.
+Then seconds later, E24's fire fighter/paramedic found [the fire fighter/paramedic] a few feet away in the first floor hallway just past the doorway to the foyer.
+Note: [The lieutenant] was found on his knees with his arms in a hunched over position in the foyer at the top of the basement stairs.
+[The fire fighter/paramedic] was found face down in the hallway toward the bedroom.
+The E26 hoseline was found in the foyer with [the lieutenant] and the door partially closed on it.
+
+About this time dispatch contacted command and stated that an E20 fire fighter's radio emergency alarm bottom had been activated.
+Note: E20 was the replacement RIC and was en route.
+The IC didn't see E20 on scene and knew that they hadn't reported to command.
+The E24 crew could hear a PASS device going off.
+BC6 heard someone say we found a downed fire fighter and heard PASS alarms going off so he radioed a ``Mayday'' and reported that there was a downed fire fighter.
+Note: The Mayday by BC6 was overridden by dispatch's information about E20's emergency alarm.
+The lieutenant from RS1A came up the stairs from the fire floor and assisted the E24 lieutenant in carrying [the lieutenant] out the garage man door.
+While going along the garage wall and a vehicle, the [lieutenant's] low pressure SCBA hose and facepiece got caught underneath the vehicle's tire.
+RS1A's fire fighter cut the hose to expedite the extrication.
+The E24 fire fighter/paramedic moved [the fire fighter/paramedic] into the foyer doorway to the garage then the fire fighter/paramedic came out of garage and yelled, ``Need help, fire fighters down.'' The fire fighter from RS1A came up the stairs from the fire floor to the foyer and assisted a T11 fire fighter with carrying [the fire fighter/paramedic] outside through the garage.
+At approximately 1110 hours the IC radioed dispatch and urgently requested 2 medic units be sent; the IC requested a second alarm one minute later.
+The IC radioed BC6 and BC9 to report to the command post.
+The [lieutenant and the fire fighter/paramedic] were transported to the local medical center where the lieutenant was pronounced dead.
+The fire fighter/paramedic died two days later from his injuries.
 \end{quote}
@@
 \begin{table}[!ht]
-\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer}}
+\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
 \begin{tabular}{cl}
@@
 Based on the goals of the analysis and the information collected, several engineering approximations were made.
-For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
 The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
@@
 This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
-The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer}.
+The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer2}.
 Additionally, there was a half-story attic that contained the structure's hot water heater.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/1st_Floor_Metric} \\
-% \includegraphics[width=5in]{../Figures/2nd_Floor_Metric}
+% \includegraphics[width=6.5in]{../Figures/1st_Floor_Metric} \\
+% \includegraphics[width=6.5in]{../Figures/2nd_Floor_Metric}
 % \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/exterior_alpha} \\
-% \includegraphics[width=5in]{../Figures/exterior_charlie}
+% \includegraphics[width=6.5in]{../Figures/exterior_alpha} \\
+% \includegraphics[width=6.5in]{../Figures/exterior_charlie}
 % \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
@@
 Simulation  &  Simulation   &  Area         &               &  Structure       \\
-{[s]}       &  {[s]}        &  [m$^2$]      &               &                  \\
+{(s)}       &  {(s)}        &  (m$^2$)      &               &                  \\
 \midrule
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/door_frame_burn}
+% \includegraphics[width=6.5in]{../Figures/door_frame_burn}
 % \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/smv_exterior_grid} \\
-% \includegraphics[width=5in]{../Figures/smv_exterior_grid_rear}
+% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid} \\
+% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid_rear}
 % \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/smv_exterior_mesh}
+% \includegraphics[width=6.5in]{../Figures/smv_exterior_mesh}
 % \caption[Front-right side of the structure within the computational domain.]
@@
 \footnotesize
-\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
 \normalsize
@@
 To examine the results of the simulations, it is important to link the timelines from the fire scene to the simulation times.
-Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{NIOSH:Bowyer} along with the corresponding simulation times.
+Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{NIOSH:Bowyer2} along with the corresponding simulation times.
 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/Chicago_Fire_HRR}
+% \includegraphics[width=6.5in]{../Figures/Chicago_Fire_HRR}
 % \caption[HRR versus time from the FDS simulations.]
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/smv_exterior_fire}
+% \includegraphics[width=6.5in]{../Figures/smv_exterior_fire}
 % \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
@@
 \section{Pressure}
+\label{sec:pressure}
 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_pres2}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_pres2}
 % \input{../Scripts/colorbar_metric_pres}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_velo_175}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_velo_175}
 % \input{../Scripts/colorbar_std_velo}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_129}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_129}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_159}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_159}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_161}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_161}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_175}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_175}
 % \input{../Scripts/colorbar_std} 
@@
 \section{Simulated Hallway Flow Path}
+\label{sec:simulated_flow_path}
+
 From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report~\cite{NIOSH:Bowyer}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
+From the NIOSH report~\cite{NIOSH:Bowyer2}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
 This indicated the presence of fire in the area of the enclosed porch.
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/Porch_Door_1}
+% \includegraphics[width=6.5in]{../Figures/Porch_Door_1}
 % \caption{Post-fire image of interior door.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/SC_Door_1} \\
-% \includegraphics[width=5in]{../Figures/SC_Door_2}
+% \includegraphics[width=6.5in]{../Figures/SC_Door_1} \\
+% \includegraphics[width=6.5in]{../Figures/SC_Door_2}
 % \caption{Post-experiment images of door failures.}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/ChicagoFlow}
+% \includegraphics[width=6.5in]{../Figures/ChicagoFlow}
 % \caption{Summary of simulated flow path on the second floor after interior door failure.}
@@
 \section{Assessing the Hazard}
+\label{sec:assessing_the_hazard}
 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_159_6ft}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_159_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_165_6ft}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_165_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/west_50th_baseline_top_220_6ft}
+% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_220_6ft}
 % \input{../Scripts/colorbar_std} 
@@
 \section{Tactical Considerations}
+\label{sec:tactical_condsiderations}
+
 There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
@@
 NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
-The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.
+The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, videos, and relevant literature.
 This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure.
@@
 \chapter*{Acknowledgments}
+
 The authors would like to thank XXXX.
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/50th_Place_1st_Floor}
-% \caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
-% \label{fig:first_floor}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/50th_Place_2nd_Floor}
-% \caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}
-% \label{fig:second_floor}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Top_Floor_Metric}
+\caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
+\label{fig:first_floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Ground_Floor_Metric}
+\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
+\label{fig:second_floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Sub_Level_1_Metric}
+\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
+\label{fig:second_floor}
+\end{figure}
 

### 2014-08-12 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG County: add reference, update devices in input files, update report

@@
 \hspace{1.5in} \= \\
+EMS \> Emergency Medical Services \\
 FDS \> Fire Dynamics Simulator \\
@@
 HRR \> Heat Release Rate \\
+HRRPUA \> Heat Release Rate per Unit Area \\
+LODD \> Line of Duty Death \\
 NIST \> National Institute of Standards and Technology \\
+SFPE \> Society of Fire Protection Engineers \\
+\end{tabbing}
+
+\chapter{List of Symbols}
+
+\begin{tabbing}
+\hspace{1.5in} \= \\
+ft \> foot \\
+m \> meter \\
+min \> minute \\
+Pa \> Pascal \\
+psi \> pound per square inch \\
+s \> second \\
+W \> Watt \\
+$k$ \> thermal conductivity \\
+$\rho$ \> density \\
+$c_{p}$ \> specific heat \\
 \end{tabbing}
@@
 \chapter{Introduction}
+Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
+The objective of these studies has been to improve the safety and effectiveness of firefighters.
+
+On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters.
+NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department.
+Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide}  software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
+The specific objectives of the simulations detailed in this report are:
+\begin{enumerate}
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
+\item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
+\end{enumerate}
+This document describes the input and the results of the FDS (version 6.0.0) simulations.
+The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
+Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
+This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discuss} discusses the simulation results as they relate to firefighter safety and effectiveness.
+Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
 
@@
 \label{fire_sum}
+The account of events for this incident was documented by the Safety Investigation Team of the Prince George's County Fire/EMS Department~\cite{PGCounty2013}.
+At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}.
+For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
+The following narrative of the incident, focused on the events which led to burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
+\begin{quote}
+Truck 809 responded from quarters, as the first due truck company, and arrived on 57$^{th}$ Avenue right behind Engine 807B.
+When Truck 809 stopped to let Engine 807B layout, Truck 809 Can dismounted the truck and had to walk up the street as it pulled away.
+Truck 809 Officer observed a lot of smoke moving extremely fast through the front yard and across the street upon exiting the truck.
+Truck 809 Officer and Truck 809 Forcible Entry proceeded directly to the front door \ldots of the structure.
+Both of them entered the structure with full PPE, including SCBA, but without the protection of a hose line.
+Truck 809 Officer and Truck 809 Forcible Entry began primary searches on the first floor.
+At some point during the primary search, as conditions worsened, the front door closed, trapping Truck 809 Officer and Truck 809 Forcible Entry inside the structure.
+This situation could not have occurred if a charged hose line was operating inside the structure at the time the door slammed shut.
+They were the only firefighters operating on the first floor at that time.
+
+Truck 809 Forcible Entry was too large in physical stature to fit through the small window opening that he found on [the front of the structure].
+Truck 809 Forcible Entry was unable to self-evacuate, and remained trapped inside.
+Due to rapidly deteriorating conditions, Truck 809 Officer was forced to self-rescue through another small window on [the front of the structure].
+
+After exiting the structure, Truck 809 Officer screamed (to those on the exterior) that a firefighter was trapped inside.
+Truck 809 Officer then proceeded to the front door \ldots in an attempt to search for and rescue Truck 809 Forcible Entry, who was trapped inside.
+At this point multiple firefighters on the exterior assisted Truck 809 Officer in the search, rescue, and removal of Truck 809 Forcible Entry.
+Both Truck 809 Officer and Truck 809 Forcible Entry sustained serious injuries and were transported to MedStar/Washington Hospital Center.
+
+While the interior operations were occurring, Truck 809 Driver and Truck 809 Hook/Ladders were on the exterior throwing ladders to the structure.
+Truck 809 Hook/Ladders threw two ladders [front and left side], while Truck 809 Driver threw one ladder ([front side]).
+\end{quote}
+
+\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+\begin{table}[!h]
+\centering
+\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}}\label{tab:fire_info}
+\begin{tabular}{cl}
+\toprule[1.5pt]
+Incident Time              &  Fire Behavior / Fireground Operation  \\
+{[hh:mm:ss]}               &                                                               \\
+\midrule
+\multirow{3}{*}{21:11:03}  &   \multirow{3}{*}{\parbox{10cm} {Dispatch for a ``box'' alarm assignment- four engine companies, two truck companies, one rescue squad, and a commanding officer.}}    \\
+                           &         \\
+                           &         \\[.25cm]
+21:12:55  &  First unit (Engine 807B) arrived on-scene.      \\[.25cm]
+21:13:44  & Truck 809 arrived on-scene. \\[.25cm]
+21:13:44                   & Volunteer Chief 809A establishes incident command (IC).      \\[.25cm]
+
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 
@@
 \label{matl}
+While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+The following lines define these materials in the FDS input file:
+
+\begin{lstlisting}
+&MATL ID = 'GYPSUM BOARD'
+    FYI = 'Wakili - Journal of Fire Sciences 2007' 
+    CONDUCTIVITY = 0.28
+    SPECIFIC_HEAT = 1.0
+    DENSITY = 810. /
+
+&MATL ID = 'WOOD MAT'
+    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
+    CONDUCTIVITY = 0.12
+    SPECIFIC_HEAT = 1.38
+    DENSITY = 510. / 
+\end{lstlisting}
 
@@
 \chapter{Discussion}
+\label{discuss}
 
@@
 
+\chapter{Dimensioned Drawings}
+\label{app_draw}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1\textwidth]{../Figures/Basement_Metric}
+\caption[Dimensioned drawing of first floor.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
+\label{fig:first_floor}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=1\textwidth]{../Figures/First_Floor_Metric}
+\caption[Dimensioned drawing of second floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
+\label{fig:second_floor}
+\end{figure}
+
 \end{document}

### 2014-08-12 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor edit to timeline (related to r551)

@@
 \midrule
-\multirow{2}{*}{17:15:00} &    & \multirow{2}{*}{\parbox{9cm} {Fire is reported with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
+\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
          & & \\[.25cm] %blank rows exist for wrapping text. # of blanks is 1 less than number of rows
-\multirow{2}{*}{17:16:00} & \multirow{2}{*}{}   &  \multirow{2}{*}{\parbox{9cm} {Dispatch for a ``Still'' alarm - two engine companies, two truck companies, and a battalion chief.}} \\
+\multirow{2}{*}{17:17:00} &    & \multirow{2}{*}{\parbox{9cm} {On-scene report of a working fire with heavy smoke coming from the front and rear of the structure's attic.}} \\ 
          & & \\[.25cm]

### 2014-08-12 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to narrative and incident timeline

@@
 \begin{quote}
-At approximately 1045 hours, 3 engine companies, 2 truck companies, 1 heavy rescue squad, and 3 battalion chiefs were dispatched to a report of curtains on fire due to an electrical short at a single family residential structure.
-E26, with [the lieutenant] and [the fire fighter/paramedic], arrived at approximately 1048 hours, positioned just north of the front door on [the front side] of the fire structure on the narrow street.
-[The lieutenant] initially grabbed the CO$_2$ extinguisher because of a reported electrical fire.
-After consulting with the occupant, [the lieutenant] and [the fire fighter/paramedic] pulled a 1~3/4'' hoseline off the engine and made entry through the front door ([front side] street level), noticing light smoke.
-[The lieutenant] radioed on the fireground channel that ``smoke was showing and we have a working fire below grade.'' The transmission was acknowledged by both BC6 and DC 3.
-
-E24 arrived at approximately 1051 hours and positioned down the hill to allow T11, who was still en route, to get around them.
-At approximately 1052 hours, E11 and BC6 (shift relief BC with no assigned aide), traveling north with a view of [the rear side] of the structure, noticed no smoke or fire visible.
-E11 caught the hydrant just north of the structure and laid 3'' supply lines to both sides of E26.
-BC6 drove around E11 and parked in a neighboring driveway just north of the fire structure.
-BC6 (initial IC) radioed E26 for their location and they replied they were trying to locate the fire.
-The IC walked to the front of the fire structure and radioed E26 again about their status but got no response.
-The E11 crew was in the process of building a wye, when the IC instructed them to get a 1~3/4'' hoseline and some irons and go down the exterior wooden stairway of [the left side of the structure] and make entry at the door that was below grade.
-At approximately 1053 hours, BC9 arrived on scene and was assigned to supervise fire attack group responsibilities per protocol as second due BC.
-BC9 followed the E26's hoseline through the front door and encountered the E26 crew ([the lieutenant and the fire fighter/paramedic]) operating in the front hallway on the street level floor near the entrance to the garage and stairway to the basement.
-[The lieutenant] stated that the fire must be a floor below them.
-BC9 stated they would attack the fire from the [left side] of the structure and exited the front door, but the [lieutenant and the fire fighter/paramedic] did not follow.
-At approximately 1054 hours, the E24 crew made entry into the garage to check for access and attempt to intercept the E26 crew.
-They thought they heard what could have been SCBA cylinders clanging and hitting the floor just inside the doorway.
-
-At approximately 1056 hours, T15 and DC3 arrived on scene.
-DC3 took command as IC.
-The IC assigned T15 to the roof for ventilation.
-RS1 signaled to command they were going to split their crew per their normal protocol while operating with an engine company: 2 crew members going on first floor (RS1A) and 2 crew members going to the second floor (RS1B).
-The IC acknowledged.
-The RS1A entered the garage and headed for the door in the right corner of the garage to meet up with E24, but struggled since the door was blocked by vehicles and storage boxes inside the garage.
-The IC did a face-to-face with BC6 and instructed BC6 to get a layout of the fire structure from a resident.
-
-At approximately 1057 hours, BC9 went down a debris filled path along the outside of the [left side of the structure] to the wooden stairs connecting the basement door to the sub-basement door.
-He went to the sub-basement and forced the door open (see Photo 1).
-After seeing the room filled with light smoke, he looked around the B/C corner and saw smoke but no fire.
-BC6 located an older woman on the street, who resided at the fire structure and tried to get an understanding of the layout.
-At this point, dark smoke was observed about 2 feet off the ceiling in the garage.
-The smoke was not turbulent.
-At approximately 1058 hours, BC9 headed to the basement level man door.
-The fire self-vented out the glass door near the C/D corner (see Photo 2).
-BC9 forced the barred security door open with his halligan bar and then kicked the door open.
-The E11 crew advanced into the basement with the 1~3/4'' hoseline.
-At the door, they felt a blast of heat and observed heavy smoke in the fully involved room.
-The heat forced the E11 fire fighter operating the nozzle to back up.
-BC9 radioed, ``We have heavy fire and smoke and need a second line on [the left side of the structure].'' (see Photo 3).
-
-E32 had arrived on scene and reported to ``Command'' minutes earlier as RIC but the IC reassigned them to back up E11 on [the left side of the structure].
-The IC requested another RIC company from dispatch.
-At approximately 1100 hours, the E24 crew and RS1A were in the garage trying to make entry into the house but were unable to get past the doorway due to the extreme heat (see Photo 4).
-BC6 went to the IC to explain the layout and had noticed the dramatic change in the smoke (i.e., from gray to dark in color, lofting to pressurized speed, and medium to heavy volume) coming out of the garage covering the command post in the street.
-The IC tried again to radio E26 but received no response.
-The IC radioed E26 again and heard a garbled response.
-The IC thought the E26 crew was on the hoseline and near BC9.
-At approximately 1102 hours, the E32 crew had deployed a charged 1~3/4'' hoseline down to [the left side of the structure] and made entry behind E11's crew and began to fight the fire (see Photo 5).
-The IC assigned BC6 to Division 3 (the second floor) and the crew from T11 to make entry at the front door to search the upper floors.
-When the T11 crew approached the door, RS1B had just come out.
-The two crews regrouped to go back in with BC6.
-E24 and RS1A backed out of the garage.
-RS1A proceeded to [the left side of the structure], E24 proceeded to the front door and met up with BC6,~T11,~and~RS1B.
-
-At approximately 1105 hours, T15 radioed the IC that they were ready to vertically ventilate.
-The IC gave T15 the go ahead.
-At about that same time, RS1A made entry on [the left side of the structure] after the E11 crew knocked down the large room and contents fire.
-RSA1 radioed command that they were conducting a primary search.
-E24, T11 and RS1B regrouped at the front door, BC6 instructed T11 to stay at the front door and help feed the hoseline as BC6, E24 and RS1B made entry.
-After entering the front door, BC6, E24 and RS1B followed the E26 hoseline.
-BC6 had a thermal imaging camera, but the soot and smoke were so heavy he could not see the camera screen in the zero visibility.
-In zero visibility conditions, the E24 crew advanced to the bottom of the stairs of the first floor hallway.
-The E24 lieutenant followed E26's hoseline which led him to a metal door to the foyer which led to the garage and basement stairs.
-He pushed open the door and found [the lieutenant] in the first floor foyer at the top of the stairs to the basement.
-Then seconds later, E24's fire fighter/paramedic found [the fire fighter/paramedic] a few feet away in the first floor hallway just past the doorway to the foyer.
-Note: [The lieutenant] was found on his knees with his arms in a hunched over position in the foyer at the top of the basement stairs.
-[The fire fighter/paramedic] was found face down in the hallway toward the bedroom.
-The E26 hoseline was found in the foyer with [the lieutenant] and the door partially closed on it.
-
-About this time dispatch contacted command and stated that an E20 fire fighter's radio emergency alarm bottom had been activated.
-Note: E20 was the replacement RIC and was en route.
-The IC didn't see E20 on scene and knew that they hadn't reported to command.
-The E24 crew could hear a PASS device going off.
-BC6 heard someone say we found a downed fire fighter and heard PASS alarms going off so he radioed a ``Mayday'' and reported that there was a downed fire fighter.
-Note: The Mayday by BC6 was overridden by dispatch's information about E20's emergency alarm.
-The lieutenant from RS1A came up the stairs from the fire floor and assisted the E24 lieutenant in carrying [the lieutenant] out the garage man door.
-While going along the garage wall and a vehicle, the [lieutenant's] low pressure SCBA hose and facepiece got caught underneath the vehicle's tire.
-RS1A's fire fighter cut the hose to expedite the extrication.
-The E24 fire fighter/paramedic moved [the fire fighter/paramedic] into the foyer doorway to the garage then the fire fighter/paramedic came out of garage and yelled, ``Need help, fire fighters down.'' The fire fighter from RS1A came up the stairs from the fire floor to the foyer and assisted a T11 fire fighter with carrying [the fire fighter/paramedic] outside through the garage.
-At approximately 1110 hours the IC radioed dispatch and urgently requested 2 medic units be sent; the IC requested a second alarm one minute later.
-The IC radioed BC6 and BC9 to report to the command post.
-The [lieutenant and the fire fighter/paramedic] were transported to the local medical center where the lieutenant was pronounced dead.
-The fire fighter/paramedic died two days later from his injuries.
+On June 02, 2011, a 48 year-old career lieutenant and a 53 year-old fire fighter/paramedic died in a multi-level residential structure fire while searching for the seat of the fire.
+Note: The residential structure where the fatalities occurred was built on a significantly sloped hillside common throughout the city.
+The fire floor was one floor below street level.
+Six companies and three command chiefs were dispatched to a report of an electrical fire at a residential home.
+
+When Engine~26, staffed with a lieutenant, fire fighter/paramedic, and driver arrived at approximately 1048 hours, they noticed light smoke showing as they made entry through the front door, side A, street level, of the building.
+Minutes later, the incident commander (IC) tried contacting them over the radio, but received no response.
+A battalion chief (BC) assigned to ``the fire attack group'' followed the hoseline through the door and spoke to the [lieutenant and fire fighter/paramedic] on the street level floor.
+The lieutenant stated to the BC that the fire must be a floor below them.
+The BC stated they would attack the fire from the [left side] of the structure and exited the front door.
+The [lieutenant and fire fighter/paramedic] did not follow.
+A few minutes later the IC again tried to contact Engine~26 via radio with no response.
+
+The crew from Engine~24, assigned to back up Engine~26, and a split crew from Rescue~1 tried to make entry through the door in the garage but could not advance due to the heat.
+The BC went to the [door on the left side of the structure], located one floor below street level, and forced the door with the Engine~11 crew on the hoseline.
+They immediately felt a blast of heat from the fully involved basement area.
+The Rescue~1 crew backed out of the garage and re-entered on [the left side of the structure] after the Engine~11 crew knocked down the large room and contents fire.
+At about the same time, the Engine~24 crew also backed out of the garage and followed the Engine~26 crew's hoseline through the front door.
+In zero visibility conditions, separate members of the Engine~24 crew independently found a downed member of the Engine~26 crew.
+
+The Incident Commander was alerted of a downed fire fighter but, did not initially realize, until moments later that it was actually two downed fire fighters.
+Both [fire fighters] were removed from the structure and immediate medical treatment was provided.
+The [fire fighters] were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
 \end{quote}
@@
 \midrule
-17:15:00       &  Reported working fire with heavy smoke coming from the     \\ 
-               &  front and rear of the structure's attic.                   \\
+10:45:00       &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
                &                                                                                      \\
-17:16:00       &  Dispatch for a ``Still'' alarm - two engine companies,     \\
-               &  two truck companies, and a battalion chief.                \\
+10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
+               &  the front door with a 1 3/4'' hoseline.                                             \\
                &                                                                                      \\
-17:20:00       &  Attic windows break - heavy smoke out of front attic       \\
-               &  window and heavy smoke and fire out of rear.               \\
+10:54:00       &  E26 crew states that the fire is located below the first floor.                     \\
                &                                                                                      \\
-17:21:00       &  E123 captain and firefighter on second floor               \\
-               &  with 1\sfrac{3}{4}-inch hoseline.                          \\
+10:56:00       &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
                &                                                                                      \\
-17:21:30       &  First floor exterior porch door opened.                    \\
+10:58:00       &  Fire self-vents from the rear side of the structure when a glass door in the        \\
+               &  basement fails.                                                                     \\
                &                                                                                      \\
-17:23:00       &  Heavy fire report in rear stairwell and enclosed porch.    \\
-               &  No response from E123 captain or firefighter.              \\
+10:59:00       &  BC9 forces open the basement door on the left side of the structure,                \\
+               &  reports heavy fire and smoke, and requests a second hoseline.                       \\
                &                                                                                      \\
-17:24:00       &  Water applied to attic from the rear exterior position.    \\
+11:00:00       &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
                &                                                                                      \\
-17:25:00       &  SQ5 makes entry through front of structure.                \\
+11:01:00       &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
+               &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
                &                                                                                      \\
-17:27:00       &  After hearing a Mayday call from SQ5, IC calls a Mayday.   \\
+11:02:00       &  E32 crew makes entry into the basement with a second hoseline.                      \\
                &                                                                                      \\
-17:29:00       &  E123 captain carried out of structure.                     \\
+11:08:00       &  Two downed E26 firefighters are found on the first floor.                           \\
+               &                                                                                      \\
+11:09:00       &  The downed E26 firefighters are carried out of the structure.                       \\
+               &                                                                                      \\
 \bottomrule

### 2014-08-13 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Fix typo
Chicago Fire: update to chemical reaction

@@
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.0.0) simulations.
+This document describes the input and the results of the FDS (version 6.1.1) simulations.
 The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
@@
 The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
-A balanced chemical reaction for wood combustion can written as:
+A balanced chemical reaction for wood combustion can be written as:
 
 \begin{multline}
-\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
-\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
+\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.91(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
+\rightarrow 5.74(0.636\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.670\,\N_{2} + 0.613\text{\sc{e}-}2\,\C)
 \label{eq:wood_comb}

### 2014-08-13 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG CO: update to event timeline

@@
 \midrule
+21:08:26   & First 911 call is made. \\[.25cm]
 \multirow{3}{*}{21:11:03}  &   \multirow{3}{*}{\parbox{10cm} {Dispatch for a ``box'' alarm assignment- four engine companies, two truck companies, one rescue squad, and a commanding officer.}}    \\
@@
 21:12:55  &  First unit (Engine 807B) arrived on-scene.  \\[.25cm]
-21:13:44  & Truck 809 arrived on-scene. \\[.25cm]
 21:13:44  & Volunteer Chief 809A establishes incident command (IC).   \\[.25cm]
-
+21:13:56  & Truck 809 arrived on-scene. \\[.25cm]
+21:14:00  & Front door opened. \\[.25cm]
+21:14:42  & Truck 809 enters structure. \\[.25cm]
+21:15:47  & Front door closed over. \\[.25cm]
+21:15:51  & Lower pane of front egress window broke. \\[.25cm]
+21:15:57  & Water applied to fire at basement. \\[.25cm]
+21:16:01  & Top pane of front egress window broke. \\[.25cm]
+21:16:16  & Truck 809 officer bailout through window. \\[.25cm]
+21:16:44  & Front door opened. \\[.25cm]
+21:17:15  & Truck 809 forcible entry firefighter rescued. \\[.25cm]
 \bottomrule[1.25pt]

### 2014-08-14 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to report (fuel section, timeline); comment out pending sections

@@
 
-The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
+% The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
 Based on the goals of the analysis and the information collected, several engineering approximations were made.
@@
 
-In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+% In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
 Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
@@
 
-The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
+% The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
 Intermediate floors are built directly off of the studs.
@@
 
-The fire, which is described in Section~\ref{sec:fire}, started in the attic and spread to the rear porch.
+% The fire, which is described in Section~\ref{sec:fire}, started in the attic and spread to the rear porch.
 Discussion of the fire's impact on the interior conditions is provided in Section~\ref{sec:model_results}.
@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these sources of information, the FDS model includes two source fire locations: an initial fire in the attic and a secondary fire on the second floor porch landing.
-The attic and rear porch primarily consisted of wood fuel: the rear porch was enclosed with wood planks covered with foam board and vinyl siding, the roof consisted of asphalt shingles over wood planking, and the attic and porch floors were composed of oriented strand board.
+Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area.
+The basement consisted of a finished living area with a large utilities area and contained primarily upholstered polyurethane furniture fuel items.
 
-Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
-The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
-A balanced chemical reaction for wood combustion can written as:
+Polyurethane fuel can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The product yields are expressed in terms of the amount soot or carbon monoxide emitted per unit mass of fuel consumed~(kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
+A balanced chemical reaction for polyurethane combustion can be written as:
 
 \begin{multline}
-\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.89(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
-\rightarrow 5.84(0.719\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.669\,\N_{2} + 0.693\text{\sc{e}-}2\,\C)
-\label{eq:wood_comb}
+\C\H_{1.8}\O_{0.30}\N_{0.05} + 5.22(0.208\,\O_{2} + 0.783\,\N_{2} + 8.34 \times 10^{-3}\,\H_{2}\O + 3.87 \times 10^{-4}\,\C\O_{2}) \\
+\rightarrow 6.06(0.129\,\C\O_{2} + 0.156\,\H_{2}\O + 0.001\,\C\O + 0.035\,\C + 0.679\,\N_{2})
+\label{eq:fuel_comb}
 \end{multline}
 
-The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The value for the heat of combustion of polyurethane used in this simulation was~26,200 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the amount of energy per unit mass of the fuel.
-The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
+The following text defines Eq.~\ref{eq:fuel_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
 
 \begin{lstlisting}
-&SPEC ID='WOOD', FORMULA='CH1.7O0.74N0.002' /
+&SPEC ID='POLYURETHANE', FORMULA='CH1.8O0.30N0.05' /
 
-&REAC ID = 'wood' 
-    FUEL = 'WOOD', 
-    HEAT_OF_COMBUSTION = 16400,
-    SOOT_YIELD = 0.015,
-    CO_YIELD = 0.004/
+&REAC ID = 'POLYURETHANE' 
+    FUEL = 'POLYURETHANE', 
+    HEAT_OF_COMBUSTION = 26200,
+    SOOT_YIELD = 0.131,
+    CO_YIELD = 0.010 /
 \end{lstlisting}
@@
 
-To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+% To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
 The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
 
-To calculate the total fire size, the appropriate burning area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
+% To calculate the total fire size, the appropriate burning area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
 Based on the floor plan of the structure, the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
@@
 \begin{lstlisting}
-&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE', TAU_Q=10 /
-&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 
-&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 
-&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
+&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
+&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER' /
+
+&SURF ID='FLASHOVER_BURNER', HRRPUA=270.563, COLOR='RED' /
+&VENT XB=0.0, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
+&DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /
 \end{lstlisting}
@@
 While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
-In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
-The following lines define these materials in the FDS input file:
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure.
+The following lines define the gypsum material in the FDS input file:
 
@@
     DENSITY = 810. /
-
-&MATL ID = 'WOOD MAT'
-    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
-    CONDUCTIVITY = 0.12
-    SPECIFIC_HEAT = 1.38
-    DENSITY = 510. / 
 \end{lstlisting}
@@
 
-The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+% The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
 Two different ventilation scenarios were considered in this study.
@@
 
-An unknown parameter in Table~\ref{tab:ventilation_timeline} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
+% An unknown parameter in Table~\ref{tab:ventilation_timeline} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
 The area of failure was also estimated based on the following observations.
@@
 \end{equation}
-From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.
+% From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$.
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
@@
 
-As discussed in Section~\ref{sec:geometry}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+% As discussed in Section~\ref{sec:geometry}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
@@
 \midrule
-17:15:00       &              &  Fire is reported with heavy smoke coming from the               \\ 
-               &              &  front and rear of the structure's attic.                        \\
+10:45:00       &              &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
                &              &                                                                                      \\
-17:16:00       &              &  Dispatch for a ``Still'' alarm - two engine companies,          \\
-               &              &  two truck companies, and a battalion chief.                     \\
+10:48:00       &              &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
+               &              &  the front door with a 1 3/4'' hoseline.                                             \\
                &              &                                                                                      \\
-               &  0           &  FDS simulation starts. Attic fire ignites. Initial              \\
-               &              &  ventilation through rear of structure. Front door open.         \\
+10:52:00       &  0           &  FDS simulation begins.                                                              \\
                &              &                                                                                      \\
-17:20:00       &  40          &  Attic windows break - heavy smoke out of front attic            \\
-               &              &  window and heavy smoke and fire out of rear.                    \\
-               &              &  Rear porch ignites in model.                                    \\
+10:54:00       &              &  E26 crew states that the fire is located below the first floor.                     \\
                &              &                                                                                      \\
-               &  45          & Ventilation through wall penetration on rear of structure.       \\
+10:56:00       &              &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
                &              &                                                                                      \\
-               &  55          & Ventilation through wall penetration on left side of structure.  \\
+10:58:00       &              &  Fire self-vents from the rear side of the structure when a glass door in the        \\
+               &              &  basement fails.                                                                     \\
                &              &                                                                                      \\
-17:21:00       &  100         & E123 captain and firefighter on second floor                     \\
-               &              & with 1\sfrac{3}{4}-inch hoseline.                                \\
+10:59:00       &              &  BC9 forces open the basement door on the left side of the structure,                \\
+               &              &  reports heavy fire and smoke, and requests a second hoseline.                       \\
                &              &                                                                                      \\
-17:21:30       &  130         & First floor exterior porch door opened.                          \\
-               &              & Porch fire ignites in FDS model.                                 \\
+11:00:00       &              &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
                &              &                                                                                      \\
-               &  135         & Ventilation through left side of structure.                      \\
+11:01:00       &              &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
+               &              &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
                &              &                                                                                      \\
-               &  160         & Top of interior door fails in FDS model.                         \\
+11:02:00       &              &  E32 crew makes entry into the basement with a second hoseline.                      \\
                &              &                                                                                      \\
-17:23:00       &  220         & Heavy fire report in rear stairwell and enclosed porch.          \\
-               &              & No response from E123 captain or firefighter.                    \\
+11:08:00       &              &  Two downed E26 firefighters are found on the first floor.                           \\
                &              &                                                                                      \\
-17:24:00       &              & Water applied to attic from the rear exterior position.          \\
+11:09:00       &              &  The downed E26 firefighters are carried out of the structure.                       \\
                &              &                                                                                      \\
-17:25:00       &              & SQ5 makes entry through front of structure.                      \\
-               &              &                                                                  \\
-17:27:00       &  300         & After hearing a Mayday call from SQ5, IC calls a Mayday.         \\
-               &              & Simulation ends.                                                 \\
-               &              &                                                                  \\
-17:29:00       &              & E123 captain carried out of structure.                           \\
 \bottomrule
@@
 
-The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
+% The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
 Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
@@
 
-In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
+% In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
 The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur.
@@
 
-Figure~\ref{fig:hrr} indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
+% Figure~\ref{fig:hrr} indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
 At 130~s, the rear door is opened in the baseline simulation.
@@
 
-As the simulated fire grows in the attic and rear porch, the pressure rises.
+% As the simulated fire grows in the attic and rear porch, the pressure rises.
 Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
@@
 
-Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
+% Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
 The temperature profile at these high hazard areas is shown via several snapshots in time to illustrate the change in the interior conditions.
@@
 
-Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+% Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
@@
 
-As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
+% As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
 
@@
 
-The results of the FDS simulations are discussed in the following two sections.
+% The results of the FDS simulations are discussed in the following two sections.
 The first section addresses the results of the computational modeling as they relate to the interior hallways conditions.
@@
 
-From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions on the second floor of the structure were initially tenable.
+% From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions on the second floor of the structure were initially tenable.
 From the NIOSH report~\cite{NIOSH:Bowyer2}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
@@
 
-Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
+% Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
 Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation.
@@
 
-After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.
+% After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.
 This resulted in a rapid change in the conditions within the flow path.
@@
 
-Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~\ref{fig:temp_top_159}.
+% Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~\ref{fig:temp_top_159}.
 The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
@@
 
-In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
+% In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
 These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
@@
 
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
+% NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, videos, and relevant literature.
@@
 
-The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
+% The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
 The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door that was located between the enclosed porch and the hallway.
@@
 \caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:first_floor}
+\label{fig:drawing_first_floor}
 \end{figure}
@@
 \caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:second_floor}
+\label{fig:drawing_second_floor}
 \end{figure}
@@
 \caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:second_floor}
+\label{fig:drawing_basement}
 \end{figure}

### 2014-08-14 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report, update devices in input files

@@
 NIST \> National Institute of Standards and Technology \\
+PPE \> Personal Protective Equipment \\
+SCBA \> Self Contained Breathing Apparatus \\
 SFPE \> Society of Fire Protection Engineers \\
@@
 This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discuss} discusses the simulation results as they relate to firefighter safety and effectiveness.
-Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
+Appendix~\ref{app_draw} contains dimensioned drawings of the basement and first floor of the structure.
 
@@
 
-\noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+The Prince George's County report~\cite{PGCounty2013}  \noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
 \begin{table}[!h]

### 2014-08-14 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add details and figures to geometry section

@@
 
-% In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
 Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
@@
 
-% The structure involved in this fire incident was a 2~\sfrac{1}{2}~story residential building with balloon frame construction and a gable roof.\footnote{Balloon frame construction is a method of framing where a continuous stud runs from the bottom horizontal member to the top plate.
-Intermediate floors are built directly off of the studs.
-One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~\ref{fig:simp_geom}.
-This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
-The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer2}.
-Additionally, there was a half-story attic that contained the structure's hot water heater.
-Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~\ref{fig:simp_geom}), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~\ref{fig:simp_geom}) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~\ref{fig:simp_geom}).
-Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
+The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane.
+The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure.
+The right side of the structure shared a common fire wall with another residential structure.
+The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located above the street level and two stories were located below the street level.
+The first and second floor (i.e., the two stories above street level) had a total interior floor area of 136~m$^2$ (1,468~ft$^2$).
+The interior walls were composed of gypsum board over insulated wood framing.
+The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (10 stairs down) or the second floor (5 stairs up).
 
-% The fire, which is described in Section~\ref{sec:fire}, started in the attic and spread to the rear porch.
-Discussion of the fire's impact on the interior conditions is provided in Section~\ref{sec:model_results}.
-Figure~\ref{fig:alpha_ex} shows the exterior of the front and rear of the structure after the incident.
-Note that the majority of the damage occurred in the attic and rear porch on the second floor.
-Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
+The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area with a large utility area.
+A laundry area was located on a landing on the stairs between the first floor and basement.
+The basement was accessible via an exterior door on the left side of the structure and an interior set of stairs.
+The basement had a balcony on the exterior of the rear side of the structure.
+The sub-basement level (i.e., the second story below street level) was not connected to the other three levels of the house, contained no windows, and was only accessible via an exterior door of the left side of the structure.
+The exterior entrances to the basement and sub-basement levels were connected via exterior wooden stairs on the left side of the structure.
+
+The fire, which is described in Section~\ref{sec:fire}, originated in the finished living room on the basement level (near the rear side of the structure), which had a floor area of 72~m$^2$ (775~ft$^2$).
+More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:model_results}.
+Figure~\ref{fig:post_exterior} shows the XX of the structure after the incident.
+Note that the majority of the damage occurred XX.
+Fully dimensioned drawings of the second floor, first floor, and basement are shown in Figs.~\ref{fig:drawing_second_floor}, \ref{fig:drawing_first_floor} and \ref{fig:drawing_basement}, respectively.
 
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/exterior_alpha} \\
-% \includegraphics[width=6.5in]{../Figures/exterior_charlie}
-% \caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
-% \label{fig:alpha_ex}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=3.20in]{../Figures/post_exterior_front}
+\hfill
+\includegraphics[width=3.20in]{../Figures/post_exterior_rear}
+\caption{Front (left) and rear (right) exterior of the structure after the incident.}
+\label{fig:post_exterior}
+\end{figure}
 
@@
 Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area.
-The basement consisted of a finished living area with a large utilities area and contained primarily upholstered polyurethane furniture fuel items.
+The basement primarily contained upholstered polyurethane furniture fuel items.
 
@@
 \caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:drawing_first_floor}
+\label{fig:drawing_second_floor}
 \end{figure}
@@
 \caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:drawing_second_floor}
+\label{fig:drawing_first_floor}
 \end{figure}

### 2014-08-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Minor fix to ambient temp.

@@
 Grid Cell Size                                             &  10~cm                                        & Section~\ref{mesh}                    \\ [.25cm]
-Ambient Temperature$^*$                                    &  20~$^{\circ}$C (77~$^{\circ}$F)              & --                                    \\ [.1cm]
+Ambient Temperature$^*$                                    &  20~$^{\circ}$C (68~$^{\circ}$F)              & --                                    \\ [.1cm]
 \multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\

### 2014-08-18 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Edit to description of temperature bounds in SLCFs
Chicago: minor update following Bruns' ERB comments

@@
 The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
-Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gasses.
+Based on the laws of conservation of mass, momentum,  and energy, the model tracks the generation and movement of fire gases.
 One of the most important advantages of FDS is that it is  mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
@@
 Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
+In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output, and the actual simulated temperatures may exceed the lower or upper bounds.
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
@@
 The results of the FDS simulations are discussed in the following two sections.
-The first section addresses the results of the computational modeling as they relate to the interior hallways conditions.
+The first section addresses the results of the computational modeling as they relate to the interior hallway's conditions.
 The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
@@
 \chapter{Summary}
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
 The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer}, post-incident pictures, videos, and relevant literature.

### 2014-08-18 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to geometry, numerical mesh, and simulation parameters sections

@@
 
-% The analysis of the simulation results is focused on the interior conditions on the second floor before and after the interior door failure.
+The analysis of the simulation results is focused on the interior conditions on the first floor where the downed firefighters were located and the conditions in the interior stairwell leading to the basement.
 Based on the goals of the analysis and the information collected, several engineering approximations were made.
-For example, the fire exhibited signs of under-ventilated conditions when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to documented observations.
-The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+The ignition time, growth rate, and HRR were estimated were estimated using documentation of the potential fuel load within the structure.
 
@@
 The right side of the structure shared a common fire wall with another residential structure.
+The structure had a 17.73~m (58~ft) by 6.38~m (21~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:simp_geom}.
+
 The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located above the street level and two stories were located below the street level.
@@
 More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:model_results}.
-Figure~\ref{fig:post_exterior} shows the XX of the structure after the incident.
-Note that the majority of the damage occurred XX.
+Figure~\ref{fig:post_exterior} shows the exterior of the front and rear of the structure after the incident.
+Note that the majority of the exterior damage occurred above the openings located on the basement floor (where the wooden balcony is located).
 Fully dimensioned drawings of the second floor, first floor, and basement are shown in Figs.~\ref{fig:drawing_second_floor}, \ref{fig:drawing_first_floor} and \ref{fig:drawing_basement}, respectively.
@@
 \end{equation}
-% From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$.
+From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$.
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 18.8 for the initial couch fire (peak HRR of 5.4~MW) and 28.3 for the basement flashover fire (HRR of 15~MW).
 Based on validation work performed for the U.S.
@@
 
-% As discussed in Section~\ref{sec:geometry}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 6.38~m (21~ft) and a total height of 5.9~m (19~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
+The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft).
+A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
 Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
-The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
+The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 \midrule
-Simulation Time                           &  5~min                                        &  --                                \\
+Simulation Time                           &  9~min                                        &  --                                \\
 Grid Cell Size                            &  10~cm                                        &  Section~\ref{sec:numerical_mesh}  \\
-Ambient Temperature$^*$                   &  20~$^{\circ}$C (77~$^{\circ}$F)              &  --                                \\
-Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fire}            \\
-                                          &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
-                                          &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
-                                          &  Heat of Combustion: 16,400~kJ/kg             &                                    \\
-Peak HRR                                  &  Attic Fire: 9~MW                             &  Section~\ref{sec:fire}            \\
-                                          &  Porch Fire: 3.3~MW                           &                                    \\
-Material: Wood~\cite{Incropera:1}         &  $k$: 0.12~\si{W/(m.K)})                      &  Section~\ref{sec:materials}       \\
-                                          &  $\rho$: 510~kg/m$^3$                         &                                    \\
-                                          &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                    \\
+Ambient Temperature$^*$                   &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
+Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fire}            \\
+                                          &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
+                                          &  CO Yield: 0.010~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
+                                          &  Heat of combustion: 26,200~kJ/kg             &                                    \\
+Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fire}            \\
+                                          &  Basement flashover fire: 15~MW               &                                    \\
 Material: Gypsum Board~\cite{WAKILI2007}  &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
                                           &  $\rho$: 810~kg/m$^3$                         &                                    \\
-                                          &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                    \\
+                                          &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}                  &                                    \\
 \bottomrule
@@
 \footnotesize
-\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
+\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
 \normalsize
@@
 
-% Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
-Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation.
-In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
-This is similar to the location of the creases in the remains of the steel door that was located between the hallway and the enclosed porch in this fire incident.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/SC_Door_1} \\
-% \includegraphics[width=6.5in]{../Figures/SC_Door_2}
-% \caption{Post-experiment images of door failures.}
-% \label{fig:SC_doorfold}
-% \end{figure}
-
 % After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.

### 2014-08-18 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor updates to input files, add tables, write up to report

@@
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
+The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel.
 The following narrative of the incident, focused on the events which led to burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
@@
 \end{quote}  
-
-The Prince George's County report~\cite{PGCounty2013}  \noindent Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the timeline of events.
 \begin{table}[!h]
 \centering
-\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}}\label{tab:fire_info}
+\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}.}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 
-The analysis of the simulation results is focused on the impact of ventilation, specifically opening and closing the front door, on the conditions on the first floor of the structure.
+The analysis of the simulation results is focused on the impact of ventilation.
+Specifically on the  interior conditions of the first floor following the establishment of a flow path through door control and how wind impacted these conditions.
+Based on the goals of the analysis and the information collected, several engineering approximations were made.
+For example, heavy smoke conditions were reported at the front of the house at the time of arrival~\cite{PGCounty2013}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event timeline (Table~\ref{tab:fire_info}) and documented observations.
+The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
 
@@
 \label{Vents}
+
+\begin{table}
+\centering
+\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
+\begin{tabular}{lllll}
+\toprule[1.5pt]
+Baseline     &   Ventilation   &  Type       & State of       &  Side of  \\
+Simulation  &  Area             &                 & Opening     &  Structure  \\
+{[s]}             &  {[m$^2$]}     &                 &                    &                  \\
+\midrule
+0                 &  1.84             &  Door        &  Opened     &  Rear  \\
+0                 &  1.40             &  Window   &  Opened     &  Rear  \\
+0                 &  0.39             &  Window   &  Opened     &  Left   \\
+100             &  1.84             &  Door        &  Opened     &  Front   \\
+207             &  1.84             &  Door        &  Closed      &  Front   \\
+211             &  0.26             &  Window   &  Opened     &  Front   \\
+221             &  0.26             &  Window   &  Opened     &  Front  \\
+264             &  1.84             &  Door        & Opened      & Front  \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\footnotesize
+\normalsize
+\end{table}
 

### 2014-08-20 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to ventilation and HRR sections

@@
                &                                                                                      \\
-10:58:00       &  Fire self-vents from the rear side of the structure when a glass door in the        \\
+10:58:42       &  Fire self-vents from the rear side of the structure when a glass door in the        \\
                &  basement fails.                                                                     \\
@@
                &                                                                                      \\
-11:02:00       &  E32 crew makes entry into the basement with a second hoseline.                      \\
+11:02:00       &  E32 crew makes entry into the basement with a second hoseline and begins            \\
+               &  suppression operations.                                                             \\
                &                                                                                      \\
@@
 
-The analysis of the simulation results is focused on the interior conditions on the first floor where the downed firefighters were located and the conditions in the interior stairwell leading to the basement.
+The analysis of the simulation results is focused on the interior conditions on the first floor where the downed firefighters were located and the conditions that resulted in the establishment of a flow path in the interior stairwell leading into the basement.
 Based on the goals of the analysis and the information collected, several engineering approximations were made.
@@
 \end{figure}
-
-\clearpage
 
@@
 
-\clearpage
-
 \section{Materials}
@@
 
-% The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
 Two different ventilation scenarios were considered in this study.
 The first scenario involves a baseline simulation in which the ventilation times and ventilation areas represent our best understanding of the incident.
-The second scenario, or alternative simulation, does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
-The times of the ventilation changes are provided in Table~\ref{tab:ventilation_timeline}.
+The second scenario, or alternative simulation, involves the exterior basement door on the left side of the structure being open during the entire simulation.
+The times of the ventilation changes of exterior doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
+
+During the time at which the downed firefighters were located, the state of the windows and doors in the structure was known, which resulted in the establishment of a flow path in the interior stairwell leading into the basement.
+However, the exact time of operation for some doors was not known.
+Therefore, these doors were assumed to be open at the start of the simulation, which included 1) the front door, 2) the interior door leading from the hallway on the first floor into the stairwell towards the basement, 3) the door leading from the first floor landing into the garage, and 4) the overhead garage door.
+
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
+The open front door at the start of the simulation and the vents created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
 
-% An unknown parameter in Table~\ref{tab:ventilation_timeline} that needed to be estimated was the time when the second floor interior/porch door failed (160~s into the simulation).
-The area of failure was also estimated based on the following observations.
-The bottom hinge from the door appeared to be closed throughout the fire due to the lack of fire damage and the lack of soot deposited on the interior faces of the hinge and remaining wood, as shown in Fig.~\ref{fig:door_frame}.
-It appears that the door collapsed and failed partially open.
-In the simulations, only the upper portion of the door was assumed to fail.
-While this time and area may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
-
-\clearpage
-
 \begin{table}[!ht]
-\caption[Timeline of ventilation changes in the simulation]{Timeline of ventilation changes in the simulation}
+\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
 \begin{tabular}{cccll}
 \toprule
-Baseline    &  Alternative  &  Ventilation  &  Type         &  Side of         \\
-Simulation  &  Simulation   &  Area         &               &  Structure       \\
+Baseline    &  Alternative  &  Ventilation  &  Type                &  Location of Vent        \\
+Simulation  &  Simulation   &  Area         &                      &                          \\
 {(s)}       &  {(s)}        &  (m$^2$)      &                      &                          \\
 \midrule
-0           &  0            &  0.11         &  Window       &  Rear            \\
-40          &  40           &  0.08         &  Breach (x2)  &  Front and Rear  \\
-45          &  45           &  0.12         &  Breach       &  Left            \\
-55          &  55           &  0.12         &  Breach       &  Rear            \\
-130         &  N/A$^*$      &  1.41         &  Door         &  Rear            \\
-135         &  N/A$^*$      &  0.2          &  Breach       &  Left            \\
-160         &  160          &  0.80         &  Door         &  Interior        \\
+0           &  0            &  1.47         &  Door                &  Front Exterior          \\
+0           &  0            &  1.68         &  Door                &  Interior (Stairwell)    \\
+0           &  0            &  1.68         &  Door                &  Interior (Garage)       \\
+0           &  0            &  10.1         &  Overhead Door       &  Front Exterior          \\
+N/A$^*$     &  0            &  1.68         &  Door                &  Left Basement Exterior  \\
+342         &  342          &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
+383         &  383          &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
+418         &  418          &  2.52         &  Window              &  Rear Basement Exterior  \\
+440         &  440          &  2.31         &  Window              &  Rear Basement Exterior  \\
+450         &  450          &  3.78         &  Sliding Glass Door  &  Rear Basement Exterior  \\
 \bottomrule
@@
 \footnotesize
-\\$^*$These ventilation events were not included in the alternative simulation.
+\\$^*$This ventilation event was not included in the baseline simulation.
 \normalsize
@@
 \end{table}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/door_frame_burn}
-% \caption[Post-incident image of rear porch door frame.]{Post-incident image of the second floor porch door frame that failed taken from inside the structure looking toward the porch.
-Note that the hinge is still intact and there is unburned, ``clean'' wood along the bottom portion of the frame.}
-% \label{fig:door_frame}
-% \end{figure}
-
-\clearpage
 
@@
 \midrule
-10:45:00       &              &  Dispatch for a curtain fire due to an electrical short at a residential structure.  \\
+10:45:00       &              &  Dispatch for a curtain fire due to an electrical short at a      \\
+               &              &  residential structure.                                           \\
                &              &                                                                   \\
-10:48:00       &              &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
-               &              &  the front door with a 1 3/4'' hoseline.                                             \\
+10:48:00       &              &  E26 arrives on scene, reports light smoke conditions, and        \\
+               &              &  makes entry into the front door with a 1 3/4'' hoseline.         \\
                &              &                                                                   \\
-10:52:00       &  0           &  FDS simulation begins.                                                              \\
+10:53:00       &  0           &  FDS simulation begins.                                           \\
                &              &                                                                   \\
-10:54:00       &              &  E26 crew states that the fire is located below the first floor.                     \\
+10:54:00       &  60          &  E26 crew states that the fire is located below the first floor.  \\
                &              &                                                                   \\
-10:56:00       &              &  BC9 observes smoke but no fire at the left rear corner of the structure.            \\
+10:56:00       &  180         &  BC9 observes smoke but no fire at the left rear corner           \\
+               &              &  of the structure.                                                \\
                &              &                                                                   \\
-10:58:00       &              &  Fire self-vents from the rear side of the structure when a glass door in the        \\
-               &              &  basement fails.                                                                     \\
+10:58:42       &  342         &  Fire self-vents from the rear side of the structure when a       \\
+               &              &  glass door in the basement fails.                                \\
                &              &                                                                   \\
-10:59:00       &              &  BC9 forces open the basement door on the left side of the structure,                \\
-               &              &  reports heavy fire and smoke, and requests a second hoseline.                       \\
+10:59:00       &  360         &  BC9 forces open the basement door on the left side of            \\
+               &              &  the structure, reports heavy fire and smoke, and requests a      \\
+               &              &  second hoseline.                                                 \\
                &              &                                                                   \\
-11:00:00       &              &  BC6 notices a severe change in conditions (heavy black smoke from garage).          \\
+11:00:00       &  420         &  BC6 notices a severe change in conditions (heavy black smoke     \\
+               &              &  from garage).                                                    \\
                &              &                                                                   \\
-11:01:00       &              &  Heavy fire and black smoke observed at rear of structure. Incident command          \\
-               &              &  (IC) attempts to contact E26 several times via radio with no reply.                 \\
+11:01:00       &  480         &  Heavy fire and black smoke observed at rear of structure.        \\
+               &              &  Incident command (IC) attempts to contact E26 several times      \\
+               &              &  via radio with no reply.                                         \\
                &              &                                                                   \\
-11:02:00       &              &  E32 crew makes entry into the basement with a second hoseline.                      \\
+11:02:00       &  540         &  E32 crew makes entry into the basement with a second hoseline    \\
+               &              &  and begins suppression operations. FDS simulation ends.          \\
                &              &                                                                   \\
@@
 
+\clearpage
+
 \section{Heat Release Rate}
@@
 
-% The heat release rate output data from FDS quantifies the simulated rate of energy release in the simulation.
-Figure~\ref{fig:hrr} shows the prescribed HRR versus time values based on the prescribed fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
-The two vertical lines represent the time at which a firefighter opened the back door of the structure ($t$ = 130 s) and the time at which the second floor interior door was estimated to fail ($t$ = 160 s).
-Due to a lack of information about the time of fire ignition or how fast the fire grew, these parameters needed to be estimated.
-The growth rate shown in Fig.~\ref{fig:hrr} (10~MW in approximately 20~s) is fast because the incipient stage of the fire growth was not considered in this study.
-The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited quickly to minimize computational time while aligning with the timeline observations of video and picture evidence from the fire.
-Using this approach, the accuracy of heat transfer to the walls of the structure may be sacrificed; however, all of the window, door, and wall failures were driven by the event timeline rather than failure temperature criteria.
+The HRR output quantity from FDS represents the predicted amount of combustion that would have occurred in the fire scenario, which depends on the amount of available fuel, oxygen, and ventilation.
+In the FDS simulations, the nominal HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
+As a result, the actual HRR in FDS can be lower than the specified HRR based on the ventilation conditions.
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/Chicago_Fire_HRR}
-% \caption[HRR versus time from the FDS simulations.]
-% {HRR versus time from the FDS simulations.
-The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
-% \label{fig:hrr}
-% \end{figure}
+Figure~\ref{fig:hrr} shows the nominal HRR vs.
+time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
+The vertical line represents the time at which the first basement window on the rear side of the structure failed (342~s).
+The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with the timeline observations from the fire scenario.
+Note that the rear window failures were driven by the event timeline rather than failure temperature criteria.
 
-% In Fig.~\ref{fig:hrr}, the solid line represents the baseline FDS simulation (this follows the noted door openings from the incident).
-The dashed line represents an alternative series of events in which the rear door does not get opened and the subsequent breach of the rear porch wall on the left side of the structure does not occur.
-The dash-dotted line represents the prescribed (or nominal) HRR that was input into FDS.
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/Fire_HRR}
+\caption[HRR vs. time from the FDS simulations.]
+{HRR vs. time from the FDS simulations. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
+\label{fig:hrr}
+\end{figure}
+
+In Fig.~\ref{fig:hrr}, the XX line represents the baseline FDS simulation.
+The XX line represents an alternative simulation in which the basement door on the left side of the structure is open throughout the simulation.
+The XX line represents the nominal HRR that was input into FDS.
 As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
-The maximum HRR value is slightly less than 9~MW before the fire becomes ventilation limited and begins to decay.
-The HRR is reduced to 5~MW as the oxygen inside the structure is consumed.
-There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the vents where fresh air is available.
-Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
-After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
-The HRR then increases towards a sustainable steady-state value.
+The maximum HRR value is approximately XX~MW before the fire becomes ventilation limited and begins to decay.
+The HRR is reduced to XX~MW as the amount of oxygen inside the structure becomes limited.
+There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the ventilation openings where fresh air is available.
+Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at XX~s.
+After additional window failures occur at XX~s and XX~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to XX~MW before it decreases to approximately XX~MW.
+The HRR then increases towards a steady-state value.
 
@@
 % \end{figure}
-
-\clearpage
 
@@
 % \end{figure}
-
-% \clearpage
 
@@
 
-\clearpage
-
 \section{Assessing the Hazard}

### 2014-08-20 Studies/2011_San_Francisco/Figures/generate_figures.py

@@ -1,0 +1,57 @@
+#!/usr/bin/env python
+
+from __future__ import division
+
+import numpy as np
+import pandas as pd
+from pylab import *
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+
+def movingaverage(interval, window_size):
+    window= np.ones(int(window_size))/float(window_size)
+    return np.convolve(interval, window, 'same')
+
+FDS_baseline_file = '../FDS_Output_Files/133_berkeley_fire_baseline_hrr.csv'
+FDS_alternative_file = '../FDS_Output_Files/133_berkeley_fire_baseline_hrr.csv'
+
+FDS_baseline = pd.read_csv(FDS_baseline_file, header=1)
+HRR_baseline = FDS_baseline['HRR'] / 1000
+HRR_baseline_avg = movingaverage(HRR_baseline, 2)
+
+FDS_alternative = pd.read_csv(FDS_alternative_file, header=1)
+HRR_alternative = FDS_alternative['HRR'] / 1000
+HRR_alternative_avg = movingaverage(HRR_alternative, 2)
+
[…]

### 2014-08-20 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update ventilation section in report

@@
 \label{geom}
+The structure involved in this fire incident was a one story, single-family structure with a basement.
+Due to the surrounding topography (the ground slopes from the front to rear of the structure), the basement on the rear side of the structure was above grade.
+The structure was wood-framed platform-framed with a gable roof.
+\footnote{Platform-framed construction means that floor joists are completely covered with a sub-floor.
+This forms a platform for which walls are built from.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}.
+This results in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
+The interior walls and ceiling were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{PGCounty2013}.
+There is a single flight of stairs in the center of the structure which connected the first floor to the basement.
+Access to the structure could be made on the front side of the first floor and the rear side of the basement.
+
+\begin{figure}[!ht]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+\includegraphics[width=.7\textwidth]{../Figures/Basement} \\
+\includegraphics[width=.7\textwidth]{../Figures/First_Floor}
+\end{tabular*}
+\caption[Plan view of basement (top) and first (bottom) floor of structure.]{Plan view of basement (top) and first (bottom) floor of structure.
+Stairs and key windows and doors are identified using measurements collected by NIST.}
+\label{fig:simp_geom}
+\end{figure}
 
@@
 \label{Vents}
+The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors, breaking windows), fire acting on the structure (fire breaching windows/doors) and wind (restricting flow, closing doors).
+Three ventilation scenarios were considered in this study.
+Each scenario followed the timeline of events outlined in Table~\ref{tab:vents}.
+The difference in each scenario is the wind boundary condition.
+Simulations were run at 0~m/s (0~mph), 4.47~m/s (10~mph), and 8.94~m/s (20~mph) wind velocities with a flow direction from the rear toward the front of the structure.
+Based on local weather conditions, mean wind velocities ranged between 4.47~m/s (10~mph) and 8.94~m/s (20~mph).
+The case without wind was run to control for the impact of wind on the flow of hot gases within the structure.
+
+Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
+The open rear basement door and two open windows at the start of the simulation are significantly larger than the total effective area of leakage of a structure of this type.
+Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
 

### 2014-08-21 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to fire/HRR description

@@
 The interior walls were composed of gypsum board over insulated wood framing.
-The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (10 stairs down) or the second floor (5 stairs up).
+The entrance stairs located on the front side of the structure led to the front door and an interior landing, which allowed access to the first floor (ten~stairs down) or the second floor (five~stairs up).
 
@@
 The basement primarily contained upholstered polyurethane furniture fuel items.
+The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
 
@@
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
+
+% The first 300~s of the HRR in the simulation follow the mattress HRR. After 300~s, the specified fire size is 20~MW.
 
@@
 The HRR output quantity from FDS represents the predicted amount of combustion that would have occurred in the fire scenario, which depends on the amount of available fuel, oxygen, and ventilation.
-In the FDS simulations, the nominal HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
+In the FDS simulations, a prescribed HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
 As a result, the actual HRR in FDS can be lower than the specified HRR based on the ventilation conditions.
 
-Figure~\ref{fig:hrr} shows the nominal HRR vs.
+Figure~\ref{fig:hrr} shows the prescribed HRR vs.
 time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
@@
 The XX line represents an alternative simulation in which the basement door on the left side of the structure is open throughout the simulation.
-The XX line represents the nominal HRR that was input into FDS.
+The XX line represents the prescribed HRR that was input into FDS.
 As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.

### 2014-08-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Remove alternative ventilation scenario/simulation

@@
 The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
-Two different ventilation scenarios were considered in this study.
-The first scenario involves a baseline simulation in which the ventilation times and ventilation areas represent our best understanding of the incident.
-The second scenario, or alternative simulation, involves the exterior basement door on the left side of the structure being open during the entire simulation.
+The ventilation times and ventilation areas represent our best understanding of the incident.
 The times of the ventilation changes of exterior doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
@@
 \caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
-\begin{tabular}{cccll}
+\begin{tabular}{ccll}
 \toprule
-Baseline    &  Alternative  &  Ventilation  &  Type                &  Location of Vent        \\
-Simulation  &  Simulation   &  Area         &                      &                          \\
-{(s)}       &  {(s)}        &  (m$^2$)      &                      &                          \\
+FDS Simulation  &  Ventilation  &  Type                &  Location of Vent        \\
+Time            &  Area         &                      &                          \\
+{(s)}           &  (m$^2$)      &                      &                          \\
 \midrule
-0           &  0            &  1.47         &  Door                &  Front Exterior          \\
-0           &  0            &  1.68         &  Door                &  Interior (Stairwell)    \\
-0           &  0            &  1.68         &  Door                &  Interior (Garage)       \\
-0           &  0            &  10.1         &  Overhead Door       &  Front Exterior          \\
-N/A$^*$     &  0            &  1.68         &  Door                &  Left Basement Exterior  \\
-342         &  342          &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
-383         &  383          &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
-418         &  418          &  2.52         &  Window              &  Rear Basement Exterior  \\
-440         &  440          &  2.31         &  Window              &  Rear Basement Exterior  \\
-450         &  450          &  3.78         &  Sliding Glass Door  &  Rear Basement Exterior  \\
+0               &  1.47         &  Door                &  Front Exterior          \\
+0               &  1.68         &  Door                &  Interior (Stairwell)    \\
+0               &  1.68         &  Door                &  Interior (Garage)       \\
+0               &  10.1         &  Overhead Door       &  Front Exterior          \\
+N/A$^*$         &  1.68         &  Door                &  Left Basement Exterior  \\
+342             &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
+383             &  1.89         &  Sliding Glass Door  &  Rear Basement Exterior  \\
+418             &  2.52         &  Window              &  Rear Basement Exterior  \\
+440             &  2.31         &  Window              &  Rear Basement Exterior  \\
+450             &  3.78         &  Sliding Glass Door  &  Rear Basement Exterior  \\
 \bottomrule
@@
 \footnotesize
-\\$^*$This ventilation event was not included in the baseline simulation.
+\\$^*$This ventilation event was not included in the simulation.
 \normalsize
@@
 
-In Fig.~\ref{fig:hrr}, the XX line represents the baseline FDS simulation.
-The XX line represents an alternative simulation in which the basement door on the left side of the structure is open throughout the simulation.
+In Fig.~\ref{fig:hrr}, the XX line represents the FDS simulation.
 The XX line represents the prescribed HRR that was input into FDS.

### 2014-08-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Updates to ventilation timeline and details

@@
                &                                                                                      \\
-10:58:42       &  Fire self-vents from the rear side of the structure when a glass door in the        \\
-               &  basement fails.                                                                     \\
+10:58:42       &  Fire self-vents from the rear side of the structure when a glass window in the      \\
+               &  basement fails. Additional glass windows on the rear side of the structure fail     \\
+               &  over the next two minutes.                                                          \\
                &                                                                                      \\
-10:59:00       &  BC9 forces open the basement door on the left side of the structure,                \\
+10:59:23       &  BC9 forces open the basement door on the left side of the structure,                \\
                &  reports heavy fire and smoke, and requests a second hoseline.                       \\
@@
 \toprule
-FDS Simulation  &  Ventilation  &  Type                &  Location of Vent        \\
-Time            &  Area         &                      &                          \\
+FDS Simulation Time  &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
 {(s)}                &  (m$^2$)           &                      &                           \\
@@
 0                    &  1.47              &  Door                &  Front Exterior           \\
+0                    &  10.1              &  Overhead Door       &  Front Exterior (Garage)  \\
 0                    &  1.68              &  Door                &  Interior (Stairwell)     \\
 0                    &  1.68              &  Door                &  Interior (Garage)        \\
-0               &  10.1         &  Overhead Door       &  Front Exterior          \\
-N/A$^*$         &  1.68         &  Door                &  Left Basement Exterior  \\
 342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
 383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
+383                  &  1.68              &  Door                &  Left Basement Exterior   \\
 418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
@@
 \end{tabular}
-\footnotesize
-\\$^*$This ventilation event was not included in the simulation.
-\normalsize
 \label{tab:ventilation_timeline}
@@
                &              &                                                                    \\
-10:58:42       &  342         &  Fire self-vents from the rear side of the structure when a       \\
-               &              &  glass door in the basement fails.                                \\
+10:58:42       &  342         &  Fire self-vents from the rear side of the structure when a glass  \\
+               &              &  window in the basement fails. Additional glass windows on the     \\
+               &              &  rear side of the structure fail over the next two minutes.        \\
                &              &                                                                    \\
-10:59:00       &  360         &  BC9 forces open the basement door on the left side of            \\
+10:59:23       &  383         &  BC9 forces open the basement door on the left side of             \\
                &              &  the structure, reports heavy fire and smoke, and requests a       \\

### 2014-08-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Additional edits to ventilation timeline and details

@@
 \toprule
-FDS Simulation Time  &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
+Simulation Time      &  Ventilation Area  &  Ventilation Type    &  Ventilation Location     \\
 {(s)}                &  (m$^2$)           &                      &                           \\
 \midrule
-0                    &  1.47              &  Door                &  Front Exterior           \\
-0                    &  10.1              &  Overhead Door       &  Front Exterior (Garage)  \\
-0                    &  1.68              &  Door                &  Interior (Stairwell)     \\
-0                    &  1.68              &  Door                &  Interior (Garage)        \\
+0                    &  1.47              &  Door                &  Front Entry Exterior     \\
+0                    &  10.1              &  Overhead Door       &  Front Garage Exterior    \\
+0                    &  1.68              &  Door                &  Stairwell Interior       \\
+0                    &  1.68              &  Door                &  Garage Interior          \\
 342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\

### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Rename figures

@@
 
-Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at the National Institute of Standars and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
@@
 \begin{figure}[!ht]
-\includegraphics[width=3.20in]{../Figures/post_exterior_front}
+\includegraphics[width=3.20in]{../Figures/Post_Exterior_Front}
 \hfill
-\includegraphics[width=3.20in]{../Figures/post_exterior_rear}
+\includegraphics[width=3.20in]{../Figures/Post_Exterior_Rear}
 \caption{Front (left) and rear (right) exterior of the structure after the incident.}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Top_Floor_Metric}
+\includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
 \caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Ground_Floor_Metric}
+\includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
 \caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Sub_Level_1_Metric}
+\includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
 \caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}

### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add plan diagrams; update exterior photos

@@
 \noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events.
-A plan view of the structure and the location where the captain collapsed are shown in Fig.~\ref{fig:simp_geom}, and more details of the fire development are provided in the following sections.
+A plan view of the structure, the location where the downed firefighters were located, and more details of the fire development are provided in the following section.
 
@@
 The right side of the structure shared a common fire wall with another residential structure.
-The structure had a 17.73~m (58~ft) by 6.38~m (21~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:simp_geom}.
+The structure had a 17.73~m (58~ft) by 8.53~m (28~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
 
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/1st_Floor_Metric} \\
-% \includegraphics[width=6.5in]{../Figures/2nd_Floor_Metric}
-% \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
-Stairs and key rooms are identified using measurements collected by NIST.}
-% \label{fig:simp_geom}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor_Metric}
+\includegraphics[width=5.0in]{../Figures/Plan_First_Floor_Metric}
+\includegraphics[width=5.0in]{../Figures/Plan_Basement_Metric}
+\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
+Stairs and rooms are identified using measurements collected by NIST.}
+\label{fig:floor_plan}
+\end{figure}
 
 \begin{figure}[!ht]
-\includegraphics[width=3.20in]{../Figures/Post_Exterior_Front}
-\hfill
-\includegraphics[width=3.20in]{../Figures/Post_Exterior_Rear}
-\caption{Front (left) and rear (right) exterior of the structure after the incident.}
+\includegraphics[width=5.50in]{../Figures/Post_Exterior_Front} \\
+\vspace{0.1in}
+\includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
+\caption{Front (top) and rear (bottom) exterior of the structure after the incident.}
 \label{fig:post_exterior}
@@
 
-As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 6.38~m (21~ft) and a total height of 5.9~m (19~ft).
+As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.

### 2014-08-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add SMV images of exterior

@@
 \noindent Table~\ref{tab:incident_timeline} shows an overview of the timeline of events.
-A plan view of the structure, the location where the downed firefighters were located, and more details of the fire development are provided in the following section.
+The following section includes a plan view of the structure, the location where the downed firefighters were located, and more details of the fire development.
 
@@
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
 The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid} \\
-% \includegraphics[width=6.5in]{../Figures/smv_exterior_grid_rear}
-% \caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
-% \label{fig:geom_grid}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
+\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Rear}
+\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
+\label{fig:SMV_exterior_grid}
+\end{figure}
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/smv_exterior_mesh}
-% \caption[Front-right side of the structure within the computational domain.]
-% {Front-right side of the structure within the computational domain (with multiple meshes). Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
-% \label{fig:mult_mesh}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
+\caption[Rear-left side of the structure within the computational domain.]
+{Rear-left side of the structure within the computational domain (with multiple meshes).}
+\label{fig:mult_mesh}
+\end{figure}
 

### 2014-08-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor formatting edits

@@
 10:48:00       &  E26 arrives on scene, reports light smoke conditions, and makes entry into          \\
-               &  the front door with a 1 3/4'' hoseline.                                             \\
+               &  the front door with a 1~\sfrac{3}{4}~in hoseline.                                   \\
                &                                                                                      \\
@@
 \footnotesize
-\\ $^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
+\\ $^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
 \normalsize
@@
 10:48:00       &              &  E26 arrives on scene, reports light smoke conditions, and           \\
-               &              &  makes entry into the front door with a 1 3/4'' hoseline.          \\
+               &              &  makes entry into the front door with a 1~\sfrac{3}{4}~in hoseline.  \\
                &              &                                                                      \\

### 2014-08-27 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg 2014 Report: Added author, changed figure names
Spartanburg: update image name and report
Spartanburg 2014: Add 286 College Test Descriptions to report appendix

@@
 Craig G. Weinschenk \\
+Keith M. Stakes \\
 
@@
 Craig G. Weinschenk \\
+Keith M. Stakes \\
 {\em Fire Research Division \\
@@
 \includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
-\caption{Instrumentation, 305 Manning, first floor}
-\label{fig:Instrumentation_305_Manning_1st_Floor}
+\caption{Instrumentation, 289 Manning, first floor}
+\label{fig:Instrumentation_289_Manning_1st_Floor}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_2nd_Floor}
-\caption{Instrumentation, 305 Manning, second floor}
-\label{fig:Instrumentation_305_Manning_2nd_Floor}
+\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_Basement}
+\caption{Instrumentation, 289 Manning, basement}
+\label{fig:Instrumentation_289_Manning_basement}
 \end{figure}
@@
 
+The first set of experiments were conducted in a single story residential structure with attached garage addressed as 286 College Street.
+The structure consisted of type 5 construction.
+The attached garage was added on to the B side of the structure for the purpose of these tests.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Three tests were conducted in this structure: 1) A living room fire with a residential sprinkler present, 2) An attached garage fire with exterior attack, and 3) A living room fire with door control.
+
 \subsection{Test 1, Living room fire with sprinkler}
+
+Test 1 consisted of a fire in the living room with residential sprinkler activation.
+Ignition occurred on a couch in the living room to the rear of the structure near the C/D corner.
+The fire was remotely ignited from the exterior of the structure.
+There was a residential sprinkler in the fire room.
+Other fire room furnishings included a sofa chair, two wooden end tables, a floor lamp, cloth window curtains, carpeted floor, and wooden paneling for wall linings.
+The fire grew uninhibited until the sprinkler activated and suppressed the bulk of the fire.
+A fire fighting crew made entry through side C for mop-up.
 
@@
 \subsection{Test 2, Garage fire, exterior attack}
+
+Test 2 consisted of a fire in the attached garage with an exterior fire attack.
+Two separate ignition points were used, one of which was inside a car located in the garage and another was located on a couch to the rear of the garage.
+The couch simulated other fuel loads commonly found within a garage.
+Several wooden pallets were also placed in the garage for additional fuel.
+The fire was ignited remotely from the exterior of the garage.
+The door from the attached garage to the interior of the structure (kitchen area) remained closed for the duration of this test.
+The fire grew uninhibited in the garage until the space reached flashover conditions and became fully-involved.
+The fire was knocked down and suppressed from the exterior of the structure by a fire fighting crew with a single hand-line in a straight stream pattern.
+The front door on Side A of the structure was then opened to simulate a crew making entry.
 
@@
 \subsection{Test 3, Living room fire}
+
+Test 3 consisted of a fire in the living room located in the front of the structure near the A/B corner.
+The ignition point for this test was the corner of a modern-style couch and was performed remotely from the exterior of the structure.
+Other fuels present in the room were another modern-style sofa and a modern-style love seat.
+The fire room was lined with OSB paneling for additional fuel.
+The front side A door was in the open position for the start of the test.
+The target room, located adjacent to the fire room near the A/D corner, was separated by a closed hollow core wooden door.
+Once ignited, the fire grew uninhibited until the room approached flashover conditions.
+Prior to this, the front door to the room was closed.
+The fire was allowed to stabilize and then the front door was opened.
+The fire fighting crew made an attack from the exterior via a straight stream pattern from a single hand-line.
+The pattern was then switched to a narrow fog for further suppression.
+The fire fighting crew then made entry into the fire room for mop-up procedures.
 

### 2014-09-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update HRR details

@@
 \caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
+The fire originated in the living room on the basement floor.
 Stairs and rooms are identified using measurements collected by NIST.}
@@
 &SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
-&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER' /
+&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER', DEVC_ID='TIMER_INITIAL_BURNER_OFF' /
+&DEVC ID='TIMER_INITIAL_BURNER_OFF', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.TRUE., SETPOINT=300 /
 
-&SURF ID='FLASHOVER_BURNER', HRRPUA=270.563, COLOR='RED' /
-&VENT XB=0.0, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
+&SURF ID='FLASHOVER_BURNER', HRRPUA=365.097, COLOR='RED' /
+&VENT XB=0.1, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
 &DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /

### 2014-09-02 Studies/2011_San_Francisco/Figures/generate_figures.py

@@ -14,16 +14,11 @@ def movingaverage(interval, window_size):
     window= np.ones(int(window_size))/float(window_size)
     return np.convolve(interval, window, 'same')
 
-FDS_baseline_file = '../FDS_Output_Files/133_berkeley_fire_baseline_hrr.csv'
-FDS_alternative_file = '../FDS_Output_Files/133_berkeley_fire_baseline_hrr.csv'
+FDS_file = '../FDS_Output_Files/133_berkeley_fire_hrr.csv'
 
-FDS_baseline = pd.read_csv(FDS_baseline_file, header=1)
-HRR_baseline = FDS_baseline['HRR'] / 1000
-HRR_baseline_avg = movingaverage(HRR_baseline, 2)
-
-FDS_alternative = pd.read_csv(FDS_alternative_file, header=1)
-HRR_alternative = FDS_alternative['HRR'] / 1000
-HRR_alternative_avg = movingaverage(HRR_alternative, 2)
+FDS = pd.read_csv(FDS_file, header=1)
+HRR = FDS['HRR'] / 1000
+HRR_avg = movingaverage(HRR, 2)
 
 prescribed_time = np.array([0, 17, 23, 25, 35, 46, 53, 65, 80, 98, 112, 125, 133, 142, 144, 147, 157, 161, 167, 177, 184, 188, 195, 197, 201, 204, 205, 208, 215, 222, 230, 235, 241, 244, 246, 247, 250, 251, 253, 257, 260, 269, 273, 279, 282, 285, 288, 292, 295, 296, 297, 299, 300, 540])
 
@@ -31,10 +26,13 @@ prescribed_HRR = np.array([0, 5, 5, 16, 12, 12, 16, 20, 49, 98, 147, 199, 225, 2
 
 figure()
 plot(prescribed_time, prescribed_HRR, 'k-', lw=2, label='Prescribed HRR')
-plot(FDS_baseline['Time'], HRR_baseline_avg, 'r--', lw=2, label='FDS Model HRR (Baseline Simulation)')
-plot(FDS_alternative['Time'], HRR_alternative_avg, 'g-.', lw=2, label='FDS Model HRR (Alternative Simulation)')
+plot(FDS['Time'], HRR_avg, 'r--', lw=2, label='FDS Model HRR')
 plt.text(342+20, 2, 'Rear Window Failures Begin')
 axvline(342, color='k', ls='--', lw=2)
[…]

### 2014-09-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to HRR description

--- 2014-08-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that spanned the entire basement floor area.
+Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that involved the entire basement floor area.
 The basement primarily contained upholstered polyurethane furniture fuel items.
@@
 
-% The first 300~s of the HRR in the simulation follow the mattress HRR. After 300~s, the specified fire size is 20~MW.
+The HRR was prescribed in FDS as follows.
+From 0~s to 300~s, the HRR in the simulation followed the experimentally measured mattress HRR.
+At 300~s, the HRR was approximately 3~MW.
+From 300~s to 342~s (the time at which the first basement window failed), the HRR increased linearly from 3~MW to 20~MW.
+From 342~s to 540~s, the HRR was 15~MW.
+Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
+A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{sec:HRR}.
 
@@
 \begin{lstlisting}
-&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Fire_Ramp' /
-&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER' /
+&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Mattress_Ramp' /
+&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER', DEVC_ID='TIMER_INITIAL_BURNER_OFF' /
+&DEVC ID='TIMER_INITIAL_BURNER_OFF', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.TRUE., SETPOINT=300 /
 
-&SURF ID='FLASHOVER_BURNER', HRRPUA=270.563, COLOR='RED' /
-&VENT XB=0.0, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER', DEVC_ID='TIMER_FLASHOVER' /
-&DEVC ID='TIMER_FLASHOVER', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.FALSE., SETPOINT=300 /
+&SURF ID='FLASHOVER_BURNER', HRRPUA=0.018255, COLOR='RED', RAMP_Q='Flashover_Ramp' /
+&VENT XB=0.1, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER' /
 \end{lstlisting}

### 2014-09-05 Projects/Spartanburg_2013/Spartanburg_2013.tex
Spartanburg 2013: Test Descriptions

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Spartanburg 2013 Test Descriptions}
\author{Keith Stakes}

\begin{document}

\maketitle

\section{214 Folsom Street}

The first test house was a single story, single family residential structure of type 5 construction addressed as 214 Folsom Street.  The single story structure The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.  The burn rooms had a combustible finish comprised of OSB sheets for wall linings.  Two tests were conducted in this structure: 1) Living room fire with exterior attack and 2) Bedroom fire with exterior attack.

\subsection{Test 1: Living Room Fire}

Ignition begins on a modern-style sofa in the living room on the A/D corner of the structure with all doors and windows closed. The fire grew uninhibited and reach the vent-limited stage. Fire fighting crew ventilated the living room window on the D side of the structure.The fire was allowed to stabilize with the new ventilation opening. The fire fighting crew then applied water, via a straight stream flow, from the exterior into the D side window for suppression.  After the exterior suppression, the front living room window on the A side of the structure was ventilated.  Water was then applied from the exterior on the A side into the living room window for further suppression. The fire fighting crew then opened the front door and made entry to complete suppression.

\subsection{Test 2: Bedroom Fire}

The fire was ignited on a modern-style soda in the bedroom located near the B/C corner of the structure.  The living room used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results. The fire was allowed to grow uninhibited and reach the vent-limited stage. The fire self-vented the upper portion of the bedroom window on the B side of the structure.  The fire fighting crew ventilated a window on the D side of the building in the adjacent room located near the C/D corner.  The fire then self-vented the remaining portion of the window in the room of origin.  The small window into the kitchen on the B side of the structure was then ventilated.  Shortly thereafter, the fire fighting crew made an exterior attack via a narrow fog into the bedroom from the self-vented B side window.

\end{document}

### 2014-09-10 Projects/Spartanburg_2013/Spartanburg_2013.tex
Spartanburg 2013: Test Descriptions Cont'd

@@
 The first test house was a single story, single family residential structure of type 5 construction addressed as 214 Folsom Street.
-The single story structure The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
 The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
@@
 
+\section{215 Folsom Street}
+
+The second test house was a single story, single family residential structure of type 5 construction addressed as 215 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Living room fire with exterior attack and 2) Bedroom fire with exterior attack.
+
+\subsection{Test 1: Living Room Fire}
+
+The fire was ignited in the front living room located near the A/B corner of the structure on a modern-style sofa.
+The fire grew uninhibited until reaching the ventilation-limited stage.
+While in the growth stage, the fire self-vented the living room window on the A side of the structure, near the A/B corner.
+After the fire fighting unit officer completed a 360 degree size-up of the structure, the front door was opened from the exterior.
+The living room window on the B side of the structure then self-vented as well.
+Shortly thereafter, the pressure from the fire compartment closed the front door.
+After a short period of time, the fire fighting crew re-opened the front door to the building.
+The fire fighting crew began an attack on the structure via a single smooth bore hose-line first knocking down the fire on the porch.
+The nozzle was then directed into the A side living room window and front doorway.
+The fire fighting crew then completed suppression and overhauled the porch area to complete mop-up procedures.
+
+\subsection{Test 2: Bedroom Fire}
+
+The fire was ignited in a rear bedroom near the C/D corner of the structure on a modern-style sofa.
+The C side window to the bedroom was half open.
+The C side window in the adjoining room also had a window in the half open position.
+The living room used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The fire was allowed to grow uninhibited and reach the vent-limited stage.
+The fire then self-vented a portion of the bedroom window on the D side.
+Once the temperatures leveled off in the fire room, the fire fighting crew ventilated the remaining portion of the window in the adjoining room, also on the D side of the structure.
+As the fire continued to grow, the fire fighting crew ventilated the remaining portion of the bedroom window in the room of origin.
+The fire room reached flashover conditions.
+The fire fighting crew then applied water into the room of origin via a single hose-line with a narrow fog pattern until the fire was completely suppressed.
+
+\section{218 Folsom Street}
+
+The third test house was a single story, single family residential structure of type 5 construction addressed as 218 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Bedroom fire with exterior attack.
+
+\subsection{Test 1: Bedroom Fire}
+
+The fire was ignited in a rear bedroom near the C/D corner of the structure on a modern-style mattress with foam padding atop.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The fire grew uninhibited until reaching the vent-limited stage.
+The officer of the fire fighting crew completed a 360 degree size-up of the structure to assess conditions.
+Shortly thereafter, the fire fighting crew ventilated the bedroom window on the D side of the building.
+The fire was allowed to stabilize given the new ventilation opening.
+The fire fighting crew then made an attack on the fire by flowing a single hand-line with a smooth bore nozzle into the room of origin through the D side window from the exterior.
+
+\subsection{Test 2: Bedroom Fire}
+
+Ignition occurred in a rear bedroom near the B/C corner of the structure on a modern-style couch.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The bedroom used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The fire grew uninhibited until reaching the vent-limited stage.
+The officer of the fire fighting crew completed a 360 degree size-up and then the fire fighting crew ventilated the target room window on the B side of the building.
+This was the window to the adjoining room in the structure located near the A/B corner.
+The fire was allowed to stabilize given the new ventilation opening.
+The fire fighting crew then ventilated the bedroom window to the room of origin on the B side next.
+This was followed up by the fire fighting crew making an attack on the fire by flowing a single hand-line with a smooth bore nozzle into the room of origin through the B side window from the exterior.
+
+\section{219 Folsom Street}
+
+The third test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living Room fire with exterior attack.
+
+\subsection{Test 1: Bedroom Fire}
+
+Ignition occurred in a rear bedroom near the B/C corner of the structure on a modern-style mattress with foam padding.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The fire grew uninhibited until reaching the vent-limited stage.
+The front door to the structure was then opened by the fire fighting crew to simulate a crew making entry or a homeowner leaving the door open upon evacuation.
+The fire continued to grow uninhibited until the fire room reached flashover conditions.
+The fire fighting crew then ventilated the bedroom window on the B side of the structure in the room of origin.
+The fire was then allowed to stabilize given the new ventilation opening.
+An unmanned monitor nozzle connected to a single hose-line was placed inside the structure at the entry to the fire room.
+This was remotely activated to simulate a fire fighting crew making an interior attack on the seat of the fire.
+The water was flowed until the fire was suppressed.
+The fire fighting crew then completed the test by making entry to the structure to complete overhaul and mop-up procedures.
+
+\subsection{Test 2: Living Room Fire}
+
+The fire was ignited in the front living room located near the A/D corner of the structure on a modern-style sofa.
+The bedroom used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The window to the living room on the D side of the structure was half-opened at the start of the test.
+The fire grew uninhibited until reaching the ventilation-limited stage.
+The window on the D side in the adjacent room near the C/D corner of the structure was ventilated next.
+The upper portion of the A side living room window self-ventilated due to the fire.
+Shortly thereafter, the fire fighting crew ventilated the remaining portion of the D side living room window.
+Once the fire had self-ventilated the remaining portion of the A side living room window, it was allowed to stabilize.
+The fire fighting crew then conducted an exterior attack via the D side living room window with a single hose-line with a smooth bore nozzle.
+
+\section{225 Folsom Street}
+
+ The third test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Bedroom fire with exterior attack.
+
 \end{document}

### 2014-09-11 Projects/Spartanburg_2013/Spartanburg_2013.tex
Spartanburg 2013: Test Descriptions Cont

@@
 The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
-Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Bedroom fire with exterior attack.
+One test was conducted in this structure comparing a legacy versus modern sofa with an exterior fire attack.
+
+ \subsection{Test 1: Legacy versus Modern Sofa}
+
+  Ignition points were located in two different rooms within the home.
+A legacy-style sofa was ignited in a rear bedroom of the structure near the C/D corner and a modern-style sofa was ignited in a front living room near the A/B corner approximately 6 minutes after the first ignition.
+The front door to the structure remained open during the test.
+Additionally, the D side window to the rear bedroom with the legacy-style sofa also remained open.
+The fires were allowed to grow uninhibited.
+The fires within the home became ventilation limited.
+The living room window on the B side of the structure self-vented, followed by the living room window on the A side of the structure.
+Once the fire grew in size and began burning the porch area, an exterior attack via a single hose-line with smooth bore nozzle was made through the front door and A side living room window.
 

### 2014-09-15 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add reference to Chicago report; edits to bibliography file

@@
 Part of the function of the Fire Research Division at the National Institute of Standars and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
 The objective of these studies has been to improve the safety and effectiveness of firefighters.

### 2014-09-18 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: add images, update plotting script, update output files, update report

@@
 \usepackage{xfrac}
-
+\pgfplotsset{compat=1.10}
 \begin{document}
@@
 \end{enumerate}
+
 This document describes the input and the results of the FDS (version 6.1.1) simulations.
@@
 From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+Table~\ref{tab:fire_info} represents the best estimate of the events and therefore all times should be considered as approximate.
+
 \begin{table}[!h]
@@
 
+The fire, which is described in Section~\ref{fire}, started in the basement and spread to the stairs which connect to the first floor.
+Discussion of the fire’s impact on the interior conditions is provided in Section~\ref{results}.
+Figure~\ref{fig:exterior} shows the exterior of the front and rear of the structure after the incident.
+Note that the majority of the damage occurred in the basement of the structure.
+Fully dimensioned drawings of the interior of the basement and first floor are shown in Figs.~\ref{fig:basement} and \ref{fig:first_floor}, respectively.
+
 \begin{figure}[!ht]
@@
 \label{fig:simp_geom}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+\includegraphics[width=5in]{../Figures/PGCo_Front} \\ 
+\includegraphics[width=5in]{../Figures/PGCo_Rear}
+\end{tabular*}
+\caption{Photographs showing the front (top) and rear (bottom) exterior of the structure after the incident.}
+\label{fig:exterior}
 \end{figure}
@@
 \caption[Dimensioned drawing of first floor.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:first_floor}
+\label{fig:basement}
 \end{figure}
@@
 \caption[Dimensioned drawing of second floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:second_floor}
+\label{fig:first_floor}
 \end{figure}

### 2014-09-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to Fire/HRR section

@@
 
-The fire, which is described in Section~\ref{sec:fire}, originated in the finished living room on the basement level (near the rear side of the structure), which had a floor area of 72~m$^2$ (775~ft$^2$).
+The fire, which is described in Section~\ref{sec:fires}, originated in the finished living room on the basement level (near the rear side of the structure), which had a floor area of 72~m$^2$ (775~ft$^2$).
 More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:model_results}.
@@
 
-\section{Fire}
-\label{sec:fire}
+\section{Fires}
+\label{sec:fires}
 
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these sources of information, the FDS model includes two source fires: an initial couch fire in the basement near the rear side of the structure, and a secondary flashover fire that involved the entire basement floor area.
-The basement primarily contained upholstered polyurethane furniture fuel items.
+Based on these sources of information, the FDS model includes three source fires: an initial couch fire in the basement, a secondary flashover fire that involved additional furniture items in the basement, and a third fire that occurred on the exterior basement balcony.
+The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood.
 The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
-
-Polyurethane fuel can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The primary fuel packages were located in the basement as shown in Fig.~\ref{fig:fuel_placement}.
+In this figure, the numbered labels indicate the order in which the fuel items were burning: 1) the initial couch fire, 2) the secondary furniture fuel items, and 3) the balcony fire.
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Plan_Basement_Fuels}
+\caption[Location of fuel items in the basement.]
+{Location of fuel items in the basement. The numbered labels indicate the order in which the fuel items were burning.}
+\label{fig:fuel_placement}
+\end{figure}
+
+Polyurethane fuel was specified for the interior basement fuel items, which can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
 The product yields are expressed in terms of the amount soot or carbon monoxide emitted per unit mass of fuel consumed~(kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
@@
 \rightarrow 6.06(0.129\,\C\O_{2} + 0.156\,\H_{2}\O + 0.001\,\C\O + 0.035\,\C + 0.679\,\N_{2})
-\label{eq:fuel_comb}
+\label{eq:fuel_polyurethane}
 \end{multline}
 
-The value for the heat of combustion of polyurethane used in this simulation was~26,200 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
-The heat of combustion quantifies the amount of energy per unit mass of the fuel.
-The following text defines Eq.~\ref{eq:fuel_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
-
-\begin{lstlisting}
-&SPEC ID='POLYURETHANE', FORMULA='CH1.8O0.30N0.05' /
+\clearpage
+
+Wood fuel was specified for the exterior basement balcony fuel items, which can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified product yields of soot ($y_{\mathrm{s}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+A balanced chemical reaction for wood combustion can be written as:
+
+\begin{multline}
+\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.91(0.208\,\O_{2} + 0.783\,\N_{2} + 8.34 \times 10^{-3}\,\H_{2}\O + 3.87 \times 10^{-4}\,\C\O_{2}) \\
+\rightarrow 5.74(0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 6.37 \times 10^{-4}\,\C\O + 5.57 \times 10^{-3}\,\C + 0.670\,\N_{2})
+\label{eq:fuel_wood}
+\end{multline}
+
+The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The heat of combustion quantifies the amount of energy released per unit mass of the fuel.
+The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the desired fuel and reaction properties discussed above:
+
+\begin{lstlisting}[basicstyle=\ttfamily\scriptsize]
+&SPEC ID = 'POLYURETHANE',    FORMULA = 'CH1.8O0.30N0.05' /
+&SPEC ID = 'WOOD',            FORMULA = 'CH1.7O0.74N0.002' /
+&SPEC ID = 'OXYGEN',          LUMPED_COMPONENT_ONLY = .TRUE. /
+&SPEC ID = 'NITROGEN',        LUMPED_COMPONENT_ONLY = .TRUE. /
+&SPEC ID = 'WATER VAPOR',     LUMPED_COMPONENT_ONLY = .TRUE. /
+&SPEC ID = 'CARBON MONOXIDE', LUMPED_COMPONENT_ONLY = .TRUE. /
+&SPEC ID = 'CARBON DIOXIDE',  LUMPED_COMPONENT_ONLY = .TRUE. /
+&SPEC ID = 'SOOT',            LUMPED_COMPONENT_ONLY = .TRUE. /
+
+&SPEC ID = 'AIR',
+    SPEC_ID = 'OXYGEN','NITROGEN','WATER VAPOR','CARBON DIOXIDE',
+    VOLUME_FRACTION = 0.208057, 0.783214, 0.008342, 0.000387,
+    BACKGROUND = .TRUE. /
+
+&SPEC ID = 'PRODUCTS_POLYURETHANE',
+    SPEC_ID = 'NITROGEN','WATER VAPOR','CARBON DIOXIDE','CARBON MONOXIDE','SOOT',
+    VOLUME_FRACTION = 0.678838, 0.155754, 0.129475, 0.001139, 0.034794 /
 
@@
     HEAT_OF_COMBUSTION = 26200,
-    SOOT_YIELD = 0.131,
-    CO_YIELD = 0.010 /
+    SPEC_ID_NU = 'POLYURETHANE','AIR','PRODUCTS_POLYURETHANE'
+    NU = -1, -5.218633, 6.057861 /
+
+&SPEC ID = 'PRODUCTS_WOOD',
+    SPEC_ID = 'NITROGEN','WATER VAPOR','CARBON DIOXIDE','CARBON MONOXIDE','SOOT',
+    VOLUME_FRACTION = 0.670128, 0.155268, 0.168397, 0.000637, 0.005570 /
+
+&REAC ID = 'WOOD'
+    FUEL = 'WOOD',
+    HEAT_OF_COMBUSTION = 16400,
+    SPEC_ID_NU = 'WOOD','AIR','PRODUCTS_WOOD'
+    NU = -1, -4.908330, 5.738119 /
 \end{lstlisting}
@@
 Note that using the input lines above will invoke the simple chemistry reaction mechanism in FDS in which fuel and air react to form only CO$_2$, CO, H$_2$O, soot, and N$_2$.
-If the inclusion for other combustion products is desired, then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
+If the inclusion of other combustion products is desired, then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
 Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
@@
 
-The HRR was prescribed in FDS as follows.
-From 0~s to 300~s, the HRR in the simulation followed the experimentally measured mattress HRR.
+\noindent The HRR for the various fuel packages was prescribed in FDS as follows.
+
+\begin{enumerate}
+\item For the inital couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR.
 At 300~s, the HRR was approximately 3~MW.
-From 300~s to 342~s (the time at which the first basement window failed), the HRR increased linearly from 3~MW to 20~MW.
-From 342~s to 540~s, the HRR was 15~MW.
+From 327~s until 540~s (the end of the simulation), the HRR was a constant 5~MW.
+
+\item The secondary fuel packages in the basement were divided among four additional furniture items (two sofas, a lounge, and a chair).
+The two large sofas in the middle of the basement were specified with a peak HRR of 5~MW.
+The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW.
+From 0~s to 300~s, these items were not burning.
+From 300~s to 342~s (the time at which the first basement window failed), the secondary fuel items were ignited, and the total HRR of the secondary fuel packages increased linearly from 0~MW to 14~MW.
+From 342~s to 540~s (the end of the simulation), the HRR was a constant 14~MW.
+
+\item The third exterior fuel item included the wood on the basement balcony and siding.
+From 0~s to 440~s, these items were not burning.
+From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW.
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
+\end{enumerate}
+
+Figure~\ref{fig:hrr} shows the prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
+In this figure, the vertical lines indicate the three stages of the fire based on the contribution of the fuel packages.
+Therefore, the estimated maximum specified fire size for this structure was approximately 20~MW.
 Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
@@
 
-% To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
-The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
-
-% To calculate the total fire size, the appropriate burning area (exposed wood area) of the attic and second floor porch enclosure needs to be determined.
-Based on the floor plan of the structure, the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
-Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
-Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
-That area was considered to be part of the porch fire.
-Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
-To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
-Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
-To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
-Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
-Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
-Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
-The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
-The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
-The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/Fire_HRR}
+\caption[Prescribed HRR vs. time.]
+{Prescribed HRR vs. time. The vertical lines indicate the three stages of the fire based on the contribution of the fuel packages.}
+\label{fig:hrr}
+\end{figure}
+
+\clearpage
+
+Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made.
+The first assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
+The second assumption is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basment balcony for the wood fuel).
 The following lines define the source fires in the FDS input file:
@@
 \begin{lstlisting}
-&SURF ID='BURNER', HRRPUA=0.25, COLOR='RED', RAMP_Q='Mattress_Ramp' /
-&VENT XB=4.2, 6.2, 15.2, 17.2, -2.8, -2.8, SURF_ID='BURNER', DEVC_ID='TIMER_INITIAL_BURNER_OFF' /
-&DEVC ID='TIMER_INITIAL_BURNER_OFF', QUANTITY='TIME', XYZ=0,0,0, INITIAL_STATE=.TRUE., SETPOINT=300 /
-
-&SURF ID='FLASHOVER_BURNER', HRRPUA=0.018255, COLOR='RED', RAMP_Q='Flashover_Ramp' /
-&VENT XB=0.1, 8.4, 8.5, 15.1, -2.8, -2.8, SURF_ID='FLASHOVER_BURNER' /
+&SURF ID='COUCH_RIGHT_INITIAL',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
+
+&SURF ID='COUCH_MIDDLE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 1.037172E-5,
+    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
+
+&SURF ID='COUCH_LEFT_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
+
+&SURF ID='LOUNGE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.853485E-6,
+    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
+
+&SURF ID='CHAIR_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.918660E-6,
+    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
+
+&SURF ID='WOOD_EXTERIOR',
+    SPEC_ID='WOOD',
+    MASS_FLUX = 0.003049,
+    RAMP_MF='WOOD_EXTERIOR_RAMP' /
 \end{lstlisting}
-Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
+Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
+The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
+
+\clearpage
 
@@
 
-While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
-In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure.
+While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
 The following lines define the gypsum material in the FDS input file:
@@
 \begin{lstlisting}
-&MATL ID = 'GYPSUM BOARD'
+&MATL ID          = 'GYPSUM'
     FYI = 'Wakili - Journal of Fire Sciences 2007' 
     CONDUCTIVITY  = 0.28
-    SPECIFIC_HEAT = 1.0
+    SPECIFIC_HEAT = 1.00
     DENSITY       = 810. /
+
+&SURF ID        = 'WALL'
+      DEFAULT   = .TRUE.
+      COLOR     = 'DARK SEA GREEN 4'
+      MATL_ID   = 'GYPSUM'
+      THICKNESS = 0.012 /
 \end{lstlisting}
@@
 Ambient Temperature$^*$                   &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
-Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fire}            \\
+Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                           &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
@@
                                           &  Heat of combustion: 26,200~kJ/kg             &                                    \\
-Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fire}            \\
+Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fires}           \\
                                           &  Basement flashover fire: 15~MW               &                                    \\
@@
 
-Figure~\ref{fig:hrr} shows the prescribed HRR vs.
+Figure~\ref{fig:hrr_w_fds} shows the prescribed HRR vs.
 time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
@@
 \begin{figure}[!ht]
-\includegraphics[width=5.5in]{../Figures/Fire_HRR}
+\includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
 \caption[HRR vs. time from the FDS simulations.]
 {HRR vs. time from the FDS simulations. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
-\label{fig:hrr}
+\label{fig:hrr_w_fds}
 \end{figure}

### 2014-09-22 Studies/2011_San_Francisco/Figures/generate_figures.py

@@ -25,9 +25,29 @@ HRR_CALC = CALC['Total HRR (kW)'] / 1000
 
 figure()
 plot(CALC['Time (s)'], HRR_CALC, 'k-', lw=2, label='Prescribed HRR')
+plt.text(98, 2.5, 'Initial couch fire')
+plt.text(320, 2.5, 'Secondary fuels')
+plt.text(455, 2.5, 'Wood patio')
+axvline(300, color='k', ls='--', lw=2)
+axvline(440, color='k', ls='--', lw=2)
+xlim([0, 540])
+ylim([0, 25])
+xlabel('Time(s)', fontsize=20)
+ylabel('HRR (MW)', fontsize=20)
+grid(True)
+ax = gca()
+for xlabel_i in ax.get_xticklabels():
+    xlabel_i.set_fontsize(16)
+for ylabel_i in ax.get_yticklabels():
+    ylabel_i.set_fontsize(16)
+savefig('Fire_HRR.pdf')
+
+figure()
+plot(CALC['Time (s)'], HRR_CALC, 'k-', lw=2, label='Prescribed HRR')
 plot(FDS['Time'][:-4], HRR_FDS_avg[:-4], 'r--', lw=2, label='FDS Model HRR')
 plt.text(342+10, 2, 'Rear Window Failures Begin')
 axvline(342, color='k', ls='--', lw=2)
+xlim([0, 540])
 ylim([0, 35])
 xlabel('Time(s)', fontsize=20)
 ylabel('HRR (MW)', fontsize=20)
@@ -38,4 +58,4 @@ for xlabel_i in ax.get_xticklabels():
     xlabel_i.set_fontsize(16)
 for ylabel_i in ax.get_yticklabels():
     ylabel_i.set_fontsize(16)
-savefig('Fire_HRR.pdf')
+savefig('Fire_HRR_w_FDS.pdf')

### 2014-09-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to report

@@
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
-The following lines define the gypsum material in the FDS input file:
+The following lines define the gypsum material and surface in the FDS input file:
 
@@
 Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
-The domain was divided into 16 meshes (each containing between 289,000 and 346,800 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
-Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 \end{figure}
+
+The domain was divided into 16 meshes (each containing between 272,000 and 367,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
+Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
+Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 Ambient Temperature$^*$                      &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
-Reaction: Wood~\cite{SFPE:Tewarson}       &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
+Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                              &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
@@
                                              &  Heat of combustion: 26,200~kJ/kg             &                                    \\
-Peak HRR                                  &  Initial couch fire: 5.4~MW                   &  Section~\ref{sec:fires}           \\
-                                          &  Basement flashover fire: 15~MW               &                                    \\
+Reaction: Wood~\cite{SFPE:Tewarson}          &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     &  Section~\ref{sec:fires}           \\
+                                             &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
+                                             &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                    \\
+                                             &  Heat of combustion: 16,400~kJ/kg             &                                    \\
+Peak HRRs                                    &  Initial couch fire: 5~MW                     &  Section~\ref{sec:fires}           \\
+                                             &  Basement flashover fire: 14~MW               &                                    \\
+                                             &  Basement balcony fire: 1~MW                  &                                    \\
 Material: Gypsum Board~\cite{WAKILI2007}     &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
@@
 \footnotesize
-\\ $^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
+\\ $^{*}$Initial interior temperature was assumed to be 20~$^{\circ}$C; actual exterior temperature was 14~$^{\circ}$C~\cite{NIOSH:Bowyer2}.
 \normalsize

### 2014-09-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to report

@@
 The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
-The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or videos: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
+The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
 
@@
 
-To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
+To estimate the type of fuel, fire size, and structure ventilation, on-scene photographs and post-incident reports were used.
 Based on these sources of information, the FDS model includes three source fires: an initial couch fire in the basement, a secondary flashover fire that involved additional furniture items in the basement, and a third fire that occurred on the exterior basement balcony.
@@
 Figure~\ref{fig:hrr} shows the prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
-In this figure, the vertical lines indicate the three stages of the fire based on the contribution of the fuel packages.
+In this figure, the text labels indicate the three stages of the fire based on the contribution of the fuel packages.
 Therefore, the estimated maximum specified fire size for this structure was approximately 20~MW.
@@
 \caption[Prescribed HRR vs. time.]
-{Prescribed HRR vs. time. The vertical lines indicate the three stages of the fire based on the contribution of the fuel packages.}
+{Prescribed HRR vs. time. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
 \label{fig:hrr}
@@
 The ventilation times and ventilation areas represent our best understanding of the incident.
-The times of the ventilation changes of exterior doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
-
-During the time at which the downed firefighters were located, the state of the windows and doors in the structure was known, which resulted in the establishment of a flow path in the interior stairwell leading into the basement.
-However, the exact time of operation for some doors was not known.
-Therefore, these doors were assumed to be open at the start of the simulation, which included 1) the front door, 2) the interior door leading from the hallway on the first floor into the stairwell towards the basement, 3) the door leading from the first floor landing into the garage, and 4) the overhead garage door.
+The times of ventilation changes for doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
+
+During the time at which the downed firefighters were located, the state of some windows and doors in the structure was known, which resulted in the establishment of a flow path in the interior stairwell leading into the basement.
+However, the exact time of operation for other doors was not known.
+Therefore, the following doors were assumed to be open at the start of the simulation: 1) the front door, 2) the interior door leading from the hallway on the first floor into the stairwell towards the basement, 3) the door leading from the garage into the first floor landing, and 4) the overhead garage door.
+The basement windows and exterior door were specified to open at certain times based on observations of failure (i.e., window breakage) or fire department operations (i.e., forcible entry) from on-scene photographs and post-incident reports.
 

### 2014-09-23 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to numerical mesh section

@@
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 18.8 for the initial couch fire (peak HRR of 5.4~MW) and 28.3 for the basement flashover fire (HRR of 15~MW).
 Based on validation work performed for the U.S.
 Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
-The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the ratio of the characteristic fire diameter to cell size ($D^*/\dx$) was 18 for the initial couch fire (combined HRR of 5~MW), 31 for the secondary flashover fire in the basement (combined HRR of 19~MW), and 32 for the maximum prescribed fire size in the structure (combined HRR of 20~MW).
+Therefore, the grid resolution used in this model results in a $D^*/\dx$ ratio that exceeds typical engineering values.
 
@@
 \includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Front} \\
-\includegraphics[width=5.0in]{../Figures/SMV_Exterior_Grid_Rear}
+\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
 \caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
@@
 \end{figure}
+
+\clearpage
 

### 2014-09-23 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to results section; add SMV and on-scene photos

@@
                &  basement fails. Additional glass windows on the rear side of the structure fail     \\
-               &  over the next two minutes.                                                          \\
+               &  within the next two minutes.                                                        \\
                &                                                                                      \\
@@
                &              &  window in the basement fails. Additional glass windows on the       \\
-               &              &  rear side of the structure fail over the next two minutes.          \\
+               &              &  rear side of the structure fail within the next two minutes.        \\
                &              &                                                                      \\
@@
 
-The HRR output quantity from FDS represents the predicted amount of combustion that would have occurred in the fire scenario, which depends on the amount of available fuel, oxygen, and ventilation.
 In the FDS simulations, a prescribed HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
-As a result, the actual HRR in FDS can be lower than the specified HRR based on the ventilation conditions.
-
-Figure~\ref{fig:hrr_w_fds} shows the prescribed HRR vs.
-time based on the specified fires along with the FDS results for the two ventilation scenarios that were described in Section~\ref{sec:ventilation}.
-The vertical line represents the time at which the first basement window on the rear side of the structure failed (342~s).
+As a result, the actual HRR in FDS can be different than the prescribed HRR based on the ventilation conditions.
+
+Figure~\ref{fig:hrr_w_fds} shows the HRR vs.
+time based on the fires that were described in Section~\ref{sec:fires}.
+The vertical dashed line represents the time at which the first basement window on the rear side of the structure failed (342~s).
 The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with the timeline observations from the fire scenario.
-Note that the rear window failures were driven by the event timeline rather than failure temperature criteria.
+Note that the rear window failures were manually specified in accordance with the event timeline rather than failure temperature criteria.
 
@@
 
-In Fig.~\ref{fig:hrr}, the XX line represents the FDS simulation.
-The XX line represents the prescribed HRR that was input into FDS.
-As shown in Fig.~\ref{fig:hrr}, the HRR output from FDS is less than the prescribed HRR because the fire in the structure becomes ventilation limited.
-The maximum HRR value is approximately XX~MW before the fire becomes ventilation limited and begins to decay.
-The HRR is reduced to XX~MW as the amount of oxygen inside the structure becomes limited.
-There is an insufficient amount of oxygen in the structure to burn all of the fuel, therefore combustion occurs locally at the ventilation openings where fresh air is available.
-Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at XX~s.
-After additional window failures occur at XX~s and XX~s (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to XX~MW before it decreases to approximately XX~MW.
-The HRR then increases towards a steady-state value.
-
-% Figure~\ref{fig:hrr} indicates that the HRRs for both of the ventilation scenarios in FDS are identical until 130~s (HRR $\approx$ 7~MW).
-At 130~s, the rear door is opened in the baseline simulation.
-At 135~s, there is an additional breach on the left side of the structure (Table~\ref{tab:ventilation_timeline}).
-The open door and breach act as additional pressure releases for the structure.
-Again, the abrupt change in ventilation causes the HRR to increase from approximately 7~MW to 9.7~MW at 139~s.
-At the time of the door failure (160~s), the HRR in both cases was approximately 9~MW because of the increased amount of ventilation.
-While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, the interior conditions in both cases presented a significant hazard to firefighters inside of the structure.
-Therefore, the analysis will focus on the results of the baseline simulation.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/smv_exterior_fire}
-% \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
-% \label{fig:smv_ext_fire}
-% \end{figure}
+\clearpage
+
+In Fig.~\ref{fig:hrr_w_fds}, the solid line represents the HRR that was prescribed in the FDS simulation, and the dashed line represents the actual HRR that was predicted by FDS based on the ventilation conditions.
+From 0~s to 300~s, the predicted HRR is in agreement with the prescribed HRR because there is an adequate amount of oxygen for all of the fuel to combust.
+From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR is lower than the prescribed HRR because the fire in the structure becomes ventilation limited.
+The maximum predicted HRR value is approximately 7~MW before the fire becomes ventilation limited and begins to decay.
+The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure becomes limited.
+At this time, there is an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurs near the ventilation openings where ambient air is available.
+
+At a time of 342~s, the first window on the rear side of the structure fails, and additional windows fail within the next two minutes.
+As additional window failures occur (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to approximately 32~MW before it reaches a steady-state value of approximately 20~MW.
+The predicted HRR increases above the prescribed HRR value because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions is now mixing with ambient air from the failed window openings and burning.
+Figure~\ref{fig:timeline_comparison} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurs through the failed windows on the rear side of the structure.
+
+\begin{figure}[!ht]
+\includegraphics[height=8.25in]{../Figures/Timeline_Comparison}
+\caption{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.}
+\label{fig:timeline_comparison}
+\end{figure}
+
+\clearpage
 

### 2014-09-23 Studies/2012_Chicago/Report/Chicago_Fire.tex
San Francisco: Minor formatting edits
Chicago Fire: update to report to fit NIST TN style

@@
 
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\lhead{}
+\rhead{}
+\chead{This publication is available free of charge from:
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}}
+\renewcommand{\headrulewidth}{0pt}
+
 \begin{document}
+\pagenumbering{gobble}
 
 \bibliographystyle{unsrt}
-\pagestyle{empty}
+%\pagestyle{empty}
 
@@
 
-\pagenumbering{roman}
-
 \begin{minipage}[t][9in][s]{6.25in}
+\pagenumbering{gobble}
 
@@
 \begingroup
+This publication is available free of charge from:
 \hypersetup{urlcolor=black}
@@
 \begin{minipage}[t][9in][s]{6.25in}
+\pagenumbering{gobble}
 
@@
 
-\pagestyle{plain}
+%\pagestyle{plain}
 \pagenumbering{roman}
+\setcounter{page}{3}
 
@@
 \chapter*{\centering Abstract}
+\pagenumbering{gobble}
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2~\sfrac{1}{2}~story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
@@
 \chapter{Introduction}
+\pagenumbering{arabic}
+\setcounter{page}{1}
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
@@
 \footnotesize
-$^{*}$ Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
 \normalsize

### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix page numbering and front matter format; other minor edits

@@
 
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\lhead{}
+\rhead{}
+\chead{}
+\renewcommand{\headrulewidth}{0pt}
+
 \begin{document}
+\pagenumbering{gobble}
 
 \bibliographystyle{unsrt}
-\pagestyle{empty}
 
@@
 \hypersetup{urlcolor=black}
+This publication is available free of charge from:
 \href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
@@
 
-\pagestyle{plain}
 \pagenumbering{roman}
+\setcounter{page}{3}
 
@@
 BC \> Battalion Chief \\
-DC \> Division Chief \\
 E \> Engine \\
@@
 LODD \> Line of Duty Death \\
-M \> Medic \\
 NIOSH \> National Institute for Occupational Safety and Health \\
 NIST \> National Institute of Standards and Technology \\
-RIC \> Rapid Intervention Crew \\
-RS \> Rescue Squad \\
 SFPE \> Society of Fire Protection Engineers \\
-T \> Tower \\
 \end{tabbing}
@@
 \chapter*{\centering Abstract}
+\pagenumbering{gobble}
 
@@
 \label{sec:introduction}
+\pagenumbering{arabic}
+\setcounter{page}{1}
 
@@
 
-While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage in the ceiling, walls, and floor.
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
-The following lines define the gypsum material and surface in the FDS input file:
+The following lines define the gypsum material and surface properties in the FDS input file:
 
@@
                                              &  Basement balcony fire: 1~MW                  &                                    \\
-Material: Gypsum Board~\cite{WAKILI2007}     &  $k$: 0.28~\si{W/(m.K)}                       &  Section~\ref{sec:materials}       \\
-                                             &  $\rho$: 810~kg/m$^3$                         &                                    \\
-                                             &  $c_{\rm p}$: 1.0~\si{kJ/(kg.K)}              &                                    \\
+Material: Gypsum Board~\cite{WAKILI2007}     &  Thermal conductivity: 0.28~\si{W/(m.K)}      &  Section~\ref{sec:materials}       \\
+                                             &  Density: 810~kg/m$^3$                        &                                    \\
+                                             &  Specific heat: 1.0~\si{kJ/(kg.K)}            &                                    \\
+                                             &  Thickness: 1.2~\si{cm}                       &                                    \\
 \bottomrule

### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to fire and HRR section

@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene photographs and post-incident reports were used.
-Based on these sources of information, the FDS model includes three source fires: an initial couch fire in the basement, a secondary flashover fire that involved additional furniture items in the basement, and a third fire that occurred on the exterior basement balcony.
+Based on these sources of information, the FDS model includes three source fires: 1) an initial couch fire in the basement, 2) a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the exterior basement balcony.
 The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood.
 The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
+
 The primary fuel packages were located in the basement as shown in Fig.~\ref{fig:fuel_placement}.
@@
 \end{figure}
+
+\clearpage
+
+Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made.
+One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
+The beginning of the simulation ($t=0$) was selected to correspond to an on-scene time of 10:53:00 (see Table~\ref{tab:incident_timeline}).
+The HRRs for the three primary source fires was prescribed in FDS as follows.
+
+\begin{enumerate}
+\item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR.
+At 300~s, the HRR was approximately 3~MW.
+From 327~s until 540~s (the end of the simulation), the HRR was a constant 5~MW.
+
+\item The secondary fuel packages in the basement were divided among four additional furniture items (two sofas, a lounge, and a chair).
+The two large sofas in the middle of the basement were specified with a peak HRR of 5~MW.
+The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW.
+From 0~s to 300~s, these items were not burning.
+From 300~s to 342~s (the time at which the first basement window failed), the secondary fuel items were ignited, and the total HRR of the secondary fuel packages increased linearly from 0~MW to 14~MW.
+From 342~s to 540~s (the end of the simulation), the HRR was a constant 14~MW.
+
+\item The third exterior fuel item included the wood on the basement balcony and siding.
+From 0~s to 440~s, these items were not burning.
+From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW.
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
+\end{enumerate}
+
+Figure~\ref{fig:hrr} shows the prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
+In this figure, the text labels indicate the three stages of the fire based on the contribution of the fuel packages.
+Therefore, the estimated maximum specified fire size for this structure was approximately 20~MW.
+Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
+A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{sec:HRR}.
+
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/Fire_HRR}
+\caption[Prescribed HRR vs. time.]
+{Prescribed HRR vs. time. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
+\label{fig:hrr}
+\end{figure}
+
+\clearpage
+
+Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel).
+The following lines define the source fires in the FDS input file:
+
+\begin{lstlisting}
+&SURF ID='COUCH_RIGHT_INITIAL',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
+
+&SURF ID='COUCH_MIDDLE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 1.037172E-5,
+    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
+
+&SURF ID='COUCH_LEFT_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
+
+&SURF ID='LOUNGE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.853485E-6,
+    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
+
+&SURF ID='CHAIR_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.918660E-6,
+    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
+
+&SURF ID='WOOD_EXTERIOR',
+    SPEC_ID='WOOD',
+    MASS_FLUX = 0.003049,
+    RAMP_MF='WOOD_EXTERIOR_RAMP' /
+\end{lstlisting}
+
+Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
+The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
 
@@
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
-
-\noindent The HRR for the various fuel packages was prescribed in FDS as follows.
-
-\begin{enumerate}
-\item For the inital couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR.
-At 300~s, the HRR was approximately 3~MW.
-From 327~s until 540~s (the end of the simulation), the HRR was a constant 5~MW.
-
-\item The secondary fuel packages in the basement were divided among four additional furniture items (two sofas, a lounge, and a chair).
-The two large sofas in the middle of the basement were specified with a peak HRR of 5~MW.
-The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW.
-From 0~s to 300~s, these items were not burning.
-From 300~s to 342~s (the time at which the first basement window failed), the secondary fuel items were ignited, and the total HRR of the secondary fuel packages increased linearly from 0~MW to 14~MW.
-From 342~s to 540~s (the end of the simulation), the HRR was a constant 14~MW.
-
-\item The third exterior fuel item included the wood on the basement balcony and siding.
-From 0~s to 440~s, these items were not burning.
-From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW.
-To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
-The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
-\end{enumerate}
-
-Figure~\ref{fig:hrr} shows the prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
-In this figure, the text labels indicate the three stages of the fire based on the contribution of the fuel packages.
-Therefore, the estimated maximum specified fire size for this structure was approximately 20~MW.
-Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
-A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{sec:HRR}.
-
-\begin{figure}[!ht]
-\includegraphics[width=5.5in]{../Figures/Fire_HRR}
-\caption[Prescribed HRR vs. time.]
-{Prescribed HRR vs. time. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
-\label{fig:hrr}
-\end{figure}
-
-\clearpage
-
-Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made.
-The first assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
-The second assumption is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basment balcony for the wood fuel).
-The following lines define the source fires in the FDS input file:
-
-\begin{lstlisting}
-&SURF ID='COUCH_RIGHT_INITIAL',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
-
-&SURF ID='COUCH_MIDDLE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 1.037172E-5,
-    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
-
-&SURF ID='COUCH_LEFT_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
-
-&SURF ID='LOUNGE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.853485E-6,
-    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
-
-&SURF ID='CHAIR_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.918660E-6,
-    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
-
-&SURF ID='WOOD_EXTERIOR',
-    SPEC_ID='WOOD',
-    MASS_FLUX = 0.003049,
-    RAMP_MF='WOOD_EXTERIOR_RAMP' /
-\end{lstlisting}
-Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
-The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
 
@@
 
-In the FDS simulations, a prescribed HRR is specified, and FDS determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
+In an FDS simulation, a prescribed HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
+FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
 As a result, the actual HRR in FDS can be different than the prescribed HRR based on the ventilation conditions.
@@
 The vertical dashed line represents the time at which the first basement window on the rear side of the structure failed (342~s).
-The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with the timeline observations from the fire scenario.
+Additional windows on the rear side of the basement continued to fail within the next two minutes.
+The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with observations from the actual fire scenario.
 Note that the rear window failures were manually specified in accordance with the event timeline rather than failure temperature criteria.
@@
 In Fig.~\ref{fig:hrr_w_fds}, the solid line represents the HRR that was prescribed in the FDS simulation, and the dashed line represents the actual HRR that was predicted by FDS based on the ventilation conditions.
-From 0~s to 300~s, the predicted HRR is in agreement with the prescribed HRR because there is an adequate amount of oxygen for all of the fuel to combust.
-From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR is lower than the prescribed HRR because the fire in the structure becomes ventilation limited.
-The maximum predicted HRR value is approximately 7~MW before the fire becomes ventilation limited and begins to decay.
-The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure becomes limited.
-At this time, there is an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurs near the ventilation openings where ambient air is available.
-
-At a time of 342~s, the first window on the rear side of the structure fails, and additional windows fail within the next two minutes.
-As additional window failures occur (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation causes the HRR to increase to approximately 32~MW before it reaches a steady-state value of approximately 20~MW.
-The predicted HRR increases above the prescribed HRR value because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions is now mixing with ambient air from the failed window openings and burning.
-Figure~\ref{fig:timeline_comparison} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurs through the failed windows on the rear side of the structure.
+From 0~s to 300~s, the predicted HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
+From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited.
+The maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay.
+The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure became limited.
+At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occured near the ventilation openings where ambient air was available.
+
+At a time of 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes.
+As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW before it reached a steady-state value of approximately 20~MW.
+The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.
+
+Figure~\ref{fig:timeline_comparison} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occured through the failed windows on the rear side of the structure.
+In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed).
 
 \begin{figure}[!ht]
-\includegraphics[height=8.25in]{../Figures/Timeline_Comparison}
-\caption{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.}
+\includegraphics[height=8.0in]{../Figures/Timeline_Comparison}
+\caption{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.
+The on-scene time is indicated on the left photograph, and the corresponding simulation time is indicated on the right Smokeview snapshot.
+For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
 \label{fig:timeline_comparison}

### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: More edits to fire and HRR section

@@
 \caption[Location of fuel items in the basement.]
-{Location of fuel items in the basement. The numbered labels indicate the order in which the fuel items were burning.}
+{Location of fuel items in the basement.
+The numbered labels indicate the order in which the fuel items were burning: Item~1 is associated with the initial couch fire in the basement, Items~2 are associated with the flashover fire that involved additional furniture items in the basement, and Item~3 is associated with a fire that occurred on the exterior basement balcony.}
 \label{fig:fuel_placement}
@@
 \item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR.
-At 300~s, the HRR was approximately 3~MW.
-From 327~s until 540~s (the end of the simulation), the HRR was a constant 5~MW.
-
-\item The secondary fuel packages in the basement were divided among four additional furniture items (two sofas, a lounge, and a chair).
-The two large sofas in the middle of the basement were specified with a peak HRR of 5~MW.
-The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW.
+The HRR at 300~s was approximately 3~MW, and the HRR at 327~s was approximately 5~MW.
+From 327~s until 540~s (the end of the simulation), the HRR of the initial couch item was specified as a constant 5~MW.
+
+\item The secondary fuel packages in the basement were divided among four additional furniture items (two couches, a lounge, and a chair).
+The two large couches in the middle of the basement were specified with a peak HRR of 5~MW for each item.
+The lounge and chair located at the perimeter of the basement were specified with a peak HRR of 2~MW for each item.
+Therefore, the peak HRR of all four furniture items was a total of 14~MW.
+
+Based on post-incident reports and photographs, the HRR of these fuels was specified as follows.
 From 0~s to 300~s, these items were not burning.
-From 300~s to 342~s (the time at which the first basement window failed), the secondary fuel items were ignited, and the total HRR of the secondary fuel packages increased linearly from 0~MW to 14~MW.
-From 342~s to 540~s (the end of the simulation), the HRR was a constant 14~MW.
+From 300~s to 342~s (the time at which the first basement window failed), the secondary fuel items were ignited, and the total HRR of the four furniture items increased linearly from 0~MW to 14~MW.
+From 342~s to 540~s (the end of the simulation), the total HRR of the four furniture items was specified as a constant 14~MW.
 
 \item The third exterior fuel item included the wood on the basement balcony and siding.
-From 0~s to 440~s, these items were not burning.
-From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW.
 To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
 The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
+
+Based on post-incident reports and photographs, the HRR of these fuels was specified as follows.
+From 0~s to 440~s, the wooden items were not burning.
+From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW (based on the surface area of the burning wood).
+From 450~s until 540~s (the end of the simulation), the HRR of the wooden balcony and siding was specified as a constant 5~MW.
 \end{enumerate}
 
-Figure~\ref{fig:hrr} shows the prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
+\clearpage
+
+Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
 In this figure, the text labels indicate the three stages of the fire based on the contribution of the fuel packages.

### 2014-09-24 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to report

@@
 The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft).
-A grid resolution of 10~cm (3.9~in) was used, which required approximately 5.1 million computational cells.
+A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 5.1 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~\ref{fig:SMV_exterior_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.
 
@@
 \includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
-\caption{Front (left) and rear (right) of the structure with a 10~cm computational mesh.}
+\caption{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
 \label{fig:SMV_exterior_grid}
@@
 \caption[Rear-left side of the structure within the computational domain.]
-{Rear-left side of the structure within the computational domain (with multiple meshes).}
+{Rear-left side of the structure within the computational domain with multiple meshes.}
 \label{fig:mult_mesh}

### 2014-09-24 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, add figures

@@
 
-% Extra packages
-\usepackage{xfrac}
-\pgfplotsset{compat=1.10}
+\usepackage{fancyhdr}
+\pagestyle{fancy}
+\lhead{}
+\rhead{}
+\chead{}
+\renewcommand{\headrulewidth}{0pt}
+
 \begin{document}
+\pagenumbering{gobble}
 
 \bibliographystyle{unsrt}
-\pagestyle{empty}
 
@@
 
-August 2014}}
+October 2014}}
 
@@
 \chapter*{\centering Abstract}
-\addcontentsline{toc}{chapter}{Abstract}
+\pagenumbering{gobble}
 
 \chapter{Introduction}
+\pagenumbering{arabic}
+\setcounter{page}{1}
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
@@
 The fire, which is described in Section~\ref{fire}, started in the basement and spread to the stairs which connect to the first floor.
-Discussion of the fire’s impact on the interior conditions is provided in Section~\ref{results}.
+Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
 Figure~\ref{fig:exterior} shows the exterior of the front and rear of the structure after the incident.
@@
 \label{mesh}
+For the simulation, a measure of how well the flow field is resolved can be estimated by using the non-dimensional expression $D^*/\dx$.
+Here, $D^*$ is the characteristic fire diameter, $\dx$ is the nominal size of a mesh cell, and $\dQ$ is the total heat release rate of the fire:
+\begin{equation}
+D^* = \left(
+     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g}}
+     \right)^\frac{2}{5} 
+\label{eq:mesh}
+\end{equation}   
+From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
+relation $Q^* = (D^*/D)^{5/2}$.
+Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Based on validation work performed for the U.S.
+Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
+The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
+
+As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
+The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
+A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
+As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
+Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
+Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
+Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
+
+\begin{figure}[!ht]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshfront}} \\
+   \scalebox{1.0}{\includegraphics[width=\textwidth]{../Figures/pg_county_meshrear}} 
+\end{tabular*}
+\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
+\label{fig:geom_grid}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=\textwidth]{../Figures/pg_county_meshtotal}
+\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
+Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
+\label{fig:mult_mesh}
+\end{figure}
+
+\begin{table}
+\centering
+\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
+\begin{tabular}{lll}
+\toprule[1.5pt]
+Parameter                                                  & Description                                   & Discussion                            \\
+\midrule
+Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
+\multirow{2}{*}{Grid Cell Size}                            &  10~cm around house                           & \multirow{2}{*}Section~\ref{mesh}}    \\ 
+                                                           &  20~cm for wind                               &                                       \\ [.25cm]
+Ambient Temperature$^*$                                    &  20~$^{\circ}$C (68~$^{\circ}$F)              & --                                    \\ [.1cm]
+\multirow{4}{*}{Reaction: Wood~\cite{SFPE:Tewarson}}       &  Formula: $\C\H_{1.7}\O_{0.74}\N_{0.002}$     & \multirow{4}{*}{Section~\ref{fire}}   \\
+                                                           &  CO Yield: 0.004~$\mathrm{kg}/\mathrm{kg}$    &                                       \\
+                                                           &  Soot Yield: 0.015~$\mathrm{kg}/\mathrm{kg}$  &                                       \\
+                                                           &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
+\multirow{2}{*}{Peak HRR}                                  &  Basement Fire: 9~MW                          & \multirow{2}{*}{Section~\ref{fire}}   \\ 
+                                                           &  Bathroom Fire: 3.3~MW                        &                                       \\ [.25cm]                     
+\multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\
+                                                           &  $\rho$: 510~kg/m$^3$                         &                                       \\
+                                                           &  $c_{p}$: 1.38~\si{kJ/(kg.K)}                 &                                       \\ [.25cm]
+\multirow{3}{*}{Material: Gypsum Board~\cite{WAKILI2007}}  &  $k$: 0.28~\si{W/(m.K)}                       &  \multirow{3}{*}{Section~\ref{matl}}  \\ 
+                                                           &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
+                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\footnotesize
+$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+\normalsize
+\end{table}
 

### 2014-09-25 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to mesh details; update mesh figure

@@
 The right side of the structure shared a common fire wall with another residential structure.
-The structure had a 17.73~m (58~ft) by 8.53~m (28~ft) footprint and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
+The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
 
@@
 
-As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 17.73~m (58~ft) by 8.53~m (28~ft) and a total height of 5.9~m (19~ft).
+As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The total volume of the computational domain was 17~m (56~ft) by 22~m (72~ft) by 13.6~m (45~ft).
-A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 5.1 million computational cells.
+The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) by 13.6~m (45~ft).
+A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
@@
 
-The domain was divided into 16 meshes (each containing between 272,000 and 367,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
+The domain was divided into 16 meshes (each containing between 184,000 and 248,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/SMV_Exterior_Meshes}
+\includegraphics[width=4.5in]{../Figures/SMV_Exterior_Meshes}
 \caption[Rear-left side of the structure within the computational domain.]

### 2014-09-25 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: minor update to mesh writeup

@@
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 15.5 for the 3.3~MW porch fire and 23 for the 9~MW attic fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 12 for the 1.5~MW bathroom fire and 20 for the 6.75~MW basement fire.
 Based on validation work performed for the U.S.
@@
 
-As discussed in Section~\ref{geom}, the structure has dimensions of 17.15~m (56~ft) by 6.15~m (20~ft) and a total height of 8.56~m (28~ft).
+As discussed in Section~\ref{geom}, the structure has dimensions of 9.14~m (30~ft) by 7.62~m (25~ft) and a total height of 7.31~m (24~ft).
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
@@
 Simulation Time                                            &  5~min                                        & --                                    \\ [.25cm]
-\multirow{2}{*}{Grid Cell Size}                            &  10~cm around house                           & \multirow{2}{*}Section~\ref{mesh}}    \\ 
+\multirow{2}{*}{Grid Cell Size}                            &  10~cm around house                           & \multirow{2}{*}{Section~\ref{mesh}}   \\ 
                                                            &  20~cm for wind                               &                                       \\ [.25cm]

### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edit
San Francisco: Minor edit to description of fire and simulation timeline

@@
 One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
-The beginning of the simulation ($t=0$) was selected to correspond to an on-scene time of 10:53:00 (see Table~\ref{tab:incident_timeline}).
-The HRRs for the three primary source fires was prescribed in FDS as follows.
+The duration of the fire simulation was 9~min (540~s).
+The beginning of the simulation (0~s) was selected to correspond to an on-scene time of 10:53:00, which was approximately five minutes after the fire department arrived on scene and approximately one minute before the E26 firefighting crew stated that the fire was located below the first floor.
+The end of the simulation (540~s) was selected to correspond to an on-scene time of 11:02:00, which is the time at which fire suppression operations began (see Table~\ref{tab:incident_timeline}).
+
+The HRRs for the three primary source fires were prescribed in FDS as follows.
 
@@
 \item The third exterior fuel item included the wood on the basement balcony and siding.
-To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data abotu the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
 The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
@@
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) by 13.6~m (45~ft).
+The dimensions of the computational domain were 11.5~m (38~ft) by 22~m (72~ft) and a height of 13.6~m (45~ft).
 A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells.

### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo

@@
 \item The third exterior fuel item included the wood on the basement balcony and siding.
-To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data abotu the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
 The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.

### 2014-09-26 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: update to mesh

@@
 As discussed in Section~\ref{geom}, the structure has dimensions of 9.14~m (30~ft) by 7.62~m (25~ft) and a total height of 7.31~m (24~ft).
-To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
-The total volume of the computational domain was 24~m (79~ft) by 10~m (33~ft) by 10~m (33~ft).
-A grid resolution of 10~cm (3.9~in) was used, which required 2.4 million computational cells.
+To sufficiently resolve the wind boundary condtion, the computational domain was extended beyond the volume of the structure.
+The large domain led to the use of two separate grid resolutions, a 10~cm resolution and a 20~cm resolution.
+The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (40ft) by 8~m (26~ft) that required 1.8 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
+
 Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.

### 2014-09-26 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add PDF metadata
San Francisco: Edits to fire section

@@
 \renewcommand{\headrulewidth}{0pt}
+
+% PDF metadata
+\hypersetup{
+  pdftitle={Simulation of a Basement Fire in a Wood Frame Residential Structure - San Francisco, CA},
+  pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
+  pdfsubject={Insert abstract here.},
+  pdfkeywords={insert; keywords; here}
+}
 
@@
 
-\clearpage
-
-Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel).
-The following lines define the source fires in the FDS input file:
-
-\begin{lstlisting}
-&SURF ID='COUCH_RIGHT_INITIAL',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
-
-&SURF ID='COUCH_MIDDLE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 1.037172E-5,
-    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
-
-&SURF ID='COUCH_LEFT_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
-
-&SURF ID='LOUNGE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.853485E-6,
-    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
-
-&SURF ID='CHAIR_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.918660E-6,
-    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
-
-&SURF ID='WOOD_EXTERIOR',
-    SPEC_ID='WOOD',
-    MASS_FLUX = 0.003049,
-    RAMP_MF='WOOD_EXTERIOR_RAMP' /
-\end{lstlisting}
-
-Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
-The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
-
 Polyurethane fuel was specified for the interior basement fuel items, which can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
@@
 The heat of combustion quantifies the amount of energy released per unit mass of the fuel.
-The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the desired fuel and reaction properties discussed above:
+The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the two fuels and reaction properties discussed above:
 
@@
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
+
+Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel).
+
+A time-dependent burning rate was specified for each of the fuel packages in terms of a fuel mass flux.
+The fuel mass flux is the amount of fuel vapor per unit area that is released from the surface of each fuel package shown in Fig.~\ref{fig:fuel_placement}.
+The specified time-dependent fuel mass flux for each fuel package corresponds to the HRRs that were described earlier.
+The HRR from each individual fuel package contributes to the total HRR shown in Fig.~\ref{fig:hrr}.
+FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
+The following lines define the fire surfaces for each fuel package in the FDS input file:
+
+\begin{lstlisting}
+&SURF ID='COUCH_RIGHT_INITIAL',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
+
+&SURF ID='COUCH_MIDDLE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 1.037172E-5,
+    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
+
+&SURF ID='COUCH_LEFT_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 5.271815E-6,
+    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
+
+&SURF ID='LOUNGE_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.853485E-6,
+    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
+
+&SURF ID='CHAIR_FLASHOVER',
+    SPEC_ID='POLYURETHANE',
+    MASS_FLUX = 7.918660E-6,
+    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
+
+&SURF ID='WOOD_EXTERIOR',
+    SPEC_ID='WOOD',
+    MASS_FLUX = 0.003049,
+    RAMP_MF='WOOD_EXTERIOR_RAMP' /
+\end{lstlisting}
+
+Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
+The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
 

### 2014-09-29 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add SMV figures for pressure, velocity, and temperature

@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Plan_Basement_Fuels}
+\includegraphics[width=5.5in]{../Figures/Plan_Basement_Fuels}
 \caption[Location of fuel items in the basement.]
@@
 
-The domain was divided into 16 meshes (each containing between 184,000 and 248,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 3~days.
+The domain was divided into 16 meshes (each containing between 184,000 and 248,200 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 2~days.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 
-Figure~\ref{fig:timeline_comparison} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occured through the failed windows on the rear side of the structure.
+Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occured through the failed windows on the rear side of the structure.
 In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed).
+Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.
 
@@
 For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
-\label{fig:timeline_comparison}
+\label{fig:timeline_comparison_rear}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=5.0in]{../Figures/Photo_Front_350_s}
+\includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
+\caption{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure.
+The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom).
+For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
+\label{fig:timeline_comparison_front}
 \end{figure}
@@
 
-% As the simulated fire grows in the attic and rear porch, the pressure rises.
-Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
-Gases at an elevated pressure will always move towards a region of lower pressure.
-The door serves as a boundary between the high and low pressure regions.
-Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
-The velocity vectors shown in Fig.~\ref{fig:velo_175s} (15~s after the interior door fails) indicate the direction of flow within the structure.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_pres2}
-% \input{../Scripts/colorbar_metric_pres}
-% \caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.}
-% \label{fig:pres_159s}
-% \end{figure}
-
-% \begin{landscape}
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_velo_175}
-% \input{../Scripts/colorbar_std_velo}
-% \input{../Scripts/colorbar_metric_velo}
-% \caption{FDS simulated velocity vectors, 15~s after interior door failure.}
-% \label{fig:velo_175s}
-% \end{figure}
-% \end{landscape}
-% \newpage
+As the simulated fire grows in the basement, the pressure in the basement rises and casues the hot gases to flow upwards from a region of high pressure (basement) to low pressure.
+Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation (342~s).
+The pressure rise in the basement ranges from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
+Gases at an elevated pressure will flow towards a region of lower pressure.
+Once the rear basement window fails, the high pressure gases flow towards the low pressure regions in the house towards the garage and front door via the stairwell.
+
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/SMV_Pres_340_s}
+\input{../Figures/colorbar_metric_pres}
+\includegraphics[width=5.5in]{../Figures/SMV_Pres_343_s}
+\input{../Figures/colorbar_metric_pres}
+\caption{FDS simulated pressure contours, 2~s prior (top) and 1~s after (bottom) first rear basement window failure. The fire originated in the living room in the basement.}
+\label{fig:smv_pressure}
+\end{figure}
+
+\clearpage
+
+\section{Velocity}
+\label{sec:velocity}
+
+The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vector} (15~s after the interior door fails) indicate the direction of flow within the structure.
+
+\begin{figure}[!ht]
+\includegraphics[width=4.5in]{../Figures/SMV_Vel_340_s}
+\input{../Figures/colorbar_metric_velo}
+\input{../Figures/colorbar_std_velo}
+\includegraphics[width=4.5in]{../Figures/SMV_Vel_402_s}
+\input{../Figures/colorbar_metric_velo}
+\input{../Figures/colorbar_std_velo}
+\caption{FDS simulated velocity contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\label{fig:smv_velocity}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_340_s}
+\input{../Figures/colorbar_metric_velo}
+\input{../Figures/colorbar_std_velo}
+\includegraphics[width=4.5in]{../Figures/SMV_Vel_Vec_402_s}
+\input{../Figures/colorbar_metric_velo}
+\input{../Figures/colorbar_std_velo}
+\caption{FDS simulated velocity vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\label{fig:smv_velocity_vector}
+\end{figure}
+
+\clearpage
 
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_129}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
-% \label{fig:temp_129s}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_159}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
-% \label{fig:temp_159s}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=4.3in]{../Figures/SMV_Temp_340_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\includegraphics[width=4.3in]{../Figures/SMV_Temp_402_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\caption{FDS simulated temperature contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\label{fig:smv_temperature}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_340_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\includegraphics[width=4.3in]{../Figures/SMV_Temp_Vec_402_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\caption{FDS simulated temperature vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\label{fig:smv_temperature_vector}
+\end{figure}
 

### 2014-09-29 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: Remove header text
Chicago Fire: minor update to headers
Chicago: update report to include metadata in PDF

@@
 \rhead{}
-\chead{This publication is available free of charge from:
-\hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}}
+\chead{}
 \renewcommand{\headrulewidth}{0pt}
+
+% PDF metadata
+\hypersetup{
+  pdftitle={Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL},
+  pdfauthor={Weinschenk, Craig G, Overholt, Kristopher J., and Madrzykowski, Daniel},
+  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2~\sfrac{1}{2}~story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
+The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The fire started in the attic and spread down through an opening into the enclosed porch on the rear of the structure.
+This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas.
+The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
+After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward.
+The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
+The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at a height of 1.86~m (6~ft).
+Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
+It appears that the captain was likely overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
+After a Mayday call, the captain was rescued from the structure, but later succumbed to his injuries.},
+  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
+}
 

### 2014-09-29 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to colorbars

@@
 \input{../Figures/colorbar_metric_pres}
-\caption{FDS simulated pressure contours, 2~s prior (top) and 1~s after (bottom) first rear basement window failure. The fire originated in the living room in the basement.}
+\caption{FDS simulated pressure contours, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
 \label{fig:smv_pressure}
@@
 \input{../Figures/colorbar_std_velo}
-\caption{FDS simulated velocity contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\caption{FDS simulated velocity contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_velocity}
@@
 \input{../Figures/colorbar_std_velo}
-\caption{FDS simulated velocity vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_velocity_vector}
@@
 \input{../Figures/colorbar_std_temp}
-\caption{FDS simulated temperature contours, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\caption{FDS simulated temperature contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_temperature}
@@
 \input{../Figures/colorbar_std_temp}
-\caption{FDS simulated temperature vectors, 2~s prior (top) and 60~s after (bottom) first rear basement window failure.}
+\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_temperature_vector}
@@
 Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
-Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class III exposure~\cite{Donnelly2006}.
-Firefighters are at increased risk levels when encountering Class III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
+Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}.
+Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
 Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 % In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
-These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
+These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.

### 2014-09-29 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: update figures and minor update to report

@@
 \renewcommand{\headrulewidth}{0pt}
+
+% PDF metadata
+\hypersetup{
+  pdftitle={Simulation of a Wind Driven Basement Fire - Riverdale Heights, MD},
+  pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
+  pdfsubject={Insert abstract here.},
+  pdfkeywords={insert; keywords; here}
+}
 
@@
 The interior walls and ceiling were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{PGCounty2013}.
-There is a single flight of stairs in the center of the structure which connected the first floor to the basement.
+There was a single flight of stairs in the center of the structure which connected the first floor to the basement.
 Access to the structure could be made on the front side of the first floor and the rear side of the basement.
@@
 \end{tabular*}
-\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
+\caption{Front (top) and rear (bottom) of the structure with 10~cm computational mesh surrounding the structure and 20~cm mesh to the left and right of the structure.}
 \label{fig:geom_grid}

### 2014-09-30 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to discussion section; add preliminary flow path figure

@@
 \begin{figure}[!ht]
-\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor_Metric}
-\includegraphics[width=5.0in]{../Figures/Plan_First_Floor_Metric}
-\includegraphics[width=5.0in]{../Figures/Plan_Basement_Metric}
+\includegraphics[width=5.0in]{../Figures/Plan_Second_Floor}
+\includegraphics[width=5.0in]{../Figures/Plan_First_Floor}
+\includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
 \caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
 The fire originated in the living room on the basement floor.
-Stairs and rooms are identified using measurements collected by NIST.}
+Stairs and rooms are identified using information collected by NIST.}
 \label{fig:floor_plan}
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_161}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption{FDS simulated temperature contours, 1~s after interior door failure.}
-% \label{fig:temp_161s}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_175}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption{FDS simulated temperature contours, 15~s after the interior door failure.}
-% \label{fig:temp_175s}
-% \end{figure}
-
 % As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
@@
 
-% The results of the FDS simulations are discussed in the following two sections.
-The first section addresses the results of the computational modeling as they relate to the interior hallways conditions.
+The results of the FDS simulations are discussed in the following two sections.
+The first section addresses the results of the simulation as they relate to the flow path and the conditions in the interior stairwell.
 The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
 
-\section{Simulated Hallway Flow Path}
+\section{Simulated Stairwell Flow Path}
 \label{sec:simulated_flow_path}
 
-% From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions on the second floor of the structure were initially tenable.
-From the NIOSH report~\cite{NIOSH:Bowyer2}, while the IC was inside the structure on the second floor, only light haze and a glow around the door between the hallway and enclosed porch was observed.
-This indicated the presence of fire in the area of the enclosed porch.
-The simulation results indicate a high hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the attic and the enclosed porch at this time.
-By the time the E123 captain and firefighter arrived on the second floor (Table~\ref{tab:combined_timeline}) and approached the rear of the structure, the rear porch was fully involved.
-Temperature conditions greater than 260~$^{\circ}$C (500~$^{\circ}$F) were present on the porch side of the steel-faced, wood-framed door at the rear of the structure.
-Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:combined_timeline}).
-Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
-Note the large crease in the steel face of the door just above the knob.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/Porch_Door_1}
-% \caption{Post-fire image of interior door.}
-% \label{fig:chicago_doorfold}
-% \end{figure}
-
-% After the interior door failed, an interior flow path was created from the enclosed porch area into the kitchen of the structure.
-This resulted in a rapid change in the conditions within the flow path.
-The combustion gases at elevated temperature and pressure in the enclosed porch were vented by the failure of the door and flowed towards lower pressure areas in the hallways and kitchen.
-The arrows shown in Fig.~\ref{fig:flowpath_1} summarize the simulated flow direction of gases on the second floor after the door failure.
+From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions in the stairwell on the front side of the structure were initially tenable.
+The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the fire was located in the basement.
+After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell below the laundry room landing area.
+The two E26 firefighters were located within the flow path between the basement and the vent outlets on the front side of the structure.
+
+After the rear basement windows failed, an interior flow path was created from the basement living room area and the vent outlets on the front side of the structure (the front door and the overhead garage door).
+The rear basement window failures resulted in a rapid change in the conditions within the flow path.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed towards lower pressure areas via the stairwell.
+The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases from the basement after the window failures.
 In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures.
@@
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/ChicagoFlow}
-% \caption{Summary of simulated flow path on the second floor after interior door failure.}
-% \label{fig:flowpath_1}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=5.0in]{../Figures/Flow_Path_Top}
+\caption{Summary of simulated flow path in the stairwell on the basement and first floors after rear basement window failures.}
+\label{fig:flow_path_top}
+\end{figure}
 
@@
 Uncoordinated ventilation can also be the cause of increased thermal hazards within a flow path.
+
+% Door control - search then close doors
+% 360 of building
+% Stay out of the flow path
+% Exterior attack from rear deck gun
 

### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add details to results and discussion sections related to flow path, hazard, and tactics; add abstract and summary

@@
 
-% The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
-After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward.
-The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway exceeded 260~$^{\circ}$C (500~$^{\circ}$F) at a height of 1.86~m (6~ft).
-Unfortunately, a captain and firefighter were advancing a hose line in the hallway near the door at the time of the door failure.
-It appears that the captain was likely overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday call, the captain was rescued from the structure, but later succumbed to his injuries.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
+The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
 
@@
 
-Part of the function of the Fire Research Division at the National Institute of Standars and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
@@
 The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure became limited.
-At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occured near the ventilation openings where ambient air was available.
+At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurred near the ventilation openings where ambient air was available.
 
@@
 The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.
+
+Note that the HRR in the simulation might be overpredicted due to limitations in the combustion model related to the reignition of fuel-rich gases.
+In other words, there is some combustion occurring in the simulation near the front door and second floor as the fuel-rich gases mix with fresh air and reignite, which is not consistent with on-scene and post-incident photographs.
+However, for the high-hazard areas that are the focus of this study (the basement and interior stairwell), the pressures, temperatures, and velocities are representative of the hazardous flow path conditions that would have occurred in this fire incident.
 
@@
 
-As the simulated fire grows in the basement, the pressure in the basement rises and casues the hot gases to flow upwards from a region of high pressure (basement) to low pressure.
-Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation (342~s).
+As the simulated fire grew in the basement, the pressure in the basement increased and caused the hot gases to flow upwards from a region of high pressure in the basement to a region low pressure via the interior stairwell.
+Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation.
+
+In this figure, the pressure profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
 The pressure rise in the basement ranges from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
-Gases at an elevated pressure will flow towards a region of lower pressure.
-Once the rear basement window fails, the high pressure gases flow towards the low pressure regions in the house towards the garage and front door via the stairwell.
 
@@
 
-The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vector} (15~s after the interior door fails) indicate the direction of flow within the structure.
+Gases at an elevated pressure will flow towards a region of lower pressure.
+Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed into the interior stairwell towards the low pressure regions in the house and exhausted via the garage door and front door.
+The velocity contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.
+
+In this figure, the velocity profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
+
+The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vectors} indicate the direction and magnitude of flow velocities within the structure before and after the rear basement window failures.
+Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the maximum velocity in the interior stairwell was approximately 9~m/s (20 mph).
 
@@
 \caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
-\label{fig:smv_velocity_vector}
+\label{fig:smv_velocity_vectors}
 \end{figure}
@@
 
-% Analysis of the temperatures from the FDS simulation focuses on the high hazard areas of the structure: the attic, the rear porch and stairwell, and the interior hallway which connects the rear porch to the front stairwell.
-The temperature profile at these high hazard areas is shown via several snapshots in time to illustrate the change in the interior conditions.
-The first snapshots are shown at a time of 129~s into the simulation, just before a firefighter opened the rear porch door (as shown in Fig.~\ref{fig:temp_129s}), and 159~s into the simulation, just before the interior door fails (as shown in Fig.~\ref{fig:temp_159s}).
+Analysis of the temperatures from the simulation focuses on the high hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door).
+The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.
+
+In this figure, The temperature profile at these high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
+
+The temperature vectors shown in Fig.~\ref{fig:smv_temperature_vectors} indicate the gas temperatures and direction of flow within the structure before and after the rear basement window failures.
+Based on the results shown in Figs.~\ref{fig:smv_temperature} and \ref{fig:smv_temperature_vectors} after the rear basement windows began to fail, the maximum temperature in the basement was in excess of 800~$^{\circ}$C (1500~$^{\circ}$F), and the maximum temperature in the interior stairwell was in excess of 600~$^{\circ}$C (1100~$^{\circ}$F).
 
@@
 \caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
-\label{fig:smv_temperature_vector}
-\end{figure}
-
-% Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
-High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
-Before the interior door fails (Fig.~\ref{fig:temp_159s}), the inflow of ambient air from the open rear door reduces the temperatures near the interior doorway, but at the same time, the HRR increases because of the additional ventilation, as shown in Fig.~\ref{fig:hrr}.
-As shown in Fig.~\ref{fig:temp_161s}, after the second floor interior door fails, the high temperature gas that filled the rear porch flows in the direction of lower pressure (i.e., towards the front door).
-Note that the conditions in the attic do not appear to change.
-
-% As shown in Fig.~\ref{fig:temp_175s}, 15~s after the door failed, high temperature gases descended to approximately 1~m (3.28~ft) above the floor through the interior hallway and are flowing into the kitchen.
+\label{fig:smv_temperature_vectors}
+\end{figure}
 
@@
 
-\section{Simulated Stairwell Flow Path}
+\section{Simulated Interior Stairwell Flow Path}
 \label{sec:simulated_flow_path}
 
-From on-scene reports (Section~\ref{sec:incident_summary}) and the FDS simulation results (Section~\ref{sec:temperature}), the interior conditions in the stairwell on the front side of the structure were initially tenable.
-The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the fire was located in the basement.
-After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell below the laundry room landing area.
-The two E26 firefighters were located within the flow path between the basement and the vent outlets on the front side of the structure.
-
-After the rear basement windows failed, an interior flow path was created from the basement living room area and the vent outlets on the front side of the structure (the front door and the overhead garage door).
+The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the interior stairwell on the front side of the structure was used to determine that the fire was located in the basement.
+From the simulation results (Section~\ref{sec:temperature}), the conditions in the interior stairwell were initially tenable.
+After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell near the laundry room landing area.
+
+After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door).
 The rear basement window failures resulted in a rapid change in the conditions within the flow path.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed towards lower pressure areas via the stairwell.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+
 The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases from the basement after the window failures.
@@
 \includegraphics[width=5.0in]{../Figures/Flow_Path_Top}
-\caption{Summary of simulated flow path in the stairwell on the basement and first floors after rear basement window failures.}
+\caption{Summary of simulated flow path in the stairwell on the basement floor and first floor after the rear basement window failures.}
 \label{fig:flow_path_top}
@@
 Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
-Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
-This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.
+Based on the simulation results shown in Section~\ref{sec:temperature}, the simulated flow path temperatures in the interior stairwell were in excess of 600~$^{\circ}$C (1100~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20 mph).
+
+% The temperature of the gases that flowed into the interior stairwell was estimated to be approximately XXX~$^{\circ}$C (XXX~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 
@@
 
+% Insert top-down figures from SMV showing laundry room landing area temperatures.
+
 % \begin{figure}[!ht]
@@
 
+In this fire incident, the failure of the basement windows on the rear side of the structure coincided with a rapid change in the thermal conditions in the interior stairwell.
+The rear basement window failures resulted in the establishment of a flow path within the interior stairwell with highly hazardous conditions.
+These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.
+
+After the primary search was conducted, closing the interior doors (i.e., door control) could have inhibited the establishment of a flow path in the interior stairwell.
+A 360$^\circ$ scene size-up by the arriving firefighters could have helped determine the location of the fire in the basement and identify potential flow paths within the structure.
+The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
+Firefighters should avoid placing themselves within a flow path, where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
+
+The timing of the interior attack in the basement occurred after delays in forcible entry operations on the exterior basement door.
+Suppression operations should be coordinated with interior operations to reduce thermal hazards related to flow paths within a structure.
+Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
+
 There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
@@
 Uncoordinated ventilation can also be the cause of increased thermal hazards within a flow path.
-
-% Door control - search then close doors
-% 360 of building
-% Stay out of the flow path
-% Exterior attack from rear deck gun
-
-% In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
-These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.
-Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.
-In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
-Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
 
@@
 
-% NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death the captain of a fire department.
-The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, videos, and relevant literature.
-This resulted in a specified source fire of 12.3~MW in the attic and rear porch of the structure.
-However, based on the limited ventilation conditions in the attic and enclosed porch, the FDS simulation results indicated a maximum HRR of approximately 9~MW as a result of the limited supply of oxygen.
-
-% The fire started in the attic and spread down into the enclosed porch on the rear of the structure.
-The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door that was located between the enclosed porch and the hallway.
-After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed and the steel faces of the door failed and collapsed inward.
-The door failure resulted in the establishment of a flow path between the higher pressure and higher temperature conditions in the enclosed porch and the lower pressure and lower temperature conditions in the hallway and kitchen areas of the second floor.
-The temperature of the gases that flowed into the hallway at face height was calculated to exceed 260~$^{\circ}$C (500~$^{\circ}$F).
-Unfortunately, a captain and firefighter were advancing a hose line in the hallway at the time of the door failure.
-The captain was overcome by the rapid change in conditions before he could exit to the safety of the kitchen area.
-After a Mayday call, the captain was rescued from the structure but later succumbed to his injuries.
+NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
+The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.
+This resulted in a maximum specified source fire of approximately 20~MW in the basement and rear balcony of the structure.
+Based on the limited ventilation conditions in the basement, the FDS simulation results indicated a HRR of approximately 2~MW as a result of the limited supply of oxygen.
+After the rear basement windows failed, the HRR increased to approximately 32~MW before it reached a steady-state value of approximately 20~MW.
+
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
+After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door).
+The rear basement window failures resulted in a rapid change in the conditions within the flow path.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+
+Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
+The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
 

### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits

@@
 \begin{enumerate}
-\item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR.
+\item For the initial couch fire in the basement, the HRR from 0~s to 327~s followed the experimentally measured mattress HRR~\cite{madrzykowski2009fire}.
 The HRR at 300~s was approximately 3~MW, and the HRR at 327~s was approximately 5~MW.
@@
 
-Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occured through the failed windows on the rear side of the structure.
+Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurred through the failed windows on the rear side of the structure.
 In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed).

### 2014-10-01 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add references for fuel packages

@@
 Based on these sources of information, the FDS model includes three source fires: 1) an initial couch fire in the basement, 2) a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the exterior basement balcony.
+
 The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood.
 The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
+The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
+Other combustible items and furnishings such as tables, stools, bookshelves, and carpet were present in the basement living room.
+However, to simplify the analysis and specification of the design fire, only the above fuel items were included because they were considered to have contributed the largest amount of energy in this fire scenario.
 
@@
 \item The secondary fuel packages in the basement were divided among four additional furniture items (two couches, a lounge, and a chair).
+The HRRs of these additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items, which reported HRRs of upholstered chairs and couches ranging from 2~MW to 5~MW~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1,Janssens:2012}.
 The two large couches in the middle of the basement were specified with a peak HRR of 5~MW for each item.

### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add figures and discussion to flow path and hazard sections

@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
@@
 The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
-The pressure rise in the basement ranges from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
+After the rear basement windows failed, the pressure rise in the basement ranged from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
 
@@
 The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vectors} indicate the direction and magnitude of flow velocities within the structure before and after the rear basement window failures.
-Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the maximum velocity in the interior stairwell was approximately 9~m/s (20 mph).
+Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the velocity in the interior stairwell was approximately 4~m/s (9~mph) before the rear basement windows failed and approximately 9~m/s (20~mph) after the rear basement windows failed.
 
@@
 The temperature vectors shown in Fig.~\ref{fig:smv_temperature_vectors} indicate the gas temperatures and direction of flow within the structure before and after the rear basement window failures.
-Based on the results shown in Figs.~\ref{fig:smv_temperature} and \ref{fig:smv_temperature_vectors} after the rear basement windows began to fail, the maximum temperature in the basement was in excess of 800~$^{\circ}$C (1500~$^{\circ}$F), and the maximum temperature in the interior stairwell was in excess of 600~$^{\circ}$C (1100~$^{\circ}$F).
+Based on the results shown in Figs.~\ref{fig:smv_temperature} and \ref{fig:smv_temperature_vectors}, 60~s after the rear basement windows began to fail, the temperature in the basement was in excess of 800~$^{\circ}$C (1500~$^{\circ}$F), and the temperature in the interior stairwell was in excess of 540~$^{\circ}$C (1000~$^{\circ}$F).
 
@@
 From the simulation results (Section~\ref{sec:temperature}), the conditions in the interior stairwell were initially tenable.
-After the rear basement windows failed, the simulation results indicate a high-hazard area (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell near the laundry room landing area.
+After the rear basement windows failed, the simulation results indicate a high-hazard area that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell near the laundry room landing area.
 
@@
 \begin{figure}[!ht]
-\includegraphics[width=5.0in]{../Figures/Flow_Path_Top}
-\caption{Summary of simulated flow path in the stairwell on the basement floor and first floor after the rear basement window failures.}
+\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_First_Floor}
+\includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
+\caption{Summary of simulated flow path in the stairwell on the first floor and basement floor 120~s after the first rear basement window failure.
+The arrows indicate the direction of flow.
+Two arrows located at a door or window indicate bi-directional flow at a vent opening.
+The maximum velocity (red) corresponds to 9~m/s (20~mph).}
 \label{fig:flow_path_top}
 \end{figure}
+
+\clearpage
 
@@
 Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
-Based on the simulation results shown in Section~\ref{sec:temperature}, the simulated flow path temperatures in the interior stairwell were in excess of 600~$^{\circ}$C (1100~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20 mph).
-
-% The temperature of the gases that flowed into the interior stairwell was estimated to be approximately XXX~$^{\circ}$C (XXX~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
-
-% Prior to the interior door failure, the elevated temperatures on the second floor were limited to the rear porch, as shown in Fig.~\ref{fig:temp_top_159}.
-The temperatures were greatest at the back-left corner where there is sufficient oxygen due to the section of porch wall that had burned away and allowed additional oxygen to mix with the fuel-rich fire gases.
-Five seconds after the interior door failed, hot gases traveled the length of the interior hallway and approached the doorway into the kitchen, which was approximately 4.5~m (14.8~ft) away from the source fire, as shown in Fig.~\ref{fig:temp_top_165}.
-Within 60~s of the interior door failure, the hallway temperatures were approximately at or above 260~$^{\circ}$C (500~$^{\circ}$F) throughout the hallway, as shown in Fig.~\ref{fig:temp_top_220}.
-These results indicate that the high temperature gases seen 5~s after failure were not just a burst but rather the front of a sustained exhaust gas flow from the fire burning in the enclosed rear porch.
-The conditions in this hallway changed from tenable to high-hazard very rapidly following the door failure.
-Figure~\ref{fig:temp_top_220} also shows that the temperatures in the kitchen were at or below 90~$^{\circ}$C (194~$^{\circ}$F), and the temperatures at the top of the stairs were at or below 70~$^{\circ}$C (158~$^{\circ}$F).
-At these locations within the structure, the exhaust gases in the flow path were cooled and diluted by the inflowing ambient gas.
-These simulated temperatures are consistent with the post-incident conditions that were documented in the kitchen and second floor stairwell.
-
-% Insert top-down figures from SMV showing laundry room landing area temperatures.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_159_6ft}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
-% {Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
-% \label{fig:temp_top_159}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_165_6ft}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption[Temperature contours on the second floor, 5~s after interior door failure.]
-% {Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
-% \label{fig:temp_top_165}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/west_50th_baseline_top_220_6ft}
-% \input{../Scripts/colorbar_std} 
-% \input{../Scripts/colorbar_metric}
-% \caption[Temperature contours on the second floor, 60~s after interior door failure.]
-% {Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
-% \label{fig:temp_top_220}
-% \end{figure}
+
+Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m from the floor) on the first floor at a time of 2~s before the first rear basement window failed.
+At this time, the temperature of the gases in the interior stairwell exceeded 200~$^{\circ}$C (400~$^{\circ}$F).
+
+\begin{figure}[!ht]
+\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_340_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
+\label{fig:smv_flow_path_top_1}
+\end{figure}
+
+Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m from the floor) on the first floor at a time of 60~s and 120~s after the first rear basement window failed.
+At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+As more rear basement windows failed and provided ambient air to the growing basement fire, the temperatures in the interior stairwell continued to rise.
+At a time of 120~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_402_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\includegraphics[width=4.3in]{../Figures/SMV_Top_Temp_462_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
+\label{fig:smv_flow_path_top_2}
+\end{figure}
+
+Based on these results and the simulation results shown in Sections~\ref{sec:velocity} and \ref{sec:temperature}, after the rear basement windows failed, the simulated flow path temperatures in the interior stairwell were in excess of 760~$^{\circ}$C (1400~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20 mph).
+The conditions in the interior stairwell changed from tenable to high-hazard very rapidly following the rear basement window failure.
+Within the structure, the exhaust gases in the flow path were moving towards the doors located on the front side of the structure via the interior stairwell.
+These simulated temperatures are consistent with the post-incident conditions that were documented in the interior stairwell.
+
+\clearpage
 
@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 600~$^{\circ}$C (1100~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 

### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to title and metadata

@@
 \hypersetup{
-  pdftitle={Simulation of a Basement Fire in a Wood Frame Residential Structure - San Francisco, CA},
+  pdftitle={Simulation of a Fire in a Hillside Residential Structure - San Francisco, CA},
   pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
-  pdfsubject={Insert abstract here.},
-  pdfkeywords={insert; keywords; here}
+  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
+The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
+The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.},
+  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
 }
@@
 \headerB{
-Simulation of a Basement Fire \\
-in a Wood Frame Residential \\
-Structure - San Francisco, CA \\
+Simulation of a Fire in a Hillside \\
+Residential Structure - \\
+San Francisco, CA \\
 }
@@
 {\em Fire Research Division \\
-Engineering Laboratory} \\
+Engineering Laboratory \\
 
@@
 Two arrows located at a door or window indicate bi-directional flow at a vent opening.
-The maximum velocity (red) corresponds to 9~m/s (20~mph).}
+The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
 \label{fig:flow_path_top}

### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in frontmatter
San Francisco: Add condensed figure captions

@@
 {\em Fire Research Division \\
-Engineering Laboratory \\
+Engineering Laboratory} \\
 
@@
 W \> Watt \\
-$k$ \> thermal conductivity \\
-$\rho$ \> density \\
-$c_{p}$ \> specific heat \\
 \end{tabbing}
@@
 \begin{table}[!ht]
-\caption[Abridged NIOSH approximate fire event timeline]{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
+\caption[Abridged NIOSH approximate fire event timeline]
+{Abridged NIOSH approximate fire event timeline~\cite{NIOSH:Bowyer2}}
 \begin{tabular}{cl}
@@
 \includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
-\caption[Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.]{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
+\caption[Plan view of second floor, first floor, and basement floor of structure.]
+{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
 The fire originated in the living room on the basement floor.
@@
 \includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
-\caption{Front (top) and rear (bottom) exterior of the structure after the incident.}
+\caption[Front and rear exterior of the structure after the incident.]
+{Front (top) and rear (bottom) exterior of the structure after the incident.}
 \label{fig:post_exterior}
@@
 \includegraphics[width=5.5in]{../Figures/Fire_HRR}
-\caption[Prescribed HRR vs. time.]
-{Prescribed HRR vs. time. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
+\caption[Prescribed HRR vs. time for the simulation.]
+{Prescribed HRR vs. time for the simulation. The text labels indicate the three stages of the fire based on the contribution of the fuel packages.}
 \label{fig:hrr}
@@
 \begin{table}[!ht]
-\caption[Timeline of ventilation events in the simulation]{Timeline of ventilation events in the simulation}
+\caption[Timeline of ventilation events in the simulation]
+{Timeline of ventilation events in the simulation}
 \begin{tabular}{ccll}
@@
 \includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
-\caption{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
+\caption[Front and rear of the structure with a 10~cm computational mesh.]
+{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
 \label{fig:SMV_exterior_grid}
@@
 \begin{table}[!ht]
-\caption[Relevant fire model input parameters]{Relevant fire model input parameters}
+\caption[Relevant fire model input parameters]
+{Relevant fire model input parameters}
 \begin{tabular}{lll}
@@
 \begin{table}[!ht]
-\caption[Fire incident and simulation event timeline]{Fire incident and simulation event timeline}
+\caption[Fire incident and simulation event timeline]
+{Fire incident and simulation event timeline}
 \begin{tabular}{ccl}
@@
 \includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
-\caption[HRR vs. time from the FDS simulations.]
-{HRR vs. time from the FDS simulations. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
+\caption[Predicted HRR vs. time from the FDS simulation.]
+{Predicted HRR vs. time from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
 \label{fig:hrr_w_fds}
@@
 \includegraphics[height=8.0in]{../Figures/Timeline_Comparison}
-\caption{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.
+\caption[Snapshots of exterior combustion occurring on the rear side of the structure.]
+{Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.
 The on-scene time is indicated on the left photograph, and the corresponding simulation time is indicated on the right Smokeview snapshot.
@@
 \includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
-\caption{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure.
+\caption[Snapshot of smoke coming out of the front side of the structure.]
+{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure.
 The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom).
@@
 
-In this figure, the pressure profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+In this figure, the pressure profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
 The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
@@
 \input{../Figures/colorbar_metric_pres}
-\caption{FDS simulated pressure contours, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s). The fire originated in the living room in the basement.}
+\caption[Simulated pressure contours on the right interior side of the structure.]
+{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s).
+The fire originated in the living room in the basement.}
 \label{fig:smv_pressure}
@@
 
-In this figure, the velocity profile within the high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+In this figure, the velocity profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
 The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
@@
 \input{../Figures/colorbar_std_velo}
-\caption{FDS simulated velocity contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+\caption[Simulated velocity contours on the right interior side of the structure.]
+{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_velocity}
@@
 \input{../Figures/colorbar_std_velo}
-\caption{FDS simulated velocity vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+\caption[Simulated velocity vectors on the right interior side of the structure.]
+{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_velocity_vectors}
@@
 
-Analysis of the temperatures from the simulation focuses on the high hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door).
+Analysis of the temperatures from the simulation focuses on the high-hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door).
 The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.
 
-In this figure, The temperature profile at these high hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+In this figure, The temperature profile at these high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
 The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
@@
 \input{../Figures/colorbar_std_temp}
-\caption{FDS simulated temperature contours, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+\caption[Simulated temperature contours on the right interior side of the structure.]
+{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_temperature}
@@
 \input{../Figures/colorbar_std_temp}
-\caption{FDS simulated temperature vectors, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+\caption[Simulated temperature vectors on the right interior side of the structure.]
+{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
 \label{fig:smv_temperature_vectors}
@@
 \includegraphics[width=6.5in]{../Figures/Flow_Path_Top_Vel_462_s_Basement_Floor}
-\caption{Summary of simulated flow path in the stairwell on the first floor and basement floor 120~s after the first rear basement window failure.
+\caption[Top view of the simulated flow path in the interior stairwell.]
+{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure.
 The arrows indicate the direction of flow.
@@
 \input{../Figures/colorbar_std_temp}
-\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
+\caption[Simulated temperature contours on the first floor before basement window failure.]
+{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
 \label{fig:smv_flow_path_top_1}
@@
 \input{../Figures/colorbar_std_temp}
-\caption{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
+\caption[Simulated temperature contours on the first floor after basement window failure.]
+{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
 \label{fig:smv_flow_path_top_2}
@@
 \begin{table}[!ht]
-\caption[Flow path related LODD/LODI incidents]{Flow path related LODD/LODI incidents}
+\caption[Flow path related LODD/LODI incidents]
+{Flow path related LODD/LODI incidents}
 \begin{tabular}{lll}
@@
 \includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
-\caption[Dimensioned drawing of the second floor.]{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of the second floor.]
+{Dimensioned drawing of the second floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:drawing_second_floor}
@@
 \includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
-\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of the first floor.]
+{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:drawing_first_floor}
@@
 \includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
-\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of the basement floor.]
+{Dimensioned drawing of the basement floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:drawing_basement}

### 2014-10-02 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to times

@@
 
-At a time of 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes.
+At 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes.
 As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW before it reached a steady-state value of approximately 20~MW.
@@
 \caption[Simulated pressure contours on the right interior side of the structure.]
-{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure (342~s).
+{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure.
 The fire originated in the living room in the basement.}
@@
 \caption[Simulated velocity contours on the right interior side of the structure.]
-{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
 \label{fig:smv_velocity}
@@
 \caption[Simulated velocity vectors on the right interior side of the structure.]
-{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
 \label{fig:smv_velocity_vectors}
@@
 \caption[Simulated temperature contours on the right interior side of the structure.]
-{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
 \label{fig:smv_temperature}
@@
 \caption[Simulated temperature vectors on the right interior side of the structure.]
-{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure (342~s).}
+{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
 \label{fig:smv_temperature_vectors}
@@
 \caption[Simulated temperature contours on the first floor before basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure (342~s).}
+{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure.}
 \label{fig:smv_flow_path_top_1}
@@
 \caption[Simulated temperature contours on the first floor after basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure (342~s).}
+{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
 \label{fig:smv_flow_path_top_2}

### 2014-10-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to flow path figure
San Francisco: Minor edit to flow path caption and acknowledgments

@@
 Two arrows located at a door or window indicate bi-directional flow at a vent opening.
-The maximum velocity is indicated by the red contour and corresponds to 9~m/s (20~mph).}
+The dashed arrow indicates a continuation of flow from the basement towards the first floor.
+The velocity contours use the same scale as Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors} with a range of 0~m/s to 9~m/s (0~mph to 20~mph).}
 \label{fig:flow_path_top}
@@
 The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}.
-Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.
+Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
 

### 2014-10-06 Projects/ECS_Testing/Report/ECS_Testing.tex
ECS Comm: add directories and data for ECS report

\documentclass[12pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../../Bibliography/commoncommands}

% Rename chapter headings
\renewcommand{\chaptername}{Section}
\renewcommand{\bibname}{References}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}
\newcommand{\Cl}{\mbox{Cl}}
\newcommand{\HCl}{\mbox{HCl}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\renewcommand{\headrulewidth}{0pt}

\hypersetup{
  pdftitle={Design Fires for Emission Control System Commissioning},
  pdfauthor={Weinschenk, Craig G and Bundy, Matt}, 
  pdfsubject={} 
  }

\begin{document}
\pagenumbering{gobble}

\bibliographystyle{unsrt}
%\pagestyle{empty}

\begin{minipage}[t][9in][s]{6.25in}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Design Fires for Emission \\
Control System Commissioning\\
}

\normalsize

\headerC{
{
\flushright{
Craig G. Weinschenk \\
Matt Bundy \\

\vspace*{2\baselineskip}

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

\vfill

\flushright{

\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}
}
}

\end{minipage}

\newpage
\hspace{5in}
\newpage

\frontmatter

\begin{minipage}[t][9in][s]{6.25in}
\pagenumbering{gobble}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Design Fires for Emission \\
Control System Commissioning\\
}

\headerC{
\flushright{
Craig G. Weinschenk \\
Matt Bundy \\
{\em Fire Research Division \\
Engineering Laboratory} \\

\vspace*{2\baselineskip}

\begingroup
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vspace*{2\baselineskip}

August 2014}}

\vfill

\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }

\titlesigs

\end{minipage}

\newpage

\begin{minipage}[t][9in][s]{6.25in}
\pagenumbering{gobble}

\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
document in order to describe an experimental procedure or concept adequately. \\
Such identification is not intended to imply recommendation or endorsement by the \\
National Institute of Standards and Technology, nor is it intended to imply that the \\
entities, materials, or equipment are necessarily the best available for the purpose. \\
}

\vspace{3in}

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
CODEN: NTNOEF }

\vfill

\hspace{1in}

\end{minipage}

\newpage

\frontmatter

\pagestyle{plain}
\pagenumbering{roman}
\setcounter{page}{3}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\chapter{List of Acronyms}

\begin{tabbing}
\hspace{1.5in} \= \\
FDS \> Fire Dynamics Simulator \\
HRR \> Heat Release Rate \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

\mainmatter

\chapter*{\centering Abstract}
\addcontentsline{toc}{chapter}{Abstract}
\pagenumbering{gobble}

\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}
The National Fire Research Laboratory (NFRL) is a fire test facility operated by the Engineering Laboratory at the National Institute of Standards and Technology (NIST). The NFRL is undergoing an expansion in order to provide additional research capabilities: test the performance of full-scale structures subjected to realistic fires and structural loading under controlled laboratory conditions, develop an experimental database on the performance of large-scale structural connections, components, sub-assemblies, and systems under realistic fire and loading, validate physics-based models to predict fire resistance performance of structures and enable performance-based standards for fire resistance design of structures and foster innovations in design and construction. To complete construction on the NFRL expansion, the updated emission control system needs to be tested to ensure the design specifications are achieved. This document will describe the source fires, appropriate lab safety, and test procedures. The objective of the fire tests is to use specifically designed source fires to test the emission control systems of the newly constructed fire research facility addition. The experiments are designed to ensure the system can handle elevated temperatures (gas burner), toxic gases (wood cribs with PVC), and particulates (group A commodities).

\chapter{Test Fires}
\label{test_fire}
The commissioning fires will take place in the pre-expansion laboratory space under a 9 m by 12 m oxygen-consumption calorimetry hood. The fuel packages will be centered under the hood, which is 6.4 m above the test floor. A flexible curtain, in place to contain combustion products, hangs 1.5 m below the lower edge of hood. Fig.~(\ref{fig:NFRL_fire}) shows a 2 MW natural gas fire under the hood during an experiment prior to the lab expansion. Note, that in the current configuration the wall to the left of the burner has been replaced by a roll-up door. The roll-up door provides access to the new testing space.

\begin{figure}
\includegraphics[width=\textwidth]{../Figures/NFRL_Fire}
\caption {Natural gas test burn in pre-construction NFRL.}
\label{fig:NFRL_fire}
\end{figure}

Based on the general experimental configuration shown in Fig.~(\ref{fig:NFRL_fire}) and \ref{app:nfrl_images}, Table ~\ref{tab:fires} outlines the fire tests to be conducted. The duplicity of tests is that similar to the existing system, the new ECS features two trains. Therefore, the scrubbing system in each train needs to be tested independently.

\begin{table}
\centering
\caption{Design fires for ECS commissioning tests}
\label{tab:fires}
\vskip.5\baselineskip
\begin{tabular}{ccccc}
\hline \hline
Test ID & Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
\hline \hline
1-3  & Natural Gas  & 2-8   & 60  & Temperature  \\
4  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 3 \\
5  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 3 \\
6  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 4 \\
7  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 4 \\
\hline
\end{tabular}
\end{table}

\section{Test 1}
\label{test1}
A natural gas burner is a very clean and well controlled source fire (generating CO$_2$ and H$_2$O products). The objective of this test is to challenge the system for hot gases using a controllable and well quantified fire. This is not designed to test scrubbing capabilities, but to prove the system can achieve the required temperature set points. It is critical to ensure the scrubber is working properly before pollutants are introduced. The natural gas burner is 1.61 m by 1.19 m by 0.88 m and is capable of delivering a fire up to 8 MW (cf. Fig.~(\ref{fig:nat_gas_burn})).

\begin{figure}
\centering
\includegraphics[width=.8\textwidth]{../Figures/Natural_Gas_Burner}
\caption {Isometric view of dimensioned natural gas burner.}
\label{fig:nat_gas_burn}
\end{figure}

The required mass flow of natural gas ($\dot{m}_{NG}$) needed to produce a desired fire size ($HRR_{NG}$) is
\begin{equation}
\dot{m}_{\mathrm{NG}} = HRR_{NG}/h_{c_{NG}}
\end{equation}
where $h_{c_{NG}}$ is the heat of combustion of natural gas. For complete combustion, the heat of combustion of natural gas is 50203 kJ/kg. Based on calculations included in \ref{app:gas_burn}, the required mass flow rate of natural gas for range of fire sizes is shown in Table~\ref{tab:ng_flow}. While the peak deliverable HRR is 8 MW, radiation from the fire to the surrounding environment at this magnitude is too significant for a 60 minute commissioning test. To test each train, a 4 MW fire will be used. To test that both trains can properly work together, an 8 MW fire will be used for a short duration, approximately 5 minutes.

\begin{table}
\centering
\caption{Mass flow rate of natural gas for experimental range of HRRs}
\label{tab:ng_flow}
\vskip.5\baselineskip
\begin{tabular}{cc}
\hline \hline
Fire Size (MW) & Flow Rate (kg/s)  \\
\hline \hline
2  &  0.04 \\
4  &  0.08 \\
6  &  0.12 \\
8  &  0.16 \\
\hline
\end{tabular}
\end{table}

\section{Test 2}
\label{test2}
To challenge the acid scrubbing capability of the system, pinewood cribs loaded with polyvinyl chloride (PVC) are used. This package is designed to deliver a controlled source of hydrochloric acid (HCl) gas that is close to the design capacity of the emission control system. Four pinewood cribs measuring 0.56 m by 0.56 m by 0.38 m will be used (cf. Fig.~(\ref{fig:wood_crib})). Each crib consists of 10 layers composed of 0.56 m by 0.04 m by 0.04 m pinewood sticks spaced 0.02 m apart. Eight 0.45 kg PVC sticks are distributed throughout each crib (cf. Fig.~(\ref{fig:wood_crib})) which brings the total mass of each crib to be 34 kg. The moisture content of the cribs should be between 6-8 \% using a commercial moisture detector. This fuel package is based on the wood crib tests from the 2001 commissioning tests.

\begin{figure}
\centering
\includegraphics[width=.75\textwidth]{../Figures/Wood_Cribs}
\caption {Isometric view of dimensioned single wood crib.}
\label{fig:wood_crib}
\end{figure}

To determine the HCL yield of PVC, we need to determine a balanced chemical reaction. First, is to assume that the test PVC can be represented by the chemical formula, $\C_2\H_3\Cl$ and that all of the Cl in PVC goes to HCl. Then, based on work by Tewarson \cite{SFPE:Tewarson}, yields for soot and CO are found ($y_{\mathrm{C}}$= 0.172, $y_{\mathrm{CO}}$= 0.063) and a balanced chemical reaction is created:

\begin{multline}
\C_2\H_3\Cl \,+\, 7.29(0.21 \O_2 \,+\, 0.79 \N_2) \\
\rightarrow 9.76(0.102\HCl \,+\, 0.103\H_2\O \,+\, 0.014 \C\O \,+\, 0.098 \C\O_2 \,+\, 0.092 \C \,+\, 0.59 \N_2)
\label{eq:hcl_reac}
\end{multline}
Based on Eq.~(\ref{eq:hcl_reac}), there is a 58 \% mass basis theoretical yield of HCl (\ref{app:crib}).  Experimental data based on burning PVC over a wide range of test conditions and using a wide range of measurement techniques puts the HCl yield between 10 and 56 \% \cite{Leeds:PVC}. Using data for a similarly scaled and ventilated test, the estimated HCl yield is 32 \% \cite{Persson1998}. Since each crib contains 3.63 kg of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65 kg (10.2 lb). Based on an estimated {\bf 60-70} \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is {\bf 1.4-1.9} kg ({\bf 3-4} lb).

The 4 cribs will be setup in two tiers. The first tier will be three cribs arranged in a triangle. The second tier will use the forth crib centered over the void created by the triangle. Each of the lower tier cribs will be raised 0.08 m off the ground to allow for a pan of heptane to slide underneath. The test configuration is shown in Fig.~(\ref{fig:test_crib}).The cribs are ignited using 500 mL of heptane poured into a round steel pan. The heptane represents about 1.5 \% of the initial mass of the crib, and burns out after about 2.5 to 3 minutes. The forth crib will ignite as a result of flame spread from the other three cribs.

\begin{figure}
\centering
\includegraphics[width=.7\textwidth]{../Figures/cribs}
\caption {Test configuration of 4 wood cribs with PVC inserts.}
\label{fig:test_crib}
\end{figure}

The burning rate of wood cribs is found from experiments performed by Madrzykowski and Stroup \cite{Madrzykowski1998} and Bryner and Mulholland \cite{Bryner1991}. The steady burning rate averaged over the peak 50 \% of burning is 0.03 kg/s. If an entire 34 kg crib burned at this rate, the burn would last approximately 19 minutes. If we estimate that 50 \% of the mass burns at 0.03 kg/s and the remaining 50 \% burns at $1/3$ the burning rate, 0.01 kg/s, then a crib burn would take approximately 40 minutes. The bottom three cribs in Fig.~(\ref{fig:test_crib}) are all ignited at nominally the same time. Therefore we can assume that all three will burn for about 40 minutes. If we assume an ignition delay of 5 minutes, a conservative estimate for total burn time is 45 minutes. This falls into the range of experimental burn durations from \cite{Bryner1991} of 40 to 65 minutes.

Wood cribs typically have peak HRR that range between 300 kW to 500 kW \cite{Madrzykowski1998,Bryner1991}. Depending on the time to peak HRR of first tier cribs relative to the second tier crib, the estimated peak HRR for these experiments is between 1.5 MW to 2 MW.

\section{Test 3}
\label{test3}
The third commissioning test is designed to test the system's capability to handle particulates, specifically soot. Standard Group A commodity boxes will be used as the fuel source. Each box, is a cube 0.53 m on a side and is filled with a plastic commodity. The plastic commodity inside the box consists of rigid crystalline polystyrene cups (empty, 0.47 L (16 fl oz) size) packaged in compartmented, single-wall, corrugated cardboard box. The cups are arranged open end down in five layers, 25 per layer for a total of 125 per box (cf. Fig.~(\ref{fig:open_box})).

\begin{figure}
\centering
\includegraphics[width=.7\textwidth]{../Figures/open_box}
\caption {Open commodity box showing top row of polystyrene cups.}
\label{fig:open_box}
\end{figure}

The mass of a polystyrene cup is 36 g. Using the 125 cup per box specification, there is 4.5 kg of polystyrene in each box. Using a soot yield of 0.16 kg soot/kg polystyrene from Tewarson \cite{SFPE:Tewarson}, then each box should produce approximately 0.72 kg of soot. Based on experimental work for the NYU-Poly ALIVE program \cite{Madrzykowski2013}, two columns of boxes with three rows of boxes in each column will burn between 20 to 25 minutes with a peak HRR of $\approx$ 2.5 MW. The six Group A commodity boxes should produce a total soot yield of 4-4.5 kg ($\approx$ 9 lb). Following the same analysis as the soot prediction and using an unburned hydrocarbon yield of 0.014 kg HC/kg polystyrene \cite{SFPE:Tewarson}, the boxes should produce approximately 0.4 kg (0.89 lb) of unburned hydrocarbons. This results in 0.96 to 1.2 kg of unburned hydrocarbons per hour (2.1 $-$ 2.6 lb/hr).

In these tests, the columns of boxes are spaced 0.15 m apart (cf. Fig.~(\ref{fig:dim_box})). It is important to note that both orientation and spacing of these boxes can have a significant impact on the burning characteristics \cite{Madrzykowski2013}.

\begin{figure}
\centering
\includegraphics[width=.7\textwidth]{../Figures/dim_box_array}
\caption {Dimensioned array of commodity boxes in test configuration.}
\label{fig:dim_box}
\end{figure}

The two columns of boxes will be ignited using shredded paper placed in the gap between the two columns of boxes. The paper will be ignited by a 1.83 m (6 ft) propane wand. As the cardboard burns away, the columns will lose structural integrity and the fire will transition into a polystyrene pool fire. The ignition point is set at the center line so that as the columns begin to collapse, they will collapse toward the center as that cardboard burned away first. The experiment will take place on top of sheets of cement board (such as USG Durock). This is done to contain the polystyrene melt in the later portion of the fire test. Fig.~(\ref{fig:comm_burn}) shows two columns of Group A commodity shortly after ignition and when the boxes are fully involved.

\begin{figure}[h!]
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\includegraphics[width=0.45\textwidth]{../Figures/comm_ignite} &
\includegraphics[width=0.45\textwidth]{../Figures/comm_burn} \\
\end{tabular*}
\caption{Two stacks of 3 boxes of group A commodities just after ignition (left) and fully involved (right). The boxes are lit with shredded paper and an electric match.  Peak heat release is $\approx$ 2.5 MW.}
\label{fig:comm_burn}
\end{figure}

\chapter{Safety}
\label{safety}
\section{Lab Safety Controls}
\label{controls}
At least two members of the NIST Fire Department will be present to perform a pre-test inspection and emergency fire suppression. A safety briefing will be connected prior to each test. All test participants and observers must attend the safety briefing. The occupancy in the lab during the commissioning fires will be determined by the AHJ. Test specific emergency procedures must be reviewed at each safety briefing.

\section{Potential Lab Hazards}
\label{lab_hazards}
For the ECS commissioning tests at the NFRL, the building will be transitioning from a construction site to an active laboratory. This combination space presents safety hazards to occupants. A partial lists of hazards to consider follows:
\begin{itemize}
\item {\bf Electrical Hazards}
%Minimum personal protective equipment (PPE) is safety glasses with side shields and steel toed safety shoes. Equipment, power cords and general housekeeping are inspected on a regular basis by Workspace Manager. Users of equipment in this workspace must have completed electrical safety training. All wall outlets are appropriately marked with voltage and breaker box number/breaker number.
\item {\bf Toxic/Corrosive Chemicals}
%All workers in this lab must complete MSDS training. CO detectors are installed near the CO cylinder and throughout work areas.  All NFRL staff members and guest workers are equipped with personal CO monitors that alarm at 10 ppm. Post fire test specimens (such as mattresses, furniture and demolished burn room structures that must be removed from building 205 are doused with water and stored in the rented construction dumpster). A thermal imaging camera will be used to insure samples have been fully extinguished before placing in this dumpster. Appropriate protective clothing and breathing apparatus will be determined according to the hazards associated with disposal of post-project debris.
\item {\bf Flammable/Reactive Materials}
%Minimum PPE is safety glasses with side shields and steel toed safety shoes. Two permanent flammable gas alarms are located above the natural gas fuel delivery line in the ceiling area. Protective barrier posts are installed at the base of the natural gas line to prevent vehicle collision. The gas line is equipped with three quarter turn shutoff valves and an automatic safety shutoff valve (secured with a key to prevent unintended use). A quarter turn valve located on the south side of building 205 can be used to shut off the gas supply to the entire building.  The natural gas flow rate and pressure are monitored when the burner is in use.
\item {\bf High Pressure Fluid Flow}
%Minimum PPE is safety glasses with side shields and steel toed safety shoes. Fire hose stream operators must complete MFRI fire suppression training and NFRL WSM led training.  Fire hose lines are routinely inspected and checked for leaks and taken out of service when leaks are found. Standpipe valves are closed and secured when not in use. A minimum of two qualified operators are required to handle a hose stream suppression line. 
\item {\bf Moving Heavy Objects}
%A forklift, hand truck, pallet jack, hoist crane and/or skid loader will be utilized to lift and move heavy objects that cannot be moved by hand. All operators will be adequately trained to use these devices. Training records must be documented in an approved project FLHR document before the start of any activity with this equipment.
\end{itemize}

\chapter{Experimental Test Procedures}
\label{test_procedure}
\subsection{Test 1 Procedure}
\label{procedure1}

\begin{enumerate}
  \item Perform leak check on all burner gas line connections and valves.
  \item Perform visual inspection to ensure spark ignitors are functioning correctly.
  \item Use a small flame to prove flame detector fuel shutoff safety system is working and will stop fuel flow if no flame is visible by shutting the Maxon safety shutoff valve.
  \item Start data collection system.
  \item Energize spark ignition system.
  \item Open pilot tube solenoid valve
  \item Slowly open manual metering valve and set fire to 100 kW.
  \item Open burner solenoid valves for banks 1 and 2 and set the fire to 500 kW.
  \item Open burner solenoid valves for banks 3 and 4 and set the fire to 2000 kW.
  \item After 15 min, slowly open the manual control valve to 4000 kW.
  \item After 15 min, slowly close the control valve and burner bank tubes and set the fire to 100 kW.
  \item Shut off the Maxon safety valve and then shut off the pilot tube after the fire is out.
  \item Close the manual shutoff valve. Wait 20 min before handling the burner.
\end{enumerate}

\subsection{Test 2 Procedure}
\label{procedure2}
\begin{enumerate}
  \item All flammable liquid stored are in outdoor containment building with a fuel spill containment floor. 
  \item A secondary containment device (graduate cylinder) will be used when transferring fuels and conducting fire tests.
  \item Position wood cribs on cement board.
  \item Fill 3 ignition pans with 500 mL heptane.
  \item Slide each pan of heptane under one of three wood cribs. 
  \item Ignite fuel pans with a 1.83 m (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.

\end{enumerate}

\subsection{Test 3 Procedure}
\label{procedure3}
\begin{enumerate}
  \item Position commodity boxes on cement board.
  \item Position shredded paper ignition source in 0.15 m gap between stacked boxes.
  \item Ignite shredded paper with 1.83 (6 ft) propane wand ignitor.
  \item Verify all post fire materials are sufficiently cool to prevent smoldering or off gassing.
  \item Workers are required to use PPE when performing post-fire cleanup.
\end{enumerate}

\chapter{Results}
Seven tests were conducted to commission the NFRL ECS:
\begin{enumerate}
\item 4 MW natural gas burn, exhaust train 3
\item 4 MW natural gas burn, exhaust train 4
\item 8 MW natural gas burn, exhaust trains 3 and 4
\item Wood crib burn, ECS train 3
\item Commodity burn, ECS train 3
\item Wood crib burn, ECS train 4
\item Commodity burn, ECS train 4
\end{enumerate}
Emission measurements were not made for tests 1, 2, and 3 since they were natural gas tests. Measurements were made during tests 4, 5, 6 and 7. The measurements were taken at the exhaust stack; the farthest downstream sensor port in the ECS.  Data was recorded throughout the duration of the experiments and then time averaged. The  Table~\ref{tab:hcl_data} shows the results including the mean mass flow rate of HCl for tests 4 and 6 as well as from a similar test conducted in 2001.

\begin{table}[h]
\centering
\caption{Exhaust measurements for wood crib experiments}
\label{tab:hcl_data}
\vskip.5\baselineskip
\begin{tabular}{cccc}
\hline \hline
Measurement Quantity & Test 4 & Test 6 & 2001 Test  \\
\hline \hline
Metered Volume (dcf)           &  47.39  &  59.22  &  36.52  \\
Total Test Time (min)          &  56.1   &  68.3   &  60     \\
Gas Temperature ($^{\circ}$F)  &  285    &  296    &  268    \\
Oxygen (\%)                    &  19.16  &  19.56  &  19.7   \\
Carbon Dioxide (\%)            &  0.81   &  1.00   &  1.1    \\
Velocity (ft/s)                &  54.37  &  54.36  &  45.09  \\
HCl Concentration (ppmdv)      &  8.60   &  10.55  &  2.98   \\
Mass Rate (lb/hr)              &  2.96   &  3.57   &  0.86   \\
\hline
\end{tabular}
\end{table}

Table~\ref{tab:hcl_data} shows the results including particulate emissions for tests 5 and 7.

\begin{table}[h]
\centering
\caption{Exhaust measurements for commodity experiments}
\label{tab:hcl_data}
\vskip.5\baselineskip
\begin{tabular}{ccc}
\hline \hline
Measurement Quantity & Test 5 & Test 7  \\
\hline \hline
Metered Volume (dcf)                &  40.97  &  38.28  \\
Total Test Time (min)               &  48.1   &  43     \\
Gas Temperature ($^{\circ}$F)       &  288    &  300    \\
Oxygen (\%)                         &  18.92  &  19.36  \\
Carbon Dioxide (\%)                 &  0.99   &  0.91   \\
Velocity (ft/s)                     &  53.75  &  55.18  \\
Particulate Concentration (g/dscf)  &  $< 4.67\text{\sc{e}-}5$   &  $< 5.08 \text{\sc{e}-}5$  \\
Mass Rate (lb/hr)                   &  $<$ 0.37   &  $<$ 0.40   \\
\hline
\end{tabular}
\end{table}

\chapter{Summary}

\chapter{Acknowledgments}

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,ECS}

\newpage

\appendix
\section{Schematics of the National Fire Research Lab}
\label{app:nfrl_images}
Images to describe the layout of the existing and additional lab space.

\begin{figure}[h!]
\includegraphics[width=\textwidth]{../Figures/plan_view2}
\caption {Plan view of the NFRL indicating location of ECS test fires.}
\label{fig:NFRL_plan}
\end{figure}

\begin{figure}[h!]
\includegraphics[width=\textwidth]{../Figures/section_2}
\caption {Rendering of the NFRL showing the original lab space (left) and the new lab space (right).}
\label{fig:NFRL_render}
\end{figure}
\end{document}

### 2014-10-06 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to Sections 1, 2, and 3

@@
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.1.1) simulations.
+This document describes the input and the results of the FDS (version 6.1.2) simulations.
 The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
@@
 This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{sec:model_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
-Appendix~\ref{sec:drawings} contains dimensioned drawings of the first and second floor of the structure.
+Appendix~\ref{sec:drawings} contains dimensioned drawings of the basement, first, and second floors of the structure.
 
@@
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
-The cells are contained together within one larger volume known as a computational domain.
+The cells are contained together within one larger volume known as the computational domain.
 The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
-Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gasses.
-One of the most important advantages of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data to ensure that it provides the expected results, given sufficient input data~\cite{FDS_Validation_Guide}.
+Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gases.
+One of the most important advantages of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data~\cite{FDS_Validation_Guide} to ensure that it provides the expected results, given sufficient input data.
 A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.
@@
 Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
-Smokeview allows the fire and fire movement to be visualized.
-This is done by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
-Smokeview also visualizes static data at particular times using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
+Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
 
@@
 Based on the goals of the analysis and the information collected, several engineering approximations were made.
-For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time, growth rate, and HRR were estimated were estimated using documentation of the potential fuel load within the structure.
-
-In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known but were estimated using documentation of the potential fuel load within the structure.
+
+In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
 Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
@@
 The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane.
-The exterior was primarily stucco with large windows on the top three stories on the rear side of the structure.
+The exterior was primarily stucco with large windows on the top three stories of the rear side of the structure.
+The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
 The right side of the structure shared a common fire wall with another residential structure.
-The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
 
@@
 A laundry area was located on a landing on the stairs between the first floor and basement.
-The basement was accessible via an exterior door on the left side of the structure and an interior set of stairs.
-The basement had a balcony on the exterior of the rear side of the structure.
+The basement was accessible via this interior set of stairs or via an exterior door on the left side of the structure.
+The basement had an exterior balcony on the rear side of the structure.
 The sub-basement level (i.e., the second story below street level) was not connected to the other three levels of the house, contained no windows, and was only accessible via an exterior door of the left side of the structure.
@@
 More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:model_results}.
-Figure~\ref{fig:post_exterior} shows the exterior of the front and rear of the structure after the incident.
-Note that the majority of the exterior damage occurred above the openings located on the basement floor (where the wooden balcony is located).
+Figure~\ref{fig:post_exterior} shows the exterior of the front and rear sides of the structure after the incident.
+Note that the majority of the exterior damage occurred above the openings located on the basement floor (where the wooden balcony was located).
 Fully dimensioned drawings of the second floor, first floor, and basement are shown in Figs.~\ref{fig:drawing_second_floor}, \ref{fig:drawing_first_floor} and \ref{fig:drawing_basement}, respectively.
@@
 \caption[Front and rear exterior of the structure after the incident.]
-{Front (top) and rear (bottom) exterior of the structure after the incident.}
+{Front (top) and rear (bottom) exterior sides of the structure after the incident.}
 \label{fig:post_exterior}
@@
 
-To estimate the type of fuel, fire size, and structure ventilation, on-scene photographs and post-incident reports were used.
-Based on these sources of information, the FDS model includes three source fires: 1) an initial couch fire in the basement, 2) a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the exterior basement balcony.
+On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure.
+Based on these sources of information, the FDS model included three source fires: 1)~an initial couch fire in the basement, 2)~a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the balcony located on the rear exterior side of the basement.
 
 The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood.
-The HRR of the initial couch fire is based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
+The HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
 The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
 Other combustible items and furnishings such as tables, stools, bookshelves, and carpet were present in the basement living room.
-However, to simplify the analysis and specification of the design fire, only the above fuel items were included because they were considered to have contributed the largest amount of energy in this fire scenario.
+However, to simplify the analysis and specification of the design fire, only the large upholstered furniture fuel items and balcony were included in the simulation because they were considered to have contributed the largest amount of energy in this fire scenario.
 
 The primary fuel packages were located in the basement as shown in Fig.~\ref{fig:fuel_placement}.
-In this figure, the numbered labels indicate the order in which the fuel items were burning: 1) the initial couch fire, 2) the secondary furniture fuel items, and 3) the balcony fire.
+In this figure, the numbered labels indicate the order in which the fuel items were burning: 1)~the initial couch fire, 2)~the secondary furniture fires, and 3)~the balcony fire.
 
@@
 
-Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifying assumptions were made.
+Since the exact time at which the fire started is not known relative to the notification of a fire or how quickly the fire spread, several simplifying assumptions were made.
 One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
@@
 The beginning of the simulation (0~s) was selected to correspond to an on-scene time of 10:53:00, which was approximately five minutes after the fire department arrived on scene and approximately one minute before the E26 firefighting crew stated that the fire was located below the first floor.
-The end of the simulation (540~s) was selected to correspond to an on-scene time of 11:02:00, which is the time at which fire suppression operations began (see Table~\ref{tab:incident_timeline}).
+The end of the simulation (540~s) was selected to correspond to an on-scene time of 11:02:00, which was the time at which substantial fire suppression operations were initiated (see Table~\ref{tab:incident_timeline}).
 
@@
 The HRR at 300~s was approximately 3~MW, and the HRR at 327~s was approximately 5~MW.
-From 327~s until 540~s (the end of the simulation), the HRR of the initial couch item was specified as a constant 5~MW.
-
-\item The secondary fuel packages in the basement were divided among four additional furniture items (two couches, a lounge, and a chair).
+From 327~s until 540~s (the end of the simulation), the HRR of the initial couch fire was specified as a constant 5~MW.
+
+\item The secondary fires in the basement were divided among four additional furniture items (two couches, a lounge, and a chair).
 The HRRs of these additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items, which reported HRRs of upholstered chairs and couches ranging from 2~MW to 5~MW~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1,Janssens:2012}.
@@
 
-\item The third exterior fuel item included the wood on the basement balcony and siding.
+\item The third fire involved the wood on the rear basement balcony and exterior siding.
 To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about the ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
@@
 From 0~s to 440~s, the wooden items were not burning.
-From 440~s to 450~s, the exterior basement balcony was ignited, and the total HRR increased linearly from 0~MW to 1~MW (based on the surface area of the burning wood).
-From 450~s until 540~s (the end of the simulation), the HRR of the wooden balcony and siding was specified as a constant 5~MW.
+From 440~s to 450~s, the exterior basement balcony and siding were ignited, and the total HRR increased linearly from 0~MW to 1~MW (based on the surface area of the burning wood).
+From 450~s until 540~s (the end of the simulation), the HRR of the wooden balcony and siding was specified as a constant 1~MW.
 \end{enumerate}
@@
 The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
-The heat of combustion quantifies the amount of energy released per unit mass of the fuel.
+The heat of combustion represents the amount of energy released per unit mass of the fuel.
 The following text defines Eqs.~\ref{eq:fuel_polyurethane} and \ref{eq:fuel_wood} for an FDS input file with the two fuels and reaction properties discussed above:
@@
 Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
+This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing, and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
 
-Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony for the wood fuel).
+Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony and siding for the wood fuel).
 
@@
 
-Note that the mass flux values here are unique for each fuel item and are specific to the input files used for these simulations.
-The key point is that each fuel item was modeled as a 3D object with flat surfaces from which a specified amount of fuel flows, mixes with air, and burns.
+Note that the mass flux values here are unique for each fuel item and are specific to the input file used for these simulations.
+The key point is that each fuel item was modeled as a 3D object with surfaces from which a specified amount of fuel flows into the domain, mixes with air, and burns.
 
@@
 
-While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage in the ceiling, walls, and floor.
+While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties of the ceiling, walls, and floors (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage.
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
@@
 
-The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (fire breaching walls, breaking windows, etc).
+The simulation in this study accounted for changes in ventilation due to a combination of fire department operations (opening doors) and fire acting on the structure (breaking windows).
 The ventilation times and ventilation areas represent our best understanding of the incident.
@@
 
-During the time at which the downed firefighters were located, the state of some windows and doors in the structure was known, which resulted in the establishment of a flow path in the interior stairwell leading into the basement.
+During the time at which the downed firefighters were found, the state of some windows and doors in the structure was known, which resulted in the establishment of a flow path in the interior stairwell leading into the basement.
 However, the exact time of operation for other doors was not known.
-Therefore, the following doors were assumed to be open at the start of the simulation: 1) the front door, 2) the interior door leading from the hallway on the first floor into the stairwell towards the basement, 3) the door leading from the garage into the first floor landing, and 4) the overhead garage door.
-The basement windows and exterior door were specified to open at certain times based on observations of failure (i.e., window breakage) or fire department operations (i.e., forcible entry) from on-scene photographs and post-incident reports.
+Therefore, the following doors were assumed to be open at the start of the simulation: 1)~the front door, 2)~the interior door leading from the hallway on the first floor into the stairwell towards the basement, 3)~the door leading from the garage into the first floor landing, and 4)~the overhead garage door.
+The rear basement windows and exterior basement door on the left side of the structure were specified to open at certain times based on observations of failure (i.e., window breakage) or fire department operations (i.e., forcible entry) from on-scene photographs and post-incident reports.
 
@@
 The open front door at the start of the simulation and the vents created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
-Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
+Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and was not included in this study.
 
@@
 \midrule
-0                    &  1.47              &  Door                &  Front Entry Exterior     \\
-0                    &  10.1              &  Overhead Door       &  Front Garage Exterior    \\
-0                    &  1.68              &  Door                &  Stairwell Interior       \\
-0                    &  1.68              &  Door                &  Garage Interior          \\
-342                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
-383                  &  1.89              &  Sliding Glass Door  &  Rear Basement Exterior   \\
-383                  &  1.68              &  Door                &  Left Basement Exterior   \\
-418                  &  2.52              &  Window              &  Rear Basement Exterior   \\
-440                  &  2.31              &  Window              &  Rear Basement Exterior   \\
-450                  &  3.78              &  Sliding Glass Door  &  Rear Basement Exterior   \\
+0                    &  1.47              &  Door                &  Exterior Front Entry     \\
+0                    &  10.1              &  Overhead Door       &  Exterior Front Garage    \\
+0                    &  1.68              &  Door                &  Interior Stairwell       \\
+0                    &  1.68              &  Door                &  Interior Garage          \\
+342                  &  1.89              &  Sliding Glass Door  &  Exterior Rear Basement   \\
+383                  &  1.89              &  Sliding Glass Door  &  Exterior Rear Basement   \\
+383                  &  1.68              &  Door                &  Exterior Left Basement   \\
+418                  &  2.52              &  Window              &  Exterior Rear Basement   \\
+440                  &  2.31              &  Window              &  Exterior Rear Basement   \\
+450                  &  3.78              &  Sliding Glass Door  &  Exterior Rear Basement   \\
 \bottomrule
@@
 Based on validation work performed for the U.S.
-Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
+Nuclear Regulatory Commission, $D^*/\dx$ values that ranged between 4 and 16 produced results that were adequate for engineering calculations~\cite{NUREG_1824}.
 Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the ratio of the characteristic fire diameter to cell size ($D^*/\dx$) was 18 for the initial couch fire (combined HRR of 5~MW), 31 for the secondary flashover fire in the basement (combined HRR of 19~MW), and 32 for the maximum prescribed fire size in the structure (combined HRR of 20~MW).
@@
 A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells.
-As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
+As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm.
 Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.
@@
 \caption[Front and rear of the structure with a 10~cm computational mesh.]
-{Front (top) and rear (bottom) of the structure with a 10~cm computational mesh.}
+{Front (top) and rear (bottom) sides of the structure with a 10~cm computational mesh.}
 \label{fig:SMV_exterior_grid}
@@
 \caption[Top view of the simulated flow path in the interior stairwell.]
-{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure.
+{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure, 1.2~m above the floor (mid-level height).
 The arrows indicate the direction of flow.
@@
 
-Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m from the floor) on the first floor at a time of 2~s before the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor at a time of 2~s before the first rear basement window failed.
 At this time, the temperature of the gases in the interior stairwell exceeded 200~$^{\circ}$C (400~$^{\circ}$F).
@@
 \caption[Simulated temperature contours on the first floor before basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 2~s before the first rear basement window failure.}
+{Top view of simulated temperature contours on the first floor, 1.2~m above the floor (mid-level height), 2~s before the first rear basement window failure.}
 \label{fig:smv_flow_path_top_1}
@@
 
-Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m from the floor) on the first floor at a time of 60~s and 120~s after the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor at a time of 60~s and 120~s after the first rear basement window failed.
 At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 \caption[Simulated temperature contours on the first floor after basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m from the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
+{Top view of simulated temperature contours on the first floor, 1.2~m above the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
 \label{fig:smv_flow_path_top_2}

### 2014-10-06 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to Section 4

@@
 FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
-As a result, the actual HRR in FDS can be different than the prescribed HRR based on the ventilation conditions.
+As a result, the prescribed HRR that was input into the simulation can be different than the HRR predicted by the simulation based on the ventilation conditions.
 
@@
 time based on the fires that were described in Section~\ref{sec:fires}.
+In this figure, the solid line represents the specified (or prescribed) HRR that was input into the simulation, and the dashed line represents the actual (or predicted) HRR that was output from the simulation based on the ventilation conditions.
 The vertical dashed line represents the time at which the first basement window on the rear side of the structure failed (342~s).
 Additional windows on the rear side of the basement continued to fail within the next two minutes.
+
 The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with observations from the actual fire scenario.
-Note that the rear window failures were manually specified in accordance with the event timeline rather than failure temperature criteria.
+Note that the rear window failures were manually specified in accordance with the event timeline rather than specifying failure temperature criteria.
 
@@
 \caption[Predicted HRR vs. time from the FDS simulation.]
-{Predicted HRR vs. time from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
+{Comparison of prescribed and predicted HRRs from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
 \label{fig:hrr_w_fds}
@@
 
-In Fig.~\ref{fig:hrr_w_fds}, the solid line represents the HRR that was prescribed in the FDS simulation, and the dashed line represents the actual HRR that was predicted by FDS based on the ventilation conditions.
+In Fig.~\ref{fig:hrr_w_fds}, the prescribed HRR that was input into the simulation is different than the HRR predicted by the simulation based on the ventilation conditions.
 From 0~s to 300~s, the predicted HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
 From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited.
-The maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay.
-The HRR decreased to approximately 2~MW as the amount of oxygen inside the structure became limited.
+At 315~s, the maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay.
+At 335~s, the HRR decreased to approximately 2~MW.
 At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurred near the ventilation openings where ambient air was available.
@@
 At 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes.
-As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW before it reached a steady-state value of approximately 20~MW.
+As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW at 385~s before it reached a steady-state value of approximately 20~MW at 465~s.
 The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.
 
-Note that the HRR in the simulation might be overpredicted due to limitations in the combustion model related to the reignition of fuel-rich gases.
-In other words, there is some combustion occurring in the simulation near the front door and second floor as the fuel-rich gases mix with fresh air and reignite, which is not consistent with on-scene and post-incident photographs.
+Note that the HRR in the simulation might be overpredicted due to limitations in the combustion model in FDS that are related to the reignition of fuel-rich gases.
+In other words, some combustion occurred in the simulation near the front door and second floor that was not consistent with on-scene and post-incident photographs because the fuel-rich gases mixed with fresh air and reignited.
+In the actual fire incident, the fuel vapors and smoke that were exiting the front of the structure were not at a high enough temperature and did not encounter an ignition source that would have resulted in reignition.
 However, for the high-hazard areas that are the focus of this study (the basement and interior stairwell), the pressures, temperatures, and velocities are representative of the hazardous flow path conditions that would have occurred in this fire incident.
@@
 Figure~\ref{fig:timeline_comparison_rear} shows a time series comparison of on-scene photographs and Smokeview snapshots of flaming combustion that occurred through the failed windows on the rear side of the structure.
-In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows failed).
+In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows had failed).
 Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.
@@
 {Comparison of on-scene photographs and Smokeview snapshots of exterior combustion occurring on the rear side of the structure.
-The on-scene time is indicated on the left photograph, and the corresponding simulation time is indicated on the right Smokeview snapshot.
+The on-scene time is indicated on the photograph (left side), and the corresponding simulation time is indicated on the Smokeview snapshot (right side).
 For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
@@
 
-As the simulated fire grew in the basement, the pressure in the basement increased and caused the hot gases to flow upwards from a region of high pressure in the basement to a region low pressure via the interior stairwell.
+As the simulated fire grew in the basement, the pressure in the basement increased and caused the hot gases to flow from a region of high pressure in the basement upwards to a region of low pressure via the interior stairwell.
 Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation.
 
-In this figure, the pressure profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
-The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
+In Fig.~\ref{fig:smv_pressure}, the pressure profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a simulation time of 340~s, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a simulation time of 343~s, which is 1~s after the first rear basement window failed.
 After the rear basement windows failed, the pressure rise in the basement ranged from a 5~Pa ($7.3 \times 10^{-4}$~psi) over-pressure at mid-level height to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
@@
 \caption[Simulated pressure contours on the right interior side of the structure.]
-{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) first rear basement window failure.
+{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) the first rear basement window failed.
 The fire originated in the living room in the basement.}
@@
 
-Gases at an elevated pressure will flow towards a region of lower pressure.
-Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed into the interior stairwell towards the low pressure regions in the house and exhausted via the garage door and front door.
+Gases will always flow from a region of high pressure towards a region of lower pressure.
+Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed into the interior stairwell towards the lower pressure regions in the house and exited the structure via the garage door and front door.
 The velocity contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.
 
-In this figure, the velocity profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
-The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
+In Fig.~\ref{fig:smv_velocity}, the velocity profile within the high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a simulation time of 340~s, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a simulation time of 402~s, which is 60~s after the first rear basement window failed.
 
@@
 \caption[Simulated velocity contours on the right interior side of the structure.]
-{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
+{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_velocity}
@@
 \caption[Simulated velocity vectors on the right interior side of the structure.]
-{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
+{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_velocity_vectors}
@@
 
-Analysis of the temperatures from the simulation focuses on the high-hazard areas of the structure: the basement and the interior stairwell which connects the basement to the exhaust vents/doors on the front side of the structure (the front door and the garage door).
+Analysis of the temperatures from the simulation focuses on the high-hazard areas of the structure: the basement, and the interior stairwell that connects the basement to the front door and garage door on the front side of the structure.
 The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.
 
-In this figure, The temperature profile at these high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
-The first snapshot is shown at a time of 340~s into the simulation, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a time of 402~s into the simulation, which is 60~s after the first rear basement window failed.
+In Fig.~\ref{fig:smv_temperature}, the temperature profile at these high-hazard areas is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a simulation time of 340~s, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a simulation time of 402~s, which is 60~s after the first rear basement window failed.
 
@@
 \caption[Simulated temperature contours on the right interior side of the structure.]
-{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
+{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_temperature}
@@
 \caption[Simulated temperature vectors on the right interior side of the structure.]
-{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) first rear basement window failure.}
+{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_temperature_vectors}

### 2014-10-06 Studies/2011_San_Francisco/Figures/generate_figures.py

@@ -44,7 +44,7 @@ savefig('Fire_HRR.pdf')
 
 figure()
 plot(CALC['Time (s)'], HRR_CALC, 'k-', lw=2, label='Prescribed HRR')
-plot(FDS['Time'][:-4], HRR_FDS_avg[:-4], 'r--', lw=2, label='FDS Model HRR')
+plot(FDS['Time'][:-4], HRR_FDS_avg[:-4], 'r--', lw=2, label='Predicted HRR')
 plt.text(342+10, 2, 'Rear Window Failures Begin')
 axvline(342, color='k', ls='--', lw=2)
 xlim([0, 540])

### 2014-10-06 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to Sections 5 and 6

@@
 
-The results of the FDS simulations are discussed in the following two sections.
-The first section addresses the results of the simulation as they relate to the flow path and the conditions in the interior stairwell.
-The second section examines the model results and observed outcomes of the fire incident as they relate to tactics discussed in recent experimental research.
+The results of the simulations are discussed in the following sections.
+Section~\ref{sec:simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell.
+Section~\ref{sec:assessing_the_hazard} examines the model results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell.
+Section~\ref{sec:tactical_condsiderations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
 
@@
 
-The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the interior stairwell on the front side of the structure was used to determine that the fire was located in the basement.
+The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the interior stairwell on the front side of the structure was initially used by firefighters to determine that the fire was located in the basement.
 From the simulation results (Section~\ref{sec:temperature}), the conditions in the interior stairwell were initially tenable.
-After the rear basement windows failed, the simulation results indicate a high-hazard area that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F) in the stairwell near the laundry room landing area.
+After the rear basement windows failed, the simulation results indicate a high-hazard area in the stairwell near the laundry room landing area that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F).
 
@@
 The rear basement window failures resulted in a rapid change in the conditions within the flow path.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the interior stairwell.
 The two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
 
-The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases from the basement after the window failures.
-In this figure, the red arrows indicate elevated gas temperatures, and the blue arrows indicate relatively cooler gas temperatures.
-The arrow that transitions from red to blue indicates that the heated gases were cooling as they flowed away from the fire towards the front of the structure.
-The two arrows located at the door on the second floor (towards the front of the structure) indicate bi-directional flow.
-At that doorway, cool ambient air flowed towards the fire near the bottom of the door, and hot gases flowed away from the fire near the top of the door.
+The arrows shown in Fig.~\ref{fig:flow_path_top} indicate the simulated flow direction of gases on the basement floor and first floor at mid-level height, 120~s after the first rear basement window failed.
+In this figure, the dashed arrow indicates a continuation of flow from the basement towards the first floor.
+The two arrows located at the door and windows on the basement floor (towards the rear of the structure) indicate bi-directional flow at a vent opening.
+At the basement door and windows, cool ambient air flowed towards the fire near the bottom of the openings, and hot gases and smoke flowed away from the fire near the top of the openings.
 
@@
 \caption[Top view of the simulated flow path in the interior stairwell.]
-{Top view of the simulated flow path on the first floor and basement floor 120~s after the first rear basement window failure, 1.2~m above the floor (mid-level height).
+{Top view of the simulated flow path on the first floor and basement floor at mid-level height, 120~s after the first rear basement window failure.
 The arrows indicate the direction of flow.
+The dashed arrow indicates a continuation of flow from the basement towards the first floor.
 Two arrows located at a door or window indicate bi-directional flow at a vent opening.
-The dashed arrow indicates a continuation of flow from the basement towards the first floor.
 The velocity contours use the same scale as Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors} with a range of 0~m/s to 9~m/s (0~mph to 20~mph).}
@@
 Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
-Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
+Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
 Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}.
@@
 
-Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor at a time of 2~s before the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor, 2~s before the first rear basement window failed.
 At this time, the temperature of the gases in the interior stairwell exceeded 200~$^{\circ}$C (400~$^{\circ}$F).
@@
 
-Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor at a time of 60~s and 120~s after the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor, 60~s and 120~s after the first rear basement window failed.
 At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 The conditions in the interior stairwell changed from tenable to high-hazard very rapidly following the rear basement window failure.
-Within the structure, the exhaust gases in the flow path were moving towards the doors located on the front side of the structure via the interior stairwell.
-These simulated temperatures are consistent with the post-incident conditions that were documented in the interior stairwell.
+Within the structure, the hot gases and smoke were moving  along the flow path from the basement towards the doors located on the front side of the structure via the interior stairwell.
+The simulated temperatures are consistent with the post-incident conditions that were documented in the interior stairwell.
 
@@
 A 360$^\circ$ scene size-up by the arriving firefighters could have helped determine the location of the fire in the basement and identify potential flow paths within the structure.
-The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
-Firefighters should avoid placing themselves within a flow path, where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
-
-The timing of the interior attack in the basement occurred after delays in forcible entry operations on the exterior basement door.
-Suppression operations should be coordinated with interior operations to reduce thermal hazards related to flow paths within a structure.
-Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
+The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure and vent openings at the front of the structure.
+Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
+
+The timing of the interior attack in the basement occurred after delays in the forcible entry operations on the exterior basement door.
+Fire suppression efforts should be coordinated with interior operations and ventilation procedures to reduce thermal hazards related to flow paths within a structure.
+Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrated that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
 
@@
 Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.
-Uncoordinated ventilation can also be the cause of increased thermal hazards within a flow path.
+Uncoordinated ventilation procedures can also be the cause of increased thermal hazards within a flow path.
 
@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+In the interior stairwell, the flow velocities were approximately 9~m/s (20 mph) and the temperature of the gases was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 
@@
 The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}.
-Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating the drawings of the structure.
+Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.
 

### 2014-10-06 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits

@@
 On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure.
-Based on these sources of information, the FDS model included three source fires: 1)~an initial couch fire in the basement, 2)~a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the balcony located on the rear exterior side of the basement.
+Based on these sources of information, the simulation included three source fires: 1)~an initial couch fire in the basement, 2)~a flashover fire that involved additional furniture items in the basement, and 3) a fire that occurred on the balcony located on the rear exterior side of the basement.
 
@@
 
-The HRRs for the three primary source fires were prescribed in FDS as follows.
+The HRRs for the three primary source fires were prescribed in the simulation as follows.
 
@@
 \footnotesize
-\\ For specific information regarding ventilation areas used in the FDS model, refer to Table~\ref{tab:ventilation_timeline}.
+\\ For specific information regarding ventilation areas used in the simulation, refer to Table~\ref{tab:ventilation_timeline}.
 \normalsize

### 2014-10-06 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL_Emissions: rename directory

--- 2014-10-06 Projects/ECS_Testing/Report/ECS_Testing.tex
@@
   pdftitle={Design Fires for Emission Control System Commissioning},
-  pdfauthor={Weinschenk, Craig G and Bundy, Matt}, 
+  pdfauthor={Weinschenk, Craig G and Bundy, Matthew}, 
   pdfsubject={} 
@@
 Craig G. Weinschenk \\
-Matt Bundy \\
+Matthew Bundy \\
 {\em Fire Research Division \\
@@
 \label{tab:fires}
-\vskip.5\baselineskip
 \begin{tabular}{ccccc}
-\hline \hline
+\toprule[1.5pt]
 Test ID & Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
-\hline \hline
+\midrule
 1-3  & Natural Gas  & 2-8   & 60  & Temperature  \\
@@
 7  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 4 \\
-\hline
-\end{tabular}
+\bottomrule[1.25pt]
+\end{tabular}\par
 \end{table}
@@
 \label{tab:ng_flow}
-\vskip.5\baselineskip
 \begin{tabular}{cc}
-\hline \hline
+\toprule[1.5pt]
 Fire Size (MW) & Flow Rate (kg/s)  \\
-\hline \hline
+\midrule
 2  &  0.04 \\
@@
 8  &  0.16 \\
-\hline
-\end{tabular}
+\bottomrule[1.25pt]
+\end{tabular}\par
 \end{table}
@@
 Since each crib contains 3.63 kg of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65 kg (10.2 lb).
-Based on an estimated {\bf 60-70} \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is {\bf 1.4-1.9} kg ({\bf 3-4} lb).
+Based on an estimated 60-70 \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is 1.4-1.9 kg (3-4 lb).
 
@@
 \label{test_procedure}
-\subsection{Test 1 Procedure}
+\section{Test 1 Procedure}
 \label{procedure1}
@@
 
-\subsection{Test 2 Procedure}
+\section{Test 2 Procedure}
 \label{procedure2}
@@
 
-\subsection{Test 3 Procedure}
+\section{Test 3 Procedure}
 \label{procedure3}
@@
 Data was recorded throughout the duration of the experiments and then time averaged.
-The  Table~\ref{tab:hcl_data} shows the results including the mean mass flow rate of HCl for tests 4 and 6 as well as from a similar test conducted in 2001.
+Table~\ref{tab:hcl_data} shows the results including the mean mass flow rate of HCl for tests 4 and 6 as well as from a similar test conducted in 2001.
 
-\begin{table}[h]
+\begin{table}[!ht]
 \centering
@@
 \label{tab:hcl_data}
-\vskip.5\baselineskip
 \begin{tabular}{cccc}
-\hline \hline
+\toprule[1.25pt]
 Measurement Quantity & Test 4 & Test 6 & 2001 Test  \\
-\hline \hline
+\midrule
 Metered Volume (dcf)           &  47.39  &  59.22  &  36.52  \\
@@
 Mass Rate (lb/hr)              &  2.96   &  3.57   &  0.86   \\
-\hline
-\end{tabular}
+\bottomrule[1.25pt]
+\end{tabular}\par
 \end{table}
 
-Table~\ref{tab:hcl_data} shows the results including particulate emissions for tests 5 and 7.
+Table~\ref{tab:part_data} shows the results including particulate emissions for tests 5 and 7.
 
-\begin{table}[h]
+\begin{table}[!ht]
 \centering
 \caption{Exhaust measurements for commodity experiments}
-\label{tab:hcl_data}
-\vskip.5\baselineskip
+\label{tab:part_data}
 \begin{tabular}{ccc}
-\hline \hline
+\toprule[1.25pt]
 Measurement Quantity & Test 5 & Test 7  \\
-\hline \hline
+\midrule
 Metered Volume (dcf)                &  40.97  &  38.28  \\
@@
 Mass Rate (lb/hr)                   &  $<$ 0.37   &  $<$ 0.40   \\
-\hline
+\bottomrule[1.25pt]
 \end{tabular}
@@
 \appendix
-\section{Schematics of the National Fire Research Lab}
+\chapter{Schematics of the National Fire Research Lab}
 \label{app:nfrl_images}
-Images to describe the layout of the existing and additional lab space.
-
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{../Figures/plan_view2}
@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
 \includegraphics[width=\textwidth]{../Figures/section_2}

### 2014-10-07 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to Assessing the Hazard section

@@
 Although firefighters wear protective gear, gear only offers a finite amount of protection.
-The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
+The polycarbonate in a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
 Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
@@
 
-\clearpage
+Ongoing research and experimental work is being conducted by NIST to gain a better understanding of convective heat transfer to firefighter personal protective equipment, including firefighting gear, helmets, self-contained breathing apparatuses, etc.
+The goal of this ongoing research is to parameterize various flow path conditions (elevated temperatures and velocities) and determine their effect on the rate of heat transfer and amount of energy storage in firefighting safety equipment.
 

### 2014-10-08 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to Section 3

@@
 Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
-Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.
 
@@
 The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
-The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the timing of the fire development, the sequence and approximate timing of ventilation openings to the outside, and weather conditions at the time of the fire.
+The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the fire development timeline, the sequence and approximate timing of ventilation openings to the outside, and weather conditions.
 
@@
 The exterior was primarily stucco with large windows on the top three stories of the rear side of the structure.
-The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft), as shown in Fig.~\ref{fig:floor_plan}.
+The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level, as shown in Fig.~\ref{fig:floor_plan}.
 The right side of the structure shared a common fire wall with another residential structure.
@@
 
-The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area with a large utility area.
-A laundry area was located on a landing on the stairs between the first floor and basement.
+The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area and a large utility area.
+A laundry area was located on a landing on the interior stairwell between the first floor and basement.
 The basement was accessible via this interior set of stairs or via an exterior door on the left side of the structure.
@@
 Fully dimensioned drawings of the second floor, first floor, and basement are shown in Figs.~\ref{fig:drawing_second_floor}, \ref{fig:drawing_first_floor} and \ref{fig:drawing_basement}, respectively.
+
+\clearpage
 
@@
 
-As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a total height of 5.9~m (19~ft).
+As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level.
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.

### 2014-10-08 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to content and figures in Assessing the Hazard section

@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
@@
 
-Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor, 2~s before the first rear basement window failed.
-At this time, the temperature of the gases in the interior stairwell exceeded 200~$^{\circ}$C (400~$^{\circ}$F).
+Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours at a height of 0.3~m (1~ft) above the floor on the first floor, 2~s before the first rear basement window failed.
+At this time, the temperature of the gases in the interior stairwell were in excess of 200~$^{\circ}$C (400~$^{\circ}$F).
 
@@
 \caption[Simulated temperature contours on the first floor before basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m above the floor (mid-level height), 2~s before the first rear basement window failure.}
+{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure.
+The orange markers indicate the locations of the downed firefighters.}
 \label{fig:smv_flow_path_top_1}
@@
 
-Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours (at a height of 1.2~m above the floor) on the first floor, 60~s and 120~s after the first rear basement window failed.
-At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours at a height of 0.3~m (1~ft) above the floor on the first floor, 60~s and 120~s after the first rear basement window failed.
+At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell were in excess of 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 As more rear basement windows failed and provided ambient air to the growing basement fire, the temperatures in the interior stairwell continued to rise.
-At a time of 120~s after the first rear basement window failed, the temperature of the gases in the interior stairwell exceeded 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+At a time of 120~s after the first rear basement window failed, the temperature of the gases in the interior stairwell were in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), and the temperatures near the door leading from the interior stairwell into the first floor hallway were in excess of 200~$^{\circ}$C (400~$^{\circ}$F) at a height of 0.3~m (1~ft) above the floor.
 
@@
 \caption[Simulated temperature contours on the first floor after basement window failure.]
-{Top view of simulated temperature contours on the first floor, 1.2~m above the floor (mid-level height), 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
+{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
 \label{fig:smv_flow_path_top_2}
@@
 
-Based on these results and the simulation results shown in Sections~\ref{sec:velocity} and \ref{sec:temperature}, after the rear basement windows failed, the simulated flow path temperatures in the interior stairwell were in excess of 760~$^{\circ}$C (1400~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20 mph).
+Based on these results and the simulation results shown in Sections~\ref{sec:velocity} and \ref{sec:temperature}, after the rear basement windows failed, the simulated flow path temperatures in the interior stairwell were in excess of 700~$^{\circ}$C (1300~$^{\circ}$F) and the flow velocities were approximately 9~m/s (20~mph).
 The conditions in the interior stairwell changed from tenable to high-hazard very rapidly following the rear basement window failure.
@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-In the interior stairwell, the flow velocities were approximately 9~m/s (20 mph) and the temperature of the gases was estimated to be in excess of 760~$^{\circ}$C (1400~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+In the interior stairwell, the flow velocities were approximately 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
 

### 2014-10-08 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits
San Francisco: Edits based on comments from division reviewer

@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
-Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
-After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
-The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.},
+The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
+Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.},
   pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
-Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
-After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
-The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
+Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.
 
@@
 On June 2, 2011, a fire in a multi-level, wood-frame residential structure claimed the life of two firefighters of the San Francisco Fire Department.
-NIST examined the fire dynamics of this incident at the request of NIOSH and the San Francisco Fire Department.
+NIST examined the fire dynamics of this incident at the request of the National Institute for Occupational Safety and Health (NIOSH) and the San Francisco Fire Department.
 Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
@@
 \begin{enumerate}
-\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-level residential structure using physics-based calculations.
+\item To examine the effect of fire-induced flow paths (including temperature, pressure, and fire conditions) in this multi-level residential structure using physics-based calculations.
 \item To provide visualizations of the fire behavior that are representative of the conditions that members of the San Francisco Fire Department likely experienced during the course of their interior operations.
@@
 
-The account of events for this incident was documented by the National Institute for Occupational Safety and Health (NIOSH) Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
+The account of events for this incident was documented by NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
@@
 
+\clearpage
+
 The analysis of the simulation results is focused on the interior conditions on the first floor where the downed firefighters were located and the conditions that resulted in the establishment of a flow path in the interior stairwell leading into the basement.
-Based on the goals of the analysis and the information collected, several engineering approximations were made.
+Based on the goals of the analysis and the information collected, several assumptions were made.
 For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known but were estimated using documentation of the potential fuel load within the structure.
-
-In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
-Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
-For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
-Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
-Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
-The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
 
@@
 
-The structure involved in this fire incident was a four-story residential building with a flat roof that consisted of a bitumen membrane.
+The structure involved in this fire incident was a four-story residential building with a flat roof.
 The exterior was primarily stucco with large windows on the top three stories of the rear side of the structure.
-The structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level, as shown in Fig.~\ref{fig:floor_plan}.
+The structure had exterior dimensions of 8.5~m (28~ft) by 17.7~m (58~ft) and a height of 5.9~m (19~ft) above street level, as shown in Fig.~\ref{fig:floor_plan}.
 The right side of the structure shared a common fire wall with another residential structure.
@@
 Note that the majority of the exterior damage occurred above the openings located on the basement floor (where the wooden balcony was located).
-Fully dimensioned drawings of the second floor, first floor, and basement are shown in Figs.~\ref{fig:drawing_second_floor}, \ref{fig:drawing_first_floor} and \ref{fig:drawing_basement}, respectively.
+Fully dimensioned drawings of the second floor, first floor, and basement are shown in Appendix~\ref{sec:drawings}.
 
@@
 The fire originated in the living room on the basement floor.
-Stairs and rooms are identified using information collected by NIST.}
+Stairs and rooms are identified using information collected by NIST.
+The sub-basement level was not connected to the other three levels of the house and is not shown.}
 \label{fig:floor_plan}
@@
 
-The basement primarily contained upholstered polyurethane furniture fuel items, and the balcony was constructed of wood.
+The basement primarily contained large upholstered polyurethane furniture items, and the balcony was constructed of wood.
 The HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
@@
 A balanced chemical reaction for polyurethane combustion can be written as:
-
 \begin{multline}
@@
 A balanced chemical reaction for wood combustion can be written as:
-
 \begin{multline}
@@
 \end{multline}
-
 The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
@@
 FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
-The following lines define the fire surfaces for each fuel package in the FDS input file:
-
-\begin{lstlisting}
-&SURF ID='COUCH_RIGHT_INITIAL',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_RIGHT_INITIAL_RAMP' /
-
-&SURF ID='COUCH_MIDDLE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 1.037172E-5,
-    RAMP_MF='COUCH_MIDDLE_FLASHOVER_RAMP' /
-
-&SURF ID='COUCH_LEFT_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 5.271815E-6,
-    RAMP_MF='COUCH_LEFT_FLASHOVER_RAMP' /
-
-&SURF ID='LOUNGE_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.853485E-6,
-    RAMP_MF='LOUNGE_FLASHOVER_RAMP' /
-
-&SURF ID='CHAIR_FLASHOVER',
-    SPEC_ID='POLYURETHANE',
-    MASS_FLUX = 7.918660E-6,
-    RAMP_MF='CHAIR_FLASHOVER_RAMP' /
-
-&SURF ID='WOOD_EXTERIOR',
-    SPEC_ID='WOOD',
-    MASS_FLUX = 0.003049,
-    RAMP_MF='WOOD_EXTERIOR_RAMP' /
-\end{lstlisting}
-
-Note that the mass flux values here are unique for each fuel item and are specific to the input file used for these simulations.
-The key point is that each fuel item was modeled as a 3D object with surfaces from which a specified amount of fuel flows into the domain, mixes with air, and burns.
-
-\clearpage
+Each fuel item was modeled as a 3D object with surfaces from which a specified amount of fuel flows into the domain, mixes with air, and burns.
+
+In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
 
@@
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
-The following lines define the gypsum material and surface properties in the FDS input file:
-
-\begin{lstlisting}
-&MATL ID          = 'GYPSUM'
-    FYI           = 'Wakili - Journal of Fire Sciences 2007' 
-    CONDUCTIVITY  = 0.28
-    SPECIFIC_HEAT = 1.00
-    DENSITY       = 810. /
-
-&SURF ID      = 'WALL'
-    DEFAULT   = .TRUE.
-    COLOR     = 'DARK SEA GREEN 4'
-    MATL_ID   = 'GYPSUM'
-    THICKNESS = 0.012 /
-\end{lstlisting}
+Table~\ref{tab:model_parameters} shows the material properties of the gypsum board that were used in the simulation.
+
+\clearpage
 
@@
 
+\clearpage
+
 \section{Numerical Mesh}
@@
 Therefore, the grid resolution used in this model results in a $D^*/\dx$ ratio that exceeds typical engineering values.
-
-As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.53~m (28~ft) by 17.73~m (58~ft) and a height of 5.9~m (19~ft) above street level.
+Note that Eq.~\ref{eq:mesh} relates to gas-phase phenomena, which is the primary concern of this study because the fires were explicitly specified instead of attempting to predict the amount of pyrolysis or flame spread in the scenario.
+
+As discussed in Section~\ref{sec:geometry}, the structure had exterior dimensions of 8.5~m (28~ft) by 17.7~m (58~ft) and a height of 5.9~m (19~ft) above street level.
 To ensure adequately resolved fluid flow in and out of the structure, the computational domain was extended beyond the volume of the structure.
@@
 
-In an FDS simulation, a prescribed HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
+In an FDS simulation, a HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
 FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
@@
 time based on the fires that were described in Section~\ref{sec:fires}.
-In this figure, the solid line represents the specified (or prescribed) HRR that was input into the simulation, and the dashed line represents the actual (or predicted) HRR that was output from the simulation based on the ventilation conditions.
+In this figure, the solid line represents the specified (or prescribed) HRR that was input into the simulation, and the dashed line represents the predicted HRR that was output from the simulation based on the ventilation conditions.
 The vertical dashed line represents the time at which the first basement window on the rear side of the structure failed (342~s).
@@
 Gases will always flow from a region of high pressure towards a region of lower pressure.
-Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed into the interior stairwell towards the lower pressure regions in the house and exited the structure via the garage door and front door.
+Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed upward into the interior stairwell and exited the structure via the garage door and front door.
 The velocity contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.
@@
 After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the interior stairwell.
-The two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+The two firefighters were located in the flow path between the basement and the doors on the front side of the structure.
 
@@
 
-After the primary search was conducted, closing the interior doors (i.e., door control) could have inhibited the establishment of a flow path in the interior stairwell.
-A 360$^\circ$ scene size-up by the arriving firefighters could have helped determine the location of the fire in the basement and identify potential flow paths within the structure.
+A 360$^\circ$ scene size-up by arriving firefighters can help determine the location of the fire and identify potential flow paths within a structure.
 The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure and vent openings at the front of the structure.
 Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
+Door control can also be used to avoid creating inlet and outlet vents that could result in the establishment of a flow path.
 
@@
 
-Unfortunately, two E26 firefighters were located in the flow path between the basement and the doors on the front side of the structure.
-After a Mayday call, both firefighters were removed from the structure and immediate medical treatment was provided.
+Two firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+After a call for assistance, both firefighters were removed from the structure and immediate medical treatment was provided.
 The two firefighters were transported to the local medical center where the lieutenant was pronounced dead and the fire fighter/paramedic died two days later.
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Drawing_Second_Floor_Metric}
+\begin{sidewaysfigure}[!ht]
+\includegraphics[width=8in]{../Figures/Drawing_Second_Floor_Metric}
 \caption[Dimensioned drawing of the second floor.]
@@
 \label{fig:drawing_second_floor}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Drawing_First_Floor_Metric}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}[!ht]
+\includegraphics[width=8in]{../Figures/Drawing_First_Floor_Metric}
 \caption[Dimensioned drawing of the first floor.]
@@
 \label{fig:drawing_first_floor}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Drawing_Basement_Metric}
+\end{sidewaysfigure}
+
+\begin{sidewaysfigure}[!ht]
+\includegraphics[width=8in]{../Figures/Drawing_Basement_Metric}
 \caption[Dimensioned drawing of the basement floor.]
@@
 \label{fig:drawing_basement}
-\end{figure}
+\end{sidewaysfigure}
 

### 2014-10-08 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edit

@@
 
-The account of events for this incident was documented by NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
+The account of events for this incident was documented in NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.

### 2014-10-09 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: More edits based on reviewer comments

@@
   pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
-The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
@@
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
-The inputs for the FDS simulations are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
@@
 NIST examined the fire dynamics of this incident at the request of the National Institute for Occupational Safety and Health (NIOSH) and the San Francisco Fire Department.
-Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
-The specific objectives of the simulations detailed in this report are:
+A computer simulation of the fire incident was conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
+The specific objectives of the simulation detailed in this report are:
 \begin{enumerate}
@@
 \end{enumerate}
-This document describes the input and the results of the FDS (version 6.1.2) simulations.
-The simulations were developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
+This document describes the input and the results of the FDS (version 6.1.2) simulation.
+The simulation was developed using a combination of knowledge of the fire scenario and appropriate engineering approximations and assumptions.
 Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
-This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{sec:model_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
+This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulation, Section~\ref{sec:model_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
 Appendix~\ref{sec:drawings} contains dimensioned drawings of the basement, first, and second floors of the structure.
@@
 
-The basement primarily contained large upholstered polyurethane furniture items, and the balcony was constructed of wood.
-The HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
+The basement primarily contained upholstered polyurethane furniture, and the balcony was constructed of wood.
+The upholstered furniture items located in the middle of the basement living room were very large and flat, similar to the size and geometry of a mattress.
+Therefore, the HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
 The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
@@
 
-In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
-Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
-For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
-Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
-Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
-The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
-
 \section{Materials}
@@
 Table~\ref{tab:model_parameters} shows the material properties of the gypsum board that were used in the simulation.
-
-\clearpage
 
@@
 
-\clearpage
-
 \section{Numerical Mesh}
@@
 A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells.
-As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm.
-Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm mesh.
+As a result, all of the obstructions, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm.
+Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm grid cells.
 
@@
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 \end{figure}
+
+\clearpage
+
+\section{Summary of Model Input Parameters}
+\label{sec:summary_of_model_inputs}
+
+Table~\ref{tab:model_parameters} shows a summary of the model input parameters for the simulation that was conducted as part of this study.
+In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario results in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
 
@@
 
-To examine the results of the simulations, it is important to link the timelines from the fire scene to the simulation times.
+To examine the results of the simulation, it is important to link the timelines from the fire scene to the simulation times.
 Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{NIOSH:Bowyer2} along with the corresponding simulation times.
@@
 
-The results of the simulations are discussed in the following sections.
+The results of the simulation are discussed in the following sections.
 Section~\ref{sec:simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell.
@@
 NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
-The fuel, fire size, and fire growth rate that were used in the FDS simulations were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.
+The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.
 This resulted in a maximum specified source fire of approximately 20~MW in the basement and rear balcony of the structure.

### 2014-10-09 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update acknowlegment

@@
 The authors would like to thank XXXX.
-The authors would also like to thank John Culbertson of Central Valley Fire District, MT, for his assistance in compiling Table~\ref{tab:LODD}.
+The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in compiling Table~\ref{tab:LODD}.
 Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.

### 2014-10-09 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report and figures

@@
 
-In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
-Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
-For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
-Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
-Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
-The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
-
 \section{Geometry}
@@
 The structure involved in this fire incident was a one story, single-family structure with a basement.
-Due to the surrounding topography (the ground slopes from the front to rear of the structure), the basement on the rear side of the structure was above grade.
-The structure was wood-framed platform-framed with a gable roof.
+The structure was platform-framed wood construction with a gable roof.
 \footnote{Platform-framed construction means that floor joists are completely covered with a sub-floor.
 This forms a platform for which walls are built from.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}.
-This results in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
-The interior walls and ceiling were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{PGCounty2013}.
+This resulted in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
+The interior walls were composed of gypsum board over insulated wood framing.~\cite{PGCounty2013}.
 There was a single flight of stairs in the center of the structure which connected the first floor to the basement.
-Access to the structure could be made on the front side of the first floor and the rear side of the basement.
+
+The structure was built on a sloped landscape such that on the front side of the structure the first floor was located above street level but the basement was below street level (Fig.~\ref{fig:slope}).
+On the rear side of the structure, the slope allowed the basement to be a walkout.
+Therefore, access to the structure could be made on the front side of the first floor and the rear side of the basement.
+
+\begin{figure}[!ht]
+\includegraphics[width=.7\textwidth]{../Figures/PGCo_Slope} \\
+\caption[Photograph of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure.}
+\label{fig:slope}
+\end{figure}
 
@@
 \begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \includegraphics[width=.7\textwidth]{../Figures/Basement} \\
+\vspace{0.2in}
 \includegraphics[width=.7\textwidth]{../Figures/First_Floor}
-\end{tabular*}
 \caption[Plan view of basement (top) and first (bottom) floor of structure.]{Plan view of basement (top) and first (bottom) floor of structure.
@@
 \begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
 \includegraphics[width=5in]{../Figures/PGCo_Front} \\ 
+\vspace{0.1in}
 \includegraphics[width=5in]{../Figures/PGCo_Rear}
-\end{tabular*}
 \caption{Photographs showing the front (top) and rear (bottom) exterior of the structure after the incident.}
@@
 \label{fire}
+
+On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure.
+
+In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
 
@@
 The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors, breaking windows), fire acting on the structure (fire breaching windows/doors) and wind (restricting flow, closing doors).
-Three ventilation scenarios were considered in this study.
-Each scenario followed the timeline of events outlined in Table~\ref{tab:vents}.
-The difference in each scenario is the wind boundary condition.
-Simulations were run at 0~m/s (0~mph), 4.47~m/s (10~mph), and 8.94~m/s (20~mph) wind velocities with a flow direction from the rear toward the front of the structure.
-Based on local weather conditions, mean wind velocities ranged between 4.47~m/s (10~mph) and 8.94~m/s (20~mph).
-The case without wind was run to control for the impact of wind on the flow of hot gases within the structure.
+The ventilation times and ventilation areas represent our best understanding of the incident.
+The times of ventilation changes for doors and windows are provided in Table~\ref{tab:vents}.
+
+During the time at which the firefighters exited the structure or were rescued from the structure, the state of some windows and doors in the structure was known.
+The state of the vents (opened versus closed) resulted in the establishment of a flow path in the interior stairwell leading from the basement to the first floor.
+However, the exact time of operation for other doors/windows was not known.
+Therefore, the following doors were assumed to be open at the start of the simulation: 1) the basement door, and 2) the basement windows on the left rear corner of the structure.
+The states of the front door and front window were specified at certain times based on observations (i.e.
+forcible entry, wind effects, forced window breakage) from post-incident reports.
 
@@
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
+
+In addition to the state of openings within the structure, three wind scenarios were considered in this study.
+Each scenario followed the timeline of events outlined in Table~\ref{tab:vents}.
+The difference in each scenario is the wind boundary condition.
+Simulations were run with 0~m/s (0~mph), 4.5~m/s (10~mph), and 8.9~m/s (20~mph) wind velocities, all with a flow direction from the rear toward the front of the structure.
+Based on local weather conditions, mean wind velocities ranged between 4.5~m/s (10~mph) and 8.9~m/s (20~mph) with gusts up to 13.4~m/s (30~mph)~\cite{PGCounty2013}.
+The case without wind was run to control for the impact of wind on the flow of hot gases within the structure.
 
@@
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 12 for the 1.5~MW bathroom fire and 20 for the 6.75~MW basement fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm (3.9~in), the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 12 for the 1.5~MW bathroom fire and 20 for the 6.75~MW basement fire.
 Based on validation work performed for the U.S.
@@
 To sufficiently resolve the wind boundary condtion, the computational domain was extended beyond the volume of the structure.
-The large domain led to the use of two separate grid resolutions, a 10~cm resolution and a 20~cm resolution.
-The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (40ft) by 8~m (26~ft) that required 1.8 million computational cells.
+The large domain led to the use of two separate grid resolutions, a 10~cm (3.9~in) resolution and a 20~cm (7.8~in) resolution.
+The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (40ft) by 8~m (26~ft) that required a total of 1.8 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
 
-Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+Figure~\ref{fig:geom_grid} shows the front of the structure and surrounding domain rendered in Smokeview with the 10~cm  and 20~cm meshes.
 The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.

### 2014-10-10 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add photo credits

@@
 \caption[Front and rear exterior of the structure after the incident.]
-{Front (top) and rear (bottom) exterior sides of the structure after the incident.}
+{Front (top) and rear (bottom) exterior sides of the structure after the incident. Photographs courtesy of the San Francisco Fire Department.}
 \label{fig:post_exterior}
@@
 \begin{figure}[!ht]
-\includegraphics[height=8.0in]{../Figures/Timeline_Comparison}
+\includegraphics[height=7.8in]{../Figures/Timeline_Comparison}
 \caption[Snapshots of exterior combustion occurring on the rear side of the structure.]
@@
 The on-scene time is indicated on the photograph (left side), and the corresponding simulation time is indicated on the Smokeview snapshot (right side).
-For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
+For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.
+Photographs courtesy of the San Francisco Fire Department.}
 \label{fig:timeline_comparison_rear}
@@
 The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom).
-For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.}
+For more information on the fire incident and simulation timeline, refer to Table~\ref{tab:combined_timeline}.
+Photograph courtesy of the San Francisco Fire Department.}
 \label{fig:timeline_comparison_front}

### 2014-10-16 Projects/NFRL_Emissions/Report/ECS_Testing.tex
Reports: Update formatting of frontmatter for new template

@@
 \begingroup
+This publication is available free of charge from:
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
 \endgroup
@@
 \begingroup
+This publication is available free of charge from:
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup
@@
 Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
-CODEN: NTNOEF }
+CODEN: NTNOEF}
+
+\begingroup
+\hypersetup{urlcolor=black}
+This publication is available free of charge from:
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
 

### 2014-10-16 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
Spartanburg 2014: Test Descriptions (ongoing)
Reports: Update formatting of frontmatter for new template

@@
 Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
-CODEN: NTNOEF }
+CODEN: NTNOEF}
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
 
@@
 \section{489 N. Forest}
+
+The next set of experiments were conducted in a two story residential structure addressed as 489 North Forest Street.
+The structure consisted of type 5 construction.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
 

### 2014-10-16 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
Reports: Update formatting of frontmatter for new template

@@
 \hypersetup{urlcolor=black}
+This publication is available free of charge from:
 \href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
@@
 Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
-CODEN: NTNOEF }
+CODEN: NTNOEF}
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
 

### 2014-10-16 Studies/2013_PG_County/Report/PG_Co_Fire.tex
Reports: Update formatting of frontmatter for new template

@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup

### 2014-10-16 Studies/2013_PG_County/Report/PG_Co_Fire.tex
Reports: Additional minor edits

@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
 \endgroup
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup

### 2014-10-16 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Report File and Bib File added

\documentclass[12pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../../Bibliography/commoncommands}

% Rename chapter headings
\renewcommand{\chaptername}{Section}
\renewcommand{\bibname}{References}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

% Center all figures
\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

% Extra packages
\usepackage{xfrac}

\begin{document}

	\bibliographystyle{unsrt}
	\pagestyle{empty}

	\begin{minipage}[t][9in][s]{6.25in}

		\begin{flushright}
			\fontsize{20}{24}\selectfont
			\bf{NIST Technical Note XXXX}
		\end{flushright}

		\headerB{
			Delaware County, PA Fire Suppression Tests \\
			Spring 2012 \\
		}

		\normalsize

		\headerC{
			{
				\flushright{
					Daniel Madrzykowski \\
					Keith M. Stakes \\

					\vspace*{2\baselineskip}

					\begingroup
					\hypersetup{urlcolor=black}
					\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
					\endgroup
				}

				\vfill

				\flushright{

					\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
				}
			}
		}

	\end{minipage}

	\newpage
	\hspace{5in}
	\newpage

	\frontmatter

	\pagenumbering{roman}

	\begin{minipage}[t][9in][s]{6.25in}

		\begin{flushright}
			\fontsize{20}{24}\selectfont
			\bf{NIST Technical Note XXXX}
		\end{flushright}

		\headerB{
			Delaware County, PA Fire Suppression Tests \\
			Spring 2012 \\
		}

		\headerC{
			\flushright{
				Daniel Madrzykowski \\
				Keith M. Stakes \\
				{\em Fire Research Division \\
					Engineering Laboratory} \\

				\vspace*{2\baselineskip}

				\begingroup
				\hypersetup{urlcolor=black}
				\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
				\endgroup

				\vspace*{2\baselineskip}

				August 2014}}

		\vfill

		\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }

		\titlesigs

	\end{minipage}

	\newpage

	\begin{minipage}[t][9in][s]{6.25in}

		\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
			document in order to describe an experimental procedure or concept adequately. \\
			Such identification is not intended to imply recommendation or endorsement by the \\
			National Institute of Standards and Technology, nor is it intended to imply that the \\
			entities, materials, or equipment are necessarily the best available for the purpose. \\
		}

		\vspace{3in}

		\large
		\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
			Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
			% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
			CODEN: NTNOEF }

		\vfill

		\hspace{1in}

	\end{minipage}

	\newpage

	\frontmatter

	\pagestyle{plain}
	\pagenumbering{roman}

	\cleardoublepage
	\phantomsection
	\addcontentsline{toc}{chapter}{Contents}
	\tableofcontents

	\cleardoublepage
	\phantomsection
	\addcontentsline{toc}{chapter}{List of Figures}
	\listoffigures

	\cleardoublepage
	\phantomsection
	\addcontentsline{toc}{chapter}{List of Tables}
	\listoftables

	\chapter{List of Acronyms}

	\begin{tabbing}
		\hspace{1.5in} \= \\
		FDS \> Fire Dynamics Simulator \\
		HGL \> Hot Gas Layer \\
		HRR \> Heat Release Rate \\
		HRRPUA \> Heat Release Rate per Unit Area \\
		NIST \> National Institute of Standards and Technology \\
	\end{tabbing}

	\mainmatter

	\chapter{Abstract}
	\label{chap:Abstract}

	\chapter{Introduction}
	\label{chap:Introduction}

	\chapter{Experimental Setup}
	\label{chap:Experimental_Setup}

	\section{Experimental Facility}
	\label{sec:Experimental_Facility}

	Two identical concrete structures were built on a concrete slab as shown in Figure 1. They were designed to simulate a single floor of a residential structure.  The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.  The interior dimensions of teach structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.  The joints and gaps between the blocks were filled with high temperature insulation.

		\begin{figure}[!ht]
			\includegraphics[width=6in]{../Figures/Pictures/DelCo_Structures}
			\caption{Delaware County, PA Fire Test Structures}
			\label{fig:Delaware_County,_PA_Fire_Test_Structures}
		\end{figure}

	Each structure had burn room, approximately 6.0 m (19.6 ft) by 4.4 m (14.3 ft) and 2.74 m (9.0 ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.  The hallway is approximately 0.95 m (3.1 ft) wide and 5.4 m (17.6 ft) and the entry foyer is 1.2 m (4.1 ft) by 1.9 m (6.1 ft).  The ceiling height in the hallway and entry foyer was 2.4 m (8 ft).  The open door on north side from the exterior to the entry foyer was 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.  The opening on the south face of the structure from the exterior to the burn room was 2.4 m (7.75 ft) high and 1.09 m (3.6 ft) wide.   A schematic plan view of the structure is given in Figure     .

	The floor of the structure was a concrete pad.  The interior walls of the structure were framed with steel studs and track.  The studs were set to 0.40 m (16 in) centers.  The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.  The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in .  Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was attached to the top of the TJIs.

	The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.  The ceiling of the burn room was the exposed “floor assembly”.  The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room. The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.

	Both structures were similar and were used to run comparative experiments on a given day.

	\section{Instrumentation}
	\label{sec:Instrumentation}

	The structures were instrumented for temperature, heat flux, and gas velocity measurements.  A schematic plan view of the instrumentation arrangement is show in ????

	\subsection{Temperature}
	\label{subsec:Temperature}

	Gas temperatures in the burn room were measured with bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5 mm (0.02 in) nominal diameter.  Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..  The vertical arrays had thermocouples located 0.03, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13 m below the bottom edge of the joist, where a ceiling would be installed.

	Additional single thermocouples were installed in conjunction with the bi-directional probes at the exterior vents and in the hallway.  The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter. Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconel sheath.  
	In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.  In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.

	\subsection{Heat Flux}
	\label{subsec:Heat_Flux}

	Total heat flux was measured with Schmidt Boelter gauges.  Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.  One of each was located near the thermocouple arrays in the burn room.  The gauges were pointed at the ceiling and positioned 0.15 m (6 in) above the floor.

	In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter’s head.  One of the gauge’s sensing surface is facing the ceiling and the other gauge is facing the pallets.  A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.  Again on gauge was facing the ceiling and one was facing the burn room.

	\subsection{Gas Velocity}
	\label{subsec:Gas_Velocity}

	Gas velocity was determined utilizing differential pressure transducers connected to bidirectional velocity probes[ ] in conjunction with a temperature measurement.  These probes were co-located with the sheathed thermocouples in the north doorway, the south window opening and the hallway.  The locations are shown in ??????

	\subsection{Mass}
	\label{subsec:Mass}

	\subsection{Moisture Content}
	\label{subsec:Moisture_Content}

	\subsection{Infrared Radiation}
	\label{subsec:Infrared_Radiation}

	\section{Fuel Load: Wood Experiments}
	\label{sec:Fuel_Load:_Wood_Experiments}

	The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood “floor assembly”.
	Two stacks of pallets with hay were used as the first items ignited in each experiment.  Each stack was composed of six pallets with a half bale of hay.  The hay was layered between each pallet.  The pallets and hay were weighed prior to each experiment.  For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4 kg (511.3 lbs).  A complete listing of the mass of each pallet and hay bales is given in Appendix ????????

	The pallet stacks were located 0.3 m (1ft) away from the east and south walls of the burn room.  The pallets were 1.2 m (48 in) long, 1.0 m (40 in ) and 123 mm (4.8 in) high.  The stacks were 150 mm (6 in) apart.  One layer of 13 mm (0.5 in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
	The east and south wall of the burn room was covered with 15 mm (0.59 in) thick, sheets of plywood.  The “wood flooring assembly”, composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.  The open doorway to the burn room on the south side was covered with a 2.4 m (8 ft) tall by 1.2 m (4 ft) wide piece of medium density fiberboard paneling that was 5 mm (0.19 in) thick.  The southeast corner of the burn room with the fuel load installed is shown in Figure 3.

			\begin{figure}[!ht]
				\includegraphics[width=6in]{../Figures/Pictures/Wood_Fuel_Package}
				\caption{Photograph of Southeast corner of burn room with wood fuel load.}
				\label{fig:Wood_Fuel_Load}
			\end{figure}

	\section{Fuel Load: Furniture Experiments}
	\label{sec:Fuel_Load:_Furniture_Experiments}

		\begin{sidewaystable}[!ht]
			\centering
			\caption{Fuel masses}
			\begin{tabular}{llcc}
				\hline\noalign{\smallskip}
				Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
				\noalign{\smallskip}\hline\noalign{\smallskip}
				% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
				%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
				%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
				%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
				% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
				%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
				%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
				3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
				2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
				3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
				Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
				2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
				2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
				3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
				3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
				3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
				Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
				3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
				Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
				\noalign{\smallskip}\hline
			\end{tabular}
			\label{tab:Fuel_Masses}
		\end{sidewaystable}

	\chapter{Experiments and Results}
	\label{chap:Experiments_and_Results}

	\section{Gas Cooling}
	\label{sec:Gas_Cooling}

	\subsection{Spray Density}
	\label{subsec:Spray_Density}

	\section{Fire Suppression}
	\label{sec:Fire_Suppression}

	\subsection{Wood Fuel Package}
	\label{subsec:Wood_Fuel_Package}

	\subsection{Furniture Fuel Package}
	\label{subsec:Furniture_Fuel_Package}

	\subsection{Spray Density}
	\label{subsec:Spray_Density}

	\chapter{Discussion and Tactical Considerations}
	\label{chap:Discussion_and_Tactical_Considerations}

	\chapter{Summary}
	\label{chap:Summary}

	\chapter{References}
	\label{chap:References}

	\chapter{Appendix}
	\label{chap:Appendix}

	\clearpage

	\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}

\end{document}

### 2014-10-17 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
Reports: Additional minor edits
San Francisco: Add figures of temperature slices in garage to Assessing the Hazard section

@@
 
+The hot gases in the flow path were exiting the structure from the garage door and front door, as shown in Fig.~\ref{fig:flow_path_top}.
+From the NIOSH report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows temperature contours in the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.
+
+\begin{figure}[!ht]
+\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_340_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\includegraphics[width=4.3in]{../Figures/SMV_Garage_Temp_352_s}
+\input{../Figures/colorbar_metric_temp}
+\input{../Figures/colorbar_std_temp}
+\caption[Simulated temperature contours in the garage after basement window failure.]
+{Top view of simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
+\label{fig:smv_flow_path_garage}
+\end{figure}
+
+\clearpage
+
+In Fig.~\ref{fig:smv_flow_path_garage}, the first snapshot is shown at a simulation time of 340~s, which is 2~s before the first rear basement window failed, and the second snapshot is shown at a simulation time of 352~s, which is 10~s after the first rear basement window failed.
+Before the rear basement window failed, the temperature of the gases exiting the garage door were less than 150~$^{\circ}$C (300~$^{\circ}$F).
+After the rear basement window failed, the temperature of the gases exiting the garage door were in excess of 430~$^{\circ}$C (800~$^{\circ}$F).
+
 Ongoing research and experimental work is being conducted by NIST to gain a better understanding of convective heat transfer to firefighter personal protective equipment, including firefighting gear, helmets, self-contained breathing apparatuses, etc.
 The goal of this ongoing research is to parameterize various flow path conditions (elevated temperatures and velocities) and determine their effect on the rate of heat transfer and amount of energy storage in firefighting safety equipment.
+
+\clearpage
 

### 2014-10-17 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in caption

@@
 \caption[Simulated temperature contours in the garage after basement window failure.]
-{Top view of simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
+{Simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_flow_path_garage}

### 2014-10-17 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, input files, output data, figure, plotting script

@@
 
+\vspace{0.1in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
 \vfill
@@
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas}.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
 The objective of these studies has been to improve the safety and effectiveness of firefighters.
@@
 \begin{quote}
-Truck 809 responded from quarters, as the first due truck company, and arrived on 57$^{th}$ Avenue right behind Engine 807B.
+Truck 809 responded from quarters, as the first due truck company, and arrived on 57th Avenue right behind Engine 807B.
 When Truck 809 stopped to let Engine 807B layout, Truck 809 Can dismounted the truck and had to walk up the street as it pulled away.
@@
 21:15:51  & Lower pane of front egress window broke. \\[.25cm]
-21:15:57  & Water applied to fire at basement. \\[.25cm]
 21:16:01  & Top pane of front egress window broke. \\[.25cm]
@@
 21:16:44  & Front door opened. \\[.25cm]
+21:17:00  & Basement door opened and water applied to fire. \\[.25cm]
 21:17:15  & Truck 809 forcible entry firefighter rescued. \\[.25cm]
@@
 \begin{figure}[!ht]
-\includegraphics[width=.7\textwidth]{../Figures/PGCo_Slope} \\
-\caption[Photograph of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure.}
+\includegraphics[width=.5\textwidth]{../Figures/PGCo_Slope}
+\includegraphics[width=.5\textwidth]{../Figures/pg_county_slope} \\
+\caption[Photograph of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure (left) and Smokeview rendering of model representation of sloped landscape (right).}
 \label{fig:slope}
@@
 The state of the vents (opened versus closed) resulted in the establishment of a flow path in the interior stairwell leading from the basement to the first floor.
-However, the exact time of operation for other doors/windows was not known.
-Therefore, the following doors were assumed to be open at the start of the simulation: 1) the basement door, and 2) the basement windows on the left rear corner of the structure.
+The exact time of operation for other doors/windows was not known.
+Therefore, the following the two basement windows on the left rear corner of the structure were assumed to be open at the start of the simulation.
 The states of the front door and front window were specified at certain times based on observations (i.e.
@@
 \midrule
-0               &  1.84             &  Door        &  Opened     &  Rear  \\
 0               &  1.40             &  Window      &  Opened     &  Rear  \\
@@
 264             &  1.84             &  Door        &  Opened     &  Front  \\
+280             &  1.84             &  Door        &  Opened     &  Rear  \\
+
 \bottomrule[1.25pt]
@@
 The large domain led to the use of two separate grid resolutions, a 10~cm (3.9~in) resolution and a 20~cm (7.8~in) resolution.
-The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (40ft) by 8~m (26~ft) that required a total of 1.8 million computational cells.
+The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (39ft) by 8~m (26~ft) that required a total of 1.3 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
+The 20~cm grid resolution extends the computational domain 5~m to the left and right sides and 4~m behind the 10~cm mesh to provide sufficient computational domain for the wind profile to develop around the structure.
+The mesh is coarser to cut down on computational time and because high accuracy in the fluid mechanics of the air flow far from the structure is not important in the analysis of this simulation.
+The 20~cm resolution resulted in an additional 216,000 computational cells.
 
-Figure~\ref{fig:geom_grid} shows the front of the structure and surrounding domain rendered in Smokeview with the 10~cm  and 20~cm meshes.
-The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
+Figure~\ref{fig:geom_grid} shows the front and rear of the structure and surrounding domain rendered in Smokeview with the 10~cm and 20~cm meshes.
+Note the finer mesh (smaller cells) surrounding the structure and the coarser mesh on each side.
+The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the stucture (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells).
+Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case to 2~days for the 20~mph wind case.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 \includegraphics[width=\textwidth]{../Figures/pg_county_meshtotal}
-\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
+\caption[Overhead front-left side of the structure within the computational domain.]{Overhead front-left view of the structure within the computational domain (with multiple meshes).
 Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
@@
 \footnotesize
-$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 7~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 10~$^{\circ}$C~\cite{NIOSH:Bowyer}.
 \normalsize

### 2014-10-21 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Add TN number and bibtex entry

@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1856}
 \end{flushright}
@@
 This publication is available free of charge from:
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1856}{http://dx.doi.org/10.6028/NIST.TN.1856}
 \endgroup
@@
 This publication is available free of charge from:
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1856}{http://dx.doi.org/10.6028/NIST.TN.1856} \\
 \endgroup
@@
 
-August 2014}}
+November 2014}}
 
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1856 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1856, \pageref{LastPage} pages (November 2014) \\
 CODEN: NTNOEF}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1856}{\bf http://dx.doi.org/10.6028/NIST.TN.1856} \\
 \endgroup

### 2014-10-21 Projects/NFRL_Emissions/Report/ECS_Testing.tex
Reports: Additional minor edits; update template
NFRL ECS: update report, formatting in bib file, update figure

@@
 Craig G. Weinschenk \\
-Matt Bundy \\
+Matthew Bundy \\
 
@@
 
+\vspace{0.2in}
+
 \begingroup
+{\bf This publication is available free of charge from:}
 \hypersetup{urlcolor=black}
-This publication is available free of charge from:
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup
@@
 \hspace{1.5in} \= \\
-FDS \> Fire Dynamics Simulator \\
+ECS \> Emisssion Control System \\
 HRR \> Heat Release Rate \\
+NFRL \> National Fire Research Laboratory \\
 NIST \> National Institute of Standards and Technology \\
+PVC \> Polyvinyl Chlorine \\
 \end{tabbing}
@@
 The National Fire Research Laboratory (NFRL) is a fire test facility operated by the Engineering Laboratory at the National Institute of Standards and Technology (NIST).
-The NFRL is undergoing an expansion in order to provide additional research capabilities: test the performance of full-scale structures subjected to realistic fires and structural loading under controlled laboratory conditions, develop an experimental database on the performance of large-scale structural connections, components, sub-assemblies, and systems under realistic fire and loading, validate physics-based models to predict fire resistance performance of structures and enable performance-based standards for fire resistance design of structures and foster innovations in design and construction.
-To complete construction on the NFRL expansion, the updated emission control system needs to be tested to ensure the design specifications are achieved.
+The NFRL underwent an expansion in order to provide additional research capabilities: test the performance of full-scale structures subjected to realistic fires and structural loading under controlled laboratory conditions, develop an experimental database on the performance of large-scale structural connections, components, sub-assemblies, and systems under realistic fire and loading, validate physics-based models to predict fire resistance performance of structures and enable performance-based standards for fire resistance design of structures and foster innovations in design and construction.
+To commission the laboratory space of the NFRL expansion, the updated emission control system needed to be tested to ensure the design specifications are achieved.
 This document will describe the source fires, appropriate lab safety, and test procedures.
-The objective of the fire tests is to use specifically designed source fires to test the emission control systems of the newly constructed fire research facility addition.
-The experiments are designed to ensure the system can handle elevated temperatures (gas burner), toxic gases (wood cribs with PVC), and particulates (group A commodities).
+The objective of the fire tests was to use specifically designed source fires to test the emission control systems to ensure the system could handle elevated temperatures, toxic gases, and particulates.
 
@@
 \label{test_fire}
-The commissioning fires will take place in the pre-expansion laboratory space under a 9 m by 12 m oxygen-consumption calorimetry hood.
-The fuel packages will be centered under the hood, which is 6.4 m above the test floor.
+The commissioning fires took place in the pre-expansion laboratory space under the 9 m by 12 m oxygen-consumption calorimetry hood (cf Fig.~\ref{fig:NFRL_plan}).
+The dark shaded area in Fig.~\ref{fig:NFRL_plan} represents the laboratory expansion.
+The fuel packages were centered under the hood, which is 6.4 m above the test floor.
 A flexible curtain, in place to contain combustion products, hangs 1.5 m below the lower edge of hood.
-Fig.~(\ref{fig:NFRL_fire}) shows a 2 MW natural gas fire under the hood during an experiment prior to the lab expansion.
-Note, that in the current configuration the wall to the left of the burner has been replaced by a roll-up door.
-The roll-up door provides access to the new testing space.
+Fig.~(\ref{fig:NFRL_fire}) shows a 2 MW natural gas fire under the calorimetry hood during the initial commission testing.
+Note, that the the roll-up door behind the burner provides protection to the additional lab space when closed and access to the expansion space when opened.
 
-\begin{figure}
-\includegraphics[width=\textwidth]{../Figures/NFRL_Fire}
-\caption {Natural gas test burn in pre-construction NFRL.}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.8\textwidth]{../Figures/plan_view2}
+\caption {Plan view of the NFRL indicating location of ECS test fires.}
+\label{fig:NFRL_plan}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.6\textwidth]{../Figures/NFRL_Fire}
+\caption {Natural gas test burn in pre-expansion side of NFRL.}
 \label{fig:NFRL_fire}
@@
 
-Based on the general experimental configuration shown in Fig.~(\ref{fig:NFRL_fire}) and \ref{app:nfrl_images}, Table ~\ref{tab:fires} outlines the fire tests to be conducted.
-The duplicity of tests is that similar to the existing system, the new ECS features two trains.
-Therefore, the scrubbing system in each train needs to be tested independently.
+Overall, three different fuel packages were used to test the system's cabilitity to independently handle elevated temperatures, scrub acid gas, and trap particulates.
+Table ~\ref{tab:fires} shows the fire tests to be conducted.
+Two tests were conducted with each fuel package to ensure that each train within the new ECS was independently tested.
+For the gas burner tests, three tests were conducted; one for each of the the trains and one with both trains running together to test heat release rates larger than 5~MW.
 
@@
 \label{tab:fires}
-\begin{tabular}{ccccc}
+\begin{tabular}{lccl}
 \toprule[1.5pt]
-Test ID & Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
+Fuel & Peak HRR (MW) & Burn Time (min) & Test Goal  \\
 \midrule
-1-3  & Natural Gas  & 2-8   & 60  & Temperature  \\
-4  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 3 \\
-5  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 3 \\
-6  & Wood w/ PVC  & $\approx$ 1.5-2 & $\approx$ 50  & Acid, Train 4 \\
-7  & Group A Comm. & $\approx$ 3 & $\approx$ 20  & Soot, Train 4 \\
+Natural Gas   & 2-8             & 60            & Temperature  \\
+Wood w/ PVC   & $\approx$ 1.5-2 & $\approx$ 50  & Acid Gases \\
+Group A Comm. & $\approx$ 3     & $\approx$ 20  & Soot \\
 \bottomrule[1.25pt]
@@
 \label{test1}
-A natural gas burner is a very clean and well controlled source fire (generating CO$_2$ and H$_2$O products).
-The objective of this test is to challenge the system for hot gases using a controllable and well quantified fire.
-This is not designed to test scrubbing capabilities, but to prove the system can achieve the required temperature set points.
-It is critical to ensure the scrubber is working properly before pollutants are introduced.
-The natural gas burner is 1.61 m by 1.19 m by 0.88 m and is capable of delivering a fire up to 8 MW (cf.
+A natural gas burner is a clean burning and well controlled source fire (predominately generating CO$_2$ and H$_2$O products).
+The objective of this test was to challenge the system for hot gases using a controllable and quantifiable fire.
+This was not designed to test scrubbing capabilities, but to prove the system can achieve the required temperature set points without failure.
+It was critical to ensure the scrubber is functional before pollutants are introduced to test its performance.
+The natural gas burner used was 1.61 m by 1.19 m by 0.88 m and was capable of delivering a fire up to 8~MW (cf.
 Fig.~(\ref{fig:nat_gas_burn})).
@@
 The required mass flow of natural gas ($\dot{m}_{NG}$) needed to produce a desired fire size ($HRR_{NG}$) is
-\begin{equation}
+\begin{equation}\label{eq:mass_ng}
 \dot{m}_{\mathrm{NG}} = HRR_{NG}/h_{c_{NG}}
@@
 where $h_{c_{NG}}$ is the heat of combustion of natural gas.
-For complete combustion, the heat of combustion of natural gas is 50203 kJ/kg.
-Based on calculations included in \ref{app:gas_burn}, the required mass flow rate of natural gas for range of fire sizes is shown in Table~\ref{tab:ng_flow}.
-While the peak deliverable HRR is 8 MW, radiation from the fire to the surrounding environment at this magnitude is too significant for a 60 minute commissioning test.
-To test each train, a 4 MW fire will be used.
-To test that both trains can properly work together, an 8 MW fire will be used for a short duration, approximately 5 minutes.
+For complete combustion, the heat of combustion of natural gas is 50203~kJ/kg.
+Using Eq.~(\ref{eq:mass_ng}), the required mass flow rate of natural gas for range of fire sizes is shown in Table~\ref{tab:ng_flow}.
+While the peak deliverable HRR is 8~MW, radiation from the fire that size to the surrounding environment would be too significant for a 60 min.
+commissioning test without add additional fire protection to the structure.
+To test each train, a fire with a peak 4~MW HRR was used.
+To test that both trains can properly work together, an 8 MW fire was used for duration of less than 5~min.
 
@@
 \label{test2}
-To challenge the acid scrubbing capability of the system, pinewood cribs loaded with polyvinyl chloride (PVC) are used.
-This package is designed to deliver a controlled source of hydrochloric acid (HCl) gas that is close to the design capacity of the emission control system.
-Four pinewood cribs measuring 0.56 m by 0.56 m by 0.38 m will be used (cf.
-Fig.~(\ref{fig:wood_crib})).
-Each crib consists of 10 layers composed of 0.56 m by 0.04 m by 0.04 m pinewood sticks spaced 0.02 m apart.
-Eight 0.45 kg PVC sticks are distributed throughout each crib (cf.
-Fig.~(\ref{fig:wood_crib})) which brings the total mass of each crib to be 34 kg.
-The moisture content of the cribs should be between 6-8 \% using a commercial moisture detector.
-This fuel package is based on the wood crib tests from the 2001 commissioning tests.
+To challenge the acid scrubbing capability of the system, pinewood cribs loaded with polyvinyl chloride (PVC) were used.
+This package was designed to deliver a controlled source of hydrochloric acid (HCl) gas that was close to the design capacity of the emission control system.
+Four pinewood cribs measuring 0.56~m by 0.56~m by 0.38~m were be used (cf.
+Fig.~\ref{fig:wood_crib}).
+Each crib consisted of 10 layers composed of 0.56~m by 0.04~m by 0.04~m pinewood sticks spaced 0.02~m apart.
+Eight 0.45~kg PVC sticks were distributed throughout each crib (cf.
+Fig.~\ref{fig:wood_crib}) which brought the total mass of each crib to be 34~kg.
+The moisture content of the cribs was be between 6-8 \%, (measured using a commercial moisture detector).
+This fuel package was based on the prior wood crib tests used in the inital commisioning of the building in 2001.
 
@@
 
-To determine the HCL yield of PVC, we need to determine a balanced chemical reaction.
-First, is to assume that the test PVC can be represented by the chemical formula, $\C_2\H_3\Cl$ and that all of the Cl in PVC goes to HCl.
-Then, based on work by Tewarson \cite{SFPE:Tewarson}, yields for soot and CO are found ($y_{\mathrm{C}}$= 0.172, $y_{\mathrm{CO}}$= 0.063) and a balanced chemical reaction is created:
+To determine the HCL yield of PVC, the first step was to calculate a balanced chemical reaction.
+PVC can be represented by the chemical formula, $\C_2\H_3\Cl$.
+If it assumed that all of the Cl in PVC goes to HCl, then, based on work by Tewarson \cite{SFPE:Tewarson}, yields for soot and CO are found: ($y_{\mathrm{C}}$= 0.172, $y_{\mathrm{CO}}$= 0.063).
+A balanced chemical reaction is created:
 
@@
 \end{multline}
-Based on Eq.~(\ref{eq:hcl_reac}), there is a 58 \% mass basis theoretical yield of HCl (\ref{app:crib}).
-Experimental data based on burning PVC over a wide range of test conditions and using a wide range of measurement techniques puts the HCl yield between 10 and 56 \% \cite{Leeds:PVC}.
-Using data for a similarly scaled and ventilated test, the estimated HCl yield is 32 \% \cite{Persson1998}.
-Since each crib contains 3.63 kg of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65 kg (10.2 lb).
-Based on an estimated 60-70 \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is 1.4-1.9 kg (3-4 lb).
+Based on Eq.~(\ref{eq:hcl_reac}), there is a 58~\% mass basis theoretical yield of HCl.
+Experimental data based on burning PVC over a wide range of test conditions and using a wide range of measurement techniques puts the HCl yield between 10 and 56~\% \cite{Leeds:PVC}.
+Using data for a similarly scaled and ventilated test, the estimated HCl yield is 32~\% \cite{Persson1998}.
+Since each crib contains 3.63~kg (8~lb) of PVC and the test calls for 4 cribs, the expected yield of HCl at the source fire is 4.65~kg (10.2~lb).
+{\em Based on an estimated 60-70 \% loss of HCl to gas phase conversion and reaction through the duct work, the estimated mass of HCL upstream of the scrubber is 1.4-1.9~kg (3-4~lb).}
 
@@
 The second tier will use the forth crib centered over the void created by the triangle.
-Each of the lower tier cribs will be raised 0.08 m off the ground to allow for a pan of heptane to slide underneath.
-The test configuration is shown in Fig.~(\ref{fig:test_crib}).The cribs are ignited using 500 mL of heptane poured into a round steel pan.
-The heptane represents about 1.5 \% of the initial mass of the crib, and burns out after about 2.5 to 3 minutes.
+Each of the lower tier cribs will be raised 0.08~m off the ground to allow for a pan of heptane to slide underneath.
+The test configuration is shown in Fig.~\ref{fig:test_crib}.The cribs are ignited using 500~mL of heptane poured into a round steel pan.
+The heptane represents about 1.5~\% of the initial mass of the crib, and burns out after about 2.5 to 3~min.
 The forth crib will ignite as a result of flame spread from the other three cribs.
@@
 The cups are arranged open end down in five layers, 25 per layer for a total of 125 per box (cf.
-Fig.~(\ref{fig:open_box})).
+Fig.~\ref{fig:open_box}).
 
@@
 In these tests, the columns of boxes are spaced 0.15 m apart (cf.
-Fig.~(\ref{fig:dim_box})).
+Fig.~\ref{fig:dim_box}).
 It is important to note that both orientation and spacing of these boxes can have a significant impact on the burning characteristics \cite{Madrzykowski2013}.
@@
 This is done to contain the polystyrene melt in the later portion of the fire test.
-Fig.~(\ref{fig:comm_burn}) shows two columns of Group A commodity shortly after ignition and when the boxes are fully involved.
+Fig.~\ref{fig:comm_burn} shows two columns of Group A commodity shortly after ignition and when the boxes are fully involved.
 
@@
 \label{app:nfrl_images}
-\begin{figure}[!ht]
-\includegraphics[width=\textwidth]{../Figures/plan_view2}
-\caption {Plan view of the NFRL indicating location of ECS test fires.}
-\label{fig:NFRL_plan}
-\end{figure}
 

### 2014-10-22 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits to captions and figure labels throughout

@@
 \includegraphics[width=5.0in]{../Figures/Plan_Basement_Floor}
-\caption[Plan view of second floor, first floor, and basement floor of structure.]
-{Plan view of second floor (top), first floor (middle), and basement floor (bottom) of structure.
+\caption[Plan view of the second floor, first floor, and basement floor.]
+{Plan view of the second floor (top), first floor (middle), and basement floor (bottom).
 The fire originated in the living room on the basement floor.
@@
 \includegraphics[width=3.50in]{../Figures/Post_Exterior_Rear}
-\caption[Front and rear exterior of the structure after the incident.]
-{Front (top) and rear (bottom) exterior sides of the structure after the incident. Photographs courtesy of the San Francisco Fire Department.}
+\caption[Front and rear sides of the structure after the incident.]
+{Front side (top) and rear side (bottom) of the structure after the incident. Photographs courtesy of the San Francisco Fire Department.}
 \label{fig:post_exterior}
@@
 \includegraphics[width=4.5in]{../Figures/SMV_Exterior_Grid_Rear}
-\caption[Front and rear of the structure with a 10~cm computational mesh.]
-{Front (top) and rear (bottom) sides of the structure with a 10~cm computational mesh.}
+\caption[Front and rear sides of the structure with a 10~cm computational mesh.]
+{Front side (top) and rear side (bottom) of structure with a 10~cm computational mesh.}
 \label{fig:SMV_exterior_grid}
@@
 \includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
-\caption[Predicted HRR vs. time from the FDS simulation.]
-{Comparison of prescribed and predicted HRRs from the FDS simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
+\caption[Predicted HRR vs. time from the simulation.]
+{Comparison of prescribed and predicted HRRs from the simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
 \label{fig:hrr_w_fds}
@@
 In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows had failed).
-Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure at approximately the time when the rear windows began to fail.
+Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the front side of the structure at approximately the time when the rear windows began to fail.
 
@@
 \includegraphics[width=5.0in]{../Figures/SMV_Front_350_s}
-\caption[Snapshot of smoke coming out of the front side of the structure.]
-{Comparison of an on-scene photograph and Smokeview snapshot of smoke coming out of the front side of the structure.
+\caption[Snapshot of smoke flowing out of the doors on the front side of the structure.]
+{Comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the doors on the front side of the structure.
 The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom).
@@
 \caption[Simulated velocity contours on the right interior side of the structure.]
-{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
+{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
 \label{fig:smv_velocity}
@@
 \caption[Simulated velocity vectors on the right interior side of the structure.]
-{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
+{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
 \label{fig:smv_velocity_vectors}
@@
 \caption[Simulated temperature contours on the right interior side of the structure.]
-{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
+{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
 \label{fig:smv_temperature}
@@
 \caption[Simulated temperature vectors on the right interior side of the structure.]
-{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.}
+{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
 \label{fig:smv_temperature_vectors}
@@
 {Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure.
-The orange markers indicate the locations of the downed firefighters.}
+The square markers indicate the locations of the downed firefighters.}
 \label{fig:smv_flow_path_top_1}
@@
 \caption[Simulated temperature contours on the first floor after basement window failure.]
-{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s (top) and 120~s (bottom) after the first rear basement window failure.}
+{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s after (top) and 120~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_flow_path_top_2}

### 2014-10-22 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: minor formatting changes
DelCo 2012: Added table, some formatting.

@@
 \vspace*{2\baselineskip}
-
 August 2014}}
@@
 CODEN: NTNOEF }
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\endgroup
 
@@
 
-	Two identical concrete structures were built on a concrete slab as shown in Figure 1.
+Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}.
 They were designed to simulate a single floor of a residential structure.
@@
 The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
-The ceiling of the burn room was the exposed “floor assembly”.
+The ceiling of the burn room was the exposed ``floor assembly".
 The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room.
@@
 
-	In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter’s head.
-One of the gauge’s sensing surface is facing the ceiling and the other gauge is facing the pallets.
+In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter's head.
+One of the gauge's sensing surface is facing the ceiling and the other gauge is facing the pallets.
 A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.
@@
 
-	The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood “floor assembly”.
+The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
@@
 The pallets and hay were weighed prior to each experiment.
-For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4 kg (511.3 lbs).
+For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
 A complete listing of the mass of each pallet and hay bales is given in Appendix ????????
 
-	The pallet stacks were located 0.3 m (1ft) away from the east and south walls of the burn room.
-The pallets were 1.2 m (48 in) long, 1.0 m (40 in ) and 123 mm (4.8 in) high.
-The stacks were 150 mm (6 in) apart.
+The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room.
+The pallets were 1.2~m (48~in) long, 1.0~m (40~in) and 123~mm (4.8~in) high.
+The stacks were 150~mm (6~in) apart.
 One layer of 13 mm (0.5 in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
-	The east and south wall of the burn room was covered with 15 mm (0.59 in) thick, sheets of plywood.
-The “wood flooring assembly”, composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.
-The open doorway to the burn room on the south side was covered with a 2.4 m (8 ft) tall by 1.2 m (4 ft) wide piece of medium density fiberboard paneling that was 5 mm (0.19 in) thick.
-The southeast corner of the burn room with the fuel load installed is shown in Figure 3.
+The east and south wall of the burn room was covered with 15~mm (0.59~in) thick, sheets of plywood.
+The ``wood flooring assembly", composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.
+The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.
+The southeast corner of the burn room with the fuel load installed is shown in Fig.~\ref{fig:Wood_Fuel_Load}.
 
@@
 
+\begin{sidewaystable}[!ht]
+	\centering
+	\caption{Test Descriptions}
+	\begin{tabular}{lllllllll}
+		\hline\noalign{\smallskip}
+		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		1 (FSE1)    &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
+		2 (FSW2)   	& 302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
+		3 (FSW3) 	&  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
+		4 (FSE4)    &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
+		5 (FSE5)    &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
+		6 (FSW6)    &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
+		7 (FSW7)    &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
+		8 (FSE8)    &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
+		9 (Attic 1) &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
+		10 (Attic 2)&  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
+		11 (FSE1)   &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
+		12 (FSW1)   &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
+		13 (FSE2)   &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
+		14 (FSW2)   &  Cotton w/ inner springs          &                            &  4.06 kg    \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+	\label{tab:Fuel_Masses}
+\end{sidewaystable}
+
 \section{Gas Cooling}

### 2014-10-22 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Added Figures

@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
+	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\label{fig:Test_11_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
+	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_11_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
+	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_12_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
+	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_12_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
+	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\label{fig:Test_13_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
+	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_13_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
+	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_14_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
+	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_14_Second_Suppression}
+\end{figure}
+
 \subsection{Furniture Fuel Package}
 \label{subsec:Furniture_Fuel_Package}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
+	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_1_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
+	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_1_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
+	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\label{fig:Test_2_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
+	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_2_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
+	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, First Suppression}
+	\label{fig:Test_3_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
+	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, Second Suppression}
+	\label{fig:Test_3_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
+	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, First Suppression}
+	\label{fig:Test_4_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
+	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, Second Suppression}
+	\label{fig:Test_4_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
+	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\label{fig:Test_5_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
+	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_5_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
+	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_6_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
+	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_6_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
+	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\label{fig:Test_7_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
+	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_7_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
+	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_8_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
+	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_8_Second_Suppression}
+\end{figure}
 

### 2014-10-22 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG_Co: minor update to report

@@
 CODEN: NTNOEF}
-
-\vspace{0.2in}
-
-\begingroup
-{\bf This publication is available free of charge from:}
-\hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
-\endgroup
 
@@
 \includegraphics[width=.5\textwidth]{../Figures/pg_county_slope} \\
-\caption[Photograph of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure (left) and Smokeview rendering of model representation of sloped landscape (right).}
+\caption[Photograph and computer model rendering of terrain.]{Photograph taken from front side street level showing the slope down to basement on the rear side of the structure (left) and Smokeview rendering of model representation of sloped landscape (right).}
 \label{fig:slope}

### 2014-10-24 Projects/NFRL_Emissions/Report/ECS_Testing.tex
ECS: minor update to report

@@
 Table ~\ref{tab:fires} shows the fire tests to be conducted.
-Two tests were conducted with each fuel package to ensure that each train within the new ECS was independently tested.
-For the gas burner tests, three tests were conducted; one for each of the the trains and one with both trains running together to test heat release rates larger than 5~MW.
+Two tests were conducted with each fuel package to ensure that each train within the ECS was independently tested.
+For the gas burner tests, three tests were conducted; one for each train and one utilizing both trains to test heat release rates larger than 5~MW.
 
-\begin{table}
+\begin{table}[!h]
 \centering
@@
 
-The burning rate of wood cribs is found from experiments performed by Madrzykowski and Stroup \cite{Madrzykowski1998} and Bryner and Mulholland \cite{Bryner1991}.
-The steady burning rate averaged over the peak 50 \% of burning is 0.03 kg/s.
-If an entire 34 kg crib burned at this rate, the burn would last approximately 19 minutes.
+The burning rate of wood cribs was found from experiments performed by Madrzykowski and Stroup \cite{Madrzykowski1998} and Bryner and Mulholland \cite{Bryner1991}.
+The steady burning rate averaged over the peak 50~\% of burning is 0.03~kg/s.
+If an entire 34~kg crib burned at this rate, the burn would last approximately 19 minutes.
 If we estimate that 50 \% of the mass burns at 0.03 kg/s and the remaining 50 \% burns at $1/3$ the burning rate, 0.01 kg/s, then a crib burn would take approximately 40 minutes.

### 2014-10-28 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Update acknowledgments

@@
 
-The authors would like to thank XXXX.
-The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in compiling Table~\ref{tab:LODD}.
+The authors would like to thank Chief of Department Joanne Hayes-White, Battalion Chief Jose L.
+Velo, and Assistant Chief David L.
+Franklin of the San Francisco Fire Department for their assistance with this study and their dedication to improving firefighter safety.
+The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in researching and compiling the flow path related LODD/LODI incidents shown in Table~\ref{tab:LODD}.
+Thanks to the NIOSH Fire Fighter Fatality Investigation and Prevention Program for their cooperation.
 Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.

### 2014-10-28 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: add figures, update report

@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
+	\caption{Delaware County, PA Fire Test Structure}
+	\label{fig:DelCoSingleStory}
+\end{figure}
+
 The floor of the structure was a concrete pad.
@@
 The structures were instrumented for temperature, heat flux, and gas velocity measurements.  A schematic plan view of the instrumentation arrangement is show in ????
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Fog_Instrumentation}
+	\caption{Photograph of the Instrumentation in the Fog Stream Tests.}
+	\label{fig:Fog_Instrumentation}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Straight_Stream_Instrumentation}
+	\caption{Photograph of the Instrumentation in the Straight Stream Tests.}
+	\label{fig:Straigh_Stream_Instrumentation}
+\end{figure}
 
@@
 		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 (FSE1)    &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
-		2 (FSW2)   	& 302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
-		3 (FSW3) 	&  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
-		4 (FSE4)    &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
-		5 (FSE5)    &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
-		6 (FSW6)    &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
-		7 (FSW7)    &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
-		8 (FSE8)    &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
-		9 (Attic 1) &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
-		10 (Attic 2)&  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
-		11 (FSE1)   &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
-		12 (FSW1)   &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
-		13 (FSE2)   &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
-		14 (FSW2)   &  Cotton w/ inner springs          &                            &  4.06 kg    \\
+		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
+		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
+		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
+		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
+		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
+		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
+		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
+		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
+		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
+		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
+		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
+		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
+		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
+		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
 		\noalign{\smallskip}\hline

### 2014-10-28 Projects/Spartanburg_2013/Spartanburg_2013.tex
Spartanburg 2013: minor update to report

@@
 
-The third test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street.
+The next test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street.
 The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
 The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
-Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living Room fire with exterior attack.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living room fire with exterior attack.
 
@@
 
- The third test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street.
+ The fifth test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street.
 The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
@@
 
+  \section{226 Folsom Street}
+
+  The following series of tests were conducted in a single story, single family residential structure of type 5 construction addressed as 226 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burns rooms had a combustible finish comprised of OSB sheets for wall linings.
+Three tests were conducted in this structure: 1) Wastebasket fire with sprinkler activation, 2) Bedroom fire with exterior attack, and 3) Living room fire with exterior attack.
+
+  \subsection{Test 1: Wastebasket Fire with Sprinkler}
+
+  This fire was ignited in a small wastebasket located between a bed with modern-style mattress and a wooden nightstand in the bedroom of the home near the A/D corner.
+The windows and door to the room were closed for the duration of the test.
+The fire grew uninhibited until the sprinkler activated suppressing the fire.
+Shortly thereafter, a fire fighting crew made entry to confirm extinguishment.
+
+  \subsection{Test 2: Bedroom Fire}
+
+  Ignition occurred on a modern-style mattress in a bedroom to the rear of the structure near the C/D corner.
+The bedroom window on side C of the structure is open during the test as is the interior bedroom doorway.
+The bedroom window on side D of the structure is closed at the beginning of the test.
+Fire growth was uninhibited.
+The fire in the room of origin grew until the D side window self-vented.
+The room of origin reached flashover conditions and the D side window became full exhaust.
+The adjoining bedroom window on the D side of the structure was vented by the fire fighting crew shortly thereafter.
+The fire fighting crew then conducted an exterior attack via a single hand-line with a smooth bore nozzle until the fire was extinguished.
+Another fire fighting crew made entry into the structure via the Side A door to confirm extinguishment and mop-up.
+
+  \subsection{Test 3: Living Room Fire}
+
+  The fire was ignited on a modern-style sofa in the living room near the A/B corner of the structure.
+The A side window to the living room, in addition to the A side front door, were open for the duration of the test.
+The fire was allowed to grow uninhibited until the fire building reached ventilation-limited conditions.
+
 \end{document}

### 2014-10-29 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL ECS: minor update to writeup

@@
 \hspace{1.5in} \= \\
-ECS \> Emisssion Control System \\
+ECS \> Emisssions Control System \\
 HRR \> Heat Release Rate \\
@@
 The objective of the fire tests was to use specifically designed source fires to test the emission control systems to ensure the system could handle elevated temperatures, toxic gases, and particulates.
+
+\chapter{Emissions Control System}
+\label{ecs}
+The emissions control system for the NFRL is a combination spray dryer and pulse jet fabric filter system.
+The purpose is to remove both particulates and polluntants produced from experiments within the laboratory.
 

### 2014-10-29 Projects/Spartanburg_2014/Report/Spartanburg.tex
Spartanburg: Combine 2013/2014 reports and rename file

--- 2014-10-16 Projects/Spartanburg_2014/Report/Spartanburg_2014.tex
@@
 \begingroup
+This publication is available free of charge from:
 \hypersetup{urlcolor=black}
-This publication is available free of charge from:
 \href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
@@
 
+\section{214 Folsom Street}
+
+The first test house was a single story, single family residential structure of type 5 construction addressed as 214 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Living room fire with exterior attack and 2) Bedroom fire with exterior attack.
+
+\subsection{Test 1: Living Room Fire}
+
+Ignition begins on a modern-style sofa in the living room on the A/D corner of the structure with all doors and windows closed.
+The fire grew uninhibited and reach the vent-limited stage.
+Fire fighting crew ventilated the living room window on the D side of the structure.The fire was allowed to stabilize with the new ventilation opening.
+The fire fighting crew then applied water, via a straight stream flow, from the exterior into the D side window for suppression.
+After the exterior suppression, the front living room window on the A side of the structure was ventilated.
+Water was then applied from the exterior on the A side into the living room window for further suppression.
+The fire fighting crew then opened the front door and made entry to complete suppression.
+
+\subsection{Test 2: Bedroom Fire}
+
+The fire was ignited on a modern-style soda in the bedroom located near the B/C corner of the structure.
+The living room used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The fire was allowed to grow uninhibited and reach the vent-limited stage.
+The fire self-vented the upper portion of the bedroom window on the B side of the structure.
+The fire fighting crew ventilated a window on the D side of the building in the adjacent room located near the C/D corner.
+The fire then self-vented the remaining portion of the window in the room of origin.
+The small window into the kitchen on the B side of the structure was then ventilated.
+Shortly thereafter, the fire fighting crew made an exterior attack via a narrow fog into the bedroom from the self-vented B side window.
+
+\section{215 Folsom Street}
+
+The second test house was a single story, single family residential structure of type 5 construction addressed as 215 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Living room fire with exterior attack and 2) Bedroom fire with exterior attack.
+
+\subsection{Test 1: Living Room Fire}
+
+The fire was ignited in the front living room located near the A/B corner of the structure on a modern-style sofa.
+The fire grew uninhibited until reaching the ventilation-limited stage.
+While in the growth stage, the fire self-vented the living room window on the A side of the structure, near the A/B corner.
+After the fire fighting unit officer completed a 360 degree size-up of the structure, the front door was opened from the exterior.
+The living room window on the B side of the structure then self-vented as well.
+Shortly thereafter, the pressure from the fire compartment closed the front door.
+After a short period of time, the fire fighting crew re-opened the front door to the building.
+The fire fighting crew began an attack on the structure via a single smooth bore hose-line first knocking down the fire on the porch.
+The nozzle was then directed into the A side living room window and front doorway.
+The fire fighting crew then completed suppression and overhauled the porch area to complete mop-up procedures.
+
+\subsection{Test 2: Bedroom Fire}
+
+The fire was ignited in a rear bedroom near the C/D corner of the structure on a modern-style sofa.
+The C side window to the bedroom was half open.
+The C side window in the adjoining room also had a window in the half open position.
+The living room used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The fire was allowed to grow uninhibited and reach the vent-limited stage.
+The fire then self-vented a portion of the bedroom window on the D side.
+Once the temperatures leveled off in the fire room, the fire fighting crew ventilated the remaining portion of the window in the adjoining room, also on the D side of the structure.
+As the fire continued to grow, the fire fighting crew ventilated the remaining portion of the bedroom window in the room of origin.
+The fire room reached flashover conditions.
+The fire fighting crew then applied water into the room of origin via a single hose-line with a narrow fog pattern until the fire was completely suppressed.
+
+\section{218 Folsom Street}
+
+The third test house was a single story, single family residential structure of type 5 construction addressed as 218 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Bedroom fire with exterior attack.
+
+\subsection{Test 1: Bedroom Fire}
+
+The fire was ignited in a rear bedroom near the C/D corner of the structure on a modern-style mattress with foam padding atop.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The fire grew uninhibited until reaching the vent-limited stage.
+The officer of the fire fighting crew completed a 360 degree size-up of the structure to assess conditions.
+Shortly thereafter, the fire fighting crew ventilated the bedroom window on the D side of the building.
+The fire was allowed to stabilize given the new ventilation opening.
+The fire fighting crew then made an attack on the fire by flowing a single hand-line with a smooth bore nozzle into the room of origin through the D side window from the exterior.
+
+\subsection{Test 2: Bedroom Fire}
+
+Ignition occurred in a rear bedroom near the B/C corner of the structure on a modern-style couch.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The bedroom used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The fire grew uninhibited until reaching the vent-limited stage.
+The officer of the fire fighting crew completed a 360 degree size-up and then the fire fighting crew ventilated the target room window on the B side of the building.
+This was the window to the adjoining room in the structure located near the A/B corner.
+The fire was allowed to stabilize given the new ventilation opening.
+The fire fighting crew then ventilated the bedroom window to the room of origin on the B side next.
+This was followed up by the fire fighting crew making an attack on the fire by flowing a single hand-line with a smooth bore nozzle into the room of origin through the B side window from the exterior.
+
+\section{219 Folsom Street}
+
+The next test house was a single story, single family residential structure of type 5 construction addressed as 219 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+Two tests were conducted in this structure: 1) Bedroom fire with exterior attack and 2) Living room fire with exterior attack.
+
+\subsection{Test 1: Bedroom Fire}
+
+Ignition occurred in a rear bedroom near the B/C corner of the structure on a modern-style mattress with foam padding.
+All doors and windows to the exterior of the structure were closed at the beginning of the test.
+The fire grew uninhibited until reaching the vent-limited stage.
+The front door to the structure was then opened by the fire fighting crew to simulate a crew making entry or a homeowner leaving the door open upon evacuation.
+The fire continued to grow uninhibited until the fire room reached flashover conditions.
+The fire fighting crew then ventilated the bedroom window on the B side of the structure in the room of origin.
+The fire was then allowed to stabilize given the new ventilation opening.
+An unmanned monitor nozzle connected to a single hose-line was placed inside the structure at the entry to the fire room.
+This was remotely activated to simulate a fire fighting crew making an interior attack on the seat of the fire.
+The water was flowed until the fire was suppressed.
+The fire fighting crew then completed the test by making entry to the structure to complete overhaul and mop-up procedures.
+
+\subsection{Test 2: Living Room Fire}
+
+The fire was ignited in the front living room located near the A/D corner of the structure on a modern-style sofa.
+The bedroom used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
+The window to the living room on the D side of the structure was half-opened at the start of the test.
+The fire grew uninhibited until reaching the ventilation-limited stage.
+The window on the D side in the adjacent room near the C/D corner of the structure was ventilated next.
+The upper portion of the A side living room window self-ventilated due to the fire.
+Shortly thereafter, the fire fighting crew ventilated the remaining portion of the D side living room window.
+Once the fire had self-ventilated the remaining portion of the A side living room window, it was allowed to stabilize.
+The fire fighting crew then conducted an exterior attack via the D side living room window with a single hose-line with a smooth bore nozzle.
+
+\section{225 Folsom Street}
+
+ The fifth test house was a single story, single family residential structure of type 5 construction addressed as 225 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+One test was conducted in this structure comparing a legacy versus modern sofa with an exterior fire attack.
+
+\subsection{Test 1: Legacy versus Modern Sofa}
+
+Ignition points were located in two different rooms within the home.
+A legacy-style sofa was ignited in a rear bedroom of the structure near the C/D corner and a modern-style sofa was ignited in a front living room near the A/B corner approximately 6 minutes after the first ignition.
+The front door to the structure remained open during the test.
+Additionally, the D side window to the rear bedroom with the legacy-style sofa also remained open.
+The fires were allowed to grow uninhibited.
+The fires within the home became ventilation limited.
+The living room window on the B side of the structure self-vented, followed by the living room window on the A side of the structure.
+Once the fire grew in size and began burning the porch area, an exterior attack via a single hose-line with smooth bore nozzle was made through the front door and A side living room window.
+
+\section{226 Folsom Street}
+
+The following series of tests were conducted in a single story, single family residential structure of type 5 construction addressed as 226 Folsom Street.
+The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
+The burns rooms had a combustible finish comprised of OSB sheets for wall linings.
+Three tests were conducted in this structure: 1) Wastebasket fire with sprinkler activation, 2) Bedroom fire with exterior attack, and 3) Living room fire with exterior attack.
+
+\subsection{Test 1: Wastebasket Fire with Sprinkler}
+
+This fire was ignited in a small wastebasket located between a bed with modern-style mattress and a wooden nightstand in the bedroom of the home near the A/D corner.
+The windows and door to the room were closed for the duration of the test.
+The fire grew uninhibited until the sprinkler activated suppressing the fire.
+Shortly thereafter, a fire fighting crew made entry to confirm extinguishment.
+
+\subsection{Test 2: Bedroom Fire}
+
+Ignition occurred on a modern-style mattress in a bedroom to the rear of the structure near the C/D corner.
+The bedroom window on side C of the structure is open during the test as is the interior bedroom doorway.
+The bedroom window on side D of the structure is closed at the beginning of the test.
+Fire growth was uninhibited.
+The fire in the room of origin grew until the D side window self-vented.
+The room of origin reached flashover conditions and the D side window became full exhaust.
+The adjoining bedroom window on the D side of the structure was vented by the fire fighting crew shortly thereafter.
+The fire fighting crew then conducted an exterior attack via a single hand-line with a smooth bore nozzle until the fire was extinguished.
+Another fire fighting crew made entry into the structure via the Side A door to confirm extinguishment and mop-up.
+
+\subsection{Test 3: Living Room Fire}
+
+The fire was ignited on a modern-style sofa in the living room near the A/B corner of the structure.
+The A side window to the living room, in addition to the A side front door, were open for the duration of the test.
+The fire was allowed to grow uninhibited until the fire building reached ventilation-limited conditions.
+
 \section{286 College}

### 2014-10-29 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL ECS: update report

@@
 The purpose is to remove both particulates and polluntants produced from experiments within the laboratory.
+Fans draw air through one of four fire calorimter exhaust hoods designed to capture combustion gases from experiments (see Table~\ref{tab:hoods}).
+Makeup air is drawn into the building via air intake dampers, to replace the air pulled through the exhaust hoods and into the process ducting.
+Before entering the spray dryer, the air passes through an inline duct burner.
+The purpose of the duct burner is to heat the air to 500~$^{\circ}$C to improve the efficiency of the spray dryer.
+Downstreat of the burner, the hot exit air helps to evaporate the limey slury mist generated by the spray dryer.
+The gas-phase lime reacts with airborne poluntants to form precipitate which collects at the bottom of the dryer, out of the air stream.
+The spray dryer also introduces a cool water mist to drop the exit temperature of the air below the threshold temperature for the final component, the baghouse.
+Air enters the baghouse and flows through a series of filter bags.
+A filter bag is constructed of a long cylindrical metal cage covered with a fine pore fabric.
+Contaiminated air flows from the outside of the cylinder through the porous media, which traps the particulates, and allows the clean air to flow out through the center of the cylinder.
+
+\begin{table}[!h]
+\centering
+\caption{Fire Calorimeter Exhaust Hoods}
+\label{tab:hoods}
+\begin{tabular}{ccc}
+\toprule[1.5pt]
+Peak HRR (MW) & Area (m$^2$) & Elevation (m)  \\
+\midrule
+1    & 3.1  $\times$ 3.2   & 2.3  \\
+3    & 6.2  $\times$ 6.2   & 4.5  \\
+10   & 8.5  $\times$ 12.3  & 6.3  \\
+20   & 13.7 $\times$ 15.2  & 12.5 \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 

### 2014-10-30 Projects/NFRL_Emissions/Report/ECS_Testing.tex
NFRL ECS: add figure, update report

@@
 
-\chapter{Emissions Control System}
+\chapter{Emissions Control System (ECS)}
 \label{ecs}
@@
 Contaiminated air flows from the outside of the cylinder through the porous media, which traps the particulates, and allows the clean air to flow out through the center of the cylinder.
+Finally the cleaned air exits the system through a 30.5~m exhaust stack which pulls the airflow out using an induction fan.
+
+The complete ECS consists of 4 duct burners, spray dryers, and bag houses, which in pairs of two, exhaust through one of two exhaust stacks.
+The system is capable of handling a maximum exhaust air flow rate of 5100~m$^3$/min ($\approx$ 20~MW fire), cleaning 5.4 kg/hr of acid gas (HCl) and trapping 181 kg/hr of particulates.
+Figure~\ref{fig:NFRL_roof} is an aeral photograph of the NFRL which highlights the location of the components of the ECS.
+Note that components labeled 1 and 2 were part of the inital system while components 3 and 4 were added with the expansion of the laboratory.
 
@@
 \end{table}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.8\textwidth]{../Figures/nfrl_roof}
+\caption {Aeral view of the NFRL with callouts indicating components of ECS.}
+\label{fig:NFRL_roof}
+\end{figure}
 

### 2014-11-03 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: New Figures (floor plan, instrumentation) and Inserted into Report
DelCo 2012: New Fuel Load Drawings
DelCo 2012: Report Re-structuring and addition of burn building figures.

@@
 
+\subsection{Burn Building - Gas Cooling}
+\label{sec:Burn_Building}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCo_Structures}
+	\caption{Delaware County, PA Fire Test Structures}
+	\label{fig:Delaware_County,_PA_Fire_Test_Structures}
+\end{figure}
+
+\subsection{Concrete Structures - Fire Suppression}
+\label{sec:Experimental Structures}
+
 Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}.
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryDimensionsMetric}
+	\caption{Floor Plan of the Test Structure.}
+	\label{fig:Test_Structure_Floor_Plan}
+\end{figure}
+
 The floor of the structure was a concrete pad.
@@
 
+\subsection{Gas Cooling Instrumentation}
+\label{subsec:Gas_Cooling_Instrumentation}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
+	\caption{Photograph of the Instrumentation Dimensions in the Gas Cooling Experiments}
+	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
+\end{figure}
+
+\subsection{Fire Suppression Instrumentation}
+\label{subsec:Fire_Suppression_Instrumentation}
+
 The structures were instrumented for temperature, heat flux, and gas velocity measurements.  A schematic plan view of the instrumentation arrangement is show in ????
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
+	\caption{Photograph of the Instrumentation Dimensions in the Fire Suppression Experiments.}
+	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
+\end{figure}
 
@@
 
+\subsubsection{Gas Cooling Experiments}
+\label{subsubsec:Gas_Cooling_Temperature_Instrumentation}
+
+\subsubsection{Fire Suppression Experiments}
+\label{subsubsec:Fire_Suppression_Temperature_Instrumentation}
+
 Gas temperatures in the burn room were measured with bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5 mm (0.02 in) nominal diameter.
@@
 \label{subsec:Heat_Flux}
+
+\subsubsection{Gas Cooling Experiments}
+\label{subsubsec:Gas_Cooling_Heat_Flux_Instrumentation}
+
+\subsubsection{Fire Suppression Experiments}
+\label{subsubsec:Fire_Suppression_Heat_Flux_Instrumentation}
 
@@
 
+\subsubsection{Gas Cooling Experiments}
+\label{subsubsec:Gas_Cooling_Gas_Velocity_Instrumentation}
+
+\subsubsection{Fire Suppression Experiments}
+\label{subsubsec:Fire_Suppression_Gas_Velocity_Instrumentation}
+
 Gas velocity was determined utilizing differential pressure transducers connected to bidirectional velocity probes[ ] in conjunction with a temperature measurement.
@@
 \label{subsec:Infrared_Radiation}
+
+\section{Fuel Load: Gas Cooling}
+\label{sec:Fuel_Load:_Gas_Cooling}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingFuelLoad}
+	\caption{Burn Building Fuel Load.}
+	\label{fig:Burn_Building_Fuel_Load}
+\end{figure}
 
@@
 \begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
+	\caption{Wood Fuel Load Dimensions.}
+	\label{fig:Wood_Fuel_Load_Dimensions}
+\end{figure}
+
+\begin{figure}[!ht]
 	\includegraphics[width=6in]{../Figures/Pictures/Wood_Fuel_Package}
@@
 \label{sec:Fuel_Load:_Furniture_Experiments}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
+	\caption{Furniture Fuel Load Dimensions.}
+	\label{fig:Furniture_Fuel_Load_Dimensions}
+\end{figure}
 
@@
 
+\section{Gas Cooling}
+\label{sec:Gas_Cooling}
+
+\subsection{Spray Density}
+\label{subsec:Spray_Density}
+
+\section{Fire Suppression}
+\label{sec:Fire_Suppression}
+
 \begin{sidewaystable}[!ht]
@@
 \end{sidewaystable}
-
-\section{Gas Cooling}
-\label{sec:Gas_Cooling}
-
-\subsection{Spray Density}
-\label{subsec:Spray_Density}
-
-\section{Fire Suppression}
-\label{sec:Fire_Suppression}
 

### 2014-11-03 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add info to fire writeup

@@
 
-October 2014}}
+November 2014}}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (August 2014) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (November 2014) \\
 CODEN: NTNOEF}
@@
 \label{fire}
+To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
+Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjecent bathoom.
+At the time of the fire, the structure was vacant so the the dominant fuel was wood: exposed ceiling joists, subfloor, cabinets, and stairs.
 
-On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure.
+Wood fuel can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified yields of carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$) and soot ($y_{\mathrm{C}}=0.015 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The product yields are expressed in terms of the amount of carbon monoxide or soot emitted per unit mass of fuel consumed (kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
+A balanced chemical reaction for wood combustion can be written as:
+
+\begin{multline}
+\C\H_{1.7}\O_{0.74}\N_{0.002} + 4.91(0.208\,\O_{2} + 0.783\,\N_{2} + 0.387\text{\sc{e}-}3\,\C\O_{2} + 0.834\text{\sc{e}-}2\,\H_{2}\O) \\ 
+\rightarrow 5.74(0.636\text{\sc{e}-}3\,\C\O + 0.168\,\C\O_{2} + 0.155\,\H_{2}\O + 0.670\,\N_{2} + 0.613\text{\sc{e}-}2\,\C)
+\label{eq:wood_comb}
+\end{multline}
+
+The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The heat of combustion quantifies the amount of energy per unit mass of the fuel.
+The following text defines Eq.~\ref{eq:wood_comb} for an FDS input file with the desired fuel and reaction properties discussed above:
+
+\begin{lstlisting}
+&SPEC ID='WOOD', FORMULA='CH1.7O0.74N0.002' /
+
+&REAC ID = 'wood' 
+    FUEL = 'WOOD', 
+    HEAT_OF_COMBUSTION = 16400,
+    SOOT_YIELD = 0.015,
+    CO_YIELD = 0.004/
+\end{lstlisting}
+
+Note that using the input lines above will invoke the simple chemistry reaction mechanism in FDS in which fuel and air react to form only CO$_2$, CO, H$_2$O, soot, and N$_2$.
+If the inclusion for other combustion products is desired, then the user must explicitly define those species and the chemical reaction that produces them~\cite{FDS_Users_Guide}.
+Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
+This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
+While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
+
+To estimate the heat release rate per unit area (HRRPUA) of wood, Babrauskas and Grayson~\cite{babrauskas1990} conducted experiments in a cone calorimeter\footnote{The cone calorimeter is an experimental apparatus used to gather data about ignition time, mass loss, combustion products, and heat release rate among other properties associated with burning small samples of materials~\cite{ASTM:E1355}.} to determine the 5-min average of the HRRPUA for several different types of wood over a range of radiant heat fluxes.
+The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
+
+To calculate the total fire size, the appropriate burning area (exposed wood area) of the basement needed to be determined.
+Based on the floor plan of the structure, the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
+Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
+Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
+That area was considered to be part of the porch fire.
+Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
+To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
+Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
+To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
+Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
+Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
+Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
+The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
+The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
+The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+The following lines define the source fires in the FDS input file:
+
+\begin{lstlisting}
+&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE', TAU_Q=10 /
+&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 
+&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 
+&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 
+&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
+\end{lstlisting}
+Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
 
@@
 The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the stucture (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells).
-Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case to 2~days for the 20~mph wind case.
+Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case to 3~days for the 20~mph wind case.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.

### 2014-11-04 Projects/DelCo_2012/Report/DelCo_2012.tex

@@
 	\caption{Test Descriptions}
-	\begin{tabular}{lllllllll}
+	\begin{tabular}{lllll}
 		\hline\noalign{\smallskip}
-		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
+		Test		& Agent		& Stream		& Flow Rate		& Comments \\
 		\noalign{\smallskip}\hline\noalign{\smallskip}
@@
 	\end{tabular}
-	\label{tab:Fuel_Masses}
+	\label{tab:Test_Descriptions}
+\end{sidewaystable}
+
+\begin{sidewaystable}[!ht]
+	\centering
+	\caption{Nozzle Activation Times}
+	\begin{tabular}{lllllllll}
+		\hline\noalign{\smallskip}
+		Test		& Agent		& Stream				& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		1 (FSE1)    &  CAF      &  30 deg Fog  	    \\
+		2 (FSW2)   	& Water     &  30 deg Fog  	    \\
+		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore      \\
+		4 (FSE4)    &  Water    &  7/8" Smooth Bore     \\
+		5 (FSE5)    &  Water    &  30 deg Fog  	    \\
+		6 (FSW6)    &  CAF      &  30 deg Fog      \\
+		7 (FSW7)    &  Water    &  30 deg Fog      \\
+		8 (FSE8)    &  CAF      &  30 deg Fog      \\
+		9 (Attic 1) &  Water    &  Straight Stream      \\
+		10 (Attic 2)&  CAF      &  Straight Stream      \\
+		11 (FSE1)   &  Water    &  30 deg Fog  	    \\
+		12 (FSW1)   &  CAF      &  30 deg Fog  	    \\
+		13 (FSE2)   &  Water    &  30 deg Fog  	   \\
+		14 (FSW2)   &  CAF      &  30 deg Fog  	   \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+	\label{tab:Nozzle_Activation_Times}
 \end{sidewaystable}

### 2014-11-04 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add two figures, update report

@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjecent bathoom.
+Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjecent bathoom (Fig.~\ref{fig:basement_fire}).
 At the time of the fire, the structure was vacant so the the dominant fuel was wood: exposed ceiling joists, subfloor, cabinets, and stairs.
+
+\begin{figure}[!ht]
+\includegraphics[width=\textwidth]{../Figures/Basement_Fire}
+\caption[Plan view of basement indicating fire location.]{Plan view of the basement indicating the location of the two fires in the FDS model.}
+\label{fig:basement_fire}
+\end{figure}
 
@@
 
-To calculate the total fire size, the appropriate burning area (exposed wood area) of the basement needed to be determined.
-Based on the floor plan of the structure, the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
-Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
-Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
-That area was considered to be part of the porch fire.
-Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
-To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
-Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
-To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
-Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
-Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
+To calculate the total fire size, the appropriate burning area (exposed wood area) of the basement needed to be determined. Based on the floor plan of the structure,
+
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
-The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
+The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.5~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
-The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (1 source for the kitchen, 1 source for the bathroom).
 The following lines define the source fires in the FDS input file:
@@
 \begin{lstlisting}
-&SURF ID='FIRE', HRRPUA=2250., COLOR='ORANGE', TAU_Q=10 /
-&VENT XB=-13.5,-13,1,5,6.16,6.16, SURF_ID='FIRE' / 
-&VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' / 
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/ 
-&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
+&SURF ID='burner1', HRRPUA = 2000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&SURF ID='burner2', HRRPUA = 4500, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&RAMP ID='BURN', T = 0,   F = 0.  /
+&RAMP ID='BURN', T = 10,  F = 1.0 /
+&RAMP ID='BURN', T = 300, F = 1.0 /
+&OBST XB=0.6,1.2,5,6.5,0.0,0.4, SURF_IDS='burner1','INERT','INERT' /  Burner1
+&OBST XB=2.5,4,5.0,6.0,0.0,0.4, SURF_IDS='burner2','INERT','INERT' /  Burner2
 \end{lstlisting}
-Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
+Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is the 2-D planar area.
 
@@
 Note the finer mesh (smaller cells) surrounding the structure and the coarser mesh on each side.
-The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the stucture (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells).
-Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case to 3~days for the 20~mph wind case.
+The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the stucture (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
+Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case and 3~days for the 20~mph wind case.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
+The boundary between the 12 10~cm meshes and 5 20~cm meshes is indicated by the {\bf bold} lines.
 Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
@@
 \centering
-\includegraphics[width=\textwidth]{../Figures/pg_county_meshtotal}
-\caption[Overhead front-left side of the structure within the computational domain.]{Overhead front-left view of the structure within the computational domain (with multiple meshes).
-Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
+\includegraphics[width=\textwidth]{../Figures/pg_county_meshtotal2}
+\caption[Overhead front-left side of the structure within the computational domain.]{Overhead front-left view of the structure within the computational domain (with 17 meshes).
+The entire computational domain is 24~m (79~ft) by 16~m (53~ft) by 8~m (26~ft).}
 \label{fig:mult_mesh}
 \end{figure}
+
+\clearpage
 
@@
                                                            &  Heat of Combustion: 16,400~kJ/kg             &                                       \\ [.25cm]
-\multirow{2}{*}{Peak HRR}                                  &  Basement Fire: 9~MW                          & \multirow{2}{*}{Section~\ref{fire}}   \\ 
-                                                           &  Bathroom Fire: 3.3~MW                        &                                       \\ [.25cm]                     
+\multirow{2}{*}{Peak HRR}                                  &  Basement Fire: 6.75~MW                       & \multirow{2}{*}{Section~\ref{fire}}   \\ 
+                                                           &  Bathroom Fire: 1.8~MW                        &                                       \\ [.25cm]                     
 \multirow{3}{*}{Material: Wood~\cite{Incropera:1} }        &  $k$: 0.12~\si{W/(m.K)})                      & \multirow{3}{*}{Section~\ref{matl}}   \\

### 2014-11-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Completed Test Tables

--- 2014-11-03 Projects/DelCo_2012/Report/DelCo_2012.tex
@@
 
+\subsection{Uncertainty}
+\label{subsec:Uncertainty}
+
 \section{Fuel Load: Gas Cooling}
@@
 		\noalign{\smallskip}\hline\noalign{\smallskip}
-		% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
-		%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
-		%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
-		%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
-		% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
-		%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
-		%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
+		3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
+		Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
+		Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
+		Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
+		2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
+		Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
+		Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
 		3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
@@
 	\caption{Test Descriptions}
-	\begin{tabular}{lllllllll}
+	\begin{tabular}{lllll}
 		\hline\noalign{\smallskip}
-		Test		& Agent		& Stream		& Flow Rate		& Comments		& Nozzle 1 Activation		& Nozzle 1 Shut Off		& Nozzle 2 Activation		& Nozzle 2 Shut Off \\
+		Test		& Agent		& Stream				& Flow Rate			& Comments \\
 		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 (FSE1)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
-		2 (FSW2)   	& Water     &  30 deg Fog  	&  120 gpm    \\
-		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  &  120 gpm/60 cfm    \\
-		4 (FSE4)    &  Water    &  7/8" Smooth Bore  &  120 gpm    \\
-		5 (FSE5)    &  Water    &  30 deg Fog  	&  120 gpm    \\
-		6 (FSW6)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
-		7 (FSW7)    &  Water    &  30 deg Fog  	&  120 gpm    \\
-		8 (FSE8)    &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
-		9 (Attic 1) &  Water    &  Straight Stream  &  120 gpm    \\
-		10 (Attic 2)&  CAF      &  Straight Stream  &  120 gpm/60 cfm    \\
-		11 (FSE1)   &  Water    &  30 deg Fog  	&  120 gpm    \\
-		12 (FSW1)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
-		13 (FSE2)   &  Water    &  30 deg Fog  	&  120 gpm    \\
-		14 (FSW2)   &  CAF      &  30 deg Fog  	&  120 gpm/60 cfm    \\
+		1 (FSE1)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
+		2 (FSW2)   	& Water     &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
+		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
+		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120 gpm    		&	Furniture Fuel Package	\\
+		5 (FSE5)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
+		6 (FSW6)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
+		7 (FSW7)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
+		8 (FSE8)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
+		9 (Attic 1) &  Water    &  Straight Stream  	&  120 gpm    		&	Furniture Fuel Package	\\
+		10 (Attic 2)&  CAF      &  Straight Stream  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
+		11 (FSE1)   &  Water    &  30 deg Fog  			&  120 gpm   		&	Wood Fuel Package, Panel Window	 \\
+		12 (FSW1)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
+		13 (FSE2)   &  Water    &  30 deg Fog  			&  120 gpm    		&	Wood Fuel Package, Panel Window  \\
+		14 (FSW2)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
 		\noalign{\smallskip}\hline
 	\end{tabular}
-	\label{tab:Fuel_Masses}
+	\label{tab:Test_Descriptions}
+\end{sidewaystable}
+
+\begin{sidewaystable}[!ht]
+	\centering
+	\caption{Nozzle Activation Times}
+	\begin{tabular}{lllllll}
+		\hline\noalign{\smallskip}
+		Test		& Agent		& Stream				& Nozzle 1 Activation	& Nozzle 1 Shut Off		& Nozzle 2 Activation	& Nozzle 2 Shut Off \\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		1 (FSE1)    &  CAF      &  30 deg Fog  	    	& 233 					& 248					& 269					& 284					\\
+		2 (FSW2)   	& Water     &  30 deg Fog  	    	& 235					& 250					& 272					& 287					\\
+		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore     & 228					& 243 					& 255					& 270					\\
+		4 (FSE4)    &  Water    &  7/8" Smooth Bore     & 233					& 248					& 268					& 283					\\
+		5 (FSE5)    &  Water    &  30 deg Fog  	    	& 232					& 247					& 257					& 272					\\
+		6 (FSW6)    &  CAF      &  30 deg Fog     		& 239					& 254					& 268					& 283					\\
+		7 (FSW7)    &  Water    &  30 deg Fog     		& 276					& 291					& 308					& 323					\\
+		8 (FSE8)    &  CAF      &  30 deg Fog     		& 245					& 260					& 275					& 290					\\
+		9 (Attic 1) &  Water    &  Straight Stream     	&						&						&						&					\\
+		10 (Attic 2)&  CAF      &  Straight Stream     	& 						&						&						&					\\
+		11 (FSE1)   &  Water    &  30 deg Fog  	   		& 315					& 330					& 345					& 360					\\
+		12 (FSW1)   &  CAF      &  30 deg Fog  	   		& 233					& 248					& 263					& 278					\\
+		13 (FSE2)   &  Water    &  30 deg Fog  	   		& 330					& 390					& 406					& 466					\\
+		14 (FSW2)   &  CAF      &  30 deg Fog  	  		& 435					& 495					& 510					& 570					\\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+	\label{tab:Nozzle_Activation_Times}
 \end{sidewaystable}

### 2014-11-07 Projects/Spartanburg_2014/Report/Spartanburg.tex
Spartanburg: Fix captions for 289 Manning
Spartanburg 2014: Minor formatting edits to report

@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
-%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
-%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
-%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
-% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
-%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
-%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
 3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
@@
 Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
+% 3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
+%   Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
+%   Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
+%   Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
+% 2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
+%   Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
+%   Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
 \noalign{\smallskip}\hline
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
-\caption{286 College, Test 1, Temperature TC\_A1}
+\caption{289 Manning, Test 1, Temperature TC\_A1}
 \label{fig:289_Manning_Test_1_TC_A1}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A4}
-\caption{286 College, Test 1, Temperature TC\_A4}
+\caption{289 Manning, Test 1, Temperature TC\_A4}
 \label{fig:289_Manning_Test_1_TC_A4}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A5}
-\caption{286 College, Test 1, Temperature TC\_A5}
+\caption{289 Manning, Test 1, Temperature TC\_A5}
 \label{fig:289_Manning_Test_1_TC_A5}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A6}
-\caption{286 College, Test 1, Temperature TC\_A6}
+\caption{289 Manning, Test 1, Temperature TC\_A6}
 \label{fig:289_Manning_Test_1_TC_A6}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A7}
-\caption{286 College, Test 1, Temperature TC\_A7}
+\caption{289 Manning, Test 1, Temperature TC\_A7}
 \label{fig:289_Manning_Test_1_TC_A7}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_S_1}
-\caption{286 College, Test 1, Temperature TC\_S\_1}
+\caption{289 Manning, Test 1, Temperature TC\_S\_1}
 \label{fig:289_Manning_Test_1_TC_S_1}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_HF}
-\caption{286 College, Test 1, Heat Flux}
+\caption{289 Manning, Test 1, Heat Flux}
 \label{fig:289_Manning_Test_1_HF}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_P_S_1}
-\caption{286 College, Test 1, Pressure}
+\caption{289 Manning, Test 1, Pressure}
 \label{fig:289_Manning_Test_1_P_S_1}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_GAS}
-\caption{286 College, Test 1, Gas Concentration}
+\caption{289 Manning, Test 1, Gas Concentration}
 \label{fig:289_Manning_Test_1_GAS}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A2}
-\caption{286 College, Test 2, Temperature TC\_A2}
+\caption{289 Manning, Test 2, Temperature TC\_A2}
 \label{fig:289_Manning_Test_2_TC_A2}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A3}
-\caption{286 College, Test 2, Temperature TC\_A3}
+\caption{289 Manning, Test 2, Temperature TC\_A3}
 \label{fig:289_Manning_Test_2_TC_A3}
@@
 \includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_HF}
-\caption{286 College, Test 2, Heat Flux}
+\caption{289 Manning, Test 2, Heat Flux}
 \label{fig:289_Manning_Test_2_HF}

### 2014-11-07 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add FDS files and update report

@@
 
+ the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
+Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
+Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
+That area was considered to be part of the porch fire.
+Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
+To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
+Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
+To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
+Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
+Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.5~MW in 10~s.
+The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
+The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
+The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+
+Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
+The first assumption is that the fires start at the beginning of the simulation and increase to a value of 4.5~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
@@
 \begin{lstlisting}
-&SURF ID='burner1', HRRPUA = 2000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
-&SURF ID='burner2', HRRPUA = 4500, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&SURF ID='burner1', HRRPUA = 1000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&SURF ID='burner2', HRRPUA = 2000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+
 &RAMP ID='BURN', T = 0,   F = 0.  /
@@
 &RAMP ID='BURN', T = 300, F = 1.0 /
-&OBST XB=0.6,1.2,5,6.5,0.0,0.4, SURF_IDS='burner1','INERT','INERT' /  Burner1
-&OBST XB=2.5,4,5.0,6.0,0.0,0.4, SURF_IDS='burner2','INERT','INERT' /  Burner2
+
+&OBST XB=0.5,1.0,5.5,6.5,0.0,0.4, SURF_IDS='burner1','INERT','INERT' /  Burner1
+&OBST XB=2.3,4.3,5.5,6.5,0.0,0.4, SURF_IDS='burner2','INERT','INERT' /  Burner2
 \end{lstlisting}
@@
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm (3.9~in), the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 12 for the 1.5~MW bathroom fire and 20 for the 6.75~MW basement fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm (3.9~in), the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 7 for the 0.5~MW bathroom fire and 17 for the 4.0~MW basement fire.
 Based on validation work performed for the U.S.
@@
 \footnotesize
-$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 10~$^{\circ}$C~\cite{NIOSH:Bowyer}.
+$^{*}$Initial interior temperatures were assumed to be 20~$^{\circ}$C; exterior temperatures were 10~$^{\circ}$C~\cite{PGCounty2013}.
 \normalsize
@@
 \label{results}
+
+To examine the results of the simulation, it is important to link the timelines from the fire scene to the simulation times.
+Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{PGCounty2013} along with the corresponding simulation times.
+
+\begin{table}[!ht]
+\caption[Fire incident and simulation event timeline]
+{Fire incident and simulation event timeline}
+\begin{tabular}{ccl}
+\toprule
+Incident Time  &  Simulation  &  Fire Behavior / Fireground Operation                                \\
+               &  Time        &                                                                      \\
+{(hh:mm:ss)}   &  {(s)}       &                                                                      \\
+\midrule
+21:08:26       &              &  First 911 call is made.                                             \\
+               &              &                                                                      \\
+21:11:03       &              &  Dispatch for a``box'' alarm assignment- four engine companies       \\
+               &              &  two truck companies, one rescue squad, and a com- manding officer.  \\
+               &              &                                                                      \\
+21:21:20       &  0           &  FDS simulation begins.                                              \\
+               &              &                                                                      \\
+21:12:55       &              &  FDFirst unit (Engine 807B) arrived on-scene.                        \\
+               &              &                                                                      \\
+21:13:44       &              &  Volunteer Chief 809A establishes incident command (IC).             \\
+               &              &                                                                      \\
+21:13:56       &              &  Truck 809 arrived on-scene.                                         \\
+               &              &                                                                      \\
+21:14:00       &  100         &  Front door opened.                                                  \\
+               &              &                                                                      \\
+21:14:42       &              &  Truck 809 enters structure.                                         \\
+               &              &                                                                      \\
+21:15:47       &  207         &  Front door closed over.                                             \\
+               &              &                                                                      \\
+21:15:51       &  211         &  Lower pane of front egress window broke.                            \\
+               &              &                                                                      \\
+21:16:01       &  221         &  Top pane of front egress window broke.                              \\
+               &              &                                                                      \\
+21:16:16       &              &  Truck 809 officer bailout through window.                           \\
+               &              &                                                                      \\
+21:16:44       &  280         &  Front door opened.                                                  \\
+               &              &                                                                      \\
+21:17:00       &              &  Basement door opened and water applied to fire.                     \\
+               &              &                                                                      \\
+21:17:15       &              &  Truck 809 forcible entry firefighter rescued.                       \\
+               &              &                                                                      \\
+\bottomrule
+\end{tabular}
+\footnotesize
+\\ For specific information regarding ventilation areas used in the simulation, refer to Table~\ref{tab:vents}.
+\normalsize
+\label{tab:combined_timeline}
+\end{table}
+
+\cleapage
 

### 2014-11-07 Projects/Spartanburg_2014/Report/Spartanburg.tex
Spartanburg 2014: Update figure references in report

@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/286_College}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/286_College}
 \caption{Instrumentation, 286 College}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_1st_Floor}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/489_N_Forest_1st_Floor}
 \caption{Instrumentation, 489 N. Forest, first floor}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/489_N_Forest_2nd_Floor}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/489_N_Forest_2nd_Floor}
 \caption{Instrumentation, 489 N. Forest, second floor}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/302_College}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/302_College}
 \caption{Instrumentation, 302 College}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/305_Manning}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/305_Manning}
 \caption{Instrumentation, 305 Manning}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_1st_Floor}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/289_Manning_1st_Floor}
 \caption{Instrumentation, 289 Manning, first floor}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/Instrumentation/289_Manning_Basement}
+\includegraphics[width=6.5in]{../Drawings/Instrumentation/289_Manning_Basement}
 \caption{Instrumentation, 289 Manning, basement}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_1_TC_A3}
 \caption{286 College, Test 1, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_1_TC_A4}
 \caption{286 College, Test 1, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_1_TC_S_1}
-\caption{286 College, Test 1, Temperature TC\_S\_1}
-\label{fig:286_College_Test_1_TC_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_1_TC_Other}
+\caption{286 College, Test 1, Temperature TC\_Other}
+\label{fig:286_College_Test_1_TC_Other}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_TC_A1}
 \caption{286 College, Test 2, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_TC_A2}
 \caption{286 College, Test 2, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A6}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_TC_A6}
 \caption{286 College, Test 2, Temperature TC\_A6}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A7}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_TC_A7}
 \caption{286 College, Test 2, Temperature TC\_A7}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_TC_A8}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_TC_A8}
 \caption{286 College, Test 2, Temperature TC\_A8}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_HF}
 \caption{286 College, Test 2, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_2_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_P}
 \caption{286 College, Test 2, Pressure}
-\label{fig:286_College_Test_2_P_S_1}
+\label{fig:286_College_Test_2_P}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_TC_A1}
 \caption{286 College, Test 3, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_TC_A4}
 \caption{286 College, Test 3, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_TC_A5}
 \caption{286 College, Test 3, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_HF}
 \caption{286 College, Test 3, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/286_College_Test_3_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_P}
 \caption{286 College, Test 3, Pressure}
-\label{fig:286_College_Test_3_P_S_1}
+\label{fig:286_College_Test_3_P}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A1}
 \caption{489 N. Forest, Test 1, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A2}
 \caption{489 N. Forest, Test 1, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_A3}
 \caption{489 N. Forest, Test 1, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_S_1}
-\caption{489 N. Forest, Test 1, Temperature TC\_S\_1}
-\label{fig:489_N_Forest_Test_1_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_TC_Other}
+\caption{489 N. Forest, Test 1, Temperature TC\_Other}
+\label{fig:489_N_Forest_Test_1_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_HF}
 \caption{489 N. Forest, Test 1, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_P_S_1}
-\caption{489 N. Forest, Test 1, Pressure}
-\label{fig:489_N_Forest_Test_1_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_1_GAS}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_BDP}
+\caption{489 N. Forest, Test 1, Velocity}
+\label{fig:489_N_Forest_Test_1_BDP}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_GAS}
 \caption{489 N. Forest, Test 1, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A4}
 \caption{489 N. Forest, Test 2, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A5}
 \caption{489 N. Forest, Test 2, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A6}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A6}
 \caption{489 N. Forest, Test 2, Temperature TC\_A6}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A7}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_A7}
 \caption{489 N. Forest, Test 2, Temperature TC\_A7}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_S_1}
-\caption{489 N. Forest, Test 2, Temperature TC\_S\_1}
-\label{fig:489_N_Forest_Test_2_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_TC_Other}
+\caption{489 N. Forest, Test 2, Temperature TC\_Other}
+\label{fig:489_N_Forest_Test_2_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_HF}
 \caption{489 N. Forest, Test 2, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/489_N_Forest_Test_2_P_S_1}
-\caption{489 N. Forest, Test 2, Pressure}
-\label{fig:489_N_Forest_Test_2_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_BDP}
+\caption{489 N. Forest, Test 2, Velocity}
+\label{fig:489_N_Forest_Test_2_BDP}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_TC_A1}
 \caption{302 College, Test 1, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_TC_A3}
 \caption{302 College, Test 1, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_TC_A4}
 \caption{302 College, Test 1, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_TC_A5}
 \caption{302 College, Test 1, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_TC_S_1}
-\caption{302 College, Test 1, Temperature TC\_S\_1}
-\label{fig:302_College_Test_1_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_TC_Other}
+\caption{302 College, Test 1, Temperature TC\_Other}
+\label{fig:302_College_Test_1_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_HF}
 \caption{302 College, Test 1, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_P}
 \caption{302 College, Test 1, Pressure}
-\label{fig:302_College_Test_1_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_1_GAS}
+\label{fig:302_College_Test_1_P}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_GAS}
 \caption{302 College, Test 1, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_TC_A1}
 \caption{302 College, Test 2, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_TC_A3}
 \caption{302 College, Test 2, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_TC_A4}
 \caption{302 College, Test 2, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_TC_A5}
 \caption{302 College, Test 2, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_TC_S_1}
-\caption{302 College, Test 2, Temperature TC\_S\_1}
-\label{fig:302_College_Test_2_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_TC_Other}
+\caption{302 College, Test 2, Temperature TC\_Other}
+\label{fig:302_College_Test_2_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_HF}
 \caption{302 College, Test 2, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_P}
 \caption{302 College, Test 2, Pressure}
-\label{fig:302_College_Test_2_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_2_GAS}
+\label{fig:302_College_Test_2_P}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_GAS}
 \caption{302 College, Test 2, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_A1}
 \caption{302 College, Test 3, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_A2}
 \caption{302 College, Test 3, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_A3}
 \caption{302 College, Test 3, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_A4}
 \caption{302 College, Test 3, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_A5}
 \caption{302 College, Test 3, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_TC_S_1}
-\caption{302 College, Test 3, Temperature TC\_S\_1}
-\label{fig:302_College_Test_3_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_TC_Other}
+\caption{302 College, Test 3, Temperature TC\_Other}
+\label{fig:302_College_Test_3_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_HF}
 \caption{302 College, Test 3, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_P}
 \caption{302 College, Test 3, Pressure}
-\label{fig:302_College_Test_3_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/302_College_Test_3_GAS}
+\label{fig:302_College_Test_3_P}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_GAS}
 \caption{302 College, Test 3, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A1}
 \caption{305 Manning, Test 1, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A2}
 \caption{305 Manning, Test 1, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A3}
 \caption{305 Manning, Test 1, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A4}
 \caption{305 Manning, Test 1, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A5}
 \caption{305 Manning, Test 1, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A6}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A6}
 \caption{305 Manning, Test 1, Temperature TC\_A6}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A7}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_TC_A7}
 \caption{305 Manning, Test 1, Temperature TC\_A7}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_HF}
 \caption{305 Manning, Test 1, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_P}
 \caption{305 Manning, Test 1, Pressure}
-\label{fig:305_Manning_Test_1_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_1_GAS}
+\label{fig:305_Manning_Test_1_P}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_GAS}
 \caption{305 Manning, Test 1, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A1}
 \caption{305 Manning, Test 2, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A2}
 \caption{305 Manning, Test 2, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A3}
 \caption{305 Manning, Test 2, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A4}
 \caption{305 Manning, Test 2, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A5}
 \caption{305 Manning, Test 2, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A6}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A6}
 \caption{305 Manning, Test 2, Temperature TC\_A6}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A7}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_A7}
 \caption{305 Manning, Test 2, Temperature TC\_A7}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_S_1}
-\caption{305 Manning, Test 2, Temperature TC\_S\_1}
-\label{fig:305_Manning_Test_2_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_TC_Other}
+\caption{305 Manning, Test 2, Temperature TC\_Other}
+\label{fig:305_Manning_Test_2_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_HF}
 \caption{305 Manning, Test 2, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_P_S_1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_P}
 \caption{305 Manning, Test 2, Pressure}
-\label{fig:305_Manning_Test_2_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_2_GAS}
+\label{fig:305_Manning_Test_2_P}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_GAS}
 \caption{305 Manning, Test 2, Gas Concentration}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
+% \includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
 % \caption{305 Manning, Test 3, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A1}
 \caption{289 Manning, Test 1, Temperature TC\_A1}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A4}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A4}
 \caption{289 Manning, Test 1, Temperature TC\_A4}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A5}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A5}
 \caption{289 Manning, Test 1, Temperature TC\_A5}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A6}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A6}
 \caption{289 Manning, Test 1, Temperature TC\_A6}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A7}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_A7}
 \caption{289 Manning, Test 1, Temperature TC\_A7}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_S_1}
-\caption{289 Manning, Test 1, Temperature TC\_S\_1}
-\label{fig:289_Manning_Test_1_TC_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_TC_Other}
+\caption{289 Manning, Test 1, Temperature TC\_Other}
+\label{fig:289_Manning_Test_1_TC_Other}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_HF}
 \caption{289 Manning, Test 1, Heat Flux}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_P_S_1}
-\caption{289 Manning, Test 1, Pressure}
-\label{fig:289_Manning_Test_1_P_S_1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_1_GAS}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_BDP}
+\caption{289 Manning, Test 1, Velocity}
+\label{fig:289_Manning_Test_1_BDP}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_GAS}
 \caption{289 Manning, Test 1, Gas Concentration}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A2}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A2}
 \caption{289 Manning, Test 2, Temperature TC\_A2}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A3}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_2_TC_A3}
 \caption{289 Manning, Test 2, Temperature TC\_A3}
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/Script_Figures/289_Manning_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_2_HF}
 \caption{289 Manning, Test 2, Heat Flux}

### 2014-11-12 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits based on reviewer comments

@@
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
 The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
@@
 
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
 The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
@@
 
+On the morning of June 02, 2011, the San Francisco Fire Department was dispatched to a residence based on a report from the occupant of curtains on fire.
 The account of events for this incident was documented in NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
-For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
+For this analysis, the details regarding the timeline are considered to be approximate values.
 The following narrative of the incident was extracted from the NIOSH incident report~\cite{NIOSH:Bowyer2}:
@@
 
-Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
-The cells are contained together within one larger volume known as the computational domain.
+The cells are contained together within a larger volume known as the computational domain.
 The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
 Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gases.
-One of the most important advantages of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data~\cite{FDS_Validation_Guide} to ensure that it provides the expected results, given sufficient input data.
+One of the most important aspects of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide} and validated against fire test data~\cite{FDS_Validation_Guide} to ensure that it is accurate and provides the expected results, given appropriate input data.
 A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Math_Guide}.
@@
 Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the fire simulation using traditional scientific methods such as displaying tracer particle flow, two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data such as temperature and flow vectors showing flow direction and magnitude.
+Smokeview visualizes smoke and other attributes of the fire simulation using advanced scientific methods such as displaying tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
 Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
@@
 The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
-The following information was gathered from witnesses, first responders, reports, and recorded media such as fire ground radios or photographs: information on the fire development timeline, the sequence and approximate timing of ventilation openings to the outside, and weather conditions.
+The following information was gathered from witnesses, first responders, reports from the San Francisco Fire Department and NIOSH, and recorded media such as fire ground radios or photographs: information on the fire development timeline, the sequence and approximate timing of ventilation openings to the outside, and weather conditions.
 
@@
 Based on the goals of the analysis and the information collected, several assumptions were made.
-For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known but were estimated using documentation of the potential fuel load within the structure.
+For example, the fire was in the early growth stage when firefighters arrived~\cite{NIOSH:Bowyer2}; however, the exact ignition time, fire growth rate, and transient heat release rate (HRR) of the fire were not known.
+The potential fuel load within the structure was estimated from post-incident photographs and the timeline from the NIOSH incident report.
 
@@
 
-The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located above the street level and two stories were located below the street level.
-The first and second floor (i.e., the two stories above street level) had a total interior floor area of 136~m$^2$ (1,468~ft$^2$).
+The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located at and above street level, and two stories were located below street level.
+The first floor and second floor (i.e., the two stories at and above street level) each had an interior floor area of 136~m$^2$ (1,470~ft$^2$).
 The interior walls were composed of gypsum board over insulated wood framing.
@@
 
-The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1301~ft$^2$) and consisted of a finished living area and a large utility area.
+The basement (i.e., the first story below street level) had a total floor area of 121~m$^2$ (1300~ft$^2$) and consisted of a finished living area and a large utility area.
 A laundry area was located on a landing on the interior stairwell between the first floor and basement.
@@
 
-The basement primarily contained upholstered polyurethane furniture, and the balcony was constructed of wood.
+The basement contained upholstered furniture composed primarily of polyurethane foam, and the balcony was constructed of wood.
 The upholstered furniture items located in the middle of the basement living room were very large and flat, similar to the size and geometry of a mattress.
 Therefore, the HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
-The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
+The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of geometrically similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
 Other combustible items and furnishings such as tables, stools, bookshelves, and carpet were present in the basement living room.
@@
 
-Since the exact time at which the fire started is not known relative to the notification of a fire or how quickly the fire spread, several simplifying assumptions were made.
-One assumption is that the initial couch fire in the basement was specified to start at the beginning of the simulation.
+Since the exact time at which the fire started was not known relative to the notification of a fire or how quickly the fire spread, several simplifying assumptions were made.
+One assumption was that the initial couch fire in the basement was specified to start at the beginning of the simulation.
 The duration of the fire simulation was 9~min (540~s).
@@
 
-\item The secondary fires in the basement were divided among four additional furniture items (two couches, a lounge, and a chair).
-The HRRs of these additional furniture items were estimated based on previous experimental work that characterized the HRR of similar upholstered furniture fuel items, which reported HRRs of upholstered chairs and couches ranging from 2~MW to 5~MW~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1,Janssens:2012}.
+\item The secondary fires in the basement were divided among four additional upholstered furniture items (two couches, a lounge chair, and a chair).
+The HRRs of these additional furniture items were estimated based on previous experimental work that characterized the HRR of geometrically similar upholstered furniture fuel items, which reported HRRs of upholstered chairs and couches ranging from 2~MW to 5~MW~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1,Janssens:2012}.
 The two large couches in the middle of the basement were specified with a peak HRR of 5~MW for each item.
@@
 
-Polyurethane fuel was specified for the interior basement fuel items, which can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
-The product yields are expressed in terms of the amount soot or carbon monoxide emitted per unit mass of fuel consumed~(kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
-A balanced chemical reaction for polyurethane combustion can be written as:
+Polyurethane foam was specified for the interior basement fuel items, which can be represented by the chemical formula, $\C\H_{1.8}\O_{0.30}\N_{0.05}$, with specified product yields of soot ($y_{\mathrm{s}}=0.131 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.010 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+The product yields are constant and are expressed in terms of the amount soot or carbon monoxide emitted per unit mass of fuel consumed~(kg/kg) and can be found in the Society of Fire Protection Engineers (SFPE) Handbook~\cite{SFPE:Tewarson}.
+A balanced chemical reaction for the combustion of polyurethane foam in ambient air at 40~\% relative humidity can be written as:
 \begin{multline}
@@
 
-Wood fuel was specified for the exterior basement balcony fuel items, which can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified product yields of soot ($y_{\mathrm{s}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
+Wood was specified for the exterior basement balcony fuel items, which can be represented by the chemical formula, $\C\H_{1.7}\O_{0.74}\N_{0.002}$, with specified product yields of soot ($y_{\mathrm{s}}=0.015 \; \mathrm{kg}/\mathrm{kg}$) and carbon monoxide ($y_{\mathrm{CO}}=0.004 \; \mathrm{kg}/\mathrm{kg}$)~\cite{SFPE:Tewarson}.
 A balanced chemical reaction for wood combustion can be written as:
@@
 \end{multline}
-The heat of combustion of polyurethane and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The heat of combustion of polyurethane foam and wood were specified as 26,200~kJ/kg and 16,400~kJ/kg, respectively, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion represents the amount of energy released per unit mass of the fuel.
@@
 Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing, and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
-While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
-
-Another simplification of the model is that the sources of the gas phase polyurethane and wood fuel have constant areas at fixed locations (five furniture items in the basement interior for the polyurethane fuel, and the exterior basement balcony and siding for the wood fuel).
+This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing, and extinction is based on a critical flame temperature~\cite{FDS_Math_Guide}.
+While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not a sufficient amount of information to justify deviating from the default specifications.
+
+Another simplification of the model is that the sources of the gas phase polyurethane foam and wood fuel had constant areas at fixed locations (five furniture items in the basement interior for the polyurethane foam, and the exterior basement balcony and siding for the wood fuel).
 
@@
 The specified time-dependent fuel mass flux for each fuel package corresponds to the HRRs that were described earlier.
-The HRR from each individual fuel package contributes to the total HRR shown in Fig.~\ref{fig:hrr}.
-FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
-Each fuel item was modeled as a 3D object with surfaces from which a specified amount of fuel flows into the domain, mixes with air, and burns.
+The HRR from each individual fuel package contributed to the total HRR shown in Fig.~\ref{fig:hrr}.
+FDS then determined the amount of combustion that occurred throughout the simulation based on the amount of available fuel and oxygen at a given location.
+Each fuel item was modeled as a 3D object with surfaces from which a specified amount of fuel flowed into the domain, mixed with air, and burned.
 
@@
 
-While the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties of the ceiling, walls, and floors (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage.
+Whereas the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties of the ceiling, walls, and floors (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage.
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
@@
 The ventilation times and ventilation areas represent our best understanding of the incident.
-The times of ventilation changes for doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
+The estimated times of ventilation changes for doors and windows are provided in Table~\ref{tab:ventilation_timeline}.
 
@@
 
-Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
+Air leakage in structures has been shown to be an important consideration when modeling enclosure fires~\cite{beal2009}.
 The open front door at the start of the simulation and the vents created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
-Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and was not included in this study.
+Therefore, any leakage in the structure would have a relatively negligible impact on the fluid mechanics and combustion within the structure and was not included in this study.
 
@@
 A grid resolution of 10~cm (3.9~in) was used, which resulted in a total of approximately 3.4 million computational cells.
-As a result, all of the obstructions, ventilation openings (holes, doors, and windows), and fire areas snapped to the nearest 10~cm.
+As a result, all of the obstructions, ventilation openings (doors and windows), and fire areas were snapped by FDS to the nearest 10~cm.
 Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm grid cells.
@@
 \begin{table}[!ht]
-\caption[Relevant fire model input parameters]
-{Relevant fire model input parameters}
+\caption[Fire model input parameters]
+{Fire model input parameters}
 \begin{tabular}{lll}
@@
 Ambient Temperature$^*$                           &  20~$^{\circ}$C (68~$^{\circ}$F)              &  --                                \\
-Reaction: Polyurethane~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
+Reaction: Polyurethane Foam~\cite{SFPE:Tewarson}  &  Formula: $\C\H_{1.8}\O_{0.30}\N_{0.05}$      &  Section~\ref{sec:fires}           \\
                                                   &  Soot Yield: 0.131~$\mathrm{kg}/\mathrm{kg}$  &                                    \\
@@
 
-In an FDS simulation, a HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
+In FDS, a HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
 FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
-As a result, the prescribed HRR that was input into the simulation can be different than the HRR predicted by the simulation based on the ventilation conditions.
+As a result, the prescribed HRR that was input into the simulation can be different than the HRR calculated by FDS based on the ventilation conditions.
 
@@
 time based on the fires that were described in Section~\ref{sec:fires}.
-In this figure, the solid line represents the specified (or prescribed) HRR that was input into the simulation, and the dashed line represents the predicted HRR that was output from the simulation based on the ventilation conditions.
+In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux from the fuel items), and the dashed line represents the HRR that was calculated by FDS based on the ventilation conditions.
 The vertical dashed line represents the time at which the first basement window on the rear side of the structure failed (342~s).
@@
 
-The maximum size of the fire used in this study was selected such that the conditions would become ventilation limited to minimize computational time while aligning with observations from the actual fire scenario.
+The maximum size of the fire specified in this study was selected such that the conditions aligned with observations from the actual fire incident.
 Note that the rear window failures were manually specified in accordance with the event timeline rather than specifying failure temperature criteria.
@@
 \includegraphics[width=5.5in]{../Figures/Fire_HRR_w_FDS}
-\caption[Predicted HRR vs. time from the simulation.]
-{Comparison of prescribed and predicted HRRs from the simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
+\caption[Prescribed and calculated HRR vs. time from the simulation.]
+{Comparison of prescribed and calculated HRRs from the simulation. The vertical line indicates the time at which the rear basement windows began to fail (342~s).}
 \label{fig:hrr_w_fds}
@@
 
-In Fig.~\ref{fig:hrr_w_fds}, the prescribed HRR that was input into the simulation is different than the HRR predicted by the simulation based on the ventilation conditions.
-From 0~s to 300~s, the predicted HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
-From 300~s to 342~s (the time at which the first basement window failed), the predicted HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited.
-At 315~s, the maximum predicted HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay.
-At 335~s, the HRR decreased to approximately 2~MW.
+In Fig.~\ref{fig:hrr_w_fds}, the prescribed HRR that was input into the simulation is different than the HRR calculated by FDS based on the ventilation conditions.
+From 0~s to 300~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
+From 300~s to 342~s (the time at which the first basement window failed), the calculated HRR was lower than the prescribed HRR because the fire conditions in the structure became ventilation limited.
+At 315~s, the maximum calculated HRR was approximately 7~MW before the fire conditions became ventilation limited and started to decay.
+At 335~s, the calculated HRR decreased to approximately 2~MW.
 At this time, there was an insufficient amount of oxygen in the structure to burn all of the fuel; therefore, localized burning occurred near the ventilation openings where ambient air was available.
@@
 At 342~s, the first window on the rear side of the structure failed, and additional windows failed within the next two minutes.
-As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the HRR to increase to approximately 32~MW at 385~s before it reached a steady-state value of approximately 20~MW at 465~s.
-The predicted HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.
-
-Note that the HRR in the simulation might be overpredicted due to limitations in the combustion model in FDS that are related to the reignition of fuel-rich gases.
+As additional window failures occurred (see Table~\ref{tab:ventilation_timeline}), the abrupt change in ventilation caused the calculated HRR to increase to approximately 32~MW at 385~s before it reached a steady-state value of approximately 20~MW at 465~s.
+The calculated HRR increased above the prescribed HRR because the unburned fuel and smoke that accumulated in the structure during ventilation-limited conditions was mixing with ambient air from the failed window openings and burning.
+
+Observations suggest that the peak HRR calculated by FDS might have been overpredicted due to limitations in the combustion model in FDS that are related to the reignition of fuel-rich gases.
 In other words, some combustion occurred in the simulation near the front door and second floor that was not consistent with on-scene and post-incident photographs because the fuel-rich gases mixed with fresh air and reignited.
@@
 
-As the simulated fire grew in the basement, the pressure in the basement increased and caused the hot gases to flow from a region of high pressure in the basement upwards to a region of low pressure via the interior stairwell.
-Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed in the simulation.
+As the fire grew in the basement, the simulated pressure in the basement increased and caused the hot gases to flow from a region of high pressure in the basement upwards to a region of low pressure via the interior stairwell.
+Figure~\ref{fig:smv_pressure} shows the calculated pressure conditions in the structure just before and after the rear basement window failed (342~s) in the simulation.
 
@@
 
-Gases will always flow from a region of high pressure towards a region of lower pressure.
+Gases flow from a region of high pressure towards a region of lower pressure.
 Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed upward into the interior stairwell and exited the structure via the garage door and front door.
@@
 
-The NIOSH report~\cite{NIOSH:Bowyer2} indicated that the interior stairwell on the front side of the structure was initially used by firefighters to determine that the fire was located in the basement.
+The NIOSH incident report~\cite{NIOSH:Bowyer2} indicated that firefighters located in the interior stairwell on the front side of the structure determined that the fire was located in the basement.
 From the simulation results (Section~\ref{sec:temperature}), the conditions in the interior stairwell were initially tenable.
-After the rear basement windows failed, the simulation results indicate a high-hazard area in the stairwell near the laundry room landing area that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F).
-
-After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door).
+After the rear basement windows failed, the simulation results indicate a high-hazard area in the stairwell near the laundry room landing area that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
+
+The simulation results indicate that a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door) after the rear basement windows failed.
 The rear basement window failures resulted in a rapid change in the conditions within the flow path.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the interior stairwell.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the interior stairwell.
 The two firefighters were located in the flow path between the basement and the doors on the front side of the structure.
@@
 Although firefighters wear protective gear, gear only offers a finite amount of protection.
-The polycarbonate in a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
+The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
 Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
@@
 The hot gases in the flow path were exiting the structure from the garage door and front door, as shown in Fig.~\ref{fig:flow_path_top}.
-From the NIOSH report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows temperature contours in the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.
+From the NIOSH incident report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows temperature contours of gases flowing out of the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.
 
@@
 \caption[Simulated temperature contours in the garage after basement window failure.]
-{Simulated temperature contours in the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
+{Simulated temperature contours of gases flowing out of the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_flow_path_garage}
@@
 
+The interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
+Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
 A 360$^\circ$ scene size-up by arriving firefighters can help determine the location of the fire and identify potential flow paths within a structure.
-The interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure and vent openings at the front of the structure.
-Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
 Door control can also be used to avoid creating inlet and outlet vents that could result in the establishment of a flow path.
 
-The timing of the interior attack in the basement occurred after delays in the forcible entry operations on the exterior basement door.
+The timing of the interior attack in the basement occurred after delays in the forcible entry operations on the exterior basement door~\cite{NIOSH:Bowyer2}.
 Fire suppression efforts should be coordinated with interior operations and ventilation procedures to reduce thermal hazards related to flow paths within a structure.
@@
 Table~\ref{tab:LODD} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
-This table lists the NIOSH investigation number, the outcome, and a brief description of the flow path details.
+This table lists the NIOSH report number, the outcome, and a brief description of the flow path details.
 
@@
 NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
-The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the NIOSH post-incident report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.
+The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the NIOSH report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.
 This resulted in a maximum specified source fire of approximately 20~MW in the basement and rear balcony of the structure.
@@
 
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards areas of lower pressure via the interior stairwell towards the front of the structure.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
 After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door).
 The rear basement window failures resulted in a rapid change in the conditions within the flow path.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure areas via the stairwell.
+After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
 In the interior stairwell, the flow velocities were approximately 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).

### 2014-11-12 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report

@@
 
- the underside of the roof was approximately 134~m$^2$ (1453~ft$^2$) with 7~m$^2$ (75~ft$^2$) walls on the front and rear sides.
-Additionally, there was 105~m$^2$ (1130~ft$^2$) of floor area in the attic.
-Examination of post-incident images indicated that the floor immediately over the rear porch burned away.
-That area was considered to be part of the porch fire.
-Based on post-incident damage, approximately 50~\% of the remaining floor area and 90~\% of the roof was considered to be fuel for the attic fire.
-To estimate the total attic fire size, the underside roof area (120~m$^2$), two end walls (14~m$^2$), and the floor area (43~m$^2$ or 463~ft$^2$) were included.
-Applying an HRRPUA of wood of 50~kW/m$^2$ results in a potential peak fire size of 9~MW.
-To estimate the size of the porch fire, the four walls of the porch enclosure (42~m$^2$ or 452~ft$^2$) and the floor and ceiling of the porch (24~m$^2$ or 258 ft$^2$) were included, which results in a total porch area of 66~m$^2$ (689~ft$^2$).
-Using the same HRRPUA of wood of 50~kW/m$^2$, the potential peak fire size on the porch was approximately 3.3~MW.
-Therefore, the maximum fire size for this structure was estimated to be 12.3~MW.
-Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the attic fire was specified to start at the beginning of the simulation and increase to a value of 9~MW in 10~s.
-The porch fire was specified to start 40~s into the simulation and increase to a value of 3.3~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
@@
 
-\cleapage
+\clearpage
 

### 2014-11-12 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to flow path description in abstract; fix LaTeX warnings

@@
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
-The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
+After the rear basement windows began to fail, the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 700~C (1300~F).
 Two firefighters were located in the flow path between the basement and the doors on the front side of the structure, were exposed to these elevated temperatures, and later died as a result of their injuries.},
@@
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
-
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
+After the rear basement windows began to fail, the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
 The temperature of the gases in the interior stairwell was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F).
@@
 Figure~\ref{fig:SMV_exterior_grid} shows the front and rear sides of the structure rendered in Smokeview with the 10~cm grid cells.
+
+\clearpage
 
@@
 
+\clearpage
+
 \begin{figure}[!ht]
@@
 
-The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure via the interior stairwell towards the front of the structure.
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
 After the rear basement windows failed, a flow path was established between the basement living room area and the doors located on the front side of the structure (the front door and the garage door).
 The rear basement window failures resulted in a rapid change in the conditions within the flow path.
-After the rear basement windows began to fail, the combustion gases at elevated temperature and pressure in the basement flowed upwards towards lower pressure regions via the stairwell.
 In the interior stairwell, the flow velocities were approximately 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 700~$^{\circ}$C (1300~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).

### 2014-11-12 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edits to references to FDS throughout

@@
   pdfauthor={Overholt, Kristopher J., Weinschenk, Craig G., and Madrzykowski, Daniel},
-  pdfsubject={The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
+  pdfsubject={Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
 The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
@@
 
-The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
+Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on June 2, 2011, within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
 The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
@@
 Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
+NIST has previously used Fire Dynamics Simulator (FDS) to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
 The objective of these studies has been to improve the safety and effectiveness of firefighters.
@@
 NIST examined the fire dynamics of this incident at the request of the National Institute for Occupational Safety and Health (NIOSH) and the San Francisco Fire Department.
-A computer simulation of the fire incident was conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
+A computer simulation of the fire incident was conducted using Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
 The specific objectives of the simulation detailed in this report are:
@@
 
-NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
+Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a multi-level, single-family residential structure in San Francisco, CA, that resulted in the death of two firefighters.
 The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the NIOSH report~\cite{NIOSH:Bowyer2}, post-incident pictures, and relevant literature.

### 2014-11-17 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to timeline.

@@
 21:14:42  & Truck 809 enters structure. \\[.25cm]
-21:15:47  & Front door closed over. \\[.25cm]
+21:15:47  & Basement door opened and water applied to fire. Front door closed over. \\[.25cm]
 21:15:51  & Lower pane of front egress window broke. \\[.25cm]
@@
 21:16:44  & Front door opened. \\[.25cm]
-21:17:00  & Basement door opened and water applied to fire. \\[.25cm]
 21:17:15  & Truck 809 forcible entry firefighter rescued. \\[.25cm]
@@
 \midrule
-0               &  1.40             &  Window      &  Opened     &  Rear  \\
-0               &  0.39             &  Window      &  Opened     &  Left   \\
-100             &  1.84             &  Door        &  Opened     &  Front   \\
-207             &  1.84             &  Door        &  Closed     &  Front   \\
-211             &  0.26             &  Window      &  Opened     &  Front   \\
-221             &  0.26             &  Window      &  Opened     &  Front  \\
-264             &  1.84             &  Door        &  Opened     &  Front  \\
-280             &  1.84             &  Door        &  Opened     &  Rear  \\
+0               &  1.40             &  Window      &  Opened     &  Rear  \\[.25cm]
+0               &  0.39             &  Window      &  Opened     &  Left  \\[.25cm]
+100             &  1.84             &  Door        &  Opened     &  Front \\[.25cm]
+207             &  1.84             &  Door        &  Closed     &  Front \\[.25cm]
+207             &  1.84             &  Door        &  Opened     &  Rear  \\[.25cm]
+211             &  0.26             &  Window      &  Opened     &  Front \\[.25cm]
+221             &  0.26             &  Window      &  Opened     &  Front \\[.25cm]
+267             &  1.84             &  Door        &  Opened     &  Front \\[.25cm]
 
@@
 21:15:47       &  207         &  Front door closed over.                                             \\
+               &              &  Basement door opened and water applied to fire.                     \\
                &              &                                                                      \\
@@
                &              &                                                                      \\
-21:16:44       &  280         &  Front door opened.                                                  \\
-               &              &                                                                      \\
-21:17:00       &              &  Basement door opened and water applied to fire.                     \\
+21:16:47       &  267         &  Front door opened.                                                  \\
                &              &                                                                      \\

### 2014-11-21 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, plotting script, FDS output data and input file

@@
 21:14:42  & Truck 809 enters structure. \\[.25cm]
-21:15:47  & Basement door opened and water applied to fire. Front door closed over. \\[.25cm]
+21:15:47  & Basement door opened and water applied to fire. Front door blown closed. \\[.25cm]
 21:15:51  & Lower pane of front egress window broke. \\[.25cm]
@@
 Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjecent bathoom (Fig.~\ref{fig:basement_fire}).
-At the time of the fire, the structure was vacant so the the dominant fuel was wood: exposed ceiling joists, subfloor, cabinets, and stairs.
+At the time of the fire, the structure was vacant so the the dominant fuel was wood: wood paneling on walls, exposed ceiling joists, subfloor, cabinets, and stairs.
 
@@
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the fires start at the beginning of the simulation and increase to a value of 4.5~MW in 10~s.
+The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.55~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
-The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (1 source for the kitchen, 1 source for the bathroom).
+Since the actual ignition time is unknown, the fire was ramped quickly to reflect the conditions determined from reports and post-incident images.
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations in the basement (1 source for the kitchen, 1 source for the bathroom).
+At 207~s, using a simple decay model, the fire size decreases lineraly to 25~\% of its peak value in 60~s.
+This is to account for the impact of firefighters putting water on the basement fire (Table~\ref{tab:fire_info}).
 The following lines define the source fires in the FDS input file:
@@
 \begin{lstlisting}
-&SURF ID='burner1', HRRPUA = 1000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
-&SURF ID='burner2', HRRPUA = 2000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&SURF ID='burner1', HRRPUA = 2000, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
+&SURF ID='burner2', HRRPUA = 4500, COLOR='BURNT ORANGE', RAMP_Q='BURN' /
 
@@
 &RAMP ID='BURN', T = 10,  F = 1.0 /
-&RAMP ID='BURN', T = 300, F = 1.0 /
+&RAMP ID='BURN', T = 207, F = 1.0 /
+&RAMP ID='BURN', T = 267, F = 0.25 /
+&RAMP ID='BURN', T = 300, F = 0.25 /
 
-&OBST XB=0.5,1.0,5.5,6.5,0.0,0.4, SURF_IDS='burner1','INERT','INERT' /  Burner1
-&OBST XB=2.3,4.3,5.5,6.5,0.0,0.4, SURF_IDS='burner2','INERT','INERT' /  Burner2
+&OBST XB=0.6,1.2,5,6.5,0.0,0.4, SURF_IDS='burner1','INERT','INERT' /  Burner1
+&OBST XB=2.5,4,5.0,6.0,0.0,0.4, SURF_IDS='burner2','INERT','INERT' /  Burner2
 \end{lstlisting}
@@
 
-In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
-Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
-For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
-Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
-Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
-The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
+Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
+In this figure, the text labels the prescribed steady peak HRR and the decay phase associated with firefighter water application.
+Therefore, the estimated maximum specified fire size for this structure was approximately 8.25~MW.
+Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
+A comparison of the prescribed HRR and the simulated HRR is discussed in Section~\ref{HRR}.
+
+\begin{figure}[!ht]
+\includegraphics[width=0.75\textwidth]{../Figures/Fire_HRR}
+\caption[Prescribed HRR vs. time for the simulation.]
+{Prescribed HRR vs. time for the simulation. The text labels indicate the prescribed steady peak HRR and the decay phase associated with firefighter water application.}
+\label{fig:hrr}
+\end{figure}
+
+\clearapge
 
@@
 \end{equation}   
-From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$.
+From the FDS User's Guide~\cite{FDS_Users_Guide}, the characteristic fire diameter is related to the characteristic fire size via the relation $Q^* = (D^*/D)^{5/2}$.
 Here, $D$ is the physical diameter of the base of the fire specified in the simulation.
-Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm (3.9~in), the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 7 for the 0.5~MW bathroom fire and 17 for the 4.0~MW basement fire.
+Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm (3.9~in), the characteristic fire diameter to cell size ($D^*/\dx$) ratio is 12 for the 1.8~MW bathroom fire and 20 for the 6.75~MW basement fire.
 Based on validation work performed for the U.S.
@@
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-The boundary between the 12 10~cm meshes and 5 20~cm meshes is indicated by the {\bf bold} lines.
+The boundary between the twelve 10~cm meshes and five 20~cm meshes is indicated by the {\bf bold} lines.
 Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
@@
 
-\begin{table}
+\section{Summary of Model Input Parameters}
+\label{sec:summary_of_model_inputs}
+
+Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulation that was conducted as part of this study.
+In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario results in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+
+\begin{table}[!ht]
 \centering

### 2014-11-24 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report and plotting script (centered averaging)

@@
 
-\clearapge
+\clearpage
 
@@
 \label{HRR}
+In FDS, a HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
+FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
+As a result, the prescribed HRR that was input into the simulation can be different than the HRR calculated by FDS based on the ventilation conditions.
+
+Figure~\ref{fig:PG_Total_HRR} shows the HRR vs.
+time based on the fires described in Section~\ref{fire}.
+In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR that was calculated by FDS based on the ventilation conditions.
+The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as breaking of a front window for emergency escape.
+See Table~\ref{tab:vents} for a detailed list of the ventilation that occuring during the indcident.
+The maximum size of the fire specified in this study was selected such that the conditions aligned with observations and fuel loads from the actual fire incident.
+
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/PG_Total_9MW_HRR}
+\caption[Prescribed and calculated HRR vs. time from the simulation.]
+{Comparison of prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
+\label{fig:PG_Total_HRR}
+\end{figure}
+
+In Fig.~\ref{fig:PG_Total_HRR}, the prescribed HRR that was input into the simulation is different than the HRR calculated by FDS based on the ventilation conditions.
+From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
 

### 2014-11-24 Studies/2013_PG_County/Scripts/pg_co_hrr.py

@@ -23,8 +23,8 @@ for i in FDS_9MW_20.columns:
 for i in FDS_9MW_20.columns:
     if 'FirstFloor_HRR_' in i:
         first_hrr_20mph_raw += FDS_9MW_20[i]/1000
-base_hrr_20mph = pd.rolling_mean(base_hrr_20mph_raw,15)
-first_hrr_20mph = pd.rolling_mean(first_hrr_20mph_raw,15)
+base_hrr_20mph = pd.rolling_mean(base_hrr_20mph_raw,10,center=True)
+first_hrr_20mph = pd.rolling_mean(first_hrr_20mph_raw,10,center=True)
 
 FDS_9MW_10 = pd.read_csv('../FDS_Output_Files/pg_county_10mph_9MW_devc.csv', header=1)
 base_hrr_10mph_raw = np.zeros(len(FDS_9MW_10['Time']))
@@ -49,6 +49,9 @@ for i in FDS_9MW_00.columns:
         first_hrr_00mph_raw += FDS_9MW_00[i]/1000
 base_hrr_00mph = movingaverage(base_hrr_00mph_raw,10)
 first_hrr_00mph = movingaverage(first_hrr_00mph_raw,10)
+
+print base_hrr_20mph
+
 
 HRR_theo = [None]*1000
 HRR_time = list(xrange(1000))
@@ -114,7 +117,7 @@ close()
 
 fig = figure()
 plt.plot(HRR_time,HRR_theo,'k-',mfc='none',label='Prescribed HRR',linewidth=2)
-plot(FDS_9MW_20['Time'],base_hrr_20mph+first_hrr_20mph,'b--',mfc='none',label='Calculated HRR)',linewidth=2)
+plot(FDS_9MW_20['Time'],base_hrr_20mph+first_hrr_20mph,'b--',mfc='none',label='Calculated HRR',linewidth=2)
 axvline(x=100,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=207,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=211,linestyle='-',linewidth=2,color = '#000000')

### 2014-12-01 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report

@@
 
-Figure~\ref{fig:PG_Total_HRR} shows the HRR vs.
+Figure~\ref{fig:PG_Total_HRR} shows the HRR in the structure vs.
 time based on the fires described in Section~\ref{fire}.
-In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR that was calculated by FDS based on the ventilation conditions.
-The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as breaking of a front window for emergency escape.
+In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR inside the structure that was calculated by FDS based on the ventilation conditions.
+The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as the breaking of a front window for emergency escape.
 See Table~\ref{tab:vents} for a detailed list of the ventilation that occuring during the indcident.
@@
 \includegraphics[width=5.5in]{../Figures/PG_Total_9MW_HRR}
-\caption[Prescribed and calculated HRR vs. time from the simulation.]
-{Comparison of prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
+\caption[Interior prescribed and calculated HRR vs. time from the simulation.]
+{Comparison of prescribed and calculated interior HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
 \label{fig:PG_Total_HRR}
@@
 From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
+The differences in presribed versus predicted HRR is a result of either fuel within the structure accumulating because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react.
+Fig.~\ref{fig:PG_9MW_HRR} shows the total calculated HRR within the computational domain (includes combustion occuring exterior to the structure) compared to the presribed HRR curve.
+
+\begin{figure}[!ht]
+\includegraphics[width=5.5in]{../Figures/PG_9MW_HRR}
+\caption[Prescribed and calculated HRR vs. time from the simulation.]
+{Comparison of total prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
+\label{fig:PG_9MW_HRR}
+\end{figure}
+
+0.675 MW
 

### 2014-12-01 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add figures, update plotting script and report

--- 2014-11-24 Studies/2013_PG_County/Report/PG_Co_Fire.tex
@@
 At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}.
-For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
+For the purpose of this analysis, the details regarding the time line are considered to be approximate values.
 The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel.
@@
 \end{quote}  
-From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the timeline of events.
+From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the time line of events.
 Table~\ref{tab:fire_info} represents the best estimate of the events and therefore all times should be considered as approximate.
@@
 For example, heavy smoke conditions were reported at the front of the house at the time of arrival~\cite{PGCounty2013}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event timeline (Table~\ref{tab:fire_info}) and documented observations.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event time line (Table~\ref{tab:fire_info}) and documented observations.
 The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
@@
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
-Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjecent bathoom (Fig.~\ref{fig:basement_fire}).
-At the time of the fire, the structure was vacant so the the dominant fuel was wood: wood paneling on walls, exposed ceiling joists, subfloor, cabinets, and stairs.
+Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjacent bathroom (Fig.~\ref{fig:basement_fire}).
+At the time of the fire, the structure was vacant so the the dominant fuel was wood: wood paneling on walls, exposed ceiling joists, sub-floor, cabinets, and stairs.
 
@@
 
-In addition to the state of openings within the structure, three wind scenarios were considered in this study.
-Each scenario followed the timeline of events outlined in Table~\ref{tab:vents}.
-The difference in each scenario is the wind boundary condition.
-Simulations were run with 0~m/s (0~mph), 4.5~m/s (10~mph), and 8.9~m/s (20~mph) wind velocities, all with a flow direction from the rear toward the front of the structure.
+In addition to the state of openings within the structure, outlined in Table~\ref{tab:vents}, an 8.9~m/s (20~mph) wind velocity boundary condition was included.
+The flow direction of the wind was from the rear toward the front of the structure.
 Based on local weather conditions, mean wind velocities ranged between 4.5~m/s (10~mph) and 8.9~m/s (20~mph) with gusts up to 13.4~m/s (30~mph)~\cite{PGCounty2013}.
-The case without wind was run to control for the impact of wind on the flow of hot gases within the structure.
 
@@
 \centering
-\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
+\captionof{table}{Time line of ventilation changes in the simulation}\label{tab:vents}
 \begin{tabular}{lllll}
@@
 Note the finer mesh (smaller cells) surrounding the structure and the coarser mesh on each side.
-The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the stucture (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
-Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 18~hours for the no wind case and 3~days for the 20~mph wind case.
+The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the structure (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
+Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 3~days for the 20~mph wind case.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
@@
 
-To examine the results of the simulation, it is important to link the timelines from the fire scene to the simulation times.
-Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{PGCounty2013} along with the corresponding simulation times.
+To examine the results of the simulation, it is important to link the time lines from the fire scene to the simulation times.
+Table~\ref{tab:combined_timeline} shows the fireground time line~\cite{PGCounty2013} along with the corresponding simulation times.
 
 \begin{table}[!ht]
-\caption[Fire incident and simulation event timeline]
-{Fire incident and simulation event timeline}
+\caption[Fire incident and simulation event time line]
+{Fire incident and simulation event time line}
 \begin{tabular}{ccl}
@@
 21:11:03       &              &  Dispatch for a``box'' alarm assignment- four engine companies       \\
-               &              &  two truck companies, one rescue squad, and a com- manding officer.  \\
+               &              &  two truck companies, one rescue squad, and a commanding officer.  \\
                &              &                                                                      \\
@@
 
-Figure~\ref{fig:PG_Total_HRR} shows the HRR vs.
+Figure~\ref{fig:PG_Total_HRR} shows the HRR in the structure vs.
 time based on the fires described in Section~\ref{fire}.
-In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR that was calculated by FDS based on the ventilation conditions.
-The vertical dashed lines represent the times at which ventilation occured: front door opening and closing as well as breaking of a front window for emergency escape.
-See Table~\ref{tab:vents} for a detailed list of the ventilation that occuring during the indcident.
+In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR inside the structure that was calculated by FDS based on the ventilation conditions.
+The vertical dashed lines represent the times at which ventilation occurred: front door opening and closing as well as the breaking of a front window for emergency escape.
+See Table~\ref{tab:vents} for a detailed list of the ventilation that occurring during the incident.
 The maximum size of the fire specified in this study was selected such that the conditions aligned with observations and fuel loads from the actual fire incident.
@@
 \begin{figure}[!ht]
-\includegraphics[width=5.5in]{../Figures/PG_Total_9MW_HRR}
-\caption[Prescribed and calculated HRR vs. time from the simulation.]
-{Comparison of prescribed and calculated HRRs from the simulation. The vertical lines indicate the times at ventilation occurred.}
+\includegraphics[width=5in]{../Figures/PG_Total_9MW_HRR}
+\caption[Interior prescribed and calculated interior HRRs vs. time from the simulation.]
+{Comparison of prescribed and calculated interior HRRs from the FDS simulation. The vertical lines indicate the times at which ventilation occurred.}
 \label{fig:PG_Total_HRR}
@@
 From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
+The differences in prescribed versus predicted HRR is a result of either fuel within the structure accumulating and not combusting because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react.
+Fig.~\ref{fig:PG_9MW_HRR} shows the total calculated HRR within the computational domain (includes combustion occurring exterior to the structure) compared to the prescribed HRR curve.
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/PG_9MW_HRR}
+\caption[Prescribed and total calculated HRRs vs. time from the simulation.]
+{Comparison of total prescribed and calculated HRRs within the entire computational domain from the FDS simulation. The vertical lines indicate the times at which ventilation occurred.}
+\label{fig:PG_9MW_HRR}
+\end{figure}
+
+A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicates that on average there was the equivalent of an approximate 0.675 MW fire(s) occurring through open external vents.
+This aligns with observed post-fire damage and post-incident report~\cite{PGCounty2013}.
+Fig.~\ref{fig:ext_fire_dam} shows a post-fire image of the back left corner of the structure as well as a Smokeview rendering of the fire from the FDS simulation prior to the front door being opening by firefighters.
+
+\begin{figure}[!ht]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{\includegraphics[width=.8\textwidth]{../Figures/Basement_External_Damage}} \\
+   \scalebox{1.0}{\includegraphics[width=.8\textwidth]{../Figures/Basement_FDS_Fire}} 
+\end{tabular*}
+\caption{External post-fire image of damage to the basement (top) and FDS model showing external fire prior to the front door of the structure being opened (bottom).}
+\label{fig:ext_fire_dam}
+\end{figure}
+
+After 100 seconds of simulation time, 5~\sfrac{1}{2}~minutes after the first 911 call, firefighters open the front door to make entry to the first floor of the structure.
+The change in ventilation to the structure impacted the HRR.
+After the door was opened, combustion no longer tool place outside of the structure, however as shown in Fig.~\ref{fig:PG_Basement_9MW_HRR}, the basement HRR was lower than the total HRR within the domain.
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/PG_Basement_9MW_HRR}
+\caption[Prescribed, calculated domain, and calculated basement HRRs vs. time from the simulation.]
+{Comparison of prescribed, total calculated domain HRR and basement calculated HRRs from the simulation. The vertical lines indicate the times at which ventilation occurred.}
+\label{fig:PG_Basement_9MW_HRR}
+\end{figure}
+
+The differences in HRR between the total HRR and the basement HRR can be accounted for in combustion occuring on the first floor of the structure.
+Fuel that was combusting outside of the structure due to a lack of oxygen combusts on the first floor of the structure as the open front door allows flow to occur within the structure and fuel to mix with available oxygen and react (Fig.~\ref{fig:PG_First_9MW_HRR}).
+
+\begin{figure}[!ht]
+\includegraphics[width=5in]{../Figures/PG_First_9MW_HRR}
+\caption[Prescribed and first floor calculated HRR vs. time from the simulation.]
+{Comparison of total prescribed and first floor calculated HRRs from the simulation. The vertical lines indicate the times at which ventilation occurred.}
+\label{fig:PG_First_9MW_HRR}
+\end{figure}
+
+\clearpage
 
 \section{Pressure}
+\label{pressure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
+\input{../Scripts/colorbar_metric_pres}
+\caption[Calculated pressure on first floor 1 second before door opens]
+{Calculated pressure slice on first floor of the structure 1 second prior to firefighter entry through front door.}
+\label{fig:pressure_slice_99s}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
+\input{../Scripts/colorbar_metric_pres}
+\caption[Calculated pressure on first floor 1 second after door opens]
+{Calculated pressure slice on first floor of the structure 1 second after firefighter entry through front door.}
+\label{fig:pressure_slice_101s}
+\end{figure}
 

### 2014-12-01 Studies/2013_PG_County/Scripts/pg_co_hrr.py

@@ -43,6 +43,8 @@ for i in range (0, 999):
 
 
 fig = figure()
+plt.plot(HRR_time,HRR_theo,'k-',mfc='none',label='Prescribed HRR',linewidth=2)
+plot(FDS_HRR_20['Time'],FDS_HRR_20['HRR']/1000.,'r-',mfc='none',label='Total Calculated HRR',linewidth=2)
 plot(FDS_9MW_20['Time'],base_hrr_20mph,'b--',mfc='none',label='Calculated Basement HRR',linewidth=2)
 axvline(x=100,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=207,linestyle='-',linewidth=2,color = '#000000')
@@ -50,7 +52,7 @@ axvline(x=211,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=221,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=267,linestyle='-',linewidth=2,color = '#000000')
 ax1 = gca()
-xlim([0, 300])
+xlim([100, 221])
 ax1.xaxis.set_major_locator(MaxNLocator(8))
 ax1_xlims = ax1.axis()[0:2]
 xlabel('Time (s)')
@@ -62,7 +64,7 @@ ax2.set_xticks([100,207,211,221,267])
 setp(xticks()[1], rotation=60)
 labels = ['Front Door Open', 'Front Door Closed','Bottom Bay Window Open', 'Top Bay Window Open','Front Door Open']
 ax2.set_xticklabels(labels, fontsize=8, ha='left')
-axis([0, 300, 0, 10])
+axis([100, 221, 6, 10])
 savefig('../Figures/PG_Basement_9MW_HRR.pdf',format='pdf')
 close()
 
@@ -74,7 +76,7 @@ axvline(x=211,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=221,linestyle='-',linewidth=2,color = '#000000')
 axvline(x=267,linestyle='-',linewidth=2,color = '#000000')
 ax1 = gca()
-xlim([0, 300])
+xlim([100, 221])
 ax1.xaxis.set_major_locator(MaxNLocator(8))
 ax1_xlims = ax1.axis()[0:2]
 xlabel('Time (s)')
@@ -86,13 +88,13 @@ ax2.set_xticks([100,207,211,221,267])
 setp(xticks()[1], rotation=60)
[…]

### 2014-12-02 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add color bar scripts, figures, update report

@@
 At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}.
-For the purpose of this analysis, the details regarding the time line are considered to be approximate values.
+For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
 The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel.
@@
 \end{quote}  
-From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the time line of events.
+From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the timeline of events.
 Table~\ref{tab:fire_info} represents the best estimate of the events and therefore all times should be considered as approximate.
@@
 For example, heavy smoke conditions were reported at the front of the house at the time of arrival~\cite{PGCounty2013}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event time line (Table~\ref{tab:fire_info}) and documented observations.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event timeline (Table~\ref{tab:fire_info}) and documented observations.
 The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
@@
 In addition to the state of openings within the structure, outlined in Table~\ref{tab:vents}, an 8.9~m/s (20~mph) wind velocity boundary condition was included.
-The flow direction of the wind was from the rear toward the front of the structure.
-Based on local weather conditions, mean wind velocities ranged between 4.5~m/s (10~mph) and 8.9~m/s (20~mph) with gusts up to 13.4~m/s (30~mph)~\cite{PGCounty2013}.
+The flow direction of the wind was from the rear toward the front of the structure, perpendicular to the rear of the structure.
+Based on local weather conditions, mean wind velocities ranged between 4.5~m/s (10~mph) and 8.9~m/s (20~mph) with gusts up to 13.4~m/s (30~mph) with a direction that angled toward the back left of the structure~\cite{PGCounty2013}.
 
@@
 \centering
-\captionof{table}{Time line of ventilation changes in the simulation}\label{tab:vents}
+\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
 \begin{tabular}{lllll}
@@
 
-To examine the results of the simulation, it is important to link the time lines from the fire scene to the simulation times.
-Table~\ref{tab:combined_timeline} shows the fireground time line~\cite{PGCounty2013} along with the corresponding simulation times.
+To examine the results of the simulation, it is important to link the timelines from the fire scene to the simulation times.
+Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{PGCounty2013} along with the corresponding simulation times.
 
 \begin{table}[!ht]
-\caption[Fire incident and simulation event time line]
-{Fire incident and simulation event time line}
+\caption[Fire incident and simulation event timeline]
+{Fire incident and simulation event timeline}
 \begin{tabular}{ccl}
@@
 
-The differences in HRR between the total HRR and the basement HRR can be accounted for in combustion occuring on the first floor of the structure.
+The differences in HRR between the total HRR and the basement HRR can be accounted for in combustion occurring on the first floor of the structure.
 Fuel that was combusting outside of the structure due to a lack of oxygen combusts on the first floor of the structure as the open front door allows flow to occur within the structure and fuel to mix with available oxygen and react (Fig.~\ref{fig:PG_First_9MW_HRR}).
@@
 
+The growth of the fire combined with a 8.9~m/s (20~mph) wind flowing normal to the rear of the structure caused the pressure to rise within the structure.
+Hot gases which may have built up within the structure will flow from high pressure to low pressure.
+Based on the event timeline, the front door was opened 100 seconds into the simulation, which would create a low pressure relief on the first floor.
+Due to firefighters entering the structure through the front door, the simulated pressure in the first floor prior to and just after opening the door is important.
+Figure~\ref{fig:pressure_slices} shows the calculated pressure conditions in the structure just before and after the front door was opened (100~s) in the simulation.
+
+In the top snapshot in Fig.~\ref{fig:pressure_slices}, the pressure profile shows an overpressure of approximately 200~Pa (2.9 $\times$ 10$^{-2}$~psi) prior to the door being opened.
+This pressure may be on the conservative side (over-prediction) because of wind speed fluctuations, wind direction, and small amounts of structure leakage.
+One second after the door was opened (bottom snapshot in Fig.~\ref{fig:pressure_slices}), the pressure on the first floor drops to between 75~Pa (1.1 $\times$ 10$^{-2}$~psi) and 85~Pa (1.2 $\times$ 10$^{-2}$~psi).
+Without the presence of wind, the pressure in the first floor prior to the door opening is is approximately 18~Pa (2.6 $\times$ 10$^{-3}$~psi) and after the door is opened the pressure drops to between 5~Pa (7.3 $\times$ 10$^{-4}$~psi) and 10~Pa (1.4 $\times$ 10$^{-3}$~psi).
+
+\clearpage
+
 \begin{figure}[!ht]
 \includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
+\input{../Scripts/colorbar_metric_pres} \\
+\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
 \input{../Scripts/colorbar_metric_pres}
-\caption[Calculated pressure on first floor 1 second before door opens]
-{Calculated pressure slice on first floor of the structure 1 second prior to firefighter entry through front door.}
-\label{fig:pressure_slice_99s}
+\caption[Calculated pressure on first floor 1~s before and after front door opens]
+{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
+\label{fig:pressure_slices}
 \end{figure}
 
+\clearpage
+
+\section{Velocity}
+\label{velocity}
+
+Gases flow from a region of high pressure towards a region of lower pressure.
+Once the front door opened, the gases in the basement at an elevated temperature and pressure flowed upward into the interior stairwell and exited the structure via the front door.
+The velocity contours shown in Fig.~\ref{fig:velocity_slices} indicate the magnitude of flow velocities within the structure before and after the front door is opened.
+
+In Fig.~\ref{fig:velocity_slices}, the velocity profile within the high-hazard area (first floor) is shown via two snapshots in time to illustrate the change in the interior conditions.
+The first snapshot is shown at a simulation time of 99~s, which is 1~s before the front door is opened, and the second snapshot is shown at a simulation time of 101~s, which is 1~s after the front door is opened.
+The velocity contours shown indicate that prior to the front door being opened, there is minimal flow on the first floor.
+However, after the front door is opened a flow path is established allowing the combustion products from the basement fire to flow to the first floor through the interior stairwell.
+The simulation calculated the flow to exit the structure at approximately 11~m/s (25~mph).
+
 \begin{figure}[!ht]
-\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
-\input{../Scripts/colorbar_metric_pres}
-\caption[Calculated pressure on first floor 1 second after door opens]
-{Calculated pressure slice on first floor of the structure 1 second after firefighter entry through front door.}
-\label{fig:pressure_slice_101s}
+\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_99s}
+\input{../Scripts/colorbar_metric_velo}
+\input{../Scripts/colorbar_std_velo} \\
+\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_101s}
+\input{../Scripts/colorbar_metric_velo}
+\input{../Scripts/colorbar_std_velo}
+\caption[Calculated velocity on first floor 1~s before and after front door opens]
+{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
+\label{fig:velocity_slices}
 \end{figure}
+
+\clearpage
 
@@
 \label{temp}
+
+Analysis of the temperatures from the simulation focuses on the high-hazard area of the structure: the first floor area between the front door and the top of the interior stairwell.
+The temperature contours shown in Fig.~\ref{fig:temperature_slices} indicate the gas temperatures within the structure before and after the front door was opened.
+
+\begin{figure}[!ht]
+\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_99s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp} \\
+\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_101s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Calculated temperature on first floor 1~s before and after front door opens]
+{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
+\label{fig:temperature_slices}
+\end{figure}
 

### 2014-12-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Edits based on reviewer comments

@@
 Analysis of the simulation results focuses on the hazardous conditions that developed following the development of a flow path inside of the structure.
-This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulation, Section~\ref{sec:model_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
+This document is organized as follows: Section~\ref{sec:incident_summary} provides a summary of the fire incident, Section~\ref{sec:model_description} describes the relevant model input parameters and assumptions that were used to develop the simulation, Section~\ref{sec:simulation_results} presents the simulation results, and Section~\ref{sec:discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
 Appendix~\ref{sec:drawings} contains dimensioned drawings of the basement, first, and second floors of the structure.
@@
 
-On the morning of June 02, 2011, the San Francisco Fire Department was dispatched to a residence based on a report from the occupant of curtains on fire.
+On the morning of June 02, 2011, the San Francisco Fire Department was dispatched to a residence based on a report of curtains on fire.
 The account of events for this incident was documented in NIOSH Fire Fighter Fatality Investigation and Prevention Program Report \#F2011-13~\cite{NIOSH:Bowyer2}.
@@
 The cells are contained together within a larger volume known as the computational domain.
-The CFD model computes the density, velocity, temperature, pressure, and species concentration of the gas in each cell.
+The CFD model computes the density, velocity, temperature, pressure, and gas concentrations in each cell.
 Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gases.
@@
 Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
-Smokeview visualizes smoke and other attributes of the fire simulation using advanced scientific methods such as displaying tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
+Smokeview visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
 Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
@@
 For the simulation results presented in this document, information was obtained from two primary sources.
-The following information was gathered from the fire scene: the geometry of the building and the compartments being modeled, the size and location of exterior and interior ventilation openings, and documentation of fire damage to the building.
-The following information was gathered from witnesses, first responders, reports from the San Francisco Fire Department and NIOSH, and recorded media such as fire ground radios or photographs: information on the fire development timeline, the sequence and approximate timing of ventilation openings to the outside, and weather conditions.
+The following information was gathered from the fire scene: geometry of the building and the compartments being modeled,  size and location of exterior and interior ventilation openings, and fire damage to the building.
+The following information was gathered from witnesses, first responders, reports from the San Francisco Fire Department and NIOSH, and recorded media such as fire ground radios or photographs: information on the fire development timeline, sequence and approximate timing of ventilation openings to the outside, and weather conditions.
 
@@
 The fire, which is described in Section~\ref{sec:fires}, originated in the finished living room on the basement level (near the rear side of the structure), which had a floor area of 72~m$^2$ (775~ft$^2$).
-More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:model_results}.
+More detailed discussion on the impact of the fire on the interior conditions is provided in Section~\ref{sec:simulation_results}.
 Figure~\ref{fig:post_exterior} shows the exterior of the front and rear sides of the structure after the incident.
@@
 
+The fire originated in the basement living room and was initiated by a handheld electrical appliance that was located near the rear basement windows~\cite{NIOSH:Bowyer2}.
+The closest significant fuel package was the couch located in the middle of the basement living room.
 On-scene photographs and post-incident reports were used to estimate the type of fuel, fire size, and ventilation openings on the structure.
@@
 The upholstered furniture items located in the middle of the basement living room were very large and flat, similar to the size and geometry of a mattress.
-Therefore, the HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the fire growth rate of a similar household furniture item.
+Therefore, the HRR of the initial couch fire was based on an experimentally measured HRR for a mattress fire~\cite{madrzykowski2009fire} to represent the approximate fire growth rate and magnitude of a similar household furniture item.
 The HRRs of the additional furniture items were estimated based on previous experimental work that characterized the HRR of geometrically similar upholstered furniture fuel items~\cite{madrzykowski2009fire,Madrzykowski:2,Babrauskas:1}.
@@
 
-Another simplification of the model is that the sources of the gas phase polyurethane foam and wood fuel had constant areas at fixed locations (five furniture items in the basement interior for the polyurethane foam, and the exterior basement balcony and siding for the wood fuel).
+Another simplification of the model is that the sources of the gaseous fuel from the polyurethane foam and wood had constant areas at fixed locations (five furniture items in the basement interior for the polyurethane foam, and the exterior basement balcony and siding for the wood fuel).
 
@@
 Whereas the fires were represented as fuel sources with a constant area (Section~\ref{sec:fires}), from a heat transfer perspective, it is important to define the material properties of the ceiling, walls, and floors (density, thermal conductivity, specific heat, and thickness) to account for heat transfer and energy storage.
-In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings of the structure.
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished ceilings, walls and floors in the structure.
 Table~\ref{tab:model_parameters} shows the material properties of the gypsum board that were used in the simulation.
@@
 Following Eq.~\ref{eq:mesh} and using a grid cell size of 10~cm, the ratio of the characteristic fire diameter to cell size ($D^*/\dx$) was 18 for the initial couch fire (combined HRR of 5~MW), 31 for the secondary flashover fire in the basement (combined HRR of 19~MW), and 32 for the maximum prescribed fire size in the structure (combined HRR of 20~MW).
-Therefore, the grid resolution used in this model results in a $D^*/\dx$ ratio that exceeds typical engineering values.
+Therefore, the grid resolution used in this simulation results in a $D^*/\dx$ ratio that exceeds typical engineering values.
 Note that Eq.~\ref{eq:mesh} relates to gas-phase phenomena, which is the primary concern of this study because the fires were explicitly specified instead of attempting to predict the amount of pyrolysis or flame spread in the scenario.
@@
 
-\chapter{Model Results}
-\label{sec:model_results}
-
-To examine the results of the simulation, it is important to link the timelines from the fire scene to the simulation times.
+\chapter{Simulation Results}
+\label{sec:simulation_results}
+
+To examine the results of the simulation, it is important to link the timeline from the fire scene to the simulation timeline.
 Table~\ref{tab:combined_timeline} shows the fireground timeline~\cite{NIOSH:Bowyer2} along with the corresponding simulation times.
@@
 Additional windows on the rear side of the basement continued to fail within the next two minutes.
-
-The maximum size of the fire specified in this study was selected such that the conditions aligned with observations from the actual fire incident.
 Note that the rear window failures were manually specified in accordance with the event timeline rather than specifying failure temperature criteria.
@@
 In this figure, the first photograph is shown at a simulation time of 321~s (approximately 20~s before the first rear basement window failed), the second photograph is shown at a simulation time of 349~s (approximately 10~s after the first rear basement window failed), the third photograph is shown at a simulation time of 440~s (approximately when the third rear basement window failed), and the fourth photograph is shown at a simulation time of 450~s (approximately when all of the rear basement windows had failed).
-Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the front side of the structure at approximately the time when the rear windows began to fail.
+Figure~\ref{fig:timeline_comparison_front} shows a comparison of an on-scene photograph and a Smokeview snapshot of smoke flowing out of the front side of the structure at approximately the time when the rear windows began to fail.
 
@@
 \caption[Snapshot of smoke flowing out of the doors on the front side of the structure.]
-{Comparison of an on-scene photograph and Smokeview snapshot of smoke flowing out of the doors on the front side of the structure.
+{Comparison of an on-scene photograph and a Smokeview snapshot of smoke flowing out of the doors on the front side of the structure.
 The on-scene time is indicated on the photograph (top), and the corresponding simulation time is indicated on the Smokeview snapshot (bottom).
@@
 \input{../Figures/colorbar_metric_pres}
-\caption[Simulated pressure contours on the right interior side of the structure.]
-{Simulated pressure contours on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) the first rear basement window failed.
+\caption[Simulated pressures on the right interior side of the structure.]
+{Simulated pressures on the right interior side of the structure, 2~s before (top) and 1~s after (bottom) the first rear basement window failed.
 The fire originated in the living room in the basement.}
@@
 Once the rear basement windows failed, the gases in the basement at an elevated temperature and pressure flowed upward into the interior stairwell and exited the structure via the garage door and front door.
-The velocity contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.
+The contours shown in Fig.~\ref{fig:smv_velocity} indicate the magnitude of flow velocities within the structure before and after the rear basement window failures.
 
@@
 
-The velocity vectors shown in Fig.~\ref{fig:smv_velocity_vectors} indicate the direction and magnitude of flow velocities within the structure before and after the rear basement window failures.
-Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the velocity in the interior stairwell was approximately 4~m/s (9~mph) before the rear basement windows failed and approximately 9~m/s (20~mph) after the rear basement windows failed.
+The vector arrows shown in Fig.~\ref{fig:smv_velocity_vectors} indicate the direction and magnitude of flow velocities within the structure before and after the rear basement window failures.
+Based on Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors}, the velocity in the interior stairwell was approximately 4~m/s (9~mph) before the rear basement windows failed~(340~s) and approximately 9~m/s (20~mph) after the rear basement windows failed~(402~s).
 
@@
 \input{../Figures/colorbar_std_velo}
-\caption[Simulated velocity contours on the right interior side of the structure.]
-{Simulated velocity contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+\caption[Simulated velocities on the right interior side of the structure.]
+{Simulated velocities on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
 The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
@@
 \input{../Figures/colorbar_std_velo}
-\caption[Simulated velocity vectors on the right interior side of the structure.]
-{Simulated velocity vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+\caption[Simulated velocities on the right interior side of the structure.]
+{Simulated velocities on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
 The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
@@
 Analysis of the temperatures from the simulation focuses on the high-hazard areas of the structure: the basement, and the interior stairwell that connects the basement to the front door and garage door on the front side of the structure.
-The temperature contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.
+The contours shown in Fig.~\ref{fig:smv_temperature} indicate the gas temperatures within the structure before and after the rear basement window failures.
 
@@
 
-The temperature vectors shown in Fig.~\ref{fig:smv_temperature_vectors} indicate the gas temperatures and direction of flow within the structure before and after the rear basement window failures.
+The vector arrows shown in Fig.~\ref{fig:smv_temperature_vectors} indicate the gas temperatures and direction of flow within the structure before and after the rear basement window failures.
 Based on the results shown in Figs.~\ref{fig:smv_temperature} and \ref{fig:smv_temperature_vectors}, 60~s after the rear basement windows began to fail, the temperature in the basement was in excess of 800~$^{\circ}$C (1500~$^{\circ}$F), and the temperature in the interior stairwell was in excess of 540~$^{\circ}$C (1000~$^{\circ}$F).
@@
 \input{../Figures/colorbar_std_temp}
-\caption[Simulated temperature contours on the right interior side of the structure.]
-{Simulated temperature contours on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+\caption[Simulated temperatures on the right interior side of the structure.]
+{Simulated temperatures on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
 The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
@@
 \input{../Figures/colorbar_std_temp}
-\caption[Simulated temperature vectors on the right interior side of the structure.]
-{Simulated temperature vectors on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
+\caption[Simulated temperatures on the right interior side of the structure.]
+{Simulated temperatures on the right interior side of the structure, 2~s before (top) and 60~s after (bottom) the first rear basement window failure.
 The structure and compartment labels are shown in Fig.~\ref{fig:smv_pressure}.}
@@
 Section~\ref{sec:simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell.
-Section~\ref{sec:assessing_the_hazard} examines the model results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell.
+Section~\ref{sec:assessing_the_hazard} examines the simulation results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell.
 Section~\ref{sec:tactical_condsiderations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
@@
 Two arrows located at a door or window indicate bi-directional flow at a vent opening.
-The velocity contours use the same scale as Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors} with a range of 0~m/s to 9~m/s (0~mph to 20~mph).}
+The contours use the same scale as Figs.~\ref{fig:smv_velocity} and \ref{fig:smv_velocity_vectors} with a range of 0~m/s to 9~m/s (0~mph to 20~mph).}
 \label{fig:flow_path_top}
@@
 
-Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperature contours at a height of 0.3~m (1~ft) above the floor on the first floor, 2~s before the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_1} shows a top view of the temperatures at a height of 0.3~m (1~ft) above the floor on the first floor, 2~s before the first rear basement window failed.
 At this time, the temperature of the gases in the interior stairwell were in excess of 200~$^{\circ}$C (400~$^{\circ}$F).
@@
 \input{../Figures/colorbar_std_temp}
-\caption[Simulated temperature contours on the first floor before basement window failure.]
-{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure.
+\caption[Simulated temperatures on the first floor before basement window failure.]
+{Top view of simulated temperatures on the first floor, 0.3~m (1~ft) above the floor, 2~s before the first rear basement window failure.
 The square markers indicate the locations of the downed firefighters.}
@@
 
-Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperature contours at a height of 0.3~m (1~ft) above the floor on the first floor, 60~s and 120~s after the first rear basement window failed.
+Figure~\ref{fig:smv_flow_path_top_2} shows a top view of the temperatures at a height of 0.3~m (1~ft) above the floor on the first floor, 60~s and 120~s after the first rear basement window failed.
 At a time of 60~s after the first rear basement window failed, the temperature of the gases in the interior stairwell were in excess of 540~$^{\circ}$C (1000~$^{\circ}$F), which exceeds the Class~III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
@@
 \input{../Figures/colorbar_std_temp}
-\caption[Simulated temperature contours on the first floor after basement window failure.]
-{Top view of simulated temperature contours on the first floor, 0.3~m (1~ft) above the floor, 60~s after (top) and 120~s after (bottom) the first rear basement window failure.}
+\caption[Simulated temperatures on the first floor after basement window failure.]
+{Top view of simulated temperatures on the first floor, 0.3~m (1~ft) above the floor, 60~s after (top) and 120~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_flow_path_top_2}
@@
 The hot gases in the flow path were exiting the structure from the garage door and front door, as shown in Fig.~\ref{fig:flow_path_top}.
-From the NIOSH incident report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows temperature contours of gases flowing out of the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.
+From the NIOSH incident report~\cite{NIOSH:Bowyer2}, at a time of 10:58:42 (approximately when the rear basement windows failed), another firefighting crew attempted to enter the house via the garage door into the first floor landing area leading into the basement and reported ``untenable conditions in the garage door to [the] house that [forced] them to look for an alternate way to enter the structure.'' Figure~\ref{fig:smv_flow_path_garage} shows the temperature of gases flowing out of the garage via two snapshots in time to illustrate the rapid change in the conditions at the front of the structure.
 
@@
 \input{../Figures/colorbar_std_temp}
-\caption[Simulated temperature contours in the garage after basement window failure.]
-{Simulated temperature contours of gases flowing out of the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
+\caption[Simulated temperatures in the garage after basement window failure.]
+{Simulated temperatures of gases flowing out of the garage, 2~s before (top) and 10~s after (bottom) the first rear basement window failure.}
 \label{fig:smv_flow_path_garage}

### 2014-12-03 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor edit to flow path table

@@
                                     &                     &  entry door and garage                     \\
-F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartme  \\
+F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartment  \\
 F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed           \\

### 2014-12-03 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, images, color bar scripts, add temperature images, update pressure and velocity images

@@
 \begin{figure}[!ht]
-\includegraphics[width=\textwidth]{../Figures/Basement_Fire}
+\includegraphics[width=0.8\textwidth]{../Figures/Basement_Fire}
 \caption[Plan view of basement indicating fire location.]{Plan view of the basement indicating the location of the two fires in the FDS model.}
@@
 \begin{figure}[!ht]
-\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
 \input{../Scripts/colorbar_metric_pres} \\
-\includegraphics[trim = 4in 2in 5in 2in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
 \input{../Scripts/colorbar_metric_pres}
 \caption[Calculated pressure on first floor 1~s before and after front door opens]
-{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
+{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
 \label{fig:pressure_slices}
@@
 
-In Fig.~\ref{fig:velocity_slices}, the velocity profile within the high-hazard area (first floor) is shown via two snapshots in time to illustrate the change in the interior conditions.
+In Fig.~\ref{fig:velocity_slices}, the velocity profile within the high-hazard area (first floor) is shown via two snapshots in time to illustrate the change in the interior conditions 0.91~m (3~ft) above the floor.
 The first snapshot is shown at a simulation time of 99~s, which is 1~s before the front door is opened, and the second snapshot is shown at a simulation time of 101~s, which is 1~s after the front door is opened.
@@
 \begin{figure}[!ht]
-\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_99s}
+\includegraphics[trim = 0in 1in 0in 1in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_99s}
 \input{../Scripts/colorbar_metric_velo}
 \input{../Scripts/colorbar_std_velo} \\
-\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_101s}
+\includegraphics[trim = 0in 1in 0in 1in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_101s}
 \input{../Scripts/colorbar_metric_velo}
@@
 \caption[Calculated velocity on first floor 1~s before and after front door opens]
-{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
+{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
 \label{fig:velocity_slices}
@@
 Analysis of the temperatures from the simulation focuses on the high-hazard area of the structure: the first floor area between the front door and the top of the interior stairwell.
-The temperature contours shown in Fig.~\ref{fig:temperature_slices} indicate the gas temperatures within the structure before and after the front door was opened.
+The temperature contours shown in Fig.~\ref{fig:temperature_slice_99s} indicate the gas temperatures within the structure 1~s before the front door was opened 0.91~m (3~ft) above the floor.
+The overlayed arrows represrent the gas flow: the length of the lines represents speeds and the direction of the arrow represents the flow direction.
+Prior to the door opening, the open living area and kitchen on the first floor were approximately 60~$^{\circ}$C (140~$^{\circ}$F) while the peak temperatures were concentrated near the interior stairwell, 105~$^{\circ}$C (220~$^{\circ}$F).
+Note that there is very minimal flow throughout the first floor.
+Figures~\ref{fig:temperature_slice_101s} and \ref{fig:temperature_slice_105s} show gas temperature contours at 0.91~m (3~ft) above the floor, 1~s and 5~s after the front door was opened.
 
 \begin{figure}[!ht]
-\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_99s}
-\input{../Scripts/colorbar_metric_temp}
-\input{../Scripts/colorbar_std_temp} \\
-\includegraphics[trim = 1in 1in 1in 4in, clip=true, width=.65\textwidth]{../Figures/velocity_slice_101s}
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.65\textwidth]{../Figures/temperature_slice_99s}
 \input{../Scripts/colorbar_metric_temp}
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on first floor 1~s before and after front door opens]
-{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door.}
-\label{fig:temperature_slices}
+\caption[Calculated temperature on first floor 1~s before front door opened]
+{Calculated temperature contours on first floor of the structure 1~s prior to firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\label{fig:temperature_slice_99s}
 \end{figure}
+
+After the front door is opened, hot fire gases from the basement begin to flow through the interior stairwall into the first floor.
+Figure~\ref{fig:temperature_slice_101s}, 1~s after the front door was opened, shows that the temperature contours at the top of the stairwell have increased to approximately 200~$^{\circ}$C (400~$^{\circ}$F) with a hot spot that approaches 425~$^{\circ}$C (800~$^{\circ}$F).
+Figure~\ref{fig:temperature_slice_105s}, 5~s after the front door was opened, shows more significant increases in temperature.
+The area of at the top of the stairs is most between 375~$^{\circ}$C (700~$^{\circ}$F) and 425~$^{\circ}$C (800~$^{\circ}$F).
+The gas temperatures 0.91~m (3~ft) above the floor at the front door have also increased to approximately 230~$^{\circ}$C (450~$^{\circ}$F) and show increased flow velocities.
+
+\begin{figure}[!ht]
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.65\textwidth]{../Figures/temperature_slice_101s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Calculated temperature on first floor 1~s after front door opens]
+{Calculated temperature contours on first floor of the structure 1~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\label{fig:temperature_slice_101s}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.65\textwidth]{../Figures/temperature_slice_105s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Calculated temperature on first floor 5~s after front door opens]
+{Calculated temperature contours on first floor of the structure 5~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\label{fig:temperature_slice_105s}
+\end{figure}
+
+\clearpage
 
@@
 \label{discuss}
+The results of the simulation are discussed in the following sections.
+Section~\ref{simulated_flow_path} addresses the results of the simulation as they relate to the flow path that was established in the interior stairwell through the front door.
+Section~\ref{assessing_hazard} examines the model results as they relate to the hazardous conditions and exposure temperatures on the first floor.
+Section~\ref{tactical_considerations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
+
+\section{Simulated Flow Path}
+\label{simulated_flow_path}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 3in 3in 3in 2in, clip=true, width=.65\textwidth]{../Figures/flow_path_99s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Flow path vectors at front door and top of stairwell 1~s before front door is opened]
+{Flow path vectors at front door and top of stairwell 1~s before front door is opened.}
+\label{fig:flow_path_99s}
+\end{figure}
+
+\section{Assessing the Hazard}
+\label{assessing_hazard}
+
+\clearpage
+
+\section{Tactical Considerations}
+\label{tactical_considerations}
+
+In this fire incident, the initial failure of the basement windows with strong incident winds on the rear side of the structure coincided with a rapid change in the thermal conditions in the interior stairwell and first floor after the front door to the structure was opened.
+The open front door resulted in the establishment of a flow path within the interior stairwell with highly hazardous conditions.
+These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.
+
+The interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
+Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
+A 360$^\circ$ scene size-up by arriving firefighters can help determine the location of the fire and identify potential flow paths within a structure.
+Door control can also be used to avoid creating inlet and outlet vents that could result in the establishment of a flow path.
+
+Fire suppression efforts should be coordinated with interior operations and ventilation procedures to reduce thermal hazards related to flow paths within a structure.
+Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrated that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
+
+There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
+Table~\ref{tab:LODD} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
+This table lists the NIOSH report number, the outcome, and a brief description of the flow path details.
+
+Based on a review of these incidents, it is clear that fires with rapidly developing or changing flow paths are a significant hazard to the fire service.
+The development of (or changes to) a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
+Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.
+Uncoordinated ventilation procedures can also be the cause of increased thermal hazards within a flow path.
+
+\begin{table}[!ht]
+\caption[Flow path related LODD/LODI incidents]
+{Flow path related LODD/LODI incidents}
+\begin{tabular}{lll}
+\toprule
+NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details                                            \\
+\midrule
+99-F01   \cite{NIOSH:Pettit}        &  3 LODDs            &  From apartment into hallway on 10th     \\
+                                    &                     &  floor of high-rise apartment building   \\
+99-F21   \cite{NIOSH:Washenitz}     &  2 LODDs            &  Basement to 1st floor                   \\
+                                    &  2 LODIs            &                                          \\
+F2000-04 \cite{NIOSH:Mezzanotte}    &  3 LODDs            &  1st floor to 2nd floor                  \\
+                                    &  3 civilian deaths  &                                          \\
+F2000-16 \cite{NIOSH:McFall}        &  1 LODD             &  2nd floor hallway through               \\
+                                    &  1 LODI             &  2nd floor apartment                     \\
+                                    &  1 civilian death   &                                          \\
+F2000-23 \cite{NIOSH:McFall2}       &  1 LODD             &  From ground level to 1st floor then to  \\
+                                    &  2 LODIs            &  2nd floor, flow exited through ceiling  \\
+F2000-43 \cite{NIOSH:McFall3}       &  1 serious LODI     &  1st floor to 2nd floor                  \\
+                                    &  2 other LODIs      &                                          \\
+F2004-02 \cite{NIOSH:Berardinelli}  &  1 LODD             &  1st floor to basement                   \\
+F2005-02 \cite{NIOSH:Koedam}        &  1 LODD             &  Rear to front of the building           \\
+                                    &  4 LODIs            &                                          \\
+F2005-04 \cite{NIOSH:McFall4}       &  1 LODD             &  Basement to 1st floor                   \\
+                                    &  9 LODIs            &                                          \\
+F2007-09 \cite{NIOSH:Tarley}        &  1 LODD             &  3 story training burn - flow through    \\
+                                    &  2 LODIs            &  all levels                              \\
+F2007-35 \cite{NIOSH:Braddee}       &  4 LODIs            &  1st floor to 2nd floor                  \\
+F2009-11 \cite{NIOSH:Merinar}       &  2 LODDs            &  Rear to front of the building           \\
+F2011-13 \cite{NIOSH:Bowyer2}       &  2 LODDs            &  Lower level up stairs and through       \\
+                                    &                     &  entry door and garage                   \\
+F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartme  \\
+F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed         \\
+                                    &  1 LODI             &  porch and then into 2nd floor           \\
+\bottomrule
+\end{tabular}
+\label{tab:LODD}
+\end{table}
+
+\clearpage
 

### 2014-12-04 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Fix typo in section label

@@
 Section~\ref{sec:assessing_the_hazard} examines the simulation results as they relate to the hazardous conditions and exposure temperatures in the interior stairwell.
-Section~\ref{sec:tactical_condsiderations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
+Section~\ref{sec:tactical_considerations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
 
@@
 \section{Tactical Considerations}
-\label{sec:tactical_condsiderations}
+\label{sec:tactical_considerations}
 

### 2014-12-04 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report and temperature color bars

@@
 
+The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were injured after making entry to the first floor and had to either bail out through a window or be rescued.
+From Section~\ref{temp}, the conditions on the first floor were initially tenable.
+After the front door was opened, however, the simulation results indicate that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
+
+The simulation results indicate that a flow path was established between the basement and front side of the structure (through the front door of the first floor) after the front door was opened.
+Strong winds (8.9~m/s (20~mph)) pushed air into the rear basement through window failures combined with boyant combustion gases pressurized the structure.
+Opening the front door provided a pressure relief; this resulted in a rapid change in the conditions within the flow path.
+After the front door was opened, the combustion gases at elevated temperature and pressure in the basement  flowed towards lower pressure regions outside of the structure on the leeward side (front of structure) via the interior stairwell.
+The two firefighters were located in the flow path on first floor between the top of the interior stairwell and the front door.
+
 \begin{figure}[!ht]

### 2014-12-05 Studies/2011_San_Francisco/Report/San_Francisco_Fire.tex
San Francisco: Minor fixes based on reviewer comments

@@
 LODD \> Line of Duty Death \\
+LODI \> Line of Duty Injury \\
 NIOSH \> National Institute for Occupational Safety and Health \\
@@
 SFPE \> Society of Fire Protection Engineers \\
+UL \> Underwriters Laboratories
 \end{tabbing}
@@
 The structure was built on a sloped landscape such that, from the front side of the structure, two stories were located at and above street level, and two stories were located below street level.
-The first floor and second floor (i.e., the two stories at and above street level) each had an interior floor area of 136~m$^2$ (1,470~ft$^2$).
+The first floor and second floor (i.e., the two stories at and above street level) each had an interior floor area of 136~m$^2$ (1470~ft$^2$).
 The interior walls were composed of gypsum board over insulated wood framing.

### 2014-12-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012 Report: Introductory material and instrumentation descriptions

@@
 
+NIST FFTG
+
+Objective: To improve the safety and effectiveness of firefighters through measurement science to advance suppression tactics, examine non-traditional means of fire suppression, and transfer of the results to the fire service.
+
+Aid the fire service across the country in the most effective and safe way to fight fires.
+
+The goal is to improve the safety of not only the responding firefighters but the public as well through the use of modern fire suppression tactics for modern fires.
+
+Approach: Real scale, instrumented fire suppression experiments.
+
+This is an STRS project that has been complemented with OA studies funding from: 
+Cal Poly 
+FDNY 
+ISFSI 
+NYU
+
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.
+The studies have resulted in guidance to the fire service regarding ventilation tactics.
+However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.
+
+Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice.
+This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
+
+Test Objectives:
+
+1)	Examine the water distribution for solid streams, straight streams, and fog streams.
+
+2)	Examine the impact of solid streams, straight streams, and fog streams on the cooling of fire gases inside a structure with various flow path configurations, structure configurations, and structure volumes.
+
+Constants: 
+Building Geometry
+Fuel Load
+Fire Room Conditions at time of water flow
+Water Flow Rate – 120 gpm
+
+Variable: 
+Smooth Bore vs Narrow Fog
+
 \chapter{Experimental Setup}
 \label{chap:Experimental_Setup}
+
+WATER DISTRIBUTION
+
+Purpose:
+- Determine the appropriate location for nozzles
+- Determine water distribution
+
+Setup:
+Task Force Tips Metro 1, Fixed Gallonage (120 gpm)
+Straight Stream
+30 degree Fog
+7/8” Smooth Bore
+100 ft of 1-3/4 inch hose
+
+The hose streams were from fixed monitor nozzles simulating a firefighter with the hose line in the structure.
+
+Controlled and operated via a gate valve from the exterior.
+
+12 Experiments:
+4 SS from room
+2 Fog from room
+2 SS from Hall
+2 Fog from Hall
+1 SB from Hall
+1 SB from Room
+
+2.5 square foot collector bin.
+
+Bins were poly boxes with interlacing lips to prevent water from going in between.
+
+Measured how much of the water ended up in what part of the room.
+
+The building was sheathed in plastic for the water flow tests as to protect and preserve the structure before any fire suppression tests were conducted.
+
+Spray Distribution Summary:
+- Experiments provided nozzle placement for gas cooling and fire suppression experiments.
+- Provide a sense of the distribution of the water throughout the test space.
+
+Hallway nozzle = gas cooling
+
+Room nozzle = seat of fire
+
+FIRE SUPPRESSION
+
+Room and contents fire inside structure
+Two points of interior attack
+- Remotely activated in hallway (indirect attack)
+- Remotely activated in fire room (direct attack)
+
+Common household furnishings.
+
+Due to the limited time and resources for testing, the extremes were chosen: smooth bore and narrow fog.
+
+Straight stream from a fog nozzle was the medium between the two.
 
@@
 
+Thermocouples:
+Work through the Seebeck effect.
+Two dissimilar metals are joined together with a weld bead.
+Each metal generates a voltage, different from one another, when exposed to a thermal gradient.
+This voltage difference increases with an increase in energy to the thermocouple and through a correlation, a corresponding temperature is found.
+
 \subsubsection{Gas Cooling Experiments}
@@
 
+Total Heat Flux:
+Water cooled heat flux gauges measure both the convective and radiative heat transfer to the sensor.
+Hot and cold side of a plate simulating the hot and cold side of a thermocouple.
+The temperature gradient generates a voltage and through correlations, a total heat flux measurement is obtained.
+The sensor is water cooled to ensure a thermal gradient remains and the sensor does not reach uniform temperature.
+The sensor top is painted black to assist with radiation absorption.
+
+Radiometer:
+The radiometer is simply a total heat flux gauge with Zirconium plate atop the sensor preventing the device from recording any heat due to convective transfer.
+
 \subsubsection{Gas Cooling Experiments}
@@
 \label{subsec:Gas_Velocity}
+
+Bi-directional Probes:
+- Fire flow measurements are taken using these devices which have a high and low pressure side.
+These flows then travel to a pressure transducer.
+Through a simple conversion, the voltages are converted to pressure and finally a velocity based on the pressure and corresponding temperature measurements.
 

### 2014-12-09 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
SVN: Fix SVN properties throughout repository

@@
 
+\section{Usage}
+
+\begin{itemize}
+\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage. Keep them powered on as long as possible during testing.
+\item Plug the voltage output wires into the DAQ.
+\item Perform zero and span calibration on all analyzers.
+Use the left and right arrows to switch gas channels.
+Use shortcut keys to jump from the home measurement screen to the zero screen (F5) and span screen (F6).
+    \begin{itemize}
+    \item Flow N$_2$ and zero the CO$_2$, CO, and O$_2$ channels.
+    \item Flow CO$_2$/CO calibration gas and span the CO$_2$ and CO channels.
+    \item Use ambient air to span the O$_2$ channel.
+    \end{itemize}
+\item Use the arrow keys to set the upper ranges to the appropriate setting, which corresponds to 5~V on the output to the DAQ.
+\item Measure the delay time for the sample gas to travel through all of the plumbing (from the sample port to the analyzer).
+You can do this by holding a gas source near the sample port and measuring the time from exposing the sample port until the gas analyzer reads an increased value.
+Record this time so that the gas concentration data can be offset during data post-processing.
+\item You are ready to record gas concentration data to the DAQ.
+\end{itemize}
+
+\section{External Plumbing}
+
+{\bf Important note:} The optimal pressure at the sample inlets or calibration gas inlets is 0~psi!
+The internal pump will pull the gas sample as needed.
+The internal gas analyzer components should never be exposed to a pressure in excess of 2~psi at the sample inlet.
+Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragm.
+For the gas sample inlets, be sure to use in-line pressure regulators (max.
+2~psi) combined with bypass valves to stop and relieve any incoming excess pressure.
+For the calibration gas inlets, be sure to use bypass tees to relieve any incoming excess pressure.
+
+\subsection{Calibration Gas Plumbing}
+
+Calibration (span) gas (CO$_2$ and CO) $\rightarrow$ Bypass tee $\rightarrow$ Span gas inlet.
+
+\subsection{Sample Gas Plumbing}
+
+Sample tubes $\rightarrow$ Filter in dry ice (for scrubbing and cooling) $\rightarrow$ Sample pump (bypass value is on) $\rightarrow$ Sample inlet on gas analyzer $\rightarrow$ Outlet tube directed away from operator.
+
+\section{Uncertainty}
+
+The uncertainty of the gas concentrations is XX.
+
 \section{Internals}
@@
 An overview of the internal components of the gas analyzer is shown in Fig.~\ref{fig:gas_analyzer_5}.
-The internal pump is located in the center of the chassis, as shown in Fig.~\ref{fig:gas_analyzer_3}.
-The O$_2$ sensor is located under the foam cover.
-The CO sensor is located towards the front panel of the gas analyzer, and the CO$_2$ sensor is located towards the rear panel.
+The internal pump is located in the center of the chassis towards the front of the analyzer, as shown in Fig.~\ref{fig:gas_analyzer_3}.
+The O$_2$ sensor is located on the right side of the analyzer under the foam cover.
+The CO sensor is located on the left side of the analyzer towards the front panel, and the CO$_2$ sensor is located on the left side of the analyzer towards the rear panel.
 
@@
 \end{figure}
-
-\section{Usage}
-
-Important note: The optimal pressure from the upstream sample and calibration gas is 0~psi!
-The internal gas analyzer components should never have an upstream pressure in excess of 2~psi.
-Pressures to the gas analyzer in excess of 2~psi may damage or dislodge the internal plumbing or pump diaphragm.
-
-\begin{itemize}
-\item Turn on the gas analyzers. The gas analyzers should warm up for about one hour before usage. Keep them powered on as long as possible during testing.
-\item Perform zero and span calibration on all analyzers. The F5 and F6 keys can be used as a shortcut to go from the home measurement screen to the zero and span screens.
-    \begin{itemize}
-    \item Flow N$_2$ and zero the CO$_2$, CO, and O$_2$ channels.
-    \item Flow CO$_2$/CO calibration gas and span the CO$_2$ and CO channels.
-    \item Use ambient air to span the O$_2$ channel.
-    \end{itemize}
-\item Set the upper ranges to the appropriate setting, which corresponds to 5~V on the output to the DAQ.
-\item Measure the delay time for the sample gas to travel through all of the plumbing (from the sample port to the analyzer).
-You can do this by holding a CO$_2$ source near the sample port and measuring the time from exposing the sample port until the gas analyzer reads an increased value.
-Record this time so that the gas concentration data can be offset at a later time.
-\item You are ready to record data to the DAQ.
-\end{itemize}
-
-\section{External Plumbing}
-
-Calibration (span) gas (CO$_2$ and CO) $\rightarrow$ Bypass tee $\rightarrow$ Span gas inlet.
-
-Sample tubes $\rightarrow$ Filter in dry ice (for scrubbing and cooling) $\rightarrow$ Sample pump (bypass value is on) $\rightarrow$ Sample inlet on gas analyzer $\rightarrow$ Outlet tube directed away from operator.
-
-\section{Uncertainty}
-
-Uncertainty
 
@@
 
+\subsection{Usage}
+
+\begin{itemize}
+\item{Run 12~V power and BNC cables to each camera. Thermal imaging cameras (TICs) need only a BNC cable. Some TICs require powered PAL to NTSC converters.}
+\item{Press the record button on the DVR to record all channels.}
+\item{Press the record button and confirm to stop recording.}
+\item{When finished, use the backup option to retrieve the data to an external USB hard drive.
+Select the time range, format (.avi), and channels that you want to export, then click the backup button.}
+\end{itemize}
+
 \subsection*{FAQ}
@@
     \end{itemize}
-\item How are hard disks formatted in DVR (FAT32, exFAT, proprietary)?
+\item How are the internal and external hard disks formatted?
     \begin{itemize}
-    \item NTFS formatted
+    \item Internal: NTFS format. External: FAT32 format. Use the menu to format hard drives.
     \end{itemize}

### 2014-12-09 Projects/Exploratory_Steam/Supporting_Material/FRD_PML_SoW.tex
SVN: Fix SVN properties throughout repository

\documentclass[12pt,letterpaper]{article}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{amsmath}
\usepackage{pdfsync}
\usepackage{url}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{siunitx}
\usepackage{tabularx,ragged2e,booktabs,caption}
\usepackage{caption}
\frenchspacing
\hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=black}
\urlstyle{same}

\renewcommand{\d}{\mathrm{d}}

\title{Assessment of Fire Fighter Steam Burn Potential by Quantifying Water Vapor Transfer in Protective Ensemble}
\date{\today}

\begin{document}

\maketitle

\section{Objective}
\label{sec:objective}

To understand the potential for steam burns by quantifying the dynamic transfer of water vapor through layers of Fire Fighter Protective Clothing (FFPC).

\section{Problem}
\label{sec:problem}

Structural fire fighters work in hot and wet environment.  Water vapor, commonly addressed as steam, comes from three sources, 1) steam/water vapor generated by the fire outside the FFPC, 2) steam/water vapor generated during fire suppression outside the FFPC, and 3) perspiration inside the FFPC.

The water vapor that diffuses across the fabric layers has significant amount of heat energy that could be released if this moisture condenses on the skin of the wearer.  Condensation of water vapor/steam releases the latent heat of vaporization that has potential to produce skin burns, often referred to as steam burns.  Currently, very little is known about water vapor transfer from external fire environment through fire fighters protective clothing.

\section{New Technical Idea}
\label{sec:tech_idea}

The new technical idea is to examine a bench-scale test device for measuring water vapor transfer in protective clothing that is related to occurrence of steam burns.  The humidity generator along with the steam chamber available in Sensor Science Division (SSD), PML will be used to create humid environment that is typically found during fire suppression activities.  The water vapor that diffuses through the clothing system will be determined by measuring the rate of increase in relative humidity (RH) and temperature for a given period of time, maximum increase in relative humidity, and time it takes for the RH to reach a steady state level.  Based on these parameters, we can derive a moisture transfer index which can indicate water vapor modulating capabilities for a given fabric assembly.

\section{Impact}

Knowledge gained from the experiments performed using the newly developed test device will improve general understanding of potential for burns from external hot water vapor/steam exposure with FFPC meeting current NFPA standards.

\section{Statement of Work}

The (SSD) will conduct exposures to firefighter protective clothing samples in an instrumented mount (provided by FRD) in their environmental chamber.  The exposure conditions will be developed between the technical leads, Christopher Meyer (SSD) and Craig Weinschenk (FRD).   SSD will collect data from the environmental chamber that documents the conditions within the test area of the chamber.  FRD will provide instrumentation and collect the data from the samples.  The exposure test will be completed by January 31, 2015.

\begin{table}
\centering
\captionof{table}{Exposure Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Series \#       &  Material                   &  Duration       &  Environment       &  Reps  \\
\midrule
1               &  None                       &  Steady-State   &  Peak T \& RH   &  5  \\[.25cm]
2               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
3               &  Woven Fabric (hood)        &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
4               &  None                       &  Steady-State   &  Min T \& RH    &  5 \\[.25cm]
5               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Min T \& RH    &  5  \\[.25cm]
6               &  Woven Fabric (hood)        &  10~min$^*$     &  Min T \& RH    &  5 \\[.25cm]
7$^+$           &  None                       &  Steady-State   &  Mid T \& RH    &  5 \\[.25cm]
8$^+$           &  Full PPE (3 layer sample)  &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
9$^+$           &  Woven Fabric (hood)        &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
\bottomrule[1.25pt]
\end{tabular}
\footnotesize
\raggedright
\\ $^*$ 10 min for first replicate. Adjust as necessary.
\\ $^+$ If necessary
\normalsize
\end{table}

\clearpage

\section{Deliverables for PML}
\begin{itemize}
\item Exposure experiments completed by January 31, 2015.
\item Written report describing the test apparatus, arrangement and exposure protocol and conditions. Report delivered to Dr. Weinschenk by February 24, 2015.
\end{itemize}

\section{Technical Point of Contacts:}

SSD: Christopher Meyer \href{mailto:christopher.meyer@nist.gov}{christopher.meyer@nist.gov} EXT: 4825 \\
FRD: Craig Weinschenk \href{matilto:craig.weinschenk@nist.gov}{craig.weinschenk@nist.gov} EXT: 6899

\end{document}

### 2014-12-09 Projects/Spartanburg_2014/Report/Spartanburg.tex
SVN: Fix SVN properties throughout repository

@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_Heat_Flux}
 \caption{286 College, Test 2, Heat Flux}
-\label{fig:286_College_Test_2_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_P}
+\label{fig:286_College_Test_2_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_2_Pressure}
 \caption{286 College, Test 2, Pressure}
-\label{fig:286_College_Test_2_P}
+\label{fig:286_College_Test_2_Pressure}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_Heat_Flux}
 \caption{286 College, Test 3, Heat Flux}
-\label{fig:286_College_Test_3_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_P}
+\label{fig:286_College_Test_3_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/286_College_Test_3_Pressure}
 \caption{286 College, Test 3, Pressure}
-\label{fig:286_College_Test_3_P}
+\label{fig:286_College_Test_3_Pressure}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_Heat_Flux}
 \caption{489 N. Forest, Test 1, Heat Flux}
-\label{fig:489_N_Forest_Test_1_HF}
+\label{fig:489_N_Forest_Test_1_Heat_Flux}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_GAS}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_1_Gas}
 \caption{489 N. Forest, Test 1, Gas Concentration}
-\label{fig:489_N_Forest_Test_1_GAS}
+\label{fig:489_N_Forest_Test_1_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/489_N_Forest_Test_2_Heat_Flux}
 \caption{489 N. Forest, Test 2, Heat Flux}
-\label{fig:489_N_Forest_Test_2_HF}
+\label{fig:489_N_Forest_Test_2_Heat_Flux}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_Heat_Flux}
 \caption{302 College, Test 1, Heat Flux}
-\label{fig:302_College_Test_1_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_P}
+\label{fig:302_College_Test_1_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_Pressure}
 \caption{302 College, Test 1, Pressure}
-\label{fig:302_College_Test_1_P}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_GAS}
+\label{fig:302_College_Test_1_Pressure}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_1_Gas}
 \caption{302 College, Test 1, Gas Concentration}
-\label{fig:302_College_Test_1_GAS}
+\label{fig:302_College_Test_1_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_Heat_Flux}
 \caption{302 College, Test 2, Heat Flux}
-\label{fig:302_College_Test_2_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_P}
+\label{fig:302_College_Test_2_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_Pressure}
 \caption{302 College, Test 2, Pressure}
-\label{fig:302_College_Test_2_P}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_GAS}
+\label{fig:302_College_Test_2_Pressure}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_2_Gas}
 \caption{302 College, Test 2, Gas Concentration}
-\label{fig:302_College_Test_2_GAS}
+\label{fig:302_College_Test_2_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_Heat_Flux}
 \caption{302 College, Test 3, Heat Flux}
-\label{fig:302_College_Test_3_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_P}
+\label{fig:302_College_Test_3_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_Pressure}
 \caption{302 College, Test 3, Pressure}
-\label{fig:302_College_Test_3_P}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_GAS}
+\label{fig:302_College_Test_3_Pressure}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/302_College_Test_3_Gas}
 \caption{302 College, Test 3, Gas Concentration}
-\label{fig:302_College_Test_3_GAS}
+\label{fig:302_College_Test_3_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_Heat_Flux}
 \caption{305 Manning, Test 1, Heat Flux}
-\label{fig:305_Manning_Test_1_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_P}
+\label{fig:305_Manning_Test_1_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_Pressure}
 \caption{305 Manning, Test 1, Pressure}
-\label{fig:305_Manning_Test_1_P}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_GAS}
+\label{fig:305_Manning_Test_1_Pressure}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_1_Gas}
 \caption{305 Manning, Test 1, Gas Concentration}
-\label{fig:305_Manning_Test_1_GAS}
+\label{fig:305_Manning_Test_1_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_Heat_Flux}
 \caption{305 Manning, Test 2, Heat Flux}
-\label{fig:305_Manning_Test_2_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_P}
+\label{fig:305_Manning_Test_2_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_Pressure}
 \caption{305 Manning, Test 2, Pressure}
-\label{fig:305_Manning_Test_2_P}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_GAS}
+\label{fig:305_Manning_Test_2_Pressure}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_2_Gas}
 \caption{305 Manning, Test 2, Gas Concentration}
-\label{fig:305_Manning_Test_2_GAS}
+\label{fig:305_Manning_Test_2_Gas}
 \end{figure}
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_3_HF}
+% \includegraphics[width=6.5in]{../Figures/Script_Figures/305_Manning_Test_3_Heat_Flux}
 % \caption{305 Manning, Test 3, Heat Flux}
-% \label{fig:305_Manning_Test_3_HF}
+% \label{fig:305_Manning_Test_3_Heat_Flux}
 % \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_Heat_Flux}
 \caption{289 Manning, Test 1, Heat Flux}
-\label{fig:289_Manning_Test_1_HF}
+\label{fig:289_Manning_Test_1_Heat_Flux}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_GAS}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_1_Gas}
 \caption{289 Manning, Test 1, Gas Concentration}
-\label{fig:289_Manning_Test_1_GAS}
+\label{fig:289_Manning_Test_1_Gas}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_2_HF}
+\includegraphics[width=6.5in]{../Figures/Script_Figures/289_Manning_Test_2_Heat_Flux}
 \caption{289 Manning, Test 2, Heat Flux}
-\label{fig:289_Manning_Test_2_HF}
+\label{fig:289_Manning_Test_2_Heat_Flux}
 \end{figure}

### 2014-12-09 Studies/2012_Chicago/Report/Chicago_Fire.tex
Chicago: update to front matter for DOI link info
SVN: Fix SVN properties throughout repository

@@
 Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.1838 \\
-CODEN: NTNOEF }
+CODEN: NTNOEF}
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\endgroup
 

### 2014-12-19 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: add figures for flow path and update report

--- 2014-12-04 Studies/2013_PG_County/Report/PG_Co_Fire.tex
@@
                &              &                                                                      \\
-21:12:55       &              &  FDFirst unit (Engine 807B) arrived on-scene.                        \\
+21:12:55       &              &  First unit (Engine 807B) arrived on-scene.                          \\
                &              &                                                                      \\
@@
 The temperature contours shown in Fig.~\ref{fig:temperature_slice_99s} indicate the gas temperatures within the structure 1~s before the front door was opened 0.91~m (3~ft) above the floor.
-The overlayed arrows represrent the gas flow: the length of the lines represents speeds and the direction of the arrow represents the flow direction.
+The overlaid arrows represent the gas flow: the length of the lines represents speeds and the direction of the arrow represents the flow direction.
 Prior to the door opening, the open living area and kitchen on the first floor were approximately 60~$^{\circ}$C (140~$^{\circ}$F) while the peak temperatures were concentrated near the interior stairwell, 105~$^{\circ}$C (220~$^{\circ}$F).
@@
 
-After the front door is opened, hot fire gases from the basement begin to flow through the interior stairwall into the first floor.
-Figure~\ref{fig:temperature_slice_101s}, 1~s after the front door was opened, shows that the temperature contours at the top of the stairwell have increased to approximately 200~$^{\circ}$C (400~$^{\circ}$F) with a hot spot that approaches 425~$^{\circ}$C (800~$^{\circ}$F).
+After the front door is opened, hot fire gases from the basement begin to flow through the interior stairwell into the first floor.
+Figure~\ref{fig:temperature_slice_101s}, 1~s after the front door was opened, shows that the temperature contours at the top of the stairwell have increased to approximately 200~$^{\circ}$C (392~$^{\circ}$F) with a hot spot that approaches 425~$^{\circ}$C (800~$^{\circ}$F).
 Figure~\ref{fig:temperature_slice_105s}, 5~s after the front door was opened, shows more significant increases in temperature.
@@
 
-\begin{figure}[!ht]
-\includegraphics[trim = 3in 3in 3in 2in, clip=true, width=.65\textwidth]{../Figures/flow_path_99s}
+The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were injured after making entry to the first floor and had to either bail out through a window or be rescued through the front door.
+From Section~\ref{temp}, the conditions on the first floor were initially tenable.
+After the front door was opened, however, the simulation results indicate that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
+
+The simulation results indicate that a flow path was established between the open vents (windows and door) on the rear side of the basement and front side of the structure (through the front door of the first floor) after the front door was opened.
+Strong winds (8.9~m/s (20~mph)) pushed air into the rear side of the basement through window failures and combined with buoyant combustion gases to pressurize the structure.
+Opening the front door provided a pressure relief; this resulted in a rapid change in the conditions within the structure and the establishment of a flow path.
+After the front door was opened, the combustion gases at elevated temperature and pressure in the basement flowed towards lower pressure regions outside of the structure on the leeward side (front of structure) via the interior stairwell.
+The two injured firefighters were located in the flow path on first floor between the top of the interior stairwell and the front door.
+
+To examine the impact of opening the front door on the establishment of a flow path, flow conditions are examined along the centerline of the interior stairwell doorway and at the front door.
+Figure~\ref{fig:flow_path_99s} shows the flow vectors at the first floor stairwell doorway 1 second before the front door was opened.
+Note that length and direction of the arrow indicates the magnitude and direction of the flow respectively.
+The color of the arrow corresponds to the values from the included temperature scales.
+Therefore, a short blue arrow represents slow moving, cool gas while a long red arrow represents fast moving, high temperature gas.
+Prior to the door opening, there is minimal flow through the first floor stairwell door and the temperature peak is approximately 125~$^{\circ}$C (257~~$^{\circ}$F) as shown in Figure~\ref{fig:flow_path_99s}.
+One second after the door opened, Figure~\ref{fig:flow_path_101s}, there is noticeable flow through both the stairwell doorway and through the front door.
+Simulation temperatures at the stairwell increased to approximately 200~$^{\circ}$C (392~~$^{\circ}$F) and temperatures through the doorway are approximately 100~$^{\circ}$C (212~~$^{\circ}$F).
+These values are also shown in planar contours 1~m above the floor in Figs.~\ref{fig:velocity_slices} and \ref{fig:temperature_slice_101s} for velocity and temperature, respectively.
+
+\begin{figure}[!ht]
+\includegraphics[trim = 2.5in 0in 4in 0in, clip=true, width=.65\textwidth]{../Figures/flow_vector_99s}
 \input{../Scripts/colorbar_metric_temp}
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell 1~s before front door is opened]
-{Flow path vectors at front door and top of stairwell 1~s before front door is opened.}
+\caption[Flow path vectors at front door and top of stairwell 1~s before front door was opened]
+{Flow path vectors at front door and top of stairwell 1~s before front door was opened.}
 \label{fig:flow_path_99s}
 \end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 2.5in 0in 4in 0in, clip=true, width=.65\textwidth]{../Figures/flow_vector_101s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Flow path vectors at front door and top of stairwell 1~s after front door was opened]
+{Flow path vectors at front door and top of stairwell 1~s after front door was opened.}
+\label{fig:flow_path_101s} 
+\end{figure}
+
+\clearpage
+
+At the estimated time of firefighter entry to the first floor (142~s into the simulation; 21:14:42 according to Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
+The modeln temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
+From the approximate timeline (Table~\ref{tab:combined_timeline}), the front door was forced closed due to airflow pushing against the front door 207~s into the simulation.
+Figures~\ref{fig:flow_path_206s} and \ref{fig:flow_path_207s} show the conditions 1~s prior to and after the front door closed.
+The figures show that while the closed door stopped significant flow through the stairwell door and onto the first floor, temperature hazard for the firefighters (temperatures at or above 400~$^{\circ}$C or 750~$^{\circ}$F) remained.
+
+\begin{figure}[!ht]
+\includegraphics[trim = 2.5in 0in 4in 0in, clip=true, width=.65\textwidth]{../Figures/flow_vector_142s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Flow path vectors at front door and top of stairwell at estimated time of first floor entry]
+{Flow path vectors at front door and top of stairwell 42~s after front door was opened, the estimated time of first floor entry.}
+\label{fig:flow_path_142s}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 2.5in 0in 4in 0in, clip=true, width=.65\textwidth]{../Figures/flow_vector_206s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Flow path vectors at front door and top of stairwell 1~s before front door was closed]
+{Flow path vectors at front door and top of stairwell 1~s before front door was closed.}
+\label{fig:flow_path_206s}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim = 2.5in 0in 4in 0in, clip=true, width=.65\textwidth]{../Figures/flow_vector_207s}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp}
+\caption[Flow path vectors at front door and top of stairwell 1~s after front door was closed]
+{Flow path vectors at front door and top of stairwell 1~s after front door was closed.}
+\label{fig:flow_path_207s}
+\end{figure}
+
+\clearpage
 

### 2014-12-19 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: more updates to report

@@
 \chapter*{\centering Abstract}
+Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story plus basement, single-family residential structure in Riverdale Heights, MD, that resulted in the injury of two firefighters.
+The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
+After the front door was opened, the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F).
+Two firefighters were located in the flow path between the interior stairwell door and the front door of the structure, were exposed to these elevated temperatures, and suffered serious burn injures.
+Four additional firefighters were injured during fire operations on the first floor.
 \pagenumbering{gobble}
@@
 The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel.
-The following narrative of the incident, focused on the events which led to burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
+The following narrative of the incident, focused on the events which led to serious burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
 \begin{quote}
@@
 \chapter{Summary}
+Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a single-story plus basement, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two firefighters.
+The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the post incident report from Prince George's Country Fire/EMS~\cite{PGCounty2013}, post-incident pictures, and relevant literature.
+This resulted in a maximum specified source fire of approximately 8.5~MW in the basement.
+Based on the limited ventilation conditions in the basement, the FDS simulation results indicated that before the front door was opened, there was combustion occurring outside the structure at the rear basement windows which had failed prior to arrival.
+Once the front door was opened, there was sufficient oxygen for combustion to occur within the structure, which intermittent flaming combustion on the first floor.
+
+The fire originated in the basement, and the interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure through the open front door of the structure.
+After the front door was opened, a flow path was established between the basement and the front side of the structure (the front door).
+The opening of the front door resulted in a rapid change in the conditions within the flow path.
+In the interior stairwell, the flow velocities were greater than 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+
+Two firefighters were located in the flow path between the basement and the doors on the front side of the structure.
+One firefighter was able to break a window to escape the hazardous conditions and after a call for assistance the second firefighter was removed from the structure and immediate medical treatment was provided.
+The two firefighters were transported to the local medical center where they were treated for their injuries.
+Four other firefighters were injured on-scene and transported to the hospital for treatment.
 
 \chapter{Acknowledgments}
+
+The authors would like to thank XXXXX of the Prince George's County Fire/EMS Department for their assistance with this study and their dedication to improving firefighter safety.
+The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in researching and compiling the flow path related LODD/LODI incidents shown in Table~\ref{tab:LODD}.
+Finally, the authors would like to thank Joseph Willi of the University of Illinois Urbana-Champaign for his assistance in creating dimensioned drawings of the structure.
 

### 2014-12-19 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor edit to report

@@
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
-The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (2 sources for the attic, 1 source for the porch).
+The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (1 source in the basement bathroom and 1 source in the basement kitchen).
 
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.55~MW in 10~s.
+The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.5~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.

### 2014-12-23 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, modify and add figures

@@
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
-NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago}.
+NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago,Overholt:San_Francisco}.
 The objective of these studies has been to improve the safety and effectiveness of firefighters.
@@
 At the estimated time of firefighter entry to the first floor (142~s into the simulation; 21:14:42 according to Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
-The modeln temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
+Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the incident wind  speed (9~m/s or 20~mph) because of the addition of the bouyancy of the fire plume.
+The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
 From the approximate timeline (Table~\ref{tab:combined_timeline}), the front door was forced closed due to airflow pushing against the front door 207~s into the simulation.
@@
 \label{assessing_hazard}
+A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
+Although firefighters wear protective gear, gear only offers a finite amount of protection.
+The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
+Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
+Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
+Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}.
+Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
+
+\begin{figure}[!ht]
+\begin{subfigure}{0.65\textwidth}
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_99s} \\
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_99s} 
+\end{subfigure}
+\begin{subfigure}{0.35\textwidth}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp} \\
+\end{subfigure}
+\caption[Interior temperature contours 1~s before front door was opened]
+{Interior temperature contours 1~s before front door was opened.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
+The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\label{fig:int_temp_99s}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{subfigure}{0.65\textwidth}
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_101s} \\
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_101s} 
+\end{subfigure}
+\begin{subfigure}{0.35\textwidth}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp} \\
+\end{subfigure}
+\caption[Interior temperature contours 1~s after front door was opened]
+{Interior temperature contours 1~s after front door was opened.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
+The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\label{fig:int_temp_101s}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{subfigure}{0.65\textwidth}
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_142s} \\
+\includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_142s} 
+\end{subfigure}
+\begin{subfigure}{0.35\textwidth}
+\input{../Scripts/colorbar_metric_temp}
+\input{../Scripts/colorbar_std_temp} \\
+\end{subfigure}
+\caption[Interior temperature contours as firefighters made entry to the structure]
+{Interior temperature contours as firefighters made entry to the structure.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
+The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\label{fig:int_temp_142s}
+\end{figure}
 

### 2014-12-29 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: edits to report

@@
 
+Figures~\ref{fig:int_temp_99s} to \ref{fig:int_temp_142s} show two interior views of temperature contours at particular snapshots in time.
+The top image is a planar view through the middle of the front door (from the front to the back of the house) which shows the conditions in the living area on the first floor and the conditions in the basement just past the bottom of the stairs.
+The bottom image shows temperature contours through the middle of the interior stairwell which connected the basement to the first floor of the structure (looking from the rear of the structure towards the front).
+Prior to the front door being opened (Fig.~\ref{fig:int_temp_99s}, temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to basement of the structure: specifically the rear of the structure and under the stairwell.
+One second after the door was opened, hazard in the structure increased within the structure with the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
+At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure of 260~$^{\circ}$C (500~$^{\circ}$F).
+These high-hazard conditions within the flowpath remained until the model HRR was reduced to simulate the action of applying water the fire.
+
 \begin{figure}[!ht]
@@
 \end{figure}
+
+Based on these results and the simulation results shown in Sections~\ref{velocity} and \ref{temp}, after the front door was opened, the simulated flow path temperatures in the interior stairwell were in excess of 400~$^{\circ}$C (750~$^{\circ}$F) and the flow velocities were in excess of 9 m/s (20 mph).
+The conditions in the interior stairwell changed from tenable to high-hazard very rapidly following the opening of the front door.
+Within the structure, the hot gases and smoke were moving along the flow path from the basement towards the door located on the front side of the structure via the interior stairwell.
+The simulated temperatures are consistent with the post-incident conditions that were documented in the interior stairwell.
+
+Ongoing research and experimental work is being conducted by NIST to gain a better understanding of convective heat transfer to firefighter personal protective equipment, including firefighting gear, helmets, self-contained breathing apparatuses, etc.
+The goal of this ongoing research is to parameterize various flow path conditions (elevated temperatures and velocities) and determine their effect on the rate of heat transfer and amount of energy storage in firefighting safety equipment.
 

### 2014-12-30 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update to report

@@
 
-To calculate the total fire size, the appropriate burning area (exposed wood area) of the basement needed to be determined. Based on the floor plan of the structure,
-
-The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
-The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations (1 source in the basement bathroom and 1 source in the basement kitchen).
+To calculate the total fire size, the appropriate burning area of the basement needed to be determined.
+Based on the floor plan of the structure and post-incident images, two distinct fires were considered: 1 source in the basement bathroom and 1 source in the basement kitchen.
 
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The first assumption is that the fires start at the beginning of the simulation and increase to a value of 8.5~MW in 10~s.
+The fires started at the beginning of the simulation and increased to a value of 8.5~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
@@
 In this figure, the text labels the prescribed steady peak HRR and the decay phase associated with firefighter water application.
-Therefore, the estimated maximum specified fire size for this structure was approximately 8.25~MW.
+Therefore, the estimated maximum specified fire size for this structure was approximately 8.5~MW.
 Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.

### 2014-12-31 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report

@@
 
-The value for the heat of combustion of wood used in this simulation was~16,400 kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
+The value for the heat of combustion of wood used in this simulation was 16,400~kJ/kg, based on data provided in the SFPE Handbook~\cite{SFPE:Tewarson}.
 The heat of combustion quantifies the amount of energy per unit mass of the fuel.
@@
 Based on the floor plan of the structure and post-incident images, two distinct fires were considered: 1 source in the basement bathroom and 1 source in the basement kitchen.
+The bathroom fire was estimated to be comprised of wood paneling along the four walls (17.3~m$^2$ or 186~ft$^2$) and wood subfloors and studs along the ceiling (2.9~m$^2$ or 31~ft$^2$).
+This results in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area at 50~kW/m$^2$ or a 1~MW energy release rate.
+
+The remainder of the combustable load in the basement was lumped into the localized kitchen fire.
 
@@
 The second assumption is that the sources of the gas phase wood fuel have constant areas at fixed locations in the basement (1 source for the kitchen, 1 source for the bathroom).
-At 207~s, using a simple decay model, the fire size decreases lineraly to 25~\% of its peak value in 60~s.
+At 207~s, using a simple decay model, the fire size decreases linearly to 25~\% of its peak value in 60~s.
 This is to account for the impact of firefighters putting water on the basement fire (Table~\ref{tab:fire_info}).
@@
 As discussed in Section~\ref{geom}, the structure has dimensions of 9.14~m (30~ft) by 7.62~m (25~ft) and a total height of 7.31~m (24~ft).
-To sufficiently resolve the wind boundary condtion, the computational domain was extended beyond the volume of the structure.
+To sufficiently resolve the wind boundary condition, the computational domain was extended beyond the volume of the structure.
 The large domain led to the use of two separate grid resolutions, a 10~cm (3.9~in) resolution and a 20~cm (7.8~in) resolution.
@@
 At the estimated time of firefighter entry to the first floor (142~s into the simulation; 21:14:42 according to Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
-Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the incident wind  speed (9~m/s or 20~mph) because of the addition of the bouyancy of the fire plume.
+Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the incident wind  speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
 The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).

### 2015-01-02 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: update report

@@
 This results in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area at 50~kW/m$^2$ or a 1~MW energy release rate.
-
-The remainder of the combustable load in the basement was lumped into the localized kitchen fire.
+The remainder of the wood combustable load in the basement was lumped into the localized kitchen fire.
+The ceiling and wall areas were included in the basement kitchen and main living area totally approximately 86~m$^2$ (926~ft$^2$).
+This would result in a 4.3~MW fire.
+
+Initial simulations were conducted with the two point location fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images.
+Specifically there was insufficient fuel in the basement to drive the basement to an underventilated condition.
+At the time of the fire the structure was unoccupied~\cite{PGCounty2013}, there were additional fuels that were not accounted for: transient fuels, sparse kitchen cabinetry, and an unknown bathroom vanity among other fuels.
+A second reason is that the 50~kW/m$^2$ HRRPUA used to estimate the first size does not account for an observed increase in burning rate during wind driven fires~\cite{madrzykowski2009fire,kerber2009fire}.
+It is not clear how to quantify the impact of wind on burning rate within a structure from first principles, so several iterations of the model with increased fire sizes were run.
+The final estimated fire size was a 1.8~MW fire in the bathroom and a 6.75~MW fire in the kitchen.
+This resulted in a total peak specified fire size of 8.55~MW.
 

### 2015-01-03 Studies/2013_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report

@@
 
-November 2014}}
+January 2015}}
 
@@
 \chapter*{\centering Abstract}
-Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story plus basement, single-family residential structure in Riverdale Heights, MD, that resulted in the injury of two firefighters.
+Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two firefighters.
 The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
 The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
-After the front door was opened, the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
+After the front door was opened the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
 The temperature of the gases in the interior stairwell was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F).
 Two firefighters were located in the flow path between the interior stairwell door and the front door of the structure, were exposed to these elevated temperatures, and suffered serious burn injures.
-Four additional firefighters were injured during fire operations on the first floor.
+Five additional firefighters were injured during fire operations on the first floor.
 \pagenumbering{gobble}
@@
 \begin{enumerate}
-\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this multi-story residential structure using physics-based calculations.
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story residential structure using physics-based calculations.
 \item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
@@
 For example, heavy smoke conditions were reported at the front of the house at the time of arrival~\cite{PGCounty2013}; however, the exact ignition time, fire growth rate, and heat release rate (HRR) of the fire were not known.
-The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to event timeline (Table~\ref{tab:fire_info}) and documented observations.
-The HRR of the fire was estimated using documentation of the potential fuel load within the structure.
+The ignition time and growth rate were estimated to reduce the amount of required calculation time while adhering to the event timeline (Table~\ref{tab:fire_info}) and documented observations.
+The HRR of the fire was estimated using documentation of the potential fuel load within the structure and relevant literature.
 
@@
 This resulted in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
-The interior walls were composed of gypsum board over insulated wood framing.~\cite{PGCounty2013}.
+The interior walls were composed of gypsum board over insulated wood framing~\cite{PGCounty2013}.
 There was a single flight of stairs in the center of the structure which connected the first floor to the basement.
 
-The structure was built on a sloped landscape such that on the front side of the structure the first floor was located above street level but the basement was below street level (Fig.~\ref{fig:slope}).
+The structure was built on a sloped landscape such that on the front side of the structure the first floor was located at street level but the basement was below street level (Fig.~\ref{fig:slope}).
 On the rear side of the structure, the slope allowed the basement to be a walkout.
-Therefore, access to the structure could be made on the front side of the first floor and the rear side of the basement.
+Therefore, access to the structure could be made on the front side to the first floor and on the rear side to the basement.
 
@@
 The two firefighters were transported to the local medical center where they were treated for their injuries.
-Four other firefighters were injured on-scene and transported to the hospital for treatment.
+Five other firefighters were injured on-scene and transported to the hospital for treatment.
 

### 2015-01-07 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: rename year on PG County fire

--- 2015-01-03 Studies/2013_PG_County/Report/PG_Co_Fire.tex
@@
 The bathroom fire was estimated to be comprised of wood paneling along the four walls (17.3~m$^2$ or 186~ft$^2$) and wood subfloors and studs along the ceiling (2.9~m$^2$ or 31~ft$^2$).
-This results in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area at 50~kW/m$^2$ or a 1~MW energy release rate.
+This resulted in 20.2~m$^2$ (217~ft$^2$) of wood burning surface area or a 1~MW fire using a 50~kW/m$^2$ HRRPUA.
 The remainder of the wood combustable load in the basement was lumped into the localized kitchen fire.
-The ceiling and wall areas were included in the basement kitchen and main living area totally approximately 86~m$^2$ (926~ft$^2$).
-This would result in a 4.3~MW fire.
-
-Initial simulations were conducted with the two point location fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images.
-Specifically there was insufficient fuel in the basement to drive the basement to an underventilated condition.
-At the time of the fire the structure was unoccupied~\cite{PGCounty2013}, there were additional fuels that were not accounted for: transient fuels, sparse kitchen cabinetry, and an unknown bathroom vanity among other fuels.
-A second reason is that the 50~kW/m$^2$ HRRPUA used to estimate the first size does not account for an observed increase in burning rate during wind driven fires~\cite{madrzykowski2009fire,kerber2009fire}.
+The ceiling and wall areas included in the basement kitchen and main living area totaled approximately 86~m$^2$ (926~ft$^2$).
+This resulted in a 4.3~MW fire.
+
+Initial simulations were conducted using the two fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images.
+Specifically there was insufficient fuel to drive the basement to an underventilated condition.
+One reason is that while the structure was unoccupied at the time of the fire~\cite{PGCounty2013}, there were additional fuels that were not accounted for: transient fuels, sparse kitchen cabinetry, and an unknown bathroom vanity among other fuels.
+A second reason is that the 50~kW/m$^2$ HRRPUA used to estimate the fire size does not account for an observed increase in burning rate during wind driven fires~\cite{madrzykowski2009fire,kerber2009fire}.
 It is not clear how to quantify the impact of wind on burning rate within a structure from first principles, so several iterations of the model with increased fire sizes were run.
@@
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The fires started at the beginning of the simulation and increased to a value of 8.5~MW in 10~s.
+The fires started at the beginning of the simulation and increased to a value of 8.55~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
@@
 
-Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the three source fires.
-In this figure, the text labels the prescribed steady peak HRR and the decay phase associated with firefighter water application.
-Therefore, the estimated maximum specified fire size for this structure was approximately 8.5~MW.
+Figure~\ref{fig:hrr} shows the overall prescribed design fire for this scenario, which is the sum of the HRRs of the two source fires.
+In this figure, the text indicates the prescribed steady peak HRR and the decay phase associated with firefighter water application.
 Note that the prescribed HRR can be different than the simulated HRR calculated by FDS based on the amount of available fuel, oxygen, and ventilation.
@@
 While the fires were represented as fuel sources with a constant area (Section~\ref{fire}), from a heat transfer perspective, it is important to define the material properties (density, thermal conductivity, and specific heat) to account for heat transfer and energy storage in the ceiling, walls, and floor.
-In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the structure.
 The following lines define these materials in the FDS input file:
@@
 \label{Vents}
-The simulations in this study account for changes in the ventilation due to a combination of fire department operations (opening doors, breaking windows), fire acting on the structure (fire breaching windows/doors) and wind (restricting flow, closing doors).
-The ventilation times and ventilation areas represent our best understanding of the incident.
+The simulation in this study accounts for changes in the ventilation due to a combination of fire department operations (opening doors), fire acting on the structure (fire breaching windows) and wind (restricting flow, closing doors).
+The ventilation times and ventilation areas represent the best understanding of the incident.
 The times of ventilation changes for doors and windows are provided in Table~\ref{tab:vents}.
@@
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open rear basement door and two open windows at the start of the simulation are significantly larger than the total effective area of leakage of a structure of this type.
+The open rear basement windows at the start of the simulation are significantly larger than the total effective area of leakage of a structure of this type.
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
@@
 The large domain led to the use of two separate grid resolutions, a 10~cm (3.9~in) resolution and a 20~cm (7.8~in) resolution.
-The 10~cm resolution encompasses the structure with a total volume 14~m (46~ft) by 12~m (39ft) by 8~m (26~ft) that required a total of 1.3 million computational cells.
+The 10~cm resolution encompassed the structure with a total volume 14~m (46~ft) by 12~m (39ft) by 8~m (26~ft) that required a total of 1.3 million computational cells.
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-The 20~cm grid resolution extends the computational domain 5~m to the left and right sides and 4~m behind the 10~cm mesh to provide sufficient computational domain for the wind profile to develop around the structure.
+The 20~cm grid resolution extended the computational domain 5~m to the left and right sides and 4~m behind the 10~cm mesh to provide sufficient computational domain for the wind profile to develop around the structure.
 The mesh is coarser to cut down on computational time and because high accuracy in the fluid mechanics of the air flow far from the structure is not important in the analysis of this simulation.
@@
 Note the finer mesh (smaller cells) surrounding the structure and the coarser mesh on each side.
-The domain was divided into 12 equally sized 10~cm meshes that surround the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the structure (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
-Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 3~days for the 20~mph wind case.
+The domain was divided into 12 equally sized 10~cm meshes that surrounded the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the structure (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
+Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 3~days from over 1~week with a uniform 10~cm mesh.
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
 The boundary between the twelve 10~cm meshes and five 20~cm meshes is indicated by the {\bf bold} lines.
-Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 In this figure, the solid line represents the prescribed HRR that was input into the simulation (based on a prescribed mass flux), and the dashed line represents the HRR inside the structure that was calculated by FDS based on the ventilation conditions.
-The vertical dashed lines represent the times at which ventilation occurred: front door opening and closing as well as the breaking of a front window for emergency escape.
+The vertical lines represent the times at which ventilation occurred: front door opening and closing as well as the breaking of a front window for emergency escape.
 See Table~\ref{tab:vents} for a detailed list of the ventilation that occurring during the incident.
@@
 From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
-The differences in prescribed versus predicted HRR is a result of either fuel within the structure accumulating and not combusting because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react.
+The differences in prescribed versus predicted HRR is a result of either fuel accumulation within the structure not combusting because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react.
 Fig.~\ref{fig:PG_9MW_HRR} shows the total calculated HRR within the computational domain (includes combustion occurring exterior to the structure) compared to the prescribed HRR curve.
@@
 
-A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicates that on average there was the equivalent of an approximate 0.675 MW fire(s) occurring through open external vents.
+A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicated that on average there was the equivalent of an approximate 0.675 MW fire(s) occurring through open external vents (basement windows).
 This aligns with observed post-fire damage and post-incident report~\cite{PGCounty2013}.
@@
 Based on the event timeline, the front door was opened 100 seconds into the simulation, which would create a low pressure relief on the first floor.
-Due to firefighters entering the structure through the front door, the simulated pressure in the first floor prior to and just after opening the door is important.
+Due to firefighters entering the structure through the front door, the simulated pressure on the first floor prior to and just after opening the door is important.
 Figure~\ref{fig:pressure_slices} shows the calculated pressure conditions in the structure just before and after the front door was opened (100~s) in the simulation.
 
-In the top snapshot in Fig.~\ref{fig:pressure_slices}, the pressure profile shows an overpressure of approximately 200~Pa (2.9 $\times$ 10$^{-2}$~psi) prior to the door being opened.
+In the top snapshot in Fig.~\ref{fig:pressure_slices}, the pressure profile shows an overpressure of approximately 200~Pa (2.9 $\times$ 10$^{-2}$~psi), 1~s prior to the door being opened.
 This pressure may be on the conservative side (over-prediction) because of wind speed fluctuations, wind direction, and small amounts of structure leakage.
@@
 The temperature contours shown in Fig.~\ref{fig:temperature_slice_99s} indicate the gas temperatures within the structure 1~s before the front door was opened 0.91~m (3~ft) above the floor.
-The overlaid arrows represent the gas flow: the length of the lines represents speeds and the direction of the arrow represents the flow direction.
+The overlaid arrows represent the gas flow: the length of the lines represents the magnitude of the speed and the direction of the arrow represents the flow direction.
 Prior to the door opening, the open living area and kitchen on the first floor were approximately 60~$^{\circ}$C (140~$^{\circ}$F) while the peak temperatures were concentrated near the interior stairwell, 105~$^{\circ}$C (220~$^{\circ}$F).
@@
 After the front door is opened, hot fire gases from the basement begin to flow through the interior stairwell into the first floor.
-Figure~\ref{fig:temperature_slice_101s}, 1~s after the front door was opened, shows that the temperature contours at the top of the stairwell have increased to approximately 200~$^{\circ}$C (392~$^{\circ}$F) with a hot spot that approaches 425~$^{\circ}$C (800~$^{\circ}$F).
+Figure~\ref{fig:temperature_slice_101s}, 1~s after the front door was opened, shows that the temperature contours at the top of the stairwell have increased to approximately 200~$^{\circ}$C (392~$^{\circ}$F) with a hot spot that approached 425~$^{\circ}$C (800~$^{\circ}$F).
 Figure~\ref{fig:temperature_slice_105s}, 5~s after the front door was opened, shows more significant increases in temperature.
-The area of at the top of the stairs is most between 375~$^{\circ}$C (700~$^{\circ}$F) and 425~$^{\circ}$C (800~$^{\circ}$F).
+The area of at the top of the stairs is between 375~$^{\circ}$C (700~$^{\circ}$F) and 425~$^{\circ}$C (800~$^{\circ}$F).
 The gas temperatures 0.91~m (3~ft) above the floor at the front door have also increased to approximately 230~$^{\circ}$C (450~$^{\circ}$F) and show increased flow velocities.
@@
 From Section~\ref{temp}, the conditions on the first floor were initially tenable.
-After the front door was opened, however, the simulation results indicate that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
-
-The simulation results indicate that a flow path was established between the open vents (windows and door) on the rear side of the basement and front side of the structure (through the front door of the first floor) after the front door was opened.
+After the front door was opened, however, the simulation results indicated that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
+
+The simulation results indicate that a flow path was established between the open vents (windows) on the rear side of the basement and front side of the structure (through the front door of the first floor) after the front door was opened.
 Strong winds (8.9~m/s (20~mph)) pushed air into the rear side of the basement through window failures and combined with buoyant combustion gases to pressurize the structure.
@@
 
-To examine the impact of opening the front door on the establishment of a flow path, flow conditions are examined along the centerline of the interior stairwell doorway and at the front door.
-Figure~\ref{fig:flow_path_99s} shows the flow vectors at the first floor stairwell doorway 1 second before the front door was opened.
+To examine the impact of opening the front door on the establishment of a flow path, flow conditions are examined along the centerline of the interior stairwell doorway and through the centerline of front door.
+Figure~\ref{fig:flow_path_99s} shows the flow vectors at the first floor stairwell doorway 1~s before the front door was opened.
 Note that length and direction of the arrow indicates the magnitude and direction of the flow respectively.
@@
 Therefore, a short blue arrow represents slow moving, cool gas while a long red arrow represents fast moving, high temperature gas.
-Prior to the door opening, there is minimal flow through the first floor stairwell door and the temperature peak is approximately 125~$^{\circ}$C (257~~$^{\circ}$F) as shown in Figure~\ref{fig:flow_path_99s}.
+Prior to the door opening, there was minimal flow through the first floor stairwell door and the temperature peak is approximately 125~$^{\circ}$C (257~~$^{\circ}$F) as shown in Figure~\ref{fig:flow_path_99s}.
 One second after the door opened, Figure~\ref{fig:flow_path_101s}, there is noticeable flow through both the stairwell doorway and through the front door.
@@
 At the estimated time of firefighter entry to the first floor (142~s into the simulation; 21:14:42 according to Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
-Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the incident wind  speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
+Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the imposed wind speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
 The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
@@
 Figures~\ref{fig:flow_path_206s} and \ref{fig:flow_path_207s} show the conditions 1~s prior to and after the front door closed.
-The figures show that while the closed door stopped significant flow through the stairwell door and onto the first floor, temperature hazard for the firefighters (temperatures at or above 400~$^{\circ}$C or 750~$^{\circ}$F) remained.
+The figures show that while the closed door stopped significant flow through the stairwell door and onto the first floor, the temperature hazard for the firefighters (temperatures at or above 400~$^{\circ}$C or 750~$^{\circ}$F) remained.
 
@@
 The bottom image shows temperature contours through the middle of the interior stairwell which connected the basement to the first floor of the structure (looking from the rear of the structure towards the front).
-Prior to the front door being opened (Fig.~\ref{fig:int_temp_99s}, temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to basement of the structure: specifically the rear of the structure and under the stairwell.
-One second after the door was opened, hazard in the structure increased within the structure with the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
+Prior to the front door being opened, (Fig.~\ref{fig:int_temp_99s} shows that temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to basement of the structure: specifically the rear of the structure and under the stairwell.
+One second after the door was opened, hazard in the structure increased within the structure, the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
 At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure of 260~$^{\circ}$C (500~$^{\circ}$F).
-These high-hazard conditions within the flowpath remained until the model HRR was reduced to simulate the action of applying water the fire.
+These high-hazard conditions within the flowpath remained until the modeled HRR was reduced to simulate the action of applying water the fire.
 
@@
 \chapter{Summary}
-Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a single-story plus basement, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two firefighters.
+Fire Dynamics Simulator was used to provide insight into the fire dynamics of a fire that occurred within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two firefighters.
 The fuel, fire size, and fire growth rate that were used in the FDS simulation were estimated by taking into account all of the available information including the post incident report from Prince George's Country Fire/EMS~\cite{PGCounty2013}, post-incident pictures, and relevant literature.
 This resulted in a maximum specified source fire of approximately 8.5~MW in the basement.
-Based on the limited ventilation conditions in the basement, the FDS simulation results indicated that before the front door was opened, there was combustion occurring outside the structure at the rear basement windows which had failed prior to arrival.
-Once the front door was opened, there was sufficient oxygen for combustion to occur within the structure, which intermittent flaming combustion on the first floor.
+Based on the limited ventilation conditions in the basement, the FDS simulation results indicated that before the front door was opened, there was combustion occurring outside the structure at the rear basement windows which had failed prior to fire department arrival.
+Once the front door was opened, there was sufficient oxygen for combustion to occur within the structure, with intermittent flaming combustion on the first floor.
 

### 2015-01-07 Projects/DelCo_2014/Scripts/hose_test_plotting.py
DelCo_2014: Added new script and info files for hose test plots and new report for hose test

@@ -1,0 +1,350 @@
+#!/usr/bin/env python
+
+import os
+import numpy as np
+import pandas as pd
+from pylab import *
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+#  =================
+#  = User Settings =
+#  =================
+
+# Location of experimental data files
+data_dir = '../Experimental_Data/'
+
+# Location of file with timing information
+timings_file = '../Experimental_Data/All_Hose_Times.csv'
+
+# Location of scaling conversion files
+scaling_file_default = '../DAQ_Files/Delco_DAQ_Channel_List.csv'
+scaling_file_master = '../DAQ_Files/Master_DelCo_DAQ_Channel_List.csv'
+scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
+scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
+# results_loc = '../Experimental_Data/'
+
+# Location of test description file
+info_file = '../Experimental_Data/Description_of_Experiments.csv'
+# Hose description file
+hose_info_file = '../Experimental_Data/Description_Hose_Experiments.csv'
+
+# Duration of pre-test time for bi-directional probes and heat flux gauges (s)
+pre_test_time = 60
+
+# List of sensor groups for each plot
+sensor_groups = [['TC_A1_'], ['TC_A2_'], ['TC_A3_'], ['TC_A4_'], ['TC_A5_'],
+                 ['TC_A6_'], ['TC_A7_'], ['TC_A8_'], ['TC_A9_'], ['TC_A10_'],
+                 ['TC_A11_'], ['TC_A12_'], ['TC_A13_'], ['TC_A14_'], ['TC_A15_'],
+                 ['TC_A16_'], ['TC_A17_'], ['TC_A18_'], ['TC_A19_'],
+                 ['TC_Ignition'],
+                 ['TC_Helmet_'],
+                 ['BDP_A4_'], ['BDP_A5_'], ['BDP_A6_'], ['BDP_A7_'],
+                 ['BDP_A8_'], ['BDP_A9_'], ['BDP_A10_'], ['BDP_A11_'],
+                 ['BDP_A12_'], ['BDP_A13_'], ['BDP_A14_'], ['BDP_A15_'],
+                 ['BDP_A18_'],
+                 ['HF_', 'RAD_'],
+                 ['GAS_', 'CO_', 'CO2_', 'O2_'],
+                 ['HOSE_']]
+
[…]

### 2015-01-07 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added inventor drawings and edited report

\documentclass[12pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../../../Bibliography/commoncommands}

% Rename chapter headings
\renewcommand{\chaptername}{Section}
\renewcommand{\bibname}{References}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

% Center all figures
\makeatletter
\g@addto@macro\@floatboxreset\centering
\makeatother

\begin{document}

\bibliographystyle{unsrt}
\pagestyle{empty}

\begin{minipage}[t][9in][s]{6.25in}

\headerB{
Delco 2014
}

\headerC{
\flushright{
Daniel Madrzykowski \\
Craig G. Weinschenk \\
Kristopher J. Overholt \\
{\em Fire Research Division \\
Engineering Laboratory \\
Gaithersburg, Maryland, USA} \\ }
}

\flushright{\today \\
}

\vfill

\flushright{
\includegraphics[width=2.in]{../../../../Bibliography/nistident_flright_vec} \\[.3in]
}

\titlesigs

\end{minipage}

\newpage

\frontmatter

\pagestyle{plain}
\pagenumbering{roman}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\chapter{List of Acronyms}

\begin{tabbing}
\hspace{1.5in} \= \\
FDS \> Fire Dynamics Simulator \\
HGL \> Hot Gas Layer \\
HRR \> Heat Release Rate \\
HRRPUA \> Heat Release Rate per Unit Area \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

\mainmatter

\chapter{Introduction}
\label{chap:Introduction}

\chapter{Experimental Setup}
\label{chap:Experimental_Setup}

\section{Experimental Structure}
\label{sec:Experimental_Structure}

\subsection{Construction}
\label{sec:Construction}
Two structures, shown in Fig.~\ref{fig:struct_pics}, were used for the experiments. Each structure contained a ground level floor composed of concrete walls. The West Structure contained a second level.

\begin{figure}[!ht]
\includegraphics[width=6in]{../Pictures/east_structure}
\\~\\
\includegraphics[width=6in]{../Pictures/west_structure}
\caption{East (top) and West (bottom) Test Structures}
\label{fig:struct_pics}
\end{figure}

\clearpage

\begin{figure}[!ht]
\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_1st_Floor}
\\
\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_2nd_Floor}
\caption{West Structure ground floor (top) and 2$^{nd}$ floor (bottom) layouts.}
\label{fig:west_drawing_general}
\end{figure}

\clearpage
\section{Fuel Load}

\section{Experimental Procedure}

\chapter{Results}
\label{chap:Results}

\section{Hose Flow Tests}
\subsection{Tests 18 and 19}

Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

%\subsection{DNXAXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
%\caption{Hose pressure, Test HOSE\_DNXAXX}
%\label{fig:HOSE_DNXAXX_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DNXOXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DNXOXF}
%\label{fig:HOSE_DNXOXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DSXAXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DSXAXF}
%\label{fig:HOSE_DSXAXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{DSXOXF}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
%\caption{Hose pressure, Test HOSE\_DSXOXF}
%\label{fig:HOSE_DSXOXF_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{IXAOXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
%\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A6}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
%\caption{Hose pressure, Test HOSE\_IXAOXX}
%\label{fig:HOSE_IXAOXX_HOSE}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{IXXAXX}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
%\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A6}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
%\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
%\caption{Hose pressure, Test HOSE\_IXXAXX}
%\label{fig:HOSE_IXXAXX_HOSE}
%\end{figure}
%
%
\subsection{Tests 18 and 19}
Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.

Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in. hose with a combination nozzle. The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream. Tests 18 and 19 involved three sets of experiments, one for each type of hose stream. For each set of experiments, four different application patterns were tested. First, water was applied while the hose was in a fixed position. Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern. Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.

To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern. Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position. After 60 seconds of water flow, the stairwell door was opened. 60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds. Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\clearpage

\subsubsection{Clockwise vs. Counterclockwise Rotation}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\begin{figure}[!ht]
\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
\label{fig:Test_18_West_063014_SS_BDP_A10}
\end{figure}

\clearpage
%
%
%\section{Fire Tests}
%
%\subsection{FIRE\_FA2S1C1NCX1\_1}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{FIRE\_FA2S1C1NCX1\_2}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
%\end{figure}
%
%
%\clearpage
%
%
%\subsection{FIRE\_FA2S1C1NCX1\_3}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_HF}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
%\end{figure}
%
%\begin{figure}[!ht]
%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
%\end{figure}
%
%
%\clearpage

\chapter{Conclusions}
\label{chap:Conclusions}

\chapter{Acknowledgments}
\label{chap:Acknowledgments}

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}

\appendix

\chapter{Appendix A}

Placeholder

\end{document}

### 2015-01-07 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -313,6 +313,7 @@ for f in os.listdir(data_dir):
         xlim(0, len(SS_data))
         ax1.xaxis.set_major_locator(MaxNLocator(8))
         ax1_xlims = ax1.axis()[0:2]
+        ax1.axhspan(0, 0, color='0.50', lw=1)
         # grid(True)
         xlabel('Time', fontsize=20)
         ylabel('Velocity (m/s)', fontsize=20)

### 2015-01-08 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo: clean up hose tests
DelCo_2014_Hose: minor update to report
DelCo_2014_Hose: Added inventor files, edited plotting script and report

@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/east_structure}
+\includegraphics[width=6in]{../../Figures/east_structure}
 \\~\\
-\includegraphics[width=6in]{../Pictures/west_structure}
+\includegraphics[width=6in]{../../Figures/west_structure}
 \caption{East (top) and West (bottom) Test Structures}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_1st_Floor}
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_1st_Floor}
 \\
-\includegraphics[width=6in]{Drawings/PDFs/West_Structure_Test_General_2nd_Floor}
-\caption{West Structure ground floor (top) and 2$^{nd}$ floor (bottom) layouts.}
-\label{fig:west_drawing_general}
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_2nd_Floor}
+\caption{West Structure first floor (top) and second floor (bottom) layouts.}
+\label{fig:west_general_plan}
 \end{figure}
@@
 \section{Experimental Procedure}
+Tests 18 and 19 varied in that the first floor rear door was opened for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).
 
-\chapter{Results}
-\label{chap:Results}
-
-\section{Hose Flow Tests}
-\subsection{Tests 18 and 19}
-
-Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.
-
-Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in.
+Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor double doors using a 1.75 in.
 hose with a combination nozzle.
@@
 After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds.
+60 seconds after the stairwell door was opened, the front right door on the second floor was opened, and water continued to flow for 60 more seconds.
 Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
 
-%\subsection{DNXAXX}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
-%\label{fig:HOSE_DNXAXX_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
-%\label{fig:HOSE_DNXAXX_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
-%\label{fig:HOSE_DNXAXX_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXAXX_HOSE}
-%\caption{Hose pressure, Test HOSE\_DNXAXX}
-%\label{fig:HOSE_DNXAXX_HOSE}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{DNXOXF}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
-%\label{fig:HOSE_DNXOXF_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
-%\label{fig:HOSE_DNXOXF_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
-%\label{fig:HOSE_DNXOXF_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DNXOXF_HOSE}
-%\caption{Hose pressure, Test HOSE\_DNXOXF}
-%\label{fig:HOSE_DNXOXF_HOSE}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{DSXAXF}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
-%\label{fig:HOSE_DSXAXF_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
-%\label{fig:HOSE_DSXAXF_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
-%\label{fig:HOSE_DSXAXF_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXAXF_HOSE}
-%\caption{Hose pressure, Test HOSE\_DSXAXF}
-%\label{fig:HOSE_DSXAXF_HOSE}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{DSXOXF}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
-%\label{fig:HOSE_DSXOXF_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
-%\label{fig:HOSE_DSXOXF_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
-%\label{fig:HOSE_DSXOXF_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_DSXOXF_HOSE}
-%\caption{Hose pressure, Test HOSE\_DSXOXF}
-%\label{fig:HOSE_DSXOXF_HOSE}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{IXAOXX}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A6}
-%\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
-%\label{fig:HOSE_IXAOXX_BDP_A6}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
-%\label{fig:HOSE_IXAOXX_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
-%\label{fig:HOSE_IXAOXX_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
-%\label{fig:HOSE_IXAOXX_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXAOXX_HOSE}
-%\caption{Hose pressure, Test HOSE\_IXAOXX}
-%\label{fig:HOSE_IXAOXX_HOSE}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{IXXAXX}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A6}
-%\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
-%\label{fig:HOSE_IXXAXX_BDP_A6}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A7}
-%\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
-%\label{fig:HOSE_IXXAXX_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
-%\label{fig:HOSE_IXXAXX_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
-%\label{fig:HOSE_IXXAXX_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/HOSE_IXXAXX_HOSE}
-%\caption{Hose pressure, Test HOSE\_IXXAXX}
-%\label{fig:HOSE_IXXAXX_HOSE}
-%\end{figure}
-%
-%
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_1st_Floor}
+\\
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
+\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
+Both double doors and the rear door were open on the first floor for the duration of the test.
+On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
+\label{fig:test_18_plan}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_1st_Floor}
+\\
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
+\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
+Both double doors were open and the rear door was closed on the first floor for the duration of the test.
+On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
+\label{fig:test_19_plan}
+\end{figure}
+
+\clearpage
+
+\chapter{Results}
+\label{chap:Results}
+
+\section{Hose Flow Tests}
+
 \subsection{Tests 18 and 19}
-Tests 18 and 19 varied in that the C side, ground level door was open for Test 18 and closed for Test 19.
-
-Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the C-side, ground level double doors using a 1.75 in.
-hose with a combination nozzle.
-The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream.
-Tests 18 and 19 involved three sets of experiments, one for each type of hose stream.
-For each set of experiments, four different application patterns were tested.
-First, water was applied while the hose was in a fixed position.
-Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern.
-Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.
-
-To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern.
-Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position.
-After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the C-side, second-level right door was opened, and water continued to flow for 60 more seconds.
-Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
 
@@
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
-\label{fig:Test_18_West_063014_SS_BDP_A10}
+\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams}
+\label{fig:Test_19_West_063014_SS_BDP_A10}
 \end{figure}
@@
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
-\label{fig:Test_18_West_063014_SS_BDP_A10}
+\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams, CW vs. CCW}
+\label{fig:Test_19_West_063014_SS_BDP_A10}
 \end{figure}
@@
 \clearpage
-%
-%
-%\section{Fire Tests}
-%
-%\subsection{FIRE\_FA2S1C1NCX1\_1}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
-%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
-%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
-%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
-%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_GAS}
-%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_HF}
-%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_HF}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
-%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
-%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
-%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
-%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
-%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-%\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{FIRE\_FA2S1C1NCX1\_2}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
-%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
-%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
-%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
-%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_GAS}
-%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_HF}
-%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_HF}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
-%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
-%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
-%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
-%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
-%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-%\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
-%\end{figure}
-%
-%
-%\clearpage
-%
-%
-%\subsection{FIRE\_FA2S1C1NCX1\_3}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
-%\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
-%\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
-%\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
-%\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
-%\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
-%\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_GAS}
-%\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_HF}
-%\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_HF}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
-%\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
-%\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
-%\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
-%\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../Figures/Script_Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
-%\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-%\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
-%\end{figure}
-%
-%
-%\clearpage
 
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}
+\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
 

### 2015-01-08 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -23,7 +23,7 @@ scaling_file_default = '../DAQ_Files/Delco_DAQ_Channel_List.csv'
 scaling_file_master = '../DAQ_Files/Master_DelCo_DAQ_Channel_List.csv'
 scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
 scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
-# results_loc = '../Experimental_Data/'
+results_loc = '../Experimental_Data/'
 
 # Location of test description file
 info_file = '../Experimental_Data/Description_of_Experiments.csv'
@@ -58,7 +58,7 @@ hose_info = pd.read_csv(hose_info_file, index_col=0)
 info = pd.read_csv(info_file, index_col=3)
 
 # Files to skip
-skip_files = ['_times', '_reduced', 'description_']
+skip_files = ['_times', '_reduced', '_results', 'description_']
 
 #creates lists for results file
 stream_id = []
@@ -123,14 +123,15 @@ for f in os.listdir(data_dir):
             # Defines start and end times for different stream patterns
             for stream in hose_info.columns[1:4]:
                 start_name = stream + '_start'
-                start = hose_info[start_name][test_name]-60
+                start = hose_info[start_name][test_name]
                 end_name = stream + '_end'
                 end = hose_info[end_name][test_name]
                 # Creates data set for specific hose stream
                 stream_data = data.iloc[start:end]
                 t_stream = stream_data['Time']
 
-                fig = figure()
+                # Creates data frame for sensor group to plot average of channels for each stream
+                stream_sensor_group = pd.DataFrame(t_stream)
 
                 for channel in stream_data.columns[1:]:
 
@@ -209,37 +210,37 @@ for f in os.listdir(data_dir):
                             line_style = '-'
                             axis_scale = 'Y Scale HOSE'
 
-                        # Save converted quantity back to exp. dataframe
+                        # Save converted quantity back to exp. dataframe and sensor group dataframe
                         stream_data[channel] = quantity
+                        stream_sensor_group[channel] = quantity
+                    
+                        # # Saves data from top BDP A10 for comparison of each hose stream
+                        # if 'BDP_A10_8' in channel:
+                        #     if stream == 'SS':
+                        #         SS_data = quantity
+                        #     if stream == 'NF':
[…]

### 2015-01-09 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014_Hose: Updated drawings and edited plotting script

@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_1st_Floor}
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_1st_Floor_Metric_Simple}
 \\
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Test_General_2nd_Floor}
+\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_2nd_Floor_Metric_Simple}
 \caption{West Structure first floor (top) and second floor (bottom) layouts.}
@@
 
+\section{Instrumentation}
+
+\section{Uncertainty}
+
 \section{Experimental Procedure}
-Tests 18 and 19 varied in that the first floor rear door was opened for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).
 
-Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor double doors using a 1.75 in.
+\subsection{Tests 18 and 19}
+Tests 18 and 19 varied in that the first floor south side door was open for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).
+
+Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor, south side double doors using a 1.75 in.
 hose with a combination nozzle.
@@
 After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the front right door on the second floor was opened, and water continued to flow for 60 more seconds.
+60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
 Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
@@
 \caption{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
-Both double doors and the rear door were open on the first floor for the duration of the test.
-On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
+Both double doors and the south side door were open on the first floor for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
 \label{fig:test_18_plan}
@@
 \caption{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
-Both double doors were open and the rear door was closed on the first floor for the duration of the test.
-On the second floor, the stairwell door and front right door were opened and closed during the experiments, while the rear door and front left door were in the closed position throughout the entire test.}
+Both double doors were open and the south side door was closed on the first floor for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
 \label{fig:test_19_plan}
@@
 
+\chapter{Future Work}
+\label{chap:Future_Work}
+
 \chapter{Acknowledgments}

### 2015-01-09 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -121,7 +121,7 @@ for f in os.listdir(data_dir):
                 continue
 
             # Defines start and end times for different stream patterns
-            for stream in hose_info.columns[1:4]:
+            for stream in hose_info.columns[2:5]:
                 start_name = stream + '_start'
                 start = hose_info[start_name][test_name]
                 end_name = stream + '_end'
@@ -136,7 +136,7 @@ for f in os.listdir(data_dir):
                 for channel in stream_data.columns[1:]:
 
                     # Skip excluded channels listed in test description file
-                    if any([substring in channel for substring in info['Excluded Channels'][test_name].split('|')]):
+                    if any([substring in channel for substring in hose_info['Excluded Channels'][test_name].split('|')]):
                         continue
 
                     if any([substring in channel for substring in group]):
@@ -214,106 +214,37 @@ for f in os.listdir(data_dir):
                         stream_data[channel] = quantity
                         stream_sensor_group[channel] = quantity
                     
-                        # # Saves data from top BDP A10 for comparison of each hose stream
-                        # if 'BDP_A10_8' in channel:
-                        #     if stream == 'SS':
-                        #         SS_data = quantity
-                        #     if stream == 'NF':
-                        #         NF_data = quantity
-                        #     if stream == 'WF':
-                        #         WF_data = quantity
-
-                        # # Calculates average for specific channel while both doors are opened
-                        # if 'BDP_A10_' in channel:
-
-                        #     avg_fix = np.mean(quantity[120:180])
-                        #     avg_sweep = np.mean(quantity[360:420])
-                        #     avg_CW = np.mean(quantity[600:660])
-                        #     avg_CCW = np.mean(quantity[840:900])
-
-                        #     fix_avg.append(round(avg_fix, 2))
-                        #     sweep_avg.append(round(avg_sweep, 2))
-                        #     CW_avg.append(round(avg_CW, 2))
-                        #     CCW_avg.append(round(avg_CCW, 2))
-                        #     stream_id.append(stream + '_' + test_name)
-                        #     channel_id.append(channel)
-
-                        #     print ' Calculated Avgs for ' + channel
-
[…]

### 2015-01-12 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago Fire: add firetech tex file

--- 2014-09-23 Studies/2012_Chicago/Report/Chicago_Fire.tex
@@
-\documentclass[12pt,oneside]{book}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%                                                                                                 %
-% The mathematical style of these documents follows                                               %
-%                                                                                                 %
-% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
-%    NIST Special Publication 881, 2008.                                                          %
-%                                                                                                 %
-% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
-%                                                                                                 %
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%% file template.tex %%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% This is a general template file for the LaTeX package SVJour3
+% for Springer journals.          Springer Heidelberg 2010/09/16
+%
+% Copy it to a new file with a new name and use it as the basis
+% for your article. Delete % signs as needed.
+%
+% This template includes a few options for different layouts and
+% content for various journals. Please consult a previous issue of
+% your journal as needed.
+%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%
+% First comes an example EPS file -- just ignore it and
+% proceed on the \documentclass line
+% your LaTeX will extract the file if required
+\begin{filecontents*}{example.eps}
+%!PS-Adobe-3.0 EPSF-3.0
+%%BoundingBox: 19 19 221 221
+%%CreationDate: Mon Sep 29 1997
+%%Creator: programmed by hand (JK)
+%%EndComments
+gsave
+newpath
+  20 20 moveto
+  20 220 lineto
+  220 220 lineto
+  220 20 lineto
+closepath
+2 setlinewidth
+gsave
+  .4 setgray fill
+grestore
+stroke
+grestore
+\end{filecontents*}
+%
+\RequirePackage{fix-cm}
+%
+%\documentclass{svjour3}                     % onecolumn (standard format)
+%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+%\documentclass[twocolumn]{svjour3}          % twocolumn
+%
+\smartqed  % flush right qed marks, e.g. at end of proof
 
 \input{../../../Bibliography/commoncommands}
-
-% Rename chapter headings
-\renewcommand{\chaptername}{Section}
-\renewcommand{\bibname}{References}
-
-% Math shortcuts
+\usepackage{graphicx}
 \renewcommand{\sb}[1]{_\mathrm{#1}}
@@
 \rhead{}
-\chead{This publication is available free of charge from:
-\hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}}
+\chead{}
 \renewcommand{\headrulewidth}{0pt}
 
+% Insert the name of "your journal" with
+\journalname{Fire Technology}
+%
 \begin{document}
-\pagenumbering{gobble}
 
-\bibliographystyle{unsrt}
-%\pagestyle{empty}
+\title{Simulation of an Attic Firein a Wood Frame Residential Structure - Chicago, IL}
 
-\begin{minipage}[t][9in][s]{6.25in}
+%\titlerunning{Short form of title}        % if too long for running head
 
-\begin{flushright}
-\fontsize{20}{24}\selectfont
-\bf{NIST Technical Note 1838}
-\end{flushright}
-
-\headerB{
-Simulation of an Attic Fire \\
-in a Wood Frame Residential \\
-Structure - Chicago, IL \\
+\author{Craig G. Weinschenk         \and
+        Kristopher J. Overholt      \and
+        Daniel Madrzykowski
 }
 
-\normalsize
+%\authorrunning{Short form of author list} % if too long for running head
 
-\headerC{
-{
-\flushright{
-Craig G. Weinschenk \\
-Kristopher J. Overholt \\
-Daniel Madrzykowski \\
-
-\vspace*{2\baselineskip}
-
-\begingroup
-\hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838}
-\endgroup
+\institute{Craig Weinschenk \at
+              National Instutue of Standards and Technology \\
+              100 Bureau Drive \\
+              Gaithersburg MD 20899-8661
+              Tel.: 301-975-6899\\
+              \email{craig.weinschenk@nist.gov}           %  \\
 }
 
-\vfill
+\date{Received: date / Accepted: date}
+% The correct dates will be entered by the editor
 
-\flushright{
+\maketitle
 
-\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
-}
-}
-}
-
-\end{minipage}
-
-\newpage
-\hspace{5in}
-\newpage
-
-\frontmatter
-
-\begin{minipage}[t][9in][s]{6.25in}
-\pagenumbering{gobble}
-
-\begin{flushright}
-\fontsize{20}{24}\selectfont
-\bf{NIST Technical Note 1838}
-\end{flushright}
-
-\headerB{
-Simulation of an Attic Fire \\
-in a Wood Frame Residential \\
-Structure - Chicago, IL \\
-}
-
-\headerC{
-\flushright{
-Craig G. Weinschenk \\
-Kristopher J. Overholt \\
-Daniel Madrzykowski \\
-{\em Fire Research Division \\
-Engineering Laboratory} \\
-
-\vspace*{2\baselineskip}
-
-\begingroup
-This publication is available free of charge from:
-\hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.1838} \\
-\endgroup
-
-\vspace*{2\baselineskip}
-
-August 2014}}
-
-\vfill
-
-\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }
-
-\titlesigs
-
-\end{minipage}
-
-\newpage
-
-\begin{minipage}[t][9in][s]{6.25in}
-\pagenumbering{gobble}
-
-\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
-document in order to describe an experimental procedure or concept adequately. \\
-Such identification is not intended to imply recommendation or endorsement by the \\
-National Institute of Standards and Technology, nor is it intended to imply that the \\
-entities, materials, or equipment are necessarily the best available for the purpose. \\
-}
-
-\vspace{3in}
-
-\large
-\flushright{\bf National Institute of Standards and Technology Technical Note 1838 \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~1838, \pageref{LastPage} pages (August 2014) \\
-% http://dx.doi.org/10.6028/NIST.TN.1838 \\
-CODEN: NTNOEF }
-
-\vfill
-
-\hspace{1in}
-
-\end{minipage}
-
-\newpage
-
-\frontmatter
-
-%\pagestyle{plain}
-\pagenumbering{roman}
-\setcounter{page}{3}
-
-\cleardoublepage
-\phantomsection
-\addcontentsline{toc}{chapter}{Contents}
-\tableofcontents
-
-\cleardoublepage
-\phantomsection
-\addcontentsline{toc}{chapter}{List of Figures}
-\listoffigures
-
-\cleardoublepage
-\phantomsection
-\addcontentsline{toc}{chapter}{List of Tables}
-\listoftables
-
-\chapter{List of Acronyms}
-
-\begin{tabbing}
-\hspace{1.5in} \= \\
-BC \> Battalion Chief \\
-E \> Engine \\
-FDS \> Fire Dynamics Simulator \\
-HGL \> Hot Gas Layer \\
-HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
-IC \> Incident Command \\
-LODD \> Line of Duty Death \\
-NIOSH \> National Institute for Occupational Safety and Health \\
-NIST \> National Institute of Standards and Technology \\
-SFPE \> Society of Fire Protection Engineers \\
-SQ \> Squad \\
-TL \> Tower Ladder \\
-\end{tabbing}
-
-\chapter{List of Symbols}
-
-\begin{tabbing}
-\hspace{1.5in} \= \\
-ft \> foot \\
-m \> meter \\
-min \> minute \\
-Pa \> Pascal \\
-psi \> pound per square inch \\
-s \> second \\
-W \> Watt \\
-$k$ \> thermal conductivity \\
-$\rho$ \> density \\
-$c_{p}$ \> specific heat \\
-\end{tabbing}
-
-\mainmatter
-
-\chapter*{\centering Abstract}
-\pagenumbering{gobble}
+\begin{abstract}
 The Fire Dynamics Simulator (FDS) fire model, which is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on November 2, 2012, within a 2~\sfrac{1}{2}~story, single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
@@
 
-\chapter{Introduction}
-\pagenumbering{arabic}
-\setcounter{page}{1}
+\keywords{LODD \and FDS \and CFD}
+\end{abstract}
+
+\section{Introduction}
+\label{intro}
 Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
@@
 
-\chapter{Summary of the Fire Incident}
+\section{Summary of the Fire Incident}
 \label{fire_sum}
@@
 
-\chapter{Model Description}
+\section{Model Description}
 \label{model}
@@
 
-In reality, the quantities associated with these input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
-Any change in an input parameter (such as the HRR) for a given scenario would result in a change in the output quantity (such as the hot gas layer (HGL) temperature).
-For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
-Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
-More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
-Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
-The following subsections describe the inputs that were used to develop the simulation, including any approximations or assumptions that were made.
-
-\section{Geometry}
+\subsection{Geometry}
 \label{geom}
@@
 
-\clearpage
-
-\section{Fire}
+\subsection{Fire}
 \label{fire}
-
 To estimate the type of fuel, fire size, and structure ventilation, on-scene videos and post-incident reports were used.
@@
 
-\clearpage
-
-\section{Materials}
+\subsection{Materials}
 \label{matl}
@@
 
-\section{Ventilation}
+\subsection{Ventilation}
 \label{Vents}
@@
 While this time and area may not be exact, the takeaway from the analysis in the following sections should be impact of the door's failure on the interior conditions of the structure.
-
-\clearpage
 
@@
 
-\section{Numerical Mesh}
+\subsection{Numerical Mesh}
 \label{mesh}
@@
 Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulations that were conducted as part of this study.
 
@@
 
-\begin{table}
+\subsection{Summary of Model Input Parameters}
+\label{sec:summary_of_model_inputs}
+
+Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulation that was conducted as part of this study.
+In reality, the quantities associated with model input parameters are not fixed values; rather, a model input parameter can be thought of as a point estimate from a distribution of possible input parameters with some associated amount of uncertainty.
+Any change in an input parameter (such as the HRR) for a given scenario results in a change in the output quantity (such as the hot gas layer (HGL) temperature).
+
+For example, according to the McCaffrey, Quintiere, and Harkleroad~\cite{SFPE:Walton} empirical correlation, the HGL temperature in a well-ventilated compartment fire is proportional to the HRR raised to the two-thirds power.
+Following this relationship, a 7.5~\% increase in the HRR would result in a 5~\% increase in the HGL temperature~\cite{NUREG_1824_Sup_1}.
+More detailed discussion on the propagation of parameter uncertainty in fire models is available in a validation study that was sponsored by the U.S.
+Nuclear Regulatory Commission~\cite{NUREG_1824_Sup_1}.
+
+\begin{table}[h!]
 \centering
@@
 
-\chapter{Model Results}
+\section{Model Results}
 \label{results}
@@
 
-\section{Heat Release Rate}
+\subsection{Heat Release Rate}
 \label{HRR}
@@
 
-\clearpage
-
-\section{Pressure}
-
+\subsection{Pressure}
+\label{pres}
 As the simulated fire grows in the attic and rear porch, the pressure rises.
@@
 
-\section{Temperature}
+\subsection{Temperature}
 \label{temp}
@@
 
-\chapter{Discussion of Simulation Results}
+\section{Discussion of Simulation Results}
 \label{discussion}
@@
 
-\section{Simulated Hallway Flow Path}
+\subsection{Simulated Hallway Flow Path}
+\label{flowpath}
 From on-scene reports (Section~\ref{fire_sum}) and the FDS simulation results (Section~\ref{temp}), the interior conditions on the second floor of the structure were initially tenable.
@@
 
-\section{Assessing the Hazard}
-
+\subsection{Assessing the Hazard}
+\label{hazard}
 A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
@@
 
-\section{Tactical Considerations}
+\subsection{Tactical Considerations}
+\label{tactical}
 There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
@@
 
-\chapter{Summary}
+\section{Summary}
+\label{summary}
 NIST's Fire Dynamics Simulator was used to provide insight into the fire dynamics within a 2~\sfrac{1}{2}~story single family structure in Chicago, IL, that resulted in the death of the captain of a fire department.
@@
 
-\chapter*{Acknowledgments}
+\begin{acknowledgements}
 The authors would like to thank the Chicago Fire Department, especially Commissioner Jose Santiago, District Chief Donald Hroma, and District Chief Kevin Krasneck.
@@
 Finally, the authors would also like to thank Keith Stakes of NIST and Joseph Willi of the University of Illinois Urbana-Champaign for their assistance in creating the drawings of the structure.
+\end{acknowledgements}
 
+% BibTeX users please use one of
+%\bibliographystyle{spbasic}      % basic style, author-year citations
+%\bibliographystyle{spmpsci}      % mathematics and physical sciences
+\bibliographystyle{spphys}       % APS-like style for physics
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
+
+\clearpage
 
@@
 
-\chapter{Dimensioned Drawings}
+\section{Dimensioned Drawings}
 \label{app_draw}
@@
 \end{document}
+% end of file template.tex

### 2015-01-13 Projects/Exploratory_Steam/Supporting_Material/FRD_PML_SoW.tex
Steam: minor edit to SoW, add experimental data and plotting script

@@
 \toprule[1.5pt]
-Series \#       &  Material                   &  Duration       &  Environment       &  Reps  \\
+Test \#       &  Material                   &  Duration       &  Environment       &  Reps  \\
 \midrule
-1               &  None                       &  Steady-State   &  Peak T \& RH   &  5  \\[.25cm]
-2               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
-3               &  Woven Fabric (hood)        &  10~min$^*$     &  Peak T \& RH   &  5  \\[.25cm]
-4               &  None                       &  Steady-State   &  Min T \& RH    &  5 \\[.25cm]
-5               &  Full PPE (3 layer sample)  &  10~min$^*$     &  Min T \& RH    &  5  \\[.25cm]
-6               &  Woven Fabric (hood)        &  10~min$^*$     &  Min T \& RH    &  5 \\[.25cm]
-7$^+$           &  None                       &  Steady-State   &  Mid T \& RH    &  5 \\[.25cm]
-8$^+$           &  Full PPE (3 layer sample)  &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
-9$^+$           &  Woven Fabric (hood)        &  10~min$^*$     &  Mid T \& RH    &  5 \\[.25cm]
+1               &  None                       &  Steady-State   &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
+2               &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
+3               &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 95~\%RH   &  5  \\[.25cm]
+4               &  None                       &  Steady-State   &  85~$^{\circ}$C \& 65~\%RH    &  5 \\[.25cm]
+5               &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 65~\%RH    &  5  \\[.25cm]
+6               &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 65~\%RH    &  5 \\[.25cm]
+7$^+$           &  None                       &  Steady-State   &  85~$^{\circ}$C \& 35~\%RH    &  5 \\[.25cm]
+8$^+$           &  Full PPE (3 layer)         &  10~min$^*$     &  85~$^{\circ}$C \& 35~\%RH    &  5 \\[.25cm]
+9$^+$           &  Woven Fabric (hood)        &  10~min$^*$     &  85~$^{\circ}$C \& 35~\%RH   &  5 \\[.25cm]
 \bottomrule[1.25pt]

### 2015-01-13 Projects/Exploratory_Steam/Scripts/steam_data_plot.py

@@ -1,0 +1,57 @@
+#Weinschenk
+#9-14
+
+from __future__ import division
+import numpy as np
+import pandas as pd
+from pylab import *
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+def DP_sub (b,c,temp,RH):
+	DP_func = (c*(log(RH/100)+ (b*temp)/(c+temp)))/(b-(log(RH/100)+ (b*temp)/(c+temp)))
+	return DP_func;
+b = 17.67
+c = 243.5
+
+sample_rate = 6.
+
+T80_RH97_FC = pd.read_csv('../Experimental_Data/80degC_97RH_Full_Chamber.csv', header=5)
+TDP_T80_RH97_FC = np.zeros(len(T80_RH97_FC['Temperature (C)']))
+T80_RH97_FC_Time = np.zeros(len(T80_RH97_FC['Temperature (C)']))
+
+T80_RH97_FS = pd.read_csv('../Experimental_Data/80degC_97RH_Full_Sample.csv', header=5)
+TDP_T80_RH97_FS = np.zeros(len(T80_RH97_FS['Temperature (C)']))
+T80_RH97_FS_Time = np.zeros(len(T80_RH97_FS['Temperature (C)']))
+
+for i in range(len(T80_RH97_FC)):
+	T80_RH97_FC_Time[i] = -4476 + i*sample_rate
+	TDP_T80_RH97_FC[i] = DP_sub(b,c,T80_RH97_FC['Temperature (C)'][i],T80_RH97_FC['Humidity (RH)'][i])
+
+k=1		
+for i in range(len(T80_RH97_FS)):
+	T80_RH97_FS_Time[i] = -4398 + i*sample_rate
+	TDP_T80_RH97_FS[i] = DP_sub(b,c,T80_RH97_FS['Temperature (C)'][i],T80_RH97_FS['Humidity (RH)'][i])
+	if TDP_T80_RH97_FS[i] > 37 and k == 1:
+		j = T80_RH97_FS_Time[i]
+		k = -1
+
+fig = figure()
+plt.plot(T80_RH97_FC_Time,TDP_T80_RH97_FC,'rs',linewidth=2, label='Test Chamber Conditions')
+plt.plot(T80_RH97_FS_Time,TDP_T80_RH97_FS,'bo',linewidth=2, label='Sample Penetration Conditions')
+axvline(x=j,linestyle='-',linewidth=2,color = '#000000')
[…]

### 2015-01-13 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Added sections in abstract for figures
DelCo 2012 Report: Figures in appendix.

@@
 
+\chapter{Appendix}
+\label{chap:Appendix}
+
+\section{Test 1 Figures}
+\label{subsec:Test_1_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
+	\caption{Test 1 (FSE1): Eastside Array}
+	\label{fig:Test_1_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
+	\caption{Test 1 (FSE1): Westside Array}
+	\label{fig:Test_1_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
+	\caption{Test 1 (FSE1): Hallway Array}
+	\label{fig:Test_1_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
+	\caption{Test 1 (FSE1): Doorway Array}
+	\label{fig:Test_1_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
+	\caption{Test 1 (FSE1): Suppression Eastside Array}
+	\label{fig:Test_1_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
+	\caption{Test 1 (FSE1): Suppression Westside Array}
+	\label{fig:Test_1_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
+	\caption{Test 1 (FSE1): Suppression Hallway Array}
+	\label{fig:Test_1_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
+	\caption{Test 1 (FSE1): Suppression Doorway Array}
+	\label{fig:Test_1_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
+	\caption{Test 1 (FSE1): Eastside Heat Flux}
+	\label{fig:Test_1_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
+	\caption{Test 1 (FSE1): Westside Heat Flux}
+	\label{fig:Test_1_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
+	\caption{Test 1 (FSE1): Hallway Heat Flux}
+	\label{fig:Test_1_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
+	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
+	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
+	\caption{Test 1 (FSE1): Hallway Velocity}
+	\label{fig:Test_1_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
+	\caption{Test 1 (FSE1): Doorway Velocity}
+	\label{fig:Test_1_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 2 Figures}
+\label{subsec:Test_2_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
+	\caption{Test 2 (FSW2): Eastside Array}
+	\label{fig:Test_2_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
+	\caption{Test 2 (FSW2: Westside Array}
+	\label{fig:Test_2_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
+	\caption{Test 2 (FSW2): Hallway Array}
+	\label{fig:Test_2_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
+	\caption{Test 2 (FSW2): Doorway Array}
+	\label{fig:Test_2_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
+	\caption{Test 2 (FSW2): Suppression Eastside Array}
+	\label{fig:Test_2_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
+	\caption{Test 2 (FSW2): Suppression Westside Array}
+	\label{fig:Test_2_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
+	\caption{Test 2 (FSW2): Suppression Hallway Array}
+	\label{fig:Test_2_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
+	\caption{Test 2 (FSW2): Suppression Doorway Array}
+	\label{fig:Test_2_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
+	\caption{Test 2 (FSW2): Eastside Heat Flux}
+	\label{fig:Test_2_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
+	\caption{Test 2 (FSW2): Westside Heat Flux}
+	\label{fig:Test_2_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
+	\caption{Test 2 (FSW2): Hallway Heat Flux}
+	\label{fig:Test_2_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
+	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
+	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
+	\caption{Test 2 (FSW2): Hallway Velocity}
+	\label{fig:Test_2_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
+	\caption{Test 2 (FSW2): Doorway Velocity}
+	\label{fig:Test_2_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 3 Figures}
+\label{subsec:Test_3_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
+	\caption{Test 3 (FSW3): Eastside Array}
+	\label{fig:Test_3_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
+	\caption{Test 3 (FSW3: Westside Array}
+	\label{fig:Test_3_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
+	\caption{Test 3 (FSW3): Hallway Array}
+	\label{fig:Test_3_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
+	\caption{Test 3 (FSW3): Doorway Array}
+	\label{fig:Test_3_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
+	\caption{Test 3 (FSW3): Suppression Eastside Array}
+	\label{fig:Test_3_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
+	\caption{Test 3 (FSW3): Suppression Westside Array}
+	\label{fig:Test_3_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
+	\caption{Test 3 (FSW3): Suppression Hallway Array}
+	\label{fig:Test_3_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
+	\caption{Test 3 (FSW3): Suppression Doorway Array}
+	\label{fig:Test_3_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
+	\caption{Test 3 (FSW3): Eastside Heat Flux}
+	\label{fig:Test_3_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
+	\caption{Test 3 (FSW3): Westside Heat Flux}
+	\label{fig:Test_3_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
+	\caption{Test 3 (FSW3): Hallway Heat Flux}
+	\label{fig:Test_3_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
+	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
+	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
+	\caption{Test 3 (FSW3): Hallway Velocity}
+	\label{fig:Test_3_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
+	\caption{Test 3 (FSW3): Doorway Velocity}
+	\label{fig:Test_3_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 4 Figures}
+\label{subsec:Test_4_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
+	\caption{Test 4 (FSE4): Eastside Array}
+	\label{fig:Test_4_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
+	\caption{Test 4 (FSE4): Westside Array}
+	\label{fig:Test_4_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
+	\caption{Test 4 (FSE4): Hallway Array}
+	\label{fig:Test_4_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
+	\caption{Test 4 (FSE4): Doorway Array}
+	\label{fig:Test_4_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
+	\caption{Test 4 (FSE4): Suppression Eastside Array}
+	\label{fig:Test_4_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
+	\caption{Test 4 (FSE4): Suppression Westside Array}
+	\label{fig:Test_4_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
+	\caption{Test 4 (FSE4): Suppression Hallway Array}
+	\label{fig:Test_4_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
+	\caption{Test 4 (FSE4): Suppression Doorway Array}
+	\label{fig:Test_4_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
+	\caption{Test 4 (FSE4): Eastside Heat Flux}
+	\label{fig:Test_4_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
+	\caption{Test 4 (FSE4): Westside Heat Flux}
+	\label{fig:Test_4_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
+	\caption{Test 4 (FSE4): Hallway Heat Flux}
+	\label{fig:Test_4_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
+	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
+	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
+	\caption{Test 4 (FSE4): Hallway Velocity}
+	\label{fig:Test_4_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
+	\caption{Test 4 (FSE4): Doorway Velocity}
+	\label{fig:Test_4_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 5 Figures}
+\label{subsec:Test_5_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
+	\caption{Test 5 (FSE5): Eastside Array}
+	\label{fig:Test_5_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
+	\caption{Test 5 (FSE5): Westside Array}
+	\label{fig:Test_5_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
+	\caption{Test 5 (FSE5): Hallway Array}
+	\label{fig:Test_5_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
+	\caption{Test 5 (FSE5): Doorway Array}
+	\label{fig:Test_5_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
+	\caption{Test 5 (FSE5): Suppression Eastside Array}
+	\label{fig:Test_5_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
+	\caption{Test 5 (FSE5): Suppression Westside Array}
+	\label{fig:Test_5_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
+	\caption{Test 5 (FSE5): Suppression Hallway Array}
+	\label{fig:Test_5_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
+	\caption{Test 5 (FSE5): Suppression Doorway Array}
+	\label{fig:Test_5_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
+	\caption{Test 5 (FSE5): Eastside Heat Flux}
+	\label{fig:Test_5_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
+	\caption{Test 5 (FSE5): Westside Heat Flux}
+	\label{fig:Test_5_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
+	\caption{Test 5 (FSE5): Hallway Heat Flux}
+	\label{fig:Test_5_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
+	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
+	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
+	\caption{Test 5 (FSE5): Hallway Velocity}
+	\label{fig:Test_5_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
+	\caption{Test 5 (FSE5): Doorway Velocity}
+	\label{fig:Test_5_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 6 Figures}
+\label{subsec:Test_6_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
+	\caption{Test 6 (FSW6): Eastside Array}
+	\label{fig:Test_6_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
+	\caption{Test 6 (FSW6: Westside Array}
+	\label{fig:Test_6_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
+	\caption{Test 6 (FSW6): Hallway Array}
+	\label{fig:Test_6_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
+	\caption{Test 6 (FSW6): Doorway Array}
+	\label{fig:Test_6_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
+	\caption{Test 6 (FSW6): Suppression Eastside Array}
+	\label{fig:Test_6_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
+	\caption{Test 6 (FSW6): Suppression Westside Array}
+	\label{fig:Test_6_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
+	\caption{Test 6 (FSW6): Suppression Hallway Array}
+	\label{fig:Test_6_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
+	\caption{Test 6 (FSW6): Suppression Doorway Array}
+	\label{fig:Test_6_Suppression_Doorway_Array}
+\end{figure}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
+	\caption{Test 6 (FSW6): Eastside Heat Flux}
+	\label{fig:Test_6_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
+	\caption{Test 6 (FSW6): Westside Heat Flux}
+	\label{fig:Test_6_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
+	\caption{Test 6 (FSW6): Hallway Heat Flux}
+	\label{fig:Test_6_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
+	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
+	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
+	\caption{Test 6 (FSW6): Hallway Velocity}
+	\label{fig:Test_6_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
+	\caption{Test 6 (FSW6): Doorway Velocity}
+	\label{fig:Test_6_Doorway_Velocity}
+\end{figure}
+
+\clearpage
+
+\section{Test 7 Figures}
+\label{subsec:Test_7_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\clearpage
+
+\section{Test 8 Figures}
+\label{subsec:Test_8_Figures}
+
+\subsection{Temperature}
+\label{subsec:Temperature}
+
+\subsection{Heat Flux}
+\label{subsec:Heat_Flux}
+
+\subsection{Velocity}
+\label{subsec:Velocity}
+
+\clearpage
+
 \chapter{References}
@@
 
-\chapter{Appendix}
-\label{chap:Appendix}
-
-\clearpage
-
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}

### 2015-01-13 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added figures and other content to report

@@
 
+\section{Background}
+\label{sec:Background}
+
+\subsection{Hose Stream Patterns}
+\label{sec:Hose_Stream_Patterns}
+
+\subsection{Application Patterns}
+\label{Application_Patterns}
+
 \chapter{Experimental Setup}
@@
 \label{sec:Construction}
-Two structures, shown in Fig.~\ref{fig:struct_pics}, were used for the experiments.
+Two structures, shown in Fig.~\ref{fig:struct_pics}, were constructed for the experiments.
 Each structure contained a ground level floor composed of concrete walls.
@@
 \includegraphics[width=6in]{../../Figures/west_structure}
-\caption{East (top) and West (bottom) Test Structures}
+\caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
 \label{fig:struct_pics}
@@
 \includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_2nd_Floor_Metric_Simple}
-\caption{West Structure first floor (top) and second floor (bottom) layouts.}
+\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts.}
 \label{fig:west_general_plan}
@@
 \clearpage
+
 \section{Fuel Load}
+\label{sec:Fuel_Load}
 
 \section{Instrumentation}
+\label{sec:Instrumentation}
 
 \section{Uncertainty}
+\label{sec:Uncertainty}
 
 \section{Experimental Procedure}
+\label{sec:Experimental_Procedure}
 
-\subsection{Tests 18 and 19}
-Tests 18 and 19 varied in that the first floor south side door was open for Test 18 (Fig. \ref{fig:test_18_plan}) and closed for Test 19 (Fig. \ref{fig:test_19_plan}).
+\subsection{Hose Stream Pattern Experiments}
+\label{sec:Hose_Stream_Pattern_Experiments}
+
+\subsection{Application Pattern Experiments}
+\label{Application_Pattern_Experiments}
+
+Two sets of experiments involving application patterns, Tests 18 and 19, were conducted.
+The two sets varied in that the first floor south side door was open for Test 18 (Fig.
+\ref{fig:test_18_plan}) and closed for Test 19 (Fig.
+\ref{fig:test_19_plan}).
 
@@
 \includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
-\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
+\caption[West Structure first and second floor layouts for Test 18]{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
 Both double doors and the south side door were open on the first floor for the duration of the test.
@@
 \includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
-\caption{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
+\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
 Both double doors were open and the south side door was closed on the first floor for the duration of the test.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_All_Streams}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams}
-\label{fig:Test_18_West_063014_SS_BDP_A10}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
+\caption{Average Velocity of Stairwell Door, Test 18, All Streams}
+\label{fig:Test_18_BDP_A10_Avg_All}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_All_Streams}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams}
-\label{fig:Test_19_West_063014_SS_BDP_A10}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
+\caption{Average Velocity of Stairwell Door, Test 19, All Streams}
+\label{fig:Test_19_BDP_A10_Avg_All}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014BDP_A10_8_CW_vs_CCW}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 18, All Streams, CW vs. CCW}
-\label{fig:Test_18_West_063014_SS_BDP_A10}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
+\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
+\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014BDP_A10_8_CW_vs_CCW}
-\caption{Velocity at Ceiling Level of Stairwell Door, Test 19, All Streams, CW vs. CCW}
-\label{fig:Test_19_West_063014_SS_BDP_A10}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
+\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
+\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
+\caption{Average Velocity of North Double Door, Test 18, All Streams, CW vs. CCW}
+\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
+\caption{Average Velocity of North Double Door, Test 19, All Streams, CW vs. CCW}
+\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
 \end{figure}

### 2015-01-14 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago Fire: update tex and add files for firetech submission

@@
 %\documentclass{svjour3}                     % onecolumn (standard format)
-%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
-\documentclass[smallextended]{svjour3}       % onecolumn (second format)
+\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
+%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
 %\documentclass[twocolumn]{svjour3}          % twocolumn
@@
 \input{../../../Bibliography/commoncommands}
-\usepackage{graphicx}
 \renewcommand{\sb}[1]{_\mathrm{#1}}
@@
 
-\title{Simulation of an Attic Firein a Wood Frame Residential Structure - Chicago, IL}
+\title{Simulation of an Attic Fire in a Wood Frame Residential Structure - Chicago, IL}
 
@@
 \caption[Plan view of first (top) and second (bottom) floor of structure.]{Plan view of first (top) and second (bottom) floor of structure.
-Stairs and key rooms are identified using measurements collected by NIST.}
+Stairs and key rooms are identified using measurements collected by NIST}
 \label{fig:simp_geom}
@@
 \end{tabular*}
-\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident.}
+\caption{Photographs showing the front (left) and rear (right) exterior of the structure after the incident}
 \label{fig:alpha_ex}
@@
 
+\clearpage
+
 \begin{lstlisting}
@@
 \end{tabular*}
-\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh.}
+\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh}
 \label{fig:geom_grid}
@@
 \includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption[Front-right side of the structure within the computational domain.]{Front-right side of the structure within the computational domain (with multiple meshes).
-Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft).}
+\caption[Front-right side of the structure within the computational domain]{Front-right side of the structure within the computational domain (with multiple meshes).
+Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft)}
 \label{fig:mult_mesh}
@@
 \caption[HRR versus time from the FDS simulations.]{HRR versus time from the FDS simulations.
-The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s).}
+The first vertical line indicates the time at which the back door failed (130~s), and the second vertical line indicates the time at which the interior hallway door failed (160~s)}
 \label{fig:hrr}
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure.}
+\caption[FDS simulated pressure contours, 1~s prior to interior door failure.]{FDS simulated pressure contours, 1~s prior to interior door failure}
 \label{fig:pres_159s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s prior to rear door opening.}
+\caption{FDS simulated temperature contours, 1~s prior to rear door opening}
 \label{fig:temp_129s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s prior to interior door failure.}
+\caption{FDS simulated temperature contours, 1~s prior to interior door failure}
 \label{fig:temp_159s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 1~s after interior door failure.}
+\caption{FDS simulated temperature contours, 1~s after interior door failure}
 \label{fig:temp_161s}
@@
 \input{../Scripts/colorbar_metric}
-\caption{FDS simulated temperature contours, 15~s after the interior door failure.}
+\caption{FDS simulated temperature contours, 15~s after the interior door failure}
 \label{fig:temp_175s}
@@
 \includegraphics[width=.4\textwidth]{../Figures/Porch_Door_1}
-\caption{Post-fire image of interior door.}
+\caption{Post-fire image of interior door}
 \label{fig:chicago_doorfold}
@@
 \end{tabular*}
-\caption{Post-experiment images of door failures.}
+\caption{Post-experiment images of door failures}
 \label{fig:SC_doorfold}
@@
 \includegraphics[width=.7\textwidth]{../Figures/ChicagoFlow}
-\caption{Summary of simulated flow path on the second floor after interior door failure.}
+\caption{Summary of simulated flow path on the second floor after interior door failure}
 \label{fig:flowpath_1}
@@
 \input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 1~s prior to interior door failure.]
-{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 1~s prior to interior door failure]
+{Temperature contours on the second floor, 1~s prior to interior door failure, 1.83~m (6~ft) above the floor}
 \label{fig:temp_top_159}
@@
 \input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 5~s after interior door failure.]
-{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 5~s after interior door failure]
+{Temperature contours on the second floor, 5~s after interior door failure, 1.83~m (6~ft) above the floor}
 \label{fig:temp_top_165}
@@
 \input{../Scripts/colorbar_metric}
-\caption[Temperature contours on the second floor, 60~s after interior door failure.]
-{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor.}
+\caption[Temperature contours on the second floor, 60~s after interior door failure]
+{Temperature contours on the second floor, 60~s after interior door failure, 1.83~m (6~ft) above the floor}
 \label{fig:temp_top_220}
@@
 \end{document}
-% end of file template.tex

### 2015-01-14 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated scripts and report with figures

@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
+	\caption{Test 7 (FSW7): Eastside Array}
+	\label{fig:Test_7_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
+	\caption{Test 7 (FSW7: Westside Array}
+	\label{fig:Test_7_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
+	\caption{Test 7 (FSW7): Hallway Array}
+	\label{fig:Test_7_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
+	\caption{Test 7 (FSW7): Doorway Array}
+	\label{fig:Test_7_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
+	\caption{Test 7 (FSW7): Suppression Eastside Array}
+	\label{fig:Test_7_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
+	\caption{Test 7 (FSW7): Suppression Westside Array}
+	\label{fig:Test_7_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
+	\caption{Test 7 (FSW7): Suppression Hallway Array}
+	\label{fig:Test_7_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
+	\caption{Test 7 (FSW7): Suppression Doorway Array}
+	\label{fig:Test_7_Suppression_Doorway_Array}
+\end{figure}
+
 \subsection{Heat Flux}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
+	\caption{Test 7 (FSW7): Eastside Heat Flux}
+	\label{fig:Test_7_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
+	\caption{Test 7 (FSW7): Westside Heat Flux}
+	\label{fig:Test_7_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
+	\caption{Test 7 (FSW7): Hallway Heat Flux}
+	\label{fig:Test_7_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
+	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
+	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
 \subsection{Velocity}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
+	\caption{Test 7 (FSW7): Hallway Velocity}
+	\label{fig:Test_7_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
+	\caption{Test 7 (FSW7): Doorway Velocity}
+	\label{fig:Test_7_Doorway_Velocity}
+\end{figure}
+
 \clearpage
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
+	\caption{Test 8 (FSE8): Eastside Array}
+	\label{fig:Test_8_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
+	\caption{Test 8 (FSE8): Westside Array}
+	\label{fig:Test_8_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
+	\caption{Test 8 (FSE8): Hallway Array}
+	\label{fig:Test_8_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
+	\caption{Test 8 (FSE8): Doorway Array}
+	\label{fig:Test_8_Doorway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
+	\caption{Test 8 (FSE8): Suppression Eastside Array}
+	\label{fig:Test_8_Suppression_Eastside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
+	\caption{Test 8 (FSE8): Suppression Westside Array}
+	\label{fig:Test_8_Suppression_Westside_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
+	\caption{Test 8 (FSE8): Suppression Hallway Array}
+	\label{fig:Test_8_Suppression_Hallway_Array}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
+	\caption{Test 8 (FSE8): Suppression Doorway Array}
+	\label{fig:Test_8_Suppression_Doorway_Array}
+\end{figure}
+
 \subsection{Heat Flux}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
+	\caption{Test 8 (FSE8): Eastside Heat Flux}
+	\label{fig:Test_8_Eastside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
+	\caption{Test 8 (FSE8): Westside Heat Flux}
+	\label{fig:Test_8_Westside_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
+	\caption{Test 8 (FSE8): Hallway Heat Flux}
+	\label{fig:Test_8_Hallway_Heat_Flux}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
+	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
+	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
+\end{figure}
+
 \subsection{Velocity}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
+	\caption{Test 8 (FSE8): Hallway Velocity}
+	\label{fig:Test_8_Hallway_Velocity}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
+	\caption{Test 8 (FSE8): Doorway Velocity}
+	\label{fig:Test_8_Doorway_Velocity}
+\end{figure}
+
 \clearpage

### 2015-01-14 Projects/DelCo_2012/Scripts/FSE_Test4.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSE4 Eastside Array' 'FSE4 Westside Array' 'FSE4 Hallway Array' 'FSE4 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSE4 Eastside Array' 'Suppression FSE4 Westside Array' 'Suppression FSE4 Hallway Array' 'Suppression FSE4 Doorway Array'};
+TC_array_names = {'FSE4_Eastside_Array' 'FSE4_Westside_Array' 'FSE4_Hallway_Array' 'FSE4_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSE4_Eastside_Array' 'Suppression_FSE4_Westside_Array' 'Suppression_FSE4_Hallway_Array' 'Suppression_FSE4_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -283,7 +283,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 80])
 legend('Eastside Heat Flux 0.15m','Eastside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSE Test 4 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSE_Test_4_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -303,7 +303,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 80])
 legend('Westside Heat Flux 0.15m','Westside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSE Test 4 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSE_Test_4_Heat_Flux_Westside'])
 hold off
 
 plot1 = figure;
@@ -323,7 +323,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 80])
[…]

### 2015-01-14 Projects/DelCo_2012/Scripts/FSE_Test8.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSE8 Eastside Array' 'FSE8 Westside Array' 'FSE8 Hallway Array' 'FSE8 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSE8 Eastside Array' 'Suppression FSE8 Westside Array' 'Suppression FSE8 Hallway Array' 'Suppression FSE8 Doorway Array'};
+TC_array_names = {'FSE8_Eastside_Array' 'FSE8_Westside_Array' 'FSE8_Hallway_Array' 'FSE8_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSE8_Eastside_Array' 'Suppression_FSE8_Westside_Array' 'Suppression_FSE8_Hallway_Array' 'Suppression_FSE8_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -297,7 +297,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([150 350 0 175])
 legend('Eastside Heat Flux 0.15m','Eastside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSE Test 8 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSE_Test_8_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -319,7 +319,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([150 350 0 175])
 legend('Westside Heat Flux 0.15m','Westside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSE Test 8 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSE_Test_8_Heat_Flux_Westside'])
 hold off
 
 plot1 = figure;
@@ -341,7 +341,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([150 350 0 175])
[…]

### 2015-01-14 Projects/DelCo_2012/Scripts/FSW_Test2.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSW2 Eastside Array' 'FSW2 Westside Array' 'FSW2 Hallway Array' 'FSW2 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSW2 Eastside Array' 'Suppression FSW2 Westside Array' 'Suppression FSW2 Hallway Array' 'Suppression FSW2 Doorway Array'};
+TC_array_names = {'FSW2_Eastside_Array' 'FSW2_Westside_Array' 'FSW2_Hallway_Array' 'FSW2_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSW2_Eastside_Array' 'Suppression_FSW2_Westside_Array' 'Suppression_FSW2_Hallway_Array' 'Suppression_FSW2_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -301,7 +301,7 @@ pos = get(legend_handle,'position');
 set(legend_handle,'position',[Legend_Width_Factor (Plot_Y+(Plot_Height-pos(4))/2) 4 pos(4)])
 set(gcf,'PaperSize',[Paper_Width_Factor Paper_Height]);
 set(gcf,'PaperPosition',[0 0 Paper_Width*1.5 Paper_Height]);
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 2 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_2_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -325,7 +325,7 @@ pos = get(legend_handle,'position');
 set(legend_handle,'position',[Legend_Width_Factor (Plot_Y+(Plot_Height-pos(4))/2) 4 pos(4)])
 set(gcf,'PaperSize',[Paper_Width_Factor Paper_Height]);
 set(gcf,'PaperPosition',[0 0 Paper_Width*1.5 Paper_Height]);
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 2 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_2_Heat_Flux_Westside'])
 hold off
 
[…]

### 2015-01-14 Projects/DelCo_2012/Scripts/FSW_Test3.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSW3 Eastside Array' 'FSW3 Westside Array' 'FSW3 Hallway Array' 'FSW3 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSW3 Eastside Array' 'Suppression FSW3 Westside Array' 'Suppression FSW3 Hallway Array' 'Suppression FSW3 Doorway Array'};
+TC_array_names = {'FSW3_Eastside_Array' 'FSW3_Westside_Array' 'FSW3_Hallway_Array' 'FSW3_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSW3_Eastside_Array' 'Suppression_FSW3_Westside_Array' 'Suppression_FSW3_Hallway_Array' 'Suppression_FSW3_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -301,7 +301,7 @@ pos = get(legend_handle,'position');
 set(legend_handle,'position',[Legend_Width_Factor (Plot_Y+(Plot_Height-pos(4))/2) 4 pos(4)])
 set(gcf,'PaperSize',[Paper_Width_Factor Paper_Height]);
 set(gcf,'PaperPosition',[0 0 Paper_Width*1.5 Paper_Height]);
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 3 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_3_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -325,7 +325,7 @@ pos = get(legend_handle,'position');
 set(legend_handle,'position',[Legend_Width_Factor (Plot_Y+(Plot_Height-pos(4))/2) 4 pos(4)])
 set(gcf,'PaperSize',[Paper_Width_Factor Paper_Height]);
 set(gcf,'PaperPosition',[0 0 Paper_Width*1.5 Paper_Height]);
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 3 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_3_Heat_Flux_Westside'])
 hold off
 
[…]

### 2015-01-14 Projects/DelCo_2012/Scripts/FSW_Test6.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSW6 Eastside Array' 'FSW6 Westside Array' 'FSW6 Hallway Array' 'FSW6 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSW6 Eastside Array' 'Suppression FSW6 Westside Array' 'Suppression FSW6 Hallway Array' 'Suppression FSW6 Doorway Array'};
+TC_array_names = {'FSW6_Eastside_Array' 'FSW6_Westside_Array' 'FSW6_Hallway_Array' 'FSW6_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSW6_Eastside_Array' 'Suppression_FSW6_Westside_Array' 'Suppression_FSW6_Hallway_Array' 'Suppression_FSW6_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -297,7 +297,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 60])
 legend('Eastside Heat Flux 0.15m','Eastside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 6 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_6_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -319,7 +319,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 60])
 legend('Westside Heat Flux 0.15m','Westside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 6 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_6_Heat_Flux_Westside'])
 hold off
 
 plot1 = figure;
@@ -341,7 +341,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 60])
[…]

### 2015-01-14 Projects/DelCo_2012/Scripts/FSW_Test7.m

@@ -43,8 +43,8 @@ plot_style
 
 Num_TC_arrays = 4;
 TC_per_array = 8;
-TC_array_names = {'FSW7 Eastside Array' 'FSW7 Westside Array' 'FSW7 Hallway Array' 'FSW7 Doorway Array'};
-TC_array_names_suppression = {'Suppression FSW7 Eastside Array' 'Suppression FSW7 Westside Array' 'Suppression FSW7 Hallway Array' 'Suppression FSW7 Doorway Array'};
+TC_array_names = {'FSW7_Eastside_Array' 'FSW7_Westside_Array' 'FSW7_Hallway_Array' 'FSW7_Doorway_Array'};
+TC_array_names_suppression = {'Suppression_FSW7_Eastside_Array' 'Suppression_FSW7_Westside_Array' 'Suppression_FSW7_Hallway_Array' 'Suppression_FSW7_Doorway_Array'};
 % for j=1:Num_TC_arrays
 %     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
 % end
@@ -296,7 +296,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 100])
 legend('Eastside Heat Flux 0.15m','Eastside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 7 Heat Flux Eastside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_7_Heat_Flux_Eastside'])
 hold off
 
 plot1 = figure;
@@ -318,7 +318,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 100])
 legend('Westside Heat Flux 0.15m','Westside Rad 0.15m','Location','NorthEastOutside')
-print(gcf,'-dpdf',[plotdirheatflux,'FSW Test 7 Heat Flux Westside'])
+print(gcf,'-dpdf',[plotdirheatflux,'FSW_Test_7_Heat_Flux_Westside'])
 hold off
 
 plot1 = figure;
@@ -340,7 +340,7 @@ xlabel('Time (s)')
 ylabel('Heat Flux (kW/m^2)')
 axis([200 350 0 100])
[…]

### 2015-01-15 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Updated floor plan .idw files, uploaded drawing PDFs, and added pictures to figures folder and report

@@
 \input{../../../../Bibliography/commoncommands}
+
+% Load packages
+\usepackage{graphicx}
 
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_1st_Floor_Metric_Simple}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_1st_Floor_Metric_Simple}
 \\
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_2nd_Floor_Metric_Simple}
-\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts.}
+\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_2nd_Floor_Metric_Simple}
+\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
 \label{fig:west_general_plan}
@@
 
-\section{Fuel Load}
-\label{sec:Fuel_Load}
-
 \section{Instrumentation}
 \label{sec:Instrumentation}
+A schematic plan overview of the instrumentation in the West Structure referenced in this report is shown in Fig.~\ref{fig:west_instrumentation}.
+There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
+Differential pressure transducers connected to bi-directional velocity probes (BDPs) were used to measure gas velocity at specific points throughout the structure ~\cite{McCaffrey:Combustion_and_Flame}.
+Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
+Fig.~\ref{fig:BDPs} shows two sets of BDPs, A5 and A6, which are located at each double door on the first floor of the West Structure.
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
+\\
+\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
+\caption[Location of Instrumentation in West Structure]{Location of Instrumentation in West Structure}
+\label{fig:west_instrumentation}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/BDPs}
+\caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
+\label{fig:BDPs}
+\end{figure}
 
@@
 \label{sec:Uncertainty}
+There are different components of uncertainty in the length, differential pressure, and gas velocity reported in this report.
+Uncertainties are grouped into two categories according to the method used to estimate them.
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means [46].
+Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%.
+After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
+Multiplying the combined standard uncertainty by a coverage factor of two results in the expanded uncertainty which correspond to a 95\% confidence interval (2$\sigma$).
+For some of these components, such as the zero and calibration elements, uncertainties are derived from instrument specifications.
+For other components, such as differential pressure, past experience with the instruments provided input in the uncertainty determination.
+
+Each length measurement was taken carefully. Length measurements such as the room dimensions,
+instrumentation array locations, and fan placement were made with a hand held laser measurement
+device which has an accuracy of $\pm$6.0 mm over a range of 0.61 m to 15.3 m [47]. However, conditions affecting the measurement, such as levelness of the device, yield an
+estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m to 10.0 m range.
+Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
+Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
+
+Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
+The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1\% [52].
+The total expanded uncertainty was estimated at 10\%.
+Bi-directional probes and single thermocouples were used to measure the velocity.
+The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
+Bare-bead Type K thermocouple are co-located with the probe.
+The estimated total expanded uncertainty for velocity in these experiments is $\pm$18\%.
+
+%46.
+Taylor, B.N., and Kuyatt, C.E., “Guidelines for Evaluating and Expressing the Uncertainty of NIST Measurement Results”, National Institute of Standards and Technology, Gaithersburg.
+MD., NIST TN 1297, January 1993.
+%47. Stanley Hand Tools, User Manual TLM 100, 1000 Stanley Drive, New Britain, CT 06053. 
+%52. Setra Model 264 Very Low Pressure Transducer Data Sheet Rev E. Setra Systems, Boxborough, MA., December 2002.
 
@@
 Two sets of experiments involving application patterns, Tests 18 and 19, were conducted.
-The two sets varied in that the first floor south side door was open for Test 18 (Fig.
-\ref{fig:test_18_plan}) and closed for Test 19 (Fig.
-\ref{fig:test_19_plan}).
+The two sets varied in that the first floor south side door was open for Test 18 (Fig~\ref{fig:test_18_plan}) and closed for Test 19 (Fig.~\ref{fig:test_19_plan}).
 
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_1st_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
 \\
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_18_2nd_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
 \caption[West Structure first and second floor layouts for Test 18]{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
@@
 
-\clearpage
-
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_1st_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
 \\
-\includegraphics[width=6in]{../../Drawings/PDFs/Without_Intrumentation/West_Structure_Hose_Test_19_2nd_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
 \caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
@@
 \label{fig:test_19_plan}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Test_18}
+\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18.
+Straight stream pattern is being applied, and flow path is fully established with the stairway door and the north side, west double door opened.}
+\label{fig:test_19_pic}
 \end{figure}

### 2015-01-15 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -144,16 +144,16 @@ for f in os.listdir(data_dir):
                         calibration_intercept = float(scaling['Calibration Intercept'][channel])
 
                         # Scale channel and set plot options depending on quantity
-                        # Plot temperatures
-                        if 'TC_' in channel:
-                            plt.rc('axes', color_cycle=['k', 'r', 'g', 'b', '0.75', 'c', 'm', 'y'])
-                            quantity = data[channel] * calibration_slope + calibration_intercept
-                            ylabel('Temperature ($^\circ$C)', fontsize=20)
-                            line_style = '-'
-                            if 'TC_Helmet_' in channel:
-                                axis_scale = 'Y Scale TC_Helmet'
-                            else:
-                                axis_scale = 'Y Scale TC'
+                        # # Plot temperatures
+                        # if 'TC_' in channel:
+                        #     plt.rc('axes', color_cycle=['k', 'r', 'g', 'b', '0.75', 'c', 'm', 'y'])
+                        #     quantity = data[channel] * calibration_slope + calibration_intercept
+                        #     ylabel('Temperature ($^\circ$C)', fontsize=20)
+                        #     line_style = '-'
+                        #     if 'TC_Helmet_' in channel:
+                        #         axis_scale = 'Y Scale TC_Helmet'
+                        #     else:
+                        #         axis_scale = 'Y Scale TC'
 
                         # Plot velocities
                         if 'BDP_' in channel:
@@ -173,41 +173,41 @@ for f in os.listdir(data_dir):
                             axis_scale = 'Y Scale BDP'
 
                         # # Plot heat fluxes
-                        if any([substring in channel for substring in heat_flux_quantities]):
-                            plt.rc('axes', color_cycle=['k', 'k',
-                                                        'r', 'r',
-                                                        'g', 'g',
-                                                        'b', 'b',
-                                                        'c', 'c'])
+                        # if any([substring in channel for substring in heat_flux_quantities]):
+                        #     plt.rc('axes', color_cycle=['k', 'k',
+                        #                                 'r', 'r',
+                        #                                 'g', 'g',
+                        #                                 'b', 'b',
[…]

### 2015-01-16 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
Delco_2014: Added content to the hose test report

@@
 \label{chap:Introduction}
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.
+The studies have resulted in guidance to the fire service regarding ventilation tactics.
+However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.
+
+Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice.
+This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
+
+This report is concerned with examining the impact of hose stream selection and the pattern in which the stream is applied on the ventilation inside a structure with various flow path configurations.
+Two types of experiments were conducted in order to examine the impact.
+First, cold flow tests were performed.
+These tests involved using a 0.46 m (18 in) diameter positive pressure ventilation (PPV) fan to move air through a structure with various flow path configurations.
+The second type of experiment involved flowing water using various stream and application patterns into a structure with flow path configurations similar to the cold flow test configurations.
+Air velocities measured during the hose flow experiments were compared to the velocities measured during the cold flow tests to determine the impact of hose stream and application pattern combinations on ventilation throughout the structure relative to the impact of using a 0.46 m (18 in) diameter PPV fan to move air throughout the structure.
+
+Three types of hose streams were each applied in four different fashions during each set of hose flow experiments.
+The three types of hose stream patterns studied were straight stream, narrow fog stream, and wide fog stream.
+Water was flowed into the structure by having the hose in a static, fixed position, moving the hose line left-to-right across the room in a sweeping motion, and rotating the hose line in both the clockwise and counterclockwise directions.
 
@@
 
-\subsection{Hose Stream Pattern Experiments}
-\label{sec:Hose_Stream_Pattern_Experiments}
+\subsection{Cold Flow Experimental Procedure}
+\label{sec:Cold_Flow_Procedure}
 
-\subsection{Application Pattern Experiments}
-\label{Application_Pattern_Experiments}
+\subsection{Water Flow Experimental Procedure}
+\label{sec:Water_Flow_Procedure}
 
@@
 \caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18.
-Straight stream pattern is being applied, and flow path is fully established with the stairway door and the north side, west double door opened.}
-\label{fig:test_19_pic}
+A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
+\label{fig:test_18_pic}
 \end{figure}
@@
 
-\section{Hose Flow Tests}
+\section{Cold Flow Test Results}
+\label{sec:Cold_Flow_Test_Results}
 
-\subsection{Tests 18 and 19}
+\section{Water Flow Test Results}
+\label{sec:Water_Flow_Test_Results}
 

### 2015-01-20 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012 Updated Files

@@
 \headerB{
-Delaware County, PA Fire Suppression Tests \\
+Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
 Spring 2012 \\
@@
 
+Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the “thermal balance,” and limit fire damage to structures.
+In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations.
+However guidance on that coordination has been limited.
+Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results.
+One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure.
+In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building.
+The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure.
+Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics.
+This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression.
+
 \chapter{Introduction}
@@
 
+3)  Examine the impact of solid streams, straight streams, and fog streams on the
+
 Constants: 
@@
 Smooth Bore vs Narrow Fog
+
+The Engineering Laboratory at National Institute of Standards and Technology has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
+One of the objectives of this program is to examine non-traditional means of fire suppression.
+This series of experiments conducted by NIST for the California Polytechnic State University, San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.
+These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.
+NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.  
+Three types of experiments were conducted; 
+1)            spray density measures under non-fire conditions 
+2)            gas layer cooling 
+3)            fire suppression in an experimental structures
+
+The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.
+The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies.
+[REF-  PROJECT ON “CAPABILITIES AND LIMITATIONS OF COMPRESSED AIR FOAM SYSTEMS (CAFS) FOR STRUCTURAL FIREFIGHTING” WORKSHOP SUMMARY, December, 13-14, 2011.
+Casey C.
+Grant, P.E., Fire Protection Research Foundation, One Batterymarch Park, Quincy, MA USA 02169-7471
+17 January 2012]
+
+Since Montgomery County (MD) Fire and Rescue Service provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+Baseline operating conditions were agreed upon at the workshop for these experiments.
+
+*Nozzles – Metro 1, fixed gallonage fog/straight/7/8”solid stream  
+100 feet of hose line – 1-3/4”
+Foam concentration – 0.3%
+CAF Flowrate – 120 gpm / 60 cfm 
+Water / air pressure (100-120 psi)
+
+2.3. Study objective
+2.3.1. FF exposure – usability / safety
+2.3.1.1. Steam blowback
+2.3.1.2. Knockdown time
+2.3.1.3. Smoke scrubbing
+2.3.1.4. Rekindle time / prevention
+2.3.1.5. Overhaul / exposure time
+2.3.2. Other Issues
+2.3.2.1. Structural fire testing
+2.3.2.2. Room / attic configuration
+
+These experiments were conducted at the Delaware County (PA) Emergency Services Training Center (ESTC) in Sharon Hill, PA.
 
@@
 
-Total heat flux was measured with Schmidt Boelter gauges.
+Total heat flux was measured with Schmidt-Boelter gauges.
 Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.

### 2015-01-20 Projects/DelCo_2012/Scripts/FSE_Test11.m

@@ -1,0 +1,500 @@
+%Test 11 of DELCO Data 
+
+clear all
+close all
+
+%------------------
+% Set Directory
+%------------------
+
+datadir = '../Raw_Data/';
+
+%------------------
+% Pull Data From File
+%------------------
+
+exp_data_read = importdata([datadir,'CAFS_DelCo_FSE_t1master.csv']); % reads in file into text and data structure
+exp_data = exp_data_read.data;                                 % assigning variable name to test data
+exp_data_header = exp_data_read.textdata;                      % assigning variable name to test headers
+
+j=1;
+for i=1:10:length(exp_data)
+    exp_data_reduced(j,:)=exp_data(i,:);
+    j=j+1;
+end
+
+%------------------
+% Set Save Location for Plots
+%------------------
+
+plotdirtemp='../Figures/Temperature/';
+plotdirheatflux='../Figures/Heat_Flux/';
+plotdirvelocity='../Figures/Velocity/';
+
+%------------------
+% Defines Parameters for Plots
+%------------------
+
+plot_style 
+
+%------------------
+% Define TC Arrays 
+%------------------
+
+Num_TC_arrays = 4;
+TC_per_array = 8;
+TC_array_names = {'FSE1 Test 11 Eastside Array' 'FSE1 Test 11 Westside Array' 'FSE1 Test 11 Hallway Array' 'FSE1 Test 11 Doorway Array'};
+TC_array_names_suppression = {'Suppression FSE1 Test 11 Eastside Array' 'Suppression FSE1 Test 11 Westside Array' 'Suppression FSE1 Test 11 Hallway Array' 'Suppression FSE1 Test 11 Doorway Array'};
+% for j=1:Num_TC_arrays
+%     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
+% end
+
+TC_array(1,:) = {'Eastside 0.03m' 'Eastside 0.3m' 'Eastside 0.61m' 'Eastside 0.91m' 'Eastside 1.22m' 'Eastside 1.52m' 'Eastside 1.83m' 'Eastside 2.13m'};
+TC_array(2,:) = {'Westside 0.03m' 'Westside 0.3m' 'Westside 0.61m' 'Westside 0.91m' 'Westside 1.22m' 'Westside 1.52m' 'Westside 1.83m' 'Westside 2.13m'};
[…]

### 2015-01-20 Projects/DelCo_2012/Scripts/FSE_Test13.m

@@ -1,0 +1,499 @@
+%Test 13 of DELCO Data 
+
+clear all
+close all
+
+%------------------
+% Set Directory
+%------------------
+
+datadir = '../Raw_Data/';
+
+%------------------
+% Pull Data From File
+%------------------
+
+exp_data_read = importdata([datadir,'CAFS_DelCo_FSE_t2master.csv']); % reads in file into text and data structure
+exp_data = exp_data_read.data;                                 % assigning variable name to test data
+exp_data_header = exp_data_read.textdata;                      % assigning variable name to test headers
+
+j=1;
+for i=1:10:length(exp_data)
+    exp_data_reduced(j,:)=exp_data(i,:);
+    j=j+1;
+end
+
+%------------------
+% Set Save Location for Plots
+%------------------
+
+plotdirtemp='../Figures/Temperature/';
+plotdirheatflux='../Figures/Heat_Flux/';
+plotdirvelocity='../Figures/Velocity/';
+
+%------------------
+% Defines Parameters for Plots
+%------------------
+
+plot_style 
+
+%------------------
+% Define TC Arrays 
+%------------------
+
+Num_TC_arrays = 4;
+TC_per_array = 8;
+TC_array_names = {'FSE2 Test 13 Eastside Array' 'FSE2 Test 13 Westside Array' 'FSE2 Test 13 Hallway Array' 'FSE2 Test 13 Doorway Array'};
+TC_array_names_suppression = {'Suppression FSE2 Test 13 Eastside Array' 'Suppression FSE2 Test 13 Westside Array' 'Suppression FSE2 Test 13 Hallway Array' 'Suppression FSE2 Test 13 Doorway Array'};
+% for j=1:Num_TC_arrays
+%     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
+% end
+
+TC_array(1,:) = {'Eastside 0.03m' 'Eastside 0.3m' 'Eastside 0.61m' 'Eastside 0.91m' 'Eastside 1.22m' 'Eastside 1.52m' 'Eastside 1.83m' 'Eastside 2.13m'};
+TC_array(2,:) = {'Westside 0.03m' 'Westside 0.3m' 'Westside 0.61m' 'Westside 0.91m' 'Westside 1.22m' 'Westside 1.52m' 'Westside 1.83m' 'Westside 2.13m'};
[…]

### 2015-01-20 Projects/DelCo_2012/Scripts/FSW_Test12.m

@@ -1,0 +1,499 @@
+%Test 12 of DELCO Data 
+
+clear all
+close all
+
+%------------------
+% Set Directory
+%------------------
+
+datadir = '../Raw_Data/';
+
+%------------------
+% Pull Data From File
+%------------------
+
+exp_data_read = importdata([datadir,'CAFS_DelCo_FSW_t1master.csv']); % reads in file into text and data structure
+exp_data = exp_data_read.data; % assigning variable name to test data
+exp_data_header = exp_data_read.textdata; % assigning variable name to test headers
+
+j=1;
+for i=1:10:length(exp_data)
+    exp_data_reduced(j,:)=exp_data(i,:);
+    j=j+1;
+end
+
+%------------------
+% Set Save Location for Plots
+%------------------
+
+plotdirtemp='../Figures/Temperature/';
+plotdirheatflux='../Figures/Heat_Flux/';
+plotdirvelocity='../Figures/Velocity/';
+
+%------------------
+% Defines Parameters for Plots
+%------------------
+
+plot_style 
+
+%------------------
+% Define TC Arrays 
+%------------------
+
+Num_TC_arrays = 4;
+TC_per_array = 8;
+TC_array_names = {'FSW1 Test 12 Eastside Array' 'FSW1 Test 12 Westside Array' 'FSW1 Test 12 Hallway Array' 'FSW1 Test 12 Doorway Array'};
+TC_array_names_suppression = {'Suppression FSW1 Test 12 Eastside Array' 'Suppression FSW1 Test 12 Westside Array' 'Suppression FSW1 Test 12 Hallway Array' 'Suppression FSW1 Test 12 Doorway Array'};
+% for j=1:Num_TC_arrays
+%     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
+% end
+
+TC_array(1,:) = {'Eastside 0.03m' 'Eastside 0.3m' 'Eastside 0.61m' 'Eastside 0.91m' 'Eastside 1.22m' 'Eastside 1.52m' 'Eastside 1.83m' 'Eastside 2.13m'};
+TC_array(2,:) = {'Westside 0.03m' 'Westside 0.3m' 'Westside 0.61m' 'Westside 0.91m' 'Westside 1.22m' 'Westside 1.52m' 'Westside 1.83m' 'Westside 2.13m'};
[…]

### 2015-01-20 Projects/DelCo_2012/Scripts/FSW_Test14.m

@@ -1,0 +1,499 @@
+%Test 14 of DELCO Data 
+
+clear all
+close all
+
+%------------------
+% Set Directory
+%------------------
+
+datadir = '../Raw_Data/';
+
+%------------------
+% Pull Data From File
+%------------------
+
+exp_data_read = importdata([datadir,'CAFS_DelCo_FSW_t2master.csv']); % reads in file into text and data structure
+exp_data = exp_data_read.data; % assigning variable name to test data
+exp_data_header = exp_data_read.textdata; % assigning variable name to test headers
+
+j=1;
+for i=1:10:length(exp_data)
+    exp_data_reduced(j,:)=exp_data(i,:);
+    j=j+1;
+end
+
+%------------------
+% Set Save Location for Plots
+%------------------
+
+plotdirtemp='../Figures/Temperature/';
+plotdirheatflux='../Figures/Heat_Flux/';
+plotdirvelocity='../Figures/Velocity/';
+
+%------------------
+% Defines Parameters for Plots
+%------------------
+
+plot_style 
+
+%------------------
+% Define TC Arrays 
+%------------------
+
+Num_TC_arrays = 4;
+TC_per_array = 8;
+TC_array_names = {'FSW2 Test 14 Eastside Array' 'FSW2 Test 14 Westside Array' 'FSW2 Test 14 Hallway Array' 'FSW2 Test 14 Doorway Array'};
+TC_array_names_suppression = {'Suppression FSW2 Test 14 Eastside Array' 'Suppression FSW2 Test 14 Westside Array' 'Suppression FSW2 Test 14 Hallway Array' 'Suppression FSW2 Test 14 Doorway Array'};
+% for j=1:Num_TC_arrays
+%     TC_array_suppression = strcat('Suppression ',TC_array_names{j});
+% end
+
+TC_array(1,:) = {'Eastside 0.03m' 'Eastside 0.3m' 'Eastside 0.61m' 'Eastside 0.91m' 'Eastside 1.22m' 'Eastside 1.52m' 'Eastside 1.83m' 'Eastside 2.13m'};
+TC_array(2,:) = {'Westside 0.03m' 'Westside 0.3m' 'Westside 0.61m' 'Westside 0.91m' 'Westside 1.22m' 'Westside 1.52m' 'Westside 1.83m' 'Westside 2.13m'};
[…]

### 2015-01-22 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014_Outline.tex
DelCo_2014: Created outline for hose test report and edited hose test report

\documentclass{article}
\usepackage{outlines}
\usepackage{enumitem}
\setenumerate[1]{label=\Roman*.}
\setenumerate[2]{label=\Alph*.}
\setenumerate[3]{label=\roman*.}
\setenumerate[4]{label=\alph*.}
\begin{document}

DelCo 2014 Hose Stream Report Outline\\

\begin{outline}[enumerate]
\1 Introduction 
	\2 Background
		\3 Overview of different techniques used throughout the fire service
		\3 Brief review of hose stream research already in existence
	\2 Description of stream and application patterns considered in report

\1 Experimental Setup
	\2 Structures
		\3 General construction (picture of both structures)
		\3 East structure dimensioned floor plan
		\3 West structure dimensioned floor plan 
	\2 Instrumentation
		\3 Description/picture(s) of instrumentation used
		\3 East structure floor plan drawing with BDP/TC locations
		\3 West structure floor plan drawing with BDP/TC locations
	\2 Uncertainty
		\3 Explanation of Type A and B uncertainties
		\3 Length measurements
		\3 BDP velocity measurements
		\3 Water flow rate and hoseline pressure measurements

\1 Experimental Procedure
	\2 Cold flow tests
		\3 Differences in each procedure (e.g., different flow path configurations)
	\2 Water flow tests
		\3 Monitor aimed at various locations
		\3 Handline with various patterns
		\3 Differences in each procedure (e.g., different flow path configurations)

\1 Results
	\2 Cold flow tests
	\2 Water flow tests
		\3 Monitor at different locations
		\3 Hose stream patterns
		\3 Application patterns
			\4 No difference between CW and CCW

\1 Conclusion

\1 Future Work

\1 Acknowledgements

\1 References

\end{outline}

\end{document}

### 2015-01-23 Projects/224_Emissions/Report/ECS_Testing.tex
224_EGFS: add tex file and directories

\documentclass[12pt,oneside]{book}
\input{../../../Bibliography/commoncommands}

\renewcommand{\chaptername}{Section}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

\chapter{Test Fires}
\label{test_fires}
To accept the Exhaust Gas Filter System (EGFS) in building 224, commissioning tests need to be performed.  During normal operation of laboratories in building 224, there are a wide range of instrumentation and fuel sources that can produce heat and/or combustion gases (soot). Elevated temperatures and large quantities of soot will challenge the integrity of the EGFS. Therefore, the commissioning tests will utilize several laboratories along with a range of fuel and experimental apparatuses in building 224 to ensure that EGFS meets the needs of NIST's Fire Research Division. Table~\ref{tab:sources} describes the sources that will be used in each of the participating laboratories.

\begin{table}[!h]
\centering
\caption{Fire Locations and Sources}
\label{tab:sources}
\begin{tabular}{cccc}
\toprule[1.5pt]
Room \# & Peak Rated HRR (kW) & Source & Test Procedure  \\
\midrule
A350     & 20   & Cone Calorimeter     & \ref{proc_cone}  \\
B345     & 10   & Flow Loop            & \ref{proc_flowloop}  \\
B347/49  & 115  & Lift (Radiant Panel) & \ref{proc_radpanel} \\
B351/53  & 50   & Pool Fire            & \ref{proc_poolfire} \\
B355     & 100  & Pool Fire            & \ref{proc_poolfire} \\
\bottomrule[1.25pt]
\end{tabular}\par
\end{table}

Based on the laboratory heat release rate (HRR) hood ratings, test equipment, and fuel sources as described in Table~\ref{tab:sources}, a test plan outlining at minimum 19 tests was established. Table~\ref{tab:fires} describes the tests, fire/heat load, and estimated duration. The first test is designed to capture background data of the system running at ambient conditions so that the Fire Research Division has a baseline to compare degrading filters and replacement filters against to assess performance. The remaining tests all stress the system by introducing hot gases and/or soot into the EGFS. As the test numbers increase, more labs will be operating in parallel to ensure the EGFS will function when Fire Research Division is testing at capacity. During testing, the Fire Research Division needs to know the temperature of the gas upstream of the filter system and the pressure drop across the filter system. Ideally, we would like to know the pressure drop across each stage of the filter system.

\begin{table}[!h]
\centering
\caption{Test Fire Scenarios}
\label{tab:fires}
\begin{tabular}{cccccc}
\toprule[1.5pt]
Test \# & Room \# & Fire HRR (kW) & Source & Purpose & Duration  \\
\midrule
1  &  All             & 0    & N/A                 & Baseline      & 48~hrs \\
2  &  B345            & 0    & Flow Loop           & Temp          & Indefinite \\
3  &  A350            & 20   & Cone                & Temp + Soot   & Indefinite \\
4  &  B351/53 $^*$    & 20   & Pool - Heptane      & Temp + Soot   & 270~s  \\
5  &  B351/53 $^*$    & 50   & Pool - Heptane      & Temp + Soot   & 140~s \\
6  &  B355 $^+$       & 20   & Pool - Heptane      & Temp + Soot   & 270~s \\
7  &  B355 $^+$       & 50   & Pool - Heptane      & Temp + Soot   & 140~s \\
8  &  B355 $^+$       & 90   & Pool - Heptane      & Temp + Soot   & 140~s \\
9  &  B351/53 $^*$    & 20   & Pool - Toluene      & Temp + Soot   & 270~s  \\
10 &  B351/53 $^*$    & 50   & Pool - Toluene      & Temp + Soot   & 140~s \\
11 &  B355 $^+$       & 20   & Pool - Toluene      & Temp + Soot   & 270~s \\
12 &  B355 $^+$       & 50   & Pool - Toluene      & Temp + Soot   & 140~s \\
13 &  B355 $^+$       & 90   & Pool - Toluene      & Temp + Soot   & 140~s \\
14 &  B347/49         & 50   & Lift                & Temp + Soot   & Indefinite \\
15 &  B347/49         & 50   & Lift - Polystyrene  & Temp + Soot   & Sample Dependent \\
16 &  B347/49         & 50   & Lift - Polyurethane & Temp + Soot   & Sample Dependent \\
17 &  B347/49$^\#$    & 50   & Lift                & Temp + Soot   & Indefinite \\
18 &  B347/49$^\#$    & 50   & Lift - Polystyrene  & Temp + Soot   & Sample Dependent \\
19 &  B347/49$^\#$    & 50   & Lift - Polyurethane & Temp + Soot   & Sample Dependent \\
\bottomrule[1.25pt]
\end{tabular}\par
\raggedright
$^*$ plus tests 2 and 3 \\
$^+$ plus tests 2, 3, and 5 \\
$^\#$ plus tests 2, 3, 5, and 13 \\
\end{table}
\justify

\chapter{Safety}
\label{safety}
\section{Lab Safety Controls}
\label{controls}
At least two members of the Fire Research Division will be present to perform a pre-test inspection. A safety briefing will be connected prior to each test. All test participants and observers must attend the safety briefing. Test specific emergency procedures must be reviewed at each safety briefing.

\section{Potential Lab Hazards}
\label{lab_hazards}
For the ECS commissioning tests at the NFRL, the building will be transitioning from a construction site to an active laboratory. This combination space presents safety hazards to occupants. A partial lists of hazards to consider follows:
\begin{itemize}
\item {\bf Electrical Hazards}
%Minimum personal protective equipment (PPE) is safety glasses with side shields and steel toed safety shoes. Equipment, power cords and general housekeeping are inspected on a regular basis by Workspace Manager. Users of equipment in this workspace must have completed electrical safety training. All wall outlets are appropriately marked with voltage and breaker box number/breaker number.
\item {\bf Toxic/Corrosive Chemicals}
%All workers in this lab must complete MSDS training. CO detectors are installed near the CO cylinder and throughout work areas.  All NFRL staff members and guest workers are equipped with personal CO monitors that alarm at 10 ppm. Post fire test specimens (such as mattresses, furniture and demolished burn room structures that must be removed from building 205 are doused with water and stored in the rented construction dumpster). A thermal imaging camera will be used to insure samples have been fully extinguished before placing in this dumpster. Appropriate protective clothing and breathing apparatus will be determined according to the hazards associated with disposal of post-project debris.
\item {\bf Flammable/Reactive Materials}
%Minimum PPE is safety glasses with side shields and steel toed safety shoes. Two permanent flammable gas alarms are located above the natural gas fuel delivery line in the ceiling area. Protective barrier posts are installed at the base of the natural gas line to prevent vehicle collision. The gas line is equipped with three quarter turn shutoff valves and an automatic safety shutoff valve (secured with a key to prevent unintended use). A quarter turn valve located on the south side of building 205 can be used to shut off the gas supply to the entire building.  The natural gas flow rate and pressure are monitored when the burner is in use.
\item {\bf High Pressure Fluid Flow}
%Minimum PPE is safety glasses with side shields and steel toed safety shoes. Fire hose stream operators must complete MFRI fire suppression training and NFRL WSM led training.  Fire hose lines are routinely inspected and checked for leaks and taken out of service when leaks are found. Standpipe valves are closed and secured when not in use. A minimum of two qualified operators are required to handle a hose stream suppression line. 
\item {\bf Moving Heavy Objects}
%A forklift, hand truck, pallet jack, hoist crane and/or skid loader will be utilized to lift and move heavy objects that cannot be moved by hand. All operators will be adequately trained to use these devices. Training records must be documented in an approved project FLHR document before the start of any activity with this equipment.
\end{itemize}

\section{Experimental Test Procedures}
\label{test_procedure}

\subsection{Cone Calorimeter}
\label{proc_cone}
\begin{enumerate}
  \item Verify operation of the room exhaust hood. Do not proceed if exhaust hood is not operating properly.
  \item Turn on bench power.
  \item Turn on heat flux water.
  \item Turn on chiller system (temperature will drop to about 2~$^{\circ}$C.
  \item Turn on weigh system. Note that 30 minute warm up time is needed.
  \item Run setup on Cone Application software.
  \item Replace the ascerite and drierite as shown by the indicator. Collect the discarded material in the appropriate waste containers.
  \item Check and clean the soot filter, replace filter as needed.
  \item Calibrate system.
  \item Prepare sample and place in specified sample holder. Place the sample such that it is not exposed to heat radiation from the cone prior to the experiment.
  \item Once sample is exposed to heat, flaming combustion can occur.
  \item Once the sample is no longer generating combustion products (e.g. no glowing embers, smoke) the sample is removed from the balance and transferred to the chemical hood. Use appropriate PPE (heat resistant gloves or channel locks held with leather gloves, safety glasses, lab jacket and closed toed shoes).
  \item Switch off the cone heater power. 
  \item Switch of the sample pump; exhaust system, methane system, weight system and chiller. Do not switch off the gas analyzers.
  \item Switch off water.
\end{enumerate}

\subsection{Flow Loop}
\label{proc_flowloop}
\begin{enumerate}
  \item Verify operation of the room exhaust hood. Do not proceed if exhaust hood is not operating properly.
  \item Adjust the equipment platform, if necessary. Plug in the platform lift controller and use the control switches to raise or lower platform. 
  \item After all equipment is setup, close the bottom opening of the flow loop test section using either the sliding door or the lift platform.  
  \item Close and secure the side door of the flow loop test section.
  \item Close the flow loop top vent located directly under the exhaust hood.
  \item  Phone the NIST fire department (x6190) to notify them of high temperature testing in the laboratory (224/B345). They need to isolate the laboratory heat detector.
  \item Turn on the blower.  Press``FDW'' button, and set controller to desired speed. ({\em Note: Always make sure blower is operating BEFORE turning on the heaters.  If heaters are activated without blower, the coils can overheat and damage the heater or the flow loop housing.})
  \item Turn the temperature controller switch to ON (on large control box on the wall). The current flow loop air temperature, and the set-point temperature will be displayed in degrees C. To select a new set-point temperature, use the arrow buttons below the display on the the temperature controller.  
  \item Unlock and remove the administrative locks from the two heater power switches (large red switches on wall next to control box).  
  \item Activate the heaters by turning the two heater power switches to ON. Controller will increase heater temperature to the set point. 
  \item Monitor the temperatures. The set point may be adjusted if desired.
  \item For this test only, open the vent on top of the flow loop (under the exhaust hood) to vent the heated air from the flow loop. Keep the configuration in this setting for duration of testing.
  \item To begin SHUTDOWN procedures, Turn OFF the heater power switches to shut off the heater. Replace and lock the administrative locks on the power switches.
  \item Open the bottom door of the flow loop test section to allow room air to be drawn into the loop for cooling.
  \item Leave the blower ON to circulate air to cool the heater and flow loop.   
  \item Monitor the temperature inside the flow loop as indicated by temperature controller.  When the interior temperature is below 50~$^{\circ}$C, the blower may be turned off.
  \item Notify the fire department that testing is finished.
\end{enumerate}

\subsection{Radiant Panel}
\label{proc_radpanel}
\begin{enumerate}
  \item Verify operation of the room exhaust hood. Do not proceed if exhaust hood is not operating properly.
  \item Fan should be operating in excess of 1500~SCFM
  \item Turn on combustion air and check rotometer flow.
  \item Turn on main gas value located on control panel along centerline of room.
  \item Turn on value at the apparatus.
  \item Light propane torch. While keeping the hand and propane bottle protected to the side and away from the panel, allow the flame to rest on teh upper face of the radiant panel.
  \item Turn on electrical start toggle switch.
  \item Observe that the UV sensor safety switch turns on.
  \item When UV light turns on, push the electrical start switch and hold until the flame rod safety switch light comes on. Flames should cover the radiant panel.
  \item Turn off propane torch and store in chemical hood.
  \item To begin SHUTDOWN, turn off gas control switch.
  \item Turn off gas to radiant panel.
  \item Turn off main gas supply.
  \item Allow combustion air to cool before turning off supply air.
  \item EMERGENCY SHUT OFFs are location at each exit door the the laboratory.      
\end{enumerate}

\subsection{Pool Fires}
\label{proc_poolfire}
\begin{enumerate}
  \item All flammable liquid stored are in safe container. 
  \item A secondary containment device (graduate cylinder) will be used when transferring fuels and conducting fire tests.
  \item Position test pan in appropriate position under test hood.
  \item Fill ignition pans with desired level of liquid fuel.
  \item Ignite fuel pans with a 1.22~m - 1.83~m (4-6~ft) propane wand igniter.
  \item Workers are required to use PPE when performing post-fire cleanup.
\end{enumerate}

\end{document}

### 2015-01-23 Projects/224_Emissions/Report/ECS_Testing.tex
Update ECS report

@@
 Based on the laboratory heat release rate (HRR) hood ratings, test equipment, and fuel sources as described in Table~\ref{tab:sources}, a test plan outlining at minimum 19 tests was established.
-Table~\ref{tab:fires} describes the tests, fire/heat load, and estimated duration.
+Table~\ref{tab:fires} describes the tests, fire/heat load, and locations.
 The first test is designed to capture background data of the system running at ambient conditions so that the Fire Research Division has a baseline to compare degrading filters and replacement filters against to assess performance.
@@
 \label{tab:fires}
-\begin{tabular}{cccccc}
+\begin{tabular}{ccccc}
 \toprule[1.5pt]
-Test \# & Room \# & Fire HRR (kW) & Source & Purpose & Duration  \\
+Test \# & Room \# & Peak Fire HRR (kW) & Source & Purpose \\
 \midrule
-1  &  All             & 0    & N/A                 & Baseline      & 48~hrs \\
-2  &  B345            & 0    & Flow Loop           & Temp          & Indefinite \\
-3  &  A350            & 20   & Cone                & Temp + Soot   & Indefinite \\
-4  &  B351/53 $^*$    & 20   & Pool - Heptane      & Temp + Soot   & 270~s  \\
-5  &  B351/53 $^*$    & 50   & Pool - Heptane      & Temp + Soot   & 140~s \\
-6  &  B355 $^+$       & 20   & Pool - Heptane      & Temp + Soot   & 270~s \\
-7  &  B355 $^+$       & 50   & Pool - Heptane      & Temp + Soot   & 140~s \\
-8  &  B355 $^+$       & 90   & Pool - Heptane      & Temp + Soot   & 140~s \\
-9  &  B351/53 $^*$    & 20   & Pool - Toluene      & Temp + Soot   & 270~s  \\
-10 &  B351/53 $^*$    & 50   & Pool - Toluene      & Temp + Soot   & 140~s \\
-11 &  B355 $^+$       & 20   & Pool - Toluene      & Temp + Soot   & 270~s \\
-12 &  B355 $^+$       & 50   & Pool - Toluene      & Temp + Soot   & 140~s \\
-13 &  B355 $^+$       & 90   & Pool - Toluene      & Temp + Soot   & 140~s \\
-14 &  B347/49         & 50   & Lift                & Temp + Soot   & Indefinite \\
-15 &  B347/49         & 50   & Lift - Polystyrene  & Temp + Soot   & Sample Dependent \\
-16 &  B347/49         & 50   & Lift - Polyurethane & Temp + Soot   & Sample Dependent \\
-17 &  B347/49$^\#$    & 50   & Lift                & Temp + Soot   & Indefinite \\
-18 &  B347/49$^\#$    & 50   & Lift - Polystyrene  & Temp + Soot   & Sample Dependent \\
-19 &  B347/49$^\#$    & 50   & Lift - Polyurethane & Temp + Soot   & Sample Dependent \\
+1  &  All             & 0    & N/A                 & Baseline      \\
+2  &  B345            & 0    & Flow Loop           & Temp          \\
+3  &  A350            & 20   & Cone                & Temp + Soot   \\
+4  &  B351/53 $^*$    & 20   & Pool - Heptane      & Temp + Soot   \\
+5  &  B351/53 $^*$    & 50   & Pool - Heptane      & Temp + Soot   \\
+6  &  B355 $^+$       & 20   & Pool - Heptane      & Temp + Soot   \\
+7  &  B355 $^+$       & 50   & Pool - Heptane      & Temp + Soot   \\
+8  &  B355 $^+$       & 90   & Pool - Heptane      & Temp + Soot   \\
+9  &  B351/53 $^*$    & 20   & Pool - Toluene      & Temp + Soot   \\
+10 &  B351/53 $^*$    & 50   & Pool - Toluene      & Temp + Soot   \\
+11 &  B355 $^+$       & 20   & Pool - Toluene      & Temp + Soot   \\
+12 &  B355 $^+$       & 50   & Pool - Toluene      & Temp + Soot   \\
+13 &  B355 $^+$       & 90   & Pool - Toluene      & Temp + Soot   \\
+14 &  B347/49         & 50   & Lift                & Temp + Soot   \\
+15 &  B347/49         & 50   & Lift - Polystyrene  & Temp + Soot   \\
+16 &  B347/49         & 50   & Lift - Polyurethane & Temp + Soot   \\
+17 &  B347/49$^\#$    & 50   & Lift                & Temp + Soot   \\
+18 &  B347/49$^\#$    & 50   & Lift - Polystyrene  & Temp + Soot   \\
+19 &  B347/49$^\#$    & 50   & Lift - Polyurethane & Temp + Soot   \\
 \bottomrule[1.25pt]
@@
 \label{lab_hazards}
-For the ECS commissioning tests at the NFRL, the building will be transitioning from a construction site to an active laboratory.
-This combination space presents safety hazards to occupants.
-A partial lists of hazards to consider follows:
+This space presents safety hazards to occupants. A list of hazards that have been considered include:
 \begin{itemize}
@@
 The natural gas flow rate and pressure are monitored when the burner is in use.
-\item {\bf High Pressure Fluid Flow}
-%Minimum PPE is safety glasses with side shields and steel toed safety shoes.
-Fire hose stream operators must complete MFRI fire suppression training and NFRL WSM led training.
-Fire hose lines are routinely inspected and checked for leaks and taken out of service when leaks are found.
-Standpipe valves are closed and secured when not in use.
-A minimum of two qualified operators are required to handle a hose stream suppression line.
 \item {\bf Moving Heavy Objects}
@@
 \end{itemize}
+Staff have been trained and will use appropriate PP including safety glasses, appropriate footwear, and gloves.
 
@@
   \item Position test pan in appropriate position under test hood.
+  \item The pan will be placed within a spill barrier during testing.
   \item Fill ignition pans with desired level of liquid fuel.
   \item Ignite fuel pans with a 1.22~m - 1.83~m (4-6~ft) propane wand igniter.
+  \item To extinguish, the pool fires will be snuffed out.
   \item Workers are required to use PPE when performing post-fire cleanup.
@@
 
+\subsection{Emergency Procedures}
+If an emergency shutdown is required, each lab will follow the shutdown procedures dictacted by the ongoing test and standard operating laboratory specfic guidelines.
+
 \end{document}

### 2015-01-28 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Added Uncertainties

@@
 NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.
+
 Three types of experiments were conducted;
+
 1)            spray density measures under non-fire conditions 
@@
 \label{subsec:Uncertainty}
+
+There are different components of uncertainty in the length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity and heat release rate reported here.
+Uncertainties are grouped into two categories according to the method used to estimate them.
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means  [ ].
+Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval (± a) is essentially 100 %.
+After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
+Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95 % confidence interval (2σ).
+For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
+For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.
+
+Each length measurement was taken carefully.
+Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of ± 6.0 mm (0.25) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft) [ ] .
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of ± 0.5 % for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
+Steel measuring tapes with a resolution of  ± 0.5 mm (0.02 in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of ±1.6 mm (0.06 in) for 9.1 m (30 ft) tapes and ±6.4 mm (0.25 in) for 30.5 m (100 ft) tapes [ ] .
+Some issues, such as “soft” edges on the upholstered furniture, result in an estimated total expanded uncertainty of  ± 1.0 %.
+
+The load cell used to weigh the fuels prior to the experiments had a range of 0 kg (0 lbs) to 200 kg (440lbs) with a resolution of a 0.05 kg (0.11 lb) and a calibration uncertainty within 1% [] .
+The expanded uncertainty is estimated to be less than  ± 5 %.
+The standard uncertainty in temperature of the thermocouple wire itself is  ± 2.2 °C at 277 °C and increases to ± 9.5 °C at 871 °C as determined by the wire manufacturer [ ] .
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty [ ,  ] .
+Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
+The estimated total expanded uncertainty for temperature in these experiments is ± 15 %.
+In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
+The manufacturer reports a ± 3 % calibration expanded uncertainty for these devices [ ] .
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically ± 8 % [] .
+
+The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of ± 1 % when compared with span gas volume fractions [].
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of ± 12 % is being applied to the results [ ].
+
+Differential pressure reading uncertainty components were derived from pressure transducer
+instrument specifications and previous experience with pressure transducers. The transducers
+were factory calibrated and the zero and span of each was checked in the laboratory prior to the
+experiments yielding an accuracy of ± 1 % [ ] . The total expanded uncertainty was estimated at 10 %.
+
+Bi-directional probes and single thermocouples were used to measure the velocity.
+The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
+Bare-bead Type K thermocouple are co-located with the probe.
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from ± 0.14 to ± 0.22 for bi-directional probes of similar design[] .
+The total expanded uncertainty for gas velocity in these experiments w estimated to be  ± 18 %.
+Water Flowrate
+Water flowrate was measured with a pressure and flow meter combination shown in Figure x.x.
+The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0 – 4.1 MPa (0 - 600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
+The manufacturer reports a ± 5 % calibration expanded uncertainty for the flow sensor and ± 3 %  for the pressure sensor [ ] .
+The pressure transducer was calibrated with a known analog pressure gauge.
+The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
+The total expanded uncertainty was estimated at ± 10 %.
 

### 2015-01-29 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated Report

@@
 
-WATER DISTRIBUTION
-
-Purpose:
-- Determine the appropriate location for nozzles
-- Determine water distribution
-
-Setup:
-Task Force Tips Metro 1, Fixed Gallonage (120 gpm)
-Straight Stream
-30 degree Fog
-7/8” Smooth Bore
-100 ft of 1-3/4 inch hose
-
-The hose streams were from fixed monitor nozzles simulating a firefighter with the hose line in the structure.
-
-Controlled and operated via a gate valve from the exterior.
-
-12 Experiments:
-4 SS from room
-2 Fog from room
-2 SS from Hall
-2 Fog from Hall
-1 SB from Hall
-1 SB from Room
-
-2.5 square foot collector bin.
-
-Bins were poly boxes with interlacing lips to prevent water from going in between.
-
-Measured how much of the water ended up in what part of the room.
-
-The building was sheathed in plastic for the water flow tests as to protect and preserve the structure before any fire suppression tests were conducted.
-
-Spray Distribution Summary:
-- Experiments provided nozzle placement for gas cooling and fire suppression experiments.
-- Provide a sense of the distribution of the water throughout the test space.
-
-Hallway nozzle = gas cooling
-
-Room nozzle = seat of fire
+The experimental set-up for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
+
+SPRAY DENSITY MEASURES
+
+Thirty two tests were conducted to determine spray density measures based on various nozzle patterns and locations.
+The purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
+This set-up is representative of a firefighter operating on a hose line within the structure.
+Therefore, it is critical to ensure proper nozzle location for the tests to follow to provide the most realistic test conditions.
+
+The nozzles chosen for these experiments were as a result of those available through the MCFRS provided engine and decided upon during the CAFS workshop.
+This test series used Task Force Tips (TFT) Metro 1, Fixed Gallonage nozzles with a flow rate of 120 gpm.
+These are automatic nozzles which have a 7/8 inch slug-tip and can be varied from a straight stream to a wide fog for application.
+The set-up also included 100 ft of 1-3/4 inch hose.
+The nozzles were mounted to a "blitz-fire" monitor device and placed inside the structures.
+The nozzles were controlled and operated via a gate valve from the exterior.
+
+The tests conducted for spray density measurement were divided between the available structures at the Delaware County ESTC.
+Twenty one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests.
+The tests varied by changing the nozzle height and location within the structure.
+Additionally, the nozzle pattern was varied as well.
+A description and drawings of these facilities can be seen in the Experimental Facility section below.
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Flows}
+	\caption{Spray Density Nozzle Patterns}
+	\label{fig:Spray_Density_Nozzle_Patterns}
+\end{figure}
+
+The experiments were conducted by placing interlocking collector bins across the floor surface area of the burn rooms within each structure.
+Each collector bin was a 2.5 square foot poly box.
+The building was sheathed in plastic for the spray density tests in order to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
+The nozzles were flowed for a set duration and once the test was concluded, the bins were removed from the structure.
+The amount of water in each bin was measured in order to determine how much of the water ended up in each part of the room dependent on the nozzle location and pattern.
+The results can be seen in the sections to follow.
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
+	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
+	\label{fig:Spray_Density_Set_Up}
+\end{figure}
+
+GAS LAYER COOLING
 
@@
 
-Room and contents fire inside structure
-Two points of interior attack
-- Remotely activated in hallway (indirect attack)
-- Remotely activated in fire room (direct attack)
-
-Common household furnishings.
+The fire suppression analysis included a series of 14 tests in two single story experimental structures, also located on the grounds of the Delaware County ESTC.
+Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.
+Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings.
+The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used.
+Several other factors including the fuel load and available ventilation were varied during these tests.
+
+Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.
+The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.
+The fires were intended to replicate room and contents fires typically seen within residential structures.
+The hose lines were pre-deployed with fixed nozzles set in two locations.
+One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle).
+The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
+Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack.
+The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.
+This position represented a direct interior attack.
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
+	\caption{Hallway Nozzle Location}
+	\label{fig:Hallway_Nozzle_Location}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
+	\caption{Room Nozzle Location}
+	\label{fig:Room_Nozzle_Location}
+\end{figure}
 
@@
 The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.
-The interior dimensions of teach structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 
+Each 
+12 Experiments:
+4 SS from room
+2 Fog from room
+2 SS from Hall
+2 Fog from Hall
+1 SB from Hall
+1 SB from Room
+
+Spray Distribution Summary:
+- Experiments provided nozzle placement for gas cooling and fire suppression experiments.
+- Provide a sense of the distribution of the water throughout the test space.
+
+Hallway nozzle = gas cooling
+
+Room nozzle = seat of fire
+
 \section{Fire Suppression}

### 2015-01-31 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Created outline for hose test report and edited hose test report
DelCo_2014: Added content to the hose test report and changed title of outline

@@
 \headerB{
-Delco 2014
+Impact of Hose Streams on Air Flows inside a Structure
 }
@@
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.
+However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams are needed.
 
@@
 
-\subsection{Hose Stream Patterns}
-\label{sec:Hose_Stream_Patterns}
-
-\subsection{Application Patterns}
-\label{Application_Patterns}
-
 \chapter{Experimental Setup}
@@
 Two structures, shown in Fig.~\ref{fig:struct_pics}, were constructed for the experiments.
-Each structure contained a ground level floor composed of concrete walls.
+Each structure contained a ground level floor composed of walls surrounded by concrete blocks.
 The West Structure contained a second level.
@@
 \label{sec:Instrumentation}
-A schematic plan overview of the instrumentation in the West Structure referenced in this report is shown in Fig.~\ref{fig:west_instrumentation}.
+Schematic plan overviews of the instrumentation in the East and West Structures are shown in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}, respectively.
 There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
-Differential pressure transducers connected to bi-directional velocity probes (BDPs) were used to measure gas velocity at specific points throughout the structure ~\cite{McCaffrey:Combustion_and_Flame}.
+Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
 Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
-Fig.~\ref{fig:BDPs} shows two sets of BDPs, A5 and A6, which are located at each double door on the first floor of the West Structure.
+Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure.
+A single thermocouple was attached to each bi-directional probe.
+The thermocouples used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter.
+Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.
+
+%\begin{figure}[!ht]
+%\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/East_Test_Structure_Devices_Hose_Test}
+%\caption[Location of Instrumentation in East Structure]{Location of Instrumentation in East Structure}
+%\label{fig:east_instrumentation}
+%\end{figure}
 
@@
 \label{sec:Uncertainty}
-There are different components of uncertainty in the length, differential pressure, and gas velocity reported in this report.
+There are different components of uncertainty in the length, differential pressure, and gas velocity reported here.
 Uncertainties are grouped into two categories according to the method used to estimate them.
-Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means [46].
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means ~\cite{Taylor&Kuyatt:1994}.
 Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Multiplying the combined standard uncertainty by a coverage factor of two results in the expanded uncertainty which correspond to a 95\% confidence interval (2$\sigma$).
-For some of these components, such as the zero and calibration elements, uncertainties are derived from instrument specifications.
-For other components, such as differential pressure, past experience with the instruments provided input in the uncertainty determination.
+Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$).
+For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
+For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.
 
 Each length measurement was taken carefully. Length measurements such as the room dimensions,
-instrumentation array locations, and fan placement were made with a hand held laser measurement
-device which has an accuracy of $\pm$6.0 mm over a range of 0.61 m to 15.3 m [47]. However, conditions affecting the measurement, such as levelness of the device, yield an
-estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m to 10.0 m range.
+instrumentation array locations, and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}.
+However, conditions affecting the measurement, such as levelness of the device, yield an
+estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
 Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in) for 30.5 m (100 ft) tapes \cite{NIST_Manual_44}.
 Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
 
-Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1\% [52].
-The total expanded uncertainty was estimated at 10\%.
 Bi-directional probes and single thermocouples were used to measure the velocity.
@@
 Bare-bead Type K thermocouple are co-located with the probe.
-The estimated total expanded uncertainty for velocity in these experiments is $\pm$18\%.
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design \cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments estimated to be $\pm18$\%.
 
-%46.
-Taylor, B.N., and Kuyatt, C.E., “Guidelines for Evaluating and Expressing the Uncertainty of NIST Measurement Results”, National Institute of Standards and Technology, Gaithersburg.
-MD., NIST TN 1297, January 1993.
-%47. Stanley Hand Tools, User Manual TLM 100, 1000 Stanley Drive, New Britain, CT 06053. 
-%52. Setra Model 264 Very Low Pressure Transducer Data Sheet Rev E. Setra Systems, Boxborough, MA., December 2002.
+Water flowrate was measured with a pressure and flow meter combination shown in Fig.
+\ref{fig:flow_meter}.
+The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0–4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
+The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor \cite{Akron}.
+The pressure transducer was calibrated with a known analog pressure gauge.
+The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
+The total expanded uncertainty was estimated at $\pm10$\%.
+
+%\begin{figure}[!ht]
+%\includegraphics[width=6in]{../../Figures/flow_meter}
+%\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
+%\label{fig:flow_meter}
+%\end{figure}
+
+In the following sections, the measurements will be presented in graphic and tabular form.
+In the graphs, an error bar will represent the estimated uncertainty of the measurement.
+In the tables, the uncertainty will be included in the table of as part of the caption.
 
@@
 \label{sec:Water_Flow_Procedure}
+A total of four sets of experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
 
 Two sets of experiments involving application patterns, Tests 18 and 19, were conducted.
-The two sets varied in that the first floor south side door was open for Test 18 (Fig~\ref{fig:test_18_plan}) and closed for Test 19 (Fig.~\ref{fig:test_19_plan}).
+The two sets varied in that the first floor south side door was open for Test 18 (Fig.~\ref{fig:test_18_plan}) and closed for Test 19 (Fig.~\ref{fig:test_19_plan}).
 

### 2015-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated Text

@@
 
+\section{Experiment Descriptions}
+\label{sec:Experiment_Descriptions}
+
 The experimental set-up for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
 
-SPRAY DENSITY MEASURES
+\subsection{Spray Density Measures}
+\label{sec:Spray_Density_Measures}
 
@@
 
-GAS LAYER COOLING
-
-FIRE SUPPRESSION
+\subsection{Gas Cooling}
+\label{sec:Gas_Cooling}
+
+\subsection{Fire Suppression}
+\label{sec:Fire_Suppression}
 
@@
 
+The series of tests described within this report were conducted at the Delaware County Emergency Services Training Center, located in Sharon Hill, PA.
+A burn building as well as two purpose built concrete structures are located on the grounds of the ESTC.
+The burn building was used for the gas cooling experiments and the purpose built concrete structures were used for the fire suppression experiments.
+
 \subsection{Burn Building - Gas Cooling}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCo_Structures}
-	\caption{Delaware County, PA Fire Test Structures}
-	\label{fig:Delaware_County,_PA_Fire_Test_Structures}
-\end{figure}
+The burn building is a purpose-built live fire training structure comprised of both a two story and three story section.
+The building is supported with reinforced concrete beams and columns.
+The floors and ceilings are also concrete with the interior walls constructed of cement block.
+The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thinck layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile.
+The floor of the burn rooms is protected with fire brick.
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
+	\caption{Delaware County, PA Burn Building}
+	\label{fig:Delaware_County,_PA_Burn_Building}
+\end{figure}
+
+The two room configuration within the burn building had overall dimensions of 6.5 m (21.3 ft) by 9.2 m (30.2 ft).
+The burn room where the fuel load was located measured 3.8 m (12.5 ft) by 5.7 m (18.7 ft) with a ceiling height of 3.35 m (11.0 ft).
+The adjacent room where the water was applied for gas cooling measured 4.1 m (13.4 ft) by 5.7 m (18.7 ft), also with a ceiling height of 3.35 m (11.0 ft).
+The open door from the adjacent room to the exterior measured 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.
 

### 2015-02-03 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: minor update to report

@@
 \begin{enumerate}
-\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story residential structure using physics-based calculations.
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story plus basement residential structure using physics-based calculations.
 \item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
+\item To provide a basis for discussing tactical operations.
 \end{enumerate}

### 2015-02-04 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report and figures based on initial reviewer comments.

@@
 \chapter*{\centering Abstract}
-Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two firefighters.
+Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two Price George's County firefighters.
 The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
-The fire started in the basement and resulted in ventilation limited (fuel rich) fire conditions in the basement area.
-After the front door was opened the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
+The fire started in the basement which generated ventilation limited (fuel rich) fire conditions in the basement area.
+After the front door was opened, the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
 The temperature of the gases in the interior stairwell was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F).
@@
 \begin{enumerate}
-\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story plus basement residential structure using physics-based calculations.
+\item To examine the effect of the flow path (including temperature, pressure, and fire conditions) in this single-story residential structure with a basement using physics-based calculations.
 \item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
@@
 
-Truck 809 Forcible Entry was too large in physical stature to fit through the small window opening that he found on [the front of the structure].
 Truck 809 Forcible Entry was unable to self-evacuate, and remained trapped inside.
@@
 
-After exiting the structure, Truck 809 Officer screamed (to those on the exterior) that a firefighter was trapped inside.
+After exiting the structure, Truck 809 Officer [alerted other firefighters] that a firefighter was trapped inside.
 Truck 809 Officer then proceeded to the front door \ldots in an attempt to search for and rescue Truck 809 Forcible Entry, who was trapped inside.
@@
 
-While the interior operations were occurring, Truck 809 Driver and Truck 809 Hook/Ladders were on the exterior throwing ladders to the structure.
-Truck 809 Hook/Ladders threw two ladders [front and left side], while Truck 809 Driver threw one ladder ([front side]).
 \end{quote}  
 From a combination of on-scene video and the narrative accounts from the Prince George's County Fire/EMS Department report~\cite{PGCounty2013}, Table~\ref{tab:fire_info} shows an overview of the timeline of events.
-Table~\ref{tab:fire_info} represents the best estimate of the events and therefore all times should be considered as approximate.
+Table~\ref{tab:fire_info} represents the best estimate of the events.
 
@@
 This resulted in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
-The interior walls were composed of gypsum board over insulated wood framing~\cite{PGCounty2013}.
+The interior walls were composed of gypsum board over wood framing~\cite{PGCounty2013}.
 There was a single flight of stairs in the center of the structure which connected the first floor to the basement.
@@
 The fire, which is described in Section~\ref{fire}, started in the basement and spread to the stairs which connect to the first floor.
+The door at the top of the stairs was open at the time of the fire.
 Discussion of the fire's impact on the interior conditions is provided in Section~\ref{results}.
@@
 Based on these sources of information, the FDS model includes two source fire locations in the basement: one fire in the kitchen area and one in the adjacent bathroom (Fig.~\ref{fig:basement_fire}).
-At the time of the fire, the structure was vacant so the the dominant fuel was wood: wood paneling on walls, exposed ceiling joists, sub-floor, cabinets, and stairs.
+At the time of the fire, the structure was unfurnished so the the dominant fuel was wood: wood paneling on walls, exposed ceiling joists, sub-floor, cabinets, and stairs.
 
@@
 The remainder of the wood combustable load in the basement was lumped into the localized kitchen fire.
-The ceiling and wall areas included in the basement kitchen and main living area totaled approximately 86~m$^2$ (926~ft$^2$).
+The ceiling and wall areas included in the basement kitchen, stairway, and main living area totaled approximately 86~m$^2$ (926~ft$^2$).
 This resulted in a 4.3~MW fire.
@@
 
-A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicated that on average there was the equivalent of an approximate 0.675 MW fire(s) occurring through open external vents (basement windows).
+A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicated that on average there was the equivalent of an approximate 0.7 MW fire(s) occurring through open external vents (basement windows).
 This aligns with observed post-fire damage and post-incident report~\cite{PGCounty2013}.
@@
 \includegraphics[width=5in]{../Figures/PG_First_9MW_HRR}
-\caption[Prescribed and first floor calculated HRR vs. time from the simulation.]
-{Comparison of total prescribed and first floor calculated HRRs from the simulation. The vertical lines indicate the times at which ventilation occurred.}
+\caption[First floor calculated HRR vs. time from the simulation.]
+{First floor calculated HRR from the simulation. The vertical lines indicate the times at which ventilation occurred.}
 \label{fig:PG_First_9MW_HRR}
@@
 From Section~\ref{temp}, the conditions on the first floor were initially tenable.
-After the front door was opened, however, the simulation results indicated that a high hazard area existed in the first floor that exceeded the conditions of a Class~III exposure (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{Donnelly2006}.
+After the front door was opened, however, the simulation results indicated that a high hazard area existed in the first floor that exceeded the conditions that would put a firefighter at risk for burn injuries (temperatures greater than 260~$^{\circ}$C or 500~$^{\circ}$F)~\cite{nfpa2013standard}.
 
@@
 \label{assessing_hazard}
-A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
+A person is susceptible to second-degree burn injuries if skin temperatures exceed 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
 Although firefighters wear protective gear, gear only offers a finite amount of protection.
 The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
-Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
-Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class~III exposure~\cite{Donnelly2006}.
-Firefighters are at increased risk levels when encountering Class~III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
+Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard}.
+Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
 
@@
 One second after the door was opened, hazard in the structure increased within the structure, the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
-At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure of 260~$^{\circ}$C (500~$^{\circ}$F).
+At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), where a fully protected firefighter would be susceptible to burn injuries.
 These high-hazard conditions within the flowpath remained until the modeled HRR was reduced to simulate the action of applying water the fire.
@@
 In this fire incident, the initial failure of the basement windows with strong incident winds on the rear side of the structure coincided with a rapid change in the thermal conditions in the interior stairwell and first floor after the front door to the structure was opened.
-The open front door resulted in the establishment of a flow path within the interior stairwell with highly hazardous conditions.
-These conditions would be equivalent to or greater than a Class~III exposure~\cite{Donnelly2006}.
+The open front door resulted in the establishment of a flow path within the interior stairwell from the high pressure side of the structure to the low presure side with highly hazardous conditions.
 
@@
 
-Fire suppression efforts should be coordinated with interior operations and ventilation procedures to reduce thermal hazards related to flow paths within a structure.
+First suppression efforts should take place at the same level as the first with the wind at the back of firefighters.
 Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrated that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
@@
 The opening of the front door resulted in a rapid change in the conditions within the flow path.
-In the interior stairwell, the flow velocities were greater than 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which exceeds the Class III exposure temperature of 260~$^{\circ}$C (500~$^{\circ}$F).
+In the interior stairwell, the flow velocities were greater than 9~m/s (20~mph) and the temperature of the gases was estimated to be in excess of 400~$^{\circ}$C (750~$^{\circ}$F), which puts fully protected firefighters at risk for burn injuries.
 
@@
 
-The authors would like to thank XXXXX of the Prince George's County Fire/EMS Department for their assistance with this study and their dedication to improving firefighter safety.
+The authors would like to thank Chief Marc Bashoor of the Prince George's County Fire/EMS Department for their assistance with this study and their dedication to improving firefighter safety.
+The authors would like to thank members of the Safety Investigation Team for compiling the report: Deputy Chief Scott Hoglander, Battalion Chief Sayshan Conver-White, Chief Richard Bowers, Deputy Chief William Goldfeder, Assistant Chief Michael Nelson, Volunteer Safety Division Chief Stefan Ganset, Paramedic Captain Roland Berg, Lieutenant Philip Bird, Lieutenant Daniel Schrader, Investigator Aaron Tyler, Fire Protection Engineer Lee McCarthy, President Charles Walker, and Administrative Aide Xiomara Lozano-Chevez.
 The authors would also like to thank John Culbertson, Director of the Montana Fire Services Training School, for his assistance in researching and compiling the flow path related LODD/LODI incidents shown in Table~\ref{tab:LODD}.

### 2015-02-05 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2102: Added Figure for Burn Building
DelCo 2012: Spray Density CSV files, updated matlab scripts, updated report (tables)

@@
 	\label{fig:Delaware_County,_PA_Burn_Building}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingDimensions}
+	\caption{Delaware County, PA Burn Building Layout}
+	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
 \end{figure}
@@
 
-\section{Gas Cooling}
-\label{sec:Gas_Cooling}
+\begin{sidewaystable}[!ht]
+	\centering
+	\caption{Temperature Comparison}
+	\begin{tabular}{ll}
+		\hline\noalign{\smallskip}
+		Temperature				 & Response		\\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
+		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
+		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
+		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
+		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
+		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
+		100 deg C (212 deg F)    & Water boils and produces steam    \\
+		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
+		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
+		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
+		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
+		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+	\label{tab:Temperature_Comparison}
+\end{sidewaystable}
+
+\begin{sidewaystable}[!ht]
+	\centering
+	\caption{Heat Flux Comparison}
+	\begin{tabular}{ll}
+		\hline\noalign{\smallskip}
+		Heat Flux	  				   & Response		\\
+		\noalign{\smallskip}\hline\noalign{\smallskip}
+		1 kW/m\textsuperscript{2}      & Sunny day      \\
+		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
+		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
+		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
+		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
+		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+	\label{tab:Heat_Flux_Comparison}
+\end{sidewaystable}
 
@@
 
-Each 
 12 Experiments:
@@
 Room nozzle = seat of fire
+
+\section{Gas Cooling}
+\label{sec:Gas_Cooling}
 

### 2015-02-05 Projects/DelCo_2012/Scripts/FSW_Test6.m

@@ -7,7 +7,7 @@ close all
 % Set Directory
 %------------------
 
-datadir = '../Raw_Data/';
+datadir = '../Experimental_Data/';
 
 %------------------
 % Pull Data From File 

### 2015-02-06 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report from WERB comments

@@
 The Prince George's County report~\cite{PGCounty2013} includes narratives of actions of the response personnel.
+Note that term following the apparatus number (e.g.
+Truck 809 Can) refers to the seating assignment and operational duties of the firefighters on board.
 The following narrative of the incident, focused on the events which led to serious burn injuries to two emergency-personnel, was taken from the Prince George's County report~\cite{PGCounty2013}:
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/PGCo_Front} \\ 
+\includegraphics[width=\textwidth]{../Figures/PGCo_Front} \\ 
 \vspace{0.1in}
-\includegraphics[width=5in]{../Figures/PGCo_Rear}
+\includegraphics[width=\textwidth]{../Figures/PGCo_Rear}
 \caption{Photographs showing the front (top) and rear (bottom) exterior of the structure after the incident.}
@@
 \begin{figure}[!ht]
-\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_99s}
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.8\textwidth]{../Figures/pressure_slice_99s}
 \input{../Scripts/colorbar_metric_pres} \\
-\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.55\textwidth]{../Figures/pressure_slice_101s}
+\vskip10pt
+\includegraphics[trim = 1in 1in 1in 1in, clip=true, width=.8\textwidth]{../Figures/pressure_slice_101s}
 \input{../Scripts/colorbar_metric_pres}
@@
 
-The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were injured after making entry to the first floor and had to either bail out through a window or be rescued through the front door.
+The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were seriosuly injured after making entry to the first floor.
+The interior conditions forced one firefighter to bail out through a window and the other firefighter to be rescued through the front door.
 From Section~\ref{temp}, the conditions on the first floor were initially tenable.
@@
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_99s} \\
+\vskip4pt
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_99s} 
@@
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_101s} \\
+\vskip4pt
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_101s} 
@@
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/side_view_142s} \\
+\vskip4pt
 \includegraphics[trim = 0in 0in 0in 0in, clip=true, width=\textwidth]{../Figures/stair_view_142s} 

### 2015-02-09 Projects/Spartanburg_2014/Report/Spartanburg.tex
Spartanburg 2014: minor edits to report

@@
 
+Interior rooms were designed as either burn rooms or non-burn rooms.
+The non-burn rooms had a limited-combustible load and walls were either paper-covered gypsum board or finished plaster board.
+The burn rooms had walls lined with combustible oriented strand board (OSB) sheets for wall linings.
+
 \section{214 Folsom Street}
 
-The first test house was a single story, single family residential structure of type 5 construction addressed as 214 Folsom Street.
-The non-burn rooms had a limited-combustible finish comprised of either paper-covered gypsum board or a finished plaster board.
-The burn rooms had a combustible finish comprised of OSB sheets for wall linings.
+214 Folsom Street was a single story, single family residential structure of type 5 construction.
 Two tests were conducted in this structure: 1) Living room fire with exterior attack and 2) Bedroom fire with exterior attack.
@@
 
-Ignition begins on a modern-style sofa in the living room on the A/D corner of the structure with all doors and windows closed.
-The fire grew uninhibited and reach the vent-limited stage.
-Fire fighting crew ventilated the living room window on the D side of the structure.The fire was allowed to stabilize with the new ventilation opening.
-The fire fighting crew then applied water, via a straight stream flow, from the exterior into the D side window for suppression.
-After the exterior suppression, the front living room window on the A side of the structure was ventilated.
+A modern-style sofa in the A/D corner of the living room was the first item ignited.
+With all exterior doors and windows closed, the fire grew uninhibited and reached a ventilation-limited stage.
+Fire fighting crews first ventilated the living room window on the D side of the structure.
+The fire was allowed to stabilize following ventilation.
+For suppression, fire fighting crews applied a straight stream from the exterior into the D side window.
+After the exterior water application, the front living room window on the A side of the structure was ventilated.
 Water was then applied from the exterior on the A side into the living room window for further suppression.
-The fire fighting crew then opened the front door and made entry to complete suppression.
+The front door was then opened and fire fighting crews entered to complete suppression.
 
@@
 
-The fire was ignited on a modern-style soda in the bedroom located near the B/C corner of the structure.
-The living room used during the previous burn was isolated from the remaining portion of the building for this test to not alter the results.
-The fire was allowed to grow uninhibited and reach the vent-limited stage.
-The fire self-vented the upper portion of the bedroom window on the B side of the structure.
-The fire fighting crew ventilated a window on the D side of the building in the adjacent room located near the C/D corner.
+Note, to not alter the results, the living room used during test 1 was isolated from the remaining portion of the building for this test.
+A modern-style sofa in the bedroom located near the B/C corner of the structure was the first item ignited.
+The fire was allowed to grow uninhibited and become ventilation-limited until the fire self-vented the upper portion of the bedroom window on the B side of the structure.
+Fire fighting crews ventilated a window on the D side of the building in the adjacent room located near the C/D corner.
 The fire then self-vented the remaining portion of the window in the room of origin.
-The small window into the kitchen on the B side of the structure was then ventilated.
+A small window into the kitchen on the B side of the structure was then ventilated by fire fighting crews.
 Shortly thereafter, the fire fighting crew made an exterior attack via a narrow fog into the bedroom from the self-vented B side window.

### 2015-02-09 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report from WERB comments

@@
 \hypersetup{
-  pdftitle={Simulation of a Wind Driven Basement Fire - Riverdale Heights, MD},
+  pdftitle={Simulation of a Wind Driven Residential Basement Fire - Riverdale Heights, MD},
   pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
@@
 \headerB{
-Simulation of a Wind Driven \\
-Basement Fire - \\
+Simulation of a Residential \\
+Wind Driven Basement Fire - \\
 Riverdale Heights, MD \\
@@
 
-January 2015}}
+February 2015}}
 
@@
 
-On February 24, 2012, a fire in residential structure injured seven Prince George's County firefighters.
+On February 24, 2012, a fire in an uninhabitated residential structure injured seven Prince George's County firefighters.
 NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department.
@@
 \item To provide visualizations of the fire behavior that are representative of the conditions that members of the Prince George's Fire Department likely experienced during the course of their interior operations.
-\item To provide a basis for discussing tactical operations.
+\item To provide a basis for analyzing tactical operations in terms of fire dynamics.
 \end{enumerate}
@@
 The account of events for this incident was documented by the Safety Investigation Team of the Prince George's County Fire/EMS Department~\cite{PGCounty2013}.
-At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}.
+At 21:11 hours on February 24, 2012 Prince George's Fire/EMS Department responded to a residential structure fire in Riverdale Heights, Maryland with a fire in the basement~\cite{PGCounty2013}.
 For the purpose of this analysis, the details regarding the timeline are considered to be approximate values.
@@
 21:14:00  & Front door opened. \\[.25cm]
-21:14:42  & Truck 809 enters structure. \\[.25cm]
+21:14:42  & Truck 809 personnel enter structure. \\[.25cm]
 21:15:47  & Basement door opened and water applied to fire. Front door blown closed. \\[.25cm]
-21:15:51  & Lower pane of front egress window broke. \\[.25cm]
-21:16:01  & Top pane of front egress window broke. \\[.25cm]
-21:16:16  & Truck 809 officer bailout through window. \\[.25cm]
+21:15:51  & Lower pane of front egress window broken. \\[.25cm]
+21:16:01  & Top pane of front egress window broken. \\[.25cm]
+21:16:16  & Truck 809 officer bailout through front window. \\[.25cm]
 21:16:44  & Front door opened. \\[.25cm]
@@
 \footnote{Platform-framed construction means that floor joists are completely covered with a sub-floor.
-This forms a platform for which walls are built from.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}.
+This forms a platform from which walls are built.} The structure had a first floor footprint of 9.14~m (30~ft) by 7.77~m (25.5~ft) with the basement being slightly smaller, 9.14~m (30~ft) by 7.16~m (23.5~ft), as show in Fig.~\ref{fig:simp_geom}.
 This resulted in a first floor area of 71~m$^2$ (764~ft$^2$) and a basement floor area of 65~m$^2$ (700~ft$^2$).
@@
 Based on the above input lines, FDS uses the default, mixing-controlled fast chemistry combustion model.
-This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing and extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
+This mechanism states that the rate of fuel consumption is proportional to both the local limiting reactant concentration and the local rate of mixing.
+Extinction is based on the critical flame temperature approach~\cite{FDS_Math_Guide}.
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
@@
 
-Initial simulations were conducted using the two fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images.
+Initial simulations were conducted using a HRR for the two fires totaling 5.3~MW, however, the fire behavior did not align with observations made during the fire incident or post-incident images.
 Specifically there was insufficient fuel to drive the basement to an underventilated condition.
@@
 It is not clear how to quantify the impact of wind on burning rate within a structure from first principles, so several iterations of the model with increased fire sizes were run.
-The final estimated fire size was a 1.8~MW fire in the bathroom and a 6.75~MW fire in the kitchen.
-This resulted in a total peak specified fire size of 8.55~MW.
+The final estimated fire size was a 1.8~MW fire in the bathroom and a 6.8~MW fire in the kitchen.
+This resulted in a total peak specified fire size of 8.6~MW.
 
 Since the time at which the fire started is not known relative to the notification of a fire or how fast the fire spread, several simplifications were made.
-The fires started at the beginning of the simulation and increased to a value of 8.55~MW in 10~s.
+The fires started at the beginning of the simulation and increased to a value of 8.6~MW in 10~s.
 The 10-s ramp up time was used to prevent abrupt changes in the velocity at the fire boundary condition in FDS.
@@
 The ventilation times and ventilation areas represent the best understanding of the incident.
-The times of ventilation changes for doors and windows are provided in Table~\ref{tab:vents}.
-
-During the time at which the firefighters exited the structure or were rescued from the structure, the state of some windows and doors in the structure was known.
+The estimated times of ventilation changes for doors and windows are provided in Table~\ref{tab:vents}.
+
+During the time when the firefighters exited the structure or were rescued from the structure, the state of some windows and doors in the structure was known.
 The state of the vents (opened versus closed) resulted in the establishment of a flow path in the interior stairwell leading from the basement to the first floor.
@@
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open rear basement windows at the start of the simulation are significantly larger than the total effective area of leakage of a structure of this type.
+The open rear basement windows at the start of the simulation were significantly larger than the typical total effective area of leakage of a structure of this type.
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
 
-In addition to the state of openings within the structure, outlined in Table~\ref{tab:vents}, an 8.9~m/s (20~mph) wind velocity boundary condition was included.
+In addition to the state of openings within the structure, outlined in Table~\ref{tab:vents}, an 8.9~m/s (20~mph) wind velocity boundary condition was assumed.
 The flow direction of the wind was from the rear toward the front of the structure, perpendicular to the rear of the structure.
@@
 \caption[Overhead front-left side of the structure within the computational domain.]{Overhead front-left view of the structure within the computational domain (with 17 meshes).
-The entire computational domain is 24~m (79~ft) by 16~m (53~ft) by 8~m (26~ft).}
+The entire computational domain was 24~m (79~ft) by 16~m (53~ft) by 8~m (26~ft).}
 \label{fig:mult_mesh}
@@
 \centering
-\captionof{table}{Relevant fire model input parameters}\label{tab:mod_param}
+\captionof{table}{Relevant fire model input parameters.}\label{tab:mod_param}
 \begin{tabular}{lll}
@@
                                                            &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
+Wind 													   &  8.9~m/s (20~mph)							   & Section~\ref{Vents}                   \\
 \bottomrule[1.25pt]
@@
 \begin{table}[!ht]
-\caption[Fire incident and simulation event timeline]
-{Fire incident and simulation event timeline}
+\caption[Fire incident and simulation event timeline.]
+{Fire incident and simulation event timeline.}
 \begin{tabular}{ccl}
@@
                &              &                                                                      \\
-21:15:51       &  211         &  Lower pane of front egress window broke.                            \\
-               &              &                                                                      \\
-21:16:01       &  221         &  Top pane of front egress window broke.                              \\
-               &              &                                                                      \\
-21:16:16       &              &  Truck 809 officer bailout through window.                           \\
+21:15:51       &  211         &  Lower pane of front egress window broken.                           \\
+               &              &                                                                      \\
+21:16:01       &  221         &  Top pane of front egress window broken.                             \\
+               &              &                                                                      \\
+21:16:16       &              &  Truck 809 officer bailout through front window.                     \\
                &              &                                                                      \\
@@
 \label{HRR}
-In FDS, a HRR is specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
+In FDS, a HRR must be specified, which results in a specified amount of fuel vapor (or pyrolyzate) being released from a fuel surface.
 FDS then determines the amount of combustion that occurs throughout the simulation based on the amount of available fuel and oxygen at a given location.
@@
 The vertical lines represent the times at which ventilation occurred: front door opening and closing as well as the breaking of a front window for emergency escape.
-See Table~\ref{tab:vents} for a detailed list of the ventilation that occurring during the incident.
+See Table~\ref{tab:vents} for a detailed list of the ventilation that occurred during the incident.
 The maximum size of the fire specified in this study was selected such that the conditions aligned with observations and fuel loads from the actual fire incident.
@@
 \caption[Interior prescribed and calculated interior HRRs vs. time from the simulation.]
-{Comparison of prescribed and calculated interior HRRs from the FDS simulation. The vertical lines indicate the times at which ventilation occurred.}
+{Comparison of prescribed and calculated interior HRRs from the FDS simulation. The vertical lines indicate the times when ventilation occurred.}
 \label{fig:PG_Total_HRR}
@@
 In Fig.~\ref{fig:PG_Total_HRR}, the prescribed HRR that was input into the simulation is different than the HRR calculated by FDS based on the ventilation conditions.
-From 0~s to approximately 9~s, the calculated HRR was in agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
+From 0~s to approximately 9~s, the calculated HRR was in approximate agreement with the prescribed HRR because there was an adequate amount of oxygen for all of the fuel to combust.
 The differences in prescribed versus predicted HRR is a result of either fuel accumulation within the structure not combusting because of a lack of oxygen or combustion occurring exterior to the structure where fuel and oxygen can mix and react.
@@
 This aligns with observed post-fire damage and post-incident report~\cite{PGCounty2013}.
-Fig.~\ref{fig:ext_fire_dam} shows a post-fire image of the back left corner of the structure as well as a Smokeview rendering of the fire from the FDS simulation prior to the front door being opening by firefighters.
+Fig.~\ref{fig:ext_fire_dam} shows a post-fire image of the back left corner of the structure as well as a Smokeview rendering of the fire from the FDS simulation prior to the front door being opened by firefighters.
 
@@
 The change in ventilation to the structure impacted the HRR.
-After the door was opened, combustion no longer tool place outside of the structure, however as shown in Fig.~\ref{fig:PG_Basement_9MW_HRR}, the basement HRR was lower than the total HRR within the domain.
+After the door was opened combustion no longer tool place outside of the structure, as shown in Fig.~\ref{fig:PG_Basement_9MW_HRR}, however the basement HRR was lower than the total HRR within the domain.
 
@@
 \caption[Prescribed, calculated domain, and calculated basement HRRs vs. time from the simulation.]
-{Comparison of prescribed, total calculated domain HRR and basement calculated HRRs from the simulation. The vertical lines indicate the times at which ventilation occurred.}
+{Comparison of prescribed, total calculated domain HRR and basement calculated HRRs from the simulation. The vertical lines indicate the times when ventilation changed.}
 \label{fig:PG_Basement_9MW_HRR}
@@
 \caption[First floor calculated HRR vs. time from the simulation.]
-{First floor calculated HRR from the simulation. The vertical lines indicate the times at which ventilation occurred.}
+{First floor calculated HRR from the simulation. The vertical lines indicate the times when ventilation changed.}
 \label{fig:PG_First_9MW_HRR}
@@
 One second after the door was opened (bottom snapshot in Fig.~\ref{fig:pressure_slices}), the pressure on the first floor drops to between 75~Pa (1.1 $\times$ 10$^{-2}$~psi) and 85~Pa (1.2 $\times$ 10$^{-2}$~psi).
-Without the presence of wind, the pressure in the first floor prior to the door opening is is approximately 18~Pa (2.6 $\times$ 10$^{-3}$~psi) and after the door is opened the pressure drops to between 5~Pa (7.3 $\times$ 10$^{-4}$~psi) and 10~Pa (1.4 $\times$ 10$^{-3}$~psi).
+Without the presence of wind, the pressure in the first floor prior to the door opening was approximately 18~Pa (2.6 $\times$ 10$^{-3}$~psi) and after the door was opened the pressure drops to between 5~Pa (7.3 $\times$ 10$^{-4}$~psi) and 10~Pa (1.4 $\times$ 10$^{-3}$~psi).
 
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption[Calculated pressure on first floor 1~s before and after front door opens]
-{Calculated pressure contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\caption[Calculated pressure on first floor 1~s before and after front door opens.]
+{Calculated pressure contours on the first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through the front door at 0.91~m (3~ft) above the floor.}
 \label{fig:pressure_slices}
@@
 Once the front door opened, the gases in the basement at an elevated temperature and pressure flowed upward into the interior stairwell and exited the structure via the front door.
-The velocity contours shown in Fig.~\ref{fig:velocity_slices} indicate the magnitude of flow velocities within the structure before and after the front door is opened.
+The velocity contours shown in Fig.~\ref{fig:velocity_slices} indicate the magnitude of flow velocities within the structure before and after the front door was opened.
 
 In Fig.~\ref{fig:velocity_slices}, the velocity profile within the high-hazard area (first floor) is shown via two snapshots in time to illustrate the change in the interior conditions 0.91~m (3~ft) above the floor.
-The first snapshot is shown at a simulation time of 99~s, which is 1~s before the front door is opened, and the second snapshot is shown at a simulation time of 101~s, which is 1~s after the front door is opened.
-The velocity contours shown indicate that prior to the front door being opened, there is minimal flow on the first floor.
-However, after the front door is opened a flow path is established allowing the combustion products from the basement fire to flow to the first floor through the interior stairwell.
-The simulation calculated the flow to exit the structure at approximately 11~m/s (25~mph).
+The first snapshot is shown at a simulation time of 99~s, which is 1~s before the front door was opened, and the second snapshot is shown at a simulation time of 101~s, which is 1~s after the front door was opened.
+The velocity contours shown indicate that prior to the front door being opened, there was minimal flow on the first floor.
+However, after the front door was opened, a flow path was established forcing the combustion products from the basement fire to flow to the first floor through the interior stairwell.
+The simulation calculated the flow exiting the structure to be approximately 11~m/s (25~mph).
 
@@
 \input{../Scripts/colorbar_std_velo}
-\caption[Calculated velocity on first floor 1~s before and after front door opens]
-{Calculated velocity contours on first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\caption[Calculated velocity on the first floor 1~s before and after front door opens]
+{Calculated velocity contours on the first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.
+Arrows indicate direction.}
 \label{fig:velocity_slices}
@@
 
-Analysis of the temperatures from the simulation focuses on the high-hazard area of the structure: the first floor area between the front door and the top of the interior stairwell.
+Analysis of the temperatures from the simulation focused on the high-hazard area of the structure: the first floor area between the front door and the top of the interior stairwell.
 The temperature contours shown in Fig.~\ref{fig:temperature_slice_99s} indicate the gas temperatures within the structure 1~s before the front door was opened 0.91~m (3~ft) above the floor.
 The overlaid arrows represent the gas flow: the length of the lines represents the magnitude of the speed and the direction of the arrow represents the flow direction.
-Prior to the door opening, the open living area and kitchen on the first floor were approximately 60~$^{\circ}$C (140~$^{\circ}$F) while the peak temperatures were concentrated near the interior stairwell, 105~$^{\circ}$C (220~$^{\circ}$F).
-Note that there is very minimal flow throughout the first floor.
+Prior to the door opening, the open living area and kitchen on the first floor were approximately 60~$^{\circ}$C (140~$^{\circ}$F), while the peak temperatures were concentrated near the interior stairwell, 105~$^{\circ}$C (220~$^{\circ}$F).
+Note that there was very minimal flow throughout the first floor.
 Figures~\ref{fig:temperature_slice_101s} and \ref{fig:temperature_slice_105s} show gas temperature contours at 0.91~m (3~ft) above the floor, 1~s and 5~s after the front door was opened.
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on first floor 1~s before front door opened]
-{Calculated temperature contours on first floor of the structure 1~s prior to firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\caption[Calculated temperature on the first floor 1~s before front door opened.]
+{Calculated temperature contours on the first floor of the structure 1~s prior to firefighter entry through front door 0.91~m (3~ft) above the floor.}
 \label{fig:temperature_slice_99s}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on first floor 1~s after front door opens]
-{Calculated temperature contours on first floor of the structure 1~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
+\caption[Calculated temperature on the first floor 1~s after front door opens.]
+{Calculated temperature contours on the first floor of the structure 1~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
 \label{fig:temperature_slice_101s}
@@
 Section~\ref{assessing_hazard} examines the model results as they relate to the hazardous conditions and exposure temperatures on the first floor.
-Section~\ref{tactical_considerations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent experimental research.
+Section~\ref{tactical_considerations} discusses tactical considerations and outcomes of the fire incident as they relate to the fire dynamics and flow path conditions that have been observed in recent anaylses, modeling, and full and bench-scale experimental research.
 
@@
 
-The report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were seriosuly injured after making entry to the first floor.
-The interior conditions forced one firefighter to bail out through a window and the other firefighter to be rescued through the front door.
+The incident report from Prince George's County Fire/EMS~\cite{PGCounty2013} indicated that two firefighters from Truck 809 were seriosuly injured after making entry to the first floor.
+The interior conditions forced one firefighter to bail out through a first floor window on the front side of the structure and the other firefighter to be rescued through the front door.
 From Section~\ref{temp}, the conditions on the first floor were initially tenable.
@@
 After the front door was opened, the combustion gases at elevated temperature and pressure in the basement flowed towards lower pressure regions outside of the structure on the leeward side (front of structure) via the interior stairwell.
-The two injured firefighters were located in the flow path on first floor between the top of the interior stairwell and the front door.
-
-To examine the impact of opening the front door on the establishment of a flow path, flow conditions are examined along the centerline of the interior stairwell doorway and through the centerline of front door.
+The two injured firefighters were located in the flow path on the first floor between the top of the interior stairwell and the front door.
+
+To examine the impact of opening the front door on the establishment of a flow path, flow conditions were examined along the centerline of the interior stairwell doorway and through the centerline of front door.
 Figure~\ref{fig:flow_path_99s} shows the flow vectors at the first floor stairwell doorway 1~s before the front door was opened.
-Note that length and direction of the arrow indicates the magnitude and direction of the flow respectively.
-The color of the arrow corresponds to the values from the included temperature scales.
+Note that the length and direction of the arrows indicate the magnitude and direction of the flow, respectively.
+The color of the arrows correspond to the values from the included temperature scales.
 Therefore, a short blue arrow represents slow moving, cool gas while a long red arrow represents fast moving, high temperature gas.
-Prior to the door opening, there was minimal flow through the first floor stairwell door and the temperature peak is approximately 125~$^{\circ}$C (257~~$^{\circ}$F) as shown in Figure~\ref{fig:flow_path_99s}.
-One second after the door opened, Figure~\ref{fig:flow_path_101s}, there is noticeable flow through both the stairwell doorway and through the front door.
-Simulation temperatures at the stairwell increased to approximately 200~$^{\circ}$C (392~~$^{\circ}$F) and temperatures through the doorway are approximately 100~$^{\circ}$C (212~~$^{\circ}$F).
+Prior to the door opening, there was minimal flow through the first floor stairwell door and the temperature peak was approximately 125~$^{\circ}$C (257~~$^{\circ}$F) as shown in Figure~\ref{fig:flow_path_99s}.
+One second after the door opened, Figure~\ref{fig:flow_path_101s}, there was noticeable flow through both the stairwell doorway and through the front door.
+Simulated temperatures at the stairwell increased to approximately 200~$^{\circ}$C (392~~$^{\circ}$F) and temperatures through the doorway were approximately 100~$^{\circ}$C (212~~$^{\circ}$F).
 These values are also shown in planar contours 1~m above the floor in Figs.~\ref{fig:velocity_slices} and \ref{fig:temperature_slice_101s} for velocity and temperature, respectively.
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell 1~s before front door was opened]
-{Flow path vectors at front door and top of stairwell 1~s before front door was opened.}
+\caption[Flow path vectors at the front door and top of the stairwell 1~s before the front door was opened.]
+{Flow path vectors at front door and top of stairwell 1~s before the front door was opened.}
 \label{fig:flow_path_99s}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell 1~s after front door was opened]
-{Flow path vectors at front door and top of stairwell 1~s after front door was opened.}
+\caption[Flow path vectors at the front door and the top of stairwell 1~s after the front door was opened.]
+{Flow path vectors at front door and top of stairwell 1~s after the front door was opened.}
 \label{fig:flow_path_101s} 
@@
 
-At the estimated time of firefighter entry to the first floor (142~s into the simulation; 21:14:42 according to Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
-Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), faster than the imposed wind speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
+At the estimated time of firefighter entry to the first floor (142~s into the simulation at 21:14:42; see Table~\ref{tab:combined_timeline}), the simulated flow magnitudes through the first floor (stairwell and front doors) remained similar to the conditions just after opening the front door.
+Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), which was faster than the imposed wind speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
 The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell at estimated time of first floor entry]
-{Flow path vectors at front door and top of stairwell 42~s after front door was opened, the estimated time of first floor entry.}
+\caption[Flow path vectors at the front door and the top of the stairwell at the estimated time of first floor entry.]
+{Flow path vectors at the front door and the top of the stairwell 42~s after the front door was opened, at the estimated time of first floor entry.}
 \label{fig:flow_path_142s}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell 1~s before front door was closed]
-{Flow path vectors at front door and top of stairwell 1~s before front door was closed.}
+\caption[Flow path vectors at the front door and the top of stairwell 1~s before the front door was closed.]
+{Flow path vectors at the front door and the top of stairwell 1~s before the front door was closed.}
 \label{fig:flow_path_206s}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Flow path vectors at front door and top of stairwell 1~s after front door was closed]
-{Flow path vectors at front door and top of stairwell 1~s after front door was closed.}
+\caption[Flow path vectors at the front door and the top of stairwell 1~s after the front door was closed.]
+{Flow path vectors at the front door and the top of stairwell 1~s after the front door was closed.}
 \label{fig:flow_path_207s}
@@
 
-Figures~\ref{fig:int_temp_99s} to \ref{fig:int_temp_142s} show two interior views of temperature contours at particular snapshots in time.
-The top image is a planar view through the middle of the front door (from the front to the back of the house) which shows the conditions in the living area on the first floor and the conditions in the basement just past the bottom of the stairs.
+Figures~\ref{fig:int_temp_99s} to \ref{fig:int_temp_142s} show two simulated interior views of temperature contours at particular snapshots in time.
+The top image is a planar view through the middle of the front door (from the front to the back of the house), which shows the conditions in the living area on the first floor and the conditions in the basement just past the bottom of the stairs.
 The bottom image shows temperature contours through the middle of the interior stairwell which connected the basement to the first floor of the structure (looking from the rear of the structure towards the front).
-Prior to the front door being opened, (Fig.~\ref{fig:int_temp_99s} shows that temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to basement of the structure: specifically the rear of the structure and under the stairwell.
-One second after the door was opened, hazard in the structure increased within the structure, the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
-At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), where a fully protected firefighter would be susceptible to burn injuries.
-These high-hazard conditions within the flowpath remained until the modeled HRR was reduced to simulate the action of applying water the fire.
+Prior to the front door being opened, (Fig.~\ref{fig:int_temp_99s} shows that temperatures in excess of 200~$^{\circ}$C (400~$^{\circ}$F) were confined to the basement of the structure: specifically the rear of the structure and under the stairwell.
+One second after the door was opened, hazard in the structure increased with the most drastic change occurring at the top of the stairwell as peak simulated temperatures exceeded 400~$^{\circ}$C (750~$^{\circ}$F).
+At the approximate time firefighters made entry to the first floor, Fig.~\ref{fig:int_temp_142s}, the conditions within the flowpath (interior stairwell through front door) had become more severe with simulated temperatures in excess of 400~$^{\circ}$C (750~$^{\circ}$F), for which a fully protected firefighter would be susceptible to burn injuries.
+These high-hazard conditions within the flowpath remained until the HRR was reduced by the simulated action of applying water on the fire.
 
@@
 \end{subfigure}
-\caption[Interior temperature contours 1~s before front door was opened]
-{Interior temperature contours 1~s before front door was opened.
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
-The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\caption {Interior temperature contours 1~s before the front door was opened.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
 \label{fig:int_temp_99s}
@@
 \end{subfigure}
-\caption[Interior temperature contours 1~s after front door was opened]
-{Interior temperature contours 1~s after front door was opened.
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
-The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\caption{Interior temperature contours 1~s after the front door was opened.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
 \label{fig:int_temp_101s}
@@
 \end{subfigure}
-\caption[Interior temperature contours as firefighters made entry to the structure]
-{Interior temperature contours as firefighters made entry to the structure.
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center front door.
-The bottom snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the interior stairwell doorway.}
+\caption{Interior temperature contours as firefighters made entry to the structure.
+The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
 \label{fig:int_temp_142s}
@@
 Two firefighters were located in the flow path between the basement and the doors on the front side of the structure.
-One firefighter was able to break a window to escape the hazardous conditions and after a call for assistance the second firefighter was removed from the structure and immediate medical treatment was provided.
+One firefighter was able to break a window to escape the hazardous conditions and after a call for assistance, the second firefighter was removed from the structure and immediate medical treatment was provided.
 The two firefighters were transported to the local medical center where they were treated for their injuries.

### 2015-02-09 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated report.

@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingSpray}
+	\caption{Nozzle Location for Gas Cooling Tests}
+	\label{fig:Nozzle_Location_Gas_Cooling_Tests}
+\end{figure}
+
 \subsection{Fire Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
-	\caption{Hallway Nozzle Location}
-	\label{fig:Hallway_Nozzle_Location}
+	\caption{Hallway Nozzle Location for Fire Suppression Tests}
+	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
 \end{figure}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
-	\caption{Room Nozzle Location}
-	\label{fig:Room_Nozzle_Location}
+	\caption{Room Nozzle Location for Fire Suppression Tests}
+	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
 \end{figure}
@@
 	\label{fig:Straigh_Stream_Instrumentation}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Single_Story_Instrumentation}
+	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
+	\label{fig:Fire_Suppression_Instrumentation}
 \end{figure}
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB1}
+	\caption{Burn Building Test 1}
+	\label{fig:Burn_Building_Test_1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB2}
+	\caption{Burn Building Test 2}
+	\label{fig:Burn_Building_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB3}
+	\caption{Burn Building Test 3}
+	\label{fig:Burn_Building_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB4}
+	\caption{Burn Building Test 4}
+	\label{fig:Burn_Building_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB5}
+	\caption{Burn Building Test 5}
+	\label{fig:Burn_Building_Test_5}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB6}
+	\caption{Burn Building Test 6}
+	\label{fig:Burn_Building_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB7}
+	\caption{Burn Building Test 7}
+	\label{fig:Burn_Building_Test_7}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB8}
+	\caption{Burn Building Test 8}
+	\label{fig:Burn_Building_Test_8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB9}
+	\caption{Burn Building Test 9}
+	\label{fig:Burn_Building_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB10}
+	\caption{Burn Building Test 10}
+	\label{fig:Burn_Building_Test_10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB11}
+	\caption{Burn Building Test 11}
+	\label{fig:Burn_Building_Test_11}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB12}
+	\caption{Burn Building Test 12}
+	\label{fig:Burn_Building_Test_12}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB13}
+	\caption{Burn Building Test 13}
+	\label{fig:Burn_Building_Test_13}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB14}
+	\caption{Burn Building Test 14}
+	\label{fig:Burn_Building_Test_14}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB15}
+	\caption{Burn Building Test 15}
+	\label{fig:Burn_Building_Test_15}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB16}
+	\caption{Burn Building Test 16}
+	\label{fig:Burn_Building_Test_16}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB17}
+	\caption{Burn Building Test 17}
+	\label{fig:Burn_Building_Test_17}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB18}
+	\caption{Burn Building Test 18}
+	\label{fig:Burn_Building_Test_18}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB19}
+	\caption{Burn Building Test 19}
+	\label{fig:Burn_Building_Test_19}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB20}
+	\caption{Burn Building Test 20}
+	\label{fig:Burn_Building_Test_20}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/BB21}
+	\caption{Burn Building Test 21}
+	\label{fig:Burn_Building_Test_21}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES1}
+	\caption{Experimental Structures Test 1}
+	\label{fig:Experimental_Structures_Test_1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES2}
+	\caption{Experimental Structures Test 2}
+	\label{fig:Experimental_Structures_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES3}
+	\caption{Experimental Structures Test 3}
+	\label{fig:Experimental_Structures_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES4}
+	\caption{Experimental Structures Test 4}
+	\label{fig:Experimental_Structures_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES5}
+	\caption{Experimental Structures Test 5}
+	\label{fig:Experimental_Structures_Test_5}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES6}
+	\caption{Experimental Structures Test 6}
+	\label{fig:Experimental_Structures_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES7}
+	\caption{Experimental Structures Test 7}
+	\label{fig:Experimental_Structures_Test_7}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES72}
+	\caption{Experimental Structures Test 7.2}
+	\label{fig:Experimental_Structures_Test_7.2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES8}
+	\caption{Experimental Structures Test 8}
+	\label{fig:Experimental_Structures_Test_8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES9}
+	\caption{Experimental Structures Test 9}
+	\label{fig:Experimental_Structures_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES10}
+	\caption{Experimental Structures Test 10}
+	\label{fig:Experimental_Structures_Test_10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Bars/ES11}
+	\caption{Experimental Structures Test 11}
+	\label{fig:Experimental_Structures_Test_11}
+\end{figure}
+
 \section{Gas Cooling}

### 2015-02-10 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report, plotting script, and figure | Bib: update reference

@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (November 2014) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2015) \\
 CODEN: NTNOEF}
@@
 \centering
-\captionof{table}[Abridged approximate fire event timeline]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}.}\label{tab:fire_info}
+\captionof{table}[Abridged approximate fire event timeline.]{Abridged Prince George's Fire/EMS approximate fire event timeline~\cite{PGCounty2013}.}\label{tab:fire_info}
 \begin{tabular}{cl}
@@
 \caption[Prescribed HRR vs. time for the simulation.]
-{Prescribed HRR vs. time for the simulation. The text labels indicate the prescribed steady peak HRR and the decay phase associated with firefighter water application.}
+{Prescribed HRR vs.
+time for the simulation.
+The text labels indicate the prescribed steady peak HRR and the decay phase associated with firefighter water application.
+Time zero represnts 21:21:20, see Table~\ref{tab:combined_timeline}}.
 \label{fig:hrr}
@@
 In addition to the state of openings within the structure, outlined in Table~\ref{tab:vents}, an 8.9~m/s (20~mph) wind velocity boundary condition was assumed.
-The flow direction of the wind was from the rear toward the front of the structure, perpendicular to the rear of the structure.
+The flow direction of the wind was asasumed from the rear toward the front of the structure, perpendicular to the rear of the structure.
 Based on local weather conditions, mean wind velocities ranged between 4.5~m/s (10~mph) and 8.9~m/s (20~mph) with gusts up to 13.4~m/s (30~mph) with a direction that angled toward the back left of the structure~\cite{PGCounty2013}.
+The following lines define the wind boundary condition in the FDS input file:
+
+\begin{lstlisting}
+&SURF ID='wind', VEL=-8.94, RAMP_V='WIND RAMP',COLOR='INVISIBLE' /
+&VENT MB = 'YMAX', SURF_ID ='wind' /
+&RAMP ID='WIND RAMP', T=0,F=0.25 /
+&RAMP ID='WIND RAMP', T=10,F=0.50 /
+&RAMP ID='WIND RAMP', T=20,F=0.75 /
+&RAMP ID='WIND RAMP', T=30,F=1.00 /
+\end{lstlisting}
+
+Note that there is a 30~s ramp time to reach peak wind speed.
+This was inlcuded to prevent an abrupt change at the FDS domain boundary.
+Since the front door does not open until 100~s into the simulation there was sufficient time to for the airflow to stabilize.
 
@@
 \centering
-\captionof{table}{Timeline of ventilation changes in the simulation}\label{tab:vents}
+\captionof{table}{Timeline of ventilation changes in the simulation.}\label{tab:vents}
 \begin{tabular}{lllll}
@@
                                                            &  $\rho$: 810~kg/m$^3$                         &                                       \\ 
-                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\
+                                                           &  $c_{p}$: 1.0~\si{kJ/(kg.K)}                  &                                       \\ [.25cm]
 Wind 													   &  8.9~m/s (20~mph)							   & Section~\ref{Vents}                   \\
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/PG_Total_9MW_HRR}
+\includegraphics[width=\textwidth]{../Figures/PG_Total_9MW_HRR}
 \caption[Interior prescribed and calculated interior HRRs vs. time from the simulation.]
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/PG_9MW_HRR}
+\includegraphics[width=\textwidth]{../Figures/PG_9MW_HRR}
 \caption[Prescribed and total calculated HRRs vs. time from the simulation.]
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/PG_Basement_9MW_HRR}
+\includegraphics[width=\textwidth]{../Figures/PG_Basement_9MW_HRR}
 \caption[Prescribed, calculated domain, and calculated basement HRRs vs. time from the simulation.]
@@
 \begin{figure}[!ht]
-\includegraphics[width=5in]{../Figures/PG_First_9MW_HRR}
+\includegraphics[width=\textwidth]{../Figures/PG_First_9MW_HRR}
 \caption[First floor calculated HRR vs. time from the simulation.]
@@
 \input{../Scripts/colorbar_metric_pres}
-\caption[Calculated pressure on first floor 1~s before and after front door opens.]
+\caption[Calculated pressure on first floor 1~s before and after the front door opened.]
 {Calculated pressure contours on the first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through the front door at 0.91~m (3~ft) above the floor.}
@@
 \input{../Scripts/colorbar_std_velo}
-\caption[Calculated velocity on the first floor 1~s before and after front door opens]
+\caption[Calculated velocity on the first floor 1~s before and after the front door opened.]
 {Calculated velocity contours on the first floor of the structure 1~s prior to (top) and 1~s after (bottom) firefighter entry through front door 0.91~m (3~ft) above the floor.
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on the first floor 1~s before front door opened.]
+\caption[Calculated temperature on the first floor 1~s before the front door opened.]
 {Calculated temperature contours on the first floor of the structure 1~s prior to firefighter entry through front door 0.91~m (3~ft) above the floor.}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on the first floor 1~s after front door opens.]
+\caption[Calculated temperature on the first floor 1~s after the front door opened.]
 {Calculated temperature contours on the first floor of the structure 1~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
@@
 \input{../Scripts/colorbar_std_temp}
-\caption[Calculated temperature on first floor 5~s after front door opens]
+\caption[Calculated temperature on first floor 5~s after the front door opened.]
 {Calculated temperature contours on first floor of the structure 5~s after firefighter entry through front door 0.91~m (3~ft) above the floor.}
@@
 The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard}.
+Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard} for less than 2.5~min.
 Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
@@
 \end{subfigure}
-\caption {Interior temperature contours 1~s before the front door was opened.
+\caption {Interior temperature contours 1~s before the front door was opened (21:13:59).
 The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
@@
 \end{subfigure}
-\caption{Interior temperature contours 1~s after the front door was opened.
+\caption{Interior temperature contours 1~s after the front door was opened (21:14:01).
 The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
@@
 \end{subfigure}
-\caption{Interior temperature contours as firefighters made entry to the structure.
+\caption{Interior temperature contours as firefighters made entry to the structure (21:14:42).
 The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
@@
 The interior stairwell acted as a chimney for hot gases in the basement to flow towards regions of lower pressure and vent openings located on the front side of the structure.
-Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to firefighting gear via convection.
+Firefighters should avoid placing themselves within a flow path where elevated temperatures and flow velocities can present hazardous conditions and increase the rate of heat transfer to the firefighter via convection.
 A 360$^\circ$ scene size-up by arriving firefighters can help determine the location of the fire and identify potential flow paths within a structure.
@@
 
-First suppression efforts should take place at the same level as the first with the wind at the back of firefighters.
+First suppression efforts should take place at the same level as the fire (i.e.
+fight basement fires from the basement level) with the wind at the back of firefighters.
 Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrated that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
@@
 
-Based on a review of these incidents, it is clear that fires with rapidly developing or changing flow paths are a significant hazard to the fire service.
+Based on a review of these incidents, it is clear that fires with rapidly developing or changing ventilation may lead to flow paths that are a significant hazard to the fire service during a response.
 The development of (or changes to) a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
@@
 \begin{table}[!ht]
-\caption[Flow path related LODD/LODI incidents]
-{Flow path related LODD/LODI incidents}
+\caption[Flow path related LODD/LODI incidents.]
+{Flow path related LODD/LODI incidents.}
 \begin{tabular}{lll}

### 2015-02-10 Studies/2012_PG_County/Scripts/pg_co_hrr.py

@@ -6,7 +6,11 @@ from __future__ import division
 import numpy as np
 import pandas as pd
 from pylab import *
-
+rc('font',**{'size':14})
+params = {'legend.fontsize': 12,
+          'legend.linewidth': 4,
+          'lines.linewidth': 1.75,
+          'lines.markersize': 6}
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
 
@@ -43,38 +47,44 @@ for i in range (0, 999):
 
 
 fig = figure()
-plt.plot(HRR_time,HRR_theo,'k-',mfc='none',label='Prescribed HRR',linewidth=2)
-plot(FDS_HRR_20['Time'],FDS_HRR_20['HRR']/1000.,'r-',mfc='none',label='Total Calculated HRR',linewidth=2)
-plot(FDS_9MW_20['Time'],base_hrr_20mph,'b--',mfc='none',label='Calculated Basement HRR',linewidth=2)
-axvline(x=100,linestyle='-',linewidth=2,color = '#000000')
-axvline(x=207,linestyle='-',linewidth=2,color = '#000000')
-axvline(x=211,linestyle='-',linewidth=2,color = '#000000')
-axvline(x=221,linestyle='-',linewidth=2,color = '#000000')
-axvline(x=267,linestyle='-',linewidth=2,color = '#000000')
+plt.plot(HRR_time,HRR_theo,'k-',mfc='none',label='Prescribed HRR')
+plot(FDS_HRR_20['Time'],FDS_HRR_20['HRR']/1000.,'r-',mfc='none',label='Total Calculated HRR')
+plot(FDS_9MW_20['Time'],base_hrr_20mph,'b--',mfc='none',label='Calculated Basement HRR')
+axvline(x=100,linestyle='-',color = '#000000')
+axvline(x=207,linestyle='-',color = '#000000')
+axvline(x=211,linestyle='-',color = '#000000')
+axvline(x=221,linestyle='-',color = '#000000')
+axvline(x=267,linestyle='-',color = '#000000')
 ax1 = gca()
 xlim([100, 221])
 ax1.xaxis.set_major_locator(MaxNLocator(8))
 ax1_xlims = ax1.axis()[0:2]
 xlabel('Time (s)')
 ylabel('HRR (MW)')
-legend(numpoints=1,loc=4 )
+legend(numpoints=1,loc=3 )
 ax2 = ax1.twiny()
[…]

### 2015-02-10 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report from ERB reader

@@
 NIST examined the fire dynamics of this incident at the request of the Prince George's Country Fire/Emergency Medical Services (EMS) Department.
-Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed in the residence during the fire.
+Computer simulations of the fire incident were conducted using the NIST Fire Dynamics Simulator~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} software to provide insight into the fire development and thermal conditions that likely existed inside the residence during the fire.
 The specific objectives of the simulations detailed in this report are:
@@
 \label{geom}
-The structure involved in this fire incident was a one story, single-family structure with a basement.
+The structure involved in this fire incident was a single-story, single-family structure with a basement.
 The structure was platform-framed wood construction with a gable roof.
@@
 The text labels indicate the prescribed steady peak HRR and the decay phase associated with firefighter water application.
-Time zero represnts 21:21:20, see Table~\ref{tab:combined_timeline}}.
+Time zero represnts 21:21:20, see Table~\ref{tab:combined_timeline}.}
 \label{fig:hrr}
@@
 The exact time of operation for other doors/windows was not known.
-Therefore, the following the two basement windows on the left rear corner of the structure were assumed to be open at the start of the simulation.
+Therefore, the two basement windows on the left rear corner of the structure were assumed to be open at the start of the simulation.
 The states of the front door and front window were specified at certain times based on observations (i.e.
@@
 \includegraphics[width=\textwidth]{../Figures/PG_Total_9MW_HRR}
-\caption[Interior prescribed and calculated interior HRRs vs. time from the simulation.]
+\caption[Comparison of prescribed and calculated interior HRRs from the FDS simulation.]
 {Comparison of prescribed and calculated interior HRRs from the FDS simulation. The vertical lines indicate the times when ventilation occurred.}
@@
 The change in ventilation to the structure impacted the HRR.
-After the door was opened combustion no longer tool place outside of the structure, as shown in Fig.~\ref{fig:PG_Basement_9MW_HRR}, however the basement HRR was lower than the total HRR within the domain.
+After the door was opened combustion no longer took place outside of the structure, as shown in Fig.~\ref{fig:PG_Basement_9MW_HRR}, however the basement HRR was lower than the total HRR within the domain.
 
@@
 The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
-From the approximate timeline (Table~\ref{tab:combined_timeline}), the front door was forced closed due to airflow pushing against the front door 207~s into the simulation.
+From the approximate timeline (Table~\ref{tab:combined_timeline}), the front door was forced closed due to airflow pushing against it, 207~s into the simulation.
 Figures~\ref{fig:flow_path_206s} and \ref{fig:flow_path_207s} show the conditions 1~s prior to and after the front door closed.
@@
 \caption {Interior temperature contours 1~s before the front door was opened (21:13:59).
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The top snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the front door.
 The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
@@
 \caption{Interior temperature contours 1~s after the front door was opened (21:14:01).
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The top snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the front door.
 The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
@@
 \caption{Interior temperature contours as firefighters made entry to the structure (21:14:42).
-The top snapshot shows temperatures on the first floor and basement on a plane that runs through the center of the front door.
+The top snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the front door.
 The bottom snapshot shows temperatures on the first floor and basement on the plane that runs through the center of the interior stairwell doorway.}
@@
 \includegraphics[width=1\textwidth]{../Figures/Basement_Metric}
-\caption[Dimensioned drawing of first floor.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of the basement.]{Dimensioned drawing of the basement. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:basement}
@@
 \includegraphics[width=1\textwidth]{../Figures/First_Floor_Metric}
-\caption[Dimensioned drawing of second floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
+\caption[Dimensioned drawing of the first floor.]{Dimensioned drawing of the first floor. The measurements are accurate to within 15~cm (6~in).}
 \label{fig:first_floor}

### 2015-02-11 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added new plots used in hose report, updated the report, and added new script to plot/analyze BDP data for specific hose streams

@@
 \usepackage{graphicx}
+\usepackage[super]{nth}
 
@@
 \label{sec:Experimental_Structure}
+This series of field experiments was conducted at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+
+Two concrete structures were built on a concrete slab as shown in Figure XX.
+They were designed to simulate a single story and a two story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.
+The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The joints and gaps between the blocks were filled with high temperature insulation.
+
+The interior walls of the first floor or each structure were framed with steel studs and track.
+The studs were set to 0.40 m (16 in) centers.
+The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.
+The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure  XX .
+Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed (nailed?) to the top of the TJIs.
+
+The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs etc…
+
+Opening front door, window, rear doors.
+
+Single story  
+The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
+The ceiling of the burn room was the exposed “floor assembly”.
+The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room.
+The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
 
@@
 \label{sec:Water_Flow_Procedure}
-A total of four sets of experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
 
-Two sets of experiments involving application patterns, Tests 18 and 19, were conducted.
-The two sets varied in that the first floor south side door was open for Test 18 (Fig.~\ref{fig:test_18_plan}) and closed for Test 19 (Fig.~\ref{fig:test_19_plan}).
+\subsubsection{East Structure Experiments}
+\label{sec:East_Structure_Water_Flow_Procedure}
 
-Tests 18 and 19 followed identical procedures that involved flowing water into the West Structure through the first floor, south side double doors using a 1.75 in.
-hose with a combination nozzle.
-The nozzle was used to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream.
+\subsubsection{West Structure Experiments}
+\label{sec:West_Structure_Water_Flow_Procedure}
+
+Four sets of water flow experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
+Water was flowed from the double doors on the first floor for all experiments.
+The experiments varied based on flow path configurations and the type of nozzle used.
+Two flow path configurations were used.
+Both configurations contained the double doors on the first level in the opened position and the stairwell door and west side double door on the second level being opened and closed depending on the time in the experiment.
+The main difference between the two configurations was that the first level, south side door was in the opened position for Flow Path Configuration 1 and was in the closed position for Flow Path Configuration 2.
+Fig.~\ref{fig:flow_path_1} and Fig.~\ref{fig:flow_path_2} contain the floor plan schematics for Flow Path Configuration 1 and Flow Path Configuration 2, respectively.
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
+\\
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
+\caption[Flow path configuration used during West Structure water flow experiments]{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
+Both double doors and the south side door were open on the first floor for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
+\label{fig:flow_path_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
+\\
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
+\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
+Both double doors were open and the south side door was closed on the first floor for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
+\label{fig:flow_path_2}
+\end{figure}
+
+\clearpage
+
+The four sets of water flow experiments conducted in the West Structure contained two different procedures for each flow path configuration.
+One of the procedures involved using a monitor nozzle to flow water at fixed positions in the first floor of the structure, and the other procedure used a handline equipped with a combination nozzle to flow water into the first floor of the structure in various application patterns.
+The second procedure used a 1$\frac{3}{4}$" handline equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+Each stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.
+
+\subsubsection{Monitor Nozzle Experimental Procedure}
+\label{sec:Monitor_Procedure}
+Two sets of the experiments, Tests 16 and 17, involved flowing water from a monitor nozzle in a straight stream, narrow fog stream, and wide fog stream pattern.
+Each stream was aimed at two different locations on the first floor interior ceiling: the "far target", which was located approximately X m (Xft) from the south interior wall, and the "near target" which was located approximately X m (Xft) from the interior wall of the double doors.
+
+\subsubsection{Handline Experimental Procedure}
+\label{sec:Handline_Procedure}
+Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1$\frac{3}{4}$" handline equipped with a combination nozzle.
+Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.
+
+Tests 18 and 19 followed identical procedures that involved flowing water from a handline using different hose stream and application pattern combination.
+The handline combination nozzle was adjusted to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream.
 Tests 18 and 19 involved three sets of experiments, one for each type of hose stream.
@@
 Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
-
-\begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
-\\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
-\caption[West Structure first and second floor layouts for Test 18]{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
-Both double doors and the south side door were open on the first floor for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
-\label{fig:test_18_plan}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
-\\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
-\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
-Both double doors were open and the south side door was closed on the first floor for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
-\label{fig:test_19_plan}
-\end{figure}
 
@@
 
+Significant air flow through the stairwell and \nth{2} level double door only occurred when the flow path was complete, or when both doors were in the open position.
+Tables~\ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} contain the average air velocity measured by the eight BDPs at the stairwell door and \nth{2} level, double door, respectively, during the time the flow path was complete for each application pattern and hose stream combination used during Tests 18 and 19.
+
+\begin{table}[!ht]
+\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
+\begin{tabular}{|l|l|c|c|c|c|}
+\hline
+\multicolumn{5}{|c|}{Test 18} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\textit{Straight} & -0.17 & 0.48 & 0.65 & 0.63 \\ \hline
+\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 \\ \hline
+\textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
+\multicolumn{5}{|c|}{Test 19} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\textit{Straight} & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
+\textit{Narrow Fog} & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
+\textit{Wide Fog} & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
+\end{tabular}
+\label{table:Tests_18_19_BDP_A10_Avgs}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
+\begin{tabular}{|c|c|c|c|c|}
+\hline
+\multicolumn{5}{|c|}{Test 18} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\textit{Straight} & -0.43 & 1.75 & 2.46 & 2.40 \\ \hline
+\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 \\ \hline
+\textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
+\multicolumn{5}{|c|}{Test 19} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\textit{Straight} & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
+\textit{Narrow Fog} & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
+\textit{Wide Fog} & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
+\end{tabular}
+\label{table:Tests_18_19_BDP_A13_Avgs}
+\end{table}
+
 \subsubsection{Clockwise vs. Counterclockwise Rotation}
@@
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
-\caption{Average Velocity of North Double Door, Test 18, All Streams, CW vs. CCW}
+\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
 \label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
@@
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
-\caption{Average Velocity of North Double Door, Test 19, All Streams, CW vs. CCW}
+\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
 \label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}

### 2015-02-11 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -1,0 +1,619 @@
+#!/usr/bin/env python
+
+import os
+import numpy as np
+import pandas as pd
+from pylab import *
+import math
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+#  =================
+#  = User Settings =
+#  =================
+
+# Location of experimental data files
+data_dir = '../Experimental_Data/'
+results_dir = '../Results/'
+
+# Location of file with timing information
+timings_file = '../Experimental_Data/All_Hose_Times.csv'
+
+# Location of scaling conversion files
+scaling_file_default = '../DAQ_Files/Delco_DAQ_Channel_List.csv'
+scaling_file_master = '../DAQ_Files/Master_DelCo_DAQ_Channel_List.csv'
+scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
+scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
+results_loc = '../Experimental_Data/'
+
+# Location of test description file
+info_file = '../Experimental_Data/Description_of_Experiments.csv'
+# Hose description file
+hose_info_file = '../Experimental_Data/Description_Hose_Experiments.csv'
+
+# Duration of pre-test time for bi-directional probes and heat flux gauges (s)
+pre_test_time = 60
+
+# List of sensor groups for each plot
+sensor_groups = [['TC_A1_'], ['TC_A2_'], ['TC_A3_'], ['TC_A4_'], ['TC_A5_'],
+                 ['TC_A6_'], ['TC_A7_'], ['TC_A8_'], ['TC_A9_'], ['TC_A10_'],
+                 ['TC_A11_'], ['TC_A12_'], ['TC_A13_'], ['TC_A14_'], ['TC_A15_'],
+                 ['TC_A16_'], ['TC_A17_'], ['TC_A18_'], ['TC_A19_'],
+                 ['TC_Ignition'],
+                 ['TC_Helmet_'],
+                 ['BDP_A4_'], ['BDP_A5_'], ['BDP_A6_'], ['BDP_A7_'],
+                 ['BDP_A8_'], ['BDP_A9_'], ['BDP_A10_'], ['BDP_A11_'],
+                 ['BDP_A12_'], ['BDP_A13_'], ['BDP_A14_'], ['BDP_A15_'],
+                 ['BDP_A18_'],
+                 ['HF_', 'RAD_'],
[…]

### 2015-02-11 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Minor text updates.

@@
 
+\clearpage
+
 \subsection{Furniture Fuel Package}
@@
 
+\clearpage
+
 \subsection{Spray Density}
@@
 \label{chap:Summary}
+
+The National Institute of Standards and Technology, with the support of the Fire Protection Research
+Foundation, the U.S. Department of Homeland Security, and the U.S. Fire Administration conducted a
+series of fire experiments to examine the impact of wind on fire spread through a multi-room structure
+and examine the capabilities of wind-control devices (WCD) and externally applied water to mitigate the
+hazard. The measurements used to examine the impact of the WCDs and the external water application
+tactics were heat release rate, temperature, heat flux, and gas velocity inside the structure. Oxygen,
+carbon dioxide, carbon monoxide, total hydrocarbons and differential pressures were also measured.
+Each of the experiments was recorded with video and thermal imaging cameras. Some of these
+measurements are not practical or affordable to make in an acquired structure, hence the need to build a
+structure and conduct the experiments within the confines of the NIST Large Fire Facility. These 354
+experiments also provided visual documentation of fire phenomena that are not typically observable on
+the fire ground.
+A limited series of heat release rate experiments were conducted to characterize the fuel load packages
+used in wind driven structure experiments. Both the bedroom and the living room contained a fuel load
+composed of furnishings with an average peak heat release rate of 7.8 MW with a total heat release of at
+least 1700 MJ, not accounting for any of the wooden furniture or interior finish materials.
+The experiments were designed to expose a public corridor area to a wind driven, post-flashover
+apartment fire. The door from the apartment to the corridor was open for each of the experiments. The
+conditions in the corridor were of critical importance because that is the portion of the building that
+firefighters would use to approach the fire apartment or that occupants from an adjoining apartment
+would use to exit the building.
+The fires were ignited in the bedroom of the apartment. Prior to the failure or venting of the bedroom
+window, which was on the upwind side of the experimental apartment, the heat release rate from the fire
+was on the order of 1 MW. Prior to implementing either of the mitigating tactics, the heat release rates
+from the post-flashover structure fire were typically between 15 MW and 20 MW. When the door from
+the apartment to the corridor was open, temperatures in the corridor area near the open doorway, 1.52 m
+(5.00 ft) below the ceiling, were in excess of 600 °C (1112 °F) for each of the experiments. The heat
+fluxes measured in the same location, during the same experiments, were in excess of 70 kW/m². These
+extreme thermal conditions are not tenable, even for a firefighter in full protective gear. These
+conditions were attained within 30 s of the window failure.
+Experiment 1 was conducted without any external wind. This experiment provided valuable baseline
+data and demonstrated several important points relevant to fire fighting:
+Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of
+the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
+unburned hydrocarbons filled the rooms of the structure. Once the window failed, the fresh air provided
+the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat
+release rate.
+Venting does not always equal cooling. In this experiment, post ventilation temperatures and
+heat fluxes all increased, due to the ventilation induced flashover.
+Fire induced flows. Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire
+growth and the flow path that was set-up between the window opening and the corridor vent.
+Avoid the flow path. The directional nature of the fire gas flow was demonstrated with thermal
+conditions, both temperature and heat flux, which were twice as high in the “flow” portion of the
+corridor as opposed to the “static” portion of the corridor in Experiment 1. Thermal conditions in the
+flow path were not consistent with firefighter survival.
+Experiments 2 through 8 all used a mechanically generated wind, ranging from 3 m/s to 9 m/s (7 mph to
+20 mph). 355
+The fuel load in the structure was the same for all of the experiments. Each of these experiments
+demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE,
+after the window failed.
+Experiments 2 through 5 focused on the impact of WCDS. In these experiments, the WCDs reduced
+the temperatures in the corridor outside the doorway by more than 50 % within 60 s of deployment. The
+heat fluxes were reduced by at least 70 % during this same time period. The WCDs also completely
+mitigated any gas velocity due to the external wind.
+Experiments 6 through 8 focused on the impact of externally applied water. In these experiments, the
+externally applied water streams were implemented in three different ways; a fog stream across the face
+of the window opening, a fog stream into the window opening, and a solid water stream into the window
+opening. The fog stream across the window was not effective at reducing the thermal conditions in the
+corridor. The fog stream in the window decreased the corridor temperature by at least 20 % and the
+corresponding heat flux measured by at least 30 %. The solid stream experiments resulted in corridor
+temperature and heat flux reductions of at least 40 % within 60 s of application. None of the water
+applications reduced the gas velocities in the structure. In some cases, the gas velocity increased during
+water application, due to momentum imparted from the water.
+These experiments demonstrated the “extreme” thermal conditions that can be generated by a “simple
+room and contents” fire and how these conditions can be extended along a flow path within a structure
+when wind and an open vent are present. Two potential tactics which could be implemented from either
+the floor above the fire in the case of a WCD, or from the floor below the fire in the case of the external
+water application were demonstrated to be effective in reducing the thermal hazard in the corridor.
+However, these experimental results also indicate that the post deployment thermal conditions for any
+single tactic were still of a level which could pose a hazard to firefighters in full PPE.
+The experiments also provided potential guidance for firefighters as a part of a fire size up and approach
+to the room of fire origin: note wind conditions in the area of the fire, look for “pulsing flames”,
+examine smoke conditions around closed doors in the potential flow path, and maintain control of doors
+in the flow path.
+Further research in actual buildings is required to fully understand the ability of firefighters to
+implement these tactics, to examine the thermal conditions throughout the structure such as in stairways,
+and to examine the interaction of these tactics with building ventilation strategies both natural and with
+positive pressure ventilation.
+If the demonstrated technologies continue to prove effective in the field trials and pilot programs, the
+next step may be to examine the need for standards and standardized test methods to define a minimum
+level of acceptable performance of these devices.
 

### 2015-02-15 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: add meta data for PDF

@@
   pdfauthor={Weinschenk, Craig G., Overholt, Kristopher J., and Madrzykowski, Daniel},
-  pdfsubject={Insert abstract here.},
-  pdfkeywords={insert; keywords; here}
+  pdfsubject={Fire Dynamics Simulator (FDS), which is a fire model that is developed and maintained by the National Institute of Standards and Technology (NIST), was used to provide insight into the dynamics of a fire that occurred on February 24, 2012, within a single-story, single-family residential structure in Riverdale Heights, MD, that resulted in the serious injury of two Price George's County firefighters.
+The inputs for the FDS simulation are documented in this report and are based on the fire scenario, including the building geometry, interior furnishings, and ventilation conditions.
+The fire started in the basement which generated ventilation limited (fuel rich) fire conditions in the basement area.
+After the front door was opened, the interior stairwell, aided by strong winds blowing into the basement, acted as a chimney for hot gases in the basement to flow towards regions of lower pressure, out through the front door.
+The temperature of the gases in the interior stairwell was estimated to be in excess of 400~C (750~F).
+Two firefighters were located in the flow path between the interior stairwell door and the front door of the structure, were exposed to these elevated temperatures, and suffered serious burn injures.
+Five additional firefighters were injured during fire operations on the first floor.},
+  pdfkeywords={flow path; fire dynamics; LODD; fire modeling; FDS simulation}
 }

### 2015-02-18 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: update report to include TN number, update input file for high frame rate slices

@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1870}
 \end{flushright}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1870}{http://dx.doi.org/10.6028/NIST.TN.1870}
 \endgroup
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1870}{http://dx.doi.org/10.6028/NIST.TN.1870} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2015) \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1870 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1870, \pageref{LastPage} pages (February 2015) \\
 CODEN: NTNOEF}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1870}{\bf http://dx.doi.org/10.6028/NIST.TN.1870} \\
 \endgroup

### 2015-02-24 Studies/2012_PG_County/Report/PG_Co_Fire.tex
PG Co: fix minor typos from ERB

@@
 \setcounter{page}{1}
-Part of the function of the Fire Research Division at NIST is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
+Part of the function of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to develop and apply technology, measurements, and standards to improve the understanding of the behavior, prevention, and control of fires to enhance fire fighting operations and equipment, fire suppression, fire investigations, and disaster response.
 NIST has previously used the Fire Dynamics Simulator (FDS) fire model to provide insight into the fire development and thermal conditions of fires that have resulted in line of duty deaths (LODDs)~\cite{Madrzykowski:1,Iowa,Texas,Bryner:Charleston,barowy:texas,Weinschenk:Chicago,Overholt:San_Francisco}.
@@
 The mesh is coarser to cut down on computational time and because high accuracy in the fluid mechanics of the air flow far from the structure is not important in the analysis of this simulation.
-The 20~cm resolution resulted in an additional 216,000 computational cells.
+The 20~cm resolution resulted in an additional 216\,000 computational cells.
 
@@
 Note the finer mesh (smaller cells) surrounding the structure and the coarser mesh on each side.
-The domain was divided into 12 equally sized 10~cm meshes that surrounded the structure (each containing 150,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the structure (each containing 32,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56,000 grid cells) for a total of 17 meshes.
+The domain was divided into 12 equally sized 10~cm meshes that surrounded the structure (each containing 150\,000 grid cells) plus 4 equally sized 20~cm meshes to the left and right of the structure (each containing 32\,000 grid cells) and one 20~cm mesh in the rear of the structure (containing 56\,000 grid cells) for a total of 17 meshes.
 Multiple meshes allowed the simulation to be processed in parallel, which reduced the amount of required calculation time to approximately 3~days from over 1~week with a uniform 10~cm mesh.
@@
 
-A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100 seconds of the simulation indicated that on average there was the equivalent of an approximate 0.7 MW fire(s) occurring through open external vents (basement windows).
+A comparison of the differences between the HRR inside the structure (Fig.~\ref{fig:PG_Total_HRR}) and the total HRR (Fig.~\ref{fig:PG_9MW_HRR}) over the first 100~s of the simulation indicated that on average there was the equivalent of an approximate 0.7 MW fire(s) occurring through open external vents (basement windows).
 This aligns with observed post-fire damage and post-incident report~\cite{PGCounty2013}.
@@
 
-After 100 seconds of simulation time, 5~\sfrac{1}{2}~minutes after the first 911 call, firefighters open the front door to make entry to the first floor of the structure.
+After 100~s of simulation time, 5.5~min after the first 911 call, firefighters open the front door to make entry to the first floor of the structure.
 The change in ventilation to the structure impacted the HRR.
@@
 Hot gases which may have built up within the structure will flow from high pressure to low pressure.
-Based on the event timeline, the front door was opened 100 seconds into the simulation, which would create a low pressure relief on the first floor.
+Based on the event timeline, the front door was opened 100~s into the simulation, which would create a low pressure relief on the first floor.
 Due to firefighters entering the structure through the front door, the simulated pressure on the first floor prior to and just after opening the door is important.
@@
 Velocities through both the doorway at the top of the stairs and the front door were approximately 13~m/s (29~mph), which was faster than the imposed wind speed (9~m/s or 20~mph) because of the addition of the buoyancy of the fire plume.
-The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750-800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
+The model temperatures increased through the stairwell doorway to between 400~$^{\circ}$C and 425~$^{\circ}$C (750~$^{\circ}$F to 800~$^{\circ}$F) and through the front door to approximately 375~$^{\circ}$C (700~$^{\circ}$F).
 From the approximate timeline (Table~\ref{tab:combined_timeline}), the front door was forced closed due to airflow pushing against it, 207~s into the simulation.

### 2015-03-06 Projects/Madrzykowski_Thesis/Madrzykowski_Thesis.tex
Commit draft of Dan's thesis.

\documentclass[twoside]{uocthesis}

\usepackage{graphicx}

\Title{Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board}
\Author{Daniel Madrzykowski}
\Year{2015}

\Supervisor{Dr Charles Fleischmann}
\Department{Department of Fire Safety Engineering}

\begin{document}

\prelimpages

\titlepage

\dedication{To my wife and family}

\abstract{%
Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.  The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus reduce the losses from fires.  However, as the result of the review of several arson cases and a review by the U.S. National Academy of Sciences, questions about the lack of the use of science in the practice of fire investigation were raised.  Specifically the National Academy of Sciences indicated that ``... research is needed on the natural variability of burn patterns...''
This study addresses that need in two ways:
\begin{enumerate} 
\item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires 
\item Examining the capability of using numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench scale and full scale fire experiments conducted in this study.
\end{enumerate}
This paper highlights the many uncertainties involved in what appear to be simple fire experiments.  A variety of uncertainties related to the composition of the fuels, measurement methods, and analysis techniques just to list a few of the areas considered.  The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.  Three different fuels were used: natural gas, gasoline, and polyurethane foam.  Each fuel had a similar top surface area.  The heat release rate data showed that the variability was greater for more complex fuels.  While the variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.  The patterns generated by the polyurethane foam fire, had more variability than the natural gas and the gasoline fire patterns.  This is likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.  The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.  The comparison of the fire pattern heights and the mean flame height demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.

This trend is the same as exhibited by the repeatability of the heat release rate measurements and the flame height measurements.   *****Computational results here ****

}

\tableofcontents

\listoffigures

\listoftables

\acknowledgments{%
I would like to thank Prof.~Fleishmann, etc.

This work was partially funded by the National Institute of Justice (NIJ) through an interagency agreement with the NIST Office of Law Enforcement Standards (OLES). I would like to thank Susan Ballou of OLES for her support of this project. This work was also partially supported by the U.S. Fire Administration.

The would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury

Finally, my family...
}

\textpages

\chapter{Introduction}
\label{chapter:Introduction}

Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.  Findings from an archeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years.[1]  This is 300 thousand years earlier than previously thought.  Despite mankind’s extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries.[2]  Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 populations.  The World Fire Statistics Center collects data from European, North American and a few Asia-Oceania countries.  Within this group of countries the fire deaths per 100,000 population range from 0.02 (Singapore) to 2.03 (Finland). [3]      There are a significant number of factors that determine the variability of fire death rates between nations, socio- economic conditions being a leading factor.[2]

In the United States, the loss of life due to unwanted fire has been decreasing steadily since the 1970’s.  This is neglecting the increased loss of life as a result of the terrorist attack on September 11, 2001.  The estimated number of fire deaths in the U.S. in 1975 was 8,100 or 3.75 deaths per 100,000 population.[4]  In 2013, there were 3,240 civilian fire fatalities or 1.02 deaths per 100,000 population.[5]  During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.  There are many reasons that led to this decrease in loss of life due to fire in the United States.  An example would be research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs to name just a few.  None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response.[6]

Fire investigation is a key element in the fire prevention system that generates data to enable the reduction of fire losses.  The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus further reduce the losses from fires.  Data such as the room of fire origin, the first item ignited and ultimately the cause of the fire is information that is critical to understanding and reducing the number of fires.  For example, the identification of products that are involved in ignitions due to a design flaw, in many cases result in the U.S. Consumer Product Safety Commission or a manufacturer issuing a product recall.  
In some cases, the fire investigation determines that the fire was intentional.  An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention.[7]  An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA 921, is “a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be.”[8]

According to the NFPA, there were approximately 282,600 intentionally set fires each year during the period of 2007 through 2011 in the United States. The average annual loss totals for that period were approximately 420 civilian deaths and 1,360 civilian injuries. More than \$1.3 billion dollars (U.S.) was lost per year due to direct property damage. Fires involving structures account for more than 84~\% of the civilian deaths, injuries and property loss from all intentional fires.  Approximately two-thirds of the structure fires occurred in residential occupancies.  95~\% of the civilian deaths and 86~\% of the civilian injuries also occurred in the intentional fires in residential occupancies. [7]

A subset of the intentional fires are considered arson.  Arson as defined by the U.S. Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.[9]

The national rate of arson fire cases cleared by arrest or exceptional means is less than 20~\%.  Of those cases approximately 46~\% of the suspects were prosecuted.[7] Arson is a challenging crime to solve because typically there are no witnesses present at the time of the crime.

Fires are investigated in order to determine the ``origin and cause'' of the fire and in cases of arson there is an effort to determine who was responsible for setting the fire.  This investigation process must follow the scientific method as documented in NFPA 921 [8].  There are numerous textbooks on the subject of conducting a fire investigation [10-15]. The NFPA guide and the texts provide information to a fire investigator collecting data from the scene, analyzing the data, and developing a hypothesis about the fire.

Patterns produced by the fire are in many cases a significant portion of the data collected and are analyzed at the scene to determine the area of origin.  One of the basic methods of documenting the fire scene is to photograph fire patterns.  As noted by Icove, DeHaan, and Haynes  “the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…”. [13]  A fire pattern is defined in NFPA 921 as, “the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects” [921].  
DeHaan [12] categorizes the fire effects that form patterns as follows:
\begin{enumerate}
\item Surface deposits – no irreversible effect on surface
\item Surface thermal effects – physical change such a discoloration or melting
\item Charring –evidence of surface burning
\item Penetration – charring below the surface
\item Consumption –loss of surface material, charring throughout
\end{enumerate}
Lentini points out that most fire patterns are generated and later observed on two-dimensional surfaces at the place where those surfaces intersect with the three-dimensional fire. Various [14] types of fire patterns, such as; “V-shaped”, “hour-glass”, and “inverted cone”, have come from common observation at actual fire scenes.  As a result, the observations are typically qualitative in nature.   
Previous fire pattern research by the National Institute of Justice (NIJ), the National Institute of Standards and Technology (NIST), and the United States Fire Administration (USFA) has shown that fire patterns provide data useful for the determination of fire origin.  The reports noted the impact of ventilation on the development of the burn patterns. [16, 17] A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s) and compartmentation, to name a few.    Given the limited number of experiments in the literature and the large number of variables, it has been difficult to fully understand a cause and effect relationship between the fire scenarios and the resulting patterns.  Therefore, fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause.[18]  Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.  A collection of the widely used correlations can be found in the U.S. Nuclear Regulatory Commission’s (NRC) Fire Dynamics Tools (FDTs).  FDTs incorporates references to the source documents and experimental work upon which the correlations are based. In addition, NRC tasked NIST with conducting a verification and validation study of the correlations. Overholt developed the NIST verification and validation study.[19] In a private communication, Overholt noted that not all of the correlations in FDTs were included in the study since a sufficient amount of reliable data in the literature to not available to conduct validation.  Two of the types of correlations, which could not be validated, were flame height and time to ignition.[19]

A survey of zone and field fire models was compiled and is posted on www.firemodelsurvey.com.[20] The survey was updated in 2014, but it includes models that were documented in the first fire model survey conducted in 1992. As a result many of the models are listed for historical purposes only.  There are 53 zone models listed. Only 3 of the 53 are being actively supported or maintained.  The survey also includes 22 field models.  10 of the 22 field models are listed as being actively supported.  All of the correlations and models have been to some extent been validated or checked against experimental data for a limited set of scenarios. [21]

Of the active field models, FDS version 6 has one of the most rigorous and publically accessible verification and validation programs.[22] In the current FDS validation guide more than 45 experimental data sets are used to quantify the prediction capabilities of the model.  Results are presented in terms of model bias and variation to inform users of whether particular quantities (temperature, heat flux, pressure, etc.) are over or under predicted compared to experimental data.

However for fire models to be demonstrated as reliable and suitable for use in court, studies such as the one conducted here need to be conducted to provide the scientific basis for the use of fire models for re-construction.  The research results may enable fire investigation teams to have a better understanding of the fire scene and enable improved support of their hypothesis on the area of origin based on fire patterns.  This idea was discussed when the Fire Protection Research Foundation convened a Research Advisory Council on Post-fire Analysis in 2002.  Recommendations for research and development in their white paper included, “advance the capabilities of computational fluid dynamics fire modeling, particularly as applied to fire ignition scenarios and fire pattern development and interpretation”  [23]

It has been pointed out in this introduction that fire is still a threat to life and property and how fire investigation plays a role in preventing future fires.  Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount or research and analysis tools directly related to this practice.  The fire investigation community recognized a need to improve the science and practice of fire investigation.  One of the manifestations of the efforts to improve the practice was the development of NFPA 921, Guide for Fire and Explosion Investigations.  The first edition of NFPA 921 was issued in 1992.  As provided by the document scope, it “… is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.”     The document’s purpose includes the goal to be “…a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.” [8] However, NFPA 921 can only incorporate the fire science and research results that have been produced.  Although NFPA 921 is a “guide” as opposed to a “standard” is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.

As the result of the review of several arson cases, most notably the cases of Ernest Ray Willis and Cameron Todd Willingham, the practice of fire investigation as a forensic science was called into question.  Beyler conducted a review of both cases for the Texas Forensic Science Commission.  Both fires occurred prior to the release of NFPA 921 in 1992.  The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases “did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.”  The fire investigators had a poor understanding of science and their findings of arson could not be sustained.[24]
Another landmark document regarding the state of forensic science in the United States was published in 2009.  The 328 page report, titled Strengthening Forensic Science in the United States: A Path Forward, by the U.S. National Academy of Sciences, reviewed 13 different forensic science disciplines including; biological evidence, friction ridge patterns, tool mark and firearms identification, and analysis of explosives evidence and fire debris, to name a few.  The review of the analysis of explosives evidence and fire debris is covered in three pages of the report.  The summary assessment of analysis of explosives evidence is positive, “the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry .”[25]  The complete summary assessment for fire debris analysis is included here: “By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.  Despite the paucity of research, some arson investigators continue to make determinations about whether or not a particular fire was set.  However, according to testimony presented to the committee, many of the rules of thumb, that were typically assumed to indicate that an accelerant was used (e.g. “alligatoring” of wood, specific char patterns) have been shown not to be true.  Experiments should be designed to put arson investigations on a more solid scientific footing .” [25]   
This study is in response to the assessment above, specifically regarding the natural variability of fire patterns.

\chapter{Scope of Study}

Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard, which is 2.4 m in height.  Given the upper bound of 2.4 m, the experiments will use small fires with mean flame heights of approximately 1.2 m.  The resulting patterns on the gypsum board wall would be representative of a pre-flashover fire pattern.

In order to understand the variability or repeatability of fire patterns, the repeatability of the fire generating the fire pattern must be quantified.  The fires were characterized in terms of heat release rate, mass loss rate (when appropriate), plume temperature, heat flux, and visible flame height.

Replicate experiments exposing gypsum wallboard to the fires were conducted in order to examine the repeatability of the fire patterns.  Correlations between the fire characteristics and the fire patterns will be examined.

The last component of this study examines the capability of using numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, as well as  bench scale and full scale fire experiments conducted in this study.

\chapter{Technical Approach}

This study includes several series of real-scale, replicate fire experiments to examine the repeatability of pre-flashover fire patterns, and ultimately examine the ability of simple correlations and the Fire Dynamic Simulator to recreate characteristics of the fire patterns.

\section{Selection of Measurement Methods and Analytical Tools}

Well-documented and characterized technologies such as thermocouples and heat flux gauges were used to assess the fire and the thermal exposure of the target material.  Oxygen consumption calorimetry and mass loss was used for the determining the heat release rate of the fires.

The most important measurements for the field investigator are the visual measurements that can be made at the scene or determined from scene photographs. Several methods of imaging were used for these experiments: still photography, digital video, and infrared video.  Computer based imaging techniques, such as those contained in the Image Stream program suite, were examined and adapted to analyze the flame height of the source fires [26].

Statistical methods were used to guide the wall fire and corner fire experiments.  The analysis ensured that the appropriate number of replicate experiments were conducted to provide an assessment of burn pattern repeatability within a given level of uncertainty.  Given that the coefficient of variation (COV) may be different for a given type of experiment, the number of replicates required would be larger for experiments with a larger COV in order obtain a valid assessment of repeatability.

The series of experiments listed below are ordered in such a manner to optimize the total number of experiments required.

\subsubsection{Characterization of Source Fires}

The fires were characterized in terms of heat release rate, mass loss rate, fire plume temperatures and emitted heat flux. Videos were recorded for each experiment.  This “field” data from the videos was  used to determine the flame heights. Experiments were conducted with three different fuel types: a gas fueled mass flow controlled burner, a liquid fueled burner, and a solid fuel.
Instrumented Calibration Target Wall – A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.

\subsubsection{Instrumented Gypsum Wallboard Target Wall}

A free standing, non-combustible, steel frame with gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.  The fires were initially placed at predetermined, fixed positions away from the wall. The burner was moved toward the wall until the burner was against the wall.  If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.

\subsubsection{Impact of Construction}

Comparative experiments were conducted to examine the impact of the method of construction and support of the walls and corner sections on the development of the burn patterns.  Three cases were examined: 1) 12.7 mm thick, regular core, painted gypsum board on the front of a wall frame (open back), 2) 12.7 mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall), and 3) 12.7 mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).  The main consideration was to identify any differences in the height, width, shape, and area of the fire patterns. The results of these experiments determined the construction of the walls and corners used in subsequent phases of this study.

\section{Fire Pattern Experiments}

\subsubsection{Wall Fires}

Each of the test compartments consisted of three 3.6 m long by 2.4 m high wood framed walls. A partial ceiling was installed over the wall. The interior of the wall sections and ceilings were covered with painted gypsum wallboard.  These experiments were conducted without instrumentation in the walls.  Based on the outcome of the instrumented calibration target wall results, burner positions were chosen. After each burn, the fire patterns were measured, photographed and analyzed for repeatability. The fire damaged wallboard was subsequently removed and replaced with new sections of painted gypsum wallboard. The number of experiments for each case was dependent on the repeatability and similarity of the pattern development.

\subsubsection{Corner Fires}

These experiments used the same test compartment as the wall fire pattern experiments.  In these cases the fire was located against both walls in a corner of the compartment.  The experimental process was the same as the wall fire pattern experiments.

\subsection{Bench Scale Experiments}

Several types of bench scale experiments were conducted to generate data. This data could be used to assist in the analysis of the fire patterns and potentially be used as input for the FDS models.
Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a “critical heat flux” that results in a clear line of demarcation, a “burn/no burn” line.  The flooring radiant panel (ASTM E648) was used to examine this value.

\subsubsection{Cone Calorimeter}

Cone calorimeter (ASTM 1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25 kW/m2 to 75 kW/m2.

\subsubsection{Fire Pattern Recreation}

Heskestad developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.[27, 28] This correlation was compared with the flame height results of the source fires and the instrumented wall experiments.

FDS[22] and Smokeview[29] were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.  Comparison between the experiments and the model will provide valuable validation data for the model.

\subsubsection{Data Analysis}

Point measurements were reduced and compared with values from the literature on fire plumes and their interaction with vertical surfaces.  The heat release rates, heat flux measurements, flame and surface temperatures were used as input for heat transfer analysis to develop empirical coefficients for the specific experimental arrangements which would be useful in the model recreations.
The key measurements for repeatability of the fire patterns on the gypsum wallboard are height, maximum width, shape, and area.  The two significant outcomes will be the repeatability of the fire patterns themselves and the ability to numerically recreate key measures of the pattern.

\section{Characterizing the Source Fires}

A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover or incipient fires.  A fixed fire source footprint, 30.5 cm square, was chosen for this study and a range of common fuels was selected.  The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.  Heat release rate, flame/plume gas temperatures, and total heat flux from the flames were measured and flame movement and height were recorded with photographs and videos.  Given the focus on residential fires, small source fires were selected so that the burn pattern would be limited to less than 2.4 m in height.  Replicate experiments were conducted with each of the fuels, in order to examine the repeatability of the fires and to quantify the variability in the flames.

\subsubsection{Fuels}

Three different fuels were used in this study.  Experiments were conducted with a natural gas fueled burner, a liquid fueled pan fire, and a solid fuel. Natural gas was chosen as a fuel because it is used for calibrating the oxygen depletion calorimeters in NIST’s Large Fire Laboratory.  Therefore the heat content of the gas was monitored and mass flow controlled to provide a heat release rate based on fuel mass flow for comparison with the heat release rate values measured with the calorimeter.  The gas burner arrangement provides the most idealized fire, in that it can be ignited and brought up to a near steady state heat release rate within a few seconds and then be shut down just as quickly.  This provided an approximate “square wave” exposure to the gypsum wallboard.  This is important for determining the potential amount of energy transferred to the exposed surface.

The natural gas burner was 30.5 cm on a side and the top surface of the burner was 7.5 cm above the floor. The shell of the burner was made from steel and filled with “pea sized” gravel with an average diameter of 6 mm.  A steady state heat release rate of approximately 80 kW was used for the experiments.

Gasoline was the fuel of choice for the liquid fueled pan fire.  Gasoline is not an ideal fuel to use in experiments because it is a mixture of components and additives that are specific to manufacturers. In addition the mixtures change from season to season, and vary based on requirements or restrictions of the locality.  However, fire incident data shows that gasoline was the first item ignited in the majority of intentional fires where flammable or combustible liquids were used 12.[30] In addition, data from forensic laboratories, collected by Babrauskas and others, indicates that gasoline is the most prevalent accelerant found as part of the analysis of fire debris samples 13, 14.[31, 32] 
The gasoline pan fire used 500 mL of unleaded, 87 octane gasoline.  The pan was constructed from 6 mm thick steel.  The inner dimension of the pan was 30.5 cm on a side and 1.9 cm high.  The pan was elevated in order to bring the pan lip height up to 7.5 cm above the floor to be the same height as the natural gas burner.  The 500 mL of gasoline had a fuel depth of 5.5 mm and provided a burn time of approximately 300 s.

Polyurethane foam was chosen as the solid fuel.  According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses. More than 1.2 billion pounds are produced in the U.S. every year 15,16.[33, 34] In studies by Ahrens and Evarts of the NFPA, upholstered furniture and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S. based on averaged data from 2005 through 2009.[35, 36]

The flexible polyurethane foam had a density of approximately 23 kg/m3.  Each block of foam was 30.5 cm on a side and was 7.5 cm thick. The bottom and sides of the foam block were wrapped in aluminum foil to prevent the fuel from flowing or spreading as it burned to ensure that the fuel area remained with the same fixed area as the gasoline and natural gas.

\subsubsection{Experimental Arrangement}

The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3 m by 3 m hood oxygen consumption calorimeter. This apparatus follows the methodology of ASTM E 2067-08, Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests.[37]  The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors. A load cell was positioned as a support for the fuels.  All of the data was recorded at intervals of 1 s on a computer based data acquisition system.

\subsection{Instrumentation and Measurement Uncertainty}

\subsubsection{Heat Release Rate}

The NIST Large Fire Research Laboratory’s 3 m by 3 m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700 kW.  Details on the operation and uncertainty in measurements associated with NIST’s 6 m by 6 m oxygen consumption calorimeter were documented by Bryant et.al. [38] Many of the same instruments are shared between the two calorimeters and calibration burns were conducted during each experimental series.  As a result, the expanded uncertainty of this device has been estimated as 11~\% on the measured heat release rate.

\subsubsection{Flame/Plume Gas Temperatures}

Gas temperatures were measured with exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm nominal diameter.  Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2 mm diameter inconel shield, 0.76 m in length.  The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer [39]  The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.[40, 41]  Small diameter thermocouples were used to limit the impact of radiative heating and cooling.  The estimated combined expanded uncertainty for temperature in these experiments is 15~\%.

\subsubsection{Heat Flux}

Water cooled, Schmidt-Boelter total heat flux gauges were used to measure the heat flux. The sensing surface of the heat flux gauges were located 0.95 m horizontally from the center of the burner/fuel and 0.50 m above the top of the burner/pan lip/fuel surface.  The manufacturer reports a 3~\% calibration expanded uncertainty for these devices 20.[42] Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically 8~\%.[43]  The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.

\subsubsection{Mass Loss}

The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91 m x 1.2 m x 12 mm thick supported by the load cell.  The load cell had a resolution of 1.0 g.[44] The expanded uncertainty is estimated to be 5~\%.  The load cell was checked between experiments with calibrated weights during the zero and span checks of the calorimeter.

\subsubsection{Video and Photographs}

A 35 mm single lens reflex camera was used to record digital still photographs of the fires.  The camera had an 8 megapixel resolution.  A mini DV camcorder with 0.7 megapixel resolution was used to capture the video.  A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.  Each camera was positioned on a tripod with a distance of 4.5 m between the centerline of burner to camera lens 4.5 m.  The height of each camera was adjusted so that the center of camera lens was positioned 0.5 m above top of the burner.

A schematic drawing of the instrumentation arrangement is shown in Fig.~\ref{Drawing_Fire_Flamer}.  The thermocouples were mounted on a steel frame.  The frame enabled the thermocouples to be installed at 10 cm intervals from 10 cm to 120 cm above the burner/pan lip/fuel surface. At each 10 cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.  A plumb bob and steel tape measure, with a resolution of $\pm$ 0.5 mm, were used to position and align the thermocouples.   The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$ 2.5~\%.  The same applies to the location of the heat flux sensor surfaces.

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Schematic_Drawing}\\
  \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus which was centered under the 3~m by 3~m oxygen consumption calorimeter.  The heat flux gauges were facing toward the center of the burner/fuel area.}
  \label{Drawing_Fire_Flamer}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Source_Fire_Flamer}\\
  \caption[A photograph of the source fire flamer and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.  In the foreground, from left to right, are the video, 35~mm SLR and thermal imaging camera.}
  \label{Fire_Flamer}
\end{figure}

\chapter{Results}

{\section{HRR}

Figures 3 through 5 are graphs showing measurement results of heat release rate versus time for the natural gas, gasoline and polyurethane foam fueled fires. In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.

On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level ($2\sigma$), based on Type A evaluation of the uncertainty is provided.[45]  A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.  In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2σ) would yield a confidence level of approximately 95~\%.

The natural gas burner provided the most repeatable results, with an average steady state heat release rate of approximately 80 kW $\pm$ 9 kW with an average total heat release of approximately 23.3 MJ $\pm$ 1.6 MJ over a 300 s period.  The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of approximately 80 kW $\pm$ 24 kW.  The total heat release of the gasoline over the 300 s period after ignition was approximately 13.6 MJ $\pm$ 0.6 MJ.  The polyurethane foam demonstrated the largest variability, as shown in Figure 5, of the three fuels in terms of peak heat release rate and time to peak heat release.  Averaging over a 15 s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of approximately 45 kW $\pm$ 21 kW.  The total heat release over the 300 s period after ignition was of 4.1$\pm$ 0.2MJ

\section{Plume Temperatures}

Plots of the centerline temperatures averaged over the replicate experiments for each of the fuels are presented in Figures 6 through 8.  The number following “TC” in the legend of the graphs represents the height of the thermocouple in increments of 10 cm (or dm) above the fuel surface.  The natural gas temperatures were averaged over a “steady-state” burning period as reflected by the data in Figure 6.  The temperature differences between the vertical thermocouple locations, for locations greater than 20 cm above the fire location, begin to decrease as the distances from the top of the burner increase.  This trend is similar for both the gasoline fires and the polyurethane foam fires as well.  The most notable difference between the natural gas and the other fuels is the growth and decay of the fire during the test period.

\section{Total Heat Flux}

The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that has periods of growth and decay.   The sensing surface of the heat flux gauges were located 0.95 m horizontally from the center of the burner/fuel and 0.50 m above the top of the burner/pan lip/fuel surface.  The average peak total heat flux for the natural gas fires were approximately 2.0 kW/m2, as shown in the example data set in Figure 9.  The average peak values for the gasoline and polyurethane foam were approximately 3.5 kW/m2 and 2.5 kW/m2 respectively.  The values are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.

\section{Mass Loss}

Mass loss measurements were not possible for the natural gas burner experiments.  The mass loss versus time curves for the gasoline and the polyurethane experiments are shown in Figures 12 and 13.  The gasoline exhibits a linear mass loss rate for the initial 150 s of approximately 0.12 kg per minute.  The polyurethane foam was ignited with a small flame in the center of the top surface of the foam block.  As the flame spread across the surface it also began to burn down into the foam sample.  As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 0.12 kg per minute.

\section{Flame Height}

Each of the experiments was photographed with a digital single lens reflex (SLR) camera, fixed on a tripod, with a capability of capturing at least five images per second.  Located adjacent to the camera was a video camera recording images at approximately thirty 30 frames per second (fps).  The experiments were also recorded with a thermal imager, however the videos were not used for analysis as it was difficult to determine the differences between the visible flame and the thermal plume from the black and white images.

In engineering terms, the “flame height” is typically discussed as the median flame height.  A position above the top of the fuel surface where the flame is observed to be present at least 50~\% of the time.  As a starting point, the mean flame height for each fuel was estimated from a measurement of the uppermost continuous flame tip from the still photographic images.

Examples of the photographic images are presented in Figures 14 and 15.  Figure 14 is a photograph of the natural gas flame taken during a period of “steady state” burning at approximately 80 kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60 kW.  Figure 9 presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100 kW.  The two photographs, taken 0.2 s apart, represent the range of the observed flame heights from one of the gasoline experiments from 0.65 m and 1.0 m, respectively.

Table 1 provides the mean visible flame height, as well as the range of flame heights for each fuel, based on analysis of the photographs for three replicate experiments.  In each case, the photographs were chosen for analysis while the fire was generating its peak heat release rate.  The range of flame heights for each fuel is approximately twice the minimum flame height or the continuous flame height. Analyzing the photographs in this manner was very time consuming and was based on making measurements on each photograph with a scale.  The limit of 5 frames per second also introduces additional uncertainty in determining the flame height.    These values will serve as a basis for comparing with mean flame height values determined with video analysis.

As noted by Beyler in his review of fire plume correlations, video tape analysis seems to provide the best estimates of flame height. [46]  Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97 fps which is the National Television Standards Committee (NTSC) standard. The resulting image in each frame was 720 pixels wide by 480 pixels high. Segments of the video which corresponded to the peak heat release of each experiment were captured with a video editing program.

For the natural gas experiments, approximately 30 s of “steady state” video were captured.  In the cases of the gasoline and polyurethane fueled experiments, the video capture period bounded the peak heat release rate.  In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30 s video capture could be made which was representative of the peak burning rate.  The peak duration for the polyurethane foam fires was shorter so, only a 15 s video capture was used.

\begin{table}
  \centering
  \begin{tabular}{|l|c|c|}
     \hline
     Fuel	            & Mean (m)  & Range (m) \\ \hline
     Natural Gas	    & 0.70	    & 0.50 to 0.98 \\
     Gasoline 	        & 0.84	    & 0.52 to 1.10 \\
     Polyurethane Foam  & 0.46	    & 0.30 to 0.78 \\
     \hline
   \end{tabular}
  \caption[Mean visible flame height and averaged minimums and maximums]{Mean visible flame height and averaged minimums and maximums (Range) of visible flame heights for each of the fuels during peak heat release rate.}
  \label{Flame_Heights}
\end{table}

Each frame from the video clip was saved as a full color Tagged Image File Format (TIFF) file and the pixel aspect ratio was changed from 0.9 to 1, so that each pixel had the same dimension in both the horizontal and vertical directions.  Once these images were rendered by the video editing program, each image was scaled and cropped to provide input for Streams, a suite of image processing programs developed by Nokes for analyzing fluid flow visualization experiments[26]. The images were scaled so that one pixel equals 5 mm in height and width.

Examples of a set of TIFF images for each fuel are shown in Figures 16 through 18.   Each figure has 56 sequential images from the video segment.  The images total almost 2 seconds of actual burn time.  Notice how the flame height cycles up and down in each of the sequences.  These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.

From each of the peak heat release rate video clips, the edited TIFF files were loaded into Streams.  For the natural gas and gasoline fueled fires, approximately 900 images were used in each image sequence.  The polyurethane foam experiments had approximately 450 images in each sequence for each experiment.  Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble.[47]  Once all of the images were converted to a pure red “flame” which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being “overlaid” on each other.  The end result is a contour plot of the intermittency of the flame ranging from zero to one.

The calculations for the intensity field are based on a user defined computation grid.  A grid sensitivity analysis was conducted with 5 mm, 10 mm, 20 mm, 40 mm and 80mm square grids.  Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Figure 19.  The outputs shown are time averaged intensity fields generated with 5 resolutions listed above. In each output the x and y axis dimensions are in mm.

Since each pixel in the original images was equal to 5 mm, in the highest resolution case, the 5 mm analysis grid would match the best resolution of the original image.  Four of the five cases resulted in similar results, only the 80 mm case generated significantly different results in flame height.  As a result of the sensitivity analysis, a 10 mm grid was chosen as an optimum size for providing a sufficient level of resolution, enabling efficient processing of 30 s worth of video frames.  At the 5 mm grid resolution, limitations within the processing system would not allow a full 30 s of video analysis.  Therefore the intensity fields and the resulting plots and data generated for this study were developed with a 10 mm grid.

Another means of quantifying field data with Streams is the use of contour plots.  Examples of the time averaged contour plots are shown in Figures 20 through 22 for a natural gas, gasoline, and polyurethane fueled experiments respectively.  Each contour line represents the percentage of time that the flame was at a given height.  Figure 20 provides an example of a natural gas experiment.  The region under examination, as shown as a black bounding rectangle, is 1400 mm high and 800 mm in width.  This example was averaged over approximately 29 s or approximately 870 images.  The number above each contour line in the plot range from 0 to 1.  The area bounded by the contour with the value 1 represents the area that the flame occupied 100~\% of the time period analyzed or the persistent flame region as defined by McCaffery. [48] The remaining contours are in the intermittent flame region, with the 0.5 contour representing the mean flame height. Outside of the final contour, value 0.0, no visible flame was recorded; hence this contour marks the definitive start of the buoyant plume region.

Figures 22 and 23 show two different contours for the polyurethane foam fueled experiment.  The results from polyurethane fueled fire characterization experiments have an increased amount of variability due to the nature of the ignition source and the fuel itself.  The polyurethane foam was readily ignited with a small pilot flame similar to that used to ignite the natural gas and the gasoline.  By comparison, a small flame ignited the gases flowing out the top of the natural gas burner and the flames from the natural gas cover entire burner surface within approximately one second.  A similar ignition sequence occurs with the gasoline pan fires. The polyurethane foam has a more complicated flame spread sequence that resulted in significant changes to the peak heat release rate and the time to peak heat release.  Once the polyurethane foam was ignited, it took approximately 60 s for the flame to spread across the top surface of the fuel.  As the flames spread horizontally across the fuel surface, the fire also burns down into the fuel.  In some cases the fire burned completely through the fuel in the center of the foam sample, resulting in a hollow flame at the time of the peak heat release rate.  An example of a contour plot, exhibiting the hollow or bifurcated flames is shown in Figure 23.  Other methods of ignition for the polyurethane foam were considered in order to have a more uniform ignition of the top surface of the foam.  Each method would have resulted in a larger release of energy from the ignition source or a starter fuel.   Based on a few scoping experiments these methods did not improve the repeatability.

Based on the field data developed using Streams average flame heights for each fuel were determined.  In Table 2, each of the values represents the average flame heights, given in mm with 95~\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.  For the natural gas fires, the averages are from ten 30 s segments, while the fire was monitored at approximately 80 kW.  In some cases more than one 30 s segment was sampled per heat release rate experiment.  Sixteen 30 second video segments, which included the peak heat release rate, were successfully analyzed from the seventeen gasoline heat release rate experiments.  One of the videos was unusable for analysis due to reflected light which could not be edited out of the images.  For same reason, the polyurethane foam flame height averages are the result from eight of the ten heat release rate experiments.

\begin{table}
\centering 
\begin{tabular}{|c|c|c|c|}
\hline
Visible         &   \multicolumn{3}{|c|}{Visible Flame Heights (mm)} \\ \cline{2-4}
Fraction (\%)   &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline
10              &       980 $\pm$ 155 (16~\%)   &	930 $\pm$ 130 (14~\%) 	& 650 $\pm$ 220 (34~\%)   \\
20              &   	890 $\pm$ 125 (14~\%)   &	850 $\pm$ 120 (14~\%) 	& 590 $\pm$ 190 (32~\%)   \\
30              &   	820 $\pm$ 125 (15~\%)   &	790 $\pm$ 110 (14~\%) 	& 540 $\pm$ 180 (33~\%)   \\
40              &   	760 $\pm$ 105 (14~\%)   &	740 $\pm$ 95 (13~\%) 	& 500 $\pm$ 165 (33~\%)   \\
50              &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
60              &   	650 $\pm$ 100 (15~\%)   &	655 $\pm$ 85 (13~\%) 	& 435 $\pm$ 135 (31~\%)   \\
70              &   	590 $\pm$ 90 (15~\%)    &	610 $\pm$ 90 (15~\%) 	& 400 $\pm$ 125 (31~\%)   \\
80              &   	530 $\pm$ 85 (16~\%)    &	555 $\pm$ 90 (16~\%) 	& 360 $\pm$ 110 (31~\%)   \\
90              &   	440 $\pm$ 75 (17~\%)    &	490 $\pm$ 95 (19~\%) 	& 315 $\pm$ 110 (35~\%)   \\
100	            &       220 $\pm$ 84 (38~\%)    &	350 $\pm$ 110 (32~\%) 	& 210 $\pm$ 125 (60~\%)   \\
\hline
\end{tabular}
 \caption[Average flame heights for three fuels]{Average flame heights with 95~\% confidence limits, for each of the source fuels shown as the percentage of time the flame was visible at that given height.}
 \label{Average_Flame_Heights}
\end{table}

For both the natural gas and the gasoline experiments the 95~\% confidence limits show less than 20 percent variation in visible flame height within the intermittent flame region.  The percentage variation increases at the continuous flame region, although the magnitudes of the height variations are similar to other sections of the intermittent flame region.  The percentage variation is higher in the continuous flame region because the height of the continuous flame region is the smallest.  The 95~\% confidence limits for the polyurethane foam are about twice those of the natural gas and the gasoline.

\section{Summary}

The source fires have been characterized in terms of heat release rate, plume temperature, total heat flux, mass loss and flame height.  This data has been collected for use in direct analysis of the burn patterns and as input into the engineering correlations and FDS models that are used later in this study.

\chapter{Instrumented Calibration (non-combustible) Wall Experiments}

\section{Experimental Arrangement}

\section{Results}

\subsection{Heat Flux Wall Temperatures}

\chapter{Instrumented Gypsum Board Wall Experiments}

\section{Characterization of Gypsum Board}

\section{Cone Calorimeter Experiments}

\bibliography{example-thesis}
\end{document}

### 2015-03-07 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: update directory structure
Madrzy_Thesis: minor formatting updates

--- 2015-03-06 Projects/Madrzykowski_Thesis/Madrzykowski_Thesis.tex
@@
 \usepackage{graphicx}
+\frenchspacing
 
@@
 
-\abstract{%
+\abstract{
 Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.
@@
 The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
-The comparison of the fire pattern heights and the mean flame height demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+The comparison of the fire pattern heights and the mean flame height demonstrated that the ``'steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
 
@@
 
-\acknowledgments{%
+\acknowledgments{
 I would like to thank Prof.~Fleishmann, etc.
@@
 Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.
-Findings from an archeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years.[1]  This is 300 thousand years earlier than previously thought.
+Findings from an archaeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years.[1]  This is 300 thousand years earlier than previously thought.
 Despite mankind’s extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries.[2]  Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 populations.
@@
 One of the basic methods of documenting the fire scene is to photograph fire patterns.
-As noted by Icove, DeHaan, and Haynes  “the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…”.
+As noted by Icove, DeHaan, and Haynes  ``'the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…''.
 [13]  A fire pattern is defined in NFPA 921 as, “the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects” [921].
@@
 Lentini points out that most fire patterns are generated and later observed on two-dimensional surfaces at the place where those surfaces intersect with the three-dimensional fire.
-Various [14] types of fire patterns, such as; “V-shaped”, “hour-glass”, and “inverted cone”, have come from common observation at actual fire scenes.
+Various [14] types of fire patterns, such as; ``V-shaped'', ``hour-glass'', and ``inverted cone'', have come from common observation at actual fire scenes.
 As a result, the observations are typically qualitative in nature.
+
 Previous fire pattern research by the National Institute of Justice (NIJ), the National Institute of Standards and Technology (NIST), and the United States Fire Administration (USFA) has shown that fire patterns provide data useful for the determination of fire origin.
@@
 
-Of the active field models, FDS version 6 has one of the most rigorous and publically accessible verification and validation programs.[22] In the current FDS validation guide more than 45 experimental data sets are used to quantify the prediction capabilities of the model.
+Of the active field models, FDS version 6 has one of the most rigorous and publicly accessible verification and validation programs.[22] In the current FDS validation guide more than 45 experimental data sets are used to quantify the prediction capabilities of the model.
 Results are presented in terms of model bias and variation to inform users of whether particular quantities (temperature, heat flux, pressure, etc.) are over or under predicted compared to experimental data.
@@
 This idea was discussed when the Fire Protection Research Foundation convened a Research Advisory Council on Post-fire Analysis in 2002.
-Recommendations for research and development in their white paper included, “advance the capabilities of computational fluid dynamics fire modeling, particularly as applied to fire ignition scenarios and fire pattern development and interpretation”  [23]
+Recommendations for research and development in their white paper included, ``advance the capabilities of computational fluid dynamics fire modeling, particularly as applied to fire ignition scenarios and fire pattern development and interpretation.''  [23]
 
@@
 The first edition of NFPA 921 was issued in 1992.
-As provided by the document scope, it “… is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.”     The document’s purpose includes the goal to be “…a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.” [8] However, NFPA 921 can only incorporate the fire science and research results that have been produced.
-Although NFPA 921 is a “guide” as opposed to a “standard” is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
+As provided by the document scope, it `` is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.'' The document’s purpose includes the goal to be ``…a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.'' [8] However, NFPA 921 can only incorporate the fire science and research results that have been produced.
+Although NFPA 921 is a ``guide'' as opposed to a ``standard'' is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
 
@@
 Both fires occurred prior to the release of NFPA 921 in 1992.
-The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases “did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.”  The fire investigators had a poor understanding of science and their findings of arson could not be sustained.[24]
+The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained.[24]
+
 Another landmark document regarding the state of forensic science in the United States was published in 2009.
@@
 The review of the analysis of explosives evidence and fire debris is covered in three pages of the report.
-The summary assessment of analysis of explosives evidence is positive, “the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry .”[25]  The complete summary assessment for fire debris analysis is included here: “By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
+The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry .''[25]  The complete summary assessment for fire debris analysis is included here: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
 Despite the paucity of research, some arson investigators continue to make determinations about whether or not a particular fire was set.
 However, according to testimony presented to the committee, many of the rules of thumb, that were typically assumed to indicate that an accelerant was used (e.g.
-“alligatoring” of wood, specific char patterns) have been shown not to be true.
-Experiments should be designed to put arson investigations on a more solid scientific footing .” [25]
+``alligatoring'' of wood, specific char patterns) have been shown not to be true.
+Experiments should be designed to put arson investigations on a more solid scientific footing .'' [25]
 This study is in response to the assessment above, specifically regarding the natural variability of fire patterns.
@@
 
-Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard, which is 2.4 m in height.
-Given the upper bound of 2.4 m, the experiments will use small fires with mean flame heights of approximately 1.2 m.
+Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard, which is 2.4~m in height.
+Given the upper bound of 2.4~m, the experiments will use small fires with mean flame heights of approximately 1.2~m.
 The resulting patterns on the gypsum board wall would be representative of a pre-flashover fire pattern.
@@
 Videos were recorded for each experiment.
-This “field” data from the videos was  used to determine the flame heights.
+This ``field'' data from the videos was  used to determine the flame heights.
 Experiments were conducted with three different fuel types: a gas fueled mass flow controlled burner, a liquid fueled burner, and a solid fuel.
@@
 Comparative experiments were conducted to examine the impact of the method of construction and support of the walls and corner sections on the development of the burn patterns.
-Three cases were examined: 1) 12.7 mm thick, regular core, painted gypsum board on the front of a wall frame (open back), 2) 12.7 mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall), and 3) 12.7 mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
+Three cases were examined: 1) 12.7~mm thick, regular core, painted gypsum board on the front of a wall frame (open back), 2) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall), and 3) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
 The main consideration was to identify any differences in the height, width, shape, and area of the fire patterns.
@@
 
-Each of the test compartments consisted of three 3.6 m long by 2.4 m high wood framed walls.
+Each of the test compartments consisted of three 3.6~m long by 2.4~m high wood framed walls.
 A partial ceiling was installed over the wall.
@@
 Several types of bench scale experiments were conducted to generate data. This data could be used to assist in the analysis of the fire patterns and potentially be used as input for the FDS models.
-Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a “critical heat flux” that results in a clear line of demarcation, a “burn/no burn” line.
+Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a “critical heat flux” that results in a clear line of demarcation, a ``burn/no burn'' line.
 The flooring radiant panel (ASTM E648) was used to examine this value.
@@
 
-Cone calorimeter (ASTM 1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25 kW/m2 to 75 kW/m2.
+Cone calorimeter (ASTM 1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
 
@@
 A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover or incipient fires.
-A fixed fire source footprint, 30.5 cm square, was chosen for this study and a range of common fuels was selected.
+A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels was selected.
 The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.
 Heat release rate, flame/plume gas temperatures, and total heat flux from the flames were measured and flame movement and height were recorded with photographs and videos.
-Given the focus on residential fires, small source fires were selected so that the burn pattern would be limited to less than 2.4 m in height.
+Given the focus on residential fires, small source fires were selected so that the burn pattern would be limited to less than 2.4~m in height.
 Replicate experiments were conducted with each of the fuels, in order to examine the repeatability of the fires and to quantify the variability in the flames.
@@
 
-The natural gas burner was 30.5 cm on a side and the top surface of the burner was 7.5 cm above the floor.
-The shell of the burner was made from steel and filled with “pea sized” gravel with an average diameter of 6 mm.
+The natural gas burner was 30.5 cm on a side and the top surface of the burner was 7.5~cm above the floor.
+The shell of the burner was made from steel and filled with “pea sized” gravel with an average diameter of 6~mm.
 A steady state heat release rate of approximately 80 kW was used for the experiments.
@@
 The gasoline pan fire used 500 mL of unleaded, 87 octane gasoline.
-The pan was constructed from 6 mm thick steel.
-The inner dimension of the pan was 30.5 cm on a side and 1.9 cm high.
-The pan was elevated in order to bring the pan lip height up to 7.5 cm above the floor to be the same height as the natural gas burner.
-The 500 mL of gasoline had a fuel depth of 5.5 mm and provided a burn time of approximately 300 s.
+The pan was constructed from 6~mm thick steel.
+The inner dimension of the pan was 30.5 cm on a side and 1.9~cm high.
+The pan was elevated in order to bring the pan lip height up to 7.5~cm above the floor to be the same height as the natural gas burner.
+The 500~mL of gasoline had a fuel depth of 5.5~mm and provided a burn time of approximately 300~s.
 
@@
 
-The flexible polyurethane foam had a density of approximately 23 kg/m3.
-Each block of foam was 30.5 cm on a side and was 7.5 cm thick.
+The flexible polyurethane foam had a density of approximately 23~kg/m$^3$.
+Each block of foam was 30.5~cm on a side and was 7.5~cm thick.
 The bottom and sides of the foam block were wrapped in aluminum foil to prevent the fuel from flowing or spreading as it burned to ensure that the fuel area remained with the same fixed area as the gasoline and natural gas.
@@
 
-The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3 m by 3 m hood oxygen consumption calorimeter.
+The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3~m by 3~m hood oxygen consumption calorimeter.
 This apparatus follows the methodology of ASTM E 2067-08, Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests.[37]  The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
 A load cell was positioned as a support for the fuels.
-All of the data was recorded at intervals of 1 s on a computer based data acquisition system.
+All of the data was recorded at intervals of 1~s on a computer based data acquisition system.
 
@@
 
-The NIST Large Fire Research Laboratory’s 3 m by 3 m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700 kW.
-Details on the operation and uncertainty in measurements associated with NIST’s 6 m by 6 m oxygen consumption calorimeter were documented by Bryant et.al.
+The NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700~kW.
+Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.
 [38] Many of the same instruments are shared between the two calorimeters and calibration burns were conducted during each experimental series.
@@
 
-Gas temperatures were measured with exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm nominal diameter.
-Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2 mm diameter inconel shield, 0.76 m in length.
+Gas temperatures were measured with exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter.
+Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2 mm diameter inconel shield, 0.76~m in length.
 The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer [39]  The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.[40, 41]  Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
@@
 Water cooled, Schmidt-Boelter total heat flux gauges were used to measure the heat flux.
-The sensing surface of the heat flux gauges were located 0.95 m horizontally from the center of the burner/fuel and 0.50 m above the top of the burner/pan lip/fuel surface.
+The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
 The manufacturer reports a 3~\% calibration expanded uncertainty for these devices 20.[42] Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically 8~\%.[43]  The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
@@
 
-The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91 m x 1.2 m x 12 mm thick supported by the load cell.
-The load cell had a resolution of 1.0 g.[44] The expanded uncertainty is estimated to be 5~\%.
+The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91~m x 1.2~m x 12~mm thick supported by the load cell.
+The load cell had a resolution of 1.0~g.[44] The expanded uncertainty is estimated to be 5~\%.
 The load cell was checked between experiments with calibrated weights during the zero and span checks of the calorimeter.
@@
 
-A 35 mm single lens reflex camera was used to record digital still photographs of the fires.
+A 35~mm single lens reflex camera was used to record digital still photographs of the fires.
 The camera had an 8 megapixel resolution.
@@
 A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.
-Each camera was positioned on a tripod with a distance of 4.5 m between the centerline of burner to camera lens 4.5 m.
+Each camera was positioned on a tripod with a distance of 4.5 m between the centerline of burner to camera lens 4.5~m.
 The height of each camera was adjusted so that the center of camera lens was positioned 0.5 m above top of the burner.
@@
 The thermocouples were mounted on a steel frame.
-The frame enabled the thermocouples to be installed at 10 cm intervals from 10 cm to 120 cm above the burner/pan lip/fuel surface.
-At each 10 cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.
-A plumb bob and steel tape measure, with a resolution of $\pm$ 0.5 mm, were used to position and align the thermocouples.
+The frame enabled the thermocouples to be installed at 10~cm intervals from 10~cm to 120~cm above the burner/pan lip/fuel surface.
+At each 10~cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.
+A plumb bob and steel tape measure, with a resolution of $\pm$ 0.5~mm, were used to position and align the thermocouples.
 The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$ 2.5~\%.
@@
   \centering
-  \includegraphics[width=\textwidth]{Schematic_Drawing}\\
+  \includegraphics[width=\textwidth]{../Figures/Schematic_Drawing}\\
   \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus which was centered under the 3~m by 3~m oxygen consumption calorimeter.
@@
   \centering
-  \includegraphics[width=\textwidth]{Source_Fire_Flamer}\\
+  \includegraphics[width=\textwidth]{../Figures/Source_Fire_Flamer}\\
   \caption[A photograph of the source fire flamer and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.
@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of approximately 80 kW $\pm$ 9 kW with an average total heat release of approximately 23.3 MJ $\pm$ 1.6 MJ over a 300 s period.
-The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of approximately 80 kW $\pm$ 24 kW.
-The total heat release of the gasoline over the 300 s period after ignition was approximately 13.6 MJ $\pm$ 0.6 MJ.
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of approximately 80~kW $\pm$ 9~kW with an average total heat release of approximately 23.3~MJ $\pm$ 1.6~MJ over a 300~s period.
+The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of approximately 80~kW $\pm$ 24~kW.
+The total heat release of the gasoline over the 300~s period after ignition was approximately 13.6~MJ $\pm$ 0.6~MJ.
 The polyurethane foam demonstrated the largest variability, as shown in Figure 5, of the three fuels in terms of peak heat release rate and time to peak heat release.
-Averaging over a 15 s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of approximately 45 kW $\pm$ 21 kW.
-The total heat release over the 300 s period after ignition was of 4.1$\pm$ 0.2MJ
+Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of approximately 45~kW $\pm$ 21~kW.
+The total heat release over the 300~s period after ignition was of 4.1~MJ $\pm$ 0.2~MJ
 
@@
 Plots of the centerline temperatures averaged over the replicate experiments for each of the fuels are presented in Figures 6 through 8.
-The number following “TC” in the legend of the graphs represents the height of the thermocouple in increments of 10 cm (or dm) above the fuel surface.
-The natural gas temperatures were averaged over a “steady-state” burning period as reflected by the data in Figure 6.
+The number following “TC” in the legend of the graphs represents the height of the thermocouple in increments of 10~cm (or dm) above the fuel surface.
+The natural gas temperatures were averaged over a ``steady-state'' burning period as reflected by the data in Figure 6.
 The temperature differences between the vertical thermocouple locations, for locations greater than 20 cm above the fire location, begin to decrease as the distances from the top of the burner increase.
@@
 The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that has periods of growth and decay.
-The sensing surface of the heat flux gauges were located 0.95 m horizontally from the center of the burner/fuel and 0.50 m above the top of the burner/pan lip/fuel surface.
-The average peak total heat flux for the natural gas fires were approximately 2.0 kW/m2, as shown in the example data set in Figure 9.
-The average peak values for the gasoline and polyurethane foam were approximately 3.5 kW/m2 and 2.5 kW/m2 respectively.
+The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
+The average peak total heat flux for the natural gas fires were approximately 2.0~kW/m$^2$, as shown in the example data set in Figure 9.
+The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$ respectively.
 The values are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.
@@
 The mass loss versus time curves for the gasoline and the polyurethane experiments are shown in Figures 12 and 13.
-The gasoline exhibits a linear mass loss rate for the initial 150 s of approximately 0.12 kg per minute.
+The gasoline exhibits a linear mass loss rate for the initial 150~s of approximately 0.12~kg per minute.
 The polyurethane foam was ignited with a small flame in the center of the top surface of the foam block.
 As the flame spread across the surface it also began to burn down into the foam sample.
-As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 0.12 kg per minute.
+As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 0.12~kg per minute.
 
@@
 
-In engineering terms, the “flame height” is typically discussed as the median flame height.
+In engineering terms, the ``flame height'' is typically discussed as the median flame height.
 A position above the top of the fuel surface where the flame is observed to be present at least 50~\% of the time.
@@
 Examples of the photographic images are presented in Figures 14 and 15.
-Figure 14 is a photograph of the natural gas flame taken during a period of “steady state” burning at approximately 80 kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60 kW.
-Figure 9 presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100 kW.
-The two photographs, taken 0.2 s apart, represent the range of the observed flame heights from one of the gasoline experiments from 0.65 m and 1.0 m, respectively.
+Figure 14 is a photograph of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
+Figure 9 presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100~kW.
+The two photographs, taken 0.2~s apart, represent the range of the observed flame heights from one of the gasoline experiments from 0.65~m and 1.0~m, respectively.
 
-Table 1 provides the mean visible flame height, as well as the range of flame heights for each fuel, based on analysis of the photographs for three replicate experiments.
+Table~\ref{tab:Flame_Heights} provides the mean visible flame height, as well as the range of flame heights for each fuel, based on analysis of the photographs for three replicate experiments.
 In each case, the photographs were chosen for analysis while the fire was generating its peak heat release rate.
@@
 As noted by Beyler in his review of fire plume correlations, video tape analysis seems to provide the best estimates of flame height.
-[46]  Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97 fps which is the National Television Standards Committee (NTSC) standard.
+[46]  Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps which is the National Television Standards Committee (NTSC) standard.
 The resulting image in each frame was 720 pixels wide by 480 pixels high.
@@
 
-For the natural gas experiments, approximately 30 s of “steady state” video were captured.
+For the natural gas experiments, approximately 30~s of ``steady state'' video were captured.
 In the cases of the gasoline and polyurethane fueled experiments, the video capture period bounded the peak heat release rate.
 In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30 s video capture could be made which was representative of the peak burning rate.
-The peak duration for the polyurethane foam fires was shorter so, only a 15 s video capture was used.
+The peak duration for the polyurethane foam fires was shorter so, only a 15~s video capture was used.
 
@@
   \caption[Mean visible flame height and averaged minimums and maximums]{Mean visible flame height and averaged minimums and maximums (Range) of visible flame heights for each of the fuels during peak heat release rate.}
-  \label{Flame_Heights}
+  \label{tab:Flame_Heights}
 \end{table}
@@
 Each figure has 56 sequential images from the video segment.
-The images total almost 2 seconds of actual burn time.
+The images total almost 2~s of actual burn time.
 Notice how the flame height cycles up and down in each of the sequences.
@@
 The polyurethane foam experiments had approximately 450 images in each sequence for each experiment.
-Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble.[47]  Once all of the images were converted to a pure red “flame” which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being “overlaid” on each other.
+Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble.[47]  Once all of the images were converted to a pure red ``flame'' which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being ``overlaid'' on each other.
 The end result is a contour plot of the intermittency of the flame ranging from zero to one.
@@
 The calculations for the intensity field are based on a user defined computation grid.
-A grid sensitivity analysis was conducted with 5 mm, 10 mm, 20 mm, 40 mm and 80mm square grids.
+A grid sensitivity analysis was conducted with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm square grids.
 Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Figure 19.
@@
 
-Since each pixel in the original images was equal to 5 mm, in the highest resolution case, the 5 mm analysis grid would match the best resolution of the original image.
-Four of the five cases resulted in similar results, only the 80 mm case generated significantly different results in flame height.
-As a result of the sensitivity analysis, a 10 mm grid was chosen as an optimum size for providing a sufficient level of resolution, enabling efficient processing of 30 s worth of video frames.
-At the 5 mm grid resolution, limitations within the processing system would not allow a full 30 s of video analysis.
-Therefore the intensity fields and the resulting plots and data generated for this study were developed with a 10 mm grid.
+Since each pixel in the original images was equal to 5~mm, in the highest resolution case, the 5~mm analysis grid would match the best resolution of the original image.
+Four of the five cases resulted in similar results, only the 80~mm case generated significantly different results in flame height.
+As a result of the sensitivity analysis, a 10~mm grid was chosen as an optimum size for providing a sufficient level of resolution, enabling efficient processing of 30~s worth of video frames.
+At the 5~mm grid resolution, limitations within the processing system would not allow a full 30~s of video analysis.
+Therefore the intensity fields and the resulting plots and data generated for this study were developed with a 10~mm grid.
 
@@
 Figure 20 provides an example of a natural gas experiment.
-The region under examination, as shown as a black bounding rectangle, is 1400 mm high and 800 mm in width.
-This example was averaged over approximately 29 s or approximately 870 images.
+The region under examination, as shown as a black bounding rectangle, is 1400~mm high and 800 mm in width.
+This example was averaged over approximately 29~s or approximately 870 images.
 The number above each contour line in the plot range from 0 to 1.
@@
 The polyurethane foam has a more complicated flame spread sequence that resulted in significant changes to the peak heat release rate and the time to peak heat release.
-Once the polyurethane foam was ignited, it took approximately 60 s for the flame to spread across the top surface of the fuel.
+Once the polyurethane foam was ignited, it took approximately 60~s for the flame to spread across the top surface of the fuel.
 As the flames spread horizontally across the fuel surface, the fire also burns down into the fuel.
@@
 Based on the field data developed using Streams average flame heights for each fuel were determined.
-In Table 2, each of the values represents the average flame heights, given in mm with 95~\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
-For the natural gas fires, the averages are from ten 30 s segments, while the fire was monitored at approximately 80 kW.
+In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in mm with 95~\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
+For the natural gas fires, the averages are from ten 30 s segments, while the fire was monitored at approximately 80~kW.
 In some cases more than one 30 s segment was sampled per heat release rate experiment.
-Sixteen 30 second video segments, which included the peak heat release rate, were successfully analyzed from the seventeen gasoline heat release rate experiments.
+Sixteen 30~s video segments, which included the peak heat release rate, were successfully analyzed from the seventeen gasoline heat release rate experiments.
 One of the videos was unusable for analysis due to reflected light which could not be edited out of the images.
@@
  \caption[Average flame heights for three fuels]{Average flame heights with 95~\% confidence limits, for each of the source fuels shown as the percentage of time the flame was visible at that given height.}
- \label{Average_Flame_Heights}
+ \label{tab:Average_Flame_Heights}
 \end{table}

### 2015-03-07 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add .bib file for Madrzykowski thesis.

@@
 \begin{document}
+
+\bibliographystyle{unsrt}
 
@@
 Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.
-Findings from an archaeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years.[1]  This is 300 thousand years earlier than previously thought.
-Despite mankind’s extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries.[2]  Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 populations.
+Findings from an archaeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
+This is 300 thousand years earlier than previously thought.
+Despite mankind’s extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries~\cite{WHO:2014}.
+Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 populations.
 The World Fire Statistics Center collects data from European, North American and a few Asia-Oceania countries.
-Within this group of countries the fire deaths per 100,000 population range from 0.02 (Singapore) to 2.03 (Finland).
-[3] There are a significant number of factors that determine the variability of fire death rates between nations, socio- economic conditions being a leading factor.[2]
+Within this group of countries the fire deaths per 100,000 population range from 0.02 (Singapore) to 2.03 (Finland)~\cite{Climate:2014}.
+There are a significant number of factors that determine the variability of fire death rates between nations, socio-economic conditions being a leading factor~\cite{WHO:2014}.
 
@@
 The estimated number of fire deaths in the U.S.
-in 1975 was 8,100 or 3.75 deaths per 100,000 population.[4]  In 2013, there were 3,240 civilian fire fatalities or 1.02 deaths per 100,000 population.[5]  During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.
+in 1975 was 8,100 or 3.75 deaths per 100,000 population~\cite{America_Burning_Revisited}.
+In 2013, there were 3,240 civilian fire fatalities or 1.02 deaths per 100,000 population~\cite{Karter:2014}.
+During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.
 There are many reasons that led to this decrease in loss of life due to fire in the United States.
 An example would be research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs to name just a few.
-None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response.[6]
+None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FIVE}.
 
@@
 In some cases, the fire investigation determines that the fire was intentional.
-An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention.[7]  An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA 921, is “a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be.”[8]
+An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention~\cite{Campbell:2014}.
+An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be.''~\cite{NFPA_921}.
 
@@
 Approximately two-thirds of the structure fires occurred in residential occupancies.
-95~\% of the civilian deaths and 86~\% of the civilian injuries also occurred in the intentional fires in residential occupancies.
-[7]
+95~\% of the civilian deaths and 86~\% of the civilian injuries also occurred in the intentional fires in residential occupancies~\cite{Campbell:2014}.
 
@@
 Arson as defined by the U.S.
-Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.[9]
+Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime}.
 
 The national rate of arson fire cases cleared by arrest or exceptional means is less than 20~\%.
-Of those cases approximately 46~\% of the suspects were prosecuted.[7] Arson is a challenging crime to solve because typically there are no witnesses present at the time of the crime.
+Of those cases approximately 46~\% of the suspects were prosecuted~\cite{Campbell:2014}.
+Arson is a challenging crime to solve because typically there are no witnesses present at the time of the crime.
 
 Fires are investigated in order to determine the ``origin and cause'' of the fire and in cases of arson there is an effort to determine who was responsible for setting the fire.
-This investigation process must follow the scientific method as documented in NFPA 921 [8].
-There are numerous textbooks on the subject of conducting a fire investigation [10-15].
+This investigation process must follow the scientific method as documented in NFPA 921~\cite{NFPA_921}.
+There are numerous textbooks on the subject of conducting a fire investigation~\cite{Almirall:2004,Fire_Investigation,DeHaan:2012,Icove:2013,Lentinin:2006,Noon:1995}.
 The NFPA guide and the texts provide information to a fire investigator collecting data from the scene, analyzing the data, and developing a hypothesis about the fire.
@@
 
-\bibliography{example-thesis}
+\bibliography{../References/Madrzykowski_Thesis}
 \end{document}

### 2015-03-08 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Editing of references.

@@
 Arson as defined by the U.S.
-Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime}.
+Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime:2010}.
 
@@
 This investigation process must follow the scientific method as documented in NFPA 921~\cite{NFPA_921}.
-There are numerous textbooks on the subject of conducting a fire investigation~\cite{Almirall:2004,Fire_Investigation,DeHaan:2012,Icove:2013,Lentinin:2006,Noon:1995}.
+There are numerous textbooks on the subject of conducting a fire investigation~\cite{Almirall:2004,Fire_Investigation,DeHaan:2012,Icove:2013,Lentini:2006,Noon:1995}.
 The NFPA guide and the texts provide information to a fire investigator collecting data from the scene, analyzing the data, and developing a hypothesis about the fire.
@@
 One of the basic methods of documenting the fire scene is to photograph fire patterns.
-As noted by Icove, DeHaan, and Haynes  ``'the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…''.
-[13]  A fire pattern is defined in NFPA 921 as, “the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects” [921].
-DeHaan [12] categorizes the fire effects that form patterns as follows:
+As noted by Icove, DeHaan, and Haynes  ``'the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…''~\cite{Icove:2013}.
+A fire pattern is defined in NFPA~921 as, ``the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects''~\cite{NFPA_921}.
+
+DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
 \begin{enumerate}
-\item Surface deposits – no irreversible effect on surface
-\item Surface thermal effects – physical change such a discoloration or melting
-\item Charring –evidence of surface burning
-\item Penetration – charring below the surface
-\item Consumption –loss of surface material, charring throughout
+\item Surface deposits -– no irreversible effect on surface
+\item Surface thermal effects –- physical change such a discoloration or melting
+\item Charring -– evidence of surface burning
+\item Penetration -– charring below the surface
+\item Consumption –- loss of surface material, charring throughout
 \end{enumerate}
 Lentini points out that most fire patterns are generated and later observed on two-dimensional surfaces at the place where those surfaces intersect with the three-dimensional fire.
-Various [14] types of fire patterns, such as; ``V-shaped'', ``hour-glass'', and ``inverted cone'', have come from common observation at actual fire scenes.
+Various types of fire patterns, such as; ``V-shaped'', ``hour-glass'', and ``inverted cone'', have come from common observation at actual fire scenes~\cite{Lentini:2006}.
 As a result, the observations are typically qualitative in nature.
@@
 Previous fire pattern research by the National Institute of Justice (NIJ), the National Institute of Standards and Technology (NIST), and the United States Fire Administration (USFA) has shown that fire patterns provide data useful for the determination of fire origin.
-The reports noted the impact of ventilation on the development of the burn patterns.
-[16, 17] A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s) and compartmentation, to name a few.
+The reports noted the impact of ventilation on the development of the burn patterns~\cite{Shanley:1997,Putorti:1997}.
+A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s) and compartmentalization, to name a few.
 Given the limited number of experiments in the literature and the large number of variables, it has been difficult to fully understand a cause and effect relationship between the fire scenarios and the resulting patterns.
-Therefore, fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause.[18]  Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
+Therefore, fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula}.
+Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
 A collection of the widely used correlations can be found in the U.S.
 Nuclear Regulatory Commission’s (NRC) Fire Dynamics Tools (FDTs).
-FDTs incorporates references to the source documents and experimental work upon which the correlations are based.
+These spread sheets incorporate references to the source documents and experimental work upon which the correlations are based.
 In addition, NRC tasked NIST with conducting a verification and validation study of the correlations.
-Overholt developed the NIST verification and validation study.[19] In a private communication, Overholt noted that not all of the correlations in FDTs were included in the study since a sufficient amount of reliable data in the literature to not available to conduct validation.
-Two of the types of correlations, which could not be validated, were flame height and time to ignition.[19]
+Overholt developed the NIST verification and validation study~\cite{Overholt:2014}.
+Not all of the correlations in the FDTs were included in the study because an insufficient amount of reliable data is available to conduct validation.
+Two correlations that could not be validated were for flame height and time to ignition.
 
-A survey of zone and field fire models was compiled and is posted on www.firemodelsurvey.com.[20] The survey was updated in 2014, but it includes models that were documented in the first fire model survey conducted in 1992.
-As a result many of the models are listed for historical purposes only.
-There are 53 zone models listed.
-Only 3 of the 53 are being actively supported or maintained.
-The survey also includes 22 field models.
-10 of the 22 field models are listed as being actively supported.
-All of the correlations and models have been to some extent been validated or checked against experimental data for a limited set of scenarios.
-[21]
+In 2003, a list of zone and computational fluid dynamics (CFD) fire models was compiled by Olenick and Carpenter~\cite{Olenick:2003}.
+A similar survey was conducted in 1992, and Olenick has updated the list in 2014.
+There are 53 zone models listed, but only three are actively supported or maintained.
+The survey also includes 22 field models of which 10 are listed as being actively supported.
+All of the correlations and models have been to some extent been validated or checked against experimental data for a limited set of scenarios~\cite{ASTM_E1355}.
 
-Of the active field models, FDS version 6 has one of the most rigorous and publicly accessible verification and validation programs.[22] In the current FDS validation guide more than 45 experimental data sets are used to quantify the prediction capabilities of the model.
+Of the active field models, FDS version 6 has one of the most rigorous and publicly accessible verification and validation programs~\cite{McGrattan:2014}.
+More than 45 experimental data sets are used to quantify the prediction capabilities of the model.
 Results are presented in terms of model bias and variation to inform users of whether particular quantities (temperature, heat flux, pressure, etc.) are over or under predicted compared to experimental data.
@@
 This idea was discussed when the Fire Protection Research Foundation convened a Research Advisory Council on Post-fire Analysis in 2002.
-Recommendations for research and development in their white paper included, ``advance the capabilities of computational fluid dynamics fire modeling, particularly as applied to fire ignition scenarios and fire pattern development and interpretation.''  [23]
+Recommendations for research and development in their white paper included, ``advance the capabilities of computational fluid dynamics fire modeling, particularly as applied to fire ignition scenarios and fire pattern development and interpretation''~\cite{RAC:2002}.
 
-It has been pointed out in this introduction that fire is still a threat to life and property and how fire investigation plays a role in preventing future fires.
 Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount or research and analysis tools directly related to this practice.
 The fire investigation community recognized a need to improve the science and practice of fire investigation.
-One of the manifestations of the efforts to improve the practice was the development of NFPA 921, Guide for Fire and Explosion Investigations.
-The first edition of NFPA 921 was issued in 1992.
-As provided by the document scope, it `` is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.'' The document’s purpose includes the goal to be ``…a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.'' [8] However, NFPA 921 can only incorporate the fire science and research results that have been produced.
-Although NFPA 921 is a ``guide'' as opposed to a ``standard'' is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
+One of the manifestations of the efforts to improve the practice was the development of NFPA~921, {\em Guide for Fire and Explosion Investigations}~\cite{NFPA_921}.
+The first edition of NFPA~921 was issued in 1992.
+As provided by the document scope, it ``is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.'' The document’s purpose includes the goal to be ``a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.'' However, NFPA~921 can only incorporate the fire science and research results that have been produced.
+Although NFPA~921 is a ``guide'' as opposed to a ``standard,'' it is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
 
@@
 Beyler conducted a review of both cases for the Texas Forensic Science Commission.
-Both fires occurred prior to the release of NFPA 921 in 1992.
-The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained.[24]
+Both fires occurred prior to the release of NFPA~921 in 1992.
+The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained~\cite{Beyler:2009}.
 
 Another landmark document regarding the state of forensic science in the United States was published in 2009.
-The 328 page report, titled Strengthening Forensic Science in the United States: A Path Forward, by the U.S.
-National Academy of Sciences, reviewed 13 different forensic science disciplines including; biological evidence, friction ridge patterns, tool mark and firearms identification, and analysis of explosives evidence and fire debris, to name a few.
+The 328 page report, entitled {\em Strengthening Forensic Science in the United States: A Path Forward}, by the U.S.~National Academy of Sciences, reviewed 13 different forensic science disciplines including biological evidence, friction ridge patterns, tool mark and firearms identification, and analysis of explosives evidence and fire debris.
 The review of the analysis of explosives evidence and fire debris is covered in three pages of the report.
-The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry .''[25]  The complete summary assessment for fire debris analysis is included here: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
+The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry ''~\cite{Forensic:2009}.
+The complete summary assessment for fire debris analysis is included here: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
 Despite the paucity of research, some arson investigators continue to make determinations about whether or not a particular fire was set.
@@
 ``alligatoring'' of wood, specific char patterns) have been shown not to be true.
-Experiments should be designed to put arson investigations on a more solid scientific footing .'' [25]
+Experiments should be designed to put arson investigations on a more solid scientific footing .''
 This study is in response to the assessment above, specifically regarding the natural variability of fire patterns.
@@
 Well-documented and characterized technologies such as thermocouples and heat flux gauges were used to assess the fire and the thermal exposure of the target material.
-Oxygen consumption calorimetry and mass loss was used for the determining the heat release rate of the fires.
+Oxygen consumption calorimetry and mass loss measurements were used for the determining the heat release rate of the fires.
 
@@
 Several methods of imaging were used for these experiments: still photography, digital video, and infrared video.
-Computer based imaging techniques, such as those contained in the Image Stream program suite, were examined and adapted to analyze the flame height of the source fires [26].
+Computer based imaging techniques, such as those contained in the Image Stream program suite, were examined and adapted to analyze the flame height of the source fires~\cite{Nokes:2011}.
 
@@
 Experiments were conducted with three different fuel types: a gas fueled mass flow controlled burner, a liquid fueled burner, and a solid fuel.
-Instrumented Calibration Target Wall – A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+
+\subsubsection{Instrumented Calibration Target Wall}
+
+A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 The fires were initially placed at predetermined, fixed positions away from the wall.
@@
 Comparative experiments were conducted to examine the impact of the method of construction and support of the walls and corner sections on the development of the burn patterns.
-Three cases were examined: 1) 12.7~mm thick, regular core, painted gypsum board on the front of a wall frame (open back), 2) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall), and 3) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
+Three cases were examined: (1) 12.7~mm thick, regular core, painted gypsum board on the front of a wall frame (open back); (2) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall); and {3) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
 The main consideration was to identify any differences in the height, width, shape, and area of the fire patterns.
@@
 Several types of bench scale experiments were conducted to generate data. This data could be used to assist in the analysis of the fire patterns and potentially be used as input for the FDS models.
-Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a “critical heat flux” that results in a clear line of demarcation, a ``burn/no burn'' line.
-The flooring radiant panel (ASTM E648) was used to examine this value.
+Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
+The flooring radiant panel (ASTM~E648) was used to examine this value.
 
@@
 
-Cone calorimeter (ASTM 1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
+Cone calorimeter (ASTM~1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
 

### 2015-03-08 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
More editing of references in Madrzykowski thesis.

@@
 
-Heskestad developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.[27, 28] This correlation was compared with the flame height results of the source fires and the instrumented wall experiments.
+Heskestad developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion~\cite{Beyler:1986,Heskestad:SFPE}.
+This correlation was compared with the flame height results of the source fires and the instrumented wall experiments.
 
-FDS[22] and Smokeview[29] were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
+FDS~\cite{McGrattan:2014} and Smokeview~\cite{Forney:2014} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
 Comparison between the experiments and the model will provide valuable validation data for the model.
@@
 The natural gas burner was 30.5 cm on a side and the top surface of the burner was 7.5~cm above the floor.
-The shell of the burner was made from steel and filled with “pea sized” gravel with an average diameter of 6~mm.
+The shell of the burner was made from steel and filled with ``pea sized'' gravel with an average diameter of 6~mm.
 A steady state heat release rate of approximately 80 kW was used for the experiments.
@@
 In addition the mixtures change from season to season, and vary based on requirements or restrictions of the locality.
-However, fire incident data shows that gasoline was the first item ignited in the majority of intentional fires where flammable or combustible liquids were used 12.[30] In addition, data from forensic laboratories, collected by Babrauskas and others, indicates that gasoline is the most prevalent accelerant found as part of the analysis of fire debris samples 13, 14.[31, 32]
-The gasoline pan fire used 500 mL of unleaded, 87 octane gasoline.
+However, fire incident data shows that gasoline was the first item ignited in the majority of intentional fires where flammable or combustible liquids were used~\cite{Rohr:2001}.
+In addition, data from forensic laboratories, collected by Babrauskas and others, indicates that gasoline is the most prevalent accelerant found as part of the analysis of fire debris samples~\cite{Babrauskas:2003,Chasteen:2010}.
+
+The gasoline pan fire used 500~mL of unleaded, 87 octane gasoline.
 The pan was constructed from 6~mm thick steel.
-The inner dimension of the pan was 30.5 cm on a side and 1.9~cm high.
+The inner dimension of the pan was 30.5~cm on a side and 1.9~cm high.
 The pan was elevated in order to bring the pan lip height up to 7.5~cm above the floor to be the same height as the natural gas burner.
@@
 More than 1.2 billion pounds are produced in the U.S.
-every year 15,16.[33, 34] In studies by Ahrens and Evarts of the NFPA, upholstered furniture and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
-based on averaged data from 2005 through 2009.[35, 36]
+every year~\cite{Foam,Touch}.
+In studies by Ahrens and Evarts of the NFPA, upholstered furniture and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
+based on averaged data from 2005 through 2009~\cite{Ahrens:2011,Evarts:2011}.
 

### 2015-03-08 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
More editing of references, Madrzykowski thesis

@@
 The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3~m by 3~m hood oxygen consumption calorimeter.
-This apparatus follows the methodology of ASTM E 2067-08, Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests.[37]  The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
+This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests}~\cite{ASTM_E2067}.
+The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
 A load cell was positioned as a support for the fuels.
@@
 The NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700~kW.
-Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.
-[38] Many of the same instruments are shared between the two calorimeters and calibration burns were conducted during each experimental series.
+Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
+Many of the same instruments are shared between the two calorimeters and calibration burns were conducted during each experimental series.
 As a result, the expanded uncertainty of this device has been estimated as 11~\% on the measured heat release rate.
@@
 Gas temperatures were measured with exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter.
-Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2 mm diameter inconel shield, 0.76~m in length.
-The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer [39]  The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.[40, 41]  Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
+Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2~mm diameter inconel shield, 0.76~m in length.
+The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer~\cite{Omega}.
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2001}.
+Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
 The estimated combined expanded uncertainty for temperature in these experiments is 15~\%.
@@
 The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
-The manufacturer reports a 3~\% calibration expanded uncertainty for these devices 20.[42] Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically 8~\%.[43]  The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
+The manufacturer reports a 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically 8~\%~\cite{Pitts:2006}.
+The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
 
@@
 The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91~m x 1.2~m x 12~mm thick supported by the load cell.
-The load cell had a resolution of 1.0~g.[44] The expanded uncertainty is estimated to be 5~\%.
+The load cell had a resolution of 1.0~g~\cite{Mettler}.
+The expanded uncertainty is estimated to be 5~\%.
 The load cell was checked between experiments with calibrated weights during the zero and span checks of the calorimeter.
@@
 
-On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level ($2\sigma$), based on Type A evaluation of the uncertainty is provided.[45]  A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
+On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level ($2\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
 In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2σ) would yield a confidence level of approximately 95~\%.
@@
 
-As noted by Beyler in his review of fire plume correlations, video tape analysis seems to provide the best estimates of flame height.
-[46]  Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps which is the National Television Standards Committee (NTSC) standard.
+As noted by Beyler in his review of fire plume correlations, video tape analysis seems to provide the best estimates of flame height~\cite{Beyler:1986}.
+Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps which is the National Television Standards Committee (NTSC) standard.
 The resulting image in each frame was 720 pixels wide by 480 pixels high.
@@
 Each frame from the video clip was saved as a full color Tagged Image File Format (TIFF) file and the pixel aspect ratio was changed from 0.9 to 1, so that each pixel had the same dimension in both the horizontal and vertical directions.
-Once these images were rendered by the video editing program, each image was scaled and cropped to provide input for Streams, a suite of image processing programs developed by Nokes for analyzing fluid flow visualization experiments[26].
-The images were scaled so that one pixel equals 5 mm in height and width.
+Once these images were rendered by the video editing program, each image was scaled and cropped to provide input for Streams, a suite of image processing programs developed by Nokes for analyzing fluid flow visualization experiments~\cite{Nokes:2011}.
+The images were scaled so that one pixel equals 5~mm in height and width.
 
@@
 The polyurethane foam experiments had approximately 450 images in each sequence for each experiment.
-Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble.[47]  Once all of the images were converted to a pure red ``flame'' which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being ``overlaid'' on each other.
+Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble~\cite{Goble:2007}.
+Once all of the images were converted to a pure red ``flame'' which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being ``overlaid'' on each other.
 The end result is a contour plot of the intermittency of the flame ranging from zero to one.
@@
 The number above each contour line in the plot range from 0 to 1.
-The area bounded by the contour with the value 1 represents the area that the flame occupied 100~\% of the time period analyzed or the persistent flame region as defined by McCaffery.
-[48] The remaining contours are in the intermittent flame region, with the 0.5 contour representing the mean flame height.
+The area bounded by the contour with the value 1 represents the area that the flame occupied 100~\% of the time period analyzed or the persistent flame region as defined by McCaffrey~\cite{McCaffrey:1979}.
+The remaining contours are in the intermittent flame region, with the 0.5 contour representing the mean flame height.
 Outside of the final contour, value 0.0, no visible flame was recorded; hence this contour marks the definitive start of the buoyant plume region.

### 2015-03-08 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add figures to Madrzykowski thesis.

@@
 
-Figures 3 through 5 are graphs showing measurement results of heat release rate versus time for the natural gas, gasoline and polyurethane foam fueled fires.
+Figure~\ref{HRR} shows the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires.
 In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/Fig3}\\
+  \includegraphics[width=4.5in]{../Figures/Fig4}\\
+  \includegraphics[width=4.5in]{../Figures/Fig5}\\
+  \caption[Heat release rates for the natural gas, gasoline and foam fires]{Heat release rates for the natural gas, gasoline, and foam fires.}
+  \label{HRR}
+\end{figure}
 
@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of approximately 80~kW $\pm$ 9~kW with an average total heat release of approximately 23.3~MJ $\pm$ 1.6~MJ over a 300~s period.
-The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of approximately 80~kW $\pm$ 24~kW.
-The total heat release of the gasoline over the 300~s period after ignition was approximately 13.6~MJ $\pm$ 0.6~MJ.
-The polyurethane foam demonstrated the largest variability, as shown in Figure 5, of the three fuels in terms of peak heat release rate and time to peak heat release.
-Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of approximately 45~kW $\pm$ 21~kW.
-The total heat release over the 300~s period after ignition was of 4.1~MJ $\pm$ 0.2~MJ
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW $\pm$ 9~kW with an average total heat release of 23.3~MJ $\pm$ 1.6~MJ over a 300~s period.
+The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW $\pm$ 24~kW.
+The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ $\pm$ 0.6~MJ.
+The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
+Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW $\pm$ 21~kW.
+The total heat release over the 300~s period after ignition was 4.1~MJ $\pm$ 0.2~MJ
 
@@
 
-Plots of the centerline temperatures averaged over the replicate experiments for each of the fuels are presented in Figures 6 through 8.
-The number following “TC” in the legend of the graphs represents the height of the thermocouple in increments of 10~cm (or dm) above the fuel surface.
-The natural gas temperatures were averaged over a ``steady-state'' burning period as reflected by the data in Figure 6.
-The temperature differences between the vertical thermocouple locations, for locations greater than 20 cm above the fire location, begin to decrease as the distances from the top of the burner increase.
+Plots of the centerline temperatures averaged over the replicate experiments for each of the fuels are presented in Fig.~\ref{Temp}.
+The natural gas temperatures were averaged over a ``steady-state'' burning period.
+The temperature differences between the vertical thermocouple locations, for locations greater than 20~cm above the fire location, begin to decrease as the distances from the top of the burner increase.
 This trend is similar for both the gasoline fires and the polyurethane foam fires as well.
@@
 
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/Fig6}\\
+  \includegraphics[width=4.5in]{../Figures/Fig7}\\
+  \includegraphics[width=4.5in]{../Figures/Fig8}\\
+  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
+The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+  \label{Temp}
+\end{figure}
+
 \section{Total Heat Flux}
 
+Plots of the total heat flux for each of the fuels are presented in Fig.~\ref{Flux}.
 The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that has periods of growth and decay.
 The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
-The average peak total heat flux for the natural gas fires were approximately 2.0~kW/m$^2$, as shown in the example data set in Figure 9.
+The average peak total heat flux for the natural gas fires were approximately 2.0~kW/m$^2$.
 The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$ respectively.
 The values are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/Fig9}\\
+  \includegraphics[width=4.5in]{../Figures/Fig10}\\
+  \includegraphics[width=4.5in]{../Figures/Fig11}\\
+  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
+  \label{Flux}
+\end{figure}
 
@@
 Mass loss measurements were not possible for the natural gas burner experiments.
-The mass loss versus time curves for the gasoline and the polyurethane experiments are shown in Figures 12 and 13.
-The gasoline exhibits a linear mass loss rate for the initial 150~s of approximately 0.12~kg per minute.
+The mass loss versus time curves for the gasoline and the polyurethane experiments are shown in Fig.~\ref{Mass}.
+The gasoline exhibits a linear mass loss rate for the initial 150~s of approximately 2~g/s.
 The polyurethane foam was ignited with a small flame in the center of the top surface of the foam block.
 As the flame spread across the surface it also began to burn down into the foam sample.
-As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 0.12~kg per minute.
+As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 2~g/s.
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/Fig12}\\
+  \includegraphics[width=4.5in]{../Figures/Fig13}\\
+  \caption[Mass loss versus time for the gasoline and foam fueled fires]{Mass loss versus time for the gasoline and foam fueled fires.}
+  \label{Mass}
+\end{figure}
 
@@
 
-Examples of the photographic images are presented in Figures 14 and 15.
+Examples of the photographic images are presented in Figs.~\ref{Gas_Foam_Photos} and \ref{Gasoline_Photos}.
 Figure 14 is a photograph of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
@@
 The two photographs, taken 0.2~s apart, represent the range of the observed flame heights from one of the gasoline experiments from 0.65~m and 1.0~m, respectively.
+
+\begin{figure}
+  \includegraphics[width=2.7in]{../Figures/Fig14a} 
+  \includegraphics[width=2.7in]{../Figures/Fig14b} \\
+  \caption[Photographs of the natural gas and polyurethane foam fires]{Photographs showing a natural gas fire (left) and a polyurethane foam fire (right) under the oxygen consumption calorimeter.}
+  \label{Gas_Foam_Photos}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=2.7in]{../Figures/Fig15a}
+  \includegraphics[width=2.7in]{../Figures/Fig15b} \\
+  \caption[Photographs of the gasoline fire]{Photograph showing a gasoline fueled experiment with a flame height of 0.65 m (left) and a photograph taken approximately 0.2 s later with a flame height of 1.0 m (right).}
+  \label{Gasoline_Photos}
+\end{figure}
 

### 2015-03-08 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add figures to Madrzykowski thesis.

@@
 Examples of the photographic images are presented in Figs.~\ref{Gas_Foam_Photos} and \ref{Gasoline_Photos}.
-Figure 14 is a photograph of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
-Figure 9 presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100~kW.
+Figure~\ref{Gas_Foam_Photos} is a photograph of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
+Figure~\ref{Gasoline_Photos} presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100~kW.
 The two photographs, taken 0.2~s apart, represent the range of the observed flame heights from one of the gasoline experiments from 0.65~m and 1.0~m, respectively.
@@
 A grid sensitivity analysis was conducted with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm square grids.
-Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Figure 19.
+Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Fig.~\ref{Intensity}.
 The outputs shown are time averaged intensity fields generated with 5 resolutions listed above.
 In each output the x and y axis dimensions are in mm.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=\textwidth]{../Figures/Fig19}\\
+  \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams.
+The images, starting with the upper left, were generated with 5 mm, 10 mm, 20 mm, 40 mm and 80 mm resolutions.}
+  \label{Intensity}
+\end{figure}
 
@@
 Another means of quantifying field data with Streams is the use of contour plots.
-Examples of the time averaged contour plots are shown in Figures 20 through 22 for a natural gas, gasoline, and polyurethane fueled experiments respectively.
-Each contour line represents the percentage of time that the flame was at a given height.
-Figure 20 provides an example of a natural gas experiment.
-The region under examination, as shown as a black bounding rectangle, is 1400~mm high and 800 mm in width.
-This example was averaged over approximately 29~s or approximately 870 images.
-The number above each contour line in the plot range from 0 to 1.
-The area bounded by the contour with the value 1 represents the area that the flame occupied 100~\% of the time period analyzed or the persistent flame region as defined by McCaffrey~\cite{McCaffrey:1979}.
+Examples of the time averaged contour plots are shown in Figs.~\ref{Gas_and_Gasoline_Contours} and \ref{Foam_Contours} for the natural gas, gasoline, and polyurethane fueled fires.
+Each contour line represents the percentage of time that the flame was at a given position.
+The region under examination, as shown as a black bounding rectangle, is 1400~mm high and 800~mm in width.
+The natural gas fire was sampled for 29~s, resulting in 870~images.
+The area bounded by the contour with the value 1 represents the area that the flame was visible 100~\% of the time sampled.
+This can be considered the persistent flame region as defined by McCaffrey~\cite{McCaffrey:1979}.
 The remaining contours are in the intermittent flame region, with the 0.5 contour representing the mean flame height.
@@
 
-Figures 22 and 23 show two different contours for the polyurethane foam fueled experiment.
+\begin{figure}
+  \includegraphics[width=2.7in]{../Figures/Fig20} 
+  \includegraphics[width=2.7in]{../Figures/Fig21} \\
+  \caption[Visibility fractions for the natural gas and gasoline fires]{Plots showing the fraction of time that the flame was visible for the natural gas (left) and gasoline (right) fires.}
+  \label{Gas_and_Gasoline_Contours}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=2.7in]{../Figures/Fig22} 
+  \includegraphics[width=2.7in]{../Figures/Fig23} \\
+  \caption[Visibility fractions for the polyurethane foam fire]{(Left) Plot showing the fraction of time that the flame was visible for the polyurethane foam fire.
+(Right) Polyurethane foam contour plot with bifurcated flames at time of peak heat release rate.}
+  \label{Foam_Contours}
+\end{figure}
+
+Figure~\ref{Foam_Contours} shows two different contours for the polyurethane foam fueled experiment.
 The results from polyurethane fueled fire characterization experiments have an increased amount of variability due to the nature of the ignition source and the fuel itself.
@@
 In some cases the fire burned completely through the fuel in the center of the foam sample, resulting in a hollow flame at the time of the peak heat release rate.
-An example of a contour plot, exhibiting the hollow or bifurcated flames is shown in Figure 23.
+An example of a contour plot, exhibiting the hollow or bifurcated flames is shown at right in Fig.~\ref{Foam_Contours}.
 Other methods of ignition for the polyurethane foam were considered in order to have a more uniform ignition of the top surface of the foam.

### 2015-03-09 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated gas cooling descriptions.

@@
 
-The Engineering Laboratory at National Institute of Standards and Technology has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
+The Engineering Laboratory at National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
 One of the objectives of this program is to examine non-traditional means of fire suppression.
-This series of experiments conducted by NIST for the California Polytechnic State University, San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.
+This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.
 These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.
+
 NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.
@@
 2)            gas layer cooling 
-3)            fire suppression in an experimental structures
+3)            fire suppression in an experimental structure
 
@@
 
+The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement.
+These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression.
+The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.
+The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.
+The developing hot gas layer spread to the adjacent room through a single doorway.
+The adjacent room developed a hot gas layer and was the focus of this series of tests.
+
 \begin{figure}[!ht]
@@
 
-\subsection{Burn Building - Gas Cooling}
+\subsection{Purpose Built Fire Training Structure - Gas Cooling}
 \label{sec:Burn_Building}
@@
 \label{sec:Fuel_Load:_Gas_Cooling}
+
+Wood pallets were used to provide the fuel for the fire used in the gas cooling experiments.
+The pallets were approximately   1.2 m (4.0 ft) by 1.0 m (3.3 ft) by 0.13 m (0.42 ft) thick.
+Forty eight of the pallets used to fuel the gas cooling experiments were weighed.
+The pallets ranged in mass from 13.6 kg (29.9 lbs) to 26.4 kg (58.1 lbs) with an average of 18.4 kg (40.5 lbs).
+The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig xx.
+Approximately one half of a bale of excelsior, 13.0  kg (28.6 lbs), was mixed with the pallets to aid with ignition.
+
+As the pallets burned burn away and the hot gas layer temperatures decreased, the steel shutters on the window to the fire room were opened and additional pallets were added to the piles of burning pallets until the flames from the piles reached the ceiling of the burn room again.
+The number of pallets added each time varied.
 

### 2015-03-11 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Uploaded GC Data

@@
 
-These experiments were conducted at the Delaware County (PA) Emergency Services Training Center (ESTC) in Sharon Hill, PA.
+These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
 
@@
 The floors and ceilings are also concrete with the interior walls constructed of cement block.
-The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thinck layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile.
+The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thick layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile.
 The floor of the burn rooms is protected with fire brick.
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
+	\caption{Instrumentation Legend}
+	\label{fig:Instrumentation_Legend}
+\end{figure}
+
 \subsection{Gas Cooling Instrumentation} 
@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter.
-Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconel sheath.
+Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconnel sheath.
 In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.

### 2015-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
TIFF images changed to PDF and incorporated into revised doc with full ToC

@@
 \chapter{Scope of Study}
+\label{chapter:Scope of Study}
 
@@
 \chapter{Technical Approach}
+\label{chapter:Technical Approach}
 
@@
 
+\section{Fire Pattern Experiments}
+
 \subsubsection{Impact of Construction}
@@
 The results of these experiments determined the construction of the walls and corners used in subsequent phases of this study.
-
-\section{Fire Pattern Experiments}
 
@@
 
-\subsection{Bench Scale Experiments}
+\section{Bench Scale Experiments}
 
 Several types of bench scale experiments were conducted to generate data. This data could be used to assist in the analysis of the fire patterns and potentially be used as input for the FDS models.
-Critical Heat Flux – Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
+
+\subsection{Critical Heat Flux}
+
+Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
 The flooring radiant panel (ASTM~E648) was used to examine this value.
@@
 
-\subsubsection{Fire Pattern Recreation}
+\section{Fire Pattern Recreation}
 
+The ability to recreate or simulate a fire pattern or certain characteristics of a fire pattern was examined with a variety of tools.
+The first characteristic examined was the ability to determine based on the calculated heat flux to the wall if a "visible or measurable physical change" would occur to the painted paper surface of the gypsum wallboard.
+The next characteristic of the fire pattern that was examined was the height.
+The height of the fire pattern was then compared to the predictive results from flame height correlations.
 Heskestad developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion~\cite{Beyler:1986,Heskestad:SFPE}.
@@
 FDS~\cite{McGrattan:2014} and Smokeview~\cite{Forney:2014} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
-Comparison between the experiments and the model will provide valuable validation data for the model.
+These simulation tools provide results in the form of visual field data, in other they provide results in the same format that the investigator would see or document the fire pattern.
+Comparison between the experiments and the model may provide valuable validation data for the model.
 
@@
 
-\section{Characterizing the Source Fires}
+\chapter{Characterizing the Source Fires}
+\label{chapter:Characterizing the Source Fires}
 
@@
 
-\subsubsection{Fuels}
+\section{Fuels}
 
@@
 
-\subsubsection{Experimental Arrangement}
+\section{Experimental Arrangement}
 
@@
 \chapter{Results}
+\label{chapter:Results}
 
@@
 
-Examples of a set of TIFF images for each fuel are shown in Figures 16 through 18.
+Examples of a set of TIFF images for each fuel are shown in Figures .~\ref{flame_height_comp_FHNG80_1} through .~\ref{flame_height_comp_FHPUF_1}.
 Each figure has 56 sequential images from the video segment.
@@
 These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/flame height comp FHNG80-1.png}\\
+	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.
+In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
+	\label{flame_height_comp_FHNG80_1}
+\end{figure}
 
-From each of the peak heat release rate video clips, the edited TIFF files were loaded into Streams.
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/flame height comp FHGAS-1.png}\\
+	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.
+In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
+	\label{flame_height_comp_FHGAS_1}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/flame height comp FHPUF-1.png}\\
+	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.
+In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4 m to 0.9 m.}
+	\label{flame_height_comp_FHPUF_1}
+\end{figure}
+
+From each of the peak heat release rate video clips, the edited TIFF files were loaded into Streams~\cite{Nokes:2011}.
 For the natural gas and gasoline fueled fires, approximately 900 images were used in each image sequence.
@@
 
-\begin{figure}
+\begin{figure}[p]
 	\centering
-  \includegraphics[width=\textwidth]{../Figures/Fig19}\\
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_5mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_10mm_10s_color}\\
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_20mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_40mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_80mm_10s_color}\\
 	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams.
@@
 \chapter{Instrumented Calibration (non-combustible) Wall Experiments}
+Purpose
 
 \section{Experimental Arrangement}
+A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+The fires were initially placed at predetermined, fixed positions away from the wall.
+The burner was moved toward the wall until the burner was against the wall.
 
@@
 
-\subsection{Heat Flux Wall Temperatures}
+\subsection{Wall Temperatures}
+
+\subsection{Heat Flux}
+
+\subsection{Fire Pattern}
 
 \chapter{Instrumented Gypsum Board Wall Experiments}
+Purpose
+\section{Experimental Arrangement}
+A free standing, non-combustible, steel frame with gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+The fires were initially placed at predetermined, fixed positions away from the wall.
+The burner was moved toward the wall until the burner was against the wall.
+If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
 
@@
 
+\section{Results}
+
+\subsection{Wall Temperatures}
+
+\subsection{Heat Flux}
+
+\subsection{Fire Pattern}
+
+\chapter{Bench Scale Experiments}
+
 \section{Cone Calorimeter Experiments}
+
+\section{Radiant Flooring Panel Experiments}
+
+\section{Radiant Panel Experiments}
+
+\section{Results}
+
+\subsection{Ignition Temperature}
+
+\subsection{Heat Release Rate per Unit Area}
+
+\subsection{Critical Heat Flux}
+
+\chapter{Fire Pattern Compartment Experiments}
+
+\section{Wall Construction Type Experiments}
+\subsection{Experimental Arrangement}
+\subsection{Results}
+
+\section{Wall Position Experiments}
+\subsection{Experimental Arrangement}
+
+\subsection{Results}
+
+\subsubsection{Natural Gas}
+\subsubsection{Gasoline}
+\subsubsection{Polyurethane Foam}
+
+\section{Corner Position Experiments}
+
+\subsection{Experimental Arrangement}
+
+\subsection{Results}
+
+\subsubsection{Natural Gas}
+\subsubsection{Gasoline}
+\subsubsection{Polyurethane Foam}
+
+\chapter{Summary of Experimental Results}
+
+Needed?
+
+\chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}
+
+\section{Evidence of a Fire Pattern}
+
+\section{Flame Height Correlation}
+
+\subsection{Correlation Descriptions}
+
+\section{Comparison of Results}
+
+\chapter{Comparison of Field Model Simulations with Experimental Results}
+
+\section{Fire Dynamics Simulator and Smokeview}
+
+\subsection{Simulation of Fires}
+
+\subsection{Input Data}
+
+\section{Comparison of FDS with Source Fire Results}
+
+\subsection{Grid Size Analysis}
+
+\subsection{Plume Temperatures}
+
+\subsection{Heat Flux}
+
+\subsection{Flame Height}
+
+\section{Comparison of FDS with Fire Pattern Results}
+
+\chapter{Discussion}
+
+\chapter{Future Research Needs}
+
+\chapter{Conclusions}
 

### 2015-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: update figure names and tex file

@@
 
-Examples of a set of TIFF images for each fuel are shown in Figures .~\ref{flame_height_comp_FHNG80_1} through .~\ref{flame_height_comp_FHPUF_1}.
+Examples of a set of TIFF images for each fuel are shown in Figures~\ref{flame_height_comp_FHNG80_1} through \ref{flame_height_comp_FHPUF_1}.
 Each figure has 56 sequential images from the video segment.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/flame height comp FHNG80-1.png}\\
+	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHNG80}\\
 	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/flame height comp FHGAS-1.png}\\
+	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHGAS}\\
 	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/flame height comp FHPUF-1.png}\\
+	\includegraphics[width=\textwidth]{../Figures/flame_height_comp_FHPUF}\\
 	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added figures to TW and IGBW

@@
 \chapter{Instrumented Calibration (non-combustible) Wall Experiments}
-Purpose
+Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.
+In these experiments the target is a non-combustible wall and therefore the wall will not contribute to the fire.
+The fires were initially placed at predetermined, fixed positions away from the wall.
+In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
+Starting at a position where the closest edge of the burner was two burner widths from the wall.
+The burner was moved toward the wall until the burner was against the wall.
 
 \section{Experimental Arrangement}
-A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
-The fires were initially placed at predetermined, fixed positions away from the wall.
-The burner was moved toward the wall until the burner was against the wall.
+A free standing steel frame wall with a 12.7 mm thick, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_NC_Wall}\\
+	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
+Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
+	\label{Instrumented_NC_Wall}
+\end{figure}
 
@@
 If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
+	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
+Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
+	\label{Instrumented_GB_Wall}
+\end{figure}
 

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Text and Figures to Instrumented NC Wall Section

@@
 Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.
-In these experiments the target is a non-combustible wall and therefore the wall will not contribute to the fire.
+In these experiments the target is a non-combustible wall.
+The non-combustible material was chosen to eliminate any contribution from the wall to the fire.
 The fires were initially placed at predetermined, fixed positions away from the wall.
 In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
-Starting at a position where the closest edge of the burner was two burner widths from the wall.
-The burner was moved toward the wall until the burner was against the wall.
+Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610 m), one burner width (0.305 m), one half burner width (0.150 m), and the touching the wall.
 
 \section{Experimental Arrangement}
-A free standing steel frame wall with a 12.7 mm thick, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2 m to 1.2 m above the burner.
+One vertical array was centered on the burner and the other vertical array was centered on the right edge of the burner.
+The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}.
+Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner.
+Photographs of the front and rear of the instrumented wall are shown in Figures~{Instrumented_Wall_Front_photo,Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall.
+The photograph in Figure~{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
 
@@
 	\label{Instrumented_NC_Wall}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Rear_photo}\\
+	\caption[Photograph of the rear side of the instrumented non-combustible wall]{Photograph of the rear side of the instrumented non-combustible wall.}
+	\label{Instrumented_Wall_Rear_photo}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_NC_Wall}\\
+	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
+Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
+	\label{Instrumented_NC_Wall}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
+	\caption[Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.]{Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.}
+	\label{Instrumented_Wall_Close_up_TC_HF_photo}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
+	\caption[Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall]{Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall.}
+	\label{Instrumented_Wall_Detail_Rear_TC_photo}
 \end{figure}

### 2015-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner.
-Photographs of the front and rear of the instrumented wall are shown in Figures~{Instrumented_Wall_Front_photo,Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall.
-The photograph in Figure~{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
+Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall.
+The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
+In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter.
 
@@
 	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Front_photo}\\
+	\caption[Photograph of the front side of the instrumented non-combustible wall]{Photograph of the front side of the instrumented non-combustible wall.}
+	\label{Instrumented_Wall_Front_photo}
+\end{figure}
+
+\begin{figure}
+	\centering
 	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Rear_photo}\\
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/Instrumented_NC_Wall}\\
-	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
-Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
-	\label{Instrumented_NC_Wall}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
+	\includegraphics[width=4.0in]{../Figures/Instrumented_Wall_Close_up_TC_HF_photo}\\
 	\caption[Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.]{Photograph showing an example of the co-location of the heat flux gauges and the thermocouples on the front surface of the wall.}
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
+	\includegraphics[width=4.0in]{../Figures/Instrumented_Wall_Detail_Rear_TC_photo}\\
 	\caption[Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall]{Photograph of an example of the co-location of the thermocouple on the rear surface of the wall relative to the thermocouple installed on the front surface of the wall.}
@@
 
+The results are presented for each of the four burner positions and each of the three fuels.
+For the natural gas fueled experiments only two replicates were conducted at each position given the high level of control and repeatability.
+For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position.
+The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.
+The measures of the fire including heat release rate and flame/plume temperatures were also recorded to ensure consistency with the data presented in the previous section.
+
 \subsection{Wall Temperatures}
+
+\begin{figure}
+	\includegraphics[width=2.7in]{../Figures/Fig20} 
+	\includegraphics[width=2.7in]{../Figures/Fig21} \\
+	\caption[Visibility fractions for the natural gas and gasoline fires]{Plots showing the fraction of time that the flame was visible for the natural gas (left) and gasoline (right) fires.}
+	\label{Gas_and_Gasoline_Contours}
+\end{figure}
+
+\begin{figure}
+	\includegraphics[width=2.7in]{../Figures/Fig22} 
+	\includegraphics[width=2.7in]{../Figures/Fig23} \\
+	\caption[Visibility fractions for the polyurethane foam fire]{(Left) Plot showing the fraction of time that the flame was visible for the polyurethane foam fire.
+(Right) Polyurethane foam contour plot with bifurcated flames at time of peak heat release rate.}
+	\label{Foam_Contours}
+\end{figure}
 

### 2015-03-13 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated report.

@@
 Keith M. Stakes \\
+Craig G. Weinschenk \\
 
@@
 Keith M. Stakes \\
+Craig G. Weinschenk \\
 {\em Fire Research Division \\
@@
 
-The Engineering Laboratory at National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
+The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
 One of the objectives of this program is to examine non-traditional means of fire suppression.
@@
 The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement.
+The tests were conducted over a period of three days in late September of 2012 and split into a 8 different series.
 These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression.

### 2015-03-15 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Kevin and Craig ignore  this version working several sections at once - don't ask.

@@
 
-A free standing, non-combustible, calcium silicate wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing, steel frame with non-combustible, calcium silicate faced wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 The fires were initially placed at predetermined, fixed positions away from the wall.
@@
 
-A free standing, non-combustible, steel frame with gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 The fires were initially placed at predetermined, fixed positions away from the wall.
@@
 \chapter{Instrumented Calibration (non-combustible) Wall Experiments}
+
 Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.
@@
 \section{Experimental Arrangement}
+
 A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
@@
 
-\begin{figure}
-	\includegraphics[width=2.7in]{../Figures/Fig20} 
-	\includegraphics[width=2.7in]{../Figures/Fig21} \\
-	\caption[Visibility fractions for the natural gas and gasoline fires]{Plots showing the fraction of time that the flame was visible for the natural gas (left) and gasoline (right) fires.}
-	\label{Gas_and_Gasoline_Contours}
-\end{figure}
-
-\begin{figure}
-	\includegraphics[width=2.7in]{../Figures/Fig22} 
-	\includegraphics[width=2.7in]{../Figures/Fig23} \\
-	\caption[Visibility fractions for the polyurethane foam fire]{(Left) Plot showing the fraction of time that the flame was visible for the polyurethane foam fire.
-(Right) Polyurethane foam contour plot with bifurcated flames at time of peak heat release rate.}
-	\label{Foam_Contours}
-\end{figure}
-
 \subsection{Heat Flux}
@@
 \section{Experimental Arrangement}
-A free standing, non-combustible, steel frame with gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 The fires were initially placed at predetermined, fixed positions away from the wall.
@@
 
+The gypsum wallboard used in all of these experiments was purchased at one time from one vendor in an effort to have the most similar panels for used between the experiments.
+The physical features of the gypsum wallboard panels are given in the table below.
+After receipt of the gypsum wallboard panels, the panels were laid out on the floor or the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
+The first coat was a latex primer.
+Once the primer dried a top coat of white latex paint was applied.
+After the panels dried paint thickness measurements were made with a ultra sonic XXXX.
+Some of the panels were then cut-up into samples     think about this   perhaps this goes into the FP Comp
+
 \section{Results}
@@
 
+The cone calorimeter is probably the most versatile oxygen consumption method for measuring heat release rate.
+It was developed at NIST in the 1980s43 and is presently the most commonly used bench-scale rate of heat release apparatus.44 The cone calorimeter has been adopted as ASTM E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter.19 It has also been adopted as an international standard, ISO 5660-1.45
+The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
+Typically, the sample is located in the open with free access of air to the combustion zone.
+The heater consists of a 5 kW electrical heating element inside an insulated stainless-steel conical shell.
+Samples can be tested in either a horizontal or vertical orientation.
+When tests are performed in the horizontal configuration, the specimen is positioned approximately 25 mm beneath the bottom plate of the cone heater.
+Flames and products of combustion pass through a circular opening at the top of the heater.
+The heater can expose samples to a maximum irradiance of approximately 100 kW/m2.
+Figure  is a schematic of the cone calorimeter.
+
+For piloted ignition tests, an electric spark ignitor is positioned at the top of vertical samples and over the center of horizontal samples.
+Samples are typically 100 mm by 100 mm, and they can be wrapped with aluminum foil to minimize edge effects.
+Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
+The flow rate can be adjusted between 0.01 and 0.03 m3/sec.
+The volumetric flow rate is kept constant during testing.
+The sample is mounted on a load cell to determine mass loss rate during a test, and smoke obscuration is measured using a laser light source.
+The gas flow rate in the exhaust duct is calculated from the pressure drop across and temperature at an orifice plate in the duct.
+Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, and other gases are measured using appropriate instruments.
+Heat release rate is calculated from the gas concentration and mass flow measurements.
+
+For this study samples were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
+Key measurements made with the cone calorimeter, in addition to heat release rate per unit area of the samples, included using a series of cone calorimeter experiments at different heat fluxes to determine a ignition time and surface temperature pairs.
+
 \section{Radiant Flooring Panel Experiments}
+
+Normally the radiant panel test is used as documented in ASTM~E162 and provides a measure of downward, opposed-flow flame spread..63  The apparatus measures the surface flammability of materials using a gas-fired radiant panel that is 305~mm × 457~mm.
+However for the purposes of this study a modified version of the test apparatus was used.
+The radiant panel and and the radiant panel controls remained in place as documented in ASTM~E162.
+However the sample mounting system was changed.
+A rail and trolley system was developed to expose fire fighter protective equipment to various heat fluxes by being able to position the test specimen to a pre-determined position that correlated with a given heat flux.
+This trolley was used to hold a sample of painted gypsum wallboard were exposed to the radiant .
+Figure
+
+The exposed surface of the samples was parallel to the radiant panel.
+The radiant panel was calibrated and mapped with a heat flux gauge.
+With the flux gauge data, positions away from the radiant panel were identified to enable the samples to be exposed to a range of heat fluxes.
+After a timed exposure the samples were examined and amount of thermal damage to the painted paper surface of the gypsum board was   A relative index of flame spread is calculated based on the distance the sample burns.
+This test method is referenced for building products as ASTM E162, Standard Test Method for Surface Flammability of Materials using a Radiant Energy Source64 and for cellular plastics as ASTM D3675, Standard Test Method for Surface Burning Characteristics of Building Materials.65 Figure 2.3.11 illustrates the radiant panel test apparatus.
 
@@
 
+The fire pattern experiments were conducted in residential scale compartments built for the purpose of these experiments.
+The compartments were constructed on top of a portable wood floor platform.
+Each of the test compartments consisted of three 3.6~m long by 2.4~m high wood framed walls.
+The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90 mm by 38 mm.
+A partial ceiling with a width of at least 1.2 m, measured from the back wall of the compartment was installed across the width of the compartment, this allowed for the plume to impact the ceiling and form a ceiling jet along the back wall, before the fire gases flowed up and out of the compartment and into the 6~m by 6~m hood in the NIST Large Fire Research Laboratory.
+The interior surface of the walls and ceiling was composed of 12.7 mm thick, regular core gypsum wallboard.
+As defined by ASTM, gypsum wallboard is designed for use on walls, ceilings, or partitions.
+It is composed of a non-combustible core, essentially gypsum, with paper bonded to the surface of the core.
+The back wall of the compartment consisted of three full gypsum board panels, each 1.2 m wide and 2.4 m high.
+The front wall of the compartment was open along the full width of the compartment to minimize the impact of entrained air being channeled through a doorway.
+These experiments were conducted without instrumentation in the walls for several reasons; to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation, to provide more realistic conditions, and to enable the conduct of additional replicate experiments given the limited laboratory availability.
+Based on the outcome of the instrumented calibration target wall results, burner positions were chosen.
+After each burn, the fire patterns were measured, photographed and analyzed for repeatability.
+The fire damaged wallboard was subsequently removed and replaced with new sections of painted gypsum wallboard.
+The number of experiments for each case was dependent on the repeatability and similarity of the pattern development.
+Several types of fire pattern experiments were conducted in the compartments, as detailed in the sections to follow, to examine the impact of the insulation behind the gypsum wallboard panel on the resulting fire pattern and other series of experiments were conducted to compare the fire patterns based on the burner centered on the rear wall or in or near a corner on the rear wall of the compartment.
+
 \section{Wall Construction Type Experiments}
+
+ Impact of Wall Construction 
+ Additional experiments were conducted with the natural gas and gasoline fires to examine the impact of the method of construction of the walls on the development of the fire patterns.
+Three cases were examined: 1) Open back, 12.7 mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated,12.7 mm thick, regular core, painted gypsum board on the front and back of a wood frame, with fiberglas batt insulation in the voids of the wood frame representative of an exterior wall.
+
+The fuel or burner was centered on the middle panel of the rear wall.
+As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5 cm above the floor of the compartment.
+Each of the painted gypsum board panels that were used for a fire pattern had a 5 cm grid drawn on it to assist with the determination of the geometry of the fire pattern.
+
 \subsection{Experimental Arrangement}

### 2015-03-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Adding Wall and Bench Experimental descriptions need additional refs

@@
 
-The cone calorimeter is probably the most versatile oxygen consumption method for measuring heat release rate.
-It was developed at NIST in the 1980s43 and is presently the most commonly used bench-scale rate of heat release apparatus.44 The cone calorimeter has been adopted as ASTM E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter.19 It has also been adopted as an international standard, ISO 5660-1.45
+The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption method.
+It was developed at NIST in the 1980s~\cite{babrauskas:1984}.
+The cone calorimeter has been adopted as ASTM E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM E1354}.
 The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
 Typically, the sample is located in the open with free access of air to the combustion zone.
-The heater consists of a 5 kW electrical heating element inside an insulated stainless-steel conical shell.
+The heater consists of a 5~kW electrical heating element inside an insulated stainless-steel conical shell.
 Samples can be tested in either a horizontal or vertical orientation.
-When tests are performed in the horizontal configuration, the specimen is positioned approximately 25 mm beneath the bottom plate of the cone heater.
+When tests are performed in the horizontal configuration, the specimen is positioned approximately 25~mm beneath the bottom plate of the cone heater.
 Flames and products of combustion pass through a circular opening at the top of the heater.
-The heater can expose samples to a maximum irradiance of approximately 100 kW/m2.
+The heater can expose samples to a maximum irradiance of approximately 100~kW/m\$\^2\$.
 Figure  is a schematic of the cone calorimeter.
@@
 For piloted ignition tests, an electric spark ignitor is positioned at the top of vertical samples and over the center of horizontal samples.
-Samples are typically 100 mm by 100 mm, and they can be wrapped with aluminum foil to minimize edge effects.
+Samples are typically 100~mm squares.
 Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
-The flow rate can be adjusted between 0.01 and 0.03 m3/sec.
+The flow rate can be adjusted between 0.01 and 0.03 m\$\^3\$/s.
 The volumetric flow rate is kept constant during testing.
@@
 The gas flow rate in the exhaust duct is calculated from the pressure drop across and temperature at an orifice plate in the duct.
-Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, and other gases are measured using appropriate instruments.
+Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, were measured using appropriate instruments.
 Heat release rate is calculated from the gas concentration and mass flow measurements.
@@
 For this study samples were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
-Key measurements made with the cone calorimeter, in addition to heat release rate per unit area of the samples, included using a series of cone calorimeter experiments at different heat fluxes to determine a ignition time and surface temperature pairs.
+The experiments were conducted with the sample in the horizontal position.
+Measurements made with the cone calorimeter, in addition to heat release rate per unit area of the samples, included using a series of experiments at different heat fluxes to determine a ignition time and surface temperature pairs.
 
@@
 
-Normally the radiant panel test is used as documented in ASTM~E162 and provides a measure of downward, opposed-flow flame spread..63  The apparatus measures the surface flammability of materials using a gas-fired radiant panel that is 305~mm × 457~mm.
+The radiant flooring panel test method is known as ASTM~E648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}.
+A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel.
+The panel is inclined at 30~\$\^°\$, providing a heat flux on the test specimen varying from 10~kW/m\$\^2\$ at the point closest to the panel to 1~kW/m\$\^2\$ at the farthest point.
+A pilot flame is used to ignite the test sample.
+The objective of the test is to determine the critical radiant flux for a given sample.
+The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped.
+For this study the samples examined were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
+
+\section{Radiant Panel Experiments}
+
+The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTME162}.
+The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm × 457~mm.
+
 However for the purposes of this study a modified version of the test apparatus was used.
@@
 However the sample mounting system was changed.
-A rail and trolley system was developed to expose fire fighter protective equipment to various heat fluxes by being able to position the test specimen to a pre-determined position that correlated with a given heat flux.
+A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux.
 This trolley was used to hold a sample of painted gypsum wallboard were exposed to the radiant .
@@
 
-The exposed surface of the samples was parallel to the radiant panel.
+In the modified test configuration the exposed surface of the sample was parallel to the radiant panel.
 The radiant panel was calibrated and mapped with a heat flux gauge.
 With the flux gauge data, positions away from the radiant panel were identified to enable the samples to be exposed to a range of heat fluxes.
-After a timed exposure the samples were examined and amount of thermal damage to the painted paper surface of the gypsum board was   A relative index of flame spread is calculated based on the distance the sample burns.
-This test method is referenced for building products as ASTM E162, Standard Test Method for Surface Flammability of Materials using a Radiant Energy Source64 and for cellular plastics as ASTM D3675, Standard Test Method for Surface Burning Characteristics of Building Materials.65 Figure 2.3.11 illustrates the radiant panel test apparatus.
-
-\section{Radiant Panel Experiments}
+After a timed exposure the samples were examined and area of thermal damage to the painted paper surface of the gypsum board was compared with heat flux mapping.
+This was another means of potentially obtaining a measure of the critical heat flux.
+Figure 2.3.11 illustrates the radiant panel test apparatus.
 

### 2015-03-16 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_Hose_Tests: Updated report with Test 16/17 figures and tables, added comments to plotting scripts

@@
 instrumentation array locations, and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}.
-However, conditions affecting the measurement, such as levelness of the device, yield an
-estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
+However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
 Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
@@
 \ref{fig:flow_meter}.
-The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0–4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 \label{sec:Handline_Procedure}
-Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1$\frac{3}{4}$" handline equipped with a combination nozzle.
+Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1.75" handline equipped with a combination nozzle.
 Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.
@@
 
+\subsection{Monitor Nozzle Experiments}
+
+Figures \ref{fig:Test_16_BDP_A10_Avg_All}-\ref{fig:Test_17_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the two application locations and three hose stream patterns for Tests 16 and 17.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_Avg}
+\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
+\label{fig:Test_16_BDP_A10_Avg_All}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
+\label{fig:Test_16_BDP_A13_Avg_All}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
+\label{fig:Test_17_BDP_A10_Avg_All}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
+\label{fig:Test_17_BDP_A13_Avg_All}
+\end{figure}
+
+\clearpage
+
+\begin{table}[!ht]
+\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Location Combinations for Tests 16 and 17}
+\begin{tabular}{|l|l|c|c|c|c|}
+\hline
+\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} & 0.84 & 0.94 \\ \hline
+\textit{Narrow Fog} & 1.41 & 1.00 \\ \hline
+\textit{Wide Fog} & 1.23 & 1.37 \\ \hline
+\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} & 0.73 & 0.69 \\ \hline
+\textit{Narrow Fog} & 0.75 & 0.75 \\ \hline
+\textit{Wide Fog} & 0.88 & 0.71 \\ \hline
+\end{tabular}
+\label{table:Tests_16_17_BDP_A10_Avgs}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 16 and 17}
+\begin{tabular}{|l|l|c|c|c|c|}
+\hline
+\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} & 2.82 & 3.10 \\ \hline
+\textit{Narrow Fog} & 4.39 & 3.26 \\ \hline
+\textit{Wide Fog} & 3.92 & 4.37 \\ \hline
+\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} & 2.66 & 2.33 \\ \hline
+\textit{Narrow Fog} & 2.58 & 2.68 \\ \hline
+\textit{Wide Fog} & 3.14 & 2.76 \\ \hline
+\end{tabular}
+\label{table:Tests_16_17_BDP_A13_Avgs}
+\end{table}
+
+\subsection{Handline Experiments}
+
+Figures \ref{fig:Test_18_BDP_A10_Avg_All}-\ref{fig:Test_19_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the four application patterns and three hose stream patterns for Tests 18 and 19.
+
 \begin{figure}[!ht]
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
-\caption{Average Velocity of Stairwell Door, Test 18, All Streams}
+\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
 \label{fig:Test_18_BDP_A10_Avg_All}
@@
 \begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
+\label{fig:Test_18_BDP_A13_Avg_All}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
 \includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
-\caption{Average Velocity of Stairwell Door, Test 19, All Streams}
+\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
 \label{fig:Test_19_BDP_A10_Avg_All}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
+\label{fig:Test_19_BDP_A13_Avg_All}
 \end{figure}
@@
 \hline
-\multicolumn{5}{|c|}{Test 18} \\ \hline
+\multicolumn{5}{|c|}{Test 18 Avg. Velocities (m/s)} \\ \hline
 \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
@@
 \textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
-\multicolumn{5}{|c|}{Test 19} \\ \hline
+\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
 \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
@@
 \textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
-\multicolumn{5}{|c|}{Test 19} \\ \hline
+\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
 \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
@@
 
-\subsubsection{Clockwise vs. Counterclockwise Rotation}
+Notice, there is a significant difference between the average air velocity caused by the fixed straight stream and the velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.
+It was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern.
+However, the straight stream hose pattern always resulted in the lowest average air velocity through each doorway for the three different hose streams at each of the four application patterns.
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
-\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
-\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
-\end{figure}
+Another important result shown in Figures \ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables \ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} is that there is statistically no significant difference in the amount of air flow through the doorways between rotating the hoseline in the clockwise and counter clockwise directions for the three hose streams tested.
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
-\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
-\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
-\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
-\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
-\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
-\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
-\end{figure}
-
-\clearpage
+%\begin{figure}[!ht]
+%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
+%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
+%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
+%\end{figure}
+%
+%\begin{figure}[!ht]
+%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
+%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
+%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
+%\end{figure}
+%
+%\clearpage
+%
+%\begin{figure}[!ht]
+%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
+%\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
+%\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
+%\end{figure}
+%
+%\clearpage
+%
+%\begin{figure}[!ht]
+%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
+%\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
+%\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
+%\end{figure}
+%
+%\clearpage
 

### 2015-03-16 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -54,7 +54,8 @@ gas_quantities = ['CO_', 'CO2_', 'O2_']
 
 # Load exp. timings, description, and averages file
 timings = pd.read_csv(timings_file, index_col=0)
-hose_info = pd.read_csv(hose_info_file, index_col=0)
+desired_tests = list(timings.columns.values)			# creates list of  column headers which
+hose_info = pd.read_csv(hose_info_file, index_col=0) 	# correspond to desired tests
 info = pd.read_csv(info_file, index_col=3)
 
 # Files to skip
@@ -73,189 +74,185 @@ CCW_avg = []
 #  ===============================
 
 for f in os.listdir(data_dir):
-    if f.endswith('.csv'):
+	if f.endswith('.csv'):
+		# Skip files with time information or reduced data files
+		if any([substring in f.lower() for substring in skip_files]):
+			continue
 
-        # Skip files with time information or reduced data files
-        if any([substring in f.lower() for substring in skip_files]):
-            continue
+		# Strip test name from file name
+		test_name = f[:-4]
+		print 'Test ' + test_name
 
-        # Strip test name from file name
-        test_name = f[:-4]
-        print 'Test ' + test_name
+		# Skips undesired tests
+		if test_name not in desired_tests:
+			continue
 
-        # Only loads desired hose tests
-        if 'Test_18_' not in test_name and 'Test_19_' not in test_name:
-            continue
+		# Load exp. data file
+		data = pd.read_csv(data_dir + f, index_col=0)
 
-        # Load exp. data file
-        data = pd.read_csv(data_dir + f, index_col=0)
+		# Load exp. scaling file
+		if 'West' in test_name:
+			scaling_file = scaling_file_west
+		elif 'East' in test_name:
+			scaling_file = scaling_file_east
+		else:
+			scaling_file = scaling_file_default
 
-        # Load exp. scaling file
-        # if 'West' in test_name:
-        scaling_file = scaling_file_west
-        # elif 'East' in test_name:
-        #     scaling_file = scaling_file_east
-        # else:
-        #     scaling_file = scaling_file_default
-        scaling = pd.read_csv(scaling_file, index_col=2)
+		scaling = pd.read_csv(scaling_file, index_col=2)
 
-        # Read in test times to offset plots 
-        start_of_test = info['Start of Test'][test_name]
-        end_of_test = info['End of Test'][test_name]
+		# Read in test times to offset plots 
+		start_of_test = info['Start of Test'][test_name]
[…]

### 2015-03-16 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -56,8 +56,8 @@ gas_quantities = ['CO_', 'CO2_', 'O2_']
 
 # Load exp. timings, description, and averages file
 timings = pd.read_csv(timings_file, index_col=0)
-desired_tests = list(timings.columns.values)			# creates list of  column headers which
-hose_info = pd.read_csv(hose_info_file, index_col=0) 	# correspond to desired tests
+desired_tests = list(timings.columns.values)			# creates list of  column headers which correspond
+hose_info = pd.read_csv(hose_info_file, index_col=0) 	# to desired tests listed in All_Hose_Time.csv file
 info = pd.read_csv(info_file, index_col=3)
 
 # Files to skip
@@ -114,10 +114,12 @@ for f in os.listdir(data_dir):
 			if any([substring in group for substring in hose_info['Included Groups'][test_name].split('|')]) == False:
 				continue
 
+			# creates empty "stream" list for the sensor group's results file
 			blank_list = []
 			group_set = {'Stream': blank_list}
  			group_results = pd.DataFrame(group_set, columns = ['Stream'])
 
+ 			# reads in the stream patterns based on hose_info file
 			for diff in hose_info['Difference'][test_name].split('|'):
 				group_results[diff] = ' '
 			row_num = 0
@@ -134,12 +136,13 @@ for f in os.listdir(data_dir):
 				if hose_info[stream][test_name] == False:
 					continue
 
+				# reads start and end times for current stream from hose_info file
 				start_name = stream + '_start'
 				start = hose_info[start_name][test_name]
 				end_name = stream + '_end'
 				end = hose_info[end_name][test_name]
 
-				# Creates data set for specific hose stream
+				# Creates data set of start and end times for current hose stream 
 				stream_data = data.iloc[start:end]
 				t_stream = stream_data['Time']
 
@@ -188,7 +191,7 @@ for f in os.listdir(data_dir):
 						stream_data[channel] = quantity
 						stream_group[channel] = quantity
 
-				# Calculates the average of all channels in sensor group 
+				# Calculates the average of all channels in sensor group from recently created sensor group dataframe
 				group_avg = []
 				for index, row in stream_group.iterrows():
 					avg = np.mean(row[1:])
@@ -197,48 +200,38 @@ for f in os.listdir(data_dir):
[…]

### 2015-03-17 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: minor latex formatting

@@
 The ability to recreate or simulate a fire pattern or certain characteristics of a fire pattern was examined with a variety of tools.
-The first characteristic examined was the ability to determine based on the calculated heat flux to the wall if a "visible or measurable physical change" would occur to the painted paper surface of the gypsum wallboard.
+The first characteristic examined was the ability to determine based on the calculated heat flux to the wall if a ``visible or measurable physical change'' would occur to the painted paper surface of the gypsum wallboard.
 The next characteristic of the fire pattern that was examined was the height.
@@
 
-The natural gas burner was 30.5 cm on a side and the top surface of the burner was 7.5~cm above the floor.
+The natural gas burner was 30.5~cm on a side and the top surface of the burner was 7.5~cm above the floor.
 The shell of the burner was made from steel and filled with ``pea sized'' gravel with an average diameter of 6~mm.
@@
 A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.
-Each camera was positioned on a tripod with a distance of 4.5 m between the centerline of burner to camera lens 4.5~m.
-The height of each camera was adjusted so that the center of camera lens was positioned 0.5 m above top of the burner.
+Each camera was positioned on a tripod with a distance of 4.5~m between the centerline of burner to camera lens 4.5~m.
+The height of each camera was adjusted so that the center of camera lens was positioned 0.5~m above top of the burner.
 
@@
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
-In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2σ) would yield a confidence level of approximately 95~\%.
+In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95~\%.
 
@@
 In the cases of the gasoline and polyurethane fueled experiments, the video capture period bounded the peak heat release rate.
-In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30 s video capture could be made which was representative of the peak burning rate.
+In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30~s video capture could be made which was representative of the peak burning rate.
 The peak duration for the polyurethane foam fires was shorter so, only a 15~s video capture was used.
@@
 
-A free standing steel frame wall with a 12.7 mm thick, 2.44 m high by 1.22 m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
-Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2 m to 1.2 m above the burner.
+A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2~m to 1.2~m above the burner.
 One vertical array was centered on the burner and the other vertical array was centered on the right edge of the burner.
 The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}.
-Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20 cm intervals, up to a height of 2.2 m above the surface of the burner.
+Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20~cm intervals, up to a height of 2.2~m above the surface of the burner.
 Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10 mm below the TC positioned on the front surface of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
@@
 Flames and products of combustion pass through a circular opening at the top of the heater.
-The heater can expose samples to a maximum irradiance of approximately 100~kW/m\$\^2\$.
+The heater can expose samples to a maximum irradiance of approximately 100~kW/m$^2$.
 Figure  is a schematic of the cone calorimeter.
@@
 Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
-The flow rate can be adjusted between 0.01 and 0.03 m\$\^3\$/s.
+The flow rate can be adjusted between 0.01 and 0.03~m$^3$/s.
 The volumetric flow rate is kept constant during testing.
@@
 A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel.
-The panel is inclined at 30~\$\^°\$, providing a heat flux on the test specimen varying from 10~kW/m\$\^2\$ at the point closest to the panel to 1~kW/m\$\^2\$ at the farthest point.
+The panel is inclined at 30~$^{\circ}$, providing a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point.
 A pilot flame is used to ignite the test sample.
@@
 Each of the test compartments consisted of three 3.6~m long by 2.4~m high wood framed walls.
-The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90 mm by 38 mm.
-A partial ceiling with a width of at least 1.2 m, measured from the back wall of the compartment was installed across the width of the compartment, this allowed for the plume to impact the ceiling and form a ceiling jet along the back wall, before the fire gases flowed up and out of the compartment and into the 6~m by 6~m hood in the NIST Large Fire Research Laboratory.
-The interior surface of the walls and ceiling was composed of 12.7 mm thick, regular core gypsum wallboard.
+The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90~mm by 38~mm.
+A partial ceiling with a width of at least 1.2~m, measured from the back wall of the compartment was installed across the width of the compartment, this allowed for the plume to impact the ceiling and form a ceiling jet along the back wall, before the fire gases flowed up and out of the compartment and into the 6~m by 6~m hood in the NIST Large Fire Research Laboratory.
+The interior surface of the walls and ceiling was composed of 12.7~mm thick, regular core gypsum wallboard.
 As defined by ASTM, gypsum wallboard is designed for use on walls, ceilings, or partitions.
 It is composed of a non-combustible core, essentially gypsum, with paper bonded to the surface of the core.
-The back wall of the compartment consisted of three full gypsum board panels, each 1.2 m wide and 2.4 m high.
+The back wall of the compartment consisted of three full gypsum board panels, each 1.2~m wide and 2.4~m high.
 The front wall of the compartment was open along the full width of the compartment to minimize the impact of entrained air being channeled through a doorway.
@@
  Additional experiments were conducted with the natural gas and gasoline fires to examine the impact of the method of construction of the walls on the development of the fire patterns.
-Three cases were examined: 1) Open back, 12.7 mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated,12.7 mm thick, regular core, painted gypsum board on the front and back of a wood frame, with fiberglas batt insulation in the voids of the wood frame representative of an exterior wall.
+Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with fiberglas batt insulation in the voids of the wood frame representative of an exterior wall.
 
 The fuel or burner was centered on the middle panel of the rear wall.
-As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5 cm above the floor of the compartment.
+As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
 Each of the painted gypsum board panels that were used for a fire pattern had a 5 cm grid drawn on it to assist with the determination of the geometry of the fire pattern.

### 2015-03-20 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Equipment: minor edit to guide

@@
 Craig G. Weinschenk \\
+Keith M. Stakes \\
 Roy A. McLane \\
@@
 
-\begin{table}[h!]
-\centering
-\captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
-\begin{tabular}{lll}
-\toprule[1.5pt]
-Thermocouple Type  &  Temperature Range     &  Error                                      \\
-\midrule
-Bare bead (SLE)    &  0 - 1250 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
-Inconel sheathed   &  0 - 1260 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
-\bottomrule[1.25pt]
-\end{tabular}\par
-\end{table}
+% \begin{table}[h!]
+% \centering
+% \captionof{table}{Thermocouple Uncertainty}\label{tab:TC_uncertain}
+% \begin{tabular}{lll}
+% \toprule[1.5pt]
+% Thermocouple Type  &  Temperature Range     &  Error                                      \\
+% \midrule
+% Bare bead (SLE)    &  0 - 1250 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
+% Inconel sheathed   &  0 - 1260 $^{\circ}$C  &  MAX($\pm$ 1.1$^{\circ}$C; $\pm$ 0.4 $\%$)  \\
+% \bottomrule[1.25pt]
+% \end{tabular}\par
+% \end{table}
 

### 2015-03-21 Studies/2012_Chicago/Report/response.tex
Chicago: update firetech version and add firetech response document

\documentclass[12pt]{article}
\frenchspacing
\begin{document}

\section{Comments from the Editor}
\begin{itemize}
\item We would appreciate more efforts in assessing or estimation somehow the error or uncertainty of your results.
\item An effort to read some of the work published in Fire Technology on the topics at hand would be appreciated by the editorial board.
\item There are too many figures (20); please consider removing some or creating an Appendix where the 5 least important figures are presented.
\item Please consider to submit the input file/s for this work as Electronic Supplementary Material.
\end{itemize}

\section{Comments from Reviewer 1}
\begin{itemize}
\item It may be better to summarize the account in the author's own words, and to link it more closely to Table 1. This would be particularly helpful for section 3.4, since the ventilation conditions are not explained in great detail. \\
{\it The authors were able to view portions of video taken during the incident that allowed for the estimation of failure times and failure areas of exterior walls and windows.}
\item I miss, however, a more critical point of view that would be essential in guiding fire modellers as to what the limits of applicability of these models is. In this context I would require that the authors elaborate on how they approached the modelling of under-ventilated conditions. FDS is known for running into problems when flaming in vitiated air occurs. In figure 7 the authors present external flaming out of the rear window. Is this realistic? FDS tends to present combustion at vents, even when the flames in the interior have already been extinguished due to lack of oxygen. Is the flow of hot gases into the hallway after the door breakage accompanied by flaming combustion?
\item The authors discard the secondary simulation based on the similarity of the overall HRR, but an alternative ventilation pattern could potentially alter the flow path inside the building. They should explain in more detail why this is not the case in this scenario (or provide images of the flow path and temperature distributions of the secondary simulation).
\item I further think that the beginning of section 5.2 is misleading. Surely second-degree burn injuries are only produced by direct contact with objects at 55C. Air at 55C would not burn the skin. It would be useful to relate the temperatures (gas and wall) to heat fluxes, as this would be a more correct approach in terms of human perception and injuries.
\end{itemize}

\section{Comments from Reviewer 2}
\begin{itemize}
 \item The authors mention that the fire was under-ventilated yet the species that they have used in the analysis are well ventilated values.  Although the results of the modelling will not be effected by the assumed fuel, the precedent set in this paper could be used by others to justify these as appropriate values for under-ventilated fire when clearly they are not.  Additional discussion on the species and why the well ventilated values used are appropriate for this analysis but should not be used when modelling under-ventilated fire. 
\item The authors used 50kW/m2 for calculating there maximum heat release rate yet this value is lower than expected.  The author should explain why this low value was chosen.  The authors then go on and use a HRRPUA=2250kW/m2.  Why did not use the original 50kW/m2 and expand the area burning?  Additional explanation would be helpful.
\item This results in a floor area of approximately 105 m2 (1100 ft2) per floor and a main living area of approximately 110 m2 (2200 ft2). 
The 110m2 should be 210m2??? \\
{\it Thanks for the keen eye. Typo is corrected.}
\item  Around the time of the incident inside the building, E49 attic window.  It is not clear if this was an attic window or the window from the 2nd floor enclosed porch where the fire was.  Urban legend has it that a fire can be pushed through a structure with a hoseline.  Some discussion why this was discounted would be helpful to the reader.
\item There was a firefighter with the Captain that perished in the fire.  What were his injuries and location if known?  Some discussion about this 2nd firefighter in the area would be useful.
\item The condition of the door clearly shows significant damage to the metal door yet the temperatures modelled in FDS are only 260°C.   Is this an artefact of Smokeview's colorbar?  What was the temperature in the porch area when the door is thought to failed?\\ {\it The authors set these bounds because 500~$^{\circ}$F is the}
\end{itemize}

\section{Comments from Reviewer 3}
\begin{itemize}
\item It is interesting that the roof is vented at 17:27 right as the Mayday is called.  I suspect that it is a coincidence as there doesn't appear to have been 30-60 seconds for any change in the flow path caused by that action to propagate...but it might be worth inclusion in Table 1 and/or a little discussion.
\item Page 6.  With the discussion of the specified fire size, I was left wondering if that would be vent limited by the model.  It turns out it was, and you covered that well...but perhaps a note in this section mentioning that might be nice.
\item Page 16 line 40-41.  If there is a reference available for the NIST testing looking at the post-fire state of doors (as shown in Figure 15) it would be nice to provide that here. (or perhaps if unpublished just footnote the person who did the testing so readers know who they could ask for further info) \\
{\it A footnote has been added with a webadress where the report will live upon publication}
\end{itemize}

\section{Comments from Reviewer 4}
\begin{itemize}
\item Are the simulation input files going to be available somewhere online or with the publication? If so, that could resolve a number of these issues and the paper should have a reference to the location of these input files. \\
{\it The main input file will be provided as part of the Fire Technology electronic submission process. Additionally, all the files used to generate the simulations and report will be avilable through an open-source repository. At this current time, google-code is shutting down. The repository has yet to be migrated but I can provide that location upon request once it finds a new home.}
\item  The abstract reference to fire spread to the 2nd floor does not necessarily make it clear that the spread is from the attic in the downward direction. It could be clarified by adding a statement that there was no fire on the first [ground] level. [see p. 1] \\
{\it The abstract was clarified to indicate the fire spread downward and that there was no fire damage on the first floor.}
\item At the end of introduction to section 3, it would be good to put a reference to the SFPE Guide to Selecting a Fire Model for a Particular Purpose and that the authors considered the relevant physics and output to decide to use FDS. [See p. 4] \\
{\it Discussion was added referring to the SFPE Guide}
\item  Section 3.3 Materials would be more helpful if it also more fully addressed the exterior walls. I am expecting these were modeled just with gypsum board given the descriptions, rather than some sort of sandwich or other heat transfer approach. [See p. 7]
\item Section 3.3 Materials should also address what was done with the windows. No description of glass was given, so this should be addressed explicitly. [See p. 7]
\item The vents are unclear to me [See Tab. 2 and accompanying text, p. 7]. For example, which vents are the ones that were cut into the roof to vent the attic? In addition, I don't see any vents in the figure of the roof [See, for example, Fig. 5, p. 9].
\item Vents: Were all of the windows considered closed? I did not find that directly stated, especially given the details about all of the windows in the last two diagrams.
\item Vents: Where is the connection between the 2nd floor porch and attic? I saw it described broadly in the paper, but don't recall it being described more fully and it is not depicted in any of the diagrams.
\item Vents: Table 2, p. 7, it would be helpful to have a quick description of what each vent is in terms of the fire incident report.
\item On the numerical resolution examination [see p. 8, lines 22-27], it would be helpful to explain that higher numbers equate to better resolution as the non-user may not appreciate this and think that being outside the range makes it an unreliable calculation.
\item HRR: The graphic [Fig. 6, p.10] is fine and accompanying text is also good. One thing that is not clear, but may be helpful to the reader is to explain that some of that combustion is occurring outside the structure [See Fig. 7, p. 12]. This is important given the discussion of temperatures, etc. If the authors know the amount of HRR within the structure, that may be an interesting/helpful value for the readers.
\item Attic fire: Was any of the roof ``consumed?'' [See Fig. 7, p. 12 and associated text] It would be interesting to know if any of the roof was ultimately consumed and whether that occurred subsequent to the modeled period or if there was another reason to disregard that phenomenon. [See Fig. 2, p. 6]
\item Pressure: Section 4.2 [See p. 12, line 30] discusses over-pressure. I am unclear about that particular part of the discussion. The text references``at 1 m'', but I think this could be more clear that you are not talking about a compartment over-pressure, but that generated by buoyancy due to temperature differences. I don't think the authors mean that the whole compartment is over-pressured. This is an important distinction, because later the discussion focuses on the door, but I am under the impression that the door folding is heat caused structural failure, not overpressure. Therefore, it's important to clarify this point.
\item Pressure: [See Fig. 8, p. 12] I am unsure how to interpret this graphic as presumably there are some lower pressures driving air into the various spaces as normal gravity flows. I think this figure should have some additional description to better explain what it's showing. Somewhere, there must be air entering these various spaces in order to continue combustion in those volumes.
\item Fig. 14, p. 16: This photo shows the door and discusses the crease, which I can see. I assume from my reading that this is the interior face of the door and that the top of the door is towards the background. This should be clarified in the caption.
\item Fig. 20, p. 24 \& Fig. 21, p. 25: These graphics are good overall. Unfortunately, the cross-hatching is difficult to interpret in some places. Furthermore, it will be impossible to read this if it is reproduced in black and white.
\item  It would be helpful to have a floor plan of the attic space that includes the locations of the roof vents.
\end{itemize}

\end{document}

### 2015-03-21 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago: update firetech version and add firetech response document

@@
 This resulted in ventilation limited (fuel rich) fire conditions in the attic and rear porch areas.
-The spread of fire and hot gases into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
+Further spread of fire and hot gases from the attic downward into the second floor of the structure was limited by a closed steel-faced, wood-framed door.
+Note that there was no evidence of fire damage on the first floor of the structure.
 After exposure to the elevated temperatures and pressure from the fire in the porch area, the wood frame of the door decomposed, the steel faces of the door failed, and the door collapsed inward.
@@
 
+Whenever a computational analysis is conducted, it is important to match needs of the analysis with the necessary level of sophistication.
+To determine the best fire model for use in this study, the SFPE Guide to Substantiating a Fire Model for a Given Application~\cite{SFPE_G.06} was used.
+The author's determined that FDS and Smokeview were most appropriate.
+
 \subsection{Geometry}
@@
 One potential issue with balloon frame construction is that without fire stops there is void space for fire to potentially travel between the floors within the wall cavity.} The structure had a 17.15~m (56~ft) by 6.15~m (20~ft) footprint, as shown in Fig.~\ref{fig:simp_geom}.
-This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 110~m$^2$ (2200~ft$^2$).
+This results in a floor area of approximately 105~m$^2$ (1100~ft$^2$) per floor and a main living area of approximately 210~m$^2$ (2200~ft$^2$).
 The interior walls were constructed from nominal lumber covered by 12.7~mm (0.5~in) gypsum board~\cite{NIOSH:Bowyer}.
@@
 Note that the majority of the damage occurred in the attic and rear porch on the second floor.
-Fully dimensioned drawings of the interior of the first and second floors are shown in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
+Fully dimensioned drawings of the interior of the first and second floors are shown in Appendix~\ref{app_draw} in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
 
@@
 Note that the coordinates here are unique for the vents are specific to the input files used for these simulations. The key point is that they are 2-D planes located at a specific area.
+
+When using any computational model, the user is responsible for understanding it's limitations.
+In this simulation, one of the main concerns is the ability to accurately model an under-ventilated structure fire.
+Due to the nature of the ``mixed-is-burnt'' concept when using fast-chemistry reactions in FDS~\cite{FDS_Tech_Guide}, there exists the possibility for flaming conduction to be predicted by the model that may not occur in a real fire.
 
@@
 As a result, all of the input model geometry lengths, ventilation openings (holes, doors, and windows), and fire areas will snap to the nearest 10~cm.
-Figure~\ref{fig:geom_grid} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
+Figure~\ref{fig:geom_grid} in Appendix~\ref{app_mesh} shows the front of the structure rendered in Smokeview with the 10~cm mesh.
 The domain was divided into 16 equally sized meshes (each containing 150,000 grid cells) that could be processed in parallel, which reduced the amount of required calculation time to approximately 1.5~days.
-Figure~\ref{fig:mult_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
-
-\begin{figure}[!ht]
-\centering
-\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
-   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
-   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
-\end{tabular*}
-\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh}
-\label{fig:geom_grid}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
-\caption[Front-right side of the structure within the computational domain]{Front-right side of the structure within the computational domain (with multiple meshes).
-Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft)}
-\label{fig:mult_mesh}
-\end{figure}
+Figure~\ref{fig:mult_mesh} in Appendix~\ref{app_mesh} shows the entire structure within the computational domain that has been divided into multiple meshes.
 
@@
 Recent experiments conducted by NIST revealed similar post-fire states after doors of similar construction were exposed to fires.
-Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation.
+Figure~\ref{fig:SC_doorfold} shows doors from two different residential fire experiments in different stages of degradation \footnote{At the time of this publication, the report detailing the structure fire experiments has not yet been published.
+Please check www.nist.gov/fire for updates regarding this work.}.
 In both cases, note that the door knob assembly served as a pivot point for the upper portion of the door to collapse around.
@@
 
+\clearpage
+
+\section{Numerical Mesh Figures}
+\label{app_mesh}
+\begin{figure}[!ht]
+\centering
+\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
+   \scalebox{1.0}{\includegraphics[width=.49\textwidth]{../Figures/smv_exterior_grid}} &
+   \scalebox{1.0}{\includegraphics[width=.488\textwidth]{../Figures/smv_exterior_grid_rear}} \\
+\end{tabular*}
+\caption{Front (left) and rear (right) of the structure with 10~cm computational mesh}
+\label{fig:geom_grid}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.60\textwidth]{../Figures/smv_exterior_mesh}
+\caption[Front-right side of the structure within the computational domain]{Front-right side of the structure within the computational domain (with multiple meshes).
+Each of the 16 meshes is 3~m (9.8~ft) by 10~m (33~ft) by 5~m (16.4~ft)}
+\label{fig:mult_mesh}
+\end{figure}
+
 \end{document}

### 2015-03-23 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Working on Ch 6 plus  Wall Construction Table needs help

@@
 
-Cone calorimeter (ASTM~1354) experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
+Cone calorimeter~\cite{ASTM_E1354} experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
 
@@
 The gas burner arrangement provides the most idealized fire, in that it can be ignited and brought up to a near steady state heat release rate within a few seconds and then be shut down just as quickly.
-This provided an approximate “square wave” exposure to the gypsum wallboard.
+This provided an approximate `square wave' exposure to the gypsum wallboard.
 This is important for determining the potential amount of energy transferred to the exposed surface.
@@
 
-The results are presented for each of the four burner positions and each of the three fuels.
-For the natural gas fueled experiments only two replicates were conducted at each position given the high level of control and repeatability.
+The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels in Appendix X.
+For the natural gas fueled experiments only two replicates were conducted at each position given the higher level of control and repeatability.
 For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position.
+The position is measured as the distance between the edge of the burner closest to the wall and the wall.
 The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.
-The measures of the fire including heat release rate and flame/plume temperatures were also recorded to ensure consistency with the data presented in the previous section.
+In the sections below, examples of the averaged data from the gasoline fueled experiments will be presented to demonstrate the impact on distance on the conditions measured on the wall.
+Then a composite graph of the measured thermal impacts on the wall versus distance will be shown for each fuel type.
 
@@
 
+Figure~\ref{IW_SC_TWGAS} shows the temperatures of the array of thermocouples located along the vertical centerline of the gasoline fueled burner.
+The beads of the thermocouples were installed in the wall and were flush with the wall surface.
+In each graph, the average temperature of the replicate experiments, for each thermocouple position is shown.
+Moving from 0.2 m above the top surface of the burner up to 2.2 m above the top of the burner surface in increments of 0.2 m.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_61m_RepsAvg}
+	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_31m_RepsAvg}\\
+	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_15m_RepsAvg}
+	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0m_RepsAvg}\\	
+	\caption[Wall Temperatures along the centerline of the gasoline fueled burner]{Wall Temperatures along the centerline of the gasoline fueled burner.
+The temperatures are averages of three replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
+	\label{IW_SC_TWGAS}
+\end{figure}
+
 \subsection{Heat Flux}
+
+Figure~\ref{IW_HFC_TWGAS} shows the temperatures of the array of total heat flux gauges located along the vertical centerline of the gasoline fueled burner.
+The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
+In each graph, the average temperature of the replicate experiments, for each total heat flux position is shown.
+Moving from 0.2 m above the top surface of the burner up to 1.2 m above the top of the burner surface in increments of 0.2 m.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_RepsAvg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_RepsAvg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_RepsAvg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_RepsAvg}\\	
+	\caption[Wall heat fluxes along the centerline of the gasoline fueled burner]{Wall heat fluxes along the centerline of the gasoline fueled burner.
+The heat fluxes are averages of three replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
+	\label{IW_HFC_TWGAS}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/nctw_ng_heatflux}\\
+	\caption[Summary of wall heat fluxes along the centerline of the natural gas fueled burner]{Summary of the heat flux to the non-combustible wall along the verticle centerline of the natural gas fueled burner compared to the position away from the wall.}
+	\label{nctw_ng_heatflux}
+\end{figure}
 
@@
 It was developed at NIST in the 1980s~\cite{babrauskas:1984}.
-The cone calorimeter has been adopted as ASTM E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM E1354}.
+The cone calorimeter has been adopted as ASTM~E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}.
 The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
@@
 
-The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTME162}.
-The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm × 457~mm.
+The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
+The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm by 457~mm.
 
@@
  Impact of Wall Construction
- Additional experiments were conducted with the natural gas and gasoline fires to examine the impact of the method of construction of the walls on the development of the fire patterns.
+
+ The initial compartment experiments were conducted to examine the impact of the method of construction of the walls on the development of the fire patterns.
+This data determined how the walls for the remaining compartment fire pattern experiments would be constructed.
 Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with fiberglas batt insulation in the voids of the wood frame representative of an exterior wall.
-
-The fuel or burner was centered on the middle panel of the rear wall.
+From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occured when the burners were positioned against the wall.
+The peak temperatures were similar for all of the fuels,approximately 80~$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
+Therefore the wall construction experiments were only conducted with the natural gas and gasoline fueled burners as the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
+
+The rear wall of the compartment was constructed in the same manner for a given set of experiments.
+The burner was centered on the middle panel of the rear wall.
 As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
@@
 \subsection{Experimental Arrangement}
+
 \subsection{Results}
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|} {\textwidth}
+		\hline
+	Fuel (number of tests) (\%)   &       Wall Type	            &   Max. Height (m)	            & Max. Width (m)    &  Height at Max. Width (m)    &  Area (m $^2$)  \\ \hline
+		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\
+		Natural Gas (10)    &   Closed 		& 0.74	$\pm$ 0.06 (8~\%)    &	0.24 $\pm$ 0.02 (7~\%) 		& 0.43 $\pm$ 0.03 (7~\%)  	& 0.14 $\pm$ 0.01 (6~\%) 	\\
+		Natural Gas (10)    &   Insulated 	& 0.71	$\pm$ 0.10 (14~\%)   &	0.23 $\pm$ 0.04 (17~\%) 	& 0.42 $\pm$ 0.07 (17~\%) 	& 0.15 $\pm$ 0.02 (14~\%)  	\\
+		Gasoline (12)       &   Open    	& 0.83	$\pm$ 0.15 (18~\%)   &	0.28 $\pm$ 0.09 (32~\%) 	& 0.44 $\pm$ 0.14 (32~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
+		Gasoline (10)       &   Closed  	& 0.80	$\pm$ 0.10 (13~\%)   &	0.29 $\pm$ 0.04 (14~\%) 	& 0.44 $\pm$ 0.06 (14~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
+		Gasoline (10)       &   Insulated	& 0.82 	$\pm$ 0.09 (11~\%)   &	0.25 $\pm$ 0.08 (32~\%) 	& 0.40 $\pm$ 0.13 (32~\%) 	& 0.13 $\pm$ 0.04 (30~\%)  	\\
+
+		\hline
+	\end{tabular}
+	\caption[Comparison of fire pattern dimensions as a function of wall construction type]{Comparison of fire pattern dimensions as a function of wall construction type.
+Values presented with 95\% confidence limits.}
+	\label{tab:Fire_Pattern_Dimensions_Wall_Construction}
+\end{table}
 
@@
 
+Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
+The cells are contained together within a larger volume known as the computational domain.
+The CFD model computes the density, velocity, temperature, pressure, and gas concentrations in each cell.
+Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gases.
+One of the most important aspects of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide}and validated against fire test data~\cite{FDS_Validation_Guide}to ensure that it is accurate and provides the expected results, given appropriate input data.
+A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Tech_Guide}.
+
+Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
+Smoke-view visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
+Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
+Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.
+
+Input data was collected from the experimental results presented in Chapters XXs and from literature sources in order to simulate the experiments      a fire using FDS or any other fire model.
+For the simulation results presented in this document, information was obtained from two primary sources
+
 \subsection{Simulation of Fires}

### 2015-03-23 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: latex cleanup

@@
 \usepackage{graphicx}
+\usepackage{rotating}
 \frenchspacing
@@
 The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
-The comparison of the fire pattern heights and the mean flame height demonstrated that the ``'steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+The comparison of the fire pattern heights and the mean flame height demonstrated that the ``steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
 
@@
 The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3~m by 3~m hood oxygen consumption calorimeter.
-This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests}~\cite{ASTM_E2067}.
+This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests} ~\cite{ASTM_E2067}.
 The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
@@
 
-On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level ($2\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
@@
   \includegraphics[width=2.7in]{../Figures/Fig15b} \\
-  \caption[Photographs of the gasoline fire]{Photograph showing a gasoline fueled experiment with a flame height of 0.65 m (left) and a photograph taken approximately 0.2 s later with a flame height of 1.0 m (right).}
+  \caption[Photographs of the gasoline fire]{Photograph showing a gasoline fueled experiment with a flame height of 0.65~m (left) and a photograph taken approximately 0.2~s later with a flame height of 1.0~m (right).}
   \label{Gasoline_Photos}
@@
 	\caption[Example of sequential video frames sampled from a natural gas fueled experiment]{Example of sequential video frames sampled from a natural gas fueled experiment.
-In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
+In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
 	\label{flame_height_comp_FHNG80_1}
@@
 	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.
-In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6 m to 1.1 m.}
+In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
 	\label{flame_height_comp_FHGAS_1}
@@
 	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.
-In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4 m to 0.9 m.}
+In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4~m to 0.9~m.}
 	\label{flame_height_comp_FHPUF_1}
@@
 In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
-Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610 m), one burner width (0.305 m), one half burner width (0.150 m), and the touching the wall.
+Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and the touching the wall.
 
@@
 In each graph, the average temperature of the replicate experiments, for each thermocouple position is shown.
-Moving from 0.2 m above the top surface of the burner up to 2.2 m above the top of the burner surface in increments of 0.2 m.
+Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m.
 
@@
 In each graph, the average temperature of the replicate experiments, for each total heat flux position is shown.
-Moving from 0.2 m above the top surface of the burner up to 1.2 m above the top of the burner surface in increments of 0.2 m.
+Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.
 
@@
 The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
-The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm by 457~mm.
+The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm × 457~mm.
 
@@
 As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
-Each of the painted gypsum board panels that were used for a fire pattern had a 5 cm grid drawn on it to assist with the determination of the geometry of the fire pattern.
+Each of the painted gypsum board panels that were used for a fire pattern had a 5~cm grid drawn on it to assist with the determination of the geometry of the fire pattern.
 
@@
 
-\begin{table}
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|} {\textwidth}
+\begin{sidewaystable}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
 	\hline
-	Fuel (number of tests) (\%)   &       Wall Type	            &   Max. Height (m)	            & Max. Width (m)    &  Height at Max. Width (m)    &  Area (m $^2$)  \\ \hline
+	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m $^2$)  \\ \hline
 		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\
@@
 		Gasoline (10)       &   Insulated	& 0.82 	$\pm$ 0.09 (11~\%)   &	0.25 $\pm$ 0.08 (32~\%) 	& 0.40 $\pm$ 0.13 (32~\%) 	& 0.13 $\pm$ 0.04 (30~\%)  	\\
-
 		\hline
@@
 	\caption[Comparison of fire pattern dimensions as a function of wall construction type]{Comparison of fire pattern dimensions as a function of wall construction type.
-Values presented with 95\% confidence limits.}
+Values presented with 95~\% confidence limits.}
 	\label{tab:Fire_Pattern_Dimensions_Wall_Construction}
-\end{table}
+\end{sidewaystable}
 

### 2015-03-25 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
DelCo_2014: Updated report with new figs and other content

@@
 \usepackage[super]{nth}
+\usepackage{placeins}
 
@@
 Three types of hose streams were each applied in four different fashions during each set of hose flow experiments.
-The three types of hose stream patterns studied were straight stream, narrow fog stream, and wide fog stream.
+The three types of hose stream patterns studied, pictured in Figure~\ref{fig:hose_streams}, were straight stream, narrow fog stream, and wide fog stream.
 Water was flowed into the structure by having the hose in a static, fixed position, moving the hose line left-to-right across the room in a sweeping motion, and rotating the hose line in both the clockwise and counterclockwise directions.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Figures/hose_streams.pdf}
+\caption[Different Hose Stream Patterns]{The three types of hose stream patterns, straight stream (left), narrow fog stream (middle), and wide fog stream (right), used during the water flow experiments.}
+\label{fig:hose_streams}
+\end{figure}
+\FloatBarrier
 
@@
 \label{sec:Experimental_Structure}
-This series of field experiments was conducted at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+This series of field experiments was conducted into two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
 
-Two concrete structures were built on a concrete slab as shown in Figure XX.
+\subsection{Construction}
+\label{sec:Construction}
+Two concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
 They were designed to simulate a single story and a two story residential structure.
@@
 
-The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs etc…
+The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs etc...
 
@@
 The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
-The ceiling of the burn room was the exposed “floor assembly”.
+The ceiling of the burn room was the exposed ``floor assembly".
 The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room.
 The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
-
-\subsection{Construction}
-\label{sec:Construction}
-Two structures, shown in Fig.~\ref{fig:struct_pics}, were constructed for the experiments.
-Each structure contained a ground level floor composed of walls surrounded by concrete blocks.
-The West Structure contained a second level.
 
@@
 \label{sec:Water_Flow_Procedure}
+A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure.
+All the experiments were conducted in either the East or West Structure; used a monitor or handline with a combination nozzle to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
+Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
 
@@
 \label{sec:East_Structure_Water_Flow_Procedure}
+Five sets of water flow experiments (Tests 29-34) were conducted to observe the impact of different hose streams and application methods on the air flow in the East Structure.
+Water was flowed from the north side double doors into Room C during Tests 29-32 and from Room C into Room B for Tests 33 and 34.
+Tests 29 and 30 followed a similar procedure that differed in that Test 29 flowed water from a monitor in a straight stream pattern, while Test 30 flowed water from a monitor nozzle in a narrow fog pattern.
 
@@
 
-Four sets of water flow experiments were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
+Four sets of water flow experiments (Tests 16-19) were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
 Water was flowed from the double doors on the first floor for all experiments.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_Avg}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
 \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A13_Avg}
+\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
 \caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
@@
 \begin{table}[!ht]
-\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Location Combinations for Tests 16 and 17}
-\begin{tabular}{|l|l|c|c|c|c|}
-\hline
-\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
-\textit{Straight} & 0.84 & 0.94 \\ \hline
-\textit{Narrow Fog} & 1.41 & 1.00 \\ \hline
-\textit{Wide Fog} & 1.23 & 1.37 \\ \hline
-\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
-\textit{Straight} & 0.73 & 0.69 \\ \hline
-\textit{Narrow Fog} & 0.75 & 0.75 \\ \hline
-\textit{Wide Fog} & 0.88 & 0.71 \\ \hline
+\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
+\begin{tabular}{|l|c|c|c|c|}
+\cline{2-5}
+\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} & 
+%%%%Test 16%%%% 
+0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
+%%%%Test 17%%%% 
+0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
+\textit{Narrow Fog} & 
+%%%%Test 16%%%% 
+1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
+%%%%Test 17%%%% 
+0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
+\textit{Wide Fog} 	& 
+%%%%Test 16%%%% 
+1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
+%%%%Test 17%%%% 
+0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
 \end{tabular}
@@
 
+%code for higher resolution in tabulated values
+%\textit{Straight} & 0.84 & 0.94 & 0.73 & 0.69 \\ \hline
+%\textit{Narrow Fog} & 1.41 & 1.00 & 0.75 & 0.75 \\ \hline
+%\textit{Wide Fog} & 1.23 & 1.37 & 0.88 & 0.71 \\ \hline
+
 \begin{table}[!ht]
-\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 16 and 17}
-\begin{tabular}{|l|l|c|c|c|c|}
-\hline
-\multicolumn{3}{|c|}{Test 16 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
-\textit{Straight} & 2.82 & 3.10 \\ \hline
-\textit{Narrow Fog} & 4.39 & 3.26 \\ \hline
-\textit{Wide Fog} & 3.92 & 4.37 \\ \hline
-\multicolumn{3}{|c|}{Test 17 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} \\ \hline
-\textit{Straight} & 2.66 & 2.33 \\ \hline
-\textit{Narrow Fog} & 2.58 & 2.68 \\ \hline
-\textit{Wide Fog} & 3.14 & 2.76 \\ \hline
+\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
+\begin{tabular}{|l|c|c|c|c|}
+\cline{2-5}
+\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
+\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
+\textit{Straight} 	& 
+%%%%Test 16%%%% 
+2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
+%%%%Test 17%%%% 
+2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
+\textit{Narrow Fog} & 
+%%%%Test 16%%%% 
+4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
+%%%%Test 17%%%% 
+2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
+\textit{Wide Fog} 	& 
+%%%%Test 16%%%% 
+3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
+%%%%Test 17%%%% 
+3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
 \end{tabular}
@@
 \end{table}
+
+%code for higher resolution in tabulated values
+%\textit{Straight} 	& 2.82 & 3.10 & 2.66 & 2.33 \\ \hline
+%\textit{Narrow Fog} & 4.39 & 3.26 & 2.58 & 2.68 \\ \hline
+%\textit{Wide Fog} 	& 3.92 & 4.37 & 3.14 & 2.76 \\ \hline
 
@@
 \begin{table}[!ht]
-\caption{Average Air Velocity Through Stairwell Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
-\begin{tabular}{|l|l|c|c|c|c|}
-\hline
-\multicolumn{5}{|c|}{Test 18 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-\textit{Straight} & -0.17 & 0.48 & 0.65 & 0.63 \\ \hline
-\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 \\ \hline
-\textit{Wide Fog} & 0.93 & 0.90 & 0.91 & 0.75 \\ \hline
-\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-\textit{Straight} & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
-\textit{Narrow Fog} & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
-\textit{Wide Fog} & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
+\addtolength{\tabcolsep}{-3.25pt}
+\small
+\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\cline{2-9}
+\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textit{Straight} 	& 
+%%%%Test 18%%%% 
+-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
+%%%%Test 19%%%% 
+ 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
+\textit{Narrow Fog} & 
+%%%%Test 18%%%% 
+ 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
+%%%%Test 19%%%% 
+ 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
+\textit{Wide Fog} 	& 
+%%%%Test 18%%%% 
+ 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
+%%%%Test 19%%%% 
+ 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
 \end{tabular}
@@
 
+%code to increase resolution of tabulated values
+%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
+%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
+%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
+
 \begin{table}[!ht]
-\caption{Average Air Velocity Through \nth{2} Level Double Door for All Hose Stream and Application Pattern Combinations for Tests 18 and 19}
-\begin{tabular}{|c|c|c|c|c|}
-\hline
-\multicolumn{5}{|c|}{Test 18 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-\textit{Straight} & -0.43 & 1.75 & 2.46 & 2.40 \\ \hline
-\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 \\ \hline
-\textit{Wide Fog} & 3.02 & 3.22 & 3.06 & 2.57 \\ \hline
-\multicolumn{5}{|c|}{Test 19 Avg. Velocities (m/s)} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-\textit{Straight} & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
-\textit{Narrow Fog} & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
-\textit{Wide Fog} & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
+\addtolength{\tabcolsep}{-3.25pt}
+\small
+\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
+\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+\cline{2-9}
+\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textit{Straight}  &
+%%%%Test 18%%%% 
+-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
+%%%%Test 19%%%%					
+ 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
+\textit{Narrow Fog} & 
+%%%%Test 18%%%%
+ 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
+%%%%Test 19%%%%
+ 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
+\textit{Wide Fog} 	& 
+%%%%Test 18%%%%
+3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
+%%%%Test 19%%%%
+3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
 \end{tabular}
@@
 \end{table}
+
+%code to increase resolution of tabulated values
+%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
+%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
+%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
 

### 2015-03-25 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -122,6 +122,7 @@ for f in os.listdir(data_dir):
  			# reads in the stream patterns based on hose_info file
 			for diff in hose_info['Difference'][test_name].split('|'):
 				group_results[diff] = ' '
+				group_results[diff + ' StDev'] = ' '
 			row_num = 0
 
 			fig = figure()
@@ -200,7 +201,7 @@ for f in os.listdir(data_dir):
 				# Adds a column of the average of all channels to the dataframe 
 				stream_group['Average of Channels'] = group_avg
 
-				# determines the max and min y values for the sensor group averages
+				# determines the max and min y values for the current stream sensor group average
 				if max(group_avg) > max_y:
 					max_y = math.ceil(max(group_avg))
 				if min(group_avg) < min_y:
@@ -210,16 +211,16 @@ for f in os.listdir(data_dir):
 				start_time = hose_info['Start'][test_name]
 				# reads in time after beginning of experiment to when FP is complete
 				FP_beg = hose_info['Flowpath complete'][test_name]
-				# Averages for when flow path is completely established for each hose stream
-				diff_avgs = []
+				# Averages and stdevs added to data row for when flow path is completely established for each hose stream
+				data_row = [stream]
 				for diff in hose_info['Difference'][test_name].split('|'):
 					FP_end = FP_beg + hose_info['Duration'][test_name]
-					diff_avgs.append(round(np.mean(stream_group['Average of Channels'][int(FP_beg):int(FP_end)]), 2))
+					data_row.append(round(np.mean(stream_group['Average of Channels'][int(FP_beg):int(FP_end)]), 1))
+					data_row.append(round(np.std(stream_group['Average of Channels'][int(FP_beg):int(FP_end)]), 1))
 					FP_beg = hose_info['Flowpath complete'][test_name] + FP_end + hose_info['Time Between'][test_name]
 				
-				# creates an array for data file for current sensor group
-				data_row = np.append(stream, diff_avgs)
-				group_results.loc[row_num]  = np.array(data_row)
+				# adds row to data file for current stream in current sensor group
+				group_results.loc[row_num]  = data_row
 				row_num = row_num + 1
 
 				t = arange(len(stream_group.index))

### 2015-03-26 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
Delco_2014: Restructured and added east hose test descriptions to experimental procedure section

@@
 
-\subsubsection{East Structure Experiments}
-\label{sec:East_Structure_Water_Flow_Procedure}
-Five sets of water flow experiments (Tests 29-34) were conducted to observe the impact of different hose streams and application methods on the air flow in the East Structure.
-Water was flowed from the north side double doors into Room C during Tests 29-32 and from Room C into Room B for Tests 33 and 34.
-Tests 29 and 30 followed a similar procedure that differed in that Test 29 flowed water from a monitor in a straight stream pattern, while Test 30 flowed water from a monitor nozzle in a narrow fog pattern.
+\subsubsection{Monitor Experiments}
+\label{sec:Water_Flow_Monitor_Procedure}
+A total of five sets of experiments were conducted using a monitor with a combination nozzle to flow water.
+Three of the tests (Tests 29, 30, and 33) occurred in the East Structure and two of the tests (Tests 16 and 17) occurred in the West Structure.
 
-\subsubsection{West Structure Experiments}
-\label{sec:West_Structure_Water_Flow_Procedure}
+Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor with a combination nozzle.
+A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30.
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}).
+After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped.
+The monitor was adjusted so the nozzle was aimed at Door BC.
+Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped.
+This process was repeated an additional time.
 
-Four sets of water flow experiments (Tests 16-19) were conducted to observe the impact of using different hose streams and application patterns on the ventilation in the West Structure.
-Water was flowed from the double doors on the first floor for all experiments.
-The experiments varied based on flow path configurations and the type of nozzle used.
-Two flow path configurations were used.
-Both configurations contained the double doors on the first level in the opened position and the stairwell door and west side double door on the second level being opened and closed depending on the time in the experiment.
-The main difference between the two configurations was that the first level, south side door was in the opened position for Flow Path Configuration 1 and was in the closed position for Flow Path Configuration 2.
-Fig.~\ref{fig:flow_path_1} and Fig.~\ref{fig:flow_path_2} contain the floor plan schematics for Flow Path Configuration 1 and Flow Path Configuration 2, respectively.
+Test 33 varied from Tests 29 and 30 in multiple ways.
+First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}.
+Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
+Then, the south side door was opened, and each stream was applied for 30 seconds again.
+
+Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure.
+The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern.
+To begin the process, the nozzle was adjusted to produce the desired hose stream pattern.
+Once the nozzle was adjusted, water was applied at the ``far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds.
+After 60 seconds of water flow, the stairwell door was opened.
+60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
+Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the ``near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).
+
+\subsubsection{Handline Experiments}
+\label{sec:Water_Flow_Handline_Procedure}
+A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water.
+Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.
+
+Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle.
+A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32.
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}) in the fixed position.
+After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds.
+Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds.
+While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated.
+After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for thirty seconds while the south side door was opened and closed.
+This entire procedure was repeated an additional time.
+
+Test 34 varied from Tests 31 and 32 in multiple ways.
+First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}.
+Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern.
+Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
+These steps were repeated for narrow fog and wide fog streams.
+Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.
+
+Tests 18 and 19 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a handline with a combination nozzle located at the south side, double doors on the first level of the West Structure.
+The difference between the two tests was that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Tests 18 and 19 repeated an identical process three times, one time for each hose stream pattern.
+To begin the process, the nozzle was adjusted to produce the desired hose stream pattern.
+Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position.
+After 60 seconds of water flow, the stairwell door was opened.
+60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
+Then, water flow stopped, the two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
 
@@
 \includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
-\caption[Flow path configuration used during West Structure water flow experiments]{West Structure first floor (top) and second floor (bottom) layouts for Test 18.
-Both double doors and the south side door were open on the first floor for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
+\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18.
+Both double doors and the south side door on the first floor were in the opened position for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
 \label{fig:flow_path_1}
 \end{figure}
+\FloatBarrier
 
@@
 \includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
-\caption[West Structure first and second floor layouts for Test 19]{West Structure first floor (top) and second floor (bottom) layouts for Test 19.
-Both double doors were open and the south side door was closed on the first floor for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the experiments, while the north side, east double door and south side door were in the closed position throughout the entire test.}
+\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19.
+Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test.
+On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
 \label{fig:flow_path_2}
 \end{figure}
-
-\clearpage
-
-The four sets of water flow experiments conducted in the West Structure contained two different procedures for each flow path configuration.
-One of the procedures involved using a monitor nozzle to flow water at fixed positions in the first floor of the structure, and the other procedure used a handline equipped with a combination nozzle to flow water into the first floor of the structure in various application patterns.
-The second procedure used a 1$\frac{3}{4}$" handline equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
-Each stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.
-
-\subsubsection{Monitor Nozzle Experimental Procedure}
-\label{sec:Monitor_Procedure}
-Two sets of the experiments, Tests 16 and 17, involved flowing water from a monitor nozzle in a straight stream, narrow fog stream, and wide fog stream pattern.
-Each stream was aimed at two different locations on the first floor interior ceiling: the "far target", which was located approximately X m (Xft) from the south interior wall, and the "near target" which was located approximately X m (Xft) from the interior wall of the double doors.
-
-\subsubsection{Handline Experimental Procedure}
-\label{sec:Handline_Procedure}
-Two sets of experiments, Tests 18 and 19, involved flowing water in different stream patterns from a 1.75" handline equipped with a combination nozzle.
-Each hose stream was flowed in four different patterns: a fixed position, a sweeping pattern, a clockwise pattern, and a counter clockwise pattern.
-
-Tests 18 and 19 followed identical procedures that involved flowing water from a handline using different hose stream and application pattern combination.
-The handline combination nozzle was adjusted to produce three types of hose streams: a straight stream, a narrow fog stream, and a wide fog stream.
-Tests 18 and 19 involved three sets of experiments, one for each type of hose stream.
-For each set of experiments, four different application patterns were tested.
-First, water was applied while the hose was in a fixed position.
-Next, the hoseline was moved from side-to-side across the open room, creating a sweeping application pattern.
-Finally, the hoseline was rotated in both the clockwise and counterclockwise directions, creating clockwise and counterclockwise application patterns.
-
-To begin each set of experiments, the combination nozzle was adjusted to produce the desired hose stream pattern.
-Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position.
-After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
-Then, the hoseline and two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
+\FloatBarrier
 
@@
 \end{figure}
-
-\clearpage
+\FloatBarrier
 

### 2015-03-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Madrzy_Thesis: update references

@@
 
-Now that the characteristics of the fires have been measured, the next step is to measure the thermal impact that the fires have on a target.
+Now that the characteristics of the fires had been measured, the next step was to measure the thermal impact that the fires had on a vertical target surface.
 In these experiments the target is a non-combustible wall.
-The non-combustible material was chosen to eliminate any contribution from the wall to the fire.
-The fires were initially placed at predetermined, fixed positions away from the wall.
+The non-combustible material was chosen to minimize any contribution from the wall to the fire.
+The fires were placed at predetermined, fixed positions away from the wall.
 In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
-Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and the touching the wall.
+Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
 
@@
 
-A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+Marinite Type I is the commercial name of the non-combustible board used in these experiments.
+It is normally used as a fire-resistant thermal insulation that also has structural strength.
+90~\% of the board is composed of calcium silicate and calcium meta-silicate.
+The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.
+Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.
+\begin{table}
+	\centering
+\begin{tabular}{|c|c|c|c|c|}
+	\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
+	\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
+	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
+	\hline  & 205 & 0.12  & 205 & 0.30 \\ 
+	\hline  & 316 & 0.11 & 316 & 0.32 \\ 
+	\hline  & 425 & 0.12 & 425 & 0.34 \\ 
+	\hline  & 538 & 0.12 &  &  \\ 
+	\hline 
+\end{tabular} 
+\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
+\label{tab:Marinite_Thermal_Properties}
+\end{table}
+
 Two vertical arrays of water cooled, Schmidt-Boelter total heat flux gauges, as previously described in the instrumentation section above, were installed at 20 cm intervals from 0.2~m to 1.2~m above the burner.
@@
 
-\section{Characterization of Gypsum Board}
+\section{Characterization of Gypsum WallBoard}
+
+According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.
+A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.
+As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to recieve decoration  ref ATSM 1396.
+The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
+By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.
+Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$  2H$_{2}O) .
+By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.
 
@@
 
+The first series of experiments were conducted with the natural gas burner.
+
+ \begin{figure}[p]
+ 	\centering
+ 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+ 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
+ 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Plume_Avg_Avg}\\
+ 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.
+The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
+ 	\label{IWGB_NG_Temp_FrontSet}
+ \end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
+	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
+	\label{IWGB_NG_Temp_RearCenter}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.
+}
+	\label{IWGB_NG_Temp_RearCenter}
+\end{figure}
+
 \subsection{Wall Temperatures}
 
+Comparisons NG to Gas to PUF
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
+	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
+The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\label{IWGB_Temp_Comp_FrontCenter}
+\end{figure}
+
 \subsection{Heat Flux}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
+	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
+The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\label{IWGB_HF_Comp_Center}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
+	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
+	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
+The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\label{IWGB_HF_Comp_Edge}
+\end{figure}
 
@@
 
-\bibliography{../References/Madrzykowski_Thesis}
+\bibliography{../References/Madrzykowski_Thesis,../../../Bibliography/FDS_refs}
 \end{document}

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
latex clean up

@@
 	\centering
-	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_5mm_10s_color}
-	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_10mm_10s_color}\\
-	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_20mm_10s_color}
-	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_40mm_10s_color}
-	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80-1_GS_80mm_10s_color}\\
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_5mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_10mm_10s_color}\\
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_20mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_40mm_10s_color}
+	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_80mm_10s_color}\\
 	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams.
-The images, starting with the upper left, were generated with 5 mm, 10 mm, 20 mm, 40 mm and 80 mm resolutions.}
+The images, starting with the upper left, were generated with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm resolutions.}
 	 \label{Intensity}
@@
 \begin{tabular}{|c|c|c|c|c|}
-	\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
-	\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
+	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\ 
+    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
 	\hline 737  & 24 & 0.13 & 93 & 0.28 \\ 
@@
 	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_RepsAvg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_RepsAvg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_RepsAvg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_RepsAvg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_Reps_Avg}\\
 	\caption[Wall heat fluxes along the centerline of the gasoline fueled burner]{Wall heat fluxes along the centerline of the gasoline fueled burner.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/nctw_ng_heatflux}\\
+	\includegraphics[width=\textwidth]{../Figures/NCTW_NG_HF_Center_Avg}\\
 	\caption[Summary of wall heat fluxes along the centerline of the natural gas fueled burner]{Summary of the heat flux to the non-combustible wall along the verticle centerline of the natural gas fueled burner compared to the position away from the wall.}
@@
 By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.
-Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$  2H$_{2}O) .
+Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .
 By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.
@@
  	\centering
- 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
- 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
- 	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Plume_Avg_Avg}\\
+ 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+ 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
+ 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
  	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.
@@
 }
-	\label{IWGB_NG_Temp_RearCenter}
+	\label{IWGB_NG_HF_RearCenter}
 \end{figure}
@@
 	\centering
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
+	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=4.in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=4.in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
 	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.
+
 \begin{table}
@@
 
-The gypsum wallboard used in all of these experiments was purchased at one time from one vendor in an effort to have the most similar panels for used between the experiments.
+The gypsum wallboard used in these experiments is referred to as "regular" as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
+The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.
 The physical features of the gypsum wallboard panels are given in the table below.
-After receipt of the gypsum wallboard panels, the panels were laid out on the floor or the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
+		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
+		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
+		\hline  	& 100 	& 0.15  &  		&  \\ 
+		\hline  	&  &  &  &  \\ 
+		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 
+		\hline  	& 100 	& 0.15 	& 100 	& 0.90 \\ 
+		\hline  	& 200 	& 0.13 	& 200 	& 0.80 \\ 
+		\hline  	& 500 	& 0.15 	& 500	& 0.90 \\ 
+		\hline 
+		\end{tabular} 
+		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
+		\label{tab:Gypsum wallboard_Thermal_Properties}
+		\end{table}
+
+% first two lines of table based on measurements of GB at NIST.  Lower 4 lines from Gross 1985
+
+After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
 The first coat was a latex primer.

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 	\begin{tabular}{|c|c|c|c|c|}
-		\hline Density (kg/m$^3&)  &Thermal Conductivity   & Specific Heat  &  &  \\ 
+		\hline Density (kg/m$^3$)  & Thermal Conductivity   & Specific Heat  &  &  \\ 
 		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
@@
  	\centering
- 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
- 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
- 	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
  	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.
@@
 	\centering
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
 	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
@@
 	\centering
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
 	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.
@@
 	\centering
-	\includegraphics[width=4.in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
-	\includegraphics[width=4.in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
-	\includegraphics[width=4.in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
 	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
@@
 	\centering
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
 	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
@@
 	\centering
-	\includegraphics[width=4.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
-	\includegraphics[width=4.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
 	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Latex table cleanup

@@
 
-The gypsum wallboard used in these experiments is referred to as "regular" as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
+The gypsum wallboard used in these experiments is referred to as ``regular'' as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
 The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.
@@
 	\begin{tabular}{|c|c|c|c|c|}
-		\hline Density (kg/m$^3$)  & Thermal Conductivity   & Specific Heat  &  &  \\ 
-		\hline   & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
+		\hline Density & \multicolumn{2}{c|}{Thermal Conductivity}   & \multicolumn{2}{c|}{Specific Heat}  \\ 
+		\hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ 
 		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\ 
 		\hline  	& 100 	& 0.15  &  		&  \\ 
-		\hline  	&  &  &  &  \\ 
 		\hline 790 	& 20 	& 0.18	& 20 	& 0.90 \\ 

### 2015-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revised Chapter Outline

@@
 
-\chapter{Scope of Study}
-\label{chapter:Scope of Study}
+\section{Scope of Study}
 
@@
 
-\chapter{Technical Approach}
-\label{chapter:Technical Approach}
+\section{Technical Approach}
 
@@
 
-\section{Selection of Measurement Methods and Analytical Tools}
+\subsection{Selection of Measurement Methods and Analytical Tools}
 
@@
 
-\section{Fire Pattern Experiments}
+\subsection{Fire Pattern Experiments}
 
@@
 
-\section{Bench Scale Experiments}
+\subsection{Bench Scale Experiments}
 
@@
 
-\subsection{Critical Heat Flux}
+\subsubsection{Critical Heat Flux}
 
@@
 
-\section{Fire Pattern Recreation}
+\subsection{Numerical Fire Pattern Analysis}
 
@@
 
-\chapter{Results}
-\label{chapter:Results}
-
-{\section{HRR}
+\section{Results}
+
+\subsection{HRR}
 
@@
 
-\section{Plume Temperatures}
+\subsection{Plume Temperatures}
 
@@
 
-\section{Total Heat Flux}
+\subsection{Total Heat Flux}
 
@@
 
-\section{Mass Loss}
+\subsection{Mass Loss}
 
@@
 
-\section{Flame Height}
+\subsection{Flame Height}
 
@@
 
-\section{Summary}
+\subsection{Summary}
 
@@
 
-\chapter{Instrumented Calibration (non-combustible) Wall Experiments}
+\chapter{Instrumented Non-combustible Wall Experiments}
 
@@
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
-In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter.
+In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter.
 
@@
 The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.
-In the sections below, examples of the averaged data from the gasoline fueled experiments will be presented to demonstrate the impact on distance on the conditions measured on the wall.
-Then a composite graph of the measured thermal impacts on the wall versus distance will be shown for each fuel type.
+In the sections below,a full set of the averaged data from the natural gas fueled experiments will be presented to demonstrate the impact on distance from the wall on the temperatures in the plume as well as the conditions measured on the wall.
+Then composite graphs of the wall temperatures and heat flux measure on the wall versus distance will be shown for each fuel type.
+
+Figures~\ref{TC_Plume_TWNG_comp} through \ref{TC_Back_Center_TWNG_comp} show a complete set of data, averaged over two replicates, for the instrumented, non combustible wall natural gas burner experiments.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
+	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+	\label{TC_Plume_TWNG_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_61m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_31m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_15m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
+	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+	\label{TC_Surf_Cent_TWNG_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
+	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+	\label{TC_Surf_Edge_TWNG_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
+	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+	\label{TC_Back_Center_TWNG_comp}
+\end{figure}
 
@@
 
-Figure~\ref{IW_SC_TWGAS} shows the temperatures of the array of thermocouples located along the vertical centerline of the gasoline fueled burner.
+Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels.
 The beads of the thermocouples were installed in the wall and were flush with the wall surface.
-In each graph, the average temperature of the replicate experiments, for each thermocouple position is shown.
+In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown.
 Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_61m_RepsAvg}
-	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_31m_RepsAvg}\\
-	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0_15m_RepsAvg}
-	\includegraphics[width=2.5in]{../Figures/TC_Surface_Center_TWGas_0m_RepsAvg}\\
-	\caption[Wall Temperatures along the centerline of the gasoline fueled burner]{Wall Temperatures along the centerline of the gasoline fueled burner.
-The temperatures are averages of three replicate experiments.
+As in the data analysis for the source fires, the peak averages were based on a 30 s period bounding the peak for the natural gas and gasoline fires.
+A 15 s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\
+
+	\caption[Composite graph of the wall temperatures along the centerline of the burners]{Composite graph of the wall temperatures along the centerline of the burners for each fuel.
+The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall.
+Beginning with the top graph position and moving down the graph for natural gas, gasoline, and polyurethane foam are presented.}
+	\label{NCTW_Surf_Center_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\
+
+	\caption[Composite graph of the wall temperatures along the edge of the burners]{Composite graph of the wall temperatures along the edge of the burners for each fuel.
+The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall.
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
+	\label{NCTW_Surf_Edge_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Back_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Back_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\
+
+	\caption[Composite graph of the backside wall temperatures along the center of the burners]{Composite graph of the backside wall temperatures along the vertical centerline of the burners for each fuel.
+The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall.
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
+	\label{NCTW_Back_Cent_comp}
+\end{figure}
+
+\subsection{Heat Flux}
+
+Figure~\ref{NCTW_HF_Center_Comp} shows the results from the array of total heat flux gauges located along the vertical centerline of the burners for each fuel.
+The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
+In each graph, the averaged peak heat flux for each of the replicate experiments and each position is shown.
+Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Center_Avg} \\
+	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Center_Avg} \\
+
+	\caption[Wall heat flux along the centerline of the burners]{Wall heat fluxes along the centerline of the burners.
+The heat fluxes are averages of replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
-	\label{IW_SC_TWGAS}
-\end{figure}
-
-\subsection{Heat Flux}
-
-Figure~\ref{IW_HFC_TWGAS} shows the temperatures of the array of total heat flux gauges located along the vertical centerline of the gasoline fueled burner.
-The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
-In each graph, the average temperature of the replicate experiments, for each total heat flux position is shown.
-Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_61m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_31m_Reps_Avg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0_15m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWGas_0m_Reps_Avg}\\
-	\caption[Wall heat fluxes along the centerline of the gasoline fueled burner]{Wall heat fluxes along the centerline of the gasoline fueled burner.
-The heat fluxes are averages of three replicate experiments.
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
+	\label{NCTW_HF_Center_Comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Offset_Avg} \\
+	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Offset_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Offset_Avg} \\
+
+	\caption[Wall heat flux along the edge of the burners]{Wall heat fluxes along the edge of the burners.
+The heat fluxes are averages of replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left position and moving from left to right the distances are 0.61~m, 0.31~m,0.15~m,and 0~m.}
-	\label{IW_HFC_TWGAS}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/NCTW_NG_HF_Center_Avg}\\
-	\caption[Summary of wall heat fluxes along the centerline of the natural gas fueled burner]{Summary of the heat flux to the non-combustible wall along the verticle centerline of the natural gas fueled burner compared to the position away from the wall.}
-	\label{nctw_ng_heatflux}
-\end{figure}
-
-\subsection{Fire Pattern}
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
+	\label{NCTW_HF_Edge_Comp}
+\end{figure}
 

### 2015-04-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update latex

@@
 
-Figure~\ref{HRR} shows the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires.
+Figures~\ref{HRR}-\ref{HRR2} show the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires.
 In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.
 
-\begin{figure}[p]
-  \centering
-  \includegraphics[width=4.5in]{../Figures/Fig3}\\
-  \includegraphics[width=4.5in]{../Figures/Fig4}\\
-  \includegraphics[width=4.5in]{../Figures/Fig5}\\
-  \caption[Heat release rates for the natural gas, gasoline and foam fires]{Heat release rates for the natural gas, gasoline, and foam fires.}
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/ST_NG_HRR}\\
+  \includegraphics[width=4.5in]{../Figures/ST_Gas_HRR}\\
+  \caption[Heat release rates for the natural gas and gasoline foam fires]{Heat release rates for the natural gas and gasoline fires.}
   \label{HRR}
@@
 
-On each fuel’s averaged heat release rate curve, a bar representing the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+\begin{figure}[h!]
+  \centering
+  \includegraphics[width=4.5in]{../Figures/ST_PUF_HRR}\\
+  \caption[Heat release rates for the polyurethane foam fires]{Heat release rates for the polyurethane foam fires.}
+  \label{HRR2}
+\end{figure}
+
+On each fuel’s averaged heat release rate curve, the filled area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
@@
 	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p15m_Reps_Avg}\\
 	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
@@
 	\centering
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_61m_Reps_Avg}\\
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_31m_Reps_Avg}\\
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0_15m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p61m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p31m_Reps_Avg}\\
+		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p15m_Reps_Avg}\\
 		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
@@
 	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p15m_Reps_Avg}\\
 	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
@@
 	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0_15m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p61m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p31m_Reps_Avg}\\
+	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p15m_Reps_Avg}\\
 	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
@@
 Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m.
-As in the data analysis for the source fires, the peak averages were based on a 30 s period bounding the peak for the natural gas and gasoline fires.
-A 15 s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.
+As in the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.
+A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.
 
@@
 	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\
-
 	\caption[Composite graph of the wall temperatures along the edge of the burners]{Composite graph of the wall temperatures along the edge of the burners for each fuel.
@@
 	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\
-
 	\caption[Composite graph of the backside wall temperatures along the center of the burners]{Composite graph of the backside wall temperatures along the vertical centerline of the burners for each fuel.
@@
 	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Center_Avg} \\
-
 	\caption[Wall heat flux along the centerline of the burners]{Wall heat fluxes along the centerline of the burners.
@@
 	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Offset_Avg} \\
-
 	\caption[Wall heat flux along the edge of the burners]{Wall heat fluxes along the edge of the burners.

### 2015-04-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Latex cleanup

@@
 At each 10~cm interval, there were five thermocouples: one centered above the burner/fuel surface and one centered above each edge of the burner/fuel surface, for a total of 70 thermocouples.
-A plumb bob and steel tape measure, with a resolution of $\pm$ 0.5~mm, were used to position and align the thermocouples.
-The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$ 2.5~\%.
+A plumb bob and steel tape measure, with a resolution of $\pm$~0.5~mm, were used to position and align the thermocouples.
+The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$~2.5~\%.
 The same applies to the location of the heat flux sensor surfaces.
@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW $\pm$ 9~kW with an average total heat release of 23.3~MJ $\pm$ 1.6~MJ over a 300~s period.
-The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW $\pm$ 24~kW.
-The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ $\pm$ 0.6~MJ.
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 300~s period.
+The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW~$\pm$~24~kW.
+The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
 The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW $\pm$ 21~kW.
-The total heat release over the 300~s period after ignition was 4.1~MJ $\pm$ 0.2~MJ
+Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW~$\pm$~21~kW.
+The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ
 

### 2015-04-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added text Chapter 3 for graphs.

@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 300~s period.
-The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 17 experiments, provided an average peak heat release rate of 80~kW~$\pm$~24~kW.
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ or 11~\% over a 100~s period.
+It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
+The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments, provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 20~\%.
 The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
 The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW~$\pm$~21~kW.
+Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 34~\%.
 The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ
@@
 
-The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels in Appendix X.
+The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels in Appendix B.
 For the natural gas fueled experiments only two replicates were conducted at each position given the higher level of control and repeatability.
@@
 Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels.
-The beads of the thermocouples were installed in the wall and were flush with the wall surface.
+Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner was moved away from the wall.
+The figures  The beads of the thermocouples were installed in the wall and were flush with the wall surface.
 In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown.
 Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m.
-As in the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.
+As with the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.
 A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.
+
+Figure~\ref{NCTW_Surf_Edge_comp} presents the temperature of the vertical array of thermocouples positioned on the wall along the edge of the burner for each of the three fuels.
+The data is treated in the same manner as in Figure~\ref{NCTW_Surf_Center_comp}.
+For each fuel the average peak temperatures at the burner edge are significantly lower when the centerline temperatures when the burner is positioned against the wall.
+As the burners were moved away from the wall the temperatures at the centerline and the edge thermocouple arrays begin to converge.
+
+Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\{NCTW_Back_Cent_comp}.
+The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner vs the corresponding temperatures on the backside of the wall have a difference of at least 400~$^\circ$C.
+It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp}, that as the burners were moved away from the wall the temperature differences are reduced.
 
@@
 
-Figure~\ref{NCTW_HF_Center_Comp} shows the results from the array of total heat flux gauges located along the vertical centerline of the burners for each fuel.
+Figures~\ref{NCTW_HF_Center_Comp} and {NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.
 The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
@@
 Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.
+Reviewing the graph for each fuel demonstrates how the heat flux at the wall decreased as the position of the burner was moved away from the wall.
+(Review video and tie in ST TC graph with edge peak NG at 0.15)
 

### 2015-04-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Working on Chapter 4 text

@@
 \section{Experimental Arrangement}
+This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.
 A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
@@
 If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
+
+The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.
+The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~ref\{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
+A thermocouple installed in this manner shown in Figure~ref\
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
+	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
+Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
+	\label{Instrumented_GB_Wall}
+\end{figure}
 

### 2015-04-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Cleanup HF data, add script, figures, remove old figures, update latex

@@
 
-\begin{figure}[h!]
+\begin{figure}[!ht]
   \centering
@@
   \centering
-  \includegraphics[width=4.5in]{../Figures/Fig9}\\
-  \includegraphics[width=4.5in]{../Figures/Fig10}\\
-  \includegraphics[width=4.5in]{../Figures/Fig11}\\
+  \includegraphics[width=3.5in]{../Figures/HF_NG}\\
+  \includegraphics[width=3.5in]{../Figures/HF_GAS}\\
+  \includegraphics[width=3.5in]{../Figures/HF_PUF}\\
   \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
@@
 These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
+
 \begin{figure}
@@
 
-Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\{NCTW_Back_Cent_comp}.
+Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\ref{NCTW_Back_Cent_comp}.
 The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner vs the corresponding temperatures on the backside of the wall have a difference of at least 400~$^\circ$C.
@@
 	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\
-
 	\caption[Composite graph of the wall temperatures along the centerline of the burners]{Composite graph of the wall temperatures along the centerline of the burners for each fuel.
@@
 
-Figures~\ref{NCTW_HF_Center_Comp} and {NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.
+Figures~\ref{NCTW_HF_Center_Comp} and \ref{NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.
 The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
@@
 \chapter{Instrumented Gypsum Board Wall Experiments}
-Purpose
+
 \section{Experimental Arrangement}
@@
 The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.
-The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~ref\{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
-A thermocouple installed in this manner shown in Figure~ref\
+The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
+A thermocouple installed in this manner shown in Figure {\bf fig reference}
 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
-	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
+% \begin{figure}
+% 	\centering
+% 	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
+% 	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
 Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
-	\label{Instrumented_GB_Wall}
-\end{figure}
+% 	\label{Instrumented_GB_Wall}
+% \end{figure}
 

### 2015-04-02 Projects/Madrzykowski_Thesis/Plot_Scripts/heatflux.py

@@ -1,0 +1,32 @@
+from __future__ import division
+import numpy as np
+import numpy.ma as ma
+import pandas as pd
+import itertools
+from pylab import *
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+data_dir = '../Experimental_Data/FHGAS/'
+plot_dir = '../Figures/'
+test_name = 'HF_GAS'
+data = pd.read_csv(data_dir + test_name + '.csv',header=0)
+data2 = pd.read_csv(data_dir + test_name + '.csv',header=0,index_col=0)
+
+markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
+colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
+
+fig = figure()
+for i in range(data.shape[1]-1):
+	y = data.iloc[:,i+1]
+	plot(data['Time (s)'],y,color=colors[i],marker=markers[i],markevery=50,ms=8,label=data.columns[i+1])
+plot(data['Time (s)'],data2.mean(axis=1),'k',label=test_name+'_AVG',linewidth=3)
+ax1 = gca()
+xlabel('Time (s)', fontsize=20)
+ylabel('Heat Flux (kW/m$^2$)', fontsize=20)
+xticks(fontsize=16)
+yticks(fontsize=16)
+legend(numpoints=1,loc=1,ncol=1,fontsize=16)
+axis([0, 300, 0, 6])
+savefig(plot_dir + test_name + '.pdf',format='pdf')
+close()

### 2015-04-02 Projects/Madrzykowski_Thesis/Plot_Scripts/hrr.py

@@ -9,11 +9,11 @@ rcParams.update({'figure.autolayout': True})
 
 data_dir = '../Experimental_Data/STHRR/'
 plot_dir = '../Figures/'
-test_name = 'ST_Gas_HRR'
+test_name = 'ST_NG_HRR'
 data = pd.read_csv(data_dir + test_name + '.csv', header=0)
 data2 = pd.read_csv(data_dir + test_name + '.csv', header=0,index_col=0)
 
-fuel = 'Gas_'
+fuel = test_name[3:-3]
 markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
 colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
 
@@ -26,9 +26,11 @@ for i in range(data.shape[1]-1):
 plot(data['Time (s)'],data2.mean(axis=1),'k',label=fuel+'_AVG',linewidth=3)
 plt.fill_between(data['Time (s)'],data2.mean(axis=1)+2*data2.std(axis=1), data2.mean(axis=1)-2*data2.std(axis=1), facecolor='gray',alpha=0.5, interpolate=True,linewidth=3)
 ax1 = gca()
-xlabel('Time (s)')
-ylabel('Heat Release Rate (kW)')
-legend(numpoints=1,loc=1,ncol=2)
+xlabel('Time (s)', fontsize=20)
+ylabel('Heat Release Rate (kW)', fontsize=20)
+xticks(fontsize=16)
+yticks(fontsize=16)
+legend(numpoints=1,loc=1,ncol=1,fontsize=16)
 axis([0, 300, 0, 120])
 savefig(plot_dir + test_name + '.pdf',format='pdf')
 close()
@@ -41,7 +43,9 @@ plot(data['Time (s)'],data2.mean(axis=1),'k',label=fuel+'_AVG',linewidth=3)
 ax1 = gca()
 xlabel('Time (s)')
 ylabel('Heat Release Rate (kW)')
-legend(numpoints=1,loc=1,ncol=2)
+xticks(fontsize=16)
+yticks(fontsize=16)
+legend(numpoints=1,loc=1,ncol=1,fontsize=16)
 axis([0, 300, 0, 120])
[…]

### 2015-04-02 Projects/Madrzykowski_Thesis/Plot_Scripts/hrr.py
Add mass loss files, plots, script, update latex, remove old figures

@@ -9,11 +9,15 @@ rcParams.update({'figure.autolayout': True})
 
 data_dir = '../Experimental_Data/STHRR/'
 plot_dir = '../Figures/'
-test_name = 'ST_NG_HRR'
+test_name = 'ST_PUF_HRR'
 data = pd.read_csv(data_dir + test_name + '.csv', header=0)
 data2 = pd.read_csv(data_dir + test_name + '.csv', header=0,index_col=0)
 
 fuel = test_name[3:-3]
+if 'Gas' in str(fuel):
+	col = 2
+else:
+	col = 1
 markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
 colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
 
@@ -30,8 +34,9 @@ xlabel('Time (s)', fontsize=20)
 ylabel('Heat Release Rate (kW)', fontsize=20)
 xticks(fontsize=16)
 yticks(fontsize=16)
-legend(numpoints=1,loc=1,ncol=1,fontsize=16)
+legend(numpoints=1,loc=1,ncol=col,fontsize=16)
 axis([0, 300, 0, 120])
+grid(True)
 savefig(plot_dir + test_name + '.pdf',format='pdf')
 close()
 
@@ -45,7 +50,8 @@ xlabel('Time (s)')
 ylabel('Heat Release Rate (kW)')
 xticks(fontsize=16)
 yticks(fontsize=16)
-legend(numpoints=1,loc=1,ncol=1,fontsize=16)
+legend(numpoints=1,loc=1,ncol=col,fontsize=16)
 axis([0, 300, 0, 120])
+grid(True)
 savefig(plot_dir + test_name + '_nosigma.pdf',format='pdf')
 close()

### 2015-04-02 Projects/Madrzykowski_Thesis/Plot_Scripts/massloss.py

@@ -7,14 +7,19 @@ from pylab import *
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
 
-data_dir = '../Experimental_Data/FHPUF/'
+data_dir = '../Experimental_Data/FHGAS/'
 plot_dir = '../Figures/'
-test_name = 'HF_PUF'
+test_name = 'ML_GAS'
 data = pd.read_csv(data_dir + test_name + '.csv',header=0)
 data2 = pd.read_csv(data_dir + test_name + '.csv',header=0,index_col=0)
 
 markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
 colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
+
+if 'ML_GAS' in str(test_name):
+	location = 4
+else:
+	location = 1
 
 fig = figure()
 for i in range(data.shape[1]-1):
@@ -23,11 +28,11 @@ for i in range(data.shape[1]-1):
 plot(data['Time (s)'],data2.mean(axis=1),'k',label=test_name+'_AVG',linewidth=3)
 ax1 = gca()
 xlabel('Time (s)', fontsize=20)
-ylabel('Heat Flux (kW/m$^2$)', fontsize=20)
+ylabel('Mass Loss (kg)', fontsize=20)
 xticks(fontsize=16)
 yticks(fontsize=16)
-legend(numpoints=1,loc=1,ncol=1,fontsize=16)
-axis([0, 300, 0, 6])
+legend(numpoints=1,loc=location,ncol=1,fontsize=16)
+axis([0, 300, 0, 0.4])
 grid(True)
 savefig(plot_dir + test_name + '.pdf',format='pdf')
 close()

### 2015-04-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add mass loss files, plots, script, update latex, remove old figures

@@
   \centering
-  \includegraphics[width=4.5in]{../Figures/Fig12}\\
-  \includegraphics[width=4.5in]{../Figures/Fig13}\\
+  \includegraphics[width=4.5in]{../Figures/ML_GAS}\\
+  \includegraphics[width=4.5in]{../Figures/ML_PUF}\\
   \caption[Mass loss versus time for the gasoline and foam fueled fires]{Mass loss versus time for the gasoline and foam fueled fires.}
@@
 
-The thermocouple arrangement for these experiments, only had one vertical array of thermocouples.
-The thermocouples were positioned between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}  As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled on the horizontal centerline between the heat flux gauges and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
-A thermocouple installed in this manner shown in Figure {\bf fig reference}
+The thermocouple arrangement for these experiments had one vertical array of thermocouples installed on the wall.
+The thermocouples were centered between the two vertical arrays of heat flux gauges as shown in Figure~\ref{Instrumented_GB_Wall}.
+As a means of ensuring contact between the gypsum wallboard and the thermocouple, the thermocouples were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
+A thermocouple installed in this manner shown in Figure~\ref{IWGB_TC_Slit}.
 
@@
 
-% \begin{figure}
-% 	\centering
-% 	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
-% 	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
-Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
-% 	\label{Instrumented_GB_Wall}
-% \end{figure}
+ \begin{figure}
+ 	\centering
+ 	\includegraphics[width=\textwidth]{../Figures/IWGB_TC_Slit}\\
+ 	\caption[Photograph of a thermocouple embedded in the gypsum wallboard]{Photograph of a nominal 0.5 mm thermocouple bead embedded in the gypsum wallboard.}
+ 	\label{IWGB_TC_Slit}
+ \end{figure}
 

### 2015-04-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update latex
add ng time avg plots, script and update latex

@@
   \centering
-  \includegraphics[width=4.5in]{../Figures/Fig6}\\
-  \includegraphics[width=4.5in]{../Figures/Fig7}\\
-  \includegraphics[width=4.5in]{../Figures/Fig8}\\
+  \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
+  \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
+  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
   \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0p15m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Plume_TWNG_0m_Reps_Avg}\\
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Plume_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Plume_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Plume_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Plume_Avg}\\
 	\caption[Plume temperatures along the centerline of the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.
@@
 
-\begin{figure}[p]
-	\centering
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p61m_Reps_Avg}\\
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p31m_Reps_Avg}\\
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0p15m_Reps_Avg}\\
-		\includegraphics[width=3.in]{../Figures/TC_Surface_Center_TWNG_0m_Reps_Avg}\\
+\begin{figure}[ht!]
+	\centering
+		\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Surface_Center_Avg}
+		\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Surface_Center_Avg}\\
+		\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Surface_Center_Avg}
+		\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Surface_Center_Avg}\\
 	\caption[Wall Temperatures along the centerline of the natural gas fueled burner]{Wall Temperatures along the centerline of the natural gas fueled burner.
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0p15m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Surface_Offset_TWNG_0m_Reps_Avg}\\
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Surface_Offset_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Surface_Offset_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Surface_Offset_Avg}\\
 	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall.
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p61m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p31m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0p15m_Reps_Avg}\\
-	\includegraphics[width=3.in]{../Figures/TC_Back_Center_TWNG_0m_Reps_Avg}\\
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/TWNG01_TC_Back_Center_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG03_TC_Back_Center_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG05_TC_Back_Center_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Back_Center_Avg}\\
 	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner.

### 2015-04-03 Projects/Madrzykowski_Thesis/Plot_Scripts/temp_ng_plume.py

@@ -1,0 +1,121 @@
+from __future__ import division
+
+import os
+import numpy as np
+import numpy.ma as ma
+import pandas as pd
+from pylab import *
+import math
+import string
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+# Location of files
+data_dir = '../Experimental_Data/TWNG/'
+plot_dir = '../Figures/'
+info_file = '../Experimental_Data/TWNG/Description_of_NG_Tests.csv'
+
+# List of sensor groups for each plot
+sensor_groups = [['TC Plume'],['TC Surface Center'],['TC Surface Offset'],['TC Back Center']]
+
+
+# Load exp. timings and description file
+info = pd.read_csv(info_file,header=0, index_col=0)
+# Skip files
+skip_files = ['description_','nctw_']
+
+#  =========================
+#  = Reading in Data Files =
+#  =========================
+
+markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
+colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
+label_plume = ['TC Plume 0.4m','TC Plume 0.6m','TC Plume 0.8m','TC Plume 1.0m','TC Plume 1.2m','TC Plume 1.4m',
+			'TC Plume 1.6m','TC Plume 1.8m','TC Plume 2.0m','TC Plume 2.2m','TC Plume 2.4m']
+label_surf_cen = ['TC Front Center 0.2m','TC Front Center 0.4m','TC Front Center 0.6m','TC Front Center 0.8m','TC Front Center 1.0m',
+					'TC Front Center 1.2m','TC Front Center 1.4m','TC Front Center 1.6m','TC Front Center 1.8m','TC Front Center 2.0m','TC Front Center 2.2m']
+label_surf_off = ['TC Front Edge 0.2m','TC Front Edge 0.4m','TC Front Edge 0.6m','TC Front Edge 0.8m','TC Front Edge 1.0m',
+					'TC Front Edge 1.2m','TC Front Edge 1.4m','TC Front Edge 1.6m','TC Front Edge 1.8m','TC Front Edge 2.0m','TC Front Edge 2.2m']
[…]

### 2015-04-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added text to Ch 4  Broke Bibtek

@@
 
-\Title{Repeatability of Pre-Flashover Fire Patterns on Gypsum Wall Board}
+\Title{Repeatability of Pre-Flashover Fire Patterns on Gypsum Wallboard}
 \Author{Daniel Madrzykowski}
@@
 90~\% of the board is composed of calcium silicate and calcium meta-silicate.
-The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz) ref BNZ MSDS.
-Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below ref BNZ Marinite I.
+The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:2012}.
+Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below~\cite{Marinite:1997}.
 
@@
 \end{tabular}
-\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ Marinite I.}
+\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}
 \label{tab:Marinite_Thermal_Properties}
@@
 Figures~\ref{TC_Plume_TWNG_comp} through \ref{TC_Back_Center_TWNG_comp} show a complete set of data, averaged over two replicates, for the instrumented, non combustible wall natural gas burner experiments.
+Comparing the temperatures of the plume at the most distant point from the wall, 0.61~m and with the plume temperatures with the burner contacting the wall in Figure~\ref{TC_Plume_TWNG_comp} shows an increase.
+However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs after approximately 3 minutes after ignition.
+A review of the heat release rates and the test videos do not yield an clues as to the reason for this decrease which occurred in both experiments.
+In both experiments the heat release rate was steady and the video did not show any change in flame movement.
+Figures~\ref{TC_Surf_Cent_TWNG_comp} and \ref{TC_Surf_Edge_TWNG_comp} show consistent trends of the thermocouple temperatures in the vertical arrays on the wall increasing as the burner was moved toward the wall.
+Figure~\ref{TC_Back_Center_TWNG_comp} shows that the peak temperatures aligned with the vertical center of the burner on the backside of the gypsum wallboard peaked at approximately 100~$^\circ$C.
 
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
 	\label{TC_Plume_TWNG_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
 	\label{TC_Surf_Cent_TWNG_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
 	\label{TC_Surf_Edge_TWNG_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top graph position and moving down the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
 	\label{TC_Back_Center_TWNG_comp}
 \end{figure}
+
+Figures~\ref{HF_Center_TWNG_comp} and \ref{HF_Edge_TWNG_comp} provide the heat flux measurements for the two vertical arrays of gauges positioned along the centerline and the edge of the natural gas burner.
+The series of graphs show that the peak heat flux increases by as the burner is moved toward the wall.
+One exception is when the burner was moved from the 0.15~m position to the 0.0~m from the wall.
+In this comparison the peak heat flux values for the gauges located above the edge of the burner do not uniformly increase.
+In fact the peak heat flux actually decreased as the burner was moved from the 0.15~m position to the 0.0~m position.
+This decrease was due to the change in view angle between the flame closest to the burner and the lower heat flux gauges at the edge of the burner.
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.61m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.31m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.15m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0m_Reps_Avg}\\
+	\caption[Heat flux at the wall along the centerline of the natural gas fueled burner]{Heat flux at the wall along the centerline of the natural gas fueled burner.
+The heat fluxes are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+	\label{HF_Center_TWNG_comp}
+\end{figure}
+
+\begin{figure}[ht!]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.61m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.31m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.15m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0m_Reps_Avg}\\
+	\caption[Heat flux at the wall along the edge of the natural gas fueled burner]{Heat flux at the wall along the edge of the natural gas fueled burner.
+The heat fluxes are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+	\label{HF_Edge_TWNG_comp}
+\end{figure}
+
+In the following sections, the data is compiled so that averaged peak values, of a given measure, for each position from the wall will be presented on a single graph for a given fuel type.
 
@@
 Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner was moved away from the wall.
-The figures  The beads of the thermocouples were installed in the wall and were flush with the wall surface.
+The beads of the thermocouples were installed in the wall and were flush with the wall surface.
 In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown.
@@
 
+\Section{Summary}
+
+These instrumented non-combustible wall experiments provide a data set for the fires conducted that can be compared against ignition data for gypsum wallboard from the literature to determine the potential for ignition of the paper surface of gypsum wallboard at a given distance from the wall with a given fuel.
+The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
+Table 19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate source.
+Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321},\cite{Quitiere:1984}.
+The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565 $\^circ$C with a critical heat flux for ignition of 35~kW/m^2.
+
+The second source, was a series of cone calorimeter experiments conducted by Dillion~\cite{ASTM_E1354},~\cite{Dillion:1998}.
+The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.5~mm thick was 515 $\^circ$C with a minimum heat flux required for ignition of 26~kW/m^2.
+
+A review of the graphs of the peak average temperatures at the wall, burner centerline array, shows that all of the fuels had at least one thermocouple position with a peak of approximately 500 $\^circ$C when the burner was against the wall.
+At 0.15~m away from the wall the peak average temperature from this data set was provided by the gasoline fueled fire and it was approximately 350 $\^circ$C.
+Based on temperature alone, the fires examined would only have the potential to ignite the paper surface of the gypsum wallboard when the burner was in contact with the wall.
+The peak average temperatures at the wall, burner edge array, would indicate that the paper may not ignite at the burner edge.
+The peak average temperature of approximately 400 $\^circ$C was generated by the gasoline fueled fire when the burner was positioned against the wall.
+
+Of course the temperatures of the thermocouples in the wall as a result the of the energy transferred to the wall and the thermo-physical properties of the wall material.
+Assuming that the properties of calcium silicate board and the gypsum board are similar, let's review the heat flux graphs.
+All of the fuels generated heat fluxes in excess of 35~kW/m^2 at the wall, burner centerline array when the burners were against the wall.
+The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/^2 at 0.15~m from the wall.
+However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
+
 \chapter{Instrumented Gypsum Board Wall Experiments}
@@
 This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.
+These experiments enable us to examine our ignition/no ignition predictions from the previous experiments.
 A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
@@
 The burner was moved toward the wall until the burner was against the wall.
-If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
+If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the experiments in the study.
 
@@
 A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.
-As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to recieve decoration  ref ATSM 1396.
+As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration  ref ATSM 1396.
 The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
@@
 The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.
+Each 1.22~m by 2.44~m by 12.7~mm thick panel weighed approximately 30.5~kg.
 The physical features of the gypsum wallboard panels are given in the table below.
@@
 After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
-The first coat was a latex primer.
-Once the primer dried a top coat of white latex paint was applied.
-After the panels dried paint thickness measurements were made with a ultra sonic XXXX.
+The first coat was a latex primer, http://buyat.ppg.com/rep_pafpainttools_files/Pghpaints/tdb/78200.pdf.
+Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep_pafpainttools_files/Olympic/tdb/78010.pdf .
+After the panels dried, they were weighed.
+The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg.
+Then the paint thickness was estimated an ultra sonic XXXX cite - in office, the thickness of the paint varied from 0.05~mm to 0.13~mm.
+
 Some of the panels were then cut-up into samples think about this perhaps this goes into the FP Comp

### 2015-04-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Continuing with Ch4

@@
 A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.
-As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration  ref ATSM 1396.
+As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}.
 The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
@@
 
-The gypsum wallboard used in these experiments is referred to as ``regular'' as opposed to a gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
+The gypsum wallboard used in these experiments is referred to as `regular' as opposed to gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
 The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.
@@
 The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg.
-Then the paint thickness was estimated an ultra sonic XXXX cite - in office, the thickness of the paint varied from 0.05~mm to 0.13~mm.
-
-Some of the panels were then cut-up into samples think about this perhaps this goes into the FP Comp
+Then the paint thickness was estimated an ultra sonic XXXX cite - in office.
+Over the course of the experiments, random painted panels where checked with the ultra sonic device.
+The thickness of the paint varied from 0.05~mm to 0.13~mm.
+Some of the painted panels were then cut-up into samples for the bench-scale experiments.
 
@@
 
-The first series of experiments were conducted with the natural gas burner.
+In this chapter, as in the previous chapter the averaged peak values for temperatures and heat fluxes will presented at varying distances from the wall.
+Figures~\ref{IWGB_NG_Temp_FrontSet},\ref{IWGB_NG_Temp_RearCenter} and \ref{IWGB_NG_HF_RearCenter} show the values for the natural gas burner experiments with the gypsum wallboard.
 

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Continued editting ch 4

@@
 This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.
+These experiments were conducted in a similar manner as the non-combustible instrumented wall experiments, the only new variable is the painted, gypsum wallboard.
 These experiments enable us to examine our ignition/no ignition predictions from the previous experiments.
@@
 	\includegraphics[width=\textwidth]{../Figures/Instrumented_GB_Wall}\\
-	\caption[Diagram of the instrumented non-combustible wall]{Diagram of the instrumented non-combustible wall.
-Two vertical arrays of total heat flux gauges and thermocouples were installed along the centerline of the burner and along the right edge of the burner.}
+	\caption[Diagram of the instrumented gypsum wallboard]{Diagram of the instrumented gypsum wallboard.
+Two vertical arrays of total heat flux gauges were installed along the centerline of the burner and along the right edge of the burner.
+A single vertical array of thermocouples was installed centered between the heat flux gauges.}
 	\label{Instrumented_GB_Wall}
@@
 
+The complete set of results from the instrumented gypsum wallboard experiments are provided in Appendix C.
+Table ~\ref{tab:IWGB_experiments}    lists the experiments that were conducted for each fuel type.
 In this chapter, as in the previous chapter the averaged peak values for temperatures and heat fluxes will presented at varying distances from the wall.
+For the gasoline and polyurethane fires, an additional position, 0.08~m from the wall was added.
+
 Figures~\ref{IWGB_NG_Temp_FrontSet},\ref{IWGB_NG_Temp_RearCenter} and \ref{IWGB_NG_HF_RearCenter} show the values for the natural gas burner experiments with the gypsum wallboard.
+Revise to match Ch 3 set
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
+		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\
+		\hline 0.61 				& 0 				& 1 				& 2 			 	\\
+		\hline 0.31					& 3	 				& 1					& 2 			 	\\
+		\hline 0.15					& 1				 	& 1					& 2 			 	\\
+		\hline 0.08					& 0 				& 1 				& 2 	 			\\
+		\hline 0.00					& 1 				& 1 				& 3 	 			\\
+		\hline
+	\end{tabular}
+	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
+	\label{tab:IWGB_experiments}
+\end{table}
 
@@
 
-Comparisons NG to Gas to PUF
+The averaged peak temperatures of the wall mounted thermocouples for the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
 
@@
 	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
-	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
-The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperatures, beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
 	\label{IWGB_Temp_Comp_FrontCenter}
@@
 \subsection{Heat Flux}
+
+Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays.
+For the gasoline fire experiment at the 0.08~m position the wall temperatures and the heat flux values from the burner edge array had values that were higher than when those measured at the 0.0 m position.
+The peak heat release rates for the positions at 0.0~m, 0.08~m and 0.15~m were 120~kW, 110~kW, and 110~kW respectively.
+So it does not seem that a change in HRR was the source of the increase.
 
@@
 	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
-	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
-The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\caption[Averaged burner centerline heat flux for the natural gas, gasoline, and foam fires]{Averaged burner centerline heat flux, beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
 	\label{IWGB_HF_Comp_Center}
@@
 	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
-	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
-The number following the TC represents the height of thermocouple in decimeters  above the surface of the burner.}
+	\caption[Averaged burner edge heat flux for the natural gas, gasoline, and foam fires]{Averaged burner edge heat flux for the natural gas, gasoline, and foam fires, from the top down.}
 	\label{IWGB_HF_Comp_Edge}
@@
 \subsection{Fire Pattern}
+
+trim photo sets added here and compare with temps and HF
 
@@
 
-The rear wall of the compartment was constructed in the same manner for a given set of experiments.
 The burner was centered on the middle panel of the rear wall.
+The wall behind the center panel of the rear wall was insulated to met the needs of the experiment.
 As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update figure names to remove ., update latex and bib file

@@
 90~\% of the board is composed of calcium silicate and calcium meta-silicate.
-The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:2012}.
+The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:MSDS}.
 Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below~\cite{Marinite:1997}.
@@
 \end{tabular}
-\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}
+\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ3~\cite{Marinite:1997}}
 \label{tab:Marinite_Thermal_Properties}
@@
 	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.61m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.31m_Reps_Avg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0.15m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p61m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p31m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p15m_Reps_Avg}
 	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0m_Reps_Avg}\\
@@
 	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.61m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.31m_Reps_Avg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0.15m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p61m_Reps_Avg}
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p31m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p15m_Reps_Avg}
 	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0m_Reps_Avg}\\
@@
 
-\Section{Summary}
+\section{Summary}
 
@@
 Table 19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate source.
-Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321},\cite{Quitiere:1984}.
-The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565 $\^circ$C with a critical heat flux for ignition of 35~kW/m^2.
-
-The second source, was a series of cone calorimeter experiments conducted by Dillion~\cite{ASTM_E1354},~\cite{Dillion:1998}.
-The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.5~mm thick was 515 $\^circ$C with a minimum heat flux required for ignition of 26~kW/m^2.
-
-A review of the graphs of the peak average temperatures at the wall, burner centerline array, shows that all of the fuels had at least one thermocouple position with a peak of approximately 500 $\^circ$C when the burner was against the wall.
-At 0.15~m away from the wall the peak average temperature from this data set was provided by the gasoline fueled fire and it was approximately 350 $\^circ$C.
+Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321,Quintiere:1985}.
+The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565~$^{\circ}$C with a critical heat flux for ignition of 35~kW/m$^2$.
+
+The second source, was a series of cone calorimeter experiments conducted by Dillon~\cite{ASTM_E1354,Dillon:1998}.
+The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.5~mm thick was 515~$^{\circ}$C with a minimum heat flux required for ignition of 26~kW/m$^2$.
+
+A review of the graphs of the peak average temperatures at the wall, burner centerline array, shows that all of the fuels had at least one thermocouple position with a peak of approximately 500~$^{\circ}$C when the burner was against the wall.
+At 0.15~m away from the wall the peak average temperature from this data set was provided by the gasoline fueled fire and it was approximately 350~$^{\circ}$C.
 Based on temperature alone, the fires examined would only have the potential to ignite the paper surface of the gypsum wallboard when the burner was in contact with the wall.
 The peak average temperatures at the wall, burner edge array, would indicate that the paper may not ignite at the burner edge.
-The peak average temperature of approximately 400 $\^circ$C was generated by the gasoline fueled fire when the burner was positioned against the wall.
+The peak average temperature of approximately 400~$^{\circ}$C was generated by the gasoline fueled fire when the burner was positioned against the wall.
 
@@
 Assuming that the properties of calcium silicate board and the gypsum board are similar, let's review the heat flux graphs.
-All of the fuels generated heat fluxes in excess of 35~kW/m^2 at the wall, burner centerline array when the burners were against the wall.
-The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/^2 at 0.15~m from the wall.
+All of the fuels generated heat fluxes in excess of 35~kW/m$^2$ at the wall, burner centerline array when the burners were against the wall.
+The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/$^2$ at 0.15~m from the wall.
 However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
@@
 		\hline Density & \multicolumn{2}{c|}{Thermal Conductivity}   & \multicolumn{2}{c|}{Specific Heat}  \\
-		\hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\
+		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\
 		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\
@@
 After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
-The first coat was a latex primer, http://buyat.ppg.com/rep_pafpainttools_files/Pghpaints/tdb/78200.pdf.
-Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep_pafpainttools_files/Olympic/tdb/78010.pdf .
+The first coat was a latex primer, http://buyat.ppg.com/rep\_pafpainttools\_files/Pghpaints/tdb/78200.pdf.
+Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep\_pafpainttools\_files/Olympic/tdb/78010.pdf.
 After the panels dried, they were weighed.
@@
 The complete set of results from the instrumented gypsum wallboard experiments are provided in Appendix C.
-Table ~\ref{tab:IWGB_experiments}    lists the experiments that were conducted for each fuel type.
+Table~\ref{tab:IWGB_experiments} lists the experiments that were conducted for each fuel type.
 In this chapter, as in the previous chapter the averaged peak values for temperatures and heat fluxes will presented at varying distances from the wall.
@@
 	\hline
-	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m $^2$)  \\ \hline
+	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline
 		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Update figures, add HF NG figures, update plotting script and latex.

@@
 	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p61m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p31m_Reps_Avg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0p15m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Center_TWNG_0m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG01_HF_Center_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG03_HF_Center_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG05_HF_Center_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG07_HF_Center_Avg}\\
 	\caption[Heat flux at the wall along the centerline of the natural gas fueled burner]{Heat flux at the wall along the centerline of the natural gas fueled burner.
@@
 	\centering
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p61m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p31m_Reps_Avg}\\
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0p15m_Reps_Avg}
-	\includegraphics[width=2.5in]{../Figures/HF_Offset_TWNG_0m_Reps_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG01_HF_Offset_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG03_HF_Offset_Avg}\\
+	\includegraphics[width=2.5in]{../Figures/TWNG05_HF_Offset_Avg}
+	\includegraphics[width=2.5in]{../Figures/TWNG07_HF_Offset_Avg}\\
 	\caption[Heat flux at the wall along the edge of the natural gas fueled burner]{Heat flux at the wall along the edge of the natural gas fueled burner.

### 2015-04-06 Projects/Madrzykowski_Thesis/Plot_Scripts/temp_ng_plume.py

@@ -17,7 +17,7 @@ plot_dir = '../Figures/'
 info_file = '../Experimental_Data/TWNG/Description_of_NG_Tests.csv'
 
 # List of sensor groups for each plot
-sensor_groups = [['TC Plume'],['TC Surface Center'],['TC Surface Offset'],['TC Back Center']]
+sensor_groups = [['TC Plume'],['TC Surface Center'],['TC Surface Offset'],['TC Back Center'],['HF Center'],['HF Offset']]
 
 
 # Load exp. timings and description file
@@ -30,7 +30,7 @@ skip_files = ['description_','nctw_']
 #  =========================
 
 markers = ['s', '*', '^', 'o', '<', '>', '8', 'h','d','x','p','v','H', 'D', '1', '2', '3', '4', '|']
-colors=['r', 'b', 'g', 'c', 'm', '0.75', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
+colors=['r', 'b', 'g', 'c', 'm', 'grey', 'y','#cc5500', '#228b22','#f4a460','#4c177d','firebrick', 'mediumblue', 'darkgreen', 'cadetblue', 'indigo', 'crimson', 'gold']
 label_plume = ['TC Plume 0.4m','TC Plume 0.6m','TC Plume 0.8m','TC Plume 1.0m','TC Plume 1.2m','TC Plume 1.4m',
 			'TC Plume 1.6m','TC Plume 1.8m','TC Plume 2.0m','TC Plume 2.2m','TC Plume 2.4m']
 label_surf_cen = ['TC Front Center 0.2m','TC Front Center 0.4m','TC Front Center 0.6m','TC Front Center 0.8m','TC Front Center 1.0m',
@@ -39,6 +39,8 @@ label_surf_off = ['TC Front Edge 0.2m','TC Front Edge 0.4m','TC Front Edge 0.6m'
 					'TC Front Edge 1.2m','TC Front Edge 1.4m','TC Front Edge 1.6m','TC Front Edge 1.8m','TC Front Edge 2.0m','TC Front Edge 2.2m']
 label_back_cen = ['TC Back Center 0.2m','TC Back Center 0.4m','TC Back Center 0.6m','TC Back Center 0.8m','TC Back Center 1.0m',
[…]

### 2015-04-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Cleanup Bib file and latex
Added Refs to Ch 4

@@
 \end{tabular}
-\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ3~\cite{Marinite:1997}}
+\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}}
 \label{tab:Marinite_Thermal_Properties}
@@
 According to the United States Geological Survey, most gypsum in the United States is used to make wallboards for homes and other structures.
-A typical home in the United States contains more than 7 metric tons of gypsum ref USGS website http://minerals.usgs.gov/minerals/pubs/commodity/gypsum/.
+A typical home in the United States contains more than 7 metric tons of gypsum ~\cite{USGS:2015}.
 As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}.
 The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
-By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass.
+By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass~\cite{GA:2010}.
 Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .
-By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water ref Lawson 1977.
+By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.
 
@@
 The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg.
-Then the paint thickness was estimated an ultra sonic XXXX cite - in office.
+Then the paint thickness was estimated an ultrasonic coating thickness gauge~\cite{defelsko}.
 Over the course of the experiments, random painted panels where checked with the ultra sonic device.

### 2015-04-07 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added IWBG_NG graphs and added equations still need some formatting aid

@@
 By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass~\cite{GA:2010}.
-Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$2H$_{2}$O) .
+Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$ $\bullet$ 2H$_{2}$O) .
 By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.
@@
 
-Figures~\ref{IWGB_NG_Temp_FrontSet},\ref{IWGB_NG_Temp_RearCenter} and \ref{IWGB_NG_HF_RearCenter} show the values for the natural gas burner experiments with the gypsum wallboard.
-Revise to match Ch 3 set
+Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set} and \ref{IWGB_NG_TC_Backside_set} show the values for the natural gas burner experiments with the gypsum wallboard.
 
@@
 	\centering
- 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Offset_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Plume_Avg}\\
- 	\caption[Averaged peak wall and plume temperatures for the natural gas burner]{Averaged peak wall and plume temperatures for the natural gas burner fires at several different positions from the instrumented gypsum board wall.
-The positions ranged from 0.3 m away from the wall to physically touching the wall, 0.0 m.}
- 	\label{IWGB_NG_Temp_FrontSet}
+	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Plume_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Plume_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Plume_Avg}\\
+	\caption[Plume temperatures for the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.
+Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
+Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
+	\label{IWGB_NG_TC_Plume_set}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Surface_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Surface_Center_Avg}\\
+	\caption[Front surface wall temperatures for the natural gas fueled burner]{Front surface wall temperatures for the natural gas fueled burner.
+Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
+Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
+	\label{IWGB_NG_TC_Wall_set}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Back_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Back_Center_Avg}\\
+	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Back_Center_Avg}\\
+	\caption[Backside wall temperatures for the natural gas fueled burner]{Backside wall temperatures along the centerline of the natural gas fueled burner.
+Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
+Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
+	\label{IWGB_NG_TC_Backside_set}
+\end{figure}
+
+ \begin{figure}[p]
+ 	\centering
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG01_HF_Center_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG04_HF_Center_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG05_HF_Center_Avg}\\
+ \caption[Wall heat flux along the centerline of the natural gas fueled burner]{Wall heat flux along the vertical centerline of the natural gas fueled burner.
+Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
+Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
+ 	\label{IWGB_NG_HF_CenterSet}
+ \end{figure}
+
+ \begin{figure}[p]
+ 	\centering
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG01_HF_Offset_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG04_HF_Offset_Avg}\\
+ 	\includegraphics[width=3.5in]{../Figures/IWGBNG05_HF_Offset_Avg}\\
+ 	\caption[Wall heat flux along the edge of the natural gas fueled burner]{Wall heat flux along the edge of the natural gas fueled burner.
+Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
+Beginning with the top graph and moving down, the distances from the wall are 0.31~m, 0.15~m, and 0~m.}
+ 	\label{IWGB_NG_HF_EdgeSet}
  \end{figure}
@@
 
+Ratio from heat flux from source fire data 
+vyto second item ignite
+
+$\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2) $ \\
+
+$\dot{q}''$ = heat flux per unit area $(kW/m^2)$ \\
+$\dot{Q}$ = heat release rate $(kW)$ \\
+$ \chi_r$ = radiative fraction \\
+$R$ = distance from the point source to the target $(m)$ \\
+
+Source fire plume temp and shape factor from vertical cylinder
+
+$\dot{q}'' = \epsilon \sigma F_12 T^4 $ \\
+
+$\epsilon$ = emissivity  \\
+$\sigma$ = Stefan-Boltzmann Constant $(5.670373(21)×10^(−8) W/m^2 K^4)$  \\
+
 \section{Flame Height Correlation}
 
+discuss the premise  
+McCaffery
+
+$Z_c = 0.08 dot{Q}^(2/5)$ \\
+
+$Z_i = 0.20 dot{Q}^(2/5)$ \\
+
+$Z_c$ = continuous flame height $(m)$  \\
+
+$Z_i$ = intermittent flame height $(m)$ \\
+
+Heskestad widely used  NRC CFITrainer  texts
+
 \subsection{Correlation Descriptions}
+Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.
+Appropriate fuels would “include liquid pool fires and other horizontal surface fires” add cites.
+Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad’s flame height equation directly.
+Setting the area of the fuel surface, 0.093~$m^2$, equal to π $D^2$/4 and then solving for $D$ yields an effective diameter of 0.344~m.
+Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0 m (3.3 ft), 1.0 m (3.3 ft), and 0.73 m (2.4 ft) for natural gas, gasoline, and polyurethane foam respectively.
+Taking the uncertainty of the measurements used to determine the heat release rate (±11~\%) into account generates a range of values.
+The range of calculated values are compared with the  mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.
+
+\begin{center} 
+$ H_f = 0.235\: \dot{Q}^{(2/5)} - 1.02 D $  \\
+\end{center}
+$ H_f$ = flame height (m)  \\
+$ \dot{Q}$ = heat release rate (kW) \\
+$ D$ = diameter of burner (m)  \\
 
@@
 
+Compare Natural Gas at 0.61 m from instrumented wall and at 0.0 m from instrumented wall - problem bounds.
+
 \subsection{Grid Size Analysis}

### 2015-04-07 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Fix equation formatting.

@@
 vyto second item ignite
-
-$\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2) $ \\
-
-$\dot{q}''$ = heat flux per unit area $(kW/m^2)$ \\
-$\dot{Q}$ = heat release rate $(kW)$ \\
-$ \chi_r$ = radiative fraction \\
-$R$ = distance from the point source to the target $(m)$ \\
+\begin{equation} \label{eq:second_item}
+\dot{q}'' = (\dot{Q} \chi_r)/(4 \pi\ R^2)
+\end{equation}
+where $\dot{q}''$ is the heat flux per unit area kW/m$^2$, $\dot{Q}$ is the heat release rate (kW), $\chi_r$ is the radiative fraction, and $R$ = distance from the point source to the target (m).
 
 Source fire plume temp and shape factor from vertical cylinder
-
-$\dot{q}'' = \epsilon \sigma F_12 T^4 $ \\
-
-$\epsilon$ = emissivity  \\
-$\sigma$ = Stefan-Boltzmann Constant $(5.670373(21)×10^(−8) W/m^2 K^4)$  \\
+\begin{equation}\label{eq:source_fire}
+\dot{q}'' = \epsilon \sigma F_{12} T^4  \\
+\end{equation}
+where $\epsilon$ is the emissivity, $\sigma$ is the Stefan\-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$) and $F_{12}$ is the radiative shape factor.
 
@@
 
-$Z_c = 0.08 dot{Q}^(2/5)$ \\
-
-$Z_i = 0.20 dot{Q}^(2/5)$ \\
-
-$Z_c$ = continuous flame height $(m)$  \\
-
-$Z_i$ = intermittent flame height $(m)$ \\
+\begin{equation}\label{eq:z_c}
+Z_c = 0.08 \dot{Q}^{\frac{2}{5}}
+\end{equation}
+where $Z_c$ is the continuous flame height~(m)
+\begin{equation}\label{eq:z_i}
+Z_i = 0.20 \dot{Q}^{\frac{2}{5}}
+\end{equation}
+where $Z_i$ is the intermittent flame height~(m)
 
@@
 Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad’s flame height equation directly.
-Setting the area of the fuel surface, 0.093~$m^2$, equal to π $D^2$/4 and then solving for $D$ yields an effective diameter of 0.344~m.
-Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0 m (3.3 ft), 1.0 m (3.3 ft), and 0.73 m (2.4 ft) for natural gas, gasoline, and polyurethane foam respectively.
-Taking the uncertainty of the measurements used to determine the heat release rate (±11~\%) into account generates a range of values.
+Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.
+Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0~m and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
+Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.
 The range of calculated values are compared with the  mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.
 
-\begin{center} 
-$ H_f = 0.235\: \dot{Q}^{(2/5)} - 1.02 D $  \\
-\end{center}
-$ H_f$ = flame height (m)  \\
-$ \dot{Q}$ = heat release rate (kW) \\
-$ D$ = diameter of burner (m)  \\
+\begin{equation}\label{eq:flame_height}
+H_f = 0.235\: \dot{Q}^{\frac{2}{5}} - 1.02 D
+\end{equation}
+where $H_{f}$ is the flame height (m), $\dot{Q}$ is the heat release rate (kW), and $D$ is the burner diameter (m).
 
@@
 
-Compare Natural Gas at 0.61 m from instrumented wall and at 0.0 m from instrumented wall - problem bounds.
+Compare Natural Gas at 0.61~m from instrumented wall and at 0.0~m from instrumented wall - problem bounds.
 

### 2015-04-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Edits to Ch 1 through 4

@@
 In the United States, the loss of life due to unwanted fire has been decreasing steadily since the 1970’s.
-This is neglecting the increased loss of life as a result of the terrorist attack on September 11, 2001.
+This trend does not include loss of life as a result of the terrorist attack on September 11, 2001.
 The estimated number of fire deaths in the U.S.
@@
 The review of the analysis of explosives evidence and fire debris is covered in three pages of the report.
-The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry ''~\cite{Forensic:2009}.
+The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry~''~\cite{Forensic:2009}.
 The complete summary assessment for fire debris analysis is included here: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
@@
 
-Conducted a series of experiments on samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
+A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
 The flooring radiant panel (ASTM~E648) was used to examine this value.
@@
 FDS~\cite{McGrattan:2014} and Smokeview~\cite{Forney:2014} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
-These simulation tools provide results in the form of visual field data, in other they provide results in the same format that the investigator would see or document the fire pattern.
+These simulation tools provide results in the form of visual field data, in other words they provide results in the same format that the investigator would see or document the fire pattern.
 Comparison between the experiments and the model may provide valuable validation data for the model.
@@
 
-The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory’s 3~m by 3~m hood oxygen consumption calorimeter.
+The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory's 3~m by 3~m hood oxygen consumption calorimeter.
 This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests} ~\cite{ASTM_E2067}.
@@
 
-The NIST Large Fire Research Laboratory’s 3~m by 3~m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700~kW.
+The NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700~kW.
 Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
@@
 
-Water cooled, Schmidt-Boelter total heat flux gauges were used to measure the heat flux.
+The heat flux was measured with water cooled, Schmidt-Boelter total heat flux gauges.
 The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
@@
 Notice how the flame height cycles up and down in each of the sequences.
-These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss and extreme (minimum or maximum) position when compared to the still photographs.
+These images provide additional information and continuity of the motion of the flame so that the analysis is less likely to miss an extreme (minimum or maximum) position when compared to the still photographs.
 
@@
 
-Now that the characteristics of the fires had been measured, the next step was to measure the thermal impact that the fires had on a vertical target surface.
+Once the characteristics of the fires had been measured, the next step was to measure the thermal impact that the fires had on a vertical target surface.
 In these experiments the target is a non-combustible wall.
@@
 Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20~cm intervals, up to a height of 2.2~m above the surface of the burner.
-Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall of the wall.
+Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall.
 The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
@@
 The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.
-In the sections below,a full set of the averaged data from the natural gas fueled experiments will be presented to demonstrate the impact on distance from the wall on the temperatures in the plume as well as the conditions measured on the wall.
+In the sections below, a full set of the averaged data from the natural gas fueled experiments will be presented to demonstrate the impact on distance from the wall on the temperatures in the plume as well as the conditions measured on the wall.
 Then composite graphs of the wall temperatures and heat flux measure on the wall versus distance will be shown for each fuel type.
@@
 However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs after approximately 3 minutes after ignition.
-A review of the heat release rates and the test videos do not yield an clues as to the reason for this decrease which occurred in both experiments.
+A review of the heat release rates and the test videos do not yield any clues as to the reason for this decrease which occurred in both experiments.
 In both experiments the heat release rate was steady and the video did not show any change in flame movement.
@@
 The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
-Table 19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate source.
+Table 19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate sources.
+
 Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321,Quintiere:1985}.
@@
 
-Of course the temperatures of the thermocouples in the wall as a result the of the energy transferred to the wall and the thermo-physical properties of the wall material.
-Assuming that the properties of calcium silicate board and the gypsum board are similar, let's review the heat flux graphs.
-All of the fuels generated heat fluxes in excess of 35~kW/m$^2$ at the wall, burner centerline array when the burners were against the wall.
+Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material.
+Assuming that the properties of calcium silicate board and the gypsum board are similar, the heat flux graphs were reviewed to see where the heat flux exceeded 35~kW/m$^2$.
+All of the fuels generated heat fluxes in excess of 35~kW/m$^2$ at the burner centerline array when the burners were against the wall.
 The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/$^2$ at 0.15~m from the wall.
@@
 Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.
-Appropriate fuels would “include liquid pool fires and other horizontal surface fires” add cites.
-Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad’s flame height equation directly.
+Appropriate fuels would ``include liquid pool fires and other horizontal surface fires'' add cites.
+Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad's flame height equation directly.
 Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.

### 2015-04-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Need more research on trim command.

@@
 
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0_15m}
+	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0m} \\	
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.0~m from the wall.}
+	\label{IWGB_NG_patterns}
+\end{figure}
+
 \chapter{Bench Scale Experiments}

### 2015-04-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
clean up trim command for fire pattern images

@@
 	\centering
-	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0_15m}
-	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0m} \\	
+	\includegraphics[trim = 14.0in 1in 16.0in 0.0in, clip=true,width=.45\columnwidth]{../Figures/IWGB_NG_0_15m_pattern}
+	\includegraphics[trim = 14.0in 1in 16.0in 0.0in, clip=true,width=.45\columnwidth]{../Figures/IWGB_NG_0m_pattern}
 	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires.

### 2015-04-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
update thesis with burn images

--- 2015-04-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
@@
 	\centering
-	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0_15m}
-	\includegraphics[trim=1.0in, 0.2in, 1.0in, 0.0in, clip=true]{../Figures/IWGB_NG_0m} \\	
+	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0_15m}
+	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0m} \\	
 	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires.
@@
 	\label{IWGB_NG_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=18.0in 4.0in 21.0in 14.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas_0_15_pattern}
+	\includegraphics[trim=18.0in 2.6in 18.0in 11.7in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas7_0_8m} \\	
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.8~m from the wall.}
+	\label{IWGB_Gas_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=10.3in 9.0in 10.3in 20.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_prebrush}
+	\includegraphics[trim=7.0in 3.5in 8.0in 18.5in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_postbrush} \\		
+	\caption[Photographs of the effect of soot removal on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
+For the image on the left, the burner was positioned 0.0~m from the wall.
+For the image on the right, the same panel after the soot was blown off, clean burn area is evident.}
+	\label{IWGB_Gas_0m_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF5_0_15m}
+	\includegraphics[trim=20.0in 1.0in 20.0in 16.4in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF12_0_8m} \\	
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.08~m from the wall.}
+	\label{IWGB_PUF_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
+	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\	
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
+	\label{IWGB_PUF_0m_patterns}
 \end{figure}

### 2015-04-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added images to wall construction section.  Images have different heights that is intended.

@@
 
+Natural gas and gasoline only
+
 \subsection{Results}
+
+\subsubsection{Natural Gas}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBNG1_P5120006}
+	\includegraphics[width=1.0in]{../Figures/GBNG2_P5120024}
+	\includegraphics[width=1.0in]{../Figures/GBNG3_P5120048}
+	\includegraphics[width=1.0in]{../Figures/GBNG4_P5120086}	
+	\includegraphics[width=1.0in]{../Figures/GBNG5_P5120137} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBNG6_P5120160}
+	\includegraphics[width=1.0in]{../Figures/GBNG7_P5120172}
+	\includegraphics[width=1.0in]{../Figures/GBNG8_P5120196}
+	\includegraphics[width=1.0in]{../Figures/GBNG10_P5120251}	
+	\includegraphics[width=1.0in]{../Figures/GBNG13_P5120356} \\
+
+	\caption[Photographs of the fire patterns from ten replicate natural gas burner against open wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against open wall construction.}
+	\label{NG_Open_Wall}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBNG14_P5130378}
+	\includegraphics[width=1.0in]{../Figures/GBNG15}
+	\includegraphics[width=1.0in]{../Figures/GBNG16}
+	\includegraphics[width=1.0in]{../Figures/GBNG17_P5130382}	
+	\includegraphics[width=1.0in]{../Figures/GBNG18_P5130386} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBNG19_P5130390}
+	\includegraphics[width=1.0in]{../Figures/GBNG20_P5130392}
+	\includegraphics[width=1.0in]{../Figures/GBNG21_P5130398}
+	\includegraphics[width=1.0in]{../Figures/GBNG22_P5130403}	
+	\includegraphics[width=1.0in]{../Figures/GBNG23_P5130412} \\
+
+	\caption[Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction.}
+	\label{NG_Closed_Wall}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBNG24_IMG_9020}
+	\includegraphics[width=1.0in]{../Figures/GBNG25_P5130419}
+	\includegraphics[width=1.0in]{../Figures/GBNG26_P5130427}
+	\includegraphics[width=1.0in]{../Figures/GBNG27}	
+	\includegraphics[width=1.0in]{../Figures/GBNG28_P5130434} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBNG29_P5130436}
+	\includegraphics[width=1.0in]{../Figures/GBNG30_P5130445}
+	\includegraphics[width=1.0in]{../Figures/GBNG31_P5130449}
+	\includegraphics[width=1.0in]{../Figures/GBNG32}	
+	\includegraphics[width=1.0in]{../Figures/GBNG33} \\
+
+	\caption[Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction.}
+	\label{NG_Insulated_Wall}
+\end{figure}
+
+\subsubsection{Gasoline}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBGAS_23_IMG_6048}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_26_IMG_6192}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_27_IMG_6210}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_28_IMG_6230}	
+	\includegraphics[width=1.0in]{../Figures/GBGAS_29_IMG_6250} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBGAS_30_IMG_6269}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_31_IMG_6288}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_32_IMG_6307}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_33_IMG_6326}	
+	\includegraphics[width=1.0in]{../Figures/GBGAS_34_IMG_6345} \\
+
+	\caption[Photographs of the fire patterns from ten replicate gasoline burner against open wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against open wall construction.}
+	\label{Gas_Open_Wall}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBGAS_02_IMG_5554}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_05_IMG_5635}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_06_IMG_5661}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_07_IMG_5679}	
+	\includegraphics[width=1.0in]{../Figures/GBGAS_08_IMG_5698} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBGAS_09_IMG_5717}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_10_IMG_5737}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_11_IMG_5756}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_12_IMG_5775}	
+	\includegraphics[width=1.0in]{../Figures/GBGAS_13_IMG_5794} \\
+
+	\caption[Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction.}
+	\label{Gas_Closed_Wall}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBGAS_03_IMG_5575} 
+	\includegraphics[width=1.0in]{../Figures/GBGAS_14_IMG_5814}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_15_IMG_5835}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_16_IMG_5855}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_17_IMG_5875}	\\
+
+	\includegraphics[width=1.0in]{../Figures/GBGAS_18_IMG_5895}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_19_IMG_5967}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_20_IMG_5986}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_21_IMG_6006}
+	\includegraphics[width=1.0in]{../Figures/GBGAS_22_IMG_6026}	\\
+
+	\caption[Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction.}
+	\label{Gas_Insulated_Wall}
+\end{figure}
+
+\subsubsection{Polyurethane Foam}
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBPUF1_IMG_9332}
+	\includegraphics[width=1.0in]{../Figures/GBPUF2_IMG_9347}
+	\includegraphics[width=1.0in]{../Figures/GBPUF3_IMG_9362}
+	\includegraphics[width=1.0in]{../Figures/GBPUF4_IMG_9376}	
+	\includegraphics[width=1.0in]{../Figures/GBPUF5_IMG_9390} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBPUF6_IMG_9403}
+	\includegraphics[width=1.0in]{../Figures/GBPUF7_IMG_9416}
+	\includegraphics[width=1.0in]{../Figures/GBPUF8_IMG_9429}
+	\includegraphics[width=1.0in]{../Figures/GBPUF9_IMG_9446}	
+	\includegraphics[width=1.0in]{../Figures/GBPUF10_IMG_9461} \\
+
+	\caption[Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction]{Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction.}
+	\label{PUF_Open_Wall}
+\end{figure}
 

### 2015-04-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 These experiments were conducted without instrumentation in the walls for several reasons; to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation, to provide more realistic conditions, and to enable the conduct of additional replicate experiments given the limited laboratory availability.
-Based on the outcome of the instrumented calibration target wall results, burner positions were chosen.
+A photograph of the compartment fire experimental arrangement is shown in Figure~\ref{Compartment_Test}.
+
+In the instrumented gypsum wallboard experiments, as the burners were moved from the position against the wall the fire effects on the wall diminished significantly.
+Therefore most of the fire pattern compartment experiments were conducted with the burners against the wall or corner of the compartment.
 After each burn, the fire patterns were measured, photographed and analyzed for repeatability.
 The fire damaged wallboard was subsequently removed and replaced with new sections of painted gypsum wallboard.
-The number of experiments for each case was dependent on the repeatability and similarity of the pattern development.
-Several types of fire pattern experiments were conducted in the compartments, as detailed in the sections to follow, to examine the impact of the insulation behind the gypsum wallboard panel on the resulting fire pattern and other series of experiments were conducted to compare the fire patterns based on the burner centered on the rear wall or in or near a corner on the rear wall of the compartment.
++++The number of experiments for each case was dependent on the repeatability and similarity of the pattern development.+++ Several types of fire pattern experiments were conducted in the compartments, as detailed in the sections to follow, to examine the impact of the wall construction on the resulting fire pattern and other series of experiments were conducted to compare the fire patterns based on the burner centered on the rear wall or in or near a corner on the rear wall of the compartment.
+
+\begin{figure}
+\includegraphics[width=1.0in]{../Figures/Compartment_Test} \\
+	\caption[Photograph of the wall fire pattern experiments compartment arrangement]{Photograph of the wall fire pattern experiments compartment arrangement.
+Experiment shown is being conducted with a polyurethane burner against the back wall.}
+	\label{Compartment_Test}
+\end{figure}
 

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Add FDS input files and coarse, medium results, update tex and bib
Adding photos and words to Chap 4, 5,6

--- 2015-04-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
@@
 \usepackage{rotating}
+\usepackage{url}
 \frenchspacing
@@
 
+Since these experiments were the culmination of the instrumented series of full scale tests, the use of gypsum wallboard was intended to provide some insight into how much fire damage would result.
+These experiments proved to be challenging in terms of time and effort.
+Each panel of gypsum wallboard had to be carefully drilled for thermocouple and heat flux gauge placement.
+Since there was only one set of heat flux gauges this reduced the number experiments that could be conducted on a given day.
+With other project demands, the number of instrumented wallboard experiments that could be conducted under the oxygen consumption calorimeter was reduced due to time constraints.
+The test matrix is shown in Table~\ref{tab:IWGB_experiments}.
+There was also a concern that these experiments would have limited value due to potential interference from the water-cooled heat flux gauges and potential physical damage caused by drilling the holes for them.
+
 \begin{figure}
@@
 Each 1.22~m by 2.44~m by 12.7~mm thick panel weighed approximately 30.5~kg.
-The physical features of the gypsum wallboard panels are given in the table below.
+The thermal properties of the gypsum wallboard panels are given in the Table~\ref{tab:Gypsum wallboard_Thermal_Properties}.
+The first two rows of data were measured from samples of the gypsum wallboard used in these experiments.
+The bottom four rows of data are from ~cite\{Gross:1985}.
+
+There have been a number of studies that have examined gypsum wallboard under elevated temperature conditions in terms of it's thermal properties or in terms of its physical change as a result to exposure to heat.
+Schroeder conducted a study on the post-fire analysis of construction materials including gypsum.
+As gypsum is heated to temperatures above 80~$^\circ$C it begins to change phase and degrade.
+Continued heating causes some of the chemically bound water to disassociate and the gypsum changes to a hemihydrate.
+This transformation occurs in the range of 98~$^\circ$C to 130~$^\circ$C.
+With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, commonly this process is known as calcination.
+Schroder exposed samples of gyspum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
+The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction  add Schroder.
+NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dyhydrated gypsum to map fire patterns.
 
@@
 
-% first two lines of table based on measurements of GB at NIST.  Lower 4 lines from Gross 1985
-
 After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
@@
 
-trim photo sets added here and compare with temps and HF
+As defined in NFPA 921, a fire is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA_921}.
+In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
+The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{nfpa_921}.
+As presented in the introduction, DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
+\begin{enumerate}
+	\item Surface deposits -– no irreversible effect on surface
+	\item Surface thermal effects –- physical change such a discoloration or melting
+	\item Charring -– evidence of surface burning
+	\item Penetration -– charring below the surface
+	\item Consumption –- loss of surface material, charring throughout
+\end{enumerate}
+
+Figure~\ref{demarcation} is a photograph of the edge of a fire pattern generated by the natural gas burner.
+It will serve as visual definition of the line of demarcation to be used in this study to determine the limits of a fire pattern.
+Referring to DeHaan's classifications, there are no surface deposits such as light soot that could be brushed or blown off the gypsum wallboard.
+There is a thin band of surface thermal effects in the form of discoloration of the paint, this could be considered an outer bound of the pattern.
+To the left of the discoloration is clearly an larger area where charring (blackening of the paint/paper), penetration (lifting of the painted/paper residue), and consumption (areas where the paint/paper reside is gone altogether).
+The last two classifications or criteria will be used in this study to define the edge of the fire pattern.
+Any area where the paper has been burned away or penetrated such that it has lifted away from the gypsum will be considered part of the fire pattern and define the lines of demarcation for this study.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/demarcation}  \\
+	\caption[Photograph showing clear lines of demarcation]{Photograph showing clear lines of demarcation from a fire pattern generated on painted gypsum wallboard by a natural gas fueled burner.}
+	\label{demarcation}
+\end{figure}
+
+Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as show in Figure~\ref{Soot_pattern}.
+From the photograph the areas of penetration and consumption can be clearly delininated while the discolored and sooted areas tend to meld together.
+Further the focus of the measurements in this study are thermal, therefore the focus is on the burned, not burned line of demarcation.
+
+Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrtaed paint/paper layer which exposed the gypsum underneath.
 
@@
 These experiments were conducted without instrumentation in the walls for several reasons; to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation, to provide more realistic conditions, and to enable the conduct of additional replicate experiments given the limited laboratory availability.
-Based on the outcome of the instrumented calibration target wall results, burner positions were chosen.
-After each burn, the fire patterns were measured, photographed and analyzed for repeatability.
-The fire damaged wallboard was subsequently removed and replaced with new sections of painted gypsum wallboard.
-The number of experiments for each case was dependent on the repeatability and similarity of the pattern development.
-Several types of fire pattern experiments were conducted in the compartments, as detailed in the sections to follow, to examine the impact of the insulation behind the gypsum wallboard panel on the resulting fire pattern and other series of experiments were conducted to compare the fire patterns based on the burner centered on the rear wall or in or near a corner on the rear wall of the compartment.
+A photograph of the compartment fire experimental arrangement is shown in Figure~\ref{Compartment_Test}.
+In the instrumented gypsum wallboard experiments, as the burners were moved away from the position against the wall, the fire effects on the wall diminished significantly.
+Therefore most of the fire pattern compartment experiments were conducted with the burners against the wall or corner of the compartment or less than one burner length from the wall.
+
+Prior to each burn, grid lines approximately 51~mm on center were drawn on the painted gypsum wallboard panel that would be exposed to the fire.
+After each burn, the fire patterns were photographed and analyzed for repeatability by looking at the portion of the grid that was burned.
+The fire damaged wallboard was subsequently removed, photographed again, and replaced with new sections of painted gypsum wallboard.
+Several types of fire pattern experiments were conducted in the compartments; to examine the impact of the wall construction on the resulting fire pattern; and to compare the fire patterns based on the burner centered on,or the rear wall, or in, or near a corner on the rear wall of the compartment.
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Compartment_Test} \\
+	\caption[Photograph of the wall fire pattern experiments compartment arrangement]{Photograph of the wall fire pattern experiments compartment arrangement.
+Experiment shown is being conducted with a polyurethane burner against the back wall.}
+	\label{Compartment_Test}
+\end{figure}
 
@@
 
- Impact of Wall Construction
-
- The initial compartment experiments were conducted to examine the impact of the method of construction of the walls on the development of the fire patterns.
-This data determined how the walls for the remaining compartment fire pattern experiments would be constructed.
-Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with fiberglas batt insulation in the voids of the wood frame representative of an exterior wall.
-From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occured when the burners were positioned against the wall.
-The peak temperatures were similar for all of the fuels,approximately 80~$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
+ The initial compartment experimental series were conducted to examine the impact of the method of construction of the walls on the development of the fire patterns.
+These experiments would determine how the walls for the remaining compartment fire pattern experiments would be constructed.
+Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
+The insulation was 90~mm thick fiber glass batting,a kraft paper facing, and an "R value" of 13.
+From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
+The peak temperatures were similar for all of the fuels, approximately 80~$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
 Therefore the wall construction experiments were only conducted with the natural gas and gasoline fueled burners as the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
 
-The burner was centered on the middle panel of the rear wall.
-The wall behind the center panel of the rear wall was insulated to met the needs of the experiment.
+\subsection{Experimental Arrangement}
+
+The burner was centered on the middle panel of the rear wall and was in contact with the wall.
+The wall behind the center panel of the rear wall was constructed either as open, closed, or insulated to meet the needs of the experiment.
+The burner was positioned against the face of the painted gypsum board.
 As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
-Each of the painted gypsum board panels that were used for a fire pattern had a 5~cm grid drawn on it to assist with the determination of the geometry of the fire pattern.
-
-\subsection{Experimental Arrangement}
-
-Natural gas and gasoline only
+The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
+The natural gas had a 300 second burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
+By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
 
@@
 
+Ten replicate experiments were conducted with each of the three wall construction types.
+The walls were exposed to both the natural gas and the gasoline burners.
+For these experiments the burner was in contact with the gypsum wallboard.
+A total of 60 experiments were conducted.
+The results will be presented by wall construction type.  The order of presentation will be open, closed, and insulated wall construction.
+
 \subsubsection{Natural Gas}
+
+Figure~\ref{NG_Open_Wall} shows a comparison of the ten fire patterns generated by the natural gas burner on the wall with open back construction.
+The images within the figure are slightly different sized however they are scaled so that the images are comparable.
+The grids were used to assist with the determination of the fire pattern area and the sizing of the images.
+In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
+The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{nfpa_921}.
 
@@
 		Natural Gas (10)    &   Insulated 	& 0.71	$\pm$ 0.10 (14~\%)   &	0.23 $\pm$ 0.04 (17~\%) 	& 0.42 $\pm$ 0.07 (17~\%) 	& 0.15 $\pm$ 0.02 (14~\%)  	\\
-		Gasoline (12)       &   Open    	& 0.83	$\pm$ 0.15 (18~\%)   &	0.28 $\pm$ 0.09 (32~\%) 	& 0.44 $\pm$ 0.14 (32~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
+		Gasoline (10)       &   Open    	& 0.83	$\pm$ 0.15 (18~\%)   &	0.28 $\pm$ 0.09 (32~\%) 	& 0.44 $\pm$ 0.14 (32~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
 		Gasoline (10)       &   Closed  	& 0.80	$\pm$ 0.10 (13~\%)   &	0.29 $\pm$ 0.04 (14~\%) 	& 0.44 $\pm$ 0.06 (14~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as show in Figure~\ref{Soot_pattern}.
-From the photograph the areas of penetration and consumption can be clearly delininated while the discolored and sooted areas tend to meld together.
+From the photograph the areas of penetration and consumption can be clearly delineated while the discolored and sooted areas tend to meld together.
 Further the focus of the measurements in this study are thermal, therefore the focus is on the burned, not burned line of demarcation.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=2.5in]{../Figures/Soot_pattern}
+	\includegraphics[width=2.5in]{../Figures/Soot_close}	\\
+	\caption[Photographs showing clear lines of demarcation with gasoline]{Photographs showing clear lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.
+Burned vs unburned area is clearly defined, where as the difference between sooted and thermally discolored areas is not as clear.}
+	\label{Soot_pattern}
+\end{figure}
 

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Clean up bib errors and latex file

@@
 An example would be research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs to name just a few.
-None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FIVE}.
+None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FEMA:2013}.
 
@@
 More than 1.2 billion pounds are produced in the U.S.
-every year~\cite{Foam,Touch}.
+every year~\cite{Foam,Polyurethane_Foam}.
 In studies by Ahrens and Evarts of the NFPA, upholstered furniture and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
@@
 In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in mm with 95~\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
-For the natural gas fires, the averages are from ten 30 s segments, while the fire was monitored at approximately 80~kW.
-In some cases more than one 30 s segment was sampled per heat release rate experiment.
+For the natural gas fires, the averages are from ten 30~s segments, while the fire was monitored at approximately 80~kW.
+In some cases more than one 30~s segment was sampled per heat release rate experiment.
 Sixteen 30~s video segments, which included the peak heat release rate, were successfully analyzed from the seventeen gasoline heat release rate experiments.
@@
 Comparing the temperatures of the plume at the most distant point from the wall, 0.61~m and with the plume temperatures with the burner contacting the wall in Figure~\ref{TC_Plume_TWNG_comp} shows an increase.
-However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs after approximately 3 minutes after ignition.
+However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs after approximately 3~min after ignition.
 A review of the heat release rates and the test videos do not yield any clues as to the reason for this decrease which occurred in both experiments.
@@
 The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
-Table 19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate sources.
+Table~19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate sources.
 
@@
 Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays.
-For the gasoline fire experiment at the 0.08~m position the wall temperatures and the heat flux values from the burner edge array had values that were higher than when those measured at the 0.0 m position.
+For the gasoline fire experiment at the 0.08~m position the wall temperatures and the heat flux values from the burner edge array had values that were higher than when those measured at the 0.0~m position.
 The peak heat release rates for the positions at 0.0~m, 0.08~m and 0.15~m were 120~kW, 110~kW, and 110~kW respectively.
@@
 In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
-The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{nfpa_921}.
+The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{NFPA_921}.
 As presented in the introduction, DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
@@
 Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3)	Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
-The insulation was 90~mm thick fiber glass batting,a kraft paper facing, and an "R value" of 13.
+The insulation was 90~mm thick fiber glass batting,a kraft paper facing, and an ``R value'' of 13.
 From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
@@
 The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
-The natural gas had a 300 second burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
+The natural gas had a 300~s burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
 By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
@@
 In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
-The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{nfpa_921}.
+The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{NFPA_921}.
 

### 2015-04-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Radiant panel data, figures and tex

@@
 
-\dedication{To my wife and family}
+\dedication{To my wife and family}  work family
 
@@
 A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel.
-The panel is inclined at 30~$^{\circ}$, providing a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point.
+The panel is inclined at 30~$^{\circ}$, and under standard operating conditions provide a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point.
+For these experiments a higher heat flux profile was required, so the gas air increased    comback   to  Figure~\ref{FRP_HF_Calibration}
+
 A pilot flame is used to ignite the test sample.
@@
 For this study the samples examined were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/FRP_HF_Calibration} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
+	\label{FRP_HF_Calibration}
+\end{figure}
 
@@
 
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+Each row of samples represents three replicate experiments at a given heat flux for 600s.
+Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.
+}
+	\label{RP_GB_Front}
+\end{figure}
+
 \subsection{Heat Release Rate per Unit Area}
@@
 \subsection{Critical Heat Flux}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/RPGB_SET} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+Each row of samples represents three replicate experiments at a given heat flux for 600s.
+Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.
+}
+	\label{RPGB_SET}
+\end{figure}
 
@@
 
-\bibliography{../References/Madrzykowski_Thesis,../../../Bibliography/FDS_refs}
+\bibliography{../References/Madrzykowski_Thesis}
 \end{document}

### 2015-04-13 Projects/Madrzykowski_Thesis/Plot_Scripts/RPGB.py

@@ -1,0 +1,38 @@
+# to run - ctrl + b
+#these first lines are standard calls for including desired packages for data and plotting
+from __future__ import division
+import numpy as np
+import pandas as pd
+from pylab import *
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+#read in data file(s) -- point to relative path in repository
+#if more than one line of headers at top of document add header=n-1
+#typically one header line, header = 1-1 -> header=0 which is default
+data = pd.read_csv('../Experimental_Data/RPGB/RP_GB.csv', header=0)
+#fds = pd.read_csv('../FDS_Output_Data/testname.csv', header=1)
+
+#plotting
+fig = figure()
+#here data['Position'] is calling for the column named Position in data file which is x data
+#data[0,2 m] is the y data
+plot(data['Time (s)'],data['10F'],'k-s', label='10 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['12_5F'],'r-*', label='12.5 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['15F'],'b-^', label='15 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['17_5F'],'g-o', label='17.5 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['20F'],'c-<', label='20 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['22_5F'],'m->', label='22.5 (kW/m$^2$)',markevery=50,ms=8)
+plot(data['Time (s)'],data['25F'],'b-s', label='25 (kW/m$^2$)',markevery=50,ms=8)
+ax1 = gca()
+xlabel('Time (s)', fontsize=20)
+ylabel('Temperature ($^{\circ}$C)', fontsize=20)
+xticks(fontsize=16)
+yticks(fontsize=16)
+grid(True)
+ax = gca()
+axis([0, 600, 0, 600])
+legend(numpoints=1,loc='upper right',fontsize=16 )
+#point figures to be written in Figures directory and desired file name
+savefig('../Figures/RP_GB_Front.pdf',format='pdf')
+close()

### 2015-04-29 Studies/2012_Chicago/Report/response.tex
Chicago Fire: update Fire Tech report and reviewer comments

@@
 \\
-{\it The authors were able to view portions of video taken during the incident that allowed for the estimation of failure times and failure areas of exterior walls and windows.}
+{\it The authors were able to view portions of video taken during the incident that allowed for the estimation of failure times and failure areas of exterior walls and windows.
+This is addressed in the text in Section 3.4.
+Since this case deals with the death of a firefighter the authors decided to leave the decription of events to narrative from the official NIOSH report.}
 \item I miss, however, a more critical point of view that would be essential in guiding fire modellers as to what the limits of applicability of these models is.
@@
 It would be useful to relate the temperatures (gas and wall) to heat fluxes, as this would be a more correct approach in terms of human perception and injuries.
+\\
+{\it The section has been updated.}
 \end{itemize}
@@
 Some discussion why this was discounted would be helpful to the reader.
-\item There was a firefighter with the Captain that perished in the fire.  What were his injuries and location if known?  Some discussion about this 2nd firefighter in the area would be useful.
+\\
+{\it The authors recognize that many in the fire service believe fire can be pushed with water but disagree with that legend.
+A properly applied straight stream or smooth bore stream will not push fire.
+A wide fog nozzle when applied from the exterior can create a pressure boundary condition at the vent and force hot combustion gas to an area of lower pressure.
+The text in the tactical consideerations section has been update to include discussion that applying water from the exterior can make conditions better for firefighters.}
+\item There was a firefighter with the Captain that perished in the fire.  What were his injuries and location if known?  Some discussion about this 2nd firefighter in the area would be useful. \\
+{\it The firefighter with the Captain was not seriously injured.}
 \item The condition of the door clearly shows significant damage to the metal door yet the temperatures modelled in FDS are only 260°C.
 Is this an artefact of Smokeview's colorbar?
-What was the temperature in the porch area when the door is thought to failed?\\ {\it The authors set these bounds because 500~$^{\circ}$F is the}
+What was the temperature in the porch area when the door is thought to failed?\\
+{\it The authors set these bounds because 500~$^{\circ}$F is the upper limit for firefighter PPE.
+There is discussion of this after the first temperature figure.
+Text was added to include temperatures on the fire side of the door prior to failure.}
 \end{itemize}

### 2015-04-29 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago Fire: update Fire Tech report and reviewer comments

@@
 The second scenario, or alternative simulation, does not include the firefighter opening the rear door to make entry to the structure and the subsequent exterior left wall fire penetration.
-The times of the ventilation changes are provided in Table~\ref{tab:vents}.
+The times of the ventilation changes and estimated areas of openings are provided in Table~\ref{tab:vents}.
+Window failures and breaches through the structure (timing and area) were estimated from video taken by a neighbor as well as post incident images.
 Structure leakage has been shown to be important when modeling enclosure fires~\cite{beal2009}.
-The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation are significantly larger than the total effective area of leakage of a structure of this type.
+The open front door at the start of the simulation and the vents (opening size and open time) created during the simulation (to best match the actual fire) are significantly larger than the total effective area of leakage of a structure of this type.
 Therefore, any leakage in the structure would have a negligible impact on the fluid mechanics within the structure and is not included in this study.
@@
 Figure~\ref{fig:temp_129s} shows temperatures of at least 260~$^{\circ}$C (500~$^{\circ}$F) in the second floor rear porch and rear portion of the attic.
-In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output, and the actual simulated temperatures may exceed the lower or upper bounds.
+In this figure, the lower temperature bound is set to 25~$^{\circ}$C (77~$^{\circ}$F), and the upper temperature bound is set to 260~$^{\circ}$C (500~$^{\circ}$F); however, these are only limits on the visualized output to reflect the typically firefighter protective gear limits, and the actual simulated temperatures may exceed the lower or upper bounds.
 High temperatures, between 80~$^{\circ}$C (185~$^{\circ}$F) and 200~$^{\circ}$C (390~$^{\circ}$F), also extend down to the rear entrance on the first floor.
@@
 Note that the conditions in the attic do not appear to change.
+While the visualized temperatures are designed to illustrate the hazard to firefighters, temperatures on the fire side of the doorway prior to failure exceeded 500~$^{\circ}$C (900~$^{\circ}$F).
 \begin{figure}[!ht]
@@
 \label{hazard}
-A person is susceptible to second-degree burn injuries if exposed to temperatures greater than 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
+A person is susceptible to second-degree burn injuries if skin temperatures exceed 55~$^{\circ}$C (130~$^{\circ}$F)~\cite{contactburn}.
 Although firefighters wear protective gear, gear only offers a finite amount of protection.
-The polycarbonate in a self contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures of 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
-Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him/her at risk.
-Exposure of equipment to temperatures of 260~$^{\circ}$C (500~$^{\circ}$F) represents a Class III exposure~\cite{Donnelly2006}.
-Firefighters are at increased risk levels when encountering Class III exposure conditions for more than 5~minutes~\cite{Donnelly2006}.
-Therefore, for the analysis of the simulated exposure temperatures, the maximum visualized temperature is set to indicate all values that are greater than or equal to 260~$^{\circ}$C (500~$^{\circ}$F).
-This means that temperatures visualized at the maximum range in the displayed model output are at a minimum of 260~$^{\circ}$C (500~$^{\circ}$F); the actual simulated temperatures could in fact be greater.
+The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
+Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard} for less than 2.5~min.
+Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
 
@@
 In this fire incident, the thermal degradation of the steel-faced, wood-framed door resulted in a rapid change in the thermal conditions in the hallway, which resulted in highly hazardous conditions.
-These conditions would be equivalent to or greater than a Class III exposure~\cite{Donnelly2006}.
 Prediction of the failure mode and failure time of the door is not a reasonable expectation given the large number of unknowns that the firefighters faced on the fire ground.
-In this case, the timing of the interior attack appears to have coincided with the failure time of the door.
-Research has been conducted~\cite{madrzykowski2009fire, kerber2009fire} and continues to be conducted by NIST, Underwriters Laboratories (UL), and others that demonstrates that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure.
+In this case, the timing of the interior attack appears to have coincided with the failure time of the door.Ongoing research by NIST, Underwriters Laboratories (UL), and others has demonstrated that applying water from the exterior into the fire area of a structure (prior to the start of interior operations) can significantly improve the safety of firefighters by reducing the thermal hazard from the fire and reducing the potential for developing high velocity hot gas flows within the structure~\cite{madrzykowski2009fire, kerber2009fire}.
 

### 2015-04-30 Studies/2012_Chicago/Report/response.tex
Chicago: update based on Fire Tech reviews

@@
 \begin{itemize}
-\item We would appreciate more efforts in assessing or estimation somehow the error or uncertainty of your results.
-\item An effort to read some of the work published in Fire Technology on the topics at hand would be appreciated by the editorial board.
-\item There are too many figures (20); please consider removing some or creating an Appendix where the 5 least important figures are presented.
-\item Please consider to submit the input file/s for this work as Electronic Supplementary Material.
+\item We would appreciate more efforts in assessing or estimation somehow the error or uncertainty of your results. \\
+{\bf Dan -- not sure about this comment - there is model uncertaintly in predicting temperature from a HRR or undercertainty in specifying uncertainty.
+I have something written at the end of Section 3.6 - but as far as error/uncertainty it could be massive based on all the unknowns we have.
+I also added a comment about 50 kW/m2 being conservative.}
+\item An effort to read some of the work published in Fire Technology on the topics at hand would be appreciated by the editorial board. \\
+{\it Added addtional references where appropriate.}
+\item There are too many figures (20); please consider removing some or creating an Appendix where the 5 least important figures are presented. \\
+{\it Moved figures}
+\item Please consider to submit the input file/s for this work as Electronic Supplementary Material. \\
+{\it Will do}
 \end{itemize}
@@
 Is the flow of hot gases into the hallway after the door breakage accompanied by flaming combustion?
+\\
+{\bf Dan - we know this behavior - exterior combustion -- is pretty realistic from the UL tests - but I cannot find the report anywhere.
+Do you have it or should I try to cite the course?
+FDS predicts minimal flaming combustion into the hallways at the ceiling right near the doorway.
+This seems realistic me but we have nothing to confirm or deny that.}
 \item The authors discard the secondary simulation based on the similarity of the overall HRR, but an alternative ventilation pattern could potentially alter the flow path inside the building.
 They should explain in more detail why this is not the case in this scenario (or provide images of the flow path and temperature distributions of the secondary simulation).
+\\
+{\it Text was added to state that in both cases the flow path path was the same and the hazard to the firefighters were similar.}
 \item I further think that the beginning of section 5.2 is misleading.
@@
 Additional discussion on the species and why the well ventilated values used are appropriate for this analysis but should not be used when modelling under-ventilated fire.
+\\
+{\it Good points! Additional discussion was added to the report after the chemical reaction and yeilds were specified.}
 \item The authors used 50kW/m2 for calculating there maximum heat release rate yet this value is lower than expected.
@@
 Additional explanation would be helpful.
+\\
+{\it The 50 kW/m2 is a conservative estimate for the HRRPUA.
+In reality the fire might have been larger - but even a fire of this size produced high hazard conditions for firefighters.
+There is discussion added to the report.
+In the attic, there could have been a larger burning area with smaller heat release rate but a compromise was made for Q* and D*.}
 \item This results in a floor area of approximately 105 m2 (1100 ft2) per floor and a main living area of approximately 110 m2 (2200 ft2).
@@
 I suspect that it is a coincidence as there doesn't appear to have been 30-60 seconds for any change in the flow path caused by that action to propagate...but it might be worth inclusion in Table 1 and/or a little discussion.
+\\
+{\it The roof vent was completed when they heard the MayDay.
+The door failed and the flow path was established before the MayDay was called therefore the roof vent was not a major factor.
+The last communication from E123 Captain was at 17:23 which is included in Table 1.}
 \item Page 6.
@@
 It turns out it was, and you covered that well...but perhaps a note in this section mentioning that might be nice.
+\\
+{\it At the stage of the discussion, the model results are not yet presented. There has been additional discussion added here based on other comments though.}
 \item Page 16 line 40-41.
@@
 [See p.
-7]
-\item Section 3.3 Materials should also address what was done with the windows. No description of glass was given, so this should be addressed explicitly. [See p. 7]
+7] \\
+{\it Added discussion.}
+\item Section 3.3 Materials should also address what was done with the windows. No description of glass was given, so this should be addressed explicitly. [See p. 7] \\
+{\it That is correct. This is clarified in the text.}
 \item The vents are unclear to me [See Tab.
@@
 9].
-\item Vents: Were all of the windows considered closed? I did not find that directly stated, especially given the details about all of the windows in the last two diagrams.
+\\
+{\it You are correct in that there were roof ventilation holes that were made. Roof ventilation occured after the interior flow path was established and was not considered in the model.}
+\item Vents: Were all of the windows considered closed? I did not find that directly stated, especially given the details about all of the windows in the last two diagrams. \\
+{\it Addressed related to prior comment.}
 \item Vents: Where is the connection between the 2nd floor porch and attic?
 I saw it described broadly in the paper, but don't recall it being described more fully and it is not depicted in any of the diagrams.
-\item Vents: Table 2, p. 7, it would be helpful to have a quick description of what each vent is in terms of the fire incident report.
+\\
+{\it Addtional text was added describing the stair connecting the porch to the attic.}
+\item Vents: Table 2, p. 7, it would be helpful to have a quick description of what each vent is in terms of the fire incident report. \\
+{\it These vents were found by watching a video of the incident. Besides the door opening they do not tie into the narrative from NIOSH.}
 \item On the numerical resolution examination [see p.
 8, lines 22-27], it would be helpful to explain that higher numbers equate to better resolution as the non-user may not appreciate this and think that being outside the range makes it an unreliable calculation.
+\\
+{\it Text added to clarify.}
 \item HRR: The graphic [Fig.
@@
 If the authors know the amount of HRR within the structure, that may be an interesting/helpful value for the readers.
+\\
+{\bf Dan - I don't have this unless I re-run the simulation with a ton of devices to calculate this.
+Not sure what value it adds though - but I could add a point that a lot of the combustion is exterior to the structure.}
 \item Attic fire: Was any of the roof ``consumed?'' [See Fig.
@@
 2, p.
-6]
+6]\\
+{\it The authors used video evidence to examine the breaches through the structure from the fire prior to the MayDay call.
+At that time there was no breach through the roof.
+Post incident there were holes cut by the fire service as well as some that might have been caused by the fire but we do not have enough evidence to make a difinitive assessment.}
 \item Pressure: Section 4.2 [See p.
@@
 Therefore, it's important to clarify this point.
+{\it Excellent point. This is clarified.}
 \item Pressure: [See Fig.
@@
 Somewhere, there must be air entering these various spaces in order to continue combustion in those volumes.
+\\
+{\it Discussion added to Pressure section.}
 \item Fig.
@@
 This should be clarified in the caption.
+\\
+{\it Clarified in the text.}
 \item Fig.
@@
 Furthermore, it will be impossible to read this if it is reproduced in black and white.
-\item  It would be helpful to have a floor plan of the attic space that includes the locations of the roof vents.
+\\
+{\bf I don't want to change this because I like the colored cross hatching, but I guess I am going to have to?}
+\item  It would be helpful to have a floor plan of the attic space that includes the locations of the roof vents. \\
+{\it Because of post-incident safety concerns we were unable to measure the attic or get accurate location of roof vents. Note that these vents were made after the interior door failed.}
 \end{itemize}

### 2015-04-30 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago: update based on Fire Tech reviews

@@
 Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~\ref{fig:simp_geom}), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~\ref{fig:simp_geom}) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~\ref{fig:simp_geom}).
+Stair 3 directly asceneds to attic without a doorway or method to isolate the rear porch from the attic (the top stair is the floor of the attic).
 Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
@@
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
+The product yeilds used in this analysis (Eq.~\ref{eq:wood_comb}) are for well-ventilated burning conditions.
+The simple chemistry reaction mechanism in FDS assumes constant, user-specified yeilds for carbon monoxide and soot.
+When a fire becomes underventilated, the yeilds of soot, carbon monoxide, or other product species change due to incomplete combustion.
+If the analysis of model results requires species concentrations, different species yeilds, a more complex chemical reaction, or finite-rate chemistry may be needed~\cite{FDS_Math_Guide}.
+The focus of this analysis is to examine the the effect on the flow conditions as a result of a interior door failure.
+Therefore, errors in species concentrations are tolerated.
 
@@
 The results of that study indicate that the HRRPUA for different types of wood is approximately 50~kW/m$^2$.
+This value may be a conservative estimate for the HRRPUA for wood.
+As a result, the actual fire may have been larger.
+However, as discusssed in this study, the fire used in the model produced interior conditions that were hazardous to fully protected firefighers.
 
@@
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
+Note that the multi-component heat transfer that would typically occur in an exterior wall (gypusum, wood studs, insultation, exterior finish, air gaps) was simplified and respresented by a single material.
 The following lines define these materials in the FDS input file:
-
-\clearpage
 
@@
 \end{lstlisting}
+
+Predicting window pane failure in FDS is currently outside of the validation space~\cite{FDS_Validation_Guide}.
+For these simulations, all windows were initially assumed to be closed and would open or ``fail'' according to incident timeline, fire responder statements, and videos of the incident.
 
@@
 Nuclear Regulatory Commission, $D^*/\dx$ values ranged between 4 and 16~\cite{NUREG_1824} and produced results that were adequate for engineering calculations.
-The grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
+Higher values for this ratio equate to better resolution in the model.
+Therefore, the grid resolution used in this model is within or exceeds typical engineering $D^*/\dx$ values.
 
@@
 
+Prior fire modeling studies have illustrated the importance of model parameters~\cite{Jahn:IAFSS9,Gutierrez:Building_and_Environment,Rein:Dalmarnock,Rein:FSJ,Xiao:FT2012}.
 Table~\ref{tab:mod_param} shows a summary of the model input parameters for the simulation that was conducted as part of this study.
@@
 At the time of the door failure (160~s), the HRR in both cases was approximately 9~MW because of the increased amount of ventilation.
-While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, the interior conditions in both cases presented a significant hazard to firefighters inside of the structure.
+While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, with respect to exposure to firefighters operating within flow path, both cases presented similar high hazard contitions.
 Therefore, the analysis will focus on the results of the baseline simulation.
@@
 Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling.
-Gases at an elevated pressure will always move towards a region of lower pressure.
-The door serves as a boundary between the high and low pressure regions.
+On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling from bouyancy due to temperature differences.
+Gases at an elevated pressure will always move towards a region of lower pressure.The door serves as a boundary between the high and low pressure regions.
 Once the door fails open, the high pressure gases flow towards the low pressure regions in the house, hallway, kitchen, and front stairwell.
@@
 \end{figure}
+
+Recall from Fig.~\ref{fig:smv_ext_fire}, the exterior combustion.
+The Smokeview image shows a bi-directional vent at the rear of the structure.
+Hot fire gases at elevated pressure exit at the top of the vent while exterior gases at ambient conditions are entrained by the plume and flow into the bottom of the vent to sustain combustion.
 
@@
 Exposure to these conditions likely weakened the structural integrity of the door, which may have led to a partial failure (Table~\ref{tab:firesim}).
-Figure~\ref{fig:chicago_doorfold} shows the state of the rear door after the fire.
+Figure~\ref{fig:chicago_doorfold} is an image of the interior face of the door with the bottom of the door on towards the right side of the image.
+Shown is the state of the rear door after the fire.
 Note the large crease in the steel face of the door just above the knob.

### 2015-05-01 Studies/2012_Chicago/Report/response.tex
Chicago_Fire: update report and response file for FireTech, add attic fire images, and cleanup input file.

@@
 \documentclass[12pt]{article}
+\usepackage[pdftex]{graphicx}
 \frenchspacing
@@
 \item We would appreciate more efforts in assessing or estimation somehow the error or uncertainty of your results. \\
-{\bf Dan -- not sure about this comment - there is model uncertaintly in predicting temperature from a HRR or undercertainty in specifying uncertainty.
-I have something written at the end of Section 3.6 - but as far as error/uncertainty it could be massive based on all the unknowns we have.
-I also added a comment about 50 kW/m2 being conservative.}
+{\it A section was added to reflect uncertainties in FDS.}
 \item An effort to read some of the work published in Fire Technology on the topics at hand would be appreciated by the editorial board. \\
@@
 \\
-{\bf Dan - we know this behavior - exterior combustion -- is pretty realistic from the UL tests - but I cannot find the report anywhere.
-Do you have it or should I try to cite the course?
-FDS predicts minimal flaming combustion into the hallways at the ceiling right near the doorway.
-This seems realistic me but we have nothing to confirm or deny that.}
+{\it The authors have witnessed this type of attic vent fire behavior in studies that are currently underway (cf.
+Fig.~\ref{fig:eave}) and previous work conducted by Underwriters' Laboratory.
+Therefore, they belive this behavoir to be realistic.}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.6\textwidth]{../Figures/PA020340}
+\caption{External buirning throught attic eave}
+\label{fig:eave}
+\end{figure}
+
 \item The authors discard the secondary simulation based on the similarity of the overall HRR, but an alternative ventilation pattern could potentially alter the flow path inside the building.
@@
 \\
-{\bf Dan - I don't have this unless I re-run the simulation with a ton of devices to calculate this.
-Not sure what value it adds though - but I could add a point that a lot of the combustion is exterior to the structure.}
+{\it Addressed by other reviewer's comments. See section in text.}
 \item Attic fire: Was any of the roof ``consumed?'' [See Fig.
@@
 \\
-{\bf I don't want to change this because I like the colored cross hatching, but I guess I am going to have to?}
+{\it Images were removed to address excess figures but a reference was made to report where figures live.}
 \item  It would be helpful to have a floor plan of the attic space that includes the locations of the roof vents. \\

### 2015-05-01 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago_Fire: update report and response file for FireTech, add attic fire images, and cleanup input file.

@@
 Note that the majority of the damage occurred in the attic and rear porch on the second floor.
-Fully dimensioned drawings of the interior of the first and second floors are shown in Appendix~\ref{app_draw} in Figs.~\ref{fig:first_floor} and \ref{fig:second_floor}, respectively.
+Fully dimensioned drawings of the interior of the first and second floors can be found in~\cite{Weinschenk:Chicago}.
 
@@
 
+\subsection{Model Uncertainy}
+\label{mod_uncertain}
+FDS can provide valuable insight into how a fire may have developed.
+However, the model is only a simulation.
+The model output is dependent on a variety of input values such as material properties, time lines, geometry, and ventilation openings.
+Since complete knowledge of every detail of the fire site, fuel load, or fire timeline is never available; estimations are incorporated into the model.
+For example, the estimation of the energy release rate of an initial ``source fire'' as a starting point for fire development and spread throughout the structure is a necessary part of recreating this fire scenario.
+These estimations and others used in this simulation are further described in Section~\ref{model} of this report.
+
+The ability of the FDS model to predict accurately the temperature and velocity of fire gases has been previously evaluated by conducting experiments, both lab-scale and fullscale, and measuring quantities of interest.
+For relatively simple fire driven flows, such as buoyant plumes and flows through doorways, FDS predictions are within the experimental uncertainty of the values measured in the experiments~\cite{FDS_Validation_Guide}.
+For example, if a gas flow velocity is measured at 0.5 m/s (1.6 ft/s) with an experimental uncertainty of $\pm$ 0.05 m/s ($\pm$ 0.2 ft/s), the FDS model gas flow velocity predictions were also in the range between 0.45 m/s and 0.55 m/s (1.5 ft/s and 1.8 ft/s).
+In large scale fire tests reported in \cite{FDS_Validation_Guide}, FDS temperature predictions were found to be within 15 \% of the measured temperatures and the FDS heat release rates were predicted to within 20 \% of the measured values.
+Therefore, the results should be considered as ranges to address these uncertainties.
+
 \section{Model Results}
@@
 Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
+Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that cofirms this type of fire behavoir.
 After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
@@
 \centering
-\includegraphics[width=.675\textwidth]{../Figures/smv_exterior_fire}
-\caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure.}
+\includegraphics[width=.5\textwidth]{../Figures/smv_exterior_fire}
+\includegraphics[width=.45\textwidth]{../Figures/PA020413}
+\caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure (left) and photograph from ongoing attic fire experiments (right).}
 \label{fig:smv_ext_fire}
@@
 Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
+In this case, according the NIOSH report the victim was not wearing gloves or flash hood~\cite{NIOSH:Bowyer}.
 
@@
 
-\section{Dimensioned Drawings}
-\label{app_draw}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1\textwidth]{../Figures/50th_Place_1st_Floor}
-\caption[Dimensioned drawing of first floor.]{Dimensioned drawing of first floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:first_floor}
-\end{figure}
-
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=1\textwidth]{../Figures/50th_Place_2nd_Floor}
-\caption[Dimensioned drawing of second floor.]{Dimensioned drawing of second floor. The measurements are accurate to within 15~cm (6~in).}
-\label{fig:second_floor}
-\end{figure}
-
-\clearpage
-
 \section{Numerical Mesh Figures}

### 2015-05-01 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago: minor update

@@
 The polycarbonate material in the facepiece of a self-contained breathing apparatus begins to soften when the material temperature reaches approximately 140~$^{\circ}$C (284~$^{\circ}$F)~\cite{mensch2011emergency}.
-Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F) or 10~kW/m$^2$~\cite{nfpa2013standard} for less than 2.5~min.
-Exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
+Structural fire fighting coats and pants are tested to withstand temperatures up to 260~$^{\circ}$C (500~$^{\circ}$F)~\cite{nfpa2013standard}.
+Prolonged exposure to elevated temperatures can result in a significant amount of heat transferred to the firefighter, putting him or her at risk.
 In this case, according the NIOSH report the victim was not wearing gloves or flash hood~\cite{NIOSH:Bowyer}.

### 2015-05-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch5

@@
 For piloted ignition tests, an electric spark ignitor is positioned at the top of vertical samples and over the center of horizontal samples.
-Samples are typically 100~mm squares.
 Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
@@
 
-For this study samples were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
-The experiments were conducted with the sample in the horizontal position.
-Measurements made with the cone calorimeter, in addition to heat release rate per unit area of the samples, included using a series of experiments at different heat fluxes to determine a ignition time and surface temperature pairs.
+For this study samples were cut from painted gypsum wallboard panels.
+The samples were 100~mm square, and 12.7~mm thick.
+The experiments were conducted with the samples in the horizontal position.
+The key measurements and observations made with the cone calorimeter were heat release rate per unit area of the samples and time to ignition.
+These experiments were conducted with heat fluxes of 25, 35, 50, 70 and 75 kW/m$^2$.
+Several other cone calorimeter experiments were conducted with a single type K thermocouple, installed in a slit in the painted paper on the gypsum wallboard samples.
+This was the same manner of thermocouple installation used in the instrumented gypsum board wall experiments.
+These experiments were conducted at heat fluxes of 25, 30, and 35 kW/m$^2$ to determine ignition time and surface temperature pairs.
 
@@
 A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel.
-The panel is inclined at 30~$^{\circ}$, and under standard operating conditions provide a heat flux on the test specimen varying from 10~kW/m$^2$ at the point closest to the panel to 1~kW/m$^2$ at the farthest point.
-For these experiments a higher heat flux profile was required, so the gas air increased    comback   to  Figure~\ref{FRP_HF_Calibration}
-
-A pilot flame is used to ignite the test sample.
+The panel is inclined at 30~$^{\circ}$, and under standard operating conditions provide a heat flux on the test specimen varying from 10~kW/m$^2$ at the measurement point, centered 100~mm from the edge of the sample closest to the panel to 1~kW/m$^2$ at the farthest measurement point 900~mm from the edge of the sample closest to the panel.
+For these experiments a higher heat flux profile was required, so the gas air increased to provide an incident flux of approximately 21~kW/m$^2$ to 2~~kW/m$^2$.
+Figure~\ref{FRP_HF_Calibration}
+
+A pilot flame from a mm long line burner is used to ignite the test sample near the edge of the sample closet to the panel.
 The objective of the test is to determine the critical radiant flux for a given sample.
 The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped.
-For this study the samples examined were cut from painted gypsum wallboard panels that were prepared with the panels used in the compartment experiments.
+For this study the samples examined were cut from painted gypsum wallboard panels that were prepared from the supply of panels that were used in the compartment experiments.
 
@@
 	\includegraphics[width=\textwidth]{../Figures/FRP_HF_Calibration} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
+	\caption[Incident heat flux profile in the radiant flooring panel test apparatus]{Incident heat flux profile along the centerline of the sample in the radiant flooring panel test apparatus}
 	\label{FRP_HF_Calibration}
@@
 Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
-Within a CFD model, the room or building is divided into small three-dimensional rectangular control volumes or computational cells.
-The cells are contained together within a larger volume known as the computational domain.
+Within a CFD model, the computational domain is divided into small three-dimensional rectangular control volumes or computational cells.
 The CFD model computes the density, velocity, temperature, pressure, and gas concentrations in each cell.
@@
 Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.
-
-Input data was collected from the experimental results presented in Chapters XXs and from literature sources in order to simulate the experiments a fire using FDS or any other fire model.
-For the simulation results presented in this document, information was obtained from two primary sources
+Smokeview also has a feature that can represent a fire pattern on a surface based on user supplied threshold criteria.
 
@@
 
+An FDS model was developed to simulate the instrumented wall experiments with the natural gas burner.
+Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.
+The three computational grid sizes used were : 80~mm, 40~mm, and 20~mm.
+
 \subsection{Input Data}
+
+Input data was collected from the experimental results presented in Chapters II and V, and from literature sources in order to simulate the instrumented wall experiments using FDS.
+
+Geometry – the domain of the model was cubic with 2.4~ m on a side.
+The resulting number computational cells for each case ranged from 27,000 for the 80~mm case to 1,728,000 for the 20~mm cases.
+An isometric view of the model outlined by the domain is shown in Figure     .
+The face of the wall is located 1.35~m from the front of the domain.
+The wall was modelled with material properties for gypsum board.
+Thermal conductivity = 0.28
+Specific Heat = 1.00
+Density = 582
+
+Instruments – FDS has devices, which are used to simulate thermocouples and total heat flux gauges.
+This devices were positioned  in locations similar to the locations used in the physical experiments, in the plume region and on the wall.
+A radiative heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.
+In addition, FDS features devices that can not be implemented such as a device, which can be used to examine the heat release rate per unit length.
+In this case, this device was used to determine flame height based on that measure.
+Fire 
+The burner was modeled as an obstruction, with the same physical size as the burner.
+It was modelled with a steady state heat release rate of 888.89 kW/sq m.
+The chosen fuel reaction was `methane’ since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.
 

### 2015-05-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Still working on Chapter 5

@@
 The heater can expose samples to a maximum irradiance of approximately 100~kW/m$^2$.
-Figure  is a schematic of the cone calorimeter.
+Figure~\ref{Cone_Cal} is a schematic of the cone calorimeter.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Cone_Cal} \\
+	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter}
+	\label{Cone_Cal}
+\end{figure}
 
@@
 The radiant flooring panel test method is known as ASTM~E648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}.
-A 1~m long test specimen is mounted horizontally beneath a pre-mixed air-gas-fueled radiant panel.
-The panel is inclined at 30~$^{\circ}$, and under standard operating conditions provide a heat flux on the test specimen varying from 10~kW/m$^2$ at the measurement point, centered 100~mm from the edge of the sample closest to the panel to 1~kW/m$^2$ at the farthest measurement point 900~mm from the edge of the sample closest to the panel.
-For these experiments a higher heat flux profile was required, so the gas air increased to provide an incident flux of approximately 21~kW/m$^2$ to 2~~kW/m$^2$.
-Figure~\ref{FRP_HF_Calibration}
-
-A pilot flame from a mm long line burner is used to ignite the test sample near the edge of the sample closet to the panel.
-The objective of the test is to determine the critical radiant flux for a given sample.
-The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped.
-For this study the samples examined were cut from painted gypsum wallboard panels that were prepared from the supply of panels that were used in the compartment experiments.
-
-\begin{figure}[p]
+The radiant flooring panel is used to measure the flame spread of a material while exposed to an incident radiant heat flux.
+The source of the heat flux is a pre-mixed air-gas-fueled radiant panel.
+The radiating surface measures 305~mm by 457~mm.
+The radiating surface is inclined at 30~$^{\circ}$ above the horizontal.
+The test specimen is mounted horizontally beneath the radiant panel.
+The surface of the test sample exposed to the radiant panel is 1~m long and 0.2~m wide.
+Under standard operating conditions the radiant panel provides a heat flux distribution on the test specimen varying from 10~kW/m$^2$ at the measurement point, centered 100~mm from the edge of the sample closest to the panel to 1~kW/m$^2$ at the farthest measurement point 900~mm from the edge of the sample closest to the panel.
+A schematic of the radiant flooring panel apparatus is shown in Figure~\ref{FLR_Radpan}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/FLR_Radpan} \\
+	\caption[Schematic of the radiant flooring panel apparatus]{Schematic of the radiant flooring panel apparatus}
+	\label{FLR_Radpan}
+\end{figure}
+
+ For these experiments a higher heat flux profile was required to propagate flame spread on the painted gypsum wallboard samples, so the air-gas flow supplying the radiant panel was increased to provide an incident flux ranging from approximately 21~kW/m$^2$ at the 100~mm position to 2~kW/m$^2$ at the 900~mm position.
+The incident heat flux curve used in these experiments is shown in Figure~\ref{FRP_HF_Calibration}.
+
+\begin{figure}
 	\centering
@@
 
+A pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
+The objective of these experiments was to determine the critical radiant flux for the painted gypsum wallboard samples.
+The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped.
+For this study the samples examined were cut from painted gypsum wallboard panels that were prepared from the supply of panels that were used in the compartment experiments.
+
 \section{Radiant Panel Experiments}
 
-The vertical radiant panel is used as documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
-The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that is 305~mm × 457~mm.
-
-However for the purposes of this study a modified version of the test apparatus was used.
-The radiant panel and and the radiant panel controls remained in place as documented in ASTM~E162.
+The vertical radiant panel used is documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
+The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that has a radiating surface 305~mm wide by 457~mm high.
+
+For the purposes of this study a modified version of the test apparatus was used.
+The radiant panel and the radiant panel controls remained in place as documented in ASTM~E162.
 However the sample mounting system was changed.
 A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux.
-This trolley was used to hold a sample of painted gypsum wallboard were exposed to the radiant .
-Figure
-
-In the modified test configuration the exposed surface of the sample was parallel to the radiant panel.
-The radiant panel was calibrated and mapped with a heat flux gauge.
-With the flux gauge data, positions away from the radiant panel were identified to enable the samples to be exposed to a range of heat fluxes.
-After a timed exposure the samples were examined and area of thermal damage to the painted paper surface of the gypsum board was compared with heat flux mapping.
+This trolley was used to hold a sample of painted gypsum wallboard that was 362~mm square.
+The samples were vertical and parallel to the radiant panel.
+Figure~\ref{Rad_Panel} has photographs which show the radiant panel test arrangement.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=2.92in]{../Figures/RAD_pan}
+	\includegraphics[width=2.08in]{../Figures/RAD_pan_iso} \\
+	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the moveable mounting frame for the gypsum wallboard sample on the left.
+The photograph on the right shows an isometric view of the test arrangement.}
+	\label{Rad_Panel}
+\end{figure}
+
+Heat flux gauge measurements, taken at the center position of the sample, were used to determine positions on the trolley track for a specific radiant exposure.
+Positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
+The area surrounding the center of the maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
+In other words, the area around the center point of the sample had heat flux measures similar, within the uncertainty of the device, to the center point measurement.
+Outside of the central area of the samples, the heat flux would decrease as the position approached the edge of the sample.
+The center point heat flux measures vs the distance from the radiating surface is provided in Figure~\ref{Rad_Panel_Cal}
+
+To conduct the experiments, the radiant panel was ignitied and allowed to pre-heat for at least 60 minutes.
+The water cooled, Schmidt-Boelter total heat flux gauge was mounted in the center the sample holder, and the heat flux positions were confirmed.
+Just before the sample was mounted on the movable trolley, an aluminium heat shield was placed between the radiant panel and the sample holder.
+Once the sample was mounted and the sample was moved to the appropriate distance from the radiant panel based on the heat flux desired for the experiment, the heat shield was removed that the experiment began.
+Each sample was exposed for 600 seconds.
+Each sample had a single bare-bead, Chromel-Alumel (type K) thermocouple, with a 0.5~mm nominal diameter bead in contact with the center point of each sample.
+During the experiments the samples were monitored for temperature and ignition.
+examined and area of thermal damage to the painted paper surface of the gypsum board was compared with heat flux mapping.
 This was another means of potentially obtaining a measure of the critical heat flux.
-Figure 2.3.11 illustrates the radiant panel test apparatus.
+.11
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/Rad_Panel_Cal} \\
+	\caption[Incident heat flux profile based on the distance between the sample face and the radiant panel]{Incident heat flux profile based on the distance between the sample face and the radiant panel}
+	\label{Rad_Panel_Cal}
+\end{figure}
 
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-Each row of samples represents three replicate experiments at a given heat flux for 600s.
-Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.
-}
-	\label{RP_GB_Front}
-\end{figure}
-
-\subsection{Heat Release Rate per Unit Area}
-
-\subsection{Critical Heat Flux}
+Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range physical damage to samples as shown in Figure~\ref{RPGB_SET}.
+However there based on visual observations there were no flaming ignitions.
+One of the samples at 15~kW/m$^2$, small sections of the paint/paper fuel would peel or partially separate from the gypsum core and would begin to glow.
+This process became more prevalent as the heat fluxes increased.
+There are no photos of the samples that were exposed to 25~kW/m$^2$.
+The radiant exposure caused the samples to collapse as they were being removed from the holder.
+Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
+Notice that the samples exposure at 17.5~kW/m$^2$ and higher have a temperature increase to a peak temperature followed by a decrease.
+This trend may be may indicative of combustion of the paint and paper adding to the energy at on the face of the sample.
 
@@
 ]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-Each row of samples represents three replicate experiments at a given heat flux for 600s.
-Begining with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.
-}
+Each row of samples represents three replicate experiments at a given heat flux.
+Beginning with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
 	\label{RPGB_SET}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
+	\caption[Time vs.
+temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel]{Time vs.
+temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.}
+	\label{RP_GB_Front}
+\end{figure}
+
+\subsection{Heat Release Rate per Unit Area}
+
+\subsection{Critical Heat Flux}
+
+Seven replicate experiments were conducted in the radiant flooring panel apparatus.
+The mean burn length was 432~mm with a 95$\%$ confidence limit of $\pm$18~mm.
+Comparing this burn length range, 414~mm to 450~mm, to the incident heat flux curve provided a critical heat flux of approximately 9~kW/m$^2$.
+Photographs showing a radiant flooring panel test underway and sample nearing the flameout position are provided in Figure~\ref{FRP_Test_Photos}.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=1.8in]{../Figures/FRP_Test_Photo1}
+	\includegraphics[width=3.2in]{../Figures/FRP_Test_Photo2} \\
+	\caption[Photographs of the radiant flooring panel experiments]{Photographs of the radiant flooring panel experiments, on the left is a photograph aimed at the radiant panel showing the pilot flame on the sample as well as the flame front on the sample.
+The photograph on the right show the flame front on the sample just prior to flame out.}
+	\label{FRP_Test_Photos}
 \end{figure}

### 2015-05-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added test and refs to Intro - draft ack

@@
 
-\dedication{To my wife and family}  work family
+\dedication{To my wife and family}
 
@@
 The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus reduce the losses from fires.
-However, as the result of the review of several arson cases and a review by the U.S.
+However, as the result of the review of several arson homicide cases and a review forensics by the U.S.
 National Academy of Sciences, questions about the lack of the use of science in the practice of fire investigation were raised.
@@
 \acknowledgments{
-I would like to thank Prof.~Fleishmann, etc.
-
-This work was partially funded by the National Institute of Justice (NIJ) through an interagency agreement with the NIST Office of Law Enforcement Standards (OLES).
+I would like to thank Prof.~Fleishmann, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
+
+The full-scale and bench-scale experiments were conducted over a period of several years whenever funding and laboratory availability coincided.
+These experiments were conducted with the support of several engineering technicians from the NIST Fire Research Division, especially Roy McLane, Jay McElroy, Laurean DeLauter, and Anthony Chakalis.
+Their assistance was essential.
+Their patience and attention to detail during this study is greatly appreciated
+
+This work was partially funded by the National Institute of Justice (NIJ) through an inter-agency agreement with the NIST Office of Law Enforcement Standards (OLES).
 I would like to thank Susan Ballou of OLES for her support of this project.
@@
 
-The would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury
-
-Finally, my family...
-}
+I would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury
+
+Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 37 years of marriage.
+I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for "buying me time" to work on my studies.}
 
@@
 Consumer Product Safety Commission or a manufacturer issuing a product recall.
+
 In some cases, the fire investigation determines that the fire was intentional.
 An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention~\cite{Campbell:2014}.
-An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be.''~\cite{NFPA_921}.
+An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be''~\cite{NFPA_921}.
 
@@
 Arson is a challenging crime to solve because typically there are no witnesses present at the time of the crime.
+
+The values cited above are believed to be the best available in the United States and perhaps one of the better fire incident databases in the world.
+However an investigative report by Icove and Hargrove, indicates that arson fires are underreported to the National Fire Incident Reporting System (NFIRS).
+The investigation provided examples from several major cities, such as New York City, where in 2011, 11 arson fires in buildings were reported to NFIRS, while the Fire Department of the City of New York's Bureau of Fire Investigation had recorded 1,347 arson fires in buildings that year.
+Similar discrepancies were found in eight other large U.S.
+cities.
+On average, three-fourths of the arsons uncovered by city fire investigators went unreported to NFIRS~\cite{Icove_2014}.
 
@@
 Given the limited number of experiments in the literature and the large number of variables, it has been difficult to fully understand a cause and effect relationship between the fire scenarios and the resulting patterns.
-Therefore, fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula}.
+
+Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula}.
 Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
@@
 Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount or research and analysis tools directly related to this practice.
+Gorbett recently conducted a review of fire pattern research that has been conducted over the last 80 years.
+The review points out many gaps, especially with how fire patterns are used to determine the area of origin.
+A key limitation is the assumption by many of the researchers, or text authors, that investigators are able to visibly assess varying degrees of fire damage and then determine the area of origin~\cite{Gorbett_2015}.
+Studies have shown that investigators have not been able to use only the location of the fire patterns as means of reliably determining the area of origin, some amount of analysis and fire dynamics knowledge is required~\cite{Carmen_2008},~\cite{Tinsley_2013}.
+
 The fire investigation community recognized a need to improve the science and practice of fire investigation.

### 2015-05-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
minor edits to intro

@@
 \acknowledgments{
-I would like to thank Prof.~Fleishmann, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
+I would like to thank Prof.~Fleishmann, my senior advisor with the University of Canterbury, as well as, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
 
@@
 Comparative experiments were conducted to examine the impact of the method of construction and support of the walls and corner sections on the development of the burn patterns.
-Three cases were examined: (1) 12.7~mm thick, regular core, painted gypsum board on the front of a wall frame (open back); (2) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame (interior wall); and {3) 12.7~mm thick, regular core, painted gypsum board on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
+Three cases were examined: (1) 12.7~mm thick, regular core, painted gypsum wallboard on the front of a wall frame (open back); (2) 12.7~mm thick, regular core, painted gypsum wallboard on the front and back of a wall frame (interior wall); and {3) 12.7~mm thick, regular core, painted gypsum wallboard on the front and back of a wall frame, with fiberglass batting insulation in the voids of the wood frame (exterior wall).
 The main consideration was to identify any differences in the height, width, shape, and area of the fire patterns.
@@
 A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
-The flooring radiant panel (ASTM~E648) was used to examine this value.
+The flooring radiant panel, ASTM~E648, and a modified radiant panel apparatus based on ASTM~E162 were used to examine this value~\cite{ASTM_E648},~\cite{ASTM_E162}.
 
@@
 
-Cone calorimeter~\cite{ASTM_E1354} experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$.
+Cone calorimeter, ASTM~E1354, experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
 
@@
 The ability to recreate or simulate a fire pattern or certain characteristics of a fire pattern was examined with a variety of tools.
-The first characteristic examined was the ability to determine based on the calculated heat flux to the wall if a ``visible or measurable physical change'' would occur to the painted paper surface of the gypsum wallboard.
+The first characteristic examined was the ability to determine, based on the calculated heat flux to the wall, if a ``visible or measurable physical change'' would occur to the painted paper surface of the gypsum wallboard.
 The next characteristic of the fire pattern that was examined was the height.

### 2015-05-14 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Adding Bench Exp results

@@
 \Supervisor{Dr Charles Fleischmann}
-\Department{Department of Fire Safety Engineering}
+\Department{College of Engineering, Civil and Natural Resources Engineering}
 
@@
 
-For piloted ignition tests, an electric spark ignitor is positioned at the top of vertical samples and over the center of horizontal samples.
-Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
+For the ignition tests, an electric spark ignitor was positioned over the center of the horizontal samples to serve as a pilot.
+Combustion products and dilution air were extracted through the hood and exhaust duct by a high temperature fan.
 The flow rate can be adjusted between 0.01 and 0.03~m$^3$/s.
-The volumetric flow rate is kept constant during testing.
-The sample is mounted on a load cell to determine mass loss rate during a test, and smoke obscuration is measured using a laser light source.
-The gas flow rate in the exhaust duct is calculated from the pressure drop across and temperature at an orifice plate in the duct.
+The volumetric flow rate was kept constant during testing.
+The sample was mounted on a load cell to determine mass loss rate during a test, and smoke obscuration was measured using a laser light source.
+The gas flow rate in the exhaust duct was calculated from the pressure drop across and temperature at an orifice plate in the duct.
 Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, were measured using appropriate instruments.
-Heat release rate is calculated from the gas concentration and mass flow measurements.
+Heat release rate was calculated from the gas concentration and mass flow measurements.
 
 For this study samples were cut from painted gypsum wallboard panels.
-The samples were 100~mm square, and 12.7~mm thick.
+The samples were 100~mm square and 12.7~mm thick.
 The experiments were conducted with the samples in the horizontal position.
@@
 This was the same manner of thermocouple installation used in the instrumented gypsum board wall experiments.
-These experiments were conducted at heat fluxes of 25, 30, and 35 kW/m$^2$ to determine ignition time and surface temperature pairs.
+These experiments were conducted at heat fluxes of 30, 35, and 50 kW/m$^2$ to determine ignition time and surface temperature pairs.
 
@@
 
-A pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
+A diffusion, propane-fueled, pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
 The objective of these experiments was to determine the critical radiant flux for the painted gypsum wallboard samples.
@@
 For the purposes of this study a modified version of the test apparatus was used.
-The radiant panel and the radiant panel controls remained in place as documented in ASTM~E162.
+The radiant panel and the controls for the radiant panel  remained in place as documented in ASTM~E162.
 However the sample mounting system was changed.
-A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux.
+A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux~\cite{Lawson:1999}.
 This trolley was used to hold a sample of painted gypsum wallboard that was 362~mm square.
@@
 	\includegraphics[width=2.08in]{../Figures/RAD_pan_iso} \\
-	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the moveable mounting frame for the gypsum wallboard sample on the left.
+	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the moveable sample mounting frame trolley for the gypsum wallboard sample on the left.
 The photograph on the right shows an isometric view of the test arrangement.}
@@
 
-Heat flux gauge measurements, taken at the center position of the sample, were used to determine positions on the trolley track for a specific radiant exposure.
-Positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
+Prior to conducting experiments with the gypsum wallboard samples, heat flux gauge measurements taken at the center position of the sample were used to determine the positions on the trolley track for a specific radiant exposure.
+The positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
 The area surrounding the center of the maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
@@
 
-To conduct the experiments, the radiant panel was ignitied and allowed to pre-heat for at least 60 minutes.
+To conduct the experiments, the radiant panel was ignited and allowed to pre-heat for at least 60 minutes.
 The water cooled, Schmidt-Boelter total heat flux gauge was mounted in the center the sample holder, and the heat flux positions were confirmed.
-Just before the sample was mounted on the movable trolley, an aluminium heat shield was placed between the radiant panel and the sample holder.
-Once the sample was mounted and the sample was moved to the appropriate distance from the radiant panel based on the heat flux desired for the experiment, the heat shield was removed that the experiment began.
+The heat flux gauge was then removed from the sample holder trolley.
+Just before the sample was mounted on the movable trolley, an aluminum heat shield was placed between the radiant panel and the sample holder trolley.
+Once the sample was mounted and the sample was moved to the appropriate distance from the radiant panel based on the heat flux desired for the experiment, the heat shield was removed.
+The removal of the heat shield would be recorded as the beginning of the exposure and therefore the beginning of the experiment.
 Each sample was exposed for 600 seconds.
@@
 During the experiments the samples were monitored for temperature and ignition.
-examined and area of thermal damage to the painted paper surface of the gypsum board was compared with heat flux mapping.
+After the exposure time was completed the heat shield was once again placed between the sample and the radiant panel.
+The samples were cooled, removed and examined.
+The area of thermal damage to the painted paper surface of the gypsum board was compared with exposure heat flux.
 This was another means of potentially obtaining a measure of the critical heat flux.
-.11
 
@@
 
-\subsection{Ignition Temperature}
+\subsection{Ignition and Ignition Temperature}
+
+Three replicate time to ignition experiments were conducted with the cone calorimeter apparatus at each heat flux.
+The results of these experiments are shown in Table~\ref{tab:Gypsum_wallboard_timetoign}.
+The time to ignition values in the table are the average of the three times.
+Note that no ignition occurred at 25~kg/m$^2$.
+The exposure at 25~kg/m$^2$ resulted in charring and cracking of the painted paper surface of the gypsum wallboard sample.
+This began to occur, on average, at 270 s of exposure time.
+The samples were exposed to 25~kg/m$^2$ for 1800~s each and no ignition occurred.
+In the experiments with heat fluxes of 35~kg/m$^2$ or higher, ignition did occur and the painted paper surface of the gypsum board was consumed, leaving the gypsum board exposed.
+There were no surprises in the data with regard to the heat flux exposures.
+The time to ignition was reduced as the incident heat flux was increased.
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Incident Heat Flux & Ignition & Time to Ignition &  Fire Effect  \\
+		\hline (kg/m$^2$) &  & (s)  &   \\
+		\hline 25	& No 	& NA 		& Paint \& paper charred \& cracked \\
+		\hline 35 	& Yes 	& 73	 	& Paint \& paper consumed \\
+		\hline 50	& Yes 	& 35 	 	& Paint \& paper consumed   \\
+		\hline 70	& Yes 	& 21 	 	& Paint \& paper consumed \\
+		\hline 75	& Yes 	& 17 		& Paint \& paper consumed \\
+		\hline
+	\end{tabular}
+	\caption[Painted gypsum wallboard time to ignition results]{Painted gypsum wallboard time to ignition results from the cone calorimeter}
+	\label{tab:Gypsum_wallboard_timetoign}
+\end{table}
+
+Additional cone calorimeter experiments were conducted in the University of Canterbury Fire Laboratory.
+In these experiments the purpose was to obtain an estimate of the temperature of the painted paper surface at the time of ignition.
+Samples of painted gypsum wallboard were shipped from the NIST Fire Research Laboratory in Gaithersburg, MD., USA.
+In these experiments an additional incident heat flux level of 30~kg/m$^2$ was added to provide another test between the 25 and 35~kg/m$^2$ levels.
+The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
+The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident heat flux values of 35 and 50~kg/m$^2$, respectively.
+The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
+		\hline (kg/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline 30 	& Yes 	& 112	& 375 	 \\
+		\hline 35	& Yes 	& 50 	& 335 	 \\
+		\hline 50	& Yes 	& 38 	& 371 	 \\
+		\hline
+	\end{tabular}
+	\caption[Painted gypsum wallboard ignition temperature results]{Painted gypsum wallboard ignition temperature results from exposure in the cone calorimeter}
+	\label{tab:Gypsum_wallboard_igntemp}
+\end{table}
+
+In the radiant flooring panel experiments the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kg/m$^2$ to kg/m$^2$ over the length of the sample.
+In addition to the heat flux from the radiant panel, there is a small flame front approximately 10 to 30~mm in height that serves as the pilot along the length of the same and provides additional energy to the fuel immediately ahead of the flame.
+The impact is to a very limited area ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
+This effect is shown in Figure~\ref{FRP_flamefront}.
+In Figure~\ref{FRP_flamefront} several thermocouples can be seen.
+The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
+This was the same installation method that was used in the instrumented gypsum board wall experiments and to measure the ignition temperature of the cone calorimeter samples.
+The thermocouples that were installed in the center of the sample at 100~mm intervals beginning at 100~mm from the edge of the sample closest to the radiant panel.
+Three replicate experiments were conducted.
+The average time that the flame front reached the thermocouples and the temperature of the thermocouple just prior to the painted paper surface of the gypsum wallboard sample igniting is presented in Table~\ref{tab:FRP_timetemp}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/FRP_flamefront} \\
+	\caption[Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel] {Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel.
+Thermocouples imbedded at 100~mm intervals in the surface of the painted paper can be seen in front of and behind the flame front.
+The flame is leaning back in the direction the radiant panel.}
+	\label{FRP_flamefront}
+\end{figure}
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline Postion & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
+		\hline (mm) & (kg/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline 100 	& 21	& Yes 	& 133	& 315 	 \\
+		\hline 200	& 18 	& Yes 	& 198 	& 296 	 \\
+		\hline 300	& 14	& Yes 	& 302 	& 279 	 \\
+		\hline 400	& 10	& Yes 	& 502 	& 242 	 \\
+		\hline 500	&  7	& No 	& NA 	&     	 \\
+		\hline
+	\end{tabular}
+	\caption[Flooring radiant panel experiment flame spread results]{Flooring radiant panel experiment flame spread results including time to ignition at 100~mm intervals and surface temperature just prior to ignition.
+The values are averages from three replicate experiments.}
+	\label{tab:FRP_timetemp}
+\end{table}
 
@@
 \subsection{Heat Release Rate per Unit Area}
+
+\begin{table}
+	\centering
+	\begin{tabular}{|c|c|}
+		\hline Incident Heat Flux & Heat Release Rate per Unit Area    \\
+		\hline (kg/m$^2$) & (kg/m$^2$)  \\
+		\hline 35 	& 163 	\\
+		\hline 50	& 179   \\
+		\hline 70	& 255  	\\
+		\hline 75	& 231 	\\
+		\hline
+	\end{tabular}
+	\caption[Painted gypsum wallboard time heat release rate per unit area results]{Painted gypsum wallboard heat release rate per unit area results from the cone calorimeter}
+	\label{tab:Gypsum wallboard_HRRA}
+\end{table}
 

### 2015-05-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Bench scale ch

@@
 
+The results from the three different bench scale experiments are presented and discussed in this section.
+All three test methods provided some insight into the ignition and the critical heat flux required for ignition or flame spread of the painted paper surface on the gypsum wall board.
+The cone calorimeter also provided values for heat release rate.
+
 \subsection{Ignition and Ignition Temperature}
@@
 The time to ignition values in the table are the average of the three times.
-Note that no ignition occurred at 25~kg/m$^2$.
-The exposure at 25~kg/m$^2$ resulted in charring and cracking of the painted paper surface of the gypsum wallboard sample.
+Note that no ignition occurred at 25~kW/m$^2$.
+The exposure at 25~kW/m$^2$ resulted in charring and cracking of the painted paper surface of the gypsum wallboard sample.
 This began to occur, on average, at 270 s of exposure time.
-The samples were exposed to 25~kg/m$^2$ for 1800~s each and no ignition occurred.
-In the experiments with heat fluxes of 35~kg/m$^2$ or higher, ignition did occur and the painted paper surface of the gypsum board was consumed, leaving the gypsum board exposed.
+The samples were exposed to 25~kW/m$^2$ for 1800~s each and no ignition occurred.
+In the experiments with heat fluxes of 35~kW/m$^2$ or higher, ignition did occur and the painted paper surface of the gypsum board was consumed, leaving the gypsum board exposed.
 There were no surprises in the data with regard to the heat flux exposures.
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition &  Fire Effect  \\
-		\hline (kg/m$^2$) &  & (s)  &   \\
+		\hline (kW/m$^2$) &  & (s)  &   \\
 		\hline 25	& No 	& NA 		& Paint \& paper charred \& cracked \\
@@
 Samples of painted gypsum wallboard were shipped from the NIST Fire Research Laboratory in Gaithersburg, MD., USA.
-In these experiments an additional incident heat flux level of 30~kg/m$^2$ was added to provide another test between the 25 and 35~kg/m$^2$ levels.
+In these experiments an additional incident heat flux level of 30~kg/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
 The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (kg/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
 		\hline 30 	& Yes 	& 112	& 375 	 \\
@@
 
-In the radiant flooring panel experiments the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kg/m$^2$ to kg/m$^2$ over the length of the sample.
-In addition to the heat flux from the radiant panel, there is a small flame front approximately 10 to 30~mm in height that serves as the pilot along the length of the same and provides additional energy to the fuel immediately ahead of the flame.
-The impact is to a very limited area ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
+In the radiant flooring panel experiments the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kW/m$^2$ to 2~kW/m$^2$ over the length of the sample.
+In addition to the heat flux from the radiant panel, there is a small flame front approximately 10 to 30~mm in height that serves as the pilot along the length of the sample and provides additional energy to the fuel immediately ahead of the flame.
+The impact is limited to a small distance ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
 This effect is shown in Figure~\ref{FRP_flamefront}.
 In Figure~\ref{FRP_flamefront} several thermocouples can be seen.
-The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the paper face made with a razor blade.
-This was the same installation method that was used in the instrumented gypsum board wall experiments and to measure the ignition temperature of the cone calorimeter samples.
-The thermocouples that were installed in the center of the sample at 100~mm intervals beginning at 100~mm from the edge of the sample closest to the radiant panel.
+The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the painted paper face made with a razor blade.
+This was the same installation method that was used in the instrumented gypsum board wall experiments and in the cone calorimeter samples to measure ignition temperature.
+The thermocouples were installed in the center of the sample at 100~mm intervals beginning at 100~mm from the edge of the sample closest to the radiant panel.
 Three replicate experiments were conducted.
-The average time that the flame front reached the thermocouples and the temperature of the thermocouple just prior to the painted paper surface of the gypsum wallboard sample igniting is presented in Table~\ref{tab:FRP_timetemp}
+The average time that the flame front reached the thermocouples and the temperature of the thermocouple just prior to the painted paper surface of the gypsum wallboard sample igniting is presented in Table~\ref{tab:FRP_timetemp}.
 
@@
 
+ With the flooring radiant panel test, the incident heat flux from the panel and the pre-heated gypsum wallboard sample enables flame spread for approximately 500~s.
+The temperatures prior to ignition ranged from an average of 315 $^{\circ}$C for the 100~mm position to 242 $^{\circ}$C for the 400~mm position.
+The average
+
 \begin{table}
@@
 		\hline Postion & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (mm) & (kg/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
 		\hline 100 	& 21	& Yes 	& 133	& 315 	 \\
@@
 		\hline 400	& 10	& Yes 	& 502 	& 242 	 \\
-		\hline 500	&  7	& No 	& NA 	&     	 \\
+		\hline 500	&  7	& No 	& NA 	& NA   	 \\
 		\hline
@@
 Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range physical damage to samples as shown in Figure~\ref{RPGB_SET}.
-However there based on visual observations there were no flaming ignitions.
-One of the samples at 15~kW/m$^2$, small sections of the paint/paper fuel would peel or partially separate from the gypsum core and would begin to glow.
+However based on visual observations there were no flaming ignitions.
+For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
 This process became more prevalent as the heat fluxes increased.
-There are no photos of the samples that were exposed to 25~kW/m$^2$.
-The radiant exposure caused the samples to collapse as they were being removed from the holder.
+The radiant exposure of 25~kW/m$^2$ caused the samples to collapse as they were being removed from the holder.
+Hence there were no photos of those samples.
 Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
-Notice that the samples exposure at 17.5~kW/m$^2$ and higher have a temperature increase to a peak temperature followed by a decrease.
-This trend may be may indicative of combustion of the paint and paper adding to the energy at on the face of the sample.
+Notice that the samples exposed to 17.5~kW/m$^2$ and higher have a temperature increase to a peak temperature followed by a decrease.
+This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
+The temperatures at which the change in rate of temperature rise occur are between 300 and 400~ $^{\circ}$C.
 
@@
 
+The cone calorimeter experiments generated heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
+The average total heat released during each burn was 2.8 MJ/m$^2$.
+
 \begin{table}
@@
 		\hline Incident Heat Flux & Heat Release Rate per Unit Area    \\
-		\hline (kg/m$^2$) & (kg/m$^2$)  \\
+		\hline (kW/m$^2$) & (kW/m$^2$)  \\
 		\hline 35 	& 163 	\\
@@
 	\end{tabular}
-	\caption[Painted gypsum wallboard time heat release rate per unit area results]{Painted gypsum wallboard heat release rate per unit area results from the cone calorimeter}
+	\caption[Painted gypsum wallboard time heat release rate per unit area results]{Painted gypsum wallboard heat release rate per unit area results from the cone calorimeter.
+Each value is based on an average of three tests.}
 	\label{tab:Gypsum wallboard_HRRA}
@@
 The mean burn length was 432~mm with a 95$\%$ confidence limit of $\pm$18~mm.
-Comparing this burn length range, 414~mm to 450~mm, to the incident heat flux curve provided a critical heat flux of approximately 9~kW/m$^2$.
+Comparing this burn length range, 414~mm to 450~mm, to the incident heat flux curve provided a critical heat flux of approximately 8.9~kW/m$^2$ with a 95$\%$ confidence limit of $\pm$~0.6~kW/m$^2$.
 Photographs showing a radiant flooring panel test underway and sample nearing the flameout position are provided in Figure~\ref{FRP_Test_Photos}.
@@
 \end{figure}
+
+While the vertical radiant panel did not provide ignition data or heat release rate values it did provide information on the fire effect development on the painted gypsum wallboard samples with respect to heat flux.
+Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining the Figure~\ref{RPGB_SET} we see surface thermal effects of discoloration on the painted paper surface of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
+The samples exposed to 15~kW/m$^2$ exhibit charring and given the thin nature of the painted paper surface penetration was evidenced on two of the three sample.
+The sample of the right also shows signs of the painted paper being consumed.
+The samples exposed to 17.5~kW/m$^2$ and above all show signs of significant levels of painted paper consumption.
+As the heat flux was increased, the area of damage also increased.
+Even though the incident heat flux values were lower than the characteristic value measured at the center of the sample, as the heat flux in the center increased heat flux at the edges also increased above 15~kW/m$^2$.
+Hence the damaged area increased outward toward the edges.
+It would appear in this test series, that 15~kW/m$^2$ is right on the threshold of painted paper penetration and consumption.
+
+DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
+\begin{enumerate}
+	\item Surface deposits -– no irreversible effect on surface
+	\item Surface thermal effects –- physical change such a discoloration or melting
+	\item Charring -– evidence of surface burning
+	\item Penetration -– charring below the surface
+	\item Consumption –- loss of surface material, charring throughout
+\end{enumerate}
+
+Each apparatus provided similar but different thermal exposure conditions and each test method has a specific parameter or parameters that they were designed to measure for.
+Currently there is no specific protocol for a fire model user to follow to develop input data.
+Nor is there a "standard" catalog of fire model inputs for a given material.
+As a result the literature is sourced for information and users may to conduct experiments, such as those above, in order to develop values or ranges of values which could be used in the calculations in Chapters 8 and 9 or to evaluate the validity of the calculations in those chapters.
 
@@
 
-\section{Wall Construction Type Experiments}
+\section{Wall Position Experiments}
 
@@
 
-\section{Wall Position Experiments}
-\subsection{Experimental Arrangement}
-
-\subsection{Results}
-
-\subsubsection{Natural Gas}
-\subsubsection{Gasoline}
-\subsubsection{Polyurethane Foam}
-
 \section{Corner Position Experiments}

### 2015-05-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Bench Scale Chapter complete, Wall Tests started

@@
+@manual{ID,
+	ALTauthor = {author},
+	ALTeditor = {editor},
+	title = {title},
+	date = {date},
+	OPTsubtitle = {subtitle},
+	OPTtitleaddon = {titleaddon},
+	OPTlanguage = {language},
+	OPTedition = {edition},@unpublished{ID,
+		author = {author},
+		title = {title},
+		date = {date},
+		OPTsubtitle = {subtitle},
+		OPTtitleaddon = {titleaddon},
+		OPTlanguage = {language},
+		OPThowpublished = {howpublished},
+		OPTnote = {note},
+		OPTlocation = {location},
+		OPTisbn = {isbn},
+		OPTdate = {date},
+		OPTmonth = {month},
+		OPTyear = {year},
+		OPTaddendum = {addendum},
+		OPTpubstate = {pubstate},
+		OPTurl = {url},
+		OPTurldate = {urldate},
+	}
+
+	OPTtype = {type},
+	OPTseries = {series},
+	OPTnumber = {number},
+	OPTversion = {version},
+	OPTnote = {note},
+	OPTorganization = {organization},
+	OPTpublisher = {publisher},
+	OPTlocation = {location},
+	OPTisbn = {isbn},
+	OPTchapter = {chapter},
+	OPTpages = {pages},
+	OPTpagetotal = {pagetotal},
+	OPTaddendum = {addendum},
+	OPTpubstate = {pubstate},
+	OPTdoi = {doi},
+	OPTeprint = {eprint},
+	OPTeprintclass = {eprintclass},
+	OPTeprinttype = {eprinttype},
+	OPTurl = {url},
+	OPTurldate = {urldate},
+}
 \documentclass[twoside]{uocthesis}
@@
 To the left of the discoloration is clearly an larger area where charring (blackening of the paint/paper), penetration (lifting of the painted/paper residue), and consumption (areas where the paint/paper reside is gone altogether).
-The last two classifications or criteria will be used in this study to define the edge of the fire pattern.
-Any area where the paper has been burned away or penetrated such that it has lifted away from the gypsum will be considered part of the fire pattern and define the lines of demarcation for this study.
+The last three classifications or criteria will be used in this study to define the edge of the fire pattern.
+Any area where the painted paper surface has been charred, penetrated such that it has lifted away from the gypsum core, or burned away will be considered part of the fire pattern and define the lines of demarcation for this study.
 
@@
 
- The initial compartment experimental series were conducted to examine the impact of the method of construction of the walls on the development of the fire patterns.
+ The initial set of compartment experiments were conducted to examine if the type of wall construction would impact the development of the fire patterns.
 These experiments would determine how the walls for the remaining compartment fire pattern experiments would be constructed.
@@
 The wall behind the center panel of the rear wall was constructed either as open, closed, or insulated to meet the needs of the experiment.
-The burner was positioned against the face of the painted gypsum board.
+The burner was positioned against the face of the painted gypsum wallboard.
 As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
@@
 A total of 60 experiments were conducted.
-The results will be presented by wall construction type.  The order of presentation will be open, closed, and insulated wall construction.
+The results will be presented by wall construction type.
+The order of presentation will be open, closed, and insulated wall construction.
+
+For this analysis, the outline of the fire pattern, or the line of demarcation~\cite{NFPA_921}, was defined as the points where charring, penetration and consumption of the paper covering the gypsum wallboard stopped.
+The grids were used to assist with the determination of the fire pattern area and the sizing of the images.
+This defining edge was used to measure the dimensions of the fire pattern, such as height and width.
+Given the irregular shape of the patterns, the area of each pattern could not be calculated based solely on the maximum height and maximum width measurements.
+Therefore the areas of the grid cells within the fire pattern were added up to determine the area of the fire patterns.
+The analysis was carried out with a resolution of a quarter grid cell or approximately 0.003~m$^2$.
+
+There were four measures that were taken to characterize each pattern: maximum height, maximum width, height at maximum width, and the area.
+Each dimensional value is presented with the 95~\% confidence level (2~$\sigma$) based on Type A statistical analysis of the fire pattern measurements.
+
+There are also a number of qualitative terms from NFPA~921 that were used to describe features of the patterns.
+For example, "clean burn" to describe a lack of soot within a fire pattern area or "inverted cone" to describe the shape of the pattern~\cite{NFPA_921}.
 
@@
 Figure~\ref{NG_Open_Wall} shows a comparison of the ten fire patterns generated by the natural gas burner on the wall with open back construction.
-The images within the figure are slightly different sized however they are scaled so that the images are comparable.
-The grids were used to assist with the determination of the fire pattern area and the sizing of the images.
-In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
-The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{NFPA_921}.
+The images within the figure are slightly different sized in an effect to make the images comparable.
+The average maximum height of the fire pattern generated by the natural gas burner on the open walls was 0.74~m~$\pm~0.12~\%$.
+The average maximum width of the fire pattern from the same experiments was 0.24~m~$\pm~0.06~\%$.
+The position from the top edge of the burner to the vertical position of the maximum width was 0.41~m~$\pm~0.07~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.05~\%$.
+
+These fire patterns, as well as all of the other patterns in this study, are fire plume generated patterns.
+The bottom width of each patterns is similar to the width of the burner.
+Moving up from the burner, about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
+As the oxygen in the air mixes with the gaseous fuel and combusts, the plume and the pattern expands.
+As the flames move up the wall the width tends to increase until about half of the peak height of the pattern, then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame is reduced.
+Based on observation alone, the visible flames extend well above the height of the resulting patterns.
+Even though the experiments were conducted under quiescent conditions, a noticable bias to one side or the other can be seen in four of the ten experiments.
+
+The fire pattern photographs from the ten closed wall construction experiments are shown in Figure~\ref{NG_Closed_Wall}. 
+The patterns appear very similar in nature and size to the patterns that were generated on the open construction walls.
+The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06~\%$.
+The 95~$\%$ confidence limit is about half of the value from the open wall experiments.
+The average maximum width of the fire patterns was 0.24~m~$\pm~0.02~\%$.
+Again similar to the previous experiments.
+The vertical position of the maximum width was 0.43~m~$\pm~0.03~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.14~$m^2~\pm~0.01~\%$.
+
+The basic shape of these patterns on the closed wall are very similar to the patterns on the open wall.
+Six of the ten patterns have a bump out or an unsymmetrical curve within 200~mm of the top of the burner.
+The cause of these bumps in the patterns could not be determined.
+Three of the patterns have a noticeable lean.
+
+The last set of wall experiments with the natural gas burner was conducted with the insulated wall.
+The patterns from the ten replicate experiments are shown in Figure~\ref{NG_Insulated_Wall}.
+The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10~\%$.
+The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04~\%$.
+The vertical position of the maximum width was 0.42~m~$\pm~0.07~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02~\%$.
+
+For all intents and purposes, the patterns generated on the three different types of wall construction were the same.
+The comparison of the numerical values can be seen in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
+Each of the sets of
+patterns have a few patterns with the bump on one side of the pattern within 200~mm of the burner, as discussed in the section on the closed wall construction.
 
@@
 \subsubsection{Gasoline}
+
+Figure~\ref{Gas_Open_Wall} shows a comparison of the ten fire patterns generated by the natural gas burner on the wall with open back construction.
+The images within the figure are slightly different sized in an effect to make the images comparable.
+The average maximum height of the fire pattern generated by the natural gas burner on the open walls was 0.74~m~$\pm~0.12~\%$.
+The average maximum width of the fire pattern from the same experiments was 0.24~m~$\pm~0.06~\%$.
+The position from the top edge of the burner to the vertical position of the maximum width was 0.41~m~$\pm~0.07~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.05~\%$.
+
+These fire patterns, as well as all of the other patterns in this study, are fire plume generated patterns.
+The bottom width of each patterns is similar to the width of the burner.
+Moving up from the burner, about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
+As the oxygen in the air mixes with the gaseous fuel and combusts, the plume and the pattern expands.
+As the flames move up the wall the width tends to increase until about half of the peak height of the pattern, then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame is reduced.
+Based on observation alone, the visible flames extend well above the height of the resulting patterns.
+Even though the experiments were conducted under quiescent conditions, a noticable bias to one side or the other can be seen in four of the ten experiments.
+
+The fire pattern photographs from the ten closed wall construction experiments are shown in Figure~\ref{Gas_Closed_Wall}. 
+The patterns appear very similar in nature and size to the patterns that were generated on the open construction walls.
+The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06~\%$.
+The 95~$\%$ confidence limit is about half of the value from the open wall experiments.
+The average maximum width of the fire patterns was 0.24~m~$\pm~0.02~\%$.
+Again similar to the previous experiments.
+The vertical position of the maximum width was 0.43~m~$\pm~0.03~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.14~$m^2~\pm~0.01~\%$.
+
+The basic shape of these patterns on the closed wall are very similar to the patterns on the open wall.
+Six of the ten patterns have a bump out or an unsymmetrical curve within 200~mm of the top of the burner.
+The cause of these bumps in the patterns could not be determined.
+Three of the patterns have a noticeable lean.
+
+The last set of wall experiments with the natural gas burner was conducted with the insulated wall.
+The patterns from the ten replicate experiments are shown in Figure~\ref{Gas_Insulated_Wall}.
+The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10~\%$.
+The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04~\%$.
+The vertical position of the maximum width was 0.42~m~$\pm~0.07~\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02~\%$.
+
+For all intents and purposes, the patterns generated on the three different types of wall construction were the same.
+The comparison of the numerical values can be seen in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
+Each of the sets of
+patterns have a few patterns with the bump on one side of the pattern within 200~mm of the burner, as discussed in the section on the closed wall construction.
 
@@
 
+Impact of Instrumentation on Walls?
+
+Impact of Wall Construction
+
 \chapter{Future Research Needs}

### 2015-06-05 Projects/DelCo_2012/Report/DelCo_2012.tex
Added files from personal directories.

@@
 The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure.
-Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics.
-This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression.
+Additionally, the type of suppression agent can affect the fire behavior within the structure.
+The suppression agent is the main focus of this study to determine whether or not compressed air foam systems provide any significant benefit to the traditional water application.
+Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics over all types of suppression agents.
+This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.
 
@@
 \label{chap:Introduction}
-
-NIST FFTG
-
-Objective: To improve the safety and effectiveness of firefighters through measurement science to advance suppression tactics, examine non-traditional means of fire suppression, and transfer of the results to the fire service.
-
-Aid the fire service across the country in the most effective and safe way to fight fires.
-
-The goal is to improve the safety of not only the responding firefighters but the public as well through the use of modern fire suppression tactics for modern fires.
-
-Approach: Real scale, instrumented fire suppression experiments.
-
-This is an STRS project that has been complemented with OA studies funding from: 
-Cal Poly 
-FDNY 
-ISFSI 
-NYU
-
-NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.
-The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However ventilation tactics alone will not result in the complete extinguishment of the fire, fire suppression with hose streams are needed.
-
-Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice.
-This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
-
-Test Objectives:
-
-1)	Examine the water distribution for solid streams, straight streams, and fog streams.
-
-2)	Examine the impact of solid streams, straight streams, and fog streams on the cooling of fire gases inside a structure with various flow path configurations, structure configurations, and structure volumes.
-
-3)  Examine the impact of solid streams, straight streams, and fog streams on the
-
-Constants: 
-Building Geometry
-Fuel Load
-Fire Room Conditions at time of water flow
-Water Flow Rate – 120 gpm
-
-Variable: 
-Smooth Bore vs Narrow Fog
 
@@
 Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means  [ ].
-Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval (± a) is essentially 100 %.
+Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval (± a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95 % confidence interval (2σ).
+Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2σ).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of ± 6.0 mm (0.25) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft) [ ] .
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of ± 0.5 % for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of ± 0.5~\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
 Steel measuring tapes with a resolution of  ± 0.5 mm (0.02 in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of ±1.6 mm (0.06 in) for 9.1 m (30 ft) tapes and ±6.4 mm (0.25 in) for 30.5 m (100 ft) tapes [ ] .
-Some issues, such as “soft” edges on the upholstered furniture, result in an estimated total expanded uncertainty of  ± 1.0 %.
-
-The load cell used to weigh the fuels prior to the experiments had a range of 0 kg (0 lbs) to 200 kg (440lbs) with a resolution of a 0.05 kg (0.11 lb) and a calibration uncertainty within 1% [] .
+Some issues, such as “soft” edges on the upholstered furniture, result in an estimated total expanded uncertainty of  ± 1.0~\%.
+
+The load cell used to weigh the fuels prior to the experiments had a range of 0 kg (0 lbs) to 200 kg (440lbs) with a resolution of a 0.05 kg (0.11 lb) and a calibration uncertainty within 1~\% [] .
 The expanded uncertainty is estimated to be less than  ± 5 %.
@@
 In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
-The manufacturer reports a ± 3 % calibration expanded uncertainty for these devices [ ] .
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically ± 8 % [] .
-
-The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of ± 1 % when compared with span gas volume fractions [].
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of ± 12 % is being applied to the results [ ].
+The manufacturer reports a ± 3~\% calibration expanded uncertainty for these devices [ ] .
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically ± 8~\% [] .
+
+The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of ± 1~\% when compared with span gas volume fractions [].
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of ± 12~\% is being applied to the results [ ].
 
@@
 were factory calibrated and the zero and span of each was checked in the laboratory prior to the
-experiments yielding an accuracy of ± 1 % [ ] . The total expanded uncertainty was estimated at 10 %.
+experiments yielding an accuracy of ± 1~\% [ ] . The total expanded uncertainty was estimated at 10~\%.
 
@@
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a ± 5 % calibration expanded uncertainty for the flow sensor and ± 3 %  for the pressure sensor [ ] .
+The manufacturer reports a ± 5~\% calibration expanded uncertainty for the flow sensor and ± 3~\%  for the pressure sensor [ ] .
 The pressure transducer was calibrated with a known analog pressure gauge.
@@
 	\label{fig:Burn_Building_Fuel_Load}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
+	\caption{Pallet Fuel Load}
+	\label{fig:Pallet_Fuel_Load}
 \end{figure}
@@
 	\centering
-	\caption{Fuel masses}
-	\begin{tabular}{llcc}
+	\caption{Fire Suppression Fuel masses}
+	\renewcommand{\tabcolsep}{1pt}
+	\begin{tabular}{lllllll}
 		\hline\noalign{\smallskip}
-		Item                         &  Material Description             &  Dimensions (m)            &  Mass (kg)  \\
+		Item               & Component		& Quantity		&  Material Description             							&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
 		\noalign{\smallskip}\hline\noalign{\smallskip}
-		3-seat Legacy Sofa         &  491 Brawley                      &  1.96 m x 0.86 m x 0.89 m  &  56.2 kg    \\
-		Cushion (left)           &  Cotton w/ inner springs          &                            &  4.06 kg    \\
-		Cushions (center)        &  Cotton w/ inner springs          &                            &  4.56 kg    \\
-		Cushions (rear)          &  Cotton w/ inner springs          &                            &  4.16 kg    \\
-		2-seat New Sofa            &  491 Brawley                      &  1.59 m x 0.91 m x 0.86 m  &  33.3 kg    \\
-		Cushion (seat)           &                                   &  0.56 m x 0.61 m x 0.14 m  &  1.6 kg     \\
-		Cushion (rear)           &  0.71 m at top, 0.58 m at bottom  &  Varies x 0.53 m x 0.20 m  &  2.0 kg     \\
-		3-seat Brown Sofa            &  302 College (front room)         &  2.24 m x 1.02 m x 0.91 m  &  61.0 kg    \\
-		2-seat Purple Stripe Sofa    &  302 College (front room)         &  1.57 m x 0.97 m x 0.86 m  &  82.0 kg    \\
-		3-seat Black Pine Leaf Sofa  &  302 College (front room)         &  2.08 m x 0.86 m x 0.86 m  &  51.0 kg    \\
-		Blue/Brown Chair             &  302 College (front room)         &  0.97 m x 0.81 m x 0.97 m  &  46.4 kg    \\
-		2-seat Floral Sofa           &  302 College (rear room)          &  1.68 m x 0.91 m x 0.91 m  &  34.5 kg    \\
-		2-seat Blue Plaid Sofa       &  302 College (rear room)          &  1.63 m x 0.97 m x 0.91 m  &  39.8 kg    \\
-		3-seat Yellow Sofa           &  302 College (rear room)          &  2.13 m x 0.91 m x 0.71 m  &  48.3 kg    \\
-		3-seat Floral Sofa           &  302 College (rear room)          &  2.29 m x 0.91 m x 0.91 m  &  48.0 kg    \\
-		3-seat New Sofa              &  289 College (front room)         &  2.13 m x 0.91 m x 0.91 m  &  43.0 kg    \\
-		Blue Chair                   &  289 College (middle room)        &  0.91 m x 0.91 m x 0.91 m  &  25.3 kg    \\
-		3-seat Floral Sofa           &  289 College (sprinkler room)     &  2.24 m x 1.02 m x 1.02 m  &  81.2 kg    \\
-		Floral Chair                 &  289 College (sprinkler room)     &  1.02 m x 1.02 m x 1.02 m  &  36.3 kg    \\
+		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
+		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
+		           	 	   &	            &               &                                                          		&                            	&             		& \\[.25cm]
+			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
+		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
+		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
+		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame     &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
+		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
+		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2mm thick&  9    			& 72 \\
+		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
+		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11mm thick &  0.89 kg/m$^2$    & 19.8 \\
+		                   &                &               &                                                               &                               & Total Mass        & 335.6 \\
 		\noalign{\smallskip}\hline
 	\end{tabular} 
-	\label{tab:Fuel_Masses}
+	\label{tab:Fire_Suppression_Fuel_Masses}
 \end{sidewaystable}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
+	\caption{Sleeper Sofa}
+	\label{fig:Sleeper_Sofa}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
+	\caption{Mattress}
+	\label{fig:Mattress}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
+	\caption{Blue Chair}
+	\label{fig:Blue_Chair}
+\end{figure}
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB1}
+	\includegraphics[width=4in]{../Figures/Bars/BB1}
 	\caption{Burn Building Test 1}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB2}
+	\includegraphics[width=4in]{../Figures/Bars/BB2}
 	\caption{Burn Building Test 2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB3}
+	\includegraphics[width=4in]{../Figures/Bars/BB3}
 	\caption{Burn Building Test 3}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB4}
+	\includegraphics[width=4in]{../Figures/Bars/BB4}
 	\caption{Burn Building Test 4}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB5}
+	\includegraphics[width=4in]{../Figures/Bars/BB5}
 	\caption{Burn Building Test 5}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB6}
+	\includegraphics[width=4in]{../Figures/Bars/BB6}
 	\caption{Burn Building Test 6}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB7}
+	\includegraphics[width=4in]{../Figures/Bars/BB7}
 	\caption{Burn Building Test 7}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB8}
+	\includegraphics[width=4in]{../Figures/Bars/BB8}
 	\caption{Burn Building Test 8}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB9}
+	\includegraphics[width=4in]{../Figures/Bars/BB9}
 	\caption{Burn Building Test 9}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB10}
+	\includegraphics[width=4in]{../Figures/Bars/BB10}
 	\caption{Burn Building Test 10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB11}
+	\includegraphics[width=4in]{../Figures/Bars/BB11}
 	\caption{Burn Building Test 11}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB12}
+	\includegraphics[width=4in]{../Figures/Bars/BB12}
 	\caption{Burn Building Test 12}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB13}
+	\includegraphics[width=4in]{../Figures/Bars/BB13}
 	\caption{Burn Building Test 13}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB14}
+	\includegraphics[width=4in]{../Figures/Bars/BB14}
 	\caption{Burn Building Test 14}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB15}
+	\includegraphics[width=4in]{../Figures/Bars/BB15}
 	\caption{Burn Building Test 15}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB16}
+	\includegraphics[width=4in]{../Figures/Bars/BB16}
 	\caption{Burn Building Test 16}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB17}
+	\includegraphics[width=4in]{../Figures/Bars/BB17}
 	\caption{Burn Building Test 17}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB18}
+	\includegraphics[width=4in]{../Figures/Bars/BB18}
 	\caption{Burn Building Test 18}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB19}
+	\includegraphics[width=4in]{../Figures/Bars/BB19}
 	\caption{Burn Building Test 19}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB20}
+	\includegraphics[width=4in]{../Figures/Bars/BB20}
 	\caption{Burn Building Test 20}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/BB21}
+	\includegraphics[width=4in]{../Figures/Bars/BB21}
 	\caption{Burn Building Test 21}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES1}
+	\includegraphics[width=4in]{../Figures/Bars/ES1}
 	\caption{Experimental Structures Test 1}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES2}
+	\includegraphics[width=4in]{../Figures/Bars/ES2}
 	\caption{Experimental Structures Test 2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES3}
+	\includegraphics[width=4in]{../Figures/Bars/ES3}
 	\caption{Experimental Structures Test 3}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES4}
+	\includegraphics[width=4in]{../Figures/Bars/ES4}
 	\caption{Experimental Structures Test 4}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES5}
+	\includegraphics[width=4in]{../Figures/Bars/ES5}
 	\caption{Experimental Structures Test 5}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES6}
+	\includegraphics[width=4in]{../Figures/Bars/ES6}
 	\caption{Experimental Structures Test 6}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES7}
+	\includegraphics[width=4in]{../Figures/Bars/ES7}
 	\caption{Experimental Structures Test 7}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES72}
+	\includegraphics[width=4in]{../Figures/Bars/ES72}
 	\caption{Experimental Structures Test 7.2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES8}
+	\includegraphics[width=4in]{../Figures/Bars/ES8}
 	\caption{Experimental Structures Test 8}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES9}
+	\includegraphics[width=4in]{../Figures/Bars/ES9}
 	\caption{Experimental Structures Test 9}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES10}
+	\includegraphics[width=4in]{../Figures/Bars/ES10}
 	\caption{Experimental Structures Test 10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Bars/ES11}
+	\includegraphics[width=4in]{../Figures/Bars/ES11}
 	\caption{Experimental Structures Test 11}
@@
 
-\subsection{Spray Density}
-\label{subsec:Spray_Density}
-
 \chapter{Discussion and Tactical Considerations}
@@
 
-The National Institute of Standards and Technology, with the support of the Fire Protection Research
-Foundation, the U.S. Department of Homeland Security, and the U.S. Fire Administration conducted a
-series of fire experiments to examine the impact of wind on fire spread through a multi-room structure
-and examine the capabilities of wind-control devices (WCD) and externally applied water to mitigate the
-hazard. The measurements used to examine the impact of the WCDs and the external water application
-tactics were heat release rate, temperature, heat flux, and gas velocity inside the structure. Oxygen,
-carbon dioxide, carbon monoxide, total hydrocarbons and differential pressures were also measured.
-Each of the experiments was recorded with video and thermal imaging cameras. Some of these
-measurements are not practical or affordable to make in an acquired structure, hence the need to build a
-structure and conduct the experiments within the confines of the NIST Large Fire Facility. These 354
-experiments also provided visual documentation of fire phenomena that are not typically observable on
-the fire ground.
-A limited series of heat release rate experiments were conducted to characterize the fuel load packages
-used in wind driven structure experiments. Both the bedroom and the living room contained a fuel load
-composed of furnishings with an average peak heat release rate of 7.8 MW with a total heat release of at
-least 1700 MJ, not accounting for any of the wooden furniture or interior finish materials.
-The experiments were designed to expose a public corridor area to a wind driven, post-flashover
-apartment fire. The door from the apartment to the corridor was open for each of the experiments. The
-conditions in the corridor were of critical importance because that is the portion of the building that
-firefighters would use to approach the fire apartment or that occupants from an adjoining apartment
-would use to exit the building.
-The fires were ignited in the bedroom of the apartment. Prior to the failure or venting of the bedroom
-window, which was on the upwind side of the experimental apartment, the heat release rate from the fire
-was on the order of 1 MW. Prior to implementing either of the mitigating tactics, the heat release rates
-from the post-flashover structure fire were typically between 15 MW and 20 MW. When the door from
-the apartment to the corridor was open, temperatures in the corridor area near the open doorway, 1.52 m
-(5.00 ft) below the ceiling, were in excess of 600 °C (1112 °F) for each of the experiments. The heat
-fluxes measured in the same location, during the same experiments, were in excess of 70 kW/m². These
-extreme thermal conditions are not tenable, even for a firefighter in full protective gear. These
-conditions were attained within 30 s of the window failure.
-Experiment 1 was conducted without any external wind. This experiment provided valuable baseline
-data and demonstrated several important points relevant to fire fighting:
 Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of
@@
 conditions, both temperature and heat flux, which were twice as high in the “flow” portion of the
-corridor as opposed to the “static” portion of the corridor in Experiment 1. Thermal conditions in the
+corridor as opposed to the “static” portion of the corridor. Thermal conditions in the
 flow path were not consistent with firefighter survival.
-Experiments 2 through 8 all used a mechanically generated wind, ranging from 3 m/s to 9 m/s (7 mph to
-20 mph). 355
+
 The fuel load in the structure was the same for all of the experiments. Each of these experiments
-demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE,
-after the window failed.
-Experiments 2 through 5 focused on the impact of WCDS. In these experiments, the WCDs reduced
-the temperatures in the corridor outside the doorway by more than 50 % within 60 s of deployment. The
-heat fluxes were reduced by at least 70 % during this same time period. The WCDs also completely
-mitigated any gas velocity due to the external wind.
-Experiments 6 through 8 focused on the impact of externally applied water. In these experiments, the
-externally applied water streams were implemented in three different ways; a fog stream across the face
+demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE.
+
+The externally applied water streams were implemented in three different ways; a fog stream across the face
 of the window opening, a fog stream into the window opening, and a solid water stream into the window
-opening. The fog stream across the window was not effective at reducing the thermal conditions in the
-corridor. The fog stream in the window decreased the corridor temperature by at least 20 % and the
-corresponding heat flux measured by at least 30 %. The solid stream experiments resulted in corridor
-temperature and heat flux reductions of at least 40 % within 60 s of application. None of the water
-applications reduced the gas velocities in the structure. In some cases, the gas velocity increased during
-water application, due to momentum imparted from the water.
+opening.
+
 These experiments demonstrated the “extreme” thermal conditions that can be generated by a “simple
-room and contents” fire and how these conditions can be extended along a flow path within a structure
-when wind and an open vent are present. Two potential tactics which could be implemented from either
-the floor above the fire in the case of a WCD, or from the floor below the fire in the case of the external
-water application were demonstrated to be effective in reducing the thermal hazard in the corridor.
-However, these experimental results also indicate that the post deployment thermal conditions for any
-single tactic were still of a level which could pose a hazard to firefighters in full PPE.
+room and contents” fire and how these conditions can be extended along a flow path within a structure.
 The experiments also provided potential guidance for firefighters as a part of a fire size up and approach
@@
 in the flow path.
+
 Further research in actual buildings is required to fully understand the ability of firefighters to
@@
 positive pressure ventilation.
-If the demonstrated technologies continue to prove effective in the field trials and pilot programs, the
-next step may be to examine the need for standards and standardized test methods to define a minimum
-level of acceptable performance of these devices.
 

### 2015-06-05 Projects/DelCo_2012/Scripts/water_plot.py

@@ -15,7 +15,7 @@ rcParams.update({'figure.autolayout': True})
 data_dir = '../Experimental_Data/'
 
 # Skip files
-skip_files = ['_reduced', 'description_','zero','gcs','fse','cafs','fsw','_attic','sc']
+skip_files = ['cafs','fse_','fsw_','sc']
 
 for f in os.listdir(data_dir):
 	if f.endswith('.csv'):
@@ -27,7 +27,7 @@ for f in os.listdir(data_dir):
 		# Strip test name from file name
 		test_name = f[:-4]
 		print 'Test ' + test_name
-
+		
 		# Load exp. data file
 		data = pd.read_csv(data_dir + f, header=0, index_col=0)
 
@@ -77,4 +77,4 @@ for f in os.listdir(data_dir):
 		z_data = np.nan_to_num(water_mass.flatten())
 		ax.bar3d(x_data, y_data, np.zeros(len(z_data)), dx, dy, z_data,zsort='max')
 		savefig('../Figures/Bars/' + test_name + '.pdf')
-		close('all')
+		close('all')	

### 2015-06-25 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update to report

@@
 \hspace{1.5in} \= \\
-FDS \> Fire Dynamics Simulator \\
-HGL \> Hot Gas Layer \\
-HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
+ESTC \> Delaware County Emergency Services Training Center \\
+MCFRS \> Montgomery County (MD) Fire and Rescue Service \\
 NIST \> National Institute of Standards and Technology \\
+TFT \> Task Force Tips \\
 \end{tabbing}
@@
 
-\chapter{Abstract}
-\label{chap:Abstract}
-
-Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the “thermal balance,” and limit fire damage to structures.
+\chapter*{\centering Abstract}
+Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the ``thermal balance'', and limit fire damage to structures.
 In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations.
@@
 This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.
+\pagenumbering{gobble}
 
@@
 \label{chap:Introduction}
+ \pagenumbering{arabic}
+\setcounter{page}{1}
 
@@
 
-Three types of experiments were conducted;
-
-1)            spray density measures under non-fire conditions 
-2)            gas layer cooling 
-3)            fire suppression in an experimental structure
+Three types of experiments were conducted: 
+\begin{enumerate}
+\item spray density measures under non-fire conditions 
+\item gas layer cooling 
+\item fire suppression in experimental structures
+\end{enumerate}
 
 The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.
-The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies.
-[REF-  PROJECT ON “CAPABILITIES AND LIMITATIONS OF COMPRESSED AIR FOAM SYSTEMS (CAFS) FOR STRUCTURAL FIREFIGHTING” WORKSHOP SUMMARY, December, 13-14, 2011.
-Casey C.
-Grant, P.E., Fire Protection Research Foundation, One Batterymarch Park, Quincy, MA USA 02169-7471
-17 January 2012]
-
-Since Montgomery County (MD) Fire and Rescue Service provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
-Baseline operating conditions were agreed upon at the workshop for these experiments.
-
-*Nozzles – Metro 1, fixed gallonage fog/straight/7/8”solid stream  
-100 feet of hose line – 1-3/4”
-Foam concentration – 0.3%
-CAF Flowrate – 120 gpm / 60 cfm 
-Water / air pressure (100-120 psi)
-
-2.3. Study objective
-2.3.1. FF exposure – usability / safety
-2.3.1.1. Steam blowback
-2.3.1.2. Knockdown time
-2.3.1.3. Smoke scrubbing
-2.3.1.4. Rekindle time / prevention
-2.3.1.5. Overhaul / exposure time
-2.3.2. Other Issues
-2.3.2.1. Structural fire testing
-2.3.2.2. Room / attic configuration
-
+The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies~\cite{Grant:2011}.
+
+Since Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+Baseline operating conditions were agreed upon at the workshop for these experiments (Table~\ref{tab:op_condition}).
 These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
 
+\begin{table}[!ht]
+\centering
+\captionof{table}{Operating conditions for experiments}\label{tab:op_condition}
+\begin{tabular}{ll}
+\toprule[1.5pt]
+Equipment    &   Operating Condition \\
+\midrule
+Nozzle       & Metro 1, fixed gallonage fog,straight, or 7/8~inch solid stream \\
+Hoseline     & 100~ft of 1-3/4~inch hoseline \\
+Foam         & 0.3\% foam concentration \\
+Pressure     & Water and Air pressure of 100 - 120~psi \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
 \chapter{Experimental Setup}
-\label{chap:Experimental_Setup}
-
-\section{Experiment Descriptions}
-\label{sec:Experiment_Descriptions}
-
-The experimental set-up for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
-
-\subsection{Spray Density Measures}
-\label{sec:Spray_Density_Measures}
-
-Thirty two tests were conducted to determine spray density measures based on various nozzle patterns and locations.
-The purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+
+\section{Description of Experiments}
+\label{sec:desc_experiments}
+The experimental setup for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
+The nozzles chosen for these experiments were decided upon during the CAFS workshop~\cite{Grant:2011}: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120 gpm.
+These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application.
+The set-up also included 100~ft of 1-3/4~inch hose.
+Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
+The nozzles were controlled and operated via a gate valve from the exterior.
+
+\subsection{Spray Density}
+\label{sec:desc_Spray_Density}
+
+Thirty-two tests were conducted to determine spray density measures based on various nozzle patterns and locations.
 The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
-This set-up is representative of a firefighter operating on a hose line within the structure.
-Therefore, it is critical to ensure proper nozzle location for the tests to follow to provide the most realistic test conditions.
-
-The nozzles chosen for these experiments were as a result of those available through the MCFRS provided engine and decided upon during the CAFS workshop.
-This test series used Task Force Tips (TFT) Metro 1, Fixed Gallonage nozzles with a flow rate of 120 gpm.
-These are automatic nozzles which have a 7/8 inch slug-tip and can be varied from a straight stream to a wide fog for application.
-The set-up also included 100 ft of 1-3/4 inch hose.
-The nozzles were mounted to a "blitz-fire" monitor device and placed inside the structures.
-The nozzles were controlled and operated via a gate valve from the exterior.
-
-The tests conducted for spray density measurement were divided between the available structures at the Delaware County ESTC.
-Twenty one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests.
-The tests varied by changing the nozzle height and location within the structure.
-Additionally, the nozzle pattern was varied as well.
-A description and drawings of these facilities can be seen in the Experimental Facility section below.
+Therefore, the purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+
+Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests.
+The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (cf.
+Fig.~\ref{fig:Spray_Density_Nozzle_Patterns}).
+A description and drawings of these facilities are included in Section~\ref{sec:Experimental Structures}.
+Detailed discussion of the tests and results are in Section~\ref{sec:Spray_Density}.
 
@@
 
-The experiments were conducted by placing interlocking collector bins across the floor surface area of the burn rooms within each structure.
-Each collector bin was a 2.5 square foot poly box.
-The building was sheathed in plastic for the spray density tests in order to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
-The nozzles were flowed for a set duration and once the test was concluded, the bins were removed from the structure.
-The amount of water in each bin was measured in order to determine how much of the water ended up in each part of the room dependent on the nozzle location and pattern.
-The results can be seen in the sections to follow.
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
-	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
-	\label{fig:Spray_Density_Set_Up}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
+% 	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
+% 	\label{fig:Spray_Density_Set_Up}
+% \end{figure}
 
 \subsection{Gas Cooling}
-\label{sec:Gas_Cooling}
-
-The purpose built fire training structure was used for a total of eighty eight experiments studying the effectiveness of cooling the upper gas layer in an adjacent space to the area of fire involvement.
-The tests were conducted over a period of three days in late September of 2012 and split into a 8 different series.
-These tests examined five different hose stream patterns through two nozzle types for both compressed air foam and typical water suppression.
-The area of the purpose built structure used for these experiments was located on the ground floor and involved two adjoining rooms.
-The fire was ignited and allowed to grow and fill the compartment with heated fire products and flame.
-The developing hot gas layer spread to the adjacent room through a single doorway.
-The adjacent room developed a hot gas layer and was the focus of this series of tests.
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingSpray}
-	\caption{Nozzle Location for Gas Cooling Tests}
-	\label{fig:Nozzle_Location_Gas_Cooling_Tests}
-\end{figure}
+\label{sec:desc_Gas_Cooling}
+
+Eighty-eight experiments were conducted to study the effectiveness of cooling the upper gas layer in a space adjacent to the area of fire involvement.
+These tests examined five different hose stream patterns, two nozzle types, and both compressed air foam and water as the suppression agent.
+The focus of this experimental series was to study the impact of the test variables on interior conditions throughout the structure when suppression tactics were applied to a room adjacent to the fire room.
+Detailed discussion of the tests and results are in Section~\ref{sec:Gas_Cooling}.
 
 \subsection{Fire Suppression}
-\label{sec:Fire_Suppression}
-
-The fire suppression analysis included a series of 14 tests in two single story experimental structures, also located on the grounds of the Delaware County ESTC.
+\label{sec:desc_Fire_Suppression}
+
+The fire suppression series included 14 tests in two single-story experimental structures.
 Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.
+
 Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings.
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
-	\caption{Delaware County, PA Burn Building}
-	\label{fig:Delaware_County,_PA_Burn_Building}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
+% 	\caption{Delaware County, PA Burn Building}
+% 	\label{fig:Delaware_County,_PA_Burn_Building}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
-	\caption{Instrumentation Legend}
-	\label{fig:Instrumentation_Legend}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
+% 	\caption{Instrumentation Legend}
+% 	\label{fig:Instrumentation_Legend}
+% \end{figure}
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Single_Story_Instrumentation}
+	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentation}
 	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
-	\caption{Pallet Fuel Load}
-	\label{fig:Pallet_Fuel_Load}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
+% 	\caption{Pallet Fuel Load}
+% 	\label{fig:Pallet_Fuel_Load}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
-	\caption{Sleeper Sofa}
-	\label{fig:Sleeper_Sofa}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
-	\caption{Mattress}
-	\label{fig:Mattress}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
-	\caption{Blue Chair}
-	\label{fig:Blue_Chair}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
+% 	\caption{Sleeper Sofa}
+% 	\label{fig:Sleeper_Sofa}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
+% 	\caption{Mattress}
+% 	\label{fig:Mattress}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
+% 	\caption{Blue Chair}
+% 	\label{fig:Blue_Chair}
+% \end{figure}
 
@@
 
-\begin{sidewaystable}[!ht]
-	\centering
-	\caption{Temperature Comparison}
-	\begin{tabular}{ll}
-		\hline\noalign{\smallskip}
-		Temperature				 & Response		\\
-		\noalign{\smallskip}\hline\noalign{\smallskip}
-		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
-		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
-		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
-		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
-		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
-		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
-		100 deg C (212 deg F)    & Water boils and produces steam    \\
-		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
-		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
-		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
-		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
-		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
-		\noalign{\smallskip}\hline
-	\end{tabular}
-	\label{tab:Temperature_Comparison}
-\end{sidewaystable}
-
-\begin{sidewaystable}[!ht]
-	\centering
-	\caption{Heat Flux Comparison}
-	\begin{tabular}{ll}
-		\hline\noalign{\smallskip}
-		Heat Flux	  				   & Response		\\
-		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 kW/m\textsuperscript{2}      & Sunny day      \\
-		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
-		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
-		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
-		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
-		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
-		\noalign{\smallskip}\hline
-	\end{tabular}
-	\label{tab:Heat_Flux_Comparison}
-\end{sidewaystable}
-
-\subsection{Spray Density}
-\label{subsec:Spray_Density}
+% \begin{sidewaystable}[!ht]
+% 	\centering
+% 	\caption{Temperature Comparison}
+% 	\begin{tabular}{ll}
+% 		\hline\noalign{\smallskip}
+% 		Temperature				 & Response		\\
+% 		\noalign{\smallskip}\hline\noalign{\smallskip}
+% 		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
+% 		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
+% 		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
+% 		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
+% 		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
+% 		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
+% 		100 deg C (212 deg F)    & Water boils and produces steam    \\
+% 		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
+% 		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
+% 		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
+% 		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
+% 		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
+% 		\noalign{\smallskip}\hline
+% 	\end{tabular}
+% 	\label{tab:Temperature_Comparison}
+% \end{sidewaystable}
+
+% \begin{sidewaystable}[!ht]
+% 	\centering
+% 	\caption{Heat Flux Comparison}
+% 	\begin{tabular}{ll}
+% 		\hline\noalign{\smallskip}
+% 		Heat Flux	  				   & Response		\\
+% 		\noalign{\smallskip}\hline\noalign{\smallskip}
+% 		1 kW/m\textsuperscript{2}      & Sunny day      \\
+% 		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
+% 		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
+% 		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
+% 		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
+% 		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
+% 		\noalign{\smallskip}\hline
+% 	\end{tabular}
+% 	\label{tab:Heat_Flux_Comparison}
+% \end{sidewaystable}
+
+\section{Spray Density}
+\label{sec:Spray_Density}
+
+The experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure.
+The building was sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
+Water flowed for a specified duration and upon completion the bins were removed from the structure.
+Each bin was then weighed to quantify the impact of nozzle location and spray pattern.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES1}
+	\includegraphics[width=4in]{../Figures/Bars/ES_1}
 	\caption{Experimental Structures Test 1}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES2}
+	\includegraphics[width=4in]{../Figures/Bars/ES_2}
 	\caption{Experimental Structures Test 2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES3}
+	\includegraphics[width=4in]{../Figures/Bars/ES_3}
 	\caption{Experimental Structures Test 3}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES4}
+	\includegraphics[width=4in]{../Figures/Bars/ES_4}
 	\caption{Experimental Structures Test 4}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES5}
+	\includegraphics[width=4in]{../Figures/Bars/ES_5}
 	\caption{Experimental Structures Test 5}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES6}
+	\includegraphics[width=4in]{../Figures/Bars/ES_6}
 	\caption{Experimental Structures Test 6}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES7}
+	\includegraphics[width=4in]{../Figures/Bars/ES_7}
 	\caption{Experimental Structures Test 7}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES72}
+	\includegraphics[width=4in]{../Figures/Bars/ES_72}
 	\caption{Experimental Structures Test 7.2}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES8}
+	\includegraphics[width=4in]{../Figures/Bars/ES_8}
 	\caption{Experimental Structures Test 8}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES9}
+	\includegraphics[width=4in]{../Figures/Bars/ES_9}
 	\caption{Experimental Structures Test 9}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES10}
+	\includegraphics[width=4in]{../Figures/Bars/ES_10}
 	\caption{Experimental Structures Test 10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES11}
+	\includegraphics[width=4in]{../Figures/Bars/ES_11}
 	\caption{Experimental Structures Test 11}
@@
 
-\chapter{Appendix}
-\label{chap:Appendix}
-
-\section{Test 1 Figures}
-\label{subsec:Test_1_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
-	\caption{Test 1 (FSE1): Eastside Array}
-	\label{fig:Test_1_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
-	\caption{Test 1 (FSE1): Westside Array}
-	\label{fig:Test_1_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
-	\caption{Test 1 (FSE1): Hallway Array}
-	\label{fig:Test_1_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
-	\caption{Test 1 (FSE1): Doorway Array}
-	\label{fig:Test_1_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
-	\caption{Test 1 (FSE1): Suppression Eastside Array}
-	\label{fig:Test_1_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
-	\caption{Test 1 (FSE1): Suppression Westside Array}
-	\label{fig:Test_1_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
-	\caption{Test 1 (FSE1): Suppression Hallway Array}
-	\label{fig:Test_1_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
-	\caption{Test 1 (FSE1): Suppression Doorway Array}
-	\label{fig:Test_1_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
-	\caption{Test 1 (FSE1): Eastside Heat Flux}
-	\label{fig:Test_1_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
-	\caption{Test 1 (FSE1): Westside Heat Flux}
-	\label{fig:Test_1_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
-	\caption{Test 1 (FSE1): Hallway Heat Flux}
-	\label{fig:Test_1_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
-	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
-	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
-	\caption{Test 1 (FSE1): Hallway Velocity}
-	\label{fig:Test_1_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
-	\caption{Test 1 (FSE1): Doorway Velocity}
-	\label{fig:Test_1_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 2 Figures}
-\label{subsec:Test_2_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
-	\caption{Test 2 (FSW2): Eastside Array}
-	\label{fig:Test_2_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
-	\caption{Test 2 (FSW2: Westside Array}
-	\label{fig:Test_2_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
-	\caption{Test 2 (FSW2): Hallway Array}
-	\label{fig:Test_2_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
-	\caption{Test 2 (FSW2): Doorway Array}
-	\label{fig:Test_2_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
-	\caption{Test 2 (FSW2): Suppression Eastside Array}
-	\label{fig:Test_2_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
-	\caption{Test 2 (FSW2): Suppression Westside Array}
-	\label{fig:Test_2_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
-	\caption{Test 2 (FSW2): Suppression Hallway Array}
-	\label{fig:Test_2_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
-	\caption{Test 2 (FSW2): Suppression Doorway Array}
-	\label{fig:Test_2_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
-	\caption{Test 2 (FSW2): Eastside Heat Flux}
-	\label{fig:Test_2_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
-	\caption{Test 2 (FSW2): Westside Heat Flux}
-	\label{fig:Test_2_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
-	\caption{Test 2 (FSW2): Hallway Heat Flux}
-	\label{fig:Test_2_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
-	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
-	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
-	\caption{Test 2 (FSW2): Hallway Velocity}
-	\label{fig:Test_2_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
-	\caption{Test 2 (FSW2): Doorway Velocity}
-	\label{fig:Test_2_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 3 Figures}
-\label{subsec:Test_3_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
-	\caption{Test 3 (FSW3): Eastside Array}
-	\label{fig:Test_3_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
-	\caption{Test 3 (FSW3: Westside Array}
-	\label{fig:Test_3_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
-	\caption{Test 3 (FSW3): Hallway Array}
-	\label{fig:Test_3_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
-	\caption{Test 3 (FSW3): Doorway Array}
-	\label{fig:Test_3_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
-	\caption{Test 3 (FSW3): Suppression Eastside Array}
-	\label{fig:Test_3_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
-	\caption{Test 3 (FSW3): Suppression Westside Array}
-	\label{fig:Test_3_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
-	\caption{Test 3 (FSW3): Suppression Hallway Array}
-	\label{fig:Test_3_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
-	\caption{Test 3 (FSW3): Suppression Doorway Array}
-	\label{fig:Test_3_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
-	\caption{Test 3 (FSW3): Eastside Heat Flux}
-	\label{fig:Test_3_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
-	\caption{Test 3 (FSW3): Westside Heat Flux}
-	\label{fig:Test_3_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
-	\caption{Test 3 (FSW3): Hallway Heat Flux}
-	\label{fig:Test_3_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
-	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
-	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
-	\caption{Test 3 (FSW3): Hallway Velocity}
-	\label{fig:Test_3_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
-	\caption{Test 3 (FSW3): Doorway Velocity}
-	\label{fig:Test_3_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 4 Figures}
-\label{subsec:Test_4_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
-	\caption{Test 4 (FSE4): Eastside Array}
-	\label{fig:Test_4_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
-	\caption{Test 4 (FSE4): Westside Array}
-	\label{fig:Test_4_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
-	\caption{Test 4 (FSE4): Hallway Array}
-	\label{fig:Test_4_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
-	\caption{Test 4 (FSE4): Doorway Array}
-	\label{fig:Test_4_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
-	\caption{Test 4 (FSE4): Suppression Eastside Array}
-	\label{fig:Test_4_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
-	\caption{Test 4 (FSE4): Suppression Westside Array}
-	\label{fig:Test_4_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
-	\caption{Test 4 (FSE4): Suppression Hallway Array}
-	\label{fig:Test_4_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
-	\caption{Test 4 (FSE4): Suppression Doorway Array}
-	\label{fig:Test_4_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
-	\caption{Test 4 (FSE4): Eastside Heat Flux}
-	\label{fig:Test_4_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
-	\caption{Test 4 (FSE4): Westside Heat Flux}
-	\label{fig:Test_4_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
-	\caption{Test 4 (FSE4): Hallway Heat Flux}
-	\label{fig:Test_4_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
-	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
-	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
-	\caption{Test 4 (FSE4): Hallway Velocity}
-	\label{fig:Test_4_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
-	\caption{Test 4 (FSE4): Doorway Velocity}
-	\label{fig:Test_4_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 5 Figures}
-\label{subsec:Test_5_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
-	\caption{Test 5 (FSE5): Eastside Array}
-	\label{fig:Test_5_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
-	\caption{Test 5 (FSE5): Westside Array}
-	\label{fig:Test_5_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
-	\caption{Test 5 (FSE5): Hallway Array}
-	\label{fig:Test_5_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
-	\caption{Test 5 (FSE5): Doorway Array}
-	\label{fig:Test_5_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
-	\caption{Test 5 (FSE5): Suppression Eastside Array}
-	\label{fig:Test_5_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
-	\caption{Test 5 (FSE5): Suppression Westside Array}
-	\label{fig:Test_5_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
-	\caption{Test 5 (FSE5): Suppression Hallway Array}
-	\label{fig:Test_5_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
-	\caption{Test 5 (FSE5): Suppression Doorway Array}
-	\label{fig:Test_5_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
-	\caption{Test 5 (FSE5): Eastside Heat Flux}
-	\label{fig:Test_5_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
-	\caption{Test 5 (FSE5): Westside Heat Flux}
-	\label{fig:Test_5_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
-	\caption{Test 5 (FSE5): Hallway Heat Flux}
-	\label{fig:Test_5_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
-	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
-	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
-	\caption{Test 5 (FSE5): Hallway Velocity}
-	\label{fig:Test_5_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
-	\caption{Test 5 (FSE5): Doorway Velocity}
-	\label{fig:Test_5_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 6 Figures}
-\label{subsec:Test_6_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
-	\caption{Test 6 (FSW6): Eastside Array}
-	\label{fig:Test_6_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
-	\caption{Test 6 (FSW6: Westside Array}
-	\label{fig:Test_6_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
-	\caption{Test 6 (FSW6): Hallway Array}
-	\label{fig:Test_6_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
-	\caption{Test 6 (FSW6): Doorway Array}
-	\label{fig:Test_6_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
-	\caption{Test 6 (FSW6): Suppression Eastside Array}
-	\label{fig:Test_6_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
-	\caption{Test 6 (FSW6): Suppression Westside Array}
-	\label{fig:Test_6_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
-	\caption{Test 6 (FSW6): Suppression Hallway Array}
-	\label{fig:Test_6_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
-	\caption{Test 6 (FSW6): Suppression Doorway Array}
-	\label{fig:Test_6_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
-	\caption{Test 6 (FSW6): Eastside Heat Flux}
-	\label{fig:Test_6_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
-	\caption{Test 6 (FSW6): Westside Heat Flux}
-	\label{fig:Test_6_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
-	\caption{Test 6 (FSW6): Hallway Heat Flux}
-	\label{fig:Test_6_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
-	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
-	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
-	\caption{Test 6 (FSW6): Hallway Velocity}
-	\label{fig:Test_6_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
-	\caption{Test 6 (FSW6): Doorway Velocity}
-	\label{fig:Test_6_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 7 Figures}
-\label{subsec:Test_7_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
-	\caption{Test 7 (FSW7): Eastside Array}
-	\label{fig:Test_7_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
-	\caption{Test 7 (FSW7: Westside Array}
-	\label{fig:Test_7_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
-	\caption{Test 7 (FSW7): Hallway Array}
-	\label{fig:Test_7_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
-	\caption{Test 7 (FSW7): Doorway Array}
-	\label{fig:Test_7_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
-	\caption{Test 7 (FSW7): Suppression Eastside Array}
-	\label{fig:Test_7_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
-	\caption{Test 7 (FSW7): Suppression Westside Array}
-	\label{fig:Test_7_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
-	\caption{Test 7 (FSW7): Suppression Hallway Array}
-	\label{fig:Test_7_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
-	\caption{Test 7 (FSW7): Suppression Doorway Array}
-	\label{fig:Test_7_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
-	\caption{Test 7 (FSW7): Eastside Heat Flux}
-	\label{fig:Test_7_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
-	\caption{Test 7 (FSW7): Westside Heat Flux}
-	\label{fig:Test_7_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
-	\caption{Test 7 (FSW7): Hallway Heat Flux}
-	\label{fig:Test_7_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
-	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
-	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
-	\caption{Test 7 (FSW7): Hallway Velocity}
-	\label{fig:Test_7_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
-	\caption{Test 7 (FSW7): Doorway Velocity}
-	\label{fig:Test_7_Doorway_Velocity}
-\end{figure}
-
-\clearpage
-
-\section{Test 8 Figures}
-\label{subsec:Test_8_Figures}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
-	\caption{Test 8 (FSE8): Eastside Array}
-	\label{fig:Test_8_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
-	\caption{Test 8 (FSE8): Westside Array}
-	\label{fig:Test_8_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
-	\caption{Test 8 (FSE8): Hallway Array}
-	\label{fig:Test_8_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
-	\caption{Test 8 (FSE8): Doorway Array}
-	\label{fig:Test_8_Doorway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
-	\caption{Test 8 (FSE8): Suppression Eastside Array}
-	\label{fig:Test_8_Suppression_Eastside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
-	\caption{Test 8 (FSE8): Suppression Westside Array}
-	\label{fig:Test_8_Suppression_Westside_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
-	\caption{Test 8 (FSE8): Suppression Hallway Array}
-	\label{fig:Test_8_Suppression_Hallway_Array}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
-	\caption{Test 8 (FSE8): Suppression Doorway Array}
-	\label{fig:Test_8_Suppression_Doorway_Array}
-\end{figure}
-
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
-	\caption{Test 8 (FSE8): Eastside Heat Flux}
-	\label{fig:Test_8_Eastside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
-	\caption{Test 8 (FSE8): Westside Heat Flux}
-	\label{fig:Test_8_Westside_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
-	\caption{Test 8 (FSE8): Hallway Heat Flux}
-	\label{fig:Test_8_Hallway_Heat_Flux}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
-	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
-	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
-\end{figure}
-
-\subsection{Velocity}
-\label{subsec:Velocity}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
-	\caption{Test 8 (FSE8): Hallway Velocity}
-	\label{fig:Test_8_Hallway_Velocity}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
-	\caption{Test 8 (FSE8): Doorway Velocity}
-	\label{fig:Test_8_Doorway_Velocity}
-\end{figure}
+% \chapter{Appendix}
+% \label{chap:Appendix}
+
+% \section{Test 1 Figures}
+% \label{subsec:Test_1_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
+% 	\caption{Test 1 (FSE1): Eastside Array}
+% 	\label{fig:Test_1_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
+% 	\caption{Test 1 (FSE1): Westside Array}
+% 	\label{fig:Test_1_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
+% 	\caption{Test 1 (FSE1): Hallway Array}
+% 	\label{fig:Test_1_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
+% 	\caption{Test 1 (FSE1): Doorway Array}
+% 	\label{fig:Test_1_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
+% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
+% 	\label{fig:Test_1_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
+% 	\caption{Test 1 (FSE1): Suppression Westside Array}
+% 	\label{fig:Test_1_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
+% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
+% 	\label{fig:Test_1_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
+% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
+% 	\label{fig:Test_1_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
+% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
+% 	\label{fig:Test_1_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
+% 	\caption{Test 1 (FSE1): Westside Heat Flux}
+% 	\label{fig:Test_1_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
+% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
+% 	\label{fig:Test_1_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
+% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
+% 	\caption{Test 1 (FSE1): Hallway Velocity}
+% 	\label{fig:Test_1_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
+% 	\caption{Test 1 (FSE1): Doorway Velocity}
+% 	\label{fig:Test_1_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 2 Figures}
+% \label{subsec:Test_2_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
+% 	\caption{Test 2 (FSW2): Eastside Array}
+% 	\label{fig:Test_2_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
+% 	\caption{Test 2 (FSW2: Westside Array}
+% 	\label{fig:Test_2_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
+% 	\caption{Test 2 (FSW2): Hallway Array}
+% 	\label{fig:Test_2_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
+% 	\caption{Test 2 (FSW2): Doorway Array}
+% 	\label{fig:Test_2_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
+% 	\caption{Test 2 (FSW2): Suppression Eastside Array}
+% 	\label{fig:Test_2_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
+% 	\caption{Test 2 (FSW2): Suppression Westside Array}
+% 	\label{fig:Test_2_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
+% 	\caption{Test 2 (FSW2): Suppression Hallway Array}
+% 	\label{fig:Test_2_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
+% 	\caption{Test 2 (FSW2): Suppression Doorway Array}
+% 	\label{fig:Test_2_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
+% 	\caption{Test 2 (FSW2): Eastside Heat Flux}
+% 	\label{fig:Test_2_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
+% 	\caption{Test 2 (FSW2): Westside Heat Flux}
+% 	\label{fig:Test_2_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
+% 	\caption{Test 2 (FSW2): Hallway Heat Flux}
+% 	\label{fig:Test_2_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
+% 	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
+% 	\caption{Test 2 (FSW2): Hallway Velocity}
+% 	\label{fig:Test_2_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
+% 	\caption{Test 2 (FSW2): Doorway Velocity}
+% 	\label{fig:Test_2_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 3 Figures}
+% \label{subsec:Test_3_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
+% 	\caption{Test 3 (FSW3): Eastside Array}
+% 	\label{fig:Test_3_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
+% 	\caption{Test 3 (FSW3: Westside Array}
+% 	\label{fig:Test_3_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
+% 	\caption{Test 3 (FSW3): Hallway Array}
+% 	\label{fig:Test_3_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
+% 	\caption{Test 3 (FSW3): Doorway Array}
+% 	\label{fig:Test_3_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
+% 	\caption{Test 3 (FSW3): Suppression Eastside Array}
+% 	\label{fig:Test_3_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
+% 	\caption{Test 3 (FSW3): Suppression Westside Array}
+% 	\label{fig:Test_3_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
+% 	\caption{Test 3 (FSW3): Suppression Hallway Array}
+% 	\label{fig:Test_3_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
+% 	\caption{Test 3 (FSW3): Suppression Doorway Array}
+% 	\label{fig:Test_3_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
+% 	\caption{Test 3 (FSW3): Eastside Heat Flux}
+% 	\label{fig:Test_3_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
+% 	\caption{Test 3 (FSW3): Westside Heat Flux}
+% 	\label{fig:Test_3_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
+% 	\caption{Test 3 (FSW3): Hallway Heat Flux}
+% 	\label{fig:Test_3_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
+% 	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
+% 	\caption{Test 3 (FSW3): Hallway Velocity}
+% 	\label{fig:Test_3_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
+% 	\caption{Test 3 (FSW3): Doorway Velocity}
+% 	\label{fig:Test_3_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 4 Figures}
+% \label{subsec:Test_4_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
+% 	\caption{Test 4 (FSE4): Eastside Array}
+% 	\label{fig:Test_4_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
+% 	\caption{Test 4 (FSE4): Westside Array}
+% 	\label{fig:Test_4_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
+% 	\caption{Test 4 (FSE4): Hallway Array}
+% 	\label{fig:Test_4_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
+% 	\caption{Test 4 (FSE4): Doorway Array}
+% 	\label{fig:Test_4_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
+% 	\caption{Test 4 (FSE4): Suppression Eastside Array}
+% 	\label{fig:Test_4_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
+% 	\caption{Test 4 (FSE4): Suppression Westside Array}
+% 	\label{fig:Test_4_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
+% 	\caption{Test 4 (FSE4): Suppression Hallway Array}
+% 	\label{fig:Test_4_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
+% 	\caption{Test 4 (FSE4): Suppression Doorway Array}
+% 	\label{fig:Test_4_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
+% 	\caption{Test 4 (FSE4): Eastside Heat Flux}
+% 	\label{fig:Test_4_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
+% 	\caption{Test 4 (FSE4): Westside Heat Flux}
+% 	\label{fig:Test_4_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
+% 	\caption{Test 4 (FSE4): Hallway Heat Flux}
+% 	\label{fig:Test_4_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
+% 	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
+% 	\caption{Test 4 (FSE4): Hallway Velocity}
+% 	\label{fig:Test_4_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
+% 	\caption{Test 4 (FSE4): Doorway Velocity}
+% 	\label{fig:Test_4_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 5 Figures}
+% \label{subsec:Test_5_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
+% 	\caption{Test 5 (FSE5): Eastside Array}
+% 	\label{fig:Test_5_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
+% 	\caption{Test 5 (FSE5): Westside Array}
+% 	\label{fig:Test_5_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
+% 	\caption{Test 5 (FSE5): Hallway Array}
+% 	\label{fig:Test_5_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
+% 	\caption{Test 5 (FSE5): Doorway Array}
+% 	\label{fig:Test_5_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
+% 	\caption{Test 5 (FSE5): Suppression Eastside Array}
+% 	\label{fig:Test_5_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
+% 	\caption{Test 5 (FSE5): Suppression Westside Array}
+% 	\label{fig:Test_5_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
+% 	\caption{Test 5 (FSE5): Suppression Hallway Array}
+% 	\label{fig:Test_5_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
+% 	\caption{Test 5 (FSE5): Suppression Doorway Array}
+% 	\label{fig:Test_5_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
+% 	\caption{Test 5 (FSE5): Eastside Heat Flux}
+% 	\label{fig:Test_5_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
+% 	\caption{Test 5 (FSE5): Westside Heat Flux}
+% 	\label{fig:Test_5_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
+% 	\caption{Test 5 (FSE5): Hallway Heat Flux}
+% 	\label{fig:Test_5_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
+% 	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
+% 	\caption{Test 5 (FSE5): Hallway Velocity}
+% 	\label{fig:Test_5_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
+% 	\caption{Test 5 (FSE5): Doorway Velocity}
+% 	\label{fig:Test_5_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 6 Figures}
+% \label{subsec:Test_6_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
+% 	\caption{Test 6 (FSW6): Eastside Array}
+% 	\label{fig:Test_6_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
+% 	\caption{Test 6 (FSW6: Westside Array}
+% 	\label{fig:Test_6_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
+% 	\caption{Test 6 (FSW6): Hallway Array}
+% 	\label{fig:Test_6_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
+% 	\caption{Test 6 (FSW6): Doorway Array}
+% 	\label{fig:Test_6_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
+% 	\caption{Test 6 (FSW6): Suppression Eastside Array}
+% 	\label{fig:Test_6_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
+% 	\caption{Test 6 (FSW6): Suppression Westside Array}
+% 	\label{fig:Test_6_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
+% 	\caption{Test 6 (FSW6): Suppression Hallway Array}
+% 	\label{fig:Test_6_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
+% 	\caption{Test 6 (FSW6): Suppression Doorway Array}
+% 	\label{fig:Test_6_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
+% 	\caption{Test 6 (FSW6): Eastside Heat Flux}
+% 	\label{fig:Test_6_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
+% 	\caption{Test 6 (FSW6): Westside Heat Flux}
+% 	\label{fig:Test_6_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
+% 	\caption{Test 6 (FSW6): Hallway Heat Flux}
+% 	\label{fig:Test_6_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
+% 	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
+% 	\caption{Test 6 (FSW6): Hallway Velocity}
+% 	\label{fig:Test_6_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
+% 	\caption{Test 6 (FSW6): Doorway Velocity}
+% 	\label{fig:Test_6_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 7 Figures}
+% \label{subsec:Test_7_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
+% 	\caption{Test 7 (FSW7): Eastside Array}
+% 	\label{fig:Test_7_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
+% 	\caption{Test 7 (FSW7: Westside Array}
+% 	\label{fig:Test_7_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
+% 	\caption{Test 7 (FSW7): Hallway Array}
+% 	\label{fig:Test_7_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
+% 	\caption{Test 7 (FSW7): Doorway Array}
+% 	\label{fig:Test_7_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
+% 	\caption{Test 7 (FSW7): Suppression Eastside Array}
+% 	\label{fig:Test_7_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
+% 	\caption{Test 7 (FSW7): Suppression Westside Array}
+% 	\label{fig:Test_7_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
+% 	\caption{Test 7 (FSW7): Suppression Hallway Array}
+% 	\label{fig:Test_7_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
+% 	\caption{Test 7 (FSW7): Suppression Doorway Array}
+% 	\label{fig:Test_7_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
+% 	\caption{Test 7 (FSW7): Eastside Heat Flux}
+% 	\label{fig:Test_7_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
+% 	\caption{Test 7 (FSW7): Westside Heat Flux}
+% 	\label{fig:Test_7_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
+% 	\caption{Test 7 (FSW7): Hallway Heat Flux}
+% 	\label{fig:Test_7_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
+% 	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
+% 	\caption{Test 7 (FSW7): Hallway Velocity}
+% 	\label{fig:Test_7_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
+% 	\caption{Test 7 (FSW7): Doorway Velocity}
+% 	\label{fig:Test_7_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 8 Figures}
+% \label{subsec:Test_8_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
+% 	\caption{Test 8 (FSE8): Eastside Array}
+% 	\label{fig:Test_8_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
+% 	\caption{Test 8 (FSE8): Westside Array}
+% 	\label{fig:Test_8_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
+% 	\caption{Test 8 (FSE8): Hallway Array}
+% 	\label{fig:Test_8_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
+% 	\caption{Test 8 (FSE8): Doorway Array}
+% 	\label{fig:Test_8_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
+% 	\caption{Test 8 (FSE8): Suppression Eastside Array}
+% 	\label{fig:Test_8_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
+% 	\caption{Test 8 (FSE8): Suppression Westside Array}
+% 	\label{fig:Test_8_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
+% 	\caption{Test 8 (FSE8): Suppression Hallway Array}
+% 	\label{fig:Test_8_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
+% 	\caption{Test 8 (FSE8): Suppression Doorway Array}
+% 	\label{fig:Test_8_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
+% 	\caption{Test 8 (FSE8): Eastside Heat Flux}
+% 	\label{fig:Test_8_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
+% 	\caption{Test 8 (FSE8): Westside Heat Flux}
+% 	\label{fig:Test_8_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
+% 	\caption{Test 8 (FSE8): Hallway Heat Flux}
+% 	\label{fig:Test_8_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
+% 	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
+% 	\caption{Test 8 (FSE8): Hallway Velocity}
+% 	\label{fig:Test_8_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
+% 	\caption{Test 8 (FSE8): Doorway Velocity}
+% 	\label{fig:Test_8_Doorway_Velocity}
+% \end{figure}
 

### 2015-06-26 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Removed unnecessary drawing files and finished folder organization

--- 2015-03-26 Projects/DelCo_2014/Report/Hose_Tests/DelCo_Hose_Tests_2014.tex
@@
 
-\input{../../../../Bibliography/commoncommands}
+\input{../../../../../Bibliography/commoncommands}
 
@@
 \flushright{
-\includegraphics[width=2.in]{../../../../Bibliography/nistident_flright_vec} \\[.3in]
+\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
 }
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/hose_streams.pdf}
-\caption[Different Hose Stream Patterns]{The three types of hose stream patterns, straight stream (left), narrow fog stream (middle), and wide fog stream (right), used during the water flow experiments.}
+\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
+\caption[Different Hose Stream Patterns]{The three types of hose stream patterns used during the water flow experiments from left to right: straight stream, narrow fog stream, and wide fog stream.}
 \label{fig:hose_streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/east_structure}
+\includegraphics[width=6in]{../Pictures/east_structure}
 \\~\\
-\includegraphics[width=6in]{../../Figures/west_structure}
+\includegraphics[width=6in]{../Pictures/west_structure}
 \caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
 \label{fig:struct_pics}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
+\caption[East Structure floor layout]{East Structure floor layout. All dimensions are in meters.}
+\label{fig:east_general_plan}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_1st_Floor_Metric_Simple}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
 \\
-\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_2nd_Floor_Metric_Simple}
+\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
 \caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
+\includegraphics[trim=0cm 0cm 0.25cm 3.75cm, clip=true, width=6in]{../Drawings/Instrumentation/East_Structure_Devices_Hose_Test}
+\caption[Location of Instrumentation in East Structure]{Location of instrumentation in East Structure}
+\label{fig:east_instrumentation}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
 \\
-\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
-\caption[Location of Instrumentation in West Structure]{Location of Instrumentation in West Structure}
+\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
+\caption[Location of Instrumentation in West Structure]{Location of instrumentation in West Structure}
 \label{fig:west_instrumentation}
@@
 
+\clearpage
+
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/BDPs}
+\includegraphics[width=6in]{../Pictures/BDPs}
 \caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
@@
 
-Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor with a combination nozzle.
+Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor equipped with a combination nozzle.
 A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30.
 Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}).
-After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped.
+After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped.
 The monitor was adjusted so the nozzle was aimed at Door BC.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_1st_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
 \\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_18_2nd_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
 \caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_1st_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
 \\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../../Drawings/PDFs/Without_Instrumentation/West_Structure_Hose_Test_19_2nd_Floor}
+\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
 \caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Test_18}
+\includegraphics[width=6in]{../Pictures/Test_18}
 \caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
 \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
 \caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
 \caption{Average Velocity through Stairwell Door, Test 17, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
 \caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
@@
 0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
+\end{tabular}
+\label{table:Tests_16_17_BDP_A10_Avgs}
+\end{table}
+
+\begin{table}[!ht]
+\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
+\\
+\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
+\midrule
+\textit{Straight} & 
+%%%%Test 16%%%% 
+0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
+%%%%Test 17%%%% 
+0.7 $\pm 0.1$ & 0.7 $\pm 0.2$
+\\	\multicolumn{5}{c}{}	\\
+\textit{Narrow Fog} & 
+%%%%Test 16%%%% 
+1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
+%%%%Test 17%%%% 
+0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $          
+\\	\multicolumn{5}{c}{}	\\
+\textit{Wide Fog} 	& 
+%%%%Test 16%%%% 
+1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
+%%%%Test 17%%%% 
+0.9 $\pm 0.2$ & 0.7 $\pm 0.2$
+\\
+\bottomrule
 \end{tabular}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
 \caption{Average Velocity through Stairwell Door, Test 18, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
 \caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
 \caption{Average Velocity through Stairwell Door, Test 19, All Streams}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
 \caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}

### 2015-06-26 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update to report and figures

@@
 Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.
-
-Additionally, two tests were conducted, one in each structure, on suppression tactics for attic fires in residential dwellings.
-The nozzle patterns were varied from straight stream to narrow fog, and in the case of the two attic tests, a smooth bore nozzle was used.
-Several other factors including the fuel load and available ventilation were varied during these tests.
-
-Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.
-The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.
-The fires were intended to replicate room and contents fires typically seen within residential structures.
-The hose lines were pre-deployed with fixed nozzles set in two locations.
-One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle).
-The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
-Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack.
-The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.
-This position represented a direct interior attack.
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
-	\caption{Hallway Nozzle Location for Fire Suppression Tests}
-	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
-	\caption{Room Nozzle Location for Fire Suppression Tests}
-	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
-\end{figure}
-
-Due to the limited time and resources for testing, the extremes were chosen: smooth bore and narrow fog.
-
-Straight stream from a fog nozzle was the medium between the two.
+The nozzle patterns were varied from straight stream to narrow fog.
+Two additional tests were conduction on suppression tactics for attic fires in residential dwellings, one in each structure.
+For these tests, a smooth bore nozzle was used.
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
+% 	\caption{Hallway Nozzle Location for Fire Suppression Tests}
+% 	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
+% 	\caption{Room Nozzle Location for Fire Suppression Tests}
+% 	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
+% \end{figure}
 
@@
 
-\subsection{Purpose Built Fire Training Structure - Gas Cooling}
+\subsection{Fire Training Structure - Gas Cooling}
 \label{sec:Burn_Building}
 
-The burn building is a purpose-built live fire training structure comprised of both a two story and three story section.
+The burn building is a live fire training structure with both a two story and three story section.
 The building is supported with reinforced concrete beams and columns.
 The floors and ceilings are also concrete with the interior walls constructed of cement block.
-The walls and ceiling of the burn rooms within the structure are protected with a 25 mm thick layer of calcium silicate insulation, which is covered by a 50 mm thick concrete tile.
+The walls and ceiling of the burn rooms are protected with a 25~mm thick layer of calcium silicate insulation and is covered by a 50~mm thick concrete tile.
 The floor of the burn rooms is protected with fire brick.
+Tests were conducted in the two-story, two-room configuration which has overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (cf.
+Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
 
@@
 
-The two room configuration within the burn building had overall dimensions of 6.5 m (21.3 ft) by 9.2 m (30.2 ft).
-The burn room where the fuel load was located measured 3.8 m (12.5 ft) by 5.7 m (18.7 ft) with a ceiling height of 3.35 m (11.0 ft).
-The adjacent room where the water was applied for gas cooling measured 4.1 m (13.4 ft) by 5.7 m (18.7 ft), also with a ceiling height of 3.35 m (11.0 ft).
-The open door from the adjacent room to the exterior measured 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.
+The burn room where the fuel load was located measured 3.8~m (12.5~ft) by 5.7~m (18.7~ft) with a ceiling height of 3.35~m (11.0~ft).
+The adjacent room where the water was applied for gas cooling measured 4.1~m (13.4~ft) by 5.7~m (18.7~ft), also with a ceiling height of 3.35~m (11.0~ft).
+The open door from the adjacent room to the exterior measured 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
 
@@
 
-Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{sec:Experimental_Facility}.
+Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}.
 They were designed to simulate a single floor of a residential structure.
-The outer wall of each structure was composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.
-The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The outer wall of each structure was composed of interlocking concrete blocks 0.61~m (2~ft) wide, 0.61~m (2~ft) high and 1.22~m (4~ft) long.
+The interior dimensions of each structure were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 
-Each structure had burn room, approximately 6.0 m (19.6 ft) by 4.4 m (14.3 ft) and 2.74 m (9.0 ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
-The hallway is approximately 0.95 m (3.1 ft) wide and 5.4 m (17.6 ft) and the entry foyer is 1.2 m (4.1 ft) by 1.9 m (6.1 ft).
-The ceiling height in the hallway and entry foyer was 2.4 m (8 ft).
-The open door on north side from the exterior to the entry foyer was 2.0 m (6.5 ft) high and 0.9 m (2.9 ft) wide.
-The opening on the south face of the structure from the exterior to the burn room was 2.4 m (7.75 ft) high and 1.09 m (3.6 ft) wide.
-A schematic plan view of the structure is given in Figure     .
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
-	\caption{Delaware County, PA Fire Test Structure}
-	\label{fig:DelCoSingleStory}
-\end{figure}
+Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
+The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
+The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).
+The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
+The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide.
+A dimensioned, plan view of the structure is included in Fig.~\ref{fig:Test_Structure_Floor_Plan}.
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
+% 	\caption{Delaware County, PA Fire Test Structure}
+% 	\label{fig:DelCoSingleStory}
+% \end{figure}
 
@@
 \label{sec:Fire_Suppression}	
+Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.
+The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.
+The fires were intended to replicate room and contents fires typically seen within residential structures.
+The hose lines were pre-deployed with fixed nozzles set in two locations.
+One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle).
+The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
+Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack.
+The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.
+This position represented a direct interior attack.
 

### 2015-06-29 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update report, figures

@@
 Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
-The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
+The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
 The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).
@@
 
-The floor of the structure was a concrete pad.
+The floor of the structure was the concrete pad.
 The interior walls of the structure were framed with steel studs and track.
-The studs were set to 0.40 m (16 in) centers.
-The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in .
-Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was attached to the top of the TJIs.
-
-The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
+The studs were set to 0.40~m (16~in) centers.
+The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
+The TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web.
+Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was attached to the top of the TJIs.
+
+The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board.
 The ceiling of the burn room was the exposed ``floor assembly".
-The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room.
-The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
-
-Both structures were similar and were used to run comparative experiments on a given day.
+The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum room.
+The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.
+
+\clearpage
 
@@
 \label{sec:Instrumentation}
+
+The structures were instrumented for temperature, gas velocity, and heat flux measurements.
+Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples.
+Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
+The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter.
+The thermocouple wire was protected with an 3.2~mm (0.125~n) diameter inconnel sheath.
+Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
+A radiometer is a total heat flux gauge with a zirconium plate to isolate radiative heat transfer.
 
@@
 
-The structures were instrumented for temperature, heat flux, and gas velocity measurements.  A schematic plan view of the instrumentation arrangement is show in ????
+  A schematic plan view of the instrumentation arrangement is show in ????
 
@@
 
-Thermocouples:
-Work through the Seebeck effect.
-Two dissimilar metals are joined together with a weld bead.
-Each metal generates a voltage, different from one another, when exposed to a thermal gradient.
-This voltage difference increases with an increase in energy to the thermocouple and through a correlation, a corresponding temperature is found.
-
 \subsubsection{Gas Cooling Experiments}
@@
 
-Gas temperatures in the burn room were measured with bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5 mm (0.02 in) nominal diameter.
 Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..
@@
 
-Additional single thermocouples were installed in conjunction with the bi-directional probes at the exterior vents and in the hallway.
-The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0 mm (0.04 in) nominal diameter.
-Just behind the bead, the thermocouple wire is protected with an 3.2 mm (0.125 in) diameter inconnel sheath.
 In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.
@@
 
-\subsection{Heat Flux}
-\label{subsec:Heat_Flux}
-
-Total Heat Flux:
-Water cooled heat flux gauges measure both the convective and radiative heat transfer to the sensor.
-Hot and cold side of a plate simulating the hot and cold side of a thermocouple.
-The temperature gradient generates a voltage and through correlations, a total heat flux measurement is obtained.
-The sensor is water cooled to ensure a thermal gradient remains and the sensor does not reach uniform temperature.
-The sensor top is painted black to assist with radiation absorption.
-
-Radiometer:
-The radiometer is simply a total heat flux gauge with Zirconium plate atop the sensor preventing the device from recording any heat due to convective transfer.
-
 \subsubsection{Gas Cooling Experiments}
@@
 \label{subsubsec:Fire_Suppression_Heat_Flux_Instrumentation}
-
-Total heat flux was measured with Schmidt-Boelter gauges.
-Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.
-One of each was located near the thermocouple arrays in the burn room.
-The gauges were pointed at the ceiling and positioned 0.15 m (6 in) above the floor.
 
@@
 
-\subsection{Gas Velocity}
-\label{subsec:Gas_Velocity}
-
-Bi-directional Probes:
-- Fire flow measurements are taken using these devices which have a high and low pressure side.
-These flows then travel to a pressure transducer.
-Through a simple conversion, the voltages are converted to pressure and finally a velocity based on the pressure and corresponding temperature measurements.
-
 \subsubsection{Gas Cooling Experiments}
@@
 \label{subsubsec:Fire_Suppression_Gas_Velocity_Instrumentation}
-
-Gas velocity was determined utilizing differential pressure transducers connected to bidirectional velocity probes[ ] in conjunction with a temperature measurement.
-These probes were co-located with the sheathed thermocouples in the north doorway, the south window opening and the hallway.
-The locations are shown in ??????
 

### 2015-06-29 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Minor changes to hose stream report and plotting script; new drawings for specific hose tests

@@
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams are needed.
+However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams is also needed.
 
@@
 \label{sec:Experimental_Structure}
-This series of field experiments was conducted into two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+This series of field experiments was conducted in two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
 
@@
 Two concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-They were designed to simulate a single story and a two story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks 0.61 m (2 ft) wide, 0.61 m (2 ft) high and 1.22 m (4 ft) long.
+They were designed to simulate a single-story and a two-story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks of dimensions 0.61 m x 0.61 m 0.61 m (2 ft x 2ft x 2ft).
 The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
@@
 
-The interior walls of the first floor or each structure were framed with steel studs and track.
+The interior walls of the first floor of each structure were framed with steel studs and track.
 The studs were set to 0.40 m (16 in) centers.
@@
 
-Opening front door, window, rear doors.
-
-Single story  
 The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
@@
 Uncertainties are grouped into two categories according to the method used to estimate them.
-Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means ~\cite{Taylor&Kuyatt:1994}.
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
 Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%.
@@
 To begin the process, the nozzle was adjusted to produce the desired hose stream pattern.
-Once the nozzle was adjusted, water was applied at the ``far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds.
+Once the nozzle was adjusted, water was applied at the "far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds.
 After 60 seconds of water flow, the stairwell door was opened.
 60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
-Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the ``near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).
+Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the "near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).
 
@@
 A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32.
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}) in the fixed position.
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_31_32_setup}) in the fixed position.
 After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds.
@@
 While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated.
-After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for thirty seconds while the south side door was opened and closed.
+After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed.
 This entire procedure was repeated an additional time.
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_31_32}
+\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
+\label{fig:Test_31_32_setup}
+\end{figure}
+\FloatBarrier
 
@@
 Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_34}
+\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
+\label{fig:Test_34_setup}
+\end{figure}
+\FloatBarrier
 
@@
 
-\begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
-\begin{tabular}{|l|c|c|c|c|}
-\cline{2-5}
-\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
-\textit{Straight} & 
-%%%%Test 16%%%% 
-0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
-%%%%Test 17%%%% 
-0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
-\textit{Narrow Fog} & 
-%%%%Test 16%%%% 
-1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
-%%%%Test 17%%%% 
-0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
-\textit{Wide Fog} 	& 
-%%%%Test 16%%%% 
-1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
-%%%%Test 17%%%% 
-0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
-\end{tabular}
-\label{table:Tests_16_17_BDP_A10_Avgs}
-\end{table}
+%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%
+%\begin{table}[!ht]
+%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
+%\begin{tabular}{|l|c|c|c|c|}
+%\cline{2-5}
+%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
+%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
+%\textit{Straight} & 
+%%%%%Test 16%%%% 
+%0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
+%%%%%Test 17%%%% 
+%0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
+%\textit{Narrow Fog} & 
+%%%%%Test 16%%%% 
+%1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
+%%%%%Test 17%%%% 
+%0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
+%\textit{Wide Fog} 	& 
+%%%%%Test 16%%%% 
+%1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
+%%%%%Test 17%%%% 
+%0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
+%\end{tabular}
+%\label{table:Tests_16_17_BDP_A10_Avgs}
+%\end{table}
+
+%code for higher resolution in tabulated values
+%\textit{Straight} & 0.84 & 0.94 & 0.73 & 0.69 \\ \hline
+%\textit{Narrow Fog} & 1.41 & 1.00 & 0.75 & 0.75 \\ \hline
+%\textit{Wide Fog} & 1.23 & 1.37 & 0.88 & 0.71 \\ \hline
+
+%\begin{table}[!ht]
+%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
+%\begin{tabular}{|l|c|c|c|c|}
+%\cline{2-5}
+%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
+%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
+%\textit{Straight} 	& 
+%%%%%Test 16%%%% 
+%2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
+%%%%%Test 17%%%% 
+%2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
+%\textit{Narrow Fog} & 
+%%%%%Test 16%%%% 
+%4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
+%%%%%Test 17%%%% 
+%2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
+%\textit{Wide Fog} 	& 
+%%%%%Test 16%%%% 
+%3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
+%%%%%Test 17%%%% 
+%3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
+%\end{tabular}
+%\label{table:Tests_16_17_BDP_A13_Avgs}
+%\end{table}
+
+%code for higher resolution in tabulated values
+%\textit{Straight} 	& 2.82 & 3.10 & 2.66 & 2.33 \\ \hline
+%\textit{Narrow Fog} & 4.39 & 3.26 & 2.58 & 2.68 \\ \hline
+%\textit{Wide Fog} 	& 3.92 & 4.37 & 3.14 & 2.76 \\ \hline
 
@@
 
-%code for higher resolution in tabulated values
-%\textit{Straight} & 0.84 & 0.94 & 0.73 & 0.69 \\ \hline
-%\textit{Narrow Fog} & 1.41 & 1.00 & 0.75 & 0.75 \\ \hline
-%\textit{Wide Fog} & 1.23 & 1.37 & 0.88 & 0.71 \\ \hline
-
 \begin{table}[!ht]
 \caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
-\begin{tabular}{|l|c|c|c|c|}
-\cline{2-5}
-\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
-\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
+\\
+\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
+\midrule
 \textit{Straight} & 
@@
 %%%%Test 17%%%% 
-2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
+2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
+\\	\multicolumn{5}{c}{}	\\
 \textit{Narrow Fog} & 
@@
 %%%%Test 17%%%% 
-2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
+2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
+\\	\multicolumn{5}{c}{}	\\
 \textit{Wide Fog} 	& 
@@
 %%%%Test 17%%%% 
-3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
+3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
+\\ 
+\bottomrule
 \end{tabular}
@@
 \end{table}
-
-%code for higher resolution in tabulated values
-%\textit{Straight} 	& 2.82 & 3.10 & 2.66 & 2.33 \\ \hline
-%\textit{Narrow Fog} & 4.39 & 3.26 & 2.58 & 2.68 \\ \hline
-%\textit{Wide Fog} 	& 3.92 & 4.37 & 3.14 & 2.76 \\ \hline
 
@@
 
+%%%%%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\begin{table}[!ht]
+%\addtolength{\tabcolsep}{-3.25pt}
+%\small
+%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
+%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+%\cline{2-9}
+%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
+%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\textit{Straight} 	& 
+%%%%%Test 18%%%% 
+%-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
+%%%%%Test 19%%%% 
+% 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
+%\textit{Narrow Fog} & 
+%%%%%Test 18%%%% 
+% 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
+%%%%%Test 19%%%% 
+% 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
+%\textit{Wide Fog} 	& 
+%%%%%Test 18%%%% 
+% 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
+%%%%%Test 19%%%% 
+% 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
+%\end{tabular}
+%\label{table:Tests_18_19_BDP_A10_Avgs}
+%\end{table}
+%
+%%code to increase resolution of tabulated values
+%%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
+%%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
+%%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
+%
+%\begin{table}[!ht]
+%\addtolength{\tabcolsep}{-3.25pt}
+%\small
+%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
+%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
+%\cline{2-9}
+%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
+%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\textit{Straight}  &
+%%%%%Test 18%%%% 
+%-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
+%%%%%Test 19%%%%					
+% 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
+%\textit{Narrow Fog} & 
+%%%%%Test 18%%%%
+% 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
+%%%%%Test 19%%%%
+% 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
+%\textit{Wide Fog} 	& 
+%%%%%Test 18%%%%
+%3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
+%%%%%Test 19%%%%
+%3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
+%\end{tabular}
+%\label{table:Tests_18_19_BDP_A13_Avgs}
+%\end{table}
+%
+%%code to increase resolution of tabulated values
+%%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
+%%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
+%%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
+
 \begin{table}[!ht]
-\addtolength{\tabcolsep}{-3.25pt}
-\small
+%\addtolength{\tabcolsep}{-3.25pt}
+%\small
 \caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\cline{2-9}
-\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{4}{c}{\underline{Test 18}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\
+\midrule 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%Test 18%%%% 
--0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
-%%%%Test 19%%%% 
- 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
+-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
+\\	\multicolumn{5}{c}{}	\\
 \textit{Narrow Fog} & 
 %%%%Test 18%%%% 
- 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
-%%%%Test 19%%%% 
- 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
+ 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ 
+\\	\multicolumn{5}{c}{}	\\
 \textit{Wide Fog} 	& 
 %%%%Test 18%%%% 
- 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
+ 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ 
+\\
+\midrule
+& \multicolumn{4}{c}{\underline{Test 19}} 
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\
+\midrule
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textit{Straight} 	& 
 %%%%Test 19%%%% 
- 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
+ 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
+\\	\multicolumn{5}{c}{}	\\
+\textit{Narrow Fog} & 
+%%%%Test 19%%%% 
+ 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$
+\\	\multicolumn{5}{c}{}	\\
+\textit{Wide Fog} 	& 
+%%%%Test 19%%%% 
+ 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$
+\\
+\bottomrule
 \end{tabular}
@@
 
-%code to increase resolution of tabulated values
-%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
-%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
-%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
-
 \begin{table}[!ht]
-\addtolength{\tabcolsep}{-3.25pt}
-\small
+%\addtolength{\tabcolsep}{-3.25pt}
+%\small
 \caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
-\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-\cline{2-9}
-\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{4}{c}{\underline{Test 18}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\
+\midrule 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%Test 18%%%% 
--0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
-%%%%Test 19%%%%					
- 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
+-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$
+\\	\multicolumn{5}{c}{}	\\
 \textit{Narrow Fog} & 
 %%%%Test 18%%%%
- 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
-%%%%Test 19%%%%
- 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
+ 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$
+ \\	\multicolumn{5}{c}{}	\\ 
 \textit{Wide Fog} 	& 
 %%%%Test 18%%%%
-3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
+3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$
+\\
+\midrule
+ & \multicolumn{4}{c}{\underline{Test 19}}	\\ 
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\
+\midrule
+\textit{Straight}  &
 %%%%Test 19%%%%					
-3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
+ 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ 
+ \\	\multicolumn{5}{c}{}	\\
+\textit{Narrow Fog} & 
+%%%%Test 19%%%%
+ 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$
+\\	\multicolumn{5}{c}{}	\\
+\textit{Wide Fog} 	& 
+%%%%Test 19%%%%
+3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$
+\\
+\bottomrule
 \end{tabular}
@@
 \end{table}
-
-%code to increase resolution of tabulated values
-%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
-%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
-%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
 
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
+\bibliography{../../../../../Bibliography/FDS_general}
 

### 2015-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: minor report edit
DelCo2012: update report

@@
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
-A radiometer is a total heat flux gauge with a zirconium plate to isolate radiative heat transfer.
+A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
 	\caption{Photograph of the Instrumentation Dimensions in the Fire Suppression Experiments.}
@@
 Uncertainties are grouped into two categories according to the method used to estimate them.
-Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means  [ ].
-Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval (± a) is essentially 100~\%.
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
+Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$ a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2σ).
+Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 Each length measurement was taken carefully.
-Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of ± 6.0 mm (0.25) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft) [ ] .
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of ± 0.5~\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
-Steel measuring tapes with a resolution of  ± 0.5 mm (0.02 in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of ±1.6 mm (0.06 in) for 9.1 m (30 ft) tapes and ±6.4 mm (0.25 in) for 30.5 m (100 ft) tapes [ ] .
-Some issues, such as “soft” edges on the upholstered furniture, result in an estimated total expanded uncertainty of  ± 1.0~\%.
-
-The load cell used to weigh the fuels prior to the experiments had a range of 0 kg (0 lbs) to 200 kg (440lbs) with a resolution of a 0.05 kg (0.11 lb) and a calibration uncertainty within 1~\% [] .
-The expanded uncertainty is estimated to be less than  ± 5 %.
-The standard uncertainty in temperature of the thermocouple wire itself is  ± 2.2 °C at 277 °C and increases to ± 9.5 °C at 871 °C as determined by the wire manufacturer [ ] .
-The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty [ ,  ] .
+Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of $\pm$ 6.0 mm (0.25) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{StanleyTools}.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$ 0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$ 1.0~\%.
+
+The load cell used to weigh the fuels prior to the experiments had a range of 0~kg (0~lb) to 200~kg (440~lb) with a resolution of a 0.05~kg (0.11~lb) and a calibration uncertainty within 1~\%~\cite{Ohaus:2000}.
+The expanded uncertainty is estimated to be less than $\pm$ 5~\%.
+
+The standard uncertainty in temperature of the thermocouple wire itself is $\pm$ 2.2 $^{\circ}$C at 277 $^{\circ}$C and increases to $\pm$ 9.5~$^{\circ}$C at 871~$^{\circ}$C as determined by the wire manufacturer\cite{Omega:2004}.
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
-The estimated total expanded uncertainty for temperature in these experiments is ± 15 %.
+The estimated total expanded uncertainty for temperature in these experiments is $\pm$ 15~\%.
+
 In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
-The manufacturer reports a ± 3~\% calibration expanded uncertainty for these devices [ ] .
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically ± 8~\% [] .
-
-The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of ± 1~\% when compared with span gas volume fractions [].
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of ± 12~\% is being applied to the results [ ].
-
-Differential pressure reading uncertainty components were derived from pressure transducer
-instrument specifications and previous experience with pressure transducers. The transducers
-were factory calibrated and the zero and span of each was checked in the laboratory prior to the
-experiments yielding an accuracy of ± 1~\% [ ] . The total expanded uncertainty was estimated at 10~\%.
+The manufacturer reports a $\pm$ 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$ 8~\%~\cite{Pitts:2006}.
+
+The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of $\pm$ 12~\% is being applied to the results~\cite{Lock:1}.
+
+Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
+The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$ 1~\%~\cite{Setra:2002}.
+The total expanded uncertainty was estimated at 10~\%.
 
@@
 Bare-bead Type K thermocouple are co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from ± 0.14 to ± 0.22 for bi-directional probes of similar design[] .
-The total expanded uncertainty for gas velocity in these experiments w estimated to be  ± 18 %.
-Water Flowrate
-Water flowrate was measured with a pressure and flow meter combination shown in Figure x.x.
-The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0 – 4.1 MPa (0 - 600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments w estimated to be  $\pm$ 18~\%.
+
+Water flowrate was measured with a pressure and flow meter combination.
+The meter consists of a section of 6.35~cm (2.5~inch) cast aluminum pipe with a 0 - 4.1~MPa (0 - 600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a ± 5~\% calibration expanded uncertainty for the flow sensor and ± 3~\%  for the pressure sensor [ ] .
+The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\%  for the pressure sensor~\cite{Akron:2009}.
 The pressure transducer was calibrated with a known analog pressure gauge.
 The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
-The total expanded uncertainty was estimated at ± 10 %.
+The total expanded uncertainty was estimated at $\pm$ 10 %.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
 	\caption{Wood Fuel Load Dimensions.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
 	\caption{Furniture Fuel Load Dimensions.}

### 2015-06-30 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added content to hose report, including new pictures and drawings

@@
 \label{sec:Instrumentation}
-Schematic plan overviews of the instrumentation in the East and West Structures are shown in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}, respectively.
+Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}.
 There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
@@
 A single thermocouple was attached to each bi-directional probe.
-The thermocouples used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter.
+The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter.
 Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.
-
-%\begin{figure}[!ht]
-%\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../../Drawings/PDFs/With_Instrumentation/East_Test_Structure_Devices_Hose_Test}
-%\caption[Location of Instrumentation in East Structure]{Location of Instrumentation in East Structure}
-%\label{fig:east_instrumentation}
-%\end{figure}
 
@@
 
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../../Figures/flow_meter}
-%\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
-%\label{fig:flow_meter}
-%\end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Pictures/flow_meter}
+\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
+\label{fig:flow_meter}
+\end{figure}
+\FloatBarrier
 
@@
 
-Test 33 varied from Tests 29 and 30 in multiple ways.
-First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}.
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
+\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 29 and 30}
+\label{fig:test_29_30_pic}
+\end{figure}
+\FloatBarrier
+
+Test 34 varied from Tests 29 and 30 in multiple ways.
+First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_setup}.
 Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
@@
 A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32.
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_31_32_setup}) in the fixed position.
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:test_29-32_setup}) in the fixed position.
 After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_31_32}
-\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
-\label{fig:Test_31_32_setup}
+\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
+\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 31 and 32}
+\label{fig:test_31_32_pic}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
+\caption[East Structure layout for Tests 29-32]{East Structure layout for Tests 29-32}
+\label{fig:test_29-32_setup}
 \end{figure}
@@
 Test 34 varied from Tests 31 and 32 in multiple ways.
-First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_34_setup}.
+First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:test_33_34_setup}.
 Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_34}
-\caption[East Structure layout for Tests 31 and 32]{East Structure layout for Tests 31 and 32.}
-\label{fig:Test_34_setup}
+\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
+\caption[East Structure layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
+\label{fig:test_33_34_setup}
 \end{figure}

### 2015-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012: update report

@@
 \vspace*{2\baselineskip}
-August 2014}}
+August 2015}}
 
@@
 
-\section{Experimental Facility}
+\section{Experimental Facilities}
 \label{sec:Experimental_Facility}
@@
 
-\subsection{Fire Training Structure - Gas Cooling}
+\subsection{Fire Training Structure}
 \label{sec:Burn_Building}
@@
 
-\subsection{Concrete Structures - Fire Suppression}
+\subsection{Concrete Block Structures}
 \label{sec:Experimental Structures}
@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple wire was protected with an 3.2~mm (0.125~n) diameter inconnel sheath.
+The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconnel sheath.
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
 A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/Legend2}
-% 	\caption{Instrumentation Legend}
-% 	\label{fig:Instrumentation_Legend}
-% \end{figure}
-
-\subsection{Gas Cooling Instrumentation}
+A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.35\columnwidth]{../Figures/Pictures/Legend2}
+	\caption{Instrumentation Legend.}
+	\label{fig:Instrumentation_Legend}
+\end{figure}
+
+\subsection{Gas Cooling}
 \label{subsec:Gas_Cooling_Instrumentation}
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
-	\caption{Photograph of the Instrumentation Dimensions in the Gas Cooling Experiments}
+The gas cooling tests included 4 bare-bead thermocouple arrays  a bi-directional probe plus solid thermocouple array, and a total heat flux gauge/radiometer pair.
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (cf.
+Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Each of the bare-bead thermocouple array had 11 thermocouples.
+The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10ft) below the ceiling.
+There were 6 velocity probes and solid thermocouples centered at the external doorway to the gas cooling room.
+The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft), and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
+The total heat flux guage/radiometer were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
+	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
 	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
@@
 
-\subsection{Fire Suppression Instrumentation}
+\clearpage
+
+\subsection{Fire Suppression}
 \label{subsec:Fire_Suppression_Instrumentation}
 
-  A schematic plan view of the instrumentation arrangement is show in ????
+The fire suppression testing included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs.
+Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf.
+Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Each bare-bead thermocouple array had 8 thermocouples.
+The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
+The three bi-directional probe arrays had unique sensor locations.
+For the window array there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit.
+For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling.
+The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit.
+The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit.
+The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The pairs of total heat flux guages were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.
 
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
-	\caption{Photograph of the Instrumentation Dimensions in the Fire Suppression Experiments.}
+	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
 	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Fog_Instrumentation}
-	\caption{Photograph of the Instrumentation in the Fog Stream Tests.}
-	\label{fig:Fog_Instrumentation}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Straight_Stream_Instrumentation}
-	\caption{Photograph of the Instrumentation in the Straight Stream Tests.}
-	\label{fig:Straigh_Stream_Instrumentation}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryInstrumentation}
-	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
-	\label{fig:Fire_Suppression_Instrumentation}
-\end{figure}
-
-\subsection{Temperature}
-\label{subsec:Temperature}
-
-\subsubsection{Gas Cooling Experiments}
-\label{subsubsec:Gas_Cooling_Temperature_Instrumentation}
-
-\subsubsection{Fire Suppression Experiments}
-\label{subsubsec:Fire_Suppression_Temperature_Instrumentation}
-
-Thermocouple arrays were installed 2.0 m (6.7 ft) from both the east and the west walls of the burn room and 2.1 m (6.9 ft) from the south wall as shown in Figure ..
-The vertical arrays had thermocouples located 0.03, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13 m below the bottom edge of the joist, where a ceiling would be installed.
-
-In the north doorway, there were seven thermocouples were located at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft) below the soffit along the vertical centerline of the doorway opening.
-In the hallway, there were seven thermocouples positioned vertically at: 0.15 m (0.5 ft), 0.30 m (1 ft), 0.61 m (2 ft), 0.91 m (3 ft), 1.22 m (4 ft), 1.51 m (5.0 ft), and 1.83 (6.0 ft)   In the south window opening, there were four thermocouples are located 0.28 m (0.95 ft), 0.58 (1.90 ft), 0.84 m (2.85 ft), and 1.16 m (3.8 ft) below the soffit.
-
-\subsubsection{Gas Cooling Experiments}
-\label{subsubsec:Gas_Cooling_Heat_Flux_Instrumentation}
-
-\subsubsection{Fire Suppression Experiments}
-\label{subsubsec:Fire_Suppression_Heat_Flux_Instrumentation}
-
-In the northwest corner of the burn room two total heat flux gauges are located approximately 0.61 m (2 ft) out of the corner and 1.52 m (5 ft) below the ceiling, a position chosen to be representative of the height of a crawling firefighter's head.
-One of the gauge's sensing surface is facing the ceiling and the other gauge is facing the pallets.
-A similar heat flux gauge installation is located in the hallway, approximately 3.81 m (12.5 ft) from the burn room and 0.3 m (1ft) from the east wall of the hallway as shown in figure xx.
-Again on gauge was facing the ceiling and one was facing the burn room.
-
-\subsubsection{Gas Cooling Experiments}
-\label{subsubsec:Gas_Cooling_Gas_Velocity_Instrumentation}
-
-\subsubsection{Fire Suppression Experiments}
-\label{subsubsec:Fire_Suppression_Gas_Velocity_Instrumentation}
-
-\subsection{Mass}
-\label{subsec:Mass}
-
-\subsection{Moisture Content}
-\label{subsec:Moisture_Content}
-
-\subsection{Infrared Radiation}
-\label{subsec:Infrared_Radiation}
+\clearpage
+
+% \subsection{Mass}
+% \label{subsec:Mass}
+
+% \subsection{Moisture Content}
+% \label{subsec:Moisture_Content}
+
+% \subsection{Infrared Radiation}
+% \label{subsec:Infrared_Radiation}
 
@@
 
-\section{Fuel Load: Gas Cooling}
-\label{sec:Fuel_Load:_Gas_Cooling}
+\section{Fuel Load}
+\label{sec:fuel_load}
+
+\subsection{Gas Cooling}
+\label{sec:Fuel_Load_Gas_Cooling}
 
@@
 
-\section{Fuel Load: Wood Experiments}
-\label{sec:Fuel_Load:_Wood_Experiments}
+\subsection{Fire Suppression}
+\label{sec:Fuel_Load_Wood_Experiments}
 
@@
 
-\section{Fuel Load: Furniture Experiments}
-\label{sec:Fuel_Load:_Furniture_Experiments}
-
 \begin{figure}[!ht]
@@
 	\centering
+	\scriptsize
 	\caption{Fire Suppression Fuel masses}
@@
 
-\chapter{References}
-\label{chap:References}
-
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}

### 2015-07-02 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Added content to hose stream report, primarily in the procedure section

@@
 \includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
-\caption[East Structure floor layout]{East Structure floor layout. All dimensions are in meters.}
+\caption[East Structure Layout]{East Structure floor layout. All dimensions are in meters.}
 \label{fig:east_general_plan}
@@
 \includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
-\caption[West Structure first and second floor layouts]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
+\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
 \label{fig:west_general_plan}
@@
 
-\section{Instrumentation}
+\subsection{Instrumentation}
 \label{sec:Instrumentation}
@@
 \includegraphics[width=6in]{../Pictures/BDPs}
-\caption[Two sets of BDPs in Doorway]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
+\caption[Two sets of BDPs in Doorway of West Structure]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
 \label{fig:BDPs}
@@
 
-Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors using a monitor equipped with a combination nozzle.
-A straight stream pattern was used during Test 29, and a narrow fog stream pattern was used during Test 30.
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:Test_29-32_setup}).
+Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a monitor equipped with a combination nozzle.
+A schematic of the structure's layout during the two tests is presented in Fig.~\ref{fig:test_29-32_setup}.
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C, as pictured in Fig.~\ref{fig:test_29_30_pic}.
 After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped.
@@
 Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped.
-This process was repeated an additional time.
+This entire procedure was repeated an additional time.
+A straight stream pattern was used during Test 29 and a narrow fog stream pattern was used during Test 30.
+
+\begin{figure}[!ht]
+\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
+\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
+\label{fig:test_29-32_setup}
+\end{figure}
+\FloatBarrier
 
@@
 \includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
-\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 29 and 30}
+\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and at Door BC (bottom row) during Tests 29 and 30}
 \label{fig:test_29_30_pic}
@@
 
-Test 34 varied from Tests 29 and 30 in multiple ways.
-First, for Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:Test_33_setup}.
-Additionally, Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
-Then, the south side door was opened, and each stream was applied for 30 seconds again.
-
-Tests 16 and 17 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a monitor with a combination nozzle located at the south side, double doors on the first level of the West Structure.
-The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Tests 16 and 17 repeated an identical process three times, one time for each hose stream pattern.
-To begin the process, the nozzle was adjusted to produce the desired hose stream pattern.
-Once the nozzle was adjusted, water was applied at the "far target", located on the ceiling approximately X m (Xft) from the south interior wall, for 60 seconds.
-After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
-Then, water flow stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the "near target", located approximately on the ceiling X m (Xft) from the interior wall of the double doors (Fig.~\ref{fig:Test_16_17}).
-
-\subsubsection{Handline Experiments}
-\label{sec:Water_Flow_Handline_Procedure}
-A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water.
-Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.
-
-Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors using a handline with a combination nozzle.
-A straight stream pattern was used during Test 31, and a narrow fog stream pattern was used during Test 32.
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C (marked in Fig.~\ref{fig:test_29-32_setup}) in the fixed position.
-After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction and then returned to the fixed position of 30 seconds.
-Next, the nozzle was rotated in the counter-clockwise direction for 30 seconds, and then returned to the fixed position for 30 seconds.
-While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated.
-After the patterns were applied with the south side door opened, the door was closed, the handline was aimed at Door BC, and each pattern was applied again for 30 seconds while the south side door was opened and closed.
-This entire procedure was repeated an additional time.
+Test 33 varied from Tests 29 and 30 in multiple ways.
+During Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as shown in Fig.~\ref{fig:test_33_pic}.
+A schematic of the structure's layout during Test 33 is presented in Fig.~\ref{fig:test_33_34_setup}.
+The test began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
+Then, the south side door was opened and each stream was applied for 30 seconds again.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
-\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left) and narrow fog stream (right) aimed at ceiling of Room C (top) and Door BC (bottom) during Tests 31 and 32}
-\label{fig:test_31_32_pic}
+\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/SS_Room_B_Test_33}
+\\~\\
+\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/NF_Room_B_Test_33}
+\\~\\
+\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/WF_Room_B_Test_33}
+\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 33]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 33}
+\label{fig:test_33_pic}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
-\caption[East Structure layout for Tests 29-32]{East Structure layout for Tests 29-32}
-\label{fig:test_29-32_setup}
-\end{figure}
-\FloatBarrier
-
-Test 34 varied from Tests 31 and 32 in multiple ways.
-First, for Test 34, the handline was located inside Room C and aimed at the ceiling of Room B, as pictured in Fig.~\ref{fig:test_33_34_setup}.
-Additionally, Test 34 began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position and then for 30 seconds in a clockwise application pattern.
-Then, the handline was aimed at Door AB, and again water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
-These steps were repeated for narrow fog and wide fog streams.
-Additionally, the procedure was repeated for the three types of streams, except a counter clockwise pattern was applied.
-
-\begin{figure}[!ht]
 \includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
-\caption[East Structure layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
+\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
 \label{fig:test_33_34_setup}
@@
 
-Tests 18 and 19 followed an identical procedure that involved flowing water in a straight stream, narrow fog stream, and wide fog stream pattern from a handline with a combination nozzle located at the south side, double doors on the first level of the West Structure.
-The difference between the two tests was that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Tests 18 and 19 repeated an identical process three times, one time for each hose stream pattern.
-To begin the process, the nozzle was adjusted to produce the desired hose stream pattern.
-Once the nozzle was adjusted, water was applied while the hoseline was in the fixed position.
+%ADD TARGET DIMENSION%
+Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
+The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately X m (X ft) from the interior side of the north wall, and a "far" target, located approximately X m (X ft) from the interior side of the north wall.
+The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Each test began by flowing water in a straight stream pattern at the far target for 60 seconds.
 After 60 seconds of water flow, the stairwell door was opened.
-60 seconds after the stairwell door was opened, the north side, west double door on the second floor was opened, and water continued to flow for 60 more seconds.
-Then, water flow stopped, the two doors were closed, and the procedure was repeated for the sweeping, clockwise, and counterclockwise application patterns.
+One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
+Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target.
+The entire process was repeated for the narrow fog and wide fog streams.
+Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.
 
@@
 \includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
-\caption[West Structure first and second floor layouts for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18.
+\caption[West Structure Layout for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18.
 Both double doors and the south side door on the first floor were in the opened position for the duration of the test.
@@
 \includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
-\caption[West Structure first and second floor layouts for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19.
+\caption[West Structure Layout for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19.
 Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test.
@@
 \FloatBarrier
+
+\begin{figure}[!ht]
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/SS_near}
+\end{center} 
+\endminipage \hfill
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/NF_near}
+\end{center}
+\endminipage \hfill
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/WF_near}
+\end{center}
+\endminipage \hfill
+\vspace{0.15in}
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/SS_far}
+\end{center} 
+\endminipage \hfill
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/NF_far}
+\end{center}
+\endminipage \hfill
+\minipage{2.15in}
+\begin{center}
+	\includegraphics[width=2in]{../Pictures/WF_far}
+\end{center}
+\endminipage \hfill
+\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Tests 16 and 17]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during Tests 16 and 17}
+\label{fig:test_16_17_pic}
+\end{figure}
+
+\clearpage
+
+\subsubsection{Handline Experiments}
+\label{sec:Water_Flow_Handline_Procedure}
+A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water.
+Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.
+
+Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a combination nozzle attached to a 1.75" handline.
+The structure's layout during both tests was identical to the layout used in Tests 29 and 30 (Fig.~\ref{fig:test_29-32_setup}).
+Each test began by flowing water with the nozzle aimed at the ceiling of Room C in a fixed position, as pictured in Fig.~\ref{fig:test_31_32_pic}.
+After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction for 30 seconds and then returned to the fixed position for 30 seconds.
+Next, the nozzle was rotated in the counterclockwise direction for 30 seconds and then returned to the fixed position for 30 seconds.
+While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated.
+After the patterns were applied with the south side door opened, the door was closed, and the process was repeated with the handline aimed at Door BC.
+The entire procedure was then repeated an additional time.
+A straight stream pattern was used during Test 31 and a narrow fog stream pattern was used during Test 32.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
+\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
+\label{fig:test_31_32_pic}
+\end{figure}
+\FloatBarrier
+
+Test 34 varied from Tests 31 and 32 in multiple ways.
+During Test 34, the handline was located inside Room C.
+The structure's layout during Test 34 was identical to the layout used in Test 33 (Fig.~\ref{fig:test_33_34_setup}).
+The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}.
+Next, the nozzle was rotated in the clockwise direction for 30 seconds.
+Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
+This process were repeated for narrow fog and wide fog streams.
+Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.
+
+%Where was the handline aimed?%
+Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline.
+The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}).
+Each test began by flowing water in a straight stream pattern and fixed position.
+After 60 seconds of water flow, the stairwell door was opened.
+One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
+Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns.
+This entire procedure was repeated for narrow fog and wide fog streams.
 

### 2015-07-02 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: continued to add pictures and content to hose stream report

@@
 \usepackage{placeins}
+\usepackage{units}
+\usepackage[percent]{overpic}
 
@@
 A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure.
-All the experiments were conducted in either the East or West Structure; used a monitor or handline with a combination nozzle to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
+All the experiments were conducted in either the East or West Structure; used a monitor %reference for specs?
+2000 LPM (500 GPM)?
+or 1 \nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
 Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
+
+\begin{figure}[!ht]
+\minipage{3in}
+\begin{center}
+	\includegraphics[width=2.9in]{../Pictures/monitor}
+\end{center} 
+\endminipage \hfill
+\minipage{3in}
+\begin{center}
+	\includegraphics[width=2.9in]{../Pictures/handline}
+\end{center}
+\endminipage \hfill
+\caption[Monitor and Handline Equipped with Combination Nozzle]{Monitor (left) and 1 \nicefrac{3}{4}" handline (right).
+Both are equipped with a combination nozzle and were used in the water flow experiments.}
+\label{fig:monitor+handline}
+\end{figure}
+\FloatBarrier
 
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
+\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
+	\put(83,24){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
+\end{overpic}
 \caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
@@
 \begin{figure}[!ht]
+\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
+	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
+\end{overpic}
+\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
+\label{fig:test_33_34_setup}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[!ht]
 \includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/SS_Room_B_Test_33}
@@
 \label{fig:test_33_pic}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
-\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
-\label{fig:test_33_34_setup}
 \end{figure}
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
+\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
+	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
+\end{overpic}
 \\
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
+\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
+	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
+\end{overpic}
 \\
@@
 \end{figure}
-\FloatBarrier
+\clearpage
 
@@
 
+\begin{figure}[!ht]
+\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
+\\~\\
+\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
+\\~\\
+\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
+\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 34]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 34}
+\label{fig:test_34_pic}
+\end{figure}
+\FloatBarrier
+
 %Where was the handline aimed?%
-Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline.
+Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline.
 The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}).
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/Test_18}
+\includegraphics[width=4.25in]{../Pictures/Test_18}
 \caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18.
@@
 
-Figures \ref{fig:Test_16_BDP_A10_Avg_All}-\ref{fig:Test_17_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the two application locations and three hose stream patterns for Tests 16 and 17.
+Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and Fig.~\ref{fig:Test_16_BDP_A13_Avg_All} contain plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) and \nth{2} level, north side, west double doorway (A13), respectively, for Test 16.
+A similar set of plots was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.
+
+Notice, the only instances in which significant air movement (average velocity greater than 0.5 m/s) occurs through either doorway is when the flow path is fully established, or when both the stairwell door and the \nth{2} level, north side, west double door are opened.
+Tables~\ref{table:Tests_16_17_BDP_A10_Avgs} and~\ref{table:Tests_16_17_BDP_A13_Avgs} contain the average air velocity measured by the bi-directional probes at A10 and A13, respectively, when the flow path was completely established for each hose stream pattern and application location for Tests 16 and 17.
 
@@
 \label{fig:Test_16_BDP_A13_Avg_All}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
-\label{fig:Test_17_BDP_A10_Avg_All}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
-\label{fig:Test_17_BDP_A13_Avg_All}
 \end{figure}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
+\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
 \begin{tabular}{lcccc}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
+\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
 \begin{tabular}{lcccc}
@@
 \appendix
+\chapter{Appendix}
+\label{chap:appendix}
 
-\chapter{Appendix A}
+\section{Additional Figures}
+\label{sec:additional_figures}
 
-Placeholder
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
+\label{fig:Test_17_BDP_A10_Avg_All}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
+\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
+\label{fig:Test_17_BDP_A13_Avg_All}
+\end{figure}
+
+\clearpage
 

### 2015-07-02 Projects/DelCo_2012/Report/DelCo_2012.tex
Delco_2012:  update report

@@
 \midrule
-Nozzle       & Metro 1, fixed gallonage fog,straight, or 7/8~inch solid stream \\
+Nozzle       & Metro 1, fixed gallonage fog, straight, or 7/8~inch solid stream \\
 Hoseline     & 100~ft of 1-3/4~inch hoseline \\
@@
 
-Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and eleven of the tests were conducted in the experimental structures to be used for the fire suppression tests.
+Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and twelve of the tests were conducted in the experimental structures to be used for the fire suppression tests.
 The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (cf.
@@
 
-Wood pallets were used to provide the fuel for the fire used in the gas cooling experiments.
-The pallets were approximately   1.2 m (4.0 ft) by 1.0 m (3.3 ft) by 0.13 m (0.42 ft) thick.
-Forty eight of the pallets used to fuel the gas cooling experiments were weighed.
-The pallets ranged in mass from 13.6 kg (29.9 lbs) to 26.4 kg (58.1 lbs) with an average of 18.4 kg (40.5 lbs).
-The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig xx.
-Approximately one half of a bale of excelsior, 13.0  kg (28.6 lbs), was mixed with the pallets to aid with ignition.
-
-As the pallets burned burn away and the hot gas layer temperatures decreased, the steel shutters on the window to the fire room were opened and additional pallets were added to the piles of burning pallets until the flames from the piles reached the ceiling of the burn room again.
-The number of pallets added each time varied.
+Wood pallets were used as the fuel source for the gas cooling experiments.
+The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick.
+The pallets ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs).
+The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Pallet_Fuel_Load}.
+Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition.
+Fig.~\ref{fig:Burn_Building_Fuel_Load}, provides dimensioned locations of the two stacks of pallets within the burn room.
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
+% 	\caption{Pallet Fuel Load}
+% 	\label{fig:Pallet_Fuel_Load}
+% \end{figure}
 
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
-% 	\caption{Pallet Fuel Load}
-% 	\label{fig:Pallet_Fuel_Load}
-% \end{figure}
+Note, that as the pallets burned away and the hot gas layer temperatures decreased, the steel shutters on the window to the burn room were opened and additional pallets were added.
+Pallets were added to the existing fuel locations until the flames from the piles reached the ceiling of the burn room again.
+The number of pallets added each time varied.
+
+\clearpage
 
 \subsection{Fire Suppression}
-\label{sec:Fuel_Load_Wood_Experiments}
+\label{sec:Fuel_Load_Fire_Suppression}
+
+\subsubsection{Wood Fuel Package}
+\label{sec:fire_suppression_pallet_fuel}
 
@@
 The hay was layered between each pallet.
+Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition.
 The pallets and hay were weighed prior to each experiment.
-For the four experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
-A complete listing of the mass of each pallet and hay bales is given in Appendix ????????
-
-The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room.
+For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
+A complete listing of the mass of each pallet and hay bales is given in Appendix~\ref{app:fuel_loads}.
+
+\begin{figure}[!ht]
+	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
+	\caption{Photograph of Southeast corner of burn room with wood fuel load.}
+	\label{fig:Wood_Fuel_Load}
+\end{figure}
+
+The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room (cf.
+Fig.~\ref{fig:Wood_Fuel_Load_Dimensions}).
 The pallets were 1.2~m (48~in) long, 1.0~m (40~in) and 123~mm (4.8~in) high.
-The stacks were 150~mm (6~in) apart.
-One layer of 13 mm (0.5 in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
+The stacks were spaced 150~mm (6~in) apart.
+One layer of 13~mm (0.5~in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
 The east and south wall of the burn room was covered with 15~mm (0.59~in) thick, sheets of plywood.
@@
 The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.
-The southeast corner of the burn room with the fuel load installed is shown in Fig.~\ref{fig:Wood_Fuel_Load}.
 
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Wood_Fuel_Package}
-	\caption{Photograph of Southeast corner of burn room with wood fuel load.}
-	\label{fig:Wood_Fuel_Load}
+\clearpage
+
+\subsubsection{Furniture Fuel Package}
+\label{sec:fire_suppression_furniture_fuel}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
+	\caption{Furniture Fuel Load Dimensions.}
+	\label{fig:Furniture_Fuel_Load}
 \end{figure}
@@
 	\renewcommand{\tabcolsep}{1pt}
-	\begin{tabular}{lllllll}
-		\hline\noalign{\smallskip}
+	\begin{tabular}{lllllcc}
+		\toprule[1.5pt]
 		Item               & Component		& Quantity		&  Material Description             							&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
-		\noalign{\smallskip}\hline\noalign{\smallskip}
-		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
+		\midrule
+		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame 	   &  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
 		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
@@
 			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
-		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
+		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame   	    &  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
 		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
-		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber and Wood Frame     &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
+		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame        &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
 		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
-		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2mm thick&  9    			& 72 \\
+		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
 		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
-		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11mm thick &  0.89 kg/m$^2$    & 19.8 \\
+		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11~mm H    &  0.89 kg/m$^2$    & 19.8 \\
 		                   &                &               &                                                               &                               & Total Mass        & 335.6 \\
-		\noalign{\smallskip}\hline
+		\bottomrule[1.25pt]
 	\end{tabular}
@@
 
-The experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure.
-The building was sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
+Spray density experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure.
+The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
 Water flowed for a specified duration and upon completion the bins were removed from the structure.
 Each bin was then weighed to quantify the impact of nozzle location and spray pattern.
-
-12 Experiments:
-4 SS from room
-2 Fog from room
-2 SS from Hall
-2 Fog from Hall
-1 SB from Hall
-1 SB from Room
-
-Spray Distribution Summary:
-- Experiments provided nozzle placement for gas cooling and fire suppression experiments.
-- Provide a sense of the distribution of the water throughout the test space.
-
-Hallway nozzle = gas cooling
-
-Room nozzle = seat of fire
+Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure.
+Table~\ref{tab:spray_density_tests} provides and overview of each individual experiment.
+In the table, BB stands for the burn building tests while CS stands for the concrete structure tests.
+For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.
+
+\begin{table}[!ht]
+\footnotesize
+\centering
+\captionof{table}{Spray Density Test Matrix}\label{tab:spray_density_tests}
+\begin{tabular}{lllllll}
+\toprule[1.5pt]
+Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Height (in) & Location (in) \\
+\midrule
+BB1        &   120              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
+BB2        &   120              & 23            & Water  &  Solid Stream       &                    &          \\
+BB3        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
+BB4        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
+BB5        &   120              & 20            & Water  &  Solid Stream       & 16                 &          \\
+BB6        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
+BB7        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
+BB8        &   120              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\
+BB9        &   120              & 24            & Water  &  30$^{\circ}$ fog   & 17~1/2             &          \\
+BB10       &   120              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\
+BB11       &   120              & 22            & Water  &  Solid 7/8~in slug  & 11~1/2             &          \\
+BB12       &   120              & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
+BB13       &   120              & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB14       &   120              & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB15       &   120              & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB16       &   120              &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
+BB17       &   120              & 20            & CAF    &  Solid Stream narrow & 15                &          \\
+BB18       &   120              & 10            & CAF    &  Solid Stream mid   &                    &          \\
+BB19       &   120              & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
+BB20       &   120              &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
+BB21       &   120              &               & CAF    &  Solid Stream back  &                    &          \\
+CS1        &   115,75           &               & Water  &  Solid Stream       &                    &          \\
+CS2        &   120,115          & 18            & Water  &  Solid Stream       &                    &          \\
+CS3        &   120              & 19            & Water  &  Solid Stream       &                    &          \\
+CS4        &   120,118          & 21            & Water  &  Solid Stream       &                    &          \\
+CS5        &   120,118          & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS6        &   120,118          & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS7        &   120,124          & 15            & Water  &  Solid 7/8~in slug  &                    &          \\
+CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  &                    &          \\
+CS8        &   120,116          & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS9        &   120,116          & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS10       &   120,116          & 16            & Water  &  Solid Stream       &                    &          \\
+CS11       &   120,117          & 16            & Water  &  Solid Stream       &                    &          \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
+\clearpage
+
+After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that the majority of the
 
@@
 
+\appendix
+
+\chapter{Fuel Load Details}
+\label{app:fuel_loads}
+
 \end{document}

### 2015-07-07 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: minor updates to hose stream report

@@
 \label{sec:Background}
+%http://www.tft.com/literature/library/files/bfa.pdf
+Bill Nelson and Keith Royer strongly recommend that the rotation be clockwise as viewed from the nozzle operator’s position.
+From many experiments it was determined that a clockwise rotation is more effective than a counterclockwise rotation.
+They say that:
+1. Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle.
+Counterclockwise rotation does just the opposite.
+2. Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation
+produces steam with an inactive and lazy action.
+3. A clockwise rotation produces a faster knockdown time.
 

### 2015-07-10 Projects/DelCo_2015/Report/Test_Matrix.tex
DelCo_2015: add tex file with table of tests

\documentclass{article}

\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{pdfsync}
\usepackage{microtype}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage{tabularx,ragged2e,booktabs,caption}
\usepackage{caption}
\frenchspacing

\begin{document}

\begin{sidewaystable}[htbp]
\centering
\captionof{table}{DelCo ESTC 2015 Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#         &  Vent Configuration         	& Attack           & Hose Stream                         & Gear      \\
\midrule
30              &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
31              &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
32              &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
33              &  PPV Test                     & & &           \\  
34              &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
35              &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
36              &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
37              &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
38              &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
39				&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
40				&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
41				&  Open A door + C doors        &                  &  CAFS, varied                       & \\
42				&  Cherry Road + upper C doors  & Allow decay      &  Straight, 150~gpm                  & \\
43				&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
44				&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
45              &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
45              &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
\bottomrule[1.25pt]
\end{tabular}
\end{sidewaystable}

\end{document}

### 2015-07-23 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Minor report updates; editing script for East tests

@@
 2000 LPM (500 GPM)?
-or 1 \nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
+or 1 \nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
 Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
@@
 Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
-The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately X m (X ft) from the interior side of the north wall, and a "far" target, located approximately X m (X ft) from the interior side of the north wall.
+The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall, and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
 The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.

### 2015-07-23 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -108,174 +108,250 @@ for f in os.listdir(data_dir):
 		# Save converted time back to dataframe
 		data['Time'] = t
 
-		#  ============
-		#  = Sorting =
-		#  ============
-
 		# Generate a plot for each quantity group
 		for group in sensor_groups:
+
 			# Skips all groups not in "included groups" in hose_info file
 			if any([substring in group for substring in hose_info['Included Groups'][test_name].split('|')]) == False:
 				continue
 
-			# creates empty "stream" list for the sensor group's results file
-			blank_list = []
-			group_set = {'Stream': blank_list}
- 			group_results = pd.DataFrame(group_set, columns = ['Stream'])
+			# West Test Plotting
+			if 'Test' in test_name:
+				# creates empty "stream" list for the sensor group's results file
+				blank_list = []
+				group_set = {'Stream': blank_list}
+	 			group_results = pd.DataFrame(group_set, columns = ['Stream'])
 
- 			# reads in the stream patterns based on hose_info file
-			for diff in hose_info['Difference'][test_name].split('|'):
-				group_results[diff] = ' '
-				group_results[diff + ' StDev'] = ' '
-			row_num = 0
-
-			fig = figure()
-
-			# resets max and min y values
-			max_y = 0
-			min_y = 0
-
-			# Defines start and end times for different stream patterns
-			for stream in hose_info.columns[2:5]:
-				# ignores streams not involved in test (specified in hose_info file)
-				if hose_info[stream][test_name] == False:
-					continue
-
-				# reads start and end times for current stream from hose_info file
-				start_name = stream + '_start'
-				start = hose_info[start_name][test_name]
-				end_name = stream + '_end'
-				end = hose_info[end_name][test_name]
-
-				# Creates data set of start and end times for current hose stream 
-				stream_data = data.iloc[start:end]
-				t_stream = stream_data['Time']
-
-				# Creates empty data frame (with time index) to plot average of channels for each stream and sensor group
-				stream_group = pd.DataFrame(t_stream)
-
-				for channel in stream_data.columns[1:]:
-					# Skip excluded channels listed in hose_info file
-					if any([substring in channel for substring in hose_info['Excluded Channels'][test_name].split('|')]):
-						continue
-
[…]

### 2015-08-11 Projects/DelCo_2015/Report/Test_Matrix.tex
Delco_2015: update test matrix table

@@
 \midrule
-30              &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
-31              &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
-32              &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
-33              &  PPV Test                     & & &           \\  
-34              &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
-35              &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
-36              &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
-37              &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
-38              &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
-39				&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
-40				&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
-41				&  Open A door + C doors        &                  &  CAFS, varied                       & \\
-42				&  Cherry Road + upper C doors  & Allow decay      &  Straight, 150~gpm                  & \\
-43				&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
-44				&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
-45              &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
-45              &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
+30 West         &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
+31 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
+32 West         &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
+33 West         &  PPV Test                     & & &           \\  
+34 West         &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
+35 West         &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
+36 West         &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
+37 West         &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
+38 West         &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
+39 West 		&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
+40 West 		&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
+41 West 		&  Open A door + C doors        &                  &  CAFS, varied                       & \\
+42 West 		&  Cherry Road + upper C doors  & Allow decay      &  Piercing Nozzle, 150~gpm           & \\
+43 West 		&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
+44 West 		&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
+45 West         &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
+46 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
+47 West         &  Cherry Road					& Coordinated      &  Straight, 140~gpm					 & head forms \\
+48 West         &  Cherry Road					& Uncoordinated    &  Straight, 180~gpm                  & head forms \\
+49 East         &  C Doors                      & Sprinklered      & & \\
+50 West         &  Cherry Road + Vertical		& Uncoordinated    &  Straight, 180~gpm                  & \\
+51 East         &  C Doors                      & Sprinklered      & & \\
+52 East			&  PPV Test 					& & &			\\
+53 East			&  PPV Test 					& & &			\\
+54 East			&  PPV Test 					& & &			\\
+55 East			&  PPV Test 					& & &			\\
+56 West			&  Cherry Road					& Coordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\ 
+57 West			&  Cherry Road					& Uncoordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\
+58 East			&  Single C door Open, A fire 	& C door    	   &  Straight, 150~gpm                  & \\
+59 East         &  C window, A fire				& C window  	   &  Straight, 150~gpm					 & \\
+60 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
+61 East         &  C window, C fire             & C window         &  Wide fog, 150~gpm                  & \\
+62 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
+63 East         &  C window + window base       & C window         & Wide fog, 150~gpm 					 & \\
+
 \bottomrule[1.25pt]

### 2015-08-31 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Updates to hose stream report and plotting/sorting scripts

@@
 
-This report is concerned with examining the impact of hose stream selection and the pattern in which the stream is applied on the ventilation inside a structure with various flow path configurations.
-Two types of experiments were conducted in order to examine the impact.
-First, cold flow tests were performed.
-These tests involved using a 0.46 m (18 in) diameter positive pressure ventilation (PPV) fan to move air through a structure with various flow path configurations.
-The second type of experiment involved flowing water using various stream and application patterns into a structure with flow path configurations similar to the cold flow test configurations.
-Air velocities measured during the hose flow experiments were compared to the velocities measured during the cold flow tests to determine the impact of hose stream and application pattern combinations on ventilation throughout the structure relative to the impact of using a 0.46 m (18 in) diameter PPV fan to move air throughout the structure.
+This report is concerned with examining the impact of hose stream and application pattern selection on the ventilation inside a structure with various flow path configurations.
+Experiments in which water was flowed using various stream and application patterns into a structure with different flow path configurations were conducted.
+Air velocities were measured and used to determine the impact of hose stream and application pattern combinations on ventilation throughout the structure.
 
@@
 %http://www.tft.com/literature/library/files/bfa.pdf
-Bill Nelson and Keith Royer strongly recommend that the rotation be clockwise as viewed from the nozzle operator’s position.
-From many experiments it was determined that a clockwise rotation is more effective than a counterclockwise rotation.
-They say that:
-1. Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle.
+Nelson and Royer suggest using a clockwise rotation instead of a counterclockwise application pattern for the following reasons:
+\begin{enumerate} 
+\item Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle.
 Counterclockwise rotation does just the opposite.
-2. Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation
+\item Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation
 produces steam with an inactive and lazy action.
-3. A clockwise rotation produces a faster knockdown time.
+\item A clockwise rotation produces a faster knockdown time.
+\end{enumerate}
 
@@
 They were designed to simulate a single-story and a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks of dimensions 0.61 m x 0.61 m 0.61 m (2 ft x 2ft x 2ft).
+The first floor of each structure had an outer wall composed of interlocking concrete blocks of dimensions 0.61 m x 0.61 m X 0.61 m (2 ft x 2 ft x 2 ft).
 The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
@@
 The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.125 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure  XX .
-Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed (nailed?) to the top of the TJIs.
+The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1\nicefrac{1}{8} in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure \ref{fig:TJI}.
+Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed to the top of the TJIs.
 
-The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs etc...
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Pictures/TJI_support}
+\caption[Truss Joist I-Beams]{Truss joist I-beams used for the ceiling/floor support in the West Structure}
+\label{fig:TJI}
+\end{figure}
+
+The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs..**** NEED MORE DETAILS ******
 
 The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
-The ceiling of the burn room was the exposed ``floor assembly".
-The walls of the hallway and entry foyer were composed of 16 mm (0.625 in) Type X gypsum room.
+The ceiling of the burn room was the exposed "floor assembly".
+The walls of the hallway and entry foyer were composed of 16 mm (\nicefrac{3}{8} in) Type X gypsum room.
 The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
@@
 There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
-Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
+Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
 Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
@@
 \includegraphics[width=6in]{../Pictures/BDPs}
-\caption[Two sets of BDPs in Doorway of West Structure]{Two sets of BDPs, A5 and A6, in each doorway of the double doors on the first floor of the West Structure}
+\caption[Sets of Bi-directional Velocity Probes in Doorway of West Structure]{Two sets (A5 and A6) of bi-directional velocity probes in each doorway of the double doors on the first floor of the West Structure}
 \label{fig:BDPs}
@@
 Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in) for 30.5 m (100 ft) tapes \cite{NIST_Manual_44}.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in) for 30.5 m (100 ft) tapes~\cite{NIST_Manual_44}.
 Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
@@
 Bare-bead Type K thermocouple are co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design \cite{Bryant:FSJ2009}.
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
 The total expanded uncertainty for gas velocity in these experiments estimated to be $\pm18$\%.
 
-Water flowrate was measured with a pressure and flow meter combination shown in Fig.
-\ref{fig:flow_meter}.
+Water flowrate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
 The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor \cite{Akron}.
+The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor~\cite{Akron}.
 The pressure transducer was calibrated with a known analog pressure gauge.
@@
 
-\subsection{Cold Flow Experimental Procedure}
-\label{sec:Cold_Flow_Procedure}
+% \subsection{Cold Flow Experimental Procedure}
+% \label{sec:Cold_Flow_Procedure}
 
-\subsection{Water Flow Experimental Procedure}
-\label{sec:Water_Flow_Procedure}
+% \subsection{Water Flow Experimental Procedure}
+% \label{sec:Water_Flow_Procedure}
 A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure.
@@
 2000 LPM (500 GPM)?
-or 1 \nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns in the structure.
+or 1~\nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns.
 Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
@@
 \label{chap:Results}
-
-\section{Cold Flow Test Results}
-\label{sec:Cold_Flow_Test_Results}
 
@@
 %\small
+\caption{Average air velocity (m/s) through Door A6 for tested combinations of stream pattern and application location during clockwise and counter clockwise rotations}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{2}{c}{\underline{Room A}} & \multicolumn{2}{c}{\underline{Room B Ceiling}}
+\\
+\textbf{Stream} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\
+\midrule 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\textit{Straight} 	& 
+%%%% Room A %%%% 
+0.6 $\pm 0.3$ & 0.8 $\pm 0.3$ 
+%%%% Room B Ceiling %%%% 
+& 0.5 $\pm 0.3$ & 0.5 $\pm 0.3$
+\\	\multicolumn{5}{c}{}	\\
+\textit{Narrow Fog} & 
+%%%% Room A %%%% 
+1.8 $\pm 0.3$ & 1.6 $\pm 0.3$
+%%%% Room B Ceiling %%%% 
+ & 1.5 $\pm 0.3$ & 1.6 $\pm 0.3$
+\\	\multicolumn{5}{c}{}	\\
+\textit{Wide Fog} 	& 
+%%%% Room A %%%% 
+ 2.1 $\pm 0.3$ & 2.2 $\pm 0.3$
+%%%% Room B Ceiling %%%% 
+ & 2.3 $\pm 0.3$ & 2.6 $\pm 0.3$ \\
+\bottomrule
+\end{tabular}
+\label{table:Test_35_CW_CCW}
+\end{table}
+
+\begin{table}[!ht]
+%\addtolength{\tabcolsep}{-3.25pt}
+%\small
 \caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}

### 2015-08-31 Studies/2012_Chicago/Report/firetech_chicago.tex
Chicago: updates to firetech version
Update figure, update firetech version

@@
 
-\input{../../../Bibliography/commoncommands}
+\usepackage{pdfsync,cite,hyperref}
+\usepackage{tikz,pgfplots}
+\usepackage{rotating,lscape}
+\usepackage{listings}
+\usepackage{multirow,tabularx,ragged2e,booktabs,caption,graphicx,longtable}
+\usepackage{mathptmx,xfrac,amsmath,siunitx}
+
+\pgfplotsset{
+  colormap={blackwhite}{[5pt]
+    rgb255(0pt)=(0,0,255);
+    rgb255(100pt)=(0,255,255);
+    rgb255(200pt)=(0,255,0);
+    rgb255(300pt)=(255,255,0);
+    rgb255(400pt)=(255,0,0)
+  },
+} % sets colors for colorbar
+
 \renewcommand{\sb}[1]{_\mathrm{#1}}
-\renewcommand{\C}{\mbox{C}}
+\newcommand{\C}{\mbox{C}}
 \renewcommand{\H}{\mbox{H}}
@@
 \newcommand{\N}{\mbox{N}}
-
-\usepackage{fancyhdr}
-\pagestyle{fancy}
-\lhead{}
-\rhead{}
-\chead{}
-\renewcommand{\headrulewidth}{0pt}
+\newcommand{\dx}{\delta x}
+\newcommand{\dQ}{\dot{Q}}
 
@@
 This document is organized as follows: Section~\ref{fire_sum} provides a summary of the fire incident, Section~\ref{model} describes the relevant model input parameters and assumptions that were used to develop the simulations, Section~\ref{results} presents the simulation results, and Section~\ref{discussion} discusses the simulation results as they relate to firefighter safety and effectiveness.
-Appendix~\ref{app_draw} contains dimensioned drawings of the first and second floor of the structure.
+Fully dimensioned drawings of the first and second floor of the structure can be found in \cite{Weinschenk:Chicago}.
 
@@
 Three sets of stairs were present in the structure: one front stairwell that connected the first and second levels (Stair 1 in Fig.~\ref{fig:simp_geom}), one rear stairwell that connected the first and second levels (Stair 2 in Fig.~\ref{fig:simp_geom}) and a second rear set of stairs which provided access to the attic (Stair 3 in Fig.~\ref{fig:simp_geom}).
-Stair 3 directly asceneds to attic without a doorway or method to isolate the rear porch from the attic (the top stair is the floor of the attic).
+Stair 3 directly ascends to attic without a doorway or method to isolate the rear porch from the attic (the top stair is the floor of the attic).
 Entry to the first floor of the structure can be made either in the front or rear, as shown in Fig.~\ref{fig:simp_geom}.
@@
 While FDS provides users with the option to use a more complex finite-rate combustion mechanism, there is not sufficient evidence in this case to justify deviating from the default specifications.
-The product yeilds used in this analysis (Eq.~\ref{eq:wood_comb}) are for well-ventilated burning conditions.
-The simple chemistry reaction mechanism in FDS assumes constant, user-specified yeilds for carbon monoxide and soot.
-When a fire becomes underventilated, the yeilds of soot, carbon monoxide, or other product species change due to incomplete combustion.
-If the analysis of model results requires species concentrations, different species yeilds, a more complex chemical reaction, or finite-rate chemistry may be needed~\cite{FDS_Math_Guide}.
+The product yields used in this analysis (Eq.~\ref{eq:wood_comb}) are for well-ventilated burning conditions.
+The simple chemistry reaction mechanism in FDS assumes constant, user-specified yields for carbon monoxide and soot.
+When a fire becomes underventilated, the yields of soot, carbon monoxide, or other product species change due to incomplete combustion.
+If the analysis of model results requires species concentrations, different species yields, a more complex chemical reaction, or finite-rate chemistry may be needed~\cite{FDS_Math_Guide}.
 The focus of this analysis is to examine the the effect on the flow conditions as a result of a interior door failure.
@@
 As a result, the actual fire may have been larger.
-However, as discusssed in this study, the fire used in the model produced interior conditions that were hazardous to fully protected firefighers.
+However, as discussed in this study, the fire used in the model produced interior conditions that were hazardous to fully protected firefighters.
 
@@
 &VENT XB=-14.5,-14,1,5,6.16,6.16, SURF_ID='FIRE' /
-&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/
-&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
+&VENT XB=-16.5,-15.5,1,2.5,3.14,3.14, 
+      SURF_ID='FIRE', DEVC_ID='SECOND FIRE'/
+&DEVC XYZ = -17.2,2,0, ID='SECOND FIRE', 
+      QUANTITY='TIME', SETPOINT=40, INITIAL_STATE=.FALSE. /
 \end{lstlisting}
@@
 In this study, the material properties of gypsum board~\cite{WAKILI2007} were specified on the finished walls and ceilings on the main two floors of the structure, and the material properties of wood~\cite{Incropera:1} were specified on the unfinished portions of the attic and rear porch.
-Note that the multi-component heat transfer that would typically occur in an exterior wall (gypusum, wood studs, insultation, exterior finish, air gaps) was simplified and respresented by a single material.
+Note that the multi-component heat transfer that would typically occur in an exterior wall (gypsum, wood studs, insulation, exterior finish, air gaps) was simplified and represented by a single material.
 The following lines define these materials in the FDS input file:
@@
 &MATL ID = 'WOOD MAT'
-    FYI = 'Incropera and DeWitt, Fundamentals of Heat and Mass Transfer'
+    FYI = 'Incropera and DeWitt, 
+          Fundamentals of Heat and Mass Transfer'
     CONDUCTIVITY = 0.12
@@
 Figure~\ref{fig:smv_ext_fire} shows flaming combustion through the failed window on the rear side of the structure and attic breach just after the second fire ignites at 40~s.
-Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that cofirms this type of fire behavoir.
+Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that confirms this type of fire behavior.
+As a fire becomes underventilated, the majority of the combustion internal to the structure occurs on the rear porch where there is sufficient oxygen.
+Despite the lack of oxygen in the attic, the wood would continue to pyrolyze due to the high heat fluxes, therefore continue to produce additional gas phase fuel \cite{SFPE:Heskestad}.
+In the attic, combustion occurred at the external vents as a lack of oxygen present prevented combustion.
 After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
@@
 At the time of the door failure (160~s), the HRR in both cases was approximately 9~MW because of the increased amount of ventilation.
-While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, with respect to exposure to firefighters operating within flow path, both cases presented similar high hazard contitions.
+While there might be some locally different burning characteristics between the baseline simulation and the alternative simulation, with respect to exposure to firefighters operating within flow path, both cases presented similar high hazard conditions.
 Therefore, the analysis will focus on the results of the baseline simulation.
@@
 \includegraphics[width=.5\textwidth]{../Figures/smv_exterior_fire}
-\includegraphics[width=.45\textwidth]{../Figures/PA020413}
+\includegraphics[width=.45\textwidth]{../Figures/PA020340}
 \caption{Smokeview rendering of exterior combustion occurring on the rear side of the structure (left) and photograph from ongoing attic fire experiments (right).}
@@
 Figure~\ref{fig:pres_159s} shows the calculated pressure conditions in the structure just before the interior door failed in the simulation.
-On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling from bouyancy due to temperature differences.
+On the rear porch, the pressure rise ranges from a 4~Pa ($5.8 \times 10^{-4}$~psi) over-pressure at a height of 1~m to greater than 10~Pa ($1.5 \times 10^{-3}$~psi) at the ceiling from buoyancy due to temperature differences.
 Gases at an elevated pressure will always move towards a region of lower pressure.The door serves as a boundary between the high and low pressure regions.

### 2015-09-01 Studies/2012_Chicago/Report/firetech_chicago.tex
Add files for FireTech pub

@@
 Figure~\ref{fig:smv_ext_fire} also shows a photograph taken during an attic fire experiment that confirms this type of fire behavior.
-As a fire becomes underventilated, the majority of the combustion internal to the structure occurs on the rear porch where there is sufficient oxygen.
-Despite the lack of oxygen in the attic, the wood would continue to pyrolyze due to the high heat fluxes, therefore continue to produce additional gas phase fuel \cite{SFPE:Heskestad}.
-In the attic, combustion occurred at the external vents as a lack of oxygen present prevented combustion.
-After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
+\textcolor{red}{As the fire becomes underventilated, the majority of the combustion internal to the structure occurs on the rear porch where there is sufficient oxygen.
+Despite the lack of oxygen in the attic, solid fuel would to pyrolyze due to the high internal temperatures and heat fluxes and therefore continue to produce additional gas phase fuel \cite{SFPE:Heskestad}.
+In the attic, combustion occurs at the external vents as a lack of oxygen present prevents combustion internal to the structure.} After additional wall breaches occur at 45~s and 55~s (see Table~\ref{tab:vents}), the abrupt change in ventilation causes the HRR to increase to 9~MW before it decreases to approximately 6~MW.
 The HRR then increases towards a sustainable steady-state value.

### 2015-09-01 Studies/2012_Chicago/Report/response2.tex
Add files for FireTech pub

\documentclass[12pt]{article}
\usepackage[pdftex]{graphicx}
\frenchspacing
\begin{document}

\section{Comments from Reviewer 1}
\begin{itemize}
\item I have had the experience that FDS completely extinguishes the internal flaming due to the lack of oxygen, burning *all* the fuel at the vents. Surely this is not realistic. If there were no flames inside, no pyrolzate would be produced to sustain the external flaming. I do not doubt the existence of external flaming, and the qualitative comparison to the attic fire experiments (Fig. 5) is indeed very good. But I would have liked the authors to elaborate a little bit more on the internal flaming (or the lack of it), and how this affected the temperature evolution inside. \\
{\it The authors have added text which explains that there is little burning internal to the attic in the model because of a lack of oxygen. At the attic level the burning is external to the structure. On the porch level there is sufficient oxygen penetration to support combustion internal to the structure. The authors agree that FDS does not allow for combustion to occur without oxygen, but all of the fuel is not burned. That is evident by the HRR curve which is analyzed over the domain of the model. The authors disagree with the reviewer's statement that if there were no flames, no pyrolzate would be produced. Pyrolosis does not require oxygen. High temperatures/heat fluxes will pyrolze a material - the presence of oxygen is what drives flaming combustion - phenomena that are appropriately modeled here.}

\end{itemize}

\section{Comments from Reviewer 4}
\begin{itemize}
\item  On p. 2, line 27 of the revised text document (this is revised text document pdf page 11), it reads ``Appendix ?? ...'' \\
{\it This was my error in Latex and been since fixed. Thank you. I am not highlighting the change in red on the updated document because the ?? should be fixed to a reference number.}
\end{itemize}

\end{document}

### 2015-09-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update Delco 2012

@@
 \flushright{
+Craig G. Weinschenk \\
+Keith M. Stakes \\
 Daniel Madrzykowski \\
-Keith M. Stakes \\
-Craig G. Weinschenk \\
 
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Distribution}
-% 	\caption{Collector Bins and Plastic Sheathing in Experimental Structures}
-% 	\label{fig:Spray_Density_Set_Up}
-% \end{figure}
-
 \subsection{Gas Cooling}
@@
 For these tests, a smooth bore nozzle was used.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
-% 	\caption{Hallway Nozzle Location for Fire Suppression Tests}
-% 	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
-% 	\caption{Room Nozzle Location for Fire Suppression Tests}
-% 	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
-% \end{figure}
 
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/burnbuilding}
-% 	\caption{Delaware County, PA Burn Building}
-% 	\label{fig:Delaware_County,_PA_Burn_Building}
-% \end{figure}
-
 \begin{figure}[!ht]
@@
 The ceiling of the burn room was the exposed ``floor assembly".
-The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum room.
+The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum board.
 The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 
-% \subsection{Mass}
-% \label{subsec:Mass}
-
-% \subsection{Moisture Content}
-% \label{subsec:Moisture_Content}
-
-% \subsection{Infrared Radiation}
-% \label{subsec:Infrared_Radiation}
-
-\subsection{Uncertainty}
+\subsection{Measurement Uncertainty}
 \label{subsec:Uncertainty}
@@
 The pallets ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs).
-The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Pallet_Fuel_Load}.
+The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Burn_Building_Fuel_Load}.
 Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition.
-Fig.~\ref{fig:Burn_Building_Fuel_Load}, provides dimensioned locations of the two stacks of pallets within the burn room.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/PalletFuelLoad}
-% 	\caption{Pallet Fuel Load}
-% 	\label{fig:Pallet_Fuel_Load}
-% \end{figure}
+Fig.~\ref{fig:Burn_Building_Fuel_Load}, also provides dimensioned locations of the two stacks of pallets within the burn room.
 
@@
 
-The fuel load for the experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
+The fuel load for these experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
@@
 \label{sec:fire_suppression_furniture_fuel}
+
+The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs.
 

### 2015-09-02 Projects/DelCo_2012/Scripts/water_plot.py

@@ -27,7 +27,7 @@ for f in os.listdir(data_dir):
 		# Strip test name from file name
 		test_name = f[:-4]
 		print 'Test ' + test_name
-		
+
 		# Load exp. data file
 		data = pd.read_csv(data_dir + f, header=0, index_col=0)
 
@@ -77,4 +77,4 @@ for f in os.listdir(data_dir):
 		z_data = np.nan_to_num(water_mass.flatten())
 		ax.bar3d(x_data, y_data, np.zeros(len(z_data)), dx, dy, z_data,zsort='max')
 		savefig('../Figures/Bars/' + test_name + '.pdf')
-		close('all')	
+		close('all'

### 2015-09-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco 2012

@@
 The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
-The total expanded uncertainty was estimated at $\pm$ 10 %.
+The total expanded uncertainty was estimated at $\pm$ 10~\%.
 
@@
 
-The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs.
+The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs, carpet, padding, and wood paneling along the southeast corner walls.
+An image of the fuel arrangement is shown in Fig.~\ref{fig:Furniture_Fuel_Load}.
+The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner.
+A chair is placed adjecent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
+In total, this fuel package contains approximately 336 kg of fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
+Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
 
@@
 		\midrule
-		2-seat New Sofa    &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame 	   &  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
-		           	 	   & \multirow{2}{*}{{Mattress}}	    & \multirow{2}{*}{{1 per sofa}}	& \multirow{2}{*}{\parbox{5cm} {Cover: 52~\% Polypropylene, 48~\% Polyester, Filling: 66~\% Polyester Fiber Pad, 34~\% Polyester Fiber  Batting}} & \multirow{2}{*}{{1.83 L X 1.21 W X 0.14 H}}  & \multirow{2}{*}{{14.6}}     \\
-		           	 	   &	            &               &                                                          		&                            	&             		& \\[.25cm]
-			           	   & Seat Cushion	& 2 per sofa	& 85~\% Urethane Foam, 15~\% Polyester Fiber   				    &  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
-		Blue Chair         &				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame   	    &  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
-		    			   & Seat Cushion   & 1 per chair   & 85~\% Urethane Foam, 15~\% Polyester Fiber					&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
-		Blue/Green Chair   & 				& 2				& 85~\% Urethane Foam, 15~\% Polyester Fiber, Wood Frame        &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
-		                   & Seat Cushion	& 1 per chair	& 85~\% Urethane Foam, 15~\% Polyester Fiber		            &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
-		Paneling           &				& 8 panels		& 3.2 mm thick medium density fiberboard                   		&  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
-		Carpeting          &				& 22.26 m$^2$	& 100~\% PET Polyester                  						&  3.68 L X 6.05 W  			&  1.44 kg/m$^2$	& 32.2 \\
-		Carpet Padding     &				& 22.26 m$^2$	& Polyurethane                 	 								&  3.68 L X 6.05 W X 11~mm H    &  0.89 kg/m$^2$    & 19.8 \\
+		2-seat Sofa        &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
+		           	 	   & Mattress	    & 1 per sofa	& Cover: 52~\% PP, 48~\% PET,                   &  1.83 L X 1.21 W X 0.14 H     &  14.6             & \\
+		           	 	   &                &               & Filling: 66~\% PET Pad, 34~\% PET Batting     &                               &                   & \\
+			           	   & Cushion    	& 2 per sofa	& 85~\% PU Foam, 15~\% PET Fiber   				&  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
+		Blue Chair         &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
+		    			   & Cushion        & 1 per chair   & 85~\% PU Foam, 15~\% PET Fiber				&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
+		Blue/Green Chair   & 				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame    &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
+		                   & Cushion    	& 1 per chair	& 85~\% PU Foam, 15~\% PET Fiber		        &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
+		Paneling           &				& 8 panels		& Medium density fiberboard                     &  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
+		Carpeting          &				& 22.3 m$^2$	& 100~\% PET                  					&  3.68 L X 6.05 W  			&  32.2				& 32.2 \\
+		Carpet Padding     &				& 22.3 m$^2$	& PU                       	 				    &  3.68 L X 6.05 W X 11~mm H    &  19.8			    & 19.8 \\
 		                   &                &               &                                               &                               & Total Mass        & 335.6 \\
@@
 \end{sidewaystable}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/SleeperSofa}
-% 	\caption{Sleeper Sofa}
-% 	\label{fig:Sleeper_Sofa}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/Mattress}
-% 	\caption{Mattress}
-% 	\label{fig:Mattress}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/BlueChair}
-% 	\caption{Blue Chair}
-% 	\label{fig:Blue_Chair}
-% \end{figure}
 
@@
 
-Spray density experiments were conducted by placing 2.5 ft$^2$ interlocking collector bins across the floor surface area of the burn rooms within each structure.
+Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure.
 The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
@@
 Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure.
-Table~\ref{tab:spray_density_tests} provides and overview of each individual experiment.
+Table~\ref{tab:spray_density_tests} provides an overview of each experiment.
 In the table, BB stands for the burn building tests while CS stands for the concrete structure tests.
@@
 \midrule
-BB1        &   120              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
-BB2        &   120              & 23            & Water  &  Solid Stream       &                    &          \\
-BB3        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
-BB4        &   120              &               & Water  &  Solid Stream       & 16                 &          \\
-BB5        &   120              & 20            & Water  &  Solid Stream       & 16                 &          \\
+BB1        &   123              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
+BB2        &   122              & 23            & Water  &  Solid Stream       &                    &          \\
+BB3        &   119              &               & Water  &  Solid Stream       & 16                 &          \\
+BB4        &   118              &               & Water  &  Solid Stream       & 16                 &          \\
+BB5        &   118              & 20            & Water  &  Solid Stream       & 16                 &          \\
 BB6        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
-BB7        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
-BB8        &   120              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\
+BB7        &   118              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
+BB8        &   119              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\
 BB9        &   120              & 24            & Water  &  30$^{\circ}$ fog   & 17~1/2             &          \\
-BB10       &   120              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\
+BB10       &   127              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\
 BB11       &   120              & 22            & Water  &  Solid 7/8~in slug  & 11~1/2             &          \\
-BB12       &   120              & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
-BB13       &   120              & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB14       &   120              & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB15       &   120              & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB16       &   120              &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
-BB17       &   120              & 20            & CAF    &  Solid Stream narrow & 15                &          \\
-BB18       &   120              & 10            & CAF    &  Solid Stream mid   &                    &          \\
-BB19       &   120              & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
-BB20       &   120              &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
-BB21       &   120              &               & CAF    &  Solid Stream back  &                    &          \\
-CS1        &   115,75           &               & Water  &  Solid Stream       &                    &          \\
-CS2        &   120,115          & 18            & Water  &  Solid Stream       &                    &          \\
+BB12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
+BB13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
+BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
+BB17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream narrow & 15                &          \\
+BB18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream mid   &                    &          \\
+BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
+BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
+BB21       &   120 / 60cfm      &               & CAF    &  Solid Stream back  &                    &          \\
+CS1        &   115              & 7             & Water  &  Solid Stream       &                    &          \\
+CS2        &   115              & 18            & Water  &  Solid Stream       &                    &          \\
 CS3        &   120              & 19            & Water  &  Solid Stream       &                    &          \\
-CS4        &   120,118          & 21            & Water  &  Solid Stream       &                    &          \\
-CS5        &   120,118          & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS6        &   120,118          & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS7        &   120,124          & 15            & Water  &  Solid 7/8~in slug  &                    &          \\
-CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  &                    &          \\
-CS8        &   120,116          & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS9        &   120,116          & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS10       &   120,116          & 16            & Water  &  Solid Stream       &                    &          \\
-CS11       &   120,117          & 16            & Water  &  Solid Stream       &                    &          \\
+CS4        &   118              & 21            & Water  &  Solid Stream       &                    &          \\
+CS5        &   118              & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS6        &   118              & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS7        &   125              & 16            & Water  &  Solid 7/8~in slug  &                    &          \\
+CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  & 18                 &          \\
+CS8        &   116              & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS9        &   116              & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS10       &   116              & 16            & Water  &  Solid Stream       &                    &          \\
+CS11       &   117              & 16            & Water  &  Solid Stream       &                    &          \\
 \bottomrule[1.25pt]

### 2015-09-03 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco 2012 writeup

@@
 
-After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution. Figure~\ref{fig:Burn_Building_Test_1} shows that the majority of the
+After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution.
+Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf.
+Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
+Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distrubtion of water is far more dispered around the gas cooling room.
+The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB2}
-	\caption{Burn Building Test 2}
-	\label{fig:Burn_Building_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB3}
-	\caption{Burn Building Test 3}
-	\label{fig:Burn_Building_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB4}
-	\caption{Burn Building Test 4}
-	\label{fig:Burn_Building_Test_4}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB5}
-	\caption{Burn Building Test 5}
-	\label{fig:Burn_Building_Test_5}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB6}
-	\caption{Burn Building Test 6}
-	\label{fig:Burn_Building_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=4in]{../Figures/Bars/BB7}
@@
 	\label{fig:Burn_Building_Test_7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB8}
-	\caption{Burn Building Test 8}
-	\label{fig:Burn_Building_Test_8}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB9}
-	\caption{Burn Building Test 9}
-	\label{fig:Burn_Building_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB10}
-	\caption{Burn Building Test 10}
-	\label{fig:Burn_Building_Test_10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB11}
-	\caption{Burn Building Test 11}
-	\label{fig:Burn_Building_Test_11}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB12}
-	\caption{Burn Building Test 12}
-	\label{fig:Burn_Building_Test_12}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB13}
-	\caption{Burn Building Test 13}
-	\label{fig:Burn_Building_Test_13}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB14}
-	\caption{Burn Building Test 14}
-	\label{fig:Burn_Building_Test_14}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB15}
-	\caption{Burn Building Test 15}
-	\label{fig:Burn_Building_Test_15}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB16}
-	\caption{Burn Building Test 16}
-	\label{fig:Burn_Building_Test_16}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB17}
-	\caption{Burn Building Test 17}
-	\label{fig:Burn_Building_Test_17}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB18}
-	\caption{Burn Building Test 18}
-	\label{fig:Burn_Building_Test_18}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB19}
-	\caption{Burn Building Test 19}
-	\label{fig:Burn_Building_Test_19}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB20}
-	\caption{Burn Building Test 20}
-	\label{fig:Burn_Building_Test_20}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB21}
-	\caption{Burn Building Test 21}
-	\label{fig:Burn_Building_Test_21}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_1}
-	\caption{Experimental Structures Test 1}
-	\label{fig:Experimental_Structures_Test_1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_2}
-	\caption{Experimental Structures Test 2}
-	\label{fig:Experimental_Structures_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_3}
-	\caption{Experimental Structures Test 3}
-	\label{fig:Experimental_Structures_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_4}
-	\caption{Experimental Structures Test 4}
-	\label{fig:Experimental_Structures_Test_4}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_5}
-	\caption{Experimental Structures Test 5}
-	\label{fig:Experimental_Structures_Test_5}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_6}
-	\caption{Experimental Structures Test 6}
-	\label{fig:Experimental_Structures_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_7}
-	\caption{Experimental Structures Test 7}
-	\label{fig:Experimental_Structures_Test_7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_72}
-	\caption{Experimental Structures Test 7.2}
-	\label{fig:Experimental_Structures_Test_7.2}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_8}
-	\caption{Experimental Structures Test 8}
-	\label{fig:Experimental_Structures_Test_8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_9}
-	\caption{Experimental Structures Test 9}
-	\label{fig:Experimental_Structures_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_10}
-	\caption{Experimental Structures Test 10}
-	\label{fig:Experimental_Structures_Test_10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_11}
-	\caption{Experimental Structures Test 11}
-	\label{fig:Experimental_Structures_Test_11}
 \end{figure}
@@
 
+\chapter{Spray Denisty Figures}
+\label{app:spray_density}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB2}
+	\caption{Burn Building Test 2}
+	\label{fig:Burn_Building_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB3}
+	\caption{Burn Building Test 3}
+	\label{fig:Burn_Building_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB4}
+	\caption{Burn Building Test 4}
+	\label{fig:Burn_Building_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB5}
+	\caption{Burn Building Test 5}
+	\label{fig:Burn_Building_Test_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB6}
+	\caption{Burn Building Test 6}
+	\label{fig:Burn_Building_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB8}
+	\caption{Burn Building Test 8}
+	\label{fig:Burn_Building_Test_8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB9}
+	\caption{Burn Building Test 9}
+	\label{fig:Burn_Building_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB10}
+	\caption{Burn Building Test 10}
+	\label{fig:Burn_Building_Test_10}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB11}
+	\caption{Burn Building Test 11}
+	\label{fig:Burn_Building_Test_11}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB12}
+	\caption{Burn Building Test 12}
+	\label{fig:Burn_Building_Test_12}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB13}
+	\caption{Burn Building Test 13}
+	\label{fig:Burn_Building_Test_13}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB14}
+	\caption{Burn Building Test 14}
+	\label{fig:Burn_Building_Test_14}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB15}
+	\caption{Burn Building Test 15}
+	\label{fig:Burn_Building_Test_15}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB16}
+	\caption{Burn Building Test 16}
+	\label{fig:Burn_Building_Test_16}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB17}
+	\caption{Burn Building Test 17}
+	\label{fig:Burn_Building_Test_17}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB18}
+	\caption{Burn Building Test 18}
+	\label{fig:Burn_Building_Test_18}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB19}
+	\caption{Burn Building Test 19}
+	\label{fig:Burn_Building_Test_19}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB20}
+	\caption{Burn Building Test 20}
+	\label{fig:Burn_Building_Test_20}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB21}
+	\caption{Burn Building Test 21}
+	\label{fig:Burn_Building_Test_21}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_1}
+	\caption{Experimental Structures Test 1}
+	\label{fig:Experimental_Structures_Test_1}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_2}
+	\caption{Experimental Structures Test 2}
+	\label{fig:Experimental_Structures_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_3}
+	\caption{Experimental Structures Test 3}
+	\label{fig:Experimental_Structures_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_4}
+	\caption{Experimental Structures Test 4}
+	\label{fig:Experimental_Structures_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_5}
+	\caption{Experimental Structures Test 5}
+	\label{fig:Experimental_Structures_Test_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_6}
+	\caption{Experimental Structures Test 6}
+	\label{fig:Experimental_Structures_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_7}
+	\caption{Experimental Structures Test 7}
+	\label{fig:Experimental_Structures_Test_7}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_72}
+	\caption{Experimental Structures Test 7.2}
+	\label{fig:Experimental_Structures_Test_7.2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_8}
+	\caption{Experimental Structures Test 8}
+	\label{fig:Experimental_Structures_Test_8}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_9}
+	\caption{Experimental Structures Test 9}
+	\label{fig:Experimental_Structures_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_10}
+	\caption{Experimental Structures Test 10}
+	\label{fig:Experimental_Structures_Test_10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_11}
+	\caption{Experimental Structures Test 11}
+	\label{fig:Experimental_Structures_Test_11}
+\end{figure}
+
 \end{document}

### 2015-09-09 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: edited hose stream report

@@
 \label{sec:Instrumentation}
-Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}.
 There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
@@
 Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure.
+To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses.
+Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}.
 A single thermocouple was attached to each bi-directional probe.
@@
 
-% \subsection{Cold Flow Experimental Procedure}
-% \label{sec:Cold_Flow_Procedure}
-
-% \subsection{Water Flow Experimental Procedure}
-% \label{sec:Water_Flow_Procedure}
 A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure.
@@
 
-\subsubsection{Monitor Experiments}
+\subsection{Monitor Experiments}
 \label{sec:Water_Flow_Monitor_Procedure}
-A total of five sets of experiments were conducted using a monitor with a combination nozzle to flow water.
-Three of the tests (Tests 29, 30, and 33) occurred in the East Structure and two of the tests (Tests 16 and 17) occurred in the West Structure.
+Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in the straight, narrow fog, and wide fog stream patterns.
+One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.
 
-Tests 29 and 30 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a monitor equipped with a combination nozzle.
-A schematic of the structure's layout during the two tests is presented in Fig.~\ref{fig:test_29-32_setup}.
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C, as pictured in Fig.~\ref{fig:test_29_30_pic}.
-After 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed, and the water flow was stopped.
-The monitor was adjusted so the nozzle was aimed at Door BC.
-Then, water flow began and after 30 seconds had elapsed, the south side door was opened for 30 seconds and then closed and the water flow was stopped.
-This entire procedure was repeated an additional time.
-A straight stream pattern was used during Test 29 and a narrow fog stream pattern was used during Test 30.
-
-\begin{figure}[!ht]
-\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_29-32}
-	\put(83,24){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
-\end{overpic}
-\caption[East Structure Layout for Tests 29-32]{East Structure layout for Tests 29-32}
-\label{fig:test_29-32_setup}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/East_monitor_C_BC.pdf}
-\caption[Straight Stream and Narrow Fog Stream during Tests 29 and 30]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and at Door BC (bottom row) during Tests 29 and 30}
-\label{fig:test_29_30_pic}
-\end{figure}
-\FloatBarrier
-
-Test 33 varied from Tests 29 and 30 in multiple ways.
-During Test 33, the monitor was located inside Room C and aimed at the ceiling of Room B, as shown in Fig.~\ref{fig:test_33_pic}.
-A schematic of the structure's layout during Test 33 is presented in Fig.~\ref{fig:test_33_34_setup}.
-The test began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
+Test 33 involved flowing water using a monitor equipped with a combination nozzle from Room C to the ceiling of Room B in the East Structure (Fig.~\ref{fig:test_33_pic}).
+A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
+Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
 Then, the south side door was opened and each stream was applied for 30 seconds again.
@@
 
-%ADD TARGET DIMENSION%
+% Add flow chart? %
 Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
-The nozzle was aimed at two targets throughout the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall, and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
+The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
 The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
@@
 
-\subsubsection{Handline Experiments}
+\subsection{Handline Experiments}
 \label{sec:Water_Flow_Handline_Procedure}
-A total of five sets of experiments were conducted using a 1.75" handline with a combination nozzle to flow water.
-Three of the tests (Tests 31, 32, and 34) occurred in the East Structure and two of the tests (Tests 18 and 19) occurred in the West Structure.
+Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water.
+One test series, Test 34, occurred in the East Structure, and the two other series, Tests 18 and 19, occurred in the West Structure.
 
-Tests 31 and 32 followed an identical procedure that involved flowing water from the north side double doors of the East Structure using a combination nozzle attached to a 1.75" handline.
-The structure's layout during both tests was identical to the layout used in Tests 29 and 30 (Fig.~\ref{fig:test_29-32_setup}).
-Each test began by flowing water with the nozzle aimed at the ceiling of Room C in a fixed position, as pictured in Fig.~\ref{fig:test_31_32_pic}.
-After 30 seconds had elapsed, the nozzle was rotated in the clockwise direction for 30 seconds and then returned to the fixed position for 30 seconds.
-Next, the nozzle was rotated in the counterclockwise direction for 30 seconds and then returned to the fixed position for 30 seconds.
-While the nozzle was in the fixed position, the south side door was opened and the application patterns were repeated.
-After the patterns were applied with the south side door opened, the door was closed, and the process was repeated with the handline aimed at Door BC.
-The entire procedure was then repeated an additional time.
-A straight stream pattern was used during Test 31 and a narrow fog stream pattern was used during Test 32.
+Test 34 involved flowing water using a 1.75" handline equipped with a combination nozzle located inside Room C.
+A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
+The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}.
+Next, the nozzle was rotated in the clockwise direction for 30 seconds.
+Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
+This process were repeated for narrow fog and wide fog streams.
+Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.
 
@@
 \end{figure}
-\clearpage
-
-Test 34 varied from Tests 31 and 32 in multiple ways.
-During Test 34, the handline was located inside Room C.
-The structure's layout during Test 34 was identical to the layout used in Test 33 (Fig.~\ref{fig:test_33_34_setup}).
-The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}.
-Next, the nozzle was rotated in the clockwise direction for 30 seconds.
-Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
-This process were repeated for narrow fog and wide fog streams.
-Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.
 
@@
 
-%Where was the handline aimed?%
+% Where was the handline aimed? Add flow chart? %
 Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline.
@@
 
-\section{Water Flow Test Results}
-\label{sec:Water_Flow_Test_Results}
+\section{Monitor Nozzle Experiments}
+\label{sec:monitor_results}
 
-\subsection{Monitor Nozzle Experiments}
-
-Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and Fig.~\ref{fig:Test_16_BDP_A13_Avg_All} contain plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) and \nth{2} level, north side, west double doorway (A13), respectively, for Test 16.
-A similar set of plots was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.
+Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
+A similar figure was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
-\caption{Average Velocity through Stairwell Door, Test 16, All Streams}
-\label{fig:Test_16_BDP_A10_Avg_All}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A13_Avg}
-\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 16, All Streams}
-\label{fig:Test_16_BDP_A13_Avg_All}
-\end{figure}
+% \begin{figure}[!ht]
+% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
+% \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
+% \label{fig:Test_16_BDP_A10_Avg_All}
+% \end{figure}
 
 \clearpage
-
-%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}[!ht]
-%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations for Tests 16 and 17}
-%\begin{tabular}{|l|c|c|c|c|}
-%\cline{2-5}
-%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
-%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
-%\textit{Straight} & 
-%%%%%Test 16%%%% 
-%0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
-%%%%%Test 17%%%% 
-%0.7 $\pm 0.1$ & 0.7 $\pm 0.2$ \\ \hline
-%\textit{Narrow Fog} & 
-%%%%%Test 16%%%% 
-%1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
-%%%%%Test 17%%%% 
-%0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $ \\ \hline
-%\textit{Wide Fog} 	& 
-%%%%%Test 16%%%% 
-%1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
-%%%%%Test 17%%%% 
-%0.9 $\pm 0.2$ & 0.7 $\pm 0.2$ \\ \hline
-%\end{tabular}
-%\label{table:Tests_16_17_BDP_A10_Avgs}
-%\end{table}
-
-%code for higher resolution in tabulated values
-%\textit{Straight} & 0.84 & 0.94 & 0.73 & 0.69 \\ \hline
-%\textit{Narrow Fog} & 1.41 & 1.00 & 0.75 & 0.75 \\ \hline
-%\textit{Wide Fog} & 1.23 & 1.37 & 0.88 & 0.71 \\ \hline
-
-%\begin{table}[!ht]
-%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations for Tests 16 and 17}
-%\begin{tabular}{|l|c|c|c|c|}
-%\cline{2-5}
-%\multicolumn{1}{c|}{} & \multicolumn{2}{c|}{Test 16} & \multicolumn{2}{c|}{Test 17} \\ \hline
-%\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\ \hline
-%\textit{Straight} 	& 
-%%%%%Test 16%%%% 
-%2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
-%%%%%Test 17%%%% 
-%2.7 $\pm 0.4$ & 2.3 $\pm 0.8$ \\ \hline
-%\textit{Narrow Fog} & 
-%%%%%Test 16%%%% 
-%4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
-%%%%%Test 17%%%% 
-%2.6 $\pm 0.6$ & 2.7 $\pm 0.6$ \\ \hline
-%\textit{Wide Fog} 	& 
-%%%%%Test 16%%%% 
-%3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
-%%%%%Test 17%%%% 
-%3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ \\ \hline
-%\end{tabular}
-%\label{table:Tests_16_17_BDP_A13_Avgs}
-%\end{table}
-
-%code for higher resolution in tabulated values
-%\textit{Straight} 	& 2.82 & 3.10 & 2.66 & 2.33 \\ \hline
-%\textit{Narrow Fog} & 4.39 & 3.26 & 2.58 & 2.68 \\ \hline
-%\textit{Wide Fog} 	& 3.92 & 4.37 & 3.14 & 2.76 \\ \hline
 
@@
 
-\begin{table}[!ht]
-\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
-\begin{tabular}{lcccc}
-\toprule
- & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
-\\
-\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
-\midrule
-\textit{Straight} & 
-%%%%Test 16%%%% 
-2.8 $\pm 0.6$ & 3.1 $\pm 0.5$ & 
-%%%%Test 17%%%% 
-2.7 $\pm 0.4$ & 2.3 $\pm 0.8$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 16%%%% 
-4.4 $\pm 0.3$ & 3.3 $\pm 0.4$ & 
-%%%%Test 17%%%% 
-2.6 $\pm 0.6$ & 2.7 $\pm 0.6$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%%Test 16%%%% 
-3.9 $\pm 0.5$ & 4.4 $\pm 0.3$ & 
-%%%%Test 17%%%% 
-3.1 $\pm 0.7$ & 2.8 $\pm 0.7$ 
-\\ 
-\bottomrule
-\end{tabular}
-\label{table:Tests_16_17_BDP_A13_Avgs}
-\end{table}
-
-\subsection{Handline Experiments}
+\section{Handline Experiments}
+\label{sec:handline_results}
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
-\caption{Average Velocity through Stairwell Door, Test 18, All Streams}
-\label{fig:Test_18_BDP_A10_Avg_All}
-\end{figure}
+% \begin{figure}[!ht]
+% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
+% \caption{Average Velocity through Stairwell Door, Test 18, All Streams}
+% \label{fig:Test_18_BDP_A10_Avg_All}
+% \end{figure}
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 18, All Streams}
-\label{fig:Test_18_BDP_A13_Avg_All}
-\end{figure}
+% \clearpage
 
-\clearpage
+% \begin{figure}[!ht]
+% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
+% \caption{Average Velocity through Stairwell Door, Test 19, All Streams}
+% \label{fig:Test_19_BDP_A10_Avg_All}
+% \end{figure}
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
-\caption{Average Velocity through Stairwell Door, Test 19, All Streams}
-\label{fig:Test_19_BDP_A10_Avg_All}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 19, All Streams}
-\label{fig:Test_19_BDP_A13_Avg_All}
-\end{figure}
-
-\clearpage
+% \clearpage
 
@@
 Tables~\ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} contain the average air velocity measured by the eight BDPs at the stairwell door and \nth{2} level, double door, respectively, during the time the flow path was complete for each application pattern and hose stream combination used during Tests 18 and 19.
-
-%%%%%%%%%%%%%%%%%%%%%%% ORIGINAL TABLES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\begin{table}[!ht]
-%\addtolength{\tabcolsep}{-3.25pt}
-%\small
-%\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
-%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-%\cline{2-9}
-%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
-%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\textit{Straight} 	& 
-%%%%%Test 18%%%% 
-%-0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ & 
-%%%%%Test 19%%%% 
-% 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ \\ \hline
-%\textit{Narrow Fog} & 
-%%%%%Test 18%%%% 
-% 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ & 
-%%%%%Test 19%%%% 
-% 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$ \\ \hline
-%\textit{Wide Fog} 	& 
-%%%%%Test 18%%%% 
-% 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ & 
-%%%%%Test 19%%%% 
-% 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$ \\ \hline
-%\end{tabular}
-%\label{table:Tests_18_19_BDP_A10_Avgs}
-%\end{table}
-%
-%%code to increase resolution of tabulated values
-%%\textit{Straight} 	& -0.17 & 0.48 & 0.65 & 0.63 & -0.05 & 0.47 & 0.67 & 0.62 \\ \hline
-%%\textit{Narrow Fog} & 0.41 & 1.02 & 0.79 & 0.99 & 1.23 & 1.18 & 1.14 & 1.22 \\ \hline
-%%\textit{Wide Fog} 	& 0.93 & 0.90 & 0.91 & 0.75 & 0.96 & 0.67 & 0.89 & 0.93 \\ \hline
-%
-%\begin{table}[!ht]
-%\addtolength{\tabcolsep}{-3.25pt}
-%\small
-%\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
-%\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
-%\cline{2-9}
-%\multicolumn{1}{c|}{} & \multicolumn{4}{c|}{Test 18} & \multicolumn{4}{c|}{Test 19} \\ \hline
-%\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} \\ \hline
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%\textit{Straight}  &
-%%%%%Test 18%%%% 
-%-0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$ &
-%%%%%Test 19%%%%					
-% 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ \\ \hline
-%\textit{Narrow Fog} & 
-%%%%%Test 18%%%%
-% 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$ & 
-%%%%%Test 19%%%%
-% 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$ \\ \hline
-%\textit{Wide Fog} 	& 
-%%%%%Test 18%%%%
-%3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$ & 
-%%%%%Test 19%%%%
-%3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$ \\ \hline
-%\end{tabular}
-%\label{table:Tests_18_19_BDP_A13_Avgs}
-%\end{table}
-%
-%%code to increase resolution of tabulated values
-%%\textit{Straight} 	& -0.43 & 1.75 & 2.46 & 2.40 & 0.20 & 1.60 & 2.47 & 2.10 \\ \hline
-%%\textit{Narrow Fog} & 1.34 & 3.61 & 2.55 & 3.48 & 4.26 & 3.48 & 3.49 & 3.66 \\ \hline
-%%\textit{Wide Fog} 	& 3.02 & 3.22 & 3.06 & 2.57 & 3.31 & 2.60 & 3.13 & 3.19 \\ \hline
 
@@
 
-\begin{table}[!ht]
-%\addtolength{\tabcolsep}{-3.25pt}
-%\small
-\caption{Average air velocity (m/s) through \nth{2} level double door for all hose stream and application pattern combinations for Tests 18 and 19}
-\begin{tabular}{lcccc}
-\toprule
- & \multicolumn{4}{c}{\underline{Test 18}}
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\
-\midrule 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textit{Straight}  &
-%%%%Test 18%%%% 
--0.4 $\pm 1.3$ & 1.8 $\pm 1.1$ & 2.5 $\pm 1.1$ & 2.4 $\pm 0.8$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 18%%%%
- 1.3 $\pm 1.1$ & 3.6 $\pm 0.9$ & 2.6 $\pm 0.8$ & 3.5 $\pm 1.6$
- \\	\multicolumn{5}{c}{}	\\ 
-\textit{Wide Fog} 	& 
-%%%%Test 18%%%%
-3.0 $\pm 0.7$ & 3.2 $\pm 1.0$ & 3.1 $\pm 1.1$ & 2.6 $\pm 1.3$
-\\
-\midrule
- & \multicolumn{4}{c}{\underline{Test 19}}	\\ 
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\
-\midrule
-\textit{Straight}  &
-%%%%Test 19%%%%					
- 0.2 $\pm 0.7$ & 1.6 $\pm 0.5$ & 2.5 $\pm 0.7$ & 2.1 $\pm 0.7$ 
- \\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 19%%%%
- 4.3 $\pm 1.0$ & 3.5 $\pm 1.0$ & 3.5 $\pm 1.5$ & 3.7 $\pm 0.9$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%%Test 19%%%%
-3.3 $\pm 0.7$ & 2.6 $\pm 0.6$ & 3.1 $\pm 0.6$ & 3.2 $\pm 0.5$
-\\
-\bottomrule
-\end{tabular}
-\label{table:Tests_18_19_BDP_A13_Avgs}
-\end{table}
-
 Notice, there is a significant difference between the average air velocity caused by the fixed straight stream and the velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.
@@
 %\clearpage
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A13_Avg_CW_vs_CCW}
-%\caption{Average Velocity of \nth{2} Level Double Door, Test 18, All Streams, CW vs. CCW}
-%\label{fig:Test_18_BDP_A13_Avg_CW_vs_CCW}
-%\end{figure}
-%
-%\clearpage
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A13_Avg_CW_vs_CCW}
-%\caption{Average Velocity of \nth{2} Level Double Door, Test 19, All Streams, CW vs. CCW}
-%\label{fig:Test_19_BDP_A13_Avg_CW_vs_CCW}
-%\end{figure}
-%
-%\clearpage
 
@@
 \label{chap:Conclusions}
+\begin{enumerate}
+\item Any movement of the hose stream increases the air flow through the structure
+\item NF and WF move significantly more air than SS
+\item No difference between rotating hose CW or CCW
+\end{enumerate}
 
@@
 \label{chap:Future_Work}
+Need to determine if air movement caused by hose streams has significant impact on flow path and fire development in involved structure
+
+compare to cold flow tests?
 
@@
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through Stairwell Door, Test 17, All Streams}
-\label{fig:Test_17_BDP_A10_Avg_All}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A13_Avg}
-\caption{Average Velocity through \nth{2} Level, North Side, West Double Door, Test 17, All Streams}
-\label{fig:Test_17_BDP_A13_Avg_All}
-\end{figure}
-
 \clearpage

### 2015-09-14 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py
Delco_2014: updated hose test script to produce code for specific LaTeX tables, edited report

@@ -1,10 +1,12 @@
 #!/usr/bin/env python
 
 import os
+import collections
 import numpy as np
 import pandas as pd
 from pylab import *
 import math
+from itertools import cycle
 
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
@@ -57,8 +59,13 @@ gas_quantities = ['CO_', 'CO2_', 'O2_']
 
 # Load exp. timings, description, and averages file
 timings = pd.read_csv(timings_file, index_col=0)
-desired_tests = list(timings.columns.values)			# creates list of  column headers which correspond
-hose_info = pd.read_csv(hose_info_file, index_col=0) 	# to desired tests listed in All_Hose_Time.csv file
+desired_tests = []			
+for name in list(timings.columns.values):				# creates list of  column headers which correspond
+	if 'HOSE_D' in name:								# to desired tests listed in All_Hose_Times.csv file
+		continue
+	else:
+		desired_tests.append(name)
+hose_info = pd.read_csv(hose_info_file, index_col=0)
 info = pd.read_csv(info_file, index_col=3)
 
 # Files to skip
@@ -75,6 +82,17 @@ def movingaverage(interval, window_size):
 # Convert voltage to pascals
 conv_inch_h2o = 0.4
 conv_pascal = 248.8
+
+# Create lists for column titles for desired latex tables
+streams = ['SS', 'NF', 'WF']
+stream_ls = pd.Series(['\\textit{Straight}', '\\textit{Narrow Fog}', '\\textit{Wide Fog}'], index = streams)
+west_hand_caption = 'Average air velocity (m/s) through stairwell door with fully established flow path for stream and pattern combinations during Tests 18 and 19'
+west_hand_label = 'table:west_hand_A10_avgs'
+west_mon_columns = ['\\textbf{Stream}', '\\textbf{Near}', '\\textbf{Far}', '\\textbf{Near}', '\\textbf{Far}']
+west_hand_columns = ['\\textbf{Stream}', '\\textbf{Fixed}', '\\textbf{Sweeping}', '\\textbf{Clockwise}', '\\begin{tabular}{@{}c@{}} \\textbf{Counter} \\\ \\textbf{Clockwise} \\\ \\end{tabular}']
+# east_mon_columns = 
[…]

### 2015-09-14 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
Delco_2014: updated hose test script to produce code for specific LaTeX tables, edited report
remove pdf, update tex file and add ignore file

@@
 
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
+\headerB{
+Impact of Hose Streams on Air Flows inside a Structure
+}
+
+\headerC{
+{
+\flushright{
+Joseph Willi \\
+Daniel Madrzykowski \\
+Craig G. Weinschenk \\
+
+\vspace*{2\baselineskip}
+
+\begingroup
+This publication is available free of charge from:
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\endgroup
+}
+
+\vfill
+
+\flushright{
+
+\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
+}
+}
+}
+
+\end{minipage}
+
+\newpage
+\hspace{5in}
+\newpage
+
+\frontmatter
+
+\pagenumbering{roman}
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
 \headerB{
@@
 \flushright{
+Joseph Willi \\
 Daniel Madrzykowski \\
 Craig G. Weinschenk \\
-Kristopher J. Overholt \\
 {\em Fire Research Division \\
-Engineering Laboratory \\
-Gaithersburg, Maryland, USA} \\ }
-}
+Engineering Laboratory} \\
 
-\flushright{\today \\
-}
+\vspace*{2\baselineskip}
+
+\begingroup
+This publication is available free of charge from:
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
+
+\vspace*{2\baselineskip}
+September 2015}}
 
@@
 
-\flushright{
-\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
+\flushright{\includegraphics[width=1in]{../../../../../Bibliography/doc} }
+
+\titlesigs
+
+\end{minipage}
+
+\newpage
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
+document in order to describe an experimental procedure or concept adequately. \\
+Such identification is not intended to imply recommendation or endorsement by the \\
+National Institute of Standards and Technology, nor is it intended to imply that the \\
+entities, materials, or equipment are necessarily the best available for the purpose. \\
 }
 
-\titlesigs
+\vspace{3in}
+
+\large
+\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2015) \\
+% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+CODEN: NTNOEF }
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\endgroup
+
+\vfill
+
+\hspace{1in}
 
@@
 
+\begin{table}[!ht]
+\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and pattern combinations during Tests 18 and 19}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{4}{c}{\underline{Test 18}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
+\\ \multicolumn{5}{c}{} \\
+\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
+\\ \midrule
+ & \multicolumn{4}{c}{\underline{Test 19}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
+\\ \bottomrule
+\end{tabular}
+\label{table:west_hand_A10_avgs}
+\end{table}
+
 Notice, there is a significant difference between the average air velocity caused by the fixed straight stream and the velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.

### 2015-09-14 Projects/DelCo_2012/Report/DelCo_2012.tex
update report and plotting script

@@
 \flushright{
+Craig G. Weinschenk \\
+Keith M. Stakes \\
 Daniel Madrzykowski \\
-Keith M. Stakes \\
-Craig G. Weinschenk \\
 {\em Fire Research Division \\
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2014) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2015) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 
-% \begin{sidewaystable}[!ht]
-% 	\centering
-% 	\caption{Temperature Comparison}
-% 	\begin{tabular}{ll}
-% 		\hline\noalign{\smallskip}
-% 		Temperature				 & Response		\\
-% 		\noalign{\smallskip}\hline\noalign{\smallskip}
-% 		37 deg C (98.6 deg F)    &  Normal human oral/body temperature      \\
-% 		44 deg C (111 deg F)   	 & Human skin begins to feel pain     \\
-% 		48 deg C (118 deg F) 	 & Human skin receives a first degree burn injury      \\
-% 		55 deg C (131 deg F)     & Human skin receives a second degree burn injury    \\
-% 		62 deg C (140 deg F)     & A phase where burned human tissue becomes numb    \\
-% 		72 deg C (162 deg F)     & Human skin instantly destroyed     \\
-% 		100 deg C (212 deg F)    & Water boils and produces steam    \\
-% 		140 deg C (284 deg F)    & Glass transition temperature of polycarbonate (SCBA Facepieces)      \\
-% 		230 deg C (446 deg F)    & Melting temperature of polycarbonate (SCBA Facepieces)    \\
-% 		250 deg C (482 deg F)    & Charring of natural cotton begins     \\
-% 		>300 deg C (>572 deg F)  & Charring of modern protective clothing fabrics begins    \\
-% 		>600 deg C (>1112 deg F) & Temperatures inside a post-flashover compartment fire     \\
-% 		\noalign{\smallskip}\hline
-% 	\end{tabular}
-% 	\label{tab:Temperature_Comparison}
-% \end{sidewaystable}
-
-% \begin{sidewaystable}[!ht]
-% 	\centering
-% 	\caption{Heat Flux Comparison}
-% 	\begin{tabular}{ll}
-% 		\hline\noalign{\smallskip}
-% 		Heat Flux	  				   & Response		\\
-% 		\noalign{\smallskip}\hline\noalign{\smallskip}
-% 		1 kW/m\textsuperscript{2}      & Sunny day      \\
-% 		2.5 kW/m\textsuperscript{2}    & Typical firefighter exposure     \\
-% 		3-5 kW/m\textsuperscript{2}    & Pain to skin within seconds      \\
-% 		20 kW/m\textsuperscript{2}     & Threshold flux to floor at flashover onset    \\
-% 		84 kW/m\textsuperscript{2}     & Thermal Protection Performance (TPP) test    \\
-% 		60-200 kW/m\textsuperscript{2} & Flames over surface     \\
-% 		\noalign{\smallskip}\hline
-% 	\end{tabular}
-% 	\label{tab:Heat_Flux_Comparison}
-% \end{sidewaystable}
-
 \section{Spray Density}
@@
 BB5        &   118              & 20            & Water  &  Solid Stream       & 16                 &          \\
-BB6        &   120              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
-BB7        &   118              & 21            & Water  &  30$^{\circ}$ fog   & 15                 &          \\
-BB8        &   119              & 22            & Water  &  30$^{\circ}$ fog   & 17                 &          \\
-BB9        &   120              & 24            & Water  &  30$^{\circ}$ fog   & 17~1/2             &          \\
-BB10       &   127              & 20            & Water  &  Solid 7/8~in slug  & 12~1/2             &          \\
-BB11       &   120              & 22            & Water  &  Solid 7/8~in slug  & 11~1/2             &          \\
+BB6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
+BB7        &   118              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
+BB8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & 17                 &          \\
+BB9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & 17~1/2             &          \\
+BB10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & 12~1/2             &          \\
+BB11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & 11~1/2             &          \\
 BB12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
@@
 BB15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
+BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
 BB17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream narrow & 15                &          \\
 BB18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream mid   &                    &          \\
-BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ fog   & 15                 &          \\
-BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ fog   & 17                 &          \\
+BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
+BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 17                 &          \\
 BB21       &   120 / 60cfm      &               & CAF    &  Solid Stream back  &                    &          \\
@@
 CS4        &   118              & 21            & Water  &  Solid Stream       &                    &          \\
-CS5        &   118              & 22            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS6        &   118              & 19            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS7        &   125              & 16            & Water  &  Solid 7/8~in slug  &                    &          \\
-CS7.2      &   120              & 17            & Water  &  Solid 7/8~in slug  & 18                 &          \\
-CS8        &   116              & 15            & Water  &  30$^{\circ}$ fog   &                    &          \\
-CS9        &   116              & 16            & Water  &  30$^{\circ}$ fog   &                    &          \\
+CS5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &                    &          \\
+CS6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &                    &          \\
+CS7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &                    &          \\
+CS7.2      &   120              & 17            & Water  &  Solid 7/8~in Slug  & 18                 &          \\
+CS8        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &                    &          \\
+CS9        &   116              & 16            & Water  &  30$^{\circ}$ Fog   &                    &          \\
 CS10       &   116              & 16            & Water  &  Solid Stream       &                    &          \\
@@
 Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
-Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distrubtion of water is far more dispered around the gas cooling room.
+Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room.
 The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.
@@
 \label{sec:Fire_Suppression}
-Several of the tests used a wood fuel load comprised of pallets and the remaining tests used a more realistic fuel load comprised of common household furnishings to include wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding.
-The burn room was located to the rear of the single story structures and the available ventilation was both through the front doorway and from a rear window, dependent on the test in question.
+There were 14 suppression tests conducted in the single story purpose-built concrete structure.
+Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
+Ignition occurred in the rear of the single story structures and the available ventilation was both through the front doorway.
+For several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
 The fires were intended to replicate room and contents fires typically seen within residential structures.
-The hose lines were pre-deployed with fixed nozzles set in two locations.
-One in the hallway on the approach to the burn room (hallway nozzle), and one just inside the burn room to the right side of the hallway (room nozzle).
+Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle).
+Each nozzle flowed 15~s of water or compressed air foam depending on the test.
 The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
-Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire, representing an indirect interior attack.
-The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire.
-This position represented a direct interior attack.
-
-\begin{sidewaystable}[!ht]
+Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack).
+The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack).
+Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.
+
+\begin{table}[!ht]
 	\centering
-	\caption{Test Descriptions}
-	\begin{tabular}{lllll}
+	\caption{Fire Suppression Test Descriptions}
+	\begin{tabular}{llllll}
 		\hline\noalign{\smallskip}
-		Test		& Agent		& Stream				& Flow Rate			& Comments \\
+		Test		& Agent		& Stream				& Flow Rate			& Fuel           & Ventilation     \\
 		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 (FSE1)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
-		2 (FSW2)   	& Water     &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
-		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
-		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120 gpm    		&	Furniture Fuel Package	\\
-		5 (FSE5)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
-		6 (FSW6)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
-		7 (FSW7)    &  Water    &  30 deg Fog  			&  120 gpm    		&	Furniture Fuel Package	\\
-		8 (FSE8)    &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
-		9 (Attic 1) &  Water    &  Straight Stream  	&  120 gpm    		&	Furniture Fuel Package	\\
-		10 (Attic 2)&  CAF      &  Straight Stream  	&  120 gpm/60 cfm   &	Furniture Fuel Package  \\
-		11 (FSE1)   &  Water    &  30 deg Fog  			&  120 gpm   		&	Wood Fuel Package, Panel Window	 \\
-		12 (FSW1)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
-		13 (FSE2)   &  Water    &  30 deg Fog  			&  120 gpm    		&	Wood Fuel Package, Panel Window  \\
-		14 (FSW2)   &  CAF      &  30 deg Fog  			&  120 gpm/60 cfm   &	Wood Fuel Package, Panel Window  \\
+		1 (FSE1)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+		2 (FSW2)   	&  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
+		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
+		5 (FSE5)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+		6 (FSW6)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+		7 (FSW7)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+		8 (FSE8)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+		9 (Attic 1) &  Water    &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
+		10 (Attic 2)&  CAF      &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+		11 (FSE11)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
+		12 (FSW12)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
+		13 (FSE13)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
+		14 (FSW14)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
 		\noalign{\smallskip}\hline
@@
 	\label{tab:Test_Descriptions}
-\end{sidewaystable}
-
-\begin{sidewaystable}[!ht]
-	\centering
-	\caption{Nozzle Activation Times}
-	\begin{tabular}{lllllll}
-		\hline\noalign{\smallskip}
-		Test		& Agent		& Stream				& Nozzle 1 Activation	& Nozzle 1 Shut Off		& Nozzle 2 Activation	& Nozzle 2 Shut Off \\
-		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 (FSE1)    &  CAF      &  30 deg Fog  	    	& 233 					& 248					& 269					& 284					\\
-		2 (FSW2)   	& Water     &  30 deg Fog  	    	& 235					& 250					& 272					& 287					\\
-		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore     & 228					& 243 					& 255					& 270					\\
-		4 (FSE4)    &  Water    &  7/8" Smooth Bore     & 233					& 248					& 268					& 283					\\
-		5 (FSE5)    &  Water    &  30 deg Fog  	    	& 232					& 247					& 257					& 272					\\
-		6 (FSW6)    &  CAF      &  30 deg Fog     		& 239					& 254					& 268					& 283					\\
-		7 (FSW7)    &  Water    &  30 deg Fog     		& 276					& 291					& 308					& 323					\\
-		8 (FSE8)    &  CAF      &  30 deg Fog     		& 245					& 260					& 275					& 290					\\
-		9 (Attic 1) &  Water    &  Straight Stream     	&						&						&						&					\\
-		10 (Attic 2)&  CAF      &  Straight Stream     	& 						&						&						&					\\
-		11 (FSE1)   &  Water    &  30 deg Fog  	   		& 315					& 330					& 345					& 360					\\
-		12 (FSW1)   &  CAF      &  30 deg Fog  	   		& 233					& 248					& 263					& 278					\\
-		13 (FSE2)   &  Water    &  30 deg Fog  	   		& 330					& 390					& 406					& 466					\\
-		14 (FSW2)   &  CAF      &  30 deg Fog  	  		& 435					& 495					& 510					& 570					\\
-		\noalign{\smallskip}\hline
-	\end{tabular}
-	\label{tab:Nozzle_Activation_Times}
-\end{sidewaystable}
-
-\subsection{Wood Fuel Package}
-\label{subsec:Wood_Fuel_Package}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
-	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
-	\label{fig:Test_11_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
-	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_11_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
-	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_12_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
-	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_12_Second_Suppression}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
-	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, First Suppression}
-	\label{fig:Test_13_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
-	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30 deg Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_13_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
-	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_14_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
-	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_14_Second_Suppression}
-\end{figure}
-
-\clearpage
+\end{table}
 
@@
 
+Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle.
+The figures provide change in temperature and heat flux at several positions and elevations through the structure.
+These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.
+
 \begin{figure}[!ht]
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
-	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
 	\label{fig:Test_1_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-	\caption{Test 1: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
 	\label{fig:Test_1_Second_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
-	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
 	\label{fig:Test_2_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
-	\caption{Test 2: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
 	\label{fig:Test_2_Second_Suppression}
@@
 
+\chapter{Discussion and Tactical Considerations}
+\label{chap:Discussion_and_Tactical_Considerations}
+
+\chapter{Summary}
+\label{chap:Summary}
+
+Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
+unburned hydrocarbons filled the rooms of the structure.
+Once the window failed, the fresh air provided the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat release rate.
+
+Venting does not always equal cooling.
+In this experiment, post ventilation temperatures and heat fluxes all increased, due to the ventilation induced flashover.
+Fire induced flows.
+Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire growth and the flow path that was set-up between the window opening and the corridor vent.
+Avoid the flow path.
+The directional nature of the fire gas flow was demonstrated with thermal conditions, both temperature and heat flux, which were twice as high in the ``flow'' portion of the
+corridor as opposed to the ``static" portion of the corridor. Thermal conditions in the flow path were not consistent with firefighter survival.
+
+The fuel load in the structure was the same for all of the experiments.
+Each of these experiments demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE.
+
+The externally applied water streams were implemented in three different ways; a fog stream across the face of the window opening, a fog stream into the window opening, and a solid water stream into the window opening.
+
+These experiments demonstrated the ``extreme'' thermal conditions that can be generated by a ``simple room and contents'' fire and how these conditions can be extended along a flow path within a structure.
+The experiments also provided potential guidance for firefighters as a part of a fire size up and approach to the room of fire origin: note wind conditions in the area of the fire, look for ``pulsing flames'', examine smoke conditions around closed doors in the potential flow path, and maintain control of doors in the flow path.
+
+Further research in actual buildings is required to fully understand the ability of firefighters to implement these tactics, to examine the thermal conditions throughout the structure such as in stairways, and to examine the interaction of these tactics with building ventilation strategies both natural and with positive pressure ventilation.
+
+% \chapter{Appendix}
+% \label{chap:Appendix}
+
+% \section{Test 1 Figures}
+% \label{subsec:Test_1_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
+% 	\caption{Test 1 (FSE1): Eastside Array}
+% 	\label{fig:Test_1_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
+% 	\caption{Test 1 (FSE1): Westside Array}
+% 	\label{fig:Test_1_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
+% 	\caption{Test 1 (FSE1): Hallway Array}
+% 	\label{fig:Test_1_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
+% 	\caption{Test 1 (FSE1): Doorway Array}
+% 	\label{fig:Test_1_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
+% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
+% 	\label{fig:Test_1_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
+% 	\caption{Test 1 (FSE1): Suppression Westside Array}
+% 	\label{fig:Test_1_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
+% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
+% 	\label{fig:Test_1_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
+% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
+% 	\label{fig:Test_1_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
+% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
+% 	\label{fig:Test_1_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
+% 	\caption{Test 1 (FSE1): Westside Heat Flux}
+% 	\label{fig:Test_1_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
+% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
+% 	\label{fig:Test_1_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
+% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
+% 	\caption{Test 1 (FSE1): Hallway Velocity}
+% 	\label{fig:Test_1_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
+% 	\caption{Test 1 (FSE1): Doorway Velocity}
+% 	\label{fig:Test_1_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 2 Figures}
+% \label{subsec:Test_2_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
+% 	\caption{Test 2 (FSW2): Eastside Array}
+% 	\label{fig:Test_2_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
+% 	\caption{Test 2 (FSW2: Westside Array}
+% 	\label{fig:Test_2_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
+% 	\caption{Test 2 (FSW2): Hallway Array}
+% 	\label{fig:Test_2_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
+% 	\caption{Test 2 (FSW2): Doorway Array}
+% 	\label{fig:Test_2_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
+% 	\caption{Test 2 (FSW2): Suppression Eastside Array}
+% 	\label{fig:Test_2_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
+% 	\caption{Test 2 (FSW2): Suppression Westside Array}
+% 	\label{fig:Test_2_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
+% 	\caption{Test 2 (FSW2): Suppression Hallway Array}
+% 	\label{fig:Test_2_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
+% 	\caption{Test 2 (FSW2): Suppression Doorway Array}
+% 	\label{fig:Test_2_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
+% 	\caption{Test 2 (FSW2): Eastside Heat Flux}
+% 	\label{fig:Test_2_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
+% 	\caption{Test 2 (FSW2): Westside Heat Flux}
+% 	\label{fig:Test_2_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
+% 	\caption{Test 2 (FSW2): Hallway Heat Flux}
+% 	\label{fig:Test_2_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
+% 	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
+% 	\caption{Test 2 (FSW2): Hallway Velocity}
+% 	\label{fig:Test_2_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
+% 	\caption{Test 2 (FSW2): Doorway Velocity}
+% 	\label{fig:Test_2_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 3 Figures}
+% \label{subsec:Test_3_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
+% 	\caption{Test 3 (FSW3): Eastside Array}
+% 	\label{fig:Test_3_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
+% 	\caption{Test 3 (FSW3: Westside Array}
+% 	\label{fig:Test_3_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
+% 	\caption{Test 3 (FSW3): Hallway Array}
+% 	\label{fig:Test_3_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
+% 	\caption{Test 3 (FSW3): Doorway Array}
+% 	\label{fig:Test_3_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
+% 	\caption{Test 3 (FSW3): Suppression Eastside Array}
+% 	\label{fig:Test_3_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
+% 	\caption{Test 3 (FSW3): Suppression Westside Array}
+% 	\label{fig:Test_3_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
+% 	\caption{Test 3 (FSW3): Suppression Hallway Array}
+% 	\label{fig:Test_3_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
+% 	\caption{Test 3 (FSW3): Suppression Doorway Array}
+% 	\label{fig:Test_3_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
+% 	\caption{Test 3 (FSW3): Eastside Heat Flux}
+% 	\label{fig:Test_3_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
+% 	\caption{Test 3 (FSW3): Westside Heat Flux}
+% 	\label{fig:Test_3_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
+% 	\caption{Test 3 (FSW3): Hallway Heat Flux}
+% 	\label{fig:Test_3_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
+% 	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
+% 	\caption{Test 3 (FSW3): Hallway Velocity}
+% 	\label{fig:Test_3_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
+% 	\caption{Test 3 (FSW3): Doorway Velocity}
+% 	\label{fig:Test_3_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 4 Figures}
+% \label{subsec:Test_4_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
+% 	\caption{Test 4 (FSE4): Eastside Array}
+% 	\label{fig:Test_4_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
+% 	\caption{Test 4 (FSE4): Westside Array}
+% 	\label{fig:Test_4_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
+% 	\caption{Test 4 (FSE4): Hallway Array}
+% 	\label{fig:Test_4_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
+% 	\caption{Test 4 (FSE4): Doorway Array}
+% 	\label{fig:Test_4_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
+% 	\caption{Test 4 (FSE4): Suppression Eastside Array}
+% 	\label{fig:Test_4_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
+% 	\caption{Test 4 (FSE4): Suppression Westside Array}
+% 	\label{fig:Test_4_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
+% 	\caption{Test 4 (FSE4): Suppression Hallway Array}
+% 	\label{fig:Test_4_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
+% 	\caption{Test 4 (FSE4): Suppression Doorway Array}
+% 	\label{fig:Test_4_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
+% 	\caption{Test 4 (FSE4): Eastside Heat Flux}
+% 	\label{fig:Test_4_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
+% 	\caption{Test 4 (FSE4): Westside Heat Flux}
+% 	\label{fig:Test_4_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
+% 	\caption{Test 4 (FSE4): Hallway Heat Flux}
+% 	\label{fig:Test_4_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
+% 	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
+% 	\caption{Test 4 (FSE4): Hallway Velocity}
+% 	\label{fig:Test_4_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
+% 	\caption{Test 4 (FSE4): Doorway Velocity}
+% 	\label{fig:Test_4_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 5 Figures}
+% \label{subsec:Test_5_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
+% 	\caption{Test 5 (FSE5): Eastside Array}
+% 	\label{fig:Test_5_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
+% 	\caption{Test 5 (FSE5): Westside Array}
+% 	\label{fig:Test_5_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
+% 	\caption{Test 5 (FSE5): Hallway Array}
+% 	\label{fig:Test_5_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
+% 	\caption{Test 5 (FSE5): Doorway Array}
+% 	\label{fig:Test_5_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
+% 	\caption{Test 5 (FSE5): Suppression Eastside Array}
+% 	\label{fig:Test_5_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
+% 	\caption{Test 5 (FSE5): Suppression Westside Array}
+% 	\label{fig:Test_5_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
+% 	\caption{Test 5 (FSE5): Suppression Hallway Array}
+% 	\label{fig:Test_5_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
+% 	\caption{Test 5 (FSE5): Suppression Doorway Array}
+% 	\label{fig:Test_5_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
+% 	\caption{Test 5 (FSE5): Eastside Heat Flux}
+% 	\label{fig:Test_5_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
+% 	\caption{Test 5 (FSE5): Westside Heat Flux}
+% 	\label{fig:Test_5_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
+% 	\caption{Test 5 (FSE5): Hallway Heat Flux}
+% 	\label{fig:Test_5_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
+% 	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
+% 	\caption{Test 5 (FSE5): Hallway Velocity}
+% 	\label{fig:Test_5_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
+% 	\caption{Test 5 (FSE5): Doorway Velocity}
+% 	\label{fig:Test_5_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 6 Figures}
+% \label{subsec:Test_6_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
+% 	\caption{Test 6 (FSW6): Eastside Array}
+% 	\label{fig:Test_6_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
+% 	\caption{Test 6 (FSW6: Westside Array}
+% 	\label{fig:Test_6_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
+% 	\caption{Test 6 (FSW6): Hallway Array}
+% 	\label{fig:Test_6_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
+% 	\caption{Test 6 (FSW6): Doorway Array}
+% 	\label{fig:Test_6_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
+% 	\caption{Test 6 (FSW6): Suppression Eastside Array}
+% 	\label{fig:Test_6_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
+% 	\caption{Test 6 (FSW6): Suppression Westside Array}
+% 	\label{fig:Test_6_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
+% 	\caption{Test 6 (FSW6): Suppression Hallway Array}
+% 	\label{fig:Test_6_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
+% 	\caption{Test 6 (FSW6): Suppression Doorway Array}
+% 	\label{fig:Test_6_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
+% 	\caption{Test 6 (FSW6): Eastside Heat Flux}
+% 	\label{fig:Test_6_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
+% 	\caption{Test 6 (FSW6): Westside Heat Flux}
+% 	\label{fig:Test_6_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
+% 	\caption{Test 6 (FSW6): Hallway Heat Flux}
+% 	\label{fig:Test_6_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
+% 	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
+% 	\caption{Test 6 (FSW6): Hallway Velocity}
+% 	\label{fig:Test_6_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
+% 	\caption{Test 6 (FSW6): Doorway Velocity}
+% 	\label{fig:Test_6_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 7 Figures}
+% \label{subsec:Test_7_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
+% 	\caption{Test 7 (FSW7): Eastside Array}
+% 	\label{fig:Test_7_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
+% 	\caption{Test 7 (FSW7: Westside Array}
+% 	\label{fig:Test_7_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
+% 	\caption{Test 7 (FSW7): Hallway Array}
+% 	\label{fig:Test_7_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
+% 	\caption{Test 7 (FSW7): Doorway Array}
+% 	\label{fig:Test_7_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
+% 	\caption{Test 7 (FSW7): Suppression Eastside Array}
+% 	\label{fig:Test_7_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
+% 	\caption{Test 7 (FSW7): Suppression Westside Array}
+% 	\label{fig:Test_7_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
+% 	\caption{Test 7 (FSW7): Suppression Hallway Array}
+% 	\label{fig:Test_7_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
+% 	\caption{Test 7 (FSW7): Suppression Doorway Array}
+% 	\label{fig:Test_7_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
+% 	\caption{Test 7 (FSW7): Eastside Heat Flux}
+% 	\label{fig:Test_7_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
+% 	\caption{Test 7 (FSW7): Westside Heat Flux}
+% 	\label{fig:Test_7_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
+% 	\caption{Test 7 (FSW7): Hallway Heat Flux}
+% 	\label{fig:Test_7_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
+% 	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
+% 	\caption{Test 7 (FSW7): Hallway Velocity}
+% 	\label{fig:Test_7_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
+% 	\caption{Test 7 (FSW7): Doorway Velocity}
+% 	\label{fig:Test_7_Doorway_Velocity}
+% \end{figure}
+
+% \clearpage
+
+% \section{Test 8 Figures}
+% \label{subsec:Test_8_Figures}
+
+% \subsection{Temperature}
+% \label{subsec:Temperature}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
+% 	\caption{Test 8 (FSE8): Eastside Array}
+% 	\label{fig:Test_8_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
+% 	\caption{Test 8 (FSE8): Westside Array}
+% 	\label{fig:Test_8_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
+% 	\caption{Test 8 (FSE8): Hallway Array}
+% 	\label{fig:Test_8_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
+% 	\caption{Test 8 (FSE8): Doorway Array}
+% 	\label{fig:Test_8_Doorway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
+% 	\caption{Test 8 (FSE8): Suppression Eastside Array}
+% 	\label{fig:Test_8_Suppression_Eastside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
+% 	\caption{Test 8 (FSE8): Suppression Westside Array}
+% 	\label{fig:Test_8_Suppression_Westside_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
+% 	\caption{Test 8 (FSE8): Suppression Hallway Array}
+% 	\label{fig:Test_8_Suppression_Hallway_Array}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
+% 	\caption{Test 8 (FSE8): Suppression Doorway Array}
+% 	\label{fig:Test_8_Suppression_Doorway_Array}
+% \end{figure}
+
+% \subsection{Heat Flux}
+% \label{subsec:Heat_Flux}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
+% 	\caption{Test 8 (FSE8): Eastside Heat Flux}
+% 	\label{fig:Test_8_Eastside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
+% 	\caption{Test 8 (FSE8): Westside Heat Flux}
+% 	\label{fig:Test_8_Westside_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
+% 	\caption{Test 8 (FSE8): Hallway Heat Flux}
+% 	\label{fig:Test_8_Hallway_Heat_Flux}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
+% 	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
+% 	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
+% \end{figure}
+
+% \subsection{Velocity}
+% \label{subsec:Velocity}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
+% 	\caption{Test 8 (FSE8): Hallway Velocity}
+% 	\label{fig:Test_8_Hallway_Velocity}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
+% 	\caption{Test 8 (FSE8): Doorway Velocity}
+% 	\label{fig:Test_8_Doorway_Velocity}
+% \end{figure}
+
 \clearpage
+
+\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
+
+\appendix
+
+\chapter{Fuel Load Details}
+\label{app:fuel_loads}
+
+\chapter{Spray Density Figures}
+\label{app:spray_density}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB2}
+	\caption{Burn Building Test 2}
+	\label{fig:Burn_Building_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB3}
+	\caption{Burn Building Test 3}
+	\label{fig:Burn_Building_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB4}
+	\caption{Burn Building Test 4}
+	\label{fig:Burn_Building_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB5}
+	\caption{Burn Building Test 5}
+	\label{fig:Burn_Building_Test_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB6}
+	\caption{Burn Building Test 6}
+	\label{fig:Burn_Building_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB8}
+	\caption{Burn Building Test 8}
+	\label{fig:Burn_Building_Test_8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB9}
+	\caption{Burn Building Test 9}
+	\label{fig:Burn_Building_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB10}
+	\caption{Burn Building Test 10}
+	\label{fig:Burn_Building_Test_10}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB11}
+	\caption{Burn Building Test 11}
+	\label{fig:Burn_Building_Test_11}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB12}
+	\caption{Burn Building Test 12}
+	\label{fig:Burn_Building_Test_12}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB13}
+	\caption{Burn Building Test 13}
+	\label{fig:Burn_Building_Test_13}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB14}
+	\caption{Burn Building Test 14}
+	\label{fig:Burn_Building_Test_14}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB15}
+	\caption{Burn Building Test 15}
+	\label{fig:Burn_Building_Test_15}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB16}
+	\caption{Burn Building Test 16}
+	\label{fig:Burn_Building_Test_16}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB17}
+	\caption{Burn Building Test 17}
+	\label{fig:Burn_Building_Test_17}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB18}
+	\caption{Burn Building Test 18}
+	\label{fig:Burn_Building_Test_18}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB19}
+	\caption{Burn Building Test 19}
+	\label{fig:Burn_Building_Test_19}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB20}
+	\caption{Burn Building Test 20}
+	\label{fig:Burn_Building_Test_20}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/BB21}
+	\caption{Burn Building Test 21}
+	\label{fig:Burn_Building_Test_21}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_1}
+	\caption{Experimental Structures Test 1}
+	\label{fig:Experimental_Structures_Test_1}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_2}
+	\caption{Experimental Structures Test 2}
+	\label{fig:Experimental_Structures_Test_2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_3}
+	\caption{Experimental Structures Test 3}
+	\label{fig:Experimental_Structures_Test_3}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_4}
+	\caption{Experimental Structures Test 4}
+	\label{fig:Experimental_Structures_Test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_5}
+	\caption{Experimental Structures Test 5}
+	\label{fig:Experimental_Structures_Test_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_6}
+	\caption{Experimental Structures Test 6}
+	\label{fig:Experimental_Structures_Test_6}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_7}
+	\caption{Experimental Structures Test 7}
+	\label{fig:Experimental_Structures_Test_7}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_72}
+	\caption{Experimental Structures Test 7.2}
+	\label{fig:Experimental_Structures_Test_7.2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_8}
+	\caption{Experimental Structures Test 8}
+	\label{fig:Experimental_Structures_Test_8}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_9}
+	\caption{Experimental Structures Test 9}
+	\label{fig:Experimental_Structures_Test_9}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_10}
+	\caption{Experimental Structures Test 10}
+	\label{fig:Experimental_Structures_Test_10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=4in]{../Figures/Bars/ES_11}
+	\caption{Experimental Structures Test 11}
+	\label{fig:Experimental_Structures_Test_11}
+\end{figure}
+
+\chapter{Fire Suppression Figures}
+\label{app:fire_suppression}
+
+\section{Furniture Fuel Package}
+\label{appsubsec:Furniture_Fuel_Package}
 
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
-	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
 	\label{fig:Test_5_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
-	\caption{Test 5: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
 	\label{fig:Test_5_Second_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
-	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
 	\label{fig:Test_6_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
-	\caption{Test 6: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
 	\label{fig:Test_6_Second_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
-	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, First Suppression}
+	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
 	\label{fig:Test_7_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
-	\caption{Test 7: Furniture Fuel Package, Water, 30 deg Fog, 120 gpm, Second Suppression}
+	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
 	\label{fig:Test_7_Second_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
-	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, First Suppression}
+	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
 	\label{fig:Test_8_First_Suppression}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
-	\caption{Test 8: Furniture Fuel Package, CAFS, 30 deg Fog, 120 gpm/60cfm, Second Suppression}
+	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
 	\label{fig:Test_8_Second_Suppression}
@@
 
-\chapter{Discussion and Tactical Considerations}
-\label{chap:Discussion_and_Tactical_Considerations}
-
-\chapter{Summary}
-\label{chap:Summary}
-
-Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of
-the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
-unburned hydrocarbons filled the rooms of the structure. Once the window failed, the fresh air provided
-the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat
-release rate.
-Venting does not always equal cooling. In this experiment, post ventilation temperatures and
-heat fluxes all increased, due to the ventilation induced flashover.
-Fire induced flows. Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire
-growth and the flow path that was set-up between the window opening and the corridor vent.
-Avoid the flow path. The directional nature of the fire gas flow was demonstrated with thermal
-conditions, both temperature and heat flux, which were twice as high in the “flow” portion of the
-corridor as opposed to the “static” portion of the corridor. Thermal conditions in the
-flow path were not consistent with firefighter survival.
-
-The fuel load in the structure was the same for all of the experiments. Each of these experiments
-demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE.
-
-The externally applied water streams were implemented in three different ways; a fog stream across the face
-of the window opening, a fog stream into the window opening, and a solid water stream into the window
-opening.
-
-These experiments demonstrated the “extreme” thermal conditions that can be generated by a “simple
-room and contents” fire and how these conditions can be extended along a flow path within a structure.
-The experiments also provided potential guidance for firefighters as a part of a fire size up and approach
-to the room of fire origin: note wind conditions in the area of the fire, look for “pulsing flames”,
-examine smoke conditions around closed doors in the potential flow path, and maintain control of doors
-in the flow path.
-
-Further research in actual buildings is required to fully understand the ability of firefighters to
-implement these tactics, to examine the thermal conditions throughout the structure such as in stairways,
-and to examine the interaction of these tactics with building ventilation strategies both natural and with
-positive pressure ventilation.
-
-% \chapter{Appendix}
-% \label{chap:Appendix}
-
-% \section{Test 1 Figures}
-% \label{subsec:Test_1_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
-% 	\caption{Test 1 (FSE1): Eastside Array}
-% 	\label{fig:Test_1_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
-% 	\caption{Test 1 (FSE1): Westside Array}
-% 	\label{fig:Test_1_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
-% 	\caption{Test 1 (FSE1): Hallway Array}
-% 	\label{fig:Test_1_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
-% 	\caption{Test 1 (FSE1): Doorway Array}
-% 	\label{fig:Test_1_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
-% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
-% 	\label{fig:Test_1_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
-% 	\caption{Test 1 (FSE1): Suppression Westside Array}
-% 	\label{fig:Test_1_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
-% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
-% 	\label{fig:Test_1_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
-% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
-% 	\label{fig:Test_1_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
-% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
-% 	\label{fig:Test_1_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
-% 	\caption{Test 1 (FSE1): Westside Heat Flux}
-% 	\label{fig:Test_1_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
-% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
-% 	\label{fig:Test_1_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
-% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
-% 	\caption{Test 1 (FSE1): Hallway Velocity}
-% 	\label{fig:Test_1_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
-% 	\caption{Test 1 (FSE1): Doorway Velocity}
-% 	\label{fig:Test_1_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 2 Figures}
-% \label{subsec:Test_2_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
-% 	\caption{Test 2 (FSW2): Eastside Array}
-% 	\label{fig:Test_2_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
-% 	\caption{Test 2 (FSW2: Westside Array}
-% 	\label{fig:Test_2_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
-% 	\caption{Test 2 (FSW2): Hallway Array}
-% 	\label{fig:Test_2_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
-% 	\caption{Test 2 (FSW2): Doorway Array}
-% 	\label{fig:Test_2_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
-% 	\caption{Test 2 (FSW2): Suppression Eastside Array}
-% 	\label{fig:Test_2_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
-% 	\caption{Test 2 (FSW2): Suppression Westside Array}
-% 	\label{fig:Test_2_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
-% 	\caption{Test 2 (FSW2): Suppression Hallway Array}
-% 	\label{fig:Test_2_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
-% 	\caption{Test 2 (FSW2): Suppression Doorway Array}
-% 	\label{fig:Test_2_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
-% 	\caption{Test 2 (FSW2): Eastside Heat Flux}
-% 	\label{fig:Test_2_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
-% 	\caption{Test 2 (FSW2): Westside Heat Flux}
-% 	\label{fig:Test_2_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
-% 	\caption{Test 2 (FSW2): Hallway Heat Flux}
-% 	\label{fig:Test_2_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
-% 	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
-% 	\caption{Test 2 (FSW2): Hallway Velocity}
-% 	\label{fig:Test_2_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
-% 	\caption{Test 2 (FSW2): Doorway Velocity}
-% 	\label{fig:Test_2_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 3 Figures}
-% \label{subsec:Test_3_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
-% 	\caption{Test 3 (FSW3): Eastside Array}
-% 	\label{fig:Test_3_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
-% 	\caption{Test 3 (FSW3: Westside Array}
-% 	\label{fig:Test_3_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
-% 	\caption{Test 3 (FSW3): Hallway Array}
-% 	\label{fig:Test_3_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
-% 	\caption{Test 3 (FSW3): Doorway Array}
-% 	\label{fig:Test_3_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
-% 	\caption{Test 3 (FSW3): Suppression Eastside Array}
-% 	\label{fig:Test_3_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
-% 	\caption{Test 3 (FSW3): Suppression Westside Array}
-% 	\label{fig:Test_3_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
-% 	\caption{Test 3 (FSW3): Suppression Hallway Array}
-% 	\label{fig:Test_3_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
-% 	\caption{Test 3 (FSW3): Suppression Doorway Array}
-% 	\label{fig:Test_3_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
-% 	\caption{Test 3 (FSW3): Eastside Heat Flux}
-% 	\label{fig:Test_3_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
-% 	\caption{Test 3 (FSW3): Westside Heat Flux}
-% 	\label{fig:Test_3_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
-% 	\caption{Test 3 (FSW3): Hallway Heat Flux}
-% 	\label{fig:Test_3_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
-% 	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
-% 	\caption{Test 3 (FSW3): Hallway Velocity}
-% 	\label{fig:Test_3_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
-% 	\caption{Test 3 (FSW3): Doorway Velocity}
-% 	\label{fig:Test_3_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 4 Figures}
-% \label{subsec:Test_4_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
-% 	\caption{Test 4 (FSE4): Eastside Array}
-% 	\label{fig:Test_4_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
-% 	\caption{Test 4 (FSE4): Westside Array}
-% 	\label{fig:Test_4_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
-% 	\caption{Test 4 (FSE4): Hallway Array}
-% 	\label{fig:Test_4_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
-% 	\caption{Test 4 (FSE4): Doorway Array}
-% 	\label{fig:Test_4_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
-% 	\caption{Test 4 (FSE4): Suppression Eastside Array}
-% 	\label{fig:Test_4_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
-% 	\caption{Test 4 (FSE4): Suppression Westside Array}
-% 	\label{fig:Test_4_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
-% 	\caption{Test 4 (FSE4): Suppression Hallway Array}
-% 	\label{fig:Test_4_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
-% 	\caption{Test 4 (FSE4): Suppression Doorway Array}
-% 	\label{fig:Test_4_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
-% 	\caption{Test 4 (FSE4): Eastside Heat Flux}
-% 	\label{fig:Test_4_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
-% 	\caption{Test 4 (FSE4): Westside Heat Flux}
-% 	\label{fig:Test_4_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
-% 	\caption{Test 4 (FSE4): Hallway Heat Flux}
-% 	\label{fig:Test_4_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
-% 	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
-% 	\caption{Test 4 (FSE4): Hallway Velocity}
-% 	\label{fig:Test_4_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
-% 	\caption{Test 4 (FSE4): Doorway Velocity}
-% 	\label{fig:Test_4_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 5 Figures}
-% \label{subsec:Test_5_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
-% 	\caption{Test 5 (FSE5): Eastside Array}
-% 	\label{fig:Test_5_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
-% 	\caption{Test 5 (FSE5): Westside Array}
-% 	\label{fig:Test_5_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
-% 	\caption{Test 5 (FSE5): Hallway Array}
-% 	\label{fig:Test_5_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
-% 	\caption{Test 5 (FSE5): Doorway Array}
-% 	\label{fig:Test_5_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
-% 	\caption{Test 5 (FSE5): Suppression Eastside Array}
-% 	\label{fig:Test_5_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
-% 	\caption{Test 5 (FSE5): Suppression Westside Array}
-% 	\label{fig:Test_5_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
-% 	\caption{Test 5 (FSE5): Suppression Hallway Array}
-% 	\label{fig:Test_5_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
-% 	\caption{Test 5 (FSE5): Suppression Doorway Array}
-% 	\label{fig:Test_5_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
-% 	\caption{Test 5 (FSE5): Eastside Heat Flux}
-% 	\label{fig:Test_5_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
-% 	\caption{Test 5 (FSE5): Westside Heat Flux}
-% 	\label{fig:Test_5_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
-% 	\caption{Test 5 (FSE5): Hallway Heat Flux}
-% 	\label{fig:Test_5_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
-% 	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
-% 	\caption{Test 5 (FSE5): Hallway Velocity}
-% 	\label{fig:Test_5_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
-% 	\caption{Test 5 (FSE5): Doorway Velocity}
-% 	\label{fig:Test_5_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 6 Figures}
-% \label{subsec:Test_6_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
-% 	\caption{Test 6 (FSW6): Eastside Array}
-% 	\label{fig:Test_6_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
-% 	\caption{Test 6 (FSW6: Westside Array}
-% 	\label{fig:Test_6_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
-% 	\caption{Test 6 (FSW6): Hallway Array}
-% 	\label{fig:Test_6_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
-% 	\caption{Test 6 (FSW6): Doorway Array}
-% 	\label{fig:Test_6_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
-% 	\caption{Test 6 (FSW6): Suppression Eastside Array}
-% 	\label{fig:Test_6_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
-% 	\caption{Test 6 (FSW6): Suppression Westside Array}
-% 	\label{fig:Test_6_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
-% 	\caption{Test 6 (FSW6): Suppression Hallway Array}
-% 	\label{fig:Test_6_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
-% 	\caption{Test 6 (FSW6): Suppression Doorway Array}
-% 	\label{fig:Test_6_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
-% 	\caption{Test 6 (FSW6): Eastside Heat Flux}
-% 	\label{fig:Test_6_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
-% 	\caption{Test 6 (FSW6): Westside Heat Flux}
-% 	\label{fig:Test_6_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
-% 	\caption{Test 6 (FSW6): Hallway Heat Flux}
-% 	\label{fig:Test_6_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
-% 	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
-% 	\caption{Test 6 (FSW6): Hallway Velocity}
-% 	\label{fig:Test_6_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
-% 	\caption{Test 6 (FSW6): Doorway Velocity}
-% 	\label{fig:Test_6_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 7 Figures}
-% \label{subsec:Test_7_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
-% 	\caption{Test 7 (FSW7): Eastside Array}
-% 	\label{fig:Test_7_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
-% 	\caption{Test 7 (FSW7: Westside Array}
-% 	\label{fig:Test_7_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
-% 	\caption{Test 7 (FSW7): Hallway Array}
-% 	\label{fig:Test_7_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
-% 	\caption{Test 7 (FSW7): Doorway Array}
-% 	\label{fig:Test_7_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
-% 	\caption{Test 7 (FSW7): Suppression Eastside Array}
-% 	\label{fig:Test_7_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
-% 	\caption{Test 7 (FSW7): Suppression Westside Array}
-% 	\label{fig:Test_7_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
-% 	\caption{Test 7 (FSW7): Suppression Hallway Array}
-% 	\label{fig:Test_7_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
-% 	\caption{Test 7 (FSW7): Suppression Doorway Array}
-% 	\label{fig:Test_7_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
-% 	\caption{Test 7 (FSW7): Eastside Heat Flux}
-% 	\label{fig:Test_7_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
-% 	\caption{Test 7 (FSW7): Westside Heat Flux}
-% 	\label{fig:Test_7_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
-% 	\caption{Test 7 (FSW7): Hallway Heat Flux}
-% 	\label{fig:Test_7_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
-% 	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
-% 	\caption{Test 7 (FSW7): Hallway Velocity}
-% 	\label{fig:Test_7_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
-% 	\caption{Test 7 (FSW7): Doorway Velocity}
-% 	\label{fig:Test_7_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 8 Figures}
-% \label{subsec:Test_8_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
-% 	\caption{Test 8 (FSE8): Eastside Array}
-% 	\label{fig:Test_8_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
-% 	\caption{Test 8 (FSE8): Westside Array}
-% 	\label{fig:Test_8_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
-% 	\caption{Test 8 (FSE8): Hallway Array}
-% 	\label{fig:Test_8_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
-% 	\caption{Test 8 (FSE8): Doorway Array}
-% 	\label{fig:Test_8_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
-% 	\caption{Test 8 (FSE8): Suppression Eastside Array}
-% 	\label{fig:Test_8_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
-% 	\caption{Test 8 (FSE8): Suppression Westside Array}
-% 	\label{fig:Test_8_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
-% 	\caption{Test 8 (FSE8): Suppression Hallway Array}
-% 	\label{fig:Test_8_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
-% 	\caption{Test 8 (FSE8): Suppression Doorway Array}
-% 	\label{fig:Test_8_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
-% 	\caption{Test 8 (FSE8): Eastside Heat Flux}
-% 	\label{fig:Test_8_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
-% 	\caption{Test 8 (FSE8): Westside Heat Flux}
-% 	\label{fig:Test_8_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
-% 	\caption{Test 8 (FSE8): Hallway Heat Flux}
-% 	\label{fig:Test_8_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
-% 	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
-% 	\caption{Test 8 (FSE8): Hallway Velocity}
-% 	\label{fig:Test_8_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
-% 	\caption{Test 8 (FSE8): Doorway Velocity}
-% 	\label{fig:Test_8_Doorway_Velocity}
-% \end{figure}
+\section{Wood Fuel Package}
+\label{appsubsec:Wood_Fuel_Package}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
+	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
+	\label{fig:Test_11_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
+	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_11_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
+	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_12_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
+	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_12_Second_Suppression}
+\end{figure}
 
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
-
-\appendix
-
-\chapter{Fuel Load Details}
-\label{app:fuel_loads}
-
-\chapter{Spray Denisty Figures}
-\label{app:spray_density}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB2}
-	\caption{Burn Building Test 2}
-	\label{fig:Burn_Building_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB3}
-	\caption{Burn Building Test 3}
-	\label{fig:Burn_Building_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB4}
-	\caption{Burn Building Test 4}
-	\label{fig:Burn_Building_Test_4}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB5}
-	\caption{Burn Building Test 5}
-	\label{fig:Burn_Building_Test_5}
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
+	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
+	\label{fig:Test_13_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
+	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
+	\label{fig:Test_13_Second_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
+	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
+	\label{fig:Test_14_First_Suppression}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
+	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
+	\label{fig:Test_14_Second_Suppression}
 \end{figure}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB6}
-	\caption{Burn Building Test 6}
-	\label{fig:Burn_Building_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB8}
-	\caption{Burn Building Test 8}
-	\label{fig:Burn_Building_Test_8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB9}
-	\caption{Burn Building Test 9}
-	\label{fig:Burn_Building_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB10}
-	\caption{Burn Building Test 10}
-	\label{fig:Burn_Building_Test_10}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB11}
-	\caption{Burn Building Test 11}
-	\label{fig:Burn_Building_Test_11}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB12}
-	\caption{Burn Building Test 12}
-	\label{fig:Burn_Building_Test_12}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB13}
-	\caption{Burn Building Test 13}
-	\label{fig:Burn_Building_Test_13}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB14}
-	\caption{Burn Building Test 14}
-	\label{fig:Burn_Building_Test_14}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB15}
-	\caption{Burn Building Test 15}
-	\label{fig:Burn_Building_Test_15}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB16}
-	\caption{Burn Building Test 16}
-	\label{fig:Burn_Building_Test_16}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB17}
-	\caption{Burn Building Test 17}
-	\label{fig:Burn_Building_Test_17}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB18}
-	\caption{Burn Building Test 18}
-	\label{fig:Burn_Building_Test_18}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB19}
-	\caption{Burn Building Test 19}
-	\label{fig:Burn_Building_Test_19}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB20}
-	\caption{Burn Building Test 20}
-	\label{fig:Burn_Building_Test_20}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB21}
-	\caption{Burn Building Test 21}
-	\label{fig:Burn_Building_Test_21}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_1}
-	\caption{Experimental Structures Test 1}
-	\label{fig:Experimental_Structures_Test_1}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_2}
-	\caption{Experimental Structures Test 2}
-	\label{fig:Experimental_Structures_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_3}
-	\caption{Experimental Structures Test 3}
-	\label{fig:Experimental_Structures_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_4}
-	\caption{Experimental Structures Test 4}
-	\label{fig:Experimental_Structures_Test_4}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_5}
-	\caption{Experimental Structures Test 5}
-	\label{fig:Experimental_Structures_Test_5}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_6}
-	\caption{Experimental Structures Test 6}
-	\label{fig:Experimental_Structures_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_7}
-	\caption{Experimental Structures Test 7}
-	\label{fig:Experimental_Structures_Test_7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_72}
-	\caption{Experimental Structures Test 7.2}
-	\label{fig:Experimental_Structures_Test_7.2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_8}
-	\caption{Experimental Structures Test 8}
-	\label{fig:Experimental_Structures_Test_8}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_9}
-	\caption{Experimental Structures Test 9}
-	\label{fig:Experimental_Structures_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_10}
-	\caption{Experimental Structures Test 10}
-	\label{fig:Experimental_Structures_Test_10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_11}
-	\caption{Experimental Structures Test 11}
-	\label{fig:Experimental_Structures_Test_11}
-\end{figure}
-
 \end{document}

### 2015-09-14 Projects/DelCo_2012/Scripts/gas_cooling_plot2.py

@@ -98,7 +98,8 @@ for entry in range(0,len(info)):
 		avg_rel_diff = sum((y-X)/((y+X)/2.))/len(X)
 
 		p = ggplot(aes('del_cafs', 'del_water'),data = del_temp) + geom_point() + stat_smooth(method='lm', color='blue',se=True) + \
-		scale_x_continuous("$\Delta$T (deg C) CAFS", limits=(0,max_axis)) + scale_y_continuous("$\Delta$T (deg C) H$_2$O",limits=(0,max_axis))
+		geom_abline(intercept=0,slope=1,colour="black") + scale_x_continuous("$\Delta$T (deg C) CAFS", limits=(0,max_axis)) + \
+		scale_y_continuous("$\Delta$T (deg C) H$_2$O",limits=(0,max_axis))
 		ggsave(p,plot_dir + info['Nozzle'][entry] + '_' + info['Position'][entry] + '_scatter_ggplot.pdf',format='pdf' )
 
 		# fig = figure()

### 2015-09-15 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: updated script to include latex code generation, deleted unnecessary scripts, added a  missing time to hose_times file, and edited hose_stream report

@@
 \flushright{
-Joseph Willi \\
+Joseph M. Willi \\
 Daniel Madrzykowski \\
@@
 \hspace{1.5in} \= \\
-FDS \> Fire Dynamics Simulator \\
-HGL \> Hot Gas Layer \\
-HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
+% FDS \> Fire Dynamics Simulator \\
+% HGL \> Hot Gas Layer \\
+% HRR \> Heat Release Rate \\
+% HRRPUA \> Heat Release Rate per Unit Area \\
+BDP \> Bi-Directional Probe \\
 NIST \> National Institute of Standards and Technology \\
@@
 
+% ================
+% = Introduction =
+% ================
+
 \chapter{Introduction}
-\label{chap:Introduction}
+\label{chap:intro}
 NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.
@@
 \includegraphics[width=6in]{../Pictures/hose_streams.pdf}
-\caption[Different Hose Stream Patterns]{The three types of hose stream patterns used during the water flow experiments from left to right: straight stream, narrow fog stream, and wide fog stream.}
+\caption[Different Hose Stream Patterns]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
 \label{fig:hose_streams}
@@
 \section{Background}
-\label{sec:Background}
+\label{sec:background}
 %http://www.tft.com/literature/library/files/bfa.pdf
@@
 
-\chapter{Experimental Setup}
-\label{chap:Experimental_Setup}
+% =========================
+% = EXPERIMENTAL OVERVIEW =
+% =========================
+\chapter{Experimental Overview}
+\label{chap:exp_overview}
+To study the impact of different hose stream and application pattern selections on air movement inside a structure, numerous experiments were conducted in structures with different ventilation patterns.
 
-\section{Experimental Structure}
-\label{sec:Experimental_Structure}
-This series of field experiments was conducted in two structures located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+\section{Experimental Setup}
+\label{sec:exp_setup}
 
-\subsection{Construction}
-\label{sec:Construction}
-Two concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
+\subsection{Test Structures}
+\label{subsec:test_structs}
+The series of field experiments described in this report was conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+
+\subsubsection{Construction}
+\label{subsubsec:construction}
+Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
 They were designed to simulate a single-story and a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks of dimensions 0.61 m x 0.61 m X 0.61 m (2 ft x 2 ft x 2 ft).
+The first floor of each structure had an outer wall composed of interlocking concrete blocks shaped as cubes with each side measuring approximately 0.61 m (2 ft) in length.
 The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
@@
 The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1\nicefrac{1}{8} in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Figure \ref{fig:TJI}.
+The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
 Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed to the top of the TJIs.
@@
 The ceiling of the burn room was the exposed "floor assembly".
-The walls of the hallway and entry foyer were composed of 16 mm (\nicefrac{3}{8} in) Type X gypsum room.
+The walls of the hallway and entry foyer were composed of 16 mm (0.38 in) Type X gypsum room.
 The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
@@
 \end{figure}
+
+\clearpage
+
+\subsubsection{Layout}
+\label{subsubsec:layout}
+**** Dimension detail, introduce floor plan figures, etc. ****
 
@@
 \subsection{Instrumentation}
-\label{sec:Instrumentation}
-There is a discussion of uncertainties for each measurement below in Section~\ref{sec:Uncertainty}.
+\label{subsec:instrumentation}
+There is a discussion of uncertainties for each measurement below in Section~\ref{subsec:uncertainty}.
 Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
@@
 To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses.
-Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_instrumentation} and Fig.~\ref{fig:west_instrumentation}.
+Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_devices} and Fig.~\ref{fig:west_devices}.
 A single thermocouple was attached to each bi-directional probe.
@@
 \caption[Location of Instrumentation in East Structure]{Location of instrumentation in East Structure}
-\label{fig:east_instrumentation}
+\label{fig:east_devices}
 \end{figure}
@@
 \caption[Location of Instrumentation in West Structure]{Location of instrumentation in West Structure}
-\label{fig:west_instrumentation}
+\label{fig:west_devices}
 \end{figure}
@@
 
-\section{Uncertainty}
-\label{sec:Uncertainty}
+\subsection{Uncertainty}
+\label{subsec:uncertainty}
 There are different components of uncertainty in the length, differential pressure, and gas velocity reported here.
@@
 \section{Experimental Procedure}
-\label{sec:Experimental_Procedure}
+\label{sec:exp_procedure}
 
@@
 2000 LPM (500 GPM)?
-or 1~\nicefrac{3}{4}" handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns.
+or 1.75 in handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns.
 Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
@@
 \subsection{Monitor Experiments}
-\label{sec:Water_Flow_Monitor_Procedure}
-Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in the straight, narrow fog, and wide fog stream patterns.
+\label{subsec:monitor_procedure}
+Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight, narrow fog, and wide fog stream pattern.
 One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.
+Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
+Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure.
 
@@
 % Add flow chart? %
-Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
+Tests 16 and 17 followed identical procedures that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
 The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
@@
 \subsection{Handline Experiments}
-\label{sec:Water_Flow_Handline_Procedure}
+\label{subsec:handline_procedure}
 Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water.
@@
 
+% ===========
+% = RESULTS =
+% ===========
+
 \chapter{Results}
@@
 
-\section{Monitor Nozzle Experiments}
+\section{Monitor Experiments}
 \label{sec:monitor_results}
@@
 
+% West Monitor Table
+
+\begin{table}[!ht]
+\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and target location for all monitor tests}
+\begin{tabular}{lccccc}
+\toprule
+ & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
+\\
+\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} & \textbf{Door AB}
+\\ \midrule
+\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
+\\ \multicolumn{6}{c}{} \\
+\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
+\\ \multicolumn{6}{c}{} \\
+\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
+\\ \bottomrule
+\end{tabular}
+\label{table:all_mon_vel_avgs}
+\end{table}
+
 \section{Handline Experiments}
@@
 
-Figures \ref{fig:Test_18_BDP_A10_Avg_All}-\ref{fig:Test_19_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the four application patterns and three hose stream patterns for Tests 18 and 19.
+Figs.~\ref{fig:Test_18_BDP_A10_Avg_All}-\ref{fig:Test_19_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the four application patterns and three hose stream patterns for Tests 18 and 19.
 
@@
 
+% #######################
+% # West Handline Table #
+% #######################
+
+\begin{table}[!ht]
+\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and application pattern combinations during Tests 18 and 19}
+\begin{tabular}{lcccc}
+\toprule
+ & \multicolumn{4}{c}{\underline{Test 18}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
+\\ \multicolumn{5}{c}{} \\
+\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
+\\ \midrule
+ & \multicolumn{4}{c}{\underline{Test 19}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
+\\ \multicolumn{5}{c}{} \\
+\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
+\\ \bottomrule
+\end{tabular}
+\label{table:west_hand_A10_avgs}
+\end{table}
+
+% #######################
+% # East Handline Table #
+% #######################
+
+\begin{table}[!ht]
+\caption{Average air velocity (m/s) through A6 with established flow path for the stream and application pattern combinations at each target (Room A and ceiling of Room B) during Test 34}
+\begin{tabular}{lcccccc}
+\toprule
+ & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
+\\
+\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
+\\ \multicolumn{7}{c}{} \\
+\textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
+\\ \multicolumn{7}{c}{} \\
+\textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
+\\ \bottomrule
+\end{tabular}
+\label{table:east_hand_A6_avgs}
+\end{table}
+
 %\begin{figure}[!ht]
@@
 
+% ===============
+% = CONCLUSIONS =
+% ===============
 \chapter{Conclusions}
@@
 
+% ===============
+% = FUTURE WORK =
+% ===============
 \chapter{Future Work}
@@
 
-compare to cold flow tests?
-
+% ====================
+% = ACKNOWLEDGEMENTS =
+% ====================
 \chapter{Acknowledgments}
-\label{chap:Acknowledgments}
+\label{chap:acknowledgments}
 

### 2015-09-15 Projects/DelCo_2014/Scripts/hose_test_plotting.py

@@ -1,529 +1,0 @@
-#!/usr/bin/env python
-
-import os
-import numpy as np
-import pandas as pd
-from pylab import *
-
-from matplotlib import rcParams
-rcParams.update({'figure.autolayout': True})
-
-#  =================
-#  = User Settings =
-#  =================
-
-# Location of experimental data files
-data_dir = '../Experimental_Data/'
-
-# Location of file with timing information
-timings_file = '../Experimental_Data/All_Hose_Times.csv'
-
-# Location of scaling conversion files
-scaling_file_default = '../DAQ_Files/Delco_DAQ_Channel_List.csv'
-scaling_file_master = '../DAQ_Files/Master_DelCo_DAQ_Channel_List.csv'
-scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
-scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
-results_loc = '../Experimental_Data/'
-
-# Location of test description file
-info_file = '../Experimental_Data/Description_of_Experiments.csv'
-# Hose description file
-hose_info_file = '../Experimental_Data/Description_Hose_Experiments.csv'
-
-# Duration of pre-test time for bi-directional probes and heat flux gauges (s)
-pre_test_time = 60
-
-# List of sensor groups for each plot
-sensor_groups = [['TC_A1_'], ['TC_A2_'], ['TC_A3_'], ['TC_A4_'], ['TC_A5_'],
-                 ['TC_A6_'], ['TC_A7_'], ['TC_A8_'], ['TC_A9_'], ['TC_A10_'],
-                 ['TC_A11_'], ['TC_A12_'], ['TC_A13_'], ['TC_A14_'], ['TC_A15_'],
-                 ['TC_A16_'], ['TC_A17_'], ['TC_A18_'], ['TC_A19_'],
-                 ['TC_Ignition'],
-                 ['TC_Helmet_'],
-                 ['BDP_A4_'], ['BDP_A5_'], ['BDP_A6_'], ['BDP_A7_'],
-                 ['BDP_A8_'], ['BDP_A9_'], ['BDP_A10_'], ['BDP_A11_'],
-                 ['BDP_A12_'], ['BDP_A13_'], ['BDP_A14_'], ['BDP_A15_'],
-                 ['BDP_A18_'],
-                 ['HF_', 'RAD_'],
[…]

### 2015-09-15 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -11,6 +11,20 @@ from itertools import cycle
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
 
+#  ==================
+#  = User functions =
+#  ==================
+
+# Allows printing of line number in code for custom printed error messages
+import inspect
+def lineno():
+    return inspect.currentframe().f_back.f_lineno
+
+# moving average   
+def movingaverage(interval, window_size):
+    window = np.ones(int(window_size))/float(window_size)
+    return np.convolve(interval, window, 'same')
+
 #  =================
 #  = User Settings =
 #  =================
@@ -71,9 +85,44 @@ info = pd.read_csv(info_file, index_col=3)
 # Files to skip
 skip_files = ['_times', '_reduced', '_results', 'description_']
 
-def movingaverage(interval, window_size):
-    window = np.ones(int(window_size))/float(window_size)
-    return np.convolve(interval, window, 'same')
+# ============================================
+# Execute or skip specific parts of the code =
+# ============================================
+
+result_file = False			# Generate a .csv file with channel avgs for specified sensor groups
+plotting = False			# Generate any plot?
+all_channel_plot = False	# Plot individual channels
+group_avg_plot = False		# or plot sensor group avgs
+latex_table_code = True     # Print code to generate tables in LaTeX?
+if(latex_table_code):		# specify table properties (if applicable)
+	# Create lists for column titles for desired latex tables
+	streams = ['SS', 'NF', 'WF']
+	stream_ls = pd.Series(['\\textit{Straight}', '\\textit{Narrow Fog}', '\\textit{Wide Fog}'], index = streams)
+
+	# West handline table
+	west_hand_caption = ('Average air velocity (m/s) through stairwell door with fully established flow path '
+		'for stream and application pattern combinations during Tests 18 and 19')
+	west_hand_label = 'table:west_hand_A10_avgs'
+	west_hand_columns = ['\\textbf{Stream}', '\\textbf{Fixed}', '\\textbf{Sweeping}', '\\textbf{Clockwise}', 
+		'\\begin{tabular}{@{}c@{}} \\textbf{Counter} \\\ \\textbf{Clockwise} \\\ \\end{tabular}']
+
+	# West monitor table
[…]

### 2015-09-15 Projects/DelCo_2012/Report/DelCo_2012.tex
edit files Delco2012

@@
 
+The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building.
+During each test, the fire was ignited and the fire developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
+Once this criteria was met, gas cooling began.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
+	\label{fig:CAFS_Water_Comp_7_8}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
+	\label{fig:CAFS_Water_Comp_SS_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Full Back Position}
+	\label{fig:CAFS_Water_Comp_SS_full}
+\end{figure}
+
 \section{Fire Suppression}
@@
 
-\subsection{Furniture Fuel Package}
-\label{subsec:Furniture_Fuel_Package}
-
-Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle.
-The figures provide change in temperature and heat flux at several positions and elevations through the structure.
+Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application on the furniture fuel package after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle (FSE1 in Table~\ref{tab:Test_Descriptions}).
+The figures provide change in temperature and heat flux measurements at several positions and elevations through the structure: structure doorway, hallway, and three locations within the burn room.
 These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.
@@
 
+The same fuel load, ventilation, and suppression application durations were also tested with water as the suppression agent (FSW2 in Table~\ref{tab:Test_Descriptions}).
+Figures~\ref{fig:Test_2_First_Suppression} and \ref{fig:Test_2_Second_Suppression} show the results from these tests.
+
 \begin{figure}[!ht]
@@
 \end{figure}
+
+Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial.
+Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
+The remainder of these fire suppression images for both the furniture and wood pallet fuel loads can be found in Appendix~\ref{app:fire_suppression}.
 
@@
 
-% \chapter{Appendix}
-% \label{chap:Appendix}
-
-% \section{Test 1 Figures}
-% \label{subsec:Test_1_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Eastside_Array}
-% 	\caption{Test 1 (FSE1): Eastside Array}
-% 	\label{fig:Test_1_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Westside_Array}
-% 	\caption{Test 1 (FSE1): Westside Array}
-% 	\label{fig:Test_1_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Hallway_Array}
-% 	\caption{Test 1 (FSE1): Hallway Array}
-% 	\label{fig:Test_1_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE1_Doorway_Array}
-% 	\caption{Test 1 (FSE1): Doorway Array}
-% 	\label{fig:Test_1_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Eastside_Array}
-% 	\caption{Test 1 (FSE1): Suppression Eastside Array}
-% 	\label{fig:Test_1_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Westside_Array}
-% 	\caption{Test 1 (FSE1): Suppression Westside Array}
-% 	\label{fig:Test_1_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Hallway_Array}
-% 	\caption{Test 1 (FSE1): Suppression Hallway Array}
-% 	\label{fig:Test_1_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE1_Doorway_Array}
-% 	\caption{Test 1 (FSE1): Suppression Doorway Array}
-% 	\label{fig:Test_1_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Eastside}
-% 	\caption{Test 1 (FSE1): Eastside Heat Flux}
-% 	\label{fig:Test_1_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Westside}
-% 	\caption{Test 1 (FSE1): Westside Heat Flux}
-% 	\label{fig:Test_1_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Hallway}
-% 	\caption{Test 1 (FSE1): Hallway Heat Flux}
-% 	\label{fig:Test_1_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_1_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 1 (FSE1): Heat Flux Near Fire Room}
-% 	\label{fig:Test_1_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Hallway_Velocity}
-% 	\caption{Test 1 (FSE1): Hallway Velocity}
-% 	\label{fig:Test_1_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_1_Doorway_Velocity}
-% 	\caption{Test 1 (FSE1): Doorway Velocity}
-% 	\label{fig:Test_1_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 2 Figures}
-% \label{subsec:Test_2_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Eastside_Array}
-% 	\caption{Test 2 (FSW2): Eastside Array}
-% 	\label{fig:Test_2_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Westside_Array}
-% 	\caption{Test 2 (FSW2: Westside Array}
-% 	\label{fig:Test_2_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Hallway_Array}
-% 	\caption{Test 2 (FSW2): Hallway Array}
-% 	\label{fig:Test_2_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW2_Doorway_Array}
-% 	\caption{Test 2 (FSW2): Doorway Array}
-% 	\label{fig:Test_2_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Eastside_Array}
-% 	\caption{Test 2 (FSW2): Suppression Eastside Array}
-% 	\label{fig:Test_2_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Westside_Array}
-% 	\caption{Test 2 (FSW2): Suppression Westside Array}
-% 	\label{fig:Test_2_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Hallway_Array}
-% 	\caption{Test 2 (FSW2): Suppression Hallway Array}
-% 	\label{fig:Test_2_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW2_Doorway_Array}
-% 	\caption{Test 2 (FSW2): Suppression Doorway Array}
-% 	\label{fig:Test_2_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Eastside}
-% 	\caption{Test 2 (FSW2): Eastside Heat Flux}
-% 	\label{fig:Test_2_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Westside}
-% 	\caption{Test 2 (FSW2): Westside Heat Flux}
-% 	\label{fig:Test_2_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Hallway}
-% 	\caption{Test 2 (FSW2): Hallway Heat Flux}
-% 	\label{fig:Test_2_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_2_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 2 (FSW2): Heat Flux Near Fire Room}
-% 	\label{fig:Test_2_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Hallway_Velocity}
-% 	\caption{Test 2 (FSW2): Hallway Velocity}
-% 	\label{fig:Test_2_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_2_Doorway_Velocity}
-% 	\caption{Test 2 (FSW2): Doorway Velocity}
-% 	\label{fig:Test_2_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 3 Figures}
-% \label{subsec:Test_3_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Eastside_Array}
-% 	\caption{Test 3 (FSW3): Eastside Array}
-% 	\label{fig:Test_3_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Westside_Array}
-% 	\caption{Test 3 (FSW3: Westside Array}
-% 	\label{fig:Test_3_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Hallway_Array}
-% 	\caption{Test 3 (FSW3): Hallway Array}
-% 	\label{fig:Test_3_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW3_Doorway_Array}
-% 	\caption{Test 3 (FSW3): Doorway Array}
-% 	\label{fig:Test_3_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Eastside_Array}
-% 	\caption{Test 3 (FSW3): Suppression Eastside Array}
-% 	\label{fig:Test_3_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Westside_Array}
-% 	\caption{Test 3 (FSW3): Suppression Westside Array}
-% 	\label{fig:Test_3_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Hallway_Array}
-% 	\caption{Test 3 (FSW3): Suppression Hallway Array}
-% 	\label{fig:Test_3_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW3_Doorway_Array}
-% 	\caption{Test 3 (FSW3): Suppression Doorway Array}
-% 	\label{fig:Test_3_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Eastside}
-% 	\caption{Test 3 (FSW3): Eastside Heat Flux}
-% 	\label{fig:Test_3_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Westside}
-% 	\caption{Test 3 (FSW3): Westside Heat Flux}
-% 	\label{fig:Test_3_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Hallway}
-% 	\caption{Test 3 (FSW3): Hallway Heat Flux}
-% 	\label{fig:Test_3_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_3_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 3 (FSW3): Heat Flux Near Fire Room}
-% 	\label{fig:Test_3_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Hallway_Velocity}
-% 	\caption{Test 3 (FSW3): Hallway Velocity}
-% 	\label{fig:Test_3_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_3_Doorway_Velocity}
-% 	\caption{Test 3 (FSW3): Doorway Velocity}
-% 	\label{fig:Test_3_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 4 Figures}
-% \label{subsec:Test_4_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Eastside_Array}
-% 	\caption{Test 4 (FSE4): Eastside Array}
-% 	\label{fig:Test_4_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Westside_Array}
-% 	\caption{Test 4 (FSE4): Westside Array}
-% 	\label{fig:Test_4_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Hallway_Array}
-% 	\caption{Test 4 (FSE4): Hallway Array}
-% 	\label{fig:Test_4_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE4_Doorway_Array}
-% 	\caption{Test 4 (FSE4): Doorway Array}
-% 	\label{fig:Test_4_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Eastside_Array}
-% 	\caption{Test 4 (FSE4): Suppression Eastside Array}
-% 	\label{fig:Test_4_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Westside_Array}
-% 	\caption{Test 4 (FSE4): Suppression Westside Array}
-% 	\label{fig:Test_4_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Hallway_Array}
-% 	\caption{Test 4 (FSE4): Suppression Hallway Array}
-% 	\label{fig:Test_4_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE4_Doorway_Array}
-% 	\caption{Test 4 (FSE4): Suppression Doorway Array}
-% 	\label{fig:Test_4_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Eastside}
-% 	\caption{Test 4 (FSE4): Eastside Heat Flux}
-% 	\label{fig:Test_4_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Westside}
-% 	\caption{Test 4 (FSE4): Westside Heat Flux}
-% 	\label{fig:Test_4_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Hallway}
-% 	\caption{Test 4 (FSE4): Hallway Heat Flux}
-% 	\label{fig:Test_4_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_4_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 4 (FSE4): Heat Flux Near Fire Room}
-% 	\label{fig:Test_4_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Hallway_Velocity}
-% 	\caption{Test 4 (FSE4): Hallway Velocity}
-% 	\label{fig:Test_4_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_4_Doorway_Velocity}
-% 	\caption{Test 4 (FSE4): Doorway Velocity}
-% 	\label{fig:Test_4_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 5 Figures}
-% \label{subsec:Test_5_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Eastside_Array}
-% 	\caption{Test 5 (FSE5): Eastside Array}
-% 	\label{fig:Test_5_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Westside_Array}
-% 	\caption{Test 5 (FSE5): Westside Array}
-% 	\label{fig:Test_5_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Hallway_Array}
-% 	\caption{Test 5 (FSE5): Hallway Array}
-% 	\label{fig:Test_5_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE5_Doorway_Array}
-% 	\caption{Test 5 (FSE5): Doorway Array}
-% 	\label{fig:Test_5_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Eastside_Array}
-% 	\caption{Test 5 (FSE5): Suppression Eastside Array}
-% 	\label{fig:Test_5_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Westside_Array}
-% 	\caption{Test 5 (FSE5): Suppression Westside Array}
-% 	\label{fig:Test_5_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Hallway_Array}
-% 	\caption{Test 5 (FSE5): Suppression Hallway Array}
-% 	\label{fig:Test_5_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE5_Doorway_Array}
-% 	\caption{Test 5 (FSE5): Suppression Doorway Array}
-% 	\label{fig:Test_5_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Eastside}
-% 	\caption{Test 5 (FSE5): Eastside Heat Flux}
-% 	\label{fig:Test_5_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Westside}
-% 	\caption{Test 5 (FSE5): Westside Heat Flux}
-% 	\label{fig:Test_5_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Hallway}
-% 	\caption{Test 5 (FSE5): Hallway Heat Flux}
-% 	\label{fig:Test_5_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_5_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 5 (FSE5): Heat Flux Near Fire Room}
-% 	\label{fig:Test_5_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Hallway_Velocity}
-% 	\caption{Test 5 (FSE5): Hallway Velocity}
-% 	\label{fig:Test_5_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_5_Doorway_Velocity}
-% 	\caption{Test 5 (FSE5): Doorway Velocity}
-% 	\label{fig:Test_5_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 6 Figures}
-% \label{subsec:Test_6_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Eastside_Array}
-% 	\caption{Test 6 (FSW6): Eastside Array}
-% 	\label{fig:Test_6_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Westside_Array}
-% 	\caption{Test 6 (FSW6: Westside Array}
-% 	\label{fig:Test_6_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Hallway_Array}
-% 	\caption{Test 6 (FSW6): Hallway Array}
-% 	\label{fig:Test_6_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW6_Doorway_Array}
-% 	\caption{Test 6 (FSW6): Doorway Array}
-% 	\label{fig:Test_6_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Eastside_Array}
-% 	\caption{Test 6 (FSW6): Suppression Eastside Array}
-% 	\label{fig:Test_6_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Westside_Array}
-% 	\caption{Test 6 (FSW6): Suppression Westside Array}
-% 	\label{fig:Test_6_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Hallway_Array}
-% 	\caption{Test 6 (FSW6): Suppression Hallway Array}
-% 	\label{fig:Test_6_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW6_Doorway_Array}
-% 	\caption{Test 6 (FSW6): Suppression Doorway Array}
-% 	\label{fig:Test_6_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Eastside}
-% 	\caption{Test 6 (FSW6): Eastside Heat Flux}
-% 	\label{fig:Test_6_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Westside}
-% 	\caption{Test 6 (FSW6): Westside Heat Flux}
-% 	\label{fig:Test_6_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Hallway}
-% 	\caption{Test 6 (FSW6): Hallway Heat Flux}
-% 	\label{fig:Test_6_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_6_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 6 (FSW6): Heat Flux Near Fire Room}
-% 	\label{fig:Test_6_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Hallway_Velocity}
-% 	\caption{Test 6 (FSW6): Hallway Velocity}
-% 	\label{fig:Test_6_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_6_Doorway_Velocity}
-% 	\caption{Test 6 (FSW6): Doorway Velocity}
-% 	\label{fig:Test_6_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 7 Figures}
-% \label{subsec:Test_7_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Eastside_Array}
-% 	\caption{Test 7 (FSW7): Eastside Array}
-% 	\label{fig:Test_7_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Westside_Array}
-% 	\caption{Test 7 (FSW7: Westside Array}
-% 	\label{fig:Test_7_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Hallway_Array}
-% 	\caption{Test 7 (FSW7): Hallway Array}
-% 	\label{fig:Test_7_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSW7_Doorway_Array}
-% 	\caption{Test 7 (FSW7): Doorway Array}
-% 	\label{fig:Test_7_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Eastside_Array}
-% 	\caption{Test 7 (FSW7): Suppression Eastside Array}
-% 	\label{fig:Test_7_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Westside_Array}
-% 	\caption{Test 7 (FSW7): Suppression Westside Array}
-% 	\label{fig:Test_7_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Hallway_Array}
-% 	\caption{Test 7 (FSW7): Suppression Hallway Array}
-% 	\label{fig:Test_7_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSW7_Doorway_Array}
-% 	\caption{Test 7 (FSW7): Suppression Doorway Array}
-% 	\label{fig:Test_7_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Eastside}
-% 	\caption{Test 7 (FSW7): Eastside Heat Flux}
-% 	\label{fig:Test_7_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Westside}
-% 	\caption{Test 7 (FSW7): Westside Heat Flux}
-% 	\label{fig:Test_7_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Hallway}
-% 	\caption{Test 7 (FSW7): Hallway Heat Flux}
-% 	\label{fig:Test_7_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSW_Test_7_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 7 (FSW7): Heat Flux Near Fire Room}
-% 	\label{fig:Test_7_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Hallway_Velocity}
-% 	\caption{Test 7 (FSW7): Hallway Velocity}
-% 	\label{fig:Test_7_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSW_Test_7_Doorway_Velocity}
-% 	\caption{Test 7 (FSW7): Doorway Velocity}
-% 	\label{fig:Test_7_Doorway_Velocity}
-% \end{figure}
-
-% \clearpage
-
-% \section{Test 8 Figures}
-% \label{subsec:Test_8_Figures}
-
-% \subsection{Temperature}
-% \label{subsec:Temperature}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Eastside_Array}
-% 	\caption{Test 8 (FSE8): Eastside Array}
-% 	\label{fig:Test_8_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Westside_Array}
-% 	\caption{Test 8 (FSE8): Westside Array}
-% 	\label{fig:Test_8_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Hallway_Array}
-% 	\caption{Test 8 (FSE8): Hallway Array}
-% 	\label{fig:Test_8_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/FSE8_Doorway_Array}
-% 	\caption{Test 8 (FSE8): Doorway Array}
-% 	\label{fig:Test_8_Doorway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Eastside_Array}
-% 	\caption{Test 8 (FSE8): Suppression Eastside Array}
-% 	\label{fig:Test_8_Suppression_Eastside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Westside_Array}
-% 	\caption{Test 8 (FSE8): Suppression Westside Array}
-% 	\label{fig:Test_8_Suppression_Westside_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Hallway_Array}
-% 	\caption{Test 8 (FSE8): Suppression Hallway Array}
-% 	\label{fig:Test_8_Suppression_Hallway_Array}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Temperature/Suppression_FSE8_Doorway_Array}
-% 	\caption{Test 8 (FSE8): Suppression Doorway Array}
-% 	\label{fig:Test_8_Suppression_Doorway_Array}
-% \end{figure}
-
-% \subsection{Heat Flux}
-% \label{subsec:Heat_Flux}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Eastside}
-% 	\caption{Test 8 (FSE8): Eastside Heat Flux}
-% 	\label{fig:Test_8_Eastside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Westside}
-% 	\caption{Test 8 (FSE8): Westside Heat Flux}
-% 	\label{fig:Test_8_Westside_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Hallway}
-% 	\caption{Test 8 (FSE8): Hallway Heat Flux}
-% 	\label{fig:Test_8_Hallway_Heat_Flux}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Heat_Flux/FSE_Test_8_Heat_Flux_Near_Fire_Room}
-% 	\caption{Test 8 (FSE8): Heat Flux Near Fire Room}
-% 	\label{fig:Test_8_Heat_Flux_Near_Fire_Room}
-% \end{figure}
-
-% \subsection{Velocity}
-% \label{subsec:Velocity}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Hallway_Velocity}
-% 	\caption{Test 8 (FSE8): Hallway Velocity}
-% 	\label{fig:Test_8_Hallway_Velocity}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Velocity/FSE_Test_8_Doorway_Velocity}
-% 	\caption{Test 8 (FSE8): Doorway Velocity}
-% 	\label{fig:Test_8_Doorway_Velocity}
-% \end{figure}
-
-\clearpage
-
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB2}
-	\caption{Burn Building Test 2}
-	\label{fig:Burn_Building_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB3}
-	\caption{Burn Building Test 3}
-	\label{fig:Burn_Building_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB4}
-	\caption{Burn Building Test 4}
-	\label{fig:Burn_Building_Test_4}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB5}
-	\caption{Burn Building Test 5}
-	\label{fig:Burn_Building_Test_5}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB6}
-	\caption{Burn Building Test 6}
-	\label{fig:Burn_Building_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB8}
-	\caption{Burn Building Test 8}
-	\label{fig:Burn_Building_Test_8}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB9}
-	\caption{Burn Building Test 9}
-	\label{fig:Burn_Building_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB10}
-	\caption{Burn Building Test 10}
-	\label{fig:Burn_Building_Test_10}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB11}
-	\caption{Burn Building Test 11}
-	\label{fig:Burn_Building_Test_11}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB12}
-	\caption{Burn Building Test 12}
-	\label{fig:Burn_Building_Test_12}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB13}
-	\caption{Burn Building Test 13}
-	\label{fig:Burn_Building_Test_13}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB14}
-	\caption{Burn Building Test 14}
-	\label{fig:Burn_Building_Test_14}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB15}
-	\caption{Burn Building Test 15}
-	\label{fig:Burn_Building_Test_15}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB16}
-	\caption{Burn Building Test 16}
-	\label{fig:Burn_Building_Test_16}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB17}
-	\caption{Burn Building Test 17}
-	\label{fig:Burn_Building_Test_17}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB18}
-	\caption{Burn Building Test 18}
-	\label{fig:Burn_Building_Test_18}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB19}
-	\caption{Burn Building Test 19}
-	\label{fig:Burn_Building_Test_19}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB20}
-	\caption{Burn Building Test 20}
-	\label{fig:Burn_Building_Test_20}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/BB21}
-	\caption{Burn Building Test 21}
-	\label{fig:Burn_Building_Test_21}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_1}
-	\caption{Experimental Structures Test 1}
-	\label{fig:Experimental_Structures_Test_1}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_2}
-	\caption{Experimental Structures Test 2}
-	\label{fig:Experimental_Structures_Test_2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_3}
-	\caption{Experimental Structures Test 3}
-	\label{fig:Experimental_Structures_Test_3}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_4}
-	\caption{Experimental Structures Test 4}
-	\label{fig:Experimental_Structures_Test_4}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_5}
-	\caption{Experimental Structures Test 5}
-	\label{fig:Experimental_Structures_Test_5}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_6}
-	\caption{Experimental Structures Test 6}
-	\label{fig:Experimental_Structures_Test_6}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_7}
-	\caption{Experimental Structures Test 7}
-	\label{fig:Experimental_Structures_Test_7}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_72}
-	\caption{Experimental Structures Test 7.2}
-	\label{fig:Experimental_Structures_Test_7.2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_8}
-	\caption{Experimental Structures Test 8}
-	\label{fig:Experimental_Structures_Test_8}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_9}
-	\caption{Experimental Structures Test 9}
-	\label{fig:Experimental_Structures_Test_9}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_10}
-	\caption{Experimental Structures Test 10}
-	\label{fig:Experimental_Structures_Test_10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Bars/ES_11}
-	\caption{Experimental Structures Test 11}
-	\label{fig:Experimental_Structures_Test_11}
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB2} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB3} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB4} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB5}
+\end{tabular*}
+\caption{Spray density figures for burn building tests 2 (upper left), 3 (upper right), 4 (lower left), and 5 (lower right).}
+\label{fig:bb_2_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB6} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB8} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB10}
+\end{tabular*}
+\caption{Spray density figures for burn building tests 6 (upper left), 8 (upper right), 9 (lower left), and 10 (lower right).}
+\label{fig:bb_6_10}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB11} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB12} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB13} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB14}
+\end{tabular*}
+\caption{Spray density figures for burn building tests 11 (upper left), 12 (upper right), 13 (lower left), and 14 (lower right).}
+\label{fig:bb_11_14}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB15} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB16} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB17} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB18}
+\end{tabular*}
+\caption{Spray density figures for burn building tests 15 (upper left), 16 (upper right), 17 (lower left), and 18 (lower right).}
+\label{fig:bb_15_18}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB19} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB20} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB21} \\
+\end{tabular*}
+\caption{Spray density figures for burn building tests 19 (upper left), 20 (upper right), and 21 (lower).}
+\label{fig:bb_19_21}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/ES_1} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_2} \\
+\includegraphics[width=3.2in]{../Figures/Bars/ES_3} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_4}
+\end{tabular*}
+\caption{Spray density figures for experimental structure tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
+\label{fig:es_1_4}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/ES_5} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_6} \\
+\includegraphics[width=3.2in]{../Figures/Bars/ES_7} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_72}
+\end{tabular*}
+\caption{Spray density figures for experimental structure tests 5 (upper left), 6 (upper right), 7 (lower left), and 7.2 (lower right).}
+\label{fig:es_5_72}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/ES_8} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_9} \\
+\includegraphics[width=3.2in]{../Figures/Bars/ES_10} &
+\includegraphics[width=3.2in]{../Figures/Bars/ES_11}
+\end{tabular*}
+\caption{Spray density figures for experimental structure tests 8 (upper left), 9 (upper right), 10 (lower left), and 11 (lower right).}
+\label{fig:es_8_11}
 \end{figure}
@@
 
-\clearpage
-
 \begin{figure}[!ht]
@@
 
-\clearpage
-
 \end{document}

### 2015-09-15 Projects/DelCo_2012/Scripts/gas_cooling_plot.py

@@ -90,7 +90,7 @@ for f in os.listdir(data_dir):
 						quantity = data[channel]
 						ylabel('Temperature ($^\circ$C)', fontsize=20)
 						line_style = '-'
-						ylim([0,800])
+						ylim([0,600])
 
 					if 'BDP_' in channel:
 						conv_inch_h2o = 0.4
@@ -127,7 +127,7 @@ for f in os.listdir(data_dir):
 							 lw=1.5,
 							 ls=line_style,
 							 marker=next(plot_markers),
-							 markevery=int((end_of_test - start_of_test)/10),
+							 markevery=int((end_of_test - start_of_test)/20),
 							 mew=1.5,
                              mec='none',
                              ms=7,label=zero['Test Specific Name'][channel])
@@ -138,10 +138,10 @@ for f in os.listdir(data_dir):
 			ax1.xaxis.set_major_locator(MaxNLocator(8))
 			ax1_xlims = ax1.axis()[0:2]
 			grid(True)
-			xlabel('Time', fontsize=20)
+			xlabel('Time (s)', fontsize=20)
 			xticks(fontsize=16)
 			yticks(fontsize=16)
-			legend(loc='lower right', fontsize=8)
+			legend(loc='upper left', fontsize=8)
 
 			print 'Plotting', group
 			savefig('../Figures/Gas_Cooling/' + test_name + '_' + group[0].rstrip('_') + '.pdf')

### 2015-09-18 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: began adding code for specific hose stream report plots

@@
 
-Test 33 involved flowing water using a monitor equipped with a combination nozzle from Room C to the ceiling of Room B in the East Structure (Fig.~\ref{fig:test_33_pic}).
+Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}).
 A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
@@
 % Add flow chart? %
-Tests 16 and 17 followed identical procedures that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
+Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
 The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
-The difference between the tests was that Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
 Each test began by flowing water in a straight stream pattern at the far target for 60 seconds.
@@
 One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Then, water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target.
-The entire process was repeated for the narrow fog and wide fog streams.
+Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target.
+The entire process was repeated using the narrow fog and wide fog streams.
 Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.
@@
 Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water.
-One test series, Test 34, occurred in the East Structure, and the two other series, Tests 18 and 19, occurred in the West Structure.
+One test series, Test 34, occurred in the East Structure, and the other two series, Tests 18 and 19, occurred in the West Structure.
 
-Test 34 involved flowing water using a 1.75" handline equipped with a combination nozzle located inside Room C.
+During Test 34, water was flowed from a 1.75" handline equipped with a combination nozzle located inside Room C.
 A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
@@
 Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/East_handline_C_BC.pdf}
-\caption[Straight Stream and Narrow Fog Stream during Tests 31 and 32]{Straight stream (left column) and narrow fog stream (right column) aimed at ceiling of Room C (top row) and Door BC (bottom row) during Tests 31 and 32}
-\label{fig:test_31_32_pic}
-\end{figure}
 
@@
 \end{figure}
-\FloatBarrier
 
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1 \nicefrac{3}{4}" handline.
+Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline.
 The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}).
@@
 One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Then, water flow stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns.
-This entire procedure was repeated for narrow fog and wide fog streams.
-
+Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns.
+This entire procedure was repeated using narrow fog and wide fog streams.
+Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18.
 \begin{figure}[!ht]
@@
 Tables~\ref{table:Tests_16_17_BDP_A10_Avgs} and~\ref{table:Tests_16_17_BDP_A13_Avgs} contain the average air velocity measured by the bi-directional probes at A10 and A13, respectively, when the flow path was completely established for each hose stream pattern and application location for Tests 16 and 17.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
-% \caption{Average Velocity through Stairwell Door, Test 16, All Streams}
-% \label{fig:Test_16_BDP_A10_Avg_All}
-% \end{figure}
-
-\clearpage
 

### 2015-09-18 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -6,24 +6,12 @@ import numpy as np
 import pandas as pd
 from pylab import *
 import math
+import inspect
 from itertools import cycle
 
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
 
-#  ==================
-#  = User functions =
-#  ==================
-
-# Allows printing of line number in code for custom printed error messages
-import inspect
-def lineno():
-    return inspect.currentframe().f_back.f_lineno
-
-# moving average   
-def movingaverage(interval, window_size):
-    window = np.ones(int(window_size))/float(window_size)
-    return np.convolve(interval, window, 'same')
 
 #  =================
 #  = User Settings =
@@ -90,10 +78,11 @@ skip_files = ['_times', '_reduced', '_results', 'description_']
 # ============================================
 
 result_file = False			# Generate a .csv file with channel avgs for specified sensor groups
-plotting = False			# Generate any plot?
-all_channel_plot = False	# Plot individual channels
-group_avg_plot = False		# or plot sensor group avgs
-latex_table_code = True     # Print code to generate tables in LaTeX?
+plotting = True	  			# Generate any plot?
+all_channel_plot = True 	# Plot individual channels
+group_avg_plot = False		# Plot sensor group avgs
+monitor_avgs_plot = False	# Plot BDP avgs from monitor experiments for SS, NF, WF application
+latex_table_code = False    # Print code to generate tables in LaTeX?
 if(latex_table_code):		# specify table properties (if applicable)
 	# Create lists for column titles for desired latex tables
 	streams = ['SS', 'NF', 'WF']
@@ -123,6 +112,54 @@ if(latex_table_code):		# specify table properties (if applicable)
 	# East monitor table
 	# east monitor data currently included in west monitor table #
 
+#  ==================
+#  = User functions =
+#  ==================
+
+# Allows printing of line number in code for custom printed error messages
+def lineno():
+    return inspect.currentframe().f_back.f_lineno
+
+def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name):
+	plt.errorbar(x_max_index, y_max, yerr=(.18)*y_max, ecolor='k')
[…]

### 2015-09-23 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: Generated new figs for report, deleted old figs

@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.25cm 4cm, clip=true, width=6in]{../Drawings/East_Structure_Metric_Simple}
-\caption[East Structure Layout]{East Structure floor layout. All dimensions are in meters.}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Test_Structure_Dimensioned}
+\caption[East Structure Layout]{East Structure floor layout.}
 \label{fig:east_general_plan}
@@
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/West_Structure_1st_Floor_Metric_Simple}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_1st_Floor_Dimensioned}
 \\
-\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/West_Structure_2nd_Floor_Metric_Simple}
-\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts. All dimensions are in meters.}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_2nd_Floor_Dimensioned}
+\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts.}
 \label{fig:west_general_plan}
@@
 Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
-Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
+The Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
 Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure.
@@
 Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}).
-A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
+A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:east_setup}.
 Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
@@
 \begin{figure}[!ht]
-\begin{overpic}[trim=0cm 0cm 0cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/East_Structure_Hose_Test_33_34}
-	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
-\end{overpic}
+% \begin{overpic}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
+% 	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
+% \end{overpic}
 \caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
-\label{fig:test_33_34_setup}
+\label{fig:east_setup}
 \end{figure}

### 2015-09-23 Projects/DelCo_2014/Scripts/hose_test_sorting_plotting_avgs.py

@@ -537,6 +537,8 @@ for f in os.listdir(data_dir):
 							print ' Plotting channel ' + channel
 
 						save_plot(x_max_index, y_max, y_min, start_plot, end_plot, group, fig_name)
+						y_min = 0
+						y_max = 0
 
 					if(group_avg_plot):
 						fig = figure()
@@ -545,20 +547,38 @@ for f in os.listdir(data_dir):
 						axis_scale = 'Y Scale BDP'
 						fig_name = fig_dir + test_name + '_' + group[0].rstrip('_') + '_avg.pdf'
 
-						quantity = group_data['Avg']
-						ma_quantity = movingaverage(quantity, 5)
+						quantity = plot_data['Avg']
+						ma_quantity = pd.rolling_mean(quantity, 5)
+						ma_quantity = ma_quantity.fillna(method='bfill')
 						y_max = max(ma_quantity)
 						y_min = min(ma_quantity)
 
 						plot(t, ma_quantity, lw=1.5, ls=line_style, label=group_results.columns[5:-1], color = 'b')
 
-						save_plot(x_max_index, y_max, y_min, start_of_test, end_of_test, group, fig_name)
+						save_plot(x_max_index, y_max, y_min, start_plot, end_plot, group, fig_name)
+						y_min = 0
+						y_max = 0
 
-					# if(monitor_avgs_plot):
-					# 	# create lists to use in plots after all files have been read
-					# 	# 
-					# 	if 'Test_16' in test_name:
-					# 		for index, row 
+					if(monitor_avgs_plot):
+						fig = plt.figure()
+						ylabel('Velocity (m/s)', fontsize=20)
+						line_style = '-'
+						axis_scale = 'Y Scale BDP'
+						fig_name = fig_dir + test_name + '_' + group[0].rstrip('_') + 'stream_avgs.pdf'
+
+						plot_markers = cycle(['s', 'o', '^', 'd', 'h', 'p','v','8','D','*','<','>','H'])
+
+						# create lists to use in plots after all files have been read
+						if 'Test_16' in test_name:
+							for index, row in group_results.iterrows():
+								seq_start = row['Start']
+								seq_end = row['End']
+								if row['Stream'] == 'SS':
+									if row['Door'] == 'All Closed':
+										if row['Location'] == 'Near':
[…]

### 2015-09-28 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
DelCo_2014: new pics to hose stream report, edited plotting script to generate new figs. for report

@@
 
+\newpage
+
+\chapter{List of Symbols}
+\begin{tabbing}
+\hspace{1.5in} \= \\
+ft \> foot \\
+GPM \> gallons per minute \\
+in. \> inch \\
+m \> meter \\
+\end{tabbing}
+
 \mainmatter
@@
 % ================
-
 \chapter{Introduction}
 \label{chap:intro}
-NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire.
+\section{Background}
+\label{sec:background}
+%More hose stream studies and explanations
+
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{}.
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
@@
 
-Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the line or if ventilation inducing hand line tactics are in practice.
-This research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
+Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice~\cite{}.
+Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
 
-This report is concerned with examining the impact of hose stream and application pattern selection on the ventilation inside a structure with various flow path configurations.
-Experiments in which water was flowed using various stream and application patterns into a structure with different flow path configurations were conducted.
-Air velocities were measured and used to determine the impact of hose stream and application pattern combinations on ventilation throughout the structure.
+There exists a multitude of different tools, methods, and techniques used to apply water for fire suppression using hose streams.
+A common type of nozzle that is used to apply water during fire suppression in residential structures is a fog nozzle.
+Most fog nozzles contain an adjustable tip that can be rotated to produce different stream patterns and are therefore often referred to as combination nozzles.
+%\textit{Essentials of Fire Fighting} defines 
+%https://docs.google.com/presentation/d/1hZ5DZhYXxCkcIEHNZKumH48b_Q53iM2D7asXkMYlVMM/embed?hl=en&size=l&slide=id.p39
 
-Three types of hose streams were each applied in four different fashions during each set of hose flow experiments.
-The three types of hose stream patterns studied, pictured in Figure~\ref{fig:hose_streams}, were straight stream, narrow fog stream, and wide fog stream.
-Water was flowed into the structure by having the hose in a static, fixed position, moving the hose line left-to-right across the room in a sweeping motion, and rotating the hose line in both the clockwise and counterclockwise directions.
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
-\caption[Different Hose Stream Patterns]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
-\label{fig:hose_streams}
-\end{figure}
-\FloatBarrier
-
-\section{Background}
-\label{sec:background}
 %http://www.tft.com/literature/library/files/bfa.pdf
-Nelson and Royer suggest using a clockwise rotation instead of a counterclockwise application pattern for the following reasons:
+%Keith Royer, WATER FOR FIRE FIGHTING, p. 7
+In addition to the type of stream pattern used, fire suppression tactics using hose streams can differ in the method used to apply the hose stream.
+For example, Nelson and Royer suggest using a clockwise rotation instead of a counterclockwise application pattern for the following reasons:
 \begin{enumerate} 
@@
 
+**** better explanation of hose streams with more complete content and information about existing research to be added ****
+
+\section{Objectives}
+\label{sec:objectives}
+This report is concerned with examining the impact of hose stream and application pattern selection on air movement inside a residential structure.
+Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
+More specifically, the experiments were conducted to fulfill the following objectives:
+\begin{enumerate}
+\item Determine which hose stream patterns cause significant air movement in a structure and the amount of air movement they induce compared to other stream patterns
+\item Determine the impact of different water application patterns on the ventilation in a structure
+\end{enumerate}
+
+Three types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
+The three types of hose stream patterns studied, pictured in Figure~\ref{fig:hose_streams}, were straight stream, narrow fog stream, and wide fog stream.
+Water was flowed into the structure by having the hose in a static, or fixed, position, by moving the hose line left-to-right across the room in a sweeping motion, and by rotating the hose line in both the clockwise and counterclockwise directions.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
+\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
+\label{fig:hose_streams}
+\end{figure}
+\FloatBarrier
+
 % =========================
@@
 \label{chap:exp_overview}
-To study the impact of different hose stream and application pattern selections on air movement inside a structure, numerous experiments were conducted in structures with different ventilation patterns.
+
+To study the impact of different hose stream and application pattern selections on air movement inside a structure, various water flow experiments were conducted in two experimental structures designed to replicate typical residential structures.
+The experiments focused on studying the differences in amount of air movement caused by specific combinations of three different hose stream patterns and four different water application patterns.
 
@@
 
+The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+Sensors were installed throughout the residential-sized test structures to measure air velocity during the water flow experiments.
+
 \subsection{Test Structures}
 \label{subsec:test_structs}
-The series of field experiments described in this report was conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
 
@@
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-They were designed to simulate a single-story and a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks shaped as cubes with each side measuring approximately 0.61 m (2 ft) in length.
-The interior dimensions of each structure were 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The structures were designed to simulate a single-story and a two-story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft).
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 The interior walls of the first floor of each structure were framed with steel studs and track.
-The studs were set to 0.40 m (16 in) centers.
-The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in) x 44 mm (1.75 in) and an 11 mm (0.43 in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and grove, 18.3 mm (0.72 in) thick, oriented strand board was screwed to the top of the TJIs.
+The studs were set to 0.40 m (16 in.) centers.
+The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in.) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in.) x 44 mm (1.75 in.) and an 11 mm (0.43 in.) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Tongue and grove, 18.3 mm (0.72 in.) thick, oriented strand board was screwed to the top of the TJIs.
 
@@
 \includegraphics[width=6in]{../Pictures/TJI_support}
-\caption[Truss Joist I-Beams]{Truss joist I-beams used for the ceiling/floor support in the West Structure}
+\caption[TJI-constructred ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams.
+View is of the east side of the structure.}
 \label{fig:TJI}
 \end{figure}
+\FloatBarrier
 
-The second story of the two level structure was built on the wood floor assembly as described above. The walls were framed with wood studs..**** NEED MORE DETAILS ******
+**** NEED TO GET SECOND STORY CONSTRUCTION DETAILS and then write a description of it here ****
 
-The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
+The second floor of the West Structure was built on the wood floor assembly as described above. The walls were framed with wood studs set to 0.40 m (16 in.) centers.
+% The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
 The ceiling of the burn room was the exposed "floor assembly".
-The walls of the hallway and entry foyer were composed of 16 mm (0.38 in) Type X gypsum room.
+The walls of the hallway and entry foyer were composed of 16 mm (0.38 in) Type ****X**** gypsum room.
 The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
@@
 \includegraphics[width=6in]{../Pictures/west_structure}
-\caption[East and West Test Structures]{East (top) and West (bottom) Test Structures}
+\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
 \label{fig:struct_pics}
@@
 \label{subsubsec:layout}
-**** Dimension detail, introduce floor plan figures, etc. ****
+The interior dimensions of each structure were approximately 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
+All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Test_Structure_Dimensioned}
-\caption[East Structure Layout]{East Structure floor layout.}
+\includegraphics[width=6in]{../Drawings/East_Test_Structure_Dimensioned}
+\caption[Plan view of the East Structure.]{East Structure floor layout.}
 \label{fig:east_general_plan}
 \end{figure}
-
-\clearpage
+\FloatBarrier
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_1st_Floor_Dimensioned}
-\\
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Test_Structure_2nd_Floor_Dimensioned}
-\caption[West Structure First and Second Floor Layout]{West Structure first floor (top) and second floor (bottom) layouts.}
+\includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
+\includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
+\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the first floor (top) and second floor (bottom) of the West Structure.}
 \label{fig:west_general_plan}
@@
 \label{subsec:instrumentation}
-There is a discussion of uncertainties for each measurement below in Section~\ref{subsec:uncertainty}.
-Gas velocity was measured at various doorways using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
-The Each set of BDPs contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
-Fig.~\ref{fig:BDPs} shows a picture of two sets of BDPs, A5 and A6, located at each double door on the first floor of the West Structure.
-To avoid potential measurement errors due to external environmental conditions, only velocity data measured by BDPs located in interior doorways were considered during analyses.
-Schematic plan overviews of the instrumentation in the East and West Structures are provided in Fig.~\ref{fig:east_devices} and Fig.~\ref{fig:west_devices}.
-A single thermocouple was attached to each bi-directional probe.
-The thermocouples that are used with the bi-directional probes are exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in) diameter.
-Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in) diameter Inconel shield, 0.76 m (2.5 ft) in length.
+A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{subsec:uncertainty}.
+For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
+An array of 6 BDPs located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
+A single thermocouple was attached to each BDP to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
+Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in.) diameter.
+Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in.) diameter Inconel shield that was 0.76 m (2.5 ft) in length.
+
+The approximate locations of the BDPs used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}.
+To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report.
+The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80 m below the soffit of the doorway.
+The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
 
 \begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.25cm 3.75cm, clip=true, width=6in]{../Drawings/Instrumentation/East_Structure_Devices_Hose_Test}
-\caption[Location of Instrumentation in East Structure]{Location of instrumentation in East Structure}
-\label{fig:east_devices}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_1st_Floor}
-\\
-\includegraphics[trim=0cm 0cm 0.75cm 5.0cm, clip=true, width=6in]{../Drawings/Instrumentation/West_Test_Structure_Devices_Hose_Test_2nd_Floor}
-\caption[Location of Instrumentation in West Structure]{Location of instrumentation in West Structure}
-\label{fig:west_devices}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/BDPs}
-\caption[Sets of Bi-directional Velocity Probes in Doorway of West Structure]{Two sets (A5 and A6) of bi-directional velocity probes in each doorway of the double doors on the first floor of the West Structure}
+\includegraphics[width=3.5in]{../Pictures/BDPs_east}
+\caption[Array of BDPs at interior doorway in East Structure.]{Array of BDPs located at the northeast interior doorway in the East Structure. View is looking at the array from Room C.}
 \label{fig:BDPs}
 \end{figure}
+\FloatBarrier
 
@@
 \label{subsec:uncertainty}
-There are different components of uncertainty in the length, differential pressure, and gas velocity reported here.
+There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity reported here.
 Uncertainties are grouped into two categories according to the method used to estimate them.
@@
 
-Each length measurement was taken carefully. Length measurements such as the room dimensions,
-instrumentation array locations, and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}.
+Each length measurement was taken carefully. Length measurements such as room dimensions,
+instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in.) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}.
 However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
 Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in) for 30.5 m (100 ft) tapes~\cite{NIST_Manual_44}.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in.) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in.) for 30.5 m (100 ft) tapes~\cite{NIST_Manual_44}.
 Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
 
-Bi-directional probes and single thermocouples were used to measure the velocity.
-The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-Bare-bead Type K thermocouple are co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments estimated to be $\pm18$\%.
+BDPs with pressure transducers and single thermocouples were used to measure the gas velocity.
+Bare-bead Type K thermocouples were co-located with the probe.
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for BDPs of similar design~\cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm18$\%.
 
-Water flowrate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 6.35 cm (2.5 inch) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
+The meter consists of a section of 6.35 cm (2.5 in.) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 The pressure transducer was calibrated with a known analog pressure gauge.
-The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
+The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate.
 The total expanded uncertainty was estimated at $\pm10$\%.
@@
 \includegraphics[width=6in]{../Pictures/flow_meter}
-\caption[Picture of Flowrate Meter]{Pressure and flow meter combination used to measure water flowrate}
+\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
 \label{fig:flow_meter}
@@
 
-In the following sections, the measurements will be presented in graphic and tabular form.
-In the graphs, an error bar will represent the estimated uncertainty of the measurement.
-In the tables, the uncertainty will be included in the table of as part of the caption.
-
 \section{Experimental Procedure}
 \label{sec:exp_procedure}
+Every experiment discussed in this report involved discharging water at a rate of 120 GPM from a combination nozzle set to flow water in a straight, narrow fog, or wide fog stream pattern.
+Specific doors were opened or closed before and/or during the experiments to change the ventilation in the structure.
 
-A variety of experiments were conducted to examine the impact of different hose streams and application methods on air flow inside a structure.
-All the experiments were conducted in either the East or West Structure; used a monitor %reference for specs?
-2000 LPM (500 GPM)?
-or 1.75 in handline with a combination nozzle (Fig.~\ref{fig:monitor+handline}) to flow water at approximately 120 GPM in a straight, narrow fog, or wide fog stream pattern; and involved opening and closing doors in the structure to change the ventilation patterns.
-Experiments that used a monitor to flow water focused on varying the location of water application, while the experiments that used a handline to flow water focused on varying the pattern in which water was applied.
+A total of six test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}).
+Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
 
@@
 \endminipage \hfill
-\caption[Monitor and Handline Equipped with Combination Nozzle]{Monitor (left) and 1 \nicefrac{3}{4}" handline (right).
-Both are equipped with a combination nozzle and were used in the water flow experiments.}
+\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in. handline (right) equipped with a combination nozzle and used to flow water during experiments.}
 \label{fig:monitor+handline}
+\end{figure}
+\FloatBarrier
+
+Three different layouts were used for the six test series.
+The test series conducted in the East Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
+Test 33 used a monitor and combination nozzle to flow water and Test 34 used a combination nozzle attached directly to a handline to flow water.
+
+The main difference between the two layouts used for the West Structure experiments is the position of the south side door on the first level.
+Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}) and Tests 17 and 19 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
+Additionally, Tests 16 and 17 used a combination nozzle attached to a monitor to flow water, and Tests 18 and 19 used a combination nozzle attached directly to a handline to flow water.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
+\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
+\label{fig:east_setup}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
+\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square).
+On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+\label{fig:flow_path_1}
+\end{figure}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
+\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square).
+On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+\label{fig:flow_path_2}
 \end{figure}
@@
 \label{subsec:monitor_procedure}
-Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight, narrow fog, and wide fog stream pattern.
+Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
 One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.
@@
 
-Test 33 involved flowing water from a monitor equipped with a combination nozzle and positioned in Room C through Door BC to Room B of the East Structure (Fig.~\ref{fig:test_33_pic}).
-A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:east_setup}.
-Test 33 began by flowing water in a straight stream pattern for 30 seconds, then in a narrow fog stream for 30 seconds, and finally in a wide fog stream for 30 seconds.
-Then, the south side door was opened and each stream was applied for 30 seconds again.
-
-\begin{figure}[!ht]
-% \begin{overpic}
-\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
-% 	\put(66,36){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
-% \end{overpic}
-\caption[East Structure Layout for Tests 33 and 34]{East Structure layout for Tests 33 and 34}
-\label{fig:east_setup}
-\end{figure}
-\FloatBarrier
+Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the East Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
+A plan view of the structure's layout annotated with the approximate location of the BDP array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
+The procedure for Test 33 was the simplest of all the test procedures.
+First, water flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally to a wide fog stream for 30 seconds.
+An identical process was repeated an additional time.
 
@@
 \includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/WF_Room_B_Test_33}
-\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 33]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 33}
+\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at area above the doorway on the south wall of Room B during Test 33.}
 \label{fig:test_33_pic}
 \end{figure}
-\FloatBarrier
 
 % Add flow chart? %
-Tests 16 and 17 followed an identical procedure that involved flowing water from the north side double doors on the first level of the West Structure using a monitor equipped with a combination nozzle.
-The nozzle was aimed at two targets during the tests: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
-Test 16 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 17 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each test began by flowing water in a straight stream pattern at the far target for 60 seconds.
+Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room.
+The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
+The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds.
 After 60 seconds of water flow, the stairwell door was opened.
-One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
+One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds.
 Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target.
@@
 Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.
-
-\begin{figure}[!ht]
-\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_1st_Floor}
-	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
-\end{overpic}
-\\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_18_2nd_Floor}
-\caption[West Structure Layout for Tests 16 and 18]{West Structure first floor (top) and second floor (bottom) layouts for Tests 16 and 18.
-Both double doors and the south side door on the first floor were in the opened position for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
-\label{fig:flow_path_1}
-\end{figure}
-\FloatBarrier
-
-\begin{figure}[!ht]
-\begin{overpic}[trim=0cm 0cm 0.75cm 4.5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_1st_Floor}
-	\put(81,23){\includegraphics[width=1in]{../Drawings/monitor_graphic}}
-\end{overpic}
-\\
-\includegraphics[trim=0cm 0cm 0.75cm 5cm, clip=true, width=6in]{../Drawings/Specific_Tests/West_Structure_Hose_Test_19_2nd_Floor}
-\caption[West Structure Layout for Tests 17 and 19]{West Structure first floor (top) and second floor (bottom) layouts for Tests 17 and 19.
-Both double doors on the first floor were in the opened position and the south side door on the first floor was in the closed position for the duration of the test.
-On the second floor, the stairwell door and north side, west double door were opened and closed during the tests, while the north side, east double door and south side door were in the closed position throughout the entire test.}
-\label{fig:flow_path_2}
-\end{figure}
-\FloatBarrier
 
@@
 \endminipage \hfill
-\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Tests 16 and 17]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during Tests 16 and 17}
+\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during the monitor experiments in the West Structure.}
 \label{fig:test_16_17_pic}
 \end{figure}
-
-\clearpage
+\FloatBarrier
 
@@
 \label{subsec:handline_procedure}
-Numerous experiments were conducted during three different test series using a 1.75" handline with a combination nozzle to flow water.
-One test series, Test 34, occurred in the East Structure, and the other two series, Tests 18 and 19, occurred in the West Structure.
+Numerous experiments were conducted during three different test series using a 1.75 in.
+handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure.
+All three test series primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
 
-During Test 34, water was flowed from a 1.75" handline equipped with a combination nozzle located inside Room C.
-A schematic of the structure's layout during the test series is presented in Fig.~\ref{fig:test_33_34_setup}.
-The test began by flowing water in a straight stream at the ceiling in Room B for 30 seconds in a fixed position, as pictured in Fig.~\ref{fig:test_34_pic}.
-Next, the nozzle was rotated in the clockwise direction for 30 seconds.
-Then, the handline was aimed at Door AB, and water was applied for 30 seconds in a fixed position and for 30 seconds in a clockwise pattern.
-This process were repeated for narrow fog and wide fog streams.
-Then, the entire procedure was repeated for the three types of streams, except a counter-clockwise pattern was applied.
+Test 34 utilized a 1.75 in.
+handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}.
+The layout of the structure was identical to the layout described above in Section~\ref{subsec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}.
+The procedure for Test 34 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
+After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds.
+Then, the nozzle was aimed at the south doorway of Room B and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern.
+This process was repeated for narrow fog and wide fog streams.
+Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counter-clockwise pattern.
 
@@
 \includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
-\caption[Straight Stream, Narrow Fog Stream, and Wide Fog Stream during Test 34]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at ceiling of Room B during Test 34}
+\caption[Straight stream, narrow fog stream, and wide fog stream during Test 34.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 34.}
 \label{fig:test_34_pic}
@@
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed an identical procedure that involved flowing water from the north side, double doors on the first level of the West Structure using a combination nozzle attached to a 1.75" handline.
-The difference between the two tests was that Test 18 contained the same flow path configuration as Test 16 (Fig.~\ref{fig:flow_path_1}), while Test 19 contained the same flow path configuration as Test 17 (Fig.~\ref{fig:flow_path_2}).
-Each test began by flowing water in a straight stream pattern and fixed position.
+Tests 18 and 19 followed identical procedures that involved using a 1.75 in.
+handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
+For every experiment during the two tests, the water stream was aimed at the south side wall of the first floor.
+The difference between Tests 18 and 19 is that Test 18 contained the same flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the same flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Each test series began by using a straight stream to flow water in a fixed position.
 After 60 seconds of water flow, the stairwell door was opened.
 One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for sweeping, clockwise, and counterclockwise application patterns.
+Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping, clockwise, and counterclockwise application patterns.
 This entire procedure was repeated using narrow fog and wide fog streams.
-Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18.
+Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18 with the flow path fully established.
+
 \begin{figure}[!ht]
 \includegraphics[width=4.25in]{../Pictures/Test_18}
-\caption[North Side of West Structure during Test 18]{North side of West Structure during Test 18.
-A straight stream pattern is being applied, and the flow path is fully established with the stairway door and the north side, west double door both opened.}
+\caption[North side of West Structure containing a fully established flow path during Test 18.]{North side of West Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 18.}
 \label{fig:test_18_pic}
 \end{figure}
-\clearpage
+\FloatBarrier
 
@@
 
-\chapter{Results}
-\label{chap:Results}
+\chapter{Results and Discussion}
+\label{chap:results}
+In the following sections, the measurements will be presented in graphic and tabular form.
+In the graphs, an error bar will represent the estimated uncertainty of the measurement.
+In the tables, the uncertainty will be included in the caption of the table.
 
@@
 
-Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains plots of the average velocity measured by the bi-directional probes in the stairwell doorway (A10) for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
-A similar figure was generated using data from Test 17 and can be found in Appendix~\ref{sec:additional_figures}.
+Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
+Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 17 and measurements obtained from the BDPs at A6 during Test 33 are presented in Appendix~\ref{subsec:monitor_figs}.
 
-Notice, the only instances in which significant air movement (average velocity greater than 0.5 m/s) occurs through either doorway is when the flow path is fully established, or when both the stairwell door and the \nth{2} level, north side, west double door are opened.
-Tables~\ref{table:Tests_16_17_BDP_A10_Avgs} and~\ref{table:Tests_16_17_BDP_A13_Avgs} contain the average air velocity measured by the bi-directional probes at A10 and A13, respectively, when the flow path was completely established for each hose stream pattern and application location for Tests 16 and 17.
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
+\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
+\label{fig:Test_16_BDP_A10_Avgs}
+\end{figure}
+\FloatBarrier
+
+For every hose stream and target location combination during the monitor experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
+Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the BDP array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, and 33.
 
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door for all hose stream and application location combinations when the flow path was fully established during Tests 16 and 17}
-\begin{tabular}{lcccc}
-\toprule
- & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}}
-\\
-\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} \\
-\midrule
-\textit{Straight} & 
-%%%%Test 16%%%% 
-0.8 $\pm 0.2$ & 0.9 $\pm 0.2$ & 
-%%%%Test 17%%%% 
-0.7 $\pm 0.1$ & 0.7 $\pm 0.2$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 16%%%% 
-1.4 $\pm 0.1$ & 1.0 $\pm 0.1$ & 
-%%%%Test 17%%%% 
-0.8 $\pm 0.2$ & 0.8 $\pm 0.1 $          
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%%Test 16%%%% 
-1.2 $\pm 0.1$ & 1.4 $\pm 0.1$ & 
-%%%%Test 17%%%% 
-0.9 $\pm 0.2$ & 0.7 $\pm 0.2$
-\\
-\bottomrule
-\end{tabular}
-\label{table:Tests_16_17_BDP_A10_Avgs}
-\end{table}
-
-% West Monitor Table
-
-\begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and target location for all monitor tests}
+\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
 \begin{tabular}{lccccc}
@@
 \\
-\textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} & \textbf{Door AB}
-\\ \midrule
+% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
+\textbf{Stream} & 
+\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
+\\ 
+\midrule
 \textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
@@
 \end{table}
+\FloatBarrier
+
+**** Discuss tabulated results, main point being fogs move more air than straight ****
 
@@
 
-Figs.~\ref{fig:Test_18_BDP_A10_Avg_All}-\ref{fig:Test_19_BDP_A13_Avg_All} contain plots of the average velocity through the stairwell door and \nth{2} level, north side, west double door, measured by the bi-directional probes in each doorway for the four application patterns and three hose stream patterns for Tests 18 and 19.
+Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
+Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 19 and measurements obtained from the BDPs at A6 during Test 34 are presented in Appendix~\ref{subsec:handline_figs}.
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg}
-% \caption{Average Velocity through Stairwell Door, Test 18, All Streams}
-% \label{fig:Test_18_BDP_A10_Avg_All}
-% \end{figure}
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
+\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
+\label{fig:Test_18_BDP_A10_Avg_All}
+\end{figure}
 
-% \clearpage
+\FloatBarrier
 
-% \begin{figure}[!ht]
-% \includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg}
-% \caption{Average Velocity through Stairwell Door, Test 19, All Streams}
-% \label{fig:Test_19_BDP_A10_Avg_All}
-% \end{figure}
+For every hose stream and application pattern combination tested during the handline experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
+Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} list the average velocity measured by the BDP array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18 and 19, respectively.
 
-% \clearpage
-
-Significant air flow through the stairwell and \nth{2} level double door only occurred when the flow path was complete, or when both doors were in the open position.
-Tables~\ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} contain the average air velocity measured by the eight BDPs at the stairwell door and \nth{2} level, double door, respectively, during the time the flow path was complete for each application pattern and hose stream combination used during Tests 18 and 19.
+% #######################
+% # East Handline Table #
+% #######################
 
 \begin{table}[!ht]
-%\addtolength{\tabcolsep}{-3.25pt}
-%\small
-\caption{Average air velocity (m/s) through Door A6 for tested combinations of stream pattern and application location during clockwise and counter clockwise rotations}
-\begin{tabular}{lcccc}
+\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 34}
+\begin{tabular}{lcccccc}
 \toprule
- & \multicolumn{2}{c}{\underline{Room A}} & \multicolumn{2}{c}{\underline{Room B Ceiling}}
+ & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
 \\
-\textbf{Stream} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\
-\midrule 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textit{Straight} 	& 
-%%%% Room A %%%% 
-0.6 $\pm 0.3$ & 0.8 $\pm 0.3$ 
-%%%% Room B Ceiling %%%% 
-& 0.5 $\pm 0.3$ & 0.5 $\pm 0.3$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%% Room A %%%% 
-1.8 $\pm 0.3$ & 1.6 $\pm 0.3$
-%%%% Room B Ceiling %%%% 
- & 1.5 $\pm 0.3$ & 1.6 $\pm 0.3$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%% Room A %%%% 
- 2.1 $\pm 0.3$ & 2.2 $\pm 0.3$
-%%%% Room B Ceiling %%%% 
- & 2.3 $\pm 0.3$ & 2.6 $\pm 0.3$ \\
-\bottomrule
+\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
+\\ \multicolumn{7}{c}{} \\
+\textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
+\\ \multicolumn{7}{c}{} \\
+\textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
+\\ \bottomrule
 \end{tabular}
-\label{table:Test_35_CW_CCW}
+\label{table:east_hand_A6_avgs}
 \end{table}
 
-\begin{table}[!ht]
-%\addtolength{\tabcolsep}{-3.25pt}
-%\small
-\caption{Average air velocity (m/s) through stairwell door for all hose stream and application pattern combinations for Tests 18 and 19}
-\begin{tabular}{lcccc}
-\toprule
- & \multicolumn{4}{c}{\underline{Test 18}}
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\
-\midrule 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textit{Straight} 	& 
-%%%%Test 18%%%% 
--0.2 $\pm 0.3$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 18%%%% 
- 0.4 $\pm 0.3$ & 1.0 $\pm 0.2$ & 0.8 $\pm 0.2$ & 1.0 $\pm 0.4$ 
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%%Test 18%%%% 
- 0.9 $\pm 0.2$ & 0.9 $\pm 0.3$ & 0.9 $\pm 0.3$ & 0.8 $\pm 0.3$ 
-\\
-\midrule
-& \multicolumn{4}{c}{\underline{Test 19}} 
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\
-\midrule
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\textit{Straight} 	& 
-%%%%Test 19%%%% 
- 0.0 $\pm 0.1$ & 0.5 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.6 $\pm 0.2$ 
-\\	\multicolumn{5}{c}{}	\\
-\textit{Narrow Fog} & 
-%%%%Test 19%%%% 
- 1.2 $\pm 0.3$ & 1.2 $\pm 0.3$ & 1.1 $\pm 0.4$ & 1.2 $\pm 0.2$
-\\	\multicolumn{5}{c}{}	\\
-\textit{Wide Fog} 	& 
-%%%%Test 19%%%% 
- 1.0 $\pm 0.2$ & 0.7 $\pm 0.2$ & 0.9 $\pm 0.2$ & 0.9 $\pm 0.2$
-\\
-\bottomrule
-\end{tabular}
-\label{table:Tests_18_19_BDP_A10_Avgs}
-\end{table}
+% #######################
+% # West Handline Table #
+% #######################
 
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and pattern combinations during Tests 18 and 19}
+\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Tests 18 and 19}
 \begin{tabular}{lcccc}
@@
 
-Notice, there is a significant difference between the average air velocity caused by the fixed straight stream and the velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.
-It was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern.
-However, the straight stream hose pattern always resulted in the lowest average air velocity through each doorway for the three different hose streams at each of the four application patterns.
+\FloatBarrier
 
-Another important result shown in Figures \ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables \ref{table:Tests_18_19_BDP_A10_Avgs} and \ref{table:Tests_18_19_BDP_A13_Avgs} is that there is statistically no significant difference in the amount of air flow through the doorways between rotating the hoseline in the clockwise and counter clockwise directions for the three hose streams tested.
+Similar to the monitor experiments, there is a significant difference between the average air velocity caused by the fixed straight stream and the average velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.
+Additionally, it was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern.
+However, the straight stream hose pattern always resulted in the lowest average air velocity through the doorway for the three different hose streams at each of the four application patterns.
 
-% #######################
-% # West Handline Table #
-% #######################
+Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there is no statistically significant difference in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.
 
-\begin{table}[!ht]
-\caption{Average air velocity (m/s) through stairwell door with fully established flow path for stream and application pattern combinations during Tests 18 and 19}
-\begin{tabular}{lcccc}
-\toprule
- & \multicolumn{4}{c}{\underline{Test 18}}
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\ \midrule
-\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
-\\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
-\\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
-\\ \midrule
- & \multicolumn{4}{c}{\underline{Test 19}}
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\ \midrule
-\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
-\\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
-\\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
-\\ \bottomrule
-\end{tabular}
-\label{table:west_hand_A10_avgs}
-\end{table}
-
-% #######################
-% # East Handline Table #
-% #######################
-
-\begin{table}[!ht]
-\caption{Average air velocity (m/s) through A6 with established flow path for the stream and application pattern combinations at each target (Room A and ceiling of Room B) during Test 34}
-\begin{tabular}{lcccccc}
-\toprule
- & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
-\\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-\\ \midrule
-\textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
-\\ \multicolumn{7}{c}{} \\
-\textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
-\\ \multicolumn{7}{c}{} \\
-\textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
-\\ \bottomrule
-\end{tabular}
-\label{table:east_hand_A6_avgs}
-\end{table}
+**** Add more specific discussion of results ****
 
@@
 
-% ===============
-% = CONCLUSIONS =
-% ===============
-\chapter{Conclusions}
-\label{chap:Conclusions}
+% ===========
+% = Summary =
+% ===========
+\chapter{Summary}
+\label{chap:summary}
+**** Will briefly restate purpose of experiments, objectives, setup, results etc. ****
+List of main findings:
 \begin{enumerate}
-\item Any movement of the hose stream increases the air flow through the structure
-\item NF and WF move significantly more air than SS
-\item No difference between rotating hose CW or CCW
+\item More air movement with NF and WF than SS
+\item More air movement when the hose stream was applied in a pattern that involved moving the nozzle compared to keeping the stream in a fixed position.
+\item No noticeable difference between rotating hose CW or CCW
 \end{enumerate}
@@
 \label{chap:Future_Work}
-Need to determine if air movement caused by hose streams has significant impact on flow path and fire development in involved structure
+Need to determine if air movement caused by hose streams has significant impact on flow path/ventilation and fire development in an involved structure.
+May want to compare air velocities to movements caused by PPV fans.
 
@@
 \section{Additional Figures}
-\label{sec:additional_figures}
+\label{sec:additional_figs}
+
+\subsection{Monitor Figures}
+\label{subsec:monitor_figs}
+
+\subsection{Handline Figures}
+\label{subsec:handline_figs}
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
+\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
+\label{fig:Test_19_BDP_A10_Avg_All}
+\end{figure}
 

### 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
add figures and tex file for hose report

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Memo
% LaTeX Template
% Version 1.0 (30/12/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rob Oakes (http://www.oak-tree.us) with modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper,11pt]{texMemo} % Set the paper size (letterpaper, a4paper, etc) and font size (10pt, 11pt or 12pt)

\usepackage{parskip} % Adds spacing between paragraphs
\usepackage{hyperref}
\frenchspacing
\setlength{\parindent}{15pt} % Indent paragraphs

\hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=blue}

%----------------------------------------------------------------------------------------
%	MEMO INFORMATION
%----------------------------------------------------------------------------------------

\memoto{NFPA 1961 Technical Committee} % Recipient(s)

\memofrom{NIST Firefighting Technology Group} % Sender(s)

\memosubject{Full-scale Exposure Testing of Hoselines} % Memo subject

\memodate{\today} % Date, set to \today for automatically printing todays date

%----------------------------------------------------------------------------------------

\begin{document}

\maketitle % Print the memo header information

%----------------------------------------------------------------------------------------
%	MEMO CONTENT
%----------------------------------------------------------------------------------------

This letter report documents two experiments performed at the request of NFPA staff for use by the NFPA Technical Committee on Fire Hose.   The objective of the experiments was to gain some insight into the failure of fire hose as a result of thermal insult.  Three different hose conditions were examined; hose filled with air, hose filled with water, hose flowing 150~gpm of water.

\section{Experimental Test Arrangement}
The experiments were conducted in a two story structure that was built to simulate a townhouse with a walk out basement. The structure was built on a concrete slab. The lower level of the structure had an outer wall composed of 2~ft thick interlocking concrete blocks. The joints and gaps between the blocks were filled with high temperature foam insulation. The interior walls of the lower level were framed with steel studs and track. The studs were set to 0.40~m (16~in.) centers. The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in.) depth. Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in.) x 44~mm (1.75~in.) and an 11~mm (0.43~in.) thick oriented strand board web. Tongue and grove, 18.3~mm (0.72~in.) thick, oriented strand board was screwed to the top of the TJIs to form the floor of the upper level. The walls and ceiling of the lower level was composed of two layers of 12.7~mm (0.5~in.) thick cement board.

The upper level of the structure was built on the wood floor assembly above. The walls were framed with wood studs set to 0.40~m (16~in.) centers. The walls and ceiling of the upper level were composed of two layers of 12.7~mm (0.5~in.) thick cement board.

The interior footprint of both the upper and lower level are each approximately 20~ft wide by 36~ft deep. 	Figures~\ref{fig:schematic_low} and \ref{fig:schematic_up} are schematics of the floor plans of the upper and lower levels. In these images, circles indicate the location of thermocouples, squares indicate the location of velocity probes and thermocouples, diamonds indicate gas measurement probes, and triangles indicate the location of heat flux measurements.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/schematic_lower}
\caption{Schematic of Lower Level}
\label{fig:schematic_low}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/schematic_upper}
\caption{Schematic of Upper Level}
\label{fig:schematic_up}
\end{figure}

On Side C of the lower level, there is a set of doors with a total opening of approximately 72~in. wide and 80~in. high. These doors were open for the duration of the hose exposure experiments.

On Side A of the lower level the single door remained closed for these experiments. The door was undercut to allow the hoses to pass through without any obstruction. Non-combustible fiber was then packed around the hoses to minimize any leakage under the door.  An open stair extends from Side A and leads to the upper level with an open doorway facing Side C of the structure. The ventilation openings on the upper level include a 36~in. by 80~in. doorway and a 66~in. wide by 36~in. high window with a 43~in. sill height on the A side. On C side of the upper level is another set of double doors similar in size to the set of doors on the lower level. All of the openings on the upper level remained closed for the duration of the hose exposure experiments. See schematics of the floor plans (Fig.~\ref{fig:schematic_low} and \ref{fig:schematic_up}) of both levels and photographs of the exterior of the structure (cf. Fig.~\ref{fig:exterior}).

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_a}
\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_c}
\caption{Photographs of Side A (Left) and Side C (Right). }
\label{fig:exterior}
\end{figure}

\section{Fuel Load}
The interior finish of the lower level consisted of 1/2~in. oriented strand board (OSB).  The OSB covered the entire ceiling, floor and the walls on Sides A, B, and D. Polyolefin carpeting over polyurethane foam padding covered the floor of the lower level.  The fuel load in the basement consisted of three sofas, oriented strand board on the ceiling and walls of the basement (cf. Fig.~\ref{fig:schematic_low}).

\section{Instrumentation}
Temperatures were measured with bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm (0.02 in) nominal diameter. A vertical thermocouple array was installed adjacent to the center of the test section of the hoses on the floor of the lower level. The vertical array had thermocouples located 0.025, 0.3, 0.61, 0.91, 1.22, 1.52, 1.83, 2.13~m (1~in., 1,2,3,4,5,6,7 ft.) below the ceiling (BC).  Additional single thermocouples were installed in contact with the outer jacket of the fire hoses.

The heat flux gauges used in the lower level were Schmidt-Boelter type, water cooled gauges.  Total heat flux was measured with Schmidt Boelter gauges. Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/test_setup_1}
\caption{Fire room with fuel load, instrumentation and hose samples installed for Experiment 1. Looking in from the Side C open doorway on the lower level. These doors are the only opening in the structure during the test. As a result the fire will move from the back of the room over the exposed hose toward the door.}
\label{fig:test_setup_1}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/test_setup_1b}
\caption{Locations of instrumented hose samples relative to the vertical thermocouple array, the heat flux gauge and the radiometer.}
\label{fig:test_setup_1b}
\end{figure}

\section{Hose}
The fire hose that was used for the experiments was ``Big - 10'' brand manufactured by Key Hose. According to the manufacturer the hose meets or exceeds all of the performance requirements of NFPA 1961. The ``1 3/4"~in. hose is constructed with 100 polyester double jacket and the rubber lining is made of a single-ply extruded tube of synthetic EPDM a minimum wall thickness of 0.040~in. The hose condition was new, right out of the box. See Attachment 1 for further hose information.

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
\caption{Schematic showing the test arrangement on the lower level. The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional probes in the open doorway on Side C.}
\label{fig:test_plan}
\end{figure}

\section{Results}
Two experiments were conducted to examine the amount of thermal exposure required to cause the fire hose to burn through. In each experiment three different hose conditions were examined: hose filled with air, hose filled with water, hose flowing 150 gpm of water. The difference between the two experiments was the location of the exposed hose section. In Experiment 1 the center of the exposed hose section and instrumentation was located 11 ft from the open doorway on Side C. In Experiment 2 the exposed hose section and instrumentation was located 4~ft from the open doorway on Side C.

In Experiment 1, all three hose samples failed during the transition to flashover. Given the high rate of change of the thermal exposure in Experiment 1, the exposed section was moved closer to the open doorway for Experiment 2 as an attempt to reduce the exposure by taking advantage of the cool air being entrained near the floor through the open door way. In Experiment 2, the hose filled with air failed followed by the hose filled with static water.  These two ruptures happened very close together in time. The water from the ruptured line suppressed the fire to a degree and protected the hose line with the flowing water, so that it did not fail although the outer jacket was burned away and the hose was compromised.

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/hose_post_exp1}
\caption{Photograph after Experiment 1. All three hoses burned through within 2 seconds of each other. The hose at the top of the photograph was the static water line.  The middle hose was filled with air. The lower hose is the hose that was flowing 150~gpm of water.}
\label{fig:post_test1_image}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_60_West_80915_TC_A3}
\caption{Thermocouple temperatures as a function of elevation at the test section for Experiment 1.}
\label{fig:temp_A3_test60}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_60_West_80915_Heat_Flux_2}
\caption{Total and radiant heat flux at the test section for Experiment 1.}
\label{fig:hf_A3_test60}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_60_West_80915_TC_Gear_2}
\caption{Thermocouple temperatures at the test section for each hose tested for Experiment 1.}
\label{fig:hose_A3_test60}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/hose_post_exp2}
\caption{Photograph showing the damage to the hose samples after Experiment 2. The hose at the top of the photograph was the static water line. The middle hose was filled with air. The lower hose is the hose that was flowing 150~gpm of water.}
\label{fig:post_test2_image}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_62_West_81015_TC_A3}
\caption{Thermocouple temperatures as a function of elevation at the test section for Experiment 2.}
\label{fig:temp_A3_test62}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_62_West_81015_Heat_Flux_2}
\caption{Total and radiant heat flux at the test section for Experiment 2.}
\label{fig:hf_A3_test62}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\columnwidth]{../Figures/Hose_Figures/Test_62_West_81015_TC_Gear_2}
\caption{Thermocouple temperatures at the test section for each hose tested for Experiment 2.}
\label{fig:hose_A3_test62}
\end{figure}

\section{Summary}
These two experiments provide some insight in the level of energy required to burn through a hose. In both experiments, flames appeared to be close to the hose, if not impinging on the hose at the time of burn through. In these experiments there was no significant difference in burn through time for the hoses filled with air, static water or flowing water.

%----------------------------------------------------------------------------------------

\end{document}

### 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
Added metric units, interior dimensions, sofa HRR

@@
 The structure was built on a concrete slab.
-The lower level of the structure had an outer wall composed of 2~ft thick interlocking concrete blocks.
+The lower level of the structure had an outer wall composed of 0.6~m (2~ft) thick interlocking concrete blocks.
 The joints and gaps between the blocks were filled with high temperature foam insulation.
@@
 
-The interior footprint of both the upper and lower level are each approximately 20~ft wide by 36~ft deep.
-	Figures~\ref{fig:schematic_low} and \ref{fig:schematic_up} are schematics of the floor plans of the upper and lower levels.
+The interior footprint of the lower level is approximately 5.7~m (18.7~ft) wide by 10.6~m (34.8~ft) deep.
+The interior area of the upper level is approximately 6.0~m (19.8~ft) wide by 11~m (36~ft) deep.	 Figures~\ref{fig:schematic_low} and \ref{fig:schematic_up} are schematics of the floor plans of the upper and lower levels.
 In these images, circles indicate the location of thermocouples, squares indicate the location of velocity probes and thermocouples, diamonds indicate gas measurement probes, and triangles indicate the location of heat flux measurements.
@@
 
-On Side C of the lower level, there is a set of doors with a total opening of approximately 72~in. wide and 80~in. high. These doors were open for the duration of the hose exposure experiments.
+On Side C of the lower level, there is a set of doors with a total opening of approximately 1.8~m (6~ft) wide and 2.0~m (6.7~ft) high.
+These doors were open for the duration of the hose exposure experiments.
 
@@
 \section{Fuel Load}
-The interior finish of the lower level consisted of 1/2~in.
-oriented strand board (OSB).
+The interior finish of the lower level consisted of 12.7~mm (1/2~in.) oriented strand board (OSB).
 The OSB covered the entire ceiling, floor and the walls on Sides A, B, and D.
@@
 Fig.~\ref{fig:schematic_low}).
+In a free burn condition, each sofa can generate a peak heat release rate of approximately 2~MW.
 
@@
 
-The heat flux gauges used in the lower level were Schmidt-Boelter type, water cooled gauges.
-Total heat flux was measured with Schmidt Boelter gauges.
-Radiant heat flux was measured with Schmidt Boelter gauges with sapphire lens.
+The heat flux gauges used were Schmidt-Boelter type, water cooled gauges.
+Total heat flux, convection and radiation, was measured with the uncovered gauge.
+Radiant heat flux was measured with a gauge covered with a sapphire lens.
 
@@
 \caption{Schematic showing the test arrangement on the lower level.
-The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional probes in the open doorway on Side C.}
+The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional velocity probes in the open doorway on Side C.}
 \label{fig:test_plan}

### 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
Added Hose disclaimer and a few more convertions

@@
 
-\memofrom{NIST Firefighting Technology Group} % Sender(s)
+\memofrom{Daniel Madrzykowski \\ Craig Weinschenk \\ NIST Firefighting Technology Group} % Sender(s)
 
@@
 The objective of the experiments was to gain some insight into the failure of fire hose as a result of thermal insult.
-Three different hose conditions were examined; hose filled with air, hose filled with water, hose flowing 150~gpm of water.
+Three different hose conditions were examined; hose filled with air, hose filled with water, hose flowing 568~lpm (150~gpm) of water.
 
@@
 See Attachment 1 for further hose information.
+Note that the brand name of this material was included for purposes of explaining the experiment.
+Identification in this report is not intended to imply recommendation or endorsement by NIST, nor is it intended to imply that such materials are necessarily the best available for the purpose.
 
@@
 The difference between the two experiments was the location of the exposed hose section.
-In Experiment 1 the center of the exposed hose section and instrumentation was located 11 ft from the open doorway on Side C.
-In Experiment 2 the exposed hose section and instrumentation was located 4~ft from the open doorway on Side C.
+In Experiment 1 the center of the exposed hose section and instrumentation was located 3.4~m (11.2~ft) from the open doorway on Side C.
+In Experiment 2 the exposed hose section and instrumentation was located 1.2~m (4~ft) from the open doorway on Side C.
 

### 2015-11-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update DelCo2012 work

@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_A3_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_A3_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
 	\label{fig:CAFS_Water_Comp_SS_mid}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Full Back Position}
-	\label{fig:CAFS_Water_Comp_SS_full}
 \end{figure}

### 2015-12-09 Projects/DelCo_2012/Report/DelCo_2012.tex
Update Delco 2012

@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingDimensions}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
 	\caption{Delaware County, PA Burn Building Layout}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStoryDimensionsMetric}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
 	\caption{Floor Plan of the Test Structure.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.35\columnwidth]{../Figures/Pictures/Legend2}
+	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend.pdf}
 	\caption{Instrumentation Legend.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoBurnBuildingInstrumentation}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation}
 	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryInstrumentationDimensions}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
 	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingFuelLoad}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
 	\caption{Burn Building Fuel Load.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryWoodFuelLoad}
+	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
 	\caption{Wood Fuel Load Dimensions.}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
-	\caption{Furniture Fuel Load Dimensions.}
+	\caption{Furniture Fuel Load.}
 	\label{fig:Furniture_Fuel_Load}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/DelCoSingleStoryFurnitureFuelLoad}
+	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
 	\caption{Furniture Fuel Load Dimensions.}

### 2015-12-09 Projects/DelCo_2012/Scripts/gas_cooling_plot2.py

@@ -1,3 +1,5 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
 #Weinschenk
 #3-15
 from __future__ import division
@@ -78,14 +80,14 @@ for entry in range(0,len(info)):
 					water_test = 'data'+str(info['Test_Series_Water'][entry+reps])
 					water_test = locals().get(water_test)
 					water_data_interval = water_test[channel][info['Start_Time_Water'][entry+reps]:info['Stop_Time_Water'][entry+reps]]
-					del_TC_3_h2o[int(channel[6:])-1,reps] = max(water_data_interval) - min(water_data_interval)
-					# del_TC_3_h2o[int(channel[6:])-1,reps] = (max(water_data_interval) - min(water_data_interval))/max(water_data_interval)
+					#del_TC_3_h2o[int(channel[6:])-1,reps] = max(water_data_interval) - min(water_data_interval)
+					del_TC_3_h2o[int(channel[6:])-1,reps] = (max(water_data_interval) - min(water_data_interval))/max(water_data_interval)
 					# print (max(water_data_interval) , min(water_data_interval), max(water_data_interval) - min(water_data_interval), channel,reps,'water')
 					cafs_test = 'data'+str(info['Test_Series_CAFS'][entry+reps])
 					cafs_test = locals().get(cafs_test)
 					cafs_data_interval = cafs_test[channel][info['Start_Time_CAFS'][entry+reps]:info['Stop_Time_CAFS'][entry+reps]]
-					del_TC_3_cafs[int(channel[6:])-1,reps] = max(cafs_data_interval) - min(cafs_data_interval)
- 					# del_TC_3_cafs[int(channel[6:])-1,reps] = (max(cafs_data_interval) - min(cafs_data_interval))/max(cafs_data_interval)
+					#del_TC_3_cafs[int(channel[6:])-1,reps] = max(cafs_data_interval) - min(cafs_data_interval)
+					del_TC_3_cafs[int(channel[6:])-1,reps] = (max(cafs_data_interval) - min(cafs_data_interval))/max(cafs_data_interval)
 					# print (max(cafs_data_interval) , min(cafs_data_interval),max(cafs_data_interval) - min(cafs_data_interval),channel,reps,'cafs')
 					# print()
 				if 'TC_A2_' in channel:

### 2015-12-09 Studies/2012_PG_County/Scripts/pg_co_hrr.py

@@ -1,3 +1,5 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
 #Weinschenk
 #9-14
 
@@ -33,7 +35,7 @@ first_hrr_20mph = pd.rolling_mean(first_hrr_20mph_raw,10,center=True)
 FDS_HRR_20 = pd.rolling_mean(pd.read_csv('../FDS_Output_Files/pg_county_20mph_9MW_hrr.csv', header=1),10,center=True)
 
 HRR_theo = [None]*1000
-HRR_time = list(xrange(1000))
+HRR_time = list(range(1000))
 
 for i in range (0, 999):
     if i <= 10:

### 2015-12-10 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to DelCo 2012

@@
 
+To compare the effectiveness of the suppression agents (CAFS, water), the temperatures from the thermocouple tree which was not directly impacted by the streams was analyzed.
+Thermocouples that were greater than 2.13~m (7~ft) below the ceiling (the bottom 3 thermocouples) were not included because of the minimal temperature readings throughout the tests.
+Gas cooling was determined by taking the normalized maximum change in temperature ($\hat{T}$) over the test interval ($T_{max}$ is peak temperature before suppression and $T_{min}$ is minimum temperature after suppression):
+\begin{equation}
+\label{eq:norm_temp}
+\hat{T} = \frac{T_{max}-T_{min}}{T_{max}}
+\end{equation}
+The normalized temperature difference is taken because of the large variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.
+
 \begin{figure}[!ht]

### 2015-12-10 Projects/DelCo_2012/Scripts/gas_cooling_plot2.py

@@ -131,7 +131,7 @@ for entry in range(0,len(info)):
 
 		fig = figure()
 		plt.scatter(X,y,alpha=0.5)
-		plt.plot(X_prime, y_hat, 'r', alpha=0.9)  # Add the regression line, colored in red
+		plt.plot(X_prime, y_hat, 'r--', alpha=0.9,linewidth=3)  # Add the regression line, colored in red
 		plt.plot(X_prime,X_prime,'k')
 		plt.fill_between(X_prime,0.85*X_prime,1.15*X_prime, facecolor='gray',alpha=0.5, interpolate=True,linewidth=3)
 		axis([0, max_axis, 0, max_axis])

### 2015-12-21 Equipment_and_Testing_Guide/Equipment_and_Testing_Guide.tex
Update Equipment Guide
Updated Equipment_and_Testing_Guide with necessary step for setting up arduino data logger

@@
 \flushright{
-Kristopher J. Overholt \\
+Roy A. McLane \\
 Craig G. Weinschenk \\
 Keith M. Stakes \\
-Roy A. McLane \\
-Jay A. McElroy \\
+Kristopher J. Overholt \\
 Daniel Madrzykowski \\
+
 \bigskip
@@
 https://www.rabbitmq.com/
+\item Create .config file 
+    \begin{itemize}
+    \item Open \textit{rabbitmq.config.example} (./etc/rabbitmq/ on Mac/Linux; ./etc/ on Windows)
+    \item Add `[ \{loopback\_users, [] \}' after the `\{rabbit,' line and save file as `rabbitmq.config' in the directory containing the example file \\
+    \textit{Note:} On Windows, may have to save it in the directory \\
+    `C:\textbackslash Users/\%USERNAME\%/AppData/Roaming/RabbitMQ/' \\
+    To find such directory, search `rabbitmq.config.example' on computer and open approriate file location.
+    \end{itemize}
 \item Copy the receive\_data.py script from the NIST-FIRE repository to the data logging computer.

### 2015-12-23 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
add tex file for convective report

\documentclass[12pt,oneside]{book}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                                                 %
% The mathematical style of these documents follows                                               %
%                                                                                                 %
% A. Thompson and B.N. Taylor. The NIST Guide for the Use of the International System of Units.   %
%    NIST Special Publication 881, 2008.                                                          %
%                                                                                                 %
% http://www.nist.gov/pml/pubs/sp811/index.cfm                                                    %
%                                                                                                 %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{../../../Bibliography/commoncommands}

% Rename chapter headings
\renewcommand{\chaptername}{Section}
\renewcommand{\bibname}{References}

% Math shortcuts
\renewcommand{\sb}[1]{_\mathrm{#1}}
\renewcommand{\C}{\mbox{C}}
\renewcommand{\H}{\mbox{H}}
\renewcommand{\O}{\mbox{O}}
\newcommand{\N}{\mbox{N}}

\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\renewcommand{\headrulewidth}{0pt}

\begin{document}
\pagenumbering{gobble}

\bibliographystyle{unsrt}
%\pagestyle{empty}

\begin{minipage}[t][9in][s]{6.25in}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Exploratory Study on the Heating of \\
Protective Clothing in a Convective Flow \\
}

\normalsize

\headerC{
{
\flushright{
Daniel Madrzykowski \\
Craig Weinschenk \\
Joeseph Willi \\

\vspace*{2\baselineskip}

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

\vfill

\flushright{

\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
}
}
}

\end{minipage}

\newpage
\hspace{5in}
\newpage

\frontmatter

\begin{minipage}[t][9in][s]{6.25in}
\pagenumbering{gobble}

\begin{flushright}
\fontsize{20}{24}\selectfont
\bf{NIST Technical Note XXXX}
\end{flushright}

\headerB{
Exploratory Study on the Heating of \\
Protective Clothing in a Convective Flow \\
}

\headerC{
\flushright{
Daniel Madrzykowski \\
Craig Weinschenk \\
Joeseph Willi \\
{\em Fire Research Division \\
Engineering Laboratory} \\

\vspace*{2\baselineskip}

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vspace*{2\baselineskip}

December 2015}}

\vfill

\flushright{\includegraphics[width=1in]{../../../Bibliography/doc} }

\titlesigs

\end{minipage}

\newpage

\begin{minipage}[t][9in][s]{6.25in}

\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
document in order to describe an experimental procedure or concept adequately. \\
Such identification is not intended to imply recommendation or endorsement by the \\
National Institute of Standards and Technology, nor is it intended to imply that the \\
entities, materials, or equipment are necessarily the best available for the purpose. \\
}

\vspace{3in}

\large
\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (December 2015) \\
CODEN: NTNOEF}

\vspace{0.2in}

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

\vfill

\hspace{1in}

\end{minipage}

\newpage

\frontmatter

\pagestyle{plain}
\pagenumbering{roman}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Figures}
\listoffigures

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{List of Tables}
\listoftables

\chapter{List of Acronyms}

\begin{tabbing}
\hspace{1.5in} \= \\
NIST \> National Institute of Standards and Technology \\
\end{tabbing}

\mainmatter

\chapter*{\centering Abstract}
\pagenumbering{gobble}
The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to would be to fill that data gap to better define the thermal limits of the operational fire environment its impact on structural firefighting PPE and deliver this information to the appropriate standards groups and the fire service.  Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.
To accomplish this, NIST will examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of PPE used by structural firefighters.  Further NIST will conduct laboratory thermal testing of commercially available this PPE as part of this phase of the study.

Tasks:

1.	NIST shall examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.    (LIST)

2.	NIST shall conduct laboratory thermal testing of commercially available structural firefighting PPE as part of this phase of the study, with a focus on convective heat transfer.  The testing shall include any relevant performance requirements for structural firefighting PPE thermal exposure in NFPA 1971.   Plunge Test $\&$ Flow Loop

3.	NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.  Field testing will be coordinated with the COR.

\chapter{Introduction}
\pagenumbering{arabic}
\setcounter{page}{1}
There is a gap in the understanding of the thermal failure temperature (melting point) of various pieces of personal protective equipment (PPE) worn or used by firefighters.  As a result, there may be a misunderstanding of the thermal conditions in which a firefighter can safely operate.  Ignition and melt testing on various pieces of PPE will define the thermal failure temperatures and lead to a better understanding of the conditions of a safer firefighting environment.  Although there are flame and heat resistance tests in NFPA 1971, Standard on Protective Ensembles for Structural Fire Fighting and Proximity Fire Fighting and NFPA 1981, Standard on Open-Circuit Self Contained Breathing Apparatus for Fire and Emergency Services, these tests do not provide the engineering data needed to connect laboratory based research data with field data (thermally damaged equipment) from actual fire incidents.

There have been incidents of failure of structural firefighting PPE has impacted the operational safety of firefighters.  There is need to examine ways to enhance the understanding of thermal performance of structural firefighting PPE to enhance protection of firefighters.

The initial phase of this study would examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.  This phase of the study would also work with the National Fire Protection Association (NFPA) 1971 Standard on Protective Ensembles for Structural Fire Fighting technical committee on ways to enhance the operational effectiveness of structural firefighting PPE.  Initial laboratory thermal testing of commercially available structural firefighting PPE shall also be conducted as part of this phase of the study.

Existing Tests – high thermal flux, short exposure
TTP Test- PPE
Thermo man – (pyro man) PPE
Flame contact – helmet
While under bench scale test conditions it is less difficult to decouple convective heating from a radiant heat exposure.  However with current test apparatus while convective heating is dominant, there is some level of radiant heating that is contributing to the heat transfer.
Under full scale conditions in a flow path the PPE is exposed to a combination of convective and radiative heating.
LoDDs
Use - Cherry Road and San Francisco as examples
Items examined

Turnout gear material
Helmets    thermoplastic shell, fiberglas shell and leather shell
Facepieces
Old Scott AV 3000?,  New Scott 3000HT
MSA Old  and New MSA 7
Tests
Heat Gun Exposure?
Flow loops
	Plunge test
		Temperature, velocity, heat flux measure?
	Thermal Flow Loop
		Temperature, velocity, heat flux
Full Scale
	Delco Exposures

Future Research

Flow loop    with 20 mph and 300 to 500 F - Donnelly
Substrates
2D vs 3D samples
Gaps – refer to Lawson and Stroup
Instrumentation – ref to Vettori
Steam

\chapter{Discussion}

\chapter{Summary}

\chapter{Acknowledgments}

\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}

\appendix

\end{document}

### 2015-12-23 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
update convective report and bib file

@@
 NIST \> National Institute of Standards and Technology \\
+PPE \> Personal Protective Equipment \\
 \end{tabbing}
@@
 \pagenumbering{gobble}
-The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to would be to fill that data gap to better define the thermal limits of the operational fire environment its impact on structural firefighting PPE and deliver this information to the appropriate standards groups and the fire service.
+The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service.
 Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.
+
 To accomplish this, NIST will examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of PPE used by structural firefighters.
-Further NIST will conduct laboratory thermal testing of commercially available this PPE as part of this phase of the study.
-
-Tasks:
-
-1.	NIST shall examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.    (LIST)
-
-2.	NIST shall conduct laboratory thermal testing of commercially available structural firefighting PPE as part of this phase of the study, with a focus on convective heat transfer.
+Further NIST will conduct laboratory thermal testing of commercially available PPE as part of this phase of the study:
+\begin{enumerate}
+\item NIST shall examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE \cite{Weinschenk:Chicago,Overholt:San_Francisco,Weinschenk:PGCounty}.
+\item NIST shall conduct laboratory thermal testing of commercially available structural firefighting PPE as part of this phase of the study, with a focus on convective heat transfer.
 The testing shall include any relevant performance requirements for structural firefighting PPE thermal exposure in NFPA 1971.
-Plunge Test $\&$ Flow Loop
-
-3.	NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.  Field testing will be coordinated with the COR.
+\item NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.
 

### 2015-12-28 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
convective report edits

@@
 \item NIST shall conduct full-scale thermal testing of structural firefighting PPE at field test sites.
+\end{enumerate}
 
@@
 Ignition and melt testing on various pieces of PPE will define the thermal failure temperatures and lead to a better understanding of the conditions of a safer firefighting environment.
-Although there are flame and heat resistance tests in NFPA 1971, Standard on Protective Ensembles for Structural Fire Fighting and Proximity Fire Fighting and NFPA 1981, Standard on Open-Circuit Self Contained Breathing Apparatus for Fire and Emergency Services, these tests do not provide the engineering data needed to connect laboratory based research data with field data (thermally damaged equipment) from actual fire incidents.
+Although there are flame and heat resistance tests in NFPA 1971, Standard on Protective Ensembles for Structural Fire Fighting and Proximity Fire Fighting~\cite{nfpa1971_2013} and NFPA 1981, Standard on Open-Circuit Self Contained Breathing Apparatus for Fire and Emergency Services~\cite{nfpa1981_2013}, these tests do not provide the engineering data needed to connect laboratory based research data with field data (thermally damaged equipment) from actual fire incidents.
 
@@
 
-The initial phase of this study would examine documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.
+The initial phase of this study examines the documented on-duty injuries and fatalities of firefighters due to thermal exposure of structural firefighting PPE.
 This phase of the study would also work with the National Fire Protection Association (NFPA) 1971 Standard on Protective Ensembles for Structural Fire Fighting technical committee on ways to enhance the operational effectiveness of structural firefighting PPE.
@@
 
-Existing Tests – high thermal flux, short exposure
-TTP Test- PPE
-Thermo man – (pyro man) PPE
-Flame contact – helmet
+\chapter{Prior On-Duty Injuries and Fatalities}
+
+There have been many previous fire incidents~\cite{NIOSH:Pettit,NIOSH:Washenitz,NIOSH:Mezzanotte,NIOSH:McFall,NIOSH:McFall2,NIOSH:McFall3,NIOSH:Berardinelli,NIOSH:Koedam,NIOSH:McFall4,NIOSH:Tarley,NIOSH:Braddee,NIOSH:Merinar,NIOSH:Bowyer2,NIOSH:Loflin,NIOSH:Bowyer} in which changes in the flow paths are thought to have had an adverse impact on firefighter and occupant safety.
+Table~\ref{tab:LODD} lists the NIOSH investigation reports from the past 15 years in which it could be determined that a flow path played a role in the related incident.
+This table lists the NIOSH report number, the outcome, and a brief description of the flow path details.
+
+Based on a review of these incidents, it is clear that fires with rapidly developing or changing ventilation may lead to flow paths that are a significant hazard to the fire service during a response.
+The development of (or changes to) a flow path could be caused by the failure of a component of the structure, such as a door, window, or portion of a ceiling, wall or floor.
+Environmental conditions such as wind can generate hazardous thermal conditions within a flow path.
+Uncoordinated ventilation procedures can also be the cause of increased thermal hazards within a flow path.
+
+\begin{table}[!ht]
+\caption[Flow path related LODD/LODI incidents.]
+{Flow path related LODD/LODI incidents.}
+\begin{tabular}{lll}
+\toprule
+NIOSH Report No. & No. of LODDs/LODIs & Flow Path Details                                              \\
+\midrule
+99-F01   \cite{NIOSH:Pettit}        &  3 LODDs            &  From apartment into hallway on 10th       \\
+                                    &                     &  floor of high-rise apartment building     \\
+99-F21   \cite{NIOSH:Washenitz}     &  2 LODDs            &  Basement to 1st floor                     \\
+                                    &  2 LODIs            &                                            \\
+F2000-04 \cite{NIOSH:Mezzanotte}    &  3 LODDs            &  1st floor to 2nd floor                    \\
+                                    &  3 civilian deaths  &                                            \\
+F2000-16 \cite{NIOSH:McFall}        &  1 LODD             &  2nd floor hallway through                 \\
+                                    &  1 LODI             &  2nd floor apartment                       \\
+                                    &  1 civilian death   &                                            \\
+F2000-23 \cite{NIOSH:McFall2}       &  1 LODD             &  From ground level to 1st floor then to    \\
+                                    &  2 LODIs            &  2nd floor, flow exited through ceiling    \\
+F2000-43 \cite{NIOSH:McFall3}       &  1 serious LODI     &  1st floor to 2nd floor                    \\
+                                    &  2 other LODIs      &                                            \\
+F2004-02 \cite{NIOSH:Berardinelli}  &  1 LODD             &  1st floor to basement                     \\
+F2005-02 \cite{NIOSH:Koedam}        &  1 LODD             &  Rear to front of the building             \\
+                                    &  4 LODIs            &                                            \\
+F2005-04 \cite{NIOSH:McFall4}       &  1 LODD             &  Basement to 1st floor                     \\
+                                    &  9 LODIs            &                                            \\
+F2007-09 \cite{NIOSH:Tarley}        &  1 LODD             &  3 story training burn - flow through      \\
+                                    &  2 LODIs            &  all levels                                \\
+F2007-35 \cite{NIOSH:Braddee}       &  4 LODIs            &  1st floor to 2nd floor                    \\
+F2009-11 \cite{NIOSH:Merinar}       &  2 LODDs            &  Rear to front of the building             \\
+F2011-13 \cite{NIOSH:Bowyer2}       &  2 LODDs            &  Lower level up stairs and through         \\
+                                    &                     &  entry door and garage                     \\
+F2011-31 \cite{NIOSH:Loflin}        &  1 LODD             &  Fire extended from lower level apartment  \\
+F2012-28 \cite{NIOSH:Bowyer}        &  1 LODD             &  Attic fire extended into closed           \\
+                                    &  1 LODI             &  porch and then into 2nd floor             \\
+\bottomrule
+\end{tabular}
+\label{tab:LODD}
+\end{table}
+
+\chapter{Existing Tests}
+Existing Tests - high thermal flux, short exposure
+
+\section{Thermal Protective Performance}
+TTP Test - PPE
+
+\section{ThemoMan}
+Thermo man - (pyro man) PPE
+
+\section{Flame Contact}
+Flame contact - helmet
+
 While under bench scale test conditions it is less difficult to decouple convective heating from a radiant heat exposure.
@@
 
-Future Research
-
+\chapter{Future Research}
 Flow loop  with 20 mph and 300 to 500 F - Donnelly
@@
 2D vs 3D samples
-Gaps – refer to Lawson and Stroup
-Instrumentation – ref to Vettori
+Gaps - refer to Lawson and Stroup
+Instrumentation - ref to Vettori
 Steam
-
-\chapter{Discussion}
 

### 2015-12-28 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
edits to ppe report

@@
 \pagenumbering{gobble}
-The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service.
+The overall objective of this inter-agency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service.
 Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.
@@
 
+{\bf LoDDs - Cherry Road and San Francisco as examples}
+
 \chapter{Existing Tests}
+
 Existing Tests - high thermal flux, short exposure
@@
 \section{Thermal Protective Performance}
-TTP Test - PPE
+TPP Test - PPE
 
-\section{ThemoMan}
+\section{ThermoMan}
 Thermo man - (pyro man) PPE
@@
 Under full scale conditions in a flow path the PPE is exposed to a combination of convective and radiative heating.
-LoDDs
-Use - Cherry Road and San Francisco as examples
-Items examined
 
+\chapter{New Tests Investigated}
 Turnout gear material
-Helmets    thermoplastic shell, fiberglas shell and leather shell
+Helmets    thermoplastic shell, fiberglass shell and leather shell
+
+items examined:\\
 Facepieces
 Old Scott AV 3000?,  New Scott 3000HT
-MSA Old  and New MSA 7
-Tests
-Heat Gun Exposure?
-Flow loops
-	Plunge test
+MSA Old  and New MSA 7\\
+
+\section{Heat Gun Exposure}
+
+\section{Flow Loops}
+
+\subsection{Plunge test}
 		Temperature, velocity, heat flux measure?
-	Thermal Flow Loop
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../../../Projects/Gear_Plunge_Tests/Pictures/Plunge_2}
+\caption{Image of plunge test apparatus configured to test a turnout gear sample.}
+\label{fig:plunge_pic}
+\end{figure}
+
+\subsection{Thermal Flow Loop}
 		Temperature, velocity, heat flux
-Full Scale
+
+\section{Full Scale Tests}
 	Delco Exposures

### 2015-12-29 Projects/DelCo_2012/Report/DelCo_2012.tex
update delco report

@@
 The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building.
-During each test, the fire was ignited and the fire developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
+During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
 Once this criteria was met, gas cooling began.
+
+\begin{figure}[ht!]
+	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
+	\caption{Time series of several gas cooling events in a continuous experiment}
+	\label{fig:gas_cooling_exp4}
+\end{figure}
 
@@
 
+\clearpage
+
 \section{Fire Suppression}
@@
 Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the rear of the single story structures and the available ventilation was both through the front doorway.
-For several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
+Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
 The fires were intended to replicate room and contents fires typically seen within residential structures.
@@
 \centering
-	\caption{Fire Suppression Test Descriptions}
-	\begin{tabular}{llllll}
-		\hline\noalign{\smallskip}
-		Test		& Agent		& Stream				& Flow Rate			& Fuel           & Ventilation     \\
-		\noalign{\smallskip}\hline\noalign{\smallskip}
-		1 (FSE1)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
-		2 (FSW2)   	&  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
-		3 (FSW3) 	&  CAF      &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
-		4 (FSE4)    &  Water    &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
-		5 (FSE5)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
-		6 (FSW6)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
-		7 (FSW7)    &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
-		8 (FSE8)    &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
-		9 (Attic 1) &  Water    &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
-		10 (Attic 2)&  CAF      &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
-		11 (FSE11)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
-		12 (FSW12)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
-		13 (FSE13)  &  Water    &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
-		14 (FSW14)  &  CAF      &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
-		\noalign{\smallskip}\hline
-	\end{tabular}
-	\label{tab:Test_Descriptions}
+\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
+\begin{tabular}{clllll}
+\toprule[1.5pt]
+Test $\#$  & Name	& Stream				& Flow Rate			& Fuel           & Ventilation     \\
+\midrule
+ 1 & CAF~1    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+ 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
+ 3 & CAF~2 	  &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+ 4 & Water~2  &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
+ 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+ 6 & CAF~3    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+ 8 & CAF~4    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
+10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
+12 & CAF~5    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
+13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
+14 & CAF~6    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
+\bottomrule[1.25pt]
+\end{tabular}\par
 \end{table}
 
-Figures~\ref{fig:Test_1_First_Suppression} and \ref{fig:Test_1_Second_Suppression} provide and overview of the impact of 30$^{\circ}$ fog CAF application on the furniture fuel package after 15~s of application from the hallway nozzle and then 15~s of application from the room nozzle (FSE1 in Table~\ref{tab:Test_Descriptions}).
-The figures provide change in temperature and heat flux measurements at several positions and elevations through the structure: structure doorway, hallway, and three locations within the burn room.
-These values are taken immediately before and after application to assess the application agent, stream, and location on interior conditions.
+Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAFs tests.
+The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
+These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
 
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
-	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_1_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-	\caption{Test 1: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_1_Second_Suppression}
-\end{figure}
-
-The same fuel load, ventilation, and suppression application durations were also tested with water as the suppression agent (FSW2 in Table~\ref{tab:Test_Descriptions}).
-Figures~\ref{fig:Test_2_First_Suppression} and \ref{fig:Test_2_Second_Suppression} show the results from these tests.
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
-	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
-	\label{fig:Test_2_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
-	\caption{Test 2: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_2_Second_Suppression}
-\end{figure}
+\begin{table}[!ht]
+\centering
+\caption{Fire Suppression Results}\label{tab:Test_Results}
+\begin{tabular}{lccc}
+\toprule[1.5pt]
+                 & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
+Test 	         & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 0.15~m (6~in) Above Floor \\
+\midrule
+CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
+Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+Water~2 Room     & 250~$^{\circ}$C - 50~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~3 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
+CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
+Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
+CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
+CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 
@@
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
-The remainder of these fire suppression images for both the furniture and wood pallet fuel loads can be found in Appendix~\ref{app:fire_suppression}.
+The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests.
+This illustrates the impact of gas cooling, indpendent of suppression agent.
+In several cases rekindling occured, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
 
@@
 
-\chapter{Fire Suppression Figures}
-\label{app:fire_suppression}
-
-\section{Furniture Fuel Package}
-\label{appsubsec:Furniture_Fuel_Package}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
-	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, First Suppression}
-	\label{fig:Test_3_First_Suppression}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
-	\caption{Test 3: Furniture Fuel Package, CAFS, 7/8" Smooth Bore, 120 gpm/60 cfm, Second Suppression}
-	\label{fig:Test_3_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
-	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, First Suppression}
-	\label{fig:Test_4_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
-	\caption{Test 4: Furniture Fuel Package, Water, 7/8" Smooth Bore, 120 gpm, Second Suppression}
-	\label{fig:Test_4_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
-	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
-	\label{fig:Test_5_First_Suppression}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
-	\caption{Test 5: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_5_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
-	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_6_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
-	\caption{Test 6: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_6_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
-	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
-	\label{fig:Test_7_First_Suppression}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
-	\caption{Test 7: Furniture Fuel Package, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_7_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
-	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_8_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
-	\caption{Test 8: Furniture Fuel Package, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_8_Second_Suppression}
-\end{figure}
-
-\clearpage
-
-\section{Wood Fuel Package}
-\label{appsubsec:Wood_Fuel_Package}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
-	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
-	\label{fig:Test_11_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
-	\caption{Test 11: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_11_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
-	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_12_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
-	\caption{Test 12: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_12_Second_Suppression}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
-	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, First Suppression}
-	\label{fig:Test_13_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
-	\caption{Test 13: Wood Fuel Package, Panel Window, Water, 30$^{\circ}$ Fog, 120 gpm, Second Suppression}
-	\label{fig:Test_13_Second_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
-	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, First Suppression}
-	\label{fig:Test_14_First_Suppression}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
-	\caption{Test 14: Wood Fuel Package, Panel Window, CAFS, 30$^{\circ}$ Fog, 120 gpm/60cfm, Second Suppression}
-	\label{fig:Test_14_Second_Suppression}
-\end{figure}
-
 \end{document}

### 2015-12-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update cafs report

@@
 \end{equation}
-The normalized temperature difference is taken because of the large variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.
+The normalized temperature difference is taken because of the variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.
+
+For the 7/8~in solid stream tests there were 7 replicate conducted for both water and CAFs suppression.
+The normalized temperature differences for the 8 thermocouples analyzed from the water experiments were compared against the same normalized temperature differences from the CAFs tests.
+These data points are visualized through a scatterplot, Fig.~\ref{fig:CAFS_Water_Comp_7_8}.
 
@@
 \end{figure}
+
+The circles in Fig.~\ref{fig:CAFS_Water_Comp_7_8} are the normalized temperature measure points.
+If water and CAFs had the exact same normalized temperature differences, all of the points would fall along solid black line in the figure.
+Circles that vary from that line represent measurements where either water or CAFS cooled more signifcantly than the other agent.
+The gray area surrounding the solid black line, represents measurment uncertainty (\ref{subsec:Uncertainty}).
+For data that fall within this area, there is an inability to determine which agent was more or less effective than the other.
+The red dashed line is the line the fits the data representing the minimal difference between the two suppression agents by a linear approximation of the data.
+Since this line falls within the gray area there is an inability to distinguish, with statistical confidence, a difference between water or CAFs to cool gases from a 7/8~in solid stream.
+
+The second water and CAFs comparison was to examine 5 replicate tests for a straight stream in the mid-position, Fig.~\ref{fig:CAFS_Water_Comp_SS_mid}.
+The same analysis was performed for this configuration.
+These results also indicate that there is
 

### 2015-12-30 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAFS report

@@
 The same analysis was performed for this configuration.
-These results also indicate that there is
+These results also illustrate the inability to discern which suppression agent is more or less effective at gas cooling.
 
@@
 \label{chap:Summary}
-
-Smoke is Fuel. A ventilation limited (fuel rich) condition had developed prior to the failure of the window. Oxygen depleted combustion products, containing carbon dioxide, carbon monoxide and
-unburned hydrocarbons filled the rooms of the structure.
-Once the window failed, the fresh air provided the oxygen needed to sustain the transition through flashover, which caused a significant increase in heat release rate.
-
-Venting does not always equal cooling.
-In this experiment, post ventilation temperatures and heat fluxes all increased, due to the ventilation induced flashover.
-Fire induced flows.
-Velocities within the structure exceeded 5 m/s (11 mph), just due to the fire growth and the flow path that was set-up between the window opening and the corridor vent.
-Avoid the flow path.
-The directional nature of the fire gas flow was demonstrated with thermal conditions, both temperature and heat flux, which were twice as high in the ``flow'' portion of the
-corridor as opposed to the ``static" portion of the corridor. Thermal conditions in the flow path were not consistent with firefighter survival.
-
-The fuel load in the structure was the same for all of the experiments.
-Each of these experiments demonstrated a rapid transition to untenable conditions in the corridor, even for a firefighter in full PPE.
-
-The externally applied water streams were implemented in three different ways; a fog stream across the face of the window opening, a fog stream into the window opening, and a solid water stream into the window opening.
-
-These experiments demonstrated the ``extreme'' thermal conditions that can be generated by a ``simple room and contents'' fire and how these conditions can be extended along a flow path within a structure.
-The experiments also provided potential guidance for firefighters as a part of a fire size up and approach to the room of fire origin: note wind conditions in the area of the fire, look for ``pulsing flames'', examine smoke conditions around closed doors in the potential flow path, and maintain control of doors in the flow path.
-
-Further research in actual buildings is required to fully understand the ability of firefighters to implement these tactics, to examine the thermal conditions throughout the structure such as in stairways, and to examine the interaction of these tactics with building ventilation strategies both natural and with positive pressure ventilation.
 

### 2015-12-31 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to cafs paper

@@
 \chapter*{\centering Abstract}
-Traditionally, fire fighting suppression operations have been conducted from the interior of the structure as a means to reduce water damage, manage the ``thermal balance'', and limit fire damage to structures.
-In current fire fighter training manuals, it is stated that these operations must be coordinated with the ventilation operations.
-However guidance on that coordination has been limited.
-Previous research and examinations of line of duty deaths have shown that ventilation events occurring with fire fighters in the structure prior to suppression have led to tragic results.
-One means of reducing the possibilities of this occurrence would be to begin to extinguish the fire prior to entering the structure.
-In effect, an offensive, exterior fire attack, in which water is directed into the structure from the exterior to cool the fire gases and reduce the heat release rate of the fire, prior to the fire fighters entering the building.
-The major concern with this type of operation is the potential harm that might occur to people trapped in the structure or the amount of water damage to the structure.
-Additionally, the type of suppression agent can affect the fire behavior within the structure.
-The suppression agent is the main focus of this study to determine whether or not compressed air foam systems provide any significant benefit to the traditional water application.
-Therefore, measurements are needed to document the changes of the thermal environment within the structure due to interior and exterior fire suppression tactics over all types of suppression agents.
-This report will focus on water distribution and fire suppression experiments conducted to develop a baseline for the interior fire suppression using both water and compressed air foam application.
+
 \pagenumbering{gobble}

### 2016-01-11 Projects/DelCo_2012/Report/DelCo_2012.tex
update figures, report, plotting scripts

@@
 Each bin was then weighed to quantify the impact of nozzle location and spray pattern.
-Thirty-three spray density tests were conducted; 21 were in the burn building and 12 were in the concrete structure.
-Table~\ref{tab:spray_density_tests} provides an overview of each experiment.
-In the table, BB stands for the burn building tests while CS stands for the concrete structure tests.
+Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments.
+Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
+In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments.
 For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.
+
+For the gas cooling tests, Table~\ref{tab:spray_density_tests}, the mid position had center line of the stream aimed at 2.44~m (8~ft) south of the North wall and 2.13~m (7~ft) west of the East wall in the concrete burn building.
+The back position had the center line of the stream aimed at 3.36~m (11~ft) south of the North wall and 2.13~m west (7~ft) of the East wall in the concrete burn building.
 
@@
 \centering
-\captionof{table}{Spray Density Test Matrix}\label{tab:spray_density_tests}
-\begin{tabular}{lllllll}
+\captionof{table}{Spray Density Test Matrix for Gas Cooling Experiments}\label{tab:spray_density_tests}
+\begin{tabular}{llllll}
 \toprule[1.5pt]
-Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Height (in) & Location (in) \\
+Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Position  \\
 \midrule
-BB1        &   123              & 15            & Water  &  Solid Stream back  & 20~7/8             &          \\
-BB2        &   122              & 23            & Water  &  Solid Stream       &                    &          \\
-BB3        &   119              &               & Water  &  Solid Stream       & 16                 &          \\
-BB4        &   118              &               & Water  &  Solid Stream       & 16                 &          \\
-BB5        &   118              & 20            & Water  &  Solid Stream       & 16                 &          \\
-BB6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
-BB7        &   118              & 21            & Water  &  30$^{\circ}$ Fog   & 15                 &          \\
-BB8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & 17                 &          \\
-BB9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & 17~1/2             &          \\
-BB10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & 12~1/2             &          \\
-BB11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & 11~1/2             &          \\
-BB12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & 12~1/2             &          \\
-BB13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in &                    &          \\
-BB16       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
-BB17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream narrow & 15                &          \\
-BB18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream mid   &                    &          \\
-BB19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & 15                 &          \\
-BB20       &   120 / 60cfm      &               & CAF    &  30$^{\circ}$ Fog   & 17                 &          \\
-BB21       &   120 / 60cfm      &               & CAF    &  Solid Stream back  &                    &          \\
-CS1        &   115              & 7             & Water  &  Solid Stream       &                    &          \\
-CS2        &   115              & 18            & Water  &  Solid Stream       &                    &          \\
-CS3        &   120              & 19            & Water  &  Solid Stream       &                    &          \\
-CS4        &   118              & 21            & Water  &  Solid Stream       &                    &          \\
-CS5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &                    &          \\
-CS6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &                    &          \\
-CS7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &                    &          \\
-CS7.2      &   120              & 17            & Water  &  Solid 7/8~in Slug  & 18                 &          \\
-CS8        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &                    &          \\
-CS9        &   116              & 16            & Water  &  30$^{\circ}$ Fog   &                    &          \\
-CS10       &   116              & 16            & Water  &  Solid Stream       &                    &          \\
-CS11       &   117              & 16            & Water  &  Solid Stream       &                    &          \\
+GC1        &   123              & 15            & Water  &  Solid Stream       & Back             \\
+GC2        &   122              & 23            & Water  &  Solid Stream       & Back             \\
+GC3        &   119              & 15            & Water  &  Solid Stream       & Mid              \\
+GC4        &   118              & 15            & Water  &  Solid Stream       & Mid              \\
+GC5        &   118              & 20            & Water  &  Solid Stream       & Mid              \\
+GC6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
+GC7        &   118              & 20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
+GC8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & Back             \\
+GC9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & Back             \\
+GC10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & Back             \\
+GC11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & Back             \\
+GC12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
+GC13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
+GC14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
+GC15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
+GC16       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
+GC17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream       & Mid             \\
+GC18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream       & Mid             \\
+GC19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC20       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC21       &   120 / 60cfm      & 15            & CAF    &  Solid Stream       & Back             \\
+
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+For the fire suppression spray density experiments, Table~\ref{tab:spray_density_tests2}, the hallway position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 1.53~m (5~ft) east of the West wall.
+The fire room position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 3.05~m (10~ft) west of the East wall.
+
+\begin{table}[!ht]
+\footnotesize
+\centering
+\captionof{table}{Spray Density Test Matrix for Fire Suppression Experiments}\label{tab:spray_density_tests2}
+\begin{tabular}{llllll}
+\toprule[1.5pt]
+Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Location  \\
+\midrule
+SE1        &   115              & 7             & Water  &  Solid Stream       &    Fire Room          \\
+SE2        &   115              & 18            & Water  &  Solid Stream       &    Fire Room          \\
+SE3        &   120              & 19            & Water  &  Solid Stream       &    Fire Room          \\
+SE4        &   118              & 21            & Water  &  Solid Stream       &    Fire Room          \\
+SE5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
+SE6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
+SE7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
+SE8        &   120              & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
+SE9        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
+SE10       &   116              & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
+SE11       &   116              & 16            & Water  &  Solid Stream       &    Hallway            \\
+SE12       &   117              & 16            & Water  &  Solid Stream       &    Hallway            \\
 \bottomrule[1.25pt]
@@
 After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution.
-Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream positioned {\bf here} the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (cf.
+Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream in the back position, the majority of the water accumulated along the North and East walls of the gas cooling room within the burn building (cf.
 Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB1}
-	\caption{Burn Building Test 1}
+	\caption{Gas Cooling Spray Density Test 1}
 	\label{fig:Burn_Building_Test_1}
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB7}
-	\caption{Burn Building Test 7}
+	\caption{Gas Cooling Spray Density Test 7}
 	\label{fig:Burn_Building_Test_7}
@@
 The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building.
-During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 260~$^{\circ}$C (500~$^{\circ}$F).
+During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
 Once this criteria was met, gas cooling began.

### 2016-01-11 Projects/DelCo_2012/Scripts/water_plot.py

@@ -1,8 +1,8 @@
-#Weinschenk
-#2-15
-
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
 from __future__ import division
 import os
+import string
 import numpy as np
 import pandas as pd
 from pylab import *

### 2016-01-14 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Tests_2014.tex
DelCo_2014 and DelCo_2015 combined into one directory

--- 2015-09-28 Projects/DelCo_2014/Report/Hose_Stream_Report/Report/DelCo_Hose_Tests_2014.tex
@@
 \includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
+\\~\\
 \includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
-\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the first floor (top) and second floor (bottom) of the West Structure.}
+\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the second floor (top) and first floor (bottom) of the West Structure.}
 \label{fig:west_general_plan}
@@
 \begin{figure}[!ht]
+\
 \includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+\\~\\
 \includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
@@
 \includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+\\~\\
 \includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_custom_BDP_A10_Avg}
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
 \caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
-\label{fig:Test_16_BDP_A10_Avgs}
+\label{fig:Test_16_BDP_A10_Avg_All}
 \end{figure}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
+\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
 \begin{tabular}{lccccc}
@@
 
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_Avg_CW_vs_CCW}
-%\caption{Average Velocity of Stairwell Door, Test 18, All Streams, CW vs. CCW}
-%\label{fig:Test_18_BDP_A10_Avg_CW_vs_CCW}
-%\end{figure}
-%
-%\begin{figure}[!ht]
-%\includegraphics[width=6in]{../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_Avg_CW_vs_CCW}
-%\caption{Average Velocity of Stairwell Door, Test 19, All Streams, CW vs. CCW}
-%\label{fig:Test_19_BDP_A10_Avg_CW_vs_CCW}
-%\end{figure}
-%
-%\clearpage
-
 % ===========
@@
 
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
+\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
+\label{fig:Test_17_BDP_A10_Avg_All}
+\end{figure}
+\FloatBarrier
+
 \subsection{Handline Figures}

### 2016-01-14 Projects/DelCo_2014_2015/Report/hose_report.tex
DelCo_2014 and DelCo_2015 combined into one directory

--- 2015-10-12 Projects/DelCo_2015/Report/hose_report.tex
@@
 \setlength{\parindent}{15pt} % Indent paragraphs
-
+\usepackage{color}
+\newcommand{\white}[1]{{\textcolor{white}{#1}}}
 \hypersetup{colorlinks=true, urlcolor=blue, citecolor=black, linkcolor=blue}
@@
 
-\memofrom{Daniel Madrzykowski \\ Craig Weinschenk \\ NIST Firefighting Technology Group} % Sender(s)
+\memofrom{Daniel Madrzykowski \\ \white{s:}Craig Weinschenk \\ \white{s:}NIST Firefighting Technology Group} % Sender(s)
 
@@
 An open stair extends from Side A and leads to the upper level with an open doorway facing Side C of the structure.
-The ventilation openings on the upper level include a 36~in.
-by 80~in.
-doorway and a 66~in.
-wide by 36~in.
-high window with a 43~in.
-sill height on the A side.
+The ventilation openings on the upper level include a 0.91~m (3~ft) by 2.0~m (6.7~ft) doorway and a 1.7~m (5.5~ft) wide by 0.91~m (3~ft) high window with a 1.1~m (3.6~ft) sill height on the A side.
 On C side of the upper level is another set of double doors similar in size to the set of doors on the lower level.
@@
 \includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_a}
-\includegraphics[width=0.45\columnwidth]{../Figures/Hose_Figures/exterior_c}
+\includegraphics[width=0.45\columnwidth,trim = 1.25in 1.5in .75in 0in, clip=true,]{../Figures/Hose_Figures/exterior_c}
 \caption{Photographs of Side A (Left) and Side C (Right). }
@@
 \centering
-\includegraphics[width=0.8\columnwidth]{../Figures/Hose_Figures/test_setup_1b}
+\includegraphics[width=0.8\columnwidth,angle =-90]{../Figures/Hose_Figures/test_setup_1b}
 \caption{Locations of instrumented hose samples relative to the vertical thermocouple array, the heat flux gauge and the radiometer.}
@@
 
-\begin{figure}[!ht]
-\centering
-\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
-\caption{Schematic showing the test arrangement on the lower level.
+% \begin{figure}[!ht]
+% \centering
+% \includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/test_plan}
+% \caption{Schematic showing the test arrangement on the lower level.
 The circle represents the thermocouple array, the diamond represents the heat flux gauge and radiometer, and the squares represent the bi-directional velocity probes in the open doorway on Side C.}
-\label{fig:test_plan}
-\end{figure}
+% \label{fig:test_plan}
+% \end{figure}
 
@@
 In Experiment 2 the exposed hose section and instrumentation was located 1.2~m (4~ft) from the open doorway on Side C.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=.8\columnwidth]{../Figures/Hose_Figures/IMG_8431}
+\caption{Photograph as the fire room transitioned to flashover in Experiment 2.}
+\label{fig:flashover}
+\end{figure}
 

### 2016-01-14 Projects/DelCo_2015/Scripts/plot.py

@@ -1,429 +1,0 @@
-# -*- coding: utf-8 -*-
-from __future__ import unicode_literals
-#!/usr/bin/env python
-
-import os
-import collections
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-from itertools import cycle
-
-from matplotlib import rcParams
-rcParams.update({'figure.autolayout': True})
-
-#  =================
-#  = User Settings =
-#  =================
-
-# Choose Test Number
-current_test = 'Test_73_Burn_2nd_Floor_101315_BDPs'
-
-# Plot mode: figure or video
-plot_mode = 'figure'
-
-# Location of experimental data files
-data_dir = '../Experimental_Data/'
-
-# Location of file with timing information
-all_times_file = '../Experimental_Data/All_Times.csv'
-
-# Location of scaling conversion files
-scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
-scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
-
-# Location of test description file
-info_file = '../Experimental_Data/Description_of_Experiments.csv'
-
-# Location to save/output figures
-if plot_mode == 'figure':
-    save_dir = '../Figures/Script_Figures/'
-elif plot_mode == 'video':
-    save_dir = '../Figures/Video_Figures/'
-
-# Time averaging window for data smoothing
-data_time_averaging_window = 5
-
-# Duration of pre-test time for bi-directional probes and heat flux gauges (s)
-pre_test_time = 60
-
-# Common quantities for y-axis labelling
-heat_flux_quantities = ['HF_', 'RAD_']
-gas_quantities = ['CO_', 'CO2_', 'O2_']
-
-# Load exp. timings and description file
-all_times = pd.read_csv(all_times_file)
-all_times = all_times.set_index('Time')
-info = pd.read_csv(info_file, index_col=3)
-
-# Files to skip
-skip_files = ['_times', '_reduced', 'description_','zero_','_rh','burn','helmet']
-#  ===================
-#  = Video Plot Mode =
-#  ===================
-
-video_test_name = 'Test_38_West_61315'
-video_groups = ['Heat Flux']
-video_channels = ['Heat Flux 1 V West','Heat Flux 1 H West','Heat Flux Mask']
-video_line_colors = ['yellow', 'cyan', 'green']
-video_ylabel = 'Heat Flux (kW/m$^2$)'
-video_rescale_factor = 1
[…]

### 2016-01-20 Projects/DelCo_2012/Report/DelCo_2012.tex
Edit CAFS title

@@
 Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
-Spring 2012 \\
 }
@@
 Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments.
+The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAFS.
 Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
@@
 \captionof{table}{Spray Density Test Matrix for Gas Cooling Experiments}\label{tab:spray_density_tests}
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule[1.5pt]
-Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Position  \\
+Test \#    &  Duration (s)  & Agent  &  Pattern            & Nozzle Position  \\
 \midrule
-GC1        &   123              & 15            & Water  &  Solid Stream       & Back             \\
-GC2        &   122              & 23            & Water  &  Solid Stream       & Back             \\
-GC3        &   119              & 15            & Water  &  Solid Stream       & Mid              \\
-GC4        &   118              & 15            & Water  &  Solid Stream       & Mid              \\
-GC5        &   118              & 20            & Water  &  Solid Stream       & Mid              \\
-GC6        &   120              & 21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
-GC7        &   118              & 20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
-GC8        &   119              & 22            & Water  &  30$^{\circ}$ Fog   & Back             \\
-GC9        &   120              & 24            & Water  &  30$^{\circ}$ Fog   & Back             \\
-GC10       &   127              & 20            & Water  &  Solid 7/8~in Slug  & Back             \\
-GC11       &   120              & 22            & Water  &  Solid 7/8~in Slug  & Back             \\
-GC12       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
-GC13       &   120 / 60cfm      & 10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
-GC14       &   120 / 60cfm      & 15            & CAF    &  Smooth Bore 7/8~in & Back             \\
-GC15       &   120 / 60cfm      & 20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
-GC16       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
-GC17       &   120 / 60cfm      & 20            & CAF    &  Solid Stream       & Mid             \\
-GC18       &   120 / 60cfm      & 10            & CAF    &  Solid Stream       & Mid             \\
-GC19       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
-GC20       &   120 / 60cfm      & 15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
-GC21       &   120 / 60cfm      & 15            & CAF    &  Solid Stream       & Back             \\
+GC1        &  15            & Water  &  Solid Stream       & Back             \\
+GC2        &  23            & Water  &  Solid Stream       & Back             \\
+GC3        &  15            & Water  &  Solid Stream       & Mid              \\
+GC4        &  15            & Water  &  Solid Stream       & Mid              \\
+GC5        &  20            & Water  &  Solid Stream       & Mid              \\
+GC6        &  21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
+GC7        &  20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
+GC8        &  22            & Water  &  30$^{\circ}$ Fog   & Back             \\
+GC9        &  24            & Water  &  30$^{\circ}$ Fog   & Back             \\
+GC10       &  20            & Water  &  Solid 7/8~in Slug  & Back             \\
+GC11       &  22            & Water  &  Solid 7/8~in Slug  & Back             \\
+GC12       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
+GC13       &  10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
+GC14       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
+GC15       &  20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
+GC16       &  15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
+GC17       &  20            & CAF    &  Solid Stream       & Mid             \\
+GC18       &  10            & CAF    &  Solid Stream       & Mid             \\
+GC19       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC20       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC21       &  15            & CAF    &  Solid Stream       & Back             \\
 
@@
 \captionof{table}{Spray Density Test Matrix for Fire Suppression Experiments}\label{tab:spray_density_tests2}
-\begin{tabular}{llllll}
+\begin{tabular}{lllll}
 \toprule[1.5pt]
-Test \#    &   Flow Rate (gpm)  & Duration (s)  & Fluid  &  Pattern            & Nozzle Location  \\
+Test \#    & Duration (s)  & Agent  &  Pattern            & Nozzle Location  \\
 \midrule
-SE1        &   115              & 7             & Water  &  Solid Stream       &    Fire Room          \\
-SE2        &   115              & 18            & Water  &  Solid Stream       &    Fire Room          \\
-SE3        &   120              & 19            & Water  &  Solid Stream       &    Fire Room          \\
-SE4        &   118              & 21            & Water  &  Solid Stream       &    Fire Room          \\
-SE5        &   118              & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
-SE6        &   118              & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
-SE7        &   125              & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
-SE8        &   120              & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
-SE9        &   116              & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
-SE10       &   116              & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
-SE11       &   116              & 16            & Water  &  Solid Stream       &    Hallway            \\
-SE12       &   117              & 16            & Water  &  Solid Stream       &    Hallway            \\
+SE1        & 7             & Water  &  Solid Stream       &    Fire Room          \\
+SE2        & 18            & Water  &  Solid Stream       &    Fire Room          \\
+SE3        & 19            & Water  &  Solid Stream       &    Fire Room          \\
+SE4        & 21            & Water  &  Solid Stream       &    Fire Room          \\
+SE5        & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
+SE6        & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
+SE7        & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
+SE8        & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
+SE9        & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
+SE10       & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
+SE11       & 16            & Water  &  Solid Stream       &    Hallway            \\
+SE12       & 16            & Water  &  Solid Stream       &    Hallway            \\
 \bottomrule[1.25pt]

### 2016-01-24 Projects/DelCo_2012/Report/DelCo_2012.tex
update cafs report

@@
 
-The fire suppression series included 14 tests in two single-story experimental structures.
-Six tests were conducted in the East structure and six tests were conducted in the West structure, each including both water and CAF application as a suppression agent.
+The fire suppression series included 18 tests in two single-story experimental structures and one two-story structure.
+Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAFs application as a suppression agent.
 The nozzle patterns were varied from straight stream to narrow fog.
-Two additional tests were conduction on suppression tactics for attic fires in residential dwellings, one in each structure.
-For these tests, a smooth bore nozzle was used.
+Two of the tests examined suppression tactics for attic fires in residential dwellings, one in each structure.
+For the attic tests, a smooth bore nozzle was used.
+The 4 two-story tests used both water and CAF from a straight-stream nozzle.
 
@@
 
-Two identical concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}.
+Two identical single story concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}.
 They were designed to simulate a single floor of a residential structure.
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=6in]{../Figures/Pictures/DelCoSingleStory}
-% 	\caption{Delaware County, PA Fire Test Structure}
-% 	\label{fig:DelCoSingleStory}
-% \end{figure}
-
 \begin{figure}[!ht]
@@
 The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.
+
+The west structure was modified to add second story to be able to test larger fires and remote effects from suppression.
+The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan.
+The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
+The second story walls were framed with steel studs and track.
+The studs were set to 0.40~m (16~in) centers.
+
+\begin{figure}[!ht]
+	\includegraphics[width=6in]{../Figures/Pictures/DelCo}
+	\caption{Delaware County, PA Fire Two-Story Test Structure}
+	\label{fig:delco_2story}
+\end{figure}
 
@@
 
-The fire suppression testing included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs.
+The fire suppression testing in the single story included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs.
 Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf.
@@
 	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
+\end{figure}
+
+Fire suppression testing in the two-story structure included similar types instrumentation but included more sensors.
+Three bare-bead thermocouple arrays and 2 bi-directional probe plus solid thermocouples arrays were used in the first floor.
+Fig.~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (cf.
+Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests.
+The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit with the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
+	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure.}
+	\label{fig:fire_supp_first_2story}
+\end{figure}
+
+The second story featured 6 bare-bead arrays and 3 bi-directional probe plus solid thermocouple arrays.
+The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground.
+Fig.~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (cf.
+Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level.
+The bi-direction probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level.
+The third bi-directional probe array (3~m (9~ft) off the North wall and 0.6~m (2~ft) off the East wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
+	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure.}
+	\label{fig:fire_supp_second_2story}
 \end{figure}
@@
 
+\paragraph{Single-Story Structures}
+\label{sec:suppresion_single}
+
 \subsubsection{Wood Fuel Package}
@@
 \end{sidewaystable}
+
+\paragraph{Two-Story Structures}
+\label{sec:suppresion_two}
 

### 2016-01-24 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to CAFS

@@
 
+\subsubsection{Furniture Fuel Package}
+\label{sec:fire_suppression_furniture_fuel_2}
+
+The fuel load for two of the experiments consisted of 3 sofas, carpet, padding, and oriented strand board (OSB) paneling along the East, West, and South walls and ceiling.
+The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart.
+The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}.
+In total, this fuel package contains approximately {\bf XXX} fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
+	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
+	\label{fig:furniture_2story}
+\end{figure
+
+\subsubsection{Furniture and Pallet Fuel Package}
+\label{sec:fire_suppression_combo_fuel_2}
+
 \chapter{Experiments and Results}

### 2016-01-28 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
updated hose stream plotting script and report

--- 2016-01-14 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Tests_2014.tex
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
+\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
 \caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
@@
 \textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
-\\ \bottomrule
+\\ \midrule
+ & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
+\textbf{Stream} &
+\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
+\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+\multicolumn{3}{c}{} 
+\\
+\midrule
+\textit{Straight} & 1.7 $\pm0.2$ & 1.9 $\pm0.2$ & \multicolumn{3}{c}{} 
+\\ \multicolumn{6}{c}{} \\
+\textit{Smooth Bore} & 1.7 $\pm0.2$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
+\\
+\bottomrule
 \end{tabular}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
+\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
 \caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
+\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
 \caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Test_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
+\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
 \caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}

### 2016-01-28 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -22,7 +22,7 @@ specify_test = False
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = False
+specify_year = True
 specific_year = '2015'
 
 # Specify structure
@@ -34,15 +34,15 @@ specify_type = False
 specific_type = 'monitor'
 
 # Files to skip
-skip_files = ['_times', '_reduced', '_results', 'description_', 'HOSE_D']
+skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh', '_burn', '_span']
 
 # =============================
 # = Specify files to generate =
 # =============================
 
 result_file = True         # Generate a .csv file with channel avgs for specified sensor groups
-all_channel_plot = True    # Plot of individual channels in sensor group
-group_avg_plot = True      # Plot avg of all channels for sensor group
+all_channel_plot = False    # Plot of individual channels in sensor group
+group_avg_plot = False     # Plot avg of all channels for sensor group
 stream_avgs_plot = True    # Plot avg of all channels for each stream tested during experiment
 
 # latex_table_code = False    # Print code to generate tables in LaTeX?
@@ -72,8 +72,8 @@ stream_avgs_plot = True    # Plot avg of all channels for each stream tested dur
 #         '\\begin{tabular}{@{}c@{}} \\textbf{Counter} \\\ \\textbf{Clockwise} \\\ \\end{tabular}', '\\textbf{Fixed}', 
 #         '\\textbf{Clockwise}', '\\begin{tabular}{@{}c@{}} \\textbf{Counter} \\\ \\textbf{Clockwise} \\\ \\end{tabular}']
 
-    # East monitor table
-    # east monitor data currently included in west monitor table #
+	# East monitor table
+	# east monitor data currently included in west monitor table #
 
 #  =======================
 #  = Directory Locations =
@@ -97,198 +97,215 @@ info = pd.read_csv(info_file, index_col=3)
 
 # Prints an error message and stops code
 def error_message(message):
-    lineno = inspect.currentframe().f_back.f_lineno
-    print '[ERROR, line '+str(lineno)+']:'  
-    print '  ' + message
-    sys.exit()
+	lineno = inspect.currentframe().f_back.f_lineno
+	print '[ERROR, line '+str(lineno)+']:'  
+	print '  ' + message
+	sys.exit()
 
 # checks if file should be skipped
 def check_name(test_name, test_year, test_type):
-    if specify_test:        # Skip if not specified test
[…]

### 2016-01-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Deleted excess biblio material from header

@@
-@manual{ID,
-	ALTauthor = {author},
-	ALTeditor = {editor},
-	title = {title},
-	date = {date},
-	OPTsubtitle = {subtitle},
-	OPTtitleaddon = {titleaddon},
-	OPTlanguage = {language},
-	OPTedition = {edition},@unpublished{ID,
-		author = {author},
-		title = {title},
-		date = {date},
-		OPTsubtitle = {subtitle},
-		OPTtitleaddon = {titleaddon},
-		OPTlanguage = {language},
-		OPThowpublished = {howpublished},
-		OPTnote = {note},
-		OPTlocation = {location},
-		OPTisbn = {isbn},
-		OPTdate = {date},
-		OPTmonth = {month},
-		OPTyear = {year},
-		OPTaddendum = {addendum},
-		OPTpubstate = {pubstate},
-		OPTurl = {url},
-		OPTurldate = {urldate},
-	}
-
-	OPTtype = {type},
-	OPTseries = {series},
-	OPTnumber = {number},
-	OPTversion = {version},
-	OPTnote = {note},
-	OPTorganization = {organization},
-	OPTpublisher = {publisher},
-	OPTlocation = {location},
-	OPTisbn = {isbn},
-	OPTchapter = {chapter},
-	OPTpages = {pages},
-	OPTpagetotal = {pagetotal},
-	OPTaddendum = {addendum},
-	OPTpubstate = {pubstate},
-	OPTdoi = {doi},
-	OPTeprint = {eprint},
-	OPTeprintclass = {eprintclass},
-	OPTeprinttype = {eprinttype},
-	OPTurl = {url},
-	OPTurldate = {urldate},
-}
 \documentclass[twoside]{uocthesis}

### 2016-02-01 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
DelCo_2014_2015: Added folder for FDS validation report

--- 2014-04-30 Projects/DelCo_2014_04/Report/DelCo_2014.tex
@@
 
-\input{../../../Bibliography/commoncommands}
+\input{../../../../../Bibliography/commoncommands}
 
@@
 \headerB{
-Delco 2014
+Overview of Fire Model Validation Experiments in Residential Scale Structures
 }
@@
 \flushright{
-Daniel Madrzykowski \\
-Craig G. Weinschenk \\
-Kristopher J. Overholt \\
+Joseph Willi \\
+Kevin McGrattan \\
+Randall McDermott \\
+Craig Weinschenk \\
 {\em Fire Research Division \\
@@
 \flushright{
-\includegraphics[width=2.in]{../../../Bibliography/nistident_flright_vec} \\[.3in]
+\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
 }
@@
 
-\chapter{Results}
-\label{chap:Results}
+\section{Experimental Structure}
+\label{sec:Experimental_Structure}
 
-\section{Hose Flow Tests}
+\subsection{Construction}
+\label{sec:Construction}
 
-\subsection{DNXAXX}
+\section{Instrumentation}
+\label{sec:Instrumentation}
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A7}
-\end{figure}
+\chapter{Experimental Procedure}
+\label{chap:Experimental_Procedure}
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXAXX_HOSE}
-\caption{Hose pressure, Test HOSE\_DNXAXX}
-\label{fig:HOSE_DNXAXX_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{DNXOXF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DNXOXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DNXOXF}
-\label{fig:HOSE_DNXOXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{DSXAXF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXAXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DSXAXF}
-\label{fig:HOSE_DSXAXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{DSXOXF}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_DSXOXF_HOSE}
-\caption{Hose pressure, Test HOSE\_DSXOXF}
-\label{fig:HOSE_DSXOXF_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{IXAOXX}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A6}
-\caption{Velocity at interior Door CD, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXAOXX_HOSE}
-\caption{Hose pressure, Test HOSE\_IXAOXX}
-\label{fig:HOSE_IXAOXX_HOSE}
-\end{figure}
-
-\clearpage
-
-\subsection{IXXAXX}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A6}
-\caption{Velocity at interior Door CD, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A6}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A7}
-\caption{Velocity at exterior Door A, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/HOSE_IXXAXX_HOSE}
-\caption{Hose pressure, Test HOSE\_IXXAXX}
-\label{fig:HOSE_IXXAXX_HOSE}
-\end{figure}
-
-\clearpage
-
-\section{Fire Tests}
-
-\subsection{FIRE\_FA2S1C1NCX1\_1}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_1_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_1}
-\label{fig:FIRE_FA2S1C1NCX1_1_TC_A5}
-\end{figure}
-
-\clearpage
-
-\subsection{FIRE\_FA2S1C1NCX1\_2}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_2_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_2}
-\label{fig:FIRE_FA2S1C1NCX1_2_TC_A5}
-\end{figure}
-
-\clearpage
-
-\subsection{FIRE\_FA2S1C1NCX1\_3}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A7}
-\caption{Velocity at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A7}
-\caption{Temperature at exterior Door A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A7}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A8}
-\caption{Velocity at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A8}
-\caption{Temperature at exterior Door C\_West, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A8}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_BDP_A9}
-\caption{Velocity at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_BDP_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A9}
-\caption{Temperature at exterior Door C\_East, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A9}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_GAS}
-\caption{Gas Concentration, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_GAS}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_HF}
-\caption{Heat Flux, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_HF}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A1}
-\caption{Temperature at TC Tree A1, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A1}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A2}
-\caption{Temperature at TC Tree A2, Room A, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A2}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A3}
-\caption{Temperature at TC Tree A3, Room B, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A3}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A4}
-\caption{Temperature at TC Tree A4, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A4}
-\end{figure}
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Figures/FIRE_FA2S1C1NCX1_3_TC_A5}
-\caption{Temperature at TC Tree A5, Room C, Test FIRE\_FA2S1C1NCX1\_3}
-\label{fig:FIRE_FA2S1C1NCX1_3_TC_A5}
-\end{figure}
-
-\clearpage
-
-\chapter{Conclusions}
-\label{chap:Conclusions}
-
-\chapter{Acknowledgements}
-\label{chap:Acknowledgements}
+\chapter{Acknowledgments}
+\label{chap:Acknowledgments}
 

### 2016-02-01 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
DelCo_2014_2015: Added folder for FDS validation report

--- 2016-01-28 Projects/DelCo_2014_2015/Report/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
@@
 \includegraphics[width=6in]{../Pictures/TJI_support}
-\caption[TJI-constructred ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams.
-View is of the east side of the structure.}
+\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
 \label{fig:TJI}

### 2016-02-01 Projects/DelCo_2014_2015/Reports/Test_Matrix_2015.tex
DelCo_2014_2015: Added folder for FDS validation report

\documentclass{article}

\usepackage{nopageno}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{pdfsync}
\usepackage{microtype}
\usepackage{siunitx}
\usepackage{rotating}
\usepackage{tabularx,ragged2e,booktabs,caption}
\usepackage{caption}
\frenchspacing

\begin{document}

\begin{sidewaystable}[htbp]
\centering
\captionof{table}{DelCo ESTC 2015 Tests}\label{tab:tests}
\begin{tabular}{lllll}
\toprule[1.5pt]
Test \#         &  Vent Configuration         	& Attack           & Hose Stream                         & Gear      \\
\midrule
30 West         &  Cherry Road                	& Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
31 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 120~gpm                  & 3 samples \\
32 West         &  Cherry Road + upper C doors  & Uncoordinated    &  Straight, 120~gpm                  & 2 samples \\
33 West         &  PPV Test                     & & &           \\  
34 West         &  Cherry Road                  & Coordinated      &  Straight, 120~gpm                  & 3 samples \\   
35 West         &  Cherry Road + PPV            & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples \\
36 West         &  Cherry Road                  & Coordinated      &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
37 West         &  Cherry Road                  & Uncoordinated    &  Straight, 180~gpm + interior fog   & 3 samples + manikin \\
38 West         &  Open A door + C doors        &                  &  Straight, CAFS, 120~gpm            & 3 samples + facepieces \\
39 West 		&  Open A door + C doors        &                  &  Straight, 130~gpm                  & \\
40 West 		&  Open A door + C doors        &                  &  Straight, CAFS, 130~gpm            & \\
41 West 		&  Open A door + C doors        &                  &  CAFS, varied                       & \\
42 West 		&  Cherry Road + upper C doors  & Allow decay      &  Piercing Nozzle, 150~gpm           & \\
43 West 		&  Open A door + C doors        &                  &  Straight/narrow fog, 120/180~gpm   & 1 sample \\
44 West 		&  Open A door + C doors        &                  &  Interior wide fog, 130~gpm         & 1 sample, facepiece \\
45 West         &  Open A door + C doors        & Delay water 44   &  Interior wide fog, 130~gpm         & 1 sample, facepiece, helmet \\
46 West         &  Cherry Road; single basement & Uncoordinated    &  Straight, 150~gpm					 & \\
47 West         &  Cherry Road					& Coordinated      &  Straight, 140~gpm					 & head forms \\
48 West         &  Cherry Road					& Uncoordinated    &  Straight, 180~gpm                  & head forms \\
49 East         &  C Doors                      & Sprinklered      & & \\
50 West         &  Cherry Road + Vertical		& Uncoordinated    &  Straight, 180~gpm                  & \\
51 East         &  C Doors                      & Sprinklered      & & \\
52 East			&  PPV Test 					& & &			\\
53 East			&  PPV Test 					& & &			\\
54 East			&  PPV Test 					& & &			\\
55 East			&  PPV Test 					& & &			\\
56 West			&  Cherry Road					& Coordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\ 
57 West			&  Cherry Road					& Uncoordinated	   &  Straight, 150~gpm					 & 3 samples + head forms \\
58 East			&  Single C door Open, A fire 	& C door    	   &  Straight, 150~gpm                  & \\
59 East         &  C window, A fire				& C window  	   &  Straight, 150~gpm					 & \\
60 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
61 East         &  C window, C fire             & C window         &  Wide fog, 150~gpm                  & \\
62 West			&  Open C Doors 				& 				   &									 & 3 hose samples \\
63 East         &  C window + window base       & C window         &  Wide fog, 150~gpm 			     & \\
64 West         &  Cherry Road + delayed vent   & Uncoordinated    &  Straight, 150~gpm					 & 3 samples + head forms \\
65 East			&  PPV Test 					& & & 			\\
66 East         &  Single C door, C fire		& C Door 		   &  Wide, narrow, straight, 150~gpm	 & \\

\bottomrule[1.25pt]
\end{tabular}
\end{sidewaystable}

\end{document}

### 2016-02-01 Projects/DelCo_2012/Report/DelCo_2012.tex
add } to fix figure error in report
edits to CAFS report

@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
-	\caption{Delaware County, PA Burn Building Layout}
+	\caption{Dimensioned Floor Plan Burn Building Layout}
 	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
@@
 \label{sec:Experimental Structures}
+\subsubsection*{Single Story Structures}
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
-	\caption{Floor Plan of the Test Structure.}
+	\caption{Dimensioned Floor Plan of the Test Structure.}
 	\label{fig:Test_Structure_Floor_Plan}
@@
 
-The west structure was modified to add second story to be able to test larger fires and remote effects from suppression.
-The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan.
-The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-The second story walls were framed with steel studs and track.
-The studs were set to 0.40~m (16~in) centers.
+\subsubsection*{2-Story Structure}
+
+The west structure was modified to add second story to test larger fires and remote suppression effects (cf. Fig~\ref{fig:delco_2story}).
 
@@
 	\label{fig:delco_2story}
+\end{figure}
+
+The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan.
+The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
+Figure~\ref{fig:dimensioned_first_2story} shows the dimensions of the reconfigured first floor.
+A stairwell was built to connect the floors.
+Stairs started 1.6~m (5.25~ft) off the South wall with a width of 1.2~m (4~ft) off the East wall.
+The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs.
+The studs were set to 0.40~m (16~in) centers.
+The interior  walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
+Figure~\ref{fig:dimensioned_second_2story} shows the dimensions of the second story of the modified west structure.
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
+	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure.}
+	\label{fig:dimensioned_first_2story}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
+	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure.}
+	\label{fig:dimensioned_second_2story}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
-	\caption{Instrumentation Schematic for the Fire Suppression Experiments.}
+	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments.}
 	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
-	\caption{Wood Fuel Load Dimensions.}
+	\caption{Wood Fuel Load in Single Story Structure.}
 	\label{fig:Wood_Fuel_Load_Dimensions}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
-	\caption{Furniture Fuel Load.}
+	\caption{Furniture Fuel Load in Single Story Structure}
 	\label{fig:Furniture_Fuel_Load}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
-	\caption{Furniture Fuel Load Dimensions.}
+	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
 	\label{fig:Furniture_Fuel_Load_Dimensions}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
 	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
 	\label{fig:furniture_2story}
-\end{figure
+\end{figure}
 
@@
 \label{sec:fire_suppression_combo_fuel_2}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
+	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure.}
+	\label{fig:pallet_furniture_2story}
+\end{figure}
 

### 2016-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
update cafs report and add new references

@@
 Craig G. Weinschenk \\
+Daniel Madrzykowski \\
 Keith M. Stakes \\
-Daniel Madrzykowski \\
+Joseph M. Willi \\
 
@@
 Craig G. Weinschenk \\
+Daniel Madrzykowski \\
 Keith M. Stakes \\
-Daniel Madrzykowski \\
+Joseph M. Willi \\
 {\em Fire Research Division \\
@@
 \vspace*{2\baselineskip}
-August 2015}}
+February 2016}}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2015) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (February 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 
+A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but have curtailed the use of these units for this purpose until potential safety implications are better understood.
+This project is expected to produce a better understanding of the effectiveness and safety implication of CAFS for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, forces needed to carry and move hoses streams both horizontally and vertically, and forces need to kink hose lines.
+The conclusions should include much better information regarding the safe and effective use of CAFS for structural firefighting.
+
+This paper documents Task 3 of the project.
 NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.
@@
 
-The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.
+The key measures were to understand the cooling and suppression capabilities of CAF compared to water.
 The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies~\cite{Grant:2011}.
+Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAF.
+
+Compressed air foam (CAF) generated with a solution of water and a Class A foam concentrate has been in use by wildland fire agencies since the late 1970’s.
+The wildland fire community found that the Class A foam reduced the surface tension of water, which improved water's ability to penetrate and soak into wildland fuels.
+A CAFS could turn a Class A foam solution into a blanket of bubbles that would allow the wildland firefighters to coat the fuels.
+The additional ``soak'' time provided by the foam layer allows the water to penetrate the hot surface of a burning fuel, and also provides additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
+An added feature of the blanket of bubbles is that firefighters could see where they had applied the agent so that they could make a more effective application.
+In the wildland, water for firefighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
+CAF increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
+Last but not least the compressed air adds energy to the water stream providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
+These CAFS advantages combine to provide wildland firefighters with a tool that could be used to pre-treat homes and structures to protect them from an approaching fire, or could be used for an exterior (indirect) fire suppression attack on a structure.
+
+In the decades that followed the development of CAFS, a number of urban/suburban fire departments across the country began to integrate CAFS into their apparatus.
+For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires, but also examined using them for structural fire fighting.
+Departments across the country began to experiment with CAFS systems for use in structural firefighting.
+In most documented cases, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAFS still has not been significantly incorporated into structural firefighting tactics.
+The importance of tactics is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, has now issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations in a structure.
+
+There has never been a comprehensive scientific study on the use of CAFS for structural fire fighting.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAFS, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAFS puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
+Much of the data has been generated by people and organizations involved in selling the technology to the fire service and, in many cases, the conclusions are based on a very limited set of instruments or comparisons between water and form that were not designed as scientific experiments.
+
+In 2005, The National Fallen Firefighters Foundation held the National Fire Service Research Agenda Symposium.
+One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland firefighting, CAFS is typically applied directly to the fuel from a remote location, typically a non-IDLH environment.
+In structural firefighting, crews typically  have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
+In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they may have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
+It is important that these distinctions and differences between exterior and interior firefighting with CAFS are understood better.
+
+Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in the State of Maryland and was a committed user of CAFS with 35 CAFS front line engines.
+MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAF was being used to fight the fire during an interior attack.
+Concerns were raised within the department regarding the ability of CAF to cool fire gases and absorb heat as well as plain water.
+As a result, on March 4, 2010, the Fire Chief of (MCFRS) issued a General Order prohibiting the use of CAFS during offensive interior attacks.
+In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAFS during structure fires and to report back his findings and recommendations.
+The catalyst for this study was as a result of this order.
 
@@
 
-\subsubsection*{2-Story Structure}
+\subsubsection*{Two Story Structure}
 
@@
 \label{subsec:Fire_Suppression_Instrumentation}
+
+\subsubsection*{Single Story Structure}
 
@@
 
+\subsubsection*{Two Story Structure}
+
 Fire suppression testing in the two-story structure included similar types instrumentation but included more sensors.
@@
 
-\paragraph{Single-Story Structures}
+\subsubsection*{Single Story Structure}
 \label{sec:suppresion_single}
@@
 For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
-A complete listing of the mass of each pallet and hay bales is given in Appendix~\ref{app:fuel_loads}.
-
 \begin{figure}[!ht]
@@
 
-\paragraph{Two-Story Structures}
+\subsubsection*{Two Story Structure}
 \label{sec:suppresion_two}
@@
 \label{sec:fire_suppression_combo_fuel_2}
+
+In June 2015 two stacks of pallets were added to the fuel load which consisted of three sofas, OSB lining on the ceiling and walls and the polypropylene carpeting over puf padding.
+Each stack had 10 pallets.
+The mass of each stack was approximately 175 kg .
+When hay was added for ignition, the bales of hay averaged 12 kg.
 
@@
 
-\chapter{Fuel Load Details}
-\label{app:fuel_loads}
-
 \chapter{Spray Density Figures}

### 2016-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to CAF paper

@@
 \hspace{1.5in} \= \\
+CAF \> Compressed Air Foam \\
 ESTC \> Delaware County Emergency Services Training Center \\

### 2016-02-02 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAF report

@@
 Much of the data has been generated by people and organizations involved in selling the technology to the fire service and, in many cases, the conclusions are based on a very limited set of instruments or comparisons between water and form that were not designed as scientific experiments.
+
+Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}.
+That study examined a broad range of tests in order to determine those parameters that most critically effect fire-fighting performance.
+The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}:
+
+\begin{table}[!ht]
+\centering
+\captionof{table}{Tests to Assess Fire Fighting Agents Compared to Water}\label{tab:agent_tests}
+\begin{tabular}{lcc}
+\toprule[1.5pt]
+Test                                    & Similar Performance & Enhanced Performance \\
+\midrule
+Specific Heat                           &  \checkmark         &                      \\
+Fuel Cooling and Penetration            &                     &  \checkmark          \\
+Mass Retention                          &                     &  \checkmark          \\
+Ignition Inhibition                     &                     &  \checkmark          \\
+Drop Size                               &  \checkmark         &                      \\
+Contact Angle                           &  \checkmark         &                      \\
+Tire Fire Suppression                   &  \checkmark         &                      \\
+Wood Crib Suppression                   &  \checkmark         &                      \\
+Heptane Fire Suppression                &  \checkmark         &                      \\
+Magnesium \& Titanium Fire Suppression  &  \checkmark         &                      \\
+Smoke Generation                        &  \checkmark         &                      \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
+Based on the results of the study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in cooling and penetrating the fuels, mass retention and ignition inhibition.
+All of these features enable the agents, when applied in the form of foam, to provide enhanced radiation exposure protection to a structure relative to plain water.
+The foams enhance the water by keeping the water in place on vertical surfaces such as walls and the reduced interfacial surface tension allows the water to penetrate absorbent fuels.
+These enhancements also make the agents valuable tools for mop-up.
+Many of the experiments conducted during this study: specific heat, drop size, contact angle, wood crib suppression, smoke generation and Class D fire suppression yielded similar results for both Class A foams and plain water.
 

### 2016-02-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Created FDS file for DelCo East Structure and table in exp. overview report

@@
 \input{../../../../../Bibliography/commoncommands}
+
+% Load Packages
+\usepackage{graphicx}
+\usepackage{placeins}
 
@@
 
+\begin{table}[!ht]
+\small
+\caption{East Structure experimental times (min:sec)}
+\begin{tabular}{lcccccccccc}
+ \toprule
+\begin{tabular}{@{}c@{}} \textbf{Test} \\ \textbf{Number} \end{tabular} & 
+\begin{tabular}{@{}c@{}} \textbf{Pilot} \\ \textbf{(Ignition)} \end{tabular} & 
+\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Corner} \\ \textbf{Burner} \end{tabular}} & 
+\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Middle} \\ \textbf{Burner} \end{tabular}} & 
+\multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Center} \\ \textbf{Burner} \end{tabular}} & 
+\begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{West Double Door} \end{tabular} & 
+\begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{East Double Door} \end{tabular} &
+\begin{tabular}{@{}c@{}} \textbf{South Side} \\ \textbf{Single Door} \end{tabular} &
+\begin{tabular}{@{}c@{}} \textbf{Roof Vent} \\ \textbf{Single Door} \end{tabular} 
+\\
+ & \textbf{On} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} &
+ \textbf{Open} & \textbf{Open} & \textbf{Open}  \\
+\midrule
+4 & 0:00 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 7:20 & 9:20 & 10:20 \\
+\bottomrule
+\end{tabular}
+\label{table:east_exp_times}
+\end{table}
+\FloatBarrier
+
 \chapter{Acknowledgments}

### 2016-02-03 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAF report

@@
 
+Water is the most widely used fire extinguishing agent because it is effective, environmentally friendly, nontoxic, inexpensive and in many cases, readily available.
+In addition, water has a very high heat of vaporization per unit mass, at least four times as high as that of any other nonflammable liquid~\cite{NFPA}.
+The latent heat of vaporization of water is 2255~kJ/kg (970~Btu/lb.)~\cite{NFPA}.
+This means that 2255~kJ (2139~Btu) of energy is required to change 1~kg (2.2~lb.) of water into steam.
+When water is vaporized, its volume increases approximately 1,600 times.
+Because the energy absorbing capabilities of water are well quantified, they can be used as a basis to calculate the theoretical minimum delivery rate of water needed to extinguish a burning material with a known heat (energy) release rate.
+Unfortunately, experience has shown that water must be applied at 10 to 100 times the theoretical rate in practice to control and extinguish the fire~\cite{Friedman:2}.
+As a result of this apparent inefficiency and the need to address fires containing a wide variety of materials, water-based fire fighting additives have been utilized for many years to enhance the fire fighting capabilities of ordinary water.
+
+The most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires.
+Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland fires.
+More recently these agents have been promoted for use on a wider range of Class A and in some cases Class B and D (combustible metal) fires.
+These agents are frequently claimed to be more effective than plain water while being environmentally safe.
+In some cases, they are also claimed to reduce the quantity and toxicity of smoke.
+To gain an understanding of how additives might enhance the fire suppression capabilities of water, it is important to examine the principles of fire suppression.
+
 \chapter{Summary}

### 2016-02-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added to FDS input file and to exp. description report

--- 2016-02-01 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
@@
 \input{../../../../../Bibliography/commoncommands}
+
+% Load Packages
+\usepackage{graphicx}
+\usepackage{placeins}
+\usepackage{lscape}
 
@@
 
+\section{East Structure}
+3 sets of 3 sequences: Tests 2-4; Test 5; Test 6
+
+Burners on $\rightarrow$ Ventilation changed by opening/closing doors or roof vent $\rightarrow$ Burners off
+
+\begin{landscape}
+\begin{table}[!ht]
+\caption{East Structure experimental event times (mm:ss)}
+\begin{tabular}{lcccccccccccccc}
+ \toprule
+% \begin{tabular}{@{}l@{}} \textbf{Test} \\ \textbf{Number} \end{tabular} & 
+% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Corner} \\ \textbf{Burner} \end{tabular}} & 
+% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Middle} \\ \textbf{Burner} \end{tabular}} & 
+% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Center} \\ \textbf{Burner} \end{tabular}} & 
+% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{West Double Door} \end{tabular} & 
+% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{East Double Door} \end{tabular} &
+% \begin{tabular}{@{}c@{}} \textbf{South Side} \\ \textbf{Single Door} \end{tabular} &
+% \begin{tabular}{@{}c@{}} \textbf{Roof Vent} \\ \textbf{Single Door} \end{tabular}
+\textbf{Test} & 
+\multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} & 
+\multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} & 
+\multicolumn{2}{c}{\textbf{\underline{Center Burner}}} & 
+\multicolumn{2}{c}{\textbf{\underline{W Double Door}}} & 
+\multicolumn{2}{c}{\textbf{\underline{E Double Door}}} & 
+\multicolumn{2}{c}{\textbf{\underline{Single Door}}} & 
+\multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
+\\
+\textbf{Number} & 
+\textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & 
+\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
+\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
+\\
+\midrule
+% Test 2
+2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 & 
+N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
+% Test 3
+3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
+N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
+% Test 4
+4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
+N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A 
+\\ \multicolumn{15}{c}{ } \\
+% Test 5a
+5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
+% Test 5b
+5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 & 
+N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
+% Test 5c
+5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 & 
+N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
+\\ \multicolumn{15}{c}{ } \\
+% Test 6a
+6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+% Test 6b
+6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+% Test 6c
+6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+\bottomrule
+\end{tabular}
+\label{table:east_exp_times}
+\end{table}
+\end{landscape}
+
 \chapter{Acknowledgments}

### 2016-02-08 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added to struct/exp description inFDS report

@@
 
+% ======================
+% = EXPERIMENTAL SETUP =
+% ======================
 \chapter{Experimental Setup}
 \label{chap:Experimental_Setup}
+The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+The fire source for all experiments was generated by three propane burners and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
 
-\section{Experimental Structure}
-\label{sec:Experimental_Structure}
+\section{Test Structures}
+\label{sec:Test_Structures}
+Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
+The structures were designed to simulate a single-story and a two-story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft).
+The joints and gaps between the blocks were filled with high temperature insulation.
 
-\subsection{Construction}
-\label{sec:Construction}
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/east_structure}
+\\~\\
+\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/west_structure}
+\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
+\label{fig:struct_pics}
+\end{figure}
+
+The interior walls of the first floor of each structure were framed with steel studs and track.
+The studs were set to 0.40 m (16 in.) centers.
+The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in.) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in.) x 44 mm (1.75 in.) and an 11 mm (0.43 in.) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Tongue and grove, 18.3 mm (0.72 in.) thick, oriented strand board was screwed to the top of the TJIs.
+
+\begin{figure}[!ht]
+\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/TJI_support}
+\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
+\label{fig:TJI}
+\end{figure}
+\FloatBarrier
+
+\subsection{East Structure}
+\label{sec:East_descr}
+
+\subsection{West Structure}
+\label{sec:West_descr}
 
@@
 
+\subsection{East Structure}
+\label{sec:East_instrument}
+
+\subsection{West Structure}
+\label{sec:West_instruments}
+
+\subsection{Uncertainty}
+\label{sec:Uncertainty}
+
+% ==========================
+% = EXPERIMENTAL PROCEDURE =
+% ==========================
 \chapter{Experimental Procedure}
 \label{chap:Experimental_Procedure}
+A similar procedure was followed for all experiments described in this report.
+First, three propane burners were ignited in sequential order.
+Next, different doors and vents in the structure were opened and closed to change the ventilation pattern within the structure.
+Finally, the burners were turned off in sequential order and the fire was extinguished.
 
 \section{East Structure}
-3 sets of 3 sequences: Tests 2-4; Test 5; Test 6
+\label{sec:East_exps}
+Three different test series (Test 4, Test 5, and Test 6) were conducted in the east structure.
+Each test series was composed of three experiments that used an identical procedure to change the ventilation pattern in the structure.
+The three procedures used during each test series are outlined in Figures~\ref{fig:Test_4_procedure}-\ref{fig:Test_6_procedure}.
 
-Burners on $\rightarrow$ Ventilation changed by opening/closing doors or roof vent $\rightarrow$ Burners off
+% \begin{figure}[!ht]
+% \includegraphics[width=6in]{../Drawings/East_Test_Structure_Dimensioned}
+% \caption[Plan view of the East Structure.]{East Structure floor layout.}
+% \label{fig:Test_4_procedure}
+% \end{figure}
+% \FloatBarrier
 
@@
  \toprule
-% \begin{tabular}{@{}l@{}} \textbf{Test} \\ \textbf{Number} \end{tabular} & 
-% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Corner} \\ \textbf{Burner} \end{tabular}} & 
-% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Middle} \\ \textbf{Burner} \end{tabular}} & 
-% \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Center} \\ \textbf{Burner} \end{tabular}} & 
-% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{West Double Door} \end{tabular} & 
-% \begin{tabular}{@{}c@{}} \textbf{North Side,} \\ \textbf{East Double Door} \end{tabular} &
-% \begin{tabular}{@{}c@{}} \textbf{South Side} \\ \textbf{Single Door} \end{tabular} &
-% \begin{tabular}{@{}c@{}} \textbf{Roof Vent} \\ \textbf{Single Door} \end{tabular}
 \textbf{Test} & 
@@
 
+\section{West Structure}
+\label{sec:West_exps}
+
 \chapter{Acknowledgments}

### 2016-02-09 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Edits to DelCo FDS validation report

@@
 \label{sec:Test_Structures}
+
+\subsection{Construction}
+\label{sec:construction}
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
@@
 
-\subsection{East Structure}
-\label{sec:East_descr}
-
 \subsection{West Structure}
@@
 \label{sec:Uncertainty}
+
+\section{Propane Burners}
+\label{sec:Burners}
+Three propane burners, each with a 0.6 m X 0.6 m square opening 0.14 m above the floor, were used as the fuel source in every experiment described in this report.
+Propane flowed at a known volumetric flow rate during the experiments.
 

### 2016-02-15 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Re-organized drawings in DelCo_2014_2015, edited struct. descr. in Hose/FDS reports

@@
 % Load Packages
-\usepackage{graphicx}
 \usepackage{placeins}
-\usepackage{lscape}
 
@@
 
+% ================
+% = Introduction =
+% ================
 \chapter{Introduction}
@@
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-The structures were designed to simulate a single-story and a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft).
+The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/east_structure}
+	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/east_structure}
 	\\~\\
-\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/west_structure}
+	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
 	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
@@
 
-The interior walls of the first floor of each structure were framed with steel studs and track.
-The studs were set to 0.40 m (16 in.) centers.
-The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in.) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in.) x 44 mm (1.75 in.) and an 11 mm (0.43 in.) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and grove, 18.3 mm (0.72 in.) thick, oriented strand board was screwed to the top of the TJIs.
+The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and \textit{were lined with 13~mm (0.5~in) thick cement board.
+The walls were composed of 16~mm (5/8~in) Type X gypsum board.
+Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.}
+\FloatBarrier
+
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../Hose_Stream_Report/Pictures/TJI_support}
-\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
+	\includegraphics[width=6in]{../../Hose_Stream_Report/Figures/Pictures/TJI_support}
+	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams.
+View is of the southeast corner of the structure.}
 	\label{fig:TJI}
@@
 
-\subsection{West Structure}
-\label{sec:West_descr}
+The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
+The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
+The interior walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
+
+% Add info about roof vent in single story
+\subsection{Layout}
+\label{sec:layout}
+Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_dimensioned_plan}
+\end{figure}
+% make new floor plan with ceiling vent included
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../Hose_Stream_Report/Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
+	\\~\\
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\label{fig:west_dimensioned_plan}
+\end{figure}
+% make new 1st floor plan with rear door completely sealed off
+
+The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+
+The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
+All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
+\FloatBarrier
 

### 2016-02-15 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Re-organized drawings in DelCo_2014_2015, edited struct. descr. in Hose/FDS reports

@@
 
-% Load packages
-\usepackage{graphicx}
-\usepackage[super]{nth}
+% Load extra packages
 \usepackage{placeins}
-\usepackage{units}
-\usepackage[percent]{overpic}
 
@@
 
-\chapter{List of Symbols}
-\begin{tabbing}
-\hspace{1.5in} \= \\
-ft \> foot \\
-GPM \> gallons per minute \\
-in. \> inch \\
-m \> meter \\
-\end{tabbing}
+% \chapter{List of Symbols}
+% \begin{tabbing}
+% \hspace{1.5in} \= \\
+% ft \> foot \\
+% GPM \> gallons per minute \\
+% in \> inch \\
+% m \> meter \\
+% \end{tabbing}
 
@@
 \begin{enumerate} 
-\item Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle.
-Counterclockwise rotation does just the opposite.
-\item Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation
-produces steam with an inactive and lazy action.
+	\item Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle. Counterclockwise rotation does just the opposite.
+	\item Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation produces steam with an inactive and lazy action.
 	\item A clockwise rotation produces a faster knockdown time.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/hose_streams.pdf}
-\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments. From left to right: straight stream, narrow fog stream, and wide fog stream.}
+	\includegraphics[width=6in]{../Figures/Pictures/hose_streams.pdf}
+	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments.
+From left to right: straight stream, narrow fog stream, and wide fog stream.}
 	\label{fig:hose_streams}
@@
 \subsection{Test Structures}
-\label{subsec:test_structs}
+\label{sec:test_structs}
 
 \subsubsection{Construction}
-\label{subsubsec:construction}
+\label{sec:construction}
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-The structures were designed to simulate a single-story and a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61 m (2 ft).
+The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
+The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
 The joints and gaps between the blocks were filled with high temperature insulation.
 
-The interior walls of the first floor of each structure were framed with steel studs and track.
-The studs were set to 0.40 m (16 in.) centers.
-The ceiling/floor support was composed of wood truss joist I-beams (TJIs) with a 299 mm (11.75 in.) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29 mm (1.13 in.) x 44 mm (1.75 in.) and an 11 mm (0.43 in.) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and grove, 18.3 mm (0.72 in.) thick, oriented strand board was screwed to the top of the TJIs.
+\begin{figure}[!ht]
+	\includegraphics[width=5.25in]{../Figures/Pictures/east_structure}
+	\\~\\
+	\includegraphics[width=5.25in]{../Figures/Pictures/west_structure}
+	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
+	\label{fig:struct_pics}
+\end{figure}
+
+The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and \textit{were lined with 13~mm (0.5~in) thick cement board.
+The walls were composed of 16~mm (5/8~in) Type X gypsum board.
+Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.}
+\FloatBarrier
+
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/TJI_support}
-\caption[TJI-constructed ceiling/floor support of the West Structure.]{Ceiling and floor support of the West Structure composed of wood truss joist I-beams. View is of the east side of the structure.}
+	\includegraphics[width=6in]{../Figures/Pictures/TJI_support}
+	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams.
+View is of the southeast corner of the structure.}
 	\label{fig:TJI}
@@
 
-**** NEED TO GET SECOND STORY CONSTRUCTION DETAILS and then write a description of it here ****
+The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
+The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
+The interior walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
 
-The second floor of the West Structure was built on the wood floor assembly as described above. The walls were framed with wood studs set to 0.40 m (16 in.) centers.
-% The interior walls of the burn room were lined with 13 mm (0.5 in) thick cement board.
-The ceiling of the burn room was the exposed "floor assembly".
-The walls of the hallway and entry foyer were composed of 16 mm (0.38 in) Type ****X**** gypsum room.
-The ceiling of the hallway and entry foyer was composed of two layers of 13 mm (0.5 in) thick cement board.
+\subsubsection{Layout}
+\label{sec:layout}
+Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively. \textbf{Add N arrow to floor plans}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/east_structure}
-\\~\\
-\includegraphics[width=6in]{../Pictures/west_structure}
-\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
-\label{fig:struct_pics}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_dimensioned_plan}
 \end{figure}
 
-\clearpage
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
+	\\~\\
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\label{fig:west_dimensioned_plan}
+\end{figure}
 
-\subsubsection{Layout}
-\label{subsubsec:layout}
-The interior dimensions of each structure were approximately 6.1 m (20 ft) wide, 11 m (36 ft) long and 2.4 m (8 ft) high.
+The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+
 The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
 All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
-
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/East_Test_Structure_Dimensioned}
-\caption[Plan view of the East Structure.]{East Structure floor layout.}
-\label{fig:east_general_plan}
-\end{figure}
 \FloatBarrier
 
-\begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/West_Test_Structure_2nd_Floor_Dimensioned}
-\\~\\
-\includegraphics[width=6in]{../Drawings/West_Test_Structure_1st_Floor_Dimensioned}
-\caption[Plan view of the second floor and first floor of the West Structure.]{Plan view of the second floor (top) and first floor (bottom) of the West Structure.}
-\label{fig:west_general_plan}
-\end{figure}
-
-\clearpage
-
 \subsection{Instrumentation}
-\label{subsec:instrumentation}
-A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{subsec:uncertainty}.
+\label{sec:instrumentation}
+A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{sec:uncertainty}.
 For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
@@
 A single thermocouple was attached to each BDP to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
-Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0 mm (0.04 in.) diameter.
-Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2 mm (0.13 in.) diameter Inconel shield that was 0.76 m (2.5 ft) in length.
+Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
+Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2~mm (0.13 in) diameter Inconel shield that was 0.76~m (2.5~ft) in length.
 
@@
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report.
-The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80 m below the soffit of the doorway.
-The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95 m below the soffit of the corresponding doorway.
+The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
+The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
 
 \begin{figure}[!ht]
-\includegraphics[width=3.5in]{../Pictures/BDPs_east}
+	\includegraphics[width=3.5in]{../Figures/Pictures/BDPs_east}
 	\caption[Array of BDPs at interior doorway in East Structure.]{Array of BDPs located at the northeast interior doorway in the East Structure. View is looking at the array from Room C.}
@@
 \subsection{Uncertainty}
-\label{subsec:uncertainty}
+\label{sec:uncertainty}
 There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity reported here.
@@
 Each length measurement was taken carefully. Length measurements such as room dimensions,
-instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$ mm (0.24 in.) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{Stanley}.
-However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0 m (6.6 ft) to 10.0 m (32.8 ft) range.
-Steel measuring tapes with a resolution of $\pm$0.5 mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$ mm (0.06 in.) for 9.1 m (30 ft) tapes and $\pm6.4$ mm (0.25 in.) for 30.5 m (100 ft) tapes~\cite{NIST_Manual_44}.
+instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$~mm (0.24 in) over a range of 0.61~m (2.00~ft) to 15.3~m (50.0~ft)~\cite{Stanley}.
+However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+Steel measuring tapes with a resolution of $\pm$0.5~mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$~mm (0.06 in) for 9.1~m (30~ft) tapes and $\pm6.4$~mm (0.25 in) for 30.5~m (100~ft) tapes~\cite{NIST_Manual_44}.
 Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
@@
 Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 6.35 cm (2.5 in.) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+The meter consists of a section of 6.35 cm (2.5 in) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Pictures/flow_meter}
+	\includegraphics[width=6in]{../Figures/Pictures/flow_meter}
 	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
@@
 	\begin{center}
-	\includegraphics[width=2.9in]{../Pictures/monitor}
+		\includegraphics[width=2.9in]{../Figures/Pictures/monitor}
 	\end{center} 
@@
 	\begin{center}
-	\includegraphics[width=2.9in]{../Pictures/handline}
+		\includegraphics[width=2.9in]{../Figures/Pictures/handline}
 	\end{center}
 	\endminipage \hfill
-\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in. handline (right) equipped with a combination nozzle and used to flow water during experiments.}
+	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
 	\label{fig:monitor+handline}
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/Specific_Tests/East_Hose_Test_Annotated}
+	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
 	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
@@
 \begin{figure}[!ht]
-\
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
 	\\~\\
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
+	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
 	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
@@
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
 	\\~\\
-\includegraphics[width=6in]{../Drawings/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
+	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
 	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
@@
 \subsection{Monitor Experiments}
-\label{subsec:monitor_procedure}
+\label{sec:monitor_procedure}
 Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/SS_Room_B_Test_33}
+	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/SS_Room_B_Test_33}
 	\\~\\
-\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/NF_Room_B_Test_33}
+	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/NF_Room_B_Test_33}
 	\\~\\
-\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Pictures/WF_Room_B_Test_33}
+	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
 	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at area above the doorway on the south wall of Room B during Test 33.}
@@
 Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room.
-The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8 m (6 ft) from the interior side of the north wall and a "far" target, located approximately 3.7 m (12 ft) from the interior side of the north wall.
+The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a "far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
 The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds.
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/SS_near}
+		\includegraphics[width=2in]{../Figures/Pictures/SS_near}
 	\end{center} 
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/NF_near}
+		\includegraphics[width=2in]{../Figures/Pictures/NF_near}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/WF_near}
+		\includegraphics[width=2in]{../Figures/Pictures/WF_near}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/SS_far}
+		\includegraphics[width=2in]{../Figures/Pictures/SS_far}
 	\end{center} 
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/NF_far}
+		\includegraphics[width=2in]{../Figures/Pictures/NF_far}
 	\end{center}
@@
 	\begin{center}
-	\includegraphics[width=2in]{../Pictures/WF_far}
+		\includegraphics[width=2in]{../Figures/Pictures/WF_far}
 	\end{center}
@@
 \subsection{Handline Experiments}
-\label{subsec:handline_procedure}
-Numerous experiments were conducted during three different test series using a 1.75 in.
-handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+\label{sec:handline_procedure}
+Numerous experiments were conducted during three different test series using a 1.75 in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
 One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure.
@@
 
-Test 34 utilized a 1.75 in.
-handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}.
-The layout of the structure was identical to the layout described above in Section~\ref{subsec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}.
+Test 34 utilized a 1.75 in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}.
+The layout of the structure was identical to the layout described above in Section~\ref{sec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}.
 The procedure for Test 34 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
@@
 \begin{figure}[!ht]
-\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/SS_Room_B_Test_34}
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/SS_Room_B_Test_34}
 	\\~\\
-\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/NF_Room_B_Test_34}
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/NF_Room_B_Test_34}
 	\\~\\
-\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Pictures/WF_Room_B_Test_34}
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
 	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 34.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 34.}
@@
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed identical procedures that involved using a 1.75 in.
-handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
+Tests 18 and 19 followed identical procedures that involved using a 1.75 in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
 For every experiment during the two tests, the water stream was aimed at the south side wall of the first floor.
@@
 \begin{figure}[!ht]
-\includegraphics[width=4.25in]{../Pictures/Test_18}
+	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
 	\caption[North side of West Structure containing a fully established flow path during Test 18.]{North side of West Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 18.}
@@
 Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
-Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 17 and measurements obtained from the BDPs at A6 during Test 33 are presented in Appendix~\ref{subsec:monitor_figs}.
+Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 17 and measurements obtained from the BDPs at A6 during Test 33 are presented in Appendix~\ref{sec:monitor_figs}.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_16_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=6in]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
@@
 Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
-Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 19 and measurements obtained from the BDPs at A6 during Test 34 are presented in Appendix~\ref{subsec:handline_figs}.
+Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 19 and measurements obtained from the BDPs at A6 during Test 34 are presented in Appendix~\ref{sec:handline_figs}.
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_18_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=6in]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
@@
 \end{figure}
-
 \FloatBarrier
@@
 \subsection{Monitor Figures}
-\label{subsec:monitor_figs}
+\label{sec:monitor_figs}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_17_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=6in]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
@@
 \subsection{Handline Figures}
-\label{subsec:handline_figs}
+\label{sec:handline_figs}
 
 \begin{figure}[!ht]
-\includegraphics[width=6in]{../../../Figures/Hose_Stream_Figures/Test_19_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=6in]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}

### 2016-02-15 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -82,7 +82,7 @@ stream_avgs_plot = True    # Plot avg of all channels for each stream tested dur
 # Location of directories
 data_dir = '../Experimental_Data/'      # Location of experimental data files
 results_dir = '../Results/'     # Location to save results files 
-fig_dir = '../Figures/Hose_Stream_Figures/'     # Location to save plots
+fig_dir = '../Reports/Hose_Stream_Report/Figures/Plots'     # Location to save plots
 all_times_file = '../Experimental_Data/All_Times.csv'       # Location of file with timing information
 info_file = '../Experimental_Data/Description_of_Experiments.csv'       # Location of test description file
 

### 2016-02-16 Projects/DelCo_2012/Report/DelCo_2012.tex
Fixing Typos in Body added text to Summary
The summary for the gas cooling is about 75% complete. Dan will
complete.

@@
 Drop Size                               &  \checkmark         &                      \\
-Contact Angle                           &  \checkmark         &                      \\
+Contact Angle                           &                     &  \checkmark          \\
 Tire Fire Suppression                   &  \checkmark         &                      \\
@@
 
-Based on the results of the study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in cooling and penetrating the fuels, mass retention and ignition inhibition.
-All of these features enable the agents, when applied in the form of foam, to provide enhanced radiation exposure protection to a structure relative to plain water.
-The foams enhance the water by keeping the water in place on vertical surfaces such as walls and the reduced interfacial surface tension allows the water to penetrate absorbent fuels.
+Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle, cooling and penetrating the fuels, mass retention on the fuels and ignition inhibition of the fuels.
+When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
+The foams enhance the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allows the water to penetrate absorbent fuels.
 These enhancements also make the agents valuable tools for mop-up.
-Many of the experiments conducted during this study: specific heat, drop size, contact angle, wood crib suppression, smoke generation and Class D fire suppression yielded similar results for both Class A foams and plain water.
+The other experiments conducted during this study: specific heat, drop size, wood crib suppression, smoke generation and Class D fire suppression yielded similar results for both Class A foams and plain water.
 
@@
 The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner.
-A chair is placed adjecent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
-In total, this fuel package contains approximately 336 kg of fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
+A chair is placed adjacent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
+In total, this fuel package contains approximately 336 kg of fuel consisting of wood, polyurethane (PU), polyester (PET),and polypropylene (PP).
 Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
@@
 
-\chapter{Discussion and Tactical Considerations}
-\label{chap:Discussion_and_Tactical_Considerations}
+\chapter{Discussion}
+\label{chap:Discussion}
+
+This study focused on two key types of fire experiments; gas cooling and fire suppression.
+In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates.
+In both types of experiments there were no measurable differences between the use of plain water or compressed air foam.
+These results were not surprising to some of the workshop attendees.
+However other workshop attendees, that use CAF very successfully in their fire departments, had additional questions.
+The research team worked to address those follow-up questions by conducting additional fire suppression experiments, one where only wood based fuels were used and another where a larger space with more ventilation was used.
+This section will discuss the results and provide potential explanations to support them.
+
+\subsection{Gas Cooling}
+\label{sec:desc_Gas_Cooling}
+
+The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83\~{}m (6\~{}ft) below the ceiling.
+During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling.
+It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
+Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
+There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
 
@@
 This means that 2255~kJ (2139~Btu) of energy is required to change 1~kg (2.2~lb.) of water into steam.
-When water is vaporized, its volume increases approximately 1,600 times.
+When water is vaporized, its volume increases approximately 1,700 times.
 Because the energy absorbing capabilities of water are well quantified, they can be used as a basis to calculate the theoretical minimum delivery rate of water needed to extinguish a burning material with a known heat (energy) release rate.
@@
 To gain an understanding of how additives might enhance the fire suppression capabilities of water, it is important to examine the principles of fire suppression.
+
+In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
+Typically the volumetric flow rate of water was 120 gpm.
+The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .
+The average time of flow was 15 s, therefore a total of X kg of water was introduced into each gas cooling experiment.
+When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
+Also calc the mass of air in the stream.
+
+Compare flow rate with coverage estimates Iowa/NFA formulas.
+
+Ref Sean Mitchell report and then close with the ref back to the two comparison graphs.
+Under the conditions of a residential scale room and contents fire it should be no surprise that the results are similar, the mass of water introduced into the hot gas layer is doing the work.
+Air filled bubbles in the CAFs stream had no discernible impact in these experiments.
+
+\subsection{Fire Suppression}
+\label{sec:Fuel_Load_Fire_Suppression}
 

### 2016-02-18 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added new drawings for hose stream and FDS validation reports

@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
 	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../../Hose_Stream_Report/Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
+	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
 	\\~\\
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_instrumentation}
+\end{figure}
+
 \subsection{West Structure}
 \label{sec:West_instruments}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
+	\\~\\
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
+	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\label{fig:west_instrumentation}
+\end{figure}
 
@@
 % \begin{figure}[!ht]
-% \includegraphics[width=6in]{../Drawings/East_Test_Structure_Dimensioned}
+% \includegraphics[width=6in]{../Drawings/East_Structure_Dimensioned}
 % \caption[Plan view of the East Structure.]{East Structure floor layout.}
@@
 % \FloatBarrier
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_test_4}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_test_5}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\label{fig:east_test_6}
+\end{figure}
 

### 2016-02-19 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added content to instrumentation section of FDS valid. report

@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
 	\label{fig:west_dimensioned_plan}
@@
 \label{sec:Instrumentation}
+The structures were instrumented for temperature, gas velocity, heat flux, and gas concentration measurements.
+Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples.
+Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
+The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter.
+The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconnel sheath.
+Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
+A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
+Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample.
+Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured.
+A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=0.35\columnwidth]{../Figures/Floor_Plans/Legend}
+% 	\caption[Instrumentation Legend.]{Instrumentation Legend.}
+% 	\label{fig:Instrumentation_Legend}
+% \end{figure}
+% \FloatBarrier
 
 \subsection{East Structure}
-\label{sec:East_instrument}
+\label{sec:East_Instrumentation}
+The East Structure was instrumented with 5 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, 5 total heat flux plus radiometer sensor pairs, and 2 gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
-	\label{fig:east_instrumentation}
+	\caption{Location of instrumentation in the East Structure.}
+	\label{fig:East_Instrumentation}
 \end{figure}
 
+Each bare-bead thermocouple array was composed of 8 thermocouples.
+The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
+The three bi-directional probe and solid thermocouple arrays located at the exterior doorways of the structure contained 8 probes centered in the doorway with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
+The fourth bi-directional probe and solid thermocouple array was located at the roof vent and contained three probes \textit{centered between the east and west sides of the vent and spaced ??
+apart between the north and south sides.} The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+Gas concentrations were pulled through \textit{3.2~mm (0.125~in) diameter stainless steel tubing located 1.22~m (4~ft) above the floor.}
+
 \subsection{West Structure}
-\label{sec:West_instruments}
+\label{sec:West_Instrumentation}
+The first floor of the West Structure was instrumented with 3 bare-bead thermocouple arrays, 3 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe, and the second floor was equipped with 3 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe.
+The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
-	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
 	\label{fig:west_instrumentation}
@@
 
-\subsection{Uncertainty}
-\label{sec:Uncertainty}
+The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure.
+The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure.
+3.2~mm (0.125~in) stainless steel tubing was located 1.22~m (4~ft) above the floor and used to pull gas samples from the environment.
 
-\section{Propane Burners}
+\subsection{Propane Burners}
 \label{sec:Burners}
@@
 Propane flowed at a known volumetric flow rate during the experiments.
+
+\subsection{Uncertainty}
+\label{sec:Uncertainty}
 

### 2016-02-19 Projects/DelCo_2012/Report/DelCo_2012.tex
Edits to the instrumentation/uncertainty sections, fixed a couple typos in DelCo_2012 report

@@
 Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
-The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconnel sheath.
+The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
+The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
@@
 Each length measurement was taken carefully.
-Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which is has an accuracy of $\pm$ 6.0 mm (0.25) over a range of 0.61 m (2.00 ft) to 15.3 m (50.0 ft)~\cite{StanleyTools}.
+Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$ 6.0~mm (0.25~in) over a range of 0.61~m (2.00~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
 However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$ 0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
 Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$ 1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
 Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$ 1.0~\%.
@@
 
-The gas measurement instruments and sampling system used in this series of experiments have been demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
 Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of $\pm$ 12~\% is being applied to the results~\cite{Lock:1}.
@@
 Bare-bead Type K thermocouple are co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments w estimated to be  $\pm$ 18~\%.
+A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$ 18~\%.
 

### 2016-02-19 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Edits to the instrumentation/uncertainty sections, fixed a couple typos in DelCo_2012 report

@@
 \pagestyle{empty}
+\begin{minipage}[t][9in][s]{6.25in}
+
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
+\headerB{
+Overview of Fire Model Validation Experiments in Residential Scale Structures \\
+}
+
+\normalsize
+
+\headerC{
+{
+\flushright{
+Joseph Willi \\
+Kevin McGrattan \\
+Randall McDermott \\
+Craig Weinschenk \\
+
+\vspace*{2\baselineskip}
+
+\begingroup
+This publication is available free of charge from:
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\endgroup
+}
+
+\vfill
+
+\flushright{
+
+\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
+}
+}
+}
+
+\end{minipage}
+
+\newpage
+\hspace{5in}
+\newpage
+
+\frontmatter
+
+\pagenumbering{roman}
 
@@
 
+\begin{flushright}
+\fontsize{20}{24}\selectfont
+\bf{NIST Technical Note XXXX}
+\end{flushright}
+
 \headerB{
-Overview of Fire Model Validation Experiments in Residential Scale Structures
+Overview of Fire Model Validation Experiments in Residential Scale Structures \\
 }
@@
 {\em Fire Research Division \\
-Engineering Laboratory \\
-Gaithersburg, Maryland, USA} \\ }
-}
+Engineering Laboratory} \\
 
-\flushright{\today \\
-}
+\vspace*{2\baselineskip}
+
+\begingroup
+This publication is available free of charge from:
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\endgroup
+
+\vspace*{2\baselineskip}
+February 2016}}
 
@@
 
-\flushright{
-\includegraphics[width=2.in]{../../../../../Bibliography/nistident_flright_vec} \\[.3in]
+\flushright{\includegraphics[width=1in]{../../../../../Bibliography/doc}}
+
+\titlesigs
+
+\end{minipage}
+
+\newpage
+
+\begin{minipage}[t][9in][s]{6.25in}
+
+\flushright{Certain commercial entities, equipment, or materials may be identified in this \\
+document in order to describe an experimental procedure or concept adequately. \\
+Such identification is not intended to imply recommendation or endorsement by the \\
+National Institute of Standards and Technology, nor is it intended to imply that the \\
+entities, materials, or equipment are necessarily the best available for the purpose. \\
 }
 
-\titlesigs
+\vspace{3in}
+
+\large
+\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (February 2016) \\
+% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+CODEN: NTNOEF }
+
+\vspace{0.2in}
+
+\begingroup
+{\bf This publication is available free of charge from:}
+\hypersetup{urlcolor=black}
+\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\endgroup
+
+\vfill
+
+\hspace{1in}
 
@@
 % \end{figure}
-% \FloatBarrier
 
-\subsection{East Structure}
-\label{sec:East_Instrumentation}
+Three propane burners, each with a square opening of side length 0.6~m (2~ft) 0.14~m (5.5~in) above the floor, were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure and used as the fuel source in each experiment.
+Propane flowed at a known volumetric flow rate during the experiments.
+\FloatBarrier
+
+\subsubsection*{East Structure}
 The East Structure was instrumented with 5 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, 5 total heat flux plus radiometer sensor pairs, and 2 gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
@@
 	\caption{Location of instrumentation in the East Structure.}
-	\label{fig:East_Instrumentation}
+	\label{fig:east_instrumentation}
 \end{figure}
@@
 Gas concentrations were pulled through \textit{3.2~mm (0.125~in) diameter stainless steel tubing located 1.22~m (4~ft) above the floor.}
+\FloatBarrier
 
-\subsection{West Structure}
-\label{sec:West_Instrumentation}
+\subsubsection*{West Structure}
 The first floor of the West Structure was instrumented with 3 bare-bead thermocouple arrays, 3 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe, and the second floor was equipped with 3 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe.
@@
 3.2~mm (0.125~in) stainless steel tubing was located 1.22~m (4~ft) above the floor and used to pull gas samples from the environment.
+\FloatBarrier
 
-\subsection{Propane Burners}
-\label{sec:Burners}
-Three propane burners, each with a 0.6 m X 0.6 m square opening 0.14 m above the floor, were used as the fuel source in every experiment described in this report.
-Propane flowed at a known volumetric flow rate during the experiments.
+\subsection{Measurement Uncertainty}
+\label{sec:Uncertainty}
+There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, and gas velocity measurements.
+Uncertainties are grouped into two categories according to the method used to estimate them.
+Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
+Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%.
+After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
+Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$).
+For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
+For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.
 
-\subsection{Uncertainty}
-\label{sec:Uncertainty}
+Each length measurement was taken carefully.
+Length measurements such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
+
+The standard uncertainty in temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
+Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
+The estimated total expanded uncertainty for temperature in these experiments is $\pm$15\%.
+
+In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
+The manufacturer reports a $\pm$3\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8\%~\cite{Pitts:2006}.
+
+The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12\% is associated with gas concentration measurements~\cite{Lock:1}.
+
+Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
+The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1\%~\cite{Setra:2002}.
+The total expanded uncertainty was estimated at 10\%.
+
+Bi-directional probes and single thermocouples were used to measure the velocity.
+The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
+Single bare-bead Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter were co-located with each probe.
+The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18\%.
+
+\textit{Gas meter flowrate error}
 
@@
 The three procedures used during each test series are outlined in Figures~\ref{fig:Test_4_procedure}-\ref{fig:Test_6_procedure}.
-
-% \begin{figure}[!ht]
-% \includegraphics[width=6in]{../Drawings/East_Structure_Dimensioned}
-% \caption[Plan view of the East Structure.]{East Structure floor layout.}
-% \label{fig:Test_4_procedure}
-% \end{figure}
-% \FloatBarrier
 
@@
 
-\bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general,references}
+\bibliography{../../../../../Bibliography/FDS_refs,../../../../../Bibliography/FDS_general}
 

### 2016-02-19 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to the instrumentation/uncertainty sections, fixed a couple typos in DelCo_2012 report

@@
 \headerB{
-Impact of Hose Streams on Air Flows inside a Structure
+Impact of Hose Streams on Air Flows inside a Structure \\
 }
@@
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report.
-The set of BDPs at the northeast interior doorway of the East Structure, denoted as "A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
-The set of BDPs at the interior doorway in the West Structure, denoted as "A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
+The set of BDPs at the northeast interior doorway of the East Structure, denoted as ``A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
+The set of BDPs at the interior doorway in the West Structure, denoted as ``A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
 
@@
 
-Each length measurement was taken carefully. Length measurements such as room dimensions,
-instrumentation array locations, and nozzle placement were made with a hand-held laser measurement device which is has an accuracy of $\pm6.0$~mm (0.24 in) over a range of 0.61~m (2.00~ft) to 15.3~m (50.0~ft)~\cite{Stanley}.
-However, conditions affecting the measurement, such as levelness of the device, yield an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
-Steel measuring tapes with a resolution of $\pm$0.5~mm were used to locate individual sensors within a measurement array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm1.6$~mm (0.06 in) for 9.1~m (30~ft) tapes and $\pm6.4$~mm (0.25 in) for 30.5~m (100~ft) tapes~\cite{NIST_Manual_44}.
-Some issues, such as "soft" edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
+Each length measurement was taken carefully.
+Length measurements such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
 

### 2016-02-19 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added content to procedure section of FDS valid. report

@@
 The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-Single bare-bead Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter were co-located with each probe.
+A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe.
 The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
@@
 
-\textit{Gas meter flowrate error}
+\textit{Gas meter flowrate/HRR error}
 
@@
 
-\section{East Structure}
-\label{sec:East_exps}
-Three different test series (Test 4, Test 5, and Test 6) were conducted in the east structure.
-Each test series was composed of three experiments that used an identical procedure to change the ventilation pattern in the structure.
-The three procedures used during each test series are outlined in Figures~\ref{fig:Test_4_procedure}-\ref{fig:Test_6_procedure}.
+\subsubsection*{East Structure}
+Three different test series -- Series 4, Series 5, and Series 6 -- were conducted in the east structure.
+Each series was composed of three experiments that used an identical procedure to change the ventilation pattern in the structure.
+The three procedures used for each test series are outlined in Figs.~\ref{fig:east_test_4}-\ref{fig:east_test_6}.
 
 \begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}[b]{cc}
+ 	\toprule
+ 	\textbf{Number} & \textbf{Event Description} \\
+ 	\midrule
+ 	1-3  & Burners ignited \\
+ 	4	 & West double door opened \\
+ 	5 	 & East double door opened \\
+ 	6	 & South side door opened \\
+ 	7-9  & Burners extinguished \\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_4}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+\end{minipage}
+\caption{Test Series 4 layout and ordered sequence of events.}
 \label{fig:east_test_4}
@@
 \begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}[b]{cc}
+ 	\toprule
+ 	\textbf{Number} & \textbf{Event Description} \\
+ 	\midrule
+ 	1-3  & Burners ignited \\
+ 	4	 & Roof vent opened \\
+ 	5 	 & West double door opened \\
+ 	6 	 & East double door opened \\	
+ 	7	 & Roof vent closed \\
+ 	8-10  & Burners extinguished \\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+\end{minipage}
+\caption{Test Series 5 layout and ordered sequence of events.}
 \label{fig:east_test_5}
@@
 \begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}[b]{cc}
+ 	\toprule
+ 	\textbf{Number} & \textbf{Event Description} \\
+ 	\midrule
+ 	1-3  & Burners ignited \\
+ 	4	 & Roof vent opened \\
+ 	5 	 & West double door opened \\
+ 	6-8  & Burners extinguished \\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_6}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+\end{minipage}
+\caption{Test Series 6 layout and ordered sequence of events.}
 \label{fig:east_test_6}
 \end{figure}
+\FloatBarrier
+
+\subsubsection*{West Structure}
+Two different test series -- Series 22 and Series 24 -- were conducted in the west structure.
+Each series was composed of two experiments that used an identical procedure to change the ventilation pattern in the structure.
+The two procedures used for each test series are outlined in Figs.~\ref{fig:west_test_22} and \ref{fig:west_test_24}.
+
+\begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}[b]{cc}
+ 	\toprule
+ 	\textbf{Number} & \textbf{Event Description} \\
+ 	\midrule
+ 	1-3  & Burners ignited \\
+ 	4	 & 2nd floor west double door opened \\
+ 	5 	 & 1st floor west double door opened \\
+ 	6	 & 2nd floor east double door opened \\
+ 	7 	 & 1st floor east double door opened \\
+ 	8-10  & Burners extinguished \\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
+	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_22}
+\end{minipage}
+\caption{Test Series 22 layout and ordered sequence of events.}
+\label{fig:west_test_22}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}[b]{cc}
+ 	\toprule
+ 	\textbf{Number} & \textbf{Event Description} \\
+ 	\midrule
+ 	1-3  & Burners ignited \\
+ 	4	 & Interior stairwell door opened \\
+ 	5 	 & 1st floor west double door opened \\
+ 	6	 & 2nd floor west double door opened \\
+ 	7 	 & 2nd floor south side door opened \\
+ 	8-10 & Burners extinguished \\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
+	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_24}
+\end{minipage}
+\caption{Test Series 24 layout and ordered sequence of events.}
+\label{fig:west_test_24}
+\end{figure}
+\FloatBarrier
+
+\chapter{Acknowledgments}
+\label{chap:Acknowledgments}
+
+\bibliography{../../../../../Bibliography/FDS_refs,../../../../../Bibliography/FDS_general}
+
+\appendix
+
+\chapter{Appendix A}
 
@@
 
-\section{West Structure}
-\label{sec:West_exps}
-
-\chapter{Acknowledgments}
-\label{chap:Acknowledgments}
-
-\bibliography{../../../../../Bibliography/FDS_refs,../../../../../Bibliography/FDS_general}
-
-\appendix
-
-\chapter{Appendix A}
-
-Placeholder
-
 \end{document}

### 2016-02-19 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to hose stream report and figure

@@
 \label{sec:background}
-%More hose stream studies and explanations
+% More hose stream studies and explanations
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/hose_streams.pdf}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/hose_streams.pdf}
 	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/TJI_support}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/TJI_support}
 	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Pictures/flow_meter}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/flow_meter}
 	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
@@
 
-A total of six test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}).
+A total of seven test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}).
 Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
 	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
 	\\~\\
-	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
 	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_2nd_Floor_Annotated}
 	\\~\\
-	\includegraphics[width=6in]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
 	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
@@
 Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room.
-The nozzle was aimed at two targets during the series: a "near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a "far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
+The nozzle was aimed at two targets during the series: a ``near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
 The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds.
@@
 	\endminipage \hfill
-	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at "near" target (top row) and "far" target (bottom row) during the monitor experiments in the West Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near" target (top row) and ``far" target (bottom row) during the monitor experiments in the West Structure.}
 	\label{fig:test_16_17_pic}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s $\pm15$\%) through interior doorway when flow path was fully established for each monitor experiment}
+\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
 \begin{tabular}{lccccc}
@@
 \midrule
-\textit{Straight} & 1.7 $\pm0.2$ & 1.9 $\pm0.2$ & \multicolumn{3}{c}{} 
+\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
 \\ \multicolumn{6}{c}{} \\
-\textit{Smooth Bore} & 1.7 $\pm0.2$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
+\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
 \\
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
 	\label{fig:Test_17_BDP_A10_Avg_All}
+	\end{figure}
+\FloatBarrier
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
+	\caption{Average velocity measured by the BDPs at A10 during Test 70 for straight stream and smooth bore stream patterns.}
+	\label{fig:Test_70_BDP_A10_Avg_All}
 	\end{figure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
+	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
 	\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}

### 2016-02-22 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Removed unnecessary plot figs, updated script to generate new hose figs

@@
 \hspace{1.5in} \= \\
-% FDS \> Fire Dynamics Simulator \\
-% HGL \> Hot Gas Layer \\
-% HRR \> Heat Release Rate \\
-% HRRPUA \> Heat Release Rate per Unit Area \\
-BDP \> Bi-Directional Probe \\
+ESTC \> Delaware County Emergency Services Training Center \\
 NIST \> National Institute of Standards and Technology \\
@@
 Most fog nozzles contain an adjustable tip that can be rotated to produce different stream patterns and are therefore often referred to as combination nozzles.
+The types of streams produced by a fog nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{Essentials_FF}.
+Increasing the angle of the stream allows for a larger area to be covered by water, thus exposing a larger water droplet surface area for heat absorption.
+However, increasing the angle decreases the distance reached by the stream and its penetration power and increases the potential to disrupt thermal layering increases.
 %\textit{Essentials of Fire Fighting} defines 
@@
 %http://www.tft.com/literature/library/files/bfa.pdf
-%Keith Royer, WATER FOR FIRE FIGHTING, p. 7
+%Keith Royer, "Water for Fire Fighting", (Engineering Extension Service, Iowa State University, Ames, Iowa) p. 6 
 In addition to the type of stream pattern used, fire suppression tactics using hose streams can differ in the method used to apply the hose stream.
-For example, Nelson and Royer suggest using a clockwise rotation instead of a counterclockwise application pattern for the following reasons:
+For example, Royer suggests using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer}:
 \begin{enumerate} 
-	\item Clockwise rotation is safer since it drive smoke, gases, and flames away from the nozzle. Counterclockwise rotation does just the opposite.
-	\item Clockwise rotation produces steam with an active rolling action. Counterclockwise rotation produces steam with an inactive and lazy action.
-	\item A clockwise rotation produces a faster knockdown time.
+	\item Clockwise rotation drives most of the heated gases, smoke, and flames away from the nozzle. Counterclockwise rotation does just the opposite.
+	\item Steam formed by the clockwise rotation has a violent rolling action. Counterclockwise rotation produces steam with an inactive and lazy action.
+	\item A clockweise roation increases the efficiency of water and produces a faster knockdown time than counterclockwise rotation.
 \end{enumerate}
-
-**** better explanation of hose streams with more complete content and information about existing research to be added ****
 
@@
 \begin{enumerate}
-	\item Determine which hose stream patterns cause significant air movement in a structure and the amount of air movement they induce compared to other stream patterns
-	\item Determine the impact of different water application patterns on the ventilation in a structure
+	\item Determine which hose stream patterns cause significant air movement in a structure 
+	\item Determine the amount of air movement induced by different stream patterns
+	\item Determine the impact of different stream application patterns on the ventilation in a structure
 \end{enumerate}
@@
 \end{figure}
+
+Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle on air flows in a structure was conducted.
+
 \FloatBarrier
@@
 \label{chap:exp_overview}
-
 To study the impact of different hose stream and application pattern selections on air movement inside a structure, various water flow experiments were conducted in two experimental structures designed to replicate typical residential structures.
-The experiments focused on studying the differences in amount of air movement caused by specific combinations of three different hose stream patterns and four different water application patterns.
+The experiments focused on studying the differences in amount of air movement caused by specific combinations of four different hose stream patterns and four different water application patterns.
 
@@
 \label{sec:exp_setup}
-
-The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
+The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
 Sensors were installed throughout the residential-sized test structures to measure air velocity during the water flow experiments.
@@
 A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{sec:uncertainty}.
-For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes (BDPs)~\cite{McCaffrey:Combustion_and_Flame}.
-An array of 6 BDPs located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
-A single thermocouple was attached to each BDP to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
-Every thermocouple attached to the BDPs were exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
+For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
+An array of 6 bi-directional probes located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
+A single thermocouple was attached to each bi-directional probes to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
+Every thermocouple attached to the bi-directional probes was exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
 Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2~mm (0.13 in) diameter Inconel shield that was 0.76~m (2.5~ft) in length.
 
-The approximate locations of the BDPs used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}.
-To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by BDPs located at interior doorways are considered in this report.
-The set of BDPs at the northeast interior doorway of the East Structure, denoted as ``A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
-The set of BDPs at the interior doorway in the West Structure, denoted as ``A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
+The approximate locations of the bi-directional probes used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}.
+To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
+The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
+The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
 
@@
 	\includegraphics[width=3.5in]{../Figures/Pictures/BDPs_east}
-	\caption[Array of BDPs at interior doorway in East Structure.]{Array of BDPs located at the northeast interior doorway in the East Structure. View is looking at the array from Room C.}
+	\caption[Array of bi-directional probes at interior doorway in East Structure.]{Array of bi-directional probes located at the northeast interior doorway in the East Structure.
+View is looking at the array from Room C.}
 	\label{fig:BDPs}
@@
 
-BDPs with pressure transducers and single thermocouples were used to measure the gas velocity.
+Bi-directional probes with pressure transducers and single thermocouples were used to measure the gas velocity.
 Bare-bead Type K thermocouples were co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for BDPs of similar design~\cite{Bryant:FSJ2009}.
+A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
 The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm18$\%.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/flow_meter}
+	\includegraphics[width=4in]{../Figures/Pictures/flow_meter}
 	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
@@
 \label{sec:exp_procedure}
-Every experiment discussed in this report involved discharging water at a rate of 120 GPM from a combination nozzle set to flow water in a straight, narrow fog, or wide fog stream pattern.
+Every experiment discussed in this report involved discharging water at a known flow rate from a combination nozzle set to flow water in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle in a solid stream pattern.
 Specific doors were opened or closed before and/or during the experiments to change the ventilation in the structure.
 
-A total of seven test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three test series used a combination nozzle attached to a monitor to flow water and the other three used a combination nozzle attached directly to a hoseline to flow water (Fig.~\ref{fig:monitor+handline}).
+A total of seven test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at 180~GPM.
 Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
@@
 	\endminipage \hfill
-	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75 in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
+	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75~in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
 	\label{fig:monitor+handline}
@@
 
-Three different layouts were used for the six test series.
+Three different layouts were used for the seven test series.
 The test series conducted in the East Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
@@
 The main difference between the two layouts used for the West Structure experiments is the position of the south side door on the first level.
-Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}) and Tests 17 and 19 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
-Additionally, Tests 16 and 17 used a combination nozzle attached to a monitor to flow water, and Tests 18 and 19 used a combination nozzle attached directly to a handline to flow water.
+Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}) and Tests 17, 19, and 70 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
+Tests 16 and 17 used a combination nozzle attached to a monitor to flow water; Tests 18 and 19 used a combination nozzle attached directly to a handline to flow water; and Test 70 used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
 
@@
 	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
-The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A6 (blue square).}
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A6 (blue square).}
 	\label{fig:east_setup}
@@
 	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square).
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A10 (blue square).
 On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
@@
 	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of BDP A10 (blue square).
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A10 (blue square).
 On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
@@
 \label{sec:monitor_procedure}
-Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
 One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.
+An additional test series, Test 70, used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
 Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
@@
 Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the East Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
-A plan view of the structure's layout annotated with the approximate location of the BDP array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
+A plan view of the structure's layout annotated with the approximate location of the bi-directional probes array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
 The procedure for Test 33 was the simplest of all the test procedures.
@@
 	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at area above the doorway on the south wall of Room B during Test 33.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at the area above the doorway on the south wall of Room B during Test 33.}
 	\label{fig:test_33_pic}
@@
 
+Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17.
+The stairwell door was opened for the entire test series.
+The test series began by flowing water in a straight stream from a combination nozzle aimed at the near target.
+Then, the west double door on the second floor was opened.
+After 60 more seconds of flow, the nozzle was closed to stop flow for 30 seconds.
+The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times.
+Then, the monitor was aimed at the far target, and the procedure was repeated.
+This entire process was repeated using the solid stream from the smooth bore nozzle.
+Fig.~\ref{fig:test_70_pic} contains images of the straight stream from the combination nozzle and solid stream from the smooth bore nozzle during Test 70.
+
+\begin{figure}[!ht]
+	\minipage{2.15in}
+	\begin{center}
+		\includegraphics[width=2in]{../Figures/Pictures/SS_70}
+	\end{center} 
+	\endminipage
+	\minipage{2.15in}
+	\begin{center}
+		\includegraphics[width=2in]{../Figures/Pictures/SB_70}
+	\end{center}
+	\endminipage
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle during Test 70.]{Straight stream (left) from combination nozzle and solid stream (right) from smooth bore nozzle during Test 70.}
+	\label{fig:test_70_pic}
+\end{figure}
+\FloatBarrier
+
 \subsection{Handline Experiments}
 \label{sec:handline_procedure}
-Numerous experiments were conducted during three different test series using a 1.75 in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+Numerous experiments were conducted during three different test series using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
 One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure.
@@
 
-Test 34 utilized a 1.75 in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}.
+Test 34 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}).
 The layout of the structure was identical to the layout described above in Section~\ref{sec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}.
@@
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed identical procedures that involved using a 1.75 in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
+Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
 For every experiment during the two tests, the water stream was aimed at the south side wall of the first floor.
@@
 
-Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
-Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 17 and measurements obtained from the BDPs at A6 during Test 33 are presented in Appendix~\ref{sec:monitor_figs}.
+Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
+Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 17 and measurements obtained from the bi-directional probes at A6 during Test 33 are presented in Appendix~\ref{sec:monitor_figs}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity measured by the BDPs at A10 during Test 16 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
 	\label{fig:Test_16_BDP_A10_Avg_All}
@@
 For every hose stream and target location combination during the monitor experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
-Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the BDP array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, and 33.
+Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, and 33.
 
@@
 
-Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the BDPs at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
-Similar plots that were generated using measurements obtained from the BDPs at A10 during Test 19 and measurements obtained from the BDPs at A6 during Test 34 are presented in Appendix~\ref{sec:handline_figs}.
+Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
+Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 19 and measurements obtained from the bi-directional probes at A6 during Test 34 are presented in Appendix~\ref{sec:handline_figs}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity measured by the BDPs at A10 during Test 18 for the three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 18 for the three hose stream patterns.}
 	\label{fig:Test_18_BDP_A10_Avg_All}
@@
 For every hose stream and application pattern combination tested during the handline experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
-Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} list the average velocity measured by the BDP array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18 and 19, respectively.
+Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18 and 19, respectively.
 
@@
 \begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
+	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
+	\label{fig:Test_33_BDP_A6_Avg_All}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[!ht]
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity measured by the BDPs at A10 during Test 17 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 17 for three hose stream patterns.}
 	\label{fig:Test_17_BDP_A10_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
-	\caption{Average velocity measured by the BDPs at A10 during Test 70 for straight stream and smooth bore stream patterns.}
+	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns.}
 	\label{fig:Test_70_BDP_A10_Avg_All}
@@
 \begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
+	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
+	\label{fig:Test_34_BDP_A6_Avg_All}
+\end{figure}
+\FloatBarrier
+
+\begin{figure}[!ht]
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity measured by the BDPs at A10 during Test 19 for the three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 19 for the three hose stream patterns.}
 	\label{fig:Test_19_BDP_A10_Avg_All}

### 2016-02-22 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -22,12 +22,12 @@ specify_test = False
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = True
+specify_year = False
 specific_year = '2015'
 
 # Specify structure
 specify_struct = True
-specific_struct = 'West'
+specific_struct = 'East'
 
 # Specify monitor or handline
 specify_type = False
@@ -40,7 +40,7 @@ skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh',
 # = Specify files to generate =
 # =============================
 
-result_file = True         # Generate a .csv file with channel avgs for specified sensor groups
+result_file = True        # Generate a .csv file with channel avgs for specified sensor groups
 all_channel_plot = False    # Plot of individual channels in sensor group
 group_avg_plot = False     # Plot avg of all channels for sensor group
 stream_avgs_plot = True    # Plot avg of all channels for each stream tested during experiment
@@ -229,10 +229,74 @@ def sort_data(test_name, start_time, test_type):
 		P_or_L_heading:P_or_L_ls,'Door':door_status_ls}
 		group_results = pd.DataFrame(group_set, 
 			columns = ['Start', 'End', 'Stream', P_or_L_heading, 'Door'])
-		return group_results, zero_time_ls
 	else:
-		print ('Need to write code for sorting East Tests')
-		sys.exit()
+		# initialize lists and start_seq value
+		start_seq = -1
+		door_status = 'C'
+		streams_ls = []
+		patterns_ls = []		
+		start_times_ls = []
+		end_times_ls = []
+		location_ls = []
+		door_status_ls = []
+		zero_time_ls = []
+		
+		for index, row in all_times.iterrows():
+			if pd.isnull(row[test_name]) or index == 0:
+				continue
+			else:
+				# mark event start time or add event info to lists
+				if start_seq == -1:
+					zero_time_ls.append(index-start_time)
+				else:
+					end_seq = index-start_time
+					streams_ls.append(stream)
+					patterns_ls.append(pattern)
+					start_times_ls.append(start_seq)
+					end_times_ls.append(end_seq)
+					location_ls.append(location)
+					door_status_ls.append(door_status)
+
+				# Determine stream type, pattern, and target location
[…]

### 2016-02-29 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Updated hose stream/FDS reports, edited drawings & condensed inventor files

@@
 \label{chap:Introduction}
+[FDS intro, importance of validation, fact this report only includes experimental setup and procedure]
 
@@
 \end{figure}
-% make new 1st floor plan with rear door completely sealed off
 
@@
 Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured.
-A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.
+A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics discussed in the follow sections.
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=0.35\columnwidth]{../Figures/Floor_Plans/Legend}
-% 	\caption[Instrumentation Legend.]{Instrumentation Legend.}
-% 	\label{fig:Instrumentation_Legend}
-% \end{figure}
+\begin{figure}[!ht]
+	\includegraphics[width=0.25\columnwidth]{../Figures/Floor_Plans/Instrumentation_Legend}
+	\caption{Instrumentation Legend.}
+	\label{fig:Instrumentation_Legend}
+\end{figure}
 
@@
 \subsubsection*{East Structure}
-Three different test series -- Series 4, Series 5, and Series 6 -- were conducted in the east structure.
-Each series was composed of three experiments that used an identical procedure to change the ventilation pattern in the structure.
-The three procedures used for each test series are outlined in Figs.~\ref{fig:east_test_4}-\ref{fig:east_test_6}.
+Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure.
+Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure.
+The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern.
+During the experiments in Test Series 5, each double door was opened and the roof vent was opened and closed throughout the procedure.
+Both the roof vent and west double door were opened during each experiment in Series 6.
+Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} outline the experimental procedures of Test Series 4--6 in more detail.
 
@@
 \end{minipage}
-\caption{Test Series 4 layout and ordered sequence of events.}
+\caption{Test Series 4 layout and sequence of events.}
 \label{fig:east_test_4}
@@
 \end{minipage}
-\caption{Test Series 5 layout and ordered sequence of events.}
+\caption{Test Series 5 layout and sequence of events.}
 \label{fig:east_test_5}
@@
 \end{minipage}
-\caption{Test Series 6 layout and ordered sequence of events.}
+\caption{Test Series 6 layout and sequence of events.}
 \label{fig:east_test_6}
@@
 \subsubsection*{West Structure}
-Two different test series -- Series 22 and Series 24 -- were conducted in the west structure.
-Each series was composed of two experiments that used an identical procedure to change the ventilation pattern in the structure.
-The two procedures used for each test series are outlined in Figs.~\ref{fig:west_test_22} and \ref{fig:west_test_24}.
+Two different test series---Series 22 and Series 24---were conducted in the west structure.
+Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure.
+Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened.
+Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure.
+Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} outline the experimental procedures of Test Series 22 and 24 in more detail.
 
@@
 	\centering
-	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_22}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
 \end{minipage}
-\caption{Test Series 22 layout and ordered sequence of events.}
+\caption{Test Series 22 layout and sequence of events.}
 \label{fig:west_test_22}
@@
 	\centering
-	% \includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_Test_24}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
 \end{minipage}
-\caption{Test Series 24 layout and ordered sequence of events.}
+\caption{Test Series 24 layout and sequence of events.}
 \label{fig:west_test_24}

### 2016-02-29 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream/FDS reports, edited drawings & condensed inventor files

@@
 \label{chap:results}
-In the following sections, the measurements will be presented in graphic and tabular form.
+In the following sections, the measurements are presented in graphic and tabular form.
 In the graphs, an error bar will represent the estimated uncertainty of the measurement.
@@
 
-Fig.~\ref{fig:Test_16_A10_Avgs} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns aimed at the near and far targets during Test 16.
-Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 17 and measurements obtained from the bi-directional probes at A6 during Test 33 are presented in Appendix~\ref{sec:monitor_figs}.
+Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16.
+Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{sec:monitor_figs}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
+	\caption{Average velocity through the interior stairwell door (A10) during Test 16 for the three hose stream patterns.}
 	\label{fig:Test_16_BDP_A10_Avg_All}
 \end{figure}
-\FloatBarrier
 
-For every hose stream and target location combination during the monitor experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
-Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, and 33.
+Excluding the straight stream during Test 33, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination during the monitor experiments.
+Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, 33, and 70.
 
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for each monitor experiment}
+\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
 \begin{tabular}{lccccc}
 \toprule
+ & \multicolumn{5}{c}{\large ------------------------ 120 GPM ------------------------} 
+\\
  & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
@@
 \\ \midrule
- & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} \\
+ & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
+\\
+ & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
+\\
 \textbf{Stream} &
@@
 \end{table}
+
+Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream.
+This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{sec:monitor_figs}.
+Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
+Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
 \FloatBarrier
-
-**** Discuss tabulated results, main point being fogs move more air than straight ****
 
@@
 
-Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average velocity measured by the bi-directional probes at A10 for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
-Similar plots that were generated using measurements obtained from the bi-directional probes at A10 during Test 19 and measurements obtained from the bi-directional probes at A6 during Test 34 are presented in Appendix~\ref{sec:handline_figs}.
+Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
+Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{sec:handline_figs}.
 
@@
 
-For every hose stream and application pattern combination tested during the handline experiments, there was always significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
-Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18 and 19, respectively.
+Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity through the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.
 
@@
 
-Similar to the monitor experiments, there is a significant difference between the average air velocity caused by the fixed straight stream and the average velocity caused by the narrow and wide fog streams; the velocities for the narrow and wide fog were always significantly higher than the velocity of the fixed stream.
-Additionally, it was only when the hose began to move around that the air velocity through the doorways for the straight stream approached the air velocities associated with the narrow and wide fogs for the corresponding pattern.
-However, the straight stream hose pattern always resulted in the lowest average air velocity through the doorway for the three different hose streams at each of the four application patterns.
+Nearly every hose stream and application pattern combination using a narrow or wide fog stream during the handline experiments produced significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
+For the straight stream, however, significant air movement through the interior doorway was only reached once the stream was applied in a pattern that involved moving the handline.
+Similar to the monitor experiments, the average air velocity through the interior doorway while the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
+
+% --- STOPPED --- %
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 13 for three hose stream patterns.}
 	\label{fig:Test_33_BDP_A6_Avg_All}

### 2016-02-29 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -22,12 +22,12 @@ specify_test = False
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = False
+specify_year = True
 specific_year = '2015'
 
 # Specify structure
 specify_struct = True
-specific_struct = 'East'
+specific_struct = 'West'
 
 # Specify monitor or handline
 specify_type = False
@@ -270,13 +270,14 @@ def sort_data(test_name, start_time, test_type):
 
 def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, plot_type, tick_info):
 	plt.errorbar(x_max_index, y_max, yerr=(.18)*y_max, ecolor='k')
-
+	if 'West' not in fig_name and plot_type == 'stream avgs':
+		end_time = end_time - 1
 	ax1 = plt.gca()
 	ax1.set_xlim([0, end_time])
 	ax1.set_ylim(math.floor(y_min)-0.1, math.ceil(y_max)+0.1)
 	ax1.xaxis.set_major_locator(plt.MaxNLocator(8))
 	ax1_xlims = ax1.axis()[0:2]
-	# grid(True)
+	grid(True)
 	plt.axhline(0, color='0.50', lw=1)
 	ax1.set_xlabel('Time (s)', fontsize=20)
 	ax1.set_ylabel('Velocity (m/s)', fontsize=20)
@@ -307,7 +308,11 @@ def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, 
 		else:
 			tick_loc = tick_info[1]
 			tick_labels = tick_info[0]
-		[plt.axvline(_x, color='0.50', lw=1) for _x in tick_loc]
+		if 'West' in fig_name:
+			[plt.axvline(_x, color='0.50', lw=1) for _x in tick_loc[:-1]]	
+		else:		
+			[plt.axvline(_x, color='0.50', lw=1) for _x in tick_loc]
+			ax1.set_xticks(tick_loc)
 		ax3.set_xticks(tick_loc)
 		plt.setp(plt.xticks()[1], rotation=60)
 		ax3.set_xticklabels(tick_labels, fontsize=10, ha='left')
@@ -731,14 +736,14 @@ for f in os.listdir(data_dir):
 								if row['Door'] == 'O':
 									continue
 								if row['Stream'] == 'SS':
-									seq_start = int(row['Start'])
+									seq_start = int(row['Start'])+1
 									seq_end = int(row['End'])
[…]

### 2016-03-02 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Edits to intro. section of FDS Exp Report

@@
 \label{chap:Introduction}
-[FDS intro, importance of validation, fact this report only includes experimental setup and procedure]
+% [FDS intro] 
+Fire dynamics 
+% [importance of validation]
+
+% [this report is (1/2) --> experimental setup and procedure]
+This report describes the full-scale fire test experiments that are used for the FDS model validation of [...].
+Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings.
+During each test, propane was provided to three burners at a known flow rate [to create a diff flame].
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected.
 
@@
 
-\subsubsection*{East Structure}
+\section{East Structure Tests}
 Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure.
@@
 The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern.
-During the experiments in Test Series 5, each double door was opened and the roof vent was opened and closed throughout the procedure.
+During the experiments in Series 5, each double door was opened and the roof vent was opened and closed.
 Both the roof vent and west double door were opened during each experiment in Series 6.
-Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} outline the experimental procedures of Test Series 4--6 in more detail.
+Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} include a schematic and additional details about the procedures used for the experiments during Series 4--6.
 
@@
 
-\subsubsection*{West Structure}
+\section{West Structure Tests}
 Two different test series---Series 22 and Series 24---were conducted in the west structure.
@@
 Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure.
-Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} outline the experimental procedures of Test Series 22 and 24 in more detail.
+Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} include a schematic and additional details about the procedures used for the experiments during Series 22 and 24.
 

### 2016-03-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Updated hose stream report, plotting script & FDS exp report

@@
 % [FDS intro]
-Fire dynamics 
+
 % [importance of validation]
@@
 % [this report is (1/2) --> experimental setup and procedure]
-This report describes the full-scale fire test experiments that are used for the FDS model validation of [...].
+This report describes a series of full-scale fire test experiments that were conducted for the purpose of FDS model validation.
 Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings.
-During each test, propane was provided to three burners at a known flow rate [to create a diff flame].
-Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected.
+During each test, propane was provided to three diffusion flame burners at a measured flow rate.
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structures while ventilation patterns were changed by opening and closing specific doors and roof vents.
 

### 2016-03-03 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report, plotting script & FDS exp report

@@
 
+One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
 NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{}.
@@
 
-\FloatBarrier
+\clearpage
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 13 for three hose stream patterns.}
+	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
 	\label{fig:Test_33_BDP_A6_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 16 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}
 	\label{fig:Test_34_BDP_A6_Avg_All}

### 2016-03-03 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -18,15 +18,15 @@ rcParams.update({'figure.autolayout': True})
 #  =================
 
 # Specify name
-specify_test = False
+specify_test = True
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = True
+specify_year = False
 specific_year = '2015'
 
 # Specify structure
-specify_struct = True
+specify_struct = False
 specific_struct = 'West'
 
 # Specify monitor or handline
@@ -618,6 +618,8 @@ for f in os.listdir(data_dir):
 					stream_names = []
 					time_btwn_seq = []
 					for index, row in group_results.iterrows():
+						if row['Door'] == 'A open' or row['Door'] == 'Closed A':	# skips part of Test 16
+							continue
 						start_seq = row['Start']
 						if index == 0:      # first row, set initial values
 							end_seq = row['End']
@@ -669,6 +671,7 @@ for f in os.listdir(data_dir):
 					stream_num = stream_num + 1
 					count = 1
 					updated_times = [0]
+					# Find smallest time between each event and updated times for plot and labels
 					while count < (len(xlabel_times)):
 						if count % 2 == 0:
 							current_diff = time_btwn_seq[(count/2)-1]
@@ -676,7 +679,7 @@ for f in os.listdir(data_dir):
 							current_diff = xlabel_times[count]-xlabel_times[count-1]
 						next_time = updated_times[-1] + current_diff
 						if next_time != updated_times[-1]:
-							updated_times.append(next_time+1)
+							updated_times.append(next_time)
 						count = count+1
 					column_num = 0
 					for column in stream_times.columns[:]:
@@ -707,6 +710,7 @@ for f in os.listdir(data_dir):
 							marker=next(plot_markers), markevery=int(len(t))/20, 
 							mew=1.5, mec='none', ms=7, ls=line_style, lw=2, label=column)
 						column_num = column_num + 1
+
 				else:
 					if test_name[7] == 'A':
 						locations = ['Room B ceiling', 'S doorway in Room B']
@@ -743,7 +747,7 @@ for f in os.listdir(data_dir):
 									stream_data.extend(group_data['Avg'].loc[seq_start:seq_end])
 									iteration += 1
 							# fill extra 3 at end for moving average
-							stream_data.extend(group_data['Avg'].loc[seq_end:seq_end+4 ])
+							stream_data.extend(group_data['Avg'].loc[seq_end:seq_end+4])
 							SS_remain = False
 							column = 'SS'
 						elif (NF_remain):

### 2016-03-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added to FDS exp report

@@
 \flushright{
-Joseph Willi \\
-Kevin McGrattan \\
-Randall McDermott \\
-Craig Weinschenk \\
 
@@
 \flushright{
-Joseph Willi \\
-Kevin McGrattan \\
-Randall McDermott \\
-Craig Weinschenk \\
+
 {\em Fire Research Division \\
@@
 
-\cleardoublepage
-\phantomsection
-\addcontentsline{toc}{chapter}{List of Tables}
-\listoftables
+% \cleardoublepage
+% \phantomsection
+% \addcontentsline{toc}{chapter}{List of Tables}
+% \listoftables
 
@@
 \label{chap:Introduction}
-% [FDS intro]
-
-% [importance of validation]
-
-% [this report is (1/2) --> experimental setup and procedure]
+[Add intro about FDS, purpose of validation, etc.] 
+\\~\\
 This report describes a series of full-scale fire test experiments that were conducted for the purpose of FDS model validation.
@@
 During each test, propane was provided to three diffusion flame burners at a measured flow rate.
-Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structures while ventilation patterns were changed by opening and closing specific doors and roof vents.
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while ventilation patterns within the structure were changed by opening and closing certain doors and vents.
 
@@
 The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
-The fire source for all experiments was generated by three propane burners and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
+The fire source for all experiments was generated by three propane burners, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
 
@@
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
+The east structure was designed to simulate a single-story residential structure, and the west structure was designed to simulate a two-story residential structure.
 The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
@@
 	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
-	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
+	\caption[North side of the east and west structures.]{North side of the east (top) and west (bottom) test structures.}
 	\label{fig:struct_pics}
@@
 
-The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and \textit{were lined with 13~mm (0.5~in) thick cement board.
-The walls were composed of 16~mm (5/8~in) Type X gypsum board.
-Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.}
+The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
+The walls were composed of 16~mm (0.625~in) Type X gypsum board.
+Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
 \FloatBarrier
 
-The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 0.30~m (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
 Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
@@
 	\includegraphics[width=6in]{../../Hose_Stream_Report/Figures/Pictures/TJI_support}
-	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams.
-View is of the southeast corner of the structure.}
+	\caption[Ceiling support of the west structure.]{First floor ceiling support of the west structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
 	\label{fig:TJI}
@@
 
-The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
+The second floor of the west structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
 The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
-The interior walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
-The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
+The interior walls were protected by 16~mm (0.625~in) fire rated gypsum board, 16~mm (0.625~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
 
-% Add info about roof vent in single story
 \subsection{Layout}
 \label{sec:layout}
-Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the east and west structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\caption[Dimensioned floor plan of the east structure.]{Dimensioned floor plan of the east structure. Structure is symmetric across horizontal centerline.}
 	\label{fig:east_dimensioned_plan}
 \end{figure}
-% make new floor plan with ceiling vent included
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
-	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Dimensioned floor plans of the west structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the west structure.}
 	\label{fig:west_dimensioned_plan}
@@
 
-The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
-
-The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
-All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
+The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high.
+The stairs connecting the two floors of the west structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+The exterior doors of both structures, the stairwell door on the second level of the west structure, and a square roof vent with side length 1.2~m (4~ft) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
 \FloatBarrier
@@
 Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples.
-Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
+Additional single thermocouples were installed in conjunction with bi-directional probes for gas velocity measurements.
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
@@
 Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured.
-A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics discussed in the follow sections.
+A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.
 
@@
 	\includegraphics[width=0.25\columnwidth]{../Figures/Floor_Plans/Instrumentation_Legend}
-	\caption{Instrumentation Legend.}
+	\caption[Instrumentation legend.]{Legend used for schematics of instrumentation locations.}
 	\label{fig:Instrumentation_Legend}
@@
 
-Three propane burners, each with a square opening of side length 0.6~m (2~ft) 0.14~m (5.5~in) above the floor, were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure and used as the fuel source in each experiment.
-Propane flowed at a known volumetric flow rate during the experiments.
+Three propane burners, each with a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor, were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure and used as the fuel source in each experiment.
+Propane was supplied to the burners at a measured flow rate during all experiments.
 \FloatBarrier
@@
 \subsubsection*{East Structure}
-The East Structure was instrumented with 5 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, 5 total heat flux plus radiometer sensor pairs, and 2 gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
+The east structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
-	\caption{Location of instrumentation in the East Structure.}
+	\caption{Location of instrumentation in the east structure.}
 	\label{fig:east_instrumentation}
@@
 
-Each bare-bead thermocouple array was composed of 8 thermocouples.
-The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
-The three bi-directional probe and solid thermocouple arrays located at the exterior doorways of the structure contained 8 probes centered in the doorway with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
-The fourth bi-directional probe and solid thermocouple array was located at the roof vent and contained three probes \textit{centered between the east and west sides of the vent and spaced ??
-apart between the north and south sides.} The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-Gas concentrations were pulled through \textit{3.2~mm (0.125~in) diameter stainless steel tubing located 1.22~m (4~ft) above the floor.}
+Each bare-bead thermocouple array was composed of eight thermocouples.
+The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
+Three bi-directional probe and solid thermocouple arrays, centered in each exterior doorway of the structure, contained eight probes with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit as shown in Fig.~\ref{fig:BDP_arrays}.
+The fourth bi-directional probe plus solid thermocouple array was located at opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}.
+The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+
+\begin{figure}[!ht]
+	\includegraphics[width=0.45\columnwidth]{../Figures/Pictures/doorway_BDPs}
+	\\~\\
+	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
+	\caption[Bi-directional probe plus solid thermocouple arrays in east structure.]{Bi-directional probe plus solid thermocouple array in exterior doorway (top) and in roof vent (bottom) of the east structure.}
+	\label{fig:BDP_arrays}
+\end{figure}
+
 \FloatBarrier
@@
 \subsubsection*{West Structure}
-The first floor of the West Structure was instrumented with 3 bare-bead thermocouple arrays, 3 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe, and the second floor was equipped with 3 bare-bead thermocouple arrays, 4 bi-directional probe plus solid thermocouple arrays, and 1 gas sample inlet pipe.
-The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
+The first floor of the west structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
+The locations of the instrumentation in the west structure is shown in Fig.~\ref{fig:west_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
-	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Location of instrumentation in the west structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the west structure.}
 	\label{fig:west_instrumentation}
@@
 
-The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure.
-The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure.
-3.2~mm (0.125~in) stainless steel tubing was located 1.22~m (4~ft) above the floor and used to pull gas samples from the environment.
+The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the east structure.
+The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the east structure.
+Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
 \FloatBarrier
@@
 Each length measurement was taken carefully.
-Length measurements such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
+Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
 However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
@@
 
-The standard uncertainty in temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
+The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
@@
 A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe.
-The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+The thermocouple wire was protected with a 3.2~mm (0.125~in) diameter inconel sheath.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
@@
 
-\textit{Gas meter flowrate/HRR error}
+\clearpage
 
@@
  	5 	 & East double door opened \\
- 	6	 & South side door opened \\
+ 	6	 & South exterior door opened \\
  	7-9  & Burners extinguished \\
@@
  	5 	 & 1st floor west double door opened \\
- 	6	 & 2nd floor east double door opened \\
- 	7 	 & 1st floor east double door opened \\
+ 	6	 & 1st floor east double door opened \\
+ 	7 	 & 2nd floor east double door opened \\
  	8-10  & Burners extinguished \\
@@
  	6	 & 2nd floor west double door opened \\
- 	7 	 & 2nd floor south side door opened \\
+ 	7 	 & 2nd floor south exterior door opened \\
  	8-10 & Burners extinguished \\
@@
 
-\chapter{Acknowledgments}
-\label{chap:Acknowledgments}
+\clearpage
+
+\chapter{Summary}
+\label{chap:Summary}
 
@@
 
-\appendix
+% \appendix
 
-\chapter{Appendix A}
+% \chapter{Appendix A}
 
-\begin{landscape}
-\begin{table}[!ht]
-\caption{East Structure experimental event times (mm:ss)}
-\begin{tabular}{lcccccccccccccc}
- \toprule
-\textbf{Test} & 
-\multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} & 
-\multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} & 
-\multicolumn{2}{c}{\textbf{\underline{Center Burner}}} & 
-\multicolumn{2}{c}{\textbf{\underline{W Double Door}}} & 
-\multicolumn{2}{c}{\textbf{\underline{E Double Door}}} & 
-\multicolumn{2}{c}{\textbf{\underline{Single Door}}} & 
-\multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
-\\
-\textbf{Number} & 
-\textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & 
-\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
-\textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
-\\
-\midrule
-% Test 2
-2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 & 
-N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
-% Test 3
-3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
-N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
-% Test 4
-4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
-N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A 
-\\ \multicolumn{15}{c}{ } \\
-% Test 5a
-5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
-N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
-% Test 5b
-5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 & 
-N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
-% Test 5c
-5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 & 
-N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
-\\ \multicolumn{15}{c}{ } \\
-% Test 6a
-6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
-N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-% Test 6b
-6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
-N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-% Test 6c
-6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
-N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-\bottomrule
-\end{tabular}
-\label{table:east_exp_times}
-\end{table}
-\end{landscape}
+% \begin{landscape}
+% \begin{table}[!ht]
+% \caption{east structure experimental event times (mm:ss)}
+% \begin{tabular}{lcccccccccccccc}
+%  \toprule
+% \textbf{Test} & 
+% \multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{Center Burner}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{W Double Door}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{E Double Door}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{Single Door}}} & 
+% \multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
+% \\
+% \textbf{Number} & 
+% \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & 
+% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
+% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
+% \\
+% \midrule
+% % Test 2
+% 2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 & 
+% N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
+% % Test 3
+% 3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
+% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
+% % Test 4
+% 4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 & 
+% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A 
+% \\ \multicolumn{15}{c}{ } \\
+% % Test 5a
+% 5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+% N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
+% % Test 5b
+% 5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 & 
+% N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
+% % Test 5c
+% 5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 & 
+% N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
+% \\ \multicolumn{15}{c}{ } \\
+% % Test 6a
+% 6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+% % Test 6b
+% 6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+% % Test 6c
+% 6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 & 
+% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
+% \bottomrule
+% \end{tabular}
+% \label{table:east_exp_times}
+% \end{table}
+% \end{landscape}
 

### 2016-03-03 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex

@@
 \label{chap:Introduction}
-[Add intro about FDS, purpose of validation, etc.] 
-\\~\\
-This report describes a series of full-scale fire test experiments that were conducted for the purpose of FDS model validation.
+
+This report describes a series of full-scale fire experiments that were conducted for the purpose of model validation.
 Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings.
@@
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-The east structure was designed to simulate a single-story residential structure, and the west structure was designed to simulate a two-story residential structure.
+The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
 The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
@@
 	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
-	\caption[North side of the east and west structures.]{North side of the east (top) and west (bottom) test structures.}
+	\caption[North side of the east and West Structures.]{North side of the east (top) and west (bottom) test structures.}
 	\label{fig:struct_pics}
@@
 	\includegraphics[width=6in]{../../Hose_Stream_Report/Figures/Pictures/TJI_support}
-	\caption[Ceiling support of the west structure.]{First floor ceiling support of the west structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
+	\caption[Ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
 	\label{fig:TJI}
@@
 
-The second floor of the west structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
+The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
 The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
@@
 \label{sec:layout}
-Dimensioned floor plans of the east and west structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the east and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the east structure.]{Dimensioned floor plan of the east structure. Structure is symmetric across horizontal centerline.}
+	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Structure is symmetric across horizontal centerline.}
 	\label{fig:east_dimensioned_plan}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
-	\caption[Dimensioned floor plans of the west structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the west structure.}
+	\caption[Dimensioned floor plans of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
 	\label{fig:west_dimensioned_plan}
@@
 The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the west structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
-The exterior doors of both structures, the stairwell door on the second level of the west structure, and a square roof vent with side length 1.2~m (4~ft) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
 \FloatBarrier
@@
 \subsubsection*{East Structure}
-The east structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
+The East Structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
-	\caption{Location of instrumentation in the east structure.}
+	\caption{Location of instrumentation in the East Structure.}
 	\label{fig:east_instrumentation}
@@
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
-	\caption[Bi-directional probe plus solid thermocouple arrays in east structure.]{Bi-directional probe plus solid thermocouple array in exterior doorway (top) and in roof vent (bottom) of the east structure.}
+	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in exterior doorway (top) and in roof vent (bottom) of the East Structure.}
 	\label{fig:BDP_arrays}
@@
 \subsubsection*{West Structure}
-The first floor of the west structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
-The locations of the instrumentation in the west structure is shown in Fig.~\ref{fig:west_instrumentation}.
+The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
+The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
-	\caption[Location of instrumentation in the west structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the west structure.}
+	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
 	\label{fig:west_instrumentation}
@@
 
-The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the east structure.
-The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the east structure.
+The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure.
+The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure.
 Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
@@
 \label{sec:Uncertainty}
+
 There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, and gas velocity measurements.
@@
 
+\subsubsection{Compartment Dimensions}
+
 Each length measurement was taken carefully.
@@
 
+\subsubsection{Thermocouples}
+
 The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
@@
 
-In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
+\subsubsection{Heat Flux Gauges}
+
+Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
 The manufacturer reports a $\pm$3\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
 Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8\%~\cite{Pitts:2006}.
+
+\subsubsection{Gas Sampling}
 
@@
 
+\subsubsection{Pressure Transducers}
+
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
@@
 The total expanded uncertainty was estimated at 10\%.
+
+\subsubsection{Bi-Directional Probes}
 
@@
 \section{East Structure Tests}
-Three different test series---Series 4, Series 5, and Series 6---were conducted in the east structure.
+Three different test series---Series 4, Series 5, and Series 6---were conducted in the East Structure.
 Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure.
@@
 \section{West Structure Tests}
-Two different test series---Series 22 and Series 24---were conducted in the west structure.
+Two different test series---Series 22 and Series 24---were conducted in the West Structure.
 Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure.
@@
 % \begin{table}[!ht]
-% \caption{east structure experimental event times (mm:ss)}
+% \caption{East Structure experimental event times (mm:ss)}
 % \begin{tabular}{lcccccccccccccc}

### 2016-03-04 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Minor edits to format of FDS exp report

@@
 \headerB{
-Overview of Fire Model Validation Experiments in Residential Scale Structures \\
+Propane Gas Fire Experiments in Residential Scale Structures \\
 }
@@
 
+% [Brief Introduction of FRD at NIST, ventilation, etc.]
+
 This report describes a series of full-scale fire experiments that were conducted for the purpose of model validation.
@@
 	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
-	\caption[North side of the east and West Structures.]{North side of the east (top) and west (bottom) test structures.}
+	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) test structures.}
 	\label{fig:struct_pics}

### 2016-03-04 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added channel list to FDS exp report

@@
 
-This report describes a series of full-scale fire experiments that were conducted for the purpose of model validation.
-Thirteen experiments that followed five different procedures were conducted in two structures designed to replicate typical residential dwellings.
+This report describes eight full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied.
+The experiments were conducted in two structures designed to replicate typical residential dwellings.
 During each test, propane was provided to three diffusion flame burners at a measured flow rate.
@@
 
-\subsubsection*{East Structure}
+\subsubsection{East Structure}
 The East Structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
@@
 
-\subsubsection*{West Structure}
+\subsubsection{West Structure}
 The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
@@
 \label{sec:Uncertainty}
-
 There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, and gas velocity measurements.
@@
 \subsubsection{Compartment Dimensions}
-
 Each length measurement was taken carefully.
@@
 \subsubsection{Thermocouples}
-
 The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
@@
 \subsubsection{Heat Flux Gauges}
-
 Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
@@
 \subsubsection{Gas Sampling}
-
 The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1\% when compared with span gas volume fractions~\cite{Bundy:2007}.
@@
 \subsubsection{Pressure Transducers}
-
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
@@
 \subsubsection{Bi-Directional Probes}
-
 Bi-directional probes and single thermocouples were used to measure the velocity.
@@
 \section{East Structure Tests}
-Three different test series---Series 4, Series 5, and Series 6---were conducted in the East Structure.
+\label{sec:east_procedure}
+Four different tests---Test 2, Test 3, Test 4, and Test 5---were conducted in the East Structure.
 Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure.
@@
 \section{West Structure Tests}
+\label{sec:west_procedure}
 Two different test series---Series 22 and Series 24---were conducted in the West Structure.
@@
 
-% \appendix
+\appendix
 
-% \chapter{Appendix A}
+\chapter{Channel Lists}
+\begin{longtable}[c]{c|lll}
+\caption{East Structure Channel List\label{table:east_channel_list}} \\
+\toprule
+\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} & 
+\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  & 
+\textbf{Channel Location} & 
+\textbf{Measurement Type} \\
+\midrule
+\endhead
+\multirow{13}{*}{\large\textbf{A1}} 
+ & TC\_A1\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A1\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A1\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A1\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A1\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A1\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A1\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A1\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A1	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A1    & 0.15~m above floor   & Radiative heat flux \\
+\cline{2-4}
+ & CO\_A      & 1.22~m above floor   & CO concentration \\
+ & CO2\_A     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_A      & 1.22~m above floor   & O$_2$ concentration \\
+\midrule
+\multirow{10}{*}{\large{\textbf{A2}}}
+ & TC\_A2\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A2\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A2\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A2\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A2\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A2\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A2\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A2\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A2	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A2    & 0.15~m above floor   & Radiative heat flux \\
+\bottomrule
+\newpage
+ \multirow{10}{*}{\large{\textbf{A3}}}
+ & TC\_A3\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A3\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A3\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A3\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A3\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A3\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A3\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A3\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A3	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A3    & 0.15~m above floor   & Radiative heat flux \\
+\midrule
+\multirow{13}{*}{\large\textbf{A4}} 
+ & TC\_A4\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A4\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A4\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A4\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A4\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A4\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A4\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A4\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A4	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A4    & 0.15~m above floor   & Radiative heat flux \\
+\cline{2-4}
+ & CO\_B      & 1.22~m above floor   & CO concentration \\
+ & CO2\_B     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
+\midrule
+\multirow{10}{*}{\large{\textbf{A5}}}
+ & TC\_A5\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A5\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A5\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A5\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A5\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A5\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A5\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A5\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A5	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A5    & 0.15~m above floor   & Radiative heat flux \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A7}}}
+ & TC\_A7\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A7\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A7\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A7\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A7\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A7\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A7\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A7\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A7\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A7\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A7\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A7\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A7\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A7\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A7\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A7\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{16}{*}{\large{\textbf{A8}}}
+ & TC\_A8\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A8\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A8\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A8\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A8\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A8\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A8\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A8\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A8\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A8\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A8\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A8\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A8\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A8\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A8\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A8\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A9}}}
+ & TC\_A9\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A9\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A9\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A9\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A9\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A9\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A9\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A9\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A9\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A9\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A9\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A9\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A9\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A9\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A9\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A9\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\end{longtable}
 

### 2016-03-05 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Combined Test_17b exp file with Test_17, updated hose plot script/report

@@
 Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16.
-Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{sec:monitor_figs}.
+Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{chap:monitor_plots}.
 
@@
 Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
-Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{sec:handline_figs}.
+Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}.
 
@@
 \appendix
-\chapter{Appendix}
-\label{chap:appendix}
-
-\section{Additional Figures}
-\label{sec:additional_figs}
-
-\subsection{Monitor Figures}
-\label{sec:monitor_figs}
+\chapter{Monitor Test Plots}
+\label{chap:monitor_plots}
 
@@
 
-\subsection{Handline Figures}
-\label{sec:handline_figs}
+\chapter{Handline Test Plots}
+\label{chap:handline_plots}
 

### 2016-03-07 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Hose stream report: New Test 17 plot, pictures, and refs

@@
 
-One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
-NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{}.
+One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and how different firefighting tactics affect the fire environment.
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
@@
 
-Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice~\cite{}.
+Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice~\cite{?}.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 Most fog nozzles contain an adjustable tip that can be rotated to produce different stream patterns and are therefore often referred to as combination nozzles.
-The types of streams produced by a fog nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{Essentials_FF}.
+The types of streams produced by a fog nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}.
 Increasing the angle of the stream allows for a larger area to be covered by water, thus exposing a larger water droplet surface area for heat absorption.
@@
 In addition to the type of stream pattern used, fire suppression tactics using hose streams can differ in the method used to apply the hose stream.
-For example, Royer suggests using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer}:
+For example, Royer suggests using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer:ISU}:
 \begin{enumerate} 
@@
 
+% \begin{figure}[!ht]
+% 	\includegraphics[width=\columnwidth]{../Figures/Pictures/hose_streams.pdf}
+% 	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments.
+From left to right: straight stream, narrow fog stream, and wide fog stream.}
+% 	\label{fig:hose_streams}
+% \end{figure}
+
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/hose_streams.pdf}
-	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments.
-From left to right: straight stream, narrow fog stream, and wide fog stream.}
+	\includegraphics[width=0.55\columnwidth]{../Figures/Pictures/hose_streams_1}
+	\\~\\
+	\includegraphics[width=0.55\columnwidth]{../Figures/Pictures/hose_streams_2}
+	\caption[Hose stream patterns used in experiments.]{The four types of stream patterns used during water flow experiments.
+Top row: narrow fog stream (left) and wide fog stream (right).
+Bottom row: straight stream from combination nozzle (left) and solid stream from smooth bore nozzle (right).}
 	\label{fig:hose_streams}
@@
 
-The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and \textit{were lined with 13~mm (0.5~in) thick cement board.
+The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
 The walls were composed of 16~mm (5/8~in) Type X gypsum board.
-Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.}
+Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
 \FloatBarrier

### 2016-03-07 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -407,6 +407,8 @@ for f in os.listdir(data_dir):
 		if check_name(test_name, test_year, test_type):     # check if file should be skipped
 			continue
 		else:   # Load exp. data file
+			if 'Test_17' in test_name:
+				f = test_name + '_original.csv'
 			data = pd.read_csv(data_dir + f)
 			data = data.set_index('TimeStamp(s)')
 			print
@@ -705,6 +707,16 @@ for f in os.listdir(data_dir):
 						count = count+1
 					column_num = 0
 					for column in test_streams:
+						plot_label = column + ' A10 Avg'
+						if column == 'SS':
+							color, marker = SS_color, SS_mark
+						elif column == 'NF':
+							color, marker = NF_color, NF_mark
+						elif column == 'WF':
+							color, marker = WF_color, WF_mark
+						elif column == 'SB':
+							color, marker = SB_color, SB_mark
+						
 						stream_data = []
 						i = 0
 						for index, row in stream_times.iterrows():
@@ -721,17 +733,6 @@ for f in os.listdir(data_dir):
 									# print start_loc, end_loc
 								i = i + 1
 								stream_data.extend(group_data['Avg'].loc[start_loc:end_loc])
-
-						plot_label = column + ' A10 Avg'
-						if column == 'SS':
-							color, marker = SS_color, SS_mark
-
-						elif column == 'NF':
-							color, marker = NF_color, NF_mark
-						elif column == 'WF':
-							color, marker = WF_color, WF_mark
-						elif column == 'SB':
-							color, marker = SB_color, SB_mark
 
 						x_max_index, y_max, y_min, t = plot_stream_avgs(stream_data, updated_times, 
 														x_max_index, y_max, y_min, marker, color, plot_label)

### 2016-03-08 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Some content added to conclusion section of hose stream report

@@
 Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream.
-This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{sec:monitor_figs}.
+This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
 Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
@@
 
-% --- STOPPED --- %
-
 Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there is no statistically significant difference in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.
-
-**** Add more specific discussion of results ****
 
@@
 \end{enumerate}
+
+A total of eight experiments were conducted to study the impact of different hose stream and application pattern combinations on air movement within residential scale structures.
+
+Three experiments studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure for different ventilation configurations.
+For each of the three experiments, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure.
+The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream.
+Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle aimed at a specified location for 60 seconds with a fully established flow path.
+The streams were compared for six different 60 seconds periods; three times for the monitor aimed at two locations.
+The results from the four monitor experiments suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
+
+In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure.
 

### 2016-03-08 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report drawings

@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout.}
+	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout. Interior dimensions are symmetric across horizontal and vertical centerlines.}
 	\label{fig:east_dimensioned_plan}
@@
 
-Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there is no statistically significant difference in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.
+Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.
 
@@
 \label{chap:summary}
-**** Will briefly restate purpose of experiments, objectives, setup, results etc. ****
-List of main findings:
-\begin{enumerate}
-\item More air movement with NF and WF than SS
-\item More air movement when the hose stream was applied in a pattern that involved moving the nozzle compared to keeping the stream in a fixed position.
-\item No noticeable difference between rotating hose CW or CCW
-\end{enumerate}
 
@@
 In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure.
+Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream.
+In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern.
+Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counter clockwise application patterns.
 
-% ===============
-% = FUTURE WORK =
-% ===============
-\chapter{Future Work}
-\label{chap:Future_Work}
-Need to determine if air movement caused by hose streams has significant impact on flow path/ventilation and fire development in an involved structure.
-May want to compare air velocities to movements caused by PPV fans.
+Overall, the water flow experiments discussed in this report reveal that hose streams can affect air movement within a structure.
+The type of hose stream used and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure.
+These experiments have shown there is a potential for hose streams to affect air flows within a structure during fire scenarios.
+To better quantify the impact of air flows from hose streams on the fire environment, additional fire experiments need to be conducted.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
+	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
 	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
+	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
 	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}

### 2016-03-09 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report, deleted unnecessary figs

@@
 
-Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice~\cite{?}.
+Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 Increasing the angle of the stream allows for a larger area to be covered by water, thus exposing a larger water droplet surface area for heat absorption.
-However, increasing the angle decreases the distance reached by the stream and its penetration power and increases the potential to disrupt thermal layering increases.
+However, increasing the angle decreases the distance reached by the stream and its penetration power and increases the potential to disrupt thermal layering.
 %\textit{Essentials of Fire Fighting} defines 
@@
 %Keith Royer, "Water for Fire Fighting", (Engineering Extension Service, Iowa State University, Ames, Iowa) p. 6 
-In addition to the type of stream pattern used, fire suppression tactics using hose streams can differ in the method used to apply the hose stream.
+In addition to the type of stream pattern used, the method used to apply the hose stream can also vary.
 For example, Royer suggests using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer:ISU}:
@@
 	\item Steam formed by the clockwise rotation has a violent rolling action. Counterclockwise rotation produces steam with an inactive and lazy action.
-	\item A clockweise roation increases the efficiency of water and produces a faster knockdown time than counterclockwise rotation.
+	\item A clockwise roation increases the efficiency of water and produces a faster knockdown time than counterclockwise rotation.
 \end{enumerate}
@@
 \end{enumerate}
-
-Three types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
-The three types of hose stream patterns studied, pictured in Figure~\ref{fig:hose_streams}, were straight stream, narrow fog stream, and wide fog stream.
+Four types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
+Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream patterns.
 Water was flowed into the structure by having the hose in a static, or fixed, position, by moving the hose line left-to-right across the room in a sweeping motion, and by rotating the hose line in both the clockwise and counterclockwise directions.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=\columnwidth]{../Figures/Pictures/hose_streams.pdf}
-% 	\caption[Hose stream patterns used in experiments.]{The three types of stream patterns used during water flow experiments.
-From left to right: straight stream, narrow fog stream, and wide fog stream.}
-% 	\label{fig:hose_streams}
-% \end{figure}
+Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle on air flows in a structure was conducted.
+Images of the four types of hose streams are presented in Fig.~\ref{fig:hose_streams}.
 
 \begin{figure}[!ht]
-	\includegraphics[width=0.55\columnwidth]{../Figures/Pictures/hose_streams_1}
+	\begin{subfigure}[b]{0.45\columnwidth}
+		\centering
+		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/NF_example}
+		\caption{Narrow fog stream}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\columnwidth}
+		\centering
+		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/WF_example}
+		\caption{Wide fog stream}
+	\end{subfigure}
 	\\~\\
-	\includegraphics[width=0.55\columnwidth]{../Figures/Pictures/hose_streams_2}
-	\caption[Hose stream patterns used in experiments.]{The four types of stream patterns used during water flow experiments.
-Top row: narrow fog stream (left) and wide fog stream (right).
-Bottom row: straight stream from combination nozzle (left) and solid stream from smooth bore nozzle (right).}
+	\begin{subfigure}[b]{0.45\columnwidth}
+		\centering
+		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SS_70}
+		\caption{Straight stream from combination nozzle}
+	\end{subfigure}
+	\begin{subfigure}[b]{0.45\columnwidth}
+		\centering
+		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
+		\caption{Solid stream from smooth bore nozzle}
+	\end{subfigure}
+	\caption[Hose stream patterns used during experiments.]{The four types of hose stream patterns used during water flow experiments.}
 	\label{fig:hose_streams}
 \end{figure}
-
-Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle on air flows in a structure was conducted.
 
@@
 The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
-The walls were composed of 16~mm (5/8~in) Type X gypsum board.
+The walls were composed of 16~mm (0.625~in) Type X gypsum board.
 Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
 Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
@@
 The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
-The interior walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
-The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
+The interior walls were protected by 16~mm (0.625~in) fire rated gypsum board, 16~mm (0.625~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
+
+\textit{Should the english units be in fractions instead of decimals? For example, 0.625 --> 5/8. And if decimals, should they all be rounded to same place?}
 
@@
 \label{sec:layout}
-Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively. \textbf{Add N arrow to floor plans}
+Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the East Structure.]{East Structure floor layout. Interior dimensions are symmetric across horizontal and vertical centerlines.}
+	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Interior dimensions are symmetric across horizontal and vertical centerlines.}
 	\label{fig:east_dimensioned_plan}
@@
 For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
-An array of 6 bi-directional probes located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
+An array of six bi-directional probes located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
 A single thermocouple was attached to each bi-directional probes to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
@@
 
-The approximate locations of the bi-directional probes used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup} and Figs.~\ref{fig:flow_path_1}-\ref{fig:flow_path_2}, respectively) found in Section~\ref{sec:exp_procedure}.
+The approximate locations of the bi-directional probes used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
-The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6", contained 6 probes located at distances of 0.30 m, 0.60 m, 0.90 m, 1.20 m, 1.50 m, and 1.80~m below the soffit of the doorway.
-The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained 8 probes located at distances of 0.08 m, 0.34 m, 0.61 m, 0.88 m, 1.15 m, 1.42 m, 1.68 m, and 1.95~m below the soffit of the corresponding doorway.
+The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6", contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
+The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
 
@@
 	\caption[Array of bi-directional probes at interior doorway in East Structure.]{Array of bi-directional probes located at the northeast interior doorway in the East Structure.
-View is looking at the array from Room C.}
+View is looking at the north side of the doorway.}
 	\label{fig:BDPs}
@@
 Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 6.35 cm (2.5 in) cast aluminum pipe with a 0-4.1 MPa (0-600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800 lpm (1250 gpm).
+The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 The total expanded uncertainty was estimated at $\pm10$\%.
-
+% FIND FLOW METER REFERENCE
 \begin{figure}[!ht]
@@
 \label{sec:exp_procedure}
-Every experiment discussed in this report involved discharging water at a known flow rate from a combination nozzle set to flow water in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle in a solid stream pattern.
+Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle in a solid stream pattern.
 Specific doors were opened or closed before and/or during the experiments to change the ventilation in the structure.
 
-A total of seven test series were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at 180~GPM.
+A total of seven tests were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at approximately 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at approximately 180~GPM.
 Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
 
+\textit{Should I present flow rates in GPM only, or LPM (GPM)? What about the tables? As of now, GPM is used, but that goes against the rule of keeping the type of units consistent in a table.}
 \begin{figure}[!ht]
@@
 
-Three different layouts were used for the seven test series.
-The test series conducted in the East Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
-Test 33 used a monitor and combination nozzle to flow water and Test 34 used a combination nozzle attached directly to a handline to flow water.
+Three different structure layouts were used for the seven tests.
+The tests conducted in the East Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
+Test 33 used a monitor and combination nozzle to flow water, and Test 34 used a combination nozzle attached directly to a handline to flow water.
 
 The main difference between the two layouts used for the West Structure experiments is the position of the south side door on the first level.
-Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}) and Tests 17, 19, and 70 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
+Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}), and Tests 17, 19, and 70 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
 Tests 16 and 17 used a combination nozzle attached to a monitor to flow water; Tests 18 and 19 used a combination nozzle attached directly to a handline to flow water; and Test 70 used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
@@
 	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
-The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A6 (blue square).}
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square).}
 	\label{fig:east_setup}
 \end{figure}
+\FloatBarrier
 
@@
 	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A10 (blue square).
-On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
+The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
 	\label{fig:flow_path_1}
@@
 	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of A10 (blue square).
-On the second floor, the stairwell door and north side, west double door were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
+The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
 	\label{fig:flow_path_2}
@@
 \label{sec:monitor_procedure}
-Numerous experiments were conducted during three different test series using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test series, Test 33, occurred in the East Structure, and the two remaining series, Tests 16 and 17, occurred in the West Structure.
-An additional test series, Test 70, used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
+Three different tests were conducted using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
+One test, Test 33, occurred in the East Structure, and the two other tests, Tests 16 and 17, occurred in the West Structure.
+A fourth test, Test 70, used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
 Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
@@
 First, water flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally to a wide fog stream for 30 seconds.
-An identical process was repeated an additional time.
+The procedure was repeated an additional time.
 

### 2016-03-10 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream report

@@
 
-\textit{Should I present flow rates in GPM only, or LPM (GPM)? What about the tables? As of now, GPM is used, but that goes against the rule of keeping the type of units consistent in a table.}
+\textit{Should I present flow rates in GPM only, or LPM (GPM)?
+What about the tables?
+As of now, GPM is used, but that goes against the rule of keeping the type of units consistent in a table.
+Same goes for ``1.75 in'' handline.}
 \begin{figure}[!ht]
@@
 One test, Test 33, occurred in the East Structure, and the two other tests, Tests 16 and 17, occurred in the West Structure.
-A fourth test, Test 70, used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
-Because monitor nozzles are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
+A fourth test, Test 70, was conducted in the West Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
+Because monitors are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
 Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure.
@@
 Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the East Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
-A plan view of the structure's layout annotated with the approximate location of the bi-directional probes array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
+A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
 The procedure for Test 33 was the simplest of all the test procedures.
-First, water flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally to a wide fog stream for 30 seconds.
+First, water was flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally to a wide fog stream for 30 seconds.
 The procedure was repeated an additional time.
@@
 	\endminipage
-	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle during Test 70.]{Straight stream (left) from combination nozzle and solid stream (right) from smooth bore nozzle during Test 70.}
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
 	\label{fig:test_70_pic}
@@
 \label{sec:handline_procedure}
-Numerous experiments were conducted during three different test series using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test series, Test 34, occurred in the East Structure, and the remaining series, Tests 18 and 19, occurred in the West Structure.
-All three test series primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
+Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
+One test, Test 34, occurred in the East Structure, and the remaining tests, Tests 18 and 19, occurred in the West Structure.
+All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
 
 Test 34 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}).
-The layout of the structure was identical to the layout described above in Section~\ref{sec:monitor_procedure} and shown in Fig.~\ref{fig:east_setup}.
-The procedure for Test 34 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
+The layout of the structure was identical to the layout for Test 33, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
+The procedure for Test 34 began by flowing water in a straight stream pattern aimed at the ceiling of Room B for 30 seconds in a fixed position.
 After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds.
-Then, the nozzle was aimed at the south doorway of Room B and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern.
+Then, the nozzle was aimed at the south doorway of Room B, and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern.
 This process was repeated for narrow fog and wide fog streams.
-Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counter-clockwise pattern.
+Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counterclockwise patterns.
 
@@
 Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
-For every experiment during the two tests, the water stream was aimed at the south side wall of the first floor.
-The difference between Tests 18 and 19 is that Test 18 contained the same flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the same flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each test series began by using a straight stream to flow water in a fixed position.
+The water stream was aimed at the south side wall of the first floor during the experiments.
+The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Each test began by using a straight stream to flow water in a fixed position.
 After 60 seconds of water flow, the stairwell door was opened.
@@
 In the graphs, an error bar will represent the estimated uncertainty of the measurement.
-In the tables, the uncertainty will be included in the caption of the table.
+In the tables, the uncertainty will be included in the caption of the table as a percentage enclosed in brackets.
 
@@
 Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{chap:monitor_plots}.
+Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, 33, and 70.
 
@@
 \end{figure}
-
-Excluding the straight stream during Test 33, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination during the monitor experiments.
-Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, 33, and 70.
 
@@
 
-Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream.
-This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
-Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
+Looking at the table and figures, a number of trends can be observed.
+For example, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test 33.
+Also, looking at Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream.
+This trend is also observed above in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and in Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
+Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
 Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
@@
 
-Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counter clockwise rotation during Test 18.
+Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counterclockwise rotation during Test 18.
 Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.
 
@@
 \FloatBarrier
-
-Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity through the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.
 
@@
 For the straight stream, however, significant air movement through the interior doorway was only reached once the stream was applied in a pattern that involved moving the handline.
-Similar to the monitor experiments, the average air velocity through the interior doorway while the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
-
-Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counter clockwise direction for any of three hose streams tested.
+Similar to the monitor experiments, the average air velocity through the interior doorway when the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
+Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
 
@@
 Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle aimed at a specified location for 60 seconds with a fully established flow path.
-The streams were compared for six different 60 seconds periods; three times for the monitor aimed at two locations.
+The streams were compared for six different 60 seconds periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
 The results from the four monitor experiments suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
@@
 In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern.
-Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counter clockwise application patterns.
+Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise application patterns.
 

### 2016-03-16 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
Added channel lists to gas burner exp report

@@
 \label{sec:layout}
-Dimensioned floor plans of the east and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{..//Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
 	\\~\\
@@
 The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
-The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and a 0.18~m (7.25~in) rise and 0.19~m (7.5~in) rise.
+The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
 \FloatBarrier
@@
 
-\subsubsection{East Structure}
+\subsection{East Structure}
 The East Structure was instrumented with five bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, five total heat flux plus radiometer sensor pairs, and two gas sample inlet pipes at the locations shown in Fig.~\ref{fig:east_instrumentation}.
@@
 \end{figure}
+\FloatBarrier
 
 Each bare-bead thermocouple array was composed of eight thermocouples.
-The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
-Three bi-directional probe and solid thermocouple arrays, centered in each exterior doorway of the structure, contained eight probes with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit as shown in Fig.~\ref{fig:BDP_arrays}.
-The fourth bi-directional probe plus solid thermocouple array was located at opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}.
-The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+Three bi-directional probe and solid thermocouple arrays, such as that presented in Fig.~\ref{fig:BDP_arrays}, were centered in each exterior doorway of the structure and contained eight probes.
+The fourth bi-directional probe plus solid thermocouple array was located at the opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}.
+The total heat flux guage/radiometer pairs were set to be aimed to view the ceiling.
+Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing.
+The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.
 
@@
 
-\FloatBarrier
+\clearpage
+% MEASUREMENT TYPE FOR BDPs = 'Velocity' OR 'Pressure'?
+\begin{longtable}[c]{c|lll}
+\caption{East Structure Channel List\label{table:east_channel_list}} \\
+\toprule
+\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} & 
+\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  & 
+\textbf{Channel Location} & 
+\textbf{Measurement Type} \\
+\midrule
+\endhead
+\multirow{13}{*}{\large\textbf{A1}} 
+ & TC\_A1\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A1\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A1\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A1\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A1\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A1\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A1\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A1\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A1	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A1    & 0.15~m above floor   & Radiative heat flux \\
+\cline{2-4}
+ & CO\_A      & 1.22~m above floor   & CO concentration \\
+ & CO2\_A     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_A      & 1.22~m above floor   & O$_2$ concentration \\
+\midrule
+\multirow{10}{*}{\large{\textbf{A2}}}
+ & TC\_A2\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A2\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A2\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A2\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A2\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A2\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A2\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A2\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A2	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A2    & 0.15~m above floor   & Radiative heat flux \\
+\midrule
+ \multirow{10}{*}{\large{\textbf{A3}}}
+ & TC\_A3\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A3\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A3\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A3\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A3\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A3\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A3\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A3\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A3	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A3    & 0.15~m above floor   & Radiative heat flux \\
+% \midrule
+\bottomrule
+\newpage
+\multirow{13}{*}{\large\textbf{A4}} 
+ & TC\_A4\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A4\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A4\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A4\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A4\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A4\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A4\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A4\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A4	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A4    & 0.15~m above floor   & Radiative heat flux \\
+\cline{2-4}
+ & CO\_B      & 1.22~m above floor   & CO concentration \\
+ & CO2\_B     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
+\midrule
+\multirow{10}{*}{\large{\textbf{A5}}}
+ & TC\_A5\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A5\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A5\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A5\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A5\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A5\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A5\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A5\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & HF\_A5	  & 0.15~m above floor   & Total heat flux \\
+ & RAD\_A5    & 0.15~m above floor   & Radiative heat flux \\
+\midrule
+\multirow{16}{*}{\large{\textbf{A7}}}
+ & TC\_A7\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A7\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A7\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A7\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A7\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A7\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A7\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A7\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A7\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A7\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A7\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A7\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A7\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A7\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A7\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A7\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A8}}}
+ & TC\_A8\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A8\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A8\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A8\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A8\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A8\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A8\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A8\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A8\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A8\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A8\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A8\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A8\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A8\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A8\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A8\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{16}{*}{\large{\textbf{A9}}}
+ & TC\_A9\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A9\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A9\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A9\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A9\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A9\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A9\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A9\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A9\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A9\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A9\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A9\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A9\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A9\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A9\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A9\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{3}{*}{\large{\textbf{A10}}}
+ & BDP\_A10\_1 & 0.32~m above ceiling & Velocity \\
+ & BDP\_A10\_2 & 0.32~m above ceiling & Velocity \\
+ & BDP\_A10\_3 & 0.32~m above ceiling & Velocity \\
+\bottomrule
+\end{longtable}
+\clearpage
 
-\subsubsection{West Structure}
+\subsection{West Structure}
 The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
@@
 Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
-\FloatBarrier
+\clearpage
+
+\begin{longtable}[c]{c|lll}
+\caption{West Structure Channel List\label{table:west_channel_list}} \\
+\toprule
+\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} & 
+\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  & 
+\textbf{Channel Location} & 
+\textbf{Measurement Type} \\
+\midrule
+\endhead
+\multirow{11}{*}{\large\textbf{A1}} 
+ & TC\_A1\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A1\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A1\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A1\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A1\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A1\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A1\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A1\_8  & 2.13~m below ceiling & Temperature \\
+\cline{2-4}
+ & CO\_A      & 1.22~m above floor   & CO concentration \\
+ & CO2\_A     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_A      & 1.22~m above floor   & O$_2$ concentration \\
+\midrule
+\multirow{10}{*}{\large{\textbf{A2}}}
+ & TC\_A2\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A2\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A2\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A2\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A2\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A2\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A2\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A2\_8  & 2.13~m below ceiling & Temperature \\
+ \midrule
+ \multirow{10}{*}{\large{\textbf{A3}}}
+ & TC\_A3\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A3\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A3\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A3\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A3\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A3\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A3\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A3\_8  & 2.13~m below ceiling & Temperature \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A4}}}
+ & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{16}{*}{\large{\textbf{A5}}}
+ & TC\_A5\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A5\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A5\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A5\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A5\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A5\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A5\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A5\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A5\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A5\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A5\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A5\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A5\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A5\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A5\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A6}}}
+ & TC\_A6\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A6\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A6\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A6\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A6\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A6\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A6\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A6\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A6\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A6\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A6\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A6\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A6\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A6\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A6\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{8}{*}{\large{\textbf{A7}}}
+ & TC\_A7\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A7\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A7\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A7\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A7\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A7\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A7\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A7\_8  & 2.13~m below ceiling & Temperature \\
+\midrule
+\multirow{8}{*}{\large{\textbf{A8}}}
+ & TC\_A8\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A8\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A8\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A8\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A8\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A8\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A8\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A8\_8  & 2.13~m below ceiling & Temperature \\
+\bottomrule
+\newpage
+\multirow{8}{*}{\large{\textbf{A9}}}
+ & TC\_A9\_1  & 0.03~m below ceiling & Temperature \\
+ & TC\_A9\_2  & 0.30~m below ceiling & Temperature \\
+ & TC\_A9\_3  & 0.61~m below ceiling & Temperature \\
+ & TC\_A9\_4  & 0.91~m below ceiling & Temperature \\
+ & TC\_A9\_5  & 1.22~m below ceiling & Temperature \\
+ & TC\_A9\_6  & 1.52~m below ceiling & Temperature \\
+ & TC\_A9\_7  & 1.83~m below ceiling & Temperature \\
+ & TC\_A9\_8  & 2.13~m below ceiling & Temperature \\
+\midrule
+\multirow{19}{*}{\large\textbf{A10}} 
+ & TC\_A10\_1  & 0.03~m below soffit & Temperature \\
+ & TC\_A10\_2  & 0.30~m below soffit & Temperature \\
+ & TC\_A10\_3  & 0.61~m below soffit & Temperature \\
+ & TC\_A10\_4  & 0.91~m below soffit & Temperature \\
+ & TC\_A10\_5  & 1.22~m below soffit & Temperature \\
+ & TC\_A10\_6  & 1.52~m below soffit & Temperature \\
+ & TC\_A10\_7  & 1.83~m below soffit & Temperature \\
+ & TC\_A10\_8  & 2.13~m below soffit & Temperature \\
+\cline{2-4}
+ & BDP\_A10\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A10\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A10\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A10\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A10\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A10\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A10\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A10\_8 & 2.13~m below soffit  & Velocity \\
+\cline{2-4}
+ & CO\_B      & 1.22~m above floor   & CO concentration \\
+ & CO2\_B     & 1.22~m above floor   & CO$_2$ concentration \\
+ & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A11}}}
+ & TC\_A11\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A11\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A11\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A11\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A11\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A11\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A11\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A11\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A11\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A11\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A11\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A11\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A11\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A11\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A11\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{16}{*}{\large{\textbf{A13}}}
+ & TC\_A13\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A13\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A13\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A13\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A13\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A13\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A13\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A13\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A13\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A13\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A13\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A13\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A13\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A13\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A13\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\newpage
+\multirow{16}{*}{\large{\textbf{A14}}}
+ & TC\_A14\_1  & 0.03~m below soffit  & Temperature \\
+ & TC\_A14\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A14\_3  & 0.61~m below soffit  & Temperature \\
+ & TC\_A14\_4  & 0.91~m below soffit  & Temperature \\
+ & TC\_A14\_5  & 1.22~m below soffit  & Temperature \\
+ & TC\_A14\_6  & 1.52~m below soffit  & Temperature \\
+ & TC\_A14\_7  & 1.83~m below soffit  & Temperature \\
+ & TC\_A14\_8  & 2.13~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A14\_1 & 0.03~m below soffit  & Velocity \\
+ & BDP\_A14\_2 & 0.30~m below soffit  & Velocity \\
+ & BDP\_A14\_3 & 0.61~m below soffit  & Velocity \\
+ & BDP\_A14\_4 & 0.91~m below soffit  & Velocity \\
+ & BDP\_A14\_5 & 1.22~m below soffit  & Velocity \\
+ & BDP\_A14\_6 & 1.52~m below soffit  & Velocity \\
+ & BDP\_A14\_7 & 1.83~m below soffit  & Velocity \\
+ & BDP\_A14\_8 & 2.13~m below soffit  & Velocity \\
+\bottomrule
+\end{longtable}
+\clearpage
 
@@
 
-\chapter{Channel Lists}
-\begin{longtable}[c]{c|lll}
-\caption{East Structure Channel List\label{table:east_channel_list}} \\
-\toprule
-\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} & 
-\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  & 
-\textbf{Channel Location} & 
-\textbf{Measurement Type} \\
-\midrule
-\endhead
-\multirow{13}{*}{\large\textbf{A1}} 
- & TC\_A1\_1  & 0.03~m below ceiling & Temperature \\
- & TC\_A1\_2  & 0.30~m below ceiling & Temperature \\
- & TC\_A1\_3  & 0.61~m below ceiling & Temperature \\
- & TC\_A1\_4  & 0.91~m below ceiling & Temperature \\
- & TC\_A1\_5  & 1.22~m below ceiling & Temperature \\
- & TC\_A1\_6  & 1.52~m below ceiling & Temperature \\
- & TC\_A1\_7  & 1.83~m below ceiling & Temperature \\
- & TC\_A1\_8  & 2.13~m below ceiling & Temperature \\
-\cline{2-4}
- & HF\_A1	  & 0.15~m above floor   & Total heat flux \\
- & RAD\_A1    & 0.15~m above floor   & Radiative heat flux \\
-\cline{2-4}
- & CO\_A      & 1.22~m above floor   & CO concentration \\
- & CO2\_A     & 1.22~m above floor   & CO$_2$ concentration \\
- & O2\_A      & 1.22~m above floor   & O$_2$ concentration \\
-\midrule
-\multirow{10}{*}{\large{\textbf{A2}}}
- & TC\_A2\_1  & 0.03~m below ceiling & Temperature \\
- & TC\_A2\_2  & 0.30~m below ceiling & Temperature \\
- & TC\_A2\_3  & 0.61~m below ceiling & Temperature \\
- & TC\_A2\_4  & 0.91~m below ceiling & Temperature \\
- & TC\_A2\_5  & 1.22~m below ceiling & Temperature \\
- & TC\_A2\_6  & 1.52~m below ceiling & Temperature \\
- & TC\_A2\_7  & 1.83~m below ceiling & Temperature \\
- & TC\_A2\_8  & 2.13~m below ceiling & Temperature \\
-\cline{2-4}
- & HF\_A2	  & 0.15~m above floor   & Total heat flux \\
- & RAD\_A2    & 0.15~m above floor   & Radiative heat flux \\
-\bottomrule
-\newpage
- \multirow{10}{*}{\large{\textbf{A3}}}
- & TC\_A3\_1  & 0.03~m below ceiling & Temperature \\
- & TC\_A3\_2  & 0.30~m below ceiling & Temperature \\
- & TC\_A3\_3  & 0.61~m below ceiling & Temperature \\
- & TC\_A3\_4  & 0.91~m below ceiling & Temperature \\
- & TC\_A3\_5  & 1.22~m below ceiling & Temperature \\
- & TC\_A3\_6  & 1.52~m below ceiling & Temperature \\
- & TC\_A3\_7  & 1.83~m below ceiling & Temperature \\
- & TC\_A3\_8  & 2.13~m below ceiling & Temperature \\
-\cline{2-4}
- & HF\_A3	  & 0.15~m above floor   & Total heat flux \\
- & RAD\_A3    & 0.15~m above floor   & Radiative heat flux \\
-\midrule
-\multirow{13}{*}{\large\textbf{A4}} 
- & TC\_A4\_1  & 0.03~m below ceiling & Temperature \\
- & TC\_A4\_2  & 0.30~m below ceiling & Temperature \\
- & TC\_A4\_3  & 0.61~m below ceiling & Temperature \\
- & TC\_A4\_4  & 0.91~m below ceiling & Temperature \\
- & TC\_A4\_5  & 1.22~m below ceiling & Temperature \\
- & TC\_A4\_6  & 1.52~m below ceiling & Temperature \\
- & TC\_A4\_7  & 1.83~m below ceiling & Temperature \\
- & TC\_A4\_8  & 2.13~m below ceiling & Temperature \\
-\cline{2-4}
- & HF\_A4	  & 0.15~m above floor   & Total heat flux \\
- & RAD\_A4    & 0.15~m above floor   & Radiative heat flux \\
-\cline{2-4}
- & CO\_B      & 1.22~m above floor   & CO concentration \\
- & CO2\_B     & 1.22~m above floor   & CO$_2$ concentration \\
- & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
-\midrule
-\multirow{10}{*}{\large{\textbf{A5}}}
- & TC\_A5\_1  & 0.03~m below ceiling & Temperature \\
- & TC\_A5\_2  & 0.30~m below ceiling & Temperature \\
- & TC\_A5\_3  & 0.61~m below ceiling & Temperature \\
- & TC\_A5\_4  & 0.91~m below ceiling & Temperature \\
- & TC\_A5\_5  & 1.22~m below ceiling & Temperature \\
- & TC\_A5\_6  & 1.52~m below ceiling & Temperature \\
- & TC\_A5\_7  & 1.83~m below ceiling & Temperature \\
- & TC\_A5\_8  & 2.13~m below ceiling & Temperature \\
-\cline{2-4}
- & HF\_A5	  & 0.15~m above floor   & Total heat flux \\
- & RAD\_A5    & 0.15~m above floor   & Radiative heat flux \\
-\bottomrule
-\newpage
-\multirow{16}{*}{\large{\textbf{A7}}}
- & TC\_A7\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A7\_2  & 0.30~m below soffit  & Temperature \\
- & TC\_A7\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A7\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A7\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A7\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A7\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A7\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A7\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A7\_2 & 0.30~m below soffit  & Velocity \\
- & BDP\_A7\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A7\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A7\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A7\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A7\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A7\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
-\multirow{16}{*}{\large{\textbf{A8}}}
- & TC\_A8\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A8\_2  & 0.30~m below soffit  & Temperature \\
- & TC\_A8\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A8\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A8\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A8\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A8\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A8\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A8\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A8\_2 & 0.30~m below soffit  & Velocity \\
- & BDP\_A8\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A8\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A8\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A8\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A8\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A8\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\newpage
-\multirow{16}{*}{\large{\textbf{A9}}}
- & TC\_A9\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A9\_2  & 0.30~m below soffit  & Temperature \\
- & TC\_A9\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A9\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A9\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A9\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A9\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A9\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A9\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A9\_2 & 0.30~m below soffit  & Velocity \\
- & BDP\_A9\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A9\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A9\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A9\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A9\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A9\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\end{longtable}
-
 % \begin{landscape}

### 2016-03-16 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to instrumentation section of gas burner report

--- 2016-03-16 Projects/DelCo_2014_2015/Reports/FDS_Validation_Report/TeX_Files/FDS_Exp_Description_Report.tex
@@
 \begin{figure}[!ht]
-	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/east_structure}
+	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/east_structure}
 	\\~\\
-	\includegraphics[width=5.25in]{../../Hose_Stream_Report/Figures/Pictures/west_structure}
+	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/west_structure}
 	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) test structures.}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=6in]{../../Hose_Stream_Report/Figures/Pictures/TJI_support}
+	\includegraphics[width=6in]{../../Hose_Stream_Tests/Figures/Pictures/TJI_support}
 	\caption[Ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams. View is of the southeast corner of the structure.}
@@
 \FloatBarrier
+
+%SIG FIGS ON DIMENSIONS - ROUND COMMON DECIMALS? Example: 0.625 -> 0.6; 0.75 -> 0.8? They could also be changed to fractions
 
@@
 The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and a 0.18~m (7.25~in) rise and 0.19~m (7.5~in) rise.
-The exterior doors of both structures, the stairwell door on the second level of the West Structure, and a square roof vent with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
+The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent of the East Structure with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
 \FloatBarrier
@@
 
-Three propane burners, each with a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor, were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure and used as the fuel source in each experiment.
+Three propane burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment.
+Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure.
 Propane was supplied to the burners at a measured flow rate during all experiments.
+% INCLUDE HRR CALCULATIONS HERE
+
+\begin{figure}[!ht]
+	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
+	\caption[Three propane burners.]{Three propane burners used as the fuel source for the experiments at a position of 0.6~m (2~ft) off the south and west walls of the East Structure.}
+	\label{fig:burners}
+\end{figure}
+
 \FloatBarrier
@@
 Each bare-bead thermocouple array was composed of eight thermocouples.
-Three bi-directional probe and solid thermocouple arrays, such as that presented in Fig.~\ref{fig:BDP_arrays}, were centered in each exterior doorway of the structure and contained eight probes.
-The fourth bi-directional probe plus solid thermocouple array was located at the opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent as pictured in Fig.~\ref{fig:BDP_arrays}.
-The total heat flux guage/radiometer pairs were set to be aimed to view the ceiling.
+Three bi-directional probe and solid thermocouple arrays were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
+The fourth bi-directional probe, also presented in Fig.~\ref{fig:BDP_arrays}, plus solid thermocouple array was located at the opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent.
+The total heat flux gauge/radiometer pairs were set to be aimed to view the ceiling.
 Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing.
@@
 \subsection{West Structure}
-The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe, and the second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
-The locations of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
+The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, two bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
+The second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, two total heat flux sensor pairs (one facing horizontal and one facing vertical), and one gas sample inlet pipe.
+The location of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
 
@@
 
-The thermocouples in the bare-bead thermocouple arrays were spaced in the same manner as the arrays in the East Structure.
-The bi-directional probe and thermocouple arrays contained 8 probes with spacing identical to the arrays at the exterior doors of the East Structure.
-Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
 \clearpage
@@
  & BDP\_A14\_8 & 2.13~m below soffit  & Velocity \\
+\midrule
+\multirow{2}{*}{\large{\textbf{A16}}}
+ & HF\_2\_H	  & 1~m above floor, facing doorway (horizontal)      & Total heat flux \\
+ & HF\_2\_V   & 1~m above floor, facing ceiling (vertical)        & Total heat flux \\
+\midrule
+\multirow{2}{*}{\large{\textbf{A17}}}
+ & HF\_1\_H	  & 1~m above floor, facing doorway (horizontal)      & Total heat flux \\
+ & HF\_1\_V	  & 1~m above floor, facing ceiling (vertical)        & Total heat flux \\
 \bottomrule

### 2016-03-20 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to gas burner report

@@
 Three bi-directional probe and solid thermocouple arrays were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
-The fourth bi-directional probe, also presented in Fig.~\ref{fig:BDP_arrays}, plus solid thermocouple array was located at the opening of the roof vent and contained three probes located approximately 0.30~m (1~ft), 0.61~m (2~ft), and 0.91~m (3~ft) off the north wall of the vent and centered between the east and west sides of the vent.
+The fourth bi-directional probe and solid thermocouple array, also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent 0.32~m (12.75 in) above the room ceiling and contained three probes centered between the east and west sides of the vent.
+The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}.
 The total heat flux gauge/radiometer pairs were set to be aimed to view the ceiling.
@@
 \midrule
-\multirow{3}{*}{\large{\textbf{A10}}}
- & BDP\_A10\_1 & 0.32~m above ceiling & Velocity \\
- & BDP\_A10\_2 & 0.32~m above ceiling & Velocity \\
- & BDP\_A10\_3 & 0.32~m above ceiling & Velocity \\
+\multirow{6}{*}{\large{\textbf{A10}}}
+ & TC\_A10\_1 & 0.91~m from S side of vent & Temperature \\
+ & TC\_A10\_2 & 0.61~m from S side of vent & Temperature \\
+ & TC\_A10\_3 & 0.30~m from S side of vent & Temperature \\
+\cline{2-4}
+ & BDP\_A10\_1 & 0.91~m from S side of vent & Velocity \\
+ & BDP\_A10\_2 & 0.61~m from S side of vent & Velocity \\
+ & BDP\_A10\_3 & 0.30~m from S side of vent & Velocity \\
 \bottomrule
@@
 \midrule
-\multirow{2}{*}{\large{\textbf{A16}}}
- & HF\_2\_H	  & 1~m above floor, facing doorway (horizontal)      & Total heat flux \\
- & HF\_2\_V   & 1~m above floor, facing ceiling (vertical)        & Total heat flux \\
-\midrule
-\multirow{2}{*}{\large{\textbf{A17}}}
- & HF\_1\_H	  & 1~m above floor, facing doorway (horizontal)      & Total heat flux \\
- & HF\_1\_V	  & 1~m above floor, facing ceiling (vertical)        & Total heat flux \\
+\multirow{3}{*}{\large{\textbf{A16}}}
+ & HF\_2\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
+ & HF\_2\_V   & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
+\midrule
+\multirow{3}{*}{\large{\textbf{A17}}}
+ & HF\_1\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
+ & HF\_1\_V	  & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
 \bottomrule
@@
 \clearpage
+% FIX 'CHANNEL LOCATION' CENTERING FOR A16/17
 
@@
 
+% \begin{table}[!ht]
+% \caption{Event times for Tests 2-4}
+% \begin{tabular}{lccc}
+% \toprule
+%  & \multicolumn{3}{c}{\textbf{\underline{Event Time (mm:ss)}}} \\
+% \textbf{Event} 				& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
+% \midrule
+% Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
+% Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
+% Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
+% West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
+% East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
+% South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
+% Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
+% Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
+% Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
+% \bottomrule
+% \end{tabular}
+% \label{table:Tests_2-4_times}
+% \end{table}
+% RAN FAN AFTER BURNER WAS OFF, BUT DIDN'T INCLUDE BECAUSE BURNERS WERE OFF
+
 \begin{figure}[!ht]
@@
 	\small
-	\begin{tabular}[b]{cc}
+	\begin{tabular}{lccc}
+\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
 \toprule
- 	\textbf{Number} & \textbf{Event Description} \\
- 	\midrule
- 	1-3  & Burners ignited \\
- 	4	 & West double door opened \\
- 	5 	 & East double door opened \\
- 	6	 & South exterior door opened \\
- 	7-9  & Burners extinguished \\
+\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
+\midrule
+(1) Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
+(2) Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
+(3) Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
+(4) West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
+(5) East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
+(6) South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
+(7) Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
+(8) Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
+(9) Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
 \bottomrule
 \end{tabular}
+	% \begin{tabular}[b]{cc}
+ % 	\toprule
+ % 	\textbf{Number} & \textbf{Event Description} \\
+ % 	\midrule
+ % 	1-3  & Burners ignited \\
+ % 	4	 & West double door opened \\
+ % 	5 	 & East double door opened \\
+ % 	6	 & South exterior door opened \\
+ % 	7-9  & Burners extinguished \\
+	% \bottomrule
+	% \end{tabular}
 	\end{flushleft}
@@
 \end{minipage}
-\caption{Test Series 4 layout and sequence of events.}
-\label{fig:east_test_4}
+\caption{Test 2-4 layout and sequence of events.}
+\label{fig:Tests_2-4_layout}
 \end{figure}
@@
 	\small
-	\begin{tabular}[b]{cc}
+\begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}{lccc}
+\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
 \toprule
- 	\textbf{Number} & \textbf{Event Description} \\
- 	\midrule
- 	1-3  & Burners ignited \\
- 	4	 & Roof vent opened \\
- 	5 	 & West double door opened \\
- 	6 	 & East double door opened \\	
- 	7	 & Roof vent closed \\
- 	8-10  & Burners extinguished \\
+\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
+\midrule
+(1) Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
+(2) Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
+(3) Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
+(4) Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
+(5) West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
+(6) East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
+(7) Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
+(7) Center burner off 			&   23:00		  &    44:15		&	   63:30	\\
+(8) Middle burner off 			&   23:20		  &    44:30		&	   63:45	\\
+(9) Corner burner off 			&   23:40		  &    44:45		&	   64:00	\\
+(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
+(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A	\\
+(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A	\\
+(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A	\\
 \bottomrule
 \end{tabular}
+
+	% \begin{tabular}[b]{cc}
+ % 	\toprule
+ % 	\textbf{Number} & \textbf{Event Description} \\
+ % 	\midrule
+ % 	1-3  & Burners ignited \\
+ % 	4	 & Roof vent opened \\
+ % 	5 	 & West double door opened \\
+ % 	6 	 & East double door opened \\	
+ % 	7	 & Roof vent closed \\
+ % 	8-10  & Burners extinguished \\
+	% \bottomrule
+	% \end{tabular}
 	\end{flushleft}

### 2016-03-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Removed section of gas fire experiment report so .tex can compile again
Fixed compile error in .tex file for gas fire experiment report
Updated east exp times/description for gas fire exp report

@@
 
-This report describes eight full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied.
+This report describes nine full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied.
 The experiments were conducted in two structures designed to replicate typical residential dwellings.
@@
 \label{sec:east_procedure}
-Four different tests---Test 2, Test 3, Test 4, and Test 5---were conducted in the East Structure.
-Each series was composed of three experiments that used an identical procedure to change the ventilation in the structure.
-The experiments conducted during Series 4 followed a procedure in which each exterior door was opened to change the ventilation pattern.
-During the experiments in Series 5, each double door was opened and the roof vent was opened and closed.
-Both the roof vent and west double door were opened during each experiment in Series 6.
-Figs.~\ref{fig:east_test_4}--\ref{fig:east_test_6} include a schematic and additional details about the procedures used for the experiments during Series 4--6.
-
-% \begin{table}[!ht]
-% \caption{Event times for Tests 2-4}
-% \begin{tabular}{lccc}
-% \toprule
-%  & \multicolumn{3}{c}{\textbf{\underline{Event Time (mm:ss)}}} \\
-% \textbf{Event} 				& \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
-% \midrule
-% Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
-% Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
-% Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
-% West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
-% East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
-% South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
-% Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
-% Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
-% Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
-% \bottomrule
-% \end{tabular}
-% \label{table:Tests_2-4_times}
-% \end{table}
-% RAN FAN AFTER BURNER WAS OFF, BUT DIDN'T INCLUDE BECAUSE BURNERS WERE OFF
+Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure.
+Tests~2--4 followed an identical order of events.
+Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4.
+The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
+Tests~5 and 6 involved performing a specific set of events three times sequentially.
+To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table).
 
@@
 	\end{tabular}
-	% \begin{tabular}[b]{cc}
- % 	\toprule
- % 	\textbf{Number} & \textbf{Event Description} \\
- % 	\midrule
- % 	1-3  & Burners ignited \\
- % 	4	 & West double door opened \\
- % 	5 	 & East double door opened \\
- % 	6	 & South exterior door opened \\
- % 	7-9  & Burners extinguished \\
-	% \bottomrule
-	% \end{tabular}
+	\\~\\
+	\textit{We ran a PPV fan after each test, but I didn't include it because the burners were off at the time.
+I can include this event if you would like, however.
+Unlike Tests 5 and 6, we did not ignite the burners again after running the PPV fan.}
 	\end{flushleft}
@@
 \end{minipage}
-\caption{Test 2-4 layout and sequence of events.}
+\caption{Tests~2-4 layout and event times.}
 \label{fig:Tests_2-4_layout}
@@
 
-\begin{figure}[!ht]
-\begin{minipage}[b]{0.8\columnwidth}
-	\begin{flushleft}
-	\small
 \begin{figure}[!ht]
@@
 	\toprule
-\multicolumn{1}{c}{\textbf{Event}} & \textbf{Test 2} & \textbf{Test 3} & \textbf{Test 4} \\
+	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
+	\midrule
+	(1)  Corner burner on 			&	3:15	&	12:45	&	21:15	\\
+	(2)  Middle burner on 			&	3:30	&	13:00	&	21:30	\\
+	(3)  Center burner on 			&	3:45	&	13:15	&	21:45	\\
+	(4)  West double door opened 	&	5:15	&   14:45	&	23:15	\\
+	(5)  Roof vent opened 			&	6:45	&	15:45 	&	24:45 	\\
+	(6)  Center burner off 		 	&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
+	(7)  Middle burner off		 	&	8:30	&   17:30	&	\\
+	(8)  Corner burner off 			&	8:45	&   17:45	&	\\
+	(9)  East double door opened	&	9:30	&   18:30	&	27:25	\\
+	(10) Roof vent closed 			&	11:35	&   20:11	&	N/A		\\
+	(11) East double door closed	&	12:02 	&	20:24	&	N/A 	\\
+	(12) West double door closed	&	12:18 	&	20:41	&	N/A		\\
+	\bottomrule
+	\end{tabular}
+	\end{flushleft}
+\end{minipage}
+\begin{minipage}[b]{0.9\columnwidth}
+	\vspace{15pt}
+	\centering
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
+\end{minipage}
+\caption{Test~5 layout and event times.}
+\label{fig:east_test_5}
+\end{figure}
+
+\begin{figure}[!ht]
+\begin{minipage}[b]{0.8\columnwidth}
+	\begin{flushleft}
+	\small
+	\begin{tabular}{lccc}
+	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\toprule
+	\multicolumn{1}{c}{\textbf{Event}} & \textbf{Seq. 1} & \textbf{Seq. 2} & \textbf{Seq. 3} \\
 	\midrule
@@
 	\end{tabular}
-
-	% \begin{tabular}[b]{cc}
- % 	\toprule
- % 	\textbf{Number} & \textbf{Event Description} \\
- % 	\midrule
- % 	1-3  & Burners ignited \\
- % 	4	 & Roof vent opened \\
- % 	5 	 & West double door opened \\
- % 	6 	 & East double door opened \\	
- % 	7	 & Roof vent closed \\
- % 	8-10  & Burners extinguished \\
-	% \bottomrule
-	% \end{tabular}
-	\end{flushleft}
-\end{minipage}
-\begin{minipage}[b]{0.9\columnwidth}
-	\vspace{15pt}
-	\centering
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
-\end{minipage}
-\caption{Test Series 5 layout and sequence of events.}
-\label{fig:east_test_5}
-\end{figure}
-
-\begin{figure}[!ht]
-\begin{minipage}[b]{0.8\columnwidth}
-	\begin{flushleft}
-	\small
-	\begin{tabular}[b]{cc}
- 	\toprule
- 	\textbf{Number} & \textbf{Event Description} \\
- 	\midrule
- 	1-3  & Burners ignited \\
- 	4	 & Roof vent opened \\
- 	5 	 & West double door opened \\
- 	6-8  & Burners extinguished \\
-	\bottomrule
-	\end{tabular}
 	\end{flushleft}
@@
 \end{minipage}
-\caption{Test Series 6 layout and sequence of events.}
+\caption{Test~6 layout and event times.}
 \label{fig:east_test_6}

### 2016-04-04 Projects/DelCo_2012/Report/DelCo_2012.tex
update script and cafs report

@@
 \label{sec:Fire_Suppression}
+
+\subsubsection*{Single Story Structure}
+\label{sec:fire_supp_single}
+
 There were 14 suppression tests conducted in the single story purpose-built concrete structure.
@@
  2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
- 3 & CAF~2 	  &  7/8" Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
- 4 & Water~2  &  7/8" Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
+ 3 & CAF~2 	  &  7/8'' Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+ 4 & Water~2  &  7/8'' Smooth Bore  	&  120~gpm    		& Furniture      & Door            \\
  5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
@@
 
+\subsubsection*{Two Story Structure}
+\label{sec:fire_supp_two}
+
+\begin{table}[!ht]
+\centering
+\footnotesize
+\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
+\begin{tabular}{clllll}
+\toprule[1.5pt]
+Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
+\midrule
+ 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
+ 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
+ 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41c & CAF~9b    &  7/8'' Slub      	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
+\begin{table}[!ht]
+\centering
+\caption{Fire Suppression Results}\label{tab:Test_Results_2}
+\begin{tabular}{lccc}
+\toprule[1.5pt]
+                     & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
+Test 	             & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 1~m (3~ft) Above Floor \\
+\midrule
+CAF~7 Stairell       & 579~$^{\circ}$C - 258~$^{\circ}$C   & 487~$^{\circ}$C - 193~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+Water~7 Stairwell    & 514~$^{\circ}$C - 260~$^{\circ}$C   & 454~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~8a Stairwell     & 474~$^{\circ}$C - 283~$^{\circ}$C   & 422~$^{\circ}$C - 249~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b Stairwell     & 452~$^{\circ}$C - 238~$^{\circ}$C   & 388~$^{\circ}$C - 189~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+Class A~1 Stairwell  & 441~$^{\circ}$C - 304~$^{\circ}$C   & 258~$^{\circ}$C - 234~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
+CAF~9a Stairwell     & 468~$^{\circ}$C - 270~$^{\circ}$C   & 418~$^{\circ}$C - 234~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b Stairwell     & 508~$^{\circ}$C - 336~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
+
 \chapter{Discussion}
@@
 
-\subsection{Gas Cooling}
-\label{sec:desc_Gas_Cooling}
-
-The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83\~{}m (6\~{}ft) below the ceiling.
-During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling.
-It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
-Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
-There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
+\section{Gas Cooling}
+\label{sec:Gas_Cooling_discuss}
 
@@
 
+The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
+During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling.
+It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
+Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
+There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
+
 In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
@@
 The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .
-The average time of flow was 15 s, therefore a total of X kg of water was introduced into each gas cooling experiment.
+The average time of flow was 15~s, therefore a total of X kg of water was introduced into each gas cooling experiment.
 When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
@@
 
-\subsection{Fire Suppression}
-\label{sec:Fuel_Load_Fire_Suppression}
+\section{Fire Suppression}
+\label{sec:Fire_Suppression_discussion}
 

### 2016-04-04 Projects/DelCo_2014_2015/Scripts/bokeh_plot.py

@@ -19,7 +19,7 @@ def mtext(p, x, y, textstr):
 
 # Choose Test Number
 
-current_test = 'Test_50_West_071615'
+current_test = 'Test_41_West_061415'
 
 # Location of experimental data files
 data_dir = '../Experimental_Data/'
@@ -28,8 +28,8 @@ data_dir = '../Experimental_Data/'
 all_times_file = '../Experimental_Data/All_Times.csv'
 
 # Location of scaling conversion files
-scaling_file_west = '../DAQ_Files/West_DelCo_DAQ_Channel_List.csv'
-scaling_file_east = '../DAQ_Files/East_DelCo_DAQ_Channel_List.csv'
+scaling_file_west = '../DAQ_Files/DAQ_Files_2015/West_DelCo_DAQ_Channel_List.csv'
+scaling_file_east = '../DAQ_Files/DAQ_Files_2015/East_DelCo_DAQ_Channel_List.csv'
 
 # Location of test description file
 info_file = '../Experimental_Data/Description_of_Experiments.csv'
@@ -112,28 +112,42 @@ for f in os.listdir(data_dir):
 			# Skip excluded groups listed in test description file
 			if any([substring in group for substring in info['Excluded Groups'][test_name].split('|')]):
 				continue
-			if 'TC A17' == group:
-				axis_scale = 'Y Scale TC'
+			if 'TC A17' == group or 'Heat Flux' == group:
+				if 'TC A17' == group:
+					axis_scale = 'Y Scale TC'
+				else:
+					axis_scale = 'Y Scale HF'
 				output_file(save_dir + test_name + '_' + group.replace(' ', '_') + '.html')
-				p=figure(tools=TOOLS, title = test_name+': '+group, x_axis_label = 'Time (s)', y_axis_label = 'Temperature (C)',plot_width=1000,plot_height=600,
+				p=figure(tools=TOOLS, title = test_name+': '+group, x_axis_label = 'Time (s)',y_axis_label = group,plot_width=1000,plot_height=600,
 					x_range=(0, end_of_test - start_of_test),y_range=(0, np.float(info[axis_scale][test_name])))
 				i=0
 				for channel in channel_groups.get_group(group).index.values:
 					# Skip excluded channels listed in test description file
 					if any([substring in channel for substring in info['Excluded Channels'][test_name].split('|')]):
 						continue
+					if 'TC A17' == group:
+						hover_value = 'Temperature'
[…]

### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
Added description to 2 story CAFs results, new dir to gas exp dir for HRR calculations

@@
 The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests.
-This illustrates the impact of gas cooling, indpendent of suppression agent.
-In several cases rekindling occured, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
+This illustrates the impact of gas cooling, independent of suppression agent.
+In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
 
@@
 \label{sec:fire_supp_two}
+
+There were 7 suppression tests conducted in the two story purpose-built structure.
+All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over puf padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
+Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door.
+The fires were intended to replicate room and contents basement fires typically seen within residential structures.
+Suppression occurred at the basement double doors of the structure.
+Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.
 
@@
 
+Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure.
+The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door.
+These values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
+
 \begin{table}[!ht]
@@
 
+Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, but the differences are not substantial.
+Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
+
 \chapter{Discussion}

### 2016-04-06 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/Burner_HRRs/Scripts/generate_training_data.py

@@ -1,0 +1,277 @@
+import os
+import numpy as np
+import pandas as pd
+import pylab
+import sys
+from scipy import ndimage
+import matplotlib.pyplot as plt
+import cv2
+	# OpenCV installation guides:
+	# Mac: https://jjyap.wordpress.com/2014/05/24/installing-opencv-2-4-9-on-mac-osx-with-python-support/
+	# Ubuntu: http://www.pyimagesearch.com/2015/06/22/install-opencv-3-0-and-python-2-7-on-ubuntu/
+import mahotas as mh
+# import theano				
+# import theano.tensor as T 	
+# import lasagne
+
+# choose type of training data to generate (uncompensated or compensated)
+uncompensated = True
+compensated = False
+
+# read-in files and set directories
+if uncompensated: 
+	info_file = 'test_info_raw.csv'
+	image_dir = 'initial_images/Raw/'			# used to troubleshoot code
+	video_dir = 'flow_meter_videos/Raw/'		# used in actual implementation
+elif compensated: 
+	info_file = 'test_info_compensated.csv'
+	image_dir = 'initial_images/Compensated/'		# used to troubleshoot code
+	video_dir = 'flow_meter_videos/Compensated/'	# used in actual implementation
+
+info = pd.read_csv(info_file, index_col='Test')
+# create dfs to store the dial's value and pixel data from each image
+# final image size and pixel names for integer/fractional dials 
+if uncompensated:
+	int_dial_width = 15
+	int_dial_height = 30
+elif compensated:
+	frac_dial_width = 55
+	frac_dial_height = 75
+	frac_df_headers = ['label']
+	for pixID in range(0, frac_dial_width*frac_dial_height): 
+		frac_df_headers.append('pixel'+str(pixID))
+	frac_img_df = pd.DataFrame(columns=frac_df_headers)
+	int_dial_width = 15
+	int_dial_height = 31
+
+int_df_headers = ['label']
+for pixID in range(0, int_dial_width*int_dial_height): 
+	int_df_headers.append('pixel'+str(pixID))
+int_img_df = pd.DataFrame(columns=int_df_headers)
+
+img_values_ls = []
+
+# for f in os.listdir(image_dir):	# testing out code with captured screenshots
+# 	if f.endswith('.png'):
+for f in os.listdir(video_dir):	# actually generating training data
+	if f.endswith('.mp4'):
+		
+		# to keep things simple initially, only consider videos of same flow meter angle 
[…]

### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
Added fuel description for 2 story structure in CAFs report

@@
 
-The fuel load for two of the experiments consisted of 3 sofas, carpet, padding, and oriented strand board (OSB) paneling along the East, West, and South walls and ceiling.
+The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of oriented strand board (OSB) paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the East, West, and South walls and ceiling.
 The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart.
 The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}.
-In total, this fuel package contains approximately {\bf XXX} fuel consisting of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
+In total, this fuel package was composed of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
 

### 2016-04-06 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edit to cafs repot

@@
 There were 7 suppression tests conducted in the two story purpose-built structure.
-All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over puf padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
+All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
 Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door.
@@
 Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure.
+The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor.
+This remote measurement location proivdes that is isolated from any direct contact from the suppression stream.
 The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door.
-These values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
+The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
 

### 2016-04-07 Projects/DelCo_2012/Report/DelCo_2012.tex
clean up temp data in fire supression section

@@
 \midrule
-CAF~7 Stairell       & 579~$^{\circ}$C - 258~$^{\circ}$C   & 487~$^{\circ}$C - 193~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-Water~7 Stairwell    & 514~$^{\circ}$C - 260~$^{\circ}$C   & 454~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a Stairwell     & 474~$^{\circ}$C - 283~$^{\circ}$C   & 422~$^{\circ}$C - 249~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b Stairwell     & 452~$^{\circ}$C - 238~$^{\circ}$C   & 388~$^{\circ}$C - 189~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
-Class A~1 Stairwell  & 441~$^{\circ}$C - 304~$^{\circ}$C   & 258~$^{\circ}$C - 234~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a Stairwell     & 468~$^{\circ}$C - 270~$^{\circ}$C   & 418~$^{\circ}$C - 234~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b Stairwell     & 508~$^{\circ}$C - 336~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~7 Stairell       & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+Water~7 Stairwell    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~8a Stairwell     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b Stairwell     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+Class A~1 Stairwell  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
+CAF~9a Stairwell     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b Stairwell     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]

### 2016-04-07 Projects/DelCo_2012/Report/DelCo_2012.tex
filled in some gaps in discussion on gas cooling

@@
 In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
-Typically the volumetric flow rate of water was 120 gpm.
-The density of water is 8.3 lbs/gal    therefore the mass flow rate was    .
-The average time of flow was 15~s, therefore a total of X kg of water was introduced into each gas cooling experiment.
+Typically the volumetric flow rate of water was 7.57~L/s (120~gpm).
+The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).
+The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
 When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.

### 2016-04-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added some HRR data for gas burner experiments

@@
 To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table).
+Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.
+
+\begin{table}[!ht]
+\caption{Calculated Heat Release Rate for East Structure Tests}
+% \begin{tabular}{lccccc}
+%  \toprule
+%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
+% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
+% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
+% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
+% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
+% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
+%  \midrule
+% Test 2 				& 360 & 690	& 950 & 680 & 350 \\
+% Test 3				& 360 & 690	& 950 & 680 & 350 \\
+% Test 4				& 360 & 690	& 950 & 680 & 350 \\
+% Test 5 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
+% Test 5 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
+% Test 5 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
+% Test 6 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
+% Test 6 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
+% Test 6 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
+\begin{tabular}{lc}
+ \toprule
+\textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
+\midrule
+Test 2 				& 			\\
+Test 3				& 			\\
+Test 4				& 	949		\\
+Test 5 - Seq. 1		&  	723		\\
+Test 5 - Seq. 2		&  	728		\\
+Test 5 - Seq. 3		&  	724	    \\
+Test 6 - Seq. 1		&  	718	    \\
+Test 6 - Seq. 2		&   714     \\
+Test 6 - Seq. 3		&   716	 	\\
+\bottomrule
+\end{tabular}
+\label{table:HRR_East}
+\end{table}
 
@@
 Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} include a schematic and additional details about the procedures used for the experiments during Series 22 and 24.
+
+\begin{table}[!ht]
+\caption{Calculated Heat Release Rate for West Structure Tests}
+\begin{tabular}{lc}
+ \toprule
+\textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
+\midrule
+Test 22 				& 	756		\\
+Test 23					& 	788		\\
+Test 24					& 	784		\\
+Test 25					&  	785		\\
+\bottomrule
+\end{tabular}
+\label{table:HRR_West}
+\end{table}
 

### 2016-04-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/Burner_HRRs/Scripts/generate_HRR_data.py

@@ -1,0 +1,158 @@
+import os
+import numpy as np
+import pandas as pd
+import pylab
+import sys
+from scipy import ndimage
+import matplotlib.pyplot as plt
+import cv2
+	# OpenCV installation guides:
+	# Mac: https://jjyap.wordpress.com/2014/05/24/installing-opencv-2-4-9-on-mac-osx-with-python-support/
+	# Ubuntu: http://www.pyimagesearch.com/2015/06/22/install-opencv-3-0-and-python-2-7-on-ubuntu/
+import mahotas as mh
+# import theano				
+# import theano.tensor as T 	
+# import lasagne
+
+# choose type of training data to generate (uncompensated or compensated)
+uncompensated = True
+compensated = False
+
+# read-in files and set directories
+results_dir = 'HRR_data/'
+video_dir = 'flow_meter_videos/All/'
+info_file = 'test_info_manual_HRR.csv'
+info = pd.read_csv(info_file, index_col='Test')
+
+HRR_df_headers = ['Time (s)', 'V_flow (ft^3)', 'V_flow (m^3)', 'mdot (kg/s)', 'HRR']
+ft3_to_m3 = 0.3048**3
+density_C3H8 = 2.423 # [kg/m^3]
+delH_C3H8 = 46.0 	# [MJ/kg]
+# density_C3H8 = 582 	# [kg/m^3]
+# delH_C3H8 = 0.42531 	# [MJ/kg]
+
+def new_row_for_df(old_time, current_time, Vold, Vnew):
+	current_time_s = current_time/1000
+	Vdot_ft3 = float(Vnew-Vold)/(current_time_s-old_time)
+	Vdot_m3 = Vdot_ft3*ft3_to_m3
+	mdot = Vdot_m3*density_C3H8
+	HRR = mdot*delH_C3H8
+	new_row = pd.Series([current_time_s, Vdot_ft3, Vdot_m3, 
+		mdot, HRR], index=HRR_df_headers)
+	print 'Saved Dataframe with new row'
+	return new_row, current_time_s, Vnew
+
+# Note: Time = 0 corresponds to video start
+for f in os.listdir(video_dir):	# actually generating training data
+	if f.endswith('.mp4'):
+
+		test_name = f[:-24]
+		if test_name[-1] == '_':
+			test_name = test_name[:-1]
+
+		print '-----' + test_name + '-----'
+		old_img_value = info['Initial Reading'][test_name]
[…]

### 2016-04-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/Burner_HRRs/Scripts/generate_training_data.py

@@ -44,12 +44,11 @@ elif compensated:
 	int_dial_width = 15
 	int_dial_height = 31
 
+# create df to store values
 int_df_headers = ['label']
 for pixID in range(0, int_dial_width*int_dial_height): 
 	int_df_headers.append('pixel'+str(pixID))
 int_img_df = pd.DataFrame(columns=int_df_headers)
-
-img_values_ls = []
 
 # for f in os.listdir(image_dir):	# testing out code with captured screenshots
 # 	if f.endswith('.png'):
@@ -83,7 +82,7 @@ for f in os.listdir(video_dir):	# actually generating training data
 		video_start = info['Video Start'][test_name].split(':')
 		video_end = [int(video_start[0])+test_duration[0], int(video_start[1])+test_duration[1]]
 		video_start_ms = (int(video_start[0])*60+int(video_start[1]))*1000
-		video_end_ms = (video_end[0]*60+video_end[1])*1000
+		video_end_ms = (video_end[0]*60+video_end[1])*1000	
 
 		while(True):
 			# read entire frame as image
@@ -108,10 +107,11 @@ for f in os.listdir(video_dir):	# actually generating training data
 				# cv2.waitKey(0)
 				# pylab.imshow(dial_img)
 				# plt.show()
+				
+				h,w,l = dial_img.shape
 
 				if compensated:
 					# resize image of dial (if necessary)
-					h,w = dial_img.shape[:2]
 					if dial_ID == 0:
 						min_width = frac_dial_width
 						min_height = frac_dial_height
@@ -148,19 +148,20 @@ for f in os.listdir(video_dir):	# actually generating training data
 							print '[ERROR] resize exceeded 5 iterations'
 							sys.exit()
 
-					print w,'x', h
-
-
-				# convert image to ls of RGB values for each pixel and store in df
-
-				# rotate image (if compensated picture and display
-				if uncompensated:
-					dial_img_visible = dial_img
-				else:
 					center = (w/2, h/2)
 					M = cv2.getRotationMatrix2D(center, rotation_angle, 1.0) # (1.0 = scaling factor)
 					dial_img_visible = cv2.warpAffine(dial_img, M, (w,h))
-				cv2.imshow('figure',dial_img_visible)
+
+				# rotate image (if compensated) to view picture
+				else:
+					if h==int_dial_height and w==int_dial_width:
+						dial_img_visible = dial_img
+					else:
+						print 'pixel length and/or width is incorrect'
+						break
+				
+				# display image
[…]

### 2016-04-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated west test descriptions in gas burner report

@@
 \label{sec:east_procedure}
-Five different tests---Test~2, Test~3, Test~4, Test~5, and Test~6---were conducted in the East Structure.
+Five different tests---Tests 2, 3, 4, 5, and 6---were conducted in the East Structure.
 Tests~2--4 followed an identical order of events.
@@
 \label{sec:west_procedure}
-Two different test series---Series 22 and Series 24---were conducted in the West Structure.
-Each series was composed of two experiments that used an identical procedure to change the ventilation in the structure.
-Experiments conducted during Series 22 followed a procedure in which each double door on the first and second floors was opened.
-Experiments from Series 24 followed a sequence of events that involved opening the interior stairwell door, opening the west double door on both the first and second level, and opening the south side exterior door on the second level of the structure.
-Figs.~\ref{fig:west_test_22}~and~\ref{fig:west_test_24} include a schematic and additional details about the procedures used for the experiments during Series 22 and 24.
+Four different tests---Tests~22, 23, 24, and 25---were conducted in the West Structure.
+Tests~22 and 23 followed an identical procedure to change the ventilation.
+Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23.
+Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
 

### 2016-04-20 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Delco Host Stream report
Added disclaimer on units
Intro -added UL FSRI to be consistent with Ref
Replaced fog nozzle with NFPA 1964 terminology.  Need to add to Bib.
Section 2 minor edits to Bi directional probe description and locations
sec 2,2 edits to door positions 3.2 Handline motion  Sec 5
acknowledgements

--- 2016-03-10 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
@@
 
+\vspace{0.2in}
+
+\Flushright{Regarding Non-Metric Units: The policy of the National Institute of Standards and Technology is to
+use metric units in all its published materials. To aid the understanding of this report, in most cases,
+measurements are reported in both metric and U.S.
+customary units.
+There are instances in this study where only the U.S.
+customary units are used as they relate to specific equipment or common fire service vernacular}
+
 \vspace{3in}
@@
 NIST \> National Institute of Standards and Technology \\
+UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute
 \end{tabbing}
@@
 
-One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and how different firefighting tactics affect the fire environment.
-NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
+One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examine how different firefighting tactics affect the fire environment.
+NIST and UL FSRI have conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However, ventilation tactics alone will not result in the complete extinguishment of the fire; fire suppression with hose streams is also needed.
+However, ventilation tactics alone will not result in the extinguishment of the fire; fire suppression with hose streams is also needed.
 
-Fire suppression tactics using hose streams also affect the ventilation in a structure and can impact the movement of smoke and heat through a structure as vents are made to advance the hose line or if ventilation inducing handline tactics are in practice.
+Fire suppression tactics using hose streams also affect the ventilation in a structure and may impact the movement of smoke and heat through a structure.
+As vents are made to advance the hose line or if ventilation inducing handline tactics are in practice, hoselane impacts on venmtilation may be even more significant.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 There exists a multitude of different tools, methods, and techniques used to apply water for fire suppression using hose streams.
-A common type of nozzle that is used to apply water during fire suppression in residential structures is a fog nozzle.
-Most fog nozzles contain an adjustable tip that can be rotated to produce different stream patterns and are therefore often referred to as combination nozzles.
-The types of streams produced by a fog nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}.
-Increasing the angle of the stream allows for a larger area to be covered by water, thus exposing a larger water droplet surface area for heat absorption.
-However, increasing the angle decreases the distance reached by the stream and its penetration power and increases the potential to disrupt thermal layering.
+A common type of nozzle that is used to apply water during fire suppression in residential structures is an adjustable-pattern spray nozzle, commonly referred to as a combination nozzle~\cite{NFPA1964}.
+Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns.
+The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}.
+Increasing the angle of the stream allows for a larger area to be covered by the water spray.
+However, increasing the angle decreases the distance reached by the stream and its penetration power.
 %\textit{Essentials of Fire Fighting} defines 
@@
 In addition to the type of stream pattern used, the method used to apply the hose stream can also vary.
-For example, Royer suggests using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer:ISU}:
+For example, Royer suggested using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer:ISU}:
 \begin{enumerate} 
@@
 \label{sec:objectives}
-This report is concerned with examining the impact of hose stream and application pattern selection on air movement inside a residential structure.
+This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside a full scale test sturctures built to represent residential sized structures.
 Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
@@
 \begin{enumerate}
-	\item Determine which hose stream patterns cause significant air movement in a structure 
-	\item Determine the amount of air movement induced by different stream patterns
-	\item Determine the impact of different stream application patterns on the ventilation in a structure
+	\item Determine which hose stream patterns and application patterns cause significant air movement in a structure 
+	\item Determine the amount of air movement induced by different hose streams and application patterns
+
 \end{enumerate}
@@
 The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
-Sensors were installed throughout the residential-sized test structures to measure air velocity during the water flow experiments.
+Differential pressure and temperature sensors were installed at ventilation points throughout the residential-sized test structures to determine air velocity during the water flow experiments.
 
@@
 The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
-The interior walls were protected by 16~mm (0.625~in) fire rated gypsum board, 16~mm (0.625~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
+The second story walls were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
+The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
 The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
@@
 \textit{Should the english units be in fractions instead of decimals? For example, 0.625 --> 5/8. And if decimals, should they all be rounded to same place?}
+\textit{check dimensions in Fig 2.4, are they consistant with text.  Upstairs is slightly larger and downstairs?}
 
@@
 \label{sec:instrumentation}
-A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{sec:uncertainty}.
-For every experiment, gas velocity at an interior doorway was measured using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
+ For every experiment, gas velocity at an interior doorway was calculated using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
 An array of six bi-directional probes located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
-A single thermocouple was attached to each bi-directional probes to measure the temperature to be used in conjunction with the pressure measurement to derive velocity.
+A single thermocouple was attached to each bi-directional probes to measure the gas temperature to be used in conjunction with the pressure measurement to derive velocity.
 Every thermocouple attached to the bi-directional probes was exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
@@
 
-The approximate locations of the bi-directional probes used to measure air velocity are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
+The approximate locations of the bi-directional probes are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
@@
 The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
+
+A discussion of uncertainties for each type of measurement in this report can be found in Section~\ref{sec:uncertainty}.
 
@@
 
-A total of seven tests were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at approximately 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at approximately 180~GPM.
-Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a hoseline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
+A total of seven scenarios were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at approximately 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at approximately 180~GPM.
+Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a manual hoseline  to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
 
@@
 The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
-The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both first and second floor doors were in the opened position.}
 	\label{fig:flow_path_1}
@@
 The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
-The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both doors were in the opened position.}
+The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both first and second floor doors were in the opened position.}
 	\label{fig:flow_path_2}
@@
 \label{sec:monitor_procedure}
-Three different tests were conducted using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
+Four different scenarios were conducted using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
 One test, Test 33, occurred in the East Structure, and the two other tests, Tests 16 and 17, occurred in the West Structure.
 A fourth test, Test 70, was conducted in the West Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
-Because monitors are designed to flow water from a set position, water was always applied in a fixed position during the monitor experiments.
-Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure.
+The monitors were set to flow water from a fixed position.
+Water was always applied in a fixed position during the monitor experiments.
+Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the stucture.
 
@@
 The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each test began by using a straight stream to flow water in a fixed position.
+Each test began by using a straight stream to flow water in a fixed,horizontal position.
 After 60 seconds of water flow, the stairwell door was opened.
 One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping, clockwise, and counterclockwise application patterns.
+Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping the ceiling, clockwise, and counterclockwise application patterns.
 This entire procedure was repeated using narrow fog and wide fog streams.
@@
 
+The authors would like to thank Roy McLane, Kristopher Overholt, Nicholas Dow, and Jay MCElroy from NIST for their contributions in preparing and conducting these experiments.
+These experiments could not have been conducted without them.
+
+The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments.
+The Delaware county team was under the direction of Kerby Kerber.
+For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection).
+We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
+
+Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
+
 \bibliography{../../../../../Bibliography/FDS_general}

### 2016-04-20 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updates to Hose Stream report

@@
 
-\Flushright{Regarding Non-Metric Units: The policy of the National Institute of Standards and Technology is to
+\flushright{Regarding Non-Metric Units: The policy of the National Institute of Standards and Technology is to
 use metric units in all its published materials. To aid the understanding of this report, in most cases,
@@
 There exists a multitude of different tools, methods, and techniques used to apply water for fire suppression using hose streams.
-A common type of nozzle that is used to apply water during fire suppression in residential structures is an adjustable-pattern spray nozzle, commonly referred to as a combination nozzle~\cite{NFPA1964}.
+A common type of nozzle that is used to apply water during fire suppression in residential structures is an adjustable-pattern spray nozzle, commonly referred to as a combination nozzle~\cite{NFPA_1964}.
 Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns.
@@
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
-The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6", contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
-The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10", contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
+The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6'', contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
+The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10'', contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
 
@@
 Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room.
-The nozzle was aimed at two targets during the series: a ``near" target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far" target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
+The nozzle was aimed at two targets during the series: a ``near'' target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
 The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds.
@@
 	\endminipage \hfill
-	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near" target (top row) and ``far" target (bottom row) during the monitor experiments in the West Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during the monitor experiments in the West Structure.}
 	\label{fig:test_16_17_pic}
@@
 
-Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17.
+Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17.
 The stairwell door was opened for the entire test series.
@@
 	\endminipage
-	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
 	\label{fig:test_70_pic}
@@
 The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each test began by using a straight stream to flow water in a fixed,horizontal position.
+Each test began by using a straight stream to flow water in a fixed, horizontal position.
 After 60 seconds of water flow, the stairwell door was opened.
 One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping the ceiling, clockwise, and counterclockwise application patterns.
+Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns.
 This entire procedure was repeated using narrow fog and wide fog streams.
@@
 \midrule
-\textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
+\textit{Straight} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & -0.3 $\pm0.1$
 \\ \multicolumn{6}{c}{} \\
-\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
+\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & 1.0 $\pm0.2$
 \\ \multicolumn{6}{c}{} \\
-\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
+\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$ & 2.4 $\pm0.4$
 \\ \midrule
@@
 \midrule
-\textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
+\textit{Straight} & 1.7 $\pm0.3$ & 1.9 $\pm0.3$ & \multicolumn{3}{c}{} 
 \\ \multicolumn{6}{c}{} \\
-\textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
+\textit{Smooth Bore} & 1.7 $\pm0.3$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
 \\
@@
 \end{table}
+
+% StdDev Values
+% \midrule
+% \textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
+% \\ \multicolumn{6}{c}{} \\
+% \textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
+% \\ \multicolumn{6}{c}{} \\
+% \textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
+% \\ \midrule
+%  & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
+% \\
+%  & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
+% \\
+% \textbf{Stream} &
+% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
+% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+% \multicolumn{3}{c}{} 
+% \\
+% \midrule
+% \textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
+% \\ \multicolumn{6}{c}{} \\
+% \textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
+% \\
+% \bottomrule
 
@@
 
-Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern, a clockwise rotation, and counterclockwise rotation during Test 18.
+Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 18.
 Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}.
@@
 \\ \midrule
-\textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
+\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
 \\ \multicolumn{7}{c}{} \\
-\textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
+\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
 \\ \multicolumn{7}{c}{} \\
-\textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
+\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ & 2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
 \\ \bottomrule
@@
 \end{table}
+
+% StdDev values
+% \\ \midrule
+% \textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
+% \\ \multicolumn{7}{c}{} \\
+% \textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
+% \\ \multicolumn{7}{c}{} \\
+% \textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
+% \\ \bottomrule
 
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Tests 18 and 19}
+\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 18 and 19}
 \begin{tabular}{lcccc}
@@
 \\ \midrule
-\textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
+\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
 \\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
+\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
 \\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
+\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
 \\ \midrule
@@
 \\ \midrule
-\textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
+\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
 \\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
+\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
 \\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
+\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
 \\ \bottomrule
@@
 \end{table}
+
+% StdDev +- values
+% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+% \\ \midrule
+% \textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
+% \\ \multicolumn{5}{c}{} \\
+% \textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
+% \\ \multicolumn{5}{c}{} \\
+% \textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
+% \\ \midrule
+%  & \multicolumn{4}{c}{\underline{Test 19}}
+% \\
+% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+% \\ \midrule
+% \textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
+% \\ \multicolumn{5}{c}{} \\
+% \textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
+% \\ \multicolumn{5}{c}{} \\
+% \textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
+% \\ \bottomrule
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns.}
+	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns.
+\textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the 2nd floor, west double door}}
 	\label{fig:Test_70_BDP_A10_Avg_All}

### 2016-05-05 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated times and HRRs for gas burner report

@@
 \caption{Calculated Heat Release Rate for East Structure Tests}
-% \begin{tabular}{lccccc}
+\begin{tabular}{lccccc}
+ \toprule
+ 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
+\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
+					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
+					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
+					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
+					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
+ \midrule
+Test 2 				& 338 & 651	& 894 & 634 & 330 \\
+Test 3				& 326 & 650	& 899 & 631 & 326 \\
+Test 4				& 351 & 654	& 902 & 652 & 337 \\
+Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
+Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
+Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
+Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
+Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
+Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
+% \begin{tabular}{lc}
 %  \toprule
-%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
-% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
-% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
-% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
-% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
-% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
+% \textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
 % \midrule
-% Test 2 				& 360 & 690	& 950 & 680 & 350 \\
-% Test 3				& 360 & 690	& 950 & 680 & 350 \\
-% Test 4				& 360 & 690	& 950 & 680 & 350 \\
-% Test 5 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
-% Test 5 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
-% Test 5 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
-% Test 6 - Seq. 1		& 360 & 690	& 950 & 680 & 350 \\
-% Test 6 - Seq. 2		& 360 & 690	& 950 & 680 & 350 \\
-% Test 6 - Seq. 3		& 360 & 690	& 950 & 680 & 350 \\
-\begin{tabular}{lc}
- \toprule
-\textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
-\midrule
-Test 2 				& 			\\
-Test 3				& 			\\
-Test 4				& 	949		\\
-Test 5 - Seq. 1		&  	723		\\
-Test 5 - Seq. 2		&  	728		\\
-Test 5 - Seq. 3		&  	724	    \\
-Test 6 - Seq. 1		&  	718	    \\
-Test 6 - Seq. 2		&   714     \\
-Test 6 - Seq. 3		&   716	 	\\
+% Test 2 				& 			\\
+% Test 3				& 			\\
+% Test 4				& 	949		\\
+% Test 5 - Seq. 1		&  	723		\\
+% Test 5 - Seq. 2		&  	728		\\
+% Test 5 - Seq. 3		&  	724	    \\
+% Test 6 - Seq. 1		&  	718	    \\
+% Test 6 - Seq. 2		&   714     \\
+% Test 6 - Seq. 3		&   716	 	\\
 \bottomrule
@@
 \caption{Calculated Heat Release Rate for West Structure Tests}
-\begin{tabular}{lc}
+% \begin{tabular}{lc}
+%  \toprule
+% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
+% \midrule
+% Test 22 				& 	756		\\
+% Test 23					& 	788		\\
+% Test 24					& 	784		\\
+% Test 25					&  	785		\\
+\begin{tabular}{lccc}
  \toprule
-\textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
-\midrule
-Test 22 				& 	756		\\
-Test 23					& 	788		\\
-Test 24					& 	784		\\
-Test 25					&  	785		\\
+ 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
+\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
+ \midrule
+Test 22				& 	  287		 	&      316			&     	759 	  \\
+Test 23				& 	  395		 	&      526			&     	788 	  \\
+Test 24				& 	  287		 	&      631			&     	787 	  \\
+Test 25				& 	  316		 	&      526			&     	785 	  \\
 \bottomrule
@@
 \begin{figure}[!ht]
+% \begin{minipage}[b]{0.8\columnwidth}
+% 	\begin{flushleft}
+% 	\small
+% 	\begin{tabular}[b]{cc}
+%  	\toprule
+%  	\textbf{Number} & \textbf{Event Description} \\
+%  	\midrule
+%  	1-3  & Burners ignited \\
+%  	4	 & 2nd floor west double door opened \\
+%  	5 	 & 1st floor west double door opened \\
+%  	6	 & 1st floor east double door opened \\
+%  	7 	 & 2nd floor east double door opened \\
+%  	8-10  & Burners extinguished \\
+% 	\bottomrule
+% 	\end{tabular}
+% 	\end{flushleft}
+% \end{minipage}
 \begin{minipage}[b]{0.8\columnwidth}
@@
 	\small
-	\begin{tabular}[b]{cc}
+	\begin{tabular}{lcc}
+	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
 	\toprule
- 	\textbf{Number} & \textbf{Event Description} \\
- 	\midrule
- 	1-3  & Burners ignited \\
- 	4	 & 2nd floor west double door opened \\
- 	5 	 & 1st floor west double door opened \\
- 	6	 & 1st floor east double door opened \\
- 	7 	 & 2nd floor east double door opened \\
- 	8-10  & Burners extinguished \\
+	\multicolumn{1}{c}{\textbf{Event}} 		& \textbf{Test 22}	& \textbf{Test 23} \\
+	\midrule
+	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
+	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
+	(3) Center burner on 					&   8:15	  		&	 4:04		\\
+	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
+	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
+	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
+	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
+	(8) PPV fan on 							&   19:10		  	&    14:01		\\
+	(9) PPV fan off              			&   21:34		  	&    16:30		\\
+	(8) Center burner off 					&   22:00		  	&    17:00		\\
+	(9) Middle burner off 					&   22:00		  	&    17:00		\\
+	(10) Corner burner off 					&   22:00		  	&    17:00		\\
+	% doors were opened, fan was on after burners turned off
 	\bottomrule
@@
 \begin{figure}[!ht]
+% \begin{minipage}[b]{0.8\columnwidth}
+% 	\begin{flushleft}
+% 	\small
+% 	\begin{tabular}[b]{cc}
+%  	\toprule
+%  	\textbf{Number} & \textbf{Event Description} \\
+%  	\midrule
+%  	1-3  & Burners ignited \\
+%  	4	 & Interior stairwell door opened \\
+%  	5 	 & 1st floor west double door opened \\
+%  	6	 & 2nd floor west double door opened \\
+%  	7 	 & 2nd floor south exterior door opened \\
+%  	8-10 & Burners extinguished \\
+% 	\bottomrule
+% 	\end{tabular}
+% 	\end{flushleft}
+% \end{minipage}
 \begin{minipage}[b]{0.8\columnwidth}
@@
 	\small
-	\begin{tabular}[b]{cc}
+	\begin{tabular}{lcc}
+	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
 	\toprule
- 	\textbf{Number} & \textbf{Event Description} \\
- 	\midrule
- 	1-3  & Burners ignited \\
- 	4	 & Interior stairwell door opened \\
- 	5 	 & 1st floor west double door opened \\
- 	6	 & 2nd floor west double door opened \\
- 	7 	 & 2nd floor south exterior door opened \\
- 	8-10 & Burners extinguished \\
+	\multicolumn{1}{c}{\textbf{Event}} 			& \textbf{Test 24}	& \textbf{Test 25} \\
+	\midrule
+	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
+	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
+	(3) Center burner on 						&   3:00	  		&	 2:00		\\
+	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
+	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
+	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
+	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
+	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
+	% (9) PPV fan off              				&   16:30		  	&    		\\
+	(8) Center burner off 						&   15:00		  	&    14:00		\\
+	(9) Middle burner off 						&   15:00		  	&    14:00		\\
+	(10) Corner burner off 						&   15:00		  	&    14:00		\\
+	% doors were opened, fan was on after burners turned off
 	\bottomrule

### 2016-05-05 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/Burner_HRRs/Scripts/generate_training_data.py

@@ -1,280 +1,0 @@
-import os
-import numpy as np
-import pandas as pd
-import pylab
-import sys
-from scipy import ndimage
-import matplotlib.pyplot as plt
-import cv2
-	# OpenCV installation guides:
-	# Mac: https://jjyap.wordpress.com/2014/05/24/installing-opencv-2-4-9-on-mac-osx-with-python-support/
-	# Ubuntu: http://www.pyimagesearch.com/2015/06/22/install-opencv-3-0-and-python-2-7-on-ubuntu/
-import mahotas as mh
-# import theano				
-# import theano.tensor as T 	
-# import lasagne
-
-# choose type of training data to generate (uncompensated or compensated)
-uncompensated = True
-compensated = False
-
-# read-in files and set directories
-if uncompensated: 
-	info_file = 'test_info_raw.csv'
-	image_dir = 'initial_images/Raw/'			# used to troubleshoot code
-	video_dir = 'flow_meter_videos/Raw/'		# used in actual implementation
-elif compensated: 
-	info_file = 'test_info_compensated.csv'
-	image_dir = 'initial_images/Compensated/'		# used to troubleshoot code
-	video_dir = 'flow_meter_videos/Compensated/'	# used in actual implementation
-
-info = pd.read_csv(info_file, index_col='Test')
-# create dfs to store the dial's value and pixel data from each image
-# final image size and pixel names for integer/fractional dials 
-if uncompensated:
-	int_dial_width = 15
-	int_dial_height = 30
-elif compensated:
-	frac_dial_width = 55
-	frac_dial_height = 75
-	frac_df_headers = ['label']
-	for pixID in range(0, frac_dial_width*frac_dial_height): 
-		frac_df_headers.append('pixel'+str(pixID))
-	frac_img_df = pd.DataFrame(columns=frac_df_headers)
-	int_dial_width = 15
-	int_dial_height = 31
-
-# create df to store values
-int_df_headers = ['label']
-for pixID in range(0, int_dial_width*int_dial_height): 
-	int_df_headers.append('pixel'+str(pixID))
-int_img_df = pd.DataFrame(columns=int_df_headers)
-
-# for f in os.listdir(image_dir):	# testing out code with captured screenshots
-# 	if f.endswith('.png'):
-for f in os.listdir(video_dir):	# actually generating training data
-	if f.endswith('.mp4'):
-		
-		# to keep things simple initially, only consider videos of same flow meter angle 
[…]

### 2016-05-07 Projects/DelCo_2012/Report/DelCo_2012.tex
Added Refs and revised Intro and sec 2
Added Cal Poly refs and rewords section 1.  Moved nozzle info to Sec 2.1
and added a 2.0 paragraph

@@
 
-A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but have curtailed the use of these units for this purpose until potential safety implications are better understood.
-This project is expected to produce a better understanding of the effectiveness and safety implication of CAFS for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, forces needed to carry and move hoses streams both horizontally and vertically, and forces need to kink hose lines.
-The conclusions should include much better information regarding the safe and effective use of CAFS for structural firefighting.
+A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAF for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
+This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2012,LaPolla:2012}.
+The research findings are provide information with the potential to improve the safe and effective use of CAFS for structural firefighting.
 
@@
 
-Compressed air foam (CAF) generated with a solution of water and a Class A foam concentrate has been in use by wildland fire agencies since the late 1970’s.
+Compressed air foam (CAF) generated with a solution of water and a Class A foam concentrate has been in use by wildland fire agencies since the late 1970's.
 The wildland fire community found that the Class A foam reduced the surface tension of water, which improved water's ability to penetrate and soak into wildland fuels.
@@
 Departments across the country began to experiment with CAFS systems for use in structural firefighting.
-In most documented cases, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAFS still has not been significantly incorporated into structural firefighting tactics.
-The importance of tactics is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, has now issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations in a structure.
-
-There has never been a comprehensive scientific study on the use of CAFS for structural fire fighting.
-Fire departments have conducted pilot programs to examine implementation and effectiveness of CAFS, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAFS puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
-Much of the data has been generated by people and organizations involved in selling the technology to the fire service and, in many cases, the conclusions are based on a very limited set of instruments or comparisons between water and form that were not designed as scientific experiments.
+In most documented cases, the findings about the effectiveness of the CAF were favorable, yet after decades of fire department trials, CAF has still not been significantly incorporated into structural firefighting tactics.
+This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
+
+There has never been a comprehensive scientific study on the use of CAF for structural fire fighting.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
 
@@
 
-Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle, cooling and penetrating the fuels, mass retention on the fuels and ignition inhibition of the fuels.
+Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle, cooling and penetrating wood based fuels, mass retention on the wood fuels and ignition inhibition of the wood fuels.
 When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
@@
 
-Since Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+\chapter{Experimental Setup}
+
+All of the experiments were conducted at full scale in compartments and structures that were representitive room sizes in a residential occupancy.
+Technical panel members whose departments rountinely use CAF for structural firefighting were invited and present at many of the fire suppression experiments.
+The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
+The data from these experiments were presented to the technical panel member.
+The fire suppression experiments were conducted with a fuel package that included upholstered furniture.
+After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package was composed mainly of wood based materials, as a way to increase the challenge of the suppression experiment.
+After the wood based fuel package experiments were completed, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
+The issue of a larger fire compartment had also been raised durning the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
+In order to accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
+
+The sections below describe the types of experiments, the experimental facilities, instrumentation, and fuel loads.
+Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
+
+\section{Description of Experiments}
+\label{sec:desc_experiments}
+The experimental setup for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
 Baseline operating conditions were agreed upon at the workshop for these experiments (Table~\ref{tab:op_condition}).
-These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
+Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
+The nozzles chosen for these experiments were: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120 gpm.
+These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application.
+The set-up also included 100~ft of 1-3/4~inch hose.
+Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
+The nozzles were controlled and operated via a gate valve from the exterior.
 
@@
 \end{table}
-
-\chapter{Experimental Setup}
-
-\section{Description of Experiments}
-\label{sec:desc_experiments}
-The experimental setup for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
-The nozzles chosen for these experiments were decided upon during the CAFS workshop~\cite{Grant:2011}: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120 gpm.
-These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application.
-The set-up also included 100~ft of 1-3/4~inch hose.
-Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
-The nozzles were controlled and operated via a gate valve from the exterior.
 

### 2016-05-09 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated West structure times in gas burner report

@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
 	\toprule
@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
 	\toprule
@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
 	\toprule
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests~22--23 Data Files} \\
 	\toprule
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
-\end{minipage}
-\caption{Test Series 22 layout and sequence of events.}
+	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
+	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
+\end{minipage}
+\caption{Tests 22--23 layout and event times.}
 \label{fig:west_test_22}
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Test Data File} \\
+	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests 24--25 Data Files} \\
 	\toprule
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
-\end{minipage}
-\caption{Test Series 24 layout and sequence of events.}
+	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
+	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
+\end{minipage}
+\caption{Tests 24--25 layout and event times.}
 \label{fig:west_test_24}

### 2016-05-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated structure names, README for hose stream report exp names

@@
 Each test structure was built on a concrete slab as shown in Fig.~\ref{fig:struct_pics}.
-The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
+The Single Story Structure was designed to simulate a single-story residential structure, and the Two Story Structure was designed to simulate a two-story residential structure.
 The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
@@
 	\includegraphics[width=5.25in]{../Figures/Pictures/west_structure}
-	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) Test Structures.}
+	\caption[North side of the Single Story and Two Story Structures.]{North side of the Single Story (top) and Two Story (bottom) Test Structures.}
 	\label{fig:struct_pics}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Pictures/TJI_support}
-	\caption[TJI-constructed ceiling support of the West Structure.]{First floor ceiling support of the West Structure composed of wood truss joist I-beams.
+	\caption[TJI-constructed ceiling support of the Two Story Structure.]{First floor ceiling support of the Two Story Structure composed of wood truss joist I-beams.
 View is of the southeast corner of the structure.}
@@
 
-The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
+The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
 The second story walls were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
@@
 \label{sec:layout}
-Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the Single Story and Two Story Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Interior dimensions are symmetric across horizontal and vertical centerlines.}
+	\caption[Dimensioned floor plan of the Single Story Structure.]{Dimensioned floor plan of the Single Story Structure. Interior dimensions are symmetric across horizontal and vertical centerlines.}
 	\label{fig:east_dimensioned_plan}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the first and second floors of the West Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Dimensioned floor plan of the first and second floors of the Two Story Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
 	\label{fig:west_dimensioned_plan}
@@
 The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
 
-The exterior doorways of each structure and the stairwell doorway on the second level of the West Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
+The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
 All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
@@
  For every experiment, gas velocity at an interior doorway was calculated using differential pressure transducers connected to bi-directional velocity probes~\cite{McCaffrey:Combustion_and_Flame}.
-An array of six bi-directional probes located at the northeast interior doorway of the East Structure is pictured below in Fig.~\ref{fig:BDPs}.
+An array of six bi-directional probes located at the northeast interior doorway of the Single Story Structure is pictured below in Fig.~\ref{fig:BDPs}.
 A single thermocouple was attached to each bi-directional probes to measure the gas temperature to be used in conjunction with the pressure measurement to derive velocity.
@@
 
-The approximate locations of the bi-directional probes are annotated in the plan views of the East Structure and West Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
+The approximate locations of the bi-directional probes are annotated in the plan views of the Single Story Structure and Two Story Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
-The set of bi-directional probes at the northeast interior doorway of the East Structure, denoted as ``A6'', contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
-The set of bi-directional probes at the interior doorway in the West Structure, denoted as ``A10'', contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
+The set of bi-directional probes at the northeast interior doorway of the Single Story Structure, denoted as ``A6'', contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
+The set of bi-directional probes at the interior doorway in the Two Story Structure, denoted as ``A10'', contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
 
@@
 	\includegraphics[width=3.5in]{../Figures/Pictures/BDPs_east}
-	\caption[Array of bi-directional probes at interior doorway in East Structure.]{Array of bi-directional probes located at the northeast interior doorway in the East Structure.
+	\caption[Array of bi-directional probes at interior doorway in Single Story Structure.]{Array of bi-directional probes located at the northeast interior doorway in the Single Story Structure.
 View is looking at the north side of the doorway.}
@@
 Three different structure layouts were used for the seven tests.
-The tests conducted in the East Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
+The tests conducted in the Single Story Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
 Test 33 used a monitor and combination nozzle to flow water, and Test 34 used a combination nozzle attached directly to a handline to flow water.
 
-The main difference between the two layouts used for the West Structure experiments is the position of the south side door on the first level.
+The main difference between the two layouts used for the Two Story Structure experiments is the position of the south side door on the first level.
 Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}), and Tests 17, 19, and 70 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
-	\caption[Plan view of the East Structure setup for Tests 33 and 34.]{Plan view of the East Structure setup for Tests 33 and 34.
+	\caption[Plan view of the Single Story Structure setup for Tests 33 and 34.]{Plan view of the Single Story Structure setup for Tests 33 and 34.
 The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square).}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
-	\caption[Plan view of the West Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 16 and 18.
+	\caption[Plan view of the Two Story Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 16 and 18.
 The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
-	\caption[Plan view of the West Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the West Structure for Tests 17 and 19.
+	\caption[Plan view of the Two Story Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 17 and 19.
 The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
@@
 Four different scenarios were conducted using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test, Test 33, occurred in the East Structure, and the two other tests, Tests 16 and 17, occurred in the West Structure.
-A fourth test, Test 70, was conducted in the West Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
+One test, Test 33, occurred in the Single Story Structure, and the two other tests, Tests 16 and 17, occurred in the Two Story Structure.
+A fourth test, Test 70, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
 The monitors were set to flow water from a fixed position.
@@
 
-Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the East Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
+Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the Single Story Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
 A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
@@
 % Add flow chart? %
-Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the West Structure to the ceiling of the first floor room.
+Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure to the ceiling of the first floor room.
 The nozzle was aimed at two targets during the series: a ``near'' target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
@@
 	\endminipage \hfill
-	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the West Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during the monitor experiments in the West Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during the monitor experiments in the Two Story Structure.}
 	\label{fig:test_16_17_pic}
@@
 Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test, Test 34, occurred in the East Structure, and the remaining tests, Tests 18 and 19, occurred in the West Structure.
+One test, Test 34, occurred in the Single Story Structure, and the remaining tests, Tests 18 and 19, occurred in the Two Story Structure.
 All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
 
-Test 34 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the East Structure into Room B (Fig.~\ref{fig:test_34_pic}).
+Test 34 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_34_pic}).
 The layout of the structure was identical to the layout for Test 33, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
@@
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the West Structure into the first floor room.
+Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
 The water stream was aimed at the south side wall of the first floor during the experiments.
@@
 	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
-	\caption[North side of West Structure containing a fully established flow path during Test 18.]{North side of West Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 18.}
+	\caption[North side of Two Story Structure containing a fully established flow path during Test 18.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 18.}
 	\label{fig:test_18_pic}

### 2016-05-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated structure names, README for hose stream report exp names

@@
 	(9) PPV fan off              			&   21:34		  	&    16:30		\\
-	(8) Center burner off 					&   22:00		  	&    17:00		\\
-	(9) Middle burner off 					&   22:00		  	&    17:00		\\
-	(10) Corner burner off 					&   22:00		  	&    17:00		\\
+	(10) Center burner off 					&   22:00		  	&    17:00		\\
+	(11) Middle burner off 					&   22:00		  	&    17:00		\\
+	(12) Corner burner off 					&   22:00		  	&    17:00		\\
 	% doors were opened, fan was on after burners turned off
@@
 	% (9) PPV fan off              				&   16:30		  	&    		\\
-	(8) Center burner off 						&   15:00		  	&    14:00		\\
-	(9) Middle burner off 						&   15:00		  	&    14:00		\\
-	(10) Corner burner off 						&   15:00		  	&    14:00		\\
+	(9) Center burner off 						&   15:00		  	&    14:00		\\
+	(10) Middle burner off 						&   15:00		  	&    14:00		\\
+	(11) Corner burner off 						&   15:00		  	&    14:00		\\
 	% doors were opened, fan was on after burners turned off

### 2016-05-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream and gas burner reports

@@
 Fire suppression tactics using hose streams also affect the ventilation in a structure and may impact the movement of smoke and heat through a structure.
-As vents are made to advance the hose line or if ventilation inducing handline tactics are in practice, hoselane impacts on venmtilation may be even more significant.
+As vents are made to advance the hoseline or if ventilation inducing handline tactics are in practice, hose stream impacts on ventilation may be even more significant.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns.
-The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}, a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}, and a wide fog stream produces an angle between 45\SI{}{\degree} to 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF} \textit{(cited 5th edition because that's where I got this info from, I'm assuming I can change it to 6th?)}.
+The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}; a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}; and a wide fog stream produces an angle between 45\SI{}{\degree} and 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF}.
 Increasing the angle of the stream allows for a larger area to be covered by the water spray.
@@
 \begin{enumerate} 
-	\item Clockwise rotation drives most of the heated gases, smoke, and flames away from the nozzle. Counterclockwise rotation does just the opposite.
+	\item Clockwise rotation drives most of the heated gases, smoke, and flames away from the nozzle, while counterclockwise rotation does just the opposite.
 	\item Steam formed by the clockwise rotation has a violent rolling action. Counterclockwise rotation produces steam with an inactive and lazy action.
-	\item A clockwise roation increases the efficiency of water and produces a faster knockdown time than counterclockwise rotation.
+	\item A clockwise rotation increases the efficiency of water and produces a faster knockdown time than counterclockwise rotation.
 \end{enumerate}
@@
 \label{sec:objectives}
-This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside a full scale test sturctures built to represent residential sized structures.
+This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside two full scale test structures built to represent residential sized structures.
 Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
@@
 Four types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
-Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream patterns.
-Water was flowed into the structure by having the hose in a static, or fixed, position, by moving the hose line left-to-right across the room in a sweeping motion, and by rotating the hose line in both the clockwise and counterclockwise directions.
-Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle on air flows in a structure was conducted.
+Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream.
+Water was flowed into the structure by having the hose in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
+Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1~in tip on air flows in a structure was conducted.
 Images of the four types of hose streams are presented in Fig.~\ref{fig:hose_streams}.
@@
 		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/NF_example}
-		\caption{Narrow fog stream}
+		\caption{Narrow fog stream from combination nozzle}
 	\end{subfigure}
@@
 		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/WF_example}
-		\caption{Wide fog stream}
+		\caption{Wide fog stream from combination nozzle}
 	\end{subfigure}
@@
 		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
-		\caption{Solid stream from smooth bore nozzle}
+		\caption{Solid stream from smooth bore nozzle with 1~tip}
 	\end{subfigure}
@@
 To study the impact of different hose stream and application pattern selections on air movement inside a structure, various water flow experiments were conducted in two experimental structures designed to replicate typical residential structures.
-The experiments focused on studying the differences in amount of air movement caused by specific combinations of four different hose stream patterns and four different water application patterns.
+The experiments focused on studying the differences in the amount of air movement caused by specific combinations of four different hose stream patterns and four different water application patterns.
 
@@
 The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
-Differential pressure and temperature sensors were installed at ventilation points throughout the residential-sized test structures to determine air velocity during the water flow experiments.
+Differential pressure and temperature sensors were installed at ventilation points throughout the residential sized test structures to determine air velocity during the water flow experiments.
 
@@
 	\includegraphics[width=5.25in]{../Figures/Pictures/west_structure}
-	\caption[North side of the Single Story and Two Story Structures.]{North side of the Single Story (top) and Two Story (bottom) Test Structures.}
+	\caption[North side of the Single Story and Two Story Structures.]{North side of the Single Story (top) and Two Story (bottom) Structures.}
 	\label{fig:struct_pics}
@@
 
-The interior walls of the first floor of each structure were framed with steel studs set to 0.40~m (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
-The walls were composed of 16~mm (0.625~in) Type X gypsum board.
+The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
+The walls were composed of 16~mm (0.63~in) Type X gypsum board.
 Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 
-The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
 Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
@@
 The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The second story walls were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
-The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
+The walls of the second floor were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
+The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
 The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
-
-\textit{Should the english units be in fractions instead of decimals? For example, 0.625 --> 5/8. And if decimals, should they all be rounded to same place?}
-\textit{check dimensions in Fig 2.4, are they consistant with text.  Upstairs is slightly larger and downstairs?}
 
@@
 \label{sec:layout}
-Dimensioned floor plans of the Single Story and Two Story Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively.
+
+The ceiling height of each structure was approximately 2.4~m (8~ft).
+The interior dimensions of the Single Story Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the Two Story Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
+The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.3~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+
+The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances during tests to change the ventilation pattern of the structure.
+All other doorways in the structures did not contain a door.
+So, in order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
+\clearpage
 
@@
 
-The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
-
-The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances to change the ventilation patterns of the structure.
-All other doorways in the structures did not contain a door, so to close the doorway, a sheet of gypsum board was used to cover the opening and the doorway remained closed for the duration of the test procedure.
-\FloatBarrier
+\clearpage
 
@@
 A single thermocouple was attached to each bi-directional probes to measure the gas temperature to be used in conjunction with the pressure measurement to derive velocity.
-Every thermocouple attached to the bi-directional probes was exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
-Starting with the exposed bead, the thermocouple wire was sheathed in a 3.2~mm (0.13 in) diameter Inconel shield that was 0.76~m (2.5~ft) in length.
+Every thermocouple attached to the bi-directional probes was an exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
+The thermocouple wire was sheathed in a 3.2~mm (0.13 in) diameter Inconel shield that started at the exposed bead and was 0.76~m (2.5~ft) in length.
 
-The approximate locations of the bi-directional probes are annotated in the plan views of the Single Story Structure and Two Story Structure experimental setups (Fig.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) found in Section~\ref{sec:exp_procedure}.
+The approximate locations of the bi-directional probes are annotated in the plan views of the experimental setups for the Single Story and Two Story Structures (Figs.~\ref{fig:east_setup}--\ref{fig:flow_path_2}) in Section~\ref{sec:exp_procedure}.
 To minimize potential measurement errors due to external environmental conditions (i.e., wind), only velocity data measured by bi-directional probes located at interior doorways are considered in this report.
-The set of bi-directional probes at the northeast interior doorway of the Single Story Structure, denoted as ``A6'', contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
+The set of bi-directional probes at the northeast interior doorway of the Single Story Structure, denoted as ``A6'' and pictured in Fig.~\ref{fig:BDPs}, contained six probes located at distances of 0.30~m (1.0~ft), 0.60~m (2.0~ft), 0.90~m (3.0~ft), 1.20~m (3.9~ft), 1.50~m (4.9~ft), and 1.80~m (5.9~ft) below the soffit of the doorway.
 The set of bi-directional probes at the interior doorway in the Two Story Structure, denoted as ``A10'', contained eight probes located at distances of 0.08~m (0.25~ft), 0.34~m (1.1~ft), 0.61~m (2.0~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit of the corresponding doorway.
@@
 Bi-directional probes with pressure transducers and single thermocouples were used to measure the gas velocity.
-Bare-bead Type K thermocouples were co-located with the probe.
-A gas velocity measurement study, examining the doorway flow of pre-flashover compartment fires, yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
+Bare-bead, type K thermocouples were co-located with the probe.
+A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
 The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm18$\%.
@@
 Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
+The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\%  for the pressure sensor~\cite{Akron}.
+The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\% for the pressure sensor~\cite{Akron:2009}.
 The pressure transducer was calibrated with a known analog pressure gauge.
@@
 \label{sec:exp_procedure}
-Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle in a solid stream pattern.
-Specific doors were opened or closed before and/or during the experiments to change the ventilation in the structure.
+Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle with a 1~in tip in a solid stream pattern.
+Specific doors were opened or closed before and/or during the tests to change the ventilation within the structure.
 
-A total of seven scenarios were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~GPM, three used a combination nozzle attached directly to a hoseline to flow water at approximately 120~GPM (Fig.~\ref{fig:monitor+handline}), and one used combination and smooth bore nozzles attached to a monitor to flow water at approximately 180~GPM.
-Experiments that used a monitor to flow water always applied the stream in a fixed position and thus were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a manual hoseline  to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
+A total of seven experiments were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
+Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
 
-\textit{Should I present flow rates in GPM only, or LPM (GPM)?
-What about the tables?
-As of now, GPM is used, but that goes against the rule of keeping the type of units consistent in a table.
-Same goes for ``1.75 in'' handline.}
 \begin{figure}[!ht]
@@
 
-Three different structure layouts were used for the seven tests.
-The tests conducted in the Single Story Structure, Tests 33 and 34, were performed using an identical structure layout, presented in Fig.~\ref{fig:east_setup}.
-Test 33 used a monitor and combination nozzle to flow water, and Test 34 used a combination nozzle attached directly to a handline to flow water.
+Three different structure layouts were used for the seven experiments.
+Tests 1 and 5 were conducted in the Single Story Structure and used the layout shown in Fig.~\ref{fig:east_setup}.
+Test 1 used a monitor and combination nozzle to flow water, and Test 5 used a combination nozzle attached directly to a handline to flow water.
 
-The main difference between the two layouts used for the Two Story Structure experiments is the position of the south side door on the first level.
-Tests 16 and 18 used the configuration with the door opened (Fig.~\ref{fig:flow_path_1}), and Tests 17, 19, and 70 used the configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
-Tests 16 and 17 used a combination nozzle attached to a monitor to flow water; Tests 18 and 19 used a combination nozzle attached directly to a handline to flow water; and Test 70 used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
+Two different layouts were used for experiments conducted in the Two Story Structure.
+The main difference between the two layouts was the position of the south side door on the first level.
+Tests 2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests 3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
+Tests 2 and 3 used a combination nozzle attached to a monitor to flow water; Tests 6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test 4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
-	\caption[Plan view of the Single Story Structure setup for Tests 33 and 34.]{Plan view of the Single Story Structure setup for Tests 33 and 34.
-The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square).}
+	\caption[Plan view of the Single Story Structure setup for Tests 1 and 5.]{Plan view of the Single Story Structure setup for Tests 1 and 5.
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square).
+The north side double doors remained opened for the entire duration of the experiments.}
 	\label{fig:east_setup}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
-	\caption[Plan view of the Two Story Structure setup for Tests 16 and 18.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 16 and 18.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
-The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both first and second floor doors were in the opened position.}
+	\caption[Plan view of the Two Story Structure setup for Tests 2 and 6.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 2 and 6.
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
+The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
 	\label{fig:flow_path_1}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
-	\caption[Plan view of the Two Story Structure setup for Tests 17 and 19.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 17 and 19.
-The approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
-The stairwell door and north side, west double door on the second floor were opened and closed at certain instances during the tests; the flow path was considered fully established when both first and second floor doors were in the opened position.}
+	\caption[Plan view of the Two Story Structure setup for Tests 3 and 7.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 3, 4, and 7.
+The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
+The stairwell door and the west double door on the north side of the second floor were opened and closed at certain instances during the tests.}
 	\label{fig:flow_path_2}
@@
 \label{sec:monitor_procedure}
-Four different scenarios were conducted using a monitor equipped with a combination nozzle to flow water at 120~GPM in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test, Test 33, occurred in the Single Story Structure, and the two other tests, Tests 16 and 17, occurred in the Two Story Structure.
-A fourth test, Test 70, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~GPM in a straight stream and solid stream, respectively.
-The monitors were set to flow water from a fixed position.
-Water was always applied in a fixed position during the monitor experiments.
-Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the stucture.
+Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
+Test 1 occurred in the Single Story Structure, and Tests 2 and 3 occurred in the Two Story Structure.
+A fourth experiment, Test 4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
+The monitor was always set to flow water from a fixed position.
+Thus, the monitor experiments primarily focused on the impact of different hose stream patterns on air movement in a structure and provided a baseline to compare the impact of the motion of the nozzle on the air movement through the structure.
 
-Test 33 utilized a monitor equipped with a combination nozzle to flow water from Room C of the Single Story Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_33_pic}).
-A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway (A6) and the general direction of the fully established flow path for Test 33 can be found in Fig.~\ref{fig:east_setup}.
-The procedure for Test 33 was the simplest of all the test procedures.
-First, water was flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally to a wide fog stream for 30 seconds.
+Test 1 utilized a monitor equipped with a combination nozzle to flow water from Room C of the Single Story Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_1_pic}).
+A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway and the general direction of the fully established flow path for Test 1 can be found in Fig.~\ref{fig:east_setup}.
+The procedure for Test 1 was the simplest of all the test procedures.
+First, water was flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog stream for 30 seconds.
 The procedure was repeated an additional time.
@@
 	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 33.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) pattern aimed at the area above the doorway on the south wall of Room B during Test 33.}
-	\label{fig:test_33_pic}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test 1 in the Single Story Structure.}
+	\label{fig:test_1_pic}
 \end{figure}
@@
 % Add flow chart? %
-Tests 16 and 17 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure to the ceiling of the first floor room.
-The nozzle was aimed at two targets during the series: a ``near'' target, located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target, located approximately 3.7~m (12~ft) from the interior side of the north wall.
-The procedure for each test series began by flowing water in a straight stream pattern at the far target for 60 seconds.
+Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
+The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall.
+The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds.
 After 60 seconds of water flow, the stairwell door was opened.
@@
 Next, the water flow was stopped, the two doors were closed, and the procedure was repeated with the monitor aimed at the near target.
-The entire process was repeated using the narrow fog and wide fog streams.
-Fig.~\ref{fig:test_16_17_pic} contains images of each type of hose stream aimed at the near and far targets.
+This entire process was repeated using the narrow fog and wide fog streams.
+Fig.~\ref{fig:test_2_3_pic} contains images of each type of hose stream aimed at the near and far targets.
 
@@
 	\endminipage \hfill
-	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during the monitor experiments in the Two Story Structure.}
-	\label{fig:test_16_17_pic}
+	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during Tests 2 and 3 in the Two Story Structure.}
+	\label{fig:test_2_3_pic}
 \end{figure}
@@
 
-Test 70 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same near and far targets used during Tests 16 and 17.
-The stairwell door was opened for the entire test series.
-The test series began by flowing water in a straight stream from a combination nozzle aimed at the near target.
+Test 4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests 2 and 3.
+The stairwell door was opened for the entire experiment.
+The test began by flowing water in a straight stream from a combination nozzle aimed at the near target.
 Then, the west double door on the second floor was opened.
-After 60 more seconds of flow, the nozzle was closed to stop flow for 30 seconds.
+After 60 more seconds of flow, the nozzle was closed to stop water flow for 30 seconds.
 The nozzle was opened for 60 seconds and then closed for 30 seconds two additional times.
-Then, the monitor was aimed at the far target, and the procedure was repeated.
-This entire process was repeated using the solid stream from the smooth bore nozzle.
-Fig.~\ref{fig:test_70_pic} contains images of the straight stream from the combination nozzle and solid stream from the smooth bore nozzle during Test 70.
+Next, the monitor was aimed at the far target, and the procedure was repeated.
+This entire process was repeated for the solid stream from the smooth bore nozzle.
+Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test 4.
 
@@
 	\endminipage
-	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 70.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 70.}
-	\label{fig:test_70_pic}
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 4.}
+	\label{fig:test_4_pic}
 \end{figure}
@@
 \label{sec:handline_procedure}
-Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream pattern.
-One test, Test 34, occurred in the Single Story Structure, and the remaining tests, Tests 18 and 19, occurred in the Two Story Structure.
+Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
+One test, Test 5, occurred in the Single Story Structure, and the remaining tests, Tests 6 and 7, occurred in the Two Story Structure.
 All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
 
-Test 34 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_34_pic}).
-The layout of the structure was identical to the layout for Test 33, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
-The procedure for Test 34 began by flowing water in a straight stream pattern aimed at the ceiling of Room B for 30 seconds in a fixed position.
+Test 5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
+The layout of the structure was identical to the layout for Test 1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
+The procedure for Test 5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
 After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds.
 Then, the nozzle was aimed at the south doorway of Room B, and water was applied for 30 seconds in a fixed position followed by 30 seconds in a clockwise pattern.
-This process was repeated for narrow fog and wide fog streams.
-Then, the entire procedure was repeated for the three types of streams being applied in the fixed and counterclockwise patterns.
+The procedure was repeated using a narrow fog stream and a wide fog stream.
+This entire process was repeated for the streams being applied in the fixed and counterclockwise patterns.
 
@@
 	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 34.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 34.}
-	\label{fig:test_34_pic}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 5.}
+	\label{fig:test_5_pic}
 \end{figure}
@@
 % Where was the handline aimed? Add flow chart? %
-Tests 18 and 19 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
+Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
 The water stream was aimed at the south side wall of the first floor during the experiments.
-The difference between Tests 18 and 19 is that Test 18 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, while Test 19 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each test began by using a straight stream to flow water in a fixed, horizontal position.
+Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Each experiment began by using a straight stream to flow water in a fixed, horizontal position.
 After 60 seconds of water flow, the stairwell door was opened.
-One minute later, the north side, west double door on the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the process was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns.
-This entire procedure was repeated using narrow fog and wide fog streams.
-Fig.~\ref{fig:test_18_pic} contains an image of a straight stream pattern being applied during Test 18 with the flow path fully established.
+One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds.
+Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns.
+This entire process was repeated using narrow fog and wide fog streams.
+Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.
 
@@
 	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
-	\caption[North side of Two Story Structure containing a fully established flow path during Test 18.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 18.}
-	\label{fig:test_18_pic}
+	\caption[North side of Two Story Structure containing a fully established flow path during Test 6.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 6.}
+	\label{fig:test_6_pic}
 \end{figure}
@@
 
-Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 16.
-Similar plots of the average measured velocity through the interior doorway for Tests 17, 33, and 70 are presented in Appendix~\ref{chap:monitor_plots}.
-Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 16, 17, 33, and 70.
+Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 2.
+Similar plots of the average measured velocity through the interior doorway for Tests 1, 3, and 4 are presented in Appendix~\ref{chap:monitor_plots}.
+Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 1--4.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through the interior stairwell door (A10) during Test 16 for the three hose stream patterns.}
-	\label{fig:Test_16_BDP_A10_Avg_All}
+	\caption{Average velocity through the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
+	\label{fig:Test_2_BDP_A10_Avg_All}
 \end{figure}
@@
 \toprule
- & \multicolumn{5}{c}{\large ------------------------ 120 GPM ------------------------} 
+ & \multicolumn{5}{c}{\large ------------------------ 120 gpm ------------------------} 
 \\
- & \multicolumn{2}{c}{\underline{Test 16}} & \multicolumn{2}{c}{\underline{Test 17}} & \underline{Test 33}
+ & \underline{Test 1} & \multicolumn{2}{c}{\underline{Test 2}} & \multicolumn{2}{c}{\underline{Test 3}}
 \\
@@
 \textbf{Stream} &
+\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &
 \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
-\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
-\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South Doorway} \\ \end{tabular}
+\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
 \\ 
 \midrule
-\textit{Straight} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & -0.3 $\pm0.1$
+\textit{Straight} & -0.3 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
 \\ \multicolumn{6}{c}{} \\
-\textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$ & 1.0 $\pm0.2$
+\textit{Narrow Fog} & 1.0 $\pm0.2$ & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
 \\ \multicolumn{6}{c}{} \\
-\textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$ & 2.4 $\pm0.4$
+\textit{Wide Fog} & 2.4 $\pm0.4$ & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
 \\ \midrule
- & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
+ & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
 \\
- & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
+ & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
 \\
@@
 % \\ \midrule
-%  & \multicolumn{2}{c}{\large --- 180 GPM ---} & \multicolumn{3}{c}{} 
+%  & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
 % \\
-%  & \multicolumn{2}{c}{\underline{Test 70}} & \multicolumn{3}{c}{} 
+%  & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
 % \\
@@
 Looking at the table and figures, a number of trends can be observed.
-For example, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test 33.
+For example, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test 1.
 Also, looking at Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream.
-This trend is also observed above in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} and in Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
+This trend is also observed above in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and in Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
 Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
-Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
+Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1 in tip produce approximately the same amount of air movement through the interior doorway.
 \FloatBarrier
@@
 
-Fig.~\ref{fig:Test_18_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 18.
-Similar plots of the average measured velocity through the interior doorway for Tests 19 and 34 are presented in Appendix~\ref{chap:handline_plots}.
-Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 34 and Tests 18-19, respectively.
+Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 6.
+Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6-7, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 18 for the three hose stream patterns.}
-	\label{fig:Test_18_BDP_A10_Avg_All}
+	\caption{Average velocity through stairwell door during Test 6 for the three hose stream patterns.}
+	\label{fig:Test_6_BDP_A10_Avg_All}
 \end{figure}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 34}
+\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 5}
 \begin{tabular}{lcccccc}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 18 and 19}
+\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
 \begin{tabular}{lcccc}
 \toprule
- & \multicolumn{4}{c}{\underline{Test 18}}
+ & \multicolumn{4}{c}{\underline{Test 6}}
 \\
@@
 \\ \midrule
- & \multicolumn{4}{c}{\underline{Test 19}}
+ & \multicolumn{4}{c}{\underline{Test 7}}
 \\
@@
 % \\ \midrule
-%  & \multicolumn{4}{c}{\underline{Test 19}}
+%  & \multicolumn{4}{c}{\underline{Test 7}}
 % \\
@@
 
-Nearly every hose stream and application pattern combination using a narrow or wide fog stream during the handline experiments produced significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established.
+Nearly every hose stream and application pattern combination using a narrow or wide fog stream during the handline experiments produced significant air movement, or a gas velocity greater than 0.5~m/s (1.1~mph), through the interior doorway while the flow path was fully established.
 For the straight stream, however, significant air movement through the interior doorway was only reached once the stream was applied in a pattern that involved moving the handline.
 Similar to the monitor experiments, the average air velocity through the interior doorway when the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
-Another important result that can be seen graphically in Figs.~\ref{fig:Test_18_BDP_A10_Avg_All} and \ref{fig:Test_19_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
+Another important result that can be seen graphically in Figs.~\ref{fig:Test_6_BDP_A10_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
 
@@
 The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream.
-Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle aimed at a specified location for 60 seconds with a fully established flow path.
+Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
 The streams were compared for six different 60 seconds periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
@@
 	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through the interior doorway during Test 33 for three hose stream patterns.}
-	\label{fig:Test_33_BDP_A6_Avg_All}
+	\caption{Average velocity through the interior doorway during Test 1 for three hose stream patterns.}
+	\label{fig:Test_1_BDP_A6_Avg_All}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 17 for three hose stream patterns.}
-	\label{fig:Test_17_BDP_A10_Avg_All}
+	\caption{Average velocity through stairwell door during Test 3 for three hose stream patterns.}
+	\label{fig:Test_3_BDP_A10_Avg_All}
 	\end{figure}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 70 for straight stream and smooth bore stream patterns.
+	\caption{Average velocity through stairwell door during Test 4 for straight stream and smooth bore stream patterns.
 \textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the 2nd floor, west double door}}
-	\label{fig:Test_70_BDP_A10_Avg_All}
+	\label{fig:Test_4_BDP_A10_Avg_All}
 	\end{figure}
@@
 	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 34 for three hose stream patterns.}
-	\label{fig:Test_34_BDP_A6_Avg_All}
+	\caption{Average velocity through stairwell door during Test 5 for three hose stream patterns.}
+	\label{fig:Test_5_BDP_A6_Avg_All}
 \end{figure}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 19 for the three hose stream patterns.}
-	\label{fig:Test_19_BDP_A10_Avg_All}
+	\caption{Average velocity through stairwell door during Test 7 for the three hose stream patterns.}
+	\label{fig:Test_7_BDP_A10_Avg_All}
 \end{figure}

### 2016-05-12 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream and gas burner reports

@@
 The total expanded uncertainty was estimated at $\pm10$\%.
-% FIND FLOW METER REFERENCE
+
 \begin{figure}[!ht]
@@
 Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
-Test 1 occurred in the Single Story Structure, and Tests 2 and 3 occurred in the Two Story Structure.
-A fourth experiment, Test 4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
+Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure.
+A fourth experiment, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
 The monitor was always set to flow water from a fixed position.
@@
 
-Test 1 utilized a monitor equipped with a combination nozzle to flow water from Room C of the Single Story Structure to the area above the doorway on the south wall of Room B (Fig.~\ref{fig:test_1_pic}).
-A plan view of the structure's layout annotated with the approximate location of the bi-directional probe array used to measure gas velocity through an interior doorway and the general direction of the fully established flow path for Test 1 can be found in Fig.~\ref{fig:east_setup}.
-The procedure for Test 1 was the simplest of all the test procedures.
-First, water was flowed in a straight stream pattern for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog stream for 30 seconds.
+Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}).
+A plan view of the structure's layout during Test~1 can be found in Fig.~\ref{fig:east_setup}.
+The figure highlights the general direction of the established flow path along with the approximate location of A6, the bi-directional probe array used to measure gas velocity through the northeast interior doorway.
+The procedure for Test~1 was the simplest of all the test procedures.
+First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds.
 The procedure was repeated an additional time.
@@
 
-% Add flow chart? %
 Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
@@
 
-% Where was the handline aimed? Add flow chart? %
 Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
@@
 
-% ===========
-% = RESULTS =
-% ===========
+% ==========================
+% = RESULTS AND DISCUSSION =
+% ==========================
 
@@
 \label{sec:monitor_results}
-
-Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns during Test 2.
-Similar plots of the average measured velocity through the interior doorway for Tests 1, 3, and 4 are presented in Appendix~\ref{chap:monitor_plots}.
-Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and target location combination studied during Tests 1--4.
+Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream during Test~2.
+Similar plots of the average measured velocity through the interior doorway for Tests~1, 3, and 4 are presented in Appendix~\ref{chap:monitor_plots}.
+Additionally, Table~\ref{table:all_mon_vel_avgs} lists the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and target location combination studied during Tests~1--4.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test 2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
 	\label{fig:Test_2_BDP_A10_Avg_All}
@@
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
-\begin{tabular}{lccccc}
+\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
+\begin{tabular}{lcccccccc}
 \toprule
- & \multicolumn{5}{c}{\large ------------------------ 120 gpm ------------------------} 
+ &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
 \\
- & \underline{Test 1} & \multicolumn{2}{c}{\underline{Test 2}} & \multicolumn{2}{c}{\underline{Test 3}}
+ &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
 \\
-% \textbf{Stream} & \textbf{Near} & \textbf{Far} & \textbf{Near} & \textbf{Far} 
-\textbf{Stream} &
-\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &
-\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+\textbf{Stream} & \textbf{Units} &
+\begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
+\begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &  &
 \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}
@@
 \midrule
-\textit{Straight} & -0.3 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
-\\ \multicolumn{6}{c}{} \\
-\textit{Narrow Fog} & 1.0 $\pm0.2$ & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
-\\ \multicolumn{6}{c}{} \\
-\textit{Wide Fog} & 2.4 $\pm0.4$ & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
+\multirow{2}{*}{\textit{Straight}} & 
+\small{m/s}   & -0.3 $\pm0.1$   & & 0.9 $\pm0.2$    & 0.9 $\pm0.2$    & & 0.7 $\pm0.1$    & 0.7 $\pm0.1$ \\ &
+\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\\ \multicolumn{9}{c}{} \\
+\multirow{2}{*}{\textit{Narrow Fog}} & 
+\small{m/s}   &   1.1 $\pm0.2$  & &   0.9 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
+\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\\ \multicolumn{9}{c}{} \\
+\multirow{2}{*}{\textit{Wide Fog}} & 
+\small{m/s}   &   2.4 $\pm0.4$  & &   1.2 $\pm0.2$  & 1.3 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
+\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
 \\ \midrule
- & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
+ &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
 \\
- & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
+ &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
 \\
-\textbf{Stream} &
+\textbf{Stream} & \textbf{Units} &
 \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
-\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
-\multicolumn{3}{c}{} 
+ \multicolumn{2}{c}{\begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular}} &
+\multicolumn{4}{c}{} 
 \\
 \midrule
-\textit{Straight} & 1.7 $\pm0.3$ & 1.9 $\pm0.3$ & \multicolumn{3}{c}{} 
-\\ \multicolumn{6}{c}{} \\
-\textit{Smooth Bore} & 1.7 $\pm0.3$ & 2.0 $\pm0.4$ & \multicolumn{3}{c}{}
+\multirow{2}{*}{\textit{Straight}} &
+\small{m/s}   &   1.7 $\pm0.3$   & \multicolumn{2}{c}{1.9 $\pm0.3$}  & \multicolumn{4}{c}{} \\ &
+\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
+\\ \multicolumn{9}{c}{} \\
+\multirow{2}{*}{\textit{Smooth Bore}} &
+\small{m/s}   &   1.7 $\pm0.3$  &  \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
+\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
 \\
+% \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
+% \begin{tabular}{@{}c@{}} -0.3 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
+% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
+% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
+% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
+% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} 
+% \\ \multicolumn{9}{c}{} \\
+% \textit{Narrow Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
+% 1.1 $\pm0.2$ & & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & & 0.8 $\pm0.1$ & 0.7 $\pm0.1$
+% \\ \multicolumn{9}{c}{} \\
+% \textit{Wide Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
+% 2.4 $\pm0.4$ & & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
+% \\ \midrule
+%  &  & \multicolumn{3}{c}{\large --- 180 gpm ---} & \multicolumn{4}{c}{} 
+% \\
+%  &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
+% \\
+% \textbf{Stream} & \textbf{Units} &
+% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &  &
+% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
+% \multicolumn{4}{c}{} 
+% \\
+% \midrule
+% \textit{Straight} &  \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
+% 1.7 $\pm0.3$ &  & 1.9 $\pm0.3$ & \multicolumn{4}{c}{} 
+% \\ \multicolumn{9}{c}{} \\
+% \textit{Smooth Bore} & 
+% 1.7 $\pm0.3$ &  & 2.0 $\pm0.4$ & \multicolumn{4}{c}{}
+% \\
 \bottomrule
@@
 
-% StdDev Values
-% \midrule
-% \textit{Straight} & 0.9 $\pm0.1$ & 0.9 $\pm0.2$ & 0.7 $\pm0.1$ & 0.7 $\pm0.2$ & -0.3 $\pm0.1$
-% \\ \multicolumn{6}{c}{} \\
-% \textit{Narrow Fog} & 0.9 $\pm0.2$ & 1.4 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.1$ & 1.0 $\pm0.6$
-% \\ \multicolumn{6}{c}{} \\
-% \textit{Wide Fog} & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.2$ & 2.4 $\pm0.3$
-% \\ \midrule
-%  & \multicolumn{2}{c}{\large --- 180 gpm ---} & \multicolumn{3}{c}{} 
-% \\
-%  & \multicolumn{2}{c}{\underline{Test 4}} & \multicolumn{3}{c}{} 
-% \\
-% \textbf{Stream} &
-% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} & 
-% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
-% \multicolumn{3}{c}{} 
-% \\
-% \midrule
-% \textit{Straight} & 1.7 $\pm0.4$ & 1.9 $\pm0.5$ & \multicolumn{3}{c}{} 
-% \\ \multicolumn{6}{c}{} \\
-% \textit{Smooth Bore} & 1.7 $\pm0.5$ & 2.0 $\pm0.5$ & \multicolumn{3}{c}{}
-% \\
-% \bottomrule
-
 Looking at the table and figures, a number of trends can be observed.
-For example, there was significant air movement (gas velocity greater than 0.5 m/s) through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test 1.
-Also, looking at Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream.
-This trend is also observed above in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and in Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
+For example, there was significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1.
+Looking at Table~\ref{table:all_mon_vel_avgs}, the narrow fog and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream.
+This trend can also be seen graphically in Fig.~\ref{fig:Test_2_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_1_BDP_A6_Avg_All}~and~\ref{fig:Test_3_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}.
 Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
-Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1 in tip produce approximately the same amount of air movement through the interior doorway.
+Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
 \FloatBarrier
@@
 \label{sec:handline_results}
-
-Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average measured velocity through the interior stairwell door (A10) for the straight, narrow fog, and wide fog stream patterns being applied in a fixed position, a sweeping pattern (back and forth left-to-right), a clockwise rotation, and counterclockwise rotation during Test 6.
+Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test 6.
 Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
-Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probe array at the interior doorway when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6-7, respectively.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6 and 7, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 6 for the three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test 6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 6 for the three hose stream patterns.}
 	\label{fig:Test_6_BDP_A10_Avg_All}
@@
 
-% #######################
-% # East Handline Table #
-% #######################
-
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) through interior doorway when flow path was fully established for Test 5}
-\begin{tabular}{lcccccc}
+\caption{Average gas velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
+\begin{tabular}{lccccccc}
 \toprule
- & \multicolumn{3}{c}{\underline{Room A}} & \multicolumn{3}{c}{\underline{Room B Ceiling}}
+ & \multicolumn{3}{c}{\underline{Room A}} &  & \multicolumn{3}{c}{\underline{Room B Ceiling}}
 \\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} &  & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
-\\ \multicolumn{7}{c}{} \\
-\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
-\\ \multicolumn{7}{c}{} \\
-\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ & 2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
+\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ &  &
+-0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
+\\ \multicolumn{8}{c}{} \\
+\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ &  & 
+0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
+\\ \multicolumn{8}{c}{} \\
+\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ &  & 
+2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
 \\ \bottomrule
@@
 
-% StdDev values
-% \\ \midrule
-% \textit{Straight} & 0.2 $\pm0.3$ & 0.6 $\pm0.2$ & 0.8 $\pm0.3$ & -0.1 $\pm0.1$ & 0.5 $\pm0.3$ & 0.5 $\pm0.2$
-% \\ \multicolumn{7}{c}{} \\
-% \textit{Narrow Fog} & 1.7 $\pm0.4$ & 1.8 $\pm0.2$ & 1.6 $\pm0.1$ & 0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.2$
-% \\ \multicolumn{7}{c}{} \\
-% \textit{Wide Fog} & 1.9 $\pm0.2$ & 2.1 $\pm0.1$ & 2.2 $\pm0.1$ & 2.1 $\pm0.3$ & 2.3 $\pm0.1$ & 2.6 $\pm0.1$
-% \\ \bottomrule
-
-% #######################
-% # West Handline Table #
-% #######################
-
 \begin{table}[!ht]
-\caption{Average air velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
+\caption{Average gas velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
 \begin{tabular}{lcccc}
@@
 \end{table}
-
-% StdDev +- values
-% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-% \\ \midrule
-% \textit{Straight} & -0.2 $\pm0.3$ & 0.5 $\pm0.2$ & 0.7 $\pm0.2$ & 0.7 $\pm0.2$
-% \\ \multicolumn{5}{c}{} \\
-% \textit{Narrow Fog} & 0.4 $\pm0.3$ & 1.0 $\pm0.2$ & 0.8 $\pm0.2$ & 1.0 $\pm0.3$
-% \\ \multicolumn{5}{c}{} \\
-% \textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.3$ & 0.9 $\pm0.3$ & 0.8 $\pm0.3$
-% \\ \midrule
-%  & \multicolumn{4}{c}{\underline{Test 7}}
-% \\
-% \textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
-% \\ \midrule
-% \textit{Straight} & -0.1 $\pm0.1$ & 0.5 $\pm0.2$ & 0.7 $\pm0.1$ & 0.6 $\pm0.2$
-% \\ \multicolumn{5}{c}{} \\
-% \textit{Narrow Fog} & 1.2 $\pm0.3$ & 1.2 $\pm0.3$ & 1.2 $\pm0.4$ & 1.2 $\pm0.2$
-% \\ \multicolumn{5}{c}{} \\
-% \textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
-% \\ \bottomrule
-
 \FloatBarrier
 
-Nearly every hose stream and application pattern combination using a narrow or wide fog stream during the handline experiments produced significant air movement, or a gas velocity greater than 0.5~m/s (1.1~mph), through the interior doorway while the flow path was fully established.
-For the straight stream, however, significant air movement through the interior doorway was only reached once the stream was applied in a pattern that involved moving the handline.
-Similar to the monitor experiments, the average air velocity through the interior doorway when the flow path was established was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
-Another important result that can be seen graphically in Figs.~\ref{fig:Test_6_BDP_A10_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} and in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
+With the exception of the narrow fog stream in the fixed position during Test 6, every hose stream and application pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
+For the straight stream, however, significant air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
+Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
+Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
+The similarities in air flow produced by the clockwise and counterclockwise application patterns can also be seen graphically in Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_5_BDP_A6_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} in Appendix~\ref{chap:handline_plots}.
 
@@
 	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through the interior doorway during Test 1 for three hose stream patterns.}
+	\caption[Average gas velocity through the interior doorway during Test 1 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior doorway (A6) during Test 1 for the three hose stream patterns.}
 	\label{fig:Test_1_BDP_A6_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 3 for three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test 3 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 3 for the three hose stream patterns.}
 	\label{fig:Test_3_BDP_A10_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 4 for straight stream and smooth bore stream patterns.
-\textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the 2nd floor, west double door}}
+	\caption[Average gas velocity through the interior stairwell door during Test 4 for the straight stream and smooth bore stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 4 for the straight stream and smooth bore stream patterns.
+\textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the west double door on the second story.}}
 	\label{fig:Test_4_BDP_A10_Avg_All}

### 2016-05-12 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to hose stream and gas burner reports

--- 2016-05-09 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (February 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (May 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 
+\subsubsection{Gas Flow Meter}
+
 \clearpage
@@
 \label{sec:east_procedure}
-Five different tests---Tests 2, 3, 4, 5, and 6---were conducted in the East Structure.
+Five different tests, Tests 2--6, were conducted in the East Structure.
 Tests~2--4 followed an identical order of events.
@@
 Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
-% \begin{tabular}{lc}
-%  \toprule
-% \textbf{Test}  		& 	\textbf{Heat Release Rate (kW)} \\
-% \midrule
-% Test 2 				& 			\\
-% Test 3				& 			\\
-% Test 4				& 	949		\\
-% Test 5 - Seq. 1		&  	723		\\
-% Test 5 - Seq. 2		&  	728		\\
-% Test 5 - Seq. 3		&  	724	    \\
-% Test 6 - Seq. 1		&  	718	    \\
-% Test 6 - Seq. 2		&   714     \\
-% Test 6 - Seq. 3		&   716	 	\\
 \bottomrule
@@
 	\midrule
-	(1) Corner burner on 			& 	21:00		  &		4:00		&		4:00	  \\
-	(2) Middle burner on 			&   24:00		  &		7:00		&		7:00	  \\
-	(3) Center burner on 			&   27:00		  &	   10:00		&	   10:00	  \\
-	(4) West double door opened 	&   28:00		  &    11:00		&	   11:00	  \\
-	(5) East double door opened 	&   30:00		  &    13:00		&	   13:00	  \\
-	(6) South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
-	(7) Center burner off 			&   33:00		  &    17:00		&	   17:00	  \\
-	(8) Middle burner off 			&   35:00		  &    19:00		&	   19:00	  \\
-	(9) Corner burner off 			&   37:00		  &    21:00		&	   21:00	  \\
+	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
+	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
+	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
+	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
+	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
+	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
+	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
+	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
+	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
+	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
+	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
 	\bottomrule
 	\end{tabular}
-	\\~\\
-	\textit{We ran a PPV fan after each test, but I didn't include it because the burners were off at the time.
-I can include this event if you would like, however.
-Unlike Tests 5 and 6, we did not ignite the burners again after running the PPV fan.}
 	\end{flushleft}
@@
 	\midrule
-	(1)  Corner burner on 			&	3:15	&	12:45	&	21:15	\\
-	(2)  Middle burner on 			&	3:30	&	13:00	&	21:30	\\
-	(3)  Center burner on 			&	3:45	&	13:15	&	21:45	\\
-	(4)  West double door opened 	&	5:15	&   14:45	&	23:15	\\
-	(5)  Roof vent opened 			&	6:45	&	15:45 	&	24:45 	\\
-	(6)  Center burner off 		 	&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
-	(7)  Middle burner off		 	&	8:30	&   17:30	&	\\
-	(8)  Corner burner off 			&	8:45	&   17:45	&	\\
-	(9)  East double door opened	&	9:30	&   18:30	&	27:25	\\
-	(10) Roof vent closed 			&	11:35	&   20:11	&	N/A		\\
-	(11) East double door closed	&	12:02 	&	20:24	&	N/A 	\\
-	(12) West double door closed	&	12:18 	&	20:41	&	N/A		\\
+	% Some door(s) opened before test start according to notes, no sign from data/limited videos
+	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
+	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
+	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
+	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
+	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
+	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
+	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
+	~(7)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
+	~(8)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
+	~(9)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
+	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
+	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
+	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
+	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
 	\bottomrule
@@
 	\midrule
-	(1) Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
-	(2) Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
-	(3) Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
-	(4) Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
-	(5) West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
-	(6) East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
-	(7) Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
-	(7) Center burner off 			&   23:00		  &    44:15		&	   63:30	\\
-	(8) Middle burner off 			&   23:20		  &    44:30		&	   63:45	\\
-	(9) Corner burner off 			&   23:40		  &    44:45		&	   64:00	\\
-	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
-	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
-	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
-	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
+	~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
+	~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
+	~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
+	~(4)~  West double door opened 	&	5:15	&   14:45	&	23:15	\\
+	~(5)~  Roof vent opened 		&	6:45	&	15:45 	&	24:45 	\\
+	~(6)~  Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
+	~(7)~  Middle burner off		&	8:30	&   17:30	&	\\
+	~(8)~  Corner burner off 		&	8:45	&   17:45	&	\\
+	~(9)~  East double door opened	&	9:30	&   18:30	&	27:25	\\
+	(10) Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
+	(11) East double door closed	&	12:02 	&	20:11	&	N/A 	\\
+	(12) West double door closed	&	12:18 	&	20:24	&	N/A		\\
 	\bottomrule
@@
 Test 24				& 	  287		 	&      631			&     	787 	  \\
-Test 25				& 	  316		 	&      526			&     	785 	  \\
+Test 25				& 	  N/A		 	&      N/A			&     	785 	  \\
 \bottomrule
@@
 \begin{figure}[!ht]
-% \begin{minipage}[b]{0.8\columnwidth}
-% 	\begin{flushleft}
-% 	\small
-% 	\begin{tabular}[b]{cc}
-%  	\toprule
-%  	\textbf{Number} & \textbf{Event Description} \\
-%  	\midrule
-%  	1-3  & Burners ignited \\
-%  	4	 & 2nd floor west double door opened \\
-%  	5 	 & 1st floor west double door opened \\
-%  	6	 & 1st floor east double door opened \\
-%  	7 	 & 2nd floor east double door opened \\
-%  	8-10  & Burners extinguished \\
-% 	\bottomrule
-% 	\end{tabular}
-% 	\end{flushleft}
-% \end{minipage}
 \begin{minipage}[b]{0.8\columnwidth}
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests~22--23 Data Files} \\
+	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
 	\toprule
@@
 	\midrule
-	(1) Corner burner on 					& 	9:05 			&	 3:45		\\
-	(2) Middle burner on 					&   8:45	  		&	 3:55		\\
-	(3) Center burner on 					&   8:15	  		&	 4:04		\\
-	(4) 2nd floor west double door opened 	&   11:30	  		&    6:00		\\
-	(5) 1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
-	(6) 1st floor east double door opened 	&   15:45		  	&    10:00		\\
-	(7) 2nd floor east double door opened	&   18:00		  	&    12:08		\\
-	(8) PPV fan on 							&   19:10		  	&    14:01		\\
-	(9) PPV fan off              			&   21:34		  	&    16:30		\\
-	(8) Center burner off 					&   22:00		  	&    17:00		\\
-	(9) Middle burner off 					&   22:00		  	&    17:00		\\
-	(10) Corner burner off 					&   22:00		  	&    17:00		\\
-	% doors were opened, fan was on after burners turned off
+	~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
+	~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
+	~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
+	~(4)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
+	~(5)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
+	~(6)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
+	~(7)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
+	~(8)~  PPV fan on 							&   19:10		  	&    14:01		\\
+	~(9)~  PPV fan off              			&   21:34		  	&    16:30		\\
+	(10) All burners off 						&   22:00		  	&    17:00		\\
+	(11) 2nd floor south exterior door opened 	&   23:19		  	&    18:01		\\
+	(12) PPV fan on 	 						&   26:00		  	&    19:30		\\
+	(13) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
 	\bottomrule
@@
 	\centering
-	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
-	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
+	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
+	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
 \end{minipage}
@@
 \begin{figure}[!ht]
-% \begin{minipage}[b]{0.8\columnwidth}
-% 	\begin{flushleft}
-% 	\small
-% 	\begin{tabular}[b]{cc}
-%  	\toprule
-%  	\textbf{Number} & \textbf{Event Description} \\
-%  	\midrule
-%  	1-3  & Burners ignited \\
-%  	4	 & Interior stairwell door opened \\
-%  	5 	 & 1st floor west double door opened \\
-%  	6	 & 2nd floor west double door opened \\
-%  	7 	 & 2nd floor south exterior door opened \\
-%  	8-10 & Burners extinguished \\
-% 	\bottomrule
-% 	\end{tabular}
-% 	\end{flushleft}
-% \end{minipage}
 \begin{minipage}[b]{0.8\columnwidth}
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{\normalsize Event Times (mm:ss) for Tests 24--25 Data Files} \\
+	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
 	\toprule
@@
 	\midrule
-	(1) Corner burner on 						& 	2:30 			&	 2:00		\\
-	(2) Middle burner on 						&   2:45	  		&	 2:00		\\
-	(3) Center burner on 						&   3:00	  		&	 2:00		\\
-	(4) Interior stairwell door opened 			&   5:00	  		&    4:00		\\
-	(5) 1st floor west double door opened 		&	7:00	  		&    6:11 	 	\\
-	(6) 2nd floor west double door opened 		&   9:00		  	&    8:00		\\
-	(7) 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
-	(8) PPV fan on 								&   13:00		  	&    12:00 		\\
-	% (9) PPV fan off              				&   16:30		  	&    		\\
-	(8) Center burner off 						&   15:00		  	&    14:00		\\
-	(9) Middle burner off 						&   15:00		  	&    14:00		\\
-	(10) Corner burner off 						&   15:00		  	&    14:00		\\
-	% doors were opened, fan was on after burners turned off
+	~(1)~ Corner burner on 						& 	2:30 			&	 2:00		\\
+	~(2)~ Middle burner on 						&   2:45	  		&	 2:00		\\
+	~(3)~ Center burner on 						&   3:00	  		&	 2:00		\\
+	~(4)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
+	~(5)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
+	~(6)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
+	~(7)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
+	~(8)~ PPV fan on 							&   13:00		  	&    12:00 		\\
+	~(9)~ All burners off 						&   15:00		  	&    14:00		\\
+	(10) 2nd floor east double door opened 		&   17:15		  	&    16:00		\\
 	\bottomrule

### 2016-05-12 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -23,12 +23,12 @@ specify_test = False
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = False
+specify_year = True
 specific_year = '2014'
 
 # Specify type
-specify_type = False
-specific_type = 'HOSE'
+specify_type = True
+specific_type = 'GAS'
 
 # Specify structure
 specify_struct = False

### 2016-05-19 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edits to gas burner report: updated drawings, more content to intro.

@@
 \label{chap:Introduction}
-
 % [Brief Introduction of FRD at NIST, ventilation, etc.]
-
-This report describes nine full-scale fire experiments in which the effects of changing the ventilation patterns within a structure were studied.
-The experiments were conducted in two structures designed to replicate typical residential dwellings.
-During each test, propane was provided to three diffusion flame burners at a measured flow rate.
-Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while ventilation patterns within the structure were changed by opening and closing certain doors and vents.
+The Fire Fighting Technology Group of the Fire Research Division at the National Institute of Standards and Technology (NIST) develops and applies technology, measurements, and standards to improve the understanding of fire behavior, prevention and suppression, which ultimately enables advances in fire fighting operations, firefighter equipment, fire suppression, fire investigations, and disaster response.
+One function of the group is to conduct research to enhance the understanding of fire fighting tactics and how they affect the fire environment.
+
+The development and behavior of compartment fires, such as a fire inside a residential structure, depend greatly on the ventilation conditions within the compartment.
+There are a variety of tactics used by firefighters that can affect the ventilation of a fire environment.
+For example, firefighters may open different doors and windows within a structure or cut holes in a structure's roof with the intention of removing hot gases and smoke from the structure's interior and introducing fresh, cool air into the environment.
+Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) on the fire ground in an attempt to improve the tenability of the fire environment.
+PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent.
+Nine full-scale fire experiments were performed to study how these tactics affect ventilation within a structure.
+The tests were conducted in two structures designed to replicate typical residential dwellings.
+During each experiment, propane was provided to three diffusion flame burners at a measured flow rate.
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents.
+During a number of the tests, a PPV fan was used in conjunction with the opening and closing of vents to further affect the ventilation conditions within the fire environment.
+This report contains in-depth descriptions of the setup and procedure used for each of the nine experiments.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
+	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Instrumentation}
 	\\~\\
@@
 \newpage
-\multirow{16}{*}{\large{\textbf{A4}}}
- & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
- & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
- & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
+% \multirow{16}{*}{\large{\textbf{A4}}}
+%  & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
+%  & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
+%  & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
+%  & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
+%  & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
+%  & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
+%  & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
+%  & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
+% \cline{2-4}
+%  & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
+%  & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
+%  & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
+%  & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
+%  & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
+%  & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
+%  & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
+%  & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
+% \midrule
 \multirow{16}{*}{\large{\textbf{A5}}}
@@
  & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\newpage
+\midrule
 \multirow{16}{*}{\large{\textbf{A6}}}
@@
  & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
+\bottomrule
+\newpage
 \multirow{8}{*}{\large{\textbf{A7}}}
@@
  & TC\_A8\_8  & 2.13~m below ceiling & Temperature \\
-\bottomrule
-\newpage
+\midrule
 \multirow{8}{*}{\large{\textbf{A9}}}
@@
  & TC\_A9\_8  & 2.13~m below ceiling & Temperature \\
-\midrule
+\bottomrule
+\newpage
 \multirow{19}{*}{\large\textbf{A10}} 
@@
  & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
-\bottomrule
-\newpage
+\midrule
 \multirow{16}{*}{\large{\textbf{A11}}}
@@
  & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
+\bottomrule
+\newpage
 \multirow{16}{*}{\large{\textbf{A13}}}
@@
  & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\newpage
+\midrule
 \multirow{16}{*}{\large{\textbf{A14}}}
@@
  & HF\_2\_V   & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
-\midrule
+\bottomrule
+\newpage
 \multirow{3}{*}{\large{\textbf{A17}}}

### 2016-05-20 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edit to intro of gas burner exp report
Re-numbered/added fan icon to test event drawings for gas burner exp report

@@
 PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent.
-Nine full-scale fire experiments were performed to study how these tactics affect ventilation within a structure.
+
+Nine full-scale fire experiments were performed to study how the tactics described above affect ventilation and the fire environment within a structure.
 The tests were conducted in two structures designed to replicate typical residential dwellings.
@@
 	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
-	~(7)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
-	~(8)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
-	~(9)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
-	(10) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
-	(11) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
-	(12) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
-	(13) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
+	~(8)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
+	~(9)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
+	(10)  Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
+	(11) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
+	(12) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
+	(13) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
+	(14) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
 	\bottomrule
@@
 	\midrule
-	~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
-	~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
-	~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
-	~(4)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
-	~(5)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
-	~(6)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
-	~(7)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
-	~(8)~  PPV fan on 							&   19:10		  	&    14:01		\\
-	~(9)~  PPV fan off              			&   21:34		  	&    16:30		\\
-	(10) All burners off 						&   22:00		  	&    17:00		\\
-	(11) 2nd floor south exterior door opened 	&   23:19		  	&    18:01		\\
-	(12) PPV fan on 	 						&   26:00		  	&    19:30		\\
-	(13) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
+	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
+	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
+	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
+	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
+	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
+	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
+	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
+	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
+	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
+	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
+	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
+	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
+	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
+	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
 	\bottomrule
@@
 	\centering
-	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
-	\includegraphics[width=0.84\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
 \end{minipage}
@@
 	\midrule
-	~(1)~ Corner burner on 						& 	2:30 			&	 2:00		\\
-	~(2)~ Middle burner on 						&   2:45	  		&	 2:00		\\
-	~(3)~ Center burner on 						&   3:00	  		&	 2:00		\\
-	~(4)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
-	~(5)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
-	~(6)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
-	~(7)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
-	~(8)~ PPV fan on 							&   13:00		  	&    12:00 		\\
-	~(9)~ All burners off 						&   15:00		  	&    14:00		\\
-	(10) 2nd floor east double door opened 		&   17:15		  	&    16:00		\\
+	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
+	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
+	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
+	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
+	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
+	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
+	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
+	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
+	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
+	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
+	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
 	\bottomrule
@@
 	\centering
-	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
-	\includegraphics[width=0.94\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
 \end{minipage}

### 2016-05-20 Projects/DelCo_2014_2015/Scripts/plot.py
Adding dimensions to pic of BDPs in hose stream report; minor edits to gas burner report

@@ -23,12 +23,12 @@ specify_test = False
 specific_name = 'Test_16_West_063014'
 
 # Specify year
-specify_year = True
+specify_year = False
 specific_year = '2014'
 
 # Specify type
 specify_type = True
-specific_type = 'GAS'
+specific_type = 'HOSE'
 
 # Specify structure
 specify_struct = False
@@ -150,9 +150,9 @@ for f in os.listdir(data_dir):
             test_year = '2015'
 
         test_type = info['Test Type'][test_name]
-
-        if test_type == 'HOSE':
-            continue
+        
+        # if test_type == 'HOSE':
+        #     continue
 
         if check_name(test_name, test_year, test_type):     # check if file should be skipped
             continue

### 2016-05-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Adding dimensions to pic of BDPs in hose stream report; minor edits to gas burner report
Minor edits to gas burner report, new annotation on BDP pic

@@
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
-	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in exterior doorway (top) and in roof vent (bottom) of the East Structure.}
+	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in south exterior doorway (top) and in roof vent (bottom) of the East Structure.}
 	\label{fig:BDP_arrays}
@@
 \subsubsection{Gas Flow Meter}
+A rotary type gas meter was used to measure the flow of propane to the gas burners. The manufacturer of the meter quantifies the maximum error as 2\%.
+
+% http://www.istec-corp.com/products/gas-meter-model-romet-rm-series-rotary.pdf
 
@@
  \midrule
-Test 2 				& 338 & 651	& 894 & 634 & 330 \\
-Test 3				& 326 & 650	& 899 & 631 & 326 \\
-Test 4				& 351 & 654	& 902 & 652 & 337 \\
-Test 5 - Seq. 1		& 263 & 526	& 723 & 486 & 263 \\
-Test 5 - Seq. 2		& 225 & 526	& 727 & 526 & 316 \\
-Test 5 - Seq. 3		& 263 & 526	& 722 & 526 & 263 \\
-Test 6 - Seq. 1		& 263 & 526	& 722 & 526 & 263 \\
-Test 6 - Seq. 2		& 225 & 526	& 718 & 526 & 287 \\
-Test 6 - Seq. 3		& 263 & 526	& 714 & N/A & N/A \\
+Test 2$^*$ 			& 338 & 651	& 901 & 634 & 330 \\
+Test 3$^*$			& 326 & 650	& 905 & 631 & 326 \\
+Test 4				& 351 & 654	& 952 & 652 & 337 \\
+Test 5 - Seq. 1		& N/A & N/A	& 725 & N/A & N/A \\
+Test 5 - Seq. 2		& N/A & N/A	& 728 & N/A & N/A \\
+Test 5 - Seq. 3		& N/A & N/A	& 723 & N/A & N/A \\
+Test 6 - Seq. 1		& N/A & N/A	& 722 & N/A & N/A \\
+Test 6 - Seq. 2		& N/A & N/A	& 721 & N/A & N/A \\
+Test 6 - Seq. 3		& N/A & N/A	& 714 & N/A & N/A \\
 \bottomrule
@@
 \caption{Calculated Heat Release Rate for West Structure Tests}
-% \begin{tabular}{lc}
-%  \toprule
-% \textbf{Test}  			& 	\begin{tabular}{c} \textbf{Heat Release Rate} \\ \textbf{(kW)} \end{tabular} \\
-% \midrule
-% Test 22 				& 	756		\\
-% Test 23					& 	788		\\
-% Test 24					& 	784		\\
-% Test 25					&  	785		\\
-\begin{tabular}{lccc}
+\begin{tabular}{lc}
  \toprule
- 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
-\textbf{Test} 		& 	1 Burner On 	& 	2 Burners On 	& 	3 Burners On \\
- \midrule
-Test 22				& 	  287		 	&      316			&     	759 	  \\
-Test 23				& 	  395		 	&      526			&     	788 	  \\
-Test 24				& 	  287		 	&      631			&     	787 	  \\
-Test 25				& 	  N/A		 	&      N/A			&     	785 	  \\
+\textbf{Test} 		& 	\textbf{Heat Release Rate (kW)}	\\
+ \midrule
+Test 22				&     	764 	  \\
+Test 23				&     	789 	  \\
+Test 24				& 	    789 	  \\
+Test 25				&     	786 	  \\
 \bottomrule
@@
 
-% \begin{landscape}
-% \begin{table}[!ht]
-% \caption{East Structure experimental event times (mm:ss)}
-% \begin{tabular}{lcccccccccccccc}
-%  \toprule
-% \textbf{Test} &
-% \multicolumn{2}{c}{\textbf{\underline{Corner Burner}}} &
-% \multicolumn{2}{c}{\textbf{\underline{Middle Burner}}} &
-% \multicolumn{2}{c}{\textbf{\underline{Center Burner}}} &
-% \multicolumn{2}{c}{\textbf{\underline{W Double Door}}} &
-% \multicolumn{2}{c}{\textbf{\underline{E Double Door}}} &
-% \multicolumn{2}{c}{\textbf{\underline{Single Door}}} &
-% \multicolumn{2}{c}{\textbf{\underline{Roof Vent}}}
-% \\
-% \textbf{Number} &
-% \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} & \textbf{On} & \textbf{Off} &
-% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open} &
-% \textbf{Close} & \textbf{Open} & \textbf{Close} & \textbf{Open}
-% \\
-% \midrule
-% % Test 2
-% 2 & 0:20 & 16:20 & 3:20 & 14:20 & 6:20 & 12:20 &
-% N/A & 7:20 & N/A & 9:20 & N/A & 10:30 & N/A & N/A \\
-% % Test 3
-% 3 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 &
-% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A \\
-% % Test 4
-% 4 & 0:20 & 17:20 & 3:20 & 15:20 & 6:20 & 13:20 &
-% N/A & 7:20 & N/A & 9:20 & N/A & 10:20 & N/A & N/A
-% \\ \multicolumn{15}{c}{ } \\
-% % Test 5a
-% 5a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
-% N/A & 3:18 & N/A & 6:18 & N/A & N/A & 7:45 & 2:53 \\
-% % Test 5b
-% 5b & 0:15 & 10:30 & 0:30 & 10:15 & 0:45 & 10:00 &
-% N/A & 3:45 & N/A & 5:15 & N/A & N/A & 8:30 & 2:15 \\
-% % Test 5c
-% 5c & 0:15 & 9:45 & 0:30 & 9:30 & 0:45 & 9:15 &
-% N/A & 3:45 & N/A & 5:16 & N/A & N/A & 7:28 & 2:15
-% \\ \multicolumn{15}{c}{ } \\
-% % Test 6a
-% 6a & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
-% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-% % Test 6b
-% 6b & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
-% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-% % Test 6c
-% 6c & 0:15 & 9:55 & 0:30 & 9:35 & 0:45 & 9:15 &
-% N/A & 3:18 & N/A & N/A & N/A & N/A & N/A & 2:53 \\
-% \bottomrule
-% \end{tabular}
-% \label{table:east_exp_times}
-% \end{table}
-% \end{landscape}
-
 \end{document}

### 2016-05-24 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to construction/layout sections in hose stream and gas burner reports

@@
 Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
+Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
 
@@
 The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The walls of the second floor were wood framed with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
+The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
 The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
@@
 The interior dimensions of the Single Story Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the Two Story Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
-The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.3~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+The stairs connecting the two floors of the Two Story Structure started 1.6~m (5.3~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run.
 
@@
 All other doorways in the structures did not contain a door.
-So, in order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
+In order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
 \clearpage

### 2016-05-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to construction/layout sections in hose stream and gas burner reports

@@
 The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
-The fire source for all experiments was generated by three propane burners, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
+Three propane burners were used to provide the fire source for all experiments, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
 
@@
 	\includegraphics[width=5.25in]{../../Hose_Stream_Tests/Figures/Pictures/west_structure}
-	\caption[North side of the East and West Structures.]{North side of the East (top) and West (bottom) test structures.}
+	\caption[North side of the East and West Structures.]{North side of the East Structure (top) and West Structure (bottom).}
 	\label{fig:struct_pics}
@@
 
-The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 0.30~m (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was screwed to the top of the TJIs.
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
 
@@
 
-%SIG FIGS ON DIMENSIONS - ROUND COMMON DECIMALS? Example: 0.625 -> 0.6; 0.75 -> 0.8? They could also be changed to fractions
-
 The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs set to 0.40~m (16~in) centers.
-The interior walls were protected by 16~mm (0.625~in) fire rated gypsum board, 16~mm (0.625~in) durarock board, and a second layer of 16~mm (0.625~in) fire rated gypsum board.
+The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
+The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
 The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Structure is symmetric across horizontal centerline.}
+	\caption[Dimensioned floor plan of the East Structure.]{Dimensioned floor plan of the East Structure. Structure dimensions are symmetric across horizontal centerline.}
 	\label{fig:east_dimensioned_plan}
@@
 
-The interior dimensions of each structure were approximately 6.1~m (20~ft) wide, 11~m (36~ft) long, and 2.4~m (8~ft) high.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall and a 0.18~m (7.25~in) rise and 0.19~m (7.5~in) rise.
-The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent of the East Structure with side length 1.2~m (4~ft) and a depth of 0.32~m (12.75~in) were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
+The ceiling height of each structure was approximately 2.4~m (8~ft).
+The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run.
+The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
 \FloatBarrier
@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+The thermocouple wire was protected with an 3.2~mm (0.13~in) diameter inconel sheath.
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
@@
 	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
-	\caption[Three propane burners.]{Three propane burners used as the fuel source for the experiments at a position of 0.6~m (2~ft) off the south and west walls of the East Structure.}
+	\caption[Three propane burners.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls of the first floor provided the fire source for the experiments.}
 	\label{fig:burners}

### 2016-05-25 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to gas burner report

@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple wire was protected with an 3.2~mm (0.13~in) diameter inconel sheath.
+The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath.
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
@@
 Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure.
-Propane was supplied to the burners at a measured flow rate during all experiments.
+Propane was supplied to the burners during all experiments.
+The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.
 % INCLUDE HRR CALCULATIONS HERE
@@
 	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
-	\caption[Three propane burners.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls of the first floor provided the fire source for the experiments.}
+	\caption[Three propane burners used as fire source.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls on the first floor provided the fire source for the experiments.}
 	\label{fig:burners}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Dimensioned_Instrumentation}
-	\caption{Location of instrumentation in the East Structure.}
+	\caption{Locations and labels of instrumentation in the East Structure.}
 	\label{fig:east_instrumentation}
@@
 Each bare-bead thermocouple array was composed of eight thermocouples.
-Three bi-directional probe and solid thermocouple arrays were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
-The fourth bi-directional probe and solid thermocouple array, also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent 0.32~m (12.75 in) above the room ceiling and contained three probes centered between the east and west sides of the vent.
+Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
+The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent and contained three probes centered between the east and west sides of the vent.
 The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}.
 The total heat flux gauge/radiometer pairs were set to be aimed to view the ceiling.
-Gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing.
+Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing.
 The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.
@@
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
-	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array in south exterior doorway (top) and in roof vent (bottom) of the East Structure.}
+	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array at the south exterior doorway (top) and roof vent (bottom) of the East Structure.}
 	\label{fig:BDP_arrays}
@@
 The first floor of the West Structure was instrumented with three bare-bead thermocouple arrays, two bi-directional probe plus solid thermocouple arrays, and one gas sample inlet pipe.
-The second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, two total heat flux sensor pairs (one facing horizontal and one facing vertical), and one gas sample inlet pipe.
+The second floor was equipped with three bare-bead thermocouple arrays, four bi-directional probe plus solid thermocouple arrays, two total heat flux sensor pairs, and one gas sample inlet pipe.
 The location of the instrumentation in the West Structure is shown in Fig.~\ref{fig:west_instrumentation}.
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Instrumentation}
-	\caption[Location of instrumentation in the West Structure.]{Location of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
+	\caption[Locations and labels of instrumentation in the West Structure.]{Locations and labels of instrumentation in the second floor (top) and first floor (bottom) of the West Structure.}
 	\label{fig:west_instrumentation}
@@
 Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor.
+The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
 \clearpage
@@
 \label{sec:Uncertainty}
-There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, and gas velocity measurements.
+There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate measurements.
 Uncertainties are grouped into two categories according to the method used to estimate them.
@@
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$).
+Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe.
-The thermocouple wire was protected with a 3.2~mm (0.125~in) diameter inconel sheath.
+The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
@@
 
-\subsubsection{Gas Flow Meter}
-A rotary type gas meter was used to measure the flow of propane to the gas burners. The manufacturer of the meter quantifies the maximum error as 2\%.
+\subsubsection{Heat Release Rate}
+A rotary type gas meter was used to measure the volume of propane provided to the gas burners.
+The manufacturer quantifies the maximum error as $\pm$2\%.
+The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
+The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm13$\%.
+***\textit{Still need to finish uncertainty estimate and include refs}***
 
@@
 First, three propane burners were ignited in sequential order.
-Next, different doors and vents in the structure were opened and closed to change the ventilation pattern within the structure.
-Finally, the burners were turned off in sequential order and the fire was extinguished.
+Next, various actions, such as opening and closing doors and roof vents or turning on a fan, were performed to change the ventilation pattern within the structure.
+Finally, the burners were turned off and the fire was extinguished.
 
@@
 \label{sec:east_procedure}
-Five different tests, Tests 2--6, were conducted in the East Structure.
+Five different tests, Tests 2--6, were conducted in the East Structure. Table~\ref{table:HRR_East} lists the calculated heat release rate for each test.
+
 Tests~2--4 followed an identical order of events.
-Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for Tests~2--4.
+Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test.
+During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
+So, when the south door was in the ``closed'' position, a gap of approximately 133~mm (5.25~in) was present between the door and its frame.
+During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test.
+For these tests, the hinged door was removed and gypsum board was used to fully close the doorway.
+
 The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
 Tests~5 and 6 involved performing a specific set of events three times sequentially.
-To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the table).
-Additionally, Table~\ref{table:HRR_East} lists the calculated heat release rate for each test and sequence.
+To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables).
 
@@
  \midrule
-Test 2$^*$ 			& 338 & 651	& 901 & 634 & 330 \\
-Test 3$^*$			& 326 & 650	& 905 & 631 & 326 \\
+Test 2 				& 338 & 651	& 901 & 634 & 330 \\
+Test 3 				& 326 & 650	& 905 & 631 & 326 \\
 Test 4				& 351 & 654	& 952 & 652 & 337 \\
@@
 \label{sec:west_procedure}
-Four different tests---Tests~22, 23, 24, and 25---were conducted in the West Structure.
+Four different tests, Tests~22--25, were conducted in the West Structure.
 Tests~22 and 23 followed an identical procedure to change the ventilation.

### 2016-05-26 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edits to gas burner report and itsfloor plan drawings

@@
 The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 180~mm (7.25~in) rise and 190~mm (7.5~in) run.
+The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run.
 The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
@@
 
-Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.375~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
 Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor.
@@
 A rotary type gas meter was used to measure the volume of propane provided to the gas burners.
-The manufacturer quantifies the maximum error as $\pm$2\%.
+The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}.
 The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
@@
 ***\textit{Still need to finish uncertainty estimate and include refs}***
-
-% http://www.istec-corp.com/products/gas-meter-model-romet-rm-series-rotary.pdf
 
@@
 During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
-So, when the south door was in the ``closed'' position, a gap of approximately 133~mm (5.25~in) was present between the door and its frame.
+So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame.
 During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test.
 For these tests, the hinged door was removed and gypsum board was used to fully close the doorway.
+A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the doorway and used during Tests~2--4.
 
@@
 Test 4				& 351 & 654	& 952 & 652 & 337 \\
-Test 5 - Seq. 1		& N/A & N/A	& 725 & N/A & N/A \\
-Test 5 - Seq. 2		& N/A & N/A	& 728 & N/A & N/A \\
-Test 5 - Seq. 3		& N/A & N/A	& 723 & N/A & N/A \\
-Test 6 - Seq. 1		& N/A & N/A	& 722 & N/A & N/A \\
-Test 6 - Seq. 2		& N/A & N/A	& 721 & N/A & N/A \\
-Test 6 - Seq. 3		& N/A & N/A	& 714 & N/A & N/A \\
+\midrule
+ & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
+\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
+& \multicolumn{3}{c}{} \\
+\midrule
+Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
+Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
+Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
 \bottomrule
@@
 	\begin{flushleft}
-	\small
 	\begin{tabular}{lccc}
@@
 	% Some door(s) opened before test start according to notes, no sign from data/limited videos
-	~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
-	~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
-	~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
-	~(4)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
-	~(5)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
-	~(6)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
-	~(7)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
-	~(8)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
-	~(9)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
-	(10)  Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
-	(11) Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
-	(12) East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
-	(13) West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
-	(14) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
+	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
+	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
+	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
+	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
+	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
+	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
+	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
+	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
+	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
+	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
+	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
+	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
+	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
+	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
+	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
+	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
 	\bottomrule
@@
 	\midrule
-	~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
-	~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
-	~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
-	~(4)~  West double door opened 	&	5:15	&   14:45	&	23:15	\\
-	~(5)~  Roof vent opened 		&	6:45	&	15:45 	&	24:45 	\\
-	~(6)~  Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
-	~(7)~  Middle burner off		&	8:30	&   17:30	&	\\
-	~(8)~  Corner burner off 		&	8:45	&   17:45	&	\\
-	~(9)~  East double door opened	&	9:30	&   18:30	&	27:25	\\
-	(10) Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
-	(11) East double door closed	&	12:02 	&	20:11	&	N/A 	\\
-	(12) West double door closed	&	12:18 	&	20:24	&	N/A		\\
+	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
+	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
+	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
+	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
+	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
+	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
+	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
+	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
+	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
+	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
+	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
+	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
+	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
+	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
 	\bottomrule
@@
 Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
+A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure.
+During Tests~22 and 23, the fan was aimed at the center of the double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
 
@@
  \toprule
-\textbf{Test} 		& 	\textbf{Heat Release Rate (kW)}	\\
+					& 	\textbf{Heat Release Rate (kW)}	\\
+\textbf{Test}		& All burners on \\
  \midrule
@@
 	\begin{flushleft}
-	\small
 	\begin{tabular}{lcc}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
+	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
 \end{minipage}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
+	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
 \end{minipage}

### 2016-05-26 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Began writing the summary for the gas burner experiments report

@@
 The tests were conducted in two structures designed to replicate typical residential dwellings.
-During each experiment, propane was provided to three diffusion flame burners at a measured flow rate.
+During each experiment, propane was provided to three diffusion flame burners.
 Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure while the ventilation within the structure was varied by opening and closing certain doors and vents.
@@
 	\centering
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
+	\includegraphics[width=0.86\columnwidth]{../Figures/Floor_Plans/East_Structure_Test_5}
 \end{minipage}
@@
 \end{minipage}
-\begin{minipage}[b]{0.9\columnwidth}
+\begin{minipage}[b]{0.86\columnwidth}
 	\vspace{15pt}
@@
 \label{chap:Summary}
+Nine full-scale fire tests were conducted in two residential-sized structures to examine how changing ventilation patterns within a structure affects the fire environment.
+The fire source for each experiment was provided by a set of three diffusion flame burners with propane as the fuel.
+Various doors and vents were opened and closed during each test to affect the ventilation within the structure.
+A PPV fan was also used during some of the experiments to change the ventilation patterns.
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during each experiment.
+The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire for each test.
 

### 2016-05-27 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Gas burner report: labeled instrumentation schematics, made minor edits to content

@@
 \vspace*{2\baselineskip}
-February 2016}}
+May 2016}}
 
@@
 The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
-\clearpage
+The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.
+% \clearpage
 
@@
  & TC\_A2\_8  & 2.13~m below ceiling & Temperature \\
- \midrule
+ \bottomrule
+ \newpage
  \multirow{10}{*}{\large{\textbf{A3}}}
@@
  & TC\_A3\_8  & 2.13~m below ceiling & Temperature \\
-\bottomrule
-\newpage
+ \midrule
 % \multirow{16}{*}{\large{\textbf{A4}}}
@@
  & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
+\bottomrule
+\newpage
 \multirow{16}{*}{\large{\textbf{A6}}}
@@
  & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\newpage
+\midrule
 \multirow{8}{*}{\large{\textbf{A7}}}
@@
  & TC\_A8\_8  & 2.13~m below ceiling & Temperature \\
-\midrule
+\bottomrule
+\newpage
 \multirow{8}{*}{\large{\textbf{A9}}}
@@
  & TC\_A9\_8  & 2.13~m below ceiling & Temperature \\
-\bottomrule
-\newpage
+\midrule
 \multirow{19}{*}{\large\textbf{A10}} 
@@
  & O2\_B      & 1.22~m above floor   & O$_2$ concentration \\
-\midrule
+\bottomrule
+\newpage
 \multirow{16}{*}{\large{\textbf{A11}}}
@@
  & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\
-\bottomrule
-\newpage
+\midrule
 \multirow{16}{*}{\large{\textbf{A13}}}
@@
  & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\
-\midrule
+\bottomrule
+\newpage
 \multirow{16}{*}{\large{\textbf{A14}}}
@@
  & HF\_2\_V   & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
-\bottomrule
-\newpage
+\midrule
 \multirow{3}{*}{\large{\textbf{A17}}}
@@
 The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
-The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm13$\%.
-***\textit{Still need to finish uncertainty estimate and include refs}***
+The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm??$\%.
+***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***
 
@@
 \label{sec:east_procedure}
-Five different tests, Tests 2--6, were conducted in the East Structure. Table~\ref{table:HRR_East} lists the calculated heat release rate for each test.
+Five different tests, Tests 2--6, were conducted in the East Structure.
+Table~\ref{table:HRR_East} lists the heat release rates for each experiment.
+The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
+Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.
 
@@
 Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test.
-During Tests~2--4, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
+A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4.
+During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
 So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame.
-During all other experiments, however, the south exterior doorway was not used to change the ventilation pattern of the structure and thus remained closed for the entirety of the test.
-For these tests, the hinged door was removed and gypsum board was used to fully close the doorway.
-A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the doorway and used during Tests~2--4.
-
-The procedures for Test~5 and Test~6 are outlined in a similar manner in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
-Tests~5 and 6 involved performing a specific set of events three times sequentially.
-To avoid repetition of identical actions in the event time table, each set of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables).
+For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test.
+To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.
+
+The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
+Tests~5 and 6 involved repeating a specific set of events three times in a row.
+To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.
 
 \begin{table}[!ht]
-\caption{Calculated Heat Release Rate for East Structure Tests}
+\caption{Heat Release Rates for East Structure Tests}
 \begin{tabular}{lccccc}
@@
 	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
-	(11) PPV fan off 					& 	52:30 		  &    36:00  		&  	   36:00$^*$  \\
+	(11) PPV fan off 					& 	52:30 		  &    N/A  		&  	   N/A        \\
 	\bottomrule
@@
 	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
-	~(1)~ All burners on 			& 	14:30		  &	   35:00		&	   55:00	\\
+	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
 	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
@@
 	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
-	~(1)~ All burners on 			&	3:45	&	13:15	&	21:45	\\
+	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
 	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
@@
 Four different tests, Tests~22--25, were conducted in the West Structure.
+Table~\ref{table:HRR_West} lists the calculated heat release rate for each test.
+Similar to Tests~5 and 6, Tests~22--25 had a duration on the order of seconds between the ignition of each burner, so only the heat release rate for when all three burners were ignited is reported.
+
+\begin{table}[!ht]
+\caption{Heat Release Rates for West Structure Tests}
+\begin{tabular}{lc}
+ \toprule
+					& 	\textbf{Heat Release Rate (kW)}	\\
+\textbf{Test}		& All burners on \\
+ \midrule
+Test 22				&     	764 	  \\
+Test 23				&     	789 	  \\
+Test 24				& 	    789 	  \\
+Test 25				&     	786 	  \\
+\bottomrule
+\end{tabular}
+\label{table:HRR_West}
+\end{table}
+
 Tests~22 and 23 followed an identical procedure to change the ventilation.
@@
 A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure.
-During Tests~22 and 23, the fan was aimed at the center of the double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
-
-\begin{table}[!ht]
-\caption{Calculated Heat Release Rate for West Structure Tests}
-\begin{tabular}{lc}
- \toprule
-					& 	\textbf{Heat Release Rate (kW)}	\\
-\textbf{Test}		& All burners on \\
- \midrule
-Test 22				&     	764 	  \\
-Test 23				&     	789 	  \\
-Test 24				& 	    789 	  \\
-Test 25				&     	786 	  \\
-\bottomrule
-\end{tabular}
-\label{table:HRR_West}
-\end{table}
+During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
 

### 2016-05-31 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Switched NF near and far data for Test 16 plot

@@
 One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth left-to-right), clockwise, and counterclockwise application patterns.
+Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise application patterns.
 This entire process was repeated using narrow fog and wide fog streams.

### 2016-05-31 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -19,7 +19,7 @@ rcParams.update({'figure.autolayout': True})
 
 # Specify name
 specify_test = True
-specific_name = 'Test_17_West_063014'
+specific_name = 'Test_16_West_063014'
 
 # Specify year
 specify_year = False
@@ -52,7 +52,7 @@ stream_avgs_plot = True    # Plot avg of all channels for each stream tested dur
 # Location of directories
 data_dir = '../Experimental_Data/'      # Location of experimental data files
 results_dir = '../Results/Hose_Stream/'     # Location to save results files 
-fig_dir = '../Reports/Hose_Stream_Report/Figures/Plots/'     # Location to save plots
+fig_dir = '../Reports/Hose_Stream_Tests/Figures/Plots/'     # Location to save plots
 all_times_file = '../Experimental_Data/All_Times.csv'       # Location of file with timing information
 info_file = '../Experimental_Data/Description_of_Experiments.csv'       # Location of test description file
 
@@ -288,10 +288,10 @@ def plot_stream_avgs(stream_data, updated_times, x_max_index, y_max, y_min, mark
 	return x_max_index, y_max, y_min, t
 
 def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, plot_type, tick_info):
-	plt.errorbar(x_max_index, y_max, yerr=(.18)*y_max, ecolor='k')
 	if 'West' not in fig_name and plot_type == 'stream avgs':
 		end_time = end_time - 1
 	ax1 = plt.gca()
+	handles1, labels1 = ax1.get_legend_handles_labels()
 	ax1.set_xlim([0, end_time])
 	ax1.set_ylim(math.floor(y_min)-0.1, math.ceil(y_max)+0.1)
 	ax1.xaxis.set_major_locator(plt.MaxNLocator(8))
@@ -304,7 +304,8 @@ def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, 
 	ax1.set_yticks(np.around(y_tick_ls,1))
 	plt.xticks(fontsize=16)
 	plt.yticks(fontsize=16)
-
+	# plt.errorbar(x_max_index, y_max, yerr=(.18)*y_max, ecolor='k')
+	
 	ax2 = ax1.twinx()
 	ax2.set_ylabel('Velocity (mph)', fontsize=20)
 	ax2.set_ylim(math.floor(y_min)-0.1, math.ceil(y_max)+0.1)
[…]

### 2016-05-31 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py
Minor changes to hose script to output avg gas velocities

@@ -19,7 +19,7 @@ rcParams.update({'figure.autolayout': True})
 
 # Specify name
 specify_test = True
-specific_name = 'Test_16_West_063014'
+specific_name = 'Test_17_West_063014'
 
 # Specify year
 specify_year = False
@@ -40,10 +40,10 @@ skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh',
 # = Specify files to generate =
 # =============================
 
-result_file = False       # Generate a .csv file with channel avgs for specified sensor groups
+result_file = True       # Generate a .csv file with channel avgs for specified sensor groups
 all_channel_plot = False    # Plot of individual channels in sensor group
 group_avg_plot = False     # Plot avg of all channels for sensor group
-stream_avgs_plot = True    # Plot avg of all channels for each stream tested during experiment
+stream_avgs_plot = False    # Plot avg of all channels for each stream tested during experiment
 
 #  =======================
 #  = Directory Locations =
@@ -195,6 +195,7 @@ def sort_data(test_name, start_time, test_type):
 					door_status = 'Closed A'
 
 				start_seq = index-start_time
+
 		group_set = {'Start': start_times_ls, 'End':end_times_ls, 'Stream':streams_ls, 
 		P_or_L_heading:P_or_L_ls,'Door':door_status_ls}
 		group_results = pd.DataFrame(group_set, 
@@ -305,7 +306,7 @@ def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, 
 	plt.xticks(fontsize=16)
 	plt.yticks(fontsize=16)
 	# plt.errorbar(x_max_index, y_max, yerr=(.18)*y_max, ecolor='k')
-	
+
 	ax2 = ax1.twinx()
 	ax2.set_ylabel('Velocity (mph)', fontsize=20)
 	ax2.set_ylim(math.floor(y_min)-0.1, math.ceil(y_max)+0.1)
@@ -408,8 +409,8 @@ for f in os.listdir(data_dir):
 		if check_name(test_name, test_year, test_type):     # check if file should be skipped
 			continue
 		else:   # Load exp. data file
-			if 'Test_17' in test_name:
-				f = test_name + '_original.csv'
+			# if 'Test_17_' in test_name:
+			# 	f = test_name + '_original.csv'
 			data = pd.read_csv(data_dir + f)
 			data = data.set_index('TimeStamp(s)')
 			print
[…]

### 2016-05-31 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Corrected dimension of PPV fan in gas burner report

@@
 Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test.
-A 533~mm (21~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4.
+A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4.
 During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
@@
 Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
-A 533~mm (21~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure.
+A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure.
 During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.

### 2016-06-02 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to hose script to output avg gas velocities
Tightened up axes limits, other minor changes to hose stream plots

@@
 
+\subsubsection{Length Measurements}
 Each length measurement was taken carefully.
@@
 
+\subsubsection{Bi-Directional Probes}
 Bi-directional probes with pressure transducers and single thermocouples were used to measure the gas velocity.
@@
 
+\subsubsection{Water Flow Rate}
 Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1 MPa (0--600 psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
+The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 Three different structure layouts were used for the seven experiments.
-Tests 1 and 5 were conducted in the Single Story Structure and used the layout shown in Fig.~\ref{fig:east_setup}.
-Test 1 used a monitor and combination nozzle to flow water, and Test 5 used a combination nozzle attached directly to a handline to flow water.
+Tests~1 and 5 were conducted in the Single Story Structure and used the layout shown in Fig.~\ref{fig:east_setup}.
+Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.
 
@@
 The main difference between the two layouts was the position of the south side door on the first level.
-Tests 2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests 3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
-Tests 2 and 3 used a combination nozzle attached to a monitor to flow water; Tests 6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test 4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
+Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
+Tests~2 and 3 used a combination nozzle attached to a monitor to flow water; Tests~6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test~4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
 
@@
 
+\subsubsection{Test 1}
 Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}).
@@
 
+\subsubsection{Tests 2 \& 3}
 Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
@@
 
+\subsubsection{Test 4}
 Test 4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests 2 and 3.
@@
 
+\subsubsection{Test 5}
 Test 5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
@@
 
+\subsubsection{Tests 6 \& 7}
 Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
@@
 \small{m/s}   & -0.3 $\pm0.1$   & & 0.9 $\pm0.2$    & 0.9 $\pm0.2$    & & 0.7 $\pm0.1$    & 0.7 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
 \\ \multicolumn{9}{c}{} \\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   1.1 $\pm0.2$  & &   0.9 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
+\small{(mph)} & (-0.7 $\pm0.1$) & & (2.1 $\pm0.4$) & (3.2 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
 \\ \multicolumn{9}{c}{} \\
 \multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   2.4 $\pm0.4$  & &   1.2 $\pm0.2$  & 1.3 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{m/s}   &   2.4 $\pm0.4$  & &   1.3 $\pm0.2$  & 1.4 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
+\small{(mph)} & (-0.7 $\pm0.1$) & & (2.8 $\pm0.5$) & (3.1 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
 \\ \midrule
@@
 Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
-Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6 and 7, respectively.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6--7, respectively.
 
@@
 
-A total of eight experiments were conducted to study the impact of different hose stream and application pattern combinations on air movement within residential scale structures.
+A total of seven experiments were conducted to study the impact of different hose stream and application pattern combinations on air movement within residential scale structures.
 
@@
 
-The authors would like to thank Roy McLane, Kristopher Overholt, Nicholas Dow, and Jay MCElroy from NIST for their contributions in preparing and conducting these experiments.
+The authors would like to thank Roy McLane, Kristopher Overholt, Keith Stakes, Nicholas Dow, and Jay MCElroy from NIST for their contributions in preparing and conducting these experiments.
 These experiments could not have been conducted without them.
@@
 \FloatBarrier
+% Streams were flowed during two 30 second, nonconsecutive periods, but plotted back-to-back for simplicity. See Section 2.2.1 for more details about the procedure
 

### 2016-06-02 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -11,23 +11,24 @@ from itertools import cycle
 
 from matplotlib import rcParams
 rcParams.update({'figure.autolayout': True})
-
+rcParams['xtick.major.pad']='6'
+rcParams['ytick.major.pad']='6'
 
 #  =================
 #  = Specify files =
 #  =================
 
 # Specify name
-specify_test = True
-specific_name = 'Test_17_West_063014'
+specify_test = False
+specific_name = 'Test_70_West_101215'
 
 # Specify year
 specify_year = False
 specific_year = '2015'
 
 # Specify structure
-specify_struct = False
-specific_struct = 'West'
+specify_struct = True
+specific_struct = 'East'
 
 # Specify monitor or handline
 specify_type = False
@@ -40,10 +41,10 @@ skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh',
 # = Specify files to generate =
 # =============================
 
-result_file = True       # Generate a .csv file with channel avgs for specified sensor groups
+result_file = False       # Generate a .csv file with channel avgs for specified sensor groups
 all_channel_plot = False    # Plot of individual channels in sensor group
 group_avg_plot = False     # Plot avg of all channels for sensor group
-stream_avgs_plot = False    # Plot avg of all channels for each stream tested during experiment
+stream_avgs_plot = True    # Plot avg of all channels for each stream tested during experiment
 
 #  =======================
 #  = Directory Locations =
@@ -291,31 +292,44 @@ def plot_stream_avgs(stream_data, updated_times, x_max_index, y_max, y_min, mark
 def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, plot_type, tick_info):
 	if 'West' not in fig_name and plot_type == 'stream avgs':
 		end_time = end_time - 1
+		ylim_min = y_min - 0.7	
+	else:
+		ylim_min = y_min - 0.4
+
 	ax1 = plt.gca()
 	handles1, labels1 = ax1.get_legend_handles_labels()
 	ax1.set_xlim([0, end_time])
[…]

### 2016-06-06 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to hose stream plotting script; can now print values for tables in report
Plotting/sorting script prints out values for tables in hose stream report; fixed typo in All_Times

@@
 \small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
 \\ \multicolumn{9}{c}{} \\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.7 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (2.1 $\pm0.4$) & (3.2 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
+\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
 \\ \multicolumn{9}{c}{} \\
 \multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   2.4 $\pm0.4$  & &   1.3 $\pm0.2$  & 1.4 $\pm0.2$    & &   0.9 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (2.8 $\pm0.5$) & (3.1 $\pm0.6$) & & (-0.7 $\pm0.1$) & (-0.7 $\pm0.1$) 
+\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
+\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
 \\ \midrule
@@
 \multirow{2}{*}{\textit{Straight}} &
-\small{m/s}   &   1.7 $\pm0.3$   & \multicolumn{2}{c}{1.9 $\pm0.3$}  & \multicolumn{4}{c}{} \\ &
-\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
+\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
+\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
 \\ \multicolumn{9}{c}{} \\
 \multirow{2}{*}{\textit{Smooth Bore}} &
-\small{m/s}   &   1.7 $\pm0.3$  &  \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
-\small{(mph)} &  (-0.7 $\pm0.1$) & \multicolumn{2}{c}{(-0.7 $\pm0.1$)} & \multicolumn{4}{c}{} 
+\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
+\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} 
 \\
-% \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
-% \begin{tabular}{@{}c@{}} -0.3 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
-% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
-% \begin{tabular}{@{}c@{}} 0.9 $\pm0.2$ \\ (-0.7 $\pm0.1$) \end{tabular} & & 
-% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} & 
-% \begin{tabular}{@{}c@{}} 0.7 $\pm0.1$ \\ (-0.7 $\pm0.1$) \end{tabular} 
-% \\ \multicolumn{9}{c}{} \\
-% \textit{Narrow Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
-% 1.1 $\pm0.2$ & & 0.9 $\pm0.2$ & 1.4 $\pm0.3$ & & 0.8 $\pm0.1$ & 0.7 $\pm0.1$
-% \\ \multicolumn{9}{c}{} \\
-% \textit{Wide Fog} & \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
-% 2.4 $\pm0.4$ & & 1.2 $\pm0.2$ & 1.3 $\pm0.2$ & & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
-% \\ \midrule
-%  &  & \multicolumn{3}{c}{\large --- 180 gpm ---} & \multicolumn{4}{c}{} 
-% \\
-%  &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
-% \\
-% \textbf{Stream} & \textbf{Units} &
-% \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &  &
-% \begin{tabular}{@{}c@{}} \textbf{Far} \\ \textbf{Target} \\ \end{tabular} &
-% \multicolumn{4}{c}{} 
-% \\
-% \midrule
-% \textit{Straight} &  \begin{tabular}{@{}c@{}} m/s \\ (mph) \end{tabular} &
-% 1.7 $\pm0.3$ &  & 1.9 $\pm0.3$ & \multicolumn{4}{c}{} 
-% \\ \multicolumn{9}{c}{} \\
-% \textit{Smooth Bore} & 
-% 1.7 $\pm0.3$ &  & 2.0 $\pm0.4$ & \multicolumn{4}{c}{}
-% \\
 \bottomrule
@@
 \begin{table}[!ht]
-\caption{Average gas velocity (m/s) [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
-\begin{tabular}{lccccccc}
+\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
+\begin{tabular}{lcccc}
 \toprule
- & \multicolumn{3}{c}{\underline{Room A}} &  & \multicolumn{3}{c}{\underline{Room B Ceiling}}
+ &  & \multicolumn{3}{c}{\underline{Room A}}
 \\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular} &  & \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\textbf{Stream} & \textbf{Units} & 
+\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\textit{Straight} & 0.2 $\pm0.04$ & 0.6 $\pm0.1$ & 0.8 $\pm0.1$ &  &
--0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.5 $\pm0.1$
-\\ \multicolumn{8}{c}{} \\
-\textit{Narrow Fog} & 1.7 $\pm0.3$ & 1.8 $\pm0.3$ & 1.6 $\pm0.3$ &  & 
-0.9 $\pm0.2$ & 1.5 $\pm0.3$ & 1.6 $\pm0.3$
-\\ \multicolumn{8}{c}{} \\
-\textit{Wide Fog} & 1.9 $\pm0.3$ & 2.1 $\pm0.4$ & 2.2 $\pm0.4$ &  & 
-2.1 $\pm0.4$ & 2.3 $\pm0.4$ & 2.6 $\pm0.5$
+\multirow{2}{*}{\textit{Straight}} & 
+\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
+\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
+\\ \multicolumn{5}{c}{} \\
+\multirow{2}{*}{\textit{Narrow Fog}} & 
+\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
+\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
+\\ \multicolumn{5}{c}{} \\
+\multirow{2}{*}{\textit{Wide Fog}} & 
+\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
+\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
+\\ \midrule
+ & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
+\\
+\textbf{Stream} & \textbf{Units} & 
+\textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\multirow{2}{*}{\textit{Straight}} & 
+\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
+\\ \multicolumn{5}{c}{} \\
+\multirow{2}{*}{\textit{Narrow Fog}} & 
+\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
+\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
+\\ \multicolumn{5}{c}{} \\
+\multirow{2}{*}{\textit{Wide Fog}} & 
+\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
+\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$)  
 \\ \bottomrule
@@
 \begin{table}[!ht]
-\caption{Average gas velocity (m/s) [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
-\begin{tabular}{lcccc}
+\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
+\begin{tabular}{lccccc}
 \toprule
- & \multicolumn{4}{c}{\underline{Test 6}}
+ & & \multicolumn{4}{c}{\underline{Test 6}}
 \\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\textbf{Stream} & \textbf{Units} & 
+\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\textit{Straight} & -0.2 $\pm0.04$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.7 $\pm0.1$
-\\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 0.4 $\pm0.1$ & 1.0 $\pm0.2$ & 0.8 $\pm0.1$ & 1.0 $\pm0.2$
-\\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$ & 0.8 $\pm0.1$
+\multirow{2}{*}{\textit{Straight}} & 
+\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
+\\ \multicolumn{6}{c}{} \\
+\multirow{2}{*}{\textit{Narrow Fog}} & 
+\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
+\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
+\\ \multicolumn{6}{c}{} \\
+\multirow{2}{*}{\textit{Wide Fog}} & 
+\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
+\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$)
 \\ \midrule
- & \multicolumn{4}{c}{\underline{Test 7}}
+ & & \multicolumn{4}{c}{\underline{Test 7}}
 \\
-\textbf{Stream} & \textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\textbf{Stream} & \textbf{Units} & 
+\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\textit{Straight} & -0.1 $\pm0.02$ & 0.5 $\pm0.1$ & 0.7 $\pm0.1$ & 0.6 $\pm0.1$
-\\ \multicolumn{5}{c}{} \\
-\textit{Narrow Fog} & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$ & 1.2 $\pm0.2$
-\\ \multicolumn{5}{c}{} \\
-\textit{Wide Fog} & 1.0 $\pm0.2$ & 0.7 $\pm0.1$ & 0.9 $\pm0.2$ & 0.9 $\pm0.2$
+\multirow{2}{*}{\textit{Straight}} & 
+\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
+\\ \multicolumn{6}{c}{} \\
+\multirow{2}{*}{\textit{Narrow Fog}} & 
+\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
+\\ \multicolumn{6}{c}{} \\
+\multirow{2}{*}{\textit{Wide Fog}} & 
+\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
 \\ \bottomrule

### 2016-06-06 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -19,16 +19,16 @@ rcParams['ytick.major.pad']='6'
 #  =================
 
 # Specify name
-specify_test = False
-specific_name = 'HOSE_IXXAXX'
+specify_test = True
+specific_name = 'Test_70_West_101215'
 
 # Specify year
 specify_year = False
 specific_year = '2014'
 
 # Specify structure
-specify_struct = True
-specific_struct = 'West'
+specify_struct = False
+specific_struct = 'East'
 
 # Specify monitor or handline
 specify_type = False
@@ -42,10 +42,10 @@ skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh',
 # =============================
 
 result_file = False       # Generate a .csv file with channel avgs for specified sensor groups
-print_results = True
+print_results = False		# print average values for tables in report
 all_channel_plot = False    # Plot of individual channels in sensor group
 group_avg_plot = False     # Plot avg of all channels for sensor group
-stream_avgs_plot = False   # Plot avg of all channels for each stream tested during experiment
+stream_avgs_plot = True   # Plot avg of all channels for each stream tested during experiment
 
 #  =======================
 #  = Directory Locations =
@@ -613,11 +613,65 @@ for f in os.listdir(data_dir):
 				seq_info = group_results.iloc[:, :last_col]
 				streams = seq_info.groupby('Stream')
 				for stream in streams.groups:
+					print '---'
 					print stream + ':'
 					print '---'
 					stream_seq_info = streams.get_group(stream)
 					if P_or_L == 'both':
-						continue
+						if test_name[7] == 'A':
+							locations = stream_seq_info.groupby('Location')
+							for location in locations.groups:
+								print '		----'
+								print '		' + location
+								print '		----'
+								location_seq_info = locations.get_group(location)								
+								patterns = location_seq_info.groupby('Pattern')
+								for pattern in patterns.groups:
+									pattern_seq_info = patterns.get_group(pattern)
+									print '			----'
+									print '			' + pattern
+									print '			----'
+									m_per_s_data = []
+									mph_data = []
+									for index, row in pattern_seq_info.iterrows():
+										m_per_s_data.append(group_data['Avg'].loc[row['Start']+3:row['End']-3])
[…]

### 2016-06-06 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream report figures and content

@@
 		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
-		\caption{Solid stream from smooth bore nozzle with 1~tip}
+		\caption{Solid stream from 1~in smooth bore nozzle}
 	\end{subfigure}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/East_Hose_Test_Annotated}
-	\caption[Plan view of the Single Story Structure setup for Tests 1 and 5.]{Plan view of the Single Story Structure setup for Tests 1 and 5.
+	\caption[Plan view of the Single Story Structure setup for Tests~1 and 5.]{Plan view of the Single Story Structure setup for Tests~1 and 5.
 The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A6 (blue square).
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_18_1st_Floor_Annotated}
-	\caption[Plan view of the Two Story Structure setup for Tests 2 and 6.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 2 and 6.
+	\caption[Plan view of the Two Story Structure setup for Tests~2 and 6.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests~2 and 6.
 The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/Specific_Tests/West_Hose_Test_19_1st_Floor_Annotated}
-	\caption[Plan view of the Two Story Structure setup for Tests 3 and 7.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests 3, 4, and 7.
+	\caption[Plan view of the Two Story Structure setup for Tests~3 and 7.]{Plan view of the second floor (top) and first floor (bottom) setup in the Two Story Structure for Tests~3, 4, and 7.
 The view is annotated with the approximate location of water flow (nozzle graphic), the direction of the established flow path (red line), and the approximate location of bi-directional probe array A10 (blue square).
@@
 
-\subsubsection{Test 1}
+\subsubsection{Test~1}
 Test~1 utilized a monitor equipped with a combination nozzle to flow water from Room~C of the Single Story Structure to the area above the doorway on the south wall of Room~B (Fig.~\ref{fig:test_1_pic}).
@@
 	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test 1 in the Single Story Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test~1 in the Single Story Structure.}
 	\label{fig:test_1_pic}
@@
 
-\subsubsection{Tests 2 \& 3}
-Tests 2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
+\subsubsection{Tests~2 \& 3}
+Tests~2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
 The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall.
@@
 	\endminipage \hfill
-	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during Tests 2 and 3 in the Two Story Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream aimed at the near and far targets in the Two Story Structure.]{Straight stream (left column), narrow fog stream (middle column), and wide fog stream (right column) aimed at ``near'' target (top row) and ``far'' target (bottom row) during Tests~2 and 3 in the Two Story Structure.}
 	\label{fig:test_2_3_pic}
@@
 
-\subsubsection{Test 4}
-Test 4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests 2 and 3.
+\subsubsection{Test~4}
+Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3.
 The stairwell door was opened for the entire experiment.
@@
 This entire process was repeated for the solid stream from the smooth bore nozzle.
-Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test 4.
+Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test~4.
 
@@
 	\endminipage
-	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test 4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test 4.}
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test~4.}
 	\label{fig:test_4_pic}
@@
 Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
-One test, Test 5, occurred in the Single Story Structure, and the remaining tests, Tests 6 and 7, occurred in the Two Story Structure.
+One test, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure.
 All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
 
-\subsubsection{Test 5}
-Test 5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
-The layout of the structure was identical to the layout for Test 1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
-The procedure for Test 5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
+\subsubsection{Test~5}
+Test~5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
+The layout of the structure was identical to the layout for Test~1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
+The procedure for Test~5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
 After 30 seconds, the nozzle was rotated in the clockwise direction for 30 seconds.
@@
 	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test 5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test 5.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test~5.}
 	\label{fig:test_5_pic}
@@
 
-\subsubsection{Tests 6 \& 7}
-Tests 6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
+\subsubsection{Tests~6 \& 7}
+Tests~6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
 The water stream was aimed at the south side wall of the first floor during the experiments.
-Test 6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test 7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
+Test~6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test~7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
 Each experiment began by using a straight stream to flow water in a fixed, horizontal position.
@@
 This entire process was repeated using narrow fog and wide fog streams.
-Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test 6 with the flow path fully established.
+Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.
 
@@
 	\includegraphics[width=4.25in]{../Figures/Pictures/Test_18}
-	\caption[North side of Two Story Structure containing a fully established flow path during Test 6.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test 6.}
+	\caption[North side of Two Story Structure containing a fully established flow path during Test~6.]{North side of Two Story Structure containing a fully established flow path while water is flowed in a straight stream pattern during Test~6.}
 	\label{fig:test_6_pic}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_16_West_063014_BDP_A10_stream_avgs}
-	\caption[Average gas velocity through the interior stairwell door during Test 2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 2 for the three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test~2 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~2 for the three hose stream patterns.}
 	\label{fig:Test_2_BDP_A10_Avg_All}
@@
 Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
-Finally, the Test 4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
+Finally, the Test~4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
 \FloatBarrier
@@
 \label{sec:handline_results}
-Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test 6.
-Similar plots of the average measured velocity through the interior doorway for Tests 5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
-Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test 5 and Tests 6--7, respectively.
+Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} contains a plot of the average gas velocity measured by the bi-directional probes in the array at the interior stairwell door (A10) for the straight stream, narrow fog stream, and wide fog stream being applied in a fixed position, a sweeping pattern (back and forth, left-to-right), a clockwise rotation, and a counterclockwise rotation during Test~6.
+Similar plots of the average measured velocity through the interior doorway for Tests~5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test~5 and Tests~6--7, respectively.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_18_West_063014_BDP_A10_stream_avgs}
-	\caption[Average gas velocity through the interior stairwell door during Test 6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 6 for the three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test~6 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~6 for the three hose stream patterns.}
 	\label{fig:Test_6_BDP_A10_Avg_All}
@@
 \begin{table}[!ht]
-\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test 5}
+\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
 \begin{tabular}{lcccc}
@@
 \begin{table}[!ht]
-\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests 6 and 7}
+\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
 \begin{tabular}{lccccc}
@@
 
-With the exception of the narrow fog stream in the fixed position during Test 6, every hose stream and application pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
+With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and application pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
 For the straight stream, however, significant air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
-	\caption[Average gas velocity through the interior doorway during Test 1 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior doorway (A6) during Test 1 for the three hose stream patterns.}
+	\includegraphics[width=\columnwidth]{../Figures/Plots/HOSE_IXXAXX_BDP_A6_stream_avgs}
+	\caption[Average gas velocity through the interior doorway during Test~1 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior doorway (A6) during Test~1 for the three hose stream patterns.}
 	\label{fig:Test_1_BDP_A6_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_17_West_063014_BDP_A10_stream_avgs}
-	\caption[Average gas velocity through the interior stairwell door during Test 3 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 3 for the three hose stream patterns.}
+	\caption[Average gas velocity through the interior stairwell door during Test~3 for the three hose stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~3 for the three hose stream patterns.}
 	\label{fig:Test_3_BDP_A10_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_70_West_101215_BDP_A10_stream_avgs}
-	\caption[Average gas velocity through the interior stairwell door during Test 4 for the straight stream and smooth bore stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test 4 for the straight stream and smooth bore stream patterns.
-\textit{Note: the increase in velocities around the 300~s mark is the result of opening and then closing the west double door on the second story.}}
+	\caption[Average gas velocity through the interior stairwell door during Test~4 for the straight stream and smooth bore stream patterns.]{Average gas velocity measured by the bi-directional probes at the interior stairwell door (A10) during Test~4 for the straight stream and smooth bore stream patterns.}
 	\label{fig:Test_4_BDP_A10_Avg_All}
@@
 	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 5 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test~5 for three hose stream patterns.}
 	\label{fig:Test_5_BDP_A6_Avg_All}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Plots/Test_19_West_063014_BDP_A10_stream_avgs}
-	\caption{Average velocity through stairwell door during Test 7 for the three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test~7 for the three hose stream patterns.}
 	\label{fig:Test_7_BDP_A10_Avg_All}

### 2016-06-06 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -20,7 +20,7 @@ rcParams['ytick.major.pad']='6'
 
 # Specify name
 specify_test = True
-specific_name = 'Test_70_West_101215'
+specific_name = 'HOSE_IXXAXX'
 
 # Specify year
 specify_year = False
@@ -283,10 +283,19 @@ def plot_stream_avgs(stream_data, updated_times, x_max_index, y_max, y_min, mark
 
 	t = ma_quantity.index.values[1:updated_times[-1]+2]
 
+
 	plt.plot(t, ma_quantity.loc[1:updated_times[-1]+1], 
 		ls = line_style, color = color, lw=2,
 		marker=marker, markevery=int(len(t))/10, 
 		mew=1.5, mec='none', ms=7, label=plot_label)
+
+	if 'Test_70' in test_name and 'SS' in plot_label:
+		annotate_range = ma_quantity.loc[260:320]
+		y_annotate = max(ma_quantity.loc[260:320])
+		x_annotate = annotate_range.idxmax(y_annotate)
+
+		plt.annotate('  Door\nopened$^*$', xy=(x_annotate, y_annotate), xytext=(x_annotate-33, y_annotate+0.4),
+			arrowprops=dict(facecolor='black', shrink=0.05, width=2, headwidth=8))
 
 	return x_max_index, y_max, y_min, t
 
@@ -305,7 +314,15 @@ def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, 
 	ax1_xlims = ax1.axis()[0:2]
 	grid(True)
 	plt.axhline(0, color='0.50', lw=1)
-	ax1.set_xlabel('Time (s)', fontsize=20)
+	if plot_type == 'stream avgs':
+		if 'Test_70' in fig_name:
+			ax1.set_xlabel('Time (s)\n', fontsize=20)
+		elif 'HOSE_IXXAXX' in fig_name:
+			ax1.set_xlabel('Time (s)\n\n', fontsize=20)
+		else:
+			ax1.set_xlabel('Time (s)', fontsize=20)
+	else:
+		ax1.set_xlabel('Time (s)', fontsize=20)
 	ax1.set_ylabel('Velocity (m/s)', fontsize=20)
 	if abs(math.floor(y_min))-abs(y_min) < 0.5:
 		min_y_tick = math.floor(y_min)
@@ -314,8 +331,16 @@ def save_plot(x_max_index, y_max, y_min, start_time, end_time, group, fig_name, 
[…]

### 2016-06-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added intro to Analysis Chapter
cleaned up equation format

@@
 
+In this chapter the application of emprical algebraic fire characterizations will be examined.
+Two different types of applications will be used.
+In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.
+In the second case, the height of the thermal damage on the gypsum board will be examined.
+
+Values generated in the bench scale experiments will be utilized as input to predict real scale results using the algorithms.
+Then the predicted results will be compared with the full-scale experiment results.
+
 \section{Evidence of a Fire Pattern}
@@
 \end{equation}
-where $\dot{q}''$ is the heat flux per unit area kW/m$^2$, $\dot{Q}$ is the heat release rate (kW), $\chi_r$ is the radiative fraction, and $R$ = distance from the point source to the target (m).
+
+\begin{tabbing}
+where: \=  \\
+
+\> $\dot{q}''$ is the heat flux per unit area kW/m$^2$\\
+\> $\dot{Q}$ is the heat release rate (kW) \\ 
+\> $\chi_r$ is the radiative fraction \\
+\> $R$ = distance from the point source to the target (m) \\
+\end{tabbing}
 
@@
 \end{equation}
-where $\epsilon$ is the emissivity, $\sigma$ is the Stefan\-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$) and $F_{12}$ is the radiative shape factor.
+
+\begin{tabbing}
+where: \=  \\
+\> $\epsilon$ is the emissivity  \\
+\> $\sigma$ is the Stefan-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$)  \\
+\> $F_{12}$ is the radiative shape factor \\
+\end{tabbing}
 

### 2016-06-07 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor formatting edits and rounded tabulated HRRs in gas burner report

@@
  \midrule
-% \multirow{16}{*}{\large{\textbf{A4}}}
-%  & TC\_A4\_1  & 0.03~m below soffit  & Temperature \\
-%  & TC\_A4\_2  & 0.30~m below soffit  & Temperature \\
-%  & TC\_A4\_3  & 0.61~m below soffit  & Temperature \\
-%  & TC\_A4\_4  & 0.91~m below soffit  & Temperature \\
-%  & TC\_A4\_5  & 1.22~m below soffit  & Temperature \\
-%  & TC\_A4\_6  & 1.52~m below soffit  & Temperature \\
-%  & TC\_A4\_7  & 1.83~m below soffit  & Temperature \\
-%  & TC\_A4\_8  & 2.13~m below soffit  & Temperature \\
-% \cline{2-4}
-%  & BDP\_A4\_1 & 0.03~m below soffit  & Velocity \\
-%  & BDP\_A4\_2 & 0.30~m below soffit  & Velocity \\
-%  & BDP\_A4\_3 & 0.61~m below soffit  & Velocity \\
-%  & BDP\_A4\_4 & 0.91~m below soffit  & Velocity \\
-%  & BDP\_A4\_5 & 1.22~m below soffit  & Velocity \\
-%  & BDP\_A4\_6 & 1.52~m below soffit  & Velocity \\
-%  & BDP\_A4\_7 & 1.83~m below soffit  & Velocity \\
-%  & BDP\_A4\_8 & 2.13~m below soffit  & Velocity \\
-% \midrule
 \multirow{16}{*}{\large{\textbf{A5}}}
@@
 Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
-Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100\%.
+Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95\% confidence interval (2$\sigma$).
+Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
 Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
-Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\%.
 
 \subsubsection{Thermocouples}
-The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$^{\circ}$C at $277^{\circ}$C and increases to $\pm$9.5$^{\circ}$C at $871^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
+The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
-The estimated total expanded uncertainty for temperature in these experiments is $\pm$15\%.
+The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.
 
@@
 Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
-The manufacturer reports a $\pm$3\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8\%~\cite{Pitts:2006}.
+The manufacturer reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
 
 \subsubsection{Gas Sampling}
-The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12\% is associated with gas concentration measurements~\cite{Lock:1}.
+The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with gas concentration measurements~\cite{Lock:1}.
 
@@
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1\%~\cite{Setra:2002}.
-The total expanded uncertainty was estimated at 10\%.
+The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}.
+The total expanded uncertainty was estimated at 10~\%.
 
@@
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18\%.
+The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18~\%.
 
@@
 A rotary type gas meter was used to measure the volume of propane provided to the gas burners.
-The manufacturer quantifies the maximum error as $\pm$2\%~\cite{Romet:2014}.
+The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}.
 The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
-The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm??$\%.
+The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm15$~\%.
 ***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***
@@
  \midrule
-Test 2 				& 338 & 651	& 901 & 634 & 330 \\
-Test 3 				& 326 & 650	& 905 & 631 & 326 \\
-Test 4				& 351 & 654	& 952 & 652 & 337 \\
+% Original Values
+% Test 2 				& 338 & 651	& 901 & 634 & 330 \\
+% Test 3 				& 326 & 650	& 905 & 631 & 326 \\
+% Test 4				& 351 & 654	& 952 & 652 & 337 \\
+% Rounded Values
+Test 2 				& 340 & 650	& 900 & 630 & 330 \\
+Test 3 				& 330 & 650	& 910 & 630 & 330 \\
+Test 4				& 350 & 650	& 950 & 650 & 337 \\
 \midrule
@@
 \midrule
-Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
-Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
-Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
+% Original Values
+% Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
+% Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
+% Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
+% Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
+% Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
+% Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
+% Rounded Values
+Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
+Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
+Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
+Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
 \bottomrule
@@
 	\midrule
+	% Old table layout --- will delete soon
 	% Some door(s) opened before test start according to notes, no sign from data/limited videos
@@
 	\midrule
+	% Old table layout --- will delete soon
 	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
@@
  \midrule
-Test 22				&     	764 	  \\
-Test 23				&     	789 	  \\
-Test 24				& 	    789 	  \\
-Test 25				&     	786 	  \\
+% Original Values
+% Test 22				&     	764 	  \\
+% Test 23				&     	789 	  \\
+% Test 24				& 	    789 	  \\
+% Test 25				&     	786 	  \\
+% Rounded Values
+Test 22				&     	760 	  \\
+Test 23				&     	790 	  \\
+Test 24				& 	    790 	  \\
+Test 25				&     	790 	  \\
 \bottomrule
@@
 	\midrule
+	% Old table layout --- will delete soon
 	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
@@
 	\midrule
+	% Old table layout --- will delete soon
 	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\

### 2016-06-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
New east dimensioned drawing, removed annotation from BDP roof vent photo for gas burner report
Added functionality to plot.py to create data sets where t=0 at ignition for gas burner experiments

@@
 	\\~\\
-	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs.png}
+	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/roof_vent_BDPs}
 	\caption[Bi-directional probe plus solid thermocouple arrays in East Structure.]{Bi-directional probe plus solid thermocouple array at the south exterior doorway (top) and roof vent (bottom) of the East Structure.}
@@
 The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
-The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}.
+Blevins found that the percent error in the measured upper layer temperature for a 1~mm bare-bead thermocouple is bounded by a maximum of 20~\%~\cite{Blevins:1999}.
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
 The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.
+***\textit{Still need to finish reviewing literature about TC uncertainty and add list of components of standard uncertainty along with description about uncertainty estimate.}***
 
@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Tests~2--4 Data Files} \\
+	\multicolumn{4}{c}{\normalsize Event Times (s) for Tests~2--4 Data Files} \\
 	\toprule
@@
 	\midrule
-	~(1)~ Corner burner on 				& 	21:00		  &		4:00		&		4:00	  \\
-	~(2)~ Middle burner on 				&   24:00		  &		7:00		&		7:00	  \\
-	~(3)~ Center burner on 				&   27:00		  &	   10:00		&	   10:00	  \\
-	~(4)~ West double door opened 		&   28:00		  &    11:00		&	   11:00	  \\
-	~(5)~ East double door opened 		&   30:00		  &    13:00		&	   13:00	  \\
-	~(6)~ South exterior door opened 	&   31:00		  &    14:00		&	   14:00	  \\
-	~(7)~ Center burner off				&   33:00		  &    17:00		&	   17:00	  \\
-	~(8)~ Middle burner off				&   35:00		  &    19:00		&	   19:00	  \\
-	~(9)~ Corner burner off				&   37:00		  &    21:00		&	   21:00	  \\
-	(10) PPV fan on 					& 	42:01		  &    26:00		&  	   26:00	  \\	
-	(11) PPV fan off 					& 	52:30 		  &    N/A  		&  	   N/A        \\
+	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
+	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
+	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
+	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
+	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
+	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
+	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
+	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
+	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
+	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
 	\bottomrule
@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~5 Data File} \\
+	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~5 Data File} \\
 	\toprule
@@
 	\midrule
-	% Old table layout --- will delete soon
-	% Some door(s) opened before test start according to notes, no sign from data/limited videos
-	% ~(1)~ Corner burner on 			& 	14:00		  &	   34:30		&	   54:30	\\
-	% ~(2)~ Middle burner on 			&   14:15		  &	   34:45		&	   54:45	\\
-	% ~(3)~ Center burner on 			&   14:30		  &	   35:00		&	   55:00	\\
-	% ~(6)~ Center burner off 		&   23:00		  &    44:15		&	   63:30	\\
-	% ~(7)~ Middle burner off 		&   23:20		  &    44:30		&	   63:45	\\
-	% ~(8)~ Corner burner off 		&   23:40		  &    44:45		&	   64:00	\\
-	~(1)~ All burners on 			& 	14:00		  &	   34:30		&	   54:30	\\
-	~(2)~ Roof vent opened 			&   16:38		  &    36:30		&	   56:30	\\
-	~(3)~ West double door opened 	&	17:03		  &	   38:00 		&	   58:00 	\\
-	~(4)~ East double door opened 	&   20:03		  &    39:30		&	   59:31	\\
-	~(5)~ Roof vent closed		 	&   21:30		  &    42:45		&	   61:43	\\
-	~(6)~ All burners off 			&   23:40		  &    44:45		&	   64:00	\\
-	~(7)~ Roof vent opened			& 	26:05 		  &	   45:30		&	   65:30	\\
-	~(8)~ East double door closed	& 	33:17 		  &	   52:38		&	   N/A		\\
-	~(9)~ West double door closed	& 	33:30 		  &	   52:55		&	   N/A		\\
-	(10) Roof vent closed		 	&   33:45		  &    53:54		&	   N/A		\\
+	~(1)~ All burners on 				& 	0			  &	   1230			&	   2430		\\
+	~(2)~ Roof vent opened 				&   128			  &    1320			&	   2520		\\
+	~(3)~ West double door opened 		&	153			  &	   1410	 		&	   2610 	\\
+	~(4)~ East double door opened 		&   333			  &    1500			&	   2700		\\
+	~(5)~ Roof vent closed		 		&   420			  &    1695			&	   2833		\\
+	~(6)~ All burners off 				&   550			  &    1815			&	   2970		\\
+	~(7)~ Roof vent opened				& 	695 		  &	   1860			&	   3060		\\
+	~(8)~ East double door closed		& 	1127 		  &	   2288			&	   N/A		\\
+	~(9)~ West double door closed		& 	1140 		  &	   2305			&	   N/A		\\
+	(10) Roof vent closed		 		&   1155		  &    2364			&	   N/A		\\
 	\bottomrule
@@
 	\begin{tabular}{lccc}
-	\multicolumn{4}{c}{\normalsize Event Times (mm:ss) for Test~6 Data File} \\
+	\multicolumn{4}{c}{\normalsize Event Times (s) for Test~6 Data File} \\
 	\toprule
@@
 	\midrule
-	% Old table layout --- will delete soon
-	% ~(1)~  Corner burner on 		&	3:15	&	12:45	&	21:15	\\
-	% ~(2)~  Middle burner on 		&	3:30	&	13:00	&	21:30	\\
-	% ~(3)~  Center burner on 		&	3:45	&	13:15	&	21:45	\\
-	% ~(4)~ Center burner off 		&	8:15	&   17:15	&	\multirow{3}{*}{Gas killed at truck (26:15)} \\
-	% ~(5)~ Middle burner off		&	8:30	&   17:30	&	\\
-	% ~(6)~ Corner burner off 		&	8:45	&   17:45	&	\\
-	~(1)~ All burners on 			&	3:15	&	12:45	&	21:45	\\
-	~(2)~ West double door opened 	&	5:15	&   14:45	&	23:15	\\
-	~(3)~ Roof vent opened 		    &	6:45	&	15:45 	&	24:45 	\\
-	~(4)~ All burners off 			&	8:45	&   17:45	&	26:15	\\
-	~(5)~ East double door opened	&	9:30	&   18:30	&	27:25	\\
-	~(6)~ Roof vent closed 			&	11:35	&   20:41	&	N/A		\\
-	~(7)~ East double door closed	&	12:02 	&	20:11	&	N/A 	\\
-	~(8)~  West double door closed	&	12:18 	&	20:24	&	N/A		\\
+	~(1)~ All burners on 				&	0				&	570				&	1080			\\
+	~(2)~ West double door opened 		&	90				&   660				&	1170			\\
+	~(3)~ Roof vent opened 		    	&	180				&	720 			& 	1260 			\\
+	~(4)~ All burners off 				&	300				&   840				&	1350			\\
+	~(5)~ East double door opened		&	345				&   885				&	1420			\\
+	~(6)~ Roof vent closed 				&	470				&   1016			&	N/A				\\
+	~(7)~ East double door closed		&	497 			&	986				&	N/A 			\\
+	~(8)~  West double door closed		&	513 			&	999				&	N/A				\\
 	\bottomrule
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{Event Times (mm:ss) for Tests~22--23 Data Files} \\
+	\multicolumn{3}{c}{Event Times (s) for Tests~22--23 Data Files} \\
 	\toprule
@@
 	\midrule
-	% Old table layout --- will delete soon
-	% ~(1)~  Corner burner on 					& 	9:05 			&	 3:45		\\
-	% ~(2)~  Middle burner on 					&   8:45	  		&	 3:55		\\
-	% ~(3)~  Center burner on 					&   8:15	  		&	 4:04		\\
-	~(1)~  All burners on 						&   8:15	  		&	 3:45		\\
-	~(2)~  2nd floor west double door opened 	&   11:30	  		&    6:00		\\
-	~(3)~  1st floor west double door opened 	&	13:30	  		&    8:02 	 	\\
-	~(4)~  1st floor east double door opened 	&   15:45		  	&    10:00		\\
-	~(5)~  2nd floor east double door opened	&   18:00		  	&    12:08		\\
-	~(6)~  PPV fan on 							&   19:10		  	&    14:01		\\
-	~(7)~  PPV fan off              			&   21:34		  	&    16:30		\\
-	~(8)~  All burners off 						&   22:00		  	&    17:00		\\
-	~(9)~  2nd floor south exterior door opened &   23:19		  	&    18:01		\\
-	(10) PPV fan on 	 						&   26:00		  	&    19:30		\\
-	(11) 2nd floor south exterior door closed   &   27:56		  	&    N/A		\\
+	~(1)~  All burners on 						&   0	  			&	 0			\\
+	~(2)~  2nd floor west double door opened 	&   127		  		&    116		\\
+	~(3)~  1st floor west double door opened 	&	247		  		&    238 	 	\\
+	~(4)~  1st floor east double door opened 	&   382			  	&    356		\\
+	~(5)~  2nd floor east double door opened	&   517			  	&    484		\\
+	~(6)~  PPV fan on 							&   587			  	&    596		\\
+	~(7)~  PPV fan off              			&   731			  	&    746		\\
+	~(8)~  All burners off 						&   757			  	&    776		\\
+	~(9)~  2nd floor south exterior door opened &   836			  	&    836		\\
+	(10) PPV fan on 	 						&   997			  	&    926		\\
+	(11) 2nd floor south exterior door closed   &   1113		  	&    N/A		\\
 	\bottomrule
@@
 	\begin{tabular}{lcc}
-	\multicolumn{3}{c}{Event Times (mm:ss) for Tests 24--25 Data Files} \\
+	\multicolumn{3}{c}{Event Times (s) for Tests 24--25 Data Files} \\
 	\toprule
@@
 	\midrule
-	% Old table layout --- will delete soon
-	% ~(1)~ Corner burner on 					& 	2:30 			&	 2:00		\\
-	% ~(2)~ Middle burner on 					&   2:45	  		&	 2:00		\\
-	% ~(3)~ Center burner on 					&   3:00	  		&	 2:00		\\
-	~(1)~ All burners on 						&   2:30	  		&	 2:00		\\
-	~(2)~ Interior stairwell door opened 		&   5:00	  		&    4:00		\\
-	~(3)~ 1st floor west double door opened 	&	7:00	  		&    6:11 	 	\\
-	~(4)~ 2nd floor west double door opened 	&   9:00		  	&    8:00		\\
-	~(5)~ 2nd floor south exterior door opened	&   11:00		  	&    10:00		\\
-	~(6)~ PPV fan on 							&   13:00		  	&    12:00 		\\
-	~(7)~ All burners off 						&   15:00		  	&    14:00		\\
-	~(8)~ 2nd floor east double door opened 	&   17:15		  	&    16:00		\\
+	~(1)~ All burners on 						&   0		  		&	 0			\\
+	~(2)~ Interior stairwell door opened 		&   120		  		&    110		\\
+	~(3)~ 1st floor west double door opened 	&	240		  		&    241 	 	\\
+	~(4)~ 2nd floor west double door opened 	&   360			  	&    350		\\
+	~(5)~ 2nd floor south exterior door opened	&   480			  	&    470		\\
+	~(6)~ PPV fan on 							&   600			  	&    590 		\\
+	~(7)~ All burners off 						&   720 		  	&    710		\\
+	~(8)~ 2nd floor east double door opened 	&   855			  	&    830		\\
 	\bottomrule

### 2016-06-08 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -28,11 +28,16 @@ specific_year = '2014'
 
 # Specify type
 specify_type = True
-specific_type = 'HOSE'
+specific_type = 'GAS'
 
 # Specify structure
 specify_struct = False
 specific_struct = 'West'
+
+# Specify if creating data sets
+#  for gas burner exp. report
+burner_report = True
+burner_data = '../Reports/Propane_Gas_Fire_Experiments/Data/'
 
 # Plot mode: figure or video
 plot_mode = 'figure'
@@ -150,19 +155,42 @@ for f in os.listdir(data_dir):
             test_year = '2015'
 
         test_type = info['Test Type'][test_name]
-        
-        # if test_type == 'HOSE':
-        #     continue
+
+        if burner_report:
+            try:
+                if 'Propane fire' not in info['Test Description'][test_name]:
+                    continue
+            except TypeError:
+                continue
 
         if check_name(test_name, test_year, test_type):     # check if file should be skipped
             continue
-
         else:   # Load exp. data file
             data = pd.read_csv(data_dir + f)
             data = data.set_index('TimeStamp(s)')
             print ('--- Loaded ' + test_name + ' ---')
 
-        # Read in test times to offset plots
+        # Read in test times to offset plots.
+        if burner_report:
+            if 'West' in test_name:     # ignore first 2 time entries
+                events = all_times[test_name].dropna()[2:]
+            else:      
+                if 'Test_5_' in test_name or 'Test_6_' in test_name:
+                    events = all_times[test_name].dropna()[3:]
+                else:
+                    events = all_times[test_name].dropna()[1:]
+            offset_time = events.index.values[0]
+            new_times = events.index.values - int(offset_time)
+            events = pd.Series(events.values, index=new_times)
+            print events
+            print
+            data['Time'] = data['Time'].values - offset_time
+            reduced_data = data.drop('Time', axis=1)
+            reduced_data.insert(0, 'Time', data['Time'])
+            reduced_data = reduced_data.set_index('Time')
+            reduced_data = reduced_data.loc[-60:, :]
+            reduced_data.to_csv(burner_data + test_name + '.csv')
+            continue
         start_of_test = info['Start of Test'][test_name]
         end_of_test = info['End of Test'][test_name]
 

### 2016-06-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated TC/HRR uncertainty sections of gas burner report

@@
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}.
-Blevins found that the percent error in the measured upper layer temperature for a 1~mm bare-bead thermocouple is bounded by a maximum of 20~\%~\cite{Blevins:1999}.
-Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
+Blevins found the maximum percent error for the upper layer temperature measured by a 1~mm bare-bead thermocouple to be 20~\%~\cite{Blevins:1999}.
+Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling.
 The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.
-***\textit{Still need to finish reviewing literature about TC uncertainty and add list of components of standard uncertainty along with description about uncertainty estimate.}***
 
@@
 The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}.
-The measurement was used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
-The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm15$~\%.
-***\textit{Still need to finish reviewing literature about HRR uncertainty and add description here about calculation and uncertainty estimate.}***
+A volumetric flow rate was calculated from the gas meter measurements and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
+The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm12$~\%.
 

### 2016-06-09 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to uncertainty section of gas burner report

@@
 The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
-The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Pitts:2003}.
-Blevins found the maximum percent error for the upper layer temperature measured by a 1~mm bare-bead thermocouple to be 20~\%~\cite{Blevins:1999}.
+The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.
+Maximum percent error has been reported to be as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple~\cite{Blevins:1999,Pitts:2003}.
 Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling.
@@
  \midrule
-% Original Values
-% Test 2 				& 338 & 651	& 901 & 634 & 330 \\
-% Test 3 				& 326 & 650	& 905 & 631 & 326 \\
-% Test 4				& 351 & 654	& 952 & 652 & 337 \\
-% Rounded Values
 Test 2 				& 340 & 650	& 900 & 630 & 330 \\
 Test 3 				& 330 & 650	& 910 & 630 & 330 \\
-Test 4				& 350 & 650	& 950 & 650 & 337 \\
+Test 4				& 350 & 650	& 950 & 650 & 340 \\
 \midrule
@@
 \midrule
-% Original Values
-% Test 5 - Seq. 1		& \multicolumn{2}{c}{725} & \multicolumn{3}{c}{} \\
-% Test 5 - Seq. 2		& \multicolumn{2}{c}{728} & \multicolumn{3}{c}{} \\
-% Test 5 - Seq. 3		& \multicolumn{2}{c}{723} & \multicolumn{3}{c}{} \\
-% Test 6 - Seq. 1		& \multicolumn{2}{c}{722} & \multicolumn{3}{c}{} \\
-% Test 6 - Seq. 2		& \multicolumn{2}{c}{721} & \multicolumn{3}{c}{} \\
-% Test 6 - Seq. 3		& \multicolumn{2}{c}{714} & \multicolumn{3}{c}{} \\
-% Rounded Values
 Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
@@
  \midrule
-% Original Values
-% Test 22				&     	764 	  \\
-% Test 23				&     	789 	  \\
-% Test 24				& 	    789 	  \\
-% Test 25				&     	786 	  \\
-% Rounded Values
 Test 22				&     	760 	  \\

### 2016-06-13 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
minor updates to text

@@
 
-One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examine how different firefighting tactics affect the fire environment.
-NIST and UL FSRI have conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
+One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examination of how different firefighting tactics affect the fire environment.
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However, ventilation tactics alone will not result in the extinguishment of the fire; fire suppression with hose streams is also needed.
+However, ventilation tactics alone will not extinguish the fire; fire suppression with hose streams is also needed.
 
 Fire suppression tactics using hose streams also affect the ventilation in a structure and may impact the movement of smoke and heat through a structure.
-As vents are made to advance the hoseline or if ventilation inducing handline tactics are in practice, hose stream impacts on ventilation may be even more significant.
+If vents are made to advance the hoseline or if ventilation inducing handline tactics are in practice, hose stream impacts on ventilation may be even more significant.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 However, increasing the angle decreases the distance reached by the stream and its penetration power.
-%\textit{Essentials of Fire Fighting} defines 
-%https://docs.google.com/presentation/d/1hZ5DZhYXxCkcIEHNZKumH48b_Q53iM2D7asXkMYlVMM/embed?hl=en&size=l&slide=id.p39
 
-%http://www.tft.com/literature/library/files/bfa.pdf
-%Keith Royer, "Water for Fire Fighting", (Engineering Extension Service, Iowa State University, Ames, Iowa) p. 6 
 In addition to the type of stream pattern used, the method used to apply the hose stream can also vary.
@@
 \label{sec:objectives}
-This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside two full scale test structures built to represent residential sized structures.
-Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
+This report focuses on examining the impact of hose stream and application pattern (or nozzle motion) selection on air movement inside two full-scale test structures built to represent residential sized structures.
+Experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
 More specifically, the experiments were conducted to fulfill the following objectives:
@@
 \end{enumerate}
-Four types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
-Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream.
+Four types of hose streams and four water application patterns were studied as part of the experiments described in this report.
+Three of the hose stream patterns studied were from a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
 Water was flowed into the structure by having the hose in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
-Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1~in tip on air flows in a structure was conducted.
+Additionally, experiments comparing the differences in impact on air flows in a structure from a combination nozzle straight stream and a solid stream from a smooth bore nozzle equipped with a 1~in tip were conducted.
 Images of the four types of hose streams are presented in Fig.~\ref{fig:hose_streams}.
@@
 The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
-Differential pressure and temperature sensors were installed at ventilation points throughout the residential sized test structures to determine air velocity during the water flow experiments.
+Differential pressure and temperature sensors were installed at ventilation points throughout the test structures to determine air velocity during the water flow experiments.
 
@@
 The Single Story Structure was designed to simulate a single-story residential structure, and the Two Story Structure was designed to simulate a two-story residential structure.
-The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
+The first floor of each structure had an outer wall composed of interlocking concrete blocks of equal side lengths of 0.61~m (2~ft).
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 
-The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances during tests to change the ventilation pattern of the structure.
+The exterior doorways of each structure and the stairwell doorway on the second level of the Two Story Structure all contained doors that were opened or closed at certain instances during tests to change the ventilation pathways within the structure.
 All other doorways in the structures did not contain a door.
@@
 An array of six bi-directional probes located at the northeast interior doorway of the Single Story Structure is pictured below in Fig.~\ref{fig:BDPs}.
-A single thermocouple was attached to each bi-directional probes to measure the gas temperature to be used in conjunction with the pressure measurement to derive velocity.
+A single thermocouple was attached to each bi-directional probes to measure the gas temperature to be used in conjunction with the pressure measurement to calculate velocity.
 Every thermocouple attached to the bi-directional probes was an exposed-bead, Chromel-Alumel (type K) with a 1.0~mm (0.04 in) diameter.
@@
 However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
-Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array.
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
-Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0\%.
 
@@
 Bi-directional probes with pressure transducers and single thermocouples were used to measure the gas velocity.
-Bare-bead, type K thermocouples were co-located with the probe.
+Inconel-sheathed, exposed bead, type K thermocouples were co-located with each probe.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.

### 2016-06-13 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated hose stream report with Dan's edits

--- 2016-06-06 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
@@
 %Keith Royer, "Water for Fire Fighting", (Engineering Extension Service, Iowa State University, Ames, Iowa) p. 6 
-In addition to the type of stream pattern used, the method used to apply the hose stream can also vary.
-For example, Royer suggested using a clockwise rotation instead of a counterclockwise application pattern for the following reasons~\cite{Royer:ISU}:
+In addition to the type of stream pattern used, the method or motion of the nozzle used to apply the hose stream can also vary.
+For example, Royer suggested using a clockwise rotation instead of a counterclockwise nozzle movement pattern for the following reasons~\cite{Royer:ISU}:
 \begin{enumerate} 
@@
 This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside two full scale test structures built to represent residential sized structures.
-Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
+Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and nozzle movement selection on ventilation in a structure.
 More specifically, the experiments were conducted to fulfill the following objectives:
 \begin{enumerate}
-	\item Determine which hose stream patterns and application patterns cause significant air movement in a structure 
-	\item Determine the amount of air movement induced by different hose streams and application patterns
+	\item Determine which hose stream patterns and nozzle movement patterns cause significant air movement in a structure 
+	\item Determine the amount of air movement induced by different hose streams and nozzle movement patterns
 
 \end{enumerate}
-Four types of hose streams and four different water application patterns were studied throughout the experiments described in this report.
+Four types of hose streams and four different nozzle movement patterns were studied throughout the experiments described in this report.
 Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream.
@@
 \label{chap:exp_overview}
-To study the impact of different hose stream and application pattern selections on air movement inside a structure, various water flow experiments were conducted in two experimental structures designed to replicate typical residential structures.
-The experiments focused on studying the differences in the amount of air movement caused by specific combinations of four different hose stream patterns and four different water application patterns.
+To study the impact of different hose stream and nozzle movement selections on air movement inside a structure, water flow experiments were conducted in two experimental structures designed to replicate typical residential structures.
+The experiments focused on studying the differences in the amount of air movement caused by specific combinations of four different hose stream patterns and four different nozzle movement patterns.
 
@@
 
-A total of seven experiments were conducted to study the impact of different hose stream and application patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
-Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern, while the experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on varying the pattern in which water was applied in addition to the stream pattern.
+A total of seven experiments were conducted to study the impact of different hose stream and nozzle movement patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
+Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern.
+The experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on impact of the motion of the nozzle.
 
@@
 
-Three different structure layouts were used for the seven experiments.
-Tests~1 and 5 were conducted in the Single Story Structure and used the layout shown in Fig.~\ref{fig:east_setup}.
+Three different structure flow path configurations were used for the seven experiments.
+Tests~1 and 5 were conducted in the Single Story Structure and used the configuration shown in Fig.~\ref{fig:east_setup}.
 Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.
 
-Two different layouts were used for experiments conducted in the Two Story Structure.
-The main difference between the two layouts was the position of the south side door on the first level.
+Two different flow path configurations were used for experiments conducted in the Two Story Structure.
+The main difference between the two flow paths was the position of the south side door on the first level.
 Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
@@
 First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds.
-The procedure was repeated an additional time.
+The procedure was repeated.
 
@@
 Tests~2 and 3 followed identical procedures that involved using a monitor equipped with a combination nozzle to flow water from the north side double doors to the interior ceiling on the first floor of the Two Story Structure.
-The nozzle was aimed at two targets during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall.
+The nozzle was aimed at two regions marked on the center of the ceiling during the series: a ``near'' target located approximately 1.8~m (6~ft) from the interior side of the north wall and a ``far'' target located approximately 3.7~m (12~ft) from the interior side of the north wall.
 The procedure for each test began by flowing water in a straight stream pattern at the far target for 60 seconds.
@@
 One test, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure.
-All three tests primarily focused on the impact of different hose stream and water application pattern selections on air movement in a structure.
+All three tests primarily focused on the impact of different hose stream and nozzle motion pattern selections on air movement in a structure.
 
@@
 One minute later, the west double door on the north side of the second floor was opened, and water continued to flow for 60 seconds.
-Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise application patterns.
+Next, the water flow was stopped, the two doors were closed, and the procedure was repeated three additional times for the sweeping (back and forth, left-to-right), clockwise, and counterclockwise nozzle motion patterns.
 This entire process was repeated using narrow fog and wide fog streams.
@@
 Similar plots of the average measured velocity through the interior doorway for Tests~5 and 7 are presented in Appendix~\ref{chap:handline_plots}.
-Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and application pattern combination studied during Test~5 and Tests~6--7, respectively.
+Additionally, Tables~\ref{table:east_hand_A6_avgs}~and~\ref{table:west_hand_A10_avgs} list the average velocity measured by the bi-directional probes in A10 when the flow path was fully established for each hose stream and nozzle movement pattern combination studied during Test~5 and Tests~6--7, respectively.
 
@@
 
-With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and application pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
+With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and nozzle movement pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
 For the straight stream, however, significant air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
-Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the application patterns using the narrow and wide fog streams than the same patterns using the straight stream.
+Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the nozzle movement patterns using the narrow and wide fog streams than the same patterns using the straight stream.
 Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
-The similarities in air flow produced by the clockwise and counterclockwise application patterns can also be seen graphically in Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_5_BDP_A6_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} in Appendix~\ref{chap:handline_plots}.
+The similarities in air flow produced by the clockwise and counterclockwise nozzle movement patterns can also be seen graphically in Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_5_BDP_A6_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} in Appendix~\ref{chap:handline_plots}.
 
@@
 
-A total of seven experiments were conducted to study the impact of different hose stream and application pattern combinations on air movement within residential scale structures.
+A total of seven experiments were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
 
@@
 The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream.
+
 Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
@@
 
-In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure.
+In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and nozzle movement pattern combinations on air movement within a structure.
 Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream.
 In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern.
-Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise application patterns.
+Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
 
@@
 These experiments have shown there is a potential for hose streams to affect air flows within a structure during fire scenarios.
-To better quantify the impact of air flows from hose streams on the fire environment, additional fire experiments need to be conducted.
+To better quantify the impact of air flows from hose streams on the fire environment, additional fire experiments need to be conducted with structure fires in a controlled environment.
 

### 2016-06-13 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Resolved merge issues with last two versions of hose stream report

@@
 \label{sec:background}
-% More hose stream studies and explanations
-
-One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examine how different firefighting tactics affect the fire environment.
-NIST and UL FSRI have conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
+One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examination of how different firefighting tactics affect the fire environment.
+NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
 The studies have resulted in guidance to the fire service regarding ventilation tactics.
-However, ventilation tactics alone will not result in the extinguishment of the fire; fire suppression with hose streams is also needed.
+However, ventilation tactics alone will not extinguish the fire; fire suppression with hose streams is also needed.
 
 Fire suppression tactics using hose streams also affect the ventilation in a structure and may impact the movement of smoke and heat through a structure.
-As vents are made to advance the hoseline or if ventilation inducing handline tactics are in practice, hose stream impacts on ventilation may be even more significant.
+If vents are made to advance the hoseline or if ventilation inducing handline tactics are in practice, hose stream impacts on ventilation may be even more significant.
 Additional research addressing the coordination of suppression tactics and the impact on ventilation is needed to complete recommendations on fire control tactics to appropriate standards, education, and training documents.
@@
 However, increasing the angle decreases the distance reached by the stream and its penetration power.
-%\textit{Essentials of Fire Fighting} defines 
-%https://docs.google.com/presentation/d/1hZ5DZhYXxCkcIEHNZKumH48b_Q53iM2D7asXkMYlVMM/embed?hl=en&size=l&slide=id.p39
 
-%http://www.tft.com/literature/library/files/bfa.pdf
-%Keith Royer, "Water for Fire Fighting", (Engineering Extension Service, Iowa State University, Ames, Iowa) p. 6 
 In addition to the type of stream pattern used, the method or motion of the nozzle used to apply the hose stream can also vary.
@@
 \label{sec:objectives}
-This report is concerned with examining the impact of hose stream and application pattern, or nozzle motion, selection on air movement inside two full scale test structures built to represent residential sized structures.
-Numerous experiments containing different flow path configurations were conducted to study the impact of hose stream and nozzle movement selection on ventilation in a structure.
+This report focuses on examining the impact of hose stream and application pattern (or nozzle motion) selection on air movement inside two full-scale test structures built to represent residential sized structures.
+Experiments containing different flow path configurations were conducted to study the impact of hose stream and water application selection on ventilation in a structure.
 More specifically, the experiments were conducted to fulfill the following objectives:
+
 \begin{enumerate}
@@
 \end{enumerate}
-Four types of hose streams and four different nozzle movement patterns were studied throughout the experiments described in this report.
-Three types of hose stream patterns using a combination nozzle were studied: straight stream, narrow fog stream, and wide fog stream.
+
+Four types of hose streams and four nozzle movement patterns patterns were studied as part of the experiments described in this report.
+Three of the hose stream patterns studied were from a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
 Water was flowed into the structure by having the hose in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
-Additionally, a set of experiments comparing the impact of a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1~in tip on air flows in a structure was conducted.
+Additionally, experiments comparing the differences in impact on air flows in a structure from a combination nozzle straight stream and a solid stream from a smooth bore nozzle equipped with a 1~in tip were conducted.
 Images of the four types of hose streams are presented in Fig.~\ref{fig:hose_streams}.

### 2016-06-16 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added test matrix to hose stream report; fixed channel list spacing in gas burner report

@@
 
-A total of seven experiments were conducted to study the impact of different hose stream and nozzle movement patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
+A total of seven experimental series, summarized in Table~\ref{table:test_matrix}, were conducted to study the impact of different hose stream and nozzle motion patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
 Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern.
 The experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on impact of the motion of the nozzle.
+
+\begin{table}[!ht]
+\caption{Summary of the seven experimental test series}
+\begin{tabular}{ccclll}
+ \toprule
+\textbf{Test \#} & \textbf{Appliance} & \textbf{Structure} & 
+\begin{tabular}{@{}l} \textbf{Flow Path} \\ \textbf{Configuration} \end{tabular} &
+\textbf{Streams} & \textbf{Nozzle Motion} \\
+\midrule
+1 & Monitor & \begin{tabular}{@{}c@{}} Single \\ Story \end{tabular} & U-shaped & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
+Fixed position 
+\\~\\
+2 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
+\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust lower \\ level south side \\ and upper level \\ north side \end{tabular} & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & Fixed position
+\\~\\
+3 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
+\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & Fixed position
+\\~\\
+4 & Monitor & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
+\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
+\begin{tabular}{@{}l} Straight, \\ Solid \\ (180~gpm) \end{tabular} & Fixed position
+\\~\\
+5 & Handline & \begin{tabular}{@{}c@{}} Single \\ Story \end{tabular} & U-shaped & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
+\begin{tabular}{@{}l} Fixed at ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular}
+\\~\\
+6 & Handline & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
+\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ exhaust lower \\ level south side \\ and upper level \\ north side \end{tabular} & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
+\begin{tabular}{@{}l} Fixed at ceiling, \\ Sweeping ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular}
+\\~\\
+7 & Handline & \begin{tabular}{@{}c@{}} Two \\ Story \end{tabular} & 
+\begin{tabular}{@{}l} Nozzle lower \\ level north side, \\ Exhaust upper \\ level north side \end{tabular} & 
+\begin{tabular}{@{}l} Straight, \\ Narrow fog, \\ Wide fog \\ (120~gpm) \end{tabular} & 
+\begin{tabular}{@{}l} Fixed at ceiling, \\ Sweeping ceiling, \\ Rotated CW, \\ Rotated CCW \end{tabular} \\
+\bottomrule
+\end{tabular}
+\label{table:test_matrix}
+\end{table}
 
@@
 \end{figure}
-\FloatBarrier
 
-Three different structure flow path configurations were used for the seven experiments.
-Tests~1 and 5 were conducted in the Single Story Structure and used the configuration shown in Fig.~\ref{fig:east_setup}.
+Three different structure flow path configurations were used for the seven experimental series.
+Tests~1 and 5 were conducted in the Single Story Structure and used a ``U-shaped'' configuration shown in Fig.~\ref{fig:east_setup}.
 Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.
 
-Two different flow path configurations were used for experiments conducted in the Two Story Structure.
+Two different flow path configurations were used for the test series conducted in the Two Story Structure.
 The main difference between the two flow paths was the position of the south side door on the first level.
@@
 \label{sec:monitor_procedure}
-Three experiments, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
+Three experimental series, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
 Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure.
-A fourth experiment, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
+A fourth series, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
 The monitor was always set to flow water from a fixed position.
@@
 Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3.
-The stairwell door was opened for the entire experiment.
+The stairwell door was opened for the entire experimental series.
 The test began by flowing water in a straight stream from a combination nozzle aimed at the near target.
@@
 \label{sec:handline_procedure}
-Three experiments were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
-One test, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure.
+Three experimental series were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
+One series, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure.
 All three tests primarily focused on the impact of different hose stream and nozzle motion pattern selections on air movement in a structure.
@@
 Test~6 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_1}, and Test~7 contained the flow path configuration presented in Fig.~\ref{fig:flow_path_2}.
-Each experiment began by using a straight stream to flow water in a fixed, horizontal position.
+Each test began by using a straight stream to flow water in a fixed, horizontal position.
 After 60 seconds of water flow, the stairwell door was opened.
@@
 \small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
-\\ \multicolumn{9}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
@@
 \small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
-\\ \multicolumn{9}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
@@
 \small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
-\\ \multicolumn{9}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Smooth Bore}} &
 \small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
-\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} 
-\\
+\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} \\
 \bottomrule
@@
 \small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
-\\ \multicolumn{5}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
@@
 \small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
-\\ \multicolumn{5}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
@@
 \small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
-\\ \multicolumn{5}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
@@
 \small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
-\\ \multicolumn{5}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
 \small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
-\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$)  
-\\ \bottomrule
+\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$) \\ 
+\bottomrule
 \end{tabular}
@@
 \small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
-\\ \multicolumn{6}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
@@
 \small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
-\\ \multicolumn{6}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
 \small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
-\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$)
-\\ \midrule
+\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$) \\ 
+\midrule
  & & \multicolumn{4}{c}{\underline{Test 7}}
@@
 \small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
-\\ \multicolumn{6}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
@@
 \small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
-\\ \multicolumn{6}{c}{} \\
+\\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
 \small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
-\\ \bottomrule
+\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$) \\ 
+\bottomrule
 \end{tabular}
@@
 
-A total of seven experiments were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
+A total of seven experimental series were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
 
-Three experiments studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure for different ventilation configurations.
-For each of the three experiments, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure.
+Three experimental series studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure for different ventilation configurations.
+For each of the three series, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure.
 The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream.
 
-Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
+Additionally, a fourth experimental series using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
 The streams were compared for six different 60 seconds periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
-The results from the four monitor experiments suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
+The results from the four monitor test series suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
 
-In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and nozzle movement pattern combinations on air movement within a structure.
+In addition to the monitor test series, three different experimental series were conducted using a handline to study the impact of different stream and nozzle movement pattern combinations on air movement within a structure.
 Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream.
 In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern.
-Additionally, throughout all handline experiments, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
+Additionally, throughout all handline test series, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
 

### 2016-06-16 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated instrumentation dimensions in channel list
Added test matrix to hose stream report; fixed channel list spacing in gas burner report

@@
 The East Structure was designed to simulate a single-story residential structure, and the West Structure was designed to simulate a two-story residential structure.
+
+\subsubsection{First Floor of Both Structures}
 The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
@@
 
+\subsubsection{Second Floor of West Structure}
 The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
@@
 \label{sec:layout}
+
+\subsubsection{Dimensions}
 Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
@@
 
+\FloatBarrier
+
 The ceiling height of each structure was approximately 2.4~m (8~ft).
@@
 The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
-\FloatBarrier
+The exterior doors were made of steel, and the stairwell door on the second level of the West Structure was made of lauan plywood.
+% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to
+
+\subsubsection{Leakage}
+An air leakage measurement system was used to measure the amount of leakage associated with each structure.
+The amount of leakage in the East Structure was measured as 0.024~m$^2$.
+For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed and as 0.054~m$^2$ when the stairway door was opened.
 
@@
 The flow of propane to each burner was controlled by a high-precision turn valve, and the total displaced gas volume was measured using a rotary gas meter.
-% INCLUDE HRR CALCULATIONS HERE
 
@@
 \clearpage
-% MEASUREMENT TYPE FOR BDPs = 'Velocity' OR 'Pressure'?
+
 \begin{longtable}[c]{c|lll}
@@
 \multirow{16}{*}{\large{\textbf{A7}}}
- & TC\_A7\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A7\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A7\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A7\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A7\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A7\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A7\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A7\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A7\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A7\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A7\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A7\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A7\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A7\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A7\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A7\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A7\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A7\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A7\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A7\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A7\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A7\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A7\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A7\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A7\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A7\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A7\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A7\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A7\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A7\_8 & 1.95~m below soffit  & Velocity \\
 \bottomrule
@@
 \multirow{16}{*}{\large{\textbf{A8}}}
- & TC\_A8\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A8\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A8\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A8\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A8\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A8\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A8\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A8\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A8\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A8\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A8\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A8\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A8\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A8\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A8\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A8\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A8\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A8\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A8\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A8\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A8\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A8\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A8\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A8\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A8\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A8\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A8\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A8\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A8\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A8\_8 & 1.95~m below soffit  & Velocity \\
 \midrule
 \multirow{16}{*}{\large{\textbf{A9}}}
- & TC\_A9\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A9\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A9\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A9\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A9\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A9\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A9\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A9\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A9\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A9\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A9\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A9\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A9\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A9\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A9\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A9\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A9\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A9\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A9\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A9\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A9\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A9\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A9\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A9\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A9\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A9\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A9\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A9\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A9\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A9\_8 & 1.95~m below soffit  & Velocity \\
 \midrule
@@
 The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.
-% \clearpage
 
@@
 \multirow{16}{*}{\large{\textbf{A5}}}
- & TC\_A5\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A5\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A5\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A5\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A5\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A5\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A5\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A5\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A5\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A5\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A5\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A5\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A5\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A5\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A5\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A5\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A5\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A5\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A5\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A5\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A5\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A5\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A5\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A5\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A5\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A5\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A5\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A5\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A5\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A5\_8 & 1.95~m below soffit  & Velocity \\
 \bottomrule
@@
 \multirow{16}{*}{\large{\textbf{A6}}}
- & TC\_A6\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A6\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A6\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A6\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A6\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A6\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A6\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A6\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A6\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A6\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A6\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A6\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A6\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A6\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A6\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A6\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A6\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A6\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A6\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A6\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A6\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A6\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A6\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A6\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A6\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A6\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A6\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A6\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A6\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A6\_8 & 1.95~m below soffit  & Velocity \\
 \midrule
@@
 \multirow{19}{*}{\large\textbf{A10}} 
- & TC\_A10\_1  & 0.03~m below soffit & Temperature \\
- & TC\_A10\_2  & 0.30~m below soffit & Temperature \\
+ & TC\_A10\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A10\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A10\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A10\_4  & 0.91~m below soffit & Temperature \\
- & TC\_A10\_5  & 1.22~m below soffit & Temperature \\
- & TC\_A10\_6  & 1.52~m below soffit & Temperature \\
- & TC\_A10\_7  & 1.83~m below soffit & Temperature \\
- & TC\_A10\_8  & 2.13~m below soffit & Temperature \\
-\cline{2-4}
- & BDP\_A10\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A10\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A10\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A10\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A10\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A10\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A10\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A10\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A10\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A10\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A10\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A10\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A10\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A10\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A10\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A10\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A10\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A10\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A10\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A10\_8 & 1.95~m below soffit  & Velocity \\
 \cline{2-4}
@@
 \multirow{16}{*}{\large{\textbf{A11}}}
- & TC\_A11\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A11\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A11\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A11\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A11\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A11\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A11\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A11\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A11\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A11\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A11\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A11\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A11\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A11\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A11\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A11\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A11\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A11\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A11\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A11\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A11\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A11\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A11\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A11\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A11\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A11\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A11\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A11\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A11\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A11\_8 & 1.95~m below soffit  & Velocity \\
 \midrule
 \multirow{16}{*}{\large{\textbf{A13}}}
- & TC\_A13\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A13\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A13\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A13\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A13\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A13\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A13\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A13\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A13\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A13\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A13\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A13\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A13\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A13\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A13\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A13\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A13\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A13\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A13\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A13\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A13\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A13\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A13\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A13\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A13\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A13\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A13\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A13\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A13\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A13\_8 & 1.95~m below soffit  & Velocity \\
 \bottomrule
@@
 \multirow{16}{*}{\large{\textbf{A14}}}
- & TC\_A14\_1  & 0.03~m below soffit  & Temperature \\
- & TC\_A14\_2  & 0.30~m below soffit  & Temperature \\
+ & TC\_A14\_1  & 0.08~m below soffit  & Temperature \\
+ & TC\_A14\_2  & 0.34~m below soffit  & Temperature \\
  & TC\_A14\_3  & 0.61~m below soffit  & Temperature \\
- & TC\_A14\_4  & 0.91~m below soffit  & Temperature \\
- & TC\_A14\_5  & 1.22~m below soffit  & Temperature \\
- & TC\_A14\_6  & 1.52~m below soffit  & Temperature \\
- & TC\_A14\_7  & 1.83~m below soffit  & Temperature \\
- & TC\_A14\_8  & 2.13~m below soffit  & Temperature \\
-\cline{2-4}
- & BDP\_A14\_1 & 0.03~m below soffit  & Velocity \\
- & BDP\_A14\_2 & 0.30~m below soffit  & Velocity \\
+ & TC\_A14\_4  & 0.88~m below soffit  & Temperature \\
+ & TC\_A14\_5  & 1.15~m below soffit  & Temperature \\
+ & TC\_A14\_6  & 1.42~m below soffit  & Temperature \\
+ & TC\_A14\_7  & 1.68~m below soffit  & Temperature \\
+ & TC\_A14\_8  & 1.95~m below soffit  & Temperature \\
+\cline{2-4}
+ & BDP\_A14\_1 & 0.08~m below soffit  & Velocity \\
+ & BDP\_A14\_2 & 0.34~m below soffit  & Velocity \\
  & BDP\_A14\_3 & 0.61~m below soffit  & Velocity \\
- & BDP\_A14\_4 & 0.91~m below soffit  & Velocity \\
- & BDP\_A14\_5 & 1.22~m below soffit  & Velocity \\
- & BDP\_A14\_6 & 1.52~m below soffit  & Velocity \\
- & BDP\_A14\_7 & 1.83~m below soffit  & Velocity \\
- & BDP\_A14\_8 & 2.13~m below soffit  & Velocity \\
+ & BDP\_A14\_4 & 0.88~m below soffit  & Velocity \\
+ & BDP\_A14\_5 & 1.15~m below soffit  & Velocity \\
+ & BDP\_A14\_6 & 1.42~m below soffit  & Velocity \\
+ & BDP\_A14\_7 & 1.68~m below soffit  & Velocity \\
+ & BDP\_A14\_8 & 1.95~m below soffit  & Velocity \\
 \midrule
 \multirow{3}{*}{\large{\textbf{A16}}}
- & HF\_2\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
- & HF\_2\_V   & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
+ & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
+ & HF\_2\_V   & \begin{tabular}{@{}l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
 \midrule
 \multirow{3}{*}{\large{\textbf{A17}}}
- & HF\_1\_H	  & \begin{tabular}{l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
- & HF\_1\_V	  & \begin{tabular}{l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
+ & HF\_1\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
+ & HF\_1\_V	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
 \bottomrule
@@
 Five different tests, Tests 2--6, were conducted in the East Structure.
-Table~\ref{table:HRR_East} lists the heat release rates for each experiment.
+Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for each experiment.
 The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
@@
 
+\subsection{Tests 2--4}
 Tests~2--4 followed an identical order of events.
@@
 
-The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
-Tests~5 and 6 involved repeating a specific set of events three times in a row.
-To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.
-
 \begin{table}[!ht]
-\caption{Heat Release Rates for East Structure Tests}
+\caption{Heat Release Rates for Tests~2--4}
 \begin{tabular}{lccccc}
@@
 Test 4				& 350 & 650	& 950 & 650 & 340 \\
-\midrule
- & \multicolumn{2}{c}{\textbf{Heat Release Rate (kW)}} & \multicolumn{3}{c}{} \\
-\textbf{Test} 		& \multicolumn{2}{c}{All Burners On} 
-& \multicolumn{3}{c}{} \\
-\midrule
-Test 5 - Seq. 1		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
-Test 5 - Seq. 2		& \multicolumn{2}{c}{730} & \multicolumn{3}{c}{} \\
-Test 5 - Seq. 3		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 1		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 2		& \multicolumn{2}{c}{720} & \multicolumn{3}{c}{} \\
-Test 6 - Seq. 3		& \multicolumn{2}{c}{710} & \multicolumn{3}{c}{} \\
 \bottomrule
 \end{tabular}
-\label{table:HRR_East}
+\label{table:HRR_Tests_2-4}
 \end{table}
@@
 \end{figure}
+\clearpage
+
+\subsection{Tests 5 \& 6}
+The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
+Tests~5 and 6 involved repeating a specific set of events three times in a row.
+To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.
+
+\begin{table}[!ht]
+\caption{Heat Release Rates for Tests~5 and 6}
+\begin{tabular}{lc}
+ \toprule
+ & \textbf{Heat Release Rate (kW)} \\
+\textbf{Test} & \textbf{All Burners On} \\
+\midrule
+Test 5 - Seq. 1		& 730 \\
+Test 5 - Seq. 2		& 730 \\
+Test 5 - Seq. 3		& 720 \\
+Test 6 - Seq. 1		& 720 \\
+Test 6 - Seq. 2		& 720 \\
+Test 6 - Seq. 3		& 710 \\
+\bottomrule
+\end{tabular}
+\label{table:HRR_Tests_5-6}
+\end{table}
 
@@
 
+\subsection{Tests~22 \& 23}
 Tests~22 and 23 followed an identical procedure to change the ventilation.
@@
 Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
-A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors was used during the tests to change the ventilation pattern within the structure.
-During Tests~22 and 23, the fan was aimed at the center of both double doors, and during Tests~24 and 25, the fan was aimed at the center of the west double door.
-
+A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
 \begin{figure}[!ht]
@@
 
+\subsection{Tests~24 \& 25}
+Similar to Tests~22 and 23, Tests~24 and 25 followed an identical procedure to change the ventilation.
+Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25.
+A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
+
 \begin{figure}[!ht]
@@
 \end{figure}
-\FloatBarrier
-
 \clearpage

### 2016-06-17 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor edits to hose stream report, new flow meter picture
Updated acknowledgements section of hose stream report

@@
 Joseph M. Willi \\
-Daniel Madrzykowski \\
-Craig G. Weinschenk \\
+Daniel Madrzykowski$^*$ \\
+Craig G. Weinschenk$^+$ \\
 {\em Fire Research Division \\
@@
 \vspace*{2\baselineskip}
-September 2015}}
+June 2016}
+
+\vspace*{2\baselineskip}
+\textit{$^*$\small Currently with UL FSRI}
+\\
+\textit{$^+$\small Currently with JENSEN HUGHES}
+}
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=4in]{../Figures/Pictures/flow_meter}
+	\includegraphics[width=3in]{../Figures/Pictures/flow_meter}
 	\caption[Flow meter used to measure flow rate during experiments.]{Pressure and flow meter combination used to measure water flow rate during the experiments.}
@@
 % ==========================
-
 \chapter{Results and Discussion}
@@
 
-The authors would like to thank Roy McLane, Kristopher Overholt, Keith Stakes, Nicholas Dow, and Jay MCElroy from NIST for their contributions in preparing and conducting these experiments.
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
 These experiments could not have been conducted without them.

### 2016-06-22 Projects/DelCo_2012/Report/DelCo_2012.tex
updates to CAFS, added pdfs that are one off plots

@@
 \headerB{
-Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
+Examination of Compressed Air Foam (CAF) for Interior Firefighting
 }
@@
 \flushright{
-Craig G. Weinschenk \\
-Daniel Madrzykowski \\
-Keith M. Stakes \\
+Craig G. Weinschenk $^+$ \\
+Daniel Madrzykowski $^*$ \\
+Keith M. Stakes $^*$ \\
 Joseph M. Willi \\
@@
 \vspace*{2\baselineskip}
-February 2016}}
+July 2016}
+
+\vspace*{2\baselineskip}
+\textit{$^+$\small Currently with JENSEN HUGHES}
+\\
+\textit{$^*$\small Currently with UL FSRI}
+}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (February 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (July 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAF for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2012,LaPolla:2012}.
+This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 The research findings are provide information with the potential to improve the safe and effective use of CAFS for structural firefighting.
@@
 
-The 88 gas cooling experiments were completed as part of 9 separate tests in the burn building.
+The 88 gas cooling events were completed as part of 9 separate tests in the burn building.
 During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
 Once this criteria was met, gas cooling began.
+Figure~\ref{fig:gas_cooling_exp4} shows 19 cooling events at one thermocouple array during a continuous test.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time series of several gas cooling events in a continuous experiment}
+	\caption{Time series of several gas cooling events in a continuous test}
 	\label{fig:gas_cooling_exp4}
@@
 
-To compare the effectiveness of the suppression agents (CAFS, water), the temperatures from the thermocouple tree which was not directly impacted by the streams was analyzed.
-Thermocouples that were greater than 2.13~m (7~ft) below the ceiling (the bottom 3 thermocouples) were not included because of the minimal temperature readings throughout the tests.
-Gas cooling was determined by taking the normalized maximum change in temperature ($\hat{T}$) over the test interval ($T_{max}$ is peak temperature before suppression and $T_{min}$ is minimum temperature after suppression):
-\begin{equation}
-\label{eq:norm_temp}
-\hat{T} = \frac{T_{max}-T_{min}}{T_{max}}
-\end{equation}
-The normalized temperature difference is taken because of the variation in pre-suppression temperature within replicates of a particular suppression agent and between suppression agents.
-
-For the 7/8~in solid stream tests there were 7 replicate conducted for both water and CAFs suppression.
-The normalized temperature differences for the 8 thermocouples analyzed from the water experiments were compared against the same normalized temperature differences from the CAFs tests.
-These data points are visualized through a scatterplot, Fig.~\ref{fig:CAFS_Water_Comp_7_8}.
+There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}).
+Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAFS tests, respectively.
+For both sets a solid 7/8 in nozzle in the middle position was used.
+The data shows that thermocouples in the plot in the upper right of both figures has more significant temperature drops than the other two arrays; this is likely a result of that thermocouple array being directly ``hit'' by the suppression stream.
+
+\begin{figure}[ht!]
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
+	\caption{Time series of several gas cooling events in a continuous test}
+	\label{fig:gas_cooling_sub1}
+\end{figure}
+
+\begin{figure}[ht!]
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A1}
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A2}
+	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
+	\caption{Time series of several gas cooling events in a continuous test}
+	\label{fig:gas_cooling_sub5}
+\end{figure}
+
+\clearpage
+
+To better quantify the effectiveness of the suppression agents (CAFS, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
+Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for the 30 replicate tests, 15 water and 15 CAFS, for all streams aimed at all positions.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_all_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for all replicate tests}
+	\label{fig:combined_all}
+\end{figure}
+
+The circles in Fig.~\ref{fig:combined_all} are the maximum temperature differences for each measurement point for all the replicate cooling events.
+If water and CAFs have the exact same temperature differences, all of the points would fall along solid black line in the figure.
+Circles that vary from that line represent measurements where either water (above) or CAFS (below) cooled more signifcantly than the other agent.
+The gray area surrounding the solid black line, represents measurement uncertainty (\ref{subsec:Uncertainty}).
+For data that fall within this area, there is an inability to determine which agent was more or less effective than the other.
+The red dashed line is the line the describes the data by minimizing the differences between the two suppression agents through a linear approximation of the data.
+Since this line falls within the gray area there is an inability to distinguish, with statistical confidence, a difference between water or CAFs to cool gases by combining all of the replicate tests.
 
@@
 \end{figure}
-
-The circles in Fig.~\ref{fig:CAFS_Water_Comp_7_8} are the normalized temperature measure points.
-If water and CAFs had the exact same normalized temperature differences, all of the points would fall along solid black line in the figure.
-Circles that vary from that line represent measurements where either water or CAFS cooled more signifcantly than the other agent.
-The gray area surrounding the solid black line, represents measurment uncertainty (\ref{subsec:Uncertainty}).
-For data that fall within this area, there is an inability to determine which agent was more or less effective than the other.
-The red dashed line is the line the fits the data representing the minimal difference between the two suppression agents by a linear approximation of the data.
-Since this line falls within the gray area there is an inability to distinguish, with statistical confidence, a difference between water or CAFs to cool gases from a 7/8~in solid stream.
 
@@
 
+\chapter{Acknowledgments}
+\label{chap:acknowledgments}
+
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
+These experiments could not have been conducted without them.
+
+The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments. The Delaware County team was under the direction of Kerby Kerber.
+
+Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
+
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}

### 2016-06-24 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added abstract to hose stream report

@@
 % ft \> foot \\
-% GPM \> gallons per minute \\
+% gpm \> gallons per minute \\
 % in \> inch \\
@@
 \mainmatter
+
+\chapter*{\centering Abstract}
+\pagenumbering{gobble}
+
+Fire suppression tactics using hose streams can affect ventilation in a structure and may impact the movement of smoke and heat through a structure.
+Seven series of experiments were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
+The experiments studied four different hose streams: a straight stream, narrow fog stream, and a wide fog stream from a combination nozzle and a solid stream from a smooth bore nozzle.
+The streams were applied in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
+Gas velocity was measured at different locations in the structure during the experiments.
+The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum of 2.6~m/s, followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
+It was discovered that the straight stream only caused significant air movement through the structure when it was applied in a moving pattern.
+Furthermore, there were no statistically significant differences in the average measured air velocity between the clockwise and counterclockwise nozzle movement patterns.
+It was determined that the type of hose stream and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure.
+To better quantify the impact of such air flows on the fire environment, additional fire experiments need to be conducted with structure fires in a controlled environment.
 
@@
 \label{sec:background}
+
 One of the objectives of the Fire Research Division at the National Institute of Standards and Technology (NIST) is to improve the safety and effectiveness of firefighters through improved knowledge of fire behavior and examination of how different firefighting tactics affect the fire environment.
@@
 
-Four types of hose streams and four nozzle movement patterns patterns were studied as part of the experiments described in this report.
+Four types of hose streams and four nozzle movement patterns were studied as part of the experiments described in this report.
 Three of the hose stream patterns studied were from a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
@@
 \multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
+\small{m/s}   &   0.0 $\pm0.01$    &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
+\small{(mph)} &  (-0.1 $\pm0.02$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.5 $\pm0.3$)
 \\~\\
 \multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$)
+\small{m/s}   &   1.3 $\pm0.2$   &   1.2 $\pm0.2$  &   1.2 $\pm0.2$   &  1.3 $\pm0.2$  \\ & 
+\small{(mph)} &  (2.9 $\pm0.5$)  &  (2.8 $\pm0.5$) &  (2.7 $\pm0.5$)  & (2.9 $\pm0.5$)
 \\~\\
 \multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &  -0.2 $\pm0.04$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.7 $\pm0.1$)  &  (2.8 $\pm0.5$) &  (3.1 $\pm0.6$)  & (2.7 $\pm0.5$) \\ 
+\small{m/s}   &   1.0 $\pm0.2$   &   0.7 $\pm0.1$  &   0.9 $\pm0.2$   &  1.0 $\pm0.2$  \\ & 
+\small{(mph)} &  (2.2 $\pm0.4$)  &  (1.6 $\pm0.3$) &  (2.1 $\pm0.4$)  & (2.2 $\pm0.4$) \\ 
 \bottomrule

### 2016-06-24 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -19,16 +19,16 @@ rcParams['ytick.major.pad']='6'
 #  =================
 
 # Specify name
-specify_test = True
+specify_test = False
 specific_name = 'HOSE_IXXAXX'
 
 # Specify year
-specify_year = False
+specify_year = True
 specific_year = '2014'
 
 # Specify structure
-specify_struct = False
-specific_struct = 'East'
+specify_struct = True
+specific_struct = 'West'
 
 # Specify monitor or handline
 specify_type = False
@@ -41,11 +41,11 @@ skip_files = ['_times', '_reduced', '_results', 'description_', 'hose_d', '_rh',
 # = Specify files to generate =
 # =============================
 
-result_file = False       # Generate a .csv file with channel avgs for specified sensor groups
-print_results = False		# print average values for tables in report
+result_file = True       # Generate a .csv file with channel avgs for specified sensor groups
+print_results = True		# print average values for tables in report
 all_channel_plot = False    # Plot of individual channels in sensor group
 group_avg_plot = False     # Plot avg of all channels for sensor group
-stream_avgs_plot = True   # Plot avg of all channels for each stream tested during experiment
+stream_avgs_plot = False   # Plot avg of all channels for each stream tested during experiment
 
 #  =======================
 #  = Directory Locations =

### 2016-06-27 Projects/DelCo_2012/Report/DelCo_2012.tex
update report and plotting script

@@
 \vspace*{2\baselineskip}
-\textit{$^+$\small Currently with JENSEN HUGHES}
+{\em $^+$\small Currently with JENSEN HUGHES}
 \\
-\textit{$^*$\small Currently with UL FSRI}
+{\em $^*$\small Currently with UL FSRI}
 }
@@
 \hspace{1.5in} \= \\
-CAF \> Compressed Air Foam \\
+CAFS \> Compressed Air Foam System \\
 ESTC \> Delaware County Emergency Services Training Center \\
@@
 
-A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAF for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAFS for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
+This project is expected to produce a better understanding of the effectiveness and safety implications of CAFS for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 The research findings are provide information with the potential to improve the safe and effective use of CAFS for structural firefighting.
@@
 
-The key measures were to understand the cooling and suppression capabilities of CAF compared to water.
+The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.
 The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies~\cite{Grant:2011}.
-Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAF.
+Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAFS.
 
@@
 In the wildland, water for firefighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
-CAF increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
+CAFS increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
 Last but not least the compressed air adds energy to the water stream providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
@@
 Departments across the country began to experiment with CAFS systems for use in structural firefighting.
-In most documented cases, the findings about the effectiveness of the CAF were favorable, yet after decades of fire department trials, CAF has still not been significantly incorporated into structural firefighting tactics.
-This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
-
-There has never been a comprehensive scientific study on the use of CAF for structural fire fighting.
-Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
+In most documented cases, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAF has still not been significantly incorporated into structural firefighting tactics.
+This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAFS inside a structure.
+
+There has never been a comprehensive scientific study on the use of CAFS for structural fire fighting.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAFS, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAFS puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
 
@@
 Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in the State of Maryland and was a committed user of CAFS with 35 CAFS front line engines.
-MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAF was being used to fight the fire during an interior attack.
-Concerns were raised within the department regarding the ability of CAF to cool fire gases and absorb heat as well as plain water.
+MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAFS was being used to fight the fire during an interior attack.
+Concerns were raised within the department regarding the ability of CAFS to cool fire gases and absorb heat as well as plain water.
 As a result, on March 4, 2010, the Fire Chief of (MCFRS) issued a General Order prohibiting the use of CAFS during offensive interior attacks.
@@
 All of the experiments were conducted at full scale in compartments and structures that were representitive room sizes in a residential occupancy.
-Technical panel members whose departments rountinely use CAF for structural firefighting were invited and present at many of the fire suppression experiments.
+Technical panel members whose departments rountinely use CAFS for structural firefighting were invited and present at many of the fire suppression experiments.
 The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
@@
 The sections below describe the types of experiments, the experimental facilities, instrumentation, and fuel loads.
-Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAFS for the experiments.
 These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
@@
 The fire suppression series included 18 tests in two single-story experimental structures and one two-story structure.
-Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAFs application as a suppression agent.
+Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAFS application as a suppression agent.
 The nozzle patterns were varied from straight stream to narrow fog.
@@
 For the attic tests, a smooth bore nozzle was used.
-The 4 two-story tests used both water and CAF from a straight-stream nozzle.
+The 4 two-story tests used both water and CAFS from a straight-stream nozzle.
 
@@
 GC11       &  22            & Water  &  Solid 7/8~in Slug  & Back             \\
-GC12       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
-GC13       &  10            & CAF    &  Smooth Bore 7/8~in & Mid              \\
-GC14       &  15            & CAF    &  Smooth Bore 7/8~in & Back             \\
-GC15       &  20            & CAF    &  Smooth Bore 7/8~in & Mid              \\
-GC16       &  15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
-GC17       &  20            & CAF    &  Solid Stream       & Mid             \\
-GC18       &  10            & CAF    &  Solid Stream       & Mid             \\
-GC19       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
-GC20       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
-GC21       &  15            & CAF    &  Solid Stream       & Back             \\
+GC12       &  15            & CAFS    &  Smooth Bore 7/8~in & Back             \\
+GC13       &  10            & CAFS    &  Smooth Bore 7/8~in & Mid              \\
+GC14       &  15            & CAFS    &  Smooth Bore 7/8~in & Back             \\
+GC15       &  20            & CAFS    &  Smooth Bore 7/8~in & Mid              \\
+GC16       &  15            & CAFS    &  30$^{\circ}$ Fog   & Mid              \\
+GC17       &  20            & CAFS    &  Solid Stream       & Mid             \\
+GC18       &  10            & CAFS    &  Solid Stream       & Mid             \\
+GC19       &  15            & CAFS    &  30$^{\circ}$ Fog   & Back             \\
+GC20       &  15            & CAFS    &  30$^{\circ}$ Fog   & Back             \\
+GC21       &  15            & CAFS    &  Solid Stream       & Back             \\
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time series of several gas cooling events in a continuous test}
+	\caption{Time Series of Multiple Gas Cooling Events From a 1 of 9 Tests}
 	\label{fig:gas_cooling_exp4}
@@
 \begin{figure}[ht!]
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
-	\caption{Time series of several gas cooling events in a continuous test}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A1}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A2}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as Suppression Agent}
 	\label{fig:gas_cooling_sub1}
@@
 \begin{figure}[ht!]
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A1}
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A2}
-	\includegraphics[width=.45\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
-	\caption{Time series of several gas cooling events in a continuous test}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A1}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A2}
+	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAFS as Suppression Agent}
 	\label{fig:gas_cooling_sub5}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_all_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for all replicate tests}
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Replicate Tests}
 	\label{fig:combined_all}
@@
 The circles in Fig.~\ref{fig:combined_all} are the maximum temperature differences for each measurement point for all the replicate cooling events.
-If water and CAFs have the exact same temperature differences, all of the points would fall along solid black line in the figure.
-Circles that vary from that line represent measurements where either water (above) or CAFS (below) cooled more signifcantly than the other agent.
+If water and CAFS have the exact same temperature differences, all of the points would fall along solid black line in the figure.
+Circles that vary from that line represent measurements where either water (above) or CAFS (below) cooled more significantly than the other agent.
 The gray area surrounding the solid black line, represents measurement uncertainty (\ref{subsec:Uncertainty}).
@@
 The red dashed line is the line the describes the data by minimizing the differences between the two suppression agents through a linear approximation of the data.
-Since this line falls within the gray area there is an inability to distinguish, with statistical confidence, a difference between water or CAFs to cool gases by combining all of the replicate tests.
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for 7/8 Solid Stream}
-	\label{fig:CAFS_Water_Comp_7_8}
-\end{figure}
-
-The second water and CAFs comparison was to examine 5 replicate tests for a straight stream in the mid-position, Fig.~\ref{fig:CAFS_Water_Comp_SS_mid}.
-The same analysis was performed for this configuration.
-These results also illustrate the inability to discern which suppression agent is more or less effective at gas cooling.
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_A3_scatter}
+Since this line falls above the gray area for the comparison, water shows a better ability to cool gas under the same test criteria as CAFS.
+
+The data can be separated to examine the impact of nozzle position (back or middle position) on the ability to cool gases for each of the suppression agents.
+Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 replicates in the back position and 3 replicates in the middle position respectively.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position}
+	\label{fig:CAFS_Water_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Back Position}
+	\label{fig:CAFS_Water_full}
+\end{figure}
+
+For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) point to water having a slight advantage in gas cooling relative to CAFS.
+At the back position (Fig.~\ref{fig:CAFS_Water_full}), for the three replicate comparisons, the least squared error line falls within the experimental uncertainty.
+This indicates an inability to distinguish between the two suppression agents with statistical confidence.
+The data can be further divided to analyze the impact of the hose stream time on comparison between water and CAFS.
+Figures~\ref{fig:CAFS_Water_78_mid} and \ref{fig:CAFS_Water_SS_mid} show the results for 7 replicate comparisons of a 7/8~in.
+solid stream and 5 replicate comparisons of a straight stream respectively; both aimed at the middle position.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for 7/8~in. Solid Stream Mid Position}
+	\label{fig:CAFS_Water_78_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
-	\label{fig:CAFS_Water_Comp_SS_mid}
-\end{figure}
+	\label{fig:CAFS_Water_SS_mid}
+\end{figure}
+
+The 7 replicate tests comparing water and CAFS from a 7/8~in.
+solid stream nozzle aimed at the middle position show a large bias towards water.
+For the 5 replicate tests with a straight stream nozzle, the line fit through the data falls right at the edge of where there is still uncertainty regarding an assessment of which suppression agent had more cooling.
+
+The back position can also be decomposed as function of stream.
+Figure~\ref{fig:CAFS_Water_SS_back} shows a single comparison between water and CAFS for a straight stream in the back position while Fig.~\ref{fig:CAFS_Water_Fog_back} shows a 2 replicate comparison between water and CAFS for a 30$^{\circ}$ Fog in the back position.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Back Position}
+	\label{fig:CAFS_Water_SS_back}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/30_Fog_full_back_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for 30$^{\circ}$ Fog Back Position}
+	\label{fig:CAFS_Water_Fog_back}
+\end{figure}
+
+For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence.
+The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back})
 
@@
 \midrule
- 1 & CAF~1    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+ 1 & CAFS~1   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
  2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
- 3 & CAF~2 	  &  7/8'' Smooth Bore  	&  120~gpm/60~cfm   & Furniture      & Door            \\
+ 3 & CAFS~2   &  7/8'' Smooth Bore  &  120~gpm/60~cfm   & Furniture      & Door            \\
  4 & Water~2  &  7/8'' Smooth Bore  &  120~gpm    		& Furniture      & Door            \\
  5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 6 & CAF~3    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 6 & CAFS~3   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
  7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 8 & CAF~4    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 8 & CAFS~4   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
  9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
@@
 11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
-12 & CAF~5    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
+12 & CAFS~5   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
-14 & CAF~6    &  30$^{\circ}$ Fog  	&  120~gpm/60~cfm   & Wood           & Door + Window   \\
+14 & CAFS~6   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 \bottomrule[1.25pt]
@@
 
-Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAFs tests.
+Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAFS tests.
 The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
@@
 \midrule
-CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAFS~1 Hallway   & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+CAFS~1 Room      & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
 Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAFS~2 Hallway   & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
+CAFS~2 Room      & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
@@
 Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAFS~3 Hallway   & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
+CAFS~3 Room      & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
 Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
-CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAFS~4 Hallway   & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
+CAFS~4 Room      & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
 Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
-CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
-CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAFS~5 Hallway   & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
+CAFS~5 Room      & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
 Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAFS~6 Hallway   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
+CAFS~6 Room      & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 \bottomrule[1.25pt]
@@
 
-Note that while there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, differences are not substantial.
+Note that while there are some differences in the changes in temperature and heat flux when comparing CAFS to Water, differences are not substantial.
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
@@
 \midrule
- 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
+ 38  & CAFS~7    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
  39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
- 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 40a & CAFS~8a   &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 40b & CAFS~8b   &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
  41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41c & CAF~9b    &  7/8'' Slub      	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41b & CAFS~9    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41c & CAFS~9b   &  7/8'' Slub      	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 
-Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFs tests conducted in the two story structure.
+Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFS tests conducted in the two story structure.
 The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor.
-This remote measurement location proivdes that is isolated from any direct contact from the suppression stream.
+This remote measurement location provides that is isolated from any direct contact from the suppression stream.
 The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door.
@@
 \midrule
-CAF~7 Stairell       & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAFS~7 Stairell      & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
 Water~7 Stairwell    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a Stairwell     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b Stairwell     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+CAFS~8a Stairwell    & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAFS~8b Stairwell    & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
 Class A~1 Stairwell  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a Stairwell     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b Stairwell     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAFS~9a Stairwell    & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAFS~9b Stairwell    & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]
@@
 
-Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAFs to Water, but the differences are not substantial.
+Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAFS to Water, but the differences are not substantial.
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
@@
 
-The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
-During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF, since the injected air, air being a great insulator, would interfere and result in less cooling.
-It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
+The gas cooling experiments were designed to measure the ability of water streams and CAFS streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
+During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS, since the injected air, air being a great insulator, would interfere and result in less cooling.
+It was the belief that the reduced gas cooling capabilities of CAFS may have lead to firefighter injuries during interior fire attacks.
 Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
-There were also thoughts that the CAF would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
+There were also thoughts that the CAFS would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
 
@@
 The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
-When a CAFs stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
+When a CAFS stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
 Also calc the mass of air in the stream.
@@
 Under the conditions of a residential scale room and contents fire it should be no surprise that the results are similar, the mass of water introduced into the hot gas layer is doing the work.
-Air filled bubbles in the CAFs stream had no discernible impact in these experiments.
+Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
 
@@
 \begin{tabular*}{\textwidth}{lr}
-\includegraphics[width=3.2in]{../Figures/Bars/BB2} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB3} \\
-\includegraphics[width=3.2in]{../Figures/Bars/BB4} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB5}
+\includegraphics[width=3.2in]{../Figures/Bars/BB1} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB2} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB3} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB4}
 \end{tabular*}
-\caption{Spray density figures for burn building tests 2 (upper left), 3 (upper right), 4 (lower left), and 5 (lower right).}
-\label{fig:bb_2_5}
+\caption{Spray density figures for burn building tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
+\label{fig:bb_1_4}
 \end{figure}
@@
 \begin{tabular*}{\textwidth}{lr}
-\includegraphics[width=3.2in]{../Figures/Bars/BB6} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB8} \\
-\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB10}
+\includegraphics[width=3.2in]{../Figures/Bars/BB5} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB6} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB7} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB8}
 \end{tabular*}
-\caption{Spray density figures for burn building tests 6 (upper left), 8 (upper right), 9 (lower left), and 10 (lower right).}
-\label{fig:bb_6_10}
+\caption{Spray density figures for burn building tests 5 (upper left), 6 (upper right), 7 (lower left), and 8 (lower right).}
+\label{fig:bb_5_8}
 \end{figure}
@@
 \begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB9} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB10} \\
 \includegraphics[width=3.2in]{../Figures/Bars/BB11} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB12} \\
-\includegraphics[width=3.2in]{../Figures/Bars/BB13} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB14}
+\includegraphics[width=3.2in]{../Figures/Bars/BB12}
 \end{tabular*}
-\caption{Spray density figures for burn building tests 11 (upper left), 12 (upper right), 13 (lower left), and 14 (lower right).}
-\label{fig:bb_11_14}
+\caption{Spray density figures for burn building tests 9 (upper left), 10 (upper right), 11 (lower left), and 12 (lower right).}
+\label{fig:bb_9_12}
 \end{figure}
@@
 \begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB13} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB14} \\
 \includegraphics[width=3.2in]{../Figures/Bars/BB15} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB16} \\
-\includegraphics[width=3.2in]{../Figures/Bars/BB17} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB18}
+\includegraphics[width=3.2in]{../Figures/Bars/BB16}
 \end{tabular*}
-\caption{Spray density figures for burn building tests 15 (upper left), 16 (upper right), 17 (lower left), and 18 (lower right).}
-\label{fig:bb_15_18}
+\caption{Spray density figures for burn building tests 13 (upper left), 14 (upper right), 15 (lower left), and 16 (lower right).}
+\label{fig:bb_13_16}
 \end{figure}
@@
 \begin{tabular*}{\textwidth}{lr}
+\includegraphics[width=3.2in]{../Figures/Bars/BB17} &
+\includegraphics[width=3.2in]{../Figures/Bars/BB18} \\
 \includegraphics[width=3.2in]{../Figures/Bars/BB19} &
-\includegraphics[width=3.2in]{../Figures/Bars/BB20} \\
-\includegraphics[width=3.2in]{../Figures/Bars/BB21} \\
+\includegraphics[width=3.2in]{../Figures/Bars/BB20}
 \end{tabular*}
-\caption{Spray density figures for burn building tests 19 (upper left), 20 (upper right), and 21 (lower).}
+\caption{Spray density figures for burn building tests 17 (upper left), 18 (upper right), 19 (lower left), and 20 (lower right).}
 \label{fig:bb_19_21}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht]
+\centering
+\includegraphics[width=3.2in]{../Figures/Bars/BB21}
+\caption{Spray density figures for burn building test 21.}
+\label{fig:bb_21}
 \end{figure}

### 2016-06-27 Projects/DelCo_2012/Scripts/gas_cooling_plot2.py

@@ -25,14 +25,14 @@ info_file = '../Experimental_Data/Gas_Cooling_Test_Matrix.csv'
 # Location of figures
 plot_dir = '../Figures/Gas_Cooling/'
 # List of sensor groups for each plot
-sensor_groups = [['TC_A1_'],['TC_A3_']]
+sensor_groups = [['TC_A1_'],['TC_A2_'],['TC_A3_']]
 
 # Load exp. timings and description file
 info = pd.read_csv(info_file, index_col=0)
 
 # Skip files
 skip_files = ['_reduced', 'description_','zero','bb','es_','fse','cafs','fsw','_attic','sc','gas_cooling','west_','east_','all_']
-skip_channels = ['_9','_10','_11']
+skip_channels = []#['_9','_10','_11']
 
 #  ===============================
 #  = Loop through all data files =
@@ -51,12 +51,12 @@ for entry in range(0,len(info)):
 	else:
 		print (info['Nozzle'][entry]+ ' ' + info['Position'][entry])
 		num_rep = info['Replicates'][entry]
-		del_TC_1_h2o = np.zeros((8,num_rep))
-		del_TC_2_h2o = np.zeros((8,num_rep))
-		del_TC_3_h2o = np.zeros((8,num_rep))
-		del_TC_1_cafs = np.zeros((8,num_rep))
-		del_TC_2_cafs = np.zeros((8,num_rep))
-		del_TC_3_cafs = np.zeros((8,num_rep))
+		del_TC_1_h2o = np.zeros((11,num_rep))
+		del_TC_2_h2o = np.zeros((11,num_rep))
+		del_TC_3_h2o = np.zeros((11,num_rep))
+		del_TC_1_cafs = np.zeros((11,num_rep))
+		del_TC_2_cafs = np.zeros((11,num_rep))
+		del_TC_3_cafs = np.zeros((11,num_rep))
 
 
 		for reps in range(0,num_rep):
@@ -80,31 +80,31 @@ for entry in range(0,len(info)):
 					water_test = 'data'+str(info['Test_Series_Water'][entry+reps])
 					water_test = locals().get(water_test)
 					water_data_interval = water_test[channel][info['Start_Time_Water'][entry+reps]:info['Stop_Time_Water'][entry+reps]]
-					#del_TC_3_h2o[int(channel[6:])-1,reps] = max(water_data_interval) - min(water_data_interval)
[…]

### 2016-06-28 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Dan's final edits to hose stream report; updated HRRs & construction description in burner report

@@
 The experiments studied four different hose streams: a straight stream, narrow fog stream, and a wide fog stream from a combination nozzle and a solid stream from a smooth bore nozzle.
-The streams were applied in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
+The streams were applied from a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
 Gas velocity was measured at different locations in the structure during the experiments.
-The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum of 2.6~m/s, followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
-It was discovered that the straight stream only caused significant air movement through the structure when it was applied in a moving pattern.
+The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum velocity of 2.6~m/s (5.8~mph) and maximum air flow rate of approximately 4.2~m$^3$/s (9000~cfm), followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
+It was discovered that the straight stream only caused air movement through the structure when it was applied in a moving pattern.
 Furthermore, there were no statistically significant differences in the average measured air velocity between the clockwise and counterclockwise nozzle movement patterns.
 It was determined that the type of hose stream and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure.
-To better quantify the impact of such air flows on the fire environment, additional fire experiments need to be conducted with structure fires in a controlled environment.
+To better quantify the impact of such air flows on the fire environment, additional experiments need to be conducted with structure fires in a controlled environment.
 
@@
 \begin{enumerate}
-	\item Determine which hose stream patterns and nozzle movement patterns cause significant air movement in a structure 
-	\item Determine the amount of air movement induced by different hose streams and nozzle movement patterns
-
+	\item Determine the amount of air movement induced by different hose streams and nozzle movement patterns.
+	\item Examine Royer's nozzle movement theory on the direction of nozzle rotation.
 \end{enumerate}
@@
 Looking at the table and figures, a number of trends can be observed.
-For example, there was significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1.
+For example, there was air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established for every hose stream and target location combination except the straight stream in Test~1.
 Looking at Table~\ref{table:all_mon_vel_avgs}, the narrow fog and wide fog streams caused higher velocities through the interior doorway when the flow path was fully established compared to the straight stream.
@@
 
-With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and nozzle movement pattern combination using a narrow fog or wide fog stream during the handline experiments produced significant air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
-For the straight stream, however, significant air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
+With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and nozzle movement pattern combination using a narrow fog or wide fog stream during the handline experiments produced air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
+For the straight stream, however, air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
 Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the nozzle movement patterns using the narrow and wide fog streams than the same patterns using the straight stream.
@@
 Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream.
-In fact, it was discovered that a straight stream only caused significant air movement through the interior doorway when it was applied in a moving pattern.
-Additionally, throughout all handline test series, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
+It was discovered that a straight stream increased air movement through the interior doorway when it was applied in a moving pattern.
+With regard to Royer's theory, throughout all handline test series, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
+However, these experiments only addressed cold flow.
 
@@
 These experiments have shown there is a potential for hose streams to affect air flows within a structure during fire scenarios.
-To better quantify the impact of air flows from hose streams on the fire environment, additional fire experiments need to be conducted with structure fires in a controlled environment.
+To better quantify the impact of air flows from hose streams on the fire environment, additional experiments need to be conducted with structure fires in a controlled environment.
 

### 2016-06-28 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Dan's final edits to hose stream report; updated HRRs & construction description in burner report

@@
 
-The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
-The walls were composed of 16~mm (0.63~in) Type X gypsum board.
+The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
 Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
-The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
 The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
@@
  \midrule
-Test 2 				& 340 & 650	& 900 & 630 & 330 \\
-Test 3 				& 330 & 650	& 910 & 630 & 330 \\
-Test 4				& 350 & 650	& 950 & 650 & 340 \\
+Test 2 				& 560 & 1080 & 1470 & 1070 & 550 \\
+Test 3 				& 530 & 1040 & 1470 & 1050 & 520 \\
+Test 4				& 580 & 1140 & 1580 & 1130 & 580 \\
 \bottomrule
@@
 \midrule
-Test 5 - Seq. 1		& 730 \\
-Test 5 - Seq. 2		& 730 \\
-Test 5 - Seq. 3		& 720 \\
-Test 6 - Seq. 1		& 720 \\
-Test 6 - Seq. 2		& 720 \\
-Test 6 - Seq. 3		& 710 \\
+Test 5 - Seq. 1		& 1190 \\
+Test 5 - Seq. 2		& 1190 \\
+Test 5 - Seq. 3		& 1190 \\
+Test 6 - Seq. 1		& 1190 \\
+Test 6 - Seq. 2		& 1190 \\
+Test 6 - Seq. 3		& 1180 \\
 \bottomrule
@@
  \midrule
-Test 22				&     	760 	  \\
-Test 23				&     	790 	  \\
-Test 24				& 	    790 	  \\
-Test 25				&     	790 	  \\
+Test 22				&     	1240 	  \\
+Test 23				&     	1290 	  \\
+Test 24				& 	    1270 	  \\
+Test 25				&     	1270 	  \\
 \bottomrule

### 2016-06-28 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/Burner_HRRs/Scripts/generate_HRR_data.py
Began to correct gas data for burner tests; airflow rate for hose stream tests

@@ -24,6 +24,9 @@ HRR_df_headers = ['Test', '1 Burner Start', '2 Burners Start',
 HRR_df = pd.read_csv(results_dir+'calculated_HRRs.csv', index_col=0)
 skip_tests = []
 for test in HRR_df['Test']:
+	test = test[:7]
+	if test[-1] == ' ':
+		test = test[:-1]
 	skip_tests.append(test)
 
 inHg_to_psi = 0.491154
@@ -372,7 +375,7 @@ for f in os.listdir(raw_video_dir):
 					print
 					print 'Start/stop for '+str(i-2)+' of 3 burners off'
 
-				if end_time-start_time > 10000:
+				if end_time-start_time > 30000:
 					# offset times by 3 seconds to ensure only the flow rate during the current seq is calculated
 					start_time = start_time+3000
 					end_time = end_time-3000
@@ -474,8 +477,9 @@ for f in os.listdir(raw_video_dir):
 						start_weather_index = generate_timestamp(start_time, video_time_diff, hh_mm_ss)
 						end_weather_index = generate_timestamp(end_time, video_time_diff, hh_mm_ss)
 						
-						T_atm_seq_data = T_atm_data.loc[start_weather_index:end_weather_index]
-						T_atm = np.mean(T_atm_seq_data)
+						# T_atm_seq_data = T_atm_data.loc[start_weather_index:end_weather_index]
+						# T_atm = np.mean(T_atm_seq_data)
+						T_atm = 100.0
 						T_adjust = 1.0-((T_atm-60)/500.0)	# adjustment is 1% reduction/increase per 5 °F above/below 60 °F
 
 						p_atm_seq_data = p_atm_data.loc[start_weather_index:end_weather_index]

### 2016-06-28 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -23,11 +23,11 @@ specify_test = False
 specific_name = 'HOSE_IXXAXX'
 
 # Specify year
-specify_year = True
+specify_year = False
 specific_year = '2014'
 
 # Specify structure
-specify_struct = True
+specify_struct = False
 specific_struct = 'West'
 
 # Specify monitor or handline
@@ -446,6 +446,11 @@ y_min = 0
 conv_inch_h2o = 0.4
 conv_pascal = 248.8
 
+# Door area used to calculate air flow
+west_area = 0.8128*2.032
+east_area = 0.9144*2.032
+m3s_to_cfm = 2118.880003
+
 for f in os.listdir(data_dir):
 	if f.endswith('.csv'):
 		# Skip files with time information or reduced data files
@@ -454,12 +459,9 @@ for f in os.listdir(data_dir):
 
 		# Strip test name from file name
 		test_name = f[:-4]
-		
-		# Skip if not a hose test or Test 20 (lost data)
-		if info['Test Type'][test_name] != 'HOSE' or test_name == 'Test_20_West_063014':
-			continue
 
-		if 'Test_17b_' in test_name:
+		# Skip if not a hose test or Test 20 (lost data)
+		if info['Test Type'][test_name] != 'HOSE' or test_name == 'Test_20_West_063014' or 'Test_17b_' in test_name:
 			continue
 
 		# Determine test year and type
@@ -485,10 +487,12 @@ for f in os.listdir(data_dir):
 			print
 			print ('--- Loaded ' + test_name + ' ---')
 
+		area = east_area
 		# Create group and channel lists
 		if test_year == '2014':
 			if 'West' in test_name:
 				channel_list_file = '../DAQ_Files/DAQ_Files_2014/West_DelCo_DAQ_Channel_List.csv'
+				area = west_area
 			elif 'East' in test_name:
 				channel_list_file = '../DAQ_Files/DAQ_Files_2014/East_DelCo_DAQ_Channel_List.csv'
 			else:
@@ -496,6 +500,7 @@ for f in os.listdir(data_dir):
 		elif test_year == '2015':
 			if 'West' in test_name:
 				channel_list_file = '../DAQ_Files/DAQ_Files_2015/West_DelCo_DAQ_Channel_List.csv'
+				area = west_area
 			else:
 				channel_list_file = '../DAQ_Files/DAQ_Files_2015/East_DelCo_DAQ_Channel_List.csv'
[…]

### 2016-06-28 Projects/DelCo_2012/Report/DelCo_2012.tex

@@
 
-For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) point to water having a slight advantage in gas cooling relative to CAFS.
-At the back position (Fig.~\ref{fig:CAFS_Water_full}), for the three replicate comparisons, the least squared error line falls within the experimental uncertainty.
+For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAFS.
+At the back position (Fig.~\ref{fig:CAFS_Water_full}), for the 3 replicate comparison, the least squared error line falls within the experimental uncertainty.
 This indicates an inability to distinguish between the two suppression agents with statistical confidence.
-The data can be further divided to analyze the impact of the hose stream time on comparison between water and CAFS.
+The data can be further divided to analyze the impact of the nozzle type on comparison between water and CAFS.
 Figures~\ref{fig:CAFS_Water_78_mid} and \ref{fig:CAFS_Water_SS_mid} show the results for 7 replicate comparisons of a 7/8~in.
@@
 solid stream nozzle aimed at the middle position show a large bias towards water.
-For the 5 replicate tests with a straight stream nozzle, the line fit through the data falls right at the edge of where there is still uncertainty regarding an assessment of which suppression agent had more cooling.
-
-The back position can also be decomposed as function of stream.
+For the 5 replicate tests with a straight stream nozzle, the least squared error line fit through the data falls along the edge of the measurement uncertainty bounds on the water side of comparison.
+
+The back position can also be decomposed to compare stream type.
 Figure~\ref{fig:CAFS_Water_SS_back} shows a single comparison between water and CAFS for a straight stream in the back position while Fig.~\ref{fig:CAFS_Water_Fog_back} shows a 2 replicate comparison between water and CAFS for a 30$^{\circ}$ Fog in the back position.
@@
 For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence.
-The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back})
+The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back}) shows that CAFS has better cooling potential compared to water.
 
@@
 
+To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAFS Test 1 as a result of the hallway (first) and room (second) suppression actions.
+
+\begin{figure}[ht!]
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
+	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+	\label{fig:fs_1_1}
+\end{figure}
+
 Note that while there are some differences in the changes in temperature and heat flux when comparing CAFS to Water, differences are not substantial.
@@
 
+\chapter{Fire Suppression Figures}
+\label{app:fire_suppression}
+
+\begin{figure}[ht!]
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
+	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+	\label{fig:app_fs_1}
+\end{figure}
+
+\begin{figure}[ht!]
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
+	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+	\label{fig:app_fs_2}
+\end{figure}
+
 \end{document}

### 2016-06-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 \Author{Daniel Madrzykowski}
-\Year{2015}
+\Year{2016}
 
@@
 \abstract{
-Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.
-The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus reduce the losses from fires.
-However, as the result of the review of several arson homicide cases and a review forensics by the U.S.
-National Academy of Sciences, questions about the lack of the use of science in the practice of fire investigation were raised.
+Unwanted fires result in loss of life and property.
+These fires can also create an adverse economic impact on a community.
+The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus reduce the losses from unwanted fires.
+Questions about the lack of science in the practice of fire investigation have been raised during the review of several arson homicide cases and a forensics science review by the U.S.
+National Academy of Sciences.
 Specifically the National Academy of Sciences indicated that ``...
@@
 \item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
-\item Examining the capability of using numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench scale and full scale fire experiments conducted in this study.
+\item Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
 \end{enumerate}
 This paper highlights the many uncertainties involved in what appear to be simple fire experiments.
-A variety of uncertainties related to the composition of the fuels, measurement methods, and analysis techniques just to list a few of the areas considered.
+Uncertainties related to the composition of the fuels, measurement methods, and analysis techniques are a few of the areas considered.
 The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
@@
 The heat release rate data showed that the variability was greater for more complex fuels.
-While the variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
+The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%.
+However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
 The patterns generated by the polyurethane foam fire, had more variability than the natural gas and the gasoline fire patterns.
@@
 \label{chapter:Introduction}
-
-Uncontrolled fires result in loss of life, property and can create an adverse economic impact on a community.
-Findings from an archaeological site in South Africa, published in 2012, indicate that mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
+\section{Background}
+
+The need for fire investigation and value to society, tools used , example.
+
+\subsection{The need and purpose for Fire Investigation}
+Unwanted fires result in loss of life, property and can create an adverse economic impact on a community.
+Recent findings from an archaeological site in South Africa, indicate that mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
 This is 300 thousand years earlier than previously thought.
-Despite mankind’s extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries~\cite{WHO:2014}.
-Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 populations.
+Despite mankind's extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries~\cite{WHO:2014}.
+Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 people.
 The World Fire Statistics Center collects data from European, North American and a few Asia-Oceania countries.

### 2016-06-29 Projects/DelCo_2012/Report/DelCo_2012.tex
update report, crop two figures, CAFS

@@
 To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAFS Test 1 as a result of the hallway (first) and room (second) suppression actions.
+Fig.~\ref{fig:fs_1_2} shows the same impacts as Fig.~\ref{fig:fs_1_1}, except that the tests used water.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1.
+	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle.
 The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
 	\label{fig:fs_1_1}
+\end{figure}
+
+\begin{figure}[ht!]
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
+	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
+	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+	\label{fig:fs_1_2}
 \end{figure}
@@
 
+\section{Spray density figures for burn building tests}
+
 \begin{figure}[ht]
@@
 
+\section{Spray density figures for experimental structure tests}
+
 \begin{figure}[ht]
@@
 \begin{figure}[ht!]
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1.
+\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
+\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle.
 The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
@@
 
+\clearpage
+
 \begin{figure}[ht!]
@@
 \includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
-	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1.
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle.
 The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
@@
 
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 2 with a 7/8'' 
+Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_3}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 2 with a 7/8'' 
+Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_4}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 3 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_5}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 3 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_6}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 4 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_7}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 4 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_8}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 5 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_11}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 5 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_12}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 6 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_13}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
+\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
+\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 6 with a 30$^{\circ}$ Fog nozzle.
+The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+\label{fig:app_fs_14}
+\end{figure}
+
 \end{document}

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
add figures, update CAFS report

@@
 This indicates an inability to distinguish between the two suppression agents with statistical confidence.
-The data can be further divided to analyze the impact of the nozzle type on comparison between water and CAFS.
+
+To further analyze the data, the temperature differences can be separated by each of the three thermocouples in the fire room.
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
+	\caption{Schematic of  the Gas Cooling Experiments.}
+	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
+\end{figure}
+Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
+Figure~\ref{fig:Burn_Building_Test_18b}, which shows the distribution of the water within the burn building from a spray density test for a straight stream with CAFS at the mid position, highlights the positions of the thermocouple trees.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Bars/BB18b}
+	\caption{Gas Cooling Spray Density Test 18}
+	\label{fig:Burn_Building_Test_18b}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A1}
+	\label{fig:CAFS_Water_A1_all}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A2}
+	\label{fig:CAFS_Water_A2_all}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A3}
+	\label{fig:CAFS_Water_A3_all}
+\end{figure}
+
+% The data can be further divided to analyze the impact of the nozzle type on comparison between water and CAFS.
 Figures~\ref{fig:CAFS_Water_78_mid} and \ref{fig:CAFS_Water_SS_mid} show the results for 7 replicate comparisons of a 7/8~in.
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for 7/8~in. Solid Stream Mid Position}
-	\label{fig:CAFS_Water_78_mid}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
-	\label{fig:CAFS_Water_SS_mid}
-\end{figure}
-
-The 7 replicate tests comparing water and CAFS from a 7/8~in.
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
+% 	\caption{CAFS vs Water Gas Cooling Comparison for 7/8~in. Solid Stream Mid Position}
+% 	\label{fig:CAFS_Water_78_mid}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
+% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
+% 	\label{fig:CAFS_Water_SS_mid}
+% \end{figure}
+
+% The 7 replicate tests comparing water and CAFS from a 7/8~in.
 solid stream nozzle aimed at the middle position show a large bias towards water.
@@
 
-The back position can also be decomposed to compare stream type.
+% The back position can also be decomposed to compare stream type.
 Figure~\ref{fig:CAFS_Water_SS_back} shows a single comparison between water and CAFS for a straight stream in the back position while Fig.~\ref{fig:CAFS_Water_Fog_back} shows a 2 replicate comparison between water and CAFS for a 30$^{\circ}$ Fog in the back position.
 
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Back Position}
-	\label{fig:CAFS_Water_SS_back}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/30_Fog_full_back_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for 30$^{\circ}$ Fog Back Position}
-	\label{fig:CAFS_Water_Fog_back}
-\end{figure}
-
-For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence.
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
+% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Back Position}
+% 	\label{fig:CAFS_Water_SS_back}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/30_Fog_full_back_scatter}
+% 	\caption{CAFS vs Water Gas Cooling Comparison for 30$^{\circ}$ Fog Back Position}
+% 	\label{fig:CAFS_Water_Fog_back}
+% \end{figure}
+
+% For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence.
 The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back}) shows that CAFS has better cooling potential compared to water.

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update CAFS report

@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Middle Position Replicates}
 	\label{fig:CAFS_Water_mid}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Back Position}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Back Position Replicates}
 	\label{fig:CAFS_Water_full}
@@
 Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
-Figure~\ref{fig:Burn_Building_Test_18b}, which shows the distribution of the water within the burn building from a spray density test for a straight stream with CAFS at the mid position, highlights the positions of the thermocouple trees.
-
+Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAFS at the mid position compared to the positions of the thermocouple trees.
 \begin{figure}[!ht]
@@
 
+There is a difference in the amount of direct impact from the suppression agent at the three spatial locations.
+Therefore, the maximum temperature differences for each thermocouple on the three different arrays should also be analyzed separately.
+Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively.
+Note that for thermocouple array A3, which has the least amount of direct suppression, the least squared error line is closest to the uniform impact line (black solid line) meaning that within the experimental uncertainty, water and CAFS are indistinguishable.
+Thermocouple array A3 also has the strongest statistical fit compared to arrays A1 and A2.
+
 \begin{figure}[!ht]
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A1}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Replicates}
 	\label{fig:CAFS_Water_A1_all}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A2}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Replicates}
 	\label{fig:CAFS_Water_A2_all}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Thermocouple Tree A3}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Replicates}
 	\label{fig:CAFS_Water_A3_all}
@@
 
-% The data can be further divided to analyze the impact of the nozzle type on comparison between water and CAFS.
-Figures~\ref{fig:CAFS_Water_78_mid} and \ref{fig:CAFS_Water_SS_mid} show the results for 7 replicate comparisons of a 7/8~in.
-solid stream and 5 replicate comparisons of a straight stream respectively; both aimed at the middle position.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/7_8_Solid_mid_scatter}
-% 	\caption{CAFS vs Water Gas Cooling Comparison for 7/8~in. Solid Stream Mid Position}
-% 	\label{fig:CAFS_Water_78_mid}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_mid_scatter}
-% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Mid Position}
-% 	\label{fig:CAFS_Water_SS_mid}
-% \end{figure}
-
-% The 7 replicate tests comparing water and CAFS from a 7/8~in.
-solid stream nozzle aimed at the middle position show a large bias towards water.
-For the 5 replicate tests with a straight stream nozzle, the least squared error line fit through the data falls along the edge of the measurement uncertainty bounds on the water side of comparison.
-
-% The back position can also be decomposed to compare stream type.
-Figure~\ref{fig:CAFS_Water_SS_back} shows a single comparison between water and CAFS for a straight stream in the back position while Fig.~\ref{fig:CAFS_Water_Fog_back} shows a 2 replicate comparison between water and CAFS for a 30$^{\circ}$ Fog in the back position.
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/SS_full_back_scatter}
-% 	\caption{CAFS vs Water Gas Cooling Comparison for Straight Stream Back Position}
-% 	\label{fig:CAFS_Water_SS_back}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/30_Fog_full_back_scatter}
-% 	\caption{CAFS vs Water Gas Cooling Comparison for 30$^{\circ}$ Fog Back Position}
-% 	\label{fig:CAFS_Water_Fog_back}
-% \end{figure}
-
-% For the straight stream comparison (Fig.~\ref{fig:CAFS_Water_SS_back}), there is an inability to distinguish between the suppression agents with statistical confidence.
-The 30$^{\circ}$ Fog replicate comparison (Fig.~\ref{fig:CAFS_Water_Fog_back}) shows that CAFS has better cooling potential compared to water.
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
+	\label{fig:CAFS_Water_A1_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
+	\label{fig:CAFS_Water_A2_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
+	\label{fig:CAFS_Water_A3_mid}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
+	\label{fig:CAFS_Water_A1_back}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
+	\label{fig:CAFS_Water_A2_back}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
+	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
+	\label{fig:CAFS_Water_A3_back}
+\end{figure}
 

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Acknowledgements
Adding names to section - still needs work

@@
 
-The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments. The Delaware County team was under the direction of Kerby Kerber.
+Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.
+Alan Butsch,   Brian Rojas,  Michael Johns, Chris Riley
+
+The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments.
+The Delaware County team was under the direction of Kerby Kerber.
+For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale and Todd John.
+
+Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
+
+  We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
 

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
update CAFS report

@@
 There is a difference in the amount of direct impact from the suppression agent at the three spatial locations.
-Therefore, the maximum temperature differences for each thermocouple on the three different arrays should also be analyzed separately.
+Therefore, the maximum temperature differences for each thermocouple on each of the three arrays should also be analyzed separately.
 Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively.
-Note that for thermocouple array A3, which has the least amount of direct suppression, the least squared error line is closest to the uniform impact line (black solid line) meaning that within the experimental uncertainty, water and CAFS are indistinguishable.
-Thermocouple array A3 also has the strongest statistical fit compared to arrays A1 and A2.
+Note that thermocouple array A3, the array which has the least amount of direct suppression, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
+The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAFS and water are indistinguishable.
+Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAFS.
 
@@
 \end{figure}
+
+\clearpage
+
+The thermocouple array data can also also be decomposed as a function of nozzle position: 12 middle position replicates and 3 back position replicates.
+Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position.
+Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 3 replicate tests with the monitor nozzle in the back position.
 
@@
 
-Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
-
 We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.

### 2016-06-30 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
minor edit to ppe report
Update BIB and PPE
added Klaene ref   and acknowledge

@@
 
+\begin{figure}[ht!]
+\includegraphics[width=\columnwidth]{../../../Projects/Gear_Plunge_Tests/Figures/Plunge_2}
+\caption{Image of plunge test apparatus configured to test a turnout gear sample.}
+\label{fig:plunge_pic}
+\end{figure}
+
 \subsection{Thermal Flow Loop}
@@
 
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
+These experiments could not have been conducted without them.
+
+Appreciation is extended to Firefighter Jacob Hoffman, Toledo Fire Department, Deputy Chief Cecil Clay (ret), Oklahoma City Fire Department, Director John Culbertson, Montana State University Fire Services Training School and their organizations for their support of this research.
+
+The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments.
+The Delaware county team was under the direction of Kerby Kerber.
+For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection).
+We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
+
+Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
+
 \bibliography{../../../Bibliography/FDS_refs,../../../Bibliography/FDS_general}

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
fix SS/SB wording in CAFS

@@
 \hspace{1.5in} \= \\
+CAF \> Compressed Air Foam \\
 CAFS \> Compressed Air Foam System \\
@@
 A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAFS for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of CAFS for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAFS for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAFS and plain water to evaluate the effectiveness of CAFS for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAFS and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
-The research findings are provide information with the potential to improve the safe and effective use of CAFS for structural firefighting.
+This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAF for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+The research findings are provide information with the potential to improve the safe and effective use of CAF for structural firefighting.
 
@@
 
-The key measures were to understand the cooling and suppression capabilities of CAFS compared to water.
-The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAFS during interior attack operations in residential occupancies~\cite{Grant:2011}.
-Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAFS.
+The key measures were to understand the cooling and suppression capabilities of CAF compared to water.
+The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAF during interior attack operations in residential occupancies~\cite{Grant:2011}.
+Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAF.
 
@@
 In the wildland, water for firefighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
-CAFS increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
+CAF increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
 Last but not least the compressed air adds energy to the water stream providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
-These CAFS advantages combine to provide wildland firefighters with a tool that could be used to pre-treat homes and structures to protect them from an approaching fire, or could be used for an exterior (indirect) fire suppression attack on a structure.
+These CAF advantages combine to provide wildland firefighters with a tool that could be used to pre-treat homes and structures to protect them from an approaching fire, or could be used for an exterior (indirect) fire suppression attack on a structure.
 
@@
 
-There has never been a comprehensive scientific study on the use of CAFS for structural fire fighting.
-Fire departments have conducted pilot programs to examine implementation and effectiveness of CAFS, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAFS puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
+There has never been a comprehensive scientific study on the use of CAF for structural fire fighting.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
 
@@
 In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they may have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
-It is important that these distinctions and differences between exterior and interior firefighting with CAFS are understood better.
-
-Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in the State of Maryland and was a committed user of CAFS with 35 CAFS front line engines.
-MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAFS was being used to fight the fire during an interior attack.
-Concerns were raised within the department regarding the ability of CAFS to cool fire gases and absorb heat as well as plain water.
-As a result, on March 4, 2010, the Fire Chief of (MCFRS) issued a General Order prohibiting the use of CAFS during offensive interior attacks.
-In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAFS during structure fires and to report back his findings and recommendations.
+It is important that these distinctions and differences between exterior and interior firefighting with CAF are understood better.
+
+Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in the State of Maryland and was a committed user of CAF with 35 CAFS front line engines.
+MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAF was being used to fight the fire during an interior attack.
+Concerns were raised within the department regarding the ability of CAF to cool fire gases and absorb heat as well as plain water.
+As a result, on March 4, 2010, the Fire Chief of (MCFRS) issued a General Order prohibiting the use of CAF during offensive interior attacks.
+In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAF during structure fires and to report back his findings and recommendations.
 The catalyst for this study was as a result of this order.
@@
 
-All of the experiments were conducted at full scale in compartments and structures that were representitive room sizes in a residential occupancy.
-Technical panel members whose departments rountinely use CAFS for structural firefighting were invited and present at many of the fire suppression experiments.
+All of the experiments were conducted at full scale in compartments and structures that were representative room sizes in a residential occupancy.
+Technical panel members whose departments routinely use CAF for structural firefighting were invited and present at many of the fire suppression experiments.
 The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
@@
 After the wood based fuel package experiments were completed, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
-The issue of a larger fire compartment had also been raised durning the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
+The issue of a larger fire compartment had also been raised during the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
 In order to accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
@@
 The sections below describe the types of experiments, the experimental facilities, instrumentation, and fuel loads.
-Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAFS for the experiments.
+Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
 These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
@@
 Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
-The nozzles chosen for these experiments were: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120 gpm.
+The nozzles chosen for these experiments were: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
 These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application.
@@
 The fire suppression series included 18 tests in two single-story experimental structures and one two-story structure.
-Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAFS application as a suppression agent.
+Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAF application as a suppression agent.
 The nozzle patterns were varied from straight stream to narrow fog.
@@
 For the attic tests, a smooth bore nozzle was used.
-The 4 two-story tests used both water and CAFS from a straight-stream nozzle.
+The 4 two-story tests used both water and CAF from a straight-stream nozzle.
 
@@
 Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments.
-The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAFS.
+The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF.
 Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
@@
 \midrule
-GC1        &  15            & Water  &  Solid Stream       & Back             \\
-GC2        &  23            & Water  &  Solid Stream       & Back             \\
-GC3        &  15            & Water  &  Solid Stream       & Mid              \\
-GC4        &  15            & Water  &  Solid Stream       & Mid              \\
-GC5        &  20            & Water  &  Solid Stream       & Mid              \\
+GC1        &  15            & Water  &  Straight Stream    & Back             \\
+GC2        &  23            & Water  &  Straight Stream    & Back             \\
+GC3        &  15            & Water  &  Straight Stream    & Mid              \\
+GC4        &  15            & Water  &  Straight Stream    & Mid              \\
+GC5        &  20            & Water  &  Straight Stream    & Mid              \\
 GC6        &  21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
@@
 GC9        &  24            & Water  &  30$^{\circ}$ Fog   & Back             \\
-GC10       &  20            & Water  &  Solid 7/8~in Slug  & Back             \\
-GC11       &  22            & Water  &  Solid 7/8~in Slug  & Back             \\
-GC12       &  15            & CAFS    &  Smooth Bore 7/8~in & Back             \\
-GC13       &  10            & CAFS    &  Smooth Bore 7/8~in & Mid              \\
-GC14       &  15            & CAFS    &  Smooth Bore 7/8~in & Back             \\
-GC15       &  20            & CAFS    &  Smooth Bore 7/8~in & Mid              \\
-GC16       &  15            & CAFS    &  30$^{\circ}$ Fog   & Mid              \\
-GC17       &  20            & CAFS    &  Solid Stream       & Mid             \\
-GC18       &  10            & CAFS    &  Solid Stream       & Mid             \\
-GC19       &  15            & CAFS    &  30$^{\circ}$ Fog   & Back             \\
-GC20       &  15            & CAFS    &  30$^{\circ}$ Fog   & Back             \\
-GC21       &  15            & CAFS    &  Solid Stream       & Back             \\
+GC10       &  20            & Water  &  Solid Stream       & Back             \\
+GC11       &  22            & Water  &  Solid Stream       & Back             \\
+GC12       &  15            & CAF    &  Solid Stream       & Back             \\
+GC13       &  10            & CAF    &  Solid Stream       & Mid              \\
+GC14       &  15            & CAF    &  Solid Stream       & Back             \\
+GC15       &  20            & CAF    &  Solid Stream       & Mid              \\
+GC16       &  15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
+GC17       &  20            & CAF    &  Straight Stream    & Mid             \\
+GC18       &  10            & CAF    &  Straight Stream    & Mid             \\
+GC19       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC20       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC21       &  15            & CAF    &  Straight Stream    & Back             \\
 
@@
 \midrule
-SE1        & 7             & Water  &  Solid Stream       &    Fire Room          \\
-SE2        & 18            & Water  &  Solid Stream       &    Fire Room          \\
-SE3        & 19            & Water  &  Solid Stream       &    Fire Room          \\
-SE4        & 21            & Water  &  Solid Stream       &    Fire Room          \\
+SE1        & 7             & Water  &  Straight Stream    &    Fire Room          \\
+SE2        & 18            & Water  &  Straight Stream    &    Fire Room          \\
+SE3        & 19            & Water  &  Straight Stream    &    Fire Room          \\
+SE4        & 21            & Water  &  Straight Stream    &    Fire Room          \\
 SE5        & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
 SE6        & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
-SE7        & 16            & Water  &  Solid 7/8~in Slug  &    Fire Room          \\
-SE8        & 17            & Water  &  Solid 7/8~in Slug  &    Hallway            \\
+SE7        & 16            & Water  &  Solid Stream       &    Fire Room          \\
+SE8        & 17            & Water  &  Solid Stream       &    Hallway            \\
 SE9        & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
 SE10       & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
-SE11       & 16            & Water  &  Solid Stream       &    Hallway            \\
-SE12       & 16            & Water  &  Solid Stream       &    Hallway            \\
+SE11       & 16            & Water  &  Straight Stream    &    Hallway            \\
+SE12       & 16            & Water  &  Straight Stream    &    Hallway            \\
 \bottomrule[1.25pt]
@@
 The 88 gas cooling events were completed as part of 9 separate tests in the burn building.
+For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
+The focus of this analysis is to look at trends within the aggregate data.
 During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
@@
 There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}).
-Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAFS tests, respectively.
-For both sets a solid 7/8 in nozzle in the middle position was used.
+Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively.
+For both sets a solid 7/8~in nozzle in the middle position was used.
 The data shows that thermocouples in the plot in the upper right of both figures has more significant temperature drops than the other two arrays; this is likely a result of that thermocouple array being directly ``hit'' by the suppression stream.
@@
 
-To better quantify the effectiveness of the suppression agents (CAFS, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
-Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for the 30 replicate tests, 15 water and 15 CAFS, for all streams aimed at all positions.
+To better quantify the effectiveness of the suppression agents (CAF, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
+Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for the 30 replicate tests, 15 water and 15 CAF, for all streams aimed at all positions.
 
@@
 If water and CAFS have the exact same temperature differences, all of the points would fall along solid black line in the figure.
-Circles that vary from that line represent measurements where either water (above) or CAFS (below) cooled more significantly than the other agent.
+Circles that vary from that line represent measurements where either water (above) or CAF (below) cooled more significantly than the other agent.
 The gray area surrounding the solid black line, represents measurement uncertainty (\ref{subsec:Uncertainty}).
@@
 The red dashed line is the line the describes the data by minimizing the differences between the two suppression agents through a linear approximation of the data.
-Since this line falls above the gray area for the comparison, water shows a better ability to cool gas under the same test criteria as CAFS.
+Since this line falls above the gray area for the comparison, water shows a better ability to cool gas under the same test criteria as CAF.
 
@@
 
-For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAFS.
+For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAF.
 At the back position (Fig.~\ref{fig:CAFS_Water_full}), for the 3 replicate comparison, the least squared error line falls within the experimental uncertainty.
@@
 Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
-Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAFS at the mid position compared to the positions of the thermocouple trees.
+Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
 \begin{figure}[!ht]
@@
 Note that thermocouple array A3, the array which has the least amount of direct suppression, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
-The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAFS and water are indistinguishable.
-Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAFS.
+The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
+Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF.
 
@@
 \midrule
- 1 & CAFS~1   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
+ 1 & CAF~1    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
  2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
- 3 & CAFS~2   &  7/8'' Smooth Bore  &  120~gpm/60~cfm   & Furniture      & Door            \\
- 4 & Water~2  &  7/8'' Smooth Bore  &  120~gpm    		& Furniture      & Door            \\
+ 3 & CAF~2    &  7/8'' Solid Stream &  120~gpm/60~cfm   & Furniture      & Door            \\
+ 4 & Water~2  &  7/8'' Solid Stream &  120~gpm    		& Furniture      & Door            \\
  5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 6 & CAFS~3   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 6 & CAF~3    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
  7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 8 & CAFS~4   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 8 & CAF~4    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
  9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
@@
 11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
-12 & CAFS~5   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+12 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
-14 & CAFS~6   &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+14 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 \bottomrule[1.25pt]
@@
 
-Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAFS tests.
+Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAF tests.
 The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
@@
 \midrule
-CAFS~1 Hallway   & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-CAFS~1 Room      & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
 Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAFS~2 Hallway   & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
-CAFS~2 Room      & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
@@
 Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAFS~3 Hallway   & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
-CAFS~3 Room      & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
 Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAFS~4 Hallway   & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
-CAFS~4 Room      & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
+CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
 Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
-CAFS~5 Hallway   & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
-CAFS~5 Room      & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
+CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
 Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAFS~6 Hallway   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
-CAFS~6 Room      & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 \bottomrule[1.25pt]
@@
 
-To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAFS Test 1 as a result of the hallway (first) and room (second) suppression actions.
+To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAF Test 1 as a result of the hallway (first) and room (second) suppression actions.
 Fig.~\ref{fig:fs_1_2} shows the same impacts as Fig.~\ref{fig:fs_1_1}, except that the tests used water.
@@
 
-Note that while there are some differences in the changes in temperature and heat flux when comparing CAFS to Water, differences are not substantial.
+Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, differences are not substantial.
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
@@
 \midrule
- 38  & CAFS~7    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
+ 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
  39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
- 40a & CAFS~8a   &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 40b & CAFS~8b   &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
  41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41b & CAFS~9    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41c & CAFS~9b   &  7/8'' Slub      	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 
-Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAFS tests conducted in the two story structure.
+Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAF tests conducted in the two story structure.
 The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor.
@@
 \midrule
-CAFS~7 Stairell      & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~7 Stairell       & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
 Water~7 Stairwell    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAFS~8a Stairwell    & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAFS~8b Stairwell    & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+CAF~8a Stairwell     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b Stairwell     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
 Class A~1 Stairwell  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAFS~9a Stairwell    & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAFS~9b Stairwell    & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~9a Stairwell     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b Stairwell     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]
@@
 
-Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAFS to Water, but the differences are not substantial.
+Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial.
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
@@
 
-The gas cooling experiments were designed to measure the ability of water streams and CAFS streams to cool a hot gas layer with a minimum temperature of  250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
+The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
 During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS, since the injected air, air being a great insulator, would interfere and result in less cooling.
-It was the belief that the reduced gas cooling capabilities of CAFS may have lead to firefighter injuries during interior fire attacks.
+It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
 Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
@@
 The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
-When a CAFS stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
+When a CAF stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
 Also calc the mass of air in the stream.
@@
 
-Ref Sean Mitchell report and then close with the ref back to the two comparison graphs.
 Under the conditions of a residential scale room and contents fire it should be no surprise that the results are similar, the mass of water introduced into the hot gas layer is doing the work.
@@
 \label{sec:Fire_Suppression_discussion}
+
+static nozzle lines all performed the same.
+
+movement, sweeping nozzle, etc -- more efficient cooling / more effective that the type of nozzle or the amount of suppressive agent.
 
@@
 \caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 2 with a 7/8'' 
-Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
 \label{fig:app_fs_3}
@@
 \caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 2 with a 7/8'' 
-Smooth Bore nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
+Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
 \label{fig:app_fs_4}

### 2016-06-30 Projects/DelCo_2012/Report/DelCo_2012.tex
modified CAF Supp Table

@@
 \centering
-\caption{Fire Suppression Results}\label{tab:Test_Results_2}
+\caption{Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
 \begin{tabular}{lccc}
@@
 \midrule
-CAF~7 Stairell       & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-Water~7 Stairwell    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a Stairwell     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b Stairwell     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
-Class A~1 Stairwell  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a Stairwell     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b Stairwell     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~7      & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+Water~7    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~8a     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+Class A~1  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
+CAF~9a     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]

### 2016-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
add suppression test data to table, cleanup tables to fit on page

@@
 \centering
-\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
+\caption{Single Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
 \begin{tabular}{clllll}
@@
 \centering
-\caption{Fire Suppression Results}\label{tab:Test_Results}
+\caption{Single Story Fire Suppression Results}\label{tab:Test_Results}
 \begin{tabular}{lccc}
@@
                  & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
-Test 	         & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	         & 0.15~m (6~in) Above Floor \\
+Test 	         & 0.3~m Below Ceiling                 & 0.3~m  Above Floor	                 & 0.15~m Above Floor \\
 \midrule
@@
 \footnotesize
-\caption{Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
+\caption{Two Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
 \begin{tabular}{clllll}
@@
 \midrule
- 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Double Doors, 1st Floor Door \\
- 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Double Doors, 1st Floor Door \\
- 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41b & CAF~9     &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
- 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Double Doors, 1st Floor Door \\
+ 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
+ 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
+ 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 40c & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 41b & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 \centering
-\caption{Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
-\begin{tabular}{lccc}
+\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
+\begin{tabular}{lcccc}
 \toprule[1.5pt]
-           & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
-Test 	   & 0.3~m (1~ft) Below Ceiling          & 0.3~m (1~ft) Above Floor	           & 1~m (3~ft) Above Floor \\
+           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
+Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
 \midrule
-CAF~7      & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-Water~7    & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a     & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b     & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
-Class A~1  & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a     & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b     & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~7      & 24            & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+Water~7    & 29            & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~8a     & 16            & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b     & 21            & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+Water~8    & 18            & 440~$^{\circ}$C - 295~$^{\circ}$C   & 375~$^{\circ}$C - 250~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
+Class A~1  & 19            & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
+CAF~9a     & 21            & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b     & 16            & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]

### 2016-07-01 Projects/DelCo_2012/Report/DelCo_2012.tex
MCFRS added to acknowledgements

@@
 Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.
-Alan Butsch,   Brian Rojas,  Michael Johns, Chris Riley
+Special appreciation goes to the MCFRS staff that participated in the experiments:    Alan Butsch, Daniel Hudson,  Michael Johns, Steven Neubauer, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph “Dewey” Thomas,  and Douglas Wallace.
+
+The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
 

### 2016-07-04 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Included CF comments through HRR
also bib typos fixed along the way

@@
 
-The need for fire investigation and value to society, tools used , example.
-
-\subsection{The need and purpose for Fire Investigation}
+This section reviews the fire problem to demonstrate the need and value to society that fire investigation can provide.
+Following the review, a brief presentation on the analysis  of fire patterns, the use of analytical tools, and the current challenges to the field of fire forensics is given as they are the reason for this study.
+In closing this section, an example of a fire incident is presented.
+In the closing section we will return to the example again.
+
+\subsection{The Need for Fire Investigation}
 Unwanted fires result in loss of life, property and can create an adverse economic impact on a community.
@@
 An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention~\cite{Campbell:2014}.
-An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be''~\cite{NFPA_921}.
+An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be''~\cite{NFPA:921}.
 
@@
 More than \$1.3 billion dollars (U.S.) was lost per year due to direct property damage.
-Fires involving structures account for more than 84~\% of the civilian deaths, injuries and property loss from all intentional fires.
-Approximately two-thirds of the structure fires occurred in residential occupancies.
-95~\% of the civilian deaths and 86~\% of the civilian injuries also occurred in the intentional fires in residential occupancies~\cite{Campbell:2014}.
+Structure fires represent less than 20~\% of intentionally set fires.
+However, fires involving structures account for more than 84~\% of the civilian deaths, injuries and property loss from all intentional fires.
+Approximately two-thirds of the intentional structure fires occurred in occupied and operating residential occupancies.
+As a result, 95~\% of the civilian deaths and 86~\% of the civilian injuries which are attributed to intentional fires occurred in residential occupancies~\cite{Campbell:2014}.
 
 A subset of the intentional fires are considered arson.
-Arson as defined by the U.S.
+The U.S.
 Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime:2010}.
-
 The national rate of arson fire cases cleared by arrest or exceptional means is less than 20~\%.
 Of those cases approximately 46~\% of the suspects were prosecuted~\cite{Campbell:2014}.
-Arson is a challenging crime to solve because typically there are no witnesses present at the time of the crime.
+Hence less than 10~\% of the arson cases resulted in successful prosecution.
 
 The values cited above are believed to be the best available in the United States and perhaps one of the better fire incident databases in the world.
-However an investigative report by Icove and Hargrove, indicates that arson fires are underreported to the National Fire Incident Reporting System (NFIRS).
+However an investigative report by Icove and Hargrove, indicates that arson fires are underreported to the U.S.
+National Fire Incident Reporting System (NFIRS).
 The investigation provided examples from several major cities, such as New York City, where in 2011, 11 arson fires in buildings were reported to NFIRS, while the Fire Department of the City of New York's Bureau of Fire Investigation had recorded 1,347 arson fires in buildings that year.
@@
 On average, three-fourths of the arsons uncovered by city fire investigators went unreported to NFIRS~\cite{Icove_2014}.
-
+In other words, the number of arson related incidents is likely to be under represented in the fire incident data.
+
+\subsection{The Use of Fire Patterns in Fire Investigation}
 Fires are investigated in order to determine the ``origin and cause'' of the fire and in cases of arson there is an effort to determine who was responsible for setting the fire.
-This investigation process must follow the scientific method as documented in NFPA 921~\cite{NFPA_921}.
+This investigation process must follow the scientific method as documented in NFPA 921~\cite{NFPA:921}.
 There are numerous textbooks on the subject of conducting a fire investigation~\cite{Almirall:2004,Fire_Investigation,DeHaan:2012,Icove:2013,Lentini:2006,Noon:1995}.
-The NFPA guide and the texts provide information to a fire investigator collecting data from the scene, analyzing the data, and developing a hypothesis about the fire.
+The NFPA guide and the texts provide information how to collect data from the scene, analyze the data, and develop a hypothesis about the fire.
 
@@
 As noted by Icove, DeHaan, and Haynes  ``'the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…''~\cite{Icove:2013}.
-A fire pattern is defined in NFPA~921 as, ``the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects''~\cite{NFPA_921}.
+A fire pattern is defined in NFPA~921 as, ``the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects''~\cite{NFPA:921}.
 
@@
 A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s) and compartmentalization, to name a few.
-Given the limited number of experiments in the literature and the large number of variables, it has been difficult to fully understand a cause and effect relationship between the fire scenarios and the resulting patterns.
-
-Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula}.
+Given the limited number of experiments in the literature and the large number of variables, it has been difficult to develop a cause and effect relationship between the fire scenarios and the resulting patterns, based solely on the research.
+
+Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula:2001}.
 Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
@@
 Not all of the correlations in the FDTs were included in the study because an insufficient amount of reliable data is available to conduct validation.
-Two correlations that could not be validated were for flame height and time to ignition.
+The correlations for flame height and time to ignition were not included in the validation study.
 
@@
 The fire investigation community recognized a need to improve the science and practice of fire investigation.
-One of the manifestations of the efforts to improve the practice was the development of NFPA~921, {\em Guide for Fire and Explosion Investigations}~\cite{NFPA_921}.
+One of the manifestations of the efforts to improve the practice was the development of NFPA~921, {\em Guide for Fire and Explosion Investigations}~\cite{NFPA:921}.
 The first edition of NFPA~921 was issued in 1992.
@@
 
-Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard, which is 2.4~m in height.
-Given the upper bound of 2.4~m, the experiments will use small fires with mean flame heights of approximately 1.2~m.
+Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupanies.
+A common height for a residential occupanices is 2.4~m in height.
+With a wall height of 2.4~m, these experiments will use small fires with mean flame heights of approximately 1.2~m.
 The resulting patterns on the gypsum board wall would be representative of a pre-flashover fire pattern.
@@
 \subsection{Fire Pattern Experiments}
+
+The first set of fire pattern experiments on painted gypsum wallboard, without potentially intrusive instrumentation, was conducted to examine the impact of the construction on the wall.
+Three different types of wall construction were examined to determine if the amount of insulation behind the exposed gypsum wallboard changed the fire pattern by a significant amount.
+The results would then be used to plan the wall construction of the remaining full- scale experiments.
 
@@
 
-A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover or incipient fires.
-A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels was selected.
+A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover or early growth stage fires.
+A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
 The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.
@@
 Experiments were conducted with a natural gas fueled burner, a liquid fueled pan fire, and a solid fuel.
-Natural gas was chosen as a fuel because it is used for calibrating the oxygen depletion calorimeters in NIST’s Large Fire Laboratory.
+Natural gas was chosen as a fuel for two reasons; it is a common fuel used for heating homes and it is used for calibrating the oxygen depletion calorimeters in NIST’s Large Fire Laboratory.
 Therefore the heat content of the gas was monitored and mass flow controlled to provide a heat release rate based on fuel mass flow for comparison with the heat release rate values measured with the calorimeter.
@@
 The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
-A load cell was positioned as a support for the fuels.
+A load cell was positioned on the floor as a support for the fuels.
 All of the data was recorded at intervals of 1~s on a computer based data acquisition system.
@@
 
-The NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter has an estimated peak heat release rate capacity of approximately 700~kW.
+The NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter had an estimated peak heat release rate capacity of approximately 700~kW.
 Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
-Many of the same instruments are shared between the two calorimeters and calibration burns were conducted during each experimental series.
+Many of the same instruments were shared between the two calorimeters and calibration burns were conducted during each experimental series.
 As a result, the expanded uncertainty of this device has been estimated as 11~\% on the measured heat release rate.
@@
 Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2~mm diameter inconel shield, 0.76~m in length.
+Thermocouple is ungrounded.
 The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer~\cite{Omega}.
-The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2001}.
+The variation of the temperature in the environment surrounding the thermocouple was known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2001}.
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
-The estimated combined expanded uncertainty for temperature in these experiments is 15~\%.
+The estimated combined expanded uncertainty for temperature in these experiments was 15~\%.
 
@@
 The manufacturer reports a 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically 8~\%~\cite{Pitts:2006}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge was typically 8~\%~\cite{Pitts:2006}.
 The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
@@
 The load cell had a resolution of 1.0~g~\cite{Mettler}.
-The expanded uncertainty is estimated to be 5~\%.
+The expanded uncertainty was estimated to be 5~\%.
 The load cell was checked between experiments with calibrated weights during the zero and span checks of the calorimeter.
@@
 A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.
-Each camera was positioned on a tripod with a distance of 4.5~m between the centerline of burner to camera lens 4.5~m.
+Each camera was positioned on a tripod with a distance of 4.5~m between the centerline of burner to camera lens.
 The height of each camera was adjusted so that the center of camera lens was positioned 0.5~m above top of the burner.
@@
 
-On each fuel’s averaged heat release rate curve, the filled area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+On each fuel’s averaged heat release rate curve, the shaded area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ or 11~\% over a 100~s period.
-It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
-The gasoline, based on the average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments, provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 20~\%.
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 100~s period.
+The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11~\% It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
+The gas burner and on/off control valve allowed the heat release rate to be similar in form to a "square-wave".
+
+The gasoline pan fire has was ignited and then burned until the fuel was consumed.
+Therefore the heat release rate curves had more of a "bell shape"  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
+Therefore the  gasoline average peak heat release rate was based on an average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments.
+This method provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 30~\%.
 The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
-The polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Averaging over a 15~s interval bounding the peak heat release rate from each of the ten experiments yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 34~\%.
-The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ
+
+The block of polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
+Similar to the gasoline that began with a fixed quantity of fuel which was ignitied and burned to completion, the polyurthane foam also generated "bell shaped" heat release rate curve.
+Since the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~s interval bounding the peak heat release rate from each of the ten experiments.
+This process yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 47~\%.
+The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ.
+
+The Figures~\ref{HRR}-\ref{HRR2} have a shaded area that shows the 95~\% confidence level.
+The more narrow the shaded area, the better the repeatability of the fire.
+This provides a quick means to assess the repeatability of a given source fire.
+Using this measure the natural gas burner fires were the most repeatable, followed by the gasoline pan fires and then the polyurethane fires.
 

### 2016-07-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 2
Addressed CF comments Ch 2 including revised figs

@@
 
+\subsection{The Use of Fire Models in Fire Investigation}
 Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula:2001}.
@@
 
+\subsection{Fire Investigation Under Review}
 The fire investigation community recognized a need to improve the science and practice of fire investigation.
@@
 
-Plots of the centerline temperatures averaged over the replicate experiments for each of the fuels are presented in Fig.~\ref{Temp}.
-The natural gas temperatures were averaged over a ``steady-state'' burning period.
+Plots of the centerline temperatures averaged over the full set of replicate experiments for each of the fuels are presented in Fig.~\ref{Temp}.
+The natural gas temperatures are averaged over a ``steady-state'' burning period.
 The temperature differences between the vertical thermocouple locations, for locations greater than 20~cm above the fire location, begin to decrease as the distances from the top of the burner increase.
@@
 The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that has periods of growth and decay.
-The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
 The average peak total heat flux for the natural gas fires were approximately 2.0~kW/m$^2$.
@@
 \begin{figure}
-  \includegraphics[width=2.7in]{../Figures/Fig14a}
-  \includegraphics[width=2.7in]{../Figures/Fig14b} \\
-  \caption[Photographs of the natural gas and polyurethane foam fires]{Photographs showing a natural gas fire (left) and a polyurethane foam fire (right) under the oxygen consumption calorimeter.}
+  \includegraphics[height=3.5in, width=1.7in]{../Figures/NG_STFire}
+  \includegraphics[height=3.5in, width=1.7in]{../Figures/Gaso_STFire} 
+  \includegraphics[height=3.5in, width=1.7in]{../Figures/PUF_STFire} \\
+  \caption[Photographs of the natural gas, gasoline, and polyurethane foam fires]{Photographs showing a natural gas fire (left), gasoline fire (center), and a polyurethane foam fire (right) under the oxygen consumption calorimeter.}
   \label{Gas_Foam_Photos}
@@
 \begin{figure}
-  \includegraphics[width=2.7in]{../Figures/Fig15a}
-  \includegraphics[width=2.7in]{../Figures/Fig15b} \\
+  \includegraphics[width=2.6in]{../Figures/Gaso_0_65m}
+  \includegraphics[width=2.6in]{../Figures/Gaso_1_0m} \\
   \caption[Photographs of the gasoline fire]{Photograph showing a gasoline fueled experiment with a flame height of 0.65~m (left) and a photograph taken approximately 0.2~s later with a flame height of 1.0~m (right).}
@@
 In some cases the fire burned completely through the fuel in the center of the foam sample, resulting in a hollow flame at the time of the peak heat release rate.
-An example of a contour plot, exhibiting the hollow or bifurcated flames is shown at right in Fig.~\ref{Foam_Contours}.
+An example of a contour plot, exhibiting the hollow or bifurcated flames is shown at right in Figure~\ref{Foam_Contours}.
+Refer back to Figure~\ref{flame_height_comp_FHPUF_1} to see photographic views of the bifurcated flames.
+It seems that the movement of the flames as they flowed away from the fuel surface blurred out the bifurcation over time with the exception of the lower elevation areas that presented at the 90 and 100~\% contours.
 Other methods of ignition for the polyurethane foam were considered in order to have a more uniform ignition of the top surface of the foam.
@@
 In these experiments the target is a non-combustible wall.
-The non-combustible material was chosen to minimize any contribution from the wall to the fire.
+The non-combustible material was chosen to prevent any contribution due to combustion from the wall to the fire.
 The fires were placed at predetermined, fixed positions away from the wall.
+The fires were prepared and conducted in the same manner as the they were in the fire characterization experiments.
+As a result the exposure time of the target wall to the fire was 300 seconds.
 In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
@@
 The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:MSDS}.
-Material properties that impact heat transfer were selected from the manufacturer's literature and are presented in the table below~\cite{Marinite:1997}.
+Material properties that impact heat transfer were selected from the manufacturer's literature and are presented In Table~\ref{tab:Marinite_Thermal_Properties}~\cite{Marinite:1997}.
 

### 2016-07-05 Projects/DelCo_2012/Report/DelCo_2012.tex
add gitignore and update CAFS report

@@
 \input{../../../Bibliography/commoncommands}
-
+\usepackage[space]{grffile}
 % Rename chapter headings
@@
 
-Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure.
+Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure (cf.
+Fig~\ref{fig:water_buckets}).
 The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
@@
 
-For the gas cooling tests, Table~\ref{tab:spray_density_tests}, the mid position had center line of the stream aimed at 2.44~m (8~ft) south of the North wall and 2.13~m (7~ft) west of the East wall in the concrete burn building.
+\begin{figure}[!ht]
+	\includegraphics[width=.5\columnwidth]{../Figures/Pictures/Water Tests Bins.png}
+	\caption{Interlocking collecting bins used to capture suppression agent during spray density tests.}
+	\label{fig:water_buckets}
+\end{figure}
+
+For the spray density tests, Table~\ref{tab:spray_density_tests}, the mid position had center line of the stream aimed at 2.44~m (8~ft) south of the North wall and 2.13~m (7~ft) west of the East wall in the concrete burn building.
 The back position had the center line of the stream aimed at 3.36~m (11~ft) south of the North wall and 2.13~m west (7~ft) of the East wall in the concrete burn building.
+Figure~\ref{fig:stream_position} shows the streams from the monitor nozzle for the middle and back positions respectively.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Mid_BB}
+	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Back_BB}
+	\caption{Stream positions mid(left) and back (right) during spray density tests.}
+	\label{fig:stream_position}
+\end{figure}
 
@@
  2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
- 3 & CAF~2    &  7/8'' Solid Stream &  120~gpm/60~cfm   & Furniture      & Door            \\
- 4 & Water~2  &  7/8'' Solid Stream &  120~gpm    		& Furniture      & Door            \\
+ 3 & CAF~2    &  Solid Stream       &  120~gpm/60~cfm   & Furniture      & Door            \\
+ 4 & Water~2  &  Solid Stream       &  120~gpm    		& Furniture      & Door            \\
  5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
@@
  41b & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 41c & CAF~9b    &  7/8'' Solid Stream  &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 41c & CAF~9b    &  Solid Stream        &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
-When a CAF stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
-Also calc the mass of air in the stream.
-
-Compare flow rate with coverage estimates Iowa/NFA formulas.
+{\bf When a CAF stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
+Also calc the mass of air in the stream.}
 
@@
 
+Currently, the fire service uses fire flow formulas to estimate the flow rate of water needed to control a structure fire.
+The formulas will be presented below and then the results from the studies presented above will be compared with the calculated fire flows.
+
+\subsection{Iowa State Univeristy Fire Flow Formula (1963)~\cite{NFPA}}
+The Iowa Formula for determining the required fire flow for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
+The required fire flow in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
+\begin{equation}\label{eq:isu_form}
+\dot{Q} = V / 100
+\end{equation}
+Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
+Applying the Iowa State University formula based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
+
+\subsection{National Fire Academy (1884)~\cite{Klaene:1}}
+The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
+This formula sets the required fire flow, in gpm, equal to the floor area (in square feet) divided by 3.
+\begin{equation}\label{eq:nfa_form}
+\dot{Q} = A / 3
+\end{equation}
+Applying the NFA formula based on floor area yields an application density of 13.6~Lpm/m$^2$ (0.33~gpm/ft$^2$).
+
 static nozzle lines all performed the same.
@@
 
+The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
+
 Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.
-Special appreciation goes to the MCFRS staff that participated in the experiments:    Alan Butsch, Daniel Hudson,  Michael Johns, Steven Neubauer, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph “Dewey” Thomas,  and Douglas Wallace.
+The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Bryan Rojtas, Chris Reilly, Sean Regan, Alan Butsch, Ralph Thomas, Daniel Hudson, Michael Johns, and Douglas Wallace.
 

### 2016-07-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 3 and 4
Continued to revise chapters based on CF comments.

@@
 Figures~\ref{HF_Center_TWNG_comp} and \ref{HF_Edge_TWNG_comp} provide the heat flux measurements for the two vertical arrays of gauges positioned along the centerline and the edge of the natural gas burner.
-The series of graphs show that the peak heat flux increases by as the burner is moved toward the wall.
+The series of graphs show that the peak heat flux increases as the burner is moved toward the wall.
 One exception is when the burner was moved from the 0.15~m position to the 0.0~m from the wall.
@@
 
-Figure~\ref{NCTW_Surf_Center_comp} shows the temperatures of the array of thermocouples located along the vertical centerline of the burners for each of the three fuels.
-Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner was moved away from the wall.
+Figure~\ref{NCTW_Surf_Center_comp} shows the wall temperatures based on the array of thermocouples installed in the wall and position along the vertical centerline of the burners for each of the three fuels.
+Reviewing the graph for each fuel demonstrates how the temperature at the wall decreased as the position of the burner increased from the wall.
 The beads of the thermocouples were installed in the wall and were flush with the wall surface.
@@
 These experiments were conducted in a similar manner as the non-combustible instrumented wall experiments, the only new variable is the painted, gypsum wallboard.
-These experiments enable us to examine our ignition/no ignition predictions from the previous experiments.
+These experiments enabled the examination of the ignition/no ignition predictions from the previous experiments.
 A free standing, steel frame with a panel of gypsum wallboard attached to the surface was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.

### 2016-07-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Started on Ch 5 CF Comments

@@
 
-As defined in NFPA 921, a fire is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA_921}.
+As defined in NFPA 921, a fire pattern is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA_921}.
 In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
@@
 
-Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as show in Figure~\ref{Soot_pattern}.
+Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as shown in Figure~\ref{Soot_pattern}.
 From the photograph the areas of penetration and consumption can be clearly delineated while the discolored and sooted areas tend to meld together.
@@
 
-\chapter{Bench Scale Experiments}
+\chapter{Bench Scale Assessment of Thermal Damage to Gypsum Wallboard}
 
@@
 
-The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption method.
+The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption calorimetry method.
 It was developed at NIST in the 1980s~\cite{babrauskas:1984}.
 The cone calorimeter has been adopted as ASTM~E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}.
-The cone calorimeter consists of a heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
+The cone calorimeter consists of a conical shaped heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
 Typically, the sample is located in the open with free access of air to the combustion zone.
@@
 Once the sample was mounted and the sample was moved to the appropriate distance from the radiant panel based on the heat flux desired for the experiment, the heat shield was removed.
-The removal of the heat shield would be recorded as the beginning of the exposure and therefore the beginning of the experiment.
+The removal of the heat shield was recorded as the beginning of the exposure and therefore the beginning of the experiment.
 Each sample was exposed for 600 seconds.
@@
 The results from the three different bench scale experiments are presented and discussed in this section.
-All three test methods provided some insight into the ignition and the critical heat flux required for ignition or flame spread of the painted paper surface on the gypsum wall board.
+All three test methods provided some insight into the ignition and the critical heat flux required for ignition or flame spread of the painted paper surface on the gypsum wallboard.
 The cone calorimeter also provided values for heat release rate.
@@
 Samples of painted gypsum wallboard were shipped from the NIST Fire Research Laboratory in Gaithersburg, MD., USA.
-In these experiments an additional incident heat flux level of 30~kg/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
+In these experiments an additional incident heat flux level of 30~kW/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
 The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
-The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident heat flux values of 35 and 50~kg/m$^2$, respectively.
+The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident heat flux values of 35 and 50~kW/m$^2$, respectively.
 The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.

### 2016-07-07 Projects/DelCo_2012/Report/DelCo_2012.tex
Text mod through 3.2
Minor adds and typos fixed.  Re-ordered fuel loads

@@
 These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.
+This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 
 A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAFS for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including: 1) A literature review of available published information on the use of CAF for structural firefighting~\cite{Mitchell:1}; 2) A workshop that brings interested and experienced parties together to discuss safety implications associated with this project and to provide guidance on the proposed experimental research plan~\cite{Grant:2011}; 3) The performance and analysis of a number of well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural firefighting; and 4) The performance and analysis of a number of fire ground evolutions to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
-The research findings are provide information with the potential to improve the safe and effective use of CAF for structural firefighting.
+This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including:
+
+\begin{enumerate}
+\item  Perform a literature review of available published information on the use of CAF for structural firefighting~\cite{Mitchell:1}
+\item  Conduct a workshop that brings interested and experienced parties together to discuss CAF experience and to provide guidance on the proposed experimental research plan~\cite{Grant:2011} 
+\item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural firefighting
+\item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+\end{enumerate}
 
 This paper documents Task 3 of the project.
-NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for different compartment fire scenarios.
-
-Three types of experiments were conducted:
+NIST conducted several series of experiments to provide scientific measurements and comparisons between CAFS and water-only hose streams for four different compartment fire scenarios.
+Three different types of experiments were conducted:
 \begin{enumerate}
@@
 
-The key measures were to understand the cooling and suppression capabilities of CAF compared to water.
+The key measures were to understand the gas cooling and fire suppression capabilities of CAF compared to water.
 The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAF during interior attack operations in residential occupancies~\cite{Grant:2011}.
@@
 A CAFS could turn a Class A foam solution into a blanket of bubbles that would allow the wildland firefighters to coat the fuels.
-The additional ``soak'' time provided by the foam layer allows the water to penetrate the hot surface of a burning fuel, and also provides additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
+The additional ``soak'' time provided by the foam layer allowed the water to penetrate the hot surface of a burning fuel, and also provided additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
 An added feature of the blanket of bubbles is that firefighters could see where they had applied the agent so that they could make a more effective application.
@@
 For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires, but also examined using them for structural fire fighting.
-Departments across the country began to experiment with CAFS systems for use in structural firefighting.
-In most documented cases, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAF has still not been significantly incorporated into structural firefighting tactics.
-This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAFS inside a structure.
+Other departments across the country began to experiment with CAFS systems for use in structural firefighting.
+In the few cases that were documented, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAF has still not been widely incorporated into structural firefighting tactics~\cite{USFA:CAFS,Lorh:2002}.
+This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
 
@@
 That study examined a broad range of tests in order to determine those parameters that most critically effect fire-fighting performance.
-The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}:
+The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.
 
@@
 When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
-The foams enhance the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allows the water to penetrate absorbent fuels.
+The foams enhanced the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allowed the water to penetrate absorbent fuels.
 These enhancements also make the agents valuable tools for mop-up.
@@
 In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAF during structure fires and to report back his findings and recommendations.
-The catalyst for this study was as a result of this order.
+That order was the catalyst for this study.
 
@@
 
-All of the experiments were conducted at full scale in compartments and structures that were representative room sizes in a residential occupancy.
+All of the experiments were conducted at full scale in compartments and structures that were representative of room sizes in a residential occupancy.
 Technical panel members whose departments routinely use CAF for structural firefighting were invited and present at many of the fire suppression experiments.
@@
 The fire suppression experiments were conducted with a fuel package that included upholstered furniture.
-After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package was composed mainly of wood based materials, as a way to increase the challenge of the suppression experiment.
-After the wood based fuel package experiments were completed, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
+After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package that was composed mainly of wood based materials.
+The thinking was that the synthetic materials in the upholstered furniture burned only on the surface and were easily extinguished.
+Wood based fuels would char and present a deep seated fire challenge to the extinguishing agents.
+After the wood based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
 The issue of a larger fire compartment had also been raised during the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
 In order to accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
+The fuel load contained both wood-based wall and ceiling finishes, pallets as well as carpeting and upholstered furniture.
 
@@
 The experimental setup for this test series is described by the three types of experiments conducted: spray density measures, gas layer cooling, and fire suppression.
-Baseline operating conditions were agreed upon at the workshop for these experiments (Table~\ref{tab:op_condition}).
 Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
@@
 The nozzles were controlled and operated via a gate valve from the exterior.
+The exterior control had a gated wye to allow the flow of CAF through a hose directed away from the test structure.
+When the flow of CAF was needed for the experiment, the gated wye would be switched to allow the CAF to flow into the test structure.
+This was done to minimize, the build-up of "dry" foam or a slug upon the initial flow of the nozzle into the test structure.
 
@@
 The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
-Therefore, the purpose of these tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+The purpose of these preliminary tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
 
@@
 These tests examined five different hose stream patterns, two nozzle types, and both compressed air foam and water as the suppression agent.
-The focus of this experimental series was to study the impact of the test variables on interior conditions throughout the structure when suppression tactics were applied to a room adjacent to the fire room.
+The focus of this experimental series was to study the impact of the test variables on the hot gas layer temperatures when a fixed hose stream was applied to a room adjacent to the fire room.
+Suppression agents were not applied to the fire in the burn room.
 Detailed discussion of the tests and results are in Section~\ref{sec:Gas_Cooling}.
@@
 The adjacent room where the water was applied for gas cooling measured 4.1~m (13.4~ft) by 5.7~m (18.7~ft), also with a ceiling height of 3.35~m (11.0~ft).
-The open door from the adjacent room to the exterior measured 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
+The open doorway that connected the burn room to the adjacent room and the doorway from the adjacent room to the exterior both measured 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
 
@@
 Pallets were added to the existing fuel locations until the flames from the piles reached the ceiling of the burn room again.
+The shutters on the window would be then closed and the temperature of the hot gas layer in the adjacent room would be monitored in preparation for starting another gas cooling experiment.
 The number of pallets added each time varied.
@@
 
+\subsubsection{Furniture Fuel Package}
+\label{sec:fire_suppression_furniture_fuel}
+
+The fuel load for experiments 1 through 8 consisted of 2 sleeper sofas and 2 chairs, carpet, padding, and wood paneling along the southeast corner walls.
+An image of the fuel arrangement is shown in Fig.~\ref{fig:Furniture_Fuel_Load}.
+The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner.
+A chair is placed adjacent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
+In total, this fuel package contains approximately 336 kg (739 lbs) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
+Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
+	\caption{Furniture Fuel Load in Single Story Structure}
+	\label{fig:Furniture_Fuel_Load}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
+	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
+	\label{fig:Furniture_Fuel_Load_Dimensions}
+\end{figure}
+
+\begin{sidewaystable}[!ht]
+	\centering
+	\scriptsize
+	\caption{Fire Suppression Furniture Fuel Package Description}
+	\renewcommand{\tabcolsep}{1pt}
+	\begin{tabular}{lllllcc}
+		\toprule[1.5pt]
+		Item               & Component		& Quantity		&  Material Description             			&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
+		\midrule
+		2-seat Sofa        &				& 2				& 85~\% PU Foam, 15~\% PE Fiber, Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
+		           	 	   & Mattress	    & 1 per sofa	& Cover: 52~\% PP, 48~\% PE,                    &  1.83 L X 1.21 W X 0.14 H     &  14.6             & \\
+		           	 	   &                &               & Filling: 66~\% PE Pad, 34~\% PE Batting       &                               &                   & \\
+			           	   & Cushion    	& 2 per sofa	& 85~\% PU Foam, 15~\% PE Fiber   				&  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
+		Blue Chair         &				& 2				& 85~\% PU Foam, 15~\% PE Fiber, Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
+		    			   & Cushion        & 1 per chair   & 85~\% PU Foam, 15~\% PE Fiber	    			&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
+		Blue/Green Chair   & 				& 2				& 85~\% PU Foam, 15~\% PE Fiber, Wood Frame     &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
+		                   & Cushion    	& 1 per chair	& 85~\% PU Foam, 15~\% PE Fiber 		        &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
+		Paneling           &				& 8 panels		& Medium density fiberboard                     &  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
+		Carpeting          &				& 22.3 m$^2$	& 100~\% Olefin fiber w/PP backing		     	&  3.68 L X 6.05 W  			&  32.2				& 32.2 \\
+		Carpet Padding     &				& 22.3 m$^2$	& PU Foam                  	 				    &  3.68 L X 6.05 W X 11~mm H    &  19.8			    & 19.8 \\
+		                   &                &               &                                               &                               & Total Mass        & 335.6 \\
+		\bottomrule[1.25pt]
+	\end{tabular}
+	\label{tab:Fire_Suppression_Fuel_Masses}
+\end{sidewaystable}
+
 \subsubsection{Wood Fuel Package}
@@
 
-The fuel load for these experiments consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
+The fuel load for experiments 11 through 14 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
@@
 
-\subsubsection{Furniture Fuel Package}
-\label{sec:fire_suppression_furniture_fuel}
-
-The fuel load for these experiments consisted of 2 sleeper sofas and 2 chairs, carpet, padding, and wood paneling along the southeast corner walls.
-An image of the fuel arrangement is shown in Fig.~\ref{fig:Furniture_Fuel_Load}.
-The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner.
-A chair is placed adjacent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
-In total, this fuel package contains approximately 336 kg of fuel consisting of wood, polyurethane (PU), polyester (PET),and polypropylene (PP).
-Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
-	\caption{Furniture Fuel Load in Single Story Structure}
-	\label{fig:Furniture_Fuel_Load}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
-	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
-	\label{fig:Furniture_Fuel_Load_Dimensions}
-\end{figure}
-
-\begin{sidewaystable}[!ht]
-	\centering
-	\scriptsize
-	\caption{Fire Suppression Fuel masses}
-	\renewcommand{\tabcolsep}{1pt}
-	\begin{tabular}{lllllcc}
-		\toprule[1.5pt]
-		Item               & Component		& Quantity		&  Material Description             			&  Dimensions (m)            	&  Mass (kg)  		& Total Mass (kg) \\
-		\midrule
-		2-seat Sofa        &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame 	&  1.68 L X 0.90 D X 0.86 H  	&  72.4    			& 144.8 \\
-		           	 	   & Mattress	    & 1 per sofa	& Cover: 52~\% PP, 48~\% PET,                   &  1.83 L X 1.21 W X 0.14 H     &  14.6             & \\
-		           	 	   &                &               & Filling: 66~\% PET Pad, 34~\% PET Batting     &                               &                   & \\
-			           	   & Cushion    	& 2 per sofa	& 85~\% PU Foam, 15~\% PET Fiber   				&  0.69 L X 0.58 D X 0.14 H  	&  2.2     			& \\
-		Blue Chair         &				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame   	&  0.81 L X 0.75 D X 0.91 H  	&  17.4    			& 34.8 \\
-		    			   & Cushion        & 1 per chair   & 85~\% PU Foam, 15~\% PET Fiber				&  0.51 L X 0.57 D X 0.14 H  	&  1.7    			& \\
-		Blue/Green Chair   & 				& 2				& 85~\% PU Foam, 15~\% PET Fiber, Wood Frame    &  0.77 L X 0.71 D X 0.89 H  	&  16    			& 32 \\
-		                   & Cushion    	& 1 per chair	& 85~\% PU Foam, 15~\% PET Fiber		        &  0.55 L X 0.53 D X 0.15 H  	&  1.6    			& \\
-		Paneling           &				& 8 panels		& Medium density fiberboard                     &  2.44 L X 1.22 W X 3.2~mm H   &  9    			& 72 \\
-		Carpeting          &				& 22.3 m$^2$	& 100~\% PET                  					&  3.68 L X 6.05 W  			&  32.2				& 32.2 \\
-		Carpet Padding     &				& 22.3 m$^2$	& PU                       	 				    &  3.68 L X 6.05 W X 11~mm H    &  19.8			    & 19.8 \\
-		                   &                &               &                                               &                               & Total Mass        & 335.6 \\
-		\bottomrule[1.25pt]
-	\end{tabular}
-	\label{tab:Fire_Suppression_Fuel_Masses}
-\end{sidewaystable}
+\subsection{Attic Fires}
+
+The fuel load for the attic fires, experiments 9 and 10, was essentially the OSB roof underlayment, and the wood trusses that support the roof.
+A 1.2 m (4 ft) square hole was opened between the center of the southern room in the single story structure and the attic space.
+A single stack of pallets as described for the wood fuel package tests was loacted below the hole and ignited.
+The fire was allowed to spread into the attic space.
+In addition to the connecting hole between the room and the attic space, the attic had openings along the eave line on both sides of the structure and gable openings on each end of the attic space.
 
@@
 \label{sec:suppresion_two}
+
+In June of 2015, the larger compartment experiments, experiments 15 through 22, were conducted in the lower level of the two story structure.
+Two different fuel packages were utitlized, the difference between the furniture fuel package used for experiments 15 and 16, and the furnitiure and pallet fuel package used in experiments 17 through 22 was the addition of two stacks of pallets.
 
@@
 The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}.
-In total, this fuel package was composed of wood, polyurethane (PU), polyester (PET),and polyprolene (PP).
+In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polyprolene (PP).
 
@@
 
+The results are arranged in the order that the experiments were conducted.
+For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilitized.
+
 \section{Spray Density}
@@
 
-Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking collector bins across the floor surface area of the burn rooms within each structure (cf.
+Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water colection pans across the floor surface area of the burn rooms within each structure (cf.
 Fig~\ref{fig:water_buckets}).
-The buildings were sheathed in plastic for the spray density tests to protect and preserve as much of the structure as possible before any fire suppression tests were conducted.
-Water flowed for a specified duration and upon completion the bins were removed from the structure.
+The depth of the pans was 0.3 m (1 ft).
+Water or CAF was flowed for a specified duration or until it appeared that a pan might be filled.
+Upon completion the bins were removed from the structure.
 Each bin was then weighed to quantify the impact of nozzle location and spray pattern.
-Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the concrete structure for the suppression experiments.
+Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the single story structure for the suppression experiments.
+The interior of the fire room in the single story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.
 The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF.
@@
 Figure~\ref{fig:stream_position} shows the streams from the monitor nozzle for the middle and back positions respectively.
+From the figures the qualitative difference of the nozzle positions can be seen.
+When the stream is in the middle position, after the stream hits the ceiling, the impact region is relatively narrow with the majority of the water hitting the walls of the corner opposite the nozzle position.
+When the nozzle is in the back position, the stream hits the ceiling at a much steeper angle and the droplets from the broken stream have a broader distribution throughout the room.
 
@@
 Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room.
-The remainder of the burn building spray density figures are included in Appnedix~\ref{app:spray_density}.
+The remainder of the burn building spray density figures are included in Appendix~\ref{app:spray_density}.
 
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB1}
-	\caption{Gas Cooling Spray Density Test 1}
+	\caption{Gas Cooling Spray Density Test 1, Straight Stream/Back nozzle position}
 	\label{fig:Burn_Building_Test_1}
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB7}
-	\caption{Gas Cooling Spray Density Test 7}
+	\caption{Gas Cooling Spray Density Test 7, 30 $^{\circ}$ Fog 
 	\label{fig:Burn_Building_Test_7}
@@
 
-The 88 gas cooling events were completed as part of 9 separate tests in the burn building.
+The 88 gas cooling events were completed as part of 9 separate burn sequences in the burn building.
 For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
-The focus of this analysis is to look at trends within the aggregate data.
+While Mitchell examined each individual experiment in detail, the results were mixed with CAF showing slightly better or slightly worse than plain water for different gas cooling experimental arrangements.
+Hence the conclusions was that there was no significant difference in gas cooling capabilities between CAF and water.
+
+Using the same data, the focus of this analysis was to look at trends within the aggregate data.
 During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
 Once this criteria was met, gas cooling began.
-Figure~\ref{fig:gas_cooling_exp4} shows 19 cooling events at one thermocouple array during a continuous test.
+Figure~\ref{fig:gas_cooling_exp4} shows 17 cooling events at one thermocouple array during a continuous burn sequence.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time Series of Multiple Gas Cooling Events From a 1 of 9 Tests}
+	\caption{Time Series of Multiple Gas Cooling Events From 1 of 9 Burn sequences}
 	\label{fig:gas_cooling_exp4}
@@
 For both sets a solid 7/8~in nozzle in the middle position was used.
-The data shows that thermocouples in the plot in the upper right of both figures has more significant temperature drops than the other two arrays; this is likely a result of that thermocouple array being directly ``hit'' by the suppression stream.
+The data shows that thermocouples from Gas Cooling Array 2 (GC_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC_1 and GC_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
+Gas Cooling Array 1 was exhibits some amount of suppression agent impact.
+Gas Cooling Array 3 is located behind the area where the stream impacts the celing for both the middle and back nozzle positions.
+As a result it remains dry and it seems to provide the best representation of the gas cooling.
 
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as Suppression Agent}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent}
 	\label{fig:gas_cooling_sub1}
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAFS as Suppression Agent}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAF as the Suppression Agent}
 	\label{fig:gas_cooling_sub5}

### 2016-07-07 Projects/DelCo_2012/Report/DelCo_2012.tex
More changes to Ch 3

@@
 
-The fire suppression series included 18 tests in two single-story experimental structures and one two-story structure.
-Fourteen tests were conducted in the single story structures (7 tests in each structure) using both water and CAF application as a suppression agent.
-The nozzle patterns were varied from straight stream to narrow fog.
-Two of the tests examined suppression tactics for attic fires in residential dwellings, one in each structure.
-For the attic tests, a smooth bore nozzle was used.
-The 4 two-story tests used both water and CAF from a straight-stream nozzle.
+The fire suppression series included 20 experiments in the single-story experimental structures and one two-story structure.
+Tweleve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent.
+The nozzle patterns were varied and included; straight stream, solid stream, and narrow fog.
+The two-story tests used both water and CAF from a straight-stream nozzle.
 
@@
 
-The fuel load for experiments 11 through 14 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
+The fuel load for experiments 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
@@
 
-\subsection{Attic Fires}
-
-The fuel load for the attic fires, experiments 9 and 10, was essentially the OSB roof underlayment, and the wood trusses that support the roof.
-A 1.2 m (4 ft) square hole was opened between the center of the southern room in the single story structure and the attic space.
-A single stack of pallets as described for the wood fuel package tests was loacted below the hole and ignited.
-The fire was allowed to spread into the attic space.
-In addition to the connecting hole between the room and the attic space, the attic had openings along the eave line on both sides of the structure and gable openings on each end of the attic space.
-
 \subsubsection*{Two Story Structure}
@@
 
-In June of 2015, the larger compartment experiments, experiments 15 through 22, were conducted in the lower level of the two story structure.
-Two different fuel packages were utitlized, the difference between the furniture fuel package used for experiments 15 and 16, and the furnitiure and pallet fuel package used in experiments 17 through 22 was the addition of two stacks of pallets.
+In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two story structure.
+Two different fuel packages were utitlized, the difference between the furniture fuel package used for experiments 13 and 14, and the furnitiure and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.
 
@@
 Each stack had 10 pallets.
-The mass of each stack was approximately 175 kg .
+The mass of each stack was approximately 175 kg.
 When hay was added for ignition, the bales of hay averaged 12 kg.
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB7}
-	\caption{Gas Cooling Spray Density Test 7, 30 $^{\circ}$ Fog 
+	\caption{Gas Cooling Spray Density Test 7, 30 $^{\circ}$ Fog} 
 	\label{fig:Burn_Building_Test_7}
@@
 
-The 88 gas cooling events were completed as part of 9 separate burn sequences in the burn building.
+The 88 gas cooling experiments were completed as part of 9 separate burn sequences in the burn building.
 For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
-While Mitchell examined each individual experiment in detail, the results were mixed with CAF showing slightly better or slightly worse than plain water for different gas cooling experimental arrangements.
-Hence the conclusions was that there was no significant difference in gas cooling capabilities between CAF and water.
+While Mitchell examined each individual experiment in detail, the results were mixed.
+In the different gas cooling scenarios CAF showed slightly better or slightly worse than plain water.
+Hence the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.
 
@@
 During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
+This condition was evidence that a hot gas layer at least 1.83~m deep had filled the room next to the burn room.
 Once this criteria was met, gas cooling began.
 Figure~\ref{fig:gas_cooling_exp4} shows 17 cooling events at one thermocouple array during a continuous burn sequence.
+No water or CAF was flowed into the burn room.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time Series of Multiple Gas Cooling Events From 1 of 9 Burn sequences}
+	\caption{Time Series of Multiple Gas Cooling Eexperiments from 1 of 9 Burn sequences}
 	\label{fig:gas_cooling_exp4}
@@
 For both sets a solid 7/8~in nozzle in the middle position was used.
-The data shows that thermocouples from Gas Cooling Array 2 (GC_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC_1 and GC_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
+The data shows that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
 Gas Cooling Array 1 was exhibits some amount of suppression agent impact.
@@
 To better quantify the effectiveness of the suppression agents (CAF, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
-Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for the 30 replicate tests, 15 water and 15 CAF, for all streams aimed at all positions.
+Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments, 15 water and 15 CAF, which were directly comparable.
+These experiments included solid stream, straight streams, and narrow fog streams at both nozzle positions.
+While the total number of experiments was 88, there where a number of experiments that were performed which did not have a directly comparable experiments between water and CAF.
+For example a set of 12 Class A solutions experiments were conducted.
+Gas cooling experiments were conducted with water applied on a wide fog nozzle setting, no significant differences were noted so a comparable series with wide fog CAF was not conducted.
+Similarly larger water flows were examined but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are not included in this comparison.
+The Mitchell report does include all of the data for the 88 experiments \cite{Mitchell:1}
+
+\textbf{Craig - the table of 30 could go here and the R squared paragraph could go with the first discussion of the red line below}
 
@@
 The data can be separated to examine the impact of nozzle position (back or middle position) on the ability to cool gases for each of the suppression agents.
-Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 replicates in the back position and 3 replicates in the middle position respectively.
+Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 pairs of experiments in the back position and 3 pairs of experiments in the middle position respectively.
 
@@
 
-To further analyze the data, the temperature differences can be separated by each of the three thermocouples in the fire room.
+To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the fire room.
 Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
+Ideally, the thermocouple is providing an estimate of the temperature of the gas that it is surrounded by.
+However, we must remember that the thermocouple is actually providing us with its own temperature.
+So if a droplet of water or some CAF cling to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.
+
 \begin{figure}[!ht]
@@
 Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
-Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
+As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
 \begin{figure}[!ht]
 	\includegraphics[width=.8\columnwidth]{../Figures/Bars/BB18b}
-	\caption{Gas Cooling Spray Density Test 18}
+	\caption{Gas Cooling Spray Density Test 18, CAF, Straight Stream}
 	\label{fig:Burn_Building_Test_18b}
@@
 Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively.
-Note that thermocouple array A3, the array which has the least amount of direct suppression, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
+Note that thermocouple array A3, the array which has the least amount of direct impact from the suppression agents, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
 The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF.
+Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF on cooling the thermocouples.
 
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Replicates}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Experimental Pairs}
 	\label{fig:CAFS_Water_A1_all}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Replicates}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Experimental Pairs}
 	\label{fig:CAFS_Water_A2_all}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Replicates}
+	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Experimental Pairs}
 	\label{fig:CAFS_Water_A3_all}
@@
 
-The thermocouple array data can also also be decomposed as a function of nozzle position: 12 middle position replicates and 3 back position replicates.
+The thermocouple array data can also also be decomposed as a function of nozzle position: 12 middle position experimental pairs and 3 back experimental pairs.
 Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position.
 Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 3 replicate tests with the monitor nozzle in the back position.
+Again note that the best fit occurs with the data from thermocouple array 3 for both nozzle positions.
+This analysis of the data results in the same conclusions at the analysis from the Mitchell paper \cite{Mitchell:1}, the gas cooling performance of CAF, under these conditions, is similar to water.
 
@@
 
-There were 14 suppression tests conducted in the single story purpose-built concrete structure.
+There were 12 suppression tests conducted in the single story purpose-built concrete structure.
 Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
@@
  8 & CAF~4    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
- 9 & Attic~1  &  Straight Stream  	&  120~gpm    		& Furniture      & Door            \\
-10 & Attic~2  &  Straight Stream  	&  120~gpm/60~cfm   & Furniture      & Door            \\
-11 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
-12 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
-13 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
-14 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+ 9 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
+10 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+11 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
+12 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 \bottomrule[1.25pt]
@@
 In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates.
-In both types of experiments there were no measurable differences between the use of plain water or compressed air foam.
-These results were not surprising to some of the workshop attendees.
-However other workshop attendees, that use CAF very successfully in their fire departments, had additional questions.
-The research team worked to address those follow-up questions by conducting additional fire suppression experiments, one where only wood based fuels were used and another where a larger space with more ventilation was used.
+In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam.
+These results were not surprising to some of the technical panel members.
+However other members, that use CAF very successfully in their fire departments every day, had additional questions.
+The research team worked to address those follow-up questions by conducting additional fire suppression experiments.
+One experiemntal used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+A final experimental series, used a larger fire room, with more ventilation.
+In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
 This section will discuss the results and provide potential explanations to support them.
@@
 
-The most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires.
-Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland fires.
-More recently these agents have been promoted for use on a wider range of Class A and in some cases Class B and D (combustible metal) fires.
-These agents are frequently claimed to be more effective than plain water while being environmentally safe.
+One of the most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires.
+Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires.
+Some of these agents are said to be more effective than plain water while being environmentally safe.
 In some cases, they are also claimed to reduce the quantity and toxicity of smoke.
@@
 The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
-During the planning of the experiments, some firefighters thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS, since the injected air, air being a great insulator, would interfere and result in less cooling.
-It was the belief that the reduced gas cooling capabilities of CAF may have lead to firefighter injuries during interior fire attacks.
+During the planning of the experiments, some workshop attendees thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS, since the injected air, air being a great insulator, would interfere and result in less cooling.
+It was the belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
 Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.

### 2016-07-08 Projects/DelCo_2012/Report/DelCo_2012.tex
continued work of discussion
modified test numbers and deleted attics

@@
 \midrule
- 38  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
- 39  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
- 40a & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 40b & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 40c & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 41a & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 41b & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 41c & CAF~9b    &  Solid Stream        &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 13  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
+ 14  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
+ 15  & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 16  & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 17  & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 20  & CAF~9b    &  Solid Stream        &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
-{\bf When a CAF stream was used it contained 0.3\% foam concentration by volume, check density of foam concentrate   point being mostly water.
-Also calc the mass of air in the stream.}
-
-Under the conditions of a residential scale room and contents fire it should be no surprise that the results are similar, the mass of water introduced into the hot gas layer is doing the work.
+
+When a CAF stream was used it contained 0.3\% foam concentration by volume, the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal), for a 15~s flow time, 3.6~kg (8.0 lb) of concentrate was used.
+In addition to the foam concentrate mixed with the water in the CAF stream is compressed air.
+The volume of air injected into the foam solution is 0.03~m$^3$/s (60~cfm).
+The density of the compressed air in the range of 100 to 150~psig, would be between 8.9~kg/m$^3$ (0.6 lb/ft$^3$) and 12.8~kg/m$^3$ (0.8 lb/ft$^3$).
+So a 15~s CAF flow would contain approximately 4.0~kg (8.8 lb) to 9.5~kg (21.0 lb) of air.
+Comparing the mass flows, and using the air mass based on the higher pressure, water still makes up more than 90~\% of the mass of the CAF stream.
+
+Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no suprised that the water is doing the work.
 Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
+At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.
 
@@
 \subsection{Iowa State Univeristy Fire Flow Formula (1963)~\cite{NFPA}}
-The Iowa Formula for determining the required fire flow for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
-The required fire flow in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
+The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
+The required fire flowrate in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
 \begin{equation}\label{eq:isu_form}
-\dot{Q} = V / 100
+\required fire flowrate = Volume / 100
 \end{equation}
 Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
-Applying the Iowa State University formula based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
+Applying the  based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
+Our fire rooms ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
+Therefore our required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
+The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).
 
@@
 \begin{equation}\label{eq:nfa_form}
-\dot{Q} = A / 3
+\required fire flowrate = Area / 3
 \end{equation}
-Applying the NFA formula based on floor area yields an application density of 13.6~Lpm/m$^2$ (0.33~gpm/ft$^2$).
+
+Our fire rooms ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
+Applying the NFA formula based on floor area yields an required flowrate for the single story fire room of 369~Lpm (97~gpm).
+The required flowrate for the fire room in the lower level of the two story would be approximately 700~Lpm (184~gpm).
+
+The flowrate used for these experiments were sufficent to quickly cool the hot gas layer and suppress each of the fires.
 

### 2016-07-08 Projects/DelCo_2012/Report/DelCo_2012.tex
Craig's paragraph and table + text changes in section 3

@@
 To better quantify the effectiveness of the suppression agents (CAF, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
-Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments, 15 water and 15 CAF, which were directly comparable.
+Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments.
+The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, which were directly comparable, see Table~\ref{tab:Gas_Cooling_Descriptions}.
 These experiments included solid stream, straight streams, and narrow fog streams at both nozzle positions.
@@
 
-\textbf{Craig - the table of 30 could go here and the R squared paragraph could go with the first discussion of the red line below}
+\begin{table}[!ht]
+\centering
+\caption{Gas Cooling Comparison Test Descriptions}\label{tab:Gas_Cooling_Descriptions}
+\begin{tabular}{clll}
+\toprule[1.5pt]
+Water Test $\#$  & CAF Test  $\#$	& Stream			  & Position  \\
+\midrule
+ 2               & 6                &  Solid Stream       &  Middle   \\
+ 3               & 7                &  Solid Stream       &  Middle   \\
+ 4               & 10               &  Solid Stream       &  Middle   \\
+ 9               & 11               &  Solid Stream       &  Middle   \\
+ 17              & 52               &  Solid Stream       &  Middle   \\
+ 18              & 53               &  Solid Stream       &  Middle   \\
+ 19              & 54               &  Solid Stream       &  Middle   \\
+ 16              & 45               &  Straight Stream    &  Middle   \\
+ 20              & 46               &  Straight Stream    &  Middle   \\
+ 21              & 47               &  Straight Stream    &  Middle   \\
+ 22              & 48               &  Straight Stream    &  Middle   \\
+ 41              & 50               &  Straight Stream    &  Middle   \\
+ 29              & 12               &  Straight Stream    &  Full Back   \\
+ 33              & 13               &  30$^{\circ}$ Fog   &  Full Back   \\
+ 34              & 14               &  30$^{\circ}$ Fog   &  Full Back   \\
+\bottomrule[1.25pt]
+\end{tabular}\par
+\end{table}
 
@@
 
+The quality of the fit of the red dashed line to the scatter in gas cooling data is represented by the coefficient of determination (R$^2$ on Fig.~\ref{fig:combined_all}).
+The coefficient of determination provides a way to quantify how significant the variation of the data is compared the the least squared error line.
+Here, the higher the value of R$^2$, the better the ordinary least square line describes the relationship between water and CAF temperature difference comparisons.
+
 The data can be separated to examine the impact of nozzle position (back or middle position) on the ability to cool gases for each of the suppression agents.
@@
 There were 12 suppression tests conducted in the single story purpose-built concrete structure.
-Four of the tests used a wood pallet fuel load (Section~\ref{sec:fire_suppression_pallet_fuel}) and the remaining tests used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for several tests a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
-The fires were intended to replicate room and contents fires typically seen within residential structures.
+Eight of the experiments used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
+The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
+Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was "opened" to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
+The fires were intended to replicate post-flashover residential room and contents fires.
 Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle).
@@
 Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack).
-The room nozzle was intended to simulate a crew which had advanced into a structure, entered the fire room, positioned just to the side of the entry door, and began suppression on the seat of the fire (direct interior attack).
+After the hallway nozzle was shutdown, there was a 15~s time period to simulate the crew advancing into the doorway of the fire room.
+The room nozzle was positioned just to the side of the entry door.
+It was also opened and flowed for approximately 15~s.
+The room nozzles was aimed in the direction of the seat of the fire (direct interior attack).
 Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.
@@
 These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
+Remeber that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow.
+As a result you can see the amount of temperature change during the period in between nozzle flows by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.
 
@@
 \begin{equation}\label{eq:isu_form}
-\required fire flowrate = Volume / 100
+required fire flowrate = Volume / 100
 \end{equation}
@@
 \begin{equation}\label{eq:nfa_form}
-\required fire flowrate = Area / 3
+required fire flowrate = Area / 3
 \end{equation}

### 2016-07-10 Projects/DelCo_2012/Report/DelCo_2012.tex
Added Abstract, keywords and start of Summary

@@
 \chapter*{\centering Abstract}
+
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.
+The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water.
+The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.
+Incidents where firefighters had experienced burn injuries or other challenges while using CAF during interior attack operations in residential occupancies served as the catalyst for this study.
+
+Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+The experimental arrangements and results are presented in this report.
+The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
+Under the test conditions both agents were effective.
+This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.
+
+This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
+
+\vspace{0.5in}
+Key words: compressed air foam, fire experiments, firefighting, fire suppression, fuel load, gas cooling, structural firefighting, suppression research
 
@@
 movement, sweeping nozzle, etc -- more efficient cooling / more effective that the type of nozzle or the amount of suppressive agent.
+air entrainment - ref hose stream study.
 
@@
 \label{chap:Summary}
+
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.
+The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.
+The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water.
+Incidents where firefighters had experienced burn injuries or other challenges while using CAF during interior attack operations in residential occupancies served as the catalyst for this study.
+
+Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+The experimental arrangements were designed to be representative of residential fire scenarios.
+
+Gas Cooling
+
+Fire Suppression
+
+The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
+Under the test conditions both agents were effective.
+This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.
+
+This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 

### 2016-07-10 Projects/DelCo_2012/Report/DelCo_2012.tex
Mods to MCFRS in Acknowledgements

@@
 
-Thank you to Chief Scott Goldstein and former Chief Steven Lohr of the Montgomery County (MD) Department of Fire and Rescue Service for their support of this study.
-The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Bryan Rojtas, Chris Reilly, Sean Regan, Alan Butsch, Ralph Thomas, Daniel Hudson, Michael Johns, and Douglas Wallace.
+Thank you to Chief Scott Goldstein and former Chief Steve Lohr of the Montgomery County (MD) Fire and Rescue Service for their support of this study.
+The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Alan Butsch, Daniel Hudson, Michael Johns, Steven Neubauer, Curtis Poole, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph Thomas, and Douglas Wallace.
 

### 2016-07-10 Projects/DelCo_2012/Report/DelCo_2012.tex
minor report edits, add data file and script for making scatters

@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup
@@
 The issue of a larger fire compartment had also been raised during the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
-In order to accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
+To accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
 The fuel load contained both wood-based wall and ceiling finishes, pallets as well as carpeting and upholstered furniture.
@@
 When the flow of CAF was needed for the experiment, the gated wye would be switched to allow the CAF to flow into the test structure.
-This was done to minimize, the build-up of "dry" foam or a slug upon the initial flow of the nozzle into the test structure.
+This was done to minimize, the build-up of``dry'' foam or a slug upon the initial flow of the nozzle into the test structure.
 
@@
 Similarly larger water flows were examined but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are not included in this comparison.
-The Mitchell report does include all of the data for the 88 experiments \cite{Mitchell:1}
+The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Replicate Tests}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Middle Position Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Back Position Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Bars/BB18b}
+	\includegraphics[width=.7\columnwidth]{../Figures/Bars/BB18b}
 	\caption{Gas Cooling Spray Density Test 18, CAF, Straight Stream}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Experimental Pairs}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Experimental Pairs}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Experimental Pairs}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
+	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
 	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
@@
 The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
-Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was "opened" to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
+Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was ``opened''to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
 The fires were intended to replicate post-flashover residential room and contents fires.
@@
 
-\subsection{Iowa State Univeristy Fire Flow Formula (1963)~\cite{NFPA}}
+\subsection{Iowa State Univeristy Fire Flow Formula (1963)}
 The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
@@
 Our fire rooms ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
-Therefore our required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
+Therefore the required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
 The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).
 
-\subsection{National Fire Academy (1884)~\cite{Klaene:1}}
+\subsection{National Fire Academy (1884)}
 The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
@@
 
-Our fire rooms ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
+The fire rooms in these experiments ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
 Applying the NFA formula based on floor area yields an required flowrate for the single story fire room of 369~Lpm (97~gpm).
@@
 
+\clearpage
+
 \chapter{Fire Suppression Figures}

### 2016-07-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Began to correct gas data for burner tests; airflow rate for hose stream tests
Added air flow rate to tables in hose stream report

@@
 
-\begin{table}[!ht]
-\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
-\begin{tabular}{lcccccccc}
+\begin{table}
+\footnotesize
+\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
+\begin{tabular}{lccccccccc}
 \toprule
- &  & \multicolumn{7}{c}{\large ----------------------------- 120 gpm -----------------------------} 
-\\
- &  & \underline{Test 1} &  & \multicolumn{2}{c}{\underline{Test 2}} &  & \multicolumn{2}{c}{\underline{Test 3}}
-\\
-\textbf{Stream} & \textbf{Units} &
+ &  &  & \multicolumn{7}{c}{\normalsize ----------------------------------- 120 gpm -----------------------------------} 
+\\
+ &  &  & \underline{\small Test 1} &  & \multicolumn{2}{c}{\underline{\small Test 2}} &  & \multicolumn{2}{c}{\underline{\small Test 3}}
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
 \begin{tabular}{@{}c@{}} \textbf{Room B} \\ \textbf{South} \\ \textbf{Doorway} \end{tabular} &  &
@@
 \midrule
-\multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   & -0.3 $\pm0.1$   & &  0.9 $\pm0.2$  &  0.9 $\pm0.2$  & &  0.7 $\pm0.1$  & 0.7 $\pm0.1$ \\ &
-\small{(mph)} & (-0.7 $\pm0.1$) & & (2.0 $\pm0.4$) & (2.1 $\pm0.4$) & & (1.5 $\pm0.3$) & (1.5 $\pm0.3$) 
-\\~\\
-\multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   1.1 $\pm0.2$  & &   1.0 $\pm0.2$  &   1.4 $\pm0.3$  & &  0.8 $\pm0.1$   & 0.8 $\pm0.1$ \\ &
-\small{(mph)} &  (2.5 $\pm0.5$) & &  (2.1 $\pm0.4$) &  (3.2 $\pm0.6$) & &  (1.7 $\pm0.3$) & (1.7 $\pm0.3$) 
-\\~\\
-\multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &  2.5 $\pm0.4$  & &   1.3 $\pm0.2$   &  1.4 $\pm0.2$   & &   1.2 $\pm0.2$  & 0.8 $\pm0.1$ \\ &
-\small{(mph)} & (5.6 $\pm1.0$) & &  (2.8 $\pm0.5$)  & (3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) & (1.7 $\pm0.3$) 
-\\ \midrule
- &  & \multicolumn{3}{c}{\large ------ 180 gpm ------} & \multicolumn{4}{c}{} 
-\\
- &  & \multicolumn{3}{c}{\underline{Test 4}} & \multicolumn{4}{c}{} 
-\\
-\textbf{Stream} & \textbf{Units} &
+\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
+& 		 m/s 	&	 -0.3 $\pm0.1$		& &	 0.9 $\pm0.2$ 	&	 0.9 $\pm0.2$	& &	 0.7 $\pm0.1$	&	 0.7 $\pm0.1$ \\
+&	&	(mph) 	& 	(-0.7 $\pm0.1$) 	& &	(2.0 $\pm0.4$)	&	(2.1 $\pm0.4$)	& &	(1.5 $\pm0.3$)	&	(1.5 $\pm0.3$) 
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
+&	 	m$^3$/s	&	 -0.6 $\pm0.1$   	& &  1.5 $\pm0.3$	&	 1.5 $\pm0.3$  	& &  1.1 $\pm0.2$   & 	 1.1 $\pm0.2$ \\
+& 	&	(cfm)	& 	(-1235 $\pm222$)	& & (3082 $\pm555$) &	(3272 $\pm589$) & & (2397 $\pm432$) &	(2413 $\pm434$) 
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Narrow} \\ \textit{\small Fog} \end{tabular}} & \multirow{2}{*}{Velocity}
+& 		 m/s   	&    1.1 $\pm0.2$  		& &	 1.0 $\pm0.2$	&	 1.4 $\pm0.3$  	& &   0.8 $\pm0.1$  & 	 0.8 $\pm0.1$ \\
+&	&	(mph) 	&	(2.5 $\pm0.5$) 		& &	(2.1 $\pm0.4$)	&	(3.2 $\pm0.6$) 	& &  (1.7 $\pm0.3$) & 	(1.7 $\pm0.3$) 
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
+&		m$^3$/s &	 2.1 $\pm0.4$   	& &  1.6 $\pm0.3$	&	 2.4 $\pm0.4$  	& &  1.3 $\pm0.2$   & 	 1.2 $\pm0.2$ \\
+& 	&	(cfm)	&	(4483 $\pm807$)		& & (3335 $\pm600$) &	(4980 $\pm896$) & & (2726 $\pm491$) &	(2631 $\pm474$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Wide} \\ \textit{\small Fog} \end{tabular}} & 
+\multirow{2}{*}{Velocity}
+& 		 m/s   	&	 2.5 $\pm0.4$  		& &  1.3 $\pm0.2$	&	 1.4 $\pm0.2$   & &	 1.2 $\pm0.2$  	& 	 0.8 $\pm0.1$ \\
+& 	& 	(mph) 	&	(5.6 $\pm1.0$) 		& & (2.8 $\pm0.5$)	&	(3.1 $\pm0.6$)  & & (2.7 $\pm0.5$) 	& 	(1.7 $\pm0.3$) 
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
+&	 	m$^3$/s	&	 4.6 $\pm0.8$   	& &  2.1 $\pm0.4$	&	 2.3 $\pm0.4$  	& &  2.0 $\pm0.4$   & 	 1.3 $\pm0.2$ \\
+& 	&	(cfm)	& 	(9812 $\pm1766$)	& & (4385 $\pm789$) &	(4784 $\pm861$) & & (4183 $\pm753$) &	(2738 $\pm493$)
+\\
+\midrule
+ &  & 	& 	\multicolumn{3}{c}{\normalsize -------- 180 gpm --------} & \multicolumn{4}{c}{} 
+\\
+ &  & 	&	\multicolumn{3}{c}{\underline{\small Test 4}} & \multicolumn{4}{c}{} 
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
 \begin{tabular}{@{}c@{}} \textbf{Near} \\ \textbf{Target} \\ \end{tabular} &
@@
 \midrule
-\multirow{2}{*}{\textit{Straight}} &
-\small{m/s}   &   1.8 $\pm0.3$   & \multicolumn{2}{c}{2.0 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
-\small{(mph)} &  (3.9 $\pm0.7$) & \multicolumn{2}{c}{(4.4 $\pm0.8$)} & \multicolumn{4}{c}{} 
-\\~\\
-\multirow{2}{*}{\textit{Smooth Bore}} &
-\small{m/s}   &   1.8 $\pm0.3$  &  \multicolumn{2}{c}{2.1 $\pm0.4$}  & \multicolumn{4}{c}{} \\ &
-\small{(mph)} &  (4.0 $\pm0.7$) & \multicolumn{2}{c}{(4.8 $\pm0.9$)} & \multicolumn{4}{c}{} \\
+\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
+& 		 m/s   	&	 1.8 $\pm0.3$		&	\multicolumn{2}{c}{ 2.0 $\pm0.4$}		& \multicolumn{4}{c}{} \\
+& 	&	(mph) 	&	(3.9 $\pm0.7$) 		&	\multicolumn{2}{c}{(4.4 $\pm0.8$)}		& \multicolumn{4}{c}{} 
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
+&		m$^3$/s &	 2.9 $\pm0.5$  		& 	\multicolumn{2}{c}{ 3.2 $\pm0.6$}		& \multicolumn{4}{c}{} \\
+& 	&	(cfm)	&	(6130 $\pm1103$) 	&	\multicolumn{2}{c}{(6884 $\pm1239$)}	& \multicolumn{4}{c}{}
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Smooth} \\ \textit{\small Bore} \end{tabular}} &
+\multirow{2}{*}{Velocity}
+&		 m/s  	&	 1.8 $\pm0.3$		&	\multicolumn{2}{c}{ 2.1 $\pm0.4$}		& \multicolumn{4}{c}{} \\
+&	&	(mph)	&	(4.0 $\pm0.7$)		&	\multicolumn{2}{c}{(4.8 $\pm0.9$)}		& \multicolumn{4}{c}{}
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} Airflow \\ Rate \end{tabular}} 
+&		m$^3$/s &	 3.0 $\pm0.5$		& 	\multicolumn{2}{c}{ 3.5 $\pm0.6$} 		& \multicolumn{4}{c}{} \\
+& 	&	(cfm)	&	(6253 $\pm1126$) 	&	\multicolumn{2}{c}{(7466 $\pm1344$)} 	& \multicolumn{4}{c}{}
+\\
 \bottomrule
@@
 \begin{table}[!ht]
-\caption{Average gas velocity [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
-\begin{tabular}{lcccc}
+\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
+\begin{tabular}{lccccc}
 \toprule
- &  & \multicolumn{3}{c}{\underline{Room A}}
-\\
-\textbf{Stream} & \textbf{Units} & 
+ &	&	&	\multicolumn{3}{c}{\underline{Room A}}
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
 \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   &   0.2 $\pm0.03$   &   0.7 $\pm0.1$  &   0.8 $\pm0.2$  \\ & 
-\small{(mph)} &  (0.4 $\pm0.1$)   &  (1.5 $\pm0.3$) &  (1.9 $\pm0.3$)
-\\~\\
-\multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   1.7 $\pm0.3$   &   1.8 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
-\small{(mph)} &  (3.9 $\pm0.7$)  &  (4.0 $\pm0.7$) &  (3.5 $\pm0.6$)
-\\~\\
-\multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   1.8 $\pm0.3$   &   2.1 $\pm0.4$  &   2.2 $\pm0.4$  \\ & 
-\small{(mph)} &  (4.1 $\pm0.7$)  &  (4.8 $\pm0.9$) &  (4.9 $\pm0.9$)  
-\\ \midrule
- & & \multicolumn{3}{c}{\underline{Room B Ceiling}}
-\\
-\textbf{Stream} & \textbf{Units} & 
+\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+& 		 \small{m/s}   	&   0.2 $\pm0.03$	&   0.7 $\pm0.1$	&	 0.8 $\pm0.2$  \\ 
+&	&	 \small{(mph)} 	&  (0.4 $\pm0.1$)	&  (1.5 $\pm0.3$)	&	(1.9 $\pm0.3$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 0.3 $\pm0.1$	&  1.2 $\pm0.2$		&	 1.6 $\pm0.3$  	\\
+& 	&	\small{(cfm)}	& 	(628 $\pm113$)	& (2584 $\pm465$) 	&	(3291 $\pm592$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+& 		\small{m/s}   	&	 1.7 $\pm0.3$   	&	 1.8 $\pm0.3$  	&   1.6 $\pm0.3$   \\
+&	&	\small{(mph)} 	&	(3.9 $\pm0.7$) 		&	(4.0 $\pm0.7$) 	&  (3.5 $\pm0.6$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 3.2 $\pm0.6$   	&	 3.3 $\pm0.6$		&	 2.9 $\pm0.5$  	\\
+& 	&	\small{(cfm)}	& 	(6786 $\pm1222$)	&	(6977 $\pm1256$) 	&	(6228 $\pm1121$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+&		\small{m/s} 	&	 1.8 $\pm0.3$   	&   2.1 $\pm0.4$  	&   2.2 $\pm0.4$  \\ 
+& 	& 	\small{(mph)}	&	(4.1 $\pm0.7$)  	&  (4.8 $\pm0.9$) 	&  (4.9 $\pm0.9$)  
+\\ ~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 3.4 $\pm0.6$   	&  4.0 $\pm0.7$		&	 4.1 $\pm0.7$  	\\
+& 	&	\small{(cfm)}	& 	(7283 $\pm1311$)	& (8463 $\pm1523$) 	&	(8669 $\pm1561$) \\
+\midrule
+&	&	&	\multicolumn{3}{c}{\underline{Room B Ceiling}}
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
 \textbf{Fixed} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   &  -0.1 $\pm0.02$    &  0.6 $\pm0.1$   &   0.5 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.2 $\pm0.04$)  &  (1.4 $\pm0.3$) &  (1.2 $\pm0.2$)
-\\~\\
-\multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   0.9 $\pm0.2$   &   1.5 $\pm0.3$  &   1.6 $\pm0.3$   \\ & 
-\small{(mph)} &  (2.1 $\pm0.4$)  &  (3.4 $\pm0.6$) &  (3.7 $\pm0.7$)
-\\~\\
-\multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   2.1 $\pm0.4$   &   2.3 $\pm0.4$  &   2.6 $\pm0.5$  \\ & 
-\small{(mph)} &  (4.7 $\pm0.8$)  &  (5.2 $\pm0.9$) &  (5.8 $\pm1.1$) \\ 
+\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+& 		 \small{m/s}   	&   -0.1 $\pm0.02$    	&   0.6 $\pm0.1$   	&	 0.5 $\pm0.1$  \\ 
+&	&	 \small{(mph)} 	&  (-0.2 $\pm0.04$)  	&  (1.4 $\pm0.3$) 	&	(1.2 $\pm0.2$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 -0.2 $\pm0.03$   	&  1.2 $\pm0.2$		&	 1.0 $\pm0.2$  	\\
+& 	&	\small{(cfm)}	& 	(-381 $\pm69$)		& (2469 $\pm445$) 	&	(2155 $\pm388$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+& 		\small{m/s}   	&   0.9 $\pm0.2$   		&   1.5 $\pm0.3$  	&   1.6 $\pm0.3$   \\
+&	&	\small{(mph)} 	&  (2.1 $\pm0.4$)  		&  (3.4 $\pm0.6$) 	&  (3.7 $\pm0.7$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 1.8 $\pm0.3$   	&  2.9 $\pm0.5$		&	 3.1 $\pm0.6$  	\\
+& 	&	\small{(cfm)}	& 	(3739 $\pm673$)		& (6046 $\pm1088$) 	&	(6479 $\pm1166$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+&		\small{m/s} 	&   2.1 $\pm0.4$   		&   2.3 $\pm0.4$  	&   2.6 $\pm0.5$  \\ 
+& 	& 	\small{(mph)}	&  (4.7 $\pm0.8$)  		&  (5.2 $\pm0.9$) 	&  (5.8 $\pm1.1$)  
+\\ ~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 3.9 $\pm0.7$   	&  4.3 $\pm0.8$		&	 4.8 $\pm0.9$  	\\
+& 	&	\small{(cfm)}	& 	(8271 $\pm1489$)	& (9165 $\pm1650$) 	&	(10273 $\pm1849$) \\
 \bottomrule
@@
 \begin{table}[!ht]
-\caption{Average gas velocity [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
-\begin{tabular}{lccccc}
+\caption{Average gas velocity and airflow rate [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
+\begin{tabular}{lcccccc}
 \toprule
- & & \multicolumn{4}{c}{\underline{Test 6}}
-\\
-\textbf{Stream} & \textbf{Units} & 
-\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+&	&	&	\multicolumn{4}{c}{\underline{Test 6}}
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
+\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & 
+\begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
 \\ \midrule
-\multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   &  -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
-\\~\\
-\multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   0.4 $\pm0.1$   &   1.1 $\pm0.2$  &   0.9 $\pm0.2$   &  1.1 $\pm0.2$  \\ & 
-\small{(mph)} &  (0.9 $\pm0.2$)  &  (2.4 $\pm0.4$) &  (1.9 $\pm0.3$)  & (2.4 $\pm0.4$)
-\\~\\
-\multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   1.0 $\pm0.2$   &   1.0 $\pm0.2$  &   1.0 $\pm0.2$   &  0.9 $\pm0.2$  \\ & 
-\small{(mph)} &  (2.2 $\pm0.4$)  &  (2.1 $\pm0.4$) &  (2.2 $\pm0.4$)  & (2.0 $\pm0.4$) \\ 
-\midrule
- & & \multicolumn{4}{c}{\underline{Test 7}}
-\\
-\textbf{Stream} & \textbf{Units} & 
-\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & \begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity} 
+& 		\small{m/s}		&   -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ 
+&	&	\small{(mph)}	&  (-0.4 $\pm0.1$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.7 $\pm0.3$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 -0.3 $\pm0.1$		&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.2 $\pm0.2$  	\\
+& 	&	\small{(cfm)}	& 	(-670 $\pm121$)		&	(1864 $\pm336$)		&	(2549 $\pm459$)		& 	(2602 $\pm468$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+&		\small{m/s}   	&	 0.4 $\pm0.1$   	&	 1.1 $\pm0.2$		&	 0.9 $\pm0.2$		&	 1.1 $\pm0.2$  \\ 
+&	&	\small{(mph)} 	&	(0.9 $\pm0.2$)  	&	(2.4 $\pm0.4$)		&	(1.9 $\pm0.3$)		& 	(2.4 $\pm0.4$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 0.7 $\pm0.1$   	&	 1.7 $\pm0.3$		&	 1.4 $\pm0.3$  		&	 1.8 $\pm0.3$  	\\
+& 	&	\small{(cfm)}	& 	(1471 $\pm265$)		&	(3688 $\pm664$) 	&	(3034 $\pm546$)		& 	(3786 $\pm682$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+&		\small{m/s}   	&    1.0 $\pm0.2$   	&	 1.0 $\pm0.2$  		&	 1.0 $\pm0.2$   	&  	 0.9 $\pm0.2$  \\  
+&	&	\small{(mph)} 	&	(2.2 $\pm0.4$)  	&	(2.1 $\pm0.4$) 		&  	(2.2 $\pm0.4$)  	& 	(2.0 $\pm0.4$) 
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 1.6 $\pm0.3$   	&	 1.6 $\pm0.3$		&	 1.6 $\pm0.3$  		&	 1.4 $\pm0.3$  	\\
+& 	&	\small{(cfm)}	& 	(3369 $\pm606$)		&	(3362 $\pm605$) 	&	(3453 $\pm622$)		& 	(3051 $\pm549$)
 \\ \midrule
-\multirow{2}{*}{\textit{Straight}} & 
-\small{m/s}   &   0.0 $\pm0.01$    &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ & 
-\small{(mph)} &  (-0.1 $\pm0.02$)  &  (1.2 $\pm0.2$) &  (1.6 $\pm0.3$)  & (1.5 $\pm0.3$)
-\\~\\
-\multirow{2}{*}{\textit{Narrow Fog}} & 
-\small{m/s}   &   1.3 $\pm0.2$   &   1.2 $\pm0.2$  &   1.2 $\pm0.2$   &  1.3 $\pm0.2$  \\ & 
-\small{(mph)} &  (2.9 $\pm0.5$)  &  (2.8 $\pm0.5$) &  (2.7 $\pm0.5$)  & (2.9 $\pm0.5$)
-\\~\\
-\multirow{2}{*}{\textit{Wide Fog}} & 
-\small{m/s}   &   1.0 $\pm0.2$   &   0.7 $\pm0.1$  &   0.9 $\pm0.2$   &  1.0 $\pm0.2$  \\ & 
-\small{(mph)} &  (2.2 $\pm0.4$)  &  (1.6 $\pm0.3$) &  (2.1 $\pm0.4$)  & (2.2 $\pm0.4$) \\ 
-\bottomrule
+& 	& 	&	\multicolumn{4}{c}{\underline{Test 7}}
+\\
+\textbf{Stream} & \textbf{Value} & \textbf{Units} &
+\textbf{Fixed} & \textbf{Sweeping} & \textbf{Clockwise} & 
+\begin{tabular}{@{}c@{}} \textbf{Counter} \\ \textbf{Clockwise} \\ \end{tabular}
+\\ \midrule
+\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+&		\small{m/s}   	&	 0.0 $\pm0.01$		&	 0.5 $\pm0.1$  		&	 0.7 $\pm0.1$   	&	 0.7 $\pm0.1$  \\ 
+&	&	\small{(mph)} 	&	(-0.1 $\pm0.02$)	&	(1.2 $\pm0.2$)		&	(1.6 $\pm0.3$)  	&	(1.5 $\pm0.3$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 -0.1 $\pm0.01$   	&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.1 $\pm0.2$  	\\
+& 	&	\small{(cfm)}	& 	(-152 $\pm27$)		&	(1804 $\pm325$) 	&	(2473 $\pm445$)		& 	(2358 $\pm425$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+&		\small{m/s}   	&	 1.3 $\pm0.2$   	&	 1.2 $\pm0.2$  		&	 1.2 $\pm0.2$   	&	 1.3 $\pm0.2$  \\ 
+&	&	\small{(mph)} 	&	(2.9 $\pm0.5$)  	&	(2.8 $\pm0.5$) 		&	(2.7 $\pm0.5$)  	&	(2.9 $\pm0.5$)
+\\~\\
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 2.1 $\pm0.4$   	&  	 2.0 $\pm0.4$		&	 2.0 $\pm0.4$  		& 	 2.1 $\pm0.4$ 	\\
+& 	&	\small{(cfm)}	& 	(4494 $\pm809$)		& 	(4326 $\pm779$) 	&	(4214 $\pm759$)		& 	(4477 $\pm806$)
+\\~\\
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+&		\small{m/s}   	&	 1.0 $\pm0.2$   	&	 0.7 $\pm0.1$  		&	 0.9 $\pm0.2$   	&	 1.0 $\pm0.2$  \\ 
+&	&	\small{(mph)} 	&	(2.2 $\pm0.4$)  	&	(1.6 $\pm0.3$) 		&	(2.1 $\pm0.4$)  	& 	(2.2 $\pm0.4$) 
+\\~\\ 
+&	\multirow{2}{*}{ \begin{tabular}{@{}c@{}} \small{Airflow} \\ \small{Rate} \end{tabular}} 
+&	 	\small{m$^3$/s}	&	 1.7 $\pm0.3$   	&	 1.2 $\pm0.2$		&	 1.6 $\pm0.3$  		& 	 1.6 $\pm0.3$	\\
+& 	&	\small{(cfm)}	& 	(3509 $\pm632$)		&	(2503 $\pm451$) 	&	(3299 $\pm594$)		& 	(3428 $\pm617$)
+\\ \bottomrule
 \end{tabular}

### 2016-07-11 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -701,8 +701,8 @@ for f in os.listdir(data_dir):
 
 									flow_rate = avg_m_per_s*area
 									print
-									print '		m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
-									print '		cfm     ' + str(round(flow_rate*m3s_to_cfm,1)) + ' (+/-)' + str(round(abs(m3s_to_cfm*flow_rate)*0.18, round_place))
+									print '			m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
+									print '			cfm     ' + str(round(flow_rate*m3s_to_cfm,1)) + ' (+/-)' + str(round(abs(m3s_to_cfm*flow_rate)*0.18, round_place))
 									print
 						else:
 							m_per_s_data = []
@@ -728,8 +728,8 @@ for f in os.listdir(data_dir):
 							
 							flow_rate = avg_m_per_s*area
 							print
-							print '		m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
-							print '		cfm     ' + str(round(flow_rate*m3s_to_cfm,1)) + ' (+/-)' + str(round(abs(m3s_to_cfm*flow_rate)*0.18, round_place))
+							print '			m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
+							print '			cfm     ' + str(round(flow_rate*m3s_to_cfm,1)) + ' (+/-)' + str(round(abs(m3s_to_cfm*flow_rate)*0.18, round_place))
 							print
 					else:
 						PorL_options = stream_seq_info.groupby(P_or_L)

### 2016-07-11 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added page numbers to hose stream report

@@
 \vspace*{2\baselineskip}
-June 2016}
+July 2016}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2015) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (July 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 To better quantify the impact of such air flows on the fire environment, additional experiments need to be conducted with structure fires in a controlled environment.
+
+\mainmatter
 

### 2016-07-12 Projects/DelCo_2012/Report/DelCo_2012.tex
editorial to build
Remove Fire Suppression Graphics
Also added tests to Spray Density Appendix

@@
 
-To better visualize the data presented in Table~\ref{tab:Test_Results}, Fig.~\ref{fig:fs_1_1} shows the thermocouple temperature and heat flux changes for CAF Test 1 as a result of the hallway (first) and room (second) suppression actions.
-Fig.~\ref{fig:fs_1_2} shows the same impacts as Fig.~\ref{fig:fs_1_1}, except that the tests used water.
-
-\begin{figure}[ht!]
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-	\label{fig:fs_1_1}
-\end{figure}
-
-\begin{figure}[ht!]
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
-	\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
-	\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-	\label{fig:fs_1_2}
-\end{figure}
-
 Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, differences are not substantial.
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
+\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right).}
 \label{fig:bb_1_4}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 5 (upper left), 6 (upper right), 7 (lower left), and 8 (lower right).}
+\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right).}
 \label{fig:bb_5_8}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 9 (upper left), 10 (upper right), 11 (lower left), and 12 (lower right).}
+\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right).}
 \label{fig:bb_9_12}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 13 (upper left), 14 (upper right), 15 (lower left), and 16 (lower right).}
+\caption{Spray density figures for burn building tests 13) CAF Solid Stream Mid (upper left), 14) CAF Solid Stream Back (upper right), 15) CAF Solid Stream Mid (lower left), and 16) CAF Fog Mid (lower right).}
 \label{fig:bb_13_16}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 17 (upper left), 18 (upper right), 19 (lower left), and 20 (lower right).}
+\caption{Spray density figures for burn building tests 17) CAF Straight Stream Mid (upper left), 18) CAF Straight Stream Mid (upper right), 19) CAF Fog Back (lower left), and 20) CAF Fog Back (lower right).}
 \label{fig:bb_19_21}
@@
 \includegraphics[width=3.2in]{../Figures/Bars/BB21}
-\caption{Spray density figures for burn building test 21.}
+\caption{Spray density figures for burn building test 21) CAF Straight Stream Back.}
 \label{fig:bb_21}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 1 (upper left), 2 (upper right), 3 (lower left), and 4 (lower right).}
+\caption{Spray density figures for experimental structure tests 1) Water Straight Stream FR (upper left), 2) Water Straight Stream FR (upper right), 3) Water Straight Stream FR (lower left), and 4) Water Straight Stream FR (lower right).}
 \label{fig:es_1_4}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 5 (upper left), 6 (upper right), 7 (lower left), and 7.2 (lower right).}
+\caption{Spray density figures for experimental structure tests 5) Water Fog FR (upper left), 6) Water Fog FR (upper right), 7) Water Solid Stream FR (lower left), and 8) Water Solid Stream H (lower right).}
 \label{fig:es_5_72}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 8 (upper left), 9 (upper right), 10 (lower left), and 11 (lower right).}
+\caption{Spray density figures for experimental structure tests 9) Water Fog H (upper left), 10) Water Fog H (upper right), 11) Water Straight Stream H (lower left), and 12) Water Straight Stream H (lower right).}
 \label{fig:es_8_11}
@@
 
-\chapter{Fire Suppression Figures}
+\chapter{Fire Suppression Data}
 \label{app:fire_suppression}
 
-\begin{figure}[ht!]
-\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1FirstSuppression}
-\includegraphics[width=.82\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest1SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 1 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_1}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest2SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 1 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_2}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest3SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 2 with a 7/8'' 
-Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_3}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoSSTest4SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 2 with a 7/8'' 
-Solid Stream nozzle. The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_4}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest5SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 3 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_5}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest6SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 3 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_6}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest7SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 4 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_7}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest8SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 4 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_8}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest11SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 5 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_11}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest12SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 5 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_12}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest13SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for Water Test 6 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_13}
-\end{figure}
-
-\clearpage
-
-\begin{figure}[ht!]
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14FirstSuppression}
-\includegraphics[width=\columnwidth]{../Figures/Pictures/Metric/DelCoFogTest14SecondSuppression}
-\caption{Impact of fire suppression actions on thermocouple and heat flux measurements for CAFS Test 6 with a 30$^{\circ}$ Fog nozzle.
-The top image shows the hallway suppression impact and the bottom images shows the room suppression impact.}
-\label{fig:app_fs_14}
-\end{figure}
-
 \end{document}

### 2016-07-12 Projects/DelCo_2012/Report/DelCo_2012.tex
more edits to CAFS

@@
 CAFS \> Compressed Air Foam System \\
+Cal Poly \> California Polytechnic State University, San Luis Obispo \\
 ESTC \> Delaware County Emergency Services Training Center \\
@@
 
-This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study, conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
 This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
@@
 These experiments included solid stream, straight streams, and narrow fog streams at both nozzle positions.
-While the total number of experiments was 88, there where a number of experiments that were performed which did not have a directly comparable experiments between water and CAF.
-For example a set of 12 Class A solutions experiments were conducted.
-Gas cooling experiments were conducted with water applied on a wide fog nozzle setting, no significant differences were noted so a comparable series with wide fog CAF was not conducted.
-Similarly larger water flows were examined but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are not included in this comparison.
-The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}
+While the total number of experiments was 88, there where a number of experiments that were performed which did not have a directly comparable experiment between water and CAF.
+For example a set of 12 Class A solution experiments were conducted.
+Gas cooling experiments were conducted with water applied on a wide fog nozzle setting, and since no significant differences were noted compared to narrow fog a comparable series with wide fog CAF was not conducted.
+Similarly, larger water flows were examined but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are also not included in this comparison.
+The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}.
 
@@
                  & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
-Test 	         & 0.3~m Below Ceiling                 & 0.3~m  Above Floor	                 & 0.15~m Above Floor \\
+Test \# \& Nozzle	         & 0.3~m Below Ceiling                 & 0.3~m  Above Floor	                 & 0.15~m Above Floor \\
 \midrule
-CAF~1 Hallway    & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-CAF~1 Room       & 250~$^{\circ}$C - 60~$^{\circ}$C    & 90~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-Water~1 Hallway  & 770~$^{\circ}$C - 300~$^{\circ}$C   & 760~$^{\circ}$C - 180~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
-Water~1 Room     & 180~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAF~2 Hallway    & 690~$^{\circ}$C - 290~$^{\circ}$C   & 690~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~2 Room       & 220~$^{\circ}$C - 80~$^{\circ}$C    & 110~$^{\circ}$C - 70~$^{\circ}$C    & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-Water~2 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-Water~2 Room     & 250~$^{\circ}$C - 50~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-Water~3 Hallway  & 770~$^{\circ}$C - 190~$^{\circ}$C   & 680~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~3 Room     & 260~$^{\circ}$C - 180~$^{\circ}$C   & 90~$^{\circ}$C - 20~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 840~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~1 Hallway    & 690~$^{\circ}$C - 180~$^{\circ}$C   & 590~$^{\circ}$C - 150~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+CAF~1 Room       & 170~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+Water~1 Hallway  & 720~$^{\circ}$C - 220~$^{\circ}$C   & 700~$^{\circ}$C - 120~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
+Water~1 Room     & 120~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~2 Hallway    & 590~$^{\circ}$C - 290~$^{\circ}$C   & 500~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
+CAF~2 Room       & 80~$^{\circ}$C -  70~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~2 Hallway  & 640~$^{\circ}$C - 410~$^{\circ}$C   & 500~$^{\circ}$C - 230~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
+Water~2 Room     & 460~$^{\circ}$C - 300~$^{\circ}$C   & 200~$^{\circ}$C - 140~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~3 Hallway  & 610~$^{\circ}$C - 300~$^{\circ}$C   & 580~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~3 Room     & 210~$^{\circ}$C - 130~$^{\circ}$C   & 60~$^{\circ}$C - 40~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 780~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
 CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-Water~4 Hallway  & 860~$^{\circ}$C - 430~$^{\circ}$C   & 870~$^{\circ}$C - 210~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~4 Room     & 260~$^{\circ}$C - 160~$^{\circ}$C   & 120~$^{\circ}$C - 50~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-CAF~4 Hallway    & 620~$^{\circ}$C - 270~$^{\circ}$C   & 550~$^{\circ}$C - 220~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
+Water~4 Hallway  & 850~$^{\circ}$C - 360~$^{\circ}$C   & 850~$^{\circ}$C - 180~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~4 Room     & 190~$^{\circ}$C - 100~$^{\circ}$C   & 130~$^{\circ}$C - 70~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~4 Hallway    & 620~$^{\circ}$C - 240~$^{\circ}$C   & 530~$^{\circ}$C - 180~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
 CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-Water~5 Hallway  & 820~$^{\circ}$C - 380~$^{\circ}$C   & 420~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
-Water~5 Room     & 400~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 90~$^{\circ}$C    & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
-CAF~5 Hallway    & 650~$^{\circ}$C - 420~$^{\circ}$C   & 690~$^{\circ}$C - 20~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
+Water~5 Hallway  & 700~$^{\circ}$C - 390~$^{\circ}$C   & 400~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
+Water~5 Room     & 210~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 100~$^{\circ}$C   & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
+CAF~5 Hallway    & 550~$^{\circ}$C - 400~$^{\circ}$C   & 360~$^{\circ}$C - 30~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
 CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
-Water~6 Hallway  & 800~$^{\circ}$C - 150~$^{\circ}$C   & 650~$^{\circ}$C - 20~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~6 Room     & 200~$^{\circ}$C - 90~$^{\circ}$C    & 60~$^{\circ}$C - 40~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
-CAF~6 Hallway    & 760~$^{\circ}$C - 180~$^{\circ}$C   & 340~$^{\circ}$C - 30~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~6 Hallway  & 770~$^{\circ}$C - 160~$^{\circ}$C   & 480~$^{\circ}$C - 50~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
+Water~6 Room     & 150~$^{\circ}$C - 90~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~6 Hallway    & 650~$^{\circ}$C - 190~$^{\circ}$C   & 570~$^{\circ}$C - 60~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
 CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
@@
 In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
+
+Rekindling and the impact of the second nozzle can been seen in the time-temperature data of thermocouples within the fire room.
+Figure~\ref{fig:fs_instruments} shows the positions of thermocouple arrays TC A1 and TC A2.
+Note that TC A1 is closer to fuel and ignition.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation2}
+	\caption{Schematic Indicating Thermcouple Arrays A1 and A2 for Fire Suppression Experiments}
+	\label{fig:fs_instruments}
+\end{figure}
+
+For the first comparison tests in the series, CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively.
+From the figures, the impact of the first suppression event (hallway nozzle on) is evident from the sharp decline in thermocouple temperatures.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
+	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
+	\label{fig:caf1_tca2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
+	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
+	\label{fig:water1_tca2}
+\end{figure}
+
+Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
+
+\clearpage
 

### 2016-07-12 Projects/DelCo_2012/Scripts/firesuppress_scatter_plot.py

@@ -32,7 +32,7 @@ info_file2 = '../Experimental_Data/Fire_Suppress_Test_Matrix.csv'
 info = pd.read_csv(info_file, index_col=3)
 info2 = pd.read_csv(info_file2, index_col=0)
 
-data_time_averaging_window = 10
+data_time_averaging_window = 1
 
 # Location of figures
 plot_dir = '../Figures/Gas_Cooling/'
@@ -41,138 +41,104 @@ plot_dir = '../Figures/Gas_Cooling/'
 # Skip files
 skip_files = ['_times','_reduced','description_','zero','bb','es_','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fire_suppress']
 
-del_TC_1_h2o = np.zeros((8,5))
-del_TC_1_cafs = np.zeros((8,5))
-del_TC_2_h2o = np.zeros((8,5))
-del_TC_2_cafs = np.zeros((8,5))
+del_TC_1_h2o_hall = np.zeros((8,6))
+del_TC_1_cafs_hall = np.zeros((8,6))
+del_TC_1_h2o_door= np.zeros((8,6))
+del_TC_1_cafs_door = np.zeros((8,6))
 
 #  ===============================
 #  = Loop through all data files =
 #  ===============================
 for f in os.listdir(data_dir):
-    if f.endswith('.csv'):
+	if f.endswith('.csv'):
 
-        # Skip files with time information or reduced data files
-        if any([substring in f.lower() for substring in skip_files]):
-            continue
+		# Skip files with time information or reduced data files
+		if any([substring in f.lower() for substring in skip_files]):
+			continue
 
-        # Strip test name from file name
-        test_name = f[:-4]
-        print ('Test ' + test_name)
+		# Strip test name from file name
+		test_name = f[:-4]
+		print ('Test ' + test_name)
 
-        # Load exp. scaling file
-        if 'FSW' in test_name:
-            if '13' in test_name[-2:]:
-                channel_list_file = scaling_file_west_2013
-            else:
-                channel_list_file = scaling_file_west
-        elif 'FSE' in test_name:
-            if '13' in test_name[-2:]:
-                channel_list_file = scaling_file_east_2013
-            else:
-                channel_list_file = scaling_file_east
+		# Load exp. scaling file
+		if 'FSW' in test_name:
+			if '13' in test_name[-2:]:
[…]

### 2016-07-12 Projects/DelCo_2012/Scripts/firesuppress_scatter_plot2.py

@@ -1,0 +1,195 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+#Weinschenk
+#3-15
+from __future__ import division
+import os
+import numpy as np
+import pandas as pd
+import itertools
+from pylab import *
+import statsmodels.api as sm
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+# Location of file with timing information
+all_times_file = '../Experimental_Data/All_Times.csv'
+
+data_dir = '../Experimental_Data/'
+save_dir = '../Figures/Script_Figures/'
+
+# Location of scaling conversion files
+scaling_file_west = '../Experimental_Data/West_DelCo_DAQ_Channel_List.csv'
+scaling_file_west_2013 = '../Experimental_Data/West_DelCo_DAQ_Channel_List_2013.csv'
+scaling_file_east = '../Experimental_Data/East_DelCo_DAQ_Channel_List.csv'
+scaling_file_east_2013 = '../Experimental_Data/East_DelCo_DAQ_Channel_List_2013.csv'
+
+# Location of test description file
+info_file = '../Experimental_Data/Description_of_Experiments.csv'
+info_file2 = '../Experimental_Data/Fire_Suppress_Test_Matrix.csv'
+
+info = pd.read_csv(info_file, index_col=3)
+info2 = pd.read_csv(info_file2, index_col=0)
+
+data_time_averaging_window = 1
+
+# Location of figures
+plot_dir = '../Figures/Gas_Cooling/'
+# List of sensor groups for each plot
+
+# Skip files
+skip_files = ['_times','_reduced','description_','zero','bb','es_','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fire_suppress']
+
+del_TC_2_h2o_hall = np.zeros((8,6))
+del_TC_2_cafs_hall = np.zeros((8,6))
+del_TC_2_h2o_door= np.zeros((8,6))
+del_TC_2_cafs_door = np.zeros((8,6))
+
+#  ===============================
+#  = Loop through all data files =
+#  ===============================
+for f in os.listdir(data_dir):
+    if f.endswith('.csv'):
+
+        # Skip files with time information or reduced data files
+        if any([substring in f.lower() for substring in skip_files]):
+            continue
+
+        # Strip test name from file name
+        test_name = f[:-4]
[…]

### 2016-07-12 Projects/DelCo_2012/Scripts/firesuppress_scatter_plot3.py

@@ -1,0 +1,196 @@
+# -*- coding: utf-8 -*-
+from __future__ import unicode_literals
+#Weinschenk
+#3-15
+from __future__ import division
+import os
+import numpy as np
+import pandas as pd
+import itertools
+from pylab import *
+import statsmodels.api as sm
+
+from matplotlib import rcParams
+rcParams.update({'figure.autolayout': True})
+
+# Location of file with timing information
+all_times_file = '../Experimental_Data/All_Times.csv'
+
+data_dir = '../Experimental_Data/'
+save_dir = '../Figures/Script_Figures/'
+
+# Location of scaling conversion files
+scaling_file_west = '../Experimental_Data/West_DelCo_DAQ_Channel_List.csv'
+scaling_file_west_2013 = '../Experimental_Data/West_DelCo_DAQ_Channel_List_2013.csv'
+scaling_file_east = '../Experimental_Data/East_DelCo_DAQ_Channel_List.csv'
+scaling_file_east_2013 = '../Experimental_Data/East_DelCo_DAQ_Channel_List_2013.csv'
+
+# Location of test description file
+info_file = '../Experimental_Data/Description_of_Experiments.csv'
+info_file2 = '../Experimental_Data/Fire_Suppress_Test_Matrix.csv'
+
+info = pd.read_csv(info_file, index_col=3)
+info2 = pd.read_csv(info_file2, index_col=0)
+
+data_time_averaging_window = 1
+
+# Location of figures
+plot_dir = '../Figures/Gas_Cooling/'
+# List of sensor groups for each plot
+
+# Skip files
+skip_files = ['_times','_reduced','description_','zero','bb','es_','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fire_suppress']
+
+del_TC_3_h2o_hall = np.zeros((7,6))
+del_TC_3_cafs_hall = np.zeros((7,6))
+del_TC_3_h2o_door = np.zeros((7,6))
+del_TC_3_cafs_door = np.zeros((7,6))
+
+#  ===============================
+#  = Loop through all data files =
+#  ===============================
+for f in os.listdir(data_dir):
+    if f.endswith('.csv'):
+
+        # Skip files with time information or reduced data files
+        if any([substring in f.lower() for substring in skip_files]):
+            continue
+
+        # Strip test name from file name
+        test_name = f[:-4]
+        print ('Test ' + test_name)
+
+        # Load exp. scaling file
+        if 'FSW' in test_name:
+            if '13' in test_name[-2:]:
[…]

### 2016-07-13 Projects/DelCo_2012/Report/DelCo_2012.tex
minor updates to report

@@
 Figure~\ref{fig:fs_instruments} shows the positions of thermocouple arrays TC A1 and TC A2.
-Note that TC A1 is closer to fuel and ignition.
+Note, TC A1 is closer to fuel and ignition.
 
@@
 
-For the first comparison tests in the series, CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively.
+For tests CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively.
 From the figures, the impact of the first suppression event (hallway nozzle on) is evident from the sharp decline in thermocouple temperatures.
+After the first suppression, there is an increase in temperature at position TC A2 as high temperature gases from a rekindle of the fire flow toward the low pressure structure exit.
+The second suppression (doorway nozzle) further dropped the temperature for both water and CAF.
+The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression}.
 

### 2016-07-13 Projects/DelCo_2012/Report/DelCo_2012.tex
change font on fire suppression timing, start appendix cafs

@@
 
+\begin{figure}[ht]
+\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
+\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
+\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top, middle) and in the Hallway (bottom) for Single-Story Fire Suppression Test CAF~1}
+\end{figure}
+
 \end{document}

### 2016-07-13 Projects/DelCo_2012/Scripts/plot.py

@@ -50,7 +50,7 @@ all_times = all_times.set_index('Time')
 info = pd.read_csv(info_file, index_col=3)
 
 # Files to skip
-skip_files = ['_times','_reduced','description_','zero','bb','es_','cafs','_attic','sc','gas_cooling_','west_','east_','gcs']
+skip_files = ['_times','_reduced','description_','zero','bb','es_','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fire_suppress']
 
 #  ===============================
 #  = Loop through all data files =
@@ -283,7 +283,7 @@ for f in os.listdir(data_dir):
                     [plt.axvline(_x - start_of_test, color='0.50', lw=1) for _x in events.index.values]
                     ax3.set_xticks(events.index.values - start_of_test)
                     plt.setp(plt.xticks()[1], rotation=60)
-                    ax3.set_xticklabels(events.values, fontsize=8, ha='left')
+                    ax3.set_xticklabels(events.values, fontsize=12, ha='left')
                     plt.xlim([0, end_of_test - start_of_test])
                     # Increase figure size for plot labels at top
                     fig.set_size_inches(10, 6)

### 2016-07-15 Projects/DelCo_2012/Report/DelCo_2012.tex
update many plotting scripts, run all scripts, add scripts, edit report CAFS

@@
 Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
-
-\clearpage
+Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was actived, respectively.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
+	\label{fig:fs_hall_a1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
+	\label{fig:fs_door_a1}
+\end{figure}
+
+In Fig.~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water.
+The R$^2$ value of 0.901 shows a strong fit to the data.
+When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticabley lower compared to the hallway nozzle, despite it being an indirect attack.
+While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
+Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (cf.
+Fig~\ref{fig:fs_door_a1}).
+At array A2, Fig.~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
+	\label{fig:fs_hall_a2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
+	\label{fig:fs_door_a2}
+\end{figure}
 
@@
 \includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
-\caption{Thermocouple Data for Arrays in the Fire Room (top, middle) and in the Hallway (bottom) for Single-Story Fire Suppression Test CAF~1}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~1}
 \end{figure}

### 2016-07-15 Projects/DelCo_2012/Scripts/firesuppress_scatter_plot.py

@@ -126,7 +126,7 @@ for f in os.listdir(data_dir):
 								continue
 							cafs_data_interval = current_channel_data[info2['Hallway_Start_Time_CAFS'][reps]:info2['Hallway_Stop_Time_CAFS'][reps]]
 							cafs_data_interval2 = current_channel_data[info2['Door_Start_Time_CAFS'][reps]:info2['Door_Stop_Time_CAFS'][reps]]
-							print(max(cafs_data_interval2),max(min(cafs_data_interval2),0))
+							# print(max(cafs_data_interval2),max(min(cafs_data_interval2),0))
 							del_TC_1_cafs_hall[ii,reps-1] =  max(max(cafs_data_interval),0) - max(min(cafs_data_interval),0.)
 							del_TC_1_cafs_door[ii,reps-1] =  max(max(cafs_data_interval2),0) - max(min(cafs_data_interval2),0.)
 							ii=ii+1

### 2016-07-15 Projects/DelCo_2012/Scripts/firesuppress_scatter_plot2.py

@@ -128,7 +128,7 @@ for f in os.listdir(data_dir):
 	        				cafs_data_interval2 = current_channel_data[info2['Door_Start_Time_CAFS'][reps]:info2['Door_Stop_Time_CAFS'][reps]]
         					del_TC_2_cafs_hall[ii,reps-1] =  max(max(cafs_data_interval),0) - max(min(cafs_data_interval),0.)
         					del_TC_2_cafs_door[ii,reps-1] =  max(max(cafs_data_interval2),0) - max(min(cafs_data_interval2),0.)
-        					print(max(cafs_data_interval2))
+        					# print(max(cafs_data_interval2))
         					ii=ii+1
 
 del_water = del_TC_2_h2o_hall

### 2016-07-15 Projects/DelCo_2012/Scripts/gas_cooling_plot.py

@@ -33,7 +33,7 @@ heatflux_cal = 5.5371
 info = pd.read_csv(info_file, index_col=0)
 zero = pd.read_csv(zero_file, header=0,index_col=0)
 # Skip files
-skip_files = ['_reduced', 'description_','zero','bb','es_','fse','cafs','fsw','_attic','sc','gas_cooling','west_','east_','all_']
+skip_files = ['_reduced', 'description_','zero','bb','es_','fse','cafs','fsw','_attic','sc','gas_cooling','west_','east_','all_','fire_suppress']
 
 #  ===============================
 #  = Loop through all data files =

### 2016-07-15 Projects/DelCo_2012/Scripts/water_plot.py

@@ -15,7 +15,7 @@ rcParams.update({'figure.autolayout': True})
 data_dir = '../Experimental_Data/'
 
 # Skip files
-skip_files = ['_times','_reduced','description_','zero','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fse_','fsw']
+skip_files = ['_times','_reduced','description_','zero','cafs','_attic','sc','gas_cooling_','west_','east_','gcs','fse_','fsw','fire_suppress']
 
 for f in os.listdir(data_dir):
 	if f.endswith('.csv'):

### 2016-07-15 Projects/DelCo_2014_2015/Scripts/bokeh_plot.py

@@ -19,7 +19,7 @@ def mtext(p, x, y, textstr):
 
 # Choose Test Number
 
-current_test = 'Test_41_West_061415'
+current_test = 'Test_40_West_061415'
 
 # Location of experimental data files
 data_dir = '../Experimental_Data/'

### 2016-07-15 Projects/DelCo_2012/Report/DelCo_2012.tex
update channel groupings, axis for plots, CAFS report

@@
 The fire suppression series included 20 experiments in the single-story experimental structures and one two-story structure.
-Tweleve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent.
+Twelve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent.
 The nozzle patterns were varied and included; straight stream, solid stream, and narrow fog.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend.pdf}
+	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend}
 	\caption{Instrumentation Legend.}
@@
 In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two story structure.
-Two different fuel packages were utitlized, the difference between the furniture fuel package used for experiments 13 and 14, and the furnitiure and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.
+Two different fuel packages were utilized, the difference between the furniture fuel package used for experiments 13 and 14, and the furniture and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.
 
@@
 The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}.
-In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polyprolene (PP).
+In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
 
@@
 The results are arranged in the order that the experiments were conducted.
-For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilitized.
+For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilized.
 
@@
 
-Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water colection pans across the floor surface area of the burn rooms within each structure (cf.
+Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water collection pans across the floor surface area of the burn rooms within each structure (cf.
 Fig~\ref{fig:water_buckets}).
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time Series of Multiple Gas Cooling Eexperiments from 1 of 9 Burn sequences}
+	\caption{Time Series of Multiple Gas Cooling Experiments from 1 of 9 Burn sequences}
 	\label{fig:gas_cooling_exp4}
@@
 Gas Cooling Array 1 was exhibits some amount of suppression agent impact.
-Gas Cooling Array 3 is located behind the area where the stream impacts the celing for both the middle and back nozzle positions.
+Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.
 As a result it remains dry and it seems to provide the best representation of the gas cooling.
@@
 These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
-Remeber that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow.
-As a result you can see the amount of temperature change during the period in between nozzle flows by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.
+Remember that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow.
+The amount of temperature change during the period in between nozzle flows is shown by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.
 
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation2}
-	\caption{Schematic Indicating Thermcouple Arrays A1 and A2 for Fire Suppression Experiments}
+	\caption{Schematic Indicating Thermocouple Arrays A1 and A2 for Fire Suppression Experiments}
 	\label{fig:fs_instruments}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
-	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
 	\label{fig:caf1_tca2}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
-	\caption{Time Series of Thermcouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
 	\label{fig:water1_tca2}
@@
 Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
-Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was actived, respectively.
+Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was activated, respectively.
 
@@
 The R$^2$ value of 0.901 shows a strong fit to the data.
-When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticabley lower compared to the hallway nozzle, despite it being an indirect attack.
+When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack.
 While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
@@
 The research team worked to address those follow-up questions by conducting additional fire suppression experiments.
-One experiemntal used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+One experimental used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
 A final experimental series, used a larger fire room, with more ventilation.
@@
 
-Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no suprised that the water is doing the work.
+Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
 Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
@@
 
-\subsection{Iowa State Univeristy Fire Flow Formula (1963)}
+\subsection{Iowa State University Fire Flow Formula (1963)}
 The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
@@
 
-The flowrate used for these experiments were sufficent to quickly cool the hot gas layer and suppress each of the fires.
+The flowrate used for these experiments were sufficient to quickly cool the hot gas layer and suppress each of the fires.
 
@@
 
-\clearpage
-
 \chapter{Fire Suppression Data}
@@
 \begin{figure}[ht]
-\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
-\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
-\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A3}
 \caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~1}
@@
 
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~1}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~1}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~1}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~1}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~1}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_3_092812_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_4_092912_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~2}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_6_093012_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_5_093912_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~3}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_8_093912_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_7_093012_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~4}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_12_051613_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_11_051613_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~5}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test CAF~6}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test CAF~6}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSW_Test_14_052013_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test CAF~6}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A2}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_TC_A3}
+\caption{Thermocouple Data for Arrays in the Fire Room (top - A1, middle - A2) and in the Hallway (bottom - A3) for Single-Story Fire Suppression Test Water~6}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_Heat_Flux_1}
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_Heat_Flux_3}
+\caption{Heat Flux and Radiometer Data in the Fire Room (top - 1/2) and in the Hallway (bottom - 3/4) for Single-Story Fire Suppression Test Water~6}
+\end{figure}
+
+\begin{figure}[ht]
+\includegraphics[width=.725\columnwidth]{../Figures/Script_Figures/FSE_Test_13_052013_BDP_A3}
+\caption{Hallway Velocity Data from Bi-Directional Probes for Single-Story Fire Suppression Test Water~6}
+\end{figure}
+
 \end{document}

### 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
add files, scripts, report edits for CAFS

@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
-	\caption{Dimensioned Floor Plan of the Test Structure.}
+	\caption{Dimensioned Floor Plan of the Test Structure}
 	\label{fig:Test_Structure_Floor_Plan}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
-	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure.}
+	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure}
 	\label{fig:dimensioned_first_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
-	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure.}
+	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure}
 	\label{fig:dimensioned_second_2story}
@@
 Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples.
-Additional single thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
+Additional single, sheathed thermocouples were installed in conjunction with the bi-directional probes for gas velocity measurements.
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple wire was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+The thermocouple was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+The sheathing protects the thermocouple from water but slows the response time because of the additional thermal mass.
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
@@
 	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Instrumentation_Legend}
-	\caption{Instrumentation Legend.}
+	\caption{Instrumentation Legend}
 	\label{fig:Instrumentation_Legend}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation}
-	\caption{Instrumentation Schematic for the Gas Cooling Experiments.}
+	\caption{Instrumentation Schematic for the Gas Cooling Experiments}
 	\label{fig:Gas_Cooling_Instrumentation_Dimensions}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
-	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments.}
+	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments}
 	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
-	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure.}
+	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure}
 	\label{fig:fire_supp_first_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
-	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure.}
+	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure}
 	\label{fig:fire_supp_second_2story}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Pallets}
-	\caption{Burn Building Fuel Load.}
+	\caption{Burn Building Fuel Load}
 	\label{fig:Burn_Building_Fuel_Load}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
-	\caption{Furniture Fuel Load Dimensions in Single Story Structure.}
+	\caption{Furniture Fuel Load Dimensions in Single Story Structure}
 	\label{fig:Furniture_Fuel_Load_Dimensions}
@@
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
-	\caption{Photograph of Southeast corner of burn room with wood fuel load.}
+	\caption{Photograph of Southeast corner of burn room with wood fuel load}
 	\label{fig:Wood_Fuel_Load}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
-	\caption{Wood Fuel Load in Single Story Structure.}
+	\caption{Wood Fuel Load in Single Story Structure}
 	\label{fig:Wood_Fuel_Load_Dimensions}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
-	\caption{Furniture Fuel Load in First Floor of Two-Story Structure.}
+	\caption{Furniture Fuel Load in First Floor of Two-Story Structure}
 	\label{fig:furniture_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
-	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure.}
+	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure}
 	\label{fig:pallet_furniture_2story}
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Pictures/Water Tests Bins.png}
-	\caption{Interlocking collecting bins used to capture suppression agent during spray density tests.}
+	\caption{Interlocking collecting bins used to capture suppression agent during spray density tests}
 	\label{fig:water_buckets}
@@
 	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Back_BB}
-	\caption{Stream positions mid(left) and back (right) during spray density tests.}
+	\caption{Stream positions mid(left) and back (right) during spray density tests}
 	\label{fig:stream_position}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
-	\caption{Schematic of  the Gas Cooling Experiments.}
+	\caption{Schematic of  the Gas Cooling Experiments}
 	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
 	\label{fig:fs_hall_a2}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
 	\label{fig:fs_door_a2}
@@
 There were 7 suppression tests conducted in the two story purpose-built structure.
-All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to this fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor south door.
+All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
+Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor door on the south side of the structure.
 The fires were intended to replicate room and contents basement fires typically seen within residential structures.
@@
  18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 20  & CAF~9b    &  Solid Stream        &  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 20  & CAF~9b    &  Solid Stream        &  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
 \bottomrule[1.25pt]
@@
 
-Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water and CAF tests conducted in the two story structure.
-The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floor.
-This remote measurement location provides that is isolated from any direct contact from the suppression stream.
-The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 1st floor level in front of the stairway door.
+Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two story structure.
+The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors.
+The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
+The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door.
+Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux guages.
+Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
+Note that these thermocouples are inconel shielded thermocouples and have slower reponse times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
 The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
@@
 \midrule
-CAF~7      & 24            & 580~$^{\circ}$C - 260~$^{\circ}$C   & 490~$^{\circ}$C - 195~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-Water~7    & 29            & 515~$^{\circ}$C - 260~$^{\circ}$C   & 455~$^{\circ}$C - 215~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a     & 16            & 475~$^{\circ}$C - 285~$^{\circ}$C   & 425~$^{\circ}$C - 250~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b     & 21            & 450~$^{\circ}$C - 240~$^{\circ}$C   & 390~$^{\circ}$C - 190~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
-Water~8    & 18            & 440~$^{\circ}$C - 295~$^{\circ}$C   & 375~$^{\circ}$C - 250~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
-Class A~1  & 19            & 440~$^{\circ}$C - 305~$^{\circ}$C   & 260~$^{\circ}$C - 235~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a     & 21            & 470~$^{\circ}$C - 270~$^{\circ}$C   & 420~$^{\circ}$C - 235~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b     & 16            & 510~$^{\circ}$C - 340~$^{\circ}$C   & 415~$^{\circ}$C - 295~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
+CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
+CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
+Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
+Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
+CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
+CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
 \bottomrule[1.25pt]
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=.9\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation2}
+	\caption{Schematic of Second Floor of Two Story Structure Indicating Thermocouple and Heat Flux Gauges}
+	\label{fig:tcs_hf_second_2story}
+\end{figure}
+
+The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10} - \ref{fig:caf9a_hf}.
+Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7 while Fig.~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
+The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression2}.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
+	\label{fig:water7_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
+	\label{fig:water7_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
+	\label{fig:caf9a_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
+	\label{fig:caf9a_hf}
+\end{figure}
+
+The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
+Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
+In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparalbe configurations.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TC_A10_scatter}
+	\caption{CAF vs Water Temperature Difference Comparison for Two Story Fire Suppression Test at Thermocouple Array A10}
+	\label{fig:fs_a10}
+\end{figure}
+
+In Fig.~\ref{fig:fs_a10}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) falls within the experimental uncertainty based around the equal cooling line (solid black line).
+This indicates an inability to distinguish whether CAF or water had a more significant impact in temperature reduction following suppression of the fire.
+The R$^2$ value of 0.975 shows a strong fit to the data between water and CAF.
 Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial.
@@
 
-\subsection{National Fire Academy (1884)}
+\subsection{National Fire Academy (1918)}
 The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right).}
+\caption{Spray density figures for burn building tests 1) Water Straight Stream Back (upper left), 2) Water Straight Stream Back (upper right), 3) Water Straight Stream Mid (lower left), and 4) Water Straight Stream Mid (lower right)}
 \label{fig:bb_1_4}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right).}
+\caption{Spray density figures for burn building tests 5) Water Straight Stream Mid (upper left), 6) Water Fog Mid (upper right), 7) Water Fog Mid (lower left), and 8) Water Fog Back (lower right)}
 \label{fig:bb_5_8}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right).}
+\caption{Spray density figures for burn building tests 9) Water Fog Back (upper left), 10) Water Solid Stream Back (upper right), 11) Water Solid Stream Back (lower left), and 12) CAF Solid Stream Back (lower right)}
 \label{fig:bb_9_12}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 13) CAF Solid Stream Mid (upper left), 14) CAF Solid Stream Back (upper right), 15) CAF Solid Stream Mid (lower left), and 16) CAF Fog Mid (lower right).}
+\caption{Spray density figures for burn building tests 13) CAF Solid Stream Mid (upper left), 14) CAF Solid Stream Back (upper right), 15) CAF Solid Stream Mid (lower left), and 16) CAF Fog Mid (lower right)}
 \label{fig:bb_13_16}
@@
 \end{tabular*}
-\caption{Spray density figures for burn building tests 17) CAF Straight Stream Mid (upper left), 18) CAF Straight Stream Mid (upper right), 19) CAF Fog Back (lower left), and 20) CAF Fog Back (lower right).}
+\caption{Spray density figures for burn building tests 17) CAF Straight Stream Mid (upper left), 18) CAF Straight Stream Mid (upper right), 19) CAF Fog Back (lower left), and 20) CAF Fog Back (lower right)}
 \label{fig:bb_19_21}
@@
 \includegraphics[width=3.2in]{../Figures/Bars/BB21}
-\caption{Spray density figures for burn building test 21) CAF Straight Stream Back.}
+\caption{Spray density figures for burn building test 21) CAF Straight Stream Back}
 \label{fig:bb_21}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 1) Water Straight Stream FR (upper left), 2) Water Straight Stream FR (upper right), 3) Water Straight Stream FR (lower left), and 4) Water Straight Stream FR (lower right).}
+\caption{Spray density figures for experimental structure tests 1) Water Straight Stream FR (upper left), 2) Water Straight Stream FR (upper right), 3) Water Straight Stream FR (lower left), and 4) Water Straight Stream FR (lower right)}
 \label{fig:es_1_4}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 5) Water Fog FR (upper left), 6) Water Fog FR (upper right), 7) Water Solid Stream FR (lower left), and 8) Water Solid Stream H (lower right).}
+\caption{Spray density figures for experimental structure tests 5) Water Fog FR (upper left), 6) Water Fog FR (upper right), 7) Water Solid Stream FR (lower left), and 8) Water Solid Stream H (lower right)}
 \label{fig:es_5_72}
@@
 \end{tabular*}
-\caption{Spray density figures for experimental structure tests 9) Water Fog H (upper left), 10) Water Fog H (upper right), 11) Water Straight Stream H (lower left), and 12) Water Straight Stream H (lower right).}
+\caption{Spray density figures for experimental structure tests 9) Water Fog H (upper left), 10) Water Fog H (upper right), 11) Water Straight Stream H (lower left), and 12) Water Straight Stream H (lower right)}
 \label{fig:es_8_11}
@@
 
-\chapter{Fire Suppression Data}
+\chapter{Single Story Fire Suppression Data}
 \label{app:fire_suppression}
+\newpage
 
@@
 
+\chapter{Two Story Fire Suppression Data}
+\label{app:fire_suppression2}
+
 \end{document}

### 2016-07-18 Projects/DelCo_2012/Scripts/firesuppress_2story_scatter.py

@@ -87,7 +87,7 @@ for f in os.listdir(data_dir):
 						if any([substring in channel for substring in info['Excluded Channels'][test_name].split('|')]):
 							continue
 						current_channel_data = data[channel]
-						if 'TC_A9' in channel:
+						if 'TC_A10' in channel:
 							water_data_interval = current_channel_data[info2['Water_On'][reps]:info2['Water_Off'][reps]]
 							del_TC_h2o[ii,reps-1] =  max(water_data_interval) - max(min(water_data_interval),0)
 							ii=ii+1
@@ -99,7 +99,7 @@ for f in os.listdir(data_dir):
 						if any([substring in channel for substring in info['Excluded Channels'][test_name].split('|')]):
 							continue
 						current_channel_data = data[channel]
-						if 'TC_A8' in channel:
+						if 'TC_A10' in channel:
 							cafs_data_interval = current_channel_data[info2['CAF_On'][reps]:info2['CAF_Off'][reps]]
 							del_TC_caf[ii,reps-1] =  max(max(cafs_data_interval),0) - max(min(cafs_data_interval),0.)
 							ii=ii+1
@@ -135,4 +135,4 @@ plt.text(0.1*max_axis , 0.95*max_axis, 'R$^2$ = ' + str(around(est.rsquared,deci
 	verticalalignment='center', bbox=dict(facecolor='none', edgecolor='black'))
 xlabel('$\Delta$T ($^{\circ}$C) CAFS')
 ylabel('$\Delta$T ($^{\circ}$C) WATER')
-savefig(save_dir + 'TC_A9_scatter.pdf',format='pdf')
+savefig(save_dir + 'TC_A10_scatter.pdf',format='pdf')

### 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
A few edits to discussion section

@@
 Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
-Note that these thermocouples are inconel shielded thermocouples and have slower reponse times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
+Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
 The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
@@
 \centering
-\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
+\caption{Two Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
 \begin{tabular}{lcccc}
@@
 Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
-In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparalbe configurations.
+In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
 
@@
 The research team worked to address those follow-up questions by conducting additional fire suppression experiments.
-One experimental used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+One set of experiments used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
 A final experimental series, used a larger fire room, with more ventilation.
-In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
+In this final series, another change was made, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
 This section will discuss the results and provide potential explanations to support them.
@@
 
-One of the most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires.
 Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires.
-Some of these agents are said to be more effective than plain water while being environmentally safe.
+These agents are said to be more effective than plain water while being environmentally safe.
 In some cases, they are also claimed to reduce the quantity and toxicity of smoke.
-To gain an understanding of how additives might enhance the fire suppression capabilities of water, it is important to examine the principles of fire suppression.
+
+So the question is, does CAF provide improved gas cooling when compared to plan water?
 
@@
 
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~7 Fire Suppression Test}
+	\label{fig:caf7_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~7 Fire Suppression Test}
+	\label{fig:caf7_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
+	\label{fig:water7_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
+	\label{fig:water7_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8a Fire Suppression Test}
+	\label{fig:caf8a_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8a Fire Suppression Test}
+	\label{fig:caf8a_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8b Fire Suppression Test}
+	\label{fig:caf8b_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8b Fire Suppression Test}
+	\label{fig:caf8b_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8 Fire Suppression Test}
+	\label{fig:caf8_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8 Fire Suppression Test}
+	\label{fig:caf8_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Class~A~1 Fire Suppression Test}
+	\label{fig:classa1_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Class~A~1 Fire Suppression Test}
+	\label{fig:classa1_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
+	\label{fig:caf9a_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
+	\label{fig:caf9a_hf}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9b Fire Suppression Test}
+	\label{fig:caf9b_tca10}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_Heat_Flux}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9b Fire Suppression Test}
+	\label{fig:caf9b_hf}
+\end{figure}
+
 \end{document}

### 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
add figures for 2 story suppression appendix, CAF

@@
 Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
-Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
+Note that these thermocouples are inconel shielded thermocouples and have slower reponse times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
 The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
@@
 \centering
-\caption{Two Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
+\caption{Two Story Fire Suppression Results, Stairwell Dooorway Temperatures}\label{tab:Test_Results_2}
 \begin{tabular}{lcccc}
@@
 Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
-In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
+In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparalbe configurations.
 
@@
 The research team worked to address those follow-up questions by conducting additional fire suppression experiments.
-One set of experiments used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+One experimental used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
 A final experimental series, used a larger fire room, with more ventilation.
-In this final series, another change was made, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
+In addition, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
 This section will discuss the results and provide potential explanations to support them.
@@
 
+One of the most widely used of the water-based agents are the foams used on Class B (liquid hydrocarbon) fires.
 Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires.
-These agents are said to be more effective than plain water while being environmentally safe.
+Some of these agents are said to be more effective than plain water while being environmentally safe.
 In some cases, they are also claimed to reduce the quantity and toxicity of smoke.
-
-So the question is, does CAF provide improved gas cooling when compared to plan water?
+To gain an understanding of how additives might enhance the fire suppression capabilities of water, it is important to examine the principles of fire suppression.
 

### 2016-07-20 Projects/DelCo_2012/Report/DelCo_2012.tex
More work on GC discussion

--- 2016-07-18 Projects/DelCo_2012/Report/DelCo_2012.tex
@@
 
-Agents designed primarily for Class A (ordinary combustible) fires have been used most extensively in conjunction with wildland or wildland urban interface fires.
-These agents are said to be more effective than plain water while being environmentally safe.
-In some cases, they are also claimed to reduce the quantity and toxicity of smoke.
-
-So the question is, does CAF provide improved gas cooling when compared to plan water?
-
-The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer with a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling.
-During the planning of the experiments, some workshop attendees thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS, since the injected air, air being a great insulator, would interfere and result in less cooling.
-It was the belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
-Other firefighters thought that the bubble structure would provide the same mass flowrate of water with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
+While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectivenss of CAF for interior structural firefighting varies widely.
+For example, does CAF provide improved gas cooling when compared to plan water?
+During the planning of the experiments, some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS.
+Their position was based on the thought that CAF has injected air.
+Since air is a great insulator, it slow heat transfer and result in less cooling.
+It was their belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
+Other member of the technical panel thought that the bubble structure would provide the same mass flowrate of water but with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
 There were also thoughts that the CAFS would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
+
+The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer, without any application of agent to the source of the heat.
+The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer,at least 1.83~m (6 ft) to form.
+During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling was attained prior to the beginning of another gas cooling experiment.
 
@@
 The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).
-The average time of flow was 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
-
-When a CAF stream was used it contained 0.3\% foam concentration by volume, the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal), for a 15~s flow time, 3.6~kg (8.0 lb) of concentrate was used.
-In addition to the foam concentrate mixed with the water in the CAF stream is compressed air.
+The average time of flow was approximately 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
+
+When a CAF stream was used it contained 0.3\% foam concentration by volume, the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal), for a 15~s flow time, 0.34~kg (0.75~lb) of concentrate was used.
+In addition to the foam concentrate and water, the CAF stream has compressed air.
 The volume of air injected into the foam solution is 0.03~m$^3$/s (60~cfm).
@@
 
-Under the given conditions of a residential scale room and the mass of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
-Air filled bubbles in the CAFS stream had no discernible impact in these experiments.
+The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$ 15~\%.
+In other words, for a difference between one measurement and another measurement to be considered significantly different, the difference would have to be greater by more than $\pm$ 15~\%.
+If the difference between two measurements was $\pm$ 15~\% or less, the results are considered to be similar.
+
+As pointed out in the results section, the conditions at TC array 3 represented the "best" gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
+
+Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
+Air filled bubbles in the CAFS stream had no discernible impact, either positive or negative, in the gas cooling experiments.
 At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.

### 2016-07-21 Projects/DelCo_2012/Report/DelCo_2012.tex
fix quote error

@@
 
-As pointed out in the results section, the conditions at TC array 3 represented the "best" gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
+As pointed out in the results section, the conditions at TC array 3 represented the ``'best'' gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
 

### 2016-07-21 Projects/DelCo_2012/Report/DelCo_2012.tex
Completed discussion of gas cooling
working on discussion of fire suppression

--- 2016-07-20 Projects/DelCo_2012/Report/DelCo_2012.tex
@@
 If the difference between two measurements was $\pm$ 15~\% or less, the results are considered to be similar.
-
-As pointed out in the results section, the conditions at TC array 3 represented the "best" gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
-
+That said, the estimated uncertainty is based on previous studies where suppression with a water based agent was included.
+
+As pointed out in the results section, the conditions at TC Array 3 represented the ``'best'' gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
 Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
@@
 At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.
+
+The data from the thermocouples in TC Array 2, provide a sense of the impact of a combination of surface cooling and gas cooling.
+For example, when the nozzle was in the "middle position" the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC array 2 and the adjacent walls.
+In this location, the data tended to favor water.
+But again this did not represent gas cooling, this represented water or CAF hitting the thermocouples and cooling the surrounding gases.
+As a result the temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid}.
+
+TC Array 1 had the worse data fit or the widest spread of temperature change because sometimes, some of the thermcouples in the array were getting impacted by water or CAF while during other nozzle streams they were not.
+Examining the spray density figures in Appendix A.1, provides a range water collected in the bucket where TC Array 1 was located.
+In many cases such as CAF Straight Stream Mid, the foam solution collected was near zero.
+In other cases such as CAF Fog Mid, the amount of foam solution colected was more than 3~kgs.
+Similar variations occurred with water.
+As a result, TC Array 1 did not provide consistant results for gas cooling.
+
+The data from this test series does not support the premise of firefighters being injured during an interior firefighting operation with CAF, because it was thought to provide less cooling than a similar hose stream of plain water.
 
@@
 The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).
-
-\subsection{National Fire Academy (1918)}
+While the formula has been widely taught over the years, there is some uncertainty about the application of the formula.
+In some texts it mentions that the Iowa Formula provides the amount of water that needs to be applied in 30 seconds.
+If that is the case then the flowrates given "per minute" must be doubled.
+So in our case the required flowrates would increase to 174~Lpm (46~gpm)
+and 336~Lpm (88 gpm), respectively.
+During the experiments the flowrate was approximately, 454~Lpm (120~gpm), which exceeds the required flowrate of the Iowa Formula.
+So the fact that all of the fires were quickly controlled is consistant with this methodology.
+
+\subsection{National Fire Academy (1981)}
 The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
@@
 The required flowrate for the fire room in the lower level of the two story would be approximately 700~Lpm (184~gpm).
+Comparing our hosestream flowrates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single story but was below the reuired flowrate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two story structure.
+This is not consistant with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~Lpm (120~gpm).
+
+Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a re-newed interest in controlling the air available to a ventilation limited compartment fire.
+By limiting the air (oxygen) available for combustion is one means of limting the heat release rate.
+If the heat release rate of a fire is reduced due to a lack of oxygen needed for combustion, then in theory the amount of water needed to cool and suppress the fire should also be reduced.
+
+Both of the formulas listed above do not overtly account for the ventilation of the fire structure only the size of the fire structure.
+Further the most recent formula was developed in 1981, based on the fire ground experience of fire chiefs.
+The experience that was shared was likely from fire that occurred in the 1960's and the 1970's.
+It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and hotter (higher heat release rate) than the natural fuels that filled the homes in the 1940's and 1950's.
+The change of materials in our homes began in the 1960's and continues through to present day.
+However it was unlikely that this change was factored in to the NFA Formula.
+
+All of the fire conditions generated during these experiments were ventilation limited or ventilation controlled fires.
+In other words if more oxygen was supplied to the fuel gases available in the fire compartment and more products of combustion were exhausted from the fire compartment, the heat release rate of the fire would have increased.
+There are simple formulas which may provide some insight here, although for full disclosure these simple algorithms have not been validated with the geometry that we used in these experiments.
+
+If we have a single open doorway to a residential scale room, which is approximately 0.9~m (3 ft) wide and 2.1~m (6.9 ft) high, the minimum heat release rate needed to flashover the room would be about 2 MW and the amount of heat release rate that the doorway could support assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection would be approximately 4 MW.
+If we double the width of the open doorway (the doorway to the lower level of the two story structure)  Then the heat release rate that could be generated inside the compartment, this does not account for flames burning outside of the compartment, would be approximately 8 MW.
 

### 2016-07-22 Projects/DelCo_2012/Report/DelCo_2012.tex
Complete draft of text

@@
 
+Shortly after the NFA equation was issued, another Federal agency, The National Bureau of Standards (now NIST) released a finding about the relationship of oxygen to the heat release rate of a fire.
+They found that for many fuels, approximately 13.1~MJ of heat were generated for every kilogram of oxygen comsumed during the combustion.
+This relationship then led to simple algorithms that addressed the relationship of the ventilation available o the room, in other words how much oxygen can flow through an opening, with the theoretical heat release rate which assumes stoichiometric conditions or 100~\% effecient burning where all of the fuel and the oxygen is consumed.
+
 All of the fire conditions generated during these experiments were ventilation limited or ventilation controlled fires.
-In other words if more oxygen was supplied to the fuel gases available in the fire compartment and more products of combustion were exhausted from the fire compartment, the heat release rate of the fire would have increased.
-There are simple formulas which may provide some insight here, although for full disclosure these simple algorithms have not been validated with the geometry that we used in these experiments.
-
-If we have a single open doorway to a residential scale room, which is approximately 0.9~m (3 ft) wide and 2.1~m (6.9 ft) high, the minimum heat release rate needed to flashover the room would be about 2 MW and the amount of heat release rate that the doorway could support assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection would be approximately 4 MW.
-If we double the width of the open doorway (the doorway to the lower level of the two story structure)  Then the heat release rate that could be generated inside the compartment, this does not account for flames burning outside of the compartment, would be approximately 8 MW.
-
-The flowrate used for these experiments were sufficient to quickly cool the hot gas layer and suppress each of the fires.
-
-static nozzle lines all performed the same.
-
-movement, sweeping nozzle, etc -- more efficient cooling / more effective that the type of nozzle or the amount of suppressive agent.
-air entrainment - ref hose stream study.
+In other words the conditions in the compart were fuel rich.
+If the ventilation was increased to allow more oxygen to be supplied to the fuel gases available in the fire compartment and more products of combustion were exhausted from the fire compartment, the heat release rate of the fire would have increased.
+There are simple formulas which may provide some insight here, although for full disclosure this simple algorithm has not been validated with the geometry that we used in these experiments.
+The purpose here is to get a sense of the amount of heat that the hose streams need to overcome.
+This algorithm, just like the NFA formula has never been validated for this application.
+
+\begin{equation} \label{eq:HRRSto_item}
+\dot{Q}_{stoichiometric} = 1500 Area \sqrt{Height} \\
+\end{equation}
+
+In this equation, the maximum heat release rate, in~kW, based on airflow through the area of the opening, in~m^2, represented by Area.
+The other input needed is the height of the opening in~m, shown as Height.
+
+If we have a single open doorway to a residential scale room, which is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high, the amount of heat release rate that the doorway could support assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection would be approximately 4 MW.
+If we double the width of the open doorway (the doorway to the lower level of the two story structure)  Then the heat release rate that could be generated inside the compartment would be approximately 8 MW, this does not account for flames burning outside of the compartment.
+With the single vent opening to the outside, the relationship should hold.
+In the single story, we had an additional window opening in some of the experiments which added ventilation to the room.
+In the two story we had an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
+Even with the additional ventilation in both cases, the conditions in the fire compartment remained fuel rich as the flames extended out of the openings from the structures.
+So it would seem that inside the compartment we would not have exceeded the 4~MW for the one story or the 8~MW for the two story stucture.
+Eariler we had noted that the latent heat of vaporization of water is 2255~kJ/kg or approximately 2.3~MJ/kg.
+Assuming ideal heat transfer the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two story.
+In our experiments our mass flow rate of water was 7.57~kg/s (16.7~lb/s), which ideally is twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two story structure.
+Again this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
+However, it demonstrates that for a residential scale room, in this study upto to 51.4~$m^2$ (553~$ft^2$) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water should be adequate quickly suppress the fire in the compartment.
+
+In all of the suppression experiments, the fire was controlled with total flow of 227~L (60~gal) or less of agent.
+During the course of the suppression experiments the fuel packages were modified to incorporate more wood based fuels.
+The thinking of some of the technical panel members was that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
+The wood based fuels, develop a char layer and therefore the burning would be "deep seated", which might provide a more significant suppression challenge.
+Since the Class A foam solution has a reduced surface tension, which could allow the solution to penetrate and cool the burning wood based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demnostrate a difference.
+As shown in Chapter 2, the wood fuel load constisted of stacks of wood pallets, plywood lined walls, and an exposed wood "ceiling" that was constructed of wood "i-beams" and oriented strand board.
+The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
+
+The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single story structure.
+Again the thought was to create a bigger fire challenge.
+As discussed previously, with the larger area and the double the ventilation, the fire should be more of a challenge to the hose streams.
+There was also another variable that would be introduced, a firefighter controlling the nozzle.
+In the suppression experiments conducted in the single story, the nozzles were in a fixed position.
+As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
+This can be seen for both the water and CAF experiments in the data provided in Appendix B.
+In some single story experiments, the fire was given time to redevelop and additional nozzle flows from the fixed positions were conducted to collect more data and to see if we could extinguish the fires.
+Would the CAF build and flow to burning areas that were not previously impacted by the hose streams.
+During the additional flows, no significant differences were seen.
+In all of the single story experiments firefighters with a hoseline were needed to extinguish the remaining fire and hot spots.
+So for the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an intelligent manner to make the best use of the hose stream and suppress the fire in the lower level of the two story.
+
+The same firefighter was used for all of the experiments conducted in the two story.
+The firefighter was from the MCFRS and had been trained in  in the use of CAF and had experience using CAF.
+The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending up to the upper level of the test structure.
+Then the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
+The nozzle was shut down when there were no flames visible from the doorway.
+
+The flow times are all less than 30 seconds.
+So even though the fire size had increased, a total flow of 227~L (60~gal) or less of agent was used to quickly cool the hot gas layer and suppress each of the fires.
+This is consistent with the ventilation analysis above.
+The nozzle movement clearly had a positive impact on suppressing the fire in the 11~m (36~ft) deep fire compartment.
+
+During the workshop there were discussions that CAF could suppress a fire perhaps as much as five times faster than water.
+During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural firefighting on a residential scale.
+Going back to the premise of the study preventing firefighters from being injured during an interior firefighting operation with CAF, there is nothing in the fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
+
+\Chapter{Future Research}
+
+One of the challenges with suppression research or determining the required flowrate of water needed on a building fire is the lack of data on realistic baseline requirements of the amount of water needed for gas cooling and suppression.
+In this study it seems clear that there was a sufficient amount of water for gas cooling and suppression.
+So one question would be, how much could the flow rate of water have been reduced before a significant difference in performance was observed?
+
+Information from actual incidents in the field, shaped this study.
+From the gas cooling and suppression perspective, the data does not indicate that the use of CAF would result in a higher thermal hazard.
+However, there are other issues like nozzle reaction force and flow separation which have been covered in the Cal Poly fire ground studies~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+These are issues that can be addressed in training.
+It is important to provide adequate training when adopting a new method or new technology.
+Perhaps these types of issues should be examined further to better understand how suppression activities take place in the field.
+What is the relationship between the training and the actual fire suppression activties that occur?
+
+Additional research is needed to examine the impact of nozzle type and nozzle movement on the fire environment.
+It is possible that some of the discomfort or injuries that firefighters experience during interior firefighting could be the result of a poor choice of nozzle or nozzle movement that results in displacing hotter gases into the area where the firefighter is located.
+Currently the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
+A study may be able to demonstrate a clear casue and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how that can impact the flow of gases within the structure.
+Based on the results of this study, it would seem that training and understanding the impact of nozzle movement are ways to look for more effective use of water.
 
@@
 
-Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting in residential stuctures.
 The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.
@@
 The experimental arrangements were designed to be representative of residential fire scenarios.
-
-Gas Cooling
-
-Fire Suppression
+The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
+This same department also experienced injuries to firefighters while using CAF during interior firefighting operations, in residential stuctures.
+This study is composed of three types of experiments; spray density, gas cooling and fire suppression.
+In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates of water.
+The flowrate for each experiment was 120~gpm of water.
+For the CAF, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate was added to the water flow.
+
+Thirty-two spray density tests were conducted to determine where the water would land within a compartment based on various nozzle patterns and locations.
+The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
+The purpose of these spray density tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+This report provides a complete set of the spray density results in graphic form.
+
+Eighty-eight gas cooling experiments were conducted to study the effectiveness of cooling the upper gas layer in a space adjacent to the area of fire involvement.
+These tests examined five different hose stream patterns, two nozzle types, and both compressed air foam and water as the suppression agent.
+The focus of this experimental series was to study the impact of the test variables on the hot gas layer temperatures when a fixed hose stream was applied to a room adjacent to the fire room.
+Suppression agents were not applied to the fire in the burn room.
+In this report an aggragate analysis is made to examine difference due to the loaction of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
+No significant differences were found in the gas cooling capabilities of the two agents.
+A more detailed analysis of the individual experiments was conducted by Mitchell of Cal Poly~\cite{Mitchell:1}.
+The conclusion of both analysises are in agreement.
+The full gas cooling data set can be found in the Mitchell report.
+
+There were two different geometries used for the fire suppression experiments.
+Twelve of the suppression experiments were conducted in a single story structure with an entry hallway that led to a fire compartment with a floor area of 27~$m^2$ (291~$ft^2$).
+Within this structure, two different types of fuel loads were used.
+In one case, most of the fuel consisted of synthetic materials in the upholstered furniture, carpet, and padding.
+The other fuel load used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+In the experiments conducted in the one story building, a fixed nozzle was flowed from the hallway for approximaetly 15~s and then another fixed nozzle located in the fire comparment was flowed for an additional 15 seconds.
+
+Seven of the suppression experiments were conducted in a two story structure.
+The fire compartment was the full lower level of the stucture and it had an open floor plan with an area of 51.4~$m^2$ (553~$ft^2$).
+At one end of the room was an open doorway, 1.8~m (6~ft) wide by
+2~m (6.7~ft) high.
+A manual hose stream application was made from outside the doorway on the lower level.
+In these experiments there was a combiantion of wood based and synthetic fuels.
+The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
+In each case the initial knockdown of the fire required 60~gal of agent or less.
 
@@
 These experiments could not have been conducted without them.
-
-The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
 

### 2016-07-23 Projects/DelCo_2012/Report/DelCo_2012.tex
initial edits to discussion section CAFS

@@
 In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam.
-These results were not surprising to some of the technical panel members.
-However other members, that use CAF very successfully in their fire departments every day, had additional questions.
-The research team worked to address those follow-up questions by conducting additional fire suppression experiments.
+To expand upon the 2012 and 2013 tests described in~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
 One set of experiments used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
@@
 In this final series, another change was made, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
-This section will discuss the results and provide potential explanations to support them.
+This section will discuss the overall results of the study and provide potential explanations to support them.
 
@@
 
-While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectivenss of CAF for interior structural firefighting varies widely.
-For example, does CAF provide improved gas cooling when compared to plan water?
-During the planning of the experiments, some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAFS.
+While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness of CAF for interior structural firefighting varies widely.
+Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
+During the planning of the experiments, there were a range of hypothesis regarding the outcome.
+Some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF.
 Their position was based on the thought that CAF has injected air.
-Since air is a great insulator, it slow heat transfer and result in less cooling.
+Since air is a great insulator, it slows heat transfer and results in less cooling.
 It was their belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
-Other member of the technical panel thought that the bubble structure would provide the same mass flowrate of water but with more surface area, which would enable a faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
+Other members of the technical panel thought that the bubble structure would provide the same mass flowrate of water but with more surface area.
+The increased surface area would enable faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
 There were also thoughts that the CAFS would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
@@
 The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer, without any application of agent to the source of the heat.
-The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer,at least 1.83~m (6 ft) to form.
+The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer, at least 1.83~m (6 ft) to form.
 During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling was attained prior to the beginning of another gas cooling experiment.
-
 In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
@@
 
-When a CAF stream was used it contained 0.3\% foam concentration by volume, the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal), for a 15~s flow time, 0.34~kg (0.75~lb) of concentrate was used.
+When a CAF stream was used it contained 0.3~\% foam concentration by volume with the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal).
+For a 15~s flow time, 0.34~kg (0.75~lb) of concentrate was used.
 In addition to the foam concentrate and water, the CAF stream has compressed air.
 The volume of air injected into the foam solution is 0.03~m$^3$/s (60~cfm).
-The density of the compressed air in the range of 100 to 150~psig, would be between 8.9~kg/m$^3$ (0.6 lb/ft$^3$) and 12.8~kg/m$^3$ (0.8 lb/ft$^3$).
-So a 15~s CAF flow would contain approximately 4.0~kg (8.8 lb) to 9.5~kg (21.0 lb) of air.
+The density of the compressed air is in the range of 100 to 150~psig, which would be between 8.9~kg/m$^3$ (0.6~lb/ft$^3$) and 12.8~kg/m$^3$ (0.8~lb/ft$^3$).
+Therefore, a 15~s CAF flow would contain approximately 4.0~kg (8.8~lb) to 9.5~kg (21.0~lb) of air.
 Comparing the mass flows, and using the air mass based on the higher pressure, water still makes up more than 90~\% of the mass of the CAF stream.
 
-The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$ 15~\%.
+The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$ 15~\% (see Section~\ref{subsec:Uncertainty}).
 In other words, for a difference between one measurement and another measurement to be considered significantly different, the difference would have to be greater by more than $\pm$ 15~\%.
@@
 
-As pointed out in the results section, the conditions at TC Array 3 represented the ``'best'' gas cooling results with the least impact of agents hitting and cooling the thermocouples themselves.
+As pointed out in the results section, the conditions at TC Array 3 represented the ``'best'' gas cooling results because that position had the least impact of agents hitting and cooling the thermocouples themselves.
 Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
-Air filled bubbles in the CAFS stream had no discernible impact, either positive or negative, in the gas cooling experiments.
+Air filled bubbles in the CAF stream had no discernible impact, either positive or negative, in the gas cooling experiments.
 At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.
@@
 The data from the thermocouples in TC Array 2, provide a sense of the impact of a combination of surface cooling and gas cooling.
-For example, when the nozzle was in the "middle position" the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC array 2 and the adjacent walls.
+For example, when the nozzle was in the ``middle position'' the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC Array 2 and the adjacent walls.
 In this location, the data tended to favor water.
-But again this did not represent gas cooling, this represented water or CAF hitting the thermocouples and cooling the surrounding gases.
-As a result the temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid}.
-
-TC Array 1 had the worse data fit or the widest spread of temperature change because sometimes, some of the thermcouples in the array were getting impacted by water or CAF while during other nozzle streams they were not.
-Examining the spray density figures in Appendix A.1, provides a range water collected in the bucket where TC Array 1 was located.
+But again this did not represent gas cooling, this represented some of the water or CAF hitting the thermocouples and cooling the surrounding gases.
+As a result, temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} respectively.
+
+TC Array 1 had the widest spread of temperature change.
+Depending on the nozzle configuration, there were tests where the Array 1 thermocouples were directly impacted by water or CAF and other tests where there was no impact.
+Examination of the spray density figures in Appendix~\ref{spray_bb}, provides the range of agent collected in the bucket where TC Array 1 was located.
 In many cases such as CAF Straight Stream Mid, the foam solution collected was near zero.
-In other cases such as CAF Fog Mid, the amount of foam solution colected was more than 3~kgs.
+In other cases such as CAF Fog Mid, the amount of foam solution collected was more than 3~kgs.
 Similar variations occurred with water.
-As a result, TC Array 1 did not provide consistant results for gas cooling.
+As a result, TC Array 1 did not provide consistent results for gas cooling.
 
@@
 The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
-The required fire flowrate in gpm is equal to the volume of the fire compartment (in cubic feet) divided by 100:
+The required fire flowrate, ($\dot{V}$), in gpm is equal to the volume ($V$) of the fire compartment (in cubic feet) divided by 100:
 \begin{equation}\label{eq:isu_form}
-required fire flowrate = Volume / 100
+\dot{V} = V / 100
 \end{equation}
 Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
-Applying the  based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
-Our fire rooms ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
+Applying the formula based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
+The fire rooms in these experiments ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
 Therefore the required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
-The required flowrate for the fire room in the lower level of the two story would be approximately 168~Lpm (44~gpm).
+The required flowrate for the fire room in the lower level of the two story structure would be approximately 168~Lpm (44~gpm).
 While the formula has been widely taught over the years, there is some uncertainty about the application of the formula.
-In some texts it mentions that the Iowa Formula provides the amount of water that needs to be applied in 30 seconds.
-If that is the case then the flowrates given "per minute" must be doubled.
-So in our case the required flowrates would increase to 174~Lpm (46~gpm)
-and 336~Lpm (88 gpm), respectively.
-During the experiments the flowrate was approximately, 454~Lpm (120~gpm), which exceeds the required flowrate of the Iowa Formula.
-So the fact that all of the fires were quickly controlled is consistant with this methodology.
+Some texts mention that the Iowa State Formula provides the amount of water that needs to be applied in 30 seconds.
+If that is the case, then the flowrates given ``per minute'' must be doubled.
+The required flowrates would increase to 174~Lpm (46~gpm) and 336~Lpm (88~gpm), respectively.
+During the experiments the flowrate was approximately, 454~Lpm (120~gpm), which exceeds the required flowrate of the Iowa State Formula.
+The fact that all of the fires were quickly controlled  during the experiments is consistent with this methodology.
 
@@
 The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
-This formula sets the required fire flow, in gpm, equal to the floor area (in square feet) divided by 3.
+This formula sets the required fire flow, ($\dot{V}$), in gpm equal to the floor area ($A$) (in square feet) divided by 3.
 \begin{equation}\label{eq:nfa_form}
-required fire flowrate = Area / 3
+\dot{V} = A / 3
 \end{equation}
@@
 The fire rooms in these experiments ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
-Applying the NFA formula based on floor area yields an required flowrate for the single story fire room of 369~Lpm (97~gpm).
+Applying the NFA formula based on floor area yields a required flowrate for the single story fire room of 369~Lpm (97~gpm).
 The required flowrate for the fire room in the lower level of the two story would be approximately 700~Lpm (184~gpm).
-Comparing our hosestream flowrates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single story but was below the reuired flowrate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two story structure.
-This is not consistant with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~Lpm (120~gpm).
+Comparing the hose stream flowrates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single story but was below the required flowrate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two story structure.
+This is not consistent with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~Lpm (120~gpm).
 
 Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a re-newed interest in controlling the air available to a ventilation limited compartment fire.
-By limiting the air (oxygen) available for combustion is one means of limting the heat release rate.
-If the heat release rate of a fire is reduced due to a lack of oxygen needed for combustion, then in theory the amount of water needed to cool and suppress the fire should also be reduced.
-
-Both of the formulas listed above do not overtly account for the ventilation of the fire structure only the size of the fire structure.
+Limiting the air (oxygen) available for combustion is one means of limiting the heat release rate.
+If the heat release rate of a fire is reduced due to a lack of oxygen needed for combustion, then in theory, the amount of water needed to cool and suppress the fire should also be reduced.
+
+Both of the formulas listed above do not overtly account for the ventilation of the fire structure, only the size of the fire structure.
 Further the most recent formula was developed in 1981, based on the fire ground experience of fire chiefs.
-The experience that was shared was likely from fire that occurred in the 1960's and the 1970's.
-It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and hotter (higher heat release rate) than the natural fuels that filled the homes in the 1940's and 1950's.
-The change of materials in our homes began in the 1960's and continues through to present day.
-However it was unlikely that this change was factored in to the NFA Formula.
+The experience that was shared was likely from fires that occurred in the 1960's and the 1970's.
+It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and with higher heat release rates than the natural fuels that filled the homes in the 1940's and 1950's.
+The change of materials in homes began in the 1960's and continues through to present day.
+However, it was unlikely that this change was factored in to the NFA Formula.
 
 Shortly after the NFA equation was issued, another Federal agency, The National Bureau of Standards (now NIST) released a finding about the relationship of oxygen to the heat release rate of a fire.
-They found that for many fuels, approximately 13.1~MJ of heat were generated for every kilogram of oxygen comsumed during the combustion.
-This relationship then led to simple algorithms that addressed the relationship of the ventilation available o the room, in other words how much oxygen can flow through an opening, with the theoretical heat release rate which assumes stoichiometric conditions or 100~\% effecient burning where all of the fuel and the oxygen is consumed.
+NIST found that for many fuels, approximately 13.1~MJ of heat are generated for every kilogram of oxygen consumed during the combustion.
+This relationship then led to simple algorithms that addressed the how much oxygen can flow through an opening with a theoretical heat release rate that assumes stoichiometric conditions (100~\% efficient burning where all of the fuel and the oxygen is consumed).
 
 All of the fire conditions generated during these experiments were ventilation limited or ventilation controlled fires.
-In other words the conditions in the compart were fuel rich.
+Essentially, the conditions in the compartment were fuel rich.
 If the ventilation was increased to allow more oxygen to be supplied to the fuel gases available in the fire compartment and more products of combustion were exhausted from the fire compartment, the heat release rate of the fire would have increased.
@@
 \begin{equation} \label{eq:HRRSto_item}
-\dot{Q}_{stoichiometric} = 1500 Area \sqrt{Height} \\
+\dot{Q}_{stoichiometric} = 1500 A_0 \sqrt{H_0} \\
 \end{equation}
 
-In this equation, the maximum heat release rate, in~kW, based on airflow through the area of the opening, in~m^2, represented by Area.
-The other input needed is the height of the opening in~m, shown as Height.
+In this equation, the maximum heat release rate, in~kW, based on airflow through the area of the opening, in m$^2$, represented by Area.
+The other input needed is the height of the opening in m, shown as Height.
 
@@
 The thinking of some of the technical panel members was that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-The wood based fuels, develop a char layer and therefore the burning would be "deep seated", which might provide a more significant suppression challenge.
+The wood based fuels, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
 Since the Class A foam solution has a reduced surface tension, which could allow the solution to penetrate and cool the burning wood based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demnostrate a difference.
-As shown in Chapter 2, the wood fuel load constisted of stacks of wood pallets, plywood lined walls, and an exposed wood "ceiling" that was constructed of wood "i-beams" and oriented strand board.
+As shown in Chapter 2, the wood fuel load constisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board.
 The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
@@
 
-\Chapter{Future Research}
+\section{Future Research}
 
@@
 \section{Spray density figures for burn building tests}
+\label{app:spray_bb}
 
@@
 \section{Spray density figures for experimental structure tests}
+\label{app:spray_es}
 

### 2016-07-23 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
editting
Fixed refs for primer and paint.  other edits

@@
 After receipt of the gypsum wallboard panels, the panels were laid out on the floor of the NIST Large Fire Research Laboratory, finished paper side up and painted with a roller.
-The first coat was a latex primer, http://buyat.ppg.com/rep\_pafpainttools\_files/Pghpaints/tdb/78200.pdf.
-Once the primer dried a top coat of white latex paint was applied http://buyat.ppg.com/rep\_pafpainttools\_files/Olympic/tdb/78010.pdf.
+The first coat was a latex primer~\cite{Latex_Primer}.
+Once the primer dried a top coat of white latex paint was applied ~\cite{Latex_Paint}.
 After the panels dried, they were weighed.
@@
 \chapter{Bench Scale Assessment of Thermal Damage to Gypsum Wallboard}
+
+The purpose of this chapter is to develop and compare data from bench scale apparatus that could be used to analyze fire damage to gypsum wallboard.
+This type of testing might be practical for a fire investigator to use based on the low cost, relative to a full-scale fire test, and the small size of the samples needed for the tests.
+In the previous sections of this study, burners were used to examine the repeatibility of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
+While the data generated from those experiments provide valuable insight, it would be of valauble to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
 
@@
 The front wall of the compartment was open along the full width of the compartment to minimize the impact of entrained air being channeled through a doorway.
-These experiments were conducted without instrumentation in the walls for several reasons; to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation, to provide more realistic conditions, and to enable the conduct of additional replicate experiments given the limited laboratory availability.
+These experiments were conducted without instrumentation in the walls for several reasons:
+\begin{enumerate}
+\item to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation
+\item to provide more realistic conditions
+\item to enable the conduct of additional replicate experiments
+\end{enumerate}
+
 A photograph of the compartment fire experimental arrangement is shown in Figure~\ref{Compartment_Test}.
@@
 Values generated in the bench scale experiments will be utilized as input to predict real scale results using the algorithms.
-Then the predicted results will be compared with the full-scale experiment results.
+Then the predicted results will be compared with the full-scale experimental results.
 

### 2016-07-24 Projects/DelCo_2012/Report/DelCo_2012.tex
finished edits to discussion and conclusions

@@
 Depending on the nozzle configuration, there were tests where the Array 1 thermocouples were directly impacted by water or CAF and other tests where there was no impact.
-Examination of the spray density figures in Appendix~\ref{spray_bb}, provides the range of agent collected in the bucket where TC Array 1 was located.
+Examination of the spray density figures in Appendix~\ref{app:spray_bb}, provides the range of agent collected in the bucket where TC Array 1 was located.
 In many cases such as CAF Straight Stream Mid, the foam solution collected was near zero.
@@
 Essentially, the conditions in the compartment were fuel rich.
-If the ventilation was increased to allow more oxygen to be supplied to the fuel gases available in the fire compartment and more products of combustion were exhausted from the fire compartment, the heat release rate of the fire would have increased.
-There are simple formulas which may provide some insight here, although for full disclosure this simple algorithm has not been validated with the geometry that we used in these experiments.
-The purpose here is to get a sense of the amount of heat that the hose streams need to overcome.
+If the ventilation was increased to allow additional oxygen to be supplied to the fuel gases in the fire compartment, the heat release rate of the fire would have increased.
+There are simple formulas which may provide some insight here, although for full disclosure this simple algorithm has not been validated with the geometry that were used in these experiments.
+The purpose here is to get a sense of the amount of heat energy that the hose streams needed to overcome.
 This algorithm, just like the NFA formula has never been validated for this application.
@@
 
-In this equation, the maximum heat release rate, in~kW, based on airflow through the area of the opening, in m$^2$, represented by Area.
-The other input needed is the height of the opening in m, shown as Height.
-
-If we have a single open doorway to a residential scale room, which is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high, the amount of heat release rate that the doorway could support assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection would be approximately 4 MW.
-If we double the width of the open doorway (the doorway to the lower level of the two story structure)  Then the heat release rate that could be generated inside the compartment would be approximately 8 MW, this does not account for flames burning outside of the compartment.
-With the single vent opening to the outside, the relationship should hold.
-In the single story, we had an additional window opening in some of the experiments which added ventilation to the room.
-In the two story we had an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
+In Eq.~\ref{eq:HRRSto_item}, the maximum heat release rate $\dot{Q}_{stoichiometric}$ in kW is based on airflow through the area of the opening, $A_0$ in m$^2$ and the height of the opening $\sqrt{H_0}$ in m.
+
+Following Eq.~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room, which is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high, could support a heat release rate of approximately 4~MW assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
+For double the width of the open doorway (the doorway to the lower level of the two story structure) the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
+This does not account for flames burning outside of the compartment, which were frequently observed during testing.
+
+In the single story, there was an additional window opening in some of the experiments which added ventilation to the room.
+In the two story, there was an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
 Even with the additional ventilation in both cases, the conditions in the fire compartment remained fuel rich as the flames extended out of the openings from the structures.
-So it would seem that inside the compartment we would not have exceeded the 4~MW for the one story or the 8~MW for the two story stucture.
-Eariler we had noted that the latent heat of vaporization of water is 2255~kJ/kg or approximately 2.3~MJ/kg.
-Assuming ideal heat transfer the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two story.
-In our experiments our mass flow rate of water was 7.57~kg/s (16.7~lb/s), which ideally is twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two story structure.
+It would seem then, that the heat release rate inside the compartment would not have exceeded 4~MW for the one story or 8~MW for the two story structure.
+
+Earlier it was noted that the latent heat of vaporization of water is 2255~kJ/kg or approximately 2.3~MJ/kg.
+Assuming ideal heat transfer, the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two story.
+In these experiments, the mass flow rate of water was 7.57~kg/s (16.7~lb/s), which is theoretically twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two story structure.
 Again this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
-However, it demonstrates that for a residential scale room, in this study upto to 51.4~$m^2$ (553~$ft^2$) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water should be adequate quickly suppress the fire in the compartment.
+However, it demonstrates that for a residential scale room (in this study up to to 51.4~$m^2$ (553~$ft^2$)) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water was adequate to quickly suppress the fire in the compartment.
 
@@
 During the course of the suppression experiments the fuel packages were modified to incorporate more wood based fuels.
-The thinking of some of the technical panel members was that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-The wood based fuels, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
-Since the Class A foam solution has a reduced surface tension, which could allow the solution to penetrate and cool the burning wood based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demnostrate a difference.
-As shown in Chapter 2, the wood fuel load constisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board.
+During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
+Wood based fuels, however develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
+Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.
+As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board.
 The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
@@
 The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single story structure.
-Again the thought was to create a bigger fire challenge.
 As discussed previously, with the larger area and the double the ventilation, the fire should be more of a challenge to the hose streams.
 There was also another variable that would be introduced, a firefighter controlling the nozzle.
-In the suppression experiments conducted in the single story, the nozzles were in a fixed position.
+Recall, that in the single story experiments a monitor nozzle was used in a fixed position.
 As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
-This can be seen for both the water and CAF experiments in the data provided in Appendix B.
-In some single story experiments, the fire was given time to redevelop and additional nozzle flows from the fixed positions were conducted to collect more data and to see if we could extinguish the fires.
-Would the CAF build and flow to burning areas that were not previously impacted by the hose streams.
+This can be seen for both the water and CAF experiments in the data provided in Appendix~\ref{app:fire_suppression}.
+In some single story experiments, the fire was given time to redevelop and additional nozzle flows from the fixed positions were conducted to collect more data and to see if the fires could be extinguished.
 During the additional flows, no significant differences were seen.
-In all of the single story experiments firefighters with a hoseline were needed to extinguish the remaining fire and hot spots.
-So for the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an intelligent manner to make the best use of the hose stream and suppress the fire in the lower level of the two story.
-
-The same firefighter was used for all of the experiments conducted in the two story.
-The firefighter was from the MCFRS and had been trained in  in the use of CAF and had experience using CAF.
-The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending up to the upper level of the test structure.
+In all of the single story experiments firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
+For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner to make the best use of the hose stream to suppress the fire in the lower level of the two story structure.
+
+The firefighting crew was from the MCFRS and all had been trained in the use of CAF and had experience using CAF.
+The firefighter on the nozzle was the same for all of the experiments conducted in the two story structure.
+The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
 Then the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
 The nozzle was shut down when there were no flames visible from the doorway.
-
-The flow times are all less than 30 seconds.
-So even though the fire size had increased, a total flow of 227~L (60~gal) or less of agent was used to quickly cool the hot gas layer and suppress each of the fires.
+The flow times were all less than 30 seconds.
+Even though the fire size had increased, a total flow of 227~L (60~gal) or less of agent was used to cool the hot gas layer and suppress each of the fires.
 This is consistent with the ventilation analysis above.
@@
 
-During the workshop there were discussions that CAF could suppress a fire perhaps as much as five times faster than water.
+During the workshop (\cite{Grant:2011}), there were discussions that CAF could suppress a fire perhaps as much as five times faster than water.
 During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural firefighting on a residential scale.
@@
 
-One of the challenges with suppression research or determining the required flowrate of water needed on a building fire is the lack of data on realistic baseline requirements of the amount of water needed for gas cooling and suppression.
+One of the challenges with suppression research or determining the required flowrate of water needed on a building fire is the lack of data on realistic baseline requirements of the total amount of water needed for gas cooling and suppression.
 In this study it seems clear that there was a sufficient amount of water for gas cooling and suppression.
-So one question would be, how much could the flow rate of water have been reduced before a significant difference in performance was observed?
+One question that arises is, how much could the flow rate of water have been reduced before a significant difference in performance was observed?
 
@@
 Perhaps these types of issues should be examined further to better understand how suppression activities take place in the field.
-What is the relationship between the training and the actual fire suppression activties that occur?
 
@@
 Currently the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
-A study may be able to demonstrate a clear casue and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how that can impact the flow of gases within the structure.
+A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how that can impact the flow of gases within the structure.
 Based on the results of this study, it would seem that training and understanding the impact of nozzle movement are ways to look for more effective use of water.
@@
 
-Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting in residential stuctures.
-The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation.
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting in residential structures.
+The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation~\cite{Grant:2011}.
 The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water.
@@
 Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
-The experimental arrangements were designed to be representative of residential fire scenarios.
+The experimental configurations were designed to be representative of residential fire scenarios.
 The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
-This same department also experienced injuries to firefighters while using CAF during interior firefighting operations, in residential stuctures.
+This same department also experienced injuries to firefighters while using CAF during interior firefighting operations in residential structures.
 This study is composed of three types of experiments; spray density, gas cooling and fire suppression.
-In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates of water.
-The flowrate for each experiment was 120~gpm of water.
-For the CAF, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate was added to the water flow.
-
-Thirty-two spray density tests were conducted to determine where the water would land within a compartment based on various nozzle patterns and locations.
+In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates of water.
+The flowrate for each water experiment was 120~gpm.
+For the CAF experiments, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate was added to the water flow.
+
+Thirty-two spray density tests were conducted to determine where the agent would land within a compartment based on various nozzle patterns and locations.
 The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
@@
 Suppression agents were not applied to the fire in the burn room.
-In this report an aggragate analysis is made to examine difference due to the loaction of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
+In this report an aggregate analysis is made to examine difference due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
 No significant differences were found in the gas cooling capabilities of the two agents.
 A more detailed analysis of the individual experiments was conducted by Mitchell of Cal Poly~\cite{Mitchell:1}.
-The conclusion of both analysises are in agreement.
+The conclusion of both analyses are in agreement.
 The full gas cooling data set can be found in the Mitchell report.
@@
 In one case, most of the fuel consisted of synthetic materials in the upholstered furniture, carpet, and padding.
-The other fuel load used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
-In the experiments conducted in the one story building, a fixed nozzle was flowed from the hallway for approximaetly 15~s and then another fixed nozzle located in the fire comparment was flowed for an additional 15 seconds.
+The other fuel load used only wood based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+In the experiments conducted in the one story building, a fixed nozzle was flowed from the hallway for approximately 15~s and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
 
 Seven of the suppression experiments were conducted in a two story structure.
-The fire compartment was the full lower level of the stucture and it had an open floor plan with an area of 51.4~$m^2$ (553~$ft^2$).
+The fire compartment was the full lower level of the structure and it had an open floor plan with an area of 51.4~$m^2$ (553~$ft^2$).
 At one end of the room was an open doorway, 1.8~m (6~ft) wide by
-2~m (6.7~ft) high.
+2~m (6.7~ft) high the led to a stairwell.
 A manual hose stream application was made from outside the doorway on the lower level.
-In these experiments there was a combiantion of wood based and synthetic fuels.
+In these experiments there was a combination of wood based and synthetic fuels.
 The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
@@
 The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
-Under the test conditions both agents were effective.
+Under these test conditions both agents were effective.
 This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~7 Fire Suppression Test}
-	\label{fig:caf7_tca10}
+	\label{fig:app_caf7_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~7 Fire Suppression Test}
-	\label{fig:caf7_hf}
+	\label{fig:app_caf7_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
-	\label{fig:water7_tca10}
+	\label{fig:app_water7_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
-	\label{fig:water7_hf}
+	\label{fig:app_water7_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8a Fire Suppression Test}
-	\label{fig:caf8a_tca10}
+	\label{fig:app_caf8a_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8a Fire Suppression Test}
-	\label{fig:caf8a_hf}
+	\label{fig:app_caf8a_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8b Fire Suppression Test}
-	\label{fig:caf8b_tca10}
+	\label{fig:app_caf8b_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8b Fire Suppression Test}
-	\label{fig:caf8b_hf}
+	\label{fig:app_caf8b_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8 Fire Suppression Test}
-	\label{fig:caf8_tca10}
+	\label{fig:app_caf8_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8 Fire Suppression Test}
-	\label{fig:caf8_hf}
+	\label{fig:app_caf8_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Class~A~1 Fire Suppression Test}
-	\label{fig:classa1_tca10}
+	\label{fig:app_classa1_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Class~A~1 Fire Suppression Test}
-	\label{fig:classa1_hf}
+	\label{fig:app_classa1_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
-	\label{fig:caf9a_tca10}
+	\label{fig:app_caf9a_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
-	\label{fig:caf9a_hf}
+	\label{fig:app_caf9a_hf}
 \end{figure}
@@
 	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9b Fire Suppression Test}
-	\label{fig:caf9b_tca10}
+	\label{fig:app_caf9b_tca10}
 \end{figure}
@@
 	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9b Fire Suppression Test}
-	\label{fig:caf9b_hf}
+	\label{fig:app_caf9b_hf}
 \end{figure}

### 2016-07-29 Projects/DelCo_2012/Report/DelCo_2012.tex
Began editing CAFS report

@@
 The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
-Under the test conditions both agents were effective.
-This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.
+Under the test conditions, both agents were effective.
+This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle relative to plain water.
 
@@
 A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAFS for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of CAF for structural firefighting through the various tasks associated with this project, including:
+This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural firefighting through the various tasks associated with this project, including:
 
@@
 \item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural firefighting
-\item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+\item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces, and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 \end{enumerate}
@@
 The key measures were to understand the gas cooling and fire suppression capabilities of CAF compared to water.
-The experimental designs were developed based on a project planning workshop which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAF during interior attack operations in residential occupancies~\cite{Grant:2011}.
+The experimental designs were developed based on a project planning workshop, which included the discussion of incidents where firefighters had concerns or experienced minor burns while using CAF during interior attack operations in residential occupancies~\cite{Grant:2011}.
 Anecdotally, other fire departments or firefighters had similar incidents or impressions of CAF.
 
-Compressed air foam (CAF) generated with a solution of water and a Class A foam concentrate has been in use by wildland fire agencies since the late 1970's.
-The wildland fire community found that the Class A foam reduced the surface tension of water, which improved water's ability to penetrate and soak into wildland fuels.
+CAF generated with a solution of water and a Class A foam concentrate has been in use by wildland fire agencies since the late 1970's.
+The wildland fire community found that the Class A foam reduced the surface tension of water, which improved the water's ability to penetrate and soak into wildland fuels.
 A CAFS could turn a Class A foam solution into a blanket of bubbles that would allow the wildland firefighters to coat the fuels.
-The additional ``soak'' time provided by the foam layer allowed the water to penetrate the hot surface of a burning fuel, and also provided additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
-An added feature of the blanket of bubbles is that firefighters could see where they had applied the agent so that they could make a more effective application.
+The additional ``soak'' time provided by the foam layer allowed the water to penetrate the hot surface of a burning fuel and also provided additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
+An added feature of the blanket of bubbles is that firefighters can see where they had applied the agent so that they could make a more effective application.
 In the wildland, water for firefighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
-CAF increases the effectiveness of water, and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
-Last but not least the compressed air adds energy to the water stream providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
-These CAF advantages combine to provide wildland firefighters with a tool that could be used to pre-treat homes and structures to protect them from an approaching fire, or could be used for an exterior (indirect) fire suppression attack on a structure.
+CAF increases the effectiveness of water and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
+Finally, the compressed air adds energy to the water stream, providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
+These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire or can be used for an exterior (indirect) fire suppression attack on a structure.
 
 In the decades that followed the development of CAFS, a number of urban/suburban fire departments across the country began to integrate CAFS into their apparatus.
-For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires, but also examined using them for structural fire fighting.
-Other departments across the country began to experiment with CAFS systems for use in structural firefighting.
-In the few cases that were documented, the findings about the effectiveness of the CAFS were favorable, yet after decades of fire department trials, CAF has still not been widely incorporated into structural firefighting tactics~\cite{USFA:CAFS,Lorh:2002}.
+For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires and also examined using them for structural fire fighting.
+Other departments across the country began to experiment with CAFS for use in structural firefighting.
+In the few cases that were documented, the findings about the effectiveness of the CAFS were favorable.
+Yet, after decades of fire department trials, CAF has still not been widely incorporated into structural firefighting tactics~\cite{USFA:CAFS,Lorh:2002}.
 This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
@@
 There has never been a comprehensive scientific study on the use of CAF for structural fire fighting.
-Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF, foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures, and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF; foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures; and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
 
 Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}.
-That study examined a broad range of tests in order to determine those parameters that most critically effect fire-fighting performance.
+That study examined a broad range of tests in order to determine those parameters that most critically effect fire fighting performance.
 The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.
@@
 
-Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle, cooling and penetrating wood based fuels, mass retention on the wood fuels and ignition inhibition of the wood fuels.
+Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle; cooling and penetrating wood-based fuels; mass retention on the wood fuels; and ignition inhibition of the wood fuels.
 When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
@@
 These enhancements also make the agents valuable tools for mop-up.
-The other experiments conducted during this study: specific heat, drop size, wood crib suppression, smoke generation and Class D fire suppression yielded similar results for both Class A foams and plain water.
+The other experiments conducted during this study---specific heat, drop size, wood crib suppression, smoke generation, and Class D fire suppression---yielded similar results for both Class A foams and plain water.
 
@@
 In structural firefighting, crews typically have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
-In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they may have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
-It is important that these distinctions and differences between exterior and interior firefighting with CAF are understood better.
-
-Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in the State of Maryland and was a committed user of CAF with 35 CAFS front line engines.
-MCFRS had experienced two incidents where firefighters received burns in residential structure fires whiles CAF was being used to fight the fire during an interior attack.
+In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
+It is important that these distinctions and differences between exterior and interior firefighting with CAF are better understood.
+
+Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in Maryland and was a committed user of CAF with 35 CAFS front line engines.
+MCFRS had experienced two incidents where firefighters received burns in residential structure fires while CAF was being used to fight the fire during an interior attack.
 Concerns were raised within the department regarding the ability of CAF to cool fire gases and absorb heat as well as plain water.
-As a result, on March 4, 2010, the Fire Chief of (MCFRS) issued a General Order prohibiting the use of CAF during offensive interior attacks.
+As a result, on March 4, 2010, the Fire Chief of MCFRS issued a General Order prohibiting the use of CAF during offensive interior attacks.
 In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAF during structure fires and to report back his findings and recommendations.
@@
 The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
-The data from these experiments were presented to the technical panel member.
+The data from these experiments were presented to the technical panel members.
 The fire suppression experiments were conducted with a fuel package that included upholstered furniture.
-After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package that was composed mainly of wood based materials.
+After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package that was composed mainly of wood-based materials.
 The thinking was that the synthetic materials in the upholstered furniture burned only on the surface and were easily extinguished.
-Wood based fuels would char and present a deep seated fire challenge to the extinguishing agents.
-After the wood based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
+wood-based fuels would char and present a deep seated fire challenge to the extinguishing agents.
+After the wood-based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
 The issue of a larger fire compartment had also been raised during the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
-To accomplish the last series of experiments, additional funding was obtained from NIST and the experiments were conducted in 2015.
+To accomplish the last series of experiments, additional funding was obtained from NIST, and the experiments were conducted in 2015.
 The fuel load contained both wood-based wall and ceiling finishes, pallets as well as carpeting and upholstered furniture.
@@
 The sections below describe the types of experiments, the experimental facilities, instrumentation, and fuel loads.
-Project partner, Montgomery County (MD) Fire and Rescue Service (MCFRS) provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
+Project partner MCFRS provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
 These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
@@
 Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
-The nozzles chosen for these experiments were: Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
-These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog for application.
-The set-up also included 100~ft of 1-3/4~inch hose.
+The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
+These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog stream for application.
+The setup also included 100~ft of 1-3/4~inch hose.
 Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
@@
 When the flow of CAF was needed for the experiment, the gated wye would be switched to allow the CAF to flow into the test structure.
-This was done to minimize, the build-up of``dry'' foam or a slug upon the initial flow of the nozzle into the test structure.
+This was done to minimize the build-up of ``dry'' foam or a slug upon the initial flow of the nozzle into the test structure.
 
@@
 
-The fire suppression series included 20 experiments in the single-story experimental structures and one two-story structure.
-Twelve experiments were conducted in the single story structures (6 in each structure) using both water and CAF application as a suppression agent.
-The nozzle patterns were varied and included; straight stream, solid stream, and narrow fog.
-The two-story tests used both water and CAF from a straight-stream nozzle.
+The fire suppression series included 20 experiments in the single-story experimental structures and one in the two-story structure.
+Twelve experiments were conducted in the single-story structures (6 in each structure) using both water and CAF application as a suppression agent.
+The nozzle patterns were varied and included straight stream, solid stream, and narrow fog stream.
+The two-story test used both water and CAF from a straight stream nozzle.
 
@@
 
-The series of tests described within this report were conducted at the Delaware County Emergency Services Training Center, located in Sharon Hill, PA.
-A burn building as well as two purpose built concrete structures are located on the grounds of the ESTC.
-The burn building was used for the gas cooling experiments and the purpose built concrete structures were used for the fire suppression experiments.
+The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA.
+A burn building and two purpose-built concrete structures are located on the grounds of the ESTC.
+The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments.
 
@@
 
-The burn building is a live fire training structure with both a two story and three story section.
-The building is supported with reinforced concrete beams and columns.
-The floors and ceilings are also concrete with the interior walls constructed of cement block.
-The walls and ceiling of the burn rooms are protected with a 25~mm thick layer of calcium silicate insulation and is covered by a 50~mm thick concrete tile.
-The floor of the burn rooms is protected with fire brick.
-Tests were conducted in the two-story, two-room configuration which has overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (cf.
+The burn building, or live fire training structure, contained a two-story section and a three-story section.
+The building was supported with reinforced concrete beams and columns.
+The floors and ceilings were also concrete, and the interior walls were constructed of cement block.
+The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile.
+The floor of the burn rooms was protected with fire brick.
+Tests were conducted in the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (cf.
 Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
@@
 \label{sec:Experimental Structures}
-\subsubsection*{Single Story Structures}
+\subsubsection*{Single-Story Structures}
 
@@
 
-There are different components of uncertainty in the length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity and heat release rate reported here.
+There are different components of uncertainty in the length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate reported here.
 Uncertainties are grouped into two categories according to the method used to estimate them.
 Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
-Type B analysis of systematic uncertainties involves estimating the upper (+ a) and lower (- a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$ a) is essentially 100~\%.
+Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$ a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
+Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 Eight of the experiments used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
-The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
+The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood-based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
 Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was ``opened''to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
@@
 To expand upon the 2012 and 2013 tests described in~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
-One set of experiments used only wood based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+One set of experiments used only wood-based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
 A final experimental series, used a larger fire room, with more ventilation.
@@
 In all of the suppression experiments, the fire was controlled with total flow of 227~L (60~gal) or less of agent.
-During the course of the suppression experiments the fuel packages were modified to incorporate more wood based fuels.
+During the course of the suppression experiments the fuel packages were modified to incorporate more wood-based fuels.
 During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-Wood based fuels, however develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
-Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.
+wood-based fuels, however develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
+Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.
 As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board.
@@
 In one case, most of the fuel consisted of synthetic materials in the upholstered furniture, carpet, and padding.
-The other fuel load used only wood based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+The other fuel load used only wood-based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
 In the experiments conducted in the one story building, a fixed nozzle was flowed from the hallway for approximately 15~s and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
@@
 A manual hose stream application was made from outside the doorway on the lower level.
-In these experiments there was a combination of wood based and synthetic fuels.
+In these experiments there was a combination of wood-based and synthetic fuels.
 The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
@@
 
+\clearpage
+
 \begin{figure}[ht]
@@
 \end{figure}
+\newpage
 
@@
 \end{figure}
+\clearpage
 

### 2016-07-29 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -203,8 +203,6 @@ for f in os.listdir(data_dir):
             offset_time = events.index.values[0]
             new_times = events.index.values - int(offset_time)
             events = pd.Series(events.values, index=new_times)
-            # print events
-            # print
             data['Time'] = data['Time'].values - offset_time
             corrected_data = data.drop('Time', axis=1)
             corrected_data.insert(0, 'Time', data['Time'])

### 2016-07-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Added edits up to pg. 36 for CAFS report

@@
 \headerB{
-Examination of Compressed Air Foam (CAF) for Interior Firefighting \\
+Examination of Compressed Air Foam (CAF) for Interior Fire Fighting \\
 }
@@
 \headerB{
-Examination of Compressed Air Foam (CAF) for Interior Firefighting
+Examination of Compressed Air Foam (CAF) for Interior Fire Fighting
 }
@@
 
-Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting.
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural fire fighting.
 The key outcomes were to measure the gas cooling and fire suppression capabilities of CAF compared to water.
@@
 \vspace{0.5in}
-Key words: compressed air foam, fire experiments, firefighting, fire suppression, fuel load, gas cooling, structural firefighting, suppression research
+Key words: compressed air foam, fire experiments, fire fighting, fire suppression, fuel load, gas cooling, structural fire fighting, suppression research
 
@@
 
-The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and firefighting tactics.
+The Engineering Laboratory at the National Institute of Standards and Technology (NIST) has a research program aimed at improving the safety and effectiveness of firefighters through improved knowledge of fire behavior and fire fighting tactics.
 One of the objectives of this program is to examine non-traditional means of fire suppression.
-This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on firefighting tactics.
-These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural firefighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural firefighting.
+This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on fire fighting tactics.
+These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting.
 This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 
-A number of fire departments throughout the US have acquired CAFS units for structural firefighting, but many have limited or stopped the use of these CAFS for structural firefighting due to operational challenges or due to lack of understanding related to fireground safety issues.
-This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural firefighting through the various tasks associated with this project, including:
+A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting due to operational challenges or due to lack of understanding related to fireground safety issues.
+This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural fire fighting through the various tasks associated with this project, including:
 
 \begin{enumerate}
-\item  Perform a literature review of available published information on the use of CAF for structural firefighting~\cite{Mitchell:1}
+\item  Perform a literature review of available published information on the use of CAF for structural fire fighting~\cite{Mitchell:1}
 \item  Conduct a workshop that brings interested and experienced parties together to discuss CAF experience and to provide guidance on the proposed experimental research plan~\cite{Grant:2011} 
-\item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural firefighting
+\item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural fire fighting
 \item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces, and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
@@
 An added feature of the blanket of bubbles is that firefighters can see where they had applied the agent so that they could make a more effective application.
-In the wildland, water for firefighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
+In the wildland, water for fire fighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
 CAF increases the effectiveness of water and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
@@
 For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires and also examined using them for structural fire fighting.
-Other departments across the country began to experiment with CAFS for use in structural firefighting.
+Other departments across the country began to experiment with CAFS for use in structural fire fighting.
 In the few cases that were documented, the findings about the effectiveness of the CAFS were favorable.
-Yet, after decades of fire department trials, CAF has still not been widely incorporated into structural firefighting tactics~\cite{USFA:CAFS,Lorh:2002}.
+Yet, after decades of fire department trials, CAF has still not been widely incorporated into structural fire fighting tactics~\cite{USFA:CAFS,Lorh:2002}.
 This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
@@
 In 2005, The National Fallen Firefighters Foundation held the National Fire Service Research Agenda Symposium.
-One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland firefighting, CAFS is typically applied directly to the fuel from a remote location, typically a non-IDLH environment.
-In structural firefighting, crews typically have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
+One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland fire fighting, CAFS is typically applied directly to the fuel from a remote location, typically a non-IDLH environment.
+In structural fire fighting, crews typically have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
 In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
-It is important that these distinctions and differences between exterior and interior firefighting with CAF are better understood.
+It is important that these distinctions and differences between exterior and interior fire fighting with CAF are better understood.
 
@@
 All of the experiments were conducted at full scale in compartments and structures that were representative of room sizes in a residential occupancy.
-Technical panel members whose departments routinely use CAF for structural firefighting were invited and present at many of the fire suppression experiments.
+Technical panel members whose departments routinely use CAF for structural fire fighting were invited and present at many of the fire suppression experiments.
 The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
@@
 Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and twelve of the tests were conducted in the experimental structures to be used for the fire suppression tests.
-The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (cf.
-Fig.~\ref{fig:Spray_Density_Nozzle_Patterns}).
+The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (Figure~\ref{fig:Spray_Density_Nozzle_Patterns}).
 A description and drawings of these facilities are included in Section~\ref{sec:Experimental Structures}.
@@
 The floor of the burn rooms was protected with fire brick.
-Tests were conducted in the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (cf.
-Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
+Tests were conducted in the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
 
@@
 
-Two identical single story concrete structures were built on a concrete slab as shown in Fig.~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}.
+Two identical single-story concrete structures were built on a concrete slab as shown in Figure~\ref{fig:Delaware_County,_PA_Fire_Test_Structures}.
 They were designed to simulate a single floor of a residential structure.
@@
 The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide.
-A dimensioned, plan view of the structure is included in Fig.~\ref{fig:Test_Structure_Floor_Plan}.
+A dimensioned, plan view of the structure is included in Figure~\ref{fig:Test_Structure_Floor_Plan}.
 
@@
 
-\subsubsection*{Two Story Structure}
-
-The west structure was modified to add second story to test larger fires and remote suppression effects (cf. Fig~\ref{fig:delco_2story}).
+\subsubsection*{Two-Story Structure}
+
+The west structure was modified to add second story to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
 
@@
 
-The outer walls of the bottom floor of the two-story structure were identical to that of the single story structures described above but with an open floor plan.
+The outer walls of the bottom floor of the two-story structure were identical to that of the single-story structures described above but with an open floor plan.
 The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
-	\caption{Dimensioned Floor Plan of First Floor of Two Story Structure}
+	\caption{Dimensioned Floor Plan of First Floor of Two-Story Structure}
 	\label{fig:dimensioned_first_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
-	\caption{Dimensioned Floor Plan of Second Floor of Two Story Structure}
+	\caption{Dimensioned Floor Plan of Second Floor of Two-Story Structure}
 	\label{fig:dimensioned_second_2story}
@@
 A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
-A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Fig.~\ref{fig:Instrumentation_Legend}.
+A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Figure~\ref{fig:Instrumentation_Legend}.
 
@@
 The gas cooling tests included 4 bare-bead thermocouple arrays  a bi-directional probe plus solid thermocouple array, and a total heat flux gauge/radiometer pair.
-Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (cf.
-Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
 Each of the bare-bead thermocouple array had 11 thermocouples.
@@
 The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft), and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
-The total heat flux guage/radiometer were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The total heat flux gauge/radiometer were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
 
@@
 
-\subsubsection*{Single Story Structure}
-
-The fire suppression testing in the single story included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux guage/radiometer pairs.
-Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (cf.
-Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+\subsubsection*{Single-Story Structure}
+
+The fire suppression testing in the single-story structure included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux gauge/radiometer pairs.
+Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
 Each bare-bead thermocouple array had 8 thermocouples.
@@
 The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit.
-The total heat flux guage/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-The pairs of total heat flux guages were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.
+The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation}
-	\caption{Instrumentation Schematic for the Single Story Fire Suppression Experiments}
+	\caption{Instrumentation Schematic for the Single-Story Fire Suppression Experiments}
 	\label{fig:Fire_Suppression_Instrumentation_Dimensions}
@@
 
-\subsubsection*{Two Story Structure}
+\subsubsection*{Two-Story Structure}
 
@@
 Three bare-bead thermocouple arrays and 2 bi-directional probe plus solid thermocouples arrays were used in the first floor.
-Fig.~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (cf.
-Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Figure~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
 Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests.
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Instrumentation}
-	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two Story Structure}
+	\caption{Instrumentation Schematic for the First Floor of Fire Suppression Experiments in Two-Story Structure}
 	\label{fig:fire_supp_first_2story}
@@
 The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground.
-Fig.~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (cf.
-Fig.~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Figure~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
 The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level.
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation}
-	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two Story Structure}
+	\caption{Instrumentation Schematic for the Second Floor of Fire Suppression Experiments in Two-Story Structure}
 	\label{fig:fire_supp_second_2story}
@@
 Each length measurement was taken carefully.
-Length measurements such as the room dimensions, instrumentation array locations and fire apparatus (for example nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$ 6.0~mm (0.25~in) over a range of 0.61~m (2.00~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
+Length measurements, such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement, were made with a hand held laser measurement device that had an accuracy of $\pm$ 6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
 However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$ 0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
-Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within an instrumentation array and to measure and position the furniture.
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$ 1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
@@
 The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments an estimated uncertainty of $\pm$ 12~\% is being applied to the results~\cite{Lock:1}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$ 12~\% was applied to the results~\cite{Lock:1}.
 
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$ 1~\%~\cite{Setra:2002}.
-The total expanded uncertainty was estimated at 10~\%.
-
-Bi-directional probes and single thermocouples were used to measure the velocity.
+The transducers were factory calibrated and the zero and span of each were checked in the laboratory prior to the experiments, yielding an accuracy of $\pm$ 1~\%~\cite{Setra:2002}.
+The total expanded uncertainty is estimated at 10~\%.
+
+Bi-directional probes and single thermocouples were used to measure gas velocity.
 The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-Bare-bead Type K thermocouple are co-located with the probe.
+A bare-bead Type K thermocouple was co-located with each probe.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$ 18~\%.
-
-Water flowrate was measured with a pressure and flow meter combination.
-The meter consists of a section of 6.35~cm (2.5~inch) cast aluminum pipe with a 0 - 4.1~MPa (0 - 600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
+The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm$ 18~\%.
+
+Water flow rate was measured with a pressure and flow meter combination.
+The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\%  for the pressure sensor~\cite{Akron:2009}.
+The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}.
 The pressure transducer was calibrated with a known analog pressure gauge.
-The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flowrate.
-The total expanded uncertainty was estimated at $\pm$ 10~\%.
+The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate.
+The total expanded uncertainty is estimated at $\pm$ 10~\%.
 
@@
 Wood pallets were used as the fuel source for the gas cooling experiments.
-The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick.
-The pallets ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs).
-The initial fuel load consisted of 10 pallets, arranged in two stacks of five as shown in Fig.~\ref{fig:Burn_Building_Fuel_Load}.
+The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick and ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs).
+The initial fuel load consisted of 10 pallets, arranged in two stacks of five, as shown in Figure~\ref{fig:Burn_Building_Fuel_Load}.
 Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition.
-Fig.~\ref{fig:Burn_Building_Fuel_Load}, also provides dimensioned locations of the two stacks of pallets within the burn room.
+Figure~\ref{fig:Burn_Building_Fuel_Load} also provides dimensioned locations of the two stacks of pallets within the burn room.
 
@@
 
-Note, that as the pallets burned away and the hot gas layer temperatures decreased, the steel shutters on the window to the burn room were opened and additional pallets were added.
+Note that as the pallets burned away and the hot gas layer temperatures decreased, the steel shutters on the window to the burn room were opened and additional pallets were added.
 Pallets were added to the existing fuel locations until the flames from the piles reached the ceiling of the burn room again.
-The shutters on the window would be then closed and the temperature of the hot gas layer in the adjacent room would be monitored in preparation for starting another gas cooling experiment.
+Then, the shutters on the window were closed, and the temperature of the hot gas layer in the adjacent room was monitored in preparation for starting another gas cooling experiment.
 The number of pallets added each time varied.
@@
 
-\subsubsection*{Single Story Structure}
+\subsubsection*{Single-Story Structure}
 \label{sec:suppresion_single}
@@
 
-The fuel load for experiments 1 through 8 consisted of 2 sleeper sofas and 2 chairs, carpet, padding, and wood paneling along the southeast corner walls.
-An image of the fuel arrangement is shown in Fig.~\ref{fig:Furniture_Fuel_Load}.
-The couches and chairs are setup to mimic a typical seating area with one couch against the south and east wall respectively with each being 0.9~m (36~in) away from the corner.
-A chair is placed adjacent to each couch and the specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:Furniture_Fuel_Load_Dimensions}.
-In total, this fuel package contains approximately 336 kg (739 lbs) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
+The fuel load for test numbers 1 through 8 consisted of two sleeper sofas, two cushioned chairs, carpet, padding, and wood paneling along the southeast corner walls.
+An image of the fuel arrangement is shown in Figure~\ref{fig:Furniture_Fuel_Load}.
+The couches and chairs were set up to mimic a typical seating area with one couch against the south wall and one couch against the east wall, each positioned 0.9~m (36~in) away from the southeast corner.
+A chair was placed adjacent to each couch.
+The specific locations can be found in the dimensioned schematic, Figure~\ref{fig:Furniture_Fuel_Load_Dimensions}.
+In total, this fuel package contains approximately 336~kg (739~lbs) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
 Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Pictures/Furniture_Fuel_Load}
-	\caption{Furniture Fuel Load in Single Story Structure}
+	\caption{Furniture Fuel Load in Single-Story Structure}
 	\label{fig:Furniture_Fuel_Load}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
-	\caption{Furniture Fuel Load Dimensions in Single Story Structure}
+	\caption{Furniture Fuel Load Dimensions in Single-Story Structure}
 	\label{fig:Furniture_Fuel_Load_Dimensions}
@@
 
-The fuel load for experiments 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets plywood on the walls and the wood ``floor assembly".
+The fuel load for test numbers 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets of plywood on the walls, and the wood ``floor assembly''.
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
-Each stack was composed of six pallets with a half bale of hay.
-The hay was layered between each pallet.
+Each stack was composed of six pallets with a half bale of hay layered between the six pallets.
 Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition.
-The pallets and hay were weighed prior to each experiment.
-For the four pallet experiments, the average mass of the two stacks of pallets and the bale of hay was 232.4~kg (511.3~lb).
+The pallets and hay were weighed prior to each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).
+
 \begin{figure}[!ht]
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
-	\caption{Photograph of Southeast corner of burn room with wood fuel load}
+	\caption{Photograph of Southeast Corner of Burn Room with Wood Fuel Load}
 	\label{fig:Wood_Fuel_Load}
@@
 
-The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room (cf.
-Fig.~\ref{fig:Wood_Fuel_Load_Dimensions}).
-The pallets were 1.2~m (48~in) long, 1.0~m (40~in) and 123~mm (4.8~in) high.
+The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room (see Figure~\ref{fig:Wood_Fuel_Load_Dimensions}).
+The pallets were 1.2~m (48~in) long, 1.0~m (40~in) wide, and 123~mm (4.8~in) high.
 The stacks were spaced 150~mm (6~in) apart.
 One layer of 13~mm (0.5~in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
-The east and south wall of the burn room was covered with 15~mm (0.59~in) thick, sheets of plywood.
-The ``wood flooring assembly", composed of 12 TGIs and 9 sheets of OSB, served as the ceiling of the burn room.
+The east and south walls of the burn room were covered with 15~mm (0.59~in) thick sheets of plywood.
+The wood ``flooring assembly'', composed of 12 TJIs and nine sheets of oriented strand board (OSB), served as the ceiling of the burn room.
 The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
-	\caption{Wood Fuel Load in Single Story Structure}
+	\caption{Wood Fuel Load in Single-Story Structure}
 	\label{fig:Wood_Fuel_Load_Dimensions}
@@
 
-\subsubsection*{Two Story Structure}
+\subsubsection*{Two-Story Structure}
 \label{sec:suppresion_two}
 
-In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two story structure.
+In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two-story structure.
 Two different fuel packages were utilized, the difference between the furniture fuel package used for experiments 13 and 14, and the furniture and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.
@@
 
-The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of oriented strand board (OSB) paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the East, West, and South walls and ceiling.
-The three couches are aligned along the West wall and spaced 1.2~m (4~ft) apart.
-The specific locations can be found in the dimensioned schematic, Fig.~\ref{fig:furniture_2story}.
-In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
+The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
+The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart.
+The specific locations can be found in the dimensioned schematic Figure~\ref{fig:furniture_2story}.
+In total, this fuel package was composed of wood, flexible polyurethane (PU), polyester (PE), and polypropylene (PP).
 
@@
 
-In June 2015 two stacks of pallets were added to the fuel load which consisted of three sofas, OSB lining on the ceiling and walls and the polypropylene carpeting over puf padding.
-Each stack had 10 pallets.
-The mass of each stack was approximately 175 kg.
-When hay was added for ignition, the bales of hay averaged 12 kg.
+In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over puf padding.
+Each stack had 10 pallets and an approximate mass of 175~kg (386~lbs).
+Hay from bales averaging a mass of 12~kg (26~lbs) was added for ignition purposes.
 
@@
 
-The results are arranged in the order that the experiments were conducted.
+The following results are arranged in the order that the experiments were conducted.
 For the fire suppression experiments, the fuel load and resulting fire hazard were intended to increase as the different structures and fuel packages were utilized.
@@
 
-Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water collection pans across the floor surface area of the burn rooms within each structure (cf.
-Fig~\ref{fig:water_buckets}).
+Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water collection pans across the floor surface area of the burn rooms within each structure (see Figure~\ref{fig:water_buckets}).
 The depth of the pans was 0.3 m (1 ft).
-Water or CAF was flowed for a specified duration or until it appeared that a pan might be filled.
-Upon completion the bins were removed from the structure.
-Each bin was then weighed to quantify the impact of nozzle location and spray pattern.
-Thirty-three spray density tests were conducted; 21 were in the burn building for the gas cooling tests and 12 were in the single story structure for the suppression experiments.
-The interior of the fire room in the single story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.
+Water or CAF was flowed for a specified duration or until it appeared that a pan was filled.
+Upon completion of the test, the bins were removed from the structure.
+Then, each bin was weighed to quantify the impact of nozzle location and spray pattern.
+Thirty-three spray density tests were conducted: 21 in the burn building used for the gas cooling tests and 12 in the single-story structure used for the fire suppression experiments.
+The interior of the fire room in the single-story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.
 The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF.
-Tables\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
-In the table, GC stands for the gas cooling experiments while SE stands for the suppression experiments.
-For all of the experiments, 100~ft (30~m) of 1~3/4~inch hoseline connected to a Blitz Fire monitor with a Metro 1 nozzle was used.
+Tables~\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
+In the table, ``GC'' stands for the gas cooling experiments, and ``SE'' stands for the suppression experiments.
+For all experiments, 30~m (100~ft) of 1~3/4~inch hoseline connected to a ``blitz-fire'' monitor with a Metro 1 nozzle was used.
 
@@
 
-For the spray density tests, Table~\ref{tab:spray_density_tests}, the mid position had center line of the stream aimed at 2.44~m (8~ft) south of the North wall and 2.13~m (7~ft) west of the East wall in the concrete burn building.
-The back position had the center line of the stream aimed at 3.36~m (11~ft) south of the North wall and 2.13~m west (7~ft) of the East wall in the concrete burn building.
-Figure~\ref{fig:stream_position} shows the streams from the monitor nozzle for the middle and back positions respectively.
-From the figures the qualitative difference of the nozzle positions can be seen.
+For the spray density tests listed in Table~\ref{tab:spray_density_tests}, the ``mid'' position had the centerline of the stream aimed at 2.44~m (8~ft) south of the north wall and 2.13~m (7~ft) west of the east wall in the concrete burn building.
+The ``back'' position had the centerline of the stream aimed at 3.36~m (11~ft) south of the north wall and 2.13~m (7~ft) west of the east wall in the concrete burn building.
+Figure~\ref{fig:stream_position} shows the streams from the monitor nozzle for the middle and back positions.
+From the images, the qualitative difference of the nozzle positions can be observed.
 When the stream is in the middle position, after the stream hits the ceiling, the impact region is relatively narrow with the majority of the water hitting the walls of the corner opposite the nozzle position.
@@
 	\includegraphics[width=.4\columnwidth]{../Figures/Pictures/Straight_Back_BB}
-	\caption{Stream positions mid(left) and back (right) during spray density tests}
+	\caption[Middle and Back Stream Positions During Spray Density Tests]{Middle (left) and Back (right) Stream Positions During Spray Density Tests}
 	\label{fig:stream_position}
@@
 \end{table}
-For the fire suppression spray density experiments, Table~\ref{tab:spray_density_tests2}, the hallway position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 1.53~m (5~ft) east of the West wall.
-The fire room position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the South wall and 3.05~m (10~ft) west of the East wall.
+For the fire suppression spray density experiments, Table~\ref{tab:spray_density_tests2}, the hallway position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the south wall and 1.53~m (5~ft) east of the west wall.
+The fire room position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the south wall and 3.05~m (10~ft) west of the east wall.
 
@@
 
-After weighing each of the bins the mass of water (kg) in each bin was plotted by position to visualize the spray distribution.
-Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream in the back position, the majority of the water accumulated along the North and East walls of the gas cooling room within the burn building (cf.
-Fig.~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
-Figure~\ref{fig:Burn_Building_Test_7} shows difference a fog stream as the distribution of water is far more dispersed around the gas cooling room.
+After weighing each of the bins, the mass of water (kg) in each bin was plotted by position to visualize the spray distribution.
+Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream in the back position, the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
+Figure~\ref{fig:Burn_Building_Test_7} shows the difference of a fog stream, as the distribution of water is far more dispersed around the gas cooling room.
 The remainder of the burn building spray density figures are included in Appendix~\ref{app:spray_density}.
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB1}
-	\caption{Gas Cooling Spray Density Test 1, Straight Stream/Back nozzle position}
+	\caption{Gas Cooling Spray Density Test 1, Straight Stream/Back Nozzle Position}
 	\label{fig:Burn_Building_Test_1}
@@
 
-The 88 gas cooling experiments were completed as part of 9 separate burn sequences in the burn building.
+The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building.
 For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
 While Mitchell examined each individual experiment in detail, the results were mixed.
-In the different gas cooling scenarios CAF showed slightly better or slightly worse than plain water.
-Hence the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.
+In the different gas cooling scenarios, CAF showed slightly better or slightly worse than plain water.
+Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.
 
 Using the same data, the focus of this analysis was to look at trends within the aggregate data.
-During each test, the fire was ignited and then developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
+During each test, the fire was ignited and developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
 This condition was evidence that a hot gas layer at least 1.83~m deep had filled the room next to the burn room.
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time Series of Multiple Gas Cooling Experiments from 1 of 9 Burn sequences}
+	\caption{Time Series of Multiple Gas Cooling Experiments from 1 of 9 Burn Sequences}
 	\label{fig:gas_cooling_exp4}
@@
 
-There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}).
+There were three thermocouple arrays in the gas cooling room (adjacent to the burn room in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}).
 Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively.
-For both sets a solid 7/8~in nozzle in the middle position was used.
-The data shows that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3); this is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
-Gas Cooling Array 1 was exhibits some amount of suppression agent impact.
+For both sets, a solid 7/8~in.
+nozzle in the middle position was used.
+The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3).
+This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
+Gas Cooling Array 1 also exhibits some amount of suppression agent impact.
 Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.
-As a result it remains dry and it seems to provide the best representation of the gas cooling.
+As a result, it remained dry and seems to provide the best representation of the gas cooling.
 
@@
 
-To better quantify the effectiveness of the suppression agents (CAF, water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
+To better quantify the effectiveness of the suppression agents (CAF and water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
 Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments.
-The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, which were directly comparable, see Table~\ref{tab:Gas_Cooling_Descriptions}.
+The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, which were directly comparable (see Table~\ref{tab:Gas_Cooling_Descriptions}).
 These experiments included solid stream, straight streams, and narrow fog streams at both nozzle positions.
-While the total number of experiments was 88, there where a number of experiments that were performed which did not have a directly comparable experiment between water and CAF.
-For example a set of 12 Class A solution experiments were conducted.
-Gas cooling experiments were conducted with water applied on a wide fog nozzle setting, and since no significant differences were noted compared to narrow fog a comparable series with wide fog CAF was not conducted.
-Similarly, larger water flows were examined but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are also not included in this comparison.
+While the total number of experiments was 88, there were a number of experiments that did not have a directly comparable experiment between water and CAF.
+For example, a set of 12 Class A solution experiments were conducted.
+Gas cooling experiments were conducted with water applied in a wide fog stream.
+Since no significant differences were noted compared to the narrow fog stream, a comparable series with a wide fog CAF was not conducted.
+Similarly, larger water flows were examined, but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are also not included in this comparison.
 The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}.
@@
 
-The circles in Fig.~\ref{fig:combined_all} are the maximum temperature differences for each measurement point for all the replicate cooling events.
-If water and CAFS have the exact same temperature differences, all of the points would fall along solid black line in the figure.
-Circles that vary from that line represent measurements where either water (above) or CAF (below) cooled more significantly than the other agent.
-The gray area surrounding the solid black line, represents measurement uncertainty (\ref{subsec:Uncertainty}).
-For data that fall within this area, there is an inability to determine which agent was more or less effective than the other.
-The red dashed line is the line the describes the data by minimizing the differences between the two suppression agents through a linear approximation of the data.
+The circles in Figure~\ref{fig:combined_all} are the maximum temperature differences for each measurement point for all the replicate cooling events.
+If water and CAF were to have the exact same temperature differences, all the points would fall along the solid black line in the figure.
+Circles that vary from that line represent measurements where either water (above the line) or CAF (below the line) cooled more significantly than the other agent.
+The gray area surrounding the solid black line represents measurement uncertainty (Section~\ref{subsec:Uncertainty}).
+For data that fall within this area, there is an inability to determine which agent was more effective.
+The red dashed line describes the data by minimizing the differences between the two suppression agents through a linear approximation of the data.
 Since this line falls above the gray area for the comparison, water shows a better ability to cool gas under the same test criteria as CAF.
 
-The quality of the fit of the red dashed line to the scatter in gas cooling data is represented by the coefficient of determination (R$^2$ on Fig.~\ref{fig:combined_all}).
+The quality of the fit of the red dashed line to the scatter in gas cooling data is represented by the coefficient of determination (R$^2$ on Figure~\ref{fig:combined_all}).
 The coefficient of determination provides a way to quantify how significant the variation of the data is compared the the least squared error line.
@@
 
-For the 12 middle position replicate comparisons (Fig.~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAF.
-At the back position (Fig.~\ref{fig:CAFS_Water_full}), for the 3 replicate comparison, the least squared error line falls within the experimental uncertainty.
+For the 12 middle position replicate comparisons (Figure~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAF.
+At the back position (Figure~\ref{fig:CAFS_Water_full}), for the 3 replicate comparison, the least squared error line falls within the experimental uncertainty.
 This indicates an inability to distinguish between the two suppression agents with statistical confidence.
@@
 \end{figure}
-Based on the monitor position (arrow at the doorway in Fig.~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
+Based on the monitor position (arrow at the doorway in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
 As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
@@
 
-\subsubsection*{Single Story Structure}
+\subsubsection*{Single-Story Structure}
 \label{sec:fire_supp_single}
 
-There were 12 suppression tests conducted in the single story purpose-built concrete structure.
+There were 12 suppression tests conducted in the single-story purpose-built concrete structure.
 Eight of the experiments used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
 The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood-based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
-Ignition occurred in the rear of the single story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was ``opened''to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
+Ignition occurred in the rear of the single-story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was ``opened''to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
 The fires were intended to replicate post-flashover residential room and contents fires.
-Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (room nozzle).
+Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (door nozzle).
 Each nozzle flowed 15~s of water or compressed air foam depending on the test.
@@
 After the hallway nozzle was shutdown, there was a 15~s time period to simulate the crew advancing into the doorway of the fire room.
-The room nozzle was positioned just to the side of the entry door.
+The door nozzle was positioned just to the side of the entry door.
 It was also opened and flowed for approximately 15~s.
-The room nozzles was aimed in the direction of the seat of the fire (direct interior attack).
+The door nozzles was aimed in the direction of the seat of the fire (direct interior attack).
 Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.
@@
 \centering
-\caption{Single Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
+\caption{Single-Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions}
 \begin{tabular}{clllll}
@@
 These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
-Remember that there was a 15~s gap between the hallway nozzle flow and the fire room nozzle flow.
+Remember that there was a 15~s gap between the hallway nozzle flow and the door nozzle flow.
 The amount of temperature change during the period in between nozzle flows is shown by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.
@@
 \centering
-\caption{Single Story Fire Suppression Results}\label{tab:Test_Results}
+\caption{Single-Story Fire Suppression Results}\label{tab:Test_Results}
 \begin{tabular}{lccc}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSE_Test_1_092812_TC_A2}
-	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story CAF~1 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A2 from Single-Story CAF~1 Fire Suppression Test}
 	\label{fig:caf1_tca2}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/FSW_Test_2_092812_TC_A2}
-	\caption{Time Series of Thermocouple Data from Array TC A2 from Single Story Water~1 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A2 from Single-Story Water~1 Fire Suppression Test}
 	\label{fig:water1_tca2}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
 	\label{fig:fs_hall_a1}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
+	\caption{CAFS vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
 	\label{fig:fs_door_a1}
@@
 
-In Fig.~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water.
+In Figure~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water.
 The R$^2$ value of 0.901 shows a strong fit to the data.
@@
 While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (cf.
-Fig~\ref{fig:fs_door_a1}).
-At array A2, Fig.~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
+Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a1}).
+At array A2, Figure~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
 
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
 	\label{fig:fs_hall_a2}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
 	\label{fig:fs_door_a2}
@@
 
-\subsubsection*{Two Story Structure}
+\subsubsection*{Two-Story Structure}
 \label{sec:fire_supp_two}
 
-There were 7 suppression tests conducted in the two story purpose-built structure.
+There were 7 suppression tests conducted in the two-story purpose-built structure.
 All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
@@
 \footnotesize
-\caption{Two Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
+\caption{Two-Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
 \begin{tabular}{clllll}
@@
 
-Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two story structure.
+Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two-story structure.
 The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors.
@@
 The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door.
-Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux guages.
+Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
 Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
-Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare bead thermocouples used in the single story.
+Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare-bead thermocouples used in the single-story.
 The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
@@
 \centering
-\caption{Two Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
+\caption{Two-Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
 \begin{tabular}{lcccc}
@@
 	\includegraphics[width=.9\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation2}
-	\caption{Schematic of Second Floor of Two Story Structure Indicating Thermocouple and Heat Flux Gauges}
+	\caption{Schematic of Second Floor of Two-Story Structure Indicating Thermocouple and Heat Flux Gauges}
 	\label{fig:tcs_hf_second_2story}
@@
 The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10} - \ref{fig:caf9a_hf}.
-Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7 while Fig.~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
+Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7 while Figure~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
 The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression2}.
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story Water~7 Fire Suppression Test}
 	\label{fig:water7_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Water~7 Fire Suppression Test}
 	\label{fig:water7_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~9a Fire Suppression Test}
 	\label{fig:caf9a_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9a Fire Suppression Test}
 	\label{fig:caf9a_hf}
@@
 Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
-In Fig.~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
+In Figure~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
 
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TC_A10_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Two Story Fire Suppression Test at Thermocouple Array A10}
+	\caption{CAF vs Water Temperature Difference Comparison for Two-Story Fire Suppression Test at Thermocouple Array A10}
 	\label{fig:fs_a10}
@@
 
-In Fig.~\ref{fig:fs_a10}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) falls within the experimental uncertainty based around the equal cooling line (solid black line).
+In Figure~\ref{fig:fs_a10}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) falls within the experimental uncertainty based around the equal cooling line (solid black line).
 This indicates an inability to distinguish whether CAF or water had a more significant impact in temperature reduction following suppression of the fire.
 The R$^2$ value of 0.975 shows a strong fit to the data between water and CAF.
-Similar to the single story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial.
+Similar to the single-story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial.
 Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
@@
 
-While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness of CAF for interior structural firefighting varies widely.
+While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness of CAF for interior structural fire fighting varies widely.
 Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
@@
 It was their belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
-Other members of the technical panel thought that the bubble structure would provide the same mass flowrate of water but with more surface area.
+Other members of the technical panel thought that the bubble structure would provide the same mass flow rate of water but with more surface area.
 The increased surface area would enable faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
@@
 
-The data from this test series does not support the premise of firefighters being injured during an interior firefighting operation with CAF, because it was thought to provide less cooling than a similar hose stream of plain water.
+The data from this test series does not support the premise of firefighters being injured during an interior fire fighting operation with CAF, because it was thought to provide less cooling than a similar hose stream of plain water.
 
@@
 \subsection{Iowa State University Fire Flow Formula (1963)}
-The Iowa Formula for determining the required fire flowrate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
-The required fire flowrate, ($\dot{V}$), in gpm is equal to the volume ($V$) of the fire compartment (in cubic feet) divided by 100:
+The Iowa Formula for determining the required fire flow rate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
+The required fire flow rate, ($\dot{V}$), in gpm is equal to the volume ($V$) of the fire compartment (in cubic feet) divided by 100:
 \begin{equation}\label{eq:isu_form}
@@
 The fire rooms in these experiments ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
-Therefore the required flowrate for the fire room in the single story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
-The required flowrate for the fire room in the lower level of the two story structure would be approximately 168~Lpm (44~gpm).
+Therefore the required flow rate for the fire room in the single-story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
+The required flow rate for the fire room in the lower level of the two-story structure would be approximately 168~Lpm (44~gpm).
 While the formula has been widely taught over the years, there is some uncertainty about the application of the formula.
 Some texts mention that the Iowa State Formula provides the amount of water that needs to be applied in 30 seconds.
-If that is the case, then the flowrates given ``per minute'' must be doubled.
-The required flowrates would increase to 174~Lpm (46~gpm) and 336~Lpm (88~gpm), respectively.
-During the experiments the flowrate was approximately, 454~Lpm (120~gpm), which exceeds the required flowrate of the Iowa State Formula.
+If that is the case, then the flow rates given ``per minute'' must be doubled.
+The required flow rates would increase to 174~Lpm (46~gpm) and 336~Lpm (88~gpm), respectively.
+During the experiments the flow rate was approximately, 454~Lpm (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
 The fact that all of the fires were quickly controlled  during the experiments is consistent with this methodology.
@@
 The fire rooms in these experiments ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
-Applying the NFA formula based on floor area yields a required flowrate for the single story fire room of 369~Lpm (97~gpm).
-The required flowrate for the fire room in the lower level of the two story would be approximately 700~Lpm (184~gpm).
-Comparing the hose stream flowrates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single story but was below the required flowrate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two story structure.
+Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 369~Lpm (97~gpm).
+The required flow rate for the fire room in the lower level of the two-story would be approximately 700~Lpm (184~gpm).
+Comparing the hose stream flow rates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two-story structure.
 This is not consistent with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~Lpm (120~gpm).
@@
 Following Eq.~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room, which is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high, could support a heat release rate of approximately 4~MW assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
-For double the width of the open doorway (the doorway to the lower level of the two story structure) the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
+For double the width of the open doorway (the doorway to the lower level of the two-story structure) the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
 This does not account for flames burning outside of the compartment, which were frequently observed during testing.
 
-In the single story, there was an additional window opening in some of the experiments which added ventilation to the room.
-In the two story, there was an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
+In the single-story, there was an additional window opening in some of the experiments which added ventilation to the room.
+In the two-story, there was an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
 Even with the additional ventilation in both cases, the conditions in the fire compartment remained fuel rich as the flames extended out of the openings from the structures.
-It would seem then, that the heat release rate inside the compartment would not have exceeded 4~MW for the one story or 8~MW for the two story structure.
+It would seem then, that the heat release rate inside the compartment would not have exceeded 4~MW for the one story or 8~MW for the two-story structure.
 
 Earlier it was noted that the latent heat of vaporization of water is 2255~kJ/kg or approximately 2.3~MJ/kg.
-Assuming ideal heat transfer, the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two story.
-In these experiments, the mass flow rate of water was 7.57~kg/s (16.7~lb/s), which is theoretically twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two story structure.
+Assuming ideal heat transfer, the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two-story.
+In these experiments, the mass flow rate of water was 7.57~kg/s (16.7~lb/s), which is theoretically twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two-story structure.
 Again this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
@@
 
-The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single story structure.
+The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single-story structure.
 As discussed previously, with the larger area and the double the ventilation, the fire should be more of a challenge to the hose streams.
 There was also another variable that would be introduced, a firefighter controlling the nozzle.
-Recall, that in the single story experiments a monitor nozzle was used in a fixed position.
+Recall, that in the single-story experiments a monitor nozzle was used in a fixed position.
 As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
 This can be seen for both the water and CAF experiments in the data provided in Appendix~\ref{app:fire_suppression}.
-In some single story experiments, the fire was given time to redevelop and additional nozzle flows from the fixed positions were conducted to collect more data and to see if the fires could be extinguished.
+In some single-story experiments, the fire was given time to redevelop and additional nozzle flows from the fixed positions were conducted to collect more data and to see if the fires could be extinguished.
 During the additional flows, no significant differences were seen.
-In all of the single story experiments firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
-For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner to make the best use of the hose stream to suppress the fire in the lower level of the two story structure.
-
-The firefighting crew was from the MCFRS and all had been trained in the use of CAF and had experience using CAF.
-The firefighter on the nozzle was the same for all of the experiments conducted in the two story structure.
+In all of the single-story experiments firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
+For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner to make the best use of the hose stream to suppress the fire in the lower level of the two-story structure.
+
+The fire fighting crew was from the MCFRS and all had been trained in the use of CAF and had experience using CAF.
+The firefighter on the nozzle was the same for all of the experiments conducted in the two-story structure.
 The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
@@
 During the workshop (\cite{Grant:2011}), there were discussions that CAF could suppress a fire perhaps as much as five times faster than water.
-During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural firefighting on a residential scale.
-Going back to the premise of the study preventing firefighters from being injured during an interior firefighting operation with CAF, there is nothing in the fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
+During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural fire fighting on a residential scale.
+Going back to the premise of the study preventing firefighters from being injured during an interior fire fighting operation with CAF, there is nothing in the fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
 
@@
 
-One of the challenges with suppression research or determining the required flowrate of water needed on a building fire is the lack of data on realistic baseline requirements of the total amount of water needed for gas cooling and suppression.
+One of the challenges with suppression research or determining the required flow rate of water needed on a building fire is the lack of data on realistic baseline requirements of the total amount of water needed for gas cooling and suppression.
 In this study it seems clear that there was a sufficient amount of water for gas cooling and suppression.
@@
 Additional research is needed to examine the impact of nozzle type and nozzle movement on the fire environment.
-It is possible that some of the discomfort or injuries that firefighters experience during interior firefighting could be the result of a poor choice of nozzle or nozzle movement that results in displacing hotter gases into the area where the firefighter is located.
+It is possible that some of the discomfort or injuries that firefighters experience during interior fire fighting could be the result of a poor choice of nozzle or nozzle movement that results in displacing hotter gases into the area where the firefighter is located.
 Currently the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
@@
 
-Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural firefighting in residential structures.
+Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural fire fighting in residential structures.
 The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation~\cite{Grant:2011}.
@@
 The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
-This same department also experienced injuries to firefighters while using CAF during interior firefighting operations in residential structures.
+This same department also experienced injuries to firefighters while using CAF during interior fire fighting operations in residential structures.
 This study is composed of three types of experiments; spray density, gas cooling and fire suppression.
 In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates of water.
-The flowrate for each water experiment was 120~gpm.
+The flow rate for each water experiment was 120~gpm.
 For the CAF experiments, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate was added to the water flow.
@@
 There were two different geometries used for the fire suppression experiments.
-Twelve of the suppression experiments were conducted in a single story structure with an entry hallway that led to a fire compartment with a floor area of 27~$m^2$ (291~$ft^2$).
+Twelve of the suppression experiments were conducted in a single-story structure with an entry hallway that led to a fire compartment with a floor area of 27~$m^2$ (291~$ft^2$).
 Within this structure, two different types of fuel loads were used.
@@
 
-Seven of the suppression experiments were conducted in a two story structure.
+Seven of the suppression experiments were conducted in a two-story structure.
 The fire compartment was the full lower level of the structure and it had an open floor plan with an area of 51.4~$m^2$ (553~$ft^2$).
@@
 
-\chapter{Single Story Fire Suppression Data}
+\chapter{Single-Story Fire Suppression Data}
 \label{app:fire_suppression}
@@
 
-\chapter{Two Story Fire Suppression Data}
+\chapter{Two-Story Fire Suppression Data}
 \label{app:fire_suppression2}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~7 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~7 Fire Suppression Test}
 	\label{fig:app_caf7_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~7 Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~7 Fire Suppression Test}
 	\label{fig:app_caf7_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Water~7 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story Water~7 Fire Suppression Test}
 	\label{fig:app_water7_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Water~7 Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Water~7 Fire Suppression Test}
 	\label{fig:app_water7_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8a Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~8a Fire Suppression Test}
 	\label{fig:app_caf8a_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8a Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8a Fire Suppression Test}
 	\label{fig:app_caf8a_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8b Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~8b Fire Suppression Test}
 	\label{fig:app_caf8b_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8b Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8b Fire Suppression Test}
 	\label{fig:app_caf8b_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~8 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~8 Fire Suppression Test}
 	\label{fig:app_caf8_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~8 Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8 Fire Suppression Test}
 	\label{fig:app_caf8_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story Class~A~1 Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story Class~A~1 Fire Suppression Test}
 	\label{fig:app_classa1_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story Class~A~1 Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Class~A~1 Fire Suppression Test}
 	\label{fig:app_classa1_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9a Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~9a Fire Suppression Test}
 	\label{fig:app_caf9a_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9a Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9a Fire Suppression Test}
 	\label{fig:app_caf9a_hf}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two Story CAF~9b Fire Suppression Test}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~9b Fire Suppression Test}
 	\label{fig:app_caf9b_tca10}
@@
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two Story CAF~9b Fire Suppression Test}
+	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9b Fire Suppression Test}
 	\label{fig:app_caf9b_hf}

### 2016-07-31 Projects/DelCo_2012/Report/DelCo_2012.tex
Added Jack's edits and Changed CAFS to CAF in gas cooling captions

@@
 In the decades that followed the development of CAFS, a number of urban/suburban fire departments across the country began to integrate CAFS into their apparatus.
-For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires and also examined using them for structural fire fighting.
+For example, the Los Angeles County Fire Department incorporated CAFS into their apparatus for wildland urban interface fires and also considered their use for structural fire fighting.
 Other departments across the country began to experiment with CAFS for use in structural fire fighting.
@@
 Technical panel members whose departments routinely use CAF for structural fire fighting were invited and present at many of the fire suppression experiments.
-The series of experiments, planned during the workshop, for examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
+The experiments were planned during the workshop.
+Three types of experiments examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
 The data from these experiments were presented to the technical panel members.
@@
 To accomplish the last series of experiments, additional funding was obtained from NIST, and the experiments were conducted in 2015.
-The fuel load contained both wood-based wall and ceiling finishes, pallets as well as carpeting and upholstered furniture.
+The fuel load contained both wood-based wall and ceiling finishes, pallets, as well as carpeting and upholstered furniture.
 
@@
 
-The fire suppression series included 20 experiments in the single-story experimental structures and one in the two-story structure.
+The fire suppression series included 20 experiments.
 Twelve experiments were conducted in the single-story structures (6 in each structure) using both water and CAF application as a suppression agent.
 The nozzle patterns were varied and included straight stream, solid stream, and narrow fog stream.
-The two-story test used both water and CAF from a straight stream nozzle.
+The six experiments in the two-story structure used both water and CAF from a straight stream nozzle.
+In addition two CAF experiments were conducted in the two-story with a solid stream.
 
@@
 
-Each structure had burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
+Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
 The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
@@
 A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
-A legend, which clarifies the instrumentation schematics discussed in the follow sections, is included in Figure~\ref{fig:Instrumentation_Legend}.
+A legend, which clarifies the instrumentation schematics discussed in the following sections, is included in Figure~\ref{fig:Instrumentation_Legend}.
 
@@
 
-The gas cooling tests included 4 bare-bead thermocouple arrays  a bi-directional probe plus solid thermocouple array, and a total heat flux gauge/radiometer pair.
+The gas cooling tests included 4 bare-bead thermocouple arrays, a bi-directional probe with a thermocouple array, and a total heat flux gauge/radiometer pair.
 Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
-Each of the bare-bead thermocouple array had 11 thermocouples.
+Each of the bare-bead thermocouple arrays had 11 thermocouples.
 The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10ft) below the ceiling.
@@
 The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft), and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
-The total heat flux gauge/radiometer were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The total heat flux gauge/radiometer set were positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
 
@@
 Each bare-bead thermocouple array had 8 thermocouples.
-The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were space 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
+The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
 The three bi-directional probe arrays had unique sensor locations.
-For the window array there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit.
+For the window array, there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit.
 For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling.
@@
 The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sense ``looking'' vertical and the other horizontal.
+The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical and the other horizontal.
 
@@
 
-Fire suppression testing in the two-story structure included similar types instrumentation but included more sensors.
-Three bare-bead thermocouple arrays and 2 bi-directional probe plus solid thermocouples arrays were used in the first floor.
+Fire suppression testing in the two-story structure included similar types of instrumentation but included more sensors.
+Three bare-bead thermocouple arrays and 2 bi-directional probe and thermocouples arrays were used in the first floor.
 Figure~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
@@
 The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-A bare-bead Type K thermocouple was co-located with each probe.
+Bare-bead Type K thermocouples are co-located with each probe.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
@@
 
-In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over puf padding.
+In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
 Each stack had 10 pallets and an approximate mass of 175~kg (386~lbs).
@@
 Figure~\ref{fig:Burn_Building_Test_1} shows that with a straight stream in the back position, the majority of the water accumulated along the north and east walls of the gas cooling room within the burn building (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
-Figure~\ref{fig:Burn_Building_Test_7} shows the difference of a fog stream, as the distribution of water is far more dispersed around the gas cooling room.
+Figure~\ref{fig:Burn_Building_Test_7} shows the results from a fog stream, where the distribution of water is far more dispersed around the gas cooling room.
 The remainder of the burn building spray density figures are included in Appendix~\ref{app:spray_density}.
@@
 For example, a set of 12 Class A solution experiments were conducted.
-Gas cooling experiments were conducted with water applied in a wide fog stream.
-Since no significant differences were noted compared to the narrow fog stream, a comparable series with a wide fog CAF was not conducted.
+Gas cooling experiments were also conducted with water applied in a wide fog stream.
+Since no significant differences were noted compared to the narrow fog stream experiments, a comparable series with a wide fog CAF was not conducted.
 Similarly, larger water flows were examined, but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are also not included in this comparison.
@@
 The data can be separated to examine the impact of nozzle position (back or middle position) on the ability to cool gases for each of the suppression agents.
-Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 pairs of experiments in the back position and 3 pairs of experiments in the middle position respectively.
+Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 pairs of experiments in the back position and 3 pairs of experiments in the middle position, respectively.
 
@@
 For the 12 middle position replicate comparisons (Figure~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAF.
-At the back position (Figure~\ref{fig:CAFS_Water_full}), for the 3 replicate comparison, the least squared error line falls within the experimental uncertainty.
+At the back position (Figure~\ref{fig:CAFS_Water_full}), for the 3 replicate comparisons, the least squared error line falls within the experimental uncertainty.
 This indicates an inability to distinguish between the two suppression agents with statistical confidence.
@@
 Therefore, the maximum temperature differences for each thermocouple on each of the three arrays should also be analyzed separately.
-Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3 respectively.
+Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3, respectively.
 Note that thermocouple array A3, the array which has the least amount of direct impact from the suppression agents, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Experimental Pairs}
 	\label{fig:CAFS_Water_A1_all}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Experimental Pairs}
 	\label{fig:CAFS_Water_A2_all}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Experimental Pairs}
 	\label{fig:CAFS_Water_A3_all}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
 	\label{fig:CAFS_Water_A1_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
 	\label{fig:CAFS_Water_A2_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
 	\label{fig:CAFS_Water_A3_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
 	\label{fig:CAFS_Water_A1_back}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
 	\label{fig:CAFS_Water_A2_back}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
-	\caption{CAFS vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
 	\label{fig:CAFS_Water_A3_back}
@@
 It was also opened and flowed for approximately 15~s.
-The door nozzles was aimed in the direction of the seat of the fire (direct interior attack).
+The door nozzle was aimed in the direction of the seat of the fire (direct interior attack).
 Table~\ref{tab:Test_Descriptions} provides an overview of the suppression tests conducted.
@@
 
-Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, differences are not substantial.
-Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
+Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, the differences are not substantial.
+Both suppression agents had similar, significant impacts in reducing the high-temperature, high-heat flux environment that existed before suppression.
 The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests.
@@
 In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
+However in most cases rekindling occured as nozzle movement was needed to completely extinguish the fire.
 
@@
 There were 7 suppression tests conducted in the two-story purpose-built structure.
-All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling, and five of the seven tests had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
+All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling.
+Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
 Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor door on the south side of the structure.
@@
 The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
-The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door.
+The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door.
 Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
@@
 To expand upon the 2012 and 2013 tests described in~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
-One set of experiments used only wood-based fuels, to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
-A final experimental series, used a larger fire room, with more ventilation.
-In this final series, another change was made, the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
+One set of experiments used only wood-based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
+A final experimental series used a larger fire room with more ventilation.
+In this final series, another change was made: the nozzle was hand held, and could be moved as needed to effectively extinguish the fire.
 This section will discuss the overall results of the study and provide potential explanations to support them.
@@
 
-Water is the most widely used fire extinguishing agent because it is effective, environmentally friendly, nontoxic, inexpensive and in many cases, readily available.
+Water is the most widely used fire extinguishing agent because it is effective, environmentally friendly, nontoxic, inexpensive, and in many cases, readily available.
 In addition, water has a very high heat of vaporization per unit mass, at least four times as high as that of any other nonflammable liquid~\cite{NFPA}.
@@
 Because the energy absorbing capabilities of water are well quantified, they can be used as a basis to calculate the theoretical minimum delivery rate of water needed to extinguish a burning material with a known heat (energy) release rate.
-Unfortunately, experience has shown that water must be applied at 10 to 100 times the theoretical rate in practice to control and extinguish the fire~\cite{Friedman:2}.
+Unfortunately, based on experience it has been estimated that water must be applied at 10 to 100 times the theoretical rate in order to control and extinguish the fire~\cite{Friedman:2}.
 As a result of this apparent inefficiency and the need to address fires containing a wide variety of materials, water-based fire fighting additives have been utilized for many years to enhance the fire fighting capabilities of ordinary water.
@@
 Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
-During the planning of the experiments, there were a range of hypothesis regarding the outcome.
+During the planning of the experiments, there were a range of hypotheses regarding the outcome.
 Some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF.
@@
 
-As pointed out in the results section, the conditions at TC Array 3 represented the ``'best'' gas cooling results because that position had the least impact of agents hitting and cooling the thermocouples themselves.
+As pointed out in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results because that position had the least impact of agents hitting and cooling the thermocouples themselves.
 Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
@@
 The data from the thermocouples in TC Array 2, provide a sense of the impact of a combination of surface cooling and gas cooling.
-For example, when the nozzle was in the ``middle position'' the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC Array 2 and the adjacent walls.
+For example, when the nozzle was in the ``middle position,'' the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC Array 2 and the adjacent walls.
 In this location, the data tended to favor water.
-But again this did not represent gas cooling, this represented some of the water or CAF hitting the thermocouples and cooling the surrounding gases.
+However this did not represent gas cooling.
+Rather, this represented some of the water or CAF hitting the thermocouples and cooling the surrounding gases.
 As a result, temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} respectively.
@@
 In many cases such as CAF Straight Stream Mid, the foam solution collected was near zero.
-In other cases such as CAF Fog Mid, the amount of foam solution collected was more than 3~kgs.
+In other cases such as CAF Fog Mid, the amount of foam solution collected was more than 3~kg.
 Similar variations occurred with water.
@@
 
-The data from this test series does not support the premise of firefighters being injured during an interior fire fighting operation with CAF, because it was thought to provide less cooling than a similar hose stream of plain water.
+The data from this test series does not support the premise of firefighters being injured during an interior fire fighting operation with CAF, since CAF provided cooling similar to that of the equivalent flowrate of plain water.
 
@@
 The required flow rate for the fire room in the lower level of the two-story structure would be approximately 168~Lpm (44~gpm).
-While the formula has been widely taught over the years, there is some uncertainty about the application of the formula.
-Some texts mention that the Iowa State Formula provides the amount of water that needs to be applied in 30 seconds.
-If that is the case, then the flow rates given ``per minute'' must be doubled.
-The required flow rates would increase to 174~Lpm (46~gpm) and 336~Lpm (88~gpm), respectively.
 During the experiments the flow rate was approximately, 454~Lpm (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
@@
 
-Both of the formulas listed above do not overtly account for the ventilation of the fire structure, only the size of the fire structure.
-Further the most recent formula was developed in 1981, based on the fire ground experience of fire chiefs.
-The experience that was shared was likely from fires that occurred in the 1960's and the 1970's.
+Both of the formulas listed above do not explicitly account for the ventilation of the fire structure, only the size of the fire structure.
+Further the most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
+This experience was likely from fires that occurred in the 1960's and the 1970's.
 It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and with higher heat release rates than the natural fuels that filled the homes in the 1940's and 1950's.
 The change of materials in homes began in the 1960's and continues through to present day.
-However, it was unlikely that this change was factored in to the NFA Formula.
+It was unlikely, however, that this change was factored in to the NFA Formula.
 
@@
 The purpose here is to get a sense of the amount of heat energy that the hose streams needed to overcome.
-This algorithm, just like the NFA formula has never been validated for this application.
+This algorithm, like the NFA formula has never been validated for this application.
 
@@
 
-In Eq.~\ref{eq:HRRSto_item}, the maximum heat release rate $\dot{Q}_{stoichiometric}$ in kW is based on airflow through the area of the opening, $A_0$ in m$^2$ and the height of the opening $\sqrt{H_0}$ in m.
+In Eq.~\ref{eq:HRRSto_item}, the maximum heat release rate $\dot{Q}_{stoichiometric}$, in kW, is based on airflow through the area of the opening, $A_0$ in m$^2$ and the squre root of the height of the opening, $\sqrt{H_0}$, in ${m}^{1/2}$.
 
@@
 During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-wood-based fuels, however develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
+Wood-based fuels, on the otherhand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
 Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.
@@
 The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single-story structure.
-As discussed previously, with the larger area and the double the ventilation, the fire should be more of a challenge to the hose streams.
-There was also another variable that would be introduced, a firefighter controlling the nozzle.
-Recall, that in the single-story experiments a monitor nozzle was used in a fixed position.
+As discussed previously, with the larger area and double the ventilation of the previous experiments, the fire should be more of a challenge to the hose streams.
+There was also another variable that would be introduced: a firefighter controlling the nozzle.
+Recall that in the single-story experiments, fixed position monitor nozzle was used in a fixed position.
 As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
@@
 In all of the single-story experiments firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
-For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner to make the best use of the hose stream to suppress the fire in the lower level of the two-story structure.
+For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner in order to make the best use of the hose stream to suppress the fire in the lower level of the two-story structure.
 
@@
 The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
-Then the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
+Then, the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
 The nozzle was shut down when there were no flames visible from the doorway.
@@
 
-During the workshop (\cite{Grant:2011}), there were discussions that CAF could suppress a fire perhaps as much as five times faster than water.
+During the workshop~\cite{Grant:2011}, there were discussions that CAF could suppress, or knockdown, a fire three to five times faster than water.
 During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural fire fighting on a residential scale.
-Going back to the premise of the study preventing firefighters from being injured during an interior fire fighting operation with CAF, there is nothing in the fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
+Going back to the premise of the study, preventing firefighters from being injured during an interior fire fighting operations.
+There is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
 
@@
 One of the challenges with suppression research or determining the required flow rate of water needed on a building fire is the lack of data on realistic baseline requirements of the total amount of water needed for gas cooling and suppression.
-In this study it seems clear that there was a sufficient amount of water for gas cooling and suppression.
+In this study, it seems clear that there was a sufficient amount of water for gas cooling and suppression.
 One question that arises is, how much could the flow rate of water have been reduced before a significant difference in performance was observed?
 
-Information from actual incidents in the field, shaped this study.
+Information from actual incidents in the field shaped this study.
 From the gas cooling and suppression perspective, the data does not indicate that the use of CAF would result in a higher thermal hazard.
-However, there are other issues like nozzle reaction force and flow separation which have been covered in the Cal Poly fire ground studies~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
-These are issues that can be addressed in training.
+However, there are other issues like nozzle reaction force and flow separation which have been covered in the Cal Poly fire ground studies that can be addressed in training~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 It is important to provide adequate training when adopting a new method or new technology.
@@
 A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how that can impact the flow of gases within the structure.
-Based on the results of this study, it would seem that training and understanding the impact of nozzle movement are ways to look for more effective use of water.
+Based on the results of this study, it would seem that training and understanding the impact of nozzle movement are ways to look for a more effective use of water.
 
@@
 This study is composed of three types of experiments; spray density, gas cooling and fire suppression.
-In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates of water.
+In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar types with similar mass flow rates of water.
 The flow rate for each water experiment was 120~gpm.
@@
 Suppression agents were not applied to the fire in the burn room.
-In this report an aggregate analysis is made to examine difference due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
+In this report, an aggregate analysis is made to examine differences due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
 No significant differences were found in the gas cooling capabilities of the two agents.
@@
 A manual hose stream application was made from outside the doorway on the lower level.
-In these experiments there was a combination of wood-based and synthetic fuels.
+In these experiments, there was a combination of wood-based and synthetic fuels.
 The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
@@
 
-Thank you for assisting NIST in generating data that will assist the fire service in making tactical choices.
+Thanks to all involved for assisting in generating data that will aid the fire service in making evidence based tactical choices.
 

### 2016-07-31 Projects/DelCo_2012/Report/DelCo_2012.tex
fix caf typos

@@
 In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
-However in most cases rekindling occured as nozzle movement was needed to completely extinguish the fire.
+However in most cases rekindling occurred as nozzle movement was needed to completely extinguish the fire.
 
@@
 During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-Wood-based fuels, on the otherhand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
+Wood-based fuels, on the other hand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
 Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.

### 2016-08-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
added references

@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-
-Values generated in the bench scale experiments will be utilized as input to predict real scale results using the algorithms.
+Applications of algorithms such as these are presented in cureent fire investigaton textbooks~\cite{Icove:2013}.
+
+Values generated in the bench scale experiments will be utilized as input to predict or simulate real scale results using the algorithms.
 Then the predicted results will be compared with the full-scale experimental results.
@@
 \section{Evidence of a Fire Pattern}
+
+The first              ~\cite{Babrauskas:1981}
 
@@
 vyto second item ignite
+
 \begin{equation} \label{eq:second_item}
@@
 
-discuss the premise
+discuss the premise    ~\cite{McCaffrey:1979}
 McCaffery

### 2016-08-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Added final edits to CAFS report, including new refs

--- 2016-07-31 Projects/DelCo_2012/Report/DelCo_2012.tex
@@
 To accomplish the last series of experiments, additional funding was obtained from NIST, and the experiments were conducted in 2015.
-The fuel load contained both wood-based wall and ceiling finishes, pallets, as well as carpeting and upholstered furniture.
+The fuel load contained both wood-based wall and ceiling finishes, pallets, carpeting, and upholstered furniture.
 
@@
 
-The west structure was modified to add second story to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
+The west structure was modified to add a second story to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
 
@@
 A stairwell was built to connect the floors.
-Stairs started 1.6~m (5.25~ft) off the South wall with a width of 1.2~m (4~ft) off the East wall.
+Stairs started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
 The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs.
 The studs were set to 0.40~m (16~in) centers.
-The interior  walls were protected by 16~mm (5/8~in) fire rated gypsum board, 16~mm (5/8~in) durarock board, and a second layer of 16~mm (5/8~in) fire rated gypsum board.
-The exterior walls were protected with 11~mm (7/16~in) oriented strand board and 8~mm (5/16~in) fiber cement lap siding.
+The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
 Figure~\ref{fig:dimensioned_second_2story} shows the dimensions of the second story of the modified west structure.
@@
 
-The gas cooling tests included 4 bare-bead thermocouple arrays, a bi-directional probe with a thermocouple array, and a total heat flux gauge/radiometer pair.
-Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+The gas cooling tests included four bare-bead thermocouple arrays, a bi-directional probe with a thermocouple array, and a total heat flux gauge/radiometer pair.
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} provides the positions within the burn room and gas cooling room where the sensors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
 Each of the bare-bead thermocouple arrays had 11 thermocouples.
@@
 There were 6 velocity probes and solid thermocouples centered at the external doorway to the gas cooling room.
-The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft), and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
+The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft) below the soffit, and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
 The total heat flux gauge/radiometer set were positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
@@
 The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical and the other horizontal.
+The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical at the ceiling and the other horizontal.
 
@@
 Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests.
-The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit with the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
+The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
 
@@
 
-The second story featured 6 bare-bead arrays and 3 bi-directional probe plus solid thermocouple arrays.
+The second story featured six bare-bead arrays and three bi-directional probe plus solid thermocouple arrays.
 The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground.
@@
 The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level.
-The bi-direction probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level.
-The third bi-directional probe array (3~m (9~ft) off the North wall and 0.6~m (2~ft) off the East wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.
+The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level.
+The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.
 
@@
 Water flow rate was measured with a pressure and flow meter combination.
-The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
+The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
@@
 Wood pallets were used as the fuel source for the gas cooling experiments.
-The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick and ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lbs).
+The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick and ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lb).
 The initial fuel load consisted of 10 pallets, arranged in two stacks of five, as shown in Figure~\ref{fig:Burn_Building_Fuel_Load}.
@@
 The specific locations can be found in the dimensioned schematic, Figure~\ref{fig:Furniture_Fuel_Load_Dimensions}.
-In total, this fuel package contains approximately 336~kg (739~lbs) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
+In total, this fuel package contains approximately 336~kg (739~lb) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
 Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
@@
 In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
-Each stack had 10 pallets and an approximate mass of 175~kg (386~lbs).
-Hay from bales averaging a mass of 12~kg (26~lbs) was added for ignition purposes.
+Each stack had 10 pallets and an approximate mass of 175~kg (386~lb).
+Hay from bales averaging a mass of 12~kg (26~lb) was added for ignition purposes.
 
@@
 
-The quality of the fit of the red dashed line to the scatter in gas cooling data is represented by the coefficient of determination (R$^2$ on Figure~\ref{fig:combined_all}).
-The coefficient of determination provides a way to quantify how significant the variation of the data is compared the the least squared error line.
+The quality of the fit of the red dashed line to the scatter in gas cooling data is represented by the coefficient of determination (R$^2$ in Figure~\ref{fig:combined_all}).
+The coefficient of determination provides a way to quantify how significant the variation of the data is compared to the least squared error line.
 Here, the higher the value of R$^2$, the better the ordinary least square line describes the relationship between water and CAF temperature difference comparisons.
@@
 
-For the 12 middle position replicate comparisons (Figure~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water has a slight advantage in gas cooling relative to CAF.
-At the back position (Figure~\ref{fig:CAFS_Water_full}), for the 3 replicate comparisons, the least squared error line falls within the experimental uncertainty.
+For the 12 middle position replicate comparisons (Figure~\ref{fig:CAFS_Water_mid}), the results (via the dashed red line) show that water had a slight advantage in gas cooling relative to CAF.
+For the three back position replicate comparisons (Figure~\ref{fig:CAFS_Water_full}), the least squared error line falls within the experimental uncertainty.
 This indicates an inability to distinguish between the two suppression agents with statistical confidence.
@@
 Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
-Ideally, the thermocouple is providing an estimate of the temperature of the gas that it is surrounded by.
+Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it.
 However, we must remember that the thermocouple is actually providing us with its own temperature.
@@
 \end{figure}
+
 Based on the monitor position (arrow at the doorway in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
-As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the mid position compared to the positions of the thermocouple trees.
+As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the middle position compared to the positions of the thermocouple trees.
+
 \begin{figure}[!ht]
@@
 Therefore, the maximum temperature differences for each thermocouple on each of the three arrays should also be analyzed separately.
-Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple trees A1, A2, and A3, respectively.
-Note that thermocouple array A3, the array which has the least amount of direct impact from the suppression agents, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
+Figures~\ref{fig:CAFS_Water_A1_all}, \ref{fig:CAFS_Water_A2_all}, and \ref{fig:CAFS_Water_A3_all} show the temperature cooling scatter for thermocouple arrays A1, A2, and A3, respectively.
+Note that thermocouple array A3, the array that had the least amount of direct impact from the suppression agents, has the closest fit compared to the solid black line that represents uniform impact for both suppression agents.
 The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Thermocouple tree A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF on cooling the thermocouples.
+Thermocouple array A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF on cooling the thermocouples.
 
@@
 
-The thermocouple array data can also also be decomposed as a function of nozzle position: 12 middle position experimental pairs and 3 back experimental pairs.
+The thermocouple array data can also be decomposed as a function of nozzle position: 12 middle position experimental pairs and 3 back experimental pairs.
 Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position.
 Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 3 replicate tests with the monitor nozzle in the back position.
-Again note that the best fit occurs with the data from thermocouple array 3 for both nozzle positions.
-This analysis of the data results in the same conclusions at the analysis from the Mitchell paper \cite{Mitchell:1}, the gas cooling performance of CAF, under these conditions, is similar to water.
+Again, note that the best fit occurs with the data from thermocouple array 3 for both nozzle positions.
+This analysis of the data results in the same conclusions as the analysis from the Mitchell paper \cite{Mitchell:1}: the gas cooling performance of CAF is similar to water under these conditions.
 
@@
 
-There were 12 suppression tests conducted in the single-story purpose-built concrete structure.
+There were 12 suppression tests conducted in the single-story, purpose-built concrete structure.
 Eight of the experiments used a fuel load comprised of typical household furnishings that included wooden wall paneling, two sofas, two overstuffed chairs, carpet, and padding (Section~\ref{sec:fire_suppression_furniture_fuel}).
-The other four experiments used wood pallet fuel load in a space with the ceiling and walls composed of wood-based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
-Ignition occurred in the rear of the single-story structures and the available ventilation was through the front doorway and for eight of the experiments a rear window was ``opened''to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
+The other four experiments used a wood pallet fuel load in a space with the ceiling and walls composed of wood-based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
+Ignition occurred in the rear of the single-story structure, and the available ventilation was through the front doorway.
+For eight of the experiments, a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
 The fires were intended to replicate post-flashover residential room and contents fires.
 Hose lines were pre-deployed with fixed nozzles set in two locations: one in the hallway on the approach to the burn room (hallway nozzle) and one just inside the burn room to the right side of the hallway (door nozzle).
-Each nozzle flowed 15~s of water or compressed air foam depending on the test.
+Each nozzle flowed 15~s of water or CAF depending on the test.
 The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
-Suppression from this location would be in the form of gas cooling as the stream was not aimed at the seat of the fire (indirect interior attack).
-After the hallway nozzle was shutdown, there was a 15~s time period to simulate the crew advancing into the doorway of the fire room.
+Suppression from this location would be in the form of gas cooling, as the stream was not aimed at the seat of the fire (indirect interior attack).
+After the hallway nozzle was shutdown, there was a 15~s time period of no nozzle flow to simulate the crew advancing into the doorway of the fire room.
 The door nozzle was positioned just to the side of the entry door.
@@
 Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAF tests.
-The table provides change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
+The table lists the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
 These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
-Remember that there was a 15~s gap between the hallway nozzle flow and the door nozzle flow.
-The amount of temperature change during the period in between nozzle flows is shown by comparing the temperature at the end of the hallway flow period with the temperature at the beginning of the room flow period.
+Recall that there was a 15~s gap between the hallway nozzle flow and the door nozzle flow.
+The amount of temperature change during the period in between nozzle flows is shown by comparing the temperature at the end of the hallway nozzle flow period with the temperature at the beginning of the door nozzle flow period.
 
@@
 CAF~1 Hallway    & 690~$^{\circ}$C - 180~$^{\circ}$C   & 590~$^{\circ}$C - 150~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-CAF~1 Room       & 170~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~1 Door       & 170~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 Water~1 Hallway  & 720~$^{\circ}$C - 220~$^{\circ}$C   & 700~$^{\circ}$C - 120~$^{\circ}$C   & 40~kW/m$^2$ - 15~kW/m$^2$  \\
-Water~1 Room     & 120~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+Water~1 Door     & 120~$^{\circ}$C - 80~$^{\circ}$C    & 80~$^{\circ}$C - 70~$^{\circ}$C     & 25~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 CAF~2 Hallway    & 590~$^{\circ}$C - 290~$^{\circ}$C   & 500~$^{\circ}$C - 110~$^{\circ}$C   & 65~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~2 Room       & 80~$^{\circ}$C -  70~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~2 Door       & 80~$^{\circ}$C -  70~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~2 Hallway  & 640~$^{\circ}$C - 410~$^{\circ}$C   & 500~$^{\circ}$C - 230~$^{\circ}$C   & 70~kW/m$^2$ - 20~kW/m$^2$  \\
-Water~2 Room     & 460~$^{\circ}$C - 300~$^{\circ}$C   & 200~$^{\circ}$C - 140~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~2 Door     & 460~$^{\circ}$C - 300~$^{\circ}$C   & 200~$^{\circ}$C - 140~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~3 Hallway  & 610~$^{\circ}$C - 300~$^{\circ}$C   & 580~$^{\circ}$C - 170~$^{\circ}$C   & 60~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~3 Room     & 210~$^{\circ}$C - 130~$^{\circ}$C   & 60~$^{\circ}$C - 40~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~3 Door     & 210~$^{\circ}$C - 130~$^{\circ}$C   & 60~$^{\circ}$C - 40~$^{\circ}$C     & 30~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 CAF~3 Hallway    & 880~$^{\circ}$C - 300~$^{\circ}$C   & 780~$^{\circ}$C - 230~$^{\circ}$C   & 80~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~3 Room       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~3 Door       & 190~$^{\circ}$C - 60~$^{\circ}$C    & 80~$^{\circ}$C - 60~$^{\circ}$C     & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~4 Hallway  & 850~$^{\circ}$C - 360~$^{\circ}$C   & 850~$^{\circ}$C - 180~$^{\circ}$C   & 125~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~4 Room     & 190~$^{\circ}$C - 100~$^{\circ}$C   & 130~$^{\circ}$C - 70~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+Water~4 Door     & 190~$^{\circ}$C - 100~$^{\circ}$C   & 130~$^{\circ}$C - 70~$^{\circ}$C    & 15~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 CAF~4 Hallway    & 620~$^{\circ}$C - 240~$^{\circ}$C   & 530~$^{\circ}$C - 180~$^{\circ}$C   & 50~kW/m$^2$ - 15~kW/m$^2$  \\
-CAF~4 Room       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~4 Door       & 190~$^{\circ}$C - 120~$^{\circ}$C   & 120~$^{\circ}$C - 180~$^{\circ}$C   & 20~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~5 Hallway  & 700~$^{\circ}$C - 390~$^{\circ}$C   & 400~$^{\circ}$C - 90~$^{\circ}$C    & 65~kW/m$^2$ - 20~kW/m$^2$  \\
-Water~5 Room     & 210~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 100~$^{\circ}$C   & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
+Water~5 Door     & 210~$^{\circ}$C - 140~$^{\circ}$C   & 120~$^{\circ}$C - 100~$^{\circ}$C   & 20~kW/m$^2$ - 15~kW/m$^2$  \\ [.25cm]
 CAF~5 Hallway    & 550~$^{\circ}$C - 400~$^{\circ}$C   & 360~$^{\circ}$C - 30~$^{\circ}$C    & 40~kW/m$^2$ - 25~kW/m$^2$  \\
-CAF~5 Room       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
+CAF~5 Door       & 390~$^{\circ}$C - 210~$^{\circ}$C   &                                     & 10~kW/m$^2$ - 5~kW/m$^2$  \\ [.25cm]
 Water~6 Hallway  & 770~$^{\circ}$C - 160~$^{\circ}$C   & 480~$^{\circ}$C - 50~$^{\circ}$C    & 60~kW/m$^2$ - 10~kW/m$^2$  \\
-Water~6 Room     & 150~$^{\circ}$C - 90~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+Water~6 Door     & 150~$^{\circ}$C - 90~$^{\circ}$C    & 70~$^{\circ}$C - 50~$^{\circ}$C     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 CAF~6 Hallway    & 650~$^{\circ}$C - 190~$^{\circ}$C   & 570~$^{\circ}$C - 60~$^{\circ}$C    & 50~kW/m$^2$ - 10~kW/m$^2$  \\
-CAF~6 Room       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
+CAF~6 Door       & 180~$^{\circ}$C - 130~$^{\circ}$C   &                                     & 5~kW/m$^2$ - 0~kW/m$^2$  \\ [.25cm]
 \bottomrule[1.25pt]
@@
 
-Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to Water, the differences are not substantial.
-Both suppression agents had similar, significant impacts in reducing the high-temperature, high-heat flux environment that existed before suppression.
-The first (hallway) suppression, an indirect attack, did a majority of the cooling in all of the tests.
+Note that while there are some differences in the changes in temperature and heat flux when comparing CAF to water, the differences are not substantial.
+Both suppression agents had similar significant impacts in reducing the high-temperature, high-heat flux environment that existed before suppression.
+The first suppression from the hallway nozzle, an indirect attack, did the majority of the cooling in all of the tests.
 This illustrates the impact of gas cooling, independent of suppression agent.
-In several cases rekindling occurred, as seen by the temperature increase between the two nozzle applications, but all cases the second (room) attack controlled the fire.
-However in most cases rekindling occured as nozzle movement was needed to completely extinguish the fire.
+In several cases, rekindling occurred, as seen by the temperature increase between the two nozzle applications.
+Despite the rekindling, the second attack from the door nozzle controlled the fire in every test.
 
@@
 
-For tests CAF~1 and Water~1, the thermocouple data from TC A2 is shown in Figs.~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively.
+The thermocouple data from TC A2 for tests CAF~1 and Water~1 are shown in Figures~\ref{fig:caf1_tca2} and \ref{fig:water1_tca2}, respectively.
 From the figures, the impact of the first suppression event (hallway nozzle on) is evident from the sharp decline in thermocouple temperatures.
-After the first suppression, there is an increase in temperature at position TC A2 as high temperature gases from a rekindle of the fire flow toward the low pressure structure exit.
-The second suppression (doorway nozzle) further dropped the temperature for both water and CAF.
+After the first suppression, there is an increase in temperature at position TC A2 as high-temperature gases from a rekindle of the fire flow toward the low-pressure structure exit.
+The second suppression (door nozzle) further dropped the temperature for both water and CAF.
 The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression}.
@@
 
-Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
-Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and then the doorway nozzle was activated, respectively.
+Similar to the gas cooling tests, the impact of water and CAF during fire suppression can be analyzed by comparing the temperature differences during the suppression interval at the two thermocouple arrays in the fire room.
+Figures~\ref{fig:fs_hall_a1} and \ref{fig:fs_door_a1} show the temperature difference comparison at thermocouple array A1 for CAF and water after the hallway nozzle was activated and after the door nozzle was activated, respectively.
 
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
 	\label{fig:fs_hall_a1}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
-	\caption{CAFS vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
 	\label{fig:fs_door_a1}
@@
 The R$^2$ value of 0.901 shows a strong fit to the data.
-When the second nozzle is activated (doorway nozzle), note that the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack.
+When the second nozzle (door nozzle) was activated, the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack.
 While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Despite being closer to the nozzles, thermocouple tree A2 shows similar the temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a1}).
-At array A2, Figure~\ref{fig:fs_door_a2}, for doorway nozzle, the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
+Despite being closer to the nozzles, thermocouple tree A2 shows similar temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a1}).
+At array A2 for the door nozzle (see Figure~\ref{fig:fs_door_a2}), the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
 
@@
 
-There were 7 suppression tests conducted in the two-story purpose-built structure.
+There were seven suppression tests conducted in the two-story, purpose-built structure.
 All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling.
 Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the southwest corner of the basement and available ventilation was through the basement double doors and the 1st floor door on the south side of the structure.
+Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the door on the south side of the second story of the structure.
 The fires were intended to replicate room and contents basement fires typically seen within residential structures.
@@
 Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two-story structure.
-The measurement location is on the floor above the fire, at the doorway to the stairwell which connects the floors.
+The measurement location was on the floor above the fire, at the doorway to the stairwell which connects the floors.
 The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
@@
 Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
-Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare-bead thermocouples used in the single-story.
+Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare-bead thermocouples used in the single-story tests.
 The values reported in the table are immediately before and after the application period to assess the application agent, stream, and location on interior conditions.
@@
 
-The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10} - \ref{fig:caf9a_hf}.
-Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7 while Figure~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
-The remainder of the fire suppression test data is included in Appendix~\ref{app:fire_suppression2}.
+The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
+Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7, while Figures~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
+The remainder of the fire suppression test data and results are included in Appendix~\ref{app:fire_suppression2}.
 
@@
 
-The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two the thermocouple arrays in the fire room.
+The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two thermocouple arrays in the fire room.
 Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
-In Figure~\ref{fig:fs_a10}, only Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
+In Figure~\ref{fig:fs_a10}, only tests Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
 
@@
 The R$^2$ value of 0.975 shows a strong fit to the data between water and CAF.
-Similar to the single-story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to Water, but the differences are not substantial.
-Both suppression agents had similar, significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
+Similar to the single-story fire suppression tests, there are some differences in the changes in temperature and heat flux when comparing CAF to water, but the differences are not substantial.
+Both suppression agents had similar significant impact in reducing the high-temperature, high-heat flux environment that existed before suppression.
 
@@
 
-This study focused on two key types of fire experiments; gas cooling and fire suppression.
-In each type of experiment a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates.
-In both types of experiments there were no significant measurable differences between the use of plain water or compressed air foam.
-To expand upon the 2012 and 2013 tests described in~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
+This study focused on two key types of fire experiments: gas cooling and fire suppression.
+In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates.
+In both types of experiments, there were no significant measurable differences between the use of plain water or compressed air foam.
+To expand upon the 2012 and 2013 tests described by Mitchell~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
 One set of experiments used only wood-based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
-A final experimental series used a larger fire room with more ventilation.
-In this final series, another change was made: the nozzle was hand held, and could be moved as needed to effectively extinguish the fire.
-This section will discuss the overall results of the study and provide potential explanations to support them.
+A final experimental series was conducted in a larger fire room with more ventilation.
+In this final series, another change was made: the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
+This section discusses the overall results of the study and provides potential explanations to support them.
 
@@
 Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
-During the planning of the experiments, there were a range of hypotheses regarding the outcome.
+During the planning of the experiments for this project, there were a range of hypotheses regarding potential outcomes.
 Some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF.
-Their position was based on the thought that CAF has injected air.
-Since air is a great insulator, it slows heat transfer and results in less cooling.
+Their position was based on the fact that CAF has injected air.
+Because air is a great insulator, it slows heat transfer and results in less cooling.
 It was their belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
 Other members of the technical panel thought that the bubble structure would provide the same mass flow rate of water but with more surface area.
-The increased surface area would enable faster heat transfer rate and therefore, improve the cooling of the hot gas layer.
+The increased surface area would enable faster heat transfer rate and therefore improve the cooling of the hot gas layer.
 There were also thoughts that the CAFS would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
 
-The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer, without any application of agent to the source of the heat.
-The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer, at least 1.83~m (6 ft) to form.
-During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at positions 1.83~m (6~ft) below the ceiling was attained prior to the beginning of another gas cooling experiment.
+The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer without any application of agent to the source of the heat.
+The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer of at least 1.83~m (6 ft) to form.
+During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at 1.83~m (6~ft) below the ceiling was attained prior to the beginning of gas cooling.
 In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
-Typically the volumetric flow rate of water was 7.57~L/s (120~gpm).
+Typically, the volumetric flow rate of water was 7.57~L/s (120~gpm).
 The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).
@@
 
-When a CAF stream was used it contained 0.3~\% foam concentration by volume with the density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal).
+When a CAF stream was used, it contained 0.3~\% foam concentration by volume.
+The density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal).
 For a 15~s flow time, 0.34~kg (0.75~lb) of concentrate was used.
-In addition to the foam concentrate and water, the CAF stream has compressed air.
-The volume of air injected into the foam solution is 0.03~m$^3$/s (60~cfm).
-The density of the compressed air is in the range of 100 to 150~psig, which would be between 8.9~kg/m$^3$ (0.6~lb/ft$^3$) and 12.8~kg/m$^3$ (0.8~lb/ft$^3$).
+In addition to the foam concentrate and water, the CAF stream contained compressed air injected into the foam solution at a rate of 0.03~m$^3$/s (60~cfm).
+The density of the compressed air is in the range of 100 to 150~psig, which translates to a range between 8.9~kg/m$^3$ (0.6~lb/ft$^3$) and 12.8~kg/m$^3$ (0.8~lb/ft$^3$).
 Therefore, a 15~s CAF flow would contain approximately 4.0~kg (8.8~lb) to 9.5~kg (21.0~lb) of air.
-Comparing the mass flows, and using the air mass based on the higher pressure, water still makes up more than 90~\% of the mass of the CAF stream.
+Comparing the mass flows and using the air mass based on the higher pressure, water still makes up more than 90~\% of the mass of the CAF stream.
 
 The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$ 15~\% (see Section~\ref{subsec:Uncertainty}).
-In other words, for a difference between one measurement and another measurement to be considered significantly different, the difference would have to be greater by more than $\pm$ 15~\%.
-If the difference between two measurements was $\pm$ 15~\% or less, the results are considered to be similar.
+So, for the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$ 15~\%.
+If the difference between two measurements was $\pm$ 15~\% or less, the results are considered similar.
 That said, the estimated uncertainty is based on previous studies where suppression with a water based agent was included.
 
-As pointed out in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results because that position had the least impact of agents hitting and cooling the thermocouples themselves.
+As mentioned in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results because due to the array's position, it was impacted the least by agents hitting and cooling the thermocouples themselves.
 Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
 Air filled bubbles in the CAF stream had no discernible impact, either positive or negative, in the gas cooling experiments.
-At the same time there was no measurable negative effect of the air bubbles with regard to gas cooling.
-
-The data from the thermocouples in TC Array 2, provide a sense of the impact of a combination of surface cooling and gas cooling.
-For example, when the nozzle was in the ``middle position,'' the straight or solid hose streams would impact near the middle of the ceiling of the room and they would create a fan pattern across the ceiling that would cause the majority of the water to impact the location of TC Array 2 and the adjacent walls.
+At the same time, there was no measurable negative effect of the air bubbles with regard to gas cooling.
+
+The data from the thermocouples in TC Array 2 provide a sense of the impact of a combination of surface cooling and gas cooling.
+For example, when the nozzle was in the ``middle'' position, the straight or solid hose streams impacted the room's ceiling near the middle and created a fan pattern across the ceiling that caused the majority of the water to impact the location of TC Array 2 and the adjacent walls.
 In this location, the data tended to favor water.
-However this did not represent gas cooling.
+However, this did not represent gas cooling.
 Rather, this represented some of the water or CAF hitting the thermocouples and cooling the surrounding gases.
-As a result, temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} respectively.
+As a result, temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in Figures~\ref{fig:CAFS_Water_A2_mid} and \ref{fig:CAFS_Water_A3_mid}, respectively.
 
 TC Array 1 had the widest spread of temperature change.
-Depending on the nozzle configuration, there were tests where the Array 1 thermocouples were directly impacted by water or CAF and other tests where there was no impact.
+Depending on the nozzle configuration, there were tests where the thermocouples in TC Array 1 were directly impacted by water or CAF and other tests where there was no impact.
 Examination of the spray density figures in Appendix~\ref{app:spray_bb}, provides the range of agent collected in the bucket where TC Array 1 was located.
-In many cases such as CAF Straight Stream Mid, the foam solution collected was near zero.
-In other cases such as CAF Fog Mid, the amount of foam solution collected was more than 3~kg.
+In many cases, such as the test CAF Straight Stream Mid, the amount of foam solution collected was near zero.
+In other cases, such as the test CAF Fog Mid, the amount of foam solution collected was more than 3~kg (6.6~lb).
 Similar variations occurred with water.
@@
 
-The data from this test series does not support the premise of firefighters being injured during an interior fire fighting operation with CAF, since CAF provided cooling similar to that of the equivalent flowrate of plain water.
+The data and results from this test series do not support the premise of firefighters being injured during an interior fire fighting operation with CAF because CAF provided cooling similar to that of the equivalent flow rate of plain water.
 
@@
 
-Currently, the fire service uses fire flow formulas to estimate the flow rate of water needed to control a structure fire.
-The formulas will be presented below and then the results from the studies presented above will be compared with the calculated fire flows.
+Currently, the fire service uses ``fire flow'' formulas to estimate the flow rate of water needed to control a structure fire.
+The formulas are presented below and the results from the experiments described in this report will be compared with the calculated fire flows.
 
 \subsection{Iowa State University Fire Flow Formula (1963)}
-The Iowa Formula for determining the required fire flow rate for a given structure was developed, by Keith Royer and Bill Nelson, based on theoretical heat absorption capabilities of water.
-The required fire flow rate, ($\dot{V}$), in gpm is equal to the volume ($V$) of the fire compartment (in cubic feet) divided by 100:
+The Iowa Formula for determining the required fire flow rate for a given structure was developed by Keith Royer and Bill Nelson and is based on theoretical heat absorption capabilities of water.
+The required fire flow rate ($\dot{V}$) in gpm is equal to the volume ($V$) of the fire compartment in cubic feet divided by 100:
+
 \begin{equation}\label{eq:isu_form}
@@
 \end{equation}
-Due to inefficiencies in applying the water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
-Applying the formula based on floor area yields an application density of 3.3~Lpm/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~Lpm/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
-The fire rooms in these experiments ranged in floor area from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
-Therefore the required flow rate for the fire room in the single-story structure based on the Iowa State University formula would be approximately 87~Lpm (23~gpm).
-The required flow rate for the fire room in the lower level of the two-story structure would be approximately 168~Lpm (44~gpm).
-During the experiments the flow rate was approximately, 454~Lpm (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
+
+Due to inefficiencies in the application of water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
+Applying the formula based on floor area yields an application density of 3.3~l/min/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~l/min/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
+The fire room compartment volumes in these experiments ranged from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
+Therefore, the required flow rate for the fire room in the single-story structure based on the Iowa State University formula was approximately 87~l/min (23~gpm), and the required flow rate for the fire room in the lower level of the two-story structure was approximately 168~l/min (44~gpm).
+During the experiments, the flow rate was approximately 454~l/min (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
 The fact that all of the fires were quickly controlled during the experiments is consistent with this methodology.
@@
 \subsection{National Fire Academy (1981)}
-The National Fire Academy (NFA) developed a formula based on a study of fire flows, which were successful in controlling a large number of working fires~\cite{Klaene:1}.
-This formula sets the required fire flow, ($\dot{V}$), in gpm equal to the floor area ($A$) (in square feet) divided by 3.
+The National Fire Academy (NFA) developed a formula based on a study of fire flows that have been successful in controlling a large number of working fires~\cite{Klaene:1}.
+This formula sets the required fire flow ($\dot{V}$) in gpm equal to the floor area ($A$) in square feet divided by 3.
+
 \begin{equation}\label{eq:nfa_form}
@@
 
-The fire rooms in these experiments ranged in floor area from approximately 27~$m^2$ (291~$ft^2$) to 51.4~$m^2$ (553~$ft^2$).
-Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 369~Lpm (97~gpm).
-The required flow rate for the fire room in the lower level of the two-story would be approximately 700~Lpm (184~gpm).
-Comparing the hose stream flow rates to the NFA Formula requirements indicates that 454~Lpm (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~Lpm (184~gpm) for the large fire compartment in the two-story structure.
-This is not consistent with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~Lpm (120~gpm).
-
-Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a re-newed interest in controlling the air available to a ventilation limited compartment fire.
+The fire rooms in these experiments ranged in floor area from approximately 27~m$^2$ (291~ft$^2$) to 51.4~m$^2$ (553~ft$^2$).
+Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 369~l/min (97~gpm).
+The required flow rate for the fire room in the lower level of the two-story would be approximately 700~l/min (184~gpm).
+Comparing the hose stream flow rates to the NFA Formula requirements indicates that 454~l/min (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~l/min (184~gpm) for the large fire compartment in the two-story structure.
+This is not consistent with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~l/min (120~gpm).
+
+Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a renewed interest in controlling the air available to a ventilation limited compartment fire.
 Limiting the air (oxygen) available for combustion is one means of limiting the heat release rate.
@@
 Both of the formulas listed above do not explicitly account for the ventilation of the fire structure, only the size of the fire structure.
-Further the most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
+Further, the most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
 This experience was likely from fires that occurred in the 1960's and the 1970's.
 It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and with higher heat release rates than the natural fuels that filled the homes in the 1940's and 1950's.
-The change of materials in homes began in the 1960's and continues through to present day.
-It was unlikely, however, that this change was factored in to the NFA Formula.
-
-Shortly after the NFA equation was issued, another Federal agency, The National Bureau of Standards (now NIST) released a finding about the relationship of oxygen to the heat release rate of a fire.
+The change of materials in homes began in the 1960's and has continued to present day~\cite{Kerber:2}.
+It was unlikely, however, that this change was factored into the NFA formula.
+
+Shortly after the NFA equation was issued, another federal agency, the National Bureau of Standards (now NIST) released a finding about the relationship of oxygen to the heat release rate of a fire~\cite{Babrauskas:3}.
 NIST found that for many fuels, approximately 13.1~MJ of heat are generated for every kilogram of oxygen consumed during the combustion.
-This relationship then led to simple algorithms that addressed the how much oxygen can flow through an opening with a theoretical heat release rate that assumes stoichiometric conditions (100~\% efficient burning where all of the fuel and the oxygen is consumed).
+This relationship led to simple algorithms that addressed the amount of oxygen that can flow through an opening with a theoretical heat release rate that assumes stoichiometric conditions (100~\% efficient burning where all of the fuel and the oxygen is consumed).
 
@@
 If the ventilation was increased to allow additional oxygen to be supplied to the fuel gases in the fire compartment, the heat release rate of the fire would have increased.
-There are simple formulas which may provide some insight here, although for full disclosure this simple algorithm has not been validated with the geometry that were used in these experiments.
+There are simple formulas which may provide some insight here, although this simple algorithm has not been validated with the geometries that were used in the experiments described in this report.
 The purpose here is to get a sense of the amount of heat energy that the hose streams needed to overcome.
-This algorithm, like the NFA formula has never been validated for this application.
+This algorithm, like the NFA formula, has never been validated for this application.
 
@@
 
-In Eq.~\ref{eq:HRRSto_item}, the maximum heat release rate $\dot{Q}_{stoichiometric}$, in kW, is based on airflow through the area of the opening, $A_0$ in m$^2$ and the squre root of the height of the opening, $\sqrt{H_0}$, in ${m}^{1/2}$.
-
-Following Eq.~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room, which is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high, could support a heat release rate of approximately 4~MW assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
-For double the width of the open doorway (the doorway to the lower level of the two-story structure) the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
+In Equation~\ref{eq:HRRSto_item}, the maximum heat release rate ($\dot{Q}_{stoichiometric}$) in kW is based on airflow through the area of the opening ($A_0$) in square meters and the square root of the height of the opening ($H_0$) in meters.
+
+Following Equation~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room that is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high could support a heat release rate of approximately 4~MW, assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
+For twice the width of the open doorway (the doorway on the lower level of the two-story structure), the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
 This does not account for flames burning outside of the compartment, which were frequently observed during testing.
 
-In the single-story, there was an additional window opening in some of the experiments which added ventilation to the room.
-In the two-story, there was an another open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the first floor and out of the structure.
-Even with the additional ventilation in both cases, the conditions in the fire compartment remained fuel rich as the flames extended out of the openings from the structures.
-It would seem then, that the heat release rate inside the compartment would not have exceeded 4~MW for the one story or 8~MW for the two-story structure.
-
-Earlier it was noted that the latent heat of vaporization of water is 2255~kJ/kg or approximately 2.3~MJ/kg.
-Assuming ideal heat transfer, the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the one story and 3.5~kg/s for the two-story.
+In the single-story structure, there was an additional window opening in some of the experiments which added ventilation to the room.
+In the two-story structure, there was an additional open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the second-story floor, and out of the structure.
+Even with the additional ventilation in both cases, the conditions in the fire compartment remained fuel rich as the flames extended out of the structure's openings.
+Based on Equation~\ref{eq:HRRSto_item}, that would indicate that the heat release rate inside the compartment did not exceed 4~MW for the single-story structure or 8~MW for the two-story structure.
+
+Earlier, it was noted that the latent heat of vaporization of water is 2255~kJ/kg, or approximately 2.3~MJ/kg.
+Assuming ideal heat transfer, the mass flow rate of water needed to absorb the heat being generated inside the fire compartment would be approximately 1.8~kg/s for the single-story and 3.5~kg/s for the two-story.
 In these experiments, the mass flow rate of water was 7.57~kg/s (16.7~lb/s), which is theoretically twice what was needed to absorb the heat in the fire compartment of the larger fire in the lower level of the two-story structure.
-Again this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
-However, it demonstrates that for a residential scale room (in this study up to to 51.4~$m^2$ (553~$ft^2$)) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water was adequate to quickly suppress the fire in the compartment.
-
-In all of the suppression experiments, the fire was controlled with total flow of 227~L (60~gal) or less of agent.
-During the course of the suppression experiments the fuel packages were modified to incorporate more wood-based fuels.
-During the planning of the experiments, some of the technical panel members felt that the synthetic fuels, such as polyurethane foam, burned mostly at the surface and therefore they were easily cooled and suppressed.
-Wood-based fuels, on the otherhand, develop a char layer and therefore the burning would be ``deep seated'', which might provide a more significant suppression challenge.
-Since the Class A foam solution has a reduced surface tension, that could allow the solution to penetrate and cool the burning wood-based fuels better, it was thought that with more exposed, burning wood surface, the better the opportunity for CAF to demonstrate a difference.
-As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and oriented strand board.
+Again, this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
+However, it demonstrates that for a residential scale room (in this study up to to 51.4~m$^2$ (553~ft$^2$)) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water was adequate to quickly suppress the fire in the compartment.
+
+In all the suppression experiments, the fire was controlled with a total flow of 227~L (60~gal) or less of agent.
+During the course of the suppression experiments, the fuel packages were modified to incorporate more wood-based fuels.
+During the planning of the experiments, some of the technical panel members felt that synthetic fuels, such as polyurethane foam, burned mostly at the surface and were therefore easily cooled and suppressed.
+Wood-based fuels, however, develop a char layer.
+Therefore the burning of wood-based fuels would be ``deep seated'', which might provide a more significant suppression challenge.
+The reduced surface tension of Class A foam solution could allow the solution to better penetrate and cool the burning wood-based fuels.
+It was thought that with more exposed burning wood surfaces in the fuel load, CAF would have a better the opportunity to demonstrate a difference in suppression.
+As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and OSB.
 The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
@@
 There was also another variable that would be introduced: a firefighter controlling the nozzle.
-Recall that in the single-story experiments, fixed position monitor nozzle was used in a fixed position.
+Recall that in the single-story experiments, a monitor nozzle was used in a fixed position.
 As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
@@
 
-The fire fighting crew was from the MCFRS and all had been trained in the use of CAF and had experience using CAF.
-The firefighter on the nozzle was the same for all of the experiments conducted in the two-story structure.
-The firefighter used the reach of the hosestream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
+The fire fighting crew was from the MCFRS and every member in the crew had been trained in the use of and had experience with using CAF.
+The firefighter on the nozzle was the same for all the experiments conducted in the two-story structure.
+The firefighter used the reach of the hose stream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
 Then, the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
@@
 
-During the workshop~\cite{Grant:2011}, there were discussions that CAF could suppress, or knockdown, a fire three to five times faster than water.
-During the course of this study there were no significant differences demonstrated between CAF and water for use in interior structural fire fighting on a residential scale.
-Going back to the premise of the study, preventing firefighters from being injured during an interior fire fighting operations.
-There is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
+During the workshop conducted for this project~\cite{Grant:2011}, there were discussions that CAF could suppress, or knockdown, a fire three to five times faster than water.
+During the course of this study, there were no significant differences demonstrated between CAF and water for use in interior structural fire fighting on a residential scale.
+Going back to the premise of the study, preventing firefighters from being injured during interior fire fighting operations with CAF, there is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
 
@@
 Information from actual incidents in the field shaped this study.
-From the gas cooling and suppression perspective, the data does not indicate that the use of CAF would result in a higher thermal hazard.
+From the gas cooling and suppression perspective, the results do not indicate that the use of CAF would result in a higher thermal hazard.
 However, there are other issues like nozzle reaction force and flow separation which have been covered in the Cal Poly fire ground studies that can be addressed in training~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
@@
 Currently the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
-A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how that can impact the flow of gases within the structure.
-Based on the results of this study, it would seem that training and understanding the impact of nozzle movement are ways to look for a more effective use of water.
+A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how such choices can impact the flow of gases within the structure.
+Based on the results of this study, it appears that training and understanding the impact of nozzle movement are ways to look for a more effective use of water.
 
@@
 
-Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+Full-scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
 The experimental configurations were designed to be representative of residential fire scenarios.
@@
 This same department also experienced injuries to firefighters while using CAF during interior fire fighting operations in residential structures.
-This study is composed of three types of experiments; spray density, gas cooling and fire suppression.
-In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar types with similar mass flow rates of water.
+This study was composed of three types of experiments: spray density, gas cooling, and fire suppression.
+In each type of experiment, a comparison was conducted between plain water and CAF being discharged from nozzles of similar types with similar mass flow rates of water.
 The flow rate for each water experiment was 120~gpm.
-For the CAF experiments, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate was added to the water flow.
-
-Thirty-two spray density tests were conducted to determine where the agent would land within a compartment based on various nozzle patterns and locations.
+For the CAF experiments, 60~cfm of air and a 0.3~\% flow of Class A foam concentrate were added to the water flow.
+
+Thirty-two spray density tests were conducted to determine where the suppression agent would land within a compartment based on various nozzle patterns and locations.
 The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
-The purpose of these spray density tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
+The purpose of these spray density tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests by gaining an understanding of the water distribution throughout the structures.
 This report provides a complete set of the spray density results in graphic form.
@@
 Suppression agents were not applied to the fire in the burn room.
-In this report, an aggregate analysis is made to examine differences due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
+In this report, an aggregate analysis was made to examine differences due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
 No significant differences were found in the gas cooling capabilities of the two agents.
 A more detailed analysis of the individual experiments was conducted by Mitchell of Cal Poly~\cite{Mitchell:1}.
-The conclusion of both analyses are in agreement.
+The conclusion of both analyses is in agreement.
 The full gas cooling data set can be found in the Mitchell report.
@@
 There were two different geometries used for the fire suppression experiments.
-Twelve of the suppression experiments were conducted in a single-story structure with an entry hallway that led to a fire compartment with a floor area of 27~$m^2$ (291~$ft^2$).
+Twelve of the suppression experiments were conducted in a single-story structure with an entry hallway that led to a fire compartment with a floor area of 27~m$^2$ (291~ft$^2$).
 Within this structure, two different types of fuel loads were used.
@@
 The other fuel load used only wood-based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
-In the experiments conducted in the one story building, a fixed nozzle was flowed from the hallway for approximately 15~s and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
+In the experiments conducted in the single-story building, a fixed nozzle was flowed from the hallway for approximately 15~s, and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
 
 Seven of the suppression experiments were conducted in a two-story structure.
-The fire compartment was the full lower level of the structure and it had an open floor plan with an area of 51.4~$m^2$ (553~$ft^2$).
-At one end of the room was an open doorway, 1.8~m (6~ft) wide by
-2~m (6.7~ft) high the led to a stairwell.
+The fire compartment was the full lower level of the structure, and it had an open floor plan with an area of 51.4~m$^2$ (553~ft$^2$).
+At one end of the room was an open doorway that was 1.8~m (6~ft) wide and 2~m (6.7~ft) high and led to a stairwell.
 A manual hose stream application was made from outside the doorway on the lower level.
@@
 The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
-In each case the initial knockdown of the fire required 60~gal of agent or less.
+In each case, the initial knockdown of the fire required 60~gal of agent or less.
 
@@
 Under these test conditions both agents were effective.
-This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle, relative to plain water.
-
-This study conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle relative to plain water.
+
+This study conducted by NIST was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
 This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
@@
 
-The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
+The NIST team would like to thank Casey Grant from the Fire Protection Research Foundation and the members of the project technical panel, especially John Culbertson, Director, Montana State University Fire Services Training School and Homer Robertson, Deputy Chief, Fort Worth Fire Department.
 

### 2016-08-03 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor changes to reports, updated West event times in propane gas burner report

@@
 \vspace*{2\baselineskip}
-July 2016}
+August 2016}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (July 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\

### 2016-08-03 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to reports, updated West event times in propane gas burner report

@@
 The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum velocity of 2.6~m/s (5.8~mph) and maximum air flow rate of approximately 4.2~m$^3$/s (9000~cfm), followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
-It was discovered that the straight stream only caused air movement through the structure when it was applied in a moving pattern.
+The data were consistent with a straight stream only causing air movement through the structure when it was applied in a moving pattern.
 Furthermore, there were no statistically significant differences in the average measured air velocity between the clockwise and counterclockwise nozzle movement patterns.
@@
 NIST has conducted a significant amount of research examining how ventilation affects the growth and spread of fire within structures and how the air flow to the fire may be controlled to limit or delay the growth of the fire~\cite{madrzykowski2009fire,kerber2009fire}.
-The studies have resulted in guidance to the fire service regarding ventilation tactics.
+The studies have provided insight for the fire service regarding ventilation tactics.
 However, ventilation tactics alone will not extinguish the fire; fire suppression with hose streams is also needed.
@@
 Most combination nozzles contain an adjustable tip that can be rotated to produce different stream patterns.
-The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}; a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}; and a wide fog stream produces an angle between 45\SI{}{\degree} and 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF}.
+The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the centerline of the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}; a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}; and a wide fog stream produces an angle between 45\SI{}{\degree} and 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF}.
 Increasing the angle of the stream allows for a larger area to be covered by the water spray.
@@
 The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track and were lined with 13~mm (0.5~in) thick cement board.
-The walls were composed of 16~mm (0.63~in) Type X gypsum board.
+A layer of 16~mm (0.63~in) thick Type X gypsum board covered the cement board.
 Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 Length measurements such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement were made with a hand held laser measurement device which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
 Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array.
@@
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm0.14$ to $\pm0.22$ for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm18$\%.
+The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm18$~\%.
 
@@
 Water flow rate was measured with a pressure and flow meter combination shown in Fig.~\ref{fig:flow_meter}.
-The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
-The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a $\pm5$\% calibration expanded uncertainty for the flow sensor and $\pm3$\% for the pressure sensor~\cite{Akron:2009}.
+The meter consisted of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0 to 4.1~MPa (600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~lpm (1250~gpm).
+The pressure transducer and paddlewheel were both connected to the battery operated control box where the pressure transducer voltage was converted to a pressure and the paddlewheel pulse count was converted to a volumetric flow rate.
+The manufacturer reports a $\pm5$~\% calibration expanded uncertainty for the flow sensor and $\pm3$~\% for the pressure sensor~\cite{Akron:2009}.
 The pressure transducer was calibrated with a known analog pressure gauge.
 The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate.
-The total expanded uncertainty was estimated at $\pm10$\%.
+The total expanded uncertainty was estimated at $\pm10$~\%.
 
@@
 \footnotesize
-\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for each monitor experiment}
+\caption{Average gas velocity and airflow rate [$\pm 18$~\%] through interior doorway when flow path was fully established for each monitor experiment}
 \begin{tabular}{lccccccccc}
@@
 &	 	m$^3$/s	&	 -0.6 $\pm0.1$   	& &  1.5 $\pm0.3$	&	 1.5 $\pm0.3$  	& &  1.1 $\pm0.2$   & 	 1.1 $\pm0.2$ \\
-& 	&	(cfm)	& 	(-1235 $\pm222$)	& & (3082 $\pm555$) &	(3272 $\pm589$) & & (2397 $\pm432$) &	(2413 $\pm434$) 
+& 	&	(cfm)	& 	(-1250 $\pm200$)	& & (3100 $\pm550$) &	(3250 $\pm600$) & & (2400 $\pm450$) &	(2400 $\pm450$) 
 \\~\\
@@
 &		m$^3$/s &	 2.1 $\pm0.4$   	& &  1.6 $\pm0.3$	&	 2.4 $\pm0.4$  	& &  1.3 $\pm0.2$   & 	 1.2 $\pm0.2$ \\
-& 	&	(cfm)	&	(4483 $\pm807$)		& & (3335 $\pm600$) &	(4980 $\pm896$) & & (2726 $\pm491$) &	(2631 $\pm474$)
+& 	&	(cfm)	&	(4500 $\pm800$)		& & (3350 $\pm600$) &	(5000 $\pm900$) & & (2750 $\pm500$) &	(2650 $\pm450$)
 \\~\\
@@
 &	 	m$^3$/s	&	 4.6 $\pm0.8$   	& &  2.1 $\pm0.4$	&	 2.3 $\pm0.4$  	& &  2.0 $\pm0.4$   & 	 1.3 $\pm0.2$ \\
-& 	&	(cfm)	& 	(9812 $\pm1766$)	& & (4385 $\pm789$) &	(4784 $\pm861$) & & (4183 $\pm753$) &	(2738 $\pm493$)
+& 	&	(cfm)	& 	(9800 $\pm1750$)	& & (4400 $\pm800$) &	(4800 $\pm850$) & & (4200 $\pm750$) &	(2750 $\pm500$)
 \\
@@
 &		m$^3$/s &	 2.9 $\pm0.5$  		& 	\multicolumn{2}{c}{ 3.2 $\pm0.6$}		& \multicolumn{4}{c}{} \\
-& 	&	(cfm)	&	(6130 $\pm1103$) 	&	\multicolumn{2}{c}{(6884 $\pm1239$)}	& \multicolumn{4}{c}{}
+& 	&	(cfm)	&	(6150 $\pm1100$) 	&	\multicolumn{2}{c}{(6900 $\pm1250$)}	& \multicolumn{4}{c}{}
 \\~\\
@@
 &		m$^3$/s &	 3.0 $\pm0.5$		& 	\multicolumn{2}{c}{ 3.5 $\pm0.6$} 		& \multicolumn{4}{c}{} \\
-& 	&	(cfm)	&	(6253 $\pm1126$) 	&	\multicolumn{2}{c}{(7466 $\pm1344$)} 	& \multicolumn{4}{c}{}
+& 	&	(cfm)	&	(6250 $\pm1150$) 	&	\multicolumn{2}{c}{(7450 $\pm1350$)} 	& \multicolumn{4}{c}{}
 \\
@@
 \begin{table}[!ht]
-\caption{Average gas velocity and airflow rate [$\pm 18$\%] through interior doorway when flow path was fully established for Test~5}
+\caption{Average gas velocity and airflow rate [$\pm 18$~\%] through interior doorway when flow path was fully established for Test~5}
 \begin{tabular}{lccccc}
@@
 \begin{table}[!ht]
-\caption{Average gas velocity and airflow rate [$\pm18$\%] through interior doorway when flow path was fully established for Tests~6 and 7}
+\caption{Average gas velocity and airflow rate [$\pm18$~\%] through interior doorway when flow path was fully established for Tests~6 and 7}
 \begin{tabular}{lcccccc}
@@
 
-Overall, the water flow experiments discussed in this report reveal that hose streams can affect air movement within a structure.
+For this limited series of water flow experiments, the data demonstrate that for these flows and configurations, hose streams can affect air movement within a structure.
 The type of hose stream used and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure.

### 2016-08-03 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to reports, updated West event times in propane gas burner report

@@
 	~(1)~  All burners on 						&   0	  			&	 0			\\
-	~(2)~  2nd floor west double door opened 	&   127		  		&    116		\\
-	~(3)~  1st floor west double door opened 	&	247		  		&    238 	 	\\
-	~(4)~  1st floor east double door opened 	&   382			  	&    356		\\
-	~(5)~  2nd floor east double door opened	&   517			  	&    484		\\
-	~(6)~  PPV fan on 							&   587			  	&    596		\\
-	~(7)~  PPV fan off              			&   731			  	&    746		\\
-	~(8)~  All burners off 						&   757			  	&    776		\\
-	~(9)~  2nd floor south exterior door opened &   836			  	&    836		\\
-	(10) PPV fan on 	 						&   997			  	&    926		\\
-	(11) 2nd floor south exterior door closed   &   1113		  	&    N/A		\\
+	~(2)~  2nd floor west double door opened 	&   195		  		&    133		\\
+	~(3)~  1st floor west double door opened 	&	315		  		&    255 	 	\\
+	~(4)~  1st floor east double door opened 	&   450			  	&    374		\\
+	~(5)~  2nd floor east double door opened	&   586			  	&    501		\\
+	~(6)~  PPV fan on 							&   653			  	&    614		\\
+	~(7)~  PPV fan off              			&   800			  	&    764		\\
+	~(8)~  All burners off 						&   830			  	&    797		\\
+	~(9)~  2nd floor south exterior door opened &   899			  	&    850		\\
+	(10) PPV fan on 	 						&   1066		  	&    943		\\
+	(11) 2nd floor south exterior door closed   &   1179		  	&    N/A		\\
 	\bottomrule
@@
 	~(1)~ All burners on 						&   0		  		&	 0			\\
-	~(2)~ Interior stairwell door opened 		&   120		  		&    110		\\
-	~(3)~ 1st floor west double door opened 	&	240		  		&    241 	 	\\
-	~(4)~ 2nd floor west double door opened 	&   360			  	&    350		\\
-	~(5)~ 2nd floor south exterior door opened	&   480			  	&    470		\\
-	~(6)~ PPV fan on 							&   600			  	&    590 		\\
-	~(7)~ All burners off 						&   720 		  	&    710		\\
-	~(8)~ 2nd floor east double door opened 	&   855			  	&    830		\\
+	~(2)~ Interior stairwell door opened 		&   120		  		&    114		\\
+	~(3)~ 1st floor west double door opened 	&	240		  		&    245 	 	\\
+	~(4)~ 2nd floor west double door opened 	&   360			  	&    354		\\
+	~(5)~ 2nd floor south exterior door opened	&   480			  	&    474		\\
+	~(6)~ PPV fan on 							&   600			  	&    595 		\\
+	~(7)~ All burners off 						&   720 		  	&    715		\\
+	~(8)~ 2nd floor east double door opened 	&   855			  	&    N/A		\\
+	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 962		\\
 	\bottomrule

### 2016-08-05 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated times in the event tables of gas burner report

@@
 	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
-	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
-	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
-	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
-	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
-	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
-	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
-	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
-	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
-	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
+	~(2)~ Middle burner on 				&   182			  &		181			&		178		  \\
+	~(3)~ Center burner on 				&   362			  &	   	361			&	   	359		  \\
+	~(4)~ West double door opened 		&   417			  &    	417			&	   	415		  \\
+	~(5)~ East double door opened 		&   538			  &    	537			&	   	535		  \\
+	~(6)~ South exterior door opened 	&   606			  &    	598			&	   	597		  \\
+	~(7)~ Center burner off				&   720			  &    	778			&	   	778		  \\
+	~(8)~ Middle burner off				&   841			  &    	898			&	   	897		  \\
+	~(9)~ Corner burner off				&   962			  &    	1018		&	   	1019	  \\
+	(10) PPV fan on 					& 	1254		  &    	1316		&  	   	1486	  \\	
 	\bottomrule
@@
 	\midrule
-	~(1)~ All burners on 				& 	0			  &	   1230			&	   2430		\\
-	~(2)~ Roof vent opened 				&   128			  &    1320			&	   2520		\\
-	~(3)~ West double door opened 		&	153			  &	   1410	 		&	   2610 	\\
-	~(4)~ East double door opened 		&   333			  &    1500			&	   2700		\\
-	~(5)~ Roof vent closed		 		&   420			  &    1695			&	   2833		\\
-	~(6)~ All burners off 				&   550			  &    1815			&	   2970		\\
-	~(7)~ Roof vent opened				& 	695 		  &	   1860			&	   3060		\\
-	~(8)~ East double door closed		& 	1127 		  &	   2288			&	   N/A		\\
-	~(9)~ West double door closed		& 	1140 		  &	   2305			&	   N/A		\\
-	(10) Roof vent closed		 		&   1155		  &    2364			&	   N/A		\\
+	~(1)~ All burners on 				& 	0			  &	   1225			&	   2426		\\
+	~(2)~ Roof vent opened 				&   155			  &    1346			&	   2546		\\
+	~(3)~ West double door opened 		&	176			  &	   1431	 		&	   2631 	\\
+	~(4)~ East double door opened 		&   361			  &    1531			&	   2731		\\
+	~(5)~ Roof vent closed		 		&   446			  &    1724			&	   2852		\\
+	~(6)~ All burners off 				&   577			  &    1840			&	   2998		\\
+	~(7)~ Roof vent opened				& 	722 		  &	   1887			&	   3087		\\
+	~(8)~ East double door closed		& 	1149 		  &	   2311			&	   N/A		\\
+	~(9)~ West double door closed		& 	1165 		  &	   2331			&	   N/A		\\
+	(10) Roof vent closed		 		&   1180		  &    2388			&	   N/A		\\
 	\bottomrule
@@
 	\midrule
-	~(1)~ All burners on 				&	0				&	570				&	1080			\\
-	~(2)~ West double door opened 		&	90				&   660				&	1170			\\
-	~(3)~ Roof vent opened 		    	&	180				&	720 			& 	1260 			\\
-	~(4)~ All burners off 				&	300				&   840				&	1350			\\
-	~(5)~ East double door opened		&	345				&   885				&	1420			\\
-	~(6)~ Roof vent closed 				&	470				&   1016			&	N/A				\\
-	~(7)~ East double door closed		&	497 			&	986				&	N/A 			\\
-	~(8)~  West double door closed		&	513 			&	999				&	N/A				\\
+	~(1)~ All burners on 				&	0				&	566				&	1077			\\
+	~(2)~ West double door opened 		&	115				&   685				&	1195			\\
+	~(3)~ Roof vent opened 		    	&	208				&	748 			& 	1288 			\\
+	~(4)~ All burners off 				&	327				&   868				&	1388			\\
+	~(5)~ East double door opened		&	371				&   911				&	1446			\\
+	~(6)~ Roof vent closed 				&	495				&   1041			&	N/A				\\
+	~(7)~ East double door closed		&	524 			&	1016			&	N/A 			\\
+	~(8)~  West double door closed		&	539 			&	1026			&	N/A				\\
 	\bottomrule
@@
 	(10) PPV fan on 	 						&   1066		  	&    943		\\
-	(11) 2nd floor south exterior door closed   &   1179		  	&    N/A		\\
+	(11) 2nd floor south exterior door closed   &   1176		  	&    N/A		\\
 	\bottomrule

### 2016-08-08 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
update Hosestream report from JH comments

@@
 ESTC \> Delaware County Emergency Services Training Center \\
+NF \> Narrow Fog Stream\\
 NIST \> National Institute of Standards and Technology \\
+SB \> Smooth Bore Stream\\
+SS \> Straight Stream \\
 UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute
+WF \> Wide Fog Stream \\
 \end{tabbing}
@@
 Seven series of experiments were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
-The experiments studied four different hose streams: a straight stream, narrow fog stream, and a wide fog stream from a combination nozzle and a solid stream from a smooth bore nozzle.
+The experiments studied four different hose streams: a straight stream, narrow fog stream, a wide fog stream from a combination nozzle, and a solid stream from a smooth bore nozzle.
 The streams were applied from a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
@@
 The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}.
 Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
@@
 \label{sec:uncertainty}
-There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity reported here.
+There are different components of uncertainty in the length, differential pressure, flow rate, and gas velocity presented in this report.
 Uncertainties are grouped into two categories according to the method used to estimate them.
@@
 \label{sec:exp_procedure}
-Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle with a 1~in tip in a solid stream pattern.
+Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle with a 1~in tip with a solid stream pattern.
 Specific doors were opened or closed before and/or during the tests to change the ventilation within the structure.
@@
 In the graphs, an error bar will represent the estimated uncertainty of the measurement.
-In the tables, the uncertainty will be included in the caption of the table as a percentage enclosed in brackets.
+In the tables, the uncertainty will be included in the caption of each table as a percentage enclosed in brackets.
 
@@
 \midrule
-\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
+\multirow{5}{*}{\textit{\small Straight (SS)}} & \multirow{2}{*}{Velocity}
 & 		 m/s 	&	 -0.3 $\pm0.1$		& &	 0.9 $\pm0.2$ 	&	 0.9 $\pm0.2$	& &	 0.7 $\pm0.1$	&	 0.7 $\pm0.1$ \\
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Narrow} \\ \textit{\small Fog} \end{tabular}} & \multirow{2}{*}{Velocity}
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Narrow} \\ \textit{\small Fog (NF)} \end{tabular}} & \multirow{2}{*}{Velocity}
 & 		 m/s   	&    1.1 $\pm0.2$  		& &	 1.0 $\pm0.2$	&	 1.4 $\pm0.3$  	& &   0.8 $\pm0.1$  & 	 0.8 $\pm0.1$ \\
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Wide} \\ \textit{\small Fog} \end{tabular}} & 
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Wide} \\ \textit{\small Fog (WF)} \end{tabular}} & 
 \multirow{2}{*}{Velocity}
@@
 \midrule
-\multirow{5}{*}{\textit{\small Straight}} & \multirow{2}{*}{Velocity}
+\multirow{5}{*}{\textit{\small Straight (SS)}} & \multirow{2}{*}{Velocity}
 & 		 m/s   	&	 1.8 $\pm0.3$		&	\multicolumn{2}{c}{ 2.0 $\pm0.4$}		& \multicolumn{4}{c}{} \\
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Smooth} \\ \textit{\small Bore} \end{tabular}} &
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{\small Smooth} \\ \textit{\small Bore (SB)} \end{tabular}} &
 \multirow{2}{*}{Velocity}
@@
 Additionally, a fourth experimental series using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
-The streams were compared for six different 60 seconds periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
+The streams were compared for six different 60 second periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
 The results from the four monitor test series suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.

### 2016-08-09 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Corrected event times for gas burner experiments

--- 2016-08-03 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
@@
 	~(1)~ Corner burner on 				& 	0		  	  &	 	0			&		0		  \\
-	~(2)~ Middle burner on 				&   180			  &		180			&		180		  \\
-	~(3)~ Center burner on 				&   360			  &	   	360			&	   	360		  \\
-	~(4)~ West double door opened 		&   420			  &    	420			&	   	420		  \\
-	~(5)~ East double door opened 		&   540			  &    	540			&	   	540		  \\
-	~(6)~ South exterior door opened 	&   600			  &    	600			&	   	600		  \\
-	~(7)~ Center burner off				&   720			  &    	780			&	   	780		  \\
-	~(8)~ Middle burner off				&   840			  &    	900			&	   	900		  \\
-	~(9)~ Corner burner off				&   960			  &    	1020		&	   	1020	  \\
-	(10) PPV fan on 					& 	1260		  &    	1320		&  	   	1320	  \\	
+	~(2)~ Middle burner on 				&   181			  &		181			&		179		  \\
+	~(3)~ Center burner on 				&   361			  &	   	361			&	   	360		  \\
+	~(4)~ West double door opened 		&   418			  &    	416			&	   	415		  \\
+	~(5)~ East double door opened 		&   538			  &    	536			&	   	535		  \\
+	~(6)~ South exterior door opened 	&   604			  &    	597			&	   	597		  \\
+	~(7)~ Center burner off				&   720			  &    	778			&	   	778		  \\
+	~(8)~ Middle burner off				&   840			  &    	898			&	   	897		  \\
+	~(9)~ Corner burner off				&   961			  &    	1018		&	   	1019	  \\
+	(10) PPV fan on 					& 	1256		  &    	1316		&  	   	1319	  \\
+	(11) PPV fan off 					& 	1892 		  & 	N/A 		& 		1380	  \\
+	(12) PPV fan on 					& 	N/A 		  & 	N/A 		& 		1487 	  \\
 	\bottomrule
@@
 	\midrule
-	~(1)~ All burners on 				& 	0			  &	   1230			&	   2430		\\
-	~(2)~ Roof vent opened 				&   128			  &    1320			&	   2520		\\
-	~(3)~ West double door opened 		&	153			  &	   1410	 		&	   2610 	\\
-	~(4)~ East double door opened 		&   333			  &    1500			&	   2700		\\
-	~(5)~ Roof vent closed		 		&   420			  &    1695			&	   2833		\\
-	~(6)~ All burners off 				&   550			  &    1815			&	   2970		\\
-	~(7)~ Roof vent opened				& 	695 		  &	   1860			&	   3060		\\
-	~(8)~ East double door closed		& 	1127 		  &	   2288			&	   N/A		\\
-	~(9)~ West double door closed		& 	1140 		  &	   2305			&	   N/A		\\
-	(10) Roof vent closed		 		&   1155		  &    2364			&	   N/A		\\
+	~(1)~ All burners on 				& 	0			  &	   1225			&	   2425		\\
+	~(2)~ Roof vent opened 				&   154			  &    1345			&	   2545		\\
+	~(3)~ West double door opened 		&	175			  &	   1432	 		&	   2632 	\\
+	~(4)~ East double door opened 		&   361			  &    1524			&	   2730		\\
+	~(5)~ Roof vent closed		 		&   445			  &    1723			&	   2852		\\
+	~(6)~ All burners off 				&   576			  &    1840			&	   2997		\\
+	~(7)~ Roof vent opened				& 	720 		  &	   1890			&	   3086		\\
+	~(8)~ East double door closed		& 	1148 		  &	   2311			&	   N/A		\\
+	~(9)~ West double door closed		& 	1164 		  &	   2330			&	   N/A		\\
+	(10) Roof vent closed		 		&   1179		  &    2387			&	   N/A		\\
 	\bottomrule
@@
 	\midrule
-	~(1)~ All burners on 				&	0				&	570				&	1080			\\
-	~(2)~ West double door opened 		&	90				&   660				&	1170			\\
-	~(3)~ Roof vent opened 		    	&	180				&	720 			& 	1260 			\\
-	~(4)~ All burners off 				&	300				&   840				&	1350			\\
-	~(5)~ East double door opened		&	345				&   885				&	1420			\\
-	~(6)~ Roof vent closed 				&	470				&   1016			&	N/A				\\
-	~(7)~ East double door closed		&	497 			&	986				&	N/A 			\\
-	~(8)~  West double door closed		&	513 			&	999				&	N/A				\\
+	~(1)~ All burners on 				&	0				&	565				&	1075			\\
+	~(2)~ West double door opened 		&	116				&   685				&	1195			\\
+	~(3)~ Roof vent opened 		    	&	207				&	747 			& 	1287 			\\
+	~(4)~ All burners off 				&	327				&   868				&	1387			\\
+	~(5)~ East double door opened		&	369				&   911				&	1446			\\
+	~(6)~ Roof vent closed 				&	494				&   1040			&	N/A				\\
+	~(7)~ East double door closed		&	522 			&	1012			&	N/A 			\\
+	~(8)~  West double door closed		&	538 			&	1025			&	N/A				\\
 	\bottomrule
@@
 	~(1)~  All burners on 						&   0	  			&	 0			\\
-	~(2)~  2nd floor west double door opened 	&   195		  		&    133		\\
-	~(3)~  1st floor west double door opened 	&	315		  		&    255 	 	\\
-	~(4)~  1st floor east double door opened 	&   450			  	&    374		\\
-	~(5)~  2nd floor east double door opened	&   586			  	&    501		\\
-	~(6)~  PPV fan on 							&   653			  	&    614		\\
-	~(7)~  PPV fan off              			&   800			  	&    764		\\
-	~(8)~  All burners off 						&   830			  	&    797		\\
-	~(9)~  2nd floor south exterior door opened &   899			  	&    850		\\
-	(10) PPV fan on 	 						&   1066		  	&    943		\\
-	(11) 2nd floor south exterior door closed   &   1179		  	&    N/A		\\
+	~(2)~  2nd floor west double door opened 	&   194		  		&    130		\\
+	~(3)~  1st floor west double door opened 	&	314		  		&    252 	 	\\
+	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
+	~(5)~  2nd floor east double door opened	&   585			  	&    498		\\
+	~(6)~  PPV fan on 							&   652			  	&    612		\\
+	~(7)~  PPV fan off              			&   798			  	&    761		\\
+	~(8)~  All burners off 						&   829			  	&    794		\\
+	~(9)~  2nd floor south exterior door opened &   899			  	&    849		\\
+	(10) PPV fan on 	 						&   1065		  	&    940		\\
+	(11) 2nd floor south exterior door closed   &   1176		  	&    N/A		\\
 	\bottomrule

### 2016-08-10 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Edited event times for gas burner tests & script that generates reduced data sets

@@
 	~(1)~ All burners on 						&   0		  		&	 0			\\
-	~(2)~ Interior stairwell door opened 		&   120		  		&    114		\\
-	~(3)~ 1st floor west double door opened 	&	240		  		&    245 	 	\\
-	~(4)~ 2nd floor west double door opened 	&   360			  	&    354		\\
-	~(5)~ 2nd floor south exterior door opened	&   480			  	&    474		\\
-	~(6)~ PPV fan on 							&   600			  	&    595 		\\
-	~(7)~ All burners off 						&   720 		  	&    715		\\
-	~(8)~ 2nd floor east double door opened 	&   855			  	&    N/A		\\
-	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 962		\\
+	~(2)~ Interior stairwell door opened 		&   144		  		&    112		\\
+	~(3)~ 1st floor west double door opened 	&	265		  		&    244 	 	\\
+	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
+	~(5)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
+	~(6)~ PPV fan on 							&   624			  	&    594 		\\
+	~(7)~ All burners off 						&   746 		  	&    721		\\
+	~(8)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
+	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 836		\\
 	\bottomrule

### 2016-08-10 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -189,25 +189,32 @@ for f in os.listdir(data_dir):
 
         # Read in test times to offset plots.
         if burner_report:
-            if 'West' in test_name:     # ignore first 2 time entries
+            if 'West' in test_name:     # ignore first 2 time entries => 3rd entry corresponds to 1st burner ignited
                 events = all_times[test_name].dropna()[2:]
                 gasA_lag_time = 12   # [s]; gas analyzer A lag time for west burner tests
                 gasB_lag_time = 12   # [s]; gas analyzer B lag time for west burner tests
-            else:      
-                if 'Test_5_' in test_name or 'Test_6_' in test_name:
-                    events = all_times[test_name].dropna()[3:]
-                else:
-                    events = all_times[test_name].dropna()[1:]
+            else:     # ignore first time entry => 2nd entry corresponds to 1st burner ignited 
+                events = all_times[test_name].dropna()[1:]
                 gasA_lag_time = 12   # [s]; gas analyzer A lag time for east burner tests
                 gasB_lag_time = 35   # [s]; gas analyzer B lag time for east burner tests
+            
+            # adjust times so t=0 corresponds to ignition of 1st burner
             offset_time = events.index.values[0]
             new_times = events.index.values - int(offset_time)
+            
+            # create series of event names & new times 
             events = pd.Series(events.values, index=new_times)
+            
+            # adjust times in data file to correspond with t=0 being ignition of 1st burner
             data['Time'] = data['Time'].values - offset_time
             corrected_data = data.drop('Time', axis=1)
             corrected_data.insert(0, 'Time', data['Time'])
             corrected_data = corrected_data.set_index('Time')
-            reduced_data = corrected_data.loc[-61:, :]
+            
+            # reduce data to relevant data (60 seconds of background data + data collected during test)
+            reduced_data = corrected_data.loc[-61:, :]  # row corresponding to -61 will be replaced with unit headers
+            
+            # set up dataframe to be filled with relevant processed sensor data
             final_reduced_data = pd.DataFrame(index=reduced_data.index)
 
             # Process data for each quantity group
@@ -223,6 +230,12 @@ for f in os.listdir(data_dir):
 
                     # Scale channel depending on quantity
                     current_channel_data = reduced_data[channel]
+                    print 'Test .loc function with current_channel_data'
+                    print current_channel_data.loc[-61:-5]
+                    print
[…]

### 2016-08-11 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated event times and generated new data sets for gas burner tests

@@
 Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23.
-Similarly, Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times that outline the procedure followed during Tests~24 and 25.
-A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of both double doors was used during the tests to change the ventilation pattern within the structure.
+A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
 \begin{figure}[!ht]
@@
 	~(4)~  1st floor east double door opened 	&   450			  	&    371		\\
-	~(5)~  2nd floor east double door opened	&   585			  	&    498		\\
-	~(6)~  PPV fan on 							&   652			  	&    612		\\
-	~(7)~  PPV fan off              			&   798			  	&    761		\\
-	~(8)~  All burners off 						&   829			  	&    794		\\
-	~(9)~  2nd floor south exterior door opened &   899			  	&    849		\\
-	(10) PPV fan on 	 						&   1065		  	&    940		\\
-	(11) 2nd floor south exterior door closed   &   1176		  	&    N/A		\\
+	~(5)~  2nd floor south exterior door closed &   511		  		&    N/A		\\
+	~(6)~  2nd floor east double door opened	&   585			  	&    498		\\
+	~(7)~  PPV fan on 							&   652			  	&    612		\\
+	~(8)~  PPV fan off              			&   798			  	&    761		\\
+	~(9)~  All burners off 						&   829			  	&    794		\\
+	(10)   2nd floor south exterior door opened &   899			  	&    849		\\
+	(11)   PPV fan on 	 						&   1065		  	&    940		\\
+	(12)   2nd floor south exterior door closed &   1176		  	&    N/A		\\
 	\bottomrule
@@
 A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
+Also, the stairwell door was unable to completely close.
+So, when it was in the ``closed'' position at the beginning of the tests, there was a 152~mm (6~in) gap between the door and its frame.
 
@@
 	~(4)~ 2nd floor west double door opened 	&   383			  	&    353		\\
-	~(5)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
-	~(6)~ PPV fan on 							&   624			  	&    594 		\\
-	~(7)~ All burners off 						&   746 		  	&    721		\\
-	~(8)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
-	~(9)~ 1st floor east double door opened		& 	N/A 			& 	 836		\\
+	~(5)~ 2nd floor south exterior door closed	&   452			  	&    N/A		\\
+	~(6)~ 2nd floor south exterior door opened	&   502			  	&    474		\\
+	~(7)~ PPV fan on 							&   624			  	&    594 		\\
+	~(8)~ All burners off 						&   746 		  	&    721		\\
+	~(9)~ 2nd floor east double door opened 	&   877			  	&    N/A		\\
+	(10)  1st floor east double door opened		& 	N/A 			& 	 836		\\
 	\bottomrule

### 2016-08-11 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -36,7 +36,7 @@ specific_struct = 'West'
 
 # Specify if creating data sets
 #  for gas burner exp. report
-burner_report = True
+burner_report = False
 burner_data = '../Reports/Propane_Gas_Fire_Experiments/Data/'
 
 # Plot mode: figure or video
@@ -156,12 +156,12 @@ for f in os.listdir(data_dir):
 
         test_type = info['Test Type'][test_name]
 
-        if burner_report:
-            try:
-                if 'Propane fire' not in info['Test Description'][test_name]:
-                    continue
-            except TypeError:
+        # if burner_report:
+        try:
+            if 'Propane fire' not in info['Test Description'][test_name]:
                 continue
+        except TypeError:
+            continue
 
         if check_name(test_name, test_year, test_type):     # check if file should be skipped
             continue
@@ -197,7 +197,7 @@ for f in os.listdir(data_dir):
                 events = all_times[test_name].dropna()[1:]
                 gasA_lag_time = 12   # [s]; gas analyzer A lag time for east burner tests
                 gasB_lag_time = 35   # [s]; gas analyzer B lag time for east burner tests
-            
+
             # adjust times so t=0 corresponds to ignition of 1st burner
             offset_time = events.index.values[0]
             new_times = events.index.values - int(offset_time)
@@ -230,12 +230,6 @@ for f in os.listdir(data_dir):
 
                     # Scale channel depending on quantity
                     current_channel_data = reduced_data[channel]
-                    print 'Test .loc function with current_channel_data'
-                    print current_channel_data.loc[-61:-5]
-                    print
-                    print '..without .loc'
-                    print current_channel_data[-61:-5]
-                    sys.exit()
                     calibration_slope = float(channel_list['Calibration Slope'][channel])
                     calibration_intercept = float(channel_list['Calibration Intercept'][channel])
                     
@@ -276,10 +270,7 @@ for f in os.listdir(data_dir):
                             sys.exit()
                         # Create list of data shifted according to analyzer lag time and calculate zero voltage
                         current_channel_data = current_channel_data.loc[-61+shift_data:].values
-                        print 'Check that data used to calculate gas zero voltage is correct:'
-                        print corrected_data[channel].loc[-120+shift_data:-60+shift_data]
-                        sys.exit()
-                        zero_voltage = np.mean(corrected_data[channel].loc[-120+shift_data:-60+shift_data])
[…]

### 2016-08-15 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex

@@
 The amount of leakage in the East Structure was measured as 0.024~m$^2$.
-For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed and as 0.054~m$^2$ when the stairway door was opened.
+For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.
 
@@
 \subsection{Tests~22 \& 23}
-Tests~22 and 23 followed an identical procedure to change the ventilation.
+Tests~22 and 23 followed a nearly identical procedure to change the ventilation.
+The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position.
 Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23.
@@
 \subsection{Tests~24 \& 25}
-Similar to Tests~22 and 23, Tests~24 and 25 followed an identical procedure to change the ventilation.
+Similar to Tests~22 and 23, Tests~24 and 25 followed a nearly identical test procedure.
+The starting configuration for Test~24 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~25 had the same door in the closed position.
+Also, the stairwell door was unable to completely close.
+When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6~in) gap between the door and its frame.
 Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25.
 A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
-Also, the stairwell door was unable to completely close.
-So, when it was in the ``closed'' position at the beginning of the tests, there was a 152~mm (6~in) gap between the door and its frame.
 

### 2016-08-15 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
examining fds data & editting fire pattern algorithms

@@
 \item to provide more realistic conditions
-\item to enable the conduct of additional replicate experiments
+\item to conduct additional replicate experiments
 \end{enumerate}
@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-Applications of algorithms such as these are presented in cureent fire investigaton textbooks~\cite{Icove:2013}.
+Applications of algorithms such as these are presented in current fire investigaton textbooks~\cite{Icove:2013}.
 
@@
 
-The first              ~\cite{Babrauskas:1981}
-
-Ratio from heat flux from source fire data
-vyto second item ignite
+The first algorithm assumes that the heat release rate is emitted from a point source in a uniform manner.
+Therefore for any given radii a sphere of uniform heat flux will be assumed.
+A schematic of this arrangement is shown...
+and the equation is presented below.
+Babrauskas applied this concept in his paper, "Will the Second Item Ignite"~\cite{Babrauskas:1981}.
+The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite, then you could potentially determine the maximum distance that the material could be located from a fire of a given HRR, with a given radiant fraction and it would still ignite.
 

### 2016-08-18 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to hose stream + gas burner reports

@@
 SS \> Straight Stream \\
-UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute
+UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
 WF \> Wide Fog Stream \\

### 2016-08-22 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added background text

@@
 
+\Subsection{The Fire Investigators' Challenge}
+
+For the moment lets step into the shoes of a fire investigator and examine a potential investigation scenario.
+It is 8:30 in the morning on a cool fall morning and you are being called to a fire scene.
+As you prepare to leave for the fire scene, you begin to collect information on the fire as you listen to your department radio.
+You have the address.
+You start to develop an image in your mind about the location of the home involved in the fire.
+The fire occured in area of older townhomes.
+The socio-economics of the neighboorhood are such the the people that live there have many life struggles.
+Enroute you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
+The husband and father also lives at that address but is unaccounted at this time.
+Upon arrival you have a conversation with the police and fire officers on the scene.
+You are provided with information regarding what the first firefighters saw on the scene, "all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
+The fornt door was forced and a hose stream was applied to the fire in the living room.
+Fire knockdown was rapid.
+The mother and chaild were rescued from a bedroom upstairs".
+You thank the fire officier and get contact information for a follow-up if necessary.
+As you wait for the fire department to complete their operations inside, the police on scene let you know that the address is familiar to them for domestic disturbance calls for the husband and wife fighting but no charges have been filed.
+They are looking for the husband and have sent a patrol car to his work place.
+
+As you begin to examine the scene, you walk around the exterior and note that on the front of the end unit, townhouse, there is fire damage on the exterior above the front door opening that extends across the ceiling of the porch.
+The is some thermal damage and smoke deposits on the from of the siding on the porch.
+There outer pane of the living room window is for the most part still intact.
+you notice that three of the four windows on the second floor have been removed.
+On the "D side" of the townhome there are no openings and no smoke or fire damage is present.
+On the rear or "Side C"
+of the house the door and windows are intact but open.  There is no somke stains or thermal damage around any of the openings on the rear. No sign of smoke alarms in the home
+
+You take some notes and photograph the exterior of the structure, the fire department is not repacking their equipment and are preparing to leave when you enter through the front doorway.
+The living room has extensive fire damage.
+Looking to your right, two chairs infront of the living room window have some thermal damage.
+There are a clear horizontal line of demarcation the large wood TV stand in the corner.
+As your eyes move from the corner back toward the rear of the townhome and the kitchen, you notice that the elevation of the line of demarcation is increasing.
+This may be an indicator that the origin of the fire is closer to the front of the living room.
+Between the two wood cabinets on the "D wall" of the living room was a wood framed sofa.
+The cushions have thermal damage, from pyrolysis.
+It is not clear that they were on fire as there is not thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
+Still standing in the entry doorway, you turn your attention to the remains of an uphostered sofa and chair.
+The wall behind the sofa and chair has extensive thermal danage.
+The wall extends from the opening to the dining/kitchen area of the house to the open stairway that goes to the upper level.
+You move to the dining area and kitchen area.
+There is plenty of smoke damage high in the space, but there are no indications of fire damage due to combustion.
+You return to the living room and walk up the stairs.
+Their is evidence of paint and paper burned off of the gypsum wallboard in the stairway.
+THe fire damage doe not extend beyond the top of the stairs.
+there is smoke damage in the upstairs hallway an in the front bedrooms.
+THE FURTHER YOU MOVE FROM THE stairs the less damage you find.
+
+You head back down the stairs to further examine the living room which appears to be the room of fire origin.
+Your are focussing on the area with the most damage, the area with the sofa and chair.
+As you are looking toward 'b wall' of the living room you note that the right side of the chair is badly burned and it is burned from the floor level up.
+The same is true from the left side of the sofa.
+The corner formed by the wall behind and the wall of the stairway has a "V pattern" burned into it, from the floor and extending up toward the ceiling.
+As you look at the debris surrounding the chair, you notice the remains of an electric heater.
+The wire from the heater extends toward the wall outlet behind the sofa.
+You have no developed your first hypothesis about the origin of the fire.
+A radiant style, electric heater was turned on and left until it ignited the fabric on the sofa or chair.
+You collect the remains of the heater for further examination to have a lab determine of the heater switch was in the "on" position.
+No you need to start testing your hypothesis.
+Is everything consistant with the other fire damage?
+
+There are different damage patterns behind the sofa.  On the right side there is fire damage on the wall behind the rightside back cushion of the sofa.
+the damaged area is distinct from the other fire damage that exists on the wall behind the sofa.
+There are pieces of charred newspaper near the right arm of the sofa.
+The burn mark on the top of the wood coffee looks like a arrow that is pointing toward the corner.
+The char on the legs of the coffee table is very directional and consistent with the heat coming from the corner.
+Looking at the inside area of the sofa, you see that there is charred wood on the inside surface of the soaf frame while the outer portions of the wood frame are not charred.
+This would indicate that the fire was inside the sofa at some point.
+Further is appears that all of the foam cushioning is burnt off of the right side of the sofa, while there is a piece of polyurethane foam cushion on the left side of the sofa.
+However that foam could have gotten moved during the fire suppression.
+
+The chair clearly has more unburned foam cushioning then the sofa does and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not be moved.
+The cushion was heated from the top down.
+Perhaps the constrion of the chair slowed the flame spread through the chair from the bottom up, if the heatere was the ignition source.
+Or the fire started in the sofa and the radiation from the flames and hot gas layer spread the fire to the chair  The heater still looks good as a source however now you have some fire damage that may not be consistent with the heater as the origin.
+Besides interviews whatelse can you do to eliminate the inconsistancies?
+We will reexamine the in Chapter XX.
+
 \chapter{Characterizing the Source Fires}
@@
 Polyurethane foam was chosen as the solid fuel.
-According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
+According to the Polyurethane Foam Associaand tion, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
 More than 1.2 billion pounds are produced in the U.S.

### 2016-08-30 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Edits to prepare final version of hose stream report

@@
 \vspace*{2\baselineskip}
-July 2016}
+September 2016}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (July 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2016) \\
 % http://dx.doi.org/10.6028/NIST.TN.XXXX \\
@@
 
-% \chapter{List of Symbols}
-% \begin{tabbing}
-% \hspace{1.5in} \= \\
-% ft \> foot \\
-% gpm \> gallons per minute \\
-% in \> inch \\
-% m \> meter \\
-% \end{tabbing}
-
 \mainmatter
@@
 Fire suppression tactics using hose streams can affect ventilation in a structure and may impact the movement of smoke and heat through a structure.
-Seven series of experiments were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
+Seven experimental series containing a total of 154 different configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
 The experiments studied four different hose streams: a straight stream, narrow fog stream, a wide fog stream from a combination nozzle, and a solid stream from a smooth bore nozzle.
@@
 
-Four types of hose streams and four nozzle movement patterns were studied as part of the experiments described in this report.
+Four types of hose streams and four nozzle movement patterns were studied under 154 different configurations during the seven test series described in this report.
 Three of the hose stream patterns studied were from a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
 Water was flowed into the structure by having the hose in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
-Additionally, experiments comparing the differences in impact on air flows in a structure from a combination nozzle straight stream and a solid stream from a smooth bore nozzle equipped with a 1~in tip were conducted.
+Additionally, experiments comparing the differences in impact on air flows in a structure from a combination nozzle straight stream and a solid stream from a smooth bore nozzle equipped with a 1~in.
+tip were conducted.
 Images of the four types of hose streams are presented in Fig.~\ref{fig:hose_streams}.
@@
 		\includegraphics[width=0.75\columnwidth]{../Figures/Pictures/SB_70}
-		\caption{Solid stream from 1~in smooth bore nozzle}
+		\caption{Solid stream from 1~in. smooth bore nozzle}
 	\end{subfigure}
@@
 The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate.
-The total expanded uncertainty was estimated at $\pm10$~\%.
+The total expanded uncertainty was estimated to be $\pm10$~\%.
 
@@
 \label{sec:exp_procedure}
-Every experiment discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle with a 1~in tip with a solid stream pattern.
+Every experimental test series discussed in this report involved discharging water at a set flow rate from a combination nozzle in a straight, narrow fog, or wide fog stream pattern or from a smooth bore nozzle with a 1~in.
+tip in a solid stream pattern.
 Specific doors were opened or closed before and/or during the tests to change the ventilation within the structure.
-
-A total of seven experimental series, summarized in Table~\ref{table:test_matrix}, were conducted to study the impact of different hose stream and nozzle motion patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
+Each time a hose stream pattern, nozzle movement pattern, target location, or ventilation pattern was changed during a test series, a new test configuration was considered to be in place.
+A total of 154 configurations were used throughout the seven experimental series.
+
+The seven experimental test series, summarized in Table~\ref{table:test_matrix}, were conducted to study the impact of different hose stream and nozzle motion patterns on gas movement in a structure; three used a combination nozzle attached to a monitor to flow water at approximately 120~gpm, three used a combination nozzle attached directly to a 1.75~in.
+handline to flow water at approximately 120~gpm (Fig.~\ref{fig:monitor+handline}), and one used both a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at approximately 180~gpm.
 Experiments that used a monitor to flow water always applied the stream in a fixed position and were focused on changing the location of water application in addition to the stream pattern.
-The experiments that used a combination nozzle attached directly to a 1.75~in handline to flow water focused on impact of the motion of the nozzle.
+The experiments that used a combination nozzle attached directly to a 1.75~in.
+handline to flow water focused on impact of the motion of the nozzle.
 
@@
 	\endminipage \hfill
-	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75~in handline (right) equipped with a combination nozzle and used to flow water during experiments.}
+	\caption[Monitor and handline equipped with a combination nozzle.]{Monitor (left) and 1.75~in. handline (right) equipped with a combination nozzle and used to flow water during experiments.}
 	\label{fig:monitor+handline}
@@
 Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
-Tests~2 and 3 used a combination nozzle attached to a monitor to flow water; Tests~6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test~4 used both a combination nozzle and a 1~in tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
+Tests~2 and 3 used a combination nozzle attached to a monitor to flow water; Tests~6 and 7 used a combination nozzle attached directly to a handline to flow water; and Test~4 used both a combination nozzle and a 1~in.
+tip smooth bore nozzle attached to a monitor to flow water in a straight and solid stream, respectively.
 
@@
 \label{sec:monitor_procedure}
-Three experimental series, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
+Three experimental test series, Tests~1--3, used a monitor equipped with a combination nozzle to flow water at 120~gpm in a straight stream, narrow fog stream, and wide fog stream.
 Test~1 occurred in the Single Story Structure, and Tests~2 and 3 occurred in the Two Story Structure.
-A fourth series, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
+A fourth test series, Test~4, was conducted in the Two Story Structure and used a combination nozzle and a smooth bore nozzle attached to a monitor to flow water at 180~gpm in a straight stream and solid stream, respectively.
 The monitor was always set to flow water from a fixed position.
@@
 \subsubsection{Test~4}
-Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3.
+Test~4 studied the differences in air movement caused by a solid stream from a smooth bore nozzle with a 1~in.
+tip and straight stream from a combination nozzle attached to a monitor aimed at the same targets used during Tests~2 and 3.
 The stairwell door was opened for the entire experimental series.
@@
 This entire process was repeated for the solid stream from the smooth bore nozzle.
-Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in tip of the smooth bore nozzle during Test~4.
+Fig.~\ref{fig:test_4_pic} contains images of the straight stream from the combination nozzle and solid stream from the 1~in.
+tip of the smooth bore nozzle during Test~4.
 
@@
 	\endminipage
-	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test~4.}
+	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in.
+tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test~4.}
 	\label{fig:test_4_pic}
@@
 \label{sec:handline_procedure}
-Three experimental series were conducted using a 1.75~in handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
+Three experimental test series were conducted using a 1.75~in.
+handline with a combination nozzle to flow water in a straight stream, narrow fog stream, and wide fog stream.
 One series, Test~5, occurred in the Single Story Structure, and the remaining tests, Tests~6 and 7, occurred in the Two Story Structure.
@@
 \subsubsection{Test~5}
-Test~5 utilized a 1.75~in handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
+Test~5 utilized a 1.75~in.
+handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
 The layout of the structure was identical to the layout for Test~1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
@@
 This entire process was repeated for the streams being applied in the fixed and counterclockwise patterns.
+The average rotation rate for configurations that involved nozzle rotation during Test~5 was 2.1 rotations per second with a maximum rate of 2.3 rotations per second and minimum of 1.9 rotations per second.
 
@@
 \subsubsection{Tests~6 \& 7}
-Tests~6 and 7 followed identical procedures that involved using a 1.75~in handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
+Tests~6 and 7 followed identical procedures that involved using a 1.75~in.
+handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
 The water stream was aimed at the south side wall of the first floor during the experiments.
@@
 Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.
+During configurations involving nozzle rotation with a wide fog stream or narrow fog stream, the average rotation rate was 1.3 rotations per second with a maximum of 1.4 rotations per second and a minimum of 1.2 rotations per second.
+The rotation rates for the clockwise and counterclockwise rotation of the straight stream were 0.8 rotations per second and 0.7 rotations per second, respectively, for Test~6, and 0.4 rotations per second for both directions during Test~7.
 
@@
 Furthermore, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream.
-Finally, the Test~4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in tip produced approximately the same amount of air movement through the interior doorway.
+Finally, the Test~4 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_4_BDP_A10_Avg_All} suggest that the straight stream from a combination nozzle and the solid stream from a smooth bore nozzle equipped with a 1~in.
+tip produced approximately the same amount of air movement through the interior doorway.
 \FloatBarrier
@@
 Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the nozzle movement patterns using the narrow and wide fog streams than the same patterns using the straight stream.
-Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
+Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences (differences greater than the error associated with the bi-directional probes) in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
 The similarities in air flow produced by the clockwise and counterclockwise nozzle movement patterns can also be seen graphically in Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_5_BDP_A6_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} in Appendix~\ref{chap:handline_plots}.
@@
 
-A total of seven experimental series were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
+Seven experimental test series containing a total of 154 different configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
 
@@
 
-Additionally, a fourth experimental series using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in tip aimed at a specified location for 60 seconds with a fully established flow path.
+Additionally, a fourth experimental series using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in.
+tip aimed at a specified location for 60 seconds with a fully established flow path.
 The streams were compared for six different 60 second periods during which the flow path was fully established: three times each for the monitor aimed at two locations.

### 2016-08-31 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Final edits to hose stream paper, just need TN # from PR, so hopefully will be published by end of year

@@
 \label{sec:layout}
-Dimensioned floor plans of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively.
+Simple floor plans showing the total length and width of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively.
+Fully dimensioned floor plan drawings are provided in Appendix~\ref{chap:floor_plans}.
 
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the Single Story Structure.]{Dimensioned floor plan of the Single Story Structure. Interior dimensions are symmetric across horizontal and vertical centerlines.}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_LxW}
+	\caption[Simple floor plan of the Single Story Structure.]{Simple floor plan of the Single Story Structure.}
 	\label{fig:east_dimensioned_plan}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
-	\\~\\
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
-	\caption[Dimensioned floor plan of the first and second floors of the Two Story Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
+	\includegraphics[width=.985\columnwidth]{../Figures/Floor_Plans/West_Test_Structure_2nd_Floor_Dimensioned_LxW}
+	\\~\\
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Test_Structure_1st_Floor_Dimensioned_LxW}
+	\caption[Simple floor plan of the first and second floors of the Two Story Structure.]{Simple floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
 	\label{fig:west_dimensioned_plan}
@@
 &	 	\small{m$^3$/s}	&	 0.3 $\pm0.1$	&  1.2 $\pm0.2$		&	 1.6 $\pm0.3$  	\\
-& 	&	\small{(cfm)}	& 	(628 $\pm113$)	& (2584 $\pm465$) 	&	(3291 $\pm592$)
+& 	&	\small{(cfm)}	& 	(650 $\pm100$)	& (2600 $\pm450$) 	&	(3300 $\pm600$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 3.2 $\pm0.6$   	&	 3.3 $\pm0.6$		&	 2.9 $\pm0.5$  	\\
-& 	&	\small{(cfm)}	& 	(6786 $\pm1222$)	&	(6977 $\pm1256$) 	&	(6228 $\pm1121$)
+& 	&	\small{(cfm)}	& 	(6800 $\pm1200$)	&	(7000 $\pm1250$) 	&	(6250 $\pm1100$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 3.4 $\pm0.6$   	&  4.0 $\pm0.7$		&	 4.1 $\pm0.7$  	\\
-& 	&	\small{(cfm)}	& 	(7283 $\pm1311$)	& (8463 $\pm1523$) 	&	(8669 $\pm1561$) \\
+& 	&	\small{(cfm)}	& 	(7300 $\pm1300$)	& (8450 $\pm1500$) 	&	(8650 $\pm1550$) \\
 \midrule
@@
 &	 	\small{m$^3$/s}	&	 -0.2 $\pm0.03$   	&  1.2 $\pm0.2$		&	 1.0 $\pm0.2$  	\\
-& 	&	\small{(cfm)}	& 	(-381 $\pm69$)		& (2469 $\pm445$) 	&	(2155 $\pm388$)
+& 	&	\small{(cfm)}	& 	(-400 $\pm50$)		& (2450 $\pm450$) 	&	(2150 $\pm400$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 1.8 $\pm0.3$   	&  2.9 $\pm0.5$		&	 3.1 $\pm0.6$  	\\
-& 	&	\small{(cfm)}	& 	(3739 $\pm673$)		& (6046 $\pm1088$) 	&	(6479 $\pm1166$)
+& 	&	\small{(cfm)}	& 	(3750 $\pm650$)		& (6050 $\pm1100$) 	&	(6500 $\pm1150$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 3.9 $\pm0.7$   	&  4.3 $\pm0.8$		&	 4.8 $\pm0.9$  	\\
-& 	&	\small{(cfm)}	& 	(8271 $\pm1489$)	& (9165 $\pm1650$) 	&	(10273 $\pm1849$) \\
+& 	&	\small{(cfm)}	& 	(8250 $\pm1500$)	& (9150 $\pm1650$) 	&	(10250 $\pm1850$) \\
 \bottomrule
@@
 &	 	\small{m$^3$/s}	&	 -0.3 $\pm0.1$		&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.2 $\pm0.2$  	\\
-& 	&	\small{(cfm)}	& 	(-670 $\pm121$)		&	(1864 $\pm336$)		&	(2549 $\pm459$)		& 	(2602 $\pm468$)
+& 	&	\small{(cfm)}	& 	(-650 $\pm100$)		&	(1850 $\pm350$)		&	(2550 $\pm450$)		& 	(2600 $\pm450$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 0.7 $\pm0.1$   	&	 1.7 $\pm0.3$		&	 1.4 $\pm0.3$  		&	 1.8 $\pm0.3$  	\\
-& 	&	\small{(cfm)}	& 	(1471 $\pm265$)		&	(3688 $\pm664$) 	&	(3034 $\pm546$)		& 	(3786 $\pm682$)
+& 	&	\small{(cfm)}	& 	(1450 $\pm250$)		&	(3700 $\pm650$) 	&	(3050 $\pm550$)		& 	(3800 $\pm700$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 1.6 $\pm0.3$   	&	 1.6 $\pm0.3$		&	 1.6 $\pm0.3$  		&	 1.4 $\pm0.3$  	\\
-& 	&	\small{(cfm)}	& 	(3369 $\pm606$)		&	(3362 $\pm605$) 	&	(3453 $\pm622$)		& 	(3051 $\pm549$)
+& 	&	\small{(cfm)}	& 	(3350 $\pm600$)		&	(3350 $\pm600$) 	&	(3450 $\pm600$)		& 	(3050 $\pm550$)
 \\ \midrule
@@
 &	 	\small{m$^3$/s}	&	 -0.1 $\pm0.01$   	&	 0.9 $\pm0.2$		&	 1.2 $\pm0.2$		&	 1.1 $\pm0.2$  	\\
-& 	&	\small{(cfm)}	& 	(-152 $\pm27$)		&	(1804 $\pm325$) 	&	(2473 $\pm445$)		& 	(2358 $\pm425$)
+& 	&	\small{(cfm)}	& 	(-150 $\pm50$)		&	(1800 $\pm300$) 	&	(2450 $\pm450$)		& 	(2350 $\pm400$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 2.1 $\pm0.4$   	&  	 2.0 $\pm0.4$		&	 2.0 $\pm0.4$  		& 	 2.1 $\pm0.4$ 	\\
-& 	&	\small{(cfm)}	& 	(4494 $\pm809$)		& 	(4326 $\pm779$) 	&	(4214 $\pm759$)		& 	(4477 $\pm806$)
+& 	&	\small{(cfm)}	& 	(4500 $\pm800$)		& 	(4350 $\pm800$) 	&	(4200 $\pm750$)		& 	(4500 $\pm800$)
 \\~\\
@@
 &	 	\small{m$^3$/s}	&	 1.7 $\pm0.3$   	&	 1.2 $\pm0.2$		&	 1.6 $\pm0.3$  		& 	 1.6 $\pm0.3$	\\
-& 	&	\small{(cfm)}	& 	(3509 $\pm632$)		&	(2503 $\pm451$) 	&	(3299 $\pm594$)		& 	(3428 $\pm617$)
+& 	&	\small{(cfm)}	& 	(3500 $\pm650$)		&	(2500 $\pm450$) 	&	(3300 $\pm600$)		& 	(3450 $\pm600$)
 \\ \bottomrule
@@
 \appendix
+\chapter{Fully Dimensioned Floor Plans}
+\label{chap:floor_plans}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/East_Test_Structure_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the Single Story Structure.]{Dimensioned floor plan of the Single Story Structure. Interior dimensions are symmetric across horizontal and vertical centerlines.}
+	\label{fig:east_dimensioned_plan}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Dimensioned_Full}
+	\\~\\
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Dimensioned_Full}
+	\caption[Dimensioned floor plan of the first and second floors of the Two Story Structure.]{Dimensioned floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
+	\label{fig:west_dimensioned_plan}
+\end{figure}
+
+\clearpage
+
 \chapter{Monitor Test Plots}

### 2016-08-31 Projects/DelCo_2014_2015/Scripts/hose_stream_sorting_plotting.py

@@ -271,6 +271,13 @@ def sort_data(test_name, start_time, test_type):
 	
 	return group_results, zero_time_ls
 
+def m3s_2_cfm(flow_rate):
+	converted_rate = m3s_to_cfm*flow_rate
+	converted_error = abs(converted_rate)*0.18
+	rounded_rate = round(converted_rate/50.0, 0)*50.0
+	rounded_error = round(converted_error/50.0, 0)*50.0
+	return int(rounded_rate), int(rounded_error)
+
 def plot_stream_avgs(stream_data, updated_times, x_max_index, y_max, y_min, marker, color, plot_label):
 	stream_data = pd.Series(data = stream_data, index=range(-3, len(stream_data)-3))
 	ma_quantity = pd.rolling_mean(stream_data, 5, center=True)
@@ -700,9 +707,10 @@ for f in os.listdir(data_dir):
 									print '			mph 	' + str(round(avg_mph, 1)) + ' (+/-)' + str(round(abs(avg_mph)*0.18, round_place))
 
 									flow_rate = avg_m_per_s*area
+									flow_rate_cfm, flow_rate_error = m3s_2_cfm(flow_rate)
 									print
-									print '			m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
-									print '			cfm     ' + str(round(flow_rate*m3s_to_cfm,1)) + ' (+/-)' + str(round(abs(m3s_to_cfm*flow_rate)*0.18, round_place))
+									print '			m3/s 	' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
+									print '			cfm     ' + str(flow_rate_cfm) + ' (+/-)' + str(flow_rate_error)
 									print
 						else:
 							m_per_s_data = []
@@ -727,9 +735,10 @@ for f in os.listdir(data_dir):
 							print '			mph 	' + str(round(avg_mph, 1)) + ' (+/-)' + str(round(abs(avg_mph)*0.18, round_place))
 							
 							flow_rate = avg_m_per_s*area
+							flow_rate_cfm, flow_rate_error = m3s_2_cfm(flow_rate)
 							print
 							print '			m3/s    ' + str(round(flow_rate,1)) + ' (+/-)' + str(round(abs(flow_rate)*0.18, round_place))
[…]

### 2016-09-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Figure to folder and text

@@
 The first algorithm assumes that the heat release rate is emitted from a point source in a uniform manner.
-Therefore for any given radii a sphere of uniform heat flux will be assumed.
-A schematic of this arrangement is shown...
-and the equation is presented below.
+Therefore for any given radii a sphere of nearly uniform heat flux will be assumed.
+A schematic of this arrangement is shown in Figure~\ref{PointSourceHF} and the equation is presented below.
 Babrauskas applied this concept in his paper, "Will the Second Item Ignite"~\cite{Babrauskas:1981}.
-The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite, then you could potentially determine the maximum distance that the material could be located from a fire of a given HRR, with a given radiant fraction and it would still ignite.
+The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite.
+Then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could recieve enough energy to ignite.
+Radiation is assumed to be the only means of heat transfer.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/PointSourceHF} \\
+	\caption[Schematic of heat flux estimation using the point source assumption]
+	\label{PointSourceHF}
+\end{figure}
 

### 2016-09-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
fix latex issues in Mad Thesis

@@
 Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 37 years of marriage.
-I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for "buying me time" to work on my studies.}
+I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for ``buying me time'' to work on my studies.}
 
@@
 
-Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupanies.
-A common height for a residential occupanices is 2.4~m in height.
+Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupancies.
+A common height for a residential occupancies is 2.4~m in height.
 With a wall height of 2.4~m, these experiments will use small fires with mean flame heights of approximately 1.2~m.
@@
 
-\Subsection{The Fire Investigators' Challenge}
+\subsection{The Fire Investigators' Challenge}
 
@@
 You start to develop an image in your mind about the location of the home involved in the fire.
-The fire occured in area of older townhomes.
-The socio-economics of the neighboorhood are such the the people that live there have many life struggles.
+The fire occurred in area of older townhomes.
+The socio-economics of the neighborhood are such the the people that live there have many life struggles.
 Enroute you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
@@
 Upon arrival you have a conversation with the police and fire officers on the scene.
-You are provided with information regarding what the first firefighters saw on the scene, "all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
-The fornt door was forced and a hose stream was applied to the fire in the living room.
+You are provided with information regarding what the first firefighters saw on the scene, ``all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
+The front door was forced and a hose stream was applied to the fire in the living room.
 Fire knockdown was rapid.
-The mother and chaild were rescued from a bedroom upstairs".
-You thank the fire officier and get contact information for a follow-up if necessary.
+The mother and child were rescued from a bedroom upstairs.''  You thank the fire officer and get contact information for a follow-up if necessary.
 As you wait for the fire department to complete their operations inside, the police on scene let you know that the address is familiar to them for domestic disturbance calls for the husband and wife fighting but no charges have been filed.
@@
 you notice that three of the four windows on the second floor have been removed.
-On the "D side" of the townhome there are no openings and no smoke or fire damage is present.
-On the rear or "Side C"
-of the house the door and windows are intact but open.  There is no somke stains or thermal damage around any of the openings on the rear. No sign of smoke alarms in the home
+On the ``D side'' of the townhome there are no openings and no smoke or fire damage is present.
+On the rear or ``Side C'' of the house the door and windows are intact but open.
+There is no smoke stains or thermal damage around any of the openings on the rear.
+No sign of smoke alarms in the home.
 
@@
 This may be an indicator that the origin of the fire is closer to the front of the living room.
-Between the two wood cabinets on the "D wall" of the living room was a wood framed sofa.
+Between the two wood cabinets on the ``D wall'' of the living room was a wood framed sofa.
 The cushions have thermal damage, from pyrolysis.
 It is not clear that they were on fire as there is not thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
-Still standing in the entry doorway, you turn your attention to the remains of an uphostered sofa and chair.
-The wall behind the sofa and chair has extensive thermal danage.
+Still standing in the entry doorway, you turn your attention to the remains of an upholstered sofa and chair.
+The wall behind the sofa and chair has extensive thermal damage.
 The wall extends from the opening to the dining/kitchen area of the house to the open stairway that goes to the upper level.
@@
 Their is evidence of paint and paper burned off of the gypsum wallboard in the stairway.
-THe fire damage doe not extend beyond the top of the stairs.
+The fire damage doe not extend beyond the top of the stairs.
 there is smoke damage in the upstairs hallway an in the front bedrooms.
-THE FURTHER YOU MOVE FROM THE stairs the less damage you find.
+The further you move from the stairs the less damage you find.
 
 You head back down the stairs to further examine the living room which appears to be the room of fire origin.
-Your are focussing on the area with the most damage, the area with the sofa and chair.
-As you are looking toward 'b wall' of the living room you note that the right side of the chair is badly burned and it is burned from the floor level up.
+Your are focusing on the area with the most damage, the area with the sofa and chair.
+As you are looking toward the ``B wall'' of the living room you note that the right side of the chair is badly burned and it is burned from the floor level up.
 The same is true from the left side of the sofa.
-The corner formed by the wall behind and the wall of the stairway has a "V pattern" burned into it, from the floor and extending up toward the ceiling.
+The corner formed by the wall behind and the wall of the stairway has a ``V pattern'' burned into it, from the floor and extending up toward the ceiling.
 As you look at the debris surrounding the chair, you notice the remains of an electric heater.
 The wire from the heater extends toward the wall outlet behind the sofa.
+
 You have no developed your first hypothesis about the origin of the fire.
 A radiant style, electric heater was turned on and left until it ignited the fabric on the sofa or chair.
-You collect the remains of the heater for further examination to have a lab determine of the heater switch was in the "on" position.
+You collect the remains of the heater for further examination to have a lab determine of the heater switch was in the ``on'' position.
 No you need to start testing your hypothesis.
-Is everything consistant with the other fire damage?
-
-There are different damage patterns behind the sofa.  On the right side there is fire damage on the wall behind the rightside back cushion of the sofa.
-the damaged area is distinct from the other fire damage that exists on the wall behind the sofa.
+Is everything consistent with the other fire damage?
+
+There are different damage patterns behind the sofa.
+On the right side there is fire damage on the wall behind the right side back cushion of the sofa.
+The damaged area is distinct from the other fire damage that exists on the wall behind the sofa.
 There are pieces of charred newspaper near the right arm of the sofa.
@@
 The char on the legs of the coffee table is very directional and consistent with the heat coming from the corner.
-Looking at the inside area of the sofa, you see that there is charred wood on the inside surface of the soaf frame while the outer portions of the wood frame are not charred.
+Looking at the inside area of the sofa, you see that there is charred wood on the inside surface of the sofa frame while the outer portions of the wood frame are not charred.
 This would indicate that the fire was inside the sofa at some point.
@@
 The cushion was heated from the top down.
-Perhaps the constrion of the chair slowed the flame spread through the chair from the bottom up, if the heatere was the ignition source.
+Perhaps the construction of the chair slowed the flame spread through the chair from the bottom up, if the heater was the ignition source.
 Or the fire started in the sofa and the radiation from the flames and hot gas layer spread the fire to the chair  The heater still looks good as a source however now you have some fire damage that may not be consistent with the heater as the origin.
-Besides interviews whatelse can you do to eliminate the inconsistancies?
+Besides interviews what else can you do to eliminate the inconsistencies?
 We will reexamine the in Chapter XX.
@@
 Polyurethane foam was chosen as the solid fuel.
-According to the Polyurethane Foam Associaand tion, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
+According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
 More than 1.2 billion pounds are produced in the U.S.
@@
 The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11~\% It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
-The gas burner and on/off control valve allowed the heat release rate to be similar in form to a "square-wave".
+The gas burner and on/off control valve allowed the heat release rate to be similar in form to a ``square-wave''.
 
 The gasoline pan fire has was ignited and then burned until the fuel was consumed.
-Therefore the heat release rate curves had more of a "bell shape"  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
+Therefore the heat release rate curves had more of a ``bell shape''  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
 Therefore the  gasoline average peak heat release rate was based on an average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments.
@@
 The block of polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Similar to the gasoline that began with a fixed quantity of fuel which was ignitied and burned to completion, the polyurthane foam also generated "bell shaped" heat release rate curve.
+Similar to the gasoline that began with a fixed quantity of fuel which was ignited and burned to completion, the polyurethane foam also generated ``bell shaped'' heat release rate curve.
 Since the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~s interval bounding the peak heat release rate from each of the ten experiments.
@@
 Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silcate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
@@
 With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, commonly this process is known as calcination.
-Schroder exposed samples of gyspum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
+Schroder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
 The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction  add Schroder.
@@
 
-As defined in NFPA 921, a fire pattern is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA_921}.
+As defined in NFPA 921, a fire pattern is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA:921}.
 In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
-The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{NFPA_921}.
+The boundary between the undamaged area and the area that has been damaged by the fire is known as the line of demarcation~\cite{NFPA:921}.
 As presented in the introduction, DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
@@
 This type of testing might be practical for a fire investigator to use based on the low cost, relative to a full-scale fire test, and the small size of the samples needed for the tests.
-In the previous sections of this study, burners were used to examine the repeatibility of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
-While the data generated from those experiments provide valuable insight, it would be of valauble to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
+In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
+While the data generated from those experiments provide valuable insight, it would be of valuable to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
 
@@
 
-For the ignition tests, an electric spark ignitor was positioned over the center of the horizontal samples to serve as a pilot.
+For the ignition tests, an electric spark igniter was positioned over the center of the horizontal samples to serve as a pilot.
 Combustion products and dilution air were extracted through the hood and exhaust duct by a high temperature fan.
@@
 Currently there is no specific protocol for a fire model user to follow to develop input data.
-Nor is there a "standard" catalog of fire model inputs for a given material.
+Nor is there a ``standard'' catalog of fire model inputs for a given material.
 As a result the literature is sourced for information and users may to conduct experiments, such as those above, in order to develop values or ranges of values which could be used in the calculations in Chapters 8 and 9 or to evaluate the validity of the calculations in those chapters.
@@
 
-For this analysis, the outline of the fire pattern, or the line of demarcation~\cite{NFPA_921}, was defined as the points where charring, penetration and consumption of the paper covering the gypsum wallboard stopped.
+For this analysis, the outline of the fire pattern, or the line of demarcation~\cite{NFPA:921}, was defined as the points where charring, penetration and consumption of the paper covering the gypsum wallboard stopped.
 The grids were used to assist with the determination of the fire pattern area and the sizing of the images.
@@
 There are also a number of qualitative terms from NFPA~921 that were used to describe features of the patterns.
-For example, "clean burn" to describe a lack of soot within a fire pattern area or "inverted cone" to describe the shape of the pattern~\cite{NFPA_921}.
+For example, ``clean burn'' to describe a lack of soot within a fire pattern area or ``inverted cone'' to describe the shape of the pattern~\cite{NFPA:921}.
 
@@
 Based on observation alone, the visible flames extend well above the height of the resulting patterns.
-Even though the experiments were conducted under quiescent conditions, a noticable bias to one side or the other can be seen in four of the ten experiments.
+Even though the experiments were conducted under quiescent conditions, a noticeable bias to one side or the other can be seen in four of the ten experiments.
 
@@
 The comparison of the numerical values can be seen in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
-Each of the sets of
-patterns have a few patterns with the bump on one side of the pattern within 200~mm of the burner, as discussed in the section on the closed wall construction.
+Each of the sets of patterns have a few patterns with the bump on one side of the pattern within 200~mm of the burner, as discussed in the section on the closed wall construction.
 
@@
 
-In this chapter the application of emprical algebraic fire characterizations will be examined.
+In this chapter the application of empirical algebraic fire characterizations will be examined.
 Two different types of applications will be used.
@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-Applications of algorithms such as these are presented in current fire investigaton textbooks~\cite{Icove:2013}.
+Applications of algorithms such as these are presented in current fire investigation textbooks~\cite{Icove:2013}.
 
@@
 A schematic of this arrangement is shown in Figure~\ref{PointSourceHF} and the equation is presented below.
-Babrauskas applied this concept in his paper, "Will the Second Item Ignite"~\cite{Babrauskas:1981}.
+Babrauskas applied this concept in his paper, ``Will the Second Item Ignite''~\cite{Babrauskas:1981}.
 The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite.
-Then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could recieve enough energy to ignite.
+Then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
 Radiation is assumed to be the only means of heat transfer.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/PointSourceHF} \\
-	\caption[Schematic of heat flux estimation using the point source assumption]
+	\includegraphics[width=\textwidth]{../Figures/PointSourceHF}
+	\caption{Schematic of heat flux estimation using the point source assumption}
 	\label{PointSourceHF}
@@
 The face of the wall is located 1.35~m from the front of the domain.
-The wall was modelled with material properties for gypsum board.
+The wall was modeled with material properties for gypsum board.
 Thermal conductivity = 0.28
@@
 The burner was modeled as an obstruction, with the same physical size as the burner.
-It was modelled with a steady state heat release rate of 888.89 kW/sq m.
+It was modeled with a steady state heat release rate of 888.89 kW/sq m.
 The chosen fuel reaction was `methane’ since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.

### 2016-09-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Compartment Corner Burner
Added NG and GAS images and refs.

@@
 
+Compartment experiments with the burner positioned in or near the corner were conducted with the open back wall construction.
+The purpose of moving the burner position toward the corner was to examine the effect of reducing the available air entrainment area around the perimeter of the burner on the resulting fire pattern.
+With the burner tight against both walls, the air entrainment perimeter was reduced by 50~\%.
+Previous studies on flame height with fires in corners have demonstrated the the flame height increased when compared to a similar fire positioned against a single wall or burning in the open~\cite{Poreh:1999,Saito:1993,Takahashi:1997,Kokkala:1993}.
+The previous studies measured temperatures, heat flux, and mass flow rates for the purpose of developing correlations to predict flame height.
+The sole purpose of these experiments is to examine the fire patterns that result from well characterized fires on painted gypsum wall board.
+
 \subsection{Experimental Arrangement}
 
+The compartment used for the corner position experiments was the same as the comapartment used for the wall positions experiments detailed in the previous section.
+The burner was positioned in the left, rear corner against the face of two pieces of painted gypsum wallboard.
+As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
+The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
+The natural gas had a 300~s burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
+By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
+Figure~\ref{GBNG34Sequence} displays a sequence of photographs taken during a natural gas burner corner experiment.
+The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.
+The grid drawn on the corner extends to 1.5 m above the top of the burner.
+
+\begin{figure}[p]
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0990}
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0991}
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0992} \\
+
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0993}
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0994} 
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0995} \\
+
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0996}
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0997}
+	\includegraphics[width=1.7in]{../Figures/GBNG34_SequenceIMG_0998} \\
+
+	\caption[Photograph sequence of a natural gas burner positioned in a corner.]{Photograph sequence of a natural gas burner positioned in a corner. The photographs were taken 0.2 of second apart.}
+	\label{GBNG34Sequence}
+\end{figure}
+
+Figure~\ref{GBGas10Sequence} displays a sequence of photographs taken during a gasoline burner corner experiment.
+The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.
+
+\begin{figure}[p]
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2046}
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2047}
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2048} \\
+
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2049}
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2050} 
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2051} \\
+
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2052}
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2053}
+	\includegraphics[width=1.7in]{../Figures/GBGAS10_IMG_2054} \\
+
+	\caption[Photograph sequence of a gasoline burner positioned in a corner.]{Photograph sequence of a gasoline burner positioned in a corner. The photographs were taken 0.2 of second apart.}
+	\label{GBGas10Sequence}
+\end{figure}
+
 \subsection{Results}
@@
 \subsubsection{Natural Gas}
+
+Figure~\ref{NG_Corner} shows a comparison of the ten fire patterns generated by the natural gas burner in the corner position with walls of open back construction.
+
+\begin{figure}[p]
+	\includegraphics[width=1.0in]{../Figures/GBNG34_P5150482}
+	\includegraphics[width=1.0in]{../Figures/GBNG35_IMG_9166}
+	\includegraphics[width=1.0in]{../Figures/GBNG36_IMG_9181}
+	\includegraphics[width=1.0in]{../Figures/GBNG37_IMG_9194}
+	\includegraphics[width=1.0in]{../Figures/GBNG38_IMG_9208} \\
+
+	\includegraphics[width=1.0in]{../Figures/GBNG39_IMG_9222}
+	\includegraphics[width=1.0in]{../Figures/GBNG40_IMG_9235}
+	\includegraphics[width=1.0in]{../Figures/GBNG41_IMG_9249}
+	\includegraphics[width=1.0in]{../Figures/GBNG42_IMG_9262}
+	\includegraphics[width=1.0in]{../Figures/GBNG43_IMG_9275} \\
+
+	\caption[Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner]{Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner.}
+	\label{NG_Corner}
+\end{figure}
+
 \subsubsection{Gasoline}
@@
 Needed?
-
+{}
 \chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}

### 2016-09-06 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor changes to hose stream + gas burner reports
Updated event drawings + added callouts for open doorways in dimensioned drawings

@@
 \end{minipage}
-\caption{Tests~2-4 layout and event times.}
+\caption{Tests~2--4 layout and event times.}
 \label{fig:Tests_2-4_layout}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_22}
-	\includegraphics[width=0.98\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
+	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_22}
 \end{minipage}
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/West_Structure_2nd_Floor_Test_24}
-	\includegraphics[width=0.97\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
+	\includegraphics[width=0.95\columnwidth]{../Figures/Floor_Plans/West_Structure_1st_Floor_Test_24}
 \end{minipage}

### 2016-09-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Resized Gas Corner images and added to tex file

@@
 Their assistance was essential.
-Their patience and attention to detail during this study is greatly appreciated
+Their patience and attention to detail during this study is greatly appreciated.
 
@@
 \subsubsection{Gasoline}
+
+Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fuleed burner in the corner position with walls of open back construction.
+
+\begin{figure}[p]
+	\includegraphics[width=1.3in]{../Figures/GBGas1C_P5270387}
+	\includegraphics[width=1.3in]{../Figures/GBGas2C_P5270454}
+	\includegraphics[width=1.3in]{../Figures/GBGas5C_P5270493}
+	\includegraphics[width=1.3in]{../Figures/GBGas6C_P5270526} \\
+
+	\includegraphics[width=1.3in]{../Figures/GBGas7C_P5270587}
+	\includegraphics[width=1.3in]{../Figures/GBGas8C_P5270629}
+	\includegraphics[width=1.3in]{../Figures/GBGas9C_P5270689}
+	\includegraphics[width=1.3in]{../Figures/GBGas10C_IMG_9818} \\
+
+	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner.}
+	\label{Gas_Corner}
+\end{figure}
+
 \subsubsection{Polyurethane Foam}

### 2016-09-07 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Updated Inventor files for new burner report drawings; minor edits to Sect. 2.1 in burner report

@@
 Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}.
-Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
+Tongue and groove OSB of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
 
@@
 The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
-The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
+The exterior walls were protected with 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
 

### 2016-09-07 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Updated Inventor files for new burner report drawings; minor edits to Sect. 2.1 in burner report

@@
 
-The interior walls of the first floor of each structure were framed with steel studs set to 400~mm (16~in) centers and track.
+All first floor exterior doors were made of steel.
+The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track.
 Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
-Additionally, the ceiling was composed of two layers of 13~mm (0.5~in) thick cement board.
+The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
 \FloatBarrier
 
-The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs) with a 298~mm (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web as shown in Fig.~\ref{fig:TJI}.
-Tongue and groove oriented strand board of 18.3~mm (0.72~in) thickness was screwed to the top of the TJIs.
+The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs).
+Each TJI had a depth of 298~mm (11.75~in) and contained laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}.
+A layer of 18.3~mm (0.72~in) thick tongue and groove OSB was attached to the top of the TJIs.
 
@@
 \subsubsection{Second Floor of West Structure}
-The second floor of the West Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The second story walls were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
-Two layers of 16~mm (0.63~in) Type X gypsum board lined the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
-The exterior walls were protected with 11~mm (0.44~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
+The second floor of the West Structure was built on the structure's first floor wood ceiling support.
+The two floors were connected by a stairwell.
+A door made of lauan plywood was located at the top of the stairwell.
+The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
+The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board.
+The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
+
+\subsubsection{Leakage}
+An air leakage measurement system was used to measure the amount of leakage associated with each structure.
+The amount of leakage in the East Structure was measured as 0.024~m$^2$.
+For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.
 
@@
 
-\subsubsection{Dimensions}
+% \subsubsection{Dimensions}
 Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
@@
 
-The ceiling height of each structure was approximately 2.4~m (8~ft).
+% The ceiling height of each compartment within the structures was approximately 2.4~m (8~ft).
 The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
 The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run.
-The exterior doors of both structures, the stairwell door on the second level of the West Structure, and the square roof vent in the East Structure with a 1.2~m (4~ft) side length and 320~mm (12.75~in) depth were opened and closed at certain instances during experiments to change the ventilation patterns within the structures.
-The exterior doors were made of steel, and the stairwell door on the second level of the West Structure was made of lauan plywood.
+
+The exterior doors of both structures, the stairwell door in the West Structure, and the square roof vent with a depth of 320~mm (12.75~in) in the East Structure were opened and closed at certain instances during the experiments to change the ventilation patterns within the structures.
+
+% The exterior doors were made of steel and the stairwell door on the second level of the West Structure was made of lauan plywood.
 % The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to
-
-\subsubsection{Leakage}
-An air leakage measurement system was used to measure the amount of leakage associated with each structure.
-The amount of leakage in the East Structure was measured as 0.024~m$^2$.
-For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.
 
@@
 Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
-The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent and contained three probes centered between the east and west sides of the vent.
+The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent, 320~mm (12.75~in) above the compartment ceiling.
+The array contained three probes centered between the east and west sides of the vent.
 The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}.
-The total heat flux gauge/radiometer pairs were set to be aimed to view the ceiling.
+The total heat flux gauge/radiometer pairs were aimed to view the ceiling.
 Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing.

### 2016-09-11 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added Summary Tables to Ch 3 and 4
Also added data and new point source graphic

@@
   \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
+  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
   \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
-  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
   \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
@@
 
-A review of the graphs of the peak average temperatures at the wall, burner centerline array, shows that all of the fuels had at least one thermocouple position with a peak of approximately 500~$^{\circ}$C when the burner was against the wall.
-At 0.15~m away from the wall the peak average temperature from this data set was provided by the gasoline fueled fire and it was approximately 350~$^{\circ}$C.
-Based on temperature alone, the fires examined would only have the potential to ignite the paper surface of the gypsum wallboard when the burner was in contact with the wall.
-The peak average temperatures at the wall, burner edge array, would indicate that the paper may not ignite at the burner edge.
-The peak average temperature of approximately 400~$^{\circ}$C was generated by the gasoline fueled fire when the burner was positioned against the wall.
+A summary of the peak average temperatures and heat fluxes at the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.
+Based on the temperature criteria for igniting gyspum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
+Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria, when positioned against the wall and at when the edge of the burner was 0.15~m away from the wall.
+
+\begin{table}
+	\centering
+	\footnotesize
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
+		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
+		\hline \hline 0.61~m & 95 & 5 & 106 & 7 & 71 & 6 \\
+		\hline 0.31~m & 164 & 14 & 232 & 24 & 148 & 16	\\
+		\hline 0.15~m & 257 & 33 & 356 & 45 & 266 & 39	\\
+		\hline 0.00~m & 487 & 43 & 621 & 70 & 526 & 65 	\\
+		\hline
+	\end{tabular}
+	\caption[Summary of instrumented non-combustible wall experiments]{Summary of peak temperatures and heat fluxes from the instrumented non-combustible wall experiments}
+	\label{tab:TW_Summary}
+\end{table}
 
 Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material.
-Assuming that the properties of calcium silicate board and the gypsum board are similar, the heat flux graphs were reviewed to see where the heat flux exceeded 35~kW/m$^2$.
-All of the fuels generated heat fluxes in excess of 35~kW/m$^2$ at the burner centerline array when the burners were against the wall.
-The gasoline and the polyurethane fueled burners also exposed the wall to heat fluxes higher than 35~kW/$^2$ at 0.15~m from the wall.
+The properties of the calcium silicate board are simlar but not identical to gypsum wallboard.
+The heat flux data is independent of the wall material, so it may be a better predictor of the fire damage to gypsum wallboard when exposed to the burners at different distances.
+All of the fuels generated heat fluxes in excess of 26~kW/m$^2$.
 However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
+The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wall board ignites.
 
@@
 		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\
-		\hline 0.61 				& 0 				& 1 				& 2 			 	\\
+		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
 		\hline 0.31					& 3	 				& 1					& 2 			 	\\
@@
 \end{figure}
+
+A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.
+
+\begin{table}
+	\centering
+	\footnotesize
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
+		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
+		\hline \hline 0.61~m & 132 & 4 & 109 & 6 & 76 & 4 \\
+		\hline 0.31~m & 160 & 11 & 185 & 18 & 151 & 12	\\
+		\hline 0.15~m & 250 & 23 & 377 & 57 & 244 & 25	\\
+		\hline 0.00~m & 539 & 55 & 590 & 61 & 415 & 59 	\\
+		\hline
+	\end{tabular}
+	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments}
+	\label{tab:IWGB_Summary}
+\end{table}
 
@@
 Needed?
+
 {}

### 2016-09-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Continue to fill gaps in Ch 4 and 6

@@
 For the gasoline fire experiment at the 0.08~m position the wall temperatures and the heat flux values from the burner edge array had values that were higher than when those measured at the 0.0~m position.
-The peak heat release rates for the positions at 0.0~m, 0.08~m and 0.15~m were 120~kW, 110~kW, and 110~kW respectively.
-So it does not seem that a change in HRR was the source of the increase.
+The peak heat release rates for the positions at 0.0~m, 0.08~m and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
+So a change in HRR was not the source of the increase.
+The increased temperatures and heat flux at this position appears to be a matter of the flame movement toward the wall.
+In general, once the burner position for either natural gas or gasoline was within 0.15~m, or half the distance of the burner side dimension, the flames tended to pull toward the wall.
+This motion was not a steady motion but an oscillatory one.
 
@@
 
+Figure~\ref{IWGBGAS6_seq} shows a comparison of a series eight photographs from the experiment where the gasoline burner was positioned 0.15~m from the instrumented gypsum wallboard.
+The photographs capture both the oscillatory motion of the flame toward the wall and the burning of the gases which are pyrolyzing off of the wall and result in the formation of the lower edge of the fire pattern.
+
+\begin{figure}[p]
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq1}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq2}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq3}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq4} \\
+
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq5}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq6}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq7}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq8} \\
+
+	\caption[Photographs of the fire pattern formation from the gasoline burner positioned 0.15~m from the wall]{Photographic sequence of the fire pattern formation from the gasoline burner positioned 0.15~m from the instrumented gypsum wallboard.}
+	\label{IWGBGAS6_seq}
+\end{figure}
+
 \begin{figure}[p]
@@
 The impact is limited to a small distance ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
-This effect is shown in Figure~\ref{FRP_flamefront}.
-In Figure~\ref{FRP_flamefront} several thermocouples can be seen.
+This effect is shown in Figure~\ref{FRP_flamefront_arrows}.
+In Figure~\ref{FRP_flamefront_arrows} several thermocouples can be seen.
 The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the painted paper face made with a razor blade.
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/FRP_flamefront} \\
+	\includegraphics[width=\textwidth]{../Figures/FRP_flamefront_arrows} \\
 	\caption[Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel] {Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel.
@@
 The flame is leaning back in the direction the radiant panel.}
-	\label{FRP_flamefront}
+	\label{FRP_flamefront_arrows}
 \end{figure}
@@
 The temperatures prior to ignition ranged from an average of 315 $^{\circ}$C for the 100~mm position to 242 $^{\circ}$C for the 400~mm position.
-The average
 

### 2016-09-14 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
add table for FDS RI Comp

@@
   \centering
-  \includegraphics[width=3.5in]{../Figures/FHNG_TC_Plume_Avg}\\
-  \includegraphics[width=3.5in]{../Figures/FHGAS_TC_Plume_Avg}\\
-  \includegraphics[width=3.5in]{../Figures/FHPUF_TC_Plume_Avg}\\
+  \includegraphics[width=.625\columnwidth]{../Figures/FHNG_TC_Plume_Avg}\\
+  \includegraphics[width=.625\columnwidth]{../Figures/FHGAS_TC_Plume_Avg}\\
+  \includegraphics[width=.625\columnwidth]{../Figures/FHPUF_TC_Plume_Avg}\\
   \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
@@
   \centering
-  \includegraphics[width=3.5in]{../Figures/HF_NG}\\
-  \includegraphics[width=3.5in]{../Figures/HF_GAS}\\
-  \includegraphics[width=3.5in]{../Figures/HF_PUF}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_NG}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_GAS}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF}\\
   \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
@@
      \hline
-     Fuel	            & Mean (m)  & Range (m) \\ \hline
+     Fuel	            & Mean (m)  & Range (m) \\ \hline \hline
      Natural Gas	    & 0.70	    & 0.50 to 0.98 \\
@@
 Visible         &   \multicolumn{3}{|c|}{Visible Flame Heights (mm)} \\ \cline{2-4}
-Fraction (\%)   &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline
+Fraction (\%)   &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
 10              &       980 $\pm$ 155 (16~\%)   &	930 $\pm$ 130 (14~\%) 	& 650 $\pm$ 220 (34~\%)   \\
@@
 	\hline Density & \multicolumn{2}{c|}{Thermal Conductivity} & \multicolumn{2}{c|}{Specific Heat}   \\
-    \hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\
+	\hline (kg/m$^3$) & Temperature ($^\circ$C) & (W/mK)  & Temperature ($^\circ$C)  & (kJ/kg $^\circ$C) \\ \hline
 	\hline 737  & 24 & 0.13 & 93 & 0.28 \\
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_PUF_TC_Surface_Center_Avg}\\
 	\caption[Composite graph of the wall temperatures along the centerline of the burners]{Composite graph of the wall temperatures along the centerline of the burners for each fuel.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Surface_Offset_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Surface_Offset_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_NG_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_GAS_TC_Surface_Offset_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_PUF_TC_Surface_Offset_Avg}\\
 	\caption[Composite graph of the wall temperatures along the edge of the burners]{Composite graph of the wall temperatures along the edge of the burners for each fuel.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/NCTW_NG_TC_Back_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_TC_Back_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_NG_TC_Back_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_GAS_TC_Back_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_PUF_TC_Back_Center_Avg}\\
 	\caption[Composite graph of the backside wall temperatures along the center of the burners]{Composite graph of the backside wall temperatures along the vertical centerline of the burners for each fuel.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Center_Avg} \\
-	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Center_Avg} \\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_NG_HF_Center_Avg} \\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_GAS_HF_Center_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_PUF_HF_Center_Avg} \\
 	\caption[Wall heat flux along the centerline of the burners]{Wall heat fluxes along the centerline of the burners.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/NCTW_NG_HF_Offset_Avg} \\
-	\includegraphics[width=3.5in]{../Figures/NCTW_GAS_HF_Offset_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/NCTW_PUF_HF_Offset_Avg} \\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_NG_HF_Offset_Avg} \\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_GAS_HF_Offset_Avg}\\
+	\includegraphics[width=.6\columnwidth]{../Figures/NCTW_PUF_HF_Offset_Avg} \\
 	\caption[Wall heat flux along the edge of the burners]{Wall heat fluxes along the edge of the burners.
@@
 		\hline Density & \multicolumn{2}{c|}{Thermal Conductivity}   & \multicolumn{2}{c|}{Specific Heat}  \\
-		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\
+		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\ \hline
 		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\
@@
 		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
-		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\
+		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ \hline
 		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Plume_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Plume_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Plume_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Plume_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Plume_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Plume_Avg}\\
 	\caption[Plume temperatures for the natural gas fueled burner]{Plume temperatures along the centerline of the natural gas fueled burner.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Surface_Center_Avg}\\
 	\caption[Front surface wall temperatures for the natural gas fueled burner]{Front surface wall temperatures for the natural gas fueled burner.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGBNG01_TC_Back_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG04_TC_Back_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGBNG05_TC_Back_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_TC_Back_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_TC_Back_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_TC_Back_Center_Avg}\\
 	\caption[Backside wall temperatures for the natural gas fueled burner]{Backside wall temperatures along the centerline of the natural gas fueled burner.
@@
  	\centering
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG01_HF_Center_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG04_HF_Center_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG05_HF_Center_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Center_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Center_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Center_Avg}\\
  \caption[Wall heat flux along the centerline of the natural gas fueled burner]{Wall heat flux along the vertical centerline of the natural gas fueled burner.
@@
  	\centering
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG01_HF_Offset_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG04_HF_Offset_Avg}\\
- 	\includegraphics[width=3.5in]{../Figures/IWGBNG05_HF_Offset_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Offset_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Offset_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Offset_Avg}\\
  	\caption[Wall heat flux along the edge of the natural gas fueled burner]{Wall heat flux along the edge of the natural gas fueled burner.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
 	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
 	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_GAS_TC_Surface_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_PUF_TC_Surface_Center_Avg}\\
 	\caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperatures, beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Center_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_GAS_HF_Center_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_PUF_HF_Center_Avg}\\
 	\caption[Averaged burner centerline heat flux for the natural gas, gasoline, and foam fires]{Averaged burner centerline heat flux, beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
@@
 	\centering
-	\includegraphics[width=3.5in]{../Figures/IWGB_NG_HF_Offset_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
-	\includegraphics[width=3.5in]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_GAS_HF_Offset_Avg}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_PUF_HF_Offset_Avg}\\
 	\caption[Averaged burner edge heat flux for the natural gas, gasoline, and foam fires]{Averaged burner edge heat flux for the natural gas, gasoline, and foam fires, from the top down.}
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition &  Fire Effect  \\
-		\hline (kW/m$^2$) &  & (s)  &   \\
+		\hline (kW/m$^2$) &  & (s)  &   \\ \hline
 		\hline 25	& No 	& NA 		& Paint \& paper charred \& cracked \\
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ \hline
 		\hline 30 	& Yes 	& 112	& 375 	 \\
@@
 	\centering
+	\small
 	\begin{tabular}{|c|c|c|c|c|}
 		\hline Postion & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\
+		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ \hline
 		\hline 100 	& 21	& Yes 	& 133	& 315 	 \\
@@
 		\hline Incident Heat Flux & Heat Release Rate per Unit Area    \\
-		\hline (kW/m$^2$) & (kW/m$^2$)  \\
+		\hline (kW/m$^2$) & (kW/m$^2$)  \\ \hline
 		\hline 35 	& 163 	\\
@@
 	\hline
-	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline
+	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline \hline
 		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\
@@
 The burner was modeled as an obstruction, with the same physical size as the burner.
-It was modeled with a steady state heat release rate of 888.89 kW/sq m.
-The chosen fuel reaction was `methane’ since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.
+It was modeled with a steady state heat release rate of 888.89 kW/m$^2$.
+The chosen fuel reaction was `methane' since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.
 
@@
 \subsection{Grid Size Analysis}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
+		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 207					   & 367					& 316 			 	\\
+		\hline 0.4			   & 518					   & 415					& 388			 	\\
+		\hline 0.6			   & 487					   & 445					& 434			 	\\
+		\hline 0.8			   & 368					   & 393					& 401				\\
+		\hline 1.0			   & 284					   & 326 					& 338				\\
+		\hline 1.2			   & 189					   & 226 					& 247				\\
+		\hline 1.4			   & 150					   & 167 					& 177				\\
+		\hline 1.6			   & 113					   & 126 					& 127				\\
+		\hline 1.8			   & 97						   & 100 					& 96				\\
+		\hline 2.0			   & 81						   & 82 					& 77				\\
+		\hline 2.2			   & 72						   & 71 					& 66				\\
+		\hline
+	\end{tabular}
+	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m}
+	\label{tab:FDSRI_wall0D}
+\end{table}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
+		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 219					   & 182					& 158 			 	\\
+		\hline 0.4			   & 310					   & 232					& 217			 	\\
+		\hline 0.6			   & 272					   & 231					& 250			 	\\
+		\hline 0.8			   & 192					   & 189					& 241				\\
+		\hline 1.0			   & 152					   & 149 					& 204				\\
+		\hline 1.2			   & 113					   & 104 					& 150				\\
+		\hline 1.4			   & 96						   & 82 					& 111				\\
+		\hline 1.6			   & 79						   & 69 					& 87				\\
+		\hline 1.8			   & 70						   & 61 					& 72				\\
+		\hline 2.0			   & 60						   & 55 					& 64				\\
+		\hline 2.2			   & 51						   & 52 					& 58				\\
+		\hline
+	\end{tabular}
+	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m}
+	\label{tab:FDSRI_wallp5D}
+\end{table}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
+		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 143					   & 132					& 109 			 	\\
+		\hline 0.4			   & 180					   & 165					& 142			 	\\
+		\hline 0.6			   & 158					   & 165					& 161			 	\\
+		\hline 0.8			   & 114					   & 139					& 157				\\
+		\hline 1.0			   & 90						   & 111 					& 136				\\
+		\hline 1.2			   & 66						   & 76 					& 100				\\
+		\hline 1.4			   & 57						   & 59 					& 74				\\
+		\hline 1.6			   & 48						   & 49 					& 58				\\
+		\hline 1.8			   & 44						   & 44 					& 50				\\
+		\hline 2.0			   & 40						   & 42 					& 47				\\
+		\hline 2.2			   & 38						   & 41 					& 45				\\
+		\hline
+	\end{tabular}
+	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m}
+	\label{tab:FDSRI_wall1D}
+\end{table}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|}
+		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
+		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 88						   & 69						& 59 			 	\\
+		\hline 0.4			   & 103					   & 82						& 74			 	\\
+		\hline 0.6			   & 95						   & 81						& 78			 	\\
+		\hline 0.8			   & 76						   & 74						& 76				\\
+		\hline 1.0			   & 64						   & 64 					& 67				\\
+		\hline 1.2			   & 50						   & 51 					& 55				\\
+		\hline 1.4			   & 43						   & 42 					& 45				\\
+		\hline 1.6			   & 36						   & 35 					& 37				\\
+		\hline 1.8			   & 32						   & 30 					& 31				\\
+		\hline 2.0			   & 28						   & 27 					& 28				\\
+		\hline 2.2			   & 26						   & 25 					& 26				\\
+		\hline
+	\end{tabular}
+	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m}
+	\label{tab:FDSRI_wall2D}
+\end{table}
 

### 2016-09-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 9 tables
Ch 9 comparison tables

@@
 An FDS model was developed to simulate the instrumented wall experiments with the natural gas burner.
+One of the key determinations that is required when developing an FDS model is the mesh or grid cell size.
+If a single plane of the data from the model were compared to a digital image we might refer to the grid cell size as the resolution of the image.
+The smaller the grid cells the better the resolution.
+However increased resolution or the smaller grid cell size, the longer it will take the simulation to run.
+
+For simulations involving buoyant plumes, a measure of how well the flow field is resolved is given by the non-dimensional expression $D^*/\dx$, where $D^*$ is a characteristic
+fire diameter
+
+\begin{equation}
+ D^* = \left(
+     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
+     \right)^\frac{2}{5} 
+ \end{equation}
+
+and $\dx$ is the nominal size of a mesh cell.
+
+The characteristic fire diameter is related to the characteristic fire size via the
+relation $Q^* = (D^*/D)^{5/2}$, where $D$ is the physical diameter of the
+fire.}.
+The quantity, $\dQ$, is the total heat release rate of the fire.
+If it changes over time, you should consider the corresponding change in resolution.
+The quantity $D^*/\dx$ can be thought of as the number of computational cells spanning the characteristic (not necessarily the physical) diameter of the fire.
+
 Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.
@@
 It was modeled with a steady state heat release rate of 888.89 kW/m$^2$.
-The chosen fuel reaction was `methane' since the majority <<<check percentage>> of the natural gas used in the laboratory experiments was methane.
+The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.
 
@@
 
-Compare Natural Gas at 0.61~m from instrumented wall and at 0.0~m from instrumented wall - problem bounds.
+In Chapter 2 the fires from the burners were characterized.
+In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
+The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will compared.
+Two burner positions are examined, 0.61~m from the wall and 0.0~m from the instrumented gypsum wallboard wall.
 
 \subsection{Grid Size Analysis}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
+		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
+		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
+		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
+		\hline 0.8			   & 442						& 600					& 522			& 198	\\
+		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
+		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
+		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
+		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
+		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
+		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
+		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
+		\hline
+	\end{tabular}
+	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.61~m from the Wall]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
+	\label{tab:FDSRI_Exp_Plume2d}
+\end{table}
+
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
+		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 458						& 604					& 658 			& 667 	\\
+		\hline 0.4			   & 751					   	& 824					& 793			& 643 	\\
+		\hline 0.6			   & 668						& 711					& 673			& 577 	\\
+		\hline 0.8			   & 519						& 575					& 581			& 353	\\
+		\hline 1.0			   & 431						& 475 					& 506			& 357	\\
+		\hline 1.2			   & 326						& 357 					& 406			& 306	\\
+		\hline 1.4			   & 274						& 285 					& 322			& 233	\\
+		\hline 1.6			   & 218						& 234 					& 257			& 201	\\
+		\hline 1.8			   & 191						& 198 					& 211			& 179	\\
+		\hline 2.0			   & 162						& 170 					& 178			& 150	\\
+		\hline 2.2			   & 146						& 148 					& 153			& 140	\\
+		\hline
+	\end{tabular}
+	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.0~m from the Wall.]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.0~m from the Wall.}
+	\label{tab:FDSRI_Exp_Plume0d}
+\end{table}
 
@@
 
+\begin{table}
+	\small
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
+		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
+		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
+		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
+		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
+		\hline 0.8			   & 442						& 600					& 522			& 198	\\
+		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
+		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
+		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
+		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
+		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
+		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
+		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
+		\hline
+	\end{tabular}
+	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
+	\label{tab:FDSRI_Exp_Plume}
+\end{table}
+
 \subsection{Heat Flux}

### 2016-09-17 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch X

@@
 
-As you begin to examine the scene, you walk around the exterior and note that on the front of the end unit, townhouse, there is fire damage on the exterior above the front door opening that extends across the ceiling of the porch.
+As you begin to examine the scene, you walk around the exterior and note that on the front of the end unit townhouse, there is fire damage on the exterior above the front door opening that extends across the ceiling of the porch.
 The is some thermal damage and smoke deposits on the from of the siding on the porch.
-There outer pane of the living room window is for the most part still intact.
+The outer pane of the living room window is for the most part still intact.
 you notice that three of the four windows on the second floor have been removed.
-On the ``D side'' of the townhome there are no openings and no smoke or fire damage is present.
-On the rear or ``Side C'' of the house the door and windows are intact but open.
+On ``side D'' of the townhome there are no openings and no smoke or fire damage is present.
+On the rear or ``side C'' of the house the door and windows are intact but open.
 There is no smoke stains or thermal damage around any of the openings on the rear.
@@
 The living room has extensive fire damage.
-Looking to your right, two chairs infront of the living room window have some thermal damage.
+Looking to your right, two chairs in front of the living room window have some thermal damage.
 There are a clear horizontal line of demarcation the large wood TV stand in the corner.
@@
 You return to the living room and walk up the stairs.
-Their is evidence of paint and paper burned off of the gypsum wallboard in the stairway.
-The fire damage doe not extend beyond the top of the stairs.
-there is smoke damage in the upstairs hallway an in the front bedrooms.
+There is evidence of paint and paper burned off of the gypsum wallboard in the stairway.
+The thermal damage does not extend beyond the top of the stairs.
+There is smoke damage in the upstairs hallway and in the front bedrooms.
 The further you move from the stairs the less damage you find.
@@
 The same is true from the left side of the sofa.
-The corner formed by the wall behind and the wall of the stairway has a ``V pattern'' burned into it, from the floor and extending up toward the ceiling.
+The corner formed by the wall behind the chair and the wall of the stairway has a ``V pattern'' burned into it, from the floor and extending up toward the ceiling.
 As you look at the debris surrounding the chair, you notice the remains of an electric heater.
-The wire from the heater extends toward the wall outlet behind the sofa.
-
-You have no developed your first hypothesis about the origin of the fire.
+The burned wire from the heater extends toward the wall outlet behind the sofa.
+
+You have now developed your first hypothesis about the origin of the fire.
 A radiant style, electric heater was turned on and left until it ignited the fabric on the sofa or chair.
-You collect the remains of the heater for further examination to have a lab determine of the heater switch was in the ``on'' position.
-No you need to start testing your hypothesis.
+You collect the remains of the heater for further examination to have a lab determine if the heater switch was in the ``on'' position.
+Now you need to start testing your hypothesis.
 Is everything consistent with the other fire damage?
@@
 There are pieces of charred newspaper near the right arm of the sofa.
-The burn mark on the top of the wood coffee looks like a arrow that is pointing toward the corner.
+The burn mark on the top of the wood coffee table looks like a arrow that is pointing toward the corner.
 The char on the legs of the coffee table is very directional and consistent with the heat coming from the corner.
@@
 
-For simulations involving buoyant plumes, a measure of how well the flow field is resolved is given by the non-dimensional expression $D^*/\dx$, where $D^*$ is a characteristic
-fire diameter
-
-\begin{equation}
- D^* = \left(
-     \frac{\dQ}{\rho_\infty \, c_p \, T_\infty \, \sqrt{g} }
-     \right)^\frac{2}{5} 
- \end{equation}
-
-and $\dx$ is the nominal size of a mesh cell.
-
-The characteristic fire diameter is related to the characteristic fire size via the
-relation $Q^* = (D^*/D)^{5/2}$, where $D$ is the physical diameter of the
-fire.}.
-The quantity, $\dQ$, is the total heat release rate of the fire.
-If it changes over time, you should consider the corresponding change in resolution.
-The quantity $D^*/\dx$ can be thought of as the number of computational cells spanning the characteristic (not necessarily the physical) diameter of the fire.
-
 Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.
@@
 
+\subsection{The Fire Investigators' Challenge}
+
+While you are reviewing the scene you meet up with the fire captain and begin asking him about the fire.
+The captain tells you that the doors and windows were closed upon arrival.
+When the front door was opened heavy smoke
+
 \chapter{Future Research Needs}
 
+degradation of gypsum board full scale
+
+Use of black paint
+
+Calcination depth
+
+Larger variation of heat release rates
+
+Realistic fuels
+
 \chapter{Conclusions}
+
+Repeatibilty
+Energy to Damage
+Flame Height
+Modeling
 

### 2016-09-18 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Updated FDS refs, comment fixes

@@
 
-\chapter{Summary of Experimental Results}
-
-Needed?
-
-{}
 \chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}
 
-In this chapter the application of empirical algebraic fire characterizations will be examined.
+Over the years, fire researchers have provided many methods for predicting flame characteristics such as: median flame height, plume temperatures and an estimation of the heat flux emitted.
+These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,FDS_Users_Guide},FDS_Tech_Guide}
+
+In this chapter the application of empirical algebraic flame characterizations will be compared against the results from the experiments documented in Chapter 2 and 4.
 Two different types of applications will be used.
@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-Applications of algorithms such as these are presented in current fire investigation textbooks~\cite{Icove:2013}.
+Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999}}.
 
@@
 	\caption{Schematic of heat flux estimation using the point source assumption}
-	\label{PointSourceHF}
-\end{figure}
+	\label{PointSourceHF},
+\end{figure},
 

### 2016-09-19 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Completed Summary table chapter 2

@@
 \dedication{To my wife and family}
+
+\tableofcontents
+
+\listoffigures
+
+\listoftables
+
+\acknowledgments{
+I would like to thank Prof.~Fleischmann, my senior advisor with the University of Canterbury, as well as, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
+
+The full-scale and bench-scale experiments were conducted over a period of several years whenever funding and laboratory availability coincided.
+These experiments were conducted with the support of several engineering technicians from the NIST Fire Research Division, especially Roy McLane, Jay McElroy, Laurean DeLauter, and Anthony Chakalis.
+Their assistance was essential.
+Their patience and attention to detail during this study is greatly appreciated.
+
+This work was partially funded by the National Institute of Justice (NIJ) through an inter-agency agreement with the NIST Office of Law Enforcement Standards (OLES).
+I would like to thank Susan Ballou of OLES for her support of this project.
+This work was also partially supported by the U.S.
+Fire Administration.
+
+I would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury
+
+Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 37 years of marriage.
+I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for ``buying me time'' to work on my studies.}
 
@@
 
-\tableofcontents
-
-\listoffigures
-
-\listoftables
-
-\acknowledgments{
-I would like to thank Prof.~Fleishmann, my senior advisor with the University of Canterbury, as well as, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
-
-The full-scale and bench-scale experiments were conducted over a period of several years whenever funding and laboratory availability coincided.
-These experiments were conducted with the support of several engineering technicians from the NIST Fire Research Division, especially Roy McLane, Jay McElroy, Laurean DeLauter, and Anthony Chakalis.
-Their assistance was essential.
-Their patience and attention to detail during this study is greatly appreciated.
-
-This work was partially funded by the National Institute of Justice (NIJ) through an inter-agency agreement with the NIST Office of Law Enforcement Standards (OLES).
-I would like to thank Susan Ballou of OLES for her support of this project.
-This work was also partially supported by the U.S.
-Fire Administration.
-
-I would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury
-
-Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 37 years of marriage.
-I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for ``buying me time'' to work on my studies.}
+\begin{table}[t!]
+  \centering
+  \begin{tabular}{l|l}
+  	Abbreviations \\
+     \hline
+     HRR	            & heat release rate (kW) \\
+     NIST        	    & National Institute of Standards and Technology (US) \\
+     PUF                & polyurethane foam  \\
+     $\dot{q}''$        & heat flux per unit area kW/m$^2$ \\
+	 $\dot{Q}$          & heat release rate (kW) \\ 
+	 $\chi_r$           & radiative fraction \\
+	 $R$                & distance from the point source to the target (m) \\
+   \end{tabular}
+ \end{table}
 
@@
 
-The source fires have been characterized in terms of heat release rate, plume temperature, total heat flux, mass loss and flame height.
+The source fires have been characterized in terms of heat release rate, total heat release, plume temperature, total heat flux, mass loss and flame height.
+Table~\ref{tab:Source_fire_summary} is a summary of the average peak heat release rate, the total heat released, the average peak heat flux, the median flame height and the average peak temperature at the thermocouple closest to the median flame height.
+In the table each of the measurements is show with the 95~\% confidence limits.
 This data has been collected for use in direct analysis of the burn patterns and as input into the engineering correlations and FDS models that are used later in this study.
+
+\begin{table}
+\small
+\centering
+\begin{tabular}{|l|c|c|c|}
+\hline
+Measurement     &   \multicolumn{3}{|c|}{Fuels} \\ \cline{2-4}
+type                    &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
+Avg. Peak HRR (kW)      &       80 $\pm$ 9 (11~\%)   &	80 $\pm$ 24 (30~\%) 	& 45 $\pm$ 21 (47~\%)   \\
+Total HR (MJ)           &   	23.3 $\pm$ 1.6 (7~\%)   &	13.6 $\pm$ 0.6 (4~\%) 	& 4.1 $\pm$ 0.2 (5~\%)   \\
+Avg Peak HF (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25~\%)   &	3.6 $\pm$ 0.9 (25~\%) 	& 2.5 $\pm$ 0.5 (20~\%)   \\
+Median FH (m)           &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
+Avg Peak Temp. (C)      &   	410 $\pm$ 103 (25~\%)   &	335 $\pm$ 41 (12~\%) 	& 334 $\pm$ 106 (32~\%)   \\
+\hline
+\end{tabular}
+ \caption[Select measurements for the three source fires]{Select measurements for the three source fires.
+Each measurement is shown with 95~\% confidence limits both in terms of a value and a percentage.}
+ \label{tab:Source_fire_summary}
+\end{table}
 
@@
  The initial set of compartment experiments were conducted to examine if the type of wall construction would impact the development of the fire patterns.
-These experiments would determine how the walls for the remaining compartment fire pattern experiments would be constructed.
+These experiments determined how the walls for the remaining compartment fire pattern experiments were constructed.
 Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3) Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
@@
 Over the years, fire researchers have provided many methods for predicting flame characteristics such as: median flame height, plume temperatures and an estimation of the heat flux emitted.
-These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,FDS_Users_Guide},FDS_Tech_Guide}
+These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,FDS_Users_Guide,FDS_Tech_Guide}.
 
@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999}}.
+Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999}.
 

### 2016-09-19 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
added ref, mass flow, number of photos

@@
 
+\subsubsection{Natural Gas Flow}
+
+The natural gas flow to the burner is measured in terms of volumetric flow with a dry test meter, that is corrected for temperature and pressure.
+The flow rate was determined to be 4.5 cubic feet per minute as output from the meter or 2.1~liters per second.
+This yields a mass flow of natural gas of approximately 2~g/s.
+
 \subsubsection{Video and Photographs}
@@
 Analyzing the photographs in this manner was very time consuming and was based on making measurements on each photograph with a scale.
+Between 6 and 10 seconds of still images, or 30 to 50 frames, were used to approximate the flames heights provided in Table~\ref{tab:Flame_Heights}.
 The limit of 5 frames per second also introduces additional uncertainty in determining the flame height.
@@
 Schroder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
-The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction  add Schroder.
-NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dyhydrated gypsum to map fire patterns.
+The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction~\cite{Schroeder:1999}.
+NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dihydrated gypsum to map fire patterns.
 

### 2016-09-20 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Minor changes to hose stream report, only missing TN#

@@
 Fire suppression tactics using hose streams can affect ventilation in a structure and may impact the movement of smoke and heat through a structure.
-Seven experimental series containing a total of 154 different configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
-The experiments studied four different hose streams: a straight stream, narrow fog stream, a wide fog stream from a combination nozzle, and a solid stream from a smooth bore nozzle.
+Seven experimental series containing a total of 154 configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
+The experiments studied four different hose streams: a straight stream, narrow fog stream, and a wide fog stream from a combination nozzle and a solid stream from a smooth bore nozzle.
 The streams were applied from a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
 Gas velocity was measured at different locations in the structure during the experiments.
-The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum velocity of 2.6~m/s (5.8~mph) and maximum air flow rate of approximately 4.2~m$^3$/s (9000~cfm), followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
+The wide fog stream caused the most air movement out of any of the tested streams, reaching a maximum velocity of 2.6~m/s (5.8~mph) and maximum air flow rate of approximately 4.8~m$^3$/s (10250~cfm), followed by the narrow fog stream, and then the straight stream and solid stream from the smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
 The data were consistent with a straight stream only causing air movement through the structure when it was applied in a moving pattern.
@@
 The types of streams produced by a combination nozzle are often divided into three categories based on the angle of the stream with respect to the centerline of the nozzle: a straight stream typically produces an angle less than 15\SI{}{\degree}; a narrow fog stream produces an angle between 15\SI{}{\degree} and 45\SI{}{\degree}; and a wide fog stream produces an angle between 45\SI{}{\degree} and 80\SI{}{\degree}~\cite{IFSTA:Essentials_of_FF}.
-Increasing the angle of the stream allows for a larger area to be covered by the water spray.
-However, increasing the angle decreases the distance reached by the stream and its penetration power.
+Increasing the angle of the stream allows for a larger area to be covered by the water spray but also decreases the distance reached by the stream and its penetration power.
 
@@
 Four types of hose streams and four nozzle movement patterns were studied under 154 different configurations during the seven test series described in this report.
-Three of the hose stream patterns studied were from a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
+Three of the hose stream patterns studied used a combination nozzle: straight stream, narrow fog stream, and wide fog stream.
 Water was flowed into the structure by having the hose in a static, or fixed, position; by moving the hoseline left-to-right across the room in a sweeping motion; and by rotating the hoseline in both the clockwise and counterclockwise directions.
-Additionally, experiments comparing the differences in impact on air flows in a structure from a combination nozzle straight stream and a solid stream from a smooth bore nozzle equipped with a 1~in.
+Additionally, experiments comparing the differences in impact on air flows in a structure between a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle equipped with a 1~in.
 tip were conducted.
@@
 The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board.
 The exterior walls were protected with 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
@@
 \label{sec:layout}
-Simple floor plans showing the total length and width of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:east_dimensioned_plan} and Fig.~\ref{fig:west_dimensioned_plan}, respectively.
+Simple floor plans with the total length and width of the Single Story and Two Story Structures are presented in Fig.~\ref{fig:simple_east_dimensioned_plan} and Fig.~\ref{fig:simple_west_dimensioned_plan}, respectively.
 Fully dimensioned floor plan drawings are provided in Appendix~\ref{chap:floor_plans}.
@@
 In order to close these doorways, a sheet of gypsum board was used to cover the opening, and the doorway remained closed for the duration of the test procedure.
-\clearpage
 
@@
 	\caption[Simple floor plan of the Single Story Structure.]{Simple floor plan of the Single Story Structure.}
-	\label{fig:east_dimensioned_plan}
+	\label{fig:simple_east_dimensioned_plan}
 \end{figure}
@@
 	\caption[Simple floor plan of the first and second floors of the Two Story Structure.]{Simple floor plan of the second floor (top) and first floor (bottom) of the Two Story Structure.}
-	\label{fig:west_dimensioned_plan}
+	\label{fig:simple_west_dimensioned_plan}
 \end{figure}
@@
 Three different structure flow path configurations were used for the seven experimental series.
-Tests~1 and 5 were conducted in the Single Story Structure and used a ``U-shaped'' configuration shown in Fig.~\ref{fig:east_setup}.
+Tests~1 and 5 were conducted in the Single Story Structure and used the ``U-shaped'' configuration shown in Fig.~\ref{fig:east_setup}.
 Test~1 used a monitor and combination nozzle to flow water, and Test~5 used a combination nozzle attached directly to a handline to flow water.
-
-Two different flow path configurations were used for the test series conducted in the Two Story Structure.
-The main difference between the two flow paths was the position of the south side door on the first level.
+The two additional flow path configurations were used for the test series conducted in the Two Story Structure.
+The main difference between the two configurations was the position of the south side door on the ground level.
 Tests~2 and 6 used a configuration with the door opened (Fig.~\ref{fig:flow_path_1}), while Tests~3, 4, and 7 used a configuration with the door closed (Fig.~\ref{fig:flow_path_2}).
@@
 First, water was flowed in a straight stream for 30 seconds, then the stream was changed to a narrow fog for 30 seconds, and finally the stream was changed to a wide fog for 30 seconds.
-The procedure was repeated.
+Then, the procedure was repeated an additional time.
 
@@
 	\includegraphics[trim=16cm 6.25cm 9cm 6cm, clip=true, width=4in]{../Figures/Pictures/WF_Room_B_Test_33}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~1.]{Water flowing from the monitor in Room C in a straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the area above the doorway on the south wall of Room B during Test~1 in the Single Story Structure.}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~1.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) from the monitor in Room C aimed at the area above the doorway on the south wall of Room B during Test~1 in the Single Story Structure.}
 	\label{fig:test_1_pic}
@@
 	\caption[Straight stream from combination nozzle and solid stream from smooth bore nozzle with 1~in.
-tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the smooth bore nozzle (right) during Test~4.}
+tip during Test~4.]{Straight stream flowing from the combination nozzle (left) and solid stream flowing from the 1~in.
+tip of the smooth bore nozzle (right) during Test~4 in the Two Story Structure.}
 	\label{fig:test_4_pic}
@@
 handline equipped with a combination nozzle to flow water from Room C of the Single Story Structure into Room B (Fig.~\ref{fig:test_5_pic}).
-The layout of the structure was identical to the layout for Test~1, described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
+The layout of the structure was identical to the layout for Test~1 described above in Section~\ref{sec:monitor_procedure} and presented in Fig.~\ref{fig:east_setup}.
 The procedure for Test~5 began by flowing water in a straight stream aimed at the ceiling of Room B for 30 seconds in a fixed position.
@@
 This entire process was repeated for the streams being applied in the fixed and counterclockwise patterns.
-The average rotation rate for configurations that involved nozzle rotation during Test~5 was 2.1 rotations per second with a maximum rate of 2.3 rotations per second and minimum of 1.9 rotations per second.
-
-\begin{figure}[!ht]
-	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/SS_Room_B_Test_34}
-	\\~\\
-	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/NF_Room_B_Test_34}
-	\\~\\
-	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.75in]{../Figures/Pictures/WF_Room_B_Test_34}
-	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) aimed at the south doorway of Room B during Test~5.}
+The average rotation rate for the configurations that involved nozzle rotation was 2.1 rotations per second with a maximum rate of 2.3 rotations per second and minimum of 1.9 rotations per second.
+
+\begin{figure}[!ht]
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.70in]{../Figures/Pictures/SS_Room_B_Test_34}
+	\\~\\
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.70in]{../Figures/Pictures/NF_Room_B_Test_34}
+	\\~\\
+	\includegraphics[trim=23cm 6.5cm 4cm 6cm, clip=true, width=3.70in]{../Figures/Pictures/WF_Room_B_Test_34}
+	\caption[Straight stream, narrow fog stream, and wide fog stream during Test~5.]{Straight stream (top), narrow fog stream (middle), and wide fog stream (bottom) from the handline in Room C aimed at the south doorway of Room B during Test~5 in the Single Story Structure.}
 	\label{fig:test_5_pic}
@@
 \subsubsection{Tests~6 \& 7}
-Tests~6 and 7 followed identical procedures that involved using a 1.75~in.
-handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor room.
+Tests~6 and 7 followed identical procedures that used a 1.75~in.
+handline equipped with a combination nozzle to flow water from the north side double doors of the Two Story Structure into the first floor compartment.
 The water stream was aimed at the south side wall of the first floor during the experiments.
@@
 Fig.~\ref{fig:test_6_pic} contains an image of a straight stream pattern being applied during Test~6 with the flow path fully established.
-During configurations involving nozzle rotation with a wide fog stream or narrow fog stream, the average rotation rate was 1.3 rotations per second with a maximum of 1.4 rotations per second and a minimum of 1.2 rotations per second.
-The rotation rates for the clockwise and counterclockwise rotation of the straight stream were 0.8 rotations per second and 0.7 rotations per second, respectively, for Test~6, and 0.4 rotations per second for both directions during Test~7.
+The average rotation rate for the configurations that involved nozzle rotation with a wide fog stream or narrow fog stream during Tests~6 and 7 was 1.3 rotations per second with a maximum of 1.4 rotations per second and a minimum of 1.2 rotations per second.
+The average rotation rate for the configurations that involved nozzle rotation with a straight stream was 0.8 rotations per second during Test~6 and 0.4 rotations per second during Test~7.
 
@@
 In the following sections, the measurements are presented in graphic and tabular form.
-In the graphs, an error bar will represent the estimated uncertainty of the measurement.
-In the tables, the uncertainty will be included in the caption of each table as a percentage enclosed in brackets.
+In the graphs, an error bar represents the estimated uncertainty of the measurement.
+In the tables, the uncertainty is included in the caption of each table as a percentage enclosed in brackets.
 
@@
 \\ \midrule
-\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\textit{Straight (SS)}} & \multirow{2}{*}{\small Velocity}
 & 		 \small{m/s}   	&   0.2 $\pm0.03$	&   0.7 $\pm0.1$	&	 0.8 $\pm0.2$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog (NF)} \end{tabular}} & \multirow{2}{*}{\small Velocity}
 & 		\small{m/s}   	&	 1.7 $\pm0.3$   	&	 1.8 $\pm0.3$  	&   1.6 $\pm0.3$   \\
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog (WF)} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
 &		\small{m/s} 	&	 1.8 $\pm0.3$   	&   2.1 $\pm0.4$  	&   2.2 $\pm0.4$  \\ 
@@
 \\ \midrule
-\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\textit{Straight (SS)}} & \multirow{2}{*}{\small Velocity}
 & 		 \small{m/s}   	&   -0.1 $\pm0.02$    	&   0.6 $\pm0.1$   	&	 0.5 $\pm0.1$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog (NF)} \end{tabular}} & \multirow{2}{*}{\small Velocity}
 & 		\small{m/s}   	&   0.9 $\pm0.2$   		&   1.5 $\pm0.3$  	&   1.6 $\pm0.3$   \\
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog (WF)} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
 &		\small{m/s} 	&   2.1 $\pm0.4$   		&   2.3 $\pm0.4$  	&   2.6 $\pm0.5$  \\ 
@@
 \\ \midrule
-\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity} 
+\multirow{5}{*}{\textit{Straight (SS)}} & \multirow{2}{*}{\small Velocity} 
 & 		\small{m/s}		&   -0.2 $\pm0.03$   &   0.5 $\pm0.1$  &   0.7 $\pm0.1$   &  0.7 $\pm0.1$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog (NF)} \end{tabular}} & \multirow{2}{*}{\small Velocity}
 &		\small{m/s}   	&	 0.4 $\pm0.1$   	&	 1.1 $\pm0.2$		&	 0.9 $\pm0.2$		&	 1.1 $\pm0.2$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog (WF)} \end{tabular}} & \multirow{2}{*}{\small Velocity}
 &		\small{m/s}   	&    1.0 $\pm0.2$   	&	 1.0 $\pm0.2$  		&	 1.0 $\pm0.2$   	&  	 0.9 $\pm0.2$  \\  
@@
 \\ \midrule
-\multirow{5}{*}{\textit{Straight}} & \multirow{2}{*}{\small Velocity}
+\multirow{5}{*}{\textit{Straight (SS)}} & \multirow{2}{*}{\small Velocity}
 &		\small{m/s}   	&	 0.0 $\pm0.01$		&	 0.5 $\pm0.1$  		&	 0.7 $\pm0.1$   	&	 0.7 $\pm0.1$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Narrow} \\ \textit{Fog (NF)} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
 &		\small{m/s}   	&	 1.3 $\pm0.2$   	&	 1.2 $\pm0.2$  		&	 1.2 $\pm0.2$   	&	 1.3 $\pm0.2$  \\ 
@@
 \\~\\
-\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
+\multirow{5}{*}{\begin{tabular}{@{}c@{}} \textit{Wide} \\ \textit{Fog (WF)} \end{tabular}} & \multirow{2}{*}{\small Velocity} 
 &		\small{m/s}   	&	 1.0 $\pm0.2$   	&	 0.7 $\pm0.1$  		&	 0.9 $\pm0.2$   	&	 1.0 $\pm0.2$  \\ 
@@
 With the exception of the narrow fog stream in the fixed position during Test~6, every hose stream and nozzle movement pattern combination using a narrow fog or wide fog stream during the handline experiments produced air movement---an average gas velocity greater than 0.5~m/s (1.1~mph)---through the interior doorway while the flow path was fully established.
-For the straight stream, however, air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the handline.
+For the straight stream, however, air movement through the interior doorway only occurred when the stream was applied in a pattern that involved moving the nozzle.
 Similar to the monitor experiments, the average air velocity through the interior doorway was always greater in magnitude for the nozzle movement patterns using the narrow and wide fog streams than the same patterns using the straight stream.
-Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences (differences greater than the error associated with the bi-directional probes) in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
+Another important result seen in Tables~\ref{table:east_hand_A6_avgs} and \ref{table:west_hand_A10_avgs} is that there are no statistically significant differences (greater than the uncertainty associated with the bi-directional probes) in the amount of air flow through the interior doorway when rotating the hoseline in the clockwise direction compared to rotating it in the counterclockwise direction for any of three hose streams tested.
 The similarities in air flow produced by the clockwise and counterclockwise nozzle movement patterns can also be seen graphically in Fig.~\ref{fig:Test_6_BDP_A10_Avg_All} and Figs.~\ref{fig:Test_5_BDP_A6_Avg_All} and \ref{fig:Test_7_BDP_A10_Avg_All} in Appendix~\ref{chap:handline_plots}.
@@
 
-Seven experimental test series containing a total of 154 different configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air movement within residential scale structures.
-
-Three experimental series studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure for different ventilation configurations.
-For each of the three series, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure.
+Seven experimental test series containing a total of 154 configurations were conducted to study the impact of different hose stream and nozzle movement pattern combinations on air flows within residential scale structures.
+
+Three of the experimental series studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure containing different ventilation configurations.
+For each of the three test series, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure.
 The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream.
-
-Additionally, a fourth experimental series using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle with a 1~in.
-tip aimed at a specified location for 60 seconds with a fully established flow path.
-The streams were compared for six different 60 second periods during which the flow path was fully established: three times each for the monitor aimed at two locations.
+Additionally, a fourth experimental series using a monitor was conducted to compare the impact of a straight stream from a combination nozzle to a solid stream from a smooth bore nozzle with a 1~in.
+tip on air flows within a structure.
+The streams were compared across six different 60 second periods with a fully established flow path: three times each for the monitor aimed at two locations.
 The results from the four monitor test series suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.
 
-In addition to the monitor test series, three different experimental series were conducted using a handline to study the impact of different stream and nozzle movement pattern combinations on air movement within a structure.
+In addition to the monitor test series, three different experimental series were conducted using a combination nozzle attached to a handline to study the impact of different stream and nozzle movement pattern combinations on air movement within a structure.
 Similar to the monitor experiments, the average air velocity through the interior doorway of a structure with a fully established flow path was greater for the wide fog and narrow fog streams than the straight stream.
-It was discovered that a straight stream increased air movement through the interior doorway when it was applied in a moving pattern.
-With regard to Royer's theory, throughout all handline test series, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
+It was discovered that a straight stream increased air movement through the interior doorway only when it was applied in a moving pattern.
+With regard to Royer's theory, throughout all the handline test series, there were no statistically significant differences in the average air velocity measured through the interior doorway between the clockwise and counterclockwise nozzle movement patterns.
 However, these experiments only addressed cold flow.
 
-For this limited series of water flow experiments, the data demonstrate that for these flows and configurations, hose streams can affect air movement within a structure.
+The results from the limited series of water flow experiments demonstrate that hose streams can affect air movement within a structure for the described flows and configurations.
 The type of hose stream used and manner in which it is applied dictates the extent to which a stream impacts the ventilation of a structure.
@@
 \appendix
-\chapter{Fully Dimensioned Floor Plans}
+\chapter{Dimensioned Floor Plans}
 \label{chap:floor_plans}
@@
 	\includegraphics[width=0.86\columnwidth]{../Figures/Plots/HOSE_IXAOXX_BDP_A6_stream_avgs}
-	\caption{Average velocity through stairwell door during Test~5 for three hose stream patterns.}
+	\caption{Average velocity through stairwell door during Test~5 for the three hose stream patterns.}
 	\label{fig:Test_5_BDP_A6_Avg_All}

### 2016-09-21 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to burner report

@@
 \subsubsection{First Floor of Both Structures}
-The first floor of each structure had an outer wall composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
+The first floor of each structure had outer walls composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
 The joints and gaps between the blocks were filled with high temperature insulation.
+All doors along the outer walls were composed of steel.
 
@@
 
-All first floor exterior doors were made of steel.
 The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track.
@@
 The second floor of the West Structure was built on the structure's first floor wood ceiling support.
-The two floors were connected by a stairwell.
+The two floors were connected by an interior stairwell.
 A door made of lauan plywood was located at the top of the stairwell.
@@
 The amount of leakage in the East Structure was measured as 0.024~m$^2$.
-For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) during Tests~24 and 25.
+For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was fully closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) used Tests~24 and 25.
+\clearpage
 
@@
 
-% \subsubsection{Dimensions}
 Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.

### 2016-09-22 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Minor edits to gas burner report made during full read through

@@
 
-% \cleardoublepage
-% \phantomsection
-% \addcontentsline{toc}{chapter}{List of Tables}
-% \listoftables
+\cleardoublepage
+\phantomsection
+\addcontentsline{toc}{chapter}{List of Tables}
+\listoftables
 
@@
 \label{chap:Introduction}
-% [Brief Introduction of FRD at NIST, ventilation, etc.]
 The Fire Fighting Technology Group of the Fire Research Division at the National Institute of Standards and Technology (NIST) develops and applies technology, measurements, and standards to improve the understanding of fire behavior, prevention and suppression, which ultimately enables advances in fire fighting operations, firefighter equipment, fire suppression, fire investigations, and disaster response.
@@
 Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample.
-Then, the dry gas sample was piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured.
+Then, the dry gas samples were piped to a series of gas analyzers and the concentrations of oxygen, carbon monoxide, and carbon dioxide were measured.
 A legend is presented in Fig.~\ref{fig:Instrumentation_Legend} to clarify the instrumentation schematics presented in the follow sections.
@@
 
-Three propane burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment.
+Three diffusion flame burners, pictured in Fig.~\ref{fig:burners}, were used as the fuel source in each experiment.
 Each burner had a square opening of side length 0.6~m (2~ft) located 0.14~m (5.5~in) above the floor and were positioned 0.6~m (2~ft) from the south and west walls on the first floor of each structure.
@@
 	\includegraphics[width=0.9\columnwidth]{../Figures/Pictures/burners}
-	\caption[Three propane burners used as fire source.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls on the first floor provided the fire source for the experiments.}
+	\caption[Three propane burners used as the fuel source.]{Three propane burners located 0.6~m (2~ft) off the south and west interior walls on the first floor that provided the fire source for the experiments.}
 	\label{fig:burners}
@@
 Each bare-bead thermocouple array was composed of eight thermocouples.
-Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in each exterior doorway of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
+Three bi-directional probe and solid thermocouple arrays (A7, A8, and A9) were centered in the exterior doorways of the structure and contained eight probes as shown in Fig.~\ref{fig:BDP_arrays}.
 The fourth bi-directional probe and solid thermocouple array (A10), also presented in Fig.~\ref{fig:BDP_arrays}, was located at the opening of the roof vent, 320~mm (12.75~in) above the compartment ceiling.
 The array contained three probes centered between the east and west sides of the vent.
-The position of each probe and thermocouple pair relative to the south wall of the vent are listed in Table~\ref{table:east_channel_list}.
+The position of each probe and thermocouple pair relative to the south wall of the vent is listed in the channel list presented in Table~\ref{table:east_channel_list}.
 The total heat flux gauge/radiometer pairs were aimed to view the ceiling.
-Gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing.
-The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:east_channel_list}.
+Gas samples were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing.
+The height of each individual sensor in the sensor arrays is listed in Table~\ref{table:east_channel_list}.
 
@@
 
-Every thermocouple array contained eight bare-bead thermocouples, each bi-directional probe and solid thermocouple array contained 8 probes, and gas concentrations were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
-Each pair of total heat flux sensors were located 1.0~m (3.3~ft) above the floor.
-The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 also contained one sensor facing the ceiling and another facing the stairway door.
-The height of each individual sensor in the sensor arrays are listed in the channel list found in Table~\ref{table:west_channel_list}.
+The thermocouple arrays and the bi-directional probe plus solid thermocouple arrays contained eight sensors per array.
+Gas samples were pulled through 9.5~mm (0.38~in) diameter stainless steel tubing located 1.2~m (4~ft) above the floor.
+Each pair of total heat flux sensors was located 1.0~m (3.3~ft) above the floor.
+The pair at A16 contained one sensor facing the ceiling and another facing the north side of the room, and the pair at A17 contained one sensor facing the ceiling and another facing the stairway door.
+The height of each individual sensor in the sensor arrays is listed in the channel list found in Table~\ref{table:west_channel_list}.
 
@@
 \multirow{3}{*}{\large{\textbf{A16}}}
- & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing doorway (horizontal) \end{tabular} & Total heat flux \\
+ & HF\_2\_H	  & \begin{tabular}{@{}l} 1~m above floor, \\ facing N wall (horizontal) \end{tabular} & Total heat flux \\
  & HF\_2\_V   & \begin{tabular}{@{}l} 1~m above floor, \\ facing ceiling (vertical) \end{tabular} 	   & Total heat flux \\
@@
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
-Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\%.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\% for length measurements.
 
 \subsubsection{Thermocouples}
-The standard uncertainty in the temperature of the thermocouple wire itself is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
+The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}.
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.
@@
 Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling.
-The estimated total expanded uncertainty for temperature in these experiments is $\pm$15~\%.
+The estimated total expanded uncertainty associated with the temperature measurements is $\pm$15~\%.
 
@@
 The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with gas concentration measurements~\cite{Lock:1}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with the gas concentrations~\cite{Lock:1}.
 
@@
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated and the zero and span of each was checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}.
-The total expanded uncertainty was estimated at 10~\%.
+The transducers were factory calibrated, and the zero and span of each were checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}.
+The total expanded uncertainty is estimated at 10~\%.
 
 \subsubsection{Bi-Directional Probes}
-Bi-directional probes and single thermocouples were used to measure the velocity.
+Bi-directional probe and single thermocouple pairs were used to measure gas velocity.
 The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
@@
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments was estimated to be $\pm$18~\%.
+The total expanded uncertainty for gas velocity measurements is estimated to be $\pm$18~\%.
 
@@
 A rotary type gas meter was used to measure the volume of propane provided to the gas burners.
-The manufacturer quantifies the maximum error as $\pm$2~\%~\cite{Romet:2014}.
-A volumetric flow rate was calculated from the gas meter measurements and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
-The total expanded uncertainty for the heat release rate obtained from this method was estimated to be $\pm12$~\%.
+The manufacturer quantifies the maximum error of the meter as $\pm$2~\%~\cite{Romet:2014}.
+A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
+The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm12$~\%.
 
@@
 \label{sec:east_procedure}
-Five different tests, Tests 2--6, were conducted in the East Structure.
-Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for each experiment.
+Five different tests, Tests~2--6, were conducted in the East Structure.
+Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for Tests~2--4 and Tests~5--6, respectively.
 The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
-Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.
+Thus, for Tests~2--4, heat release rates are reported for one, two, and three burners, and for Tests~5 and 6, a single heat release rate for three burners is reported.
+% Thus, for Tests~2--4, heat release rates are reported for each time period between a burner being turned on or off, and a single heat release rate for when all burners were ignited is reported for Tests~5 and 6.
 
 \subsection{Tests 2--4}
-Tests~2--4 followed an identical order of events.
+Tests~2--4 followed a nearly identical order of events.
 Fig.~\ref{fig:Tests_2-4_layout} includes a floor plan schematic and table of event times corresponding to the data files for each test.
-A 61~cm (24~in) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4.
-During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport propane to the burners.
+A 0.61~cm (2.0~ft) diameter PPV fan located 1.6~m (5.2~ft) away from the south exterior door was aimed at the center of the doorway and used during Tests~2--4.
+During these experiments, the south exterior door was not able to completely close due to an obstruction caused by the hoses used to transport the propane to the burners.
 So, when the south door was in the ``closed'' position, a 133~mm (5.25~in) opening was present between the door and its frame.
 For all other experiments, however, the south exterior door was not used and the doorway remained closed for the entirety of the test.
-To fully close the doorway during these tests, the hinged door was removed and gypsum board was used to cover the doorway.
+To fully close the doorway during these tests, the hinged door was removed, and gypsum board was used to cover the doorway.
 
@@
 \caption{Heat Release Rates for Tests~2--4}
-\begin{tabular}{lccccc}
+\begin{tabular}{lccc}
  \toprule
- 					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
-\textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
-					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
-					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
-					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
-					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
- \midrule
-Test 2 				& 560 & 1080 & 1470 & 1070 & 550 \\
-Test 3 				& 530 & 1040 & 1470 & 1050 & 520 \\
-Test 4				& 580 & 1140 & 1580 & 1130 & 580 \\
+ 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
+\textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
+					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
+					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
+ \midrule
+Test 2 				& 560 & 1080 & 1470 \\
+Test 3 				& 530 & 1040 & 1470 \\
+Test 4				& 580 & 1140 & 1580 \\
 \bottomrule
@@
 \end{table}
+
+% \begin{table}[!ht]
+% \caption{Heat Release Rates for Tests~2--4}
+% \begin{tabular}{lccccc}
+%  \toprule
+%  					& 	\multicolumn{5}{c}{\textbf{Heat Release Rate (kW)}} \\
+% \textbf{Test} 		&	\begin{tabular}{c} Corner \\ Burner On \end{tabular} 
+% 					&	\begin{tabular}{c} Middle \\ Burner On \end{tabular}
+% 					&	\begin{tabular}{c} Center \\ Burner On \end{tabular}
+% 					& 	\begin{tabular}{c} Center \\ Burner Off \end{tabular}
+% 					&   \begin{tabular}{c} Middle \\ Burner Off \end{tabular} \\
+%  \midrule
+% Test 2 				& 560 & 1080 & 1470 & 1070 & 550 \\
+% Test 3 				& 530 & 1040 & 1470 & 1050 & 520 \\
+% Test 4				& 580 & 1140 & 1580 & 1130 & 580 \\
+% \bottomrule
+% \end{tabular}
+% \label{table:HRR_Tests_2-4}
+% \end{table}
 
@@
 \subsection{Tests 5 \& 6}
-The procedures for Test~5 and Test~6 are outlined in Fig.~\ref{fig:east_test_5} and Fig.~\ref{fig:east_test_6}, respectively.
-Tests~5 and 6 involved repeating a specific set of events three times in a row.
-To avoid listing the identical actions three separate times in the event column of the table, each repetition of events has been denoted as a ``sequence'' (abbreviated as ``seq.'' in the tables) and given its own column in the event table.
+The procedures for Tests~5 and 6 are outlined in Figs.~\ref{fig:east_test_5} and \ref{fig:east_test_6}, respectively.
+Both tests involved repeating a specific set of events three times in a row.
+To avoid listing the identical actions three separate times in the ``event'' column of the tables, each repetition of events is denoted as a ``sequence'' (abbreviated as ``seq.''), and each table contains three columns of times---one for each sequence.
 
@@
 					& 	\textbf{Heat Release Rate (kW)}	\\
-\textbf{Test}		& All burners on \\
+\textbf{Test}		& \textbf{All Burners On} \\
  \midrule
@@
 \subsection{Tests~22 \& 23}
-Tests~22 and 23 followed a nearly identical procedure to change the ventilation.
-The starting configuration for Test~22 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~23 had the same door in the closed position.
+Tests~22 and 23 followed a nearly identical procedure.
+The starting configuration for Test~22 had the second story south exterior door in the opened position, while the starting configuration for Test~23 had the same door in the closed position.
 Fig.~\ref{fig:west_test_22} includes a floor plan schematic and table of event times corresponding to the data files for Tests~22 and 23.
-A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
+A 0.61~m (2.0~ft) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the two doors was used during the tests to change the ventilation pattern within the structure.
 \begin{figure}[!ht]
@@
 \subsection{Tests~24 \& 25}
-Similar to Tests~22 and 23, Tests~24 and 25 followed a nearly identical test procedure.
-The starting configuration for Test~24 had the south exterior door on the 2nd level in the opened position, while the starting configuration for Test~25 had the same door in the closed position.
-Also, the stairwell door was unable to completely close.
-When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6~in) gap between the door and its frame.
+Like Tests~22 and 23, Tests~24 and 25 followed a nearly identical procedure.
+The starting configuration for Test~24 had the south exterior door on the second level in the opened position, while the starting configuration for Test~25 had the same door in the closed position.
+During both tests, the stairwell door was unable to completely close.
+When it was in the ``closed'' position at the beginning of each test, there was a 152~mm (6.0~in) gap between the door and its frame.
 Fig.~\ref{fig:west_test_24} includes a floor plan schematic and table of event times corresponding to the data files for Tests~24 and 25.
-A 61~cm (24~in) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
+A 0.61~m (2.0~ft) diameter PPV fan located 2.3~m (7.5~ft) away from the first level double doors and aimed at the center of the west double door was used during the tests to change the ventilation pattern within the structure.
 
@@
 The fire source for each experiment was provided by a set of three diffusion flame burners with propane as the fuel.
-Various doors and vents were opened and closed during each test to affect the ventilation within the structure.
+Various doors and vents were opened and closed during each test to change ventilation within the structure.
 A PPV fan was also used during some of the experiments to change the ventilation patterns.
-Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during each experiment.
-The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire for each test.
+Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during the experiments.
+The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire during each test.
 

### 2016-09-24 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added FDS comparison figures
also copied original .cls file into repo

@@
 
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0pD_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RI}\\
+  \caption[FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_Plume_Grid_TWNG_comp}
+\end{figure}
+
 \begin{table}
@@
 
-\subsection{Plume Temperatures}
+\subsection{Temperatures}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D}\\
+  \caption[FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_TCPlume_TWNG_comp}
+\end{figure}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
+  \caption[FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_TCWall_TWNG_comp}
+\end{figure}
 
@@
 
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
+  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_HFCL_TWNG_comp}
+\end{figure}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0D}\\
+  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_HFEdge_TWNG_comp}
+\end{figure}
+
 \subsection{Flame Height}
+
+Table to compare measured flame height with FDS cal.
 

### 2016-09-24 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added FDS Images to Figures Dstar  update bib

@@
 In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
-The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will compared.
-Two burner positions are examined, 0.61~m from the wall and 0.0~m from the instrumented gypsum wallboard wall.
+The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will be compared.
+Then the data generated from the instrumented gypsum wallboard fires are compared with results from FDS simulations.
+Four burner positions are examined, beginning 0.61~m from the wall to moving to 0.0~m, where one edge of the burner is in contact with the instrumented gypsum wallboard wall.
+First the the plume data will be examined based on the size of the computational grid cells used in the FDS simulations.
 
 \subsection{Grid Size Analysis}
+
+Choosing the size of the grid when performing an amalysis with FDS is critical.
+In studies where large rooms or portions of buildings have been involved grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Vettori:2000,Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
+
+ A measure of how well the flow field is resolved is given by the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
+This value has been referred to as the plume resolution index.
+Given that the fire plume region is the focus of this study, it is important to understand how changes in plume mesh resolution impact the results.
+
+\begin{equation}
+ D^* = \left(
+     \frac{\dot Q}{\rho_\infty  c_p  T_\infty  \sqrt{g} }
+     \right)^\frac{2}{5} 
+ \end{equation}
+
+The characteristic fire diameter is defined by the relationship of the characteristic fire size to the physical diameter of the fire, ${Q^*} = ({D^*}/{D})^{5/2}$, where $D$ is the physical diameter of the fire.
+The quantity, $\dot Q$, is the total heat release rate of the fire.
+The quantity $({D^*}/{\delta x})$ is approximately the number of computational grid cells that span the characteristic diameter of the fire ~\cite{FDS_Users_Guide,FDS_Validation_Guide}.
+
+Computational grid cell sizes of 80~mm, 40~mm, and 20~mm where used in FDS to model the fire.
+The resulting plume resolutions were approximately 4.4, 8.8, and 17.5 respectively.
+Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.
+Figure~ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons
 

### 2016-09-25 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
FDS chapter images and text

@@
 Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.
-Figure~ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons
+Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the data from
 
@@
   \label{FDS_Plume_Grid_TWNG_comp}
+\end{figure}
+
+One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in 3 dimensions to allow the generation of visualizations.
+The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=05_0601crop}
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=10_0601crop}
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=20_0601crop}\\
+  \caption[Flame images generated with FDS and Smokeview]{Flame images generated with FDS and Smokeview.
+The left image has a mesh size of 80~mm, the center image has a mesh size of 40~mm and the image on the right has amesh size of 20~mm.}
+  \label{FDS_Flame_Image_comp}
+\end{figure}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
+  \caption[FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_Wall_Temp_TWNG_comp}
 \end{figure}
@@
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_TCPlume_TWNG_comp}
+  \label{FDS_TCPlume_IWGB_comp}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0601T}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_601T}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0600T}\\
+	\caption[FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.
+Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
+	\label{FDS_Plume_Temp_IWGB_Comp_}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0300WT}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}\\
+	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0300WT}\\
+	\caption[FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.
+Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
+	\label{FDS_Wall_Temp_IWGB_Comp_}
 \end{figure}
@@
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_TCWall_TWNG_comp}
+  \label{FDS_TCSurface_IWGB_comp}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300WT}\\
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300WT}
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300WT}\\
+  \caption[FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall]{FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_TCWall_IWGB_comp}
 \end{figure}
@@
 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300HF}
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300HF}\\
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300HF}
+  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300HF}\\
+  \caption[FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall]{FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_WallHF_IWGB_comp}
+\end{figure}
+
 \subsection{Flame Height}
@@
 \section{Comparison of FDS with Fire Pattern Results}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/WallTemp_10mm_0D_0_8m_guideline}
+  \includegraphics[width=2.5in]{../Figures/350CThresholdwall_temp_0_8m_guideline}\\
+  \hspace{4 mm}  \\ 
+  \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
+The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
+This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
+  \label{FDS_FirePattern_comp}
+\end{figure}
 

### 2016-09-25 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
FDS Flame height ref and values
update tex file

@@
 
-\begin{table}[t!]
-  \centering
-  \begin{tabular}{l|l}
-  	Abbreviations \\
-     \hline
-     HRR	            & heat release rate (kW) \\
-     NIST        	    & National Institute of Standards and Technology (US) \\
-     PUF                & polyurethane foam  \\
-     $\dot{q}''$        & heat flux per unit area kW/m$^2$ \\
-	 $\dot{Q}$          & heat release rate (kW) \\ 
-	 $\chi_r$           & radiative fraction \\
-	 $R$                & distance from the point source to the target (m) \\
-   \end{tabular}
- \end{table}
+\clearpage
+Abbreviations
+\begin{tabbing}
+\hspace{1.5in} \= \\
+EMS \> Emergency Medical Services \\
+FDS \> Fire Dynamics Simulator \\
+HGL \> Hot Gas Layer \\
+HRR \> Heat Release Rate \\
+HRRPUA \> Heat Release Rate per Unit Area \\
+NIST \> National Institute of Standards and Technology \\
+\end{tabbing}
+
+List of Symbols
+\begin{tabbing}
+\hspace{1.5in} \= \\
+$c_{p}$ \> specific heat \\
+$k$ \> thermal conductivity \\
+$\chi_r$ \> radiative fraction \\
+$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
+$\dot{Q}$ \> heat release rate (kW) \\ 
+$R$ \> distance from the point source to the target (m) \\
+$\rho$ \> density \\
+\end{tabbing}
 
@@
 Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.
-Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the data from
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RI}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0pD_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RI}\\
-  \caption[FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
-Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_Plume_Grid_TWNG_comp}
-\end{figure}
-
-One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in 3 dimensions to allow the generation of visualizations.
-The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=05_0601crop}
-  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=10_0601crop}
-  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=20_0601crop}\\
-  \caption[Flame images generated with FDS and Smokeview]{Flame images generated with FDS and Smokeview.
-The left image has a mesh size of 80~mm, the center image has a mesh size of 40~mm and the image on the right has amesh size of 20~mm.}
-  \label{FDS_Flame_Image_comp}
-\end{figure}
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
-  \caption[FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
-Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_Wall_Temp_TWNG_comp}
-\end{figure}
-
-\begin{table}
+Tables~\ref{tab:FDSRI_Exp_Plume2d} and \ref{tab:FDSRI_Exp_Plume0d} shows the plume temperature results for the three grid resolutions compared the experimental data with a wall spacing of 0.61~m and 0.0~m respectively.
+Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the same data.
+
+\begin{table}[ht!]
   \small
@@
 
-\begin{table}
+\begin{table}[ht!]
   \small
@@
 
-\begin{table}
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
-		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
-		\hline 0.2 			   & 207					   & 367					& 316 			 	\\
-		\hline 0.4			   & 518					   & 415					& 388			 	\\
-		\hline 0.6			   & 487					   & 445					& 434			 	\\
-		\hline 0.8			   & 368					   & 393					& 401				\\
-		\hline 1.0			   & 284					   & 326 					& 338				\\
-		\hline 1.2			   & 189					   & 226 					& 247				\\
-		\hline 1.4			   & 150					   & 167 					& 177				\\
-		\hline 1.6			   & 113					   & 126 					& 127				\\
-		\hline 1.8			   & 97						   & 100 					& 96				\\
-		\hline 2.0			   & 81						   & 82 					& 77				\\
-		\hline 2.2			   & 72						   & 71 					& 66				\\
-		\hline
-	\end{tabular}
-	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0~m}
-	\label{tab:FDSRI_wall0D}
-\end{table}
-
-\begin{table}
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
-		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
-		\hline 0.2 			   & 219					   & 182					& 158 			 	\\
-		\hline 0.4			   & 310					   & 232					& 217			 	\\
-		\hline 0.6			   & 272					   & 231					& 250			 	\\
-		\hline 0.8			   & 192					   & 189					& 241				\\
-		\hline 1.0			   & 152					   & 149 					& 204				\\
-		\hline 1.2			   & 113					   & 104 					& 150				\\
-		\hline 1.4			   & 96						   & 82 					& 111				\\
-		\hline 1.6			   & 79						   & 69 					& 87				\\
-		\hline 1.8			   & 70						   & 61 					& 72				\\
-		\hline 2.0			   & 60						   & 55 					& 64				\\
-		\hline 2.2			   & 51						   & 52 					& 58				\\
-		\hline
-	\end{tabular}
-	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.15~m}
-	\label{tab:FDSRI_wallp5D}
-\end{table}
-
-\begin{table}
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
-		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
-		\hline 0.2 			   & 143					   & 132					& 109 			 	\\
-		\hline 0.4			   & 180					   & 165					& 142			 	\\
-		\hline 0.6			   & 158					   & 165					& 161			 	\\
-		\hline 0.8			   & 114					   & 139					& 157				\\
-		\hline 1.0			   & 90						   & 111 					& 136				\\
-		\hline 1.2			   & 66						   & 76 					& 100				\\
-		\hline 1.4			   & 57						   & 59 					& 74				\\
-		\hline 1.6			   & 48						   & 49 					& 58				\\
-		\hline 1.8			   & 44						   & 44 					& 50				\\
-		\hline 2.0			   & 40						   & 42 					& 47				\\
-		\hline 2.2			   & 38						   & 41 					& 45				\\
-		\hline
-	\end{tabular}
-	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.30~m}
-	\label{tab:FDSRI_wall1D}
-\end{table}
-
-\begin{table}
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|}
-		\hline Distance Above  & Resolution Index = 5      & Resolution Index = 10     & Resolution Index = 20 \\
-		Burner~(m)	   & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C) & Temperature~($^{\circ}$C)	\\ \hline
-		\hline 0.2 			   & 88						   & 69						& 59 			 	\\
-		\hline 0.4			   & 103					   & 82						& 74			 	\\
-		\hline 0.6			   & 95						   & 81						& 78			 	\\
-		\hline 0.8			   & 76						   & 74						& 76				\\
-		\hline 1.0			   & 64						   & 64 					& 67				\\
-		\hline 1.2			   & 50						   & 51 					& 55				\\
-		\hline 1.4			   & 43						   & 42 					& 45				\\
-		\hline 1.6			   & 36						   & 35 					& 37				\\
-		\hline 1.8			   & 32						   & 30 					& 31				\\
-		\hline 2.0			   & 28						   & 27 					& 28				\\
-		\hline 2.2			   & 26						   & 25 					& 26				\\
-		\hline
-	\end{tabular}
-	\caption[Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m]{Impact of Grid Resolution on FDS Wall Temperatures with Wall at 0.61~m}
-	\label{tab:FDSRI_wall2D}
-\end{table}
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0pD_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RI}\\
+  \caption[FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_Plume_Grid_TWNG_comp}
+\end{figure}
+
+One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in 3 dimensions to allow the generation of visualizations.
+The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=05_0601crop}
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=10_0601crop}
+  \includegraphics[width=1.7in]{../Figures/NG_80kW_GBWall_2D_RI=20_0601crop}\\
+  \caption[Flame images generated with FDS and Smokeview]{Flame images generated with FDS and Smokeview.
+The left image has a mesh size of 80~mm, the center image has a mesh size of 40~mm and the image on the right has amesh size of 20~mm.}
+  \label{FDS_Flame_Image_comp}
+\end{figure}
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
+  \caption[FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_Wall_Temp_TWNG_comp}
+\end{figure}
 
@@
 
-\begin{table}
-	\small
-	\centering
-	\begin{tabular}{|c|c|c|c|c|}
-		\hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid 		& Experiment Avg. \\
-		Burner~(m)	   & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C)	\\ \hline
-		\hline 0.2 			   & 458						& 500					& 666 			& 620 	\\
-		\hline 0.4			   & 738					   	& 819					& 761			& 527 	\\
-		\hline 0.6			   & 632						& 769					& 643			& 385 	\\
-		\hline 0.8			   & 442						& 600					& 522			& 198	\\
-		\hline 1.0			   & 346						& 459 					& 402			& 151	\\
-		\hline 1.2			   & 251						& 307 					& 284			& 119	\\
-		\hline 1.4			   & 209						& 236 					& 213			& 98	\\
-		\hline 1.6			   & 166						& 188 					& 164			& 86	\\
-		\hline 1.8			   & 145						& 154 					& 133			& 76	\\
-		\hline 2.0			   & 123						& 130 					& 112			& 69	\\
-		\hline 2.2			   & 111						& 113 					& 99			& 61	\\
-		\hline
-	\end{tabular}
-	\caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
-	\label{tab:FDSRI_Exp_Plume}
-\end{table}
-
 \subsection{Heat Flux}
@@
 
-Table to compare measured flame height with FDS cal.
+Table to compare measured flame height with FDS cal~\cite{McDermott:2011}
+
+Flame Height 2D  20~mm  at 99~\%  1.28~m
+
+Flame Height 0D  20~mm  at 99~\%  1.46~m
 
@@
 
+lessons learned  cameras   black paint
+
 \chapter{Conclusions}
@@
 \bibliography{../References/Madrzykowski_Thesis}
+
 \end{document}

### 2016-09-26 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revisions Ch1 through Ch5
Added photo for Investigator Challenge

@@
 In 2003, a list of zone and computational fluid dynamics (CFD) fire models was compiled by Olenick and Carpenter~\cite{Olenick:2003}.
-A similar survey was conducted in 1992, and Olenick has updated the list in 2014.
+A similar survey was conducted in 1992, and Olenick updated the list in 2014.
 There are 53 zone models listed, but only three are actively supported or maintained.
 The survey also includes 22 field models of which 10 are listed as being actively supported.
-All of the correlations and models have been to some extent been validated or checked against experimental data for a limited set of scenarios~\cite{ASTM_E1355}.
+All of the correlations and models have, to some extent, been validated or checked against experimental data for a limited set of scenarios~\cite{ASTM_E1355}.
 
@@
 
-Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount or research and analysis tools directly related to this practice.
+Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
 Gorbett recently conducted a review of fire pattern research that has been conducted over the last 80 years.
@@
 Both fires occurred prior to the release of NFPA~921 in 1992.
-The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 – 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained~\cite{Beyler:2009}.
+The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 {\textendash} 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained~\cite{Beyler:2009}.
 
@@
 
-\subsection{The Fire Investigators' Challenge}
-
-For the moment lets step into the shoes of a fire investigator and examine a potential investigation scenario.
+\section{The Fire Investigators' Challenge}
+
+For the moment let's step into the shoes of a fire investigator and examine a potential investigation scenario.
 It is 8:30 in the morning on a cool fall morning and you are being called to a fire scene.
@@
 Enroute you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
-The husband and father also lives at that address but is unaccounted at this time.
+The husband and father also lives at that address but is unaccounted for at this time.
 Upon arrival you have a conversation with the police and fire officers on the scene.
-You are provided with information regarding what the first firefighters saw on the scene, ``all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
+You are provided with information regarding what the first firefighters saw on the scene; ``all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
 The front door was forced and a hose stream was applied to the fire in the living room.
@@
 As you wait for the fire department to complete their operations inside, the police on scene let you know that the address is familiar to them for domestic disturbance calls for the husband and wife fighting but no charges have been filed.
-They are looking for the husband and have sent a patrol car to his work place.
+They are looking for the husband and have sent a patrol car to his place of work.
 
 As you begin to examine the scene, you walk around the exterior and note that on the front of the end unit townhouse, there is fire damage on the exterior above the front door opening that extends across the ceiling of the porch.
-The is some thermal damage and smoke deposits on the from of the siding on the porch.
-The outer pane of the living room window is for the most part still intact.
-you notice that three of the four windows on the second floor have been removed.
+There is some thermal damage and smoke deposits on the front siding above the porch.
+The outer pane of the living room window is, for the most part, still intact.
+You notice that three of the four windows on the second floor have been removed.
 On ``side D'' of the townhome there are no openings and no smoke or fire damage is present.
 On the rear or ``side C'' of the house the door and windows are intact but open.
-There is no smoke stains or thermal damage around any of the openings on the rear.
+There are no smoke stains or thermal damage around any of the openings on the rear.
 No sign of smoke alarms in the home.
 
-You take some notes and photograph the exterior of the structure, the fire department is not repacking their equipment and are preparing to leave when you enter through the front doorway.
-The living room has extensive fire damage.
+You take some notes and photograph the exterior of the structure, the fire department is repacking their equipment and are preparing to leave when you enter through the front doorway.
+The living room has extensive fire damage, as shown in Figure~\ref{EXT_INTLR}.
 Looking to your right, two chairs in front of the living room window have some thermal damage.
-There are a clear horizontal line of demarcation the large wood TV stand in the corner.
+There are is a clear horizontal line of demarcation on the large wood TV stand in the corner.
 As your eyes move from the corner back toward the rear of the townhome and the kitchen, you notice that the elevation of the line of demarcation is increasing.
 This may be an indicator that the origin of the fire is closer to the front of the living room.
-Between the two wood cabinets on the ``D wall'' of the living room was a wood framed sofa.
+Between the two wood cabinets on the ``D wall'' of the living room there is a wood framed sofa.
 The cushions have thermal damage, from pyrolysis.
-It is not clear that they were on fire as there is not thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
+It is not clear that they were on fire as there is no thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
 Still standing in the entry doorway, you turn your attention to the remains of an upholstered sofa and chair.
@@
 There is smoke damage in the upstairs hallway and in the front bedrooms.
-The further you move from the stairs the less damage you find.
+The further you move from the stairs the less thermal damage you find.
 
@@
 The same is true from the left side of the sofa.
+In fact, the left side of the sofa has more fire damage to the wood frame of the sofa than the right side of the sofa frame.
 The corner formed by the wall behind the chair and the wall of the stairway has a ``V pattern'' burned into it, from the floor and extending up toward the ceiling.
@@
 The burned wire from the heater extends toward the wall outlet behind the sofa.
+Figure~\ref{EXT_LRDetails} shows some of these details.
 
 You have now developed your first hypothesis about the origin of the fire.
-A radiant style, electric heater was turned on and left until it ignited the fabric on the sofa or chair.
+A radiant style, electric heater was turned on.
+It was too close to the furniture and ignited the fabric on the sofa or chair.
 You collect the remains of the heater for further examination to have a lab determine if the heater switch was in the ``on'' position.
@@
 There are pieces of charred newspaper near the right arm of the sofa.
-The burn mark on the top of the wood coffee table looks like a arrow that is pointing toward the corner.
+The burn mark on the top of the wood coffee table looks like an arrow that is pointing toward the corner.
 The char on the legs of the coffee table is very directional and consistent with the heat coming from the corner.
@@
 
-The chair clearly has more unburned foam cushioning then the sofa does and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not be moved.
+The chair has more unburned foam cushioning then the sofa does and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not been moved.
 The cushion was heated from the top down.
@@
 Besides interviews what else can you do to eliminate the inconsistencies?
-We will reexamine the in Chapter XX.
+The fire investigators' challenge we be reexamined in Chapter IX.
+
+\begin{figure}[ht!]
+	\centering
+		\includegraphics[width=2.5in]{../Figures/EXT_SideA}
+		\includegraphics[width=2.5in]{../Figures/INT_SideD}\\
+		\hspace{3 mm}  \\
+		\includegraphics[width=2.5in]{../Figures/INT_SideC}
+		\includegraphics[width=2.5in]{../Figures/INT_SideA}\\
+	\caption[Photographs of the exterior and interior of a townhouse post fire]{Photographs of the exterior and interior of a townhouse post fire.
+The three interior photos show the right side wall of the living room (Side D), the back wall of the living room (Side C), and the front wall of the living room (Side A).}
+	\label{EXT_INTLR}
+\end{figure}
+
+\begin{figure}[ht!]
+	\centering
+		\includegraphics[width=2.5in]{../Figures/V_pattern}
+		\includegraphics[width=2.5in]{../Figures/Heater}\\
+		\hspace{3 mm}  \\
+		\includegraphics[width=2.5in]{../Figures/Sofa}
+		\includegraphics[width=2.5in]{../Figures/Table}\\
+	\caption[Photographs of the some of the details of the living room fire area]{Photographs of the some of the details of the living room fire area including the V pattern, heater behind the chair and sofa, the varied thermal damage on the sofa, and the thermal damage to the coffee table and the interior of the sofa frame.}
+	\label{EXT_LRDetails}
+\end{figure}
 
@@
 
-A schematic drawing of the instrumentation arrangement is shown in Fig.~\ref{Drawing_Fire_Flamer}.
+A schematic drawing of the instrumentation arrangement is shown in Figure~\ref{Drawing_Fire_Flamer}.
 The thermocouples were mounted on a steel frame.
@@
 
-The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 100~s period.
+The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 300~s period.
 The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11~\% It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
@@
 The polyurethane foam was readily ignited with a small pilot flame similar to that used to ignite the natural gas and the gasoline.
-By comparison, a small flame ignited the gases flowing out the top of the natural gas burner and the flames from the natural gas cover entire burner surface within approximately one second.
+By comparison, a small flame ignited the gases flowing out of the top of the natural gas burner and the flames from the natural gas cover the entire burner surface within approximately one second.
 A similar ignition sequence occurs with the gasoline pan fires.
@@
 One of the videos was unusable for analysis due to reflected light which could not be edited out of the images.
-For same reason, the polyurethane foam flame height averages are the result from eight of the ten heat release rate experiments.
+For the same reason, the polyurethane foam flame height averages are the result from eight of the ten heat release rate experiments.
 
@@
 Avg Peak HF (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25~\%)   &	3.6 $\pm$ 0.9 (25~\%) 	& 2.5 $\pm$ 0.5 (20~\%)   \\
-Median FH (m)           &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
+Median FH (mm)           &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
 Avg Peak Temp. (C)      &   	410 $\pm$ 103 (25~\%)   &	335 $\pm$ 41 (12~\%) 	& 334 $\pm$ 106 (32~\%)   \\
@@
 Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array,a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array, a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
@@
 
-The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels in Appendix B.
+The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels.
 For the natural gas fueled experiments only two replicates were conducted at each position given the higher level of control and repeatability.
@@
 Comparing the temperatures of the plume at the most distant point from the wall, 0.61~m and with the plume temperatures with the burner contacting the wall in Figure~\ref{TC_Plume_TWNG_comp} shows an increase.
-However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs after approximately 3~min after ignition.
-A review of the heat release rates and the test videos do not yield any clues as to the reason for this decrease which occurred in both experiments.
-In both experiments the heat release rate was steady and the video did not show any change in flame movement.
+However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs approximately 3~min after ignition.
+It is worth noting that as the plume temperatures decrease the temperatures of the thermocouples installed in the wall face increased, indicating that after the wall heats up the flame pulls toward the wall.
+Perhpas as a result of increased convection on the face of the wall.
+
 Figures~\ref{TC_Surf_Cent_TWNG_comp} and \ref{TC_Surf_Edge_TWNG_comp} show consistent trends of the thermocouple temperatures in the vertical arrays on the wall increasing as the burner was moved toward the wall.
@@
 The data is treated in the same manner as in Figure~\ref{NCTW_Surf_Center_comp}.
-For each fuel the average peak temperatures at the burner edge are significantly lower when the centerline temperatures when the burner is positioned against the wall.
+For each fuel the average peak temperatures at the burner edge are significantly lower than the centerline temperatures when the burner is positioned against the wall.
 As the burners were moved away from the wall the temperatures at the centerline and the edge thermocouple arrays begin to converge.
@@
 Reviewing the graph for each fuel demonstrates how the heat flux at the wall decreased as the position of the burner was moved away from the wall.
-(Review video and tie in ST TC graph with edge peak NG at 0.15)
 
@@
 	\end{tabular}
-	\caption[Summary of instrumented non-combustible wall experiments]{Summary of peak temperatures and heat fluxes from the instrumented non-combustible wall experiments}
+	\caption[Summary of instrumented non-combustible wall experiments]{Summary of peak temperatures and heat fluxes from the instrumented non-combustible wall experiments.
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.}
 	\label{tab:TW_Summary}
@@
 
-The complete set of results from the instrumented gypsum wallboard experiments are provided in Appendix C.
 Table~\ref{tab:IWGB_experiments} lists the experiments that were conducted for each fuel type.
@@
 
-Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set} and \ref{IWGB_NG_TC_Backside_set} show the values for the natural gas burner experiments with the gypsum wallboard.
+A complete set of data temperature and heat flux data for the six natural gas burner experiments are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+The data for the burner positioned 0.31~m from the wall is the average of three replicate experiments.
+Note that the data set for the burner position 0.0~m from the wall only has 200~seconds of fire data.
+This was the result of a an early shut down of the gas supply.
+This decrepancy was not noticed until the data was reviewed.
+However at the point there was no opprotunity to rerun the experiment.
 
@@
 In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
-While the data generated from those experiments provide valuable insight, it would be of valuable to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
+While the data generated from those experiments provide valuable insight, it would be of value to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
 
@@
 The positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
-The area surrounding the center of the maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
+The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
 In other words, the area around the center point of the sample had heat flux measures similar, within the uncertainty of the device, to the center point measurement.
@@
 The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.
+Given the uncertainty if the temperature measurement these temperatures are not significantly different.
+Taking the average ignition temperature across all of these cone experiments yields a value of 360~$^{\circ}$C $\pm~54$~$^{\circ}$C.
 
@@
 	\end{tabular}
-	\caption[Painted gypsum wallboard ignition temperature results]{Painted gypsum wallboard ignition temperature results from exposure in the cone calorimeter}
+	\caption[Painted gypsum wallboard ignition temperature results]{Painted gypsum wallboard ignition temperature results from exposure in the cone calorimeter.
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\%.}
 	\label{tab:Gypsum_wallboard_igntemp}
@@
 	\caption[Flooring radiant panel experiment flame spread results]{Flooring radiant panel experiment flame spread results including time to ignition at 100~mm intervals and surface temperature just prior to ignition.
-The values are averages from three replicate experiments.}
+The values are averages from three replicate experiments.
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for heat flux.}
 	\label{tab:FRP_timetemp}
@@
 
-Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range physical damage to samples as shown in Figure~\ref{RPGB_SET}.
+Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range of physical damage to samples as shown in Figure~\ref{RPGB_SET}.
 However based on visual observations there were no flaming ignitions.
@@
 Nor is there a ``standard'' catalog of fire model inputs for a given material.
-As a result the literature is sourced for information and users may to conduct experiments, such as those above, in order to develop values or ranges of values which could be used in the calculations in Chapters 8 and 9 or to evaluate the validity of the calculations in those chapters.
+As a result the literature is sourced for information and users may need VII and VIII or to evaluate the validity of the calculations in those chapters.
 

### 2016-09-27 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Added abstract to burner report; acronyms to hose stream report

@@
 NIST \> National Institute of Standards and Technology \\
+OSB \> Oriented Strand Board \\
 SB \> Smooth Bore Stream\\
 SS \> Straight Stream \\
+TJI \> Truss Joist I-beams \\ 
 UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\

### 2016-09-27 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added author names & abstract section heading to report
Added abstract to burner report; acronyms to hose stream report

@@
 \flushright{
-
+Joseph M. Willi \\
+Craig G. Weinschenk \\
 \vspace*{2\baselineskip}
@@
 \flushright{
-
+Joseph M. Willi \\
+Craig G. Weinschenk$^*$ \\
 {\em Fire Research Division \\
@@
 \vspace*{2\baselineskip}
-May 2016}}
+September 2016}
+
+\vspace*{2\baselineskip}
+\textit{$^*$\small Currently with JENSEN HUGHES}
+}
 
@@
 \hspace{1.5in} \= \\
-FDS \> Fire Dynamics Simulator \\
-HGL \> Hot Gas Layer \\
-HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
+PPA \> Positive Pressure Attack \\
+PPV \> Positive Pressure Ventilation \\ 
 NIST \> National Institute of Standards and Technology \\
+OSB \> Oriented Strand Board \\
+TJI \> Truss Joist I-beams \\ 
+UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
 \end{tabbing}
+
+\mainmatter
+
+\chapter*{\centering Abstract}
+\pagenumbering{gobble}
+Nine full-scale fire experiments were conducted in two residential-scale structures to study how different fire fighting tactics, specifically horizontal, vertical, and positive pressure ventilation, affect the fire environment within a structure.
+The fire source for each experiment was provided by three propane burners.
+Five of the tests were conducted in a structure designed to simulate a single-story residential structure, and four of the tests were conducted in a structure designed to simulate a two-story residential structure.
+The structures were instrumented with sensors to collect local measurements of temperature, gas velocity, heat flux, and gas concentrations at various locations during the experiments.
+Different doors and vents were opened and closed during the tests to simulate horizontal and vertical ventilation.
+A PPV fan was also used during some of the experiments to further affect the ventilation conditions.
+This report contains detailed descriptions of the setup and procedure used for each of the nine experiments.
 
@@
 Five different tests, Tests~2--6, were conducted in the East Structure.
-Tables~\ref{table:HRR_Tests_2-4} and \ref{table:HRR_Tests_5-6} list the heat release rates for Tests~2--4 and Tests~5--6, respectively.
-The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
+Table~\ref{table:HRR_Tests_5-6} lists the heat release rates for Tests~5 and 6.
+The time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
+As a result, a single heat release rate, one for all three burners ignited, is reported.
+The heat release rates for Tests~2--4 are not reported because they were not able to be accurately measured during the tests.
+% The time between the ignition of each gas burner for Tests~2--4 was on the order of minutes, while the time between the ignition of each gas burner for Tests~5 and 6 was on the order of seconds.
 Thus, for Tests~2--4, heat release rates are reported for one, two, and three burners, and for Tests~5 and 6, a single heat release rate for three burners is reported.
@@
 
-\begin{table}[!ht]
-\caption{Heat Release Rates for Tests~2--4}
-\begin{tabular}{lccc}
- \toprule
- 					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
-\textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
-					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
-					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
- \midrule
-Test 2 				& 560 & 1080 & 1470 \\
-Test 3 				& 530 & 1040 & 1470 \\
-Test 4				& 580 & 1140 & 1580 \\
-\bottomrule
-\end{tabular}
-\label{table:HRR_Tests_2-4}
-\end{table}
+% \begin{table}[!ht]
+% \caption{Heat Release Rates for Tests~2--4}
+% \begin{tabular}{lccc}
+%  \toprule
+%  					& 	\multicolumn{3}{c}{\textbf{Heat Release Rate (kW)}} \\
+% \textbf{Test} 		&	\begin{tabular}{c} \textbf{One} \\ \textbf{Burner On} \end{tabular} 
+% 					&	\begin{tabular}{c} \textbf{Two} \\ \textbf{Burners On} \end{tabular}
+% 					&	\begin{tabular}{c} \textbf{Three} \\ \textbf{Burners On} \end{tabular} \\
+%  \midrule
+% Test 2 				& 560 & 1080 & 1470 \\
+% Test 3 				& 530 & 1040 & 1470 \\
+% Test 4				& 580 & 1140 & 1580 \\
+% \bottomrule
+% \end{tabular}
+% \label{table:HRR_Tests_2-4}
+% \end{table}
 
@@
 
+\chapter{Acknowledgments}
+\label{chap:acknowledgments}
+The authors would like to thank Daniel Madrzykowski (currently with UL FSRI), Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), and Keith Stakes (currently with UL FSRI) from NIST for their contributions in preparing and conducting these experiments.
+These experiments could not have been conducted without them.
+
 \bibliography{../../../../../Bibliography/FDS_refs,../../../../../Bibliography/FDS_general}

### 2016-09-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Reworking Chapter 4

@@
 
-Polyurethane foam was chosen as the solid fuel.
+Flexible polyurethane foam was chosen as the solid fuel.
 According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
@@
 Thermocouple is ungrounded.
-The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer~\cite{Omega}.
+The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer.
+The response time constant is approximately 0.2~seconds~\cite{Omega}.
 The variation of the temperature in the environment surrounding the thermocouple was known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2001}.
@@
 
-Mass loss measurements were not possible for the natural gas burner experiments.
+Mass loss measurements were not possible for the natural gas burner experiments, although as noted previously the mass flow of natural gas was approximately 2~g/s.
 The mass loss versus time curves for the gasoline and the polyurethane experiments are shown in Fig.~\ref{Mass}.
@@
 
-A complete set of data temperature and heat flux data for the six natural gas burner experiments are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+A complete set of data temperature and heat flux data for the natural gas burner experiments conducted at 0.31~m, 0.15~m, and 0.0~m are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
 The data for the burner positioned 0.31~m from the wall is the average of three replicate experiments.
-Note that the data set for the burner position 0.0~m from the wall only has 200~seconds of fire data.
+Note that the data set for the burner position 0.0~m from the wall only has 180~seconds of fire data.
 This was the result of a an early shut down of the gas supply.
 This decrepancy was not noticed until the data was reviewed.
-However at the point there was no opprotunity to rerun the experiment.
+However at the point there was no opportunity to rerun the experiment.
+
+The temperatures measured along the vertical center axis of the burner provide distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature see Figure~\ref{IWGB_NG_TC_Plume_set}.
+The persistant flame region appears to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
+Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seem to be in the intermittent flame region.
+The thermocouples position at or above 1.4~m appear to be in the buoyant plume region.
+The fluctuations in the peak temperatures for this ``steady state'' fire are the result of the flame movement away from the thermocouples centered above the burner.
+Note that the thermocouple positioned 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
+
+The temperatures measured on the front surface of the painted gypsum wallboard are displayed in Figure~\ref{IWGB_NG_TC_Wall_set}.
+When the burner was located 0.31~m and 0.15~m away from the wall the temperatures started at ambient and slowly increased  reaching the peak temperatures at 300~seconds when the burner was shut off.
+For the case where the burner was in contact with the wall, the two of the thermocouples located in the persistant flame region indicated a decreasing temperature trend after after the paper on the gypsum wallboard had burned away.
+The decrease in temperature my have had been the result of material from the burned gysum wallboard shielding otherwise impacting those thermocouples.
+The thermocouple positioned 0.2~m above the burner was exhibiting the same behavior as in the previous experiment, but the problem was resolved during the experiment.
+The restored connection to the data system accounts for the rapid rise in temperature at 60~seconds into the experiment.
+
+Figure~\ref{IWGB_NG_TC_Backside_set} has graphs of the temperature time histories of the themrocouples installed on the back face of the 12.7~mm thick gypsum wallboard.
+In each case the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
+As the position of the fire moves closer to the wall the rate of temperature rise on the back increases.
+The peak temperatures in each case were approximately 80~$^\circ$C.
+
+The heat flux values from the arrays of sensors mounted flush with the surface of the gypsum wallboard are given in Figures~\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+The data from the array centered on the burner and the data from the array located at the right edge of the burner are similar in response and magnitude when the burner is positioned away from the wall.
+Similar to the wall surface temperatures the heat flux increase as the burner is moved closer to the wall.
+However once the burner is in contact with the wall the flame is moving side to side.
+As a result, the peaks in the heat flux alternate between the center array and the edge array, as the flame moves and changes shape.
+This movement causes changes in the peak heat flux of approximately 20~kW/m$^2$.
+The averaged heat flux values graphed with respect to the burner position from the wall are shown in Figure~\ref{IWGB_NG_HF_CandEAvg}.
 
@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_TC_Back_Center_Avg}\\
-	\caption[Averaged peak temperatures on the backside of the gypsum board wall for the natural gas burner fires.]{Averaged peak temperatures along the vertical centerline of the backside of the gypsum board wall for the natural gas burner fires}
-	\label{IWGB_NG_Temp_RearCenter}
-\end{figure}
-
 \begin{figure}
@@
 }
-	\label{IWGB_NG_HF_RearCenter}
+	\label{IWGB_NG_HF_CandEAvg}
 \end{figure}
@@
 
-The averaged peak temperatures of the wall mounted thermocouples for the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
+Given that the focus of this study is on generating thermal damage on the face of the gypsum wallboard, the temperature and heat flux at the wall surface are important to examine.
+The averaged peak temperatures of the wall mounted thermocouples for each of the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
+This figure allows the comparison of the averaged peak temperatures at the wall based on the difference in fuel type and based on the burner's distance from the wall.
+The graphs in the Figure~\ref{IWGB_Temp_Comp_FrontCenter} show that generally the temperature at the wall surface decreases as the burner moves away from the wall.
+The exception to this appears to be at 0.08~m distance from the wall for the gasoline and polyurethane foam experiments.
+This position, 1/4 of the width of the burner away from the wall, caused the flame to oscillate toward the wall.
+As the flame moved toward the wall the flame impact zone on the wall moved around, higher to lower and side to side, which caused the scatter in the averaged data for that fire position.
 
@@
 
-Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays.
-For the gasoline fire experiment at the 0.08~m position the wall temperatures and the heat flux values from the burner edge array had values that were higher than when those measured at the 0.0~m position.
-The peak heat release rates for the positions at 0.0~m, 0.08~m and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
-So a change in HRR was not the source of the increase.
-The increased temperatures and heat flux at this position appears to be a matter of the flame movement toward the wall.
-In general, once the burner position for either natural gas or gasoline was within 0.15~m, or half the distance of the burner side dimension, the flames tended to pull toward the wall.
-This motion was not a steady motion but an oscillatory one.
+Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays for the natural gas, gasoline and polyurethane foam arrays.
+For the gasoline fire experiment at the 0.08~m position the heat flux values from the burner edge array had values that were similar or higher than those measured at the 0.0~m position.
+As discussed with temperatures above, this was a result of flame movement and the flame briefly contacting the wall near the right edge of the pan more so than seeing the increase at the centerline heat flux array.
+A review of the heat release rates for these experiments was made to see if that might have contributed to the higher heat flux, the peak heat release rates for the burner positions at 0.0~m, 0.08~m and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
+So a change in HRR did not contribute to the increase at the 0.08~m position.
+
+At the 0.15~m position the heat flux exhibits only a small decrease to the 0.2~m and 0.4~m above the burner heat flux sensors in the centerline array.
+However, the heat flux sensor positioned at 0.6~m above the burner showed an increase.
+As indicated above, the data which goes against the general trend of the data, is a result of the movement of the flame.
+For this experiment a sequence of photographs, Figure~\ref{IWGBGAS6_seq}, captured the oscillatory motion of the flame which moved from the vertical centerline toward the wall and back again.
+In the process the fire pattern on the wall was generated.
+
+The heat flux data from the polyurethane foam burner experiments also exhibited variations, although less pronounced than those of the gasoline experiments, at the 0.08~m and the 0.15~m position.
+The polyurethane foam generated less heat release rate and a shorter flame than the gasoline, so even though the flame was moving toward the wall, impact was not as great.
+Again this motion was not a steady motion but an oscillatory one.
 
@@
 	\label{IWGB_HF_Comp_Edge}
+\end{figure}
+
+\begin{figure}[p]
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq1}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq2}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq3}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq4} \\
+
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq5}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq6}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq7}
+	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq8} \\
+
+	\caption[Photographs of motion of the flame with the gasoline burner positioned 0.15~m from the wall]{Photographic sequence with the gasoline burner positioned 0.15~m from the instrumented gypsum wallboard.
+These photos capture both the oscillatory motion of the flame toward the wall as well as the burning of the gases which are pyrolyzing off of the wall and result in the formation of the lower edge of the fire pattern.}
+	\label{IWGBGAS6_seq}
 \end{figure}
@@
 Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as shown in Figure~\ref{Soot_pattern}.
-From the photograph the areas of penetration and consumption can be clearly delineated while the discolored and sooted areas tend to meld together.
-Further the focus of the measurements in this study are thermal, therefore the focus is on the burned, not burned line of demarcation.
+From the photograph the areas of penetration and consumption can be delineated while the discolored and sooted areas tend to meld together.
+Further the focus of the measurements in this study are on thermal damage, therefore the focus is on the burned to not burned line of demarcation.
 
@@
 	\label{IWGB_Gas_patterns}
-\end{figure}
-
-Figure~\ref{IWGBGAS6_seq} shows a comparison of a series eight photographs from the experiment where the gasoline burner was positioned 0.15~m from the instrumented gypsum wallboard.
-The photographs capture both the oscillatory motion of the flame toward the wall and the burning of the gases which are pyrolyzing off of the wall and result in the formation of the lower edge of the fire pattern.
-
-\begin{figure}[p]
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq1}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq2}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq3}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq4} \\
-
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq5}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq6}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq7}
-	\includegraphics[width=1.3in]{../Figures/IWGBGAS6_Seq8} \\
-
-	\caption[Photographs of the fire pattern formation from the gasoline burner positioned 0.15~m from the wall]{Photographic sequence of the fire pattern formation from the gasoline burner positioned 0.15~m from the instrumented gypsum wallboard.}
-	\label{IWGBGAS6_seq}
 \end{figure}

### 2016-09-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Edits to 3 and 4

@@
 
-These instrumented non-combustible wall experiments provide a data set for the fires conducted that can be compared against ignition data for gypsum wallboard from the literature to determine the potential for ignition of the paper surface of gypsum wallboard at a given distance from the wall with a given fuel.
+These instrumented non-combustible wall experiments provide a data set for the fires to be conducted that can be compared against ignition data for gypsum wallboard from the literature to determine the potential for ignition of the paper surface of gypsum wallboard at a given distance from the wall with a given fuel.
 The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
@@
 However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
-The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wall board ignites.
+Based on the heat flux data from Figures~\ref{NCTW_HF_Center_Comp} the natural gas burner should burn the paint and paper off of the face of the gypsum wallboard up to a height of between 0.6~m amd 0.8~m above the burner.
+Similarly, the gasoline burner should generate a burn area between 0.8~m and 1.0~m high on a wall composed of gypsum wallboard.
+Using the same analysis, the polyurethane foam burner would create a shorter burn region approximately 0.4~m to 0.6~m.
+The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the may gypsum wall board ignite.
 
@@
 	\includegraphics[width=2.5in]{../Figures/Soot_close}	\\
-	\caption[Photographs showing clear lines of demarcation with gasoline]{Photographs showing clear lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.
+	\caption[Photographs showing lines of demarcation with gasoline]{Photographs showing lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.
 Burned vs unburned area is clearly defined, where as the difference between sooted and thermally discolored areas is not as clear.}
@@
 
-Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrtaed paint/paper layer which exposed the gypsum underneath.
+Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath.
 

### 2016-09-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
complete 4 and revising Ch5

@@
 		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
-		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
+		\hline  Position & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) 	\\
 		\hline \hline 0.61~m & 95 & 5 & 106 & 7 & 71 & 6 \\
@@
 	\end{tabular}
-	\caption[Summary of instrumented non-combustible wall experiments]{Summary of peak temperatures and heat fluxes from the instrumented non-combustible wall experiments.
+	\caption[Summary of instrumented non-combustible wall experiments]{Summary of averaged peak temperatures and averaged heat fluxes from the instrumented non-combustible wall experiments.
 The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.}
@@
 A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.
+While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary} a closer look reveals that most of the values are not ``significantly '' different.
+In other words the range of expanded uncertainty values overlap.
+For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$pm$73~$^\circ$C (15~\%).
+So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
+While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' different.
 
@@
 		\hline {Burner} & \multicolumn{2}{c}{Natural Gas} & \multicolumn{2}{c}{Gasoline} & \multicolumn{2}{c|}{PU Foam} \\
-		\hline  Position & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) & Temp~(C) & HF~(kW/m$^{2}$) 	\\
+		\hline  Position & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) 	\\
 		\hline \hline 0.61~m & 132 & 4 & 109 & 6 & 76 & 4 \\
@@
 	\end{tabular}
-	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments}
+	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of averaged peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments.
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.}
 	\label{tab:IWGB_Summary}
@@
 Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath.
+The peak height of the consumed and penetrated paper, i.e.
+the burned region, was 0.8~above the burner.
+This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible was experiments.
 
@@
 
+Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
+When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed with the lowest point approximately 0.1~m above the burner and extending up to the 0.4~m above the burner on the left side.
+The formation of the burned area was captured on film and is shown in Figure~\ref{IWGBGAS6_seq}.
+The burned region on the gypsum wallboard from exposure to the gasoling fire position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
+The width of the burned region was approximately one half of the burner width at it's maximum.
+Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by gas burner when it is tight against the gypsum wallboard.
+Two views are shown.
+The image on the left shows the wall shortly after the fire went out.
+The burned area came be discerned, but a close look is required.
+In the photograph on the right, the same piece of gypsum wallboard was lightly brushed off, which revealed a clearer view of the area where the paint and paper were burned off.
+The peak height of that fire pattern is just short of 0.8~m.
+The maxim width is approximately the full width of the burner.
+
 \begin{figure}[p]
@@
 
+Figures~\ref{IWGB_PUF_patterns} and~\ref{IWGB_PUF_0m_patterns} show the progression of thermal damage caused by the polyurethane fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the instrumented gypsum wallboard.
+The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage, the only damage to the wall is from soot deposition.
+When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but the was no consumption or penetration of the paper finish layer.
+Three replicate experiments were conducted with the polyurethane foam fueled burner tight against the instrumented gypsum wallboard.
+The resulting patterns are shown in Figure~\ref{IWGB_PUF_0m_patterns}.
+The average height of the burned region of the painted paper finish on the wallboard was 0.3~m above the top of the burner.
+The maximum width of the burned region was approximately equal to the width of the burner.
+
 \begin{figure}[p]
@@
 	\centering
-	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
-	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
+	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF7_0m_crop}
+	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
+	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on three instrumented gypsum wallboards exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
 	\label{IWGB_PUF_0m_patterns}
 \end{figure}
+
+With this set of experiments, fire patterns as the result of thermal damage have finally generated in a few cases.
+To recap our crude predictions from the previous chapter, the natural gas burner had the potential to cause a fire pattern with a height between 0.6~m and 0.8~m.
+With the natural gas burner against the wall, a pattern with a maximum burn area of 0.8~m in height was generated.
+From Chapter III, the gasoline had a potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
+In the single instrumented gypsum wallboard experiment with the gasoline burner located against the wall, the maximum height of the burned region was just short of 0.8~m.
+The prediction for the potential height of the fire pattern that could be created with the polyurethane burner against the wall was between 0.4~ and 0.6~m.
+With the polyurethane burner three replicate experiments were conducted.
+The range of the maximum heights of the burned region was 0.2~m to 0.35~m.
+The average peak burned region height was 0.3~m.
+The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Ch III provided a ``ballpark'' estimate of the maximum height of the burned region.
 
@@
 In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
-While the data generated from those experiments provide valuable insight, it would be of value to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests.
+While the data generated from those full scale laboratory experiments provide valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests in an effort to validate or improve the existing data in the literature.
 
@@
 
-For the ignition tests, an electric spark igniter was positioned over the center of the horizontal samples to serve as a pilot.
+For the ignition tests, an electric spark igniter is positioned over the center of the horizontal samples to serve as a pilot.
 Combustion products and dilution air were extracted through the hood and exhaust duct by a high temperature fan.
@@
 The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
-In other words, the area around the center point of the sample had heat flux measures similar, within the uncertainty of the device, to the center point measurement.
+In other words, the area around the center point of the sample had heat flux measures similar, in other words within the uncertainty of the heat flux sensor, to the center point measurement.
 Outside of the central area of the samples, the heat flux would decrease as the position approached the edge of the sample.

### 2016-09-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revising Chapter 6

@@
 
+Table~\ref{tab:Fire_Pattern_Dimensions_Corners}
+
+\begin{sidewaystable}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+	Fuel (\# of tests)      &   Wall Type   & Max. Height Left (m)	 	& Area Left (m$^2$)				&  Max. Height Right (m)        & Area (m$^2$)  				\\ \hline \hline
+		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.15 (20~\%)  & 0.061 $\pm$ 0.028 (46~\%) 	&  0.78 $\pm$ 0.17 (22~\%) 	 	& 0.061 $\pm$ 0.028 (46~\%)  	\\
+		Gasoline (10)       &   Open    	& 0.47	$\pm$ 0.26 (55~\%)  & 0.027 $\pm$ 0.019 (70~\%) 	&  0.45 $\pm$ 0.31 (69~\%)  	& 0.019 $\pm$ 0.011 (58~\%)\\
+		PUF (3)       		&   Open 		& 0.32	$\pm$ 0.13 (41~\%)  & 0.056 $\pm$ 0.034 (61~\%) 	&  0.36 $\pm$ 0.091 (25~\%)  	& 0.071 $\pm$ 0.023 (32~\%)\\
+	\hline
+	\end{tabular}
+	\caption[Comparison of corner fire pattern height and area for the three types of burners]{Comparison of corner fire pattern height and area for the three types of burners.
+Values presented with 95~\% confidence limits.}
+	\label{tab:Fire_Pattern_Dimensions_Corners}
+\end{sidewaystable}
+
 \subsubsection{Natural Gas}
@@
 
-Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fuleed burner in the corner position with walls of open back construction.
+Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fueled burner in the corner position with walls of open back construction.
 
@@
 
-	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner.}
+	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner with walls of open construction.}
 	\label{Gas_Corner}
@@
 \subsubsection{Polyurethane Foam}
+
+Figure~\ref{PUF_Corner} shows a comparison of three fire patterns generated by the polyurethane foam fueled burner in the corner position with walls of open back construction.
+Only three replicates could be conducted due to the limits on the foam supply that was sourced from the same purchase.
+
+\begin{figure}[p]
+	\includegraphics[width=1.7in]{../Figures/GBPUF11_Corner}
+	\includegraphics[width=1.7in]{../Figures/GBPUF12_Corner}
+	\includegraphics[width=1.7in]{../Figures/GBPUF13_Corner} \\
+
+	\caption[Photographs of the fire patterns from three replicate polyurethane foam burner experiments positioned in a corner]{Photographs of the fire patterns from three replicate polyurethane foam fueled burner experiments positioned in a corner with walls of open construction.}
+	\label{PUF_Corner}
+\end{figure}
 

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
fix adobe error

@@
 
-A complete set of data temperature and heat flux data for the natural gas burner experiments conducted at 0.31~m, 0.15~m, and 0.0~m are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
-The data for the burner positioned 0.31~m from the wall is the average of three replicate experiments.
-Note that the data set for the burner position 0.0~m from the wall only has 180~seconds of fire data.
-This was the result of a an early shut down of the gas supply.
-This decrepancy was not noticed until the data was reviewed.
-However at the point there was no opportunity to rerun the experiment.
-
-The temperatures measured along the vertical center axis of the burner provide distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature see Figure~\ref{IWGB_NG_TC_Plume_set}.
-The persistant flame region appears to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
-Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seem to be in the intermittent flame region.
-The thermocouples position at or above 1.4~m appear to be in the buoyant plume region.
-The fluctuations in the peak temperatures for this ``steady state'' fire are the result of the flame movement away from the thermocouples centered above the burner.
-Note that the thermocouple positioned 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
-
-The temperatures measured on the front surface of the painted gypsum wallboard are displayed in Figure~\ref{IWGB_NG_TC_Wall_set}.
-When the burner was located 0.31~m and 0.15~m away from the wall the temperatures started at ambient and slowly increased  reaching the peak temperatures at 300~seconds when the burner was shut off.
-For the case where the burner was in contact with the wall, the two of the thermocouples located in the persistant flame region indicated a decreasing temperature trend after after the paper on the gypsum wallboard had burned away.
-The decrease in temperature my have had been the result of material from the burned gysum wallboard shielding otherwise impacting those thermocouples.
-The thermocouple positioned 0.2~m above the burner was exhibiting the same behavior as in the previous experiment, but the problem was resolved during the experiment.
-The restored connection to the data system accounts for the rapid rise in temperature at 60~seconds into the experiment.
-
-Figure~\ref{IWGB_NG_TC_Backside_set} has graphs of the temperature time histories of the themrocouples installed on the back face of the 12.7~mm thick gypsum wallboard.
-In each case the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
-As the position of the fire moves closer to the wall the rate of temperature rise on the back increases.
-The peak temperatures in each case were approximately 80~$^\circ$C.
-
-The heat flux values from the arrays of sensors mounted flush with the surface of the gypsum wallboard are given in Figures~\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
-The data from the array centered on the burner and the data from the array located at the right edge of the burner are similar in response and magnitude when the burner is positioned away from the wall.
-Similar to the wall surface temperatures the heat flux increase as the burner is moved closer to the wall.
-However once the burner is in contact with the wall the flame is moving side to side.
-As a result, the peaks in the heat flux alternate between the center array and the edge array, as the flame moves and changes shape.
-This movement causes changes in the peak heat flux of approximately 20~kW/m$^2$.
-The averaged heat flux values graphed with respect to the burner position from the wall are shown in Figure~\ref{IWGB_NG_HF_CandEAvg}.
-
-\begin{table}
+\begin{table}[ht!]
 	\centering
@@
 
-\begin{figure}[p]
+A complete set of data temperature and heat flux data for the natural gas burner experiments conducted at 0.31~m, 0.15~m, and 0.0~m are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+The data for the burner positioned 0.31~m from the wall is the average of three replicate experiments.
+Note that the data set for the burner position 0.0~m from the wall only has 180~seconds of fire data.
+This was the result of a an early shut down of the gas supply.
+This decrepancy was not noticed until the data was reviewed.
+However at the point there was no opportunity to rerun the experiment.
+
+The temperatures measured along the vertical center axis of the burner provide distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature see Figure~\ref{IWGB_NG_TC_Plume_set}.
+The persistant flame region appears to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
+Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seem to be in the intermittent flame region.
+The thermocouples position at or above 1.4~m appear to be in the buoyant plume region.
+The fluctuations in the peak temperatures for this ``steady state'' fire are the result of the flame movement away from the thermocouples centered above the burner.
+Note that the thermocouple positioned 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
+
+\begin{figure}[ht!]
 	\centering
@@
 
-\begin{figure}[p]
+The temperatures measured on the front surface of the painted gypsum wallboard are displayed in Figure~\ref{IWGB_NG_TC_Wall_set}.
+When the burner was located 0.31~m and 0.15~m away from the wall the temperatures started at ambient and slowly increased  reaching the peak temperatures at 300~seconds when the burner was shut off.
+For the case where the burner was in contact with the wall, the two of the thermocouples located in the persistant flame region indicated a decreasing temperature trend after after the paper on the gypsum wallboard had burned away.
+The decrease in temperature my have had been the result of material from the burned gysum wallboard shielding otherwise impacting those thermocouples.
+The thermocouple positioned 0.2~m above the burner was exhibiting the same behavior as in the previous experiment, but the problem was resolved during the experiment.
+The restored connection to the data system accounts for the rapid rise in temperature at 60~seconds into the experiment.
+
+\begin{figure}[ht!]
 	\centering
@@
 
-\begin{figure}[p]
+Figure~\ref{IWGB_NG_TC_Backside_set} has graphs of the temperature time histories of the themrocouples installed on the back face of the 12.7~mm thick gypsum wallboard.
+In each case the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
+As the position of the fire moves closer to the wall the rate of temperature rise on the back increases.
+The peak temperatures in each case were approximately 80~$^\circ$C.
+
+\begin{figure}[ht!]
 	\centering
@@
 
- \begin{figure}[p]
+\clearpage
+
+The heat flux values from the arrays of sensors mounted flush with the surface of the gypsum wallboard are given in Figures~\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+The data from the array centered on the burner and the data from the array located at the right edge of the burner are similar in response and magnitude when the burner is positioned away from the wall.
+Similar to the wall surface temperatures the heat flux increase as the burner is moved closer to the wall.
+However once the burner is in contact with the wall the flame is moving side to side.
+As a result, the peaks in the heat flux alternate between the center array and the edge array, as the flame moves and changes shape.
+This movement causes changes in the peak heat flux of approximately 20~kW/m$^2$.
+The averaged heat flux values graphed with respect to the burner position from the wall are shown in Figure~\ref{IWGB_NG_HF_CandEAvg}.
+
+ \begin{figure}[ht!]
  	\centering
@@
 
- \begin{figure}[p]
+  \begin{figure}[ht!]
  	\centering
  	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG01_HF_Offset_Avg}\\
- 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Offset_Avg}\\
+ 	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG04_HF_Center_Avg}\\
  	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Offset_Avg}\\
- 	\caption[Wall heat flux along the edge of the natural gas fueled burner]{Wall heat flux along the edge of the natural gas fueled burner.
+ \caption[Wall heat flux along the endge of the natural gas fueled burner]{Wall heat flux along the vertical edge of the natural gas fueled burner.
 Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
@@
 
-\begin{figure}
+\begin{figure}[ht!]
 	\centering
@@
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
-	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.
-}
+	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.}
 	\label{IWGB_NG_HF_CandEAvg}
 \end{figure}
+
+\clearpage
 
@@
 In other words the range of expanded uncertainty values overlap.
-For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$pm$73~$^\circ$C (15~\%).
+For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15~\%).
 So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
@@
 	\centering
-	\footnotesize
+	\scriptsize
 	\begin{tabular}{|c|c|c|c|c|c|c|}

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
working on conclusions
skipped ahead

@@
 HRRPUA \> Heat Release Rate per Unit Area \\
+NFPA \> National Fire Protection Association  \\
 NIST \> National Institute of Standards and Technology \\
@@
 
+distance from the wall
+
 degradation of gypsum board full scale
@@
 
+duration
+
 lessons learned  cameras   black paint
 
+corners
+
 \chapter{Conclusions}
 
-Repeatibilty
-Energy to Damage
-Flame Height
-Modeling
+The main objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
+The first step was to exmaine the repeatability of different pre-flashover fires.
+Three different fuels were used: natural gas, gasoline, and polyurethane foam.
+Each fuel had a similar top surface area.
+The heat release rate data showed that the variability was greater for more complex fuels.
+While the variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11~\%, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
+The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
+The patterns generated by the polyurethane foam fueled fire, had more variability than the natural gas and the gasoline fire patterns.
+This is likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
+The comparison of the fire pattern heights and the mean flame height demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+This trend is the same as exhibited by the repeatability of the heat release rate measurements.
+Given that heat release rate is the source of the energy which is transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the unceratinty in pattern and any associated thermal measurements.
+
+This paper also highlighted the many uncertainties that need to be considered in what appear to be simple fire experiments.
+There were a variety of uncertainties related to the composition of the fuels, measurement methods, and analysis techniques just to list a few of the areas considered.
+
+The second objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+The numerical tools used ranged from simple empirical algorithms to a computational fluid dynamics model.
+Each of the tools are freely available to investigators and many of the tools have been packaged in a form that allows the user to input the ``data'' and generate a result.
+There is software available to aid with the development of the computational fluid dynamics model.
+The first challenge in using the numerical tools is finding the appropriate data to us as input.
 

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
discussion

@@
 
+Comparison of Fire Patterns and Flame Heights
+
+Each of the two sets of experiments, the fire source characterization and the fire pattern, had uncertainties associated with them.
+In the case of the fire source characterization, there were uncertainties associated with the fuel composition itself, the measurement of the heat release rate, temperature, heat flux and flame height.
+The fire pattern experiments had additional uncertainties which included: the composition and thickness of the gypsum wallboard, moisture content and paint thickness.
+In both sets of experiments, efforts were made to limit the uncertainties in the fuels, the measurement techniques and the gypsum wallboard.
+In this laboratory based study, the key question is – for a given fire pattern, is there a relationship that can be demonstrated to determine the source fire?
+
+At this stage of the research, the answer to the above question is yes and no.
+Figure 16 shows the comparisons of the average maximum fire pattern heights with those of the mean flame height based on the analysis of the video images.
+The associated 95~\% confidence limits are also shown for each height.
+
+The comparison for the fire pattern heights and flame heights from the natural gas fueled fires are very similar.
+This is expected in part because the natural gas fires are “steady state”.
+The “steady” nature of the fire aids in the repeatability or the reduction of variability in the experiments.
+For example the energy transfer to the gypsum wall board is also fairly “steady” for the duration of the experiment.
+Based on the average total heat released, approximately 23 MJ, more energy was transferred to the wall board when compared to the other two fuels.
+This energy is needed to “dry” out the gypsum wallboard both of water absorbed from the environment and the chemically bound water, to allow the paper cover and paint to burn.
+
+The gasoline fueled fires also had similar fire pattern heights and flame heights; however, the similarity was not as strong as the natural gas fires.
+The transient nature of the fire played a strong role here, there was less energy transferred to the gypsum wall board and the exposure time for portions of the wall board more distant from the fuel surface was less.
+Another issue that comes into the discussion is the length of time, 30 s, that was used for flame height analysis.
+This period of time was used to ensure that the flame height at the time of peak heat release rate was included in the analysis.
+However, this ultimately may have had the effect of reducing the mean flame height.
+The mean flame height based on the photo analysis was 0.84 m.
+The photo analysis was also performed over a 30 s period bounding the peak heat release rate but the number of images analyzed was about one sixth of the images analyzed with the video technique.
+It should also be noted that the range of the flame heights increased, especially on the lower bound, with the video analysis compared to the photo analysis.
+
+The polyurethane foam fueled fire heights and the associated fire pattern heights had the least similarity when compared to the other two fuels.
+This follows with the other findings about the polyurethane fueled fires in this study.
+The most prominent being the complications added by the fuel being solid and the uncertainties of the flame spread and localized burning rates, leading to poor repeatability of the fire growth and the heat release rate relative to the natural gas and the gasoline fueled fires.
+
+Mean flame height has been identified by Heskestad and others as having a strong relation to a given heat release rate from fires with a horizontal fuel surface~\cite{Heskestad:SFPE, Beyler:1986}.
+However, the ability to relate the mean flame height to the fire pattern height, based on the limited tests here is best suited to a “steady state” case.
+In cases where transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wall board or other target fuel even for “simple” pre-flashover fire patterns.
+
 \subsection{The Fire Investigators' Challenge}
@@
 The captain tells you that the doors and windows were closed upon arrival.
-When the front door was opened heavy smoke
+When the front door was opened heavy smoke and flame
+flow path
+inconsistant fire pattern near the right side of the sofa.  It appears that pattern was generated pre-flashover.  The pattern height is on the order of   calc HRR and FH for cushion.
 

### 2016-09-29 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex

@@
 Joseph M. Willi \\
-Craig G. Weinschenk$^*$ \\
+Craig G. Weinschenk \\
 {\em Fire Research Division \\
@@
 
-\vspace*{2\baselineskip}
-\textit{$^*$\small Currently with JENSEN HUGHES}
 }
@@
 \pagenumbering{gobble}
-Nine full-scale fire experiments were conducted in two residential-scale structures to study how different fire fighting tactics, specifically horizontal, vertical, and positive pressure ventilation, affect the fire environment within a structure.
-The fire source for each experiment was provided by three propane burners.
-Five of the tests were conducted in a structure designed to simulate a single-story residential structure, and four of the tests were conducted in a structure designed to simulate a two-story residential structure.
-The structures were instrumented with sensors to collect local measurements of temperature, gas velocity, heat flux, and gas concentrations at various locations during the experiments.
-Different doors and vents were opened and closed during the tests to simulate horizontal and vertical ventilation.
-A PPV fan was also used during some of the experiments to further affect the ventilation conditions.
+Nine full-scale fire experiments were conducted in two residential-scale structures to measure the effect of passive and forced ventilation on the fire conditions.
+The fires were fueled by three propane burners.
+Five of the experiments were conducted in a single-story structure, and four were conducted in a two-story structure.
+The structures were instrumented to measure temperature, gas velocity, heat flux, and oxygen, carbon dioxide and carbon monoxide concentrations.
+Various doors and vents were opened and closed during the experiments to provide passive horizontal and vertical ventilation.
+A fan was used to provide forced ventilation.
 This report contains detailed descriptions of the setup and procedure used for each of the nine experiments.
@@
 There are a variety of tactics used by firefighters that can affect the ventilation of a fire environment.
-For example, firefighters may open different doors and windows within a structure or cut holes in a structure's roof with the intention of removing hot gases and smoke from the structure's interior and introducing fresh, cool air into the environment.
-Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) on the fire ground in an attempt to improve the tenability of the fire environment.
-PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh, exterior air through the opening into the structure and exhaust hot gases and smoke out of the structure through a separate vent.
+For example, firefighters may open different doors and windows within a structure or cut holes in the roof to remove hot gases and smoke.
+Additionally, firefighters sometimes employ a tactic known as ``positive pressure attack'' (PPA) or ``positive pressure ventilation'' (PPV) in an attempt to improve the tenability of the fire environment.
+PPA/PPV involves using a fan aimed at an opening of a structure and is intended to force fresh air into the structure and force hot gases and smoke out through a separate exterior vent.
 
 Nine full-scale fire experiments were performed to study how the tactics described above affect ventilation and the fire environment within a structure.
-The tests were conducted in two structures designed to replicate typical residential dwellings.
+The experiments were conducted in two structures designed to replicate typical residential dwellings.
 During each experiment, propane was provided to three diffusion flame burners.
@@
 \label{chap:Experimental_Setup}
-The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, PA.
-Three propane burners were used to provide the fire source for all experiments, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
+The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, Pennsylvania.
+Three propane burners were used to fuel the fire for all experiments, and various sensors were used to collect gas temperature, gas velocity, heat flux, and gas concentration measurements throughout the structure.
 
@@
 The first floor ceiling support of each structure was composed of wood truss joist I-beams (TJIs).
-Each TJI had a depth of 298~mm (11.75~in) and contained laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}.
+Each TJI had a depth of 298~mm (11.75~in) and contained laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) by 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web as shown in Fig.~\ref{fig:TJI}.
 A layer of 18.3~mm (0.72~in) thick tongue and groove OSB was attached to the top of the TJIs.
@@
 \label{sec:Uncertainty}
-There are different components of uncertainty in the reported length, mass, temperature, heat flux, gas concentration, differential pressure, gas velocity, and heat release rate measurements.
-Uncertainties are grouped into two categories according to the method used to estimate them.
-Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
-Type B analysis of systematic uncertainties involves estimating the upper (+a) and lower (-a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$a) is essentially 100~\%.
-After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
-For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
-For other components, referenced research results and past experience with the instruments provided input in the uncertainty determination.
+This section lists the uncertainties in the reported length, mass, temperature, heat flux, gas concentration, gas velocity, and heat release rate measurements.
+Uncertainty estimates are based either on manufacturer literature or analyses performed by others for similar measurement devices and techniques.
+In accordance with NIST guidelines~\cite{Taylor&Kuyatt:1994}, measurement accuracy is reported as an {\em expanded uncertainty} or 95~\% ($2\,\sigma$) confidence interval.
+Most manufactures express accuracy in terms of a {\em standard  uncertainty} or 68~\% ($1\,\sigma$) confidence interval.
 
 \subsubsection{Compartment Dimensions}
-Each length measurement was taken carefully.
-Length measurements such as the room dimensions and instrumentation array locations were made with a hand held laser measurement device, which has an accuracy of $\pm$6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
-Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate individual sensors within a measurement array and to measure and position the furniture.
+Room dimensions and instrumentation array locations were made with a hand held laser measurement device with a standard uncertainty of $\pm$6.0~mm (0.25~in) over a range of 0.6~m (2.0~ft) to 15~m (50.0~ft)~\cite{StanleyTools}.
+Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate measurement devices.
 The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
-Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$1.0~\% for length measurements.
+These uncertainties are all well within the precision of the reported dimensions, which are typically rounded to the nearest 10~cm (4~in).
 
@@
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.
-Maximum percent error has been reported to be as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple~\cite{Blevins:1999,Pitts:2003}.
+Expanded uncertainties as high as 20~\% for upper layer temperatures measured by a 1~mm bare-bead type K thermocouple have been reported by NIST researchers~\cite{Blevins:1999,Pitts:2003}.
 Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling.
-The estimated total expanded uncertainty associated with the temperature measurements is $\pm$15~\%.
+The estimated relative expanded uncertainty associated with the temperature measurements is $\pm$15~\%.
 
 \subsubsection{Heat Flux Gauges}
-Total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
+Total heat flux measurements were made with water-cooled Schmidt-Boelter gauges.
 The manufacturer reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the relative expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
 
 \subsubsection{Gas Sampling}
-The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$12~\% is associated with the gas concentrations~\cite{Lock:1}.
-
-\subsubsection{Pressure Transducers}
-Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated, and the zero and span of each were checked in the laboratory prior to the experiments yielding an accuracy of $\pm$1~\%~\cite{Setra:2002}.
-The total expanded uncertainty is estimated at 10~\%.
+The gas sampling system has a relative expanded uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.
 
 \subsubsection{Bi-Directional Probes}
-Bi-directional probe and single thermocouple pairs were used to measure gas velocity.
-The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-A single bare-bead Chromel-Alumel (type K) thermocouple with a 1.0~mm (0.04~in) nominal diameter was co-located with each probe.
-The thermocouple wire was protected with a 3.2~mm (0.13~in) diameter inconel sheath.
-A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$0.14 to $\pm$0.22 for bi-directional probes similar to the ones described here~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity measurements is estimated to be $\pm$18~\%.
+Bi-directional probes were used to measure gas velocity in doorways.
+Bryant~\cite{Bryant:FSJ2009} estimates that the relative expanded uncertainty of this measurement ranges from $\pm$14~\% to $\pm$22~\%.
 
 \subsubsection{Heat Release Rate}
-A rotary type gas meter was used to measure the volume of propane provided to the gas burners.
-The manufacturer quantifies the maximum error of the meter as $\pm$2~\%~\cite{Romet:2014}.
+A rotary type gas meter was used to measure the volume flow rate of propane into the gas burners.
+The manufacturer reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014}.
 A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
 The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm12$~\%.
-
-\clearpage
 
@@
 
-\chapter{Acknowledgments}
+\chapter*{Acknowledgments}
+\addcontentsline{toc}{chapter}{Acknowledgments}
 \label{chap:acknowledgments}
-The authors would like to thank Daniel Madrzykowski (currently with UL FSRI), Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), and Keith Stakes (currently with UL FSRI) from NIST for their contributions in preparing and conducting these experiments.
-These experiments could not have been conducted without them.
+The authors would like to thank Daniel Madrzykowski, Roy McLane, Kristopher Overholt, and Keith Stakes for their contributions in preparing and conducting these experiments.
 

### 2016-09-29 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Moved Craig's name to acknowledgements

@@
 Joseph M. Willi \\
-Craig G. Weinschenk \\
 \vspace*{2\baselineskip}
@@
 Joseph M. Willi \\
-Craig G. Weinschenk \\
 {\em Fire Research Division \\
@@
 Five of the experiments were conducted in a single-story structure, and four were conducted in a two-story structure.
-The structures were instrumented to measure temperature, gas velocity, heat flux, and oxygen, carbon dioxide and carbon monoxide concentrations.
+The structures were instrumented to measure temperature, gas velocity, heat flux, and oxygen, carbon dioxide, and carbon monoxide concentrations.
 Various doors and vents were opened and closed during the experiments to provide passive horizontal and vertical ventilation.
@@
 
-% The ceiling height of each compartment within the structures was approximately 2.4~m (8~ft).
-The interior dimensions of the East Structure were approximately 6.1~m (20~ft) by 11~m (36~ft), and the interior dimensions of the first and second floors of the West Structure were 5.8~m (19~ft) by 10.7~m (35.1~ft) and 6.1~m (20~ft) by 10.9~m (35.8~ft), respectively.
-The stairs connecting the two floors of the West Structure started 1.6~m (5.3~ft) off the interior south wall with a width of 1.2~m (4~ft) off the interior east wall and contained a 184~mm (7.25~in) rise and 191~mm (7.5~in) run.
-
 The exterior doors of both structures, the stairwell door in the West Structure, and the square roof vent with a depth of 320~mm (12.75~in) in the East Structure were opened and closed at certain instances during the experiments to change the ventilation patterns within the structures.
-
-% The exterior doors were made of steel and the stairwell door on the second level of the West Structure was made of lauan plywood.
-% The roof vent was composed of 16~mm (0.63~in) thick Type X gypsum board (interior side) attached to
 
@@
 \label{chap:acknowledgments}
-The authors would like to thank Daniel Madrzykowski, Roy McLane, Kristopher Overholt, and Keith Stakes for their contributions in preparing and conducting these experiments.
+The author would like to thank Daniel Madrzykowski, Roy McLane, Kristopher Overholt, Keith Stakes, and Craig Weinschenk for their contributions in preparing and conducting these experiments.
 

### 2016-09-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
New FDS Images Corner

@@
 
+\begin{figure}[p]
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner1}
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner2}
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner3} \\
+
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner4}
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner5} 
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner6} \\
+
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner7}
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner8}
+	\includegraphics[width=1.2in]{../Figures/FDSNG_Corner9} \\
+
+	\caption[Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner.]{Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner.
+The time interval between images is 0.3 of second.}
+	\label{GBNG34Sequence}
+\end{figure}
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/10}
+  \includegraphics[width=2.5in]{../Figures/11}\\
+  \hspace{4 mm}  \\ 
+  \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
+The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
+This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
+  \label{FDS_FirePattern_comp}
+\end{figure}
+
 \chapter{Discussion}

### 2016-09-30 Projects/DelCo_2012/Report/DelCo_2012.tex
Final copy of hose stream report; minor edits to CAF and burner reports

@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1927}
 \end{flushright}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.1927}
 \endgroup
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (August 2016) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (August 2016) \\
 CODEN: NTNOEF }
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1927}{\bf http://dx.doi.org/10.6028/NIST.TN.1927} \\
 \endgroup
@@
 \vspace{0.5in}
-Key words: compressed air foam, fire experiments, fire fighting, fire suppression, fuel load, gas cooling, structural fire fighting, suppression research
+Keywords: compressed air foam, fire experiments, fire fighting, fire suppression, fuel load, gas cooling, structural fire fighting, suppression research
 

### 2016-09-30 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
Final copy of hose stream report; minor edits to CAF and burner reports

--- 2016-09-20 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1938}
 \end{flushright}
@@
 \headerB{
-Impact of Hose Streams on Air Flows inside a Structure \\
+Impact of Hose Streams on Air Flows Inside a Structure \\
 }
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1938}{http://dx.doi.org/10.6028/NIST.TN.1938}
 \endgroup
@@
 \headerB{
-Impact of Hose Streams on Air Flows inside a Structure
+Impact of Hose Streams on Air Flows Inside a Structure
 }
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1938}{http://dx.doi.org/10.6028/NIST.TN.1938} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (September 2016) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1938 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1938, \pageref{LastPage} pages (September 2016) \\
 CODEN: NTNOEF }
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.1838} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1938}{\bf http://dx.doi.org/10.6028/NIST.TN.1938} \\
 \endgroup
@@
 \hspace{1.5in} \= \\
-ESTC \> Delaware County Emergency Services Training Center \\
 NF \> Narrow Fog Stream\\
 NIST \> National Institute of Standards and Technology \\
+OSB \> Oriented Strand Board \\
 SB \> Smooth Bore Stream\\
 SS \> Straight Stream \\
+TJI \> Truss Joist I-beams \\ 
 UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
@@
 To better quantify the impact of such air flows on the fire environment, additional experiments need to be conducted with structure fires in a controlled environment.
+
+\vspace{0.5in}
+Keywords: fire fighting, fire suppression, hose streams, nozzles, ventilation
 
@@
 \label{sec:exp_setup}
-The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
+The series of field experiments described in this report were conducted in two structures of similar design located at the Delaware County Emergency Services Training Center in Sharon Hill, Pennsylvania.
 Differential pressure and temperature sensors were installed at ventilation points throughout the test structures to determine air velocity during the water flow experiments.
@@
 
-The second floor of the Two Story Structure was built on the wood ceiling support described above and was connected to the first floor by a stairwell.
-The walls of the second floor were wood-frame with nominal 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
-The interior walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+The second floor of the Two Story Structure was built on the structure's first floor wood ceiling support.
+The two floors were connected by an interior stairwell.
+A door made of lauan plywood was located at the top of the stairwell.
+The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
 The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board.
-The exterior walls were protected with 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
+The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
 

### 2016-09-30 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Final copy of hose stream report; minor edits to CAF and burner reports
Added manufacturer + device names to uncertainty section

@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XX, \pageref{LastPage} pages (May 2016) \\
-% http://dx.doi.org/10.6028/NIST.TN.XXXX \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (October 2016) \\
 CODEN: NTNOEF }
@@
 The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board.
-The exterior side of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
+The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
 
@@
 \subsubsection{Thermocouples}
-The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}.
+The standard uncertainty in the temperature of the thermocouple wire itself as determined by the wire manufacturer, OMEGA Engineering, Inc., is $\pm$2.2$~^{\circ}$C at $277~^{\circ}$C and increases to $\pm$9.5$~^{\circ}$C at $871~^{\circ}$C~\cite{Omega:2004}.
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty.
@@
 Total heat flux measurements were made with water-cooled Schmidt-Boelter gauges.
-The manufacturer reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
+The manufacturer, MEDTHERM Corporation, reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
 Results from an international study on total heat flux gauge calibration and response demonstrated that the relative expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
@@
 \subsubsection{Gas Sampling}
-The gas sampling system has a relative expanded uncertainty of $\pm$1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+A gas sampling system with relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} from California Analytical Instruments, Inc.
+(model 602P) was used to make gas concentration measurements.
 However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.
@@
 \subsubsection{Bi-Directional Probes}
-Bi-directional probes were used to measure gas velocity in doorways.
+Bi-directional probes with Setra 264 pressure transducers from Setra Systems, Inc.
+were used to measure gas velocity in doorways.
 Bryant~\cite{Bryant:FSJ2009} estimates that the relative expanded uncertainty of this measurement ranges from $\pm$14~\% to $\pm$22~\%.
@@
 A rotary type gas meter was used to measure the volume flow rate of propane into the gas burners.
-The manufacturer reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014}.
+The manufacturer, Romet Limited, reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014} for this type of meter (model RM-3000).
 A volumetric flow rate was calculated from the gas meter volume readings and used in conjunction with the heat of combustion of propane to calculate the heat release rate of the fire.
-The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm12$~\%.
+The total expanded uncertainty for the heat release rate obtained from this method is estimated to be $\pm8$~\%.
 

### 2016-10-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
add corner comp
Added STC heat data files for HF
modified HF dot py file

@@
 Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0~m and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
+It should be noted that the coefficient, 0.235, is dependent on the ratio of the heat of combustion to the actual mass stoichiometric ratio of air to volatiles of the fuel.
+For many liquid and gaseous fuels this coefficient is representative, Heskestad points out, however, that some common fuels, such as gasoline, deviate from the cited range.
+For gasoline a coefficient value of 0.2 should be used 32.
 Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.
@@
 \section{Comparison of Results}
+
+From Interflam  Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
+These calculated values were compared to the measured results from “real fuels” and provided reasonable results.
+Ranges of values were calculated in order to address the uncertainty in the heat release rate measurements.
+Other uncertainties, such as lack of knowledge on the exact fuel composition need to be addressed, as this may well be the case in a real fire investigation.
+Even accounting for uncertainties in heat release rate measurement, the flame height estimates tended to be better aligned with the peak flame height than the median flame height.
+A specific coefficient for “gasoline” was used in Heskestad’s equation which resulted in the measured median flame height being within the range of the predictions.
+The heat flux estimations were calculated with a range of radiant heat fractions, with the intent of the “actual” value being in that range.
+With the exception of gasoline, the estimated heat flux values tended to under predict the measured results.
+Given the limitations of the data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
+These algorithms are tools which can be used to provide insight into a problem, but not an accurate single value answer.
 
@@
   \hspace{4 mm}  \\ 
-  \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
+  \includegraphics[width=.8\columnwidth]{../Figures/NGCorner_guideline}\\
   \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
-The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
+The image with the three replicate fire patterns has a red line indicating a position approximately 1.6~m above the burner.
 This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
+
   \label{FDS_FirePattern_comp}
@@
 corners
+
+While the results from this project will provide some insight into the repeatability of pre-flashover fire patterns, a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions, are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
 

### 2016-10-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added refs and text to Chs 2 through 5

@@
 The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
+An initial series of heat release rate experiments included a heat flux gauge located 2~m from the centerline of the burner and positioned 0.5~m above the top of the burner.
+the data is provided.
+Once the frame was needed to support and position the thermocouples and heat flux gauges, the flux gauge at the 2~m local was not longer used due to concerns fo the frame interferring with the measurement.
 The manufacturer reports a 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm}.
@@
 The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$ respectively.
-The values are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.
+The values in Fig.~\ref{Flux} are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.
+
+In the initial heat release rate experiments another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~ above the top of the burners.
+At this location the average peak total heat flux measured for the natural gas fires were approximately 0.42~kW/m$^2$.
+The average peak values for the gasoline and polyurethane foam were approximately 0.74~kW/m$^2$ and 0.35~kW/m$^2$ respectively.
 
@@
 
-\subsection{Summary}
+\section{Summary}
 
@@
 \begin{table}
-\small
+\footnotesize
 \centering
@@
 type                    &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
-Avg. Peak HRR (kW)      &       80 $\pm$ 9 (11~\%)   &	80 $\pm$ 24 (30~\%) 	& 45 $\pm$ 21 (47~\%)   \\
+Peak HRR (kW)      &       80 $\pm$ 9 (11~\%)   &	80 $\pm$ 24 (30~\%) 	& 45 $\pm$ 21 (47~\%)   \\
 Total HR (MJ)           &   	23.3 $\pm$ 1.6 (7~\%)   &	13.6 $\pm$ 0.6 (4~\%) 	& 4.1 $\pm$ 0.2 (5~\%)   \\
-Avg Peak HF (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25~\%)   &	3.6 $\pm$ 0.9 (25~\%) 	& 2.5 $\pm$ 0.5 (20~\%)   \\
+Peak HF @ 0.95~m (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25~\%)   &	3.6 $\pm$ 0.9 (25~\%) 	& 2.5 $\pm$ 0.5 (20~\%)   \\
+Peak HF @ 2.0~m (kW/m$^2$)   &   	0.42 $\pm$ 0.03 (8~\%)   &	0.74 $\pm$ 0.24 (32~\%) 	& 0.35 $\pm$ 0.18 (51~\%)   \\
 Median FH (mm)           &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
-Avg Peak Temp. (C)      &   	410 $\pm$ 103 (25~\%)   &	335 $\pm$ 41 (12~\%) 	& 334 $\pm$ 106 (32~\%)   \\
+Peak Temp. (C)      &   	410 $\pm$ 103 (25~\%)   &	335 $\pm$ 41 (12~\%) 	& 334 $\pm$ 106 (32~\%)   \\
 \hline
 \end{tabular}
- \caption[Select measurements for the three source fires]{Select measurements for the three source fires.
+ \caption[Select average measurements for the three source fires]{Select average measurements for the three source fires.
 Each measurement is shown with 95~\% confidence limits both in terms of a value and a percentage.}
@@
 
-These instrumented non-combustible wall experiments provide a data set for the fires to be conducted that can be compared against ignition data for gypsum wallboard from the literature to determine the potential for ignition of the paper surface of gypsum wallboard at a given distance from the wall with a given fuel.
-The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
-Table~19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate sources.
-
-Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321,Quintiere:1985}.
-The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565~$^{\circ}$C with a critical heat flux for ignition of 35~kW/m$^2$.
-
-The second source, was a series of cone calorimeter experiments conducted by Dillon~\cite{ASTM_E1354,Dillon:1998}.
-The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.5~mm thick was 515~$^{\circ}$C with a minimum heat flux required for ignition of 26~kW/m$^2$.
-
-A summary of the peak average temperatures and heat fluxes at the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.
-Based on the temperature criteria for igniting gyspum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
-Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria, when positioned against the wall and at when the edge of the burner was 0.15~m away from the wall.
+A series of experiments were conducted with the three different burners positioned a several distances from a non-combustible wall.
+The main purpose was to collect data under conditions where the wall would provide a geometric and thermal influence without any contribution to the heat release rate.
+A summary of the peak average temperatures and heat fluxes at the face of the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.
 
@@
 
+This set of experimental results provided an opportunity to make a pre-test fire pattern assessment for the gypsum wallboard experiments which followed.
+By comparing the measured temperature and heat flux data against ignition data for gypsum wallboard from the literature, a determination was made on the potential for ignition of the painted, paper surface of gypsum wallboard at a given distance from the wall with a given fuel.
+The Ignition Handbook by Babrauskas is the most comprehensive set of ignition data and related information ever written~\cite{Babrauskas:2003}.
+Table~19 in the Ignition Handbook includes calculated ignition temperatures from experimental data from two separate sources.
+
+Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, a test apparatus which they developed ~\cite{ASTM_E1321,Quintiere:1985}.
+The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565~$^{\circ}$C with a critical heat flux for ignition of 35~kW/m$^2$.
+
+The second source, was a series of cone calorimeter experiments conducted by Dillon~\cite{ASTM_E1354,Dillon:1998}.
+The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.7~mm thick was 515~$^{\circ}$C with a minimum heat flux required for ignition of 26~kW/m$^2$.
+
 Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material.
@@
 Using the same analysis, the polyurethane foam burner would create a shorter burn region approximately 0.4~m to 0.6~m.
-The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the may gypsum wall board ignite.
+The experiments conducted with the instrumented painted gypsum wallboard will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wallboard ignited and if the paint and paper contributed to the heat release rate and spread of the fire pattern.
 
@@
 NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dihydrated gypsum to map fire patterns.
+
+McGraw and Mowrer conducted a study to examine both the flammability and dehydration of unpainted and painted gypsum wallboard~\cite{McGraw:1999}.
+Their study exposed gypsum wallboard samples to heat fluxes of 25, 50, and 75~kW/m~$^2$ using a cone calorimeter.
+None of the samples ignited at 25~kW/m~$^2$, even with exposure times of 15 minutes.
+The results showed that two coats of latex paint had little effect on the time to ignition at 50~kW/m~$^2$.
+However it did increase the peak heat release rate per unit area from 111~kW/m~$^2$ to 211~kW/m~$^2$.
+The total heat released per unit area over the course of the exposure also increased from 1561~kJ/m~$^2$ to 2284~kJ/m~$^2$.
+After the Type X gypsum wallboard samples were exposed to the heat flux, the samples were cut and the depth of dehydration was assessed by length measurement.
+Analytic means were used to determine that two coats of latex paint would not contribute the flame spread on the gypsum wallboard and using the moisture mass loss, a secondary means was used to approximate the depth of calcination.
+The limited impact of the paint on the flammability of the gypsum board was important in the development of this current study.
 
@@
 Note that the data set for the burner position 0.0~m from the wall only has 180~seconds of fire data.
-This was the result of a an early shut down of the gas supply.
+This was the result of an early shut down of the gas supply.
 This decrepancy was not noticed until the data was reviewed.
@@
 The fluctuations in the peak temperatures for this ``steady state'' fire are the result of the flame movement away from the thermocouples centered above the burner.
-Note that the thermocouple positioned 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
 
@@
 When the burner was located 0.31~m and 0.15~m away from the wall the temperatures started at ambient and slowly increased  reaching the peak temperatures at 300~seconds when the burner was shut off.
+Note that during the 0.15~m burner position experiment, the thermocouple located 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
 For the case where the burner was in contact with the wall, the two of the thermocouples located in the persistant flame region indicated a decreasing temperature trend after after the paper on the gypsum wallboard had burned away.
@@
 This movement causes changes in the peak heat flux of approximately 20~kW/m$^2$.
-The averaged heat flux values graphed with respect to the burner position from the wall are shown in Figure~\ref{IWGB_NG_HF_CandEAvg}.
+
+In Figure~\ref{IWGB_NG_HF_CandEAvg}, the averaged peak heat flux values for the natural gas burner experiments are graphed with respect to the distance that the burner was positioned from the gypsum wallboard.
+The data for both of the vertical heat flux gauge arrays, located on the centerline and the right edge of the burner are provided.
+In general the heat flux trends from higher in the positions near the wall to lower as the burner was positioned further from the wall.
+However once the burner was within 0.15~m of the wall or less, the flame was drawn toward the wall.
+As a result some of the peak heat fluxes occurred at heights that were out of sync with the trends at the positions further from the wall.
 
@@
 
-\subsection{Fire Pattern}
+\subsection{Fire Patterns}
 
@@
 
-Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as shown in Figure~\ref{Soot_pattern}.
-From the photograph the areas of penetration and consumption can be delineated while the discolored and sooted areas tend to meld together.
-Further the focus of the measurements in this study are on thermal damage, therefore the focus is on the burned to not burned line of demarcation.
+Soot and discoloration alone were not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as shown in Figure~\ref{Soot_pattern}.
+From the photograph the areas of penetration and consumption can be delineated while the discolored and sooted areas tended to blend together.
+Further the focus of the measurements in this study are on thermal damage, therefore the focus is on the ``burned to not burned'' line of demarcation.
 
@@
 	\caption[Photographs showing lines of demarcation with gasoline]{Photographs showing lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.
-Burned vs unburned area is clearly defined, where as the difference between sooted and thermally discolored areas is not as clear.}
+Burned vs unburned area was clearly defined, where as the difference between sooted and thermally discolored areas was not as clear.}
 	\label{Soot_pattern}
@@
 
-A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.
+Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath.
+The peak height of the consumed and penetrated paper, i.e.
+the burned region, was 0.8~above the burner.
+This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible wall experiments.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0_15m}
+	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0m} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.0~m from the wall.}
+	\label{IWGB_NG_patterns}
+\end{figure}
+
+Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
+When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed with the lowest point approximately 0.1~m above the burner and extending up to the 0.4~m above the burner on the left side.
+The formation of the burned area was captured on film and is shown in Figure~\ref{IWGBGAS6_seq}.
+The burned region on the gypsum wallboard from exposure to the gasoline fire position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
+The width of the burned region was approximately one half of the burner width at it's maximum.
+Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by gas burner when it was tight against the gypsum wallboard.
+Two views are shown.
+The image on the left shows the wall shortly after the fire went out.
+The burned area can be discerned, but a close look is required.
+In the photograph on the right, the same piece of gypsum wallboard was lightly brushed off, which revealed a clearer view of the area where the paint and paper were burned off.
+The peak height of that fire pattern is just short of 0.8~m.
+The maxim width is approximately the full width of the burner.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=18.0in 4.0in 21.0in 14.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas_0_15_pattern}
+	\includegraphics[trim=18.0in 2.6in 18.0in 11.7in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas7_0_8m} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.8~m from the wall.}
+	\label{IWGB_Gas_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=10.3in 9.0in 10.3in 20.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_prebrush}
+	\includegraphics[trim=7.0in 3.5in 8.0in 18.5in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_postbrush} \\
+	\caption[Photographs of the effect of soot removal on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
+For the image on the left, the burner was positioned 0.0~m from the wall.
+For the image on the right, the same panel after the soot was blown off, clean burn area is evident.}
+	\label{IWGB_Gas_0m_patterns}
+\end{figure}
+
+Figures~\ref{IWGB_PUF_patterns} and~\ref{IWGB_PUF_0m_patterns} show the progression of thermal damage caused by the polyurethane fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the instrumented gypsum wallboard.
+The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage, the only damage to the wall is from soot deposition.
+When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but there was no consumption or penetration of the paper finish layer.
+Three replicate experiments were conducted with the polyurethane foam fueled burner tight against the instrumented gypsum wallboard.
+The resulting patterns are shown in Figure~\ref{IWGB_PUF_0m_patterns}.
+The average height of the burned region of the painted paper finish on the wallboard was 0.3~m above the top of the burner.
+The maximum width of the burned region was approximately equal to the width of the burner.
+The pattern generated from the polyurethane burner was different in shape and composition when compared to the patterns generated by the natural gas and gasoline burners.
+The shape of the polyurethane generated pattern was triangular with the base near the top edge of the burner and the peak toward the vertical centerline of the burner.
+The natural gas and gasoline patterns were much taller and typically had a region just above the top edge of the burner that narrowed and then widened as the height of the pattern increased.
+The patterns reached a near steady width, 200 to 300~mm above the burner and then narrowed to a point near the top of the fire pattern.
+Another difference had to do with handling the patterns post test.
+While the the loose soot and burnt paper could be brushed away with a ``light touch'' for the brush, that was not the case for the polyurethane patterns.
+The burnt paper was still attached to the gypsum and the soot seemed to adhere to the gypsum as well.
+As a result, post test brushing the patterns would not be done conducted for the compartment wall experiments.
+Among the concerns was an introduction of other uncertainties with regard to: how hard the brush was applied, what was the bristle stiffness of the brush, and would a new brush be needed each time?
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF5_0_15m}
+	\includegraphics[trim=20.0in 1.0in 20.0in 16.4in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF12_0_8m} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires.
+For the image on the left, the burner was positioned 0.15~m from the wall.
+For the image on the right, the burner was positioned 0.08~m from the wall.}
+	\label{IWGB_PUF_patterns}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF7_0m_crop}
+	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
+	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on three instrumented gypsum wallboards exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
+	\label{IWGB_PUF_0m_patterns}
+\end{figure}
+
+\section{Summary}
+
+A summary of the peak average temperatures and heat fluxes measured at the wall surface is provided in Table~\ref{tab:IWGB_Summary}.
 While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary} a closer look reveals that most of the values are not ``significantly '' different.
@@
 So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
-While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' different.
+While a few of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' significantly different.
 
@@
 
-Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath.
-The peak height of the consumed and penetrated paper, i.e.
-the burned region, was 0.8~above the burner.
-This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible was experiments.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0_15m}
-	\includegraphics[trim=19.0in 5.0in 19.0in 15.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_NG_0m} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the natural gas burner fires.
-For the image on the left, the burner was positioned 0.15~m from the wall.
-For the image on the right, the burner was positioned 0.0~m from the wall.}
-	\label{IWGB_NG_patterns}
-\end{figure}
-
-Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
-When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed with the lowest point approximately 0.1~m above the burner and extending up to the 0.4~m above the burner on the left side.
-The formation of the burned area was captured on film and is shown in Figure~\ref{IWGBGAS6_seq}.
-The burned region on the gypsum wallboard from exposure to the gasoling fire position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
-The width of the burned region was approximately one half of the burner width at it's maximum.
-Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by gas burner when it is tight against the gypsum wallboard.
-Two views are shown.
-The image on the left shows the wall shortly after the fire went out.
-The burned area came be discerned, but a close look is required.
-In the photograph on the right, the same piece of gypsum wallboard was lightly brushed off, which revealed a clearer view of the area where the paint and paper were burned off.
-The peak height of that fire pattern is just short of 0.8~m.
-The maxim width is approximately the full width of the burner.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[trim=18.0in 4.0in 21.0in 14.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas_0_15_pattern}
-	\includegraphics[trim=18.0in 2.6in 18.0in 11.7in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas7_0_8m} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
-For the image on the left, the burner was positioned 0.15~m from the wall.
-For the image on the right, the burner was positioned 0.8~m from the wall.}
-	\label{IWGB_Gas_patterns}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[trim=10.3in 9.0in 10.3in 20.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_prebrush}
-	\includegraphics[trim=7.0in 3.5in 8.0in 18.5in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_Gas5_0m_postbrush} \\
-	\caption[Photographs of the effect of soot removal on the instrumented gypsum wallboard exposed to the gasoline burner fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the gasoline burner fires.
-For the image on the left, the burner was positioned 0.0~m from the wall.
-For the image on the right, the same panel after the soot was blown off, clean burn area is evident.}
-	\label{IWGB_Gas_0m_patterns}
-\end{figure}
-
-Figures~\ref{IWGB_PUF_patterns} and~\ref{IWGB_PUF_0m_patterns} show the progression of thermal damage caused by the polyurethane fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the instrumented gypsum wallboard.
-The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage, the only damage to the wall is from soot deposition.
-When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but the was no consumption or penetration of the paper finish layer.
-Three replicate experiments were conducted with the polyurethane foam fueled burner tight against the instrumented gypsum wallboard.
-The resulting patterns are shown in Figure~\ref{IWGB_PUF_0m_patterns}.
-The average height of the burned region of the painted paper finish on the wallboard was 0.3~m above the top of the burner.
-The maximum width of the burned region was approximately equal to the width of the burner.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF5_0_15m}
-	\includegraphics[trim=20.0in 1.0in 20.0in 16.4in, clip=true, width=0.4\columnwidth]{../Figures/IWGB_PUF12_0_8m} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to the polyurethane foam fires.
-For the image on the left, the burner was positioned 0.15~m from the wall.
-For the image on the right, the burner was positioned 0.08~m from the wall.}
-	\label{IWGB_PUF_patterns}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[trim=0.0in 0.0in 0.0in 0.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF7_0m_crop}
-	\includegraphics[trim=5.0in 1.7in 5.0in 15.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF8_0m_pattern2}
-	\includegraphics[trim=5.0in 3.5in 5.0in 13.0in, clip=true, width=0.3\columnwidth]{../Figures/IWGB_PUF9_0m_pattern} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to replicate polyurethane foam fires]{Photographs of the fire effects on three instrumented gypsum wallboards exposed to replicate polyurethane foam fires with the burner positioned 0.0~m from the wall.}
-	\label{IWGB_PUF_0m_patterns}
-\end{figure}
-
-With this set of experiments, fire patterns as the result of thermal damage have finally generated in a few cases.
-To recap our crude predictions from the previous chapter, the natural gas burner had the potential to cause a fire pattern with a height between 0.6~m and 0.8~m.
+With this set of experiments, fire patterns as the result of thermal damage were finally generated in a few cases.
+To recap our predictions from the previous chapter, the natural gas burner had the potential to cause a fire pattern with a height between 0.6~m and 0.8~m.
 With the natural gas burner against the wall, a pattern with a maximum burn area of 0.8~m in height was generated.
-From Chapter III, the gasoline had a potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
+Also from Chapter 3, according to the heat flux and the ignition data from the literature, the gasoline had a potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
 In the single instrumented gypsum wallboard experiment with the gasoline burner located against the wall, the maximum height of the burned region was just short of 0.8~m.
@@
 The average peak burned region height was 0.3~m.
-The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Ch III provided a ``ballpark'' estimate of the maximum height of the burned region.
+The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the predictions from Ch 3 provided reasonable ``ballpark'' estimates of the maximum height of the burned region.
 
@@
 
-The purpose of this chapter is to develop and compare data from bench scale apparatus that could be used to analyze fire damage to gypsum wallboard.
-This type of testing might be practical for a fire investigator to use based on the low cost, relative to a full-scale fire test, and the small size of the samples needed for the tests.
-In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
-While the data generated from those full scale laboratory experiments provide valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests in an effort to validate or improve the existing data in the literature.
+The purpose of this chapter was to develop and compare data from bench scale apparatus that could be used to analyze fire damage to gypsum wallboard.
+This type of testing might be practical for a fire investigator to use based on the low cost, relative to a full-scale fire test, and the relatively small size of the samples needed for the tests.
+In the previous chapters of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
+While the data generated from those full scale laboratory experiments provided valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests in an effort to validate or add to the existing data in the literature.
+The bench scale apparatus used in this study include: the cone calorimeter, the radiant flooring panel, and a vertical radiant panel.
+A lateral ignition and flamespread test (LIFT) apparatus may have also provided useful results for this study, but an operational LIFT apparatus was not available at NIST over the course of this study.
 
@@
 
-The cone calorimeter is one of the most commonly used bench-scale rate of heat release apparatus that uses the oxygen consumption calorimetry method.
-It was developed at NIST in the 1980s~\cite{babrauskas:1984}.
-The cone calorimeter has been adopted as ASTM~E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}.
-The cone calorimeter consists of a conical shaped heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
+The cone calorimeter is one of the most versitile and commonly used bench-scale apparatus that uses the oxygen consumption calorimetry method to measure heat release rate.
+It was developed by Babrauskas at NIST in the 1980s~\cite{babrauskas:1984}.
+The cone calorimeter has been adopted by the ASTM as the Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter, ASTM~E1354~\cite{ASTM_E1354}.
+The cone calorimeter consists of a conically shaped heater, shutter, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
+In addition, the instrumentation required to measure mass flow, gas concentrations, and optical density are connected to the exhaust duct work.
 Typically, the sample is located in the open with free access of air to the combustion zone.
@@
 	\includegraphics[width=\textwidth]{../Figures/Cone_Cal} \\
-	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter}
+	\caption[Schematic of the cone calorimeter]{Schematic of the cone calorimeter adapted from~\cite{Babrauskas:1992}}
 	\label{Cone_Cal}
@@
 
-For the ignition tests, an electric spark igniter is positioned over the center of the horizontal samples to serve as a pilot.
+For the ignition tests, an electric spark igniter was positioned over the center of the horizontal samples to serve as a pilot for the pyrolysis gases.
 Combustion products and dilution air were extracted through the hood and exhaust duct by a high temperature fan.
-The flow rate can be adjusted between 0.01 and 0.03~m$^3$/s.
+The flow rate may be adjusted between 0.01 and 0.03~m$^3$/s.
 The volumetric flow rate was kept constant during testing.
@@
 The gas flow rate in the exhaust duct was calculated from the pressure drop across and temperature at an orifice plate in the duct.
-Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, were measured using appropriate instruments.
+The concentrations of oxygen, carbon dioxide, carbon monoxide, were measured using appropriate instruments.
 Heat release rate was calculated from the gas concentration and mass flow measurements.
@@
 	\includegraphics[width=\textwidth]{../Figures/FLR_Radpan} \\
-	\caption[Schematic of the radiant flooring panel apparatus]{Schematic of the radiant flooring panel apparatus}
+	\caption[Schematic of the radiant flooring panel apparatus]{Schematic of the radiant flooring panel apparatus adapted from~\cite{Benjamin:1975}}
 	\label{FLR_Radpan}
@@
 
-Prior to conducting experiments with the gypsum wallboard samples, heat flux gauge measurements taken at the center position of the sample were used to determine the positions on the trolley track for a specific radiant exposure.
+Prior to conducting experiments with the gypsum wallboard samples, total heat flux gauge measurements taken at the center position of the sample were used to determine the positions on the trolley track for a specific radiant exposure.
 The positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
-The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
-In other words, the area around the center point of the sample had heat flux measures similar, in other words within the uncertainty of the heat flux sensor, to the center point measurement.
+The heat flux gauge was used to map the heat flux across the area where the sample to determine the extent of a near uniform radiant flux.
+The area that was exposed to near uniform flux condition surrounding the center of the painted gypsum wallboard sample extended at least 70~mm on either side of the center point and 100~mm above and below the center point.
+In other words, the area around the center point of the sample had heat flux measures similar, in other words, within the 8~\% uncertainty of the heat flux sensor, to the center point measurement.
 Outside of the central area of the samples, the heat flux would decrease as the position approached the edge of the sample.
@@
 To conduct the experiments, the radiant panel was ignited and allowed to pre-heat for at least 60 minutes.
-The water cooled, Schmidt-Boelter total heat flux gauge was mounted in the center the sample holder, and the heat flux positions were confirmed.
+The water cooled, Schmidt-Boelter total heat flux gauge was mounted in the center of the sample holder, and the heat flux positions were confirmed.
 The heat flux gauge was then removed from the sample holder trolley.
@@
 Each sample was exposed for 600 seconds.
-Each sample had a single bare-bead, Chromel-Alumel (type K) thermocouple, with a 0.5~mm nominal diameter bead in contact with the center point of each sample.
-During the experiments the samples were monitored for temperature and ignition.
+A single bare bead, Chromel-Alumel (Type K) thermocouple, with a 0.5~mm diameter bead was installed in contact with the center point of each sample.
+In these experiments, the thermocouple wire was attached to the exposed surface of the painted gypsum wallboard and the thermocouple bead was held in contact with the face of the sample by compression casued by the bending the wire.
+
+During the experiments the samples were monitored for discoloration, charring, and ignition.
 After the exposure time was completed the heat shield was once again placed between the sample and the radiant panel.
@@
 The results of these experiments are shown in Table~\ref{tab:Gypsum_wallboard_timetoign}.
-The time to ignition values in the table are the average of the three times.
+The time to ignition values in the table are the average of the three ignition times.
 Note that no ignition occurred at 25~kW/m$^2$.
@@
 The samples were exposed to 25~kW/m$^2$ for 1800~s each and no ignition occurred.
+During the 25~kW/m$^2$ exposures, the painted paper on the gypsum wallboard sample could be seen off gassing as the surface discolored and charred.
+Although the painted paper was heated up and pyrolyzing, the gypsum substrate was potentially absorbing heat and, or offgasing water vapor which delayed ignition, until the fuel in the painted paper was degraded to the point that it could not ignite.
 In the experiments with heat fluxes of 35~kW/m$^2$ or higher, ignition did occur and the painted paper surface of the gypsum board was consumed, leaving the gypsum board exposed.
@@
 
-Additional cone calorimeter experiments were conducted in the University of Canterbury Fire Laboratory.
-In these experiments the purpose was to obtain an estimate of the temperature of the painted paper surface at the time of ignition.
+In order to gain some insight into the surface temperature at ignition and have a time to ignition between 25 and 35 ~kW/m$^2$ additional cone calorimeter experiments were conducted in the University of Canterbury Fire Laboratory.
+In these experiments the main purpose was to obtain an estimate of the temperature of the painted paper surface at the time of ignition.
 Samples of painted gypsum wallboard were shipped from the NIST Fire Research Laboratory in Gaithersburg, MD., USA.
 In these experiments an additional incident heat flux level of 30~kW/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
-The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
-The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident heat flux values of 35 and 50~kW/m$^2$, respectively.
+The averaged time to ignition and temperature pairs from three replicate experiments at three heat flux levels are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
+The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident benchmark heat flux values of 35 and 50~kW/m$^2$, respectively.
 The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.
-Given the uncertainty if the temperature measurement these temperatures are not significantly different.
+Given the uncertainty of the temperature measurement these temperatures are not significantly different.
 Taking the average ignition temperature across all of these cone experiments yields a value of 360~$^{\circ}$C $\pm~54$~$^{\circ}$C.
+This temperature is at least 200~$^{\circ}$C less than the ignition temperature values from the literature of 565~$^{\circ}$C and 515~$^{\circ}$C from~\cite{Quintiere:1985,Dillon:1998}.
+No solid reason for the signifcant difference in between the ignition temperatures from the cone experiments and the data in the literature.
+In this study the surface mounted thermocouples were installed, as in the instrumented gypsum wallboard experiments so that they would maintain contact with the sample.
+Perhaps this caused an improvement in the measurement or perhaps the thermocouple lost more heat to the substrate gypsum than the paper due to its conductive nature.
+More reseach is needed into the best practice of measuring surface temperatures without influencing the results.
 
@@
 In the radiant flooring panel experiments the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kW/m$^2$ to 2~kW/m$^2$ over the length of the sample.
-In addition to the heat flux from the radiant panel, there is a small flame front approximately 10 to 30~mm in height that serves as the pilot along the length of the sample and provides additional energy to the fuel immediately ahead of the flame.
+In addition to the heat flux from the radiant panel, a propane fueled line burner is positioned in contact with the sample within approximately 20~mm of the end of the sample.
+Once the sample was ignited a flame front would move away from the burner, consuming the painted paper on the gypsum wallboard as it spread.
+This flame front was approximately 10 to 30~mm in height and served as the pilot along the length of the sample and provided some additional energy to the fuel immediately ahead of the flame.
 The impact is limited to a small distance ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
@@
 
- With the flooring radiant panel test, the incident heat flux from the panel and the pre-heated gypsum wallboard sample enables flame spread for approximately 500~s.
+ With the flooring radiant panel test, the incident heat flux from the panel and the heating of the gypsum wallboard sample enabled flame spread for approximately 500~seconds.
 The temperatures prior to ignition ranged from an average of 315 $^{\circ}$C for the 100~mm position to 242 $^{\circ}$C for the 400~mm position.
@@
 The cone calorimeter experiments generated heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
-The average total heat released during each burn was 2.8 MJ/m$^2$.
+The average total heat released during each burn was 2.8 kJ/m$^2$.
 
@@
 
+Radiative Fraction
+
+As noted in the study, there has been a significant amount of research conducted on the radiant energy emitted from flames and how to estimate it~\cite{McGrattan:2000,Hostikka:3,Beyler:1999,Modak:1991,Hamins:1991,Babrauskas:1981,Back, McCaffrey:1982}.
+Fire investigators and fire analysts would benefit from additional research on the radiative fraction from fuels that are more representative of what a fire invetsigator might find as a first or second item ignited.
+For example how different is the radiative fraction of methane vs natural gas, heptane vs gasoline, or pmma vs an upholstered chair?
+The "pure" materials are typically found in the literature but the fuel more likely to be found on a fire scene are not.
+Further the values that are in the literature for materials such as gasoline tend to provide single values to define what could be significant difference found between different grades and blends of gasoline.
+Additional values would improve the use of the models to assess the radiant heat transfer from a flame to a target to determine if thermal damage or ignition due to the fire would occur.
+
 Calcination depth
@@
 While the results from this project will provide some insight into the repeatability of pre-flashover fire patterns, a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions, are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
+
+More reseach is needed into the best practice of measuring surface temperatures without influencing the results.
 

### 2016-10-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Completed Ch 5 and working Ch 6 edits

@@
 
-In the initial heat release rate experiments another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~ above the top of the burners.
+In the initial heat release rate experiments another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~m above the top of the burners.
 At this location the average peak total heat flux measured for the natural gas fires were approximately 0.42~kW/m$^2$.
 The average peak values for the gasoline and polyurethane foam were approximately 0.74~kW/m$^2$ and 0.35~kW/m$^2$ respectively.
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_NG}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_GAS}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF}\\
+  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
+  \label{Flux}
+\end{figure}
 
@@
 
-Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range of physical damage to samples as shown in Figure~\ref{RPGB_SET}.
-However based on visual observations there were no flaming ignitions.
-For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
-This process became more prevalent as the heat fluxes increased.
-The radiant exposure of 25~kW/m$^2$ caused the samples to collapse as they were being removed from the holder.
-Hence there were no photos of those samples.
-Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
-Notice that the samples exposed to 17.5~kW/m$^2$ and higher have a temperature increase to a peak temperature followed by a decrease.
-This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
-The temperatures at which the change in rate of temperature rise occur are between 300 and 400~ $^{\circ}$C.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/RPGB_SET} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-Each row of samples represents three replicate experiments at a given heat flux.
-Beginning with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
-	\label{RPGB_SET}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
-	\caption[Time vs.
-temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel]{Time vs.
-temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.}
-	\label{RP_GB_Front}
-\end{figure}
-
 \subsection{Heat Release Rate per Unit Area}
 
-The cone calorimeter experiments generated heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
-The average total heat released during each burn was 2.8 kJ/m$^2$.
+The cone calorimeter experiments generated peak heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
+The average total heat released during each burn was 2.8 MJ/m$^2$.
+The total heat released during the cone calorimeter experiments compares favorably with the study by McGraw and Mowrer~\cite{McGraw:1999}, where the total heat released for the gypsum wallboard with 2 coats of latex paint was 2.3 to 2.7~MJ/m$^2$.
 
@@
 	\end{tabular}
-	\caption[Painted gypsum wallboard time heat release rate per unit area results]{Painted gypsum wallboard heat release rate per unit area results from the cone calorimeter.
+	\caption[Painted gypsum wallboard peak heat release rate per unit area results]{Painted gypsum wallboard peak heat release rate per unit area results from the cone calorimeter.
 Each value is based on an average of three tests.}
@@
 Comparing this burn length range, 414~mm to 450~mm, to the incident heat flux curve provided a critical heat flux of approximately 8.9~kW/m$^2$ with a 95$\%$ confidence limit of $\pm$~0.6~kW/m$^2$.
-Photographs showing a radiant flooring panel test underway and sample nearing the flameout position are provided in Figure~\ref{FRP_Test_Photos}.
+Photographs showing a radiant flooring panel test underway and a close up of a sample near the location where the flame self extinguished are provided in Figure~\ref{FRP_Test_Photos}.
 
@@
 
+Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range of physical damage to samples as shown in Figure~\ref{RPGB_SET}.
+However based on visual observations there were no flaming ignitions.
+For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
+This process became more prevalent as the heat fluxes increased.
+The radiant exposure of 25~kW/m$^2$ caused all of the painted paper to be burned off of the sample and the exposure dehydrated the gypsum to the point where the samples collapsed as they were being removed from the apparatus.
+Therefore no 25~kW/m$^2$ samples are shown in Figure~\ref{RPGB_SET}.
+Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
+Notice that the samples exposed to 17.5~kW/m$^2$ and higher have noticable temperature increase to a peak temperature followed by a decrease.
+This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
+The temperatures at which the change in rate of temperature rise occurred are between 300 and 400~$^{\circ}$C.
+The temperature curve respresenting the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300~$^{\circ}$C after more than 400~seconds of exposure.
+Multiplying the time that each temperature peaked by the exposure heat flux yields the lowest total of heat was expended to create the most thermal damage, in the shortest time was at the 25~kW/m$^2$ exposure.
+While at the 15~kW/m$^2$ exposure used more than twice the total amount of heat over a longer duration and yielded a lesser amount of damage.
+The flux levels bounded by 15~kW/m$^2$ and 25~kW/m$^2$,have total energy exposures whihch are also bounded by the two extremes.
+This data indicates that depending on the exposure the amount of energy required to raise the temperature of the target material toward an ignition temperature, under these conditions, differs by a significant amount.
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/RPGB_SET} \\
+	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
+Each row of samples represents three replicate experiments at a given heat flux.
+Beginning with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
+	\label{RPGB_SET}
+\end{figure}
+
+\begin{figure}[p]
+	\centering
+	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
+	\caption[Time vs.
+temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel]{Time vs.
+temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.}
+	\label{RP_GB_Front}
+\end{figure}
+
 While the vertical radiant panel did not provide ignition data or heat release rate values it did provide information on the fire effect development on the painted gypsum wallboard samples with respect to heat flux.
-Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining the Figure~\ref{RPGB_SET} we see surface thermal effects of discoloration on the painted paper surface of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
+Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining the Figure~\ref{RPGB_SET} we see surface thermal effects of discoloration on the painted paper cover of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
 The samples exposed to 15~kW/m$^2$ exhibit charring and given the thin nature of the painted paper surface penetration was evidenced on two of the three sample.
-The sample of the right also shows signs of the painted paper being consumed.
+The 15~kW/m$^2$ sample on the right also shows signs of the painted paper being consumed.
 The samples exposed to 17.5~kW/m$^2$ and above all show signs of significant levels of painted paper consumption.
@@
 Hence the damaged area increased outward toward the edges.
-It would appear in this test series, that 15~kW/m$^2$ is right on the threshold of painted paper penetration and consumption.
-
-DeHaan~\cite{DeHaan:2012} categorizes the fire effects that form patterns as follows:
-\begin{enumerate}
-	\item Surface deposits -– no irreversible effect on surface
-	\item Surface thermal effects –- physical change such a discoloration or melting
-	\item Charring -– evidence of surface burning
-	\item Penetration -– charring below the surface
-	\item Consumption –- loss of surface material, charring throughout
-\end{enumerate}
-
-Each apparatus provided similar but different thermal exposure conditions and each test method has a specific parameter or parameters that they were designed to measure for.
+It would appear in this test series, that 15~kW/m$^2$ heat flux exposure is on the threshold of painted paper penetration and consumption stage.
+
+\section{Summary}
+
+Each apparatus provided a thermal exposure to painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
+Each test method has a specific parameter or parameters that they were designed to measure for.
+As a result, the data presented in this chapter provides a wide range of values that can not be taken as a single number an applied.
+In other words the data must be taken in context with how it was generated and analyzed accordingly.
+This is a challenge for fire investigators, analysts, and engineers alike.
+
+The nature of the bench scale experimental data does not allow one to simply pick a value from a table an directly applying it as an input to a fire model.
 Currently there is no specific protocol for a fire model user to follow to develop input data.
-Nor is there a ``standard'' catalog of fire model inputs for a given material.
-As a result the literature is sourced for information and users may need VII and VIII or to evaluate the validity of the calculations in those chapters.
+For example, there is no guidance on how to conduct a series of experiments to generate all of the data needed for the models.
+Using the gypsum wall board as an example, material propeties such as density, specific heat, and thermal conductivity change over time as a result of the thermal exposure~\cite{Schroeder:1999,McGraw:1999}.
+Of course this behavior is not unique to gypsum wallboard.
+The ideal case for the fire investigation user community would be a ``standard'' catalog of fire model inputs for a given material under a wide range of conditions.
+
+There are other test methods that were not utilized here.
+The lateral ignition and flame spread apparatus can be used to generate time to ignition and ignition temperature data in addition to critical heat flux for flame spread data.
+The LIFT also considers time into the data where as the radiant flooring panel does not.
+Further the LIFT and the cone calorimeter apparatus can be conducted in both horizontal and vertical orientation to better represent the end use of the sample material.
+Thermogravimetric analysis (TGA) is another type of test which can be used to measure the mass loss rate of a material as a function of time and temperature.
+Differential scanning calorimetry (DSC) is a test method which can be used to measure the specific heat capacity and in way phase change.
+The TGA and DSC use samples that are on the order of a few grams.
+This can make testing with a composite material as well as interpreting the results of a composite material difficult.
+
+This chapter was anticipated to provide data that that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures, 10 to 75~kW/m$^2$.
+The ignition temperatures measured in the cone calorimeter experiments conducted as part of this side do not align with the data in the published literature but the reason for the 200~$^{\circ}$C could not be resolved other than issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
 
@@
 In the instrumented gypsum wallboard experiments, as the burners were moved away from the position against the wall, the fire effects on the wall diminished significantly.
-Therefore most of the fire pattern compartment experiments were conducted with the burners against the wall or corner of the compartment or less than one burner length from the wall.
+Therefore the fire pattern compartment experiments were conducted with the burners against the wall or in the corner of the compartment.
 
@@
 The fire damaged wallboard was subsequently removed, photographed again, and replaced with new sections of painted gypsum wallboard.
-Several types of fire pattern experiments were conducted in the compartments; to examine the impact of the wall construction on the resulting fire pattern; and to compare the fire patterns based on the burner centered on,or the rear wall, or in, or near a corner on the rear wall of the compartment.
+Several types of fire pattern experiments were conducted in the compartments; to examine the impact of the wall construction on the resulting fire pattern; and to compare the fire patterns based on the burner centered on the rear wall, or in a corner on the rear wall of the compartment.
 
@@
 These experiments determined how the walls for the remaining compartment fire pattern experiments were constructed.
-Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum board on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3) Insulated, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
-The insulation was 90~mm thick fiber glass batting,a kraft paper facing, and an ``R value'' of 13.
+Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum wallboard on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3) Insulated, 12.7~mm thick, regular core, painted gypsum wallboard on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
+The insulation was 90~mm thick fiber glass batting, with a kraft paper facing, and an ``R value'' of 13.
 From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
@@
 The walls were exposed to both the natural gas and the gasoline burners.
-For these experiments the burner was in contact with the gypsum wallboard.
+For all of these experiments the burner was in contact with the gypsum wallboard.
 A total of 60 experiments were conducted.
@@
 Therefore the areas of the grid cells within the fire pattern were added up to determine the area of the fire patterns.
-The analysis was carried out with a resolution of a quarter grid cell or approximately 0.003~m$^2$.
+The analysis was carried out with a resolution of a quarter grid cell or approximately 0.001~m$^2$.
 
@@
 The previous studies measured temperatures, heat flux, and mass flow rates for the purpose of developing correlations to predict flame height.
-The sole purpose of these experiments is to examine the fire patterns that result from well characterized fires on painted gypsum wall board.
+The sole purpose of these experiments was to examine the fire patterns that result from well characterized fires on painted gypsum wall board.
 
@@
 The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
-The natural gas had a 300~s burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
+The natural gas had a 300~s burn time which was approximately the upper bound for complete extinguishment (total burn time) for the 500~mL of gasoline and the polyurethane urethane block.
+Typically the gasiline and polyurethane burners were in decay approximately 120~seconds after ignition.
 By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
 Figure~\ref{GBNG34Sequence} displays a sequence of photographs taken during a natural gas burner corner experiment.
-The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.
+The photographs taken at a rate of five images per second show the significant movement of the regions of visible combustion.
 The grid drawn on the corner extends to 1.5 m above the top of the burner.

### 2016-10-02 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Syncing versions with added Fig 2.7

--- 2016-10-01 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
@@
 The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$ respectively.
-The values are only presented for the experiments which had two heat flux gauges installed as described in the instrumentation section above.
+The values in Fig.~\ref{Flux} are only presented for the experiments which had two heat flux gauges installed at 0.95~m from the centerline of the burners and 0.5~m above the top edge of the burners.
+
+In the initial set of heat release rate experiments another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~m above the top of the burners.
+At this location the average peak total heat flux measured for the natural gas fires was approximately 0.42~kW/m$^2$.
+The average peak values for the gasoline and polyurethane foam were approximately 0.74~kW/m$^2$ and 0.30~kW/m$^2$ respectively.
+Graphs of the heat flux time histories from the 2~m position are given in Figure~\ref{Flux_2m}
 
@@
   \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF}\\
-  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires]{Total heat flux versus time for natural gas, gasoline, and foam fires.}
+  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires at 0.95~m]{Total heat flux versus time for natural gas, gasoline, and foam fires at a position 0.95~m from the vertical centerline of the burner.}
   \label{Flux}
+\end{figure}
+
+\begin{figure}[p]
+  \centering
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_NG_2m}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_Gas_2m}\\
+  \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF_2m}\\
+  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires at 2~m]{Total heat flux versus time for natural gas, gasoline, and foam fires at a position 2~m from the vertical centerline of the burner.}
+  \label{Flux_2m}
 \end{figure}
@@
 
-Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range of physical damage to samples as shown in Figure~\ref{RPGB_SET}.
-However based on visual observations there were no flaming ignitions.
-For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
-This process became more prevalent as the heat fluxes increased.
-The radiant exposure of 25~kW/m$^2$ caused the samples to collapse as they were being removed from the holder.
-Hence there were no photos of those samples.
-Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
-Notice that the samples exposed to 17.5~kW/m$^2$ and higher have a temperature increase to a peak temperature followed by a decrease.
-This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
-The temperatures at which the change in rate of temperature rise occur are between 300 and 400~ $^{\circ}$C.
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/RPGB_SET} \\
-	\caption[Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-]{Photographs of the fire effects on the instrumented gypsum wallboard exposed to radiant heat from a natural gas fired panel.
-Each row of samples represents three replicate experiments at a given heat flux.
-Beginning with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
-	\label{RPGB_SET}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=\textwidth]{../Figures/RP_GB_Front} \\
-	\caption[Time vs.
-temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel]{Time vs.
-temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.}
-	\label{RP_GB_Front}
-\end{figure}
-
 \subsection{Heat Release Rate per Unit Area}
 
-The cone calorimeter experiments generated heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
+The cone calorimeter experiments generated peak heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
 The average total heat released during each burn was 2.8 MJ/m$^2$.
+The total heat released during the cone calorimeter experiments compares favorably with the study by McGraw and Mowrer~\cite{McGraw:1999}, where the total heat released for the gypsum wallboard with 2 coats of latex paint was 2.3 to 2.7~MJ/m$^2$.
 

### 2016-10-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added imaes to ch 6 and tables and text to Ch 7
cut out mccaffrey eqn to save

@@
 Six of the ten patterns have a bump out or an unsymmetrical curve within 200~mm of the top of the burner.
-The cause of these bumps in the patterns could not be determined.
+The exact cause of these bumps in the patterns could not be determined, but they were generated later in the burn after the most of the fire pattern was created.
 Three of the patterns have a noticeable lean.
@@
 	\centering
+	\footnotesize
 	\begin{tabular}{|c|c|c|c|c|c|}
@@
 		Gasoline (10)       &   Insulated	& 0.82 	$\pm$ 0.09 (11~\%)   &	0.25 $\pm$ 0.08 (32~\%) 	& 0.40 $\pm$ 0.13 (32~\%) 	& 0.13 $\pm$ 0.04 (30~\%)  	\\
+		Polyurethane (10)	&   Open 		& 0.24  $\pm$ 0.12 (50~\%) 	 &  0.28 $\pm$ 0.08 (29~\%) 	& 0.40 $\pm$ 0.24 (60~\%)   & 0.05 $\pm$ 0.03 (57~\%)   \\
 		\hline
@@
 Figure~\ref{GBGas10Sequence} displays a sequence of photographs taken during a gasoline burner corner experiment.
-The photographs taken at a rate of five per second show the significant movement of the regions of visible combustion.
+The photographs taken at a rate of five images per second show the significant movement of the regions of visible combustion, similar to the movement of the flames from the natural gas burner.
 
@@
 
-Table~\ref{tab:Fire_Pattern_Dimensions_Corners}
+The corner experiments demonstrated the expected extension of the combustion zone, especially in the cases of the natural gas and gasoline fires.
+In the extreme case the flames from the gasoline burner briefly impinged on the ceiling, which is approximately 2.4~m above the top of the burner.
+The shape of the fire pattern to the wall was also different then the patterns generated on the flat wall.
+Much samller areas of the wall had the painted paper charred, penetrated, and burned.
+For each of the fuels there was significantly more area where it was difficult to separate the charred areas from the surface deposits and discoloration.
+The sectons below include post test images of the fire patterns.
+The dimensions of the corner fire patterns are given in Table~\ref{tab:Fire_Pattern_Dimensions_Corners}.
 
@@
 Figure~\ref{NG_Corner} shows a comparison of the ten fire patterns generated by the natural gas burner in the corner position with walls of open back construction.
+In the corner burns there is an area in the corner where the paper is not burned off.
+From the flame sequence shown in Figure~\ref{GBNG34Sequence} it can be seen that the flame in the persitent flame region is close to the walls of the corner, but moving up into the intermittent region, the flame burns away from the walls, hence less energy is transferred to the walls and perhaps a bit more soot condenses out on the cooler walls.
 
@@
 Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fueled burner in the corner position with walls of open back construction.
+Due to a camera malfunction there were no comparable images for the other two experiments.
+The patterns are darker than the patterns generated on the flat walls.
+Given that the air to the combustion zone was constrained it follows that the combustion may have been less efficient than the flat wall experiments whihch resulted in the sootier patterns.
+The combustion zone for the gasoline fires positioned in the corner stretched from the top of the burner up to the ceiling of the compartment.
+Figure~\ref{GBGas10Sequence} shows the flame extension and similar to the natural gas burner fires shows how the flame in the intermittant zone appeared to move away from the corner.
 
@@
 Figure~\ref{PUF_Corner} shows a comparison of three fire patterns generated by the polyurethane foam fueled burner in the corner position with walls of open back construction.
-Only three replicates could be conducted due to the limits on the foam supply that was sourced from the same purchase.
+Only three replicates were conducted due to the limits on the foam supply that was sourced from the same purchase.
+The flame length from the polyurethane foam fueled burner was also longer compared to the flat wall experiments.
+However the change was not as big compared to the higher heat release rate natural gas and gasoline fueled burners.
+The resulting patterns, similar to the other corner burner patterns, were darker in color with less definition in the lines of demarcation.
 
@@
 
+\section{Summary}
+
+After the experiments the gypsum wallboard panels were removed from the compartment for documentation and measurement of the fire patterns.
+A comparsion on a fire pattern from each type of burner is shown in Figure~\ref{PT_Corners}.
+Another image of the gasoline generated corner fire pattern, Figure~\ref{C_PTGASClose}, is included to show the reader how viewing a fire pattern at different angles enabled a better sense of the area of the fire damage.
+
+\begin{figure}[p]
+	\includegraphics[width=1.7in]{../Figures/C_PTGBNG_42}
+	\includegraphics[width=1.7in]{../Figures/C_PTGBGAS_51_10c}
+	\includegraphics[width=1.7in]{../Figures/C_PTGBPUF_11} \\
+
+	\caption[Photographs of the fire patterns from three different burner experiments positioned in a corner]{Photographs of the fire patterns from three different burner experiments positioned in a corner with walls of open construction.
+The patterns were generated by the following fuels, from are from left to right, natural gas, gasoline, polyurethane foam.}
+	\label{PT_Corners}
+\end{figure}
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/C_PTGASClose} \\
+
+	\caption[Photographs of a gasoline generated corner fire pattern taken at an angle]{Photographs of a gasoline generated corner fire pattern taken at an angle in order to improve the visibility of the lines of demarcation.}
+	\label{C_PTGASClose}
+\end{figure}
+
+In general, the experiments, where the the burners were positioned against the center of a flat wall, provided very repeatable results with the natural gas and gasoline fueled burners.
+Under these pre-flashover, short burn duration fire conditions it was clear that the wall construction did not have any impact on the resulting fire pattern.
+Also comparing these patterns to those generated with the instrumented gypsum wallboard, it did not appear that the instrumentation had any impact that changed the fire pattern.
+With an expanded uncertainty of 2~$\sigma$, the height of the fire patterns were within $\pm$ 18~\% for both the natural gas and the gasoline fuel burner fires.
+The uncertainties regarding the width and area of the patterns were higher up to $\pm$ 33~\%.
+While the natural gas and the gasoline are diffent fuels there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
+The larger uncertainty in the areas of the pattern may be due to the slight movement of the flames back and forth across the wall.
+
+The comparison for the fire pattern heights and flame heights from the natural gas fueled fires are very similar.
+This is expected in part because the natural gas fires are “steady state”.
+The “steady” nature of the fire aids in the repeatability or the reduction of variability in the experiments.
+
+The gasoline fueled fires also had similar fire pattern heights and flame heights; however, the similarity was not as strong as the natural gas fires.
+The transient nature of the fire was believed to have had an impact since there was less energy transferred to the gypsum wall board and the exposure time for portions of the wall board more distant from the fuel surface was less.
+
+The polyurethane foam exhibited a higher variability in the fire pattern heights, $\pm$ 50~\%, and areas, $\pm$ 57~\%, due in part to variabilities in fire growth rates, a lower peak heat release rate, and a lower total heat release, than the other two fuels.
+Since the fire patterns generated by the polyurethane fueled burners were shorter and smaller, than the patterns generated by the 80 kW heat release rate fuels, the uncertainty in terms of percentage difference is magnified.
+The positive message is that the repeatability of the patterns qualitatively agree with the repeatability, or lack there of, of the heat release rate of the polyurethane foam burner which was $\pm$ 47~\% during the burner characterization experiments.
+
 \chapter{Comparison of Algebraic Fire Characterizations with Fire Pattern Results}
@@
 Over the years, fire researchers have provided many methods for predicting flame characteristics such as: median flame height, plume temperatures and an estimation of the heat flux emitted.
-These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,FDS_Users_Guide,FDS_Tech_Guide}.
-
-In this chapter the application of empirical algebraic flame characterizations will be compared against the results from the experiments documented in Chapter 2 and 4.
+These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,Heskestad:SFPE,FDS_Users_Guide,FDS_Tech_Guide}.
+
+In this chapter the application of empirical algebraic flame characterizations will be compared against the results from the experiments documented in previous chapters.
 Two different types of applications will be used.
@@
 In the second case, the height of the thermal damage on the gypsum board will be examined.
-Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999}.
-
-Values generated in the bench scale experiments will be utilized as input to predict or simulate real scale results using the algorithms.
+Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks as well as other application oriented documents~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999,NUREG_1805}.
+Values generated in the fire characterizations, instrumented bench scale experiments, and values from the literature will be utilized as input to predict or simulate real scale results using the algorithms.
 Then the predicted results will be compared with the full-scale experimental results.
+keep in mind that with these algorithms time is not a factor.
+Methods of this type are commonly referred to as ``back of the envelope'' estimates.
+they are intended to provide insight as opposed to a hard and fast numerical answer.
+As the experiments have shown so far there are many uncertainities which impact the results.
 
@@
 Radiation is assumed to be the only means of heat transfer.
+However this method is noted to work the best when the distance of the target is at least two to four times the distance of the flame height way from the fire.
 
@@
 	\centering
-	\includegraphics[width=\textwidth]{../Figures/PointSourceHF}
+	\includegraphics[width=4.5in]{../Figures/PointSourceHF}
 	\caption{Schematic of heat flux estimation using the point source assumption}
@@
 where: \=  \\
-
+{}
 \> $\dot{q}''$ is the heat flux per unit area kW/m$^2$\\
@@
 
-Source fire plume temp and shape factor from vertical cylinder
-\begin{equation}\label{eq:source_fire}
-\dot{q}'' = \epsilon \sigma F_{12} T^4  \\
-\end{equation}
-
-\begin{tabbing}
-where: \=  \\
-\> $\epsilon$ is the emissivity  \\
-\> $\sigma$ is the Stefan-Boltzmann Constant (5.67 $\times 10^{−8}$~W/m$^2$~K$^4$)  \\
-\> $F_{12}$ is the radiative shape factor \\
-\end{tabbing}
+The question is can we use this simple model to estimate the burner positions where the heat flux would be high enough to generate thermal damage on the painted gypsum board wall?
+From the source fire characterizations, the average peak heat release rates from the three burners can be input into the equation along with the distance, R, and the $\chi_r$, or the radiant fraction.
+R is measured from the vertical centerline of the burners so in addition to the distance between the edge of the burner and the wall, half of the burner width, 0.15~m must be added.
+A typical default value used for the radiant fraction is 0.35.
+Table~\ref{tab:Point_Source_HFNGG} lists the input value of the average peak heat release rate of 80~kW for both the natural gas and gasoline burner fires along with a $\chi_r$ of 0.35, and the five burner positions that were used.
+
+The predictions provide good agreement with the natural gas results at distances greater than 1 burner width away, then the predictions trend higher.
+In the instrumented gypsum wallboard experiments the natural gas burner at $R=0.31~m$ generated a discoloration on the surface of the painted gypsum wallboard.
+At $R=0.15~m$, burner touching the wall, enough energy was transferred to the wall fast enough that caused charring, penetration, and consumption of the painted paper surface.
+Based on the data from the cone calorimeter experiments conducted as part of this study, charring, penetration, and consumption would occur somewhere between 25 and 30~kW/m$^2$.
+Dillon provided a value of 26kW/m$^2$ as the minimum heat flux where ignition of the gypsum wallboard would occur~\cite{Dillon:1998}.
+So at $R=0.31~m$ conditions are on the edge both with the prediction and the measurement of ignition but not high enough to cause the paper to char or worse, there was only enough energy to cause discoloration.
+Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
+Indicating that the a fire pattern has been burned into the wall and that was infact true.
+
+The predictions provided in Table~\ref{tab:Point_Source_HFNGG} are significantly lower than the measured peak heat flux values from the gasoline fueled burner experiments at every burner position.
+That said, the predictions indicate that at $R=0.31~m$  the heat flux is just before the ignition threshold provided in the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
+The single gasoline experiment at $R=0.31~m$ showed a peak heat flux of 57~kW/m$^2$.
+The exposure was brief at this peak due to the flame movement toward the wall.
+This makes the experimental values at the three closest location to the wall difficult to compare as the point source model, and most models for that matter, can not account for the flame being drawn toward the wall.
+An important observation is that the fire damage on the wall was limited to an uneven horseshoe shaped pattern within 100~mm above the top of the burner edge.
+This ignition was captured in Ch 4, Figure~\ref{IWGBGAS6_seq}.
+At the two closer positions the char, penetration, and consumption was evident and at these locations both the predictions and the measured heat fluxes are well above the threshold ignition heat flux.
+
+\begin{table}
+	\centering
+	\footnotesize
+	\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+		HRR (kW) &   $\chi_r$   & R (m)	 & Heat Flux (kW/m$^2$)     &  Nat. Gas (kW/m$^2$)      & Gasoline (kW/m$^2$) 	\\ \hline \hline
+		80    &   .35 		& 0.76 	     & 3.8 $\pm$ 0.30 (8~\%) 	&  4 $\pm$ 0.32 (8~\%) 	 	   & 6 $\pm$ 0.5 (8~\%)     \\
+		80    &   .35    	& 0.46	     & 10.6 $\pm$ 0.80 (8~\%) 	&  11 $\pm$ 0.88 (8~\%)  	   & 18 $\pm$ 1.4 (8~\%)    \\
+		80    &   .35 		& 0.31	     & 24.0 $\pm$ 1.9 (8~\%) 	&  23 $\pm$ 1.8 (8~\%)  	   & 57 $\pm$ 4.6 (8~\%)     \\
+        80    &   .35 		& 0.23	     & 43.0 $\pm$ 3.4 (8~\%) 	&  NA 					  	   & 60 $\pm$ 4.8 (8~\%)     \\
+        80    &   .35 		& 0.15	     & 95.0 $\pm$ 7.6 (8~\%) 	&  55 $\pm$ 4.4 (8~\%)  	   & 61 $\pm$ 4.9 (8~\%)     \\
+	\hline
+	\end{tabular}
+	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum boardwall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum boardwall experiments.
+Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
+	\label{tab:Point_Source_HFNGG}
+\end{table}
+
+Table~\ref{tab:Point_Source_HFPUF} displays a similar development based on the average peak heat release rate,45~kW, for the polyurethane foan burner.
+Similar to the results from the gasoline comparison, the predictive heat flux values at all of the burner positions are low relative to the experimental data.
+But again we will examine the results along a more qualitative basis.
+The experimental data provides an average peak value of 25~kW/m$^2$ for $R=0.31~m$.
+For the polyurethane foam burns the peak values were only averaged over a 15 second range due to the brief nature of the peak heat release rate.
+At $R=0.31~m$ there was no charring of the painted paper on the gypsum wallboard, only soot deposition.
+No thermal damage.
+At at $R=0.23~m$ or less, the heat flux is high enough to indicate ignition in the experiments and that was the result.
+Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threhold heat flux.
+
+\begin{table}
+	\centering
+	\footnotesize
+	\begin{tabular}{|c|c|c|c|c|}
+	\hline
+		HRR (kW) &   $\chi_r$   & R (m)	     & Heat Flux (kW/m$^2$)     &  Polyurethane (kW/m$^2$)    	\\ \hline \hline
+		45       &   .35 		& 0.76 	     & 2.1 $\pm$ 0.17 (8~\%) 	&  3.5 $\pm$ 0.28 (8~\%) 	   	 \\
+		45       &   .35    	& 0.46	     & 6.0 $\pm$ 0.48 (8~\%) 	&  12.3 $\pm$ 0.98 (8~\%)  	     \\
+		45       &   .35 		& 0.31	     & 13.5 $\pm$ 1.1 (8~\%) 	&  25 $\pm$ 2.0 (8~\%)   	      \\
+        45       &   .35 		& 0.23	     & 24.1 $\pm$ 1.9 (8~\%) 	&  36 $\pm$ 2.9 (8~\%)		      \\
+        45       &   .35 		& 0.15	     & 53.5 $\pm$ 4.3 (8~\%) 	&  59 $\pm$ 4.7 (8~\%)   	       \\
+	\hline
+	\end{tabular}
+	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum boardwall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum boardwall experiments.
+Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
+	\label{tab:Point_Source_HFPUF}
+\end{table}
+
+This was an interesting exercise but was not definitive in any way.
+If we were to attempt to improve the predictions by using radiative fractions that are known to be representative of the fuels, the predictions in some cases might get worse.
+For example, recommended values in the literature for the $chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
+The default radiative fraction of 0.35 is inline with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
+Literature values for polyurethane foam were elusive.
+
+One more way to assess the point source model was to examine the heat flux data measured at 2~m away from the vertical centerline on the burners during some of the early source fire characterization experiments.
+If we rearrange the point source equation, to solve for $\chi_r$ by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2~m away the resulting value for $\chi_r$ are 0.26, 0.46 and 0.33 for the natural gas, gasoline and polyurethane burners respectively.
+This distance should be more appropriate for the use the point source model but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
+It appears that more research is needed on radiative fractions of fire sizes and realistic fuels that might be found in a residential setting
 
@@
 
-discuss the premise    ~\cite{McCaffrey:1979}
-McCaffery
-
-\begin{equation}\label{eq:z_c}
-Z_c = 0.08 \dot{Q}^{\frac{2}{5}}
-\end{equation}
-where $Z_c$ is the continuous flame height~(m)
-\begin{equation}\label{eq:z_i}
-Z_i = 0.20 \dot{Q}^{\frac{2}{5}}
-\end{equation}
-where $Z_i$ is the intermittent flame height~(m)
-
-Heskestad widely used  NRC CFITrainer  texts
-
-\subsection{Correlation Descriptions}
+The desire to use flame height correlations is based on the thought that the flame height will correlate to the height of the associated fire pattern.
+With the heat release rate data that we have from these experiments, comparisons will be made with the one of the more widely used empirical algorithms, known as the Heskestad flame height correlation.
+
+\subsection{Correlation Description}
+
 Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.
-Appropriate fuels would ``include liquid pool fires and other horizontal surface fires'' add cites.
-Given that the fuel configurations are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad's flame height equation directly.
-Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.
-Calculating the flame heights with the average peak heat release rates measured from the three fuels yields 1.0~m and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
-It should be noted that the coefficient, 0.235, is dependent on the ratio of the heat of combustion to the actual mass stoichiometric ratio of air to volatiles of the fuel.
-For many liquid and gaseous fuels this coefficient is representative, Heskestad points out, however, that some common fuels, such as gasoline, deviate from the cited range.
-For gasoline a coefficient value of 0.2 should be used 32.
-Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.
-The range of calculated values are compared with the mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.
+Appropriate fuels would include liquid pool fires and other horizontal surface fires~\cite{Heskestad:SFPE,Beyler:1986}.
+The inputs required to use the model are the heat release rate and the diameter of the fire or the burner.
 
@@
 
-\section{Comparison of Results}
-
-From Interflam  Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
-These calculated values were compared to the measured results from “real fuels” and provided reasonable results.
-Ranges of values were calculated in order to address the uncertainty in the heat release rate measurements.
-Other uncertainties, such as lack of knowledge on the exact fuel composition need to be addressed, as this may well be the case in a real fire investigation.
-Even accounting for uncertainties in heat release rate measurement, the flame height estimates tended to be better aligned with the peak flame height than the median flame height.
-A specific coefficient for “gasoline” was used in Heskestad’s equation which resulted in the measured median flame height being within the range of the predictions.
-The heat flux estimations were calculated with a range of radiant heat fractions, with the intent of the “actual” value being in that range.
-With the exception of gasoline, the estimated heat flux values tended to under predict the measured results.
-Given the limitations of the data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
-These algorithms are tools which can be used to provide insight into a problem, but not an accurate single value answer.
+Given that the burner used in this study are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad's flame height equation directly.
+Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.
+
+Once again the average peak heat release rates from Ch 2 will be used.
+The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80 kW.
+The polyurethane fueled burner had an average peak heat release rate of 45 kW.
+Calculating the median flame heights with the average peak heat release rates measured from the three fuels yielded 1.0~m, 1.0~m, and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
+It should be noted that the coefficient, 0.235, is dependent on the ratio of the heat of combustion to the actual mass stoichiometric ratio of air to volatiles of the fuel.
+For many liquid and gaseous fuels this coefficient is representative, Heskestad points out, however, that some common fuels, such as gasoline, deviate from the cited range.
+For gasoline a coefficient value of 0.2 should be used~\cite{Heskestad:SFPE}.
+Changing the coefficient yields a median flame height of 0.8~m for gasoline.
+
+Based on the video based flame height analysis conducted as part of this study the median flame heights were 0.705~m, 0.695~m, and 0.470~m for natural gas, gasoline, and polyurethane, respectively.
+Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.
+The range of calculated values are compared with the mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.
+
+\begin{table}
+\centering
+\footnotesize
+\begin{tabular}{|c|c|c|c|}
+\hline
+Method          &   \multicolumn{3}{|c|}{Flame Heights (m)} \\ \cline{2-4}
+                &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
+Photographic    &       0.70 $\pm$ 0.23 (33~\%)   &	0.84 $\pm$ 0.28 (33~\%) 	& 0.46 $\pm$ 0.23 (50~\%)   \\
+Video Based     &   	0.70 $\pm$ 0.11 (15~\%)   &	0.70 $\pm$ 0.1 (14~\%) 	& 0.47 $\pm$ 0.16 (34~\%)   \\
+Fire Pattern    &   	0.74 $\pm$ 0.12 (16~\%)   &	0.83 $\pm$ 0.15 (18~\%) 	& 0.24 $\pm$ 0.12 (50~\%)   \\
+Heskestad (range)  &   	0.94 to 1.06		    &	0.65 to 0.93        	& 0.48 to 0.90   \\
+\hline
+\end{tabular}
+ \caption[Comparison of the median flame height measurement results with the fire pattern heights and the Heskestad predictions]{Comparison of the median flame height measurement results with the fire pattern heights and the Heskestad predictions.
+The measured results are shown with 95~\% confidence limits.
+The Heskestad median flame height calculations are presented as a range based on the uncertainies of the peak heat release rate of each fuel type.}
+ \label{tab:Comparing_Flame_Heights}
+\end{table}
 
 \chapter{Comparison of Field Model Simulations with Experimental Results}
+
+Similar to the previous chapter the goal is to utilize an analytical tool to predict or simulate the results from some of the key experiments conducted in this study.
+Unlike the previous chapter the computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
+The CFD models require more knowledge and more input data to utilize correctly.
+Currently modelers need to develop there own data or rely on ill defined databases with the hope that the material tested is similar to the materials of interest.
 
@@
 
-The comparison for the fire pattern heights and flame heights from the natural gas fueled fires are very similar.
-This is expected in part because the natural gas fires are “steady state”.
-The “steady” nature of the fire aids in the repeatability or the reduction of variability in the experiments.
-For example the energy transfer to the gypsum wall board is also fairly “steady” for the duration of the experiment.
-Based on the average total heat released, approximately 23 MJ, more energy was transferred to the wall board when compared to the other two fuels.
-This energy is needed to “dry” out the gypsum wallboard both of water absorbed from the environment and the chemically bound water, to allow the paper cover and paint to burn.
-
-The gasoline fueled fires also had similar fire pattern heights and flame heights; however, the similarity was not as strong as the natural gas fires.
-The transient nature of the fire played a strong role here, there was less energy transferred to the gypsum wall board and the exposure time for portions of the wall board more distant from the fuel surface was less.
-Another issue that comes into the discussion is the length of time, 30 s, that was used for flame height analysis.
-This period of time was used to ensure that the flame height at the time of peak heat release rate was included in the analysis.
-However, this ultimately may have had the effect of reducing the mean flame height.
-The mean flame height based on the photo analysis was 0.84 m.
-The photo analysis was also performed over a 30 s period bounding the peak heat release rate but the number of images analyzed was about one sixth of the images analyzed with the video technique.
-It should also be noted that the range of the flame heights increased, especially on the lower bound, with the video analysis compared to the photo analysis.
-
-The polyurethane foam fueled fire heights and the associated fire pattern heights had the least similarity when compared to the other two fuels.
-This follows with the other findings about the polyurethane fueled fires in this study.
-The most prominent being the complications added by the fuel being solid and the uncertainties of the flame spread and localized burning rates, leading to poor repeatability of the fire growth and the heat release rate relative to the natural gas and the gasoline fueled fires.
-
 Mean flame height has been identified by Heskestad and others as having a strong relation to a given heat release rate from fires with a horizontal fuel surface~\cite{Heskestad:SFPE, Beyler:1986}.
@@
 In cases where transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wall board or other target fuel even for “simple” pre-flashover fire patterns.
+
+From Interflam  Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
+These calculated values were compared to the measured results from “real fuels” and provided reasonable results.
+Ranges of values were calculated in order to address the uncertainty in the heat release rate measurements.
+Other uncertainties, such as lack of knowledge on the exact fuel composition need to be addressed, as this may well be the case in a real fire investigation.
+Even accounting for uncertainties in heat release rate measurement, the flame height estimates tended to be better aligned with the peak flame height than the median flame height.
+A specific coefficient for “gasoline” was used in Heskestad’s equation which resulted in the measured median flame height being within the range of the predictions.
+The heat flux estimations were calculated with a range of radiant heat fractions, with the intent of the “actual” value being in that range.
+With the exception of gasoline, the estimated heat flux values tended to under predict the measured results.
+Given the limitations of the data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
+These algorithms are tools which may be used to provide insight into a problem, but not an accurate single value answer.
 

### 2016-10-03 Projects/DelCo_2014_2015/Reports/Hose_Stream_Tests/TeX_Files/DelCo_Hose_Stream_Tests.tex
fix type in Hose acknowledgements

@@
 
-The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay MCElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Nicholas Dow (SURF student), and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
 These experiments could not have been conducted without them.

### 2016-10-03 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added Durock name in construction section

@@
 \vspace*{2\baselineskip}
-September 2016}
+October 2016}
 
@@
 The first floor interior walls of each structure were framed with steel studs set to 400~mm (16~in) centers and track.
-Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
-The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick cement board.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the steel studs, and a layer of 13~mm (0.5~in) thick Durock cement board covered the gypsum board.
+The interior ceiling of each structure was covered by two layers of 13~mm (0.5~in) thick Durock cement board.
 \FloatBarrier
@@
 The walls on the second floor were of wood-frame with 51~mm (2~in) by 102~mm (4~in) studs set to 400~mm (16~in) centers.
-Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick cement board covered the gypsum board.
-The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick cement board.
+Two layers of 16~mm (0.63~in) Type X gypsum board lined the interior side of the wood studs, and a layer of 13~mm (0.5~in) thick Durock cement board covered the gypsum board.
+The interior ceiling of the second story was covered by two layers of 13~mm (0.5~in) thick Durock cement board.
 The exterior sides of the outer walls on the second floor were protected by 11~mm (0.44~in) thick OSB and 8~mm (0.31~in) fiber cement lap siding.
@@
 \subsubsection{Gas Sampling}
-A gas sampling system with relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} from California Analytical Instruments, Inc.
-(model 602P) was used to make gas concentration measurements.
+A gas sampling system from California Analytical Instruments, Inc.
+(model 602P) having a relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} was used to make gas concentration measurements.
 However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.

### 2016-10-03 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex

@@
 Another means of quantifying field data with Streams is the use of contour plots.
-Examples of the time averaged contour plots are shown in Figs.~\ref{Gas_and_Gasoline_Contours} and \ref{Foam_Contours} for the natural gas, gasoline, and polyurethane fueled fires.
+Examples of the time averaged contour plots are shown in Figures~\ref{Gas_and_Gasoline_Contours} and \ref{Foam_Contours} for the natural gas, gasoline, and polyurethane fueled fires.
 Each contour line represents the percentage of time that the flame was at a given position.
@@
 This series of experiments combined the instrumentation used in the non-combustible wall experiments with gypsum wallboard, which has a combustible paper surface.
-These experiments were conducted in a similar manner as the non-combustible instrumented wall experiments, the only new variable is the painted, gypsum wallboard.
+These experiments were conducted in a manner similar to the non-combustible instrumented wall experiments, the only new variable being the painted, gypsum wallboard.
 These experiments enabled the examination of the ignition/no ignition predictions from the previous experiments.
@@
 
-Since these experiments were the culmination of the instrumented series of full scale tests, the use of gypsum wallboard was intended to provide some insight into how much fire damage would result.
+Since these experiments were the culmination of the instrumented series of full scale tests, the use of gypsum wallboard was intended to provide some insight into the amount of fire damage that would result.
 These experiments proved to be challenging in terms of time and effort.
 Each panel of gypsum wallboard had to be carefully drilled for thermocouple and heat flux gauge placement.
-Since there was only one set of heat flux gauges this reduced the number experiments that could be conducted on a given day.
+Since there was only one set of heat flux gauges, this reduced the number experiments that could be conducted on a given day.
 With other project demands, the number of instrumented wallboard experiments that could be conducted under the oxygen consumption calorimeter was reduced due to time constraints.
@@
 By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass~\cite{GA:2010}.
-Chemically gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$ $\bullet$ 2H$_{2}$O) .
-By weight pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.
-
-The gypsum wallboard used in these experiments is referred to as `regular' as opposed to gypsum wallboard `Type C' or `Type X' which are used in fire rated assemblies.
-The gypsum wallboard used in these experiments was purchased from same manufacturer in an effort to have the most similar panels for use between the experiments.
+Chemically, gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$ $\bullet$ 2H$_{2}$O) .
+By weight, pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.
+
+The gypsum wallboard used in these experiments is referred to as `regular' as opposed to `Type C' or `Type X' gypsum wallboard, which are used in fire rated assemblies.
+The gypsum wallboard used in these experiments was purchased from the same manufacturer in an effort to have the most similar panels for use between the experiments.
 Each 1.22~m by 2.44~m by 12.7~mm thick panel weighed approximately 30.5~kg.
@@
 The first two rows of data were measured from samples of the gypsum wallboard used in these experiments.
-The bottom four rows of data are from ~cite\{Gross:1985}.
-
-There have been a number of studies that have examined gypsum wallboard under elevated temperature conditions in terms of it's thermal properties or in terms of its physical change as a result to exposure to heat.
+The bottom four rows of data are from ~\cite{Gross:1985}.
+
+There have been a number of studies that have examined gypsum wallboard under elevated temperature conditions in terms of either its thermal properties or in terms of its physical change as a result of exposure to heat.
 Schroeder conducted a study on the post-fire analysis of construction materials including gypsum.
@@
 This transformation occurs in the range of 98~$^\circ$C to 130~$^\circ$C.
-With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, commonly this process is known as calcination.
+With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, a process commonly known as calcination.
 Schroder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
@@
 		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\ \hline
-		\hline 807  & 24 	& 0.14 	&  		& 1.09 \\
+		\hline 807  & 24 	& 0.14 	& 20	& 1.09 \\
 		\hline  	& 100 	& 0.15  &  		&  \\
@@
 The average mass of paint on the finished surface of the gypsum wallboard was 0.33~kg.
-Then the paint thickness was estimated an ultrasonic coating thickness gauge~\cite{defelsko}.
+Then the paint thickness was estimated using an ultrasonic coating thickness gauge~\cite{defelsko}.
 Over the course of the experiments, random painted panels where checked with the ultra sonic device.
@@
 Table~\ref{tab:IWGB_experiments} lists the experiments that were conducted for each fuel type.
-In this chapter, as in the previous chapter the averaged peak values for temperatures and heat fluxes will presented at varying distances from the wall.
-For the gasoline and polyurethane fires, an additional position, 0.08~m from the wall was added.
+In this chapter, as in the previous chapter, the averaged peak values for temperatures and heat fluxes are presented at varying distances from the wall.
+For the gasoline and polyurethane fires, an additional position, 0.08~m from the wall, was added.
 
@@
 
-A complete set of data temperature and heat flux data for the natural gas burner experiments conducted at 0.31~m, 0.15~m, and 0.0~m are provided in Figures~\ref{IWGB_NG_TC_Plume_set},\ref{IWGB_NG_TC_Wall_set},\ref{IWGB_NG_TC_Backside_set},\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
+A complete set of temperature and heat flux data for the natural gas burner experiments conducted at 0.31~m, 0.15~m, and 0.0~m are provided in Figures~\ref{IWGB_NG_TC_Plume_set}, \ref{IWGB_NG_TC_Wall_set}, \ref{IWGB_NG_TC_Backside_set}, \ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
 The data for the burner positioned 0.31~m from the wall is the average of three replicate experiments.
@@
 This was the result of a an early shut down of the gas supply.
-This decrepancy was not noticed until the data was reviewed.
-However at the point there was no opportunity to rerun the experiment.
-
-The temperatures measured along the vertical center axis of the burner provide distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature see Figure~\ref{IWGB_NG_TC_Plume_set}.
-The persistant flame region appears to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
-Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seem to be in the intermittent flame region.
+This decrepancy was not noticed until the data was reviewed, at which point there was no opportunity to rerun the experiment.
+
+The temperatures measured along the vertical center axis of the burner provided distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature, see Figure~\ref{IWGB_NG_TC_Plume_set}.
+The persistant or continuous flame region appeared to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
+Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seemed to be in the intermittent flame region.
 The thermocouples position at or above 1.4~m appear to be in the buoyant plume region.
@@
 The temperatures measured on the front surface of the painted gypsum wallboard are displayed in Figure~\ref{IWGB_NG_TC_Wall_set}.
-When the burner was located 0.31~m and 0.15~m away from the wall the temperatures started at ambient and slowly increased  reaching the peak temperatures at 300~seconds when the burner was shut off.
-For the case where the burner was in contact with the wall, the two of the thermocouples located in the persistant flame region indicated a decreasing temperature trend after after the paper on the gypsum wallboard had burned away.
+When the burner was located 0.31~m and 0.15~m away from the wall, the temperatures started at ambient and slowly increased, reaching the peak temperatures at 300~seconds, then the burner was shut off.
+For the case where the burner was in contact with the wall, the two thermocouples located in the persistant flame region indicated a decreasing temperature trend after the paper on the gypsum wallboard had burned away.
 The decrease in temperature my have had been the result of material from the burned gysum wallboard shielding otherwise impacting those thermocouples.
@@
 
-Figure~\ref{IWGB_NG_TC_Backside_set} has graphs of the temperature time histories of the themrocouples installed on the back face of the 12.7~mm thick gypsum wallboard.
-In each case the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
+Figure~\ref{IWGB_NG_TC_Backside_set} has graphs of the temperature time histories of the thermocouples installed on the back face of the 12.7~mm thick gypsum wallboard.
+In each case, the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
 As the position of the fire moves closer to the wall the rate of temperature rise on the back increases.
@@
 
-The heat flux values from the arrays of sensors mounted flush with the surface of the gypsum wallboard are given in Figures~\ref{IWGB_NG_HF_CenterSet}, and \ref{IWGB_NG_HF_EdgeSet}.
-The data from the array centered on the burner and the data from the array located at the right edge of the burner are similar in response and magnitude when the burner is positioned away from the wall.
-Similar to the wall surface temperatures the heat flux increase as the burner is moved closer to the wall.
-However once the burner is in contact with the wall the flame is moving side to side.
-As a result, the peaks in the heat flux alternate between the center array and the edge array, as the flame moves and changes shape.
-This movement causes changes in the peak heat flux of approximately 20~kW/m$^2$.
+The heat flux values from the arrays of sensors mounted flush with the surface of the gypsum wallboard are given in Figures~\ref{IWGB_NG_HF_CenterSet} and \ref{IWGB_NG_HF_EdgeSet}.
+The data from the array centered on the burner and the data from the array located at the right edge of the burner were similar in response and magnitude when the burner is positioned away from the wall.
+Similar to the wall surface temperatures, the heat flux increased as the burner was moved closer to the wall.
+However, once the burner is in contact with the wall, the flame is moved side to side.
+As a result, the peaks in the heat flux alternated between the center array and the edge array, as the flame moved and changed shape.
+This movement caused changes in the peak heat flux of approximately 20~kW/m$^2$.
 The averaged heat flux values graphed with respect to the burner position from the wall are shown in Figure~\ref{IWGB_NG_HF_CandEAvg}.
@@
 
-Given that the focus of this study is on generating thermal damage on the face of the gypsum wallboard, the temperature and heat flux at the wall surface are important to examine.
+Since the focus of this study is on generating thermal damage on the face of the gypsum wallboard, the temperature and heat flux at the wall surface are important to examine.
 The averaged peak temperatures of the wall mounted thermocouples for each of the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
-This figure allows the comparison of the averaged peak temperatures at the wall based on the difference in fuel type and based on the burner's distance from the wall.
-The graphs in the Figure~\ref{IWGB_Temp_Comp_FrontCenter} show that generally the temperature at the wall surface decreases as the burner moves away from the wall.
+This figure allows the comparison of the averaged peak temperatures at the wall based on the difference in fuel type and on the burner's distance from the wall.
+The graphs in Figure~\ref{IWGB_Temp_Comp_FrontCenter} show that generally the temperature at the wall surface decreases as the burner moves away from the wall.
 The exception to this appears to be at 0.08~m distance from the wall for the gasoline and polyurethane foam experiments.
@@
 A review of the heat release rates for these experiments was made to see if that might have contributed to the higher heat flux, the peak heat release rates for the burner positions at 0.0~m, 0.08~m and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
-So a change in HRR did not contribute to the increase at the 0.08~m position.
+This change in HRR did not contribute to the increase at the 0.08~m position.
 
@@
 However, the heat flux sensor positioned at 0.6~m above the burner showed an increase.
-As indicated above, the data which goes against the general trend of the data, is a result of the movement of the flame.
-For this experiment a sequence of photographs, Figure~\ref{IWGBGAS6_seq}, captured the oscillatory motion of the flame which moved from the vertical centerline toward the wall and back again.
-In the process the fire pattern on the wall was generated.
+As indicated above, this data which goes against the general trend of the data, was a result of the movement of the flame.
+For this experiment, a sequence of photographs, Figure~\ref{IWGBGAS6_seq}, captured the oscillatory motion of the flame, which moved from the vertical centerline toward the wall and back again.
+In the process, the fire pattern on the wall was generated.
 
 The heat flux data from the polyurethane foam burner experiments also exhibited variations, although less pronounced than those of the gasoline experiments, at the 0.08~m and the 0.15~m position.
-The polyurethane foam generated less heat release rate and a shorter flame than the gasoline, so even though the flame was moving toward the wall, impact was not as great.
-Again this motion was not a steady motion but an oscillatory one.
+The polyurethane foam generated a lower heat release rate and a shorter flame than the gasoline, so even though the flame was moving toward the wall, the impact was not as great.
+Again, this motion was not a steady motion, but an oscillatory one.
 
@@
 Referring to DeHaan's classifications, there are no surface deposits such as light soot that could be brushed or blown off the gypsum wallboard.
-There is a thin band of surface thermal effects in the form of discoloration of the paint, this could be considered an outer bound of the pattern.
-To the left of the discoloration is clearly an larger area where charring (blackening of the paint/paper), penetration (lifting of the painted/paper residue), and consumption (areas where the paint/paper reside is gone altogether).
+There is a thin band of surface thermal effects in the form of discoloration of the paint, that could be considered an outer bound of the pattern.
+To the left of the discoloration is clearly a larger area where charring (blackening of the paint/paper), penetration (lifting of the painted/paper residue), and consumption (areas where the paint/paper residue is gone altogether).
 The last three classifications or criteria will be used in this study to define the edge of the fire pattern.
@@
 
-Soot and discoloration alone was not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot as shown in Figure~\ref{Soot_pattern}.
-From the photograph the areas of penetration and consumption can be delineated while the discolored and sooted areas tend to meld together.
-Further the focus of the measurements in this study are on thermal damage, therefore the focus is on the burned to not burned line of demarcation.
+Soot and discoloration alone were not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot, as shown in Figure~\ref{Soot_pattern}.
+From the photograph, the areas of penetration and consumption can be delineated while the discolored and sooted areas tend to meld together.
+Further, the focus of the measurements in this study are on thermal damage.
+Therefore the focus is on the ``burned to unburned'' line of demarcation.
 
@@
 A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.
-While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary} a closer look reveals that most of the values are not ``significantly '' different.
-In other words the range of expanded uncertainty values overlap.
-For example at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15~\%).
-So the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
-While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are ``that '' different.
+While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary}, a closer look reveals that most of the values are not ``significantly '' different.
+In other words, the range of expanded uncertainty values overlap.
+For example, at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15~\%).
+So, the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
+While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are substantially different.
 
@@
 
-Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath.
+Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath when the burner was against the wall.
 The peak height of the consumed and penetrated paper, i.e.
 the burned region, was 0.8~above the burner.
-This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible was experiments.
+This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible wall experiments.
 
@@
 
-Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
-When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed with the lowest point approximately 0.1~m above the burner and extending up to the 0.4~m above the burner on the left side.
+Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by the gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
+When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed, with the lowest point approximately 0.1~m above the burner and extending up to 0.4~m above the burner on the left side.
 The formation of the burned area was captured on film and is shown in Figure~\ref{IWGBGAS6_seq}.
-The burned region on the gypsum wallboard from exposure to the gasoling fire position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
-The width of the burned region was approximately one half of the burner width at it's maximum.
-Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by gas burner when it is tight against the gypsum wallboard.
+The burned region on the gypsum wallboard from exposure to the gasoline burner position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
+The width of the burned region was approximately one half of the burner width at its maximum.
+Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by the gasoline burner when it is tight against the gypsum wallboard.
 Two views are shown.
 The image on the left shows the wall shortly after the fire went out.
-The burned area came be discerned, but a close look is required.
-In the photograph on the right, the same piece of gypsum wallboard was lightly brushed off, which revealed a clearer view of the area where the paint and paper were burned off.
+The burned area can be discerned, but a close inspection is required.
+In the photograph on the right, the same piece of gypsum wallboard was lightly brushed off, which revealed an improved view of the area where the paint and paper were burned off.
 The peak height of that fire pattern is just short of 0.8~m.
-The maxim width is approximately the full width of the burner.
+The maximum width is approximately the full width of the burner.
 
@@
 Figures~\ref{IWGB_PUF_patterns} and~\ref{IWGB_PUF_0m_patterns} show the progression of thermal damage caused by the polyurethane fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the instrumented gypsum wallboard.
-The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage, the only damage to the wall is from soot deposition.
-When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but the was no consumption or penetration of the paper finish layer.
-Three replicate experiments were conducted with the polyurethane foam fueled burner tight against the instrumented gypsum wallboard.
+The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage.
+The only damage to the wall is from soot deposition.
+When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but there was no consumption or penetration of the paper finish layer.
+Three replicate experiments were conducted with the polyurethane foam fueled burner placed tight against the instrumented gypsum wallboard.
 The resulting patterns are shown in Figure~\ref{IWGB_PUF_0m_patterns}.
@@
 
-With this set of experiments, fire patterns as the result of thermal damage have finally generated in a few cases.
-To recap our crude predictions from the previous chapter, the natural gas burner had the potential to cause a fire pattern with a height between 0.6~m and 0.8~m.
+With this set of experiments, fire patterns as the result of thermal damage were finally observed in a few cases.
+To recap the crude predictions from the previous chapter, the natural gas burner had the potential to cause a fire pattern with a height between 0.6~m and 0.8~m.
 With the natural gas burner against the wall, a pattern with a maximum burn area of 0.8~m in height was generated.
-From Chapter III, the gasoline had a potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
+From Chapter 3, the gasoline had the potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
 In the single instrumented gypsum wallboard experiment with the gasoline burner located against the wall, the maximum height of the burned region was just short of 0.8~m.
-The prediction for the potential height of the fire pattern that could be created with the polyurethane burner against the wall was between 0.4~ and 0.6~m.
-With the polyurethane burner three replicate experiments were conducted.
+The prediction for the potential height of the fire pattern that could be created with the polyurethane burner against the wall was between 0.4~m and 0.6~m.
+With the polyurethane burner, three replicate experiments were conducted.
 The range of the maximum heights of the burned region was 0.2~m to 0.35~m.
 The average peak burned region height was 0.3~m.
-The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Ch III provided a ``ballpark'' estimate of the maximum height of the burned region.
+The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Ch 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
 
@@
 The purpose of this chapter is to develop and compare data from bench scale apparatus that could be used to analyze fire damage to gypsum wallboard.
-This type of testing might be practical for a fire investigator to use based on the low cost, relative to a full-scale fire test, and the small size of the samples needed for the tests.
-In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance and the damage to a section of painted gypsum wallboard.
+This type of testing might be practical for a fire investigator to use based on the low cost relative to a full-scale fire test and the small size of the samples needed for the tests.
+In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance, and the damage to a section of painted gypsum wallboard.
 While the data generated from those full scale laboratory experiments provide valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests in an effort to validate or improve the existing data in the literature.
@@
 The gas flow rate in the exhaust duct was calculated from the pressure drop across and temperature at an orifice plate in the duct.
-Finally, the concentrations of oxygen, carbon dioxide, carbon monoxide, were measured using appropriate instruments.
+Finally, the concentrations of oxygen, carbon dioxide, and carbon monoxide were measured using appropriate instruments.
 Heat release rate was calculated from the gas concentration and mass flow measurements.
 
-For this study samples were cut from painted gypsum wallboard panels.
+For this study, samples were cut from painted gypsum wallboard panels.
 The samples were 100~mm square and 12.7~mm thick.
@@
 The key measurements and observations made with the cone calorimeter were heat release rate per unit area of the samples and time to ignition.
-These experiments were conducted with heat fluxes of 25, 35, 50, 70 and 75 kW/m$^2$.
+These experiments were conducted with heat fluxes of 25, 35, 50, 70, and 75 kW/m$^2$.
 Several other cone calorimeter experiments were conducted with a single type K thermocouple, installed in a slit in the painted paper on the gypsum wallboard samples.
@@
 
- For these experiments a higher heat flux profile was required to propagate flame spread on the painted gypsum wallboard samples, so the air-gas flow supplying the radiant panel was increased to provide an incident flux ranging from approximately 21~kW/m$^2$ at the 100~mm position to 2~kW/m$^2$ at the 900~mm position.
+ For these experiments, a higher heat flux profile was required to propagate flame spread on the painted gypsum wallboard samples, so the air-gas flow supplying the radiant panel was increased to provide an incident flux ranging from approximately 21~kW/m$^2$ at the 100~mm position to 2~kW/m$^2$ at the 900~mm position.
 The incident heat flux curve used in these experiments is shown in Figure~\ref{FRP_HF_Calibration}.
@@
 
-A diffusion, propane-fueled, pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
+A diffusion, propane-fueled, pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~E648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
 The objective of these experiments was to determine the critical radiant flux for the painted gypsum wallboard samples.
@@
 
-For the purposes of this study a modified version of the test apparatus was used.
-The radiant panel and the controls for the radiant panel  remained in place as documented in ASTM~E162.
-However the sample mounting system was changed.
+For the purposes of this study, a modified version of the test apparatus was used.
+The radiant panel and the controls for the radiant panel remained in place, as documented in ASTM~E162.
+However, the sample mounting system was changed.
 A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux~\cite{Lawson:1999}.
@@
 The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
-In other words, the area around the center point of the sample had heat flux measures similar, in other words within the uncertainty of the heat flux sensor, to the center point measurement.
+In other words, the area around the center point of the sample had heat flux measures that were similar, meaning that they were within the uncertainty of the heat flux sensor, to the center point measurement.
 Outside of the central area of the samples, the heat flux would decrease as the position approached the edge of the sample.
@@
 Samples of painted gypsum wallboard were shipped from the NIST Fire Research Laboratory in Gaithersburg, MD., USA.
-In these experiments an additional incident heat flux level of 30~kW/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
+In these experiments, an additional incident heat flux level of 30~kW/m$^2$ was added to provide another test between the 25 and 35~kW/m$^2$ levels.
 The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
@@
 The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.
-Given the uncertainty if the temperature measurement these temperatures are not significantly different.
+Given the uncertainty of the temperature measurement, these temperatures are not significantly different.
 Taking the average ignition temperature across all of these cone experiments yields a value of 360~$^{\circ}$C $\pm~54$~$^{\circ}$C.
@@
 This effect is shown in Figure~\ref{FRP_flamefront_arrows}.
-In Figure~\ref{FRP_flamefront_arrows} several thermocouples can be seen.
+In Figure~\ref{FRP_flamefront_arrows}, several thermocouples can be seen.
 The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the painted paper face made with a razor blade.
@@
 
-The cone calorimeter experiments generated peak heat release are per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
-The average total heat released during each burn was 2.8 MJ/m$^2$.
+The cone calorimeter experiments generated peak heat release rate per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
+The average total heat released per unit area during each burn was 2.8 MJ/m$^2$.
 The total heat released during the cone calorimeter experiments compares favorably with the study by McGraw and Mowrer~\cite{McGraw:1999}, where the total heat released for the gypsum wallboard with 2 coats of latex paint was 2.3 to 2.7~MJ/m$^2$.
@@
 Exposing the painted gypsum wallboard samples to the vertical radiant panel provided a wide range of physical damage to samples as shown in Figure~\ref{RPGB_SET}.
-However based on visual observations there were no flaming ignitions.
+However, based on visual observations, there were no flaming ignitions.
 For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
@@
 Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining the Figure~\ref{RPGB_SET} we see surface thermal effects of discoloration on the painted paper cover of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
-The samples exposed to 15~kW/m$^2$ exhibit charring and given the thin nature of the painted paper surface penetration was evidenced on two of the three sample.
+The samples exposed to 15~kW/m$^2$ exhibit charring and given the thin nature of the painted paper surface, penetration was evidenced on two of the three samples.
 The 15~kW/m$^2$ sample on the right also shows signs of the painted paper being consumed.
@@
 Even though the incident heat flux values were lower than the characteristic value measured at the center of the sample, as the heat flux in the center increased heat flux at the edges also increased above 15~kW/m$^2$.
-Hence the damaged area increased outward toward the edges.
+Hence, the damaged area increased outward toward the edges.
 It would appear in this test series, that 15~kW/m$^2$ heat flux exposure is on the threshold of painted paper penetration and consumption stage.
@@
 
-Each apparatus provided a thermal exposure to painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
-Each test method has a specific parameter or parameters that they were designed to measure for.
-As a result, the data presented in this chapter provides a wide range of values that can not be taken as a single number an applied.
-In other words the data must be taken in context with how it was generated and analyzed accordingly.
+Each apparatus provided a slightly different thermal exposure to painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
+Each test method has a specific parameter or parameters for which they were designed to measure.
+As a result, the data presented in this chapter provides a wide range of values that cannot be taken as a single number and applied.
+In other words, the data must be taken in context with how it was generated and analyzed accordingly.
 This is a challenge for fire investigators, analysts, and engineers alike.
 
-The nature of the bench scale experimental data does not allow one to simply pick a value from a table an directly applying it as an input to a fire model.
+The nature of the bench scale experimental data does not allow one to simply pick a value from a table and directly apply it as a universal input to a fire model.
 Currently there is no specific protocol for a fire model user to follow to develop input data.
 For example, there is no guidance on how to conduct a series of experiments to generate all of the data needed for the models.
-Using the gypsum wall board as an example, material propeties such as density, specific heat, and thermal conductivity change over time as a result of the thermal exposure~\cite{Schroeder:1999,McGraw:1999}.
+Using the gypsum wallboard as an example, material propeties such as density, specific heat, and thermal conductivity change over time as a result of the thermal exposure~\cite{Schroeder:1999,McGraw:1999}.
 Of course this behavior is not unique to gypsum wallboard.
@@
 This chapter was anticipated to provide data that that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures, 10 to 75~kW/m$^2$.
-The ignition temperatures measured in the cone calorimeter experiments conducted as part of this side do not align with the data in the published literature but the reason for the 200~$^{\circ}$C could not be resolved other than issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
+The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature but the reason for the 200~$^{\circ}$C could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
 
@@
 
-In this chapter the application of empirical algebraic flame characterizations will be compared against the results from the experiments documented in previous chapters.
+In this chapter the application of two empirical algebraic flame characterizations will be compared against the results from the experiments documented in previous chapters.
 Two different types of applications will be used.
-In the first case relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target, in this case gypsum board, will be examined.
-In the second case, the height of the thermal damage on the gypsum board will be examined.
+In the first case, relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target will be examined.
+The target in question is the painted gypsum wallboard.
+In the second case, the height of the thermal damage on the gypsum wallboard will be examined with the use of a flame height correlation.
 Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks as well as other application oriented documents~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999,NUREG_1805}.
 Values generated in the fire characterizations, instrumented bench scale experiments, and values from the literature will be utilized as input to predict or simulate real scale results using the algorithms.
-Then the predicted results will be compared with the full-scale experimental results.
-keep in mind that with these algorithms time is not a factor.
+Then the numerical results will be compared with the full-scale experimental results.
+Keep in mind that with these algorithms time is not a factor.
 Methods of this type are commonly referred to as ``back of the envelope'' estimates.
-they are intended to provide insight as opposed to a hard and fast numerical answer.
+They are intended to provide insight as opposed to a hard and fast numerical answer.
 As the experiments have shown so far there are many uncertainities which impact the results.
@@
 Babrauskas applied this concept in his paper, ``Will the Second Item Ignite''~\cite{Babrauskas:1981}.
-The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite.
-Then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
+The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite, then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
 Radiation is assumed to be the only means of heat transfer.
-However this method is noted to work the best when the distance of the target is at least two to four times the distance of the flame height way from the fire.
+This method is noted to work the best when the distance to the target is remote, at least two times the distance of the diameter of the burner away from the fire~\cite{Hamins:1991,Modak:1977}.
 
@@
 
-The predictions provide good agreement with the natural gas results at distances greater than 1 burner width away, then the predictions trend higher.
+The predictions provide good agreement with the natural gas results at distances greater than 1 burner width away.
+Closer than one burner width array the predictions trend higher.
 In the instrumented gypsum wallboard experiments the natural gas burner at $R=0.31~m$ generated a discoloration on the surface of the painted gypsum wallboard.
-At $R=0.15~m$, burner touching the wall, enough energy was transferred to the wall fast enough that caused charring, penetration, and consumption of the painted paper surface.
+At $R=0.15~m$, with the burner touching the wall, enough energy was transferred to the wall fast enough that caused charring, penetration, and consumption of the painted paper surface.
 Based on the data from the cone calorimeter experiments conducted as part of this study, charring, penetration, and consumption would occur somewhere between 25 and 30~kW/m$^2$.
 Dillon provided a value of 26kW/m$^2$ as the minimum heat flux where ignition of the gypsum wallboard would occur~\cite{Dillon:1998}.
-So at $R=0.31~m$ conditions are on the edge both with the prediction and the measurement of ignition but not high enough to cause the paper to char or worse, there was only enough energy to cause discoloration.
+So at $R=0.31~m$ conditions are on the edge of the threshold heat flux for ignition, both with the prediction and the measurement.
+Neither value is high enough to cause the paper to char and ignite, there was only enough energy to cause discoloration.
 Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
-Indicating that the a fire pattern has been burned into the wall and that was infact true.
+Indicating that a fire pattern has been burned into the wall and that was in fact true.
 
 The predictions provided in Table~\ref{tab:Point_Source_HFNGG} are significantly lower than the measured peak heat flux values from the gasoline fueled burner experiments at every burner position.
-That said, the predictions indicate that at $R=0.31~m$  the heat flux is just before the ignition threshold provided in the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
+That said, the predictions indicate that at $R=0.31~m$  the heat flux is near the ignition threshold provided in the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
 The single gasoline experiment at $R=0.31~m$ showed a peak heat flux of 57~kW/m$^2$.
 The exposure was brief at this peak due to the flame movement toward the wall.
-This makes the experimental values at the three closest location to the wall difficult to compare as the point source model, and most models for that matter, can not account for the flame being drawn toward the wall.
+This makes the experimental values at the three closest locations to the wall difficult to compare with the point source model, and most models for that matter, since they cannot account for the flame being drawn toward the wall.
 An important observation is that the fire damage on the wall was limited to an uneven horseshoe shaped pattern within 100~mm above the top of the burner edge.
 This ignition was captured in Ch 4, Figure~\ref{IWGBGAS6_seq}.
+In other words, at $R=0.31~m$, there was an ignition of the fuel gases that were pyrolyzing from the painted gypsum board wall, but barely and in a very limited area relative to the flame shape near the surface.
 At the two closer positions the char, penetration, and consumption was evident and at these locations both the predictions and the measured heat fluxes are well above the threshold ignition heat flux.
@@
 
-Table~\ref{tab:Point_Source_HFPUF} displays a similar development based on the average peak heat release rate,45~kW, for the polyurethane foan burner.
+Table~\ref{tab:Point_Source_HFPUF} displays a similar development based on the average peak heat release rate, 45~kW, for the polyurethane foam burner.
 Similar to the results from the gasoline comparison, the predictive heat flux values at all of the burner positions are low relative to the experimental data.
-But again we will examine the results along a more qualitative basis.
+But again the results will be examined along a more qualitative basis.
 The experimental data provides an average peak value of 25~kW/m$^2$ for $R=0.31~m$.
@@
 No thermal damage.
-At at $R=0.23~m$ or less, the heat flux is high enough to indicate ignition in the experiments and that was the result.
+At $R=0.23~m$ or less, the heat flux was high enough to indicate ignition in the experiments and that was the result.
 Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threhold heat flux.
@@
 
-This was an interesting exercise but was not definitive in any way.
+This was an interesting exercise but it was not very definitive.
 If we were to attempt to improve the predictions by using radiative fractions that are known to be representative of the fuels, the predictions in some cases might get worse.
@@
 
-One more way to assess the point source model was to examine the heat flux data measured at 2~m away from the vertical centerline on the burners during some of the early source fire characterization experiments.
+Another means to assess the point source model was to examine the heat flux data measured at 2~m away from the vertical centerline of the burners during some of the source fire characterization experiments.
 If we rearrange the point source equation, to solve for $\chi_r$ by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2~m away the resulting value for $\chi_r$ are 0.26, 0.46 and 0.33 for the natural gas, gasoline and polyurethane burners respectively.
-This distance should be more appropriate for the use the point source model but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
-It appears that more research is needed on radiative fractions of fire sizes and realistic fuels that might be found in a residential setting
+This distance should be more appropriate for the use of the point source model but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
+It appears that more research is needed on radiative fractions of fire sizes and realistic fuels that might be found in a residential setting.
 
@@
 
-The desire to use flame height correlations is based on the thought that the flame height will correlate to the height of the associated fire pattern.
+The desire to use flame height correlations is based on the thought that the median flame height will correlate to the height of the associated fire pattern.
 With the heat release rate data that we have from these experiments, comparisons will be made with the one of the more widely used empirical algorithms, known as the Heskestad flame height correlation.
@@
 
-Given that the burner used in this study are square, a conversion of the fuel surface area to the effective diameter is required in order to use Heskestad's flame height equation directly.
+Given that the burners used in this study were square, a conversion of the fuel surface area to the effective diameter was required in order to use Heskestad's flame height equation directly.
 Setting the area of the fuel surface, 0.093~m$^2$, equal to $\pi D^2/4$ and then solving for $D$ yields an effective diameter of 0.344~m.
 
-Once again the average peak heat release rates from Ch 2 will be used.
+Once again the average peak heat release rates from Ch 2 were be used.
 The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80 kW.
@@
 Changing the coefficient yields a median flame height of 0.8~m for gasoline.
-
-Based on the video based flame height analysis conducted as part of this study the median flame heights were 0.705~m, 0.695~m, and 0.470~m for natural gas, gasoline, and polyurethane, respectively.
-Taking the uncertainty of the measurements used to determine the heat release rate ($\pm$ 11~\%) into account generates a range of values.
-The range of calculated values are compared with the mean flame height and range for flame heights  based on photographic analysis for each of the fuels in Table z.
+The assumption was made that this guidance should be followed for the polyurethane as well.
+Changing the coefficient for polyurethane resulted in a median flame height value of 0.57~m.
+
+Median flame height has been assessed a number of ways during this study: a manual analysis of a series of photographs, a computational analysis of video segments, and measuring the height of the fire patterns.
+An expanded uncertainty was calculated for each method which resulted in the range of 95~\% confidence limits for each value.
+A range of values was established with the Heskestad flame height calculation by taking the 95~\% certainty limits determined for the average peak heat release rates of the three different fuels in Chapter 2.
+The range of calculated values for median flame height are compared with the applicable measurements from this study in Table~\ref{tab:Comparing_Flame_Heights}.
 
@@
 Fire Pattern    &   	0.74 $\pm$ 0.12 (16~\%)   &	0.83 $\pm$ 0.15 (18~\%) 	& 0.24 $\pm$ 0.12 (50~\%)   \\
-Heskestad (range)  &   	0.94 to 1.06		    &	0.65 to 0.93        	& 0.48 to 0.90   \\
+Heskestad (range)  &   	0.94 to 1.06		    &	0.65 to 0.93        	& 0.36 to 0.72   \\
 \hline
@@
 The measured results are shown with 95~\% confidence limits.
-The Heskestad median flame height calculations are presented as a range based on the uncertainies of the peak heat release rate of each fuel type.}
+The Heskestad median flame height calculations are presented as a range based on the uncertainies of the average peak heat release rate of each fuel type.}
  \label{tab:Comparing_Flame_Heights}
@@
 
+ The comparison for the natural gas burner shows agreement between the measured median flame height and the average maximum fire pattern height.
+However, the range of calculated median flame height values is significantly different from the mesured values.
+Based on the computational flame height assessment, Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10~\% of the time.
+
+The comparsion of the median flame height values, the average maximum fire pattern height, and the calculated flame height range are all in agreement for the gasoline fueled pan fires.
+This is significant because the 95~\% confidence limits for the fire pattern and the video based flame height are both less than 20~\%.
+
+The measured and calculated values for the polyurethane fueled burner fires are also in agreement.
+The agreement in this case is a result of of the 95~\% confidence limits of the average maximum fire pattern heights being 50~\%.
+
+Overall the Heskestad equation provided reasonable estimates of the median flame height.
+The key to the successful use of any model regardles of the simplicity or complexity is using appropriate data.
+
 \chapter{Comparison of Field Model Simulations with Experimental Results}
@@
 Unlike the previous chapter the computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
-The CFD models require more knowledge and more input data to utilize correctly.
-Currently modelers need to develop there own data or rely on ill defined databases with the hope that the material tested is similar to the materials of interest.
+The CFD models require more knowledge, more computer resources, and more input data to utilize correctly.
+Currently modelers need to develop there own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the materials of interest.
 
@@
 
-Fire Dynamics Simulator~\cite{FDS_Users_Guide} is a computational fluid dynamics (CFD) model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
-Within a CFD model, the computational domain is divided into small three-dimensional rectangular control volumes or computational cells.
+The Fire Dynamics Simulator (FDS) and the scientific visualization tool, Smokeview, are the most widely used and well documented CFD tools in the fire protection engineering community.
+Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate as description of the model here other than to direct the reader to the volumes of information and data that exist for the FDS and Smookeview suite.
+
+FDS~\cite{FDS_Users_Guide} is a CFD model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+A CFD model has a computational domain that is divided into  three-dimensional rectangular control volumes or computational cells.
+The size and arrangement of computational cells is sometimes referred to as the grid or the mesh.
 The CFD model computes the density, velocity, temperature, pressure, and gas concentrations in each cell.
@@
 
-Smokeview is a software tool designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
+Smokeview is a software tool specifically designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
 Smoke-view visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
@@
 
-An FDS model was developed to simulate the instrumented wall experiments with the natural gas burner.
+Two FDS models were developed: 1) to simulate the instrumented gypsum wallboard experiments with the natural gas burner and 2) to simulate the compartment fire pattern experiments with the natural gas burner.
 One of the key determinations that is required when developing an FDS model is the mesh or grid cell size.
@@
 
-Three different computational cell resolutions were examined to determine which resolution provided the best match to both the data from the instruments as well as the data from the fire patterns generated in the wall experiments.
-The three computational grid sizes used were : 80~mm, 40~mm, and 20~mm.
+Choosing the size of the grid when performing an analysis with FDS is critical in order to get the level of resolution needed to adequately simulate the required details within a simulation.
+In studies where large rooms or portions of buildings have been involved grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Vettori:2000,Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
+
+ The FDS documents provide a method to determine how well a flow field will be resolved buy using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
+This value has been referred to as the plume resolution index.
+Given that the fire plume region is the focus of this study, it is important to understand how changes in plume mesh resolution impact the results.
+
+\begin{equation}
+ D^* = \left(
+     \frac{\dot Q}{\rho_\infty  c_p  T_\infty  \sqrt{g} }
+     \right)^\frac{2}{5} 
+ \end{equation}
+
+The characteristic fire diameter is defined by the relationship of the characteristic fire size to the physical diameter of the fire, ${Q^*} = ({D^*}/{D})^{5/2}$, where $D$ is the physical diameter of the fire.
+The quantity, $\dot Q$, is the total heat release rate of the fire.
+The quantity $({D^*}/{\delta x})$ is approximately the number of computational grid cells that span the characteristic diameter of the fire ~\cite{FDS_Users_Guide,FDS_Validation_Guide}.
+
+To examime the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were choosen to model the fire.
+The resulting plume resolution index (RI) values were approximately 4.4, 8.8, and 17.5 respectively.
+Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) plume resolution results from the grid cell size choices.
 
@@
 
-Input data was collected from the experimental results presented in Chapters II and V, and from literature sources in order to simulate the instrumented wall experiments using FDS.
-
-Geometry – the domain of the model was cubic with 2.4~ m on a side.
-The resulting number computational cells for each case ranged from 27,000 for the 80~mm case to 1,728,000 for the 20~mm cases.
+The first FDS model that was developed was the simultion of the instrumented gypsum wallboard experiments.
+The first input needed was the definition of the compuational domain.
+The domain of the model had the geometry of a cube with 2.4~m on a side.
+The resulting number of computational cells for each case ranged from 27,000 for the 80~mm cells to 1,728,000 for the 20~mm cells.
 An isometric view of the model outlined by the domain is shown in Figure      .
@@
 Density = 582
+
+Input data was collected from the experimental results presented in previous chapters of this study as well as from literature sources in order to simulate the instrumented wall experiments using FDS.
 
@@
 
-Choosing the size of the grid when performing an amalysis with FDS is critical.
-In studies where large rooms or portions of buildings have been involved grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Vettori:2000,Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
-
- A measure of how well the flow field is resolved is given by the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
-This value has been referred to as the plume resolution index.
-Given that the fire plume region is the focus of this study, it is important to understand how changes in plume mesh resolution impact the results.
-
-\begin{equation}
- D^* = \left(
-     \frac{\dot Q}{\rho_\infty  c_p  T_\infty  \sqrt{g} }
-     \right)^\frac{2}{5} 
- \end{equation}
-
-The characteristic fire diameter is defined by the relationship of the characteristic fire size to the physical diameter of the fire, ${Q^*} = ({D^*}/{D})^{5/2}$, where $D$ is the physical diameter of the fire.
-The quantity, $\dot Q$, is the total heat release rate of the fire.
-The quantity $({D^*}/{\delta x})$ is approximately the number of computational grid cells that span the characteristic diameter of the fire ~\cite{FDS_Users_Guide,FDS_Validation_Guide}.
-
-Computational grid cell sizes of 80~mm, 40~mm, and 20~mm where used in FDS to model the fire.
-The resulting plume resolutions were approximately 4.4, 8.8, and 17.5 respectively.
-Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, a course, medium, and fine plume resolution results from the grid cell size choices.
  Tables~\ref{tab:FDSRI_Exp_Plume2d} and \ref{tab:FDSRI_Exp_Plume0d} shows the plume temperature results for the three grid resolutions compared the experimental data with a wall spacing of 0.61~m and 0.0~m respectively.
@@
 This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
-
   \label{FDS_FirePattern_comp}

### 2016-10-04 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
FDS text

@@
 $\chi_r$ \> radiative fraction \\
-$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
+discusion$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
 $\dot{Q}$ \> heat release rate (kW) \\ 
@@
 Following the review, a brief presentation on the analysis  of fire patterns, the use of analytical tools, and the current challenges to the field of fire forensics is given as they are the reason for this study.
-In closing this section, an example of a fire incident is presented.
-In the closing section we will return to the example again.
+At the end of this chapter, an example of a fire incident is presented.
+In Chapter 9, we will return to the example again.
 
 \subsection{The Need for Fire Investigation}
-Unwanted fires result in loss of life, property and can create an adverse economic impact on a community.
+Unwanted fires result in loss of life, property, and can create an adverse economic impact on a community.
 Recent findings from an archaeological site in South Africa, indicate that mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
@@
 The estimated number of fire deaths in the U.S.
-in 1975 was 8,100 or 3.75 deaths per 100,000 population~\cite{America_Burning_Revisited}.
-In 2013, there were 3,240 civilian fire fatalities or 1.02 deaths per 100,000 population~\cite{Karter:2014}.
+in 1975 was 8,100, or 3.75 deaths per 100,000 population~\cite{America_Burning_Revisited}.
+In 2013, there were 3,240 civilian fire fatalities, or 1.02 deaths per 100,000 population~\cite{Karter:2014}.
 During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.
 There are many reasons that led to this decrease in loss of life due to fire in the United States.
-An example would be research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs to name just a few.
-None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FEMA:2013}.
+One example is research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs.
+None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations in order to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FEMA:2013}.
 
 Fire investigation is a key element in the fire prevention system that generates data to enable the reduction of fire losses.
-The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause and thus further reduce the losses from fires.
-Data such as the room of fire origin, the first item ignited and ultimately the cause of the fire is information that is critical to understanding and reducing the number of fires.
-For example, the identification of products that are involved in ignitions due to a design flaw, in many cases result in the U.S.
+The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause, and thus further reduce the losses from fires.
+Data such as the room of fire origin, the first item ignited, and ultimately the cause of the fire is information that is critical to understanding and reducing the number of fires.
+For example, the identification of products that are involved in ignitions due to a design flaw in many cases result in the U.S.
 Consumer Product Safety Commission or a manufacturer issuing a product recall.
@@
 In some cases, the fire investigation determines that the fire was intentional.
-An intentional fire as defined in the National Fire Incident Reporting System (NFIRS)  are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention~\cite{Campbell:2014}.
+An intentional fire, as defined in the National Fire Incident Reporting System (NFIRS), are those fires that are deliberately set and include fires that result from deliberate misuse of a heat source, fires of an incendiary nature (arson), as well as controlled burn fires, such as crop clearing, that required fire service intervention~\cite{Campbell:2014}.
 An incendiary fire, as defined by the National Fire Protection Association (NFPA) Guide for Fire \& Explosion Investigations, commonly referred to as NFPA~921, is ``a fire that is deliberately set with the intent to cause a fire to occur in an area where the fire should not be''~\cite{NFPA:921}.
@@
 
-The values cited above are believed to be the best available in the United States and perhaps one of the better fire incident databases in the world.
-However an investigative report by Icove and Hargrove, indicates that arson fires are underreported to the U.S.
+The statistics cited above are believed to be the best available in the United States, which is perhaps one of the better fire incident databases in the world.
+However, an investigative report by Icove and Hargrove indicates that arson fires are underreported to the U.S.
 National Fire Incident Reporting System (NFIRS).
-The investigation provided examples from several major cities, such as New York City, where in 2011, 11 arson fires in buildings were reported to NFIRS, while the Fire Department of the City of New York's Bureau of Fire Investigation had recorded 1,347 arson fires in buildings that year.
+The investigation provided examples from several major cities, such as New York City.
+In 2011, 11 arson fires in buildings were reported to NFIRS, while the Fire Department of the City of New York's Bureau of Fire Investigation recorded 1,347 arson fires in buildings that year.
 Similar discrepancies were found in eight other large U.S.
@@
 \subsection{The Use of Fire Patterns in Fire Investigation}
-Fires are investigated in order to determine the ``origin and cause'' of the fire and in cases of arson there is an effort to determine who was responsible for setting the fire.
-This investigation process must follow the scientific method as documented in NFPA 921~\cite{NFPA:921}.
+Fires are investigated in order to determine the ``origin and cause'' of the fire.
+In cases of arson, there is an additional effort to determine who was responsible for setting the fire.
+This investigation process must follow the scientific method, as documented in NFPA 921~\cite{NFPA:921}.
 There are numerous textbooks on the subject of conducting a fire investigation~\cite{Almirall:2004,Fire_Investigation,DeHaan:2012,Icove:2013,Lentini:2006,Noon:1995}.
@@
 The reports noted the impact of ventilation on the development of the burn patterns~\cite{Shanley:1997,Putorti:1997}.
-A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s) and compartmentalization, to name a few.
+A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s), and compartmentalization, to name a few.
 Given the limited number of experiments in the literature and the large number of variables, it has been difficult to develop a cause and effect relationship between the fire scenarios and the resulting patterns, based solely on the research.
@@
 A collection of the widely used correlations can be found in the U.S.
-Nuclear Regulatory Commission’s (NRC) Fire Dynamics Tools (FDTs).
-These spread sheets incorporate references to the source documents and experimental work upon which the correlations are based.
-In addition, NRC tasked NIST with conducting a verification and validation study of the correlations.
+Nuclear Regulatory Commission’s (NRC) Fire Dynamics Tools (FDTs)~\cite{NUREG_1805}.
+These spreadsheets incorporate references to the source documents and experimental work upon which the correlations are based.
+NRC tasked NIST with conducting a verification and validation study of these correlations.
 Overholt developed the NIST verification and validation study~\cite{Overholt:2014}.
-Not all of the correlations in the FDTs were included in the study because an insufficient amount of reliable data is available to conduct validation.
+Not all of the correlations in the FDTs were included in the study, because an insufficient amount of reliable data is available to conduct validation.
 The correlations for flame height and time to ignition were not included in the validation study.
@@
 There are 53 zone models listed, but only three are actively supported or maintained.
-The survey also includes 22 field models of which 10 are listed as being actively supported.
-All of the correlations and models have, to some extent, been validated or checked against experimental data for a limited set of scenarios~\cite{ASTM_E1355}.
+The survey also includes 22 field models, of which 10 are listed as being actively supported.
+All of the correlations and models have been validated to some extent, or checked against experimental data for a limited set of scenarios~\cite{ASTM_E1355}.
 
@@
 
-However for fire models to be demonstrated as reliable and suitable for use in court, studies such as the one conducted here need to be conducted to provide the scientific basis for the use of fire models for re-construction.
-The research results may enable fire investigation teams to have a better understanding of the fire scene and enable improved support of their hypothesis on the area of origin based on fire patterns.
+In order for fire models to be demonstrated as reliable and suitable for use in court, studies such as the one conducted here need to be conducted to provide the scientific basis for the use of fire models for re-construction.
+These research results may enable fire investigation teams to have a better understanding of the fire scene and enable improved support of their hypothesis on the area of origin based on fire patterns.
 This idea was discussed when the Fire Protection Research Foundation convened a Research Advisory Council on Post-fire Analysis in 2002.
@@
 
-Given that fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
+Since fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
 Gorbett recently conducted a review of fire pattern research that has been conducted over the last 80 years.
@@
 A key limitation is the assumption by many of the researchers, or text authors, that investigators are able to visibly assess varying degrees of fire damage and then determine the area of origin~\cite{Gorbett_2015}.
-Studies have shown that investigators have not been able to use only the location of the fire patterns as means of reliably determining the area of origin, some amount of analysis and fire dynamics knowledge is required~\cite{Carmen_2008},~\cite{Tinsley_2013}.
+Studies have shown that investigators have not been able to use only the location of the fire patterns as means of reliably determining the area of origin.
+Some amount of analysis and fire dynamics knowledge is required~\cite{Carmen_2008},~\cite{Tinsley_2013}.
 
@@
 As the result of the review of several arson cases, most notably the cases of Ernest Ray Willis and Cameron Todd Willingham, the practice of fire investigation as a forensic science was called into question.
-Beyler conducted a review of both cases for the Texas Forensic Science Commission.
+Beyler conducted a review of both cases for the Texas Forensic Science Commission~\cite{Beyler:2009}.
 Both fires occurred prior to the release of NFPA~921 in 1992.
@@
 
-Given that the majority of intentional fires in structures occurred in residential occupancies, this study will focus on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupancies.
+The majority of intentional fires in structures have occurred in residential occupancies, therefore this study focused on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupancies.
 A common height for a residential occupancies is 2.4~m in height.
-With a wall height of 2.4~m, these experiments will use small fires with mean flame heights of approximately 1.2~m.
+With a wall height of 2.4~m, these experiments used small fires with flame heights of approximately 1.2~m.
 The resulting patterns on the gypsum board wall would be representative of a pre-flashover fire pattern.
@@
 
-This study includes several series of real-scale, replicate fire experiments to examine the repeatability of pre-flashover fire patterns, and ultimately examine the ability of simple correlations and the Fire Dynamic Simulator to recreate characteristics of the fire patterns.
+This study includes several series of real-scale, replicate fire experiments to examine the repeatability of pre-flashover fire patterns and, ultimately, examine the ability of simple correlations and the Fire Dynamic Simulator to recreate characteristics of the fire patterns.
 
@@
 The analysis ensured that the appropriate number of replicate experiments were conducted to provide an assessment of burn pattern repeatability within a given level of uncertainty.
-Given that the coefficient of variation (COV) may be different for a given type of experiment, the number of replicates required would be larger for experiments with a larger COV in order obtain a valid assessment of repeatability.
+Since the coefficient of variation (COV) may be different for a given type of experiment, the number of replicates required would be larger for experiments with a larger COV in order obtain a valid assessment of repeatability.
 
@@
 The fires were initially placed at predetermined, fixed positions away from the wall.
-The burner was moved toward the wall until the burner was against the wall.
+The burner was moved closer toward the wall until the burner was against the wall.
 
@@
 The fires were initially placed at predetermined, fixed positions away from the wall.
-The burner was moved toward the wall until the burner was against the wall.
+The burner was moved closer toward the wall until the burner was against the wall.
 If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
@@
 These experiments used the same test compartment as the wall fire pattern experiments.
-In these cases the fire was located against both walls in a corner of the compartment.
+In these cases, the fire was located against both walls in a corner of the compartment.
 The experimental process was the same as the wall fire pattern experiments.
@@
 
-Cone calorimeter, ASTM~E1354, experiments were conducted to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
+Cone calorimeter experiments were conducted, based on ASTM~E1354, to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
 
@@
 FDS~\cite{McGrattan:2014} and Smokeview~\cite{Forney:2014} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
-These simulation tools provide results in the form of visual field data, in other words they provide results in the same format that the investigator would see or document the fire pattern.
+These simulation tools provide results in the form of visual field data.
+In other words they provide results in the same format that the investigator would see or document the fire pattern.
 Comparison between the experiments and the model may provide valuable validation data for the model.
@@
 Point measurements were reduced and compared with values from the literature on fire plumes and their interaction with vertical surfaces.
-The heat release rates, heat flux measurements, flame and surface temperatures were used as input for heat transfer analysis to develop empirical coefficients for the specific experimental arrangements which would be useful in the model recreations.
+The heat release rates, heat flux measurements, and flame and surface temperatures were used as input for heat transfer analysis to develop empirical coefficients for the specific experimental arrangements, which would be useful in the model recreations.
 The key measurements for repeatability of the fire patterns on the gypsum wallboard are height, maximum width, shape, and area.
@@
 
-A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover or early growth stage fires.
-A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
+A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover, or early growth stage, fires.
+A fixed fire source footprint, a 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
 The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.
@@
 Therefore the heat content of the gas was monitored and mass flow controlled to provide a heat release rate based on fuel mass flow for comparison with the heat release rate values measured with the calorimeter.
-The gas burner arrangement provides the most idealized fire, in that it can be ignited and brought up to a near steady state heat release rate within a few seconds and then be shut down just as quickly.
+The gas burner arrangement provided the most idealized fire, in that it could be ignited and brought up to a near steady state heat release rate within a few seconds and then be shut down just as quickly.
 This provided an approximate `square wave' exposure to the gypsum wallboard.
@@
 
-The natural gas burner was 30.5~cm on a side and the top surface of the burner was 7.5~cm above the floor.
-The shell of the burner was made from steel and filled with ``pea sized'' gravel with an average diameter of 6~mm.
+The natural gas burner measured 30.5~cm on each side and the top surface of the burner was elevated 7.5~cm above the floor.
+The shell of the burner was made from steel and was filled with ``pea sized'' gravel with an average diameter of 6~mm.
 A steady state heat release rate of approximately 80 kW was used for the experiments.
@@
 Gasoline is not an ideal fuel to use in experiments because it is a mixture of components and additives that are specific to manufacturers.
-In addition the mixtures change from season to season, and vary based on requirements or restrictions of the locality.
+In addition, the mixtures change from season to season, and vary based on requirements or restrictions of the locality.
 However, fire incident data shows that gasoline was the first item ignited in the majority of intentional fires where flammable or combustible liquids were used~\cite{Rohr:2001}.
@@
 The pan was constructed from 6~mm thick steel.
-The inner dimension of the pan was 30.5~cm on a side and 1.9~cm high.
+The inner dimensions of the pan were 30.5~cm on each side and 1.9~cm high.
 The pan was elevated in order to bring the pan lip height up to 7.5~cm above the floor to be the same height as the natural gas burner.
@@
 every year~\cite{Foam,Polyurethane_Foam}.
-In studies by Ahrens and Evarts of the NFPA, upholstered furniture and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
+In studies by Ahrens and Evarts of the NFPA, upholstered furniture, and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
 based on averaged data from 2005 through 2009~\cite{Ahrens:2011,Evarts:2011}.
@@
 The flexible polyurethane foam had a density of approximately 23~kg/m$^3$.
-Each block of foam was 30.5~cm on a side and was 7.5~cm thick.
+Each block of foam was 30.5~cm on each side and was 7.5~cm thick.
 The bottom and sides of the foam block were wrapped in aluminum foil to prevent the fuel from flowing or spreading as it burned to ensure that the fuel area remained with the same fixed area as the gasoline and natural gas.
@@
 
-On each fuel’s averaged heat release rate curve, the shaded area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+On the averaged heat release rate curve for each fuel, the shaded area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
@@
 
+the data is plotted in the style used in FDS Validation
+
+continuous flame region 
+intermittant flame region
+plume region
+
 \begin{figure}[ht!]
@@
 \chapter{Future Research Needs}
+
+steep thermal gardiant
 

### 2016-10-04 Projects/DelCo_2012/Report/DelCo_2012.tex
Added majority of Nelson's edits to CAF report

@@
 \vspace*{2\baselineskip}
-August 2016}
+October 2016}
 
 \vspace*{2\baselineskip}
-{\em $^+$\small Currently with JENSEN HUGHES}
+{\em $^+$\small Currently with JENSEN HUGHES, Baltimore MD}
 \\
-{\em $^*$\small Currently with UL FSRI}
+{\em $^*$\small Currently with Underwriters Laboratories Firefighter \\ 
+Safety Research Institute, Columbia MD}
 }
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (August 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (October 2016) \\
 CODEN: NTNOEF }
@@
 \item  Perform a literature review of available published information on the use of CAF for structural fire fighting~\cite{Mitchell:1}
-\item  Conduct a workshop that brings interested and experienced parties together to discuss CAF experience and to provide guidance on the proposed experimental research plan~\cite{Grant:2011} 
+\item  Conduct a workshop that brings interested and experienced parties together to discuss CAF experience and to provide input on the proposed experimental research plan~\cite{Grant:2011} 
 \item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural fire fighting
@@
 When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
-The foams enhanced the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allowed the water to penetrate absorbent fuels.
-These enhancements also make the agents valuable tools for mop-up.
+The foams enhanced the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allowed the water to penetrate adsorbent fuels.
+These enhancements also make the agents valuable tools for mop-up or overhaul.
 The other experiments conducted during this study---specific heat, drop size, wood crib suppression, smoke generation, and Class D fire suppression---yielded similar results for both Class A foams and plain water.
@@
 In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAF during structure fires and to report back his findings and recommendations.
-That order was the catalyst for this study.
+That order was a catalyst for this study.
 
@@
 After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package that was composed mainly of wood-based materials.
-The thinking was that the synthetic materials in the upholstered furniture burned only on the surface and were easily extinguished.
-wood-based fuels would char and present a deep seated fire challenge to the extinguishing agents.
+The logic was that the synthetic materials in the upholstered furniture burned only on the surface and were easily extinguished.
+Wood-based fuels would char and present a deep seated fire challenge to the extinguishing agents.
 After the wood-based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
@@
 The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
-These are automatic nozzles which have a 7/8~inch slug-tip and can be varied from a straight stream to a wide fog stream for application.
-The setup also included 100~ft of 1-3/4~inch hose.
+These are automatic nozzles which have a 7/8~inch (22~mm) slug-tip and can be varied from a straight stream to a wide fog stream for application.
+The setup also included 100~ft (30.5~m) of 1-3/4~inch (44~mm) hose.
 Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
@@
 Foam         & 0.3\% foam concentration \\
-Pressure     & Water and Air pressure of 100 - 120~psi \\
+Pressure     & Water and Air pressure of 100--120~psi (689--827~kPa)\\
 \bottomrule[1.25pt]
@@
 The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board.
-The ceiling of the burn room was the exposed ``floor assembly".
+The ceiling of the burn room was the exposed ``floor assembly''.
 The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum board.
@@
 The studs were set to 0.40~m (16~in) centers.
-The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) durarock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
 The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
@@
 
-The structures were instrumented for temperature, gas velocity, and heat flux measurements.
+The structures were instrumented for gas temperature, gas velocity, and heat flux measurements.
 Gas temperatures in the burn rooms were measured with bare-bead, Chromel-Alumel (type K) thermocouples.
@@
 The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
-The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 1~m (3~ft) above the floor on the 2nd floor level in front of the stairway door.
+The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 1~m (3~ft) above the floor on the second floor level in front of the stairway door.
 Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
@@
 As mentioned in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results because due to the array's position, it was impacted the least by agents hitting and cooling the thermocouples themselves.
-Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is doing the work.
+Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is absorbing the energy from the upper layer.
 Air filled bubbles in the CAF stream had no discernible impact, either positive or negative, in the gas cooling experiments.
@@
 
-The data and results from this test series do not support the premise of firefighters being injured during an interior fire fighting operation with CAF because CAF provided cooling similar to that of the equivalent flow rate of plain water.
+The data and results from this test series are not consistent with a hypothesis that firefighters were being injured during an interior fire fighting operation with CAF because CAF provided cooling similar to that of the equivalent flow rate of plain water.
 
@@
 The required flow rate for the fire room in the lower level of the two-story would be approximately 700~l/min (184~gpm).
-Comparing the hose stream flow rates to the NFA Formula requirements indicates that 454~l/min (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~l/min (184~gpm) for the large fire compartment in the two-story structure.
+Comparing the hose stream flow rates to the NFA formula requirements indicates that 454~l/min (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~l/min (184~gpm) for the large fire compartment in the two-story structure.
 This is not consistent with the observations of a rapid fire knockdown with both water and CAF hose streams flowing 454~l/min (120~gpm).
@@
 
-During the workshop conducted for this project~\cite{Grant:2011}, there were discussions that CAF could suppress, or knockdown, a fire three to five times faster than water.
-During the course of this study, there were no significant differences demonstrated between CAF and water for use in interior structural fire fighting on a residential scale.
+During the workshop conducted for this project~\cite{Grant:2011}, it was suggested that CAF could suppress, or knockdown, a fire three to five times faster than water.
+The data collected during this study does not demonstrate significant differences between CAF and water for use in interior structural fire fighting on a residential scale.
 Going back to the premise of the study, preventing firefighters from being injured during interior fire fighting operations with CAF, there is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
@@
 One of the challenges with suppression research or determining the required flow rate of water needed on a building fire is the lack of data on realistic baseline requirements of the total amount of water needed for gas cooling and suppression.
-In this study, it seems clear that there was a sufficient amount of water for gas cooling and suppression.
+In this study, the data demonstrates that there was a sufficient amount of water for gas cooling and suppression.
 One question that arises is, how much could the flow rate of water have been reduced before a significant difference in performance was observed?
@@
 Information from actual incidents in the field shaped this study.
-From the gas cooling and suppression perspective, the results do not indicate that the use of CAF would result in a higher thermal hazard.
+From the gas cooling and suppression perspective, the results did not demonstrate significant differences between plain water and CAF.
 However, there are other issues like nozzle reaction force and flow separation which have been covered in the Cal Poly fire ground studies that can be addressed in training~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 It is important to provide adequate training when adopting a new method or new technology.
-Perhaps these types of issues should be examined further to better understand how suppression activities take place in the field.
+These types of issues should be examined further to better understand how suppression activities take place in the field.
 
@@
 It is possible that some of the discomfort or injuries that firefighters experience during interior fire fighting could be the result of a poor choice of nozzle or nozzle movement that results in displacing hotter gases into the area where the firefighter is located.
-Currently the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
+Currently, the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
 A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how such choices can impact the flow of gases within the structure.
-Based on the results of this study, it appears that training and understanding the impact of nozzle movement are ways to look for a more effective use of water.
+Based on the results of this study, it appears that training and understanding the impact of nozzle movement may be potential paths to more effective use of water.
 
@@
 The experimental configurations were designed to be representative of residential fire scenarios.
-The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
+%The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
 This same department also experienced injuries to firefighters while using CAF during interior fire fighting operations in residential structures.

### 2016-10-04 Projects/DelCo_2012/Report/DelCo_2012.tex
minor edits to CAFS

@@
 This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on fire fighting tactics.
-These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting with the objective of enhancing the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting.
+These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting.
+The objective is to enhance the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting.
 This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 
-A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting due to operational challenges or due to lack of understanding related to fireground safety issues.
+A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting.
+This is due to operational challenges or due to lack of understanding related to fireground safety issues.
 This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural fire fighting through the various tasks associated with this project, including:
@@
 Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}.
-That study examined a broad range of tests in order to determine those parameters that most critically effect fire fighting performance.
+That study examined a broad range of tests to determine those parameters which most critically effect fire fighting performance.
 The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.

### 2016-10-09 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added draft discussion on wall construction

@@
 
-Impact of Instrumentation on Walls?
-
-Impact of Wall Construction
-
-Comparison of Fire Patterns and Flame Heights
+\section{Comparison of Fire Patterns and Flame Heights}
+
+\subsection{Impact of Instrumentation on Walls}
+
+Compare flame height results IGWB with Fire Pattern Experiments
+
+\subsection{Impact of Wall Construction}
+
+In these experiments, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
+The results from the instrumented gypsum wallboard experiments in Chapter 4, which respresented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
+The corresponding peak temperatures on the face of the gypsum wall board ranged from the    ~$^\circ$C.
+This demonstrates the insulatative capability of the gypsum wallboard.
+Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.
+
+steep thermal gradiant
+
+Therefore with the limited fire exposure time of approximately 300~seconds, and the small, pre-flashover fires used in this study the
 
@@
 
-\subsection{The Fire Investigators' Challenge}
+\subsection{Modeling Results}
+
+\section{The Fire Investigators' Challenge}
 
@@
 \chapter{Future Research Needs}
-
-steep thermal gardiant
 

### 2016-10-10 Projects/DelCo_2012/Report/DelCo_2012.tex
minor updates from JH review to CAFS

@@
 \hspace{1.5in} \= \\
+BDP \> Bi-Directional Probe \\
 CAF \> Compressed Air Foam \\
@@
 Cal Poly \> California Polytechnic State University, San Luis Obispo \\
+DHS \> Department of Homeland Security \\
+FEMA \> Federal Emergency Management Administration \\
+HF \> Heat Flux \\
+IDLH \> Immediate Danger to Life and Health \\
 ESTC \> Delaware County Emergency Services Training Center \\
@@
 NIST \> National Institute of Standards and Technology \\
+OSB \> Oriented Strand Board \\
+TC \> Thermocouple \\
 TFT \> Task Force Tips \\
+TJI \> Trust Joist I-Joist \\
+UL FSRI \> UL Firefighter Safety Research Institute \\
+
 \end{tabbing}
@@
 
-This study, conducted by NIST, was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study, conducted by the National Institute of Standards and Technology (NIST), was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
 This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
@@
 One of the objectives of this program is to examine non-traditional means of fire suppression.
-This series of experiments conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service complements the NIST research program on fire fighting tactics.
+This series of experiments was conducted by NIST for the California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+It complements the NIST research program on fire fighting tactics.
 These experiments are part of a larger research project led by Cal Poly with the purpose of investigating the capabilities and limitations of compressed air foam systems (CAFS) for structural fire fighting.
 The objective is to enhance the scientific knowledge base regarding the effectiveness and safety implications associated with the use of CAFS for structural fire fighting.
-This project was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
-
-A number of fire departments throughout the US have acquired CAFS units for structural fire fighting, but many have limited or stopped the use of these CAFS for structural fire fighting.
+This project was supported in part by a Department of Homeland Security/Federal Emergency Management Administration (DHS/FEMA) Assistance to Firefighters Research and Development Grant.
+
+A number of fire departments throughout the US have acquired CAFS units for structural fire fighting.
+Many have limited or stopped the use of these CAFS for structural fire fighting.
 This is due to operational challenges or due to lack of understanding related to fireground safety issues.
@@
 The wildland fire community found that the Class A foam reduced the surface tension of water, which improved the water's ability to penetrate and soak into wildland fuels.
-A CAFS could turn a Class A foam solution into a blanket of bubbles that would allow the wildland firefighters to coat the fuels.
+A CAFS could turn a Class A aqueous solution into an aerated form (a blanket of bubbles) that would allow the wildland firefighters to coat the fuels.
 The additional ``soak'' time provided by the foam layer allowed the water to penetrate the hot surface of a burning fuel and also provided additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
@@
 CAF increases the effectiveness of water and may reduce the quantity required to suppress fires and prevent the ignition of adjacent fuels.
-Finally, the compressed air adds energy to the water stream, providing additional reach and volume to a hose stream with a relatively low mass flow rate of water.
+Finally, the compressed air adds energy to the water stream, providing additional reach to a hose stream with a relatively low mass flow rate of water.
 These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire or can be used for an exterior (indirect) fire suppression attack on a structure.
@@
 Yet, after decades of fire department trials, CAF has still not been widely incorporated into structural fire fighting tactics~\cite{USFA:CAFS,Lorh:2002}.
-This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, had issued an order that the CAFS should not be used after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
+This is illustrated by the example of one community, which after putting a fleet of CAFS equipped fire engines into service, issued an order that the CAFS should not be used.
+The order was issued after incidents occurred where firefighters were burned while performing interior suppression operations with CAF inside a structure.
 
 There has never been a comprehensive scientific study on the use of CAF for structural fire fighting.
-Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF; foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures; and test laboratories and universities have examined small sections of the CAF puzzle, but none of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
+Fire departments have conducted pilot programs to examine implementation and effectiveness of CAF; foam suppliers and equipment manufacturers have conducted minimally instrumented experiments, typically in acquired structures; and test laboratories and universities have examined small sections of the CAF puzzle.
+None of these efforts has resulted in the body of knowledge needed by the fire service~\cite{Madrzykowski:3,USFA:CAFS,Colletti:1,Boyd:1,Tafreshi:1,Madrzykowski:4,Colletti:2,Tafreshi:2,Lorh:2002,Colletti:3,Kim:2012}.
 
@@
 \centering
-\captionof{table}{Tests to Assess Fire Fighting Agents Compared to Water}\label{tab:agent_tests}
+\captionof{table}{Tests to Assess CAF Fire Fighting Agent Compared to Water}\label{tab:agent_tests}
 \begin{tabular}{lcc}
@@
 Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle; cooling and penetrating wood-based fuels; mass retention on the wood fuels; and ignition inhibition of the wood fuels.
-When applied in the form of foam, the water agent solutions provide enhanced radiation exposure protection to a structure relative to plain water.
+When applied in the form of foam, the aqueous solutions provide enhanced radiation exposure protection to a structure relative to plain water.
 The foams enhanced the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allowed the water to penetrate adsorbent fuels.
@@
 In 2005, The National Fallen Firefighters Foundation held the National Fire Service Research Agenda Symposium.
-One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland fire fighting, CAFS is typically applied directly to the fuel from a remote location, typically a non-IDLH environment.
+One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland fire fighting, CAFS is typically applied directly to the fuel from a remote location, typically an environment that is not an immediate danger to life and health (non-IDLH environment).
 In structural fire fighting, crews typically have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.

### 2016-11-21 Projects/DelCo_2012/Report/DelCo_2012.tex
JH edits up to pg. 45 of CAF report

@@
 \vspace*{2\baselineskip}
-October 2016}
+December 2016}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (October 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (December 2016) \\
 CODEN: NTNOEF }
@@
 Technical panel members whose departments routinely use CAF for structural fire fighting were invited and present at many of the fire suppression experiments.
-The experiments were planned during the workshop.
+The experiments were planned during the workshop~\cite{Grant:2011}.
 Three types of experiments examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
@@
 The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
-These are automatic nozzles which have a 7/8~inch (22~mm) slug-tip and can be varied from a straight stream to a wide fog stream for application.
-The setup also included 100~ft (30.5~m) of 1-3/4~inch (44~mm) hose.
+These are automatic nozzles which have a 22~mm (0.88~in) slug-tip and can be varied from a straight stream to a wide fog stream for application.
+The setup also included 30.5~m (100~ft) of 44~mm (1.75~in) diameter hose.
 Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
@@
 \midrule
-Nozzle       & Metro 1, fixed gallonage fog, straight, or 7/8~inch solid stream \\
-Hoseline     & 100~ft of 1-3/4~inch hoseline \\
+Nozzle       & Metro 1, fixed gallonage fog, straight, or 44~mm (0.88~in) solid stream \\
+Hoseline     & 30.5~m (100~ft) of 44~mm (1.75~inch) diameter hoseline \\
 Foam         & 0.3\% foam concentration \\
-Pressure     & Water and Air pressure of 100--120~psi (689--827~kPa)\\
+Pressure     & Water and Air pressure of 689--827~kPa (100--120~psi) \\
 \bottomrule[1.25pt]
@@
 	\includegraphics[width=6in]{../Figures/Pictures/Flows}
-	\caption{Spray Density Nozzle Patterns}
+	\caption[Spray Density Nozzle Patterns]{Spray Density Nozzle Patterns (Left-To-Right: Straight Stream, Narrow Fog Stream, and Solid Stream)}
 	\label{fig:Spray_Density_Nozzle_Patterns}
@@
 The six experiments in the two-story structure used both water and CAF from a straight stream nozzle.
-In addition two CAF experiments were conducted in the two-story with a solid stream.
+In addition, two CAF experiments were conducted in the two-story burn building with a solid stream.
 
@@
 The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile.
-The floor of the burn rooms was protected with fire brick.
-Tests were conducted in the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
+The floors of the burn rooms were protected with fire brick.
+Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
 
@@
 The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.125~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web.
+The TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web.
 Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was attached to the top of the TJIs.
@@
 The ceiling of the burn room was the exposed ``floor assembly''.
-The walls of the hallway and entry foyer were composed of 16~mm (0.625~in) Type X gypsum board.
+The walls of the hallway and entry foyer were composed of 16~mm (0.63~in) Type X gypsum board.
 The ceiling of the hallway and entry foyer was composed of two layers of 13~mm (0.5~in) thick cement board.
@@
 
-The west structure was modified to add a second story to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
+A second story was added to the west single-story structure in order to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
 
@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple was protected with an 3.2~mm (0.125~in) diameter inconel sheath.
+The thermocouple was protected with an 3.2~mm (0.13~in) diameter inconel sheath.
 The sheathing protects the thermocouple from water but slows the response time because of the additional thermal mass.
@@
 Hay from bales averaging a mass of 12~kg (26~lb) was added for ignition purposes.
+The specific locations of the fuel load's contents can be found in the dimensioned schematic Figure~\ref{fig:pallet_furniture_2story}.
 
@@
 The interior of the fire room in the single-story structure was sheathed in plastic for the spray density tests to protect the gypsum board from being soaked with water prior to the fire suppression experiments.
-The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm for CAF.
+The flow rate for each test was 120~gpm for water and 120~gpm plus 60~cfm air for CAF.
 Tables~\ref{tab:spray_density_tests} and \ref{tab:spray_density_tests2} provide an overview of each experiment.
 In the table, ``GC'' stands for the gas cooling experiments, and ``SE'' stands for the suppression experiments.
-For all experiments, 30~m (100~ft) of 1~3/4~inch hoseline connected to a ``blitz-fire'' monitor with a Metro 1 nozzle was used.
+For all experiments, 30~m (100~ft) of 4.45~cm (1.75~in) diameter hoseline connected to a ``blitz-fire'' monitor with a Metro 1 nozzle was used.
 
@@
 GC5        &  20            & Water  &  Straight Stream 	& Mid              \\
-GC6        &  21            & Water  &  30$^{\circ}$ Fog   & Mid              \\
-GC7        &  20            & Water  &  30$^{\circ}$ Fog   & Mid              \\
-GC8        &  22            & Water  &  30$^{\circ}$ Fog   & Back             \\
-GC9        &  24            & Water  &  30$^{\circ}$ Fog   & Back             \\
+GC6        &  21            & Water  &  Narrow Fog   		& Mid              \\
+GC7        &  20            & Water  &  Narrow Fog   		& Mid              \\
+GC8        &  22            & Water  &  Narrow Fog   		& Back             \\
+GC9        &  24            & Water  &  Narrow Fog   		& Back             \\
 GC10       &  20            & Water  &  Solid Stream       	& Back             \\
@@
 GC15       &  20            & CAF    &  Solid Stream       	& Mid              \\
-GC16       &  15            & CAF    &  30$^{\circ}$ Fog   & Mid              \\
+GC16       &  15            & CAF    &  Narrow Fog   		& Mid              \\
 GC17       &  20            & CAF    &  Straight Stream    	& Mid             \\
 GC18       &  10            & CAF    &  Straight Stream    	& Mid             \\
-GC19       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
-GC20       &  15            & CAF    &  30$^{\circ}$ Fog   & Back             \\
+GC19       &  15            & CAF    &  Narrow Fog   		& Back             \\
+GC20       &  15            & CAF    &  Narrow Fog   		& Back             \\
 GC21       &  15            & CAF    &  Straight Stream    	& Back             \\
-
 \bottomrule[1.25pt]
@@
 SE4        & 21            & Water  &  Straight Stream    &    Fire Room          \\
-SE5        & 22            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
-SE6        & 19            & Water  &  30$^{\circ}$ Fog   &    Fire Room          \\
+SE5        & 22            & Water  &  Narrow Fog  		  &    Fire Room          \\
+SE6        & 19            & Water  &  Narrow Fog   	  &    Fire Room          \\
 SE7        & 16            & Water  &  Solid Stream       &    Fire Room          \\
 SE8        & 17            & Water  &  Solid Stream       &    Hallway            \\
-SE9        & 15            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
-SE10       & 16            & Water  &  30$^{\circ}$ Fog   &    Hallway            \\
+SE9        & 15            & Water  &  Narrow Fog   	  &    Hallway            \\
+SE10       & 16            & Water  &  Narrow Fog   	  &    Hallway            \\
 SE11       & 16            & Water  &  Straight Stream    &    Hallway            \\
@@
 	\includegraphics[width=4in]{../Figures/Bars/BB7}
-	\caption{Gas Cooling Spray Density Test 7, 30 $^{\circ}$ Fog} 
+	\caption{Gas Cooling Spray Density Test 7, Narrow Fog} 
 	\label{fig:Burn_Building_Test_7}
@@
 Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively.
-For both sets, a solid 7/8~in.
-nozzle in the middle position was used.
+For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used.
 The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3).
@@
 
-To better quantify the effectiveness of the suppression agents (CAF and water), the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
+To better quantify the effectiveness of the suppression agents, the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
 Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments.
-The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, which were directly comparable (see Table~\ref{tab:Gas_Cooling_Descriptions}).
-These experiments included solid stream, straight streams, and narrow fog streams at both nozzle positions.
+The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, that were directly comparable (see Table~\ref{tab:Gas_Cooling_Descriptions}).
+These experiments included solid streams, straight streams, and narrow fog streams at both nozzle positions.
 While the total number of experiments was 88, there were a number of experiments that did not have a directly comparable experiment between water and CAF.
-For example, a set of 12 Class A solution experiments were conducted.
-Gas cooling experiments were also conducted with water applied in a wide fog stream.
-Since no significant differences were noted compared to the narrow fog stream experiments, a comparable series with a wide fog CAF was not conducted.
-Similarly, larger water flows were examined, but 120 gpm was the maximum water flow that could be generated with the CAFS, so those experiments are also not included in this comparison.
+For example, 12 of the experiments used Class A solution as the suppression agent.
+Furthermore, gas cooling experiments were conducted with water applied in a wide fog stream, but no experiments with CAF applied in a wide fog stream were conducted because no significant differences were noted between CAF and water in the narrow fog stream experiments.
+Similarly, larger water flows were examined, but 120 gpm was the maximum water flow that could be generated with the CAFS.
+So, those experiments are also not included in this comparison.
 The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}.
@@
  29              & 12               &  Straight Stream    &  Full Back   \\
- 33              & 13               &  30$^{\circ}$ Fog   &  Full Back   \\
- 34              & 14               &  30$^{\circ}$ Fog   &  Full Back   \\
+ 33              & 13               &  Narrow Fog   	  &  Full Back   \\
+ 34              & 14               &  Narrow Fog   	  &  Full Back   \\
 \bottomrule[1.25pt]
@@
 Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it.
-However, we must remember that the thermocouple is actually providing us with its own temperature.
-So if a droplet of water or some CAF cling to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.
+However, the thermocouple is actually measuring its own temperature.
+So, if a droplet of water or some CAF clings to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.
 
@@
 This analysis of the data results in the same conclusions as the analysis from the Mitchell paper \cite{Mitchell:1}: the gas cooling performance of CAF is similar to water under these conditions.
+Or, more accurately, water is nearly always equal to or better than CAF.
 
@@
 \midrule
- 1 & CAF~1    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
- 2 & Water~1  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door            \\
+ 1 & CAF~1    &  Narrow Fog   &  120~gpm/60~cfm   & Furniture      & Door            \\
+ 2 & Water~1  &  Narrow Fog  	&  120~gpm    		& Furniture      & Door            \\
  3 & CAF~2    &  Solid Stream       &  120~gpm/60~cfm   & Furniture      & Door            \\
  4 & Water~2  &  Solid Stream       &  120~gpm    		& Furniture      & Door            \\
- 5 & Water~3  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 6 & CAF~3    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
- 7 & Water~4  &  30$^{\circ}$ Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
- 8 & CAF~4    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
- 9 & Water~5  &  30$^{\circ}$ Fog  	&  120~gpm   		& Wood           & Door + Window   \\
-10 & CAF~5    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
-11 & Water~6  &  30$^{\circ}$ Fog  	&  120~gpm    		& Wood           & Door + Window   \\
-12 & CAF~6    &  30$^{\circ}$ Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+ 5 & Water~3  &  Narrow Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+ 6 & CAF~3    &  Narrow Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 7 & Water~4  &  Narrow Fog  	&  120~gpm    		& Furniture      & Door + Window   \\
+ 8 & CAF~4    &  Narrow Fog   &  120~gpm/60~cfm   & Furniture      & Door + Window   \\
+ 9 & Water~5  &  Narrow Fog  	&  120~gpm   		& Wood           & Door + Window   \\
+10 & CAF~5    &  Narrow Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
+11 & Water~6  &  Narrow Fog  	&  120~gpm    		& Wood           & Door + Window   \\
+12 & CAF~6    &  Narrow Fog   &  120~gpm/60~cfm   & Wood           & Door + Window   \\
 \bottomrule[1.25pt]
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
-	\label{fig:fs_hall_a1}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
-	\label{fig:fs_door_a1}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
+% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
+% 	\label{fig:fs_hall_a1}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
+% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
+% 	\label{fig:fs_door_a1}
+% \end{figure}
 
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
-	\label{fig:fs_hall_a2}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
-	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
-	\label{fig:fs_door_a2}
-\end{figure}
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
+% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
+% 	\label{fig:fs_hall_a2}
+% \end{figure}
+
+% \begin{figure}[!ht]
+% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
+% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
+% 	\label{fig:fs_door_a2}
+% \end{figure}
 

### 2016-11-21 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated figures based on JH + Nelson edits

@@
 	\includegraphics[width=6in]{../Figures/Pictures/Flows}
-	\caption[Spray Density Nozzle Patterns]{Spray Density Nozzle Patterns (Left-To-Right: Straight Stream, Narrow Fog Stream, and Solid Stream)}
+	\caption[Spray Density Nozzle Patterns]{Spray Density Nozzle Patterns. Left-To-Right: Straight Stream, Narrow Fog Stream, and Solid Stream.}
 	\label{fig:Spray_Density_Nozzle_Patterns}
@@
 The floors of the burn rooms were protected with fire brick.
-Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft) (see Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout}).
+Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft).
+Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Plain}
-	\caption{Dimensioned Floor Plan Burn Building Layout}
+	\caption{Basic Floor Plan of the Burn Building Layout}
 	\label{fig:Delaware_County,_PA_Burn_Building_Layout}
@@
 The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide.
-A dimensioned, plan view of the structure is included in Figure~\ref{fig:Test_Structure_Floor_Plan}.
+A basic plan view of the structure is presented in Figure~\ref{fig:Test_Structure_Floor_Plan}, and a fully dimensioned plan view of the structure is included in in Appendix~\ref{app:floor_plans}.
 
@@
 	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Plain}
-	\caption{Dimensioned Floor Plan of the Test Structure}
+	\caption{Basic Floor Plan of the Single-Story Test Structure}
 	\label{fig:Test_Structure_Floor_Plan}
@@
 	\includegraphics[width=6in]{../Figures/Pictures/DelCo}
-	\caption{Delaware County, PA Fire Two-Story Test Structure}
+	\caption{Delaware County, PA Two-Story Fire Test Structure}
 	\label{fig:delco_2story}
@@
 The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-Figure~\ref{fig:dimensioned_first_2story} shows the dimensions of the reconfigured first floor.
-A stairwell was built to connect the floors.
-Stairs started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
+Figure~\ref{fig:dimensioned_first_2story} shows a basic floor plan of the reconfigured first floor.
+A fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
+A stairwell was built to connect the two floors of the structure.
+The stairs had a 180~mm (7.25~in) rise and 190~mm (7.5~in) run and started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
 The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs.
@@
 The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
-Figure~\ref{fig:dimensioned_second_2story} shows the dimensions of the second story of the modified west structure.
+Figure~\ref{fig:dimensioned_second_2story} shows a basic floor plan of the second story of the modified west structure, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
 
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
-	\caption{Dimensioned Floor Plan of First Floor of Two-Story Structure}
+	\caption{Basic Floor Plan of the First Floor of the Two-Story Structure}
 	\label{fig:dimensioned_first_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
-	\caption{Dimensioned Floor Plan of Second Floor of Two-Story Structure}
+	\caption{Basic Floor Plan of the Second Floor of the Two-Story Structure}
 	\label{fig:dimensioned_second_2story}
@@
 Each of the bare-bead thermocouple arrays had 11 thermocouples.
-The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10ft) below the ceiling.
-There were 6 velocity probes and solid thermocouples centered at the external doorway to the gas cooling room.
-The top probes were 0.15~m (0.5~ft) below the door soffit, the second probes were 0.3~m (1~ft) below the soffit, and the remaining 4 were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
-The total heat flux gauge/radiometer set were positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10~ft) below the ceiling.
+There were six velocity probes and solid thermocouples centered at the external doorway to the gas cooling room.
+The top probe was 0.15~m (0.5~ft) below the door soffit, the second probe was 0.3~m (1~ft) below the soffit, and the remaining four were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
+The total heat flux gauge/radiometer set was positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
 
@@
 
-The fire suppression testing in the single-story structure included 2 bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, 2 total heat flux gauge pairs, and 2 total heat flux gauge/radiometer pairs.
-Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the senors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
-Each bare-bead thermocouple array had 8 thermocouples.
+The fire suppression testing in the single-story structure included two bare-bead thermocouple arrays, three bi-directional probe plus solid thermocouple arrays, two total heat flux gauge pairs, and two total heat flux gauge/radiometer pairs.
+Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} provides the positions within the burn room, hallway, and entrance foyer where the sensors were located (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
+Each bare-bead thermocouple array had eight thermocouples.
 The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
@@
 For the window array, there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit.
-For the hallway array, the 7 sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling.
-The doorway array also had 7 sensor pairs, but the first sensors were located 0.15~m (0.5~ft) below the soffit.
+For the hallway array, the seven sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling.
+The doorway array also had seven sensor pairs, but the first pair was located 0.15~m (0.5~ft) below the soffit.
 The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit.
@@
 
-Fire suppression testing in the two-story structure included similar types of instrumentation but included more sensors.
-Three bare-bead thermocouple arrays and 2 bi-directional probe and thermocouples arrays were used in the first floor.
+Fire suppression testing in the two-story structure included similar types of instrumentation but with more sensors.
+Three bare-bead thermocouple arrays and two bi-directional probe and thermocouple arrays were used in the first floor.
 Figure~\ref{fig:fire_supp_first_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
-Each of the bare-bead arrays had 8 thermocouples with the same spacing as the single-story tests.
-The bi-directional probe and solid thermocouple arrays also had 8 sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
+Each of the bare-bead arrays had eight thermocouples with the same spacing as the single-story tests.
+The bi-directional probe and solid thermocouple arrays also had eight sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
 
@@
 Figure~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
-The bare-bead thermocouple arrays featured 8 sensors with the same spacing as the basement level.
-The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of 8 sensor pairs with the same spacing as the basement level.
-The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) has 8 sensor pairs with the same spacing at the bare-bead thermocouple arrays.
+The bare-bead thermocouple arrays featured eight sensors with the same spacing as the basement level.
+The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of eight sensor pairs with the same spacing as the ground level.
+The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) had eight sensor pairs with the same spacing at the bare-bead thermocouple arrays.
 
@@
 Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
-Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$ a) is essentially 100~\%.
+Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$~a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
@@
 Each length measurement was taken carefully.
-Length measurements, such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement, were made with a hand held laser measurement device that had an accuracy of $\pm$ 6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
-However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$ 0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
-Steel measuring tapes with a resolution of  $\pm$ 0.5~mm (0.02~in) were used to locate individual sensors within an instrumentation array and to measure and position the furniture.
-The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$ 1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$ 6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
-Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$ 1.0~\%.
+Length measurements, such as the room dimensions, instrumentation array locations, and fire apparatus (e.g., nozzle, sprinkler, or fan) placement, were made with a hand held laser measurement device that had an accuracy of $\pm$~6.0~mm (0.25~in) over a range of 0.61~m (2.0~ft) to 15.3~m (50.0~ft)~\cite{StanleyTools}.
+However, conditions affecting the measurement, such as levelness of the device, yields an estimated uncertainty of $\pm$~0.5~\% for measurements in the 2.0~m (6.6~ft) to 10.0~m (32.8~ft) range.
+Steel measuring tapes with a resolution of  $\pm$~0.5~mm (0.02~in) were used to locate individual sensors within an instrumentation array and to measure and position the furniture.
+The steel measuring tapes were manufactured in compliance with NIST Manual 44, which specifies a tolerance of $\pm$~1.6~mm (0.06~in) for 9.1~m (30~ft) tapes and $\pm$~6.4~mm (0.25~in) for 30.5~m (100~ft) tapes~\cite{Butcher:2012}.
+Some issues, such as ``soft'' edges on the upholstered furniture, result in an estimated total expanded uncertainty of $\pm$~1.0~\%.
 
 The load cell used to weigh the fuels prior to the experiments had a range of 0~kg (0~lb) to 200~kg (440~lb) with a resolution of a 0.05~kg (0.11~lb) and a calibration uncertainty within 1~\%~\cite{Ohaus:2000}.
-The expanded uncertainty is estimated to be less than $\pm$ 5~\%.
-
-The standard uncertainty in temperature of the thermocouple wire itself is $\pm$ 2.2 $^{\circ}$C at 277 $^{\circ}$C and increases to $\pm$ 9.5~$^{\circ}$C at 871~$^{\circ}$C as determined by the wire manufacturer\cite{Omega:2004}.
+The expanded uncertainty is estimated to be less than $\pm$~5~\%.
+
+The standard uncertainty in temperature of the thermocouple wire itself is $\pm$~2.2~$^{\circ}$C at 277~$^{\circ}$C and increases to $\pm$~9.5~$^{\circ}$C at 871~$^{\circ}$C as determined by the wire manufacturer~\cite{Omega:2004}.
 The variation of the temperature in the environment surrounding the thermocouple is known to be much greater than that of the wire uncertainty~\cite{Blevins:1999,Pitts:2003}.
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
-The estimated total expanded uncertainty for temperature in these experiments is $\pm$ 15~\%.
-
-In this study, total heat flux measurements were made with water-cooled Schimidt-Bolter gauges.
-The manufacturer reports a $\pm$ 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$ 8~\%~\cite{Pitts:2006}.
-
-The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k = 2) relative uncertainty of $\pm$ 1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$ 12~\% was applied to the results~\cite{Lock:1}.
+The estimated total expanded uncertainty for temperature in these experiments is $\pm$~15~\%.
+
+In this study, total heat flux measurements were made with water-cooled Schmidt-Boelter gauges.
+The manufacturer reports a $\pm$~3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge is typically $\pm$~8~\%~\cite{Pitts:2006}.
+
+The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k~=~2) relative uncertainty of $\pm$~1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$~12~\% was applied to the results~\cite{Lock:1}.
 
 Differential pressure reading uncertainty components were derived from pressure transducer instrument specifications and previous experience with pressure transducers.
-The transducers were factory calibrated and the zero and span of each were checked in the laboratory prior to the experiments, yielding an accuracy of $\pm$ 1~\%~\cite{Setra:2002}.
-The total expanded uncertainty is estimated at 10~\%.
+The transducers were factory calibrated and the zero and span of each were checked in the laboratory prior to the experiments, yielding an accuracy of $\pm$~1~\%~\cite{Setra:2002}.
+The total expanded uncertainty is estimated as $\pm$~10~\%.
 
@@
 Bare-bead Type K thermocouples are co-located with each probe.
-A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$ 0.14 to $\pm$ 0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
-The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm$ 18~\%.
+A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$~0.14 to $\pm$~0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
+The total expanded uncertainty for gas velocity in these experiments is estimated to be $\pm$~18~\%.
 
 Water flow rate was measured with a pressure and flow meter combination.
-The meter consists of a section of 6.35~cm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm).
+The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm).
 The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
-The manufacturer reports a $\pm$ 5~\% calibration expanded uncertainty for the flow sensor and $\pm$ 3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}.
+The manufacturer reports a $\pm$~5~\% calibration expanded uncertainty for the flow sensor and $\pm$~3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}.
 The pressure transducer was calibrated with a known analog pressure gauge.
 The flow meter was calibrated by capturing water over time and measuring that mass of water to determine the flow rate.
-The total expanded uncertainty is estimated at $\pm$ 10~\%.
+The total expanded uncertainty is estimated at $\pm$~10~\%.
 
@@
 
-The fuel load for test numbers 9 through 12 consisted of one bale of hay, twelve pallets, eleven and a half sheets of plywood on the walls, and the wood ``floor assembly''.
+The fuel load for test numbers 9 through 12 consisted of one bale of hay, 12 pallets, 11.5 sheets of plywood on the walls, and the wood ``floor assembly''.
 Two stacks of pallets with hay were used as the first items ignited in each experiment.
@@
 Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition.
-The pallets and hay were weighed prior to each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).
+The pallets and hay were weighed before each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).
 
@@
 	\includegraphics[width=0.65\columnwidth]{../Figures/Pictures/Wood_Fuel_Package}
-	\caption{Photograph of Southeast Corner of Burn Room with Wood Fuel Load}
+	\caption{Southeast Corner of Burn Room with Wood Fuel Load}
 	\label{fig:Wood_Fuel_Load}
@@
 	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
-	\caption{Wood Fuel Load in Single-Story Structure}
+	\caption{Wood Fuel Load Dimensions in Single-Story Structure}
 	\label{fig:Wood_Fuel_Load_Dimensions}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Only}
-	\caption{Furniture Fuel Load in First Floor of Two-Story Structure}
+	\caption{Furniture Fuel Load Dimensions in First Floor of Two-Story Structure}
 	\label{fig:furniture_2story}
@@
 	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Furniture_Pallets}
-	\caption{Furniture and Pallet Fuel Load in First Floor of Two-Story Structure}
+	\caption{Furniture and Pallet Fuel Load Dimensions in First Floor of Two-Story Structure}
 	\label{fig:pallet_furniture_2story}
@@
 The 88 gas cooling experiments were completed as part of nine separate burn sequences in the burn building.
-For detailed discussion on each of the individual events, please refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
+For detailed discussion on each of the individual events, refer to a prior analysis conducted by Mitchell \cite{Mitchell:1}.
 While Mitchell examined each individual experiment in detail, the results were mixed.
@@
 As a result, it remained dry and seems to provide the best representation of the gas cooling.
-
+`'
 \begin{figure}[ht!]
@@
 So, those experiments are also not included in this comparison.
-The Mitchell report includes the data for all 88 experiments \cite{Mitchell:1}.
+The Mitchell report includes the data for all 88 experiments~\cite{Mitchell:1}.
 
@@
 The data can be separated to examine the impact of nozzle position (back or middle position) on the ability to cool gases for each of the suppression agents.
-Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 pairs of experiments in the back position and 3 pairs of experiments in the middle position, respectively.
+Figures~\ref{fig:CAFS_Water_mid} and \ref{fig:CAFS_Water_full} show the cooling comparison for 12 pairs of experiments in the back position and three pairs of experiments in the middle position, respectively.
 
@@
 To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the fire room.
-Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
 Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it.
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Instrumentation2}
-	\caption{Schematic of  the Gas Cooling Experiments}
-	\label{fig:Gas_Cooling_Instrumentation_Dimensions2}
-\end{figure}
-
-Based on the monitor position (arrow at the doorway in Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions2}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
+Based on the monitor position (see Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
 As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the middle position compared to the positions of the thermocouple trees.
@@
 The fit lines for A1 and A3 also fall within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Thermocouple array A2, which gets the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF on cooling the thermocouples.
+Thermocouple array A2, which received the most significant direct impact from the suppression agents, shows a bias towards water being more effective than CAF on cooling the thermocouples.
 
@@
 
-The thermocouple array data can also be decomposed as a function of nozzle position: 12 middle position experimental pairs and 3 back experimental pairs.
+The thermocouple array data can also be decomposed as a function of nozzle position: 12 middle position experimental pairs and three back experimental pairs.
 Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position.
-Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 3 replicate tests with the monitor nozzle in the back position.
+Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the three replicate tests with the monitor nozzle in the back position.
 Again, note that the best fit occurs with the data from thermocouple array 3 for both nozzle positions.
@@
 Rekindling and the impact of the second nozzle can been seen in the time-temperature data of thermocouples within the fire room.
-Figure~\ref{fig:fs_instruments} shows the positions of thermocouple arrays TC A1 and TC A2.
+Figure~\ref{fig:Fire_Suppression_Instrumentation_Dimensions} shows the positions of thermocouple arrays TC A1 and TC A2.
 Note, TC A1 is closer to fuel and ignition.
-
-\begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Instrumentation2}
-	\caption{Schematic Indicating Thermocouple Arrays A1 and A2 for Fire Suppression Experiments}
-	\label{fig:fs_instruments}
-\end{figure}
 
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
-% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
-% 	\label{fig:fs_hall_a1}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
-% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
-% 	\label{fig:fs_door_a1}
-% \end{figure}
-
-In Figure~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, indicates near equal cooling between CAF and water.
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_hallnozzle_scatter}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Hallway Nozzle}
+	\label{fig:fs_hall_a1}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA1_doornozzle_scatter}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A1 after Door Nozzle}
+	\label{fig:fs_door_a1}
+\end{figure}
+
+In Figure~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, which indicates near equal cooling between CAF and water.
 The R$^2$ value of 0.901 shows a strong fit to the data.
 When the second nozzle (door nozzle) was activated, the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack.
-While the fit is not as strong (R$^2$ = 0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
+While the fit is not as strong (R$^2$~=~0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
 Despite being closer to the nozzles, thermocouple tree A2 shows similar temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a1}).
@@
 
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
-% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
-% 	\label{fig:fs_hall_a2}
-% \end{figure}
-
-% \begin{figure}[!ht]
-% 	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
-% 	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
-% 	\label{fig:fs_door_a2}
-% \end{figure}
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_hallnozzle_scatter}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Hallway Nozzle}
+	\label{fig:fs_hall_a2}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=.7\columnwidth]{../Figures/Script_Figures/TCA2_doornozzle_scatter}
+	\caption{CAF vs Water Temperature Difference Comparison for Single-Story Fire Suppression Tests at Thermocouple Array A2 after Door Nozzle}
+	\label{fig:fs_door_a2}
+\end{figure}
 
@@
 The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 1~m (3~ft) above the floor on the second floor level in front of the stairway door.
-Figure~\ref{fig:tcs_hf_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
+Figure~\ref{fig:fire_supp_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
 Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=.9\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Instrumentation2}
-	\caption{Schematic of Second Floor of Two-Story Structure Indicating Thermocouple and Heat Flux Gauges}
-	\label{fig:tcs_hf_second_2story}
-\end{figure}
-
-The time history profile of the temperature response along with the heat flux at three positions are shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
+The time history profile of the temperature response along with the heat flux at three positions is shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
 Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7, while Figures~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
@@
 
-The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$ 15~\% (see Section~\ref{subsec:Uncertainty}).
-So, for the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$ 15~\%.
-If the difference between two measurements was $\pm$ 15~\% or less, the results are considered similar.
+The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$~15~\% (see Section~\ref{subsec:Uncertainty}).
+So, for the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$~15~\%.
+If the difference between two measurements was $\pm$~15~\% or less, the results are considered similar.
 That said, the estimated uncertainty is based on previous studies where suppression with a water based agent was included.
@@
 
+\chapter{Dimensioned Floor Plans}
+\label{app:floor_plans}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/West_Structure/DelCo_2012_West_Structure_Detailed}
+	\caption{Fully Dimensioned Floor Plan of the Burn Building Layout}
+	\label{fig:Delaware_County,_PA_Burn_Building_Layout_Detailed}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Detailed}
+	\caption{Fully Dimensioned Floor Plan of the Single-Story Test Structure}
+	\label{fig:Test_Structure_Floor_Plan_Detailed}
+\end{figure}
+
+\clearpage
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
+	\caption{Fully Dimensioned Floor Plan of the First Floor of the Two-Story Structure}
+	\label{fig:dimensioned_first_2story_detailed}
+\end{figure}
+
+\begin{figure}[!ht]
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
+	\caption{Fully Dimensioned Floor Plan of the Second Floor of the Two-Story Structure}
+	\label{fig:dimensioned_second_2story_detailed}
+\end{figure}
+
 \chapter{Spray Density Figures}

### 2016-11-22 Projects/DelCo_2012/Report/DelCo_2012.tex
update report and door legend CAF

@@
 \flushright{
-Craig G. Weinschenk $^+$ \\
+Craig G. Weinschenk $^*$ \\
 Daniel Madrzykowski $^*$ \\
@@
 \vspace*{2\baselineskip}
-{\em $^+$\small Currently with JENSEN HUGHES, Baltimore MD}
-\\
 {\em $^*$\small Currently with Underwriters Laboratories Firefighter \\ 
@@
 The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments.
+Figure~\ref{fig:Door_Status_Legend} provides the key for determining the status of open or closed doors in the facility schematics.
+
+\begin{figure}[!ht]
+	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Door_Legend}
+	\caption{Door Status Legend}
+	\label{fig:Door_Status_Legend}
+\end{figure}
 
@@
 
-The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Keith Stakes (currently with UL FSRI), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
 These experiments could not have been conducted without them.

### 2016-11-22 Projects/DelCo_2012/Report/DelCo_2012.tex
edits to CAF report from JH comments

@@
 Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
-The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1, fixed gallonage nozzles with a flow rate of 120~gpm.
+The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1 \textregistered, fixed gallonage nozzles with a flow rate of 120~gpm.
 These are automatic nozzles which have a 22~mm (0.88~in) slug-tip and can be varied from a straight stream to a wide fog stream for application.
 The setup also included 30.5~m (100~ft) of 44~mm (1.75~in) diameter hose.
-Nozzles were mounted to a ``blitz-fire'' monitor device and placed inside the structures.
+Nozzles were mounted to a Blitz-Fire \textregistered monitor device and placed inside the structures.
 The nozzles were controlled and operated via a gate valve from the exterior.
@@
 In Figure~\ref{fig:fs_hall_a1}, the red dashed line (linear fit to the data, see Section~\ref{sec:Gas_Cooling}) closely follows the black line, which indicates near equal cooling between CAF and water.
-The R$^2$ value of 0.901 shows a strong fit to the data.
-When the second nozzle (door nozzle) was activated, the temperature differences are noticeably lower compared to the hallway nozzle, despite it being an indirect attack.
+The R$^2$ value of 0.879 shows a strong fit to the data.
+When the second nozzle (door nozzle) was activated, the temperature differences are noticeably lower compared to the hallway nozzle (indirect attack).
 While the fit is not as strong (R$^2$~=~0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Despite being closer to the nozzles, thermocouple tree A2 shows similar temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a1}).
+Despite being closer to the nozzles, thermocouple tree A2 shows similar temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a2}).
 At array A2 for the door nozzle (see Figure~\ref{fig:fs_door_a2}), the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
@@
 Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.
+In all cases, ventilation was provided through open basement doors and a door on the first floor.
 
@@
 \centering
-\footnotesize
+\small
 \caption{Two-Story Fire Suppression Test Descriptions}\label{tab:Test_Descriptions_2}
-\begin{tabular}{clllll}
+\begin{tabular}{cllll}
 \toprule[1.5pt]
-Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    & Ventilation  \\
+Test $\#$  & Name	& Stream			& Flow Rate		& Fuel                    \\
 \midrule
- 13  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           & Basement Doors, 1st Floor Door \\
- 14  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           & Basement Doors, 1st Floor Door \\
- 15  & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 16  & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 17  & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
- 20  & CAF~9b    &  Solid Stream        &  120~gpm/60~cfm   & Furniture + Pallet  & Basement Doors, 1st Floor Door \\
+ 13  & CAF~7     &  Straight Stream  	&  120~gpm/60~cfm   & Furniture           \\
+ 14  & Water~7   &  Straight Stream  	&  120~gpm    		& Furniture           \\
+ 15  & CAF~8a    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  \\
+ 16  & CAF~8b    &  Straight Stream  	&  120~gpm/60~cfm   & Furniture + Pallet  \\
+ 17  & Water~8   &  Straight Stream     &  120~gpm          & Furniture + Pallet  \\
+ 18  & Class A~1 &  Straight Stream  	&  120~gpm		    & Furniture + Pallet  \\
+ 19  & CAF~9a    &  1 3/8'' Ball    	&  120~gpm/60~cfm   & Furniture + Pallet  \\
+ 20  & CAF~9b    &  Solid Stream        &  120~gpm/60~cfm   & Furniture + Pallet  \\
 \bottomrule[1.25pt]
@@
 
-The time history profile of the temperature response along with the heat flux at three positions is shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
+The time history profile of the temperature response along with the total heat flux at three positions is shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
 Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7, while Figures~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
@@
 
-While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness of CAF for interior structural fire fighting varies widely.
+While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness or advantages of CAF for interior structural fire fighting was undocumented by experimental data.
 Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
@@
 There were also thoughts that the CAFS would coat the ceiling and eliminate energy feedback from the ceiling to the hot gas layer, thereby providing enhanced cooling.
+However, CAF has not been widely used for structure fires.
 
@@
 The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).
-The average time of flow was approximately 15~s, therefore a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
+The average time of flow was approximately 15~s.
+A total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
 
@@
 The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$~15~\% (see Section~\ref{subsec:Uncertainty}).
-So, for the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$~15~\%.
+For the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$~15~\%.
 If the difference between two measurements was $\pm$~15~\% or less, the results are considered similar.
-That said, the estimated uncertainty is based on previous studies where suppression with a water based agent was included.
-
-As mentioned in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results because due to the array's position, it was impacted the least by agents hitting and cooling the thermocouples themselves.
+The estimated uncertainty is based on previous studies where suppression with a water based agent was included.
+
+As mentioned in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results.
+It was impacted the least by agents hitting and cooling the thermocouples themselves.
 Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is absorbing the energy from the upper layer.
@@
 
-\subsection{Iowa State University Fire Flow Formula (1963)}
-The Iowa Formula for determining the required fire flow rate for a given structure was developed by Keith Royer and Bill Nelson and is based on theoretical heat absorption capabilities of water.
+\subsection{Iowa State University Fire Flow Formula}
+The Iowa Formula for determining the required fire flow rate for a given structure was developed by Keith Royer and Bill Nelson and is based on theoretical heat absorption capabilities of water \cite{Royer:ISU}.
 The required fire flow rate ($\dot{V}$) in gpm is equal to the volume ($V$) of the fire compartment in cubic feet divided by 100:
@@
 The fire room compartment volumes in these experiments ranged from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
-Therefore, the required flow rate for the fire room in the single-story structure based on the Iowa State University formula was approximately 87~l/min (23~gpm), and the required flow rate for the fire room in the lower level of the two-story structure was approximately 168~l/min (44~gpm).
+The required flow rate for the fire room in the single-story structure based on the Iowa State University formula was approximately 87~l/min (23~gpm), and the required flow rate for the fire room in the lower level of the two-story structure was approximately 168~l/min (44~gpm).
 During the experiments, the flow rate was approximately 454~l/min (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
@@
 
-\subsection{National Fire Academy (1981)}
+\subsection{National Fire Academy}
 The National Fire Academy (NFA) developed a formula based on a study of fire flows that have been successful in controlling a large number of working fires~\cite{Klaene:1}.
@@
 Both of the formulas listed above do not explicitly account for the ventilation of the fire structure, only the size of the fire structure.
-Further, the most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
+The most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
 This experience was likely from fires that occurred in the 1960's and the 1970's.
@@
 There are simple formulas which may provide some insight here, although this simple algorithm has not been validated with the geometries that were used in the experiments described in this report.
-The purpose here is to get a sense of the amount of heat energy that the hose streams needed to overcome.
+The purpose here is to estimate the amount of heat energy that the hose streams needed to overcome.
 This algorithm, like the NFA formula, has never been validated for this application.
+The heat release rate is:
 
@@
 Wood-based fuels, however, develop a char layer.
-Therefore the burning of wood-based fuels would be ``deep seated'', which might provide a more significant suppression challenge.
+The burning of wood-based fuels would be ``deep seated'', which might provide a more significant suppression challenge.
 The reduced surface tension of Class A foam solution could allow the solution to better penetrate and cool the burning wood-based fuels.
 It was thought that with more exposed burning wood surfaces in the fuel load, CAF would have a better the opportunity to demonstrate a difference in suppression.
-As shown in Chapter~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and OSB.
+As shown in Section~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and OSB.
 The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
@@
 The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single-story structure.
-As discussed previously, with the larger area and double the ventilation of the previous experiments, the fire should be more of a challenge to the hose streams.
-There was also another variable that would be introduced: a firefighter controlling the nozzle.
+As discussed previously, with the larger area and double the ventilation of the previous experiments, the fire should have been more challenging to the hose streams.
+There was also another variable that was be introduced: a firefighter controlling the nozzle.
 Recall that in the single-story experiments, a monitor nozzle was used in a fixed position.
@@
 The data collected during this study does not demonstrate significant differences between CAF and water for use in interior structural fire fighting on a residential scale.
-Going back to the premise of the study, preventing firefighters from being injured during interior fire fighting operations with CAF, there is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
+There is nothing in these fire suppression results to suggest that CAF would present a thermal hazard, provided that an adequate amount of water is being flowed for the given fire condition.
 
@@
 \label{chap:Summary}
+
+This study conducted by NIST was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 
@@
 In this report, an aggregate analysis was made to examine differences due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
-No significant differences were found in the gas cooling capabilities of the two agents.
+The results showed that water was generally more effective than CAF, though both agents were successful with respect to gas cooling and fire suppression.
 A more detailed analysis of the individual experiments was conducted by Mitchell of Cal Poly~\cite{Mitchell:1}.
@@
 
-This study conducted by NIST was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
-This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
-
 \chapter{Acknowledgments}
@@
 The Delaware County team was under the direction of Kerby Kerber.
-For construction and test support the team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale and Todd John.
-
-We also thank the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
+The construction and test support team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale and Todd John.
+
+Thanks are given to the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
 

### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Added windows to floor plans

@@
 	\includegraphics[width=.35\columnwidth]{../Figures/Floor_Plans/PDFs/DelCo_2012_Door_Legend}
-	\caption{Door Status Legend}
+	\caption{Door and Window Legend}
 	\label{fig:Door_Status_Legend}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Furniture}
 	\caption{Furniture Fuel Load Dimensions in Single-Story Structure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.8\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
+	\includegraphics[width=\columnwidth]{../Figures/Floor_Plans/PDFs/East_Structure/DelCo_2012_East_Structure_Pallets}
 	\caption{Wood Fuel Load Dimensions in Single-Story Structure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Plain}
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_1st_Floor_Detailed}
 	\caption{Fully Dimensioned Floor Plan of the First Floor of the Two-Story Structure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Plain}
+	\includegraphics[width=\columnwidth]{../../DelCo_2014_2015/Drawings/PDFs/CAFS/West_Structure_2nd_Floor_Detailed}
 	\caption{Fully Dimensioned Floor Plan of the Second Floor of the Two-Story Structure}

### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor changes to CAF report

@@
 The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments.
-Figure~\ref{fig:Door_Status_Legend} provides the key for determining the status of open or closed doors in the facility schematics.
+Figure~\ref{fig:Door_Status_Legend} provides the key used to identify doors and windows in the facility schematics.
 
@@
 Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft).
-Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
+Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor.
+A fully dimensioned plan view of the floor is presented in Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout_Detailed} in Appendix~\ref{app:floor_plans}.
 
@@
 While Mitchell examined each individual experiment in detail, the results were mixed.
-In the different gas cooling scenarios, CAF showed slightly better or slightly worse than plain water.
+In the different gas cooling scenarios, CAF performed slightly better or slightly worse than plain water.
 Hence, the conclusion was that there was no significant difference in gas cooling capabilities between CAF and water.
@@
 As a result, it remained dry and seems to provide the best representation of the gas cooling.
-`'
+
 \begin{figure}[ht!]
@@
 
-To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the fire room.
+To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the gas cooling room.
 Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).

### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
update channels, plots, descriptions, and report for CAF study

@@
 For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used.
-The data show that thermocouples from Gas Cooling Array 2 (GC\_2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (GC\_1 and GC\_3).
-This is the result of Gas Cooling Array 2 being directly ``hit'' by the suppression stream.
+The data show that thermocouples from Array 2 (TC\_A2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (TC\_A1 and TC\_A3).
+This is the result of Array 2 being directly ``hit'' by the suppression stream.
 Gas Cooling Array 1 also exhibits some amount of suppression agent impact.
-Gas Cooling Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.
+Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.
 As a result, it remained dry and seems to provide the best representation of the gas cooling.
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent. Shown are Tests 2, 3, and 4 from Table~\ref{tab:Gas_Cooling_Descriptions}}
 	\label{fig:gas_cooling_sub1}
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAF as the Suppression Agent}
+	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAF as the Suppression Agent. Shown are Tests 52, 53, and 54 from Table~\ref{tab:Gas_Cooling_Descriptions}}
 	\label{fig:gas_cooling_sub5}
@@
 This analysis of the data results in the same conclusions as the analysis from the Mitchell paper \cite{Mitchell:1}: the gas cooling performance of CAF is similar to water under these conditions.
-Or, more accurately, water is nearly always equal to or better than CAF.
+Or, more accurately, water is nearly always equal to or slightly better than CAF.
 
@@
 If the ventilation was increased to allow additional oxygen to be supplied to the fuel gases in the fire compartment, the heat release rate of the fire would have increased.
-There are simple formulas which may provide some insight here, although this simple algorithm has not been validated with the geometries that were used in the experiments described in this report.
+There are simple formulas which may provide some insight here, although this simple algorithm has not been validated with the geometries that were used in the experiments described in this report~\cite{Babrauskas:4}.
 The purpose here is to estimate the amount of heat energy that the hose streams needed to overcome.
@@
 
-In Equation~\ref{eq:HRRSto_item}, the maximum heat release rate ($\dot{Q}_{stoichiometric}$) in kW is based on airflow through the area of the opening ($A_0$) in square meters and the square root of the height of the opening ($H_0$) in meters.
+In Equation~\ref{eq:HRRSto_item}, the maximum heat release rate ($\dot{Q}_{stoichiometric}$) in kW is based on airflow through the area of the opening ($A_0$) in square meters and the square root of the height of the opening ($H_0$) in meters~\cite{Babrauskas:4}.
 

### 2016-12-01 Projects/DelCo_2012/Report/DelCo_2012.tex
update acknowledgements to CAF report

@@
 
+This study was part of a larger DHS/FEMA Assistance to Firefighters Research and Development Grant project led by California Polytechnic State University (Cal Poly), San Luis Obispo.
+The authors would like to acknowledge the support of the Cal Poly team, especially: Fred Mowrer, Christopher Dicus, Thomas Korman and Sean Mitchell.
+
 The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
@@
 Thanks to all involved for assisting in generating data that will aid the fire service in making evidence based tactical choices.
+A special thanks to Joseph Scheffey of Jensen Hughes and Nelson Bryner of NIST for a thorough technical review of this manuscript.
 

### 2016-12-02 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor text changes to CAF report; resolved plot.py flag issue

@@
 
-In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the lower level of the two-story structure.
-Two different fuel packages were utilized, the difference between the furniture fuel package used for experiments 13 and 14, and the furniture and pallet fuel package used in experiments 15 through 20 was the addition of two stacks of pallets.
+In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the two-story structure.
+Two different fuel packages located on the ground level were utilized throughout the experiments: experiments 13 and 14 used a fuel package composed primarily of furniture, and experiments 15 through 20 used the same fuel package with an addition of two stacks of wood pallets.
 
@@
 
-The fuel load for two of the experiments consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
+The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
 The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart.
@@
 
-In June 2015, two stacks of pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
+For experiments 15 through 20, two stacks of wood pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
 Each stack had 10 pallets and an approximate mass of 175~kg (386~lb).
-Hay from bales averaging a mass of 12~kg (26~lb) was added for ignition purposes.
+Hay from bales with an average a mass of 12~kg (26~lb) was added for ignition purposes.
 The specific locations of the fuel load's contents can be found in the dimensioned schematic Figure~\ref{fig:pallet_furniture_2story}.
@@
 For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used.
-The data show that thermocouples from Array 2 (TC\_A2 in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (TC\_A1 and TC\_A3).
+The data show that thermocouples from Array 2 (``TC~A2'' in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (``TC~A1'' and ``TC~A3'').
 This is the result of Array 2 being directly ``hit'' by the suppression stream.
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries12_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with Water as the Suppression Agent. Shown are Tests 2, 3, and 4 from Table~\ref{tab:Gas_Cooling_Descriptions}}
+	\caption{Time Series of Thermocouple Data from Three Arrays in Gas Cooling Room with Water as the Suppression Agent. Shown are Tests 2, 3, and 4 from Table~\ref{tab:Gas_Cooling_Descriptions}}
 	\label{fig:gas_cooling_sub1}
@@
 	\includegraphics[width=.5\columnwidth]{../Figures/Gas_Cooling/GCSeries52_TC_A3}
-	\caption{Time Series of Thermocouple Data from 3 Arrays in Gas Cooling Room with CAF as the Suppression Agent. Shown are Tests 52, 53, and 54 from Table~\ref{tab:Gas_Cooling_Descriptions}}
+	\caption{Time Series of Thermocouple Data from Three Arrays in Gas Cooling Room with CAF as the Suppression Agent. Shown are Tests 52, 53, and 54 from Table~\ref{tab:Gas_Cooling_Descriptions}}
 	\label{fig:gas_cooling_sub5}
@@
 Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the door on the south side of the second story of the structure.
+Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the south exterior door on the second story of the structure.
 The fires were intended to replicate room and contents basement fires typically seen within residential structures.
-Suppression occurred at the basement double doors of the structure.
+Suppression occurred at the ground level double doors of the structure.
 Table~\ref{tab:Test_Descriptions_2} provides an overview of the suppression tests conducted.
-In all cases, ventilation was provided through open basement doors and a door on the first floor.
 
@@
 
-The impact of water and CAF during fire suppression can  again be analyzed by comparing the temperature differences during the suppression interval at the two thermocouple arrays in the fire room.
-Figure~\ref{fig:fs_a10} shows the temperature difference comparison at thermocouple array A10 for CAF and water after basement suppression.
-In Figure~\ref{fig:fs_a10}, only tests Water~7 \& 8 are compared to CAF~7 \& 8a as those are tests with comparable configurations.
+The impact of water and CAF during fire suppression can again be analyzed by comparing the temperature differences during the suppression interval at the various thermocouple arrays throughout the structure.
+Figure~\ref{fig:fs_a10} shows the temperature difference comparison at array A10 for CAF and water after suppression.
+In Figure~\ref{fig:fs_a10}, the tests Water~7 \& 8 are compared to CAF~7 \& 8a because they all contained similar experimental configurations.
 

### 2016-12-02 Projects/DelCo_2014_2015/Scripts/plot.py

@@ -27,7 +27,7 @@ specify_year = False
 specific_year = '2014'
 
 # Specify type
-specify_type = True
+specify_type = False
 specific_type = 'GAS'
 
 # Specify structure
@@ -36,7 +36,7 @@ specific_struct = 'West'
 
 # Specify if creating data sets
 #  for gas burner exp. report
-burner_report = True
+burner_report = False
 burner_data = '../Reports/Propane_Gas_Fire_Experiments/Data/'
 
 # Plot mode: figure or video
@@ -91,11 +91,11 @@ video_plots = collections.OrderedDict()
 #  ==========================
 
 # # Prints an error message and stops code
-# def error_message(message):
-#     lineno = inspect.currentframe().f_back.f_lineno
-#     print '[ERROR, line '+str(lineno)+']:'
-#     print '  ' + message
-#     sys.exit()
+def error_message(message):
+    lineno = inspect.currentframe().f_back.f_lineno
+    print '[ERROR, line '+str(lineno)+']:'
+    print '  ' + message
+    sys.exit()
 
 # checks if file should be skipped
 def check_name(test_name, test_year, test_type):
@@ -157,11 +157,11 @@ for f in os.listdir(data_dir):
         test_type = info['Test Type'][test_name]
 
         # if burner_report:
-        try:
-            if 'Propane fire' not in info['Test Description'][test_name]:
-                continue
-        except TypeError:
-            continue
+        # try:
+        #     if 'Propane fire' not in info['Test Description'][test_name]:
+        #         continue
+        # except TypeError:
+        #     continue
 
         if check_name(test_name, test_year, test_type):     # check if file should be skipped
             continue

### 2016-12-06 Projects/DelCo_2012/Report/DelCo_2012.tex
minor update to CAFs report

@@
 The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
-The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 1~m (3~ft) above the floor on the second floor level in front of the stairway door.
-Figure~\ref{fig:fire_supp_second_2story} shows the position of the thermocouple array (TC A10) as well as the three pairs of heat flux gauges.
-Table~\ref{tab:Test_Results_2} shows the heat flux at position 1, that faces in the vertical direction (toward the ceiling).
+The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor in front of the stairway door.
+Figure~\ref{fig:fire_supp_second_2story} shows the position of the thermocouple array (TC A10).
 Note that these thermocouples are inconel shielded thermocouples and have slower response times (smaller $\Delta$T's over similar time intervals) compared to the bare-bead thermocouples used in the single-story tests.
@@
 \caption{Two-Story Fire Suppression Results, Stairwell Doorway Temperatures}\label{tab:Test_Results_2}
-\begin{tabular}{lcccc}
+\begin{tabular}{lccc}
 \toprule[1.5pt]
-           &               & \multicolumn{2}{c}{Temperature Change}                                    & Heat Flux Change \\
-Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               & 1~m Above Floor \\
+           &               & \multicolumn{2}{c}{Temperature Change}                                    \\
+Test 	   & Flow Time (s) & 0.3~m Below Ceiling                 & 0.3~m Above Floor	               \\
 \midrule
-CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   & 24~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   & 17~kW/m$^2$ - 17~kW/m$^2$  \\[.25cm]
-CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   & 21~kW/m$^2$ - 14~kW/m$^2$  \\
-CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   & 13~kW/m$^2$ - 12~kW/m$^2$  \\[.25cm]
-Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   & 19~kW/m$^2$ - 14~kW/m$^2$  \\[.25cm]
-Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   & 13~kW/m$^2$ - 11~kW/m$^2$  \\
-CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   & 17~kW/m$^2$ - 16~kW/m$^2$  \\
-CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   & 20~kW/m$^2$ - 17~kW/m$^2$  \\
+CAF~7      & 24            & 530~$^{\circ}$C - 425~$^{\circ}$C   & 670~$^{\circ}$C - 425~$^{\circ}$C   \\[.25cm]
+Water~7    & 29            & 560~$^{\circ}$C - 430~$^{\circ}$C   & 670~$^{\circ}$C - 400~$^{\circ}$C   \\[.25cm]
+CAF~8a     & 16            & 475~$^{\circ}$C - 425~$^{\circ}$C   & 580~$^{\circ}$C - 460~$^{\circ}$C   \\
+CAF~8b     & 21            & 475~$^{\circ}$C - 400~$^{\circ}$C   & 540~$^{\circ}$C - 400~$^{\circ}$C   \\[.25cm]
+Water~8    & 18            & 520~$^{\circ}$C - 460~$^{\circ}$C   & 530~$^{\circ}$C - 440~$^{\circ}$C   \\[.25cm]
+Class A~1  & 19            & 470~$^{\circ}$C - 430~$^{\circ}$C   & 590~$^{\circ}$C - 500~$^{\circ}$C   \\
+CAF~9a     & 21            & 530~$^{\circ}$C - 440~$^{\circ}$C   & 620~$^{\circ}$C - 450~$^{\circ}$C   \\
+CAF~9b     & 16            & 580~$^{\circ}$C - 510~$^{\circ}$C   & 660~$^{\circ}$C - 525~$^{\circ}$C   \\
 \bottomrule[1.25pt]
@@
 
-The time history profile of the temperature response along with the total heat flux at three positions is shown in Figures~\ref{fig:water7_tca10}--\ref{fig:caf9a_hf}.
-Figures~\ref{fig:water7_tca10} and \ref{fig:water7_hf} show the results for test Water~7, while Figures~\ref{fig:caf9a_tca10} and \ref{fig:caf9a_hf} show the results for test CAF~9a.
+The time history profile of the temperature response is shown in Figures~\ref{fig:water7_tca10} and \ref{fig:caf7_tca10}.
+Figure~\ref{fig:water7_tca10} shows the results for test Water~7, while Figure~\ref{fig:caf7_tca10} shows the results for test CAF~7.
 The remainder of the fire suppression test data and results are included in Appendix~\ref{app:fire_suppression2}.
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Water~7 Fire Suppression Test}
-	\label{fig:water7_hf}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
-	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~9a Fire Suppression Test}
-	\label{fig:caf9a_tca10}
-\end{figure}
-
-\begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9a Fire Suppression Test}
-	\label{fig:caf9a_hf}
+	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_TC_A10}
+	\caption{Time Series of Thermocouple Data from Array TC A10 at the Top of the Stairwell for Two-Story CAF~7 Fire Suppression Test}
+	\label{fig:caf7_tca10}
 \end{figure}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_38_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~7 Fire Suppression Test}
-	\label{fig:app_caf7_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_39_West_061315_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Water~7 Fire Suppression Test}
-	\label{fig:app_water7_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40a_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8a Fire Suppression Test}
-	\label{fig:app_caf8a_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40b_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8b Fire Suppression Test}
-	\label{fig:app_caf8b_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_40c_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~8 Fire Suppression Test}
-	\label{fig:app_caf8_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41a_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story Class~A~1 Fire Suppression Test}
-	\label{fig:app_classa1_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_TC_A10}
@@
 \begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9a Fire Suppression Test}
-	\label{fig:app_caf9a_hf}
-\end{figure}
-
-\begin{figure}[!ht]
 	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_TC_A10}
@@
 
-\begin{figure}[!ht]
-	\includegraphics[width=.85\columnwidth]{../Figures/Script_Figures/Test_41c_West_061415_Heat_Flux}
-	\caption{Time Series of Heat Flux Data at Three Locations on the Second Floor for Two-Story CAF~9b Fire Suppression Test}
-	\label{fig:app_caf9b_hf}
-\end{figure}
-
 \end{document}

### 2016-12-06 Projects/DelCo_2012/Report/DelCo_2012.tex
Dan final revisions

@@
 TFT \> Task Force Tips \\
-TJI \> Trust Joist I-Joist \\
 UL FSRI \> UL Firefighter Safety Research Institute \\
@@
 The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
-Under the test conditions, both agents were effective.
+Under the test conditions, both agents were effective in reducing the gas temperatures and suppressing fires in a compartment.
 This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle relative to plain water.
@@
 Finally, the compressed air adds energy to the water stream, providing additional reach to a hose stream with a relatively low mass flow rate of water.
-These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire or can be used for an exterior (indirect) fire suppression attack on a structure.
+These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire or CAF can be used for an exterior (indirect) fire suppression attack on a structure.
 
@@
 \centering
-\captionof{table}{Tests to Assess CAF Fire Fighting Agent Compared to Water}\label{tab:agent_tests}
+\captionof{table}{Tests to Assess Class A Fire Fighting Agents Compared to Water}\label{tab:agent_tests}
 \begin{tabular}{lcc}
@@
 One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland fire fighting, CAFS is typically applied directly to the fuel from a remote location, typically an environment that is not an immediate danger to life and health (non-IDLH environment).
-In structural fire fighting, crews typically have to enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
-In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer or try to cool interior surfaces as they move toward the fire.
+In structural fire fighting, crews typically enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
+In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer and or try to cool interior surfaces as they move toward the fire.
 It is important that these distinctions and differences between exterior and interior fire fighting with CAF are better understood.
@@
 In this same order, the Chief directed the Division Chief of Operations to continue to evaluate the use of CAF during structure fires and to report back his findings and recommendations.
-That order was a catalyst for this study.
+That order and the experience of the MCFRS played a major role in the development of this study.
 
@@
 The nozzle patterns were varied and included straight stream, solid stream, and narrow fog stream.
-The six experiments in the two-story structure used both water and CAF from a straight stream nozzle.
+Six experiments were conducted in the lower level of the two-story structure using both water and CAF from a straight stream nozzle.
 In addition, two CAF experiments were conducted in the two-story burn building with a solid stream.
+The lower level of the two story structure allowed for a fire compartment that was approximately twice as large as the fire compartment in the single story.
 
@@
 
-Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.74~m (9.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
+Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.4~m (8.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
 The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
@@
 
-A second story was added to the west single-story structure in order to test larger fires and remote suppression effects (see Figure~\ref{fig:delco_2story}).
+A second story was added to the west single-story structure in order to conduct suppression experiments in a larger fire compartment than the fire compartment in the single story and to examine the impact of the fire and suppression in a remote compartment (upstairs) that was not directly exposed to the hose stream (see Figure~\ref{fig:delco_2story}).
 
@@
 An image of the fuel arrangement is shown in Figure~\ref{fig:Furniture_Fuel_Load}.
-The couches and chairs were set up to mimic a typical seating area with one couch against the south wall and one couch against the east wall, each positioned 0.9~m (36~in) away from the southeast corner.
+The sofas and chairs were set up to mimic a typical seating area with one couch against the south wall and one couch against the east wall, each positioned 0.9~m (36~in) away from the southeast corner.
 A chair was placed adjacent to each couch.
@@
 
-The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (559~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
+The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (553~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
 The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart.
@@
 During each test, the fire was ignited and developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
-This condition was evidence that a hot gas layer at least 1.83~m deep had filled the room next to the burn room.
+This condition was evidence that a hot gas layer at least 1.83~m (6~ft) deep had filled the room next to the burn room.
 Once this criteria was met, gas cooling began.
@@
 A final experimental series was conducted in a larger fire room with more ventilation.
-In this final series, another change was made: the nozzle was hand held and could be moved as needed to effectively extinguish the fire.
+In this final series, another change was made: the nozzle was hand held and could be moved as needed to completely extinguish the fire.
 This section discusses the overall results of the study and provides potential explanations to support them.
@@
 While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness or advantages of CAF for interior structural fire fighting was undocumented by experimental data.
-Questions remain regarding whether CAF provides improved gas cooling when compared to plain water.
+Questions remained regarding whether CAF provides improved gas cooling when compared to plain water.
 During the planning of the experiments for this project, there were a range of hypotheses regarding potential outcomes.
@@
 Their position was based on the fact that CAF has injected air.
-Because air is a great insulator, it slows heat transfer and results in less cooling.
+Because air is a great insulator, it might slow the heat transfer rate between the water and the fire gases and result in a reduced cooling rate.
 It was their belief that the reduced gas cooling capabilities of CAF may have led to firefighter injuries during interior fire attacks.
@@
 
+For the formula as written, it is assumed that the fire compartment is "fully involved" and that the fire is ventilation limited.
 Due to inefficiencies in the application of water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
@@
 
-The fire rooms in these experiments ranged in floor area from approximately 27~m$^2$ (291~ft$^2$) to 51.4~m$^2$ (553~ft$^2$).
-Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 369~l/min (97~gpm).
+The fire rooms in these experiments ranged in floor area from approximately 26~m$^2$ (280~ft$^2$) to 51.4~m$^2$ (553~ft$^2$).
+Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 352~l/min (93~gpm).
 The required flow rate for the fire room in the lower level of the two-story would be approximately 700~l/min (184~gpm).
@@
 
+\subsection{Ventilation Limited Fires}
 Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a renewed interest in controlling the air available to a ventilation limited compartment fire.
@@
 
-In all the suppression experiments, the fire was controlled with a total flow of 227~L (60~gal) or less of agent.
+\subsection{Fuel Loads: Natural vs Synthetic}
+In all the suppression experiments, the fire was controlled with no more than 227~L (60~gal) or less of plain water or water in the form of CAF.
 During the course of the suppression experiments, the fuel packages were modified to incorporate more wood-based fuels.
@@
 
+\subsection{Fire Compartment Size}
 The final set of suppression experiments used a larger space than the previous two sets of suppression experiments in the single-story structure.
@@
 
-The fire fighting crew was from the MCFRS and every member in the crew had been trained in the use of and had experience with using CAF.
+The fire fighting crew was from the MCFRS and every member in the crew had been trained in the use of CAF and they had experience with using CAF.
 The firefighter on the nozzle was the same for all the experiments conducted in the two-story structure.
 The firefighter used the reach of the hose stream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
-Then, the hoseline was advanced and the nozzle was moved rapidly to hit the fuels inside the compartment.
+Then the hoseline was advanced to the doorway and the nozzle was moved rapidly to hit the fuel surfaces inside the compartment.
 The nozzle was shut down when there were no flames visible from the doorway.
@@
 The experimental configurations were designed to be representative of residential fire scenarios.
+The experience of the MCFRS played a major role in the development of this study.
 %The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
@@
 There were two different geometries used for the fire suppression experiments.
-Twelve of the suppression experiments were conducted in a single-story structure with an entry hallway that led to a fire compartment with a floor area of 27~m$^2$ (291~ft$^2$).
-Within this structure, two different types of fuel loads were used.
+Twelve of the suppression experiments were conducted in single-story structures with an entry hallway that led to a fire compartment with a floor area of 26~m$^2$ (280~ft$^2$).
+Within these structures, two different types of fuel loads were used.
 In one case, most of the fuel consisted of synthetic materials in the upholstered furniture, carpet, and padding.
 The other fuel load used only wood-based fuels to examine the value of the reduced surface tension of the water in the CAF and its interaction with the surface of the wood fuel.
-In the experiments conducted in the single-story building, a fixed nozzle was flowed from the hallway for approximately 15~s, and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
+In the experiments conducted in the single-story buildings, a fixed nozzle was flowed from the hallway for approximately 15~s, and then another fixed nozzle located in the fire compartment was flowed for an additional 15~s.
 
@@
 The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
-In each case, the initial knockdown of the fire required 60~gal of agent or less.
+In each case, the initial knockdown of the fire required no more than 60~gal of of plain water or water in the form of CAF.
 
 The results from both the gas cooling and the suppression of residential scale room fires showed the effectiveness of water and CAF hose streams to be similar.
-Under these test conditions both agents were effective.
+Under the test conditions, both water and CAF were effective in rapidly reducing the gas temperatures and suppressing fires in a compartment.
 This study did not address the previously documented attributes of CAF for improved exposure protection and improved prevention of a fire re-kindle relative to plain water.

### 2016-12-07 Projects/DelCo_2012/Report/DelCo_2012.tex
fix front matter caf
Minor changes to wording to remove inconsistencies (up to Section 2.3)

@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1927}{http://dx.doi.org/10.6028/NIST.TN.1927} \\
 \endgroup
@@
 IDLH \> Immediate Danger to Life and Health \\
-ESTC \> Delaware County Emergency Services Training Center \\
+ESTC \> Emergency Services Training Center \\
 MCFRS \> Montgomery County (MD) Fire and Rescue Service \\
@@
 TC \> Thermocouple \\
-TFT \> Task Force Tips \\
-UL FSRI \> UL Firefighter Safety Research Institute \\
+% TFT \> Task Force Tips \\
+% UL FSRI \> Underwriters Laboratories Firefighter Safety Research Institute \\
 
@@
 
-Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+Full scale fire experiments designed to address the key outcomes were conducted over a period of years from 2012 through 2015.
 The experimental arrangements and results are presented in this report.
@@
 
-This study, conducted by the National Institute of Standards and Technology (NIST), was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
-This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
+This study, conducted by the National Institute of Standards and Technology, was part of a larger research project led by California Polytechnic State University, San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study was supported in part by a Department of Homeland Security/Federal Emergency Management Administration Assistance to Firefighters Research and Development Grant.
 
@@
 
-A number of fire departments throughout the US have acquired CAFS units for structural fire fighting.
+A number of fire departments throughout the United States have acquired CAFS units for structural fire fighting.
 Many have limited or stopped the use of these CAFS for structural fire fighting.
-This is due to operational challenges or due to lack of understanding related to fireground safety issues.
+This is due to operational challenges or due to lack of understanding related to fire ground safety issues.
 This project is expected to produce a better understanding of the effectiveness and safety implications of compressed air foam (CAF) for structural fire fighting through the various tasks associated with this project, including:
@@
 \item  Conduct a workshop that brings interested and experienced parties together to discuss CAF experience and to provide input on the proposed experimental research plan~\cite{Grant:2011} 
-\item  Conduct and document well-instrumented large-scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural fire fighting
-\item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution, nozzle reaction force, the force to kink the hose, potential for slipping on a variety of surfaces, and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
+\item  Conduct and document well-instrumented large scale enclosure fire tests using both CAF and plain water to evaluate the effectiveness of CAF for interior structural fire fighting
+\item  Conduct and document identified fire ground related experiments to evaluate differences between CAF and plain water hose lines related to issues such as effective hose stream throw and distribution; nozzle reaction force; the force to kink the hose; potential for slipping on a variety of surfaces; and flow separation~\cite{Carracino:2013,Dicus:2013,LaPolla:2012}.
 \end{enumerate}
@@
 The additional ``soak'' time provided by the foam layer allowed the water to penetrate the hot surface of a burning fuel and also provided additional time for water to penetrate into fuels being pre-treated in an effort to prevent ignition.
-An added feature of the blanket of bubbles is that firefighters can see where they had applied the agent so that they could make a more effective application.
+An added feature of the blanket of bubbles is that firefighters can see where they have already applied the agent, allowing them to make a more effective application.
 In the wildland, water for fire fighting is typically a precious resource, is in limited supply, and has to be carried to where it is needed.
@@
 Finally, the compressed air adds energy to the water stream, providing additional reach to a hose stream with a relatively low mass flow rate of water.
-These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire or CAF can be used for an exterior (indirect) fire suppression attack on a structure.
+These CAF advantages combine to provide wildland firefighters with a tool that can be used to pre-treat homes and structures to protect them from an approaching fire, or CAF can be used for an exterior (indirect) fire suppression attack on a structure.
 
@@
 Demonstration of Biodegradable, Environmentally Safe, Non-toxic Fire Suppression Liquids NISTIR 6191 was published in 1998~\cite{Madrzykowski:4}.
-That study examined a broad range of tests to determine those parameters which most critically effect fire fighting performance.
+The study examined a broad range of tests to determine the parameters that most critically affect fire fighting performance.
 The types of experiments conducted and the impact of additives relative to water are included in Table~\ref{tab:agent_tests}.
@@
 Based on the results of the NIST 1998 study, the fire fighting agents, commonly referred to as Class A foams, were superior to water in reducing contact angle; cooling and penetrating wood-based fuels; mass retention on the wood fuels; and ignition inhibition of the wood fuels.
-When applied in the form of foam, the aqueous solutions provide enhanced radiation exposure protection to a structure relative to plain water.
-The foams enhanced the water by keeping the water in place on vertical surfaces such as walls and the reduced inter-facial surface tension allowed the water to penetrate adsorbent fuels.
-These enhancements also make the agents valuable tools for mop-up or overhaul.
+When applied in the form of foam, the aqueous solutions provided enhanced radiation exposure protection to a structure relative to plain water.
+The foams enhanced the water by keeping the water in place on vertical surfaces such as walls, and the reduced inter-facial surface tension allowed the water to penetrate adsorbent fuels.
+These enhancements make the agents valuable tools for mop-up or overhaul.
 The other experiments conducted during this study---specific heat, drop size, wood crib suppression, smoke generation, and Class D fire suppression---yielded similar results for both Class A foams and plain water.
 
-In 2005, The National Fallen Firefighters Foundation held the National Fire Service Research Agenda Symposium.
-One of the needs identified was ``improved extinguishing agents and delivery systems.'' The report states that ``The primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems.'' In wildland fire fighting, CAFS is typically applied directly to the fuel from a remote location, typically an environment that is not an immediate danger to life and health (non-IDLH environment).
+In 2005, the National Fallen Firefighters Foundation held the National Fire Service Research Agenda Symposium.
+One of the needs identified during the event was ``improved extinguishing agents and delivery systems''.
+The report from the symposium states that ``the primary objective of this research should be to reduce the exposure of firefighters to the risks of interior fire suppression by developing more effective extinguishing agents and systems''.
+In wildland fire fighting, CAF is typically applied directly to the fuel from a remote location, typically an environment that is not an immediate danger to life and health (non-IDLH environment).
 In structural fire fighting, crews typically enter the building, which contains the fire, and move under or through hot combustion products and pre-heated areas of the building (IDLH environment) as they approach the fire.
-In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer and or try to cool interior surfaces as they move toward the fire.
+In many cases, before the firefighters are able to apply the suppression agent directly to the burning fuel, they have to mitigate the hazard of the hot gas layer and/or try to cool interior surfaces as they move toward the fire.
 It is important that these distinctions and differences between exterior and interior fire fighting with CAF are better understood.
@@
 Montgomery County (MD) Fire and Rescue Service (MCFRS) is one of the larger fire departments in Maryland and was a committed user of CAF with 35 CAFS front line engines.
-MCFRS had experienced two incidents where firefighters received burns in residential structure fires while CAF was being used to fight the fire during an interior attack.
+MCFRS experienced two incidents where firefighters received burns in residential structure fires while CAF was being used to fight the fire during an interior attack.
 Concerns were raised within the department regarding the ability of CAF to cool fire gases and absorb heat as well as plain water.
@@
 
-All of the experiments were conducted at full scale in compartments and structures that were representative of room sizes in a residential occupancy.
+All experiments described in this report were conducted at full scale in compartments and structures that were representative of room sizes in a residential occupancy.
 Technical panel members whose departments routinely use CAF for structural fire fighting were invited and present at many of the fire suppression experiments.
-The experiments were planned during the workshop~\cite{Grant:2011}.
-Three types of experiments examining spray density measures, gas layer cooling, and fire suppression were conducted in the fall of 2012.
+The experiments were planned during a workshop with the interested parties~\cite{Grant:2011}.
+Three types of experiments examining spray density measures, gas layer cooling, and fire suppression of fuel packages containing upholstered furniture were conducted in the fall of 2012.
 The data from these experiments were presented to the technical panel members.
-The fire suppression experiments were conducted with a fuel package that included upholstered furniture.
 After a review of the data, a decision was made to conduct an additional series of suppression experiments with a fuel package that was composed mainly of wood-based materials.
-The logic was that the synthetic materials in the upholstered furniture burned only on the surface and were easily extinguished.
-Wood-based fuels would char and present a deep seated fire challenge to the extinguishing agents.
-After the wood-based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that other experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
+The idea was that the synthetic materials in the upholstered furniture burned only on the surface and thus were easily extinguished.
+Wood-based fuels, however, would char and present a deep seated fire challenge to the extinguishing agents.
+After the wood-based fuel package experiments were completed in 2013, it was decided in discussions with members of the technical panel that the following additional experimental conditions needed to be examined: room size, additional ventilation, and a manually operated handline.
 The issue of a larger fire compartment had also been raised during the workshop discussion, but the desire for replicate experiments and financial limitations removed the large floor plan experiments from the original plan.
 To accomplish the last series of experiments, additional funding was obtained from NIST, and the experiments were conducted in 2015.
-The fuel load contained both wood-based wall and ceiling finishes, pallets, carpeting, and upholstered furniture.
-
-The sections below describe the types of experiments, the experimental facilities, instrumentation, and fuel loads.
-Project partner MCFRS provided the CAFS equipped engines and the staffing needed to provide both the water and CAF for the experiments.
-These experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
+The fuel load contained wood-based wall and ceiling finishes; wooden pallets; carpeting; and upholstered furniture.
+
+The following sections describe the various types of experiments, facilities, instrumentation, and fuel loads used during the tests.
+Project partner MCFRS provided the CAFS equipped engines along with the necessary staffing to provide both water and CAF for the experiments.
+All experiments were conducted at the Delaware County Emergency Services Training Center (ESTC) in Sharon Hill, PA.
 
@@
 Baseline operating conditions were agreed upon at the CAFS workshop for these experiments (Table~\ref{tab:op_condition})~\cite{Grant:2011}.
-The nozzles chosen for these experiments were Task Force Tips (TFT) Metro 1 \textregistered, fixed gallonage nozzles with a flow rate of 120~gpm.
-These are automatic nozzles which have a 22~mm (0.88~in) slug-tip and can be varied from a straight stream to a wide fog stream for application.
+The nozzles chosen for these experiments were Task Force Tips Metro 1~\textregistered, fixed gallonage nozzles with a flow rate of 120~gpm.
+These were automatic nozzles with a 22~mm (0.88~in) slug-tip and were able to be adjusted between a straight stream and a wide fog stream for application.
 The setup also included 30.5~m (100~ft) of 44~mm (1.75~in) diameter hose.
-Nozzles were mounted to a Blitz-Fire \textregistered monitor device and placed inside the structures.
-The nozzles were controlled and operated via a gate valve from the exterior.
+Nozzles were mounted to a Blitz-Fire~\textregistered~ monitor device and placed inside the structures.
+The nozzles were controlled and operated from the exterior via a gate valve.
 The exterior control had a gated wye to allow the flow of CAF through a hose directed away from the test structure.
-When the flow of CAF was needed for the experiment, the gated wye would be switched to allow the CAF to flow into the test structure.
-This was done to minimize the build-up of ``dry'' foam or a slug upon the initial flow of the nozzle into the test structure.
+When the flow of CAF was needed for the experiment, the gated wye was adjusted to allow the CAF to flow into the test structure.
+This technique minimized the build-up of ``dry'' foam on the slug upon the initial flow of the nozzle into the test structure.
 
@@
 Thirty-two tests were conducted to determine spray density measures based on various nozzle patterns and locations.
+The purpose of these preliminary tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests by gaining an understanding of the water distribution throughout the structures.
 The gas cooling and fire suppression tests simulated an interior fire attack through the deployment of hose lines inside the structures with fixed nozzles.
-The purpose of these preliminary tests was to determine the appropriate nozzle locations for the gas cooling and fire suppression tests to follow by gaining an understanding of the water distribution throughout the structures.
-
-Twenty-one of the tests were conducted in the concrete burn building where the gas cooling tests would take place, and twelve of the tests were conducted in the experimental structures to be used for the fire suppression tests.
+
+Twenty-one of the spray density tests were conducted in the concrete burn building that was later used for the gas cooling tests, and twelve of the tests were conducted in the experimental structures that were later used for the fire suppression tests.
 The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (Figure~\ref{fig:Spray_Density_Nozzle_Patterns}).
-A description and drawings of these facilities are included in Section~\ref{sec:Experimental Structures}.
-Detailed discussion of the tests and results are in Section~\ref{sec:Spray_Density}.
+Descriptions of these facilities and their floor plan schematics are included in Section~\ref{sec:Experimental Structures}.
+A detailed discussion of the spray density tests and results is included in Section~\ref{sec:Spray_Density}.
 
@@
 Suppression agents were not applied to the fire in the burn room.
-Detailed discussion of the tests and results are in Section~\ref{sec:Gas_Cooling}.
+A detailed discussion of the gas cooling tests and results is included in Section~\ref{sec:Gas_Cooling}.
 
@@
 The fire suppression series included 20 experiments.
-Twelve experiments were conducted in the single-story structures (6 in each structure) using both water and CAF application as a suppression agent.
+Twelve experiments were conducted in the single-story structures (six in each structure) using both water and CAF application as a suppression agent.
 The nozzle patterns were varied and included straight stream, solid stream, and narrow fog stream.
 Six experiments were conducted in the lower level of the two-story structure using both water and CAF from a straight stream nozzle.
-In addition, two CAF experiments were conducted in the two-story burn building with a solid stream.
-The lower level of the two story structure allowed for a fire compartment that was approximately twice as large as the fire compartment in the single story.
+Additionally, two CAF experiments were conducted in the two-story burn building with a solid stream.
+The lower level of the two-story structure allowed for a fire compartment that was approximately twice as large as the fire compartment in the single-story.
 
@@
 The series of tests described within this report were conducted at the Delaware County ESTC in Sharon Hill, PA.
-A burn building and two purpose-built concrete structures are located on the grounds of the ESTC.
+A burn building and two purpose-built concrete structures were located on the grounds of the ESTC.
 The burn building was used for the gas cooling experiments, and the purpose-built concrete structures were used for the fire suppression experiments.
-Figure~\ref{fig:Door_Status_Legend} provides the key used to identify doors and windows in the facility schematics.
+Various floor plan schematics of the structures are included in the following sections.
+Figure~\ref{fig:Door_Status_Legend} provides the key used to identify doors and windows in the schematics.
 
@@
 The floors of the burn rooms were protected with fire brick.
-Tests were conducted on the ground floor of the two-story, two-room configuration, which had overall dimensions of 6.5~m (21.3~ft) by 9.2~m (30.2~ft).
-Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the test floor.
-A fully dimensioned plan view of the floor is presented in Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout_Detailed} in Appendix~\ref{app:floor_plans}.
+Tests were conducted in a two-room configuration located on the ground floor of the two-story section.
+The overall dimensions of the test floor were 6.5~m (21.3~ft) by 9.2~m (30.2~ft).
+Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout} contains a basic plan view of the two-room configuration, and a fully dimensioned plan view of the test floor is presented in Figure~\ref{fig:Delaware_County,_PA_Burn_Building_Layout_Detailed} in Appendix~\ref{app:floor_plans}.
 
@@
 
-The burn room where the fuel load was located measured 3.8~m (12.5~ft) by 5.7~m (18.7~ft) with a ceiling height of 3.35~m (11.0~ft).
-The adjacent room where the water was applied for gas cooling measured 4.1~m (13.4~ft) by 5.7~m (18.7~ft), also with a ceiling height of 3.35~m (11.0~ft).
-The open doorway that connected the burn room to the adjacent room and the doorway from the adjacent room to the exterior both measured 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
+The fuel load was located in the burn room, which had interior dimensions of 3.8~m (12.5~ft) by 5.7~m (18.7~ft) and a ceiling height of 3.4~m (11.0~ft).
+Water application for the purpose of gas cooling always occurred in the adjacent room, which had interior dimensions of 4.1~m (13.4~ft) by 5.7~m (18.7~ft) and a ceiling height of 3.4~m (11.0~ft).
+The open doorway that connected the burn room to the gas cooling room and the doorway from the gas cooling room to the exterior both measured 2.0~m (6.5~ft) high and 0.9~m (3.0~ft) wide.
 
@@
 They were designed to simulate a single floor of a residential structure.
-The outer wall of each structure was composed of interlocking concrete blocks 0.61~m (2~ft) wide, 0.61~m (2~ft) high and 1.22~m (4~ft) long.
-The interior dimensions of each structure were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
+The outer wall of each structure was composed of interlocking concrete blocks 0.6~m (2.0~ft) wide, 0.6~m (2.0~ft) high and 1.2~m (4.0~ft) long.
+The interior dimensions of each structure were 6.1~m (20.0~ft) wide, 11.0~m (36.0~ft) long, and 2.4~m (8.0~ft) high.
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 
-Each structure had a burn room, approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) and 2.4~m (8.0~ft) in height and a hallway connecting the burn room to the front of the structure via a small entry foyer.
-The hallway was 0.95~m (3.1~ft) wide and 5.4~m (17.6~ft) long and the entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft).
-The ceiling height in the hallway and entry foyer was 2.4~m (8~ft).
-The open door on north side from the exterior to the entry foyer was 2.0~m (6.5~ft) high and 0.9~m (2.9~ft) wide.
+Each structure had a burn room with interior dimensions of approximately 6.0~m (19.6~ft) by 4.4~m (14.3~ft) by 2.4~m (8.0~ft) high.
+A 5.4~m (17.6~ft) long hallway with a width of 0.9~m (3.1~ft) and ceiling height of 2.4~m (8.0~ft) connected the burn room to a small entry foyer at the front of the structure.
+The entry foyer was 1.2~m (4.1~ft) by 1.9~m (6.1~ft) and had a ceiling height of 2.4~m (8.0~ft).
+A 2.0~m (6.5~ft) high by 0.9~m (3.0~ft) wide open doorway on the north side of the structure connected the entry foyer to the exterior.
 The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide.
-A basic plan view of the structure is presented in Figure~\ref{fig:Test_Structure_Floor_Plan}, and a fully dimensioned plan view of the structure is included in in Appendix~\ref{app:floor_plans}.
+A basic plan view of the structure is presented in Figure~\ref{fig:Test_Structure_Floor_Plan}, and a fully dimensioned plan view is included in Figure~\ref{fig:Test_Structure_Floor_Plan_Detailed} in Appendix~\ref{app:floor_plans}.
 
@@
 The interior walls of the structure were framed with steel studs and track.
-The studs were set to 0.40~m (16~in) centers.
-The ceiling support was composed of wood truss joist I-beams (TJIs) with a 299~mm (11.75~in) depth.
-The TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board web.
-Tongue and grove, 18.3~mm (0.72~in) thick, oriented strand board was attached to the top of the TJIs.
+The studs were set to 0.4~m (16~in) centers.
+The ceiling support was composed of wood truss joist I-beams (TJIs) with a 0.3~m (11.75~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web.
+Tongue and grove, 18~mm (0.72~in) thick, OSB was attached to the top of the TJIs.
 
 The interior walls of the burn room were lined with 13~mm (0.5~in) thick cement board.
-The ceiling of the burn room was the exposed ``floor assembly''.
+The ceiling of the burn room was the exposed wood TJIs from the structure's ceiling support.
 The walls of the hallway and entry foyer were composed of 16~mm (0.63~in) Type X gypsum board.
@@
 
-A second story was added to the west single-story structure in order to conduct suppression experiments in a larger fire compartment than the fire compartment in the single story and to examine the impact of the fire and suppression in a remote compartment (upstairs) that was not directly exposed to the hose stream (see Figure~\ref{fig:delco_2story}).
+A second story was added to the west single-story structure in order to conduct suppression experiments in a fire compartment larger than the single-story fire compartment and to examine the impact of the fire and suppression on a remote compartment (the second floor) not directly exposed to the hose stream (see Figure~\ref{fig:delco_2story}).
 
@@
 
-The outer walls of the bottom floor of the two-story structure were identical to that of the single-story structures described above but with an open floor plan.
-The interior dimensions were 6.1~m (20~ft) wide, 11~m (36~ft) long and 2.4~m (8~ft) high.
-Figure~\ref{fig:dimensioned_first_2story} shows a basic floor plan of the reconfigured first floor.
-A fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
-A stairwell was built to connect the two floors of the structure.
-The stairs had a 180~mm (7.25~in) rise and 190~mm (7.5~in) run and started 1.6~m (5.25~ft) off the south wall with a width of 1.2~m (4~ft) off the east wall.
-The second story walls were wood framed with 51~mm (2~in) by 102~mm (4~in) studs.
+The outer walls of the bottom floor of the two-story structure were identical to the outer walls of the single-story structures described above, but the interior layout of the bottom floor was an open floor plan.
+The large, open space on the interior of the ground floor was approximately 6.1~m (20.0~ft) wide, 11.0~m (36.0~ft) long, and 2.4~m (8.0~ft) high.
+A basic plan view of the reconfigured floor is presented in Figure~\ref{fig:dimensioned_first_2story}, and a fully dimensioned plan view is included in Figure~\ref{fig:dimensioned_first_2story_detailed} in Appendix~\ref{app:floor_plans}.
+
+A set of stairs, each with a 180~mm (7.25~in) rise and 190~mm (7.5~in) run, was built along the interior of the east wall to connect the two floors of the structure.
+The stairway was 1.2~m (4.0~ft) wide, and the edge of the bottom step was located 1.6~m (5.25~ft) from the south wall.The second story walls were wood framed with 51~mm (2.0~in) by 102~mm (4.0~in) studs.
 The studs were set to 0.40~m (16~in) centers.
-The interior  walls were protected by 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
-The exterior walls were protected with 11~mm (0.31~in) oriented strand board and 8~mm (0.31~in) fiber cement lap siding.
-Figure~\ref{fig:dimensioned_second_2story} shows a basic floor plan of the second story of the modified west structure, and a fully dimensioned plan view of the floor is included in Appendix~\ref{app:floor_plans}.
+The interior walls were protected by a layer of 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock cement board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
+The exterior walls were protected by 11~mm (0.31~in) thick OSB and 8~mm (0.31~in) thick fiber cement lap siding.
+Figure~\ref{fig:dimensioned_second_2story} shows a basic plan view of the second story of the modified west structure, and a fully dimensioned plan view of the floor is provided in Figure~\ref{fig:dimensioned_second_2story_detailed} in Appendix~\ref{app:floor_plans}.
 
@@
 The east and south walls of the burn room were covered with 15~mm (0.59~in) thick sheets of plywood.
-The wood ``flooring assembly'', composed of 12 TJIs and nine sheets of oriented strand board (OSB), served as the ceiling of the burn room.
+The wood ``flooring assembly'', composed of 12 TJIs and nine sheets of OSB, served as the ceiling of the burn room.
 The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.
@@
 \subsection{Ventilation Limited Fires}
-Due to recent research conducted by NIST and the UL Firefighter Safety Research Institute (FSRI), the fire service has a renewed interest in controlling the air available to a ventilation limited compartment fire.
+Due to recent research conducted by NIST and the Underwriters Laboratories Firefighter Safety Research Institute, the fire service has a renewed interest in controlling the air available to a ventilation limited compartment fire.
 Limiting the air (oxygen) available for combustion is one means of limiting the heat release rate.
@@
 
-This study conducted by NIST was part of a larger research project led by California Polytechnic State University (Cal Poly), San Luis Obispo in collaboration with the Montgomery County (MD) Fire and Rescue Service.
+This study conducted by NIST was part of a larger research project led Cal Poly in collaboration with the MCFRS.
 This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
 
-Experiments were conducted to investigate the capabilities and limitations of compressed air foam (CAF) relative to water when used for interior structural fire fighting in residential structures.
+Experiments were conducted to investigate the capabilities and limitations of CAF relative to water when used for interior structural fire fighting in residential structures.
 The experimental designs were developed based on a project planning workshop led by the Fire Protection Research Foundation~\cite{Grant:2011}.
@@
 
-Full-scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
 The experimental configurations were designed to be representative of residential fire scenarios.
@@
 
-This study was part of a larger DHS/FEMA Assistance to Firefighters Research and Development Grant project led by California Polytechnic State University (Cal Poly), San Luis Obispo.
-The authors would like to acknowledge the support of the Cal Poly team, especially: Fred Mowrer, Christopher Dicus, Thomas Korman and Sean Mitchell.
-
-The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Adam Barowy (currently with UL), Kelly Opert (currently with UL) and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
+This study was part of a larger DHS/FEMA Assistance to Firefighters Research and Development Grant project led by Cal Poly.
+The authors would like to acknowledge the support of the Cal Poly team, especially: Fred Mowrer, Christopher Dicus, Thomas Korman, and Sean Mitchell.
+
+The authors would like to thank Roy McLane (currently with Thermal Fabrication), Kristopher Overholt (currently with Continuum Analytics), Adam Barowy (currently with Underwriters Laboratories), Kelly Opert (currently with Underwriters Laboratories), and Jay McElroy (retired) from NIST for their contributions in preparing and conducting these experiments.
 These experiments could not have been conducted without them.
 
-Thank you to Chief Scott Goldstein and former Chief Steve Lohr of the Montgomery County (MD) Fire and Rescue Service for their support of this study.
-The authors would also like to thank the Montgomery County (MD) firefighters that supported the experiments: Alan Butsch, Daniel Hudson, Michael Johns, Steven Neubauer, Curtis Poole, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph Thomas, and Douglas Wallace.
+Thank you to Chief Scott Goldstein and former Chief Steve Lohr of the MCFRS for their support of this study.
+The authors would also like to thank the MCFRS firefighters that supported the experiments: Alan Butsch, Daniel Hudson, Michael Johns, Steven Neubauer, Curtis Poole, Sean Regan, Chris Reilly, Bryan Rojtas, Ralph Thomas, and Douglas Wallace.
 
@@
 
-The Delaware County Emergency Services Training Center provided the location and logistical support for these experiments.
+The Delaware County ESTC provided the location and logistical support for these experiments.
 The Delaware County team was under the direction of Kerby Kerber.
-The construction and test support team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale and Todd John.
+The construction and test support team included: Joe Bingham, Dave Wright, Dave Nercesian (small engine repair), Mike Gura, Scott Wiercinski, Bill Fields (Fields Fire Protection), John Hale, and Todd John.
 
@@
 Thanks to all involved for assisting in generating data that will aid the fire service in making evidence based tactical choices.
-A special thanks to Joseph Scheffey of Jensen Hughes and Nelson Bryner of NIST for a thorough technical review of this manuscript.
+A special thanks to Joseph Scheffey of JENSEN HUGHES and Nelson Bryner of NIST for a thorough technical review of this manuscript.
 

### 2016-12-07 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor edits to CAF report

@@
 
-Twenty-one of the spray density tests were conducted in the concrete burn building that was later used for the gas cooling tests, and twelve of the tests were conducted in the experimental structures that were later used for the fire suppression tests.
+Twenty-one of the spray density tests were conducted in the concrete burn building that was later used for the gas cooling tests, and 12 of the tests were conducted in the experimental structures that were later used for the fire suppression tests.
 The test variables were the nozzle height, nozzle location within the test structure, and the nozzle pattern (Figure~\ref{fig:Spray_Density_Nozzle_Patterns}).
@@
 A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
-A legend, which clarifies the instrumentation schematics discussed in the following sections, is included in Figure~\ref{fig:Instrumentation_Legend}.
+A legend to clarify the instrumentation schematics presented in the following sections is included in Figure~\ref{fig:Instrumentation_Legend}.
 
@@
 Each of the bare-bead thermocouple arrays had 11 thermocouples.
-The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1~ft) apart with the bottom thermocouple being 3.05~m (10~ft) below the ceiling.
+The top thermocouple was placed at the ceiling and each subsequent thermocouple was spaced 0.3~m (1.0~ft) apart with the bottom thermocouple being 3.1~m (10.0~ft) below the ceiling.
 There were six velocity probes and solid thermocouples centered at the external doorway to the gas cooling room.
-The top probe was 0.15~m (0.5~ft) below the door soffit, the second probe was 0.3~m (1~ft) below the soffit, and the remaining four were spaced 0.3~m (1~ft) apart with the bottom probe being 1.52~m (5~ft) below the soffit.
-The total heat flux gauge/radiometer set was positioned 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
+The top probe was 0.2~m (0.5~ft) below the door soffit, the second probe was 0.3~m (1.0~ft) below the soffit, and the remaining four were spaced 0.3~m (1.0~ft) apart with the bottom probe being 1.5~m (5.0~ft) below the soffit.
+The total heat flux gauge/radiometer set was positioned 0.2~m (0.5~ft) off the ground and aimed to view the ceiling.
 
@@
 Each bare-bead thermocouple array had eight thermocouples.
-The top sensor was 0.03~m (1~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1~ft) apart with the bottom thermocouple being 2.13~m (7~ft) below the ceiling.
+The top sensor was 0.03~m (1.0~in) below the ceiling and the remaining thermocouples were spaced 0.3~m (1.0~ft) apart with the bottom thermocouple being 2.1~m (7.0~ft) below the ceiling.
 The three bi-directional probe arrays had unique sensor locations.
-For the window array, there were four sensor pairs located 0.28~m (0.95~ft), 0.58~m (1.90~ft), 0.84~m (2.85~ft), and 1.16~m (3.8~ft) below the soffit.
-For the hallway array, the seven sensor pairs started 0.3~m (1~ft) below the ceiling and were spaced every 0.3~m (1~ft) ending 2.13~m (7~ft) below the ceiling.
-The doorway array also had seven sensor pairs, but the first pair was located 0.15~m (0.5~ft) below the soffit.
-The remaining sensors were spaced every 0.3~m (1~ft) with the bottom pair 1.83~m (6~ft) below the doorway soffit.
-The total heat flux gauge/radiometer pairs were set to be 0.15~m (0.5~ft) off the ground and aimed to view the ceiling.
-The pairs of total heat flux gauges were set 1~m (3~ft) off the ground with one sensor ``looking'' vertical at the ceiling and the other horizontal.
+For the window array, there were four sensor pairs located 0.3~m (1.0~ft), 0.6~m (1.9~ft), 0.9~m (2.9~ft), and 1.2~m (3.8~ft) below the soffit.
+For the hallway array, the seven sensor pairs started 0.3~m (1.0~ft) below the ceiling and were spaced every 0.3~m (1.0~ft) ending 2.1~m (7.0~ft) below the ceiling.
+The doorway array also had seven sensor pairs, but the first pair was located 0.2~m (0.5~ft) below the soffit.
+The remaining sensors were spaced every 0.3~m (1.0~ft) with the bottom pair 1.8~m (6.0~ft) below the doorway soffit.
+The total heat flux gauge/radiometer pairs were set to be 0.2~m (0.5~ft) off the ground and aimed to view the ceiling.
+The pairs of total heat flux gauges were set 1.0~m (3.3~ft) off the ground with one sensor ``looking'' vertical at the ceiling and the other horizontal.
 
@@
 Each of the bare-bead arrays had eight thermocouples with the same spacing as the single-story tests.
-The bi-directional probe and solid thermocouple arrays also had eight sensors with the first probe 0.08~m (0.25~ft) below the soffit and the remaining probes at 0.34~m (1.1~ft), 0.61~m (2~ft), 0.88~m (2.9~ft), 1.15~m (3.7~ft), 1.42~m (4.7~ft), 1.68~m (5.5~ft), and 1.95~m (6.4~ft) below the soffit.
+The bi-directional probe and solid thermocouple arrays also had eight sensors with the first pair 0.1~m (0.3~ft) below the soffit and the remaining pairs at 0.3~m (1.1~ft), 0.6~m (2.0~ft), 0.9~m (2.9~ft), 1.2~m (3.8~ft), 1.4~m (4.7~ft), 1.7~m (5.5~ft), and 2.0~m (6.4~ft) below the soffit.
 
@@
 
-The second story featured six bare-bead arrays and three bi-directional probe plus solid thermocouple arrays.
-The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1~m (3~ft) off the ground.
+The second story featured six bare-bead thermocouple arrays and three bi-directional probe plus solid thermocouple arrays.
+The second floor also had three heat flux sensor pairs (one facing horizontal and one facing vertical) that were 1.0~m (3.3~ft) off the ground.
 Figure~\ref{fig:fire_supp_second_2story} shows the positions of the instrumentation (see Figure~\ref{fig:Instrumentation_Legend} for reference on the symbols).
-The bare-bead thermocouple arrays featured eight sensors with the same spacing as the basement level.
-The bi-directional probe arrays at the south wall door and at the top of the stairwell were comprised of eight sensor pairs with the same spacing as the ground level.
-The third bi-directional probe array (3~m (9~ft) off the north wall and 0.6~m (2~ft) off the east wall) had eight sensor pairs with the same spacing at the bare-bead thermocouple arrays.
+The bare-bead thermocouple arrays featured eight sensors with the same spacing as the ground level.
+The bi-directional probe arrays at the south exterior door and at the top of the stairwell were comprised of eight sensor pairs with the same spacing as the ground level.
+The third bi-directional probe array located 3.0~m (9.8~ft) off the north wall and 0.6~m (2.0~ft) off the east wall had eight sensor pairs with the same spacing as the bare-bead thermocouple arrays.
 
@@
 Uncertainties are grouped into two categories according to the method used to estimate them.
-Type A uncertainties are those which are evaluated by statistical methods, and Type B are those which are evaluated by other means~\cite{Taylor&Kuyatt:1994}.
+Type A uncertainties are those evaluated by statistical methods, and Type B are those evaluated by other means~\cite{Taylor&Kuyatt:1994}.
 Type B analysis of systematic uncertainties involves estimating the upper (+~a) and lower (-~a) limits for the quantity in question such that the probability that the value would be in the interval ($\pm$~a) is essentially 100~\%.
 After estimating uncertainties by either Type A or B analysis, the uncertainties are combined in quadrature to yield the combined standard uncertainty.
-Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in the expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
+Then, the combined standard uncertainty is multiplied by a coverage factor of two, which results in an expanded uncertainty with a 95~\% confidence interval (2$\sigma$).
 For some of these components, such as the zero and calibration elements, uncertainties are derived from referenced instrument specifications.
@@
 The gas measurement instruments and sampling system used in this series of experiments have demonstrated an expanded (k~=~2) relative uncertainty of $\pm$~1~\% when compared with span gas volume fractions~\cite{Bundy:2007}.
-Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$~12~\% was applied to the results~\cite{Lock:1}.
+Given the non-uniformities and movement of the fire gas environment and the limited set of sampling points in these experiments, an estimated uncertainty of $\pm$~12~\% is applied to the results~\cite{Lock:1}.
 
@@
 The bi-directional probes used similar pressure transducers as those used for the differential pressure measurements discussed above.
-Bare-bead Type K thermocouples are co-located with each probe.
+Bare-bead Type K thermocouples were co-located with each probe.
 A gas velocity measurement study examining the doorway flow of pre-flashover compartment fires yielded expanded uncertainty measurements ranging from $\pm$~0.14 to $\pm$~0.22 for bi-directional probes of similar design~\cite{Bryant:FSJ2009}.
@@
 Water flow rate was measured with a pressure and flow meter combination.
-The meter consists of a section of 63.5~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4800~l/min (1250~gpm).
-The pressure transducer and paddlewheel both connect to the battery operated control box where the pressure transducer voltage is converted to a pressure and the paddlewheel pulse count is converted to a volumetric flow rate.
+The meter consisted of a section of 64~mm (2.5~in) cast aluminum pipe with a 0--4.1~MPa (0--600~psi) pressure transducer and a paddlewheel type flow sensor with a range of 0 to 4730~l/min (1250~gpm).
+The pressure transducer and paddlewheel both connected to the battery operated control box where the pressure transducer voltage was converted to a pressure and the paddlewheel pulse count was converted to a volumetric flow rate.
 The manufacturer reports a $\pm$~5~\% calibration expanded uncertainty for the flow sensor and $\pm$~3~\% calibration expanded uncertainty for the pressure sensor~\cite{Akron:2009}.
@@
 Wood pallets were used as the fuel source for the gas cooling experiments.
-The pallets were approximately 1.2~m (4.0~ft) by 1.0~m (3.3~ft) by 0.13~m (0.42~ft) thick and ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lb).
-The initial fuel load consisted of 10 pallets, arranged in two stacks of five, as shown in Figure~\ref{fig:Burn_Building_Fuel_Load}.
+The pallets were approximately 1.2~m (3.9~ft) by 1.0~m (3.3~ft) by 123~mm (4.8~in) thick and ranged in mass from 13.6~kg (29.9~lb) to 26.4~kg (58.1~lb) with an average of 18.4~kg (40.5~lb).
+The initial fuel load consisted of 10 pallets, arranged in two stacks of five, at the locations shown in Figure~\ref{fig:Burn_Building_Fuel_Load}.
 Approximately one half of a bale of excelsior, 13.0~kg (28.6~lb), was mixed with the pallets to aid with ignition.
-Figure~\ref{fig:Burn_Building_Fuel_Load} also provides dimensioned locations of the two stacks of pallets within the burn room.
 
@@
 Pallets were added to the existing fuel locations until the flames from the piles reached the ceiling of the burn room again.
-Then, the shutters on the window were closed, and the temperature of the hot gas layer in the adjacent room was monitored in preparation for starting another gas cooling experiment.
+Then, the shutters on the window were closed, and the temperature of the hot gas layer in the adjacent room was monitored in preparation for another gas cooling experiment.
 The number of pallets added each time varied.
@@
 An image of the fuel arrangement is shown in Figure~\ref{fig:Furniture_Fuel_Load}.
-The sofas and chairs were set up to mimic a typical seating area with one couch against the south wall and one couch against the east wall, each positioned 0.9~m (36~in) away from the southeast corner.
+The sofas and chairs were set up to mimic a typical seating area with one couch against the south wall and one couch against the east wall, each positioned 0.9~m (3.0~ft) away from the southeast corner.
 A chair was placed adjacent to each couch.
-The specific locations can be found in the dimensioned schematic, Figure~\ref{fig:Furniture_Fuel_Load_Dimensions}.
-In total, this fuel package contains approximately 336~kg (739~lb) of fuel consisting of wood, flexible polyurethane (PU), polyester (PE),and polypropylene (PP).
+The specific locations can be found in Figure~\ref{fig:Furniture_Fuel_Load_Dimensions}.
+In total, this fuel package contained approximately 336~kg (739~lb) of fuel comprised of wood, flexible polyurethane (PU), polyester (PE), and polypropylene (PP).
 Table~\ref{tab:Fire_Suppression_Fuel_Masses} provides a breakdown on the fuel composition for these experiments.
@@
 The fuel load for test numbers 9 through 12 consisted of one bale of hay, 12 pallets, 11.5 sheets of plywood on the walls, and the wood ``floor assembly''.
-Two stacks of pallets with hay were used as the first items ignited in each experiment.
+Two stacks of pallets with hay were the first items ignited in each experiment.
 Each stack was composed of six pallets with a half bale of hay layered between the six pallets.
 Figure~\ref{fig:Wood_Fuel_Load} shows the pallets prior to ignition.
-The pallets and hay were weighed before each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232.4~kg (511.3~lb).
+The pallets and hay were weighed before each experiment, and the average mass of the two stacks of pallets and the bale of hay over the four experiments was 232~kg (511~lb).
 
@@
 
-The pallet stacks were located 0.3~m (12~in) away from the east and south walls of the burn room (see Figure~\ref{fig:Wood_Fuel_Load_Dimensions}).
-The pallets were 1.2~m (48~in) long, 1.0~m (40~in) wide, and 123~mm (4.8~in) high.
-The stacks were spaced 150~mm (6~in) apart.
+The pallet stacks were located 0.3~m (1.0~ft) away from the east and south walls of the burn room (see Figure~\ref{fig:Wood_Fuel_Load_Dimensions}).
+The pallets were 1.2~m (3.9~ft) long, 1.0~m (3.3~ft) wide, and 123~mm (4.8~in) high.
+The stacks were spaced 150~mm (6.0~in) apart.
 One layer of 13~mm (0.5~in) thick gypsum board panels were laid on the concrete floor under the wood pallets to form a protective layer to minimize thermal damage to the concrete floor.
-The east and south walls of the burn room were covered with 15~mm (0.59~in) thick sheets of plywood.
-The wood ``flooring assembly'', composed of 12 TJIs and nine sheets of OSB, served as the ceiling of the burn room.
-The open doorway to the burn room on the south side was covered with a 2.4~m (8~ft) tall by 1.2~m (4~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.19~in) thick.
+The east and south walls of the burn room were covered with 15~mm (0.6~in) thick sheets of plywood.
+The ceiling of the burn room was composed of 12 wood TJIs and nine sheets of OSB that were part of the structure's ceiling support.
+The opening to the exterior on the south side of the burn room was covered with a 2.4~m (8.0~ft) tall by 1.2~m (4.0~ft) wide piece of medium density fiberboard paneling that was 5~mm (0.2~in) thick.
 
@@
 In June of 2015, the larger compartment experiments, experiments 13 through 20, were conducted in the two-story structure.
-Two different fuel packages located on the ground level were utilized throughout the experiments: experiments 13 and 14 used a fuel package composed primarily of furniture, and experiments 15 through 20 used the same fuel package with an addition of two stacks of wood pallets.
+Two different fuel packages located on the ground level were utilized throughout the experiments: experiments 13 and 14 used a fuel package composed primarily of furniture, and experiments 15 through 20 used the same fuel package with the addition of two stacks of wood pallets.
 
@@
 
-The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg; 51.4~m$^2$ (553~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.63~in) x 1.2~m (4~ft) x 2.4~m (8~ft) along the east, west, and south walls and ceiling.
-The three couches were aligned along the west wall and spaced 1.2~m (4~ft) apart.
+The fuel load for experiments 13 and 14 consisted of three sofas with an average mass of 48.7~kg (107~lb); 51.4~m$^2$ (553~ft$^2$) of carpet and padding; and approximately 38 sheets of OSB paneling with dimensions 16~mm (0.6~in) x 1.2~m (4.0~ft) x 2.4~m (8.0~ft) along the east, west, and south walls and ceiling.
+The three couches were aligned along the west wall and spaced 1.2~m (4.0~ft) apart.
 The specific locations can be found in the dimensioned schematic Figure~\ref{fig:furniture_2story}.
@@
 
-For experiments 15 through 20, two stacks of wood pallets were added to the fuel load consisting of three sofas; OSB lining on the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
+For experiments 15 through 20, two stacks of wood pallets were added to the fuel load consisting of three sofas; OSB lining the ceiling and walls; and the polypropylene carpeting over polyurethane foam padding.
 Each stack had 10 pallets and an approximate mass of 175~kg (386~lb).
@@
 Spray density experiments were conducted by placing 0.23~m$^2$ (2.5~ft$^2$) interlocking water collection pans across the floor surface area of the burn rooms within each structure (see Figure~\ref{fig:water_buckets}).
-The depth of the pans was 0.3 m (1 ft).
+The depth of the pans was 0.3~m (1.0~ft).
 Water or CAF was flowed for a specified duration or until it appeared that a pan was filled.
@@
 In the table, ``GC'' stands for the gas cooling experiments, and ``SE'' stands for the suppression experiments.
-For all experiments, 30~m (100~ft) of 4.45~cm (1.75~in) diameter hoseline connected to a ``blitz-fire'' monitor with a Metro 1 nozzle was used.
+For all experiments, 30.0~m (100~ft) of 45~mm (1.75~in) diameter hoseline connected to a ``blitz-fire'' monitor with a Metro 1 nozzle was used.
 
@@
 
-For the spray density tests listed in Table~\ref{tab:spray_density_tests}, the ``mid'' position had the centerline of the stream aimed at 2.44~m (8~ft) south of the north wall and 2.13~m (7~ft) west of the east wall in the concrete burn building.
-The ``back'' position had the centerline of the stream aimed at 3.36~m (11~ft) south of the north wall and 2.13~m (7~ft) west of the east wall in the concrete burn building.
+For the spray density tests listed in Table~\ref{tab:spray_density_tests}, the ``mid'' position had the centerline of the stream aimed at 2.4~m (8.0~ft) south of the north wall and 2.1~m (7.0~ft) west of the east wall in the concrete burn building.
+The ``back'' position had the centerline of the stream aimed at 3.4~m (11.0~ft) south of the north wall and 2.1~m (7.0~ft) west of the east wall in the concrete burn building.
 Figure~\ref{fig:stream_position} shows the streams from the monitor nozzle for the middle and back positions.
@@
 \end{table}
-For the fire suppression spray density experiments, Table~\ref{tab:spray_density_tests2}, the hallway position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the south wall and 1.53~m (5~ft) east of the west wall.
-The fire room position had the center of the stream aimed at the ceiling of the burn room, 2.14~m (7~ft) north of the south wall and 3.05~m (10~ft) west of the east wall.
+For the fire suppression spray density experiments listed in Table~\ref{tab:spray_density_tests2}, the ``hallway'' position had the center of the stream aimed at the ceiling of the burn room, 2.1~m (7.0~ft) north of the south wall and 1.5~m (5.0~ft) east of the west wall.
+The ``fire room'' position had the center of the stream aimed at the ceiling of the burn room, 2.1~m (7.0~ft) north of the south wall and 3.1~m (10.0~ft) west of the east wall.
 
@@
 Using the same data, the focus of this analysis was to look at trends within the aggregate data.
-During each test, the fire was ignited and developed until the temperature 1.83~m (6~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
-This condition was evidence that a hot gas layer at least 1.83~m (6~ft) deep had filled the room next to the burn room.
+During each test, the fire was ignited and developed until the temperature 1.8~m (6.0~ft) below the ceiling in the gas cooling room reached or exceeded 250~$^{\circ}$C (482~$^{\circ}$F).
+This condition was evidence that a hot gas layer at least 1.8~m (6.0~ft) deep had filled the room adjacent to the burn room.
 Once this criteria was met, gas cooling began.
@@
 	\includegraphics[width=\columnwidth]{../Figures/Gas_Cooling/GCSeries4_TC_A3}
-	\caption{Time Series of Multiple Gas Cooling Experiments from 1 of 9 Burn Sequences}
+	\caption{Time Series of Multiple Gas Cooling Experiments During a Continuous Burn Sequence}
 	\label{fig:gas_cooling_exp4}
@@
 Figures~\ref{fig:gas_cooling_sub1} and \ref{fig:gas_cooling_sub5} show the variation of the impact of the suppression stream on cooling location for three consecutive water and CAF tests, respectively.
-For both sets, a solid stream from a 22~mm (0.88~in) nozzle in the middle position was used.
-The data show that thermocouples from Array 2 (``TC~A2'' in the legend), the middle plot of both figures, has more significant temperature decreases than the other two arrays (``TC~A1'' and ``TC~A3'').
+For both sets, a solid stream from a 22~mm (0.9~in) nozzle in the middle position was used.
+The data show that thermocouples from Array 2 (``TC~A2'' in the legend), the middle plot in both figures, have more significant temperature decreases than the other two arrays (``TC~A1'' and ``TC~A3'').
 This is the result of Array 2 being directly ``hit'' by the suppression stream.
 Gas Cooling Array 1 also exhibits some amount of suppression agent impact.
-Array 3 is located behind the area where the stream impacts the ceiling for both the middle and back nozzle positions.
-As a result, it remained dry and seems to provide the best representation of the gas cooling.
+Array 3 was located behind the area where the stream impacted the ceiling for both the middle and back nozzle positions.
+As a result, it remained dry and appears to provide the best representation of the gas cooling.
 
@@
 
-To better quantify the effectiveness of the suppression agents, the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple trees were analyzed.
+To better quantify the effectiveness of the suppression agents, the maximum temperature differences associated with each gas cooling event for each agent from the three thermocouple arrays were analyzed.
 Figure~\ref{fig:combined_all} compares the temperature differences at each thermocouple position (via a scatterplot) for 30 of the 88 experiments.
-The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, that were directly comparable (see Table~\ref{tab:Gas_Cooling_Descriptions}).
+The 30 experiments are actually pairs of experiments, 15 water and 15 CAF, that are directly comparable (see Table~\ref{tab:Gas_Cooling_Descriptions}).
 These experiments included solid streams, straight streams, and narrow fog streams at both nozzle positions.
@@
 To further analyze the data, the temperature differences can be separated by each of the three thermocouple arrays in the gas cooling room.
-Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of three thermocouple arrays (TC A1, TC A2, and TC A3).
-Ideally, the thermocouple is providing an estimate of the temperature of the gas that surrounded it.
-However, the thermocouple is actually measuring its own temperature.
+Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions} shows the placement of the three thermocouple arrays (TC A1, TC A2, and TC A3).
+Ideally, a thermocouple provides an estimate of the temperature of the gas surrounding it.
+However, a thermocouple actually measures its own temperature.
 So, if a droplet of water or some CAF clings to a thermocouple, the temperature provided by that thermocouple will be different than the surrounding gas temperature.
@@
 Based on the monitor position (see Figure~\ref{fig:Gas_Cooling_Instrumentation_Dimensions}), thermocouple arrays A1 and A2 had more direct impact from the suppression agent compared to thermocouple array A3.
-As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the middle position compared to the positions of the thermocouple trees.
+As an example, Figure~\ref{fig:Burn_Building_Test_18b} shows the distribution of the agent within the burn building from a spray density test for a straight stream with CAF at the middle position compared to the positions of the thermocouple arrays.
 
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A1_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A1 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Array A1 Experimental Pairs}
 	\label{fig:CAFS_Water_A1_all}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A2_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A2 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Array A2 Experimental Pairs}
 	\label{fig:CAFS_Water_A2_all}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_A3_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Tree A3 Experimental Pairs}
+	\caption{CAF vs Water Gas Cooling Comparison for All Thermocouple Array A3 Experimental Pairs}
 	\label{fig:CAFS_Water_A3_all}
@@
 The thermocouple array data can also be decomposed as a function of nozzle position: 12 middle position experimental pairs and three back experimental pairs.
-Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the 12 replicate tests with the monitor nozzle in the middle position.
-Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3 respectively for the three replicate tests with the monitor nozzle in the back position.
-Again, note that the best fit occurs with the data from thermocouple array 3 for both nozzle positions.
+Figures~\ref{fig:CAFS_Water_A1_mid}, \ref{fig:CAFS_Water_A2_mid}, and \ref{fig:CAFS_Water_A3_mid} show the temperature difference scatter at thermocouple arrays A1, A2, and A3, respectively, for the 12 replicate tests with the monitor nozzle in the middle position.
+Figures~\ref{fig:CAFS_Water_A1_back}, \ref{fig:CAFS_Water_A2_back}, and \ref{fig:CAFS_Water_A3_back} show the temperature difference scatter at thermocouple arrays A1, A2, and A3, respectively, for the three replicate tests with the monitor nozzle in the back position.
+Again, note that the best fit occurs with the data from thermocouple array A3 for both nozzle positions.
 This analysis of the data results in the same conclusions as the analysis from the Mitchell paper \cite{Mitchell:1}: the gas cooling performance of CAF is similar to water under these conditions.
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A1_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A1 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Array A1 Replicates}
 	\label{fig:CAFS_Water_A1_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A2_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A2 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Array A2 Replicates}
 	\label{fig:CAFS_Water_A2_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_mid_A3_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Tree A3 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Middle Position Thermocouple Array A3 Replicates}
 	\label{fig:CAFS_Water_A3_mid}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A1_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A1 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Array A1 Replicates}
 	\label{fig:CAFS_Water_A1_back}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A2_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A2 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Array A2 Replicates}
 	\label{fig:CAFS_Water_A2_back}
@@
 	\includegraphics[width=.7\columnwidth]{../Figures/Gas_Cooling/Combined_fullback_A3_scatter}
-	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Tree A3 Replicates}
+	\caption{CAF vs Water Gas Cooling Comparison for Back Position Thermocouple Array A3 Replicates}
 	\label{fig:CAFS_Water_A3_back}
@@
 The other four experiments used a wood pallet fuel load in a space with the ceiling and walls composed of wood-based materials (Section~\ref{sec:fire_suppression_pallet_fuel}).
-Ignition occurred in the rear of the single-story structure, and the available ventilation was through the front doorway.
+Ignition occurred in the south of the single-story structure, and the available ventilation was through the north doorway.
 For eight of the experiments, a rear window was opened to provide additional ventilation (see Table~\ref{tab:Test_Descriptions}).
@@
 The hallway nozzle was intended to simulate a crew advancing into a structure towards the burn room.
-Suppression from this location would be in the form of gas cooling, as the stream was not aimed at the seat of the fire (indirect interior attack).
+Suppression from this location was in the form of gas cooling, as the stream was not aimed at the seat of the fire (indirect interior attack).
 After the hallway nozzle was shutdown, there was a 15~s time period of no nozzle flow to simulate the crew advancing into the doorway of the fire room.
@@
 Table~\ref{tab:Test_Results} provides the impact of the two nozzle applications for the water and CAF tests.
-The table lists the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor as well as the change in heat flux 0.15~m (6~in) above the floor at the measurement location closest to the fire.
-These values reported in the table are immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
+The table lists the change in temperature 0.3~m (1.0~ft) below the ceiling and 0.3~m (1.0~ft) above the floor as well as the change in heat flux 0.2~m (6.0~in) above the floor at the measurement location closest to the fire.
+The values reported in the table are from immediately before and after the 15~s application period to assess the application agent, stream, and location on interior conditions.
 Recall that there was a 15~s gap between the hallway nozzle flow and the door nozzle flow.
@@
 While the fit is not as strong (R$^2$~=~0.643), the red line still falls within the experimental uncertainty, meaning that differences in the impact of CAF and water are indistinguishable.
-Despite being closer to the nozzles, thermocouple tree A2 shows similar temperature difference results from the hallway nozzle activation to the A1 array (see Figure~\ref{fig:fs_door_a2}).
+Despite being closer to the nozzles, thermocouple array A2 shows temperature difference results from the hallway nozzle activation that are similar to the A1 array (see Figure~\ref{fig:fs_door_a2}).
 At array A2 for the door nozzle (see Figure~\ref{fig:fs_door_a2}), the red dashed falls outside of the experimental uncertainty, indicating a slight advantage of cooling for CAF.
@@
 Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
-Ignition occurred in the southwest corner of the ground floor and available ventilation was through the ground floor double doors and the south exterior door on the second story of the structure.
+Ignition occurred in the southwest corner of the ground floor, and available ventilation was through the ground floor double doors and the south exterior door on the second story of the structure.
 The fires were intended to replicate room and contents basement fires typically seen within residential structures.
@@
 Table~\ref{tab:Test_Results_2} provides the impact of suppression for the water, class A foam, and CAF tests conducted in the two-story structure.
-The measurement location was on the floor above the fire, at the doorway to the stairwell which connects the floors.
-The thermocouples at this measurement location were isolated from any direct contact from the suppression stream.
-The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1~ft) above the floor in front of the stairway door.
+The measurement location was on the floor above the fire at the doorway to the stairwell.
+The thermocouples at this measurement location were isolated from any direct contact with the suppression stream.
+The table provides the change in temperature 0.3~m (1~ft) below the ceiling and 0.3~m (1.0~ft) above the floor in front of the stairway door.
 Figure~\ref{fig:fire_supp_second_2story} shows the position of the thermocouple array (TC A10).
@@
 This study focused on two key types of fire experiments: gas cooling and fire suppression.
-In each type of experiment, a comparison was conducted between plain water and compressed air foam being discharged from nozzles of similar type with similar mass flow rates.
-In both types of experiments, there were no significant measurable differences between the use of plain water or compressed air foam.
+In each type of experiment, a comparison was conducted between plain water and CAF being discharged from nozzles of similar type with similar mass flow rates.
+In both types of experiments, there were no significant measurable differences between the use of plain water or CAF.
 To expand upon the 2012 and 2013 tests described by Mitchell~\cite{Mitchell:1}, additional fire suppression experiments were conducted.
@@
 Water is the most widely used fire extinguishing agent because it is effective, environmentally friendly, nontoxic, inexpensive, and in many cases, readily available.
-In addition, water has a very high heat of vaporization per unit mass, at least four times as high as that of any other nonflammable liquid~\cite{NFPA}.
-The latent heat of vaporization of water is 2255~kJ/kg (970~Btu/lb.)~\cite{NFPA}.
-This means that 2255~kJ (2139~Btu) of energy is required to change 1~kg (2.2~lb.) of water into steam.
-When water is vaporized, its volume increases approximately 1,700 times.
+Additionally, water has a very high heat of vaporization per unit mass, at least four times as high as any other nonflammable liquid~\cite{NFPA}.
+The latent heat of vaporization of water is 2255~kJ/kg (970~Btu/lb)~\cite{NFPA}.
+This means that 2255~kJ (2139~Btu) of energy is required to change 1.0~kg (2.2~lb) of water into steam.
+When water is vaporized, its volume increases by approximately 1,700 times.
 Because the energy absorbing capabilities of water are well quantified, they can be used as a basis to calculate the theoretical minimum delivery rate of water needed to extinguish a burning material with a known heat (energy) release rate.
-Unfortunately, based on experience it has been estimated that water must be applied at 10 to 100 times the theoretical rate in order to control and extinguish the fire~\cite{Friedman:2}.
+Unfortunately, it has been estimated based on experience that water must be applied at 10 to 100 times the theoretical rate in order to control and extinguish a fire~\cite{Friedman:2}.
 As a result of this apparent inefficiency and the need to address fires containing a wide variety of materials, water-based fire fighting additives have been utilized for many years to enhance the fire fighting capabilities of ordinary water.
@@
 While CAF has been readily accepted for use in the wildland and wildland urban interface, the effectiveness or advantages of CAF for interior structural fire fighting was undocumented by experimental data.
-Questions remained regarding whether CAF provides improved gas cooling when compared to plain water.
+Questions remained regarding whether CAF provides improved gas cooling compared to plain water.
 During the planning of the experiments for this project, there were a range of hypotheses regarding potential outcomes.
 Some technical panel members thought that the excellent heat absorbing capacity of plain water would exceed the heat absorbing capabilities of CAF.
-Their position was based on the fact that CAF has injected air.
+Their position was based on the fact that CAF contains injected air.
 Because air is a great insulator, it might slow the heat transfer rate between the water and the fire gases and result in a reduced cooling rate.
@@
 The gas cooling experiments were designed to measure the ability of water streams and CAF streams to cool a hot gas layer without any application of agent to the source of the heat.
-The 3.35~m (11~ft) tall ceiling in the burn building allowed a hot gas layer of at least 1.83~m (6 ft) to form.
-During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at 1.83~m (6~ft) below the ceiling was attained prior to the beginning of gas cooling.
+The 3.4~m (11.0~ft) tall ceiling in the burn building allowed a hot gas layer of at least 1.8~m (6.0~ft) to form.
+During the testing, a minimum temperature of 250~$^{\circ}$C (482~$^{\circ}$F) at 1.8~m (6.0~ft) below the ceiling was attained prior to the beginning of gas cooling.
 In each gas cooling experiment, the same mass flow rate of water was used for both the plain water stream and the CAF stream.
-Typically, the volumetric flow rate of water was 7.57~L/s (120~gpm).
-The density of water is 1000~kg/m$^3$ (8.3~lb/gal), therefore the mass flow rate was 7.57~kg/s (16.7~lb/s).
+Typically, the volumetric flow rate of water was 7.57~l/s (120~gpm).
+The density of water is 1000~kg/m$^3$ (8.3~lb/gal).
+Therefore, the mass flow rate was 7.57~kg/s (16.7~lb/s).
 The average time of flow was approximately 15~s.
-A total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
+So, a total of 114~kg (251~lb) of water was introduced into each gas cooling experiment.
 
 When a CAF stream was used, it contained 0.3~\% foam concentration by volume.
-The density of the foam concentrate is 1055~kg/m$^3$ (8.8~lb/gal).
+The density of the foam concentrate was 1055~kg/m$^3$ (8.8~lb/gal).
 For a 15~s flow time, 0.34~kg (0.75~lb) of concentrate was used.
@@
 
-The estimated total expanded uncertainty of the temperature measurements in these experiments is $\pm$~15~\% (see Section~\ref{subsec:Uncertainty}).
-For the difference between two temperature measurements to be considered significantly different, the difference would have to be greater by more than $\pm$~15~\%.
+The total expanded uncertainty of the temperature measurements from these experiments was estimated as $\pm$~15~\% (see Section~\ref{subsec:Uncertainty}).
+So, in order for a difference between two temperature measurements to be considered significantly different, the two measurements must vary by more than $\pm$~15~\%.
 If the difference between two measurements was $\pm$~15~\% or less, the results are considered similar.
-The estimated uncertainty is based on previous studies where suppression with a water based agent was included.
-
-As mentioned in the results section, the conditions at TC Array 3 represented the ``best'' gas cooling results.
-It was impacted the least by agents hitting and cooling the thermocouples themselves.
-Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, it should be no surprise that the water is absorbing the energy from the upper layer.
-Air filled bubbles in the CAF stream had no discernible impact, either positive or negative, in the gas cooling experiments.
-At the same time, there was no measurable negative effect of the air bubbles with regard to gas cooling.
-
-The data from the thermocouples in TC Array 2 provide a sense of the impact of a combination of surface cooling and gas cooling.
-For example, when the nozzle was in the ``middle'' position, the straight or solid hose streams impacted the room's ceiling near the middle and created a fan pattern across the ceiling that caused the majority of the water to impact the location of TC Array 2 and the adjacent walls.
+The estimated uncertainty was based on previous studies where suppression with a water based agent was included.
+
+As mentioned in the results section (Section~\ref{sec:Gas_Cooling}), the conditions at TC Array 3 represented the ``best'' gas cooling results; it was impacted the least by agents hitting and cooling the thermocouples themselves.
+Under the given conditions of a residential scale room and the amount of water introduced into the hot gas layer, the water absorbed the energy from the upper layer.
+Air filled bubbles in the CAF stream had no discernible impact, positive or negative, in the gas cooling experiments.
+
+The data from the thermocouples in array A2 provide a sense of the impact of a combination of surface cooling and gas cooling.
+For example, when the nozzle was in the ``middle'' position, the straight or solid hose streams impacted the room's ceiling near the middle and created a fan pattern across the ceiling that caused the majority of the water to impact the location of array A2 and the adjacent walls.
 In this location, the data tended to favor water.
-However, this did not represent gas cooling.
+However, this wasn't representative of gas cooling.
 Rather, this represented some of the water or CAF hitting the thermocouples and cooling the surrounding gases.
-As a result, temperature reductions of the thermocouples in TC Array 2 are higher than those of the thermocouples in TC Array 3, as shown in Figures~\ref{fig:CAFS_Water_A2_mid} and \ref{fig:CAFS_Water_A3_mid}, respectively.
-
-TC Array 1 had the widest spread of temperature change.
-Depending on the nozzle configuration, there were tests where the thermocouples in TC Array 1 were directly impacted by water or CAF and other tests where there was no impact.
-Examination of the spray density figures in Appendix~\ref{app:spray_bb}, provides the range of agent collected in the bucket where TC Array 1 was located.
+As a result, temperature reductions measured by the thermocouples in array A2 were higher than those of the thermocouples in array A3, as shown in Figures~\ref{fig:CAFS_Water_A2_mid} and \ref{fig:CAFS_Water_A3_mid}, respectively.
+
+Array A1 had the widest spread of temperature change.
+Depending on the nozzle configuration, there were tests where the thermocouples in A1 were directly impacted by water or CAF and other tests where there was no impact.
+Examination of the spray density figures in Appendix~\ref{app:spray_bb} provides the range of agent collected in the bucket where array A1 was located.
 In many cases, such as the test CAF Straight Stream Mid, the amount of foam solution collected was near zero.
-In other cases, such as the test CAF Fog Mid, the amount of foam solution collected was more than 3~kg (6.6~lb).
+In other cases, such as the test CAF Fog Mid, the amount of foam solution collected was more than 3.0~kg (6.6~lb).
 Similar variations occurred with water.
-As a result, TC Array 1 did not provide consistent results for gas cooling.
-
-The data and results from this test series are not consistent with a hypothesis that firefighters were being injured during an interior fire fighting operation with CAF because CAF provided cooling similar to that of the equivalent flow rate of plain water.
+As a result, array A1 did not provide consistent results for gas cooling.
+
+The data and results from this test series are not consistent with a hypothesis that firefighters were being injured during interior fire fighting operations with CAF because CAF provided cooling similar to that of the equivalent flow rate of plain water.
 
@@
 Currently, the fire service uses ``fire flow'' formulas to estimate the flow rate of water needed to control a structure fire.
-The formulas are presented below and the results from the experiments described in this report will be compared with the calculated fire flows.
+The formulas are presented below, and the results from the experiments described in this report are compared with the calculated fire flows.
 
 \subsection{Iowa State University Fire Flow Formula}
-The Iowa Formula for determining the required fire flow rate for a given structure was developed by Keith Royer and Bill Nelson and is based on theoretical heat absorption capabilities of water \cite{Royer:ISU}.
+The Iowa State University formula for determining the required fire flow rate for a given structure was developed by Keith Royer and Bill Nelson and is based on theoretical heat absorption capabilities of water \cite{Royer:ISU}.
 The required fire flow rate ($\dot{V}$) in gpm is equal to the volume ($V$) of the fire compartment in cubic feet divided by 100:
@@
 
-For the formula as written, it is assumed that the fire compartment is "fully involved" and that the fire is ventilation limited.
-Due to inefficiencies in the application of water, some feel that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
-Applying the formula based on floor area yields an application density of 3.3~l/min/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.44~m (8~ft) or 4.1~l/min/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.05~m (10~ft).
-The fire room compartment volumes in these experiments ranged from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
+The formula assumes that the fire compartment is "fully involved" and that the fire is ventilation limited.
+Due to inefficiencies in the application of water, some think that the fire flow value from the Iowa State University formula should be multiplied by a factor of two to four~\cite{NFPA}.
+Applying the formula based on floor area yields an application density of 3.3~l/min/m$^2$ (0.08~gpm/ft$^2$) for ceiling heights of 2.4~m (8.0~ft) or 4.1~l/min/m$^2$ (0.10~gpm/ft$^2$) for ceiling heights of 3.1~m (10.0~ft).
+The fire room compartment volumes for the experiments described in this report ranged from approximately 66~m$^3$ (2330~ft$^3$) to 125~m$^3$ (4410~ft$^3$).
 The required flow rate for the fire room in the single-story structure based on the Iowa State University formula was approximately 87~l/min (23~gpm), and the required flow rate for the fire room in the lower level of the two-story structure was approximately 168~l/min (44~gpm).
-During the experiments, the flow rate was approximately 454~l/min (120~gpm), which exceeds the required flow rate of the Iowa State Formula.
+During the experiments, the flow rate was approximately 454~l/min (120~gpm), which exceeds the required flow rate produced by the Iowa State University formula.
 The fact that all of the fires were quickly controlled during the experiments is consistent with this methodology.
@@
 
-The fire rooms in these experiments ranged in floor area from approximately 26~m$^2$ (280~ft$^2$) to 51.4~m$^2$ (553~ft$^2$).
-Applying the NFA formula based on floor area yields a required flow rate for the single-story fire room of 352~l/min (93~gpm).
-The required flow rate for the fire room in the lower level of the two-story would be approximately 700~l/min (184~gpm).
+The fire rooms described in this report ranged in floor area from approximately 26~m$^2$ (280~ft$^2$) to 51.4~m$^2$ (553~ft$^2$).
+Applying the NFA formula based on floor area yields a required flow rate of 352~l/min (93~gpm) for the single-story fire room and a required flow rate of 700~l/min (184~gpm) for the fire room in the lower level of the two-story.
 Comparing the hose stream flow rates to the NFA formula requirements indicates that 454~l/min (120~gpm) was sufficient for the smaller room fire in the single-story but was below the required flow rate of approximately 700~l/min (184~gpm) for the large fire compartment in the two-story structure.
@@
 Limiting the air (oxygen) available for combustion is one means of limiting the heat release rate.
-If the heat release rate of a fire is reduced due to a lack of oxygen needed for combustion, then in theory, the amount of water needed to cool and suppress the fire should also be reduced.
-
-Both of the formulas listed above do not explicitly account for the ventilation of the fire structure, only the size of the fire structure.
-The most recent of the two formulas was developed in 1981, based on the fire ground experience of fire chiefs.
+If the heat release rate of a fire is reduced due to a lack of oxygen needed for combustion, then, in theory, the amount of water needed to cool and suppress the fire should also be reduced.
+
+Both of the formulas listed above account only for the size of the fire structure; they do not explicitly account for the ventilation of the structure.
+The most recent of the two formulas was developed based on the fire ground experience of fire chiefs in 1981.
 This experience was likely from fires that occurred in the 1960's and the 1970's.
-It has been demonstrated that the synthetic fuels which fill the homes of the 2000's burn faster and with higher heat release rates than the natural fuels that filled the homes in the 1940's and 1950's.
+It has been demonstrated that the synthetic fuels that fill the homes of the 2000's burn faster and with higher heat release rates than the natural fuels that filled homes in the 1940's and 1950's.
 The change of materials in homes began in the 1960's and has continued to present day~\cite{Kerber:2}.
-It was unlikely, however, that this change was factored into the NFA formula.
+It's unlikely that this change in fuels was factored into the NFA formula.
 
@@
 
-Following Equation~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room that is approximately 0.9~m (3~ft) wide and 2.1~m (6.9~ft) high could support a heat release rate of approximately 4~MW, assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
+Following Equation~\ref{eq:HRRSto_item}, a single open doorway to a residential scale room that is approximately 0.9~m (3.0~ft) wide and 2.1~m (6.9~ft) high could support a heat release rate of approximately 4~MW, assuming complete combustion of the oxygen that would flow through the doorway opening via natural convection.
 For twice the width of the open doorway (the doorway on the lower level of the two-story structure), the theoretical heat release rate that could be supported inside the compartment would be approximately 8~MW.
@@
 
-In the single-story structure, there was an additional window opening in some of the experiments which added ventilation to the room.
+In the single-story structure, there was an additional window opening in some of the experiments that added ventilation to the room.
 In the two-story structure, there was an additional open doorway that allowed exhaust gases from the fire compartment to flow up the stairs, through the second-story floor, and out of the structure.
@@
 Again, this is a simplified analysis, much like the current tools provided in fire department literature for the required fire flow rate.
-However, it demonstrates that for a residential scale room (in this study up to to 51.4~m$^2$ (553~ft$^2$)) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second or 120~gpm of water was adequate to quickly suppress the fire in the compartment.
+However, it demonstrates that for a residential scale room (in this study up to to 51.4~m$^2$ (553~ft$^2$)) with the equivalent of two open doorways supplying fresh air, a flow of 2~gallons per second, or 120~gpm, of water was adequate to quickly suppress the fire in the compartment.
 
 \subsection{Fuel Loads: Natural vs Synthetic}
-In all the suppression experiments, the fire was controlled with no more than 227~L (60~gal) or less of plain water or water in the form of CAF.
+In all the suppression experiments, the fire was controlled with no more than 227~l (60~gal) or less of plain water or water in the form of CAF.
 During the course of the suppression experiments, the fuel packages were modified to incorporate more wood-based fuels.
@@
 It was thought that with more exposed burning wood surfaces in the fuel load, CAF would have a better the opportunity to demonstrate a difference in suppression.
-As shown in Section~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling'' that was constructed of wood ``i-beams'' and OSB.
+As shown in Section~\ref{sec:fuel_load}, the wood fuel load consisted of stacks of wood pallets, plywood lined walls, and an exposed wood ``ceiling support'' that was constructed of wood TJIs and OSB.
 The experiments conducted with the wood fuel load did not demonstrate a significant difference between water and CAF.
@@
 As discussed previously, with the larger area and double the ventilation of the previous experiments, the fire should have been more challenging to the hose streams.
-There was also another variable that was be introduced: a firefighter controlling the nozzle.
+There was also another variable introduced in these experiments: a firefighter controlling the nozzle.
 Recall that in the single-story experiments, a monitor nozzle was used in a fixed position.
-As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surface of the burning fuel sufficiently and a rekindle would occur.
+As a result, after the initial fire knockdown, it was typical that the agent was not able to hit all surfaces of the burning fuel sufficiently and a rekindle would occur.
 This can be seen for both the water and CAF experiments in the data provided in Appendix~\ref{app:fire_suppression}.
@@
 During the additional flows, no significant differences were seen.
-In all of the single-story experiments firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
-For the last set of experiments, the choice was made to use a firefighter so that the nozzle would be moved in an informed manner in order to make the best use of the hose stream to suppress the fire in the lower level of the two-story structure.
-
-The fire fighting crew was from the MCFRS and every member in the crew had been trained in the use of CAF and they had experience with using CAF.
+In all of the single-story experiments, firefighters with a hoseline were needed to extinguish any remaining fire and hot spots.
+For the last set of experiments in the two-story structure, a firefighter was used instead of a fixed monitor so that the nozzle was moved in an informed manner in order to make the best use of the hose stream to suppress the fire in the lower level of the structure.
+
+The fire fighting crew used was from the MCFRS, and every member in the crew had been trained in the use of CAF and had experience with using CAF.
 The firefighter on the nozzle was the same for all the experiments conducted in the two-story structure.
-The firefighter used the reach of the hose stream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the basement.
-Then the hoseline was advanced to the doorway and the nozzle was moved rapidly to hit the fuel surfaces inside the compartment.
+The firefighter used the reach of the hose stream to cool the fire gases just inside the doorway as a means to knockdown the flames that were extending through the open double doors of the ground floor.
+Then, the hoseline was advanced to the doorway and the nozzle was moved rapidly to hit the fuel surfaces inside the compartment.
 The nozzle was shut down when there were no flames visible from the doorway.
@@
 This is consistent with the ventilation analysis above.
-The nozzle movement clearly had a positive impact on suppressing the fire in the 11~m (36~ft) deep fire compartment.
+The nozzle movement clearly had a positive impact on suppressing the fire in the 11.0~m (36.0~ft) deep fire compartment.
 
@@
 Currently, the fire service relies on experience to develop a feel for the correct combination of nozzle type and movement.
-A study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how such choices can impact the flow of gases within the structure.
+A future study may be able to demonstrate a clear cause and effect relationship between the amount of water flowing, the type of nozzle, and the movement of the nozzle and how such choices can impact the flow of gases within the structure.
 Based on the results of this study, it appears that training and understanding the impact of nozzle movement may be potential paths to more effective use of water.
@@
 
-This study conducted by NIST was part of a larger research project led Cal Poly in collaboration with the MCFRS.
+This study conducted by NIST was part of a larger research project led by Cal Poly in collaboration with the MCFRS.
 This study was supported in part by a DHS/FEMA Assistance to Firefighters Research and Development Grant.
@@
 
-Full scale fire experiments designed to address those questions were conducted over a period of years from 2012 through 2015.
+Full scale fire experiments designed to address the key outcomes were conducted over a period of years from 2012 through 2015.
 The experimental configurations were designed to be representative of residential fire scenarios.
 The experience of the MCFRS played a major role in the development of this study.
-%The water and CAF flows were based on those used by a fire department with 35 CAFS front line engines.
-This same department also experienced injuries to firefighters while using CAF during interior fire fighting operations in residential structures.
 This study was composed of three types of experiments: spray density, gas cooling, and fire suppression.
@@
 Suppression agents were not applied to the fire in the burn room.
-In this report, an aggregate analysis was made to examine differences due to the location of the instrumentation relative to the impact area of the agent and compare the differences in the amount of gas cooling between plain water and CAF hose streams.
+In this report, an aggregate analysis was made to examine differences due to the location of the instrumentation relative to the impact area of the agent and to compare the differences in the amount of gas cooling between plain water and CAF hose streams.
 The results showed that water was generally more effective than CAF, though both agents were successful with respect to gas cooling and fire suppression.
@@
 The fire compartment was the full lower level of the structure, and it had an open floor plan with an area of 51.4~m$^2$ (553~ft$^2$).
-At one end of the room was an open doorway that was 1.8~m (6~ft) wide and 2~m (6.7~ft) high and led to a stairwell.
+At one end of the room was an open doorway that was 1.8~m (6.0~ft) wide and 2.0~m (6.7~ft) high and led to a stairwell.
 A manual hose stream application was made from outside the doorway on the lower level.
 In these experiments, there was a combination of wood-based and synthetic fuels.
-The fires were allowed to transition through flashover and then the initial fire suppression attack was made.
-In each case, the initial knockdown of the fire required no more than 60~gal of of plain water or water in the form of CAF.
+The fires were allowed to transition through flashover before the initial fire suppression attack was made.
+In each case, the initial knockdown of the fire required no more than 60~gal of plain water or water in the form of CAF.
 

### 2016-12-12 Projects/DelCo_2012/Report/DelCo_2012.tex
Minor edits to dimension accuracy and acknowledgement section

@@
 Six experiments were conducted in the lower level of the two-story structure using both water and CAF from a straight stream nozzle.
-Additionally, two CAF experiments were conducted in the two-story burn building with a solid stream.
+Additionally, two CAF experiments were conducted in the two-story structure with a solid stream.
 The lower level of the two-story structure allowed for a fire compartment that was approximately twice as large as the fire compartment in the single-story.
@@
 The floors and ceilings were also concrete, and the interior walls were constructed of cement block.
-The walls and ceiling of the burn rooms were protected with a 25~mm (1~in) thick layer of calcium silicate insulation and was covered by 50~mm (2~in) thick concrete tile.
+The walls and ceiling of the burn rooms were protected with a 25~mm (1.0~in) thick layer of calcium silicate insulation and was covered by 51~mm (2.0~in) thick concrete tile.
 The floors of the burn rooms were protected with fire brick.
@@
 Water application for the purpose of gas cooling always occurred in the adjacent room, which had interior dimensions of 4.1~m (13.4~ft) by 5.7~m (18.7~ft) and a ceiling height of 3.4~m (11.0~ft).
-The open doorway that connected the burn room to the gas cooling room and the doorway from the gas cooling room to the exterior both measured 2.0~m (6.5~ft) high and 0.9~m (3.0~ft) wide.
+The window on the west face of the structure from the exterior to the burn room was 1.1~m (3.5~ft) by 1.1~m (3.5~ft).
 
@@
 They were designed to simulate a single floor of a residential structure.
-The outer wall of each structure was composed of interlocking concrete blocks 0.6~m (2.0~ft) wide, 0.6~m (2.0~ft) high and 1.2~m (4.0~ft) long.
+The outer wall of each structure was composed of interlocking concrete blocks 0.6~m (2.0~ft) wide, 0.6~m (2.0~ft) high, and 1.2~m (4.0~ft) long.
 The interior dimensions of each structure were 6.1~m (20.0~ft) wide, 11.0~m (36.0~ft) long, and 2.4~m (8.0~ft) high.
@@
 A 2.0~m (6.5~ft) high by 0.9~m (3.0~ft) wide open doorway on the north side of the structure connected the entry foyer to the exterior.
-The opening on the south face of the structure from the exterior to the burn room was 2.4~m (7.75~ft) high and 1.09~m (3.6~ft) wide.
+The window on the south face of the structure from the exterior to the burn room was 1.2~m (4.0~ft) tall by 1.1~m (3.5~ft) wide.
 A basic plan view of the structure is presented in Figure~\ref{fig:Test_Structure_Floor_Plan}, and a fully dimensioned plan view is included in Figure~\ref{fig:Test_Structure_Floor_Plan_Detailed} in Appendix~\ref{app:floor_plans}.
@@
 The interior walls of the structure were framed with steel studs and track.
-The studs were set to 0.4~m (16~in) centers.
-The ceiling support was composed of wood truss joist I-beams (TJIs) with a 0.3~m (11.75~in) depth.
-Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.13~in) x 44~mm (1.75~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web.
+The studs were set to 0.4~m (16.0~in) centers.
+The ceiling support was composed of wood truss joist I-beams (TJIs) with a 0.3~m (11.8~in) depth.
+Each TJI was composed of laminated veneer lumber flanges with a cross section of 29~mm (1.1~in) x 44~mm (1.8~in) and an 11~mm (0.43~in) thick oriented strand board (OSB) web.
 Tongue and grove, 18~mm (0.72~in) thick, OSB was attached to the top of the TJIs.
@@
 The stairway was 1.2~m (4.0~ft) wide, and the edge of the bottom step was located 1.6~m (5.25~ft) from the south wall.The second story walls were wood framed with 51~mm (2.0~in) by 102~mm (4.0~in) studs.
-The studs were set to 0.40~m (16~in) centers.
+The studs were set to 0.4~m (16.0~in) centers.
 The interior walls were protected by a layer of 16~mm (0.63~in) fire rated gypsum board, 16~mm (0.63~in) Durock cement board, and a second layer of 16~mm (0.63~in) fire rated gypsum board.
@@
 The single thermocouples were bare-bead, Chromel-Alumel (type K) thermocouples with a 1.0~mm (0.04~in) nominal diameter.
-The thermocouple was protected with an 3.2~mm (0.13~in) diameter inconel sheath.
+The thermocouple was protected with a 3.2~mm (0.13~in) diameter inconel sheath.
 The sheathing protects the thermocouple from water but slows the response time because of the additional thermal mass.
@@
 
-There were seven suppression tests conducted in the two-story, purpose-built structure.
-All seven of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling.
-Five of the seven tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
+There were eight suppression tests conducted in the two-story, purpose-built structure.
+All eight of the tests used a fuel load consisting of three sofas, polypropylene carpeting over polyurethane foam padding, and OSB paneling along three walls and the ceiling.
+Six of the eight tests also had two stacks of wooden pallets in addition to the initial fuel load (Section~\ref{sec:fire_suppression_furniture_fuel}).
 Ignition occurred in the southwest corner of the ground floor, and available ventilation was through the ground floor double doors and the south exterior door on the second story of the structure.
@@
 
-Seven of the suppression experiments were conducted in a two-story structure.
+Eight of the suppression experiments were conducted in a two-story structure.
 The fire compartment was the full lower level of the structure, and it had an open floor plan with an area of 51.4~m$^2$ (553~ft$^2$).
@@
 This study was part of a larger DHS/FEMA Assistance to Firefighters Research and Development Grant project led by Cal Poly.
-The authors would like to acknowledge the support of the Cal Poly team, especially: Fred Mowrer, Christopher Dicus, Thomas Korman, and Sean Mitchell.
+The authors would like to acknowledge the support of the Cal Poly team, especially Fred Mowrer, Christopher Dicus, Thomas Korman, and Sean Mitchell.
 
@@
 
-Thanks are given to the dedicated team of fire instructors and firefighters that supported these experiments; Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
+Thanks are given to the dedicated team of fire instructors and firefighters that supported these experiments: Brian Righter (Rudy), John McGowan, Matthew Poissant, John Frey, Brian Embert, Raymond Keller III, Mike Bramble, Edward McBride, Mark Morrissey, Bill Norris, and Matt LeTourneau.
 

### 2017-01-13 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
DelCo report: Add header info to longtables.
Minor change to gas burner report

@@
 \subsubsection{First Floor of Both Structures}
-The first floor of each structure had outer walls composed of interlocking concrete blocks with equal side lengths of 0.61~m (2~ft).
+The first floor of each structure had outer walls composed of interlocking concrete blocks measuring 0.6~m (2.0~ft) wide, 0.6~m (2.0~ft) high, and 1.2~m (4.0~ft) long.
 The joints and gaps between the blocks were filled with high temperature insulation.
@@
 
-Dimensioned floor plans of the East and West Structures are presented in Figures~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
+Dimensioned floor plans of the East and West Structures are presented in Figs.~\ref{fig:east_dimensioned_plan}~and~\ref{fig:west_dimensioned_plan}, respectively.
 
@@
 \begin{longtable}[c]{c|lll}
-\caption{East Structure Channel List\label{table:east_channel_list}} \\
+\caption[East Structure Channel List]{East Structure Channel List}
+\label{table:east_channel_list}\\
+\toprule
+\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} &
+\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  &
+\textbf{Channel Location} &
+\textbf{Measurement Type} \\
+\midrule
+\endfirsthead
+\caption[]{East Structure Channel List (continued)} \\
 \toprule
@@
 \begin{longtable}[c]{c|lll}
-\caption{West Structure Channel List\label{table:west_channel_list}} \\
+\caption[West Structure Channel List]{West Structure Channel List}
+\label{table:west_channel_list}\\
+\toprule
+\begin{tabular}{c} \textbf{Device} \\ \textbf{Location} \end{tabular} &
+\begin{tabular}{c} \textbf{Channel} \\ \textbf{Name} \end{tabular}  &
+\textbf{Channel Location} &
+\textbf{Measurement Type} \\
+\midrule
+\endfirsthead
+\caption[]{West Structure Channel List (continued)} \\
 \toprule

### 2017-01-17 Projects/DelCo_2012/Report/DelCo_2012.tex
Updated month/year on title pages

@@
 \vspace*{2\baselineskip}
-December 2016}
+January 2017}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note 1927 \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (December 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1927, \pageref{LastPage} pages (January 2017) \\
 CODEN: NTNOEF }

### 2017-01-19 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Added Nelson's edits to gas burner report

@@
 \subsubsection{Leakage}
-An air leakage measurement system was used to measure the amount of leakage associated with each structure.
-The amount of leakage in the East Structure was measured as 0.024~m$^2$.
+An air leakage measurement system was used to measure the leakage area associated with each structure.
+The leakage area in the East Structure was measured as 0.024~m$^2$.
 For the West Structure, the leakage was measured as 0.027~m$^2$ when the stairway door was fully closed, 0.054~m$^2$ when the stairway door was fully opened, and 0.048~m$^2$ when the stairway door was in the ``closed'' position (having a 152~mm (6~in) gap between the door and the frame) used Tests~24 and 25.
@@
 Schmidt-Boelter gauges were used to measure both total heat flux and radiant heat flux (radiometer).
-A radiometer is a total heat flux gauge with a zirconium plate to prevent contributions from convective heat transfer.
+A radiometer is a total heat flux gauge with a zirconium window to prevent contributions from convective heat transfer.
 Calibrated pumps pulled gas samples through a sample conditioning system to eliminate moisture in the sample.
@@
 In accordance with NIST guidelines~\cite{Taylor&Kuyatt:1994}, measurement accuracy is reported as an {\em expanded uncertainty} or 95~\% ($2\,\sigma$) confidence interval.
-Most manufactures express accuracy in terms of a {\em standard  uncertainty} or 68~\% ($1\,\sigma$) confidence interval.
+Most manufacturer specifications express accuracy in terms of a {\em standard  uncertainty} or 68~\% ($1\,\sigma$) confidence interval.
 
 \subsubsection{Compartment Dimensions}
-Room dimensions and instrumentation array locations were made with a hand held laser measurement device with a standard uncertainty of $\pm$6.0~mm (0.25~in) over a range of 0.6~m (2.0~ft) to 15~m (50.0~ft)~\cite{StanleyTools}.
+Room dimensions and instrumentation array locations were made with a hand held laser measurement device with a standard uncertainty of $\pm$6.0~mm (0.25~in) over a range of 0.6~m (2.0~ft) to 15~m (50.0~ft) according to the manufacturer~\cite{StanleyTools}.
 Steel measuring tapes with a resolution of $\pm$0.5~mm (0.02~in) were used to locate measurement devices.
@@
 Small diameter thermocouples were used during these experiments to limit the impact of radiative heating and cooling.
-The estimated relative expanded uncertainty associated with the temperature measurements is $\pm$15~\%.
+The estimated expanded uncertainty associated with the temperature measurements is $\pm$15~\%.
 
@@
 The manufacturer, MEDTHERM Corporation, reports a $\pm$3~\% calibration expanded uncertainty for these devices~\cite{Medtherm:2003}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the relative expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the expanded uncertainty of a Schmidt-Boelter gauge is typically $\pm$8~\%~\cite{Pitts:2006}.
 
@@
 (model 602P) having a relative expanded uncertainty of $\pm$1~\% when compared to span gas volume fractions~\cite{Bundy:2007} was used to make gas concentration measurements.
-However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated relative expanded uncertainty of $\pm$12~\%.
+However, according to a study by Lock~et~al.~\cite{Lock:1}, the non-uniformity and movement of exhaust gases contribute to an estimated expanded uncertainty of $\pm$12~\%.
 
@@
 were used to measure gas velocity in doorways.
-Bryant~\cite{Bryant:FSJ2009} estimates that the relative expanded uncertainty of this measurement ranges from $\pm$14~\% to $\pm$22~\%.
+Bryant~\cite{Bryant:FSJ2009} calculated an expanded uncertainty ranging from $\pm$14~\% to $\pm$22~\% for bi-directional probes of similar design.
 
 \subsubsection{Heat Release Rate}
-A rotary type gas meter was used to measure the volume flow rate of propane into the gas burners.
+A positive displacement rotary gas meter was used to measure the volume flow rate of propane into the gas burners.
 The manufacturer, Romet Limited, reports a relative standard uncertainty of $\pm$2~\%~\cite{Romet:2014} for this type of meter (model RM-3000).
@@
 Local measurements of temperature, gas velocity, heat flux, and gas concentrations were collected at various locations throughout the structure during the experiments.
-The total volume of propane delivered to the burners was measured by a rotary gas meter and was used to calculate the heat release rate of the fire during each test.
+The total volume of propane delivered to the burners was measured by a positive displacement rotary gas meter and was used to calculate the heat release rate of the fire during each test.
 

### 2017-01-19 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Changed date on gas burner report

@@
 \vspace*{2\baselineskip}
-October 2016}
+January 2017}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (October 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (January 2016) \\
 CODEN: NTNOEF }

### 2017-02-08 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Final edits to gas burner report

@@
 \vspace*{2\baselineskip}
-January 2017}
+February 2017}
 
@@
 \flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (January 2016) \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2017) \\
 CODEN: NTNOEF }
@@
 Finally, the burners were turned off and the fire was extinguished.
+The nine tests were conducted in series with a variety of other experiments.
+In order to be consistent with the original test numbering, the experiments are referred to as Tests~2--6 and Tests~22--25 throughout this report.
 

### 2017-02-17 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex

@@
 The nine tests were conducted in series with a variety of other experiments.
-In order to be consistent with the original test numbering, the experiments are referred to as Tests~2--6 and Tests~22--25 throughout this report.
+In order to be consistent with the original test numbering, the gas burner experiments presented in this report are referred to as Tests~2--6 and Tests~22--25.
 

### 2017-02-27 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
minor changes

@@
 The Fire Dynamics Simulator (FDS) and the scientific visualization tool, Smokeview, are the most widely used and well documented CFD tools in the fire protection engineering community.
-Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate as description of the model here other than to direct the reader to the volumes of information and data that exist for the FDS and Smookeview suite.
-
-FDS~\cite{FDS_Users_Guide} is a CFD model developed and maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+In addition these tools have on going verification and validation programs.
+Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data that exist for the FDS and Smookeview suite.
+
+FDS~\cite{FDS_Users_Guide} is a CFD model initially developed and currently maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
 A CFD model has a computational domain that is divided into  three-dimensional rectangular control volumes or computational cells.
@@
 Smokeview is a software tool specifically designed to visualize simulation results from FDS~\cite{Smokeview_Users_Guide}.
-Smoke-view visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
+Smokeview visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
 Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
 Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.
-Smokeview also has a feature that can represent a fire pattern on a surface based on user supplied threshold criteria.
+Smokeview also has a feature that can represent a fire or char pattern on a surface based on user supplied threshold criteria.
 
@@
 
-Two FDS models were developed: 1) to simulate the instrumented gypsum wallboard experiments with the natural gas burner and 2) to simulate the compartment fire pattern experiments with the natural gas burner.
+Several FDS models were developed to correlate with the different types of experiments conducted over the course of this study: 1) simulations of the source fire characterization experiments documented in Chapter 2, 2) simulations of the instrumented gypsum wallboard experiments with the natural gas burner as documented in Chapter 4, and 3) simulations of the compartment fire pattern experiments with the natural gas burner in positions against a wall and in a corner as documented in Chapter 6.
+
+The source fire simulation will be compared against the source fire characterization data to determine the best grid cell resolution and other inputs to use to provide the best fire simulation for use in the simulations of the wall and compartment experiments.
+
+\subsection{Natural Gas Source Fires}
+
 One of the key determinations that is required when developing an FDS model is the mesh or grid cell size.

### 2017-03-05 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Updated FDS ref and developing FDS section text

@@
 
-Similar to the previous chapter the goal is to utilize an analytical tool to predict or simulate the results from some of the key experiments conducted in this study.
+The goal of this chapter is to utilize an analytical tool to predict or simulate the results from some of the key experiments conducted in this study.
 Unlike the previous chapter the computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
 The CFD models require more knowledge, more computer resources, and more input data to utilize correctly.
-Currently modelers need to develop there own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the materials of interest.
+Currently modelers need to develop there own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the specific material of interest.
 
@@
 The Fire Dynamics Simulator (FDS) and the scientific visualization tool, Smokeview, are the most widely used and well documented CFD tools in the fire protection engineering community.
-In addition these tools have on going verification and validation programs.
-Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data that exist for the FDS and Smookeview suite.
+In addition, these tools have on going verification and validation programs.
+Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data repository that exist for the FDS and Smookeview suite.
 
@@
 One of the most important aspects of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide}and validated against fire test data~\cite{FDS_Validation_Guide}to ensure that it is accurate and provides the expected results, given appropriate input data.
+The data that FDS has been validated against can be found on-line is repository of the reports that were the source of the data~\cite{FDS-SMV_repository}.
 A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Tech_Guide}.
@@
 Smokeview also has a feature that can represent a fire or char pattern on a surface based on user supplied threshold criteria.
+Smokeview also has a Technical Reference Guide~\cite{Smokeview_Tech_Guide} and a Verification Guide~\cite{Smokeview_Verification_Guide}.
 
@@
 
-The source fire simulation will be compared against the source fire characterization data to determine the best grid cell resolution and other inputs to use to provide the best fire simulation for use in the simulations of the wall and compartment experiments.
+Several source fire simulations will be modelled with a range of grid cell resolutions and radiative fraction values.
+The results are compared against the source fire characterization data to determine which grid cell resolution and radiative fraction will provide the best fire simulation for use in the simulations of the wall and compartment experiments.
 
@@
 The smaller the grid cells the better the resolution.
-However increased resolution or the smaller grid cell size, the longer it will take the simulation to run.
+However increased resolution will require more computational resources and additional run time.
+The question is does it provide a more realistic answer.
+As with most pursuits there is no one answer.
+The `best' grid size depends on the scenario being modeled.
 
@@
 
- The FDS documents provide a method to determine how well a flow field will be resolved buy using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
+ The FDS User Guide provides a method to determine how well a flow field will be resolved buy using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
 This value has been referred to as the plume resolution index.
@@
 To examime the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were choosen to model the fire.
-The resulting plume resolution index (RI) values were approximately 4.4, 8.8, and 17.5 respectively.
-Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) plume resolution results from the grid cell size choices.
+The resulting mesh resolution index (RI) values were approximately 4.4, 8.8, and 17.5, respectively.
+Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) mesh resolution.
+FDS simulations of the source fire characterization experiments will be conducted with these mesh resolutions and compared with the results from the experiments.
 
 \subsection{Input Data}
+
+Source term model description ....
 

### 2017-03-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
added FH graphs to Ch 8

@@
 
-\subsection{Input Data}
-
-Source term model description ....
-
-The first FDS model that was developed was the simultion of the instrumented gypsum wallboard experiments.
+\subsubsection{Input Data Source Fire Characterization}
+
+The FDS model for simulating the source fires is very basic, consisting of the definition of the computational domain in space and time, a definition of the burner geometry and the combustion model for the fuel, and specification for measurement points that can be used for analysis temperature, heat flux, and flame height.
+
+The computational domain of the model had the geometry of a cube with 2.4~m on a side.
+The resulting number of computational cells for each case ranged from 27,000 for the 80~mm cells to 1,728,000 for the 20~mm cells.
+For the 80 and 40~mm computational cell scenarios, the cases were run as a single mesh.
+For the 20~mm case, the computational domain was divided into 8 uniform meshes.
+Each mesh was 2.4~m by 1.2~m and 0.6~m tall.
+The time domain for each model was chosen to be 300 seconds, which is similar to the burn time fior each of the fuels.
+
+The burner was modeled as an obstruction with a open top area of 0.09 m$^2$, elevated 0.08~m above the test surface.
+This is the same physical size of the natural gas burner used in the experiments.
+It was modeled with a steady state heat release rate flux of 888.89 kW/m$^2$, or a heat release rate of 80~kW.
+The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.
+In FDS version 6, the default radiant fraction for the `methane' reaction was set to 0.2.
+
+FDS has devices, which are used to simulate thermocouples and total heat flux gauges.
+These devices were positioned in locations similar to the locations used in the source fire experiments.
+The thermocouples were positioned in a vertical array, centered on the burner, beginning 0.1~m above the burner surface and spaced every 0.1~m upto 1.2~m above the burner surface.
+A total heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.
+In addition, FDS features devices that can not be physically implemented.
+One such device, is used to determine the heat release rate per unit length.
+This device was used to determine flame height based on that measure.
+
+\subsubsection{Comparison of FDS with Source Fire Results}
+
+In Chapter 2 the fires from the burners were characterized.
+In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
+The average plume temperatures at elevations from 0.1~m through 1.2~ above the top face of the burner in 0.1~m increments will be compared.
+
+\subsubsection{Grid Size Analysis}
+Figure~\ref{FHNG01_RI} shows the comparison of the centerline gas burner temperatures with three different sets of FDS results.
+The only variable in the simulations is the RI.
+The RIs include three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).
+The associated 95~\% confidence limits are also shown the temperature value for each height.
+The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) has the best agreement with the temperatures along centerline of the plume.
+The two simulations with the higher RI values provide less agreement that the course mesh.
+This seems to be counter intuitive to the results expected from an increased RI.
+However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich) which results in temperatures significantly lower than measured.
+This affect of this fuel rich area above the burner results poorer agreement with increasing RI.
+It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is higher than what was measured.
+
+Another comparison can be made examining the `thermocouple' results from FDS to see if the model of the thermocouple provides improved argeement with the temperatures measured via physical thermocouples.
+This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
+Again the best agreement along the vertical array of temperatures was provided by the RI=5 model.
+Not surprisely the sub model of the thermocouple device shifted the FDS values slightly.
+Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bean are influencing the diffrences between the gas temperature and the mesuared temperature FDS values.
+
+Mc caffery plume
+
+continuous flame region 
+intermittant flame region
+plume region
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/FHNG01_RI} \\
+
+	\caption[Comparison of burner centerline gas temperatures with FDS simulated gas temperatures.]{Comparison of burner centerline gas temperatures with FDS simulated gas temperatures generated with three different RIs 5, 10 and 20.}
+	\label{FHNG01_RI}
+\end{figure}
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/FHNG01_RI_TC} \\
+
+	\caption[Comparison of burner centerline gas temperatures with FDS simulated gas temperatures.]{Comparison of burner centerline gas temperatures with FDS simulated gas temperatures generated with three different RIs 5, 10 and 20.}
+	\label{FHNG01_RI_TC}
+\end{figure}
+
+\subsection{Natural Gas Instrumented Wall Fires}
+
+that was developed was the simultion of the instrumented gypsum wallboard experiments.
 The first input needed was the definition of the compuational domain.
@@
 Fire
-The burner was modeled as an obstruction, with the same physical size as the burner.
-It was modeled with a steady state heat release rate of 888.89 kW/m$^2$.
-The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.
-
-\section{Comparison of FDS with Source Fire Results}
-
-In Chapter 2 the fires from the burners were characterized.
-In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
-The average plume temperatures at elevations from 0.2~m through 2.2~ above the top face of the burner in 0.2~m increments will be compared.
+
 Then the data generated from the instrumented gypsum wallboard fires are compared with results from FDS simulations.
 Four burner positions are examined, beginning 0.61~m from the wall to moving to 0.0~m, where one edge of the burner is in contact with the instrumented gypsum wallboard wall.
-First the the plume data will be examined based on the size of the computational grid cells used in the FDS simulations.
-
-\subsection{Grid Size Analysis}
 

### 2017-03-06 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
a little more cp 8

@@
 However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich) which results in temperatures significantly lower than measured.
-This affect of this fuel rich area above the burner results poorer agreement with increasing RI.
-It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is higher than what was measured.
+The affect of this fuel rich area above the burner results in poorer agreement with increasing RI.
+It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is moved to a higher elevation relative to what was measured.
+For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seem to coincide with the measured value at 0.3~m above the burner.
+Making the adjustment appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
+
+These simulation results are consistant with the comparison made to the McCaffery ref   in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
 

### 2017-03-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
ch 8
?

@@
 
-Mc caffery plume
-
-continuous flame region 
-intermittant flame region
-plume region
+%Mc caffery plume    
+%continuous flame region 
+%intermittant flame region
+%plume region
 
@@
 
+\subsubsection{Radiative Fraction}
+
+From Chapter 2 the
+
 \subsection{Natural Gas Instrumented Wall Fires}
+
+The next comparsions will be made with the natural gas source fire at 4 different distance from an gypsum board wall.
+Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
+The simulations will replicate the same distances.
+The simulation includes a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
+The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter
+
+\subsubsection{Input Data Natural Gas Instrumented Wall Fires}
+
+The computational domain of the model was the same as the volume considered for the source fire simulations, a cube with 2.4~m on a side.
 

### 2017-03-10 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
rearrange Ch 8 heading
reviewing graphs

@@
 
-FDS~\cite{McGrattan:2014} and Smokeview~\cite{Forney:2014} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
+FDS~\cite{FDS_Users_Guide} and Smokeview~\cite{Smokeview_Users_Guide} were used to examine the ability to numerically reproduce the source fires and the instrumented wall experiments.
 These simulation tools provide results in the form of visual field data.
@@
 
-\subsection{Simulation of Fires}
+\section{Simulation of Fires}
 
@@
 
-\subsubsection{Comparison of FDS with Source Fire Results}
+\section{Comparison of FDS with Source Fire Results}
 
@@
 
-\subsubsection{Grid Size Analysis}
+\subsection{Grid Size Analysis}
 Figure~\ref{FHNG01_RI} shows the comparison of the centerline gas burner temperatures with three different sets of FDS results.
@@
 
-\subsubsection{Radiative Fraction}
+\subsection{Radiative Fraction}
 
@@
 
-\subsection{Natural Gas Instrumented Wall Fires}
+\section{Natural Gas Instrumented Wall Fires}
 
@@
 
-\subsubsection{Input Data Natural Gas Instrumented Wall Fires}
+\subsection{Input Data Natural Gas Instrumented Wall Fires}
 

### 2017-03-10 Projects/Madrzykowski_Thesis/Plot_Scripts/vert_hf_ri.py

@@ -32,7 +32,7 @@ errorbar(data_slice,y_data,xerr=0.15*data_slice,linestyle='None',marker='o',ms=8
 plot(fds_slice_05,y_fds,'k',label = 'FDS 05')
 plot(fds_slice_10,y_fds,'r',label = 'FDS 10')
 # plot(fds_slice_20,y_fds,'b',label = 'FDS 20')	
-xlabel('Temperature ($^{\circ}$C)', fontsize=20)
+xlabel('Heat flux (kW/m$^{2}$)', fontsize=20)
 ylabel('Distance above Burner (m)', fontsize=20)
 xticks(fontsize=16)
 yticks(fontsize=16)

### 2017-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch 8 90%

@@
 In addition, these tools have on going verification and validation programs.
-Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data repository that exist for the FDS and Smookeview suite.
+Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data repository that exist for the FDS and Smokeview suite.
 
@@
 
-Several source fire simulations will be modelled with a range of grid cell resolutions and radiative fraction values.
+In this section, the natural gas burner will be modelled with a range of grid cell resolutions and radiative fraction values.
 The results are compared against the source fire characterization data to determine which grid cell resolution and radiative fraction will provide the best fire simulation for use in the simulations of the wall and compartment experiments.
 
-\subsection{Natural Gas Source Fires}
+\subsection{Natural Gas Source Fire}
 
@@
 However increased resolution will require more computational resources and additional run time.
-The question is does it provide a more realistic answer.
+The question is, does it provide a more realistic answer?
 As with most pursuits there is no one answer.
-The `best' grid size depends on the scenario being modeled.
+The `best' grid size may depend on a several different parameters of the scenario being modeled.
 
 Choosing the size of the grid when performing an analysis with FDS is critical in order to get the level of resolution needed to adequately simulate the required details within a simulation.
-In studies where large rooms or portions of buildings have been involved grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Vettori:2000,Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
-
- The FDS User Guide provides a method to determine how well a flow field will be resolved buy using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
+In studies where large rooms or portions of buildings have been modeled grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Madrzykowski:2004,Vettori:2000, Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
+
+ The FDS User Guide provides a method to determine how well a flow field will be resolved by using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
 This value has been referred to as the plume resolution index.
@@
 
-The FDS model for simulating the source fires is very basic, consisting of the definition of the computational domain in space and time, a definition of the burner geometry and the combustion model for the fuel, and specification for measurement points that can be used for analysis temperature, heat flux, and flame height.
+The FDS model for simulating the source fires is very basic, consisting of the definition of the computational domain in space and time, a definition of the burner geometry, the combustion model for the fuel, and the specification of measurement points that can be used to examine temperature, heat flux, and flame height.
 
@@
 The thermocouples were positioned in a vertical array, centered on the burner, beginning 0.1~m above the burner surface and spaced every 0.1~m upto 1.2~m above the burner surface.
-A total heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.
+A total heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 0.5 m above the top of the burner.
 In addition, FDS features devices that can not be physically implemented.
@@
 
-In Chapter 2 the fires from the burners were characterized.
+In Chapter 2 the fires from the burners were characterized in terms of plume temperature, heat flux remote from the plume, and flame height.
 In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
-The average plume temperatures at elevations from 0.1~m through 1.2~ above the top face of the burner in 0.1~m increments will be compared.
+The average plume temperatures at elevations from 0.1~m through 1.2~m above the top face of the burner in 0.1~m increments will be compared.
 
@@
 The associated 95~\% confidence limits are also shown the temperature value for each height.
-The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) has the best agreement with the temperatures along centerline of the plume.
-The two simulations with the higher RI values provide less agreement that the course mesh.
-This seems to be counter intuitive to the results expected from an increased RI.
-However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich) which results in temperatures significantly lower than measured.
+The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) had the best agreement with the temperatures along centerline of the plume.
+The two simulations with the higher RI values provided less agreement than the course mesh.
+
+This seemed to be counter intuitive to the results expected from an increased RI.
+However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich), which resulted in temperatures significantly lower than measured.
 The affect of this fuel rich area above the burner results in poorer agreement with increasing RI.
-It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone is moved to a higher elevation relative to what was measured.
-For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seem to coincide with the measured value at 0.3~m above the burner.
+It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone was moved to a higher elevation relative to what was measured.
+For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seemed to coincide with the measured value at 0.3~m above the burner.
 Making the adjustment appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
-
-These simulation results are consistant with the comparison made to the McCaffery ref   in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
-
+As FDS is a complex model, this explaination may be only one possibility.
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/FHNG01_RI} \\
+	\caption[Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
+	\label{FHNG01_RI}
+\end{figure}
+
+These simulation results are consistant with the comparisons made to the McCaffery's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
+McCaffery used a natural gas burner, 0.30~m square, which is similar in size to the burner used in this study.
+McCaffery noted that, "visually non-axisymmetric behavior could be observed only very close to the burner surface".
+In the study, temperatures were measured with Type K thermocouples covered with a 1.0~mm stainless steel sheath.
+The peak heat release rate in McCaffery's plume study was 57.5~kW, this heat release rate was also the closest to the 80~kW fires in the current study.
+The comparison between the McCaffery plume correlation and the FDS simulations at RI values of 5, 10 and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
+Focusing on the data between the burner surface and the 1~m above the burner surface, FDS underpredicted the temperature near the surface of the burner and then overpredicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases respectively.
+Once the temperature comparisons were above the continuous and intermittant flame regions, the agreement between the cases and the correlation began to improve.
+Similar to the current study, increased RIs did not improve the simulation of the vertical centerline temperatures close to the burner.
+
+\begin{figure}
+	\includegraphics[width=5in] {../Figures/McCaffrey_Plume_comp}  \\
+	\caption[Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures.] {Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20 from the FDS Validation Guide~\cite{FDS_Validation_Guide}.}
+	\label{McCaffrey_Plume_comp}
+\end{figure}
+
+The comparisons above used the predicted gas temperature from the model.
 Another comparison can be made examining the `thermocouple' results from FDS to see if the model of the thermocouple provides improved argeement with the temperatures measured via physical thermocouples.
 This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
-Again the best agreement along the vertical array of temperatures was provided by the RI=5 model.
-Not surprisely the sub model of the thermocouple device shifted the FDS values slightly.
-Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bean are influencing the diffrences between the gas temperature and the mesuared temperature FDS values.
-
-%Mc caffery plume    
-%continuous flame region 
-%intermittant flame region
-%plume region
-
-\begin{figure}[h]
-	\includegraphics[width=5in]{../Figures/FHNG01_RI} \\
-
-	\caption[Comparison of burner centerline gas temperatures with FDS simulated gas temperatures.]{Comparison of burner centerline gas temperatures with FDS simulated gas temperatures generated with three different RIs 5, 10 and 20.}
-	\label{FHNG01_RI}
-\end{figure}
+Not surprisely, the sub model of the thermocouple device shifted the FDS values slightly.
+At temperatures greater than 700~$^\circ$C, the `thermocouple' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
+At temperatures less than 700~$^\circ$C, the `thermocouple' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
+The best agreement along the vertical array of temperatures was provided by the RI=5 model.
+Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bead are generating the diffrences between the gas temperature and the measured temperature FDS values.
 
@@
 	\includegraphics[width=5in]{../Figures/FHNG01_RI_TC} \\
-
-	\caption[Comparison of burner centerline gas temperatures with FDS simulated gas temperatures.]{Comparison of burner centerline gas temperatures with FDS simulated gas temperatures generated with three different RIs 5, 10 and 20.}
+	\caption[Comparison of vertical centerline `thermocouple' temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline `thermocouple' temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
 	\label{FHNG01_RI_TC}
@@
 
-From Chapter 2 the
-
-\section{Natural Gas Instrumented Wall Fires}
-
-The next comparsions will be made with the natural gas source fire at 4 different distance from an gypsum board wall.
-Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
-The simulations will replicate the same distances.
-The simulation includes a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
-The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter
-
-\subsection{Input Data Natural Gas Instrumented Wall Fires}
-
-The computational domain of the model was the same as the volume considered for the source fire simulations, a cube with 2.4~m on a side.
-
-that was developed was the simultion of the instrumented gypsum wallboard experiments.
-The first input needed was the definition of the compuational domain.
-The domain of the model had the geometry of a cube with 2.4~m on a side.
-The resulting number of computational cells for each case ranged from 27,000 for the 80~mm cells to 1,728,000 for the 20~mm cells.
-An isometric view of the model outlined by the domain is shown in Figure      .
-The face of the wall is located 1.35~m from the front of the domain.
-The wall was modeled with material properties for gypsum board.
-Thermal conductivity = 0.28
-Specific Heat = 1.00
-Density = 582
-
-Input data was collected from the experimental results presented in previous chapters of this study as well as from literature sources in order to simulate the instrumented wall experiments using FDS.
-
-Instruments – FDS has devices, which are used to simulate thermocouples and total heat flux gauges.
-This devices were positioned  in locations similar to the locations used in the physical experiments, in the plume region and on the wall.
-A radiative heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 1.0 m above the top of the burner.
-In addition, FDS features devices that can not be implemented such as a device, which can be used to examine the heat release rate per unit length.
-In this case, this device was used to determine flame height based on that measure.
-Fire
-
-Then the data generated from the instrumented gypsum wallboard fires are compared with results from FDS simulations.
-Four burner positions are examined, beginning 0.61~m from the wall to moving to 0.0~m, where one edge of the burner is in contact with the instrumented gypsum wallboard wall.
-
-Tables~\ref{tab:FDSRI_Exp_Plume2d} and \ref{tab:FDSRI_Exp_Plume0d} shows the plume temperature results for the three grid resolutions compared the experimental data with a wall spacing of 0.61~m and 0.0~m respectively.
-Figure~\ref{FDS_Plume_Grid_TWNG_comp} contains graphic comparisons of the same data.
-
-\begin{table}[ht!]
+From the Chapter 2 source fire characterization experiments, the measured heat flux at 0.95~m from the centerline of the burner and 0.5~m above the top of the burner. 
+In Figure~\ref{FHNG01_HF_RI} the averaged values from both heat flux gages are plotted against the FDS calculated heat flux at three different RIs of 5, 10 and 20.
+These FDS simulations used the default radiative fraction value of 0.2.
+As with the temperature comparisons, the course grid with an RI equal to 5 provided the best agreement to the measurements, however all of the values were lower than the measured heat flux.
+
+\begin{figure}
+	\includegraphics[width=5in]{../Figures/FHNG01_HF_RI} \\
+	\caption[Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values.]{Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values generated with three different RIs 5, 10, and 20.}
+	\label{FHNG01_HF_RI}
+\end{figure}
+
+Reviewing the heat flux data documented in Chapter 2 from both the 0.95~m  and the 2.0~m from the vertical centerline of the burner positions provided average steady state heat flux values of approximately 2.0~kW/m$^2$ and 0.43~kW/m$^2$, respectively.
+Applying the point source method, discussed in Chapter 7, conservative values for the radiative fraction were determined to be in the range of 0.25 to 0.28.
+Values found in the literature for natural gas range from 0.15 to 0.25~\cite{Modak:1977,Hostikka:3}.
+Therefore it was of interest to conduct FDS simulations with radiative fractions ranging from 0.2 to 0.3.
+This was based on the default value used in FDS and the upper bound of the literature values as this range covered the radiative fraction values estimated from the experiments.
+The course grid, RI=5, was used for the FDS models.
+The comparison of the results is shown in~\ref{FHNG01_HF_RI5}.
+The radiative fraction of 0.22 provided the best agreement with the measurement.
+
+\begin{figure}
+	\includegraphics[width=5in]{../Figures/FHNG01_HF_RI5} \\
+	\caption[Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values based on varied $\chi_r$ values.]{Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values with $\chi_r$ values of 0.20, 0.22, 0.25, and 0.30.
+The RI for the simulations was 5.}
+	\label{FHNG01_HF_RI5}
+\end{figure}
+
+One last check on the plume temperature predictions was made to examine the impact of the range of radiative fractions on the FDS results.
+The comparisons were made using the course grid, RI=5, the radiative fraction values of 0.20, 0.22, 0.25, and 0.30, as before.
+The simulations with radiative fractions between 0.2 and 0.25 were within the 2~$\sigma$ limits of the temperature measurements at each elevation.
+
+\begin{figure}
+	\includegraphics[width=5in]{../Figures/FHNG01_RF_RI5} \\
+	\caption[Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures based on varied $\chi_r$.]{Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures with $\chi_r$ values of 0.20, 0.22, 0.25, and 0.30.
+The RI for the simulations was 5.}
+	\label{FHNG01_RF_RI5}
+\end{figure}
+
+\subsubsection{Flame Height}
+
+One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height when energy stops being released along the vertical centerline of the gas burner.
+Estimates of the flame height were made by estimating the height where 0.95 to 0.99~$\%$ of the total energy had been released.
+Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
+The course and medium grids, RI=5 and R=10, are not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range.
+
+\begin{table}[h]
   \small
   \centering
-  \begin{tabular}{|c|c|c|c|c|}
-    \hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid    & Experiment Avg. \\
-    Burner~(m)     & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C) \\ \hline
-    \hline 0.2         & 458            & 500           & 666     & 620   \\
-    \hline 0.4         & 738            & 819           & 761     & 527   \\
-    \hline 0.6         & 632            & 769           & 643     & 385   \\
-    \hline 0.8         & 442            & 600           & 522     & 198 \\
-    \hline 1.0         & 346            & 459           & 402     & 151 \\
-    \hline 1.2         & 251            & 307           & 284     & 119 \\
-    \hline 1.4         & 209            & 236           & 213     & 98  \\
-    \hline 1.6         & 166            & 188           & 164     & 86  \\
-    \hline 1.8         & 145            & 154           & 133     & 76  \\
-    \hline 2.0         & 123            & 130           & 112     & 69  \\
-    \hline 2.2         & 111            & 113           & 99      & 61  \\
+  \begin{tabular}{|c|c|c|c|}
+    \hline Peak Visible Flame Height   	& RI=5       		& RI=10      		& RI=20  \\
+    Range          						&  (80~mm grid)  	&  (40~mm grid)  	&  (20~mm grid)  \\
+    (m)     							& (m) 				& (m) 				& (m)  			 \\ \hline
+    \hline 0.73 to 1.14         		& 1.02 to 1.27      & 1.07 to 1.27      & 1.28 to 1.42   \\
     \hline
   \end{tabular}
-  \caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.61~m from the Wall]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.61~m from the Wall.}
-  \label{tab:FDSRI_Exp_Plume2d}
+  \caption[Comparison of estimations of flame height from the natural gas burner experiments and FDS simulations with RIs of 5, 10 and 20.]{Comparison of estimations of flame height from the natural gas burner experiments and FDS simulations with RIs of 5, 10 and 20.}
+  \label{tab:FDS_FH}
 \end{table}
 
-\begin{table}[ht!]
-  \small
-  \centering
-  \begin{tabular}{|c|c|c|c|c|}
-    \hline Distance Above  & 80~mm grid      & 40~mm grid     & 20~mm grid    & Experiment Avg. \\
-    Burner~(m)     & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C) & Temp.~($^{\circ}$C)  & Temp.~($^{\circ}$C) \\ \hline
-    \hline 0.2         & 458            & 604           & 658     & 667   \\
-    \hline 0.4         & 751            & 824           & 793     & 643   \\
-    \hline 0.6         & 668            & 711           & 673     & 577   \\
-    \hline 0.8         & 519            & 575           & 581     & 353 \\
-    \hline 1.0         & 431            & 475           & 506     & 357 \\
-    \hline 1.2         & 326            & 357           & 406     & 306 \\
-    \hline 1.4         & 274            & 285           & 322     & 233 \\
-    \hline 1.6         & 218            & 234           & 257     & 201 \\
-    \hline 1.8         & 191            & 198           & 211     & 179 \\
-    \hline 2.0         & 162            & 170           & 178     & 150 \\
-    \hline 2.2         & 146            & 148           & 153     & 140 \\
-    \hline
-  \end{tabular}
-  \caption[Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperatures, 0.0~m from the Wall.]{Comparison of FDS Grid Resolution and Experimental FDS Natural Gas Burner Plume Temperature Averages with the Burner Located at 0.0~m from the Wall.}
-  \label{tab:FDSRI_Exp_Plume0d}
-\end{table}
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RI}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0pD_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RI}\\
-  \caption[FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with plume temperature measurements along the centerline of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
-Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_Plume_Grid_TWNG_comp}
-\end{figure}
-
 One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in 3 dimensions to allow the generation of visualizations.
-The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}
+The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}.
+The increased resolution leads to a flame structure that provides a better match to the look of the actual flame.
+However in this scenario, the increased resolution within the flow field has not resulted in improved numerical agreement.
 
@@
   \caption[Flame images generated with FDS and Smokeview]{Flame images generated with FDS and Smokeview.
-The left image has a mesh size of 80~mm, the center image has a mesh size of 40~mm and the image on the right has amesh size of 20~mm.}
+The left image has a grid size of 80~mm (RI=5), the center image has a grid size of 40~mm (RI=10) and the image on the right has a grid size of 20~mm (RI=20).}
   \label{FDS_Flame_Image_comp}
@@
 
+\subsubsection{Source Fire Summary}
+
+The comparisons of the temperature, heat flux, and flame heights for this specific scenerio show the best agreement with the 80~mm grid (RI=5) FDS simulations.
+Even though the differences between the radiative fractions of 0.2 and 0.22 are small, for the remaining simulation cases, 0.22 will be used.
+While the best agreement for the fire was demonstrated with the RI= 5 grid, the RI=10 grid will also be used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models get additional obstructions and surfaces.
+
+\section{Comparison of FDS with Natural Gas Instrumented Gypsum Board Wall Experiments}
+
+The next comparsions will be made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
+Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
+The simulations will replicate the same distances.
+The simulation includes a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
+The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter 4.
+The values that are compared in the section include: vertical centerline temperatures above the burner, wall temperatures, and heat flux values at the position of the wall surface.
+
+\subsection{Input Data Natural Gas Instrumented Gypsum Board Wall Experiments}
+
+The computational domain of the model was the same as the volume considered for the source fire simulations, a cube with 2.4~m on a side.
+The models were run with two different sized computational grid cells, an 80~mm (RI=5) grid and a 40~mm (RI=10) grid.
+The face of the wall is located 1.95~m from the front of the domain.
+The wall was modeled with material properties for gypsum wallboard that were documented in Chapter 4.
+The input properties were: thermal conductivity (0.28 W/m K), specific heat (1.00 kJ/kg K) and density (807 kg/m$^3$).
+In addition FDS includes a default value of 0.9 for emissivity, this value should be representative of the painted surface of the gypsum wallboard.
+As noted earlier in this study, gypsum wallboard undergoes chemical and physical changes as it is heated.
+These changes include the loss of homogeneity of the gypsum material, a change in density and as the paper is charred or burned there is a potential for a change in emissivity.
+The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500~$^\circ$C~\cite{Gross:1985}.
+While FDS can accomodate changes in thermoconductivy and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
+For the purposes of this study, the input values will remain constant throught out the course of the simulations.
+The only variable will be the distance between the edge of the burner and the wall.
+
+As before the FDS simultions will include devices, which are used to simulate thermocouples and total heat flux gauges.
+This devices were positioned in locations similar to the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
+In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simluated by FDS.
+
+\subsection{Temperatures}
+
+ The temperatures measured by thermocouples positioned along the vertical centerline of the natural gas burner will be compared with FDS generated temperures from two simulations, one with RI-5 and one with RI=10.
+The measurement points were at intervals of 0.2~m from 0.2~m to 2.2~m above the burner.
+Figure~\ref{FDS_Plume_IWGB_comp} contains four graphs.
+Each graph shows the same types of comparison, the only difference is the distance away from the gypsum wallboard.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.
+
+ There seem to be a couple of items that stick out from the graphs.
+First is what appears to be a separation of the temperature data into three distinct sections.
+The bottom three positions, 0.2~m through 0.6~m, represent the hottest section.
+The next two measurement positions at 0.8~m and 1.0~m are similar in temperature.
+The third section extends from 1.2 through 2.2~m above the burner and has the shape of a smooth curve decreasing in temperature with increasing elevation.
+Comparing the temperatures to the flame height analysis in Chapter 2, the first section aligns with the median flame height, the second section aligns with the portion of the flame that intermittent, 40~$\%$ of the time or less.
+The upper most section of the temperature data aligns with the thermal plume above the flame.
+
+ The second issue is that the FDS predictions do not align equally well with the data from each position, with the best agreement occurring when the burner is positioned against the wall.
+Further the temperatures for the burner position, 0.61~m from the was thought to be equivalent to the source fire experiments documented in Chapter 2.
+However that is not the case.
+The installation of the wall resulted in movement of the flame and plume.
+The flames oscillate toward the wall and as a result move away from the thermocouples centered over the burner.
+The resulting decrease in temperature may account for the difference between the plume tempertaures and the simulated temperatures from FDS.
+
 \begin{figure}[ht!]
   \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
-  \caption[FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on three different resolutions compared with the wall surface temperature measurements along the centerline of the natural gas fueled burner.
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D_RF_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0p5D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D_RF_RI}\\
+  \caption[FDS values based on two different RI values compared with temperature measurements along the vertical centerline of the natural gas fueled burner]{FDS values based on two different RI values compared with temperature measurements along the vertical centerline of the natural gas fueled burner.
 The temperatures are averages of two replicate experiments.
@@
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_Wall_Temp_TWNG_comp}
-\end{figure}
-
-\subsection{Temperatures}
-
-the data is plotted in the style used in FDS Validation
-
-continuous flame region 
-intermittant flame region
-plume region
+  \label{FDS_Plume_IWGB_comp}
+\end{figure}
+
+Figure~\ref{FDS_Wall_Temp_IWGB_comp} is analogous to Figure~\ref{FDS_Plume_IWGB_comp} except it compares the gypsum wallboard surface temperatures against the FDS simulated temperatures.
+So while the FDS values for the plume over predicted the temperatures, the FDS values for the wall surface temperatures are underpredicting.
+This is consistent with the flame and plume moving away from the plume centerline and toward the wall.
+The agreement between the FDS results and the measurements improves as the burner moves closer to the wall, however once the burner is against the wall, the degree of agreement between the FDS results and the measured temperatures decreased.
+At this position the FDS results are overpredicting the temperature.
+This differences at the wall are most distinct in the region where the flame impinged on the wall.
+The agreement improves in the plume area above the flames.
+In the comparisons with the source fire experiments, the FDS generated temperatures were underpredicting closer to the burner surface and the overpredicting in the flame region as a result of the `combustion' occuring at higher elevations above the burner.
+If a similar phenomena is occuring here, the wall maybe exaggerating the effect.
 
@@
   \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Plume_Avg_0D}\\
-  \caption[FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with plume temperature measurements along the centerline of the natural gas fueled burner.
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D_RF_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D_RF_RI}\\
+  \caption[FDS values based on two different RI values compared with the wall surface temperature measurements.]{FDS values based on two different RI values compared with the wall surface temperature measurements.
 The temperatures are averages of two replicate experiments.
@@
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_TCPlume_IWGB_comp}
+  \label{FDS_Wall_Temp_IWGB_comp}
 \end{figure}
@@
 	\label{FDS_Wall_Temp_IWGB_Comp_}
-\end{figure}
-
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D}\\
-  \caption[FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with the wall temperature measurements along the centerline of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
-Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_TCSurface_IWGB_comp}
 \end{figure}
@@
 
+The instrumented gypsum wallboard had two vertical arrays of total heat flux gauges positioned at 0.2~m intervals.
+Each array had six gauges installed from 0.2~m up through 1.2~m above the burner.
+One array was installed in line with the center of the burner and the other array was installed on the right edge of the burner.
+The comparisons between the measured heat flux and the FDS simulations are provided in Figure~\ref{FDS_HFCL_IWNG_comp} and Figure~\ref{FDS_HFEdge_IWNG_comp}.
+For the centerline gauges the trends between the heat flux measurements and the FDS values are similar to the trends with the temperatures and are consistant with the flame moving or leaning toward the wall.
+This resulted in higher heat flux measures relative to the FDS values at the three positions away from the wall.
+When the burner was positioned against the wall the FDS values and the measurements converged to a higher level of agreement.
+
+The FDS values significantly underpredict the measured heat flux values along the right edge of the burner.
+The best agreement occurs at the burner positions away from the wall.
+At this position, the fire pattern on the walls show that the lines of demarcation are occuring very close to the edge of the burner.
+Again flame movement seems to to be the main cause of the difference that is accentuated by a measurement location that is very sensitive to heat flux and position.
+
 \begin{figure}[ht!]
@@
   \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
-  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
+  \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.]{FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.
+The heat fluxes are averages of two replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_HFCL_TWNG_comp}
-\end{figure}
+  \label{FDS_HFCL_IWNG_comp}
+\end{figure}{}
 
@@
   \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0D}\\
-  \caption[FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner]{FDS values based on 40~mm grid compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner.
-The temperatures are averages of two replicate experiments.
+  \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner]{FDS values based on two different RI values compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner.
+The heat fluxes are averages of two replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_HFEdge_TWNG_comp}
+  \label{FDS_HFEdge_IWNG_comp}
 \end{figure}
@@
 inconsistant fire pattern near the right side of the sofa.  It appears that pattern was generated pre-flashover.  The pattern height is on the order of   calc HRR and FH for cushion.
+air equation
 

### 2017-03-12 Projects/Madrzykowski_Thesis/Plot_Scripts/vert_center_hf_ri.py

@@ -1,0 +1,41 @@
+from __future__ import division
+import numpy as np
+import pandas as pd
+import itertools
+from pylab import *
+from itertools import cycle
+rcParams.update({'figure.autolayout': True})
+
+data_dir = '../Experimental_Data/Vertical_Comp/'
+fds_dir = '../FDS_Output_Files/'
+plot_dir = '../Figures/'
+
+y_data = [0.2,0.4,0.6,0.8,1.0,1.2]
+y_fds = [0.2,0.4,0.6,0.8,1.0,1.2]
+
+test_name = 'IWGB_NG_HF_Center_Avg'
+fds_name = 'hfwallcl_avg_2D'
+distance = ['_0D','_0p5D','_1D','_2D']
+
+data = pd.read_csv(data_dir+test_name+'.csv', header=0)
+fds  = pd.read_csv(data_dir+test_name+'_FDS.csv', header=0)
+
+for i in range(4):
+	data_slice = np.squeeze(np.asarray(data.iloc[[i],1:]))
+	fds_slice = np.squeeze(np.asarray(fds.iloc[[i],1:]))
+
+	fig = figure()
+	errorbar(data_slice,y_data,xerr=0.15*data_slice,linestyle='None',marker='o',ms=8,color='k',label='Experiment')
+	plot(fds_slice,y_fds,'k',label = 'FDS')
+	ax1 = gca()
+	xlabel('Heat Flux (kW/m$^{2}$)', fontsize=20)
+	ylabel('Distance above Burner (m)', fontsize=20)
+	xticks(fontsize=16)
+	yticks(fontsize=16)
+	grid(True)
+	ax = gca()
+	axis([0, 45, 0, 1.2])
+	legend(numpoints=1,loc='upper right',fontsize=16 )
+	savefig(plot_dir + test_name + distance[i] + '_RI.pdf',format='pdf')
+	close()
+

### 2017-03-12 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
cut excess figures moved to CH 8 extra

@@
 
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0601T}\\
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_601T}\\
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0600T}\\
-	\caption[FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview plume temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.
-Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
-	\label{FDS_Plume_Temp_IWGB_Comp_}
-\end{figure}
-
-\begin{figure}[p]
-	\centering
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=05_0300WT}\\
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}\\
-	\includegraphics[width=.625\columnwidth]{../Figures/NG_80kW_GBWall_2D_RI=20_0300WT}\\
-	\caption[FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s for the 80~mm, 40~mm, and 20~mm mesh resolution cases]{FDS Smokeview wall temperatures with the burner 0.61~m from the wall at approximately 180 s of the steady state simulation.
-Beginning with the top graphic and moving down, the 80~mm, 40~mm, and 20~mm mesh resolution cases are presented.}
-	\label{FDS_Wall_Temp_IWGB_Comp_}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300WT}
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300WT}\\
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300WT}
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300WT}\\
-  \caption[FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall]{FDS wall temperatures based on 40~mm grid compared with natural gas burner different distances from the wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_TCWall_IWGB_comp}
-\end{figure}
-
 \subsection{Heat Flux}
@@
   \label{FDS_HFCL_IWNG_comp}
-\end{figure}{}
+\end{figure}
 
@@
   \label{FDS_HFEdge_IWNG_comp}
-\end{figure}
-
-\begin{figure}[h]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_2D_RI=10_0300HF}
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_1D_RI=10_0300HF}\\
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_p5D_RI=10_0300HF}
-  \includegraphics[width=2.5in]{../Figures/NG_80kW_GBWall_0D_RI=10_0300HF}\\
-  \caption[FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall]{FDS gauge heat flux values based on 40~mm grid with natural gas burner positioned different distances from the wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_WallHF_IWGB_comp}
 \end{figure}

### 2017-03-13 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
n

@@
 The CFD models require more knowledge, more computer resources, and more input data to utilize correctly.
-Currently modelers need to develop there own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the specific material of interest.
+Currently modelers need to develop their own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the specific material of interest.
 
@@
 
+\begin{figure}[h!]
+	\includegraphics[width=5in]{../Figures/FHNG01_RI} \\
+	\caption[Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
+	\label{FHNG01_RI}
+\end{figure}
+
 This seemed to be counter intuitive to the results expected from an increased RI.
 However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich), which resulted in temperatures significantly lower than measured.
-The affect of this fuel rich area above the burner results in poorer agreement with increasing RI.
+The effect of this fuel rich area above the burner results in poorer agreement with increasing RI.
 It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone was moved to a higher elevation relative to what was measured.
@@
 As FDS is a complex model, this explaination may be only one possibility.
-
-\begin{figure}[h]
-	\includegraphics[width=5in]{../Figures/FHNG01_RI} \\
-	\caption[Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
-	\label{FHNG01_RI}
-\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure}[h]
 	\includegraphics[width=5in] {../Figures/McCaffrey_Plume_comp}  \\
@@
 This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
-Not surprisely, the sub model of the thermocouple device shifted the FDS values slightly.
+Not surprisingly, the sub model of the thermocouple device shifted the FDS values slightly.
 At temperatures greater than 700~$^\circ$C, the `thermocouple' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
@@
 While FDS can accomodate changes in thermoconductivy and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
-For the purposes of this study, the input values will remain constant throught out the course of the simulations.
+For the purposes of this study, the input values will remain constant throughout the course of the simulations.
 The only variable will be the distance between the edge of the burner and the wall.
 
-As before the FDS simultions will include devices, which are used to simulate thermocouples and total heat flux gauges.
-This devices were positioned in locations similar to the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
+As before, the FDS simultions will include devices which are used to simulate thermocouples and total heat flux gauges.
+These devices were positioned in locations similar to the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
 In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simluated by FDS.
@@
 Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.
-
- There seem to be a couple of items that stick out from the graphs.
-First is what appears to be a separation of the temperature data into three distinct sections.
-The bottom three positions, 0.2~m through 0.6~m, represent the hottest section.
-The next two measurement positions at 0.8~m and 1.0~m are similar in temperature.
-The third section extends from 1.2 through 2.2~m above the burner and has the shape of a smooth curve decreasing in temperature with increasing elevation.
-Comparing the temperatures to the flame height analysis in Chapter 2, the first section aligns with the median flame height, the second section aligns with the portion of the flame that intermittent, 40~$\%$ of the time or less.
-The upper most section of the temperature data aligns with the thermal plume above the flame.
-
- The second issue is that the FDS predictions do not align equally well with the data from each position, with the best agreement occurring when the burner is positioned against the wall.
-Further the temperatures for the burner position, 0.61~m from the was thought to be equivalent to the source fire experiments documented in Chapter 2.
-However that is not the case.
-The installation of the wall resulted in movement of the flame and plume.
-The flames oscillate toward the wall and as a result move away from the thermocouples centered over the burner.
-The resulting decrease in temperature may account for the difference between the plume tempertaures and the simulated temperatures from FDS.
 
@@
 
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D_RF_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D_RF_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D_RF_RI}\\
+  \caption[FDS values based on two different RI values compared with the wall surface temperature measurements.]{FDS values based on two different RI values compared with the wall surface temperature measurements.
+The temperatures are averages of two replicate experiments.
+Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+  \label{FDS_Wall_Temp_IWGB_comp}
+\end{figure}
+
+ There seem to be a couple of items that stick out from the graphs.
+First is what appears to be a separation of the temperature data into three distinct sections.
+The bottom three positions, 0.2~m through 0.6~m, represent the hottest section.
+The next two measurement positions at 0.8~m and 1.0~m are similar in temperature.
+The third section extends from 1.2 through 2.2~m above the burner and has the shape of a smooth curve decreasing in temperature with increasing elevation.
+Comparing the temperatures to the flame height analysis in Chapter 2, the first section aligns with the median flame height, the second section aligns with the portion of the flame that is intermittent, 40~$\%$ of the time or less.
+The upper most section of the temperature data aligns with the thermal plume above the flame.
+
+ The second issue is that the FDS predictions do not align equally well with the data from each position, with the best agreement occurring when the burner is positioned against the wall.
+Further the temperatures for the burner position, 0.61~m from the was thought to be equivalent to the source fire experiments documented in Chapter 2.
+However that is not the case.
+The installation of the wall resulted in movement of the flame and plume.
+The flames oscillate toward the wall and as a result move away from the thermocouples centered over the burner.
+The resulting decrease in temperature may account for the difference between the plume tempertaures and the simulated temperatures from FDS.
+
 Figure~\ref{FDS_Wall_Temp_IWGB_comp} is analogous to Figure~\ref{FDS_Plume_IWGB_comp} except it compares the gypsum wallboard surface temperatures against the FDS simulated temperatures.
@@
 
-\begin{figure}[ht!]
-  \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_2D_RF_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_1D_RF_RI}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0p5D_RF_RI}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_TC_Surface_Center_Avg_0D_RF_RI}\\
-  \caption[FDS values based on two different RI values compared with the wall surface temperature measurements.]{FDS values based on two different RI values compared with the wall surface temperature measurements.
-The temperatures are averages of two replicate experiments.
-Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
-  \label{FDS_Wall_Temp_IWGB_comp}
-\end{figure}
-
 \subsection{Heat Flux}
@@
 
-The FDS values significantly underpredict the measured heat flux values along the right edge of the burner.
-The best agreement occurs at the burner positions away from the wall.
-At this position, the fire pattern on the walls show that the lines of demarcation are occuring very close to the edge of the burner.
-Again flame movement seems to to be the main cause of the difference that is accentuated by a measurement location that is very sensitive to heat flux and position.
-
 \begin{figure}[ht!]
   \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_2D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_1D_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0p5D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Center_Avg_0D_RI}\\
   \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.]{FDS values based on two different RI values compared with heat flux measurements on the wall along the centerline of the natural gas fueled burner.
@@
 
+The FDS values significantly underpredict the measured heat flux values along the right edge of the burner.
+The best agreement occurs at the burner positions away from the wall.
+At this position, the fire pattern on the walls show that the lines of demarcation are occuring very close to the edge of the burner.
+Again flame movement seems to to be the main cause of the difference that is accentuated by a measurement location that is very sensitive to heat flux and position.
+
 \begin{figure}[ht!]
   \centering
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_2D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_1D}\\
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0p5D}
-  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0D}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_2D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_1D_RI}\\
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0p5D_RI}
+  \includegraphics[width=2.5in]{../Figures/IWGB_NG_HF_Offset_Avg_0D_RI}\\
   \caption[FDS values based on two different RI values compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner]{FDS values based on two different RI values compared with heat flux measurements on the wall along the right edge of the natural gas fueled burner.
@@
 
-Table to compare measured flame height with FDS cal~\cite{McDermott:2011}
-
-Flame Height 2D  20~mm  at 99~\%  1.28~m
-
-Flame Height 0D  20~mm  at 99~\%  1.46~m
+Complete to compare measured flame height with FDS cal~\cite{McDermott:2011}
+
+\begin{table}[h]
+  \small
+  \centering
+  \begin{tabular}{|c|c|c|c|} \hline 
+Distance from Wall 		&  Flame Height 			  	& RI=5       		& RI=10      		  \\
+    					&  Range          				&  (80~mm grid)  	&  (40~mm grid)  	  \\
+    (m)					&  (m) 							& (m) 				& (m) 				  \\ 
+\hline    0.61			&  0.73 to 1.14         		& 1.02 to 1.27      & 1.xx to 1.28         \\
+\hline    0.31			&								&					&					    \\
+\hline    0.15			&								&					&						\\
+\hline	  0.0			&								&					&  1.xx to 1.46 	  \\
+\hline
+  \end{tabular}
+  \caption[Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5 and 10.]{Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5, and 10.}
+  \label{tab:FDS_FH_IWNG}
+\end{table}
 

### 2017-03-14 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
FH Table  CH 8
Incorp CF comments in Ch1

@@
 \acknowledgments{
-I would like to thank Prof.~Fleischmann, my senior advisor with the University of Canterbury, as well as, Dr.~Kevin McGrattan, and Dr.~Craig Weinschenk from the National Institute of Standards and Technology for their guidance, assistance, and support throughout this study.
+I would like to thank Prof.~Fleischmann, my senior advisor with the University of Canterbury, Dr.~Kevin McGrattan from the National Institute of Standards and Technology, and Dr.~Craig Weinschenk from the UL Firefigther Safety Research Institute for their guidance, assistance, and support throughout this study.
 
@@
 
-Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 37 years of marriage.
+Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 38 years of marriage.
 I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for ``buying me time'' to work on my studies.}
@@
 $\chi_r$ \> radiative fraction \\
-discusion$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
+$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
 $\dot{Q}$ \> heat release rate (kW) \\ 
@@
 Overholt developed the NIST verification and validation study~\cite{Overholt:2014}.
-Not all of the correlations in the FDTs were included in the study, because an insufficient amount of reliable data is available to conduct validation.
+Not all of the correlations in the FDTs were included in the study, because a sufficient amount of reliable data was not available to conduct a proper validation.
 The correlations for flame height and time to ignition were not included in the validation study.
@@
 The majority of intentional fires in structures have occurred in residential occupancies, therefore this study focused on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupancies.
-A common height for a residential occupancies is 2.4~m in height.
+A common height for a residential occupancies is 2.4~m.
 With a wall height of 2.4~m, these experiments used small fires with flame heights of approximately 1.2~m.
@@
 Replicate experiments exposing gypsum wallboard to the fires were conducted in order to examine the repeatability of the fire patterns.
-Correlations between the fire characteristics and the fire patterns will be examined.
+Correlations between the fire characteristics and the fire patterns were be examined.
 
@@
 In other words they provide results in the same format that the investigator would see or document the fire pattern.
-Comparison between the experiments and the model may provide valuable validation data for the model.
+Comparison between the experiments and the model provide valuable validation data for the model.
 
@@
 
+N.B.
+This section may be considered atypical for an engineering thesis but it is included here for two reasons.
+Firstly, to provide a narrative description for readers that may be unfamiliar with how fire patterns are routinely relied on in fire investigations.
+The second is to put this work into an applied context that is familiar to fire investigators that may be un accustomed to reading detailed research as found in this thesis.
+
 For the moment let's step into the shoes of a fire investigator and examine a potential investigation scenario.
-It is 8:30 in the morning on a cool fall morning and you are being called to a fire scene.
+It is 8:30 on a cool fall morning and you are being called to a fire scene.
 As you prepare to leave for the fire scene, you begin to collect information on the fire as you listen to your department radio.
@@
 The fire occurred in area of older townhomes.
-The socio-economics of the neighborhood are such the the people that live there have many life struggles.
+The socio-economics of the neighborhood are such that the people that live there have many life struggles.
 Enroute you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
@@
 On the rear or ``side C'' of the house the door and windows are intact but open.
-There are no smoke stains or thermal damage around any of the openings on the rear.
+There are no smoke stains and no thermal damage around any of the openings on the rear.
 No sign of smoke alarms in the home.
@@
 Looking to your right, two chairs in front of the living room window have some thermal damage.
-There are is a clear horizontal line of demarcation on the large wood TV stand in the corner.
+There is a clear horizontal line of demarcation on the large wood TV stand in the corner.
 As your eyes move from the corner back toward the rear of the townhome and the kitchen, you notice that the elevation of the line of demarcation is increasing.
@@
 Your are focusing on the area with the most damage, the area with the sofa and chair.
+You think that this may be the area of origin.
+
 As you are looking toward the ``B wall'' of the living room you note that the right side of the chair is badly burned and it is burned from the floor level up.
@@
 
-You have now developed your first hypothesis about the origin of the fire.
+You have now developed your first hypothesis about the cause of the fire.
 A radiant style, electric heater was turned on.
@@
 This would indicate that the fire was inside the sofa at some point.
-Further is appears that all of the foam cushioning is burnt off of the right side of the sofa, while there is a piece of polyurethane foam cushion on the left side of the sofa.
+Further, it appears that all of the foam cushioning is burnt off of the right side of the sofa, while there is a piece of polyurethane foam cushion on the left side of the sofa.
 However that foam could have gotten moved during the fire suppression.
@@
 Besides interviews what else can you do to eliminate the inconsistencies?
-The fire investigators' challenge we be reexamined in Chapter IX.
+The fire investigators' challenge will be reexamined in Chapter IX.
 
@@
     (m)					&  (m) 							& (m) 				& (m) 				  \\ 
-\hline    0.61			&  0.73 to 1.14         		& 1.02 to 1.27      & 1.xx to 1.28         \\
-\hline    0.31			&								&					&					    \\
-\hline    0.15			&								&					&						\\
-\hline	  0.0			&								&					&  1.xx to 1.46 	  \\
+\hline    0.61			&  0.73 to 1.14         		& 0.88 to 1.02      & 1.01 to 1.24         \\
+\hline    0.31			&		-						& 0.93 to 1.28		& 1.00 to 1.23		    \\
+\hline    0.15			&		-						& 0.91 to 1.23		& 1.01 to 1.24			\\
+\hline	  0.0			&		-						& 1.03 to 1.34		& 1.20 to 1.52   	  \\
 \hline

### 2017-03-15 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
CF changes incorp Ch 2 through 5

@@
 
-You have now developed your first hypothesis about the cause of the fire.
+Based on the evidence observed so far, you have now developed your first hypothesis about the cause of the fire.
 A radiant style, electric heater was turned on.
@@
 A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover, or early growth stage, fires.
-A fixed fire source footprint, a 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
+A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
 The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.
-Heat release rate, flame/plume gas temperatures, and total heat flux from the flames were measured and flame movement and height were recorded with photographs and videos.
+Heat release rate, flame/plume gas temperatures, and total heat flux from the flames were measured.
+In addition, flame movement and height were recorded with photographs and videos.
 Given the focus on residential fires, small source fires were selected so that the burn pattern would be limited to less than 2.4~m in height.
@@
 Starting from the exposed bead, the thermocouple wire was sheathed in a 3.2~mm diameter inconel shield, 0.76~m in length.
-Thermocouple is ungrounded.
+The thermocouple was ungrounded.
 The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer.
@@
 
-The natural gas flow to the burner is measured in terms of volumetric flow with a dry test meter, that is corrected for temperature and pressure.
-The flow rate was determined to be 4.5 cubic feet per minute as output from the meter or 2.1~liters per second.
-This yields a mass flow of natural gas of approximately 2~g/s.
+The natural gas flow to the burner was measured in terms of volumetric flow with a dry test meter that was corrected for temperature and pressure.
+The flow rate was determined to be 2.1~liters per second.
+This yielded a mass flow of natural gas of approximately 2~g/s.
 
@@
   \includegraphics[width=\textwidth]{../Figures/Source_Fire_Flamer}\\
-  \caption[A photograph of the source fire flamer and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.
+  \caption[A photograph of the source fire flame and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.
 In the foreground, from left to right, are the video, 35~mm SLR and thermal imaging camera.}
@@
 
-The gasoline pan fire has was ignited and then burned until the fuel was consumed.
+The gasoline pan fire was ignited and then burned until the fuel was consumed.
 Therefore the heat release rate curves had more of a ``bell shape''  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
@@
 Examples of the photographic images are presented in Figs.~\ref{Gas_Foam_Photos} and \ref{Gasoline_Photos}.
-Figure~\ref{Gas_Foam_Photos} is a photograph of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW and a photograph of the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
+Figure~\ref{Gas_Foam_Photos} has photographs of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW, the gasoline taken near its average peak heat release rate of 80~kW, and the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
 Figure~\ref{Gasoline_Photos} presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100~kW.
@@
      \hline
-     Fuel	            & Mean (m)  & Range (m) \\ \hline \hline
+     Fuel	            & Mean (m)  & Range (m) \\ \hline 
      Natural Gas	    & 0.70	    & 0.50 to 0.98 \\
@@
 The fires were placed at predetermined, fixed positions away from the wall.
-The fires were prepared and conducted in the same manner as the they were in the fire characterization experiments.
+The fires were prepared and conducted in the same manner as they were in the fire characterization experiments.
 As a result the exposure time of the target wall to the fire was 300 seconds.
@@
 
-\begin{table}
+\begin{table}[h]
 	\centering
@@
 Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array, a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the TC positioned on the front surface of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array, a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the thermocouple positioned on the front surface of the wall.
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
@@
 
+\subsection{Natural Gas Burner Plume and Wall Exposures}
 Figures~\ref{TC_Plume_TWNG_comp} through \ref{TC_Back_Center_TWNG_comp} show a complete set of data, averaged over two replicates, for the instrumented, non combustible wall natural gas burner experiments.
@@
 
-\subsection{Wall Temperatures}
+\subsection{Wall Exposures from Source Fires}
 
@@
 \end{figure}
-
-\subsection{Heat Flux}
 
@@
 
-\section{Summary}
+\section{Fire Pattern Prediction}
 
@@
 		\hline  Position & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) & Temp~($^\circ$C) & HF~(kW/m$^{2}$) 	\\
-		\hline \hline 0.61~m & 95 & 5 & 106 & 7 & 71 & 6 \\
+		\hline 0.61~m & 95 & 5 & 106 & 7 & 71 & 6 \\
 		\hline 0.31~m & 164 & 14 & 232 & 24 & 148 & 16	\\
@@
 Using the same analysis, the polyurethane foam burner would create a shorter burn region approximately 0.4~m to 0.6~m.
-The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the may gypsum wall board ignite.
+The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wall board may ignite.
 
@@
 With other project demands, the number of instrumented wallboard experiments that could be conducted under the oxygen consumption calorimeter was reduced due to time constraints.
-The test matrix is shown in Table~\ref{tab:IWGB_experiments}.
 There was also a concern that these experiments would have limited value due to potential interference from the water-cooled heat flux gauges and potential physical damage caused by drilling the holes for them.
@@
 		\hline Density & \multicolumn{2}{c|}{Thermal Conductivity}   & \multicolumn{2}{c|}{Specific Heat}  \\
-		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\ \hline
+		\hline (kg/m$^3$) & Temperature ($^{\circ}$C) & (W/mK)  & Temperature ($^{\circ}$C)  & (kJ/kg $^{\circ}$C) \\ 
 		\hline 807  & 24 	& 0.14 	& 20	& 1.09 \\
@@
 		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
-		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ \hline
+		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ 
 		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
@@
 
-At the 0.15~m position the heat flux exhibits only a small decrease to the 0.2~m and 0.4~m above the burner heat flux sensors in the centerline array.
+At the 0.15~m position the heat flux exhibits only a small decrease to the heat flux sensors 0.2~m and 0.4~m above the burner in the centerline array.
 However, the heat flux sensor positioned at 0.6~m above the burner showed an increase.
@@
 the burned region, was 0.8~above the burner.
-This is consistent with the prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible wall experiments.
+This is consistent with the Chapter 3 prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible wall experiments.
 
@@
 For the image on the left, the burner was positioned 0.15~m from the wall.
-For the image on the right, the burner was positioned 0.8~m from the wall.}
+For the image on the right, the burner was positioned 0.0~m from the wall.}
 	\label{IWGB_Gas_patterns}
@@
 The average peak burned region height was 0.3~m.
-The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Ch 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
+The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Chapter 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
 
@@
 	\includegraphics[width=\textwidth]{../Figures/Cone_Cal} \\
-	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter}
+	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter~\cite{babrauskas:1984}}
 	\label{Cone_Cal}
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition &  Fire Effect  \\
-		\hline (kW/m$^2$) &  & (s)  &   \\ \hline
+		\hline (kW/m$^2$) &  & (s)  &   \\ 
 		\hline 25	& No 	& NA 		& Paint \& paper charred \& cracked \\
@@
 		\hline Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ \hline
+		\hline (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ 
 		\hline 30 	& Yes 	& 112	& 375 	 \\
@@
 		\hline Postion & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
-		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ \hline
+		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ 
 		\hline 100 	& 21	& Yes 	& 133	& 315 	 \\
@@
 		\hline Incident Heat Flux & Heat Release Rate per Unit Area    \\
-		\hline (kW/m$^2$) & (kW/m$^2$)  \\ \hline
+		\hline (kW/m$^2$) & (kW/m$^2$)  \\ 
 		\hline 35 	& 163 	\\
@@
 
-Each apparatus provided a slightly different thermal exposure to painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
+Each apparatus provided a slightly different thermal exposure to the painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
 Each test method has a specific parameter or parameters for which they were designed to measure.
@@
 This chapter was anticipated to provide data that that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures, 10 to 75~kW/m$^2$.
-The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature but the reason for the 200~$^{\circ}$C could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
+The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature but the reason for the approximately 200~$^{\circ}$C different could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
 
@@
 	\hline
-	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline \hline
+	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline 
 		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\
@@
 	\hline
-	Fuel (\# of tests)      &   Wall Type   & Max. Height Left (m)	 	& Area Left (m$^2$)				&  Max. Height Right (m)        & Area (m$^2$)  				\\ \hline \hline
+	Fuel (\# of tests)      &   Wall Type   & Max. Height Left (m)	 	& Area Left (m$^2$)				&  Max. Height Right (m)        & Area (m$^2$)  				\\     \hline
 		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.15 (20~\%)  & 0.061 $\pm$ 0.028 (46~\%) 	&  0.78 $\pm$ 0.17 (22~\%) 	 	& 0.061 $\pm$ 0.028 (46~\%)  	\\
@@
 The uncertainties regarding the width and area of the patterns were higher up to $\pm$ 33~\%.
-While the natural gas and the gasoline are diffent fuels there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
+While the natural gas and the gasoline are different fuels there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
 The larger uncertainty in the areas of the pattern may be due to the slight movement of the flames back and forth across the wall.

### 2017-03-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Ch  8 images

@@
 The goal of this chapter is to utilize an analytical tool to predict or simulate the results from some of the key experiments conducted in this study.
-Unlike the previous chapter the computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
+Computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
 The CFD models require more knowledge, more computer resources, and more input data to utilize correctly.
-Currently modelers need to develop their own data or rely on poorly defined databases with the hope that the material tested in the database is similar to the specific material of interest.
+Currently modelers need to develop their own data or rely on loosely defined databases with the hope that the material tested in the database is similar to the specific material of interest.
 
@@
 In this section, the natural gas burner will be modelled with a range of grid cell resolutions and radiative fraction values.
-The results are compared against the source fire characterization data to determine which grid cell resolution and radiative fraction will provide the best fire simulation for use in the simulations of the wall and compartment experiments.
+The results are compared against the source fire characterization data to determine which grid cell resolution and radiative fraction provided the best fire simulation for use in the simulations of the wall and compartment experiments.
 
@@
 To examime the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were choosen to model the fire.
-The resulting mesh resolution index (RI) values were approximately 4.4, 8.8, and 17.5, respectively.
-Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) mesh resolution.
-FDS simulations of the source fire characterization experiments will be conducted with these mesh resolutions and compared with the results from the experiments.
+The resulting resolution index (RI) values were approximately 4.4, 8.8, and 17.5, respectively.
+Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) resolution.
+FDS simulations of the source fire characterization experiments will be conducted with these resolutions and compared with the results from the experiments.
 
@@
 
-The burner was modeled as an obstruction with a open top area of 0.09 m$^2$, elevated 0.08~m above the test surface.
+The burner was modeled as an obstruction with a open top area of 0.09~m$^2$, elevated 0.08~m above the test surface.
 This is the same physical size of the natural gas burner used in the experiments.
@@
 The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.
-In FDS version 6, the default radiant fraction for the `methane' reaction was set to 0.2.
+In FDS version 6, the default radiant fraction for the `methane' reaction was set to~0.2.
 
@@
 One such device, is used to determine the heat release rate per unit length.
-This device was used to determine flame height based on that measure.
+This device was used to determine flame height~\cite{McDermott:2011}.
 
@@
 Figure~\ref{FHNG01_RI} shows the comparison of the centerline gas burner temperatures with three different sets of FDS results.
-The only variable in the simulations is the RI.
-The RIs include three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).
+The only variable between these simulations was the RI.
+The RIs included three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).
 The associated 95~\% confidence limits are also shown the temperature value for each height.
@@
 The effect of this fuel rich area above the burner results in poorer agreement with increasing RI.
-It appears that the the RI=10 and RI=20 models follow the correct trend, however the combuston zone was moved to a higher elevation relative to what was measured.
+It appears that the the RI=10 and RI=20 models follow the correct trend, however the combustion zone was moved to a higher elevation relative to what was measured.
 For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seemed to coincide with the measured value at 0.3~m above the burner.
-Making the adjustment appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
+Adjusting the FDS corresponding predictions from the RI=10 and RI=20 models down to the 0.3~m position appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
 As FDS is a complex model, this explaination may be only one possibility.
 
-These simulation results are consistant with the comparisons made to the McCaffery's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
-McCaffery used a natural gas burner, 0.30~m square, which is similar in size to the burner used in this study.
-McCaffery noted that, "visually non-axisymmetric behavior could be observed only very close to the burner surface".
-In the study, temperatures were measured with Type K thermocouples covered with a 1.0~mm stainless steel sheath.
+These simulation results are consistant with the comparisons made to the McCaffrey's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
+McCaffrey used a natural gas burner, 0.30~m square, which is similar in size to the burner used in this study.
+McCaffrey noted that, "visually non-axisymmetric behavior could be observed only very close to the burner surface".
+In the McCaffrey study, temperatures were measured with Type K thermocouples covered with a 1.0~mm stainless steel sheath.
 The peak heat release rate in McCaffery's plume study was 57.5~kW, this heat release rate was also the closest to the 80~kW fires in the current study.
-The comparison between the McCaffery plume correlation and the FDS simulations at RI values of 5, 10 and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
+The comparison between the McCaffrey plume correlation and the FDS simulations at RI values of 5, 10 and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
 Focusing on the data between the burner surface and the 1~m above the burner surface, FDS underpredicted the temperature near the surface of the burner and then overpredicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases respectively.
@@
 The best agreement along the vertical array of temperatures was provided by the RI=5 model.
-Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bead are generating the diffrences between the gas temperature and the measured temperature FDS values.
+Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bead may be generating the differences between the gas temperature and the measured temperature FDS values.
 
@@
 
-From the Chapter 2 source fire characterization experiments, the measured heat flux at 0.95~m from the centerline of the burner and 0.5~m above the top of the burner. 
+The heat flux data being used for comparison was from the Chapter 2 source fire characterization experiments, the measured heat flux at 0.95~m from the centerline of the burner and 0.5~m above the top of the burner.
 In Figure~\ref{FHNG01_HF_RI} the averaged values from both heat flux gages are plotted against the FDS calculated heat flux at three different RIs of 5, 10 and 20.
-These FDS simulations used the default radiative fraction value of 0.2.
-As with the temperature comparisons, the course grid with an RI equal to 5 provided the best agreement to the measurements, however all of the values were lower than the measured heat flux.
+These FDS simulations used the default radiative fraction value of~0.2.
+As with the temperature comparisons, the course grid with an RI=5 provided the best agreement to the measurements, however all of the values were lower than the measured heat flux.
 
@@
 
-One last check on the plume temperature predictions was made to examine the impact of the range of radiative fractions on the FDS results.
-The comparisons were made using the course grid, RI=5, the radiative fraction values of 0.20, 0.22, 0.25, and 0.30, as before.
+Another examinination of the plume temperature predictions was made to examine the impact of the range of radiative fractions on the FDS results.
+The comparisons were made using the course grid, RI=5, and radiative fraction values of 0.20, 0.22, 0.25, and 0.30, as before.
 The simulations with radiative fractions between 0.2 and 0.25 were within the 2~$\sigma$ limits of the temperature measurements at each elevation.
@@
 
-One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height when energy stops being released along the vertical centerline of the gas burner.
+One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height when energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
 Estimates of the flame height were made by estimating the height where 0.95 to 0.99~$\%$ of the total energy had been released.
 Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
-The course and medium grids, RI=5 and R=10, are not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range.
+The course and medium grids, RI=5 and R=10, were not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range.
 
@@
     Range          						&  (80~mm grid)  	&  (40~mm grid)  	&  (20~mm grid)  \\
-    (m)     							& (m) 				& (m) 				& (m)  			 \\ \hline
+    (m)     							& (m) 				& (m) 				& (m)  			 \\ 
     \hline 0.73 to 1.14         		& 1.02 to 1.27      & 1.07 to 1.27      & 1.28 to 1.42   \\
@@
 
-The comparisons of the temperature, heat flux, and flame heights for this specific scenerio show the best agreement with the 80~mm grid (RI=5) FDS simulations.
-Even though the differences between the radiative fractions of 0.2 and 0.22 are small, for the remaining simulation cases, 0.22 will be used.
+The comparisons of the temperature, heat flux, and flame heights for this specific scenerio showed the best agreement with the 80~mm grid (RI=5) FDS simulations.
+Even though the differences between the radiative fractions of 0.2 and 0.22 were small, for the remaining simulation cases, 0.22 will be used.
 While the best agreement for the fire was demonstrated with the RI= 5 grid, the RI=10 grid will also be used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models get additional obstructions and surfaces.
@@
 
-The next comparsions will be made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
+The next comparsions were made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
 Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
 The simulations will replicate the same distances.
-The simulation includes a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
+The simulation included a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
 The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter 4.
@@
 
-As before, the FDS simultions will include devices which are used to simulate thermocouples and total heat flux gauges.
+As before, the FDS simulations included devices which are used to simulate thermocouples and total heat flux gauges.
 These devices were positioned in locations similar to the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
-In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simluated by FDS.
+In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simulated by FDS.
 
@@
  There seem to be a couple of items that stick out from the graphs.
-First is what appears to be a separation of the temperature data into three distinct sections.
+First, there appears to be a separation of the temperature data into three distinct sections.
 The bottom three positions, 0.2~m through 0.6~m, represent the hottest section.
@@
  The second issue is that the FDS predictions do not align equally well with the data from each position, with the best agreement occurring when the burner is positioned against the wall.
-Further the temperatures for the burner position, 0.61~m from the was thought to be equivalent to the source fire experiments documented in Chapter 2.
+Further the temperatures for the burner position, 0.61~m from the wall, was thought to be equivalent to the source fire experiments documented in Chapter 2.
 However that is not the case.
@@
 The flames oscillate toward the wall and as a result move away from the thermocouples centered over the burner.
-The resulting decrease in temperature may account for the difference between the plume tempertaures and the simulated temperatures from FDS.
+The resulting decrease in temperature may account for the difference between the plume temperatures and the simulated temperatures from FDS.
 
@@
 
+Reviewing the videos from a natural gas burner instrumented gypsum wallboard experiment with the burner positioned at 0.310~m from the wall, we can see examples of the flame movement.
+In the top row of Figure~\ref{FDS_IWNG_Flame_comp} the three images exhibit points in time where the flame was moving toward the instrumented wall and away from the verticle array of thermocouples that are positioned above the center line of the burner.
+The bottom row of images are from the same fire experiment looking at it from the front.
+These images also show how the pulsations and movements of the flame change positions relative to the fixed positions of the thermocouples and heat flux gauges.
+
+\begin{figure}[ht!]
+  \centering
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Side1}
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Side2} 
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Side3}       \\
+ \vspace{5mm}                                                             
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Front1}   
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Front2}     
+  \includegraphics[width=1.5in]{../Figures/IWGB_NG_Front3}      \\
+  \caption[Images of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.]{FImages of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.
+The natural gas burner was poistioned 0.31~m from the instrumented gypsumboard wall.}
+  \label{FDS_IWNG_Flame_comp}
+\end{figure}
+
 \subsection{Flame Height}
 
-Complete to compare measured flame height with FDS cal~\cite{McDermott:2011}
+A flame height range was calculated from each FDS simulation by multiplying the total energy released by 95 and 99~\%, and linking those values to the corresponding height form the *****.
 

### 2017-03-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
CH 8 and spell check

@@
 \acknowledgments{
-I would like to thank Prof.~Fleischmann, my senior advisor with the University of Canterbury, Dr.~Kevin McGrattan from the National Institute of Standards and Technology, and Dr.~Craig Weinschenk from the UL Firefigther Safety Research Institute for their guidance, assistance, and support throughout this study.
+I would like to thank Prof.~Fleischmann, my senior advisor with the University of Canterbury, Dr.~Kevin McGrattan from the National Institute of Standards and Technology, and Dr.~Craig Weinschenk from the UL Firefighter Safety Research Institute for their guidance, assistance, and support throughout this study.
 
@@
 A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
-The flooring radiant panel, ASTM~E648, and a modified radiant panel apparatus based on ASTM~E162 were used to examine this value~\cite{ASTM_E648},~\cite{ASTM_E162}.
+The flooring radiant panel, ASTM~E 648, and a modified radiant panel apparatus based on ASTM~E 162 were used to examine this value~\cite{ASTM_E648},~\cite{ASTM_E162}.
 
@@
 
-Cone calorimeter experiments were conducted, based on ASTM~E1354, to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
+Cone calorimeter experiments were conducted, based on ASTM~E 1354, to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
 
@@
 Firstly, to provide a narrative description for readers that may be unfamiliar with how fire patterns are routinely relied on in fire investigations.
-The second is to put this work into an applied context that is familiar to fire investigators that may be un accustomed to reading detailed research as found in this thesis.
+The second is to put this work into an applied context that is familiar to fire investigators that may be unaccustomed to reading detailed research as found in this thesis.
 
@@
 You start to develop an image in your mind about the location of the home involved in the fire.
-The fire occurred in area of older townhomes.
+The fire occurred in area of older town homes.
 The socio-economics of the neighborhood are such that the people that live there have many life struggles.
-Enroute you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
+En route you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
 The husband and father also lives at that address but is unaccounted for at this time.
@@
 You notice that three of the four windows on the second floor have been removed.
-On ``side D'' of the townhome there are no openings and no smoke or fire damage is present.
+On ``side D'' of the town home there are no openings and no smoke or fire damage is present.
 On the rear or ``side C'' of the house the door and windows are intact but open.
@@
 There is a clear horizontal line of demarcation on the large wood TV stand in the corner.
-As your eyes move from the corner back toward the rear of the townhome and the kitchen, you notice that the elevation of the line of demarcation is increasing.
+As your eyes move from the corner back toward the rear of the town home and the kitchen, you notice that the elevation of the line of demarcation is increasing.
 This may be an indicator that the origin of the fire is closer to the front of the living room.
@@
 A 35~mm single lens reflex camera was used to record digital still photographs of the fires.
-The camera had an 8 megapixel resolution.
-A mini DV camcorder with 0.7 megapixel resolution was used to capture the video.
+The camera had an 8 mega-pixel resolution.
+A mini DV camcorder with 0.7 mega-pixel resolution was used to capture the video.
 A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.
@@
 It is worth noting that as the plume temperatures decrease the temperatures of the thermocouples installed in the wall face increased, indicating that after the wall heats up the flame pulls toward the wall.
-Perhpas as a result of increased convection on the face of the wall.
+Perhaps as a result of increased convection on the face of the wall.
 
@@
 A summary of the peak average temperatures and heat fluxes at the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.
-Based on the temperature criteria for igniting gyspum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
+Based on the temperature criteria for igniting gypsum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
 Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria, when positioned against the wall and at when the edge of the burner was 0.15~m away from the wall.
@@
 Of course the temperatures of the thermocouples in the wall are a result of the energy transferred to the wall and the thermo-physical properties of the wall material.
-The properties of the calcium silicate board are simlar but not identical to gypsum wallboard.
+The properties of the calcium silicate board are similar but not identical to gypsum wallboard.
 The heat flux data is independent of the wall material, so it may be a better predictor of the fire damage to gypsum wallboard when exposed to the burners at different distances.
@@
 However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
-Based on the heat flux data from Figures~\ref{NCTW_HF_Center_Comp} the natural gas burner should burn the paint and paper off of the face of the gypsum wallboard up to a height of between 0.6~m amd 0.8~m above the burner.
+Based on the heat flux data from Figures~\ref{NCTW_HF_Center_Comp} the natural gas burner should burn the paint and paper off of the face of the gypsum wallboard up to a height of between 0.6~m and 0.8~m above the burner.
 Similarly, the gasoline burner should generate a burn area between 0.8~m and 1.0~m high on a wall composed of gypsum wallboard.
 Using the same analysis, the polyurethane foam burner would create a shorter burn region approximately 0.4~m to 0.6~m.
-The experiments conducted with the instrumented gypsum wall board will provide data for comparsion with data provided in this chapter and provide insight in to where the gypsum wall board may ignite.
+The experiments conducted with the instrumented gypsum wall board will provide data for comparison with data provided in this chapter and provide insight in to where the gypsum wall board may ignite.
 
@@
 With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, a process commonly known as calcination.
-Schroder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
+Schroeder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
 The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction~\cite{Schroeder:1999}.
-NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dihydrated gypsum to map fire patterns.
+NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dehydrated gypsum to map fire patterns.
 
@@
 This was the result of a an early shut down of the gas supply.
-This decrepancy was not noticed until the data was reviewed, at which point there was no opportunity to rerun the experiment.
+This discrepancy was not noticed until the data was reviewed, at which point there was no opportunity to rerun the experiment.
 
 The temperatures measured along the vertical center axis of the burner provided distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature, see Figure~\ref{IWGB_NG_TC_Plume_set}.
-The persistant or continuous flame region appeared to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
+The persistent or continuous flame region appeared to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
 Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seemed to be in the intermittent flame region.
@@
 When the burner was located 0.31~m and 0.15~m away from the wall, the temperatures started at ambient and slowly increased, reaching the peak temperatures at 300~seconds, then the burner was shut off.
-For the case where the burner was in contact with the wall, the two thermocouples located in the persistant flame region indicated a decreasing temperature trend after the paper on the gypsum wallboard had burned away.
-The decrease in temperature my have had been the result of material from the burned gysum wallboard shielding otherwise impacting those thermocouples.
+For the case where the burner was in contact with the wall, the two thermocouples located in the persistent flame region indicated a decreasing temperature trend after the paper on the gypsum wallboard had burned away.
+The decrease in temperature my have had been the result of material from the burned gypsum wallboard shielding otherwise impacting those thermocouples.
 The thermocouple positioned 0.2~m above the burner was exhibiting the same behavior as in the previous experiment, but the problem was resolved during the experiment.
@@
  	\includegraphics[width=.625\columnwidth]{../Figures/IWGBNG05_HF_Offset_Avg}\\
- \caption[Wall heat flux along the endge of the natural gas fueled burner]{Wall heat flux along the vertical edge of the natural gas fueled burner.
+ \caption[Wall heat flux along the edge of the natural gas fueled burner]{Wall heat flux along the vertical edge of the natural gas fueled burner.
 Each graph displays data from a different distance between the edge of the burner and the instrumented gypsum wallboard.
@@
 The average peak burned region height was 0.3~m.
-The uncertainty of the repeatibility of the burn patterns has not been assessed yet, but it appears that the crude predictions from Chapter 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
+The uncertainty of the repeatability of the burn patterns has not been assessed yet, but it appears that the crude predictions from Chapter 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
 
@@
 It was developed at NIST in the 1980s~\cite{babrauskas:1984}.
-The cone calorimeter has been adopted as ASTM~E1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}.
-The cone calorimeter consists of a conical shaped heater, spark ignitor, sample holder, and load cell located underneath an exhaust hood.
+The cone calorimeter has been adopted as ASTM~E 1354, Test Method for Heat and Visible Smoke Release Rates for Materials and Products Using an Oxygen Consumption Calorimeter~\cite{ASTM_E1354}.
+The cone calorimeter consists of a conical shaped heater, spark ignition, sample holder, and load cell located underneath an exhaust hood.
 Typically, the sample is located in the open with free access of air to the combustion zone.
@@
 
-The radiant flooring panel test method is known as ASTM~E648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}.
+The radiant flooring panel test method is known as ASTM~E 648, Standard Method of Test for Critical Radiant Flux of Floor-Covering Systems Using a Radiant Heat Energy Source~\cite{ASTM_E648}.
 The radiant flooring panel is used to measure the flame spread of a material while exposed to an incident radiant heat flux.
@@
 
-A diffusion, propane-fueled, pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~E648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
+A diffusion, propane-fueled, pilot flame from a 254~mm long wide stainless steel burner tube, as specified in ASTM~E 648, was used to ignite the test sample near the edge of the sample closet to the panel~\cite{ASTM_E648}.
 The objective of these experiments was to determine the critical radiant flux for the painted gypsum wallboard samples.
@@
 
-The vertical radiant panel used is documented in ASTM~E162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
+The vertical radiant panel used is documented in ASTM~E 162 and normally provides a measure of downward, opposed-flow flame spread~\cite{ASTM_E162}.
 The apparatus measures the surface flammability of materials using a pre-mixed air-gas-fired radiant panel that has a radiating surface 305~mm wide by 457~mm high.
@@
 	\includegraphics[width=2.08in]{../Figures/RAD_pan_iso} \\
-	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the moveable sample mounting frame trolley for the gypsum wallboard sample on the left.
+	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the movable sample mounting frame trolley for the gypsum wallboard sample on the left.
 The photograph on the right shows an isometric view of the test arrangement.}
@@
 	\caption[Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel] {Photograph of the flame front burning on the gypsum wallboard sample in the flooring radiant panel.
-Thermocouples imbedded at 100~mm intervals in the surface of the painted paper can be seen in front of and behind the flame front.
+Thermocouples embedded at 100~mm intervals in the surface of the painted paper can be seen in front of and behind the flame front.
 The flame is leaning back in the direction the radiant panel.}
@@
 	\begin{tabular}{|c|c|c|c|c|}
-		\hline Postion & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
+		\hline Position & Incident Heat Flux & Ignition & Time to Ignition & Ignition Temperature \\
 		\hline (mm) & (kW/m$^2$) & (Yes or No) & (s)  & Temperature ($^{\circ}$C)   \\ 
@@
 Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
-Notice that the samples exposed to 17.5~kW/m$^2$ and higher have noticable temperature increase to a peak temperature followed by a decrease.
+Notice that the samples exposed to 17.5~kW/m$^2$ and higher have noticeable temperature increase to a peak temperature followed by a decrease.
 This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
 The temperatures at which the change in rate of temperature rise occurred are between 300 and 400~$^{\circ}$C.
-The temperature curve respresenting the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300~$^{\circ}$C after more than 400~seconds of exposure.
+The temperature curve representing the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300~$^{\circ}$C after more than 400~seconds of exposure.
 Multiplying the time that each temperature peaked by the exposure heat flux yields the lowest total of heat was expended to create the most thermal damage, in the shortest time was at the 25~kW/m$^2$ exposure.
 While at the 15~kW/m$^2$ exposure used more than twice the total amount of heat over a longer duration and yielded a lesser amount of damage.
-The flux levels bounded by 15~kW/m$^2$ and 25~kW/m$^2$,have total energy exposures whihch are also bounded by the two extremes.
+The flux levels bounded by 15~kW/m$^2$ and 25~kW/m$^2$,have total energy exposures which are also bounded by the two extremes.
 This data indicates that depending on the exposure the amount of energy required to raise the temperature of the target material toward an ignition temperature, under these conditions, differs by a significant amount.
@@
 For example, there is no guidance on how to conduct a series of experiments to generate all of the data needed for the models.
-Using the gypsum wallboard as an example, material propeties such as density, specific heat, and thermal conductivity change over time as a result of the thermal exposure~\cite{Schroeder:1999,McGraw:1999}.
+Using the gypsum wallboard as an example, material properties such as density, specific heat, and thermal conductivity change over time as a result of the thermal exposure~\cite{Schroeder:1999,McGraw:1999}.
 Of course this behavior is not unique to gypsum wallboard.
@@
 Moving up from the burner, about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
-As the oxygen in the air mixes with the gaseous fuel and combusts, the plume and the pattern expands.
+As the oxygen in the air mixes with the gaseous fuel and burns, the plume and the pattern expands.
 As the flames move up the wall the width tends to increase until about half of the peak height of the pattern, then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame is reduced.
@@
 
-The compartment used for the corner position experiments was the same as the comapartment used for the wall positions experiments detailed in the previous section.
+The compartment used for the corner position experiments was the same as the compartment used for the wall positions experiments detailed in the previous section.
 The burner was positioned in the left, rear corner against the face of two pieces of painted gypsum wallboard.
@@
 The natural gas had a 300~s burn time which was approximately the upper bound for complete extinguishment (total burn time) for the 500~mL of gasoline and the polyurethane urethane block.
-Typically the gasiline and polyurethane burners were in decay approximately 120~seconds after ignition.
+Typically the gasoline and polyurethane burners were in decay approximately 120~seconds after ignition.
 By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
@@
 The shape of the fire pattern to the wall was also different then the patterns generated on the flat wall.
-Much samller areas of the wall had the painted paper charred, penetrated, and burned.
+Much smaller areas of the wall had the painted paper charred, penetrated, and burned.
 For each of the fuels there was significantly more area where it was difficult to separate the charred areas from the surface deposits and discoloration.
-The sectons below include post test images of the fire patterns.
+The sections below include post test images of the fire patterns.
 The dimensions of the corner fire patterns are given in Table~\ref{tab:Fire_Pattern_Dimensions_Corners}.
@@
 In the corner burns there is an area in the corner where the paper is not burned off.
-From the flame sequence shown in Figure~\ref{GBNG34Sequence} it can be seen that the flame in the persitent flame region is close to the walls of the corner, but moving up into the intermittent region, the flame burns away from the walls, hence less energy is transferred to the walls and perhaps a bit more soot condenses out on the cooler walls.
+From the flame sequence shown in Figure~\ref{GBNG34Sequence} it can be seen that the flame in the persistent flame region is close to the walls of the corner, but moving up into the intermittent region, the flame burns away from the walls, hence less energy is transferred to the walls and perhaps a bit more soot condenses out on the cooler walls.
 
@@
 The patterns are darker than the patterns generated on the flat walls.
-Given that the air to the combustion zone was constrained it follows that the combustion may have been less efficient than the flat wall experiments whihch resulted in the sootier patterns.
+Given that the air to the combustion zone was constrained it follows that the combustion may have been less efficient than the flat wall experiments which resulted in the sootier patterns.
 The combustion zone for the gasoline fires positioned in the corner stretched from the top of the burner up to the ceiling of the compartment.
-Figure~\ref{GBGas10Sequence} shows the flame extension and similar to the natural gas burner fires shows how the flame in the intermittant zone appeared to move away from the corner.
+Figure~\ref{GBGas10Sequence} shows the flame extension and similar to the natural gas burner fires shows how the flame in the intermittent zone appeared to move away from the corner.
 
@@
 After the experiments the gypsum wallboard panels were removed from the compartment for documentation and measurement of the fire patterns.
-A comparsion on a fire pattern from each type of burner is shown in Figure~\ref{PT_Corners}.
+A comparison on a fire pattern from each type of burner is shown in Figure~\ref{PT_Corners}.
 Another image of the gasoline generated corner fire pattern, Figure~\ref{C_PTGASClose}, is included to show the reader how viewing a fire pattern at different angles enabled a better sense of the area of the fire damage.
@@
 They are intended to provide insight as opposed to a hard and fast numerical answer.
-As the experiments have shown so far there are many uncertainities which impact the results.
+As the experiments have shown so far there are many uncertainties which impact the results.
 
@@
 Neither value is high enough to cause the paper to char and ignite, there was only enough energy to cause discoloration.
-Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
+Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantitatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
 Indicating that a fire pattern has been burned into the wall and that was in fact true.
@@
 	\end{tabular}
-	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum boardwall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum boardwall experiments.
+	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum board wall experiments.
 Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
@@
 
-One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height when energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
+One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height where energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
 Estimates of the flame height were made by estimating the height where 0.95 to 0.99~$\%$ of the total energy had been released.
-Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
+The peak visible flame height range estimate was developed from the location where the flame exists only 10~\% of the time with the 95~\% certainty range.
+The Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
 The course and medium grids, RI=5 and R=10, were not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range.
@@
     (m)     							& (m) 				& (m) 				& (m)  			 \\ 
-    \hline 0.73 to 1.14         		& 1.02 to 1.27      & 1.07 to 1.27      & 1.28 to 1.42   \\
+    \hline 0.83 to 1.14         		& 1.02 to 1.27      & 1.07 to 1.27      & 1.28 to 1.42   \\
     \hline
@@
 These images also show how the pulsations and movements of the flame change positions relative to the fixed positions of the thermocouples and heat flux gauges.
+Figure~\ref{FDS_IWNG_SMV_comp} has a frontview and a side view Smokeview image from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.
+This simulation is comparable to the experiment used for Figure~\ref{FDS_IWNG_Flame_comp}.
+While the simultion does not demonstrate the amount of eddy generation or side to side movement from the front, the image from the side does show that FDS is simulating that the flame is moving toward the wall, although not to the extent that the actual flame did.
 
@@
   \caption[Images of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.]{FImages of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.
-The natural gas burner was poistioned 0.31~m from the instrumented gypsumboard wall.}
+The natural gas burner was positioned 0.31~m from the instrumented gypsumboard wall.}
   \label{FDS_IWNG_Flame_comp}
@@
 
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=2.3]{NG_80kW_GBWall_022_2D_RI=10_frontview}
+  \includegraphics[width=2.3]{NG_80kW_GBWall_022_2D_RI=10_sideview}   \\
+  \caption[Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.] {Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.}
+  \label{FDS_IWNG_SMV_comp}
+
 \subsection{Flame Height}
 
-A flame height range was calculated from each FDS simulation by multiplying the total energy released by 95 and 99~\%, and linking those values to the corresponding height form the *****.
+The flame height range was calculated using the HRRPUL from each of the FDS simulations at each position from the wall and for RI=5 and RI=10.
+The peak visible flame height range estimate was developed from the location where the flame exists only 10~\% of the time with the 95~\% certainty range.
+This information is presented in Table~\ref{tab:FDS_FH_IWNG} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
+The course and medium grids, RI=5 and R=10, were not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range at the position most remote from the wall.
 
@@
   \begin{tabular}{|c|c|c|c|} \hline 
-Distance from Wall 		&  Flame Height 			  	& RI=5       		& RI=10      		  \\
+Distance from Wall 		&  Peak Visible Flame Height 			  	& RI=5       		& RI=10      		  \\
     					&  Range          				&  (80~mm grid)  	&  (40~mm grid)  	  \\
     (m)					&  (m) 							& (m) 				& (m) 				  \\ 
-\hline    0.61			&  0.73 to 1.14         		& 0.88 to 1.02      & 1.01 to 1.24         \\
+\hline    0.61			&  0.0.83 to 1.14         		& 0.88 to 1.02      & 1.01 to 1.24         \\
 \hline    0.31			&		-						& 0.93 to 1.28		& 1.00 to 1.23		    \\
@@
 In these experiments, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
-The results from the instrumented gypsum wallboard experiments in Chapter 4, which respresented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
+The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
 The corresponding peak temperatures on the face of the gypsum wall board ranged from the    ~$^\circ$C.
-This demonstrates the insulatative capability of the gypsum wallboard.
+This demonstrates the insulation capability of the gypsum wallboard.
 Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.
 
-steep thermal gradiant
+steep thermal gradient
 
@@
 
-From Interflam  Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
+Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
 These calculated values were compared to the measured results from “real fuels” and provided reasonable results.
@@
 flow path
-inconsistant fire pattern near the right side of the sofa.  It appears that pattern was generated pre-flashover.  The pattern height is on the order of   calc HRR and FH for cushion.
+inconsistent fire pattern near the right side of the sofa.  It appears that pattern was generated pre-flashover.  The pattern height is on the order of   calculate HRR and FH for cushion.
 air equation
@@
 The main objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
-The first step was to exmaine the repeatability of different pre-flashover fires.
+The first step was to examine the repeatability of different pre-flashover fires.
 Three different fuels were used: natural gas, gasoline, and polyurethane foam.
@@
 This trend is the same as exhibited by the repeatability of the heat release rate measurements.
-Given that heat release rate is the source of the energy which is transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the unceratinty in pattern and any associated thermal measurements.
+Given that heat release rate is the source of the energy which is transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the uncertainty in pattern and any associated thermal measurements.
 

### 2017-03-16 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Built and incorporated new FDS images
Completed spell check through Ch 8

@@
 A mini DV camcorder with 0.7 mega-pixel resolution was used to capture the video.
-A firefighting type thermal imager with 0.08 megapixel resolution was used to capture infrared images in the 8 to 14 micron range.
+A firefighting type thermal imager with 0.08 mega-pixel resolution was used to capture infrared images in the 8 to 14 micron range.
 Each camera was positioned on a tripod with a distance of 4.5~m between the centerline of burner to camera lens.
@@
 For the purposes of this study, a modified version of the test apparatus was used.
-The radiant panel and the controls for the radiant panel remained in place, as documented in ASTM~E162.
+The radiant panel and the controls for the radiant panel remained in place, as documented in ASTM~E 162.
 However, the sample mounting system was changed.
@@
 At $R=0.23~m$ or less, the heat flux was high enough to indicate ignition in the experiments and that was the result.
-Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threhold heat flux.
+Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threshold heat flux.
 
@@
 	\end{tabular}
-	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum boardwall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum boardwall experiments.
+	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum board wall experiments.
 Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
@@
 For example, recommended values in the literature for the $chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
-The default radiative fraction of 0.35 is inline with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
+The default radiative fraction of 0.35 is in line with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
 Literature values for polyurethane foam were elusive.
@@
 The measured results are shown with 95~\% confidence limits.
-The Heskestad median flame height calculations are presented as a range based on the uncertainies of the average peak heat release rate of each fuel type.}
+The Heskestad median flame height calculations are presented as a range based on the uncertainties of the average peak heat release rate of each fuel type.}
  \label{tab:Comparing_Flame_Heights}
@@
  The comparison for the natural gas burner shows agreement between the measured median flame height and the average maximum fire pattern height.
-However, the range of calculated median flame height values is significantly different from the mesured values.
+However, the range of calculated median flame height values is significantly different from the measured values.
 Based on the computational flame height assessment, Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10~\% of the time.
 
-The comparsion of the median flame height values, the average maximum fire pattern height, and the calculated flame height range are all in agreement for the gasoline fueled pan fires.
+The comparison of the median flame height values, the average maximum fire pattern height, and the calculated flame height range are all in agreement for the gasoline fueled pan fires.
 This is significant because the 95~\% confidence limits for the fire pattern and the video based flame height are both less than 20~\%.
@@
 Overall the Heskestad equation provided reasonable estimates of the median flame height.
-The key to the successful use of any model regardles of the simplicity or complexity is using appropriate data.
+The key to the successful use of any model regardless of the simplicity or complexity is using appropriate data.
 
@@
 
-In this section, the natural gas burner will be modelled with a range of grid cell resolutions and radiative fraction values.
+In this section, the natural gas burner will be modeled with a range of grid cell resolutions and radiative fraction values.
 The results are compared against the source fire characterization data to determine which grid cell resolution and radiative fraction provided the best fire simulation for use in the simulations of the wall and compartment experiments.
@@
 Choosing the size of the grid when performing an analysis with FDS is critical in order to get the level of resolution needed to adequately simulate the required details within a simulation.
-In studies where large rooms or portions of buildings have been modeled grid cells on the order of 100~mm have been used and resulted in the successful simultation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Madrzykowski:2004,Vettori:2000, Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
+In studies where large rooms or portions of buildings have been modeled grid cells on the order of 100~mm have been used and resulted in the successful simulation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Madrzykowski:2004,Vettori:2000, Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
 
@@
 
-To examime the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were choosen to model the fire.
+To examine the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were chosen to model the fire.
 The resulting resolution index (RI) values were approximately 4.4, 8.8, and 17.5, respectively.
@@
 Each mesh was 2.4~m by 1.2~m and 0.6~m tall.
-The time domain for each model was chosen to be 300 seconds, which is similar to the burn time fior each of the fuels.
+The time domain for each model was chosen to be 300 seconds, which is similar to the burn time for each of the fuels.
 
@@
 These devices were positioned in locations similar to the locations used in the source fire experiments.
-The thermocouples were positioned in a vertical array, centered on the burner, beginning 0.1~m above the burner surface and spaced every 0.1~m upto 1.2~m above the burner surface.
-A total heat flux gauge was also modelled to provide data at the 0.95 m from the centerline of the burner and 0.5 m above the top of the burner.
+The thermocouples were positioned in a vertical array, centered on the burner, beginning 0.1~m above the burner surface and spaced every 0.1~m up to 1.2~m above the burner surface.
+A total heat flux gauge was also modeled to provide data at the 0.95 m from the centerline of the burner and 0.5 m above the top of the burner.
 In addition, FDS features devices that can not be physically implemented.
@@
 Adjusting the FDS corresponding predictions from the RI=10 and RI=20 models down to the 0.3~m position appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
-As FDS is a complex model, this explaination may be only one possibility.
-
-These simulation results are consistant with the comparisons made to the McCaffrey's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
+As FDS is a complex model, this explanation may be only one possibility.
+
+These simulation results are consistent with the comparisons made to the McCaffrey's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
 McCaffrey used a natural gas burner, 0.30~m square, which is similar in size to the burner used in this study.
@@
 The comparison between the McCaffrey plume correlation and the FDS simulations at RI values of 5, 10 and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
-Focusing on the data between the burner surface and the 1~m above the burner surface, FDS underpredicted the temperature near the surface of the burner and then overpredicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases respectively.
-Once the temperature comparisons were above the continuous and intermittant flame regions, the agreement between the cases and the correlation began to improve.
+Focusing on the data between the burner surface and the 1~m above the burner surface, FDS under predicted the temperature near the surface of the burner and then over predicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases respectively.
+Once the temperature comparisons were above the continuous and intermittent flame regions, the agreement between the cases and the correlation began to improve.
 Similar to the current study, increased RIs did not improve the simulation of the vertical centerline temperatures close to the burner.
@@
 The comparisons above used the predicted gas temperature from the model.
-Another comparison can be made examining the `thermocouple' results from FDS to see if the model of the thermocouple provides improved argeement with the temperatures measured via physical thermocouples.
+Another comparison can be made examining the `thermocouple' results from FDS to see if the model of the thermocouple provides improved agreement with the temperatures measured via physical thermocouples.
 This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
@@
 
-Another examinination of the plume temperature predictions was made to examine the impact of the range of radiative fractions on the FDS results.
+Another examination of the plume temperature predictions was made to examine the impact of the range of radiative fractions on the FDS results.
 The comparisons were made using the course grid, RI=5, and radiative fraction values of 0.20, 0.22, 0.25, and 0.30, as before.
@@
 
-The comparisons of the temperature, heat flux, and flame heights for this specific scenerio showed the best agreement with the 80~mm grid (RI=5) FDS simulations.
+The comparisons of the temperature, heat flux, and flame heights for this specific scenario showed the best agreement with the 80~mm grid (RI=5) FDS simulations.
 Even though the differences between the radiative fractions of 0.2 and 0.22 were small, for the remaining simulation cases, 0.22 will be used.
@@
 
-The next comparsions were made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
+The next comparisons were made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
 Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
@@
 The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500~$^\circ$C~\cite{Gross:1985}.
-While FDS can accomodate changes in thermoconductivy and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
+While FDS can accommodate changes in thermo-conductivity and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
 For the purposes of this study, the input values will remain constant throughout the course of the simulations.
@@
 
- The temperatures measured by thermocouples positioned along the vertical centerline of the natural gas burner will be compared with FDS generated temperures from two simulations, one with RI-5 and one with RI=10.
+ The temperatures measured by thermocouples positioned along the vertical centerline of the natural gas burner will be compared with FDS generated temperatures from two simulations, one with RI-5 and one with RI=10.
 The measurement points were at intervals of 0.2~m from 0.2~m to 2.2~m above the burner.
@@
 Figure~\ref{FDS_Wall_Temp_IWGB_comp} is analogous to Figure~\ref{FDS_Plume_IWGB_comp} except it compares the gypsum wallboard surface temperatures against the FDS simulated temperatures.
-So while the FDS values for the plume over predicted the temperatures, the FDS values for the wall surface temperatures are underpredicting.
+So while the FDS values for the plume over predicted the temperatures, the FDS values for the wall surface temperatures are under predicting.
 This is consistent with the flame and plume moving away from the plume centerline and toward the wall.
 The agreement between the FDS results and the measurements improves as the burner moves closer to the wall, however once the burner is against the wall, the degree of agreement between the FDS results and the measured temperatures decreased.
-At this position the FDS results are overpredicting the temperature.
+At this position the FDS results are over predicting the temperature.
 This differences at the wall are most distinct in the region where the flame impinged on the wall.
 The agreement improves in the plume area above the flames.
-In the comparisons with the source fire experiments, the FDS generated temperatures were underpredicting closer to the burner surface and the overpredicting in the flame region as a result of the `combustion' occuring at higher elevations above the burner.
-If a similar phenomena is occuring here, the wall maybe exaggerating the effect.
+In the comparisons with the source fire experiments, the FDS generated temperatures were under predicting closer to the burner surface and the over predicting in the flame region as a result of the `combustion' occurring at higher elevations above the burner.
+If a similar phenomena is occurring here, the wall maybe exaggerating the effect.
 
@@
 The comparisons between the measured heat flux and the FDS simulations are provided in Figure~\ref{FDS_HFCL_IWNG_comp} and Figure~\ref{FDS_HFEdge_IWNG_comp}.
-For the centerline gauges the trends between the heat flux measurements and the FDS values are similar to the trends with the temperatures and are consistant with the flame moving or leaning toward the wall.
+For the centerline gauges the trends between the heat flux measurements and the FDS values are similar to the trends with the temperatures and are consistent with the flame moving or leaning toward the wall.
 This resulted in higher heat flux measures relative to the FDS values at the three positions away from the wall.
@@
 
-The FDS values significantly underpredict the measured heat flux values along the right edge of the burner.
+The FDS values significantly under predict the measured heat flux values along the right edge of the burner.
 The best agreement occurs at the burner positions away from the wall.
-At this position, the fire pattern on the walls show that the lines of demarcation are occuring very close to the edge of the burner.
+At this position, the fire pattern on the walls show that the lines of demarcation are occurring very close to the edge of the burner.
 Again flame movement seems to to be the main cause of the difference that is accentuated by a measurement location that is very sensitive to heat flux and position.
@@
 Reviewing the videos from a natural gas burner instrumented gypsum wallboard experiment with the burner positioned at 0.310~m from the wall, we can see examples of the flame movement.
-In the top row of Figure~\ref{FDS_IWNG_Flame_comp} the three images exhibit points in time where the flame was moving toward the instrumented wall and away from the verticle array of thermocouples that are positioned above the center line of the burner.
+In the top row of Figure~\ref{FDS_IWNG_Flame_comp} the three images exhibit points in time where the flame was moving toward the instrumented wall and away from the vertical array of thermocouples that are positioned above the center line of the burner.
 The bottom row of images are from the same fire experiment looking at it from the front.
 These images also show how the pulsations and movements of the flame change positions relative to the fixed positions of the thermocouples and heat flux gauges.
-Figure~\ref{FDS_IWNG_SMV_comp} has a frontview and a side view Smokeview image from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.
+Figure~\ref{FDS_IWNG_SMV_comp} has a front view and a side view Smokeview image from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.
 This simulation is comparable to the experiment used for Figure~\ref{FDS_IWNG_Flame_comp}.
-While the simultion does not demonstrate the amount of eddy generation or side to side movement from the front, the image from the side does show that FDS is simulating that the flame is moving toward the wall, although not to the extent that the actual flame did.
+While the simulation does not demonstrate the amount of eddy generation or side to side movement from the front, the image from the side does show that FDS is simulating that the flame is moving toward the wall, although not to the extent that the actual flame did.
 
@@
   \includegraphics[width=1.5in]{../Figures/IWGB_NG_Front3}      \\
-  \caption[Images of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.]{FImages of flame movement which are consistant with the measurements and explain the differences between the measured and FDS values.
-The natural gas burner was positioned 0.31~m from the instrumented gypsumboard wall.}
+  \caption[Images of flame movement which are consistent with the measurements and explain the differences between the measured and FDS values.]{FImages of flame movement which are consistent with the measurements and explain the differences between the measured and FDS values.
+The natural gas burner was positioned 0.31~m from the instrumented gypsum board wall.}
   \label{FDS_IWNG_Flame_comp}
@@
   \centering
-  \includegraphics[width=2.3]{NG_80kW_GBWall_022_2D_RI=10_frontview}
-  \includegraphics[width=2.3]{NG_80kW_GBWall_022_2D_RI=10_sideview}   \\
+  \includegraphics[width=2.3in]{../Figures/FDS_NG_80kW_GBWall_frontview}
+  \includegraphics[width=2.3in]{../Figures/FDS_NG_80kW_GBWall_sideview}   \\
   \caption[Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.] {Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.}
   \label{FDS_IWNG_SMV_comp}
+\end{figure}
 

### 2017-03-19 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revised Ch 7 and 8

@@
 
-In this chapter the application of two empirical algebraic flame characterizations will be compared against the results from the experiments documented in previous chapters.
-Two different types of applications will be used.
-In the first case, relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target will be examined.
-The target in question is the painted gypsum wallboard.
-In the second case, the height of the thermal damage on the gypsum wallboard will be examined with the use of a flame height correlation.
+In this chapter the application of two different types of algorithms was be compared against the results from the experiments documented in previous chapters.
+In the first case, relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target were be examined.
+The target under examination was painted gypsum wallboard.
+In the second case, the height of the thermal damage on the gypsum wallboard was compared with the use of a flame height correlation.
+
 Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks as well as other application oriented documents~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999,NUREG_1805}.
-Values generated in the fire characterizations, instrumented bench scale experiments, and values from the literature will be utilized as input to predict or simulate real scale results using the algorithms.
-Then the numerical results will be compared with the full-scale experimental results.
+Values from the source fire characterizations, instrumented bench scale experiments, and from the literature were utilized as input to predict or simulate real scale results using the algorithms.
+Then the numerical results were compared with the full-scale experimental fire pattern results.
 Keep in mind that with these algorithms time is not a factor.
@@
 Babrauskas applied this concept in his paper, ``Will the Second Item Ignite''~\cite{Babrauskas:1981}.
-The idea being that if you knew the threshold heat flux that a material needed to be exposed to for the item to ignite, then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
+The data needed to use the method includes the HRR and radiant fraction from the source fire and the threshold ignition heat flux of the target material.
+The idea being that if you knew the threshold heat flux that a given material needed to achieve auto ignition, then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
 Radiation is assumed to be the only means of heat transfer.
@@
 
-The question is can we use this simple model to estimate the burner positions where the heat flux would be high enough to generate thermal damage on the painted gypsum board wall?
-From the source fire characterizations, the average peak heat release rates from the three burners can be input into the equation along with the distance, R, and the $\chi_r$, or the radiant fraction.
-R is measured from the vertical centerline of the burners so in addition to the distance between the edge of the burner and the wall, half of the burner width, 0.15~m must be added.
-A typical default value used for the radiant fraction is 0.35.
+The question is can this simple model be used to estimate the burner positions where the heat flux would be high enough to generate thermal damage on the painted gypsum board wall?
+The average peak heat release rates from the three burners, from the source fire characterizations, were input into the equation along with the distance, R, and the $\chi_r$, or the radiant fraction.
+R was measured from the vertical centerline of the burners.
+Therefore in addition to the distance between the edge of the burner and the wall, half of the burner width, 0.15~m was added.
+As a starting value for $\chi_r$, the typical default value of 0.35 was used.
 Table~\ref{tab:Point_Source_HFNGG} lists the input value of the average peak heat release rate of 80~kW for both the natural gas and gasoline burner fires along with a $\chi_r$ of 0.35, and the five burner positions that were used.
 
-The predictions provide good agreement with the natural gas results at distances greater than 1 burner width away.
+The predictions provided good agreement with the natural gas results at distances greater than 1 burner width away.
 Closer than one burner width array the predictions trend higher.
@@
 Based on the data from the cone calorimeter experiments conducted as part of this study, charring, penetration, and consumption would occur somewhere between 25 and 30~kW/m$^2$.
-Dillon provided a value of 26kW/m$^2$ as the minimum heat flux where ignition of the gypsum wallboard would occur~\cite{Dillon:1998}.
-So at $R=0.31~m$ conditions are on the edge of the threshold heat flux for ignition, both with the prediction and the measurement.
-Neither value is high enough to cause the paper to char and ignite, there was only enough energy to cause discoloration.
+Dillon provided a value of 26~kW/m$^2$ as the minimum heat flux where ignition of the gypsum wallboard would occur~\cite{Dillon:1998}.
+At $R=0.31~m$ the heat flux conditions were very close to the 26~kW/m$^2$ threshold heat flux for ignition, both with the prediction and the measurement.
+Neither value was high enough to cause the paper to char and ignite, there was only enough energy to cause some discoloration.
 Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantitatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
@@
 
-The predictions provided in Table~\ref{tab:Point_Source_HFNGG} are significantly lower than the measured peak heat flux values from the gasoline fueled burner experiments at every burner position.
-That said, the predictions indicate that at $R=0.31~m$  the heat flux is near the ignition threshold provided in the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
+The predictions provided in Table~\ref{tab:Point_Source_HFNGG} were significantly lower than the measured peak heat flux values from the gasoline fueled burner experiments at every burner position.
+That said, the predictions indicate that at $R=0.31~m$  the heat flux is near the ignition threshold provided from the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
 The single gasoline experiment at $R=0.31~m$ showed a peak heat flux of 57~kW/m$^2$.
-The exposure was brief at this peak due to the flame movement toward the wall.
+The exposure was brief at this peak value as is was caused by movement of the flame toward the wall.
 This makes the experimental values at the three closest locations to the wall difficult to compare with the point source model, and most models for that matter, since they cannot account for the flame being drawn toward the wall.
-An important observation is that the fire damage on the wall was limited to an uneven horseshoe shaped pattern within 100~mm above the top of the burner edge.
-This ignition was captured in Ch 4, Figure~\ref{IWGBGAS6_seq}.
-In other words, at $R=0.31~m$, there was an ignition of the fuel gases that were pyrolyzing from the painted gypsum board wall, but barely and in a very limited area relative to the flame shape near the surface.
-At the two closer positions the char, penetration, and consumption was evident and at these locations both the predictions and the measured heat fluxes are well above the threshold ignition heat flux.
+In this case, an important observation is that the fire damage on the wall was limited to an uneven horseshoe shaped pattern within 100~mm above the top of the burner edge.
+This ignition was documented in Ch 4, Figure~\ref{IWGBGAS6_seq}.
+In other words, at $R=0.31~m$, there was an ignition of the fuel gases that were pyrolyzing from the painted gypsum board wall,which resulted in a smaller fire area of fire damage relative to the flame shaped damaged when the burner was against the wall surface.
+At the two closer radii, 0.23 and 0.15~M, the char, penetration, and consumption were evident and at these locations both the predictions and the measured heat fluxes are well above the threshold ignition heat flux.
+Perhaps coincidental, but at each location where the predicted heat flux was similar to the threshold from the literature, ignition of the paper on the gypsum board occurred, even though the values did not provide reasonable agreement with the from the gasoline fire measurements.
 
@@
 	\hline
-		HRR (kW) &   $\chi_r$   & R (m)	 & Heat Flux (kW/m$^2$)     &  Nat. Gas (kW/m$^2$)      & Gasoline (kW/m$^2$) 	\\ \hline \hline
-		80    &   .35 		& 0.76 	     & 3.8 $\pm$ 0.30 (8~\%) 	&  4 $\pm$ 0.32 (8~\%) 	 	   & 6 $\pm$ 0.5 (8~\%)     \\
-		80    &   .35    	& 0.46	     & 10.6 $\pm$ 0.80 (8~\%) 	&  11 $\pm$ 0.88 (8~\%)  	   & 18 $\pm$ 1.4 (8~\%)    \\
-		80    &   .35 		& 0.31	     & 24.0 $\pm$ 1.9 (8~\%) 	&  23 $\pm$ 1.8 (8~\%)  	   & 57 $\pm$ 4.6 (8~\%)     \\
-        80    &   .35 		& 0.23	     & 43.0 $\pm$ 3.4 (8~\%) 	&  NA 					  	   & 60 $\pm$ 4.8 (8~\%)     \\
-        80    &   .35 		& 0.15	     & 95.0 $\pm$ 7.6 (8~\%) 	&  55 $\pm$ 4.4 (8~\%)  	   & 61 $\pm$ 4.9 (8~\%)     \\
+		HRR (kW) &   $\chi_r$   & R (m)	 & Heat Flux (kW/m$^2$)     &  Nat. Gas (kW/m$^2$)      & Gasoline (kW/m$^2$) 	\\ \hline 
+		80    &   .35 		& 0.76 	     & 3.9 $\pm$ 0.4 (11~\%) 	&  4 $\pm$ 0.32 (8~\%) 	 	   & 6 $\pm$ 0.5 (8~\%)     \\
+		80    &   .35    	& 0.46	     & 10.5 $\pm$ 1.2 (11~\%) 	&  11 $\pm$ 0.88 (8~\%)  	   & 18 $\pm$ 1.4 (8~\%)    \\
+		80    &   .35 		& 0.31	     & 23.0 $\pm$ 2.6 (11~\%) 	&  23 $\pm$ 1.8 (8~\%)  	   & 57 $\pm$ 4.6 (8~\%)     \\
+        80    &   .35 		& 0.23	     & 42.0 $\pm$ 4.6 (11~\%) 	&  NA 					  	   & 60 $\pm$ 4.8 (8~\%)     \\
+        80    &   .35 		& 0.15	     & 90.0 $\pm$ 10.9 (11~\%) 	&  55 $\pm$ 4.4 (8~\%)  	   & 61 $\pm$ 4.9 (8~\%)     \\
 	\hline
@@
 	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum board wall experiments.
-Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
+Values presented with 95~\% confidence limits based on the estimated uncertainty of HRR and heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
 	\label{tab:Point_Source_HFNGG}
@@
 No thermal damage.
-At $R=0.23~m$ or less, the heat flux was high enough to indicate ignition in the experiments and that was the result.
+At $R=0.23~m$ the calculated heat flux was close to but less than the threshold ignition heat flux, however in the experiments the paper ignited at this position.
 Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threshold heat flux.
@@
 	\hline
-		HRR (kW) &   $\chi_r$   & R (m)	     & Heat Flux (kW/m$^2$)     &  Polyurethane (kW/m$^2$)    	\\ \hline \hline
-		45       &   .35 		& 0.76 	     & 2.1 $\pm$ 0.17 (8~\%) 	&  3.5 $\pm$ 0.28 (8~\%) 	   	 \\
-		45       &   .35    	& 0.46	     & 6.0 $\pm$ 0.48 (8~\%) 	&  12.3 $\pm$ 0.98 (8~\%)  	     \\
-		45       &   .35 		& 0.31	     & 13.5 $\pm$ 1.1 (8~\%) 	&  25 $\pm$ 2.0 (8~\%)   	      \\
-        45       &   .35 		& 0.23	     & 24.1 $\pm$ 1.9 (8~\%) 	&  36 $\pm$ 2.9 (8~\%)		      \\
-        45       &   .35 		& 0.15	     & 53.5 $\pm$ 4.3 (8~\%) 	&  59 $\pm$ 4.7 (8~\%)   	       \\
+		HRR (kW) &   $\chi_r$   & R (m)	     & Heat Flux (kW/m$^2$)     &  Polyurethane (kW/m$^2$)    	\\ \hline 
+		45       &   .35 		& 0.76 	     & 2.2 $\pm$ 0.24 (8~\%) 	&  3.5 $\pm$ 0.28 (8~\%) 	   	 \\
+		45       &   .35    	& 0.46	     & 6.0 $\pm$ 0.65 (8~\%) 	&  12.3 $\pm$ 0.98 (8~\%)  	     \\
+		45       &   .35 		& 0.31	     & 13.1 $\pm$ 1.4 (8~\%) 	&  25 $\pm$ 2.0 (8~\%)   	      \\
+        45       &   .35 		& 0.23	     & 23.7 $\pm$ 2.6 (8~\%) 	&  36 $\pm$ 2.9 (8~\%)		      \\
+        45       &   .35 		& 0.15	     & 55.7 $\pm$ 6.1 (8~\%) 	&  59 $\pm$ 4.7 (8~\%)   	       \\
 	\hline
@@
 	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum board wall experiments.
-Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Pitts:2006}.}
+Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
 	\label{tab:Point_Source_HFPUF}
@@
 This was an interesting exercise but it was not very definitive.
-If we were to attempt to improve the predictions by using radiative fractions that are known to be representative of the fuels, the predictions in some cases might get worse.
+One means of potentially improving the predictions would be to use radiative fractions that are known to be representative of the fuels.
 For example, recommended values in the literature for the $chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
 The default radiative fraction of 0.35 is in line with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
-Literature values for polyurethane foam were elusive.
-
-Another means to assess the point source model was to examine the heat flux data measured at 2~m away from the vertical centerline of the burners during some of the source fire characterization experiments.
-If we rearrange the point source equation, to solve for $\chi_r$ by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2~m away the resulting value for $\chi_r$ are 0.26, 0.46 and 0.33 for the natural gas, gasoline and polyurethane burners respectively.
+Literature values for the radiative fraction of polyurethane foam were elusive.
+
+Another means to assess the point source model was to examine the heat flux data measured at 2.15~m away from the vertical centerline of the burners during some of the source fire characterization experiments.
+By rearranging the point source equation, to solve for $\chi_r$ and by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2.15~m away from the burner centerline, the resulting values for $\chi_r$ were 0.25, 0.47 and 0.33 for the natural gas, gasoline and polyurethane burners respectively.
 This distance should be more appropriate for the use of the point source model but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
-It appears that more research is needed on radiative fractions of fire sizes and realistic fuels that might be found in a residential setting.
+
+The radiant fractions determined from the measurements were applied at the two most distance locations from the wall.
+At these locations it was clear that only radiative heat transfer from the fires was the only means of heat transfer.
+At the closer the locations, based on the magnitude of the heat flux relative to the HRR, it appeared that convective heat transfer from the flame was playing a role.
+Again this is more consistent with the use guidelines of the algorithm.
+The comparison between the averaged peak measured heat flux and the calculated heat flux is presented in Table~\ref{tab:Point_Source_ModChir}
+
+\begin{table}
+	\centering
+	\footnotesize
+	\begin{tabular}{|c|c|c|c|c|c|}
+	\hline
+		Fuel 		& HRR  &   $\chi_r$   & R)	     & Calculated Heat Flux      & Measured Heat Flux      \\     
+					& (kW) &  			  & (m)		&  (kW/m$^2$)				&   (kW/m$^2$)                        \\ \hline 
+		Nat. Gas 	& 80       &   .25 	& 0.76 	     & 2.8 $\pm$ 0.30 (11~\%) 				&  4 $\pm$ 0.32 (8~\%) 	   	 \\
+		Nat. Gas 	& 80       &   .25  & 0.46	     & 7.5 $\pm$ 0.83 (11~\%) 				&  11 $\pm$ 0.88 (8~\%)  	     \\
+		Gasoline 	& 80       &   .47 	& 0.76	     & 5.2 $\pm$ 0.57 (11~\%) 				&  6 $\pm$ 0.5 (8~\%)   	      \\
+        Gasoline 	& 80       &   .47 	& 0.46	     & 14.1 $\pm$ 1.6 (11~\%) 				&  18 $\pm$ 1.4 (8~\%)		      \\
+       Polyurethane & 45       &   .33 	& 0.76	     & 2.1 $\pm$ 0.23 (11~\%) 				&  3.5 $\pm$ 0.28 (8~\%)   	       \\
+       Polyurethane & 45       &   .33 	& 0.46	     & 5.6 $\pm$ 0.62 (11~\%) 				& 12.3 $\pm$ 0.98 (8~\%)   	       \\
+	\hline
+	\end{tabular}
+	\caption[Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments.
+Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
+	\label{tab:Point_Source_ModChir}
+\end{table}
+
+The calculated values in Table~\ref{tab:Point_Source_ModChir} under predict the measured values.
+The $\chi_r$ values determined from the source fire measurements improved the agreement between the calculated and measured heat flux values for gasoline, even though the determined values of the radiative fraction for natural gas and gasoline appear to be on the high side.
+However since the determined values of $\chi_r$ for natural gas and polyurethane were less that the default value of 0.35, the agreement between the calculated and measured values decreased.
+
+The physics of the algorithm are sound, the challenge for the end user is determining the appropriate input values and making sure to use the algorithm within the appropriate distance range.
+More information or research is needed on the radiative fractions of various fuels.
+For example the majority of natural gas is composed of methane.
+However natural gas may also contain small amounts of ethane, propane, hexane, butane, and pentane.
+Some of these gases have higher radiative fractions than methane.
+In one widely used text, a table listing radiative energy fraction values for burner diameters larger than 0.5~m, lists butane in the 20 to 40 $\%$ range and hexane in the 40 to 60 $\%$ range ~\cite{Quintiere:1997}.
+So it is possible that the radiative fraction for natural gas could be higher that the radiative fraction associated with methane.
+The radiative fraction value in the literature for gasoline is 0.45~\cite{Quintiere:1997, IAAI:2017}.
+This is in line with the determined value.
+
+Based on the information here, it seems that it would be difficult to use the point source method for determining the ignition of a target in a residential room and contents fire scenario.
+In order to generate a heat flux greater than 20 kW/m$^2$, at a distance of 0.76~m, with a radiative fraction of 35, the HRR would have to be about 420 kW.
+The fire investigation community would be well served to have additional research to examine the use of algorithms such as the point source method with realistic fuels that might be currently found in a residential setting.
 
@@
 
-The desire to use flame height correlations is based on the thought that the median flame height will correlate to the height of the associated fire pattern.
-With the heat release rate data that we have from these experiments, comparisons will be made with the one of the more widely used empirical algorithms, known as the Heskestad flame height correlation.
+The desire to use flame height correlations was based on the thought that the median flame height would correlate to the height of the associated fire pattern.
+With the heat release rate data that we have from these experiments, comparisons were made with the one of the more widely used empirical algorithms, known as the Heskestad flame height correlation.
 
@@
 Appropriate fuels would include liquid pool fires and other horizontal surface fires~\cite{Heskestad:SFPE,Beyler:1986}.
-The inputs required to use the model are the heat release rate and the diameter of the fire or the burner.
+The inputs required to use the model are the heat release rate and the diameter of the base of the fire or the burner.
 
@@
 
-Once again the average peak heat release rates from Ch 2 were be used.
-The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80 kW.
-The polyurethane fueled burner had an average peak heat release rate of 45 kW.
+Once again the average peak heat release rates from Chapter 2 were be used.
+The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80~ kW.
+The polyurethane fueled burner had an average peak heat release rate of 45~kW.
 Calculating the median flame heights with the average peak heat release rates measured from the three fuels yielded 1.0~m, 1.0~m, and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
@@
 Method          &   \multicolumn{3}{|c|}{Flame Heights (m)} \\ \cline{2-4}
-                &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
+                &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline 
 Photographic    &       0.70 $\pm$ 0.23 (33~\%)   &	0.84 $\pm$ 0.28 (33~\%) 	& 0.46 $\pm$ 0.23 (50~\%)   \\
@@
 
-The comparison of the median flame height values, the average maximum fire pattern height, and the calculated flame height range are all in agreement for the gasoline fueled pan fires.
+For the gasoline fueled fires, the comparison of the median flame height, the average maximum fire pattern height, and the calculated flame height range values are all in agreement.
 This is significant because the 95~\% confidence limits for the fire pattern and the video based flame height are both less than 20~\%.
@@
 The measured and calculated values for the polyurethane fueled burner fires are also in agreement.
-The agreement in this case is a result of of the 95~\% confidence limits of the average maximum fire pattern heights being 50~\%.
+However the agreement in this case is largely the result of the broad 95~\% confidence limits of the range of the average peak heat release rate of the polyurethane foam.
+The burning variation of polyurethane foam resulting in the wide range of flame heights and patterns with 95~\% confidence limits of $\pm$ 50~\%.
 
 Overall the Heskestad equation provided reasonable estimates of the median flame height.
-The key to the successful use of any model regardless of the simplicity or complexity is using appropriate data.
+The key to the successful use of any model regardless of the simplicity or complexity is using the appropriate data and understanding the basis of the algorithm, in order to assess any underlying assumptions.
 
@@
 Even though the differences between the radiative fractions of 0.2 and 0.22 were small, for the remaining simulation cases, 0.22 will be used.
-While the best agreement for the fire was demonstrated with the RI= 5 grid, the RI=10 grid will also be used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models get additional obstructions and surfaces.
+While the best agreement for the fire was demonstrated with the RI=5 grid, the RI=10 grid will also be used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models get additional obstructions and surfaces.
 
@@
 
+The program Smokeview uses the numerical results of FDS to create scientific visualizations.
+In this section, comparisons were made between Smokeview generated images and photographs of fire patterns.
+The criteria for the `charred' area of the gypsum wall board was a threshold temperature of 360~$^\circ$C.
+This value was chosen based on the ignition temperature data collected as part of this study and documented in Chapter~5.
+
+Keep in mind that this ignition temperature is lower, by more than 150~$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
+It is possible that the paint on the surface of the samples used in this study, had an impact or that during the decades between the studies the properties of the material have been changed in someway.
+Thermal properties data on the gypsum board paper used in the study was not available from the manufacturer.
+
+The comparisons were made for the natural gas burner fire positioned against a painted gypsum board wall.
+Figure~\ref{FDS_FirePattern_comp} displays two Smokeview images.
+In the image on the left the isothermal areas of the wall shown with a temperature range of 20~$^\circ$C to greater than 520~$^\circ$C.
+The Smokeview image on the right has the `char' feature applied with the threshold temperature of 360~$^\circ$C to coincide with cone calorimeter ignition temperature data.
+The upper edge of the char area is approximately 1~m above the burner.
+The upper edge of the 520~$^\circ$C area in the left image was approximately 0.8~m above the burner.
+This images were generated with the RI=10 model which has grid cells that were 0.4~m in size.
+The FDS images are compared with three photographs of fire patterns from the compartment fire pattern experiments documented in Chapter~6.
+The three images from left to right exhibit a range of fire pattern heights from approximately 0.7 to 0.8~m.
+The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95~\% certainty range of $pm$~0.12~m.
+The simulated fire pattern is taller than the actual patterns.
+However is the upper ignition temperature was used the height values between the actual and the simulated would have been similar.
+The RI=10 simulation was used as a means to optimize the graphical resolution, even though the temperature range of the flames were shifted up relative to the RI=5 case.
+
 \begin{figure}[h]
@@
   \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
 The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
-This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
+This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
   \label{FDS_FirePattern_comp}
 \end{figure}
+
+The next set of comparison were made with the natural gas burner fire positioned in the corner against two painted gypsum board walls.
+From the perspective of the impact of the corner on the visual fire behavior, the RI=20 simulation captures the extension of the combustion zone.
+The similarity of the images in Figure~\ref{FDS_Corner_Sequence} and those in Figure~\ref{GBNG34Sequence} is very good.
 
@@
 The time interval between images is 0.3 of second.}
-	\label{GBNG34Sequence}
-\end{figure}
+	\label{FDS_Corner_Sequence}
+\end{figure}
+The next comparison was between the Smokeview corner fire pattern images and photographs of corner fire patterns.
+The images and photographs are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
+The isotherms in the Smokeview images range from 20~$^\circ$C to greater than 360~$^\circ$C.
+The `char' area with the threshold value of 360~$^\circ$C is shown in the Smokeview image on the right.
+The upper edge of the char image was approximately 1.5~m above the burner.
+As noted in Chapter 6, even though the combustion zone extended toward the ceiling, the flames appeared to move away from the walls as the flames moved away from the burner.
+The natural gas generated corner fire patterns were similar in height to the natural gas burner generated wall patterns with an average height of 0.74~m.
+The FDS value is approximately twice that.
+Of course changing the ignition temperature to 520~$^\circ$C would bring the simulated char height close to the measured values.
 
@@
   \includegraphics[width=.8\columnwidth]{../Figures/NGCorner_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
-The image with the three replicate fire patterns has a red line indicating a position approximately 1.6~m above the burner.
-This height corresponds with the height of the top of the 350~$^\circ$C mark in the FDS image.}
-  \label{FDS_FirePattern_comp}
-\end{figure}
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
+The image with the three replicate fire patterns has a red line indicating a position approximately 1.5~m above the burner.
+This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
+  \label{FDS_FirePattern_Corner_comp}
+\end{figure}
+
+Another difference that was not factored into the model, was the potential change in heat transfer between the corner and the wall experiments.
+For the wall experiments the burner was centered on a void space between the vertical wood studs which formed the frame work of the compartment.
+In the corner,the wood stud walls are attached and wood stud was positioned so that the corner edge of each gypsum wallboard panel could be attached to it.
+As a result there was an additional heat sink extending approximately 35~mm out from the corner om each side and extending the height of the wall.
+
+As noted in the previous chapter the successful use of any model regardless is using the appropriate data and understanding the basis of the model and any subroutines.
+FDS is a very complex set of equations and subroutines.
+The model authors have done an incredible job providing digital documentation that is searchable and understandable.
+The challenge in these case is the input data.
+Our understanding of the physical portion of these comparisons may not be as good as the understanding of the theory.
+Hence more research is needed especially of the ignition criteria for gypsum board.
+
+The observations of the flame movement provided some insight into the differences between the model results and the measurements during the wall experiments and the modeled combustion issues near the burner seem to address the temperature differences in the combustion zone just above the burner.
 
 \chapter{Discussion}
+
+The scope of this study has included several series of experiments that ranged in size from bench scale tests with 100~mm sized samples to full scale compartment experiments with samples 2.4~m tall.
+The key objective was to address the National Academy of Sciences call for research to address `the natural variability of burn patterns'.
+This study examined the repeatability of several similar small fire sources and the pre-flashover fire patterns that were generated by those fires.
+
+In addition a few popular numerical models were to use simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale, and the full-scale fire experiments conducted in this study.
 

### 2017-03-19 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added front piece refs and working on discussion

@@
 \clearpage
-Abbreviations
-\begin{tabbing}
-\hspace{1.5in} \= \\
-EMS \> Emergency Medical Services \\
-FDS \> Fire Dynamics Simulator \\
-HGL \> Hot Gas Layer \\
-HRR \> Heat Release Rate \\
-HRRPUA \> Heat Release Rate per Unit Area \\
-NFPA \> National Fire Protection Association  \\
-NIST \> National Institute of Standards and Technology \\
-\end{tabbing}
 
@@
 \end{tabbing}
+
+\textbf{Material covered in Chapters 2 and 6 has been previously published in:}
+
+Madrzykowski, D. and Fleischmann, C., Fire Pattern Repeatability: A Study in Uncertainty, Journal of
+Testing and Evaluation, ASTM International, W. Conshohocken, PA.,Vol 40, No. 1, January 2012, pp 1-11.
+
+Madrzykowski, D.
+and Fleischmann, C., "Fire Pattern Repeatability: A Laboratory Study on Gypsum Wallboard." In Proceedings ISFI 2010: International Symposium on Fire Investigation Science and Technology, Hyattsville, MD, USA.
+Sarasota, FL, USA 2010.
+pp 381-392.
+
+\textbf{Material covered in Chapters 2 and 7 has been previously published in:}
+
+Madrzykowski, D.
+and Fleischmann, C., "Flame Heights and Heat Transfer from Gaseous, Liquid and Solid Fuels for Burn Pattern Repeatability Research." In INTERFLAM 2010: 12th International Conference on Fire Science and Engineering, Nottingham, UK.
+London, UK, 2010.
+pp 1930-1942.
 
@@
 
-In addition a few popular numerical models were to use simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale, and the full-scale fire experiments conducted in this study.
+In addition a few popular numerical models were used to simulate the fires or the effects of the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale experiments, and the full-scale fire experiments conducted as part of this study.
+The results of the calculations were then compared to the measured values to examine the level of agreement.
+
+In Chapters 2 through 8 results from specific test series or calculations were presented.
+Typically there was some discussion specific to the experiments or calculations being addressed in each chapter.
+In this chapter the discussion will be more inclusive in examining the key outcomes and the remaining gaps.
+
+\section{Repeatability of Pre-Flashover Fire Patterns}
+
+As noted in the Introduction, gypsum wall board was chosen as a target for the fire patterns due to its common usage in construction and the frequency of fires that occur in buildings where gypsum wall board may be used as an interior finish.
+The size of the fires were chosen such that the fire damaged area (paper consumed) of the pattern was contained to less than 2.4~m.
 
@@
 
+`Essentially, all models are wrong, but some are useful.'   Quote by George E.P. Box  statistician
+
 \section{The Fire Investigators' Challenge}
@@
 
+Uncertainty and Modeling
+
+NFPA 921, Guide for Fire and Explosion Investigations considers mathematical modeling techniques as a means to provide the fire investigator with tools for testing hypotheses regarding the origin and cause of the fire and the cause of the resulting damage to property or injury to people.
+NFPA 921 cautions that `mathematical modeling, whether simplified hand calculations or computer fire models, has inherent limitations and assumptions that should be considered.
+Models generally rely upon empirical data and are validated via comparison with other empirical data.
+Care must be taken to assure that the model is being used with due regard for limitations, assumptions, and validation'~\cite{NFPA:921}.
+In these experiments, the natural gas burner and the gasoline pool fire were the type of fire source that the models were developed with or have been validated against.
+Basically the burners provided fire sources that were very repeatable and could generally be defined by the two dimensional planar surface where the fuel is emitted.
+
+Fire investigators, however, examine fire scenes where the first item ignited may have involved a piece of furniture, an appliance, or even a car.
+These items are three dimensional and the fuel could be emitted from multiple surfaces at any given time in the fire event.
+Further thermoplastics are commonly used in the construction of these items, with furniture being a prevalent item.
+As the thermoplastic is heated it melts, flows, drips, and burns.
+As a result the flame geometry generated by a piece of furniture may not be representative of the flame geometry characterized by the studies using gas burners and pool fires.
+In this study even using a block of polyurethane foam with a simple geometry led to increased uncertainty.
+
 \chapter{Conclusions}
@@
 The main objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
-The first step was to examine the repeatability of different pre-flashover fires.
+The first step was to examine the repeatability of different fire sources.
 Three different fuels were used: natural gas, gasoline, and polyurethane foam.
@@
 While the variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11~\%, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
-The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
+The fire pattern heights generated on painted gypsum wall board by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
 The patterns generated by the polyurethane foam fueled fire, had more variability than the natural gas and the gasoline fire patterns.
@@
 The comparison of the fire pattern heights and the mean flame height demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
-This trend is the same as exhibited by the repeatability of the heat release rate measurements.
-Given that heat release rate is the source of the energy which is transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the uncertainty in pattern and any associated thermal measurements.
+This trend was the same as exhibited by the repeatability of the heat release rate measurements.
+Given that heat release rate is the source of the energy which was transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the uncertainty in pattern and any associated thermal measurements.
 

### 2017-03-22 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Drafted abstract

@@
 This paper highlights the many uncertainties involved in what appear to be simple fire experiments.
-Uncertainties related to the composition of the fuels, measurement methods, and analysis techniques are a few of the areas considered.
+Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
 The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
@@
 However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
-The patterns generated by the polyurethane foam fire, had more variability than the natural gas and the gasoline fire patterns.
-This is likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
+
+The variability in the heat release rate of the fires resulted in higher levels of variability in the resulting fire patterns.
 The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
@@
 
-This trend is the same as exhibited by the repeatability of the heat release rate measurements and the flame height measurements.   *****Computational results here ****
+A range of methods used to simulate characteristics of fires were applied using data from the source fire experiments as input.
+The algebra based predictions for heat flux to a target under predicted the measured values.
+The gasoline fueled fires best agreement of 22~\% or less for the heat flux predictions.
+The polyurethane foam results exhibited the worst agreement with difference of at least 40~\% between the measured and calculated values.
+Improved understanding of the radiative fraction from different fuels would improve the capability of the predictions.
+
+The best agreement between measured flame height, the measured height of the fire pattern, and flame height predictions occurred with the gasoline fueled fires.
+Given the overlap of the expanded uncertainty and predicted range of values, the measured and predicted heights would be considered similar.
+The gasoline fueled fires released the highest amount of energy and has a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
+
+The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as example with poor agreement.
+The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface, as the distance between the burner surface increased the predicted values tended to converge with the measured values.
+The wall located adjacent to the burn had a significant impact on the flow field in and around the flame and plume region.
+The horizontal flame movements observed during the experiments was not simulated to the same degree by the model.
+Given the areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
+
+The models are useful tools for gaining insight into fire behavior but in many cases many require specific experimental data for input or for validation.
+Further research is needed to understand the appropriate resolution for implementing the results based on fuel type, fuel geometry, and ventilation.
+There is a critical need to extend this research to better understand the capabilities and limitations of predictive methods using fuels and scenarios that fire investigators are likely to encounter.
 

### 2017-03-22 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Revised Ch 8.1 through 8.5 per CF comments

@@
 
-The goal of this chapter is to utilize an analytical tool to predict or simulate the results from some of the key experiments conducted in this study.
+The goal of this chapter is to utilize a numerical tool to predict or simulate the results from some of the key experiments conducted in this study.
 Computational fluid dynamics (CFD) models are not as widely used by fire investigators as the algebraic tools are.
@@
  The FDS User Guide provides a method to determine how well a flow field will be resolved by using the non-dimensional expression ${D^*}/{\delta x}$, where $D^*$ is a characteristic fire diameter and $\delta x$ is the nominal size of a mesh or grid cell.
-This value has been referred to as the plume resolution index.
+This value has been referred to as the plume resolution index~(RI).
 Given that the fire plume region is the focus of this study, it is important to understand how changes in plume mesh resolution impact the results.
@@
 The comparisons above used the predicted gas temperature from the model.
-Another comparison can be made examining the `thermocouple' results from FDS to see if the model of the thermocouple provides improved agreement with the temperatures measured via physical thermocouples.
+Another comparison can be made examining the `THERMOCOUPLE' results from FDS to see if the model of the thermocouple provides improved agreement with the temperatures measured via physical thermocouples.
 This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
 Not surprisingly, the sub model of the thermocouple device shifted the FDS values slightly.
-At temperatures greater than 700~$^\circ$C, the `thermocouple' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
-At temperatures less than 700~$^\circ$C, the `thermocouple' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
+At temperatures greater than 700~$^\circ$C, the `THERMOCOUPLE' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
+At temperatures less than 700~$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
 The best agreement along the vertical array of temperatures was provided by the RI=5 model.
@@
 	\includegraphics[width=5in]{../Figures/FHNG01_RI_TC} \\
-	\caption[Comparison of vertical centerline `thermocouple' temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline `thermocouple' temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
+	\caption[Comparison of vertical centerline `THERMOCOUPLE' temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline `THERMOCOUPLE' temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
 	\label{FHNG01_RI_TC}
@@
 Reviewing the heat flux data documented in Chapter 2 from both the 0.95~m  and the 2.0~m from the vertical centerline of the burner positions provided average steady state heat flux values of approximately 2.0~kW/m$^2$ and 0.43~kW/m$^2$, respectively.
-Applying the point source method, discussed in Chapter 7, conservative values for the radiative fraction were determined to be in the range of 0.25 to 0.28.
+Applying the point source method, discussed in Chapter 7, values for the radiative fraction were determined to be in the range of 0.25 to 0.28.
 Values found in the literature for natural gas range from 0.15 to 0.25~\cite{Modak:1977,Hostikka:3}.
@@
 The course grid, RI=5, was used for the FDS models.
-The comparison of the results is shown in~\ref{FHNG01_HF_RI5}.
+The comparison of the results is shown in Figure~\ref{FHNG01_HF_RI5}.
 The radiative fraction of 0.22 provided the best agreement with the measurement.
@@
 One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height where energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
-Estimates of the flame height were made by estimating the height where 0.95 to 0.99~$\%$ of the total energy had been released.
-The peak visible flame height range estimate was developed from the location where the flame exists only 10~\% of the time with the 95~\% certainty range.
+Estimates of the flame height were made by estimating the height where 95 to 99~$\%$ of the total energy had been released.
+To have a value, based on a measurement, for comparison to the HRRPUL the peak visible flame height range estimate was developed.
+The peak visible flame height ranged from the location where the flame existed only 10~\% of the time with the 95~\% certainty range.
 The Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
@@
 The increased resolution leads to a flame structure that provides a better match to the look of the actual flame.
-However in this scenario, the increased resolution within the flow field has not resulted in improved numerical agreement.
+However in this scenario, the increased resolution within the flow field has not resulted in improved numerical agreement with the measured values.
 
@@
 The wall was modeled with material properties for gypsum wallboard that were documented in Chapter 4.
-The input properties were: thermal conductivity (0.28 W/m K), specific heat (1.00 kJ/kg K) and density (807 kg/m$^3$).
+The input properties were: thermal conductivity (0.15 W/m K), specific heat (1.00 kJ/kg K) and density (807 kg/m$^3$).
 In addition FDS includes a default value of 0.9 for emissivity, this value should be representative of the painted surface of the gypsum wallboard.
@@
 As before, the FDS simulations included devices which are used to simulate thermocouples and total heat flux gauges.
-These devices were positioned in locations similar to the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
+These devices were positioned in the same locations as the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
 In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simulated by FDS.
@@
 
- There seem to be a couple of items that stick out from the graphs.
+ There seem to be a couple of noticeable trends from the graphs.
 First, there appears to be a separation of the temperature data into three distinct sections.
@@
 
-Reviewing the videos from a natural gas burner instrumented gypsum wallboard experiment with the burner positioned at 0.310~m from the wall, we can see examples of the flame movement.
+Examples of the flame movement were found by reviewing the videos from a natural gas burner, instrumented gypsum wallboard experiment with the burner positioned at 0.310~m from the wall.
+Figure~\ref{FDS_IWNG_Flame_comp} shows images from two different locations, from the front of the burner and from the right side of the burner.
 In the top row of Figure~\ref{FDS_IWNG_Flame_comp} the three images exhibit points in time where the flame was moving toward the instrumented wall and away from the vertical array of thermocouples that are positioned above the center line of the burner.
@@
 The peak visible flame height range estimate was developed from the location where the flame exists only 10~\% of the time with the 95~\% certainty range.
-This information is presented in Table~\ref{tab:FDS_FH_IWNG} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
+This information is presented in Table~\ref{tab:FDS_FH_IWNG} displays estimated values from the models using two of the RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
 The course and medium grids, RI=5 and R=10, were not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range at the position most remote from the wall.
@@
 The upper edge of the 520~$^\circ$C area in the left image was approximately 0.8~m above the burner.
-This images were generated with the RI=10 model which has grid cells that were 0.4~m in size.
+This images were generated with the RI=10 model which has grid cells that were 0.04~m in size.
 The FDS images are compared with three photographs of fire patterns from the compartment fire pattern experiments documented in Chapter~6.
 The three images from left to right exhibit a range of fire pattern heights from approximately 0.7 to 0.8~m.
-The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95~\% certainty range of $pm$~0.12~m.
+The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95~\% certainty range of $\pm$~0.12~m.
 The simulated fire pattern is taller than the actual patterns.
-However is the upper ignition temperature was used the height values between the actual and the simulated would have been similar.
+However if the upper ignition temperature was used the height values between the actual and the simulated would have been similar.
 The RI=10 simulation was used as a means to optimize the graphical resolution, even though the temperature range of the flames were shifted up relative to the RI=5 case.

### 2017-03-22 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
revised abstract     working on conclusion

@@
 \end{enumerate}
-This paper highlights the many uncertainties involved in what appear to be simple fire experiments.
+This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.
 Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
@@
 Each fuel had a similar top surface area.
-The heat release rate data showed that the variability was greater for more complex fuels.
+The heat release rate data showed that the variability between replicates was greater for more complex fuels.
 The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%.
@@
 
-The variability in the heat release rate of the fires resulted in higher levels of variability in the resulting fire patterns.
+The variability in the heat release rate of the fires resulted in higher levels of variability of the replicate fire patterns.
 The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
@@
 
-The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as example with poor agreement.
+The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
 The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface, as the distance between the burner surface increased the predicted values tended to converge with the measured values.
@@
 The models are useful tools for gaining insight into fire behavior but in many cases many require specific experimental data for input or for validation.
+The availability   of well characterized input data is limited and data for newer materials is unavailable.
+Additional research is needed for modeling data development protocols.
+Improved data repositories are also needed.
 Further research is needed to understand the appropriate resolution for implementing the results based on fuel type, fuel geometry, and ventilation.
-There is a critical need to extend this research to better understand the capabilities and limitations of predictive methods using fuels and scenarios that fire investigators are likely to encounter.
-
+Most importantly, there is a critical need to extend this research to better understand the capabilities and limitations of predictive methods using fuels and scenarios that fire investigators are likely to encounter during a fire investigation.
 }
@@
 
+Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
+
 The main objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
@@
 
+Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+
 The second objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
@@
 
+\item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
+\item Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+
+This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.
+Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
+The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
+Three different fuels were used: natural gas, gasoline, and polyurethane foam.
+Each fuel had a similar top surface area.
+The heat release rate data showed that the variability between replicates was greater for more complex fuels.
+The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%.
+However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
+
+The variability in the heat release rate of the fires resulted in higher levels of variability of the replicate fire patterns.
+The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
+The comparison of the fire pattern heights and the mean flame height demonstrated that the ``steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+
+A range of methods used to simulate characteristics of fires were applied using data from the source fire experiments as input.
+The algebra based predictions for heat flux to a target under predicted the measured values.
+The gasoline fueled fires best agreement of 22~\% or less for the heat flux predictions.
+The polyurethane foam results exhibited the worst agreement with difference of at least 40~\% between the measured and calculated values.
+Improved understanding of the radiative fraction from different fuels would improve the capability of the predictions.
+
+The best agreement between measured flame height, the measured height of the fire pattern, and flame height predictions occurred with the gasoline fueled fires.
+Given the overlap of the expanded uncertainty and predicted range of values, the measured and predicted heights would be considered similar.
+The gasoline fueled fires released the highest amount of energy and has a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
+
+The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
+The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface, as the distance between the burner surface increased the predicted values tended to converge with the measured values.
+The wall located adjacent to the burn had a significant impact on the flow field in and around the flame and plume region.
+The horizontal flame movements observed during the experiments was not simulated to the same degree by the model.
+Given the areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
+
+The models are useful tools for gaining insight into fire behavior but in many cases many require specific experimental data for input or for validation.
+The availability   of well characterized input data is limited and data for newer materials is unavailable.
+Additional research is needed for modeling data development protocols.
+Improved data repositories are also needed.
+Further research is needed to understand the appropriate resolution for implementing the results based on fuel type, fuel geometry, and ventilation.
+Most importantly, there is a critical need to extend this research to better understand the capabilities and limitations of predictive methods using fuels and scenarios that fire investigators are likely to encounter during a fire investigation.
+
 \bibliography{../References/Madrzykowski_Thesis}

### 2017-03-24 Projects/DelCo_2014_2015/Reports/Propane_Gas_Fire_Experiments/TeX_Files/Propane_Gas_Fire_Experiments.tex
Final gas burner report edits that weren't pushed previously

@@
 \fontsize{20}{24}\selectfont
-\bf{NIST Technical Note XXXX}
+\bf{NIST Technical Note 1953}
 \end{flushright}
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
+\href{http://dx.doi.org/10.6028/NIST.TN.1953}{http://dx.doi.org/10.6028/NIST.TN.1953}
 \endgroup
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1953}{http://dx.doi.org/10.6028/NIST.TN.1953} \\
 \endgroup
@@
 \large
-\flushright{\bf National Institute of Standards and Technology Technical Note XXXX \\
-Natl.~Inst.~Stand.~Technol.~Tech.~Note~XXXX, \pageref{LastPage} pages (February 2017) \\
+\flushright{\bf National Institute of Standards and Technology Technical Note 1953 \\
+Natl.~Inst.~Stand.~Technol.~Tech.~Note~1953, \pageref{LastPage} pages (February 2017) \\
 CODEN: NTNOEF }
@@
 \hypersetup{urlcolor=black}
-\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
+\href{http://dx.doi.org/10.6028/NIST.TN.1953}{\bf http://dx.doi.org/10.6028/NIST.TN.1953} \\
 \endgroup

### 2017-03-26 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
add nij ref   added table ch 8
future ref work

@@
 In this section, comparisons were made between Smokeview generated images and photographs of fire patterns.
+The values from the FDS boundary files are used to examine the temperature of the gypsum wall board and the heat flux exposure to the gypsum wallboard.
+Based on the FDS values, Smokeview can create isosurface areas based on defined boundaries which can be set to a black color to represent a charred area on the target surface.
+This isosurface char technique will be used visualize an FDS generated fire pattern and the peak heights of the fire pattern.
+
+\subsection{Temperature Based Comparison}
+
 The criteria for the `charred' area of the gypsum wall board was a threshold temperature of 360~$^\circ$C.
@@
 
+The visualization parameters for the wall temperature were changed to generate a isosurface `char' pattern in Smokeview.
+Both the ignition temperatures for gypsum wall board from Dillon, 515~$^\circ$C, and Quintiere and Harkleroad, 565~$^\circ$C, were examined~\cite{Dillon:1998,Quintiere:1985}.
+The result from both temperatures was a small, narrow, oval shaped area.
+The peak heights of the char areas were 0.60 and 0.48~m above the burner, respectively.
+These values are below the 95~\% certainty range of the measured fire pattern height, 0.74$\pm$~0.12~m.
+
+The data from the bench scale experiments have a range that spans more than 200~$^\circ$C.
+These values used with Smokeview generated a range of fire pattern shapes and peak fire pattern heights.
+The peak fire pattern heights bounded the measured heights.
+However, the lower ignition temperature provided a more realistic shape than the higher ignition temperatures, which provided a shape of such a small size that it was not reproduced here as it was be hard to discern on the printed image.
+Clearly more data on the ignition temperature of gypsum wall board is needed to better resolve the actual value.
+Based on the Smokeview tool the ignition temperature would be approximately 400~$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
+
 \begin{figure}[h]
@@
 
-As noted in the previous chapter the successful use of any model regardless is using the appropriate data and understanding the basis of the model and any subroutines.
+\subsection{Heat Flux Based Comparison}
+
+Smokeview can be used to provide visuals, based on values from FDS simulations, of instantaneous heat flux exposure to a surface.
+Isosurface controls can be used to define an area with an outer boundary of a given minimum heat flux value.
+Currently, Smokeview cannot generate a time averaged exposure to the surface, therefore the cumulative time history of the heat flux exposure cannot be visualized.
+However the Smokeview simulation can be paused and numerical data relative to the geometry taken from the image.
+
+Table~\ref{tab:FDS_CriticalHF_IWNG} has a range of heat flux values that were based on the series of gypsum wall board experiments documented in Chapter 5 where a threshold or critical heat flux was measured to determine the line of demarcation between the burned and unburned section of the painted paper on the wallboard.
+The last two values 25 and 30 kW/m$^2$ bound the ignition heat flux of painted gypsum wall board.
+The FDS values used for this examination were taken from the FDS simulation (RI=10) of the natural gas burner instrumented wall experiments.
+The peak fire pattern heights based on heat flux from the FDS simulations were compared with the measured peak fire pattern heights of 0.74$\pm$~0.12~m.
+The heights based on heat flux over predicted the height of the fire pattern.
+These result were consistent with the FDS temperature based predictions which also generated fire pattern heights higher than the measured values.
+
+\begin{table}[h]
+  \small
+  \centering
+  \begin{tabular}{|c|c|c|c|} \hline 
+Heat Flux 		&  Peak Fire Pattern Height  	      		  \\
+    			&  Based on FDS Heat Flux    	  	  	  \\
+    (kW/m$^2$)			&  (m) 					 				   \\ 
+\hline    15.0			&  1.04~$\pm$~0.08       		            \\
+\hline    17.5			&  1.04~$\pm$~0.08							    \\
+\hline    20.0			&  1.00~$\pm$~0.08								\\
+\hline	  25.0			&  0.96~$\pm$~0.08							   	  \\
+\hline    30.0   		&  0.92~$\pm$~0.07							\\  \hline
+  \end{tabular}
+  \caption[Heat flux based estimations of the peak fire pattern height from the FDS simulation (RI=10) of the natural gas burner instrumented wall experiments.]{Heat flux based estimations of the peak fire pattern height from the FDS simulation (RI=10) of the natural gas burner instrumented wall experiments.}
+  \label{tab:FDS_CriticalHF_IWNG}
+\end{table}
+
+\subsection{Summary}
+
+As noted in the previous chapter, the successful use of any model is using the appropriate data and understanding the basis of the model and any subroutines.
 FDS is a very complex set of equations and subroutines.
 The model authors have done an incredible job providing digital documentation that is searchable and understandable.
-The challenge in these case is the input data.
+One of the  challenges in these cases is the input data.
 Our understanding of the physical portion of these comparisons may not be as good as the understanding of the theory.
-Hence more research is needed especially of the ignition criteria for gypsum board.
-
-The observations of the flame movement provided some insight into the differences between the model results and the measurements during the wall experiments and the modeled combustion issues near the burner seem to address the temperature differences in the combustion zone just above the burner.
+Hence more research is needed especially on the ignition criteria for gypsum wall board.
+
+The observations of the flame movement provided some insight into the differences between the model results and the measurements during the wall experiments.
+The model's combustion issues near the burner seem to address the temperature differences in the combustion zone just above the burner.
 
@@
 The scope of this study has included several series of experiments that ranged in size from bench scale tests with 100~mm sized samples to full scale compartment experiments with samples 2.4~m tall.
-The key objective was to address the National Academy of Sciences call for research to address `the natural variability of burn patterns'.
+The key objective was to address the National Academy of Science's call for research to address `the natural variability of burn patterns'.
 This study examined the repeatability of several similar small fire sources and the pre-flashover fire patterns that were generated by those fires.
 
-In addition a few popular numerical models were used to simulate the fires or the effects of the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale experiments, and the full-scale fire experiments conducted as part of this study.
+In addition a few popular numerical models were used to simulate the effects of the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale experiments, and the full-scale fire experiments conducted as part of this study.
 The results of the calculations were then compared to the measured values to examine the level of agreement.
 
-In Chapters 2 through 8 results from specific test series or calculations were presented.
+In Chapters 2 through 8, results from specific test series or calculations were presented.
 Typically there was some discussion specific to the experiments or calculations being addressed in each chapter.
-In this chapter the discussion will be more inclusive in examining the key outcomes and the remaining gaps.
+In this chapter the discussion will be more overarching in examining the key outcomes and the remaining gaps.
 
@@
 
-Compare flame height results IGWB with Fire Pattern Experiments
+Compare flame height results IGWB with Fire Pattern Experiments   steep thermal gradient
 
@@
 The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
-The corresponding peak temperatures on the face of the gypsum wall board ranged from the    ~$^\circ$C.
+The corresponding peak temperatures on the face of the gypsum wall board ranged from 415 to 540~$^\circ$C.
 This demonstrates the insulation capability of the gypsum wallboard.
-Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.
-
-steep thermal gradient
-
-Therefore with the limited fire exposure time of approximately 300~seconds, and the small, pre-flashover fires used in this study the
+Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material.
+Therefore with the limited fire exposure time of approximately 300~seconds and the small, pre-flashover fires used in this study, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.
 
@@
 
+This study examined a very limited set of conditions as a means to provide a baseline for future research efforts that would expand on the results from this study in order more completely address the National Academy of Science ...
+natural repeatability of fire patterns.
+Since the National Academy of Science report was issued in 2009, the  the U.S.
+National Institute of Justice, Fire and Arson Investigation Technology Working Group has identified 5 areas where scientific research is needed: (1) understanding of the effects of ventilation on fire damage and patterns; (2) characterization of electrical system response as a means to study fire progression; (3) repeatability and reproducibility of test measurements of large-scale structure fires, (4) materials property data inputs for accurate computer models, and (5) evaluation of incident heat flux profiles to walls and neighboring items in support of fire model validation~\cite{NIJ:2016}.
+The areas suggested for future research in this study involve 4 of the 5 topic areas from the NIJ working group.
+
+Pre-flashover experiments in compartments using well characterized burner fires should be conducted with a broad range of heat release rates and varied burn sizes to 
+to determine if the repeatability results from this study can be replicated.
+
+The flow field between the burner and the adjacent wall or walls should have further research conducted to better understand the movement of the flame and the plume.
+The  when the fire was adjacent to the wall or a corner should receive further examination.
 distance from the wall
@@
 
-\item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
-\item Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
+Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
 

### 2017-03-26 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Completed Future research Chapter

@@
 
-\chapter{Future Research Needs}
+\chapter{Future Research}
 
 This study examined a very limited set of conditions as a means to provide a baseline for future research efforts that would expand on the results from this study in order more completely address the National Academy of Science ...
-natural repeatability of fire patterns.
+natural repeatability of fire patterns~\cite{Forensic:2009}.
 Since the National Academy of Science report was issued in 2009, the  the U.S.
@@
 
-Pre-flashover experiments in compartments using well characterized burner fires should be conducted with a broad range of heat release rates and varied burn sizes to 
-to determine if the repeatability results from this study can be replicated.
+\section{Experiments}
+
+While the results from this project provided a baseline regarding the repeatability of pre-flashover fire patterns, a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions, are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
+
+Pre-flashover experiments in compartments using well characterized burner fires should be conducted with a broad range of heat release rates, burn durations, and varied burner sizes to determine if the repeatability results from this study can be replicated.
 
 The flow field between the burner and the adjacent wall or walls should have further research conducted to better understand the movement of the flame and the plume.
-The  when the fire was adjacent to the wall or a corner should receive further examination.
-distance from the wall
-
-degradation of gypsum board full scale
-
-Use of black paint
-
-Calcination depth
-
-Larger variation of heat release rates
-
-Realistic fuels
-
-duration
-
-lessons learned  cameras   black paint
-
-corners
-
-While the results from this project will provide some insight into the repeatability of pre-flashover fire patterns, a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions, are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
-
-Uncertainty and Modeling
+This may also lead to improved information on the side to side motion of the flame when the burner was against the wall.
+
+Research on fire patterns also needs to be conducted with fuels similar to those that the fire investigators will encounter in the field, such as furnishings and appliances. 
+These fuels release fuel from 3-dimensional surfaces, as opposed to a 2-dimensional burner surface,  In addition, many furnishing items are composed of thermoplastic materials which may melt, flow and drip, potentially spreading the fire and changing the fire pattern during the course of the burn.
+
+There is a great need to understand the impact of ventilation on fire patterns within a structure.
+Fires that stop pre-flashover as well as fires that burn post-flashover need to be studied.
+The structure itself will have an impact on the movement and flow of both fresh air to the fire as well as containing and channeling the movement of combustion products away from the fire, both of which can affect the development of the fire pattern.
+Post-flashover fires are particularly challenging for fire investigators as the potential is high that significant fire damage may be generated remote from the area of origin.
+
+There is a need for continued research on materials used in construction and other furnishings (first items ignited).
+Since the start of this study, a few notable items have changed that may challenge the investigators.
+The gypsum wall board used in this study is considered to be regular gypsum wall board, it was widely used and would be what was readily available at construction material supply stores across the U.S.
+Today, the regular gypsum board has been replaced on store shelves by a less dense version of 12.7~mm thick gypsum wall board.
+A finished lightweight gypsum wall board panel has 30~\% less mass than the regular gypsum wall board that was the de facto construction standard just a few years ago.
+How the lightweight gypsum wall board degrades when exposed to fire has not been quantified.
+
+\section{Modeling}
 
@@
 As a result the flame geometry generated by a piece of furniture may not be representative of the flame geometry characterized by the studies using gas burners and pool fires.
-In this study even using a block of polyurethane foam with a simple geometry led to increased uncertainty.
+In this study even using a block of polyurethane foam with a simple geometry led to increased uncertainty of the peak heat release rate and decreased fire pattern repeatability.
+
+While all of the experimental studies recommended in the previous section may support model validation studies, it is important that a specific validation study be conducted with fuels normally found in real fire investigations to determine the applicability of various numerical methods under realistic fire conditions.
 

### 2017-03-26 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
90 % Discussion

@@
 
-The next set of comparison were made with the natural gas burner fire positioned in the corner against two painted gypsum board walls.
+The next set of comparisons were made with the natural gas burner fire positioned in the corner against two painted gypsum board walls.
 From the perspective of the impact of the corner on the visual fire behavior, the RI=20 simulation captures the extension of the combustion zone.
@@
 \end{figure}
-The next comparison was between the Smokeview corner fire pattern images and photographs of corner fire patterns.
-The images and photographs are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
+The comparison between the Smokeview corner fire pattern images and photographs of corner fire patterns are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
 The isotherms in the Smokeview images range from 20~$^\circ$C to greater than 360~$^\circ$C.
@@
 
+The fire patterns generated by the natural gas and gasoline fires had a high level of repeatability.
+The 95~\% certainty range of the peak fire pattern heights, over 30 experiments from each fuel, was within approximately $\pm$0.1~m.
+The maximum width range of the same experiments was within $\pm$0.07~m.
+The ratio of the height to the width of the the pattern was 3 to 1.
+
+The fire patterns formed by the polyurethane fires, which had an average peak heat release rate almost half of that of the natural gas and gasoline burner fires, had measured certainty ranges for height and width that were similar in magnitude ($\pm$0.12~m and $\pm$0.08~m) to the other two fire sources.
+The polyurethane patterns where almost triangular in shape and had a height to width ratio of almost 1 to 1.
+As a result the percentage difference between the average peak height of the pattern and range of of 95~\% certainty was approximately 3 times higher that the percentage differences from the natural gas and gasoline fires.
+
+For all of the source fires the width of the patterns was similar to the width of the burner.
+The difference in the pattern height was due to the differences in heat release rate.
+The average fire pattern areas of the natural gas and gasoline fires were approximately 0.15~m$^2$.
+The average fire pattern area for the polyurethane foam fires was  0.05~m$^2$.
+Given that the width of the fire pattern was tied to the burner width for this set of experiments, the ratio on the areas between the polyurethane foam and the other fuels was similar to the ratio of the heights of the fire patterns.
+
+These experiments showed that the more repeatable the heat release rate, the more repeatable the fire pattern.
+
 \section{Comparison of Fire Patterns and Flame Heights}
 
+The average peak height of the fire patterns from the natural gas burner, 0.73~m, was closely aligned with the median flame height of 0.71~m.
+The average peak height of the fire patterns from gasoline pan fires was 0.82~m.
+The median flame height for the gasoline was lower, 0.70~m.
+Examining the visible flame heights determined in Chapter 2, the average peak height of the fire pattern aligns better with the height where the gasoline flame was present for approximately 25~\% of the time.
+The gasoline has a radiant fraction that is about twice as high as the natural gas.
+This may account for the additional height on the gasoline fire patterns, relative to the natural gas fire patterns.
+
+An observation from the experiments was that after a period of exposure time, the fire damage to the gypsum wall board would occur within seconds, and then the flame spread on the painted paper would stop and the pattern would not change size for the duration of the burn.
+In one of the compartment fire pattern experiments the natural gas burner was allowed to burn for 15 minutes, yet the pattern did not increase after the initial formation.
+This may be due to the steep thermal gradients that occurred at the line of demarcation between burned and not burned.
+
+Both the fire source characterization and the compartment fire pattern experiments, had uncertainties associated with them.
+In the case of the fire source characterization, there were uncertainties associated with the fuel composition itself, the measurement of the heat release rate, temperature, heat flux and flame height.
+The fire pattern experiments had additional uncertainties or assumptions associated with the composition, thickness, and moisture content of the gypsum wall board.
+In both sets of experiments, efforts were made to limit the uncertainties in the fuels, the measurement techniques and the gypsum wallboard.
+one of the key question's was, is there a relationship that can be demonstrated to determine the source fire heat release rate based on the fire pattern?
+
+Figure~\ref{FH_FP_comp} shows the comparisons of the average maximum fire pattern heights with those of the mean flame height based on the analysis of the video images.
+The associated 95~\% confidence limits are also shown for each height.
+For each of the fuels, the 95~\% certainty ranges of the fire pattern heights and flame heights overlap indicating that the values, while not an exact match, are similar.
+
+\begin{figure}[h]
+  \centering
+  \includegraphics[width=5.0in]{../Figures/FH_FP_Comp}  \\
+  \caption[Comparisons of the average maximum fire pattern heights compared with the mean flame heights.]{Comparisons of the average maximum fire pattern heights compared with the mean flame heights.
+The associated 95~\% confidence limits are also shown for each height.}
+  \label{FH_FP_comp}
+\end{figure}
+
 \subsection{Impact of Instrumentation on Walls}
 
-Compare flame height results IGWB with Fire Pattern Experiments   steep thermal gradient
+Comparing the limited number of fire pattern heights from the instrumented gypsum wall board experiments with the sets of 10 replicates from the compartment fire pattern experiments, show that the peak fire pattern heights were similar.
+Based on these measurements, it would appear that the instrumentation did not impact the fire pattern results.
 
@@
 
-In these experiments, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
+In the compartment experiments, where 3 different wall construction methods were used, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
 The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
 The corresponding peak temperatures on the face of the gypsum wall board ranged from 415 to 540~$^\circ$C.
-This demonstrates the insulation capability of the gypsum wallboard.
-Given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material.
-Therefore with the limited fire exposure time of approximately 300~seconds and the small, pre-flashover fires used in this study, it follows that the additional insulation added with the closed and insulated construction methods would not have created temperature differences at the face of the gypsum wallboard.
-
-Each of the two sets of experiments, the fire source characterization and the fire pattern, had uncertainties associated with them.
-In the case of the fire source characterization, there were uncertainties associated with the fuel composition itself, the measurement of the heat release rate, temperature, heat flux and flame height.
-The fire pattern experiments had additional uncertainties which included: the composition and thickness of the gypsum wallboard, moisture content and paint thickness.
-In both sets of experiments, efforts were made to limit the uncertainties in the fuels, the measurement techniques and the gypsum wallboard.
-In this laboratory based study, the key question is – for a given fire pattern, is there a relationship that can be demonstrated to determine the source fire?
-
-At this stage of the research, the answer to the above question is yes and no.
-Figure 16 shows the comparisons of the average maximum fire pattern heights with those of the mean flame height based on the analysis of the video images.
-The associated 95~\% confidence limits are also shown for each height.
-
-Mean flame height has been identified by Heskestad and others as having a strong relation to a given heat release rate from fires with a horizontal fuel surface~\cite{Heskestad:SFPE, Beyler:1986}.
-However, the ability to relate the mean flame height to the fire pattern height, based on the limited tests here is best suited to a “steady state” case.
-In cases where transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wall board or other target fuel even for “simple” pre-flashover fire patterns.
-
-Screening algorithms utilizing the heat release rate results were employed to estimate the flame height and heat flux to a target surface.
+This demonstrated the insulative capability of the gypsum wall board.
+Given the relatively low energy flow through the gypsum wall board as represented by the limited temperature increase on the backside of the material.
+Therefore with the limited fire exposure time of approximately 300~seconds and the small, pre-flashover fires used in this study, it follows that the additional insulation added with the closed and insulated construction methods would not have created significant temperature differences at the face of the gypsum wallboard.
+
+\section{Modeling Results}
+
+A few general thoughts to put the numerical methods in perspective.
+In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95~\% certainty range of $\pm11\%$.
+This range was the same as that associated with the heat release rate measurement system, so this would be the best agreement that we should expect.
+The gasoline and the polyurethane introduced additional variability and the 95~\% certainty ranges on the peak heat release rate values increased to 30~\% and 47~\% respectively.
+As the physical variability of the experiments increases what is the expectation of numerical methods which simulate the physical experiments
+
+A statistician, George E.P.
+Box, is credited with the quote, `Essentially, all models are wrong, but some are useful.'  The ability of the numerical methods to simulate the results of the physical experiments was mixed.
+Limited in some cases, by the available input data, inappropriate application, or lack of rigor in the underlying physics.
+That said the models tended to provide enough inside to get a user `in the ballpark'.
+
+\subsection{Algebraic Numerical Methods}
+
+Screening algorithms utilizing the heat release rate results were employed to estimate the heat flux to a target surface and the flame height.
 These calculated values were compared to the measured results from “real fuels” and provided reasonable results.
@@
 With the exception of gasoline, the estimated heat flux values tended to under predict the measured results.
-Given the limitations of the data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
+Given the limitations of the input data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
 These algorithms are tools which may be used to provide insight into a problem, but not an accurate single value answer.
 
-\subsection{Modeling Results}
-
-`Essentially, all models are wrong, but some are useful.'   Quote by George E.P. Box  statistician
+Mean flame height has been identified by Heskestad and others as having a strong relation to a given heat release rate from fires with a horizontal fuel surface~\cite{Heskestad:SFPE, Beyler:1986}.
+However, the ability to relate the mean flame height to the fire pattern height, based on the limited tests here is best suited to a “steady state” case.
+In cases where transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wall board or other target fuel even for “simple” pre-flashover fire patterns.
+
+\subsection{Field Models}
+
+The field model comparisons began with examining the vertical centerline temperatures and a remote heat flux measurement of the natural gas source fire with no walls present.
+The simulation with a plume resolution index of 5 (RI=5) provided the best agreement.
+Best agreement in this case meaning that the predicted temperature and heat flux values were within the experimental uncertainty of the measured values.
+The flame height calculated using the HRRPUL provided similar results to the measured values.
+Other RIs were tried and provided results that provided less agreement, therefore it seems critical that end users ensure that they have chosen a grid size that best represents the scale of fire flow field being modeled.
+
+Once the wall was introduced, the flame and plume of the fire were displaced off of the vertical centerline toward the wall.
+The amount of displacement in the physical experiments exceeded the simulated displacement.
+This resulted in poor agreement, meaning simulated values outside of the uncertainty bounds of the measured values.
+Once the burner was positioned against the wall the simulated values and the measured temperature values converged.
+
+The flame and plume movement issue carried through the predicted conditions on the wall surface for both the temperature and the centerline heat flux values.
+The simulated values trended with the measured values but the level of agreement between was mixed.
+The worst agreement was observed at the vertical heat flux array positioned on the edge of the burner.
+As the burner was moved closer to the wall the agreement between the measurement and the predicted heat flux be came worst.
+This was due to the steep thermal gradient along the vertical edge as evidenced by the fire pattern line of demarcation between the burned and unburned paper on the gypsum wall board.
+In the physical experiments the flames moved over the sensors, while in the simulation the flames seem to be offset from the sensors which resulted in under-predicted heat flux values especially at the positions closer to the wall.
+
+The numerical methods are useful tools for gaining insight into fire behavior but in many cases many would require specific experimental data for input or for validation before the results could be relied upon for fire investigation use.
 
@@
 
-While you are reviewing the scene you meet up with the fire captain and begin asking him about the fire.
-The captain tells you that the doors and windows were closed upon arrival.
-When the front door was opened heavy smoke and flame
+In Chapter 1, as the investigator, you had completed your review of the scene and had collected evidence which included an electric heater.
+You are not sure sure about the fire's progression or the area of origin.
+Before leaving the scene, you meet up with the fire captain and begin asking him about the fire.
+The captain tells you that the doors and windows of the townhouse were closed upon arrival.
+When the front door was opened heavy smoke flowed out, followed by flames.
+Other fire fighters were venting the upstairs windows.
+The fire grew and burned for a short time before water was applied to the
 flow path

### 2017-03-27 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Completed Draft

@@
 \Author{Daniel Madrzykowski}
-\Year{2016}
+\Year{2017}
 
@@
 
-Of the active field models, FDS version 6 has one of the most rigorous and publicly accessible verification and validation programs~\cite{McGrattan:2014}.
+Of the active field models, FDS version 6 has one of the most rigorous and publicly accessible verification and validation programs~\cite{FDS_Verification_Guide,FDS_Validation_Guide}.
 More than 45 experimental data sets are used to quantify the prediction capabilities of the model.
@@
 Limited in some cases, by the available input data, inappropriate application, or lack of rigor in the underlying physics.
-That said the models tended to provide enough inside to get a user `in the ballpark'.
+That said the models tended to provide enough insight to get a user `in the ballpark'.
 
@@
 Other fire fighters were venting the upstairs windows.
-The fire grew and burned for a short time before water was applied to the
-flow path
-inconsistent fire pattern near the right side of the sofa.  It appears that pattern was generated pre-flashover.  The pattern height is on the order of   calculate HRR and FH for cushion.
-air equation
+The fire grew and burned for a short time before water was applied through the front door and the fire was knocked down.
+
+Comparing the captain's description with your scene, it would seem that the fire started and burned as a fuel-limited fire, before transitioning to a ventilation limited 
+fire, where the heat and fuel where adequate to sustain combustion, but perhaps oxygen was in short supply.
+This fits the description of the fire flaring up and exiting the front door, shortly after it was opened.
+With the information that other firefighters were opening the upstairs windows at this time, you starting thinking about the flow path in the town home.
+The front door served as a bi-directional vent with the lower portion serving as an air inlet and the upper portion serving as an exhaust for flames.
+In the upstairs bedroom there was mostly smoke damage and no significant heat damage.
+It seems that the open bedroom window served as a smoke exhaust vent.
+
+The large V pattern on the wall behind the sofa and the stair wall may have been generated after the door and upstairs window was opened.
+This is an area where the fuel rich hot fire gases would mix with fresh air entering the front door and burn.
+Area of the living room that was more remote from the front door, the source of oxygen, did not have as much fire damage.
+You remember that there was fire damage to the wall behind the right side of the sofa.
+This burned area on the wall seems distinct and disconnected from the area with the most fire damage, which is to the left of the sofa.
+You decide to go back in the town house for another look, Figure~\ref{Pre_Flashover_Pattern}.
+The pattern behind the sofa had to be generated early in the fire event as it is away from the front door.
+Further the wall behind the sofa between this pattern and the larger area of fire damage closer to the front door was protected and not exposed to flaming combustion.
+The inside of the sofa's seat frame was charred on the inside but not on the outside in the area in front of this pattern.
+The bottom of pattern is located near the base of the sofa seat cushion.
+The pattern height is approximately 0.7~m high extending just above the top of the wood sofa frame.
+The base of the pattern is approximately 0.3~m.
+
+Using Heskestad's flame height equation and solving for the heat release rate based on the pattern height yields a heat release rate on the order of 55~kW.
+Unknowns include the impact of the back portion of the sofa, but this fire size seems reasonable to you with regard to the vision of a sofa cushion burning.
+This information coupled with sequence of events provided by the fire captain and other fire damage would indicate that the right side of the sofa is likely the area of origin, even though it does not have the most fire damage.
+You still need to interview the occupants, was an accidental ignition due to careless smoking possible?
+or a lithium ion battery powered device?
+Also you are still going to check if the heater switch was in the on position, if not that further supports your current hypothesis about the right side of the sofa.
+You will also take samples of the debris in the area of the right seat cushion to send to the lab.
+You have done all that you can at the scene.
+
+If needed, you have the dimensions of the house and the opening so you could have a computer model of the house made to examine how long it would take a small fire to decrease the level of the oxygen within the house to 15~\%.
+This might be needed to get insight on a time line that you might get from the interviews of the occupants.
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/Pre_Flashover_Pattern} \\
+	\caption[Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.]{Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.}
+	\label{Pre_Flashover_Pattern}
+\end{figure}
+
+\begin{figure}[h]
+	\includegraphics[width=5in]{../Figures/Table} \\
+	\caption[Photograph showing the charred inside of the sofa's seat frame.]{Photograph showing the charred inside of the sofa's seat frame.}
+	\label{Table}
+\end{figure}
+
+N.B.
+This section was included to provide a sense of how a fire investigator might use their knowledge of fire behavior, fire patterns, and numerical methods to assist them in following the scientific method.
+Fire investigation requires significantly more than pattern interpretation, the totality of facts from the whole situation must gathered to the extent possible and then after analysis of the evidence, a fire cause may be determined.
 
@@
 
-Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
-
-The main objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
+The main objective of this research study was to examine the repeatability of pre-flashover fire patterns on gypsum wallboard.
+The patterns were generated from exposure to short duration (300 s maximum) well characterized fires.
+
 The first step was to examine the repeatability of different fire sources.
 Three different fuels were used: natural gas, gasoline, and polyurethane foam.
-Each fuel had a similar top surface area.
+Each fuel source had a similar top surface area.
 The heat release rate data showed that the variability was greater for more complex fuels.
-While the variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11~\%, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
-The fire pattern heights generated on painted gypsum wall board by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
-The patterns generated by the polyurethane foam fueled fire, had more variability than the natural gas and the gasoline fire patterns.
-This is likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
-The comparison of the fire pattern heights and the mean flame height demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+The variation in the average peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11~\%.
+However the variation in the average peak heat release rates of the gasoline and the polyurethane foam increased due to uncertainties in the burning behavior of the fuels.
+The average peak heat release rate of gasoline had a 95~\% confidence limit of $\pm$30~\% and the same value for the polyurethane foam was $\pm$47~\%.
+
+The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
+The patterns generated by the polyurethane foam fueled fire, had more than twice the variability of the natural gas and the gasoline fire patterns.
+This was likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
+
+The comparison of the fire pattern heights and the mean flame heights demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
 This trend was the same as exhibited by the repeatability of the heat release rate measurements.
-Given that heat release rate is the source of the energy which was transferred to the walls in order generate the fire patterns, it stands to reason that the greater the uncertainty in the heat release rate the greater the uncertainty in pattern and any associated thermal measurements.
+Given that the heat release rate from the fires was the source of the energy transferred to the walls to generate the fire patterns.
+It stands to reason that the greater the uncertainty in the heat release rate, the greater the uncertainty in the resulting pattern and any associated thermal measurements.
 
@@
 
-Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
-
-The second objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+Another objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted as part of this study.
 The numerical tools used ranged from simple empirical algorithms to a computational fluid dynamics model.
 Each of the tools are freely available to investigators and many of the tools have been packaged in a form that allows the user to input the ``data'' and generate a result.
-There is software available to aid with the development of the computational fluid dynamics model.
-The first challenge in using the numerical tools is finding the appropriate data to us as input.
-
-Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
-Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
-
-This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.
-Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
-The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
-Three different fuels were used: natural gas, gasoline, and polyurethane foam.
-Each fuel had a similar top surface area.
-The heat release rate data showed that the variability between replicates was greater for more complex fuels.
-The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%.
-However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
-
-The variability in the heat release rate of the fires resulted in higher levels of variability of the replicate fire patterns.
-The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
-The comparison of the fire pattern heights and the mean flame height demonstrated that the ``steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+There is also graphical user interface software available to aid with the development of the computational fluid dynamics model.
+The first challenge in using the numerical tools is finding the appropriate data to use as input.
 
@@
 The algebra based predictions for heat flux to a target under predicted the measured values.
-The gasoline fueled fires best agreement of 22~\% or less for the heat flux predictions.
+The gasoline fueled fires had the best agreement of 22~\% or less for the heat flux predictions.
 The polyurethane foam results exhibited the worst agreement with difference of at least 40~\% between the measured and calculated values.
@@
 
-The best agreement between measured flame height, the measured height of the fire pattern, and flame height predictions occurred with the gasoline fueled fires.
+The best agreement between measured flame height, the measured height of the fire pattern, and flame height predictions from Heskestad's formula occurred with the gasoline fueled fires.
 Given the overlap of the expanded uncertainty and predicted range of values, the measured and predicted heights would be considered similar.
-The gasoline fueled fires released the highest amount of energy and has a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
-
-The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
-The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface, as the distance between the burner surface increased the predicted values tended to converge with the measured values.
-The wall located adjacent to the burn had a significant impact on the flow field in and around the flame and plume region.
-The horizontal flame movements observed during the experiments was not simulated to the same degree by the model.
-Given the areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
-
-The models are useful tools for gaining insight into fire behavior but in many cases many require specific experimental data for input or for validation.
+The gasoline fueled fires released the highest amount of energy and had a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
+The flame height algorithm tended to over predict the values for the natural gas and the polyurethane fueled fires.
+
+The agreement between the values predicted by the computational fluid dynamic model, FDS, and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
+The differences were a result, in some cases, by limitations within the combustion sub-model close to the burner surface.
+In those cases as the distance between the burner surface increased the predicted values tended to converge with the measured values.
+
+The wall located adjacent to the burner had a significant impact on the flow field in and around the flame and plume region.
+The horizontal flame movements observed during the experiments were not simulated to the same degree by the model.
+Since areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
+
+The models proved to be useful tools for gaining insight into fire behavior but in many cases the models require specific experimental data for input or for validation.
 The availability of well characterized input data is limited and data for newer materials is unavailable.

### 2017-03-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
fixed % and abstract

@@
 
-I would also like to thank Roger Nokes for his development and continued assistance with Streams and to the New Zealand Fire Commission for their financial support to the University of Canterbury
+I would also like to thank Dr.
+Roger Nokes for his development and continued assistance with Streams, and to the New Zealand Fire Commission for their financial support to the University of Canterbury.
 
 Last but not least, I thank my wife, Liz, for her patience and support of my pursuit of higher education throughout our 38 years of marriage.
-I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica for ``buying me time'' to work on my studies.}
+I would also like to thank my children; Catherine, Stephanie, Michael, Christina, and Veronica, for buying me time to work on my studies.}
 
@@
 National Academy of Sciences.
-Specifically the National Academy of Sciences indicated that ``...
+Specifically, the National Academy of Sciences indicated that ``...
 research is needed on the natural variability of burn patterns...''
@@
 \begin{enumerate}
-\item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires
-\item Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted in this study.
+\item Examining the repeatability of several small fire sources and the fire patterns that were generated by those fires.
+\item Examining the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, bench-scale experiments, and full-scale fire experiments.
 \end{enumerate}
+
 This manuscript highlights the many uncertainties involved in what appear to be simple fire experiments.
 Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
-The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum) well characterized fires.
+The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum), well characterized fires.
 Three different fuels were used: natural gas, gasoline, and polyurethane foam.
@@
 The heat release rate data showed that the variability between replicates was greater for more complex fuels.
-The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11~\%.
+The variation in peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, 11\%.
 However, the variation in the peak heat release rates of the gasoline and the polyurethane foam increased due to increased uncertainties in the burning behavior of the fuels.
@@
 The variability in the heat release rate of the fires resulted in higher levels of variability of the replicate fire patterns.
-The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
-The comparison of the fire pattern heights and the mean flame height demonstrated that the ``steady state'' natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+The maximum fire pattern heights generated from the natural gas and gasoline fires were shown to have uncertainties of 18\% or less based on a Type A statistical analysis with 95\% confidence limits.
+The comparison of the fire pattern heights and the mean flame height demonstrated that the steady state natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
 
 A range of methods used to simulate characteristics of fires were applied using data from the source fire experiments as input.
-The algebra based predictions for heat flux to a target under predicted the measured values.
-The gasoline fueled fires best agreement of 22~\% or less for the heat flux predictions.
-The polyurethane foam results exhibited the worst agreement with difference of at least 40~\% between the measured and calculated values.
+The algebra-based predictions for heat flux to a target under-predicted the measured values.
+The gasoline fueled fires exhibited best agreement of 22\% or less for the heat flux predictions.
+The polyurethane foam results exhibited the worst agreement with a difference of at least 40\% between the measured and calculated values.
 Improved understanding of the radiative fraction from different fuels would improve the capability of the predictions.
@@
 Given the overlap of the expanded uncertainty and predicted range of values, the measured and predicted heights would be considered similar.
-The gasoline fueled fires released the highest amount of energy and has a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
+The gasoline fueled fires released the highest amount of energy and had a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
 
 The agreement between the computational fluid dynamics predicted values and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
-The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface, as the distance between the burner surface increased the predicted values tended to converge with the measured values.
+The differences were driven in some cases by limitations within the combustion sub-model close to the burner surface; as the distance between the burner surface increased, the predicted values tended to converge with the measured values.
 The wall located adjacent to the burn had a significant impact on the flow field in and around the flame and plume region.
 The horizontal flame movements observed during the experiments was not simulated to the same degree by the model.
-Given the areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
+Given the areas around the flame have steep thermal gradients, small differences in position can result in large differences in temperature and heat flux.
 
 The models are useful tools for gaining insight into fire behavior but in many cases many require specific experimental data for input or for validation.
-The availability   of well characterized input data is limited and data for newer materials is unavailable.
+The availability of well characterized input data is limited, and data for newer materials is unavailable.
 Additional research is needed for modeling data development protocols.
@@
 $\chi_r$ \> radiative fraction \\
-$\dot{q}''$ \> heat flux per unit area kW/m$^2$ \\
+$\dot{q}''$ \> heat flux per unit area (kW/m$^2$) \\
 $\dot{Q}$ \> heat release rate (kW) \\ 
@@
 Madrzykowski, D.
-and Fleischmann, C., "Fire Pattern Repeatability: A Laboratory Study on Gypsum Wallboard." In Proceedings ISFI 2010: International Symposium on Fire Investigation Science and Technology, Hyattsville, MD, USA.
+and Fleischmann, C., `Fire Pattern Repeatability: A Laboratory Study on Gypsum Wallboard.' In Proceedings ISFI 2010: International Symposium on Fire Investigation Science and Technology, Hyattsville, MD, USA.
 Sarasota, FL, USA 2010.
@@
 Madrzykowski, D.
-and Fleischmann, C., "Flame Heights and Heat Transfer from Gaseous, Liquid and Solid Fuels for Burn Pattern Repeatability Research." In INTERFLAM 2010: 12th International Conference on Fire Science and Engineering, Nottingham, UK.
+and Fleischmann, C., `Flame Heights and Heat Transfer from Gaseous, Liquid, and Solid Fuels for Burn Pattern Repeatability Research.' In INTERFLAM 2010: 12th International Conference on Fire Science and Engineering, Nottingham, UK.
 London, UK, 2010.
@@
 More than \$1.3 billion dollars (U.S.) was lost per year due to direct property damage.
-Structure fires represent less than 20~\% of intentionally set fires.
-However, fires involving structures account for more than 84~\% of the civilian deaths, injuries and property loss from all intentional fires.
+Structure fires represent less than 20\% of intentionally set fires.
+However, fires involving structures account for more than 84\% of the civilian deaths, injuries and property loss from all intentional fires.
 Approximately two-thirds of the intentional structure fires occurred in occupied and operating residential occupancies.
-As a result, 95~\% of the civilian deaths and 86~\% of the civilian injuries which are attributed to intentional fires occurred in residential occupancies~\cite{Campbell:2014}.
+As a result, 95\% of the civilian deaths and 86\% of the civilian injuries which are attributed to intentional fires occurred in residential occupancies~\cite{Campbell:2014}.
 
@@
 Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime:2010}.
-The national rate of arson fire cases cleared by arrest or exceptional means is less than 20~\%.
-Of those cases approximately 46~\% of the suspects were prosecuted~\cite{Campbell:2014}.
-Hence less than 10~\% of the arson cases resulted in successful prosecution.
+The national rate of arson fire cases cleared by arrest or exceptional means is less than 20\%.
+Of those cases approximately 46\% of the suspects were prosecuted~\cite{Campbell:2014}.
+Hence less than 10\% of the arson cases resulted in successful prosecution.
 
@@
 every year~\cite{Foam,Polyurethane_Foam}.
-In studies by Ahrens and Evarts of the NFPA, upholstered furniture, and mattresses and bedding were the first items ignited in 33~\% of the fatal fires in the U.S.
+In studies by Ahrens and Evarts of the NFPA, upholstered furniture, and mattresses and bedding were the first items ignited in 33\% of the fatal fires in the U.S.
 based on averaged data from 2005 through 2009~\cite{Ahrens:2011,Evarts:2011}.
@@
 Many of the same instruments were shared between the two calorimeters and calibration burns were conducted during each experimental series.
-As a result, the expanded uncertainty of this device has been estimated as 11~\% on the measured heat release rate.
+As a result, the expanded uncertainty of this device has been estimated as 11\% on the measured heat release rate.
 
@@
 Small diameter thermocouples were used to limit the impact of radiative heating and cooling.
-The estimated combined expanded uncertainty for temperature in these experiments was 15~\%.
+The estimated combined expanded uncertainty for temperature in these experiments was 15\%.
 
@@
 The sensing surface of the heat flux gauges were located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
-The manufacturer reports a 3~\% calibration expanded uncertainty for these devices~\cite{Medtherm}.
-Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge was typically 8~\%~\cite{Pitts:2006}.
+The manufacturer reports a 3\% calibration expanded uncertainty for these devices~\cite{Medtherm}.
+Results from an international study on total heat flux gauge calibration and response demonstrated that the uncertainty of a Schmidt-Boelter gauge was typically 8\%~\cite{Pitts:2006}.
 The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
@@
 The load cell had a resolution of 1.0~g~\cite{Mettler}.
-The expanded uncertainty was estimated to be 5~\%.
+The expanded uncertainty was estimated to be 5\%.
 The load cell was checked between experiments with calibrated weights during the zero and span checks of the calorimeter.
@@
 A plumb bob and steel tape measure, with a resolution of $\pm$~0.5~mm, were used to position and align the thermocouples.
-The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$~2.5~\%.
+The expanded uncertainty for the location of each thermocouple tip is estimated to be $\pm$~2.5\%.
 The same applies to the location of the heat flux sensor surfaces.
@@
 
-On the averaged heat release rate curve for each fuel, the shaded area surrounding the average represents the 95~\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+On the averaged heat release rate curve for each fuel, the shaded area surrounding the average represents the 95\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
-In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95~\%.
+In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95\%.
 
 The natural gas burner provided the most repeatable results, with an average steady state heat release rate of 80~kW~$\pm$~9~kW with an average total heat release of 23.3~MJ~$\pm$~1.6~MJ over a 300~s period.
-The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11~\% It should be noted that 11~\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
+The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11\% It should be noted that 11\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
 The gas burner and on/off control valve allowed the heat release rate to be similar in form to a ``square-wave''.
@@
 Therefore the  gasoline average peak heat release rate was based on an average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments.
-This method provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 30~\%.
+This method provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 30\%.
 The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
@@
 Since the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~s interval bounding the peak heat release rate from each of the ten experiments.
-This process yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 47~\%.
+This process yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 47\%.
 The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ.
 
-The Figures~\ref{HRR}-\ref{HRR2} have a shaded area that shows the 95~\% confidence level.
+The Figures~\ref{HRR}-\ref{HRR2} have a shaded area that shows the 95\% confidence level.
 The more narrow the shaded area, the better the repeatability of the fire.
@@
 In engineering terms, the ``flame height'' is typically discussed as the median flame height.
-A position above the top of the fuel surface where the flame is observed to be present at least 50~\% of the time.
+A position above the top of the fuel surface where the flame is observed to be present at least 50\% of the time.
 As a starting point, the mean flame height for each fuel was estimated from a measurement of the uppermost continuous flame tip from the still photographic images.
@@
 The natural gas fire was sampled for 29~s, resulting in 870~images.
-The area bounded by the contour with the value 1 represents the area that the flame was visible 100~\% of the time sampled.
+The area bounded by the contour with the value 1 represents the area that the flame was visible 100\% of the time sampled.
 This can be considered the persistent flame region as defined by McCaffrey~\cite{McCaffrey:1979}.
@@
 Refer back to Figure~\ref{flame_height_comp_FHPUF_1} to see photographic views of the bifurcated flames.
-It seems that the movement of the flames as they flowed away from the fuel surface blurred out the bifurcation over time with the exception of the lower elevation areas that presented at the 90 and 100~\% contours.
+It seems that the movement of the flames as they flowed away from the fuel surface blurred out the bifurcation over time with the exception of the lower elevation areas that presented at the 90 and 100\% contours.
 Other methods of ignition for the polyurethane foam were considered in order to have a more uniform ignition of the top surface of the foam.
@@
 Based on the field data developed using Streams average flame heights for each fuel were determined.
-In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in mm with 95~\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
+In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in mm with 95\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
 For the natural gas fires, the averages are from ten 30~s segments, while the fire was monitored at approximately 80~kW.
@@
 Fraction (\%)   &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
-10              &       980 $\pm$ 155 (16~\%)   &	930 $\pm$ 130 (14~\%) 	& 650 $\pm$ 220 (34~\%)   \\
-20              &   	890 $\pm$ 125 (14~\%)   &	850 $\pm$ 120 (14~\%) 	& 590 $\pm$ 190 (32~\%)   \\
-30              &   	820 $\pm$ 125 (15~\%)   &	790 $\pm$ 110 (14~\%) 	& 540 $\pm$ 180 (33~\%)   \\
-40              &   	760 $\pm$ 105 (14~\%)   &	740 $\pm$ 95 (13~\%) 	& 500 $\pm$ 165 (33~\%)   \\
-50              &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
-60              &   	650 $\pm$ 100 (15~\%)   &	655 $\pm$ 85 (13~\%) 	& 435 $\pm$ 135 (31~\%)   \\
-70              &   	590 $\pm$ 90 (15~\%)    &	610 $\pm$ 90 (15~\%) 	& 400 $\pm$ 125 (31~\%)   \\
-80              &   	530 $\pm$ 85 (16~\%)    &	555 $\pm$ 90 (16~\%) 	& 360 $\pm$ 110 (31~\%)   \\
-90              &   	440 $\pm$ 75 (17~\%)    &	490 $\pm$ 95 (19~\%) 	& 315 $\pm$ 110 (35~\%)   \\
-100	            &       220 $\pm$ 84 (38~\%)    &	350 $\pm$ 110 (32~\%) 	& 210 $\pm$ 125 (60~\%)   \\
+10              &       980 $\pm$ 155 (16\%)   &	930 $\pm$ 130 (14\%) 	& 650 $\pm$ 220 (34\%)   \\
+20              &   	890 $\pm$ 125 (14\%)   &	850 $\pm$ 120 (14\%) 	& 590 $\pm$ 190 (32\%)   \\
+30              &   	820 $\pm$ 125 (15\%)   &	790 $\pm$ 110 (14\%) 	& 540 $\pm$ 180 (33\%)   \\
+40              &   	760 $\pm$ 105 (14\%)   &	740 $\pm$ 95 (13\%) 	& 500 $\pm$ 165 (33\%)   \\
+50              &   	705 $\pm$ 106 (15\%)   &	695 $\pm$ 95 (14\%) 	& 470 $\pm$ 160 (34\%)   \\
+60              &   	650 $\pm$ 100 (15\%)   &	655 $\pm$ 85 (13\%) 	& 435 $\pm$ 135 (31\%)   \\
+70              &   	590 $\pm$ 90 (15\%)    &	610 $\pm$ 90 (15\%) 	& 400 $\pm$ 125 (31\%)   \\
+80              &   	530 $\pm$ 85 (16\%)    &	555 $\pm$ 90 (16\%) 	& 360 $\pm$ 110 (31\%)   \\
+90              &   	440 $\pm$ 75 (17\%)    &	490 $\pm$ 95 (19\%) 	& 315 $\pm$ 110 (35\%)   \\
+100	            &       220 $\pm$ 84 (38\%)    &	350 $\pm$ 110 (32\%) 	& 210 $\pm$ 125 (60\%)   \\
 \hline
 \end{tabular}
- \caption[Average flame heights for three fuels]{Average flame heights with 95~\% confidence limits, for each of the source fuels shown as the percentage of time the flame was visible at that given height.}
+ \caption[Average flame heights for three fuels]{Average flame heights with 95\% confidence limits, for each of the source fuels shown as the percentage of time the flame was visible at that given height.}
  \label{tab:Average_Flame_Heights}
@@
 
-For both the natural gas and the gasoline experiments the 95~\% confidence limits show less than 20 percent variation in visible flame height within the intermittent flame region.
+For both the natural gas and the gasoline experiments the 95\% confidence limits show less than 20 percent variation in visible flame height within the intermittent flame region.
 The percentage variation increases at the continuous flame region, although the magnitudes of the height variations are similar to other sections of the intermittent flame region.
 The percentage variation is higher in the continuous flame region because the height of the continuous flame region is the smallest.
-The 95~\% confidence limits for the polyurethane foam are about twice those of the natural gas and the gasoline.
+The 95\% confidence limits for the polyurethane foam are about twice those of the natural gas and the gasoline.
 
@@
 Table~\ref{tab:Source_fire_summary} is a summary of the average peak heat release rate, the total heat released, the average peak heat flux, the median flame height and the average peak temperature at the thermocouple closest to the median flame height.
-In the table each of the measurements is show with the 95~\% confidence limits.
+In the table each of the measurements is show with the 95\% confidence limits.
 This data has been collected for use in direct analysis of the burn patterns and as input into the engineering correlations and FDS models that are used later in this study.
@@
 type                    &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline \hline
-Avg. Peak HRR (kW)      &       80 $\pm$ 9 (11~\%)   &	80 $\pm$ 24 (30~\%) 	& 45 $\pm$ 21 (47~\%)   \\
-Total HR (MJ)           &   	23.3 $\pm$ 1.6 (7~\%)   &	13.6 $\pm$ 0.6 (4~\%) 	& 4.1 $\pm$ 0.2 (5~\%)   \\
-Avg Peak HF (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25~\%)   &	3.6 $\pm$ 0.9 (25~\%) 	& 2.5 $\pm$ 0.5 (20~\%)   \\
-Median FH (mm)           &   	705 $\pm$ 106 (15~\%)   &	695 $\pm$ 95 (14~\%) 	& 470 $\pm$ 160 (34~\%)   \\
-Avg Peak Temp. (C)      &   	410 $\pm$ 103 (25~\%)   &	335 $\pm$ 41 (12~\%) 	& 334 $\pm$ 106 (32~\%)   \\
+Avg. Peak HRR (kW)      &       80 $\pm$ 9 (11\%)   &	80 $\pm$ 24 (30\%) 	& 45 $\pm$ 21 (47\%)   \\
+Total HR (MJ)           &   	23.3 $\pm$ 1.6 (7\%)   &	13.6 $\pm$ 0.6 (4\%) 	& 4.1 $\pm$ 0.2 (5\%)   \\
+Avg Peak HF (kW/m$^2$)   &   	2.0 $\pm$ 0.5 (25\%)   &	3.6 $\pm$ 0.9 (25\%) 	& 2.5 $\pm$ 0.5 (20\%)   \\
+Median FH (mm)           &   	705 $\pm$ 106 (15\%)   &	695 $\pm$ 95 (14\%) 	& 470 $\pm$ 160 (34\%)   \\
+Avg Peak Temp. (C)      &   	410 $\pm$ 103 (25\%)   &	335 $\pm$ 41 (12\%) 	& 334 $\pm$ 106 (32\%)   \\
 \hline
@@
  \caption[Select measurements for the three source fires]{Select measurements for the three source fires.
-Each measurement is shown with 95~\% confidence limits both in terms of a value and a percentage.}
+Each measurement is shown with 95\% confidence limits both in terms of a value and a percentage.}
  \label{tab:Source_fire_summary}
@@
 It is normally used as a fire-resistant thermal insulation that also has structural strength.
-90~\% of the board is composed of calcium silicate and calcium meta-silicate.
-The remaining 10~\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:MSDS}.
+90\% of the board is composed of calcium silicate and calcium meta-silicate.
+The remaining 10\% of the board is composed of a combination of organic fibers, fiber glass filament and crystalline silica (quartz)~\cite{BNZ:MSDS}.
 Material properties that impact heat transfer were selected from the manufacturer's literature and are presented In Table~\ref{tab:Marinite_Thermal_Properties}~\cite{Marinite:1997}.
@@
 	\caption[Summary of instrumented non-combustible wall experiments]{Summary of averaged peak temperatures and averaged heat fluxes from the instrumented non-combustible wall experiments.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\% and $\pm$8\% for the heat flux.}
 	\label{tab:TW_Summary}
@@
 The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
-By weight, wallboard is composed of more than 85~\% gypsum, less than 10~\% cellulose, less than 3~\% starch and approximately 1~\% of both crystalline silica and fibrous glass~\cite{GA:2010}.
+By weight, wallboard is composed of more than 85\% gypsum, less than 10\% cellulose, less than 3\% starch and approximately 1\% of both crystalline silica and fibrous glass~\cite{GA:2010}.
 Chemically, gypsum can be described as calcium sulfate dihydrate, (CaSO$_{4}$ $\bullet$ 2H$_{2}$O) .
-By weight, pure gypsum is approximately 79~\% calcium sulfate and 21~\% chemically bound water~\cite{Lawson:1977}.
+By weight, pure gypsum is approximately 79\% calcium sulfate and 21\% chemically bound water~\cite{Lawson:1977}.
 
@@
 In other words, the range of expanded uncertainty values overlap.
-For example, at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15~\%).
+For example, at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15\%).
 So, the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
@@
 	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of averaged peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for the heat flux.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\% and $\pm$8\% for the heat flux.}
 	\label{tab:IWGB_Summary}
@@
 The averaged ignition time and temperature pairs are shown in Table~\ref{tab:Gypsum_wallboard_igntemp}.
-The average time to ignition values between the two different calorimeters are within $\pm~50~\%$ and $\pm~10~\%$ at incident heat flux values of 35 and 50~kW/m$^2$, respectively.
+The average time to ignition values between the two different calorimeters are within $\pm~50\%$ and $\pm~10\%$ at incident heat flux values of 35 and 50~kW/m$^2$, respectively.
 The average ignition temperatures from the nine experiments ranged from 335 to 375~$^{\circ}$C.
@@
 	\caption[Painted gypsum wallboard ignition temperature results]{Painted gypsum wallboard ignition temperature results from exposure in the cone calorimeter.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\%.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\%.}
 	\label{tab:Gypsum_wallboard_igntemp}
@@
 The values are averages from three replicate experiments.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15~\% and $\pm$8~\% for heat flux.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\% and $\pm$8\% for heat flux.}
 	\label{tab:FRP_timetemp}
@@
 There were four measures that were taken to characterize each pattern: maximum height, maximum width, height at maximum width, and the area.
-Each dimensional value is presented with the 95~\% confidence level (2~$\sigma$) based on Type A statistical analysis of the fire pattern measurements.
+Each dimensional value is presented with the 95\% confidence level (2~$\sigma$) based on Type A statistical analysis of the fire pattern measurements.
 
@@
 The images within the figure are slightly different sized in an effect to make the images comparable.
-The average maximum height of the fire pattern generated by the natural gas burner on the open walls was 0.74~m~$\pm~0.12~\%$.
-The average maximum width of the fire pattern from the same experiments was 0.24~m~$\pm~0.06~\%$.
-The position from the top edge of the burner to the vertical position of the maximum width was 0.41~m~$\pm~0.07~\%$.
-The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.05~\%$.
+The average maximum height of the fire pattern generated by the natural gas burner on the open walls was 0.74~m~$\pm~0.12\%$.
+The average maximum width of the fire pattern from the same experiments was 0.24~m~$\pm~0.06\%$.
+The position from the top edge of the burner to the vertical position of the maximum width was 0.41~m~$\pm~0.07\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.05\%$.
 
@@
 The patterns appear very similar in nature and size to the patterns that were generated on the open construction walls.
-The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06~\%$.
+The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06\%$.
 The 95~$\%$ confidence limit is about half of the value from the open wall experiments.
-The average maximum width of the fire patterns was 0.24~m~$\pm~0.02~\%$.
+The average maximum width of the fire patterns was 0.24~m~$\pm~0.02\%$.
 Again similar to the previous experiments.
-The vertical position of the maximum width was 0.43~m~$\pm~0.03~\%$.
-The area of the burn estimated by examining the damaged grid cells was 0.14~$m^2~\pm~0.01~\%$.
+The vertical position of the maximum width was 0.43~m~$\pm~0.03\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.14~$m^2~\pm~0.01\%$.
 
@@
 The patterns from the ten replicate experiments are shown in Figure~\ref{NG_Insulated_Wall}.
-The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10~\%$.
-The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04~\%$.
-The vertical position of the maximum width was 0.42~m~$\pm~0.07~\%$.
-The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02~\%$.
+The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10\%$.
+The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04\%$.
+The vertical position of the maximum width was 0.42~m~$\pm~0.07\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02\%$.
 
@@
 The patterns from the ten replicate experiments are shown in Figure~\ref{Gas_Insulated_Wall}.
-The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10~\%$.
-The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04~\%$.
-The vertical position of the maximum width was 0.42~m~$\pm~0.07~\%$.
-The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02~\%$.
+The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10\%$.
+The average maximum width of the fire patterns on the insulated walls were 0.23~m~$\pm~0.04\%$.
+The vertical position of the maximum width was 0.42~m~$\pm~0.07\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.15~$m^2~\pm~0.02\%$.
 
@@
 	Fuel (\# of tests)      &   Wall Type   &   Max. Height (m)	         & Max. Width (m)               &  Height at Max. Width (m) &  Area (m$^2$)  \\ \hline 
-		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16~\%)   &	0.24 $\pm$ 0.06 (25~\%) 	& 0.41 $\pm$ 0.07 (17~\%)	& 0.15 $\pm$ 0.05 (33~\%) 	\\
-		Natural Gas (10)    &   Closed 		& 0.74	$\pm$ 0.06 (8~\%)    &	0.24 $\pm$ 0.02 (7~\%) 		& 0.43 $\pm$ 0.03 (7~\%)  	& 0.14 $\pm$ 0.01 (6~\%) 	\\
-		Natural Gas (10)    &   Insulated 	& 0.71	$\pm$ 0.10 (14~\%)   &	0.23 $\pm$ 0.04 (17~\%) 	& 0.42 $\pm$ 0.07 (17~\%) 	& 0.15 $\pm$ 0.02 (14~\%)  	\\
-		Gasoline (10)       &   Open    	& 0.83	$\pm$ 0.15 (18~\%)   &	0.28 $\pm$ 0.09 (32~\%) 	& 0.44 $\pm$ 0.14 (32~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
-		Gasoline (10)       &   Closed  	& 0.80	$\pm$ 0.10 (13~\%)   &	0.29 $\pm$ 0.04 (14~\%) 	& 0.44 $\pm$ 0.06 (14~\%) 	& 0.17 $\pm$ 0.04 (24~\%)  	\\
-		Gasoline (10)       &   Insulated	& 0.82 	$\pm$ 0.09 (11~\%)   &	0.25 $\pm$ 0.08 (32~\%) 	& 0.40 $\pm$ 0.13 (32~\%) 	& 0.13 $\pm$ 0.04 (30~\%)  	\\
-		Polyurethane (10)	&   Open 		& 0.24  $\pm$ 0.12 (50~\%) 	 &  0.28 $\pm$ 0.08 (29~\%) 	& 0.40 $\pm$ 0.24 (60~\%)   & 0.05 $\pm$ 0.03 (57~\%)   \\
+		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.12 (16\%)   &	0.24 $\pm$ 0.06 (25\%) 	& 0.41 $\pm$ 0.07 (17\%)	& 0.15 $\pm$ 0.05 (33\%) 	\\
+		Natural Gas (10)    &   Closed 		& 0.74	$\pm$ 0.06 (8\%)    &	0.24 $\pm$ 0.02 (7\%) 		& 0.43 $\pm$ 0.03 (7\%)  	& 0.14 $\pm$ 0.01 (6\%) 	\\
+		Natural Gas (10)    &   Insulated 	& 0.71	$\pm$ 0.10 (14\%)   &	0.23 $\pm$ 0.04 (17\%) 	& 0.42 $\pm$ 0.07 (17\%) 	& 0.15 $\pm$ 0.02 (14\%)  	\\
+		Gasoline (10)       &   Open    	& 0.83	$\pm$ 0.15 (18\%)   &	0.28 $\pm$ 0.09 (32\%) 	& 0.44 $\pm$ 0.14 (32\%) 	& 0.17 $\pm$ 0.04 (24\%)  	\\
+		Gasoline (10)       &   Closed  	& 0.80	$\pm$ 0.10 (13\%)   &	0.29 $\pm$ 0.04 (14\%) 	& 0.44 $\pm$ 0.06 (14\%) 	& 0.17 $\pm$ 0.04 (24\%)  	\\
+		Gasoline (10)       &   Insulated	& 0.82 	$\pm$ 0.09 (11\%)   &	0.25 $\pm$ 0.08 (32\%) 	& 0.40 $\pm$ 0.13 (32\%) 	& 0.13 $\pm$ 0.04 (30\%)  	\\
+		Polyurethane (10)	&   Open 		& 0.24  $\pm$ 0.12 (50\%) 	 &  0.28 $\pm$ 0.08 (29\%) 	& 0.40 $\pm$ 0.24 (60\%)   & 0.05 $\pm$ 0.03 (57\%)   \\
 		\hline
@@
 	\caption[Comparison of fire pattern dimensions as a function of wall construction type]{Comparison of fire pattern dimensions as a function of wall construction type.
-Values presented with 95~\% confidence limits.}
+Values presented with 95\% confidence limits.}
 	\label{tab:Fire_Pattern_Dimensions_Wall_Construction}
@@
 The purpose of moving the burner position toward the corner was to examine the effect of reducing the available air entrainment area around the perimeter of the burner on the resulting fire pattern.
-With the burner tight against both walls, the air entrainment perimeter was reduced by 50~\%.
+With the burner tight against both walls, the air entrainment perimeter was reduced by 50\%.
 Previous studies on flame height with fires in corners have demonstrated the the flame height increased when compared to a similar fire positioned against a single wall or burning in the open~\cite{Poreh:1999,Saito:1993,Takahashi:1997,Kokkala:1993}.
@@
 	Fuel (\# of tests)      &   Wall Type   & Max. Height Left (m)	 	& Area Left (m$^2$)				&  Max. Height Right (m)        & Area (m$^2$)  				\\     \hline
-		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.15 (20~\%)  & 0.061 $\pm$ 0.028 (46~\%) 	&  0.78 $\pm$ 0.17 (22~\%) 	 	& 0.061 $\pm$ 0.028 (46~\%)  	\\
-		Gasoline (10)       &   Open    	& 0.47	$\pm$ 0.26 (55~\%)  & 0.027 $\pm$ 0.019 (70~\%) 	&  0.45 $\pm$ 0.31 (69~\%)  	& 0.019 $\pm$ 0.011 (58~\%)\\
-		PUF (3)       		&   Open 		& 0.32	$\pm$ 0.13 (41~\%)  & 0.056 $\pm$ 0.034 (61~\%) 	&  0.36 $\pm$ 0.091 (25~\%)  	& 0.071 $\pm$ 0.023 (32~\%)\\
+		Natural Gas (10)    &   Open 		& 0.74 	$\pm$ 0.15 (20\%)  & 0.061 $\pm$ 0.028 (46\%) 	&  0.78 $\pm$ 0.17 (22\%) 	 	& 0.061 $\pm$ 0.028 (46\%)  	\\
+		Gasoline (10)       &   Open    	& 0.47	$\pm$ 0.26 (55\%)  & 0.027 $\pm$ 0.019 (70\%) 	&  0.45 $\pm$ 0.31 (69\%)  	& 0.019 $\pm$ 0.011 (58\%)\\
+		PUF (3)       		&   Open 		& 0.32	$\pm$ 0.13 (41\%)  & 0.056 $\pm$ 0.034 (61\%) 	&  0.36 $\pm$ 0.091 (25\%)  	& 0.071 $\pm$ 0.023 (32\%)\\
 	\hline
@@
 	\caption[Comparison of corner fire pattern height and area for the three types of burners]{Comparison of corner fire pattern height and area for the three types of burners.
-Values presented with 95~\% confidence limits.}
+Values presented with 95\% confidence limits.}
 	\label{tab:Fire_Pattern_Dimensions_Corners}
@@
 Also comparing these patterns to those generated with the instrumented gypsum wallboard, it did not appear that the instrumentation had any impact that changed the fire pattern.
-With an expanded uncertainty of 2~$\sigma$, the height of the fire patterns were within $\pm$ 18~\% for both the natural gas and the gasoline fuel burner fires.
-The uncertainties regarding the width and area of the patterns were higher up to $\pm$ 33~\%.
+With an expanded uncertainty of 2~$\sigma$, the height of the fire patterns were within $\pm$ 18\% for both the natural gas and the gasoline fuel burner fires.
+The uncertainties regarding the width and area of the patterns were higher up to $\pm$ 33\%.
 While the natural gas and the gasoline are different fuels there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
@@
 
-The polyurethane foam exhibited a higher variability in the fire pattern heights, $\pm$ 50~\%, and areas, $\pm$ 57~\%, due in part to variabilities in fire growth rates, a lower peak heat release rate, and a lower total heat release, than the other two fuels.
+The polyurethane foam exhibited a higher variability in the fire pattern heights, $\pm$ 50\%, and areas, $\pm$ 57\%, due in part to variabilities in fire growth rates, a lower peak heat release rate, and a lower total heat release, than the other two fuels.
 Since the fire patterns generated by the polyurethane fueled burners were shorter and smaller, than the patterns generated by the 80 kW heat release rate fuels, the uncertainty in terms of percentage difference is magnified.
-The positive message is that the repeatability of the patterns qualitatively agree with the repeatability, or lack there of, of the heat release rate of the polyurethane foam burner which was $\pm$ 47~\% during the burner characterization experiments.
+The positive message is that the repeatability of the patterns qualitatively agree with the repeatability, or lack there of, of the heat release rate of the polyurethane foam burner which was $\pm$ 47\% during the burner characterization experiments.
 
@@
 		HRR (kW) &   $\chi_r$   & R (m)	 & Heat Flux (kW/m$^2$)     &  Nat. Gas (kW/m$^2$)      & Gasoline (kW/m$^2$) 	\\ \hline 
-		80    &   .35 		& 0.76 	     & 3.9 $\pm$ 0.4 (11~\%) 	&  4 $\pm$ 0.32 (8~\%) 	 	   & 6 $\pm$ 0.5 (8~\%)     \\
-		80    &   .35    	& 0.46	     & 10.5 $\pm$ 1.2 (11~\%) 	&  11 $\pm$ 0.88 (8~\%)  	   & 18 $\pm$ 1.4 (8~\%)    \\
-		80    &   .35 		& 0.31	     & 23.0 $\pm$ 2.6 (11~\%) 	&  23 $\pm$ 1.8 (8~\%)  	   & 57 $\pm$ 4.6 (8~\%)     \\
-        80    &   .35 		& 0.23	     & 42.0 $\pm$ 4.6 (11~\%) 	&  NA 					  	   & 60 $\pm$ 4.8 (8~\%)     \\
-        80    &   .35 		& 0.15	     & 90.0 $\pm$ 10.9 (11~\%) 	&  55 $\pm$ 4.4 (8~\%)  	   & 61 $\pm$ 4.9 (8~\%)     \\
+		80    &   .35 		& 0.76 	     & 3.9 $\pm$ 0.4 (11\%) 	&  4 $\pm$ 0.32 (8\%) 	 	   & 6 $\pm$ 0.5 (8\%)     \\
+		80    &   .35    	& 0.46	     & 10.5 $\pm$ 1.2 (11\%) 	&  11 $\pm$ 0.88 (8\%)  	   & 18 $\pm$ 1.4 (8\%)    \\
+		80    &   .35 		& 0.31	     & 23.0 $\pm$ 2.6 (11\%) 	&  23 $\pm$ 1.8 (8\%)  	   & 57 $\pm$ 4.6 (8\%)     \\
+        80    &   .35 		& 0.23	     & 42.0 $\pm$ 4.6 (11\%) 	&  NA 					  	   & 60 $\pm$ 4.8 (8\%)     \\
+        80    &   .35 		& 0.15	     & 90.0 $\pm$ 10.9 (11\%) 	&  55 $\pm$ 4.4 (8\%)  	   & 61 $\pm$ 4.9 (8\%)     \\
 	\hline
@@
 	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum board wall experiments.
-Values presented with 95~\% confidence limits based on the estimated uncertainty of HRR and heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
+Values presented with 95\% confidence limits based on the estimated uncertainty of HRR and heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
 	\label{tab:Point_Source_HFNGG}
@@
 		HRR (kW) &   $\chi_r$   & R (m)	     & Heat Flux (kW/m$^2$)     &  Polyurethane (kW/m$^2$)    	\\ \hline 
-		45       &   .35 		& 0.76 	     & 2.2 $\pm$ 0.24 (8~\%) 	&  3.5 $\pm$ 0.28 (8~\%) 	   	 \\
-		45       &   .35    	& 0.46	     & 6.0 $\pm$ 0.65 (8~\%) 	&  12.3 $\pm$ 0.98 (8~\%)  	     \\
-		45       &   .35 		& 0.31	     & 13.1 $\pm$ 1.4 (8~\%) 	&  25 $\pm$ 2.0 (8~\%)   	      \\
-        45       &   .35 		& 0.23	     & 23.7 $\pm$ 2.6 (8~\%) 	&  36 $\pm$ 2.9 (8~\%)		      \\
-        45       &   .35 		& 0.15	     & 55.7 $\pm$ 6.1 (8~\%) 	&  59 $\pm$ 4.7 (8~\%)   	       \\
+		45       &   .35 		& 0.76 	     & 2.2 $\pm$ 0.24 (8\%) 	&  3.5 $\pm$ 0.28 (8\%) 	   	 \\
+		45       &   .35    	& 0.46	     & 6.0 $\pm$ 0.65 (8\%) 	&  12.3 $\pm$ 0.98 (8\%)  	     \\
+		45       &   .35 		& 0.31	     & 13.1 $\pm$ 1.4 (8\%) 	&  25 $\pm$ 2.0 (8\%)   	      \\
+        45       &   .35 		& 0.23	     & 23.7 $\pm$ 2.6 (8\%) 	&  36 $\pm$ 2.9 (8\%)		      \\
+        45       &   .35 		& 0.15	     & 55.7 $\pm$ 6.1 (8\%) 	&  59 $\pm$ 4.7 (8\%)   	       \\
 	\hline
@@
 	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum board wall experiments.
-Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
+Values presented with 95\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
 	\label{tab:Point_Source_HFPUF}
@@
 					& (kW) &  			  & (m)		&  (kW/m$^2$)				&   (kW/m$^2$)                        \\ \hline 
-		Nat. Gas 	& 80       &   .25 	& 0.76 	     & 2.8 $\pm$ 0.30 (11~\%) 				&  4 $\pm$ 0.32 (8~\%) 	   	 \\
-		Nat. Gas 	& 80       &   .25  & 0.46	     & 7.5 $\pm$ 0.83 (11~\%) 				&  11 $\pm$ 0.88 (8~\%)  	     \\
-		Gasoline 	& 80       &   .47 	& 0.76	     & 5.2 $\pm$ 0.57 (11~\%) 				&  6 $\pm$ 0.5 (8~\%)   	      \\
-        Gasoline 	& 80       &   .47 	& 0.46	     & 14.1 $\pm$ 1.6 (11~\%) 				&  18 $\pm$ 1.4 (8~\%)		      \\
-       Polyurethane & 45       &   .33 	& 0.76	     & 2.1 $\pm$ 0.23 (11~\%) 				&  3.5 $\pm$ 0.28 (8~\%)   	       \\
-       Polyurethane & 45       &   .33 	& 0.46	     & 5.6 $\pm$ 0.62 (11~\%) 				& 12.3 $\pm$ 0.98 (8~\%)   	       \\
+		Nat. Gas 	& 80       &   .25 	& 0.76 	     & 2.8 $\pm$ 0.30 (11\%) 				&  4 $\pm$ 0.32 (8\%) 	   	 \\
+		Nat. Gas 	& 80       &   .25  & 0.46	     & 7.5 $\pm$ 0.83 (11\%) 				&  11 $\pm$ 0.88 (8\%)  	     \\
+		Gasoline 	& 80       &   .47 	& 0.76	     & 5.2 $\pm$ 0.57 (11\%) 				&  6 $\pm$ 0.5 (8\%)   	      \\
+        Gasoline 	& 80       &   .47 	& 0.46	     & 14.1 $\pm$ 1.6 (11\%) 				&  18 $\pm$ 1.4 (8\%)		      \\
+       Polyurethane & 45       &   .33 	& 0.76	     & 2.1 $\pm$ 0.23 (11\%) 				&  3.5 $\pm$ 0.28 (8\%)   	       \\
+       Polyurethane & 45       &   .33 	& 0.46	     & 5.6 $\pm$ 0.62 (11\%) 				& 12.3 $\pm$ 0.98 (8\%)   	       \\
 	\hline
@@
 	\caption[Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments.
-Values presented with 95~\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
+Values presented with 95\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
 	\label{tab:Point_Source_ModChir}
@@
 Median flame height has been assessed a number of ways during this study: a manual analysis of a series of photographs, a computational analysis of video segments, and measuring the height of the fire patterns.
-An expanded uncertainty was calculated for each method which resulted in the range of 95~\% confidence limits for each value.
-A range of values was established with the Heskestad flame height calculation by taking the 95~\% certainty limits determined for the average peak heat release rates of the three different fuels in Chapter 2.
+An expanded uncertainty was calculated for each method which resulted in the range of 95\% confidence limits for each value.
+A range of values was established with the Heskestad flame height calculation by taking the 95\% certainty limits determined for the average peak heat release rates of the three different fuels in Chapter 2.
 The range of calculated values for median flame height are compared with the applicable measurements from this study in Table~\ref{tab:Comparing_Flame_Heights}.
@@
                 &       Natural Gas	            &   Gasoline	            & Polyurethane Foam \\ \hline 
-Photographic    &       0.70 $\pm$ 0.23 (33~\%)   &	0.84 $\pm$ 0.28 (33~\%) 	& 0.46 $\pm$ 0.23 (50~\%)   \\
-Video Based     &   	0.70 $\pm$ 0.11 (15~\%)   &	0.70 $\pm$ 0.1 (14~\%) 	& 0.47 $\pm$ 0.16 (34~\%)   \\
-Fire Pattern    &   	0.74 $\pm$ 0.12 (16~\%)   &	0.83 $\pm$ 0.15 (18~\%) 	& 0.24 $\pm$ 0.12 (50~\%)   \\
+Photographic    &       0.70 $\pm$ 0.23 (33\%)   &	0.84 $\pm$ 0.28 (33\%) 	& 0.46 $\pm$ 0.23 (50\%)   \\
+Video Based     &   	0.70 $\pm$ 0.11 (15\%)   &	0.70 $\pm$ 0.1 (14\%) 	& 0.47 $\pm$ 0.16 (34\%)   \\
+Fire Pattern    &   	0.74 $\pm$ 0.12 (16\%)   &	0.83 $\pm$ 0.15 (18\%) 	& 0.24 $\pm$ 0.12 (50\%)   \\
 Heskestad (range)  &   	0.94 to 1.06		    &	0.65 to 0.93        	& 0.36 to 0.72   \\
@@
  \caption[Comparison of the median flame height measurement results with the fire pattern heights and the Heskestad predictions]{Comparison of the median flame height measurement results with the fire pattern heights and the Heskestad predictions.
-The measured results are shown with 95~\% confidence limits.
+The measured results are shown with 95\% confidence limits.
 The Heskestad median flame height calculations are presented as a range based on the uncertainties of the average peak heat release rate of each fuel type.}
@@
 However, the range of calculated median flame height values is significantly different from the measured values.
-Based on the computational flame height assessment, Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10~\% of the time.
+Based on the computational flame height assessment, Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10\% of the time.
 
 For the gasoline fueled fires, the comparison of the median flame height, the average maximum fire pattern height, and the calculated flame height range values are all in agreement.
-This is significant because the 95~\% confidence limits for the fire pattern and the video based flame height are both less than 20~\%.
+This is significant because the 95\% confidence limits for the fire pattern and the video based flame height are both less than 20\%.
 
 The measured and calculated values for the polyurethane fueled burner fires are also in agreement.
-However the agreement in this case is largely the result of the broad 95~\% confidence limits of the range of the average peak heat release rate of the polyurethane foam.
-The burning variation of polyurethane foam resulting in the wide range of flame heights and patterns with 95~\% confidence limits of $\pm$ 50~\%.
+However the agreement in this case is largely the result of the broad 95\% confidence limits of the range of the average peak heat release rate of the polyurethane foam.
+The burning variation of polyurethane foam resulting in the wide range of flame heights and patterns with 95\% confidence limits of $\pm$ 50\%.
 
@@
 It was modeled with a steady state heat release rate flux of 888.89 kW/m$^2$, or a heat release rate of 80~kW.
-The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95~\% methane.
+The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95\% methane.
 In FDS version 6, the default radiant fraction for the `methane' reaction was set to~0.2.
@@
 The RIs included three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).
-The associated 95~\% confidence limits are also shown the temperature value for each height.
+The associated 95\% confidence limits are also shown the temperature value for each height.
 The FDS simulated temperatures based on the course cell size of 80~mm (RI=5) had the best agreement with the temperatures along centerline of the plume.
@@
 To have a value, based on a measurement, for comparison to the HRRPUL the peak visible flame height range estimate was developed.
-The peak visible flame height ranged from the location where the flame existed only 10~\% of the time with the 95~\% certainty range.
+The peak visible flame height ranged from the location where the flame existed only 10\% of the time with the 95\% certainty range.
 The Table~\ref{tab:FDS_FH} displays estimated values from the models using all three RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
@@
 The flame height range was calculated using the HRRPUL from each of the FDS simulations at each position from the wall and for RI=5 and RI=10.
-The peak visible flame height range estimate was developed from the location where the flame exists only 10~\% of the time with the 95~\% certainty range.
+The peak visible flame height range estimate was developed from the location where the flame exists only 10\% of the time with the 95\% certainty range.
 This information is presented in Table~\ref{tab:FDS_FH_IWNG} displays estimated values from the models using two of the RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
@@
 The three images from left to right exhibit a range of fire pattern heights from approximately 0.7 to 0.8~m.
-The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95~\% certainty range of $\pm$~0.12~m.
+The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% certainty range of $\pm$~0.12~m.
 The simulated fire pattern is taller than the actual patterns.
@@
 The peak heights of the char areas were 0.60 and 0.48~m above the burner, respectively.
-These values are below the 95~\% certainty range of the measured fire pattern height, 0.74$\pm$~0.12~m.
+These values are below the 95\% certainty range of the measured fire pattern height, 0.74$\pm$~0.12~m.
 
@@
 The fire patterns generated by the natural gas and gasoline fires had a high level of repeatability.
-The 95~\% certainty range of the peak fire pattern heights, over 30 experiments from each fuel, was within approximately $\pm$0.1~m.
+The 95\% certainty range of the peak fire pattern heights, over 30 experiments from each fuel, was within approximately $\pm$0.1~m.
 The maximum width range of the same experiments was within $\pm$0.07~m.
@@
 The polyurethane patterns where almost triangular in shape and had a height to width ratio of almost 1 to 1.
-As a result the percentage difference between the average peak height of the pattern and range of of 95~\% certainty was approximately 3 times higher that the percentage differences from the natural gas and gasoline fires.
+As a result the percentage difference between the average peak height of the pattern and range of of 95\% certainty was approximately 3 times higher that the percentage differences from the natural gas and gasoline fires.
 
@@
 The median flame height for the gasoline was lower, 0.70~m.
-Examining the visible flame heights determined in Chapter 2, the average peak height of the fire pattern aligns better with the height where the gasoline flame was present for approximately 25~\% of the time.
+Examining the visible flame heights determined in Chapter 2, the average peak height of the fire pattern aligns better with the height where the gasoline flame was present for approximately 25\% of the time.
 The gasoline has a radiant fraction that is about twice as high as the natural gas.
@@
 Figure~\ref{FH_FP_comp} shows the comparisons of the average maximum fire pattern heights with those of the mean flame height based on the analysis of the video images.
-The associated 95~\% confidence limits are also shown for each height.
-For each of the fuels, the 95~\% certainty ranges of the fire pattern heights and flame heights overlap indicating that the values, while not an exact match, are similar.
+The associated 95\% confidence limits are also shown for each height.
+For each of the fuels, the 95\% certainty ranges of the fire pattern heights and flame heights overlap indicating that the values, while not an exact match, are similar.
 
@@
   \caption[Comparisons of the average maximum fire pattern heights compared with the mean flame heights.]{Comparisons of the average maximum fire pattern heights compared with the mean flame heights.
-The associated 95~\% confidence limits are also shown for each height.}
+The associated 95\% confidence limits are also shown for each height.}
   \label{FH_FP_comp}
@@
 A few general thoughts to put the numerical methods in perspective.
-In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95~\% certainty range of $\pm11\%$.
+In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95\% certainty range of $\pm11\%$.
 This range was the same as that associated with the heat release rate measurement system, so this would be the best agreement that we should expect.
-The gasoline and the polyurethane introduced additional variability and the 95~\% certainty ranges on the peak heat release rate values increased to 30~\% and 47~\% respectively.
+The gasoline and the polyurethane introduced additional variability and the 95\% certainty ranges on the peak heat release rate values increased to 30\% and 47\% respectively.
 As the physical variability of the experiments increases what is the expectation of numerical methods which simulate the physical experiments
@@
 
-If needed, you have the dimensions of the house and the opening so you could have a computer model of the house made to examine how long it would take a small fire to decrease the level of the oxygen within the house to 15~\%.
+If needed, you have the dimensions of the house and the opening so you could have a computer model of the house made to examine how long it would take a small fire to decrease the level of the oxygen within the house to 15\%.
 This might be needed to get insight on a time line that you might get from the interviews of the occupants.
@@
 Today, the regular gypsum board has been replaced on store shelves by a less dense version of 12.7~mm thick gypsum wall board.
-A finished lightweight gypsum wall board panel has 30~\% less mass than the regular gypsum wall board that was the de facto construction standard just a few years ago.
+A finished lightweight gypsum wall board panel has 30\% less mass than the regular gypsum wall board that was the de facto construction standard just a few years ago.
 How the lightweight gypsum wall board degrades when exposed to fire has not been quantified.
@@
 The heat release rate data showed that the variability was greater for more complex fuels.
-The variation in the average peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11~\%.
+The variation in the average peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11\%.
 However the variation in the average peak heat release rates of the gasoline and the polyurethane foam increased due to uncertainties in the burning behavior of the fuels.
-The average peak heat release rate of gasoline had a 95~\% confidence limit of $\pm$30~\% and the same value for the polyurethane foam was $\pm$47~\%.
-
-The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18~\% or less based on a Type A statistical analysis with 95~\% confidence limits.
+The average peak heat release rate of gasoline had a 95\% confidence limit of $\pm$30\% and the same value for the polyurethane foam was $\pm$47\%.
+
+The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18\% or less based on a Type A statistical analysis with 95\% confidence limits.
 The patterns generated by the polyurethane foam fueled fire, had more than twice the variability of the natural gas and the gasoline fire patterns.
@@
 The algebra based predictions for heat flux to a target under predicted the measured values.
-The gasoline fueled fires had the best agreement of 22~\% or less for the heat flux predictions.
-The polyurethane foam results exhibited the worst agreement with difference of at least 40~\% between the measured and calculated values.
+The gasoline fueled fires had the best agreement of 22\% or less for the heat flux predictions.
+The polyurethane foam results exhibited the worst agreement with difference of at least 40\% between the measured and calculated values.
 Improved understanding of the radiative fraction from different fuels would improve the capability of the predictions.

### 2017-03-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Replace fig Ch 9   In corporated revised to Ch 1 and 2

@@
 This section reviews the fire problem to demonstrate the need and value to society that fire investigation can provide.
-Following the review, a brief presentation on the analysis  of fire patterns, the use of analytical tools, and the current challenges to the field of fire forensics is given as they are the reason for this study.
+Following the review, a brief presentation on the analysis  of fire patterns, the use of analytical tools, and the current challenges to the field of fire forensics is given because they are the reason for this study.
 At the end of this chapter, an example of a fire incident is presented.
@@
 \subsection{The Need for Fire Investigation}
-Unwanted fires result in loss of life, property, and can create an adverse economic impact on a community.
-Recent findings from an archaeological site in South Africa, indicate that mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
-This is 300 thousand years earlier than previously thought.
-Despite mankind's extensive history with fire, according to the World Health Organization, an estimated 265,000 people die each year as a result of burn injuries~\cite{WHO:2014}.
+Unwanted fires result in loss of life and property, and can create an adverse economic impact on a community.
+Recent findings from an archaeological site in South Africa indicate mankind has productively used fire for approximately 1 million years~\cite{Berna:2012}.
+This is 300,000 years earlier than previously thought.
+Despite mankind's extensive history with fire, according to the World Health Organization an estimated 265,000 people die each year as a result of burn injuries~\cite{WHO:2014}.
 Based on an estimated global population of 7.3 billion people, the death rate due to burns from all sources would be 3.6 per 100,000 people.
-The World Fire Statistics Center collects data from European, North American and a few Asia-Oceania countries.
-Within this group of countries the fire deaths per 100,000 population range from 0.02 (Singapore) to 2.03 (Finland)~\cite{Climate:2014}.
+The World Fire Statistics Center collects data from European, North American, and a few Asia-Oceania countries.
+Within this group of countries the fire deaths per 100,000 people range from 0.02 (Singapore) to 2.03 (Finland)~\cite{Climate:2014}.
 There are a significant number of factors that determine the variability of fire death rates between nations, socio-economic conditions being a leading factor~\cite{WHO:2014}.
@@
 In the United States, the loss of life due to unwanted fire has been decreasing steadily since the 1970’s.
-This trend does not include loss of life as a result of the terrorist attack on September 11, 2001.
-The estimated number of fire deaths in the U.S.
-in 1975 was 8,100, or 3.75 deaths per 100,000 population~\cite{America_Burning_Revisited}.
-In 2013, there were 3,240 civilian fire fatalities, or 1.02 deaths per 100,000 population~\cite{Karter:2014}.
+(This trend does not include loss of life as a result of the terrorist attack on September 11, 2001.)  The estimated number of fire deaths in the U.S.
+in 1975 was 8,100, or 3.75 deaths per 100,000 people~\cite{America_Burning_Revisited}.
+In 2013, there were 3,240 civilian fire fatalities, or 1.02 deaths per 100,000 people~\cite{Karter:2014}.
 During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.
@@
 One example is research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs.
-None of this happened without the constant effort of agencies at the Federal, state, and, local levels working with professional fire organizations in order to deliver the five E’s of fire prevention; Engineering, Education, Enforcement, Economic Incentive, and Emergency Response~\cite{FEMA:2013}.
+None of this happened without the constant effort of agencies at the federal, state, and local levels working with professional fire organizations in order to deliver the five E’s of fire prevention: engineering, education, enforcement, economic Incentive, and emergency Response~\cite{FEMA:2013}.
 
@@
 
-According to the NFPA, there were approximately 282,600 intentionally set fires each year during the period of 2007 through 2011 in the United States.
+According to the NFPA, there were approximately 282,600 intentionally set fires each year from 2007 through 2011 in the United States.
 The average annual loss totals for that period were approximately 420 civilian deaths and 1,360 civilian injuries.
@@
 Approximately two-thirds of the intentional structure fires occurred in occupied and operating residential occupancies.
-As a result, 95\% of the civilian deaths and 86\% of the civilian injuries which are attributed to intentional fires occurred in residential occupancies~\cite{Campbell:2014}.
+As a result, 95\% of the civilian deaths and 86\% of the civilian injuries attributed to intentional fires occurred in residential occupancies~\cite{Campbell:2014}.
 
@@
 Federal Bureau of Investigation (FBI) Uniform Crime Reporting (UCR) Program defines arson as any willful or malicious burning or attempting to burn, with or without intent to defraud, a dwelling house, public building, motor vehicle or aircraft, personal property of another, etc.~\cite{Crime:2010}.
-The national rate of arson fire cases cleared by arrest or exceptional means is less than 20\%.
-Of those cases approximately 46\% of the suspects were prosecuted~\cite{Campbell:2014}.
+The national rate of arson fire cases cleared by arrest or exceptional means was less than 20\%.
+Of those cases, approximately 46\% of the suspects were prosecuted~\cite{Campbell:2014}.
 Hence less than 10\% of the arson cases resulted in successful prosecution.
 
-The statistics cited above are believed to be the best available in the United States, which is perhaps one of the better fire incident databases in the world.
-However, an investigative report by Icove and Hargrove indicates that arson fires are underreported to the U.S.
+The statistics cited above are believed to be the best available in the United States, which maintains perhaps one of the better fire incident databases in the world.
+However, an investigative report by Icove and Hargrove indicates arson fires are underreported to the U.S.
 National Fire Incident Reporting System (NFIRS).
@@
 On average, three-fourths of the arsons uncovered by city fire investigators went unreported to NFIRS~\cite{Icove_2014}.
-In other words, the number of arson related incidents is likely to be under represented in the fire incident data.
+In other words, the number of arson-related incidents is likely to be under represented in the fire incident data.
 
 \subsection{The Use of Fire Patterns in Fire Investigation}
-Fires are investigated in order to determine the ``origin and cause'' of the fire.
+Fires are investigated in order to determine their origin and cause.
 In cases of arson, there is an additional effort to determine who was responsible for setting the fire.
@@
 One of the basic methods of documenting the fire scene is to photograph fire patterns.
-As noted by Icove, DeHaan, and Haynes  ``'the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes…''~\cite{Icove:2013}.
+As noted by Icove, DeHaan, and Haynes,  ``the ability to document and interpret fire patterns accurately is essential to investigators reconstructing fire scenes''~\cite{Icove:2013}.
 A fire pattern is defined in NFPA~921 as, ``the visible or measurable physical change, or identifiable shapes, formed by a fire effect or group of fire effects''~\cite{NFPA:921}.
@@
 \begin{enumerate}
-\item Surface deposits -– no irreversible effect on surface
-\item Surface thermal effects –- physical change such a discoloration or melting
-\item Charring -– evidence of surface burning
-\item Penetration -– charring below the surface
-\item Consumption –- loss of surface material, charring throughout
+\item Surface deposits: no irreversible effect on surface
+\item Surface thermal effects: physical change such as discoloration or melting
+\item Charring: evidence of surface burning
+\item Penetration: charring below the surface
+\item Consumption: loss of surface material, charring throughout
 \end{enumerate}
+
 Lentini points out that most fire patterns are generated and later observed on two-dimensional surfaces at the place where those surfaces intersect with the three-dimensional fire.
-Various types of fire patterns, such as; ``V-shaped'', ``hour-glass'', and ``inverted cone'', have come from common observation at actual fire scenes~\cite{Lentini:2006}.
+Various types of fire patterns, such as V-shaped, hour-glass, and inverted cone, have come from common observation at actual fire scenes~\cite{Lentini:2006}.
 As a result, the observations are typically qualitative in nature.
@@
 A large number of other factors affect the formation of these patterns: burn time, heat release rate of the fire source, fire exposure, target fuel composition, adjacent fuel(s), and compartmentalization, to name a few.
-Given the limited number of experiments in the literature and the large number of variables, it has been difficult to develop a cause and effect relationship between the fire scenarios and the resulting patterns, based solely on the research.
+Given the limited number of experiments in the literature and the large number of variables, it has been difficult to identify a cause and effect relationship between fire scenarios and the resulting patterns, based solely on the research.
 
 \subsection{The Use of Fire Models in Fire Investigation}
-Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigator’s hypothesis on origin and cause~\cite{Sutula:2001}.
+Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigators' hypothesis on origin and cause~\cite{Sutula:2001}.
 Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
@@
 More than 45 experimental data sets are used to quantify the prediction capabilities of the model.
-Results are presented in terms of model bias and variation to inform users of whether particular quantities (temperature, heat flux, pressure, etc.) are over or under predicted compared to experimental data.
-
-In order for fire models to be demonstrated as reliable and suitable for use in court, studies such as the one conducted here need to be conducted to provide the scientific basis for the use of fire models for re-construction.
+Results are presented in terms of model bias and variation to inform users of whether particular quantities (temperature, heat flux, pressure, etc.) are over- or under-predicted compared to experimental data.
+
+In order for fire models to be demonstrated as reliable and suitable for use in court, studies such as the one conducted here must be conducted to provide the scientific basis for the use of fire models for re-construction.
 These research results may enable fire investigation teams to have a better understanding of the fire scene and enable improved support of their hypothesis on the area of origin based on fire patterns.
@@
 
-Since fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
+Because fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
 Gorbett recently conducted a review of fire pattern research that has been conducted over the last 80 years.
 The review points out many gaps, especially with how fire patterns are used to determine the area of origin.
-A key limitation is the assumption by many of the researchers, or text authors, that investigators are able to visibly assess varying degrees of fire damage and then determine the area of origin~\cite{Gorbett_2015}.
+A key limitation is the assumption by many of the researchers and text authors that investigators are able to visibly assess varying degrees of fire damage and then determine the area of origin~\cite{Gorbett_2015}.
 Studies have shown that investigators have not been able to use only the location of the fire patterns as means of reliably determining the area of origin.
@@
 As provided by the document scope, it ``is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.'' The document’s purpose includes the goal to be ``a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.'' However, NFPA~921 can only incorporate the fire science and research results that have been produced.
-Although NFPA~921 is a ``guide'' as opposed to a ``standard,'' it is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
-
-As the result of the review of several arson cases, most notably the cases of Ernest Ray Willis and Cameron Todd Willingham, the practice of fire investigation as a forensic science was called into question.
+Although NFPA~921 is a guide as opposed to a standard, it is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
+
+As a result of the review of several arson cases, most notably the cases of Ernest Ray Willis and Cameron Todd Willingham, the practice of fire investigation as a forensic science was called into question.
 Beyler conducted a review of both cases for the Texas Forensic Science Commission~\cite{Beyler:2009}.
 Both fires occurred prior to the release of NFPA~921 in 1992.
-The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980 {\textendash} 1992.'' The fire investigators had a poor understanding of science and their findings of arson could not be sustained~\cite{Beyler:2009}.
+The Beyler analysis, issued in August of 2009, concluded that the investigations of both cases ``did not comport with either the modern standard of care expressed by NFPA 921, or the standard of care expressed by fire investigation texts and papers in the period 1980{\textendash}1992.'' The fire investigators had a poor understanding of science, and their findings of arson could not be sustained~\cite{Beyler:2009}.
 
@@
 The review of the analysis of explosives evidence and fire debris is covered in three pages of the report.
-The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry~''~\cite{Forensic:2009}.
-The complete summary assessment for fire debris analysis is included here: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
+The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry''~\cite{Forensic:2009}.
+The complete summary assessment for fire debris analysis states: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
 Despite the paucity of research, some arson investigators continue to make determinations about whether or not a particular fire was set.
-However, according to testimony presented to the committee, many of the rules of thumb, that were typically assumed to indicate that an accelerant was used (e.g.
-``alligatoring'' of wood, specific char patterns) have been shown not to be true.
-Experiments should be designed to put arson investigations on a more solid scientific footing .''
+However, according to testimony presented to the committee, many of the rules of thumb that were typically assumed to indicate that an accelerant was used (e.g., alligatoring of wood, specific char patterns) have been shown not to be true.
+Experiments should be designed to put arson investigations on a more solid scientific footing.''
 This study is in response to the assessment above, specifically regarding the natural variability of fire patterns.
@@
 
-The majority of intentional fires in structures have occurred in residential occupancies, therefore this study focused on fire patterns on painted gypsum wallboard which is a common interior finish for residential occupancies.
+The majority of intentional fires in structures have occurred in residential occupancies, so this study focused on fire patterns on painted gypsum wallboard, which is a common interior finish for residential occupancies.
 A common height for a residential occupancies is 2.4~m.
 With a wall height of 2.4~m, these experiments used small fires with flame heights of approximately 1.2~m.
-The resulting patterns on the gypsum board wall would be representative of a pre-flashover fire pattern.
+The resulting patterns on the gypsum board wall were be representative of a pre-flashover fire pattern.
 
@@
 Replicate experiments exposing gypsum wallboard to the fires were conducted in order to examine the repeatability of the fire patterns.
-Correlations between the fire characteristics and the fire patterns were be examined.
-
-The last component of this study examines the capability of using numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, as well as bench scale and full scale fire experiments conducted in this study.
+Correlations between the fire characteristics and the fire patterns were examined.
+
+The last component of this study examined the capability of using numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, as well as bench scale and full scale fire experiments conducted in this study.
 
@@
 
-This study includes several series of real-scale, replicate fire experiments to examine the repeatability of pre-flashover fire patterns and, ultimately, examine the ability of simple correlations and the Fire Dynamic Simulator to recreate characteristics of the fire patterns.
+This study included several series of real-scale, replicate fire experiments to examine the repeatability of pre-flashover fire patterns and, ultimately, examine the ability of simple correlations and the Fire Dynamic Simulator to recreate characteristics of the fire patterns.
 
@@
 Several methods of imaging were used for these experiments: still photography, digital video, and infrared video.
-Computer based imaging techniques, such as those contained in the Image Stream program suite, were examined and adapted to analyze the flame height of the source fires~\cite{Nokes:2011}.
+Computer-based imaging techniques, such as those contained in the Image Stream program suite, were examined and adapted to analyze the flame height of the source fires~\cite{Nokes:2011}.
 
@@
 The analysis ensured that the appropriate number of replicate experiments were conducted to provide an assessment of burn pattern repeatability within a given level of uncertainty.
-Since the coefficient of variation (COV) may be different for a given type of experiment, the number of replicates required would be larger for experiments with a larger COV in order obtain a valid assessment of repeatability.
+Because the coefficient of variation (COV) may be different for a given type of experiment, the number of replicates required would be larger for experiments with a larger COV in order obtain a valid assessment of repeatability.
 
@@
 
-The fires were characterized in terms of heat release rate, mass loss rate, fire plume temperatures and emitted heat flux.
+The fires were characterized in terms of heat release rate, mass loss rate, fire plume temperatures, and emitted heat flux.
 Videos were recorded for each experiment.
@@
 
-A free standing, steel frame with non-combustible, calcium silicate faced wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing, steel frame with a non-combustible, calcium silicate-faced wall was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 The fires were initially placed at predetermined, fixed positions away from the wall.
-The burner was moved closer toward the wall until the burner was against the wall.
+The burner was then moved toward the wall until the burner was against the wall.
 
@@
 The fires were initially placed at predetermined, fixed positions away from the wall.
-The burner was moved closer toward the wall until the burner was against the wall.
+The burner was then moved toward the wall until the burner was against the wall.
 If the results indicated that no burn pattern would result from a given combination of fuel and position, then that fuel and position combination were eliminated from the remainder of the test matrix.
@@
 Three different types of wall construction were examined to determine if the amount of insulation behind the exposed gypsum wallboard changed the fire pattern by a significant amount.
-The results would then be used to plan the wall construction of the remaining full- scale experiments.
+The results were used to plan the wall construction of the remaining full- scale experiments.
 
@@
 
-A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a ``critical heat flux'' that results in a clear line of demarcation, a ``burn/no burn'' line.
+A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a critical heat flux that results in a clear line of demarcation, a burn/no burn line.
 The flooring radiant panel, ASTM~E 648, and a modified radiant panel apparatus based on ASTM~E 162 were used to examine this value~\cite{ASTM_E648},~\cite{ASTM_E162}.
@@
 
-Cone calorimeter experiments were conducted, based on ASTM~E 1354, to estimate the ignition temperature, the time to ignition and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
+Cone calorimeter experiments were conducted, based on ASTM~E 1354, to estimate the ignition temperature, the time to ignition, and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
 
@@
 The ability to recreate or simulate a fire pattern or certain characteristics of a fire pattern was examined with a variety of tools.
-The first characteristic examined was the ability to determine, based on the calculated heat flux to the wall, if a ``visible or measurable physical change'' would occur to the painted paper surface of the gypsum wallboard.
-The next characteristic of the fire pattern that was examined was the height.
+The first characteristic examined was the ability to determine, based on the calculated heat flux to the wall, if a visible or measurable physical change would occur to the painted paper surface of the gypsum wallboard.
+The next characteristic of the fire pattern examined was the height.
 The height of the fire pattern was then compared to the predictive results from flame height correlations.
-Heskestad developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion~\cite{Beyler:1986,Heskestad:SFPE}.
+Heskestad developed an empirical method for calculating the mean visible flame height for fuels that do not have substantial in-depth combustion~\cite{Beyler:1986,Heskestad:SFPE}.
 This correlation was compared with the flame height results of the source fires and the instrumented wall experiments.
@@
 These simulation tools provide results in the form of visual field data.
-In other words they provide results in the same format that the investigator would see or document the fire pattern.
+In other words, they provide results in the same format an investigator would see or use to document the fire pattern.
 Comparison between the experiments and the model provide valuable validation data for the model.
@@
 The key measurements for repeatability of the fire patterns on the gypsum wallboard are height, maximum width, shape, and area.
-The two significant outcomes will be the repeatability of the fire patterns themselves and the ability to numerically recreate key measures of the pattern.
+The two significant outcomes would be the repeatability of the fire patterns themselves, and the ability to numerically recreate key measures of the pattern.
 
@@
 N.B.
-This section may be considered atypical for an engineering thesis but it is included here for two reasons.
-Firstly, to provide a narrative description for readers that may be unfamiliar with how fire patterns are routinely relied on in fire investigations.
-The second is to put this work into an applied context that is familiar to fire investigators that may be unaccustomed to reading detailed research as found in this thesis.
+This section may be considered atypical for an engineering thesis, but it is included here for two reasons.
+First, to provide a narrative description for readers that may be unfamiliar with how fire patterns are routinely relied on in fire investigations.
+Second, is to put this work into an applied context that is familiar to fire investigators who may be unaccustomed to reading detailed research.
 
 For the moment let's step into the shoes of a fire investigator and examine a potential investigation scenario.
-It is 8:30 on a cool fall morning and you are being called to a fire scene.
+It is 8:30 on a cool fall morning and you are called to a fire scene.
 As you prepare to leave for the fire scene, you begin to collect information on the fire as you listen to your department radio.
@@
 The fire occurred in area of older town homes.
-The socio-economics of the neighborhood are such that the people that live there have many life struggles.
-En route you learn that the fire department rescued a mother and child from the home and they are being transported to the hospital.
+The socio-economics of the neighborhood are such that the people who live there have many life struggles.
+En route you learn the fire department rescued a mother and child from the home and that they are being transported to the hospital.
 The husband and father also lives at that address but is unaccounted for at this time.
-Upon arrival you have a conversation with the police and fire officers on the scene.
-You are provided with information regarding what the first firefighters saw on the scene; ``all of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
+Upon arrival you have a conversation with the police and fire officers on scene.
+You are provided with information regarding what the first firefighters saw on scene: ``All of the doors and windows were closed, and smoke was leaking from around the front door and living room window.
 The front door was forced and a hose stream was applied to the fire in the living room.
@@
 The mother and child were rescued from a bedroom upstairs.'' You thank the fire officer and get contact information for a follow-up if necessary.
-As you wait for the fire department to complete their operations inside, the police on scene let you know that the address is familiar to them for domestic disturbance calls for the husband and wife fighting but no charges have been filed.
+As you wait for the fire department to complete their operations inside, the police on scene let you know the address is familiar to them for domestic disturbance calls for the husband and wife fighting, but no charges have been filed.
 They are looking for the husband and have sent a patrol car to his place of work.
@@
 You notice that three of the four windows on the second floor have been removed.
-On ``side D'' of the town home there are no openings and no smoke or fire damage is present.
-On the rear or ``side C'' of the house the door and windows are intact but open.
+On side D of the town home, there are no openings and no smoke or fire damage is present.
+On the rear or side C of the house, the door and windows are intact but open.
 There are no smoke stains and no thermal damage around any of the openings on the rear.
@@
 
-You take some notes and photograph the exterior of the structure, the fire department is repacking their equipment and are preparing to leave when you enter through the front doorway.
+You take some notes and photograph the exterior of the structure.
+The fire department is repacking their equipment and is preparing to leave when you enter through the front doorway.
 The living room has extensive fire damage, as shown in Figure~\ref{EXT_INTLR}.
@@
 This may be an indicator that the origin of the fire is closer to the front of the living room.
-Between the two wood cabinets on the ``D wall'' of the living room there is a wood framed sofa.
-The cushions have thermal damage, from pyrolysis.
-It is not clear that they were on fire as there is no thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
+Between the two wood cabinets on the D wall of the living room there is a wood framed sofa.
+The cushions show thermal damage from pyrolysis.
+It is not clear that they were on fire because there is no thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
 Still standing in the entry doorway, you turn your attention to the remains of an upholstered sofa and chair.
@@
 There is smoke damage in the upstairs hallway and in the front bedrooms.
-The further you move from the stairs the less thermal damage you find.
-
-You head back down the stairs to further examine the living room which appears to be the room of fire origin.
-Your are focusing on the area with the most damage, the area with the sofa and chair.
-You think that this may be the area of origin.
-
-As you are looking toward the ``B wall'' of the living room you note that the right side of the chair is badly burned and it is burned from the floor level up.
+The further you move from the stairs, the less thermal damage you find.
+
+You head back down the stairs to further examine the living room, which appears to be the room of fire origin.
+Your focus on the area with the most damage, the area with the sofa and chair.
+You think this may be the area of origin.
+
+As you look toward the B wall of the living room, you note that the right side of the chair is badly burned, and burned from the floor level up.
 The same is true from the left side of the sofa.
-In fact, the left side of the sofa has more fire damage to the wood frame of the sofa than the right side of the sofa frame.
-The corner formed by the wall behind the chair and the wall of the stairway has a ``V pattern'' burned into it, from the floor and extending up toward the ceiling.
+In fact, the left side of the sofa has more fire damage to its wood frame than the right side.
+The corner formed by the wall behind the chair and the wall of the stairway has a V pattern burned into it from the floor and extending up toward the ceiling.
 As you look at the debris surrounding the chair, you notice the remains of an electric heater.
@@
 The char on the legs of the coffee table is very directional and consistent with the heat coming from the corner.
-Looking at the inside area of the sofa, you see that there is charred wood on the inside surface of the sofa frame while the outer portions of the wood frame are not charred.
-This would indicate that the fire was inside the sofa at some point.
+Looking at the inside area of the sofa, you see there is charred wood on the inside surface of the sofa frame while the outer portions of the wood frame are not charred.
+This would indicate the fire was inside the sofa at some point.
 Further, it appears that all of the foam cushioning is burnt off of the right side of the sofa, while there is a piece of polyurethane foam cushion on the left side of the sofa.
@@
 
-The chair has more unburned foam cushioning then the sofa does and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not been moved.
+The chair has more unburned foam cushioning then the sofa does, and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not been moved.
 The cushion was heated from the top down.
 Perhaps the construction of the chair slowed the flame spread through the chair from the bottom up, if the heater was the ignition source.
-Or the fire started in the sofa and the radiation from the flames and hot gas layer spread the fire to the chair  The heater still looks good as a source however now you have some fire damage that may not be consistent with the heater as the origin.
-Besides interviews what else can you do to eliminate the inconsistencies?
+Or the fire started in the sofa and the radiation from the flames and hot gas layer spread the fire to the chair.
+
+The heater still looks good as a source, but now you have some fire damage that may not be consistent with the heater as the origin.
+Besides interviews, what else can you do to eliminate the inconsistencies?
+
 The fire investigators' challenge will be reexamined in Chapter IX.
@@
 	\caption[Photographs of the exterior and interior of a townhouse post fire]{Photographs of the exterior and interior of a townhouse post fire.
-The three interior photos show the right side wall of the living room (Side D), the back wall of the living room (Side C), and the front wall of the living room (Side A).}
+The three interior photos show the right side wall of the living room (side D), the back wall of the living room (side C), and the front wall of the living room (side A).}
 	\label{EXT_INTLR}
@@
 		\includegraphics[width=2.5in]{../Figures/Table}\\
-	\caption[Photographs of the some of the details of the living room fire area]{Photographs of the some of the details of the living room fire area including the V pattern, heater behind the chair and sofa, the varied thermal damage on the sofa, and the thermal damage to the coffee table and the interior of the sofa frame.}
+	\caption[Photographs of the some of the details of the living room fire area.]{Photographs of the some of the details of the living room fire area,including the V pattern, the heater behind the chair and sofa, the varied thermal damage on the sofa, and the thermal damage to the coffee table and the interior of the sofa frame.}
 	\label{EXT_LRDetails}
@@
   \centering
-  \includegraphics[width=5.0in]{../Figures/FH_FP_Comp}  \\
+  \includegraphics[width=5.0in]{../Figures/FH_FP_Comp1}  \\
   \caption[Comparisons of the average maximum fire pattern heights compared with the mean flame heights.]{Comparisons of the average maximum fire pattern heights compared with the mean flame heights.

### 2017-03-28 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Added new summary tables to Ch 8

@@
 
+\begin{table}[h]
+  \small
+  \centering
+  \begin{tabular}{|c|c|c|c|} \hline 
+Char Criteria 					&  \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	  	  \\
+\hline								&  RI=5					&  RI=10			&  RI=20            \\
+\hline Tign=360~$^\circ~C$  	&  0.72					&  1.04				&	0.86			    \\
+\hline Tign=515~$^\circ~C$		&  0.48					&  0.72				&   0.62                \\
+\hline Tign=565~$^\circ~C$		&  na					&  na				&   na                  \\ 
+\hline  CHF=15.0~kW/m$^2$		&  1.36     			& 1.44 		        &   1.40                \\
+\hline  CHF=17.5~kW/m$^2$		&  1.12					& 1.40				&   1.40                \\
+\hline  CHF=20.0~kW/m$^2$		&  1.04					& 1.36				&   1.36                \\
+\hline	CHF=25.~kW/m$^2$		&  0.88					& 1.28				&   1.26 	            \\
+\hline  CHF=30.0~kW/m$^2$   	&  0.80					& 1.12				&   1.16			    \\  \hline
+  \end{tabular}
+  \caption[Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner compartment wall experiments.]{Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner against the compartment wall experiments.
+Values from three plume resolution indexes (RI) are shown.
+The measured value for the peak fire pattern height was  0.74~$\pm$~0.12.
+na indicates that the value was not reached on the wall in the simulation.}
+  \label{tab:FDS_IGNT_CHF_Wall}
+\end{table}
+
+\begin{table}[h]
+  \small
+  \centering
+  \begin{tabular}{|c|c|c|c|} \hline 
+Char Criteria 					& \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	\\
+\hline								&  RI=5					&  RI=10			&  RI=20            \\
+\hline Tign=360~$^\circ~C$  	&  1.60					&  1.56				&  1.56				    \\
+\hline Tign=515~$^\circ~C$		&  1.04					&  0.96				&  0.96                 \\
+\hline Tign=565~$^\circ~C$		&  0.72					&  na				&  na                   \\
+\hline  CHF=15.0~kW/m$^2$		&  2.08    				&  1.84		        &  1.94                 \\
+\hline  CHF=17.5~kW/m$^2$		&  2.00					&  1.80				&  1.90                 \\
+\hline  CHF=20.0~kW/m$^2$		&  1.92					&  1.76				&  1.86	                \\
+\hline	CHF=25.~kW/m$^2$		&  1.76     			&  1.68				&  1.80	                \\
+\hline  CHF=30.0~kW/m$^2$   	&  1.44 				&  1.60				&  1.60   				\\  \hline
+  \end{tabular}
+  \caption[Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner compartment corner experiments.]{Ignition temperature and heat flux based estimations of the peak fire pattern height from the FDS simulations of the natural gas burner against the compartment corner experiments.
+Values from three plume resolution indexes (RI) are shown.
+The measured value for the peak fire pattern height was  0.74~$\pm$~0.13.
+na indicates that the value was not reached on the wall in the simulation.}
+  \label{tab:FDS_IGNT_CHF_Corner}
+\end{table}
+
 \subsection{Summary}

### 2017-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Jed comments incorporated Abstract through Ch 4

@@
 
-A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover, or early growth stage, fires.
-A fixed fire source footprint, 30.5~cm square, was chosen for this study and a range of common fuels that could be found in and around a residence were selected.
+A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover/early growth stage fires.
+A fixed fire source footprint, 30.5~cm square, was chosen for this study, and a range of common fuels that could be found in and around a residence were selected.
 The fires were positioned under an oxygen consumption calorimetry hood to determine the heat release rate.
@@
 Given the focus on residential fires, small source fires were selected so that the burn pattern would be limited to less than 2.4~m in height.
-Replicate experiments were conducted with each of the fuels, in order to examine the repeatability of the fires and to quantify the variability in the flames.
+Replicate experiments were conducted with each of the fuels in order to examine the repeatability of the fires and to quantify the variability in the flames.
 
@@
 Experiments were conducted with a natural gas fueled burner, a liquid fueled pan fire, and a solid fuel.
-Natural gas was chosen as a fuel for two reasons; it is a common fuel used for heating homes and it is used for calibrating the oxygen depletion calorimeters in NIST’s Large Fire Laboratory.
-Therefore the heat content of the gas was monitored and mass flow controlled to provide a heat release rate based on fuel mass flow for comparison with the heat release rate values measured with the calorimeter.
-The gas burner arrangement provided the most idealized fire, in that it could be ignited and brought up to a near steady state heat release rate within a few seconds and then be shut down just as quickly.
-This provided an approximate `square wave' exposure to the gypsum wallboard.
+Natural gas was chosen as a fuel for two reasons.
+It is a common fuel used for heating homes, and it is used for calibrating the oxygen depletion calorimeters in NIST's Large Fire Laboratory.
+Therefore, the heat content of the gas was monitored and mass flow controlled to provide a heat release rate based on fuel mass flow for comparison with the heat release rate values measured with the calorimeter.
+The gas burner arrangement provided the most idealized fire, in that it could be ignited and brought up to a near steady state heat release rate within a few seconds, and then be shut down just as quickly.
+This provided an approximate square wave exposure to the gypsum wallboard.
 This is important for determining the potential amount of energy transferred to the exposed surface.
 
-The natural gas burner measured 30.5~cm on each side and the top surface of the burner was elevated 7.5~cm above the floor.
-The shell of the burner was made from steel and was filled with ``pea sized'' gravel with an average diameter of 6~mm.
+The natural gas burner measured 30.5~cm on each side, and the top surface of the burner was elevated 7.5~cm above the floor.
+The shell of the burner was made from steel and was filled with pea-sized gravel with an average diameter of 6~mm.
 A steady state heat release rate of approximately 80 kW was used for the experiments.
@@
 Flexible polyurethane foam was chosen as the solid fuel.
-According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishing and mattresses.
+According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishings and mattresses.
 More than 1.2 billion pounds are produced in the U.S.
@@
 Each block of foam was 30.5~cm on each side and was 7.5~cm thick.
-The bottom and sides of the foam block were wrapped in aluminum foil to prevent the fuel from flowing or spreading as it burned to ensure that the fuel area remained with the same fixed area as the gasoline and natural gas.
+The bottom and sides of the foam block were wrapped in aluminum foil to prevent the fuel from flowing or spreading as it burned to ensure that the fuel area remained within the same fixed area as the gasoline and natural gas.
 
@@
 
-The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory's 3~m by 3~m hood oxygen consumption calorimeter.
+The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory's 3~m x 3~m hood oxygen consumption calorimeter.
 This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests} ~\cite{ASTM_E2067}.
-The fires were centered under the hood of the calorimeter and positioned in an open steel frame which provided support for the thermocouples and heat flux sensors.
+The fires were centered under the hood of the calorimeter and positioned in an open steel frame, which provided support for the thermocouples and heat flux sensors.
 A load cell was positioned on the floor as a support for the fuels.
-All of the data was recorded at intervals of 1~s on a computer based data acquisition system.
+All of the data was recorded at intervals of 1~s on a computer-based data acquisition system.
 
@@
 
-The NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter had an estimated peak heat release rate capacity of approximately 700~kW.
-Details on the operation and uncertainty in measurements associated with NIST’s 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
+The NIST Large Fire Research Laboratory's 3~m x 3~m oxygen depletion calorimeter had an estimated peak heat release rate capacity of approximately 700~kW.
+Details on the operation and uncertainty in measurements associated with NIST's 6~m x 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
 Many of the same instruments were shared between the two calorimeters and calibration burns were conducted during each experimental series.
@@
 The thermocouple was ungrounded.
-The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer.
+The standard uncertainty in temperature of the thermocouple wire itself is 2.2$^\circ$C at 277$^\circ$C and increases to 9.5$^\circ$C at 871$^\circ$C as determined by the wire manufacturer.
 The response time constant is approximately 0.2~seconds~\cite{Omega}.
@@
 Each camera was positioned on a tripod with a distance of 4.5~m between the centerline of burner to camera lens.
-The height of each camera was adjusted so that the center of camera lens was positioned 0.5~m above top of the burner.
+The height of each camera was adjusted so that the center of camera lens was positioned 0.5~m above the top of the burner.
 
@@
   \includegraphics[width=\textwidth]{../Figures/Schematic_Drawing}\\
-  \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus which was centered under the 3~m by 3~m oxygen consumption calorimeter.
+  \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus, which was centered under the 3~m x 3~m oxygen consumption calorimeter.
 The heat flux gauges were facing toward the center of the burner/fuel area.}
@@
   \includegraphics[width=\textwidth]{../Figures/Source_Fire_Flamer}\\
-  \caption[A photograph of the source fire flame and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.
-In the foreground, from left to right, are the video, 35~mm SLR and thermal imaging camera.}
+  \caption[A photograph of the source fire flame and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus, which was centered under the 3~m x 3~m hood of the oxygen consumption calorimeter.
+In the foreground from left to right are the video, 35~mm SLR, and thermal imaging cameras.}
   \label{Fire_Flamer}
@@
 
-Figures~\ref{HRR}-\ref{HRR2} show the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires.
+Figures~\ref{HRR} and \ref{HRR2} show the measured heat release rates for the natural gas, gasoline and polyurethane foam fueled fires.
 In each graph, the replicate heat release time histories are overlaid to give a sense of the experimental repeatability for each fuel.
@@
 
-On the averaged heat release rate curve for each fuel, the shaded area surrounding the average represents the 95\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty is provided~\cite{Taylor:1994}.
+On the averaged heat release rate curve for each fuel, the shaded area surrounding the average represents the 95\% confidence level (2$\sigma$), based on Type A evaluation of the uncertainty~\cite{Taylor:1994}.
 A Type A evaluation of the uncertainty is any statistical analysis of the data from a series of observations.
-In this case the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95\%.
+In this case, the evaluation assumed a normal distribution of the data such that doubling the calculated standard deviation (2$\sigma$) would yield a confidence level of approximately 95\%.
 
@@
 The uncertainty of the steady state heat release rate measurement is approximately~$\pm$~11\% It should be noted that 11\% is also the (2$\sigma$) uncertainty estimate of the calorimeter.
-The gas burner and on/off control valve allowed the heat release rate to be similar in form to a ``square-wave''.
-
-The gasoline pan fire was ignited and then burned until the fuel was consumed.
-Therefore the heat release rate curves had more of a ``bell shape''  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
-Therefore the  gasoline average peak heat release rate was based on an average over a 30 s interval bounding the peak heat release rate of each of the 18 experiments.
-This method provided an average peak heat release rate of 80~kW~$\pm$~24~kW or 30\%.
-The total heat release of the gasoline over the 300~s period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
+The gas burner and on/off control valve allowed the heat release rate to be similar in form to a square-wave.
+
+The gasoline pan fire was ignited and then burned until all the fuel was consumed.
+This produced heat release rate curves with more of a bell shape  as opposed to the flat steady- state peak heat release rate region of the natural gas burner.
+Therefore, the  gasoline average peak heat release rate was based on an average over a 30 second interval bounding the peak heat release rate of each of the 18 experiments.
+This method provided an average peak heat release rate of 80~kW~$\pm$~24~kW, or 30\%.
+The total heat release of the gasoline over the 300~seconds period after ignition was 13.6~MJ~$\pm$~0.6~MJ.
 
 The block of polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Similar to the gasoline that began with a fixed quantity of fuel which was ignited and burned to completion, the polyurethane foam also generated ``bell shaped'' heat release rate curve.
-Since the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~s interval bounding the peak heat release rate from each of the ten experiments.
-This process yielded an average peak heat release rate of 45~kW~$\pm$~21~kW or 47\%.
-The total heat release over the 300~s period after ignition was 4.1~MJ~$\pm$~0.2~MJ.
-
-The Figures~\ref{HRR}-\ref{HRR2} have a shaded area that shows the 95\% confidence level.
+Similar to the gasoline that began with a fixed quantity of fuel which was ignited and burned to completion, the polyurethane foam also generated bell shaped heat release rate curve.
+Because the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~second interval bounding the peak heat release rate from each of the 10 experiments.
+This process yielded an average peak heat release rate of 45~kW~$\pm$~21~kW, or 47\%.
+The total heat release over the 300~second period after ignition was 4.1~MJ~$\pm$~0.2~MJ.
+
+The Figures~\ref{HRR} and \ref{HRR2} have a shaded area that shows the 95\% confidence level.
 The more narrow the shaded area, the better the repeatability of the fire.
 This provides a quick means to assess the repeatability of a given source fire.
-Using this measure the natural gas burner fires were the most repeatable, followed by the gasoline pan fires and then the polyurethane fires.
+Using this measure, the natural gas burner fires were the most repeatable, followed by the gasoline pan fires and then the polyurethane fires.
 
@@
 Plots of the centerline temperatures averaged over the full set of replicate experiments for each of the fuels are presented in Fig.~\ref{Temp}.
-The natural gas temperatures are averaged over a ``steady-state'' burning period.
+The natural gas temperatures are averaged over a steady state burning period.
 The temperature differences between the vertical thermocouple locations, for locations greater than 20~cm above the fire location, begin to decrease as the distances from the top of the burner increase.
@@
   \includegraphics[width=.625\columnwidth]{../Figures/FHPUF_TC_Plume_Avg}\\
-  \caption[Averaged centerline temperature for the natural gas, gasoline, and foam fires]{Averaged centerline temperature for the natural gas, gasoline, and foam fires.
+  \caption[Averaged centerline temperatures for the natural gas, gasoline, and foam fires]{Averaged centerline temperatures for the natural gas, gasoline, and foam fires.
 The number following the TC represents the height of thermocouple in decimeters above the surface of the burner.}
@@
 Plots of the total heat flux for each of the fuels are presented in Fig.~\ref{Flux}.
-The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that has periods of growth and decay.
+The repeatability of the total heat flux values varied in a manner similar to the heat release rates, in that the natural gas fires provided a steady state value while the gasoline and the polyurethane foam fires generated a fire curve that features periods of growth and decay.
 The average peak total heat flux for the natural gas fires were approximately 2.0~kW/m$^2$.
-The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$ respectively.
-The values in Fig.~\ref{Flux} are only presented for the experiments which had two heat flux gauges installed at 0.95~m from the centerline of the burners and 0.5~m above the top edge of the burners.
-
-In the initial set of heat release rate experiments another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~m above the top of the burners.
-At this location the average peak total heat flux measured for the natural gas fires was approximately 0.42~kW/m$^2$.
-The average peak values for the gasoline and polyurethane foam were approximately 0.74~kW/m$^2$ and 0.30~kW/m$^2$ respectively.
-Graphs of the heat flux time histories from the 2~m position are given in Figure~\ref{Flux_2m}
+The average peak values for the gasoline and polyurethane foam were approximately 3.5~kW/m$^2$ and 2.5~kW/m$^2$, respectively.
+The values in Fig.~\ref{Flux} are only presented for the experiments that had two heat flux gauges installed at 0.95~m from the centerline of the burners and 0.5~m above the top edge of the burners.
+
+In the initial set of heat release rate experiments, another heat flux gauge was used to measure the total heat flux at a location 2~m from the vertical centerline of the burners and 0.5~m above the top of the burners.
+At this location, the average peak total heat flux measured for the natural gas fires was approximately 0.42~kW/m$^2$.
+The average peak values for the gasoline and polyurethane foam were approximately 0.74~kW/m$^2$ and 0.30~kW/m$^2$, respectively.
+Graphs of the heat flux time histories from the 2~m position are given in Figure~\ref{Flux_2m}.
 
@@
   \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF}\\
-  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires at 0.95~m]{Total heat flux versus time for natural gas, gasoline, and foam fires at a position 0.95~m from the vertical centerline of the burner.}
+  \caption[Total heat flux vs.
+time for natural gas, gasoline, and foam fires at 0.95~m]{Total heat flux vs.
+time for natural gas, gasoline, and foam fires at a position 0.95~m from the vertical centerline of the burner.}
   \label{Flux}
@@
   \includegraphics[width=.635\columnwidth]{../Figures/HF_PUF_2m}\\
-  \caption[Total heat flux versus time for natural gas, gasoline, and foam fires at 2~m]{Total heat flux versus time for natural gas, gasoline, and foam fires at a position 2~m from the vertical centerline of the burner.}
+  \caption[Total heat flux vs.
+time for natural gas, gasoline, and foam fires at 2~m]{Total heat flux vs.
+time for natural gas, gasoline, and foam fires at a position 2~m from the vertical centerline of the burner.}
   \label{Flux_2m}
@@
 The polyurethane foam was ignited with a small flame in the center of the top surface of the foam block.
-As the flame spread across the surface it also began to burn down into the foam sample.
+As the flame spread across the surface, it also began to burn down into the foam sample.
 As a result the exposed surface of the foam began to take the shape of a bowl as the burning rate became linear at approximately 2~g/s.
@@
   \includegraphics[width=4.5in]{../Figures/ML_PUF}\\
-  \caption[Mass loss versus time for the gasoline and foam fueled fires]{Mass loss versus time for the gasoline and foam fueled fires.}
+  \caption[Mass loss vs. time for the gasoline and foam fueled fires]{Mass loss vs. time for the gasoline and foam fueled fires.}
   \label{Mass}
@@
 
-Each of the experiments was photographed with a digital single lens reflex (SLR) camera, fixed on a tripod, with a capability of capturing at least five images per second.
-Located adjacent to the camera was a video camera recording images at approximately thirty 30 frames per second (fps).
-The experiments were also recorded with a thermal imager, however the videos were not used for analysis as it was difficult to determine the differences between the visible flame and the thermal plume from the black and white images.
-
-In engineering terms, the ``flame height'' is typically discussed as the median flame height.
-A position above the top of the fuel surface where the flame is observed to be present at least 50\% of the time.
-As a starting point, the mean flame height for each fuel was estimated from a measurement of the uppermost continuous flame tip from the still photographic images.
-
-Examples of the photographic images are presented in Figs.~\ref{Gas_Foam_Photos} and \ref{Gasoline_Photos}.
-Figure~\ref{Gas_Foam_Photos} has photographs of the natural gas flame taken during a period of ``steady state'' burning at approximately 80~kW, the gasoline taken near its average peak heat release rate of 80~kW, and the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
+Each of the experiments was photographed with a digital single lens reflex (SLR) camera fixed on a tripod, with a capability of capturing at least five still images per second.
+Located adjacent to the camera was a video camera recording images at approximately 30 frames per second (fps).
+The experiments were also recorded with a thermal imager, but those videos were not used for analysis because it was difficult to determine the differences between the visible flame and the thermal plume from the black and white images.
+
+In engineering terms, flame height is typically discussed as the median flame height.
+The median flame height is a position above the top of the fuel surface where the flame is observed to be present at least 50\% of the time.
+As a starting point, the mean flame height for each fuel was estimated from a measurement of the uppermost continuous flame tip from the still images.
+
+Examples of the still images are presented in Figs.~\ref{Gas_Foam_Photos} and \ref{Gasoline_Photos}.
+Figure~\ref{Gas_Foam_Photos} has photographs of the natural gas flame taken during a period of steady state burning at approximately 80~kW, the gasoline taken near its average peak heat release rate of 80~kW, and the polyurethane foam fire taken near its peak heat release rate of approximately 60~kW.
 Figure~\ref{Gasoline_Photos} presents two photographs of the same gasoline fueled fire when it was burning near its peak heat release rate of 100~kW.
@@
 Analyzing the photographs in this manner was very time consuming and was based on making measurements on each photograph with a scale.
-Between 6 and 10 seconds of still images, or 30 to 50 frames, were used to approximate the flames heights provided in Table~\ref{tab:Flame_Heights}.
-The limit of 5 frames per second also introduces additional uncertainty in determining the flame height.
+Between 6 to 10 seconds of still images, or 30 to 50 frames, were used to approximate the flames heights provided in Table~\ref{tab:Flame_Heights}.
+The limit of 5 frames per second also introduced additional uncertainty in determining the flame height.
 These values will serve as a basis for comparing with mean flame height values determined with video analysis.
@@
 As noted by Beyler in his review of fire plume correlations, video tape analysis seems to provide the best estimates of flame height~\cite{Beyler:1986}.
-Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps which is the National Television Standards Committee (NTSC) standard.
-The resulting image in each frame was 720 pixels wide by 480 pixels high.
+Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps, which is the National Television Standards Committee (NTSC) standard.
+The resulting image in each frame was 720 pixels wide x 480 pixels high.
 Segments of the video which corresponded to the peak heat release of each experiment were captured with a video editing program.
 
-For the natural gas experiments, approximately 30~s of ``steady state'' video were captured.
+For the natural gas experiments, approximately 30~seconds of steady state video were captured.
 In the cases of the gasoline and polyurethane fueled experiments, the video capture period bounded the peak heat release rate.
-In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30~s video capture could be made which was representative of the peak burning rate.
-The peak duration for the polyurethane foam fires was shorter so, only a 15~s video capture was used.
+In the case of the gasoline fueled fires, the peaks occurred over a long period of time, so a 30~second video capture could be made that was representative of the peak burning rate.
+The peak duration for the polyurethane foam fires was shorter, so only a 15~second video capture was used.
 
@@
 
-Each frame from the video clip was saved as a full color Tagged Image File Format (TIFF) file and the pixel aspect ratio was changed from 0.9 to 1, so that each pixel had the same dimension in both the horizontal and vertical directions.
+Each frame from the video clip was saved as a full color Tagged Image File Format (TIFF) file, and the pixel aspect ratio was changed from 0.9 to 1 so that each pixel had the same dimension in both the horizontal and vertical directions.
 Once these images were rendered by the video editing program, each image was scaled and cropped to provide input for Streams, a suite of image processing programs developed by Nokes for analyzing fluid flow visualization experiments~\cite{Nokes:2011}.
@@
 Each figure has 56 sequential images from the video segment.
-The images total almost 2~s of actual burn time.
+The images total almost 2~seconds of actual burn time.
 Notice how the flame height cycles up and down in each of the sequences.
@@
 	\caption[Example of sequential video frames sampled from a gasoline fueled experiment]{Example of sequential video frames sampled from a gasoline fueled experiment.
-In this set of images which spans almost two seconds the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
+In this set of images, which spans almost two seconds, the visual continuous flame height fluctuates from approximately 0.6~m to 1.1~m.}
 	\label{flame_height_comp_FHGAS_1}
@@
 	\caption[Example of sequential video frames sampled from a polyurethane foam fueled experiment]{Example of sequential video frames sampled from a polyurethane foam fueled experiment.
-In this set of images which spans almost two seconds the continuous visual flame height fluctuates from 0.4~m to 0.9~m.}
+In this set of images, which spans almost two seconds, the continuous visual flame height fluctuates from 0.4~m to 0.9~m.}
 	\label{flame_height_comp_FHPUF_1}
@@
 Once the image sequence was created, a series of filters and amplifiers are applied to the images to eliminate all colors but red, based on a method developed by Goble~\cite{Goble:2007}.
-Once all of the images were converted to a pure red ``flame'' which represented the area of visible fire, on a black background, the images were processed within Streams to develop an intensity field based on all of the images being ``overlaid'' on each other.
+Once all of the images were converted to a pure red ``flame'' that represented the area of visible fire on a black background, the images were processed within Streams to develop an intensity field based on all of the images being overlaid on each other.
 The end result is a contour plot of the intermittency of the flame ranging from zero to one.
 
-The calculations for the intensity field are based on a user defined computation grid.
-A grid sensitivity analysis was conducted with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm square grids.
+The calculations for the intensity field are based on a user-defined computation grid.
+A grid sensitivity analysis was conducted with 5~mm, 10~mm, 20~mm, 40~mm, and 80~mm square grids.
 Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Fig.~\ref{Intensity}.
-The outputs shown are time averaged intensity fields generated with 5 resolutions listed above.
-In each output the x and y axis dimensions are in mm.
+The outputs shown are time-averaged intensity fields generated with the resolutions listed above.
+In each output the x and y axis dimensions are in millimeters.
 
@@
 	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams.
-The images, starting with the upper left, were generated with 5~mm, 10~mm, 20~mm, 40~mm and 80~mm resolutions.}
+The images, starting with the upper left, were generated with 5~mm, 10~mm, 20~mm, 40~mm, and 80~mm resolutions.}
 	 \label{Intensity}
@@
 
-Since each pixel in the original images was equal to 5~mm, in the highest resolution case, the 5~mm analysis grid would match the best resolution of the original image.
-Four of the five cases resulted in similar results, only the 80~mm case generated significantly different results in flame height.
-As a result of the sensitivity analysis, a 10~mm grid was chosen as an optimum size for providing a sufficient level of resolution, enabling efficient processing of 30~s worth of video frames.
+Because each pixel in the original images equaled 5~mm in the highest resolution case, the 5~mm analysis grid would match the best resolution of the original image.
+Four of the five cases resulted in similar results, with only the 80~mm case generating significantly different results in flame height.
+As a result of the sensitivity analysis, a 10~mm grid was chosen as an optimum size for providing a sufficient level of resolution, enabling efficient processing of 30~seconds worth of video frames.
 At the 5~mm grid resolution, limitations within the processing system would not allow a full 30~s of video analysis.
@@
 Another means of quantifying field data with Streams is the use of contour plots.
-Examples of the time averaged contour plots are shown in Figures~\ref{Gas_and_Gasoline_Contours} and \ref{Foam_Contours} for the natural gas, gasoline, and polyurethane fueled fires.
+Examples of the time-averaged contour plots are shown in Figures~\ref{Gas_and_Gasoline_Contours} and \ref{Foam_Contours} for the natural gas, gasoline, and polyurethane fueled fires.
 Each contour line represents the percentage of time that the flame was at a given position.
-The region under examination, as shown as a black bounding rectangle, is 1400~mm high and 800~mm in width.
-The natural gas fire was sampled for 29~s, resulting in 870~images.
+The region under examination, as shown as a black bounding rectangle, is 1,400~mm high and 800~mm in width.
+The natural gas fire was sampled for 29~seconds, resulting in 870~images.
 The area bounded by the contour with the value 1 represents the area that the flame was visible 100\% of the time sampled.
@@
   \includegraphics[width=2.7in]{../Figures/Fig21} \\
-  \caption[Visibility fractions for the natural gas and gasoline fires]{Plots showing the fraction of time that the flame was visible for the natural gas (left) and gasoline (right) fires.}
+  \caption[Visibility fractions for the natural gas and gasoline fires]{Plots showing the fraction of time the flame was visible for the natural gas (left) and gasoline (right) fires.}
   \label{Gas_and_Gasoline_Contours}
@@
 Figure~\ref{Foam_Contours} shows two different contours for the polyurethane foam fueled experiment.
-The results from polyurethane fueled fire characterization experiments have an increased amount of variability due to the nature of the ignition source and the fuel itself.
-The polyurethane foam was readily ignited with a small pilot flame similar to that used to ignite the natural gas and the gasoline.
-By comparison, a small flame ignited the gases flowing out of the top of the natural gas burner and the flames from the natural gas cover the entire burner surface within approximately one second.
+The results from polyurethane fueled fire characterization experiments featured an increased amount of variability due to the nature of the ignition source and the fuel itself.
+
+Specifically, a small flame ignited the gases flowing out of the top of the natural gas burner and the flames from the natural gas cover the entire burner surface within approximately one second.
 A similar ignition sequence occurs with the gasoline pan fires.
-The polyurethane foam has a more complicated flame spread sequence that resulted in significant changes to the peak heat release rate and the time to peak heat release.
-Once the polyurethane foam was ignited, it took approximately 60~s for the flame to spread across the top surface of the fuel.
+The polyurethane foam was readily ignited with a small pilot flame similar to that used to ignite the natural gas and the gasoline but the polyurethane foam has a more complicated flame spread sequence that resulted in significant changes to the peak heat release rate and the time to peak heat release.
+Once the polyurethane foam was ignited, it took approximately 60~seconds for the flame to spread across the top surface of the fuel.
 As the flames spread horizontally across the fuel surface, the fire also burns down into the fuel.
-In some cases the fire burned completely through the fuel in the center of the foam sample, resulting in a hollow flame at the time of the peak heat release rate.
+In some cases, the fire burned completely through the fuel in the center of the foam sample, resulting in a hollow flame at the time of the peak heat release rate.
 An example of a contour plot, exhibiting the hollow or bifurcated flames is shown at right in Figure~\ref{Foam_Contours}.
-Refer back to Figure~\ref{flame_height_comp_FHPUF_1} to see photographic views of the bifurcated flames.
-It seems that the movement of the flames as they flowed away from the fuel surface blurred out the bifurcation over time with the exception of the lower elevation areas that presented at the 90 and 100\% contours.
+(Refer back to Figure~\ref{flame_height_comp_FHPUF_1} to see photographic views of the bifurcated flames.)
+
+It seems that the movement of the flames as they flowed away from the fuel surface blurred out the bifurcation over time with the exception of the lower elevation areas that presented at the 90\% and 100\% contours.
 Other methods of ignition for the polyurethane foam were considered in order to have a more uniform ignition of the top surface of the foam.
@@
 
-Based on the field data developed using Streams average flame heights for each fuel were determined.
-In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in mm with 95\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
-For the natural gas fires, the averages are from ten 30~s segments, while the fire was monitored at approximately 80~kW.
-In some cases more than one 30~s segment was sampled per heat release rate experiment.
-Sixteen 30~s video segments, which included the peak heat release rate, were successfully analyzed from the seventeen gasoline heat release rate experiments.
-One of the videos was unusable for analysis due to reflected light which could not be edited out of the images.
-For the same reason, the polyurethane foam flame height averages are the result from eight of the ten heat release rate experiments.
+Based on the field data developed using Streams, average flame heights for each fuel were determined.
+In Table~\ref{tab:Average_Flame_Heights}, each of the values represents the average flame heights, given in millimeters with 95\% confidence limits based on a Type A statistical analysis of the data, for each of the source fuels shown as the percentage of time the flame was visible at that given height.
+For the natural gas fires, the averages are from ten 30~second segments, while the fire was monitored at approximately 80~kW.
+In some cases more than one 30~second segment was sampled per heat release rate experiment.
+Sixteen 30~second video segments, which included the peak heat release rate, were successfully analyzed from the 17 gasoline heat release rate experiments.
+One of the videos was unusable for analysis due to reflected light that could not be edited out of the images.
+For the same reason, the polyurethane foam flame height averages are the result from eight of the 10 heat release rate experiments.
 
@@
 
-For both the natural gas and the gasoline experiments the 95\% confidence limits show less than 20 percent variation in visible flame height within the intermittent flame region.
+For both the natural gas and the gasoline experiments, the 95\% confidence limits show less than 20\% variation in visible flame height within the intermittent flame region.
 The percentage variation increases at the continuous flame region, although the magnitudes of the height variations are similar to other sections of the intermittent flame region.
@@
 
-The source fires have been characterized in terms of heat release rate, total heat release, plume temperature, total heat flux, mass loss and flame height.
-Table~\ref{tab:Source_fire_summary} is a summary of the average peak heat release rate, the total heat released, the average peak heat flux, the median flame height and the average peak temperature at the thermocouple closest to the median flame height.
-In the table each of the measurements is show with the 95\% confidence limits.
-This data has been collected for use in direct analysis of the burn patterns and as input into the engineering correlations and FDS models that are used later in this study.
+The source fires were characterized in terms of heat release rate, total heat release, plume temperature, total heat flux, mass loss, and flame height.
+Table~\ref{tab:Source_fire_summary} summarizes the average peak heat release rate, the total heat released, the average peak heat flux, the median flame height, and the average peak temperature at the thermocouple closest to the median flame height.
+In the table, each of the measurements is shown with the 95\% confidence limits.
+This data was collected for use in direct analysis of the burn patterns and as input into the engineering correlations and FDS models used later in this study.
 
@@
 
-\chapter{Instrumented Non-combustible Wall Experiments}
-
-Once the characteristics of the fires had been measured, the next step was to measure the thermal impact that the fires had on a vertical target surface.
-In these experiments the target is a non-combustible wall.
+\chapter{Instrumented Non Combustible Wall Experiments}
+
+Once the characteristics of the fires had been measured, the next step was to measure the thermal impact the fires had on a vertical target surface.
+In these experiments the target was a non-combustible wall.
 The non-combustible material was chosen to prevent any contribution due to combustion from the wall to the fire.
@@
 The fires were prepared and conducted in the same manner as they were in the fire characterization experiments.
-As a result the exposure time of the target wall to the fire was 300 seconds.
-In the remainder of the report the term burner will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.
+As a result, the exposure time of the target wall to the fire was 300 seconds.
 Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
+(Note: From this point forward, the term `burner' will be considered synonymous with the pan for the liquid fuel or the block of solid fuel.)
 
@@
 
-A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide, calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing steel frame wall with a 12.7~mm thick, 2.44~m high x 1.22~m wide calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 Marinite Type I is the commercial name of the non-combustible board used in these experiments.
@@
 \end{tabular}
-\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}}
+\caption[Thermal properties for Marinite I]{Thermal properties for Marinite I, as reported by the manufacturer BNZ~\cite{Marinite:1997}.}
 \label{tab:Marinite_Thermal_Properties}
@@
 The arrangement is shown in Fig.~\ref{Instrumented_NC_Wall}.
-Bare-bead, Chromel-Alumel (type K) thermocouples, with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensors and continued, at 20~cm intervals, up to a height of 2.2~m above the surface of the burner.
-Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo} The thermocouples where installed in small holes from the back of the wall.
-The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo} For the center array, a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the thermocouple positioned on the front surface of the wall.
+Bare-bead, Chromel-Alumel (type K) thermocouples with a 0.5~mm nominal diameter were installed next to the center of each heat flux sensor and continued, at 20~cm intervals, up to a height of 2.2~m above the surface of the burner.
+Photographs of the front and rear of the instrumented wall are shown in Figures~\ref{Instrumented_Wall_Front_photo} and \ref{Instrumented_Wall_Rear_photo}.
+The thermocouples were installed in small holes from the back of the wall.
+The bead of the thermocouple was flush with the surface on the calcium silicate board and was in contact with the board, as shown in Figure~\ref{Instrumented_Wall_Close_up_TC_HF_photo}.
+For the center array, a second thermocouple was installed on the backside of the calcium silicate board, approximately 10~mm below the thermocouple positioned on the front surface of the wall.
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
-In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter.
+In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory's 3~m x 3~m oxygen depletion calorimeter.
 
@@
 The results are presented for each of the four burner positions, (0.61~m, 0.31~m, 0.15~m and 0.0~m), and each of the three fuels.
-For the natural gas fueled experiments only two replicates were conducted at each position given the higher level of control and repeatability.
+For the natural gas fueled experiments, only two replicates were conducted at each position given the higher level of control and repeatability.
 For the gasoline and polyurethane fueled experiments, three replicates were conducted at each position.
@@
 The results of the wall temperatures and heat fluxes are presented as averages of the replicate experiments.
-In the sections below, a full set of the averaged data from the natural gas fueled experiments will be presented to demonstrate the impact on distance from the wall on the temperatures in the plume as well as the conditions measured on the wall.
+In the sections below, a full set of the averaged data from the natural gas fueled experiments are presented to demonstrate the impact on distance from the wall on the temperatures in the plume as well as the conditions measured on the wall.
 Then composite graphs of the wall temperatures and heat flux measure on the wall versus distance will be shown for each fuel type.
@@
 \subsection{Natural Gas Burner Plume and Wall Exposures}
-Figures~\ref{TC_Plume_TWNG_comp} through \ref{TC_Back_Center_TWNG_comp} show a complete set of data, averaged over two replicates, for the instrumented, non combustible wall natural gas burner experiments.
-Comparing the temperatures of the plume at the most distant point from the wall, 0.61~m and with the plume temperatures with the burner contacting the wall in Figure~\ref{TC_Plume_TWNG_comp} shows an increase.
-However for the burner position, 0.15~m from the wall, a decrease in plume temperatures occurs approximately 3~min after ignition.
-It is worth noting that as the plume temperatures decrease the temperatures of the thermocouples installed in the wall face increased, indicating that after the wall heats up the flame pulls toward the wall.
+Figures~\ref{TC_Plume_TWNG_comp} through \ref{TC_Back_Center_TWNG_comp} show a complete set of data, averaged over two replicates, for the instrumented, non-combustible wall, natural gas burner experiments.
+Comparing the temperatures of the plume at the most distant point from the wall (0.61~m) and with the plume temperatures with the burner contacting the wall in Figure~\ref{TC_Plume_TWNG_comp} shows an increase.
+However, for the burner position 0.15~m from the wall, a decrease in plume temperatures occurs approximately 3~min after ignition.
+It is worth noting that as the plume temperatures decrease, the temperatures of the thermocouples installed in the wall face increased, indicating that after the wall heats up the flame pulls toward the wall.
 Perhaps as a result of increased convection on the face of the wall.
@@
 Figures~\ref{TC_Surf_Cent_TWNG_comp} and \ref{TC_Surf_Edge_TWNG_comp} show consistent trends of the thermocouple temperatures in the vertical arrays on the wall increasing as the burner was moved toward the wall.
-Figure~\ref{TC_Back_Center_TWNG_comp} shows that the peak temperatures aligned with the vertical center of the burner on the backside of the gypsum wallboard peaked at approximately 100~$^\circ$C.
+Figure~\ref{TC_Back_Center_TWNG_comp} shows that the peak temperatures aligned with the vertical center of the burner on the backside of the gypsum wallboard peaked at approximately 100$^\circ$C.
 
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{TC_Plume_TWNG_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{TC_Surf_Cent_TWNG_comp}
@@
 	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Surface_Offset_Avg}\\
-	\caption[Wall Temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner, when facing the wall.
+	\caption[Wall temperatures along the edge of the natural gas fueled burner]{Wall Temperatures along the right edge of the natural gas fueled burner when facing the wall.
 The temperatures are averages of two replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{TC_Surf_Edge_TWNG_comp}
@@
 	\includegraphics[width=2.5in]{../Figures/TWNG07_TC_Back_Center_Avg}\\
-	\caption[Backside wall Temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner.
+	\caption[Backside wall temperatures along the centerline of the natural gas fueled burner]{Backside wall Temperatures along the centerline of the natural gas fueled burner.
 The temperatures are averages of two replicate experiments.
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{TC_Back_Center_TWNG_comp}
@@
 Figures~\ref{HF_Center_TWNG_comp} and \ref{HF_Edge_TWNG_comp} provide the heat flux measurements for the two vertical arrays of gauges positioned along the centerline and the edge of the natural gas burner.
-The series of graphs show that the peak heat flux increases as the burner is moved toward the wall.
-One exception is when the burner was moved from the 0.15~m position to the 0.0~m from the wall.
-In this comparison the peak heat flux values for the gauges located above the edge of the burner do not uniformly increase.
-In fact the peak heat flux actually decreased as the burner was moved from the 0.15~m position to the 0.0~m position.
+The series of graphs show that the peak heat flux increases as the burner was moved toward the wall.
+One exception was when the burner was moved from the 0.15~m position to the 0.0~m from the wall.
+In this comparison, the peak heat flux values for the gauges located above the edge of the burner did not uniformly increase.
+In fact, the peak heat flux actually decreased as the burner was moved from the 0.15~m position to the 0.0~m position.
 This decrease was due to the change in view angle between the flame closest to the burner and the lower heat flux gauges at the edge of the burner.
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{HF_Center_TWNG_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
 	\label{HF_Edge_TWNG_comp}
@@
 
-In the following sections, the data is compiled so that averaged peak values, of a given measure, for each position from the wall will be presented on a single graph for a given fuel type.
+In the following sections, the data was compiled so that averaged peak values of a given measure for each position from the wall are presented on a single graph for a given fuel type.
 
@@
 The beads of the thermocouples were installed in the wall and were flush with the wall surface.
-In each graph, the average peak temperature of the replicate experiments, for each thermocouple position is shown.
-Moving from 0.2~m above the top surface of the burner up to 2.2~m above the top of the burner surface in increments of 0.2~m.
+Each graph shows the average peak temperature of the replicate experiments for each thermocouple position.
+The thermocouple positions begin at 0.2~m above the top surface of the burner and stop at 2.2~m above the top of the burner surface.
+The thermocouples are spaced at intervals of 0.2~m.
 As with the data analysis for the source fires, the peak averages were based on a 30~s period bounding the peak for the natural gas and gasoline fires.
-A 15~s interval bounding the peak was used for the polyurethane, in order to be more representative of the peak conditions.
+A 15~seconds interval bounding the peak was used for the polyurethane in order to be more representative of the peak conditions.
 
@@
 The data is treated in the same manner as in Figure~\ref{NCTW_Surf_Center_comp}.
-For each fuel the average peak temperatures at the burner edge are significantly lower than the centerline temperatures when the burner is positioned against the wall.
-As the burners were moved away from the wall the temperatures at the centerline and the edge thermocouple arrays begin to converge.
-
-Temperatures were also measured on the backside of the wall, along the vertical centerline of the burners, Figure~\ref{NCTW_Back_Cent_comp}.
-The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner vs the corresponding temperatures on the backside of the wall have a difference of at least 400~$^\circ$C.
-It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp}, that as the burners were moved away from the wall the temperature differences are reduced.
+For each fuel, the average peak temperatures at the burner edge were significantly lower than the centerline temperatures when the burner was positioned against the wall.
+As the burners were moved away from the wall, the temperatures at the centerline and the edge thermocouple arrays began to converge.
+
+Temperatures were also measured on the backside of the wall along the vertical centerline of the burners, see Figure~\ref{NCTW_Back_Cent_comp}.
+The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner versus the corresponding temperatures on the backside of the wall show a difference of at least 400$^\circ$C.
+It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp} that as the burners were moved away from the wall, the temperature differences decreased.
 
@@
 The peak temperatures are averages of replicate experiments for each instrument location at each position from the wall.
-Beginning with the top graph position and moving down the graph for natural gas, gasoline, and polyurethane foam are presented.}
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam are presented.}
 	\label{NCTW_Surf_Center_comp}
@@
 Figures~\ref{NCTW_HF_Center_Comp} and \ref{NCTW_HF_Edge_Comp} show the results from the arrays of total heat flux gauges located along the vertical centerline and the edge of the burners for each fuel.
-The sensing surface of the gauges were installed flush with the wall surface and exposed to the fire.
+The sensing surfaces of the gauges were installed flush with the wall surface and exposed to the fire.
 In each graph, the averaged peak heat flux for each of the replicate experiments and each position is shown.
-Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface in increments of 0.2~m.
+Moving from 0.2~m above the top surface of the burner up to 1.2~m above the top of the burner surface the gauges were positioned at intervals of 0.2~m.
 Reviewing the graph for each fuel demonstrates how the heat flux at the wall decreased as the position of the burner was moved away from the wall.
@@
 
-Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed ~\cite{ASTM_E1321,Quintiere:1985}.
-The ignition temperature value calculated from the LIFT data for regular gypsum wallboard, 12.7~mm thick was 565~$^{\circ}$C with a critical heat flux for ignition of 35~kW/m$^2$.
-
-The second source, was a series of cone calorimeter experiments conducted by Dillon~\cite{ASTM_E1354,Dillon:1998}.
-The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard, 12.5~mm thick was 515~$^{\circ}$C with a minimum heat flux required for ignition of 26~kW/m$^2$.
+Quintiere and Harkleroad conducted a study with the Lateral Ignition and Flame Spread (LIFT) apparatus, which they developed~\cite{ASTM_E1321,Quintiere:1985}.
+The ignition temperature value calculated from the LIFT data for regular gypsum wallboard 12.7~mm thick was 565~$^{\circ}$C with a critical heat flux for ignition of 35~kW/m$^2$.
+
+The second source was a series of cone calorimeter experiments conducted by Dillon~\cite{ASTM_E1354,Dillon:1998}.
+The ignition temperature calculated from the cone calorimeter experiments for regular gypsum wallboard 12.5~mm thick was 515~$^{\circ}$C with a minimum heat flux required for ignition of 26~kW/m$^2$.
 
 A summary of the peak average temperatures and heat fluxes at the non-combustible wall is provided in Table~\ref{tab:TW_Summary}.
-Based on the temperature criteria for igniting gypsum wallboard, found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
-Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria, when positioned against the wall and at when the edge of the burner was 0.15~m away from the wall.
+Based on the temperature criteria for igniting gypsum wallboard found in the literature, only the gasoline and polyurethane foam burners positioned against the wall provided temperatures in excess of 515~$^{\circ}$C.
+Based on heat flux, each of the burners exceeded the 26~kW/m$^2$ ignition criteria when positioned against the wall and when the edge of the burner was 0.15~m away from the wall.
 
@@
 All of the fuels generated heat fluxes in excess of 26~kW/m$^2$.
-However only the burner against the wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
-Based on the heat flux data from Figures~\ref{NCTW_HF_Center_Comp} the natural gas burner should burn the paint and paper off of the face of the gypsum wallboard up to a height of between 0.6~m and 0.8~m above the burner.
+However, only the burner-against-the-wall positions provided a combination of heat flux and temperature that had the potential to ignite the paper on the gypsum wallboard based on the handbook data.
+Based on the heat flux data from Figures~\ref{NCTW_HF_Center_Comp}, the natural gas burner should burn the paint and paper off the face of the gypsum wallboard up to a height of between 0.6~m and 0.8~m above the burner.
 Similarly, the gasoline burner should generate a burn area between 0.8~m and 1.0~m high on a wall composed of gypsum wallboard.
-Using the same analysis, the polyurethane foam burner would create a shorter burn region approximately 0.4~m to 0.6~m.
-The experiments conducted with the instrumented gypsum wall board will provide data for comparison with data provided in this chapter and provide insight in to where the gypsum wall board may ignite.
+Using the same analysis, the polyurethane foam burner should create a shorter burn region (approximately 0.4~m to 0.6~m).
+The experiments conducted with the instrumented gypsum wall board will provide data for comparison with data provided in this chapter and provide insight into where the gypsum wall board may ignite.
 
@@
 
-Since these experiments were the culmination of the instrumented series of full scale tests, the use of gypsum wallboard was intended to provide some insight into the amount of fire damage that would result.
-These experiments proved to be challenging in terms of time and effort.
+Because these experiments were the culmination of the instrumented series of full scale tests, the use of gypsum wallboard was intended to provide some insight into the amount of fire damage that would result.
+These experiments proved challenging in terms of time and effort.
 Each panel of gypsum wallboard had to be carefully drilled for thermocouple and heat flux gauge placement.
-Since there was only one set of heat flux gauges, this reduced the number experiments that could be conducted on a given day.
+Because there was only one set of heat flux gauges, this reduced the number experiments that could be conducted on a given day.
 With other project demands, the number of instrumented wallboard experiments that could be conducted under the oxygen consumption calorimeter was reduced due to time constraints.
@@
 A typical home in the United States contains more than 7 metric tons of gypsum ~\cite{USGS:2015}.
-As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}.
+As defined by ASTM, gypsum wallboard is gypsum board designed for use on walls, ceilings, or partitions, and that affords a surface suitable to receive decoration~\cite{ASTM_C1396}.
 The ASTM standard further describes gypsum wallboard as having a noncombustible core, surfaced with paper bonded to the core.
@@
 
-The gypsum wallboard used in these experiments is referred to as `regular' as opposed to `Type C' or `Type X' gypsum wallboard, which are used in fire rated assemblies.
+The gypsum wallboard used in these experiments is referred to as ``regular'' as opposed to Type C or Type X gypsum wallboard, which are used in fire-rated assemblies.
 The gypsum wallboard used in these experiments was purchased from the same manufacturer in an effort to have the most similar panels for use between the experiments.
-Each 1.22~m by 2.44~m by 12.7~mm thick panel weighed approximately 30.5~kg.
+Each 1.22~m x 2.44~m x 12.7~mm thick panel weighed approximately 30.5~kg.
 The thermal properties of the gypsum wallboard panels are given in the Table~\ref{tab:Gypsum wallboard_Thermal_Properties}.
 The first two rows of data were measured from samples of the gypsum wallboard used in these experiments.
-The bottom four rows of data are from ~\cite{Gross:1985}.
-
-There have been a number of studies that have examined gypsum wallboard under elevated temperature conditions in terms of either its thermal properties or in terms of its physical change as a result of exposure to heat.
-Schroeder conducted a study on the post-fire analysis of construction materials including gypsum.
-As gypsum is heated to temperatures above 80~$^\circ$C it begins to change phase and degrade.
-Continued heating causes some of the chemically bound water to disassociate and the gypsum changes to a hemihydrate.
-This transformation occurs in the range of 98~$^\circ$C to 130~$^\circ$C.
-With additional heating the residue of the gypsum continues to transform and soften turning into anhydrite, a process commonly known as calcination.
-Schroeder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
-The crystal phase and the depth of penetration of the phase change was determined with the use of X~\-ray diffraction~\cite{Schroeder:1999}.
-NFPA 921 also discusses calcination and how the investigator can use the visual appearance or probing of the soft dehydrated gypsum to map fire patterns.
+The bottom four rows of data are from the Gypsum Association~\cite{Gross:1985}.
+
+A number of studies have examined gypsum wallboard under elevated temperature conditions in terms of either its thermal properties or its physical change as a result of exposure to heat.
+Schroeder conducted a study on the post-fire analysis of construction materials, including gypsum.
+As gypsum is heated to temperatures above 80$^\circ$C it begins to change phase and degrade.
+Continued heating causes some of the chemically bound water to disassociate, and the gypsum changes to a hemihydrate.
+This transformation occurs in the range of 98$^\circ$C to 130$^\circ$C.
+With additional heating, the residue of the gypsum continues to transform and soften, turning into anhydrite, a process commonly known as calcination.
+Schroeder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80$^\circ$C (dihydrate phase), 200$^\circ$C (hemihydrate phase), and 500$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
+The crystal phase and the depth of penetration of the phase change was determined with the use of X-ray diffraction~\cite{Schroeder:1999}.
+NFPA 921 also discusses calcination and how an investigator can use the visual appearance or probing of the soft dehydrated gypsum to map fire patterns.
 
@@
 		\end{tabular}
-		\caption[Thermal properties for 12.7~mm gypsum wallboard]{Thermal properties for 12.7~mm gypsum wallboard}
+		\caption[Thermal properties for 12.7~mm gypsum wallboard.]{Thermal properties for 12.7~mm gypsum wallboard.}
 		\label{tab:Gypsum wallboard_Thermal_Properties}
@@
 The first coat was a latex primer~\cite{Latex_Primer}.
-Once the primer dried a top coat of white latex paint was applied ~\cite{Latex_Paint}.
+Once the primer dried, a top coat of white latex paint was applied ~\cite{Latex_Paint}.
 After the panels dried, they were weighed.
@@
 Then the paint thickness was estimated using an ultrasonic coating thickness gauge~\cite{defelsko}.
-Over the course of the experiments, random painted panels where checked with the ultra sonic device.
+Over the course of the experiments, random painted panels where checked with the ultra-sonic device.
 The thickness of the paint varied from 0.05~mm to 0.13~mm.
-Some of the painted panels were then cut-up into samples for the bench-scale experiments.
+Some of the painted panels were then cut into samples for the bench-scale experiments.
 
@@
 
-Table~\ref{tab:IWGB_experiments} lists the experiments that were conducted for each fuel type.
+Table~\ref{tab:IWGB_experiments} lists the experiments conducted for each fuel type.
 In this chapter, as in the previous chapter, the averaged peak values for temperatures and heat fluxes are presented at varying distances from the wall.
@@
 	\begin{tabular}{|c|c|c|c|}
-		\hline Distance from wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
+		\hline Distance From Wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
 		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ 
@@
 	\end{tabular}
-	\caption[Matrix of instrumented gypsum wallboard experiments]{Matrix of instrumented gypsum wallboard experiments}
+	\caption[Matrix of instrumented gypsum wallboard experiments.]{Matrix of instrumented gypsum wallboard experiments.}
 	\label{tab:IWGB_experiments}
@@
 This was the result of a an early shut down of the gas supply.
-This discrepancy was not noticed until the data was reviewed, at which point there was no opportunity to rerun the experiment.
-
-The temperatures measured along the vertical center axis of the burner provided distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature, see Figure~\ref{IWGB_NG_TC_Plume_set}.
+This discrepancy was not noticed until the data was reviewed, at which point there was no opportunity to re-run the experiment.
+
+The temperatures measured along the vertical center axis of the burner provided distinct differences between the flame regions and the buoyant plume region based on the significant differences in temperature (see Figure~\ref{IWGB_NG_TC_Plume_set}).
 The persistent or continuous flame region appeared to be recorded at the thermocouple positions 0.2~ through 0.6~m above the burner.
 Based on the temperature time histories, the thermocouples positioned 0.8~m through 1.2~m seemed to be in the intermittent flame region.
-The thermocouples position at or above 1.4~m appear to be in the buoyant plume region.
-The fluctuations in the peak temperatures for this ``steady state'' fire are the result of the flame movement away from the thermocouples centered above the burner.
+The thermocouples positioned at or above 1.4~m appear to be in the buoyant plume region.
+The fluctuations in the peak temperatures for this steady state fire are the result of the flame movement away from the thermocouples centered above the burner.
 Note that the thermocouple positioned 0.2~m above the burner did not increase in temperature due to a connection problem in the data acquisition system.
@@
 The temperatures measured on the front surface of the painted gypsum wallboard are displayed in Figure~\ref{IWGB_NG_TC_Wall_set}.
-When the burner was located 0.31~m and 0.15~m away from the wall, the temperatures started at ambient and slowly increased, reaching the peak temperatures at 300~seconds, then the burner was shut off.
-For the case where the burner was in contact with the wall, the two thermocouples located in the persistent flame region indicated a decreasing temperature trend after the paper on the gypsum wallboard had burned away.
-The decrease in temperature my have had been the result of material from the burned gypsum wallboard shielding otherwise impacting those thermocouples.
+When the burner was located 0.31~m and 0.15~m away from the wall, the temperatures started at ambient and slowly increased, reaching the peak temperatures at 300~seconds, and then the burner was shut off.
+For the case in which the burner was in contact with the wall, the two thermocouples located in the persistent flame region indicated a decreasing temperature trend after the paper on the gypsum wallboard had burned away.
+The decrease in temperature may have been the result of material from the burned gypsum wallboard shielding or otherwise impacting those thermocouples.
 The thermocouple positioned 0.2~m above the burner was exhibiting the same behavior as in the previous experiment, but the problem was resolved during the experiment.
-The restored connection to the data system accounts for the rapid rise in temperature at 60~seconds into the experiment.
+The restored connection to the data system accounts for the rapid rise in temperature 60~seconds into the experiment.
 
@@
 In each case, the temperatures increase while the front face of the gypsum wallboard is exposed to the fire.
-As the position of the fire moves closer to the wall the rate of temperature rise on the back increases.
-The peak temperatures in each case were approximately 80~$^\circ$C.
+As the position of the fire moves closer to the wall, the rate of temperature rise on the back increases.
+The peak temperatures in each case were approximately 80$^\circ$C.
 
@@
 Similar to the wall surface temperatures, the heat flux increased as the burner was moved closer to the wall.
-However, once the burner is in contact with the wall, the flame is moved side to side.
+However, once the burner is in contact with the wall, the flame moved side to side.
 As a result, the peaks in the heat flux alternated between the center array and the edge array, as the flame moved and changed shape.
@@
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_NG_HF_Offset_Avg}\\
-	\caption[Averaged peak heat flux on the gypsum board wall for the natural gas burner fires.]{Averaged peak heat flux on the gypsum board wall along the vertical centerline and edge of the natural gas burner fires.}
+	\caption[Averaged peak heat flux on the instrumented gypsum wallboard for the natural gas burner fires.]{Averaged peak heat flux on the instrumented gypsum wallboard along the vertical centerline and edge of the natural gas burner fires.}
 	\label{IWGB_NG_HF_CandEAvg}
@@
 
-Since the focus of this study is on generating thermal damage on the face of the gypsum wallboard, the temperature and heat flux at the wall surface are important to examine.
-The averaged peak temperatures of the wall mounted thermocouples for each of the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
-This figure allows the comparison of the averaged peak temperatures at the wall based on the difference in fuel type and on the burner's distance from the wall.
+The focus of this study is on generating thermal damage on the face of the gypsum wallboard, so the temperature and heat flux at the wall surface are important to examine.
+The averaged peak temperatures of the wall-mounted thermocouples for each of the three different fuels are shown in Figure~\ref{IWGB_Temp_Comp_FrontCenter}.
+This figure allows the comparison of the averaged peak temperatures at the wall based on the difference in fuel type and the burner's distance from the wall.
 The graphs in Figure~\ref{IWGB_Temp_Comp_FrontCenter} show that generally the temperature at the wall surface decreases as the burner moves away from the wall.
-The exception to this appears to be at 0.08~m distance from the wall for the gasoline and polyurethane foam experiments.
-This position, 1/4 of the width of the burner away from the wall, caused the flame to oscillate toward the wall.
-As the flame moved toward the wall the flame impact zone on the wall moved around, higher to lower and side to side, which caused the scatter in the averaged data for that fire position.
+The exception to this appears to be at 0.08~m from the wall for the gasoline and polyurethane foam experiments.
+This position, one-quarter of the width of the burner away from the wall, caused the flame to oscillate toward the wall.
+As the flame moved toward the wall, the flame impact zone on the wall moved around, higher to lower and side to side, which caused the scatter in the averaged data for that fire position.
 
@@
 
-Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays for the natural gas, gasoline and polyurethane foam arrays.
-For the gasoline fire experiment at the 0.08~m position the heat flux values from the burner edge array had values that were similar or higher than those measured at the 0.0~m position.
+Figures~\ref{IWGB_HF_Comp_Center} and \ref{IWGB_HF_Comp_Edge} present the averaged peak values from the two heat flux gauge arrays for the natural gas, gasoline, and polyurethane foam arrays.
+For the gasoline fire experiment at the 0.08~m position, the heat flux values from the burner edge array had values that were similar or higher than those measured at the 0.0~m position.
 As discussed with temperatures above, this was a result of flame movement and the flame briefly contacting the wall near the right edge of the pan more so than seeing the increase at the centerline heat flux array.
-A review of the heat release rates for these experiments was made to see if that might have contributed to the higher heat flux, the peak heat release rates for the burner positions at 0.0~m, 0.08~m and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
+A review of the heat release rates for these experiments was made to see if that might have contributed to the higher heat flux, but the peak heat release rates for the burner positions at 0.0~m, 0.08~m, and 0.15~m were within the average peak heat release rate range of 80~kW~$\pm$~24~kW.
 This change in HRR did not contribute to the increase at the 0.08~m position.
 
-At the 0.15~m position the heat flux exhibits only a small decrease to the heat flux sensors 0.2~m and 0.4~m above the burner in the centerline array.
+At the 0.15~m position, the heat flux exhibits only a small decrease to the heat flux sensors 0.2~m and 0.4~m above the burner in the centerline array.
 However, the heat flux sensor positioned at 0.6~m above the burner showed an increase.
-As indicated above, this data which goes against the general trend of the data, was a result of the movement of the flame.
+As indicated above, this atypical data was a result of the movement of the flame.
 For this experiment, a sequence of photographs, Figure~\ref{IWGBGAS6_seq}, captured the oscillatory motion of the flame, which moved from the vertical centerline toward the wall and back again.
-In the process, the fire pattern on the wall was generated.
-
-The heat flux data from the polyurethane foam burner experiments also exhibited variations, although less pronounced than those of the gasoline experiments, at the 0.08~m and the 0.15~m position.
+This process generated the fire pattern on the wall.
+
+The heat flux data from the polyurethane foam burner experiments also exhibited variations, although less pronounced than those of the gasoline experiments, at the 0.08~m and the 0.15~m positions.
 The polyurethane foam generated a lower heat release rate and a shorter flame than the gasoline, so even though the flame was moving toward the wall, the impact was not as great.
@@
 	\includegraphics[width=.625\columnwidth]{../Figures/IWGB_PUF_HF_Center_Avg}\\
-	\caption[Averaged burner centerline heat flux for the natural gas, gasoline, and foam fires]{Averaged burner centerline heat flux, beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
+	\caption[Averaged burner centerline heat flux for the natural gas, gasoline, and foam fires]{Averaged burner centerline heat flux.
+Beginning with the top graph position and moving down, the graphs for natural gas, gasoline, and polyurethane foam fires are presented.}
 	\label{IWGB_HF_Comp_Center}
@@
 	\caption[Photographs of motion of the flame with the gasoline burner positioned 0.15~m from the wall]{Photographic sequence with the gasoline burner positioned 0.15~m from the instrumented gypsum wallboard.
-These photos capture both the oscillatory motion of the flame toward the wall as well as the burning of the gases which are pyrolyzing off of the wall and result in the formation of the lower edge of the fire pattern.}
+These photos capture both the oscillatory motion of the flame toward the wall as well as the burning of the gases pyrolyzing off  the wall, which result in the formation of the lower edge of the fire pattern.}
 	\label{IWGBGAS6_seq}
@@
 
-As defined in NFPA 921, a fire pattern is the visible or measurable physical changes, or identifiable shapes, formed by a fire effect or group of fire effects~\cite{NFPA:921}.
+As defined in NFPA 921, a fire pattern is the visible or measurable physical changes or identifiable shapes formed by a fire effect or group of fire effects~\cite{NFPA:921}.
 In order to measure the dimensions of the fire pattern, such as height and width, a determination had to be made as to where the fire pattern stops.
@@
 \begin{enumerate}
-	\item Surface deposits -– no irreversible effect on surface
-	\item Surface thermal effects –- physical change such a discoloration or melting
-	\item Charring -– evidence of surface burning
-	\item Penetration -– charring below the surface
-	\item Consumption –- loss of surface material, charring throughout
+	\item Surface deposits: no irreversible effect on surface
+	\item Surface thermal effects: physical change such a discoloration or melting
+	\item Charring: evidence of surface burning
+	\item Penetration: charring below the surface
+	\item Consumption: loss of surface material, charring throughout
 \end{enumerate}
@@
 It will serve as visual definition of the line of demarcation to be used in this study to determine the limits of a fire pattern.
-Referring to DeHaan's classifications, there are no surface deposits such as light soot that could be brushed or blown off the gypsum wallboard.
-There is a thin band of surface thermal effects in the form of discoloration of the paint, that could be considered an outer bound of the pattern.
+Referring to DeHaan's classifications, the photograph shows no surface deposits such as light soot that could be brushed or blown off the gypsum wallboard.
+There is a thin band of surface thermal effects in the form of discoloration of the paint that could be considered an outer bound of the pattern.
 To the left of the discoloration is clearly a larger area where charring (blackening of the paint/paper), penetration (lifting of the painted/paper residue), and consumption (areas where the paint/paper residue is gone altogether).
-The last three classifications or criteria will be used in this study to define the edge of the fire pattern.
-Any area where the painted paper surface has been charred, penetrated such that it has lifted away from the gypsum core, or burned away will be considered part of the fire pattern and define the lines of demarcation for this study.
+The last three classifications or criteria are used in this study to define the edge of the fire pattern.
+Any area where the painted paper surface was charred, penetrated such that it has lifted away from the gypsum core, or burned away was considered part of the fire pattern and defined the lines of demarcation for this study.
 
@@
 
-Soot and discoloration alone were not used in this study, since the gasoline and the polyurethane foam generate significant quantities of soot, as shown in Figure~\ref{Soot_pattern}.
-From the photograph, the areas of penetration and consumption can be delineated while the discolored and sooted areas tend to meld together.
+Soot and discoloration alone were not used in this study, because the gasoline and the polyurethane foam generate significant quantities of soot, as shown in Figure~\ref{Soot_pattern}.
+From the photograph, the areas of penetration and consumption are delineated while the discolored and sooted areas tend to meld together.
 Further, the focus of the measurements in this study are on thermal damage.
-Therefore the focus is on the ``burned to unburned'' line of demarcation.
+Therefore the focus is on the burned to unburned line of demarcation.
 
@@
 	\caption[Photographs showing lines of demarcation with gasoline]{Photographs showing lines of demarcation from a fire pattern generated on painted gypsum wallboard by a gasoline fueled burner.
-Burned vs unburned area is clearly defined, where as the difference between sooted and thermally discolored areas is not as clear.}
+The burned vs.
+unburned area is clearly defined, whereas the difference between sooted and thermally discolored areas is not as clear.}
 	\label{Soot_pattern}
@@
 
-A summary of the peak average temperatures and heat fluxes at the wall is provided in Table~\ref{tab:IWGB_Summary}.
-While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary}, a closer look reveals that most of the values are not ``significantly '' different.
+A summary of the peak average temperatures and heat fluxes at the wall appears in Table~\ref{tab:IWGB_Summary}.
+While the values in this summary table differ from the values in Table~\ref{tab:TW_Summary}, a closer look reveals that most of the values are not significantly different.
 In other words, the range of expanded uncertainty values overlap.
-For example, at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15\%).
-So, the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
+For example, at 0.0~m position with natural gas, the average peak temperature was 487$^\circ$C~$\pm$73$^\circ$C (15\%).
+So, the upper bound would be 560$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539$^\circ$C.
 While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are substantially different.
@@
 	\caption[Summary of instrumented gypsum wallboard experiments]{Summary of averaged peak temperatures and heat fluxes from the instrumented gypsum wallboard experiments.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\% and $\pm$8\% for the heat flux.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$ 15\% and $\pm$ 8\% for the heat flux.}
 	\label{tab:IWGB_Summary}
@@
 
-Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer which exposed the gypsum underneath when the burner was against the wall.
-The peak height of the consumed and penetrated paper, i.e.
-the burned region, was 0.8~above the burner.
-This is consistent with the Chapter 3 prediction based on the lower heat flux ignition value found in the literature and the average peak heat flux from the non-combustible wall experiments.
+Figure~\ref{IWGB_NG_patterns} provides a comparison between the area of discoloration of the paint with the natural gas burner positioned at 0.15~m away from the wall versus the area of consumed and penetrated paint/paper layer that exposed the gypsum underneath when the burner was against the wall.
+The peak height of the consumed and penetrated paper (i.e.
+the burned region) was 0.8~above the burner.
+This is consistent with the Chapter 3 prediction based on the lower heat flux ignition value found in the literature, and the average peak heat flux from the non-combustible wall experiments.
 
@@
 Figures~\ref{IWGB_Gas_patterns} and~\ref{IWGB_Gas_0m_patterns} show the progression of thermal damage caused by the gasoline fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the gypsum wallboard.
-When the burner was positioned at 0.15~m away from the wall, a semi-circular narrow burn line formed, with the lowest point approximately 0.1~m above the burner and extending up to 0.4~m above the burner on the left side.
-The formation of the burned area was captured on film and is shown in Figure~\ref{IWGBGAS6_seq}.
-The burned region on the gypsum wallboard from exposure to the gasoline burner position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
+When the burner was positioned 0.15~m away from the wall, a semi-circular narrow burn line formed, with the lowest point approximately 0.1~m above the burner and extending up to 0.4~m above the burner on the left side.
+(The formation of the burned area was captured on film and appears in Figure~\ref{IWGBGAS6_seq}.)  The burned region on the gypsum wallboard from exposure to the gasoline burner position 0.08~m away began at 0.2~m above the burner and extended up to 0.6~m.
 The width of the burned region was approximately one half of the burner width at its maximum.
-Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by the gasoline burner when it is tight against the gypsum wallboard.
+
+Figure~\ref{IWGB_Gas_0m_patterns} shows the fire pattern formed by the gasoline burner when it was tight against the gypsum wallboard.
 Two views are shown.
@@
 For the image on the left, the burner was positioned 0.0~m from the wall.
-For the image on the right, the same panel after the soot was blown off, clean burn area is evident.}
+For the image on the right, the same panel after the soot was blown off, a clean burn area is evident.}
 	\label{IWGB_Gas_0m_patterns}
@@
 Figures~\ref{IWGB_PUF_patterns} and~\ref{IWGB_PUF_0m_patterns} show the progression of thermal damage caused by the polyurethane fueled burner at 0.15~m, 0.08~m, and 0.0~m away from the instrumented gypsum wallboard.
-The burner positioned at 0.15~m from the wall did not transfer enough energy to cause any thermal damage.
-The only damage to the wall is from soot deposition.
-When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted but there was no consumption or penetration of the paper finish layer.
+The burner positioned 0.15~m from the wall did not transfer enough energy to cause any thermal damage.
+The only damage to the wall was from soot deposition.
+When the burner was located 0.08~m away from the wall, the paint/paper finish over the gypsum was discolored and heavily sooted, but there was no consumption or penetration of the paper finish layer.
 Three replicate experiments were conducted with the polyurethane foam fueled burner placed tight against the instrumented gypsum wallboard.
-The resulting patterns are shown in Figure~\ref{IWGB_PUF_0m_patterns}.
+The resulting patterns appear in Figure~\ref{IWGB_PUF_0m_patterns}.
 The average height of the burned region of the painted paper finish on the wallboard was 0.3~m above the top of the burner.
@@
 With the natural gas burner against the wall, a pattern with a maximum burn area of 0.8~m in height was generated.
-From Chapter 3, the gasoline had the potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
+
+The Chapter 3 predictions suggested the gasoline had the potential to create a fire pattern with a maximum height between 0.8~m and 1.0~m.
 In the single instrumented gypsum wallboard experiment with the gasoline burner located against the wall, the maximum height of the burned region was just short of 0.8~m.
+
 The prediction for the potential height of the fire pattern that could be created with the polyurethane burner against the wall was between 0.4~m and 0.6~m.
@@
 The average peak burned region height was 0.3~m.
-The uncertainty of the repeatability of the burn patterns has not been assessed yet, but it appears that the crude predictions from Chapter 3 provided a ``ballpark'' estimate of the maximum height of the burned region.
-
-\chapter{Bench Scale Assessment of Thermal Damage to Gypsum Wallboard}
-
-The purpose of this chapter is to develop and compare data from bench scale apparatus that could be used to analyze fire damage to gypsum wallboard.
+
+The uncertainty of the repeatability of the burn patterns has not been assessed yet, but it appears that the crude predictions from Chapter 3, based on heat flux, provided reasonable estimates of the maximum height of the burned region.
+
+\chapter{Bench-Scale Assessment of Thermal Damage to Gypsum Wallboard}
+
+The purpose of this chapter is to develop and compare data from bench-scale apparatus that could be used to analyze fire damage to gypsum wallboard.
 This type of testing might be practical for a fire investigator to use based on the low cost relative to a full-scale fire test and the small size of the samples needed for the tests.
-In the previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance, and the damage to a section of painted gypsum wallboard.
-While the data generated from those full scale laboratory experiments provide valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench scale tests in an effort to validate or improve the existing data in the literature.
+Previous sections of this study, burners were used to examine the repeatability of each fire's characteristics, the amount of heat transfered to a wall as a function of distance, and the damage to a section of painted gypsum wallboard.
+While the data generated from those full-scale laboratory experiments provide valuable insight, it would be better to be able to develop assessments of fire patterns based on data from one or a series of bench-scale tests in an effort to validate or improve the existing data in the literature.
 
@@
 	\includegraphics[width=\textwidth]{../Figures/Cone_Cal} \\
-	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter~\cite{babrauskas:1984}}
+	\caption[Sketch of the cone calorimeter]{Sketch of the cone calorimeter~\cite{babrauskas:1984}.}
 	\label{Cone_Cal}
@@
 For the ignition tests, an electric spark igniter is positioned over the center of the horizontal samples to serve as a pilot.
-Combustion products and dilution air were extracted through the hood and exhaust duct by a high temperature fan.
+Combustion products and dilution air are extracted through the hood and exhaust duct by a high temperature fan.
 The flow rate can be adjusted between 0.01 and 0.03~m$^3$/s.
-The volumetric flow rate was kept constant during testing.
-The sample was mounted on a load cell to determine mass loss rate during a test, and smoke obscuration was measured using a laser light source.
-The gas flow rate in the exhaust duct was calculated from the pressure drop across and temperature at an orifice plate in the duct.
-Finally, the concentrations of oxygen, carbon dioxide, and carbon monoxide were measured using appropriate instruments.
-Heat release rate was calculated from the gas concentration and mass flow measurements.
+The volumetric flow rate is kept constant during testing.
+The sample is mounted on a load cell to determine the mass loss rate during a test, and smoke obscuration is measured using a laser light source.
+The gas flow rate in the exhaust duct is calculated from the pressure drop across and temperature at an orifice plate in the duct.
+Finally, the concentrations of oxygen, carbon dioxide, and carbon monoxide are measured using appropriate instruments.
+Heat release rate is calculated from the gas concentration and mass flow measurements.
 
@@
 The experiments were conducted with the samples in the horizontal position.
-The key measurements and observations made with the cone calorimeter were heat release rate per unit area of the samples and time to ignition.
+The key measurements and observations made with the cone calorimeter were heat release rate per unit area of the samples, and time to ignition.
 These experiments were conducted with heat fluxes of 25, 35, 50, 70, and 75 kW/m$^2$.
-Several other cone calorimeter experiments were conducted with a single type K thermocouple, installed in a slit in the painted paper on the gypsum wallboard samples.
-This was the same manner of thermocouple installation used in the instrumented gypsum board wall experiments.
+Several other cone calorimeter experiments were conducted with a single type K thermocouple installed in a slit in the painted paper on the gypsum wallboard samples.
+This was the same manner of thermocouple installation used in the instrumented gypsum  wallboard experiments.
 These experiments were conducted at heat fluxes of 30, 35, and 50 kW/m$^2$ to determine ignition time and surface temperature pairs.
@@
 The radiant flooring panel is used to measure the flame spread of a material while exposed to an incident radiant heat flux.
-The source of the heat flux is a pre-mixed air-gas-fueled radiant panel.
-The radiating surface measures 305~mm by 457~mm.
-The radiating surface is inclined at 30~$^{\circ}$ above the horizontal.
+The source of the heat flux is a pre-mixed, air-gas-fueled radiant panel.
+The radiating surface measures 305~mm x 457~mm.
+The radiating surface is inclined 30~$^{\circ}$ above the horizontal.
 The test specimen is mounted horizontally beneath the radiant panel.
@@
 	\includegraphics[width=\textwidth]{../Figures/FLR_Radpan} \\
-	\caption[Schematic of the radiant flooring panel apparatus]{Schematic of the radiant flooring panel apparatus}
+	\caption[Schematic of the radiant flooring panel apparatus.]{Schematic of the radiant flooring panel apparatus.}
 	\label{FLR_Radpan}
@@
 	\includegraphics[width=\textwidth]{../Figures/FRP_HF_Calibration} \\
-	\caption[Incident heat flux profile in the radiant flooring panel test apparatus]{Incident heat flux profile along the centerline of the sample in the radiant flooring panel test apparatus}
+	\caption[Incident heat flux profile in the radiant flooring panel test apparatus.]{Incident heat flux profile along the centerline of the sample in the radiant flooring panel test apparatus.}
 	\label{FRP_HF_Calibration}
@@
 The critical radiant flux corresponds to the flux at the point of maximum flame propagation, or the point on the sample where the flame spread stopped.
-For this study the samples examined were cut from painted gypsum wallboard panels that were prepared from the supply of panels that were used in the compartment experiments.
+For this study, the samples examined were cut from painted gypsum wallboard panels prepared from the supply of panels used in the compartment experiments.
 
@@
 However, the sample mounting system was changed.
-A rail and trolley system was developed by Lawson and Twilley to expose fire fighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux~\cite{Lawson:1999}.
+A rail and trolley system was developed by Lawson and Twilley to expose firefighter protective equipment to various heat fluxes by being able to move the test specimen to a predetermined position that correlated with a given heat flux~\cite{Lawson:1999}.
 This trolley was used to hold a sample of painted gypsum wallboard that was 362~mm square.
 The samples were vertical and parallel to the radiant panel.
-Figure~\ref{Rad_Panel} has photographs which show the radiant panel test arrangement.
+Figure~\ref{Rad_Panel} has photographs that show the radiant panel test arrangement.
 
@@
 	\includegraphics[width=2.08in]{../Figures/RAD_pan_iso} \\
-	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement, on the left is a photograph which shows the radiant panel on the right, the aluminum heat shield in the center and the movable sample mounting frame trolley for the gypsum wallboard sample on the left.
+	\caption[Photographs of the radiant panel experimental arrangement]{Photographs of the radiant panel experimental arrangement.
+In the left photograph, the radiant panel is on the right, the aluminum heat shield is in the center, and the movable sample mounting frame trolley for the gypsum wallboard sample is on the left.
 The photograph on the right shows an isometric view of the test arrangement.}
@@
 The positions were marked for 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.
-The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point and 100~mm above and below the center point.
-In other words, the area around the center point of the sample had heat flux measures that were similar, meaning that they were within the uncertainty of the heat flux sensor, to the center point measurement.
+The area surrounding the center of the painted gypsum wallboard sample maintained the desired heat flux within at least 70~mm on either side of the center point, and 100~mm above and below the center point.
+In other words, the area around the center point of the sample had heat flux measures that were similar, meaning they were within the uncertainty of the heat flux sensor, to the center point measurement.
 Outside of the central area of the samples, the heat flux would decrease as the position approached the edge of the sample.
-The center point heat flux measures vs the distance from the radiating surface is provided in Figure~\ref{Rad_Panel_Cal}
+The center point heat flux measures versus the distance from the radiating surface is provided in Figure~\ref{Rad_Panel_Cal}.
 
@@
 The removal of the heat shield was recorded as the beginning of the exposure and therefore the beginning of the experiment.
+
 Each sample was exposed for 600 seconds.
 Each sample had a single bare-bead, Chromel-Alumel (type K) thermocouple, with a 0.5~mm nominal diameter bead in contact with the center point of each sample.
-During the experiments the samples were monitored for temperature and ignition.
-After the exposure time was completed the heat shield was once again placed between the sample and the radiant panel.
-The samples were cooled, removed and examined.
+During the experiments, the samples were monitored for temperature and ignition.
+After the exposure time was completed, the heat shield was once again placed between the sample and the radiant panel.
+The samples were cooled, removed, and examined.
 The area of thermal damage to the painted paper surface of the gypsum board was compared with exposure heat flux.
@@
 	\includegraphics[width=\textwidth]{../Figures/Rad_Panel_Cal} \\
-	\caption[Incident heat flux profile based on the distance between the sample face and the radiant panel]{Incident heat flux profile based on the distance between the sample face and the radiant panel}
+	\caption[Incident heat flux profile based on the distance between the sample face and the radiant panel.]{Incident heat flux profile based on the distance between the sample face and the radiant panel.}
 	\label{Rad_Panel_Cal}
@@
 
-The results from the three different bench scale experiments are presented and discussed in this section.
+The results from the three different bench-scale experiments are presented and discussed in this section.
 All three test methods provided some insight into the ignition and the critical heat flux required for ignition or flame spread of the painted paper surface on the gypsum wallboard.
@@
 
-Three replicate time to ignition experiments were conducted with the cone calorimeter apparatus at each heat flux.
+Three replicate time-to-ignition experiments were conducted with the cone calorimeter apparatus at each heat flux.
 The results of these experiments are shown in Table~\ref{tab:Gypsum_wallboard_timetoign}.
@@
 The exposure at 25~kW/m$^2$ resulted in charring and cracking of the painted paper surface of the gypsum wallboard sample.
-This began to occur, on average, at 270 s of exposure time.
-The samples were exposed to 25~kW/m$^2$ for 1800~s each and no ignition occurred.
+This began to occur, on average, at 270 seconds of exposure time.
+The samples were exposed to 25~kW/m$^2$ for 1,800~seconds each, and no ignition occurred.
 In the experiments with heat fluxes of 35~kW/m$^2$ or higher, ignition did occur and the painted paper surface of the gypsum board was consumed, leaving the gypsum board exposed.
@@
 	\end{tabular}
-	\caption[Painted gypsum wallboard time to ignition results]{Painted gypsum wallboard time to ignition results from the cone calorimeter}
+	\caption[Painted gypsum wallboard time to ignition results.]{Painted gypsum wallboard time to ignition results from the cone calorimeter.}
 	\label{tab:Gypsum_wallboard_timetoign}
@@
 	\caption[Painted gypsum wallboard ignition temperature results]{Painted gypsum wallboard ignition temperature results from exposure in the cone calorimeter.
-The estimated combined expanded uncertainty for temperature in these experiments was $\pm$15\%.}
+The estimated combined expanded uncertainty for temperature in these experiments was $\pm$ 15\%.}
 	\label{tab:Gypsum_wallboard_igntemp}
@@
 
-In the radiant flooring panel experiments the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kW/m$^2$ to 2~kW/m$^2$ over the length of the sample.
-In addition to the heat flux from the radiant panel, there is a small flame front approximately 10 to 30~mm in height that serves as the pilot along the length of the sample and provides additional energy to the fuel immediately ahead of the flame.
-The impact is limited to a small distance ahead of the flame, estimated to be less than 5~mm, since the flame is drawn back to the leading edge of the sample (burned portion) by the draft of the radiant panel.
+In the radiant flooring panel experiments, the gypsum wallboard was exposed to an incident heat flux that ranged from approximately 21~kW/m$^2$ to 2~kW/m$^2$ over the length of the sample.
+In addition to the heat flux from the radiant panel, there is a small flame front approximately 10~mm to 30~mm in height that serves as the pilot along the length of the sample and provides additional energy to the fuel immediately ahead of the flame.
+The impact is limited to a small distance ahead of the flame, estimated to be less than 5~mm, because the flame is drawn back to the leading edge of the sample (the burned portion) by the draft of the radiant panel.
+
 This effect is shown in Figure~\ref{FRP_flamefront_arrows}.
@@
 The exposed-bead, Chromel-Alumel (type K) thermocouples, with a 1.0~mm nominal diameter, were installed by pulling the positive and negative wires through holes drilled through the gypsum wallboard sample and positioning the bead of the thermocouple in a slit in the painted paper face made with a razor blade.
-This was the same installation method that was used in the instrumented gypsum board wall experiments and in the cone calorimeter samples to measure ignition temperature.
+This was the same installation method used in the instrumented gypsum  wallboard experiments and in the cone calorimeter samples to measure ignition temperature.
 The thermocouples were installed in the center of the sample at 100~mm intervals beginning at 100~mm from the edge of the sample closest to the radiant panel.
@@
  With the flooring radiant panel test, the incident heat flux from the panel and the pre-heated gypsum wallboard sample enables flame spread for approximately 500~s.
-The temperatures prior to ignition ranged from an average of 315 $^{\circ}$C for the 100~mm position to 242 $^{\circ}$C for the 400~mm position.
+The temperatures prior to ignition ranged from an average of 315$^{\circ}$C for the 100~mm position to 242$^{\circ}$C for the 400~mm position.
 
@@
 	\end{tabular}
-	\caption[Flooring radiant panel experiment flame spread results]{Flooring radiant panel experiment flame spread results including time to ignition at 100~mm intervals and surface temperature just prior to ignition.
+	\caption[Flooring radiant panel experiment flame spread results]{Flooring radiant panel experiment flame spread results, including time to ignition at 100~mm intervals and surface temperature just prior to ignition.
 The values are averages from three replicate experiments.
@@
 
-The cone calorimeter experiments generated peak heat release rate per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$ to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
+The cone calorimeter experiments generated peak heat release rate per unit area values ranging from a low of approximately 160 kW/m$^2$ at an incident heat flux of 35 kW/m$^2$to approximately 230 kW/m$^2$ at an incident heat flux of 75 kW/m$^2$.
 The average total heat released per unit area during each burn was 2.8 MJ/m$^2$.
-The total heat released during the cone calorimeter experiments compares favorably with the study by McGraw and Mowrer~\cite{McGraw:1999}, where the total heat released for the gypsum wallboard with 2 coats of latex paint was 2.3 to 2.7~MJ/m$^2$.
+The total heat released during the cone calorimeter experiments compares favorably with the study by McGraw and Mowrer~\cite{McGraw:1999}, in which the total heat released for the gypsum wallboard with two coats of latex paint was 2.3 to 2.7~MJ/m$^2$.
 
@@
 Seven replicate experiments were conducted in the radiant flooring panel apparatus.
-The mean burn length was 432~mm with a 95$\%$ confidence limit of $\pm$18~mm.
-Comparing this burn length range, 414~mm to 450~mm, to the incident heat flux curve provided a critical heat flux of approximately 8.9~kW/m$^2$ with a 95$\%$ confidence limit of $\pm$~0.6~kW/m$^2$.
+The mean burn length was 432~mm with a 95$\%$ confidence limit of $\pm$ 18~mm.
+Comparing this burn length range (414~mm to 450~mm) to the incident heat flux curve provided a critical heat flux of approximately 8.9~kW/m$^2$ with a 95$\%$ confidence limit of $\pm$~0.6~kW/m$^2$.
 Photographs showing a radiant flooring panel test underway and a close up of a sample near the location where the flame self extinguished are provided in Figure~\ref{FRP_Test_Photos}.
@@
 	\includegraphics[width=3.2in]{../Figures/FRP_Test_Photo2} \\
-	\caption[Photographs of the radiant flooring panel experiments]{Photographs of the radiant flooring panel experiments, on the left is a photograph aimed at the radiant panel showing the pilot flame on the sample as well as the flame front on the sample.
-The photograph on the right show the flame front on the sample just prior to flame out.}
+	\caption[Photographs of the radiant flooring panel experiments.]{Photographs of the radiant flooring panel experiments.
+The left photograph is aimed at the radiant panel and shows the pilot flame on the sample and the flame front on the sample.
+The photograph on the right shows the flame front on the sample just prior to flame out.}
 	\label{FRP_Test_Photos}
@@
 However, based on visual observations, there were no flaming ignitions.
-For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and would begin to glow.
+For one of the samples at 15~kW/m$^2$, small sections of the painted paper surface on the gypsum wall board would lift or partially separate from the gypsum core and begin to glow.
 This process became more prevalent as the heat fluxes increased.
-The radiant exposure of 25~kW/m$^2$ caused all of the painted paper to be burned off of the sample and the exposure dehydrated the gypsum to the point where the samples collapsed as they were being removed from the apparatus.
-Therefore no 25~kW/m$^2$ samples are shown in Figure~\ref{RPGB_SET}.
-Figure~\ref{RP_GB_Front} is a graph of the averaged time vs temperature curves for the three replicates at the 7 different heat flux levels.
-Notice that the samples exposed to 17.5~kW/m$^2$ and higher have noticeable temperature increase to a peak temperature followed by a decrease.
+The radiant exposure of 25~kW/m$^2$caused all of the painted paper to burn off the sample, and the exposure dehydrated the gypsum to the point where the samples collapsed as they were being removed from the apparatus.
+Therefore, no 25~kW/m$^2$ samples are shown in Figure~\ref{RPGB_SET}.
+
+Figure~\ref{RP_GB_Front} is a graph of the averaged time versus temperature curves for the three replicates at the seven different heat flux levels.
+Notice that the samples exposed to 17.5~kW/m$^2$ and higher had a noticeable temperature increase to a peak temperature, followed by a decrease.
 This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
-The temperatures at which the change in rate of temperature rise occurred are between 300 and 400~$^{\circ}$C.
-The temperature curve representing the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300~$^{\circ}$C after more than 400~seconds of exposure.
-Multiplying the time that each temperature peaked by the exposure heat flux yields the lowest total of heat was expended to create the most thermal damage, in the shortest time was at the 25~kW/m$^2$ exposure.
-While at the 15~kW/m$^2$ exposure used more than twice the total amount of heat over a longer duration and yielded a lesser amount of damage.
-The flux levels bounded by 15~kW/m$^2$ and 25~kW/m$^2$,have total energy exposures which are also bounded by the two extremes.
-This data indicates that depending on the exposure the amount of energy required to raise the temperature of the target material toward an ignition temperature, under these conditions, differs by a significant amount.
+The temperatures at which the change in rate of temperature rise occurred are between 300 and 400$^{\circ}$C.
+The temperature curve representing the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300$^{\circ}$C after more than 400~seconds of exposure.
+
+Multiplying the time each temperature peaked by the exposure heat flux shows that the most thermal damage created in the shortest time with the lowest total heat was at the 25~kW/m$^2$ exposure.
+At the other extreme, 15~kW/m$^2$ exposure used more than twice the total amount of heat over a longer duration and yielded a lesser amount of damage.
+The flux levels bounded by 15~kW/m$^2$ and 25~kW/m$^2$ have total energy exposures that were also bounded by the two extremes.
+This data indicates that depending on the exposure, the amount of energy required to raise the temperature of the target material toward an ignition temperature, under these conditions, differs by a significant amount.
 
@@
 Each row of samples represents three replicate experiments at a given heat flux.
-Beginning with the top row and moving down the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
+Beginning with the top row and moving down, the exposure heat fluxes were 10, 12.5, 15, 17.5, 20, and 22.5~kW/m$^2$.}
 	\label{RPGB_SET}
@@
 temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel]{Time vs.
-temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5 and 25~kW/m$^2$.}
+temperature curves for the gypsum wallboard samples exposed to radiant heat from a natural gas fired panel at heat fluxes of 10, 12.5, 15, 17.5, 20, 22.5, and 25~kW/m$^2$.}
 	\label{RP_GB_Front}
@@
 
-While the vertical radiant panel did not provide ignition data or heat release rate values it did provide information on the fire effect development on the painted gypsum wallboard samples with respect to heat flux.
-Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining the Figure~\ref{RPGB_SET} we see surface thermal effects of discoloration on the painted paper cover of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
-The samples exposed to 15~kW/m$^2$ exhibit charring and given the thin nature of the painted paper surface, penetration was evidenced on two of the three samples.
+While the vertical radiant panel did not provide ignition data or heat release rate values, it did provide information on the fire effect development on the painted gypsum wallboard samples with respect to heat flux.
+Referring again to the five fire effect categories listed by DeHann~\cite{DeHaan:2012} and examining Figure~\ref{RPGB_SET}, we see surface thermal effects of discoloration on the painted paper cover of the gypsum wallboard samples at both the 10 and 12.5~kW/m$^2$ incident heat flux exposures.
+The samples exposed to 15~kW/m$^2$ exhibit charring, and given the thin nature of the painted paper surface, penetration was evidenced on two of the three samples.
 The 15~kW/m$^2$ sample on the right also shows signs of the painted paper being consumed.
@@
 As the heat flux was increased, the area of damage also increased.
-Even though the incident heat flux values were lower than the characteristic value measured at the center of the sample, as the heat flux in the center increased heat flux at the edges also increased above 15~kW/m$^2$.
+Even though the incident heat flux values were lower than the characteristic value measured at the center of the sample, as the heat flux in the center increased, heat flux at the edges also increased above 15~kW/m$^2$.
 Hence, the damaged area increased outward toward the edges.
-It would appear in this test series, that 15~kW/m$^2$ heat flux exposure is on the threshold of painted paper penetration and consumption stage.
+It would appear that in this test series, 15~kW/m$^2$ heat flux exposure is on the threshold of painted paper penetration and consumption stage.
 
@@
 
-Each apparatus provided a slightly different thermal exposure to the painted gypsum wallboard samples and an array of data was generated including: time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
-Each test method has a specific parameter or parameters for which they were designed to measure.
+Each apparatus provided a slightly different thermal exposure to the painted gypsum wallboard samples, and an array of data was generated, including time to ignition, ignition temperature, heat release rate per unit area, and critical heat flux.
+Each test method had a specific parameter or parameters they were designed to measure.
 As a result, the data presented in this chapter provides a wide range of values that cannot be taken as a single number and applied.
@@
 
-The nature of the bench scale experimental data does not allow one to simply pick a value from a table and directly apply it as a universal input to a fire model.
+The nature of the bench-scale experimental data does not allow one to simply pick a value from a table and directly apply it as a universal input to a fire model.
 Currently there is no specific protocol for a fire model user to follow to develop input data.
@@
 Of course this behavior is not unique to gypsum wallboard.
-The ideal case for the fire investigation user community would be a ``standard'' catalog of fire model inputs for a given material under a wide range of conditions.
+The ideal case for the fire investigation user community would be a standard catalog of fire model inputs for a given material under a wide range of conditions.
 
@@
 The lateral ignition and flame spread apparatus can be used to generate time to ignition and ignition temperature data in addition to critical heat flux for flame spread data.
-The LIFT also considers time into the data where as the radiant flooring panel does not.
-Further the LIFT and the cone calorimeter apparatus can be conducted in both horizontal and vertical orientation to better represent the end use of the sample material.
-Thermogravimetric analysis (TGA) is another type of test which can be used to measure the mass loss rate of a material as a function of time and temperature.
-Differential scanning calorimetry (DSC) is a test method which can be used to measure the specific heat capacity and in way phase change.
-The TGA and DSC use samples that are on the order of a few grams.
+The LIFT also considers time into the data, whereas the radiant flooring panel does not.
+Further, the LIFT and the cone calorimeter apparatus can be conducted in both horizontal and vertical orientation to better represent the end use of the sample material.
+Thermogravimetric analysis (TGA) is another type of test that can be used to measure the mass loss rate of a material as a function of time and temperature.
+Differential scanning calorimetry (DSC) is a test method that can be used to measure the specific heat capacity and phase change.
+The TGA and DSC use samples that weigh a few grams.
 This can make testing with a composite material as well as interpreting the results of a composite material difficult.
 
-This chapter was anticipated to provide data that that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures, 10 to 75~kW/m$^2$.
-The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature but the reason for the approximately 200~$^{\circ}$C different could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum board material properties over longer exposure times.
+This chapter was anticipated to provide data that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures (10 to 75~kW/m$^2$).
+The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature, but the reason for the approximately 200$^{\circ}$C difference could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum wallboard material properties over longer exposure times.
 
@@
 From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
-The peak temperatures were similar for all of the fuels, approximately 80~$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
+The peak temperatures were similar for all of the fuels, approximately 80$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
 Therefore the wall construction experiments were only conducted with the natural gas and gasoline fueled burners as the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
@@
 Not surprisingly, the sub model of the thermocouple device shifted the FDS values slightly.
-At temperatures greater than 700~$^\circ$C, the `THERMOCOUPLE' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
-At temperatures less than 700~$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
+At temperatures greater than 700$^\circ$C, the `THERMOCOUPLE' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
+At temperatures less than 700$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
 The best agreement along the vertical array of temperatures was provided by the RI=5 model.
@@
 These changes include the loss of homogeneity of the gypsum material, a change in density and as the paper is charred or burned there is a potential for a change in emissivity.
-The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500~$^\circ$C~\cite{Gross:1985}.
+The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500$^\circ$C~\cite{Gross:1985}.
 While FDS can accommodate changes in thermo-conductivity and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
@@
 
-The criteria for the `charred' area of the gypsum wall board was a threshold temperature of 360~$^\circ$C.
+The criteria for the `charred' area of the gypsum wall board was a threshold temperature of 360$^\circ$C.
 This value was chosen based on the ignition temperature data collected as part of this study and documented in Chapter~5.
 
-Keep in mind that this ignition temperature is lower, by more than 150~$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
+Keep in mind that this ignition temperature is lower, by more than 150$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
 It is possible that the paint on the surface of the samples used in this study, had an impact or that during the decades between the studies the properties of the material have been changed in someway.
@@
 Figure~\ref{FDS_FirePattern_comp} displays two Smokeview images.
-In the image on the left the isothermal areas of the wall shown with a temperature range of 20~$^\circ$C to greater than 520~$^\circ$C.
-The Smokeview image on the right has the `char' feature applied with the threshold temperature of 360~$^\circ$C to coincide with cone calorimeter ignition temperature data.
+In the image on the left the isothermal areas of the wall shown with a temperature range of 20$^\circ$C to greater than 520$^\circ$C.
+The Smokeview image on the right has the `char' feature applied with the threshold temperature of 360$^\circ$C to coincide with cone calorimeter ignition temperature data.
 The upper edge of the char area is approximately 1~m above the burner.
-The upper edge of the 520~$^\circ$C area in the left image was approximately 0.8~m above the burner.
+The upper edge of the 520$^\circ$C area in the left image was approximately 0.8~m above the burner.
 This images were generated with the RI=10 model which has grid cells that were 0.04~m in size.
@@
 The visualization parameters for the wall temperature were changed to generate a isosurface `char' pattern in Smokeview.
-Both the ignition temperatures for gypsum wall board from Dillon, 515~$^\circ$C, and Quintiere and Harkleroad, 565~$^\circ$C, were examined~\cite{Dillon:1998,Quintiere:1985}.
+Both the ignition temperatures for gypsum wall board from Dillon, 515$^\circ$C, and Quintiere and Harkleroad, 565$^\circ$C, were examined~\cite{Dillon:1998,Quintiere:1985}.
 The result from both temperatures was a small, narrow, oval shaped area.
@@
 
-The data from the bench scale experiments have a range that spans more than 200~$^\circ$C.
+The data from the bench scale experiments have a range that spans more than 200$^\circ$C.
 These values used with Smokeview generated a range of fire pattern shapes and peak fire pattern heights.
@@
 Clearly more data on the ignition temperature of gypsum wall board is needed to better resolve the actual value.
-Based on the Smokeview tool the ignition temperature would be approximately 400~$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
+Based on the Smokeview tool the ignition temperature would be approximately 400$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
 
@@
   \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
 The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
-This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
+This height corresponds with the height of the top of the 360$^\circ$C mark in the FDS image.}
   \label{FDS_FirePattern_comp}
@@
 The comparison between the Smokeview corner fire pattern images and photographs of corner fire patterns are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
-The isotherms in the Smokeview images range from 20~$^\circ$C to greater than 360~$^\circ$C.
-The `char' area with the threshold value of 360~$^\circ$C is shown in the Smokeview image on the right.
+The isotherms in the Smokeview images range from 20$^\circ$C to greater than 360$^\circ$C.
+The `char' area with the threshold value of 360$^\circ$C is shown in the Smokeview image on the right.
 The upper edge of the char image was approximately 1.5~m above the burner.
@@
 The FDS value is approximately twice that.
-Of course changing the ignition temperature to 520~$^\circ$C would bring the simulated char height close to the measured values.
+Of course changing the ignition temperature to 520$^\circ$C would bring the simulated char height close to the measured values.
 
@@
   \includegraphics[width=.8\columnwidth]{../Figures/NGCorner_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
 The image with the three replicate fire patterns has a red line indicating a position approximately 1.5~m above the burner.
-This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
+This height corresponds with the height of the top of the 360$^\circ$C mark in the FDS image.}
   \label{FDS_FirePattern_Corner_comp}
@@
 \hline								&  RI=5					&  RI=10			&  RI=20            \\
-\hline Tign=360~$^\circ~C$  	&  0.72					&  1.04				&	0.86			    \\
-\hline Tign=515~$^\circ~C$		&  0.48					&  0.72				&   0.62                \\
-\hline Tign=565~$^\circ~C$		&  na					&  na				&   na                  \\ 
+\hline Tign=360$^\circ~C$  	&  0.72					&  1.04				&	0.86			    \\
+\hline Tign=515$^\circ~C$		&  0.48					&  0.72				&   0.62                \\
+\hline Tign=565$^\circ~C$		&  na					&  na				&   na                  \\ 
 \hline  CHF=15.0~kW/m$^2$		&  1.36     			& 1.44 		        &   1.40                \\
@@
 \hline								&  RI=5					&  RI=10			&  RI=20            \\
-\hline Tign=360~$^\circ~C$  	&  1.60					&  1.56				&  1.56				    \\
-\hline Tign=515~$^\circ~C$		&  1.04					&  0.96				&  0.96                 \\
-\hline Tign=565~$^\circ~C$		&  0.72					&  na				&  na                   \\
+\hline Tign=360$^\circ~C$  	&  1.60					&  1.56				&  1.56				    \\
+\hline Tign=515$^\circ~C$		&  1.04					&  0.96				&  0.96                 \\
+\hline Tign=565$^\circ~C$		&  0.72					&  na				&  na                   \\
 \hline  CHF=15.0~kW/m$^2$		&  2.08    				&  1.84		        &  1.94                 \\
@@
 In the compartment experiments, where 3 different wall construction methods were used, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
-The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
-The corresponding peak temperatures on the face of the gypsum wall board ranged from 415 to 540~$^\circ$C.
+The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80$^\circ$C.
+The corresponding peak temperatures on the face of the gypsum wall board ranged from 415 to 540$^\circ$C.
 This demonstrated the insulative capability of the gypsum wall board.

### 2017-03-29 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Jed edits Ch5 through 7

@@
 The compartments were constructed on top of a portable wood floor platform.
-Each of the test compartments consisted of three 3.6~m long by 2.4~m high wood framed walls.
-The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90~mm by 38~mm.
-A partial ceiling with a width of at least 1.2~m, measured from the back wall of the compartment was installed across the width of the compartment, this allowed for the plume to impact the ceiling and form a ceiling jet along the back wall, before the fire gases flowed up and out of the compartment and into the 6~m by 6~m hood in the NIST Large Fire Research Laboratory.
+Each of the test compartments consisted of three 3.6~m long x 2.4~m high wood framed walls.
+The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90~mm x 38~mm.
+A partial ceiling with a width of at least 1.2~m (measured from the back wall of the compartment) was installed across the width of the compartment, which allowed for the plume to impact the ceiling and form a ceiling jet along the back wall before the fire gases flowed up and out of the compartment and into the 6~m x 6~m hood in the NIST Large Fire Research Laboratory.
 The interior surface of the walls and ceiling was composed of 12.7~mm thick, regular core gypsum wallboard.
@@
 The front wall of the compartment was open along the full width of the compartment to minimize the impact of entrained air being channeled through a doorway.
+
 These experiments were conducted without instrumentation in the walls for several reasons:
 \begin{enumerate}
-\item to compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation
-\item to provide more realistic conditions
-\item to conduct additional replicate experiments
+\item To compare the non-instrumented gypsum wallboard fire pattern with the instrumented gypsum wallboard fire pattern results to determine if the instrumentation affected the pattern generation.
+\item To provide more realistic conditions.
+\item To conduct additional replicate experiments.
 \end{enumerate}
@@
 A photograph of the compartment fire experimental arrangement is shown in Figure~\ref{Compartment_Test}.
-In the instrumented gypsum wallboard experiments, as the burners were moved away from the position against the wall, the fire effects on the wall diminished significantly.
+In the instrumented gypsum wallboard experiments, as the burners were moved away from the wall, the fire effects on the wall diminished significantly.
 Therefore the fire pattern compartment experiments were conducted with the burners against the wall or in the corner of the compartment.
@@
 	\caption[Photograph of the wall fire pattern experiments compartment arrangement]{Photograph of the wall fire pattern experiments compartment arrangement.
-Experiment shown is being conducted with a polyurethane burner against the back wall.}
+Experiment shown was conducted with a polyurethane burner against the back wall.}
 	\label{Compartment_Test}
@@
 These experiments determined how the walls for the remaining compartment fire pattern experiments were constructed.
-Three cases were examined: 1) Open back, 12.7~mm thick, regular core, painted gypsum wallboard on the front of a wood frame only, 2) Closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall, and 3) Insulated, 12.7~mm thick, regular core, painted gypsum wallboard on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
-The insulation was 90~mm thick fiber glass batting, with a kraft paper facing, and an ``R value'' of 13.
+Three cases were examined: 1) open back, 12.7~mm thick, regular core, painted gypsum wallboard on the front of a wood frame only; 2) closed back, 12.7~mm thick, regular core, painted gypsum board on the front and back of a wood frame representative of an interior wall; and 3) insulated, 12.7~mm thick, regular core, painted gypsum wallboard on the front and back of a wood frame, with insulation in the voids of the wood frame representative of an exterior wall.
+
+ The insulation was 90~mm thick fiber glass batting, with a kraft paper facing, and an R value of 13.
 From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
-The peak temperatures were similar for all of the fuels, approximately 80$^\circ$C, although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
-Therefore the wall construction experiments were only conducted with the natural gas and gasoline fueled burners as the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
+The peak temperatures were similar for all of the fuels (approximately 80$^\circ$C), although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
+Therefore the wall construction experiments were conducted with only the natural gas and gasoline fueled burners because the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
 
@@
 The burner was positioned against the face of the painted gypsum wallboard.
-As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
-The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
-The natural gas had a 300~s burn time which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
+As in the fire source characterization experiments, the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
+The source fires remained the same in terms of fuels, amounts of fuels used, burner size, and burn duration.
+The natural gas had a 300~seconds burn time, which was approximately the upper bound for the total burn time for the 500~mL of gasoline.
 By using the same burners, these compartment fire pattern experiments can be correlated with the instrumented wall experimental results.
@@
 The walls were exposed to both the natural gas and the gasoline burners.
-For all of these experiments the burner was in contact with the gypsum wallboard.
+For all of these experiments, the burner was in contact with the gypsum wallboard.
 A total of 60 experiments were conducted.
@@
 Therefore the areas of the grid cells within the fire pattern were added up to determine the area of the fire patterns.
-The analysis was carried out with a resolution of a quarter grid cell or approximately 0.001~m$^2$.
-
-There were four measures that were taken to characterize each pattern: maximum height, maximum width, height at maximum width, and the area.
+The analysis was carried out with a resolution of a quarter grid cell, or approximately 0.001~m$^2$.
+
+Four measures were taken to characterize each pattern: maximum height, maximum width, height at maximum width, and the area.
 Each dimensional value is presented with the 95\% confidence level (2~$\sigma$) based on Type A statistical analysis of the fire pattern measurements.
 
-There are also a number of qualitative terms from NFPA~921 that were used to describe features of the patterns.
-For example, ``clean burn'' to describe a lack of soot within a fire pattern area or ``inverted cone'' to describe the shape of the pattern~\cite{NFPA:921}.
+A number of qualitative terms from NFPA~921 were used to describe features of the patterns.
+For example, ``clean burn'' describes a lack of soot within a fire pattern area, and ``inverted cone'' describes the shape of the pattern~\cite{NFPA:921}.
 
@@
 
-Figure~\ref{NG_Open_Wall} shows a comparison of the ten fire patterns generated by the natural gas burner on the wall with open back construction.
-The images within the figure are slightly different sized in an effect to make the images comparable.
+Figure~\ref{NG_Open_Wall} shows a comparison of the 10 fire patterns generated by the natural gas burner on the wall with open back construction.
+The images within the figure are slightly different sizes to make the images comparable.
 The average maximum height of the fire pattern generated by the natural gas burner on the open walls was 0.74~m~$\pm~0.12\%$.
@@
 These fire patterns, as well as all of the other patterns in this study, are fire plume generated patterns.
-The bottom width of each patterns is similar to the width of the burner.
-Moving up from the burner, about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
+The bottom width of each pattern is similar to the width of the burner.
+Moving up from the burner about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
 As the oxygen in the air mixes with the gaseous fuel and burns, the plume and the pattern expands.
-As the flames move up the wall the width tends to increase until about half of the peak height of the pattern, then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame is reduced.
+As the flames move up the wall, the width tends to increase until about half of the peak height of the pattern.
+Then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame decreases.
 Based on observation alone, the visible flames extend well above the height of the resulting patterns.
-Even though the experiments were conducted under quiescent conditions, a noticeable bias to one side or the other can be seen in four of the ten experiments.
+Even though the experiments were conducted under quiescent conditions, a noticeable bias to one side or the other can be seen in four of the 10 experiments.
 
@@
 The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06\%$.
-The 95~$\%$ confidence limit is about half of the value from the open wall experiments.
+The 95~$\%$ confidence limit is about half the value from the open wall experiments.
 The average maximum width of the fire patterns was 0.24~m~$\pm~0.02\%$.
-Again similar to the previous experiments.
+Again, similar to the previous experiments.
 The vertical position of the maximum width was 0.43~m~$\pm~0.03\%$.
@@
 
-	\caption[Photographs of the fire patterns from ten replicate natural gas burner against open wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against open wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate natural gas burner against open wall construction experiments.]{Photographs of the fire patterns from 10 replicate natural gas burner against open wall construction experiments.}
 	\label{NG_Open_Wall}
@@
 
-	\caption[Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against closed wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate natural gas burner against closed wall construction experiments.]{Photographs of the fire patterns from 10 replicate natural gas burner against closed wall construction experiments.}
 	\label{NG_Closed_Wall}
@@
 
-	\caption[Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction]{Photographs of the fire patterns from ten replicate natural gas burner against insulated wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate natural gas burner against insulated wall construction experiments.]{Photographs of the fire patterns from 10 replicate natural gas burner against insulated wall construction experiments.}
 	\label{NG_Insulated_Wall}
@@
 These fire patterns, as well as all of the other patterns in this study, are fire plume generated patterns.
-The bottom width of each patterns is similar to the width of the burner.
-Moving up from the burner, about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
+The bottom width of each pattern is similar to the width of the burner.
+Moving up from the burner about 25~mm, the pattern width is reduced as a result of air entrainment into the plume.
 As the oxygen in the air mixes with the gaseous fuel and burns, the plume and the pattern expands.
-As the flames move up the wall the width tends to increase until about half of the peak height of the pattern, then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame is reduced.
+As the flames move up the wall, the width tends to increase until about half of the peak height of the pattern.
+Then the pattern starts to reduce in width as the fuel is consumed and the volume of the flame decreases.
 Based on observation alone, the visible flames extend well above the height of the resulting patterns.
-Even though the experiments were conducted under quiescent conditions, a noticeable bias to one side or the other can be seen in four of the ten experiments.
-
-The fire pattern photographs from the ten closed wall construction experiments are shown in Figure~\ref{Gas_Closed_Wall}. 
+Even though the experiments were conducted under quiescent conditions, a noticeable bias to one side or the other can be seen in four of the 10 experiments.
+
+The fire pattern photographs from the 10 closed wall construction experiments are shown in Figure~\ref{Gas_Closed_Wall}.
 The patterns appear very similar in nature and size to the patterns that were generated on the open construction walls.
 The average maximum height of the fire patterns generated by the natural gas burner on the closed construction wall was the same as the patterns generated on the open construction wall, 0.74~m~$\pm~0.06\%$.
-The 95~$\%$ confidence limit is about half of the value from the open wall experiments.
+The 95~$\%$ confidence limit is about half the value from the open wall experiments.
 The average maximum width of the fire patterns was 0.24~m~$\pm~0.02\%$.
-Again similar to the previous experiments.
+Again, similar to the previous experiments.
 The vertical position of the maximum width was 0.43~m~$\pm~0.03\%$.
-The area of the burn estimated by examining the damaged grid cells was 0.14~$m^2~\pm~0.01\%$.
+The area of the burn estimated by examining the damaged grid cells was 0.14~m$^2~\pm~0.01\%$.
 
 The basic shape of these patterns on the closed wall are very similar to the patterns on the open wall.
-Six of the ten patterns have a bump out or an unsymmetrical curve within 200~mm of the top of the burner.
+Six of the 10 patterns have a bump out or an unsymmetrical curve within 200~mm of the top of the burner.
 The exact cause of these bumps in the patterns could not be determined, but they were generated later in the burn after the most of the fire pattern was created.
@@
 The last set of wall experiments with the natural gas burner was conducted with the insulated wall.
-The patterns from the ten replicate experiments are shown in Figure~\ref{Gas_Insulated_Wall}.
+The patterns from the 10 replicate experiments are shown in Figure~\ref{Gas_Insulated_Wall}.
 The average maximum height of the fire patterns generated by the natural gas burner on the insulated walls was 0.71~m~$\pm~0.10\%$.
@@
 
-	\caption[Photographs of the fire patterns from ten replicate gasoline burner against open wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against open wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate gasoline burner against open wall construction experiments.]{Photographs of the fire patterns from ten replicate gasoline burner against open wall construction experiments.}
 	\label{Gas_Open_Wall}
@@
 
-	\caption[Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against closed wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate gasoline burner against closed wall construction experiments.]{Photographs of the fire patterns from 10 replicate gasoline burner against closed wall construction experiments.}
 	\label{Gas_Closed_Wall}
@@
 
-	\caption[Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction]{Photographs of the fire patterns from ten replicate gasoline burner against insulated wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate gasoline burner against insulated wall construction experiments.]{Photographs of the fire patterns from 10 replicate gasoline burner against insulated wall construction experiments.}
 	\label{Gas_Insulated_Wall}
@@
 
-	\caption[Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction]{Photographs of the fire patterns from ten replicate polyurethane foam burner against open wall construction.}
+	\caption[Photographs of the fire patterns from 10 replicate polyurethane foam burner against open wall construction experiments.]{Photographs of the fire patterns from 10 replicate polyurethane foam burner against open wall construction experiments.}
 	\label{PUF_Open_Wall}
@@
 With the burner tight against both walls, the air entrainment perimeter was reduced by 50\%.
-Previous studies on flame height with fires in corners have demonstrated the the flame height increased when compared to a similar fire positioned against a single wall or burning in the open~\cite{Poreh:1999,Saito:1993,Takahashi:1997,Kokkala:1993}.
-The previous studies measured temperatures, heat flux, and mass flow rates for the purpose of developing correlations to predict flame height.
-The sole purpose of these experiments was to examine the fire patterns that result from well characterized fires on painted gypsum wall board.
+Previous studies on flame height with fires in corners have demonstrated the flame height increased when compared to a similar fire positioned against a single wall or burning in the open~\cite{Poreh:1999,Saito:1993,Takahashi:1997,Kokkala:1993}.
+The previous studies measured temperatures, heat flux, and mass flow rates to develop correlations to predict flame height.
+The sole purpose of these experiments was to examine the fire patterns that result from well-characterized fires on painted gypsum wallboard.
 
@@
 The burner was positioned in the left, rear corner against the face of two pieces of painted gypsum wallboard.
-As in the fire source characterization experiments the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
+As in the fire source characterization experiments, the top of the fuel in each case was positioned 7.5~cm above the floor of the compartment.
 The source fires remained the same in terms of fuels, amounts of fuels used, burner size and burn duration.
-The natural gas had a 300~s burn time which was approximately the upper bound for complete extinguishment (total burn time) for the 500~mL of gasoline and the polyurethane urethane block.
+The natural gas had a 300~second burn time, which was approximately the upper bound for complete extinguishment (i.e.
+total burn time) for the 500~mL of gasoline and the polyurethane urethane block.
 Typically the gasoline and polyurethane burners were in decay approximately 120~seconds after ignition.
@@
 The corner experiments demonstrated the expected extension of the combustion zone, especially in the cases of the natural gas and gasoline fires.
-In the extreme case the flames from the gasoline burner briefly impinged on the ceiling, which is approximately 2.4~m above the top of the burner.
-The shape of the fire pattern to the wall was also different then the patterns generated on the flat wall.
+In an extreme case, the flames from the gasoline burner briefly impinged on the ceiling, which was approximately 2.4~m above the top of the burner.
+The shape of the fire pattern to the wall was also different than the patterns generated on the flat wall.
 Much smaller areas of the wall had the painted paper charred, penetrated, and burned.
-For each of the fuels there was significantly more area where it was difficult to separate the charred areas from the surface deposits and discoloration.
+For each of the fuels, there was significantly more area where it was difficult to separate the charred areas from the surface deposits and discoloration.
 The sections below include post test images of the fire patterns.
@@
 
-Figure~\ref{NG_Corner} shows a comparison of the ten fire patterns generated by the natural gas burner in the corner position with walls of open back construction.
+Figure~\ref{NG_Corner} shows a comparison of the 10 fire patterns generated by the natural gas burner in the corner position with walls of open back construction.
 In the corner burns there is an area in the corner where the paper is not burned off.
-From the flame sequence shown in Figure~\ref{GBNG34Sequence} it can be seen that the flame in the persistent flame region is close to the walls of the corner, but moving up into the intermittent region, the flame burns away from the walls, hence less energy is transferred to the walls and perhaps a bit more soot condenses out on the cooler walls.
+The flame sequence in Figure~\ref{GBNG34Sequence} shows the flame in the persistent flame region is close to the walls of the corner, but moving up into the intermittent region, the flame burns away from the walls.
+Hence, less energy is transferred to the walls, and perhaps a bit more soot condenses out on the cooler walls.
 
@@
 
-	\caption[Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner]{Photographs of the fire patterns from ten replicate natural gas burner experiments positioned in a corner.}
+	\caption[Photographs of the fire patterns from 10 replicate natural gas burner experiments positioned in a corner.]{Photographs of the fire patterns from 10 replicate natural gas burner experiments positioned in a corner.}
 	\label{NG_Corner}
@@
 
-Figure~\ref{Gas_Corner} shows a comparison of eight of the ten fire patterns generated by the gasoline fueled burner in the corner position with walls of open back construction.
-Due to a camera malfunction there were no comparable images for the other two experiments.
+Figure~\ref{Gas_Corner} shows a comparison of eight of the 10 fire patterns generated by the gasoline fueled burner in the corner position with walls of open back construction.
+Due to a camera malfunction, there were no comparable images for the other two experiments.
 The patterns are darker than the patterns generated on the flat walls.
-Given that the air to the combustion zone was constrained it follows that the combustion may have been less efficient than the flat wall experiments which resulted in the sootier patterns.
+Given that the air to the combustion zone was constrained, it follows that the combustion may have been less efficient than the flat wall experiments, which resulted in the sootier patterns.
 The combustion zone for the gasoline fires positioned in the corner stretched from the top of the burner up to the ceiling of the compartment.
-Figure~\ref{GBGas10Sequence} shows the flame extension and similar to the natural gas burner fires shows how the flame in the intermittent zone appeared to move away from the corner.
+Figure~\ref{GBGas10Sequence} shows the flame extension and, similar to the natural gas burner fires, shows how the flame in the intermittent zone appeared to move away from the corner.
 
@@
 
-	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner with walls of open construction.}
+	\caption[Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner.]{Photographs of the fire patterns from eight replicate gasoline burner experiments positioned in a corner with walls of open construction.}
 	\label{Gas_Corner}
@@
 Figure~\ref{PUF_Corner} shows a comparison of three fire patterns generated by the polyurethane foam fueled burner in the corner position with walls of open back construction.
-Only three replicates were conducted due to the limits on the foam supply that was sourced from the same purchase.
+Only three replicates were conducted due to the limits of the foam supply that was sourced from the same purchase.
 The flame length from the polyurethane foam fueled burner was also longer compared to the flat wall experiments.
-However the change was not as big compared to the higher heat release rate natural gas and gasoline fueled burners.
+However, the change was not as big compared to the higher heat release rate of the natural gas and gasoline fueled burners.
 The resulting patterns, similar to the other corner burner patterns, were darker in color with less definition in the lines of demarcation.
@@
 
-	\caption[Photographs of the fire patterns from three replicate polyurethane foam burner experiments positioned in a corner]{Photographs of the fire patterns from three replicate polyurethane foam fueled burner experiments positioned in a corner with walls of open construction.}
+	\caption[Photographs of the fire patterns from three replicate polyurethane foam burner experiments positioned in a corner.]{Photographs of the fire patterns from three replicate polyurethane foam fueled burner experiments positioned in a corner with walls of open construction.}
 	\label{PUF_Corner}
@@
 
-After the experiments the gypsum wallboard panels were removed from the compartment for documentation and measurement of the fire patterns.
+After the experiments, the gypsum wallboard panels were removed from the compartment for documentation and measurement of the fire patterns.
 A comparison on a fire pattern from each type of burner is shown in Figure~\ref{PT_Corners}.
-Another image of the gasoline generated corner fire pattern, Figure~\ref{C_PTGASClose}, is included to show the reader how viewing a fire pattern at different angles enabled a better sense of the area of the fire damage.
+Another image of the gasoline generated corner fire pattern, Figure~\ref{C_PTGASClose}, is included to show  how viewing a fire pattern at different angles enables a better sense of the area of the fire damage.
 
@@
 
-	\caption[Photographs of the fire patterns from three different burner experiments positioned in a corner]{Photographs of the fire patterns from three different burner experiments positioned in a corner with walls of open construction.
-The patterns were generated by the following fuels, from are from left to right, natural gas, gasoline, polyurethane foam.}
+	\caption[Photographs of the fire patterns from three different burner experiments positioned in a corner.]{Photographs of the fire patterns from three different burner experiments positioned in a corner with walls of open construction.
+The patterns were generated by the following fuels from are from left to right: natural gas, gasoline, polyurethane foam.}
 	\label{PT_Corners}
@@
 
-	\caption[Photographs of a gasoline generated corner fire pattern taken at an angle]{Photographs of a gasoline generated corner fire pattern taken at an angle in order to improve the visibility of the lines of demarcation.}
+	\caption[Photographs of a gasoline generated corner fire pattern taken at an angle.]{Photographs of a gasoline generated corner fire pattern taken at an angle to improve the visibility of the lines of demarcation.}
 	\label{C_PTGASClose}
@@
 
-In general, the experiments, where the the burners were positioned against the center of a flat wall, provided very repeatable results with the natural gas and gasoline fueled burners.
-Under these pre-flashover, short burn duration fire conditions it was clear that the wall construction did not have any impact on the resulting fire pattern.
-Also comparing these patterns to those generated with the instrumented gypsum wallboard, it did not appear that the instrumentation had any impact that changed the fire pattern.
+In general, the experiments in which the burners were positioned against the center of a flat wall provided very repeatable results with the natural gas and gasoline fueled burners.
+Under these pre-flashover, short burn duration fire conditions, it was clear the wall construction did not have any impact on the resulting fire pattern.
+And when comparing these patterns to those generated with the instrumented gypsum wallboard, it did not appear that the instrumentation had any impact that changed the fire pattern either.
 With an expanded uncertainty of 2~$\sigma$, the height of the fire patterns were within $\pm$ 18\% for both the natural gas and the gasoline fuel burner fires.
 The uncertainties regarding the width and area of the patterns were higher up to $\pm$ 33\%.
-While the natural gas and the gasoline are different fuels there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
+Although the natural gas and the gasoline are different fuels, there was no significant difference in any of the measured pattern dimensions between the two as show in Table~\ref{tab:Fire_Pattern_Dimensions_Wall_Construction}.
 The larger uncertainty in the areas of the pattern may be due to the slight movement of the flames back and forth across the wall.
@@
 The gasoline fueled fires also had similar fire pattern heights and flame heights; however, the similarity was not as strong as the natural gas fires.
-The transient nature of the fire was believed to have had an impact since there was less energy transferred to the gypsum wall board and the exposure time for portions of the wall board more distant from the fuel surface was less.
-
-The polyurethane foam exhibited a higher variability in the fire pattern heights, $\pm$ 50\%, and areas, $\pm$ 57\%, due in part to variabilities in fire growth rates, a lower peak heat release rate, and a lower total heat release, than the other two fuels.
-Since the fire patterns generated by the polyurethane fueled burners were shorter and smaller, than the patterns generated by the 80 kW heat release rate fuels, the uncertainty in terms of percentage difference is magnified.
-The positive message is that the repeatability of the patterns qualitatively agree with the repeatability, or lack there of, of the heat release rate of the polyurethane foam burner which was $\pm$ 47\% during the burner characterization experiments.
+The transient nature of the fire was believed to have had an impact because there was less energy transferred to the gypsum wallboard, and the exposure time for portions of the wallboard more distant from the fuel surface was less.
+
+The polyurethane foam exhibited a higher variability in the fire pattern heights ($\pm$ 50\%), and areas ($\pm$ 57\%), due in part to variabilities in fire growth rates, a lower peak heat release rate, and a lower total heat release, than the other two fuels.
+Because the fire patterns generated by the polyurethane fueled burners were shorter and smaller than the patterns generated by the 80 kW heat release rate fuels, the uncertainty in terms of percentage difference is magnified.
+The positive message is that the repeatability of the patterns qualitatively agree with the repeatability, or lack thereof, of the heat release rate of the polyurethane foam burner, which was $\pm$ 47\% during the burner characterization experiments.
 
@@
 
-Over the years, fire researchers have provided many methods for predicting flame characteristics such as: median flame height, plume temperatures and an estimation of the heat flux emitted.
-These methods range from simple, empirically based, algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,Heskestad:SFPE,FDS_Users_Guide,FDS_Tech_Guide}.
-
-In this chapter the application of two different types of algorithms was be compared against the results from the experiments documented in previous chapters.
-In the first case, relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target were be examined.
+Over the years, fire researchers have provided many methods for predicting flame characteristics, such as median flame height, plume temperatures, and an estimation of the heat flux emitted.
+These methods range from simple, empirically based algorithms to computational fluid dynamics models~\cite{Beyler:1986,Beyler:1999,Heskestad:SFPE,FDS_Users_Guide,FDS_Tech_Guide}.
+
+For this chapter, the application of two different types of algorithms was compared against the results from the experiments documented in previous chapters.
+In the first case, relationships between the energy generated by a given fire source and the potential to transfer enough heat to generate thermal damage on a target were examined.
 The target under examination was painted gypsum wallboard.
@@
 Applications of algorithms such as these are presented in current fire dynamics and investigation textbooks as well as other application oriented documents~\cite{Icove:2013,Quintiere:1997,Asseal:2010,Beyler:1999,NUREG_1805}.
-Values from the source fire characterizations, instrumented bench scale experiments, and from the literature were utilized as input to predict or simulate real scale results using the algorithms.
+Values from the source fire characterizations, instrumented bench scale experiments, and the literature were utilized as input to predict or simulate real scale results using the algorithms.
 Then the numerical results were compared with the full-scale experimental fire pattern results.
-Keep in mind that with these algorithms time is not a factor.
+Keep in mind that with these algorithms, time is not a factor.
 Methods of this type are commonly referred to as ``back of the envelope'' estimates.
 They are intended to provide insight as opposed to a hard and fast numerical answer.
-As the experiments have shown so far there are many uncertainties which impact the results.
+As the experiments have shown so far, many uncertainties impact the results.
 
@@
 The first algorithm assumes that the heat release rate is emitted from a point source in a uniform manner.
-Therefore for any given radii a sphere of nearly uniform heat flux will be assumed.
-A schematic of this arrangement is shown in Figure~\ref{PointSourceHF} and the equation is presented below.
-Babrauskas applied this concept in his paper, ``Will the Second Item Ignite''~\cite{Babrauskas:1981}.
-The data needed to use the method includes the HRR and radiant fraction from the source fire and the threshold ignition heat flux of the target material.
-The idea being that if you knew the threshold heat flux that a given material needed to achieve auto ignition, then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
+Therefore, for any given radii a sphere of nearly uniform heat flux is assumed.
+(A schematic of this arrangement is shown in Figure~\ref{PointSourceHF}, and the equation is presented below.) Babrauskas applied this concept in his paper, ``Will the Second Item Ignite''~\cite{Babrauskas:1981}.
+The data needed to use the method includes the HRR and radiant fraction from the source fire, and the threshold ignition heat flux of the target material.
+The idea being that if one knew the threshold heat flux that a given material needed to achieve auto ignition, then given a fire with a specified HRR and radiant fraction, one could determine the range of distances from the fire where the material could receive enough energy to ignite.
 Radiation is assumed to be the only means of heat transfer.
@@
 	\includegraphics[width=4.5in]{../Figures/PointSourceHF}
-	\caption{Schematic of heat flux estimation using the point source assumption}
+	\caption{Schematic of heat flux estimation using the point source assumption.}
 	\label{PointSourceHF},
@@
 
-The question is can this simple model be used to estimate the burner positions where the heat flux would be high enough to generate thermal damage on the painted gypsum board wall?
-The average peak heat release rates from the three burners, from the source fire characterizations, were input into the equation along with the distance, R, and the $\chi_r$, or the radiant fraction.
+The question: Can this simple model estimate the burner positions where the heat flux would be high enough to generate thermal damage on the painted gypsum wallboard?
+The average peak heat release rates from the three burners from the source fire characterizations were input into the equation, along with the distance, R, and the $\chi_r$, or the radiant fraction.
 R was measured from the vertical centerline of the burners.
-Therefore in addition to the distance between the edge of the burner and the wall, half of the burner width, 0.15~m was added.
+Therefore, in addition to the distance between the edge of the burner and the wall, half of the burner width, 0.15~m, was added.
 As a starting value for $\chi_r$, the typical default value of 0.35 was used.
-Table~\ref{tab:Point_Source_HFNGG} lists the input value of the average peak heat release rate of 80~kW for both the natural gas and gasoline burner fires along with a $\chi_r$ of 0.35, and the five burner positions that were used.
-
-The predictions provided good agreement with the natural gas results at distances greater than 1 burner width away.
-Closer than one burner width array the predictions trend higher.
-In the instrumented gypsum wallboard experiments the natural gas burner at $R=0.31~m$ generated a discoloration on the surface of the painted gypsum wallboard.
-At $R=0.15~m$, with the burner touching the wall, enough energy was transferred to the wall fast enough that caused charring, penetration, and consumption of the painted paper surface.
+Table~\ref{tab:Point_Source_HFNGG} lists the input value of the average peak heat release rate of 80~kW for both the natural gas and gasoline burner fires along with a $\chi_r$ of 0.35, and the five burner positions used.
+
+The predictions provided good agreement with the natural gas results at distances greater than one burner width away.
+Closer than one burner width away, the predictions trend higher.
+In the instrumented gypsum wallboard experiments the natural gas burner at R=0.31~m generated a discoloration on the surface of the painted gypsum wallboard.
+At R=0.15~m, with the burner touching the wall, enough energy was transferred to the wall fast enough that charring, penetration, and consumption of the painted paper surface occurred.
 Based on the data from the cone calorimeter experiments conducted as part of this study, charring, penetration, and consumption would occur somewhere between 25 and 30~kW/m$^2$.
 Dillon provided a value of 26~kW/m$^2$ as the minimum heat flux where ignition of the gypsum wallboard would occur~\cite{Dillon:1998}.
-At $R=0.31~m$ the heat flux conditions were very close to the 26~kW/m$^2$ threshold heat flux for ignition, both with the prediction and the measurement.
-Neither value was high enough to cause the paper to char and ignite, there was only enough energy to cause some discoloration.
-Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantitatively in agreement, both provide a heat flux in excess of 26~kW/m$^2$.
-Indicating that a fire pattern has been burned into the wall and that was in fact true.
+At R=0.31~m;the heat flux conditions were very close to the 26~kW/m$^2$ threshold heat flux for ignition, both with the prediction and the measurement.
+Neither value was high enough to cause the paper to char and ignite; there was only enough energy to cause some discoloration.
+Once the natural gas burner was moved next to the wall, the prediction and the measurement, even though they are not quantitatively in agreement, both provided a heat flux in excess of 26~kW/m$^2$.
+This indicated a fire pattern had been burned into the wall, and that was in fact true.
 
 The predictions provided in Table~\ref{tab:Point_Source_HFNGG} were significantly lower than the measured peak heat flux values from the gasoline fueled burner experiments at every burner position.
-That said, the predictions indicate that at $R=0.31~m$  the heat flux is near the ignition threshold provided from the literature and at $R=0.23~m$ or less the heat flux is high enough to indicate ignition of the gypsum wallboard.
-The single gasoline experiment at $R=0.31~m$ showed a peak heat flux of 57~kW/m$^2$.
-The exposure was brief at this peak value as is was caused by movement of the flame toward the wall.
-This makes the experimental values at the three closest locations to the wall difficult to compare with the point source model, and most models for that matter, since they cannot account for the flame being drawn toward the wall.
+That said, the predictions indicate that at R=0.31~m the heat flux is near the ignition threshold provided from the literature, and at R=0.23~m or less, the heat flux is high enough to indicate ignition of the gypsum wallboard.
+The single gasoline experiment at R=0.31~m showed a peak heat flux of 57~kW/m$^2$.
+The exposure was brief at this peak value because it was caused by movement of the flame toward the wall.
+This makes the experimental values at the three closest locations to the wall difficult to compare with the point source model, and most models for that matter, because they cannot account for the flame being drawn toward the wall.
 In this case, an important observation is that the fire damage on the wall was limited to an uneven horseshoe shaped pattern within 100~mm above the top of the burner edge.
-This ignition was documented in Ch 4, Figure~\ref{IWGBGAS6_seq}.
-In other words, at $R=0.31~m$, there was an ignition of the fuel gases that were pyrolyzing from the painted gypsum board wall,which resulted in a smaller fire area of fire damage relative to the flame shaped damaged when the burner was against the wall surface.
-At the two closer radii, 0.23 and 0.15~M, the char, penetration, and consumption were evident and at these locations both the predictions and the measured heat fluxes are well above the threshold ignition heat flux.
-Perhaps coincidental, but at each location where the predicted heat flux was similar to the threshold from the literature, ignition of the paper on the gypsum board occurred, even though the values did not provide reasonable agreement with the from the gasoline fire measurements.
+(This ignition was documented in Ch 4, Figure~\ref{IWGBGAS6_seq}.) In other words, at R=0.31~m, there was an ignition of the fuel gases that were pyrolyzing from the painted gypsum wallboard, which resulted in a smaller fire area of fire damage relative to the flame shaped damage when the burner was against the wall surface.
+At the two closer radii, 0.23 and 0.15~m, the char, penetration, and consumption were evident, and at these locations both the predictions and the measured heat fluxes were well above the threshold ignition heat flux.
+Perhaps coincidental, but at each location where the predicted heat flux was similar to the threshold from the literature, ignition of the paper on the gypsum board occurred, even though the values did not provide reasonable agreement with the gasoline fire measurements.
 
@@
 	\end{tabular}
-	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum board wall experiments.
+	\caption[Comparison of calculated point source values (HRR = 80~kW) with heat flux data from the instrumented gypsum wallboard experiments.]{Comparison of calculated point source values with heat flux data from the natural gas and the gasoline instrumented gypsum wallboard experiments.
 Values presented with 95\% confidence limits based on the estimated uncertainty of HRR and heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
@@
 Similar to the results from the gasoline comparison, the predictive heat flux values at all of the burner positions are low relative to the experimental data.
-But again the results will be examined along a more qualitative basis.
-The experimental data provides an average peak value of 25~kW/m$^2$ for $R=0.31~m$.
-For the polyurethane foam burns the peak values were only averaged over a 15 second range due to the brief nature of the peak heat release rate.
-At $R=0.31~m$ there was no charring of the painted paper on the gypsum wallboard, only soot deposition.
-No thermal damage.
-At $R=0.23~m$ the calculated heat flux was close to but less than the threshold ignition heat flux, however in the experiments the paper ignited at this position.
-Only the prediction at $R=0.15~m$ would definitely indicate that the gypsum wallboard would ignite based on the threshold heat flux.
+But again, the results will be examined along a more qualitative basis.
+The experimental data provides an average peak value of 25~kW/m$^2$ for R=0.31~m.
+For the polyurethane foam burns, the peak values were only averaged over a 15 second range due to the brief nature of the peak heat release rate.
+At R=0.31~m there was no charring of the painted paper on the gypsum wallboard, only soot deposition with no thermal damage.
+At R=0.23~m the calculated heat flux was close to, but less than the threshold ignition heat flux.
+However in the experiments the paper ignited at this position.
+Only the prediction at R=0.15~m would definitely indicate the gypsum wallboard would ignite based on the threshold heat flux.
 
@@
 	\end{tabular}
-	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum board wall experiments.
+	\caption[Comparison of calculated point source values (HRR = 45~kW) with heat flux data from the instrumented gypsum wallboard experiments.]{Comparison of calculated point source values with heat flux data from the polyurethane foam burner instrumented gypsum wallboard experiments.
 Values presented with 95\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
@@
 
-This was an interesting exercise but it was not very definitive.
-One means of potentially improving the predictions would be to use radiative fractions that are known to be representative of the fuels.
+This was an interesting exercise, but it was not very definitive.
+One means of potentially improving the predictions would be to use radiative fractions known to represent of the fuels.
 For example, recommended values in the literature for the $chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
 The default radiative fraction of 0.35 is in line with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
-Literature values for the radiative fraction of polyurethane foam were elusive.
+Literature values for the radiative fraction of polyurethane foam proved elusive.
 
 Another means to assess the point source model was to examine the heat flux data measured at 2.15~m away from the vertical centerline of the burners during some of the source fire characterization experiments.
-By rearranging the point source equation, to solve for $\chi_r$ and by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2.15~m away from the burner centerline, the resulting values for $\chi_r$ were 0.25, 0.47 and 0.33 for the natural gas, gasoline and polyurethane burners respectively.
-This distance should be more appropriate for the use of the point source model but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
+By rearranging the point source equation to solve for $\chi_r$, and by using the measured average peak heat release rates and average peak heat fluxes at a distance of 2.15~m away from the burner centerline, the resulting values for $\chi_r$ were 0.25, 0.47 and 0.33 for the natural gas, gasoline and polyurethane burners, respectively.
+This distance should be more appropriate for the point source model, but the resultant radiative fractions for the natural gas and gasoline seem high compared to the values found in the literature.
 
 The radiant fractions determined from the measurements were applied at the two most distance locations from the wall.
-At these locations it was clear that only radiative heat transfer from the fires was the only means of heat transfer.
-At the closer the locations, based on the magnitude of the heat flux relative to the HRR, it appeared that convective heat transfer from the flame was playing a role.
-Again this is more consistent with the use guidelines of the algorithm.
-The comparison between the averaged peak measured heat flux and the calculated heat flux is presented in Table~\ref{tab:Point_Source_ModChir}
+At these locations, it was clear that radiative heat transfer from the fires was the only means of heat transfer.
+At the closer locations, based on the magnitude of the heat flux relative to the HRR, it appeared that convective heat transfer from the flame was playing a role.
+Again, this is more consistent with the use guidelines of the algorithm.
+The comparison between the averaged peak measured heat flux and the calculated heat flux is presented in Table~\ref{tab:Point_Source_ModChir}.
 
@@
 	\end{tabular}
-	\caption[Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments]{Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum board wall experiments.
+	\caption[Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum wallboard experiments]{Comparison of calculated point source values based on radiative fractions determined from the source fire characterization with heat flux data from the instrumented gypsum wallboard experiments.
 Values presented with 95\% confidence limits based on the estimated uncertainty of heat flux values from the literature~\cite{Bryant:2003,Pitts:2006}.}
@@
 
-The calculated values in Table~\ref{tab:Point_Source_ModChir} under predict the measured values.
+The calculated values in Table~\ref{tab:Point_Source_ModChir} under-predict the measured values.
 The $\chi_r$ values determined from the source fire measurements improved the agreement between the calculated and measured heat flux values for gasoline, even though the determined values of the radiative fraction for natural gas and gasoline appear to be on the high side.
-However since the determined values of $\chi_r$ for natural gas and polyurethane were less that the default value of 0.35, the agreement between the calculated and measured values decreased.
-
-The physics of the algorithm are sound, the challenge for the end user is determining the appropriate input values and making sure to use the algorithm within the appropriate distance range.
+However, since the determined values of $\chi_r$ for natural gas and polyurethane were less that the default value of 0.35, the agreement between the calculated and measured values decreased.
+
+The physics of the algorithm are sound.
+The challenge for the end user is determining the appropriate input values and making sure to use the algorithm within the appropriate distance range.
 More information or research is needed on the radiative fractions of various fuels.
-For example the majority of natural gas is composed of methane.
-However natural gas may also contain small amounts of ethane, propane, hexane, butane, and pentane.
+For example, the majority of natural gas is composed of methane.
+However, natural gas may also contain small amounts of ethane, propane, hexane, butane, and pentane.
 Some of these gases have higher radiative fractions than methane.
-In one widely used text, a table listing radiative energy fraction values for burner diameters larger than 0.5~m, lists butane in the 20 to 40 $\%$ range and hexane in the 40 to 60 $\%$ range ~\cite{Quintiere:1997}.
-So it is possible that the radiative fraction for natural gas could be higher that the radiative fraction associated with methane.
+In one widely used text, a table listing radiative energy fraction values for burner diameters larger than 0.5~m lists butane in the 20 to 40 $\%$ range and hexane in the 40 to 60 $\%$ range ~\cite{Quintiere:1997}.
+So, it is possible that the radiative fraction for natural gas could be higher that the radiative fraction associated with methane.
 The radiative fraction value in the literature for gasoline is 0.45~\cite{Quintiere:1997, IAAI:2017}.
@@
 
-Based on the information here, it seems that it would be difficult to use the point source method for determining the ignition of a target in a residential room and contents fire scenario.
-In order to generate a heat flux greater than 20 kW/m$^2$, at a distance of 0.76~m, with a radiative fraction of 35, the HRR would have to be about 420 kW.
-The fire investigation community would be well served to have additional research to examine the use of algorithms such as the point source method with realistic fuels that might be currently found in a residential setting.
+Based on this information, it seems it would be difficult to use the point source method for determining the ignition of a target in a residential room and contents fire scenario.
+In order to generate a heat flux greater than 20 kW/m$^2$ at a distance of 0.76~m with a radiative fraction of 35, the HRR would have to be about 420 kW.
+The fire investigation community would be well served to have additional research to examine the use of algorithms such as the point source method with realistic fuels currently found in residential settings.
 
@@
 The desire to use flame height correlations was based on the thought that the median flame height would correlate to the height of the associated fire pattern.
-With the heat release rate data that we have from these experiments, comparisons were made with the one of the more widely used empirical algorithms, known as the Heskestad flame height correlation.
+With the heat release rate data obtained from these experiments, comparisons were made with the one of the more widely used empirical algorithms, the Heskestad flame height equation.
 
@@
 
-Heskestad, developed an empirical method for calculating the mean visible flame height for fuels which do not have substantial in-depth combustion.
+Heskestad developed an empirical method for calculating the mean visible flame height for fuels that do not have substantial in-depth combustion.
 Appropriate fuels would include liquid pool fires and other horizontal surface fires~\cite{Heskestad:SFPE,Beyler:1986}.
 The inputs required to use the model are the heat release rate and the diameter of the base of the fire or the burner.
+The equation:
 
@@
 \end{equation}
-where $H_{f}$ is the flame height (m), $\dot{Q}$ is the heat release rate (kW), and $D$ is the burner diameter (m).
+
+\begin{tabbing}
+where: \=  \\
+{}
+\> $H_{f}$ is the flame height (m)\\
+\> $\dot{Q}$ is the heat release rate (kW) \\ 
+\> $D$ is the burner diameter (m) \\
+\end{tabbing}
 
@@
 
-Once again the average peak heat release rates from Chapter 2 were be used.
-The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80~ kW.
+Once again, the average peak heat release rates from Chapter 2 were used.
+The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80~kW.
 The polyurethane fueled burner had an average peak heat release rate of 45~kW.
-Calculating the median flame heights with the average peak heat release rates measured from the three fuels yielded 1.0~m, 1.0~m, and 0.73~m for natural gas, gasoline, and polyurethane foam respectively.
+Calculating the median flame heights with the average peak heat release rates measured from the three fuels yielded 1.0~m, 1.0~m, and 0.73~m for natural gas, gasoline, and polyurethane foam, respectively.
 It should be noted that the coefficient, 0.235, is dependent on the ratio of the heat of combustion to the actual mass stoichiometric ratio of air to volatiles of the fuel.
-For many liquid and gaseous fuels this coefficient is representative, Heskestad points out, however, that some common fuels, such as gasoline, deviate from the cited range.
-For gasoline a coefficient value of 0.2 should be used~\cite{Heskestad:SFPE}.
+For many liquid and gaseous fuels, this coefficient is representative, but Heskestad points out that some common fuels (such as gasoline) deviate from the cited range.
+For gasoline, a coefficient value of 0.2 should be used~\cite{Heskestad:SFPE}.
 Changing the coefficient yields a median flame height of 0.8~m for gasoline.
@@
 However, the range of calculated median flame height values is significantly different from the measured values.
-Based on the computational flame height assessment, Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10\% of the time.
+Based on the computational flame height assessment in Figure~\ref{Gas_and_Gasoline_Contours}, the Heskestad correlation provided a flame height value in the intermittent region where the flame is present less than 10\% of the time.
 
 For the gasoline fueled fires, the comparison of the median flame height, the average maximum fire pattern height, and the calculated flame height range values are all in agreement.
-This is significant because the 95\% confidence limits for the fire pattern and the video based flame height are both less than 20\%.
+This is significant because the 95\% confidence limits for the fire pattern and the video-based flame height are both less than 20\%.
 
@@
 Overall the Heskestad equation provided reasonable estimates of the median flame height.
-The key to the successful use of any model regardless of the simplicity or complexity is using the appropriate data and understanding the basis of the algorithm, in order to assess any underlying assumptions.
+The key to the successful use of any model regardless of the simplicity or complexity is using the appropriate data and understanding the basis of the algorithm in order to assess any underlying assumptions.
 

### 2017-03-30 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Completed JED revisions Ch 9 -11

@@
 The CFD models require more knowledge, more computer resources, and more input data to utilize correctly.
-Currently modelers need to develop their own data or rely on loosely defined databases with the hope that the material tested in the database is similar to the specific material of interest.
+Currently modelers must develop their own data or rely on loosely defined databases with the hope that the material tested in the database is similar to the specific material of interest.
 
@@
 
-The Fire Dynamics Simulator (FDS) and the scientific visualization tool, Smokeview, are the most widely used and well documented CFD tools in the fire protection engineering community.
-In addition, these tools have on going verification and validation programs.
+The Fire Dynamics Simulator (FDS) and the scientific visualization tool, Smokeview, are the most widely used and well-documented CFD tools in the fire protection engineering community.
+In addition, these tools have on-going verification and validation programs.
 Given the extent and high quality of the existing FDS documentation, there is no value to attempting to recreate a description of the model here other than to direct the reader to the volumes of information and data repository that exist for the FDS and Smokeview suite.
 
-FDS~\cite{FDS_Users_Guide} is a CFD model initially developed and currently maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow with an emphasis on smoke and heat transport from fires.
+FDS~\cite{FDS_Users_Guide} is a CFD model initially developed and currently maintained by NIST that solves a form of the Navier-Stokes equations appropriate for low-speed, thermally driven flow, with an emphasis on smoke and heat transport from fires.
 A CFD model has a computational domain that is divided into  three-dimensional rectangular control volumes or computational cells.
@@
 Based on the laws of conservation of mass, momentum, and energy, the model tracks the generation and movement of fire gases.
-One of the most important aspects of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide}and validated against fire test data~\cite{FDS_Validation_Guide}to ensure that it is accurate and provides the expected results, given appropriate input data.
-The data that FDS has been validated against can be found on-line is repository of the reports that were the source of the data~\cite{FDS-SMV_repository}.
+One of the most important aspects of FDS is that it is mathematically verified~\cite{FDS_Verification_Guide}and validated against fire test data~\cite{FDS_Validation_Guide} to ensure that it is accurate and provides the expected results, given appropriate input data.
+The data FDS has been validated against can be found on-line in a repository of the reports that were the source of the data~\cite{FDS-SMV_repository}.
 A complete description of the FDS model is provided in the FDS Technical Reference Guide~\cite{FDS_Tech_Guide}.
@@
 Smokeview visualizes smoke and other attributes of the fire simulation by showing tracer particle flow and two dimensional (2D) or three dimensional (3D) shaded contours of gas flow data, including temperature and flow vectors showing flow direction and magnitude.
-Smokeview has the ability to visualize fire and smoke by displaying a series of partially transparent planes where the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
+Smokeview can visualize fire and smoke by displaying a series of partially transparent planes in which the transparencies in each plane (at each grid node) are determined from soot densities computed by FDS.
 Smokeview can also visualize data at particular snapshots in time using 2D or 3D contours of data that show temperature, flow direction, and flow magnitude.
-Smokeview also has a feature that can represent a fire or char pattern on a surface based on user supplied threshold criteria.
+Smokeview also has a feature that can represent a fire or char pattern on a surface based on user-supplied temperature threshold criteria.
 Smokeview also has a Technical Reference Guide~\cite{Smokeview_Tech_Guide} and a Verification Guide~\cite{Smokeview_Verification_Guide}.
@@
 
-One of the key determinations that is required when developing an FDS model is the mesh or grid cell size.
-If a single plane of the data from the model were compared to a digital image we might refer to the grid cell size as the resolution of the image.
-The smaller the grid cells the better the resolution.
-However increased resolution will require more computational resources and additional run time.
+One of the key determinations required when developing an FDS model is the mesh or grid cell size.
+If a single plane of the data from the model were compared to a digital image, we might refer to the grid cell size as the resolution of the image.
+The smaller the grid cells, the better the resolution.
+However, increased resolution will require more computational resources and additional run time.
 The question is, does it provide a more realistic answer?
 As with most pursuits there is no one answer.
-The `best' grid size may depend on a several different parameters of the scenario being modeled.
+The best grid size may depend on a several different parameters of the scenario being modeled.
 
 Choosing the size of the grid when performing an analysis with FDS is critical in order to get the level of resolution needed to adequately simulate the required details within a simulation.
-In studies where large rooms or portions of buildings have been modeled grid cells on the order of 100~mm have been used and resulted in the successful simulation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Madrzykowski:2004,Vettori:2000, Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
+In studies in which large rooms or portions of buildings have been modeled, grid cells on the order of 100~mm have been used and resulted in the successful simulation of fire flow and fire growth trends ~\cite{Grosshandler:Station,Madrzykowski:2004,Vettori:2000, Barowy:2012,Overholt:San_Francisco,Weinschenk:Chicago}.
 
@@
 
-To examine the impact of computational grid cell size on the results, three different computational cell sizes; 80~mm, 40~mm, and 20~mm were chosen to model the fire.
+To examine the impact of computational grid cell size on the results, three different computational cell sizes (80~mm, 40~mm, and 20~mm), were chosen to model the fire.
 The resulting resolution index (RI) values were approximately 4.4, 8.8, and 17.5, respectively.
 Given the range of grid cell sizes and the characteristic diameter of fire, 0.35~m, this resulted in what could be considered a course (RI=5), medium (RI=10), and fine (RI=20) resolution.
-FDS simulations of the source fire characterization experiments will be conducted with these resolutions and compared with the results from the experiments.
+FDS simulations of the source fire characterization experiments were conducted with these resolutions and compared with the results from the experiments.
 
@@
 
-The FDS model for simulating the source fires is very basic, consisting of the definition of the computational domain in space and time, a definition of the burner geometry, the combustion model for the fuel, and the specification of measurement points that can be used to examine temperature, heat flux, and flame height.
+The FDS model for simulating the source fires is very basic, consisting of the definition of the computational domain in space and time, a definition of the burner geometry, the combustion model for the fuel, and the specification of measurement points used to examine temperature, heat flux, and flame height.
 
@@
 For the 80 and 40~mm computational cell scenarios, the cases were run as a single mesh.
-For the 20~mm case, the computational domain was divided into 8 uniform meshes.
-Each mesh was 2.4~m by 1.2~m and 0.6~m tall.
+For the 20~mm case, the computational domain was divided into eight uniform meshes.
+Each mesh was 2.4~m x 1.2~m, and 0.6~m tall.
 The time domain for each model was chosen to be 300 seconds, which is similar to the burn time for each of the fuels.
@@
 It was modeled with a steady state heat release rate flux of 888.89 kW/m$^2$, or a heat release rate of 80~kW.
-The chosen fuel reaction was `methane' since the natural gas used in the laboratory experiments contained approximately 95\% methane.
-In FDS version 6, the default radiant fraction for the `methane' reaction was set to~0.2.
-
-FDS has devices, which are used to simulate thermocouples and total heat flux gauges.
+The chosen fuel reaction was METHANE since the natural gas used in the laboratory experiments contained approximately 95\% methane.
+In FDS version 6, the default radiant fraction for the METHANE reaction was set to~0.2.
+
+FDS has devices used to simulate thermocouples and total heat flux gauges.
 These devices were positioned in locations similar to the locations used in the source fire experiments.
 The thermocouples were positioned in a vertical array, centered on the burner, beginning 0.1~m above the burner surface and spaced every 0.1~m up to 1.2~m above the burner surface.
-A total heat flux gauge was also modeled to provide data at the 0.95 m from the centerline of the burner and 0.5 m above the top of the burner.
+A total heat flux gauge was also modeled to provide data at 0.95 m from the centerline of the burner and 0.5 m above the top of the burner.
 In addition, FDS features devices that can not be physically implemented.
-One such device, is used to determine the heat release rate per unit length.
+One such device is used to determine the heat release rate per unit length.
 This device was used to determine flame height~\cite{McDermott:2011}.
@@
 
-In Chapter 2 the fires from the burners were characterized in terms of plume temperature, heat flux remote from the plume, and flame height.
-In this section the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
-The average plume temperatures at elevations from 0.1~m through 1.2~m above the top face of the burner in 0.1~m increments will be compared.
+In Chapter 2, the fires from the burners were characterized in terms of plume temperature, heat flux remote from the plume, and flame height.
+In this section, the results from FDS simulations of the fire generated by the natural gas burner experiments are compared with the experimental results.
+The average plume temperatures at elevations from 0.1~m through 1.2~m above the top face of the burner in 0.1~m increments are compared.
 
@@
 The only variable between these simulations was the RI.
-The RIs included three different computational cell sizes; 80~mm (RI=5), 40~mm~(RI=10), 20~mm~(RI=20).
+The RIs included three different computational cell sizes: 80~mm (RI=5), 40~mm~(RI=10), and 20~mm~(RI=20).
 The associated 95\% confidence limits are also shown the temperature value for each height.
@@
 
-This seemed to be counter intuitive to the results expected from an increased RI.
-However in each of the FDS models, the results closest to the burner seem to indicate that the model may not be `burning' the appropriate amount of fuel (fuel rich), which resulted in temperatures significantly lower than measured.
+This seemed counter intuitive to the results expected from an increased RI.
+However, in each of the FDS models, the results closest to the burner seem to indicate that the model may not be ``burning'' the appropriate amount of fuel (fuel rich), which resulted in temperatures significantly lower than measured.
 The effect of this fuel rich area above the burner results in poorer agreement with increasing RI.
-It appears that the the RI=10 and RI=20 models follow the correct trend, however the combustion zone was moved to a higher elevation relative to what was measured.
-For example the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases respectively, seemed to coincide with the measured value at 0.3~m above the burner.
+It appears the RI=10 and RI=20 models follow the correct trend, but the combustion zone moved to a higher elevation relative to what was measured.
+For example, the values at 0.5~m and 0.8~m above the burner, from the RI=10 and RI=20 cases, respectively, seemed to coincide with the measured value at 0.3~m above the burner.
 Adjusting the FDS corresponding predictions from the RI=10 and RI=20 models down to the 0.3~m position appears to move the remaining temperatures above those points into alignment with the measurements along the centerline of the plume.
-As FDS is a complex model, this explanation may be only one possibility.
-
-These simulation results are consistent with the comparisons made to the McCaffrey's plume correlation from his study, `Purely Buoyant Diffusion Flames'~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
-McCaffrey used a natural gas burner, 0.30~m square, which is similar in size to the burner used in this study.
-McCaffrey noted that, "visually non-axisymmetric behavior could be observed only very close to the burner surface".
+FDS is a complex model, so this explanation may be only one possibility.
+
+These simulation results are consistent with the comparisons made to the McCaffrey's plume correlation from his study, Purely Buoyant Diffusion Flames~\cite{McCaffrey:1979}, in the FDS Validation Guide~\cite{FDS_Validation_Guide}.
+McCaffrey used a natural gas burner 0.30~m square, which is similar in size to the burner used in this study.
+McCaffrey noted that, ``visually non-axisymmetric behavior could be observed only very close to the burner surface''.
 In the McCaffrey study, temperatures were measured with Type K thermocouples covered with a 1.0~mm stainless steel sheath.
-The peak heat release rate in McCaffery's plume study was 57.5~kW, this heat release rate was also the closest to the 80~kW fires in the current study.
-The comparison between the McCaffrey plume correlation and the FDS simulations at RI values of 5, 10 and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
-Focusing on the data between the burner surface and the 1~m above the burner surface, FDS under predicted the temperature near the surface of the burner and then over predicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases respectively.
+The peak heat release rate in McCaffery's plume study was 57.5~kW, which was also the closest to the 80~kW fires in the current study.
+The comparison between the McCaffrey plume correlation and the FDS simulations at RI values of 5, 10, and 20 are shown in Figure~\ref{McCaffrey_Plume_comp}.
+Focusing on the data between the burner surface and 1~m above the burner surface, FDS under-predicted the temperature near the surface of the burner, and then over-predicted as the elevation increased to approximately 0.4~m and 1.3~m above the burner for the RI=10 and 20 cases, respectively.
 Once the temperature comparisons were above the continuous and intermittent flame regions, the agreement between the cases and the correlation began to improve.
@@
 	\includegraphics[width=5in] {../Figures/McCaffrey_Plume_comp}  \\
-	\caption[Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures.] {Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20 from the FDS Validation Guide~\cite{FDS_Validation_Guide}.}
+	\caption[Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures.] {Comparison of vertical centerline temperatures above a 0.3~m natural gas burner from McCaffrey with FDS simulated gas temperatures generated with three different RIs (5, 10, and 20) from the FDS Validation Guide~\cite{FDS_Validation_Guide}.}
 	\label{McCaffrey_Plume_comp}
@@
 The comparisons above used the predicted gas temperature from the model.
-Another comparison can be made examining the `THERMOCOUPLE' results from FDS to see if the model of the thermocouple provides improved agreement with the temperatures measured via physical thermocouples.
+Another comparison can be made examining the THERMOCOUPLE results from FDS to see if the model of the thermocouple provides improved agreement with the temperatures measured via physical thermocouples.
 This comparison is shown in Figure~\ref{FHNG01_RI_TC}.
 Not surprisingly, the sub model of the thermocouple device shifted the FDS values slightly.
-At temperatures greater than 700$^\circ$C, the `THERMOCOUPLE' temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
+At temperatures greater than 700$^\circ$C, the THERMOCOUPLE temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
 At temperatures less than 700$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
 The best agreement along the vertical array of temperatures was provided by the RI=5 model.
-Variables such as density and emissivity required for modeling the thermal response and heat transfer to the thermocouple bead may be generating the differences between the gas temperature and the measured temperature FDS values.
+Variables such as density and emissivity required for modeling the thermal response, and heat transfer to the thermocouple bead, may have generated the differences between the gas temperature and the measured temperature FDS values.
 
@@
 	\includegraphics[width=5in]{../Figures/FHNG01_RI_TC} \\
-	\caption[Comparison of vertical centerline `THERMOCOUPLE' temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline `THERMOCOUPLE' temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs 5, 10, and 20.}
+	\caption[Comparison of vertical centerline THERMOCOUPLE temperatures above the natural gas burner with FDS simulated gas temperatures.]{Comparison of vertical centerline `THERMOCOUPLE' temperatures above the natural gas burner with FDS simulated gas temperatures generated with three different RIs (5, 10, and 20).}
 	\label{FHNG01_RI_TC}
@@
 
-The heat flux data being used for comparison was from the Chapter 2 source fire characterization experiments, the measured heat flux at 0.95~m from the centerline of the burner and 0.5~m above the top of the burner.
-In Figure~\ref{FHNG01_HF_RI} the averaged values from both heat flux gages are plotted against the FDS calculated heat flux at three different RIs of 5, 10 and 20.
+The heat flux data used for comparison was from the Chapter 2 source fire characterization experiments, the measured heat flux at 0.95~m from the centerline of the burner and 0.5~m above the top of the burner.
+In Figure~\ref{FHNG01_HF_RI}, the averaged values from both heat flux gauges are plotted against the FDS calculated heat flux at three different RIs of 5, 10, and 20.
 These FDS simulations used the default radiative fraction value of~0.2.
-As with the temperature comparisons, the course grid with an RI=5 provided the best agreement to the measurements, however all of the values were lower than the measured heat flux.
+As with the temperature comparisons, the course grid with an RI=5 provided the best agreement to the measurements, but all the values were lower than the measured heat flux.
 
@@
 	\includegraphics[width=5in]{../Figures/FHNG01_HF_RI} \\
-	\caption[Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values.]{Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values generated with three different RIs 5, 10, and 20.}
+	\caption[Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values.]{Comparison of the average heat flux measured 0.95~m from the centerline and 0.5~m above the top of the natural gas burner with FDS simulated heat flux values generated with three different RIs (5, 10, and 20).}
 	\label{FHNG01_HF_RI}
@@
 Reviewing the heat flux data documented in Chapter 2 from both the 0.95~m  and the 2.0~m from the vertical centerline of the burner positions provided average steady state heat flux values of approximately 2.0~kW/m$^2$ and 0.43~kW/m$^2$, respectively.
-Applying the point source method, discussed in Chapter 7, values for the radiative fraction were determined to be in the range of 0.25 to 0.28.
+Applying the point source method discussed in Chapter 7, values for the radiative fraction were determined to be in the range of 0.25 to 0.28.
 Values found in the literature for natural gas range from 0.15 to 0.25~\cite{Modak:1977,Hostikka:3}.
@@
 
-One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL), it has been used to determine the height where energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
+One of the outputs that can be gotten from FDS is a heat release rate per unit length (HRRPUL) that has been used to determine the height where energy stops being released along the vertical centerline of the gas burner~\cite{McDermott:2011}.
 Estimates of the flame height were made by estimating the height where 95 to 99~$\%$ of the total energy had been released.
-To have a value, based on a measurement, for comparison to the HRRPUL the peak visible flame height range estimate was developed.
+To obtain a value based on a measurement for comparison to the HRRPUL, the peak visible flame height range estimate was developed.
 The peak visible flame height ranged from the location where the flame existed only 10\% of the time with the 95\% certainty range.
@@
 
-One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in 3 dimensions to allow the generation of visualizations.
+One of the advantages of a computational fluid dynamics model such as FDS is the ability produce enough spatial data in three dimensions to allow the generation of visualizations.
 The impact of the mesh resolution can be seen in the three images of the fire shown in Figure~\ref{FDS_Flame_Image_comp}.
 The increased resolution leads to a flame structure that provides a better match to the look of the actual flame.
-However in this scenario, the increased resolution within the flow field has not resulted in improved numerical agreement with the measured values.
+However, in this scenario, the increased resolution within the flow field did not result in improved numerical agreement with the measured values.
 
@@
   \caption[Flame images generated with FDS and Smokeview]{Flame images generated with FDS and Smokeview.
-The left image has a grid size of 80~mm (RI=5), the center image has a grid size of 40~mm (RI=10) and the image on the right has a grid size of 20~mm (RI=20).}
+The left image has a grid size of 80~mm (RI=5), the center image has a grid size of 40~mm (RI=10), and the right image has a grid size of 20~mm (RI=20).}
   \label{FDS_Flame_Image_comp}
@@
 The comparisons of the temperature, heat flux, and flame heights for this specific scenario showed the best agreement with the 80~mm grid (RI=5) FDS simulations.
-Even though the differences between the radiative fractions of 0.2 and 0.22 were small, for the remaining simulation cases, 0.22 will be used.
-While the best agreement for the fire was demonstrated with the RI=5 grid, the RI=10 grid will also be used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models get additional obstructions and surfaces.
+Even though the differences between the radiative fractions of 0.2 and 0.22 were small, for the remaining simulation cases, 0.22 were used.
+While the best agreement for the fire was demonstrated with the RI=5 grid, the RI=10 grid was used in the subsequent instrumented wall and the compartment model sections to see if the increased resolution comes into play as the models got additional obstructions and surfaces.
 
@@
 
-The next comparisons were made with the natural gas source fire at 4 different distances from an instrumented gypsum board wall.
+The next comparisons were made with the natural gas source fire at four different distances from an instrumented gypsum board wall.
 Experiments were conducted with the closest edge of the burner located in the following positions from the wall: two burner widths (0.610~m), one burner width (0.305~m), one half burner width (0.150~m), and then touching the wall (0.0~m).
-The simulations will replicate the same distances.
-The simulation included a vertical gypsum board wall, 1.2~m wide, that extends from the floor of the model up to the top of the domain.
-The material properties of the wall are based solely on the properties of gypsum that were cited in Chapter 4.
-The values that are compared in the section include: vertical centerline temperatures above the burner, wall temperatures, and heat flux values at the position of the wall surface.
+The simulations replicated the same distances.
+The simulation included a vertical gypsum board wall 1.2~m wide that extended from the floor of the model up to the top of the domain.
+The material properties of the wall are based solely on the properties of gypsum cited in Chapter 4.
+The values compared in the section include vertical centerline temperatures above the burner, wall temperatures, and heat flux values at the position of the wall surface.
 
@@
 
-The computational domain of the model was the same as the volume considered for the source fire simulations, a cube with 2.4~m on a side.
-The models were run with two different sized computational grid cells, an 80~mm (RI=5) grid and a 40~mm (RI=10) grid.
+The computational domain of the model was the same as the volume considered for the source fire simulations, a cube 2.4~m on a side.
+The models were run with two different-sized computational grid cells, an 80~mm (RI=5) grid and a 40~mm (RI=10) grid.
 The face of the wall is located 1.95~m from the front of the domain.
 The wall was modeled with material properties for gypsum wallboard that were documented in Chapter 4.
-The input properties were: thermal conductivity (0.15 W/m K), specific heat (1.00 kJ/kg K) and density (807 kg/m$^3$).
-In addition FDS includes a default value of 0.9 for emissivity, this value should be representative of the painted surface of the gypsum wallboard.
+The input properties were thermal conductivity (0.15 W/m K), specific heat (1.00 kJ/kg K), and density (807 kg/m$^3$).
+In addition, FDS includes a default value of 0.9 for emissivity, and this value was representative of the painted surface of the gypsum wallboard.
 As noted earlier in this study, gypsum wallboard undergoes chemical and physical changes as it is heated.
-These changes include the loss of homogeneity of the gypsum material, a change in density and as the paper is charred or burned there is a potential for a change in emissivity.
+These changes include the loss of homogeneity of the gypsum material, a change in density, and, as the paper is charred or burned, potential change in emissivity.
 The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500$^\circ$C~\cite{Gross:1985}.
-While FDS can accommodate changes in thermo-conductivity and specific heat with respect to time, density and emissivity must be held constant~\cite{FDS_Users_Guide}.
+While FDS can accommodate changes in thermo-conductivity and specific heat with respect to time, density, and emissivity must remain constant~\cite{FDS_Users_Guide}.
 For the purposes of this study, the input values will remain constant throughout the course of the simulations.
@@
 
-As before, the FDS simulations included devices which are used to simulate thermocouples and total heat flux gauges.
+As before, the FDS simulations included devices used to simulate thermocouples and total heat flux gauges.
 These devices were positioned in the same locations as the locations used in the physical experiments, above the centerline of the burner and on the wall as shown in Chapter 4, Figure~\ref{Instrumented_GB_Wall}.
-In addition, HRRPUL will again be used as a means to gain insight into the peak flame height simulated by FDS.
+In addition, HRRPUL was again used to gain insight into the peak flame height simulated by FDS.
 
@@
 
- The temperatures measured by thermocouples positioned along the vertical centerline of the natural gas burner will be compared with FDS generated temperatures from two simulations, one with RI-5 and one with RI=10.
+ The temperatures measured by thermocouples positioned along the vertical centerline of the natural gas burner was compared with FDS generated temperatures from two simulations, one with RI-5 and one with RI=10.
 The measurement points were at intervals of 0.2~m from 0.2~m to 2.2~m above the burner.
 Figure~\ref{FDS_Plume_IWGB_comp} contains four graphs.
-Each graph shows the same types of comparison, the only difference is the distance away from the gypsum wallboard.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.
+Each graph shows the same types of comparison, and the only difference is the distance away from the gypsum wallboard.
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.
 
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
   \label{FDS_Plume_IWGB_comp}
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
   \label{FDS_Wall_Temp_IWGB_comp}
@@
 
- There seem to be a couple of noticeable trends from the graphs.
+ There seem to be a couple noticeable trends in the graphs.
 First, there appears to be a separation of the temperature data into three distinct sections.
@@
 The next two measurement positions at 0.8~m and 1.0~m are similar in temperature.
-The third section extends from 1.2 through 2.2~m above the burner and has the shape of a smooth curve decreasing in temperature with increasing elevation.
-Comparing the temperatures to the flame height analysis in Chapter 2, the first section aligns with the median flame height, the second section aligns with the portion of the flame that is intermittent, 40~$\%$ of the time or less.
-The upper most section of the temperature data aligns with the thermal plume above the flame.
+The third section extends from 1.2 through 2.2~m above the burner and follows a smooth curve decreasing in temperature with increasing elevation.
+Comparing the temperatures to the flame height analysis in Chapter 2, the first section aligns with the median flame height, and the second section aligns with the intermittent portion of the flame, 40~$\%$ of the time or less.
+The upper-most section of the temperature data aligns with the thermal plume above the flame.
 
  The second issue is that the FDS predictions do not align equally well with the data from each position, with the best agreement occurring when the burner is positioned against the wall.
-Further the temperatures for the burner position, 0.61~m from the wall, was thought to be equivalent to the source fire experiments documented in Chapter 2.
-However that is not the case.
+Further, the temperatures for the burner position 0.61~m from the wall was thought to be equivalent to the source fire experiments documented in Chapter 2.
+However, that was not the case.
 The installation of the wall resulted in movement of the flame and plume.
-The flames oscillate toward the wall and as a result move away from the thermocouples centered over the burner.
+The flames oscillate toward the wall and, as a result, move away from the thermocouples centered over the burner.
 The resulting decrease in temperature may account for the difference between the plume temperatures and the simulated temperatures from FDS.
@@
 Figure~\ref{FDS_Wall_Temp_IWGB_comp} is analogous to Figure~\ref{FDS_Plume_IWGB_comp} except it compares the gypsum wallboard surface temperatures against the FDS simulated temperatures.
-So while the FDS values for the plume over predicted the temperatures, the FDS values for the wall surface temperatures are under predicting.
-This is consistent with the flame and plume moving away from the plume centerline and toward the wall.
-The agreement between the FDS results and the measurements improves as the burner moves closer to the wall, however once the burner is against the wall, the degree of agreement between the FDS results and the measured temperatures decreased.
-At this position the FDS results are over predicting the temperature.
-This differences at the wall are most distinct in the region where the flame impinged on the wall.
-The agreement improves in the plume area above the flames.
-In the comparisons with the source fire experiments, the FDS generated temperatures were under predicting closer to the burner surface and the over predicting in the flame region as a result of the `combustion' occurring at higher elevations above the burner.
-If a similar phenomena is occurring here, the wall maybe exaggerating the effect.
+So, while the FDS values for the plume over-predicted the temperatures, the FDS values for the wall surface temperatures under-predicted.
+This was consistent with the flame and plume moving away from the plume centerline and toward the wall.
+The agreement between the FDS results and the measurements improved as the burner moved closer to the wall, but once the burner was against the wall, the degree of agreement between the FDS results and the measured temperatures decreased.
+At this position, the FDS results over-predicted the temperature.
+These differences at the wall were most distinct in the region where the flame impinged on the wall.
+The agreement improved in the plume area above the flames.
+In the comparisons with the source fire experiments, the FDS-generated temperatures were under-predicting closer to the burner surface and over-predicting in the flame region as a result of the ``combustion'' occurring at higher elevations above the burner.
+If a similar phenomena occurred here, the wallmight have exaggerated the effect.
 
@@
 Each array had six gauges installed from 0.2~m up through 1.2~m above the burner.
-One array was installed in line with the center of the burner and the other array was installed on the right edge of the burner.
-The comparisons between the measured heat flux and the FDS simulations are provided in Figure~\ref{FDS_HFCL_IWNG_comp} and Figure~\ref{FDS_HFEdge_IWNG_comp}.
-For the centerline gauges the trends between the heat flux measurements and the FDS values are similar to the trends with the temperatures and are consistent with the flame moving or leaning toward the wall.
+One array was installed in line with the center of the burner, and the other array was installed on the right edge of the burner.
+(The comparisons between the measured heat flux and the FDS simulations are provided in Figure~\ref{FDS_HFCL_IWNG_comp} and Figure~\ref{FDS_HFEdge_IWNG_comp}).
+For the centerline gauges, the trends between the heat flux measurements and the FDS values were similar to the trends with the temperatures and were consistent with the flame moving or leaning toward the wall.
 This resulted in higher heat flux measures relative to the FDS values at the three positions away from the wall.
-When the burner was positioned against the wall the FDS values and the measurements converged to a higher level of agreement.
+When the burner was positioned against the wall, the FDS values and the measurements converged to a higher level of agreement.
 
@@
 
-The FDS values significantly under predict the measured heat flux values along the right edge of the burner.
-The best agreement occurs at the burner positions away from the wall.
-At this position, the fire pattern on the walls show that the lines of demarcation are occurring very close to the edge of the burner.
-Again flame movement seems to to be the main cause of the difference that is accentuated by a measurement location that is very sensitive to heat flux and position.
+The FDS values significantly under-predicted the measured heat flux values along the right edge of the burner.
+The best agreement occurred at the burner positions away from the wall.
+At this position, the fire pattern on the walls showed that the lines of demarcation occurred very close to the edge of the burner.
+Again, flame movement seemed to mainly cause the difference, which was accentuated by a measurement location very sensitive to heat flux and position.
 
@@
 Each graph displays data from a different distance between the edge of the burner and the instrumented wall.
-Beginning with the top left graph position and viewing left to right the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m respectively.}
+Beginning with the top left graph position and viewing left to right, the distances from the wall are 0.61~m, 0.31~m, 0.15~m, and 0~m, respectively.}
   \label{FDS_HFEdge_IWNG_comp}
@@
 Figure~\ref{FDS_IWNG_Flame_comp} shows images from two different locations, from the front of the burner and from the right side of the burner.
-In the top row of Figure~\ref{FDS_IWNG_Flame_comp} the three images exhibit points in time where the flame was moving toward the instrumented wall and away from the vertical array of thermocouples that are positioned above the center line of the burner.
+In the top row of Figure~\ref{FDS_IWNG_Flame_comp}, the three images exhibit points in time when the flame was moving toward the instrumented wall and away from the vertical array of thermocouples positioned above the center line of the burner.
 The bottom row of images are from the same fire experiment looking at it from the front.
@@
 This simulation is comparable to the experiment used for Figure~\ref{FDS_IWNG_Flame_comp}.
-While the simulation does not demonstrate the amount of eddy generation or side to side movement from the front, the image from the side does show that FDS is simulating that the flame is moving toward the wall, although not to the extent that the actual flame did.
+Although the simulation does not demonstrate the amount of eddy generation or side to side movement from the front, the image from the side does show that FDS is simulating that the flame is moving toward the wall, although not to the extent that the actual flame did.
 
@@
   \includegraphics[width=1.5in]{../Figures/IWGB_NG_Front3}      \\
-  \caption[Images of flame movement which are consistent with the measurements and explain the differences between the measured and FDS values.]{FImages of flame movement which are consistent with the measurements and explain the differences between the measured and FDS values.
-The natural gas burner was positioned 0.31~m from the instrumented gypsum board wall.}
+  \caption[Images of flame movement consistent with the measurements and explain the differences between the measured and FDS values.]{Images of flame movement consistent with the measurements explain the differences between the measured and FDS values.
+The natural gas burner was positioned 0.31~m from the instrumented gypsum wallboard.}
   \label{FDS_IWNG_Flame_comp}
@@
   \includegraphics[width=2.3in]{../Figures/FDS_NG_80kW_GBWall_sideview}   \\
-  \caption[Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.] {Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.}
+  \caption[Smokeview images from the FDS RI=10 simulation with the burner positioned at 0.31~m from the wall.] {Smokeview images from the FDS RI=10 simulation with the burner positioned 0.31~m from the wall.}
   \label{FDS_IWNG_SMV_comp}
@@
 
-The flame height range was calculated using the HRRPUL from each of the FDS simulations at each position from the wall and for RI=5 and RI=10.
+The flame height range was calculated using the HRRPUL from each of the FDS simulations at each position from the wall, and for RI=5 and RI=10.
 The peak visible flame height range estimate was developed from the location where the flame exists only 10\% of the time with the 95\% certainty range.
-This information is presented in Table~\ref{tab:FDS_FH_IWNG} displays estimated values from the models using two of the RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
+This information, is presented in Table~\ref{tab:FDS_FH_IWNG}, displays estimated values from the models using two of the RI values as well as the 95~$\%$ certainty range for the peak visible flame height from Chapter 2.
 The course and medium grids, RI=5 and R=10, were not significantly different from the estimations of the peak visible flame height 95~$\%$ certainty value range at the position most remote from the wall.
@@
   \end{tabular}
-  \caption[Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5 and 10.]{Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5, and 10.}
+  \caption[Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5 and 10.]{Comparison of estimations of flame height from the natural gas instrumented wall experiments and FDS simulations with RIs of 5 and 10.}
   \label{tab:FDS_FH_IWNG}
@@
 The program Smokeview uses the numerical results of FDS to create scientific visualizations.
-In this section, comparisons were made between Smokeview generated images and photographs of fire patterns.
-The values from the FDS boundary files are used to examine the temperature of the gypsum wall board and the heat flux exposure to the gypsum wallboard.
-Based on the FDS values, Smokeview can create isosurface areas based on defined boundaries which can be set to a black color to represent a charred area on the target surface.
-This isosurface char technique will be used visualize an FDS generated fire pattern and the peak heights of the fire pattern.
+In this section, comparisons were made between Smokeview-generated images and photographs of fire patterns.
+The values from the FDS boundary files were used to examine the temperature of the gypsum wall board and the heat flux exposure to the gypsum wallboard.
+Based on the FDS values, Smokeview can create isosurface areas based on defined boundaries, which can be set to a black color to represent a charred area on the target surface.
+This isosurface char technique was used visualize an FDS-generated fire pattern and the peak heights of the fire pattern.
 
@@
 
-The criteria for the `charred' area of the gypsum wall board was a threshold temperature of 360$^\circ$C.
-This value was chosen based on the ignition temperature data collected as part of this study and documented in Chapter~5.
+The criteria for the ``charred'' area of the gypsum wall board was a threshold temperature of 360$^\circ$C.
+This value was chosen based on the ignition temperature data collected in this study and documented in Chapter~5.
 
 Keep in mind that this ignition temperature is lower, by more than 150$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
-It is possible that the paint on the surface of the samples used in this study, had an impact or that during the decades between the studies the properties of the material have been changed in someway.
+It is possible that the paint on the surface of the samples used in this study had an impact, or that during the decades between the studies the properties of the material have changed in some way.
 Thermal properties data on the gypsum board paper used in the study was not available from the manufacturer.
 
-The comparisons were made for the natural gas burner fire positioned against a painted gypsum board wall.
+The comparisons were made for the natural gas burner fire positioned against a painted gypsum wallboard.
 Figure~\ref{FDS_FirePattern_comp} displays two Smokeview images.
-In the image on the left the isothermal areas of the wall shown with a temperature range of 20$^\circ$C to greater than 520$^\circ$C.
-The Smokeview image on the right has the `char' feature applied with the threshold temperature of 360$^\circ$C to coincide with cone calorimeter ignition temperature data.
+In the image on the left, the isothermal areas of the wall are shown with a temperature range of 20$^\circ$C to greater than 520$^\circ$C.
+The Smokeview image on the right has the char feature applied with the threshold temperature of 360$^\circ$C to coincide with cone calorimeter ignition temperature data.
 The upper edge of the char area is approximately 1~m above the burner.
 The upper edge of the 520$^\circ$C area in the left image was approximately 0.8~m above the burner.
-This images were generated with the RI=10 model which has grid cells that were 0.04~m in size.
+Those images were generated with the RI=10 model, which had grid cells that were 0.04~m in size.
+
 The FDS images are compared with three photographs of fire patterns from the compartment fire pattern experiments documented in Chapter~6.
@@
 The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% certainty range of $\pm$~0.12~m.
-The simulated fire pattern is taller than the actual patterns.
-However if the upper ignition temperature was used the height values between the actual and the simulated would have been similar.
+The simulated fire pattern was taller than the actual patterns.
+However if the upper ignition temperature was used, the height values between the actual and the simulated would have been similar.
 The RI=10 simulation was used as a means to optimize the graphical resolution, even though the temperature range of the flames were shifted up relative to the RI=5 case.
 
-The visualization parameters for the wall temperature were changed to generate a isosurface `char' pattern in Smokeview.
-Both the ignition temperatures for gypsum wall board from Dillon, 515$^\circ$C, and Quintiere and Harkleroad, 565$^\circ$C, were examined~\cite{Dillon:1998,Quintiere:1985}.
-The result from both temperatures was a small, narrow, oval shaped area.
+The visualization parameters for the wall temperature were changed to generate a isosurface char pattern in Smokeview.
+Both the ignition temperatures for gypsum wallboard from Dillon, (515$^\circ$C), and Quintiere and Harkleroad, (565$^\circ$C), were examined~\cite{Dillon:1998,Quintiere:1985}.
+The result from both temperatures was a small, narrow, oval-shaped area.
 The peak heights of the char areas were 0.60 and 0.48~m above the burner, respectively.
 These values are below the 95\% certainty range of the measured fire pattern height, 0.74$\pm$~0.12~m.
-
-The data from the bench scale experiments have a range that spans more than 200$^\circ$C.
-These values used with Smokeview generated a range of fire pattern shapes and peak fire pattern heights.
+The Smokeview-generated patterns based on these higher ignition temperatures were not representative of the shape of the patterns from the experiments.
+
+The data from the bench-scale experiments had a range that spans more than 200$^\circ$C.
+When used with Smokeview, these values generated a range of fire pattern shapes and peak fire pattern heights.
 The peak fire pattern heights bounded the measured heights.
-However, the lower ignition temperature provided a more realistic shape than the higher ignition temperatures, which provided a shape of such a small size that it was not reproduced here as it was be hard to discern on the printed image.
+However, the lower ignition temperature provided a more realistic shape than the higher ignition temperatures, which provided a shape of such a small size that it was not reproduced here because it was hard to discern on the printed image.
 Clearly more data on the ignition temperature of gypsum wall board is needed to better resolve the actual value.
-Based on the Smokeview tool the ignition temperature would be approximately 400$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
+Based on the Smokeview tool, the ignition temperature would be approximately 400$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
 
@@
 
-The next set of comparisons were made with the natural gas burner fire positioned in the corner against two painted gypsum board walls.
+The next set of comparisons were made with the natural gas burner fire positioned in the corner against two painted gypsum wallboards.
 From the perspective of the impact of the corner on the visual fire behavior, the RI=20 simulation captures the extension of the combustion zone.
-The similarity of the images in Figure~\ref{FDS_Corner_Sequence} and those in Figure~\ref{GBNG34Sequence} is very good.
+The similarity of the images in Figure~\ref{FDS_Corner_Sequence} and those in Figure~\ref{GBNG34Sequence} is very similar.
 
@@
 	\caption[Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner.]{Image sequence of an FDS/Smokeview simulation of the natural gas burner positioned in a corner.
-The time interval between images is 0.3 of second.}
+The time interval between images is 0.3 of a second.}
 	\label{FDS_Corner_Sequence}
 \end{figure}
+
 The comparison between the Smokeview corner fire pattern images and photographs of corner fire patterns are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
 The isotherms in the Smokeview images range from 20$^\circ$C to greater than 360$^\circ$C.
-The `char' area with the threshold value of 360$^\circ$C is shown in the Smokeview image on the right.
+The char area with the threshold value of 360$^\circ$C is shown in the Smokeview image on the right.
 The upper edge of the char image was approximately 1.5~m above the burner.
@@
 The natural gas generated corner fire patterns were similar in height to the natural gas burner generated wall patterns with an average height of 0.74~m.
-The FDS value is approximately twice that.
-Of course changing the ignition temperature to 520$^\circ$C would bring the simulated char height close to the measured values.
+The FDS value was approximately twice that.
+Of course, changing the ignition temperature to 520$^\circ$C would bring the simulated char height close to the measured values.
 
@@
 
-Another difference that was not factored into the model, was the potential change in heat transfer between the corner and the wall experiments.
-For the wall experiments the burner was centered on a void space between the vertical wood studs which formed the frame work of the compartment.
-In the corner,the wood stud walls are attached and wood stud was positioned so that the corner edge of each gypsum wallboard panel could be attached to it.
-As a result there was an additional heat sink extending approximately 35~mm out from the corner om each side and extending the height of the wall.
+A difference not factored into the model was the potential change in heat transfer between the corner and the wall experiments.
+For the wall experiments, the burner was centered on a void space between the vertical wood studs that formed the frame work of the compartment.
+In the corner, the wood stud walls are attached and a wood stud was positioned so that the corner edge of each gypsum wallboard panel could be attached to it.
+As a result, there was an additional heat sink extending approximately 35~mm out from the corner on each side and extending the height of the wall.
 
@@
 Smokeview can be used to provide visuals, based on values from FDS simulations, of instantaneous heat flux exposure to a surface.
-Isosurface controls can be used to define an area with an outer boundary of a given minimum heat flux value.
-Currently, Smokeview cannot generate a time averaged exposure to the surface, therefore the cumulative time history of the heat flux exposure cannot be visualized.
+Isosurface controls can define an area with an outer boundary of a given minimum heat flux value.
+Currently, Smokeview cannot generate a time averaged exposure to the surface, so the cumulative time history of the heat flux exposure cannot be visualized.
 However the Smokeview simulation can be paused and numerical data relative to the geometry taken from the image.
-
-Table~\ref{tab:FDS_CriticalHF_IWNG} has a range of heat flux values that were based on the series of gypsum wall board experiments documented in Chapter 5 where a threshold or critical heat flux was measured to determine the line of demarcation between the burned and unburned section of the painted paper on the wallboard.
-The last two values 25 and 30 kW/m$^2$ bound the ignition heat flux of painted gypsum wall board.
+Picking the maximum point was done by observation.
+This method may add additional uncertainty to the values.
+
+Table~\ref{tab:FDS_CriticalHF_IWNG} has a range of heat flux values based on the series of gypsum wallboard experiments documented in Chapter 5 in which a threshold or critical heat flux was measured to determine the line of demarcation between the burned and unburned section of the painted paper on the wallboard.
+The last two values 25 and 30 kW/m$^2$ bound the ignition heat flux of painted gypsum wallboard.
 The FDS values used for this examination were taken from the FDS simulation (RI=10) of the natural gas burner instrumented wall experiments.
-The peak fire pattern heights based on heat flux from the FDS simulations were compared with the measured peak fire pattern heights of 0.74$\pm$~0.12~m.
-The heights based on heat flux over predicted the height of the fire pattern.
-These result were consistent with the FDS temperature based predictions which also generated fire pattern heights higher than the measured values.
+The peak fire pattern heights based on heat flux from the FDS simulations were compared with the measured peak fire pattern heights of 0.74~$\pm$~0.12~m.
+The heights based on heat flux over-predicted the height of the fire pattern.
+These result were consistent with the FDS temperature-based predictions, which also generated fire pattern heights higher than the measured values.
 
@@
 As noted in the previous chapter, the successful use of any model is using the appropriate data and understanding the basis of the model and any subroutines.
-FDS is a very complex set of equations and subroutines.
+FDS includes a very complex set of equations and subroutines.
 The model authors have done an incredible job providing digital documentation that is searchable and understandable.
@@
 Our understanding of the physical portion of these comparisons may not be as good as the understanding of the theory.
-Hence more research is needed especially on the ignition criteria for gypsum wall board.
+Hence more research is needed, especially on the ignition criteria for gypsum wallboard.
 
 The observations of the flame movement provided some insight into the differences between the model results and the measurements during the wall experiments.
-The model's combustion issues near the burner seem to address the temperature differences in the combustion zone just above the burner.
+The model's combustion issues near the burner seemed to address the temperature differences in the combustion zone just above the burner.
 
@@
 
-The scope of this study has included several series of experiments that ranged in size from bench scale tests with 100~mm sized samples to full scale compartment experiments with samples 2.4~m tall.
-The key objective was to address the National Academy of Science's call for research to address `the natural variability of burn patterns'.
+The scope of this study has included several series of experiments that ranged in size from bench-scale tests with 100~mm sized samples to full-scale compartment experiments with samples 2.4~m tall.
+The key objective was to address the National Academy of Science's call for research to address ``the natural variability of burn patterns''.
 This study examined the repeatability of several similar small fire sources and the pre-flashover fire patterns that were generated by those fires.
 
-In addition a few popular numerical models were used to simulate the effects of the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale experiments, and the full-scale fire experiments conducted as part of this study.
+In addition, a few popular numerical models were used to simulate the effects of the fires and the resulting fire patterns based on input data collected from engineering reference sources, the bench-scale experiments, and the full-scale fire experiments conducted as part of this study.
 The results of the calculations were then compared to the measured values to examine the level of agreement.
@@
 In Chapters 2 through 8, results from specific test series or calculations were presented.
-Typically there was some discussion specific to the experiments or calculations being addressed in each chapter.
-In this chapter the discussion will be more overarching in examining the key outcomes and the remaining gaps.
+Typically there was some discussion specific to the experiments or calculations addressed in each chapter.
+In this chapter, the discussion is more overarching in examining the key outcomes and the remaining gaps.
 
@@
 
-As noted in the Introduction, gypsum wall board was chosen as a target for the fire patterns due to its common usage in construction and the frequency of fires that occur in buildings where gypsum wall board may be used as an interior finish.
+As noted in the Introduction, gypsum wallboard was chosen as a target for the fire patterns due to its common usage in construction and the frequency of fires that occur in buildings in which gypsum wallboard may be used as an interior finish.
 The size of the fires were chosen such that the fire damaged area (paper consumed) of the pattern was contained to less than 2.4~m.
@@
 The fire patterns generated by the natural gas and gasoline fires had a high level of repeatability.
-The 95\% certainty range of the peak fire pattern heights, over 30 experiments from each fuel, was within approximately $\pm$0.1~m.
-The maximum width range of the same experiments was within $\pm$0.07~m.
+The 95\% certainty range of the peak fire pattern heights in over 30 experiments from each fuel, was within approximately $\pm$~0.1~m.
+The maximum width range of the same experiments was within $\pm$~0.07~m.
 The ratio of the height to the width of the the pattern was 3 to 1.
 
-The fire patterns formed by the polyurethane fires, which had an average peak heat release rate almost half of that of the natural gas and gasoline burner fires, had measured certainty ranges for height and width that were similar in magnitude ($\pm$0.12~m and $\pm$0.08~m) to the other two fire sources.
+The fire patterns formed by the polyurethane fires, which had an average peak heat release rate almost half of that of the natural gas and gasoline burner fires, had measured certainty ranges for height and width that were similar in magnitude ($\pm$~0.12~m and $\pm$~0.08~m), respectively to the other two fire sources.
 The polyurethane patterns where almost triangular in shape and had a height to width ratio of almost 1 to 1.
-As a result the percentage difference between the average peak height of the pattern and range of of 95\% certainty was approximately 3 times higher that the percentage differences from the natural gas and gasoline fires.
+As a result, the percentage difference between the average peak height of the pattern and range of of 95\% certainty was approximately three times higher that the percentage differences from the natural gas and gasoline fires.
 
@@
 The median flame height for the gasoline was lower, 0.70~m.
-Examining the visible flame heights determined in Chapter 2, the average peak height of the fire pattern aligns better with the height where the gasoline flame was present for approximately 25\% of the time.
+When examining the visible flame heights determined in Chapter 2, the average peak height of the fire pattern aligned better with the height where the gasoline flame was present for approximately 25\% of the time.
 The gasoline has a radiant fraction that is about twice as high as the natural gas.
-This may account for the additional height on the gasoline fire patterns, relative to the natural gas fire patterns.
-
-An observation from the experiments was that after a period of exposure time, the fire damage to the gypsum wall board would occur within seconds, and then the flame spread on the painted paper would stop and the pattern would not change size for the duration of the burn.
-In one of the compartment fire pattern experiments the natural gas burner was allowed to burn for 15 minutes, yet the pattern did not increase after the initial formation.
+This may account for the additional height on the gasoline fire patterns relative to the natural gas fire patterns.
+
+One observation from the experiments was that after a period of exposure time, the fire damage to the gypsum wallboard would occur within seconds, and then the flame-spread on the painted paper would stop and the pattern would not change size for the duration of the burn.
+In one of the compartment fire pattern experiments, the natural gas burner was allowed to burn for 15 minutes, yet the pattern did not increase after the initial formation.
 This may be due to the steep thermal gradients that occurred at the line of demarcation between burned and not burned.
 
-Both the fire source characterization and the compartment fire pattern experiments, had uncertainties associated with them.
-In the case of the fire source characterization, there were uncertainties associated with the fuel composition itself, the measurement of the heat release rate, temperature, heat flux and flame height.
-The fire pattern experiments had additional uncertainties or assumptions associated with the composition, thickness, and moisture content of the gypsum wall board.
-In both sets of experiments, efforts were made to limit the uncertainties in the fuels, the measurement techniques and the gypsum wallboard.
-one of the key question's was, is there a relationship that can be demonstrated to determine the source fire heat release rate based on the fire pattern?
+Both the fire source characterization and the compartment fire pattern experiments had uncertainties associated with them.
+In the case of the fire source characterization, there were uncertainties associated with the fuel composition itself, the measurement of the heat release rate, temperature, heat flux, and flame height.
+The fire pattern experiments had additional uncertainties or assumptions associated with the composition, thickness, and moisture content of the gypsum wallboard.
+In both sets of experiments, efforts were made to limit the uncertainties in the fuels, the measurement techniques, and the gypsum wallboard.
+One of the key questions was, is there a relationship that can be demonstrated to determine the source fire heat release rate based on the fire pattern?
 
@@
 The associated 95\% confidence limits are also shown for each height.
-For each of the fuels, the 95\% certainty ranges of the fire pattern heights and flame heights overlap indicating that the values, while not an exact match, are similar.
+For each of the fuels, the 95\% certainty ranges of the fire pattern heights and flame heights overlap, indicating that the values, while not an exact match, are similar.
 
@@
 
-Comparing the limited number of fire pattern heights from the instrumented gypsum wall board experiments with the sets of 10 replicates from the compartment fire pattern experiments, show that the peak fire pattern heights were similar.
-Based on these measurements, it would appear that the instrumentation did not impact the fire pattern results.
+Comparing the limited number of fire pattern heights from the instrumented gypsum wallboard experiments with the sets of 10 replicates from the compartment fire pattern experiments show that the peak fire pattern heights were similar.
+Based on these measurements, it would appear the instrumentation did not impact the fire pattern results.
 
@@
 
-In the compartment experiments, where 3 different wall construction methods were used, no significant differences were noted between the patterns generated between the open, closed and insulated construction methods for the walls.
-The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed that the peak temperatures on the backside of the gypsum board were approximately 80$^\circ$C.
-The corresponding peak temperatures on the face of the gypsum wall board ranged from 415 to 540$^\circ$C.
-This demonstrated the insulative capability of the gypsum wall board.
-Given the relatively low energy flow through the gypsum wall board as represented by the limited temperature increase on the backside of the material.
-Therefore with the limited fire exposure time of approximately 300~seconds and the small, pre-flashover fires used in this study, it follows that the additional insulation added with the closed and insulated construction methods would not have created significant temperature differences at the face of the gypsum wallboard.
+In the compartment experiments, which featured three different wall construction methods, no significant differences were noted between the patterns generated in the open, closed, and insulated construction methods for the walls.
+The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed the peak temperatures on the backside of the gypsum board were approximately 80$^\circ$C.
+The corresponding peak temperatures on the face of the gypsum wallboard ranged from 415 to 540$^\circ$C.
+This demonstrated the insulative capability of the gypsum wallboard given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material.
+Therefore, with the limited fire exposure time of approximately 300~seconds and the small, pre-flashover fires used in this study, it follows that the additional insulation added with the closed and insulated construction methods would not have created significant temperature differences at the face of the gypsum wallboard.
 
@@
 
-A few general thoughts to put the numerical methods in perspective.
-In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95\% certainty range of $\pm11\%$.
-This range was the same as that associated with the heat release rate measurement system, so this would be the best agreement that we should expect.
-The gasoline and the polyurethane introduced additional variability and the 95\% certainty ranges on the peak heat release rate values increased to 30\% and 47\% respectively.
-As the physical variability of the experiments increases what is the expectation of numerical methods which simulate the physical experiments
+A few general thoughts to place the numerical methods in perspective.
+In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95\% certainty range of $\pm~11\%$.
+This range was the same as that associated with the heat release rate measurement system, so this would be the best agreement we should expect.
+The gasoline and the polyurethane introduced additional variability, and the 95\% certainty ranges on the peak heat release rate values increased to 30\% and 47\%, respectively.
+As the physical variability of the experiments increases, what is the expectation of numerical methods that simulate the physical experiments?
 
 A statistician, George E.P.
-Box, is credited with the quote, `Essentially, all models are wrong, but some are useful.'  The ability of the numerical methods to simulate the results of the physical experiments was mixed.
-Limited in some cases, by the available input data, inappropriate application, or lack of rigor in the underlying physics.
-That said the models tended to provide enough insight to get a user `in the ballpark'.
+Box, is credited with the quote, ``Essentially, all models are wrong, but some are useful.''  The ability of the numerical methods to simulate the results of the physical experiments was mixed.
+These methods were limited in some cases by the available input data, inappropriate application, or lack of rigor in the underlying physics.
+That said, the models tended to provide enough insight to get a user a reasonable estimate.
 
@@
 Ranges of values were calculated in order to address the uncertainty in the heat release rate measurements.
-Other uncertainties, such as lack of knowledge on the exact fuel composition need to be addressed, as this may well be the case in a real fire investigation.
+Other uncertainties, such as lack of knowledge on the exact fuel composition, must be addressed because this may well be the case in a real fire investigation.
 Even accounting for uncertainties in heat release rate measurement, the flame height estimates tended to be better aligned with the peak flame height than the median flame height.
-A specific coefficient for “gasoline” was used in Heskestad’s equation which resulted in the measured median flame height being within the range of the predictions.
+A specific coefficient for gasoline was used in Heskestad's equation, which resulted in the measured median flame height falling within the range of the predictions.
 The heat flux estimations were calculated with a range of radiant heat fractions, with the intent of the “actual” value being in that range.
-With the exception of gasoline, the estimated heat flux values tended to under predict the measured results.
+With the exception of gasoline, the estimated heat flux values tended to under-predict the measured results.
 Given the limitations of the input data, the algorithms provided reasonable estimates of the mean flame height and the heat flux.
-These algorithms are tools which may be used to provide insight into a problem, but not an accurate single value answer.
+These algorithms are tools that may be used to provide insight into a problem, but not an accurate single value answer.
 
 Mean flame height has been identified by Heskestad and others as having a strong relation to a given heat release rate from fires with a horizontal fuel surface~\cite{Heskestad:SFPE, Beyler:1986}.
-However, the ability to relate the mean flame height to the fire pattern height, based on the limited tests here is best suited to a “steady state” case.
-In cases where transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wall board or other target fuel even for “simple” pre-flashover fire patterns.
+However, the ability to relate the mean flame height to the fire pattern height, based on the limited tests here, is best suited to a “steady state” case.
+In cases when transient fire growth must be considered, flame height alone may not be enough to determine the heat release rate of the fire without further information to enable an energy balance calculation on the gypsum wallboard or other target fuel, even for simple pre-flashover fire patterns.
 
@@
 The simulation with a plume resolution index of 5 (RI=5) provided the best agreement.
-Best agreement in this case meaning that the predicted temperature and heat flux values were within the experimental uncertainty of the measured values.
+Best agreement in this case meant that the predicted temperature and heat flux values were within the experimental uncertainty of the measured values.
 The flame height calculated using the HRRPUL provided similar results to the measured values.
-Other RIs were tried and provided results that provided less agreement, therefore it seems critical that end users ensure that they have chosen a grid size that best represents the scale of fire flow field being modeled.
+Other RIs were tried and provided results that provided less agreement, so it seems critical that end users ensure they have chosen a grid size that best represents the scale of fire flow field being modeled.
 
@@
 The amount of displacement in the physical experiments exceeded the simulated displacement.
-This resulted in poor agreement, meaning simulated values outside of the uncertainty bounds of the measured values.
-Once the burner was positioned against the wall the simulated values and the measured temperature values converged.
+This resulted in poor agreement, with simulated values falling outside of the uncertainty bounds of the measured values.
+Once the burner was positioned against the wall, the simulated values and the measured temperature values converged.
 
 The flame and plume movement issue carried through the predicted conditions on the wall surface for both the temperature and the centerline heat flux values.
-The simulated values trended with the measured values but the level of agreement between was mixed.
-The worst agreement was observed at the vertical heat flux array positioned on the edge of the burner.
-As the burner was moved closer to the wall the agreement between the measurement and the predicted heat flux be came worst.
-This was due to the steep thermal gradient along the vertical edge as evidenced by the fire pattern line of demarcation between the burned and unburned paper on the gypsum wall board.
-In the physical experiments the flames moved over the sensors, while in the simulation the flames seem to be offset from the sensors which resulted in under-predicted heat flux values especially at the positions closer to the wall.
-
-The numerical methods are useful tools for gaining insight into fire behavior but in many cases many would require specific experimental data for input or for validation before the results could be relied upon for fire investigation use.
+The simulated values trended with the measured values, but the level of agreement between them was mixed.
+The worst agreement was observed with the vertical heat flux array positioned on the edge of the burner.
+As the burner was moved closer to the wall, the agreement between the measurement and the predicted heat flux moved apart.
+This was due to the steep thermal gradient along the vertical edge as evidenced by the fire pattern line of demarcation between the burned and unburned paper on the gypsum wallboard.
+In the physical experiments, the flames moved over the sensors, while in the simulation the flames seem to be offset from the sensors, which resulted in under-predicted heat flux values, especially at the positions closer to the wall.
+
+The numerical methods are useful tools for gaining insight into fire behavior, but in many cases they would require specific experimental data for input or for validation before the results could be relied upon for fire investigation use.
 
@@
 
-In Chapter 1, as the investigator, you had completed your review of the scene and had collected evidence which included an electric heater.
+In Chapter 1, as the investigator you had completed your review of the scene and had collected evidence, which included an electric heater.
 You are not sure sure about the fire's progression or the area of origin.
 Before leaving the scene, you meet up with the fire captain and begin asking him about the fire.
-The captain tells you that the doors and windows of the townhouse were closed upon arrival.
-When the front door was opened heavy smoke flowed out, followed by flames.
+The captain tells you the doors and windows of the townhouse were closed upon arrival.
+When the front door was opened, heavy smoke flowed out, followed by flames.
 Other fire fighters were venting the upstairs windows.
@@
 
-Comparing the captain's description with your scene, it would seem that the fire started and burned as a fuel-limited fire, before transitioning to a ventilation limited 
-fire, where the heat and fuel where adequate to sustain combustion, but perhaps oxygen was in short supply.
-This fits the description of the fire flaring up and exiting the front door, shortly after it was opened.
+Comparing the captain's description with your scene, it would seem that the fire started and burned as a fuel-limited fire, before transitioning to a ventilation-limited 
+fire in which the heat and fuel where adequate to sustain combustion, but perhaps oxygen was in short supply.
+This fits the description of the fire flaring up and exiting the front door shortly after it was opened.
 With the information that other firefighters were opening the upstairs windows at this time, you starting thinking about the flow path in the town home.
@@
 In the upstairs bedroom there was mostly smoke damage and no significant heat damage.
-It seems that the open bedroom window served as a smoke exhaust vent.
+It seems the open bedroom window served as a smoke exhaust vent.
 
 The large V pattern on the wall behind the sofa and the stair wall may have been generated after the door and upstairs window was opened.
-This is an area where the fuel rich hot fire gases would mix with fresh air entering the front door and burn.
-Area of the living room that was more remote from the front door, the source of oxygen, did not have as much fire damage.
-You remember that there was fire damage to the wall behind the right side of the sofa.
+This is an area where the fuel-rich hot fire gases would mix with fresh air entering the front door and burn.
+The area of the living room more remote from the front door, (the source of oxygen), did not have as much fire damage.
+You remember there was fire damage to the wall behind the right side of the sofa.
 This burned area on the wall seems distinct and disconnected from the area with the most fire damage, which is to the left of the sofa.
-You decide to go back in the town house for another look, Figure~\ref{Pre_Flashover_Pattern}.
-The pattern behind the sofa had to be generated early in the fire event as it is away from the front door.
-Further the wall behind the sofa between this pattern and the larger area of fire damage closer to the front door was protected and not exposed to flaming combustion.
-The inside of the sofa's seat frame was charred on the inside but not on the outside in the area in front of this pattern.
-The bottom of pattern is located near the base of the sofa seat cushion.
+
+You decide to go back in the town house for another look Figure~\ref{Pre_Flashover_Pattern}.
+The pattern behind the sofa had to be generated early in the fire event because it is away from the front door.
+Further, the wall behind the sofa between this pattern and the larger area of fire damage closer to the front door was protected and not exposed to flaming combustion.
+The inside of the sofa's seat frame was charred on the inside but not on the outside in the area in front of this pattern, Figure~\ref{Table}.
+The bottom of the pattern is located near the base of the sofa seat cushion.
 The pattern height is approximately 0.7~m high extending just above the top of the wood sofa frame.
@@
 Unknowns include the impact of the back portion of the sofa, but this fire size seems reasonable to you with regard to the vision of a sofa cushion burning.
-This information coupled with sequence of events provided by the fire captain and other fire damage would indicate that the right side of the sofa is likely the area of origin, even though it does not have the most fire damage.
-You still need to interview the occupants, was an accidental ignition due to careless smoking possible?
-or a lithium ion battery powered device?
-Also you are still going to check if the heater switch was in the on position, if not that further supports your current hypothesis about the right side of the sofa.
+This information, coupled with the sequence of events provided by the fire captain and other fire damage, indicate the right side of the sofa is likely the area of origin even though it does not have the most fire damage.
+You still need to interview the occupants.
+Was an accidental ignition due to careless smoking possible?
+Or a lithium ion battery powered device?
+Also, you will still check if the heater switch was in the on position.
+If not, that further supports your current hypothesis about the right side of the sofa.
 You will also take samples of the debris in the area of the right seat cushion to send to the lab.
@@
 If needed, you have the dimensions of the house and the opening so you could have a computer model of the house made to examine how long it would take a small fire to decrease the level of the oxygen within the house to 15\%.
-This might be needed to get insight on a time line that you might get from the interviews of the occupants.
+This might prove necessary to get insight on a time line you might get from the interviews of the occupants.
 
@@
 	\includegraphics[width=5in]{../Figures/Pre_Flashover_Pattern} \\
-	\caption[Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.]{Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.}
+	\caption[Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.]{Photograph showing the wall with the standalone fire pattern toward the right side of the sofa.}
 	\label{Pre_Flashover_Pattern}
@@
 
-N.B.
-This section was included to provide a sense of how a fire investigator might use their knowledge of fire behavior, fire patterns, and numerical methods to assist them in following the scientific method.
-Fire investigation requires significantly more than pattern interpretation, the totality of facts from the whole situation must gathered to the extent possible and then after analysis of the evidence, a fire cause may be determined.
+N.B.: This section was included to provide a sense of how a fire investigator might use their knowledge of fire behavior, fire patterns, and numerical methods to assist them in following the scientific method.
+Fire investigation requires significantly more than pattern interpretation.
+The totality of facts from the whole situation must gathered to the extent possible, and then after analysis of the evidence, a fire cause may be determined.
 
@@
 
-This study examined a very limited set of conditions as a means to provide a baseline for future research efforts that would expand on the results from this study in order more completely address the National Academy of Science ...
+This study examined a very limited set of conditions to provide a baseline for future research efforts that would expand on the results to completely address the National Academy of Science ...
 natural repeatability of fire patterns~\cite{Forensic:2009}.
-Since the National Academy of Science report was issued in 2009, the  the U.S.
-National Institute of Justice, Fire and Arson Investigation Technology Working Group has identified 5 areas where scientific research is needed: (1) understanding of the effects of ventilation on fire damage and patterns; (2) characterization of electrical system response as a means to study fire progression; (3) repeatability and reproducibility of test measurements of large-scale structure fires, (4) materials property data inputs for accurate computer models, and (5) evaluation of incident heat flux profiles to walls and neighboring items in support of fire model validation~\cite{NIJ:2016}.
-The areas suggested for future research in this study involve 4 of the 5 topic areas from the NIJ working group.
+Since 2009, when the National Academy of Science report was issued, the U.S.
+National Institute of Justice (NIJ), Fire and Arson Investigation Technology Working Group has identified five areas that need scientific research: 1) understanding of the effects of ventilation on fire damage and patterns; 2) characterization of electrical system response as a means to study fire progression; 3) repeatability and reproducibility of test measurements of large-scale structure fires; 4) materials property data inputs for accurate computer models; and 5) evaluation of incident heat flux profiles to walls and neighboring items in support of fire model validation~\cite{NIJ:2016}.
+The areas suggested for future research in this study involve four of the five topic areas from the NIJ working group.
 
@@
 
-While the results from this project provided a baseline regarding the repeatability of pre-flashover fire patterns, a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions, are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
-
-Pre-flashover experiments in compartments using well characterized burner fires should be conducted with a broad range of heat release rates, burn durations, and varied burner sizes to determine if the repeatability results from this study can be replicated.
+The results from this project provided a baseline regarding the repeatability of pre-flashover fire patterns, but a significant amount of research examining other fuels, wall coverings, the impacts of compartmentation, ventilation, and post-flashover conditions are just a few of the parameters that need to be examined to develop a more complete understanding of fire patterns.
+
+Pre-flashover experiments in compartments using well-characterized burner fires should be conducted with a broad range of heat release rates, burn durations, and varied burner sizes to determine if the repeatability results from this study can be replicated.
 
 The flow field between the burner and the adjacent wall or walls should have further research conducted to better understand the movement of the flame and the plume.
-This may also lead to improved information on the side to side motion of the flame when the burner was against the wall.
-
-Research on fire patterns also needs to be conducted with fuels similar to those that the fire investigators will encounter in the field, such as furnishings and appliances. 
-These fuels release fuel from 3-dimensional surfaces, as opposed to a 2-dimensional burner surface,  In addition, many furnishing items are composed of thermoplastic materials which may melt, flow and drip, potentially spreading the fire and changing the fire pattern during the course of the burn.
+This may also lead to improved information on the side-to-side motion of the flame when the burner was against the wall.
+
+Research on fire patterns also needs to be conducted with fuels similar to those fire investigators will encounter in the field, such as furnishings and appliances. 
+These fuels release fuel from three-dimensional surfaces, as opposed to a two-dimensional burner surface.
+In addition, many furnishing items are composed of thermoplastic materials that may melt, flow, and drip, potentially spreading the fire and changing the fire pattern during the course of the burn.
 
 There is a great need to understand the impact of ventilation on fire patterns within a structure.
-Fires that stop pre-flashover as well as fires that burn post-flashover need to be studied.
-The structure itself will have an impact on the movement and flow of both fresh air to the fire as well as containing and channeling the movement of combustion products away from the fire, both of which can affect the development of the fire pattern.
-Post-flashover fires are particularly challenging for fire investigators as the potential is high that significant fire damage may be generated remote from the area of origin.
+Fires that stop pre-flashover and fires that burn post-flashover need study.
+The structure itself will have an impact on the movement and flow of both fresh air to the fire and containing and channeling the movement of combustion products away from the fire, both of which can affect the development of the fire pattern.
+Post-flashover fires are particularly challenging for fire investigators because the potential is high significant fire damage may be generated remote from the area of origin.
 
 There is a need for continued research on materials used in construction and other furnishings (first items ignited).
-Since the start of this study, a few notable items have changed that may challenge the investigators.
-The gypsum wall board used in this study is considered to be regular gypsum wall board, it was widely used and would be what was readily available at construction material supply stores across the U.S.
-Today, the regular gypsum board has been replaced on store shelves by a less dense version of 12.7~mm thick gypsum wall board.
-A finished lightweight gypsum wall board panel has 30\% less mass than the regular gypsum wall board that was the de facto construction standard just a few years ago.
+Since the start of this study, a few notable items have changed that may challenge investigators.
+For example, the gypsum wallboard used in this study is considered to be regular gypsum wallboard, it was widely used and it was readily available at construction material supply stores across the United States.
+Today, however, the regular gypsum board has been replaced on store shelves by a less dense version of 12.7~mm thick gypsum wallboard.
+This lightweight gypsum wallboard panel has 30\% less mass than the regular gypsum wallboard that was the de facto construction standard just a few years ago.
 How the lightweight gypsum wall board degrades when exposed to fire has not been quantified.
@@
 
-NFPA 921, Guide for Fire and Explosion Investigations considers mathematical modeling techniques as a means to provide the fire investigator with tools for testing hypotheses regarding the origin and cause of the fire and the cause of the resulting damage to property or injury to people.
-NFPA 921 cautions that `mathematical modeling, whether simplified hand calculations or computer fire models, has inherent limitations and assumptions that should be considered.
+NFPA 921, Guide for Fire and Explosion Investigations, considers mathematical modeling techniques to provide the fire investigator with tools for testing hypotheses regarding the origin and cause of the fire.
+NFPA 921 cautions that ``mathematical modeling, whether simplified hand calculations or computer fire models, has inherent limitations and assumptions that should be considered.
 Models generally rely upon empirical data and are validated via comparison with other empirical data.
-Care must be taken to assure that the model is being used with due regard for limitations, assumptions, and validation'~\cite{NFPA:921}.
-In these experiments, the natural gas burner and the gasoline pool fire were the type of fire source that the models were developed with or have been validated against.
-Basically the burners provided fire sources that were very repeatable and could generally be defined by the two dimensional planar surface where the fuel is emitted.
-
-Fire investigators, however, examine fire scenes where the first item ignited may have involved a piece of furniture, an appliance, or even a car.
-These items are three dimensional and the fuel could be emitted from multiple surfaces at any given time in the fire event.
+Care must be taken to assure that the model is being used with due regard for limitations, assumptions, and validation''~\cite{NFPA:921}.
+In these experiments, the natural gas burner and the gasoline pool fire were the type of fire source the models were developed with or have been validated against.
+Basically, the burners provided fire sources that were very repeatable and could generally be defined by the two-dimensional planar surface where the fuel was emitted.
+
+Fire investigators, however, examine fire scenes in which the first item ignited may have involved a piece of furniture, an appliance, or even a car.
+These items are three- dimensional, and the fuel could be emitted from multiple surfaces at any time in the fire event.
 Further thermoplastics are commonly used in the construction of these items, with furniture being a prevalent item.
-As the thermoplastic is heated it melts, flows, drips, and burns.
-As a result the flame geometry generated by a piece of furniture may not be representative of the flame geometry characterized by the studies using gas burners and pool fires.
-In this study even using a block of polyurethane foam with a simple geometry led to increased uncertainty of the peak heat release rate and decreased fire pattern repeatability.
-
-While all of the experimental studies recommended in the previous section may support model validation studies, it is important that a specific validation study be conducted with fuels normally found in real fire investigations to determine the applicability of various numerical methods under realistic fire conditions.
+As the thermoplastic is heated, it melts, flows, drips, and burns.
+As a result, the flame geometry generated by a piece of furniture may not be representative of the flame geometry characterized by the studies using gas burners and pool fires.
+In this study, even using a block of polyurethane foam with a simple geometry led to increased uncertainty of the peak heat release rate and decreased fire pattern repeatability.
+
+Although all of the experimental studies recommended in the previous section may support model validation studies, it is important that a specific validation study be conducted with fuels normally found in real fire investigations to determine the applicability of various numerical methods under realistic fire conditions.
 
@@
 The main objective of this research study was to examine the repeatability of pre-flashover fire patterns on gypsum wallboard.
-The patterns were generated from exposure to short duration (300 s maximum) well characterized fires.
+The patterns were generated from exposure to short duration (300 seconds maximum), well characterized fires.
 
@@
 The variation in the average peak heat release rate with the natural gas was similar to the expanded uncertainty of the measurement system, $\pm$ 11\%.
-However the variation in the average peak heat release rates of the gasoline and the polyurethane foam increased due to uncertainties in the burning behavior of the fuels.
-The average peak heat release rate of gasoline had a 95\% confidence limit of $\pm$30\% and the same value for the polyurethane foam was $\pm$47\%.
+However, the variation in the average peak heat release rates of the gasoline and the polyurethane foam increased due to uncertainties in the burning behavior of the fuels.
+The average peak heat release rate of gasoline had a 95\% confidence limit of $\pm$~30\% and the same value for the polyurethane foam was $\pm$~47\%.
 
 The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18\% or less based on a Type A statistical analysis with 95\% confidence limits.
-The patterns generated by the polyurethane foam fueled fire, had more than twice the variability of the natural gas and the gasoline fire patterns.
+The patterns generated by the polyurethane foam fueled fire had more than twice the variability of the natural gas and the gasoline fire patterns.
 This was likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
 
-The comparison of the fire pattern heights and the mean flame heights demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
-This trend was the same as exhibited by the repeatability of the heat release rate measurements.
-Given that the heat release rate from the fires was the source of the energy transferred to the walls to generate the fire patterns.
-It stands to reason that the greater the uncertainty in the heat release rate, the greater the uncertainty in the resulting pattern and any associated thermal measurements.
-
-This paper also highlighted the many uncertainties that need to be considered in what appear to be simple fire experiments.
-There were a variety of uncertainties related to the composition of the fuels, measurement methods, and analysis techniques just to list a few of the areas considered.
-
-Another objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and bench-scale and full-scale fire experiments conducted as part of this study.
+The comparison of the fire pattern heights and the mean flame heights demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement, and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
+This trend was the same as that exhibited by the repeatability of the heat release rate measurements.
+Given the heat release rate from the fires was the source of the energy transferred to the walls to generate the fire patterns, it stands to reason the greater the uncertainty in the heat release rate, the greater the uncertainty in the resulting pattern and any associated thermal measurements.
+
+This paper also highlighted the many uncertainties that must be considered in what appear to be simple fire experiments.
+There were a variety of uncertainties related to the composition of the fuels, measurement methods, and analysis techniques, just to list a few of the areas considered.
+
+Another objective of this study was to examine the capability of numerical models to simulate the fires and the resulting fire patterns based on input data collected from engineering reference sources, and this study's bench-scale and full-scale fire experiments.
 The numerical tools used ranged from simple empirical algorithms to a computational fluid dynamics model.
-Each of the tools are freely available to investigators and many of the tools have been packaged in a form that allows the user to input the ``data'' and generate a result.
+Each of the tools are freely available to investigators, and many of the tools have been packaged in a form that allows the user to input ``data'' and generate a result.
 There is also graphical user interface software available to aid with the development of the computational fluid dynamics model.
@@
 A range of methods used to simulate characteristics of fires were applied using data from the source fire experiments as input.
-The algebra based predictions for heat flux to a target under predicted the measured values.
+The algebra based predictions for heat flux to a target under-predicted the measured values.
 The gasoline fueled fires had the best agreement of 22\% or less for the heat flux predictions.
-The polyurethane foam results exhibited the worst agreement with difference of at least 40\% between the measured and calculated values.
+The polyurethane foam results exhibited the worst agreement with a difference of at least 40\% between the measured and calculated values.
 Improved understanding of the radiative fraction from different fuels would improve the capability of the predictions.
@@
 The gasoline fueled fires released the highest amount of energy and had a higher radiative fraction than the natural gas and polyurethane foam fueled fires.
-The flame height algorithm tended to over predict the values for the natural gas and the polyurethane fueled fires.
-
-The agreement between the values predicted by the computational fluid dynamic model, FDS, and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates as well as examples with poor agreement.
-The differences were a result, in some cases, by limitations within the combustion sub-model close to the burner surface.
-In those cases as the distance between the burner surface increased the predicted values tended to converge with the measured values.
+The flame height algorithm tended to over-predict the values for the natural gas and the polyurethane fueled fires.
+
+The agreement between the values predicted by the computational fluid dynamic model (FDS) and the measurements from these experiments demonstrated examples of agreement that were within the measurement uncertainty estimates, as well as examples with poor agreement.
+The differences were a result, in some cases, of limitations within the combustion sub-model close to the burner surface.
+In those cases, as the distance between the burner surface increased, the predicted values tended to converge with the measured values.
 
@@
 The horizontal flame movements observed during the experiments were not simulated to the same degree by the model.
-Since areas around the flame have steep thermal gradients small differences in position can result in large differences in temperature and heat flux.
-
-The models proved to be useful tools for gaining insight into fire behavior but in many cases the models require specific experimental data for input or for validation.
-The availability of well characterized input data is limited and data for newer materials is unavailable.
+Because areas around the flame have steep thermal gradients, small differences in position can result in large differences in temperature and heat flux.
+
+The models proved useful for gaining insight into fire behavior, but in many cases the models require specific experimental data for input or validation.
+The availability of well-characterized input data is limited, and data for newer materials is unavailable.
 Additional research is needed for modeling data development protocols.

### 2017-03-30 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
?

@@
 Uncertainties related to fuel type, measurement methods, and analysis techniques were examined.
-The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 s maximum), well characterized fires.
+The objective of the research was to examine the repeatability of pre-flashover fire patterns generated from exposure to short duration (300 seconds maximum), well characterized fires.
 Three different fuels were used: natural gas, gasoline, and polyurethane foam.

### 2017-03-30 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Final Draft
march 29

@@
 \usepackage{url}
+\urlstyle{same}
 \frenchspacing
@@
 
+Table~\ref{tab:FDS_IGNT_CHF_Wall} summarizes the peak fire pattern heights predicted for the compartment experiments with the natural gas burner position against the wall.
+The values were determined using both the char feature in Smokeview with ignition temperatures for the gypsum wallboard ranging from 360$^\circ~C$ to 565$^\circ~C$ and heat flux values ranging from 15~kW/m$^2$ to 30.0~kW/m$^2$.
+In addition the table presents values for all three of the RI cases (5,10, 20).
+The measured value to use for comparison is 0.74~$\pm$~0.12.
+As with the initial source fire comparison, the RI=5 model provides the best agreement, not only with the peak height but also with the shape of the char area that was produced.
+The best agreement occurs either at an ignition temperature of 360$^\circ~C$ or a critical heat flux of 30.0~kW/m$^2$.
+Genrally the heat flux-generated values over-predicted the measured values.
+
 \begin{table}[h]
@@
   \begin{tabular}{|c|c|c|c|} \hline 
-Char Criteria 					&  \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	  	  \\
+Char Criteria 					&  \multicolumn{3}{c} {Peak Wall Fire Pattern Height from Smokeview (m)}	  	  \\
 \hline								&  RI=5					&  RI=10			&  RI=20               \\
@@
 \hline  CHF=20.0~kW/m$^2$			&  1.04					& 1.36				&   1.36                \\
-\hline	CHF=25.~kW/m$^2$		&  0.88					& 1.28				&   1.26 	            \\
+\hline	CHF=25.0~kW/m$^2$			&  0.88					& 1.28				&   1.26 	            \\
 \hline  CHF=30.0~kW/m$^2$   		&  0.80					& 1.12				&   1.16			    \\  \hline
@@
 
+Table~\ref{tab:FDS_IGNT_CHF_Corner} summarizes the peak fire pattern heights predicted for the compartment experiments with the natural gas burner position in the corner.
+The values were determined as described for the table above.
+The measured value to use for comparison is 0.74~$\pm$~0.13.
+Again, the RI=5 model provides the best agreement, not only with the peak height but also with the shape of the char area that was produced.
+The best agreement occurs either at an ignition temperature of 565$^\circ~C$.
+All of the other values were significantly over-predicted.
+The trends that were shown before with the model predictions are repeated with the Smokeview analysis, as it should be.
+
 \begin{table}[h]
@@
   \begin{tabular}{|c|c|c|c|} \hline 
-Char Criteria 					& \multicolumn{3}{c} {Peak Wall Fire Pattern Height from FDS Smokeview (m)}	\\
+Char Criteria 					& \multicolumn{3}{c} {Peak Wall Fire Pattern Height from Smokeview (m)}	\\
 \hline								&  RI=5					&  RI=10			&  RI=20           		 \\
@@
 
-This study examined a very limited set of conditions to provide a baseline for future research efforts that would expand on the results to completely address the National Academy of Science ...
-natural repeatability of fire patterns~\cite{Forensic:2009}.
+This study examined a very limited set of conditions to provide a baseline for future research efforts that would expand on the results to completely address the National Academy of Sciences' call for research on the natural repeatability of fire patterns~\cite{Forensic:2009}.
 Since 2009, when the National Academy of Science report was issued, the U.S.

### 2017-08-20 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
KM Comments & CAF Figures JPG

@@
 A range of methods used to simulate characteristics of fires were applied using data from the source fire experiments as input.
-The algebra-based predictions for heat flux to a target under-predicted the measured values.
+The empirical-based predictions for heat flux to a target under-predicted the measured values.
 The gasoline fueled fires exhibited best agreement of 22\% or less for the heat flux predictions.
@@
 At the end of this chapter, an example of a fire incident is presented.
-In Chapter 9, we will return to the example again.
+In Chapter 9, the example fire incident will be revisited.
 
@@
 In 2013, there were 3,240 civilian fire fatalities, or 1.02 deaths per 100,000 people~\cite{Karter:2014}.
-During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.24 million fires.
+During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.2 million fires.
 There are many reasons that led to this decrease in loss of life due to fire in the United States.
 One example is research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs.
-None of this happened without the constant effort of agencies at the federal, state, and local levels working with professional fire organizations in order to deliver the five E’s of fire prevention: engineering, education, enforcement, economic Incentive, and emergency Response~\cite{FEMA:2013}.
+None of this happened without the constant effort of agencies at the federal, state, and local levels working with professional fire organizations in order to deliver the five E’s of fire prevention: engineering, education, enforcement, economic incentive, and emergency response~\cite{FEMA:2013}.
 
@@
 However, an investigative report by Icove and Hargrove indicates arson fires are underreported to the U.S.
-National Fire Incident Reporting System (NFIRS).
+National Fire Incident Reporting System (NFIRS)~\cite{Icove_2014}.
 The investigation provided examples from several major cities, such as New York City.
@@
 As provided by the document scope, it ``is designed to assist individuals who are charged with the responsibility of investigating and analyzing fire and explosion incidents and rendering opinions as to the origin, cause, responsibility, or prevention of such incidents, and the damage and injuries which arise from such incidents.'' The document’s purpose includes the goal to be ``a model for the advancement and practice of fire and explosion investigation, fire science, and methodology.'' However, NFPA~921 can only incorporate the fire science and research results that have been produced.
-Although NFPA~921 is a guide as opposed to a standard, it is considered the standard of care for the fire investigation community in countries that recognize and use NFPA standards and guides.
+Although NFPA~921 is a guide as opposed to a standard, it is considered the \textit{standard of care} for the fire investigation community in countries that recognize and use NFPA standards and guides.
 
@@
 The summary assessment of analysis of explosives evidence is positive, ``the scientific foundations exist to support the analysis of explosions, because such analysis is based primarily on well-established chemistry''~\cite{Forensic:2009}.
-The complete summary assessment for fire debris analysis states: ``By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
+The complete summary assessment for fire debris analysis states:
+
+\begin{quotation}
+By contrast, much more research is needed on the natural variability of burn patterns and damage characteristics and how they are affected by the presence of various accelerants.
 Despite the paucity of research, some arson investigators continue to make determinations about whether or not a particular fire was set.
 However, according to testimony presented to the committee, many of the rules of thumb that were typically assumed to indicate that an accelerant was used (e.g., alligatoring of wood, specific char patterns) have been shown not to be true.
-Experiments should be designed to put arson investigations on a more solid scientific footing.''
+Experiments should be designed to put arson investigations on a more solid scientific footing.
+\end{quotation}
+
 This study is in response to the assessment above, specifically regarding the natural variability of fire patterns.
@@
 
-The majority of intentional fires in structures have occurred in residential occupancies, so this study focused on fire patterns on painted gypsum wallboard, which is a common interior finish for residential occupancies.
+The majority of intentional fires in structures in the United States have occurred in residential occupancies, so this study focused on fire patterns on painted gypsum wallboard, which is a common interior finish for residential occupancies.
 A common height for a residential occupancies is 2.4~m.
@@
 You notice that three of the four windows on the second floor have been removed.
-On side D of the town home, there are no openings and no smoke or fire damage is present.
-On the rear or side C of the house, the door and windows are intact but open.
+On the right side of the town home, there are no openings and no smoke or fire damage is present.
+On the rear of the house, the door and windows are intact but open.
 There are no smoke stains and no thermal damage around any of the openings on the rear.
-No sign of smoke alarms in the home.
 
@@
 This may be an indicator that the origin of the fire is closer to the front of the living room.
-Between the two wood cabinets on the D wall of the living room there is a wood framed sofa.
+Between the two wood cabinets on the right wall of the living room there is a wood framed sofa or futon.
 The cushions show thermal damage from pyrolysis.
-It is not clear that they were on fire because there is no thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
-Still standing in the entry doorway, you turn your attention to the remains of an upholstered sofa and chair.
+It is not clear that they were actually aflame because there is no thermal damage on the wall directly above the top of the sofa cushions that would indicate the presence of a thermal plume.
+Still standing in the entry doorway, you look almost straight ahead to the remains of an upholstered sofa and chair.
 The wall behind the sofa and chair has extensive thermal damage.
@@
 The further you move from the stairs, the less thermal damage you find.
-
-You head back down the stairs to further examine the living room, which appears to be the room of fire origin.
-Your focus on the area with the most damage, the area with the sofa and chair.
+There is no sign of smoke alarms in the home.
+
+You head back down the stairs to further examine the living room, which based on the fire damage appears to be the room of fire origin.
+You focus on the area with the most damage, the area with the sofa and chair.
 You think this may be the area of origin.
 
-As you look toward the B wall of the living room, you note that the right side of the chair is badly burned, and burned from the floor level up.
-The same is true from the left side of the sofa.
+As you look again at the chair between the stair and the sofa, you note that the right side of the chair is badly burned, and burned from the floor level up.
+The same is true for the left side of the sofa.
 In fact, the left side of the sofa has more fire damage to its wood frame than the right side.
@@
 
-A series of experiments were conducted to characterize a limited set of  residential scale, pre-flashover/early growth stage fires.
+A series of experiments was conducted to characterize a limited set of  residential scale, pre-flashover/early growth stage fires.
 A fixed fire source footprint, 30.5~cm square, was chosen for this study, and a range of common fuels that could be found in and around a residence were selected.
@@
 
-The gasoline pan fire used 500~mL of unleaded, 87 octane gasoline.
+The gasoline pan fire used 500~mL of unleaded gasoline with an octane rating of 87, which is the average of the research octane and motor octane numbers.
 The pan was constructed from 6~mm thick steel.
@@
 According to the Polyurethane Foam Association, flexible polyurethane foam is the most widely used cushioning material in upholstered furnishings and mattresses.
-More than 1.2 billion pounds are produced in the U.S.
+More than 544 million kg are produced in the U.S.
 every year~\cite{Foam,Polyurethane_Foam}.
@@
 
-The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory's 3~m x 3~m hood oxygen consumption calorimeter.
+The source fire characterization experiments were conducted in the NIST Large Fire Research Laboratory's 3~m by 3~m hood oxygen consumption calorimeter.
 This apparatus follows the methodology of ASTM~E 2067-08, {\em Standard Practice for Full-Scale Oxygen Consumption Calorimetry Fire Tests} ~\cite{ASTM_E2067}.
@@
 
-The NIST Large Fire Research Laboratory's 3~m x 3~m oxygen depletion calorimeter had an estimated peak heat release rate capacity of approximately 700~kW.
-Details on the operation and uncertainty in measurements associated with NIST's 6~m x 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
+The NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter had an estimated peak heat release rate capacity of approximately 700~kW.
+Details on the operation and uncertainty in measurements associated with NIST's 6~m by 6~m oxygen consumption calorimeter were documented by Bryant et al.~\cite{Bryant:2004}.
 Many of the same instruments were shared between the two calorimeters and calibration burns were conducted during each experimental series.
@@
 The thermocouple was ungrounded.
-The standard uncertainty in temperature of the thermocouple wire itself is 2.2$^\circ$C at 277$^\circ$C and increases to 9.5$^\circ$C at 871$^\circ$C as determined by the wire manufacturer.
+The standard uncertainty in temperature of the thermocouple wire itself is 2.2~$^\circ$C at 277~$^\circ$C and increases to 9.5~$^\circ$C at 871~$^\circ$C as determined by the wire manufacturer.
 The response time constant is approximately 0.2~seconds~\cite{Omega}.
@@
 
-The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91~m x 1.2~m x 12~mm thick supported by the load cell.
+The fires were centered under the hood of the calorimeter on a non-combustible platform measuring 0.91~m by 1.2~m by 12~mm thick supported by the load cell.
 The load cell had a resolution of 1.0~g~\cite{Mettler}.
@@
 The natural gas flow to the burner was measured in terms of volumetric flow with a dry test meter that was corrected for temperature and pressure.
-The flow rate was determined to be 2.1~liters per second.
+The flow rate was determined to be 2.1~L/s.
 This yielded a mass flow of natural gas of approximately 2~g/s.
@@
   \includegraphics[width=\textwidth]{../Figures/Schematic_Drawing}\\
-  \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus, which was centered under the 3~m x 3~m oxygen consumption calorimeter.
+  \caption[Diagram of the source fire flame and plume instrumentation apparatus]{Diagram of the source fire flame and plume instrumentation apparatus, which was centered under the 3~m by 3~m oxygen consumption calorimeter.
 The heat flux gauges were facing toward the center of the burner/fuel area.}
@@
   \includegraphics[width=\textwidth]{../Figures/Source_Fire_Flamer}\\
-  \caption[A photograph of the source fire flame and plume instrumentation apparatus]{A photograph of the source fire flamer and plume instrumentation apparatus, which was centered under the 3~m x 3~m hood of the oxygen consumption calorimeter.
+  \caption[A photograph of the source fire flame and plume instrumentation apparatus]{A photograph of the source fire flame and plume instrumentation apparatus, which was centered under the 3~m by 3~m hood of the oxygen consumption calorimeter.
 In the foreground from left to right are the video, 35~mm SLR, and thermal imaging cameras.}
@@
 The block of polyurethane foam demonstrated the largest variability of the three fuels in terms of peak heat release rate and time to peak heat release.
-Similar to the gasoline that began with a fixed quantity of fuel which was ignited and burned to completion, the polyurethane foam also generated bell shaped heat release rate curve.
+Similar to the gasoline that began with a fixed quantity of fuel which was ignited and burned to completion, the polyurethane foam also generated a bell shaped heat release rate curve.
 Because the duration of the heat release rate peaks were less than those of the gasoline, the peak heat release rate averaging was performed over a 15~second interval bounding the peak heat release rate from each of the 10 experiments.
@@
 Each experiment was recorded with a digital video camera at a refresh rate frequency of 29.97~fps, which is the National Television Standards Committee (NTSC) standard.
-The resulting image in each frame was 720 pixels wide x 480 pixels high.
+The resulting image in each frame was 720 pixels wide by 480 pixels high.
 Segments of the video which corresponded to the peak heat release of each experiment were captured with a video editing program.
@@
 
-A free standing steel frame wall with a 12.7~mm thick, 2.44~m high x 1.22~m wide calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
+A free standing steel frame wall with a 12.7~mm thick, 2.44~m high by 1.22~m wide calcium silicate board face was instrumented to measure the thermal exposure of the wall from the fire in terms of temperature and heat flux.
 Marinite Type I is the commercial name of the non-combustible board used in these experiments.
@@
 The photograph in Figure~\ref{Instrumented_Wall_Detail_Rear_TC_photo} shows a rear thermocouple with the bead in contact with the rear surface of the wall and the relative position to the thermocouple on the front surface of the wall.
-In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory's 3~m x 3~m oxygen depletion calorimeter.
+In a manner similar to the source fire characterization experiments, the instrumented wall experiments were conducted under the NIST Large Fire Research Laboratory's 3~m by 3~m oxygen depletion calorimeter.
 
@@
 Figures~\ref{TC_Surf_Cent_TWNG_comp} and \ref{TC_Surf_Edge_TWNG_comp} show consistent trends of the thermocouple temperatures in the vertical arrays on the wall increasing as the burner was moved toward the wall.
-Figure~\ref{TC_Back_Center_TWNG_comp} shows that the peak temperatures aligned with the vertical center of the burner on the backside of the gypsum wallboard peaked at approximately 100$^\circ$C.
+Figure~\ref{TC_Back_Center_TWNG_comp} shows that the peak temperatures aligned with the vertical center of the burner on the backside of the gypsum wallboard peaked at approximately 100~$^\circ$C.
 
@@
 Temperatures were also measured on the backside of the wall along the vertical centerline of the burners, see Figure~\ref{NCTW_Back_Cent_comp}.
-The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner versus the corresponding temperatures on the backside of the wall show a difference of at least 400$^\circ$C.
+The temperature difference between the peak average temperatures on the front (fire side) of the wall at 0.2~m above the burner versus the corresponding temperatures on the backside of the wall show a difference of at least 400~$^\circ$C.
 It is consistent with the temperature data shown in Figures~\ref{NCTW_Surf_Center_comp} and \ref{NCTW_Surf_Edge_comp} that as the burners were moved away from the wall, the temperature differences decreased.
@@
 The gypsum wallboard used in these experiments was purchased from the same manufacturer in an effort to have the most similar panels for use between the experiments.
-Each 1.22~m x 2.44~m x 12.7~mm thick panel weighed approximately 30.5~kg.
+Each 1.22~m by 2.44~m by 12.7~mm thick panel weighed approximately 30.5~kg.
 The thermal properties of the gypsum wallboard panels are given in the Table~\ref{tab:Gypsum wallboard_Thermal_Properties}.
@@
 Schroeder conducted a study on the post-fire analysis of construction materials, including gypsum.
-As gypsum is heated to temperatures above 80$^\circ$C it begins to change phase and degrade.
+As gypsum is heated to temperatures above 80~$^\circ$C it begins to change phase and degrade.
 Continued heating causes some of the chemically bound water to disassociate, and the gypsum changes to a hemihydrate.
-This transformation occurs in the range of 98$^\circ$C to 130$^\circ$C.
+This transformation occurs in the range of 98~$^\circ$C to 130~$^\circ$C.
 With additional heating, the residue of the gypsum continues to transform and soften, turning into anhydrite, a process commonly known as calcination.
-Schroeder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80$^\circ$C (dihydrate phase), 200$^\circ$C (hemihydrate phase), and 500$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
+Schroeder exposed samples of gypsum to a range of heat fluxes and temperatures to determine the time for 80~$^\circ$C (dihydrate phase), 200~$^\circ$C (hemihydrate phase), and 500~$^\circ$C (anhydrous phase) isotherms to penetrate to different depths in the gypsum.
 The crystal phase and the depth of penetration of the phase change was determined with the use of X-ray diffraction~\cite{Schroeder:1999}.
@@
 		\hline Distance From Wall  	& Natural Gas 		& Gasoline			& Polyurethane Foam \\
-		\hline (m) 					& Number of Tests 	& Number of Tests  	& Number of Tests 	\\ 
+		\hline (m) 					& No. of Tests 		& No. of Tests  	& No. of Tests 	    \\ 
 		\hline 0.61 				& 1 				& 1 				& 2 			 	\\
@@
 As the position of the fire moves closer to the wall, the rate of temperature rise on the back increases.
-The peak temperatures in each case were approximately 80$^\circ$C.
+The peak temperatures in each case were approximately 80~$^\circ$C.
 
@@
 In other words, the range of expanded uncertainty values overlap.
-For example, at 0.0~m position with natural gas, the average peak temperature was 487$^\circ$C~$\pm$73$^\circ$C (15\%).
-So, the upper bound would be 560$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539$^\circ$C.
+For example, at 0.0~m position with natural gas, the average peak temperature was 487~$^\circ$C~$\pm$73~$^\circ$C (15\%).
+So, the upper bound would be 560~$^\circ$C, which includes the corresponding averaged peak value from the instrumented gypsum wallboard experiments of 539~$^\circ$C.
 While all of the values do not have overlapping uncertainties, the point is that none of the averaged peak values are substantially different.
@@
 The source of the heat flux is a pre-mixed, air-gas-fueled radiant panel.
-The radiating surface measures 305~mm x 457~mm.
+The radiating surface measures 305~mm by 457~mm.
 The radiating surface is inclined 30~$^{\circ}$ above the horizontal.
@@
  With the flooring radiant panel test, the incident heat flux from the panel and the pre-heated gypsum wallboard sample enables flame spread for approximately 500~s.
-The temperatures prior to ignition ranged from an average of 315$^{\circ}$C for the 100~mm position to 242$^{\circ}$C for the 400~mm position.
+The temperatures prior to ignition ranged from an average of 315~$^{\circ}$C for the 100~mm position to 242~$^{\circ}$C for the 400~mm position.
 
@@
 This trend may be indicative of the combustion of the paint and paper adding to the energy at the face of the sample.
-The temperatures at which the change in rate of temperature rise occurred are between 300 and 400$^{\circ}$C.
-The temperature curve representing the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300$^{\circ}$C after more than 400~seconds of exposure.
+The temperatures at which the change in rate of temperature rise occurred are between 300 and 400~$^{\circ}$C.
+The temperature curve representing the 15~kW/m$^2$ experiments also demonstrates an increase in the rate of temperature rise beginning at approximately 300~$^{\circ}$C after more than 400~seconds of exposure.
 
@@
 This chapter was anticipated to provide data that correlated better than it does, although this should not have been a surprise given the wide range of thermal exposures (10 to 75~kW/m$^2$).
-The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature, but the reason for the approximately 200$^{\circ}$C difference could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum wallboard material properties over longer exposure times.
+The ignition temperatures measured in the cone calorimeter experiments conducted as part of this study do not align with the data in the published literature, but the reason for the approximately 200~$^{\circ}$C difference could not be resolved other than potential issues with thermocouple mounting, the use of paint, or changes to the gypsum wallboard material properties over longer exposure times.
 
@@
 The compartments were constructed on top of a portable wood floor platform.
-Each of the test compartments consisted of three 3.6~m long x 2.4~m high wood framed walls.
-The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90~mm x 38~mm.
-A partial ceiling with a width of at least 1.2~m (measured from the back wall of the compartment) was installed across the width of the compartment, which allowed for the plume to impact the ceiling and form a ceiling jet along the back wall before the fire gases flowed up and out of the compartment and into the 6~m x 6~m hood in the NIST Large Fire Research Laboratory.
+Each of the test compartments consisted of three 3.6~m long by 2.4~m high wood framed walls.
+The wood elements of the frame were composed of kiln-dried fir with a nominal cross section of 90~mm by 38~mm.
+A partial ceiling with a width of at least 1.2~m (measured from the back wall of the compartment) was installed across the width of the compartment, which allowed for the plume to impact the ceiling and form a ceiling jet along the back wall before the fire gases flowed up and out of the compartment and into the 6~m by 6~m hood in the NIST Large Fire Research Laboratory.
 The interior surface of the walls and ceiling was composed of 12.7~mm thick, regular core gypsum wallboard.
@@
 From the instrumented gypsum wallboard experiments, the peak temperatures on the backside of the wallboard occurred when the burners were positioned against the wall.
-The peak temperatures were similar for all of the fuels (approximately 80$^\circ$C), although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
+The peak temperatures were similar for all of the fuels (approximately 80~$^\circ$C), although the duration of the higher temperatures on the rear of the wallboard was longer for the natural gas and the gasoline fueled burners.
 Therefore the wall construction experiments were conducted with only the natural gas and gasoline fueled burners because the impact of insulating the back of the walls exposed to the fuels with the highest energy would produce the most significant differences, if any, to the fire patterns.
@@
 	\caption{Schematic of heat flux estimation using the point source assumption.}
-	\label{PointSourceHF},
-\end{figure},
+	\label{PointSourceHF}
+\end{figure}
 
@@
 One means of potentially improving the predictions would be to use radiative fractions known to represent of the fuels.
-For example, recommended values in the literature for the $chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
+For example, recommended values in the literature for the $\chi_r$ of natural gas range from 0.15 to 0.25 for similar sized burners~\cite{Hostikka:3,McCaffrey:1982}.
 The default radiative fraction of 0.35 is in line with the values found in the literature for gasoline~\cite{Hamins:1991,McGrattan:2000}.
@@
 Appropriate fuels would include liquid pool fires and other horizontal surface fires~\cite{Heskestad:SFPE,Beyler:1986}.
+It is noted that the empirical data used to develop this algorithm did not include fires against walls or in corners.
 The inputs required to use the model are the heat release rate and the diameter of the base of the fire or the burner.
@@
 
-Once again, the average peak heat release rates from Chapter 2 were used.
+The average peak heat release rates from Chapter 2 were used.
 The natural gas and the gasoline fueled burners both had an average peak heat release rate of 80~kW.
@@
 Overall the Heskestad equation provided reasonable estimates of the median flame height.
+However, the use of the Heskestad equation may not be appropriate for predicting the fire damage on a wall since the empirical data upon which the alorithm is based did not include any obstructions of the air entrainment to the flame.
 The key to the successful use of any model regardless of the simplicity or complexity is using the appropriate data and understanding the basis of the algorithm in order to assess any underlying assumptions.
@@
 For the 20~mm case, the computational domain was divided into eight uniform meshes.
-Each mesh was 2.4~m x 1.2~m, and 0.6~m tall.
+Each mesh was 2.4~m by 1.2~m, and 0.6~m tall.
 The time domain for each model was chosen to be 300 seconds, which is similar to the burn time for each of the fuels.
@@
 Not surprisingly, the sub model of the thermocouple device shifted the FDS values slightly.
-At temperatures greater than 700$^\circ$C, the THERMOCOUPLE temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
-At temperatures less than 700$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
+At temperatures greater than 700~$^\circ$C, the THERMOCOUPLE temperatures tended to be lower than the gas temperatures, perhaps due to radiant heat transfer losses.
+At temperatures less than 700~$^\circ$C, the `THERMOCOUPLE' temperatures tended to be a higher than the gas temperatures, perhaps due to gains from radiant heat transfer.
 The best agreement along the vertical array of temperatures was provided by the RI=5 model.
@@
 These changes include the loss of homogeneity of the gypsum material, a change in density, and, as the paper is charred or burned, potential change in emissivity.
-The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500$^\circ$C~\cite{Gross:1985}.
+The thermal conductivity and the specific heat of the gypsum wallboard varies on the order of 20~$\%$ over the temperature range from 20 to 500~$^\circ$C~\cite{Gross:1985}.
 While FDS can accommodate changes in thermo-conductivity and specific heat with respect to time, density, and emissivity must remain constant~\cite{FDS_Users_Guide}.
@@
 
-The criteria for the ``charred'' area of the gypsum wall board was a threshold temperature of 360$^\circ$C.
+The criteria for the ``charred'' area of the gypsum wall board was a threshold temperature of 360~$^\circ$C.
 This value was chosen based on the ignition temperature data collected in this study and documented in Chapter~5.
 
-Keep in mind that this ignition temperature is lower, by more than 150$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
+Keep in mind that this ignition temperature is lower, by more than 150~$^\circ$C, than other values for the ignition temperature of gypsum wallboard in the literature~\cite{Dillon:1998,Babrauskas:2003}.
 It is possible that the paint on the surface of the samples used in this study had an impact, or that during the decades between the studies the properties of the material have changed in some way.
@@
 Figure~\ref{FDS_FirePattern_comp} displays two Smokeview images.
-In the image on the left, the isothermal areas of the wall are shown with a temperature range of 20$^\circ$C to greater than 520$^\circ$C.
-The Smokeview image on the right has the char feature applied with the threshold temperature of 360$^\circ$C to coincide with cone calorimeter ignition temperature data.
+In the image on the left, the isothermal areas of the wall are shown with a temperature range of 20~$^\circ$C to greater than 520~$^\circ$C.
+The Smokeview image on the right has the char feature applied with the threshold temperature of 360~$^\circ$C to coincide with cone calorimeter ignition temperature data.
 The upper edge of the char area is approximately 1~m above the burner.
-The upper edge of the 520$^\circ$C area in the left image was approximately 0.8~m above the burner.
+The upper edge of the 520~$^\circ$C area in the left image was approximately 0.8~m above the burner.
 Those images were generated with the RI=10 model, which had grid cells that were 0.04~m in size.
@@
 The three images from left to right exhibit a range of fire pattern heights from approximately 0.7 to 0.8~m.
-The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% certainty range of $\pm$~0.12~m.
+The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% certainty range of $\pm$0.12~m.
 The simulated fire pattern was taller than the actual patterns.
@@
 The visualization parameters for the wall temperature were changed to generate a isosurface char pattern in Smokeview.
-Both the ignition temperatures for gypsum wallboard from Dillon, (515$^\circ$C), and Quintiere and Harkleroad, (565$^\circ$C), were examined~\cite{Dillon:1998,Quintiere:1985}.
+Both the ignition temperatures for gypsum wallboard from Dillon, (515~$^\circ$C), and Quintiere and Harkleroad, (565~$^\circ$C), were examined~\cite{Dillon:1998,Quintiere:1985}.
 The result from both temperatures was a small, narrow, oval-shaped area.
@@
 
-The data from the bench-scale experiments had a range that spans more than 200$^\circ$C.
+The data from the bench-scale experiments had a range that spans more than 200~$^\circ$C.
 When used with Smokeview, these values generated a range of fire pattern shapes and peak fire pattern heights.
@@
 Clearly more data on the ignition temperature of gypsum wall board is needed to better resolve the actual value.
-Based on the Smokeview tool, the ignition temperature would be approximately 400$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
+Based on the Smokeview tool, the ignition temperature would be approximately 400~$^\circ$C to generate a char pattern with a similar height and shape as the measured fire patterns.
 
@@
   \includegraphics[width=.625\columnwidth]{../Figures/GBNGreps_w_1m_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned against the wall.
 The image with the three replicate fire patterns has a red line indicating a position approximately 1.0~m above the burner.
-This height corresponds with the height of the top of the 360$^\circ$C mark in the FDS image.}
+This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
   \label{FDS_FirePattern_comp}
@@
 The comparison between the Smokeview corner fire pattern images and photographs of corner fire patterns are presented in Figure~\ref{FDS_FirePattern_Corner_comp}.
-The isotherms in the Smokeview images range from 20$^\circ$C to greater than 360$^\circ$C.
-The char area with the threshold value of 360$^\circ$C is shown in the Smokeview image on the right.
+The isotherms in the Smokeview images range from 20~$^\circ$C to greater than 360~$^\circ$C.
+The char area with the threshold value of 360~$^\circ$C is shown in the Smokeview image on the right.
 The upper edge of the char image was approximately 1.5~m above the burner.
@@
 The FDS value was approximately twice that.
-Of course, changing the ignition temperature to 520$^\circ$C would bring the simulated char height close to the measured values.
+Of course, changing the ignition temperature to 520~$^\circ$C would bring the simulated char height close to the measured values.
 
@@
   \includegraphics[width=.8\columnwidth]{../Figures/NGCorner_guideline}\\
-  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
+  \caption[FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 360~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner]{FDS fire pattern surrogates based on 40~mm grid using a threshold temperature of 350~$^\circ$C compared with three replicate fire patterns from the natural gas burner positioned in the corner.
 The image with the three replicate fire patterns has a red line indicating a position approximately 1.5~m above the burner.
-This height corresponds with the height of the top of the 360$^\circ$C mark in the FDS image.}
+This height corresponds with the height of the top of the 360~$^\circ$C mark in the FDS image.}
   \label{FDS_FirePattern_Corner_comp}
@@
 Table~\ref{tab:FDS_IGNT_CHF_Wall} summarizes the peak fire pattern heights predicted for the compartment experiments with the natural gas burner position against the wall.
-The values were determined using both the char feature in Smokeview with ignition temperatures for the gypsum wallboard ranging from 360$^\circ~C$ to 565$^\circ~C$ and heat flux values ranging from 15~kW/m$^2$ to 30.0~kW/m$^2$.
+The values were determined using both the char feature in Smokeview with ignition temperatures for the gypsum wallboard ranging from 360~$^\circ$C to 565~$^\circ$C and heat flux values ranging from 15~kW/m$^2$ to 30.0~kW/m$^2$.
 In addition the table presents values for all three of the RI cases (5,10, 20).
@@
 As with the initial source fire comparison, the RI=5 model provides the best agreement, not only with the peak height but also with the shape of the char area that was produced.
-The best agreement occurs either at an ignition temperature of 360$^\circ~C$ or a critical heat flux of 30.0~kW/m$^2$.
-Genrally the heat flux-generated values over-predicted the measured values.
+The best agreement occurs either at an ignition temperature of 360~$^\circ$C or a critical heat flux of 30.0~kW/m$^2$.
+Generally the heat flux-generated values over-predicted the measured values.
 
@@
 \hline								&  RI=5					&  RI=10			&  RI=20               \\
-\hline Tign=360$^\circ~C$  			&  0.72					&  1.04				&	0.86			    \\
-\hline Tign=515$^\circ~C$			&  0.48					&  0.72				&   0.62                \\
-\hline Tign=565$^\circ~C$			&  na					&  na				&   na                  \\ 
+\hline Tign=360~$^\circ$C  			&  0.72					&  1.04				&	0.86			    \\
+\hline Tign=515~$^\circ$C		&  0.48					&  0.72				&   0.62                \\
+\hline Tign=565~$^\circ$C			&  na					&  na				&   na                  \\ 
 \hline  CHF=15.0~kW/m$^2$			&  1.36     			& 1.44 		        &   1.40                \\
@@
 Again, the RI=5 model provides the best agreement, not only with the peak height but also with the shape of the char area that was produced.
-The best agreement occurs either at an ignition temperature of 565$^\circ~C$.
+The best agreement occurs either at an ignition temperature of 565~$^\circ$C.
 All of the other values were significantly over-predicted.
@@
 \hline								&  RI=5					&  RI=10			&  RI=20           		 \\
-\hline Tign=360$^\circ~C$  			&  1.60					&  1.56				&  1.56				    \\
-\hline Tign=515$^\circ~C$			&  1.04					&  0.96				&  0.96                 \\
-\hline Tign=565$^\circ~C$			&  0.72					&  na				&  na                   \\
+\hline Tign=360~$^\circ$C  			&  1.60					&  1.56				&  1.56				    \\
+\hline Tign=515~$^\circ$C			&  1.04					&  0.96				&  0.96                 \\
+\hline Tign=565~$^\circ$C			&  0.72					&  na				&  na                   \\
 \hline  CHF=15.0~kW/m$^2$			&  2.08    				&  1.84		        &  1.94                 \\
@@
 \hline  CHF=20.0~kW/m$^2$			&  1.92					&  1.76				&  1.86	                \\
-\hline	CHF=25.~kW/m$^2$			&  1.76     			&  1.68				&  1.80	                \\
+\hline	CHF=25.0~kW/m$^2$			&  1.76     			&  1.68				&  1.80	                \\
 \hline  CHF=30.0~kW/m$^2$   		&  1.44 				&  1.60				&  1.60   				\\  \hline
@@
 In the compartment experiments, which featured three different wall construction methods, no significant differences were noted between the patterns generated in the open, closed, and insulated construction methods for the walls.
-The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed the peak temperatures on the backside of the gypsum board were approximately 80$^\circ$C.
-The corresponding peak temperatures on the face of the gypsum wallboard ranged from 415 to 540$^\circ$C.
+The results from the instrumented gypsum wallboard experiments in Chapter 4, which represented an open construction type of wall, showed the peak temperatures on the backside of the gypsum board were approximately 80~$^\circ$C.
+The corresponding peak temperatures on the face of the gypsum wallboard ranged from 415 to 540~$^\circ$C.
 This demonstrated the insulative capability of the gypsum wallboard given the relatively low energy flow through the gypsum wallboard as represented by the limited temperature increase on the backside of the material.
@@
 In Chapter 1, as the investigator you had completed your review of the scene and had collected evidence, which included an electric heater.
-You are not sure sure about the fire's progression or the area of origin.
+You are not sure about the fire's progression or the area of origin.
 Before leaving the scene, you meet up with the fire captain and begin asking him about the fire.

### 2017-08-31 Projects/Madrzykowski_Thesis/Report/Madrzykowski_Thesis.tex
Annotate Figures, correct ref save final revision

@@
 During this same period, the number of fires in the United States has decreased from 2.5 million fires to 1.2 million fires.
+
 There are many reasons that led to this decrease in loss of life due to fire in the United States.
 One example is research and data that enabled the development of product safety standards, improved building codes, improved fire safety systems, and fire prevention programs.
-None of this happened without the constant effort of agencies at the federal, state, and local levels working with professional fire organizations in order to deliver the five E’s of fire prevention: engineering, education, enforcement, economic incentive, and emergency response~\cite{FEMA:2013}.
-
-Fire investigation is a key element in the fire prevention system that generates data to enable the reduction of fire losses.
+None of this happened without the constant effort of agencies at the federal, state, and local levels working with professional fire organizations in order to deliver the five E’s of fire prevention: engineering, education (of the public), enforcement, economic incentive, and emergency response~\cite{FEMA:2013}.
+
+Fire investigation is one element in the fire prevention system that generates data to enable the reduction of fire losses.
 The investigation of fires provides a means to identify the cause of the fire in order to develop a knowledge base that could enable the elimination of that cause, and thus further reduce the losses from fires.
@@
 Consumer Product Safety Commission or a manufacturer issuing a product recall.
+There are two notable and recent examples of this process.
+As result of reports of fire and overheating incidents, 1.9 million Samsung Galaxy Note7 Smartphones and 0.5 million hoverboards were recalled in 2016~\cite{CPSC:Samsung,CPSC:Hoverboards}.
 
@@
 \subsection{The Use of Fire Models in Fire Investigation}
-Fire models are another tool that may be used by a fire investigation team to gain insight into the growth and development of a fire and to test the investigators' hypothesis on origin and cause~\cite{Sutula:2001}.
+Fire models are another tool that may be used by an engineer on a fire investigation team to gain insight into the growth and development of a fire and to test the investigators' hypothesis on origin and cause~\cite{Sutula:2001}.
 Many theoretical and empirical correlations and computational fire models have been developed for use in fire protection design, fire hazard analysis, and fire investigation.
@@
 
+Despite the current validation studies, the implementation of fire models for a room and contents fire in a home is challenging for a number of reasons which include; the lack of appropriate input data, the differences between well characterized fuels used for validation studies and the fuels found in homes, ventilation limited fire behavior, and the inability to reliably predict failure of windows or wall systems (i.e.
+changes in ventilation).
+
 Because fire pattern interpretation and analysis is a critical step in most fire investigations, it is surprising to find the limited amount of research and analysis tools directly related to this practice.
@@
 
+The topic of fire pattern repeatability covers scenarios that could range from a small kitchen fire to a multi-compartment, multi-story fire in a commercial building.
+Therefore the scope of study had to be narrowed considerably.
+
 The majority of intentional fires in structures in the United States have occurred in residential occupancies, so this study focused on fire patterns on painted gypsum wallboard, which is a common interior finish for residential occupancies.
 A common height for a residential occupancies is 2.4~m.
-With a wall height of 2.4~m, these experiments used small fires with flame heights of approximately 1.2~m.
-The resulting patterns on the gypsum board wall were be representative of a pre-flashover fire pattern.
+With a wall height of 2.4~m, these experiments designed for small fires with flame heights of approximately 1.2~m in order to allow for additional vertical flame spread on the wall, without exceeding the height of the wall.
+The resulting patterns on the gypsum board wall were representative of a pre-flashover fire pattern.
 
@@
 The fires were characterized in terms of heat release rate, mass loss rate (when appropriate), plume temperature, heat flux, and visible flame height.
+While conducting scoping studies the size of the burner or fuel surface area was determined.
+
+One parameter that needed to be considered was time.
+These fires were intended to represent the generation of a pre-flashover burn pattern in a residential scale room.
+Studies conducted in residential scale structures with furnished rooms showed that the fire development in the room of origin was reduced due to ventilation limits within 5 minutes or less after ignition of a bed or upholstered furniture item with a flaming ignition source~\cite{Kerber:2010,Madrzykowski:2009}.
+Even in cases where the compartment transitioned through flashover, the fire in the area of origin may have stopped burning due to a localized lack of oxygen.
+A burn time of 300 seconds was chosen.
+
+Time is not a critical factor when using a natural gas fueled burner.
+However, the 300 second limit was also a practical consideration to ensure that enough gasoline or polyurethane foam could be repeatably and reliably supplied to burn for the duration of a given experiment.
 
@@
 
+The critical heat flux boundary has been defined in full scale experiments as the limit of fire propagation by Newman and Tewarson~\cite{Newman}.
+This concept has also been identifed in bench scale radiant panel tests~\cite{Adams:1977}.
+
 A series of experiments were conducted with samples of painted gypsum wallboard to determine the repeatability of a critical heat flux that results in a clear line of demarcation, a burn/no burn line.
@@
 Cone calorimeter experiments were conducted, based on ASTM~E 1354, to estimate the ignition temperature, the time to ignition, and the heat release rate from samples of painted gypsum wallboard under thermal flux conditions ranging from 25~kW/m$^2$ to 75~kW/m$^2$ ~\cite{ASTM_E1354}.
-
+{}
 \subsection{Numerical Fire Pattern Analysis}
-
+{}
 The ability to recreate or simulate a fire pattern or certain characteristics of a fire pattern was examined with a variety of tools.
@@
 
-The chair has more unburned foam cushioning then the sofa does, and the seat cushion is still in place with it's distinctive shape, so you know that cushion has not been moved.
+The chair has more unburned foam cushioning then the sofa does, and the seat cushion is still in place with its distinctive shape, so you know that cushion has not been moved.
 The cushion was heated from the top down.
@@
 based on averaged data from 2005 through 2009~\cite{Ahrens:2011,Evarts:2011}.
+Between 2007 and 2011, 11\% of all of the mattress and bedding fires and 9\% of all of the upholstered furniture fires in the United states were ignited by smoking materials.
+Fires ignited with smoking material are a leading cause of fatal fires, with 29\% and 31\% of all fatal fires involving mattresses and bedding, and upholstered furniture, respectively~\cite{Hall:2013}.
+For this study, the polyurethane foam would be ignited with a small flame to reduce some of the uncertainties associated with a smoldering cigarette ignition.
 
@@
 The gauges were mounted to uprights of the steel instrumentation support frame on opposite sides of the fire.
+
+For several of the source fire characterization fires, an additional Schmidt-Boelter total heat flux gauges was positioned 2~m located 0.95~m horizontally from the center of the burner/fuel and 0.50~m above the top of the burner/pan lip/fuel surface.
+These 3 gauges were used to measure the heat flux to determine the radiative fraction for each fuel.
 
@@
 
-The calculations for the intensity field are based on a user-defined computation grid.
+The calculations for the time-averaged cumulative light intensity field are based on a user-defined computation grid.
 A grid sensitivity analysis was conducted with 5~mm, 10~mm, 20~mm, 40~mm, and 80~mm square grids.
 Examples of grid cell resolution outputs from Streams for the natural gas fueled burner are shown in Fig.~\ref{Intensity}.
-The outputs shown are time-averaged intensity fields generated with the resolutions listed above.
+The outputs shown are time-averaged light intensity fields generated with the resolutions listed above.
 In each output the x and y axis dimensions are in millimeters.
@@
 	\includegraphics[trim=0in 0in 3.5in 0in,clip=true,width=1.7in]{../Figures/FHNG80_1_GS_80mm_10s_color}\\
-	 \caption[Comparison images of intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of intensity fields derived from the video images of the natural gas fueled fire using Streams.
+	 \caption[Comparison images of time-averaged light intensity fields derived from the video images of the natural gas fueled fire]{Comparison images of time-averaged light intensity fields derived from the video images of the natural gas fueled fire using Streams.
 The images, starting with the upper left, were generated with 5~mm, 10~mm, 20~mm, 40~mm, and 80~mm resolutions.}
@@
 \begin{figure}
-  \includegraphics[width=2.7in]{../Figures/Fig20}
+  \includegraphics[width=2.42in]{../Figures/Fig20}
   \includegraphics[width=2.7in]{../Figures/Fig21} \\
@@
 Perhaps as a result of increased convection on the face of the wall.
+the distance that the flame moved toward the wall varied.
+At 0.15~m distance from the wall, after 150 to 200~ seconds, the flame would intermittently contact the wall.
 
@@
 In one widely used text, a table listing radiative energy fraction values for burner diameters larger than 0.5~m lists butane in the 20 to 40 $\%$ range and hexane in the 40 to 60 $\%$ range ~\cite{Quintiere:1997}.
-So, it is possible that the radiative fraction for natural gas could be higher that the radiative fraction associated with methane.
+So, it is possible that the radiative fraction for natural gas could be higher than the radiative fraction associated with methane.
 The radiative fraction value in the literature for gasoline is 0.45~\cite{Quintiere:1997, IAAI:2017}.
@@
 The three images from left to right exhibit a range of fire pattern heights from approximately 0.7 to 0.8~m.
-The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% certainty range of $\pm$0.12~m.
+The average height of the natural gas fire patterns from this open wall construction series was 0.74 with a 95\% uncertainty range of $\pm$0.12~m.
 The simulated fire pattern was taller than the actual patterns.
@@
 A few general thoughts to place the numerical methods in perspective.
-In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95\% certainty range of $\pm~11\%$.
+In the experimental portion of this study, we established with the gas burner experiments that the steady state heat release rate values had a 95\% uncertainty range of $\pm~11\%$.
 This range was the same as that associated with the heat release rate measurement system, so this would be the best agreement we should expect.
-The gasoline and the polyurethane introduced additional variability, and the 95\% certainty ranges on the peak heat release rate values increased to 30\% and 47\%, respectively.
+The gasoline and the polyurethane introduced additional variability, and the 95\% uncertainty ranges on the peak heat release rate values increased to 30\% and 47\%, respectively.
 As the physical variability of the experiments increases, what is the expectation of numerical methods that simulate the physical experiments?
+
+In this study, a single oxygen consumption calorimeter was used to measure the HRRs of the source fuels used in this study.
+This calorimeter has been associated with a validation study and was calibrated throughout the study~\cite{Bryant:2003b}.
+In 2000, Janssens conducted a round robin study on the repeatability of heat release rates from full scale oxygen consumption furniture calorimeters.
+The study involved 4 laboratories, each burning 3 replicates of 4 different fuels.
+The range of relative repeatability standard deviations were 16 to 58\% and 34 to 69\% for peak HRR and total heat released, respectively~\cite{Janssens:2002}.
+The lack of uniformity of the results from these measurement devices is of concern and is clearly another area that needs to be researched and addressed, especially if a single organization is going to be generating HRR data for database or modeling input purposes.
 
@@
 In Chapter 1, as the investigator you had completed your review of the scene and had collected evidence, which included an electric heater.
-You are not sure about the fire's progression or the area of origin.
+At this point, you are not sure about the fire's progression or the area of origin.
 Before leaving the scene, you meet up with the fire captain and begin asking him about the fire.
@@
 When the front door was opened, heavy smoke flowed out, followed by flames.
-Other fire fighters were venting the upstairs windows.
+Other fire fighters were venting the upstairs windows on the front of the townhouse.
 The fire grew and burned for a short time before water was applied through the front door and the fire was knocked down.
 
-Comparing the captain's description with your scene, it would seem that the fire started and burned as a fuel-limited fire, before transitioning to a ventilation-limited 
-fire in which the heat and fuel where adequate to sustain combustion, but perhaps oxygen was in short supply.
+\subsection{Hypothesis Testing, Applying Fire Dynamics}
+
+Comparing the captain's description with your scene and applying your knowledge of fire dynamics, it would seem that the fire started and burned as a fuel-limited fire, before transitioning to a ventilation-limited fire in which the heat and fuel where adequate to sustain combustion, but perhaps oxygen was in short supply.
 This fits the description of the fire flaring up and exiting the front door shortly after it was opened.
-With the information that other firefighters were opening the upstairs windows at this time, you starting thinking about the flow path in the town home.
-The front door served as a bi-directional vent with the lower portion serving as an air inlet and the upper portion serving as an exhaust for flames.
+With the information that other firefighters were opening the upstairs windows at this time, you begin thinking about the flow path in the town home.
+The front door served as a bi-directional vent with the lower portion serving as the air (oxygen) inlet and the upper portion serving as an exhaust for flames and combustion products.
 In the upstairs bedroom there was mostly smoke damage and no significant heat damage.
@@
 
-The large V pattern on the wall behind the sofa and the stair wall may have been generated after the door and upstairs window was opened.
+The large V pattern on the corner behind the chair next to the stair wall may have been generated post-flashover, after the flow paths between the front door and upstairs window were opened.
 This is an area where the fuel-rich hot fire gases would mix with fresh air entering the front door and burn.
-The area of the living room more remote from the front door, (the source of oxygen), did not have as much fire damage.
-You remember there was fire damage to the wall behind the right side of the sofa.
-This burned area on the wall seems distinct and disconnected from the area with the most fire damage, which is to the left of the sofa.
-
-You decide to go back in the town house for another look Figure~\ref{Pre_Flashover_Pattern}.
-The pattern behind the sofa had to be generated early in the fire event because it is away from the front door.
-Further, the wall behind the sofa between this pattern and the larger area of fire damage closer to the front door was protected and not exposed to flaming combustion.
-The inside of the sofa's seat frame was charred on the inside but not on the outside in the area in front of this pattern, Figure~\ref{Table}.
+In other words, the basic qualitative requirements of the fire triangle could be met.
+The area of the living room more remote from the front door (the source of oxygen), did not have as much fire damage.
+You remember there was limited fire damage to the wall behind the right side of the sofa.
+This burned area on the wall seemed distinct and disconnected from the area with the most fire damage, which is to the left of the sofa.
+
+You decide to go back into the town house for another look Figure~\ref{Pre_Flashover_Markup}.
+The dark colored fire pattern (inside yellow oval), behind the sofa and above the location of the right seat cushion, had to be generated early in the fire event because it is away from the front door.
+Further, the wall behind the sofa between this pattern and the larger area of fire damage (V pattern between red lines in the left corner) closer to the front door was protected and not exposed to flaming combustion.
+Comparing the views of the sofa frame from Figure~\ref{Pre_Flashover_Markup} and Figure~\ref{Table}, it can be seen that the inside of the sofa's seat frame was charred on the inside but not on the outside in the area in front of this pattern.
+The burning inside the sofa frame may have been the result of the sofa cushion melting, dripping, burning.
 The bottom of the pattern is located near the base of the sofa seat cushion.
@@
 Using Heskestad's flame height equation and solving for the heat release rate based on the pattern height yields a heat release rate on the order of 55~kW.
-Unknowns include the impact of the back portion of the sofa, but this fire size seems reasonable to you with regard to the vision of a sofa cushion burning.
+There are other unknowns (for example the fire contribution of the back portion of the sofa, the impact of the melting, dripping, and burning seat cushion) but this fire size seems reasonable with regard to the vision of a sofa cushion burning early in the fire incident.
 This information, coupled with the sequence of events provided by the fire captain and other fire damage, indicate the right side of the sofa is likely the area of origin even though it does not have the most fire damage.
-You still need to interview the occupants.
+You still need to interview the occupants, to get additional information to examine your hypothesis.
 Was an accidental ignition due to careless smoking possible?
 Or a lithium ion battery powered device?
-Also, you will still check if the heater switch was in the on position.
+Also, you will still want a forensic analysis of the heater switch, was in the on position?
 If not, that further supports your current hypothesis about the right side of the sofa.
@@
 
-If needed, you have the dimensions of the house and the opening so you could have a computer model of the house made to examine how long it would take a small fire to decrease the level of the oxygen within the house to 15\%.
-This might prove necessary to get insight on a time line you might get from the interviews of the occupants.
+If needed, you have taken the dimensions of the house and the openings so you could have a computer model developed to examine how long it would take a small fire to decrease the level of the oxygen within the house to below 15\%.
+This might prove necessary to get insight on the time line you might get from the interviews of the occupants.
 
 \begin{figure}[h]
-	\includegraphics[width=5in]{../Figures/Pre_Flashover_Pattern} \\
-	\caption[Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.]{Photograph showing the wall with the standalone fire pattern toward the right side of the sofa.}
-	\label{Pre_Flashover_Pattern}
+	\includegraphics[width=5in]{../Figures/Pre_Flashover_Markup} \\
+	\caption[Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa.]{Photograph showing the wall with the stand alone fire pattern toward the right side of the sofa (inside yellow oval).
+Note that the wall behind the sofa and to the left of the stand alone fire pattern does not have significant fire damage.
+While, the corner area to the left of the sofa and behind the chair has a V pattern shaped fire pattern}
+	\label{Pre_Flashover_Markup}
 \end{figure}
@@
 N.B.: This section was included to provide a sense of how a fire investigator might use their knowledge of fire behavior, fire patterns, and numerical methods to assist them in following the scientific method.
-Fire investigation requires significantly more than pattern interpretation.
-The totality of facts from the whole situation must gathered to the extent possible, and then after analysis of the evidence, a fire cause may be determined.
+Fire investigation requires significantly more analysis than pattern interpretation.
+The totality of facts from the whole situation must gathered to the extent possible, and then after analysis of the evidence, an area of origin can be located and the fire cause may be determined.
+In some cases, despite a trained investigators best efforts, the cause of the fire may have to be documented as "undetermined".
+In Chapter 1, information was provided about the occupants of the house.
+The investigator must be careful that information about the occupants, or other information not related to evidence at the scene, does not create a cognitive bias.
+
+The photographs used to support this scenario were taken from a fire experiment in an acquired structure.
+The fire was ignited on the right side of the sofa with a small flaming source.
+The ventilation of the structure occurred as described and resulting in the fire patterns as shown.
+
+An improved understanding of the cause and effect relationship between the heat release rate, heat transfer, and the resulting fire damage on simple targets, such as walls, can be used to assess fire damage such as the stand alone, preflashover pattern in this scenario.
+Further validation and an improved understanding of both the capabilities and limitations of numerical methods to recreate fire patterns is needed to assist in hypothesis testing.
+
+This study provides a foundational understanding of the repeatability of pre-flashover patterns, such as the one shown in this fire Investigator's Challenge.
+While the existing numerical methods have been examined with simple source fires in this study and others, further examination is needed with typical first items ignitied, such as a upholstered chair or sofa to understand the applicability and the impact of the compartment.
 
@@
 
+A oxygen consumption calorimeter round robin study should be conducted among the major federal and private laboratories to determine if the conditions that Janssens reported in 2000 still exist, and if so, what is the underlying cause for the measurement discrepancies~\cite{Janssens:2002}.
+This type of study is critical for both the fundamental understanding of the fire behavior of materials as well as the need for quality input data for numerical models.
+
 Pre-flashover experiments in compartments using well-characterized burner fires should be conducted with a broad range of heat release rates, burn durations, and varied burner sizes to determine if the repeatability results from this study can be replicated.
@@
 The structure itself will have an impact on the movement and flow of both fresh air to the fire and containing and channeling the movement of combustion products away from the fire, both of which can affect the development of the fire pattern.
-Post-flashover fires are particularly challenging for fire investigators because the potential is high significant fire damage may be generated remote from the area of origin.
+Post-flashover fires are particularly challenging for fire investigators because the potential is high that significant fire damage may be generated remote from the area of origin.
 
@@
 The patterns were generated from exposure to short duration (300 seconds maximum), well characterized fires.
+The results provide investigators with baseline data on the repeatability of fire patterns under near ideal conditions.
+Applications of analyzing the patterns with existing data from the literature, as well as with a range of numerical methods, demonstrated a number of current limitations and the need for additional research and data to support the application of engineering analysis of fire patterns.
 
@@
 The average peak heat release rate of gasoline had a 95\% confidence limit of $\pm$~30\% and the same value for the polyurethane foam was $\pm$~47\%.
-
-The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have uncertainties of $\pm$ 18\% or less based on a Type A statistical analysis with 95\% confidence limits.
+Therefore applying the HRR uncertainty of the measurement device to numerical method input values is not sufficient, the uncertainty related to the behavior or composition of the fuel must also be taken into consideration.
+
+The fire pattern heights generated on painted gypsum wallboard by the natural gas burner and gasoline fueled fires were shown to have expanded uncertainties with a coverage factor of 2 (i.e.
+95\% confidence limits) of $\pm$ 18\% or less.
 The patterns generated by the polyurethane foam fueled fire had more than twice the variability of the natural gas and the gasoline fire patterns.
-This was likely due to the greater variability of the burning of the solid fuel and the lower heat release rate.
-
+This was likely due to the greater variability of the burning of the solid fuel and the lower heat release rate
 The comparison of the fire pattern heights and the mean flame heights demonstrated that the “steady state” natural gas fires exhibited the highest level of agreement, and polyurethane foam fueled fire exhibited the least agreement, with the gasoline fueled fires in between.
@@
 The models proved useful for gaining insight into fire behavior, but in many cases the models require specific experimental data for input or validation.
-The availability of well-characterized input data is limited, and data for newer materials is unavailable.
+The availability of well-characterized input data is limited, and data for newer materials may be unavailable.
 Additional research is needed for modeling data development protocols.
